---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `relig`
* Variable label: `Any form of religious participation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Cuba 

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w1_relig','10-66.1066-Cuba-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 cuba}
t1066_cuba_w1_relig <- opal.execute(o,'t1066_cuba_w1_relig')
vari <- t1066_cuba_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_cuba_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_relig$id)
t1066_ds_cuba_w1$relig <- car::recode(as.vector(t1066_cuba_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_cuba_w1$relig <- labelled(t1066_ds_cuba_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba}
vari <- t1066_ds_cuba_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba}
AfterH <- table(t1066_ds_cuba_w1$relig)
BeforeH <- table(t1066_cuba_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 

### Wave 2
Not found.

## Dominican Republic

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 DR}
opal.assign.table.tibble(o, 't1066_DR_w1_relig','10-66.1066-DominicanRepublic-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 DR}
t1066_DR_w1_relig <- opal.execute(o,'t1066_DR_w1_relig')
vari <- t1066_DR_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_DR_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_relig$id)
t1066_ds_DR_w1$relig <- car::recode(as.vector(t1066_DR_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_DR_w1$relig <- labelled(t1066_ds_DR_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR}
vari <- t1066_ds_DR_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR}
AfterH <- table(t1066_ds_DR_w1$relig)
BeforeH <- table(t1066_DR_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 


### Wave 2
Not found.

## India
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 india}
opal.assign.table.tibble(o, 't1066_india_w1_relig','10-66.1066-India-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 india}
t1066_india_w1_relig <- opal.execute(o,'t1066_india_w1_relig')
vari <-  t1066_india_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_india_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_relig$id)
t1066_ds_india_w1$relig <- car::recode(as.vector(t1066_india_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_india_w1$relig <- labelled(t1066_ds_india_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india}
vari <- t1066_ds_india_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india}
AfterH <- table(t1066_ds_india_w1$relig)
BeforeH <- table(t1066_india_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 



### Wave 2
Not found.

## Puerto Rico

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 PR}
opal.assign.table.tibble(o, 't1066_PR_w1_relig','10-66.1066-PuertoRico-Baseline', 
                        variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 PR}
t1066_PR_w1_relig <- opal.execute(o,'t1066_PR_w1_relig')
vari <- t1066_PR_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_PR_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 PR, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_relig$id)
t1066_ds_PR_w1$relig <- car::recode(as.vector(t1066_PR_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_PR_w1$relig <- labelled(t1066_ds_PR_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR}
vari <- t1066_ds_PR_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR}
AfterH <- table(t1066_ds_PR_w1$relig)
BeforeH <- table(t1066_PR_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 


### Wave 2
Not found.

## Rural China

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 RCH}
opal.assign.table.tibble(o, 't1066_RCh_w1_relig','10-66.1066-RuralChina-Baseline', 
                        variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 RCH}
t1066_RCh_w1_relig <- opal.execute(o,'t1066_RCh_w1_relig')
vari <- t1066_RCh_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_RCh_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 RCH, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_relig$id)
t1066_ds_RCh_w1$relig <- car::recode(as.vector(t1066_RCh_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_RCh_w1$relig <- labelled(t1066_ds_RCh_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCH}
vari <- t1066_ds_RCh_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCH}
AfterH <- table(t1066_ds_RCh_w1$relig)
BeforeH <- table(t1066_RCh_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 


### Wave 2
Not found.

## Rural Mexico
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 RM}
opal.assign.table.tibble(o, 't1066_RM_w1_relig','10-66.1066-RuralMexico-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 RM}
t1066_RM_w1_relig <- opal.execute(o,'t1066_RM_w1_relig')
vari <- t1066_RM_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_RM_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 RM, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_relig$id)
t1066_ds_RM_w1$relig <- car::recode(as.vector(t1066_RM_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_RM_w1$relig <- labelled(t1066_ds_RM_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RM}
vari <- t1066_ds_RM_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RM}
AfterH <- table(t1066_ds_RM_w1$relig)
BeforeH <- table(t1066_RM_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1")
kable(C)
```

 
 


### Wave 2
Not found.

## Rural Peru
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 RP}
opal.assign.table.tibble(o, 't1066_RP_w1_relig','10-66.1066-RuralPeru-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 RP}
t1066_RP_w1_relig <- opal.execute(o,'t1066_RP_w1_relig')
vari <- t1066_RP_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_RP_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 RP, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_relig$id)
t1066_ds_RP_w1$relig <- car::recode(as.vector(t1066_RP_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_RP_w1$relig <- labelled(t1066_ds_RP_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP}
vari <- t1066_ds_RP_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP}
AfterH <- table(t1066_ds_RP_w1$relig)
BeforeH <- table(t1066_RP_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")

kable(C)
```

 
 

### Wave 2
Not found.

## Urban China

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1 UCH}
opal.assign.table.tibble(o, 't1066_UCh_w1_relig','10-66.1066-UrbanChina-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1 UCH}
t1066_UCh_w1_relig <- opal.execute(o,'t1066_UCh_w1_relig')
vari <- t1066_UCh_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_UCh_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1 UCH, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_relig$id)
t1066_ds_UCh_w1$relig <- car::recode(as.vector(t1066_UCh_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_UCh_w1$relig <- labelled(t1066_ds_UCh_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UCH}
vari <- t1066_ds_UCh_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UCH}
AfterH <- table(t1066_ds_UCh_w1$relig)
BeforeH <- table(t1066_UCh_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1")
kable(C)
```

 
 


### Wave 2
Not found.

## Urban Mexico

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1  UM}
opal.assign.table.tibble(o, 't1066_UM_w1_relig','10-66.1066-UrbanMexico-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1  UM}
t1066_UM_w1_relig <- opal.execute(o,'t1066_UM_w1_relig')
vari <- t1066_UM_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_UM_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1  UM, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_relig$id)
t1066_ds_UM_w1$relig <- car::recode(as.vector(t1066_UM_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_UM_w1$relig <- labelled(t1066_ds_UM_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1  UM}
vari <- t1066_ds_UM_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1  UM}
AfterH <- table(t1066_ds_UM_w1$relig)
BeforeH <- table(t1066_UM_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 


## Urban Peru
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1  UP}
opal.assign.table.tibble(o, 't1066_UP_w1_relig','10-66.1066-UrbanPeru-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1  UP}
t1066_UP_w1_relig <- opal.execute(o,'t1066_UP_w1_relig')
vari <- t1066_UP_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_UP_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1  UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_relig$id)
t1066_ds_UP_w1$relig <- car::recode(as.vector(t1066_UP_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_UP_w1$relig <- labelled(t1066_ds_UP_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1  UP}
vari <- t1066_ds_UP_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1  UP}
AfterH <- table(t1066_ds_UP_w1$relig)
BeforeH <- table(t1066_UP_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 


## Venezuela

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PGOCHCH`
* Label: `Frequency of religious observance`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

* Description: 
```{r assign1  VEN}
opal.assign.table.tibble(o, 't1066_Ven_w1_relig','10-66.1066-Venezuela-Baseline',variables=list('PGOCHCH'), missings = TRUE)
```

```{r local1  VEN}
t1066_Ven_w1_relig <- opal.execute(o,'t1066_Ven_w1_relig')
vari <- t1066_Ven_w1_relig$PGOCHCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_relig$PGOCHCH, missing_values = NA)
ggplot(t1066_Ven_w1_relig, aes(x=factor(PGOCHCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of religious observance") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 or 2(?) into 0`
* `NA into 999`

**R script:**

```{r harmo1  VEN, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_relig$id)
t1066_ds_Ven_w1$relig <- car::recode(as.vector(t1066_Ven_w1_relig$PGOCHCH), "1='1'; 0='0'; 2='0'; NA='999'")
t1066_ds_Ven_w1$relig <- labelled(t1066_ds_Ven_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1  VEN}
vari <- t1066_ds_Ven_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1  VEN}
AfterH <- table(t1066_ds_Ven_w1$relig)
BeforeH <- table(t1066_Ven_w1_relig$PGOCHCH, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,3)])
BeforeH1[[2]] <- BeforeH[[2]]
BeforeH1[[3]] <- BeforeH[[4]]
BeforeH <- BeforeH1
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0&2->0","1->1","NA->999")
kable(C)
```

 
 

### Wave 2
Not found.



```{r save,  echo=FALSE}
relig <- t1066_ds_cuba_w1
save(relig, file = "../RData/cuba_w1/relig.RData")
rm(relig)


relig <- t1066_ds_india_w1
save(relig, file = "../RData/india_w1/relig.RData")
rm(relig)


relig <- t1066_ds_UCh_w1
save(relig, file = "../RData/UCh_w1/relig.RData")
rm(relig)


relig <- t1066_ds_RCh_w1
save(relig, file = "../RData/RCh_w1/relig.RData")
rm(relig)


relig <- t1066_ds_DR_w1
save(relig, file = "../RData/DR_w1/relig.RData")
rm(relig)



relig <- t1066_ds_Ven_w1
save(relig, file = "../RData/Ven_w1/relig.RData")
rm(relig)


relig <- t1066_ds_UP_w1
save(relig, file = "../RData/UP_w1/relig.RData")
rm(relig)



relig <- t1066_ds_RP_w1
save(relig, file = "../RData/RP_w1/relig.RData")
rm(relig)



relig <- t1066_ds_UM_w1
save(relig, file = "../RData/UM_w1/relig.RData")
rm(relig)

relig <- t1066_ds_RM_w1
save(relig, file = "../RData/RM_w1/relig.RData")
rm(relig)


relig <- t1066_ds_PR_w1
save(relig, file = "../RData/PR_w1/relig.RData")
rm(relig)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
