---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process


## Cuba

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assigncuba1, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_part_clubs','10-66.1066-Cuba-Baseline', variables=list('PCLUBS'), missings = TRUE)
```

```{r localcuba1, echo=F}
t1066_cuba_w1_part_clubs <- opal.execute(o,'t1066_cuba_w1_part_clubs')
Categorical_summary(var = t1066_cuba_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_cuba_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmocuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_part_clubs$id)
t1066_ds_cuba_w1$part_clubs <- car::recode(as.vector(t1066_cuba_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_cuba_w1$part_clubs <- labelled(t1066_ds_cuba_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptcuba1, echo=F}
Categorical_summary(var = t1066_ds_cuba_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationcuba1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$part_clubs)
BeforeH <- table(t1066_cuba_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assigncuba2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_part_clubs','10-66.1066-Cuba-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localcuba2, echo=F}
t1066_cuba_w2_part_clubs <- opal.execute(o,'t1066_cuba_w2_part_clubs')
Categorical_summary(var = t1066_cuba_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_cuba_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmocuba2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_part_clubs$id)
t1066_ds_cuba_w2$part_clubs <- car::recode(as.vector(t1066_cuba_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_cuba_w2$part_clubs <- labelled(t1066_ds_cuba_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptcuba2, echo=F}
Categorical_summary(var = t1066_ds_cuba_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationcuba2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$part_clubs)
BeforeH <- table(t1066_cuba_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```




## Dominican Republic

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assigndr1, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_part_clubs','10-66.1066-DominicanRepublic-Baseline', variables=list('PCLUBS'), missings = TRUE)
```

```{r localdr1, echo=F}
t1066_DR_w1_part_clubs <- opal.execute(o,'t1066_DR_w1_part_clubs')
Categorical_summary(var = t1066_DR_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_DR_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmodr1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_part_clubs$id)
t1066_ds_DR_w1$part_clubs <- car::recode(as.vector(t1066_DR_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_DR_w1$part_clubs <- labelled(t1066_ds_DR_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptdr1, echo=F}
Categorical_summary(var = t1066_ds_DR_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationdr1, echo=F}
AfterH <- table(t1066_ds_DR_w1$part_clubs)
BeforeH <- table(t1066_DR_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assigndr2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_part_clubs','10-66.1066-DominicanRepublic-Followup', 
                        variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localdr2, echo=F}
t1066_DR_w2_part_clubs <- opal.execute(o,'t1066_DR_w2_part_clubs')
Categorical_summary(var = t1066_DR_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_DR_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmodr2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_part_clubs$id)
t1066_ds_DR_w2$part_clubs <- car::recode(as.vector(t1066_DR_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_DR_w2$part_clubs <- labelled(t1066_ds_DR_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptdr2, echo=F}
Categorical_summary(var = t1066_ds_DR_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationdr2, echo=F}
AfterH <- table(t1066_ds_DR_w2$part_clubs)
BeforeH <- table(t1066_DR_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignindia1, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_part_clubs','10-66.1066-India-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localindia1, echo=F}
t1066_india_w1_part_clubs <- opal.execute(o,'t1066_india_w1_part_clubs')
Categorical_summary(var = t1066_india_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_india_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoindia1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_part_clubs$id)
t1066_ds_india_w1$part_clubs <- car::recode(as.vector(t1066_india_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_india_w1$part_clubs <- labelled(t1066_ds_india_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptindia1, echo=F}
Categorical_summary(var = t1066_ds_india_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationindia1, echo=F}
AfterH <- table(t1066_ds_india_w1$part_clubs)
BeforeH <- table(t1066_india_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## Puerto Rico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignpr1, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_part_clubs','10-66.1066-PuertoRico-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localpr1, echo=F}
t1066_PR_w1_part_clubs <- opal.execute(o,'t1066_PR_w1_part_clubs')
Categorical_summary(var = t1066_PR_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_PR_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmopr1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_part_clubs$id)
t1066_ds_PR_w1$part_clubs <- car::recode(as.vector(t1066_PR_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_PR_w1$part_clubs <- labelled(t1066_ds_PR_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptpr1, echo=F}
Categorical_summary(var = t1066_ds_PR_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationpr1, echo=F}
AfterH <- table(t1066_ds_PR_w1$part_clubs)
BeforeH <- table(t1066_PR_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignpr2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_part_clubs','10-66.1066-PuertoRico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localpr2, echo=F}
t1066_PR_w2_part_clubs <- opal.execute(o,'t1066_PR_w2_part_clubs')
Categorical_summary(var = t1066_PR_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_PR_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmopr2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_part_clubs$id)
t1066_ds_PR_w2$part_clubs <- car::recode(as.vector(t1066_PR_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_PR_w2$part_clubs <- labelled(t1066_ds_PR_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptpr2, echo=F}
Categorical_summary(var = t1066_ds_PR_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationpr2, echo=F}
AfterH <- table(t1066_ds_PR_w2$part_clubs)
BeforeH <- table(t1066_PR_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```




## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrc1, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_part_clubs','10-66.1066-RuralChina-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localrc1, echo=F}
t1066_RCh_w1_part_clubs <- opal.execute(o,'t1066_RCh_w1_part_clubs')
Categorical_summary(var = t1066_RCh_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_RCh_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorc1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_part_clubs$id)
t1066_ds_RCh_w1$part_clubs <- car::recode(as.vector(t1066_RCh_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RCh_w1$part_clubs <- labelled(t1066_ds_RCh_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrc1, echo=F}
Categorical_summary(var = t1066_ds_RCh_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrc1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$part_clubs)
BeforeH <- table(t1066_RCh_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrc2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_part_clubs','10-66.1066-RuralChina-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localrc2, echo=F}
t1066_RCh_w2_part_clubs <- opal.execute(o,'t1066_RCh_w2_part_clubs')
Categorical_summary(var = t1066_RCh_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_RCh_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorc2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_part_clubs$id)
t1066_ds_RCh_w2$part_clubs <- car::recode(as.vector(t1066_RCh_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RCh_w2$part_clubs <- labelled(t1066_ds_RCh_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrc2, echo=F}
Categorical_summary(var = t1066_ds_RCh_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrc2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$part_clubs)
BeforeH <- table(t1066_RCh_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```






## Rural Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrm1, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_part_clubs','10-66.1066-RuralMexico-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localrm1, echo=F}
t1066_RM_w1_part_clubs <- opal.execute(o,'t1066_RM_w1_part_clubs')
Categorical_summary(var = t1066_RM_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_RM_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorm1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_part_clubs$id)
t1066_ds_RM_w1$part_clubs <- car::recode(as.vector(t1066_RM_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RM_w1$part_clubs <- labelled(t1066_ds_RM_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrm1, echo=F}
Categorical_summary(var = t1066_ds_RM_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrm1, echo=F}
AfterH <- table(t1066_ds_RM_w1$part_clubs)
BeforeH <- table(t1066_RM_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrm2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_part_clubs','10-66.1066-RuralMexico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localrm2, echo=F}
t1066_RM_w2_part_clubs <- opal.execute(o,'t1066_RM_w2_part_clubs')
Categorical_summary(var = t1066_RM_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_RM_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorm2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_part_clubs$id)
t1066_ds_RM_w2$part_clubs <- car::recode(as.vector(t1066_RM_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RM_w2$part_clubs <- labelled(t1066_ds_RM_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrm2, echo=F}
Categorical_summary(var = t1066_ds_RM_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrm2, echo=F}
AfterH <- table(t1066_ds_RM_w2$part_clubs)
BeforeH <- table(t1066_RM_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```




## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrp1, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_part_clubs','10-66.1066-RuralPeru-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localrp1, echo=F}
t1066_RP_w1_part_clubs <- opal.execute(o,'t1066_RP_w1_part_clubs')
Categorical_summary(var = t1066_RP_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_RP_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorp1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_part_clubs$id)
t1066_ds_RP_w1$part_clubs <- car::recode(as.vector(t1066_RP_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RP_w1$part_clubs <- labelled(t1066_ds_RP_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrp1, echo=F}
Categorical_summary(var = t1066_ds_RP_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrp1, echo=F}
AfterH <- table(t1066_ds_RP_w1$part_clubs)
BeforeH <- table(t1066_RP_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignrp2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_part_clubs','10-66.1066-RuralPeru-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localrp2, echo=F}
t1066_RP_w2_part_clubs <- opal.execute(o,'t1066_RP_w2_part_clubs')
Categorical_summary(var = t1066_RP_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_RP_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorp2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_part_clubs$id)
t1066_ds_RP_w2$part_clubs <- car::recode(as.vector(t1066_RP_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RP_w2$part_clubs <- labelled(t1066_ds_RP_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrp2, echo=F}
Categorical_summary(var = t1066_ds_RP_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrp2, echo=F}
AfterH <- table(t1066_ds_RP_w2$part_clubs)
BeforeH <- table(t1066_RP_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





## Urban China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignuc1, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_part_clubs','10-66.1066-UrbanChina-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localuc1, echo=F}
t1066_UCh_w1_part_clubs <- opal.execute(o,'t1066_UCh_w1_part_clubs')
Categorical_summary(var = t1066_UCh_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_UCh_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmouc1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_part_clubs$id)
t1066_ds_UCh_w1$part_clubs <- car::recode(as.vector(t1066_UCh_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UCh_w1$part_clubs <- labelled(t1066_ds_UCh_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptuc1, echo=F}
Categorical_summary(var = t1066_ds_UCh_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationuc1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$part_clubs)
BeforeH <- table(t1066_UCh_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignuc2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_part_clubs','10-66.1066-UrbanChina-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localuc2, echo=F}
t1066_UCh_w2_part_clubs <- opal.execute(o,'t1066_UCh_w2_part_clubs')
Categorical_summary(var = t1066_UCh_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_UCh_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmouc2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_part_clubs$id)
t1066_ds_UCh_w2$part_clubs <- car::recode(as.vector(t1066_UCh_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UCh_w2$part_clubs <- labelled(t1066_ds_UCh_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptuc2, echo=F}
Categorical_summary(var = t1066_ds_UCh_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationuc2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$part_clubs)
BeforeH <- table(t1066_UCh_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





## Urban Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignum1, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_part_clubs','10-66.1066-UrbanMexico-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localum1, echo=F}
t1066_UM_w1_part_clubs <- opal.execute(o,'t1066_UM_w1_part_clubs')
Categorical_summary(var = t1066_UM_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_UM_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoum1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_part_clubs$id)
t1066_ds_UM_w1$part_clubs <- car::recode(as.vector(t1066_UM_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UM_w1$part_clubs <- labelled(t1066_ds_UM_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptum1, echo=F}
Categorical_summary(var = t1066_ds_UM_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationum1, echo=F}
AfterH <- table(t1066_ds_UM_w1$part_clubs)
BeforeH <- table(t1066_UM_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignum2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_part_clubs','10-66.1066-UrbanMexico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localum2, echo=F}
t1066_UM_w2_part_clubs <- opal.execute(o,'t1066_UM_w2_part_clubs')
Categorical_summary(var = t1066_UM_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_UM_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoum2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_part_clubs$id)
t1066_ds_UM_w2$part_clubs <- car::recode(as.vector(t1066_UM_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UM_w2$part_clubs <- labelled(t1066_ds_UM_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptum2, echo=F}
Categorical_summary(var = t1066_ds_UM_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationum2, echo=F}
AfterH <- table(t1066_ds_UM_w2$part_clubs)
BeforeH <- table(t1066_UM_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```




## Urban Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignup1, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_part_clubs','10-66.1066-UrbanPeru-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localup1, echo=F}
t1066_UP_w1_part_clubs <- opal.execute(o,'t1066_UP_w1_part_clubs')
Categorical_summary(var = t1066_UP_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_UP_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoup1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_part_clubs$id)
t1066_ds_UP_w1$part_clubs <- car::recode(as.vector(t1066_UP_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UP_w1$part_clubs <- labelled(t1066_ds_UP_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptup1, echo=F}
Categorical_summary(var = t1066_ds_UP_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationup1, echo=F}
AfterH <- table(t1066_ds_UP_w1$part_clubs)
BeforeH <- table(t1066_UP_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignup2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_part_clubs','10-66.1066-UrbanPeru-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localup2, echo=F}
t1066_UP_w2_part_clubs <- opal.execute(o,'t1066_UP_w2_part_clubs')
Categorical_summary(var = t1066_UP_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_UP_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoup2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_part_clubs$id)
t1066_ds_UP_w2$part_clubs <- car::recode(as.vector(t1066_UP_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UP_w2$part_clubs <- labelled(t1066_ds_UP_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptup2, echo=F}
Categorical_summary(var = t1066_ds_UP_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationup2, echo=F}
AfterH <- table(t1066_ds_UP_w2$part_clubs)
BeforeH <- table(t1066_UP_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```






## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignv1, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_part_clubs','10-66.1066-Venezuela-Baseline',variables=list('PCLUBS'), missings = TRUE)
```

```{r localv1, echo=F}
t1066_Ven_w1_part_clubs <- opal.execute(o,'t1066_Ven_w1_part_clubs')
Categorical_summary(var = t1066_Ven_w1_part_clubs$PCLUBS, missing_values = NA)
ggplot(t1066_Ven_w1_part_clubs, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmov1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_part_clubs$id)
t1066_ds_Ven_w1$part_clubs <- car::recode(as.vector(t1066_Ven_w1_part_clubs$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_Ven_w1$part_clubs <- labelled(t1066_ds_Ven_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptv1, echo=F}
Categorical_summary(var = t1066_ds_Ven_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationv1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$part_clubs)
BeforeH <- table(t1066_Ven_w1_part_clubs$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PCLUBS`
* Label: `Frequency of attending clubs`
* Categories: 
    + `0 = no`
    + `1 = yes, regularly`
    + `2 = yes, occasionally`

```{r assignv2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_part_clubs','10-66.1066-Venezuela-Followup',variables=list('f_PCLUBS'), missings = TRUE)
```

```{r localv2, echo=F}
t1066_Ven_w2_part_clubs <- opal.execute(o,'t1066_Ven_w2_part_clubs')
Categorical_summary(var = t1066_Ven_w2_part_clubs$f_PCLUBS, missing_values = NA)
ggplot(t1066_Ven_w2_part_clubs, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmov2}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_part_clubs$id)
t1066_ds_Ven_w2$part_clubs <- car::recode(as.vector(t1066_Ven_w2_part_clubs$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_Ven_w2$part_clubs <- labelled(t1066_ds_Ven_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptv2, echo=F}
Categorical_summary(var = t1066_ds_Ven_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationv2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$part_clubs)
BeforeH <- table(t1066_Ven_w2_part_clubs$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[13,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[13,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  part_clubs <- lb.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(lb.hds)[index],"/part_clubs.RData"))
}

for(index in seq_along(lf.hds)){
  part_clubs <- lf.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(lf.hds)[index],"/part_clubs.RData"))
}


```
<!-- ########################################################## --> 







# Quality estimation

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
