---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process


## Cuba

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-Cuba-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assigncuba1, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline', variables=list('PCLUBS'), missings = TRUE)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')
```

```{r localcuba1, echo=F}
vbl <- t1066_cuba_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmocuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$part_clubs <- car::recode(as.vector(t1066_cuba_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_cuba_w1$part_clubs <- labelled(t1066_ds_cuba_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptcuba1, echo=F}
vbl <- t1066_ds_cuba_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationcuba1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$part_clubs)
BeforeH <- table(t1066_cuba_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-Cuba-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assigncuba2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
```

```{r localcuba2, echo=F}
vbl <- t1066_cuba_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmocuba2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$part_clubs <- car::recode(as.vector(t1066_cuba_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_cuba_w2$part_clubs <- labelled(t1066_ds_cuba_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptcuba2, echo=F}
vbl <- t1066_ds_cuba_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationcuba2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$part_clubs)
BeforeH <- table(t1066_cuba_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## India

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-India-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignindia1, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')
```

```{r localindia1, echo=F}
vbl <- t1066_india_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoindia1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$part_clubs <- car::recode(as.vector(t1066_india_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_india_w1$part_clubs <- labelled(t1066_ds_india_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptindia1, echo=F}
vbl <- t1066_ds_india_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationindia1, echo=F}
AfterH <- table(t1066_ds_india_w1$part_clubs)
BeforeH <- table(t1066_india_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## Urban China

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanChina-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignuc1, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')
```

```{r localuc1, echo=F}
vbl <- t1066_UCh_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmouc1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$part_clubs <- car::recode(as.vector(t1066_UCh_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UCh_w1$part_clubs <- labelled(t1066_ds_UCh_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptuc1, echo=F}
vbl <- t1066_ds_UCh_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationuc1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$part_clubs)
BeforeH <- table(t1066_UCh_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanChina-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignuc2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
```

```{r localuc2, echo=F}
vbl <- t1066_UCh_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmouc2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$part_clubs <- car::recode(as.vector(t1066_UCh_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UCh_w2$part_clubs <- labelled(t1066_ds_UCh_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptuc2, echo=F}
vbl <- t1066_ds_UCh_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationuc2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$part_clubs)
BeforeH <- table(t1066_UCh_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





## Rural China

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralChina-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrc1, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')
```

```{r localrc1, echo=F}
vbl <- t1066_RCh_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorc1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$part_clubs <- car::recode(as.vector(t1066_RCh_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RCh_w1$part_clubs <- labelled(t1066_ds_RCh_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrc1, echo=F}
vbl <- t1066_ds_RCh_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrc1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$part_clubs)
BeforeH <- table(t1066_RCh_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralChina-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrc2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')
```

```{r localrc2, echo=F}
vbl <- t1066_RCh_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorc2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$part_clubs <- car::recode(as.vector(t1066_RCh_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RCh_w2$part_clubs <- labelled(t1066_ds_RCh_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrc2, echo=F}
vbl <- t1066_ds_RCh_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrc2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$part_clubs)
BeforeH <- table(t1066_RCh_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```







## Dominican Republic

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-DominicanRepublic-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assigndr1, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline', variables=list('PCLUBS'), missings = TRUE)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')
```

```{r localdr1, echo=F}
vbl <- t1066_DR_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmodr1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$part_clubs <- car::recode(as.vector(t1066_DR_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_DR_w1$part_clubs <- labelled(t1066_ds_DR_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptdr1, echo=F}
vbl <- t1066_ds_DR_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationdr1, echo=F}
AfterH <- table(t1066_ds_DR_w1$part_clubs)
BeforeH <- table(t1066_DR_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-DominicanRepublic-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assigndr2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup', variables=list('f_PCLUBS'), missings = TRUE)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
```

```{r localdr2, echo=F}
vbl <- t1066_DR_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmodr2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$part_clubs <- car::recode(as.vector(t1066_DR_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_DR_w2$part_clubs <- labelled(t1066_ds_DR_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptdr2, echo=F}
vbl <- t1066_ds_DR_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationdr2, echo=F}
AfterH <- table(t1066_ds_DR_w2$part_clubs)
BeforeH <- table(t1066_DR_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## Venezuela

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-Venezuela-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignv1, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')
```

```{r localv1, echo=F}
vbl <- t1066_Ven_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmov1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$part_clubs <- car::recode(as.vector(t1066_Ven_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_Ven_w1$part_clubs <- labelled(t1066_ds_Ven_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptv1, echo=F}
vbl <- t1066_ds_Ven_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationv1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$part_clubs)
BeforeH <- table(t1066_Ven_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-Venezuela-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignv2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')
```

```{r localv2, echo=F}
vbl <- t1066_Ven_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmov2}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$part_clubs <- car::recode(as.vector(t1066_Ven_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_Ven_w2$part_clubs <- labelled(t1066_ds_Ven_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptv2, echo=F}
vbl <- t1066_ds_Ven_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationv2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$part_clubs)
BeforeH <- table(t1066_Ven_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```






## Urban Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanMexico-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignum1, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')
```

```{r localum1, echo=F}
vbl <- t1066_UM_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoum1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$part_clubs <- car::recode(as.vector(t1066_UM_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UM_w1$part_clubs <- labelled(t1066_ds_UM_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptum1, echo=F}
vbl <- t1066_ds_UM_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationum1, echo=F}
AfterH <- table(t1066_ds_UM_w1$part_clubs)
BeforeH <- table(t1066_UM_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanMexico-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignum2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')
```

```{r localum2, echo=F}
vbl <- t1066_UM_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoum2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$part_clubs <- car::recode(as.vector(t1066_UM_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UM_w2$part_clubs <- labelled(t1066_ds_UM_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptum2, echo=F}
vbl <- t1066_ds_UM_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationum2, echo=F}
AfterH <- table(t1066_ds_UM_w2$part_clubs)
BeforeH <- table(t1066_UM_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```







## Rural Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralMexico-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrm1, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')
```

```{r localrm1, echo=F}
vbl <- t1066_RM_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorm1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$part_clubs <- car::recode(as.vector(t1066_RM_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RM_w1$part_clubs <- labelled(t1066_ds_RM_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrm1, echo=F}
vbl <- t1066_ds_RM_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrm1, echo=F}
AfterH <- table(t1066_ds_RM_w1$part_clubs)
BeforeH <- table(t1066_RM_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralMexico-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrm2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')
```

```{r localrm2, echo=F}
vbl <- t1066_RM_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorm2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$part_clubs <- car::recode(as.vector(t1066_RM_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RM_w2$part_clubs <- labelled(t1066_ds_RM_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrm2, echo=F}
vbl <- t1066_ds_RM_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrm2, echo=F}
AfterH <- table(t1066_ds_RM_w2$part_clubs)
BeforeH <- table(t1066_RM_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```






## Urban Peru

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanPeru-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignup1, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')
```

```{r localup1, echo=F}
vbl <- t1066_UP_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoup1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$part_clubs <- car::recode(as.vector(t1066_UP_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UP_w1$part_clubs <- labelled(t1066_ds_UP_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptup1, echo=F}
vbl <- t1066_ds_UP_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationup1, echo=F}
AfterH <- table(t1066_ds_UP_w1$part_clubs)
BeforeH <- table(t1066_UP_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-UrbanPeru-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignup2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')
```

```{r localup2, echo=F}
vbl <- t1066_UP_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmoup2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$part_clubs <- car::recode(as.vector(t1066_UP_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_UP_w2$part_clubs <- labelled(t1066_ds_UP_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptup2, echo=F}
vbl <- t1066_ds_UP_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationup2, echo=F}
AfterH <- table(t1066_ds_UP_w2$part_clubs)
BeforeH <- table(t1066_UP_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```






## Rural Peru

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralPeru-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrp1, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')
```

```{r localrp1, echo=F}
vbl <- t1066_RP_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorp1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$part_clubs <- car::recode(as.vector(t1066_RP_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RP_w1$part_clubs <- labelled(t1066_ds_RP_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrp1, echo=F}
vbl <- t1066_ds_RP_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrp1, echo=F}
AfterH <- table(t1066_ds_RP_w1$part_clubs)
BeforeH <- table(t1066_RP_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-RuralPeru-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignrp2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
```

```{r localrp2, echo=F}
vbl <- t1066_RP_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmorp2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$part_clubs <- car::recode(as.vector(t1066_RP_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_RP_w2$part_clubs <- labelled(t1066_ds_RP_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptrp2, echo=F}
vbl <- t1066_ds_RP_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationrp2, echo=F}
AfterH <- table(t1066_ds_RP_w2$part_clubs)
BeforeH <- table(t1066_RP_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1")
kable(C)
```






## Puerto Rico

### Wave 1 

#### Study-specific variable description



| **Name** | `PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-PuertoRico-Baseline`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignpr1, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('PCLUBS'), missings = TRUE)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')
```

```{r localpr1, echo=F}
vbl <- t1066_PR_w1$PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmopr1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$part_clubs <- car::recode(as.vector(t1066_PR_w1$PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_PR_w1$part_clubs <- labelled(t1066_ds_PR_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptpr1, echo=F}
vbl <- t1066_ds_PR_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationpr1, echo=F}
AfterH <- table(t1066_ds_PR_w1$part_clubs)
BeforeH <- table(t1066_PR_w1$PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `f_PCLUBS`|
|-|-|
| **Label** | `Frequency of attending clubs`|
| **Table name** |`1066-PuertoRico-Followup`|
| **Categories** |`0 = no`<br/>`1 = yes, regularly`<br/>`2 = yes, occasionally`|
| **Description** |  |




```{r assignpr2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('f_PCLUBS'), missings = TRUE)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')
```

```{r localpr2, echo=F}
vbl <- t1066_PR_w2$f_PCLUBS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PCLUBS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PCLUBS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of attending clubs") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmopr2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$part_clubs <- car::recode(as.vector(t1066_PR_w2$f_PCLUBS), "1:2='1'; 0='0'; NA='999'")
t1066_ds_PR_w2$part_clubs <- labelled(t1066_ds_PR_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptpr2, echo=F}
vbl <- t1066_ds_PR_w2$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationpr2, echo=F}
AfterH <- table(t1066_ds_PR_w2$part_clubs)
BeforeH <- table(t1066_PR_w2$f_PCLUBS, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[3]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0->0","1:2->1","NA->999")
kable(C)
```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```




# Quality estimation

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
