---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/bereavDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/bereavDS.R')
```


<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_bereav','10-66.1066-Cuba-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 cuba, echo=F}
t1066_cuba_w1_bereav <- opal.execute(o,'t1066_cuba_w1_bereav')
vari <- t1066_cuba_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_cuba_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_bereav$id)
t1066_ds_cuba_w1$bereav <- car::recode(as.vector(t1066_cuba_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_cuba_w1$bereav <- labelled(t1066_ds_cuba_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba, echo=F}
vari <- t1066_ds_cuba_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w1$bereav)
BeforeH <- table(t1066_cuba_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_bereav','10-66.1066-Cuba-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 cuba, echo=F}
t1066_cuba_w2_bereav <- opal.execute(o,'t1066_cuba_w2_bereav')
vari <- t1066_cuba_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_cuba_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 cuba, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_bereav$id)
t1066_ds_cuba_w2$bereav <- car::recode(as.vector(t1066_cuba_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_cuba_w2$bereav <- labelled(t1066_ds_cuba_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba, echo=F}
vari <- t1066_ds_cuba_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w2$bereav)
BeforeH <- table(t1066_cuba_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Dominican Republic
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_bereav','10-66.1066-DominicanRepublic-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 DR, echo=F}
t1066_DR_w1_bereav <- opal.execute(o,'t1066_DR_w1_bereav')
vari <- t1066_DR_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_DR_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_bereav$id)
t1066_ds_DR_w1$bereav <- car::recode(as.vector(t1066_DR_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_DR_w1$bereav <- labelled(t1066_ds_DR_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR, echo=F}
vari <- t1066_ds_DR_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR, echo=F}
AfterH <- table(t1066_ds_DR_w1$bereav)
BeforeH <- table(t1066_DR_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_bereav','10-66.1066-DominicanRepublic-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 DR, echo=F}
t1066_DR_w2_bereav <- opal.execute(o,'t1066_DR_w2_bereav')
vari <- t1066_DR_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_DR_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 DR, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_bereav$id)
t1066_ds_DR_w2$bereav <- car::recode(as.vector(t1066_DR_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_DR_w2$bereav <- labelled(t1066_ds_DR_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 DR, echo=F}
vari <- t1066_ds_DR_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 DR, echo=F}
AfterH <- table(t1066_ds_DR_w2$bereav)
BeforeH <- table(t1066_DR_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 INDIA, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_bereav','10-66.1066-India-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 INDIA, echo=F}
t1066_india_w1_bereav <- opal.execute(o,'t1066_india_w1_bereav')
vari <- t1066_india_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_india_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 INDIA, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_bereav$id)
t1066_ds_india_w1$bereav <- car::recode(as.vector(t1066_india_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_india_w1$bereav <- labelled(t1066_ds_india_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 INDIA, echo=F}
vari <- t1066_ds_india_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 INDIA, echo=F}
AfterH <- table(t1066_ds_india_w1$bereav)
BeforeH <- table(t1066_india_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 

## Puerto Rico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_bereav','10-66.1066-PuertoRico-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 PR, echo=F}
t1066_PR_w1_bereav <- opal.execute(o,'t1066_PR_w1_bereav')
vari <- t1066_PR_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_PR_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 PR, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_bereav$id)
t1066_ds_PR_w1$bereav <- car::recode(as.vector(t1066_PR_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_PR_w1$bereav <- labelled(t1066_ds_PR_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR, echo=F}
vari <- t1066_ds_PR_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR, echo=F}
AfterH <- table(t1066_ds_PR_w1$bereav)
BeforeH <- table(t1066_PR_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_bereav','10-66.1066-PuertoRico-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 PR, echo=F}
t1066_PR_w2_bereav <- opal.execute(o,'t1066_PR_w2_bereav')
vari <- t1066_PR_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_PR_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 PR, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_bereav$id)
t1066_ds_PR_w2$bereav <- car::recode(as.vector(t1066_PR_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_PR_w2$bereav <- labelled(t1066_ds_PR_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 PR, echo=F}
vari <- t1066_ds_PR_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 PR, echo=F}
AfterH <- table(t1066_ds_PR_w2$bereav)
BeforeH <- table(t1066_PR_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Rural China
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 RCH, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_bereav','10-66.1066-RuralChina-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 RCH, echo=F}
t1066_RCh_w1_bereav <- opal.execute(o,'t1066_RCh_w1_bereav')
vari <- t1066_RCh_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_RCh_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 RCH, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_bereav$id)
t1066_ds_RCh_w1$bereav <- car::recode(as.vector(t1066_RCh_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_RCh_w1$bereav <- labelled(t1066_ds_RCh_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCH, echo=F}
vari <- t1066_ds_RCh_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCH, echo=F}
AfterH <- table(t1066_ds_RCh_w1$bereav)
BeforeH <- table(t1066_RCh_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 RCH, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_bereav','10-66.1066-RuralChina-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 RCH, echo=F}
t1066_RCh_w2_bereav <- opal.execute(o,'t1066_RCh_w2_bereav')
vari <- t1066_RCh_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_RCh_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 RCH, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_bereav$id)
t1066_ds_RCh_w2$bereav <- car::recode(as.vector(t1066_RCh_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_RCh_w2$bereav <- labelled(t1066_ds_RCh_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RCH, echo=F}
vari <- t1066_ds_RCh_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RCH, echo=F}
AfterH <- table(t1066_ds_RCh_w2$bereav)
BeforeH <- table(t1066_RCh_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 

## Rural Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 RMEX, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_bereav','10-66.1066-RuralMexico-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 RMEX, echo=F}
t1066_RM_w1_bereav <- opal.execute(o,'t1066_RM_w1_bereav')
vari <- t1066_RM_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_RM_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 RMEX, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_bereav$id)
t1066_ds_RM_w1$bereav <- car::recode(as.vector(t1066_RM_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_RM_w1$bereav <- labelled(t1066_ds_RM_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RMEX, echo=F}
vari <- t1066_ds_RM_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RMEX, echo=F}
AfterH <- table(t1066_ds_RM_w1$bereav)
BeforeH <- table(t1066_RM_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 RMEX, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_bereav','10-66.1066-RuralMexico-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 RMEX, echo=F}
t1066_RM_w2_bereav <- opal.execute(o,'t1066_RM_w2_bereav')
vari <- t1066_RM_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_RM_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 RMEX, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_bereav$id)
t1066_ds_RM_w2$bereav <- car::recode(as.vector(t1066_RM_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_RM_w2$bereav <- labelled(t1066_ds_RM_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RMEX, echo=F}
vari <- t1066_ds_RM_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RMEX, echo=F}
AfterH <- table(t1066_ds_RM_w2$bereav)
BeforeH <- table(t1066_RM_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Rural Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_bereav','10-66.1066-RuralPeru-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 RP, echo=F}
t1066_RP_w1_bereav <- opal.execute(o,'t1066_RP_w1_bereav')
vari <- t1066_RP_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_RP_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 RP, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_bereav$id)
t1066_ds_RP_w1$bereav <- car::recode(as.vector(t1066_RP_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_RP_w1$bereav <- labelled(t1066_ds_RP_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP, echo=F}
vari <- t1066_ds_RP_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP, echo=F}
AfterH <- table(t1066_ds_RP_w1$bereav)
BeforeH <- table(t1066_RP_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_bereav','10-66.1066-RuralPeru-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 RP, echo=F}
t1066_RP_w2_bereav <- opal.execute(o,'t1066_RP_w2_bereav')
vari <- t1066_RP_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_RP_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 RP, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_bereav$id)
t1066_ds_RP_w2$bereav <- car::recode(as.vector(t1066_RP_w2_bereav$f_BEREAVE),"NA='999'")
t1066_ds_RP_w2$bereav <- labelled(t1066_ds_RP_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RP, echo=F}
vari <- t1066_ds_RP_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RP, echo=F}
AfterH <- table(t1066_ds_RP_w2$bereav)
BeforeH <- table(t1066_RP_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Urban China
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 UCH, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_bereav','10-66.1066-UrbanChina-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 UCH, echo=F}
t1066_UCh_w1_bereav <- opal.execute(o,'t1066_UCh_w1_bereav')
vari <- t1066_UCh_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_UCh_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 UCH, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_bereav$id)
t1066_ds_UCh_w1$bereav <- car::recode(as.vector(t1066_UCh_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_UCh_w1$bereav <- labelled(t1066_ds_UCh_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UCH, echo=F}
vari <- t1066_ds_UCh_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UCH, echo=F}
AfterH <- table(t1066_ds_UCh_w1$bereav)
BeforeH <- table(t1066_UCh_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 UCH, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_bereav','10-66.1066-UrbanChina-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 UCH, echo=F}
t1066_UCh_w2_bereav <- opal.execute(o,'t1066_UCh_w2_bereav')
vari <- t1066_UCh_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_UCh_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 UCH, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_bereav$id)
t1066_ds_UCh_w2$bereav <- car::recode(as.vector(t1066_UCh_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_UCh_w2$bereav <- labelled(t1066_ds_UCh_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UCH, echo=F}
vari <- t1066_ds_UCh_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UCH, echo=F}
AfterH <- table(t1066_ds_UCh_w2$bereav)
BeforeH <- table(t1066_UCh_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Urban Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 UMEX, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_bereav','10-66.1066-UrbanMexico-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 UMEX, echo=F}
t1066_UM_w1_bereav <- opal.execute(o,'t1066_UM_w1_bereav')
vari <- t1066_UM_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_UM_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 UMEX, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_bereav$id)
t1066_ds_UM_w1$bereav <- car::recode(as.vector(t1066_UM_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_UM_w1$bereav <- labelled(t1066_ds_UM_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UMEX, echo=F}
vari <- t1066_ds_UM_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UMEX, echo=F}
AfterH <- table(t1066_ds_UM_w1$bereav)
BeforeH <- table(t1066_UM_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 UMEX, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_bereav','10-66.1066-UrbanMexico-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 UMEX, echo=F}
t1066_UM_w2_bereav <- opal.execute(o,'t1066_UM_w2_bereav')
vari <- t1066_UM_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_UM_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 UMEX, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_bereav$id)
t1066_ds_UM_w2$bereav <- car::recode(as.vector(t1066_UM_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_UM_w2$bereav <- labelled(t1066_ds_UM_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UMEX, echo=F}
vari <- t1066_ds_UM_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UMEX, echo=F}
AfterH <- table(t1066_ds_UM_w2$bereav)
BeforeH <- table(t1066_UM_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Urban Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_bereav','10-66.1066-UrbanPeru-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 UP, echo=F}
t1066_UP_w1_bereav <- opal.execute(o,'t1066_UP_w1_bereav')
vari <- t1066_UP_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_UP_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_bereav$id)
t1066_ds_UP_w1$bereav <- car::recode(as.vector(t1066_UP_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_UP_w1$bereav <- labelled(t1066_ds_UP_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UP, echo=F}
vari <- t1066_ds_UP_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UP, echo=F}
AfterH <- table(t1066_ds_UP_w1$bereav)
BeforeH <- table(t1066_UP_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_bereav','10-66.1066-UrbanPeru-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 UP, echo=F}
t1066_UP_w2_bereav <- opal.execute(o,'t1066_UP_w2_bereav')
vari <- t1066_UP_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_UP_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 UP, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_bereav$id)
t1066_ds_UP_w2$bereav <- car::recode(as.vector(t1066_UP_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_UP_w2$bereav <- labelled(t1066_ds_UP_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UP, echo=F}
vari <- t1066_ds_UP_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UP, echo=F}
AfterH <- table(t1066_ds_UP_w2$bereav)
BeforeH <- table(t1066_UP_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`

* Description: 
```{r assign1 VEN, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_bereav','10-66.1066-Venezuela-Baseline',variables=list('BEREAVE'), missings = TRUE)
```

```{r local1 VEN, echo=F}
t1066_Ven_w1_bereav <- opal.execute(o,'t1066_Ven_w1_bereav')
vari <- t1066_Ven_w1_bereav$BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_bereav$BEREAVE, missing_values = NA)
ggplot(t1066_Ven_w1_bereav, aes(x=factor(BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo1 VEN, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_bereav$id)
t1066_ds_Ven_w1$bereav <- car::recode(as.vector(t1066_Ven_w1_bereav$BEREAVE), "NA='999'")
t1066_ds_Ven_w1$bereav <- labelled(t1066_ds_Ven_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 VEN, echo=F}
vari <- t1066_ds_Ven_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 VEN, echo=F}
AfterH <- table(t1066_ds_Ven_w1$bereav)
BeforeH <- table(t1066_Ven_w1_bereav$BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_BEREAVE`
* Label: `bereavement?`
* Categories: 
    + `0.0 = no`
    + `1.0 = yes`
* Description: 
```{r assign2 VEN, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_bereav','10-66.1066-Venezuela-Followup',variables=list('f_BEREAVE'), missings = TRUE)
```

```{r local2 VEN, echo=F}
t1066_Ven_w2_bereav <- opal.execute(o,'t1066_Ven_w2_bereav')
vari <- t1066_Ven_w2_bereav$f_BEREAVE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_bereav$f_BEREAVE, missing_values = NA)
ggplot(t1066_Ven_w2_bereav, aes(x=factor(f_BEREAVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA -> 999 and the rest leave as it is`

 
**R script:**
```{r harmo2 VEN, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_bereav$id)
t1066_ds_Ven_w2$bereav <- car::recode(as.vector(t1066_Ven_w2_bereav$f_BEREAVE), "NA='999'")
t1066_ds_Ven_w2$bereav <- labelled(t1066_ds_Ven_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 VEN, echo=F}
vari <- t1066_ds_Ven_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("bereavement?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 VEN, echo=F}
AfterH <- table(t1066_ds_Ven_w2$bereav)
BeforeH <- table(t1066_Ven_w2_bereav$f_BEREAVE, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[13,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[13,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  bereav <- lb.hds[[index]]
  save(bereav, file = paste0(datafolder,names(lb.hds)[index],"/bereav.RData"))
}

for(index in seq_along(lf.hds)){
  bereav <- lf.hds[[index]]
  save(bereav, file = paste0(datafolder,names(lf.hds)[index],"/bereav.RData"))
}


```
<!-- ########################################################## --> 



# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```