---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```


<!-- ########################################################## --> 

# Data process

## Cuba


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    

* Description: 
```{r assign1 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_divorce','10-66.1066-Cuba-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 cuba, echo=F}
t1066_cuba_w1_divorce <- opal.execute(o,'t1066_cuba_w1_divorce')
vari <-  t1066_cuba_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_cuba_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_divorce$id)
t1066_ds_cuba_w1$divorce <- car::recode(as.vector(t1066_cuba_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_cuba_w1$divorce <- labelled(t1066_ds_cuba_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba, echo=F}
vari <- t1066_ds_cuba_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w1$divorce)
BeforeH <- table(t1066_cuba_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_divorce','10-66.1066-Cuba-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 cuba, echo=F}
t1066_cuba_w2_divorce <- opal.execute(o,'t1066_cuba_w2_divorce')
vari <-  t1066_cuba_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_cuba_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 cuba, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_cuba_w1 (divorce)
# new = t1066_cuba_w2_divorce (f_PMARRY)

t1066_cuba_w2_divorce_2 <- same_indiv(t1066_ds_cuba_w1, t1066_cuba_w2_divorce)
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_divorce_2$id)

t1066_cuba_w2_divorce_2$divorce <- car::recode(as.vector(t1066_cuba_w2_divorce_2$divorce), "NA='-999'")
t1066_cuba_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_cuba_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_cuba_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_cuba_w2_divorce_2[1])){
  if( t1066_cuba_w2_divorce_2$divorce[i] == 1 | t1066_cuba_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_cuba_w2$divorce[i] = 1 }
  else if( t1066_cuba_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_cuba_w2$divorce[i] = 0 }
}

t1066_ds_cuba_w2$divorce <- car::recode(as.vector(t1066_ds_cuba_w2$divorce), "NA='999'")
t1066_ds_cuba_w2$divorce <- labelled(t1066_ds_cuba_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba, echo=F}
vari <- t1066_ds_cuba_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w2$divorce)
BeforeH <- table(t1066_cuba_w2_divorce_2$f_PMARRY, t1066_cuba_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), sum(BeforeH[5,c(1,3)]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Dominican Republic
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_divorce','10-66.1066-DominicanRepublic-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 DR, echo=F}
t1066_DR_w1_divorce <- opal.execute(o,'t1066_DR_w1_divorce')
vari <-  t1066_DR_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_DR_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_divorce$id)
t1066_ds_DR_w1$divorce <- car::recode(as.vector(t1066_DR_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_DR_w1$divorce <- labelled(t1066_ds_DR_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR, echo=F}
vari <- t1066_ds_DR_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR, echo=F}
AfterH <- table(t1066_ds_DR_w1$divorce)
BeforeH <- table(t1066_DR_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_divorce','10-66.1066-DominicanRepublic-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 DR, echo=F}
t1066_DR_w2_divorce <- opal.execute(o,'t1066_DR_w2_divorce')
vari <-  t1066_DR_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_DR_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 DR, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_DR_w1 (divorce)
# new = t1066_DR_w2_divorce (f_PMARRY)

t1066_DR_w2_divorce_2 <- same_indiv(t1066_ds_DR_w1, t1066_DR_w2_divorce)
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_divorce_2$id)

t1066_DR_w2_divorce_2$divorce <- car::recode(as.vector(t1066_DR_w2_divorce_2$divorce), "NA='-999'")
t1066_DR_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_DR_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_DR_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_DR_w2_divorce_2[1])){
  if( t1066_DR_w2_divorce_2$divorce[i] == 1 | t1066_DR_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_DR_w2$divorce[i] = 1 }
  else if( t1066_DR_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_DR_w2$divorce[i] = 0 }
}

t1066_ds_DR_w2$divorce <- car::recode(as.vector(t1066_ds_DR_w2$divorce), "NA='999'")
t1066_ds_DR_w2$divorce <- labelled(t1066_ds_DR_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 DR, echo=F}
vari <- t1066_ds_DR_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 DR, echo=F}
AfterH <- table(t1066_ds_DR_w2$divorce)
BeforeH <- table(t1066_DR_w2_divorce_2$f_PMARRY, t1066_DR_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), sum(BeforeH[5,c(1,3)]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_divorce','10-66.1066-India-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 india, echo=F}
t1066_india_w1_divorce <- opal.execute(o,'t1066_india_w1_divorce')
vari <-  t1066_india_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_india_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_divorce$id)
t1066_ds_india_w1$divorce <- car::recode(as.vector(t1066_india_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_india_w1$divorce <- labelled(t1066_ds_india_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- t1066_ds_india_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}
AfterH <- table(t1066_ds_india_w1$divorce)
BeforeH <- table(t1066_india_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```

## Puerto Rico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_divorce','10-66.1066-PuertoRico-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 PR, echo=F}
t1066_PR_w1_divorce <- opal.execute(o,'t1066_PR_w1_divorce')
vari <-  t1066_PR_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_PR_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 PR, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_divorce$id)
t1066_ds_PR_w1$divorce <- car::recode(as.vector(t1066_PR_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_PR_w1$divorce <- labelled(t1066_ds_PR_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR, echo=F}
vari <- t1066_ds_PR_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR, echo=F}
AfterH <- table(t1066_ds_PR_w1$divorce)
BeforeH <- table(t1066_PR_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_divorce','10-66.1066-PuertoRico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 PR, echo=F}
t1066_PR_w2_divorce <- opal.execute(o,'t1066_PR_w2_divorce')
vari <-  t1066_PR_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_PR_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 PR, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_PR_w1 (divorce)
# new = t1066_PR_w2_divorce (f_PMARRY)

t1066_PR_w2_divorce_2 <- same_indiv(t1066_ds_PR_w1, t1066_PR_w2_divorce)
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_divorce_2$id)

t1066_PR_w2_divorce_2$divorce <- car::recode(as.vector(t1066_PR_w2_divorce_2$divorce), "NA='-999'")
t1066_PR_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_PR_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_PR_w2$divorce <- c(NA)
for(i in 1:dim(t1066_PR_w2_divorce_2[1])){
  if( t1066_PR_w2_divorce_2$divorce[i] == 1 | t1066_PR_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_PR_w2$divorce[i] = 1 }
  else if( t1066_PR_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_PR_w2$divorce[i] = 0 }
}

t1066_ds_PR_w2$divorce <- car::recode(as.vector(t1066_ds_PR_w2$divorce), "NA='999'")
t1066_ds_PR_w2$divorce <- labelled(t1066_ds_PR_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 PR, echo=F}
vari <- t1066_ds_PR_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 PR, echo=F}
AfterH <- table(t1066_ds_PR_w2$divorce)
BeforeH <- table(t1066_PR_w2_divorce_2$f_PMARRY, t1066_PR_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), sum(BeforeH[5,c(1,3)]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_divorce','10-66.1066-RuralChina-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 RCh, echo=F}
t1066_RCh_w1_divorce <- opal.execute(o,'t1066_RCh_w1_divorce')
vari <-  t1066_RCh_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_RCh_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 RCh, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_divorce$id)
t1066_ds_RCh_w1$divorce <- car::recode(as.vector(t1066_RCh_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_RCh_w1$divorce <- labelled(t1066_ds_RCh_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCh, echo=F}
vari <- t1066_ds_RCh_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCh, echo=F}
AfterH <- table(t1066_ds_RCh_w1$divorce)
BeforeH <- table(t1066_RCh_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_divorce','10-66.1066-RuralChina-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 RCh, echo=F}
t1066_RCh_w2_divorce <- opal.execute(o,'t1066_RCh_w2_divorce')
vari <-  t1066_RCh_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_RCh_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 RCh, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_RCh_w1 (divorce)
# new = t1066_RCh_w2_divorce (f_PMARRY)

t1066_RCh_w2_divorce_2 <- same_indiv(t1066_ds_RCh_w1, t1066_RCh_w2_divorce)
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_divorce_2$id)

t1066_RCh_w2_divorce_2$divorce <- car::recode(as.vector(t1066_RCh_w2_divorce_2$divorce), "NA='-999'")
t1066_RCh_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_RCh_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_RCh_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_RCh_w2_divorce_2[1])){
  if( t1066_RCh_w2_divorce_2$divorce[i] == 1 | t1066_RCh_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_RCh_w2$divorce[i] = 1 }
  else if( t1066_RCh_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_RCh_w2$divorce[i] = 0 }
}

t1066_ds_RCh_w2$divorce <- car::recode(as.vector(t1066_ds_RCh_w2$divorce), "NA='999'")
t1066_ds_RCh_w2$divorce <- labelled(t1066_ds_RCh_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RCh, echo=F}
vari <- t1066_ds_RCh_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RCh, echo=F}
AfterH <- table(t1066_ds_RCh_w2$divorce)
BeforeH <- table(t1066_RCh_w2_divorce_2$f_PMARRY, t1066_RCh_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[2,2], BeforeH[4,1])
BeforeH1[[1]] <- sum(BeforeH[c(1,2,3),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

## Rural Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_divorce','10-66.1066-RuralMexico-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 RM, echo=F}
t1066_RM_w1_divorce <- opal.execute(o,'t1066_RM_w1_divorce')
vari <-  t1066_RM_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_RM_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 RM, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_divorce$id)
t1066_ds_RM_w1$divorce <- car::recode(as.vector(t1066_RM_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_RM_w1$divorce <- labelled(t1066_ds_RM_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RM, echo=F}
vari <- t1066_ds_RM_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RM, echo=F}
AfterH <- table(t1066_ds_RM_w1$divorce)
BeforeH <- table(t1066_RM_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_divorce','10-66.1066-RuralMexico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 RM, echo=F}
t1066_RM_w2_divorce <- opal.execute(o,'t1066_RM_w2_divorce')
vari <-  t1066_RM_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_RM_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 RM, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_RM_w1 (divorce)
# new = t1066_RM_w2_divorce (f_PMARRY)

t1066_RM_w2_divorce_2 <- same_indiv(t1066_ds_RM_w1, t1066_RM_w2_divorce)
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_divorce_2$id)

t1066_RM_w2_divorce_2$divorce <- car::recode(as.vector(t1066_RM_w2_divorce_2$divorce), "NA='-999'")
t1066_RM_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_RM_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_RM_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_RM_w2_divorce_2[1])){
  if( t1066_RM_w2_divorce_2$divorce[i] == 1 | t1066_RM_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_RM_w2$divorce[i] = 1 }
  else if( t1066_RM_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_RM_w2$divorce[i] = 0 }
}

t1066_ds_RM_w2$divorce <- car::recode(as.vector(t1066_ds_RM_w2$divorce), "NA='999'")
t1066_ds_RM_w2$divorce <- labelled(t1066_ds_RM_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RM, echo=F}
vari <- t1066_ds_RM_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RM, echo=F}
AfterH <- table(t1066_ds_RM_w2$divorce)
BeforeH <- table(t1066_RM_w2_divorce_2$f_PMARRY, t1066_RM_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), sum(BeforeH[5,c(1,3)]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_divorce','10-66.1066-RuralPeru-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 RP, echo=F}
t1066_RP_w1_divorce <- opal.execute(o,'t1066_RP_w1_divorce')
vari <-  t1066_RP_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_RP_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 RP, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_divorce$id)
t1066_ds_RP_w1$divorce <- car::recode(as.vector(t1066_RP_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_RP_w1$divorce <- labelled(t1066_ds_RP_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP, echo=F}
vari <- t1066_ds_RP_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP, echo=F}
AfterH <- table(t1066_ds_RP_w1$divorce)
BeforeH <- table(t1066_RP_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
``` 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_divorce','10-66.1066-RuralPeru-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 RP, echo=F}
t1066_RP_w2_divorce <- opal.execute(o,'t1066_RP_w2_divorce')
vari <-  t1066_RP_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_RP_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 RP, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_RP_w1 (divorce)
# new = t1066_RP_w2_divorce (f_PMARRY)

t1066_RP_w2_divorce_2 <- same_indiv(t1066_ds_RP_w1, t1066_RP_w2_divorce)
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_divorce_2$id)

t1066_RP_w2_divorce_2$divorce <- car::recode(as.vector(t1066_RP_w2_divorce_2$divorce), "NA='-999'")
t1066_RP_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_RP_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_RP_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_RP_w2_divorce_2[1])){
  if( t1066_RP_w2_divorce_2$divorce[i] == 1 | t1066_RP_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_RP_w2$divorce[i] = 1 }
  else if( t1066_RP_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_RP_w2$divorce[i] = 0 }
}

t1066_ds_RP_w2$divorce <- car::recode(as.vector(t1066_ds_RP_w2$divorce), "NA='999'")
t1066_ds_RP_w2$divorce <- labelled(t1066_ds_RP_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RP, echo=F}
vari <- t1066_ds_RP_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RP, echo=F}
AfterH <- table(t1066_ds_RP_w2$divorce)
BeforeH <- table(t1066_RP_w2_divorce_2$f_PMARRY, t1066_RP_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), BeforeH[4,1])
BeforeH1[[1]] <- sum(BeforeH[c(1,2,3),c(1,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
``` 

## Urban China
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_divorce','10-66.1066-UrbanChina-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 UCh, echo=F}
t1066_UCh_w1_divorce <- opal.execute(o,'t1066_UCh_w1_divorce')
vari <-  t1066_UCh_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_UCh_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 UCh, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_divorce$id)
t1066_ds_UCh_w1$divorce <- car::recode(as.vector(t1066_UCh_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_UCh_w1$divorce <- labelled(t1066_ds_UCh_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UCh, echo=F}
vari <- t1066_ds_UCh_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UCh, echo=F}
AfterH <- table(t1066_ds_UCh_w1$divorce)
BeforeH <- table(t1066_UCh_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1")
kable(C)
``` 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_divorce','10-66.1066-UrbanChina-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 UCh, echo=F}
t1066_UCh_w2_divorce <- opal.execute(o,'t1066_UCh_w2_divorce')
vari <-  t1066_UCh_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_UCh_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 UCh, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_UCh_w1 (divorce)
# new = t1066_UCh_w2_divorce (f_PMARRY)

t1066_UCh_w2_divorce_2 <- same_indiv(t1066_ds_UCh_w1, t1066_UCh_w2_divorce)
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_divorce_2$id)

t1066_UCh_w2_divorce_2$divorce <- car::recode(as.vector(t1066_UCh_w2_divorce_2$divorce), "NA='-999'")
t1066_UCh_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_UCh_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_UCh_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_UCh_w2_divorce_2[1])){
  if( t1066_UCh_w2_divorce_2$divorce[i] == 1 | t1066_UCh_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_UCh_w2$divorce[i] = 1 }
  else if( t1066_UCh_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_UCh_w2$divorce[i] = 0 }
}

t1066_ds_UCh_w2$divorce <- car::recode(as.vector(t1066_ds_UCh_w2$divorce), "NA='999'")
t1066_ds_UCh_w2$divorce <- labelled(t1066_ds_UCh_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UCh, echo=F}
vari <- t1066_ds_UCh_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UCh, echo=F}
AfterH <- table(t1066_ds_UCh_w2$divorce)
BeforeH <- table(t1066_UCh_w2_divorce_2$f_PMARRY, t1066_UCh_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[4,1]
BeforeH1[[1]] <- sum(BeforeH[c(1,2,3),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
``` 

## Urban Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_divorce','10-66.1066-UrbanMexico-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 UM, echo=F}
t1066_UM_w1_divorce <- opal.execute(o,'t1066_UM_w1_divorce')
vari <-  t1066_UM_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_UM_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 UM, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_divorce$id)
t1066_ds_UM_w1$divorce <- car::recode(as.vector(t1066_UM_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_UM_w1$divorce <- labelled(t1066_ds_UM_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UM, echo=F}
vari <- t1066_ds_UM_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UM, echo=F}
AfterH <- table(t1066_ds_UM_w1$divorce)
BeforeH <- table(t1066_UM_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1")
kable(C)
``` 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_divorce','10-66.1066-UrbanMexico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 UM, echo=F}
t1066_UM_w2_divorce <- opal.execute(o,'t1066_UM_w2_divorce')
vari <-  t1066_UM_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_UM_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 UM, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_UM_w1 (divorce)
# new = t1066_UM_w2_divorce (f_PMARRY)

t1066_UM_w2_divorce_2 <- same_indiv(t1066_ds_UM_w1, t1066_UM_w2_divorce)
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_divorce_2$id)

t1066_UM_w2_divorce_2$divorce <- car::recode(as.vector(t1066_UM_w2_divorce_2$divorce), "NA='-999'")
t1066_UM_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_UM_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_UM_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_UM_w2_divorce_2[1])){
  if( t1066_UM_w2_divorce_2$divorce[i] == 1 | t1066_UM_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_UM_w2$divorce[i] = 1 }
  else if( t1066_UM_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_UM_w2$divorce[i] = 0 }
}

t1066_ds_UM_w2$divorce <- car::recode(as.vector(t1066_ds_UM_w2$divorce), "NA='999'")
t1066_ds_UM_w2$divorce <- labelled(t1066_ds_UM_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UM, echo=F}
vari <- t1066_ds_UM_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UM, echo=F}
AfterH <- table(t1066_ds_UM_w2$divorce)
BeforeH <- table(t1066_UM_w2_divorce_2$f_PMARRY, t1066_UM_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), BeforeH[5,1])
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),1])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
``` 

## Urban Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_divorce','10-66.1066-UrbanPeru-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 UP, echo=F}
t1066_UP_w1_divorce <- opal.execute(o,'t1066_UP_w1_divorce')
vari <-  t1066_UP_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_UP_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_divorce$id)
t1066_ds_UP_w1$divorce <- car::recode(as.vector(t1066_UP_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_UP_w1$divorce <- labelled(t1066_ds_UP_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UP, echo=F}
vari <- t1066_ds_UP_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UP, echo=F}
AfterH <- table(t1066_ds_UP_w1$divorce)
BeforeH <- table(t1066_UP_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
``` 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_divorce','10-66.1066-UrbanPeru-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 UP, echo=F}
t1066_UP_w2_divorce <- opal.execute(o,'t1066_UP_w2_divorce')
vari <-  t1066_UP_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_UP_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 UP, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_UP_w1 (divorce)
# new = t1066_UP_w2_divorce (f_PMARRY)

t1066_UP_w2_divorce_2 <- same_indiv(t1066_ds_UP_w1, t1066_UP_w2_divorce)
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_divorce_2$id)

t1066_UP_w2_divorce_2$divorce <- car::recode(as.vector(t1066_UP_w2_divorce_2$divorce), "NA='-999'")
t1066_UP_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_UP_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_UP_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_UP_w2_divorce_2[1])){
  if( t1066_UP_w2_divorce_2$divorce[i] == 1 | t1066_UP_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_UP_w2$divorce[i] = 1 }
  else if( t1066_UP_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_UP_w2$divorce[i] = 0 }
}

t1066_ds_UP_w2$divorce <- car::recode(as.vector(t1066_ds_UP_w2$divorce), "NA='999'")
t1066_ds_UP_w2$divorce <- labelled(t1066_ds_UP_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UP, echo=F}
vari <- t1066_ds_UP_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UP, echo=F}
AfterH <- table(t1066_ds_UP_w2$divorce)
BeforeH <- table(t1066_UP_w2_divorce_2$f_PMARRY, t1066_UP_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[4,c(1,3)]), sum(BeforeH[,2]))
BeforeH1[[1]] <- sum(BeforeH[c(1,2,3),c(1,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
``` 

## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r assign1 Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_divorce','10-66.1066-Venezuela-Baseline',variables=list('PMARRY'), missings = TRUE)
```

```{r local1 Ven, echo=F}
t1066_Ven_w1_divorce <- opal.execute(o,'t1066_Ven_w1_divorce')
vari <-  t1066_Ven_w1_divorce$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_divorce$PMARRY, missing_values = NA)
ggplot(t1066_Ven_w1_divorce, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1 Ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_divorce$id)
t1066_ds_Ven_w1$divorce <- car::recode(as.vector(t1066_Ven_w1_divorce$PMARRY), "1:3='0'; 4='1'; NA='999'")
t1066_ds_Ven_w1$divorce <- labelled(t1066_ds_Ven_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 Ven, echo=F}
vari <- t1066_ds_Ven_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 Ven, echo=F}
AfterH <- table(t1066_ds_Ven_w1$divorce)
BeforeH <- table(t1066_Ven_w1_divorce$PMARRY, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
``` 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
*We also use harmonized variable divorce from the previous wave*


* Description: 
```{r assign2 Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_divorce','10-66.1066-Venezuela-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r local2 Ven, echo=F}
t1066_Ven_w2_divorce <- opal.execute(o,'t1066_Ven_w2_divorce')
vari <-  t1066_Ven_w2_divorce$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_divorce$f_PMARRY, missing_values = NA)
ggplot(t1066_Ven_w2_divorce, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then recode into 1`
* `f_PMARRY=4 into 1`
* `f_PMARRY in {1,2,3} into 0`
* `NA into 999`

**R script:**

```{r harmo2 Ven, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, f_PMARRY=new$f_PMARRY, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = t1066_ds_Ven_w1 (divorce)
# new = t1066_Ven_w2_divorce (f_PMARRY)

t1066_Ven_w2_divorce_2 <- same_indiv(t1066_ds_Ven_w1, t1066_Ven_w2_divorce)
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_divorce_2$id)

t1066_Ven_w2_divorce_2$divorce <- car::recode(as.vector(t1066_Ven_w2_divorce_2$divorce), "NA='-999'")
t1066_Ven_w2_divorce_2$f_PMARRY <- car::recode(as.vector(t1066_Ven_w2_divorce_2$f_PMARRY), "NA='-999'")

t1066_ds_Ven_w2$divorce <- c(NA)   
for(i in 1:dim(t1066_Ven_w2_divorce_2[1])){
  if( t1066_Ven_w2_divorce_2$divorce[i] == 1 | t1066_Ven_w2_divorce_2$f_PMARRY[i] == 4 ) { t1066_ds_Ven_w2$divorce[i] = 1 }
  else if( t1066_Ven_w2_divorce_2$f_PMARRY[i] %in% c(1,2,3) ) { t1066_ds_Ven_w2$divorce[i] = 0 }
}

t1066_ds_Ven_w2$divorce <- car::recode(as.vector(t1066_ds_Ven_w2$divorce), "NA='999'")
t1066_ds_Ven_w2$divorce <- labelled(t1066_ds_Ven_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 Ven, echo=F}
vari <- t1066_ds_Ven_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 Ven, echo=F}
AfterH <- table(t1066_ds_Ven_w2$divorce)
BeforeH <- table(t1066_Ven_w2_divorce_2$f_PMARRY, t1066_Ven_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[,2]), sum(BeforeH[5,c(1,3)]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,4),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```







## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[13,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[13,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```





```{r save,  echo=FALSE}
divorce <- t1066_ds_cuba_w1
save(divorce, file = "../RData/cuba_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_cuba_w2
save(divorce, file = "../RData/cuba_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_india_w1
save(divorce, file = "../RData/india_w1/divorce.RData")
rm(divorce)


divorce <- t1066_ds_UCh_w1
save(divorce, file = "../RData/UCh_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_UCh_w2
save(divorce, file = "../RData/UCh_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RCh_w1
save(divorce, file = "../RData/RCh_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RCh_w2
save(divorce, file = "../RData/RCh_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_DR_w1
save(divorce, file = "../RData/DR_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_DR_w2
save(divorce, file = "../RData/DR_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_Ven_w1
save(divorce, file = "../RData/Ven_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_Ven_w2
save(divorce, file = "../RData/Ven_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_UP_w1
save(divorce, file = "../RData/UP_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_UP_w2
save(divorce, file = "../RData/UP_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RP_w1
save(divorce, file = "../RData/RP_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RP_w2
save(divorce, file = "../RData/RP_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_UM_w1
save(divorce, file = "../RData/UM_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_UM_w2
save(divorce, file = "../RData/UM_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RM_w1
save(divorce, file = "../RData/RM_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_RM_w2
save(divorce, file = "../RData/RM_w2/divorce.RData")
rm(divorce)

divorce <- t1066_ds_PR_w1
save(divorce, file = "../RData/PR_w1/divorce.RData")
rm(divorce)

divorce <- t1066_ds_PR_w2
save(divorce, file = "../RData/PR_w2/divorce.RData")
rm(divorce)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
