---
title: "Ever experienced financial problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `fin_prob`
* Variable label: `Ever experienced financial problems?`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Cuba
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w1_fin_prob','10-66.1066-Cuba-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 cuba}
t1066_cuba_w1_fin_prob <- opal.execute(o,'t1066_cuba_w1_fin_prob')
vari <- t1066_cuba_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_cuba_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_fin_prob$id)
t1066_ds_cuba_w1$fin_prob <- car::recode(as.vector(t1066_cuba_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_cuba_w1$fin_prob <- labelled(t1066_ds_cuba_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba}
vari <- t1066_ds_cuba_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba}
AfterH <- table(t1066_ds_cuba_w1$fin_prob)
BeforeH <- table(t1066_cuba_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w2_fin_prob','10-66.1066-Cuba-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 cuba}
t1066_cuba_w2_fin_prob <- opal.execute(o,'t1066_cuba_w2_fin_prob')
vari <- t1066_cuba_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_cuba_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 cuba, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_fin_prob$id)
t1066_ds_cuba_w2$fin_prob <- car::recode(as.vector(t1066_cuba_w2_fin_prob$f_ZB15), "c(0,1)='0'; c(2,3,4)='1'; NA='999'")
t1066_ds_cuba_w2$fin_prob <- labelled(t1066_ds_cuba_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba}
vari <- t1066_ds_cuba_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba}
AfterH <- table(t1066_ds_cuba_w2$fin_prob)
BeforeH <- table(t1066_cuba_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Dominican Republic

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 dr}
opal.assign.table.tibble(o, 't1066_DR_w1_fin_prob','10-66.1066-DominicanRepublic-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 dr}
t1066_DR_w1_fin_prob <- opal.execute(o,'t1066_DR_w1_fin_prob')
vari <- t1066_DR_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_DR_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 dr, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_fin_prob$id)
t1066_ds_DR_w1$fin_prob <- car::recode(as.vector(t1066_DR_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_DR_w1$fin_prob <- labelled(t1066_ds_DR_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 dr}
vari <- t1066_ds_DR_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 dr}
AfterH <- table(t1066_ds_DR_w1$fin_prob)
BeforeH <- table(t1066_DR_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 dr}
opal.assign.table.tibble(o, 't1066_DR_w2_fin_prob','10-66.1066-DominicanRepublic-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 dr}
t1066_DR_w2_fin_prob <- opal.execute(o,'t1066_DR_w2_fin_prob')
vari <- t1066_DR_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_DR_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 dr, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_fin_prob$id)
t1066_ds_DR_w2$fin_prob <- car::recode(as.vector(t1066_DR_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_DR_w2$fin_prob <- labelled(t1066_ds_DR_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 dr}
vari <- t1066_ds_DR_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 dr}
AfterH <- table(t1066_ds_DR_w2$fin_prob)
BeforeH <- table(t1066_DR_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## India
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 india}
opal.assign.table.tibble(o, 't1066_india_w1_fin_prob','10-66.1066-India-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 india}
t1066_india_w1_fin_prob <- opal.execute(o,'t1066_india_w1_fin_prob')
vari <- t1066_india_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_india_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_fin_prob$id)
t1066_ds_india_w1$fin_prob <- car::recode(as.vector(t1066_india_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_india_w1$fin_prob <- labelled(t1066_ds_india_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india}
vari <- t1066_ds_india_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india}
AfterH <- table(t1066_ds_india_w1$fin_prob)
BeforeH <- table(t1066_india_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


## Puerto Rico

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 pr}
opal.assign.table.tibble(o, 't1066_PR_w1_fin_prob','10-66.1066-PuertoRico-Baseline', 
                        variables=list('ZB15'), missings = TRUE)
```

```{r local1 pr}
t1066_PR_w1_fin_prob <- opal.execute(o,'t1066_PR_w1_fin_prob')
vari <- t1066_PR_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_PR_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 pr, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_fin_prob$id)
t1066_ds_PR_w1$fin_prob <- car::recode(as.vector(t1066_PR_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_PR_w1$fin_prob <- labelled(t1066_ds_PR_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pr}
vari <- t1066_ds_PR_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pr}
AfterH <- table(t1066_ds_PR_w1$fin_prob)
BeforeH <- table(t1066_PR_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 pr}
opal.assign.table.tibble(o, 't1066_PR_w2_fin_prob','10-66.1066-PuertoRico-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 pr}
t1066_PR_w2_fin_prob <- opal.execute(o,'t1066_PR_w2_fin_prob')
vari <- t1066_PR_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_PR_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 pr, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_fin_prob$id)
t1066_ds_PR_w2$fin_prob <- car::recode(as.vector(t1066_PR_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_PR_w2$fin_prob <- labelled(t1066_ds_PR_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pr}
vari <- t1066_ds_PR_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pr}
AfterH <- table(t1066_ds_PR_w2$fin_prob)
BeforeH <- table(t1066_PR_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Rural China

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 rch}
opal.assign.table.tibble(o, 't1066_RCh_w1_fin_prob','10-66.1066-RuralChina-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 rch}
t1066_RCh_w1_fin_prob <- opal.execute(o,'t1066_RCh_w1_fin_prob')
vari <- t1066_RCh_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_RCh_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 rch, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_fin_prob$id)
t1066_ds_RCh_w1$fin_prob <- car::recode(as.vector(t1066_RCh_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RCh_w1$fin_prob <- labelled(t1066_ds_RCh_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rch}
vari <- t1066_ds_RCh_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rch}
AfterH <- table(t1066_ds_RCh_w1$fin_prob)
BeforeH <- table(t1066_RCh_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 rch}
opal.assign.table.tibble(o, 't1066_RCh_w2_fin_prob','10-66.1066-RuralChina-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 rch}
t1066_RCh_w2_fin_prob <- opal.execute(o,'t1066_RCh_w2_fin_prob')
vari <- t1066_RCh_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_RCh_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 rch, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_fin_prob$id)
t1066_ds_RCh_w2$fin_prob <- car::recode(as.vector(t1066_RCh_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RCh_w2$fin_prob <- labelled(t1066_ds_RCh_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rch}
vari <- t1066_ds_RCh_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rch}
AfterH <- table(t1066_ds_RCh_w2$fin_prob)
BeforeH <- table(t1066_RCh_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Rural Mexico
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 rm}
opal.assign.table.tibble(o, 't1066_RM_w1_fin_prob','10-66.1066-RuralMexico-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 rm}
t1066_RM_w1_fin_prob <- opal.execute(o,'t1066_RM_w1_fin_prob')
vari <- t1066_RM_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_RM_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 rm, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_fin_prob$id)
t1066_ds_RM_w1$fin_prob <- car::recode(as.vector(t1066_RM_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RM_w1$fin_prob <- labelled(t1066_ds_RM_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rm}
vari <- t1066_ds_RM_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rm}
AfterH <- table(t1066_ds_RM_w1$fin_prob)
BeforeH <- table(t1066_RM_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 rm}
opal.assign.table.tibble(o, 't1066_RM_w2_fin_prob','10-66.1066-RuralMexico-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 rm}
t1066_RM_w2_fin_prob <- opal.execute(o,'t1066_RM_w2_fin_prob')
vari <- t1066_RM_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_RM_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 rm, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_fin_prob$id)
t1066_ds_RM_w2$fin_prob <- car::recode(as.vector(t1066_RM_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RM_w2$fin_prob <- labelled(t1066_ds_RM_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rm}
vari <- t1066_ds_RM_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rm}
AfterH <- table(t1066_ds_RM_w2$fin_prob)
BeforeH <- table(t1066_RM_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Rural Peru
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 rp}
opal.assign.table.tibble(o, 't1066_RP_w1_fin_prob','10-66.1066-RuralPeru-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 rp}
t1066_RP_w1_fin_prob <- opal.execute(o,'t1066_RP_w1_fin_prob')
vari <- t1066_RP_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_RP_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 rp, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_fin_prob$id)
t1066_ds_RP_w1$fin_prob <- car::recode(as.vector(t1066_RP_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RP_w1$fin_prob <- labelled(t1066_ds_RP_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rp}
vari <- t1066_ds_RP_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rp}
AfterH <- table(t1066_ds_RP_w1$fin_prob)
BeforeH <- table(t1066_RP_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 rp}
opal.assign.table.tibble(o, 't1066_RP_w2_fin_prob','10-66.1066-RuralPeru-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 rp}
t1066_RP_w2_fin_prob <- opal.execute(o,'t1066_RP_w2_fin_prob')
vari <- t1066_RP_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_RP_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 rp, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_fin_prob$id)
t1066_ds_RP_w2$fin_prob <- car::recode(as.vector(t1066_RP_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_RP_w2$fin_prob <- labelled(t1066_ds_RP_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rp}
vari <- t1066_ds_RP_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rp}
AfterH <- table(t1066_ds_RP_w2$fin_prob)
BeforeH <- table(t1066_RP_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Urban China
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 uch}
opal.assign.table.tibble(o, 't1066_UCh_w1_fin_prob','10-66.1066-UrbanChina-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 uch}
t1066_UCh_w1_fin_prob <- opal.execute(o,'t1066_UCh_w1_fin_prob')
vari <- t1066_UCh_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_UCh_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 uch, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_fin_prob$id)
t1066_ds_UCh_w1$fin_prob <- car::recode(as.vector(t1066_UCh_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UCh_w1$fin_prob <- labelled(t1066_ds_UCh_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 uch}
vari <- t1066_ds_UCh_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 uch}
AfterH <- table(t1066_ds_UCh_w1$fin_prob)
BeforeH <- table(t1066_UCh_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 uch}
opal.assign.table.tibble(o, 't1066_UCh_w2_fin_prob','10-66.1066-UrbanChina-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 uch}
t1066_UCh_w2_fin_prob <- opal.execute(o,'t1066_UCh_w2_fin_prob')
vari <- t1066_UCh_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_UCh_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 uch, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_fin_prob$id)
t1066_ds_UCh_w2$fin_prob <- car::recode(as.vector(t1066_UCh_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UCh_w2$fin_prob <- labelled(t1066_ds_UCh_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 uch}
vari <- t1066_ds_UCh_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 uch}
AfterH <- table(t1066_ds_UCh_w2$fin_prob)
BeforeH <- table(t1066_UCh_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Urban Mexico

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 um}
opal.assign.table.tibble(o, 't1066_UM_w1_fin_prob','10-66.1066-UrbanMexico-Baseline', variables=list('ZB15'), missings = TRUE)
```

```{r local1 um}
t1066_UM_w1_fin_prob <- opal.execute(o,'t1066_UM_w1_fin_prob')
vari <- t1066_UM_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_UM_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 um, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_fin_prob$id)
t1066_ds_UM_w1$fin_prob <- car::recode(as.vector(t1066_UM_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UM_w1$fin_prob <- labelled(t1066_ds_UM_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 um}
vari <- t1066_ds_UM_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 um}
AfterH <- table(t1066_ds_UM_w1$fin_prob)
BeforeH <- table(t1066_UM_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 um}
opal.assign.table.tibble(o, 't1066_UM_w2_fin_prob','10-66.1066-UrbanMexico-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 um}
t1066_UM_w2_fin_prob <- opal.execute(o,'t1066_UM_w2_fin_prob')
vari <- t1066_UM_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_UM_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 um, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_fin_prob$id)
t1066_ds_UM_w2$fin_prob <- car::recode(as.vector(t1066_UM_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UM_w2$fin_prob <- labelled(t1066_ds_UM_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 um}
vari <- t1066_ds_UM_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 um}
AfterH <- table(t1066_ds_UM_w2$fin_prob)
BeforeH <- table(t1066_UM_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


## Urban Peru
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 up}
opal.assign.table.tibble(o, 't1066_UP_w1_fin_prob','10-66.1066-UrbanPeru-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 up}
t1066_UP_w1_fin_prob <- opal.execute(o,'t1066_UP_w1_fin_prob')
vari <- t1066_UP_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_UP_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 up, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_fin_prob$id)
t1066_ds_UP_w1$fin_prob <- car::recode(as.vector(t1066_UP_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UP_w1$fin_prob <- labelled(t1066_ds_UP_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 up}
vari <- t1066_ds_UP_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 up}
AfterH <- table(t1066_ds_UP_w1$fin_prob)
BeforeH <- table(t1066_UP_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 up}
opal.assign.table.tibble(o, 't1066_UP_w2_fin_prob','10-66.1066-UrbanPeru-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 up}
t1066_UP_w2_fin_prob <- opal.execute(o,'t1066_UP_w2_fin_prob')
vari <- t1066_UP_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_UP_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 up, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_fin_prob$id)
t1066_ds_UP_w2$fin_prob <- car::recode(as.vector(t1066_UP_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_UP_w2$fin_prob <- labelled(t1066_ds_UP_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 up}
vari <- t1066_ds_UP_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 up}
AfterH <- table(t1066_ds_UP_w2$fin_prob)
BeforeH <- table(t1066_UP_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

## Venezuela

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign1 ven}
opal.assign.table.tibble(o, 't1066_Ven_w1_fin_prob','10-66.1066-Venezuela-Baseline',variables=list('ZB15'), missings = TRUE)
```

```{r local1 ven}
t1066_Ven_w1_fin_prob <- opal.execute(o,'t1066_Ven_w1_fin_prob')
vari <- t1066_Ven_w1_fin_prob$ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_fin_prob$ZB15, missing_values = NA)
ggplot(t1066_Ven_w1_fin_prob, aes(x=factor(ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo1 ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_fin_prob$id)
t1066_ds_Ven_w1$fin_prob <- car::recode(as.vector(t1066_Ven_w1_fin_prob$ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_Ven_w1$fin_prob <- labelled(t1066_ds_Ven_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ven}
vari <- t1066_ds_Ven_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ven}
AfterH <- table(t1066_ds_Ven_w1$fin_prob)
BeforeH <- table(t1066_Ven_w1_fin_prob$ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_ZB15`
* Label: `ZB15 - financial stress`
* Categories: 
    + `0 = never`
    + `1 = rarely`
    + `2 = sometimes`
    + `3 = quite frequently`
    + `4 = nearly always`

* Description: 
```{r assign2 ven}
opal.assign.table.tibble(o, 't1066_Ven_w2_fin_prob','10-66.1066-Venezuela-Followup',variables=list('f_ZB15'), missings = TRUE)
```

```{r local2 ven}
t1066_Ven_w2_fin_prob <- opal.execute(o,'t1066_Ven_w2_fin_prob')
vari <- t1066_Ven_w2_fin_prob$f_ZB15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_fin_prob$f_ZB15, missing_values = NA)
ggplot(t1066_Ven_w2_fin_prob, aes(x=factor(f_ZB15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ZB15 - financial stress") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `0,1 into 0`
* `NA into 999`

**R script:**

```{r harmo2 ven, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_fin_prob$id)
t1066_ds_Ven_w2$fin_prob <- car::recode(as.vector(t1066_Ven_w2_fin_prob$f_ZB15), "2:4='1'; 0:1='0'; NA='999'")
t1066_ds_Ven_w2$fin_prob <- labelled(t1066_ds_Ven_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 ven}
vari <- t1066_ds_Ven_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 ven}
AfterH <- table(t1066_ds_Ven_w2$fin_prob)
BeforeH <- table(t1066_Ven_w2_fin_prob$f_ZB15, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0:1->0","2:4->1","NA->999")
kable(C)
```

```{r save,  echo=FALSE }
fin_prob <- t1066_ds_cuba_w1
save(fin_prob, file = "../RData/cuba_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_cuba_w2
save(fin_prob, file = "../RData/cuba_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_india_w1
save(fin_prob, file = "../RData/india_w1/fin_prob.RData")
rm(fin_prob)


fin_prob <- t1066_ds_UCh_w1
save(fin_prob, file = "../RData/UCh_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_UCh_w2
save(fin_prob, file = "../RData/UCh_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RCh_w1
save(fin_prob, file = "../RData/RCh_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RCh_w2
save(fin_prob, file = "../RData/RCh_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_DR_w1
save(fin_prob, file = "../RData/DR_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_DR_w2
save(fin_prob, file = "../RData/DR_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_Ven_w1
save(fin_prob, file = "../RData/Ven_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_Ven_w2
save(fin_prob, file = "../RData/Ven_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_UP_w1
save(fin_prob, file = "../RData/UP_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_UP_w2
save(fin_prob, file = "../RData/UP_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RP_w1
save(fin_prob, file = "../RData/RP_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RP_w2
save(fin_prob, file = "../RData/RP_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_UM_w1
save(fin_prob, file = "../RData/UM_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_UM_w2
save(fin_prob, file = "../RData/UM_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RM_w1
save(fin_prob, file = "../RData/RM_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_RM_w2
save(fin_prob, file = "../RData/RM_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_PR_w1
save(fin_prob, file = "../RData/PR_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- t1066_ds_PR_w2
save(fin_prob, file = "../RData/PR_w2/fin_prob.RData")
rm(fin_prob)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
