---
title: "Felt loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `loneliness`
* Variable label: `felt loneliness?`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w1_loneliness','10-66.1066-Cuba-Baseline',variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 cuba}
t1066_cuba_w1_loneliness <- opal.execute(o,'t1066_cuba_w1_loneliness')

vari <-  t1066_cuba_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_cuba_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <-t1066_cuba_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_cuba_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <-  t1066_cuba_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_cuba_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_loneliness$id)

t1066_cuba_w1_loneliness$Q871 <- car::recode(as.vector(t1066_cuba_w1_loneliness$Q871), "NA='-999'")
t1066_cuba_w1_loneliness$Q881 <- car::recode(as.vector(t1066_cuba_w1_loneliness$Q881), "NA='-999'")
t1066_cuba_w1_loneliness$Q882 <- car::recode(as.vector(t1066_cuba_w1_loneliness$Q882), "NA='-999'")

t1066_ds_cuba_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_cuba_w1_loneliness)[1]){
  if( t1066_cuba_w1_loneliness$Q871[i] %in% c(1,2) | t1066_cuba_w1_loneliness$Q881[i] == 1 | t1066_cuba_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_cuba_w1$loneliness[i] = 1 }
  else if( t1066_cuba_w1_loneliness$Q871[i] == 0 & t1066_cuba_w1_loneliness$Q881[i] == 0 & t1066_cuba_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_cuba_w1$loneliness[i] = 0 }
  else if(  t1066_cuba_w1_loneliness$Q871[i] == 8 | t1066_cuba_w1_loneliness$Q881[i] == 8 | t1066_cuba_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_cuba_w1$loneliness[i] = 995 }
  else if( t1066_cuba_w1_loneliness$Q871[i] == 9 | t1066_cuba_w1_loneliness$Q881[i] == 9 | t1066_cuba_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_cuba_w1$loneliness[i] = 999 }
}

t1066_ds_cuba_w1$loneliness <- car::recode(as.vector(t1066_ds_cuba_w1$loneliness), "NA='999'")
t1066_ds_cuba_w1$loneliness <- labelled(t1066_ds_cuba_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba}
vari <- t1066_ds_cuba_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w2_loneliness','10-66.1066-Cuba-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 cuba}
t1066_cuba_w2_loneliness <- opal.execute(o,'t1066_cuba_w2_loneliness')

vari <- t1066_cuba_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_cuba_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_cuba_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_cuba_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_cuba_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_cuba_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_cuba_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 cuba, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_loneliness$id)

t1066_cuba_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_cuba_w2_loneliness$f_Q871), "NA='-999'")
t1066_cuba_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_cuba_w2_loneliness$f_Q881), "NA='-999'")
t1066_cuba_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_cuba_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_cuba_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_cuba_w2_loneliness)[1]){
  if( t1066_cuba_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_cuba_w2_loneliness$f_Q881[i] == 1 | t1066_cuba_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_cuba_w2$loneliness[i] = 1 }
  else if( t1066_cuba_w2_loneliness$f_Q871[i] == 0 & t1066_cuba_w2_loneliness$f_Q881[i] == 0 & t1066_cuba_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_cuba_w2$loneliness[i] = 0 }
  else if(  t1066_cuba_w2_loneliness$f_Q871[i] == 8 | t1066_cuba_w2_loneliness$f_Q881[i] == 8 | t1066_cuba_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_cuba_w2$loneliness[i] = 995 }
  else if( t1066_cuba_w2_loneliness$f_Q871[i] == 9 | t1066_cuba_w2_loneliness$f_Q881[i] == 9 | t1066_cuba_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_cuba_w2$loneliness[i] = 999 }
}

t1066_ds_cuba_w2$loneliness <- car::recode(as.vector(t1066_ds_cuba_w2$loneliness), "NA='999'")
t1066_ds_cuba_w2$loneliness <- labelled(t1066_ds_cuba_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba}
vari <- t1066_ds_cuba_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba}

```

## Dominican Republic

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 dr}
opal.assign.table.tibble(o, 't1066_DR_w1_loneliness','10-66.1066-DominicanRepublic-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 dr}
t1066_DR_w1_loneliness <- opal.execute(o,'t1066_DR_w1_loneliness')

vari <- t1066_DR_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_DR_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_DR_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_DR_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_DR_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_DR_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 dr, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_loneliness$id)

t1066_DR_w1_loneliness$Q871 <- car::recode(as.vector(t1066_DR_w1_loneliness$Q871), "NA='-999'")
t1066_DR_w1_loneliness$Q881 <- car::recode(as.vector(t1066_DR_w1_loneliness$Q881), "NA='-999'")
t1066_DR_w1_loneliness$Q882 <- car::recode(as.vector(t1066_DR_w1_loneliness$Q882), "NA='-999'")

t1066_ds_DR_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_DR_w1_loneliness)[1]){
  if( t1066_DR_w1_loneliness$Q871[i] %in% c(1,2) | t1066_DR_w1_loneliness$Q881[i] == 1 | t1066_DR_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_DR_w1$loneliness[i] = 1 }
  else if( t1066_DR_w1_loneliness$Q871[i] == 0 & t1066_DR_w1_loneliness$Q881[i] == 0 & t1066_DR_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_DR_w1$loneliness[i] = 0 }
  else if(  t1066_DR_w1_loneliness$Q871[i] == 8 | t1066_DR_w1_loneliness$Q881[i] == 8 | t1066_DR_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_DR_w1$loneliness[i] = 995 }
  else if( t1066_DR_w1_loneliness$Q871[i] == 9 | t1066_DR_w1_loneliness$Q881[i] == 9 | t1066_DR_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_DR_w1$loneliness[i] = 999 }
}

t1066_ds_DR_w1$loneliness <- car::recode(as.vector(t1066_ds_DR_w1$loneliness), "NA='999'")
t1066_ds_DR_w1$loneliness <- labelled(t1066_ds_DR_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 dr}
vari <- t1066_ds_DR_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 dr}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 dr}
opal.assign.table.tibble(o, 't1066_DR_w2_loneliness','10-66.1066-DominicanRepublic-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 dr}
t1066_DR_w2_loneliness <- opal.execute(o,'t1066_DR_w2_loneliness')

vari <-t1066_DR_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_DR_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_DR_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_DR_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_DR_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_DR_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_DR_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 dr, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_loneliness$id)

t1066_DR_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_DR_w2_loneliness$f_Q871), "NA='-999'")
t1066_DR_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_DR_w2_loneliness$f_Q881), "NA='-999'")
t1066_DR_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_DR_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_DR_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_DR_w2_loneliness)[1]){
  if( t1066_DR_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_DR_w2_loneliness$f_Q881[i] == 1 | t1066_DR_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_DR_w2$loneliness[i] = 1 }
  else if( t1066_DR_w2_loneliness$f_Q871[i] == 0 & t1066_DR_w2_loneliness$f_Q881[i] == 0 & t1066_DR_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_DR_w2$loneliness[i] = 0 }
  else if(  t1066_DR_w2_loneliness$f_Q871[i] == 8 | t1066_DR_w2_loneliness$f_Q881[i] == 8 | t1066_DR_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_DR_w2$loneliness[i] = 995 }
  else if( t1066_DR_w2_loneliness$f_Q871[i] == 9 | t1066_DR_w2_loneliness$f_Q881[i] == 9 | t1066_DR_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_DR_w2$loneliness[i] = 999 }
}

t1066_ds_DR_w2$loneliness <- car::recode(as.vector(t1066_ds_DR_w2$loneliness), "NA='999'")
t1066_ds_DR_w2$loneliness <- labelled(t1066_ds_DR_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 dr}
vari <- t1066_ds_DR_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 dr}

```

## India
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 india}
opal.assign.table.tibble(o, 't1066_india_w1_loneliness','10-66.1066-India-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 india}
t1066_india_w1_loneliness <- opal.execute(o,'t1066_india_w1_loneliness')

vari <-t1066_india_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_india_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_india_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_india_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_india_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_india_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_india_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_india_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_india_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_loneliness$id)

t1066_india_w1_loneliness$Q871 <- car::recode(as.vector(t1066_india_w1_loneliness$Q871), "NA='-999'")
t1066_india_w1_loneliness$Q881 <- car::recode(as.vector(t1066_india_w1_loneliness$Q881), "NA='-999'")
t1066_india_w1_loneliness$Q882 <- car::recode(as.vector(t1066_india_w1_loneliness$Q882), "NA='-999'")

t1066_ds_india_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_india_w1_loneliness)[1]){
  if( t1066_india_w1_loneliness$Q871[i] %in% c(1,2) | t1066_india_w1_loneliness$Q881[i] == 1 | t1066_india_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_india_w1$loneliness[i] = 1 }
  else if( t1066_india_w1_loneliness$Q871[i] == 0 & t1066_india_w1_loneliness$Q881[i] == 0 & t1066_india_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_india_w1$loneliness[i] = 0 }
  else if(  t1066_india_w1_loneliness$Q871[i] == 8 | t1066_india_w1_loneliness$Q881[i] == 8 | t1066_india_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_india_w1$loneliness[i] = 995 }
  else if( t1066_india_w1_loneliness$Q871[i] == 9 | t1066_india_w1_loneliness$Q881[i] == 9 | t1066_india_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_india_w1$loneliness[i] = 999 }
}

t1066_ds_india_w1$loneliness <- car::recode(as.vector(t1066_ds_india_w1$loneliness), "NA='999'")
t1066_ds_india_w1$loneliness <- labelled(t1066_ds_india_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india}
vari <- t1066_ds_india_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india}

```

## Puerto Rico
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 pr}
opal.assign.table.tibble(o, 't1066_PR_w1_loneliness','10-66.1066-PuertoRico-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 pr}
t1066_PR_w1_loneliness <- opal.execute(o,'t1066_PR_w1_loneliness')

vari <- t1066_PR_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_PR_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_PR_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_PR_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_PR_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_PR_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 pr, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_loneliness$id)

t1066_PR_w1_loneliness$Q871 <- car::recode(as.vector(t1066_PR_w1_loneliness$Q871), "NA='-999'")
t1066_PR_w1_loneliness$Q881 <- car::recode(as.vector(t1066_PR_w1_loneliness$Q881), "NA='-999'")
t1066_PR_w1_loneliness$Q882 <- car::recode(as.vector(t1066_PR_w1_loneliness$Q882), "NA='-999'")

t1066_ds_PR_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_PR_w1_loneliness)[1]){
  if( t1066_PR_w1_loneliness$Q871[i] %in% c(1,2) | t1066_PR_w1_loneliness$Q881[i] == 1 | t1066_PR_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_PR_w1$loneliness[i] = 1 }
  else if( t1066_PR_w1_loneliness$Q871[i] == 0 & t1066_PR_w1_loneliness$Q881[i] == 0 & t1066_PR_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_PR_w1$loneliness[i] = 0 }
  else if(  t1066_PR_w1_loneliness$Q871[i] == 8 | t1066_PR_w1_loneliness$Q881[i] == 8 | t1066_PR_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_PR_w1$loneliness[i] = 995 }
  else if( t1066_PR_w1_loneliness$Q871[i] == 9 | t1066_PR_w1_loneliness$Q881[i] == 9 | t1066_PR_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_PR_w1$loneliness[i] = 999 }
}

t1066_ds_PR_w1$loneliness <- car::recode(as.vector(t1066_ds_PR_w1$loneliness), "NA='999'")
t1066_ds_PR_w1$loneliness <- labelled(t1066_ds_PR_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pr}
vari <- t1066_ds_PR_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pr}

```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 pr}
opal.assign.table.tibble(o, 't1066_PR_w2_loneliness','10-66.1066-PuertoRico-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 pr}
t1066_PR_w2_loneliness <- opal.execute(o,'t1066_PR_w2_loneliness')

vari <- t1066_PR_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_PR_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_PR_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_PR_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_PR_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_PR_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_PR_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 pr, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_loneliness$id)

t1066_PR_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_PR_w2_loneliness$f_Q871), "NA='-999'")
t1066_PR_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_PR_w2_loneliness$f_Q881), "NA='-999'")
t1066_PR_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_PR_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_PR_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_PR_w2_loneliness)[1]){
  if( t1066_PR_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_PR_w2_loneliness$f_Q881[i] == 1 | t1066_PR_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_PR_w2$loneliness[i] = 1 }
  else if( t1066_PR_w2_loneliness$f_Q871[i] == 0 & t1066_PR_w2_loneliness$f_Q881[i] == 0 & t1066_PR_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_PR_w2$loneliness[i] = 0 }
  else if(  t1066_PR_w2_loneliness$f_Q871[i] == 8 | t1066_PR_w2_loneliness$f_Q881[i] == 8 | t1066_PR_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_PR_w2$loneliness[i] = 995 }
  else if( t1066_PR_w2_loneliness$f_Q871[i] == 9 | t1066_PR_w2_loneliness$f_Q881[i] == 9 | t1066_PR_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_PR_w2$loneliness[i] = 999 }
}

t1066_ds_PR_w2$loneliness <- car::recode(as.vector(t1066_ds_PR_w2$loneliness), "NA='999'")
t1066_ds_PR_w2$loneliness <- labelled(t1066_ds_PR_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pr}
vari <- t1066_ds_PR_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pr}

```
## Rural China
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 rch}
opal.assign.table.tibble(o, 't1066_RCh_w1_loneliness','10-66.1066-RuralChina-Baseline',variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 rch}
t1066_RCh_w1_loneliness <- opal.execute(o,'t1066_RCh_w1_loneliness')

vari <- t1066_RCh_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_RCh_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RCh_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_RCh_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RCh_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_RCh_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 rch, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_loneliness$id)

t1066_RCh_w1_loneliness$Q871 <- car::recode(as.vector(t1066_RCh_w1_loneliness$Q871), "NA='-999'")
t1066_RCh_w1_loneliness$Q881 <- car::recode(as.vector(t1066_RCh_w1_loneliness$Q881), "NA='-999'")
t1066_RCh_w1_loneliness$Q882 <- car::recode(as.vector(t1066_RCh_w1_loneliness$Q882), "NA='-999'")

t1066_ds_RCh_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_RCh_w1_loneliness)[1]){
  if( t1066_RCh_w1_loneliness$Q871[i] %in% c(1,2) | t1066_RCh_w1_loneliness$Q881[i] == 1 | t1066_RCh_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_RCh_w1$loneliness[i] = 1 }
  else if( t1066_RCh_w1_loneliness$Q871[i] == 0 & t1066_RCh_w1_loneliness$Q881[i] == 0 & t1066_RCh_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_RCh_w1$loneliness[i] = 0 }
  else if(  t1066_RCh_w1_loneliness$Q871[i] == 8 | t1066_RCh_w1_loneliness$Q881[i] == 8 | t1066_RCh_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_RCh_w1$loneliness[i] = 995 }
  else if( t1066_RCh_w1_loneliness$Q871[i] == 9 | t1066_RCh_w1_loneliness$Q881[i] == 9 | t1066_RCh_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_RCh_w1$loneliness[i] = 999 }
}

t1066_ds_RCh_w1$loneliness <- car::recode(as.vector(t1066_ds_RCh_w1$loneliness), "NA='999'")
t1066_ds_RCh_w1$loneliness <- labelled(t1066_ds_RCh_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rch}
vari <- t1066_ds_RCh_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rch}

```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 rch}
opal.assign.table.tibble(o, 't1066_RCh_w2_loneliness','10-66.1066-RuralChina-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 rch}
t1066_RCh_w2_loneliness <- opal.execute(o,'t1066_RCh_w2_loneliness')

vari <- t1066_RCh_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_RCh_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RCh_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_RCh_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RCh_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RCh_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_RCh_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 rch, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_loneliness$id)

t1066_RCh_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_RCh_w2_loneliness$f_Q871), "NA='-999'")
t1066_RCh_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_RCh_w2_loneliness$f_Q881), "NA='-999'")
t1066_RCh_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_RCh_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_RCh_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_RCh_w2_loneliness)[1]){
  if( t1066_RCh_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_RCh_w2_loneliness$f_Q881[i] == 1 | t1066_RCh_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_RCh_w2$loneliness[i] = 1 }
  else if( t1066_RCh_w2_loneliness$f_Q871[i] == 0 & t1066_RCh_w2_loneliness$f_Q881[i] == 0 & t1066_RCh_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_RCh_w2$loneliness[i] = 0 }
  else if(  t1066_RCh_w2_loneliness$f_Q871[i] == 8 | t1066_RCh_w2_loneliness$f_Q881[i] == 8 | t1066_RCh_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_RCh_w2$loneliness[i] = 995 }
  else if( t1066_RCh_w2_loneliness$f_Q871[i] == 9 | t1066_RCh_w2_loneliness$f_Q881[i] == 9 | t1066_RCh_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_RCh_w2$loneliness[i] = 999 }
}

t1066_ds_RCh_w2$loneliness <- car::recode(as.vector(t1066_ds_RCh_w2$loneliness), "NA='999'")
t1066_ds_RCh_w2$loneliness <- labelled(t1066_ds_RCh_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rch}
vari <- t1066_ds_RCh_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rch}

```

## Rural Mexico

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 rm}
opal.assign.table.tibble(o, 't1066_RM_w1_loneliness','10-66.1066-RuralMexico-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 rm}
t1066_RM_w1_loneliness <- opal.execute(o,'t1066_RM_w1_loneliness')

vari <- t1066_RM_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_RM_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RM_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_RM_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RM_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_RM_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 rm, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_loneliness$id)

t1066_RM_w1_loneliness$Q871 <- car::recode(as.vector(t1066_RM_w1_loneliness$Q871), "NA='-999'")
t1066_RM_w1_loneliness$Q881 <- car::recode(as.vector(t1066_RM_w1_loneliness$Q881), "NA='-999'")
t1066_RM_w1_loneliness$Q882 <- car::recode(as.vector(t1066_RM_w1_loneliness$Q882), "NA='-999'")

t1066_ds_RM_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_RM_w1_loneliness)[1]){
  if( t1066_RM_w1_loneliness$Q871[i] %in% c(1,2) | t1066_RM_w1_loneliness$Q881[i] == 1 | t1066_RM_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_RM_w1$loneliness[i] = 1 }
  else if( t1066_RM_w1_loneliness$Q871[i] == 0 & t1066_RM_w1_loneliness$Q881[i] == 0 & t1066_RM_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_RM_w1$loneliness[i] = 0 }
  else if(  t1066_RM_w1_loneliness$Q871[i] == 8 | t1066_RM_w1_loneliness$Q881[i] == 8 | t1066_RM_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_RM_w1$loneliness[i] = 995 }
  else if( t1066_RM_w1_loneliness$Q871[i] == 9 | t1066_RM_w1_loneliness$Q881[i] == 9 | t1066_RM_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_RM_w1$loneliness[i] = 999 }
}

t1066_ds_RM_w1$loneliness <- car::recode(as.vector(t1066_ds_RM_w1$loneliness), "NA='999'")
t1066_ds_RM_w1$loneliness <- labelled(t1066_ds_RM_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rm}
vari <- t1066_ds_RM_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rm}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 rm}
opal.assign.table.tibble(o, 't1066_RM_w2_loneliness','10-66.1066-RuralMexico-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 rm}
t1066_RM_w2_loneliness <- opal.execute(o,'t1066_RM_w2_loneliness')

vari <- t1066_RM_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_RM_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RM_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_RM_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RM_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RM_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_RM_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 rm, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_loneliness$id)

t1066_RM_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_RM_w2_loneliness$f_Q871), "NA='-999'")
t1066_RM_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_RM_w2_loneliness$f_Q881), "NA='-999'")
t1066_RM_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_RM_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_RM_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_RM_w2_loneliness)[1]){
  if( t1066_RM_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_RM_w2_loneliness$f_Q881[i] == 1 | t1066_RM_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_RM_w2$loneliness[i] = 1 }
  else if( t1066_RM_w2_loneliness$f_Q871[i] == 0 & t1066_RM_w2_loneliness$f_Q881[i] == 0 & t1066_RM_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_RM_w2$loneliness[i] = 0 }
  else if(  t1066_RM_w2_loneliness$f_Q871[i] == 8 | t1066_RM_w2_loneliness$f_Q881[i] == 8 | t1066_RM_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_RM_w2$loneliness[i] = 995 }
  else if( t1066_RM_w2_loneliness$f_Q871[i] == 9 | t1066_RM_w2_loneliness$f_Q881[i] == 9 | t1066_RM_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_RM_w2$loneliness[i] = 999 }
}

t1066_ds_RM_w2$loneliness <- car::recode(as.vector(t1066_ds_RM_w2$loneliness), "NA='999'")
t1066_ds_RM_w2$loneliness <- labelled(t1066_ds_RM_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rm}
vari <- t1066_ds_RM_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rm}

```

## Rural Peru
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 rp}
opal.assign.table.tibble(o, 't1066_RP_w1_loneliness','10-66.1066-RuralPeru-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 rp}
t1066_RP_w1_loneliness <- opal.execute(o,'t1066_RP_w1_loneliness')

vari <- t1066_RP_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_RP_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RP_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_RP_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RP_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_RP_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 rp, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_loneliness$id)

t1066_RP_w1_loneliness$Q871 <- car::recode(as.vector(t1066_RP_w1_loneliness$Q871), "NA='-999'")
t1066_RP_w1_loneliness$Q881 <- car::recode(as.vector(t1066_RP_w1_loneliness$Q881), "NA='-999'")
t1066_RP_w1_loneliness$Q882 <- car::recode(as.vector(t1066_RP_w1_loneliness$Q882), "NA='-999'")

t1066_ds_RP_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_RP_w1_loneliness)[1]){
  if( t1066_RP_w1_loneliness$Q871[i] %in% c(1,2) | t1066_RP_w1_loneliness$Q881[i] == 1 | t1066_RP_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_RP_w1$loneliness[i] = 1 }
  else if( t1066_RP_w1_loneliness$Q871[i] == 0 & t1066_RP_w1_loneliness$Q881[i] == 0 & t1066_RP_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_RP_w1$loneliness[i] = 0 }
  else if(  t1066_RP_w1_loneliness$Q871[i] == 8 | t1066_RP_w1_loneliness$Q881[i] == 8 | t1066_RP_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_RP_w1$loneliness[i] = 995 }
  else if( t1066_RP_w1_loneliness$Q871[i] == 9 | t1066_RP_w1_loneliness$Q881[i] == 9 | t1066_RP_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_RP_w1$loneliness[i] = 999 }
}

t1066_ds_RP_w1$loneliness <- car::recode(as.vector(t1066_ds_RP_w1$loneliness), "NA='999'")
t1066_ds_RP_w1$loneliness <- labelled(t1066_ds_RP_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rp}
vari <- t1066_ds_RP_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rp}

```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 rp}
opal.assign.table.tibble(o, 't1066_RP_w2_loneliness','10-66.1066-RuralPeru-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 rp}
t1066_RP_w2_loneliness <- opal.execute(o,'t1066_RP_w2_loneliness')

vari <- t1066_RP_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_RP_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_RP_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_RP_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_RP_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_RP_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_RP_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 rp, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_loneliness$id)

t1066_RP_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_RP_w2_loneliness$f_Q871), "NA='-999'")
t1066_RP_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_RP_w2_loneliness$f_Q881), "NA='-999'")
t1066_RP_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_RP_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_RP_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_RP_w2_loneliness)[1]){
  if( t1066_RP_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_RP_w2_loneliness$f_Q881[i] == 1 | t1066_RP_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_RP_w2$loneliness[i] = 1 }
  else if( t1066_RP_w2_loneliness$f_Q871[i] == 0 & t1066_RP_w2_loneliness$f_Q881[i] == 0 & t1066_RP_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_RP_w2$loneliness[i] = 0 }
  else if(  t1066_RP_w2_loneliness$f_Q871[i] == 8 | t1066_RP_w2_loneliness$f_Q881[i] == 8 | t1066_RP_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_RP_w2$loneliness[i] = 995 }
  else if( t1066_RP_w2_loneliness$f_Q871[i] == 9 | t1066_RP_w2_loneliness$f_Q881[i] == 9 | t1066_RP_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_RP_w2$loneliness[i] = 999 }
}

t1066_ds_RP_w2$loneliness <- car::recode(as.vector(t1066_ds_RP_w2$loneliness), "NA='999'")
t1066_ds_RP_w2$loneliness <- labelled(t1066_ds_RP_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rp}
vari <- t1066_ds_RP_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rp}

```

## Urban China

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 uch}
opal.assign.table.tibble(o, 't1066_UCh_w1_loneliness','10-66.1066-UrbanChina-Baseline', variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 uch}
t1066_UCh_w1_loneliness <- opal.execute(o,'t1066_UCh_w1_loneliness')

vari <- t1066_UCh_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_UCh_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_UCh_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_UCh_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_UCh_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_UCh_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 uch, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_loneliness$id)

t1066_UCh_w1_loneliness$Q871 <- car::recode(as.vector(t1066_UCh_w1_loneliness$Q871), "NA='-999'")
t1066_UCh_w1_loneliness$Q881 <- car::recode(as.vector(t1066_UCh_w1_loneliness$Q881), "NA='-999'")
t1066_UCh_w1_loneliness$Q882 <- car::recode(as.vector(t1066_UCh_w1_loneliness$Q882), "NA='-999'")

t1066_ds_UCh_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_UCh_w1_loneliness)[1]){
  if( t1066_UCh_w1_loneliness$Q871[i] %in% c(1,2) | t1066_UCh_w1_loneliness$Q881[i] == 1 | t1066_UCh_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_UCh_w1$loneliness[i] = 1 }
  else if( t1066_UCh_w1_loneliness$Q871[i] == 0 & t1066_UCh_w1_loneliness$Q881[i] == 0 & t1066_UCh_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_UCh_w1$loneliness[i] = 0 }
  else if(  t1066_UCh_w1_loneliness$Q871[i] == 8 | t1066_UCh_w1_loneliness$Q881[i] == 8 | t1066_UCh_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_UCh_w1$loneliness[i] = 995 }
  else if( t1066_UCh_w1_loneliness$Q871[i] == 9 | t1066_UCh_w1_loneliness$Q881[i] == 9 | t1066_UCh_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_UCh_w1$loneliness[i] = 999 }
}

t1066_ds_UCh_w1$loneliness <- car::recode(as.vector(t1066_ds_UCh_w1$loneliness), "NA='999'")
t1066_ds_UCh_w1$loneliness <- labelled(t1066_ds_UCh_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 uch}
vari <- t1066_ds_UCh_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 uch}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 uch}
opal.assign.table.tibble(o, 't1066_UCh_w2_loneliness','10-66.1066-UrbanChina-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 uch}
t1066_UCh_w2_loneliness <- opal.execute(o,'t1066_UCh_w2_loneliness')

vari <- t1066_UCh_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_UCh_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_UCh_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_UCh_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <-t1066_UCh_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UCh_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_UCh_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 uch, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_loneliness$id)

t1066_UCh_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_UCh_w2_loneliness$f_Q871), "NA='-999'")
t1066_UCh_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_UCh_w2_loneliness$f_Q881), "NA='-999'")
t1066_UCh_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_UCh_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_UCh_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_UCh_w2_loneliness)[1]){
  if( t1066_UCh_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_UCh_w2_loneliness$f_Q881[i] == 1 | t1066_UCh_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_UCh_w2$loneliness[i] = 1 }
  else if( t1066_UCh_w2_loneliness$f_Q871[i] == 0 & t1066_UCh_w2_loneliness$f_Q881[i] == 0 & t1066_UCh_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_UCh_w2$loneliness[i] = 0 }
  else if(  t1066_UCh_w2_loneliness$f_Q871[i] == 8 | t1066_UCh_w2_loneliness$f_Q881[i] == 8 | t1066_UCh_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_UCh_w2$loneliness[i] = 995 }
  else if( t1066_UCh_w2_loneliness$f_Q871[i] == 9 | t1066_UCh_w2_loneliness$f_Q881[i] == 9 | t1066_UCh_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_UCh_w2$loneliness[i] = 999 }
}

t1066_ds_UCh_w2$loneliness <- car::recode(as.vector(t1066_ds_UCh_w2$loneliness), "NA='999'")
t1066_ds_UCh_w2$loneliness <- labelled(t1066_ds_UCh_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 uch}
vari <- t1066_ds_UCh_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 uch}

```

## Urban Mexico
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1 um}
opal.assign.table.tibble(o, 't1066_UM_w1_loneliness','10-66.1066-UrbanMexico-Baseline',variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1 um}
t1066_UM_w1_loneliness <- opal.execute(o,'t1066_UM_w1_loneliness')

vari <-t1066_UM_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_UM_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_UM_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_UM_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <-t1066_UM_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_UM_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1 um, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_loneliness$id)

t1066_UM_w1_loneliness$Q871 <- car::recode(as.vector(t1066_UM_w1_loneliness$Q871), "NA='-999'")
t1066_UM_w1_loneliness$Q881 <- car::recode(as.vector(t1066_UM_w1_loneliness$Q881), "NA='-999'")
t1066_UM_w1_loneliness$Q882 <- car::recode(as.vector(t1066_UM_w1_loneliness$Q882), "NA='-999'")

t1066_ds_UM_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_UM_w1_loneliness)[1]){
  if( t1066_UM_w1_loneliness$Q871[i] %in% c(1,2) | t1066_UM_w1_loneliness$Q881[i] == 1 | t1066_UM_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_UM_w1$loneliness[i] = 1 }
  else if( t1066_UM_w1_loneliness$Q871[i] == 0 & t1066_UM_w1_loneliness$Q881[i] == 0 & t1066_UM_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_UM_w1$loneliness[i] = 0 }
  else if(  t1066_UM_w1_loneliness$Q871[i] == 8 | t1066_UM_w1_loneliness$Q881[i] == 8 | t1066_UM_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_UM_w1$loneliness[i] = 995 }
  else if( t1066_UM_w1_loneliness$Q871[i] == 9 | t1066_UM_w1_loneliness$Q881[i] == 9 | t1066_UM_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_UM_w1$loneliness[i] = 999 }
}

t1066_ds_UM_w1$loneliness <- car::recode(as.vector(t1066_ds_UM_w1$loneliness), "NA='999'")
t1066_ds_UM_w1$loneliness <- labelled(t1066_ds_UM_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 um}
vari <- t1066_ds_UM_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 um}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2 um}
opal.assign.table.tibble(o, 't1066_UM_w2_loneliness','10-66.1066-UrbanMexico-Followup', variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2 um}
t1066_UM_w2_loneliness <- opal.execute(o,'t1066_UM_w2_loneliness')

vari <-  t1066_UM_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_UM_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_UM_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_UM_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_UM_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UM_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_UM_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2 um, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_loneliness$id)

t1066_UM_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_UM_w2_loneliness$f_Q871), "NA='-999'")
t1066_UM_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_UM_w2_loneliness$f_Q881), "NA='-999'")
t1066_UM_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_UM_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_UM_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_UM_w2_loneliness)[1]){
  if( t1066_UM_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_UM_w2_loneliness$f_Q881[i] == 1 | t1066_UM_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_UM_w2$loneliness[i] = 1 }
  else if( t1066_UM_w2_loneliness$f_Q871[i] == 0 & t1066_UM_w2_loneliness$f_Q881[i] == 0 & t1066_UM_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_UM_w2$loneliness[i] = 0 }
  else if(  t1066_UM_w2_loneliness$f_Q871[i] == 8 | t1066_UM_w2_loneliness$f_Q881[i] == 8 | t1066_UM_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_UM_w2$loneliness[i] = 995 }
  else if( t1066_UM_w2_loneliness$f_Q871[i] == 9 | t1066_UM_w2_loneliness$f_Q881[i] == 9 | t1066_UM_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_UM_w2$loneliness[i] = 999 }
}

t1066_ds_UM_w2$loneliness <- car::recode(as.vector(t1066_ds_UM_w2$loneliness), "NA='999'")
t1066_ds_UM_w2$loneliness <- labelled(t1066_ds_UM_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 um}
vari <- t1066_ds_UM_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 um}

```
## Urban Peru

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1  up}
opal.assign.table.tibble(o, 't1066_UP_w1_loneliness','10-66.1066-UrbanPeru-Baseline',variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1  up}
t1066_UP_w1_loneliness <- opal.execute(o,'t1066_UP_w1_loneliness')

vari <- t1066_UP_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_UP_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <-t1066_UP_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_UP_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <-t1066_UP_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_UP_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1  up, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_loneliness$id)

t1066_UP_w1_loneliness$Q871 <- car::recode(as.vector(t1066_UP_w1_loneliness$Q871), "NA='-999'")
t1066_UP_w1_loneliness$Q881 <- car::recode(as.vector(t1066_UP_w1_loneliness$Q881), "NA='-999'")
t1066_UP_w1_loneliness$Q882 <- car::recode(as.vector(t1066_UP_w1_loneliness$Q882), "NA='-999'")

t1066_ds_UP_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_UP_w1_loneliness)[1]){
  if( t1066_UP_w1_loneliness$Q871[i] %in% c(1,2) | t1066_UP_w1_loneliness$Q881[i] == 1 | t1066_UP_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_UP_w1$loneliness[i] = 1 }
  else if( t1066_UP_w1_loneliness$Q871[i] == 0 & t1066_UP_w1_loneliness$Q881[i] == 0 & t1066_UP_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_UP_w1$loneliness[i] = 0 }
  else if(  t1066_UP_w1_loneliness$Q871[i] == 8 | t1066_UP_w1_loneliness$Q881[i] == 8 | t1066_UP_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_UP_w1$loneliness[i] = 995 }
  else if( t1066_UP_w1_loneliness$Q871[i] == 9 | t1066_UP_w1_loneliness$Q881[i] == 9 | t1066_UP_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_UP_w1$loneliness[i] = 999 }
}

t1066_ds_UP_w1$loneliness <- car::recode(as.vector(t1066_ds_UP_w1$loneliness), "NA='999'")
t1066_ds_UP_w1$loneliness <- labelled(t1066_ds_UP_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1  up}
vari <- t1066_ds_UP_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1  up}

```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2  up}
opal.assign.table.tibble(o, 't1066_UP_w2_loneliness','10-66.1066-UrbanPeru-Followup',variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2  up}
t1066_UP_w2_loneliness <- opal.execute(o,'t1066_UP_w2_loneliness')

vari <- t1066_UP_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_UP_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_UP_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_UP_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_UP_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_UP_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_UP_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2  up, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_loneliness$id)

t1066_UP_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_UP_w2_loneliness$f_Q871), "NA='-999'")
t1066_UP_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_UP_w2_loneliness$f_Q881), "NA='-999'")
t1066_UP_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_UP_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_UP_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_UP_w2_loneliness)[1]){
  if( t1066_UP_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_UP_w2_loneliness$f_Q881[i] == 1 | t1066_UP_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_UP_w2$loneliness[i] = 1 }
  else if( t1066_UP_w2_loneliness$f_Q871[i] == 0 & t1066_UP_w2_loneliness$f_Q881[i] == 0 & t1066_UP_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_UP_w2$loneliness[i] = 0 }
  else if(  t1066_UP_w2_loneliness$f_Q871[i] == 8 | t1066_UP_w2_loneliness$f_Q881[i] == 8 | t1066_UP_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_UP_w2$loneliness[i] = 995 }
  else if( t1066_UP_w2_loneliness$f_Q871[i] == 9 | t1066_UP_w2_loneliness$f_Q881[i] == 9 | t1066_UP_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_UP_w2$loneliness[i] = 999 }
}

t1066_ds_UP_w2$loneliness <- car::recode(as.vector(t1066_ds_UP_w2$loneliness), "NA='999'")
t1066_ds_UP_w2$loneliness <- labelled(t1066_ds_UP_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2  up}
vari <- t1066_ds_UP_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2  up}

```

## Venezuela
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign1  ven}
opal.assign.table.tibble(o, 't1066_Ven_w1_loneliness','10-66.1066-Venezuela-Baseline',variables=list('Q871','Q881','Q882'), missings = TRUE)
```

```{r local1  ven}
t1066_Ven_w1_loneliness <- opal.execute(o,'t1066_Ven_w1_loneliness')

vari <- t1066_Ven_w1_loneliness$Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w1_loneliness$Q871, missing_values = NA)
ggplot(t1066_Ven_w1_loneliness, aes(x=factor(Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_Ven_w1_loneliness$Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w1_loneliness$Q881, missing_values = NA)
ggplot(t1066_Ven_w1_loneliness, aes(x=factor(Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_Ven_w1_loneliness$Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w1_loneliness$Q882, missing_values = NA)
ggplot(t1066_Ven_w1_loneliness, aes(x=factor(Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo1  ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_loneliness$id)

t1066_Ven_w1_loneliness$Q871 <- car::recode(as.vector(t1066_Ven_w1_loneliness$Q871), "NA='-999'")
t1066_Ven_w1_loneliness$Q881 <- car::recode(as.vector(t1066_Ven_w1_loneliness$Q881), "NA='-999'")
t1066_Ven_w1_loneliness$Q882 <- car::recode(as.vector(t1066_Ven_w1_loneliness$Q882), "NA='-999'")

t1066_ds_Ven_w1$loneliness <- c(NA)
for(i in 1:dim(t1066_Ven_w1_loneliness)[1]){
  if( t1066_Ven_w1_loneliness$Q871[i] %in% c(1,2) | t1066_Ven_w1_loneliness$Q881[i] == 1 | t1066_Ven_w1_loneliness$Q882[i] == 1 ) {
    t1066_ds_Ven_w1$loneliness[i] = 1 }
  else if( t1066_Ven_w1_loneliness$Q871[i] == 0 & t1066_Ven_w1_loneliness$Q881[i] == 0 & t1066_Ven_w1_loneliness$Q882[i] == 0 ) {
    t1066_ds_Ven_w1$loneliness[i] = 0 }
  else if(  t1066_Ven_w1_loneliness$Q871[i] == 8 | t1066_Ven_w1_loneliness$Q881[i] == 8 | t1066_Ven_w1_loneliness$Q882[i] == 8 ) { 
    t1066_ds_Ven_w1$loneliness[i] = 995 }
  else if( t1066_Ven_w1_loneliness$Q871[i] == 9 | t1066_Ven_w1_loneliness$Q881[i] == 9 | t1066_Ven_w1_loneliness$Q882[i] == 9 ) { 
    t1066_ds_Ven_w1$loneliness[i] = 999 }
}

t1066_ds_Ven_w1$loneliness <- car::recode(as.vector(t1066_ds_Ven_w1$loneliness), "NA='999'")
t1066_ds_Ven_w1$loneliness <- labelled(t1066_ds_Ven_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1  ven}
vari <- t1066_ds_Ven_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1  ven}

```




### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_Q871`
* Label: `Admits to feeling loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes but mild to moderate intensity, infrequent or fleeting`
    + `2 = Yes and severe, frequent or persistent`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q881`
* Label: `88.1 Feels loneliness and cannot turn away from it`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
    
* Name: `f_Q882`
* Label: `88.2 Bothered or depressed by current loneliness`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings: 
    + `8 = no answer`
    + `9 = not asked`
  

* Description: 
```{r assign2  ven}
opal.assign.table.tibble(o, 't1066_Ven_w2_loneliness','10-66.1066-Venezuela-Followup',variables=list('f_Q871','f_Q881','f_Q882'), missings = TRUE)
```

```{r local2  ven}
t1066_Ven_w2_loneliness <- opal.execute(o,'t1066_Ven_w2_loneliness')

vari <- t1066_Ven_w2_loneliness$f_Q871
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w2_loneliness$f_Q871, missing_values = NA)
ggplot(t1066_Ven_w2_loneliness, aes(x=factor(f_Q871))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Admits to feeling loneliness") + ylab("Frequency")

vari <- t1066_Ven_w2_loneliness$f_Q881
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w2_loneliness$f_Q881, missing_values = NA)
ggplot(t1066_Ven_w2_loneliness, aes(x=factor(f_Q881))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Feels loneliness and cannot turn away from it") + ylab("Frequency")

vari <- t1066_Ven_w2_loneliness$f_Q882
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_Ven_w2_loneliness$f_Q882, missing_values = NA)
ggplot(t1066_Ven_w2_loneliness, aes(x=factor(f_Q882))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bothered or depressed by current loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 (or 2) then 1`
* `else if all are equal 0 then 0`
* `8 into 995`
* `9 or NA into 999`

**R script:**

```{r harmo2  ven, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_loneliness$id)

t1066_Ven_w2_loneliness$f_Q871 <- car::recode(as.vector(t1066_Ven_w2_loneliness$f_Q871), "NA='-999'")
t1066_Ven_w2_loneliness$f_Q881 <- car::recode(as.vector(t1066_Ven_w2_loneliness$f_Q881), "NA='-999'")
t1066_Ven_w2_loneliness$f_Q882 <- car::recode(as.vector(t1066_Ven_w2_loneliness$f_Q882), "NA='-999'")

t1066_ds_Ven_w2$loneliness <- c(NA)
for(i in 1:dim(t1066_Ven_w2_loneliness)[1]){
  if( t1066_Ven_w2_loneliness$f_Q871[i] %in% c(1,2) | t1066_Ven_w2_loneliness$f_Q881[i] == 1 | t1066_Ven_w2_loneliness$f_Q882[i] == 1 ) {
    t1066_ds_Ven_w2$loneliness[i] = 1 }
  else if( t1066_Ven_w2_loneliness$f_Q871[i] == 0 & t1066_Ven_w2_loneliness$f_Q881[i] == 0 & t1066_Ven_w2_loneliness$f_Q882[i] == 0 ) {
    t1066_ds_Ven_w2$loneliness[i] = 0 }
  else if(  t1066_Ven_w2_loneliness$f_Q871[i] == 8 | t1066_Ven_w2_loneliness$f_Q881[i] == 8 | t1066_Ven_w2_loneliness$f_Q882[i] == 8 ) { 
    t1066_ds_Ven_w2$loneliness[i] = 995 }
  else if( t1066_Ven_w2_loneliness$f_Q871[i] == 9 | t1066_Ven_w2_loneliness$f_Q881[i] == 9 | t1066_Ven_w2_loneliness$f_Q882[i] == 9 ) { 
    t1066_ds_Ven_w2$loneliness[i] = 999 }
}

t1066_ds_Ven_w2$loneliness <- car::recode(as.vector(t1066_ds_Ven_w2$loneliness), "NA='999'")
t1066_ds_Ven_w2$loneliness <- labelled(t1066_ds_Ven_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2  ven}
vari <- t1066_ds_Ven_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2  ven}

```

 
 
```{r save,  echo=FALSE}
loneliness <- t1066_ds_cuba_w1
save(loneliness, file = "../RData/cuba_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_cuba_w2
save(loneliness, file = "../RData/cuba_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_india_w1
save(loneliness, file = "../RData/india_w1/loneliness.RData")
rm(loneliness)


loneliness <- t1066_ds_UCh_w1
save(loneliness, file = "../RData/UCh_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_UCh_w2
save(loneliness, file = "../RData/UCh_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RCh_w1
save(loneliness, file = "../RData/RCh_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RCh_w2
save(loneliness, file = "../RData/RCh_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_DR_w1
save(loneliness, file = "../RData/DR_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_DR_w2
save(loneliness, file = "../RData/DR_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_Ven_w1
save(loneliness, file = "../RData/Ven_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_Ven_w2
save(loneliness, file = "../RData/Ven_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_UP_w1
save(loneliness, file = "../RData/UP_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_UP_w2
save(loneliness, file = "../RData/UP_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RP_w1
save(loneliness, file = "../RData/RP_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RP_w2
save(loneliness, file = "../RData/RP_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_UM_w1
save(loneliness, file = "../RData/UM_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_UM_w2
save(loneliness, file = "../RData/UM_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RM_w1
save(loneliness, file = "../RData/RM_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_RM_w2
save(loneliness, file = "../RData/RM_w2/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_PR_w1
save(loneliness, file = "../RData/PR_w1/loneliness.RData")
rm(loneliness)

loneliness <- t1066_ds_PR_w2
save(loneliness, file = "../RData/PR_w2/loneliness.RData")
rm(loneliness)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

