---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process


## Cuba
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`

* Description: 
```{r cuba assign1}
opal.assign.table.tibble(o, 't1066_cuba_w1_spouse','10-66.1066-Cuba-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r cuba local1}
t1066_cuba_w1_spouse <- opal.execute(o,'t1066_cuba_w1_spouse')
vari <- t1066_cuba_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_cuba_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

 **R script:**

```{r cuba harmo1, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_spouse$id)
t1066_ds_cuba_w1$spouse <- car::recode(as.vector(t1066_cuba_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_cuba_w1$spouse <- labelled(t1066_ds_cuba_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r cuba descript1}
vari <- t1066_ds_cuba_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r cuba crosstabulation1}
AfterH <- table(t1066_ds_cuba_w1$spouse)
BeforeH <- table(t1066_cuba_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r cuba assign2}
opal.assign.table.tibble(o, 't1066_cuba_w2_spouse','10-66.1066-Cuba-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r cuba local2}
t1066_cuba_w2_spouse <- opal.execute(o,'t1066_cuba_w2_spouse')
vari <- t1066_cuba_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_cuba_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

 **R script:**

```{r cuba harmo2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_spouse$id)
t1066_ds_cuba_w2$spouse <- car::recode(as.vector(t1066_cuba_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_cuba_w2$spouse <- labelled(t1066_ds_cuba_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r cuba descript2}
vari <- t1066_ds_cuba_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r cuba crosstabulation2}
AfterH <- table(t1066_ds_cuba_w2$spouse)
BeforeH <- table(t1066_cuba_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 





## Dominican Republic
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r DR assign1}
opal.assign.table.tibble(o, 't1066_DR_w1_spouse','10-66.1066-DominicanRepublic-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r DR local1}
t1066_DR_w1_spouse <- opal.execute(o,'t1066_DR_w1_spouse')
vari <- t1066_DR_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_DR_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r DR harmo1, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_spouse$id)
t1066_ds_DR_w1$spouse <- car::recode(as.vector(t1066_DR_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_DR_w1$spouse <- labelled(t1066_ds_DR_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r DR descript1}
vari <- t1066_ds_DR_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r DR crosstabulation1}
AfterH <- table(t1066_ds_DR_w1$spouse)
BeforeH <- table(t1066_DR_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r DR assign2}
opal.assign.table.tibble(o, 't1066_DR_w2_spouse','10-66.1066-DominicanRepublic-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r DR local2}
t1066_DR_w2_spouse <- opal.execute(o,'t1066_DR_w2_spouse')
vari <- t1066_DR_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_DR_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

 
**R script:**
```{r DR harmo2, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_spouse$id)
t1066_ds_DR_w2$spouse <- car::recode(as.vector(t1066_DR_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_DR_w2$spouse <- labelled(t1066_ds_DR_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r DR descript2}
vari <- t1066_ds_DR_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r DR crosstabulation2}
AfterH <- table(t1066_ds_DR_w2$spouse)
BeforeH <- table(t1066_DR_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 





## India
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r india assign1}
opal.assign.table.tibble(o, 't1066_india_w1_spouse','10-66.1066-India-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r india local1}
t1066_india_w1_spouse <- opal.execute(o,'t1066_india_w1_spouse')
vari <- t1066_india_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_india_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

 
**R script:**
```{r india harmo1, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_spouse$id)
t1066_ds_india_w1$spouse <- car::recode(as.vector(t1066_india_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_india_w1$spouse <- labelled(t1066_ds_india_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r india descript1}
vari <- t1066_ds_india_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r india crosstabulation1}
AfterH <- table(t1066_ds_india_w1$spouse)
BeforeH <- table(t1066_india_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
### Wave 2
Not found.



## Puerto Rico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r PR assign1}
opal.assign.table.tibble(o, 't1066_PR_w1_spouse','10-66.1066-PuertoRico-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r PR local1}
t1066_PR_w1_spouse <- opal.execute(o,'t1066_PR_w1_spouse')
vari <- t1066_PR_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_PR_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r PR harmo1, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_spouse$id)
t1066_ds_PR_w1$spouse <- car::recode(as.vector(t1066_PR_w1_spouse$PMARRY),  "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_PR_w1$spouse <- labelled(t1066_ds_PR_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r PR descript1}
vari <- t1066_ds_PR_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r PR crosstabulation1}
AfterH <- table(t1066_ds_PR_w1$spouse)
BeforeH <- table(t1066_PR_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r PR assign2}
opal.assign.table.tibble(o, 't1066_PR_w2_spouse','10-66.1066-PuertoRico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r PR local2}
t1066_PR_w2_spouse <- opal.execute(o,'t1066_PR_w2_spouse')
vari <- t1066_PR_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_PR_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r PR harmo2, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_spouse$id)
t1066_ds_PR_w2$spouse <- car::recode(as.vector(t1066_PR_w2_spouse$f_PMARRY),  "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_PR_w2$spouse <- labelled(t1066_ds_PR_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r PR descript2}
vari <- t1066_ds_PR_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r PR crosstabulation2}
AfterH <- table(t1066_ds_PR_w2$spouse)
BeforeH <- table(t1066_PR_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r RCh assign1}
opal.assign.table.tibble(o, 't1066_RCh_w1_spouse','10-66.1066-RuralChina-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r RCh local1}
t1066_RCh_w1_spouse <- opal.execute(o,'t1066_RCh_w1_spouse')
vari <- t1066_RCh_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_RCh_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r RCh harmo1, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_spouse$id)
t1066_ds_RCh_w1$spouse <- car::recode(as.vector(t1066_RCh_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RCh_w1$spouse <- labelled(t1066_ds_RCh_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RCh descript1}
vari <- t1066_ds_RCh_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RCh crosstabulation1}
AfterH <- table(t1066_ds_RCh_w1$spouse)
BeforeH <- table(t1066_RCh_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r RCh assign2}
opal.assign.table.tibble(o, 't1066_RCh_w2_spouse','10-66.1066-RuralChina-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r RCh local2}
t1066_RCh_w2_spouse <- opal.execute(o,'t1066_RCh_w2_spouse')
vari <- t1066_RCh_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_RCh_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r RCh harmo2, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_spouse$id)
t1066_ds_RCh_w2$spouse <- car::recode(as.vector(t1066_RCh_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RCh_w2$spouse <- labelled(t1066_ds_RCh_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RCh descript2}
vari <- t1066_ds_RCh_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RCh crosstabulation2}
AfterH <- table(t1066_ds_RCh_w2$spouse)
BeforeH <- table(t1066_RCh_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")
kable(C)
```

 
 




## Rural Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
    
* Description:
```{r RM assign1}
opal.assign.table.tibble(o, 't1066_RM_w1_spouse','10-66.1066-RuralMexico-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r RM local1}
t1066_RM_w1_spouse <- opal.execute(o,'t1066_RM_w1_spouse')
vari <- t1066_RM_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_RM_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

 
**R script:**
```{r RM harmo1, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_spouse$id)
t1066_ds_RM_w1$spouse <- car::recode(as.vector(t1066_RM_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RM_w1$spouse <- labelled(t1066_ds_RM_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RM descript1}
vari <- t1066_ds_RM_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RM crosstabulation1}
AfterH <- table(t1066_ds_RM_w1$spouse)
BeforeH <- table(t1066_RM_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r RM assign2}
opal.assign.table.tibble(o, 't1066_RM_w2_spouse','10-66.1066-RuralMexico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r RM local2}
t1066_RM_w2_spouse <- opal.execute(o,'t1066_RM_w2_spouse')
vari <- t1066_RM_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_RM_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r RM harmo2, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_spouse$id)
t1066_ds_RM_w2$spouse <- car::recode(as.vector(t1066_RM_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RM_w2$spouse <- labelled(t1066_ds_RM_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RM descript2}
vari <- t1066_ds_RM_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RM crosstabulation2}
AfterH <- table(t1066_ds_RM_w2$spouse)
BeforeH <- table(t1066_RM_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 



## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r RP assign1}
opal.assign.table.tibble(o, 't1066_RP_w1_spouse','10-66.1066-RuralPeru-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r RP local1}
t1066_RP_w1_spouse <- opal.execute(o,'t1066_RP_w1_spouse')
vari <- t1066_RP_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_RP_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r RP harmo1, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_spouse$id)
t1066_ds_RP_w1$spouse <- car::recode(as.vector(t1066_RP_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RP_w1$spouse <- labelled(t1066_ds_RP_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RP descript1}
vari <- t1066_ds_RP_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RP crosstabulation1}
AfterH <- table(t1066_ds_RP_w1$spouse)
BeforeH <- table(t1066_RP_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r RP assign2}
opal.assign.table.tibble(o, 't1066_RP_w2_spouse','10-66.1066-RuralPeru-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r RP local2}
t1066_RP_w2_spouse <- opal.execute(o,'t1066_RP_w2_spouse')
vari <- t1066_RP_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_RP_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r RP harmo2, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_spouse$id)
t1066_ds_RP_w2$spouse <- car::recode(as.vector(t1066_RP_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_RP_w2$spouse <- labelled(t1066_ds_RP_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r RP descript2}
vari <- t1066_ds_RP_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r RP crosstabulation2}
AfterH <- table(t1066_ds_RP_w2$spouse)
BeforeH <- table(t1066_RP_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")
kable(C)
```

 
 



## Urban China
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UCh assign1}
opal.assign.table.tibble(o, 't1066_UCh_w1_spouse','10-66.1066-UrbanChina-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r UCh local1}
t1066_UCh_w1_spouse <- opal.execute(o,'t1066_UCh_w1_spouse')
vari <- t1066_UCh_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_UCh_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UCh harmo1, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_spouse$id)
t1066_ds_UCh_w1$spouse <- car::recode(as.vector(t1066_UCh_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UCh_w1$spouse <- labelled(t1066_ds_UCh_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UCh descript1}
vari <- t1066_ds_UCh_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UCh crosstabulation1}
AfterH <- table(t1066_ds_UCh_w1$spouse)
BeforeH <- table(t1066_UCh_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UCh assign2}
opal.assign.table.tibble(o, 't1066_UCh_w2_spouse','10-66.1066-UrbanChina-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r UCh local2}
t1066_UCh_w2_spouse <- opal.execute(o,'t1066_UCh_w2_spouse')
vari <- t1066_UCh_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_UCh_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UCh harmo2, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_spouse$id)
t1066_ds_UCh_w2$spouse <- car::recode(as.vector(t1066_UCh_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UCh_w2$spouse <- labelled(t1066_ds_UCh_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UCh descript2}
vari <- t1066_ds_UCh_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UCh crosstabulation2}
AfterH <- table(t1066_ds_UCh_w2$spouse)
BeforeH <- table(t1066_UCh_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")

kable(C)
```

 
 




 
## Urban Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UM assign1}
opal.assign.table.tibble(o, 't1066_UM_w1_spouse','10-66.1066-UrbanMexico-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r UM local1}
t1066_UM_w1_spouse <- opal.execute(o,'t1066_UM_w1_spouse')
vari <- t1066_UM_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_UM_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UM harmo1, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_spouse$id)
t1066_ds_UM_w1$spouse <- car::recode(as.vector(t1066_UM_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UM_w1$spouse <- labelled(t1066_ds_UM_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UM descript1}
vari <- t1066_ds_UM_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UM crosstabulation1}
AfterH <- table(t1066_ds_UM_w1$spouse)
BeforeH <- table(t1066_UM_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UM assign2}
opal.assign.table.tibble(o, 't1066_UM_w2_spouse','10-66.1066-UrbanMexico-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r UM local2}
t1066_UM_w2_spouse <- opal.execute(o,'t1066_UM_w2_spouse')
vari <- t1066_UM_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_UM_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UM harmo2, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_spouse$id)
t1066_ds_UM_w2$spouse <- car::recode(as.vector(t1066_UM_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UM_w2$spouse <- labelled(t1066_ds_UM_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UM descript2}
vari <- t1066_ds_UM_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UM crosstabulation2}
AfterH <- table(t1066_ds_UM_w2$spouse)
BeforeH <- table(t1066_UM_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")

kable(C)
```

 
 



## Urban Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UP assign1}
opal.assign.table.tibble(o, 't1066_UP_w1_spouse','10-66.1066-UrbanPeru-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r UP local1}
t1066_UP_w1_spouse <- opal.execute(o,'t1066_UP_w1_spouse')
vari <- t1066_UP_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_UP_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UP harmo1, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_spouse$id)
t1066_ds_UP_w1$spouse <- car::recode(as.vector(t1066_UP_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UP_w1$spouse <- labelled(t1066_ds_UP_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UP descript1}
vari <- t1066_ds_UP_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UP crosstabulation1}
AfterH <- table(t1066_ds_UP_w1$spouse)
BeforeH <- table(t1066_UP_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r UP assign2}
opal.assign.table.tibble(o, 't1066_UP_w2_spouse','10-66.1066-UrbanPeru-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r UP local2}
t1066_UP_w2_spouse <- opal.execute(o,'t1066_UP_w2_spouse')
vari <- t1066_UP_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_UP_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r UP harmo2, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_spouse$id)
t1066_ds_UP_w2$spouse <- car::recode(as.vector(t1066_UP_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_UP_w2$spouse <- labelled(t1066_ds_UP_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r UP descript2}
vari <- t1066_ds_UP_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r UP crosstabulation2}
AfterH <- table(t1066_ds_UP_w2$spouse)
BeforeH <- table(t1066_UP_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1")

kable(C)
```

 
 




## Venezuela
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r Ven assign1}
opal.assign.table.tibble(o, 't1066_Ven_w1_spouse','10-66.1066-Venezuela-Baseline', variables=list('PMARRY'), missings = TRUE)
```

```{r Ven local1}
t1066_Ven_w1_spouse <- opal.execute(o,'t1066_Ven_w1_spouse')
vari <- t1066_Ven_w1_spouse$PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_spouse$PMARRY, missing_values = NA)
ggplot(t1066_Ven_w1_spouse, aes(x=factor(PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r Ven harmo1, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_spouse$id)
t1066_ds_Ven_w1$spouse <- car::recode(as.vector(t1066_Ven_w1_spouse$PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_Ven_w1$spouse <- labelled(t1066_ds_Ven_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r Ven descript1}
vari <- t1066_ds_Ven_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r Ven crosstabulation1}
AfterH <- table(t1066_ds_Ven_w1$spouse)
BeforeH <- table(t1066_Ven_w1_spouse$PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PMARRY`
* Label: `marital status`
* Categories: 
    + `1.0 = never married`
    + `2.0 = married/ cohabiting`
    + `3.0 = widowed`
    + `4.0 = divorced/ separated`
* Description:
```{r Ven assign2}
opal.assign.table.tibble(o, 't1066_Ven_w2_spouse','10-66.1066-Venezuela-Followup',variables=list('f_PMARRY'), missings = TRUE)
```

```{r Ven local2}
t1066_Ven_w2_spouse <- opal.execute(o,'t1066_Ven_w2_spouse')
vari <- t1066_Ven_w2_spouse$f_PMARRY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_spouse$f_PMARRY, missing_values = NA)
ggplot(t1066_Ven_w2_spouse, aes(x=factor(f_PMARRY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 married/cohabiting into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:** 

```{r Ven harmo2, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_spouse$id)
t1066_ds_Ven_w2$spouse <- car::recode(as.vector(t1066_Ven_w2_spouse$f_PMARRY), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
t1066_ds_Ven_w2$spouse <- labelled(t1066_ds_Ven_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r Ven descript2}
vari <- t1066_ds_Ven_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r Ven crosstabulation2}
AfterH <- table(t1066_ds_Ven_w2$spouse)
BeforeH <- table(t1066_Ven_w2_spouse$f_PMARRY, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1,3,4->1","NA->999")

kable(C)
```

 
```{r save,  echo=FALSE}
spouse <- t1066_ds_cuba_w1
save(spouse, file = "../RData/cuba_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_cuba_w2
save(spouse, file = "../RData/cuba_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_india_w1
save(spouse, file = "../RData/india_w1/spouse.RData")
rm(spouse)


spouse <- t1066_ds_UCh_w1
save(spouse, file = "../RData/UCh_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_UCh_w2
save(spouse, file = "../RData/UCh_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RCh_w1
save(spouse, file = "../RData/RCh_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RCh_w2
save(spouse, file = "../RData/RCh_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_DR_w1
save(spouse, file = "../RData/DR_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_DR_w2
save(spouse, file = "../RData/DR_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_Ven_w1
save(spouse, file = "../RData/Ven_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_Ven_w2
save(spouse, file = "../RData/Ven_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_UP_w1
save(spouse, file = "../RData/UP_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_UP_w2
save(spouse, file = "../RData/UP_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RP_w1
save(spouse, file = "../RData/RP_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RP_w2
save(spouse, file = "../RData/RP_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_UM_w1
save(spouse, file = "../RData/UM_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_UM_w2
save(spouse, file = "../RData/UM_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RM_w1
save(spouse, file = "../RData/RM_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_RM_w2
save(spouse, file = "../RData/RM_w2/spouse.RData")
rm(spouse)

spouse <- t1066_ds_PR_w1
save(spouse, file = "../RData/PR_w1/spouse.RData")
rm(spouse)

spouse <- t1066_ds_PR_w2
save(spouse, file = "../RData/PR_w2/spouse.RData")
rm(spouse)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
