---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `Do you have any children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 cuba}
opal.assign.table.tibble(o, 't1066_cuba_w1_child','10-66.1066-Cuba-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 cuba}
t1066_cuba_w1_child <- opal.execute(o,'t1066_cuba_w1_child')
vari <- t1066_cuba_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_child$PCH, missing_values = NA)
ggplot(t1066_cuba_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_child$id)
t1066_ds_cuba_w1$child <- car::recode(as.vector(t1066_cuba_w1_child$PCH), "NA='999'")
t1066_ds_cuba_w1$child <- labelled(t1066_ds_cuba_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba}
vari <- t1066_ds_cuba_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba}
AfterH <- table(t1066_ds_cuba_w1$child)
BeforeH <- table(t1066_cuba_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Nos found.


## Dominican Republic
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 DR}
opal.assign.table.tibble(o, 't1066_DR_w1_child','10-66.1066-DominicanRepublic-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 DR}
t1066_DR_w1_child <- opal.execute(o,'t1066_DR_w1_child')
vari <- t1066_DR_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_child$PCH, missing_values = NA)
ggplot(t1066_DR_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_child$id)
t1066_ds_DR_w1$child <- car::recode(as.vector(t1066_DR_w1_child$PCH), "NA='999'")
t1066_ds_DR_w1$child <- labelled(t1066_ds_DR_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR}
vari <- t1066_ds_DR_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR}
AfterH <- table(t1066_ds_DR_w1$child)
BeforeH <- table(t1066_DR_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Not found.


## India
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 india}
opal.assign.table.tibble(o, 't1066_india_w1_child','10-66.1066-India-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 india}
t1066_india_w1_child <- opal.execute(o,'t1066_india_w1_child')
vari <- t1066_india_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_child$PCH, missing_values = NA)
ggplot(t1066_india_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_child$id)
t1066_ds_india_w1$child <- car::recode(as.vector(t1066_india_w1_child$PCH), "NA='999'")
t1066_ds_india_w1$child <- labelled(t1066_ds_india_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india}
vari <- t1066_ds_india_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india}
AfterH <- table(t1066_ds_india_w1$child)
BeforeH <- table(t1066_india_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 

### Wave 2
Not found.

## Puerto Rico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 PR}
opal.assign.table.tibble(o, 't1066_PR_w1_child','10-66.1066-PuertoRico-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 PR}
t1066_PR_w1_child <- opal.execute(o,'t1066_PR_w1_child')
vari <- t1066_PR_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_child$PCH, missing_values = NA)
ggplot(t1066_PR_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 PR, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_child$id)
t1066_ds_PR_w1$child <- car::recode(as.vector(t1066_PR_w1_child$PCH), "NA='999'")
t1066_ds_PR_w1$child <- labelled(t1066_ds_PR_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR}
vari <- t1066_ds_PR_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR}
AfterH <- table(t1066_ds_PR_w1$child)
BeforeH <- table(t1066_PR_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Not found.


## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 RCh}
opal.assign.table.tibble(o, 't1066_RCh_w1_child','10-66.1066-RuralChina-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 RCh}
t1066_RCh_w1_child <- opal.execute(o,'t1066_RCh_w1_child')
vari <- t1066_RCh_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_child$PCH, missing_values = NA)
ggplot(t1066_RCh_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 RCh, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_child$id)
t1066_ds_RCh_w1$child <- car::recode(as.vector(t1066_RCh_w1_child$PCH), "NA='999'")
t1066_ds_RCh_w1$child <- labelled(t1066_ds_RCh_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCh}
vari <- t1066_ds_RCh_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCh}
AfterH <- table(t1066_ds_RCh_w1$child)
BeforeH <- table(t1066_RCh_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 


### Wave 2

Not found.



## Rural Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 RM}
opal.assign.table.tibble(o, 't1066_RM_w1_child','10-66.1066-RuralMexico-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 RM}
t1066_RM_w1_child <- opal.execute(o,'t1066_RM_w1_child')
vari <- t1066_RM_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_child$PCH, missing_values = NA)
ggplot(t1066_RM_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, bnut NA into 999`

 **R script:**

```{r harmo1 RM, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_child$id)
t1066_ds_RM_w1$child <- car::recode(as.vector(t1066_RM_w1_child$PCH), "NA='999'")
t1066_ds_RM_w1$child <- labelled(t1066_ds_RM_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RM}
vari <- t1066_ds_RM_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RM}
AfterH <- table(t1066_ds_RM_w1$child)
BeforeH <- table(t1066_RM_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 


### Wave 2

Not found.



## Rural Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 RP}
opal.assign.table.tibble(o, 't1066_RP_w1_child','10-66.1066-RuralPeru-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 RP}
t1066_RP_w1_child <- opal.execute(o,'t1066_RP_w1_child')
vari <- t1066_RP_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_child$PCH, missing_values = NA)
ggplot(t1066_RP_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 RP, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_child$id)
t1066_ds_RP_w1$child <- car::recode(as.vector(t1066_RP_w1_child$PCH), "NA='999'")
t1066_ds_RP_w1$child <- labelled(t1066_ds_RP_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP}
vari <- t1066_ds_RP_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP}
AfterH <- table(t1066_ds_RP_w1$child)
BeforeH <- table(t1066_RP_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Not found.



## Urban China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 UCh}
opal.assign.table.tibble(o, 't1066_UCh_w1_child','10-66.1066-UrbanChina-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 UCh}
t1066_UCh_w1_child <- opal.execute(o,'t1066_UCh_w1_child')
vari <- t1066_UCh_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_child$PCH, missing_values = NA)
ggplot(t1066_UCh_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 UCh, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_child$id)
t1066_ds_UCh_w1$child <- car::recode(as.vector(t1066_UCh_w1_child$PCH), "NA='999'")
t1066_ds_UCh_w1$child <- labelled(t1066_ds_UCh_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UCh}
vari <- t1066_ds_UCh_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UCh}
AfterH <- table(t1066_ds_UCh_w1$child)
BeforeH <- table(t1066_UCh_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 


### Wave 2

Not found.



## Urban Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 UM}
opal.assign.table.tibble(o, 't1066_UM_w1_child','10-66.1066-UrbanMexico-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 UM}
t1066_UM_w1_child <- opal.execute(o,'t1066_UM_w1_child')
vari <- t1066_UM_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_child$PCH, missing_values = NA)
ggplot(t1066_UM_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is, but NA into 999`

 **R script:**

```{r harmo1 UM, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_child$id)
t1066_ds_UM_w1$child <- car::recode(as.vector(t1066_UM_w1_child$PCH), "NA='999'")
t1066_ds_UM_w1$child <- labelled(t1066_ds_UM_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UM}
vari <- t1066_ds_UM_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UM}
AfterH <- table(t1066_ds_UM_w1$child)
BeforeH <- table(t1066_UM_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Not found.


## Urban Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 UP}
opal.assign.table.tibble(o, 't1066_UP_w1_child','10-66.1066-UrbanPeru-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 UP}
t1066_UP_w1_child <- opal.execute(o,'t1066_UP_w1_child')
vari <- t1066_UP_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_child$PCH, missing_values = NA)
ggplot(t1066_UP_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is but NA into 999`

 **R script:**

```{r harmo1 UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_child$id)
t1066_ds_UP_w1$child <- car::recode(as.vector(t1066_UP_w1_child$PCH), "NA='999'")
t1066_ds_UP_w1$child <- labelled(t1066_ds_UP_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UP}
vari <- t1066_ds_UP_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UP}
AfterH <- table(t1066_ds_UP_w1$child)
BeforeH <- table(t1066_UP_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 2

Not found.


## Venezuela
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PCH`
* Label: `has children?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 Ven}
opal.assign.table.tibble(o, 't1066_Ven_w1_child','10-66.1066-Venezuela-Baseline',variables=list('PCH'), missings = TRUE)
```

```{r local1 Ven}
t1066_Ven_w1_child <- opal.execute(o,'t1066_Ven_w1_child')
vari <- t1066_Ven_w1_child$PCH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_child$PCH, missing_values = NA)
ggplot(t1066_Ven_w1_child, aes(x=factor(PCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `as it is but NA into 999`

 **R script:**

```{r harmo1 Ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_child$id)
t1066_ds_Ven_w1$child <- car::recode(as.vector(t1066_Ven_w1_child$PCH), "NA='999'")
t1066_ds_Ven_w1$child <- labelled(t1066_ds_Ven_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 Ven}
vari <- t1066_ds_Ven_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 Ven}
AfterH <- table(t1066_ds_Ven_w1$child)
BeforeH <- table(t1066_Ven_w1_child$PCH, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



### Wave 2

Not found.

```{r save,  echo=FALSE}
child <- t1066_ds_cuba_w1
save(child, file = "../RData/cuba_w1/child.RData")
rm(child)


child <- t1066_ds_india_w1
save(child, file = "../RData/india_w1/child.RData")
rm(child)


child <- t1066_ds_UCh_w1
save(child, file = "../RData/UCh_w1/child.RData")
rm(child)



child <- t1066_ds_RCh_w1
save(child, file = "../RData/RCh_w1/child.RData")
rm(child)



child <- t1066_ds_DR_w1
save(child, file = "../RData/DR_w1/child.RData")
rm(child)


child <- t1066_ds_Ven_w1
save(child, file = "../RData/Ven_w1/child.RData")
rm(child)



child <- t1066_ds_UP_w1
save(child, file = "../RData/UP_w1/child.RData")
rm(child)



child <- t1066_ds_RP_w1
save(child, file = "../RData/RP_w1/child.RData")
rm(child)



child <- t1066_ds_UM_w1
save(child, file = "../RData/UM_w1/child.RData")
rm(child)



child <- t1066_ds_RM_w1
save(child, file = "../RData/RM_w1/child.RData")
rm(child)



child <- t1066_ds_PR_w1
save(child, file = "../RData/PR_w1/child.RData")
rm(child)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
