---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/oth_famDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/oth_famDS.R')
```


<!-- ########################################################## --> 

# Data process

## Cuba
### Wave 1 

#### Study-specific variable description


| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-Cuba-Baseline`|`1066-Cuba-Baseline`|`1066-Cuba-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |


```{r assign1 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_oth_fam','10-66.1066-Cuba-Baseline',variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_cuba_w1_oth_fam <- opal.execute(o,'t1066_cuba_w1_oth_fam')
```

```{r local1 cuba, echo=F}

vari <-  t1066_cuba_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_cuba_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_cuba_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_oth_fam$id)

t1066_cuba_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_cuba_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_cuba_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_cuba_w1_oth_fam$r_sibs), "NA='-999'")
t1066_cuba_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_cuba_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_cuba_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_cuba_w1_oth_fam)[1]){
  if( t1066_cuba_w1_oth_fam$r_inlaw[i] >0 | t1066_cuba_w1_oth_fam$r_sibs[i] >0 | t1066_cuba_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_cuba_w1$oth_fam[i] = 1 }
  else if( t1066_cuba_w1_oth_fam$r_inlaw[i] == 0 & t1066_cuba_w1_oth_fam$r_sibs[i] == 0 & t1066_cuba_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_cuba_w1$oth_fam[i] = 0 }
}
  
t1066_ds_cuba_w1$oth_fam <- car::recode(as.vector(t1066_ds_cuba_w1$oth_fam), "NA='999'")
t1066_ds_cuba_w1$oth_fam <- labelled(t1066_ds_cuba_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba, echo=F}
vari <- t1066_ds_cuba_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_cuba_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description


| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-Cuba-Followup`|`1066-Cuba-Followup`|`1066-Cuba-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_oth_fam','10-66.1066-Cuba-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_cuba_w2_oth_fam <- opal.execute(o,'t1066_cuba_w2_oth_fam')
```

```{r local2 cuba, echo=F}

vari <-  t1066_cuba_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_cuba_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_cuba_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_cuba_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 cuba, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_oth_fam$id)

t1066_cuba_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_cuba_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_cuba_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_cuba_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_cuba_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_cuba_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_cuba_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_cuba_w2_oth_fam)[1]){
  if( t1066_cuba_w2_oth_fam$f_r_inlaw[i] >0 | t1066_cuba_w2_oth_fam$f_r_sibs[i] >0 | t1066_cuba_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_cuba_w2$oth_fam[i] = 1 }
  else if( t1066_cuba_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_cuba_w2_oth_fam$f_r_sibs[i] == 0 & t1066_cuba_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_cuba_w2$oth_fam[i] = 0 }
}
  
t1066_ds_cuba_w2$oth_fam <- car::recode(as.vector(t1066_ds_cuba_w2$oth_fam), "NA='999'")
t1066_ds_cuba_w2$oth_fam <- labelled(t1066_ds_cuba_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba, echo=F}
vari <- t1066_ds_cuba_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_cuba_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba, echo=F}

```

 
 





## India

### Wave 1 

#### Study-specific variable description


| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-India-Baseline`|`1066-India-Baseline`|`1066-India-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_oth_fam','10-66.1066-India-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_india_w1_oth_fam <- opal.execute(o,'t1066_india_w1_oth_fam')
```

```{r local1 india, echo=F}

vari <-  t1066_india_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_india_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_india_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_india_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_india_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_india_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_oth_fam$id)

t1066_india_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_india_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_india_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_india_w1_oth_fam$r_sibs), "NA='-999'")
t1066_india_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_india_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_india_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_india_w1_oth_fam)[1]){
  if( t1066_india_w1_oth_fam$r_inlaw[i] >0 | t1066_india_w1_oth_fam$r_sibs[i] >0 | t1066_india_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_india_w1$oth_fam[i] = 1 }
  else if( t1066_india_w1_oth_fam$r_inlaw[i] == 0 & t1066_india_w1_oth_fam$r_sibs[i] == 0 & t1066_india_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_india_w1$oth_fam[i] = 0 }
}
  
t1066_ds_india_w1$oth_fam <- car::recode(as.vector(t1066_ds_india_w1$oth_fam), "NA='999'")
t1066_ds_india_w1$oth_fam <- labelled(t1066_ds_india_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- t1066_ds_india_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_india_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}

```

 
 



 


## Urban China
### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanChina-Baseline`|`1066-UrbanChina-Baseline`|`1066-UrbanChina-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_oth_fam','10-66.1066-UrbanChina-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_UCh_w1_oth_fam <- opal.execute(o,'t1066_UCh_w1_oth_fam')
```

```{r local1 UCh, echo=F}

vari <-  t1066_UCh_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UCh_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <- t1066_UCh_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 UCh, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_oth_fam$id)

t1066_UCh_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_UCh_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_UCh_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_UCh_w1_oth_fam$r_sibs), "NA='-999'")
t1066_UCh_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_UCh_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_UCh_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UCh_w1_oth_fam)[1]){
  if( t1066_UCh_w1_oth_fam$r_inlaw[i] >0 | t1066_UCh_w1_oth_fam$r_sibs[i] >0 | t1066_UCh_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_UCh_w1$oth_fam[i] = 1 }
  else if( t1066_UCh_w1_oth_fam$r_inlaw[i] == 0 & t1066_UCh_w1_oth_fam$r_sibs[i] == 0 & t1066_UCh_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_UCh_w1$oth_fam[i] = 0 }
}
  
t1066_ds_UCh_w1$oth_fam <- car::recode(as.vector(t1066_ds_UCh_w1$oth_fam), "NA='999'")
t1066_ds_UCh_w1$oth_fam <- labelled(t1066_ds_UCh_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UCh, echo=F}
vari <- t1066_ds_UCh_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UCh_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UCh, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanChina-Followup`|`1066-UrbanChina-Followup`|`1066-UrbanChina-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_oth_fam','10-66.1066-UrbanChina-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_UCh_w2_oth_fam <- opal.execute(o,'t1066_UCh_w2_oth_fam')
```

```{r local2 UCh, echo=F}

vari <-   t1066_UCh_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UCh_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <- t1066_UCh_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UCh_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 UCh, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_oth_fam$id)

t1066_UCh_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_UCh_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_UCh_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_UCh_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_UCh_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_UCh_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_UCh_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UCh_w2_oth_fam)[1]){
  if( t1066_UCh_w2_oth_fam$f_r_inlaw[i] >0 | t1066_UCh_w2_oth_fam$f_r_sibs[i] >0 | t1066_UCh_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_UCh_w2$oth_fam[i] = 1 }
  else if( t1066_UCh_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_UCh_w2_oth_fam$f_r_sibs[i] == 0 & t1066_UCh_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_UCh_w2$oth_fam[i] = 0 }
}
  
t1066_ds_UCh_w2$oth_fam <- car::recode(as.vector(t1066_ds_UCh_w2$oth_fam), "NA='999'")
t1066_ds_UCh_w2$oth_fam <- labelled(t1066_ds_UCh_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UCh, echo=F}
vari <- t1066_ds_UCh_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UCh_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UCh, echo=F}

```

 
 



## Rural China
### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralChina-Baseline`|`1066-RuralChina-Baseline`|`1066-RuralChina-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_oth_fam','10-66.1066-RuralChina-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_RCh_w1_oth_fam <- opal.execute(o,'t1066_RCh_w1_oth_fam')
```

```{r local1 RCh, echo=F}

vari <-  t1066_RCh_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RCh_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RCh_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 RCh, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_oth_fam$id)

t1066_RCh_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_RCh_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_RCh_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_RCh_w1_oth_fam$r_sibs), "NA='-999'")
t1066_RCh_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_RCh_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_RCh_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RCh_w1_oth_fam)[1]){
  if( t1066_RCh_w1_oth_fam$r_inlaw[i] >0 | t1066_RCh_w1_oth_fam$r_sibs[i] >0 | t1066_RCh_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_RCh_w1$oth_fam[i] = 1 }
  else if( t1066_RCh_w1_oth_fam$r_inlaw[i] == 0 & t1066_RCh_w1_oth_fam$r_sibs[i] == 0 & t1066_RCh_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_RCh_w1$oth_fam[i] = 0 }
}
  
t1066_ds_RCh_w1$oth_fam <- car::recode(as.vector(t1066_ds_RCh_w1$oth_fam), "NA='999'")
t1066_ds_RCh_w1$oth_fam <- labelled(t1066_ds_RCh_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCh, echo=F}
vari <- t1066_ds_RCh_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RCh_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCh, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralChina-Followup`|`1066-RuralChina-Followup`|`1066-RuralChina-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_oth_fam','10-66.1066-RuralChina-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_RCh_w2_oth_fam <- opal.execute(o,'t1066_RCh_w2_oth_fam')
```

```{r local2 RCh, echo=F}

vari <-  t1066_RCh_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RCh_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RCh_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RCh_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 RCh, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_oth_fam$id)

t1066_RCh_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_RCh_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_RCh_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_RCh_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_RCh_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_RCh_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_RCh_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RCh_w2_oth_fam)[1]){
  if( t1066_RCh_w2_oth_fam$f_r_inlaw[i] >0 | t1066_RCh_w2_oth_fam$f_r_sibs[i] >0 | t1066_RCh_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_RCh_w2$oth_fam[i] = 1 }
  else if( t1066_RCh_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_RCh_w2_oth_fam$f_r_sibs[i] == 0 & t1066_RCh_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_RCh_w2$oth_fam[i] = 0 }
}
  
t1066_ds_RCh_w2$oth_fam <- car::recode(as.vector(t1066_ds_RCh_w2$oth_fam), "NA='999'")
t1066_ds_RCh_w2$oth_fam <- labelled(t1066_ds_RCh_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RCh, echo=F}
vari <- t1066_ds_RCh_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RCh_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RCh, echo=F}

```

 
 

## Dominican Republic

### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-DominicanRepublic-Baseline`|`1066-DominicanRepublic-Baseline`|`1066-DominicanRepublic-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_oth_fam','10-66.1066-DominicanRepublic-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_DR_w1_oth_fam <- opal.execute(o,'t1066_DR_w1_oth_fam')
```

```{r local1 DR, echo=F}

vari <-  t1066_DR_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_cuba_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_DR_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_oth_fam$id)

t1066_DR_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_DR_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_DR_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_DR_w1_oth_fam$r_sibs), "NA='-999'")
t1066_DR_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_DR_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_DR_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_DR_w1_oth_fam)[1]){
  if( t1066_DR_w1_oth_fam$r_inlaw[i] >0 | t1066_DR_w1_oth_fam$r_sibs[i] >0 | t1066_DR_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_DR_w1$oth_fam[i] = 1 }
  else if( t1066_DR_w1_oth_fam$r_inlaw[i] == 0 & t1066_DR_w1_oth_fam$r_sibs[i] == 0 & t1066_DR_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_DR_w1$oth_fam[i] = 0 }
}
  
t1066_ds_DR_w1$oth_fam <- car::recode(as.vector(t1066_ds_DR_w1$oth_fam), "NA='999'")
t1066_ds_DR_w1$oth_fam <- labelled(t1066_ds_DR_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR, echo=F}
vari <- t1066_ds_DR_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_DR_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-DominicanRepublic-Followup`|`1066-DominicanRepublic-Followup`|`1066-DominicanRepublic-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_oth_fam','10-66.1066-DominicanRepublic-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_DR_w2_oth_fam <- opal.execute(o,'t1066_DR_w2_oth_fam')
```

```{r local2 DR, echo=F}

vari <-  t1066_DR_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_DR_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_DR_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_DR_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 DR, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_oth_fam$id)

t1066_DR_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_DR_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_DR_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_DR_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_DR_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_DR_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_DR_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_DR_w2_oth_fam)[1]){
  if( t1066_DR_w2_oth_fam$f_r_inlaw[i] >0 | t1066_DR_w2_oth_fam$f_r_sibs[i] >0 | t1066_DR_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_DR_w2$oth_fam[i] = 1 }
  else if( t1066_DR_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_DR_w2_oth_fam$f_r_sibs[i] == 0 & t1066_DR_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_DR_w2$oth_fam[i] = 0 }
}
  
t1066_ds_DR_w2$oth_fam <- car::recode(as.vector(t1066_ds_DR_w2$oth_fam), "NA='999'")
t1066_ds_DR_w2$oth_fam <- labelled(t1066_ds_DR_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 DR, echo=F}
vari <- t1066_ds_DR_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_DR_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 DR, echo=F}

```





## Venezuela
### Wave 1 

#### Study-specific variable description


| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-Venezuela-Baseline`|`1066-Venezuela-Baseline`|`1066-Venezuela-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_oth_fam','10-66.1066-Venezuela-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_Ven_w1_oth_fam <- opal.execute(o,'t1066_Ven_w1_oth_fam')
```

```{r local1 Ven, echo=F}

vari <-  t1066_Ven_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_Ven_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_Ven_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 Ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_oth_fam$id)

t1066_Ven_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_Ven_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_Ven_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_Ven_w1_oth_fam$r_sibs), "NA='-999'")
t1066_Ven_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_Ven_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_Ven_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_Ven_w1_oth_fam)[1]){
  if( t1066_Ven_w1_oth_fam$r_inlaw[i] >0 | t1066_Ven_w1_oth_fam$r_sibs[i] >0 | t1066_Ven_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_Ven_w1$oth_fam[i] = 1 }
  else if( t1066_Ven_w1_oth_fam$r_inlaw[i] == 0 & t1066_Ven_w1_oth_fam$r_sibs[i] == 0 & t1066_Ven_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_Ven_w1$oth_fam[i] = 0 }
}
  
t1066_ds_Ven_w1$oth_fam <- car::recode(as.vector(t1066_ds_Ven_w1$oth_fam), "NA='999'")
t1066_ds_Ven_w1$oth_fam <- labelled(t1066_ds_Ven_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 Ven, echo=F}
vari <- t1066_ds_Ven_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_Ven_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 Ven, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-Venezuela-Followup`|`1066-Venezuela-Followup`|`1066-Venezuela-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_oth_fam','10-66.1066-Venezuela-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_Ven_w2_oth_fam <- opal.execute(o,'t1066_Ven_w2_oth_fam')
```

```{r local2 Ven, echo=F}

vari <- t1066_Ven_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-   t1066_Ven_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_Ven_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_Ven_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 Ven, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_oth_fam$id)

t1066_Ven_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_Ven_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_Ven_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_Ven_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_Ven_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_Ven_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_Ven_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_Ven_w2_oth_fam)[1]){
  if( t1066_Ven_w2_oth_fam$f_r_inlaw[i] >0 | t1066_Ven_w2_oth_fam$f_r_sibs[i] >0 | t1066_Ven_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_Ven_w2$oth_fam[i] = 1 }
  else if( t1066_Ven_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_Ven_w2_oth_fam$f_r_sibs[i] == 0 & t1066_Ven_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_Ven_w2$oth_fam[i] = 0 }
}
  
t1066_ds_Ven_w2$oth_fam <- car::recode(as.vector(t1066_ds_Ven_w2$oth_fam), "NA='999'")
t1066_ds_Ven_w2$oth_fam <- labelled(t1066_ds_Ven_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 Ven, echo=F}
vari <- t1066_ds_Ven_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_Ven_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 Ven, echo=F}

```







## Urban Peru
### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanPeru-Baseline`|`1066-UrbanPeru-Baseline`|`1066-UrbanPeru-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_oth_fam','10-66.1066-UrbanPeru-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_UP_w1_oth_fam <- opal.execute(o,'t1066_UP_w1_oth_fam')
```

```{r local1 UP, echo=F}

vari <-  t1066_UP_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UP_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_UP_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_oth_fam$id)

t1066_UP_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_UP_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_UP_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_UP_w1_oth_fam$r_sibs), "NA='-999'")
t1066_UP_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_UP_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_UP_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UP_w1_oth_fam)[1]){
  if( t1066_UP_w1_oth_fam$r_inlaw[i] >0 | t1066_UP_w1_oth_fam$r_sibs[i] >0 | t1066_UP_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_UP_w1$oth_fam[i] = 1 }
  else if( t1066_UP_w1_oth_fam$r_inlaw[i] == 0 & t1066_UP_w1_oth_fam$r_sibs[i] == 0 & t1066_UP_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_UP_w1$oth_fam[i] = 0 }
}
  
t1066_ds_UP_w1$oth_fam <- car::recode(as.vector(t1066_ds_UP_w1$oth_fam), "NA='999'")
t1066_ds_UP_w1$oth_fam <- labelled(t1066_ds_UP_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UP, echo=F}
vari <- t1066_ds_UP_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UP_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UP, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanPeru-Followup`|`1066-UrbanPeru-Followup`|`1066-UrbanPeru-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_oth_fam','10-66.1066-UrbanPeru-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_UP_w2_oth_fam <- opal.execute(o,'t1066_UP_w2_oth_fam')
```

```{r local2 UP, echo=F}

vari <- t1066_UP_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UP_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_UP_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UP_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 UP, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_oth_fam$id)

t1066_UP_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_UP_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_UP_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_UP_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_UP_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_UP_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_UP_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UP_w2_oth_fam)[1]){
  if( t1066_UP_w2_oth_fam$f_r_inlaw[i] >0 | t1066_UP_w2_oth_fam$f_r_sibs[i] >0 | t1066_UP_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_UP_w2$oth_fam[i] = 1 }
  else if( t1066_UP_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_UP_w2_oth_fam$f_r_sibs[i] == 0 & t1066_UP_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_UP_w2$oth_fam[i] = 0 }
}
  
t1066_ds_UP_w2$oth_fam <- car::recode(as.vector(t1066_ds_UP_w2$oth_fam), "NA='999'")
t1066_ds_UP_w2$oth_fam <- labelled(t1066_ds_UP_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UP, echo=F}
vari <- t1066_ds_UP_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UP_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UP, echo=F}

```

 




## Rural Peru
### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralPeru-Baseline`|`1066-RuralPeru-Baseline`|`1066-RuralPeru-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_oth_fam','10-66.1066-RuralPeru-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_RP_w1_oth_fam <- opal.execute(o,'t1066_RP_w1_oth_fam')
```

```{r local1 RP, echo=F}

vari <-  t1066_RP_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RP_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RP_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 RP, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_oth_fam$id)

t1066_RP_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_RP_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_RP_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_RP_w1_oth_fam$r_sibs), "NA='-999'")
t1066_RP_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_RP_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_RP_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RP_w1_oth_fam)[1]){
  if( t1066_RP_w1_oth_fam$r_inlaw[i] >0 | t1066_RP_w1_oth_fam$r_sibs[i] >0 | t1066_RP_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_RP_w1$oth_fam[i] = 1 }
  else if( t1066_RP_w1_oth_fam$r_inlaw[i] == 0 & t1066_RP_w1_oth_fam$r_sibs[i] == 0 & t1066_RP_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_RP_w1$oth_fam[i] = 0 }
}
  
t1066_ds_RP_w1$oth_fam <- car::recode(as.vector(t1066_ds_RP_w1$oth_fam), "NA='999'")
t1066_ds_RP_w1$oth_fam <- labelled(t1066_ds_RP_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP, echo=F}
vari <- t1066_ds_RP_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RP_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralPeru-Followup`|`1066-RuralPeru-Followup`|`1066-RuralPeru-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_oth_fam','10-66.1066-RuralPeru-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_RP_w2_oth_fam <- opal.execute(o,'t1066_RP_w2_oth_fam')
```

```{r local2 RP, echo=F}

vari <-  t1066_RP_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RP_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RP_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RP_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 RP, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_oth_fam$id)

t1066_RP_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_RP_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_RP_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_RP_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_RP_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_RP_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_RP_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RP_w2_oth_fam)[1]){
  if( t1066_RP_w2_oth_fam$f_r_inlaw[i] >0 | t1066_RP_w2_oth_fam$f_r_sibs[i] >0 | t1066_RP_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_RP_w2$oth_fam[i] = 1 }
  else if( t1066_RP_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_RP_w2_oth_fam$f_r_sibs[i] == 0 & t1066_RP_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_RP_w2$oth_fam[i] = 0 }
}
  
t1066_ds_RP_w2$oth_fam <- car::recode(as.vector(t1066_ds_RP_w2$oth_fam), "NA='999'")
t1066_ds_RP_w2$oth_fam <- labelled(t1066_ds_RP_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RP, echo=F}
vari <- t1066_ds_RP_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RP_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RP, echo=F}

```

 
 


## Urban Mexico
### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanMexico-Baseline`|`1066-UrbanMexico-Baseline`|`1066-UrbanMexico-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_oth_fam','10-66.1066-UrbanMexico-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_UM_w1_oth_fam <- opal.execute(o,'t1066_UM_w1_oth_fam')
```

```{r local1 UM, echo=F}

vari <- t1066_UM_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UM_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_UM_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 UM, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_oth_fam$id)

t1066_UM_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_UM_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_UM_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_UM_w1_oth_fam$r_sibs), "NA='-999'")
t1066_UM_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_UM_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_UM_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UM_w1_oth_fam)[1]){
  if( t1066_UM_w1_oth_fam$r_inlaw[i] >0 | t1066_UM_w1_oth_fam$r_sibs[i] >0 | t1066_UM_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_UM_w1$oth_fam[i] = 1 }
  else if( t1066_UM_w1_oth_fam$r_inlaw[i] == 0 & t1066_UM_w1_oth_fam$r_sibs[i] == 0 & t1066_UM_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_UM_w1$oth_fam[i] = 0 }
}
  
t1066_ds_UM_w1$oth_fam <- car::recode(as.vector(t1066_ds_UM_w1$oth_fam), "NA='999'")
t1066_ds_UM_w1$oth_fam <- labelled(t1066_ds_UM_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 UM, echo=F}
vari <- t1066_ds_UM_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UM_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UM, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-UrbanMexico-Followup`|`1066-UrbanMexico-Followup`|`1066-UrbanMexico-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |
 
```{r assign2 UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_oth_fam','10-66.1066-UrbanMexico-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_UM_w2_oth_fam <- opal.execute(o,'t1066_UM_w2_oth_fam')
```

```{r local2 UM, echo=F}

vari <-  t1066_UM_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_UM_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_UM_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_UM_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 UM, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_oth_fam$id)

t1066_UM_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_UM_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_UM_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_UM_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_UM_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_UM_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_UM_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_UM_w2_oth_fam)[1]){
  if( t1066_UM_w2_oth_fam$f_r_inlaw[i] >0 | t1066_UM_w2_oth_fam$f_r_sibs[i] >0 | t1066_UM_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_UM_w2$oth_fam[i] = 1 }
  else if( t1066_UM_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_UM_w2_oth_fam$f_r_sibs[i] == 0 & t1066_UM_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_UM_w2$oth_fam[i] = 0 }
}
  
t1066_ds_UM_w2$oth_fam <- car::recode(as.vector(t1066_ds_UM_w2$oth_fam), "NA='999'")
t1066_ds_UM_w2$oth_fam <- labelled(t1066_ds_UM_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 UM, echo=F}
vari <- t1066_ds_UM_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_UM_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UM, echo=F}

```

 



## Rural Mexico

### Wave 1 

#### Study-specific variable description



| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralMexico-Baseline`|`1066-RuralMexico-Baseline`|`1066-RuralMexico-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_oth_fam','10-66.1066-RuralMexico-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_RM_w1_oth_fam <- opal.execute(o,'t1066_RM_w1_oth_fam')
```

```{r local1 RM, echo=F}

vari <-  t1066_RM_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#(var = t1066_RM_w1_oth_fam$r_inlaw, missing_values = NA)
ggplot(t1066_RM_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RM_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RM_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RM_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RM_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 RM, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_oth_fam$id)

t1066_RM_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_RM_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_RM_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_RM_w1_oth_fam$r_sibs), "NA='-999'")
t1066_RM_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_RM_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_RM_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RM_w1_oth_fam)[1]){
  if( t1066_RM_w1_oth_fam$r_inlaw[i] >0 | t1066_RM_w1_oth_fam$r_sibs[i] >0 | t1066_RM_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_RM_w1$oth_fam[i] = 1 }
  else if( t1066_RM_w1_oth_fam$r_inlaw[i] == 0 & t1066_RM_w1_oth_fam$r_sibs[i] == 0 & t1066_RM_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_RM_w1$oth_fam[i] = 0 }
}
  
t1066_ds_RM_w1$oth_fam <- car::recode(as.vector(t1066_ds_RM_w1$oth_fam), "NA='999'")
t1066_ds_RM_w1$oth_fam <- labelled(t1066_ds_RM_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 RM, echo=F}
vari <- t1066_ds_RM_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RM_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RM, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-RuralMexico-Followup`|`1066-RuralMexico-Followup`|`1066-RuralMexico-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_oth_fam','10-66.1066-RuralMexico-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_RM_w2_oth_fam <- opal.execute(o,'t1066_RM_w2_oth_fam')
```

```{r local2 RM, echo=F}

vari <-  t1066_RM_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RM_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_RM_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RM_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_RM_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_RM_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 RM, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_oth_fam$id)

t1066_RM_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_RM_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_RM_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_RM_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_RM_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_RM_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_RM_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_RM_w2_oth_fam)[1]){
  if( t1066_RM_w2_oth_fam$f_r_inlaw[i] >0 | t1066_RM_w2_oth_fam$f_r_sibs[i] >0 | t1066_RM_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_RM_w2$oth_fam[i] = 1 }
  else if( t1066_RM_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_RM_w2_oth_fam$f_r_sibs[i] == 0 & t1066_RM_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_RM_w2$oth_fam[i] = 0 }
}
  
t1066_ds_RM_w2$oth_fam <- car::recode(as.vector(t1066_ds_RM_w2$oth_fam), "NA='999'")
t1066_ds_RM_w2$oth_fam <- labelled(t1066_ds_RM_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 RM, echo=F}
vari <- t1066_ds_RM_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_RM_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RM, echo=F}

```

 
 
 




## Puerto Rico
### Wave 1 

#### Study-specific variable description


| **Name** |`r_inlaw`|`r_othrel`|`r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-PuertoRico-Baseline`|`1066-PuertoRico-Baseline`|`1066-PuertoRico-Baseline`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign1 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_oth_fam','10-66.1066-PuertoRico-Baseline', 
                        variables=list('r_inlaw','r_othrel','r_sibs'), missings = TRUE)
t1066_PR_w1_oth_fam <- opal.execute(o,'t1066_PR_w1_oth_fam')
```

```{r local1 PR, echo=F}

vari <-  t1066_PR_w1_oth_fam$r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w1_oth_fam, aes(x=factor(r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_PR_w1_oth_fam$r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w1_oth_fam, aes(x=factor(r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_PR_w1_oth_fam$r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w1_oth_fam, aes(x=factor(r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo1 PR, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_oth_fam$id)

t1066_PR_w1_oth_fam$r_inlaw <- car::recode(as.vector(t1066_PR_w1_oth_fam$r_inlaw), "NA='-999'")
t1066_PR_w1_oth_fam$r_sibs <- car::recode(as.vector(t1066_PR_w1_oth_fam$r_sibs), "NA='-999'")
t1066_PR_w1_oth_fam$r_othrel <- car::recode(as.vector(t1066_PR_w1_oth_fam$r_othrel), "NA='-999'")

t1066_ds_PR_w1$oth_fam <- c(NA)  
for(i in 1:dim(t1066_PR_w1_oth_fam)[1]){
  if( t1066_PR_w1_oth_fam$r_inlaw[i] >0 | t1066_PR_w1_oth_fam$r_sibs[i] >0 | t1066_PR_w1_oth_fam$r_othrel[i] >0 ){
    t1066_ds_PR_w1$oth_fam[i] = 1 }
  else if( t1066_PR_w1_oth_fam$r_inlaw[i] == 0 & t1066_PR_w1_oth_fam$r_sibs[i] == 0 & t1066_PR_w1_oth_fam$r_othrel[i] == 0 ){
    t1066_ds_PR_w1$oth_fam[i] = 0 }
}
  
t1066_ds_PR_w1$oth_fam <- car::recode(as.vector(t1066_ds_PR_w1$oth_fam), "NA='999'")
t1066_ds_PR_w1$oth_fam <- labelled(t1066_ds_PR_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR, echo=F}
vari <- t1066_ds_PR_w1$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_PR_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description




| **Name** |`f_r_inlaw`|`f_r_othrel`|`f_r_sibs`|
|-|-|-|-|
| **Label** |`number of coresident sons and daughters-in-law`|`number of coresident other relatives`|`number of coresident siblings`|
| **Table name** |`1066-PuertoRico-Followup`|`1066-PuertoRico-Followup`|`1066-PuertoRico-Followup`|
| **Units** |`people`|`people`|`people`|
| **Description** |  |  |  |

```{r assign2 PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_oth_fam','10-66.1066-PuertoRico-Followup', 
                        variables=list('f_r_inlaw','f_r_othrel','f_r_sibs'), missings = TRUE)
t1066_PR_w2_oth_fam <- opal.execute(o,'t1066_PR_w2_oth_fam')
```

```{r local2 PR, echo=F}

vari <- t1066_PR_w2_oth_fam$f_r_inlaw
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w2_oth_fam, aes(x=factor(f_r_inlaw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident sons and daughters-in-law") + ylab("Frequency")

vari <-  t1066_PR_w2_oth_fam$f_r_othrel
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w2_oth_fam, aes(x=factor(f_r_othrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident other relatives") + ylab("Frequency")

vari <-  t1066_PR_w2_oth_fam$f_r_sibs
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")

ggplot(t1066_PR_w2_oth_fam, aes(x=factor(f_r_sibs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("number of coresident siblings") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any > 0 then 1`
* `if all then 0`
* `NA into 999`

**R script:**

```{r harmo2 PR, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_oth_fam$id)

t1066_PR_w2_oth_fam$f_r_inlaw <- car::recode(as.vector(t1066_PR_w2_oth_fam$f_r_inlaw), "NA='-999'")
t1066_PR_w2_oth_fam$f_r_sibs <- car::recode(as.vector(t1066_PR_w2_oth_fam$f_r_sibs), "NA='-999'")
t1066_PR_w2_oth_fam$f_r_othrel <- car::recode(as.vector(t1066_PR_w2_oth_fam$f_r_othrel), "NA='-999'")

t1066_ds_PR_w2$oth_fam <- c(NA)  
for(i in 1:dim(t1066_PR_w2_oth_fam)[1]){
  if( t1066_PR_w2_oth_fam$f_r_inlaw[i] >0 | t1066_PR_w2_oth_fam$f_r_sibs[i] >0 | t1066_PR_w2_oth_fam$f_r_othrel[i] >0 ){
    t1066_ds_PR_w2$oth_fam[i] = 1 }
  else if( t1066_PR_w2_oth_fam$f_r_inlaw[i] == 0 & t1066_PR_w2_oth_fam$f_r_sibs[i] == 0 & t1066_PR_w2_oth_fam$f_r_othrel[i] == 0 ){
    t1066_ds_PR_w2$oth_fam[i] = 0 }
}
  
t1066_ds_PR_w2$oth_fam <- car::recode(as.vector(t1066_ds_PR_w2$oth_fam), "NA='999'")
t1066_ds_PR_w2$oth_fam <- labelled(t1066_ds_PR_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 PR, echo=F}
vari <- t1066_ds_PR_w2$oth_fam
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(t1066_ds_PR_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 PR, echo=F}

```

 








## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```



# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
