---
title: "Frequency of face to face and phone contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_cont_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_cont_frDS.R')
```

# Data process


## Cuba

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-Cuba-Baseline`|`1066-Cuba-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign1_cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')
```

```{r local1_cuba, echo=F}
vbl <- t1066_cuba_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_cuba_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_cuba}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)

t1066_cuba_w1$PFRD <- car::recode(as.vector(t1066_cuba_w1$PFRD), "NA='-999'")
t1066_cuba_w1$PFRDFRQ <- car::recode(as.vector(t1066_cuba_w1$PFRDFRQ), "NA='-999'")

t1066_ds_cuba_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_cuba_w1)[1]){
  if( t1066_cuba_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_cuba_w1$f_cont_fr[i] = 1 }
  else if( t1066_cuba_w1$PFRDFRQ[i] == 3 ) { t1066_ds_cuba_w1$f_cont_fr[i] = 2 }
  else if( t1066_cuba_w1$PFRDFRQ[i] == 4 ) { t1066_ds_cuba_w1$f_cont_fr[i] = 3 }
  else if( t1066_cuba_w1$PFRDFRQ[i] == 5 ) { t1066_ds_cuba_w1$f_cont_fr[i] = 4 }
  else if( t1066_cuba_w1$PFRDFRQ[i] == 0 | t1066_cuba_w1$PFRD[i] == 0 ) { t1066_ds_cuba_w1$f_cont_fr[i] = 5 }
}
t1066_ds_cuba_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_cuba_w1$f_cont_fr), "NA='999'")
t1066_ds_cuba_w1$f_cont_fr <- labelled(t1066_ds_cuba_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_cuba, echo=F}
vbl <- t1066_ds_cuba_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_cuba, echo=F}

```





### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-Cuba-Followup`|`1066-Cuba-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign2_cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_cuba, echo=F}
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
vbl <- t1066_cuba_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_cuba_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_cuba}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)

t1066_cuba_w2$f_PFRD <- car::recode(as.vector(t1066_cuba_w2$f_PFRD), "NA='-999'")
t1066_cuba_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_cuba_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_cuba_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_cuba_w2)[1]){
  if( t1066_cuba_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_cuba_w2$f_cont_fr[i] = 1 }
  else if( t1066_cuba_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_cuba_w2$f_cont_fr[i] = 2 }
  else if( t1066_cuba_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_cuba_w2$f_cont_fr[i] = 3 }
  else if( t1066_cuba_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_cuba_w2$f_cont_fr[i] = 4 }
  else if( t1066_cuba_w2$f_PFRDFRQ[i] == 0 | t1066_cuba_w2$f_PFRD[i] == 0 ) { t1066_ds_cuba_w2$f_cont_fr[i] = 5 }
}
t1066_ds_cuba_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_cuba_w2$f_cont_fr), "NA='999'")
t1066_ds_cuba_w2$f_cont_fr <- labelled(t1066_ds_cuba_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_cuba, echo=F}
vbl <- t1066_ds_cuba_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_cuba, echo=F}

```





## Dominican Republic

### Wave 1 

#### Study-specific variable description



| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-DominicanRepublic-Baseline`|`1066-DominicanRepublic-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_DR, echo=F}
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')
vbl <- t1066_DR_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_DR_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_DR}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)

t1066_DR_w1$PFRD <- car::recode(as.vector(t1066_DR_w1$PFRD), "NA='-999'")
t1066_DR_w1$PFRDFRQ <- car::recode(as.vector(t1066_DR_w1$PFRDFRQ), "NA='-999'")

t1066_ds_DR_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_DR_w1)[1]){
  if( t1066_DR_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_DR_w1$f_cont_fr[i] = 1 }
  else if( t1066_DR_w1$PFRDFRQ[i] == 3 ) { t1066_ds_DR_w1$f_cont_fr[i] = 2 }
  else if( t1066_DR_w1$PFRDFRQ[i] == 4 ) { t1066_ds_DR_w1$f_cont_fr[i] = 3 }
  else if( t1066_DR_w1$PFRDFRQ[i] == 5 ) { t1066_ds_DR_w1$f_cont_fr[i] = 4 }
  else if( t1066_DR_w1$PFRDFRQ[i] == 0 | t1066_DR_w1$PFRD[i] == 0 ) { t1066_ds_DR_w1$f_cont_fr[i] = 5 }
}
t1066_ds_DR_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_DR_w1$f_cont_fr), "NA='999'")
t1066_ds_DR_w1$f_cont_fr <- labelled(t1066_ds_DR_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_DR, echo=F}
vbl <- t1066_ds_DR_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_DR, echo=F}

```






### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-DominicanRepublic-Followup`|`1066-DominicanRepublic-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign2_DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_DR, echo=F}
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
vbl <- t1066_DR_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_DR_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_DR}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)

t1066_DR_w2$f_PFRD <- car::recode(as.vector(t1066_DR_w2$f_PFRD), "NA='-999'")
t1066_DR_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_DR_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_DR_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_DR_w2)[1]){
  if( t1066_DR_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_DR_w2$f_cont_fr[i] = 1 }
  else if( t1066_DR_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_DR_w2$f_cont_fr[i] = 2 }
  else if( t1066_DR_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_DR_w2$f_cont_fr[i] = 3 }
  else if( t1066_DR_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_DR_w2$f_cont_fr[i] = 4 }
  else if( t1066_DR_w2$f_PFRDFRQ[i] == 0 | t1066_DR_w2$f_PFRD[i] == 0 ) { t1066_ds_DR_w2$f_cont_fr[i] = 5 }
}
t1066_ds_DR_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_DR_w2$f_cont_fr), "NA='999'")
t1066_ds_DR_w2$f_cont_fr <- labelled(t1066_ds_DR_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_DR, echo=F}
vbl <- t1066_ds_DR_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_DR, echo=F}

```







## India

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-India-Baseline`|`1066-India-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_india, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_india, echo=F}
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')
vbl <- t1066_india_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_india_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_india}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)

t1066_india_w1$PFRD <- car::recode(as.vector(t1066_india_w1$PFRD), "NA='-999'")
t1066_india_w1$PFRDFRQ <- car::recode(as.vector(t1066_india_w1$PFRDFRQ), "NA='-999'")

t1066_ds_india_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_india_w1)[1]){
  if( t1066_india_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_india_w1$f_cont_fr[i] = 1 }
  else if( t1066_india_w1$PFRDFRQ[i] == 3 ) { t1066_ds_india_w1$f_cont_fr[i] = 2 }
  else if( t1066_india_w1$PFRDFRQ[i] == 4 ) { t1066_ds_india_w1$f_cont_fr[i] = 3 }
  else if( t1066_india_w1$PFRDFRQ[i] == 5 ) { t1066_ds_india_w1$f_cont_fr[i] = 4 }
  else if( t1066_india_w1$PFRDFRQ[i] == 0 | t1066_india_w1$PFRD[i] == 0 ) { t1066_ds_india_w1$f_cont_fr[i] = 5 }
}
t1066_ds_india_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_india_w1$f_cont_fr), "NA='999'")
t1066_ds_india_w1$f_cont_fr <- labelled(t1066_ds_india_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_india, echo=F}
vbl <- t1066_ds_india_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_india, echo=F}

```




## Puerto Rico

### Wave 1 

#### Study-specific variable description



| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-PuertoRico-Baseline`|`1066-PuertoRico-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |

```{r assign1_PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_PR, echo=F}
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')
vbl <- t1066_PR_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_PR_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_PR}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)

t1066_PR_w1$PFRD <- car::recode(as.vector(t1066_PR_w1$PFRD), "NA='-999'")
t1066_PR_w1$PFRDFRQ <- car::recode(as.vector(t1066_PR_w1$PFRDFRQ), "NA='-999'")

t1066_ds_PR_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_PR_w1)[1]){
  if( t1066_PR_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_PR_w1$f_cont_fr[i] = 1 }
  else if( t1066_PR_w1$PFRDFRQ[i] == 3 ) { t1066_ds_PR_w1$f_cont_fr[i] = 2 }
  else if( t1066_PR_w1$PFRDFRQ[i] == 4 ) { t1066_ds_PR_w1$f_cont_fr[i] = 3 }
  else if( t1066_PR_w1$PFRDFRQ[i] == 5 ) { t1066_ds_PR_w1$f_cont_fr[i] = 4 }
  else if( t1066_PR_w1$PFRDFRQ[i] == 0 | t1066_PR_w1$PFRD[i] == 0 ) { t1066_ds_PR_w1$f_cont_fr[i] = 5 }
}
t1066_ds_PR_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_PR_w1$f_cont_fr), "NA='999'")
t1066_ds_PR_w1$f_cont_fr <- labelled(t1066_ds_PR_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_PR, echo=F}
vbl <- t1066_ds_PR_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_PR, echo=F}

```





### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-PuertoRico-Followup`|`1066-PuertoRico-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |

```{r assign2_PR, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_PR, echo=F}
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')
vbl <- t1066_PR_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_PR_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_PR}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)

t1066_PR_w2$f_PFRD <- car::recode(as.vector(t1066_PR_w2$f_PFRD), "NA='-999'")
t1066_PR_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_PR_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_PR_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_PR_w2)[1]){
  if( t1066_PR_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_PR_w2$f_cont_fr[i] = 1 }
  else if( t1066_PR_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_PR_w2$f_cont_fr[i] = 2 }
  else if( t1066_PR_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_PR_w2$f_cont_fr[i] = 3 }
  else if( t1066_PR_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_PR_w2$f_cont_fr[i] = 4 }
  else if( t1066_PR_w2$f_PFRDFRQ[i] == 0 | t1066_PR_w2$f_PFRD[i] == 0 ) { t1066_ds_PR_w2$f_cont_fr[i] = 5 }
}
t1066_ds_PR_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_PR_w2$f_cont_fr), "NA='999'")
t1066_ds_PR_w2$f_cont_fr <- labelled(t1066_ds_PR_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_PR, echo=F}
vbl <- t1066_ds_PR_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_PR, echo=F}

```




## Rural China

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralChina-Baseline`|`1066-RuralChina-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_RCh, echo=F}
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')
vbl <- t1066_RCh_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RCh_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_RCh}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)

t1066_RCh_w1$PFRD <- car::recode(as.vector(t1066_RCh_w1$PFRD), "NA='-999'")
t1066_RCh_w1$PFRDFRQ <- car::recode(as.vector(t1066_RCh_w1$PFRDFRQ), "NA='-999'")

t1066_ds_RCh_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RCh_w1)[1]){
  if( t1066_RCh_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RCh_w1$f_cont_fr[i] = 1 }
  else if( t1066_RCh_w1$PFRDFRQ[i] == 3 ) { t1066_ds_RCh_w1$f_cont_fr[i] = 2 }
  else if( t1066_RCh_w1$PFRDFRQ[i] == 4 ) { t1066_ds_RCh_w1$f_cont_fr[i] = 3 }
  else if( t1066_RCh_w1$PFRDFRQ[i] == 5 ) { t1066_ds_RCh_w1$f_cont_fr[i] = 4 }
  else if( t1066_RCh_w1$PFRDFRQ[i] == 0 | t1066_RCh_w1$PFRD[i] == 0 ) { t1066_ds_RCh_w1$f_cont_fr[i] = 5 }
}
t1066_ds_RCh_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_RCh_w1$f_cont_fr), "NA='999'")
t1066_ds_RCh_w1$f_cont_fr <- labelled(t1066_ds_RCh_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_RCh, echo=F}
vbl <- t1066_ds_RCh_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_RCh, echo=F}

```






### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralChina-Followup`|`1066-RuralChina-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign2_RCh, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_RCh, echo=F}
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')
vbl <- t1066_RCh_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RCh_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_RCh}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)

t1066_RCh_w2$f_PFRD <- car::recode(as.vector(t1066_RCh_w2$f_PFRD), "NA='-999'")
t1066_RCh_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_RCh_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_RCh_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RCh_w2)[1]){
  if( t1066_RCh_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RCh_w2$f_cont_fr[i] = 1 }
  else if( t1066_RCh_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_RCh_w2$f_cont_fr[i] = 2 }
  else if( t1066_RCh_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_RCh_w2$f_cont_fr[i] = 3 }
  else if( t1066_RCh_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_RCh_w2$f_cont_fr[i] = 4 }
  else if( t1066_RCh_w2$f_PFRDFRQ[i] == 0 | t1066_RCh_w2$f_PFRD[i] == 0 ) { t1066_ds_RCh_w2$f_cont_fr[i] = 5 }
}
t1066_ds_RCh_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_RCh_w2$f_cont_fr), "NA='999'")
t1066_ds_RCh_w2$f_cont_fr <- labelled(t1066_ds_RCh_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_RCh, echo=F}
vbl <- t1066_ds_RCh_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_RCh, echo=F}

```





## Rural Mexico

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralMexico-Baseline`|`1066-RuralMexico-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_RM, echo=F}
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')
vbl <- t1066_RM_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RM_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_RM}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)

t1066_RM_w1$PFRD <- car::recode(as.vector(t1066_RM_w1$PFRD), "NA='-999'")
t1066_RM_w1$PFRDFRQ <- car::recode(as.vector(t1066_RM_w1$PFRDFRQ), "NA='-999'")

t1066_ds_RM_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RM_w1)[1]){
  if( t1066_RM_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RM_w1$f_cont_fr[i] = 1 }
  else if( t1066_RM_w1$PFRDFRQ[i] == 3 ) { t1066_ds_RM_w1$f_cont_fr[i] = 2 }
  else if( t1066_RM_w1$PFRDFRQ[i] == 4 ) { t1066_ds_RM_w1$f_cont_fr[i] = 3 }
  else if( t1066_RM_w1$PFRDFRQ[i] == 5 ) { t1066_ds_RM_w1$f_cont_fr[i] = 4 }
  else if( t1066_RM_w1$PFRDFRQ[i] == 0 | t1066_RM_w1$PFRD[i] == 0 ) { t1066_ds_RM_w1$f_cont_fr[i] = 5 }
}
t1066_ds_RM_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_RM_w1$f_cont_fr), "NA='999'")
t1066_ds_RM_w1$f_cont_fr <- labelled(t1066_ds_RM_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_RM, echo=F}
vbl <- t1066_ds_RM_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_RM, echo=F}

```






### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralMexico-Followup`|`1066-RuralMexico-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign2_RM, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_RM, echo=F}
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')
vbl <- t1066_RM_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RM_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_RM}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)

t1066_RM_w2$f_PFRD <- car::recode(as.vector(t1066_RM_w2$f_PFRD), "NA='-999'")
t1066_RM_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_RM_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_RM_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RM_w2)[1]){
  if( t1066_RM_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RM_w2$f_cont_fr[i] = 1 }
  else if( t1066_RM_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_RM_w2$f_cont_fr[i] = 2 }
  else if( t1066_RM_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_RM_w2$f_cont_fr[i] = 3 }
  else if( t1066_RM_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_RM_w2$f_cont_fr[i] = 4 }
  else if( t1066_RM_w2$f_PFRDFRQ[i] == 0 | t1066_RM_w2$f_PFRD[i] == 0 ) { t1066_ds_RM_w2$f_cont_fr[i] = 5 }
}
t1066_ds_RM_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_RM_w2$f_cont_fr), "NA='999'")
t1066_ds_RM_w2$f_cont_fr <- labelled(t1066_ds_RM_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_RM, echo=F}
vbl <- t1066_ds_RM_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_RM, echo=F}

```





## Rural Peru

### Wave 1  

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralPeru-Baseline`|`1066-RuralPeru-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign1_RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_RP, echo=F}
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')
vbl <- t1066_RP_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RP_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_RP}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)

t1066_RP_w1$PFRD <- car::recode(as.vector(t1066_RP_w1$PFRD), "NA='-999'")
t1066_RP_w1$PFRDFRQ <- car::recode(as.vector(t1066_RP_w1$PFRDFRQ), "NA='-999'")

t1066_ds_RP_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RP_w1)[1]){
  if( t1066_RP_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RP_w1$f_cont_fr[i] = 1 }
  else if( t1066_RP_w1$PFRDFRQ[i] == 3 ) { t1066_ds_RP_w1$f_cont_fr[i] = 2 }
  else if( t1066_RP_w1$PFRDFRQ[i] == 4 ) { t1066_ds_RP_w1$f_cont_fr[i] = 3 }
  else if( t1066_RP_w1$PFRDFRQ[i] == 5 ) { t1066_ds_RP_w1$f_cont_fr[i] = 4 }
  else if( t1066_RP_w1$PFRDFRQ[i] == 0 | t1066_RP_w1$PFRD[i] == 0 ) { t1066_ds_RP_w1$f_cont_fr[i] = 5 }
}
t1066_ds_RP_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_RP_w1$f_cont_fr), "NA='999'")
t1066_ds_RP_w1$f_cont_fr <- labelled(t1066_ds_RP_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_RP, echo=F}
vbl <- t1066_ds_RP_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_RP, echo=F}

```






### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-RuralPeru-Followup`|`1066-RuralPeru-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |

```{r assign2_RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_RP, echo=F}
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
vbl <- t1066_RP_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_RP_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_RP}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)

t1066_RP_w2$f_PFRD <- car::recode(as.vector(t1066_RP_w2$f_PFRD), "NA='-999'")
t1066_RP_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_RP_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_RP_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_RP_w2)[1]){
  if( t1066_RP_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_RP_w2$f_cont_fr[i] = 1 }
  else if( t1066_RP_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_RP_w2$f_cont_fr[i] = 2 }
  else if( t1066_RP_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_RP_w2$f_cont_fr[i] = 3 }
  else if( t1066_RP_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_RP_w2$f_cont_fr[i] = 4 }
  else if( t1066_RP_w2$f_PFRDFRQ[i] == 0 | t1066_RP_w2$f_PFRD[i] == 0 ) { t1066_ds_RP_w2$f_cont_fr[i] = 5 }
}
t1066_ds_RP_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_RP_w2$f_cont_fr), "NA='999'")
t1066_ds_RP_w2$f_cont_fr <- labelled(t1066_ds_RP_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_RP, echo=F}
vbl <- t1066_ds_RP_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_RP, echo=F}

```






## Urban China

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanChina-Baseline`|`1066-UrbanChina-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign1_UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_UCh, echo=F}
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')
vbl <- t1066_UCh_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UCh_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_UCh}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)

t1066_UCh_w1$PFRD <- car::recode(as.vector(t1066_UCh_w1$PFRD), "NA='-999'")
t1066_UCh_w1$PFRDFRQ <- car::recode(as.vector(t1066_UCh_w1$PFRDFRQ), "NA='-999'")

t1066_ds_UCh_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UCh_w1)[1]){
  if( t1066_UCh_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UCh_w1$f_cont_fr[i] = 1 }
  else if( t1066_UCh_w1$PFRDFRQ[i] == 3 ) { t1066_ds_UCh_w1$f_cont_fr[i] = 2 }
  else if( t1066_UCh_w1$PFRDFRQ[i] == 4 ) { t1066_ds_UCh_w1$f_cont_fr[i] = 3 }
  else if( t1066_UCh_w1$PFRDFRQ[i] == 5 ) { t1066_ds_UCh_w1$f_cont_fr[i] = 4 }
  else if( t1066_UCh_w1$PFRDFRQ[i] == 0 | t1066_UCh_w1$PFRD[i] == 0 ) { t1066_ds_UCh_w1$f_cont_fr[i] = 5 }
}
t1066_ds_UCh_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_UCh_w1$f_cont_fr), "NA='999'")
t1066_ds_UCh_w1$f_cont_fr <- labelled(t1066_ds_UCh_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_UCh, echo=F}
vbl <- t1066_ds_UCh_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_UCh, echo=F}

```







### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanChina-Followup`|`1066-UrbanChina-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign2_UCh, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_UCh, echo=F}
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
vbl <- t1066_UCh_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UCh_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_UCh}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)

t1066_UCh_w2$f_PFRD <- car::recode(as.vector(t1066_UCh_w2$f_PFRD), "NA='-999'")
t1066_UCh_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_UCh_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_UCh_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UCh_w2)[1]){
  if( t1066_UCh_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UCh_w2$f_cont_fr[i] = 1 }
  else if( t1066_UCh_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_UCh_w2$f_cont_fr[i] = 2 }
  else if( t1066_UCh_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_UCh_w2$f_cont_fr[i] = 3 }
  else if( t1066_UCh_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_UCh_w2$f_cont_fr[i] = 4 }
  else if( t1066_UCh_w2$f_PFRDFRQ[i] == 0 | t1066_UCh_w2$f_PFRD[i] == 0 ) { t1066_ds_UCh_w2$f_cont_fr[i] = 5 }
}
t1066_ds_UCh_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_UCh_w2$f_cont_fr), "NA='999'")
t1066_ds_UCh_w2$f_cont_fr <- labelled(t1066_ds_UCh_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_UCh, echo=F}
vbl <- t1066_ds_UCh_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_UCh, echo=F}

```





## Urban Mexico

### Wave 1  

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanMexico-Baseline`|`1066-UrbanMexico-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_UM, echo=F}
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')
vbl <- t1066_UM_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UM_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_UM}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)

t1066_UM_w1$PFRD <- car::recode(as.vector(t1066_UM_w1$PFRD), "NA='-999'")
t1066_UM_w1$PFRDFRQ <- car::recode(as.vector(t1066_UM_w1$PFRDFRQ), "NA='-999'")

t1066_ds_UM_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UM_w1)[1]){
  if( t1066_UM_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UM_w1$f_cont_fr[i] = 1 }
  else if( t1066_UM_w1$PFRDFRQ[i] == 3 ) { t1066_ds_UM_w1$f_cont_fr[i] = 2 }
  else if( t1066_UM_w1$PFRDFRQ[i] == 4 ) { t1066_ds_UM_w1$f_cont_fr[i] = 3 }
  else if( t1066_UM_w1$PFRDFRQ[i] == 5 ) { t1066_ds_UM_w1$f_cont_fr[i] = 4 }
  else if( t1066_UM_w1$PFRDFRQ[i] == 0 | t1066_UM_w1$PFRD[i] == 0 ) { t1066_ds_UM_w1$f_cont_fr[i] = 5 }
}
t1066_ds_UM_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_UM_w1$f_cont_fr), "NA='999'")
t1066_ds_UM_w1$f_cont_fr <- labelled(t1066_ds_UM_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_UM, echo=F}
vbl <- t1066_ds_UM_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_UM, echo=F}

```





### Wave 2

#### Study-specific variable description



| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanMexico-Followup`|`1066-UrbanMexico-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign2_UM, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_UM, echo=F}
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')
vbl <- t1066_UM_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UM_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_UM}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)

t1066_UM_w2$f_PFRD <- car::recode(as.vector(t1066_UM_w2$f_PFRD), "NA='-999'")
t1066_UM_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_UM_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_UM_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UM_w2)[1]){
  if( t1066_UM_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UM_w2$f_cont_fr[i] = 1 }
  else if( t1066_UM_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_UM_w2$f_cont_fr[i] = 2 }
  else if( t1066_UM_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_UM_w2$f_cont_fr[i] = 3 }
  else if( t1066_UM_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_UM_w2$f_cont_fr[i] = 4 }
  else if( t1066_UM_w2$f_PFRDFRQ[i] == 0 | t1066_UM_w2$f_PFRD[i] == 0 ) { t1066_ds_UM_w2$f_cont_fr[i] = 5 }
}
t1066_ds_UM_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_UM_w2$f_cont_fr), "NA='999'")
t1066_ds_UM_w2$f_cont_fr <- labelled(t1066_ds_UM_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_UM, echo=F}
vbl <- t1066_ds_UM_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_UM, echo=F}

```





## Urban Peru

### Wave 1 

#### Study-specific variable description


| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanPeru-Baseline`|`1066-UrbanPeru-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign1_UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_UP, echo=F}
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')
vbl <- t1066_UP_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UP_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_UP}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)

t1066_UP_w1$PFRD <- car::recode(as.vector(t1066_UP_w1$PFRD), "NA='-999'")
t1066_UP_w1$PFRDFRQ <- car::recode(as.vector(t1066_UP_w1$PFRDFRQ), "NA='-999'")

t1066_ds_UP_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UP_w1)[1]){
  if( t1066_UP_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UP_w1$f_cont_fr[i] = 1 }
  else if( t1066_UP_w1$PFRDFRQ[i] == 3 ) { t1066_ds_UP_w1$f_cont_fr[i] = 2 }
  else if( t1066_UP_w1$PFRDFRQ[i] == 4 ) { t1066_ds_UP_w1$f_cont_fr[i] = 3 }
  else if( t1066_UP_w1$PFRDFRQ[i] == 5 ) { t1066_ds_UP_w1$f_cont_fr[i] = 4 }
  else if( t1066_UP_w1$PFRDFRQ[i] == 0 | t1066_UP_w1$PFRD[i] == 0 ) { t1066_ds_UP_w1$f_cont_fr[i] = 5 }
}
t1066_ds_UP_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_UP_w1$f_cont_fr), "NA='999'")
t1066_ds_UP_w1$f_cont_fr <- labelled(t1066_ds_UP_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_UP, echo=F}
vbl <- t1066_ds_UP_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_UP, echo=F}

```





### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-UrbanPeru-Followup`|`1066-UrbanPeru-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign2_UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_UP, echo=F}
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')
vbl <- t1066_UP_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_UP_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_UP}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)

t1066_UP_w2$f_PFRD <- car::recode(as.vector(t1066_UP_w2$f_PFRD), "NA='-999'")
t1066_UP_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_UP_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_UP_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_UP_w2)[1]){
  if( t1066_UP_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_UP_w2$f_cont_fr[i] = 1 }
  else if( t1066_UP_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_UP_w2$f_cont_fr[i] = 2 }
  else if( t1066_UP_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_UP_w2$f_cont_fr[i] = 3 }
  else if( t1066_UP_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_UP_w2$f_cont_fr[i] = 4 }
  else if( t1066_UP_w2$f_PFRDFRQ[i] == 0 | t1066_UP_w2$f_PFRD[i] == 0 ) { t1066_ds_UP_w2$f_cont_fr[i] = 5 }
}
t1066_ds_UP_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_UP_w2$f_cont_fr), "NA='999'")
t1066_ds_UP_w2$f_cont_fr <- labelled(t1066_ds_UP_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_UP, echo=F}
vbl <- t1066_ds_UP_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_UP, echo=F}

```








## Venezuela

### Wave 1  

#### Study-specific variable description



| **Name** |`PFRDFRQ`|`PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-Venezuela-Baseline`|`1066-Venezuela-Baseline`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |



```{r assign1_Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('PFRDFRQ','PFRD'), missings = TRUE)
```

```{r local1_Ven, echo=F}
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')
vbl <- t1066_Ven_w1$PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_Ven_w1$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if PFRDFRQ=1 OR 2 => 1`
* `if PFRDFRQ=3 => 2`
* `if PFRDFRQ=4 => 3`
* `if PFRDFRQ=5 => 4`
* `if PFRD=0 OR PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo1_Ven}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)

t1066_Ven_w1$PFRD <- car::recode(as.vector(t1066_Ven_w1$PFRD), "NA='-999'")
t1066_Ven_w1$PFRDFRQ <- car::recode(as.vector(t1066_Ven_w1$PFRDFRQ), "NA='-999'")

t1066_ds_Ven_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_Ven_w1)[1]){
  if( t1066_Ven_w1$PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_Ven_w1$f_cont_fr[i] = 1 }
  else if( t1066_Ven_w1$PFRDFRQ[i] == 3 ) { t1066_ds_Ven_w1$f_cont_fr[i] = 2 }
  else if( t1066_Ven_w1$PFRDFRQ[i] == 4 ) { t1066_ds_Ven_w1$f_cont_fr[i] = 3 }
  else if( t1066_Ven_w1$PFRDFRQ[i] == 5 ) { t1066_ds_Ven_w1$f_cont_fr[i] = 4 }
  else if( t1066_Ven_w1$PFRDFRQ[i] == 0 | t1066_Ven_w1$PFRD[i] == 0 ) { t1066_ds_Ven_w1$f_cont_fr[i] = 5 }
}
t1066_ds_Ven_w1$f_cont_fr <- car::recode(as.vector(t1066_ds_Ven_w1$f_cont_fr), "NA='999'")
t1066_ds_Ven_w1$f_cont_fr <- labelled(t1066_ds_Ven_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_Ven, echo=F}
vbl <- t1066_ds_Ven_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_Ven, echo=F}

```





### Wave 2

#### Study-specific variable description


| **Name** |`f_PFRDFRQ`|`f_PFRD`|
|-|-|-|
| **Label** |`frequency of seeing friends`|`has friends?`|
| **Table name** |`1066-Venezuela-Followup`|`1066-Venezuela-Followup`|
| **Categories** |`0 = no friends/ never`<br/>`1 = daily`<br/>`2 = 2-3 times/ week`<br/>`3 = at least weekly`<br/>`4 = at least monthly`<br/>`5 = less often`|`0 = no`<br/>`1 = yes`|
| **Description** |  |  |


```{r assign2_Ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_PFRDFRQ','f_PFRD'), missings = TRUE)
```

```{r local2_Ven, echo=F}
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')
vbl <- t1066_Ven_w2$f_PFRDFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "f_PFRDFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")
vbl <- t1066_Ven_w2$PNEIFRQ
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "PNEIFRQ")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if f_PFRDFRQ=1 OR 2 => 1`
* `if f_PFRDFRQ=3 => 2`
* `if f_PFRDFRQ=4 => 3`
* `if f_PFRDFRQ=5 => 4`
* `if f_PFRD=0 OR f_PFRDFRQ=0 => 5`	
* `NA into 999`

**R script:**

```{r harmo2_Ven}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)

t1066_Ven_w2$f_PFRD <- car::recode(as.vector(t1066_Ven_w2$f_PFRD), "NA='-999'")
t1066_Ven_w2$f_PFRDFRQ <- car::recode(as.vector(t1066_Ven_w2$f_PFRDFRQ), "NA='-999'")

t1066_ds_Ven_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(t1066_Ven_w2)[1]){
  if( t1066_Ven_w2$f_PFRDFRQ[i] %in% c(1,2) ) { t1066_ds_Ven_w2$f_cont_fr[i] = 1 }
  else if( t1066_Ven_w2$f_PFRDFRQ[i] == 3 ) { t1066_ds_Ven_w2$f_cont_fr[i] = 2 }
  else if( t1066_Ven_w2$f_PFRDFRQ[i] == 4 ) { t1066_ds_Ven_w2$f_cont_fr[i] = 3 }
  else if( t1066_Ven_w2$f_PFRDFRQ[i] == 5 ) { t1066_ds_Ven_w2$f_cont_fr[i] = 4 }
  else if( t1066_Ven_w2$f_PFRDFRQ[i] == 0 | t1066_Ven_w2$f_PFRD[i] == 0 ) { t1066_ds_Ven_w2$f_cont_fr[i] = 5 }
}
t1066_ds_Ven_w2$f_cont_fr <- car::recode(as.vector(t1066_ds_Ven_w2$f_cont_fr), "NA='999'")
t1066_ds_Ven_w2$f_cont_fr <- labelled(t1066_ds_Ven_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_Ven, echo=F}
vbl <- t1066_ds_Ven_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_Ven, echo=F}

```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```



# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
