---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_fr`
* Variable label: `Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 cuba }
opal.assign.table.tibble(o, 't1066_cuba_w1_cont_fr','10-66.1066-Cuba-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 cuba }
t1066_cuba_w1_cont_fr <- opal.execute(o,'t1066_cuba_w1_cont_fr')
vari <- t1066_cuba_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_cuba_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_cuba_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_cuba_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_cuba_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_cuba_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 cuba , echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_cont_fr$id)

t1066_cuba_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_cuba_w1_cont_fr$PFRD), "NA='-999'")
t1066_cuba_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_cuba_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_cuba_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_cuba_w1_cont_fr$PNEIFRQ), "NA='-999'")



t1066_ds_cuba_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_cuba_w1_cont_fr)[1]){
  if( (t1066_cuba_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_cuba_w1_cont_fr$PFRD[i] == 0 ) & t1066_cuba_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_cuba_w1$cont_fr[i] = 0 }
  else if(t1066_cuba_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_cuba_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_cuba_w1$cont_fr[i] = 1 }
  else if( t1066_cuba_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_cuba_w1$cont_fr[i] = 996 }
}
t1066_ds_cuba_w1$cont_fr <- car::recode(as.vector(t1066_ds_cuba_w1$cont_fr), "NA='999'")
t1066_ds_cuba_w1$cont_fr <- labelled(t1066_ds_cuba_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba }
vari <- t1066_ds_cuba_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba }

```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 cuba }
opal.assign.table.tibble(o, 't1066_cuba_w2_cont_fr','10-66.1066-Cuba-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 cuba }
t1066_cuba_w2_cont_fr <- opal.execute(o,'t1066_cuba_w2_cont_fr')

vari <- t1066_cuba_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_cuba_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_cuba_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_cuba_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_cuba_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_cuba_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 cuba , echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_cont_fr$id)

t1066_cuba_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_cuba_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_cuba_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_cuba_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_cuba_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_cuba_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_cuba_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_cuba_w2_cont_fr)[1]){
  if( ( t1066_cuba_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_cuba_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_cuba_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_cuba_w2$cont_fr[i] = 0 }
  else if(t1066_cuba_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_cuba_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_cuba_w2$cont_fr[i] = 1 }
  else if( t1066_cuba_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_cuba_w2$cont_fr[i] = 996 }
}
t1066_ds_cuba_w2$cont_fr <- car::recode(as.vector(t1066_ds_cuba_w2$cont_fr), "NA='999'")
t1066_ds_cuba_w2$cont_fr <- labelled(t1066_ds_cuba_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba }
vari <- t1066_ds_cuba_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba }

```

 
 


## Dominican Republic
### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 DR }
opal.assign.table.tibble(o, 't1066_DR_w1_cont_fr','10-66.1066-DominicanRepublic-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 DR }
t1066_DR_w1_cont_fr <- opal.execute(o,'t1066_DR_w1_cont_fr')

vari <- t1066_DR_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_DR_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_DR_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_DR_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_DR_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_DR_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 DR , echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_cont_fr$id)

t1066_DR_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_DR_w1_cont_fr$PFRD), "NA='-999'")
t1066_DR_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_DR_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_DR_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_DR_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_DR_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_DR_w1_cont_fr)[1]){
  if( (t1066_DR_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_DR_w1_cont_fr$PFRD[i] == 0 ) & t1066_DR_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_DR_w1$cont_fr[i] = 0 }
  else if( t1066_cuba_w1_cont_fr$PFRD[i] == 0 & t1066_cuba_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ){ 
    t1066_ds_cuba_w1$cont_fr[i] = 0 }
  else if(t1066_DR_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_DR_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_DR_w1$cont_fr[i] = 1 }
  else if( t1066_DR_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_DR_w1$cont_fr[i] = 996 }
}
t1066_ds_DR_w1$cont_fr <- car::recode(as.vector(t1066_ds_DR_w1$cont_fr), "NA='999'")
t1066_ds_DR_w1$cont_fr <- labelled(t1066_ds_DR_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR }
vari <- t1066_ds_DR_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR }

```

 
 



### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 DR }
opal.assign.table.tibble(o, 't1066_DR_w2_cont_fr','10-66.1066-DominicanRepublic-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 DR }
t1066_DR_w2_cont_fr <- opal.execute(o,'t1066_DR_w2_cont_fr')

vari <- t1066_DR_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_DR_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_DR_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_DR_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_DR_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_DR_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 DR , echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_cont_fr$id)

t1066_DR_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_DR_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_DR_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_DR_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_DR_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_DR_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_DR_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_DR_w2_cont_fr)[1]){
  if( ( t1066_DR_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_DR_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_DR_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_DR_w2$cont_fr[i] = 0 }
  else if(t1066_DR_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_DR_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_DR_w2$cont_fr[i] = 1 }
  else if(t1066_DR_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_DR_w2$cont_fr[i] = 996 }
}
t1066_ds_DR_w2$cont_fr <- car::recode(as.vector(t1066_ds_DR_w2$cont_fr), "NA='999'")
t1066_ds_DR_w2$cont_fr <- labelled(t1066_ds_DR_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 DR }
vari <- t1066_ds_DR_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 DR }

```

 
 


## India

### Wave 1 


#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 india }
opal.assign.table.tibble(o, 't1066_india_w1_cont_fr','10-66.1066-India-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 india }
t1066_india_w1_cont_fr <- opal.execute(o,'t1066_india_w1_cont_fr')

vari <-t1066_india_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_india_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_india_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_india_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_india_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_india_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 india , echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_cont_fr$id)

t1066_india_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_india_w1_cont_fr$PFRD), "NA='-999'")
t1066_india_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_india_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_india_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_india_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_india_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_india_w1_cont_fr)[1]){
  if( ( t1066_india_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_india_w1_cont_fr$PFRD[i] == 0 ) & t1066_india_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_india_w1$cont_fr[i] = 0 }
  else if(t1066_india_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_india_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_india_w1$cont_fr[i] = 1 }
  else if( t1066_india_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_india_w1$cont_fr[i] = 996 }
}
t1066_ds_india_w1$cont_fr <- car::recode(as.vector(t1066_ds_india_w1$cont_fr), "NA='999'")
t1066_ds_india_w1$cont_fr <- labelled(t1066_ds_india_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 india }
vari <- t1066_ds_india_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india }

```

 
 


### Wave 2
Not found.

## Puerto Rico
### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 PR }
opal.assign.table.tibble(o, 't1066_PR_w1_cont_fr','10-66.1066-PuertoRico-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 PR }
t1066_PR_w1_cont_fr <- opal.execute(o,'t1066_PR_w1_cont_fr')

vari <- t1066_PR_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_PR_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_PR_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_PR_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_PR_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_PR_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 PR , echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_cont_fr$id)

t1066_PR_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_PR_w1_cont_fr$PFRD), "NA='-999'")
t1066_PR_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_PR_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_PR_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_PR_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_PR_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_PR_w1_cont_fr)[1]){
  if( ( t1066_PR_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_PR_w1_cont_fr$PFRD[i] == 0 ) & t1066_PR_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_PR_w1$cont_fr[i] = 0 }
  else if(t1066_PR_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_PR_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_PR_w1$cont_fr[i] = 1 }
  else if( t1066_PR_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_PR_w1$cont_fr[i] = 996 }
}
t1066_ds_PR_w1$cont_fr <- car::recode(as.vector(t1066_ds_PR_w1$cont_fr), "NA='999'")
t1066_ds_PR_w1$cont_fr <- labelled(t1066_ds_PR_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 PR }
vari <- t1066_ds_PR_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 PR }

```

 
 


### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 PR }
opal.assign.table.tibble(o, 't1066_PR_w2_cont_fr','10-66.1066-PuertoRico-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 PR }
t1066_PR_w2_cont_fr <- opal.execute(o,'t1066_PR_w2_cont_fr')

vari <- t1066_PR_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_PR_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_PR_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_PR_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_PR_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_PR_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 PR , echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_cont_fr$id)

t1066_PR_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_PR_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_PR_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_PR_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_PR_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_PR_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_PR_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_PR_w2_cont_fr)[1]){
  if( ( t1066_PR_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_PR_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_PR_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_PR_w2$cont_fr[i] = 0 }
  else if(t1066_PR_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_PR_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_PR_w2$cont_fr[i] = 1 }
  else if( t1066_PR_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_PR_w2$cont_fr[i] = 996 }
}
t1066_ds_PR_w2$cont_fr <- car::recode(as.vector(t1066_ds_PR_w2$cont_fr), "NA='999'")
t1066_ds_PR_w2$cont_fr <- labelled(t1066_ds_PR_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 PR }
vari <- t1066_ds_PR_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 PR }

```

 
 


## Rural China
### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 RCh }
opal.assign.table.tibble(o, 't1066_RCh_w1_cont_fr','10-66.1066-RuralChina-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 RCh }
t1066_RCh_w1_cont_fr <- opal.execute(o,'t1066_RCh_w1_cont_fr')

vari <- t1066_RCh_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_RCh_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RCh_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_RCh_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RCh_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_RCh_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 RCh , echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_cont_fr$id)

t1066_RCh_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_RCh_w1_cont_fr$PFRD), "NA='-999'")
t1066_RCh_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_RCh_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_RCh_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_RCh_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_RCh_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RCh_w1_cont_fr)[1]){
  if( ( t1066_RCh_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_RCh_w1_cont_fr$PFRD[i] == 0 ) & t1066_RCh_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RCh_w1$cont_fr[i] = 0 }
  else if(t1066_RCh_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RCh_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RCh_w1$cont_fr[i] = 1 }
  else if( t1066_RCh_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_RCh_w1$cont_fr[i] = 996 }
}
t1066_ds_RCh_w1$cont_fr <- car::recode(as.vector(t1066_ds_RCh_w1$cont_fr), "NA='999'")
t1066_ds_RCh_w1$cont_fr <- labelled(t1066_ds_RCh_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 RCh }
vari <- t1066_ds_RCh_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RCh }

```

 
 



### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 RCh }
opal.assign.table.tibble(o, 't1066_RCh_w2_cont_fr','10-66.1066-RuralChina-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 RCh }
t1066_RCh_w2_cont_fr <- opal.execute(o,'t1066_RCh_w2_cont_fr')

vari <- t1066_RCh_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_RCh_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RCh_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_RCh_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RCh_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_RCh_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 RCh , echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_cont_fr$id)

t1066_RCh_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_RCh_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_RCh_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_RCh_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_RCh_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_RCh_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_RCh_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RCh_w2_cont_fr)[1]){
  if( ( t1066_RCh_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_RCh_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_RCh_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RCh_w2$cont_fr[i] = 0 }
  else if(t1066_RCh_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RCh_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RCh_w2$cont_fr[i] = 1 }
  else if( t1066_RCh_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_RCh_w2$cont_fr[i] = 996 }
}
t1066_ds_RCh_w2$cont_fr <- car::recode(as.vector(t1066_ds_RCh_w2$cont_fr), "NA='999'")
t1066_ds_RCh_w2$cont_fr <- labelled(t1066_ds_RCh_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 RCh }
vari <- t1066_ds_RCh_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RCh }

```

 
 


## Rural Mexico
### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 RM }
opal.assign.table.tibble(o, 't1066_RM_w1_cont_fr','10-66.1066-RuralMexico-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 RM }
t1066_RM_w1_cont_fr <- opal.execute(o,'t1066_RM_w1_cont_fr')

vari <- t1066_RM_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_RM_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RM_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_RM_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RM_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_RM_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 RM , echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_cont_fr$id)

t1066_RM_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_RM_w1_cont_fr$PFRD), "NA='-999'")
t1066_RM_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_RM_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_RM_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_RM_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_RM_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RM_w1_cont_fr)[1]){
  if( ( t1066_RM_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_RM_w1_cont_fr$PFRD[i] == 0 ) & t1066_RM_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RM_w1$cont_fr[i] = 0 }
  else if(t1066_RM_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RM_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RM_w1$cont_fr[i] = 1 }
  else if( t1066_RM_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_RM_w1$cont_fr[i] = 996 }
}
t1066_ds_RM_w1$cont_fr <- car::recode(as.vector(t1066_ds_RM_w1$cont_fr), "NA='999'")
t1066_ds_RM_w1$cont_fr <- labelled(t1066_ds_RM_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 RM }
vari <- t1066_ds_RM_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RM }

```

 
 


### Wave 2
 

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 RM }
opal.assign.table.tibble(o, 't1066_RM_w2_cont_fr','10-66.1066-RuralMexico-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 RM }
t1066_RM_w2_cont_fr <- opal.execute(o,'t1066_RM_w2_cont_fr')

vari <- t1066_RM_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_RM_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RM_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_RM_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RM_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_RM_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 RM , echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_cont_fr$id)

t1066_RM_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_RM_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_RM_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_RM_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_RM_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_RM_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_RM_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RM_w2_cont_fr)[1]){
  if( ( t1066_RM_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_RM_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_RM_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RM_w2$cont_fr[i] = 0 }
  else if(t1066_RM_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RM_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RM_w2$cont_fr[i] = 1 }
  else if( t1066_RM_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_RM_w2$cont_fr[i] = 996 }
}
t1066_ds_RM_w2$cont_fr <- car::recode(as.vector(t1066_ds_RM_w2$cont_fr), "NA='999'")
t1066_ds_RM_w2$cont_fr <- labelled(t1066_ds_RM_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 RM }
vari <- t1066_ds_RM_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RM }

```

 
 



## Rural Peru


### Wave 1  

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 RP }
opal.assign.table.tibble(o, 't1066_RP_w1_cont_fr','10-66.1066-RuralPeru-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 RP }
t1066_RP_w1_cont_fr <- opal.execute(o,'t1066_RP_w1_cont_fr')

vari <- t1066_RP_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_RP_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RP_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_RP_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RP_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_RP_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 RP , echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_cont_fr$id)

t1066_RP_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_RP_w1_cont_fr$PFRD), "NA='-999'")
t1066_RP_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_RP_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_RP_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_RP_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_RP_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RP_w1_cont_fr)[1]){
  if( ( t1066_RP_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_RP_w1_cont_fr$PFRD[i] == 0 ) & t1066_RP_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RP_w1$cont_fr[i] = 0 }
  else if(t1066_RP_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RP_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RP_w1$cont_fr[i] = 1 }
  else if( t1066_RP_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_RP_w1$cont_fr[i] = 996 }
  }
t1066_ds_RP_w1$cont_fr <- car::recode(as.vector(t1066_ds_RP_w1$cont_fr), "NA='999'")
t1066_ds_RP_w1$cont_fr <- labelled(t1066_ds_RP_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 RP }
vari <- t1066_ds_RP_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 RP }

```

 
 



### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 RP }
opal.assign.table.tibble(o, 't1066_RP_w2_cont_fr','10-66.1066-RuralPeru-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 RP }
t1066_RP_w2_cont_fr <- opal.execute(o,'t1066_RP_w2_cont_fr')

vari <- t1066_RP_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_RP_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_RP_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_RP_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_RP_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_RP_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 RP , echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_cont_fr$id)

t1066_RP_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_RP_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_RP_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_RP_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_RP_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_RP_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_RP_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_RP_w2_cont_fr)[1]){
  if( ( t1066_RP_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_RP_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_RP_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_RP_w2$cont_fr[i] = 0 }
  else if(t1066_RP_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_RP_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_RP_w2$cont_fr[i] = 1 }
  else if( t1066_RP_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_RP_w2$cont_fr[i] = 996 }
}
t1066_ds_RP_w2$cont_fr <- car::recode(as.vector(t1066_ds_RP_w2$cont_fr), "NA='999'")
t1066_ds_RP_w2$cont_fr <- labelled(t1066_ds_RP_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 RP }
vari <- t1066_ds_RP_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 RP }

```

 
 



## Urban China
### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 Uch }
opal.assign.table.tibble(o, 't1066_UCh_w1_cont_fr','10-66.1066-UrbanChina-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 Uch }
t1066_UCh_w1_cont_fr <- opal.execute(o,'t1066_UCh_w1_cont_fr')

vari <- t1066_UCh_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_UCh_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UCh_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_UCh_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UCh_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_UCh_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 Uch , echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_cont_fr$id)

t1066_UCh_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_UCh_w1_cont_fr$PFRD), "NA='-999'")
t1066_UCh_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_UCh_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_UCh_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_UCh_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_UCh_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UCh_w1_cont_fr)[1]){
  if( ( t1066_UCh_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_UCh_w1_cont_fr$PFRD[i] == 0 ) & t1066_UCh_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UCh_w1$cont_fr[i] = 0 }
  else if(t1066_UCh_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UCh_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UCh_w1$cont_fr[i] = 1 }
  else if( t1066_UCh_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_UCh_w1$cont_fr[i] = 996 }
}
t1066_ds_UCh_w1$cont_fr <- car::recode(as.vector(t1066_ds_UCh_w1$cont_fr), "NA='999'")
t1066_ds_UCh_w1$cont_fr <- labelled(t1066_ds_UCh_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 Uch }
vari <- t1066_ds_UCh_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 Uch }

```

 
 


### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 Uch }
opal.assign.table.tibble(o, 't1066_UCh_w2_cont_fr','10-66.1066-UrbanChina-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 Uch }
t1066_UCh_w2_cont_fr <- opal.execute(o,'t1066_UCh_w2_cont_fr')

vari <- t1066_UCh_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_UCh_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UCh_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_UCh_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UCh_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_UCh_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 Uch , echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_cont_fr$id)

t1066_UCh_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_UCh_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_UCh_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_UCh_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_UCh_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_UCh_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_UCh_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UCh_w2_cont_fr)[1]){
  if( ( t1066_UCh_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_UCh_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_UCh_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UCh_w2$cont_fr[i] = 0 }
  else if(t1066_UCh_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UCh_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UCh_w2$cont_fr[i] = 1 }
  else if( t1066_UCh_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_UCh_w2$cont_fr[i] = 996 }
}
t1066_ds_UCh_w2$cont_fr <- car::recode(as.vector(t1066_ds_UCh_w2$cont_fr), "NA='999'")
t1066_ds_UCh_w2$cont_fr <- labelled(t1066_ds_UCh_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 Uch }
vari <- t1066_ds_UCh_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 Uch }

```

 
 


## Urban Mexico

### Wave 1  

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 UM}
opal.assign.table.tibble(o, 't1066_UM_w1_cont_fr','10-66.1066-UrbanMexico-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 UM}
t1066_UM_w1_cont_fr <- opal.execute(o,'t1066_UM_w1_cont_fr')

vari <- t1066_UM_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_UM_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UM_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_UM_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UM_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_UM_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 UM, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_cont_fr$id)

t1066_UM_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_UM_w1_cont_fr$PFRD), "NA='-999'")
t1066_UM_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_UM_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_UM_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_UM_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_UM_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UM_w1_cont_fr)[1]){
  if( ( t1066_UM_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_UM_w1_cont_fr$PFRD[i] == 0 ) & t1066_UM_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UM_w1$cont_fr[i] = 0 }
  else if(t1066_UM_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UM_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UM_w1$cont_fr[i] = 1 }
  else if( t1066_UM_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_UM_w1$cont_fr[i] = 996 }
}
t1066_ds_UM_w1$cont_fr <- car::recode(as.vector(t1066_ds_UM_w1$cont_fr), "NA='999'")
t1066_ds_UM_w1$cont_fr <- labelled(t1066_ds_UM_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 UM}
vari <- t1066_ds_UM_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UM}

```

 
 


### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 UM}
opal.assign.table.tibble(o, 't1066_UM_w2_cont_fr','10-66.1066-UrbanMexico-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 UM}
t1066_UM_w2_cont_fr <- opal.execute(o,'t1066_UM_w2_cont_fr')

vari <- t1066_UM_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_UM_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UM_w2_cont_fr$f_PNEIFRQ 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_UM_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UM_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_UM_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 UM, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_cont_fr$id)

t1066_UM_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_UM_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_UM_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_UM_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_UM_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_UM_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_UM_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UM_w2_cont_fr)[1]){
  if( ( t1066_UM_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_UM_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_UM_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UM_w2$cont_fr[i] = 0 }
  else if(t1066_UM_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UM_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UM_w2$cont_fr[i] = 1 }
  else if( t1066_UM_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_UM_w2$cont_fr[i] = 996 }
}
t1066_ds_UM_w2$cont_fr <- car::recode(as.vector(t1066_ds_UM_w2$cont_fr), "NA='999'")
t1066_ds_UM_w2$cont_fr <- labelled(t1066_ds_UM_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 UM}
vari <- t1066_ds_UM_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UM}

```

 
 


## Urban Peru

### Wave 1 

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 UP}
opal.assign.table.tibble(o, 't1066_UP_w1_cont_fr','10-66.1066-UrbanPeru-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 UP}
t1066_UP_w1_cont_fr <- opal.execute(o,'t1066_UP_w1_cont_fr')

vari <- t1066_UP_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_UP_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UP_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_UP_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UP_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_UP_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 UP, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_cont_fr$id)

t1066_UP_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_UP_w1_cont_fr$PFRD), "NA='-999'")
t1066_UP_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_UP_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_UP_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_UP_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_UP_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UP_w1_cont_fr)[1]){
  if( ( t1066_UP_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_UP_w1_cont_fr$PFRD[i] == 0 ) & t1066_UP_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UP_w1$cont_fr[i] = 0 }
  else if(t1066_UP_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UP_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UP_w1$cont_fr[i] = 1 }
  else if( t1066_UP_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_UP_w1$cont_fr[i] = 996 }
}
t1066_ds_UP_w1$cont_fr <- car::recode(as.vector(t1066_ds_UP_w1$cont_fr), "NA='999'")
t1066_ds_UP_w1$cont_fr <- labelled(t1066_ds_UP_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 UP}
vari <- t1066_ds_UP_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 UP}

```

 
 


### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 UP}
opal.assign.table.tibble(o, 't1066_UP_w2_cont_fr','10-66.1066-UrbanPeru-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 UP}
t1066_UP_w2_cont_fr <- opal.execute(o,'t1066_UP_w2_cont_fr')

vari <- t1066_UP_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_UP_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_UP_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_UP_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_UP_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_UP_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 UP, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_cont_fr$id)

t1066_UP_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_UP_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_UP_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_UP_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_UP_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_UP_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_UP_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_UP_w2_cont_fr)[1]){
  if( ( t1066_UP_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_UP_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_UP_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_UP_w2$cont_fr[i] = 0 }
  else if(t1066_UP_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_UP_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_UP_w2$cont_fr[i] = 1 }
  else if( t1066_UP_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_UP_w2$cont_fr[i] = 996 }
}
t1066_ds_UP_w2$cont_fr <- car::recode(as.vector(t1066_ds_UP_w2$cont_fr), "NA='999'")
t1066_ds_UP_w2$cont_fr <- labelled(t1066_ds_UP_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 UP}
vari <- t1066_ds_UP_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 UP}

```

 
 



## Venezuela

### Wave 1  

#### Study-specific variables


* Name: `PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 Ven}
opal.assign.table.tibble(o, 't1066_Ven_w1_cont_fr','10-66.1066-Venezuela-Baseline',variables=list('PFRDFRQ','PFRD','PNEIFRQ'), missings = TRUE)
```

```{r local1 Ven}
t1066_Ven_w1_cont_fr <- opal.execute(o,'t1066_Ven_w1_cont_fr')

vari <- t1066_Ven_w1_cont_fr$PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_cont_fr$PFRDFRQ, missing_values = NA)
ggplot(t1066_Ven_w1_cont_fr, aes(x=factor(PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_Ven_w1_cont_fr$PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_cont_fr$PNEIFRQ, missing_values = NA)
ggplot(t1066_Ven_w1_cont_fr, aes(x=factor(PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_Ven_w1_cont_fr$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_cont_fr$PFRD, missing_values = NA)
ggplot(t1066_Ven_w1_cont_fr, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(PFRDFRQ in (0,5) OR PFRD=0) AND PNEIFRQ in (0,5) into 0`
* `PFRDFRQ in (1,2,3,4) OR PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo1 Ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_cont_fr$id)

t1066_Ven_w1_cont_fr$PFRD <- car::recode(as.vector(t1066_Ven_w1_cont_fr$PFRD), "NA='-999'")
t1066_Ven_w1_cont_fr$PFRDFRQ <- car::recode(as.vector(t1066_Ven_w1_cont_fr$PFRDFRQ), "NA='-999'")
t1066_Ven_w1_cont_fr$PNEIFRQ <- car::recode(as.vector(t1066_Ven_w1_cont_fr$PNEIFRQ), "NA='-999'")

t1066_ds_Ven_w1$cont_fr <- c(NA)  
for(i in 1:dim(t1066_Ven_w1_cont_fr)[1]){
  if( ( t1066_Ven_w1_cont_fr$PFRDFRQ[i] %in% c(0,5) | t1066_Ven_w1_cont_fr$PFRD[i] == 0 ) & t1066_Ven_w1_cont_fr$PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_Ven_w1$cont_fr[i] = 0 }
  else if(t1066_Ven_w1_cont_fr$PFRDFRQ[i] %in% c(1,2,3,4) | t1066_Ven_w1_cont_fr$PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_Ven_w1$cont_fr[i] = 1 }
  else if( t1066_Ven_w1_cont_fr$PFRD[i] == 0 ){ 
    t1066_ds_Ven_w1$cont_fr[i] = 996 }
  }
t1066_ds_Ven_w1$cont_fr <- car::recode(as.vector(t1066_ds_Ven_w1$cont_fr), "NA='999'")
t1066_ds_Ven_w1$cont_fr <- labelled(t1066_ds_Ven_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 Ven}
vari <- t1066_ds_Ven_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 Ven}

```

 
 


### Wave 2

#### Study-specific variables


* Name: `f_PFRDFRQ`
* Label: `frequency of seeing friends`
* Categories: 
    + `0	= no friends/ never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`

* Name: `f_PNEIFRQ`
* Label: `frequency of seeing neighbours`
* Categories: 
    + `0	= never`
    + `1	= daily`
    + `2	= 2-3 times/ week`
    + `3	= at least weekly`	
    + `4	= at least monthly`
    + `5	= less often`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign2 Ven}
opal.assign.table.tibble(o, 't1066_Ven_w2_cont_fr','10-66.1066-Venezuela-Followup',variables=list('f_PFRDFRQ','f_PFRD','f_PNEIFRQ'), missings = TRUE)
```

```{r local2 Ven}
t1066_Ven_w2_cont_fr <- opal.execute(o,'t1066_Ven_w2_cont_fr')
vari <- t1066_Ven_w2_cont_fr$f_PFRDFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_cont_fr$f_PFRDFRQ, missing_values = NA)
ggplot(t1066_Ven_w2_cont_fr, aes(x=factor(f_PFRDFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing friends") + ylab("Frequency")

vari <- t1066_Ven_w2_cont_fr$f_PNEIFRQ
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_cont_fr$f_PNEIFRQ, missing_values = NA)
ggplot(t1066_Ven_w2_cont_fr, aes(x=factor(f_PNEIFRQ))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("frequency of seeing neighbours") + ylab("Frequency")

vari <- t1066_Ven_w2_cont_fr$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_cont_fr$f_PFRD, missing_values = NA)
ggplot(t1066_Ven_w2_cont_fr, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(f_PFRDFRQ in (0,5) OR f_PFRD=0) AND f_PNEIFRQ in (0,5) into 0`
* `f_PFRDFRQ in (1,2,3,4) OR f_PNEIFRQ in (1,2,3,4) into 1`
* `NA into 999`

**R script:**

```{r harmo2 Ven, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_cont_fr$id)

t1066_Ven_w2_cont_fr$f_PFRD <- car::recode(as.vector(t1066_Ven_w2_cont_fr$f_PFRD), "NA='-999'")
t1066_Ven_w2_cont_fr$f_PFRDFRQ <- car::recode(as.vector(t1066_Ven_w2_cont_fr$f_PFRDFRQ), "NA='-999'")
t1066_Ven_w2_cont_fr$f_PNEIFRQ <- car::recode(as.vector(t1066_Ven_w2_cont_fr$f_PNEIFRQ), "NA='-999'")

t1066_ds_Ven_w2$cont_fr <- c(NA)  
for(i in 1:dim(t1066_Ven_w2_cont_fr)[1]){
  if( ( t1066_Ven_w2_cont_fr$f_PFRDFRQ[i] %in% c(0,5) | t1066_Ven_w2_cont_fr$f_PFRD[i] == 0 ) & t1066_Ven_w2_cont_fr$f_PNEIFRQ[i] %in% c(0,5) ) { 
    t1066_ds_Ven_w2$cont_fr[i] = 0 }
  else if(t1066_Ven_w2_cont_fr$f_PFRDFRQ[i] %in% c(1,2,3,4) | t1066_Ven_w2_cont_fr$f_PNEIFRQ[i] %in% c(1,2,3,4) ){ 
    t1066_ds_Ven_w2$cont_fr[i] = 1 }
  else if( t1066_Ven_w2_cont_fr$f_PFRD[i] == 0 ){ 
    t1066_ds_Ven_w2$cont_fr[i] = 996 }
}
t1066_ds_Ven_w2$cont_fr <- car::recode(as.vector(t1066_ds_Ven_w2$cont_fr), "NA='999'")
t1066_ds_Ven_w2$cont_fr <- labelled(t1066_ds_Ven_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 Ven}
vari <- t1066_ds_Ven_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 Ven}

```

 
```{r save,  echo=FALSE}
cont_fr <- t1066_ds_cuba_w1
save(cont_fr, file = "../RData/cuba_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_cuba_w2
save(cont_fr, file = "../RData/cuba_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_india_w1
save(cont_fr, file = "../RData/india_w1/cont_fr.RData")
rm(cont_fr)


cont_fr <- t1066_ds_UCh_w1
save(cont_fr, file = "../RData/UCh_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_UCh_w2
save(cont_fr, file = "../RData/UCh_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RCh_w1
save(cont_fr, file = "../RData/RCh_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RCh_w2
save(cont_fr, file = "../RData/RCh_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_DR_w1
save(cont_fr, file = "../RData/DR_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_DR_w2
save(cont_fr, file = "../RData/DR_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_Ven_w1
save(cont_fr, file = "../RData/Ven_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_Ven_w2
save(cont_fr, file = "../RData/Ven_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_UP_w1
save(cont_fr, file = "../RData/UP_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_UP_w2
save(cont_fr, file = "../RData/UP_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RP_w1
save(cont_fr, file = "../RData/RP_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RP_w2
save(cont_fr, file = "../RData/RP_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_UM_w1
save(cont_fr, file = "../RData/UM_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_UM_w2
save(cont_fr, file = "../RData/UM_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RM_w1
save(cont_fr, file = "../RData/RM_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_RM_w2
save(cont_fr, file = "../RData/RM_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_PR_w1
save(cont_fr, file = "../RData/PR_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- t1066_ds_PR_w2
save(cont_fr, file = "../RData/PR_w2/cont_fr.RData")
rm(cont_fr)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
