---
title: "Instrumental support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/inst_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/inst_supDS.R')
```




<!-- ########################################################## --> 

# Data process

## Cuba
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_inst_sup','10-66.1066-Cuba-Baseline', variables=list('PFRDSAT','PFRD'), missings = TRUE)
```

```{r local1 cuba, echo=F}
t1066_cuba_w1_inst_sup <- opal.execute(o,'t1066_cuba_w1_inst_sup')
vari <- t1066_cuba_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_cuba_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_cuba_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_cuba_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 cuba, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_inst_sup$id)

t1066_cuba_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_cuba_w1_inst_sup$PFRD), "NA='-999'")
t1066_cuba_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_cuba_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_cuba_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_cuba_w1_inst_sup)[1]){
  if( t1066_cuba_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_cuba_w1$inst_sup[i] = 0 }
  else if(t1066_cuba_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_cuba_w1$inst_sup[i] = 1 }
  else if( t1066_cuba_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_cuba_w1$inst_sup[i] = 0 }
}
t1066_ds_cuba_w1$inst_sup <- car::recode(as.vector(t1066_ds_cuba_w1$inst_sup), "NA='999'")
t1066_ds_cuba_w1$inst_sup <- labelled(t1066_ds_cuba_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cuba, echo=F}
vari <- t1066_ds_cuba_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w1$inst_sup)
BeforeH <- table(t1066_cuba_w1_inst_sup$PFRDSAT, t1066_cuba_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 cuba, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_inst_sup','10-66.1066-Cuba-Followup', variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 cuba, echo=F}
t1066_cuba_w2_inst_sup <- opal.execute(o,'t1066_cuba_w2_inst_sup')
vari <- t1066_cuba_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_cuba_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_cuba_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_cuba_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has got any friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 cuba, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_inst_sup$id)

t1066_cuba_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_cuba_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_cuba_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_cuba_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_cuba_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_cuba_w2_inst_sup)[1]){
  if( t1066_cuba_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_cuba_w2$inst_sup[i] = 0 }
  else if(t1066_cuba_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_cuba_w2$inst_sup[i] = 1 }
  else if( t1066_cuba_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_cuba_w2$inst_sup[i] = 0 }
}
t1066_ds_cuba_w2$inst_sup <- car::recode(as.vector(t1066_ds_cuba_w2$inst_sup), "NA='999'")
t1066_ds_cuba_w2$inst_sup <- labelled(t1066_ds_cuba_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cuba, echo=F}
vari <- t1066_ds_cuba_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cuba, echo=F}
AfterH <- table(t1066_ds_cuba_w2$inst_sup)
BeforeH <- table(t1066_cuba_w2_inst_sup$f_PFRDSAT, t1066_cuba_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


## Dominican Republic


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_inst_sup','10-66.1066-DominicanRepublic-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 DR, echo=F}
t1066_DR_w1_inst_sup <- opal.execute(o,'t1066_DR_w1_inst_sup')
vari <- t1066_DR_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_DR_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_DR_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_DR_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 DR, echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_inst_sup$id)

t1066_DR_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_DR_w1_inst_sup$PFRD), "NA='-999'")
t1066_DR_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_DR_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_DR_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_DR_w1_inst_sup)[1]){
  if( t1066_DR_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_DR_w1$inst_sup[i] = 0 }
  else if(t1066_DR_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_DR_w1$inst_sup[i] = 1 }
  else if( t1066_DR_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_DR_w1$inst_sup[i] = 0 }
}
t1066_ds_DR_w1$inst_sup <- car::recode(as.vector(t1066_ds_DR_w1$inst_sup), "NA='999'")
t1066_ds_DR_w1$inst_sup <- labelled(t1066_ds_DR_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 DR, echo=F}
vari <- t1066_ds_DR_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 DR, echo=F}
AfterH <- table(t1066_ds_DR_w1$inst_sup)
BeforeH <- table(t1066_DR_w1_inst_sup$PFRDSAT, t1066_DR_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`

* Description: 
```{r assign2 DR, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_inst_sup','10-66.1066-DominicanRepublic-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 DR, echo=F}
t1066_DR_w2_inst_sup <- opal.execute(o,'t1066_DR_w2_inst_sup')
vari <- t1066_DR_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_DR_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_DR_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_DR_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 DR, echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_inst_sup$id)

t1066_DR_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_DR_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_DR_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_DR_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_DR_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_DR_w2_inst_sup)[1]){
  if( t1066_DR_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_DR_w2$inst_sup[i] = 0 }
  else if(t1066_DR_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_DR_w2$inst_sup[i] = 1 }
  else if( t1066_DR_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_DR_w2$inst_sup[i] = 0 }
}
t1066_ds_DR_w2$inst_sup <- car::recode(as.vector(t1066_ds_DR_w2$inst_sup), "NA='999'")
t1066_ds_DR_w2$inst_sup <- labelled(t1066_ds_DR_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 DR, echo=F}
vari <- t1066_ds_DR_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 DR, echo=F}
AfterH <- table(t1066_ds_DR_w2$inst_sup)
BeforeH <- table(t1066_DR_w2_inst_sup$f_PFRDSAT, t1066_DR_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



## India


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_inst_sup','10-66.1066-India-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 india, echo=F}
t1066_india_w1_inst_sup <- opal.execute(o,'t1066_india_w1_inst_sup')
vari <- t1066_india_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_india_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_india_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_india_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_inst_sup$id)

t1066_india_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_india_w1_inst_sup$PFRD), "NA='-999'")
t1066_india_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_india_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_india_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_india_w1_inst_sup)[1]){
  if( t1066_india_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_india_w1$inst_sup[i] = 0 }
  else if(t1066_india_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_india_w1$inst_sup[i] = 1 }
  else if( t1066_india_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_india_w1$inst_sup[i] = 0 }
}
t1066_ds_india_w1$inst_sup <- car::recode(as.vector(t1066_ds_india_w1$inst_sup), "NA='999'")
t1066_ds_india_w1$inst_sup <- labelled(t1066_ds_india_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- t1066_ds_india_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}
AfterH <- table(t1066_ds_india_w1$inst_sup)
BeforeH <- table(t1066_india_w1_inst_sup$PFRDSAT, t1066_india_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Puerto Rico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 pr, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_inst_sup','10-66.1066-PuertoRico-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 pr, echo=F}
t1066_PR_w1_inst_sup <- opal.execute(o,'t1066_PR_w1_inst_sup')
vari <- t1066_PR_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_PR_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_PR_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_PR_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 pr, echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_inst_sup$id)

t1066_PR_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_PR_w1_inst_sup$PFRD), "NA='-999'")
t1066_PR_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_PR_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_PR_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_PR_w1_inst_sup)[1]){
  if( t1066_PR_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_PR_w1$inst_sup[i] = 0 }
  else if(t1066_PR_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_PR_w1$inst_sup[i] = 1 }
  else if( t1066_PR_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_PR_w1$inst_sup[i] = 0 }
}
t1066_ds_PR_w1$inst_sup <- car::recode(as.vector(t1066_ds_PR_w1$inst_sup), "NA='999'")
t1066_ds_PR_w1$inst_sup <- labelled(t1066_ds_PR_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pr, echo=F}
vari <- t1066_ds_PR_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pr, echo=F}
AfterH <- table(t1066_ds_PR_w1$inst_sup)
BeforeH <- table(t1066_PR_w1_inst_sup$PFRDSAT, t1066_PR_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 pr, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_inst_sup','10-66.1066-PuertoRico-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 pr, echo=F}
t1066_PR_w2_inst_sup <- opal.execute(o,'t1066_PR_w2_inst_sup')
vari <- t1066_PR_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_PR_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_PR_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_PR_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 pr, echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_inst_sup$id)

t1066_PR_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_PR_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_PR_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_PR_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_PR_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_PR_w2_inst_sup)[1]){
  if( t1066_PR_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_PR_w2$inst_sup[i] = 0 }
  else if( t1066_PR_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_PR_w2$inst_sup[i] = 1 }
  else if( t1066_PR_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_PR_w2$inst_sup[i] = 0 }
}
t1066_ds_PR_w2$inst_sup <- car::recode(as.vector(t1066_ds_PR_w2$inst_sup), "NA='999'")
t1066_ds_PR_w2$inst_sup <- labelled(t1066_ds_PR_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pr, echo=F}
vari <- t1066_ds_PR_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pr, echo=F}
AfterH <- table(t1066_ds_PR_w2$inst_sup)
BeforeH <- table(t1066_PR_w2_inst_sup$f_PFRDSAT, t1066_PR_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 rch, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_inst_sup','10-66.1066-RuralChina-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 rch, echo=F}
t1066_RCh_w1_inst_sup <- opal.execute(o,'t1066_RCh_w1_inst_sup')
vari <- t1066_RCh_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_RCh_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RCh_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_RCh_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 rch, echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_inst_sup$id)

t1066_RCh_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_RCh_w1_inst_sup$PFRD), "NA='-999'")
t1066_RCh_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_RCh_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_RCh_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_RCh_w1_inst_sup)[1]){
  if( t1066_RCh_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_RCh_w1$inst_sup[i] = 0 }
  else if(t1066_RCh_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_RCh_w1$inst_sup[i] = 1 }
  else if( t1066_RCh_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_RCh_w1$inst_sup[i] = 0 }
}
t1066_ds_RCh_w1$inst_sup <- car::recode(as.vector(t1066_ds_RCh_w1$inst_sup), "NA='999'")
t1066_ds_RCh_w1$inst_sup <- labelled(t1066_ds_RCh_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rch, echo=F}
vari <- t1066_ds_RCh_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rch, echo=F}
AfterH <- table(t1066_ds_RCh_w1$inst_sup)
BeforeH <- table(t1066_RCh_w1_inst_sup$PFRDSAT, t1066_RCh_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`

* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 rch, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_inst_sup','10-66.1066-RuralChina-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 rch, echo=F}
t1066_RCh_w2_inst_sup <- opal.execute(o,'t1066_RCh_w2_inst_sup')
vari <- t1066_RCh_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_RCh_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RCh_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_RCh_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 rch, echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_inst_sup$id)

t1066_RCh_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_RCh_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_RCh_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_RCh_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_RCh_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_RCh_w2_inst_sup)[1]){
  if( t1066_RCh_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_RCh_w2$inst_sup[i] = 0 }
  else if(t1066_RCh_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_RCh_w2$inst_sup[i] = 1 }
  else if( t1066_RCh_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_RCh_w2$inst_sup[i] = 0 }
}
t1066_ds_RCh_w2$inst_sup <- car::recode(as.vector(t1066_ds_RCh_w2$inst_sup), "NA='999'")
t1066_ds_RCh_w2$inst_sup <- labelled(t1066_ds_RCh_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rch, echo=F}
vari <- t1066_ds_RCh_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rch, echo=F}
AfterH <- table(t1066_ds_RCh_w2$inst_sup)
BeforeH <- table(t1066_RCh_w2_inst_sup$f_PFRDSAT, t1066_RCh_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Rural Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`

* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`


* Description: 
```{r assign1 rm, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_inst_sup','10-66.1066-RuralMexico-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 rm, echo=F}
t1066_RM_w1_inst_sup <- opal.execute(o,'t1066_RM_w1_inst_sup')
vari <- t1066_RM_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_RM_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RM_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_RM_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 rm, echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_inst_sup$id)

t1066_RM_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_RM_w1_inst_sup$PFRD), "NA='-999'")
t1066_RM_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_RM_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_RM_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_RM_w1_inst_sup)[1]){
  if( t1066_RM_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_RM_w1$inst_sup[i] = 0 }
  else if(t1066_RM_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_RM_w1$inst_sup[i] = 1 }
  else if( t1066_RM_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_RM_w1$inst_sup[i] = 0 }
}
t1066_ds_RM_w1$inst_sup <- car::recode(as.vector(t1066_ds_RM_w1$inst_sup), "NA='999'")
t1066_ds_RM_w1$inst_sup <- labelled(t1066_ds_RM_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rm, echo=F}
vari <- t1066_ds_RM_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rm, echo=F}
AfterH <- table(t1066_ds_RM_w1$inst_sup)
BeforeH <- table(t1066_RM_w1_inst_sup$PFRDSAT, t1066_RM_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 rm, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_inst_sup','10-66.1066-RuralMexico-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 rm, echo=F}
t1066_RM_w2_inst_sup <- opal.execute(o,'t1066_RM_w2_inst_sup')
vari <- t1066_RM_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_RM_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RM_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_RM_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 rm, echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_inst_sup$id)

t1066_RM_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_RM_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_RM_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_RM_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_RM_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_RM_w2_inst_sup)[1]){
  if( t1066_RM_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_RM_w2$inst_sup[i] = 0 }
  else if(t1066_RM_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_RM_w2$inst_sup[i] = 1 }
  else if( t1066_RM_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_RM_w2$inst_sup[i] = 0 }
}
t1066_ds_RM_w2$inst_sup <- car::recode(as.vector(t1066_ds_RM_w2$inst_sup), "NA='999'")
t1066_ds_RM_w2$inst_sup <- labelled(t1066_ds_RM_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rm, echo=F}
vari <- t1066_ds_RM_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rm, echo=F}
AfterH <- table(t1066_ds_RM_w2$inst_sup)
BeforeH <- table(t1066_RM_w2_inst_sup$f_PFRDSAT, t1066_RM_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`

* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 rp, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_inst_sup','10-66.1066-RuralPeru-Baseline', variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 rp, echo=F}
t1066_RP_w1_inst_sup <- opal.execute(o,'t1066_RP_w1_inst_sup')
vari <- t1066_RP_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_RP_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RP_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_RP_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 rp, echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_inst_sup$id)

t1066_RP_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_RP_w1_inst_sup$PFRD), "NA='-999'")
t1066_RP_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_RP_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_RP_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_RP_w1_inst_sup)[1]){
  if( t1066_RP_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_RP_w1$inst_sup[i] = 0 }
  else if(t1066_RP_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_RP_w1$inst_sup[i] = 1 }
  else if( t1066_RP_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_RP_w1$inst_sup[i] = 0 }
}
t1066_ds_RP_w1$inst_sup <- car::recode(as.vector(t1066_ds_RP_w1$inst_sup), "NA='999'")
t1066_ds_RP_w1$inst_sup <- labelled(t1066_ds_RP_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 rp, echo=F}
vari <- t1066_ds_RP_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 rp, echo=F}
AfterH <- table(t1066_ds_RP_w1$inst_sup)
BeforeH <- table(t1066_RP_w1_inst_sup$PFRDSAT, t1066_RP_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`    

* Description: 
```{r assign2 rp, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_inst_sup','10-66.1066-RuralPeru-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 rp, echo=F}
t1066_RP_w2_inst_sup <- opal.execute(o,'t1066_RP_w2_inst_sup')
vari <- t1066_RP_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_RP_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_RP_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_RP_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 rp, echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_inst_sup$id)

t1066_RP_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_RP_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_RP_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_RP_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_RP_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_RP_w2_inst_sup)[1]){
  if( t1066_RP_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_RP_w2$inst_sup[i] = 0 }
  else if(t1066_RP_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_RP_w2$inst_sup[i] = 1 }
  else if( t1066_RP_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_RP_w2$inst_sup[i] = 0 }
}
t1066_ds_RP_w2$inst_sup <- car::recode(as.vector(t1066_ds_RP_w2$inst_sup), "NA='999'")
t1066_ds_RP_w2$inst_sup <- labelled(t1066_ds_RP_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 rp, echo=F}
vari <- t1066_ds_RP_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 rp, echo=F}
AfterH <- table(t1066_ds_RP_w2$inst_sup)
BeforeH <- table(t1066_RP_w2_inst_sup$f_PFRDSAT, t1066_RP_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Urban China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 uch, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_inst_sup','10-66.1066-UrbanChina-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 uch, echo=F}
t1066_UCh_w1_inst_sup <- opal.execute(o,'t1066_UCh_w1_inst_sup')
vari <- t1066_UCh_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_UCh_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UCh_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_UCh_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 uch, echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_inst_sup$id)

t1066_UCh_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_UCh_w1_inst_sup$PFRD), "NA='-999'")
t1066_UCh_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_UCh_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_UCh_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_UCh_w1_inst_sup)[1]){
  if( t1066_UCh_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_UCh_w1$inst_sup[i] = 0 }
  else if(t1066_UCh_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_UCh_w1$inst_sup[i] = 1 }
  else if( t1066_UCh_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_UCh_w1$inst_sup[i] = 0 }
}
t1066_ds_UCh_w1$inst_sup <- car::recode(as.vector(t1066_ds_UCh_w1$inst_sup), "NA='999'")
t1066_ds_UCh_w1$inst_sup <- labelled(t1066_ds_UCh_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 uch, echo=F}
vari <- t1066_ds_UCh_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 uch, echo=F}
AfterH <- table(t1066_ds_UCh_w1$inst_sup)
BeforeH <- table(t1066_UCh_w1_inst_sup$PFRDSAT, t1066_UCh_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 uch, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_inst_sup','10-66.1066-UrbanChina-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 uch, echo=F}
t1066_UCh_w2_inst_sup <- opal.execute(o,'t1066_UCh_w2_inst_sup')
vari <- t1066_UCh_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_UCh_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UCh_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_UCh_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 uch, echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_inst_sup$id)

t1066_UCh_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_UCh_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_UCh_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_UCh_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_UCh_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_UCh_w2_inst_sup)[1]){
  if( t1066_UCh_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_UCh_w2$inst_sup[i] = 0 }
  else if(t1066_UCh_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_UCh_w2$inst_sup[i] = 1 }
  else if( t1066_UCh_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_UCh_w2$inst_sup[i] = 0 }
}
t1066_ds_UCh_w2$inst_sup <- car::recode(as.vector(t1066_ds_UCh_w2$inst_sup), "NA='999'")
t1066_ds_UCh_w2$inst_sup <- labelled(t1066_ds_UCh_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 uch, echo=F}
vari <- t1066_ds_UCh_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 uch, echo=F}
AfterH <- table(t1066_ds_UCh_w2$inst_sup)
BeforeH <- table(t1066_UCh_w2_inst_sup$f_PFRDSAT, t1066_UCh_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Urban Mexico
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 um, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_inst_sup','10-66.1066-UrbanMexico-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 um, echo=F}
t1066_UM_w1_inst_sup <- opal.execute(o,'t1066_UM_w1_inst_sup')
vari <- t1066_UM_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_UM_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UM_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_UM_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 um, echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_inst_sup$id)

t1066_UM_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_UM_w1_inst_sup$PFRD), "NA='-999'")
t1066_UM_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_UM_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_UM_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_UM_w1_inst_sup)[1]){
  if( t1066_UM_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_UM_w1$inst_sup[i] = 0 }
  else if(t1066_UM_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_UM_w1$inst_sup[i] = 1 }
  else if( t1066_UM_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_UM_w1$inst_sup[i] = 0 }
}
t1066_ds_UM_w1$inst_sup <- car::recode(as.vector(t1066_ds_UM_w1$inst_sup), "NA='999'")
t1066_ds_UM_w1$inst_sup <- labelled(t1066_ds_UM_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 um, echo=F}
vari <- t1066_ds_UM_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 um, echo=F}
AfterH <- table(t1066_ds_UM_w1$inst_sup)
BeforeH <- table(t1066_UM_w1_inst_sup$PFRDSAT, t1066_UM_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999','1'])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 um, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_inst_sup','10-66.1066-UrbanMexico-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 um, echo=F}
t1066_UM_w2_inst_sup <- opal.execute(o,'t1066_UM_w2_inst_sup')
vari <- t1066_UM_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_UM_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UM_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_UM_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 um, echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_inst_sup$id)

t1066_UM_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_UM_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_UM_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_UM_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_UM_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_UM_w2_inst_sup)[1]){
  if( t1066_UM_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_UM_w2$inst_sup[i] = 0 }
  else if(t1066_UM_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_UM_w2$inst_sup[i] = 1 }
  else if( t1066_UM_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_UM_w2$inst_sup[i] = 0 }
}
t1066_ds_UM_w2$inst_sup <- car::recode(as.vector(t1066_ds_UM_w2$inst_sup), "NA='999'")
t1066_ds_UM_w2$inst_sup <- labelled(t1066_ds_UM_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 um, echo=F}
vari <- t1066_ds_UM_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 um, echo=F}
AfterH <- table(t1066_ds_UM_w2$inst_sup)
BeforeH <- table(t1066_UM_w2_inst_sup$f_PFRDSAT, t1066_UM_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


## Urban Peru
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 up, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_inst_sup','10-66.1066-UrbanPeru-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 up, echo=F}
t1066_UP_w1_inst_sup <- opal.execute(o,'t1066_UP_w1_inst_sup')
vari <- t1066_UP_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_UP_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UP_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_UP_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 up, echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_inst_sup$id)

t1066_UP_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_UP_w1_inst_sup$PFRD), "NA='-999'")
t1066_UP_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_UP_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_UP_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_UP_w1_inst_sup)[1]){
  if( t1066_UP_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_UP_w1$inst_sup[i] = 0 }
  else if(t1066_UP_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_UP_w1$inst_sup[i] = 1 }
  else if( t1066_UP_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_UP_w1$inst_sup[i] = 0 }
}
t1066_ds_UP_w1$inst_sup <- car::recode(as.vector(t1066_ds_UP_w1$inst_sup), "NA='999'")
t1066_ds_UP_w1$inst_sup <- labelled(t1066_ds_UP_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 up, echo=F}
vari <- t1066_ds_UP_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 up, echo=F}
AfterH <- table(t1066_ds_UP_w1$inst_sup)
BeforeH <- table(t1066_UP_w1_inst_sup$PFRDSAT, t1066_UP_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 up, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_inst_sup','10-66.1066-UrbanPeru-Followup', variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 up, echo=F}
t1066_UP_w2_inst_sup <- opal.execute(o,'t1066_UP_w2_inst_sup')
vari <- t1066_UP_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_UP_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_UP_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_UP_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 up, echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_inst_sup$id)

t1066_UP_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_UP_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_UP_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_UP_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_UP_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_UP_w2_inst_sup)[1]){
  if( t1066_UP_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_UP_w2$inst_sup[i] = 0 }
  else if(t1066_UP_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_UP_w2$inst_sup[i] = 1 }
  else if( t1066_UP_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_UP_w2$inst_sup[i] = 0 }
}
t1066_ds_UP_w2$inst_sup <- car::recode(as.vector(t1066_ds_UP_w2$inst_sup), "NA='999'")
t1066_ds_UP_w2$inst_sup <- labelled(t1066_ds_UP_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 up, echo=F}
vari <- t1066_ds_UP_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 up, echo=F}
AfterH <- table(t1066_ds_UP_w2$inst_sup)
BeforeH <- table(t1066_UP_w2_inst_sup$f_PFRDSAT, t1066_UP_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign1 ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_inst_sup','10-66.1066-Venezuela-Baseline',variables=list('PFRDSAT', 'PFRD'), missings = TRUE)
```

```{r local1 ven, echo=F}
t1066_Ven_w1_inst_sup <- opal.execute(o,'t1066_Ven_w1_inst_sup')
vari <- t1066_Ven_w1_inst_sup$PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_inst_sup$PFRDSAT, missing_values = NA)
ggplot(t1066_Ven_w1_inst_sup, aes(x=factor(PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_Ven_w1_inst_sup$PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_inst_sup$PFRD, missing_values = NA)
ggplot(t1066_Ven_w1_inst_sup, aes(x=factor(PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo1 ven, echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_inst_sup$id)

t1066_Ven_w1_inst_sup$PFRD <- car::recode(as.vector(t1066_Ven_w1_inst_sup$PFRD), "NA='-999'")
t1066_Ven_w1_inst_sup$PFRDSAT <- car::recode(as.vector(t1066_Ven_w1_inst_sup$PFRDSAT), "NA='-999'")

t1066_ds_Ven_w1$inst_sup <- c(NA)
for(i in 1:dim(t1066_Ven_w1_inst_sup)[1]){
  if( t1066_Ven_w1_inst_sup$PFRDSAT[i] == 0 ) { 
    t1066_ds_Ven_w1$inst_sup[i] = 0 }
  else if(t1066_Ven_w1_inst_sup$PFRDSAT[i] == 1 ){ 
    t1066_ds_Ven_w1$inst_sup[i] = 1 }
  else if( t1066_Ven_w1_inst_sup$PFRD[i] == 0 ){ 
    t1066_ds_Ven_w1$inst_sup[i] = 0 }
}
t1066_ds_Ven_w1$inst_sup <- car::recode(as.vector(t1066_ds_Ven_w1$inst_sup), "NA='999'")
t1066_ds_Ven_w1$inst_sup <- labelled(t1066_ds_Ven_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ven, echo=F}
vari <- t1066_ds_Ven_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ven, echo=F}
AfterH <- table(t1066_ds_Ven_w1$inst_sup)
BeforeH <- table(t1066_Ven_w1_inst_sup$PFRDSAT, t1066_Ven_w1_inst_sup$PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `f_PFRDSAT`
* Label: `satisfaction with support from friends`
* Categories: 
    + `0 = dissatisfied`
    + `1 = satisfied`
    
* Name: `f_PFRD`
* Label: `has friends?`
* Categories: 
    + `0 = no`
    + `1 = yes`

* Description: 
```{r assign2 ven, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_inst_sup','10-66.1066-Venezuela-Followup',variables=list('f_PFRDSAT', 'f_PFRD'), missings = TRUE)
```

```{r local2 ven, echo=F}
t1066_Ven_w2_inst_sup <- opal.execute(o,'t1066_Ven_w2_inst_sup')
vari <- t1066_Ven_w2_inst_sup$f_PFRDSAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_inst_sup$f_PFRDSAT, missing_values = NA)
ggplot(t1066_Ven_w2_inst_sup, aes(x=factor(f_PFRDSAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("satisfaction with support from friends") + ylab("Frequency")
vari <- t1066_Ven_w2_inst_sup$f_PFRD
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_inst_sup$f_PFRD, missing_values = NA)
ggplot(t1066_Ven_w2_inst_sup, aes(x=factor(f_PFRD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has any friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `0 into 0`
* `else if PFRD=0 then 0`
* `NA into 999`

**R script:**

```{r harmo2 ven, echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_inst_sup$id)

t1066_Ven_w2_inst_sup$f_PFRD <- car::recode(as.vector(t1066_Ven_w2_inst_sup$f_PFRD), "NA='-999'")
t1066_Ven_w2_inst_sup$f_PFRDSAT <- car::recode(as.vector(t1066_Ven_w2_inst_sup$f_PFRDSAT), "NA='-999'")

t1066_ds_Ven_w2$inst_sup <- c(NA)
for(i in 1:dim(t1066_Ven_w2_inst_sup)[1]){
  if( t1066_Ven_w2_inst_sup$f_PFRDSAT[i] == 0 ) { 
    t1066_ds_Ven_w2$inst_sup[i] = 0 }
  else if(t1066_Ven_w2_inst_sup$f_PFRDSAT[i] == 1 ){ 
    t1066_ds_Ven_w2$inst_sup[i] = 1 }
  else if( t1066_Ven_w2_inst_sup$f_PFRD[i] == 0 ){ 
    t1066_ds_Ven_w2$inst_sup[i] = 0 }
}
t1066_ds_Ven_w2$inst_sup <- car::recode(as.vector(t1066_ds_Ven_w2$inst_sup), "NA='999'")
t1066_ds_Ven_w2$inst_sup <- labelled(t1066_ds_Ven_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 ven, echo=F}
vari <- t1066_ds_Ven_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 ven, echo=F}
AfterH <- table(t1066_ds_Ven_w2$inst_sup)
BeforeH <- table(t1066_Ven_w2_inst_sup$f_PFRDSAT, t1066_Ven_w2_inst_sup$f_PFRD, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH['0',]), sum(BeforeH['-999','0']))
BeforeH1[[2]] <- sum(BeforeH['1',])
BeforeH1[[3]] <- sum(BeforeH['-999',c('1','-999')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


```{r save,  echo=FALSE}
inst_sup <- t1066_ds_cuba_w1
save(inst_sup, file = "../RData/cuba_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_india_w1
save(inst_sup, file = "../RData/india_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_UCh_w1
save(inst_sup, file = "../RData/UCh_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_RCh_w1
save(inst_sup, file = "../RData/RCh_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_DR_w1
save(inst_sup, file = "../RData/DR_w1/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_Ven_w1
save(inst_sup, file = "../RData/Ven_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_UP_w1
save(inst_sup, file = "../RData/UP_w1/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_RP_w1
save(inst_sup, file = "../RData/RP_w1/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_UM_w1
save(inst_sup, file = "../RData/UM_w1/inst_sup.RData")
rm(inst_sup)

inst_sup <- t1066_ds_RM_w1
save(inst_sup, file = "../RData/RM_w1/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_PR_w1
save(inst_sup, file = "../RData/PR_w1/inst_sup.RData")
rm(inst_sup)




inst_sup <- t1066_ds_cuba_w2
save(inst_sup, file = "../RData/cuba_w2/inst_sup.RData")
rm(inst_sup)




inst_sup <- t1066_ds_UCh_w2
save(inst_sup, file = "../RData/UCh_w2/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_RCh_w2
save(inst_sup, file = "../RData/RCh_w2/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_DR_w2
save(inst_sup, file = "../RData/DR_w2/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_Ven_w2
save(inst_sup, file = "../RData/Ven_w2/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_UP_w2
save(inst_sup, file = "../RData/UP_w2/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_PR_w2
save(inst_sup, file = "../RData/PR_w2/inst_sup.RData")
rm(inst_sup)



inst_sup <- t1066_ds_UM_w2
save(inst_sup, file = "../RData/UM_w2/inst_sup.RData")
rm(inst_sup)

inst_sup <- t1066_ds_RM_w2
save(inst_sup, file = "../RData/RM_w2/inst_sup.RData")
rm(inst_sup)


inst_sup <- t1066_ds_RP_w2
save(inst_sup, file = "../RData/RP_w2/inst_sup.RData")
rm(inst_sup)

```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
