---
title: "Stroke or myocardial infarction (heart attack) or angina"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cvdDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cvdDS.R')
```

# Data process




## SHARE


### Wave 1

#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w1, echo=F}

load(paste0(datafolder,"w1/mi_ha.RData"))
SHARE_w1 <- tibble(id=mi_ha$id)
SHARE_w1$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w1/stroke.RData"))
SHARE_w1$stroke <- stroke$stroke
rm(stroke)

```

```{r local w1, echo=F}

vbl <- SHARE_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `cvd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `997 -> 997`
* `998 -> 998`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$cvd <- rep(999,length(SHARE_w1$id))
SHARE_ds_w1$cvd[which(SHARE_w1$mi_ha==998 | SHARE_w1$stroke==998)] <- 998
SHARE_ds_w1$cvd[which(SHARE_w1$mi_ha==997 | SHARE_w1$stroke==997)] <- 997
SHARE_ds_w1$cvd[which(SHARE_w1$mi_ha==0 & SHARE_w1$stroke==0)] <- 0
SHARE_ds_w1$cvd[which(SHARE_w1$mi_ha==1 | SHARE_w1$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- SHARE_ds_w1$cvd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(cvd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(SHARE_ds_w1$cvd)
X <- c(
  sum(SHARE_w1$mi_ha==0 & SHARE_w1$stroke==0,na.rm = T),
  sum(SHARE_w1$mi_ha==1 | SHARE_w1$stroke==1,na.rm=T),
  sum((SHARE_w1$mi_ha==997 | SHARE_w1$stroke==997),na.rm=T),
  sum((SHARE_w1$mi_ha==998 | SHARE_w1$stroke==998),na.rm = T)
)
BeforeH <- c(X[1:4],length(SHARE_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998","otherwise -> 999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w2, echo=F}

load(paste0(datafolder,"w2/mi_ha.RData"))
SHARE_w2 <- tibble(id=mi_ha$id)
SHARE_w2$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w2/stroke.RData"))
SHARE_w2$stroke <- stroke$stroke
rm(stroke)

```

```{r local w2, echo=F}

vbl <- SHARE_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w2)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w2)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `997 -> 997`
* `998 -> 998`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$cvd <- rep(999,length(SHARE_w2$id))
SHARE_ds_w2$cvd[which(SHARE_w2$mi_ha==998 | SHARE_w2$stroke==998)] <- 998
SHARE_ds_w2$cvd[which(SHARE_w2$mi_ha==997 | SHARE_w2$stroke==997)] <- 997
SHARE_ds_w2$cvd[which(SHARE_w2$mi_ha==0 & SHARE_w2$stroke==0)] <- 0
SHARE_ds_w2$cvd[which(SHARE_w2$mi_ha==1 | SHARE_w2$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- SHARE_ds_w2$cvd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(cvd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w2$cvd)
X <- c(
  sum(SHARE_w2$mi_ha==0 & SHARE_w2$stroke==0,na.rm = T),
  sum(SHARE_w2$mi_ha==1 | SHARE_w2$stroke==1,na.rm=T),
  sum((SHARE_w2$mi_ha==997 | SHARE_w2$stroke==997),na.rm=T),
  sum((SHARE_w2$mi_ha==998 | SHARE_w2$stroke==998),na.rm = T)
)
BeforeH <- c(X[1:4],length(SHARE_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998","otherwise -> 999")
kable(C)

```



### Wave 3

Not found.



### Wave 4


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w4, echo=F}

load(paste0(datafolder,"w4/mi_ha.RData"))
SHARE_w4 <- tibble(id=mi_ha$id)
SHARE_w4$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w4/stroke.RData"))
SHARE_w4$stroke <- stroke$stroke
rm(stroke)

```

```{r local w4, echo=F}

vbl <- SHARE_w4$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w4)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w4)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `997 -> 997`
* `998 -> 998`
* `otherwise into 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$cvd <- rep(999,length(SHARE_w4$id))
SHARE_ds_w4$cvd[which(SHARE_w4$mi_ha==998 | SHARE_w4$stroke==998)] <- 998
SHARE_ds_w4$cvd[which(SHARE_w4$mi_ha==997 | SHARE_w4$stroke==997)] <- 997
SHARE_ds_w4$cvd[which(SHARE_w4$mi_ha==0 & SHARE_w4$stroke==0)] <- 0
SHARE_ds_w4$cvd[which(SHARE_w4$mi_ha==1 | SHARE_w4$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- SHARE_ds_w4$cvd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(cvd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w4$cvd)
X <- c(
  sum(SHARE_w4$mi_ha==0 & SHARE_w4$stroke==0,na.rm = T),
  sum(SHARE_w4$mi_ha==1 | SHARE_w4$stroke==1,na.rm=T),
  sum((SHARE_w4$mi_ha==997 | SHARE_w4$stroke==997),na.rm=T),
  sum((SHARE_w4$mi_ha==998 | SHARE_w4$stroke==998),na.rm = T)
)
BeforeH <- c(X[1:4],length(SHARE_w4$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998","otherwise -> 999")
kable(C)

```




### Wave 5


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w5, echo=F}

load(paste0(datafolder,"w5/mi_ha.RData"))
SHARE_w5 <- tibble(id=mi_ha$id)
SHARE_w5$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w5/stroke.RData"))
SHARE_w5$stroke <- stroke$stroke
rm(stroke)

```

```{r local w5, echo=F}

vbl <- SHARE_w5$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w5)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w5$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(SHARE_w5)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `997 -> 997`
* `998 -> 998`
* `otherwise into 999`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$cvd <- rep(999,length(SHARE_w5$id))
SHARE_ds_w5$cvd[which(SHARE_w5$mi_ha==998 | SHARE_w5$stroke==998)] <- 998
SHARE_ds_w5$cvd[which(SHARE_w5$mi_ha==997 | SHARE_w5$stroke==997)] <- 997
SHARE_ds_w5$cvd[which(SHARE_w5$mi_ha==0 & SHARE_w5$stroke==0)] <- 0
SHARE_ds_w5$cvd[which(SHARE_w5$mi_ha==1 | SHARE_w5$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- SHARE_ds_w5$cvd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(cvd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w5$cvd)
X <- c(
  sum(SHARE_w5$mi_ha==0 & SHARE_w5$stroke==0,na.rm = T),
  sum(SHARE_w5$mi_ha==1 | SHARE_w5$stroke==1,na.rm=T),
  sum((SHARE_w5$mi_ha==997 | SHARE_w5$stroke==997),na.rm=T),
  sum((SHARE_w5$mi_ha==998 | SHARE_w5$stroke==998),na.rm = T)
)
BeforeH <- c(X[1:4],length(SHARE_w5$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998","otherwise -> 999")
kable(C)

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation

It contains information about myocardial infarction and stroke harmonized variables. 







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





