---
title: "Multimorbidity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/multimorbidDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/multimorbidDS.R')
```



# Data process


## SHARE

### Wave 1

#### Study-specific variable description



| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`|`mi_ha`| `stroke`|
|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  |`share_w1_hd`|`share_w1_hd`|`share_w1_hd`|`share_w1_hd`|`share_w1_hd`| `share_w1_hd` |`share_w1_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes` |
| **Missings** |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |

```{r assign w1, echo=F}


opal.assign.table.tibble(o, 'share_w1','SHARE_HD.share_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','mi_ha','stroke'), missings = T)
share_w1 <- opal.execute(o,'share_w1')

```

```{r local w1, echo=F}

vbl <- share_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_joint_disorders, stroke, mi_ha, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w1}

SHARE_ds_w1 <- share_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- SHARE_ds_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}
```


### Wave 2

#### Study-specific variable description



| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`|`mi_ha`| `stroke`|
|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  |`share_w2_hd`|`share_w2_hd`|`share_w2_hd`|`share_w2_hd`|`share_w2_hd`| `share_w2_hd` |`share_w2_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes` |
| **Missings** |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |

```{r assign w2, echo=F}


opal.assign.table.tibble(o, 'share_w2','SHARE_HD.share_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','mi_ha','stroke'), missings = T)
share_w2 <- opal.execute(o,'share_w2')

```

```{r local w2, echo=F}

vbl <- share_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_joint_disorders, stroke, mi_ha, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w2}

SHARE_ds_w2 <- share_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- SHARE_ds_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}
```

### Wave 3
Not harmonisable.

### Wave 4

#### Study-specific variable description



| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`|`mi_ha`| `stroke`|
|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  |`share_w4_hd`|`share_w4_hd`|`share_w4_hd`|`share_w4_hd`|`share_w4_hd`| `share_w4_hd` |`share_w4_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes` |
| **Missings** |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |

```{r assign w4, echo=F}


opal.assign.table.tibble(o, 'share_w4','SHARE_HD.share_w4_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','mi_ha','stroke'), missings = T)
share_w4 <- opal.execute(o,'share_w4')

```

```{r local w4, echo=F}

vbl <- share_w4$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w4$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_joint_disorders, stroke, mi_ha, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w4}

SHARE_ds_w4 <- share_w4 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- SHARE_ds_w4$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F}
```


### Wave 5

#### Study-specific variable description



| **Name** |`h_diabetes`|`h_hypertension`|`h_joint_disorders`|`h_cpd`|`mi_ha`| `stroke`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  |`share_w5_hd`|`share_w5_hd`|`share_w5_hd`|`share_w5_hd`|`share_w5_hd`| `share_w5_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes` |
| **Missings** |`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` | `997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |

```{r assign w5, echo=F}


opal.assign.table.tibble(o, 'share_w5','SHARE_HD.share_w5_hd',variables=list('h_diabetes','h_hypertension','h_joint_disorders','h_cpd','mi_ha','stroke'), missings = T)
share_w5 <- opal.execute(o,'share_w5')

```

```{r local w5, echo=F}

vbl <- share_w5$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w5$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w5$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w5$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w5$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- share_w5$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(share_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_hypertension, h_joint_disorders, stroke, mi_ha, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w5}

SHARE_ds_w5 <- share_w5 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- SHARE_ds_w5$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F}
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
