---
title: "Respiratory diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_respiratory`
* Variable label: `Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`
* Variable description: `The participant has one or more of the following respiratory diseases: respiratory, chronic bronchitis, emphysema, chronic pulmonary disease, chronic obstructive pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no respiratory disease
1        | yes, respiratory disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## SHARE


### Wave 1

#### Study-specific variable description

| **Name** | `ph006d7` |`ph006d6`|
|-|-|-|
| **Label** | `doctor told you had: asthma` |`doctor told you had: chronic lung disease`|
| **Table name**  | `sharew1_rel2-6-0_ph` | `sharew1_rel2-6-0_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` |`1 = selected`<br/>`0 = not selected` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_ph',variables=list('ph006d7','ph006d6'), missings = T)
SHARE_w1 <- opal.execute(o,'SHARE_w1')

```

```{r local w1, echo=F}

vbl <- SHARE_w1$ph006d7
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(ph006d7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w1$ph006d6
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(ph006d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `ph006d7 == 0 and ph006d6 == 0 into 0`
* `ph006d7 == 1 or ph006d6 ==  1 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$h_respiratory <- rep(999,length(SHARE_w1$id))

SHARE_ds_w1$h_respiratory[which(SHARE_w1$ph006d7==0 & SHARE_w1$ph006d6==0)] <- 0
SHARE_ds_w1$h_respiratory[which(SHARE_w1$ph006d7 == 1 | SHARE_w1$ph006d6 == 1)] <- 1
SHARE_ds_w1$h_respiratory[which((SHARE_w1$ph006d7==-2 & (SHARE_w1$ph006d6 != 1 | is.na(SHARE_w1$ph006d6))) | (SHARE_w1$ph006d6==-2 & (SHARE_w1$ph006d7 != 1 | is.na(SHARE_w1$ph006d7))))] <- 997
SHARE_ds_w1$h_respiratory[which((SHARE_w1$ph006d7==-1 & (SHARE_w1$ph006d6 != 1 | is.na(SHARE_w1$ph006d6))) | (SHARE_w1$ph006d6==-1 & (SHARE_w1$ph006d7 != 1 | is.na(SHARE_w1$ph006d7))))] <- 998

# We build a global table in order to have updated the status of all the individuals through the different waves
SHARE_ds <- SHARE_ds_w1
SHARE_ds$asthma <- car::recode(SHARE_w1$ph006d7,"-2=997;-1=998;NA=999")
SHARE_ds$cpd <- car::recode(SHARE_w1$ph006d6,"-2=997;-1=998;NA=999")


```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- SHARE_ds_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(SHARE_ds_w1$h_respiratory)
X <- c(
  sum(SHARE_w1$ph006d7==0 & SHARE_w1$ph006d6==0,na.rm = T),
  sum(SHARE_w1$ph006d7 == 1 | SHARE_w1$ph006d6 == 1,na.rm=T),
  sum((SHARE_w1$ph006d7==-2 & (SHARE_w1$ph006d6 != 1 | is.na(SHARE_w1$ph006d6))) | (SHARE_w1$ph006d6==-2 & (SHARE_w1$ph006d7 != 1 | is.na(SHARE_w1$ph006d7))),na.rm=T),
  sum((SHARE_w1$ph006d7==-1 & (SHARE_w1$ph006d6 != 1 | is.na(SHARE_w1$ph006d6))) | (SHARE_w1$ph006d6==-1 & (SHARE_w1$ph006d7 != 1 | is.na(SHARE_w1$ph006d7))),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `ph006d7` |`ph006d6`|
|-|-|-|
| **Label** | `doctor told you had: asthma` |`doctor told you had: chronic lung disease`|
| **Table name**  | `sharew2_rel2-6-0_ph` | `sharew2_rel2-6-0_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` |`1 = selected`<br/>`0 = not selected` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |`-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_ph',variables=list('ph006d7','ph006d6'), missings = T)
SHARE_w2 <- opal.execute(o,'SHARE_w2')

```

```{r local w2, echo=F}

vbl <- SHARE_w2$ph006d7
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(ph006d7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w2$ph006d6
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(ph006d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `ph006d7 (w1) == 0 and ph006d7 (w2) == 0 and ph006d6 (w1) == 0 and ph006d6 (w2) == 0 into 0`
* `ph006d7 (w1) == 1 or ph006d7 (w2) == 1 or ph006d6 (w1) == 1 or ph006d6 (w2) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
SHARE_w2 <- left_join(SHARE_w2, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)

SHARE_ds_w2$asthma <- rep(999,length(SHARE_w2$id))
SHARE_ds_w2$asthma[which((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == 0)] <- 0
SHARE_ds_w2$asthma[which((SHARE_w2$asthma == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d7 == 1)] <- 1
SHARE_ds_w2$asthma[which((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == -2)] <- 997
SHARE_ds_w2$asthma[which((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == -1)] <- 998

SHARE_ds_w2$cpd <- rep(999,length(SHARE_w2$id))
SHARE_ds_w2$cpd[which((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == 0)] <- 0
SHARE_ds_w2$cpd[which((SHARE_w2$cpd == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d6 == 1)] <- 1
SHARE_ds_w2$cpd[which((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == -2)] <- 997
SHARE_ds_w2$cpd[which((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == -1)] <- 998

SHARE_ds_w2$h_respiratory <- rep(999,length(SHARE_ds_w2$id))
SHARE_ds_w2$h_respiratory[which(SHARE_ds_w2$asthma == 0 & SHARE_ds_w2$cpd == 0)] <- 0
SHARE_ds_w2$h_respiratory[which(SHARE_ds_w2$asthma == 1 | SHARE_ds_w2$cpd == 1)] <- 1
SHARE_ds_w2$h_respiratory[which((SHARE_ds_w2$asthma == 997 & SHARE_ds_w2$cpd != 1) | (SHARE_ds_w2$cpd == 997 & SHARE_ds_w2$asthma != 1))] <- 997
SHARE_ds_w2$h_respiratory[which((SHARE_ds_w2$asthma == 998 & SHARE_ds_w2$cpd != 1) | (SHARE_ds_w2$cpd == 998 & SHARE_ds_w2$asthma != 1))] <- 998

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w2,log_vec=SHARE_ds_w2$id,col_end_index = 2, col_st_index = 7)
SHARE_ds_aux <- SHARE_ds_prov
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w2,log_vec=SHARE_ds_w2$id,col_end_index = 3, col_st_index = 5)
SHARE_ds_aux$asthma <- SHARE_ds_prov$asthma
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w2,log_vec=SHARE_ds_w2$id,col_end_index = 4, col_st_index = 6)
SHARE_ds_aux$cpd <- SHARE_ds_prov$cpd
SHARE_ds <- SHARE_ds_aux
rm(SHARE_ds_prov)
rm(SHARE_ds_aux)

SHARE_ds_w2 <- SHARE_ds_w2[,c("id","h_respiratory")]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- SHARE_ds_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w2$h_respiratory)
X <- c(
  sum(((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == 0) & ((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == 0),na.rm = T),
  sum(((SHARE_w2$asthma == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d7 == 1) | ((SHARE_w2$cpd == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d6 == 1),na.rm=T),
  
  sum((((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == -2) & !((!is.na(SHARE_w2$cpd) & SHARE_w2$cpd == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d6 == 1)) | (((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == -2) & !((!is.na(SHARE_w2$asthma) & SHARE_w2$asthma == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d7 == 1)),na.rm=T),
  sum((((SHARE_w2$asthma != 1 | is.na(SHARE_w2$asthma)) & SHARE_w2$ph006d7 == -1) & !((!is.na(SHARE_w2$cpd) & SHARE_w2$cpd == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d6 == 1)) | (((SHARE_w2$cpd != 1 | is.na(SHARE_w2$cpd)) & SHARE_w2$ph006d6 == -1) & !((!is.na(SHARE_w2$asthma) & SHARE_w2$asthma == 1 & !(is.na(SHARE_w2$ph006d7) & is.na(SHARE_w2$ph006d6))) | SHARE_w2$ph006d7 == 1)),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)



cat("There are 375 individuals which tell in this wave they do not have asthma, and answered that they had in the first wave. There are 486 individuals which tell they have chronic lung diseases in the first wave and they don't in the second. All them are harmonized as having chronic respiratory disorders.")
kable(frq(SHARE_w2$ph006d7[which(SHARE_w2$asthma==1)]), align='c')
kable(frq(SHARE_w2$ph006d6[which(SHARE_w2$cpd==1)]), align = 'c')

```



### Wave 3

Not found.



### Wave 4


#### Study-specific variable description

| **Name** | `ph006d7` |`ph006d6`|
|-|-|-|
| **Label** | `doctor told you had: asthma` |`doctor told you had: chronic lung disease`|
| **Table name**  | `sharew4_rel1-1-1_ph` | `sharew4_rel1-1-1_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` |`1 = selected`<br/>`0 = not selected`|
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |`-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_ph',variables=list('ph006d7','ph006d6'), missings = T)
SHARE_w4 <- opal.execute(o,'SHARE_w4')

```

```{r local w4, echo=F}

vbl <- SHARE_w4$ph006d7
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(ph006d7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w4$ph006d6
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(ph006d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `ph006d7 (w1) == 0 and ph006d7 (w2) == 0 and ph006d7 (w4) == 0 and ph006d6 (w1) == 0 and ph006d6 (w2) == 0 and ph006d6 (w4) == 0 into 0`
* `ph006d7 (w1) == 1 or ph006d7 (w2) == 1 or ph006d7 (w4) == 1 or ph006d6 (w1) == 1 or ph006d6 (w2) == 1 or ph006d6 (w4) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
SHARE_w4 <- left_join(SHARE_w4, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)

SHARE_ds_w4$asthma <- rep(999,length(SHARE_w4$id))
SHARE_ds_w4$asthma[which((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == 0)] <- 0
SHARE_ds_w4$asthma[which((SHARE_w4$asthma == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d7 == 1)] <- 1
SHARE_ds_w4$asthma[which((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == -2)] <- 997
SHARE_ds_w4$asthma[which((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == -1)] <- 998

SHARE_ds_w4$cpd <- rep(999,length(SHARE_w4$id))
SHARE_ds_w4$cpd[which((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == 0)] <- 0
SHARE_ds_w4$cpd[which((SHARE_w4$cpd == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d6 == 1)] <- 1
SHARE_ds_w4$cpd[which((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == -2)] <- 997
SHARE_ds_w4$cpd[which((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == -1)] <- 998

SHARE_ds_w4$h_respiratory <- rep(999,length(SHARE_ds_w4$id))
SHARE_ds_w4$h_respiratory[which(SHARE_ds_w4$asthma == 0 & SHARE_ds_w4$cpd == 0)] <- 0
SHARE_ds_w4$h_respiratory[which(SHARE_ds_w4$asthma == 1 | SHARE_ds_w4$cpd == 1)] <- 1
SHARE_ds_w4$h_respiratory[which((SHARE_ds_w4$asthma == 997 & SHARE_ds_w4$cpd != 1) | (SHARE_ds_w4$cpd == 997 & SHARE_ds_w4$asthma != 1))] <- 997
SHARE_ds_w4$h_respiratory[which((SHARE_ds_w4$asthma == 998 & SHARE_ds_w4$cpd != 1) | (SHARE_ds_w4$cpd == 998 & SHARE_ds_w4$asthma != 1))] <- 998



# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w4,log_vec=SHARE_ds_w4$id,col_end_index = 2, col_st_index = 7)
SHARE_ds_aux <- SHARE_ds_prov
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w4,log_vec=SHARE_ds_w4$id,col_end_index = 3, col_st_index = 5)
SHARE_ds_aux$asthma <- SHARE_ds_prov$asthma
SHARE_ds_prov <- assign_merge(SHARE_ds,SHARE_ds_w4,log_vec=SHARE_ds_w4$id,col_end_index = 4, col_st_index = 6)
SHARE_ds_aux$cpd <- SHARE_ds_prov$cpd
SHARE_ds <- SHARE_ds_aux
rm(SHARE_ds_prov)
rm(SHARE_ds_aux)

SHARE_ds_w4 <- SHARE_ds_w4[,c("id","h_respiratory")]

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- SHARE_ds_w4$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w4$h_respiratory)
X <- c(
  sum(((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == 0) & ((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == 0),na.rm = T),
  sum(((SHARE_w4$asthma == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d7 == 1) | ((SHARE_w4$cpd == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d6 == 1),na.rm=T),
  sum((((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == -2) & !((!is.na(SHARE_w4$cpd) & SHARE_w4$cpd == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d6 == 1)) | (((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == -2) & !((!is.na(SHARE_w4$asthma) & SHARE_w4$asthma == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d7 == 1)),na.rm=T),
  sum((((SHARE_w4$asthma != 1 | is.na(SHARE_w4$asthma)) & SHARE_w4$ph006d7 == -1) & !((!is.na(SHARE_w4$cpd) & SHARE_w4$cpd == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d6 == 1)) | (((SHARE_w4$cpd != 1 | is.na(SHARE_w4$cpd)) & SHARE_w4$ph006d6 == -1) & !((!is.na(SHARE_w4$asthma) & SHARE_w4$asthma == 1 & !(is.na(SHARE_w4$ph006d7) & is.na(SHARE_w4$ph006d6))) | SHARE_w4$ph006d7 == 1)),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w4$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

cat("There are 1030 individuals which tell in this wave they do not have asthma, and answered that they had in previous waves. There are 631 individuals which tell they have chronic lung diseases in the previous waves and they don't in the present one. All them are harmonized as having chronic respiratory disorders.")
kable(frq(SHARE_w4$ph006d7[which(SHARE_w4$asthma==1)]), align='c')
kable(frq(SHARE_w4$ph006d6[which(SHARE_w4$cpd==1)]), align = 'c')

```




### Wave 5


#### Study-specific variable description

| **Name** |`ph006d6`|
|-|-|-|
| **Label** |`doctor told you had: chronic lung disease`|
| **Table name**  |`sharew5_rel1-0-0_ph` |
| **Categories** |`1 = selected`<br/>`0 = not selected` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |

```{r assign w5, echo=F}

opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_ph',variables=list('ph006d6'), missings = T)
SHARE_w5 <- opal.execute(o,'SHARE_w5')

```

```{r local w5, echo=F}

vbl <- SHARE_w5$ph006d6
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(ph006d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `ph006d6 (w1) == 0 and ph006d6 (w2) == 0 and ph006d6 (w4) == 0 and ph006d6 (w5) == 0 and ph006d7 (w1) == 0 and ph006d7 (w2) == 0 and ph006d7 (w4) == 0 into 0`
* `ph006d6 (w1) == 1 or ph006d6 (w2) == 1 or ph006d6 (w4) == 1 or ph006d6 (w5) == 1 or ph006d7 (w1) == 1 or ph006d7 (w2) == 1 or ph006d7 (w4) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w5}

# We use the harmonized variable of previous waves instead of the study-specific variables
SHARE_w5 <- left_join(SHARE_w5, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)

SHARE_ds_w5$asthma <- rep(999,length(SHARE_w5$id))
SHARE_ds_w5$asthma[which(SHARE_w5$asthma == 1)] <- 1

SHARE_ds_w5$cpd <- rep(999,length(SHARE_w5$id))
SHARE_ds_w5$cpd[which((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == 0)] <- 0
SHARE_ds_w5$cpd[which((SHARE_w5$cpd == 1 & !is.na(SHARE_w5$ph006d6)) | SHARE_w5$ph006d6 == 1)] <- 1
SHARE_ds_w5$cpd[which((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == -2)] <- 997
SHARE_ds_w5$cpd[which((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == -1)] <- 998

SHARE_ds_w5$h_respiratory <- rep(999,length(SHARE_ds_w5$id))
SHARE_ds_w5$h_respiratory[which(SHARE_ds_w5$asthma != 1 & SHARE_ds_w5$cpd == 0)] <- 0
SHARE_ds_w5$h_respiratory[which(SHARE_ds_w5$asthma == 1 | SHARE_ds_w5$cpd == 1)] <- 1
SHARE_ds_w5$h_respiratory[which(SHARE_ds_w5$cpd == 997 & SHARE_ds_w5$asthma != 1)] <- 997
SHARE_ds_w5$h_respiratory[which(SHARE_ds_w5$cpd == 998 & SHARE_ds_w5$asthma != 1)] <- 998

SHARE_ds_w5 <- SHARE_ds_w5[,c("id","h_respiratory")]

# We update the status of the individuals in the global table
rm(SHARE_ds)

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- SHARE_ds_w5$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w5$h_respiratory)
X <- c(
  sum((SHARE_w5$asthma != 1 | is.na(SHARE_w5$asthma)) & ((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == 0),na.rm = T),
  sum(SHARE_w5$asthma == 1 | ((SHARE_w5$cpd == 1 & !is.na(SHARE_w5$ph006d6)) | SHARE_w5$ph006d6 == 1),na.rm=T),
  sum((SHARE_w5$asthma != 1 | is.na(SHARE_w5$asthma)) & ((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == -2),na.rm=T),
  sum((SHARE_w5$asthma != 1 | is.na(SHARE_w5$asthma)) & ((SHARE_w5$cpd != 1 | is.na(SHARE_w5$cpd)) & SHARE_w5$ph006d6 == -1),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w5$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

# Checking
cat("There are 1641 individuals which tell they have chronic lung diseases in the previous waves and they don't in this one. All them are harmonized as having chronic respiratory disorders.")
kable(frq(SHARE_w5$ph006d6[which(SHARE_w5$cpd==1)]), align = 'c')

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(w1 = SHARE_ds_w1, w2 = SHARE_ds_w2, w4 = SHARE_ds_w4, w5 = SHARE_ds_w5)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("SHARE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]])
             )
names(t.hds)<-c("val", "label", "w1", "w2", "w4", "w5")
kable(t.hds)

dbb <- merge(SHARE_m_ds_w1[,c("id","h_respiratory")], SHARE_m_ds_w2[,c("id","h_respiratory")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,SHARE_m_ds_w4[,c("id","h_respiratory")], by="id", all=T)
dbb <- merge(dbb, SHARE_m_ds_w5[,c("id","h_respiratory")], by="id", suffixes = c(".w4",".w5"), all=T)
names(dbb) <- c("id", "w1", "w2","w4","w5")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

We assume that if an individual answers it has some chronic respiratory disease in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
It contains information about asthma and chronic lung disease


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_respiratory <- l.hds[[index]]
  save(h_respiratory, file = paste0(datafolder,names(l.hds)[index],"/h_respiratory.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





