---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hypertensionDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hypertensionDS.R')
```




# Data process



## SHARE


### Wave 1

#### Study-specific variable description

| **Name** | `ph006d2` |`ph009_2`|
|-|-|-|
| **Label** | `doctor told you had: high blood pressure or hypertension` |`age high blood pressure`|
| **Table name**  | `sharew1_rel2-6-0_ph` | `sharew1_rel2-6-0_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` | `continuous` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_ph',variables=list('ph006d2','ph009_2'), missings = T)
SHARE_w1 <- opal.execute(o,'SHARE_w1')

```

```{r local w1, echo=F}

vbl <- SHARE_w1$ph006d2
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(ph006d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w1$ph009_2
kable(Continuous_summary(var = vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w1, aes(ph009_2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```

#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = ph009_2`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-1 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$h_hypertension <- car::recode(SHARE_w1$ph006d2, "-2=997;-1=998;NA = 999")

# Continuous variable harmonization
hypertension_age <- car::recode(SHARE_w1$ph009_2[which(SHARE_ds_w1$h_hypertension == 1)],"-1=998; -2=997; NA=999")
SHARE_ds_w1$h_hypertension_age <- car::recode(SHARE_ds_w1$h_hypertension, "0 = 996; 1 = hypertension_age; miss_values_vector=999")

# We build a global table in order to have updated the hypertension status of all the individuals through the different waves
SHARE_ds <- SHARE_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- SHARE_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SHARE_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(SHARE_ds_w1$h_hypertension)
BeforeH <- table(SHARE_w1$ph006d2, useNA = "ifany")[c(3,4,1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","-2->997","-1->998","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `ph006d2` |`ph009_2`|
|-|-|-|
| **Label** | `doctor told you had: high blood pressure or hypertension` |`age high blood pressure`|
| **Table name**  | `sharew2_rel2-6-0_ph` | `sharew2_rel2-6-0_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` | `continuous` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |`-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_ph',variables=list('ph006d2','ph009_2'), missings = T)
SHARE_w2 <- opal.execute(o,'SHARE_w2')

```

```{r local w2, echo=F}

vbl <- SHARE_w2$ph006d2
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(ph006d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w2$ph009_2
kable(Continuous_summary(var = vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[3])
pander(Continuous_summary(vbl, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w2, aes(ph009_2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `ph006d2 (w1) == 0 and ph006d2 (w2) == 0 into 0`
* `ph006d2 (w1) == 1 or ph006d2 (w2) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and missing age in w1, h_hypertension_age = ph009_2`
* `if h_hypertension == 1 in w2 and non-missing age in w1, h_hypertension_age = as in w1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
SHARE_w2 <- left_join(SHARE_w2, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$h_hypertension <- rep(999,length(SHARE_ds_w2$id))
SHARE_ds_w2$h_hypertension[which(SHARE_w2$ph006d2 == 0 & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)))] <- 0
SHARE_ds_w2$h_hypertension[which(SHARE_w2$ph006d2 == 1 | ((!is.na(SHARE_w2$ph006d2)) & SHARE_w2$h_hypertension == 1))] <- 1
SHARE_ds_w2$h_hypertension[which(SHARE_w2$ph006d2 == -1 & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)))] <- 998
SHARE_ds_w2$h_hypertension[which(SHARE_w2$ph006d2 == -2 & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)))] <- 997

# Continuous variable harmonization
SHARE_ds_w2$h_hypertension_age <- rep(999,length(SHARE_ds_w2$id))
SHARE_ds_w2$h_hypertension_age[which(SHARE_ds_w2$h_hypertension==0)] <- 996
# if h_hypertension == 1 in w2 and missing age in w1, h_hypertension_age = ph009_2
SHARE_ds_w2$h_hypertension_age[which(SHARE_ds_w2$h_hypertension==1 & (is.na(SHARE_w2$h_hypertension_age) | SHARE_w2$h_hypertension_age %in% miss_values_vector))] <- SHARE_w2$ph009_2[which(SHARE_ds_w2$h_hypertension==1 & (is.na(SHARE_w2$h_hypertension_age) | SHARE_w2$h_hypertension_age %in% miss_values_vector))]
# if h_hypertension == 1 in w2 and non-missing age in w1, h_hypertension_age = as in w1
SHARE_ds_w2$h_hypertension_age[which(SHARE_ds_w2$h_hypertension==1 & !(is.na(SHARE_w2$h_hypertension_age) | SHARE_w2$h_hypertension_age %in% miss_values_vector))] <- SHARE_w2$h_hypertension_age[which(SHARE_ds_w2$h_hypertension==1 & !(is.na(SHARE_w2$h_hypertension_age) | SHARE_w2$h_hypertension_age %in% miss_values_vector))]
SHARE_ds_w2$h_hypertension_age <- car::recode(SHARE_ds_w2$h_hypertension_age, "-1=998;-2=997;NA=999")

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
SHARE_ds_prov <- SHARE_ds[,c(1,2)]
SHARE_ds_prov <- assign_merge(SHARE_ds_prov,SHARE_ds_w2,log_vec=SHARE_ds_w2$id,col_end_index = 2, col_st_index = 3)
SHARE_ds_aux <- SHARE_ds[,c(1,3)]
SHARE_ds_aux <- assign_merge(SHARE_ds_aux,SHARE_ds_w2,log_vec=SHARE_ds_w2$id[which(SHARE_ds_w2$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
SHARE_ds <- SHARE_ds_prov
SHARE_ds$h_hypertension_age <- SHARE_ds_aux$h_hypertension_age
rm(SHARE_ds_prov)
rm(SHARE_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- SHARE_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SHARE_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w2$h_hypertension)
X <- c(
  sum(((!is.na(SHARE_w2$ph006d2)) & SHARE_w2$ph006d2 == 0) & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)),na.rm = T),
  sum(((!is.na(SHARE_w2$ph006d2)) & SHARE_w2$ph006d2 == 1) | ((!is.na(SHARE_w2$h_hypertension)) & (!is.na(SHARE_w2$ph006d2)) & SHARE_w2$h_hypertension == 1)),
  sum(((!is.na(SHARE_w2$ph006d2)) & SHARE_w2$ph006d2 == -2) & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)),na.rm=T),
  sum(((!is.na(SHARE_w2$ph006d2)) & SHARE_w2$ph006d2 == -1) & (SHARE_w2$h_hypertension != 1 | is.na(SHARE_w2$h_hypertension)),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

# Checking
cat("There are 1443 individuals whose answer in the first wave is that they were diagnosed to have high blood pressure or hypertension and in the second wave is that they do not have it. We compute them in the harmonized variable as having hypertension")
kable(frq(SHARE_w2$ph006d2[which(SHARE_w2$h_hypertension==1)]), align = 'c')

kable(SHARE_w2[which(!is.na(SHARE_w2$ph009_2) & SHARE_w2$ph006d2==0),],align = 'c',caption = 'There are 2 individuals answering they have no hypertension but an age of diagnostic. We keep it as non having hypertension and correct the age to missing')

kable(SHARE_w2[which(!is.na(SHARE_w2$h_hypertension_age) & !is.na(SHARE_w2$ph009_2) & !SHARE_w2$h_hypertension_age %in% miss_values_vector & SHARE_w2$h_hypertension_age!=SHARE_w2$ph009_2),], align = 'c',caption = 'There are 51 individuals which answer different diagnostic ages in the two waves. We harmonize the age from wave 1')

```



### Wave 3

Not found.



### Wave 4


#### Study-specific variable description

| **Name** | `ph006d2` |`ph009_2`|
|-|-|-|
| **Label** | `doctor told you had: high blood pressure or hypertension` |`age high blood pressure`|
| **Table name**  | `sharew4_rel1-1-1_ph` | `sharew4_rel1-1-1_ph` |
| **Categories** | `1 = selected`<br/>`0 = not selected` | `continuous` |
| **Missings** | `-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |`-1 = don't know`<br/>`-2 = refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_ph',variables=list('ph006d2','ph009_2'), missings = T)
SHARE_w4 <- opal.execute(o,'SHARE_w4')

```

```{r local w4, echo=F}

vbl <- SHARE_w4$ph006d2
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(ph006d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w4$ph009_2
kable(Continuous_summary(var = vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[3])
pander(Continuous_summary(vbl, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w4, aes(ph009_2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,100)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `ph006d2 (w1) == 0 and ph006d2 (w2) == 0 and ph006d2 (w4) == 0 into 0`
* `ph006d2 (w1) == 1 or ph006d2 (w2) == 1 or ph006d2 (w4) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w4 and missing age previously, h_hypertension_age = ph009_2`
* `if h_hypertension == 1 in w4 and non-missing age previously, h_hypertension_age = as before`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-2 into 997`
* `-1 into 998`
* `missing ages into 991`
* `otherwise 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
SHARE_w4 <- left_join(SHARE_w4, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$h_hypertension <- rep(999,length(SHARE_ds_w4$id))
SHARE_ds_w4$h_hypertension[which(SHARE_w4$ph006d2 == 0 & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)))] <- 0
SHARE_ds_w4$h_hypertension[which(SHARE_w4$ph006d2 == 1 | ((!is.na(SHARE_w4$ph006d2)) & SHARE_w4$h_hypertension == 1))] <- 1
SHARE_ds_w4$h_hypertension[which(SHARE_w4$ph006d2 == -1 & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)))] <- 998
SHARE_ds_w4$h_hypertension[which(SHARE_w4$ph006d2 == -2 & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)))] <- 997

# Continuous variable harmonization
SHARE_ds_w4$h_hypertension_age <- rep(999,length(SHARE_ds_w4$id))
SHARE_ds_w4$h_hypertension_age[which(SHARE_ds_w4$h_hypertension==0)] <- 996
# if h_hypertension == 1 in w4 and missing age previously, h_hypertension_age = ph009_2
SHARE_ds_w4$h_hypertension_age[which(SHARE_ds_w4$h_hypertension==1 & (is.na(SHARE_w4$h_hypertension_age) | SHARE_w4$h_hypertension_age %in% miss_values_vector))] <- SHARE_w4$ph009_2[which(SHARE_ds_w4$h_hypertension==1 & (is.na(SHARE_w4$h_hypertension_age) | SHARE_w4$h_hypertension_age %in% miss_values_vector))]
# if h_hypertension == 1 in w4 and non-missing age previously, h_hypertension_age = as before
SHARE_ds_w4$h_hypertension_age[which(SHARE_ds_w4$h_hypertension==1 & !(is.na(SHARE_w4$h_hypertension_age) | SHARE_w4$h_hypertension_age %in% miss_values_vector))] <- SHARE_w4$h_hypertension_age[which(SHARE_ds_w4$h_hypertension==1 & !(is.na(SHARE_w4$h_hypertension_age) | SHARE_w4$h_hypertension_age %in% miss_values_vector))]
SHARE_ds_w4$h_hypertension_age <- car::recode(SHARE_ds_w4$h_hypertension_age, "-1=998;-2=997;NA=999")
# Two corrections. The age of diagnostic values 105 and 1995 are missing (in the first case can be checked that the age of the individual is less than 105).
SHARE_ds_w4$h_hypertension_age[which(SHARE_w4$ph009_2 %in% c(105,1995))] <- 991



# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
SHARE_ds_prov <- SHARE_ds[,c(1,2)]
SHARE_ds_prov <- assign_merge(SHARE_ds_prov,SHARE_ds_w4,log_vec=SHARE_ds_w4$id,col_end_index = 2, col_st_index = 3)
SHARE_ds_aux <- SHARE_ds[,c(1,3)]
SHARE_ds_aux <- assign_merge(SHARE_ds_aux,SHARE_ds_w4,log_vec=SHARE_ds_w4$id[which(SHARE_ds_w4$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
SHARE_ds <- SHARE_ds_prov
SHARE_ds$h_hypertension_age <- SHARE_ds_aux$h_hypertension_age
rm(SHARE_ds_prov)
rm(SHARE_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- SHARE_ds_w4$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SHARE_ds_w4$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w4$h_hypertension)
X <- c(
  sum(((!is.na(SHARE_w4$ph006d2)) & SHARE_w4$ph006d2 == 0) & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)),na.rm = T),
  sum(((!is.na(SHARE_w4$ph006d2)) & SHARE_w4$ph006d2 == 1) | ((!is.na(SHARE_w4$h_hypertension)) & (!is.na(SHARE_w4$ph006d2)) & SHARE_w4$h_hypertension == 1)),
  sum(((!is.na(SHARE_w4$ph006d2)) & SHARE_w4$ph006d2 == -2) & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)),na.rm=T),
  sum(((!is.na(SHARE_w4$ph006d2)) & SHARE_w4$ph006d2 == -1) & (SHARE_w4$h_hypertension != 1 | is.na(SHARE_w4$h_hypertension)),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w4$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

# Checking
cat("There are 1937 individuals whose answer in previous waves is that they were told to have high blood pressure or hypertension and in the fourth wave is that they do not have it. We compute them in the harmonized variable as having hypertension")
kable(frq(SHARE_w4$ph006d2[which(SHARE_w4$h_hypertension==1)]), align = 'c')

kable(SHARE_w4[which(!is.na(SHARE_w4$h_hypertension_age) & !is.na(SHARE_w4$ph009_2) & !SHARE_w4$h_hypertension_age %in% miss_values_vector & !SHARE_w4$ph009_2 %in% c(-1,-2) & SHARE_w4$h_hypertension_age!=SHARE_w4$ph009_2),], align = 'c',caption = paste0('There are ',length(SHARE_w4$id[which(!is.na(SHARE_w4$h_hypertension_age) & !is.na(SHARE_w4$ph009_2) & !SHARE_w4$h_hypertension_age %in% miss_values_vector & !SHARE_w4$ph009_2 %in% c(-1,-2) & SHARE_w4$h_hypertension_age!=SHARE_w4$ph009_2)]),' individuals which answer different diagnostic ages across waves. We harmonize the first age answered.'))

```




### Wave 5


#### Study-specific variable description

| **Name** | `ph006d2` |`ph009_2`|
|-|-|-|
| **Label** | `Doctor told you had: high blood pressure or hypertension` |`Age high blood pressure`|
| **Table name**  | `sharew5_rel1-0-0_ph` | `sharew5_rel1-0-0_ph` |
| **Categories** | `1 = Selected`<br/>`0 = Not selected` | `Continuous` |
| **Missings** | `-1 = Don't know`<br/>`-2 = Refusal`<br/>`NA` |`-1 = Don't know`<br/>`-2 = Refusal`<br/>`NA` |
| **Description** |  |  |

```{r assign w5, echo=F}

opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_ph',variables=list('ph006d2','ph009_2'), missings = T)
SHARE_w5 <- opal.execute(o,'SHARE_w5')

```

```{r local w5, echo=F}

vbl <- SHARE_w5$ph006d2
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(ph006d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w5$ph009_2
kable(Continuous_summary(var = vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[3])
pander(Continuous_summary(vbl, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w5, aes(ph009_2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `ph006d2 (w1) == 0 and ph006d2 (w2) == 0 and ph006d2 (w4) == 0 and ph006d2 (w5) == 0 into 0`
* `ph006d2 (w1) == 1 or ph006d2 (w2) == 1 or ph006d2 (w4) == 1 or ph006d2 (w5) == 1 into 1`
* `-2 into 997`
* `-1 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w5 and missing age previously, h_hypertension_age = ph009_2`
* `if h_hypertension == 1 in w5 and non-missing age previously, h_hypertension_age = as before`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-2 into 997`
* `-1 into 998`
* `otherwise 999`

**R script:**

```{r harmo w5}

# We use the harmonized variable of previous waves instead of the study-specific variables
SHARE_w5 <- left_join(SHARE_w5, SHARE_ds, by = "id")

# Categorical variable harmonization
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$h_hypertension <- rep(999,length(SHARE_ds_w5$id))
SHARE_ds_w5$h_hypertension[which(SHARE_w5$ph006d2 == 0 & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)))] <- 0
SHARE_ds_w5$h_hypertension[which(SHARE_w5$ph006d2 == 1 | ((!is.na(SHARE_w5$ph006d2)) & SHARE_w5$h_hypertension == 1))] <- 1
SHARE_ds_w5$h_hypertension[which(SHARE_w5$ph006d2 == -1 & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)))] <- 998
SHARE_ds_w5$h_hypertension[which(SHARE_w5$ph006d2 == -2 & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)))] <- 997

# Continuous variable harmonization
SHARE_ds_w5$h_hypertension_age <- rep(999,length(SHARE_ds_w5$id))
SHARE_ds_w5$h_hypertension_age[which(SHARE_ds_w5$h_hypertension==0)] <- 996
# if h_hypertension == 1 in w5 and missing age previously, h_hypertension_age = ph009_2
SHARE_ds_w5$h_hypertension_age[which(SHARE_ds_w5$h_hypertension==1 & (is.na(SHARE_w5$h_hypertension_age) | SHARE_w5$h_hypertension_age %in% miss_values_vector))] <- SHARE_w5$ph009_2[which(SHARE_ds_w5$h_hypertension==1 & (is.na(SHARE_w5$h_hypertension_age) | SHARE_w5$h_hypertension_age %in% miss_values_vector))]
# if h_hypertension == 1 in w5 and non-missing age previously, h_hypertension_age = as before
SHARE_ds_w5$h_hypertension_age[which(SHARE_ds_w5$h_hypertension==1 & !(is.na(SHARE_w5$h_hypertension_age) | SHARE_w5$h_hypertension_age %in% miss_values_vector))] <- SHARE_w5$h_hypertension_age[which(SHARE_ds_w5$h_hypertension==1 & !(is.na(SHARE_w5$h_hypertension_age) | SHARE_w5$h_hypertension_age %in% miss_values_vector))]
SHARE_ds_w5$h_hypertension_age <- car::recode(SHARE_ds_w5$h_hypertension_age, "-1=998;-2=997;NA=999")

# We update the hypertension status of the individuals in the global table
rm(SHARE_ds)

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- SHARE_ds_w5$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SHARE_ds_w5$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w5, echo=F, results='asis'}

AfterH <- table(SHARE_ds_w5$h_hypertension)
X <- c(
  sum(((!is.na(SHARE_w5$ph006d2)) & SHARE_w5$ph006d2 == 0) & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)),na.rm = T),
  sum(((!is.na(SHARE_w5$ph006d2)) & SHARE_w5$ph006d2 == 1) | ((!is.na(SHARE_w5$h_hypertension)) & (!is.na(SHARE_w5$ph006d2)) & SHARE_w5$h_hypertension == 1)),
  sum(((!is.na(SHARE_w5$ph006d2)) & SHARE_w5$ph006d2 == -2) & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)),na.rm=T),
  sum(((!is.na(SHARE_w5$ph006d2)) & SHARE_w5$ph006d2 == -1) & (SHARE_w5$h_hypertension != 1 | is.na(SHARE_w5$h_hypertension)),na.rm=T)
)
BeforeH <- c(X[1:4],length(SHARE_w5$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","-2->997","-1->998","NA->999")
kable(C)

# Checking
cat("There are 4042 individuals whose answer in previous waves is that they were diagnosed to have high blood pressure or hypertension and in the fourth wave is that they do not have it. We compute them in the harmonized variable as having hypertension")
kable(frq(SHARE_w5$ph006d2[which(SHARE_w5$h_hypertension==1)]), align = 'c')

kable(SHARE_w5[which(!is.na(SHARE_w5$h_hypertension_age) & !is.na(SHARE_w5$ph009_2) & !SHARE_w5$h_hypertension_age %in% miss_values_vector & !SHARE_w5$ph009_2 %in% c(-1,-2) & SHARE_w5$h_hypertension_age!=SHARE_w5$ph009_2),], align = 'c',caption = paste0('There are ',length(SHARE_w5$id[which(!is.na(SHARE_w5$h_hypertension_age) & !is.na(SHARE_w5$ph009_2) & !SHARE_w5$h_hypertension_age %in% miss_values_vector & !SHARE_w5$ph009_2 %in% c(-1,-2) & SHARE_w5$h_hypertension_age!=SHARE_w5$ph009_2)]),' individuals which answer different diagnostic ages across waves. We harmonize the first age answered.'))

```









<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

sharelist <- lmlist # SHARE list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_hypertension` accross populations and waves


Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(hd_vbl %in% names(get0(paste0("SHARE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sharelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sharelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_hypertension_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("SHARE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sharelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sharelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```






# Quality estimation

We assume that if an individual answers it has hypertension in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.

There are individuals whose diagnostic age appear to be zero. Since we have no more information about that, we keep their data.

```{r echo=F}



l.hds <- list(w1 = SHARE_w1, w2 = SHARE_w2, w4 = SHARE_w4, w5 = SHARE_w5)

pdbb <- merge(SHARE_w1[,c("id","ph009_2")], SHARE_w2[,c("id","ph009_2")], by="id", suffixes = c(".w1",".w2"), all=T)
pdbb <- merge(pdbb,SHARE_w4[,c("id","ph009_2")], by="id", all=T)
pdbb <- merge(pdbb, SHARE_w5[,c("id","ph009_2")], by="id", suffixes = c(".w4",".w5"), all=T)
names(pdbb) <- c("id", "w1", "w2","w4","w5")

pdbb$val0 <- sapply(pdbb$id,function(ind) TRUE %in% (pdbb[pdbb$id==ind,2:5]==0))


qdbb <- pdbb[pdbb$val0==TRUE,]

kable(qdbb, align = 'c', caption = 'Individuals whose diagnostic age is 0 in some wave')


dbb <- merge(SHARE_ds_w1[,c("id","h_hypertension")], SHARE_ds_w2[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,SHARE_ds_w4[,c("id","h_hypertension")], by="id", all=T)
dbb <- merge(dbb, SHARE_ds_w5[,c("id","h_hypertension")], by="id", suffixes = c(".w4",".w5"), all=T)
dbb <- merge(dbb,SHARE_ds_w1[,c("id","h_hypertension_age")], by="id", all=T)
dbb <- merge(dbb,SHARE_ds_w2[,c("id","h_hypertension_age")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,SHARE_ds_w4[,c("id","h_hypertension_age")], by="id", all=T)
dbb <- merge(dbb,SHARE_ds_w5[,c("id","h_hypertension_age")], by="id", suffixes = c(".w4",".w5"), all=T)
names(dbb) <- c("id", "w1", "w2","w4","w5", "w1 age", "w2 age","w4 age","w5 age")


kable(dbb[dbb$id %in% qdbb$id,], align='c', caption = 'Final harmonisation data of those individuals')

```




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





