---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```


# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `mintw`
* Variable label: `month of interview`
* Variable description: `month of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


### HAPIEE - Poland - Baseline 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `hqdate`
* Label: `Date of Completion of Health questionnaire`
* Type of variable: `countinous`

```{r assign_po1}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_dinter','HAPIEE.Po_baseline_etic',
                         variables=list('hqdate'), missings = TRUE)
```

```{r local_po1}
HAPIEE_pol_w1_dinter <- opal.execute(o,'HAPIEE_pol_w1_dinter')
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_pol_w1_dinter <- cbind(HAPIEE_pol_w1_dinter,Date_of_birth(HAPIEE_pol_w1_dinter$hqdate))
Categorical_summary(var = HAPIEE_pol_w1_dinter$Month, missing_values = NA)
ggplot(HAPIEE_pol_w1_dinter, aes(x=factor(Month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To computed the harmonize variable form the study-specific variable, it has to be recoded as follows:

* `recode 'jan' into 1`
* `recode 'feb' into 2`
* `recode 'mar' into 3`
* `recode 'apr' into 4`
* `recode 'jun' into 5`
* `recode 'may' into 6`
* `recode 'jul' into 7`
* `recode 'aug' into 8`
* `recode 'sep' into 9`
* `recode 'oct' into 10`
* `recode 'nov' into 11`
* `recode 'dec' into 12`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo_po1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_dinter$id)
HAPIEE_pol_ds_w1$mintw <- car::recode(HAPIEE_pol_w1_dinter$Month, "'jan'=1; 'feb'=2; 'mar'=3; 'apr'=4; 'may'=5; 'jun'=6; 'jul'=7; 'aug'=8; 'sep'=9; 'oct'=10; 'nov'=11; 'dec'=12; NA=999")
HAPIEE_pol_ds_w1$mintw <- as.numeric(as.character(HAPIEE_pol_ds_w1$mintw))
HAPIEE_pol_ds_w1$mintw <- labelled(HAPIEE_pol_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1}
Categorical_summary(var = HAPIEE_pol_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1}
BeforeH <- table(HAPIEE_pol_w1_dinter$Month, useNA = "ifany")
BeforeH <- BeforeH[c(4,3,5,1,6,7,2)]
AfterH <- table(HAPIEE_pol_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("jan->1", 'feb->2', 'mar->3', 'apr->4', 'may->5', 'nov->11', 'dec->12')
C
```


#### Import to OPAL
```{r importOPAL_po1}
val_labels(HAPIEE_pol_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
mintw <- HAPIEE_pol_ds_w1
save(mintw, file = "../RData/pol_w1/mintw.RData")
rm(mintw)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$mintw <- car::recode(HAPIEE_pol_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### HAPIEE - Poland - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_po2}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_dinter','HAPIEE.Po_reexamination_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_po2}
HAPIEE_pol_w2_dinter <- opal.execute(o,'HAPIEE_pol_w2_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    if(is.na(date[i])){
      D[i,] <- rep(NA,2)
    }
    else{
      D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5),last=c(4, 7))))
    } 
  }
 colnames(D) <- c("Year", "Month")    
 D
}

HAPIEE_pol_w2_minter <- cbind(HAPIEE_pol_w2_dinter, Date_of_birth(HAPIEE_pol_w2_dinter$w2date))
Categorical_summary(var = HAPIEE_pol_w2_minter$Month, missing_values = NA)
ggplot(HAPIEE_pol_w2_minter, aes(x=factor(Month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To computed the harmonize variable form the study-specific variable, it has to be recoded as follows:

* `recode 'jan' into 1`
* `recode 'feb' into 2`
* `recode 'mar' into 3`
* `recode 'apr' into 4`
* `recode 'jun' into 5`
* `recode 'may' into 6`
* `recode 'jul' into 7`
* `recode 'aug' into 8`
* `recode 'sep' into 9`
* `recode 'oct' into 10`
* `recode 'nov' into 11`
* `recode 'dec' into 12`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo_po2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_minter$id)
HAPIEE_pol_ds_w2$mintw <- car::recode(HAPIEE_pol_w2_minter$Month, "'jan'=1; 'feb'=2; 'mar'=3; 'apr'=4; 'may'=5; 'jun'=6; 'jul'=7; 'aug'=8; 'sep'=9; 'oct'=10; 'nov'=11; 'dec'=12; NA=999")
HAPIEE_pol_ds_w2$mintw <- as.numeric(as.character(HAPIEE_pol_ds_w2$mintw))
HAPIEE_pol_ds_w2$mintw <- labelled(HAPIEE_pol_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po2}
Categorical_summary(var = HAPIEE_pol_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po2}
BeforeH <- table(HAPIEE_pol_w2_minter$Month, useNA = "ifany")
BeforeH <- BeforeH[c(5, 4, 8, 1, 9, 7, 6, 2, 12, 11, 10, 3, 13)]
AfterH <- table(HAPIEE_pol_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("jan->1", 'feb->2', 'mar->3', 'apr->4', 'may->5', 'jun->6', 'jul->7', 'aug->8', 'sep->9', 'oct->10', 'nov->11', 'dec->12', 'NA->999')
C
```

#### Import to OPAL
```{r importOPAL_po2}
val_labels(HAPIEE_pol_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
mintw <- HAPIEE_pol_ds_w2
save(mintw, file = "../RData/pol_w2/mintw.RData")
rm(mintw)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$mintw <- car::recode(HAPIEE_pol_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### HAPIEE - Czech Republic - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `hqdate`
* Label: `Date of Completion of Health questionnaire`
* Type of variable: `countinous`

```{r assign_cz1}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_dinter','HAPIEE.Cz_baseline_etic',
                         variables=list('hqdate'), missings = TRUE)
```

```{r local_cz1}
HAPIEE_cz_w1_dinter <- opal.execute(o,'HAPIEE_cz_w1_dinter')
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_dinter <- cbind(HAPIEE_cz_w1_dinter,Date_of_birth(HAPIEE_cz_w1_dinter$hqdate))
Continuous_summary(var = HAPIEE_cz_w1_dinter$Month, missing_values = NA)
ggplot(HAPIEE_cz_w1_dinter, aes(Month)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
To computed the harmonize variable form the study-specific variable, it has to be recoded as follows:

* `recode 'jan' into 1`
* `recode 'feb' into 2`
* `recode 'mar' into 3`
* `recode 'apr' into 4`
* `recode 'jun' into 5`
* `recode 'may' into 6`
* `recode 'jul' into 7`
* `recode 'aug' into 8`
* `recode 'sep' into 9`
* `recode 'oct' into 10`
* `recode 'nov' into 11`
* `recode 'dec' into 12`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cz1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_dinter$id)
HAPIEE_cz_ds_w1$mintw <- car::recode(HAPIEE_cz_w1_dinter$Month, "'jan'=1; 'feb'=2; 'mar'=3; 'apr'=4; 'may'=5; 'jun'=6; 'jul'=7; 'aug'=8; 'sep'=9; 'oct'=10; 'nov'=11; 'dec'=12; NA=999")
HAPIEE_cz_ds_w1$mintw <- as.numeric(as.character(HAPIEE_cz_ds_w1$mintw))
HAPIEE_cz_ds_w1$mintw <- labelled(HAPIEE_cz_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1}
Categorical_summary(var = HAPIEE_cz_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1}
BeforeH <- table(HAPIEE_cz_w1_dinter$Month, useNA = "ifany")
BeforeH <- BeforeH[c(4,3, 6, 1, 7, 5, 10, 9, 8, 2)]
AfterH <- table(HAPIEE_cz_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("jan->1", 'feb->2', 'mar->3', 'apr->4', 'may->5', 'jun->6', 'sep->9', 'oct->10', 'nov->11', 'dec->12')
C
```


#### Import to OPAL
```{r importOPAL_cz1}
val_labels(HAPIEE_cz_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
mintw <- HAPIEE_cz_ds_w1
save(mintw, file = "../RData/cz_w1/mintw.RData")
rm(mintw)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$mintw <- car::recode(HAPIEE_cz_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```









### HAPIEE - Czech Republic - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_cz2}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_dinter','HAPIEE.Cz_reexamination_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_cz2}
HAPIEE_cz_w1_dinter <- opal.execute(o,'HAPIEE_cz_w1_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_dinter <- cbind(HAPIEE_cz_w1_dinter, Date_of_birth(HAPIEE_cz_w1_dinter$w2date))
Categorical_summary(var = HAPIEE_cz_w1_dinter$Month, missing_values = NA)
ggplot(HAPIEE_cz_w1_dinter, aes(x=factor(Month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To computed the harmonize variable form the study-specific variable, it has to be recoded as follows:

* `recode 'jan' into 1`
* `recode 'feb' into 2`
* `recode 'mar' into 3`
* `recode 'apr' into 4`
* `recode 'jun' into 5`
* `recode 'may' into 6`
* `recode 'jul' into 7`
* `recode 'aug' into 8`
* `recode 'sep' into 9`
* `recode 'oct' into 10`
* `recode 'nov' into 11`
* `recode 'dec' into 12`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cz2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w1_dinter$id)
HAPIEE_cz_ds_w2$mintw <- car::recode(HAPIEE_cz_w1_dinter$Month, "'jan'=1; 'feb'=2; 'mar'=3; 'apr'=4; 'may'=5; 'jun'=6; 'jul'=7; 'aug'=8; 'sep'=9; 'oct'=10; 'nov'=11; 'dec'=12; NA=999")
HAPIEE_cz_ds_w2$mintw <- as.numeric(as.character(HAPIEE_cz_ds_w2$mintw))
HAPIEE_cz_ds_w2$mintw <- labelled(HAPIEE_cz_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz2}
Categorical_summary(var = HAPIEE_cz_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz2}
BeforeH <- table(HAPIEE_cz_w1_dinter$Month, useNA = "ifany")
BeforeH <- BeforeH[c(5, 4, 8, 1, 9, 7, 6, 2, 12, 11, 10, 3, 13)]
AfterH <- table(HAPIEE_cz_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("jan->1", 'feb->2', 'mar->3', 'apr->4', 'may->5', 'jun->6', 'jul->7', 'aug->8', 'sep->9', 'oct->10', 'nov->11', 'dec->12', 'NA->999')
C
```

#### Import to OPAL
```{r importOPAL_cz2}
val_labels(HAPIEE_cz_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
mintw <- HAPIEE_cz_ds_w2
save(mintw, file = "../RData/cz_w2/mintw.RData")
rm(mintw)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$mintw <- car::recode(HAPIEE_cz_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```









### HAPIEE - Lithuania - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_li1}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_dinter','HAPIEE.Li_baseline_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_li1}
HAPIEE_li_w1_dinter <- opal.execute(o,'HAPIEE_li_w1_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_li_w1_dinter <- cbind(HAPIEE_li_w1_dinter, Date_of_birth(HAPIEE_li_w1_dinter$w2date))
Categorical_summary(var = HAPIEE_li_w1_dinter$Month, missing_values = NA)
ggplot(HAPIEE_li_w1_dinter, aes(x=factor(Month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To computed the harmonize variable form the study-specific variable, it has to be recoded as follows:

* `recode 'jan' into 1`
* `recode 'feb' into 2`
* `recode 'mar' into 3`
* `recode 'apr' into 4`
* `recode 'jun' into 5`
* `recode 'may' into 6`
* `recode 'jul' into 7`
* `recode 'aug' into 8`
* `recode 'sep' into 9`
* `recode 'oct' into 10`
* `recode 'nov' into 11`
* `recode 'dec' into 12`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_dinter$id)
HAPIEE_li_ds_w1$mintw <- car::recode(HAPIEE_li_w1_dinter$Month, "'jan'=1; 'feb'=2; 'mar'=3; 'apr'=4; 'may'=5; 'jun'=6; 'jul'=7; 'aug'=8; 'sep'=9; 'oct'=10; 'nov'=11; 'dec'=12; NA=999")
HAPIEE_li_ds_w1$mintw <- as.numeric(as.character(HAPIEE_li_ds_w1$mintw))
HAPIEE_li_ds_w1$mintw <- labelled(HAPIEE_li_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1}
Categorical_summary(var = HAPIEE_li_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1}
BeforeH <- table(HAPIEE_li_w1_dinter$Month, useNA = "ifany")
BeforeH <- BeforeH[c(4,3,6,1,7,5,10,9,8,2,11)]
AfterH <- table(HAPIEE_li_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("jan->1", 'feb->2', 'mar->3', 'apr->4', 'may->5', 'jun->6', 'sep->9', 'oct->10', 'nov->11', 'dec->12', 'NA->999')
C
```

#### Quality estimation
No comments.




#### Import to OPAL
```{r importOPAL_li1}
val_labels(HAPIEE_li_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
mintw <- HAPIEE_li_ds_w1
save(mintw, file = "../RData/li_w1/mintw.RData")
rm(mintw)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$mintw <- car::recode(HAPIEE_li_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```






```{r closeRsession, echo=FALSE}
opal.logout(o)
```
