---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `yintw`
* Variable label: `year of interview`
* Variable description: `year of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


### HAPIEE - Poland - Baseline 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `hqdate`
* Label: `Date of Completion of Health questionnaire`
* Type of variable: `countinous`

```{r assign_po1}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_dinter','HAPIEE.Po_baseline_etic',
                         variables=list('hqdate'), missings = TRUE)
```

```{r local_po1}
HAPIEE_pol_w1_dinter <- opal.execute(o,'HAPIEE_pol_w1_dinter')
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_pol_w1_dinter <- cbind(HAPIEE_pol_w1_dinter,Date_of_birth(HAPIEE_pol_w1_dinter$hqdate))
Categorical_summary(var = HAPIEE_pol_w1_dinter$Year, missing_values = NA)
ggplot(HAPIEE_pol_w1_dinter, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as 2007 since is the most frequent value. 

R code of the ALGORITHM:

```{r harmo_po1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_dinter$id)
HAPIEE_pol_ds_w1$yintw <- car::recode(HAPIEE_pol_w1_dinter$Year, "NA=2007")
HAPIEE_pol_ds_w1$yintw <- labelled(HAPIEE_pol_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1}
Categorical_summary(var = HAPIEE_pol_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1}
BeforeH <- table(HAPIEE_pol_w1_dinter$Year, useNA = "ifany")
AfterH <- table(HAPIEE_pol_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


#### Import to OPAL
```{r importOPAL_po1}
val_labels(HAPIEE_pol_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
yintw <- HAPIEE_pol_ds_w1
save(yintw, file = "../RData/pol_w1/yintw.RData")
rm(yintw)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$yintw <- car::recode(HAPIEE_pol_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### HAPIEE - Poland - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_po2}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_dinter','HAPIEE.Po_reexamination_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_po2}
HAPIEE_pol_w2_dinter <- opal.execute(o,'HAPIEE_pol_w2_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    if(is.na(date[i])){
      D[i,] <- rep(NA,2)
    }
    else{
      D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5),last=c(4, 7))))
    } 
  }
 colnames(D) <- c("Year", "Month")    
 D
}

HAPIEE_pol_w2_yinter <- cbind(HAPIEE_pol_w2_dinter, Date_of_birth(HAPIEE_pol_w2_dinter$w2date))
Categorical_summary(var = HAPIEE_pol_w2_yinter$Year, missing_values = NA)
ggplot(HAPIEE_pol_w2_yinter, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missing values have to be recoded as follows:

`NA into 999`


R code of the ALGORITHM:

```{r harmo_po2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_yinter$id)
HAPIEE_pol_ds_w2$yintw <- car::recode(as.numeric(as.character(HAPIEE_pol_w2_yinter$Year)), "NA=999")
HAPIEE_pol_ds_w2$yintw <- labelled(HAPIEE_pol_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po2}
Categorical_summary(var = HAPIEE_pol_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po2}
BeforeH <- table(HAPIEE_pol_w2_yinter$Year, useNA = "ifany")
AfterH <- table(HAPIEE_pol_ds_w2$yintw)[c(2:4,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2006", "2007", "2008", "NA->999")
kable(C)
```


#### Import to OPAL
```{r importOPAL_po2}
val_labels(HAPIEE_pol_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
yintw <- HAPIEE_pol_ds_w2
save(yintw, file = "../RData/pol_w2/yintw.RData")
rm(yintw)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$yintw <- car::recode(HAPIEE_pol_m_ds_w2$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### HAPIEE - Czech Republic - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `hqdate`
* Label: `Date of Completion of Health questionnaire`
* Type of variable: `countinous`

```{r assign_cz1}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_dinter','HAPIEE.Cz_baseline_etic',
                         variables=list('hqdate'), missings = TRUE)
```

```{r local_cz1}
HAPIEE_cz_w1_dinter <- opal.execute(o,'HAPIEE_cz_w1_dinter')
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_dinter <- cbind(HAPIEE_cz_w1_dinter,Date_of_birth(HAPIEE_cz_w1_dinter$hqdate))
Categorical_summary(var = HAPIEE_cz_w1_dinter$Year, missing_values = NA)
ggplot(HAPIEE_cz_w1_dinter, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable.

R code of the ALGORITHM:

```{r harmo_cz1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_dinter$id)
HAPIEE_cz_ds_w1$yintw <- HAPIEE_cz_w1_dinter$Year
HAPIEE_cz_ds_w1$yintw <- labelled(HAPIEE_cz_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1}
Categorical_summary(var = HAPIEE_cz_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1}
BeforeH <- table(HAPIEE_cz_w1_dinter$Year, useNA = "ifany")
AfterH <- table(HAPIEE_cz_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


#### Import to OPAL
```{r importOPAL_cz1}
val_labels(HAPIEE_cz_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
yintw <- HAPIEE_cz_ds_w1
save(yintw, file = "../RData/cz_w1/yintw.RData")
rm(yintw)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$yintw <- car::recode(HAPIEE_cz_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```









### HAPIEE - Czech Republic - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_cz2}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_dinter','HAPIEE.Cz_reexamination_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_cz2}
HAPIEE_cz_w1_dinter <- opal.execute(o,'HAPIEE_cz_w1_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_dinter <- cbind(HAPIEE_cz_w1_dinter, Date_of_birth(HAPIEE_cz_w1_dinter$w2date))
Categorical_summary(var = HAPIEE_cz_w1_dinter$Year, missing_values = NA)
ggplot(HAPIEE_cz_w1_dinter, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows 

`NA into 999`

R code of the ALGORITHM:

```{r harmo_cz2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w1_dinter$id)
HAPIEE_cz_ds_w2$yintw <- car::recode(HAPIEE_cz_w1_dinter$Year, "NA=999")
HAPIEE_cz_ds_w2$yintw <- labelled(HAPIEE_cz_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz2}
Categorical_summary(var = HAPIEE_cz_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz2}
BeforeH <- table(HAPIEE_cz_w1_dinter$Year, useNA = "ifany")
AfterH <- table(HAPIEE_cz_ds_w2$yintw)[c(2:4,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2006", "2007", "2008", "NA->999")
kable(C)
```

#### Import to OPAL
```{r importOPAL_cz2}
val_labels(HAPIEE_cz_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
yintw <- HAPIEE_cz_ds_w2
save(yintw, file = "../RData/cz_w2/yintw.RData")
rm(yintw)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$yintw <- car::recode(HAPIEE_cz_m_ds_w2$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```









### HAPIEE - Lithuania - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2date`
* Label: `Date of interview-in date format`
* Type of variable: `countinous`

```{r assign_li1}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_dinter','HAPIEE.Li_baseline_etic',
                         variables=list('w2date'), missings = TRUE)
```

```{r local_li1}
HAPIEE_li_w1_dinter <- opal.execute(o,'HAPIEE_li_w1_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_li_w1_dinter <- cbind(HAPIEE_li_w1_dinter, Date_of_birth(HAPIEE_li_w1_dinter$w2date))
Categorical_summary(var = HAPIEE_li_w1_dinter$Year, missing_values = NA)
ggplot(HAPIEE_li_w1_dinter, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as 2007 since is the most frecuent value. 


R code of the ALGORITHM:

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_dinter$id)
HAPIEE_li_ds_w1$yintw <- car::recode(HAPIEE_li_w1_dinter$Year, "NA=2007")
HAPIEE_li_ds_w1$yintw <- labelled(HAPIEE_li_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1}
Categorical_summary(var = HAPIEE_li_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1}
BeforeH <- table(HAPIEE_li_w1_dinter$Year, useNA = "ifany")
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2,4)]), BeforeH[3])
AfterH <- table(HAPIEE_li_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2006", "(NA,2007)->2007", "2008")
kable(C)
```

#### Quality estimation
The date was the same as the study specific variable taking into account the wave time lapse information, the missing values have been recoded as the most frequent year between the no missing values. 


#### Import to OPAL
```{r importOPAL_li1}
val_labels(HAPIEE_li_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
yintw <- HAPIEE_li_ds_w1
save(yintw, file = "../RData/li_w1/yintw.RData")
rm(yintw)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$yintw <- car::recode(HAPIEE_li_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```






```{r closeRsession, echo=FALSE}
opal.logout(o)
```
