---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```



<!-- ########################################################## --> 

# Data process

## Poland 

### Wave 1

#### Study-specific variable description

```{r assign_po1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_po1, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_pol_ds_w1$respondent <- 0
HAPIEE_pol_ds_w1$respondent <- labelled(HAPIEE_pol_ds_w1$respondent, labels = cat_label)
label(HAPIEE_pol_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_po1, echo=FALSE}
vari <- HAPIEE_pol_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_po1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- HAPIEE_pol_ds_w1
save(respondent, file = "../RData/pol_w1/respondent.RData")
rm(respondent)
```



### Wave 2

#### Study-specific variable description

```{r assign_po2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic',
                         variables=list('adult'), missings = TRUE)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_po2, echo=TRUE}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2$id)
HAPIEE_pol_ds_w2$respondent <- 0
HAPIEE_pol_ds_w2$respondent <- labelled(HAPIEE_pol_ds_w2$respondent, labels = cat_label)
label(HAPIEE_pol_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_po2, echo=FALSE}
vari <- HAPIEE_pol_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_po2, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
respondent <- HAPIEE_pol_ds_w2
save(respondent, file = "../RData/pol_w2/respondent.RData")
rm(respondent)
```






## Czech Republic 

### Wave 1

#### Study-specific variable description

 
```{r assign_cz1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_cz1, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_cz_ds_w1$respondent <- 0
HAPIEE_cz_ds_w1$respondent <- labelled(HAPIEE_cz_ds_w1$respondent, labels = cat_label)
label(HAPIEE_cz_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_cz1, echo=FALSE}
vari <- HAPIEE_cz_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_cz1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- HAPIEE_cz_ds_w1
save(respondent, file = "../RData/cz_w1/respondent.RData")
rm(respondent)
```







### Wave 2

#### Study-specific variable description

 
```{r assign_cz2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic',
                         variables=list('adult'), missings = TRUE)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_cz2, echo=TRUE}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2$id)
HAPIEE_cz_ds_w2$respondent <- 0
HAPIEE_cz_ds_w2$respondent <- labelled(HAPIEE_cz_ds_w2$respondent, labels = cat_label)
label(HAPIEE_cz_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_cz2, echo=FALSE}
vari <- HAPIEE_cz_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_cz2, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
respondent <- HAPIEE_cz_ds_w2
save(respondent, file = "../RData/cz_w2/respondent.RData")
rm(respondent)
```







## Lithuania 

### Wave 1

#### Study-specific variable description

```{r assign_li1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_li1, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_li_ds_w1$respondent <- 0
HAPIEE_li_ds_w1$respondent <- labelled(HAPIEE_li_ds_w1$respondent, labels = cat_label)
label(HAPIEE_li_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_li1, echo=FALSE}
vari <- HAPIEE_li_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



```{r importOPAL_li1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- HAPIEE_li_ds_w1
save(respondent, file = "../RData/li_w1/respondent.RData")
rm(respondent)
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
