---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `relig`
* Variable label: `Any form of religious participation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6618_relig`
* Label: `Attend religious services`
* Categories: 
    + `1 = Never`
    + `2 = Once/twice per year`
    + `3 = Once/twice per month`
    + `4 = Once/twice per week`
    + `5 = Daily`
* Missings:
    + `8 = DK`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_relig','Courage.Courage_Finland_w1',variables=list('q6618_relig'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_relig <- opal.execute(o,'COURAGE_fin_w1_relig')
vari <- COURAGE_fin_w1_relig$q6618_relig
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_fin_w1_relig$q6618_relig, missing_values = NA)
ggplot(COURAGE_fin_w1_relig, aes(x=factor(q6618_relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Attend religious services - frequency") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3, 4 or 5 then 1`
* `1 or 2 then 0`
* `8 into 998`
* `9,NA into 999`

 
**R script:**
```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_relig$id)
COURAGE_ds_fin_w1$relig <- car::recode(as.vector(COURAGE_fin_w1_relig$q6618_relig), "1:2='0'; 3:5='1'; 8='998'; 9='999'; NA='999'")
COURAGE_ds_fin_w1$relig <- labelled(COURAGE_ds_fin_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH <- table(COURAGE_ds_fin_w1$relig)
BeforeH <- table(COURAGE_fin_w1_relig$q6618_relig, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
BeforeH1[[4]] <- sum(BeforeH[c(7:8)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","8->998","NA->999")
kable(C)
```

 
 


## Polish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6618_relig`
* Label: `Attend religious services`
* Categories: 
    + `1 = Never`
    + `2 = Once/twice per year`
    + `3 = Once/twice per month`
    + `4 = Once/twice per week`
    + `5 = Daily`
* Missings:
    + `8 = DK`

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_relig','Courage.Courage_Poland_w1',variables=list('q6618_relig'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_relig <- opal.execute(o,'COURAGE_pol_w1_relig')
vari <- COURAGE_pol_w1_relig$q6618_relig
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w1_relig$q6618_relig, missing_values = NA)
ggplot(COURAGE_pol_w1_relig, aes(x=factor(q6618_relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Attend religious services - frequency") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3, 4 or 5 then 1`
* `1 or 2 then 0`
* `8 into 998`
* `NA into 999`

 
**R script:**
```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_relig$id)
COURAGE_ds_pol_w1$relig <- car::recode(as.vector(COURAGE_pol_w1_relig$q6618_relig), "1:2='0'; 3:5='1'; 8='998'; NA='999'")
COURAGE_ds_pol_w1$relig <- labelled(COURAGE_ds_pol_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}
AfterH <- table(COURAGE_ds_pol_w1$relig)
BeforeH <- table(COURAGE_pol_w1_relig$q6618_relig, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6618_relig_s1`
* Label: `Attend religious services`
* Categories: 
    + `1 = Never`
    + `2 = Once/twice per year`
    + `3 = Once/twice per month`
    + `4 = Once/twice per week`
    + `5 = Daily`
* Missings:
    + `8 = DK`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_relig','Courage.Courage_Poland_w2', variables=list('q6618_relig_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_relig <- opal.execute(o,'COURAGE_pol_w2_relig')
vari <- COURAGE_pol_w2_relig$q6618_relig_s1
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w2_relig$q6618_relig_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_relig, aes(x=factor(q6618_relig_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Attend religious services - frequency") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3, 4 or 5 then 1`
* `1 or 2 then 0`
* `8 into 998`
* `NA into 999`

 
**R script:**
```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_relig$id)
COURAGE_ds_pol_w2$relig <- car::recode(as.vector(COURAGE_pol_w2_relig$q6618_relig_s1), "1:2='0'; 3:5='1'; 8='998'; NA='999'")
COURAGE_ds_pol_w2$relig <- labelled(COURAGE_ds_pol_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}
AfterH <- table(COURAGE_ds_pol_w2$relig)
BeforeH <- table(COURAGE_pol_w2_relig$q6618_relig_s1, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```

 
 


## Spanish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6618_relig`
* Label: `Attend religious services`
* Categories: 
    + `1 = Never`
    + `2 = Once/twice per year`
    + `3 = Once/twice per month`
    + `4 = Once/twice per week`
    + `5 = Daily`
* Missings:
    + `8 = DK`

* Description: 
```{r assign1 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_relig','Courage.Courage_Spain_w1',variables=list('q6618_relig'), missings = TRUE)
```

```{r local1 spain}
COURAGE_spain_w1_relig <- opal.execute(o,'COURAGE_spain_w1_relig')
vari <- COURAGE_spain_w1_relig$q6618_relig
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w1_relig$q6618_relig, missing_values = NA)
ggplot(COURAGE_spain_w1_relig, aes(x=factor(q6618_relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Attend religious services - frequency") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3, 4 or 5 then 1`
* `1 or 2 then 0`
* `8 into 998`
* `9,NA into 999`

 
**R script:**
```{r harmo1 spain, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_relig$id)
COURAGE_ds_spain_w1$relig <- car::recode(as.vector(COURAGE_spain_w1_relig$q6618_relig), "1:2='0'; 3:5='1'; 8='998'; 9='999'; NA='999'")
COURAGE_ds_spain_w1$relig <- labelled(COURAGE_ds_spain_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 spain}
vari <- COURAGE_ds_spain_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 spain}
AfterH <- table(COURAGE_ds_spain_w1$relig)
BeforeH <- table(COURAGE_spain_w1_relig$q6618_relig, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
BeforeH1[[4]] <- sum(BeforeH[c(7:8)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","8->998","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6618_relig_s1`
* Label: `Attend religious services`
* Categories: 
    + `1 = Never`
    + `2 = Once/twice per year`
    + `3 = Once/twice per month`
    + `4 = Once/twice per week`
    + `5 = Daily`
* Missings:
    + `8 = DK`

* Description: 
```{r assign2 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_relig','Courage.Courage_Spain_w2_1',variables=list('q6618_relig_s1'), missings = TRUE)
```

```{r local2 spain}
COURAGE_spain_w2_relig <- opal.execute(o,'COURAGE_spain_w2_relig')
vari <- COURAGE_spain_w2_relig$q6618_relig_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_relig$q6618_relig_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_relig, aes(x=factor(q6618_relig_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Attend religious services - frequency") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3, 4 or 5 then 1`
* `1 or 2 then 0`
* `8 into 998`
* `NA into 999`

 
**R script:**
```{r harmo2 spain, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_relig$id)
COURAGE_ds_spain_w2$relig <- car::recode(as.vector(COURAGE_spain_w2_relig$q6618_relig_s1), "1:2='0'; 3:5='1'; 8='998'; NA='999'")
COURAGE_ds_spain_w2$relig <- labelled(COURAGE_ds_spain_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 spain}
vari <- COURAGE_ds_spain_w2$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 spain}
AfterH <- table(COURAGE_ds_spain_w2$relig)
BeforeH <- table(COURAGE_spain_w2_relig$q6618_relig_s1, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```

 
 

```{r save, echo=FALSE}
relig <- COURAGE_ds_spain_w1
save(relig, file = "../RData/spain_w1/relig.RData")
rm(relig)

relig <- COURAGE_ds_spain_w2
save(relig, file = "../RData/spain_w2/relig.RData")
rm(relig)

relig <- COURAGE_ds_pol_w1
save(relig, file = "../RData/pol_w1/relig.RData")
rm(relig)

relig <- COURAGE_ds_pol_w2
save(relig, file = "../RData/pol_w2/relig.RData")
rm(relig)

relig <- COURAGE_ds_fin_w1
save(relig, file = "../RData/fin_w1/relig.RData")
rm(relig)
```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

