---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `confidant`
* Variable label: `Has friend(s)/confidant`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Finnish Population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends`
* Label: `Friends?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_confidant','Courage.Courage_Finland_w1', variables=list('q6010g_friends'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_confidant <- opal.execute(o,'COURAGE_fin_w1_confidant')
vari <-  COURAGE_fin_w1_confidant$q6010g_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_confidant$q6010g_friends, missing_values = NA)
ggplot(COURAGE_fin_w1_confidant, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `NA into 999`

 

**R script:** 
```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_confidant$id)
COURAGE_ds_fin_w1$confidant <-  car::recode(as.vector(COURAGE_fin_w1_confidant$q6010g_friends), "1='1'; 2='0'; NA='999'")
COURAGE_ds_fin_w1$confidant <- labelled(COURAGE_ds_fin_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH <- table(COURAGE_ds_fin_w1$confidant)
BeforeH <- table(COURAGE_fin_w1_confidant$q6010g_friends,useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
 





## Polish Population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends`
* Label: `Friends?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_confidant','Courage.Courage_Poland_w1', variables=list('q6010g_friends'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_confidant <- opal.execute(o,'COURAGE_pol_w1_confidant')
vari <-  COURAGE_pol_w1_confidant$q6010g_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_confidant$q6010g_friends, missing_values = NA)
ggplot(COURAGE_pol_w1_confidant, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `NA into 999`

 

**R script:** 
```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_confidant$id)
COURAGE_ds_pol_w1$confidant <- car::recode(as.vector(COURAGE_pol_w1_confidant$q6010g_friends), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w1$confidant <- labelled(COURAGE_ds_pol_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}
AfterH <- table(COURAGE_ds_pol_w1$confidant)
BeforeH <- table(COURAGE_pol_w1_confidant$q6010g_friends,useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends_s1`
* Label: `Friends?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_confidant','Courage.Courage_Poland_w2', variables=list('q6010g_friends_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_confidant <- opal.execute(o,'COURAGE_pol_w2_confidant')
vari <-  COURAGE_pol_w2_confidant$q6010g_friends_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_confidant$q6010g_friends_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_confidant, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `NA into 999`

 

**R script:** 
```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_confidant$id)
COURAGE_ds_pol_w2$confidant <- car::recode(as.vector(COURAGE_pol_w2_confidant$q6010g_friends_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w2$confidant <- labelled(COURAGE_ds_pol_w2$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}
AfterH <- table(COURAGE_ds_pol_w2$confidant)
BeforeH <- table(COURAGE_pol_w2_confidant$q6010g_friends_s1,useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
 





## Spanish Population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends`
* Label: `Friends?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1 sp}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_confidant','Courage.Courage_Spain_w1', variables=list('q6010g_friends'), missings = TRUE)
```

```{r local1 sp}
COURAGE_spain_w1_confidant <- opal.execute(o,'COURAGE_spain_w1_confidant')
vari <-  COURAGE_spain_w1_confidant$q6010g_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_confidant$q6010g_friends, missing_values = NA)
ggplot(COURAGE_spain_w1_confidant, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `NA into 999`

 

**R script:** 
```{r harmo1 sp, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_confidant$id)
COURAGE_ds_spain_w1$confidant <- car::recode(as.vector(COURAGE_spain_w1_confidant$q6010g_friends), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w1$confidant <- labelled(COURAGE_ds_spain_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 sp}
vari <- COURAGE_ds_spain_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 sp}
AfterH <- table(COURAGE_ds_spain_w1$confidant)
BeforeH <- table(COURAGE_spain_w1_confidant$q6010g_friends,useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends_s1`
* Label: `Friends?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign2 sp}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_confidant','Courage.Courage_Spain_w2_1', variables=list('q6010g_friends_s1'), missings = TRUE)
```

```{r local2 sp}
COURAGE_spain_w2_confidant <- opal.execute(o,'COURAGE_spain_w2_confidant')
vari <-  COURAGE_spain_w2_confidant$q6010g_friends_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_confidant$q6010g_friends_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_confidant, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `NA into 999`

 

**R script:** 
```{r harmo2 sp, echo=TRUE} 
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_confidant$id)
COURAGE_ds_spain_w2$confidant <- car::recode(as.vector(COURAGE_spain_w2_confidant$q6010g_friends_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w2$confidant <- labelled(COURAGE_ds_spain_w2$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 sp}
vari <- COURAGE_ds_spain_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 sp}
AfterH <- table(COURAGE_ds_spain_w2$confidant)
BeforeH <- table(COURAGE_spain_w2_confidant$q6010g_friends_s1,useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
```{r save, echo=FALSE}
confidant <- COURAGE_ds_spain_w1
save(confidant, file = "../RData/spain_w1/confidant.RData")
rm(confidant)

confidant <- COURAGE_ds_spain_w2
save(confidant, file = "../RData/spain_w2/confidant.RData")
rm(confidant)

confidant <- COURAGE_ds_pol_w1
save(confidant, file = "../RData/pol_w1/confidant.RData")
rm(confidant)

confidant <- COURAGE_ds_pol_w2
save(confidant, file = "../RData/pol_w2/confidant.RData")
rm(confidant)

confidant <- COURAGE_ds_fin_w1
save(confidant, file = "../RData/fin_w1/confidant.RData")
rm(confidant)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```