---
title: "Ever experienced financial problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `fin_prob`
* Variable label: `Ever experienced financial problems?`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0411b_problems`
* Label: `hosehold had financial problems with paying for bills`
* Categories: 
    + `1 = YES`
    + `2 = NO`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_fin_prob','Courage.Courage_Finland_w1',variables=list('q0411b_problems'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_fin_prob <- opal.execute(o,'COURAGE_fin_w1_fin_prob')
vari <- COURAGE_fin_w1_fin_prob$q0411b_problems
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_fin_prob$q0411b_problems, missing_values = NA)
ggplot(COURAGE_fin_w1_fin_prob, aes(x=factor(q0411b_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("hosehold had financial problems with paying for bills") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_fin_prob$id)
COURAGE_ds_fin_w1$fin_prob <- car::recode(as.vector(COURAGE_fin_w1_fin_prob$q0411b_problems), "1='1'; 2='0'; NA='999'")
COURAGE_ds_fin_w1$fin_prob <- labelled(COURAGE_ds_fin_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH <- table(COURAGE_ds_fin_w1$fin_prob)
BeforeH <- table(COURAGE_fin_w1_fin_prob$q0411b_problems, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```

## Polish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0411b_problems`
* Label: `hosehold had financial problems with paying for bills`
* Categories: 
    + `1 = YES`
    + `2 = NO`

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_fin_prob','Courage.Courage_Poland_w1',variables=list('q0411b_problems'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_fin_prob <- opal.execute(o,'COURAGE_pol_w1_fin_prob')
vari <- COURAGE_pol_w1_fin_prob$q0411b_problems
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_fin_prob$q0411b_problems, missing_values = NA)
ggplot(COURAGE_pol_w1_fin_prob, aes(x=factor(q0411b_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("household had financial problems with paying for bills") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_fin_prob$id)
COURAGE_ds_pol_w1$fin_prob <- car::recode(as.vector(COURAGE_pol_w1_fin_prob$q0411b_problems), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w1$fin_prob <- labelled(COURAGE_ds_pol_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}
AfterH <- table(COURAGE_ds_pol_w1$fin_prob)
BeforeH <- table(COURAGE_pol_w1_fin_prob$q0411b_problems, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```


### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0411b_problems_s1`
* Label: `hosehold had financial problems with paying for bills`
* Categories: 
    + `1 = YES`
    + `2 = NO`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_fin_prob','Courage.Courage_Poland_w2',variables=list('q0411b_problems_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_fin_prob <- opal.execute(o,'COURAGE_pol_w2_fin_prob')
vari <- COURAGE_pol_w2_fin_prob$q0411b_problems_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_fin_prob$q0411b_problems_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_fin_prob, aes(x=factor(q0411b_problems_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("hosehold had financial problems with paying for bills") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_fin_prob$id)
COURAGE_ds_pol_w2$fin_prob <- car::recode(as.vector(COURAGE_pol_w2_fin_prob$q0411b_problems_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w2$fin_prob <- labelled(COURAGE_ds_pol_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}
AfterH <- table(COURAGE_ds_pol_w2$fin_prob)
BeforeH <- table(COURAGE_pol_w2_fin_prob$q0411b_problems_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```

## Spanish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0411b_problems`
* Label: `hosehold had financial problems with paying for bills`
* Categories: 
    + `1 = YES`
    + `2 = NO`

* Description: 
```{r assign1 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_fin_prob','Courage.Courage_Spain_w1',variables=list('q0411b_problems'), missings = TRUE)
```

```{r local1 spain}
COURAGE_spain_w1_fin_prob <- opal.execute(o,'COURAGE_spain_w1_fin_prob')
vari <- COURAGE_spain_w1_fin_prob$q0411b_problems
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_fin_prob$q0411b_problems, missing_values = NA)
ggplot(COURAGE_spain_w1_fin_prob, aes(x=factor(q0411b_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("hosehold had financial problems with paying for bills") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo1 spain, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_fin_prob$id)
COURAGE_ds_spain_w1$fin_prob <- car::recode(as.vector(COURAGE_spain_w1_fin_prob$q0411b_problems), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w1$fin_prob <- labelled(COURAGE_ds_spain_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 spain}
vari <- COURAGE_ds_spain_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 spain}
AfterH <- table(COURAGE_ds_spain_w1$fin_prob)
BeforeH <- table(COURAGE_spain_w1_fin_prob$q0411b_problems, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```


### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0411b_problems_s1`
* Label: `hosehold had financial problems with paying for bills`
* Categories: 
    + `1 = YES`
    + `2 = NO`

* Description: 
```{r assign2 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_fin_prob','Courage.Courage_Spain_w2_1',variables=list('q0411b_problems_s1'), missings = TRUE)
```

```{r local2 spain}
COURAGE_spain_w2_fin_prob <- opal.execute(o,'COURAGE_spain_w2_fin_prob')
vari <- COURAGE_spain_w2_fin_prob$q0411b_problems_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_fin_prob$q0411b_problems_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_fin_prob, aes(x=factor(q0411b_problems_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("hosehold had financial problems with paying for bills") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo2 spain, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_fin_prob$id)
COURAGE_ds_spain_w2$fin_prob <- car::recode(as.vector(COURAGE_spain_w2_fin_prob$q0411b_problems_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w2$fin_prob <- labelled(COURAGE_ds_spain_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 spain}
vari <- COURAGE_ds_spain_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 spain}
AfterH <- table(COURAGE_ds_spain_w2$fin_prob)
BeforeH <- table(COURAGE_spain_w2_fin_prob$q0411b_problems_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```

```{r save, echo=FALSE}
fin_prob <- COURAGE_ds_fin_w1
save(fin_prob, file = "../RData/fin_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- COURAGE_ds_pol_w1
save(fin_prob, file = "../RData/pol_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- COURAGE_ds_pol_w2
save(fin_prob, file = "../RData/pol_w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- COURAGE_ds_spain_w1
save(fin_prob, file = "../RData/spain_w1/fin_prob.RData")
rm(fin_prob)


fin_prob <- COURAGE_ds_spain_w2
save(fin_prob, file = "../RData/spain_w2/fin_prob.RData")
rm(fin_prob)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

