---
title: "Felt loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `loneliness`
* Variable label: `felt loneliness?`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


## Finnish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6351_companion`
* Label: `How often lack of companionship?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6352_leftout`
* Label: `How often left out?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6353_isolated`
* Label: `How often isolated from others?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_loneliness','Courage.Courage_Finland_w1', variables=list('q6351_companion','q6352_leftout','q6353_isolated'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_loneliness <- opal.execute(o,'COURAGE_fin_w1_loneliness')

vari <- COURAGE_fin_w1_loneliness$q6351_companion
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_loneliness$q6351_companion, missing_values = NA)
ggplot(COURAGE_fin_w1_loneliness, aes(x=factor(q6351_companion))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often lack of companionship?") + ylab("Frequency")

vari <- COURAGE_fin_w1_loneliness$q6352_leftout
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_loneliness$q6352_leftout, missing_values = NA)
ggplot(COURAGE_fin_w1_loneliness, aes(x=factor(q6352_leftout))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often left out?") + ylab("Frequency")

vari <- COURAGE_fin_w1_loneliness$q6353_isolated
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_loneliness$q6353_isolated, missing_values = NA)
ggplot(COURAGE_fin_w1_loneliness, aes(x=factor(q6353_isolated))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often isolated from others?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3 or 2 then 1`
* `if all are equal 1 then 0`
* `NA into 999`

**R script:**

```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_loneliness$id)

COURAGE_fin_w1_loneliness$q6351_companion <- car::recode(as.vector(COURAGE_fin_w1_loneliness$q6351_companion), "NA='-999'")
COURAGE_fin_w1_loneliness$q6352_leftout <- car::recode(as.vector(COURAGE_fin_w1_loneliness$q6352_leftout), "NA='-999'")
COURAGE_fin_w1_loneliness$q6353_isolated <- car::recode(as.vector(COURAGE_fin_w1_loneliness$q6353_isolated), "NA='-999'")

COURAGE_ds_fin_w1$loneliness <- c(NA)
for(i in 1:dim(COURAGE_fin_w1_loneliness)[1]){
  if( COURAGE_fin_w1_loneliness$q6351_companion[i] %in% c(2,3) | COURAGE_fin_w1_loneliness$q6352_leftout[i] %in% c(2,3) | 
        COURAGE_fin_w1_loneliness$q6353_isolated[i] %in% c(2,3) ) {
    COURAGE_ds_fin_w1$loneliness[i] = 1 }
  else if( COURAGE_fin_w1_loneliness$q6351_companion[i] == 1 &
             COURAGE_fin_w1_loneliness$q6352_leftout[i] == 1 & 
             COURAGE_fin_w1_loneliness$q6353_isolated[i] == 1 ) {
    COURAGE_ds_fin_w1$loneliness[i] = 0 }
}

COURAGE_ds_fin_w1$loneliness <- car::recode(as.vector(COURAGE_ds_fin_w1$loneliness), "NA='999'")
COURAGE_ds_fin_w1$loneliness <- labelled(COURAGE_ds_fin_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}

```

## Polish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6351_companion`
* Label: `How often lack of companionship?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6352_leftout`
* Label: `How often left out?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6353_isolated`
* Label: `How often isolated from others?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_loneliness','Courage.Courage_Poland_w1', variables=list('q6351_companion','q6352_leftout','q6353_isolated'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_loneliness <- opal.execute(o,'COURAGE_pol_w1_loneliness')

vari <- COURAGE_pol_w1_loneliness$q6351_companion
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_loneliness$q6351_companion, missing_values = NA)
ggplot(COURAGE_pol_w1_loneliness, aes(x=factor(q6351_companion))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often lack of companionship?") + ylab("Frequency")

vari <- COURAGE_pol_w1_loneliness$q6352_leftout
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_loneliness$q6352_leftout, missing_values = NA)
ggplot(COURAGE_pol_w1_loneliness, aes(x=factor(q6352_leftout))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often left out?") + ylab("Frequency")

vari <- COURAGE_pol_w1_loneliness$q6353_isolated
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_loneliness$q6353_isolated, missing_values = NA)
ggplot(COURAGE_pol_w1_loneliness, aes(x=factor(q6353_isolated))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often isolated from others?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3 or 2 then 1`
* `if all are equal 1 then 0`
* `NA into 999`

**R script:**

```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_loneliness$id)

COURAGE_pol_w1_loneliness$q6351_companion <- car::recode(as.vector(COURAGE_pol_w1_loneliness$q6351_companion), "NA='-999'")
COURAGE_pol_w1_loneliness$q6352_leftout <- car::recode(as.vector(COURAGE_pol_w1_loneliness$q6352_leftout), "NA='-999'")
COURAGE_pol_w1_loneliness$q6353_isolated <- car::recode(as.vector(COURAGE_pol_w1_loneliness$q6353_isolated), "NA='-999'")

COURAGE_ds_pol_w1$loneliness <- c(NA)
for(i in 1:dim(COURAGE_pol_w1_loneliness)[1]){
  if( COURAGE_pol_w1_loneliness$q6351_companion[i] %in% c(2,3) | COURAGE_pol_w1_loneliness$q6352_leftout[i] %in% c(2,3) | 
        COURAGE_pol_w1_loneliness$q6353_isolated[i] %in% c(2,3) ) {
    COURAGE_ds_pol_w1$loneliness[i] = 1 }
  else if( COURAGE_pol_w1_loneliness$q6351_companion[i] == 1 & 
             COURAGE_pol_w1_loneliness$q6352_leftout[i] == 1 & 
             COURAGE_pol_w1_loneliness$q6353_isolated[i] == 1 ) {
    COURAGE_ds_pol_w1$loneliness[i] = 0 }
}

COURAGE_ds_pol_w1$loneliness <- car::recode(as.vector(COURAGE_ds_pol_w1$loneliness), "NA='999'")
COURAGE_ds_pol_w1$loneliness <- labelled(COURAGE_ds_pol_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}

```




### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6351_companion_s1`
* Label: `How often lack of companionship?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6352_leftout_s1`
* Label: `How often left out?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6353_isolated_s1`
* Label: `How often isolated from others?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_loneliness','Courage.Courage_Poland_w2',variables=list('q6351_companion_s1','q6352_leftout_s1','q6353_isolated_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_loneliness <- opal.execute(o,'COURAGE_pol_w2_loneliness')

vari <- COURAGE_pol_w2_loneliness$q6351_companion_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_loneliness$q6351_companion_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_loneliness, aes(x=factor(q6351_companion_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often lack of companionship?") + ylab("Frequency")

vari <- COURAGE_pol_w2_loneliness$q6352_leftout_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_loneliness$q6352_leftout_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_loneliness, aes(x=factor(q6352_leftout_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often left out?") + ylab("Frequency")

vari <- COURAGE_pol_w2_loneliness$q6353_isolated_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_loneliness$q6353_isolated_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_loneliness, aes(x=factor(q6353_isolated_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often isolated from others?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3 or 2 then 1`
* `if all are equal 1 then 0`
* `NA into 999`

**R script:**

```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_loneliness$id)

COURAGE_pol_w2_loneliness$q6351_companion_s1 <- car::recode(as.vector(COURAGE_pol_w2_loneliness$q6351_companion_s1), "NA='-999'")
COURAGE_pol_w2_loneliness$q6352_leftout_s1 <- car::recode(as.vector(COURAGE_pol_w2_loneliness$q6352_leftout_s1), "NA='-999'")
COURAGE_pol_w2_loneliness$q6353_isolated_s1 <- car::recode(as.vector(COURAGE_pol_w2_loneliness$q6353_isolated_s1), "NA='-999'")

COURAGE_ds_pol_w2$loneliness <- c(NA)
for(i in 1:dim(COURAGE_pol_w2_loneliness)[1]){
  if( COURAGE_pol_w2_loneliness$q6351_companion_s1[i] %in% c(2,3) | COURAGE_pol_w2_loneliness$q6352_leftout_s1[i] %in% c(2,3) | 
        COURAGE_pol_w2_loneliness$q6353_isolated_s1[i] %in% c(2,3) ) {
    COURAGE_ds_pol_w2$loneliness[i] = 1 }
  else if( COURAGE_pol_w2_loneliness$q6351_companion_s1[i] == 1 & 
             COURAGE_pol_w2_loneliness$q6352_leftout_s1[i] == 1 & 
             COURAGE_pol_w2_loneliness$q6353_isolated_s1[i] == 1 ) {
    COURAGE_ds_pol_w2$loneliness[i] = 0 }
}

COURAGE_ds_pol_w2$loneliness <- car::recode(as.vector(COURAGE_ds_pol_w2$loneliness), "NA='999'")
COURAGE_ds_pol_w2$loneliness <- labelled(COURAGE_ds_pol_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}

```

## Spanish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6351_companion`
* Label: `How often lack of companionship?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6352_leftout`
* Label: `How often left out?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
    
* Name: `q6353_isolated`
* Label: `How often isolated from others?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`

* Description: 
```{r assign1 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_loneliness','Courage.Courage_Spain_w1',variables=list('q6351_companion','q6352_leftout','q6353_isolated'), missings = TRUE)
```

```{r local1 spain}
COURAGE_spain_w1_loneliness <- opal.execute(o,'COURAGE_spain_w1_loneliness')

vari <- COURAGE_spain_w1_loneliness$q6351_companion
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_loneliness$q6351_companion, missing_values = NA)
ggplot(COURAGE_spain_w1_loneliness, aes(x=factor(q6351_companion))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often lack of companionship?") + ylab("Frequency")

vari <- COURAGE_spain_w1_loneliness$q6352_leftout
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_loneliness$q6352_leftout, missing_values = NA)
ggplot(COURAGE_spain_w1_loneliness, aes(x=factor(q6352_leftout))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often left out?") + ylab("Frequency")

vari <- COURAGE_spain_w1_loneliness$q6353_isolated
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_loneliness$q6353_isolated, missing_values = NA)
ggplot(COURAGE_spain_w1_loneliness, aes(x=factor(q6353_isolated))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often isolated from others?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3 or 2 then 1`
* `if all are equal 1 then 0`
* `NA into 999`

**R script:**

```{r harmo1 spain, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_loneliness$id)

COURAGE_spain_w1_loneliness$q6351_companion <- car::recode(as.vector(COURAGE_spain_w1_loneliness$q6351_companion), "NA='-999'")
COURAGE_spain_w1_loneliness$q6352_leftout <- car::recode(as.vector(COURAGE_spain_w1_loneliness$q6352_leftout), "NA='-999'")
COURAGE_spain_w1_loneliness$q6353_isolated <- car::recode(as.vector(COURAGE_spain_w1_loneliness$q6353_isolated), "NA='-999'")

COURAGE_ds_spain_w1$loneliness <- c(NA)
for(i in 1:dim(COURAGE_spain_w1_loneliness)[1]){
  if( COURAGE_spain_w1_loneliness$q6351_companion[i] %in% c(2,3) | COURAGE_spain_w1_loneliness$q6352_leftout[i] %in% c(2,3) | 
        COURAGE_spain_w1_loneliness$q6353_isolated[i] %in% c(2,3) ) {
    COURAGE_ds_spain_w1$loneliness[i] = 1 }
  else if( COURAGE_spain_w1_loneliness$q6351_companion[i] == 1 & 
             COURAGE_spain_w1_loneliness$q6352_leftout[i] == 1 & 
             COURAGE_spain_w1_loneliness$q6353_isolated[i] == 1 ) {
    COURAGE_ds_spain_w1$loneliness[i] = 0 }
}

COURAGE_ds_spain_w1$loneliness <- car::recode(as.vector(COURAGE_ds_spain_w1$loneliness), "NA='999'")
COURAGE_ds_spain_w1$loneliness <- labelled(COURAGE_ds_spain_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 spain}
vari <- COURAGE_ds_spain_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 spain}

```


### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6351_companion_s1`
* Label: `How often lack of companionship?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
* Missings:
    + `8 = DK`
    
* Name: `q6352_leftout_s1`
* Label: `How often left out?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
* Missings:
    + `8 = DK`
    
* Name: `q6353_isolated_s1`
* Label: `How often isolated from others?`
* Categories: 
    + `1 = Hardly ever`
    + `2 = Some of the time`
    + `3 = Often`
* Missings:
    + `8 = DK`

* Description: 
```{r assign2 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_loneliness','Courage.Courage_Spain_w2_1', variables=list('q6351_companion_s1','q6352_leftout_s1','q6353_isolated_s1'), missings = TRUE)
```

```{r local2 spain}
COURAGE_spain_w2_loneliness <- opal.execute(o,'COURAGE_spain_w2_loneliness')

vari <- COURAGE_spain_w2_loneliness$q6351_companion_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_loneliness$q6351_companion_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_loneliness, aes(x=factor(q6351_companion_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often lack of companionship?") + ylab("Frequency")

vari <- COURAGE_spain_w2_loneliness$q6352_leftout_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_loneliness$q6352_leftout_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_loneliness, aes(x=factor(q6352_leftout_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often left out?") + ylab("Frequency")

vari <- COURAGE_spain_w2_loneliness$q6353_isolated_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_loneliness$q6353_isolated_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_loneliness, aes(x=factor(q6353_isolated_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often isolated from others?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3 or 2 then 1`
* `if all are equal 1 then 0`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo2 spain, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_loneliness$id)

COURAGE_spain_w2_loneliness$q6351_companion_s1 <- car::recode(as.vector(COURAGE_spain_w2_loneliness$q6351_companion_s1), "NA='-999'")
COURAGE_spain_w2_loneliness$q6352_leftout_s1 <- car::recode(as.vector(COURAGE_spain_w2_loneliness$q6352_leftout_s1), "NA='-999'")
COURAGE_spain_w2_loneliness$q6353_isolated_s1 <- car::recode(as.vector(COURAGE_spain_w2_loneliness$q6353_isolated_s1), "NA='-999'")

COURAGE_ds_spain_w2$loneliness <- c(NA)
for(i in 1:dim(COURAGE_spain_w2_loneliness)[1]){
  if( COURAGE_spain_w2_loneliness$q6351_companion_s1[i] %in% c(2,3) | COURAGE_spain_w2_loneliness$q6352_leftout_s1[i] %in% c(2,3) | 
        COURAGE_spain_w2_loneliness$q6353_isolated_s1[i] %in% c(2,3) ) {
    COURAGE_ds_spain_w2$loneliness[i] = 1 }
  else if( COURAGE_spain_w2_loneliness$q6351_companion_s1[i] == 1 & 
             COURAGE_spain_w2_loneliness$q6352_leftout_s1[i] == 1 & 
             COURAGE_spain_w2_loneliness$q6353_isolated_s1[i] == 1 ) {
    COURAGE_ds_spain_w2$loneliness[i] = 0 }
  else if( COURAGE_spain_w2_loneliness$q6351_companion_s1[i] == 8 | 
             COURAGE_spain_w2_loneliness$q6352_leftout_s1[i] == 8 | 
             COURAGE_spain_w2_loneliness$q6353_isolated_s1[i] == 8 ) {
    COURAGE_ds_spain_w2$loneliness[i] = 998 }
}

COURAGE_ds_spain_w2$loneliness <- car::recode(as.vector(COURAGE_ds_spain_w2$loneliness), "NA='999'")
COURAGE_ds_spain_w2$loneliness <- labelled(COURAGE_ds_spain_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 spain}
vari <- COURAGE_ds_spain_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 spain}

```

```{r save, echo=FALSE}

loneliness <- COURAGE_ds_fin_w1
save(loneliness, file = "../RData/fin_w1/loneliness.RData")
rm(loneliness)

loneliness <- COURAGE_ds_pol_w1
save(loneliness, file = "../RData/pol_w1/loneliness.RData")
rm(loneliness)

loneliness <- COURAGE_ds_pol_w2
save(loneliness, file = "../RData/pol_w2/loneliness.RData")
rm(loneliness)

loneliness <- COURAGE_ds_spain_w1
save(loneliness, file = "../RData/spain_w1/loneliness.RData")
rm(loneliness)



loneliness <- COURAGE_ds_spain_w2
save(loneliness, file = "../RData/spain_w2/loneliness.RData")
rm(loneliness)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

