---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Finnish population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `3.0 = COHABITING`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_spouse','Courage.Courage_Finland_w1', variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_spouse <- opal.execute(o,'COURAGE_fin_w1_spouse')
vari <- COURAGE_fin_w1_spouse$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_spouse$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_fin_w1_spouse, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_spouse$id)
COURAGE_ds_fin_w1$spouse <- car::recode(as.vector(COURAGE_fin_w1_spouse$q1012_mar_stat), "2:3='1'; 1='0'; 4:5='0'; NA='999'")
COURAGE_ds_fin_w1$spouse <- labelled(COURAGE_ds_fin_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH <- table(COURAGE_ds_fin_w1$spouse)
BeforeH <- table(COURAGE_fin_w1_spouse$q1012_mar_stat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH[[3]] <- BeforeH[[6]]
BeforeH <- BeforeH[c(1,2,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","NA->999")

kable(C)
```

 
 



## Polish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `3.0 = COHABITING`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_spouse','Courage.Courage_Poland_w1', variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_spouse <- opal.execute(o,'COURAGE_pol_w1_spouse')
vari <- COURAGE_pol_w1_spouse$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_spouse$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_pol_w1_spouse, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_spouse$id)
COURAGE_ds_pol_w1$spouse <- car::recode(as.vector(COURAGE_pol_w1_spouse$q1012_mar_stat), "2:3='1'; 1='0'; 4:5='0'; NA='999'")
COURAGE_ds_pol_w1$spouse <- labelled(COURAGE_ds_pol_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}
AfterH <- table(COURAGE_ds_pol_w1$spouse)
BeforeH <- table(COURAGE_pol_w1_spouse$q1012_mar_stat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1")

kable(C)
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012_mar_stat_s1`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`
    
* Name: `p1012_mar_stat_s1`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`
    + `88.0 = WIDOWED`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_spouse','Courage.Courage_Poland_w2', 
                        variables=list('q1012_mar_stat_s1', 'p1012_mar_stat_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_spouse <- opal.execute(o,'COURAGE_pol_w2_spouse')

vari <- COURAGE_pol_w2_spouse$q1012_mar_stat_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_spouse$q1012_mar_stat_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_spouse, aes(x=factor(q1012_mar_stat_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status - individual respondent") + ylab("Frequency")

vari <- COURAGE_pol_w2_spouse$p1012_mar_stat_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_spouse$p1012_mar_stat_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_spouse, aes(x=factor(p1012_mar_stat_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status - proxy respondent") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q1012_mar_stat_s1=2 OR p1012_mar_stat_s1=2 into 1`
* `q1012_mar_stat_s1 in (1,4,5) OR p1012_mar_stat_s1 in (1,4,5,88) into 0`
* `NA into 999`

**R script:**

```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_spouse$id)

COURAGE_pol_w2_spouse$q1012_mar_stat_s1 <- car::recode(as.vector(COURAGE_pol_w2_spouse$q1012_mar_stat_s1), "NA='-999'")
COURAGE_pol_w2_spouse$p1012_mar_stat_s1 <- car::recode(as.vector(COURAGE_pol_w2_spouse$p1012_mar_stat_s1), "NA='-999'")

COURAGE_ds_pol_w2$spouse <- c(NA) # I think it is required here
for(i in 1:dim(COURAGE_pol_w2_spouse)[1]){
if(COURAGE_pol_w2_spouse$q1012_mar_stat_s1[i] == 2 | COURAGE_pol_w2_spouse$p1012_mar_stat_s1[i] == 2) {
  COURAGE_ds_pol_w2$spouse[i] = 1 }
else if(COURAGE_pol_w2_spouse$q1012_mar_stat_s1[i] %in% c(1,4,5) | 
        COURAGE_pol_w2_spouse$p1012_mar_stat_s1[i] %in% c(1,4,5,88)){ COURAGE_ds_pol_w2$spouse[i] = 0 }
}

COURAGE_ds_pol_w2$spouse <- car::recode(as.vector(COURAGE_ds_pol_w2$spouse), "NA='999'")
COURAGE_ds_pol_w2$spouse <- labelled(COURAGE_ds_pol_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}
AfterH <- table(COURAGE_ds_pol_w2$spouse)
BeforeH1 <- table(COURAGE_pol_w2_spouse$q1012_mar_stat_s1, COURAGE_pol_w2_spouse$p1012_mar_stat_s1, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH1[3,1], BeforeH1[1,3])
BeforeH[[2]] <- sum(BeforeH1[2,1],BeforeH1[4,1],BeforeH1[5,1],BeforeH1[1,2],BeforeH1[1,4],BeforeH1[1,5],BeforeH1[1,6])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 


## Spanish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `3.0 = COHABITING`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_spouse','Courage.Courage_Spain_w1', 
                        variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local1}
COURAGE_spain_w1_spouse <- opal.execute(o,'COURAGE_spain_w1_spouse')
vari <- COURAGE_spain_w1_spouse$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_spouse$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_spain_w1_spouse, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_spouse$id)
COURAGE_ds_spain_w1$spouse <- car::recode(as.vector(COURAGE_spain_w1_spouse$q1012_mar_stat), "2:3='1'; 1='0'; 4:5='0'; NA='999'")
COURAGE_ds_spain_w1$spouse <- labelled(COURAGE_ds_spain_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- COURAGE_ds_spain_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(COURAGE_ds_spain_w1$spouse)
BeforeH <- table(COURAGE_spain_w1_spouse$q1012_mar_stat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1")

kable(C)
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012_mar_stat_s1`
* Label: `Marital status`
* Categories: 
    + `1.0 = NEVER MARRIED (AND NO COHABITING)`
    + `2.0 = CURRENTLY MARRIED`
    + `3.0 = COHABITING`
    + `4.0 = SEPARATED/DIVORCED`
    + `5.0 = WIDOWED`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_spouse','Courage.Courage_Spain_w2_1', variables=list('q1012_mar_stat_s1'), missings = TRUE)
```

```{r local2}
COURAGE_spain_w2_spouse <- opal.execute(o,'COURAGE_spain_w2_spouse')
vari <- COURAGE_spain_w2_spouse$q1012_mar_stat_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_spouse$q1012_mar_stat_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_spouse, aes(x=factor(q1012_mar_stat_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_spouse$id)
COURAGE_ds_spain_w2$spouse <- car::recode(as.vector(COURAGE_spain_w2_spouse$q1012_mar_stat_s1), "2:3='1'; 1='0'; 4:5='0'; NA='999'")
COURAGE_ds_spain_w2$spouse <- labelled(COURAGE_ds_spain_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- COURAGE_ds_spain_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(COURAGE_ds_spain_w2$spouse)
BeforeH <- table(COURAGE_spain_w2_spouse$q1012_mar_stat_s1, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH[[3]] <- BeforeH[[6]]
BeforeH <- BeforeH[c(1,2,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","NA->999")

kable(C)
```

 
  
```{r save, echo=FALSE}
spouse <- COURAGE_ds_spain_w1
save(spouse, file = "../RData/spain_w1/spouse.RData")
rm(spouse)

spouse <- COURAGE_ds_spain_w2
save(spouse, file = "../RData/spain_w2/spouse.RData")
rm(spouse)

spouse <- COURAGE_ds_pol_w1
save(spouse, file = "../RData/pol_w1/spouse.RData")
rm(spouse)

spouse <- COURAGE_ds_pol_w2
save(spouse, file = "../RData/pol_w2/spouse.RData")
rm(spouse)

spouse <- COURAGE_ds_fin_w1
save(spouse, file = "../RData/fin_w1/spouse.RData")
rm(spouse)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

