---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010c_children`
* Label: `Children?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6010d_grandch`
* Label: `Grandchildren?`
* Categories: 
    + `1 = Yes`
    + `2 = No`


* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_child','Courage.Courage_Finland_w1',variables=list('q6010c_children','q6010d_grandch'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_child <- opal.execute(o,'COURAGE_fin_w1_child')

vari <-  COURAGE_fin_w1_child$q6010c_children
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_child$q6010c_children, missing_values = NA)
ggplot(COURAGE_fin_w1_child, aes(x=factor(q6010c_children))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")


vari <-  COURAGE_fin_w1_child$q6010d_grandch
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_child$q6010d_grandch, missing_values = NA)
ggplot(COURAGE_fin_w1_child, aes(x=factor(q6010d_grandch))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_child$id)

COURAGE_ds_fin_w1$child <- car::recode(as.vector(COURAGE_fin_w1_child$q6010c_children), "1='1'; 2='0'; NA='999'")
COURAGE_ds_fin_w1$child <- labelled(COURAGE_ds_fin_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

COURAGE_ds_fin_w1$grchild <- car::recode(as.vector(COURAGE_fin_w1_child$q6010d_grandch), "1='1'; 2='0'; NA='999'")
COURAGE_ds_fin_w1$grchild <- labelled(COURAGE_ds_fin_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <-  COURAGE_ds_fin_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH1 <- table(COURAGE_ds_fin_w1$child)
BeforeH1 <- table(COURAGE_fin_w1_child$q6010c_children, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "child")

AfterH2 <- table(COURAGE_ds_fin_w1$grchild)
BeforeH2 <- table(COURAGE_fin_w1_child$q6010d_grandch, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "grchild")
```

 
 


## Polish population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010c_children`
* Label: `Children?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6010d_grandch`
* Label: `Grandchildren?`
* Categories: 
    + `1 = Yes`
    + `2 = No`


* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_child','Courage.Courage_Poland_w1',variables=list('q6010c_children','q6010d_grandch'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_child <- opal.execute(o,'COURAGE_pol_w1_child')
vari <-  COURAGE_pol_w1_child$q6010c_children
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_child$q6010c_children, missing_values = NA)
ggplot(COURAGE_pol_w1_child, aes(x=factor(q6010c_children))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")

vari <-  COURAGE_pol_w1_child$q6010d_grandch
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_child$q6010d_grandch, missing_values = NA)
ggplot(COURAGE_pol_w1_child, aes(x=factor(q6010d_grandch))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_child$id)

COURAGE_ds_pol_w1$child <- car::recode(as.vector(COURAGE_pol_w1_child$q6010c_children), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w1$child <- labelled(COURAGE_ds_pol_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

COURAGE_ds_pol_w1$grchild <- car::recode(as.vector(COURAGE_pol_w1_child$q6010d_grandch), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w1$grchild <- labelled(COURAGE_ds_pol_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- COURAGE_ds_pol_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}
AfterH1 <- table(COURAGE_ds_pol_w1$child)
BeforeH1 <- table(COURAGE_pol_w1_child$q6010c_children, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "child")

AfterH2 <- table(COURAGE_ds_pol_w1$grchild)
BeforeH2 <- table(COURAGE_pol_w1_child$q6010d_grandch, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "grchild")
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010c_children_s1`
* Label: `Children?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6010d_grandch_s1`
* Label: `Grandchildren?`
* Categories: 
    + `1 = Yes`
    + `2 = No`

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_child','Courage.Courage_Poland_w2',variables=list('q6010c_children_s1','q6010d_grandch_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_child <- opal.execute(o,'COURAGE_pol_w2_child')
vari <- COURAGE_pol_w2_child$q6010c_children_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_child$q6010c_children_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_child, aes(x=factor(q6010c_children_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")

vari <- COURAGE_pol_w2_child$q6010d_grandch_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_child$q6010d_grandch_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_child, aes(x=factor(q6010d_grandch_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`

 **R script:**

```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_child$id)

COURAGE_ds_pol_w2$child <- car::recode(as.vector(COURAGE_pol_w2_child$q6010c_children_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w2$child <- labelled(COURAGE_ds_pol_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

COURAGE_ds_pol_w2$grchild <- car::recode(as.vector(COURAGE_pol_w2_child$q6010d_grandch_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_pol_w2$grchild <- labelled(COURAGE_ds_pol_w2$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")

vari <- COURAGE_ds_pol_w2$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}
AfterH1 <- table(COURAGE_ds_pol_w2$child)
BeforeH1 <- table(COURAGE_pol_w2_child$q6010c_children_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "child")

AfterH2 <- table(COURAGE_ds_pol_w2$grchild)
BeforeH2 <- table(COURAGE_pol_w2_child$q6010d_grandch_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "grchild")
```

 
 


## Spanish population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010c_children`
* Label: `Children?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6010d_grandch`
* Label: `Grandchildren?`
* Categories: 
    + `1 = Yes`
    + `2 = No`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_child','Courage.Courage_Spain_w1',variables=list('q6010c_children','q6010d_grandch'), missings = TRUE)
```

```{r local1}
COURAGE_spain_w1_child <- opal.execute(o,'COURAGE_spain_w1_child')
vari <- COURAGE_spain_w1_child$q6010c_children
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_child$q6010c_children, missing_values = NA)
ggplot(COURAGE_spain_w1_child, aes(x=factor(q6010c_children))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")
vari <- COURAGE_spain_w1_child$q6010d_grandch
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_child$q6010d_grandch, missing_values = NA)
ggplot(COURAGE_spain_w1_child, aes(x=factor(q6010d_grandch))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_child$id)

COURAGE_ds_spain_w1$child <- car::recode(as.vector(COURAGE_spain_w1_child$q6010c_children), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w1$child <- labelled(COURAGE_ds_spain_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

COURAGE_ds_spain_w1$grchild <- car::recode(as.vector(COURAGE_spain_w1_child$q6010d_grandch), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w1$grchild <- labelled(COURAGE_ds_spain_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- COURAGE_ds_spain_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- COURAGE_ds_spain_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH1 <- table(COURAGE_ds_spain_w1$child)
BeforeH1 <- table(COURAGE_spain_w1_child$q6010c_children, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "child")

AfterH2 <- table(COURAGE_ds_spain_w1$grchild)
BeforeH2 <- table(COURAGE_spain_w1_child$q6010d_grandch, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "grchild")
```

 
 



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6010c_children_s1`
* Label: `Children?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6010d_grandch_s1`
* Label: `Grandchildren?`
* Categories: 
    + `1 = Yes`
    + `2 = No`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_child','Courage.Courage_Spain_w2_1',variables=list('q6010c_children_s1','q6010d_grandch_s1'), missings = TRUE)
```

```{r local2}
COURAGE_spain_w2_child <- opal.execute(o,'COURAGE_spain_w2_child')
vari <- COURAGE_spain_w2_child$q6010c_children_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_child$q6010c_children_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_child, aes(x=factor(q6010c_children_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")

vari <- COURAGE_spain_w2_child$q6010d_grandch_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_child$q6010d_grandch_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_child, aes(x=factor(q6010d_grandch_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999` 

 **R script:**

```{r harmo2, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_child$id)

COURAGE_ds_spain_w2$child <- car::recode(as.vector(COURAGE_spain_w2_child$q6010c_children_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w2$child <- labelled(COURAGE_ds_spain_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

COURAGE_ds_spain_w2$grchild <- car::recode(as.vector(COURAGE_spain_w2_child$q6010d_grandch_s1), "1='1'; 2='0'; NA='999'")
COURAGE_ds_spain_w2$grchild <- labelled(COURAGE_ds_spain_w2$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- COURAGE_ds_spain_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children?") + ylab("Frequency")

vari <- COURAGE_ds_spain_w2$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH1 <- table(COURAGE_ds_spain_w2$child)
BeforeH1 <- table(COURAGE_spain_w2_child$q6010c_children_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "child")

AfterH2 <- table(COURAGE_ds_spain_w2$grchild)
BeforeH2 <- table(COURAGE_spain_w2_child$q6010d_grandch_s1, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","NA->999")
kable(C, caption = "grchild")
```

 
 


```{r save, echo=FALSE}
child <- COURAGE_ds_spain_w1[,-3]
save(child, file = "../RData/spain_w1/child.RData")
rm(child)

child <- COURAGE_ds_spain_w2[,-3]
save(child, file = "../RData/spain_w2/child.RData")
rm(child)

child <- COURAGE_ds_pol_w1[,-3]
save(child, file = "../RData/pol_w1/child.RData")
rm(child)

child <- COURAGE_ds_pol_w2[,-3]
save(child, file = "../RData/pol_w2/child.RData")
rm(child)

child <- COURAGE_ds_fin_w1[,-3]
save(child, file = "../RData/fin_w1/child.RData")
rm(child)

grchild <- COURAGE_ds_spain_w1[,-2]
save(grchild, file = "../RData/spain_w1/grchild.RData")
rm(grchild)

grchild <- COURAGE_ds_spain_w2[,-2]
save(grchild, file = "../RData/spain_w2/grchild.RData")
rm(grchild)

grchild <- COURAGE_ds_pol_w1[,-2]
save(grchild, file = "../RData/pol_w1/grchild.RData")
rm(grchild)

grchild <- COURAGE_ds_pol_w2[,-2]
save(grchild, file = "../RData/pol_w2/grchild.RData")
rm(grchild)

grchild <- COURAGE_ds_fin_w1[,-2]
save(grchild, file = "../RData/fin_w1/grchild.RData")
rm(grchild)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
# Quality estimation