---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `oth_fam`
* Variable label: `Has other (living) family members (e.g. parents, siblings, in-laws, etc.)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population


### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010b_parents`
* Label: `Parents?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
    
* Name: `q6010e_other`
* Label: `Other relatives?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_oth_fam','Courage.Courage_Finland_w1', 
                        variables=list('q6010b_parents','q6010e_other'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_oth_fam <- opal.execute(o,'COURAGE_fin_w1_oth_fam')
vari <- COURAGE_fin_w1_oth_fam$q6010b_parents
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_oth_fam$q6010b_parents, missing_values = NA)
ggplot(COURAGE_fin_w1_oth_fam, aes(x=factor(q6010b_parents))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has parents?") + ylab("Frequency")

vari <-  COURAGE_fin_w1_oth_fam$q6010e_other
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_oth_fam$q6010e_other, missing_values = NA)
ggplot(COURAGE_fin_w1_oth_fam, aes(x=factor(q6010e_other))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other relatives?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 1 into 1`
* `2 and 2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_oth_fam$id)

COURAGE_fin_w1_oth_fam$q6010b_parents <- car::recode(as.vector(COURAGE_fin_w1_oth_fam$q6010b_parents), "NA='-999'")
COURAGE_fin_w1_oth_fam$q6010e_other <- car::recode(as.vector(COURAGE_fin_w1_oth_fam$q6010e_other), "NA='-999'")

COURAGE_ds_fin_w1$oth_fam <- c(NA)
for(i in 1:dim(COURAGE_fin_w1_oth_fam)[1]){
  if( COURAGE_fin_w1_oth_fam$q6010b_parents[i] == 1 | COURAGE_fin_w1_oth_fam$q6010e_other[i] == 1 ){
    COURAGE_ds_fin_w1$oth_fam[i] = 1 }
  else if( COURAGE_fin_w1_oth_fam$q6010b_parents[i] == 2 & COURAGE_fin_w1_oth_fam$q6010e_other[i] == 2 ){
    COURAGE_ds_fin_w1$oth_fam[i] = 0 }
}

COURAGE_ds_fin_w1$oth_fam <- car::recode(as.vector(COURAGE_ds_fin_w1$oth_fam), "NA='999'")
COURAGE_ds_fin_w1$oth_fam <- labelled(COURAGE_ds_fin_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}
AfterH <- table(COURAGE_ds_fin_w1$oth_fam)
BeforeH1 <- table(COURAGE_fin_w1_oth_fam$q6010b_parents, COURAGE_fin_w1_oth_fam$q6010e_other, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- BeforeH1['2','2']
BeforeH[[2]] <- sum(sum(BeforeH1['1',]),sum(BeforeH1[c('-999','2'),'1'])) 
BeforeH[[3]] <- sum(sum(BeforeH1['-999',]),sum(BeforeH1['2','-999']))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 



## Polish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010b_parents`
* Label: `Parents?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
    
* Name: `q6010e_other`
* Label: `Other relatives?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_oth_fam','Courage.Courage_Poland_w1', 
                        variables=list('q6010b_parents','q6010e_other'), missings = TRUE)
```

```{r local1pol}
COURAGE_pol_w1_oth_fam <- opal.execute(o,'COURAGE_pol_w1_oth_fam')
vari <-  COURAGE_pol_w1_oth_fam$q6010b_parents
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_oth_fam$q6010b_parents, missing_values = NA)
ggplot(COURAGE_pol_w1_oth_fam, aes(x=factor(q6010b_parents))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has parents?") + ylab("Frequency")

vari <-  COURAGE_pol_w1_oth_fam$q6010e_othe
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_oth_fam$q6010e_other, missing_values = NA)
ggplot(COURAGE_pol_w1_oth_fam, aes(x=factor(q6010e_other))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other relatives?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 1 into 1`
* `2 and 2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_oth_fam$id)

COURAGE_pol_w1_oth_fam$q6010b_parents <- car::recode(as.vector(COURAGE_pol_w1_oth_fam$q6010b_parents), "NA='-999'")
COURAGE_pol_w1_oth_fam$q6010e_other <- car::recode(as.vector(COURAGE_pol_w1_oth_fam$q6010e_other), "NA='-999'")

COURAGE_ds_pol_w1$oth_fam <- c(NA)
for(i in 1:dim(COURAGE_pol_w1_oth_fam)[1]){
  if( COURAGE_pol_w1_oth_fam$q6010b_parents[i] == 1 | COURAGE_pol_w1_oth_fam$q6010e_other[i] == 1 ){
    COURAGE_ds_pol_w1$oth_fam[i] = 1 }
  else if( COURAGE_pol_w1_oth_fam$q6010b_parents[i] == 2 & COURAGE_pol_w1_oth_fam$q6010e_other[i] == 2 ){
    COURAGE_ds_pol_w1$oth_fam[i] = 0 }
}

COURAGE_ds_pol_w1$oth_fam <- car::recode(as.vector(COURAGE_ds_pol_w1$oth_fam), "NA='999'")
COURAGE_ds_pol_w1$oth_fam <- labelled(COURAGE_ds_pol_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1pol}
vari <- COURAGE_ds_pol_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1pol}
AfterH <- table(COURAGE_ds_pol_w1$oth_fam)
BeforeH1 <- table(COURAGE_pol_w1_oth_fam$q6010b_parents, COURAGE_pol_w1_oth_fam$q6010e_other, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- BeforeH1['2','2']
BeforeH[[2]] <- sum(sum(BeforeH1['1',]),sum(BeforeH1[c('-999','2'),'1'])) 
BeforeH[[3]] <- sum(sum(BeforeH1['-999',]),sum(BeforeH1['2','-999']))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 



### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010b_parents_s1`
* Label: `Parents?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
    
* Name: `q6010e_other_s1`
* Label: `Other relatives?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign2pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_oth_fam','Courage.Courage_Poland_w2', 
                        variables=list('q6010b_parents_s1','q6010e_other_s1'), missings = TRUE)
```

```{r local2pol}
COURAGE_pol_w2_oth_fam <- opal.execute(o,'COURAGE_pol_w2_oth_fam')
vari <- COURAGE_pol_w2_oth_fam$q6010b_parents_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_oth_fam$q6010b_parents_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_oth_fam, aes(x=factor(q6010b_parents_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has parents?") + ylab("Frequency")

vari <- COURAGE_pol_w2_oth_fam$q6010e_other_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_oth_fam$q6010e_other_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_oth_fam, aes(x=factor(q6010e_other_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other relatives?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 1 into 1`
* `2 and 2 into 0`
* `NA into 999`

 **R script:**

```{r harmo2pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_oth_fam$id)

COURAGE_pol_w2_oth_fam$q6010b_parents_s1 <- car::recode(as.vector(COURAGE_pol_w2_oth_fam$q6010b_parents_s1), "NA='-999'")
COURAGE_pol_w2_oth_fam$q6010e_other_s1 <- car::recode(as.vector(COURAGE_pol_w2_oth_fam$q6010e_other_s1), "NA='-999'")

COURAGE_ds_pol_w2$oth_fam <- c(NA)
for(i in 1:dim(COURAGE_pol_w2_oth_fam)[1]){
  if( COURAGE_pol_w2_oth_fam$q6010b_parents_s1[i] == 1 | COURAGE_pol_w2_oth_fam$q6010e_other_s1[i] == 1 ){
    COURAGE_ds_pol_w2$oth_fam[i] = 1 }
  else if( COURAGE_pol_w2_oth_fam$q6010b_parents_s1[i] == 2 & COURAGE_pol_w2_oth_fam$q6010e_other_s1[i] == 2 ){
    COURAGE_ds_pol_w2$oth_fam[i] = 0 }
}

COURAGE_ds_pol_w2$oth_fam <- car::recode(as.vector(COURAGE_ds_pol_w2$oth_fam), "NA='999'")
COURAGE_ds_pol_w2$oth_fam <- labelled(COURAGE_ds_pol_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2pol}
vari <- COURAGE_ds_pol_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2pol}
AfterH <- table(COURAGE_ds_pol_w2$oth_fam)
BeforeH1 <- table(COURAGE_pol_w2_oth_fam$q6010b_parents_s1, COURAGE_pol_w2_oth_fam$q6010e_other_s1, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- BeforeH1['2','2']
BeforeH[[2]] <- sum(sum(BeforeH1['1',]),sum(BeforeH1[c('-999','2'),'1'])) 
BeforeH[[3]] <- sum(sum(BeforeH1['-999',]),sum(BeforeH1['2','-999']))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 



## Spanish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010b_parents`
* Label: `Parents?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
    
* Name: `q6010e_other`
* Label: `Other relatives?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign1 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_oth_fam','Courage.Courage_Spain_w1', 
                        variables=list('q6010b_parents','q6010e_other'), missings = TRUE)
```

```{r local1 spain}
COURAGE_spain_w1_oth_fam <- opal.execute(o,'COURAGE_spain_w1_oth_fam')
vari <- COURAGE_spain_w1_oth_fam$q6010b_parents
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_oth_fam$q6010b_parents, missing_values = NA)
ggplot(COURAGE_spain_w1_oth_fam, aes(x=factor(q6010b_parents))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has parents?") + ylab("Frequency")
vari <- COURAGE_spain_w1_oth_fam$q6010e_other
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_oth_fam$q6010e_other, missing_values = NA)
ggplot(COURAGE_spain_w1_oth_fam, aes(x=factor(q6010e_other))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other relatives?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 1 into 1`
* `2 and 2 into 0`
* `NA into 999`

 **R script:**

```{r harmo1 spain, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_oth_fam$id)

COURAGE_spain_w1_oth_fam$q6010b_parents <- car::recode(as.vector(COURAGE_spain_w1_oth_fam$q6010b_parents), "NA='-999'")
COURAGE_spain_w1_oth_fam$q6010e_other <- car::recode(as.vector(COURAGE_spain_w1_oth_fam$q6010e_other), "NA='-999'")

COURAGE_ds_spain_w1$oth_fam <- c(NA)
for(i in 1:dim(COURAGE_spain_w1_oth_fam)[1]){
  if( COURAGE_spain_w1_oth_fam$q6010b_parents[i] == 1 | COURAGE_spain_w1_oth_fam$q6010e_other[i] == 1 ){
    COURAGE_ds_spain_w1$oth_fam[i] = 1 }
  else if( COURAGE_spain_w1_oth_fam$q6010b_parents[i] == 2 & COURAGE_spain_w1_oth_fam$q6010e_other[i] == 2 ){
    COURAGE_ds_spain_w1$oth_fam[i] = 0 }
}

COURAGE_ds_spain_w1$oth_fam <- car::recode(as.vector(COURAGE_ds_spain_w1$oth_fam), "NA='999'")
COURAGE_ds_spain_w1$oth_fam <- labelled(COURAGE_ds_spain_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 spain}
vari <- COURAGE_ds_spain_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 spain}
AfterH <- table(COURAGE_ds_spain_w1$oth_fam)
BeforeH1 <- table(COURAGE_spain_w1_oth_fam$q6010b_parents, COURAGE_spain_w1_oth_fam$q6010e_other, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- BeforeH1['2','2']
BeforeH[[2]] <- sum(sum(BeforeH1['1',]),sum(BeforeH1[c('-999','2'),'1'])) 
BeforeH[[3]] <- sum(sum(BeforeH1['-999',]),sum(BeforeH1['2','-999']))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 



### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010b_parents_s1`
* Label: `Parents?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
    
* Name: `q6010e_other_s1`
* Label: `Other relatives?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign2 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_oth_fam','Courage.Courage_Spain_w2_1', 
                        variables=list('q6010b_parents_s1','q6010e_other_s1'), missings = TRUE)
```

```{r local2 spain}
COURAGE_spain_w2_oth_fam <- opal.execute(o,'COURAGE_spain_w2_oth_fam')
vari <- COURAGE_spain_w2_oth_fam$q6010b_parents_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_oth_fam$q6010b_parents_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_oth_fam, aes(x=factor(q6010b_parents_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has parents?") + ylab("Frequency")
vari <- COURAGE_spain_w2_oth_fam$q6010e_other_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_oth_fam$q6010e_other_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_oth_fam, aes(x=factor(q6010e_other_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other relatives?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 1 into 1`
* `2 and 2 into 0`
* `NA into 999`

 **R script:**

```{r harmo2 spain, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_oth_fam$id)

COURAGE_spain_w2_oth_fam$q6010b_parents_s1 <- car::recode(as.vector(COURAGE_spain_w2_oth_fam$q6010b_parents_s1), "NA='-999'")
COURAGE_spain_w2_oth_fam$q6010e_other_s1 <- car::recode(as.vector(COURAGE_spain_w2_oth_fam$q6010e_other_s1), "NA='-999'")

COURAGE_ds_spain_w2$oth_fam <- c(NA)
for(i in 1:dim(COURAGE_spain_w2_oth_fam)[1]){
  if( COURAGE_spain_w2_oth_fam$q6010b_parents_s1[i] == 1 | COURAGE_spain_w2_oth_fam$q6010e_other_s1[i] == 1 ){
    COURAGE_ds_spain_w2$oth_fam[i] = 1 }
  else if( COURAGE_spain_w2_oth_fam$q6010b_parents_s1[i] == 2 & COURAGE_spain_w2_oth_fam$q6010e_other_s1[i] == 2 ){
    COURAGE_ds_spain_w2$oth_fam[i] = 0 }
}

COURAGE_ds_spain_w2$oth_fam <- car::recode(as.vector(COURAGE_ds_spain_w2$oth_fam), "NA='999'")
COURAGE_ds_spain_w2$oth_fam <- labelled(COURAGE_ds_spain_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 spain}
vari <- COURAGE_ds_spain_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 spain}
AfterH <- table(COURAGE_ds_spain_w2$oth_fam)
BeforeH1 <- table(COURAGE_spain_w2_oth_fam$q6010b_parents_s1, COURAGE_spain_w2_oth_fam$q6010e_other_s1, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- BeforeH1['2','2']
BeforeH[[2]] <- sum(sum(BeforeH1['1',]),sum(BeforeH1[c('-999','2'),'1'])) 
BeforeH[[3]] <- sum(sum(BeforeH1['-999',]),sum(BeforeH1['2','-999']))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


```{r save, echo=FALSE}
oth_fam <- COURAGE_ds_spain_w1
save(oth_fam, file = "../RData/spain_w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- COURAGE_ds_spain_w2
save(oth_fam, file = "../RData/spain_w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- COURAGE_ds_pol_w1
save(oth_fam, file = "../RData/pol_w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- COURAGE_ds_pol_w2
save(oth_fam, file = "../RData/pol_w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- COURAGE_ds_fin_w1
save(oth_fam, file = "../RData/fin_w1/oth_fam.RData")
rm(oth_fam)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


 
 


