---
title: "Frequency of face to face and phone contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_cont_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_cont_frDS.R')
```

# Data process


## Finland

### Wave 1 

#### Study-specific variable description


| **Name** |`q6010g_friends`|`q6217_friends`|
|-|-|-|
| **Label** |`Friends?`|`Friends face-to-face`|
| **Table name** |`Courage_Finland_w1`|`Courage_Finland_w1`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Never`<br/>`2 = Once/few times per year`<br/>`3 = Once/few times per month`<br/>`4 = Once/few times per week`<br/>`5 = Daily`|
| **Missings** |  |`8`<br/>`9 = NA`|
| **Description** |  |


```{r assign1_fin, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q6010g_friends','q6217_friends'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
```

```{r local1_fin, echo=F}
vbl <- COURAGE_fin_w1$q6217_friends
vbl_miss <-c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "q6217_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")
vbl <- COURAGE_fin_w1$q6010g_friends
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6010g_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217_friends=1 or q6010g_friends=2 into 5`
* `q6217_friends=2 into 4`
* `q6217_friends=3 into 3`
* `q6217_friends=4 into 2`
* `q6217_friends=5 into 1`
* `q6217_friends=9 or 8 or NA into 999`

**R script:**

```{r harmo1_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)

COURAGE_fin_w1$q6010g_friends <- car::recode(as.vector(COURAGE_fin_w1$q6010g_friends), "NA='-999'")
COURAGE_fin_w1$q6217_friends <- car::recode(as.vector(COURAGE_fin_w1$q6217_friends), "NA='-999'")

COURAGE_ds_fin_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(COURAGE_fin_w1)[1]){
  if( COURAGE_fin_w1$q6217_friends[i] == 1 | COURAGE_fin_w1$q6010g_friends[i] == 2 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 5 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 2 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 4 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 3 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 3 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 4 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 2 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 5 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 1 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 8 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 999 }
  else if( COURAGE_fin_w1$q6217_friends[i] == 9 ) { 
    COURAGE_ds_fin_w1$f_cont_fr[i] = 999 }
}

COURAGE_ds_fin_w1$f_cont_fr <- car::recode(as.vector(COURAGE_ds_fin_w1$f_cont_fr), "NA='999'")
COURAGE_ds_fin_w1$f_cont_fr <- labelled(COURAGE_ds_fin_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_fin, echo=F}
vbl <- COURAGE_ds_fin_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_fin, echo=F}

```



## Poland

### Wave 1 

#### Study-specific variable description


| **Name** |`q6010g_friends`|`q6217_friends`|
|-|-|-|
| **Label** |`Friends?`|`Friends face-to-face`|
| **Table name** |`Courage_Poland_w1`|`Courage_Poland_w1`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Never`<br/>`2 = Once/few times per year`<br/>`3 = Once/few times per month`<br/>`4 = Once/few times per week`<br/>`5 = Daily`|
| **Missings** |`NA`|`NA`|
| **Description** |  |
    

```{r assign1_pol, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q6010g_friends','q6217_friends'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
```

```{r local1_pol, echo=F}
vbl <- COURAGE_pol_w1$q6217_friends
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6217_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")
vbl <- COURAGE_pol_w1$q6010g_friends
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6010g_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217_friends=1 or q6010g_friends=2 into 5`
* `q6217_friends=2 into 4`
* `q6217_friends=3 into 3`
* `q6217_friends=4 into 2`
* `q6217_friends=5 into 1`
* `q6217_friends=NA into 999`

**R script:**

```{r harmo1_pol}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)

COURAGE_pol_w1$q6010g_friends <- car::recode(as.vector(COURAGE_pol_w1$q6010g_friends), "NA='-999'")
COURAGE_pol_w1$q6217_friends <- car::recode(as.vector(COURAGE_pol_w1$q6217_friends), "NA='-999'")

COURAGE_ds_pol_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(COURAGE_pol_w1)[1]){
  if( COURAGE_pol_w1$q6217_friends[i] == 1 | COURAGE_pol_w1$q6010g_friends[i] == 2 ) { 
    COURAGE_ds_pol_w1$f_cont_fr[i] = 5 }
  else if( COURAGE_pol_w1$q6217_friends[i] == 2 ) { 
    COURAGE_ds_pol_w1$f_cont_fr[i] = 4 }
  else if( COURAGE_pol_w1$q6217_friends[i] == 3 ) { 
    COURAGE_ds_pol_w1$f_cont_fr[i] = 3 }
  else if( COURAGE_pol_w1$q6217_friends[i] == 4 ) { 
    COURAGE_ds_pol_w1$f_cont_fr[i] = 2 }
  else if( COURAGE_pol_w1$q6217_friends[i] == 5 ) { 
    COURAGE_ds_pol_w1$f_cont_fr[i] = 1 }
}

COURAGE_ds_pol_w1$f_cont_fr <- car::recode(as.vector(COURAGE_ds_pol_w1$f_cont_fr), "NA='999'")
COURAGE_ds_pol_w1$f_cont_fr <- labelled(COURAGE_ds_pol_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_pol, echo=F}
vbl <- COURAGE_ds_pol_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_pol, echo=F}

```


### Wave 2 

#### Study-specific variable description



| **Name** |`q6010g_friends_s1`|`q6217_friends_s1`|
|-|-|-|
| **Label** |`Friends?`|`Friends face-to-face`|
| **Table name** |`Courage_Poland_w2`|`Courage_Poland_w2`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Never`<br/>`2 = Once/few times per year`<br/>`3 = Once/few times per month`<br/>`4 = Once/few times per week`<br/>`5 = Daily`|
| **Missings** |`NA`|`NA`|
| **Description** |  |
    


```{r assign2_pol, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',variables=list('q6010g_friends_s1','q6217_friends_s1'), missings = TRUE)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')
```

```{r local2_pol, echo=F}
vbl <- COURAGE_pol_w2$q6217_friends_s1
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6217_friends_s1")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q6217_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")
vbl <- COURAGE_pol_w2$q6218_neighbours
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6218_neighbours")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217_friends_s1=1 or q6010g_friends_s1=2 into 5`
* `q6217_friends_s1=2 into 4`
* `q6217_friends_s1=3 into 3`
* `q6217_friends_s1=4 into 2`
* `q6217_friends_s1=5 into 1`
* `q6217_friends_s1=NA into 999`

**R script:**

```{r harmo2_pol}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)

COURAGE_pol_w2$q6010g_friends_s1 <- car::recode(as.vector(COURAGE_pol_w2$q6010g_friends_s1), "NA='-999'")
COURAGE_pol_w2$q6217_friends_s1 <- car::recode(as.vector(COURAGE_pol_w2$q6217_friends_s1), "NA='-999'")

COURAGE_ds_pol_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(COURAGE_pol_w2)[1]){
  if( COURAGE_pol_w2$q6217_friends_s1[i] == 1 | COURAGE_pol_w2$q6010g_friends_s1[i] == 2 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 5 }
  else if( COURAGE_pol_w2$q6217_friends_s1[i] == 2 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 4 }
  else if( COURAGE_pol_w2$q6217_friends_s1[i] == 3 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 3 }
  else if( COURAGE_pol_w2$q6217_friends_s1[i] == 4 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 2 }
  else if( COURAGE_pol_w2$q6217_friends_s1[i] == 5 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 1 }
  else if( COURAGE_pol_w2$q6217_friends_s1[i] == 9 ) { 
    COURAGE_ds_pol_w2$f_cont_fr[i] = 999 }
}

COURAGE_ds_pol_w2$f_cont_fr <- car::recode(as.vector(COURAGE_ds_pol_w2$f_cont_fr), "NA='999'")
COURAGE_ds_pol_w2$f_cont_fr <- labelled(COURAGE_ds_pol_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_pol, echo=F}
vbl <- COURAGE_ds_pol_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_pol, echo=F}

```



## Spain

### Wave 1 

#### Study-specific variable description


| **Name** |`q6010g_friends`|`q6217_friends`|
|-|-|-|
| **Label** |`Friends?`|`Friends face-to-face`|
| **Table name** |`Courage_Spain_w1`|`Courage_Spain_w1`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Never`<br/>`2 = Once/few times per year`<br/>`3 = Once/few times per month`<br/>`4 = Once/few times per week`<br/>`5 = Daily`|
| **Missings** |`NA`|`NA`|
| **Description** |  |
    


```{r assign1_spain, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q6010g_friends','q6217_friends'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
```

```{r local1_spain, echo=F}
vbl <- COURAGE_spain_w1$q6217_friends
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6217_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")
vbl <- COURAGE_spain_w1$q6010g_friends
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6010g_friends")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217_friends=1 or q6010g_friends=2 into 5`
* `q6217_friends=2 into 4`
* `q6217_friends=3 into 3`
* `q6217_friends=4 into 2`
* `q6217_friends=5 into 1`
* `q6217_friends=NA into 999`

**R script:**

```{r harmo1_spain}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)

COURAGE_spain_w1$q6010g_friends <- car::recode(as.vector(COURAGE_spain_w1$q6010g_friends), "NA='-999'")
COURAGE_spain_w1$q6217_friends <- car::recode(as.vector(COURAGE_spain_w1$q6217_friends), "NA='-999'")

COURAGE_ds_spain_w1$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(COURAGE_spain_w1)[1]){
  if( COURAGE_spain_w1$q6217_friends[i] == 1 | COURAGE_spain_w1$q6010g_friends[i] == 2 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 5 }
  else if( COURAGE_spain_w1$q6217_friends[i] == 2 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 4 }
  else if( COURAGE_spain_w1$q6217_friends[i] == 3 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 3 }
  else if( COURAGE_spain_w1$q6217_friends[i] == 4 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 2 }
  else if( COURAGE_spain_w1$q6217_friends[i] == 5 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 1 }
  else if( COURAGE_spain_w1$q6217_friends[i] == 9 ) { 
    COURAGE_ds_spain_w1$f_cont_fr[i] = 999 }
}

COURAGE_ds_spain_w1$f_cont_fr <- car::recode(as.vector(COURAGE_ds_spain_w1$f_cont_fr), "NA='999'")
COURAGE_ds_spain_w1$f_cont_fr <- labelled(COURAGE_ds_spain_w1$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1_spain, echo=F}
vbl <- COURAGE_ds_spain_w1$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1_spain, echo=F}

```



### Wave 2 

#### Study-specific variable description


| **Name** |`q6010g_friends_s1`|`q6217_friends_s1`|
|-|-|-|
| **Label** |`Friends?`|`Friends face-to-face`|
| **Table name** |`Courage_Spain_w2_1`|`Courage_Spain_w2_1`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Never`<br/>`2 = Once/few times per year`<br/>`3 = Once/few times per month`<br/>`4 = Once/few times per week`<br/>`5 = Daily`|
| **Missings** |`NA`|`NA`|
| **Description** |  |
        

```{r assign2_spain, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q6010g_friends_s1','q6217_friends_s1'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
```

```{r local2_spain, echo=F}
vbl <- COURAGE_spain_w2$q6217_friends_s1
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6217_friends_s1")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q6217_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")
vbl <- COURAGE_spain_w2$q6218_neighbours
vbl_miss <-NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "q6218_neighbours")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217_friends_s1=1 or q6010g_friends_s1=2 into 5`
* `q6217_friends_s1=2 into 4`
* `q6217_friends_s1=3 into 3`
* `q6217_friends_s1=4 into 2`
* `q6217_friends_s1=5 into 1`
* `q6217_friends_s1=NA into 999`

**R script:**

```{r harmo2_spain}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)

COURAGE_spain_w2$q6010g_friends_s1 <- car::recode(as.vector(COURAGE_spain_w2$q6010g_friends_s1), "NA='-999'")
COURAGE_spain_w2$q6217_friends_s1 <- car::recode(as.vector(COURAGE_spain_w2$q6217_friends_s1), "NA='-999'")

COURAGE_ds_spain_w2$f_cont_fr <- c(NA) # I think it is required
for(i in 1:dim(COURAGE_spain_w2)[1]){
  if( COURAGE_spain_w2$q6217_friends_s1[i] == 1 | COURAGE_spain_w2$q6010g_friends_s1[i] == 2 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 5 }
  else if( COURAGE_spain_w2$q6217_friends_s1[i] == 2 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 4 }
  else if( COURAGE_spain_w2$q6217_friends_s1[i] == 3 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 3 }
  else if( COURAGE_spain_w2$q6217_friends_s1[i] == 4 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 2 }
  else if( COURAGE_spain_w2$q6217_friends_s1[i] == 5 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 1 }
  else if( COURAGE_spain_w2$q6217_friends_s1[i] == 9 ) { 
    COURAGE_ds_spain_w2$f_cont_fr[i] = 999 }
}

COURAGE_ds_spain_w2$f_cont_fr <- car::recode(as.vector(COURAGE_ds_spain_w2$f_cont_fr), "NA='999'")
COURAGE_ds_spain_w2$f_cont_fr <- labelled(COURAGE_ds_spain_w2$f_cont_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2_spain, echo=F}
vbl <- COURAGE_ds_spain_w2$f_cont_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(f_cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of face to face contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2_spain, echo=F}

```



## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
