---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_fr`
* Variable label: `Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6010g_friends`
* Label: `Friends?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6217_friends`
* Label: `Friends face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    
* Name: `q6010h_neighbours`
* Label: `Neighbours?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `q6218_neighbours`
* Label: `Neighbors face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
  
    

* Description: 
```{r assign1 fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_cont_fr','Courage.Courage_Finland_w1', 
                        variables=list('q6010g_friends','q6217_friends','q6010h_neighbours','q6218_neighbours'), missings = TRUE)
```

```{r local1 fin}
COURAGE_fin_w1_cont_fr <- opal.execute(o,'COURAGE_fin_w1_cont_fr')

vari <- COURAGE_fin_w1_cont_fr$q6217_friends
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_fin_w1_cont_fr$q6217_friends, missing_values = NA)
ggplot(COURAGE_fin_w1_cont_fr, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")

vari <- COURAGE_fin_w1_cont_fr$q6218_neighbours
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_fin_w1_cont_fr$q6218_neighbours, missing_values = NA)
ggplot(COURAGE_fin_w1_cont_fr, aes(x=factor(q6218_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Neighbors face-to-face") + ylab("Frequency")

vari <- COURAGE_fin_w1_cont_fr$q6010g_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_cont_fr$q6010g_friends, missing_values = NA)
ggplot(COURAGE_fin_w1_cont_fr, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

vari <- COURAGE_fin_w1_cont_fr$q6010h_neighbours
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_cont_fr$q6010h_neighbours, missing_values = NA)
ggplot(COURAGE_fin_w1_cont_fr, aes(x=factor(q6010h_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has neighbours?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217 in (1,2) AND q6218 in (1,2) then 0`
* `q6010g=2 AND q6218 in (1,2) then 0`
* `q6217 in (1,2) AND q6010h=2 then 0`
* `q6217 in (3,4,5) OR q6218 in (3,4,5) into 1`
* `q6010g=2 AND q6010h=2 INTO 996`
* `q6217 = 9 OR q6218 = 9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1 fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_cont_fr$id)

COURAGE_fin_w1_cont_fr$q6010g_friends <- car::recode(as.vector(COURAGE_fin_w1_cont_fr$q6010g_friends), "NA='-999'")
COURAGE_fin_w1_cont_fr$q6010h_neighbours <- car::recode(as.vector(COURAGE_fin_w1_cont_fr$q6010h_neighbours), "NA='-999'")
COURAGE_fin_w1_cont_fr$q6217_friends <- car::recode(as.vector(COURAGE_fin_w1_cont_fr$q6217_friends), "NA='-999'")
COURAGE_fin_w1_cont_fr$q6218_neighbours <- car::recode(as.vector(COURAGE_fin_w1_cont_fr$q6218_neighbours), "NA='-999'")

COURAGE_ds_fin_w1$cont_fr <- c(NA)  
for(i in 1:dim(COURAGE_fin_w1_cont_fr)[1]){
  if( COURAGE_fin_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_fin_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_fin_w1$cont_fr[i] = 0 }
  else if( COURAGE_fin_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_fin_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_fin_w1$cont_fr[i] = 0 }
  else if( COURAGE_fin_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_fin_w1_cont_fr$q6010h_neighbours[i] == 2 ) { 
    COURAGE_ds_fin_w1$cont_fr[i] = 0 }
  else if(COURAGE_fin_w1_cont_fr$q6217_friends[i] %in% c(3,4,5) | COURAGE_fin_w1_cont_fr$q6218_neighbours[i] %in% c(3,4,5) ){ 
    COURAGE_ds_fin_w1$cont_fr[i] = 1 }
  else if(COURAGE_fin_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_fin_w1_cont_fr$q6010h_neighbours[i] == 2 ){
    COURAGE_ds_fin_w1$cont_fr[i] = 996 }
  else if(COURAGE_fin_w1_cont_fr$q6217_friends[i] == 9 | COURAGE_fin_w1_cont_fr$q6218_neighbours[i] == 9 ){ 
    COURAGE_ds_fin_w1$cont_fr[i] = 996 }
}

COURAGE_ds_fin_w1$cont_fr <- car::recode(as.vector(COURAGE_ds_fin_w1$cont_fr), "NA='999'")
COURAGE_ds_fin_w1$cont_fr <- labelled(COURAGE_ds_fin_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 fin}
vari <- COURAGE_ds_fin_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 fin}

```

 
 



## Polish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6217_friends`
* Label: `Friends face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    
* Name: `q6218_neighbours`
* Label: `Neighbors face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    

* Description: 
```{r assign1 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_cont_fr','Courage.Courage_Poland_w1', 
                        variables=list('q6010g_friends','q6217_friends','q6010h_neighbours','q6218_neighbours'), missings = TRUE)
```

```{r local1 pol}
COURAGE_pol_w1_cont_fr <- opal.execute(o,'COURAGE_pol_w1_cont_fr')

vari <- COURAGE_pol_w1_cont_fr$q6217_friends
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w1_cont_fr$q6217_friends, missing_values = NA)
ggplot(COURAGE_pol_w1_cont_fr, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")

vari <- COURAGE_pol_w1_cont_fr$q6218_neighbours
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w1_cont_fr$q6218_neighbours, missing_values = NA)
ggplot(COURAGE_pol_w1_cont_fr, aes(x=factor(q6218_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Neighbors face-to-face") + ylab("Frequency")

vari <- COURAGE_pol_w1_cont_fr$q6010g_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_cont_fr$q6010g_friends, missing_values = NA)
ggplot(COURAGE_pol_w1_cont_fr, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

vari <- COURAGE_pol_w1_cont_fr$q6010h_neighbours
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_cont_fr$q6010h_neighbours, missing_values = NA)
ggplot(COURAGE_pol_w1_cont_fr, aes(x=factor(q6010h_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has neighbours?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217 in (1,2) AND q6218 in (1,2) then 0`
* `q6010g=2 AND q6218 in (1,2) then 0`
* `q6217 in (1,2) AND q6010h=2 then 0`
* `q6217 in (3,4,5) OR q6218 in (3,4,5) into 1`
* `q6010g=2 AND q6010h=2 INTO 996`
* `q6217 = 9 OR q6218 = 9 into 996`
* `NA into 999`

**R script:** 

```{r harmo1 pol, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_cont_fr$id)

COURAGE_pol_w1_cont_fr$q6010g_friends <- car::recode(as.vector(COURAGE_pol_w1_cont_fr$q6010g_friends), "NA='-999'")
COURAGE_pol_w1_cont_fr$q6010h_neighbours <- car::recode(as.vector(COURAGE_pol_w1_cont_fr$q6010h_neighbours), "NA='-999'")
COURAGE_pol_w1_cont_fr$q6217_friends <- car::recode(as.vector(COURAGE_pol_w1_cont_fr$q6217_friends), "NA='-999'")
COURAGE_pol_w1_cont_fr$q6218_neighbours <- car::recode(as.vector(COURAGE_pol_w1_cont_fr$q6218_neighbours), "NA='-999'")

COURAGE_ds_pol_w1$cont_fr <- c(NA)  
for(i in 1:dim(COURAGE_pol_w1_cont_fr)[1]){
  if( COURAGE_pol_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_pol_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_pol_w1$cont_fr[i] = 0 }
  else if( COURAGE_pol_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_pol_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_pol_w1$cont_fr[i] = 0 }
  else if( COURAGE_pol_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_pol_w1_cont_fr$q6010h_neighbours[i] == 2 ) { 
    COURAGE_ds_pol_w1$cont_fr[i] = 0 }
  else if(COURAGE_pol_w1_cont_fr$q6217_friends[i] %in% c(3,4,5) | COURAGE_pol_w1_cont_fr$q6218_neighbours[i] %in% c(3,4,5) ){ 
    COURAGE_ds_pol_w1$cont_fr[i] = 1 }
  else if(COURAGE_pol_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_pol_w1_cont_fr$q6010h_neighbours[i] == 2 ){
    COURAGE_ds_pol_w1$cont_fr[i] = 996 }
  else if(COURAGE_pol_w1_cont_fr$q6217_friends[i] == 9 | COURAGE_pol_w1_cont_fr$q6218_neighbours[i] == 9 ){ 
    COURAGE_ds_pol_w1$cont_fr[i] = 996 }
}

COURAGE_ds_pol_w1$cont_fr <- car::recode(as.vector(COURAGE_ds_pol_w1$cont_fr), "NA='999'")
COURAGE_ds_pol_w1$cont_fr <- labelled(COURAGE_ds_pol_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol}
vari <- COURAGE_ds_pol_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol}

```

 
 



### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6217_friends_s1`
* Label: `Friends face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    
* Name: `q6218_neighbours_s1`
* Label: `Neighbors face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    

* Description: 
```{r assign2 pol}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_cont_fr','Courage.Courage_Poland_w2', 
                        variables=list('q6010g_friends_s1','q6217_friends_s1','q6010h_neighbours_s1','q6218_neighbours_s1'), missings = TRUE)
```

```{r local2 pol}
COURAGE_pol_w2_cont_fr <- opal.execute(o,'COURAGE_pol_w2_cont_fr')

vari <- COURAGE_pol_w2_cont_fr$q6217_friends_s1
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w2_cont_fr$q6217_friends_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_cont_fr, aes(x=factor(q6217_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")

vari <- COURAGE_pol_w2_cont_fr$q6218_neighbours_s1
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w2_cont_fr$q6218_neighbours_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_cont_fr, aes(x=factor(q6218_neighbours_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Neighbors face-to-face") + ylab("Frequency")

vari <- COURAGE_pol_w2_cont_fr$q6010g_friends_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_cont_fr$q6010g_friends_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_cont_fr, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

vari <- COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_cont_fr, aes(x=factor(q6010h_neighbours_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has neighbours?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217 in (1,2) AND q6218 in (1,2) then 0`
* `q6010g=2 AND q6218 in (1,2) then 0`
* `q6217 in (1,2) AND q6010h=2 then 0`
* `q6217 in (3,4,5) OR q6218 in (3,4,5) into 1`
* `q6010g=2 AND q6010h=2 INTO 996`
* `q6217 = 9 OR q6218 = 9 into 996`
* `NA into 999`

**R script:** 

```{r harmo2 pol, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_cont_fr$id)

COURAGE_pol_w2_cont_fr$q6010g_friends_s1 <- car::recode(as.vector(COURAGE_pol_w2_cont_fr$q6010g_friends_s1), "NA='-999'")
COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1 <- car::recode(as.vector(COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1), "NA='-999'")
COURAGE_pol_w2_cont_fr$q6217_friends_s1 <- car::recode(as.vector(COURAGE_pol_w2_cont_fr$q6217_friends_s1), "NA='-999'")
COURAGE_pol_w2_cont_fr$q6218_neighbours_s1 <- car::recode(as.vector(COURAGE_pol_w2_cont_fr$q6218_neighbours_s1), "NA='-999'")

COURAGE_ds_pol_w2$cont_fr <- c(NA)  
for(i in 1:dim(COURAGE_pol_w2_cont_fr)[1]){
  if( COURAGE_pol_w2_cont_fr$q6217_friends_s1[i] %in% c(1,2) & COURAGE_pol_w2_cont_fr$q6218_neighbours_s1[i] %in% c(1,2) ) { 
    COURAGE_ds_pol_w2$cont_fr[i] = 0 }
  else if( COURAGE_pol_w2_cont_fr$q6010g_friends_s1[i] == 2 & COURAGE_pol_w2_cont_fr$q6218_neighbours_s1[i] %in% c(1,2) ) { 
    COURAGE_ds_pol_w2$cont_fr[i] = 0 }
  else if( COURAGE_pol_w2_cont_fr$q6217_friends_s1[i] %in% c(1,2) & COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1[i] == 2 ) { 
    COURAGE_ds_pol_w2$cont_fr[i] = 0 }
  else if(COURAGE_pol_w2_cont_fr$q6217_friends_s1[i] %in% c(3,4,5) | COURAGE_pol_w2_cont_fr$q6218_neighbours_s1[i] %in% c(3,4,5) ){ 
    COURAGE_ds_pol_w2$cont_fr[i] = 1 }
  else if(COURAGE_pol_w2_cont_fr$q6010g_friends_s1[i] == 2 & COURAGE_pol_w2_cont_fr$q6010h_neighbours_s1[i] == 2 ){
    COURAGE_ds_pol_w2$cont_fr[i] = 996 }
  else if(COURAGE_pol_w2_cont_fr$q6217_friends_s1[i] == 9 | COURAGE_pol_w2_cont_fr$q6218_neighbours_s1[i] == 9 ){ 
    COURAGE_ds_pol_w2$cont_fr[i] = 996 }
}

COURAGE_ds_pol_w2$cont_fr <- car::recode(as.vector(COURAGE_ds_pol_w2$cont_fr), "NA='999'")
COURAGE_ds_pol_w2$cont_fr <- labelled(COURAGE_ds_pol_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 pol}
vari <- COURAGE_ds_pol_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 pol}

```

 
 


## Spanish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6217_friends`
* Label: `Friends face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    
* Name: `q6218_neighbours`
* Label: `Neighbors face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    

* Description: 
```{r assign1 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_cont_fr','Courage.Courage_Spain_w1', 
                        variables=list('q6010g_friends','q6217_friends','q6010h_neighbours','q6218_neighbours'), missings = TRUE)
```

```{r local1 spain}
COURAGE_spain_w1_cont_fr <- opal.execute(o,'COURAGE_spain_w1_cont_fr')

vari <- COURAGE_spain_w1_cont_fr$q6217_friends
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w1_cont_fr$q6217_friends, missing_values = NA)
ggplot(COURAGE_spain_w1_cont_fr, aes(x=factor(q6217_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")

vari <- COURAGE_spain_w1_cont_fr$q6218_neighbours
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w1_cont_fr$q6218_neighbours, missing_values = NA)
ggplot(COURAGE_spain_w1_cont_fr, aes(x=factor(q6218_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Neighbors face-to-face") + ylab("Frequency")

vari <- COURAGE_spain_w1_cont_fr$q6010g_friends 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_cont_fr$q6010g_friends, missing_values = NA)
ggplot(COURAGE_spain_w1_cont_fr, aes(x=factor(q6010g_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

vari <- COURAGE_spain_w1_cont_fr$q6010h_neighbours
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_cont_fr$q6010h_neighbours, missing_values = NA)
ggplot(COURAGE_spain_w1_cont_fr, aes(x=factor(q6010h_neighbours))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has neighbours?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217 in (1,2) AND q6218 in (1,2) then 0`
* `q6010g=2 AND q6218 in (1,2) then 0`
* `q6217 in (1,2) AND q6010h=2 then 0`
* `q6217 in (3,4,5) OR q6218 in (3,4,5) into 1`
* `q6010g=2 AND q6010h=2 INTO 996`
* `q6217 = 9 OR q6218 = 9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1 spain, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_cont_fr$id)

COURAGE_spain_w1_cont_fr$q6010g_friends <- car::recode(as.vector(COURAGE_spain_w1_cont_fr$q6010g_friends), "NA='-999'")
COURAGE_spain_w1_cont_fr$q6010h_neighbours <- car::recode(as.vector(COURAGE_spain_w1_cont_fr$q6010h_neighbours), "NA='-999'")
COURAGE_spain_w1_cont_fr$q6217_friends <- car::recode(as.vector(COURAGE_spain_w1_cont_fr$q6217_friends), "NA='-999'")
COURAGE_spain_w1_cont_fr$q6218_neighbours <- car::recode(as.vector(COURAGE_spain_w1_cont_fr$q6218_neighbours), "NA='-999'")

COURAGE_ds_spain_w1$cont_fr <- c(NA)  
for(i in 1:dim(COURAGE_spain_w1_cont_fr)[1]){
  if( COURAGE_spain_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_spain_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_spain_w1$cont_fr[i] = 0 }
  else if( COURAGE_spain_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_spain_w1_cont_fr$q6218_neighbours[i] %in% c(1,2) ) { 
    COURAGE_ds_spain_w1$cont_fr[i] = 0 }
  else if( COURAGE_spain_w1_cont_fr$q6217_friends[i] %in% c(1,2) & COURAGE_spain_w1_cont_fr$q6010h_neighbours[i] == 2 ) { 
    COURAGE_ds_spain_w1$cont_fr[i] = 0 }
  else if(COURAGE_spain_w1_cont_fr$q6217_friends[i] %in% c(3,4,5) | COURAGE_spain_w1_cont_fr$q6218_neighbours[i] %in% c(3,4,5) ){ 
    COURAGE_ds_spain_w1$cont_fr[i] = 1 }
  else if(COURAGE_spain_w1_cont_fr$q6010g_friends[i] == 2 & COURAGE_spain_w1_cont_fr$q6010h_neighbours[i] == 2 ){
    COURAGE_ds_spain_w1$cont_fr[i] = 996 }
  else if(COURAGE_spain_w1_cont_fr$q6217_friends[i] == 9 | COURAGE_spain_w1_cont_fr$q6218_neighbours[i] == 9 ){ 
    COURAGE_ds_spain_w1$cont_fr[i] = 996 }
}

COURAGE_ds_spain_w1$cont_fr <- car::recode(as.vector(COURAGE_ds_spain_w1$cont_fr), "NA='999'")
COURAGE_ds_spain_w1$cont_fr <- labelled(COURAGE_ds_spain_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript1 spain}
vari <- COURAGE_ds_spain_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 spain}

```

 
 



### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q6217_friends_s1`
* Label: `Friends face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    
* Name: `q6218_neighbours_s1`
* Label: `Neighbors face-to-face`
* Categories:
    + `1 = Never`
    + `2 = Once/few times per year`
    + `3 = Once/few times per month`
    + `4 = Once/few times per week`
    + `5 = Daily`
* Missings:
    + `9 = NA`
    

* Description: 
```{r assign2 spain}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_cont_fr','Courage.Courage_Spain_w2_1', 
                        variables=list('q6010g_friends_s1','q6217_friends_s1','q6010h_neighbours_s1','q6218_neighbours_s1'), missings = TRUE)
```

```{r local2 spain}
COURAGE_spain_w2_cont_fr <- opal.execute(o,'COURAGE_spain_w2_cont_fr')
vari <- COURAGE_spain_w2_cont_fr$q6217_friends_s1
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w2_cont_fr$q6217_friends_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_cont_fr, aes(x=factor(q6217_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Friends face-to-face") + ylab("Frequency")

vari <- COURAGE_spain_w2_cont_fr$q6218_neighbours_s1
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w2_cont_fr$q6218_neighbours_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_cont_fr, aes(x=factor(q6218_neighbours_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Neighbors face-to-face") + ylab("Frequency")

vari <- COURAGE_spain_w2_cont_fr$q6010g_friends_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_cont_fr$q6010g_friends_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_cont_fr, aes(x=factor(q6010g_friends_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")
vari <- COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_cont_fr, aes(x=factor(q6010h_neighbours_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has neighbours?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q6217 in (1,2) AND q6218 in (1,2) then 0`
* `q6010g=2 AND q6218 in (1,2) then 0`
* `q6217 in (1,2) AND q6010h=2 then 0`
* `q6217 in (3,4,5) OR q6218 in (3,4,5) into 1`
* `q6010g=2 AND q6010h=2 INTO 996`
* `q6217 = 9 OR q6218 = 9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo2 spain, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_cont_fr$id)

COURAGE_spain_w2_cont_fr$q6010g_friends_s1 <- car::recode(as.vector(COURAGE_spain_w2_cont_fr$q6010g_friends_s1), "NA='-999'")
COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1 <- car::recode(as.vector(COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1), "NA='-999'")
COURAGE_spain_w2_cont_fr$q6217_friends_s1 <- car::recode(as.vector(COURAGE_spain_w2_cont_fr$q6217_friends_s1), "NA='-999'")
COURAGE_spain_w2_cont_fr$q6218_neighbours_s1 <- car::recode(as.vector(COURAGE_spain_w2_cont_fr$q6218_neighbours_s1), "NA='-999'")

COURAGE_ds_spain_w2$cont_fr <- c(NA)  
for(i in 1:dim(COURAGE_spain_w2_cont_fr)[1]){
  if( COURAGE_spain_w2_cont_fr$q6217_friends_s1[i] %in% c(1,2) & COURAGE_spain_w2_cont_fr$q6218_neighbours_s1[i] %in% c(1,2) ) { 
    COURAGE_ds_spain_w2$cont_fr[i] = 0 }
  else if( COURAGE_spain_w2_cont_fr$q6010g_friends_s1[i] == 2 & COURAGE_spain_w2_cont_fr$q6218_neighbours_s1[i] %in% c(1,2) ) { 
    COURAGE_ds_spain_w2$cont_fr[i] = 0 }
  else if( COURAGE_spain_w2_cont_fr$q6217_friends_s1[i] %in% c(1,2) & COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1[i] == 2 ) { 
    COURAGE_ds_spain_w2$cont_fr[i] = 0 }
  else if(COURAGE_spain_w2_cont_fr$q6217_friends_s1[i] %in% c(3,4,5) | COURAGE_spain_w2_cont_fr$q6218_neighbours_s1[i] %in% c(3,4,5) ){ 
    COURAGE_ds_spain_w2$cont_fr[i] = 1 }
  else if(COURAGE_spain_w2_cont_fr$q6010g_friends_s1[i] == 2 & COURAGE_spain_w2_cont_fr$q6010h_neighbours_s1[i] == 2 ){
    COURAGE_ds_spain_w2$cont_fr[i] = 996 }
  else if(COURAGE_spain_w2_cont_fr$q6217_friends_s1[i] == 9 | COURAGE_spain_w2_cont_fr$q6218_neighbours_s1[i] == 9 ){ 
    COURAGE_ds_spain_w2$cont_fr[i] = 996 }
}

COURAGE_ds_spain_w2$cont_fr <- car::recode(as.vector(COURAGE_ds_spain_w2$cont_fr), "NA='999'")
COURAGE_ds_spain_w2$cont_fr <- labelled(COURAGE_ds_spain_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991 ))
```

#### Statistical description of the new harmonised variable
```{r descript2 spain}
vari <- COURAGE_ds_spain_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 spain}

```

 
```{r save, echo=FALSE}
cont_fr <- COURAGE_ds_spain_w1
save(cont_fr, file = "../RData/spain_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- COURAGE_ds_spain_w2
save(cont_fr, file = "../RData/spain_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- COURAGE_ds_pol_w1
save(cont_fr, file = "../RData/pol_w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- COURAGE_ds_pol_w2
save(cont_fr, file = "../RData/pol_w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- COURAGE_ds_fin_w1
save(cont_fr, file = "../RData/fin_w1/cont_fr.RData")
rm(cont_fr)
```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

