---
title: "Political activity - involving (membership to a political organisation, participation in political meetings/events etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/pol_actDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/pol_actDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst 


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome234`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_pol_act','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('tome234'), missings = TRUE)
```

```{r local1 5, echo=F}
JSTAR_aksst_w1_pol_act <- opal.execute(o,'JSTAR_aksst_w1_pol_act')
vari <- JSTAR_aksst_w1_pol_act$tome234
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_pol_act$tome234, missing_values = NA)
ggplot(JSTAR_aksst_w1_pol_act, aes(x=factor(tome234))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 5, echo=TRUE}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_pol_act$id)
JSTAR_ds_aksst_w1$pol_act <- car::recode(as.vector(JSTAR_aksst_w1_pol_act$tome234), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_aksst_w1$pol_act <- labelled(JSTAR_ds_aksst_w1$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 5, echo=F}
vari <- JSTAR_ds_aksst_w1$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w1$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5, echo=F}

```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome250`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_pol_act','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('tome250'), missings = TRUE)
```

```{r local2 5, echo=F}
JSTAR_aksst_w2_pol_act <- opal.execute(o,'JSTAR_aksst_w2_pol_act')
vari <- JSTAR_aksst_w2_pol_act$tome250
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w2_pol_act$tome250, missing_values = NA)
ggplot(JSTAR_aksst_w2_pol_act, aes(x=factor(tome250))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 5, echo=TRUE}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_pol_act$id)
JSTAR_ds_aksst_w2$pol_act <- car::recode(as.vector(JSTAR_aksst_w2_pol_act$tome250), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_aksst_w2$pol_act <- labelled(JSTAR_ds_aksst_w2$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 5, echo=F}
vari <- JSTAR_ds_aksst_w2$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w2$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 5, echo=F}

```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q17_1_5`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign3 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_pol_act','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('q17_1_5'), missings = TRUE)
```

```{r local3 5, echo=F}
JSTAR_aksst_w3_pol_act <- opal.execute(o,'JSTAR_aksst_w3_pol_act')
vari <- JSTAR_aksst_w3_pol_act$q17_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_pol_act$q17_1_5, missing_values = NA)
ggplot(JSTAR_aksst_w3_pol_act, aes(x=factor(q17_1_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo3 5, echo=TRUE}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_pol_act$id)
JSTAR_ds_aksst_w3$pol_act <- car::recode(as.vector(JSTAR_aksst_w3_pol_act$q17_1_5), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_aksst_w3$pol_act <- labelled(JSTAR_ds_aksst_w3$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 5, echo=F}
vari <- JSTAR_ds_aksst_w3$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w3$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3 5, echo=F}

```

 
 


## tn
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome234`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_pol_act','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('tome234'), missings = TRUE)
```

```{r local1 2, echo=F}
JSTAR_tn_w1_pol_act <- opal.execute(o,'JSTAR_tn_w1_pol_act')
vari <- JSTAR_tn_w1_pol_act$tome234
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_pol_act$tome234, missing_values = NA)
ggplot(JSTAR_tn_w1_pol_act, aes(x=factor(tome234))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_pol_act$id)
JSTAR_ds_tn_w1$pol_act <- car::recode(as.vector(JSTAR_tn_w1_pol_act$tome234), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_tn_w1$pol_act <- labelled(JSTAR_ds_tn_w1$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 2, echo=F}
vari <- JSTAR_ds_tn_w1$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w1$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w1, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2, echo=F}

```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q17_1_5`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_pol_act','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('q17_1_5'), missings = TRUE)
```

```{r local2 2, echo=F}
JSTAR_tn_w2_pol_act <- opal.execute(o,'JSTAR_tn_w2_pol_act')
vari <- JSTAR_tn_w2_pol_act$q17_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_pol_act$q17_1_5, missing_values = NA)
ggplot(JSTAR_tn_w2_pol_act, aes(x=factor(q17_1_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 2, echo=TRUE}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_pol_act$id)
JSTAR_ds_tn_w2$pol_act <- car::recode(as.vector(JSTAR_tn_w2_pol_act$q17_1_5), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_tn_w2$pol_act <- labelled(JSTAR_ds_tn_w2$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2, echo=F}
vari <- JSTAR_ds_tn_w2$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w2$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w2, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 2, echo=F}

```

 
 



## cth
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q24_1_5`
* Label: `In the past month, have you done non-work activities with anyone other thanfamily or friends? Q24-1:WHAT ARE THOSE ACTIVITIES? -5- POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_pol_act','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('q24_1_5'), missings = TRUE)
```

```{r local1 3, echo=F}
JSTAR_cth_w1_pol_act <- opal.execute(o,'JSTAR_cth_w1_pol_act')
vari <- JSTAR_cth_w1_pol_act$q24_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_cth_w1_pol_act$q24_1_5, missing_values = NA)
ggplot(JSTAR_cth_w1_pol_act, aes(x=factor(q24_1_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity in political organization (in the past month)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_pol_act$id)
JSTAR_ds_cth_w1$pol_act <- car::recode(as.vector(JSTAR_cth_w1_pol_act$q24_1_5), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_cth_w1$pol_act <- labelled(JSTAR_ds_cth_w1$pol_act, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 3, echo=F}
vari <- JSTAR_ds_cth_w1$pol_act
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_cth_w1$pol_act, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_cth_w1, aes(x=factor(pol_act))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Political activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3, echo=F}

```

 
 
 
 

## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W1", "AKSST_W2", "AKSST_W3", "TN_W1", "TN_W2", "CTH_W1")
kable(t.hds)

```



 


```{r save, echo=FALSE}
pol_act <- JSTAR_ds_tn_w1
save(pol_act, file = "../RData/tn_w1/pol_act.RData")
rm(pol_act)

# pol_act <- JSTAR_ds_tn_w2
# save(pol_act, file = "../RData/tn_w2/pol_act.RData")
# rm(pol_act)

pol_act <- JSTAR_ds_aksst_w1
save(pol_act, file = "../RData/aksst_w1/pol_act.RData")
rm(pol_act)

pol_act <- JSTAR_ds_aksst_w2
save(pol_act, file = "../RData/aksst_w2/pol_act.RData")
rm(pol_act)

pol_act <- JSTAR_ds_aksst_w3
save(pol_act, file = "../RData/aksst_w3/pol_act.RData")
rm(pol_act)


pol_act <- JSTAR_ds_cth_w1
save(pol_act, file = "../RData/cth_w1/pol_act.RData")
rm(pol_act)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
