---
title: "Sport Activities"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sportDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sportDS.R')
```

<!-- ########################################################## --> 


# Data process

## aksst

### Wave 1 

#### Study-specific variable description



| **Name** | `	tome237`|`tome229`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE, SPORTS, TAKING A WALK-`|`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`|
| **Table name** |`jstar_2007_5cities`|`jstar_2007_5cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign1 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_sport','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('tome229','tome237'), missings = TRUE)
JSTAR_aksst_w1_sport <- opal.execute(o,'JSTAR_aksst_w1_sport')
```

```{r local1 5, echo=F}
vari <- JSTAR_aksst_w1_sport$tome229
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(JSTAR_aksst_w1_sport, aes(x=factor(tome229))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


vari <- JSTAR_aksst_w1_sport$tome237
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_sport, aes(x=factor(tome237))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `tome229 == 2 into 0`
* `tome229 == 3 into 998`
* `tome237 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo1 5, echo=TRUE}

JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_sport$id)
JSTAR_ds_aksst_w1$sport <- car::recode(as.vector(JSTAR_aksst_w1_sport$tome229), "2='0'; 3='998'; NA='999'; 1 = 999")
JSTAR_ds_aksst_w1$sport[which(JSTAR_aksst_w1_sport$tome237 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript1 5, echo=F}
vari <- JSTAR_ds_aksst_w1$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(JSTAR_ds_aksst_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5, echo=F}

```

 
 



### Wave 2

#### Study-specific variable description



| **Name** | `tome253`|`tome245`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS-`|`Q21:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`|
| **Table name** |`jstar_2009_5cities`|`jstar_2009_5cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign2 5, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2_sport','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('tome245','tome253'), missings = TRUE)
JSTAR_aksst_w2_sport <- opal.execute(o,'JSTAR_aksst_w2_sport')

```

```{r local2 5, echo=F}

vari <- JSTAR_aksst_w2_sport$tome245
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_sport, aes(x=factor(tome245))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w2_sport$tome253
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_sport, aes(x=factor(tome253))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `tome245 == 2 into 0`
* `tome245 == 3 into 998`
* `tome253 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo2 5, echo=TRUE}

JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_sport$id)
JSTAR_ds_aksst_w2$sport <- car::recode(as.vector(JSTAR_aksst_w2_sport$tome245), "1='999'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_aksst_w2$sport[which(JSTAR_aksst_w2_sport$tome253 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript2 5, echo=F}
vari <- JSTAR_ds_aksst_w2$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 5, echo=F}

```

 
 



### Wave 3

#### Study-specific variable description



| **Name** | `q17_1_8`|`q17`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS-`|`11Q17:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS FOR A MONTH`|
| **Table name** |`jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign3 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_sport','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('q17','q17_1_8'), missings = TRUE)
JSTAR_aksst_w3_sport <- opal.execute(o,'JSTAR_aksst_w3_sport')
```

```{r local3 5, echo=F}

vari <- JSTAR_aksst_w3_sport$q17
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_sport, aes(x=factor(q17))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w3_sport$q17_1_8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_sport, aes(x=factor(q17_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `q17 == 2 into 0`
* `q17 == 3 into 998`
* `q17_1_8 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo3 5, echo=TRUE}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_sport$id)
JSTAR_ds_aksst_w3$sport <- car::recode(as.vector(JSTAR_aksst_w3_sport$q17), "1='999'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_aksst_w3$sport[which(JSTAR_aksst_w3_sport$q17_1_8 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript3 5, echo=F}
vari <- JSTAR_ds_aksst_w3$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3 5, echo=F}

```

 
 


## tn

### Wave 1 

#### Study-specific variable description



| **Name** | `tome237`|`tome229`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`|`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`|
| **Table name** |`jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign1 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_sport','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('tome229','tome237'), missings = TRUE)
JSTAR_tn_w1_sport <- opal.execute(o,'JSTAR_tn_w1_sport')
```

```{r local1 2, echo=F}

vari <- JSTAR_tn_w1_sport$tome229
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_sport, aes(x=factor(tome229))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w1_sport$tome237
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_sport, aes(x=factor(tome237))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `tome229 == 2 into 0`
* `tome229 == 3 into 998`
* `tome237 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_sport$id)
JSTAR_ds_tn_w1$sport <- car::recode(as.vector(JSTAR_tn_w1_sport$tome229), "1='999'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_tn_w1$sport[which(JSTAR_tn_w1_sport$tome237 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript1 2, echo=F}
vari <- JSTAR_ds_tn_w1$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(JSTAR_ds_tn_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2, echo=F}

```

 
 



### Wave 2

#### Study-specific variable description



| **Name** | `q17_1_8`|`q17`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`|`11Q17:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS FOR A MONTH`|
| **Table name** |`jstar_2011_2cities`|`jstar_2011_2cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign2 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_sport','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('q17','q17_1_8'), missings = TRUE)
JSTAR_tn_w2_sport <- opal.execute(o,'JSTAR_tn_w2_sport')
```

```{r local2 2, echo=F}

vari <- JSTAR_tn_w2_sport$q17
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_sport, aes(x=factor(q17_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w2_sport$q17
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_sport, aes(x=factor(q17_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `q17 == 2 into 0`
* `q17 == 3 into 998`
* `q17_1_8 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo2 2, echo=TRUE}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_sport$id)
JSTAR_ds_tn_w2$sport <- car::recode(as.vector(JSTAR_tn_w2_sport$q17), "1='999'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_tn_w2$sport[which(JSTAR_tn_w2_sport$q17_1_8 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript2 2, echo=F}
vari <- JSTAR_ds_tn_w2$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(JSTAR_ds_tn_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 2, echo=F}

```

 
 


## cth
### Wave 1 

#### Study-specific variable description



| **Name** | `	q24_1_8`|`q24`|
|-|-|-|
| **Label** | `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`|`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`|
| **Table name** |`jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** |  |`1 = Yes`<br/>`2 = No`<br/>`3 = Don't know`|
| **Description** |  |  |


```{r assign1 3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_sport','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q24','q24_1_8'), missings = TRUE)
JSTAR_cth_w1_sport <- opal.execute(o,'JSTAR_cth_w1_sport')
```

```{r local1 3, echo=F}

vari <- JSTAR_cth_w1_sport$q24
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_sport, aes(x=factor(q24))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_cth_w1_sport$q24_1_8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_sport, aes(x=factor(q24_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables they have to be recoded as follows:

* `q24 == 2 into 0`
* `q24 == 3 into 998`
* `q24_1_8 == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_sport$id)
JSTAR_ds_cth_w1$sport <- car::recode(as.vector(JSTAR_cth_w1_sport$q24), "1='999'; 2='0'; 3='998'; NA='999'")
JSTAR_ds_cth_w1$sport[which(JSTAR_cth_w1_sport$q24_1_8 == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript1 3, echo=F}
vari <- JSTAR_ds_cth_w1$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(JSTAR_ds_cth_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3, echo=F}

```



## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

