---
title: "Any participation in organized/group sport activities (like sport clubs, do sport with other people, membership of gyms, exercise classes etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `sport`
* Variable label: `Sport activities`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## aksst

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `	tome237`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE, SPORTS, TAKING A WALK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_sport','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('tome237'), missings = TRUE)
```

```{r local1 5}
JSTAR_aksst_w1_sport <- opal.execute(o,'JSTAR_aksst_w1_sport')
vari <- JSTAR_aksst_w1_sport$tome237
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_sport$tome237, missing_values = NA)
ggplot(JSTAR_aksst_w1_sport, aes(x=factor(tome237))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE, SPORTS, TAKING A WALK") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 5, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_sport$id)
JSTAR_aksst_ds_w1$sport <- car::recode(as.vector(JSTAR_aksst_w1_sport$tome237), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_aksst_ds_w1$sport <- labelled(JSTAR_aksst_ds_w1$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 5}
vari <- JSTAR_aksst_ds_w1$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5}

```

 
 



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `	tome253`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_sport','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('tome253'), missings = TRUE)
```

```{r local2 5}
JSTAR_aksst_w2_sport <- opal.execute(o,'JSTAR_aksst_w2_sport')
vari <- JSTAR_aksst_w2_sport$tome253
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w2_sport$tome253, missing_values = NA)
ggplot(JSTAR_aksst_w2_sport, aes(x=factor(tome253))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE/SPORTS") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 5, echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_sport$id)
JSTAR_aksst_ds_w2$sport <- car::recode(as.vector(JSTAR_aksst_w2_sport$tome253), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_aksst_ds_w2$sport <- labelled(JSTAR_aksst_ds_w2$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 5}
vari <- JSTAR_aksst_ds_w2$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w2$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 5}

```

 
 



### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q17_1_8`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign3 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_sport','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('q17_1_8'), missings = TRUE)
```

```{r local3 5}
JSTAR_aksst_w3_sport <- opal.execute(o,'JSTAR_aksst_w3_sport')
vari <- JSTAR_aksst_w3_sport$q17_1_8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_sport$q17_1_8, missing_values = NA)
ggplot(JSTAR_aksst_w3_sport, aes(x=factor(q17_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE/SPORTS") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo3 5, echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_sport$id)
JSTAR_aksst_ds_w3$sport <- car::recode(as.vector(JSTAR_aksst_w3_sport$q17_1_8), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_aksst_ds_w3$sport <- labelled(JSTAR_aksst_ds_w3$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 5}
vari <- JSTAR_aksst_ds_w3$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3 5}

```

 
 


## tn

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `	tome237`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 2}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_sport','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('tome237'), missings = TRUE)
```

```{r local1 2}
JSTAR_tn_w1_sport <- opal.execute(o,'JSTAR_tn_w1_sport')
vari <- JSTAR_tn_w1_sport$tome237
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_sport$tome237, missing_values = NA)
ggplot(JSTAR_tn_w1_sport, aes(x=factor(tome237))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE/SPORTS") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_sport$id)
JSTAR_tn_ds_w1$sport <- car::recode(as.vector(JSTAR_tn_w1_sport$tome237), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_tn_ds_w1$sport <- labelled(JSTAR_tn_ds_w1$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 2}
vari <- JSTAR_tn_ds_w1$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2}

```

 
 



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q17_1_8`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 2}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_sport','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('q17_1_8'), missings = TRUE)
```

```{r local2 2}
JSTAR_tn_w2_sport <- opal.execute(o,'JSTAR_tn_w2_sport')
vari <- JSTAR_tn_w2_sport$q17_1_8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_sport$q17_1_8, missing_values = NA)
ggplot(JSTAR_tn_w2_sport, aes(x=factor(q17_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE/SPORTS") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 2, echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_sport$id)
JSTAR_tn_ds_w2$sport <- car::recode(as.vector(JSTAR_tn_w2_sport$q17_1_8), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_tn_ds_w2$sport <- labelled(JSTAR_tn_ds_w2$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2}
vari <- JSTAR_tn_ds_w2$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 2}

```

 
 


## cth
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `	q24_1_8`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? What kind of activity was it? -8-EXERCISE/SPORTS`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 3}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_sport','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q24_1_8'), missings = TRUE)
```

```{r local1 3}
JSTAR_cth_w1_sport <- opal.execute(o,'JSTAR_cth_w1_sport')
vari <- JSTAR_cth_w1_sport$q24_1_8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_cth_w1_sport$q24_1_8, missing_values = NA)
ggplot(JSTAR_cth_w1_sport, aes(x=factor(q24_1_8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Activity - EXERCISE/SPORTS") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_sport$id)
JSTAR_cth_ds_w1$sport <- car::recode(as.vector(JSTAR_cth_w1_sport$q24_1_8), "1='1'; 2='0'; 3='998'; NA='999'")
JSTAR_cth_ds_w1$sport <- labelled(JSTAR_cth_ds_w1$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 3}
vari <- JSTAR_cth_ds_w1$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3}

```

 
 
```{r save, echo=FALSE}
sport <- JSTAR_tn_ds_w1
save(sport, file = "../RData/tn_w1/sport.RData")
rm(sport)

sport <- JSTAR_tn_ds_w2
save(sport, file = "../RData/tn_w2/sport.RData")
rm(sport)


sport <- JSTAR_aksst_ds_w1
save(sport, file = "../RData/aksst_w1/sport.RData")
rm(sport)

sport <- JSTAR_aksst_ds_w2
save(sport, file = "../RData/aksst_w2/sport.RData")
rm(sport)

sport <- JSTAR_aksst_ds_w3
save(sport, file = "../RData/aksst_w3/sport.RData")
rm(sport)

sport <- JSTAR_cth_ds_w1
save(sport, file = "../RData/cth_w1/sport.RData")
rm(sport)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

