---
title: "Any voluntary/charitable activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `volun`
* Variable label: `Any voluntary/charitable activity`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## aksst
### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	tome231`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome232`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_volun','JSTAR_datasets_restricted.jstar_2007_5cities', 
                        variables=list('tome231','tome232'), missings = TRUE)
```

```{r local1 5}
JSTAR_aksst_w1_volun <- opal.execute(o,'JSTAR_aksst_w1_volun')
vari <- JSTAR_aksst_w1_volun$tome231
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_volun$tome231, missing_values = NA)
ggplot(JSTAR_aksst_w1_volun, aes(x=factor(tome231))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_aksst_w1_volun$tome232
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_volun$tome232, missing_values = NA)
ggplot(JSTAR_aksst_w1_volun, aes(x=factor(tome232))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 5, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_volun$id)

JSTAR_aksst_w1_volun$tome231 <- car::recode(as.vector(JSTAR_aksst_w1_volun$tome231), "NA='-999'")
JSTAR_aksst_w1_volun$tome232 <- car::recode(as.vector(JSTAR_aksst_w1_volun$tome232), "NA='-999'")

JSTAR_aksst_ds_w1$volun <- c(NA)
for(i in 1:dim(JSTAR_aksst_w1_volun)[1]){
  if( JSTAR_aksst_w1_volun$tome231[i] == 1 | JSTAR_aksst_w1_volun$tome232[i] == 1 ) { 
    JSTAR_aksst_ds_w1$volun[i] = 1 }
  else if( JSTAR_aksst_w1_volun$tome231[i] == 2 & JSTAR_aksst_w1_volun$tome232[i] == 2 ) { 
    JSTAR_aksst_ds_w1$volun[i] = 0 }
  else if( JSTAR_aksst_w1_volun$tome231[i] == 3 | JSTAR_aksst_w1_volun$tome232[i] == 3 ) { 
    JSTAR_aksst_ds_w1$volun[i] = 998 }
}

JSTAR_aksst_ds_w1$volun <- car::recode(as.vector(JSTAR_aksst_ds_w1$volun), "NA='999'")
JSTAR_aksst_ds_w1$volun <- labelled(JSTAR_aksst_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 5}
vari <- JSTAR_aksst_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5}

```

 
 




### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	tome247`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome248`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_volun','JSTAR_datasets_restricted.jstar_2009_5cities', 
                        variables=list('tome247','tome248'), missings = TRUE)
```

```{r local2 5}
JSTAR_aksst_w2_volun <- opal.execute(o,'JSTAR_aksst_w2_volun')

vari <- JSTAR_aksst_w2_volun$tome247
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w2_volun$tome247, missing_values = NA)
ggplot(JSTAR_aksst_w2_volun, aes(x=factor(tome247))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_aksst_w2_volun$tome248
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w2_volun$tome248, missing_values = NA)
ggplot(JSTAR_aksst_w2_volun, aes(x=factor(tome248))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 5, echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_volun$id)

JSTAR_aksst_w2_volun$tome247 <- car::recode(as.vector(JSTAR_aksst_w2_volun$tome247), "NA='-999'")
JSTAR_aksst_w2_volun$tome248 <- car::recode(as.vector(JSTAR_aksst_w2_volun$tome248), "NA='-999'")

JSTAR_aksst_ds_w2$volun <- c(NA)
for(i in 1:dim(JSTAR_aksst_w2_volun)[1]){
  if( JSTAR_aksst_w2_volun$tome247[i] == 1 | JSTAR_aksst_w2_volun$tome248[i] == 1 ) { 
    JSTAR_aksst_ds_w2$volun[i] = 1 }
  else if( JSTAR_aksst_w2_volun$tome247[i] == 2 & JSTAR_aksst_w2_volun$tome248[i] == 2 ) { 
    JSTAR_aksst_ds_w2$volun[i] = 0 }
  else if( JSTAR_aksst_w2_volun$tome247[i] == 3 | JSTAR_aksst_w2_volun$tome248[i] == 3 ) { 
    JSTAR_aksst_ds_w2$volun[i] = 998 }
}

JSTAR_aksst_ds_w2$volun <- car::recode(as.vector(JSTAR_aksst_ds_w2$volun), "NA='999'")
JSTAR_aksst_ds_w2$volun <- labelled(JSTAR_aksst_ds_w2$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 5}
vari <- JSTAR_aksst_ds_w2$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w2$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 5}

```

 
 





### Wave 3

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	q17_1_2`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_3`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign3 5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_volun','JSTAR_datasets_restricted.jstar_2011_5cities', 
                        variables=list('q17_1_2','q17_1_3'), missings = TRUE)
```

```{r local3 5}
JSTAR_aksst_w3_volun <- opal.execute(o,'JSTAR_aksst_w3_volun')

vari <- JSTAR_aksst_w3_volun$q17_1_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_volun$q17_1_2, missing_values = NA)
ggplot(JSTAR_aksst_w3_volun, aes(x=factor(q17_1_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_aksst_w3_volun$q17_1_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_volun$q17_1_3, missing_values = NA)
ggplot(JSTAR_aksst_w3_volun, aes(x=factor(q17_1_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo3 5, echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_volun$id)

JSTAR_aksst_w3_volun$q17_1_2 <- car::recode(as.vector(JSTAR_aksst_w3_volun$q17_1_2), "NA='-999'")
JSTAR_aksst_w3_volun$q17_1_3 <- car::recode(as.vector(JSTAR_aksst_w3_volun$q17_1_3), "NA='-999'")

JSTAR_aksst_ds_w3$volun <- c(NA)
for(i in 1:dim(JSTAR_aksst_w3_volun)[1]){
  if( JSTAR_aksst_w3_volun$q17_1_2[i] == 1 | JSTAR_aksst_w3_volun$q17_1_3[i] == 1 ) { 
    JSTAR_aksst_ds_w3$volun[i] = 1 }
  else if( JSTAR_aksst_w3_volun$q17_1_2[i] == 2 & JSTAR_aksst_w3_volun$q17_1_3[i] == 2 ) { 
    JSTAR_aksst_ds_w3$volun[i] = 0 }
  else if( JSTAR_aksst_w3_volun$q17_1_2[i] == 3 | JSTAR_aksst_w3_volun$q17_1_3[i] == 3 ) { 
    JSTAR_aksst_ds_w3$volun[i] = 998 }
}

JSTAR_aksst_ds_w3$volun <- car::recode(as.vector(JSTAR_aksst_ds_w3$volun), "NA='999'")
JSTAR_aksst_ds_w3$volun <- labelled(JSTAR_aksst_ds_w3$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 5}
vari <- JSTAR_aksst_ds_w3$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3 5}

```

 
 



## tn
### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	tome231`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome232`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 2}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_volun','JSTAR_datasets_restricted.jstar_2009_2cities', 
                        variables=list('tome231','tome232'), missings = TRUE)
```

```{r local1 2}
JSTAR_tn_w1_volun <- opal.execute(o,'JSTAR_tn_w1_volun')

vari <- JSTAR_tn_w1_volun$tome231
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_volun$tome231, missing_values = NA)
ggplot(JSTAR_tn_w1_volun, aes(x=factor(tome231))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_tn_w1_volun$tome232
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_volun$tome232, missing_values = NA)
ggplot(JSTAR_tn_w1_volun, aes(x=factor(tome232))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_volun$id)

JSTAR_tn_w1_volun$tome231 <- car::recode(as.vector(JSTAR_tn_w1_volun$tome231), "NA='-999'")
JSTAR_tn_w1_volun$tome232 <- car::recode(as.vector(JSTAR_tn_w1_volun$tome232), "NA='-999'")

JSTAR_tn_ds_w1$volun <- c(NA)
for(i in 1:dim(JSTAR_tn_w1_volun)[1]){
  if( JSTAR_tn_w1_volun$tome231[i] == 1 | JSTAR_tn_w1_volun$tome232[i] == 1 ) { 
    JSTAR_tn_ds_w1$volun[i] = 1 }
  else if( JSTAR_tn_w1_volun$tome231[i] == 2 & JSTAR_tn_w1_volun$tome232[i] == 2 ) { 
    JSTAR_tn_ds_w1$volun[i] = 0 }
  else if( JSTAR_tn_w1_volun$tome231[i] == 3 | JSTAR_tn_w1_volun$tome232[i] == 3 ) { 
    JSTAR_tn_ds_w1$volun[i] = 998 }
}

JSTAR_tn_ds_w1$volun <- car::recode(as.vector(JSTAR_tn_ds_w1$volun), "NA='999'")
JSTAR_tn_ds_w1$volun <- labelled(JSTAR_tn_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 2}
vari <- JSTAR_tn_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2}

```

 
 




### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	q17_1_2`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_3`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign2 2}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_volun','JSTAR_datasets_restricted.jstar_2011_2cities', 
                        variables=list('q17_1_2','q17_1_3'), missings = TRUE)
```

```{r local2 2}
JSTAR_tn_w2_volun <- opal.execute(o,'JSTAR_tn_w2_volun')

vari <- JSTAR_tn_w2_volun$q17_1_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_volun$q17_1_2, missing_values = NA)
ggplot(JSTAR_tn_w2_volun, aes(x=factor(q17_1_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_tn_w2_volun$q17_1_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_volun$q17_1_3, missing_values = NA)
ggplot(JSTAR_tn_w2_volun, aes(x=factor(q17_1_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo2 2, echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_volun$id)

JSTAR_tn_w2_volun$q17_1_2 <- car::recode(as.vector(JSTAR_tn_w2_volun$q17_1_2), "NA='-999'")
JSTAR_tn_w2_volun$q17_1_3 <- car::recode(as.vector(JSTAR_tn_w2_volun$q17_1_3), "NA='-999'")

JSTAR_tn_ds_w2$volun <- c(NA)
for(i in 1:dim(JSTAR_tn_w2_volun)[1]){
  if( JSTAR_tn_w2_volun$q17_1_2[i] == 1 | JSTAR_tn_w2_volun$q17_1_3[i] == 1 ) { 
    JSTAR_tn_ds_w2$volun[i] = 1 }
  else if( JSTAR_tn_w2_volun$q17_1_2[i] == 2 & JSTAR_tn_w2_volun$q17_1_3[i] == 2 ) { 
    JSTAR_tn_ds_w2$volun[i] = 0 }
  else if( JSTAR_tn_w2_volun$q17_1_2[i] == 3 | JSTAR_tn_w2_volun$q17_1_3[i] == 3 ) { 
    JSTAR_tn_ds_w2$volun[i] = 998 }
}

JSTAR_tn_ds_w2$volun <- car::recode(as.vector(JSTAR_tn_ds_w2$volun), "NA='999'")
JSTAR_tn_ds_w2$volun <- labelled(JSTAR_tn_ds_w2$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2}
vari <- JSTAR_tn_ds_w2$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 2}

```

 
 


## cth

### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `	q24_1_2`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -2- -PROVIDING HELP NEIGHBOURS-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q24_1_3`
* Label: `Q24-1:WHAT ARE THOSE ACTIVITIES? -3- -VOLUNTARY OR CHARITY WORK-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Description: 
```{r assign1 3}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_volun','JSTAR_datasets_restricted.jstar_2011_3cities', 
                        variables=list('q24_1_2','q24_1_3'), missings = TRUE)
```

```{r local1 3}
JSTAR_cth_w1_volun <- opal.execute(o,'JSTAR_cth_w1_volun')

vari <-  JSTAR_cth_w1_volun$q24_1_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_cth_w1_volun$q24_1_2, missing_values = NA)
ggplot(JSTAR_cth_w1_volun, aes(x=factor(q24_1_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-PROVIDING HELP NEIGHBOURS-") + ylab("Frequency")

vari <- JSTAR_cth_w1_volun$q24_1_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_cth_w1_volun$q24_1_3, missing_values = NA)
ggplot(JSTAR_cth_w1_volun, aes(x=factor(q24_1_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-VOLUNTARY OR CHARITY WORK-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_volun$id)

JSTAR_cth_w1_volun$q24_1_2 <- car::recode(as.vector(JSTAR_cth_w1_volun$q24_1_2), "NA='-999'")
JSTAR_cth_w1_volun$q24_1_3 <- car::recode(as.vector(JSTAR_cth_w1_volun$q24_1_3), "NA='-999'")

JSTAR_cth_ds_w1$volun <- c(NA)
for(i in 1:dim(JSTAR_cth_w1_volun)[1]){
  if( JSTAR_cth_w1_volun$q24_1_2[i] == 1 | JSTAR_cth_w1_volun$q24_1_3[i] == 1 ) { 
    JSTAR_cth_ds_w1$volun[i] = 1 }
  else if( JSTAR_cth_w1_volun$q24_1_2[i] == 2 & JSTAR_cth_w1_volun$q24_1_3[i] == 2 ) { 
    JSTAR_cth_ds_w1$volun[i] = 0 }
  else if( JSTAR_cth_w1_volun$q24_1_2[i] == 3 | JSTAR_cth_w1_volun$q24_1_3[i] == 3 ) { 
    JSTAR_cth_ds_w1$volun[i] = 998 }
}

JSTAR_cth_ds_w1$volun <- car::recode(as.vector(JSTAR_cth_ds_w1$volun), "NA='999'")
JSTAR_cth_ds_w1$volun <- labelled(JSTAR_cth_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 3}
vari <- JSTAR_cth_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3}

```

 
 
```{r save, echo=FALSE}
volun <- JSTAR_tn_ds_w1
save(volun, file = "../RData/tn_w1/volun.RData")
rm(volun)

volun <- JSTAR_tn_ds_w2
save(volun, file = "../RData/tn_w2/volun.RData")
rm(volun)


volun <- JSTAR_aksst_ds_w1
save(volun, file = "../RData/aksst_w1/volun.RData")
rm(volun)

volun <- JSTAR_aksst_ds_w2
save(volun, file = "../RData/aksst_w2/volun.RData")
rm(volun)

volun <- JSTAR_aksst_ds_w3
save(volun, file = "../RData/aksst_w3/volun.RData")
rm(volun)

volun <- JSTAR_cth_ds_w1
save(volun, file = "../RData/cth_w1/volun.RData")
rm(volun)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
