---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process

## aksst

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome230`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome233`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome234`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assigna1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_part_clubs','JSTAR_datasets_restricted.jstar_2007_5cities', 
                        variables=list('tome230','tome233','tome234'), missings = TRUE)
JSTAR_aksst_w1_part_clubs <- opal.execute(o,'JSTAR_aksst_w1_part_clubs')
```

```{r locala1, echo=F}
Categorical_summary(var = JSTAR_aksst_w1_part_clubs$tome230, missing_values = NA)
ggplot(JSTAR_aksst_w1_part_clubs, aes(x=factor(tome230))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa1}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_part_clubs$id)

JSTAR_aksst_w1_part_clubs$tome230 <- car::recode(as.vector(JSTAR_aksst_w1_part_clubs$tome230), "NA='-999'")
JSTAR_aksst_w1_part_clubs$tome233 <- car::recode(as.vector(JSTAR_aksst_w1_part_clubs$tome233), "NA='-999'")
JSTAR_aksst_w1_part_clubs$tome234 <- car::recode(as.vector(JSTAR_aksst_w1_part_clubs$tome234), "NA='-999'")

JSTAR_ds_aksst_w1$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_aksst_w1_part_clubs)[1]){
  if( JSTAR_aksst_w1_part_clubs$tome230[i] == 1 | JSTAR_aksst_w1_part_clubs$tome233[i] == 1 | JSTAR_aksst_w1_part_clubs$tome234[i] == 1 ) { 
    JSTAR_ds_aksst_w1$part_clubs[i] = 1 }
  else if( JSTAR_aksst_w1_part_clubs$tome230[i] == 2 & JSTAR_aksst_w1_part_clubs$tome233[i] == 2 & JSTAR_aksst_w1_part_clubs$tome234[i] == 2 ) { 
    JSTAR_ds_aksst_w1$part_clubs[i] = 0 }
  else if( JSTAR_aksst_w1_part_clubs$tome230[i] == 3 | JSTAR_aksst_w1_part_clubs$tome233[i] == 3 | JSTAR_aksst_w1_part_clubs$tome234[i] == 3 ) { 
    JSTAR_ds_aksst_w1$part_clubs[i] = 998 }

}

JSTAR_ds_aksst_w1$part_clubs <- car::recode(as.vector(JSTAR_ds_aksst_w1$part_clubs), "NA='999'")
JSTAR_ds_aksst_w1$part_clubs <- labelled(JSTAR_ds_aksst_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descripta1, echo=F}
Categorical_summary(var = JSTAR_ds_aksst_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationa1, echo=F}

```







### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome246`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`

* Name: `	tome249`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome250`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assigna2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_part_clubs','JSTAR_datasets_restricted.jstar_2009_5cities', 
                        variables=list('tome246','tome249','tome250'), missings = TRUE)
```

```{r locala2, echo=F}
JSTAR_aksst_w2_part_clubs <- opal.execute(o,'JSTAR_aksst_w2_part_clubs')
Categorical_summary(var = JSTAR_aksst_w2_part_clubs$tome246, missing_values = NA)
ggplot(JSTAR_aksst_w2_part_clubs, aes(x=factor(tome246))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_part_clubs$id)

JSTAR_aksst_w2_part_clubs$tome246 <- car::recode(as.vector(JSTAR_aksst_w2_part_clubs$tome246), "NA='-999'")
JSTAR_aksst_w2_part_clubs$tome249 <- car::recode(as.vector(JSTAR_aksst_w2_part_clubs$tome249), "NA='-999'")
JSTAR_aksst_w2_part_clubs$tome250 <- car::recode(as.vector(JSTAR_aksst_w2_part_clubs$tome250), "NA='-999'")

JSTAR_ds_aksst_w2$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_aksst_w2_part_clubs)[1]){
  if( JSTAR_aksst_w2_part_clubs$tome246[i] == 1 | JSTAR_aksst_w2_part_clubs$tome249[i] == 1 | JSTAR_aksst_w2_part_clubs$tome250[i] == 1 ) { 
    JSTAR_ds_aksst_w2$part_clubs[i] = 1 }
  else if( JSTAR_aksst_w2_part_clubs$tome246[i] == 2 & JSTAR_aksst_w2_part_clubs$tome249[i] == 2 & JSTAR_aksst_w2_part_clubs$tome250[i] == 2 ) { 
    JSTAR_ds_aksst_w2$part_clubs[i] = 0 }
  else if( JSTAR_aksst_w2_part_clubs$tome246[i] == 3 | JSTAR_aksst_w2_part_clubs$tome249[i] == 3 | JSTAR_aksst_w2_part_clubs$tome250[i] == 3 ) { 
    JSTAR_ds_aksst_w2$part_clubs[i] = 998 }

}

JSTAR_ds_aksst_w2$part_clubs <- car::recode(as.vector(JSTAR_ds_aksst_w2$part_clubs), "NA='999'")
JSTAR_ds_aksst_w2$part_clubs <- labelled(JSTAR_ds_aksst_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descripta2, echo=F}
Categorical_summary(var = JSTAR_ds_aksst_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationa2, echo=F}

```







### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q17_1_1`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_4`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_5`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assigna3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_part_clubs','JSTAR_datasets_restricted.jstar_2011_5cities', 
                        variables=list('q17_1_1','q17_1_4','q17_1_5'), missings = TRUE)
```

```{r locala3, echo=F}
JSTAR_aksst_w3_part_clubs <- opal.execute(o,'JSTAR_aksst_w3_part_clubs')
Categorical_summary(var = JSTAR_aksst_w3_part_clubs$q17_1_1, missing_values = NA)
ggplot(JSTAR_aksst_w3_part_clubs, aes(x=factor(q17_1_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_part_clubs$id)

JSTAR_aksst_w3_part_clubs$q17_1_1 <- car::recode(as.vector(JSTAR_aksst_w3_part_clubs$q17_1_1), "NA='-999'")
JSTAR_aksst_w3_part_clubs$q17_1_4 <- car::recode(as.vector(JSTAR_aksst_w3_part_clubs$q17_1_4), "NA='-999'")
JSTAR_aksst_w3_part_clubs$q17_1_5 <- car::recode(as.vector(JSTAR_aksst_w3_part_clubs$q17_1_5), "NA='-999'")

JSTAR_ds_aksst_w3$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_aksst_w3_part_clubs)[1]){
  if( JSTAR_aksst_w3_part_clubs$q17_1_1[i] == 1 | JSTAR_aksst_w3_part_clubs$q17_1_4[i] == 1 | JSTAR_aksst_w3_part_clubs$q17_1_5[i] == 1 ) { 
    JSTAR_ds_aksst_w3$part_clubs[i] = 1 }
  else if( JSTAR_aksst_w3_part_clubs$q17_1_1[i] == 2 & JSTAR_aksst_w3_part_clubs$q17_1_4[i] == 2 & JSTAR_aksst_w3_part_clubs$q17_1_5[i] == 2 ) { 
    JSTAR_ds_aksst_w3$part_clubs[i] = 0 }
  else if( JSTAR_aksst_w3_part_clubs$q17_1_1[i] == 3 | JSTAR_aksst_w3_part_clubs$q17_1_4[i] == 3 | JSTAR_aksst_w3_part_clubs$q17_1_5[i] == 3 ) { 
    JSTAR_ds_aksst_w3$part_clubs[i] = 998 }

}

JSTAR_ds_aksst_w3$part_clubs <- car::recode(as.vector(JSTAR_ds_aksst_w3$part_clubs), "NA='999'")
JSTAR_ds_aksst_w3$part_clubs <- labelled(JSTAR_ds_aksst_w3$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descripta3, echo=F}
Categorical_summary(var = JSTAR_ds_aksst_w3$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationa3, echo=F}

```




## tn


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	tome230`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome233`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	tome234`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assignt1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_part_clubs','JSTAR_datasets_restricted.jstar_2009_2cities', 
                        variables=list('tome230','tome233','tome234'), missings = TRUE)
```

```{r localt1, echo=F}
JSTAR_tn_w1_part_clubs <- opal.execute(o,'JSTAR_tn_w1_part_clubs')
Categorical_summary(var = JSTAR_tn_w1_part_clubs$tome230, missing_values = NA)
ggplot(JSTAR_tn_w1_part_clubs, aes(x=factor(tome230))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmot1}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_part_clubs$id)

JSTAR_tn_w1_part_clubs$tome230 <- car::recode(as.vector(JSTAR_tn_w1_part_clubs$tome230), "NA='-999'")
JSTAR_tn_w1_part_clubs$tome233 <- car::recode(as.vector(JSTAR_tn_w1_part_clubs$tome233), "NA='-999'")
JSTAR_tn_w1_part_clubs$tome234 <- car::recode(as.vector(JSTAR_tn_w1_part_clubs$tome234), "NA='-999'")

JSTAR_ds_tn_w1$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_tn_w1_part_clubs)[1]){
  if( JSTAR_tn_w1_part_clubs$tome230[i] == 1 | JSTAR_tn_w1_part_clubs$tome233[i] == 1 | JSTAR_tn_w1_part_clubs$tome234[i] == 1 ) { 
    JSTAR_ds_tn_w1$part_clubs[i] = 1 }
  else if( JSTAR_tn_w1_part_clubs$tome230[i] == 2 & JSTAR_tn_w1_part_clubs$tome233[i] == 2 & JSTAR_tn_w1_part_clubs$tome234[i] == 2 ) { 
    JSTAR_ds_tn_w1$part_clubs[i] = 0 }
  else if( JSTAR_tn_w1_part_clubs$tome230[i] == 3 | JSTAR_tn_w1_part_clubs$tome233[i] == 3 | JSTAR_tn_w1_part_clubs$tome234[i] == 3 ) { 
    JSTAR_ds_tn_w1$part_clubs[i] = 998 }
}

JSTAR_ds_tn_w1$part_clubs <- car::recode(as.vector(JSTAR_ds_tn_w1$part_clubs), "NA='999'")
JSTAR_ds_tn_w1$part_clubs <- labelled(JSTAR_ds_tn_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptt1, echo=F}
Categorical_summary(var = JSTAR_ds_tn_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationt1, echo=F}

```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q17_1_1`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_4`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q17_1_5`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assignt2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_part_clubs','JSTAR_datasets_restricted.jstar_2011_2cities', 
                        variables=list('q17_1_1','q17_1_4','q17_1_5'), missings = TRUE)
```

```{r localt2, echo=F}
JSTAR_tn_w2_part_clubs <- opal.execute(o,'JSTAR_tn_w2_part_clubs')
Categorical_summary(var = JSTAR_tn_w2_part_clubs$q17_1_1, missing_values = NA)
ggplot(JSTAR_tn_w2_part_clubs, aes(x=factor(q17_1_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmot2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_part_clubs$id)

JSTAR_tn_w2_part_clubs$q17_1_1 <- car::recode(as.vector(JSTAR_tn_w2_part_clubs$q17_1_1), "NA='-999'")
JSTAR_tn_w2_part_clubs$q17_1_4 <- car::recode(as.vector(JSTAR_tn_w2_part_clubs$q17_1_4), "NA='-999'")
JSTAR_tn_w2_part_clubs$q17_1_5 <- car::recode(as.vector(JSTAR_tn_w2_part_clubs$q17_1_5), "NA='-999'")

JSTAR_ds_tn_w2$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_tn_w2_part_clubs)[1]){
  if( JSTAR_tn_w2_part_clubs$q17_1_1[i] == 1 | JSTAR_tn_w2_part_clubs$q17_1_4[i] == 1 | JSTAR_tn_w2_part_clubs$q17_1_5[i] == 1 ) { 
    JSTAR_ds_tn_w2$part_clubs[i] = 1 }
  else if( JSTAR_tn_w2_part_clubs$q17_1_1[i] == 2 & JSTAR_tn_w2_part_clubs$q17_1_4[i] == 2 & JSTAR_tn_w2_part_clubs$q17_1_5[i] == 2 ) { 
    JSTAR_ds_tn_w2$part_clubs[i] = 0 }
  else if( JSTAR_tn_w2_part_clubs$q17_1_1[i] == 3 | JSTAR_tn_w2_part_clubs$q17_1_4[i] == 3 | JSTAR_tn_w2_part_clubs$q17_1_5[i] == 3 ) { 
    JSTAR_ds_tn_w2$part_clubs[i] = 998 }
}

JSTAR_ds_tn_w2$part_clubs <- car::recode(as.vector(JSTAR_ds_tn_w2$part_clubs), "NA='999'")
JSTAR_ds_tn_w2$part_clubs <- labelled(JSTAR_ds_tn_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptt2, echo=F}
Categorical_summary(var = JSTAR_ds_tn_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationt2, echo=F}

```




## cth

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	q24_1_1`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -1-COMMUNITY ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q24_1_4`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -4-RELIGIOUS ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    
* Name: `	q24_1_5`
* Label: `In the past month, have you done non-work activities with anyone other than family or friends? -5-POLITICAL ORGANIZATION-`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `3 = Don't know`
    

```{r assignc1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_part_clubs','JSTAR_datasets_restricted.jstar_2011_3cities', 
                        variables=list('q24_1_1','q24_1_4','q24_1_5'), missings = TRUE)
```

```{r localc1, echo=F}
JSTAR_cth_w1_part_clubs <- opal.execute(o,'JSTAR_cth_w1_part_clubs')
Categorical_summary(var = JSTAR_cth_w1_part_clubs$q24_1_1, missing_values = NA)
ggplot(JSTAR_cth_w1_part_clubs, aes(x=factor(q24_1_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("-COMMUNITY ORGANIZATION-") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoc1}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_part_clubs$id)

JSTAR_cth_w1_part_clubs$q24_1_1 <- car::recode(as.vector(JSTAR_cth_w1_part_clubs$q24_1_1), "NA='-999'")
JSTAR_cth_w1_part_clubs$q24_1_4 <- car::recode(as.vector(JSTAR_cth_w1_part_clubs$q24_1_4), "NA='-999'")
JSTAR_cth_w1_part_clubs$q24_1_5 <- car::recode(as.vector(JSTAR_cth_w1_part_clubs$q24_1_5), "NA='-999'")

JSTAR_ds_cth_w1$part_clubs <- c(NA)
for(i in 1:dim(JSTAR_cth_w1_part_clubs)[1]){
  if( JSTAR_cth_w1_part_clubs$q24_1_1[i] == 1 | JSTAR_cth_w1_part_clubs$q24_1_4[i] == 1 | JSTAR_cth_w1_part_clubs$q24_1_5[i] == 1 ) { 
    JSTAR_ds_cth_w1$part_clubs[i] = 1 }
  else if( JSTAR_cth_w1_part_clubs$q24_1_1[i] == 2 & JSTAR_cth_w1_part_clubs$q24_1_4[i] == 2 & JSTAR_cth_w1_part_clubs$q24_1_5[i] == 2 ) { 
    JSTAR_ds_cth_w1$part_clubs[i] = 0 }
  else if( JSTAR_cth_w1_part_clubs$q24_1_1[i] == 3 | JSTAR_cth_w1_part_clubs$q24_1_4[i] == 3 | JSTAR_cth_w1_part_clubs$q24_1_5[i] == 3 ) { 
    JSTAR_ds_cth_w1$part_clubs[i] = 998 }

}

JSTAR_ds_cth_w1$part_clubs <- car::recode(as.vector(JSTAR_ds_cth_w1$part_clubs), "NA='999'")
JSTAR_ds_cth_w1$part_clubs <- labelled(JSTAR_ds_cth_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptc1, echo=F}
Categorical_summary(var = JSTAR_ds_cth_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_cth_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulationc1, echo=F}

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))   )
names(t.hds)<-c("val", "label", toupper(names(l.hds)))
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  part_clubs <- l.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(l.hds)[index],"/part_clubs.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```









