---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process

## aksst

### Wave 1 

#### Study-specific variable description



| **Name** | `tome229`|`tome230`|`tome233`| `tome234`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2007_5cities`|`jstar_2007_5cities`|`jstar_2007_5cities`|`jstar_2007_5cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |

    

```{r assigna1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_part_clubs','JSTAR_datasets_restricted.jstar_2007_5cities', 
                        variables=list('tome229','tome230','tome233','tome234'), missings = TRUE)
JSTAR_aksst_w1_part_clubs <- opal.execute(o,'JSTAR_aksst_w1_part_clubs')
```

```{r locala1, echo=F}

vari <- JSTAR_aksst_w1_part_clubs$tome229
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_aksst_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w1_part_clubs$tome230
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w1_part_clubs$tome233
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w1_part_clubs$tome234
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa1}
JSTAR_ds_aksst_w1 <- JSTAR_aksst_w1_part_clubs %>% 
  mutate(part_clubs = case_when(((tome229 == 1 | is.na(tome229)) & (tome230 == 1 | tome233 == 1 | tome234 == 1)) ~ 1, 
                              tome229 == 2 ~ 0, 
                              tome229 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descripta1, echo=F}

vari <- JSTAR_ds_aksst_w1$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulationa1, echo=F}

```







### Wave 2

#### Study-specific variable description



| **Name** | `tome245`|`tome246`|`tome249`| `tome250`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |



```{r assigna2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_part_clubs','JSTAR_datasets_restricted.jstar_2009_5cities', 
                        variables=list('tome245','tome246','tome249','tome250'), missings = TRUE)
JSTAR_aksst_w2_part_clubs <- opal.execute(o,'JSTAR_aksst_w2_part_clubs')
```

```{r locala2, echo=F}
vari <- JSTAR_aksst_w2_part_clubs$tome245
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_aksst_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w2_part_clubs$tome246
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w2_part_clubs$tome249
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w2_part_clubs$tome250
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa2}
JSTAR_ds_aksst_w2 <- JSTAR_aksst_w2_part_clubs %>% 
  mutate(part_clubs = case_when(((tome245 == 1 | is.na(tome245)) & (tome246 == 1 | tome249 == 1 | tome250 == 1)) ~ 1, 
                              tome245 == 2 ~ 0, 
                              tome245 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descripta2, echo=F}

vari <- JSTAR_ds_aksst_w2$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulationa2, echo=F}

```







### Wave 3

#### Study-specific variable description


| **Name** | `q17`|`q17_1_1`|`q17_1_4`| `q17_1_5`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2011_5cities`|`jstar_2011_5cities`|`jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |



    

```{r assigna3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_part_clubs','JSTAR_datasets_restricted.jstar_2011_5cities', 
                        variables=list('q17','q17_1_1','q17_1_4','q17_1_5'), missings = TRUE)
JSTAR_aksst_w3_part_clubs <- opal.execute(o,'JSTAR_aksst_w3_part_clubs')
```

```{r locala3, echo=F}
vari <- JSTAR_aksst_w3_part_clubs$q17
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_aksst_w3_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w3_part_clubs$q17_1_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w3_part_clubs$q17_1_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w3_part_clubs$q17_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoa3}
JSTAR_ds_aksst_w3 <- JSTAR_aksst_w3_part_clubs %>% 
  mutate(part_clubs = case_when(((q17 == 1 | is.na(q17)) & (q17_1_1 == 1 | q17_1_4 == 1 | q17_1_5 == 1)) ~ 1, 
                              q17 == 2 ~ 0, 
                              q17 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descripta3, echo=F}
vari <- JSTAR_ds_aksst_w3$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulationa3, echo=F}

```




## tn


### Wave 1 

#### Study-specific variable description



| **Name** | `tome229`|`tome230`|`tome233`| `tome234`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2009_2cities`|`jstar_2009_2cities`|`jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |



```{r assignt1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_part_clubs','JSTAR_datasets_restricted.jstar_2009_2cities', 
                        variables=list('tome229','tome230','tome233','tome234'), missings = TRUE)
JSTAR_tn_w1_part_clubs <- opal.execute(o,'JSTAR_tn_w1_part_clubs')
```

```{r localt1, echo=F}

vari <- JSTAR_tn_w1_part_clubs$tome229
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_tn_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w1_part_clubs$tome230
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w1_part_clubs$tome233
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w1_part_clubs$tome234
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmot1}
JSTAR_ds_tn_w1 <- JSTAR_tn_w1_part_clubs %>% 
  mutate(part_clubs = case_when(((tome229 == 1 | is.na(tome229)) & (tome230 == 1 | tome233 == 1 | tome234 == 1)) ~ 1, 
                              tome229 == 2 ~ 0, 
                              tome229 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descriptt1, echo=F}
vari <- JSTAR_ds_tn_w1$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulationt1, echo=F}

```





### Wave 2

#### Study-specific variable description


| **Name** | `q17`|`q17_1_1`|`q17_1_4`| `q17_1_5`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2011_2cities`|`jstar_2011_2cities`|`jstar_2011_2cities`|`jstar_2011_2cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |


    

```{r assignt2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_part_clubs','JSTAR_datasets_restricted.jstar_2011_2cities', 
                        variables=list('q17','q17_1_1','q17_1_4','q17_1_5'), missings = TRUE)
JSTAR_tn_w2_part_clubs <- opal.execute(o,'JSTAR_tn_w2_part_clubs')
```

```{r localt2, echo=F}
vari <- JSTAR_tn_w2_part_clubs$q17
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_tn_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w2_part_clubs$q17_1_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w2_part_clubs$q17_1_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w2_part_clubs$q17_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmot2}
JSTAR_ds_tn_w2 <- JSTAR_tn_w2_part_clubs %>% 
  mutate(part_clubs = case_when(((q17 == 1 | is.na(q17)) & (q17_1_1 == 1 | q17_1_4 == 1 | q17_1_5 == 1)) ~ 1, 
                              q17 == 2 ~ 0, 
                              q17 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descriptt2, echo=F}
vari <- JSTAR_ds_tn_w2$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulationt2, echo=F}

```




## cth

### Wave 1 

#### Study-specific variable description



| **Name** | `q24`|`q24_1_1`|`q24_1_4`| `q24_1_5`|
|-|-|-|-|-|
| **Label** |`Q24:ACTIVITY WITH PEOPLE OTHER THAN FAMILY OR FRIENDS, LAST MONTH`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -1- -COMMUNITY ORGANIZATION-`| `Q24-1:WHAT ARE THOSE ACTIVITIES? -4-RELIGIOUS ORGANIZATION-`|`Q24-1:WHAT ARE THOSE ACTIVITIES? -5-POLITICAL ORGANIZATION-`|
| **Table name** |`jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`|`1 = Yes`|`1 = Yes`|
| **Missings** |`3 = Don't know`<br/>`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |



    

```{r assignc1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_part_clubs','JSTAR_datasets_restricted.jstar_2011_3cities', 
                        variables=list('q24','q24_1_1','q24_1_4','q24_1_5'), missings = TRUE)
JSTAR_cth_w1_part_clubs <- opal.execute(o,'JSTAR_cth_w1_part_clubs')
```

```{r localc1, echo=F}
vari <- JSTAR_cth_w1_part_clubs$q24
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_cth_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_cth_w1_part_clubs$q24_1_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_cth_w1_part_clubs$q24_1_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_cth_w1_part_clubs$q24_1_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_part_clubs, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 2 then 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmoc1}
JSTAR_ds_cth_w1 <- JSTAR_cth_w1_part_clubs %>% 
  mutate(part_clubs = case_when(((q24 == 1 | is.na(q24)) & (q24_1_1 == 1 | q24_1_4 == 1 | q24_1_5 == 1)) ~ 1, 
                              q24 == 2 ~ 0, 
                              q24 == 3 ~ 998, 
                              TRUE ~ 999)) %>%
  select(id, part_clubs)
```

#### Statistics of the new harmonised variable
```{r descriptc1, echo=F}
vari <- JSTAR_ds_cth_w1$part_clubs
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulationc1, echo=F}

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```


```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```









