---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/bereavDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/bereavDS.R')
```


<!-- ########################################################## --> 

# Data process

## aksst

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: `A-007:MARITAL HISTORY OF THE SOLITARY`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is dead`
    + `3 = I am divorced`
* Missings:
    + `4 = Don't know`
    + `5 = Refused to answer`
    
    
* Name: `a_013`
* Label: `A-013:IS PARENT STILL ALIVE`
* Categories: 
    + `1 = Yes,both`
    + `2 = Only father living`
    + `3 = Only mother living`
    + `4 = Both parents dead`
* Missings:
    + `5 = Don't know`
    + `6 = Refused to answer`
    

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_bereav','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('a_007','a_013'), missings = TRUE)
```

```{r local1, echo=F}
JSTAR_aksst_w1_bereav <- opal.execute(o,'JSTAR_aksst_w1_bereav')
vari <- JSTAR_aksst_w1_bereav$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_bereav$a_007, missing_values = NA)
ggplot(JSTAR_aksst_w1_bereav, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MARITAL HISTORY OF THE SOLITAR") + ylab("Frequency")

vari <- JSTAR_aksst_w1_bereav$a_013
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_bereav$a_013, missing_values = NA)
ggplot(JSTAR_aksst_w1_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IS PARENT STILL ALIVE") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `a_007 == 2 OR a_013 in (2,3,4) into 1`
* `a_007 in (1,3) AND a_013 == 1 into 0`
* `a_007 in (1,3) AND a_013 == 5 into 998`
* `a_007 in (1,3) AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 1 into 998`
* `a_007 == 6 AND a_013 == 1 into 997`
* `a_007 == 5 AND a_013 == 5 into 998`
* `a_007 == 6 AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 6 into 999`
* `a_007 == 6 AND a_013 == 5 into 999`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_bereav$id)

JSTAR_aksst_w1_bereav$a_007 <- car::recode(as.vector(JSTAR_aksst_w1_bereav$a_007),"NA='-999'")
JSTAR_aksst_w1_bereav$a_013 <- car::recode(as.vector(JSTAR_aksst_w1_bereav$a_013), "NA='-999'")

JSTAR_ds_aksst_w1$bereav <- c(NA) 
for(i in 1:dim(JSTAR_aksst_w1_bereav)[1]){
if(JSTAR_aksst_w1_bereav$a_007[i] == 2 | JSTAR_aksst_w1_bereav$a_013[i] %in% c(2,3,4) ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 1 }
else if(JSTAR_aksst_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_aksst_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 0 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_aksst_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 998 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_aksst_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 997 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 5 & JSTAR_aksst_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 998 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 6 & JSTAR_aksst_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 997 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 5 & JSTAR_aksst_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 998 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 6 & JSTAR_aksst_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 997 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 5 & JSTAR_aksst_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 999 }
  else if(JSTAR_aksst_w1_bereav$a_007[i] == 6 & JSTAR_aksst_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_aksst_w1$bereav[i] = 999 }
}

JSTAR_ds_aksst_w1$bereav <- car::recode(as.vector(JSTAR_ds_aksst_w1$bereav), "NA='999'")
JSTAR_ds_aksst_w1$bereav <- labelled(JSTAR_ds_aksst_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- JSTAR_ds_aksst_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`
    
* Name: `a_013`
* Label: `A-013:CHANGES IN THE PARENT'S SITUATION`
* Categories: 
    + `1.0 = Father passed away in ____`
    + `2.0 = Mother passed away in ____`
    + `3.0 = Father passed away in ____ and mother passed away in ____`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004`
* Label: `A-004:CHANGES IN THE NUMBER OF CHILDREN`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_bereav','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('a_001_a','a_013','a_004'), missings = TRUE)
```

```{r local2, echo=F}
JSTAR_aksst_w2_bereav <- opal.execute(o,'JSTAR_aksst_w2_bereav')

vari <- JSTAR_aksst_w2_bereav$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_bereav$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w2_bereav, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGE IN MARITAL STATUS") + ylab("Frequency")

vari <- JSTAR_aksst_w2_bereav$a_013
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_bereav$a_013, missing_values = NA)
ggplot(JSTAR_aksst_w2_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGES IN THE PARENT'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w2_bereav$a_004
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_bereav$a_004, missing_values = NA)
ggplot(JSTAR_aksst_w2_bereav, aes(x=factor(a_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGES IN THE NUMBER OF CHILDREN") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `[ (W1.a_007 == 2) OR (W1.a_007 in (1,3) and a_001_a == 3) OR W1.a_013 in (2,3,4) OR  ` 
  `   W2.a_013 in (1,2,3) OR a_004 == 2 ] INTO 1`

* `[ W1.a_007 in (1,3) AND a_001_a in (1,2,4) AND W1.a_013 == 1 AND !(W2.a_013 in (1,2,3)) AND `
  `  !(a_004 == 2) ] INTO 0`
  
* `MISSINGS:`
* `[ W1.a_007 == 4/5 OR a_001_a == 6/7 OR W1.a_013 == 5/6 OR W2.a_013 == 4/5 OR a_004 == 4/5 ] INTO 999`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, 
                       a_001_a=new$a_001_a, a_013.x=new$a_013, a_004=new$a_004, # a_013.x means it is from Wave2
                       a_007=new_2$a_007, a_013.y=new_2$a_013)                  # a_013.y means it is from Wave1
  new_22
}

# old = JSTAR_aksst_w1_bereav
# new = JSTAR_aksst_w2_bereav

JSTAR_aksst_merge_w12 <- same_indiv(JSTAR_aksst_w1_bereav, JSTAR_aksst_w2_bereav) 


JSTAR_aksst_merge_w12$a_001_a <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_001_a), "NA='-999'")
JSTAR_aksst_merge_w12$a_013.x <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_013.x), "NA='-999'")
JSTAR_aksst_merge_w12$a_013.y <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_013.y), "NA='-999'")
JSTAR_aksst_merge_w12$a_004 <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_004), "NA='-999'")
JSTAR_aksst_merge_w12$a_007 <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_007), "NA='-999'")

JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_bereav$id)


  
JSTAR_ds_aksst_w2$bereav <- c(NA) 
for(i in 1:dim(JSTAR_aksst_merge_w12)[1]){
  if( (JSTAR_aksst_merge_w12$a_007[i] == 2 | 
       (JSTAR_aksst_merge_w12$a_007[i] %in% c(1,3) & JSTAR_aksst_merge_w12$a_001_a[i] == 3) |
       JSTAR_aksst_merge_w12$a_013.y[i] %in% c(2,3,4) | JSTAR_aksst_merge_w12$a_013.x[i] %in% c(1,2,3) |
       JSTAR_aksst_merge_w12$a_004[i] == 2 ) ) { 
    JSTAR_ds_aksst_w2$bereav[i] = 1 }
  
  else if( JSTAR_aksst_merge_w12$a_007[i] %in% c(1,3) & 
           JSTAR_aksst_merge_w12$a_001_a[i] %in% c(1,2,4) &
           JSTAR_aksst_merge_w12$a_013.y[i] == 1 & 
           !(JSTAR_aksst_merge_w12$a_013.x[i] %in% c(1,2,3)) &
           !(JSTAR_aksst_merge_w12$a_004[i] == 2) ) { 
    JSTAR_ds_aksst_w2$bereav[i] = 0 }
  
  else if( JSTAR_aksst_merge_w12$a_007[i] %in% c(4,5) | JSTAR_aksst_merge_w12$a_001_a[i] %in% c(6,7) |
       JSTAR_aksst_merge_w12$a_013.y[i] %in% c(5,6) | JSTAR_aksst_merge_w12$a_013.x[i] %in% c(4,5) |
       JSTAR_aksst_merge_w12$a_004[i] %in% c(4,5) ) { 
    JSTAR_ds_aksst_w2$bereav[i] = 999 }
}

JSTAR_ds_aksst_w2$bereav <- car::recode(as.vector(JSTAR_ds_aksst_w2$bereav), "NA='999'")
JSTAR_ds_aksst_w2$bereav <- labelled(JSTAR_ds_aksst_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- JSTAR_ds_aksst_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `11A-001: CHANGES IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`
    
* Name: `a_013`
* Label: `11A-013:CHANGES IN THE PARENT'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Changed`
* Missings:
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_004_1_1_a`
* Label: `11A-004-1-1:CONFIRMATION ON THE 1ST CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_2_a`
* Label: `11A-004-1-2:CONFIRMATION ON THE 2ND CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_3_a`
* Label: `11A-004-1-3:CONFIRMATION ON THE 3RD CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_4_a`
* Label: `11A-004-1-4:CONFIRMATION ON THE 4TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_5_a`
* Label: `11A-004-1-5:CONFIRMATION ON THE 5TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_6_a`
* Label: `11A-004-1-6:CONFIRMATION ON THE 6TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_7_a`
* Label: `11A-004-1-7:CONFIRMATION ON THE 7TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_8_a`
* Label: `11A-004-1-8:CONFIRMATION ON THE 8TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_9_a`
* Label: `11A-004-1-9:CONFIRMATION ON THE 9TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_bereav','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('a_004_1_1_a','a_004_1_2_a','a_004_1_3_a','a_004_1_4_a',
                                        'a_004_1_5_a','a_004_1_6_a','a_004_1_7_a','a_004_1_8_a',
                                        'a_004_1_9_a', 'a_001_a','a_013'), missings = TRUE)
```

```{r local3, echo=F}
JSTAR_aksst_w3_bereav <- opal.execute(o,'JSTAR_aksst_w3_bereav')

vari <- JSTAR_aksst_w3_bereav$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGES IN MARITAL STATUS") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_013
kable(Categorical_summary(vari, missing_values = c(3,4))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(3,4))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(3,4))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_013, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGES IN THE PARENT'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_1_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_1_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 1ST CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_2_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_2_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 2ND CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_3_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_3_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 3RD CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_4_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_4_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 4TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_5_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_5_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 5TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_6_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_6_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 6TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_7_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_7_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 7TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_8_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_8_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 8TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_aksst_w3_bereav$a_004_1_9_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_bereav, aes(x=factor(a_004_1_9_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 9TH CHILD'S SITUATION") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

` if (JSTAR_ds_aksst_w2$bereav==0 AND (a_001_a==3 OR  a_013==2 a_004_1_i_a==2 for some i) ) OR  `  
`     JSTAR_ds_aksst_w2$bereav==1  recode into 1`
  
` else if (JSTAR_ds_aksst_w2$bereav==0 AND a_001_a in (1,2,4) AND a_013==1 AND a_004_1_i_a==1 for every i) `
`         recode into 0`

` MISSINGS:`
` else if (JSTAR_ds_aksst_w2$bereav==999 OR a_001_a in (6,7) OR a_013 IN (3,4) OR a_004_1_i_a IN (4,5) for some i) `
`         recode into 999`
`NA into 999`

   
**R script:**

```{r harmo3, echo=TRUE}
same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, bereav=new_2$bereav, 
                       a_004_1_1_a=new$a_004_1_1_a, a_004_1_2_a=new$a_004_1_2_a, a_004_1_3_a=new$a_004_1_3_a,
                       a_004_1_4_a=new$a_004_1_4_a, a_004_1_5_a=new$a_004_1_5_a, a_004_1_6_a=new$a_004_1_6_a,
                       a_004_1_7_a=new$a_004_1_7_a, a_004_1_8_a=new$a_004_1_8_a, a_004_1_9_a=new$a_004_1_9_a,
                       a_001_a=new$a_001_a, a_013a_013=new$a_013)
  new_22
}

# old = JSTAR_ds_aksst_w2
# new = JSTAR_aksst_w3_bereav

JSTAR_aksst_merge_w23 <- same_indiv(JSTAR_ds_aksst_w2, JSTAR_aksst_w3_bereav) 

JSTAR_aksst_merge_w23$a_001_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_001_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_013 <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_013), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_1_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_1_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_2_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_2_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_3_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_3_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_4_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_4_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_5_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_5_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_6_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_6_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_7_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_7_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_8_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_8_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_1_9_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_1_9_a), "NA='-999'")
JSTAR_aksst_merge_w23$bereav <- car::recode(as.vector(JSTAR_aksst_merge_w23$bereav)," '  1'=1")

JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_bereav$id)

JSTAR_ds_aksst_w3$bereav <- c(NA) 
for(i in 1:dim(JSTAR_aksst_merge_w23)[1]){
  if( (JSTAR_aksst_merge_w23$bereav[i] == 0 & (JSTAR_aksst_merge_w23$a_001_a[i] == 3 |
                                              JSTAR_aksst_merge_w23$a_013[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_1_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_2_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_3_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_4_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_5_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_6_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_7_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_8_a[i] == 2 |
                                              JSTAR_aksst_merge_w23$a_004_1_9_a[i] == 2 ) ) |
      JSTAR_aksst_merge_w23$bereav[i] == 1 )  {
    JSTAR_ds_aksst_w3$bereav[i] = 1 }
  
  
  else if(JSTAR_aksst_merge_w23$bereav[i] == 0 & JSTAR_aksst_merge_w23$a_001_a[i] %in% c(1,2,4) &
          JSTAR_aksst_merge_w23$a_013[i] == 1 & JSTAR_aksst_merge_w23$a_004_1_1_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_2_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_3_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_4_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_5_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_6_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_7_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_8_a[i] == 1 &
                                              JSTAR_aksst_merge_w23$a_004_1_9_a[i] == 1 ) {
    JSTAR_ds_aksst_w3$bereav[i] = 0 }
  
  else if(JSTAR_aksst_merge_w23$bereav[i] == 999 | JSTAR_aksst_merge_w23$a_001_a[i] %in% c(6,7) |
          JSTAR_aksst_merge_w23$a_013[i] %in% c(3,4) | JSTAR_aksst_merge_w23$a_004_1_1_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_2_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_3_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_4_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_5_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_6_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_7_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_8_a[i] %in% c(4,5) |
                                                       JSTAR_aksst_merge_w23$a_004_1_9_a[i] %in% c(4,5) ) {
    JSTAR_ds_aksst_w3$bereav[i] = 999 }
}

JSTAR_ds_aksst_w3$bereav <- car::recode(as.vector(JSTAR_ds_aksst_w3$bereav), "NA='999'")
JSTAR_ds_aksst_w3$bereav <- labelled(JSTAR_ds_aksst_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- JSTAR_ds_aksst_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 


## tn
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: `A-007:MARITAL HISTORY OF THE SOLITARY`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is dead`
    + `3 = I am divorced`
* Missings:
    + `4 = Don't know`
    + `5 = Refused to answer`
    
    
* Name: `a_013`
* Label: `A-013:IS PARENT STILL ALIVE`
* Categories: 
    + `1 = Yes,both`
    + `2 = Only father living`
    + `3 = Only mother living`
    + `4 = Both parents dead`
* Missings:
    + `5 = Don't know`
    + `6 = Refused to answer`
    

* Description: 
```{r assign1 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_bereav','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_007','a_013'), missings = TRUE)
```

```{r local1 2, echo=F}
JSTAR_tn_w1_bereav <- opal.execute(o,'JSTAR_tn_w1_bereav')

vari <- JSTAR_tn_w1_bereav$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w1_bereav$a_007, missing_values = NA)
ggplot(JSTAR_tn_w1_bereav, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MARITAL HISTORY OF THE SOLITARY")+ ylab("Frequency")

vari <-JSTAR_tn_w1_bereav$a_013 
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w1_bereav$a_013, missing_values = NA)
ggplot(JSTAR_tn_w1_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IS PARENT STILL ALIVE") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `a_007 == 2 OR a_013 in (2,3,4) into 1`
* `a_007 in (1,3) AND a_013 == 1 into 0`
* `a_007 in (1,3) AND a_013 == 5 into 998`
* `a_007 in (1,3) AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 1 into 998`
* `a_007 == 6 AND a_013 == 1 into 997`
* `a_007 == 5 AND a_013 == 5 into 998`
* `a_007 == 6 AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 6 into 999`
* `a_007 == 6 AND a_013 == 5 into 999`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_bereav$id)

JSTAR_tn_w1_bereav$a_007 <- car::recode(as.vector(JSTAR_tn_w1_bereav$a_007), "NA='-999'")
JSTAR_tn_w1_bereav$a_013 <- car::recode(as.vector(JSTAR_tn_w1_bereav$a_013), "NA='-999'")

JSTAR_ds_tn_w1$bereav <- c(NA)  
for(i in 1:dim(JSTAR_tn_w1_bereav)[1]){
if(JSTAR_tn_w1_bereav$a_007[i] == 2 | JSTAR_tn_w1_bereav$a_013[i] %in% c(2,3,4) ) { 
  JSTAR_ds_tn_w1$bereav[i] = 1 }
else if(JSTAR_tn_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_tn_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 0 }
  else if(JSTAR_tn_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_tn_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 998 }
  else if(JSTAR_tn_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_tn_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 997 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 5 & JSTAR_tn_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 998 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 6 & JSTAR_tn_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 997 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 5 & JSTAR_tn_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 998 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 6 & JSTAR_tn_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 997 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 5 & JSTAR_tn_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 999 }
  else if(JSTAR_tn_w1_bereav$a_007[i] == 6 & JSTAR_tn_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_tn_w1$bereav[i] = 999 }
}

JSTAR_ds_tn_w1$bereav <- car::recode(as.vector(JSTAR_ds_tn_w1$bereav), "NA='999'")
JSTAR_ds_tn_w1$bereav <- labelled(JSTAR_ds_tn_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 2, echo=F}
vari <- JSTAR_ds_tn_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`
    
* Name: `a_013`
* Label: `11A-013:CHANGES IN THE PARENT'S SITUATION`
* Categories: 
    + `1 = No change (alive)`
    + `2 = Changed (deceased)`
* Missings:
    + `3 = Don't know`
    + `4 = Refused to answer`
    
* Name: `a_004_1_1_a`
* Label: `11A-004-1-1:CONFIRMATION ON THE 1ST CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_2_a`
* Label: `11A-004-1-2:CONFIRMATION ON THE 2ND CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_3_a`
* Label: `11A-004-1-3:CONFIRMATION ON THE 3RD CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_4_a`
* Label: `11A-004-1-4:CONFIRMATION ON THE 4TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_5_a`
* Label: `11A-004-1-5:CONFIRMATION ON THE 5TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_6_a`
* Label: `11A-004-1-6:CONFIRMATION ON THE 6TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_7_a`
* Label: `11A-004-1-7:CONFIRMATION ON THE 7TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_8_a`
* Label: `11A-004-1-8:CONFIRMATION ON THE 8TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`
    
* Name: `a_004_1_9_a`
* Label: `11A-004-1-9:CONFIRMATION ON THE 9TH CHILD'S SITUATION`
* Categories: 
    + `1.0 = Same`
    + `2.0 = Passed away in __ __`
    + `3.0 = Other (specify)`
* Missings:
    + `4.0 = Don't know`
    + `5.0 = Refused to answer`

* Description: 
```{r assign2 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_bereav','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('a_001_a','a_013','a_004_1',
                                        'a_004_1_1_a','a_004_1_2_a','a_004_1_3_a','a_004_1_4_a',
                                        'a_004_1_5_a','a_004_1_6_a','a_004_1_7_a','a_004_1_8_a',
                                        'a_004_1_9_a'), missings = TRUE)
```

```{r local2 2, echo=F}
JSTAR_tn_w2_bereav <- opal.execute(o,'JSTAR_tn_w2_bereav')

vari <- JSTAR_tn_w2_bereav$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_001_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGE IN MARITAL STATUS") + ylab("Frequency")


vari <- JSTAR_tn_w2_bereav$a_013
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_013, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CHANGES IN THE PARENT'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_1_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_1_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 1ST CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_2_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_2_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 2ND CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_3_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_3_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 3RD CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_4_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_4_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 4TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_5_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_5_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 5TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_6_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_6_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 6TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_7_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_7_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 7TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_8_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_8_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 8TH CHILD'S SITUATION") + ylab("Frequency")

vari <- JSTAR_tn_w2_bereav$a_004_1_9_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_bereav$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_tn_w2_bereav, aes(x=factor(a_004_1_9_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONFIRMATION ON THE 9TH CHILD'S SITUATION") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 
*` if (JSTAR_ds_tn_w2$bereav==0 AND (a_001_a==3 OR  a_013==2 a_004_1_i_a==2 for some i) ) OR  `  
`     JSTAR_ds_tn_w2$bereav==1  recode into 1`
  
` else if (JSTAR_ds_tn_w2$bereav==0 AND a_001_a in (1,2,4) AND a_013==1 AND a_004_1_i_a==1 for every i) `
`         recode into 0`

` MISSINGS:`
` else if (JSTAR_ds_tn_w2$bereav==999 OR a_001_a in (6,7) OR a_013 IN (3,4) OR a_004_1_i_a IN (4,5) for some i) `
`         recode into 999`
`NA into 999`


**R script:**

```{r harmo2 2, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, bereav=new_2$bereav, 
                       a_004_1_1_a=new$a_004_1_1_a, a_004_1_2_a=new$a_004_1_2_a, a_004_1_3_a=new$a_004_1_3_a,
                       a_004_1_4_a=new$a_004_1_4_a, a_004_1_5_a=new$a_004_1_5_a, a_004_1_6_a=new$a_004_1_6_a,
                       a_004_1_7_a=new$a_004_1_7_a, a_004_1_8_a=new$a_004_1_8_a, a_004_1_9_a=new$a_004_1_9_a,
                       a_001_a=new$a_001_a, a_013=new$a_013)
  new_22
}

# old = JSTAR_ds_tn_w2
# new = JSTAR_tn_w2_bereav

JSTAR_tn_merge_w12 <- same_indiv(old=JSTAR_ds_tn_w1, new=JSTAR_tn_w2_bereav) 


JSTAR_tn_merge_w12$a_001_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_001_a), "NA='-999'")
JSTAR_tn_merge_w12$a_013 <- car::recode(as.vector(JSTAR_tn_merge_w12$a_013), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_1_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_1_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_2_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_2_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_3_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_3_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_4_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_4_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_5_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_5_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_6_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_6_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_7_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_7_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_8_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_8_a), "NA='-999'")
JSTAR_tn_merge_w12$a_004_1_9_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_004_1_9_a), "NA='-999'")
JSTAR_tn_merge_w12$bereav <- car::recode(as.vector(JSTAR_tn_merge_w12$bereav)," '  1'=1; '  0'=0")

JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_bereav$id)

JSTAR_ds_tn_w2$bereav <- c(NA)  
for(i in 1:dim(JSTAR_tn_merge_w12)[1]){
  if( (JSTAR_tn_merge_w12$bereav[i] == 0 & (JSTAR_tn_merge_w12$a_001_a[i] == 3 |
                                              JSTAR_tn_merge_w12$a_013[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_1_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_2_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_3_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_4_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_5_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_6_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_7_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_8_a[i] == 2 |
                                              JSTAR_tn_merge_w12$a_004_1_9_a[i] == 2 ) ) |
      JSTAR_tn_merge_w12$bereav[i] == 1 )  {
    JSTAR_ds_tn_w2$bereav[i] = 1 }
  
  
  else if(JSTAR_tn_merge_w12$bereav[i] == 0 & JSTAR_tn_merge_w12$a_001_a[i] %in% c(1,2,4) &
          JSTAR_tn_merge_w12$a_013[i] == 1 & JSTAR_tn_merge_w12$a_004_1_1_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_2_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_3_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_4_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_5_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_6_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_7_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_8_a[i] == 1 &
                                              JSTAR_tn_merge_w12$a_004_1_9_a[i] == 1 ) {
    JSTAR_ds_tn_w2$bereav[i] = 0 }
  
  else if(JSTAR_tn_merge_w12$bereav[i] %in% c('997','998','999') | JSTAR_tn_merge_w12$a_001_a[i] %in% c(6,7) |
          JSTAR_tn_merge_w12$a_013[i] %in% c(3,4) | JSTAR_tn_merge_w12$a_004_1_1_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_2_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_3_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_4_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_5_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_6_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_7_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_8_a[i] %in% c(4,5) |
                                                       JSTAR_tn_merge_w12$a_004_1_9_a[i] %in% c(4,5) ) {
    JSTAR_ds_tn_w2$bereav[i] = 999 }
}

# Todos quedan NA pq JSTAR_tn_merge_w12$bereav es factor y el resto numericas
JSTAR_ds_tn_w2$bereav <- car::recode(as.vector(JSTAR_ds_tn_w2$bereav), "NA='999'")
JSTAR_ds_tn_w2$bereav <- labelled(JSTAR_ds_tn_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2, echo=F}
vari <- JSTAR_ds_tn_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2 2, echo=F}

```

 
 


## cth

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: `A-007:MARITAL HISTORY OF THE SOLITARY`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is dead`
    + `3 = I am divorced`
* Missings:
    + `4 = Don't know`
    + `5 = Refused to answer`
    
    
* Name: `a_013`
* Label: `A-013:IS PARENT STILL ALIVE`
* Categories: 
    + `1 = Both parents are alive`
    + `2 = Only father is alive`
    + `3 = Only mother is alive`
    + `4 = Both parents are deceased`
* Missings:
    + `5 = Don't know`
    + `6 = Refused to answer`
    

* Description: 
```{r assign1 3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_bereav','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_007','a_013'), missings = TRUE)
```

```{r local1 3, echo=F}
JSTAR_cth_w1_bereav <- opal.execute(o,'JSTAR_cth_w1_bereav')

vari <- JSTAR_cth_w1_bereav$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_w1_bereav$a_007, missing_values = NA)
ggplot(JSTAR_cth_w1_bereav, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MARITAL HISTORY OF THE SOLITARY") + ylab("Frequency")


vari <- JSTAR_cth_w1_bereav$a_013
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_w1_bereav$a_013, missing_values = NA)
ggplot(JSTAR_cth_w1_bereav, aes(x=factor(a_013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IS PARENT STILL ALIVE") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `a_007 == 2 OR a_013 in (2,3,4) into 1`
* `a_007 in (1,3) AND a_013 == 1 into 0`
* `a_007 in (1,3) AND a_013 == 5 into 998`
* `a_007 in (1,3) AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 1 into 998`
* `a_007 == 6 AND a_013 == 1 into 997`
* `a_007 == 5 AND a_013 == 5 into 998`
* `a_007 == 6 AND a_013 == 6 into 997`
* `a_007 == 5 AND a_013 == 6 into 999`
* `a_007 == 6 AND a_013 == 5 into 999`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_bereav$id)

JSTAR_cth_w1_bereav$a_007 <- car::recode(as.vector(JSTAR_cth_w1_bereav$a_007), "NA='-999'")
JSTAR_cth_w1_bereav$a_013 <- car::recode(as.vector(JSTAR_cth_w1_bereav$a_013), "NA='-999'")

JSTAR_ds_cth_w1$bereav <- c(NA) 
for(i in 1:dim(JSTAR_cth_w1_bereav)[1]){
if(JSTAR_cth_w1_bereav$a_007[i] == 2 | JSTAR_cth_w1_bereav$a_013[i] %in% c(2,3,4) ) { 
  JSTAR_ds_cth_w1$bereav[i] = 1 }
else if(JSTAR_cth_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_cth_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 0 }
  else if(JSTAR_cth_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_cth_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 998 }
  else if(JSTAR_cth_w1_bereav$a_007[i] %in% c(1,3) & JSTAR_cth_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 997 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 5 & JSTAR_cth_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 998 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 6 & JSTAR_cth_w1_bereav$a_013[i] == 1 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 997 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 5 & JSTAR_cth_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 998 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 6 & JSTAR_cth_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 997 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 5 & JSTAR_cth_w1_bereav$a_013[i] == 6 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 999 }
  else if(JSTAR_cth_w1_bereav$a_007[i] == 6 & JSTAR_cth_w1_bereav$a_013[i] == 5 ) { 
  JSTAR_ds_cth_w1$bereav[i] = 999 }
}

JSTAR_ds_cth_w1$bereav <- car::recode(as.vector(JSTAR_ds_cth_w1$bereav), "NA='999'")
JSTAR_ds_cth_w1$bereav <- labelled(JSTAR_ds_cth_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 3, echo=F}
vari <- JSTAR_ds_cth_w1$bereav 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_cth_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_cth_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3, echo=F}

```



 

## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", toupper(names(l.hds)))
kable(t.hds)

```




```{r save, echo=FALSE}
bereav <- JSTAR_ds_tn_w1
save(bereav, file = "../RData/tn_w1/bereav.RData")
rm(bereav)

bereav <- JSTAR_ds_tn_w2
save(bereav, file = "../RData/tn_w2/bereav.RData")
rm(bereav)


bereav <- JSTAR_ds_aksst_w1
save(bereav, file = "../RData/aksst_w1/bereav.RData")
rm(bereav)

bereav <- JSTAR_ds_aksst_w2
save(bereav, file = "../RData/aksst_w2/bereav.RData")
rm(bereav)

bereav <- JSTAR_ds_aksst_w3
save(bereav, file = "../RData/aksst_w3/bereav.RData")
rm(bereav)

bereav <- JSTAR_ds_cth_w1
save(bereav, file = "../RData/cth_w1/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```