---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: ` A-007:MARITAL HISTORY OF THE SOLITARY`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is dead`
    + `3 = I am divorced`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`


* Description: 
```{r assign1 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_divorce','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_007'), missings = TRUE)
```

```{r local1 5, echo=F}
JSTAR_aksst_w1_divorce <- opal.execute(o,'JSTAR_aksst_w1_divorce')
vari <- JSTAR_aksst_w1_divorce$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_divorce$a_007, missing_values = NA)
ggplot(JSTAR_aksst_w1_divorce, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MARITAL HISTORY OF THE SOLITARY") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 into 1`
* `1,2 into 0`
* `4 Don't know into 998`
* `5 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1 5, echo=TRUE}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_divorce$id)
JSTAR_ds_aksst_w1$divorce <- car::recode(as.vector(JSTAR_aksst_w1_divorce$a_007), "3='1'; 1:2='0'; 4='998'; 5='997'; NA='999'")
JSTAR_ds_aksst_w1$divorce <- labelled(JSTAR_ds_aksst_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 5, echo=F}
vari <- JSTAR_ds_aksst_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5, echo=F}

```

 

### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that divorce passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`
    
* Name: `divorce` **harmonized in Wave1**   


* Description: 
```{r assign2 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_divorce','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('a_001_a'), missings = TRUE)
```

```{r local2 5, echo=F}
JSTAR_aksst_w2_divorce <- opal.execute(o,'JSTAR_aksst_w2_divorce')
vari <- JSTAR_aksst_w2_divorce$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_divorce$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w2_divorce, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `(divorce(W1) = 1 or a_001_a(W2) = 4) into 1`
* `(divorce(W1) = 0 and a_001_a(W2) NE 4) into 0`
* `6 into 998`
* `7 into 997`
* `NA into 999`

**R script:**

```{r harmo2 5, echo=TRUE}
JSTAR_aksst_merge_w12 <- left_join(JSTAR_aksst_w2_divorce, JSTAR_ds_aksst_w1, by='id')
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_merge_w12$id)

JSTAR_aksst_merge_w12$divorce <- car::recode(as.vector(JSTAR_aksst_merge_w12$divorce), "NA='-999'")
JSTAR_aksst_merge_w12$a_001_a <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_001_a), "NA='-999'")

JSTAR_ds_aksst_w2$divorce <- c(NA)
for(i in 1:dim(JSTAR_aksst_merge_w12)[1]){
  if( JSTAR_aksst_merge_w12$divorce[i] == 1 | JSTAR_aksst_merge_w12$a_001_a[i] == 4 ) {
    JSTAR_ds_aksst_w2$divorce[i] = 1 }
  else if( JSTAR_aksst_merge_w12$divorce[i] == 0 & JSTAR_aksst_merge_w12$a_001_a[i] %in% c(1,2,3,5) ) { 
    JSTAR_ds_aksst_w2$divorce[i] = 0 }
  else if( JSTAR_aksst_merge_w12$a_001_a[i] == 6 ) { 
    JSTAR_ds_aksst_w2$divorce[i] = 998 }
  else if( JSTAR_aksst_merge_w12$a_001_a[i] == 7 ) { 
    JSTAR_ds_aksst_w2$divorce[i] = 997 }
}

JSTAR_ds_aksst_w2$divorce <- car::recode(as.vector(JSTAR_ds_aksst_w2$divorce), "NA='999'")
JSTAR_ds_aksst_w2$divorce <- labelled(JSTAR_ds_aksst_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 5, echo=F}
vari <- JSTAR_ds_aksst_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2 5, echo=F}

```

 
### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `11A-001: CHANGES IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that divorce passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`

* Name: `divorce` **from Wave2**


* Description: 
```{r assign3 5, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_divorce','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('a_001_a'), missings = TRUE)
```

```{r local3 5, echo=F}
JSTAR_aksst_w3_divorce <- opal.execute(o,'JSTAR_aksst_w3_divorce')
vari <- JSTAR_aksst_w3_divorce$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w3_divorce$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_divorce, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `(divorce(W2) = 1 or a_001_a(W3) = 4) into 1`
* `(divorce(W2) = 0 and a_001_a(W3) NE 4) into 0`
* `6 into 998`
* `7 into 997`
* `NA into 999`

**R script:**

```{r harmo3 5, echo=TRUE}

JSTAR_aksst_merge_w23 <- left_join(JSTAR_aksst_w3_divorce, JSTAR_ds_aksst_w2, by='id')

JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_merge_w23$id)

JSTAR_aksst_merge_w23$divorce <- car::recode(as.vector(JSTAR_aksst_merge_w23$divorce), "NA='-999'")
JSTAR_aksst_merge_w23$a_001_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_001_a), "NA='-999'")

JSTAR_ds_aksst_w3$divorce <- c(NA)
for(i in 1:dim(JSTAR_aksst_merge_w23)[1]){
  if( JSTAR_aksst_merge_w23$divorce[i] == 1 | JSTAR_aksst_merge_w23$a_001_a[i] == 4 ) { 
    JSTAR_ds_aksst_w3$divorce[i] = 1 }
  else if( JSTAR_aksst_merge_w23$divorce[i] == 0 & JSTAR_aksst_merge_w23$a_001_a[i] %in% c(1,2,3,5) ) { 
    JSTAR_ds_aksst_w3$divorce[i] = 1 }
  else if( JSTAR_aksst_merge_w12$a_001_a[i] == 6 ) { 
    JSTAR_ds_aksst_w2$divorce[i] = 998 }
  else if( JSTAR_aksst_merge_w12$a_001_a[i] == 7 ) { 
    JSTAR_ds_aksst_w2$divorce[i] = 997 }
}

JSTAR_ds_aksst_w3$divorce <- car::recode(as.vector(JSTAR_ds_aksst_w3$divorce), "NA='999'")
JSTAR_ds_aksst_w3$divorce <- labelled(JSTAR_ds_aksst_w3$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 5, echo=F}
vari <- JSTAR_ds_aksst_w3$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_aksst_w3$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of divorce/separation") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3 5, echo=F}

```


## tn  

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: `A-007:REASON FOR NOT HAVING A SPOUSE`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is dead`
    + `3 = I am divorced`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Description: 
```{r assign1 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_divorce','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_007'), missings = TRUE)
```

```{r local1 2, echo=F}
JSTAR_tn_w1_divorce <- opal.execute(o,'JSTAR_tn_w1_divorce')
vari <-  JSTAR_tn_w1_divorce$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w1_divorce$a_007, missing_values = NA)
ggplot(JSTAR_tn_w1_divorce, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("A-007:REASON FOR NOT HAVING A SPOUSE") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 into 1`
* `1,2 into 0`
* `4 Don't know into 998`
* `5 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1 2, echo=TRUE}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_divorce$id)
JSTAR_ds_tn_w1$divorce <- car::recode(as.vector(JSTAR_tn_w1_divorce$a_007), "3='1'; 1:2='0'; 4='998'; 5='997'; NA='999'")
JSTAR_ds_tn_w1$divorce <- labelled(JSTAR_ds_tn_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 2, echo=F}
vari <- JSTAR_ds_tn_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2, echo=F}

```

 

### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that divorce passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`
    
* Name: `divorce` **from wave1**

* Description: 
```{r assign2 2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_divorce','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('a_001_a'), missings = TRUE)
```

```{r local2 2, echo=F}
JSTAR_tn_w2_divorce <- opal.execute(o,'JSTAR_tn_w2_divorce')
vari <-  JSTAR_tn_w2_divorce$a_001_a
kable(Categorical_summary(vari, missing_values = c(6,7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(6,7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6,7))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w2_divorce$a_001_a, missing_values = NA)
ggplot(JSTAR_tn_w2_divorce, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `(divorce(W1) = 1 or a_001_a(W2) = 4) into 1`
* `(divorce(W1) = 0 and a_001_a(W2) NE 4) into 0`
* `6 into 998`
* `7 into 997`
* `NA into 999`

**R script:**

```{r harmo2 2, echo=TRUE}

JSTAR_tn_merge_w12 <- left_join(JSTAR_tn_w2_divorce, JSTAR_ds_tn_w1, by='id')

JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_merge_w12$id)

JSTAR_tn_merge_w12$divorce <- car::recode(as.vector(JSTAR_tn_merge_w12$divorce), "NA='-999'")
JSTAR_tn_merge_w12$a_001_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_001_a), "NA='-999'")

JSTAR_ds_tn_w2$divorce <- c(NA)
for(i in 1:dim(JSTAR_tn_merge_w12)[1]){
  if( JSTAR_tn_merge_w12$divorce[i] == 1 | JSTAR_tn_merge_w12$a_001_a[i] == 4 ) { 
    JSTAR_ds_tn_w2$divorce[i] = 1 }
  else if( JSTAR_tn_merge_w12$divorce[i] == 0 & JSTAR_tn_merge_w12$a_001_a[i] %in% c(1,2,3,5) ) { 
    JSTAR_ds_tn_w2$divorce[i] = 1 }
  else if( JSTAR_tn_merge_w12$a_001_a[i] == 6 ) { 
    JSTAR_ds_tn_w2$divorce[i] = 998 }
  else if( JSTAR_tn_merge_w12$a_001_a[i] == 7 ) { 
    JSTAR_ds_tn_w2$divorce[i] = 997 }
}

JSTAR_ds_tn_w2$divorce <- car::recode(as.vector(JSTAR_ds_tn_w2$divorce), "NA='999'")
JSTAR_ds_tn_w2$divorce <- labelled(JSTAR_ds_tn_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2, echo=F}
vari <- JSTAR_ds_tn_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_tn_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_tn_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2 2, echo=F}

```

## cth

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_007`
* Label: `A-007:REASON FOR NOT HAVING A SPOUSE`
* Categories: 
    + `1 = I have never been married`
    + `2 = My spouse is deceased`
    + `3 = I am divorced`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`


* Description: 
```{r assign1 3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_divorce','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_007'), missings = TRUE)
```

```{r local1 3, echo=F}
JSTAR_cth_w1_divorce <- opal.execute(o,'JSTAR_cth_w1_divorce')
vari <-  JSTAR_cth_w1_divorce$a_007
kable(Categorical_summary(vari, missing_values = c(4,5))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_w1_divorce$a_007, missing_values = NA)
ggplot(JSTAR_cth_w1_divorce, aes(x=factor(a_007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital or common-law partner?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 into 1`
* `1,2 into 0`
* `4 Don't know into 998`
* `5 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1 3, echo=TRUE}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_divorce$id)
JSTAR_ds_cth_w1$divorce <- car::recode(as.vector(JSTAR_cth_w1_divorce$a_007), "3='1'; 1:2='0'; 4='998'; 5='997'; NA='999'")
JSTAR_ds_cth_w1$divorce <- labelled(JSTAR_ds_cth_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 3, echo=F}
vari <- JSTAR_ds_cth_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_ds_cth_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_ds_cth_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 3, echo=F}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", toupper(names(l.hds)))
kable(t.hds)

```



 
```{r save, echo=FALSE}


divorce <- JSTAR_ds_aksst_w1
save(divorce, file = "../RData/aksst_w1/divorce.RData")
rm(divorce)

divorce <- JSTAR_ds_aksst_w2
save(divorce, file = "../RData/aksst_w2/divorce.RData")
rm(divorce)

divorce <- JSTAR_ds_aksst_w3
save(divorce, file = "../RData/aksst_w3/divorce.RData")
rm(divorce)

divorce <- JSTAR_ds_tn_w1
save(divorce, file = "../RData/tn_w1/divorce.RData")
rm(divorce)

divorce <- JSTAR_ds_tn_w2
save(divorce, file = "../RData/tn_w2/divorce.RData")
rm(divorce)

divorce <- JSTAR_ds_cth_w1
save(divorce, file = "../RData/cth_w1/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


