---
title: "Loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lonelinessDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lonelinessDS.R')
```

# Data process

## AKSST

### Wave 1 

#### Study-specific variable description



| **Name** | `tome58`|
|-|-|
| **Label** | `Q8:MENTAL CONDITION FOR THE PAST WEEK -14- DID YOU FEEL LONELY?`|
| **Table name** |`jstar_2007_5cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign1AKSST, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('tome58'), missings = TRUE)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local1AKSST, echo=F}
vbl <- JSTAR_aksst_w1$tome58
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "tome58")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(tome58))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MENTAL CONDITION FOR THE PAST WEEK - DID YOU FEEL LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo1AKSST}

JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$loneliness <- car::recode(as.vector(JSTAR_aksst_w1$tome58), "2:4='1'; 1='0'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1AKSST, echo=F}
vbl <- JSTAR_ds_aksst_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```



'
### Wave 2

#### Study-specific variable description



| **Name** | `tome114`|
|-|-|
| **Label** | `Q8:MENTAL CONDITION FOR THE PAST WEEK -14- DID YOU FEEL LONELY?`|
| **Table name** |`jstar_2009_5cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign2AKSST, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('tome114'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local2AKSST, echo=F}

vbl <- JSTAR_aksst_w2$tome114
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "tome114")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(tome114))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MENTAL CONDITION FOR THE PAST WEEK - DID YOU FEEL LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo2AKSST}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$loneliness <- car::recode(as.vector(JSTAR_aksst_w2$tome114), "2:4='1'; 1='0'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript2AKSST, echo=F}
vbl <- JSTAR_ds_aksst_w2$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2AKSST, echo=F}

```





### Wave 3

#### Study-specific variable description



| **Name** | `q8_14`|
|-|-|
| **Label** | `11Q8:CONDITION LAST WEEK -14- FELT LONELY`|
| **Table name** |`jstar_2011_5cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`.m`<br/>`NA`|
| **Description** |  |


```{r assign3AKSST, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('q8_14'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local3AKSST, echo=F}
vbl <- JSTAR_aksst_w3$q8_14
kable(Categorical_summary(vbl, missing_values = c('.m'))[3], caption = "q8_14")
kable(Categorical_summary(vbl, missing_values = c('.m'))[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(q8_14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONDITION LAST WEEK - FELT LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `.m,NA into 999`

**R script:**

```{r harmo3AKSST}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$loneliness <- car::recode(as.vector(JSTAR_aksst_w3$q8_14), "2:4='1'; 1='0'; NA='999'; '.m' = 999")

```

#### Statistics of the new harmonised variable
```{r descript3AKSST, echo=F}
vbl <- JSTAR_ds_aksst_w3$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3AKSST, echo=F}

```


## TN

### Wave 1 

#### Study-specific variable description



| **Name** | `tome58`|
|-|-|
| **Label** | `Q8:MENTAL CONDITION FOR THE PAST WEEK -14- DID YOU FEEL LONELY?`|
| **Table name** |`jstar_2009_2cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign1TN, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('tome58'), missings = TRUE)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local1TN, echo=F}
vbl <- JSTAR_tn_w1$tome58
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "tome58")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(tome58))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MENTAL CONDITION FOR THE PAST WEEK - DID YOU FEEL LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo1TN}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$loneliness <- car::recode(as.vector(JSTAR_tn_w1$tome58), "2:4='1'; 1='0'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1TN, echo=F}
vbl <- JSTAR_ds_tn_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1TN, echo=F}

```





### Wave 2

#### Study-specific variable description



| **Name** | `q8_14`|
|-|-|
| **Label** | `11Q8:CONDITION LAST WEEK -14- FELT LONELY`|
| **Table name** |`jstar_2011_2cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign2TN, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('q8_14'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local2TN, echo=F}
vbl <- JSTAR_tn_w2$q8_14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q8_14")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(q8_14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("CONDITION LAST WEEK - FELT LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo2TN}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$loneliness <- car::recode(as.vector(JSTAR_tn_w2$q8_14), "2:4='1'; 1='0'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript2TN, echo=F}
vbl <- JSTAR_ds_tn_w2$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2TN, echo=F}

```



## CTH

### Wave 1 

#### Study-specific variable description



| **Name** | `q8_14`|
|-|-|
| **Label** | `11Q8:MENTAL CONDITION LAST WEEK -14- FELT LONELY`|
| **Table name** |`jstar_2011_3cities`|
| **Categories** |`1 = Not at all`<br/>`2 = 1-2 days`<br/>`3 = 3-4 days`<br/>`4 = 5 days or more`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign1CTH, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('q8_14'), missings = TRUE)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')
```

```{r local1CTH, echo=F}
vbl <- JSTAR_cth_w1$q8_14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q8_14")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(q8_14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MENTAL CONDITION LAST WEEK - FELT LONELY?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo1CTH}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$loneliness <- car::recode(as.vector(JSTAR_cth_w1$q8_14), "2:4='1'; 1='0'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1CTH, echo=F}
vbl <- JSTAR_ds_cth_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1CTH, echo=F}

```









## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:







```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

