---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## aksst

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_003`
* Label: `A-003:EXISTENCE OF MARITAL OR COMMON-LAW PARTNAER`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`

* Description: 
```{r assign1-5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_spouse','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('a_003'), missings = TRUE)
```

```{r local1-5}
JSTAR_aksst_w1_spouse <- opal.execute(o,'JSTAR_aksst_w1_spouse')
vari <- JSTAR_aksst_w1_spouse$a_003
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_spouse$a_003, missing_values = NA)
ggplot(JSTAR_aksst_w1_spouse, aes(x=factor(a_003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital or common-law partner?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `3 Don't know into 998`
* `4 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1-5, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_spouse$id)
JSTAR_aksst_ds_w1$spouse <- car::recode(as.vector(JSTAR_aksst_w1_spouse$a_003), "1='1'; 2='0'; 3='998'; 4='997'; NA='999'")
JSTAR_aksst_ds_w1$spouse <- labelled(JSTAR_aksst_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1-5}
vari <- JSTAR_aksst_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1-5}
AfterH <- table(JSTAR_aksst_ds_w1$spouse)
BeforeH <- table(JSTAR_aksst_w1_spouse$a_003, useNA='ifany')
BeforeH <- c(BeforeH[2], BeforeH[1], BeforeH[3], BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","4->997", "NA->999")
kable(C)

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`

* Description: 
```{r assign2-5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_spouse','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('a_001_a'), missings = TRUE)
```

```{r local2-5}
JSTAR_aksst_w2_spouse <- opal.execute(o,'JSTAR_aksst_w2_spouse')
vari <- JSTAR_aksst_w2_spouse$a_001_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w2_spouse$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w2_spouse, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `(a_003(W1) = 2 AND a_001_a(W2) in (1,3,4)) OR (a_003=1 AND a_001_a in (3,4)) into 0`
* `(a_003(W1) = 1 AND a_001_a(W2) in (1,2)) OR (a_003=2 AND a_001_a = 2) into 1`
* `NA into 999`

**R script:**

```{r harmo2-5, echo=TRUE}

# ID - MERGE - FUNCTION:
#old: table with different number of individuals with the information that you need
#new: table with the individuals that you want

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_001_a=new$a_001_a, a_003=new_2$a_003)  # a_003(W1), a_001_a(W2)
  new_22
}

# old = JSTAR_aksst_w1_spouse
# new = JSTAR_aksst_w2_spouse


JSTAR_aksst_merge_w12 <- same_indiv(JSTAR_aksst_w1_spouse, JSTAR_aksst_w2_spouse)

JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_spouse$id)

JSTAR_aksst_merge_w12$a_003 <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_003), "NA='-999'")
JSTAR_aksst_merge_w12$a_001_a  <- car::recode(as.vector(JSTAR_aksst_merge_w12$a_001_a), "NA='-999'")

JSTAR_aksst_ds_w2$spouse <- c(NA)  # I think it is required
for(i in 1:dim(JSTAR_aksst_merge_w12)[1]){
  if( (JSTAR_aksst_merge_w12$a_003[i] == 2 & JSTAR_aksst_merge_w12$a_001_a[i] %in% c(1,3,4))
      | (JSTAR_aksst_merge_w12$a_003[i] == 1 & JSTAR_aksst_merge_w12$a_001_a[i] %in% c(3,4))
  ) { JSTAR_aksst_ds_w2$spouse[i] = 0 }
  else if( (JSTAR_aksst_merge_w12$a_003[i] == 1 & JSTAR_aksst_merge_w12$a_001_a[i] %in% c(1,2))
      | (JSTAR_aksst_merge_w12$a_003[i] == 2 & JSTAR_aksst_merge_w12$a_001_a[i] == 2)
       ) { JSTAR_aksst_ds_w2$spouse[i] = 1 }
}

JSTAR_aksst_ds_w2$spouse <- car::recode(as.vector(JSTAR_aksst_ds_w2$spouse), "NA='999'")
JSTAR_aksst_ds_w2$spouse <- labelled(JSTAR_aksst_ds_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2-5}
vari <- JSTAR_aksst_ds_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2-5}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `11A-001: CHANGES IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`

* Description: 
```{r assign3-5}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_spouse','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('a_001_a'), missings = TRUE)
```

```{r local3-5}
JSTAR_aksst_w3_spouse <- opal.execute(o,'JSTAR_aksst_w3_spouse')
vari <- JSTAR_aksst_w3_spouse$a_001_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_spouse$a_001_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_spouse, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

`if (JSTAR_aksst_ds_w2$spouse=0 AND a_001_a in (1,3,4)) OR (JSTAR_aksst_ds_w2$spouse=1 AND a_001_a in (3,4)) recode into 0;`
`if (JSTAR_aksst_ds_w2$spouse=1 AND  a_001_a in (1,2)) OR (JSTAR_aksst_ds_w2$spouse=0 AND a_001_a=2) recode into 1;`
`NA into 999`

**R script:**

```{r harmo3-5, echo=TRUE}

# ID - MERGE - FUNCTION:

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_001_a=new$a_001_a, spouse=new_2$spouse) 
  new_22
}

# old = JSTAR_aksst_ds_w2
# new = JSTAR_aksst_w3_spouse

JSTAR_aksst_merge_w23 <- same_indiv(JSTAR_aksst_ds_w2, JSTAR_aksst_w3_spouse)



JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_spouse$id)

JSTAR_aksst_merge_w23$spouse <- car::recode(as.vector(JSTAR_aksst_merge_w23$spouse), "NA='-999'")
JSTAR_aksst_merge_w23$a_001_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_001_a), "NA='-999'")

JSTAR_aksst_ds_w3$spouse <- c(NA)  # I think it is required
for(i in 1:dim(JSTAR_aksst_merge_w23)[1]){
  if( (JSTAR_aksst_merge_w23$spouse[i] == 0 & JSTAR_aksst_merge_w23$a_001_a[i] %in% c(1,3,4))
      | (JSTAR_aksst_merge_w23$spouse[i] == 1 & JSTAR_aksst_merge_w23$a_001_a[i] %in% c(3,4))
  ) { JSTAR_aksst_ds_w3$spouse[i] = 0 }
  else if( (JSTAR_aksst_merge_w23$spouse[i] == 1 & JSTAR_aksst_merge_w23$a_001_a[i] %in% c(1,2))
      | (JSTAR_aksst_merge_w23$spouse[i] == 0 & JSTAR_aksst_merge_w23$a_001_a[i] == 2)
       ) { JSTAR_aksst_ds_w3$spouse[i] = 1 }
}

JSTAR_aksst_ds_w3$spouse <- car::recode(as.vector(JSTAR_aksst_ds_w3$spouse), "NA='999'")
JSTAR_aksst_ds_w3$spouse <- labelled(JSTAR_aksst_ds_w3$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3-5}
vari <- JSTAR_aksst_ds_w3$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has spouse/partner") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3-5}

```

 
 



## cth
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_003`
* Label: `A-003:HAS MARITAL OR COMMON-LAW PARTNER`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`

* Description: 
```{r assign1-3}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_spouse','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_003'), missings = TRUE)
```

```{r local1-3}
JSTAR_cth_w1_spouse <- opal.execute(o,'JSTAR_cth_w1_spouse')
vari <- JSTAR_cth_w1_spouse$a_003
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_cth_w1_spouse$a_003, missing_values = NA)
ggplot(JSTAR_cth_w1_spouse, aes(x=factor(a_003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital or common-law partner?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `3 Don't know into 998`
* `4 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1-3, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_spouse$id)
JSTAR_cth_ds_w1$spouse <- car::recode(as.vector(JSTAR_cth_w1_spouse$a_003), "1='1'; 2='0'; 3='998'; 4='997'; NA='999'")
JSTAR_cth_ds_w1$spouse <- labelled(JSTAR_cth_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1-3}
vari <- JSTAR_cth_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1-3}
AfterH <- table(JSTAR_cth_ds_w1$spouse)
BeforeH <- table(JSTAR_cth_w1_spouse$a_003, useNA='ifany')
BeforeH <- c(BeforeH[2], BeforeH[1], BeforeH[3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","4->997")
kable(C)

```

 
 




## tn
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_003`
* Label: `A-003:HAS MARITAL OR COMMON-LAW PARTNAER`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_spouse','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_003'), missings = TRUE)
```

```{r local1}
JSTAR_tn_w1_spouse <- opal.execute(o,'JSTAR_tn_w1_spouse')
vari <- JSTAR_tn_w1_spouse$a_003
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_spouse$a_003, missing_values = NA)
ggplot(JSTAR_tn_w1_spouse, aes(x=factor(a_003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital or Common-law partner?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `3 Don't know into 998`
* `4 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_spouse$id)
JSTAR_tn_ds_w1$spouse <- car::recode(as.vector(JSTAR_tn_w1_spouse$a_003), "1='1'; 2='0'; 3='998'; 4='997'; NA='999'")
JSTAR_tn_ds_w1$spouse <- labelled(JSTAR_tn_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- JSTAR_tn_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(JSTAR_tn_ds_w1$spouse)
BeforeH <- table(JSTAR_tn_w1_spouse$a_003, useNA='ifany')
BeforeH <- c(BeforeH[2], BeforeH[1], BeforeH[3], BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","4->997", "NA->999")
kable(C)

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `a_001_a`
* Label: `A-001: CHANGE IN MARITAL STATUS`
* Categories: 
    + `1.0 = Same`
    + `2.0 = (Re-)married in ___`
    + `3.0 = After that spouse passed away in ____`
    + `4.0 = Divorced in ___`
    + `5.0 = Other (specify)`
* Missings:    
    + `6.0 = Don't know`
    + `7.0 = Refused to answer`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_spouse','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('a_001_a'), missings = TRUE)
```

```{r local2}
JSTAR_tn_w2_spouse <- opal.execute(o,'JSTAR_tn_w2_spouse')
JSTAR_tn_w1_spouse <- opal.execute(o,'JSTAR_tn_w1_spouse')
vari <- JSTAR_tn_w2_spouse$a_001_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_spouse$a_001_a, missing_values = NA)
ggplot(JSTAR_tn_w2_spouse, aes(x=factor(a_001_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in marital status") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `(a_003(W1) = 2 AND a_001_a(W2) in (1,3,4)) OR (a_003=1 AND a_001_a in (3,4)) into 0`
* `(a_003(W1) = 1 AND a_001_a(W2) in (1,2)) OR (a_003=2 AND a_001_a = 2) into 1`
* `NA into 999`


**R script:**

```{r harmo2, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_001_a=new$a_001_a, a_003=new_2$a_003) 
  new_22
}

# old = JSTAR_tn_w1_spouse
# new = JSTAR_tn_w2_spouse

JSTAR_tn_merge_w12 <- same_indiv(JSTAR_tn_w1_spouse, JSTAR_tn_w2_spouse)



JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_spouse$id)

JSTAR_tn_merge_w12$a_003 <- car::recode(as.vector(JSTAR_tn_merge_w12$a_003), "NA='-999'")
JSTAR_tn_merge_w12$a_001_a <- car::recode(as.vector(JSTAR_tn_merge_w12$a_001_a), "NA='-999'")

JSTAR_tn_ds_w2$spouse <- c(NA)  # I think it is required
for(i in 1:dim(JSTAR_tn_merge_w12)[1]){
  if( (JSTAR_tn_merge_w12$a_003[i] == 2 & JSTAR_tn_merge_w12$a_001_a[i] %in% c(1,3,4))
      | (JSTAR_tn_merge_w12$a_003[i] == 1 & JSTAR_tn_merge_w12$a_001_a[i] %in% c(3,4))
  ) { JSTAR_tn_ds_w2$spouse[i] = 0 }
  else if( (JSTAR_tn_merge_w12$a_003[i] == 1 & JSTAR_tn_merge_w12$a_001_a[i] %in% c(1,2))
      | (JSTAR_tn_merge_w12$a_003[i] == 2 & JSTAR_tn_merge_w12$a_001_a[i] == 2)
       ) { JSTAR_tn_ds_w2$spouse[i] = 1 }
}

JSTAR_tn_ds_w2$spouse <- car::recode(as.vector(JSTAR_tn_ds_w2$spouse), "NA='999'")
JSTAR_tn_ds_w2$spouse <- labelled(JSTAR_tn_ds_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- JSTAR_tn_ds_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2}

```

 
 


```{r save, echo=FALSE}
spouse <- JSTAR_tn_ds_w1
save(spouse, file = "../RData/tn_w1/spouse.RData")
rm(spouse)

spouse <- JSTAR_tn_ds_w2
save(spouse, file = "../RData/tn_w2/spouse.RData")
rm(spouse)


spouse <- JSTAR_aksst_ds_w1
save(spouse, file = "../RData/aksst_w1/spouse.RData")
rm(spouse)

spouse <- JSTAR_aksst_ds_w2
save(spouse, file = "../RData/aksst_w2/spouse.RData")
rm(spouse)

spouse <- JSTAR_aksst_ds_w3
save(spouse, file = "../RData/aksst_w3/spouse.RData")
rm(spouse)

spouse <- JSTAR_cth_ds_w1
save(spouse, file = "../RData/cth_w1/spouse.RData")
rm(spouse)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```