---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## aksst

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_010`
* Label: `A-010:EXISTENCE OF CHILD`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`

* Description: 
```{r assign1 5cities}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_child','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('a_010'), missings = TRUE)
```

```{r local1 5cities}
JSTAR_aksst_w1_child <- opal.execute(o,'JSTAR_aksst_w1_child')
vari <-  JSTAR_aksst_w1_child$a_010
kable(Categorical_summary(vari, missing_values = c(3,4))[3]) 
kable(Categorical_summary(vari, missing_values = c(3,4))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(3,4))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_child$a_010, missing_values = NA)
ggplot(JSTAR_aksst_w1_child, aes(x=factor(a_010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Existence of child") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `3 Don't know into 998`
* `4 Refused to answer into 997`
* `NA into 999`

**R script:**

```{r harmo1 5cities, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_child$id)
JSTAR_aksst_ds_w1$child <- car::recode(as.vector(JSTAR_aksst_w1_child$a_010), "1='1'; 2='0'; 3='998'; 4='997'; NA='999'")
JSTAR_aksst_ds_w1$child <- labelled(JSTAR_aksst_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 5cities}
vari <- JSTAR_aksst_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 5cities}
AfterH <- table(JSTAR_aksst_ds_w1$child)
BeforeH <- table(JSTAR_aksst_w1_child$a_010, useNA='ifany')
BeforeH <- c(BeforeH[2:1], BeforeH[3:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1", "4->997", "NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_004`
* Label: `A-004:CHANGES IN THE NUMBER OF CHILDREN`
* Categories: 
    + `1 = Same`
    + `2 = Number of children increased`
    + `3 = Number of children decreased`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Name: `a_004_1_1_a`
* Label: `A-004-1-1:CONFIRMATION ON THE FIRST CHILD'S INFORMATION`
* Categories: 
    + `1 = No change`
    + `2 = Passed on (year and month)`
    + `3 = Other(Specify)`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Name: `a_004_1_2_a`
* Label: `A-004-1-2:CONFIRMATION ON THE SECOND CHILD'S INFORMATION`
* Categories: 
    + `1 = No change`
    + `2 = Passed on (year and month)`
    + `3 = Other(Specify)`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Name: `a_004_1_3_a`
* Label: `A-004-1-3:CONFIRMATION ON THE THIRD CHILD'S INFORMATION`
* Categories: 
    + `1 = No change`
    + `2 = Passed on (year and month)`
    + `3 = Other(Specify)`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Name: `a_004_1_4_a`
* Label: `A-004-1-1:CONFIRMATION ON THE FOURTH CHILD'S INFORMATION`
* Categories: 
    + `1 = No change`
    + `2 = Passed on (year and month)`
    + `3 = Other(Specify)`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    
* Name: `a_004_1_5_a`
* Label: `A-004-1-1:CONFIRMATION ON THE FIFTH CHILD'S INFORMATION`
* Categories: 
    + `1 = No change`
    + `2 = Passed on (year and month)`
    + `3 = Other(Specify)`
* Missings:    
    + `4 = Don't know`
    + `5 = Refused to answer`
    

    
    
* FROM THE FIRST WAVE:

* Name: `a_010`
* Label: `A-010:EXISTENCE OF CHILD`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_011_b`
* Label: `A-011:NUMBER OF CHILDREN`

     

* Description: 
```{r assign2 5cities}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_child','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('a_004','a_004', 'a_004_1_1_a', 'a_004_1_2_a','a_004_1_3_a',
                                        'a_004_1_4_a', 'a_004_1_5_a'), missings = TRUE)

opal.assign.table.tibble(o, 'JSTAR_aksst_w1_w2_child','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_010','a_011_b'), missings = TRUE)
```

```{r local2 5cities}
JSTAR_aksst_w2_child <- opal.execute(o,'JSTAR_aksst_w2_child')

vari <- JSTAR_aksst_w2_child$a_004
kable(Categorical_summary(vari, missing_values = c(4,5))[3]) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_child$a_004, missing_values = NA)
ggplot(JSTAR_aksst_w2_child, aes(x=factor(a_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Changes in the number of children") + ylab("Frequency")

vari <- JSTAR_aksst_w2_child$a_004
kable(Categorical_summary(vari, missing_values = c(4,5))[3]) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_child$a_004, missing_values = NA)
ggplot(JSTAR_aksst_w2_child, aes(x=factor(a_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Changes in the number of children") + ylab("Frequency")

vari <- JSTAR_aksst_w2_child$a_004_1_1_a
kable(Categorical_summary(vari, missing_values = c(4,5))[3]) 
kable(Categorical_summary(vari, missing_values = c(4,5))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(4,5))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w2_child$a_004_1_1_a, missing_values = NA)
ggplot(JSTAR_aksst_w2_child, aes(x=factor(a_004_1_1_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Confirmation of the 1st child information") + ylab("Frequency")
# same up to a_004_1_5_a



JSTAR_aksst_w1_w2_child <- opal.execute(o,'JSTAR_aksst_w1_w2_child')

vari <- JSTAR_aksst_w1_w2_child$a_010
kable(Categorical_summary(vari, missing_values = c(3,4))[3]) 
kable(Categorical_summary(vari, missing_values = c(3,4))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(3,4))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_w2_child$a_010, missing_values = NA)
ggplot(JSTAR_aksst_w1_w2_child, aes(x=factor(a_010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Existence of child") + ylab("Frequency")

vari <- JSTAR_aksst_w1_w2_child$a_011_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w1_w2_child$a_011_b, missing_values = NA)
ggplot(JSTAR_aksst_w1_w2_child, aes(x=factor(a_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 


* `IF ( a_010(W1)=2 AND a_004(W2)=1 ) OR { a_010(W1)=1 AND `
`[ (a_011_b(W1)=1 AND a_004_1_1_a=2) OR  `
`(a_011_b(W1)=2 AND a_004_1_1_a=2 AND  a_004_1_2_a=2) OR `
`(a_011_b(W1)=3 AND a_004_1_1_a=2 AND  a_004_1_2_a=2 AND a_004_1_3_a=2) OR `
`(a_011_b(W1)=4 AND a_004_1_1_a=2 AND  a_004_1_2_a=2 AND a_004_1_3_a=2 AND a_004_1_4_a=2) OR `
`(a_011_b(W1)=5 AND a_004_1_1_a=2 AND  a_004_1_2_a=2 AND a_004_1_3_a=2 AND a_004_1_4_a=2 AND a_004_1_5_a=2) OR `
`(a_011_b(W1)=6AND a_004_1_1_a=2 AND  a_004_1_2_a=2 AND a_004_1_3_a=2 AND a_004_1_4_a=2 AND a_004_1_5_a=2  ]}`
` RECODE INTO 0.`
* `IF ( a_010(W1)=1 and a_004(W2)=1 ) OR ( a_010(W1)=2 and a_004=2 ) RECODE INTO 1.`



**R script:**

```{r harmo2 5cities, echo=TRUE}

# ID - MERGE - FUNCTION:
#old: table with different number of individuals with the information that you need
#new: table with the individuals that you want

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_004=new$a_004, a_004_1_1_a=new$a_004_1_1_a, a_004_1_2_a=new$a_004_1_2_a,
                       a_004_1_3_a=new$a_004_1_3_a, a_004_1_4_a=new$a_004_1_4_a, a_004_1_5_a=new$a_004_1_5_a,
                       a_010=new_2$a_010, a_011_b=new_2$a_011_b)
  new_22
}

# old = JSTAR_aksst_w1_w2_child, with variables a_010,a_011_b
# new = JSTAR_aksst_w2_child, with variables a_004,a_004_1_1_a,a_004_1_2_a,a_004_1_3_a,a_004_1_4_a,a_004_1_5_a

JSTAR_aksst_merge_w12 <- same_indiv(old=JSTAR_aksst_w1_w2_child, new=JSTAR_aksst_w2_child)


JSTAR_aksst_merge_w12$a_010 <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_010), "NA='-999'")
JSTAR_aksst_merge_w12$a_004 <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004), "NA='-999'")
JSTAR_aksst_merge_w12$a_011_b <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_011_b), "NA='-999'")
JSTAR_aksst_merge_w12$a_004_1_1_a <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004_1_1_a), "NA='-999'")
JSTAR_aksst_merge_w12$a_004_1_2_a <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004_1_2_a), "NA='-999'")
JSTAR_aksst_merge_w12$a_004_1_3_a <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004_1_3_a), "NA='-999'")
JSTAR_aksst_merge_w12$a_004_1_4_a <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004_1_4_a), "NA='-999'")
JSTAR_aksst_merge_w12$a_004_1_5_a <-car::recode(as.vector(JSTAR_aksst_merge_w12$a_004_1_5_a), "NA='-999'")

  
         

JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_child$id)
JSTAR_aksst_ds_w2$child <- c(NA)   
for(i in 1:dim(JSTAR_aksst_merge_w12)[1]){
  if( (JSTAR_aksst_merge_w12$a_010[i] == 2 & JSTAR_aksst_merge_w12$a_004[i] == 1 ) |
      (JSTAR_aksst_merge_w12$a_010[i] == 1 & (
        # 1 child and passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 1 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2) |
        # 2 children and both passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_2_a[i] == 2) |
        # 3 children and all passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 3 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_2_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_3_a[i] == 2) |
        # 4 children and all passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 4 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_2_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_3_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_4_a[i] == 2) |
        # 5 children and all passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 5 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_2_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_3_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_4_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_5_a[i] == 2) |
        # 6 children and all passed:
        (JSTAR_aksst_merge_w12$a_011_b[i] == 6 & JSTAR_aksst_merge_w12$a_004_1_1_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_2_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_3_a[i] == 2
         & JSTAR_aksst_merge_w12$a_004_1_4_a[i] == 2 & JSTAR_aksst_merge_w12$a_004_1_5_a[i] == 2 ))
      )
  ) { JSTAR_aksst_ds_w2$child[i] = 0 }
  else if( (JSTAR_aksst_merge_w12$a_010[i] == 1 & JSTAR_aksst_merge_w12$a_004[i] == 1) |
      (JSTAR_aksst_merge_w12$a_010[i] == 2 & JSTAR_aksst_merge_w12$a_004[i] == 2)
       ) { JSTAR_aksst_ds_w2$child[i] = 1 }
}

JSTAR_aksst_ds_w2$child <- car::recode(as.vector(JSTAR_aksst_ds_w2$child), "NA='999'")
JSTAR_aksst_ds_w2$child <- labelled(JSTAR_aksst_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 5cities}
vari <- JSTAR_aksst_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2 5cities}

```

 
 



### Wave 3

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `a_004_a`
* Label: `11A-004:CHANGES IN THE NUMBER OF CHILDREN`
* Categories: 
    + `1 = No change`
    + `2 = The number of sons/daughters increased by (__) or decreased by (__)`
* Missings:    
    + `3 = Don't know`
    + `4 = Refused to answer`
    
    
* Name: `a_004_0_1_b`
* Label: `1A-004-0:CONFIRMATION ON THE 1ST CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_2_b`
* Label: `1A-004-0:CONFIRMATION ON THE 2ND CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_3_b`
* Label: `1A-004-0:CONFIRMATION ON THE 3RD CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_4_b`
* Label: `1A-004-0:CONFIRMATION ON THE 4TH CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_5_b`
* Label: `1A-004-0:CONFIRMATION ON THE 5TH CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`


* Name: `a_004_0_1_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 1ST CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_2_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 2ND CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_3_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 3RD CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_4_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 4TH CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_1_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 5TH CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`



* Description: 
```{r assign3 5cities}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_child','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('a_004_a','a_004_0_1_b','a_004_0_2_b','a_004_0_3_b',
                                        'a_004_0_4_b','a_004_0_5_b','a_004_0_1_h','a_004_0_2_h',
                                        'a_004_0_3_h','a_004_0_4_h','a_004_0_5_h'), missings = TRUE)
```

```{r local3 5cities}
JSTAR_aksst_w3_child <- opal.execute(o,'JSTAR_aksst_w3_child')

vari <- JSTAR_aksst_w3_child$a_004_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_child$a_004_a, missing_values = NA)
ggplot(JSTAR_aksst_w3_child, aes(x=factor(a_004_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in the number of children") + ylab("Frequency")

vari <- JSTAR_aksst_w3_child$a_004_0_1_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_aksst_w3_child$a_004_0_1_b, missing_values = NA)
ggplot(JSTAR_aksst_w3_child, aes(x=factor(a_004_0_1_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Confirmation about the 1st child: existence") + ylab("Frequency")

vari <- JSTAR_aksst_w3_child$a_004_0_1_h
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = JSTAR_aksst_w3_child$a_004_0_1_h, missing_values = NA)
ggplot(JSTAR_aksst_w3_child, aes(x=factor(a_004_0_1_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of grandchildren from the 1st child") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* CHILDREN:
* `IF (child=0 and a_004_a(W3)=1) OR (child=1 and a_004_a(W3)=2 and !(a_004_0_1_b=1 | a_004_0_2_b=1 | a_004_0_3_b=1 | a_004_0_4_b=1 | a_004_0_5_b=1) ) RECODE INTO 0.`
* `IF (child=1 and a_004_a(W3)=1) OR (child=0 and a_004_a(W3)=2 and (a_004_0_1_b=1 | a_004_0_2_b=1 | a_004_0_3_b=1 | a_004_0_4_b=1 | a_004_0_5_b=1) ) RECODE INTO 1.`

* GRANDCHILDREN:
* `IF a_004_0_1_h>0 or a_004_0_2_h>0 or a_004_0_3_h>0 or a_004_0_4_h>0 or a_004_0_5_h>0 RECODE INTO 1.`
* `IF a_004_0_1_h=0 & a_004_0_2_h=0 & a_004_0_3_h=0 & a_004_0_4_h=0 & a_004_0_5_h=0 RECODE INTO 0.`


**R script:**

```{r harmo3 5cities, echo=TRUE}

# ID - MERGE - FUNCTION:
#old: table with different number of individuals with the information that you need
#new: table with the individuals that you want

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_004_a=new$a_004_a, a_004_0_1_b=new$a_004_0_1_b, 
                       a_004_0_2_b=new$a_004_0_2_b, a_004_0_3_b=new$a_004_0_3_b, a_004_0_4_b=new$a_004_0_4_b,
                       a_004_0_5_b=new$a_004_0_5_b, a_004_0_1_h=new$a_004_0_1_h, a_004_0_2_h=new$a_004_0_2_h, 
                       a_004_0_3_h=new$a_004_0_3_h, a_004_0_4_h=new$a_004_0_4_h, a_004_0_5_h=new$a_004_0_5_h,
                       child=new_2$child)
  new_22
}

# old = JSTAR_aksst_ds_w2, with variable child
# new = JSTAR_aksst_w3_child, with variables a_004_a, a_004_0_1_b, a_004_0_2_b, a_004_0_3_b, a_004_0_4_b, a_004_0_5_b,                                                       a_004_0_1_h, a_004_0_2_h, a_004_0_3_h, a_004_0_4_h, a_004_0_5_h

JSTAR_aksst_merge_w23 <- same_indiv(JSTAR_aksst_ds_w2, JSTAR_aksst_w3_child)


JSTAR_aksst_merge_w23$child <- car::recode(as.vector(JSTAR_aksst_merge_w23$child), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_a <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_a), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_0_1_b <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_0_1_b), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_0_2_b <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_0_2_b), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_0_3_b <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_0_3_b), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_0_4_b <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_0_4_b), "NA='-999'")
JSTAR_aksst_merge_w23$a_004_0_5_b <- car::recode(as.vector(JSTAR_aksst_merge_w23$a_004_0_5_b), "NA='-999'")



JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_child$id)
JSTAR_aksst_ds_w3$child <- c(NA)   
for(i in 1:dim(JSTAR_aksst_merge_w23)[1]){
  
  if( (JSTAR_aksst_merge_w23$child[i] == 0 & JSTAR_aksst_merge_w23$a_004_a[i] == 1) |
      (JSTAR_aksst_merge_w23$child[i] == 1 & JSTAR_aksst_merge_w23$a_004_a[i] == 2 &
       !( JSTAR_aksst_merge_w23$a_004_0_1_b[i]==1 & JSTAR_aksst_merge_w23$a_004_0_2_b[i]==1 &
          JSTAR_aksst_merge_w23$a_004_0_3_b[i]==1 & JSTAR_aksst_merge_w23$a_004_0_4_b[i]==1 &
          JSTAR_aksst_merge_w23$a_004_0_5_b[i]==1 ) )
  ) { JSTAR_aksst_ds_w3$child[i] = 0 }
  
  else if( (JSTAR_aksst_merge_w23$child[i] == 1 & JSTAR_aksst_merge_w23$a_004_a[i] == 1) | 
           (JSTAR_aksst_merge_w23$child[i] == 0 & JSTAR_aksst_merge_w23$a_004_a[i] == 2 &
            ( JSTAR_aksst_merge_w23$a_004_0_1_b[i]==1 | JSTAR_aksst_merge_w23$a_004_0_2_b[i]==1 |
              JSTAR_aksst_merge_w23$a_004_0_3_b[i]==1 | JSTAR_aksst_merge_w23$a_004_0_4_b[i]==1 |
              JSTAR_aksst_merge_w23$a_004_0_5_b[i]==1 ) )
  ) { JSTAR_aksst_ds_w3$child[i] = 1 }
}

JSTAR_aksst_ds_w3$child <- car::recode(as.vector(JSTAR_aksst_ds_w3$child), "NA='999'")
JSTAR_aksst_ds_w3$child <- labelled(JSTAR_aksst_ds_w3$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))



JSTAR_aksst_w3_child$a_004_0_1_h <- car::recode(as.vector(JSTAR_aksst_w3_child$a_004_0_1_h), "NA='-999'")
JSTAR_aksst_w3_child$a_004_0_2_h <- car::recode(as.vector(JSTAR_aksst_w3_child$a_004_0_2_h), "NA='-999'")
JSTAR_aksst_w3_child$a_004_0_3_h <- car::recode(as.vector(JSTAR_aksst_w3_child$a_004_0_3_h), "NA='-999'")
JSTAR_aksst_w3_child$a_004_0_4_h <- car::recode(as.vector(JSTAR_aksst_w3_child$a_004_0_4_h), "NA='-999'")
JSTAR_aksst_w3_child$a_004_0_5_h <- car::recode(as.vector(JSTAR_aksst_w3_child$a_004_0_5_h), "NA='-999'")


JSTAR_aksst_ds_w3$grchild <- c(NA)   
for(i in 1:dim(JSTAR_aksst_w3_child)[1]){
  
  if( JSTAR_aksst_w3_child$a_004_0_1_h[i]>0 & JSTAR_aksst_w3_child$a_004_0_2_h[i]>0 &
      JSTAR_aksst_w3_child$a_004_0_3_h[i]>0 & JSTAR_aksst_w3_child$a_004_0_4_h[i]>0 &
      JSTAR_aksst_w3_child$a_004_0_5_h[i]>0 ) { 
    JSTAR_aksst_ds_w3$grchild[i] = 1 }
  
  else if( JSTAR_aksst_w3_child$a_004_0_1_h[i]==0 & JSTAR_aksst_w3_child$a_004_0_2_h[i]==0 &
           JSTAR_aksst_w3_child$a_004_0_3_h[i]==0 & JSTAR_aksst_w3_child$a_004_0_4_h[i]==0 &
           JSTAR_aksst_w3_child$a_004_0_5_h[i]==0 ) {
    JSTAR_aksst_ds_w3$child[i] = 0 }
}

JSTAR_aksst_ds_w3$grchild <- car::recode(as.vector(JSTAR_aksst_ds_w3$grchild), "NA='999'")
JSTAR_aksst_ds_w3$grchild <- labelled(JSTAR_aksst_ds_w3$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 5cities}
vari <- JSTAR_aksst_ds_w3$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has children") + ylab("Frequency")

vari <- JSTAR_aksst_ds_w3$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "grchild") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has grandchildren") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3 5cities}

```

 
 



## tn

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_010`
* Label: `A-010:HAS CHILD(REN)`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_1_3_2`
* Label: `A-012-1-3-2:1ST CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_2_3_2`
* Label: `A-012-2-3-2:2ND CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_3_3_2`
* Label: `A-012-3-3-2:3RD CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_4_3_2`
* Label: `A-012-4-3-2:4TH CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_5_3_2`
* Label: `A-012-5-3-2:5TH CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    

* Description: 
```{r assign1 2cities}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_child','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_010','a_012_1_3_2','a_012_2_3_2','a_012_3_3_2',
                                        'a_012_4_3_2','a_012_5_3_2'), missings = TRUE)
```

```{r local1 2cities}
JSTAR_tn_w1_child <- opal.execute(o,'JSTAR_tn_w1_child')
vari <- JSTAR_tn_w1_child$a_010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_child$a_010, missing_values = NA)
ggplot(JSTAR_tn_w1_child, aes(x=factor(a_010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has child(ren)") + ylab("Frequency")

vari <- JSTAR_tn_w1_child$a_012_1_3_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w1_child$a_012_1_3_2, missing_values = NA)
ggplot(JSTAR_tn_w1_child, aes(x=factor(a_012_1_3_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Does the 1st child has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* CHILDREN
* `1 Yes into 1`
* `2 No into 0`
* `3 Don't know into 998`
* `4 Refused to answer into 997`
* `NA into 999`

* GRANDCHILDREN
* `if any of a_012_i_3_2=1 INTO 1`
* `if all of a_012_i_3_2=0 INTO 0`
* `NA into 999`

**R script:**

```{r harmo1 2cities, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_child$id)
JSTAR_tn_ds_w1$child <- car::recode(as.vector(JSTAR_tn_w1_child$a_010), "1='1'; 2='0'; 3='998'; 4='997'; NA='999'")
JSTAR_tn_ds_w1$child <- labelled(JSTAR_tn_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


JSTAR_tn_w1_child$a_012_1_3_2 <- car::recode(as.vector(JSTAR_tn_w1_child$a_012_1_3_2), "NA='-999'")
JSTAR_tn_w1_child$a_012_2_3_2 <- car::recode(as.vector(JSTAR_tn_w1_child$a_012_2_3_2), "NA='-999'")
JSTAR_tn_w1_child$a_012_3_3_2 <- car::recode(as.vector(JSTAR_tn_w1_child$a_012_3_3_2), "NA='-999'")
JSTAR_tn_w1_child$a_012_4_3_2 <- car::recode(as.vector(JSTAR_tn_w1_child$a_012_4_3_2), "NA='-999'")
JSTAR_tn_w1_child$a_012_5_3_2 <- car::recode(as.vector(JSTAR_tn_w1_child$a_012_5_3_2), "NA='-999'")


JSTAR_tn_ds_w1$grchild <- c(NA)   
for(i in 1:dim(JSTAR_tn_w1_child)[1]){
  
  if( JSTAR_tn_w1_child$a_012_1_3_2[i]==0 & JSTAR_tn_w1_child$a_012_2_3_2[i]==0 &
      JSTAR_tn_w1_child$a_012_3_3_2[i]==0 & JSTAR_tn_w1_child$a_012_4_3_2[i]==0 &
      JSTAR_tn_w1_child$a_012_5_3_2[i]==0 ) { 
    JSTAR_tn_ds_w1$grchild[i] = 0 }
  
  else if( JSTAR_tn_w1_child$a_012_1_3_2[i]==1 | JSTAR_tn_w1_child$a_012_2_3_2[i]==1 |
      JSTAR_tn_w1_child$a_012_3_3_2[i]==1 | JSTAR_tn_w1_child$a_012_4_3_2[i]==1 |
      JSTAR_tn_w1_child$a_012_5_3_2[i]==1 ) { 
    JSTAR_tn_ds_w1$grchild[i] = 1 }
}
JSTAR_tn_ds_w1$grchild <- car::recode(as.vector(JSTAR_tn_ds_w1$grchild), "NA='999'")
JSTAR_tn_ds_w1$grchild <- labelled(JSTAR_tn_ds_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript1 2cities}
vari <- JSTAR_tn_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- JSTAR_tn_ds_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "grchild") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 2cities}

```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_004_a`
* Label: `11A-004:CHANGES IN THE NUMBER OF CHILDREN`
* Categories: 
    + `1 = No change`
    + `2 = The number of sons/daughters increased by (__) or decreased by (__)`
* Missings:    
    + `3 = Don't know`
    + `4 = Refused to answer`
    
    
* Name: `a_004_0_1_b`
* Label: `1A-004-0:CONFIRMATION ON THE 1ST CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_2_b`
* Label: `1A-004-0:CONFIRMATION ON THE 2ND CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_3_b`
* Label: `1A-004-0:CONFIRMATION ON THE 3RD CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_4_b`
* Label: `1A-004-0:CONFIRMATION ON THE 4TH CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`
    
* Name: `a_004_0_5_b`
* Label: `1A-004-0:CONFIRMATION ON THE 5TH CHILD'S INFORMATION: EXISTENCE`
* Categories:
    + `1 = Alive`
    + `2 = Died`


* Name: `a_004_0_1_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 1ST CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_2_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 2ND CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_3_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 3RD CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_4_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 4TH CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`

* Name: `a_004_0_1_h`
* Label: ` 11A-004-0:CONFIRMATION ON THE 5TH CHILD'S INFORMATION: NUMBER OF GRANDCHILDREN`



* Description: 
```{r assign2 2cities}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_child','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('a_004_a','a_004_0_1_b','a_004_0_2_b','a_004_0_3_b',
                                        'a_004_0_4_b','a_004_0_5_b','a_004_0_1_h','a_004_0_2_h',
                                        'a_004_0_3_h','a_004_0_4_h','a_004_0_5_h'), missings = TRUE)
```

```{r local2 2cities}
JSTAR_tn_w2_child <- opal.execute(o,'JSTAR_tn_w2_child')

vari <- JSTAR_tn_w2_child$a_004_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_child$a_004_a, missing_values = NA)
ggplot(JSTAR_tn_w2_child, aes(x=factor(a_004_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Change in the number of children") + ylab("Frequency")

vari <- JSTAR_tn_w2_child$a_004_0_1_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = JSTAR_tn_w2_child$a_004_0_1_b, missing_values = NA)
ggplot(JSTAR_tn_w2_child, aes(x=factor(a_004_0_1_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Confirmation about the 1st child: existence") + ylab("Frequency")

vari <- JSTAR_tn_w2_child$a_004_0_1_h
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = JSTAR_tn_w2_child$a_004_0_1_h, missing_values = NA)
ggplot(JSTAR_tn_w2_child, aes(x=factor(a_004_0_1_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of grandchildren from the 1st child") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* CHILDREN:
* ` IF (child=0 and a_004_a(W3)=1) OR (child=1 and a_004_a(W3)=2 and !(a_004_0_1_b=1 | a_004_0_2_b=1 | a_004_0_3_b=1 | a_004_0_4_b=1 | a_004_0_5_b=1) ) RECODE INTO 0.`
* ` IF (child=1 and a_004_a(W3)=1) OR (child=0 and a_004_a(W3)=2 and (a_004_0_1_b=1 | a_004_0_2_b=1 | a_004_0_3_b=1 | a_004_0_4_b=1 | a_004_0_5_b=1) ) RECODE INTO 1.`

* GRANDCHILDREN:
* ` IF a_004_0_1_h>0 or a_004_0_2_h>0 or a_004_0_3_h>0 or a_004_0_4_h>0 or a_004_0_5_h>0 RECODE INTO 1.`
* ` IF a_004_0_1_h=0 & a_004_0_2_h=0 & a_004_0_3_h=0 & a_004_0_4_h=0 & a_004_0_5_h=0 RECODE INTO 0.`

* `NA into 999`

**R script:**

```{r harmo2 2cities, echo=TRUE}

# ID - MERGE - FUNCTION:
#old: table with different number of individuals with the information that you need
#new: table with the individuals that you want

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, a_004_a=new$a_004_a, a_004_0_1_b=new$a_004_0_1_b, 
                       a_004_0_2_b=new$a_004_0_2_b, a_004_0_3_b=new$a_004_0_3_b, a_004_0_4_b=new$a_004_0_4_b,
                       a_004_0_5_b=new$a_004_0_5_b, a_004_0_1_h=new$a_004_0_1_h, a_004_0_2_h=new$a_004_0_2_h, 
                       a_004_0_3_h=new$a_004_0_3_h, a_004_0_4_h=new$a_004_0_4_h, a_004_0_5_h=new$a_004_0_5_h,
                       child=new_2$child)
  new_22
}

# old = JSTAR_tn_ds_w1
# new = JSTAR_tn_w2_child

JSTAR_tn_merge_w12 <- same_indiv(JSTAR_tn_ds_w1, JSTAR_tn_w2_child)


JSTAR_tn_merge_w12$child <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_a <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_0_1_b <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_0_2_b <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_0_3_b <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_0_4_b <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")
JSTAR_tn_merge_w12$a_004_0_5_b <- car::recode(as.vector(JSTAR_tn_merge_w12$child), "NA='-999'")



JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_child$id)
JSTAR_tn_ds_w2$child <- c(NA)   
for(i in 1:dim(JSTAR_tn_merge_w12)[1]){
  
  if( (JSTAR_tn_merge_w12$child[i] == 0 & JSTAR_tn_merge_w12$a_004_a[i] == 1) |
      (JSTAR_tn_merge_w12$child[i] == 1 & JSTAR_tn_merge_w12$a_004_a[i] == 2 &
       !( JSTAR_tn_merge_w12$a_004_0_1_b[i]==1 & JSTAR_tn_merge_w12$a_004_0_2_b[i]==1 &
          JSTAR_tn_merge_w12$a_004_0_3_b[i]==1 & JSTAR_tn_merge_w12$a_004_0_4_b[i]==1 &
          JSTAR_tn_merge_w12$a_004_0_5_b[i]==1 ) )
  ) { JSTAR_tn_ds_w2$child[i] = 0 }
  
  else if( (JSTAR_tn_merge_w12$child[i] == 1 & JSTAR_tn_merge_w12$a_004_a[i] == 1) | 
           (JSTAR_tn_merge_w12$child[i] == 0 & JSTAR_tn_merge_w12$a_004_a[i] == 2 &
            ( JSTAR_tn_merge_w12$a_004_0_1_b[i]==1 | JSTAR_tn_merge_w12$a_004_0_2_b[i]==1 |
              JSTAR_tn_merge_w12$a_004_0_3_b[i]==1 | JSTAR_tn_merge_w12$a_004_0_4_b[i]==1 |
              JSTAR_tn_merge_w12$a_004_0_5_b[i]==1 ) )
  ) { JSTAR_tn_ds_w2$child[i] = 1 }
}

JSTAR_tn_ds_w2$child <- car::recode(as.vector(JSTAR_tn_ds_w2$child), "NA='999'")
JSTAR_tn_ds_w2$child <- labelled(JSTAR_tn_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


JSTAR_tn_w2_child$a_004_0_1_h <- car::recode(as.vector(JSTAR_tn_w2_child$a_004_0_1_h), "NA='999'")
JSTAR_tn_w2_child$a_004_0_2_h <- car::recode(as.vector(JSTAR_tn_w2_child$a_004_0_1_h), "NA='999'")
JSTAR_tn_w2_child$a_004_0_3_h <- car::recode(as.vector(JSTAR_tn_w2_child$a_004_0_1_h), "NA='999'")
JSTAR_tn_w2_child$a_004_0_4_h <- car::recode(as.vector(JSTAR_tn_w2_child$a_004_0_1_h), "NA='999'")
JSTAR_tn_w2_child$a_004_0_5_h <- car::recode(as.vector(JSTAR_tn_w2_child$a_004_0_1_h), "NA='999'")


JSTAR_tn_ds_w2$grchild <- c(NA)   
for(i in 1:dim(JSTAR_tn_w2_child)[1]){
  
  if( JSTAR_tn_w2_child$a_004_0_1_h[i]>0 & JSTAR_tn_w2_child$a_004_0_2_h[i]>0 &
      JSTAR_tn_w2_child$a_004_0_3_h[i]>0 & JSTAR_tn_w2_child$a_004_0_4_h[i]>0 &
      JSTAR_tn_w2_child$a_004_0_5_h[i]>0 ) { 
    JSTAR_tn_ds_w2$grchild[i] = 1 }
  
  else if( JSTAR_tn_w2_child$a_004_0_1_h[i]==0 & JSTAR_tn_w2_child$a_004_0_2_h[i]==0 &
           JSTAR_tn_w2_child$a_004_0_3_h[i]==0 & JSTAR_tn_w2_child$a_004_0_4_h[i]==0 &
           JSTAR_tn_w2_child$a_004_0_5_h[i]==0 ) {
    JSTAR_tn_ds_w2$child[i] = 0 }
}

JSTAR_tn_ds_w2$grchild <- car::recode(as.vector(JSTAR_tn_ds_w2$grchild), "NA='999'")
JSTAR_tn_ds_w2$grchild <- labelled(JSTAR_tn_ds_w2$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 2cities}
vari <- JSTAR_tn_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- JSTAR_tn_ds_w2$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "grchild") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation 
```{r crosstabulation2 2cities}

```

 
 



## cth
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a_011_b`
* Label: `A-011:THE NUMBER OF CHILDREN`
    
    
* Name: `a_012_1_3_2_a`
* Label: `A-012-1-3-2:1ST CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_2_3_2_a`
* Label: `A-012-2-3-2:2ND CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_3_3_2_a`
* Label: `A-012-3-3-2:3RD CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_4_3_2_a`
* Label: `A-012-4-3-2:4TH CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
* Name: `a_012_5_3_2_a`
* Label: `A-012-5-3-2:5TH CHILD HAS CHILDREN`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:    
    + `3.0 = Don't know`
    + `4.0 = Refused to answer`
    
    

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_child','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_011_b','a_012_1_3_2_a','a_012_2_3_2_a','a_012_3_3_2_a',
                                        'a_012_4_3_2_a','a_012_5_3_2_a'), missings = TRUE)
```




```{r local1}
JSTAR_cth_w1_child <- opal.execute(o,'JSTAR_cth_w1_child')
vari <- JSTAR_cth_w1_child$a_011_b
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = JSTAR_cth_w1_child$a_011_b, missing_values = NA)
ggplot(JSTAR_cth_w1_child, aes(x=factor(a_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has child(ren)") + ylab("Frequency")

vari <- JSTAR_cth_w1_child$a_012_1_3_2_a
kable(Categorical_summary(vari, missing_values = c(3,4))[3]) 
kable(Categorical_summary(vari, missing_values = c(3,4))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(3,4))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_w1_child$a_012_1_3_2, missing_values = NA)
ggplot(JSTAR_cth_w1_child, aes(x=factor(a_012_1_3_2_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Does the 1st child has children?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* CHILDREN
* `a_011_b>0 into 1`
* `a_011_b=0 into 0`
* `NA into 999`

* GRANDCHILDREN
* `if any of a_012_i_3_2_a=1 INTO 1`
* `if all of a_012_i_3_2_a=0 INTO 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_child$id)
JSTAR_cth_ds_w1$child <- car::recode(as.vector(JSTAR_cth_w1_child$a_011_b), "0='0'; NA='999'; 1:hi='1'")
JSTAR_cth_ds_w1$child <- labelled(JSTAR_cth_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


JSTAR_cth_w1_child$a_012_1_3_2_a <- car::recode(as.vector(JSTAR_cth_w1_child$a_012_1_3_2_a), "NA='-999'")
JSTAR_cth_w1_child$a_012_2_3_2_a <- car::recode(as.vector(JSTAR_cth_w1_child$a_012_2_3_2_a), "NA='-999'")
JSTAR_cth_w1_child$a_012_3_3_2_a <- car::recode(as.vector(JSTAR_cth_w1_child$a_012_3_3_2_a), "NA='-999'")
JSTAR_cth_w1_child$a_012_4_3_2_a <- car::recode(as.vector(JSTAR_cth_w1_child$a_012_4_3_2_a), "NA='-999'")
JSTAR_cth_w1_child$a_012_5_3_2_a <- car::recode(as.vector(JSTAR_cth_w1_child$a_012_5_3_2_a), "NA='-999'")


JSTAR_cth_ds_w1$grchild <- c(NA)   
for(i in 1:dim(JSTAR_cth_w1_child)[1]){
  
  if( JSTAR_cth_w1_child$a_012_1_3_2_a[i]==0 & JSTAR_cth_w1_child$a_012_2_3_2_a[i]==0 &
      JSTAR_cth_w1_child$a_012_3_3_2_a[i]==0 & JSTAR_cth_w1_child$a_012_4_3_2_a[i]==0 &
      JSTAR_cth_w1_child$a_012_5_3_2_a[i]==0 ) { 
    JSTAR_cth_ds_w1$grchild[i] = 0 }
  
  else if( JSTAR_cth_w1_child$a_012_1_3_2_a[i]==1 | JSTAR_cth_w1_child$a_012_2_3_2_a[i]==1 |
      JSTAR_cth_w1_child$a_012_3_3_2_a[i]==1 | JSTAR_cth_w1_child$a_012_4_3_2_a[i]==1 |
      JSTAR_cth_w1_child$a_012_5_3_2_a[i]==1 ) { 
    JSTAR_cth_ds_w1$grchild[i] = 1 }
}

JSTAR_cth_ds_w1$grchild <- car::recode(as.vector(JSTAR_cth_ds_w1$grchild), "NA='999'")
JSTAR_cth_ds_w1$grchild <- labelled(JSTAR_cth_ds_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- JSTAR_cth_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "child") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- JSTAR_cth_ds_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "grchild") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

 
 
```{r save, echo=FALSE}
child <- JSTAR_tn_ds_w1[,-3]
save(child, file = "../RData/tn_w1/child.RData")
rm(child)

child <- JSTAR_tn_ds_w2[,-3]
save(child, file = "../RData/tn_w2/child.RData")
rm(child)


child <- JSTAR_aksst_ds_w1
save(child, file = "../RData/aksst_w1/child.RData")
rm(child)

child <- JSTAR_aksst_ds_w2
save(child, file = "../RData/aksst_w2/child.RData")
rm(child)

child <- JSTAR_aksst_ds_w3[,-3]
save(child, file = "../RData/aksst_w3/child.RData")
rm(child)

child <- JSTAR_cth_ds_w1[,-3]
save(child, file = "../RData/cth_w1/child.RData")
rm(child)

grchild <- JSTAR_tn_ds_w1[,-2]
save(grchild, file = "../RData/tn_w1/grchild.RData")
rm(grchild)

grchild <- JSTAR_tn_ds_w2[,-2]
save(grchild, file = "../RData/tn_w2/grchild.RData")
rm(grchild)



grchild <- JSTAR_aksst_ds_w3[,-2]
save(grchild, file = "../RData/aksst_w3/grchild.RData")
rm(grchild)

grchild <- JSTAR_cth_ds_w1[,-2]
save(grchild, file = "../RData/cth_w1/grchild.RData")
rm(grchild)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


