---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
id_missings <- c("Cf-397794-01", "DE-271503-01", "Ih-306138-02", "Ih-737574-01", "Ih-907477-01", "NL-027316-01", "NL-037198-01", "NL-073637-01", "NL-155292-01", "NL-372323-01", "NL-922959-01", "NL-924571-01", "GR-190740-02", "Bn-330112-02", "DK-639322-02", "ES-932056-02", "PL-691802-02", "SE-764326-05", "AT-215568-02", "AT-864946-01", "AT-886095-01", "CZ-023045-01", "CZ-033227-01", "CZ-191583-01", "CZ-356553-01", "CZ-373473-04", "CZ-384175-01", "CZ-526053-01", "CZ-638063-01", "CZ-694720-01", "CZ-695635-01", "F1-191516-01", "F1-728117-01", "HU-042621-01", "PT-022802-01", "PT-073544-01", "PT-443942-01", "PT-713628-01", "PT-843462-01", "DK-197676-02", "Eg-036951-05", "Eg-197395-02", "Eg-758727-02", "Eg-904129-02", "Ih-826469-03", "LU-989099-01", "NL-132447-01", "NL-756812-02", "NL-785371-02", "NL-948960-02", "SE-368759-02", "SE-607164-02", "SE-684973-02", "SI-139484-02")

```



# Data process

## SHARE

### Wave 1 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew1_rel2-6-0_cv_r_whitout_nointw1` |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_cv_r_whitout_nointw1',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w1 <- opal.execute(o,'SHARE_w1')
```

```{r local1, echo=F}
vari <- SHARE_w1$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w1, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo1}



yrbirth_missing <- (SHARE_w1 %>% filter(is.na(yrbirth) | yrbirth %in% c(-1,-2)))$id
SHARE_miss <- SHARE_w1 %>% select(id,yrbirth) %>% filter(id %in% id_missings)


# Wave 1 missing yrbirth data is non-missing in posterior waves tables for some id's (look at validation of yrbirth at the end). Here is imputed.

SHARE_w1$yrbirth[which(SHARE_w1$id=="Ih-306138-02")] <- 1934
SHARE_w1$yrbirth[which(SHARE_w1$id=="NL-037198-01")] <- 1919


SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$ybirth <- car::recode(SHARE_w1$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w1$ybirth <- labelled(SHARE_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F,results='asis'}

```









### Wave 2 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew2_rel2-6-0_cv_r_without_noint` |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w2 <- opal.execute(o,'SHARE_w2')
```

```{r local2, echo=F}
vari <- SHARE_w2$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w2, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo2}




#Some missing yrbirth data is available from previous waves
SHARE_w2 <- left_join(SHARE_w2,SHARE_w1 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w1"))
SHARE_w2$yrbirth[which(is.na(SHARE_w2$yrbirth) | (SHARE_w2$yrbirth %in% c(-1,-2) & !is.na(SHARE_w2$yrbirth_w1)))] <- SHARE_w2$yrbirth_w1[which(is.na(SHARE_w2$yrbirth) | (SHARE_w2$yrbirth %in% c(-1,-2) & !is.na(SHARE_w2$yrbirth_w1)))]
SHARE_w2 <- SHARE_w2 %>% select(-yrbirth_w1)



yrbirth_missing <- union(yrbirth_missing,(SHARE_w2 %>% filter(is.na(yrbirth) | yrbirth %in% c(-1,-2)))$id)
SHARE_miss <- full_join(SHARE_miss,SHARE_w2 %>% select(id,yrbirth) %>% filter(id %in% id_missings),by="id",suffix = c("_w1","_w2"))


SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$ybirth <- car::recode(SHARE_w2$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w2$ybirth <- labelled(SHARE_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F,results='asis'}

```






### Wave 3 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew3_rel1_cv_r_without_noint` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w3 <- opal.execute(o,'SHARE_w3')
```

```{r local3, echo=F}
vari <- SHARE_w3$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w3, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo3}


#Some missing yrbirth data is available from previous waves
SHARE_w3 <- left_join(SHARE_w3,SHARE_w1 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w1"))
SHARE_w3$yrbirth[which(is.na(SHARE_w3$yrbirth) | (SHARE_w3$yrbirth %in% c(-1,-2) & !is.na(SHARE_w3$yrbirth_w1)))] <- SHARE_w3$yrbirth_w1[which(is.na(SHARE_w3$yrbirth) | (SHARE_w3$yrbirth %in% c(-1,-2) & !is.na(SHARE_w3$yrbirth_w1)))]
SHARE_w3 <- left_join(SHARE_w3,SHARE_w2 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w2"))
SHARE_w3$yrbirth[which(is.na(SHARE_w3$yrbirth) | (SHARE_w3$yrbirth %in% c(-1,-2) & !is.na(SHARE_w3$yrbirth_w2)))] <- SHARE_w3$yrbirth_w2[which(is.na(SHARE_w3$yrbirth) | (SHARE_w3$yrbirth %in% c(-1,-2) & !is.na(SHARE_w3$yrbirth_w2)))]
SHARE_w3 <- SHARE_w3 %>% select(-yrbirth_w1,-yrbirth_w2)


yrbirth_missing <- union(yrbirth_missing,(SHARE_w3 %>% filter(is.na(yrbirth) | yrbirth %in% c(-1,-2)))$id)
SHARE_miss <- full_join(SHARE_miss,SHARE_w3 %>% select(id,yrbirth) %>% filter(id %in% id_missings),by="id")

# Wave 3 missing yrbirth data is non-missing in posterior waves tables for some id's (look at validation of yrbirth at the end). Here is imputed.

SHARE_w3$yrbirth[SHARE_w3$id=="SE-764326-05"] <- 1951



SHARE_ds_w3 <- tibble(id=SHARE_w3$id)
SHARE_ds_w3$ybirth <- car::recode(SHARE_w3$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w3$ybirth <- labelled(SHARE_ds_w3$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F,results='asis'}

```








### Wave 4 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew4_rel1-1-1_cv_r_without_noint` |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know`<br/>`NA` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w4 <- opal.execute(o,'SHARE_w4')
```

```{r local4, echo=F}
vari <- SHARE_w4$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w4, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

There is an individual with 2011 as year of birth that is imposible because 2011 is the year of interview. Therefore this value will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo4}


#Some missing yrbirth data is available from previous waves
SHARE_w4 <- left_join(SHARE_w4,SHARE_w1 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w1"))
SHARE_w4$yrbirth[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w1)))] <- SHARE_w4$yrbirth_w1[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w1)))]
SHARE_w4 <- left_join(SHARE_w4,SHARE_w2 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w2"))
SHARE_w4$yrbirth[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w2)))] <- SHARE_w4$yrbirth_w2[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w2)))]
SHARE_w4 <- left_join(SHARE_w4,SHARE_w3 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w3"))
SHARE_w4$yrbirth[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w3)))] <- SHARE_w4$yrbirth_w3[which(is.na(SHARE_w4$yrbirth) | (SHARE_w4$yrbirth %in% c(-1,-2) & !is.na(SHARE_w4$yrbirth_w3)))]
SHARE_w4 <- SHARE_w4 %>% select(-yrbirth_w1,-yrbirth_w2,-yrbirth_w3)



yrbirth_missing <- union(yrbirth_missing,(SHARE_w4 %>% filter(is.na(yrbirth) | yrbirth %in% c(-1,-2)))$id)
SHARE_miss <- full_join(SHARE_miss,SHARE_w4 %>% select(id,yrbirth) %>% filter(id %in% id_missings),by="id",suffix = c("_w3","_w4"))

# Wave 4 missing yrbirth data is non-missing in posterior waves tables for some id's (look at validation of yrbirth at the end). Here is imputed.

SHARE_w4$yrbirth[which(SHARE_w4$id=="AT-864946-01")] <- 1945
SHARE_w4$yrbirth[which(SHARE_w4$id=="AT-886095-01")] <- 1926
SHARE_w4$yrbirth[which(SHARE_w4$id=="CZ-373473-04")] <- 1950
SHARE_w4$yrbirth[which(SHARE_w4$id=="CZ-694720-01")] <- 1954
SHARE_w4$yrbirth[which(SHARE_w4$id=="F1-191516-01")] <- 1950
SHARE_w4$yrbirth[which(SHARE_w4$id=="F1-728117-01")] <- 1946


SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$ybirth <- car::recode(SHARE_w4$yrbirth, "-2=997; -1=998; 2011=999;  NA=999")
SHARE_ds_w4$ybirth <- labelled(SHARE_ds_w4$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F,results='asis'}

```







### Wave 5 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew5_rel1-0-0_cv_r_without_noint` |
| **Missings** |`-2 = refusal`<br/>`-1 = don't know`<br/>`NA` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w5 <- opal.execute(o,'SHARE_w5')
```

```{r local5, echo=F}
vari <- SHARE_w5$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w5, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There is an individual with 2013 as year of birth that is imposible because 2011 is the year of interview. Therefore this value will be recoded as 999. 

**R script:**

```{r harmo5}



#Some missing yrbirth data is available from previous waves
SHARE_w5 <- left_join(SHARE_w5,SHARE_w1 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w1"))
SHARE_w5$yrbirth[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w1)))] <- SHARE_w5$yrbirth_w1[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w1)))]
SHARE_w5 <- left_join(SHARE_w5,SHARE_w2 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w2"))
SHARE_w5$yrbirth[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w2)))] <- SHARE_w5$yrbirth_w2[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w2)))]
SHARE_w5 <- left_join(SHARE_w5,SHARE_w3 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w3"))
SHARE_w5$yrbirth[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w3)))] <- SHARE_w5$yrbirth_w3[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w3)))]
SHARE_w5 <- left_join(SHARE_w5,SHARE_w4 %>% select(id,yrbirth) %>% filter(!yrbirth %in% c(-1,-2)),by = "id", suffix = c("","_w4"))
SHARE_w5$yrbirth[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w4)))] <- SHARE_w5$yrbirth_w4[which(is.na(SHARE_w5$yrbirth) | (SHARE_w5$yrbirth %in% c(-1,-2) & !is.na(SHARE_w5$yrbirth_w4)))]
SHARE_w5 <- SHARE_w5 %>% select(-yrbirth_w1,-yrbirth_w2,-yrbirth_w3,-yrbirth_w4)



yrbirth_missing <- union(yrbirth_missing,(SHARE_w5 %>% filter(is.na(yrbirth) | yrbirth %in% c(-1,-2)))$id)
SHARE_miss <- full_join(SHARE_miss,SHARE_w5 %>% select(id,yrbirth) %>% filter(id %in% id_missings),by="id")


SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$ybirth <- car::recode(SHARE_w5$yrbirth, "-2=997; -1=998; 2013=999;  NA=999")
SHARE_ds_w5$ybirth <- labelled(SHARE_ds_w5$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F,results='asis'}

```




### Validation of `yrbirth` across waves

```{r, echo=FALSE}

yrbirth_missing <- unique(yrbirth_missing)
cat("Validation of id's with previous missing yrbirth: ",identical(yrbirth_missing,id_missings))
kable(SHARE_miss %>% mutate(TNA=rowSums(is.na(.) | . == -1 | . == -2)) %>% filter(TNA!=5) %>% select(-TNA),caption = "Id's with yrbirth data but previous missing values")

```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation

```{r, echo=F}

SHARE <- full_join(SHARE_ds_w1[which(!SHARE_ds_w1$ybirth %in% miss_values_vector),],SHARE_ds_w2[which(!SHARE_ds_w2$ybirth %in% miss_values_vector),], by="id", suffix=c(".w1",".w2"))
SHARE <- full_join(SHARE,SHARE_ds_w3[which(!SHARE_ds_w3$ybirth %in% miss_values_vector),], by="id")
SHARE <- full_join(SHARE,SHARE_ds_w4[which(!SHARE_ds_w4$ybirth %in% miss_values_vector),], by="id", suffix=c(".w3",".w4"))
SHARE <- full_join(SHARE,SHARE_ds_w5[which(!SHARE_ds_w5$ybirth %in% miss_values_vector),], by="id")
SHARE$var <- apply(SHARE[,-1],1,function(x) var(x, na.rm = T))

SHstr <- paste("There are ",length(SHARE$id[which(SHARE$var!=0)])," individuals with year of birth data changing across waves.")

kable(frq(SHARE$var==0), align = 'c', caption = SHstr)
kable(SHARE[which(SHARE$var>0.5),], align = 'c', caption = 'There are 156 individuals for which the difference between their years of birth answered is greater than 1 year.')
kable(SHARE[which(SHARE$var>0 & SHARE$var<=0.5),], align = 'c', caption = 'There are 42 individuals for which the difference between their years of birth answered is 1 year.')

```

We do not anything thereon.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
