---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```



# Data process

## SHARE

### Wave 1 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew1_rel2-6-0_cv_r_whitout_nointw1` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_ybirth','SHARE.sharew1_rel2-6-0_cv_r_whitout_nointw1',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w1_ybirth <- opal.execute(o,'SHARE_w1_ybirth')
```

```{r local1, echo=F}
vari <- SHARE_w1_ybirth$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w1_ybirth, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_ybirth$id)
SHARE_ds_w1$ybirth <- car::recode(SHARE_w1_ybirth$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w1$ybirth <- labelled(SHARE_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F,results='asis'}
cat("There are 12 different values between the harmonized variable and the study-specific variable that correspond to the missing values:",sum(SHARE_w1_ybirth$yrbirth!=SHARE_ds_w1$ybirth))
```









### Wave 2 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew2_rel2-6-0_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_ybirth','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w2_ybirth <- opal.execute(o,'SHARE_w2_ybirth')
```

```{r local2, echo=F}
vari <- SHARE_w2_ybirth$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w2_ybirth, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_ybirth$id)
SHARE_ds_w2$ybirth <- car::recode(SHARE_w2_ybirth$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w2$ybirth <- labelled(SHARE_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F,results='asis'}
cat("There is 1 different value between the harmonized variable and the study-specific variable that corresponds to the missing value.",sum(SHARE_w2_ybirth$yrbirth!=SHARE_ds_w2$ybirth))
```






### Wave 3 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew3_rel1_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3_ybirth','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w3_ybirth <- opal.execute(o,'SHARE_w3_ybirth')
```

```{r local3, echo=F}
vari <- SHARE_w3_ybirth$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w3_ybirth, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_ybirth$id)
SHARE_ds_w3$ybirth <- car::recode(SHARE_w3_ybirth$yrbirth, "-2=997; -1=998;  NA=999")
SHARE_ds_w3$ybirth <- labelled(SHARE_ds_w3$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F,results='asis'}
cat("There are no different values between the harmonized variable and the study-specific variable:",sum(SHARE_w3_ybirth$yrbirth!=SHARE_ds_w3$ybirth,na.rm=T))
```








### Wave 4 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew4_rel1-1-1_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_ybirth','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w4_ybirth <- opal.execute(o,'SHARE_w4_ybirth')
```

```{r local4, echo=F}
vari <- SHARE_w4_ybirth$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w4_ybirth, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

There is an individual with 2011 as year of birth that is imposible because 2011 is the year of interview. Therefore this value will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_ybirth$id)
SHARE_ds_w4$ybirth <- car::recode(SHARE_w4_ybirth$yrbirth, "-2=997; -1=998; 2011=999;  NA=999")
SHARE_ds_w4$ybirth <- labelled(SHARE_ds_w4$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F,results='asis'}
cat("There are 2 different values between the study-specific variable and the harmonized variable -one is a missing value and the other is the impossible year of birth 2011: ",sum(SHARE_w4_ybirth$yrbirth!=SHARE_ds_w4$ybirth,na.rm=T))
```







### Wave 5 

#### Study-specific variable description

| **Name** | `yrbirth` |
|----------|------------|
| **Label** | `year of birth` |
| **Table name** | `sharew5_rel1-0-0_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_ybirth','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('yrbirth'), missings = TRUE)
SHARE_w5_ybirth <- opal.execute(o,'SHARE_w5_ybirth')
```

```{r local5, echo=F}
vari <- SHARE_w5_ybirth$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w5_ybirth, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% c(-1,-2))) + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There is an individual with 2013 as year of birth that is imposible because 2011 is the year of interview. Therefore this value will be recoded as 999. 

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_ybirth$id)
SHARE_ds_w5$ybirth <- car::recode(SHARE_w5_ybirth$yrbirth, "-2=997; -1=998; 2013=999;  NA=999")
SHARE_ds_w5$ybirth <- labelled(SHARE_ds_w5$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F,results='asis'}
cat("There are 4 different values between the harmonized variable and the study-specific variable that correspond to the missing values and the impossible year of birth 2013:",sum(SHARE_w5_ybirth$yrbirth!=SHARE_ds_w5$ybirth,na.rm=T))
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation

```{r, echo=F}

SHARE <- full_join(SHARE_ds_w1[which(!SHARE_ds_w1$ybirth %in% miss_values_vector),],SHARE_ds_w2[which(!SHARE_ds_w2$ybirth %in% miss_values_vector),], by="id", suffix=c(".w1",".w2"))
SHARE <- full_join(SHARE,SHARE_ds_w3[which(!SHARE_ds_w3$ybirth %in% miss_values_vector),], by="id")
SHARE <- full_join(SHARE,SHARE_ds_w4[which(!SHARE_ds_w4$ybirth %in% miss_values_vector),], by="id", suffix=c(".w3",".w4"))
SHARE <- full_join(SHARE,SHARE_ds_w5[which(!SHARE_ds_w5$ybirth %in% miss_values_vector),], by="id")
SHARE$var <- apply(SHARE[,-1],1,function(x) var(x, na.rm = T))

SHstr <- paste("There are ",length(SHARE$id[which(SHARE$var!=0)])," individuals with year of birth data changing across waves.")

kable(frq(SHARE$var==0), align = 'c', caption = SHstr)
kable(SHARE[which(SHARE$var>0.5),], align = 'c', caption = 'There are 156 individuals for which the difference between their years of birth answered is greater than 1 year.')
kable(SHARE[which(SHARE$var>0 & SHARE$var<=0.5),], align = 'c', caption = 'There are 42 individuals for which the difference between their years of birth answered is 1 year.')

```

We do not anything thereon.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
