---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process

## SHARE

### Wave 1 

#### Study-specific variable description

| **Name** | `yrbirth`|`mobirth`| `int_year` | `int_month` |
|-|-|-|-|-|
| **Label** | `year of birth`| `month of birth` | `interview year` | `interview month` |
| **Table name** | `sharew1_rel2-6-0_cv_r_whitout_nointw1` | `idem` | `idem` | `idem` |
| **Categories** |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` |  | `-2 = refusal`<br/>`-1 = don't know` |
| **Description** |  |  |  |  |






```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_age','SHARE.sharew1_rel2-6-0_cv_r_whitout_nointw1',
                         variables=list('yrbirth', 'mobirth', 'int_year', 'int_month'), missings = TRUE)
SHARE_w1_age <- opal.execute(o,'SHARE_w1_age')
```

```{r local1, echo=F}
vari <- SHARE_w1_age$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w1_age, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency")+xlim(1900,1980)

vari <- SHARE_w1_age$mobirth
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of birth") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_age, aes(x=factor(mobirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- SHARE_w1_age$int_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w1_age, aes(x=factor(int_year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

vari <- SHARE_w1_age$int_month
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of interview") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_age, aes(x=factor(int_month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables it has to be computed by applying the following formula: 

* `date of interview - date of birth`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_age$id)

#harmonise year of birth
SHARE_w1_age$year_of_birth <- car::recode(SHARE_w1_age$yrbirth, "-2=997; -1=998;  NA=999")

#harmonise month of birth
SHARE_w1_age$month_of_birth <- car::recode(SHARE_w1_age$mobirth, "-2=997; -1=998;  NA=999")

#harmonise month of interview
SHARE_w1_age$month_of_interview <- car::recode(SHARE_w1_age$int_month, "-2=997; -1=998;  c(13,NA)='999'")

#harmonise year of interview
SHARE_w1_age$year_of_interview <- car::recode(SHARE_w1_age$int_year, "NA=999")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SHARE_ds_w1$age <- comp_age(y_birth=SHARE_w1_age$year_of_birth , m_birth=SHARE_w1_age$month_of_birth ,
         y_int=SHARE_w1_age$year_of_interview , m_int=SHARE_w1_age$month_of_interview , miss=c(997, 998, 999))



SHARE_ds_w1$age <- labelled(SHARE_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age") + ylab("Frequency")+xlim(25,105)
```

#### Validation
```{r crosstabulation1, echo=F}
```






### Wave 2 

#### Study-specific variable description




| **Name** |`mobirth`| `yrbirth`| `int_month_w2` | `int_year_w2` |
|-|-|-|-|-|
| **Label** | `month of birth` | `year of birth`| `interview month` | `interview year` |
| **Table name** | `sharew2_rel2-6-0_cv_r_without_noint` | `idem` | `idem` | `idem` |
| **Categories** | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` |  |
| **Description** |  |  |  |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_age','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('mobirth', 'yrbirth', 'int_month_w2', 'int_year_w2'), missings = TRUE)
SHARE_w2_age <- opal.execute(o,'SHARE_w2_age')
```

```{r local2, echo=F}
vari <- SHARE_w2_age$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w2_age, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency")+xlim(1900,1995)

vari <- SHARE_w2_age$mobirth
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of birth") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_age, aes(x=factor(mobirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- SHARE_w2_age$int_year_w2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w2_age, aes(x=factor(int_year_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

vari <- SHARE_w2_age$int_month_w2
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of interview") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_age, aes(x=factor(int_month_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables it has to be computed by applying the following formula: 

* `date of interview - date of birth`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_age$id)

#harmonise year of birth
SHARE_w2_age$year_of_birth <- car::recode(SHARE_w2_age$yrbirth, "-2=997; -1=998;  NA=999")

#harmonise month of birth
SHARE_w2_age$month_of_birth <- car::recode(SHARE_w2_age$mobirth, "-2=997; -1=998;  NA=999")

#harmonise month of interview
SHARE_w2_age$month_of_interview <- car::recode(SHARE_w2_age$int_month_w2, "-2=997; -1=998;  c(13,NA)='999'")

#harmonise year of interview
SHARE_w2_age$year_of_interview <- car::recode(SHARE_w2_age$int_year_w2, "NA=999")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SHARE_ds_w2$age <- comp_age(y_birth=SHARE_w2_age$year_of_birth , m_birth=SHARE_w2_age$month_of_birth ,
         y_int=SHARE_w2_age$year_of_interview , m_int=SHARE_w2_age$month_of_interview , miss=c(997, 998, 999))
SHARE_ds_w2$age <- labelled(SHARE_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age") + ylab("Frequency")+xlim(10,105)
```

#### Validation
```{r crosstabulation2, echo=F}
```






### Wave 3 

#### Study-specific variable description



| **Name** |`mobirth`| `yrbirth`| `int_month_w3` | `int_year_w3` |
|-|-|-|-|-|
| **Label** | `month of birth` | `year of birth`| `interview month` | `interview year` |
| **Table name** | `sharew3_rel1_cv_r_without_noint` | `idem` | `idem` | `idem` |
| **Categories** | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` |  |
| **Description** |  |  |  |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3_age','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('yrbirth', 'mobirth', 'int_month_w3', 'int_year_w3'), missings = TRUE)
SHARE_w3_age <- opal.execute(o,'SHARE_w3_age')
```

```{r local3, echo=F}
vari <- SHARE_w3_age$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w3_age, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency")+xlim(1905,1985)

vari <- SHARE_w3_age$mobirth
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of birth") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w3_age, aes(x=factor(mobirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- SHARE_w3_age$int_year_w3
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w3_age, aes(x=factor(int_year_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

vari <- SHARE_w3_age$int_month_w3
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of interview") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w3_age, aes(x=factor(int_month_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables it has to be computed by applying the following formula: 

* `date of interview - date of birth`

**R script:**

```{r harmo3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_age$id)
#harmonise year of birth
SHARE_w3_age$year_of_birth <- car::recode(SHARE_w3_age$yrbirth, "-2=997; -1=998;  NA=999")

#harmonise month of birth
SHARE_w3_age$month_of_birth <- car::recode(SHARE_w3_age$mobirth, "-2=997; -1=998;  NA=999")

#harmonise month of interview
SHARE_w3_age$month_of_interview <- car::recode(SHARE_w3_age$int_month_w3, "-2=997; -1=998;  c(13,NA)='999'")

#harmonise year of interview
SHARE_w3_age$year_of_interview <- car::recode(SHARE_w3_age$int_year_w3, "NA=2009")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SHARE_ds_w3$age <- comp_age(y_birth=SHARE_w3_age$year_of_birth , m_birth=SHARE_w3_age$month_of_birth ,
         y_int=SHARE_w3_age$year_of_interview , m_int=SHARE_w3_age$month_of_interview , miss=c(997, 998, 999))



SHARE_ds_w3$age <- labelled(SHARE_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w3, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age") + ylab("Frequency")+xlim(20,105)
```

#### Validation
```{r crosstabulation3, echo=F}
```








### Wave 4 

#### Study-specific variable description




| **Name** |`mobirth`| `yrbirth`| `int_month_w4` | `int_year_w4` |
|-|-|-|-|-|
| **Label** | `month of birth` | `year of birth`| `interview month` | `interview year` |
| **Table name** | `sharew4_rel1-1-1_cv_r_without_noint` | `idem` | `idem` | `idem` |
| **Categories** | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-3 = implausible/ suspected wrong` |
| **Description** |  |  |  |  |

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_age','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('mobirth', 'yrbirth', 'int_month_w4', 'int_year_w4'), missings = TRUE)
SHARE_w4_age <- opal.execute(o,'SHARE_w4_age')
```

```{r local4, echo=F}
vari <- SHARE_w4_age$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w4_age, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency")+xlim(1900,2015)

vari <- SHARE_w4_age$mobirth
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of birth") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_age, aes(x=factor(mobirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- SHARE_w4_age$int_year_w4
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w4_age, aes(x=factor(int_year_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

vari <- SHARE_w4_age$int_month_w4
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of interview") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_age, aes(x=factor(int_month_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables it has to be computed by applying the following formula: 

* `date of interview - date of birth`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_age$id)

#harmonise year of birth
SHARE_w4_age$yrbirth <- car::recode(SHARE_w4_age$yrbirth, "-2=997; -1=998;  NA=999")

#harmonise month of birth
SHARE_w4_age$mobirth <- car::recode(SHARE_w4_age$mobirth, "-2=997; -1=998;  NA=999")

#harmonise month of interview
SHARE_w4_age$int_month_w4 <- car::recode(SHARE_w4_age$int_month_w4, "-2=997; -1=998;  c(13,NA)='999'")

#harmonise year of interview
SHARE_w4_age$int_year_w4 <- car::recode(SHARE_w4_age$int_year_w4,  "-3=999; NA=2011")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SHARE_w4_age$age <- comp_age(y_birth=SHARE_w4_age$yrbirth , m_birth=SHARE_w4_age$mobirth ,
         y_int=SHARE_w4_age$int_year_w4 , m_int=SHARE_w4_age$int_month_w4 , miss=c(997, 998, 999))


SHARE_ds_w4$age <- car::recode(SHARE_w4_age$age, "0=999; NA=999")
SHARE_ds_w4$age <- labelled(SHARE_ds_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age") + ylab("Frequency")+xlim(20,110)
```

#### Validation
```{r crosstabulation4, echo=F}
```








### Wave 5 

#### Study-specific variable description



| **Name** |`mobirth`| `yrbirth`| `int_month_w5` | `int_year_w5` |
|-|-|-|-|-|
| **Label** | `month of birth` | `year of birth`| `interview month` | `interview year` |
| **Table name** | `sharew5_rel1-0-0_cv_r_without_noint` | `idem` | `idem` | `idem` |
| **Categories** | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  | `1 = january`<br/>`2 = february`<br/>`3 = march`<br/>`4 = april`<br/>`5 = may`<br/>`6 = june`<br/>`7 = july`<br/>`8 = august`<br/>`9 = september`<br/>`10 = october`<br/>`11 = november`<br/>`12 = december`<br/>`13 = today` |  |
| **Missings** | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` | `-2 = refusal`<br/>`-1 = don't know` |
| **Description** |  |  |  |  |



```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_age','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('yrbirth', 'mobirth', 'int_year_w5', 'int_month_w5'), missings = TRUE)
SHARE_w5_age <- opal.execute(o,'SHARE_w5_age')
```

```{r local5, echo=F}
vari <- SHARE_w5_age$yrbirth
kable(Continuous_summary(var = vari, missing_values = c(-2,-1))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w5_age, aes(yrbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency")+xlim(1905,2015)

vari <- SHARE_w5_age$mobirth
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of birth") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w5_age, aes(x=factor(mobirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- SHARE_w5_age$int_year_w5
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w5_age, aes(x=factor(int_year_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

vari <- SHARE_w5_age$int_month_w5
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "Month of interview") 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w5_age, aes(x=factor(int_month_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variables it has to be computed by applying the following formula: 

* `date of interview - date of birth`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_age$id)
#harmonise year of birth
SHARE_w5_age$year_of_birth <- car::recode(SHARE_w5_age$yrbirth, "-2=997; -1=998;  NA=999")

#harmonise month of birth
SHARE_w5_age$month_of_birth <- car::recode(SHARE_w5_age$mobirth, "-2=997; -1=998;  NA=999")

#harmonise month of interview
SHARE_w5_age$month_of_interview <- car::recode(SHARE_w5_age$int_month_w5, "-2=997; -1=998;  13=999; NA=999")

#harmonise year of interview
SHARE_w5_age$year_of_interview <- car::recode(SHARE_w5_age$int_year_w5, "-2=997; -1=998; NA=999")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SHARE_w5_age$age <- comp_age(y_birth=SHARE_w5_age$year_of_birth , m_birth=SHARE_w5_age$month_of_birth ,
         y_int=SHARE_w5_age$year_of_interview , m_int=SHARE_w5_age$month_of_interview , miss=c(997, 998, 999))


SHARE_ds_w5$age <- car::recode(SHARE_w5_age$age, "0=999; NA=999")
SHARE_ds_w5$age <- labelled(SHARE_ds_w5$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age") + ylab("Frequency")+xlim(20,110)
```

#### Validation
```{r crosstabulation5, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
