---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



```{r lab, echo=FALSE}
ds_label <- "Education"
ds_label_all <- "Highest level of formal education achieved"
```


<!-- ########################################################## --> 

# Data process

## SHARE 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `isced_r` |
|----------|------------|
| **Label** | `ISCED-97 coding of education` |
| **Table name** | `sharew1_rel2-6-0_gv_isced` |
| **Categories** | `0 = none; 1 = isced-97 code 1; 2 = isced-97 code 2; 3 = isced-97 code 3; 4 = isced-97 code 4; 5 = isced-97 code 5; 6 = isced-97 code 6; 95 = still in school; 97 = other` |
| **Missings** | `-7 = not yet coded (temporary); -2 = refusal; -1 = don't know` |
| **Description** |  |



```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_educ','SHARE.sharew1_rel2-6-0_gv_isced',
                         variables=list('isced_r'), missings = TRUE)
SHARE_w1_educ <- opal.execute(o,'SHARE_w1_educ')
```

```{r local1,  echo=FALSE}
vari <- SHARE_w1_educ$isced_r
kable(Categorical_summary(vari, missing_values = c(-7,-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-7,-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_educ, aes(x=factor(isced_r))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "none" into 0`
* `keep "isced-97 code 1" into 1`
* `keep "isced-97 code 2" into 2`
* `recode 3 "isced-97 code 3" into 2`
* `recode 4 "isced-97 code 4" into 2`
* `recode 5 "isced-97 code 5" into 3`
* `recode 6 "isced-97 code 6" into 3`
* `recode 95 "still in school" into 996`
* `recode 97 "other" into 999`
* `recode -7 "not yet coded (temporary)" into 994`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo1,   echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_educ$id)
SHARE_ds_w1$education <- car::recode(SHARE_w1_educ$isced_r, "3=2; 4=2; 5=3; 6=3; 95=996; 97=999; -7=994;-2=997; -1=998;  NA=999")
SHARE_ds_w1$education <- labelled(SHARE_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- SHARE_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(SHARE_w1_educ$isced_r)
BeforeH <- c(BeforeH[3], BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:9]), BeforeH[10], BeforeH[1], BeforeH[2], sum(BeforeH[11],sum(is.na(SHARE_w1_educ$isced_r))))
AfterH <- table(SHARE_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "(2,3,4)->2", "(5,6)->3", "95->996", "-2->997", "-1->998", "(97,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
label(SHARE_ds_w1$education) <- ds_label_all
education <- SHARE_ds_w1
save(education, file = "../RData/w1/education.RData")
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import( o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$education <- car::recode(SHARE_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import( o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description


 
| **Name** | `isced_r` |
|----------|------------|
| **Label** | `ISCED-97 coding of education` |
| **Table name** | `sharew2_rel2-6-0_gv_isced` |
| **Categories** | `0 = none; 1 = isced-97 code 1; 2 = isced-97 code 2; 3 = isced-97 code 3; 4 = isced-97 code 4; 5 = isced-97 code 5; 6 = isced-97 code 6; 95 = still in school; 97 = other` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_educ','SHARE.sharew2_rel2-6-0_gv_isced',
                         variables=list('isced_r'), missings = TRUE)
SHARE_w2_educ <- opal.execute(o,'SHARE_w2_educ')
```

```{r local2,  echo=FALSE}
vari <- SHARE_w2_educ$isced_r
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_educ, aes(x=factor(isced_r))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "none" into 0`
* `keep "isced-97 code 1" into 1`
* `keep "isced-97 code 2" into 2`
* `recode 3 "isced-97 code 3" into 2`
* `recode 4 "isced-97 code 4" into 2`
* `recode 5 "isced-97 code 5" into 3`
* `recode 6 "isced-97 code 6" into 3`
* `recode 95 "still in school" into 996`
* `recode 97 "other" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo2,   echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_educ$id)
SHARE_ds_w2$education <- car::recode(SHARE_w2_educ$isced_r, "3=2; 4=2; 5=3; 6=3; 95=996; 97=999; -2=997; -1=998;  NA=999")
SHARE_ds_w2$education <- labelled(SHARE_ds_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- SHARE_ds_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(SHARE_w2_educ$isced_r)
BeforeH <- c(BeforeH[3], BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:9]), BeforeH[10], BeforeH[1], BeforeH[2], sum(BeforeH[11],sum(is.na(SHARE_w2_educ$isced_r))))
AfterH <- table(SHARE_ds_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "(2,3,4)->2", "(5,6)->3", "95->996", "-2->997", "-1->998", "(97,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL2,  echo=FALSE}
label(SHARE_ds_w2$education) <- ds_label_all
education <- SHARE_ds_w2
save(education, file = "../RData/w2/education.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import( o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$education <- car::recode(SHARE_m_ds_w2$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import( o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

There is no variable.






### Wave 4 

#### Study-specific variable description

 
| **Name** | `isced_r` |
|----------|------------|
| **Label** | `ISCED-97 coding of education` |
| **Table name** | `sharew4_rel1-1-1_gv_isced` |
| **Categories** | `0 = none; 1 = isced-97 code 1; 2 = isced-97 code 2; 3 = isced-97 code 3; 4 = isced-97 code 4; 5 = isced-97 code 5; 6 = isced-97 code 6; 95 = still in school; 97 = other` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_educ','SHARE.sharew4_rel1-1-1_gv_isced',
                         variables=list('isced_r'), missings = TRUE)
opal.assign.table.tibble(o, 'SHARE_w4_id','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('hhid4'), missings = TRUE)
SHARE_w4_educ <- opal.execute(o,'SHARE_w4_educ')
SHARE_w4_id <- opal.execute(o,'SHARE_w4_id')
```

```{r local4,  echo=FALSE}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], isced_r=as.numeric(new_2[,2]))
  new_22
}

SHARE_w4_educ <- Add_indiv(old = SHARE_w4_educ, new = SHARE_w4_id)

vari <- SHARE_w4_educ$isced_r
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_educ, aes(x=factor(isced_r))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "none" into 0`
* `keep "isced-97 code 1" into 1`
* `keep "isced-97 code 2" into 2`
* `recode 3 "isced-97 code 3" into 2`
* `recode 4 "isced-97 code 4" into 2`
* `recode 5 "isced-97 code 5" into 3`
* `recode 6 "isced-97 code 6" into 3`
* `recode 95 "still in school" into 996`
* `recode 97 "other" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo4,   echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_educ$id)
SHARE_ds_w4$education <- car::recode(SHARE_w4_educ$isced_r, "3=2; 4=2; 5=3; 6=3; 95=996; 97=999;-2=997; -1=998;  NA=999")
SHARE_ds_w4$education <- labelled(SHARE_ds_w4$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- SHARE_ds_w4$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4,  echo=FALSE}
BeforeH <- table(SHARE_w4_educ$isced_r)
BeforeH <- c(BeforeH[3], BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:9]), BeforeH[10], BeforeH[1], BeforeH[2], sum(BeforeH[11],sum(is.na(SHARE_w4_educ$isced_r))))
AfterH <- table(SHARE_ds_w4$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "(2,3,4)->2", "(5,6)->3", "95->996", "-2->997", "-1->998", "(97,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL4,  echo=FALSE}
label(SHARE_ds_w4$education) <- ds_label_all
education <- SHARE_ds_w4
save(education, file = "../RData/w4/education.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import( o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$education <- car::recode(SHARE_m_ds_w4$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import( o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description


| **Name** | `isced2011_r` |
|----------|------------|
| **Label** | `ISCED-11 coding of education` |
| **Table name** | `sharew5_rel1-0-0_gv_isced` |
| **Categories** | `0 = none; 1 = isced-11 code 1; 2 = isced-11 code 2; 3 = isced-11 code 3; 4 = isced-11 code 4; 5 = isced-11 code 5; 6 = isced-11 code 6; 7 = ISCED-11 code 7; 8 = ISCED-11 code 8; 95 = still in school; 97 = other` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



* Description: 
```{r assign5,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_educ','SHARE.sharew5_rel1-0-0_gv_isced',
                         variables=list('isced2011_r'), missings = TRUE)
opal.assign.table.tibble(o, 'SHARE_w5_id','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('hhid5'), missings = TRUE)
SHARE_w5_educ <- opal.execute(o,'SHARE_w5_educ')
SHARE_w5_id <- opal.execute(o,'SHARE_w5_id')
```

```{r local5,  echo=FALSE}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], isced2011_r=as.numeric(new_2[,2]))
  new_22
}

SHARE_w5_educ <- Add_indiv(old = SHARE_w5_educ, new = SHARE_w5_id)

vari <- SHARE_w5_educ$isced2011_r
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w5_educ, aes(x=factor(isced2011_r))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "None" into 0`
* `keep "ISCED-11 code 1" into 1`
* `keep "ISCED-11 code 2" into 2`
* `recode 3 "ISCED-11 code 3" into 2`
* `recode 4 "ISCED-11 code 4" into 2`
* `recode 5 "ISCED-11 code 5" into 3`
* `recode 6 "ISCED-11 code 6" into 3`
* `recode 7 "ISCED-11 code 7" into 3`
* `recode 8 "ISCED-11 code 8" into 3`
* `recode 95 "still in school" into 996`
* `recode 97 "other" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo5,   echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_w5_educ$id)
SHARE_ds_w5$education <- car::recode(SHARE_w5_educ$isced2011_r, "3=2; 4=2; 5=3; 6=3;7=3; 8=3; 95=996; 97=999;-2=997; -1=998;  NA=999")
SHARE_ds_w5$education <- labelled(SHARE_ds_w5$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5,  echo=FALSE}
vari <- SHARE_ds_w5$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5,  echo=FALSE}
BeforeH <- table(SHARE_w5_educ$isced2011_r)
BeforeH <- c(BeforeH[3], BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:11]), BeforeH[1], BeforeH[2], sum(BeforeH[12],sum(is.na(SHARE_w5_educ$isced2011_r))))
AfterH <- table(SHARE_ds_w5$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "(2,3,4)->2", "(5,6,7,8)->3", "-2->997", "-1->998", "(97,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL5,  echo=FALSE}
label(SHARE_ds_w5$education) <- ds_label_all
education <- SHARE_ds_w5
save(education, file = "../RData/w5/education.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import( o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$education <- car::recode(SHARE_m_ds_w5$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import( o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```


# Quality estimation

The SHARE study used the ISCED to create the education variable. They used the ISCED-1997 in w1, w2, w4 and ISCED-2011 in w4. We transformed that into a 4-label categorical variable taking into account the ISCED directions. 

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
