---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```


<!-- ########################################################## --> 

# Data process

## India

### Wave 1 

#### Study-specific variable description


| **Name** | `ht301`| `ht302` | `ht303` | `ht304` | `ht305` | `ht306` | `ht307` | `ht308` | `ht309` | `ht310` | 
|-|-|-|-|-|-|-|-|-|-|-| 
| **Label** | `bothered by things that do not usually bother me`| `did not feel like eating` | `could not shake off blues` | `felt not as good as others` | `had trouble focusing` | `felt depressed` | `felt everything was an effort` | `felt hopeless about future` | `felt life was a failure` | `felt fearful` | 
| **Table name** | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | 
| **Categories** |`0 = rarely or none of the time; less than 1 day`| `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | 
| | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days`| ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | 
| | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | 
| | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | 
| **Missing** |`5 = dk`| `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | 
| | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | 


| **Name** | `ht311`| `ht312` | `ht313` | `ht314` | `ht315` | `ht316` | `ht317` | `ht318` | `ht319` | `ht320` | 
|-|-|-|-|-|-|-|-|-|-|-| 
| **Label** | `sleep was restless`| `felt unhappy` | `talked less than usual` | `felt lonely` | `people were unfriendly` | `did not enjoy life` | `crying spells` | `felt sad` | `people disliked me` | `could not get going` | 
| **Table name** | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | 
| **Categories** |`0 = rarely or none of the time; less than 1 day`| `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | `0 = rarely or none of the time; less than 1 day` | 
| | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days`| ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | ` 2 = some or little of the time; 1 to 2 days` | 
| | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | ` 3 = occasionally or a moderate amount of the time; 3 to 4 days` | 
| | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | ` 4 = most or all of the time; 5 to 7 days` | 
| **Missing** |`5 = dk`| `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | `5 = dk` | 
| | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | `6 = rf` | 


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_dep','LASI.LASI-Pilot_all',
                         variables=list('ht301', 'ht302', 'ht303', 'ht304', 'ht305', 'ht306', 'ht307', 'ht308', 'ht309', 'ht310', 'ht311', 'ht312', 'ht313', 'ht314', 'ht315', 'ht316', 'ht317', 'ht318', 'ht319', 'ht320'), missings = TRUE)
LASI_dep <- opal.execute(o,'LASI_dep')
```

```{r local1, echo=FALSE}
vari <- LASI_dep$ht301
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht302
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht303
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht304
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht305
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht306
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht307
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht308
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht309
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht310
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht311
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht312
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht313
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht314
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht315
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht316
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht317
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht318
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht319
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_dep$ht320
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
ggplot(LASI_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 
* The reversed items ht304, ht308, ht312, ht316: 
  + `recode 1 into 3`
  + `keep 2`
  + `recode 3 into 1`
  + `recode 4 into 0`
* The direct items ht301, ht302, ht303, ht305, ht306, ht307, ht309, ht310, ht311, ht313, ht314, ht315,ht317, ht318, ht319, ht320: 
  + `recode 1 into 0`
  + `recode 2 into 1`
  + `recode 3 into 2`
  + `recode 4 into 3`

Secondly in order to get the final score the items have to be summed. If one to 4 items are missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 20. If more than 4 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 
* `0-15 into 0`
* `>16 into 1`
* `NA into`
  + `997 if the individual has more items = 6 than 5 and NA`
  + `998 if the individual has more items = 5 than 6 and NA`
  + `999 if the individual has more items = NA than 5 and 6`

**R script:**

```{r harmo1, echo=TRUE}
#reversed items
LASI_dep$p304 <- car::recode(LASI_dep$ht304, "1=3; 3=1; 4=0; 5=NA; 6=NA")
LASI_dep$p308 <- car::recode(LASI_dep$ht308, "1=3; 3=1; 4=0; 5=NA; 6=NA")
LASI_dep$p312 <- car::recode(LASI_dep$ht312, "1=3; 3=1; 4=0; 5=NA; 6=NA")
LASI_dep$p316 <- car::recode(LASI_dep$ht316, "1=3; 3=1; 4=0; 5=NA; 6=NA")

#direct items
LASI_dep$p301 <- car::recode(LASI_dep$ht301, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p302 <- car::recode(LASI_dep$ht302, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p303 <- car::recode(LASI_dep$ht303, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p305 <- car::recode(LASI_dep$ht305, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p306 <- car::recode(LASI_dep$ht306, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p307 <- car::recode(LASI_dep$ht307, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p309 <- car::recode(LASI_dep$ht309, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p310 <- car::recode(LASI_dep$ht310, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p311 <- car::recode(LASI_dep$ht311, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p313 <- car::recode(LASI_dep$ht313, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p314 <- car::recode(LASI_dep$ht314, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p315 <- car::recode(LASI_dep$ht315, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p317 <- car::recode(LASI_dep$ht317, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p318 <- car::recode(LASI_dep$ht318, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p319 <- car::recode(LASI_dep$ht319, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")
LASI_dep$p320 <- car::recode(LASI_dep$ht320, "1=0; 2=1; 3=2; 4=3; 5=NA; 6=NA")

LASI_dep$nmiss <- apply(LASI_dep[,22:41], MARGIN = 1, FUN = function(x) sum(is.na(x)))


LASI_dep$final_score <- apply(LASI_dep[,22:41], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))


LASI_dep$final_score[which(LASI_dep$nmiss==3)] <- (LASI_dep$final_score[which(LASI_dep$nmiss==3)]/17)*20
LASI_dep$final_score[which(LASI_dep$nmiss==2)] <- (LASI_dep$final_score[which(LASI_dep$nmiss==2)]/18)*20
LASI_dep$final_score[which(LASI_dep$nmiss==1)] <- (LASI_dep$final_score[which(LASI_dep$nmiss==1)]/19)*20

LASI_dep$n5 <- apply(LASI_dep[,2:21], MARGIN = 1, FUN = function(x) sum(x==5, na.rm = TRUE))
LASI_dep$n6 <- apply(LASI_dep[,2:21], MARGIN = 1, FUN = function(x) sum(x==6, na.rm = TRUE))
LASI_dep$nNA <- apply(LASI_dep[,2:21], MARGIN = 1, FUN = function(x) sum(is.na(x)))

LASI_dep$max_5_6_NA <- apply(LASI_dep[,44:46], MARGIN = 1, FUN = function(x) which.max(x))
LASI_dep$max_5_6_NA <- car::recode(LASI_dep$max_5_6_NA, "1=998;2=997;3=999")

LASI_dep$final_score[which(LASI_dep$nmiss>4)] <- LASI_dep$max_5_6_NA[which(LASI_dep$nmiss>4)]


LASI_ds_w1 <- tibble(id=LASI_dep$id)
LASI_ds_w1$depression <- car::recode(LASI_dep$final_score, "0:15.99999999=0; 16:900=1")
LASI_ds_w1$depression <- labelled(LASI_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- LASI_ds_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(LASI_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- c(sum(na.omit(LASI_dep$final_score)<16), sum(na.omit(LASI_dep$final_score)>=16 & na.omit(LASI_dep$final_score)<900), sum(na.omit(LASI_dep$final_score)==997), sum(na.omit(LASI_dep$final_score)==998), sum(na.omit(LASI_dep$final_score)==999))
AfterH <- table(LASI_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<16->0",">=16->1","6->997", "5->998", "NA->999") 
kable(C)
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')

label(LASI_ds_w1$depression) <- ds_label_all
depression <- LASI_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(depression)

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$depression <- car::recode(LASI_m_ds_w1$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation

They used the Center for Epidemiologic Studies Depression Scale (CES-D). 20-ITEM VERSION
We didn't have the final score variable, thus we got the harmonized depression variable using single items.
In this tool (CES-D) there are some reversed items. In the LASI study instead of use these reversed items, they changed it > ORIGINAL 'I was happy' - LASI 'I felt unnhappy'; ORIGINAL 'I enjoyed life' - LASI 'I did not enjoy life'
The missing values were treated as follows: maximum 3 missing items were allowed > score the completed items divided by the number of items answered and multiplied by 20.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
