---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```

  
# Data process

## South Africa

### Wave 1 


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_ls','SAGE.southAfricaINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_SA_ls <- opal.execute(o,'SAGE_SA_ls')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_ls$id)
SAGE_SA_ds_w1$living_status <- 0
SAGE_SA_ds_w1$living_status <- labelled(SAGE_SA_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SAGE_SA_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_SA_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_SA_ds_w1
save(living_status, file = "../RData/SA_w1/living_status.RData")
rm(living_status)

SAGE_SA_m_ds_w1 <- SAGE_SA_ds_w1
SAGE_SA_m_ds_w1$living_status <- car::recode(SAGE_SA_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_SA_m_ds_w1', SAGE_SA_m_ds_w1)
#opal.symbol_import(o,'SAGE_SA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




## Ghana

### Wave 1 


```{r assign_ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_ls','SAGE.ghanaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_ghana_ls <- opal.execute(o,'SAGE_ghana_ls')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_ghana}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_ls$id)
SAGE_ghana_ds_w1$living_status <- 0
SAGE_ghana_ds_w1$living_status <- labelled(SAGE_ghana_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vari <- SAGE_ghana_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ghana_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ghana, echo=F}
```





```{r importOPAL_ghana, echo=F}

#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_ghana_ds_w1
save(living_status, file = "../RData/ghana_w1/living_status.RData")
rm(living_status)

SAGE_ghana_m_ds_w1 <- SAGE_ghana_ds_w1
SAGE_ghana_m_ds_w1$living_status <- car::recode(SAGE_ghana_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```





## China

### Wave 1 


```{r assign_china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_ls','SAGE.chinaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_china_ls <- opal.execute(o,'SAGE_china_ls')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_china}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_ls$id)
SAGE_china_ds_w1$living_status <- 0
SAGE_china_ds_w1$living_status <- labelled(SAGE_china_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vari <- SAGE_china_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_china_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_china, echo=F}
```





```{r importOPAL_china, echo=F}

#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_china_ds_w1
save(living_status, file = "../RData/china_w1/living_status.RData")
rm(living_status)

SAGE_china_m_ds_w1 <- SAGE_china_ds_w1
SAGE_china_m_ds_w1$living_status <- car::recode(SAGE_china_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## India

### Wave 1 


```{r assign_india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_ls','SAGE.indiaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_india_ls <- opal.execute(o,'SAGE_india_ls')
```



#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_india}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_ls$id)
SAGE_india_ds_w1$living_status <- 0
SAGE_india_ds_w1$living_status <- labelled(SAGE_india_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vari <- SAGE_india_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_india_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_india, echo=F}
```





```{r importOPAL_india, echo=F}

#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_india_ds_w1
save(living_status, file = "../RData/india_w1/living_status.RData")
rm(living_status)

SAGE_india_m_ds_w1 <- SAGE_india_ds_w1
SAGE_india_m_ds_w1$living_status <- car::recode(SAGE_india_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Russia

### Wave 1 


```{r assign_russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_ls','SAGE.russiaINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_russia_ls <- opal.execute(o,'SAGE_russia_ls')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_russia}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_ls$id)
SAGE_russia_ds_w1$living_status <- 0
SAGE_russia_ds_w1$living_status <- labelled(SAGE_russia_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vari <- SAGE_russia_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_russia_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_russia, echo=F}
```





```{r importOPAL_russia, echo=F}

#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_russia_ds_w1
save(living_status, file = "../RData/russia_w1/living_status.RData")
rm(living_status)

SAGE_russia_m_ds_w1 <- SAGE_russia_ds_w1
SAGE_russia_m_ds_w1$living_status <- car::recode(SAGE_russia_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Mexico

### Wave 1 


```{r assign_Mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_ls','SAGE.mexicoINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_mexico_ls <- opal.execute(o,'SAGE_mexico_ls')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_Mexico}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_ls$id)
SAGE_mexico_ds_w1$living_status <- 0
SAGE_mexico_ds_w1$living_status <- labelled(SAGE_mexico_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vari <- SAGE_mexico_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_mexico_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
```





```{r importOPAL_Mexico, echo=F}

#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
living_status <- SAGE_mexico_ds_w1
save(living_status, file = "../RData/mexico_w1/living_status.RData")
rm(living_status)

SAGE_mexico_m_ds_w1 <- SAGE_mexico_ds_w1
SAGE_mexico_m_ds_w1$living_status <- car::recode(SAGE_mexico_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
