---
title: "Eye sight - General vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_gen`
* Variable label: `Eyesight - general vision`
* Variable description: `Difficulties in  eye sight using glasses or corrective lens as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Korea

### Wave 1 

#### Study-specific variable description




| **Name** | `w01C063`|
|-|-|
| **Label** | `Eyesight` |
| **Table name** | `w01_main_e` |
| **Categories** |  `1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_eye_gen','KLOSA.w01_main_e', variables=list('w01C063'), missings = TRUE)
```

```{r local w1, echo=F}
KLOSA_w1_eye_gen <- opal.execute(o,'KLOSA_w1_eye_gen')
vari <- KLOSA_w1_eye_gen$w01C063
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w01C063")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_eye_gen, aes(x=factor(w01C063))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0`
* `NA into 999`

**R script:**
```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_eye_gen$id)
KLOSA_ds_w1$eye_gen <- car::recode(KLOSA_w1_eye_gen$w01C063, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w1$eye_gen <- labelled(KLOSA_ds_w1$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- KLOSA_ds_w1$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(KLOSA_ds_w1$eye_gen)
X<-table(KLOSA_w1_eye_gen$w01C063)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(KLOSA_w1_eye_gen$w01C063)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")  
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(KLOSA_ds_w1$eye_gen) <- "eyesight"
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
eye_gen <- KLOSA_ds_w1
save(eye_gen, file = "../RData/w1/eye_gen.RData")

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$eye_gen <- car::recode(KLOSA_m_ds_w1$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `w02C075`|
|-|-|
| **Label** | `Eyesight(wearing glasses)` |
| **Table name** | `w02_main_e_spss` |
| **Categories** |  `1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_eye_gen','KLOSA.w02_main_e_spss', variables=list('w02C075'), missings = TRUE)
```

```{r local w2, echo=F}
KLOSA_w2_eye_gen <- opal.execute(o,'KLOSA_w2_eye_gen')
vari <- KLOSA_w2_eye_gen$w02C075
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w02C075")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_eye_gen, aes(x=factor(w02C075))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_eye_gen$id)
KLOSA_ds_w2$eye_gen <- car::recode(KLOSA_w2_eye_gen$w02C075, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w2$eye_gen <- labelled(KLOSA_ds_w2$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- KLOSA_ds_w2$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(KLOSA_ds_w2$eye_gen)
X<-table(KLOSA_w2_eye_gen$w02C075)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(KLOSA_w2_eye_gen$w02C075)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")  
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(KLOSA_ds_w2$eye_gen) <- "eyesight"
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
eye_gen <- KLOSA_ds_w2
save(eye_gen, file = "../RData/w2/eye_gen.RData")

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$eye_gen <- car::recode(KLOSA_m_ds_w2$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `w03C075`|
|-|-|
| **Label** | `Eyesight` |
| **Table name** | `w03_main_e_spss_albert` |
| **Categories** |  `1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|
| **Missings** |`NA` |
| **Description** |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_eye_gen','KLOSA.w03_main_e_spss_albert', variables=list('w03C075'), missings = TRUE)
KLOSA_w3_eye_gen <- opal.execute(o,'KLOSA_w3_eye_gen')

# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_eye_gen$id <- substr(KLOSA_w3_eye_gen$id,1,nchar(KLOSA_w3_eye_gen$id)-2)
```

```{r local w3, echo=F}
vari <- KLOSA_w3_eye_gen$w03C075
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w03C075")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_eye_gen, aes(x=factor(w03C075))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_eye_gen$id)
KLOSA_ds_w3$eye_gen <- car::recode(KLOSA_w3_eye_gen$w03C075, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w3$eye_gen <- labelled(KLOSA_ds_w3$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- KLOSA_ds_w3$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(KLOSA_ds_w3$eye_gen)
X<-table(KLOSA_w3_eye_gen$w03C075)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(KLOSA_w3_eye_gen$w03C075)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")  
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(KLOSA_ds_w3$eye_gen) <- "eyesight"
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
eye_gen <- KLOSA_ds_w3
save(eye_gen, file = "../RData/w3/eye_gen.RData")

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$eye_gen <- car::recode(KLOSA_m_ds_w3$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description




| **Name** | `w04C075`|
|-|-|
| **Label** | `Eyesight` |
| **Table name** | `w04_main_e_spss` |
| **Categories** |  `1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_eye_gen','KLOSA.w04_main_e_spss', variables=list('w04C075'), missings = TRUE)
```

```{r local w4, echo=F}
KLOSA_w4_eye_gen <- opal.execute(o,'KLOSA_w4_eye_gen')
vari <- KLOSA_w4_eye_gen$w04C075
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w04C075")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_eye_gen, aes(x=factor(w04C075))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_eye_gen$id)
KLOSA_ds_w4$eye_gen <- car::recode(KLOSA_w4_eye_gen$w04C075, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w4$eye_gen <- labelled(KLOSA_ds_w4$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- KLOSA_ds_w4$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(KLOSA_ds_w4$eye_gen)
X<-table(KLOSA_w4_eye_gen$w04C075)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(KLOSA_w4_eye_gen$w04C075)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")  
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(KLOSA_ds_w4$eye_gen) <- "eyesight"
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
eye_gen <- KLOSA_ds_w4
save(eye_gen, file = "../RData/w4/eye_gen.RData")

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$eye_gen <- car::recode(KLOSA_m_ds_w4$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
