---
title: "Eye sight - Near vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_near`
* Variable label: `Eyesight - Near vision`
* Variable description: `Difficulties for near vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Korea

### Wave 1 

##### Study-specific variables



| **Name** | `w01C062`|`w01C065`|
|-|-|-|
| **Label** | `At ordinary times, whether use glasses and contact lenses` |`Eyesight for near object` |
| **Table name** | `w01_main_e` |`w01_main_e` |
| **Categories** |`1 = Yes; 3 = Legally blind; 5 = No`|`1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|
| **Missings** |`NA` |`NA` |
| **Description** |  |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_eye_near','KLOSA.w01_main_e', variables=list('w01C062','w01C065'), missings = TRUE)
```

```{r local w1, echo=F}
KLOSA_w1_eye_near <- opal.execute(o,'KLOSA_w1_eye_near')
vari <- KLOSA_w1_eye_near$w01C062
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w01C062")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_eye_near, aes(x=factor(w01C062))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Glasses") + ylab("Frequency")
vari <- KLOSA_w1_eye_near$w01C065
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w01C065")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_eye_near, aes(x=factor(w01C065))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w01C062==3 into 0`
* `1,2 into 1` 
* `3,4,5 into 0`
* `NA into 999`

**R script:**
```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_eye_near$id)
KLOSA_ds_w1$eye_near <- car::recode(KLOSA_w1_eye_near$w01C065, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w1$eye_near[which(KLOSA_w1_eye_near$w01C062==3)] <- 0
KLOSA_ds_w1$eye_near <- labelled(KLOSA_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- KLOSA_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(KLOSA_ds_w1$eye_near)
X<-table(KLOSA_w1_eye_near$w01C065)
BeforeH <- c(sum(X[3:5],length(which(KLOSA_w1_eye_near$w01C062==3))),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5,blind->0","1,2->1")  
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(KLOSA_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- KLOSA_ds_w1
save(eye_near, file = "../RData/w1/eye_near.RData")

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$eye_near <- car::recode(KLOSA_m_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

##### Study-specific variables




| **Name** | `w02C077`|`w02C074`|
|-|-|-|
| **Label** | `Eyesight for near object` |`Usually whether used glasses and contact lenses or not`|
| **Table name** | `w02_main_e_spss` |`w02_main_e_spss` |
| **Categories** |`1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|`1 = yes; 3 = Visually disabled (blind); 5 = no`|
| **Missings** |`NA` |  |
| **Description** |  |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_eye_near','KLOSA.w02_main_e_spss', variables=list('w02C077','w02C074'), missings = TRUE)
```

```{r local w2, echo=F}
KLOSA_w2_eye_near <- opal.execute(o,'KLOSA_w2_eye_near')
vari <- KLOSA_w2_eye_near$w02C077
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w02C077")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_eye_near, aes(x=factor(w02C077))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
vari <- KLOSA_w2_eye_near$w02C074
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w02C074")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_eye_near, aes(x=factor(w02C074))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Glasses") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`
* `w02C074==3 into 0`

**R script:**
```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_eye_near$id)
KLOSA_ds_w2$eye_near <- car::recode(KLOSA_w2_eye_near$w02C077, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w2$eye_near[which(KLOSA_w2_eye_near$w02C074==3)] <- 0
KLOSA_ds_w2$eye_near <- labelled(KLOSA_ds_w2$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- KLOSA_ds_w2$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(KLOSA_ds_w2$eye_near)
X<-table(KLOSA_w2_eye_near$w02C077)
BeforeH <- c(sum(X[3:5]),sum(X[1:2],length(which(KLOSA_w2_eye_near$w02C074==3))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5,blind->0","1,2->1")  
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(KLOSA_ds_w2$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
eye_near <- KLOSA_ds_w2
save(eye_near, file = "../RData/w2/eye_near.RData")

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$eye_near <- car::recode(KLOSA_m_ds_w2$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

##### Study-specific variables




| **Name** | `w03C077`|`w03C074`|
|-|-|-|
| **Label** | `Eyesight for near object` |`At ordinary times, whether use glasses and contact lenses`|
| **Table name** | `w03_main_e_spss_albert` | `w03_main_e_spss_albert` |
| **Categories** |`1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|`1 = yes; 3 = Visually disabled (blind); 5 = no`|
| **Missings** |`NA` |  |
| **Description** |  |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_eye_near','KLOSA.w03_main_e_spss_albert', variables=list('w03C077','w03C074'), missings = TRUE)
KLOSA_w3_eye_near <- opal.execute(o,'KLOSA_w3_eye_near')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_eye_near$id <- substr(KLOSA_w3_eye_near$id,1,nchar(KLOSA_w3_eye_near$id)-2)
```

```{r local w3, echo=F}
vari <- KLOSA_w3_eye_near$w03C077
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w03C077")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_eye_near, aes(x=factor(w03C077))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
vari <- KLOSA_w3_eye_near$w03C074
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w03C074")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_eye_near, aes(x=factor(w03C074))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Glasses") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`
* `w03C074==3 into 0`

**R script:**
```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_eye_near$id)
KLOSA_ds_w3$eye_near <- car::recode(KLOSA_w3_eye_near$w03C077, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w3$eye_near[which(KLOSA_w3_eye_near$w03C074==3)] <- 0
KLOSA_ds_w3$eye_near <- labelled(KLOSA_ds_w3$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- KLOSA_ds_w3$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(KLOSA_ds_w3$eye_near)
X<-table(KLOSA_w3_eye_near$w03C077)
BeforeH <- c(sum(X[3:5]),sum(X[1:2],length(which(KLOSA_w2_eye_near$w02C074==3))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5,blind->0","1,2->1")  
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(KLOSA_ds_w3$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
eye_near <- KLOSA_ds_w3
save(eye_near, file = "../RData/w3/eye_near.RData")

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$eye_near <- car::recode(KLOSA_m_ds_w3$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

##### Study-specific variables




| **Name** | `w04C077`|`w04C074`|
|-|-|-|
| **Label** | `Eyesight for near object` |`At ordinary times, whether use glasses and contact lenses`|
| **Table name** | `w04_main_e_spss` | `w04_main_e_spss` |
| **Categories** |`1 = Very good; 2 = Good; 3 = Fair; 4 = Poor; 5 = Very poor`|`1 = yes; 3 = Visually disabled (blind); 5 = no`|
| **Missings** |`NA` |`-9 = Don't know`|
| **Description** |  |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_eye_near','KLOSA.w04_main_e_spss', variables=list('w04C077','w04C074'), missings = TRUE)
```

```{r local w4, echo=F}
KLOSA_w4_eye_near <- opal.execute(o,'KLOSA_w4_eye_near')
vari <- KLOSA_w4_eye_near$w04C077
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w04C077")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_eye_near, aes(x=factor(w04C077))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
vari <- KLOSA_w4_eye_near$w04C074
kable(Categorical_summary(vari, missing_values = c(-9))[3], caption = "w04C074")
kable(Categorical_summary(vari, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w4_eye_near, aes(x=factor(w04C074))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Glasses") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4,5 into 0` 
* `NA into 999`
* `w04C074==3 into 0`

**R script:**
```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_eye_near$id)
KLOSA_ds_w4$eye_near <- car::recode(KLOSA_w4_eye_near$w04C077, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';NA = '999' ")
KLOSA_ds_w4$eye_near[which(KLOSA_w4_eye_near$w04C074==3)] <- 0

KLOSA_ds_w4$eye_near <- labelled(KLOSA_ds_w4$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- KLOSA_ds_w4$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(KLOSA_ds_w4$eye_near)
X<-table(KLOSA_w4_eye_near$w04C077)
BeforeH <- c(sum(X[3:5]),sum(X[1:2],length(which(KLOSA_w2_eye_near$w02C074==3))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5,blind->0","1,2->1")  
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(KLOSA_ds_w4$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
eye_near <- KLOSA_ds_w4
save(eye_near, file = "../RData/w4/eye_near.RData")

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$eye_near <- car::recode(KLOSA_m_ds_w4$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```





# Quality estimation

We must remark that the individuals with missing values in the 'eyesight for near object' variables coincide with the blind individuals in the 'glasses variables'.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
