---
title: "ADL- Getting in or out of bed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `adl_bed`
* Variable label: `ADL-Difficulties for getting in or out of bed`
* Variable description: `ADL-Difficulties for getting in or out of bed`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## Korea
### Wave 1

Not found.



### Wave 2 

#### Study-specific variable description

 


* Name: `w02C205`
* Label: `ADL(Necessity of aid for daily life)_getting out of bed and walking out of the room`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_adl_bed','KLOSA.w02_main_e_spss', variables=list('w02C205'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
KLOSA_w2_adl_bed <- opal.execute(o,'KLOSA_w2_adl_bed')
vari <- KLOSA_w2_adl_bed$w02C205 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(KLOSA_w2_adl_bed$w02C205)
ggplot(KLOSA_w2_adl_bed, aes(x=factor(w02C205))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Getting in or out of bed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`
**R script:**
```{r harmo w2,   echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_adl_bed$id)
KLOSA_ds_w2$adl_bed <- car::recode( KLOSA_w2_adl_bed$w02C205, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w2$adl_bed <- labelled(KLOSA_ds_w2$adl_bed, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- KLOSA_ds_w2$adl_bed # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$adl_bed, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(adl_bed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Getting in or out of bed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(KLOSA_ds_w2$adl_bed)
X<-table(KLOSA_w2_adl_bed$w02C205)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```


```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(KLOSA_ds_w2) <- NULL
label(KLOSA_ds_w2$adl_bed) <- "Difficulties for getting in or out of bed"
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$adl_bed <- car::recode( KLOSA_m_ds_w2$adl_bed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_bed<- KLOSA_ds_w2
save(adl_bed, file = paste0(datafolder, "/w2/adl_bed.RData"))
```

### Wave 3

Not found. 


### Wave 4

Not found.

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
