---
title: "IADLs - Doing housework"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_housewk`
* Variable label: `IADL - Difficulties for doing housework`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## Korea
### Wave 1 

#### Study-specific variable description

 


* Name: `w01Cb09`
* Label: `Home cleaning/arrangement putting in order/dish washing etc..`
* Categories:
    + `1 = No, I don't need any help.`
    + `3 = Yes, I need help to some extent.`
    + `5 = Yes, I need help in every respect.`
* Missings
   
* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_iadl_housewk','KLOSA.w01_main_e', variables=list('w01Cb09'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
KLOSA_w1_iadl_housewk <- opal.execute(o,'KLOSA_w1_iadl_housewk')
vari <- KLOSA_w1_iadl_housewk$w01Cb09
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(KLOSA_w1_iadl_housewk$w01Cb09)
ggplot(KLOSA_w1_iadl_housewk, aes(x=factor(w01Cb09))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:** 
```{r harmo w1,   echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_iadl_housewk$id)
KLOSA_ds_w1$iadl_housewk <- car::recode(KLOSA_w1_iadl_housewk$w01Cb09, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w1$iadl_housewk <- labelled(KLOSA_ds_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- KLOSA_ds_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(KLOSA_ds_w1$iadl_housewk)
X<-table(KLOSA_w1_iadl_housewk$w01Cb09)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(KLOSA_ds_w1) <- NULL
label(KLOSA_ds_w1$iadl_housewk) <- "Home cleaning/arrangement putting in order/dish washing etc."
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$iadl_housewk <- car::recode(KLOSA_m_ds_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- KLOSA_ds_w1
save(iadl_housewk, file = paste0(datafolder, "/w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


* Name: `w02C209`
* Label: `IADL(Necessity of aid for daily life)_doing housework`
* Categories:
    + `1 = No, I don't need any help.`
    + `3 = Yes, I need help to some extent.`
    + `5 = Yes, I need help in every respect.`
* Missings


* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_iadl_housewk','KLOSA.w02_main_e_spss', variables=list('w02C209'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
KLOSA_w2_iadl_housewk <- opal.execute(o,'KLOSA_w2_iadl_housewk')
vari <- KLOSA_w2_iadl_housewk$w02C209
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(KLOSA_w2_iadl_housewk$w02C209)
ggplot(KLOSA_w2_iadl_housewk, aes(x=factor(w02C209))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:** 
```{r harmo w2,   echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_iadl_housewk$id)
KLOSA_ds_w2$iadl_housewk <- car::recode(KLOSA_w2_iadl_housewk$w02C209, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w2$iadl_housewk <- labelled(KLOSA_ds_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- KLOSA_ds_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(KLOSA_ds_w2$iadl_housewk)
X<-table(KLOSA_w2_iadl_housewk$w02C209)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(KLOSA_ds_w2) <- NULL
label(KLOSA_ds_w2$iadl_housewk) <- "Home cleaning/arrangement putting in order/dish washing etc."
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$iadl_housewk <- car::recode(KLOSA_m_ds_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- KLOSA_ds_w2
save(iadl_housewk, file = paste0(datafolder, "/w2/iadl_housewk.RData"))
```


### Wave 3 

#### Study-specific variable description

 


* Name: `w03C209`
* Label: `Home cleaning/arrangement putting in order/dish washing etc..`
* Categories:
    + `1 = No, I don't need any help.`
    + `3 = Yes, I need help to some extent.`
    + `5 = Yes, I need help in every respect.`
* Missings


* Description: 
```{r assign w3,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_iadl_housewk','KLOSA.w03_main_e_spss_albert', variables=list('w03C209'), missings = TRUE)
KLOSA_w3_iadl_housewk <- opal.execute(o,'KLOSA_w3_iadl_housewk')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_iadl_housewk$id <- substr(KLOSA_w3_iadl_housewk$id,1,nchar(KLOSA_w3_iadl_housewk$id)-2)
```

```{r local w3,  echo=FALSE}
vari <- KLOSA_w3_iadl_housewk$w03C209
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(KLOSA_w3_iadl_housewk$w03C209)
ggplot(KLOSA_w3_iadl_housewk, aes(x=factor(w03C209))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:** 
```{r harmo w3,   echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_iadl_housewk$id)
KLOSA_ds_w3$iadl_housewk <- car::recode(KLOSA_w3_iadl_housewk$w03C209, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w3$iadl_housewk <- labelled(KLOSA_ds_w3$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- KLOSA_ds_w3$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(KLOSA_ds_w3$iadl_housewk)
X<-table(KLOSA_w3_iadl_housewk$w03C209)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

 
 


 
```{r importOPAL w3, echo=FALSE,  echo=FALSE}
val_labels(KLOSA_ds_w3) <- NULL
label(KLOSA_ds_w3$iadl_housewk) <- "Home cleaning/arrangement putting in order/dish washing etc."
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$iadl_housewk <- car::recode(KLOSA_m_ds_w3$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- KLOSA_ds_w3
save(iadl_housewk, file = paste0(datafolder, "/w3/iadl_housewk.RData"))
```

### Wave 4

#### Study-specific variable description

 


* Name: `w04C209`
* Label: `Home cleaning/arrangement putting in order/dish washing etc..`
* Categories:
    + `1 = No, I don't need any help.`
    + `3 = Yes, I need help to some extent.`
    + `5 = Yes, I need help in every respect.`
* Missings


* Description: 
```{r assign w4,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_iadl_housewk','KLOSA.w04_main_e_spss', variables=list('w04C209'), missings = TRUE)
```

```{r local w4,  echo=FALSE}
KLOSA_w4_iadl_housewk <- opal.execute(o,'KLOSA_w4_iadl_housewk')
vari <- KLOSA_w4_iadl_housewk$w04C209
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(KLOSA_w4_iadl_housewk$w04C209)
ggplot(KLOSA_w4_iadl_housewk, aes(x=factor(w04C209))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:** 
```{r harmo w4,   echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_iadl_housewk$id)
KLOSA_ds_w4$iadl_housewk <- car::recode(KLOSA_w4_iadl_housewk$w04C209, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w4$iadl_housewk <- labelled(KLOSA_ds_w4$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
vari <- KLOSA_ds_w4$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(KLOSA_ds_w4$iadl_housewk)
X<-table(KLOSA_w4_iadl_housewk$w04C209)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

 
 


 
```{r importOPAL w4, echo=FALSE,  echo=FALSE}
val_labels(KLOSA_ds_w4) <- NULL
label(KLOSA_ds_w4$iadl_housewk) <- "Home cleaning/arrangement putting in order/dish washing etc."
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$iadl_housewk <- car::recode(KLOSA_m_ds_w4$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- KLOSA_ds_w4
save(iadl_housewk, file = paste0(datafolder, "/w4/iadl_housewk.RData"))
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
