---
title: "IADL - Getting out of home"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_outhome`
* Variable label: `IADL - Difficulties for getting out of home`
* Variable description: `IADL - Difficulties for getting out of home`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for getting out of home"
```


# Data process

## Korea

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `w01Cb13`
* Label: ` Going out that use transportation`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings
   + `-8 = Refuse to answer`
   
```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_iadl_outhome','KLOSA.w01_main_e', variables=list('w01Cb13'), missings = TRUE)
KLOSA_w1_iadl_outhome <- opal.execute(o,'KLOSA_w1_iadl_outhome')
```

```{r local w1, echo=FALSE}
vari <- KLOSA_w1_iadl_outhome$w01Cb13
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
ggplot(KLOSA_w1_iadl_outhome, aes(x=factor(w01Cb13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`
* `-8 into 997`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_iadl_outhome$id)
KLOSA_ds_w1$iadl_outhome <- car::recode(KLOSA_w1_iadl_outhome$w01Cb13, "1 = '1';3 = '0';5 = '0';-8 = '997' ")
KLOSA_ds_w1$iadl_outhome <- labelled(KLOSA_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- KLOSA_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(KLOSA_ds_w1$iadl_outhome)
X<-table(KLOSA_w1_iadl_outhome$w01Cb13)
BeforeH <- c(sum(X[c(3,4)]),X[c(2,1)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1","-8->997") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(KLOSA_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- KLOSA_ds_w1
save(iadl_outhome, file = "../RData/w1/iadl_outhome.RData")
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$iadl_outhome <- car::recode(KLOSA_m_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w02C213`
* Label: ` IADL(Necessity of aid for daily life)_going out using transportation`
* Categories:
   + `1 = No, I don't need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_iadl_outhome','KLOSA.w02_main_e_spss', variables=list('w02C213'), missings = TRUE)
KLOSA_w2_iadl_outhome <- opal.execute(o,'KLOSA_w2_iadl_outhome')
```

```{r local w2, echo=FALSE}
vari <- KLOSA_w2_iadl_outhome$w02C213
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_iadl_outhome, aes(x=factor(w02C213))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_iadl_outhome$id)
KLOSA_ds_w2$iadl_outhome <- car::recode(KLOSA_w2_iadl_outhome$w02C213, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w2$iadl_outhome <- labelled(KLOSA_ds_w2$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- KLOSA_ds_w2$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(KLOSA_ds_w2$iadl_outhome)
X<-table(KLOSA_w2_iadl_outhome$w02C213)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(KLOSA_ds_w2$iadl_outhome) <- ds_label
iadl_outhome <- KLOSA_ds_w2
save(iadl_outhome, file = "../RData/w2/iadl_outhome.RData")
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$iadl_outhome <- car::recode(KLOSA_m_ds_w2$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w03C213`
* Label: ` Going out that use transportation`
* Categories:
   + `1 = No, I don't need any help.`
   + `3 = yese extent.`
   + `5 = yesry respect.`
* Missings


```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_iadl_outhome','KLOSA.w03_main_e_spss_albert', variables=list('w03C213'), missings = TRUE)
KLOSA_w3_iadl_outhome <- opal.execute(o,'KLOSA_w3_iadl_outhome')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_iadl_outhome$id <- substr(KLOSA_w3_iadl_outhome$id,1,nchar(KLOSA_w3_iadl_outhome$id)-2)
```

```{r local w3, echo=FALSE}
Categorical_summary(KLOSA_w3_iadl_outhome$w03C213)
ggplot(KLOSA_w3_iadl_outhome, aes(x=factor(w03C213))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_iadl_outhome$id)
KLOSA_ds_w3$iadl_outhome <- car::recode(KLOSA_w3_iadl_outhome$w03C213, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w3$iadl_outhome <- labelled(KLOSA_ds_w3$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- KLOSA_ds_w3$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(KLOSA_ds_w3$iadl_outhome)
X<-table(KLOSA_w3_iadl_outhome$w03C213)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(KLOSA_ds_w3$iadl_outhome) <- ds_label
iadl_outhome <- KLOSA_ds_w3
save(iadl_outhome, file = "../RData/w3/iadl_outhome.RData")
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$iadl_outhome <- car::recode(KLOSA_m_ds_w3$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w04C213`
* Label: ` Going out that use transportation`
* Categories:
   + `1 = No, I don't need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_iadl_outhome','KLOSA.w04_main_e_spss', variables=list('w04C213'), missings = TRUE)
KLOSA_w4_iadl_outhome <- opal.execute(o,'KLOSA_w4_iadl_outhome')
```

```{r local w4, echo=FALSE}
vari <- KLOSA_w4_iadl_outhome$w04C213
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_iadl_outhome, aes(x=factor(w04C213))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_iadl_outhome$id)
KLOSA_ds_w4$iadl_outhome <- car::recode(KLOSA_w4_iadl_outhome$w04C213, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w4$iadl_outhome <- labelled(KLOSA_ds_w4$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- KLOSA_ds_w4$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(KLOSA_ds_w4$iadl_outhome)
X<-table(KLOSA_w4_iadl_outhome$w04C213)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(KLOSA_ds_w4$iadl_outhome) <- ds_label
iadl_outhome <- KLOSA_ds_w4
save(iadl_outhome, file = "../RData/w4/iadl_outhome.RData")
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$iadl_outhome <- car::recode(KLOSA_m_ds_w4$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
