---
title: "Limitations in ADLs - Shopping for groceries"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("../../setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_shopping`
* Variable label: `IADL - Difficulties for shopping groceries`
* Variable description: `IADL - Difficulties for shopping groceries`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for shopping groceries"
```


# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `w01Cb14`
* Label: `Marketing at shop`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings
   + `-8 = Refuse to answer`
   
```{r assign w1}
opal.assign.table.tibble(o, 'KLOSA_w1_iadl_shopping','KLOSA.w01_main_e', variables=list('w01Cb14'), missings = TRUE)
KLOSA_w1_iadl_shopping <- opal.execute(o,'KLOSA_w1_iadl_shopping')
```

```{r local w1}
vari <- KLOSA_w1_iadl_shopping$w01Cb14
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
ggplot(KLOSA_w1_iadl_shopping, aes(x=factor(w01Cb14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`
* `-8 into 997`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_iadl_shopping$id)
KLOSA_ds_w1$iadl_shopping <- car::recode(KLOSA_w1_iadl_shopping$w01Cb14, "1 = '1';3 = '0';5 = '0';-8 = '997' ")
KLOSA_ds_w1$iadl_shopping <- labelled(KLOSA_ds_w1$iadl_shopping, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_attempt_not_done=996, Does_not_answer=995,  Not_applicable=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1}
vari <- KLOSA_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1}
AfterH <- table(KLOSA_ds_w1$iadl_shopping)
X<-table(KLOSA_w1_iadl_shopping$w01Cb14)
BeforeH <- c(sum(X[c(3,4)]),X[c(2,1)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1","-8->997") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(KLOSA_ds_w1$iadl_shopping) <- ds_label
iadl_shopping <- KLOSA_ds_w1
save(iadl_shopping, file = "../RData/w1/iadl_shopping.RData")
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$iadl_shopping <- car::recode(KLOSA_m_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `w02C214`
* Label: `IADL(Necessity of aid for daily life)_shopping`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


```{r assign w2}
opal.assign.table.tibble(o, 'KLOSA_w2_iadl_shopping','KLOSA.w02_main_e_spss', variables=list('w02C214'), missings = TRUE)
KLOSA_w2_iadl_shopping <- opal.execute(o,'KLOSA_w2_iadl_shopping')
```

```{r local w2}
vari <- KLOSA_w2_iadl_shopping$w02C214
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_iadl_shopping, aes(x=factor(w02C214))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_iadl_shopping$id)
KLOSA_ds_w2$iadl_shopping <- car::recode(KLOSA_w2_iadl_shopping$w02C214, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w2$iadl_shopping <- labelled(KLOSA_ds_w2$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2}
vari <- KLOSA_ds_w2$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2}
AfterH <- table(KLOSA_ds_w2$iadl_shopping)
X<-table(KLOSA_w2_iadl_shopping$w02C214)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(KLOSA_ds_w2$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- KLOSA_ds_w2
save(iadl_shopping, file = "../RData/w2/iadl_shopping.RData")
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$iadl_shopping <- car::recode(KLOSA_m_ds_w2$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w03C214`
* Label: `Marketing at shop`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


```{r assign w3}
opal.assign.table.tibble(o, 'KLOSA_w3_iadl_shopping','KLOSA.w03_main_e_spss_albert', variables=list('w03C214'), missings = TRUE)
KLOSA_w3_iadl_shopping <- opal.execute(o,'KLOSA_w3_iadl_shopping')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_iadl_shopping$id <- substr(KLOSA_w3_iadl_shopping$id,1,nchar(KLOSA_w3_iadl_shopping$id)-2)
```

```{r local w3}
vari <- KLOSA_w3_iadl_shopping$w03C214
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_iadl_shopping, aes(x=factor(w03C214))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_iadl_shopping$id)
KLOSA_ds_w3$iadl_shopping <- car::recode(KLOSA_w3_iadl_shopping$w03C214, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w3$iadl_shopping <- labelled(KLOSA_ds_w3$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3}
vari <- KLOSA_ds_w3$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3}
AfterH <- table(KLOSA_ds_w3$iadl_shopping)
X<-table(KLOSA_w3_iadl_shopping$w03C214)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(KLOSA_ds_w3$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- KLOSA_ds_w3
save(iadl_shopping, file = "../RData/w1/iadl_shopping.RData")
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$iadl_shopping <- car::recode(KLOSA_m_ds_w3$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w04C214`
* Label: `Marketing at shop`
* Categories:
   + `1 = No, I Do not need any help.`
   + `3 = Yes, I need help to some extent.`
   + `5 = Yes, I need help in every respect.`
* Missings


```{r assign w4}
opal.assign.table.tibble(o, 'KLOSA_w4_iadl_shopping','KLOSA.w04_main_e_spss', variables=list('w04C214'), missings = TRUE)
KLOSA_w4_iadl_shopping <- opal.execute(o,'KLOSA_w4_iadl_shopping')
```

```{r local w4}
vari <- KLOSA_w4_iadl_shopping$w04C214
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_iadl_shopping, aes(x=factor(w04C214))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `3 into 0`
* `5 into 0`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_iadl_shopping$id)
KLOSA_ds_w4$iadl_shopping <- car::recode(KLOSA_w4_iadl_shopping$w04C214, "1 = '1';3 = '0';5 = '0' ")
KLOSA_ds_w4$iadl_shopping <- labelled(KLOSA_ds_w4$iadl_shopping, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_attempt_not_done=996, Does_not_answer=995,  Not_applicable=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4}
vari <- KLOSA_ds_w4$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4}
AfterH <- table(KLOSA_ds_w4$iadl_shopping)
X<-table(KLOSA_w4_iadl_shopping$w04C214)
BeforeH <- c(sum(X[c(2,3)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,5->0","1->1") 
kable(C)
```


```{r importOPAL w4, echo=FALSE}
label(KLOSA_ds_w4$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- KLOSA_ds_w4
save(iadl_shopping, file = "../RData/w1/iadl_shopping.RData")
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$iadl_shopping <- car::recode(KLOSA_m_ds_w4$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments





```{r closeRsession, echo=FALSE}
opal.logout(o)
```
