---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("../../setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## Korea

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `w01C001`
* Label: `Respondent's (principal) subjective health`
* Categories:
   + `1 = Very Good`
   + `2 = good`
   + `3 = fair`
   + `4 = poor`
   + `5 = Very poor`
* Missings


```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_srh','KLOSA.w01_main_e', variables=list('w01C001'), missings = TRUE)
KLOSA_w1_srh <- opal.execute(o,'KLOSA_w1_srh')
```

```{r local w1, echo=FALSE}
vari <- KLOSA_w1_srh$w01C001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_srh, aes(x=factor(w01C001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_srh$id)
KLOSA_ds_w1$srh <- car::recode(KLOSA_w1_srh$w01C001, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3'")
KLOSA_ds_w1$srh <- labelled(KLOSA_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- KLOSA_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(KLOSA_ds_w1$srh)
X<-table(KLOSA_w1_srh$w01C001)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","4->2","5->3")
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(KLOSA_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- KLOSA_ds_w1
save(srh, file = "../RData/w1/srh.RData")
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$srh <- car::recode(KLOSA_m_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w02C001`
* Label: `Respondent's (principal) subjective health`
* Categories:
   + `1 = Very Good`
   + `2 = good`
   + `3 = fair`
   + `4 = poor`
   + `5 = Very poor`
* Missings


```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_srh','KLOSA.w02_main_e_spss', variables=list('w02C001'), missings = TRUE)
KLOSA_w2_srh <- opal.execute(o,'KLOSA_w2_srh')
```

```{r local w2, echo=FALSE}
vari <- KLOSA_w2_srh$w02C001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_srh, aes(x=factor(w02C001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_srh$id)
KLOSA_ds_w2$srh <- car::recode(KLOSA_w2_srh$w02C001, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3'")
KLOSA_ds_w2$srh <- labelled(KLOSA_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- KLOSA_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(KLOSA_ds_w2$srh)
X<-table(KLOSA_w2_srh$w02C001)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","4->2","5->3")
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(KLOSA_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- KLOSA_ds_w2
save(srh, file = "../RData/w2/srh.RData")
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$srh <- car::recode(KLOSA_m_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w03C001`
* Label: `Respondent's (principal) subjective health`
* Categories:
   + `1 = Very Good`
   + `2 = good`
   + `3 = fair`
   + `4 = poor`
   + `5 = Very poor`
* Missings


```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_srh','KLOSA.w03_main_e_spss_albert', variables=list('w03C001'), missings = TRUE)
KLOSA_w3_srh <- opal.execute(o,'KLOSA_w3_srh')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_srh$id <- substr(KLOSA_w3_srh$id,1,nchar(KLOSA_w3_srh$id)-2)
```

```{r local w3, echo=FALSE}
vari <- KLOSA_w3_srh$w03C001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_srh, aes(x=factor(w03C001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_srh$id)
KLOSA_ds_w3$srh <- car::recode(KLOSA_w3_srh$w03C001, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3'")
KLOSA_ds_w3$srh <- labelled(KLOSA_ds_w3$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- KLOSA_ds_w3$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(KLOSA_ds_w3$srh)
X<-table(KLOSA_w3_srh$w03C001)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","4->2","5->3")
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(KLOSA_ds_w3$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- KLOSA_ds_w3
save(srh, file = "../RData/w3/srh.RData")
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$srh <- car::recode(KLOSA_m_ds_w3$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w04C001`
* Label: `Respondent's (principal) subjective health`
* Categories:
   + `1 = Very Good`
   + `2 = good`
   + `3 = fair`
   + `4 = poor`
   + `5 = Very poor`
* Missings


```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_srh','KLOSA.w04_main_e_spss', variables=list('w04C001'), missings = TRUE)
KLOSA_w4_srh <- opal.execute(o,'KLOSA_w4_srh')
```

```{r local w4, echo=FALSE}
vari <- KLOSA_w4_srh$w04C001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_srh, aes(x=factor(w04C001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_srh$id)
KLOSA_ds_w4$srh <- car::recode(KLOSA_w4_srh$w04C001, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3'")
KLOSA_ds_w4$srh <- labelled(KLOSA_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- KLOSA_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(KLOSA_ds_w4$srh)
X<-table(KLOSA_w4_srh$w04C001)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","4->2","5->3")
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(KLOSA_ds_w4$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- KLOSA_ds_w4
save(srh, file = "../RData/w4/srh.RData")
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$srh <- car::recode(KLOSA_m_ds_w4$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



# Quality estimation

All waves: Two questions on self-rated health with different scales were used, and respondents were asked to rate their health status twice, once at the beginning of the general health section and again at the end. Question order was assigned
randomly.

The PSSJD work-team has decided to take the first question which the person has answered based on the conclusions extracted in Bowling and Windsor - JECH 2008;62:81–85.

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
