---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## Korea

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w01C046`
* Label: `Hurt from a fall experience during the latest 2 years`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings

		
```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_recent_falls','KLOSA.w01_main_e', variables=list('w01C046'), missings = TRUE)
KLOSA_w1_recent_falls <- opal.execute(o,'KLOSA_w1_recent_falls')
```

```{r local w1, echo=FALSE}
vari <- KLOSA_w1_recent_falls$w01C046
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_recent_falls, aes(x=factor(w01C046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_recent_falls$id)
KLOSA_ds_w1$recent_falls <- car::recode(KLOSA_w1_recent_falls$w01C046, "1 = '0';5 = '1' ")
KLOSA_ds_w1$recent_falls <- labelled(KLOSA_ds_w1$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- KLOSA_ds_w1$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(KLOSA_ds_w1$recent_falls)
X<-table(KLOSA_w1_recent_falls$w01C046)
BeforeH <- c(X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","5->1") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(KLOSA_ds_w1$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- KLOSA_ds_w1
save(recent_falls, file = "../RData/w1/recent_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$recent_falls <- car::recode(KLOSA_m_ds_w1$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w02C056`
* Label: `Since previous interview, whether experienced a falling accident or not`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings

		
```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_recent_falls','KLOSA.w02_main_e_spss', variables=list('w02C056'), missings = TRUE)
KLOSA_w2_recent_falls <- opal.execute(o,'KLOSA_w2_recent_falls')
```

```{r local w2, echo=FALSE}
vari <- KLOSA_w2_recent_falls$w02C056
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_recent_falls, aes(x=factor(w02C056))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_recent_falls$id)
KLOSA_ds_w2$recent_falls <- car::recode(KLOSA_w2_recent_falls$w02C056, "1 = '0';5 = '1' ")
KLOSA_ds_w2$recent_falls <- labelled(KLOSA_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- KLOSA_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(KLOSA_ds_w2$recent_falls)
X<-table(KLOSA_w2_recent_falls$w02C056)
BeforeH <- c(X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","5->1") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(KLOSA_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- KLOSA_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$recent_falls <- car::recode(KLOSA_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w03C056`
* Label: `Hurt from a fall experience since previous interview`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
  
		
```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_recent_falls','KLOSA.w03_main_e_spss_albert', variables=list('w03C056'), missings = TRUE)
KLOSA_w3_recent_falls <- opal.execute(o,'KLOSA_w3_recent_falls')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_recent_falls$id <- substr(KLOSA_w3_recent_falls$id,1,nchar(KLOSA_w3_recent_falls$id)-2)
```

```{r local w3, echo=FALSE}
vari <- KLOSA_w3_recent_falls$w03C056
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_recent_falls, aes(x=factor(w03C056))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_recent_falls$id)
KLOSA_ds_w3$recent_falls <- car::recode(KLOSA_w3_recent_falls$w03C056, "1 = '0';5 = '1' ")
KLOSA_ds_w3$recent_falls <- labelled(KLOSA_ds_w3$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- KLOSA_ds_w3$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(KLOSA_ds_w3$recent_falls)
X<-table(KLOSA_w3_recent_falls$w03C056)
BeforeH <- c(X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","5->1") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(KLOSA_ds_w3$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- KLOSA_ds_w3
save(recent_falls, file = "../RData/w3/recent_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$recent_falls <- car::recode(KLOSA_m_ds_w3$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w04C056`
* Label: `Hurt from a fall experience since previous interview`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
  
		
```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_recent_falls','KLOSA.w04_main_e_spss', variables=list('w04C056'), missings = TRUE)
KLOSA_w4_recent_falls <- opal.execute(o,'KLOSA_w4_recent_falls')
```

```{r local w4, echo=FALSE}
vari <- KLOSA_w4_recent_falls$w04C056
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_recent_falls, aes(x=factor(w04C056))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_recent_falls$id)
KLOSA_ds_w4$recent_falls <- car::recode(KLOSA_w4_recent_falls$w04C056, "1 = '0';5 = '1' ")
KLOSA_ds_w4$recent_falls <- labelled(KLOSA_ds_w4$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- KLOSA_ds_w4$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(KLOSA_ds_w4$recent_falls)
X<-table(KLOSA_w4_recent_falls$w04C056)
BeforeH <- c(X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","5->1") 
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(KLOSA_ds_w4$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- KLOSA_ds_w4
save(recent_falls, file = "../RData/w4/recent_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$recent_falls <- car::recode(KLOSA_m_ds_w4$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


# Quality estimation
This variable, in all waves except for w2, relates to consequencies of falls and not the fall event itself. 
However there is not any variable that suits the potential variable proposed in the definition for this 
study in the database. The labels in the dataset and those in the questionnaire do not match (there are 
variables available that ask about whether the participant had fallen recently or not but these could not 
be found in the database).
Also it refers to the last 2 years and not the las 6-12 months as in the original variable definition.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
