---
title: "Consequences of falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `conseq_falls`
* Variable label: `Consequences of falls`
* Variable description: `Consequences of falls (injury, treatment,.)`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Consequences of falls"
ds_label_all <- "Consequences of falls (injury, treatment,.)"
```

# Data process

## Korea

### Wave 1 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `w01C048`
* Label: `whether Treatment is or not necessary serious hurt from a fall experience`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
		
```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_conseq_falls','KLOSA.w01_main_e', variables=list('w01C048'), missings = TRUE)
KLOSA_w1_conseq_falls <- opal.execute(o,'KLOSA_w1_conseq_falls')
```

```{r local w1, echo=FALSE}
vari <- KLOSA_w1_conseq_falls$w01C048
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_conseq_falls, aes(x=factor(w01C048))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_conseq_falls$id)
KLOSA_ds_w1$conseq_falls <- car::recode(KLOSA_w1_conseq_falls$w01C048, "1 = '1';5 = '0';NA = '999' ")
KLOSA_ds_w1$conseq_falls <- labelled(KLOSA_ds_w1$conseq_falls, labels = c("No"=0, "Yes"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- KLOSA_ds_w1$conseq_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(conseq_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(KLOSA_ds_w1$conseq_falls)
X<-table(KLOSA_w1_conseq_falls$w01C048)
BeforeH <- c(X[c(2,1)],sum(is.na(KLOSA_w1_conseq_falls$w01C048)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(KLOSA_ds_w1$conseq_falls) <- "Consequences of falls (injury, treatment,.)"
conseq_falls <- KLOSA_ds_w1
save(conseq_falls, file = "../RData/w1/conseq_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$conseq_falls <- car::recode(KLOSA_m_ds_w1$conseq_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w02C058`
* Label: `Severity level of falling accident_treatment`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
   
* Name: `w02C059`
* Label: `On a pelvis wealth bone fracture by injuries from a falling accident`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
   
* Name: `w02C060`
* Label: `Whether have daily activity difficulty by a falling accident or not`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`

* Name: `w02C056`
* Label: `Since previous interveiw, whether experienced a falling accident or not`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
		
```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_conseq_falls','KLOSA.w02_main_e_spss', variables=list('w02C058', 'w02C059', 'w02C060', 'w02C056'), missings = TRUE)
KLOSA_w2_conseq_falls <- opal.execute(o,'KLOSA_w2_conseq_falls')
```

```{r local w2, echo=FALSE}
vari <- KLOSA_w2_conseq_falls$w02C058
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_conseq_falls, aes(x=factor(w02C058))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")

vari <- KLOSA_w2_conseq_falls$w02C059
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_conseq_falls, aes(x=factor(w02C059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")

vari <- KLOSA_w2_conseq_falls$w02C060
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_conseq_falls, aes(x=factor(w02C060))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")

vari <- KLOSA_w2_conseq_falls$w02C056
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_conseq_falls, aes(x=factor(w02C056))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* if `w02C056=1`
    + if `w02C058`, `w02C059` or `w02C060 = 1` into `1` 
    + otherwise into `0`
* if `w02C056=5` into `996`
* `NA into 999`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_conseq_falls$id)
KLOSA_ds_w2$conseq_falls <- NA
KLOSA_ds_w2$conseq_falls[which(KLOSA_w2_conseq_falls$w02C056==5)] <- 996
KLOSA_ds_w2$conseq_falls[which(KLOSA_w2_conseq_falls$w02C056==1 & (KLOSA_w2_conseq_falls$w02C058==1 | KLOSA_w2_conseq_falls$w02C059==1 | KLOSA_w2_conseq_falls$w02C060==1))] <- 1
KLOSA_ds_w2$conseq_falls[which(KLOSA_w2_conseq_falls$w02C056==1 & (KLOSA_w2_conseq_falls$w02C058==5 & KLOSA_w2_conseq_falls$w02C059==5 & KLOSA_w2_conseq_falls$w02C060==5))] <- 0
KLOSA_ds_w2$conseq_falls <- labelled(KLOSA_ds_w2$conseq_falls, labels = c("No"=0, "Yes"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- KLOSA_ds_w2$conseq_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(conseq_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
BeforeH <- c(sum(KLOSA_w2_conseq_falls$w02C056==1 & (KLOSA_w2_conseq_falls$w02C058==5 & KLOSA_w2_conseq_falls$w02C059==5 & KLOSA_w2_conseq_falls$w02C060==5)), sum(KLOSA_w2_conseq_falls$w02C056==1 & (KLOSA_w2_conseq_falls$w02C058==1 | KLOSA_w2_conseq_falls$w02C059==1 | KLOSA_w2_conseq_falls$w02C060==1)), sum(KLOSA_w2_conseq_falls$w02C056==5))
AfterH <- table(KLOSA_ds_w2$conseq_falls)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(KLOSA_ds_w2$conseq_falls) <- "Consequences of falls (injury, treatment,.)"
conseq_falls <- KLOSA_ds_w2
save(conseq_falls, file = "../RData/w2/conseq_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$conseq_falls <- car::recode(KLOSA_m_ds_w2$conseq_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w03C058`
* Label: `whether Treatment is or not necessary serious hurt from a fall experience`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
		
```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_conseq_falls','KLOSA.w03_main_e_spss_albert', variables=list('w03C058'), missings = TRUE)
KLOSA_w3_conseq_falls <- opal.execute(o,'KLOSA_w3_conseq_falls')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_conseq_falls$id <- substr(KLOSA_w3_conseq_falls$id,1,nchar(KLOSA_w3_conseq_falls$id)-2)
```

```{r local w3, echo=FALSE}
vari <- KLOSA_w3_conseq_falls$w03C058
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_conseq_falls, aes(x=factor(w03C058))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_conseq_falls$id)
KLOSA_ds_w3$conseq_falls <- car::recode(KLOSA_w3_conseq_falls$w03C058, "1 = '1';5 = '0';NA = '999'")
KLOSA_ds_w3$conseq_falls <- labelled(KLOSA_ds_w3$conseq_falls, labels = c("No"=0, "Yes"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- KLOSA_ds_w3$conseq_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(conseq_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(KLOSA_ds_w3$conseq_falls)
X<-table(KLOSA_w3_conseq_falls$w03C058)
BeforeH <- c(X[c(2,1)],sum(is.na(KLOSA_w3_conseq_falls$w03C058)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(KLOSA_ds_w3$conseq_falls) <- "Consequences of falls (injury, treatment,.)"
conseq_falls <- KLOSA_ds_w3
save(conseq_falls, file = "../RData/w3/conseq_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$conseq_falls <- car::recode(KLOSA_m_ds_w3$conseq_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


 
### Wave 4 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `w04C058`
* Label: `whether Treatment is or not necessary serious hurt from a fall experience`
* Categories:
   + `1 = yes`
   + `5 = no`
* Missings
   + `NA`
		
```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_conseq_falls','KLOSA.w04_main_e_spss', variables=list('w04C058'), missings = TRUE)
KLOSA_w4_conseq_falls <- opal.execute(o,'KLOSA_w4_conseq_falls')
```

```{r local w4, echo=FALSE}
vari <- KLOSA_w4_conseq_falls$w04C058
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_conseq_falls, aes(x=factor(w04C058))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_conseq_falls$id)
KLOSA_ds_w4$conseq_falls <- car::recode(KLOSA_w4_conseq_falls$w04C058, "1 = '1';5 = '0';NA = '999'")
KLOSA_ds_w4$conseq_falls <- labelled(KLOSA_ds_w4$conseq_falls, labels = c("No"=0, "Yes"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- KLOSA_ds_w4$conseq_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(conseq_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(KLOSA_ds_w4$conseq_falls)
X<-table(KLOSA_w4_conseq_falls$w04C058)
BeforeH <- c(X[c(2,1)],sum(is.na(KLOSA_w4_conseq_falls$w04C058)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","5->0","NA->999") 
kable(C)
```


```{r importOPAL w4, echo=FALSE}
label(KLOSA_ds_w4$conseq_falls) <- "Consequences of falls (injury, treatment,.)"
conseq_falls <- KLOSA_ds_w4
save(conseq_falls, file = "../RData/w4/conseq_falls.RData")
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$conseq_falls <- car::recode(KLOSA_m_ds_w4$conseq_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


# Quality estimation
Refers to the last 2 years and not the last 6-12 months as in the original variable definition.
There is a new proposal regarding wave 2 in which w02C058 or w02C059 or w02C060, or  w02C062 = 1 
coud be taken as consequences of recent falls (while a value of 5 in all of these variables would 
mean the falls had no consequences) instead of taking variable w02C056 which, as it figures in the database 
(opal) has "Since previous interview, whether experienced a falling accident or not" as label
ande, therefore, does not match the definition of the original variable.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
