---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Korea

### Wave 1

Not found.

### Wave 2

##### Study-specific variable description



| **Name** | `w02C145`|
|-|-|
| **Label** | `Felt tired out or low in energy` |
| **Table name** | `w02_main_e_spss` |
| **Categories** | `1 = Very rarely (less than one day); 2 = Sometimes (1-2 days); 3 = Often (3-4 days); 4 = Almost always (5-7 days)` |
| **Missings** | `-9 = Don't know; NA` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_energy','KLOSA.w02_main_e_spss', variables=list('w02C145'), missings = TRUE)
```

```{r local w2, echo=F}
KLOSA_w2_energy <- opal.execute(o,'KLOSA_w2_energy')
vari <- KLOSA_w2_energy$w02C145
kable(Categorical_summary(vari, missing_values = c(-9))[3], caption = "w02C145")
kable(Categorical_summary(vari, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w2_energy, aes(x=factor(w02C145))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2,3,4 into 1`
  * `-9 Don't know into 998`
  * `NA into 999`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_energy$id)
KLOSA_ds_w2$energy <- car::recode(KLOSA_w2_energy$w02C145, "1 = '1';2 = '0';3 = '0';4 = '0';-9 = '998'; NA = '999' ")
KLOSA_ds_w2$energy <- labelled(KLOSA_ds_w2$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- KLOSA_ds_w2$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(KLOSA_ds_w2$energy)
X<-table(KLOSA_w2_energy$w02C145)
BeforeH <- c(sum(X[3:5]),X[c(2:1)],sum(is.na(KLOSA_w2_energy$w02C145)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","-9->998","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}

label(KLOSA_ds_w2$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
energy <- KLOSA_ds_w2
save(energy, file = "../RData/w2/energy.RData")

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$energy <- car::recode(KLOSA_m_ds_w2$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

Not found.

### Wave 4

Not found.



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
