---
title: "Ever smoked"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ever_smokedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ever_smokedDS.R')
```


# Data process


## Greece

### Wave 1 

#### Study-specific variable description

| **Name** | `smoking` |
|-|-|
| **Label** | `Smoking habits ever` |
| **Table name** | `ATTICA_Baseline` |
| **Categories:**| `0 = No` <br/> `1 = Yes` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1','ATTICA.ATTICA_Baseline', variables=list('smoking'), missings = TRUE)
ATTICA_w1 <- opal.execute(o,'ATTICA_w1')
```

```{r local w1, echo=F}
vbl <- ATTICA_w1$smoking
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ATTICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ATTICA_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:


* `NA into 999`

**R script:**

```{r harmo w1}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1$id)
ATTICA_ds_w1$ever_smoked <- car::recode(ATTICA_w1$smoking, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ATTICA_ds_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=F}
ever_smoked <- ATTICA_ds_w1 
save(ever_smoked, file = paste0(datafolder,"w1/ever_smoked.RData"))
rm(ever_smoked)
```




### Wave 2

Not found


### Wave 3

Not found



# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
