---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/yintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/yintwDS.R')
```

<!-- ########################################################## --> 

# Data process


## South Africa

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `Date (YYYY)`|
| **Table name** |`SAGE_SouthAfrica_di_la`|
| **Units** |`year`|
| **Description** |  |


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1_id','SAGE.southAfricaINDdata', variables=list('q0002'), missings = TRUE)
SAGE_SA_w1_id <- opal.execute(o,'SAGE_SA_w1_id')

opal.assign.table.tibble(o, 'SAGE_SA_w1_yinter','SAGE.SAGE_SouthAfrica_di_la', variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_SA_w1_yinter <- opal.execute(o,'SAGE_SA_w1_yinter')

```

```{r local1, echo=F}

#The table SAGE_SA_w1_yinter has hhid and SAGE_SA_w1_id has a individual id
#this function compute a table with the individuals id and year of interview
#of each individual

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_SA_w1 <- Add_indiv(old = SAGE_SA_w1_yinter, new = SAGE_SA_w1_id)

vbl <- SAGE_SA_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 


**R script:**

```{r harmo1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$yintw <- car::recode(SAGE_SA_w1$q0006_yyyy, "NA=2007")
SAGE_ds_SA_w1$yintw <- labelled(SAGE_ds_SA_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- SAGE_ds_SA_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(SAGE_SA_w1$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_ds_SA_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
kable(C)
```




## Ghana

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `date (yyyy)`|
| **Table name** |`SAGE_Ghana_HHData_di_la`|
| **Units** |`year`|
| **Description** |  |


```{r assign_ghana, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1_id','SAGE.ghanaINDData', variables=list('q0002'), missings = TRUE)
SAGE_ghana_w1_id <- opal.execute(o,'SAGE_ghana_w1_id')

opal.assign.table.tibble(o, 'SAGE_ghana_w1_yinter','SAGE.SAGE_Ghana_HHData_di_la',variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_ghana_w1_yinter <- opal.execute(o,'SAGE_ghana_w1_yinter')

```

```{r local_ghana, echo=F}

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i], NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_ghana_w1 <- Add_indiv(old = SAGE_ghana_w1_yinter, new = SAGE_ghana_w1_id)
vbl <- SAGE_ghana_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

**R script:**

```{r harmo_ghana}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$yintw <- car::recode(SAGE_ghana_w1$q0006_yyyy, "NA=2007")
SAGE_ds_ghana_w1$yintw <- labelled(SAGE_ds_ghana_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vbl <- SAGE_ds_ghana_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana, echo=F}
BeforeH <- table(SAGE_ghana_w1$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_ds_ghana_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
kable(C)
```







## China

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `Date (YYYY)`|
| **Table name** |`SAGE_China_HH_di_la`|
| **Units** |`year`|
| **Description** |  |


```{r assign_china, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1_id','SAGE.chinaINDData',variables=list('q0002'), missings = TRUE)
SAGE_china_w1_id <- opal.execute(o,'SAGE_china_w1_id')

opal.assign.table.tibble(o, 'SAGE_china_w1_yinter','SAGE.SAGE_China_HH_di_la',variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_china_w1_yinter <- opal.execute(o,'SAGE_china_w1_yinter')

```

```{r local_china, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i], NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_china_w1 <- Add_indiv(old = SAGE_china_w1_yinter, new = SAGE_china_w1_id)
vbl <- SAGE_china_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

**R script:**

```{r harmo_china}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$yintw <- car::recode(SAGE_china_w1$q0006_yyyy, "NA=2007")
SAGE_ds_china_w1$yintw <- labelled(SAGE_ds_china_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vbl <- SAGE_ds_china_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china, echo=F}
BeforeH <- table(SAGE_china_w1$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,4)]), BeforeH[2:3])
AfterH <- table(SAGE_ds_china_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008", "2009")
kable(C)
```





## India

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `Date (YYYY)`|
| **Table name** |`SAGE_India_HHData_di_la`|
| **Units** |`year`|
| **Description** |  |

```{r assign_india, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1_id','SAGE.indiaINDData', variables=list('q0002'), missings = TRUE)
SAGE_india_w1_id <- opal.execute(o,'SAGE_india_w1_id')

opal.assign.table.tibble(o, 'SAGE_india_w1_yinter','SAGE.SAGE_India_HHData_di_la',variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_india_w1_yinter <- opal.execute(o,'SAGE_india_w1_yinter')

```

```{r local_india, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i], NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_india_w1 <- Add_indiv(old = SAGE_india_w1_yinter, new = SAGE_india_w1_id)
vbl <- SAGE_india_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007. 

**R script:**

```{r harmo_india}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$yintw <- car::recode(SAGE_india_w1$q0006_yyyy, "NA=2007")
SAGE_ds_india_w1$yintw <- labelled(SAGE_ds_india_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vbl <- SAGE_ds_india_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india, echo=F}
BeforeH <- sum(table(SAGE_india_w1$q0006_yyyy, useNA = "ifany"))
AfterH <- table(SAGE_ds_india_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007")
kable(C)
```







## Russia

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `Date (YYYY)`|
| **Table name** |`SAGE_Russia_HH_di_la`|
| **Units** |`year`|
| **Description** |  |

```{r assign_russia, echo=F}

opal.assign.table.tibble(o, 'SAGE_russia_w1_id','SAGE.russiaINDdata', variables=list('q0002'), missings = TRUE)
SAGE_russia_w1_id <- opal.execute(o,'SAGE_russia_w1_id')

opal.assign.table.tibble(o, 'SAGE_russia_w1_yinter','SAGE.SAGE_Russia_HH_di_la', variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_russia_w1_yinter <- opal.execute(o,'SAGE_russia_w1_yinter')

```

```{r local_russia, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i], NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_russia_w1 <- Add_indiv(old = SAGE_russia_w1_yinter, new = SAGE_russia_w1_id)
vbl <- SAGE_russia_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

**R script:**

```{r harmo_russia}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$yintw <- car::recode(SAGE_russia_w1$q0006_yyyy, "NA=2007")
SAGE_ds_russia_w1$yintw <- labelled(SAGE_ds_russia_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vbl <- SAGE_ds_russia_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia, echo=F}
BeforeH <- table(SAGE_russia_w1$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_ds_russia_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
kable(C)
```







## Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_yyyy`|
|-|-|
| **Label** | `Date (YYYY)`|
| **Table name** |`SAGE_Mexico_HHData_di_la`|
| **Units** |`year`|
| **Description** |  |

```{r assign_Mexico, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1_id','SAGE.mexicoINDdata', variables=list('q0002'), missings = TRUE)
SAGE_mexico_w1_id <- opal.execute(o,'SAGE_mexico_w1_id')

opal.assign.table.tibble(o, 'SAGE_mexico_w1_yinter','SAGE.SAGE_Mexico_HHData_di_la', variables=list('q0002','q0006_yyyy'), missings = TRUE)
SAGE_mexico_w1_yinter <- opal.execute(o,'SAGE_mexico_w1_yinter')

```

```{r local_Mexico, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i], NA,new$q0002[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_mexico_w1 <- Add_indiv(old = SAGE_mexico_w1_yinter, new = SAGE_mexico_w1_id)
vbl <- SAGE_mexico_w1$q0006_yyyy
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "q0006_yyyy")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2009 since is the most frecuent value. 

**R script:**

```{r harmo_Mexico}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$yintw <- car::recode(SAGE_mexico_w1$q0006_yyyy, "NA=2009")
SAGE_ds_mexico_w1$yintw <- labelled(SAGE_ds_mexico_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vbl <- SAGE_ds_mexico_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
BeforeH <- table(SAGE_mexico_w1$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_ds_mexico_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2009,NA)->2009", "2010")
kable(C)
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
The harmonized variable is the same of the study-specific variable but taking into account the time lapse in each wave.
Missing values were recoded as 2007 since it was the most frecuent value. 




```{r closeRsession, echo=FALSE}
opal.logout(o)
```

