---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `yintw`
* Variable label: `year of interview`
* Domain: `Other administrative variables`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


### SAGE - South Africa - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `Date (YYYY)`
* Type of variable: `countinous`


```{r assign1}
opal.assign.table.tibble(o, 'SAGE_SA_w1_id','SAGE.southAfricaINDdata',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_SA_w1_yinter','SAGE.SAGE_SouthAfrica_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)
```

```{r local1}
SAGE_SA_w1_id <- opal.execute(o,'SAGE_SA_w1_id')
SAGE_SA_w1_yinter <- opal.execute(o,'SAGE_SA_w1_yinter')

#The table SAGE_SA_w1_yinter has hhid and SAGE_SA_w1_id has a individual id
#this function compute a table with the individuals id and year of interview
#of each individual

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_SA_w1_yinter2 <- Add_indiv(old = SAGE_SA_w1_yinter, new = SAGE_SA_w1_id)
Categorical_summary(var = SAGE_SA_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_SA_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 


R code of the ALGORITHM:

```{r harmo1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_yinter2$id)
SAGE_SA_ds_w1$yintw <- car::recode(SAGE_SA_w1_yinter2$q0006_yyyy, "NA=2007")
SAGE_SA_ds_w1$yintw <- labelled(SAGE_SA_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Categorical_summary(var = SAGE_SA_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
BeforeH <- table(SAGE_SA_w1_yinter2$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_SA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
C
```


#### Import to OPAL
```{r importOPAL1}
val_labels(SAGE_SA_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_SA_m_ds_w1 <- SAGE_SA_ds_w1
SAGE_SA_m_ds_w1$yintw <- car::recode(SAGE_SA_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_SA_m_ds_w1', SAGE_SA_m_ds_w1)
#opal.symbol_import(o,'SAGE_SA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### SAGE - Ghana - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `date (yyyy)`
* Type of variable: `countinous`


```{r assign_ghana}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_id','SAGE.ghanaINDData',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_ghana_w1_yinter','SAGE.SAGE_Ghana_HHData_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)
```

```{r local_ghana}
SAGE_ghana_w1_id <- opal.execute(o,'SAGE_ghana_w1_id')
SAGE_ghana_w1_yinter <- opal.execute(o,'SAGE_ghana_w1_yinter')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_ghana_w1_yinter2 <- Add_indiv(old = SAGE_ghana_w1_yinter, new = SAGE_ghana_w1_id)
Categorical_summary(var = SAGE_ghana_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_ghana_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

R code of the ALGORITHM:

```{r harmo_ghana}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_yinter2$id)
SAGE_ghana_ds_w1$yintw <- car::recode(SAGE_ghana_w1_yinter2$q0006_yyyy, "NA=2007")
SAGE_ghana_ds_w1$yintw <- labelled(SAGE_ghana_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana}
Categorical_summary(var = SAGE_ghana_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana}
BeforeH <- table(SAGE_ghana_w1_yinter2$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_ghana_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
C
```

#### Import to OPAL
```{r importOPAL_ghana}
val_labels(SAGE_ghana_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_ghana_m_ds_w1 <- SAGE_ghana_ds_w1
SAGE_ghana_m_ds_w1$yintw <- car::recode(SAGE_ghana_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### SAGE - China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `Date (YYYY)`
* Type of variable: `countinous`


```{r assign_china}
opal.assign.table.tibble(o, 'SAGE_china_w1_id','SAGE.chinaINDData',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_china_w1_yinter','SAGE.SAGE_China_HH_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)

```

```{r local_china}
SAGE_china_w1_id <- opal.execute(o,'SAGE_china_w1_id')
SAGE_china_w1_yinter <- opal.execute(o,'SAGE_china_w1_yinter')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_china_w1_yinter2 <- Add_indiv(old = SAGE_china_w1_yinter, new = SAGE_china_w1_id)
Categorical_summary(var = SAGE_china_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_china_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

R code of the ALGORITHM:

```{r harmo_china}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_yinter2$id)
SAGE_china_ds_w1$yintw <- car::recode(SAGE_china_w1_yinter2$q0006_yyyy, "NA=2007")
SAGE_china_ds_w1$yintw <- labelled(SAGE_china_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china}
Categorical_summary(var = SAGE_china_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china}
BeforeH <- table(SAGE_china_w1_yinter2$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,4)]), BeforeH[2:3])
AfterH <- table(SAGE_china_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008", "2009")
C
```


#### Import to OPAL
```{r importOPAL_china}
val_labels(SAGE_china_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_china_m_ds_w1 <- SAGE_china_ds_w1
SAGE_china_m_ds_w1$yintw <- car::recode(SAGE_china_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```








### SAGE - India - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `Date (YYYY)`
* Type of variable: `countinous`

```{r assign_india}
opal.assign.table.tibble(o, 'SAGE_india_w1_id','SAGE.indiaINDData',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_india_w1_yinter','SAGE.SAGE_India_HHData_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)
```

```{r local_india}
SAGE_india_w1_id <- opal.execute(o,'SAGE_india_w1_id')
SAGE_india_w1_yinter <- opal.execute(o,'SAGE_india_w1_yinter')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_india_w1_yinter2 <- Add_indiv(old = SAGE_india_w1_yinter, new = SAGE_india_w1_id)
Categorical_summary(var = SAGE_india_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_india_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007. 

R code of the ALGORITHM:

```{r harmo_india}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_yinter2$id)
SAGE_india_ds_w1$yintw <- car::recode(SAGE_india_w1_yinter2$q0006_yyyy, "NA=2007")
SAGE_india_ds_w1$yintw <- labelled(SAGE_india_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india}
Categorical_summary(var = SAGE_india_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india}
BeforeH <- sum(table(SAGE_india_w1_yinter2$q0006_yyyy, useNA = "ifany"))
AfterH <- table(SAGE_india_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007")
C
```


#### Import to OPAL
```{r importOPAL_india}
val_labels(SAGE_india_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_india_m_ds_w1 <- SAGE_india_ds_w1
SAGE_india_m_ds_w1$yintw <- car::recode(SAGE_india_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### SAGE - Russia - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `Date (YYYY)`
* Type of variable: `countinous`

```{r assign_russia}
opal.assign.table.tibble(o, 'SAGE_russia_w1_id','SAGE.russiaINDdata',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_russia_w1_yinter','SAGE.SAGE_Russia_HH_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)
```

```{r local_russia}
SAGE_russia_w1_id <- opal.execute(o,'SAGE_russia_w1_id')
SAGE_russia_w1_yinter <- opal.execute(o,'SAGE_russia_w1_yinter')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_russia_w1_yinter2 <- Add_indiv(old = SAGE_russia_w1_yinter, new = SAGE_russia_w1_id)
Categorical_summary(var = SAGE_russia_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_russia_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2007 since is the most frecuent value. 

R code of the ALGORITHM:

```{r harmo_russia}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_yinter2$id)
SAGE_russia_ds_w1$yintw <- car::recode(SAGE_russia_w1_yinter2$q0006_yyyy, "NA=2007")
SAGE_russia_ds_w1$yintw <- labelled(SAGE_russia_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia}
Categorical_summary(var = SAGE_russia_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia}
BeforeH <- table(SAGE_russia_w1_yinter2$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_russia_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2007,NA)->2007", "2008")
C
```

#### Import to OPAL
```{r importOPAL_russia}
val_labels(SAGE_russia_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_russia_m_ds_w1 <- SAGE_russia_ds_w1
SAGE_russia_m_ds_w1$yintw <- car::recode(SAGE_russia_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```








### SAGE - Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_yyyy`
* Label: `Date (YYYY)`
* Type of variable: `countinous`

```{r assign_Mexico}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_id','SAGE.mexicoINDdata',
                         variables=list('q0002'), missings = TRUE)
opal.assign.table.tibble(o, 'SAGE_mexico_w1_yinter','SAGE.SAGE_Mexico_HHData_di_la',
                         variables=list('q0002','q0006_yyyy'), missings = TRUE)

```

```{r local_Mexico}
SAGE_mexico_w1_id <- opal.execute(o,'SAGE_mexico_w1_id')
SAGE_mexico_w1_yinter <- opal.execute(o,'SAGE_mexico_w1_yinter')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=4)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$q0002)){
    if(sum(new$q0002[i]==old$q0002)>=1){
      new_2[i,] <- c(new$id[i],oldm[which(new$q0002[i]==old$q0002),])
    } else {
      new_2[i,] <- c(new$id[i],new$q0002[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], hhid=as.numeric(new_2[,2]), 
                       q0002=as.numeric(new_2[,3]), q0006_yyyy=as.numeric(new_2[,4]))
  new_22
}

SAGE_mexico_w1_yinter2 <- Add_indiv(old = SAGE_mexico_w1_yinter, new = SAGE_mexico_w1_id)
Categorical_summary(var = SAGE_mexico_w1_yinter2$q0006_yyyy, missing_values = NA)
ggplot(SAGE_mexico_w1_yinter2, aes(x=factor(q0006_yyyy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as 2009 since is the most frecuent value. 

R code of the ALGORITHM:

```{r harmo_Mexico}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_yinter2$id)
SAGE_mexico_ds_w1$yintw <- car::recode(SAGE_mexico_w1_yinter2$q0006_yyyy, "NA=2009")
SAGE_mexico_ds_w1$yintw <- labelled(SAGE_mexico_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico}
Categorical_summary(var = SAGE_mexico_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico}
BeforeH <- table(SAGE_mexico_w1_yinter2$q0006_yyyy, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), BeforeH[2])
AfterH <- table(SAGE_mexico_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(2009,NA)->2009", "2010")
C
```

#### Quality estimation
The harmonized variable is the same of the study-specific variable but taking into account the time lapse in each wave.
Missing values were recoded as 2007 since it was the most frecuent value. 


#### Import to OPAL
```{r importOPAL_Mexico}
val_labels(SAGE_mexico_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_mexico_m_ds_w1 <- SAGE_mexico_ds_w1
SAGE_mexico_m_ds_w1$yintw <- car::recode(SAGE_mexico_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
yintw <- SAGE_SA_ds_w1
save(yintw, file = paste0(datafolder, "/SA_w1/yintw.RData"))
```

```{r,  echo=FALSE}
yintw <- SAGE_ghana_ds_w1
save(yintw, file = paste0(datafolder, "/ghana_w1/yintw.RData"))
```

```{r,  echo=FALSE}
yintw <- SAGE_china_ds_w1
save(yintw, file = paste0(datafolder, "/china_w1/yintw.RData"))
```

```{r,  echo=FALSE}
yintw <- SAGE_india_ds_w1
save(yintw, file = paste0(datafolder, "/india_w1/yintw.RData"))
```

```{r,  echo=FALSE}
yintw <- SAGE_russia_ds_w1
save(yintw, file = paste0(datafolder, "/russia_w1/yintw.RData"))
```

```{r,  echo=FALSE}
yintw <- SAGE_mexico_ds_w1
save(yintw, file = paste0(datafolder, "/mexico_w1/yintw.RData"))
```




```{r closeRsession, echo=FALSE}
opal.logout(o)
```

