---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```



# Data process




## South Africa


### Wave 1


#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `southAfricaINDdata`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |

```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('pweight'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_SA_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm


**R script:**

```{r harmo SA_w1}

SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
n <- length(SAGE_SA_w1$id[which(!is.na(SAGE_SA_w1$pweight))])
N <- sum(SAGE_SA_w1$pweight,na.rm = T)
SAGE_ds_SA_w1$w <- car::recode(SAGE_SA_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_SA_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}

```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `ghanaINDData`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('pweight'), missings = T)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')

```

```{r local ghana_w1, echo=F}

vbl <- SAGE_ghana_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_ghana_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo ghana_w1}

SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
n <- length(SAGE_ghana_w1$id[which(!is.na(SAGE_ghana_w1$pweight))])
N <- sum(SAGE_ghana_w1$pweight,na.rm = T)
SAGE_ds_ghana_w1$w <- car::recode(SAGE_ghana_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_ghana_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}

```





## China


### Wave 1



#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `chinaINDData`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('pweight'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_china_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo china_w1}

SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
n <- length(SAGE_china_w1$id[which(!is.na(SAGE_china_w1$pweight))])
N <- sum(SAGE_china_w1$pweight,na.rm = T)
SAGE_ds_china_w1$w <- car::recode(SAGE_china_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_china_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}

```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `indiaINDData`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('pweight'), missings = T)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')

```

```{r local india_w1, echo=F}

vbl <- SAGE_india_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_india_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo india_w1}

SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
n <- length(SAGE_india_w1$id[which(!is.na(SAGE_india_w1$pweight))])
N <- sum(SAGE_india_w1$pweight,na.rm = T)
SAGE_ds_india_w1$w <- car::recode(SAGE_india_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_india_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

```





## Russian Federation

### Wave 1

#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `russiaINDdata`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |

```{r assign russia_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',variables=list('pweight'), missings = T)
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')

```

```{r local russia_w1, echo=F}

vbl <- SAGE_russia_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_russia_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo russia_w1}

SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
n <- length(SAGE_russia_w1$id[which(!is.na(SAGE_russia_w1$pweight))])
N <- sum(SAGE_russia_w1$pweight,na.rm = T)
SAGE_ds_russia_w1$w <- car::recode(SAGE_russia_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript russia_w1, echo=F}

vbl <- SAGE_ds_russia_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_russia_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation russia_w1, echo=F}

```



## Mexico


### Wave 1

#### Study-specific variable description

| **Name** | `pweight`|
|-|-|
| **Label** | `post-stratified person weight`|
| **Table name**  | `mexicoINDdata`|
| **Categories** | `continuous`|
| **Missings** | `NA` | 
| **Description** |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('pweight'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$pweight
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'pweight')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_mexico_w1,!vbl %in% vbl_miss), aes(pweight)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo mexico_w1}

SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
n <- length(SAGE_mexico_w1$id[which(!is.na(SAGE_mexico_w1$pweight))])
N <- sum(SAGE_mexico_w1$pweight,na.rm = T)
SAGE_ds_mexico_w1$w <- car::recode(SAGE_mexico_w1$pweight*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_mexico_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}

```






# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(index in seq_along(l.hds)){
  label(l.hds[[index]][[2]]) <- ds_label
  w <- l.hds[[index]]
  save(w, file = paste0(datafolder,names(l.hds)[index],"/w.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





