---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```

# Data process

## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `q1000b`|
|-|-|
| **Label** | `q1000b: contact with:`|
| **Table name** | `southAfricaINDdata` |
| **Categories** |`1 = respondent`|
| | `2 = proxy respondent` |
| | `3 = no one` |
| **Missings** | `8 = don't know` | 
| | `9 = not applicable` | 
| **Description** |  |


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.southAfricaINDdata',variables=list('q1000b'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')

```


```{r local1,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "respondent" into 0`
* `recode 2 "proxy respondent" into 1`
* `recode 3 "no one" into 999`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
SAGE_ds_SA_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_SA_w1$proxy <- car::recode(SAGE_proxy[[2]], "1=0; 2=1; 3=999; 8=998; 9=996; NA=999")
SAGE_ds_SA_w1$proxy <- labelled(SAGE_ds_SA_w1$proxy, labels = cat_label)
label(SAGE_ds_SA_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- SAGE_ds_SA_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL1,  echo=FALSE}
proxy <- SAGE_ds_SA_w1
save(proxy, file = "../RData/SA_w1/proxy.RData")
rm(proxy)
```





## Ghana

### Wave 1 

#### Study-specific variable description

| **Name** | `q1000b`|
|-|-|
| **Label** | `q1000b: contact with:`|
| **Table name** | `ghanaINDData` |
| **Categories** |`1 = respondent`|
| | `2 = proxy respondent` |
| | `3 = no one` |
| **Missings** | `8 = don't know` | 
| | `9 = not applicable` | 
| **Description** |  |


```{r assign_ghana,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.ghanaINDData',
                         variables=list('q1000b'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')
```

```{r local_ghana,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "respondent" into 0`
* `recode 2 "proxy respondent" into 1`
* `recode 3 "no one" into 999`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_ghana,   echo=TRUE}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_ghana_w1$proxy <- car::recode(SAGE_proxy[[2]], "1=0; 2=1; 3=999; 8=998; 9=996; NA=999")
SAGE_ds_ghana_w1$proxy <- labelled(SAGE_ds_ghana_w1$proxy, labels = cat_label)
label(SAGE_ds_ghana_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript_ghana,  echo=FALSE}
vari <- SAGE_ds_ghana_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_ghana,  echo=FALSE}
proxy <- SAGE_ds_ghana_w1
save(proxy, file = "../RData/ghana_w1/proxy.RData")
rm(proxy)
```



## China

### Wave 1 

#### Study-specific variable description

| **Name** | `q1000b`|
|-|-|
| **Label** | `q1000b: contact with:`|
| **Table name** | `chinaINDData` |
| **Categories** |`1 = respondent`|
| | `2 = proxy respondent` |
| | `3 = no one` |
| **Missings** | `8 = don't know` | 
| | `9 = not applicable` | 
| **Description** |  |

```{r assign_china,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.chinaINDData',variables=list('q1000b','q1005','q1004'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')
```

```{r local_china,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "respondent" into 0`
* `recode 2 "proxy respondent" into 1`
* `recode 3 "no one" into 999`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`


**R script:**

```{r harmo_china,   echo=TRUE}
SAGE_ds_china_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_china_w1$proxy <- car::recode(SAGE_proxy[[2]], "1=0; 2=1; 3=999; 8=998; 9=996; NA=999")
SAGE_ds_china_w1$proxy <- labelled(SAGE_ds_china_w1$proxy, labels = cat_label)
label(SAGE_ds_china_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript_china,  echo=FALSE}
vari <- SAGE_ds_china_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_china,  echo=FALSE}
proxy <- SAGE_ds_china_w1
save(proxy, file = "../RData/china_w1/proxy.RData")
rm(proxy)
```





## India

### Wave 1 

#### Study-specific variable description

| **Name** | `q1000b`|
|-|-|
| **Label** | `Q1000B: Contact with:`|
| **Table name** | `indiaINDData` |
| **Categories** |`1 = respondent`|
| | `2 = proxy respondent` |
| | `3 = no one` |
| **Missings** | `8 = don't know` | 
| | `9 = not applicable` | 
| **Description** |  |

```{r assign_india,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.indiaINDData',
                         variables=list('q1000b'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')
```

```{r local_india,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "respondent" into 0`
* `recode 2 "proxy respondent" into 1`
* `recode 3 "no one" into 999`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_india,   echo=TRUE}
SAGE_ds_india_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_india_w1$proxy <- car::recode(SAGE_proxy[[2]], "1=0; 2=1; 3=999; 8=998; 9=996; NA=999")
SAGE_ds_india_w1$proxy <- labelled(SAGE_ds_india_w1$proxy, labels = cat_label)
label(SAGE_ds_india_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript_india,  echo=FALSE}
vari <- SAGE_ds_india_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_india,  echo=FALSE}
proxy <- SAGE_ds_india_w1
save(proxy, file = "../RData/india_w1/proxy.RData")
rm(proxy)
```





## Russia

### Wave 1 

#### Study-specific variable description

| **Name** | `q1000b`|
|-|-|
| **Label** | `q1000b: contact with:`|
| **Table name** | `russiaINDdata` |
| **Categories** |`1 = respondent`|
| | `2 = proxy respondent` |
| | `3 = no one` |
| **Missings** | `8 = don't know` | 
| | `9 = not applicable` | 
| **Description** |  |

```{r assign_russia,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.russiaINDdata',
                         variables=list('q1000b'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')
```

```{r local_russia,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "respondent" into 0`
* `recode 2 "proxy respondent" into 1`
* `recode 3 "no one" into 999`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_russia,   echo=TRUE}
SAGE_ds_russia_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_russia_w1$proxy <- car::recode(SAGE_proxy[[2]], "1=0; 2=1; 3=999; 8=998; 9=996; NA=999")
SAGE_ds_russia_w1$proxy <- labelled(SAGE_ds_russia_w1$proxy, labels = cat_label)
label(SAGE_ds_russia_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript_russia,  echo=FALSE}
vari <- SAGE_ds_russia_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_russia,  echo=FALSE}
proxy <- SAGE_ds_russia_w1
save(proxy, file = "../RData/russia_w1/proxy.RData")
rm(proxy)
```




## Mexico

### Wave 1 

#### Study-specific variable description

 
| **Name** | `q1005`|
|-|-|
| **Label** | `q1005: proxy`|
| **Table name** | `mexicoINDdata` |
| **Categories** |`1 = spouse`|
| | `2 = non-spouse` |
| **Missings** | `NA` | 
| **Description** |  |

```{r assign_Mexico,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_proxy','SAGE.mexicoINDdata',variables=list('q1005'), missings = TRUE)
SAGE_proxy <- opal.execute(o,'SAGE_proxy')
```

```{r local_Mexico,  echo=FALSE}
vari <- SAGE_proxy[[2]]
kable(Categorical_summary(vari, missing_values = c(8, 9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8, 9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8, 9))[2], caption = "Type of missing")
ggplot(SAGE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1,2 into 1`
* `recode NA into 0`

**R script:**

```{r harmo_Mexico,   echo=TRUE}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_proxy$id)
SAGE_ds_mexico_w1$proxy <- car::recode(SAGE_proxy$q1005, "c(1,2)=1; NA=0")
SAGE_ds_mexico_w1$proxy <- labelled(SAGE_ds_mexico_w1$proxy, labels = cat_label)
label(SAGE_ds_mexico_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript_Mexico,  echo=FALSE}
vari <- SAGE_ds_mexico_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_Mexico,  echo=FALSE}
proxy <- SAGE_ds_mexico_w1
save(proxy, file = "../RData/mexico_w1/proxy.RData")
rm(proxy)
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}



```




# Quality estimation

* There are other variables with proxy respondent information, but most of `q1005` variables (the equivalent to the ones harmonised for COURAGE study) are only missing data (except for Mexico and China), and we think that `q1000b` fit better with the definition of the proxy variable than `q0003` and  `q1004`.
* As for Mexico, data in `q1000b` is all missing, we use `q1005`. For China we use `q1000b` for harmonisation in order to keep coherence with the other populations. 


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```

