---
title: "ADL - Getting dressed"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_dressing`
* Variable label: `ADL-Difficulties for getting dressed`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 

## Cuba
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign Cuba w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w1_adl_dressing','10-66.1066-Cuba-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local Cuba w1,  echo=FALSE}
s1066_Cuba_w1_adl_dressing <- opal.execute(o,'s1066_Cuba_w1_adl_dressing')
vari <- s1066_Cuba_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_Cuba_w1_adl_dressing$PDAS9)
ggplot(s1066_Cuba_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Cuba w1,   echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_adl_dressing$id)
t1066_ds_cuba_w1$adl_dressing <- car::recode(s1066_Cuba_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_cuba_w1$adl_dressing <- labelled(t1066_ds_cuba_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1,  echo=FALSE}
vari <- t1066_ds_cuba_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1,  echo=FALSE}
AfterH <- table(t1066_ds_cuba_w1$adl_dressing)
X<-table(s1066_Cuba_w1_adl_dressing$PDAS9)
nas<-length(s1066_Cuba_w1_adl_dressing$PDAS9)-length(na.omit(s1066_Cuba_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Cuba w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_cuba_w1) <- NULL
label(t1066_ds_cuba_w1$adl_dressing) <- "Difficulties for getting dressed"
##opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$adl_dressing <- car::recode(t1066_m_ds_cuba_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
##opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_cuba_w1
save(adl_dressing, file = paste0(datafolder, "/cuba_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign Cuba w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w2_adl_dressing','10-66.1066-Cuba-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local Cuba w2,  echo=FALSE}
s1066_Cuba_w2_adl_dressing <- opal.execute(o,'s1066_Cuba_w2_adl_dressing')
vari <- s1066_Cuba_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_Cuba_w2_adl_dressing$f_PDAS9)
ggplot(s1066_Cuba_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Cuba w2,   echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_adl_dressing$id)
t1066_ds_cuba_w2$adl_dressing <-  car::recode(s1066_Cuba_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_cuba_w2$adl_dressing <- labelled(t1066_ds_cuba_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2,  echo=FALSE}
vari <- t1066_ds_cuba_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2,  echo=FALSE}
AfterH <- table(t1066_ds_cuba_w2$adl_dressing)
X<-table(s1066_Cuba_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_Cuba_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_Cuba_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Cuba w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_cuba_w2) <- NULL
label(t1066_ds_cuba_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$adl_dressing <- car::recode(t1066_m_ds_cuba_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_cuba_w2
save(adl_dressing, file = paste0(datafolder, "/cuba_w2/adl_dressing.RData"))
```

## India
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign India w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_India_w1_adl_dressing','10-66.1066-India-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local India w1,  echo=FALSE}
s1066_India_w1_adl_dressing <- opal.execute(o,'s1066_India_w1_adl_dressing')
vari <- s1066_India_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_India_w1_adl_dressing$PDAS9)
ggplot(s1066_India_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo India w1,   echo=TRUE}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_adl_dressing$id)
t1066_ds_india_w1$adl_dressing <- car::recode(s1066_India_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_india_w1$adl_dressing <- labelled(t1066_ds_india_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1,  echo=FALSE}
vari <- t1066_ds_india_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1,  echo=FALSE}
AfterH <- table(t1066_ds_india_w1$adl_dressing)
X<-table(s1066_India_w1_adl_dressing$PDAS9)
nas<-length(s1066_India_w1_adl_dressing$PDAS9)-length(na.omit(s1066_India_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL India w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_india_w1) <- NULL
label(t1066_ds_india_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$adl_dressing <- car::recode(t1066_m_ds_india_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_india_w1
save(adl_dressing, file = paste0(datafolder, "/india_w1/adl_dressing.RData"))
```

### Wave 2 

Not found.

## Urban China
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign UrbanChina w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_adl_dressing','10-66.1066-UrbanChina-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local UrbanChina w1,  echo=FALSE}
s1066_UrbanChina_w1_adl_dressing <- opal.execute(o,'s1066_UrbanChina_w1_adl_dressing')
vari <- s1066_UrbanChina_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanChina_w1_adl_dressing$PDAS9)
ggplot(s1066_UrbanChina_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanChina w1,   echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_adl_dressing$id)
t1066_ds_UCh_w1$adl_dressing <- car::recode(s1066_UrbanChina_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UCh_w1$adl_dressing <- labelled(t1066_ds_UCh_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1,  echo=FALSE}
vari <- t1066_ds_UCh_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1,  echo=FALSE}
AfterH <- table(t1066_ds_UCh_w1$adl_dressing)
X<-table(s1066_UrbanChina_w1_adl_dressing$PDAS9)
nas<-length(s1066_UrbanChina_w1_adl_dressing$PDAS9)-length(na.omit(s1066_UrbanChina_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanChina w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UCh_w1) <- NULL
label(t1066_ds_UCh_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$adl_dressing <- car::recode(t1066_m_ds_UCh_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UCh_w1
save(adl_dressing, file = paste0(datafolder, "/Uch_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
  

* Description: 
```{r assign UrbanChina w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_adl_dressing','10-66.1066-UrbanChina-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local UrbanChina w2,  echo=FALSE}
s1066_UrbanChina_w2_adl_dressing <- opal.execute(o,'s1066_UrbanChina_w2_adl_dressing')
vari <- s1066_UrbanChina_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanChina_w2_adl_dressing$f_PDAS9)
ggplot(s1066_UrbanChina_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo UrbanChina w2,   echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_adl_dressing$id)
t1066_ds_UCh_w2$adl_dressing <-  car::recode(s1066_UrbanChina_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UCh_w2$adl_dressing <- labelled(t1066_ds_UCh_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2,  echo=FALSE}
vari <- t1066_ds_UCh_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2,  echo=FALSE}
AfterH <- table(t1066_ds_UCh_w2$adl_dressing)
X<-table(s1066_UrbanChina_w2_adl_dressing$f_PDAS9)
#nas<-length(s1066_UrbanChina_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_UrbanChina_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1,2,3,4->0")
kable(C)
```

 
 


 
```{r importOPAL UrbanChina w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UCh_w2) <- NULL
label(t1066_ds_UCh_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$adl_dressing <- car::recode(t1066_m_ds_UCh_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UCh_w2
save(adl_dressing, file = paste0(datafolder, "/UCh_w2/adl_dressing.RData"))
```

## Rural China
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings



* Description: 
```{r assign RuralChina w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_adl_dressing','10-66.1066-RuralChina-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local RuralChina w1,  echo=FALSE}
s1066_RuralChina_w1_adl_dressing <- opal.execute(o,'s1066_RuralChina_w1_adl_dressing')
vari <- s1066_RuralChina_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralChina_w1_adl_dressing$PDAS9)
ggplot(s1066_RuralChina_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralChina w1,   echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_adl_dressing$id)
t1066_ds_RCh_w1$adl_dressing <- car::recode(s1066_RuralChina_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RCh_w1$adl_dressing <- labelled(t1066_ds_RCh_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1,  echo=FALSE}
vari <- t1066_ds_RCh_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1,  echo=FALSE}
AfterH <- table(t1066_ds_RCh_w1$adl_dressing)
X<-table(s1066_RuralChina_w1_adl_dressing$PDAS9)
#nas<-length(s1066_RuralChina_w1_adl_dressing$PDAS9)-length(na.omit(s1066_RuralChina_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL RuralChina w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RCh_w1) <- NULL
label(t1066_ds_RCh_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$adl_dressing <- car::recode(t1066_m_ds_RCh_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RCh_w1
save(adl_dressing, file = paste0(datafolder, "/RCh_w1/adl_dressing.RData"))
```


### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings


* Description: 
```{r assign RuralChina w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_adl_dressing','10-66.1066-RuralChina-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local RuralChina w2,  echo=FALSE}
s1066_RuralChina_w2_adl_dressing <- opal.execute(o,'s1066_RuralChina_w2_adl_dressing')
vari <- s1066_RuralChina_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralChina_w2_adl_dressing$f_PDAS9)
ggplot(s1066_RuralChina_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralChina w2,   echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_adl_dressing$id)
t1066_ds_RCh_w2$adl_dressing <-  car::recode(s1066_RuralChina_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RCh_w2$adl_dressing <- labelled(t1066_ds_RCh_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2,  echo=FALSE}
vari <- t1066_ds_RCh_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2,  echo=FALSE}
AfterH <- table(t1066_ds_RCh_w2$adl_dressing)
X<-table(s1066_RuralChina_w2_adl_dressing$f_PDAS9)
#nas<-length(s1066_RuralChina_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_RuralChina_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1,2,3,4->0")
kable(C)
```

 
 


 
```{r importOPAL RuralChina w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RCh_w2) <- NULL
label(t1066_ds_RCh_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$adl_dressing <- car::recode(t1066_m_ds_RCh_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RCh_w2
save(adl_dressing, file = paste0(datafolder, "/RCh_w2/adl_dressing.RData"))
```

## Dominican Republic
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign DominicanRepublic w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_adl_dressing','10-66.1066-DominicanRepublic-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local DominicanRepublic w1,  echo=FALSE}
s1066_DominicanRepublic_w1_adl_dressing <- opal.execute(o,'s1066_DominicanRepublic_w1_adl_dressing')
vari <- s1066_DominicanRepublic_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_DominicanRepublic_w1_adl_dressing$PDAS9)
ggplot(s1066_DominicanRepublic_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo DominicanRepublic w1,   echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_adl_dressing$id)
t1066_ds_DR_w1$adl_dressing <- car::recode(s1066_DominicanRepublic_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_DR_w1$adl_dressing <- labelled(t1066_ds_DR_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1,  echo=FALSE}
vari <- t1066_ds_DR_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1,  echo=FALSE}
AfterH <- table(t1066_ds_DR_w1$adl_dressing)
X<-table(s1066_DominicanRepublic_w1_adl_dressing$PDAS9)
nas<-length(s1066_DominicanRepublic_w1_adl_dressing$PDAS9)-length(na.omit(s1066_DominicanRepublic_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL DominicanRepublic w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_DR_w1) <- NULL
label(t1066_ds_DR_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$adl_dressing <- car::recode(t1066_m_ds_DR_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_DR_w1
save(adl_dressing, file = paste0(datafolder, "/DR_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign DominicanRepublic w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_adl_dressing','10-66.1066-DominicanRepublic-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local DominicanRepublic w2,  echo=FALSE}
s1066_DominicanRepublic_w2_adl_dressing <- opal.execute(o,'s1066_DominicanRepublic_w2_adl_dressing')
vari <- s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9)
ggplot(s1066_DominicanRepublic_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo DominicanRepublic w2,   echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_adl_dressing$id)
t1066_ds_DR_w2$adl_dressing <-  car::recode(s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_DR_w2$adl_dressing <- labelled(t1066_ds_DR_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2,  echo=FALSE}
vari <- t1066_ds_DR_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2,  echo=FALSE}
AfterH <- table(t1066_ds_DR_w2$adl_dressing)
X<-table(s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_DominicanRepublic_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL DominicanRepublic w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_DR_w2) <- NULL
label(t1066_ds_DR_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$adl_dressing <- car::recode(t1066_m_ds_DR_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_DR_w2
save(adl_dressing, file = paste0(datafolder, "/DR_w2/adl_dressing.RData"))
```

## Venezuela
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign Venezuela w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_adl_dressing','10-66.1066-Venezuela-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local Venezuela w1,  echo=FALSE}
s1066_Venezuela_w1_adl_dressing <- opal.execute(o,'s1066_Venezuela_w1_adl_dressing')
vari <- s1066_Venezuela_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_Venezuela_w1_adl_dressing$PDAS9)
ggplot(s1066_Venezuela_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Venezuela w1,   echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_adl_dressing$id)
t1066_ds_Ven_w1$adl_dressing <- car::recode(s1066_Venezuela_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_Ven_w1$adl_dressing <- labelled(t1066_ds_Ven_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1,  echo=FALSE}
vari <- t1066_ds_Ven_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1,  echo=FALSE}
AfterH <- table(t1066_ds_Ven_w1$adl_dressing)
X<-table(s1066_Venezuela_w1_adl_dressing$PDAS9)
nas<-length(s1066_Venezuela_w1_adl_dressing$PDAS9)-length(na.omit(s1066_Venezuela_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Venezuela w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_Ven_w1) <- NULL
label(t1066_ds_Ven_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$adl_dressing <- car::recode(t1066_m_ds_Ven_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_Ven_w1
save(adl_dressing, file = paste0(datafolder, "/Ven_w1/adl_dressing.RData"))
```


### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign Venezuela w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_adl_dressing','10-66.1066-Venezuela-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local Venezuela w2,  echo=FALSE}
s1066_Venezuela_w2_adl_dressing <- opal.execute(o,'s1066_Venezuela_w2_adl_dressing')
vari <- s1066_Venezuela_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_Venezuela_w2_adl_dressing$f_PDAS9)
ggplot(s1066_Venezuela_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Venezuela w2,   echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_adl_dressing$id)
t1066_ds_Ven_w2$adl_dressing <-  car::recode(s1066_Venezuela_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_Ven_w2$adl_dressing <- labelled(t1066_ds_Ven_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2,  echo=FALSE}
vari <- t1066_ds_Ven_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2,  echo=FALSE}
AfterH <- table(t1066_ds_Ven_w2$adl_dressing)
X<-table(s1066_Venezuela_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_Venezuela_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_Venezuela_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Venezuela w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_Ven_w2) <- NULL
label(t1066_ds_Ven_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$adl_dressing <- car::recode(t1066_m_ds_Ven_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_Ven_w2
save(adl_dressing, file = paste0(datafolder, "/Ven_w2/adl_dressing.RData"))
```

## Urban Peru 
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign UrbanPeru w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_adl_dressing','10-66.1066-UrbanPeru-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local UrbanPeru w1,  echo=FALSE}
s1066_UrbanPeru_w1_adl_dressing <- opal.execute(o,'s1066_UrbanPeru_w1_adl_dressing')
vari <- s1066_UrbanPeru_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanPeru_w1_adl_dressing$PDAS9)
ggplot(s1066_UrbanPeru_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanPeru w1,   echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_adl_dressing$id)
t1066_ds_UP_w1$adl_dressing <- car::recode(s1066_UrbanPeru_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UP_w1$adl_dressing <- labelled(t1066_ds_UP_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1,  echo=FALSE}
vari <- t1066_ds_UP_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1,  echo=FALSE}
AfterH <- table(t1066_ds_UP_w1$adl_dressing)
X<-table(s1066_UrbanPeru_w1_adl_dressing$PDAS9)
nas<-length(s1066_UrbanPeru_w1_adl_dressing$PDAS9)-length(na.omit(s1066_UrbanPeru_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanPeru w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UP_w1) <- NULL
label(t1066_ds_UP_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$adl_dressing <- car::recode(t1066_m_ds_UP_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UP_w1
save(adl_dressing, file = paste0(datafolder, "/UP_w1/adl_dressing.RData"))
```


### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings


* Description: 
```{r assign UrbanPeru w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_adl_dressing','10-66.1066-UrbanPeru-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local UrbanPeru w2,  echo=FALSE}
s1066_UrbanPeru_w2_adl_dressing <- opal.execute(o,'s1066_UrbanPeru_w2_adl_dressing')
vari <- s1066_UrbanPeru_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanPeru_w2_adl_dressing$f_PDAS9)
ggplot(s1066_UrbanPeru_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo UrbanPeru w2,   echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_adl_dressing$id)
t1066_ds_UP_w2$adl_dressing <-  car::recode(s1066_UrbanPeru_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UP_w2$adl_dressing <- labelled(t1066_ds_UP_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2,  echo=FALSE}
vari <- t1066_ds_UP_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2,  echo=FALSE}
AfterH <- table(t1066_ds_UP_w2$adl_dressing)
X<-table(s1066_UrbanPeru_w2_adl_dressing$f_PDAS9)
#nas<-length(s1066_UrbanPeru_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_UrbanPeru_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL UrbanPeru w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UP_w2) <- NULL
label(t1066_ds_UP_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$adl_dressing <- car::recode(t1066_m_ds_UP_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UP_w2
save(adl_dressing, file = paste0(datafolder, "/UP_w2/adl_dressing.RData"))
```

## Rural Peru 
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign RuralPeru w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_adl_dressing','10-66.1066-RuralPeru-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local RuralPeru w1,  echo=FALSE}
s1066_RuralPeru_w1_adl_dressing <- opal.execute(o,'s1066_RuralPeru_w1_adl_dressing')
vari <- s1066_RuralPeru_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralPeru_w1_adl_dressing$PDAS9)
ggplot(s1066_RuralPeru_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo RuralPeru w1,   echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_adl_dressing$id)
t1066_ds_RP_w1$adl_dressing <- car::recode(s1066_RuralPeru_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RP_w1$adl_dressing <- labelled(t1066_ds_RP_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1,  echo=FALSE}
vari <- t1066_ds_RP_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1,  echo=FALSE}
AfterH <- table(t1066_ds_RP_w1$adl_dressing)
X<-table(s1066_RuralPeru_w1_adl_dressing$PDAS9)
nas<-length(s1066_RuralPeru_w1_adl_dressing$PDAS9)-length(na.omit(s1066_RuralPeru_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL RuralPeru w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RP_w1) <- NULL
label(t1066_ds_RP_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$adl_dressing <- car::recode(t1066_m_ds_RP_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RP_w1
save(adl_dressing, file = paste0(datafolder, "/RP_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings


* Description: 
```{r assign RuralPeru w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_adl_dressing','10-66.1066-RuralPeru-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local RuralPeru w2,  echo=FALSE}
s1066_RuralPeru_w2_adl_dressing <- opal.execute(o,'s1066_RuralPeru_w2_adl_dressing')
vari <- s1066_RuralPeru_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralPeru_w2_adl_dressing$f_PDAS9)
ggplot(s1066_RuralPeru_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralPeru w2,   echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_adl_dressing$id)
t1066_ds_RP_w2$adl_dressing <-  car::recode(s1066_RuralPeru_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RP_w2$adl_dressing <- labelled(t1066_ds_RP_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2,  echo=FALSE}
vari <- t1066_ds_RP_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2,  echo=FALSE}
AfterH <- table(t1066_ds_RP_w2$adl_dressing)
X<-table(s1066_RuralPeru_w2_adl_dressing$f_PDAS9)
#nas<-length(s1066_RuralPeru_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_RuralPeru_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL RuralPeru w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RP_w2) <- NULL
label(t1066_ds_RP_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$adl_dressing <- car::recode(t1066_m_ds_RP_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RP_w2
save(adl_dressing, file = paste0(datafolder, "/RP_w2/adl_dressing.RData"))
```
## Urban Mexico
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign UrbanMexico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_adl_dressing','10-66.1066-UrbanMexico-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local UrbanMexico w1,  echo=FALSE}
s1066_UrbanMexico_w1_adl_dressing <- opal.execute(o,'s1066_UrbanMexico_w1_adl_dressing')
vari <- s1066_UrbanMexico_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanMexico_w1_adl_dressing$PDAS9)
ggplot(s1066_UrbanMexico_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanMexico w1,   echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_adl_dressing$id)
t1066_ds_UM_w1$adl_dressing <- car::recode(s1066_UrbanMexico_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UM_w1$adl_dressing <- labelled(t1066_ds_UM_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1,  echo=FALSE}
vari <- t1066_ds_UM_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1,  echo=FALSE}
AfterH <- table(t1066_ds_UM_w1$adl_dressing)
X<-table(s1066_UrbanMexico_w1_adl_dressing$PDAS9)
nas<-length(s1066_UrbanMexico_w1_adl_dressing$PDAS9)-length(na.omit(s1066_UrbanMexico_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanMexico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UM_w1) <- NULL
label(t1066_ds_UM_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$adl_dressing <- car::recode(t1066_m_ds_UM_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UM_w1
save(adl_dressing, file = paste0(datafolder, "/UM_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign UrbanMexico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_adl_dressing','10-66.1066-UrbanMexico-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local UrbanMexico w2,  echo=FALSE}
s1066_UrbanMexico_w2_adl_dressing <- opal.execute(o,'s1066_UrbanMexico_w2_adl_dressing')
vari <- s1066_UrbanMexico_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_UrbanMexico_w2_adl_dressing$f_PDAS9)
ggplot(s1066_UrbanMexico_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanMexico w2,   echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_adl_dressing$id)
t1066_ds_UM_w2$adl_dressing <-  car::recode(s1066_UrbanMexico_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UM_w2$adl_dressing <- labelled(t1066_ds_UM_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2,  echo=FALSE}
vari <- t1066_ds_UM_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2,  echo=FALSE}
AfterH <- table(t1066_ds_UM_w2$adl_dressing)
X<-table(s1066_UrbanMexico_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_UrbanMexico_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_UrbanMexico_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanMexico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UM_w2) <- NULL
label(t1066_ds_UM_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$adl_dressing <- car::recode(t1066_m_ds_UM_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_UM_w2
save(adl_dressing, file = paste0(datafolder, "/UM_w2/adl_dressing.RData"))
```

## Rural Mexico
### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings



* Description: 
```{r assign RuralMexico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_adl_dressing','10-66.1066-RuralMexico-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local RuralMexico w1,  echo=FALSE}
s1066_RuralMexico_w1_adl_dressing <- opal.execute(o,'s1066_RuralMexico_w1_adl_dressing')
vari <- s1066_RuralMexico_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralMexico_w1_adl_dressing$PDAS9)
ggplot(s1066_RuralMexico_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralMexico w1,   echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_adl_dressing$id)
t1066_ds_RM_w1$adl_dressing <- car::recode(s1066_RuralMexico_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RM_w1$adl_dressing <- labelled(t1066_ds_RM_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1,  echo=FALSE}
vari <- t1066_ds_RM_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1,  echo=FALSE}
AfterH <- table(t1066_ds_RM_w1$adl_dressing)
X<-table(s1066_RuralMexico_w1_adl_dressing$PDAS9)
#nas<-length(s1066_RuralMexico_w1_adl_dressing$PDAS9)-length(na.omit(s1066_RuralMexico_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL RuralMexico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RM_w1) <- NULL
label(t1066_ds_RM_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$adl_dressing <- car::recode(t1066_m_ds_RM_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RM_w1
save(adl_dressing, file = paste0(datafolder, "/RM_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign RuralMexico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_adl_dressing','10-66.1066-RuralMexico-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local RuralMexico w2,  echo=FALSE}
s1066_RuralMexico_w2_adl_dressing <- opal.execute(o,'s1066_RuralMexico_w2_adl_dressing')
vari <- s1066_RuralMexico_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_RuralMexico_w2_adl_dressing$f_PDAS9)
ggplot(s1066_RuralMexico_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo RuralMexico w2,   echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_adl_dressing$id)
t1066_ds_RM_w2$adl_dressing <-  car::recode(s1066_RuralMexico_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RM_w2$adl_dressing <- labelled(t1066_ds_RM_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2,  echo=FALSE}
vari <- t1066_ds_RM_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2,  echo=FALSE}
AfterH <- table(t1066_ds_RM_w2$adl_dressing)
X<-table(s1066_RuralMexico_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_RuralMexico_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_RuralMexico_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL RuralMexico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RM_w2) <- NULL
label(t1066_ds_RM_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$adl_dressing <- car::recode(t1066_m_ds_RM_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_RM_w2
save(adl_dressing, file = paste0(datafolder, "/RM_w2/adl_dressing.RData"))
```

## Puerto Rico

### Wave 1 

#### Study-specific variable description

 


* Name: `PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`


* Description: 
```{r assign PuertoRico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_adl_dressing','10-66.1066-PuertoRico-Baseline', variables=list('PDAS9'), missings = TRUE)
```

```{r local PuertoRico w1,  echo=FALSE}
s1066_PuertoRico_w1_adl_dressing <- opal.execute(o,'s1066_PuertoRico_w1_adl_dressing')
vari <- s1066_PuertoRico_w1_adl_dressing$PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_PuertoRico_w1_adl_dressing$PDAS9)
ggplot(s1066_PuertoRico_w1_adl_dressing, aes(x=factor(PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo PuertoRico w1,   echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_adl_dressing$id)
t1066_ds_PR_w1$adl_dressing <- car::recode(s1066_PuertoRico_w1_adl_dressing$PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_PR_w1$adl_dressing <- labelled(t1066_ds_PR_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1,  echo=FALSE}
vari <- t1066_ds_PR_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1,  echo=FALSE}
AfterH <- table(t1066_ds_PR_w1$adl_dressing)
X<-table(s1066_PuertoRico_w1_adl_dressing$PDAS9)
nas<-length(s1066_PuertoRico_w1_adl_dressing$PDAS9)-length(na.omit(s1066_PuertoRico_w1_adl_dressing$PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL PuertoRico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_PR_w1) <- NULL
label(t1066_ds_PR_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$adl_dressing <- car::recode(t1066_m_ds_PR_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```

```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_PR_w1
save(adl_dressing, file = paste0(datafolder, "/PR_w1/adl_dressing.RData"))
```

### Wave 2 

#### Study-specific variable description

 


* Name: `f_PDAS9`
* Label: `difficulty with getting dressed`
* Categories:
    + `0 None`
    + `1 Mild difficulty` 
    + `2 Moderate difficulty`
    + `3 Severe difficulty`
    + `4 Extreme difficulty/cannot do`
* Missings
    + `NA`

* Description: 
```{r assign PuertoRico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_adl_dressing','10-66.1066-PuertoRico-Followup', variables=list('f_PDAS9'), missings = TRUE)
```

```{r local PuertoRico w2,  echo=FALSE}
s1066_PuertoRico_w2_adl_dressing <- opal.execute(o,'s1066_PuertoRico_w2_adl_dressing')
vari <- s1066_PuertoRico_w2_adl_dressing$f_PDAS9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(s1066_PuertoRico_w2_adl_dressing$f_PDAS9)
ggplot(s1066_PuertoRico_w2_adl_dressing, aes(x=factor(f_PDAS9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo PuertoRico w2,   echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_adl_dressing$id)
t1066_ds_PR_w2$adl_dressing <-  car::recode(s1066_PuertoRico_w2_adl_dressing$f_PDAS9, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_PR_w2$adl_dressing <- labelled(t1066_ds_PR_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2,  echo=FALSE}
vari <- t1066_ds_PR_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$adl_dressing,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2,  echo=FALSE}
AfterH <- table(t1066_ds_PR_w2$adl_dressing)
X<-table(s1066_PuertoRico_w2_adl_dressing$f_PDAS9)
nas<-length(s1066_PuertoRico_w2_adl_dressing$f_PDAS9)-length(na.omit(s1066_PuertoRico_w2_adl_dressing$f_PDAS9))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL PuertoRico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_PR_w2) <- NULL
label(t1066_ds_PR_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$adl_dressing <- car::recode(t1066_m_ds_PR_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```


```{r ,  echo=FALSE}
adl_dressing <- t1066_ds_PR_w2
save(adl_dressing, file = paste0(datafolder, "/PR_w2/adl_dressing.RData"))
```
# Quality control

No comments.


```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
