---
title: "IADLs - Doing housework"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/iadl_housewkDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/iadl_housewkDS.R')
```


<!-- ########################################################## --> 

# Data process



## Cuba

### Wave 1 

#### Study-specific variable description


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-Cuba-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign Cuba w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w1_iadl_housewk','10-66.1066-Cuba-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local Cuba w1,  echo=FALSE}
s1066_Cuba_w1_iadl_housewk <- opal.execute(o,'s1066_Cuba_w1_iadl_housewk')
vari <- s1066_Cuba_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_Cuba_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Cuba w1,   echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_iadl_housewk$id)
t1066_ds_cuba_w1$iadl_housewk <- car::recode(s1066_Cuba_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_cuba_w1$iadl_housewk <- labelled(t1066_ds_cuba_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1,  echo=FALSE}
vari <- t1066_ds_cuba_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_cuba_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1,  echo=FALSE}
AfterH <- table(t1066_ds_cuba_w1$iadl_housewk)
X<-table(s1066_Cuba_w1_iadl_housewk$PDAS2)
nas<-length(s1066_Cuba_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_Cuba_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Cuba w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_cuba_w1) <- NULL
label(t1066_ds_cuba_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$iadl_housewk <- car::recode(t1066_m_ds_cuba_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_cuba_w1
save(iadl_housewk, file = paste0(datafolder, "/cuba_w1/iadl_housewk.RData"))
```

### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-Cuba-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign Cuba w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w2_iadl_housewk','10-66.1066-Cuba-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local Cuba w2,  echo=FALSE}
s1066_Cuba_w2_iadl_housewk <- opal.execute(o,'s1066_Cuba_w2_iadl_housewk')
vari <- s1066_Cuba_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_Cuba_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Cuba w2,   echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_iadl_housewk$id)
t1066_ds_cuba_w2$iadl_housewk <-  car::recode(s1066_Cuba_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_cuba_w2$iadl_housewk <- labelled(t1066_ds_cuba_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2,  echo=FALSE}
vari <- t1066_ds_cuba_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_cuba_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2,  echo=FALSE}
AfterH <- table(t1066_ds_cuba_w2$iadl_housewk)
X<-table(s1066_Cuba_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_Cuba_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_Cuba_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Cuba w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_cuba_w2) <- NULL
label(t1066_ds_cuba_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$iadl_housewk <- car::recode(t1066_m_ds_cuba_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_cuba_w2
save(iadl_housewk, file = paste0(datafolder, "/cuba_w2/iadl_housewk.RData"))
```

## India
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-India-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign India w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_India_w1_iadl_housewk','10-66.1066-India-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local India w1,  echo=FALSE}
s1066_India_w1_iadl_housewk <- opal.execute(o,'s1066_India_w1_iadl_housewk')
vari <- s1066_India_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_India_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo India w1,   echo=TRUE}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_iadl_housewk$id)
t1066_ds_india_w1$iadl_housewk <- car::recode(s1066_India_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_india_w1$iadl_housewk <- labelled(t1066_ds_india_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1,  echo=FALSE}
vari <- t1066_ds_india_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_india_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1,  echo=FALSE}
AfterH <- table(t1066_ds_india_w1$iadl_housewk)
X<-table(s1066_India_w1_iadl_housewk$PDAS2)
nas<-length(s1066_India_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_India_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL India w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_india_w1) <- NULL
label(t1066_ds_india_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$iadl_housewk <- car::recode(t1066_m_ds_india_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_india_w1
save(iadl_housewk, file = paste0(datafolder, "/india_w1/iadl_housewk.RData"))
```




## Urban China
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanChina-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign UrbanChina w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_iadl_housewk','10-66.1066-UrbanChina-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local UrbanChina w1,  echo=FALSE}
s1066_UrbanChina_w1_iadl_housewk <- opal.execute(o,'s1066_UrbanChina_w1_iadl_housewk')
vari <- s1066_UrbanChina_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanChina_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanChina w1,   echo=TRUE}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_iadl_housewk$id)
t1066_ds_UCh_w1$iadl_housewk <- car::recode(s1066_UrbanChina_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UCh_w1$iadl_housewk <- labelled(t1066_ds_UCh_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1,  echo=FALSE}
vari <- t1066_ds_UCh_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UCh_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1,  echo=FALSE}
AfterH <- table(t1066_ds_UCh_w1$iadl_housewk)
X<-table(s1066_UrbanChina_w1_iadl_housewk$PDAS2)
nas<-length(s1066_UrbanChina_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_UrbanChina_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanChina w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UCh_w1) <- NULL
label(t1066_ds_UCh_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$iadl_housewk <- car::recode(t1066_m_ds_UCh_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UCh_w1
save(iadl_housewk, file = paste0(datafolder, "/UCh_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanChina-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |






 
  


```{r assign UrbanChina w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_iadl_housewk','10-66.1066-UrbanChina-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local UrbanChina w2,  echo=FALSE}
s1066_UrbanChina_w2_iadl_housewk <- opal.execute(o,'s1066_UrbanChina_w2_iadl_housewk')
vari <- s1066_UrbanChina_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanChina_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo UrbanChina w2,   echo=TRUE}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_iadl_housewk$id)
t1066_ds_UCh_w2$iadl_housewk <-  car::recode(s1066_UrbanChina_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UCh_w2$iadl_housewk <- labelled(t1066_ds_UCh_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2,  echo=FALSE}
vari <- t1066_ds_UCh_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UCh_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2,  echo=FALSE}
AfterH <- table(t1066_ds_UCh_w2$iadl_housewk)
X<-table(s1066_UrbanChina_w2_iadl_housewk$f_PDAS2)
#nas<-length(s1066_UrbanChina_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_UrbanChina_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1,2,3,4->0")
kable(C)
```

 
 


 
```{r importOPAL UrbanChina w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UCh_w2) <- NULL
label(t1066_ds_UCh_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$iadl_housewk <- car::recode(t1066_m_ds_UCh_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UCh_w2
save(iadl_housewk, file = paste0(datafolder, "/UCh_w2/iadl_housewk.RData"))
```

## Rural China
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralChina-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralChina w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_iadl_housewk','10-66.1066-RuralChina-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local RuralChina w1,  echo=FALSE}
s1066_RuralChina_w1_iadl_housewk <- opal.execute(o,'s1066_RuralChina_w1_iadl_housewk')
vari <- s1066_RuralChina_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralChina_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo RuralChina w1,   echo=TRUE}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_iadl_housewk$id)
t1066_ds_RCh_w1$iadl_housewk <- car::recode(s1066_RuralChina_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RCh_w1$iadl_housewk <- labelled(t1066_ds_RCh_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1,  echo=FALSE}
vari <- t1066_ds_RCh_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RCh_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1,  echo=FALSE}
AfterH <- table(t1066_ds_RCh_w1$iadl_housewk)
X<-table(s1066_RuralChina_w1_iadl_housewk$PDAS2)
nas<-length(s1066_RuralChina_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_RuralChina_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL RuralChina w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RCh_w1) <- NULL
label(t1066_ds_RCh_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$iadl_housewk <- car::recode(t1066_m_ds_RCh_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RCh_w1
save(iadl_housewk, file = paste0(datafolder, "/RCh_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralChina-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralChina w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_iadl_housewk','10-66.1066-RuralChina-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local RuralChina w2,  echo=FALSE}
s1066_RuralChina_w2_iadl_housewk <- opal.execute(o,'s1066_RuralChina_w2_iadl_housewk')
vari <- s1066_RuralChina_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralChina_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralChina w2,   echo=TRUE}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_iadl_housewk$id)
t1066_ds_RCh_w2$iadl_housewk <-  car::recode(s1066_RuralChina_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RCh_w2$iadl_housewk <- labelled(t1066_ds_RCh_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2,  echo=FALSE}
vari <- t1066_ds_RCh_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RCh_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2,  echo=FALSE}
AfterH <- table(t1066_ds_RCh_w2$iadl_housewk)
X<-table(s1066_RuralChina_w2_iadl_housewk$f_PDAS2)
#nas<-length(s1066_RuralChina_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_RuralChina_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1,2,3,4->0")
kable(C)
```

 
 


 
```{r importOPAL RuralChina w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RCh_w2) <- NULL
label(t1066_ds_RCh_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$iadl_housewk <- car::recode(t1066_m_ds_RCh_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RCh_w2
save(iadl_housewk, file = paste0(datafolder, "/RCh_w2/iadl_housewk.RData"))
```


## Dominican Republic
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-DominicanRepublic-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign DominicanRepublic w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_iadl_housewk','10-66.1066-DominicanRepublic-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local DominicanRepublic w1,  echo=FALSE}
s1066_DominicanRepublic_w1_iadl_housewk <- opal.execute(o,'s1066_DominicanRepublic_w1_iadl_housewk')
vari <- s1066_DominicanRepublic_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_DominicanRepublic_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo DominicanRepublic w1,   echo=TRUE}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_iadl_housewk$id)
t1066_ds_DR_w1$iadl_housewk <- car::recode(s1066_DominicanRepublic_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_DR_w1$iadl_housewk <- labelled(t1066_ds_DR_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1,  echo=FALSE}
vari <- t1066_ds_DR_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_DR_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1,  echo=FALSE}
AfterH <- table(t1066_ds_DR_w1$iadl_housewk)
X<-table(s1066_DominicanRepublic_w1_iadl_housewk$PDAS2)
nas<-length(s1066_DominicanRepublic_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_DominicanRepublic_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL DominicanRepublic w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_DR_w1) <- NULL
label(t1066_ds_DR_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$iadl_housewk <- car::recode(t1066_m_ds_DR_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_DR_w1
save(iadl_housewk, file = paste0(datafolder, "/DR_w1/iadl_housewk.RData"))
```

### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-DominicanRepublic-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign DominicanRepublic w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_iadl_housewk','10-66.1066-DominicanRepublic-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local DominicanRepublic w2,  echo=FALSE}
s1066_DominicanRepublic_w2_iadl_housewk <- opal.execute(o,'s1066_DominicanRepublic_w2_iadl_housewk')
vari <- s1066_DominicanRepublic_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_DominicanRepublic_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo DominicanRepublic w2,   echo=TRUE}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_iadl_housewk$id)
t1066_ds_DR_w2$iadl_housewk <-  car::recode(s1066_DominicanRepublic_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_DR_w2$iadl_housewk <- labelled(t1066_ds_DR_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2,  echo=FALSE}
vari <- t1066_ds_DR_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_DR_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2,  echo=FALSE}
AfterH <- table(t1066_ds_DR_w2$iadl_housewk)
X<-table(s1066_DominicanRepublic_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_DominicanRepublic_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_DominicanRepublic_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL DominicanRepublic w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_DR_w2) <- NULL
label(t1066_ds_DR_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$iadl_housewk <- car::recode(t1066_m_ds_DR_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_DR_w2
save(iadl_housewk, file = paste0(datafolder, "/DR_w2/iadl_housewk.RData"))
```

## Venezuela
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-Venezuela-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign Venezuela w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_iadl_housewk','10-66.1066-Venezuela-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local Venezuela w1,  echo=FALSE}
s1066_Venezuela_w1_iadl_housewk <- opal.execute(o,'s1066_Venezuela_w1_iadl_housewk')
vari <- s1066_Venezuela_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_Venezuela_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Venezuela w1,   echo=TRUE}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_iadl_housewk$id)
t1066_ds_Ven_w1$iadl_housewk <- car::recode(s1066_Venezuela_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_Ven_w1$iadl_housewk <- labelled(t1066_ds_Ven_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1,  echo=FALSE}
vari <- t1066_ds_Ven_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_Ven_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1,  echo=FALSE}
AfterH <- table(t1066_ds_Ven_w1$iadl_housewk)
X<-table(s1066_Venezuela_w1_iadl_housewk$PDAS2)
nas<-length(s1066_Venezuela_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_Venezuela_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Venezuela w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_Ven_w1) <- NULL
label(t1066_ds_Ven_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$iadl_housewk <- car::recode(t1066_m_ds_Ven_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_Ven_w1
save(iadl_housewk, file = paste0(datafolder, "/Ven_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-Venezuela-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign Venezuela w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_iadl_housewk','10-66.1066-Venezuela-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local Venezuela w2,  echo=FALSE}
s1066_Venezuela_w2_iadl_housewk <- opal.execute(o,'s1066_Venezuela_w2_iadl_housewk')
vari <- s1066_Venezuela_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_Venezuela_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo Venezuela w2,   echo=TRUE}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_iadl_housewk$id)
t1066_ds_Ven_w2$iadl_housewk <-  car::recode(s1066_Venezuela_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_Ven_w2$iadl_housewk <- labelled(t1066_ds_Ven_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2,  echo=FALSE}
vari <- t1066_ds_Ven_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_Ven_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2,  echo=FALSE}
AfterH <- table(t1066_ds_Ven_w2$iadl_housewk)
X<-table(s1066_Venezuela_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_Venezuela_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_Venezuela_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL Venezuela w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_Ven_w2) <- NULL
label(t1066_ds_Ven_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$iadl_housewk <- car::recode(t1066_m_ds_Ven_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_Ven_w2
save(iadl_housewk, file = paste0(datafolder, "/Ven_w2/iadl_housewk.RData"))
```

## Urban Peru
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanPeru-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanPeru w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_iadl_housewk','10-66.1066-UrbanPeru-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local UrbanPeru w1,  echo=FALSE}
s1066_UrbanPeru_w1_iadl_housewk <- opal.execute(o,'s1066_UrbanPeru_w1_iadl_housewk')
vari <- s1066_UrbanPeru_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanPeru_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanPeru w1,   echo=TRUE}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_iadl_housewk$id)
t1066_ds_UP_w1$iadl_housewk <- car::recode(s1066_UrbanPeru_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UP_w1$iadl_housewk <- labelled(t1066_ds_UP_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1,  echo=FALSE}
vari <- t1066_ds_UP_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UP_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1,  echo=FALSE}
AfterH <- table(t1066_ds_UP_w1$iadl_housewk)
X<-table(s1066_UrbanPeru_w1_iadl_housewk$PDAS2)
nas<-length(s1066_UrbanPeru_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_UrbanPeru_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanPeru w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UP_w1) <- NULL
label(t1066_ds_UP_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$iadl_housewk <- car::recode(t1066_m_ds_UP_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UP_w1
save(iadl_housewk, file = paste0(datafolder, "/UP_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanPeru-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanPeru w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_iadl_housewk','10-66.1066-UrbanPeru-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local UrbanPeru w2,  echo=FALSE}
s1066_UrbanPeru_w2_iadl_housewk <- opal.execute(o,'s1066_UrbanPeru_w2_iadl_housewk')
vari <- s1066_UrbanPeru_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanPeru_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo UrbanPeru w2,   echo=TRUE}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_iadl_housewk$id)
t1066_ds_UP_w2$iadl_housewk <-  car::recode(s1066_UrbanPeru_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UP_w2$iadl_housewk <- labelled(t1066_ds_UP_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2,  echo=FALSE}
vari <- t1066_ds_UP_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UP_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2,  echo=FALSE}
AfterH <- table(t1066_ds_UP_w2$iadl_housewk)
X<-table(s1066_UrbanPeru_w2_iadl_housewk$f_PDAS2)
#nas<-length(s1066_UrbanPeru_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_UrbanPeru_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL UrbanPeru w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UP_w2) <- NULL
label(t1066_ds_UP_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$iadl_housewk <- car::recode(t1066_m_ds_UP_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UP_w2
save(iadl_housewk, file = paste0(datafolder, "/UP_w2/iadl_housewk.RData"))
```

## Rural Peru
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralPeru-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign RuralPeru w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_iadl_housewk','10-66.1066-RuralPeru-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local RuralPeru w1,  echo=FALSE}
s1066_RuralPeru_w1_iadl_housewk <- opal.execute(o,'s1066_RuralPeru_w1_iadl_housewk')
vari <- s1066_RuralPeru_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralPeru_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo RuralPeru w1,   echo=TRUE}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_iadl_housewk$id)
t1066_ds_RP_w1$iadl_housewk <- car::recode(s1066_RuralPeru_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RP_w1$iadl_housewk <- labelled(t1066_ds_RP_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1,  echo=FALSE}
vari <- t1066_ds_RP_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RP_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1,  echo=FALSE}
AfterH <- table(t1066_ds_RP_w1$iadl_housewk)
X<-table(s1066_RuralPeru_w1_iadl_housewk$PDAS2)
nas<-length(s1066_RuralPeru_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_RuralPeru_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL RuralPeru w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RP_w1) <- NULL
label(t1066_ds_RP_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$iadl_housewk <- car::recode(t1066_m_ds_RP_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RP_w1
save(iadl_housewk, file = paste0(datafolder, "/RP_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralPeru-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralPeru w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_iadl_housewk','10-66.1066-RuralPeru-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local RuralPeru w2,  echo=FALSE}
s1066_RuralPeru_w2_iadl_housewk <- opal.execute(o,'s1066_RuralPeru_w2_iadl_housewk')
vari <- s1066_RuralPeru_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralPeru_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralPeru w2,   echo=TRUE}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_iadl_housewk$id)
t1066_ds_RP_w2$iadl_housewk <-  car::recode(s1066_RuralPeru_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RP_w2$iadl_housewk <- labelled(t1066_ds_RP_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2,  echo=FALSE}
vari <- t1066_ds_RP_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RP_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2,  echo=FALSE}
AfterH <- table(t1066_ds_RP_w2$iadl_housewk)
X<-table(s1066_RuralPeru_w2_iadl_housewk$f_PDAS2)
#nas<-length(s1066_RuralPeru_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_RuralPeru_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL RuralPeru w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RP_w2) <- NULL
label(t1066_ds_RP_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$iadl_housewk <- car::recode(t1066_m_ds_RP_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RP_w2
save(iadl_housewk, file = paste0(datafolder, "/RP_w2/iadl_housewk.RData"))
```

## Urban Mexico
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanMexico-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanMexico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_iadl_housewk','10-66.1066-UrbanMexico-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local UrbanMexico w1,  echo=FALSE}
s1066_UrbanMexico_w1_iadl_housewk <- opal.execute(o,'s1066_UrbanMexico_w1_iadl_housewk')
vari <- s1066_UrbanMexico_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanMexico_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanMexico w1,   echo=TRUE}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_iadl_housewk$id)
t1066_ds_UM_w1$iadl_housewk <- car::recode(s1066_UrbanMexico_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UM_w1$iadl_housewk <- labelled(t1066_ds_UM_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1,  echo=FALSE}
vari <- t1066_ds_UM_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UM_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1,  echo=FALSE}
AfterH <- table(t1066_ds_UM_w1$iadl_housewk)
X<-table(s1066_UrbanMexico_w1_iadl_housewk$PDAS2)
nas<-length(s1066_UrbanMexico_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_UrbanMexico_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanMexico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UM_w1) <- NULL
label(t1066_ds_UM_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$iadl_housewk <- car::recode(t1066_m_ds_UM_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UM_w1
save(iadl_housewk, file = paste0(datafolder, "/UM_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-UrbanMexico-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanMexico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_iadl_housewk','10-66.1066-UrbanMexico-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local UrbanMexico w2,  echo=FALSE}
s1066_UrbanMexico_w2_iadl_housewk <- opal.execute(o,'s1066_UrbanMexico_w2_iadl_housewk')
vari <- s1066_UrbanMexico_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_UrbanMexico_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo UrbanMexico w2,   echo=TRUE}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_iadl_housewk$id)
t1066_ds_UM_w2$iadl_housewk <-  car::recode(s1066_UrbanMexico_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_UM_w2$iadl_housewk <- labelled(t1066_ds_UM_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2,  echo=FALSE}
vari <- t1066_ds_UM_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_UM_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2,  echo=FALSE}
AfterH <- table(t1066_ds_UM_w2$iadl_housewk)
X<-table(s1066_UrbanMexico_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_UrbanMexico_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_UrbanMexico_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL UrbanMexico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_UM_w2) <- NULL
label(t1066_ds_UM_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$iadl_housewk <- car::recode(t1066_m_ds_UM_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_UM_w2
save(iadl_housewk, file = paste0(datafolder, "/UM_w2/iadl_housewk.RData"))
```

## Rural Mexico
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralMexico-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign RuralMexico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_iadl_housewk','10-66.1066-RuralMexico-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local RuralMexico w1,  echo=FALSE}
s1066_RuralMexico_w1_iadl_housewk <- opal.execute(o,'s1066_RuralMexico_w1_iadl_housewk')
vari <- s1066_RuralMexico_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralMexico_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`


**R script:** 
```{r harmo RuralMexico w1,   echo=TRUE}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_iadl_housewk$id)
t1066_ds_RM_w1$iadl_housewk <- car::recode(s1066_RuralMexico_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RM_w1$iadl_housewk <- labelled(t1066_ds_RM_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1,  echo=FALSE}
vari <- t1066_ds_RM_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RM_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1,  echo=FALSE}
AfterH <- table(t1066_ds_RM_w1$iadl_housewk)
X<-table(s1066_RuralMexico_w1_iadl_housewk$PDAS2)
#nas<-length(s1066_RuralMexico_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_RuralMexico_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1")
kable(C)
```

 
 


 
```{r importOPAL RuralMexico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RM_w1) <- NULL
label(t1066_ds_RM_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$iadl_housewk <- car::recode(t1066_m_ds_RM_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RM_w1
save(iadl_housewk, file = paste0(datafolder, "/RM_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-RuralMexico-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |







    
    

```{r assign RuralMexico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_iadl_housewk','10-66.1066-RuralMexico-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local RuralMexico w2,  echo=FALSE}
s1066_RuralMexico_w2_iadl_housewk <- opal.execute(o,'s1066_RuralMexico_w2_iadl_housewk')
vari <- s1066_RuralMexico_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_RuralMexico_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo RuralMexico w2,   echo=TRUE}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_iadl_housewk$id)
t1066_ds_RM_w2$iadl_housewk <-  car::recode(s1066_RuralMexico_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_RM_w2$iadl_housewk <- labelled(t1066_ds_RM_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2,  echo=FALSE}
vari <- t1066_ds_RM_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_RM_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2,  echo=FALSE}
AfterH <- table(t1066_ds_RM_w2$iadl_housewk)
X<-table(s1066_RuralMexico_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_RuralMexico_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_RuralMexico_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL RuralMexico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_RM_w2) <- NULL
label(t1066_ds_RM_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$iadl_housewk <- car::recode(t1066_m_ds_RM_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_RM_w2
save(iadl_housewk, file = paste0(datafolder, "/RM_w2/iadl_housewk.RData"))
```

## Puerto Rico
### Wave 1 

#### Study-specific variable description

 


| **Name** |`PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-PuertoRico-Baseline`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |










```{r assign PuertoRico w1,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_iadl_housewk','10-66.1066-PuertoRico-Baseline', variables=list('PDAS2'), missings = TRUE)
```

```{r local PuertoRico w1,  echo=FALSE}
s1066_PuertoRico_w1_iadl_housewk <- opal.execute(o,'s1066_PuertoRico_w1_iadl_housewk')
vari <- s1066_PuertoRico_w1_iadl_housewk$PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_PuertoRico_w1_iadl_housewk, aes(x=factor(PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo PuertoRico w1,   echo=TRUE}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_iadl_housewk$id)
t1066_ds_PR_w1$iadl_housewk <- car::recode(s1066_PuertoRico_w1_iadl_housewk$PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_PR_w1$iadl_housewk <- labelled(t1066_ds_PR_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1,  echo=FALSE}
vari <- t1066_ds_PR_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_PR_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1,  echo=FALSE}
AfterH <- table(t1066_ds_PR_w1$iadl_housewk)
X<-table(s1066_PuertoRico_w1_iadl_housewk$PDAS2)
nas<-length(s1066_PuertoRico_w1_iadl_housewk$PDAS2)-length(na.omit(s1066_PuertoRico_w1_iadl_housewk$PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL PuertoRico w1, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_PR_w1) <- NULL
label(t1066_ds_PR_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$iadl_housewk <- car::recode(t1066_m_ds_PR_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```
```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_PR_w1
save(iadl_housewk, file = paste0(datafolder, "/PR_w1/iadl_housewk.RData"))
```


### Wave 2 

#### Study-specific variable description

 


| **Name** |`f_PDAS2`|
|-|-|
| **Label** |`difficulty with household responsibilities`|
| **Table name** |`1066-PuertoRico-Followup`|
| **Categories** |`0 = None`<br/>`1 = Mild difficulty`<br/>`2 = Moderate difficulty`<br/>`3 = Severe difficulty`<br/>`4 = Extreme difficulty/cannot do`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign PuertoRico w2,  echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_iadl_housewk','10-66.1066-PuertoRico-Followup', variables=list('f_PDAS2'), missings = TRUE)
```

```{r local PuertoRico w2,  echo=FALSE}
s1066_PuertoRico_w2_iadl_housewk <- opal.execute(o,'s1066_PuertoRico_w2_iadl_housewk')
vari <- s1066_PuertoRico_w2_iadl_housewk$f_PDAS2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(s1066_PuertoRico_w2_iadl_housewk, aes(x=factor(f_PDAS2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0` 
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo PuertoRico w2,   echo=TRUE}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_iadl_housewk$id)
t1066_ds_PR_w2$iadl_housewk <-  car::recode(s1066_PuertoRico_w2_iadl_housewk$f_PDAS2, "0 = '1';1='0';2 = '0';3='0';4='0';NA='999'")
t1066_ds_PR_w2$iadl_housewk <- labelled(t1066_ds_PR_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2,  echo=FALSE}
vari <- t1066_ds_PR_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(t1066_ds_PR_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2,  echo=FALSE}
AfterH <- table(t1066_ds_PR_w2$iadl_housewk)
X<-table(s1066_PuertoRico_w2_iadl_housewk$f_PDAS2)
nas<-length(s1066_PuertoRico_w2_iadl_housewk$f_PDAS2)-length(na.omit(s1066_PuertoRico_w2_iadl_housewk$f_PDAS2))
BeforeH <-c(sum(X[2:5]),X[1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","0->1","NA->999")
kable(C)
```

 
 


 
```{r importOPAL PuertoRico w2, echo=FALSE,  echo=FALSE}
val_labels(t1066_ds_PR_w2) <- NULL
label(t1066_ds_PR_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$iadl_housewk <- car::recode(t1066_m_ds_PR_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- t1066_ds_PR_w2
save(iadl_housewk, file = paste0(datafolder, "/PR_w2/iadl_housewk.RData"))
```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}


```







# Quality estimation

No comments


```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
