---
title: "Verbal fluency"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_verb_c`
* Variable label: `Cognition - verbal fluency - Continuous`
* Variable description: `Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute`
* Domain: `Health status and functional limitations`
* Value type: `Countinous`
* Comments: `Means of all sistolic blood pressure measures.`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cog_verb`
* Variable label: `Cognition - verbal fluency`
* Variable description: `Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Verbal fluency"
ds_label_cog_verb_c <- "Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute"
ds_label_cog_verb <- "Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## Cuba

### Wave 1 

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign Cuba w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w1_cog_verb','10-66.1066-Cuba-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_Cuba_w1_cog_verb <- opal.execute(o,'s1066_Cuba_w1_cog_verb')
```

```{r local Cuba w1, echo=FALSE}
vari <- s1066_Cuba_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_Cuba_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Cuba w1}
#cog_verb_c
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_cog_verb$id)
t1066_ds_cuba_w1$cog_verb_c <- car::recode(s1066_Cuba_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_cuba_w1$cog_verb_c <- labelled(t1066_ds_cuba_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_cuba_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_cuba_w1$cog_verb <- car::recode(t1066_ds_cuba_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_cuba_w1$cog_verb <- labelled(t1066_ds_cuba_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1, echo=FALSE}
vari <- t1066_ds_cuba_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_cuba_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_cuba_w1[[2]])<=Q), sum(na.omit(t1066_ds_cuba_w1[[2]])>Q & na.omit(t1066_ds_cuba_w1[[2]])<900))
Dicotomic <- table(t1066_ds_cuba_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","7:12->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Cuba w1, echo=FALSE}
#label(t1066_ds_cuba_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_cuba_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_cuba_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_cuba_w1
save(cog_verb, file = "../RData/cuba_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings
   + `NA`

```{r assign Cuba w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w2_cog_verb','10-66.1066-Cuba-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_Cuba_w2_cog_verb <- opal.execute(o,'s1066_Cuba_w2_cog_verb')
```

```{r local Cuba w2, echo=FALSE}
vari <- s1066_Cuba_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_Cuba_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_cog_verb$id)
t1066_ds_cuba_w2$cog_verb_c <- recode(s1066_Cuba_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_cuba_w2$cog_verb_c <- labelled(t1066_ds_cuba_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_cuba_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_cuba_w2$cog_verb <- car::recode(t1066_ds_cuba_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_cuba_w2$cog_verb <- labelled(t1066_ds_cuba_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2, echo=FALSE}
vari <- t1066_ds_cuba_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_cuba_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_cuba_w2[[2]])<=Q), sum(na.omit(t1066_ds_cuba_w2[[2]])>Q & na.omit(t1066_ds_cuba_w2[[2]])<900), sum(na.omit(t1066_ds_cuba_w2[[2]])==999))
Dicotomic <- table(t1066_ds_cuba_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Cuba w2, echo=FALSE}
#label(t1066_ds_cuba_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_cuba_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_cuba_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_cuba_w2
save(cog_verb, file = "../RData/cuba_w2/cog_verb.RData")
```



## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign India w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_India_w1_cog_verb','10-66.1066-India-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_India_w1_cog_verb <- opal.execute(o,'s1066_India_w1_cog_verb')
```

```{r local India w1, echo=FALSE}
vari <- s1066_India_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_India_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_cog_verb$id)
t1066_ds_india_w1$cog_verb_c <- recode(s1066_India_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_india_w1$cog_verb_c <- labelled(t1066_ds_india_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_india_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_india_w1$cog_verb <- car::recode(t1066_ds_india_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_india_w1$cog_verb <- labelled(t1066_ds_india_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=FALSE}
vari <- t1066_ds_india_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_india_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_india_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_india_w1[[2]])<=Q), sum(na.omit(t1066_ds_india_w1[[2]])>Q & na.omit(t1066_ds_india_w1[[2]])<900), sum(na.omit(t1066_ds_india_w1[[2]])==999))
Dicotomic <- table(t1066_ds_india_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:7->0","8:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL India w1, echo=FALSE}
#label(t1066_ds_india_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_india_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_india_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_india_w1
save(cog_verb, file = "../RData/india_w1/cog_verb.RData")
```



### Wave 2 

Not found.



## Urban China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign UrbanChina w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_cog_verb','10-66.1066-UrbanChina-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_UrbanChina_w1_cog_verb <- opal.execute(o,'s1066_UrbanChina_w1_cog_verb')
```

```{r local UrbanChina w1, echo=FALSE}
vari <- s1066_UrbanChina_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanChina_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanChina w1}
#cog_verb_c
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_cog_verb$id)
t1066_ds_UCh_w1$cog_verb_c <- recode(s1066_UrbanChina_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_UCh_w1$cog_verb_c <- labelled(t1066_ds_UCh_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UCh_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UCh_w1$cog_verb <- car::recode(t1066_ds_UCh_w1[[2]], "0:11=0; 12:900=1")
t1066_ds_UCh_w1$cog_verb <- labelled(t1066_ds_UCh_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=FALSE}
vari <- t1066_ds_UCh_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UCh_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UCh_w1[[2]])<=Q), sum(na.omit(t1066_ds_UCh_w1[[2]])>Q & na.omit(t1066_ds_UCh_w1[[2]])<900))
Dicotomic <- table(t1066_ds_UCh_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","12:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanChina w1, echo=FALSE}
#label(t1066_ds_UCh_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_UCh_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UCh_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UCh_w1
save(cog_verb, file = "../RData/UCh_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign UrbanChina w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_cog_verb','10-66.1066-UrbanChina-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_UrbanChina_w2_cog_verb <- opal.execute(o,'s1066_UrbanChina_w2_cog_verb')
```

```{r local UrbanChina w2, echo=FALSE}
vari <- s1066_UrbanChina_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanChina_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanChina w2}
#cog_verb_c
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_cog_verb$id)
t1066_ds_UCh_w2$cog_verb_c <- recode(s1066_UrbanChina_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_UCh_w2$cog_verb_c <- labelled(t1066_ds_UCh_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UCh_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UCh_w2$cog_verb <- car::recode(t1066_ds_UCh_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_UCh_w2$cog_verb <- labelled(t1066_ds_UCh_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=FALSE}
vari <- t1066_ds_UCh_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UCh_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UCh_w2[[2]])<=Q), sum(na.omit(t1066_ds_UCh_w2[[2]])>Q & na.omit(t1066_ds_UCh_w2[[2]])<900))
Dicotomic <- table(t1066_ds_UCh_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:9->0","10:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanChina w2, echo=FALSE}
#label(t1066_ds_UCh_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_UCh_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UCh_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UCh_w2
save(cog_verb, file = "../RData/UCh_w2/cog_verb.RData")
```




## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign RuralChina w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_cog_verb','10-66.1066-RuralChina-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_RuralChina_w1_cog_verb <- opal.execute(o,'s1066_RuralChina_w1_cog_verb')
```

```{r local RuralChina w1, echo=FALSE}
vari <- s1066_RuralChina_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralChina_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo RuralChina w1}
#cog_verb_c
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_cog_verb$id)
t1066_ds_RCh_w1$cog_verb_c <- recode(s1066_RuralChina_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_RCh_w1$cog_verb_c <- labelled(t1066_ds_RCh_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RCh_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RCh_w1$cog_verb <- car::recode(t1066_ds_RCh_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RCh_w1$cog_verb <- labelled(t1066_ds_RCh_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=FALSE}
vari <- t1066_ds_RCh_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RCh_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RCh_w1[[2]])<=Q), sum(na.omit(t1066_ds_RCh_w1[[2]])>Q & na.omit(t1066_ds_RCh_w1[[2]])<900))
Dicotomic <- table(t1066_ds_RCh_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralChina w1, echo=FALSE}
#label(t1066_ds_RCh_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_RCh_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RCh_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RCh_w1
save(cog_verb, file = "../RData/RCh_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign RuralChina w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_cog_verb','10-66.1066-RuralChina-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_RuralChina_w2_cog_verb <- opal.execute(o,'s1066_RuralChina_w2_cog_verb')
```

```{r local RuralChina w2, echo=FALSE}
vari <- s1066_RuralChina_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralChina_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo RuralChina w2}
#cog_verb_c
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_cog_verb$id)
t1066_ds_RCh_w2$cog_verb_c <- recode(s1066_RuralChina_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_RCh_w2$cog_verb_c <- labelled(t1066_ds_RCh_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RCh_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RCh_w2$cog_verb <- car::recode(t1066_ds_RCh_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RCh_w2$cog_verb <- labelled(t1066_ds_RCh_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=FALSE}
vari <- t1066_ds_RCh_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RCh_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RCh_w2[[2]])<=Q), sum(na.omit(t1066_ds_RCh_w2[[2]])>Q & na.omit(t1066_ds_RCh_w2[[2]])<900))
Dicotomic <- table(t1066_ds_RCh_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralChina w2, echo=FALSE}
#label(t1066_ds_RCh_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_RCh_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RCh_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RCh_w2
save(cog_verb, file = "../RData/RCh_w2/cog_verb.RData")
```



## Dominican Republic

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign DominicanRepublic w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_cog_verb','10-66.1066-DominicanRepublic-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_DominicanRepublic_w1_cog_verb <- opal.execute(o,'s1066_DominicanRepublic_w1_cog_verb')
```

```{r local DominicanRepublic w1, echo=FALSE}
vari <- s1066_DominicanRepublic_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_DominicanRepublic_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo DominicanRepublic w1}
#cog_verb_c
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_cog_verb$id)
t1066_ds_DR_w1$cog_verb_c <- recode(s1066_DominicanRepublic_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_DR_w1$cog_verb_c <- labelled(t1066_ds_DR_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_DR_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_DR_w1$cog_verb <- car::recode(t1066_ds_DR_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_DR_w1$cog_verb <- labelled(t1066_ds_DR_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=FALSE}
vari <- t1066_ds_DR_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_DR_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_DR_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_DR_w1[[2]])<=Q), sum(na.omit(t1066_ds_DR_w1[[2]])>Q & na.omit(t1066_ds_DR_w1[[2]])<900))
Dicotomic <- table(t1066_ds_DR_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL DominicanRepublic w1, echo=FALSE}
#label(t1066_ds_DR_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_DR_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_DR_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_DR_w1
save(cog_verb, file = "../RData/DR_w1/cog_verb.RData")
```


## Dominican Republic

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings
   + `NA`

```{r assign DominicanRepublic w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_cog_verb','10-66.1066-DominicanRepublic-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_DominicanRepublic_w2_cog_verb <- opal.execute(o,'s1066_DominicanRepublic_w2_cog_verb')
```

```{r local DominicanRepublic w2, echo=FALSE}
vari <- s1066_DominicanRepublic_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_DominicanRepublic_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo DominicanRepublic w2}
#cog_verb_c
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_cog_verb$id)
t1066_ds_DR_w2$cog_verb_c <- recode(s1066_DominicanRepublic_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_DR_w2$cog_verb_c <- labelled(t1066_ds_DR_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_DR_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_DR_w2$cog_verb <- car::recode(t1066_ds_DR_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_DR_w2$cog_verb <- labelled(t1066_ds_DR_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=FALSE}
vari <- t1066_ds_DR_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_DR_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_DR_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_DR_w2[[2]])<=Q), sum(na.omit(t1066_ds_DR_w2[[2]])>Q & na.omit(t1066_ds_DR_w2[[2]])<900), sum(na.omit(t1066_ds_DR_w2[[2]])==999))
Dicotomic <- table(t1066_ds_DR_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL DominicanRepublic w2, echo=FALSE}
#label(t1066_ds_DR_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_DR_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_DR_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_DR_w2
save(cog_verb, file = "../RData/DR_w2/cog_verb.RData")
```



## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign Venezuela w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_cog_verb','10-66.1066-Venezuela-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_Venezuela_w1_cog_verb <- opal.execute(o,'s1066_Venezuela_w1_cog_verb')
```

```{r local Venezuela w1, echo=FALSE}
vari <- s1066_Venezuela_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_Venezuela_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Venezuela w1}
#cog_verb_c
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_cog_verb$id)
t1066_ds_Ven_w1$cog_verb_c <- recode(s1066_Venezuela_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_Ven_w1$cog_verb_c <- labelled(t1066_ds_Ven_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_Ven_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_Ven_w1$cog_verb <- car::recode(t1066_ds_Ven_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_Ven_w1$cog_verb <- labelled(t1066_ds_Ven_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=FALSE}
vari <- t1066_ds_Ven_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_Ven_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_Ven_w1[[2]])<=Q), sum(na.omit(t1066_ds_Ven_w1[[2]])>Q & na.omit(t1066_ds_Ven_w1[[2]])<900))
Dicotomic <- table(t1066_ds_Ven_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:13->0","14:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Venezuela w1, echo=FALSE}
#label(t1066_ds_Ven_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_Ven_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_Ven_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_Ven_w1
save(cog_verb, file = "../RData/Ven_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign Venezuela w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_cog_verb','10-66.1066-Venezuela-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_Venezuela_w2_cog_verb <- opal.execute(o,'s1066_Venezuela_w2_cog_verb')
```

```{r local Venezuela w2, echo=FALSE}
vari <- s1066_Venezuela_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_Venezuela_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Venezuela w2}
#cog_verb_c
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_cog_verb$id)
t1066_ds_Ven_w2$cog_verb_c <- recode(s1066_Venezuela_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_Ven_w2$cog_verb_c <- labelled(t1066_ds_Ven_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_Ven_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_Ven_w2$cog_verb <- car::recode(t1066_ds_Ven_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_Ven_w2$cog_verb <- labelled(t1066_ds_Ven_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=FALSE}
vari <- t1066_ds_Ven_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_Ven_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_Ven_w2[[2]])<=Q), sum(na.omit(t1066_ds_Ven_w2[[2]])>Q & na.omit(t1066_ds_Ven_w2[[2]])<900))
Dicotomic <- table(t1066_ds_Ven_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","12:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Venezuela w2, echo=FALSE}
#label(t1066_ds_Ven_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_Ven_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_Ven_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_Ven_w2
save(cog_verb, file = "../RData/Ven_w2/cog_verb.RData")
```



## Urban Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign UrbanPeru w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_cog_verb','10-66.1066-UrbanPeru-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_UrbanPeru_w1_cog_verb <- opal.execute(o,'s1066_UrbanPeru_w1_cog_verb')
```

```{r local UrbanPeru w1, echo=FALSE}
vari <- s1066_UrbanPeru_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanPeru_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanPeru w1}
#cog_verb_c
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_cog_verb$id)
t1066_ds_UP_w1$cog_verb_c <- recode(s1066_UrbanPeru_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_UP_w1$cog_verb_c <- labelled(t1066_ds_UP_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UP_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UP_w1$cog_verb <- car::recode(t1066_ds_UP_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_UP_w1$cog_verb <- labelled(t1066_ds_UP_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=FALSE}
vari <- t1066_ds_UP_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UP_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UP_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UP_w1[[2]])<=Q), sum(na.omit(t1066_ds_UP_w1[[2]])>Q & na.omit(t1066_ds_UP_w1[[2]])<900))
Dicotomic <- table(t1066_ds_UP_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:13->0","14:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanPeru w1, echo=FALSE}
#label(t1066_ds_UP_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_UP_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UP_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UP_w1
save(cog_verb, file = "../RData/UP_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign UrbanPeru w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_cog_verb','10-66.1066-UrbanPeru-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_UrbanPeru_w2_cog_verb <- opal.execute(o,'s1066_UrbanPeru_w2_cog_verb')
```

```{r local UrbanPeru w2, echo=FALSE}
vari <- s1066_UrbanPeru_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanPeru_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanPeru w2}
#cog_verb_c
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_cog_verb$id)
t1066_ds_UP_w2$cog_verb_c <- recode(s1066_UrbanPeru_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_UP_w2$cog_verb_c <- labelled(t1066_ds_UP_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UP_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UP_w2$cog_verb <- car::recode(t1066_ds_UP_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_UP_w2$cog_verb <- labelled(t1066_ds_UP_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=FALSE}
vari <- t1066_ds_UP_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UP_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UP_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UP_w2[[2]])<=Q), sum(na.omit(t1066_ds_UP_w2[[2]])>Q & na.omit(t1066_ds_UP_w2[[2]])<900))
Dicotomic <- table(t1066_ds_UP_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:13->0","14:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanPeru w2, echo=FALSE}
#label(t1066_ds_UP_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_UP_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UP_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UP_w2
save(cog_verb, file = "../RData/UP_w2/cog_verb.RData")
```



## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign RuralPeru w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_cog_verb','10-66.1066-RuralPeru-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_RuralPeru_w1_cog_verb <- opal.execute(o,'s1066_RuralPeru_w1_cog_verb')
```

```{r local RuralPeru w1, echo=FALSE}
vari <-s1066_RuralPeru_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralPeru_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo RuralPeru w1}
#cog_verb_c
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_cog_verb$id)
t1066_ds_RP_w1$cog_verb_c <- recode(s1066_RuralPeru_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_RP_w1$cog_verb_c <- labelled(t1066_ds_RP_w1$cog_verb_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RP_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RP_w1$cog_verb <- car::recode(t1066_ds_RP_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RP_w1$cog_verb <- labelled(t1066_ds_RP_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=FALSE}
vari <- t1066_ds_RP_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RP_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RP_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RP_w1[[2]])<=Q), sum(na.omit(t1066_ds_RP_w1[[2]])>Q & na.omit(t1066_ds_RP_w1[[2]])<900))
Dicotomic <- table(t1066_ds_RP_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:12->0","13:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralPeru w1, echo=FALSE}
#label(t1066_ds_RP_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_RP_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RP_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RP_w1
save(cog_verb, file = "../RData/RP_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings


```{r assign RuralPeru w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_cog_verb','10-66.1066-RuralPeru-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_RuralPeru_w2_cog_verb <- opal.execute(o,'s1066_RuralPeru_w2_cog_verb')
```

```{r local RuralPeru w2, echo=FALSE}
vari <- s1066_RuralPeru_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralPeru_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo RuralPeru w2}
#cog_verb_c
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_cog_verb$id)
t1066_ds_RP_w2$cog_verb_c <- recode(s1066_RuralPeru_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_RP_w2$cog_verb_c <- labelled(t1066_ds_RP_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RP_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RP_w2$cog_verb <- car::recode(t1066_ds_RP_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RP_w2$cog_verb <- labelled(t1066_ds_RP_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=FALSE}
vari <- t1066_ds_RP_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RP_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RP_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RP_w2[[2]])<=Q), sum(na.omit(t1066_ds_RP_w2[[2]])>Q & na.omit(t1066_ds_RP_w2[[2]])<900))
Dicotomic <- table(t1066_ds_RP_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralPeru w2, echo=FALSE}
#label(t1066_ds_RP_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_RP_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RP_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RP_w2
save(cog_verb, file = "../RData/RP_w2/cog_verb.RData")
```



## Urban Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign UrbanMexico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_cog_verb','10-66.1066-UrbanMexico-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_UrbanMexico_w1_cog_verb <- opal.execute(o,'s1066_UrbanMexico_w1_cog_verb')
```

```{r local UrbanMexico w1, echo=FALSE}
vari <- s1066_UrbanMexico_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanMexico_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanMexico w1}
#cog_verb_c
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_cog_verb$id)
t1066_ds_UM_w1$cog_verb_c <- recode(s1066_UrbanMexico_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_UM_w1$cog_verb_c <- labelled(t1066_ds_UM_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UM_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UM_w1$cog_verb <- car::recode(t1066_ds_UM_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_UM_w1$cog_verb <- labelled(t1066_ds_UM_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=FALSE}
vari <- t1066_ds_UM_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UM_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UM_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UM_w1[[2]])<=Q), sum(na.omit(t1066_ds_UM_w1[[2]])>Q & na.omit(t1066_ds_UM_w1[[2]])<900))
Dicotomic <- table(t1066_ds_UM_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","12:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanMexico w1, echo=FALSE}
#label(t1066_ds_UM_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_UM_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UM_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UM_w1
save(cog_verb, file = "../RData/UM_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings
   + `NA`

```{r assign UrbanMexico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_cog_verb','10-66.1066-UrbanMexico-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_UrbanMexico_w2_cog_verb <- opal.execute(o,'s1066_UrbanMexico_w2_cog_verb')
```

```{r local UrbanMexico w2, echo=FALSE}
vari <- s1066_UrbanMexico_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_UrbanMexico_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo UrbanMexico w2}
#cog_verb_c
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_cog_verb$id)
t1066_ds_UM_w2$cog_verb_c <- recode(s1066_UrbanMexico_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_UM_w2$cog_verb_c <- labelled(t1066_ds_UM_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_UM_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_UM_w2$cog_verb <- car::recode(t1066_ds_UM_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_UM_w2$cog_verb <- labelled(t1066_ds_UM_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=FALSE}
vari <- t1066_ds_UM_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_UM_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_UM_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_UM_w2[[2]])<=Q), sum(na.omit(t1066_ds_UM_w2[[2]])>Q & na.omit(t1066_ds_UM_w2[[2]])<900), sum(na.omit(t1066_ds_UM_w2[[2]])==999))
Dicotomic <- table(t1066_ds_UM_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","12:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL UrbanMexico w2, echo=FALSE}
#label(t1066_ds_UM_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_UM_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_UM_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_UM_w2
save(cog_verb, file = "../RData/UM_w2/cog_verb.RData")
```




## Rural Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign RuralMexico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_cog_verb','10-66.1066-RuralMexico-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_RuralMexico_w1_cog_verb <- opal.execute(o,'s1066_RuralMexico_w1_cog_verb')
```

```{r local RuralMexico w1, echo=FALSE}
s1066_RuralMexico_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralMexico_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo RuralMexico w1}
#cog_verb_c
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_cog_verb$id)
t1066_ds_RM_w1$cog_verb_c <- recode(s1066_RuralMexico_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_RM_w1$cog_verb_c <- labelled(t1066_ds_RM_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RM_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RM_w1$cog_verb <- car::recode(t1066_ds_RM_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RM_w1$cog_verb <- labelled(t1066_ds_RM_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=FALSE}
vari <- t1066_ds_RM_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RM_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RM_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RM_w1[[2]])<=Q), sum(na.omit(t1066_ds_RM_w1[[2]])>Q & na.omit(t1066_ds_RM_w1[[2]])<900))
Dicotomic <- table(t1066_ds_RM_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralMexico w1, echo=FALSE}
#label(t1066_ds_RM_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_RM_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RM_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RM_w1
save(cog_verb, file = "../RData/RM_w1/cog_verb.RData")
```



## Rural Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings
   + `NA`

```{r assign RuralMexico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_cog_verb','10-66.1066-RuralMexico-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_RuralMexico_w2_cog_verb <- opal.execute(o,'s1066_RuralMexico_w2_cog_verb')
```

```{r local RuralMexico w2, echo=FALSE}
vari <- s1066_RuralMexico_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_RuralMexico_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**


```{r harmo RuralMexico w2}
#cog_verb_c
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_cog_verb$id)
t1066_ds_RM_w2$cog_verb_c <- car::recode(s1066_RuralMexico_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_RM_w2$cog_verb_c <- labelled(t1066_ds_RM_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_RM_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_RM_w2$cog_verb <- car::recode(t1066_ds_RM_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_RM_w2$cog_verb <- labelled(t1066_ds_RM_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=FALSE}
vari <- t1066_ds_RM_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_RM_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_RM_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_RM_w2[[2]])<=Q), sum(na.omit(t1066_ds_RM_w2[[2]])>Q & na.omit(t1066_ds_RM_w2[[2]])<900), sum(na.omit(t1066_ds_RM_w2[[2]])==999))
Dicotomic <- table(t1066_ds_RM_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:9->0","10:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL RuralMexico w2, echo=FALSE}
#label(t1066_ds_RM_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_RM_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_RM_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_RM_w2
save(cog_verb, file = "../RData/RM_w2/cog_verb.RData")
```




## Puerto Rico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings

```{r assign PuertoRico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_cog_verb','10-66.1066-PuertoRico-Baseline', variables=list('ANIMALS'), missings = TRUE)
s1066_PuertoRico_w1_cog_verb <- opal.execute(o,'s1066_PuertoRico_w1_cog_verb')
```

```{r local PuertoRico w1, echo=FALSE}
vari <- s1066_PuertoRico_w1_cog_verb$ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_PuertoRico_w1_cog_verb, aes(x=factor(ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo PuertoRico w1}
#cog_verb_c
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_cog_verb$id)
t1066_ds_PR_w1$cog_verb_c <- recode(s1066_PuertoRico_w1_cog_verb$ANIMALS, "NA=999")
t1066_ds_PR_w1$cog_verb_c <- labelled(t1066_ds_PR_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_PR_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_PR_w1$cog_verb <- car::recode(t1066_ds_PR_w1[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_PR_w1$cog_verb <- labelled(t1066_ds_PR_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=FALSE}
vari <- t1066_ds_PR_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_PR_w1, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_PR_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_PR_w1[[2]])<=Q), sum(na.omit(t1066_ds_PR_w1[[2]])>Q & na.omit(t1066_ds_PR_w1[[2]])<900))
Dicotomic <- table(t1066_ds_PR_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:10->0","11:160->1") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL PuertoRico w1, echo=FALSE}
#label(t1066_ds_PR_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')

label(t1066_ds_PR_w1$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_PR_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_PR_w1
save(cog_verb, file = "../RData/PR_w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_ANIMALS`
* Label: `verbal fluency - CERAD animal naming`
* Categories:
   + `Continuous Variable 0 to Maximum`
* Missings
   + `NA`

```{r assign PuertoRico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_cog_verb','10-66.1066-PuertoRico-Followup', variables=list('f_ANIMALS'), missings = TRUE)
s1066_PuertoRico_w2_cog_verb <- opal.execute(o,'s1066_PuertoRico_w2_cog_verb')
```

```{r local PuertoRico w2, echo=FALSE}
vari <- s1066_PuertoRico_w2_cog_verb$f_ANIMALS
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(s1066_PuertoRico_w2_cog_verb, aes(x=factor(f_ANIMALS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo PuertoRico w2}
#cog_verb_c
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_cog_verb$id)
t1066_ds_PR_w2$cog_verb_c <- recode(s1066_PuertoRico_w2_cog_verb$f_ANIMALS, "NA=999")
t1066_ds_PR_w2$cog_verb_c <- labelled(t1066_ds_PR_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(t1066_ds_PR_w2$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

t1066_ds_PR_w2$cog_verb <- car::recode(t1066_ds_PR_w2[[2]], "0:Q=0; (Q+1):900=1")
t1066_ds_PR_w2$cog_verb <- labelled(t1066_ds_PR_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=FALSE}
vari <- t1066_ds_PR_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(t1066_ds_PR_w2, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- t1066_ds_PR_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=FALSE}
Continous <- c(sum(na.omit(t1066_ds_PR_w2[[2]])<=Q), sum(na.omit(t1066_ds_PR_w2[[2]])>Q & na.omit(t1066_ds_PR_w2[[2]])<900), sum(na.omit(t1066_ds_PR_w2[[2]])==999))
Dicotomic <- table(t1066_ds_PR_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:9->0","10:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL PuertoRico w2, echo=FALSE}
#label(t1066_ds_PR_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')

label(t1066_ds_PR_w2$cog_verb_c) <- ds_label_cog_verb_c
label(t1066_ds_PR_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- t1066_ds_PR_w2
save(cog_verb, file = "../RData/PR_w2/cog_verb.RData")
```




# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
