---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/srhDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/srhDS.R')
```


# Data process

## Cuba

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-Cuba-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign Cuba w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w1_srh','10-66.1066-Cuba-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_Cuba_w1_srh <- opal.execute(o,'s1066_Cuba_w1_srh')
```

```{r local Cuba w1, echo=FALSE}
vari <- s1066_Cuba_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo Cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_srh$id)
t1066_ds_cuba_w1$srh <- car::recode(s1066_Cuba_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_cuba_w1$srh <- labelled(t1066_ds_cuba_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1, echo=FALSE}
vari <- t1066_ds_cuba_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1, echo=FALSE}
AfterH <- table(t1066_ds_cuba_w1$srh)
X<-table(s1066_Cuba_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_Cuba_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL Cuba w1, echo=FALSE}
label(t1066_ds_cuba_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_cuba_w1
save(srh, file = "../RData/cuba_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$srh <- car::recode(t1066_m_ds_cuba_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-Cuba-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign Cuba w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Cuba_w2_srh','10-66.1066-Cuba-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_Cuba_w2_srh <- opal.execute(o,'s1066_Cuba_w2_srh')
```

```{r local Cuba w2, echo=FALSE}
vari <- s1066_Cuba_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo Cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_srh$id)
t1066_ds_cuba_w2$srh <- car::recode(s1066_Cuba_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_cuba_w2$srh <- labelled(t1066_ds_cuba_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2, echo=FALSE}
vari <- t1066_ds_cuba_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2, echo=FALSE}
AfterH <- table(t1066_ds_cuba_w2$srh)
X<-table(s1066_Cuba_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_Cuba_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL Cuba w2, echo=FALSE}
label(t1066_ds_cuba_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_cuba_w2
save(srh, file = "../RData/cuba_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$srh <- car::recode(t1066_m_ds_cuba_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```




## India

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-India-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign India w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_India_w1_srh','10-66.1066-India-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_India_w1_srh <- opal.execute(o,'s1066_India_w1_srh')
```

```{r local India w1, echo=FALSE}
vari <- s1066_India_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_India_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_srh$id)
t1066_ds_india_w1$srh <- car::recode(s1066_India_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_india_w1$srh <- labelled(t1066_ds_india_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=FALSE}
vari <- t1066_ds_india_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=FALSE}
AfterH <- table(t1066_ds_india_w1$srh)
X<-table(s1066_India_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_India_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL India w1, echo=FALSE}
label(t1066_ds_india_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_india_w1
save(srh, file = "../RData/india_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$srh <- car::recode(t1066_m_ds_india_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```



## Urban China

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanChina-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanChina w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_srh','10-66.1066-UrbanChina-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_UrbanChina_w1_srh <- opal.execute(o,'s1066_UrbanChina_w1_srh')
```

```{r local UrbanChina w1, echo=FALSE}
vari <- s1066_UrbanChina_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_srh$id)
t1066_ds_UCh_w1$srh <- car::recode(s1066_UrbanChina_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UCh_w1$srh <- labelled(t1066_ds_UCh_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=FALSE}
vari <- t1066_ds_UCh_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=FALSE}
AfterH <- table(t1066_ds_UCh_w1$srh)
X<-table(s1066_UrbanChina_w1_srh$PDASALL1)
#nas<-sum(is.na(s1066_UrbanChina_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL UrbanChina w1, echo=FALSE}
label(t1066_ds_UCh_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UCh_w1
save(srh, file = "../RData/UCh_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$srh <- car::recode(t1066_m_ds_UCh_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanChina-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign UrbanChina w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_srh','10-66.1066-UrbanChina-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_UrbanChina_w2_srh <- opal.execute(o,'s1066_UrbanChina_w2_srh')
```

```{r local UrbanChina w2, echo=FALSE}
vari <- s1066_UrbanChina_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_srh$id)
t1066_ds_UCh_w2$srh <- car::recode(s1066_UrbanChina_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UCh_w2$srh <- labelled(t1066_ds_UCh_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=FALSE}
vari <- t1066_ds_UCh_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=FALSE}
AfterH <- table(t1066_ds_UCh_w2$srh)
X<-table(s1066_UrbanChina_w2_srh$f_PDASALL1)
#nas<-sum(is.na(s1066_UrbanChina_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL UrbanChina w2, echo=FALSE}
label(t1066_ds_UCh_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UCh_w2
save(srh, file = "../RData/UCh_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$srh <- car::recode(t1066_m_ds_UCh_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```




## Rural China

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralChina-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralChina w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_srh','10-66.1066-RuralChina-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_RuralChina_w1_srh <- opal.execute(o,'s1066_RuralChina_w1_srh')
```

```{r local RuralChina w1, echo=FALSE}
vari <- s1066_RuralChina_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_srh$id)
t1066_ds_RCh_w1$srh <- car::recode(s1066_RuralChina_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RCh_w1$srh <- labelled(t1066_ds_RCh_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=FALSE}
vari <- t1066_ds_RCh_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=FALSE}
AfterH <- table(t1066_ds_RCh_w1$srh)
X<-table(s1066_RuralChina_w1_srh$PDASALL1)
#nas<-sum(is.na(s1066_RuralChina_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL RuralChina w1, echo=FALSE}
label(t1066_ds_RCh_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RCh_w1
save(srh, file = "../RData/RCh_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$srh <- car::recode(t1066_m_ds_RCh_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralChina-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign RuralChina w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_srh','10-66.1066-RuralChina-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_RuralChina_w2_srh <- opal.execute(o,'s1066_RuralChina_w2_srh')
```

```{r local RuralChina w2, echo=FALSE}
vari <- s1066_RuralChina_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_srh$id)
t1066_ds_RCh_w2$srh <- car::recode(s1066_RuralChina_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RCh_w2$srh <- labelled(t1066_ds_RCh_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=FALSE}
vari <- t1066_ds_RCh_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=FALSE}
AfterH <- table(t1066_ds_RCh_w2$srh)
X<-table(s1066_RuralChina_w2_srh$f_PDASALL1)
#nas<-sum(is.na(s1066_RuralChina_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL RuralChina w2, echo=FALSE}
label(t1066_ds_RCh_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RCh_w2
save(srh, file = "../RData/RCh_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$srh <- car::recode(t1066_m_ds_RCh_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```



## Dominican Republic

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-DominicanRepublic-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign DominicanRepublic w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_srh','10-66.1066-DominicanRepublic-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_DominicanRepublic_w1_srh <- opal.execute(o,'s1066_DominicanRepublic_w1_srh')
```

```{r local DominicanRepublic w1, echo=FALSE}
vari <- s1066_DominicanRepublic_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_srh$id)
t1066_ds_DR_w1$srh <- car::recode(s1066_DominicanRepublic_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_DR_w1$srh <- labelled(t1066_ds_DR_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=FALSE}
vari <- t1066_ds_DR_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=FALSE}
AfterH <- table(t1066_ds_DR_w1$srh)
X<-table(s1066_DominicanRepublic_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_DominicanRepublic_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL DominicanRepublic w1, echo=FALSE}
label(t1066_ds_DR_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_DR_w1
save(srh, file = "../RData/DR_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$srh <- car::recode(t1066_m_ds_DR_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-DominicanRepublic-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign DominicanRepublic w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_srh','10-66.1066-DominicanRepublic-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_DominicanRepublic_w2_srh <- opal.execute(o,'s1066_DominicanRepublic_w2_srh')
```

```{r local DominicanRepublic w2, echo=FALSE}
vari <- s1066_DominicanRepublic_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_srh$id)
t1066_ds_DR_w2$srh <- car::recode(s1066_DominicanRepublic_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_DR_w2$srh <- labelled(t1066_ds_DR_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=FALSE}
vari <- t1066_ds_DR_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=FALSE}
AfterH <- table(t1066_ds_DR_w2$srh)
X<-table(s1066_DominicanRepublic_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_DominicanRepublic_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL DominicanRepublic w2, echo=FALSE}
label(t1066_ds_DR_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_DR_w2
save(srh, file = "../RData/DR_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$srh <- car::recode(t1066_m_ds_DR_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```




## Venezuela

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-Venezuela-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign Venezuela w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_srh','10-66.1066-Venezuela-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_Venezuela_w1_srh <- opal.execute(o,'s1066_Venezuela_w1_srh')
```

```{r local Venezuela w1, echo=FALSE}
vari <- s1066_Venezuela_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_srh$id)
t1066_ds_Ven_w1$srh <- car::recode(s1066_Venezuela_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_Ven_w1$srh <- labelled(t1066_ds_Ven_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=FALSE}
vari <- t1066_ds_Ven_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=FALSE}
AfterH <- table(t1066_ds_Ven_w1$srh)
X<-table(s1066_Venezuela_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_Venezuela_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL Venezuela w1, echo=FALSE}
label(t1066_ds_Ven_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_Ven_w1
save(srh, file = "../RData/Ven_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$srh <- car::recode(t1066_m_ds_Ven_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-Venezuela-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign Venezuela w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_srh','10-66.1066-Venezuela-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_Venezuela_w2_srh <- opal.execute(o,'s1066_Venezuela_w2_srh')
```

```{r local Venezuela w2, echo=FALSE}
vari <- s1066_Venezuela_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_srh$id)
t1066_ds_Ven_w2$srh <- car::recode(s1066_Venezuela_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_Ven_w2$srh <- labelled(t1066_ds_Ven_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=FALSE}
vari <- t1066_ds_Ven_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=FALSE}
AfterH <- table(t1066_ds_Ven_w2$srh)
X<-table(s1066_Venezuela_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_Venezuela_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL Venezuela w2, echo=FALSE}
label(t1066_ds_Ven_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_Ven_w2
save(srh, file = "../RData/Ven_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$srh <- car::recode(t1066_m_ds_Ven_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```




## Urban Peru

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanPeru-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanPeru w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_srh','10-66.1066-UrbanPeru-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_UrbanPeru_w1_srh <- opal.execute(o,'s1066_UrbanPeru_w1_srh')
```

```{r local UrbanPeru w1, echo=FALSE}
vari <- s1066_UrbanPeru_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_srh$id)
t1066_ds_UP_w1$srh <- car::recode(s1066_UrbanPeru_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UP_w1$srh <- labelled(t1066_ds_UP_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=FALSE}
vari <- t1066_ds_UP_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=FALSE}
AfterH <- table(t1066_ds_UP_w1$srh)
X<-table(s1066_UrbanPeru_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_UrbanPeru_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL UrbanPeru w1, echo=FALSE}
label(t1066_ds_UP_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UP_w1
save(srh, file = "../RData/UP_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$srh <- car::recode(t1066_m_ds_UP_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanPeru-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign UrbanPeru w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_srh','10-66.1066-UrbanPeru-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_UrbanPeru_w2_srh <- opal.execute(o,'s1066_UrbanPeru_w2_srh')
```

```{r local UrbanPeru w2, echo=FALSE}
vari <- s1066_UrbanPeru_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_srh$id)
t1066_ds_UP_w2$srh <- car::recode(s1066_UrbanPeru_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UP_w2$srh <- labelled(t1066_ds_UP_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=FALSE}
vari <- t1066_ds_UP_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=FALSE}
AfterH <- table(t1066_ds_UP_w2$srh)
X<-table(s1066_UrbanPeru_w2_srh$f_PDASALL1)
#nas<-sum(is.na(s1066_UrbanPeru_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL UrbanPeru w2, echo=FALSE}
label(t1066_ds_UP_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UP_w2
save(srh, file = "../RData/UP_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$srh <- car::recode(t1066_m_ds_UP_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```




## Rural Peru

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralPeru-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralPeru w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_srh','10-66.1066-RuralPeru-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_RuralPeru_w1_srh <- opal.execute(o,'s1066_RuralPeru_w1_srh')
```

```{r local RuralPeru w1, echo=FALSE}
vari <- s1066_RuralPeru_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_srh$id)
t1066_ds_RP_w1$srh <- car::recode(s1066_RuralPeru_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RP_w1$srh <- labelled(t1066_ds_RP_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=FALSE}
vari <- t1066_ds_RP_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=FALSE}
AfterH <- table(t1066_ds_RP_w1$srh)
X<-table(s1066_RuralPeru_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_RuralPeru_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL RuralPeru w1, echo=FALSE}
label(t1066_ds_RP_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RP_w1
save(srh, file = "../RData/RP_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$srh <- car::recode(t1066_m_ds_RP_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralPeru-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign RuralPeru w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_srh','10-66.1066-RuralPeru-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_RuralPeru_w2_srh <- opal.execute(o,'s1066_RuralPeru_w2_srh')
```

```{r local RuralPeru w2, echo=FALSE}
vari <- s1066_RuralPeru_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_srh$id)
t1066_ds_RP_w2$srh <- car::recode(s1066_RuralPeru_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RP_w2$srh <- labelled(t1066_ds_RP_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=FALSE}
vari <- t1066_ds_RP_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=FALSE}
AfterH <- table(t1066_ds_RP_w2$srh)
X<-table(s1066_RuralPeru_w2_srh$f_PDASALL1)
#nas<-sum(is.na(s1066_RuralPeru_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL RuralPeru w2, echo=FALSE}
label(t1066_ds_RP_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RP_w2
save(srh, file = "../RData/RP_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$srh <- car::recode(t1066_m_ds_RP_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```




## Urban Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanMexico-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign UrbanMexico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_srh','10-66.1066-UrbanMexico-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_UrbanMexico_w1_srh <- opal.execute(o,'s1066_UrbanMexico_w1_srh')
```

```{r local UrbanMexico w1, echo=FALSE}
vari <- s1066_UrbanMexico_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_srh$id)
t1066_ds_UM_w1$srh <- car::recode(s1066_UrbanMexico_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UM_w1$srh <- labelled(t1066_ds_UM_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=FALSE}
vari <- t1066_ds_UM_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=FALSE}
AfterH <- table(t1066_ds_UM_w1$srh)
X<-table(s1066_UrbanMexico_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_UrbanMexico_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL UrbanMexico w1, echo=FALSE}
label(t1066_ds_UM_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UM_w1
save(srh, file = "../RData/UM_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$srh <- car::recode(t1066_m_ds_UM_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-UrbanMexico-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign UrbanMexico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_srh','10-66.1066-UrbanMexico-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_UrbanMexico_w2_srh <- opal.execute(o,'s1066_UrbanMexico_w2_srh')
```

```{r local UrbanMexico w2, echo=FALSE}
vari <- s1066_UrbanMexico_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_srh$id)
t1066_ds_UM_w2$srh <- car::recode(s1066_UrbanMexico_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_UM_w2$srh <- labelled(t1066_ds_UM_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=FALSE}
vari <- t1066_ds_UM_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=FALSE}
AfterH <- table(t1066_ds_UM_w2$srh)
X<-table(s1066_UrbanMexico_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_UrbanMexico_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL UrbanMexico w2, echo=FALSE}
label(t1066_ds_UM_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_UM_w2
save(srh, file = "../RData/UM_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$srh <- car::recode(t1066_m_ds_UM_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```



## Rural Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralMexico-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign RuralMexico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_srh','10-66.1066-RuralMexico-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_RuralMexico_w1_srh <- opal.execute(o,'s1066_RuralMexico_w1_srh')
```

```{r local RuralMexico w1, echo=FALSE}
vari <- s1066_RuralMexico_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`

**R script:**

```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_srh$id)
t1066_ds_RM_w1$srh <- car::recode(s1066_RuralMexico_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RM_w1$srh <- labelled(t1066_ds_RM_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=FALSE}
vari <- t1066_ds_RM_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=FALSE}
AfterH <- table(t1066_ds_RM_w1$srh)
X<-table(s1066_RuralMexico_w1_srh$PDASALL1)
#nas<-sum(is.na(s1066_RuralMexico_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3")
kable(C)
```

```{r importOPAL RuralMexico w1, echo=FALSE}
label(t1066_ds_RM_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RM_w1
save(srh, file = "../RData/RM_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$srh <- car::recode(t1066_m_ds_RM_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-RuralMexico-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign RuralMexico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_srh','10-66.1066-RuralMexico-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_RuralMexico_w2_srh <- opal.execute(o,'s1066_RuralMexico_w2_srh')
```

```{r local RuralMexico w2, echo=FALSE}
vari <- s1066_RuralMexico_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_srh$id)
t1066_ds_RM_w2$srh <- car::recode(s1066_RuralMexico_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_RM_w2$srh <- labelled(t1066_ds_RM_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=FALSE}
vari <- t1066_ds_RM_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=FALSE}
AfterH <- table(t1066_ds_RM_w2$srh)
X<-table(s1066_RuralMexico_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_RuralMexico_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL RuralMexico w2, echo=FALSE}
label(t1066_ds_RM_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_RM_w2
save(srh, file = "../RData/RM_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$srh <- car::recode(t1066_m_ds_RM_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```




## Puerto Rico

### Wave 1 

#### Study-specific variable description




| **Name** | `PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-PuertoRico-Baseline`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |









```{r assign PuertoRico w1, echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_srh','10-66.1066-PuertoRico-Baseline', variables=list('PDASALL1'), missings = TRUE)
s1066_PuertoRico_w1_srh <- opal.execute(o,'s1066_PuertoRico_w1_srh')
```

```{r local PuertoRico w1, echo=FALSE}
vari <- s1066_PuertoRico_w1_srh$PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w1_srh, aes(x=factor(PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_srh$id)
t1066_ds_PR_w1$srh <- car::recode(s1066_PuertoRico_w1_srh$PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_PR_w1$srh <- labelled(t1066_ds_PR_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=FALSE}
vari <- t1066_ds_PR_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=FALSE}
AfterH <- table(t1066_ds_PR_w1$srh)
X<-table(s1066_PuertoRico_w1_srh$PDASALL1)
nas<-sum(is.na(s1066_PuertoRico_w1_srh$PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL PuertoRico w1, echo=FALSE}
label(t1066_ds_PR_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_PR_w1
save(srh, file = "../RData/PR_w1/srh.RData")
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$srh <- car::recode(t1066_m_ds_PR_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PDASALL1`|
|-|-|
| **Label** | `self rated health in past 30 days`|
| **Table name** |`1066-PuertoRico-Followup`|
| **Categories** |`0 = Very good`<br/>`1 = Good`<br/>`2 = Moderate`<br/>`3 = Bad`<br/>`4 = Very bad`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign PuertoRico w2, echo=FALSE}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_srh','10-66.1066-PuertoRico-Followup', variables=list('f_PDASALL1'), missings = TRUE)
s1066_PuertoRico_w2_srh <- opal.execute(o,'s1066_PuertoRico_w2_srh')
```

```{r local PuertoRico w2, echo=FALSE}
vari <- s1066_PuertoRico_w2_srh$f_PDASALL1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w2_srh, aes(x=factor(f_PDASALL1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 1`
* `2 into 2`
* `3 into 3`
* `4 into 3`
* `NA into 999`

**R script:**

```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_srh$id)
t1066_ds_PR_w2$srh <- car::recode(s1066_PuertoRico_w2_srh$f_PDASALL1, "0='1'; 4='3';NA='999'")
t1066_ds_PR_w2$srh <- labelled(t1066_ds_PR_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=FALSE}
vari <- t1066_ds_PR_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=FALSE}
AfterH <- table(t1066_ds_PR_w2$srh)
X<-table(s1066_PuertoRico_w2_srh$f_PDASALL1)
nas<-sum(is.na(s1066_PuertoRico_w2_srh$f_PDASALL1))
BeforeH <-c(sum(X[1:2]),X[3],sum(X[4:5]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->1","2->2","3,4->3","NA->999")
kable(C)
```

```{r importOPAL PuertoRico w2, echo=FALSE}
label(t1066_ds_PR_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- t1066_ds_PR_w2
save(srh, file = "../RData/PR_w2/srh.RData")
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$srh <- car::recode(t1066_m_ds_PR_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:




```{r helpfunctions, echo=F}

labelling <- function(l.hds, m.hds, vbl_name = hd_vbl, ds_label = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
    aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds, m.hds, lnames, vbl_name = hd_vbl){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],ds_label = ds_label_all)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]], ds_label = ds_label_all)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}


```









# Quality estimation

No comments. 




```{r closeRsession, echo=FALSE, echo=FALSE}
opal.logout(o)
```
