---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```


# Data process

## Cuba

### Wave 1

#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-Cuba-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |

```{r assign_cuba1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-Cuba-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_cuba1, echo=FALSE}
vbl <- t1066_wb$Q1561
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = label(vbl)) 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_wb$id)
t1066_ds_cuba_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_cuba1, echo=FALSE}
vari <- t1066_ds_cuba_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_cuba1, echo=FALSE}
evaluative_wb <- t1066_ds_cuba_w1
save(evaluative_wb, file = "../RData/cuba_w1/evaluative_wb.RData")
```


### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-Cuba-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_cuba2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-Cuba-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_cuba2, echo=FALSE}
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`


**R script:**

```{r harmo_cuba2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_wb$id)
t1066_ds_cuba_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_cuba2, echo=FALSE}
vari <- t1066_ds_cuba_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL_cuba_w2, echo=FALSE}
evaluative_wb <- t1066_ds_cuba_w2
save(evaluative_wb, file = "../RData/cuba_w2/evaluative_wb.RData")
```





## India

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-India-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign_india1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-India-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')

```

```{r local_india1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`


**R script:**

```{r harmo_india1}
t1066_ds_india_w1 <- tibble(id=t1066_wb$id)
t1066_ds_india_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_india1, echo=FALSE}
vari <- t1066_ds_india_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india1, echo=FALSE}
```

```{r importOPAL_india1, echo=FALSE}
evaluative_wb <- t1066_ds_india_w1
save(evaluative_wb, file = "../RData/india_w1/evaluative_wb.RData")
```


## Urban China

### Wave 1

#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanChina-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign__UCh1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanChina-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_UCh1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_UCh1, echo=FALSE}
t1066_ds_UCh_w1 <- tibble(id=t1066_wb$id)
t1066_ds_UCh_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_UCh1, echo=FALSE}
vari <- t1066_ds_UCh_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_UCh1, echo=FALSE}
evaluative_wb <- t1066_ds_UCh_w1
save(evaluative_wb, file = "../RData/UCh_w1/evaluative_wb.RData")
```





### Wave 2 

#### Study-specific variable description

 
| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanChina-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_UCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanChina-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')

```

```{r local_UCh2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_UCh2, echo=TRUE} 
t1066_ds_UCh_w2 <- tibble(id=t1066_wb$id)
t1066_ds_UCh_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_UCh2, echo=FALSE} 
vari <- t1066_ds_UCh_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=FALSE} 
```

 
```{r importOPAL_UCh2, echo=FALSE}
evaluative_wb <- t1066_ds_UCh_w2
save(evaluative_wb, file = "../RData/UCh_w2/evaluative_wb.RData")
```


## Rural China

### Wave 1
#### Study-specific variable description


| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralChina-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |

```{r assign__RCh1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralChina-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_RCh1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`


**R script:**

```{r harmo_RCh1}
t1066_ds_RCh_w1 <- tibble(id=t1066_wb$id)
t1066_ds_RCh_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_RCh1, echo=FALSE}
vari <- t1066_ds_RCh_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_RCh1, echo=FALSE}
evaluative_wb <- t1066_ds_RCh_w1
save(evaluative_wb, file = "../RData/RCh_w1/evaluative_wb.RData")
```




### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralChina-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_RCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralChina-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_RCh2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_RCh2, echo=TRUE} 
t1066_ds_RCh_w2 <- tibble(id=t1066_wb$id)
t1066_ds_RCh_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_RCh2, echo=FALSE} 
vari <- t1066_ds_RCh_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=FALSE} 
```

```{r importOPAL_RCh2, echo=FALSE}
evaluative_wb <- t1066_ds_RCh_w2
save(evaluative_wb, file = "../RData/RCh_w2/evaluative_wb.RData")
```


## Dominican Republic

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-DominicanRepublic-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |

```{r assign_DR1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_DR1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`


**R script:**

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_wb$id)
t1066_ds_DR_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_DR1, echo=FALSE}
vari <- t1066_ds_DR_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_DR1, echo=FALSE}
evaluative_wb <- t1066_ds_DR_w1
save(evaluative_wb, file = "../RData/DR_w1/evaluative_wb.RData")
```





### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-DominicanRepublic-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_DR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-DominicanRepublic-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_DR2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo_DR2, echo=TRUE} 
t1066_ds_DR_w2 <- tibble(id=t1066_wb$id)
t1066_ds_DR_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_DR2, echo=FALSE} 
vari <- t1066_ds_DR_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=FALSE} 
```

 
```{r importOPAL_DR2, echo=FALSE}
evaluative_wb <- t1066_ds_DR_w2
save(evaluative_wb, file = "../RData/DR_w2/evaluative_wb.RData")
```




## Venezuela

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-Venezuela-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign_V1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-Venezuela-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_V1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_V1}
t1066_ds_Ven_w1 <- tibble(id=t1066_wb$id)
t1066_ds_Ven_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_V1, echo=FALSE}
vari <- t1066_ds_Ven_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_V1, echo=FALSE}
evaluative_wb <- t1066_ds_Ven_w1
save(evaluative_wb, file = "../RData/Ven_w1/evaluative_wb.RData")
```






### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-Venezuela-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_V2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-Venezuela-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_V2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo_V2, echo=TRUE} 
t1066_ds_Ven_w2 <- tibble(id=t1066_wb$id)
t1066_ds_Ven_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_V2, echo=FALSE} 
vari <- t1066_ds_Ven_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=FALSE} 
```

 
```{r importOPAL_V2, echo=FALSE}
evaluative_wb <- t1066_ds_Ven_w2
save(evaluative_wb, file = "../RData/Ven_w2/evaluative_wb.RData")
```
 



## Urban Peru

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanPeru-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign__UP1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanPeru-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_UP1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_wb$id)
t1066_ds_UP_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_UP1, echo=FALSE}
vari <- t1066_ds_UP_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_UP1, echo=FALSE}
evaluative_wb <- t1066_ds_UP_w1
save(evaluative_wb, file = "../RData/UP_w1/evaluative_wb.RData")
```



### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanPeru-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_UP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanPeru-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_UP2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo_UP2, echo=TRUE} 
t1066_ds_UP_w2 <- tibble(id=t1066_wb$id)
t1066_ds_UP_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_UP2, echo=FALSE} 
vari <- t1066_ds_UP_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=FALSE} 
```

 
```{r importOPAL_UP_w2, echo=FALSE}
evaluative_wb <- t1066_ds_UP_w2
save(evaluative_wb, file = "../RData/UP_w2/evaluative_wb.RData")
```



## Rural Peru

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralPeru-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign_RP, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralPeru-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')

```

```{r local_RP, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_iRP}
t1066_ds_RP_w1 <- tibble(id=t1066_wb$id)
t1066_ds_RP_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_RP, echo=FALSE}
vari <- t1066_ds_RP_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_RP, echo=FALSE}
evaluative_wb <- t1066_ds_RP_w1
save(evaluative_wb, file = "../RData/RP_w1/evaluative_wb.RData")
```







### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralPeru-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_RP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralPeru-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_RP2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_RP2, echo=TRUE} 
t1066_ds_RP_w2 <- tibble(id=t1066_wb$id)
t1066_ds_RP_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_RP2, echo=FALSE} 
vari <- t1066_ds_RP_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=FALSE} 
```

```{r importOPALRP_w2, echo=FALSE}
evaluative_wb <- t1066_ds_RP_w2
save(evaluative_wb, file = "../RData/RP_w2/evaluative_wb.RData")
```








## Urban Mexico

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanMexico-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign_UM1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanMexico-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_UM1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_wb$id)
t1066_ds_UM_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_UM1, echo=FALSE}
vari <- t1066_ds_UM_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_UM1, echo=FALSE}
evaluative_wb <- t1066_ds_UM_w1
save(evaluative_wb, file = "../RData/UM_w1/evaluative_wb.RData")
```







### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-UrbanMexico-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |

```{r assign_UM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-UrbanMexico-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_UM2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_UM2, echo=TRUE} 
t1066_ds_UM_w2 <- tibble(id=t1066_wb$id)
t1066_ds_UM_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_UM2, echo=FALSE} 
vari <- t1066_ds_UM_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=FALSE} 
```

```{r importOPAL_UM_w2, echo=FALSE}
evaluative_wb <- t1066_ds_UM_w2
save(evaluative_wb, file = "../RData/UM_w2/evaluative_wb.RData")
```





## Rural Mexico

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralMexico-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `NA` |
| **Description** |  |


```{r assign_RM1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralMexico-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_RM1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `NA into 999`


**R script:**

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_wb$id)
t1066_ds_RM_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_RM1, echo=FALSE}
vari <- t1066_ds_RM_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_RM1, echo=FALSE}
evaluative_wb <- t1066_ds_RM_w1
save(evaluative_wb, file = "../RData/RM_w1/evaluative_wb.RData")
```







### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-RuralMexico-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |



```{r assign_RM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-RuralMexico-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_RM2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo_RM2, echo=TRUE} 
t1066_ds_RM_w2 <- tibble(id=t1066_wb$id)
t1066_ds_RM_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_RM2, echo=FALSE} 
vari <- t1066_ds_RM_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=FALSE} 
```

 
```{r importOPAL_RM_w2, echo=FALSE}
evaluative_wb <- t1066_ds_RM_w2
save(evaluative_wb, file = "../RData/RM_w2/evaluative_wb.RData")
```
 






## Puerto Rico

### Wave 1
#### Study-specific variable description

| **Name** | `Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-PuertoRico-Baseline` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |



```{r assign_PR1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-PuertoRico-Baseline',
                         variables=list('Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_PR1, echo=FALSE}
vbl <- t1066_wb$Q1561
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_wb$id)
t1066_ds_PR_w1$evaluative_wb <- car::recode(t1066_wb$Q1561, "0=2; 2=0; 3=0; 8 = 998; 9 = 996; NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_PR1, echo=FALSE}
vari <- t1066_ds_PR_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation

```{r importOPAL_PR1, echo=FALSE}
evaluative_wb <- t1066_ds_PR_w1
save(evaluative_wb, file = "../RData/PR_w1/evaluative_wb.RData")
```







### Wave 2

#### Study-specific variable description

| **Name** | `f_Q1561` | 
|-|-|
| **Label** | `156.1 How happy are you?` | 
| **Table name** | `1066-PuertoRico-Followup` | 
| **Categories** |`0 = very happy` <br/> `1 = fairly happy` <br/> `2 = not very happy` <br/> `3 = not happy at all` | 
| **Missing Values** | `8 = don't know` <br/> `9 = not applicable` |
| **Description** |  |


```{r assign_PR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_wb','10-66.1066-PuertoRico-Followup',
                         variables=list('f_Q1561'), missings = TRUE)
t1066_wb <- opal.execute(o,'t1066_wb')
```

```{r local_PR2, echo=FALSE} 
vbl <- t1066_wb$f_Q1561
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(t1066_wb, aes(x=factor(f_Q1561))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* keep `1 into 1`
* `2,3 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo_PR2, echo=TRUE} 
t1066_ds_PR_w2 <- tibble(id=t1066_wb$id)
t1066_ds_PR_w2$evaluative_wb <- car::recode(t1066_wb$f_Q1561, "0=2; 2=0; 3=0; 8=998; 9=996; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_PR2, echo=FALSE} 
vari <- t1066_ds_PR_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=FALSE} 
```

```{r importOPAL_PR_w2, echo=FALSE}
evaluative_wb <- t1066_ds_PR_w2
save(evaluative_wb, file = "../RData/PR_w2/evaluative_wb.RData")
```



# Quality estimation

<!--Not available except for India. -->



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
