---
title: "Sleep"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `sleep`
* Variable label: `Sleep`
* Variable description: `Sleeping problems.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## Cuba

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign Cuba w1, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w1_sleep','10-66.1066-Cuba-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local Cuba w1, echo=F}
s1066_Cuba_w1_sleep <- opal.execute(o,'s1066_Cuba_w1_sleep')
vari <- s1066_Cuba_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo Cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_sleep$id)
t1066_ds_cuba_w1$sleep <- car::recode(s1066_Cuba_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_cuba_w1$sleep <- labelled(t1066_ds_cuba_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1, echo=F}
vari <- t1066_ds_cuba_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$sleep)
X<-table(s1066_Cuba_w1_sleep$SLEEP)
nas<-length(s1066_Cuba_w1_sleep$SLEEP)-length(na.omit(s1066_Cuba_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL cuba w1, echo=FALSE}

label(t1066_ds_cuba_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_cuba_w1
save(sleep, file = "../RData/cuba_w1/sleep.RData")

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$sleep <- car::recode(t1066_m_ds_cuba_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-Cuba-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign Cuba w2, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w2_sleep','10-66.1066-Cuba-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local Cuba w2, echo=F}
s1066_Cuba_w2_sleep <- opal.execute(o,'s1066_Cuba_w2_sleep')
vari <- s1066_Cuba_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo Cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_sleep$id)
t1066_ds_cuba_w2$sleep <-  car::recode(s1066_Cuba_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_cuba_w2$sleep <- labelled(t1066_ds_cuba_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2, echo=F}
vari <- t1066_ds_cuba_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$sleep)
X<-table(s1066_Cuba_w2_sleep$f_SLEEP)
nas<-length(s1066_Cuba_w2_sleep$f_SLEEP)-length(na.omit(s1066_Cuba_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```





```{r importOPAL cuba w2, echo=FALSE}

label(t1066_ds_cuba_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_cuba_w2
save(sleep, file = "../RData/cuba_w2/sleep.RData")

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$sleep <- car::recode(t1066_m_ds_cuba_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```


## India

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-India-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 's1066_India_w1_sleep','10-66.1066-India-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local India w1, echo=F}
s1066_India_w1_sleep <- opal.execute(o,'s1066_India_w1_sleep')
vari <- s1066_India_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_India_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_sleep$id)
t1066_ds_india_w1$sleep <- car::recode(s1066_India_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_india_w1$sleep <- labelled(t1066_ds_india_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
vari <- t1066_ds_india_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$sleep)
X<-table(s1066_India_w1_sleep$SLEEP)
nas<-length(s1066_India_w1_sleep$SLEEP)-length(na.omit(s1066_India_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL india w1, echo=FALSE}

label(t1066_ds_india_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_india_w1
save(sleep, file = "../RData/india_w1/sleep.RData")

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$sleep <- car::recode(t1066_m_ds_india_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

Not found.

## UrbanChina

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_sleep','10-66.1066-UrbanChina-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local UrbanChina w1, echo=F}
s1066_UrbanChina_w1_sleep <- opal.execute(o,'s1066_UrbanChina_w1_sleep')
vari <- s1066_UrbanChina_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_sleep$id)
t1066_ds_UCh_w1$sleep <- car::recode(s1066_UrbanChina_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_UCh_w1$sleep <- labelled(t1066_ds_UCh_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
vari <- t1066_ds_UCh_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$sleep)
X<-table(s1066_UrbanChina_w1_sleep$SLEEP)
nas<-length(s1066_UrbanChina_w1_sleep$SLEEP)-length(na.omit(s1066_UrbanChina_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UCh w1, echo=FALSE}

label(t1066_ds_UCh_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UCh_w1
save(sleep, file = "../RData/UCh_w1/sleep.RData")

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$sleep <- car::recode(t1066_m_ds_UCh_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanChina-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign UrbanChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_sleep','10-66.1066-UrbanChina-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local UrbanChina w2, echo=F}
s1066_UrbanChina_w2_sleep <- opal.execute(o,'s1066_UrbanChina_w2_sleep')
vari <- s1066_UrbanChina_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_sleep$id)
t1066_ds_UCh_w2$sleep <-  car::recode(s1066_UrbanChina_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_UCh_w2$sleep <- labelled(t1066_ds_UCh_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=F}
vari <- t1066_ds_UCh_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$sleep)
X<-table(s1066_UrbanChina_w2_sleep$f_SLEEP)
nas<-length(s1066_UrbanChina_w2_sleep$f_SLEEP)-length(na.omit(s1066_UrbanChina_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL UCh w2, echo=FALSE}

label(t1066_ds_UCh_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UCh_w2
save(sleep, file = "../RData/UCh_w2/sleep.RData")

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$sleep <- car::recode(t1066_m_ds_UCh_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```


## RuralChina

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_sleep','10-66.1066-RuralChina-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local RuralChina w1, echo=F}
s1066_RuralChina_w1_sleep <- opal.execute(o,'s1066_RuralChina_w1_sleep')
vari <- s1066_RuralChina_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_sleep$id)
t1066_ds_RCh_w1$sleep <- car::recode(s1066_RuralChina_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_RCh_w1$sleep <- labelled(t1066_ds_RCh_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
vari <- t1066_ds_RCh_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$sleep)
X<-table(s1066_RuralChina_w1_sleep$SLEEP)
nas<-length(s1066_RuralChina_w1_sleep$SLEEP)-length(na.omit(s1066_RuralChina_w1_sleep$SLEEP))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","NA->999") 
kable(C)
```






```{r importOPAL RCh w1, echo=FALSE}

label(t1066_ds_RCh_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RCh_w1
save(sleep, file = "../RData/RCh_w1/sleep.RData")

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$sleep <- car::recode(t1066_m_ds_RCh_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralChina-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign RuralChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_sleep','10-66.1066-RuralChina-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local RuralChina w2, echo=F}
s1066_RuralChina_w2_sleep <- opal.execute(o,'s1066_RuralChina_w2_sleep')
vari <- s1066_RuralChina_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_sleep$id)
t1066_ds_RCh_w2$sleep <-  car::recode(s1066_RuralChina_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_RCh_w2$sleep <- labelled(t1066_ds_RCh_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=F}
vari <- t1066_ds_RCh_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$sleep)
X<-table(s1066_RuralChina_w2_sleep$f_SLEEP)
nas<-length(s1066_RuralChina_w2_sleep$f_SLEEP)-length(na.omit(s1066_RuralChina_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL RCh w2, echo=FALSE}

label(t1066_ds_RCh_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RCh_w2
save(sleep, file = "../RData/RCh_w2/sleep.RData")

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$sleep <- car::recode(t1066_m_ds_RCh_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```


## DominicanRepublic

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_sleep','10-66.1066-DominicanRepublic-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local DominicanRepublic w1, echo=F}
s1066_DominicanRepublic_w1_sleep <- opal.execute(o,'s1066_DominicanRepublic_w1_sleep')
vari <- s1066_DominicanRepublic_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_sleep$id)
t1066_ds_DR_w1$sleep <- car::recode(s1066_DominicanRepublic_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_DR_w1$sleep <- labelled(t1066_ds_DR_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
vari <- t1066_ds_DR_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$sleep)
X<-table(s1066_DominicanRepublic_w1_sleep$SLEEP)
nas<-length(s1066_DominicanRepublic_w1_sleep$SLEEP)-length(na.omit(s1066_DominicanRepublic_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```





```{r importOPAL DR w1, echo=FALSE}

label(t1066_ds_DR_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_DR_w1
save(sleep, file = "../RData/DR_w1/sleep.RData")

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$sleep <- car::recode(t1066_m_ds_DR_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign DominicanRepublic w2, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_sleep','10-66.1066-DominicanRepublic-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local DominicanRepublic w2, echo=F}
s1066_DominicanRepublic_w2_sleep <- opal.execute(o,'s1066_DominicanRepublic_w2_sleep')
vari <- s1066_DominicanRepublic_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_sleep$id)
t1066_ds_DR_w2$sleep <-  car::recode(s1066_DominicanRepublic_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_DR_w2$sleep <- labelled(t1066_ds_DR_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=F}
vari <- t1066_ds_DR_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=F}
AfterH <- table(t1066_ds_DR_w2$sleep)
X<-table(s1066_DominicanRepublic_w2_sleep$f_SLEEP)
nas<-length(s1066_DominicanRepublic_w2_sleep$f_SLEEP)-length(na.omit(s1066_DominicanRepublic_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL DR w2, echo=FALSE}

label(t1066_ds_DR_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_DR_w2
save(sleep, file = "../RData/DR_w2/sleep.RData")

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$sleep <- car::recode(t1066_m_ds_DR_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```


## Venezuela

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-Venezuela-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_sleep','10-66.1066-Venezuela-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local Venezuela w1, echo=F}
s1066_Venezuela_w1_sleep <- opal.execute(o,'s1066_Venezuela_w1_sleep')
vari <- s1066_Venezuela_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_sleep$id)
t1066_ds_Ven_w1$sleep <- car::recode(s1066_Venezuela_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_Ven_w1$sleep <- labelled(t1066_ds_Ven_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
vari <- t1066_ds_Ven_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$sleep)
X<-table(s1066_Venezuela_w1_sleep$SLEEP)
nas<-length(s1066_Venezuela_w1_sleep$SLEEP)-length(na.omit(s1066_Venezuela_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL Ven w1, echo=FALSE}

label(t1066_ds_Ven_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_Ven_w1
save(sleep, file = "../RData/Ven_w1/sleep.RData")

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$sleep <- car::recode(t1066_m_ds_Ven_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-Venezuela-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign Venezuela w2, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_sleep','10-66.1066-Venezuela-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local Venezuela w2, echo=F}
s1066_Venezuela_w2_sleep <- opal.execute(o,'s1066_Venezuela_w2_sleep')
vari <- s1066_Venezuela_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_sleep$id)
t1066_ds_Ven_w2$sleep <-  car::recode(s1066_Venezuela_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_Ven_w2$sleep <- labelled(t1066_ds_Ven_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=F}
vari <- t1066_ds_Ven_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$sleep)
X<-table(s1066_Venezuela_w2_sleep$f_SLEEP)
nas<-length(s1066_Venezuela_w2_sleep$f_SLEEP)-length(na.omit(s1066_Venezuela_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL Ven w2, echo=FALSE}

label(t1066_ds_Ven_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_Ven_w2
save(sleep, file = "../RData/Ven_w2/sleep.RData")

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$sleep <- car::recode(t1066_m_ds_Ven_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```


## UrbanPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_sleep','10-66.1066-UrbanPeru-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local UrbanPeru w1, echo=F}
s1066_UrbanPeru_w1_sleep <- opal.execute(o,'s1066_UrbanPeru_w1_sleep')
vari <- s1066_UrbanPeru_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_sleep$id)
t1066_ds_UP_w1$sleep <- car::recode(s1066_UrbanPeru_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_UP_w1$sleep <- labelled(t1066_ds_UP_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
vari <- t1066_ds_UP_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$sleep)
X<-table(s1066_UrbanPeru_w1_sleep$SLEEP)
nas<-length(s1066_UrbanPeru_w1_sleep$SLEEP)-length(na.omit(s1066_UrbanPeru_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UP w1, echo=FALSE}

label(t1066_ds_UP_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UP_w1
save(sleep, file = "../RData/UP_w1/sleep.RData")

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$sleep <- car::recode(t1066_m_ds_UP_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanPeru-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign UrbanPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_sleep','10-66.1066-UrbanPeru-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local UrbanPeru w2, echo=F}
s1066_UrbanPeru_w2_sleep <- opal.execute(o,'s1066_UrbanPeru_w2_sleep')
vari <- s1066_UrbanPeru_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_sleep$id)
t1066_ds_UP_w2$sleep <-  car::recode(s1066_UrbanPeru_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_UP_w2$sleep <- labelled(t1066_ds_UP_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=F}
vari <- t1066_ds_UP_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=F}
AfterH <- table(t1066_ds_UP_w2$sleep)
X<-table(s1066_UrbanPeru_w2_sleep$f_SLEEP)
nas<-length(s1066_UrbanPeru_w2_sleep$f_SLEEP)-length(na.omit(s1066_UrbanPeru_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL UP w2, echo=FALSE}

label(t1066_ds_UP_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UP_w2
save(sleep, file = "../RData/UP_w2/sleep.RData")

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$sleep <- car::recode(t1066_m_ds_UP_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```


## RuralPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_sleep','10-66.1066-RuralPeru-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local RuralPeru w1, echo=F}
s1066_RuralPeru_w1_sleep <- opal.execute(o,'s1066_RuralPeru_w1_sleep')
vari <- s1066_RuralPeru_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_sleep$id)
t1066_ds_RP_w1$sleep <- car::recode(s1066_RuralPeru_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_RP_w1$sleep <- labelled(t1066_ds_RP_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
vari <- t1066_ds_RP_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$sleep)
X<-table(s1066_RuralPeru_w1_sleep$SLEEP)
nas<-length(s1066_RuralPeru_w1_sleep$SLEEP)-length(na.omit(s1066_RuralPeru_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL RP w1, echo=FALSE}

label(t1066_ds_RP_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RP_w1
save(sleep, file = "../RData/RP_w1/sleep.RData")

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$sleep <- car::recode(t1066_m_ds_RP_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralPeru-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign RuralPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_sleep','10-66.1066-RuralPeru-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local RuralPeru w2, echo=F}
s1066_RuralPeru_w2_sleep <- opal.execute(o,'s1066_RuralPeru_w2_sleep')
vari <- s1066_RuralPeru_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_sleep$id)
t1066_ds_RP_w2$sleep <-  car::recode(s1066_RuralPeru_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_RP_w2$sleep <- labelled(t1066_ds_RP_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=F}
vari <- t1066_ds_RP_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=F}
AfterH <- table(t1066_ds_RP_w2$sleep)
X<-table(s1066_RuralPeru_w2_sleep$f_SLEEP)
nas<-length(s1066_RuralPeru_w2_sleep$f_SLEEP)-length(na.omit(s1066_RuralPeru_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL RP w2, echo=FALSE}

label(t1066_ds_RP_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RP_w2
save(sleep, file = "../RData/RP_w2/sleep.RData")

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$sleep <- car::recode(t1066_m_ds_RP_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```



## UrbanMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_sleep','10-66.1066-UrbanMexico-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local UrbanMexico w1, echo=F}
s1066_UrbanMexico_w1_sleep <- opal.execute(o,'s1066_UrbanMexico_w1_sleep')
vari <- s1066_UrbanMexico_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_sleep$id)
t1066_ds_UM_w1$sleep <- car::recode(s1066_UrbanMexico_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_UM_w1$sleep <- labelled(t1066_ds_UM_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
vari <- t1066_ds_UM_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$sleep)
X<-table(s1066_UrbanMexico_w1_sleep$SLEEP)
nas<-length(s1066_UrbanMexico_w1_sleep$SLEEP)-length(na.omit(s1066_UrbanMexico_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UM w1, echo=FALSE}

label(t1066_ds_UM_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UM_w1
save(sleep, file = "../RData/UM_w1/sleep.RData")

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$sleep <- car::recode(t1066_m_ds_UM_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-UrbanMexico-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign UrbanMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_sleep','10-66.1066-UrbanMexico-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local UrbanMexico w2, echo=F}
s1066_UrbanMexico_w2_sleep <- opal.execute(o,'s1066_UrbanMexico_w2_sleep')
vari <- s1066_UrbanMexico_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_sleep$id)
t1066_ds_UM_w2$sleep <-  car::recode(s1066_UrbanMexico_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_UM_w2$sleep <- labelled(t1066_ds_UM_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=F}
vari <- t1066_ds_UM_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=F}
AfterH <- table(t1066_ds_UM_w2$sleep)
X<-table(s1066_UrbanMexico_w2_sleep$f_SLEEP)
nas<-length(s1066_UrbanMexico_w2_sleep$f_SLEEP)-length(na.omit(s1066_UrbanMexico_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL UM w2, echo=FALSE}

label(t1066_ds_UM_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_UM_w2
save(sleep, file = "../RData/UM_w2/sleep.RData")

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$sleep <- car::recode(t1066_m_ds_UM_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```


## RuralMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_sleep','10-66.1066-RuralMexico-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local RuralMexico w1, echo=F}
s1066_RuralMexico_w1_sleep <- opal.execute(o,'s1066_RuralMexico_w1_sleep')
vari <- s1066_RuralMexico_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_sleep$id)
t1066_ds_RM_w1$sleep <- car::recode(s1066_RuralMexico_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_RM_w1$sleep <- labelled(t1066_ds_RM_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
vari <- t1066_ds_RM_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$sleep)
X<-table(s1066_RuralMexico_w1_sleep$SLEEP)
nas<-length(s1066_RuralMexico_w1_sleep$SLEEP)-length(na.omit(s1066_RuralMexico_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL RM w1, echo=FALSE}

label(t1066_ds_RM_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RM_w1
save(sleep, file = "../RData/RM_w1/sleep.RData")

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$sleep <- car::recode(t1066_m_ds_RM_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-RuralMexico-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign RuralMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_sleep','10-66.1066-RuralMexico-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local RuralMexico w2, echo=F}
s1066_RuralMexico_w2_sleep <- opal.execute(o,'s1066_RuralMexico_w2_sleep')
vari <- s1066_RuralMexico_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_sleep$id)
t1066_ds_RM_w2$sleep <-  car::recode(s1066_RuralMexico_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_RM_w2$sleep <- labelled(t1066_ds_RM_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=F}
vari <- t1066_ds_RM_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=F}
AfterH <- table(t1066_ds_RM_w2$sleep)
X<-table(s1066_RuralMexico_w2_sleep$f_SLEEP)
nas<-length(s1066_RuralMexico_w2_sleep$f_SLEEP)-length(na.omit(s1066_RuralMexico_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL RM w2, echo=FALSE}

label(t1066_ds_RM_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_RM_w2
save(sleep, file = "../RData/RM_w2/sleep.RData")

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$sleep <- car::recode(t1066_m_ds_RM_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```


## PuertoRico

### Wave 1 

#### Study-specific variable description




| **Name** | `SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |







```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_sleep','10-66.1066-PuertoRico-Baseline', variables=list('SLEEP'), missings = TRUE)
```

```{r local PuertoRico w1, echo=F}
s1066_PuertoRico_w1_sleep <- opal.execute(o,'s1066_PuertoRico_w1_sleep')
vari <- s1066_PuertoRico_w1_sleep$SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w1_sleep, aes(x=factor(SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_sleep$id)
t1066_ds_PR_w1$sleep <- car::recode(s1066_PuertoRico_w1_sleep$SLEEP, "1 = '0';0='1';NA='999'")
t1066_ds_PR_w1$sleep <- labelled(t1066_ds_PR_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
vari <- t1066_ds_PR_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$sleep)
X<-table(s1066_PuertoRico_w1_sleep$SLEEP)
nas<-length(s1066_PuertoRico_w1_sleep$SLEEP)-length(na.omit(s1066_PuertoRico_w1_sleep$SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL PR w1, echo=FALSE}

label(t1066_ds_PR_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_PR_w1
save(sleep, file = "../RData/PR_w1/sleep.RData")

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$sleep <- car::recode(t1066_m_ds_PR_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description




| **Name** | `f_SLEEP`|
|-|-|
| **Label** | `difficulty sleeping?` |
| **Table name** | `1066-PuertoRico-Followup` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |






```{r assign PuertoRico w2, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_sleep','10-66.1066-PuertoRico-Followup', variables=list('f_SLEEP'), missings = TRUE)
```

```{r local PuertoRico w2, echo=F}
s1066_PuertoRico_w2_sleep <- opal.execute(o,'s1066_PuertoRico_w2_sleep')
vari <- s1066_PuertoRico_w2_sleep$f_SLEEP
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_SLEEP")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w2_sleep, aes(x=factor(f_SLEEP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_sleep$id)
t1066_ds_PR_w2$sleep <-  car::recode(s1066_PuertoRico_w2_sleep$f_SLEEP, "1 = '0';0='1'; NA='999'")
t1066_ds_PR_w2$sleep <- labelled(t1066_ds_PR_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=F}
vari <- t1066_ds_PR_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=F}
AfterH <- table(t1066_ds_PR_w2$sleep)
X<-table(s1066_PuertoRico_w2_sleep$f_SLEEP)
nas<-length(s1066_PuertoRico_w2_sleep$f_SLEEP)-length(na.omit(s1066_PuertoRico_w2_sleep$f_SLEEP))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1", "NA->999") 
kable(C)
```






```{r importOPAL PR w2, echo=FALSE}

label(t1066_ds_PR_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')
sleep <- t1066_ds_PR_w2
save(sleep, file = "../RData/PR_w2/sleep.RData")

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$sleep <- car::recode(t1066_m_ds_PR_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
