---
title: "Incontinence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/incontinenceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/incontinenceDS.R')
```

# Data process




## Cuba

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Cuba w1, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w1_incontinence','10-66.1066-Cuba-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local Cuba w1, echo=F}
s1066_Cuba_w1_incontinence <- opal.execute(o,'s1066_Cuba_w1_incontinence')
vari <- s1066_Cuba_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo Cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_incontinence$id)
t1066_ds_cuba_w1$incontinence <- car::recode(s1066_Cuba_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_cuba_w1$incontinence <- labelled(t1066_ds_cuba_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1, echo=F}
vari <- t1066_ds_cuba_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$incontinence)
X<-table(s1066_Cuba_w1_incontinence$ONS21)
nas<-length(s1066_Cuba_w1_incontinence$ONS21)-length(na.omit(s1066_Cuba_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL Cuba w1, echo=FALSE}

label(t1066_ds_cuba_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_cuba_w1
save(incontinence, file = "../RData/cuba_w1/incontinence.RData")

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$incontinence <- car::recode(t1066_m_ds_cuba_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-Cuba-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Cuba w2, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w2_incontinence','10-66.1066-Cuba-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local Cuba w2, echo=F}
s1066_Cuba_w2_incontinence <- opal.execute(o,'s1066_Cuba_w2_incontinence')
vari <- s1066_Cuba_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo Cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_incontinence$id)
t1066_ds_cuba_w2$incontinence <-  car::recode(s1066_Cuba_w2_incontinence$f_PINCONT, "0='1';1 = '1';2 = '0';3 = '0';NA='999'")
t1066_ds_cuba_w2$incontinence <- labelled(t1066_ds_cuba_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2, echo=F}
vari <- t1066_ds_cuba_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$incontinence)
X<-table(s1066_Cuba_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),sum(is.na(s1066_Cuba_w2_incontinence$f_PINCONT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999")
kable(C)
```






```{r importOPAL Cuba w2, echo=FALSE}

label(t1066_ds_cuba_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_cuba_w2
save(incontinence, file = "../RData/cuba_w2/incontinence.RData")

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$incontinence <- car::recode(t1066_m_ds_cuba_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```



## India

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-India-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 's1066_India_w1_incontinence','10-66.1066-India-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local India w1, echo=F}
s1066_India_w1_incontinence <- opal.execute(o,'s1066_India_w1_incontinence')
vari <- s1066_India_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_India_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_incontinence$id)
t1066_ds_india_w1$incontinence <- car::recode(s1066_India_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_india_w1$incontinence <- labelled(t1066_ds_india_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
vari <- t1066_ds_india_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$incontinence)
X<-table(s1066_India_w1_incontinence$ONS21)
nas<-length(s1066_India_w1_incontinence$ONS21)-length(na.omit(s1066_India_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL India w1, echo=FALSE}

label(t1066_ds_india_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_india_w1
save(incontinence, file = "../RData/india_w1/incontinence.RData")

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$incontinence <- car::recode(t1066_m_ds_india_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```




## UrbanChina

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_incontinence','10-66.1066-UrbanChina-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local UrbanChina w1, echo=F}
s1066_UrbanChina_w1_incontinence <- opal.execute(o,'s1066_UrbanChina_w1_incontinence')
vari <- s1066_UrbanChina_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_incontinence$id)
t1066_ds_UCh_w1$incontinence <- car::recode(s1066_UrbanChina_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_UCh_w1$incontinence <- labelled(t1066_ds_UCh_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
vari <- t1066_ds_UCh_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$incontinence)
X<-table(s1066_UrbanChina_w1_incontinence$ONS21)
nas<-length(s1066_UrbanChina_w1_incontinence$ONS21)-length(na.omit(s1066_UrbanChina_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UrbanChina w1, echo=FALSE}

label(t1066_ds_UCh_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UCh_w1
save(incontinence, file = "../RData/UCh_w1/incontinence.RData")

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$incontinence <- car::recode(t1066_m_ds_UCh_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-UrbanChina-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign UrbanChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_incontinence','10-66.1066-UrbanChina-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local UrbanChina w2, echo=F}
s1066_UrbanChina_w2_incontinence <- opal.execute(o,'s1066_UrbanChina_w2_incontinence')
vari <- s1066_UrbanChina_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_incontinence$id)
t1066_ds_UCh_w2$incontinence <-  car::recode(s1066_UrbanChina_w2_incontinence$f_PINCONT, "0 = '1';1 = '1';2='0';3 = '0';NA='999'")
t1066_ds_UCh_w2$incontinence <- labelled(t1066_ds_UCh_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=F}
vari <- t1066_ds_UCh_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$incontinence)
X<-table(s1066_UrbanChina_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1")
kable(C)
```






```{r importOPAL UrbanChina w2, echo=FALSE}

label(t1066_ds_UCh_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UCh_w2
save(incontinence, file = "../RData/UCh_w2/incontinence.RData")

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$incontinence <- car::recode(t1066_m_ds_UCh_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```



## RuralChina

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_incontinence','10-66.1066-RuralChina-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local RuralChina w1, echo=F}
s1066_RuralChina_w1_incontinence <- opal.execute(o,'s1066_RuralChina_w1_incontinence')
vari <- s1066_RuralChina_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_incontinence$id)
t1066_ds_RCh_w1$incontinence <- car::recode(s1066_RuralChina_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_RCh_w1$incontinence <- labelled(t1066_ds_RCh_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
vari <- t1066_ds_RCh_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$incontinence)
X<-table(s1066_RuralChina_w1_incontinence$ONS21)
nas<-length(s1066_RuralChina_w1_incontinence$ONS21)-length(na.omit(s1066_RuralChina_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL RuralChina w1, echo=FALSE}

label(t1066_ds_RCh_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RCh_w1
save(incontinence, file = "../RData/RCh_w1/incontinence.RData")

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$incontinence <- car::recode(t1066_m_ds_RCh_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-RuralChina-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_incontinence','10-66.1066-RuralChina-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local RuralChina w2, echo=F}
s1066_RuralChina_w2_incontinence <- opal.execute(o,'s1066_RuralChina_w2_incontinence')
vari <- s1066_RuralChina_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_incontinence$id)
t1066_ds_RCh_w2$incontinence <-  car::recode(s1066_RuralChina_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';NA='999'")
t1066_ds_RCh_w2$incontinence <- labelled(t1066_ds_RCh_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=F}
vari <- t1066_ds_RCh_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$incontinence)
X<-table(s1066_RuralChina_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),sum(is.na(s1066_RuralChina_w2_incontinence$f_PINCONT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999")
kable(C)
```






```{r importOPAL RuralChina w2, echo=FALSE}

label(t1066_ds_RCh_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RCh_w2
save(incontinence, file = "../RData/RCh_w2/incontinence.RData")

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$incontinence <- car::recode(t1066_m_ds_RCh_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```



## DominicanRepublic

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_incontinence','10-66.1066-DominicanRepublic-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local DominicanRepublic w1, echo=F}
s1066_DominicanRepublic_w1_incontinence <- opal.execute(o,'s1066_DominicanRepublic_w1_incontinence')
vari <- s1066_DominicanRepublic_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_incontinence$id)
t1066_ds_DR_w1$incontinence <- car::recode(s1066_DominicanRepublic_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_DR_w1$incontinence <- labelled(t1066_ds_DR_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
vari <- t1066_ds_DR_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$incontinence)
X<-table(s1066_DominicanRepublic_w1_incontinence$ONS21)
nas<-length(s1066_DominicanRepublic_w1_incontinence$ONS21)-length(na.omit(s1066_DominicanRepublic_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL DominicanRepublic w1, echo=FALSE}

label(t1066_ds_DR_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_DR_w1
save(incontinence, file = "../RData/DR_w1/incontinence.RData")

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$incontinence <- car::recode(t1066_m_ds_DR_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `9; NA` |
| **Description** |  |




```{r assign DominicanRepublic w2, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_incontinence','10-66.1066-DominicanRepublic-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local DominicanRepublic w2, echo=F}
s1066_DominicanRepublic_w2_incontinence <- opal.execute(o,'s1066_DominicanRepublic_w2_incontinence')
vari <- s1066_DominicanRepublic_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `9,NA into 999`

**R script:**
```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_incontinence$id)
t1066_ds_DR_w2$incontinence <-  car::recode(s1066_DominicanRepublic_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1'; 9 = '999';NA='999'")
t1066_ds_DR_w2$incontinence <- labelled(t1066_ds_DR_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=F}
vari <- t1066_ds_DR_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=F}
AfterH <- table(t1066_ds_DR_w2$incontinence)
X<-table(s1066_DominicanRepublic_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]),sum(sum(s1066_DominicanRepublic_w2_incontinence$f_PINCONT==9,na.rm=T),sum(is.na(s1066_DominicanRepublic_w2_incontinence$f_PINCONT))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","9,NA->999")
kable(C)
```






```{r importOPAL DominicanRepublic w2, echo=FALSE}

label(t1066_ds_DR_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_DR_w2
save(incontinence, file = "../RData/DR_w2/incontinence.RData")

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$incontinence <- car::recode(t1066_m_ds_DR_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```



## Venezuela

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-Venezuela-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_incontinence','10-66.1066-Venezuela-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local Venezuela w1, echo=F}
s1066_Venezuela_w1_incontinence <- opal.execute(o,'s1066_Venezuela_w1_incontinence')
vari <- s1066_Venezuela_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_incontinence$id)
t1066_ds_Ven_w1$incontinence <- car::recode(s1066_Venezuela_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_Ven_w1$incontinence <- labelled(t1066_ds_Ven_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
vari <- t1066_ds_Ven_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$incontinence)
X<-table(s1066_Venezuela_w1_incontinence$ONS21)
nas<-length(s1066_Venezuela_w1_incontinence$ONS21)-length(na.omit(s1066_Venezuela_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL Venezuela w1, echo=FALSE}

label(t1066_ds_Ven_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_Ven_w1
save(incontinence, file = "../RData/Ven_w1/incontinence.RData")

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$incontinence <- car::recode(t1066_m_ds_Ven_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-Venezuela-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `9; NA` |
| **Description** |  |




```{r assign Venezuela w2, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_incontinence','10-66.1066-Venezuela-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local Venezuela w2, echo=F}
s1066_Venezuela_w2_incontinence <- opal.execute(o,'s1066_Venezuela_w2_incontinence')
vari <- s1066_Venezuela_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(s1066_Venezuela_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `9,NA into 999`

**R script:**
```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_incontinence$id)
t1066_ds_Ven_w2$incontinence <-  car::recode(s1066_Venezuela_w2_incontinence$f_PINCONT, "2 = '0';3 = '0'; 0='1'; 1='1';9='999';NA='999'")
t1066_ds_Ven_w2$incontinence <- labelled(t1066_ds_Ven_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=F}
vari <- t1066_ds_Ven_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$incontinence)
X<-table(s1066_Venezuela_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]),sum(sum(s1066_Venezuela_w2_incontinence$f_PINCONT==9,na.rm=T),sum(is.na(s1066_Venezuela_w2_incontinence$f_PINCONT))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","9,NA->999")
kable(C)
```






```{r importOPAL Venezuela w2, echo=FALSE}

label(t1066_ds_Ven_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_Ven_w2
save(incontinence, file = "../RData/Ven_w2/incontinence.RData")

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$incontinence <- car::recode(t1066_m_ds_Ven_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```



## UrbanPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_incontinence','10-66.1066-UrbanPeru-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local UrbanPeru w1, echo=F}
s1066_UrbanPeru_w1_incontinence <- opal.execute(o,'s1066_UrbanPeru_w1_incontinence')
vari <- s1066_UrbanPeru_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_incontinence$id)
t1066_ds_UP_w1$incontinence <- car::recode(s1066_UrbanPeru_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_UP_w1$incontinence <- labelled(t1066_ds_UP_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
vari <- t1066_ds_UP_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$incontinence)
X<-table(s1066_UrbanPeru_w1_incontinence$ONS21)
nas<-length(s1066_UrbanPeru_w1_incontinence$ONS21)-length(na.omit(s1066_UrbanPeru_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UrbanPeru w1, echo=FALSE}

label(t1066_ds_UP_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UP_w1
save(incontinence, file = "../RData/UP_w1/incontinence.RData")

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$incontinence <- car::recode(t1066_m_ds_UP_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-UrbanPeru-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign UrbanPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_incontinence','10-66.1066-UrbanPeru-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local UrbanPeru w2, echo=F}
s1066_UrbanPeru_w2_incontinence <- opal.execute(o,'s1066_UrbanPeru_w2_incontinence')
vari <- s1066_UrbanPeru_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_incontinence$id)
t1066_ds_UP_w2$incontinence <-  car::recode(s1066_UrbanPeru_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';NA='999'")
t1066_ds_UP_w2$incontinence <- labelled(t1066_ds_UP_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=F}
vari <- t1066_ds_UP_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=F}
AfterH <- table(t1066_ds_UP_w2$incontinence)
X<-table(s1066_UrbanPeru_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1")
kable(C)
```






```{r importOPAL UrbanPeru w2, echo=FALSE}

label(t1066_ds_UP_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UP_w2
save(incontinence, file = "../RData/UP_w2/incontinence.RData")

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$incontinence <- car::recode(t1066_m_ds_UP_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```



## RuralPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_incontinence','10-66.1066-RuralPeru-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local RuralPeru w1, echo=F}
s1066_RuralPeru_w1_incontinence <- opal.execute(o,'s1066_RuralPeru_w1_incontinence')
vari <- s1066_RuralPeru_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_incontinence$id)
t1066_ds_RP_w1$incontinence <- car::recode(s1066_RuralPeru_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_RP_w1$incontinence <- labelled(t1066_ds_RP_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
vari <- t1066_ds_RP_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$incontinence)
X<-table(s1066_RuralPeru_w1_incontinence$ONS21)
nas<-length(s1066_RuralPeru_w1_incontinence$ONS21)-length(na.omit(s1066_RuralPeru_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL RuralPeru w1, echo=FALSE}

label(t1066_ds_RP_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RP_w1
save(incontinence, file = "../RData/RP_w1/incontinence.RData")

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$incontinence <- car::recode(t1066_m_ds_RP_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-RuralPeru-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |




```{r assign RuralPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_incontinence','10-66.1066-RuralPeru-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local RuralPeru w2, echo=F}
s1066_RuralPeru_w2_incontinence <- opal.execute(o,'s1066_RuralPeru_w2_incontinence')
vari <- s1066_RuralPeru_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_incontinence$id)
t1066_ds_RP_w2$incontinence <-  car::recode(s1066_RuralPeru_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';NA='999'")
t1066_ds_RP_w2$incontinence <- labelled(t1066_ds_RP_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=F}
vari <- t1066_ds_RP_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=F}
AfterH <- table(t1066_ds_RP_w2$incontinence)
X<-table(s1066_RuralPeru_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1")
kable(C)
```






```{r importOPAL RuralPeru w2, echo=FALSE}

label(t1066_ds_RP_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RP_w2
save(incontinence, file = "../RData/RP_w2/incontinence.RData")

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$incontinence <- car::recode(t1066_m_ds_RP_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```



## UrbanMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_incontinence','10-66.1066-UrbanMexico-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local UrbanMexico w1, echo=F}
s1066_UrbanMexico_w1_incontinence <- opal.execute(o,'s1066_UrbanMexico_w1_incontinence')
vari <- s1066_UrbanMexico_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_incontinence$id)
t1066_ds_UM_w1$incontinence <- car::recode(s1066_UrbanMexico_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_UM_w1$incontinence <- labelled(t1066_ds_UM_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
vari <- t1066_ds_UM_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$incontinence)
X<-table(s1066_UrbanMexico_w1_incontinence$ONS21)
nas<-length(s1066_UrbanMexico_w1_incontinence$ONS21)-length(na.omit(s1066_UrbanMexico_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL UrbanMexico w1, echo=FALSE}

label(t1066_ds_UM_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UM_w1
save(incontinence, file = "../RData/UM_w1/incontinence.RData")

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$incontinence <- car::recode(t1066_m_ds_UM_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-UrbanMexico-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `9;NA` |
| **Description** |  |





```{r assign UrbanMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_incontinence','10-66.1066-UrbanMexico-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local UrbanMexico w2, echo=F}
s1066_UrbanMexico_w2_incontinence <- opal.execute(o,'s1066_UrbanMexico_w2_incontinence')
vari <- s1066_UrbanMexico_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(s1066_UrbanMexico_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `9,NA into 999`

**R script:**
```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_incontinence$id)
t1066_ds_UM_w2$incontinence <-  car::recode(s1066_UrbanMexico_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';9='999';NA='999'")
t1066_ds_UM_w2$incontinence <- labelled(t1066_ds_UM_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=F}
vari <- t1066_ds_UM_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=F}
AfterH <- table(t1066_ds_UM_w2$incontinence)
X<-table(s1066_UrbanMexico_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]),sum(sum(s1066_UrbanMexico_w2_incontinence$f_PINCONT==9,na.rm=T),sum(is.na(s1066_UrbanMexico_w2_incontinence$f_PINCONT))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","9,NA->999")
kable(C)
```






```{r importOPAL UrbanMexico w2, echo=FALSE}

label(t1066_ds_UM_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_UM_w2
save(incontinence, file = "../RData/UM_w2/incontinence.RData")

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$incontinence <- car::recode(t1066_m_ds_UM_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```



## RuralMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_incontinence','10-66.1066-RuralMexico-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local RuralMexico w1, echo=F}
s1066_RuralMexico_w1_incontinence <- opal.execute(o,'s1066_RuralMexico_w1_incontinence')
vari <- s1066_RuralMexico_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_incontinence$id)
t1066_ds_RM_w1$incontinence <- car::recode(s1066_RuralMexico_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_RM_w1$incontinence <- labelled(t1066_ds_RM_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
vari <- t1066_ds_RM_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$incontinence)
X<-table(s1066_RuralMexico_w1_incontinence$ONS21)
nas<-length(s1066_RuralMexico_w1_incontinence$ONS21)-length(na.omit(s1066_RuralMexico_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL RuralMexico w1, echo=FALSE}

label(t1066_ds_RM_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RM_w1
save(incontinence, file = "../RData/RM_w1/incontinence.RData")

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$incontinence <- car::recode(t1066_m_ds_RM_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-RuralMexico-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_incontinence','10-66.1066-RuralMexico-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local RuralMexico w2, echo=F}
s1066_RuralMexico_w2_incontinence <- opal.execute(o,'s1066_RuralMexico_w2_incontinence')
vari <- s1066_RuralMexico_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `NA into 999`

**R script:**
```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_incontinence$id)
t1066_ds_RM_w2$incontinence <-  car::recode(s1066_RuralMexico_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';NA='999'")
t1066_ds_RM_w2$incontinence <- labelled(t1066_ds_RM_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=F}
vari <- t1066_ds_RM_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=F}
AfterH <- table(t1066_ds_RM_w2$incontinence)
X<-table(s1066_RuralMexico_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]),sum(is.na(s1066_RuralMexico_w2_incontinence$f_PINCONT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999")
kable(C)
```






```{r importOPAL RuralMexico w2, echo=FALSE}

label(t1066_ds_RM_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_RM_w2
save(incontinence, file = "../RData/RM_w2/incontinence.RData")

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$incontinence <- car::recode(t1066_m_ds_RM_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```



## PuertoRico

### Wave 1 

#### Study-specific variable description




| **Name** | `ONS21`|
|-|-|
| **Label** | `HAS-DDS early symptoms - urinary incontinence` |
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** | `0 No; 1 Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_incontinence','10-66.1066-PuertoRico-Baseline', variables=list('ONS21'), missings = TRUE)
```

```{r local PuertoRico w1, echo=F}
s1066_PuertoRico_w1_incontinence <- opal.execute(o,'s1066_PuertoRico_w1_incontinence')
vari <- s1066_PuertoRico_w1_incontinence$ONS21
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ONS21")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w1_incontinence, aes(x=factor(ONS21))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_incontinence$id)
t1066_ds_PR_w1$incontinence <- car::recode(s1066_PuertoRico_w1_incontinence$ONS21, "1 = '0';0='1';NA='999'")
t1066_ds_PR_w1$incontinence <- labelled(t1066_ds_PR_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
vari <- t1066_ds_PR_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$incontinence)
X<-table(s1066_PuertoRico_w1_incontinence$ONS21)
nas<-length(s1066_PuertoRico_w1_incontinence$ONS21)-length(na.omit(s1066_PuertoRico_w1_incontinence$ONS21))
BeforeH <- c(X[2:1],nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL PuertoRico w1, echo=FALSE}

label(t1066_ds_PR_w1$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_PR_w1
save(incontinence, file = "../RData/PR_w1/incontinence.RData")

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$incontinence <- car::recode(t1066_m_ds_PR_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_PINCONT`|
|-|-|
| **Label** | `incontinence` |
| **Table name** | `1066-PuertoRico-Followup` |
| **Categories** | `0 no; 1 rarely; 2 often; 3 very often` |
| **Missings** | `9; NA` |
| **Description** |  |


```{r assign PuertoRico w2, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_incontinence','10-66.1066-PuertoRico-Followup', variables=list('f_PINCONT'), missings = TRUE)
```

```{r local PuertoRico w2, echo=F}
s1066_PuertoRico_w2_incontinence <- opal.execute(o,'s1066_PuertoRico_w2_incontinence')
vari <- s1066_PuertoRico_w2_incontinence$f_PINCONT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "f_PINCONT")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(s1066_PuertoRico_w2_incontinence, aes(x=factor(f_PINCONT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 0` 
* `0,1 into 1`
* `9,NA into 999`

**R script:**
```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_incontinence$id)
t1066_ds_PR_w2$incontinence <-  car::recode(s1066_PuertoRico_w2_incontinence$f_PINCONT, "2 = '0';3 = '0';0='1';1='1';9='999';NA='999'")
t1066_ds_PR_w2$incontinence <- labelled(t1066_ds_PR_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=F}
vari <- t1066_ds_PR_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=F}
AfterH <- table(t1066_ds_PR_w2$incontinence)
X<-table(s1066_PuertoRico_w2_incontinence$f_PINCONT)
BeforeH <- c(sum(X[3:4]),sum(X[2:1]),sum(sum(s1066_PuertoRico_w2_incontinence$f_PINCONT==9,na.rm=T),sum(is.na(s1066_PuertoRico_w2_incontinence$f_PINCONT))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999")
kable(C)
```






```{r importOPAL PuertoRico w2, echo=FALSE}

label(t1066_ds_PR_w2$incontinence) <- "Incontinence"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')
incontinence <- t1066_ds_PR_w2
save(incontinence, file = "../RData/PR_w2/incontinence.RData")

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$incontinence <- car::recode(t1066_m_ds_PR_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```








## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}


```





# Quality estimation

In wave 2, there are two variables related to "incontinence": `f_PINCONT` and `f_ONS21`. The difference is that `ONS21` is part of the informant questionnaire. Study owners suggested that `f_PINCONT` is more suitable with far fewer missings than the variable `f_ONS21`. On the other hand, wave 1 has only `ONS21` and we decided to harmonised it. Therefore, there may be inconsistences of reporting incontinence between waves.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
