---
title: "Hearing general"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process



## Cuba

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign Cuba w1, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w1_hearing_gen','10-66.1066-Cuba-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local Cuba w1, echo=F}
s1066_Cuba_w1_hearing_gen <- opal.execute(o,'s1066_Cuba_w1_hearing_gen')
vari <- s1066_Cuba_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo Cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_Cuba_w1_hearing_gen$id)
t1066_ds_cuba_w1$hearing_gen <- car::recode(s1066_Cuba_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_cuba_w1$hearing_gen <- labelled(t1066_ds_cuba_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w1, echo=F}
vari <- t1066_ds_cuba_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$hearing_gen)
X<-table(s1066_Cuba_w1_hearing_gen$PEAR)
nas<-length(s1066_Cuba_w1_hearing_gen$PEAR)-length(na.omit(s1066_Cuba_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL Cuba w1, echo=FALSE}

label(t1066_ds_cuba_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_cuba_w1
save(hearing_gen, file = "../RData/cuba_w1/hearing_gen.RData")

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$hearing_gen <- car::recode(t1066_m_ds_cuba_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-Cuba-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Cuba w2, echo=F}
opal.assign.table.tibble(o, 's1066_Cuba_w2_hearing_gen','10-66.1066-Cuba-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local Cuba w2, echo=F}
s1066_Cuba_w2_hearing_gen <- opal.execute(o,'s1066_Cuba_w2_hearing_gen')
vari <- s1066_Cuba_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Cuba_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo Cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_Cuba_w2_hearing_gen$id)
t1066_ds_cuba_w2$hearing_gen <-  car::recode(s1066_Cuba_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_cuba_w2$hearing_gen <- labelled(t1066_ds_cuba_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Cuba w2, echo=F}
vari <- t1066_ds_cuba_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Cuba w2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$hearing_gen)
X<-table(s1066_Cuba_w2_hearing_gen$f_PEAR)
nas<-length(s1066_Cuba_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_Cuba_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL Cuba w2, echo=FALSE}

label(t1066_ds_cuba_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_cuba_w2', t1066_ds_cuba_w2)
#opal.symbol_import(o,'t1066_ds_cuba_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_cuba_w2
save(hearing_gen, file = "../RData/cuba_w2/hearing_gen.RData")

t1066_m_ds_cuba_w2 <- t1066_ds_cuba_w2
t1066_m_ds_cuba_w2$hearing_gen <- car::recode(t1066_m_ds_cuba_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w2', t1066_m_ds_cuba_w2)
#opal.symbol_import(o,'t1066_m_ds_cuba_w2', project='_Athlos_Harm_Dataset')
```



## India

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-India-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 's1066_India_w1_hearing_gen','10-66.1066-India-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local India w1, echo=F}
s1066_India_w1_hearing_gen <- opal.execute(o,'s1066_India_w1_hearing_gen')
vari <- s1066_India_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_India_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_hearing_gen$id)
t1066_ds_india_w1$hearing_gen <- car::recode(s1066_India_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_india_w1$hearing_gen <- labelled(t1066_ds_india_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
vari <- t1066_ds_india_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$hearing_gen)
X<-table(s1066_India_w1_hearing_gen$PEAR)
nas<-length(s1066_India_w1_hearing_gen$PEAR)-length(na.omit(s1066_India_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL India w1, echo=FALSE}

label(t1066_ds_india_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_india_w1
save(hearing_gen, file = "../RData/india_w1/hearing_gen.RData")

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$hearing_gen <- car::recode(t1066_m_ds_india_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

Not found.

## UrbanChina

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |



```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_hearing_gen','10-66.1066-UrbanChina-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local UrbanChina w1, echo=F}
s1066_UrbanChina_w1_hearing_gen <- opal.execute(o,'s1066_UrbanChina_w1_hearing_gen')
vari <- s1066_UrbanChina_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_hearing_gen$id)
t1066_ds_UCh_w1$hearing_gen <- car::recode(s1066_UrbanChina_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UCh_w1$hearing_gen <- labelled(t1066_ds_UCh_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
vari <- t1066_ds_UCh_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$hearing_gen)
X<-table(s1066_UrbanChina_w1_hearing_gen$PEAR)
#nas<-length(s1066_UrbanChina_w1_hearing_gen$PEAR)-length(na.omit(s1066_UrbanChina_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1") 
kable(C)
```






```{r importOPAL UrbanChina w1, echo=FALSE}

label(t1066_ds_UCh_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UCh_w1
save(hearing_gen, file = "../RData/UCh_w1/hearing_gen.RData")

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$hearing_gen <- car::recode(t1066_m_ds_UCh_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanChina-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign UrbanChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_hearing_gen','10-66.1066-UrbanChina-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local UrbanChina w2, echo=F}
s1066_UrbanChina_w2_hearing_gen <- opal.execute(o,'s1066_UrbanChina_w2_hearing_gen')
vari <- s1066_UrbanChina_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanChina_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_hearing_gen$id)
t1066_ds_UCh_w2$hearing_gen <-  car::recode(s1066_UrbanChina_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UCh_w2$hearing_gen <- labelled(t1066_ds_UCh_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=F}
vari <- t1066_ds_UCh_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$hearing_gen)
X<-table(s1066_UrbanChina_w2_hearing_gen$f_PEAR)
nas<-length(s1066_UrbanChina_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_UrbanChina_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL UrbanChina w2, echo=FALSE}

label(t1066_ds_UCh_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UCh_w2', t1066_ds_UCh_w2)
#opal.symbol_import(o,'t1066_ds_UCh_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UCh_w2
save(hearing_gen, file = "../RData/UCh_w2/hearing_gen.RData")

t1066_m_ds_UCh_w2 <- t1066_ds_UCh_w2
t1066_m_ds_UCh_w2$hearing_gen <- car::recode(t1066_m_ds_UCh_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w2', t1066_m_ds_UCh_w2)
#opal.symbol_import(o,'t1066_m_ds_UCh_w2', project='_Athlos_Harm_Dataset')
```



## RuralChina

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |



```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_hearing_gen','10-66.1066-RuralChina-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local RuralChina w1, echo=F}
s1066_RuralChina_w1_hearing_gen <- opal.execute(o,'s1066_RuralChina_w1_hearing_gen')
vari <- s1066_RuralChina_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_hearing_gen$id)
t1066_ds_RCh_w1$hearing_gen <- car::recode(s1066_RuralChina_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RCh_w1$hearing_gen <- labelled(t1066_ds_RCh_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
vari <- t1066_ds_RCh_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$hearing_gen)
X<-table(s1066_RuralChina_w1_hearing_gen$PEAR)
#nas<-length(s1066_RuralChina_w1_hearing_gen$PEAR)-length(na.omit(s1066_RuralChina_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1") 
kable(C)
```






```{r importOPAL RuralChina w1, echo=FALSE}

label(t1066_ds_RCh_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RCh_w1
save(hearing_gen, file = "../RData/RCh_w1/hearing_gen.RData")

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$hearing_gen <- car::recode(t1066_m_ds_RCh_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralChina-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |

 

```{r assign RuralChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_hearing_gen','10-66.1066-RuralChina-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local RuralChina w2, echo=F}
s1066_RuralChina_w2_hearing_gen <- opal.execute(o,'s1066_RuralChina_w2_hearing_gen')
vari <- s1066_RuralChina_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralChina_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_hearing_gen$id)
t1066_ds_RCh_w2$hearing_gen <-  car::recode(s1066_RuralChina_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RCh_w2$hearing_gen <- labelled(t1066_ds_RCh_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=F}
vari <- t1066_ds_RCh_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$hearing_gen)
X<-table(s1066_RuralChina_w2_hearing_gen$f_PEAR)
#nas<-length(s1066_RuralChina_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_RuralChina_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1")
kable(C)
```






```{r importOPAL RuralChina w2, echo=FALSE}

label(t1066_ds_RCh_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RCh_w2', t1066_ds_RCh_w2)
#opal.symbol_import(o,'t1066_ds_RCh_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RCh_w2
save(hearing_gen, file = "../RData/RCh_w2/hearing_gen.RData")

t1066_m_ds_RCh_w2 <- t1066_ds_RCh_w2
t1066_m_ds_RCh_w2$hearing_gen <- car::recode(t1066_m_ds_RCh_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w2', t1066_m_ds_RCh_w2)
#opal.symbol_import(o,'t1066_m_ds_RCh_w2', project='_Athlos_Harm_Dataset')
```



## DominicanRepublic

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_hearing_gen','10-66.1066-DominicanRepublic-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local DominicanRepublic w1, echo=F}
s1066_DominicanRepublic_w1_hearing_gen <- opal.execute(o,'s1066_DominicanRepublic_w1_hearing_gen')
vari <- s1066_DominicanRepublic_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_hearing_gen$id)
t1066_ds_DR_w1$hearing_gen <- car::recode(s1066_DominicanRepublic_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_DR_w1$hearing_gen <- labelled(t1066_ds_DR_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
vari <- t1066_ds_DR_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$hearing_gen)
X<-table(s1066_DominicanRepublic_w1_hearing_gen$PEAR)
nas<-length(s1066_DominicanRepublic_w1_hearing_gen$PEAR)-length(na.omit(s1066_DominicanRepublic_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL DominicanRepublic w1, echo=FALSE}

label(t1066_ds_DR_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_DR_w1
save(hearing_gen, file = "../RData/DR_w1/hearing_gen.RData")

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$hearing_gen <- car::recode(t1066_m_ds_DR_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign DominicanRepublic w2, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_hearing_gen','10-66.1066-DominicanRepublic-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local DominicanRepublic w2, echo=F}
s1066_DominicanRepublic_w2_hearing_gen <- opal.execute(o,'s1066_DominicanRepublic_w2_hearing_gen')
vari <- s1066_DominicanRepublic_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_DominicanRepublic_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_hearing_gen$id)
t1066_ds_DR_w2$hearing_gen <-  car::recode(s1066_DominicanRepublic_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_DR_w2$hearing_gen <- labelled(t1066_ds_DR_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=F}
vari <- t1066_ds_DR_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=F}
AfterH <- table(t1066_ds_DR_w2$hearing_gen)
X<-table(s1066_DominicanRepublic_w2_hearing_gen$f_PEAR)
nas<-length(s1066_DominicanRepublic_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_DominicanRepublic_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL DominicanRepublic w2, echo=FALSE}

label(t1066_ds_DR_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_DR_w2', t1066_ds_DR_w2)
#opal.symbol_import(o,'t1066_ds_DR_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_DR_w2
save(hearing_gen, file = "../RData/DR_w2/hearing_gen.RData")

t1066_m_ds_DR_w2 <- t1066_ds_DR_w2
t1066_m_ds_DR_w2$hearing_gen <- car::recode(t1066_m_ds_DR_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w2', t1066_m_ds_DR_w2)
#opal.symbol_import(o,'t1066_m_ds_DR_w2', project='_Athlos_Harm_Dataset')
```



## Venezuela

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-Venezuela-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_hearing_gen','10-66.1066-Venezuela-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local Venezuela w1, echo=F}
s1066_Venezuela_w1_hearing_gen <- opal.execute(o,'s1066_Venezuela_w1_hearing_gen')
vari <- s1066_Venezuela_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_hearing_gen$id)
t1066_ds_Ven_w1$hearing_gen <- car::recode(s1066_Venezuela_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_Ven_w1$hearing_gen <- labelled(t1066_ds_Ven_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
vari <- t1066_ds_Ven_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$hearing_gen)
X<-table(s1066_Venezuela_w1_hearing_gen$PEAR)
nas<-length(s1066_Venezuela_w1_hearing_gen$PEAR)-length(na.omit(s1066_Venezuela_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL Venezuela w1, echo=FALSE}

label(t1066_ds_Ven_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_Ven_w1
save(hearing_gen, file = "../RData/Ven_w1/hearing_gen.RData")

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$hearing_gen <- car::recode(t1066_m_ds_Ven_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-Venezuela-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Venezuela w2, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_hearing_gen','10-66.1066-Venezuela-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local Venezuela w2, echo=F}
s1066_Venezuela_w2_hearing_gen <- opal.execute(o,'s1066_Venezuela_w2_hearing_gen')
vari <- s1066_Venezuela_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_Venezuela_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_hearing_gen$id)
t1066_ds_Ven_w2$hearing_gen <-  car::recode(s1066_Venezuela_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_Ven_w2$hearing_gen <- labelled(t1066_ds_Ven_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=F}
vari <- t1066_ds_Ven_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$hearing_gen)
X<-table(s1066_Venezuela_w2_hearing_gen$f_PEAR)
nas<-length(s1066_Venezuela_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_Venezuela_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL Venezuela w2, echo=FALSE}

label(t1066_ds_Ven_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_Ven_w2', t1066_ds_Ven_w2)
#opal.symbol_import(o,'t1066_ds_Ven_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_Ven_w2
save(hearing_gen, file = "../RData/Ven_w2/hearing_gen.RData")

t1066_m_ds_Ven_w2 <- t1066_ds_Ven_w2
t1066_m_ds_Ven_w2$hearing_gen <- car::recode(t1066_m_ds_Ven_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w2', t1066_m_ds_Ven_w2)
#opal.symbol_import(o,'t1066_m_ds_Ven_w2', project='_Athlos_Harm_Dataset')
```



## UrbanPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_hearing_gen','10-66.1066-UrbanPeru-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local UrbanPeru w1, echo=F}
s1066_UrbanPeru_w1_hearing_gen <- opal.execute(o,'s1066_UrbanPeru_w1_hearing_gen')
vari <- s1066_UrbanPeru_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_hearing_gen$id)
t1066_ds_UP_w1$hearing_gen <- car::recode(s1066_UrbanPeru_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UP_w1$hearing_gen <- labelled(t1066_ds_UP_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
vari <- t1066_ds_UP_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$hearing_gen)
X<-table(s1066_UrbanPeru_w1_hearing_gen$PEAR)
nas<-length(s1066_UrbanPeru_w1_hearing_gen$PEAR)-length(na.omit(s1066_UrbanPeru_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL UrbanPeru w1, echo=FALSE}

label(t1066_ds_UP_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UP_w1
save(hearing_gen, file = "../RData/UP_w1/hearing_gen.RData")

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$hearing_gen <- car::recode(t1066_m_ds_UP_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanPeru-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |


```{r assign UrbanPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_hearing_gen','10-66.1066-UrbanPeru-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local UrbanPeru w2, echo=F}
s1066_UrbanPeru_w2_hearing_gen <- opal.execute(o,'s1066_UrbanPeru_w2_hearing_gen')
vari <- s1066_UrbanPeru_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanPeru_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_hearing_gen$id)
t1066_ds_UP_w2$hearing_gen <-  car::recode(s1066_UrbanPeru_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UP_w2$hearing_gen <- labelled(t1066_ds_UP_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=F}
vari <- t1066_ds_UP_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=F}
AfterH <- table(t1066_ds_UP_w2$hearing_gen)
X<-table(s1066_UrbanPeru_w2_hearing_gen$f_PEAR)
#nas<-length(s1066_UrbanPeru_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_UrbanPeru_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1")
kable(C)
```






```{r importOPAL UrbanPeru w2, echo=FALSE}

label(t1066_ds_UP_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UP_w2', t1066_ds_UP_w2)
#opal.symbol_import(o,'t1066_ds_UP_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UP_w2
save(hearing_gen, file = "../RData/UP_w2/hearing_gen.RData")

t1066_m_ds_UP_w2 <- t1066_ds_UP_w2
t1066_m_ds_UP_w2$hearing_gen <- car::recode(t1066_m_ds_UP_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w2', t1066_m_ds_UP_w2)
#opal.symbol_import(o,'t1066_m_ds_UP_w2', project='_Athlos_Harm_Dataset')
```



## RuralPeru

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_hearing_gen','10-66.1066-RuralPeru-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local RuralPeru w1, echo=F}
s1066_RuralPeru_w1_hearing_gen <- opal.execute(o,'s1066_RuralPeru_w1_hearing_gen')
vari <- s1066_RuralPeru_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_hearing_gen$id)
t1066_ds_RP_w1$hearing_gen <- car::recode(s1066_RuralPeru_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RP_w1$hearing_gen <- labelled(t1066_ds_RP_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
vari <- t1066_ds_RP_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$hearing_gen)
X<-table(s1066_RuralPeru_w1_hearing_gen$PEAR)
nas<-length(s1066_RuralPeru_w1_hearing_gen$PEAR)-length(na.omit(s1066_RuralPeru_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL RuralPeru w1, echo=FALSE}

label(t1066_ds_RP_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RP_w1
save(hearing_gen, file = "../RData/RP_w1/hearing_gen.RData")

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$hearing_gen <- car::recode(t1066_m_ds_RP_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralPeru-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |



```{r assign RuralPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_hearing_gen','10-66.1066-RuralPeru-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local RuralPeru w2, echo=F}
s1066_RuralPeru_w2_hearing_gen <- opal.execute(o,'s1066_RuralPeru_w2_hearing_gen')
vari <- s1066_RuralPeru_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralPeru_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_hearing_gen$id)
t1066_ds_RP_w2$hearing_gen <-  car::recode(s1066_RuralPeru_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RP_w2$hearing_gen <- labelled(t1066_ds_RP_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=F}
vari <- t1066_ds_RP_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=F}
AfterH <- table(t1066_ds_RP_w2$hearing_gen)
X<-table(s1066_RuralPeru_w2_hearing_gen$f_PEAR)
#nas<-length(s1066_RuralPeru_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_RuralPeru_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1")
kable(C)
```






```{r importOPAL RuralPeru w2, echo=FALSE}

label(t1066_ds_RP_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RP_w2', t1066_ds_RP_w2)
#opal.symbol_import(o,'t1066_ds_RP_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RP_w2
save(hearing_gen, file = "../RData/RP_w2/hearing_gen.RData")

t1066_m_ds_RP_w2 <- t1066_ds_RP_w2
t1066_m_ds_RP_w2$hearing_gen <- car::recode(t1066_m_ds_RP_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w2', t1066_m_ds_RP_w2)
#opal.symbol_import(o,'t1066_m_ds_RP_w2', project='_Athlos_Harm_Dataset')
```



## UrbanMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |



```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_hearing_gen','10-66.1066-UrbanMexico-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local UrbanMexico w1, echo=F}
s1066_UrbanMexico_w1_hearing_gen <- opal.execute(o,'s1066_UrbanMexico_w1_hearing_gen')
vari <- s1066_UrbanMexico_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_hearing_gen$id)
t1066_ds_UM_w1$hearing_gen <- car::recode(s1066_UrbanMexico_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UM_w1$hearing_gen <- labelled(t1066_ds_UM_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
vari <- t1066_ds_UM_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$hearing_gen)
X<-table(s1066_UrbanMexico_w1_hearing_gen$PEAR)
#nas<-length(s1066_UrbanMexico_w1_hearing_gen$PEAR)-length(na.omit(s1066_UrbanMexico_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1") 
kable(C)
```






```{r importOPAL UrbanMexico w1, echo=FALSE}

label(t1066_ds_UM_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UM_w1
save(hearing_gen, file = "../RData/UM_w1/hearing_gen.RData")

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$hearing_gen <- car::recode(t1066_m_ds_UM_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-UrbanMexico-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign UrbanMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_hearing_gen','10-66.1066-UrbanMexico-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local UrbanMexico w2, echo=F}
s1066_UrbanMexico_w2_hearing_gen <- opal.execute(o,'s1066_UrbanMexico_w2_hearing_gen')
vari <- s1066_UrbanMexico_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_UrbanMexico_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_hearing_gen$id)
t1066_ds_UM_w2$hearing_gen <-  car::recode(s1066_UrbanMexico_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_UM_w2$hearing_gen <- labelled(t1066_ds_UM_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=F}
vari <- t1066_ds_UM_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=F}
AfterH <- table(t1066_ds_UM_w2$hearing_gen)
X<-table(s1066_UrbanMexico_w2_hearing_gen$f_PEAR)
nas<-length(s1066_UrbanMexico_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_UrbanMexico_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL UrbanMexico w2, echo=FALSE}

label(t1066_ds_UM_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_UM_w2', t1066_ds_UM_w2)
#opal.symbol_import(o,'t1066_ds_UM_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_UM_w2
save(hearing_gen, file = "../RData/UM_w2/hearing_gen.RData")

t1066_m_ds_UM_w2 <- t1066_ds_UM_w2
t1066_m_ds_UM_w2$hearing_gen <- car::recode(t1066_m_ds_UM_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w2', t1066_m_ds_UM_w2)
#opal.symbol_import(o,'t1066_m_ds_UM_w2', project='_Athlos_Harm_Dataset')
```



## RuralMexico

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Description** |  |



```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_hearing_gen','10-66.1066-RuralMexico-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local RuralMexico w1, echo=F}
s1066_RuralMexico_w1_hearing_gen <- opal.execute(o,'s1066_RuralMexico_w1_hearing_gen')
vari <- s1066_RuralMexico_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_hearing_gen$id)
t1066_ds_RM_w1$hearing_gen <- car::recode(s1066_RuralMexico_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RM_w1$hearing_gen <- labelled(t1066_ds_RM_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
vari <- t1066_ds_RM_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$hearing_gen)
X<-table(s1066_RuralMexico_w1_hearing_gen$PEAR)
#nas<-length(s1066_RuralMexico_w1_hearing_gen$PEAR)-length(na.omit(s1066_RuralMexico_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1") 
kable(C)
```






```{r importOPAL RuralMexico w1, echo=FALSE}

label(t1066_ds_RM_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RM_w1
save(hearing_gen, file = "../RData/RM_w1/hearing_gen.RData")

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$hearing_gen <- car::recode(t1066_m_ds_RM_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-RuralMexico-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign RuralMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_hearing_gen','10-66.1066-RuralMexico-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local RuralMexico w2, echo=F}
s1066_RuralMexico_w2_hearing_gen <- opal.execute(o,'s1066_RuralMexico_w2_hearing_gen')
vari <- s1066_RuralMexico_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_RuralMexico_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_hearing_gen$id)
t1066_ds_RM_w2$hearing_gen <-  car::recode(s1066_RuralMexico_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_RM_w2$hearing_gen <- labelled(t1066_ds_RM_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=F}
vari <- t1066_ds_RM_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=F}
AfterH <- table(t1066_ds_RM_w2$hearing_gen)
X<-table(s1066_RuralMexico_w2_hearing_gen$f_PEAR)
nas<-length(s1066_RuralMexico_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_RuralMexico_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL RuralMexico w2, echo=FALSE}

label(t1066_ds_RM_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_RM_w2', t1066_ds_RM_w2)
#opal.symbol_import(o,'t1066_ds_RM_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_RM_w2
save(hearing_gen, file = "../RData/RM_w2/hearing_gen.RData")

t1066_m_ds_RM_w2 <- t1066_ds_RM_w2
t1066_m_ds_RM_w2$hearing_gen <- car::recode(t1066_m_ds_RM_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w2', t1066_m_ds_RM_w2)
#opal.symbol_import(o,'t1066_m_ds_RM_w2', project='_Athlos_Harm_Dataset')
```



## PuertoRico

### Wave 1 

#### Study-specific variable description




| **Name** | `PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_hearing_gen','10-66.1066-PuertoRico-Baseline', variables=list('PEAR'), missings = TRUE)
```

```{r local PuertoRico w1, echo=F}
s1066_PuertoRico_w1_hearing_gen <- opal.execute(o,'s1066_PuertoRico_w1_hearing_gen')
vari <- s1066_PuertoRico_w1_hearing_gen$PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w1_hearing_gen, aes(x=factor(PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_hearing_gen$id)
t1066_ds_PR_w1$hearing_gen <- car::recode(s1066_PuertoRico_w1_hearing_gen$PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_PR_w1$hearing_gen <- labelled(t1066_ds_PR_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
vari <- t1066_ds_PR_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$hearing_gen)
X<-table(s1066_PuertoRico_w1_hearing_gen$PEAR)
nas<-length(s1066_PuertoRico_w1_hearing_gen$PEAR)-length(na.omit(s1066_PuertoRico_w1_hearing_gen$PEAR))
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","0,1->1","NA->999") 
kable(C)
```






```{r importOPAL PuertoRico w1, echo=FALSE}

label(t1066_ds_PR_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_PR_w1
save(hearing_gen, file = "../RData/PR_w1/hearing_gen.RData")

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$hearing_gen <- car::recode(t1066_m_ds_PR_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `f_PEAR`|
|-|-|
| **Label** | `hearing problem` |
| **Table name** | `1066-PuertoRico-Followup` |
| **Categories** |`0 no problem; 1 has problem, interferes not at all; 2 has problem, interferes a little; 3 has problem, interferes a lot` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign PuertoRico w2, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_hearing_gen','10-66.1066-PuertoRico-Followup', variables=list('f_PEAR'), missings = TRUE)
```

```{r local PuertoRico w2, echo=F}
s1066_PuertoRico_w2_hearing_gen <- opal.execute(o,'s1066_PuertoRico_w2_hearing_gen')
vari <- s1066_PuertoRico_w2_hearing_gen$f_PEAR
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "f_PEAR")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(s1066_PuertoRico_w2_hearing_gen, aes(x=factor(f_PEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 1`
* `2 into 0` 
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_hearing_gen$id)
t1066_ds_PR_w2$hearing_gen <-  car::recode(s1066_PuertoRico_w2_hearing_gen$f_PEAR, "0 = '1';1='1';2 = '0';3='0';NA='999'")
t1066_ds_PR_w2$hearing_gen <- labelled(t1066_ds_PR_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=F}
vari <- t1066_ds_PR_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=F}
AfterH <- table(t1066_ds_PR_w2$hearing_gen)
X<-table(s1066_PuertoRico_w2_hearing_gen$f_PEAR)
nas<-length(s1066_PuertoRico_w2_hearing_gen$f_PEAR)-length(na.omit(s1066_PuertoRico_w2_hearing_gen$f_PEAR))
BeforeH <-c(sum(X[3:4]),sum(X[1:2]),nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```






```{r importOPAL PuertoRico w2, echo=FALSE}

label(t1066_ds_PR_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 't1066_ds_PR_w2', t1066_ds_PR_w2)
#opal.symbol_import(o,'t1066_ds_PR_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- t1066_ds_PR_w2
save(hearing_gen, file = "../RData/PR_w2/hearing_gen.RData")

t1066_m_ds_PR_w2 <- t1066_ds_PR_w2
t1066_m_ds_PR_w2$hearing_gen <- car::recode(t1066_m_ds_PR_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w2', t1066_m_ds_PR_w2)
#opal.symbol_import(o,'t1066_m_ds_PR_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
