---
title: "Hearing a conversation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_conv`
* Variable label: `Difficulty for hearing what is said in a conversation`
* Variable description: `It measures if the participant experiences some difficulty (including total disability) for following a conversation  (i.e., if there is a background noise, or several people talking) or not, using a hearing aid as usual.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Australia

### Wave 1

#### Study-specific variable description




| **Name** | `BACKGRND`|
|-|-|
| **Label** | `Difficulty with conversation with background noise` |
| **Table name** | `ALSA-Wave1` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `9 = Missing` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_hearing_conv','ALSA.ALSA-Wave1', variables=list('BACKGRND'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_hearing_conv <- opal.execute(o,'ALSA_w1_hearing_conv')
vari <- ALSA_w1_hearing_conv$BACKGRND
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "BACKGRND")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_hearing_conv, aes(x=factor(BACKGRND))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_hearing_conv$id)
ALSA_ds_w1$hearing_conv <- car::recode(ALSA_w1_hearing_conv$BACKGRND, "1 = '0';2 = '1';9 = '999'; NA = '999' ")
ALSA_ds_w1$hearing_conv <- labelled(ALSA_ds_w1$hearing_conv, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$hearing_conv
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_conv")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(hearing_conv))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$hearing_conv)
X<-table(ALSA_w1_hearing_conv$BACKGRND)
BeforeH <- c((X[1]),X[2],X[3]+sum(is.na(ALSA_w1_hearing_conv$BACKGRND)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$hearing_conv) <- "Difficulty for hearing what is said in a conversation"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
hearing_conv <- ALSA_ds_w1
save(hearing_conv, file = "../RData/w1/hearing_conv.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$hearing_conv <- car::recode(ALSA_m_ds_w1$hearing_conv, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.



### Wave 3

#### Study-specific variable description




| **Name** | `BACKGRW3`|
|-|-|
| **Label** | `Difficulty with conversation with background noise` |
| **Table name** | `ALSA-Wave3` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `9 = Missing` |
| **Description** |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_hearing_conv','ALSA.ALSA-Wave3', variables=list('BACKGRW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_hearing_conv <- opal.execute(o,'ALSA_w3_hearing_conv')
vari <- ALSA_w3_hearing_conv$BACKGRW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "BACKGRW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_hearing_conv, aes(x=factor(BACKGRW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_hearing_conv$id)
ALSA_ds_w3$hearing_conv <- car::recode(ALSA_w3_hearing_conv$BACKGRW3, "1 = '0';2 = '1';9 = '999'; NA = '999' ")
ALSA_ds_w3$hearing_conv <- labelled(ALSA_ds_w3$hearing_conv, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$hearing_conv
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_conv")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(hearing_conv))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$hearing_conv)
X<-table(ALSA_w3_hearing_conv$BACKGRW3)
BeforeH <- c((X[1]),X[2],X[3]+sum(is.na(ALSA_w3_hearing_conv$BACKGRW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$hearing_conv) <- "Difficulty for hearing what is said in a conversation"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
hearing_conv <- ALSA_ds_w3
save(hearing_conv, file = "../RData/w3/hearing_conv.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$hearing_conv <- car::recode(ALSA_m_ds_w3$hearing_conv, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.

### Wave 8

Not found.

### Wave 9

Not found.

### Wave 10

Not found.

### Wave 11

Not found.

### Wave 12

Not found.

### Wave 13

Not found.



# Quality estimation

The variable is not exaclty the same, but the content seems transposable. 



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
