---
title: "Mobility - Walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_walk`
* Variable label: `Mobility - walking`
* Variable description: `Difficulty for walking by yourself and without using any special equipment`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


## Australia

### Wave 1

#### Study-specific variable description




| **Name** | `WLKHLFML`|
|-|-|
| **Label** | `Able to walk half mile without help` |
| **Table name** | `ALSA-Wave1` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `9 = Missing; NA` |
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_mob_walk','ALSA.ALSA-Wave1', variables=list('WLKHLFML'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_mob_walk <- opal.execute(o,'ALSA_w1_mob_walk')
vari <- ALSA_w1_mob_walk$WLKHLFML
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "WLKHLFML")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_mob_walk, aes(x=factor(WLKHLFML))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_mob_walk$id)
ALSA_ds_w1$mob_walk <- car::recode(ALSA_w1_mob_walk$WLKHLFML, "1 = '1';2 = '0';9 = '999';NA = '999' ")
ALSA_ds_w1$mob_walk <- labelled(ALSA_ds_w1$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$mob_walk)
X<-table(ALSA_w1_mob_walk$WLKHLFML)
BeforeH <- c((X[2:1]),X[c(3)]+sum(is.na(ALSA_w1_mob_walk$WLKHLFML)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w1
save(mob_walk, file = "../RData/w1/mob_walk.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$mob_walk <- car::recode(ALSA_m_ds_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `Q28`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave2` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2_mob_walk','ALSA.ALSA-Wave2', variables=list('Q28'), missings = TRUE)
```

```{r local w2, echo=F}
ALSA_w2_mob_walk <- opal.execute(o,'ALSA_w2_mob_walk')
vari <- ALSA_w2_mob_walk$Q28
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Q28")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w2_mob_walk, aes(x=factor(Q28))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `NA into 999`

**R script:**
```{r harmo w2}
ALSA_ds_w2 <- tibble(id=ALSA_w2_mob_walk$id)
ALSA_ds_w2$mob_walk <- car::recode(ALSA_w2_mob_walk$Q28, "1 = '1';2 = '0';NA = '999' ")
ALSA_ds_w2$mob_walk <- labelled(ALSA_ds_w2$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ALSA_ds_w2$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ALSA_ds_w2$mob_walk)
X<-table(ALSA_w2_mob_walk$Q28)
BeforeH <- c((X[2:1]),sum(is.na(ALSA_w2_mob_walk$Q28)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(ALSA_ds_w2$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w2
save(mob_walk, file = "../RData/w2/mob_walk.RData")

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$mob_walk <- car::recode(ALSA_m_ds_w2$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `WLKHLFW3`|
|-|-|
| **Label** | `Able to walk half mile without help` |
| **Table name** | `ALSA-Wave3` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_mob_walk','ALSA.ALSA-Wave3', variables=list('WLKHLFW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_mob_walk <- opal.execute(o,'ALSA_w3_mob_walk')
vari <- ALSA_w3_mob_walk$WLKHLFW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "WLKHLFW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_mob_walk, aes(x=factor(WLKHLFW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_mob_walk$id)
ALSA_ds_w3$mob_walk <- car::recode(ALSA_w3_mob_walk$WLKHLFW3, "1 = '1';2 = '0';9 = '999';NA = '999' ")
ALSA_ds_w3$mob_walk <- labelled(ALSA_ds_w3$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$mob_walk)
X<-table(ALSA_w3_mob_walk$WLKHLFW3)
BeforeH <- c((X[2:1]),X[3]+sum(is.na(ALSA_w3_mob_walk$WLKHLFW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w3
save(mob_walk, file = "../RData/w3/mob_walk.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$mob_walk <- car::recode(ALSA_m_ds_w3$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description




| **Name** | `WLKHLFW4`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave4` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `-1 = Don't know` |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4_mob_walk','ALSA.ALSA-Wave4', variables=list('WLKHLFW4'), missings = TRUE)
```

```{r local w4, echo=F}
ALSA_w4_mob_walk <- opal.execute(o,'ALSA_w4_mob_walk')
vari <- ALSA_w4_mob_walk$WLKHLFW4
kable(Categorical_summary(vari, missing_values = c(-1))[3], caption = "WLKHLFW4")
kable(Categorical_summary(vari, missing_values = c(-1))[1], caption = "Category")
ggplot(ALSA_w4_mob_walk, aes(x=factor(WLKHLFW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `-1 into 998`

**R script:**
```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_mob_walk$id)
ALSA_ds_w4$mob_walk <- car::recode(ALSA_w4_mob_walk$WLKHLFW4, "1 = '1';2 = '0';-1 = '998' ")
ALSA_ds_w4$mob_walk <- labelled(ALSA_ds_w4$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ALSA_ds_w4$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ALSA_ds_w4$mob_walk)
X<-table(ALSA_w4_mob_walk$WLKHLFW4)
BeforeH <- c(X[3:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","-1->998") 
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(ALSA_ds_w4$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w4
save(mob_walk, file = "../RData/w4/mob_walk.RData")

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$mob_walk <- car::recode(ALSA_m_ds_w4$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description




| **Name** | `WLKHLFW5`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave5` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `3 = Don't know` |
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5_mob_walk','ALSA.ALSA-Wave5', variables=list('WLKHLFW5'), missings = TRUE)
```

```{r local w5, echo=F}
ALSA_w5_mob_walk <- opal.execute(o,'ALSA_w5_mob_walk')
vari <- ALSA_w5_mob_walk$WLKHLFW5
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "WLKHLFW5")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(ALSA_w5_mob_walk, aes(x=factor(WLKHLFW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 998`

**R script:**
```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_mob_walk$id)
ALSA_ds_w5$mob_walk <- car::recode(ALSA_w5_mob_walk$WLKHLFW5, "1 = '1';2 = '0';3 = '998' ")
ALSA_ds_w5$mob_walk <- labelled(ALSA_ds_w5$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ALSA_ds_w5$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ALSA_ds_w5$mob_walk)
X<-table(ALSA_w5_mob_walk$WLKHLFW5)
BeforeH <- X[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","3->998") 
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(ALSA_ds_w5$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w5
save(mob_walk, file = "../RData/w5/mob_walk.RData")

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$mob_walk <- car::recode(ALSA_m_ds_w5$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6

#### Study-specific variable description




| **Name** | `WLKHLFW6`|
|-|-|
| **Label** | `able to walk half a mile` |
| **Table name** | `ALSA-Wave6` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_mob_walk','ALSA.ALSA-Wave6', variables=list('WLKHLFW6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_mob_walk <- opal.execute(o,'ALSA_w6_mob_walk')
vari <- ALSA_w6_mob_walk$WLKHLFW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "WLKHLFW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_mob_walk, aes(x=factor(WLKHLFW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `0 into 995`
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_mob_walk$id)
ALSA_ds_w6$mob_walk <- car::recode(ALSA_w6_mob_walk$WLKHLFW6, "1 = '1';2 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$mob_walk <- labelled(ALSA_ds_w6$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$mob_walk)
X<-table(ALSA_w6_mob_walk$WLKHLFW6)
BeforeH <- c(X[c(3:1)],sum(is.na(ALSA_w6_mob_walk$WLKHLFW6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w6
save(mob_walk, file = "../RData/w6/mob_walk.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$mob_walk <- car::recode(ALSA_m_ds_w6$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `wlkhlfw7`|
|-|-|
| **Label** | `able to walk half a mile` |
| **Table name** | `ALSA-Wave7` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `0 = Not answered; NA` |
| **Description** |  |


```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_mob_walk','ALSA.ALSA-Wave7', variables=list('wlkhlfw7'), missings = TRUE)
```

```{r local w7, echo=F}
ALSA_w7_mob_walk <- opal.execute(o,'ALSA_w7_mob_walk')
vari <- ALSA_w7_mob_walk$wlkhlfw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "wlkhlfw7")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7_mob_walk, aes(x=factor(wlkhlfw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `0 into 995`
* `NA into 999`

**R script:**
```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_mob_walk$id)
ALSA_ds_w7$mob_walk <- car::recode(ALSA_w7_mob_walk$wlkhlfw7, "1 = '1';2 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$mob_walk <- labelled(ALSA_ds_w7$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ALSA_ds_w7$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$mob_walk)
X<-table(ALSA_w7_mob_walk$wlkhlfw7)
BeforeH <- c(X[c(3:1)],sum(is.na(ALSA_w7_mob_walk$wlkhlfw7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w7
save(mob_walk, file = "../RData/w7/mob_walk.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$mob_walk <- car::recode(ALSA_m_ds_w7$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

#### Study-specific variable description




| **Name** | `wlkhlfw8`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave8` |
| **Categories** |`1 = Yes; 2 = No`|
| **Description** |  |


```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_mob_walk','ALSA.ALSA-Wave8', variables=list('wlkhlfw8'), missings = TRUE)
```

```{r local w8, echo=F}
ALSA_w8_mob_walk <- opal.execute(o,'ALSA_w8_mob_walk')
vari <- ALSA_w8_mob_walk$wlkhlfw8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "wlkhlfw8")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8_mob_walk, aes(x=factor(wlkhlfw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 

**R script:**
```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_mob_walk$id)
ALSA_ds_w8$mob_walk <- car::recode(ALSA_w8_mob_walk$wlkhlfw8, "1 = '1';2 = '0' ")
ALSA_ds_w8$mob_walk <- labelled(ALSA_ds_w8$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vari <- ALSA_ds_w8$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$mob_walk)
X<-table(ALSA_w8_mob_walk$wlkhlfw8)
BeforeH <- c(X[c(2:1)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1") 
kable(C)
```






```{r importOPAL w8, echo=FALSE}

label(ALSA_ds_w8$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w8
save(mob_walk, file = "../RData/w8/mob_walk.RData")

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$mob_walk <- car::recode(ALSA_m_ds_w8$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9

#### Study-specific variable description




| **Name** | `WLKHLFW9`|
|-|-|
| **Label** | `able to walk half a mile` |
| **Table name** | `ALSA-Wave9` |
| **Categories** |`1 = Yes; 2 = No`|
| **Missings** | `NA` |
| **Description** |  |


```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_mob_walk','ALSA.ALSA-Wave9', variables=list('WLKHLFW9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_mob_walk <- opal.execute(o,'ALSA_w9_mob_walk')
vari <- ALSA_w9_mob_walk$WLKHLFW9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "WLKHLFW9")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_mob_walk, aes(x=factor(WLKHLFW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_mob_walk$id)
ALSA_ds_w9$mob_walk <- car::recode(ALSA_w9_mob_walk$WLKHLFW9, "1 = '1';2 = '0';NA = '999' ")
ALSA_ds_w9$mob_walk <- labelled(ALSA_ds_w9$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$mob_walk)
X<-table(ALSA_w9_mob_walk$WLKHLFW9)
BeforeH <- c(X[c(2:1)],sum(is.na(ALSA_w9_mob_walk$WLKHLFW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w9
save(mob_walk, file = "../RData/w9/mob_walk.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$mob_walk <- car::recode(ALSA_m_ds_w9$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description




| **Name** | `wlkhlfw10`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave10` |
| **Categories** |`1 = Yes; 0 = No`|
| **Description** |  |

```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_mob_walk','ALSA.ALSA-Wave10', variables=list('wlkhlfw10'), missings = TRUE)
```

```{r local w10, echo=F}
ALSA_w10_mob_walk <- opal.execute(o,'ALSA_w10_mob_walk')
vari <- ALSA_w10_mob_walk$wlkhlfw10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "wlkhlfw10")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10_mob_walk, aes(x=factor(wlkhlfw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0` 

**R script:**
```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_mob_walk$id)
ALSA_ds_w10$mob_walk <- car::recode(ALSA_w10_mob_walk$wlkhlfw10, "1 = '1';0 = '0' ")
ALSA_ds_w10$mob_walk <- labelled(ALSA_ds_w10$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vari <- ALSA_ds_w10$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=F}
AfterH <- table(ALSA_ds_w10$mob_walk)
X<-table(ALSA_w10_mob_walk$wlkhlfw10)
BeforeH <- c(X[c(1:2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```






```{r importOPAL w10, echo=FALSE}

label(ALSA_ds_w10$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w10
save(mob_walk, file = "../RData/w10/mob_walk.RData")

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$mob_walk <- car::recode(ALSA_m_ds_w10$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description




| **Name** | `WLKHLFW11`|
|-|-|
| **Label** | `Able to walk half a mile` |
| **Table name** | `ALSA-Wave11` |
| **Categories** |`1 = Yes; 0 = No`|
| **Missings** | `NA` |
| **Description** |  |


```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_mob_walk','ALSA.ALSA-Wave11', variables=list('WLKHLFW11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_mob_walk <- opal.execute(o,'ALSA_w11_mob_walk')
vari <- ALSA_w11_mob_walk$WLKHLFW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "WLKHLFW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_mob_walk, aes(x=factor(WLKHLFW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0` 
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_mob_walk$id)
ALSA_ds_w11$mob_walk <- car::recode(ALSA_w11_mob_walk$WLKHLFW11, "1 = '1';0 = '0';NA = '999' ")
ALSA_ds_w11$mob_walk <- labelled(ALSA_ds_w11$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$mob_walk)
X<-table(ALSA_w11_mob_walk$WLKHLFW11)
BeforeH <- c(X[c(1:2)],sum(is.na(ALSA_w11_mob_walk$WLKHLFW11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w11
save(mob_walk, file = "../RData/w11/mob_walk.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$mob_walk <- car::recode(ALSA_m_ds_w11$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description




| **Name** | `WLKHLFW12`|
|-|-|
| **Label** | `Able to walk half a mile` |
| **Table name** | `ALSA-Wave12` |
| **Categories** |`1 = Yes; 0 = No`|
| **Description** |  |

```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_mob_walk','ALSA.ALSA-Wave12', variables=list('WLKHLFW12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_mob_walk <- opal.execute(o,'ALSA_w12_mob_walk')
vari <- ALSA_w12_mob_walk$WLKHLFW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "WLKHLFW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_mob_walk, aes(x=factor(WLKHLFW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0` 

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_mob_walk$id)
ALSA_ds_w12$mob_walk <- car::recode(ALSA_w12_mob_walk$WLKHLFW12, "1 = '1';0 = '0' ")
ALSA_ds_w12$mob_walk <- labelled(ALSA_ds_w12$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$mob_walk)
X<-table(ALSA_w12_mob_walk$WLKHLFW12)
BeforeH <- c(X[c(1:2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w12
save(mob_walk, file = "../RData/w12/mob_walk.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$mob_walk <- car::recode(ALSA_m_ds_w12$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description




| **Name** | `WLKHLFW13`|
|-|-|
| **Label** | `Walk half a mile without help?` |
| **Table name** | `ALSA-Wave13` |
| **Categories** |`1 = Yes; 0 = No`|
| **Description** |  |


```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_mob_walk','ALSA.ALSA-Wave13', variables=list('WLKHLFW13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_mob_walk <- opal.execute(o,'ALSA_w13_mob_walk')
vari <- ALSA_w13_mob_walk$WLKHLFW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "WLKHLFW13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_mob_walk, aes(x=factor(WLKHLFW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0` 

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_mob_walk$id)
ALSA_ds_w13$mob_walk <- car::recode(ALSA_w13_mob_walk$WLKHLFW13, "1 = '1';0 = '0' ")
ALSA_ds_w13$mob_walk <- labelled(ALSA_ds_w13$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$mob_walk)
X<-table(ALSA_w13_mob_walk$WLKHLFW13)
BeforeH <- c(X[c(1:2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
mob_walk <- ALSA_ds_w13
save(mob_walk, file = "../RData/w13/mob_walk.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$mob_walk <- car::recode(ALSA_m_ds_w13$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```




# Quality estimation
This study used 0.5 miles as the unit of reference while other studies used 100 yards, 100m, 1km, 2km...


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
