---
title: "Mobility - Stooping, kneeling, crouching"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_stoop`
* Variable label: `Difficulty for stooping, kneeling or crouching`
* Variable description: `Difficulty for stooping, kneeling or crouching`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Australia

### Wave 1

#### Study-specific variable description




| **Name** | `STPCRKNL`|
|-|-|
| **Label** | `What about stooping, crouching or kneeling` |
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`9 = Missing; NA`|
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_mob_stoop','ALSA.ALSA-Wave1', variables=list('STPCRKNL'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_mob_stoop <- opal.execute(o,'ALSA_w1_mob_stoop')
vari <- ALSA_w1_mob_stoop$STPCRKNL
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "STPCRKNL")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_mob_stoop, aes(x=factor(STPCRKNL))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_mob_stoop$id)
ALSA_ds_w1$mob_stoop <- car::recode(ALSA_w1_mob_stoop$STPCRKNL, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '999';NA = '999' ")
ALSA_ds_w1$mob_stoop <- labelled(ALSA_ds_w1$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$mob_stoop)
X<-table(ALSA_w1_mob_stoop$STPCRKNL)
BeforeH <- c(sum(X[c(2:5)]),X[1],X[6]+sum(is.na(ALSA_w1_mob_stoop$STPCRKNL)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w1
save(mob_stoop, file = "../RData/w1/mob_stoop.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$mob_stoop <- car::recode(ALSA_m_ds_w1$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `Q30`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave2`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2_mob_stoop','ALSA.ALSA-Wave2', variables=list('Q30'), missings = TRUE)
```

```{r local w2, echo=F}
ALSA_w2_mob_stoop <- opal.execute(o,'ALSA_w2_mob_stoop')
vari <- ALSA_w2_mob_stoop$Q30
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Q30")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w2_mob_stoop, aes(x=factor(Q30))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 

**R script:**
```{r harmo w2}
ALSA_ds_w2 <- tibble(id=ALSA_w2_mob_stoop$id)
ALSA_ds_w2$mob_stoop <- car::recode(ALSA_w2_mob_stoop$Q30, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'")
ALSA_ds_w2$mob_stoop <- labelled(ALSA_ds_w2$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ALSA_ds_w2$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ALSA_ds_w2$mob_stoop)
X<-table(ALSA_w2_mob_stoop$Q30)
BeforeH <- c(sum(X[c(2:5)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(ALSA_ds_w2$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w2
save(mob_stoop, file = "../RData/w2/mob_stoop.RData")

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$mob_stoop <- car::recode(ALSA_m_ds_w2$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `STPCRKW3`|
|-|-|
| **Label** | `Stooping, crouching or kneeling` |
| **Table name** |`ALSA-Wave3`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`9 = Missing; NA`|
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_mob_stoop','ALSA.ALSA-Wave3', variables=list('STPCRKW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_mob_stoop <- opal.execute(o,'ALSA_w3_mob_stoop')
vari <- ALSA_w3_mob_stoop$STPCRKW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "STPCRKW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_mob_stoop, aes(x=factor(STPCRKW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_mob_stoop$id)
ALSA_ds_w3$mob_stoop <- car::recode(ALSA_w3_mob_stoop$STPCRKW3, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '999'; NA = '999' ")
ALSA_ds_w3$mob_stoop <- labelled(ALSA_ds_w3$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$mob_stoop)
X<-table(ALSA_w3_mob_stoop$STPCRKW3)
BeforeH <- c(sum(X[c(2:5)]),X[1],X[6]+sum(is.na(ALSA_w3_mob_stoop$STPCRKW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w3
save(mob_stoop, file = "../RData/w3/mob_stoop.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$mob_stoop <- car::recode(ALSA_m_ds_w3$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description




| **Name** | `STPCRKW4`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave4`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4_mob_stoop','ALSA.ALSA-Wave4', variables=list('STPCRKW4'), missings = TRUE)
```

```{r local w4, echo=F}
ALSA_w4_mob_stoop <- opal.execute(o,'ALSA_w4_mob_stoop')
vari <- ALSA_w4_mob_stoop$STPCRKW4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "STPCRKW4")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4_mob_stoop, aes(x=factor(STPCRKW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_mob_stoop$id)
ALSA_ds_w4$mob_stoop <- car::recode(ALSA_w4_mob_stoop$STPCRKW4, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
ALSA_ds_w4$mob_stoop <- labelled(ALSA_ds_w4$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ALSA_ds_w4$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ALSA_ds_w4$mob_stoop)
X<-table(ALSA_w4_mob_stoop$STPCRKW4)
BeforeH <- c(sum(X[c(2:5)]),X[1],sum(is.na(ALSA_w4_mob_stoop$STPCRKW4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(ALSA_ds_w4$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w4
save(mob_stoop, file = "../RData/w4/mob_stoop.RData")

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$mob_stoop <- car::recode(ALSA_m_ds_w4$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description




| **Name** | `STPCRKW5`|
|-|-|
| **Label** | `What about stooping, crouching, or kneeling?` |
| **Table name** |`ALSA-Wave5`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`6 = Refused`|
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5_mob_stoop','ALSA.ALSA-Wave5', variables=list('STPCRKW5'), missings = TRUE)
```

```{r local w5, echo=F}
ALSA_w5_mob_stoop <- opal.execute(o,'ALSA_w5_mob_stoop')
vari <- ALSA_w5_mob_stoop$STPCRKW5
kable(Categorical_summary(vari, missing_values = c(6))[3], caption = "STPCRKW5")
kable(Categorical_summary(vari, missing_values = c(6))[1], caption = "Category")
ggplot(ALSA_w5_mob_stoop, aes(x=factor(STPCRKW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `6 into 997` 

**R script:**
```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_mob_stoop$id)
ALSA_ds_w5$mob_stoop <- car::recode(ALSA_w5_mob_stoop$STPCRKW5, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';6 = '997' ")
ALSA_ds_w5$mob_stoop <- labelled(ALSA_ds_w5$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ALSA_ds_w5$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ALSA_ds_w5$mob_stoop)
X<-table(ALSA_w5_mob_stoop$STPCRKW5)
BeforeH <- c(sum(X[c(2:5)]),X[1],X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","6->997") 
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(ALSA_ds_w5$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w5
save(mob_stoop, file = "../RData/w5/mob_stoop.RData")

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$mob_stoop <- car::recode(ALSA_m_ds_w5$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6

#### Study-specific variable description




| **Name** | `STPCRKW6`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave6`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`0 = No answer; NA`|
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_mob_stoop','ALSA.ALSA-Wave6', variables=list('STPCRKW6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_mob_stoop <- opal.execute(o,'ALSA_w6_mob_stoop')
vari <- ALSA_w6_mob_stoop$STPCRKW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "STPCRKW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_mob_stoop, aes(x=factor(STPCRKW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_mob_stoop$id)
ALSA_ds_w6$mob_stoop <- car::recode(ALSA_w6_mob_stoop$STPCRKW6, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$mob_stoop <- labelled(ALSA_ds_w6$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$mob_stoop)
X<-table(ALSA_w6_mob_stoop$STPCRKW6)
BeforeH <- c(sum(X[c(3:6)]),X[2],X[1],sum(is.na(ALSA_w6_mob_stoop$STPCRKW6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w6
save(mob_stoop, file = "../RData/w6/mob_stoop.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$mob_stoop <- car::recode(ALSA_m_ds_w6$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `stpcrkw7`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave7`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`0 = No answer; NA`|
| **Description** |  |


```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_mob_stoop','ALSA.ALSA-Wave7', variables=list('stpcrkw7'), missings = TRUE)
```

```{r local w7, echo=F}
ALSA_w7_mob_stoop <- opal.execute(o,'ALSA_w7_mob_stoop')
vari <- ALSA_w7_mob_stoop$stpcrkw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "stpcrkw7")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7_mob_stoop, aes(x=factor(stpcrkw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_mob_stoop$id)
ALSA_ds_w7$mob_stoop <- car::recode(ALSA_w7_mob_stoop$stpcrkw7, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$mob_stoop <- labelled(ALSA_ds_w7$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ALSA_ds_w7$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$mob_stoop)
X<-table(ALSA_w7_mob_stoop$stpcrkw7)
BeforeH <- c(sum(X[c(3:6)]),X[2],X[1],sum(is.na(ALSA_w7_mob_stoop$stpcrkw7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w7
save(mob_stoop, file = "../RData/w7/mob_stoop.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$mob_stoop <- car::recode(ALSA_m_ds_w7$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

#### Study-specific variable description




| **Name** | `stpcrkw8`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave8`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`0 = No answer`|
| **Description** |  |


```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_mob_stoop','ALSA.ALSA-Wave8', variables=list('stpcrkw8'), missings = TRUE)
```

```{r local w8, echo=F}
ALSA_w8_mob_stoop <- opal.execute(o,'ALSA_w8_mob_stoop')
vari <- ALSA_w8_mob_stoop$stpcrkw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "stpcrkw8")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w8_mob_stoop, aes(x=factor(stpcrkw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `0 into 995` 

**R script:**
```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_mob_stoop$id)
ALSA_ds_w8$mob_stoop <- car::recode(ALSA_w8_mob_stoop$stpcrkw8, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';0 = '995' ")
ALSA_ds_w8$mob_stoop <- labelled(ALSA_ds_w8$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vari <- ALSA_ds_w8$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$mob_stoop)
X<-table(ALSA_w8_mob_stoop$stpcrkw8)
BeforeH <- c(sum(X[c(3:6)]),X[2],X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","0->995") 
kable(C)
```






```{r importOPAL w8, echo=FALSE}

label(ALSA_ds_w8$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w8
save(mob_stoop, file = "../RData/w8/mob_stoop.RData")

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$mob_stoop <- car::recode(ALSA_m_ds_w8$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9

#### Study-specific variable description




| **Name** | `STPCRKW9`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave9`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`0 = No answer; NA`|
| **Description** |  |


```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_mob_stoop','ALSA.ALSA-Wave9', variables=list('STPCRKW9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_mob_stoop <- opal.execute(o,'ALSA_w9_mob_stoop')
vari <- ALSA_w9_mob_stoop$STPCRKW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "STPCRKW9")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9_mob_stoop, aes(x=factor(STPCRKW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_mob_stoop$id)
ALSA_ds_w9$mob_stoop <- car::recode(ALSA_w9_mob_stoop$STPCRKW9, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';0 = '995';NA = '999' ")
ALSA_ds_w9$mob_stoop <- labelled(ALSA_ds_w9$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$mob_stoop)
X<-table(ALSA_w9_mob_stoop$STPCRKW9)
BeforeH <- c(sum(X[c(3:6)]),X[2],X[1],sum(is.na(ALSA_w9_mob_stoop$STPCRKW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w9
save(mob_stoop, file = "../RData/w9/mob_stoop.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$mob_stoop <- car::recode(ALSA_m_ds_w9$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description




| **Name** | `stpcrkw10`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave10`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Description** |  |


```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_mob_stoop','ALSA.ALSA-Wave10', variables=list('stpcrkw10'), missings = TRUE)
```

```{r local w10, echo=F}
ALSA_w10_mob_stoop <- opal.execute(o,'ALSA_w10_mob_stoop')
vari <- ALSA_w10_mob_stoop$stpcrkw10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "stpcrkw10")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10_mob_stoop, aes(x=factor(stpcrkw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 

**R script:**
```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_mob_stoop$id)
ALSA_ds_w10$mob_stoop <- car::recode(ALSA_w10_mob_stoop$stpcrkw10, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0' ")
ALSA_ds_w10$mob_stoop <- labelled(ALSA_ds_w10$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vari <- ALSA_ds_w10$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=F}
AfterH <- table(ALSA_ds_w10$mob_stoop)
X<-table(ALSA_w10_mob_stoop$stpcrkw10)
BeforeH <- c(sum(X[c(2:5)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1") 
kable(C)
```






```{r importOPAL w10, echo=FALSE}

label(ALSA_ds_w10$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w10
save(mob_stoop, file = "../RData/w10/mob_stoop.RData")

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$mob_stoop <- car::recode(ALSA_m_ds_w10$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description




| **Name** | `STPCRKW11`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave11`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_mob_stoop','ALSA.ALSA-Wave11', variables=list('STPCRKW11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_mob_stoop <- opal.execute(o,'ALSA_w11_mob_stoop')
vari <- ALSA_w11_mob_stoop$STPCRKW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "STPCRKW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_mob_stoop, aes(x=factor(STPCRKW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_mob_stoop$id)
ALSA_ds_w11$mob_stoop <- car::recode(ALSA_w11_mob_stoop$STPCRKW11, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
ALSA_ds_w11$mob_stoop <- labelled(ALSA_ds_w11$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$mob_stoop)
X<-table(ALSA_w11_mob_stoop$STPCRKW11)
BeforeH <- c(sum(X[c(2:5)]),X[1],sum(is.na((ALSA_w11_mob_stoop$STPCRKW11))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w11
save(mob_stoop, file = "../RData/w11/mob_stoop.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$mob_stoop <- car::recode(ALSA_m_ds_w11$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description




| **Name** | `STPCRKW12`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave12`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Description** |  |


```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_mob_stoop','ALSA.ALSA-Wave12', variables=list('STPCRKW12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_mob_stoop <- opal.execute(o,'ALSA_w12_mob_stoop')
vari <- ALSA_w12_mob_stoop$STPCRKW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "STPCRKW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_mob_stoop, aes(x=factor(STPCRKW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_mob_stoop$id)
ALSA_ds_w12$mob_stoop <- car::recode(ALSA_w12_mob_stoop$STPCRKW12, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0' ")
ALSA_ds_w12$mob_stoop <- labelled(ALSA_ds_w12$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$mob_stoop)
X<-table(ALSA_w12_mob_stoop$STPCRKW12)
BeforeH <- c(sum(X[c(2:5)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w12
save(mob_stoop, file = "../RData/w12/mob_stoop.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$mob_stoop <- car::recode(ALSA_m_ds_w12$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description




| **Name** | `STPCRKW13`|
|-|-|
| **Label** | `Difficulty stooping/crouching/kneeling` |
| **Table name** |`ALSA-Wave13`|
| **Categories** |`1 = No difficulty at all; 2 = A little difficulty; 3 = Some difficulty; 4 = A lot of difficulty; 5 = Just unable to do it`|
| **Description** |  |


```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_mob_stoop','ALSA.ALSA-Wave13', variables=list('STPCRKW13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_mob_stoop <- opal.execute(o,'ALSA_w13_mob_stoop')
vari <- ALSA_w13_mob_stoop$STPCRKW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "STPCRKW13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_mob_stoop, aes(x=factor(STPCRKW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_mob_stoop$id)
ALSA_ds_w13$mob_stoop <- car::recode(ALSA_w13_mob_stoop$STPCRKW13, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0' ")
ALSA_ds_w13$mob_stoop <- labelled(ALSA_ds_w13$mob_stoop, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$mob_stoop
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_stoop")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(mob_stoop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Stooping, Crouching or Kneeling") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$mob_stoop)
X<-table(ALSA_w13_mob_stoop$STPCRKW13)
BeforeH <- c(sum(X[c(2:5)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$mob_stoop) <- "Difficulty for stooping, kneeling or crouching"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
mob_stoop <- ALSA_ds_w13
save(mob_stoop, file = "../RData/w13/mob_stoop.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$mob_stoop <- car::recode(ALSA_m_ds_w13$mob_stoop, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```

# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
