---
title: "ADL - Using the toilet"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_toilet`
* Variable label: `ADL-Difficulties for using the toilet`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 
## Australian population

### Wave 1

#### Study-specific variable description

 


* Name: `DIFFIC5`
* Label: `Difficulty with: Toileting`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `NA`

* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_adl_toilet','ALSA.ALSA-Wave1', variables=list('DIFFIC5'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
ALSA_w1_adl_toilet <- opal.execute(o,'ALSA_w1_adl_toilet')
#Categorical_summary(ALSA_w1_adl_toilet$DIFFIC5)
vari <- ALSA_w1_adl_toilet$DIFFIC5 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")




ggplot(ALSA_w1_adl_toilet, aes(x=factor(DIFFIC5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_adl_toilet$id)
ALSA_ds_w1$adl_toilet <- car::recode(ALSA_w1_adl_toilet$DIFFIC5, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w1$adl_toilet <- labelled(ALSA_ds_w1$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- ALSA_ds_w1$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
                    
ggplot(ALSA_ds_w1, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(ALSA_ds_w1$adl_toilet)
X<-table(ALSA_w1_adl_toilet$DIFFIC5)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w1_adl_toilet$DIFFIC5)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 

```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w1) <- NULL
label(ALSA_ds_w1$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$adl_toilet <- car::recode(ALSA_m_ds_w1$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w1
save(adl_toilet, file = paste0(datafolder, "/w1/adl_toilet.RData"))
```

### Wave 2

#### Study-specific variable description

 


* Name: `Q34.5`
* Label: `Difficulties with:`
* Categories:
    + `1 = Bathing, sponge bath or shower ` 
    + `2 = Personal grooming` 
    + `3 = Dressing` 
    + `4 = Eating`
    + `5 = Using the toilet`
    + `6 = Getting about away from home`
    + `7 = Moving about inside the house`
    + `8 = Getting from a bed to a chair`
    + `9 = No difficulties with any of these`
* Missings
    + `NA`

* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_adl_toilet','ALSA.ALSA-Wave2', variables=list('Q34.5'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
ALSA_w2_adl_toilet <- opal.execute(o,'ALSA_w2_adl_toilet')
#Categorical_summary(ALSA_w2_adl_toilet$Q34C.5)
vari <- ALSA_w2_adl_toilet$Q34.5 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


ggplot(ALSA_w2_adl_toilet, aes(x=factor(Q34.5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

Attention must be paid to this variable in the quality estimation part.
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 into 0`
* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 1` 
* `6 into 1` 
* `7 into 1`
* `8 into 1` 
* `9 into 1` 
* `NA into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_adl_toilet$id)
ALSA_ds_w2$adl_toilet <- car::recode(ALSA_w2_adl_toilet$Q34.5, "5 = '0';1 = '1';2 = '1';3 = '1';4 = '1';6 = '1';7 = '1';8 = '1';9 = '1';NA = '999' ")
ALSA_ds_w2$adl_toilet <- labelled(ALSA_ds_w2$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w2$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w2$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(ALSA_ds_w2, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(ALSA_ds_w2$adl_toilet)
X<-table(ALSA_w2_adl_toilet$Q34.5)
BeforeH <- c(X[1],sum(X[c(2:4)]),sum(is.na(ALSA_w2_adl_toilet$Q34.5)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,4,6,7,8,9->0","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w2) <- NULL
label(ALSA_ds_w2$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$adl_toilet <- car::recode(ALSA_m_ds_w2$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w2
save(adl_toilet, file = paste0(datafolder, "/w2/adl_toilet.RData"))
```

### Wave 3

#### Study-specific variable description

 


* Name: `ADLDF5W3`
* Label: `TOILET DIFFICULTY`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `9 = Missing`
    + `NA`

* Description: 
```{r assign w3,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_adl_toilet','ALSA.ALSA-Wave3', variables=list('ADLDF5W3'), missings = TRUE)
```

```{r local w3,  echo=FALSE}
ALSA_w3_adl_toilet <- opal.execute(o,'ALSA_w3_adl_toilet')
vari <- ALSA_w3_adl_toilet$ADLDF5W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_adl_toilet, aes(x=factor(ADLDF5W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `9 into 999`
* `NA into 999`

**R script:** 
```{r harmo w3,   echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_adl_toilet$id)
ALSA_ds_w3$adl_toilet <- car::recode(ALSA_w3_adl_toilet$ADLDF5W3, "1 = '1';2 = '0';3 = '0';4 = '0';9 = '999'; NA = '999' ")
ALSA_ds_w3$adl_toilet <- labelled(ALSA_ds_w3$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w3$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w3$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(ALSA_ds_w3, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(ALSA_ds_w3$adl_toilet)
X<-table(ALSA_w3_adl_toilet$ADLDF5W3)
BeforeH <- c(sum(X[c(2:4)]),X[1],X[5]+sum(is.na(ALSA_w3_adl_toilet$ADLDF5W3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","9,NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w3, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w3) <- NULL
label(ALSA_ds_w3$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$adl_toilet <- car::recode(ALSA_m_ds_w3$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w3
save(adl_toilet, file = paste0(datafolder, "/w3/adl_toilet.RData"))
```

### Wave 4

#### Study-specific variable description


* Name: `ADLND5W4`
* Label: `Difficulties with:`
* Categories:
    + `0 = No`
    + `1 = Bathing, sponge bath or shower ` 
    + `2 = Personal grooming` 
    + `3 = Dressing` 
    + `4 = Eating`
    + `5 = Using the toilet`
    + `6 = Getting about away from home`
    + `7 = Moving about inside the house`
    + `8 = Getting from a bed to a chair`
    + `9 = No difficulties with any of these`
    + `10 = Not applicable/in institution`
* Missings
    + `NA`

* Description: 
```{r assign w4,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_adl_toilet','ALSA.ALSA-Wave4', variables=list('ADLND5W4'), missings = TRUE)
```

```{r local w4,  echo=FALSE}
ALSA_w4_adl_toilet <- opal.execute(o,'ALSA_w4_adl_toilet')
vari <- ALSA_w4_adl_toilet$ADLND5W4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4_adl_toilet, aes(x=factor(ADLND5W4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm
Attention must be paid to this variable in the quality estimation part.
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:



* `0 into 1`
* `5 into 0`
* `NA into 999`

**R script:** 
```{r harmo w4,   echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_adl_toilet$id)
ALSA_ds_w4$adl_toilet <- car::recode(ALSA_w4_adl_toilet$ADLND5W4, "0 = '1';5 = '0';NA = '999' ")
ALSA_ds_w4$adl_toilet <- labelled(ALSA_ds_w4$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w4$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w4$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(ALSA_ds_w4, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(ALSA_ds_w4$adl_toilet)
X<-table(ALSA_w4_adl_toilet$ADLND5W4)
BeforeH <- c(X[2], X[1], sum(is.na(ALSA_w4_adl_toilet$ADLND5W4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","0,1,2,3,4,6,7,8,9->0","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w4, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w4) <- NULL
label(ALSA_ds_w4$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$adl_toilet <- car::recode(ALSA_m_ds_w4$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w4
save(adl_toilet, file = paste0(datafolder, "/w4/adl_toilet.RData"))
```

### Wave 5

#### Study-specific variable description

 


* Name: `ADLHP5W5`
* Label: `Using the toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `NA`

* Description: 
```{r assign w5,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_adl_toilet','ALSA.ALSA-Wave5', variables=list('ADLHP5W5'), missings = TRUE)
```

```{r local w5,  echo=FALSE}
ALSA_w5_adl_toilet <- opal.execute(o,'ALSA_w5_adl_toilet')
vari <- ALSA_w5_adl_toilet$ADLHP5W5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w5_adl_toilet, aes(x=factor(ADLHP5W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w5,   echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_adl_toilet$id)
ALSA_ds_w5$adl_toilet <- car::recode(ALSA_w5_adl_toilet$ADLHP5W5, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w5$adl_toilet <- labelled(ALSA_ds_w5$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w5$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w5$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5,  echo=FALSE}
AfterH <- table(ALSA_ds_w5$adl_toilet)
X<-table(ALSA_w5_adl_toilet$ADLHP5W5)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w5_adl_toilet$ADLHP5W5)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w5, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w5) <- NULL
label(ALSA_ds_w5$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$adl_toilet <- car::recode(ALSA_m_ds_w5$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w5
save(adl_toilet, file = paste0(datafolder, "/w5/adl_toilet.RData"))
```

### Wave 6

#### Study-specific variable description

 


* Name: `ADLDF5W6`
* Label: `level of difficulty using toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `0 = No answer`
    + `NA`

* Description: 
```{r assign w6,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_adl_toilet','ALSA.ALSA-Wave6', variables=list('ADLDF5W6'), missings = TRUE)
```

```{r local w6,  echo=FALSE}
ALSA_w6_adl_toilet <- opal.execute(o,'ALSA_w6_adl_toilet')
vari <- ALSA_w6_adl_toilet$ADLDF5W6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6_adl_toilet, aes(x=factor(ADLDF5W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0`  
* `0 into 995` 
* `NA into 999`

**R script:** 
```{r harmo w6,   echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_adl_toilet$id)
ALSA_ds_w6$adl_toilet <- car::recode(ALSA_w6_adl_toilet$ADLDF5W6, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$adl_toilet <- labelled(ALSA_ds_w6$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w6$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w6$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6,  echo=FALSE}
AfterH <- table(ALSA_ds_w6$adl_toilet)
X<-table(ALSA_w6_adl_toilet$ADLDF5W6)
BeforeH <- c(sum(X[c(3:5)]),X[2],X[1],sum(is.na(ALSA_w6_adl_toilet$ADLDF5W6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w6, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w6) <- NULL
label(ALSA_ds_w6$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$adl_toilet <- car::recode(ALSA_m_ds_w6$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w6
save(adl_toilet, file = paste0(datafolder, "/w6/adl_toilet.RData"))
```

### Wave 7

#### Study-specific variable description

 


* Name: `adldf5w7`
* Label: `level of difficulty using toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `0 = No answer`
    + `NA`

* Description: 
```{r assign w7,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_adl_toilet','ALSA.ALSA-Wave7', variables=list('adldf5w7'), missings = TRUE)
```

```{r local w7,  echo=FALSE}
ALSA_w7_adl_toilet <- opal.execute(o,'ALSA_w7_adl_toilet')
vari <- ALSA_w7_adl_toilet$adldf5w7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7_adl_toilet, aes(x=factor(adldf5w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:** 
```{r harmo w7,   echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_adl_toilet$id)
ALSA_ds_w7$adl_toilet <- car::recode(ALSA_w7_adl_toilet$adldf5w7 , "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$adl_toilet <- labelled(ALSA_ds_w7$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w7$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7,  echo=FALSE}
AfterH <- table(ALSA_ds_w7$adl_toilet)
X<-table(ALSA_w7_adl_toilet$adldf5w7)
BeforeH <- c(sum(X[c(3:5)]),X[2],X[1],sum(is.na(ALSA_w7_adl_toilet$adldf5w7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w7, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w7) <- NULL
label(ALSA_ds_w7$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$adl_toilet <- car::recode(ALSA_m_ds_w7$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w7
save(adl_toilet, file = paste0(datafolder, "/w7/adl_toilet.RData"))
```


### Wave 8

#### Study-specific variable description

 


* Name: `adlnd5w8`
* Label: `Using the toilet`
* Categories:
    + `1 = Yes` 
    + `2 = No`
* Missings
    + `NA`

* Description: 
```{r assign w8,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w8_adl_toilet','ALSA.ALSA-Wave8', variables=list('adlnd5w8'), missings = TRUE)
```

```{r local w8,  echo=FALSE}
ALSA_w8_adl_toilet <- opal.execute(o,'ALSA_w8_adl_toilet')
vari <- ALSA_w8_adl_toilet$adlnd5w8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8_adl_toilet, aes(x=factor(adlnd5w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2 into 1`  
* `NA into 999`

**R script:** 
```{r harmo w8,   echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_adl_toilet$id)
ALSA_ds_w8$adl_toilet <- car::recode(ALSA_w8_adl_toilet$adlnd5w8, "1 = '0';2 = '1';NA = '999' ")
ALSA_ds_w8$adl_toilet <- labelled(ALSA_ds_w8$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w8$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8,  echo=FALSE}
AfterH <- table(ALSA_ds_w8$adl_toilet)
X<-table(ALSA_w8_adl_toilet$adlnd5w8)
BeforeH <- c(X[1:2],sum(is.na(ALSA_w8_adl_toilet$adlnd5w8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w8, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w8) <- NULL
label(ALSA_ds_w8$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$adl_toilet <- car::recode(ALSA_m_ds_w8$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w8
save(adl_toilet, file = paste0(datafolder, "/w8/adl_toilet.RData"))
```

### Wave 9

#### Study-specific variable description

 


* Name: `ADLDF5W9`
* Label: `level of difficulty using toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
   + `0 = No answer`
   + `NA`

* Description: 
```{r assign w9,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_adl_toilet','ALSA.ALSA-Wave9', variables=list('ADLDF5W9'), missings = TRUE)
```

```{r local w9,  echo=FALSE}
ALSA_w9_adl_toilet <- opal.execute(o,'ALSA_w9_adl_toilet')
vari <- ALSA_w9_adl_toilet$ADLDF5W9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_adl_toilet, aes(x=factor(ADLDF5W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:** 
```{r harmo w9,   echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_adl_toilet$id)
ALSA_ds_w9$adl_toilet <- car::recode(ALSA_w9_adl_toilet$ADLDF5W9, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w9$adl_toilet <- labelled(ALSA_ds_w9$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w9$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9,  echo=FALSE}
AfterH <- table(ALSA_ds_w9$adl_toilet)
X<-table(ALSA_w9_adl_toilet$ADLDF5W9)
BeforeH <- c(sum(X[c(3:5)]),X[2:1],sum(is.na(ALSA_w9_adl_toilet$ADLDF5W9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w9, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w9) <- NULL
label(ALSA_ds_w9$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$adl_toilet <- car::recode(ALSA_m_ds_w9$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w9
save(adl_toilet, file = paste0(datafolder, "/w9/adl_toilet.RData"))
```

### Wave 10

#### Study-specific variable description

 


* Name: `adlnd5w10`
* Label: `Difficulties using the toilet?`
* Categories:
    + `0 = No` 
    + `1 = Yes`
* Missings
    + `NA`

* Description: 
```{r assign w10,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_adl_toilet','ALSA.ALSA-Wave10', variables=list('adlnd5w10'), missings = TRUE)
```

```{r local w10,  echo=FALSE}
ALSA_w10_adl_toilet <- opal.execute(o,'ALSA_w10_adl_toilet')
vari <- ALSA_w10_adl_toilet$adlnd5w10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10_adl_toilet, aes(x=factor(adlnd5w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo w10,   echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_adl_toilet$id)
ALSA_ds_w10$adl_toilet <- car::recode(ALSA_w10_adl_toilet$adlnd5w10, "1 = '0';0 = '1';NA = '999' ")
ALSA_ds_w10$adl_toilet <- labelled(ALSA_ds_w10$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w10$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10,  echo=FALSE}
AfterH <- table(ALSA_ds_w10$adl_toilet)
X<-table(ALSA_w10_adl_toilet$adlnd5w10)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```

 
 


 
```{r importOPAL w10, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w10) <- NULL
label(ALSA_ds_w10$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$adl_toilet <- car::recode(ALSA_m_ds_w10$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w10
save(adl_toilet, file = paste0(datafolder, "/w10/adl_toilet.RData"))
```

### Wave 11

#### Study-specific variable description

 


* Name: `ADLDF5W11`
* Label: `Difficulty using the toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty`
* Missings
    + `NA`

* Description: 
```{r assign w11,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_adl_toilet','ALSA.ALSA-Wave11', variables=list('ADLDF5W11'), missings = TRUE)
```

```{r local w11,  echo=FALSE}
ALSA_w11_adl_toilet <- opal.execute(o,'ALSA_w11_adl_toilet')
vari <- ALSA_w11_adl_toilet$ADLDF5W11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_adl_toilet, aes(x=factor(ADLDF5W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w11,   echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_adl_toilet$id)
ALSA_ds_w11$adl_toilet <- car::recode(ALSA_w11_adl_toilet$ADLDF5W11, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w11$adl_toilet <- labelled(ALSA_ds_w11$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w11$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11,  echo=FALSE}
AfterH <- table(ALSA_ds_w11$adl_toilet)
X<-table(ALSA_w11_adl_toilet$ADLDF5W11)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na((ALSA_w11_adl_toilet$ADLDF5W11))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w11, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w11) <- NULL
label(ALSA_ds_w11$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$adl_toilet <- car::recode(ALSA_m_ds_w11$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w11
save(adl_toilet, file = paste0(datafolder, "/w11/adl_toilet.RData"))
```

### Wave 12

#### Study-specific variable description

 


* Name: `ADLDF5W12`
* Label: `Difficulty using the toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `NA`

* Description: 
```{r assign w12,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_adl_toilet','ALSA.ALSA-Wave12', variables=list('ADLDF5W12'), missings = TRUE)
```

```{r local w12,  echo=FALSE}
ALSA_w12_adl_toilet <- opal.execute(o,'ALSA_w12_adl_toilet')
vari <- ALSA_w12_adl_toilet$ADLDF5W12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_adl_toilet, aes(x=factor(ADLDF5W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w12,   echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_adl_toilet$id)
ALSA_ds_w12$adl_toilet <- car::recode(ALSA_w12_adl_toilet$ADLDF5W12, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w12$adl_toilet <- labelled(ALSA_ds_w12$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w12$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w12$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12,  echo=FALSE}
AfterH <- table(ALSA_ds_w12$adl_toilet)
X<-table(ALSA_w12_adl_toilet$ADLDF5W12)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w12_adl_toilet$ADLDF5W12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w12, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w12) <- NULL
label(ALSA_ds_w12$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$adl_toilet <- car::recode(ALSA_m_ds_w12$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w12
save(adl_toilet, file = paste0(datafolder, "/w12/adl_toilet.RData"))
```

### Wave 13

#### Study-specific variable description

 


* Name: `ADLDF5W13`
* Label: `Difficulty using the toilet`
* Categories:
    + `1 = No difficulty at all` 
    + `2 = A little difficulty` 
    + `3 = Some difficulty` 
    + `4 = A lot of difficulty` 
* Missings
    + `NA`

* Description: 
```{r assign w13,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_adl_toilet','ALSA.ALSA-Wave13', variables=list('ADLDF5W13'), missings = TRUE)
```

```{r local w13,  echo=FALSE}
ALSA_w13_adl_toilet <- opal.execute(o,'ALSA_w13_adl_toilet')
vari <- ALSA_w13_adl_toilet$ADLDF5W13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_adl_toilet, aes(x=factor(ADLDF5W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w13,   echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_adl_toilet$id)
ALSA_ds_w13$adl_toilet <- car::recode(ALSA_w13_adl_toilet$ADLDF5W13, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w13$adl_toilet <- labelled(ALSA_ds_w13$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13,  echo=FALSE}
#Categorical_summary(var = ALSA_ds_w13$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ALSA_ds_w13$adl_toilet
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13,  echo=FALSE}
AfterH <- table(ALSA_ds_w13$adl_toilet)
X<-table(ALSA_w13_adl_toilet$ADLDF5W13)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w13_adl_toilet$ADLDF5W13)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w13, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w13) <- NULL
label(ALSA_ds_w13$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$adl_toilet <- car::recode(ALSA_m_ds_w13$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_toilet <- ALSA_ds_w13
save(adl_toilet, file = paste0(datafolder, "/w13/adl_toilet.RData"))
```


# Quality estimation
Waves 2 and 4 should be handled carefully because of controversies in the original variables.

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
