---
title: "ADL - Eating"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/adl_eatingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/adl_eatingDS.R')
```

# Data process



## Australia
### Wave 1

#### Study-specific variable description

 


| **Name** |`ACTIV4`|
|-|-|
| **Label** |`Eating`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`0 = No problem`<br/>`1 = Problem`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_adl_eating','ALSA.ALSA-Wave1', variables=list('ACTIV4'), missings = TRUE)
ALSA_w1_adl_eating <- opal.execute(o,'ALSA_w1_adl_eating')
```


```{r local w1, echo=FALSE}
vari <- ALSA_w1_adl_eating$ACTIV4 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w1_adl_eating, aes(x=factor(ACTIV4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_adl_eating$id)
ALSA_ds_w1$adl_eating <- car::recode(ALSA_w1_adl_eating$ACTIV4, "0 = '1';1 = '0';NA = '999' ")
ALSA_ds_w1$adl_eating <- labelled(ALSA_ds_w1$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- ALSA_ds_w1$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w1, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}

```

 
 
 

### Wave 2


#### Study-specific variable description

 


| **Name** |`Q34`|`Q34.4`|
|-|-|-|
| **Label** |`Difficulties with:`|`Difficulties with:`|
| **Table name** |`ALSA-Wave2`|`ALSA-Wave2`|
| **Categories** |`1 = Bathing, sponge bath or shower`<br/>`2 = Personal grooming`<br/>`3 = Dressing`<br/>`4 = Eating`<br/>`5 = Using the toilet`<br/>`6 = Getting about away from home`<br/>`7 = Moving about inside the house`<br/>`8 = Getting from a bed to a chair`<br/>`9 = No difficulties with any of these`|`1 = Bathing, sponge bath or shower`<br/>`2 = Personal grooming`<br/>`3 = Dressing`<br/>`4 = Eating`<br/>`5 = Using the toilet`<br/>`6 = Getting about away from home`<br/>`7 = Moving about inside the house`<br/>`8 = Getting from a bed to a chair`<br/>`9 = No difficulties with any of these`|
| **Missings** |`10 = Not applicable/in institution`<br/>`NA`|`NA`|
| **Description ** |  |  |



```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_adl_eating','ALSA.ALSA-Wave2', variables=list('Q34','Q34.4'), missings = TRUE)
ALSA_w2_adl_eating <- opal.execute(o,'ALSA_w2_adl_eating')
```

```{r local w2,  echo=FALSE}
vari <- ALSA_w2_adl_eating$Q34 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w2_adl_eating, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w2_adl_eating$Q34.4 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w2_adl_eating, aes(x=factor(Q34.4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `4 into 0`
* `9 into 1`
* `10 into 996`
* `NA into 999`
* `other into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_adl_eating$id)
ALSA_ds_w2$adl_eating <- car::recode(ALSA_w2_adl_eating$Q34.4, "4 = '0';c(5,6,7,8)=999; NA = '999' ")
ALSA_ds_w2$adl_eating[which(ALSA_w2_adl_eating$Q34 == 9)] <- 1
ALSA_ds_w2$adl_eating[which(ALSA_w2_adl_eating$Q34 == 10)] <- 996
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- ALSA_ds_w2$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w2, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}

```

 
 


### Wave 3

#### Study-specific variable description

 


| **Name** |`ADLDF4W3`|
|-|-|
| **Label** |`Eating difficulty`|
| **Table name** |`ALSA-Wave3`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`9 = Missing`<br/>`NA`|
| **Description** |  |


```{r assign w3,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_adl_eating','ALSA.ALSA-Wave3', variables=list('ADLDF4W3'), missings = TRUE)
ALSA_w3_adl_eating <- opal.execute(o,'ALSA_w3_adl_eating')
```

```{r local w3,  echo=FALSE}
vari <- ALSA_w3_adl_eating$ADLDF4W3 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w3_adl_eating, aes(x=factor(ADLDF4W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm


To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `9 into 999`
* `NA into 999`

**R script:** 
```{r harmo w3,   echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_adl_eating$id)
ALSA_ds_w3$adl_eating <- car::recode(ALSA_w3_adl_eating$ADLDF4W3, "1 = '1';2 = '0';3 = '0';4 = '0';9 = '999'; NA = '999' ")
ALSA_ds_w3$adl_eating <- labelled(ALSA_ds_w3$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- ALSA_ds_w3$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w3, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(ALSA_ds_w3$adl_eating)
X<-table(ALSA_w3_adl_eating$ADLDF4W3)
BeforeH <- c(sum(X[c(2:4)]),X[1],X[5]+sum(is.na(ALSA_w3_adl_eating$ADLDF4W3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","9,NA->999") 
kable(C)
```

 
 


### Wave 4

#### Study-specific variable description



| **Name** |`ADLDN4W4`|
|-|-|
| **Label** |`Difficulties with:`|
| **Table name** |`ALSA-Wave4`|
| **Categories** |`0 = No`<br/>`1 = Bathing, sponge bath or shower `<br/>`2 = Personal grooming`<br/>`3 = Dressing`<br/>`4 = Eating`<br/>`5 = Using the toilet`<br/>`6 = Getting about away from home`<br/>`7 = Moving about inside the house`<br/>`8 = Getting from a bed to a chair`<br/>`9 = No difficulties with any of these`|
| **Missings** |`10 = Not applicable/in institution`<br/>`NA`|
| **Description** |  |




```{r assign w4,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_adl_eating','ALSA.ALSA-Wave4', variables=list('ADLND4W4'), missings = TRUE)
ALSA_w4_adl_eating <- opal.execute(o,'ALSA_w4_adl_eating')
```

```{r local w4,  echo=FALSE}
vari <- ALSA_w4_adl_eating$ADLND4W4 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w4_adl_eating, aes(x=factor(ADLND4W4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
Attention must be paid to this variable in the quality estimation part.
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w4,   echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_adl_eating$id)
ALSA_ds_w4$adl_eating <- car::recode(ALSA_w4_adl_eating$ADLND4W4, "0 = '1';4 = '0'; NA = '999' ")
ALSA_ds_w4$adl_eating <- labelled(ALSA_ds_w4$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
vari <- ALSA_ds_w4$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w4, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(ALSA_ds_w4$adl_eating)
X<-table(ALSA_w4_adl_eating$ADLND4W4)
BeforeH <- c(X[2:1],sum(is.na(ALSA_w4_adl_eating$ADLND4W4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description


| **Name** |`ADLND4W5`|
|-|-|
| **Label** |`Difficulty for - EATING,LIKE HOLDING A FORK,CUTTING FOOD`|
| **Table name** |`ALSA-Wave5`|
| **Categories** |`0 = No`<br/>`1 = Bathing, sponge bath or shower `<br/>`2 = Personal grooming`<br/>`3 = Dressing`<br/>`4 = Eating`<br/>`5 = Using the toilet`<br/>`6 = Getting about away from home`<br/>`7 = Moving about inside the house`<br/>`8 = Getting from a bed to a chair`<br/>`9 = No difficulties`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w5,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_adl_eating','ALSA.ALSA-Wave5', variables=list('ADLND4W5'), missings = TRUE)
ALSA_w5_adl_eating <- opal.execute(o,'ALSA_w5_adl_eating')
```

```{r local w5,  echo=FALSE}
vari <- ALSA_w5_adl_eating$ADLND4W5 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w5_adl_eating, aes(x=factor(ADLND4W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 0`
* `0 into 1` 


**R script:** 
```{r harmo w5,   echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_adl_eating$id)
ALSA_ds_w5$adl_eating <- car::recode(ALSA_w5_adl_eating$ADLND4W5, "4 = '0';0='1'")
ALSA_ds_w5$adl_eating <- labelled(ALSA_ds_w5$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5,  echo=FALSE}
vari <- ALSA_ds_w5$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w5, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5,  echo=FALSE}
AfterH <- table(ALSA_ds_w5$adl_eating)
X<-table(ALSA_w5_adl_eating$ADLND4W5)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","0->1") 
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

 

| **Name** |`ADLDF4W6`|
|-|-|
| **Label** |`level of difficulty eating`|
| **Table name** |`ALSA-Wave6`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`0 = No answer`<br/>`NA`|
| **Description** |  |


```{r assign w6,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_adl_eating','ALSA.ALSA-Wave6', variables=list('ADLDF4W6'), missings = TRUE)
ALSA_w6_adl_eating <- opal.execute(o,'ALSA_w6_adl_eating')
```

```{r local w6,  echo=FALSE}
vari <- ALSA_w6_adl_eating$ADLDF4W6 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w6_adl_eating, aes(x=factor(ADLDF4W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0`  
* `0 into 995` 
* `NA into 999`


**R script:** 
```{r harmo w6,   echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_adl_eating$id)
ALSA_ds_w6$adl_eating <- car::recode(ALSA_w6_adl_eating$ADLDF4W6, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$adl_eating <- labelled(ALSA_ds_w6$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6,  echo=FALSE}
vari <- ALSA_ds_w6$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w6, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6,  echo=FALSE}
AfterH <- table(ALSA_ds_w6$adl_eating)
X<-table(ALSA_w6_adl_eating$ADLDF4W6)
BeforeH <- c(sum(X[c(3:5)]),X[2],X[1],sum(is.na(ALSA_w6_adl_eating$ADLDF4W6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

 


| **Name** |`adldf4w7`|
|-|-|
| **Label** |`level of difficulty eating`|
| **Table name** |`ALSA-Wave7`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`0 = No answer`<br/>`NA`|
| **Description** |  |



```{r assign w7,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_adl_eating','ALSA.ALSA-Wave7', variables=list('adldf4w7'), missings = TRUE)
ALSA_w7_adl_eating <- opal.execute(o,'ALSA_w7_adl_eating')
```

```{r local w7,  echo=FALSE}
vari <- ALSA_w7_adl_eating$adldf4w7 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w7_adl_eating, aes(x=factor(adldf4w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:** 
```{r harmo w7,   echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_adl_eating$id)
ALSA_ds_w7$adl_eating <- car::recode(ALSA_w7_adl_eating$adldf4w7 , "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$adl_eating <- labelled(ALSA_ds_w7$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7,  echo=FALSE}
vari <- ALSA_ds_w7$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w7, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7,  echo=FALSE}
AfterH <- table(ALSA_ds_w7$adl_eating)
X<-table(ALSA_w7_adl_eating$adldf4w7)
BeforeH <- c(sum(X[c(3:5)]),X[2],X[1],sum(is.na(ALSA_w7_adl_eating$adldf4w7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


| **Name** |`adlnd4w8`|
|-|-|
| **Label** |`Difficulties with: Eating like holding a fork, cutting food or drinking from a glass`|
| **Table name** |`ALSA-Wave8`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings** |`NA`|
| **Description** |  |

 
```{r assign w8,  echo=FALSE}
opal.assign.table.tibble(o,'ALSA_w8_adl_eating','ALSA.ALSA-Wave8',variables=list('adlnd4w8'), missings = TRUE)
ALSA_w8_adl_eating <- opal.execute(o,'ALSA_w8_adl_eating')
```

```{r local w8,  echo=FALSE}
vari <- ALSA_w8_adl_eating$adlnd4w8 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w8_adl_eating, aes(x=factor(adlnd4w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2 into 1` 
* `NA into 999`

**R script:** 
```{r harmo w8,   echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_adl_eating$id)
ALSA_ds_w8$adl_eating <- car::recode(ALSA_w8_adl_eating$adlnd4w8, "1 = '0';2 = '1';NA = '999' ")
ALSA_ds_w8$adl_eating <- labelled(ALSA_ds_w8$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8,  echo=FALSE}
vari <- ALSA_ds_w8$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w8, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8,  echo=FALSE}
AfterH <- table(ALSA_ds_w8$adl_eating)
X<-table(ALSA_w8_adl_eating$adlnd4w8)
BeforeH <- c(X[1:2],sum(is.na(ALSA_w8_adl_eating$adlnd4w8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w8, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w8) <- NULL
label(ALSA_ds_w8$adl_eating) <- "Difficulties for eating"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$adl_eating <- car::recode(ALSA_m_ds_w8$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ALSA_ds_w8
save(adl_eating, file = paste0(datafolder, "/w8/adl_eating.RData"))
```

### Wave 9

#### Study-specific variable description

 


| **Name** |`ADLDF4W9`|
|-|-|
| **Label** |`level of difficulty eating`|
| **Table name** |`ALSA-Wave9`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`0 = No answer`<br/>`NA`|
| **Description** |  |



```{r assign w9,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_adl_eating','ALSA.ALSA-Wave9', variables=list('ADLDF4W9'), missings = TRUE)
ALSA_w9_adl_eating <- opal.execute(o,'ALSA_w9_adl_eating')
```

```{r local w9,  echo=FALSE}
vari <- ALSA_w9_adl_eating$ADLDF4W9 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w9_adl_eating, aes(x=factor(ADLDF4W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:** 
```{r harmo w9,   echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_adl_eating$id)
ALSA_ds_w9$adl_eating <- car::recode(ALSA_w9_adl_eating$ADLDF4W9, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w9$adl_eating <- labelled(ALSA_ds_w9$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9,  echo=FALSE}
vari <- ALSA_ds_w9$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w9, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9,  echo=FALSE}
AfterH <- table(ALSA_ds_w9$adl_eating)
X<-table(ALSA_w9_adl_eating$ADLDF4W9)
BeforeH <- c(sum(X[c(3:5)]),X[2:1],sum(is.na(ALSA_w9_adl_eating$ADLDF4W9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 

| **Name** |`adlnd4w10`|
|-|-|
| **Label** |`Difficulties with: Eating like holding a fork, cutting food or drinking from a glass`|
| **Table name** |`ALSA-Wave10`|
| **Categories** |`1 = Yes`<br/>`0 = No`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign w10,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_adl_eating','ALSA.ALSA-Wave10', variables=list('adlnd4w10'), missings = TRUE)
ALSA_w10_adl_eating <- opal.execute(o,'ALSA_w10_adl_eating')
```

```{r local w10,  echo=FALSE}
vari <- ALSA_w10_adl_eating$adlnd4w10 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w10_adl_eating, aes(x=factor(adlnd4w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo w10,   echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_adl_eating$id)
ALSA_ds_w10$adl_eating <- car::recode(ALSA_w10_adl_eating$adlnd4w10, "1 = '0';0 = '1';NA = '999' ")
ALSA_ds_w10$adl_eating <- labelled(ALSA_ds_w10$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10,  echo=FALSE}
vari <- ALSA_ds_w10$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w10, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10,  echo=FALSE}
AfterH <- table(ALSA_ds_w10$adl_eating)
X<-table(ALSA_w10_adl_eating$adlnd4w10)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 
| **Name** |`ADLDF4W11`|
|-|-|
| **Label** |`Difficulty eating`|
| **Table name** |`ALSA-Wave11`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`NA`|
| **Description** |  |




```{r assign w11,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_adl_eating','ALSA.ALSA-Wave11', variables=list('ADLDF4W11'), missings = TRUE)
ALSA_w11_adl_eating <- opal.execute(o,'ALSA_w11_adl_eating')
```

```{r local w11,  echo=FALSE}
vari <- ALSA_w11_adl_eating$ADLDF4W11 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w11_adl_eating, aes(x=factor(ADLDF4W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w11,   echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_adl_eating$id)
ALSA_ds_w11$adl_eating <- car::recode(ALSA_w11_adl_eating$ADLDF4W11, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w11$adl_eating <- labelled(ALSA_ds_w11$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11,  echo=FALSE}
vari <- ALSA_ds_w11$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w11, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11,  echo=FALSE}
AfterH <- table(ALSA_ds_w11$adl_eating)
X<-table(ALSA_w11_adl_eating$ADLDF4W11)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na((ALSA_w11_adl_eating$ADLDF4W11))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 



### Wave 12

#### Study-specific variable description

 


| **Name** |`ADLDF4W12`|
|-|-|
| **Label** |`Difficulty eating`|
| **Table name** |`ALSA-Wave12`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign w12,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_adl_eating','ALSA.ALSA-Wave12', variables=list('ADLDF4W12'), missings = TRUE)
ALSA_w12_adl_eating <- opal.execute(o,'ALSA_w12_adl_eating')
```

```{r local w12,  echo=FALSE}
vari <- ALSA_w12_adl_eating$ADLDF4W12 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w12_adl_eating, aes(x=factor(ADLDF4W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w12,   echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_adl_eating$id)
ALSA_ds_w12$adl_eating <- car::recode(ALSA_w12_adl_eating$ADLDF4W12, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w12$adl_eating <- labelled(ALSA_ds_w12$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12,  echo=FALSE}
vari <- ALSA_ds_w12$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w12, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12,  echo=FALSE}
AfterH <- table(ALSA_ds_w12$adl_eating)
X<-table(ALSA_w12_adl_eating$ADLDF4W12)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w12_adl_eating$ADLDF4W12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 




### Wave 13

#### Study-specific variable description

 



| **Name** |`ADLDF4W13`|
|-|-|
| **Label** |`Difficulty eating`|
| **Table name** |`ALSA-Wave13`|
| **Categories** |`1 = No difficulty at all`<br/>`2 = A little difficulty`<br/>`3 = Some difficulty`<br/>`4 = A lot of difficulty`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w13,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_adl_eating','ALSA.ALSA-Wave13', variables=list('ADLDF4W13'), missings = TRUE)
ALSA_w13_adl_eating <- opal.execute(o,'ALSA_w13_adl_eating')
```

```{r local w13,  echo=FALSE}
vari <- ALSA_w13_adl_eating$ADLDF4W13 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w13_adl_eating, aes(x=factor(ADLDF4W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w13,   echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_adl_eating$id)
ALSA_ds_w13$adl_eating <- car::recode(ALSA_w13_adl_eating$ADLDF4W13, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w13$adl_eating <- labelled(ALSA_ds_w13$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13,  echo=FALSE}
vari <- ALSA_ds_w13$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w13, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13,  echo=FALSE}
AfterH <- table(ALSA_ds_w13$adl_eating)
X<-table(ALSA_w13_adl_eating$ADLDF4W13)
BeforeH <- c(sum(X[c(2:4)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1") 
kable(C)
```

 
 

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation

Waves 2, 4, 5, 8 and 10 should be handled carefully because of controversies in the original variables.

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
