---
title: "IADL - Difficulties for managing money"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_money`
* Variable label: `IADL - Difficulties for managing money, bills, expenses`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## Australian population

### Wave 1

#### Study-specific variable description

 


* Name: `IACTIV7`
* Label: `Managing money`
* Categories:
   + `0 = No problem` 
   + `1 = Problem`
* Missings
   + `NA`

* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_iadl_money','ALSA.ALSA-Wave1', variables=list('IACTIV7'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
ALSA_w1_iadl_money <- opal.execute(o,'ALSA_w1_iadl_money')
vari <- ALSA_w1_iadl_money$IACTIV7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w1_iadl_money$IACTIV7)
ggplot(ALSA_w1_iadl_money, aes(x=factor(IACTIV7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_iadl_money$id)
ALSA_ds_w1$iadl_money <- car::recode(ALSA_w1_iadl_money$IACTIV7, "1 = '0';0 = '1';NA = '999' ")
ALSA_ds_w1$iadl_money <- labelled(ALSA_ds_w1$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- ALSA_ds_w1$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(ALSA_ds_w1$iadl_money)
X<-table(ALSA_w1_iadl_money$IACTIV7)
BeforeH <- c(sum(X[c(2)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w1) <- NULL
label(ALSA_ds_w1$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$iadl_money <- car::recode(ALSA_m_ds_w1$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w1
save(iadl_money, file = paste0(datafolder, "/w1/iadl_money.RData"))
```

### Wave 2

#### Study-specific variable description



* Name: `Q35.7`
* Label: `Difficulties with daily living activities:  Managing money `
* Categories:
   + `1 = Laundry/linen` 
   + `2 = Light housework` 
   + `3 = Heavy housework` 
   + `4 = Home maintenance & gardening tasks` 
   + `5 = Preparing own meals` 
   + `6 = Using the telephone` 
   + `7 = Managing own money` 
   + `8 = Writing letters` 
   + `9 = Using public transport` 
   + `10 = Shopping for groceries and other necessities` 
* Missings
   + `NA`

* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_iadl_money','ALSA.ALSA-Wave2', variables=list('Q35.7'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
ALSA_w2_iadl_money <- opal.execute(o,'ALSA_w2_iadl_money')
vari <- ALSA_w2_iadl_money$Q35.7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w2_iadl_money$Q35.7)
ggplot(ALSA_w2_iadl_money, aes(x=factor(Q35.7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 0` 
* `8,9,10 into 1`
* `NA into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_iadl_money$id)
ALSA_ds_w2$iadl_money <- car::recode(ALSA_w2_iadl_money$Q35.7, "7 = '0';8 = '1';9 = '1';10 = '1';NA = '999' ")
ALSA_ds_w2$iadl_money <- labelled(ALSA_ds_w2$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- ALSA_ds_w2$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w2$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w2, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(ALSA_ds_w2$iadl_money)
X<-table(ALSA_w2_iadl_money$Q35.7)
BeforeH <- c(X[1] ,sum(X[-1]),sum(is.na(ALSA_w2_iadl_money$Q35.7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","8,9,10->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w2) <- NULL
label(ALSA_ds_w2$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$iadl_money <- car::recode(ALSA_m_ds_w2$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w2
save(iadl_money, file = paste0(datafolder, "/w2/iadl_money.RData"))
```

### Wave 3

#### Study-specific variable description

 


* Name: `IDIFF7W3`
* Label: `Managing money difficulty`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty`
* Missings
   + `NA`

* Description: 
```{r assign w3,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_iadl_money','ALSA.ALSA-Wave3', variables=list('IDIFF7W3'), missings = TRUE)
```

```{r local w3,  echo=FALSE}
ALSA_w3_iadl_money <- opal.execute(o,'ALSA_w3_iadl_money')
vari <- ALSA_w3_iadl_money$IDIFF7W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w3_iadl_money$IDIFF7W3)
ggplot(ALSA_w3_iadl_money, aes(x=factor(IDIFF7W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `NA into 999`

**R script:** 
```{r harmo w3,   echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_iadl_money$id)
ALSA_ds_w3$iadl_money <- car::recode(ALSA_w3_iadl_money$IDIFF7W3, "1 = '1';2 = '0';3 = '0';4 = '0'; NA = '999' ")
ALSA_ds_w3$iadl_money <- labelled(ALSA_ds_w3$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- ALSA_ds_w3$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w3$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(ALSA_ds_w3$iadl_money)
X<-table(ALSA_w3_iadl_money$IDIFF7W3)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w3_iadl_money$IDIFF7W3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w3, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w3) <- NULL
label(ALSA_ds_w3$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$iadl_money <- car::recode(ALSA_m_ds_w3$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w3
save(iadl_money, file = paste0(datafolder, "/w3/iadl_money.RData"))
```

### Wave 4

#### Study-specific variable description


* Name: `IADN7W4`
* Label: `Difficulties with: Managing money`
* Categories:
    + `0 = No difficulties` 
    + `6 = Difficulties with managing money` 
* Missings
   + `NA`

* Description: 
```{r assign w4,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_iadl_money','ALSA.ALSA-Wave4', variables=list('IADN7W4'), missings = TRUE)
```

```{r local w4,  echo=FALSE}
ALSA_w4_iadl_money <- opal.execute(o,'ALSA_w4_iadl_money')
vari <- ALSA_w4_iadl_money$IADN7W4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w4_iadl_money$IADN7W4)
ggplot(ALSA_w4_iadl_money, aes(x=factor(IADN7W4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 0` 
* `0 into 1`
* `NA into 999`

**R script:** 
```{r harmo w4,   echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_iadl_money$id)
ALSA_ds_w4$iadl_money <- car::recode(ALSA_w4_iadl_money$IADN7W4, "7 = '0';0 = '1';NA = '999' ")
ALSA_ds_w4$iadl_money <- labelled(ALSA_ds_w4$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
vari <- ALSA_ds_w4$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w4$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w4, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(ALSA_ds_w4$iadl_money)
X<-table(ALSA_w4_iadl_money$IADN7W4)
BeforeH <- c(X[2:1],sum(is.na(ALSA_w4_iadl_money$IADN7W4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0", "0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w4, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w4) <- NULL
label(ALSA_ds_w4$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$iadl_money <- car::recode(ALSA_m_ds_w4$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w4
save(iadl_money, file = paste0(datafolder, "/w4/iadl_money.RData"))
```

### Wave 5

#### Study-specific variable description

 


* Name: `IADL7W5`
* Label: `Have you (Has he/she) had any difficulties or have had any help with managing your own money ?`
* Categories:
   + `1 = Difficulty with activity` 
   + `2 = No difficulty` 
* Missings
   + `3 = Do not do activity`
   + `NA`

* Description: 
```{r assign w5,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_iadl_money','ALSA.ALSA-Wave5', variables=list('IADL7W5'), missings = TRUE)
```

```{r local w5,  echo=FALSE}
ALSA_w5_iadl_money <- opal.execute(o,'ALSA_w5_iadl_money')
vari <- ALSA_w5_iadl_money$IADL7W5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w5_iadl_money$IADL7W5)
ggplot(ALSA_w5_iadl_money, aes(x=factor(IADL7W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `3 into 994`
* `NA into 999`

**R script:** 
```{r harmo w5,   echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_iadl_money$id)
ALSA_ds_w5$iadl_money <- car::recode(ALSA_w5_iadl_money$IADL7W5, "1 = '0';2 = '1';3 = '994';NA = '999' ")
ALSA_ds_w5$iadl_money <- labelled(ALSA_ds_w5$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5,  echo=FALSE}
vari <- ALSA_ds_w5$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w5$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w5, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5,  echo=FALSE}
AfterH <- table(ALSA_ds_w5$iadl_money)
X<-table(ALSA_w5_iadl_money$IADL7W5)
BeforeH <- c(X[1:3],sum(is.na(ALSA_w5_iadl_money$IADL7W5)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","3->994","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w5, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w5) <- NULL
label(ALSA_ds_w5$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$iadl_money <- car::recode(ALSA_m_ds_w5$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w5
save(iadl_money, file = paste0(datafolder, "/w5/iadl_money.RData"))
```

### Wave 6

#### Study-specific variable description

 


* Name: `IDIFF7W6`
* Label: `level of difficulty doing managing money`
* Categories:
   + `1 = no difficulty at all` 
   + `2 = a little difficulty` 
   + `3 = some difficulty` 
   + `4 = a lot of difficulty` 
* Missings
   + `0 = No answer`
   + `NA`

* Description: 
```{r assign w6,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_iadl_money','ALSA.ALSA-Wave6', variables=list('IDIFF7W6'), missings = TRUE)
```

```{r local w6,  echo=FALSE}
ALSA_w6_iadl_money <- opal.execute(o,'ALSA_w6_iadl_money')
vari <- ALSA_w6_iadl_money$IADL7W6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w6_iadl_money$IDIFF7W6)
ggplot(ALSA_w6_iadl_money, aes(x=factor(IDIFF7W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:** 
```{r harmo w6,   echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_iadl_money$id)
ALSA_ds_w6$iadl_money <- car::recode(ALSA_w6_iadl_money$IDIFF7W6, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$iadl_money <- labelled(ALSA_ds_w6$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6,  echo=FALSE}
vari <- ALSA_ds_w6$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w6$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6,  echo=FALSE}
AfterH <- table(ALSA_ds_w6$iadl_money)
X<-table(ALSA_w6_iadl_money$IDIFF7W6)
BeforeH <- c(sum(X[3:5]),X[2:1],sum(is.na(ALSA_w6_iadl_money$IDIFF7W6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w6, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w6) <- NULL
label(ALSA_ds_w6$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$iadl_money <- car::recode(ALSA_m_ds_w6$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w6
save(iadl_money, file = paste0(datafolder, "/w6/iadl_money.RData"))
```

### Wave 7

#### Study-specific variable description

 


* Name: `idiff7w7`
* Label: `level of difficulty doing managing money`
* Categories:
   + `1 = no difficulty at all` 
   + `2 = a little difficulty` 
   + `3 = some difficulty` 
   + `4 = a lot of difficulty` 
* Missings
   + `0 = Not answered`
   + `NA`

* Description: 
```{r assign w7,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_iadl_money','ALSA.ALSA-Wave7', variables=list('idiff7w7'), missings = TRUE)
```

```{r local w7,  echo=FALSE}
ALSA_w7_iadl_money <- opal.execute(o,'ALSA_w7_iadl_money')
vari <- ALSA_w7_iadl_money$idiff7w7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w7_iadl_money$idiff7w7)
ggplot(ALSA_w7_iadl_money, aes(x=factor(idiff7w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:** 
```{r harmo w7,   echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_iadl_money$id)
ALSA_ds_w7$iadl_money <- car::recode(ALSA_w7_iadl_money$idiff7w7, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$iadl_money <- labelled(ALSA_ds_w7$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7,  echo=FALSE}
vari <- ALSA_ds_w7$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w7$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7,  echo=FALSE}
AfterH <- table(ALSA_ds_w7$iadl_money)
X<-table(ALSA_w7_iadl_money$idiff7w7)
BeforeH <- c(sum(X[3:5]),X[2:1],sum(is.na(ALSA_w7_iadl_money$idiff7w7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w7, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w7) <- NULL
label(ALSA_ds_w7$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$iadl_money <- car::recode(ALSA_m_ds_w7$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w7
save(iadl_money, file = paste0(datafolder, "/w7/iadl_money.RData"))
```

### Wave 8

#### Study-specific variable description

 


* Name: `iadl7w8`
* Label: `difficulty managing money`
* Categories:
   + `1 = Difficulties` 
   + `2 = No Difficulties` 
* Missings
   + `3 = Don't do`
   + `0 = Not Answered`
   + `NA`

* Description: 
```{r assign w8,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w8_iadl_money','ALSA.ALSA-Wave8', variables=list('iadl7w8'), missings = TRUE)
```

```{r local w8,  echo=FALSE}
ALSA_w8_iadl_money <- opal.execute(o,'ALSA_w8_iadl_money')
vari <- ALSA_w8_iadl_money$iadl7w8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w8_iadl_money$iadl7w8)
ggplot(ALSA_w8_iadl_money, aes(x=factor(iadl7w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `0 into 995`
* `3 into 994`
* `NA into 999`

**R script:** 
```{r harmo w8,   echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_iadl_money$id)
ALSA_ds_w8$iadl_money <- car::recode(ALSA_w8_iadl_money$iadl7w8, "1 = '0';2 = '1';3 = '994';0 = '995';NA = '999' ")
ALSA_ds_w8$iadl_money <- labelled(ALSA_ds_w8$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8,  echo=FALSE}
vari <- ALSA_ds_w8$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w8$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w8, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8,  echo=FALSE}
AfterH <- table(ALSA_ds_w8$iadl_money)
X<-table(ALSA_w8_iadl_money$iadl7w8)
BeforeH <- c(X[c(2,3,1,4)],sum(is.na(ALSA_w8_iadl_money$iadl7w8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","0->995","3->994","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w8, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w8) <- NULL
label(ALSA_ds_w8$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$iadl_money <- car::recode(ALSA_m_ds_w8$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w8
save(iadl_money, file = paste0(datafolder, "/w8/iadl_money.RData"))
```

### Wave 9

#### Study-specific variable description

 


* Name: `IDIFF7W9`
* Label: `level of difficulty managing money`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `0 = Not Answered`
   + `NA`

* Description: 
```{r assign w9,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_iadl_money','ALSA.ALSA-Wave9', variables=list('IDIFF7W9'), missings = TRUE)
```

```{r local w9,  echo=FALSE}
ALSA_w9_iadl_money <- opal.execute(o,'ALSA_w9_iadl_money')
vari <- ALSA_w9_iadl_money$IDIFF7W9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w9_iadl_money$IDIFF7W9)
ggplot(ALSA_w9_iadl_money, aes(x=factor(IDIFF7W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:** 
```{r harmo w9,   echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_iadl_money$id)
ALSA_ds_w9$iadl_money <- car::recode(ALSA_w9_iadl_money$IDIFF7W9, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w9$iadl_money <- labelled(ALSA_ds_w9$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9,  echo=FALSE}
vari <- ALSA_ds_w9$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9,  echo=FALSE}
AfterH <- table(ALSA_ds_w9$iadl_money)
X<-table(ALSA_w9_iadl_money$IDIFF7W9)
BeforeH <- c(sum(X[c(3:5)]),X[2:1],sum(is.na(ALSA_w9_iadl_money$IDIFF7W9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w9, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w9) <- NULL
label(ALSA_ds_w9$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$iadl_money <- car::recode(ALSA_m_ds_w9$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w9
save(iadl_money, file = paste0(datafolder, "/w9/iadl_money.RData"))
```

### Wave 10

#### Study-specific variable description

 


* Name: `iadl7w10`
* Label: `Do you have any difficulty with managing your own money?`
* Categories:
   + `0 = No` 
   + `1 = yes`
* Missings
   + `99 = Not applicable`
   + `NA`

* Description: 
```{r assign w10,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_iadl_money','ALSA.ALSA-Wave10', variables=list('iadl7w10'), missings = TRUE)
```

```{r local w10,  echo=FALSE}
ALSA_w10_iadl_money <- opal.execute(o,'ALSA_w10_iadl_money')
vari <- ALSA_w10_iadl_money$iadl7w10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w10_iadl_money$iadl7w10)
ggplot(ALSA_w10_iadl_money, aes(x=factor(iadl7w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `99 into 994`
* `NA into 999`

**R script:** 
```{r harmo w10,   echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_iadl_money$id)
ALSA_ds_w10$iadl_money <- car::recode(ALSA_w10_iadl_money$iadl7w10, "1 = '0';0 = '1';99 = '994';NA = '999' ")
ALSA_ds_w10$iadl_money <- labelled(ALSA_ds_w10$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10,  echo=FALSE}
vari <- ALSA_ds_w10$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w10$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w10, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10,  echo=FALSE}
AfterH <- table(ALSA_ds_w10$iadl_money)
X<-table(ALSA_w10_iadl_money$iadl7w10)
BeforeH <- c(X[c(2:1,3)],sum(is.na(ALSA_w10_iadl_money$iadl7w10)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","99->994","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w10, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w10) <- NULL
label(ALSA_ds_w10$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$iadl_money <- car::recode(ALSA_m_ds_w10$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w10
save(iadl_money, file = paste0(datafolder, "/w10/iadl_money.RData"))
```

### Wave 11

#### Study-specific variable description

 


* Name: `IDIFF7W11`
* Label: `Level of difficulty managing own money`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `NA`

* Description: 
```{r assign w11,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_iadl_money','ALSA.ALSA-Wave11', variables=list('IDIFF7W11'), missings = TRUE)
```

```{r local w11,  echo=FALSE}
ALSA_w11_iadl_money <- opal.execute(o,'ALSA_w11_iadl_money')
vari <- ALSA_w11_iadl_money$IDIFF7W11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w11_iadl_money$IDIFF7W11)
ggplot(ALSA_w11_iadl_money, aes(x=factor(IDIFF7W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w11,   echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_iadl_money$id)
ALSA_ds_w11$iadl_money <- car::recode(ALSA_w11_iadl_money$IDIFF7W11,"1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w11$iadl_money <- labelled(ALSA_ds_w11$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11,  echo=FALSE}
vari <- ALSA_ds_w11$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11,  echo=FALSE}
AfterH <- table(ALSA_ds_w11$iadl_money)
X<-table(ALSA_w11_iadl_money$IDIFF7W11)
BeforeH <- c(sum(X[c(2:3)]),X[1],sum(is.na(ALSA_w11_iadl_money$IDIFF7W11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w11, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w11) <- NULL
label(ALSA_ds_w11$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$iadl_money <- car::recode(ALSA_m_ds_w11$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w11
save(iadl_money, file = paste0(datafolder, "/w11/iadl_money.RData"))
```

### Wave 12

#### Study-specific variable description

 


* Name: `IDIFF7W12`
* Label: `Level of difficulty managing own money`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `NA`

* Description: 
```{r assign w12,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_iadl_money','ALSA.ALSA-Wave12', variables=list('IDIFF7W12'), missings = TRUE)
```

```{r local w12,  echo=FALSE}
ALSA_w12_iadl_money <- opal.execute(o,'ALSA_w12_iadl_money')
vari <- ALSA_w12_iadl_money$IDIFF7W12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w12_iadl_money$IDIFF7W12)
ggplot(ALSA_w12_iadl_money, aes(x=factor(IDIFF7W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w12,   echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_iadl_money$id)
ALSA_ds_w12$iadl_money <- car::recode(ALSA_w12_iadl_money$IDIFF7W12,"1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w12$iadl_money <- labelled(ALSA_ds_w12$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12,  echo=FALSE}
vari <- ALSA_ds_w12$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12,  echo=FALSE}
AfterH <- table(ALSA_ds_w12$iadl_money)
X<-table(ALSA_w12_iadl_money$IDIFF7W12)
BeforeH <- c(sum(X[c(2)]),X[1],sum(is.na(ALSA_w12_iadl_money$IDIFF7W12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w12, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w12) <- NULL
label(ALSA_ds_w12$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$iadl_money <- car::recode(ALSA_m_ds_w12$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w12
save(iadl_money, file = paste0(datafolder, "/w12/iadl_money.RData"))
```

### Wave 13

#### Study-specific variable description

 


* Name: `IADLDF7W13`
* Label: `Difficulty managing money`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `NA`

* Description: 
```{r assign w13,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_iadl_money','ALSA.ALSA-Wave13', variables=list('IADLDF7W13'), missings = TRUE)
```

```{r local w13,  echo=FALSE}
ALSA_w13_iadl_money <- opal.execute(o,'ALSA_w13_iadl_money')
vari <- ALSA_w13_iadl_money$IDIFF7W13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ALSA_w13_iadl_money$IADLDF7W13)
ggplot(ALSA_w13_iadl_money, aes(x=factor(IADLDF7W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w13,   echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_iadl_money$id)
ALSA_ds_w13$iadl_money <- car::recode(ALSA_w13_iadl_money$IADLDF7W13,"1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w13$iadl_money <- labelled(ALSA_ds_w13$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13,  echo=FALSE}
vari <- ALSA_ds_w13$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w13$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w13, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13,  echo=FALSE}
AfterH <- table(ALSA_ds_w13$iadl_money)
X<-table(ALSA_w13_iadl_money$IADLDF7W13)
BeforeH <- c(sum(X[c(2:3)]),X[1],sum(is.na(ALSA_w13_iadl_money$IADLDF7W13)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w13, echo=FALSE,  echo=FALSE}
val_labels(ALSA_ds_w13) <- NULL
label(ALSA_ds_w13$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$iadl_money <- car::recode(ALSA_m_ds_w13$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- ALSA_ds_w13
save(iadl_money, file = paste0(datafolder, "/w13/iadl_money.RData"))
```

# Quality estimation
Waves 2 and 4 should be handled carefully because of controversies in the original variables.
```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
