---
title: "IADL - Getting out of home"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_outhome`
* Variable label: `IADL - Difficulties for getting out of home`
* Variable description: `IADL - Difficulties for getting out of home`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for getting out of home"
```


# Data process

## ALSA

### Wave 1 	

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `ACTIV6`
* Label: `Going to a place away from home`
* Categories:
   + `0 = No problem` 
   + `1 = Problem`
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_iadl_outhome','ALSA.ALSA-Wave1', variables=list('ACTIV6'), missings = TRUE)
ALSA_w1_iadl_outhome <- opal.execute(o,'ALSA_w1_iadl_outhome')
```

```{r local w1, echo=FALSE}
vari <- ALSA_w1_iadl_outhome$ACTIV6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1_iadl_outhome, aes(x=factor(ACTIV6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 0` 
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_iadl_outhome$id)
ALSA_ds_w1$iadl_outhome <- car::recode(ALSA_w1_iadl_outhome$ACTIV6, "1 = '0';0 = '1';NA = '999' ")
ALSA_ds_w1$iadl_outhome <- labelled(ALSA_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- ALSA_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(ALSA_ds_w1$iadl_outhome)
X<-table(ALSA_w1_iadl_outhome$ACTIV6)
BeforeH <- c(sum(X[c(2)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(ALSA_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w1
save(iadl_outhome, file = "../RData/w1/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$iadl_outhome <- car::recode(ALSA_m_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `Q34.6`
* Label: `Difficulties with: Going to or getting around a place away from home`
* Categories:
   + `1 = Bathing, sponge bath or shower` 
   + `2 = Personal grooming` 
   + `3 = Dressing` 
   + `4 = Eating` 
   + `5 = Using the toilet`
   + `6 = Getting about away from home` 
   + `7 = Moving about inside the house` 
   + `8 = Getting from a bed to a chair` 
   + `9 = No difficulties with any of these`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_iadl_outhome','ALSA.ALSA-Wave2', variables=list('Q34.6'), missings = TRUE)
ALSA_w2_iadl_outhome <- opal.execute(o,'ALSA_w2_iadl_outhome')
```

```{r local w2, echo=FALSE}
vari <- ALSA_w2_iadl_outhome$Q34.6
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
ggplot(ALSA_w2_iadl_outhome, aes(x=factor(Q34.6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 into 0`
* `7,8,9 into 1` 
* `NA into 999`

**R script:**

```{r harmo w2}
ALSA_ds_w2 <- tibble(id=ALSA_w2_iadl_outhome$id)
ALSA_ds_w2$iadl_outhome <- car::recode(ALSA_w2_iadl_outhome$Q34.6, "6 = '0';7 = '1';8 = '1';NA = '999' ")
ALSA_ds_w2$iadl_outhome <- labelled(ALSA_ds_w2$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- ALSA_ds_w2$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(ALSA_ds_w2$iadl_outhome)
X<-table(ALSA_w2_iadl_outhome$Q34.6)
BeforeH <- c(X[1],sum(X[2:3]),sum(is.na(ALSA_w2_iadl_outhome$Q34.6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->0","7,8->1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(ALSA_ds_w2$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w2
save(iadl_outhome, file = "../RData/w2/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$iadl_outhome <- car::recode(ALSA_m_ds_w2$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLDF6W3`
* Label: `AWAY FROM HOME DIFFICULTY`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty`
* Missings
   + `9 = Missing`
   + `NA`

```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_iadl_outhome','ALSA.ALSA-Wave3', variables=list('ADLDF6W3'), missings = TRUE)
ALSA_w3_iadl_outhome <- opal.execute(o,'ALSA_w3_iadl_outhome')
```

```{r local w3, echo=FALSE}
vari <- ALSA_w3_iadl_outhome$ADLDF6W3
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
ggplot(ALSA_w3_iadl_outhome, aes(x=factor(ADLDF6W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_iadl_outhome$id)
ALSA_ds_w3$iadl_outhome <- car::recode(ALSA_w3_iadl_outhome$ADLDF6W3, "1 = '1';2 = '0';3 = '0';4 = '0';9 = '999'; NA = '999' ")
ALSA_ds_w3$iadl_outhome <- labelled(ALSA_ds_w3$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- ALSA_ds_w3$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(ALSA_ds_w3$iadl_outhome)
X<-table(ALSA_w3_iadl_outhome$ADLDF6W3)
BeforeH <- c(sum(X[2:4]),X[1],X[5]+sum(is.na(ALSA_w3_iadl_outhome$ADLDF6W3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","0->1","9,NA->999") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(ALSA_ds_w3$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w3
save(iadl_outhome, file = "../RData/w3/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$iadl_outhome <- car::recode(ALSA_m_ds_w3$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `IADN6W4`
* Label: `DIFFICULTIES WITH: Going to or getting around a place away from home`
* Categories:
    + `0 = No difficulties` 
    + `6 = Difficulties with going to or getting around a place away from home` 
* Missings
   + `NA`

```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_iadl_outhome','ALSA.ALSA-Wave4', variables=list('IADN6W4'), missings = TRUE)
ALSA_w4_iadl_outhome <- opal.execute(o,'ALSA_w4_iadl_outhome')
```

```{r local w4, echo=FALSE}
vari <- ALSA_w4_iadl_outhome$IADN6W4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4_iadl_outhome, aes(x=factor(IADN6W4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**

```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_iadl_outhome$id)
ALSA_ds_w4$iadl_outhome <- car::recode(ALSA_w4_iadl_outhome$IADN6W4, "6 = '0';0 = '1';NA = '999' ")
ALSA_ds_w4$iadl_outhome <- labelled(ALSA_ds_w4$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- ALSA_ds_w4$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(ALSA_ds_w4$iadl_outhome)
X<-table(ALSA_w4_iadl_outhome$IADN6W4)
BeforeH <- c(X[2:1],sum(is.na(ALSA_w4_iadl_outhome$IADN6W4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->0","1->0","NA->999") 
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(ALSA_ds_w4$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w4
save(iadl_outhome, file = "../RData/w4/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$iadl_outhome <- car::recode(ALSA_m_ds_w4$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLND6W5`
* Label: `GOING TO OR GETTING AROUND A PLACE AWAY`
* Categories:
   + `1 = Bathing` 
   + `2 = Personal grooming` 
   + `3 = Dressing` 
   + `4 = Eating` 
   + `5 = Using the toliet` 
   + `6 = Going to or getting around a place` 
   + `7 = Moving about the house` 
   + `8 = Getting from a bed to a chair ` 
   + `9 = No difficulties` 
* Missings
   + `0 = No answer`
   + `NA`

```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_iadl_outhome','ALSA.ALSA-Wave5', variables=list('ADLND6W5'), missings = TRUE)
ALSA_w5_iadl_outhome <- opal.execute(o,'ALSA_w5_iadl_outhome')
```

```{r local w5, echo=FALSE}
vari <- ALSA_w5_iadl_outhome$ADLND6W5
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
ggplot(ALSA_w5_iadl_outhome, aes(x=factor(ADLND6W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 into 0` 
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_iadl_outhome$id)
ALSA_ds_w5$iadl_outhome <- car::recode(ALSA_w5_iadl_outhome$ADLND6W5, "6 = '0';0 = '995';NA = '999' ")
ALSA_ds_w5$iadl_outhome <- labelled(ALSA_ds_w5$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- ALSA_ds_w5$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
AfterH <- table(ALSA_ds_w5$iadl_outhome)
X<-table(ALSA_w5_iadl_outhome$ADLND6W5)
BeforeH <- X[2:1]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->0","0->995") 
kable(C)
```

```{r importOPAL w5, echo=FALSE}
label(ALSA_ds_w5$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w5
save(iadl_outhome, file = "../RData/w5/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$iadl_outhome <- car::recode(ALSA_m_ds_w5$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLDF6W6`
* Label: `level of difficulty getting around`
* Categories:
   + `1 = no difficulty at all` 
   + `2 = a little difficulty` 
   + `3 = some difficulty` 
   + `4 = a lot of difficulty` 
* Missings
   + `0 = No answer`
   + `NA`

```{r assign w6, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_iadl_outhome','ALSA.ALSA-Wave6', variables=list('ADLDF6W6'), missings = TRUE)
ALSA_w6_iadl_outhome <- opal.execute(o,'ALSA_w6_iadl_outhome')
```

```{r local w6, echo=FALSE}
vari <- ALSA_w6_iadl_outhome$ADLDF6W6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
ggplot(ALSA_w6_iadl_outhome, aes(x=factor(ADLDF6W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_iadl_outhome$id)
ALSA_ds_w6$iadl_outhome <- car::recode(ALSA_w6_iadl_outhome$ADLDF6W6, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$iadl_outhome <- labelled(ALSA_ds_w6$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=FALSE}
vari <- ALSA_ds_w6$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=FALSE}
AfterH <- table(ALSA_ds_w6$iadl_outhome)
X<-table(ALSA_w6_iadl_outhome$ADLDF6W6)
BeforeH <- c(sum(X[3:5]),X[2:1],sum(is.na(ALSA_w6_iadl_outhome$ADLDF6W6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

```{r importOPAL w6, echo=FALSE}
label(ALSA_ds_w6$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w6
save(iadl_outhome, file = "../RData/w6/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$iadl_outhome <- car::recode(ALSA_m_ds_w6$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `adldf6w7`
* Label: `level of difficulty getting around`
* Categories:
   + `1 = no difficulty at all` 
   + `2 = a little difficulty` 
   + `3 = some difficulty` 
   + `4 = a lot of difficulty` 
* Missings
   + `0 = Not answered`
   + `NA`

```{r assign w7, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_iadl_outhome','ALSA.ALSA-Wave7', variables=list('adldf6w7'), missings = TRUE)
ALSA_w7_iadl_outhome <- opal.execute(o,'ALSA_w7_iadl_outhome')
```

```{r local w7, echo=FALSE}
vari <- ALSA_w7_iadl_outhome$adldf6w7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
ggplot(ALSA_w7_iadl_outhome, aes(x=factor(adldf6w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_iadl_outhome$id)
ALSA_ds_w7$iadl_outhome <- car::recode(ALSA_w7_iadl_outhome$adldf6w7, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w7$iadl_outhome <- labelled(ALSA_ds_w7$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}
vari <- ALSA_ds_w7$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=FALSE}
AfterH <- table(ALSA_ds_w7$iadl_outhome)
X<-table(ALSA_w7_iadl_outhome$adldf6w7)
BeforeH <- c(sum(X[3:5]),X[2:1],sum(is.na(ALSA_w7_iadl_outhome$adldf6w7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

```{r importOPAL w7, echo=FALSE}
label(ALSA_ds_w7$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w7
save(iadl_outhome, file = "../RData/w7/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$iadl_outhome <- car::recode(ALSA_m_ds_w7$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `adlnd6w8`
* Label: `Going to or getting around a place away from home`
* Categories:
   + `1 = Yes` 
   + `2 = No` 
* Missings
   + `NA`

```{r assign w8}
opal.assign.table.tibble(o, 'ALSA_w8_iadl_outhome','ALSA.ALSA-Wave8', variables=list('adlnd6w8'), missings = TRUE)
ALSA_w8_iadl_outhome <- opal.execute(o,'ALSA_w8_iadl_outhome')
```

```{r local w8}
vari <- ALSA_w8_iadl_outhome$adlnd6w8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8_iadl_outhome, aes(x=factor(adlnd6w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `NA into 999`

**R script:**

```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_iadl_outhome$id)
ALSA_ds_w8$iadl_outhome <- car::recode(ALSA_w8_iadl_outhome$adlnd6w8, "1 = '0';2 = '1';NA = '999' ")
ALSA_ds_w8$iadl_outhome <- labelled(ALSA_ds_w8$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=FALSE}
vari <- ALSA_ds_w8$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=FALSE}
AfterH <- table(ALSA_ds_w8$iadl_outhome)
X<-table(ALSA_w8_iadl_outhome$adlnd6w8)
BeforeH <- c(X[1:2],sum(is.na(ALSA_w8_iadl_outhome$adlnd6w8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```

```{r importOPAL w8, echo=FALSE}
label(ALSA_ds_w8$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w8
save(iadl_outhome, file = "../RData/w8/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$iadl_outhome <- car::recode(ALSA_m_ds_w8$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLDF6W9`
* Label: `level of difficulty getting around`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `0 = Not Answered`
   + `NA`

```{r assign w9, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_iadl_outhome','ALSA.ALSA-Wave9', variables=list('ADLDF6W9'), missings = TRUE)
ALSA_w9_iadl_outhome <- opal.execute(o,'ALSA_w9_iadl_outhome')
```

```{r local w9, echo=FALSE}
vari <- ALSA_w9_iadl_outhome$ADLDF6W9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
ggplot(ALSA_w9_iadl_outhome, aes(x=factor(ADLDF6W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_iadl_outhome$id)
ALSA_ds_w9$iadl_outhome <- car::recode(ALSA_w9_iadl_outhome$ADLDF6W9, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w9$iadl_outhome <- labelled(ALSA_ds_w9$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=FALSE}
vari <- ALSA_ds_w9$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=FALSE}
AfterH <- table(ALSA_ds_w9$iadl_outhome)
X<-table(ALSA_w9_iadl_outhome$ADLDF6W9)
BeforeH <- c(sum(X[c(3:5)]),X[2:1],sum(is.na(ALSA_w9_iadl_outhome$ADLDF6W9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```

```{r importOPAL w9, echo=FALSE}
label(ALSA_ds_w9$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w9
save(iadl_outhome, file = "../RData/w9/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$iadl_outhome <- car::recode(ALSA_m_ds_w9$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10 	

#### Study-specific variable description


The study-specific variables elected to be harmonised is:

* Name: `adlnd6w10`
* Label: `Difficulties going to/ getting around away from home?`
* Categories:
   + `0 = No` 
   + `1 = yes`
* Missings
   + `99 = Not applicable`
   + `NA`

```{r assign w10, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_iadl_outhome','ALSA.ALSA-Wave10', variables=list('adlnd6w10'), missings = TRUE)
ALSA_w10_iadl_outhome <- opal.execute(o,'ALSA_w10_iadl_outhome')
```

```{r local w10, echo=FALSE}
vari <- ALSA_w10_iadl_outhome$adlnd6w10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(ALSA_w10_iadl_outhome, aes(x=factor(adlnd6w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `99 into 996`
* `NA into 999`

**R script:**

```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_iadl_outhome$id)
ALSA_ds_w10$iadl_outhome <- car::recode(ALSA_w10_iadl_outhome$adlnd6w10, "1 = '0';0 = '1';99 = '996';NA = '999' ")
ALSA_ds_w10$iadl_outhome <- labelled(ALSA_ds_w10$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=FALSE}
vari <- ALSA_ds_w10$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=FALSE}
AfterH <- table(ALSA_ds_w10$iadl_outhome)
X<-table(ALSA_w10_iadl_outhome$adlnd6w10)
BeforeH <- c(X[c(2:1,3)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","99->996") 
kable(C)
```

```{r importOPAL w10, echo=FALSE}
label(ALSA_ds_w10$iadl_outhome) <-ds_label
iadl_outhome <- ALSA_ds_w10
save(iadl_outhome, file = "../RData/w10/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$iadl_outhome <- car::recode(ALSA_m_ds_w10$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLDF6W11`
* Label: `Difficulty getting around`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `NA`

```{r assign w11, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_iadl_outhome','ALSA.ALSA-Wave11', variables=list('ADLDF6W11'), missings = TRUE)
ALSA_w11_iadl_outhome <- opal.execute(o,'ALSA_w11_iadl_outhome')
```

```{r local w11, echo=FALSE}
vari <- ALSA_w11_iadl_outhome$ADLDF6W11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_iadl_outhome, aes(x=factor(ADLDF6W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_iadl_outhome$id)
ALSA_ds_w11$iadl_outhome <- car::recode(ALSA_w11_iadl_outhome$ADLDF6W11,"1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w11$iadl_outhome <- labelled(ALSA_ds_w11$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=FALSE}
vari <- ALSA_ds_w11$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=FALSE}
AfterH <- table(ALSA_ds_w11$iadl_outhome)
X<-table(ALSA_w11_iadl_outhome$ADLDF6W11)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w11_iadl_outhome$ADLDF6W11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w11, echo=FALSE}
label(ALSA_ds_w11$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w11
save(iadl_outhome, file = "../RData/w11/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$iadl_outhome <- car::recode(ALSA_m_ds_w11$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLDF6W12`
* Label: `Difficulty getting around`
* Categories:
   + `1 = No difficulty at all` 
   + `2 = A little difficulty` 
   + `3 = Some difficulty` 
   + `4 = A lot of difficulty` 
* Missings
   + `NA`

```{r assign w12, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_iadl_outhome','ALSA.ALSA-Wave12', variables=list('ADLDF6W12'), missings = TRUE)
ALSA_w12_iadl_outhome <- opal.execute(o,'ALSA_w12_iadl_outhome')
```

```{r local w12, echo=FALSE}
vari <- ALSA_w12_iadl_outhome$ADLDF6W12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_iadl_outhome, aes(x=factor(ADLDF6W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:**

```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_iadl_outhome$id)
ALSA_ds_w12$iadl_outhome <- car::recode(ALSA_w12_iadl_outhome$ADLDF6W12,"1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w12$iadl_outhome <- labelled(ALSA_ds_w12$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=FALSE}
vari <- ALSA_ds_w12$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=FALSE}
AfterH <- table(ALSA_ds_w12$iadl_outhome)
X<-table(ALSA_w12_iadl_outhome$ADLDF6W12)
BeforeH <- c(sum(X[c(2:4)]),X[1],sum(is.na(ALSA_w12_iadl_outhome$ADLDF6W12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w12, echo=FALSE}
label(ALSA_ds_w12$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w12
save(iadl_outhome, file = "../RData/w12/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$iadl_outhome <- car::recode(ALSA_m_ds_w12$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13 	

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ADLND6W13`
* Label: `any difficulty away from home`
* Categories:
   + `0 = No` 
   + `1 = Yes` 
* Missings
   + `99 = Not applicable`
   + `NA`

```{r assign w13, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_iadl_outhome','ALSA.ALSA-Wave13', variables=list('ADLND6W13'), missings = TRUE)
ALSA_w13_iadl_outhome <- opal.execute(o,'ALSA_w13_iadl_outhome')
```

```{r local w13, echo=FALSE}
vari <- ALSA_w13_iadl_outhome$ADLND6W13
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(ALSA_w13_iadl_outhome, aes(x=factor(ADLND6W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `99 into 996`
* `NA into 999`

**R script:**

```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_iadl_outhome$id)
ALSA_ds_w13$iadl_outhome <- car::recode(ALSA_w13_iadl_outhome$ADLND6W13,"0 = '1';1 = '0';99 = '996';NA = '999' ")
ALSA_ds_w13$iadl_outhome <- labelled(ALSA_ds_w13$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=FALSE}
vari <- ALSA_ds_w13$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=FALSE}
AfterH <- table(ALSA_ds_w13$iadl_outhome)
X<-table(ALSA_w13_iadl_outhome$ADLND6W13)
BeforeH <- c(X[c(2,1,3)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","99->996") 
kable(C)
```

```{r importOPAL w13, echo=FALSE}
label(ALSA_ds_w13$iadl_outhome) <- ds_label
iadl_outhome <- ALSA_ds_w13
save(iadl_outhome, file = "../RData/w13/iadl_outhome.RData")
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$iadl_outhome <- car::recode(ALSA_m_ds_w13$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
Waves 2, 4 and 5 should be handled carefully because of controversies in the original variables.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
