---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Australia

### Wave 1 

#### Study-specific variable description


| **Name** |`MONTH`|`YEAR`|
|-|-|-|
| **Label** |`MMSE Day - month`|`MMSE Day - year`|
| **Table name** |`ALSA-Wave1`|`ALSA-Wave1`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`3 = No codable reply, refusal; 4 = Not asked; 9 = Missing; NA`|`3 = No codable reply, refusal; 4 = Not asked; 9 = Missing; NA`|
| **Description** |  |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_orientation','ALSA.ALSA-Wave1', variables=list('MONTH','YEAR'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_orientation <- opal.execute(o,'ALSA_w1_orientation')
vari <- ALSA_w1_orientation$MONTH
kable(Categorical_summary(vari, missing_values = c(3,4,9))[3], caption = "MONTH")
kable(Categorical_summary(vari, missing_values =  c(3,4,9))[1], caption = "Category")
ggplot(ALSA_w1_orientation, aes(x=factor(MONTH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w1_orientation$YEAR
kable(Categorical_summary(vari, missing_values =  c(3,4,9))[3], caption = "YEAR")
kable(Categorical_summary(vari, missing_values =  c(3,4,9))[1], caption = "Category")
ggplot(ALSA_w1_orientation, aes(x=factor(YEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `4 into 994`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_orientation$id)
ALSA_ds_w1$orientation <- rep(888,length(ALSA_ds_w1$id))
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==1))]<-1
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==2)|(ALSA_w1_orientation$YEAR==2))]<-0
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==9)&(ALSA_w1_orientation$YEAR!=2))]<-999
ALSA_ds_w1$orientation[which((is.na(ALSA_w1_orientation$MONTH))&(ALSA_w1_orientation$YEAR!=2))]<-999
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$YEAR==9)&(ALSA_w1_orientation$MONTH!=2))]<-999
ALSA_ds_w1$orientation[which((is.na(ALSA_w1_orientation$YEAR))&(ALSA_w1_orientation$MONTH!=2))]<-999
ALSA_ds_w1$orientation[which(is.na(ALSA_w1_orientation$YEAR)&is.na(ALSA_w1_orientation$MONTH))]<-999
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$YEAR==9)&(ALSA_w1_orientation$MONTH==9))]<-999
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==1))]<-994
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==3))]<-994
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==4))]<-994
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==4))]<-994
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==4))]<-994
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==1))]<-997
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==3))]<-997
ALSA_ds_w1$orientation[which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==3))]<-997

ALSA_ds_w1$orientation <- labelled(ALSA_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```


#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$orientation)
combi<-c(
length(which((ALSA_w1_orientation$MONTH==2)|(ALSA_w1_orientation$YEAR==2))),
length(which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==1))),
length(which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==1)))+
length(which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==3)))+
length(which((ALSA_w1_orientation$MONTH==4)&(ALSA_w1_orientation$YEAR==4)))+
length(which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==4)))+
length(which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==4))),
length(which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==1)))+
length(which((ALSA_w1_orientation$MONTH==1)&(ALSA_w1_orientation$YEAR==3)))+
length(which((ALSA_w1_orientation$MONTH==3)&(ALSA_w1_orientation$YEAR==3))),
length(which((ALSA_w1_orientation$MONTH==9)&(ALSA_w1_orientation$YEAR!=2)))+
length(which((is.na(ALSA_w1_orientation$MONTH))&(ALSA_w1_orientation$YEAR!=2)))+
length(which((ALSA_w1_orientation$YEAR==9)&(ALSA_w1_orientation$MONTH!=2)))+
length(which((is.na(ALSA_w1_orientation$YEAR))&(ALSA_w1_orientation$MONTH!=2)))+
length(which(is.na(ALSA_w1_orientation$YEAR)&is.na(ALSA_w1_orientation$MONTH)))-
length(which((ALSA_w1_orientation$YEAR==9)&(ALSA_w1_orientation$MONTH==9))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","4->994","3->997","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w1
save(orientation, file = "../RData/w1/orientation.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$orientation <- car::recode(ALSA_m_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.



### Wave 3 

#### Study-specific variable description


| **Name** |`MONTHW3`|`YEARW3`|
|-|-|-|
| **Label** |`MMSE Day - month`|`MMSE Day - year`|
| **Table name** |`ALSA-Wave3`|`ALSA-Wave3`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`9 = Missing; NA`|`9 = Missing; NA`|
| **Description** |  |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_orientation','ALSA.ALSA-Wave3', variables=list('MONTHW3','YEARW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_orientation <- opal.execute(o,'ALSA_w3_orientation')
vari <- ALSA_w3_orientation$MONTHW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "MONTHW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_orientation, aes(x=factor(MONTHW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w3_orientation$YEARW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "YEARW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_orientation, aes(x=factor(YEARW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_orientation$id)
ALSA_ds_w3$orientation <- rep(999,length(ALSA_ds_w3$id))
ALSA_ds_w3$orientation[which((ALSA_w3_orientation$MONTHW3==1)&(ALSA_w3_orientation$YEARW3==1))]<-1
ALSA_ds_w3$orientation[which((ALSA_w3_orientation$MONTHW3==2)|(ALSA_w3_orientation$YEARW3==2))]<-0

ALSA_ds_w3$orientation <- labelled(ALSA_ds_w3$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$orientation)
combi<-c(
length(which((ALSA_w3_orientation$MONTHW3==2)|(ALSA_w3_orientation$YEARW3==2))),
length(which((ALSA_w3_orientation$MONTHW3==1)&(ALSA_w3_orientation$YEARW3==1))),
length(which((ALSA_w3_orientation$MONTHW3==9)&(ALSA_w3_orientation$YEARW3!=2)))+
length(which((is.na(ALSA_w3_orientation$MONTHW3))&(ALSA_w3_orientation$YEARW3!=2)))+
length(which((ALSA_w3_orientation$YEARW3==9)&(ALSA_w3_orientation$MONTHW3!=2)))+
length(which((is.na(ALSA_w3_orientation$YEARW3))&(ALSA_w3_orientation$MONTHW3!=2)))+
length(which(is.na(ALSA_w3_orientation$YEARW3)&is.na(ALSA_w3_orientation$MONTHW3)))-
length(which((ALSA_w3_orientation$YEARW3==9)&(ALSA_w3_orientation$MONTHW3==9))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w3
save(orientation, file = "../RData/w3/orientation.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$orientation <- car::recode(ALSA_m_ds_w3$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6 

#### Study-specific variable description



| **Name** |`MONTHW6`|`YEARW6`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave6`|`ALSA-Wave6`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`0 = Missing; NA`|`0 = Missing; NA`|
| **Description** |  |  |



```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_orientation','ALSA.ALSA-Wave6', variables=list('MONTHW6','YEARW6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_orientation <- opal.execute(o,'ALSA_w6_orientation')
vari <- ALSA_w6_orientation$MONTHW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "MONTHW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_orientation, aes(x=factor(MONTHW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w6_orientation$YEARW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "YEARW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_orientation, aes(x=factor(YEARW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `0 into 999`
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_orientation$id)
ALSA_ds_w6$orientation <- rep(999,length(ALSA_ds_w6$id))
ALSA_ds_w6$orientation[which((ALSA_w6_orientation$MONTHW6==1)&(ALSA_w6_orientation$YEARW6==1))]<-1
ALSA_ds_w6$orientation[which((ALSA_w6_orientation$MONTHW6==2)|(ALSA_w6_orientation$YEARW6==2))]<-0

ALSA_ds_w6$orientation <- labelled(ALSA_ds_w6$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$orientation)
combi<-c(
length(which((ALSA_w6_orientation$MONTHW6==2)|(ALSA_w6_orientation$YEARW6==2))),
length(which((ALSA_w6_orientation$MONTHW6==1)&(ALSA_w6_orientation$YEARW6==1))),
length(which((ALSA_w6_orientation$MONTHW6==0)&(ALSA_w6_orientation$YEARW6!=2)))+
length(which((is.na(ALSA_w6_orientation$MONTHW6))&(ALSA_w6_orientation$YEARW6!=2)))+
length(which((ALSA_w6_orientation$YEARW6==0)&(ALSA_w6_orientation$MONTHW6!=2)))+
length(which((is.na(ALSA_w6_orientation$YEARW6))&(ALSA_w6_orientation$MONTHW6!=2)))+
length(which(is.na(ALSA_w6_orientation$YEARW6)&is.na(ALSA_w6_orientation$MONTHW6)))-
length(which((ALSA_w6_orientation$YEARW6==0)&(ALSA_w6_orientation$MONTHW6==0))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","0,NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w6
save(orientation, file = "../RData/w6/orientation.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$orientation <- car::recode(ALSA_m_ds_w6$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7 

#### Study-specific variable description




| **Name** |`monthw7`|`yearw7`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave7`|`ALSA-Wave7`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`0 = Missing; NA`|`0 = Missing; NA`|
| **Description** |  |  |



```{r assign W7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_orientation','ALSA.ALSA-Wave7', variables=list('monthw7','yearw7'), missings = TRUE)
```

```{r local W7, echo=F}
ALSA_w7_orientation <- opal.execute(o,'ALSA_w7_orientation')
vari <- ALSA_w7_orientation$monthw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "monthw7")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7_orientation, aes(x=factor(monthw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w7_orientation$yearw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "yearw7")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7_orientation, aes(x=factor(yearw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `0 into 999`
* `NA into 999`

**R script:**
```{r harmo W7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_orientation$id)
ALSA_ds_w7$orientation <- rep(999,length(ALSA_ds_w7$id))
ALSA_ds_w7$orientation[which((ALSA_w7_orientation$monthw7==1)&(ALSA_w7_orientation$yearw7==1))]<-1
ALSA_ds_w7$orientation[which((ALSA_w7_orientation$monthw7==2)|(ALSA_w7_orientation$yearw7==2))]<-0

ALSA_ds_w7$orientation <- labelled(ALSA_ds_w7$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript W7, echo=F}
vari <- ALSA_ds_w7$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation W7, echo=F}
AfterH <- table(ALSA_ds_w7$orientation)
combi<-c(
length(which((ALSA_w7_orientation$monthw7==2)|(ALSA_w7_orientation$yearw7==2))),
length(which((ALSA_w7_orientation$monthw7==1)&(ALSA_w7_orientation$yearw7==1))),
length(which((ALSA_w7_orientation$monthw7==0)&(ALSA_w7_orientation$yearw7!=2)))+
length(which((is.na(ALSA_w7_orientation$monthw7))&(ALSA_w7_orientation$yearw7!=2)))+
length(which((ALSA_w7_orientation$yearw7==0)&(ALSA_w7_orientation$monthw7!=2)))+
length(which((is.na(ALSA_w7_orientation$yearw7))&(ALSA_w7_orientation$monthw7!=2)))+
length(which(is.na(ALSA_w7_orientation$yearw7)&is.na(ALSA_w7_orientation$monthw7)))-
length(which((ALSA_w7_orientation$yearw7==0)&(ALSA_w7_orientation$monthw7==0))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","0,NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w7
save(orientation, file = "../RData/w7/orientation.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$orientation <- car::recode(ALSA_m_ds_w7$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8 

#### Study-specific variable description



| **Name** |`monthw8`|`yearw8`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave8`|`ALSA-Wave8`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`3 = no codable reply, refusal; 0 = Missing; NA`|`3 = no codable reply, refusal; 0 = Missing; NA`|
| **Description** |  |  |



```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_orientation','ALSA.ALSA-Wave8', variables=list('monthw8','yearw8'), missings = TRUE)
```

```{r local w8, echo=F}
ALSA_w8_orientation <- opal.execute(o,'ALSA_w8_orientation')
vari <- ALSA_w8_orientation$monthw8
kable(Categorical_summary(vari, missing_values = c(3,0))[3], caption = "monthw8")
kable(Categorical_summary(vari, missing_values = c(3,0))[1], caption = "Category")
ggplot(ALSA_w8_orientation, aes(x=factor(monthw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w8_orientation$yearw8
kable(Categorical_summary(vari, missing_values = c(3,0))[3], caption = "yearw8")
kable(Categorical_summary(vari, missing_values = c(3,0))[1], caption = "Category")
ggplot(ALSA_w8_orientation, aes(x=factor(yearw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `0 into 999`
* `NA into 999`

**R script:**
```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_orientation$id)
ALSA_ds_w8$orientation <- rep(999,length(ALSA_ds_w8$id))
ALSA_ds_w8$orientation[which((ALSA_w8_orientation$monthw8==1)&(ALSA_w8_orientation$yearw8==1))]<-1
ALSA_ds_w8$orientation[which((ALSA_w8_orientation$monthw8==2)|(ALSA_w8_orientation$yearw8==2))]<-0
ALSA_ds_w8$orientation[which((ALSA_w8_orientation$monthw8==3)&(ALSA_w8_orientation$yearw8==1))]<-997
ALSA_ds_w8$orientation[which((ALSA_w8_orientation$monthw8==1)&(ALSA_w8_orientation$yearw8==3))]<-997
ALSA_ds_w8$orientation[which((ALSA_w8_orientation$monthw8==3)&(ALSA_w8_orientation$yearw8==3))]<-997

ALSA_ds_w8$orientation <- labelled(ALSA_ds_w8$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vari <- ALSA_ds_w8$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$orientation)
combi<-c(
length(which((ALSA_w8_orientation$monthw8==2)|(ALSA_w8_orientation$yearw8==2))),
length(which((ALSA_w8_orientation$monthw8==1)&(ALSA_w8_orientation$yearw8==1))),
length(which((ALSA_w8_orientation$monthw8==3)&(ALSA_w8_orientation$yearw8==1)))+
length(which((ALSA_w8_orientation$monthw8==1)&(ALSA_w8_orientation$yearw8==3)))+
length(which((ALSA_w8_orientation$monthw8==3)&(ALSA_w8_orientation$yearw8==3))),
length(which((ALSA_w8_orientation$monthw8==0)&(ALSA_w8_orientation$yearw8!=2)))+
length(which((is.na(ALSA_w8_orientation$monthw8))&(ALSA_w8_orientation$yearw8!=2)))+
length(which((ALSA_w8_orientation$yearw8==0)&(ALSA_w8_orientation$monthw8!=2)))+
length(which((is.na(ALSA_w8_orientation$yearw8))&(ALSA_w8_orientation$monthw8!=2)))+
length(which(is.na(ALSA_w8_orientation$yearw8)&is.na(ALSA_w8_orientation$monthw8)))-
length(which((ALSA_w8_orientation$yearw8==0)&(ALSA_w8_orientation$monthw8==0))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","3->997","0,NA->999") 
kable(C)
```






```{r importOPAL w8, echo=FALSE}

label(ALSA_ds_w8$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w8
save(orientation, file = "../RData/w8/orientation.RData")

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$orientation <- car::recode(ALSA_m_ds_w8$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9 

#### Study-specific variable description




| **Name** |`MONTHW9`|`YEARW9`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave9`|`ALSA-Wave9`|
| **Categories** |`1 = Correct; 2 = Incorrect`|`1 = Correct; 2 = Incorrect`|
| **Missings** |`0 = Missing; NA`|`0 = Missing; NA`|
| **Description** |  |  |

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_orientation','ALSA.ALSA-Wave9', variables=list('MONTHW9','YEARW9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_orientation <- opal.execute(o,'ALSA_w9_orientation')
vari <- ALSA_w9_orientation$MONTHW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "MONTHW9")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9_orientation, aes(x=factor(MONTHW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w9_orientation$YEARW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "YEARW9")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9_orientation, aes(x=factor(YEARW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `0 into 999`
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_orientation$id)
ALSA_ds_w9$orientation <- rep(999,length(ALSA_ds_w9$id))
ALSA_ds_w9$orientation[which((ALSA_w9_orientation$MONTHW9==1)&(ALSA_w9_orientation$YEARW9==1))]<-1
ALSA_ds_w9$orientation[which((ALSA_w9_orientation$MONTHW9==2)|(ALSA_w9_orientation$YEARW9==2))]<-0

ALSA_ds_w9$orientation <- labelled(ALSA_ds_w9$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$orientation)
combi<-c(
length(which((ALSA_w9_orientation$MONTHW9==2)|(ALSA_w9_orientation$YEARW9==2))),
length(which((ALSA_w9_orientation$MONTHW9==1)&(ALSA_w9_orientation$YEARW9==1))),
length(which((ALSA_w9_orientation$MONTHW9==0)&(ALSA_w9_orientation$YEARW9!=2)))+
length(which((is.na(ALSA_w9_orientation$MONTHW9))&(ALSA_w9_orientation$YEARW9!=2)))+
length(which((ALSA_w9_orientation$YEARW9==0)&(ALSA_w9_orientation$MONTHW9!=2)))+
length(which((is.na(ALSA_w9_orientation$YEARW9))&(ALSA_w9_orientation$MONTHW9!=2)))+
length(which(is.na(ALSA_w9_orientation$YEARW9)&is.na(ALSA_w9_orientation$MONTHW9)))-
length(which((ALSA_w9_orientation$YEARW9==0)&(ALSA_w9_orientation$MONTHW9==0))))
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","0,NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w9
save(orientation, file = "../RData/w9/orientation.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$orientation <- car::recode(ALSA_m_ds_w9$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description




| **Name** |`monthw10`|`yearw10`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave10`|`ALSA-Wave10`|
| **Categories** |`1 = Correct; 0 = Incorrect`|`1 = Correct; 0 = Incorrect`|
| **Missings** |`99 = Not answered; NA`|`99 = Not answered; NA`|
| **Description** |  |  |



```{r assign W10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_orientation','ALSA.ALSA-Wave10', variables=list('monthw10','yearw10'), missings = TRUE)
```

```{r local W10, echo=F}
ALSA_w10_orientation <- opal.execute(o,'ALSA_w10_orientation')
vari <- ALSA_w10_orientation$monthw10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "monthw10")
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
ggplot(ALSA_w10_orientation, aes(x=factor(monthw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w10_orientation$yearw10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "yearw10")
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
ggplot(ALSA_w10_orientation, aes(x=factor(yearw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `99 into 995`
* `NA into 999`

**R script:**
```{r harmo W10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_orientation$id)
ALSA_ds_w10$orientation <- rep(888,length(ALSA_ds_w10$id))
ALSA_ds_w10$orientation[which((ALSA_w10_orientation$monthw10==1)&(ALSA_w10_orientation$yearw10==1))]<-1
ALSA_ds_w10$orientation[which((ALSA_w10_orientation$monthw10==0)|(ALSA_w10_orientation$yearw10==0))]<-0
ALSA_ds_w10$orientation[which((ALSA_w10_orientation$monthw10==99)&(ALSA_w10_orientation$yearw10!=0))]<-995
ALSA_ds_w10$orientation[which((is.na(ALSA_w10_orientation$monthw10))&(ALSA_w10_orientation$yearw10!=0))]<-999
ALSA_ds_w10$orientation[which((ALSA_w10_orientation$yearw10==99)&(ALSA_w10_orientation$monthw10!=0))]<-995
ALSA_ds_w10$orientation[which((is.na(ALSA_w10_orientation$yearw10))&(ALSA_w10_orientation$monthw10!=0))]<-999
ALSA_ds_w10$orientation[which(is.na(ALSA_w10_orientation$yearw10)&is.na(ALSA_w10_orientation$monthw10))]<-999

ALSA_ds_w10$orientation <- labelled(ALSA_ds_w10$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=990, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript W10, echo=F}
vari <- ALSA_ds_w10$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation W10, echo=F}
AfterH <- table(ALSA_ds_w10$orientation)
combi<-c(
length(which((ALSA_w10_orientation$monthw10==0)|(ALSA_w10_orientation$yearw10==0))),
length(which((ALSA_w10_orientation$monthw10==1)&(ALSA_w10_orientation$yearw10==1))),
length(which((ALSA_w10_orientation$monthw10==99)&(ALSA_w10_orientation$yearw10!=0)))+
length(which((ALSA_w10_orientation$yearw10==99)&(ALSA_w10_orientation$monthw10!=0)))-
length(which((ALSA_w10_orientation$yearw10==99)&(ALSA_w10_orientation$monthw10==99))),
length(which((is.na(ALSA_w10_orientation$yearw10))&(ALSA_w10_orientation$monthw10!=0)))+
length(which(is.na(ALSA_w10_orientation$yearw10)&is.na(ALSA_w10_orientation$monthw10)))
)
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","99->995","NA->999") 
kable(C)
```






```{r importOPAL w10, echo=FALSE}

label(ALSA_ds_w10$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w10
save(orientation, file = "../RData/w10/orientation.RData")

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$orientation <- car::recode(ALSA_m_ds_w10$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description




| **Name** |`MONTHW11`|`YEARW11`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave11`|`ALSA-Wave11`|
| **Categories** |`1 = Correct; 0 = Incorrect`|`1 = Correct; 0 = Incorrect`|
| **Missings** |`NA`|`NA`|
| **Description** |  |  |



```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_orientation','ALSA.ALSA-Wave11', variables=list('MONTHW11','YEARW11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_orientation <- opal.execute(o,'ALSA_w11_orientation')
vari <- ALSA_w11_orientation$MONTHW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "MONTHW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_orientation, aes(x=factor(MONTHW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w11_orientation$YEARW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "YEARW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_orientation, aes(x=factor(YEARW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_orientation$id)
ALSA_ds_w11$orientation <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$orientation[which((ALSA_w11_orientation$MONTHW11==1)&(ALSA_w11_orientation$YEARW11==1))]<-1
ALSA_ds_w11$orientation[which((ALSA_w11_orientation$MONTHW11==0)|(ALSA_w11_orientation$YEARW11==0))]<-0

ALSA_ds_w11$orientation <- labelled(ALSA_ds_w11$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=990, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$orientation)
combi<-c(
length(which((ALSA_w11_orientation$MONTHW11==0)|(ALSA_w11_orientation$YEARW11==0))),
length(which((ALSA_w11_orientation$MONTHW11==1)&(ALSA_w11_orientation$YEARW11==1))),
length(which((is.na(ALSA_w11_orientation$YEARW11))&(ALSA_w11_orientation$MONTHW11!=0)))+
length(which(is.na(ALSA_w11_orientation$YEARW11)&is.na(ALSA_w11_orientation$MONTHW11)))
)
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w11
save(orientation, file = "../RData/w11/orientation.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$orientation <- car::recode(ALSA_m_ds_w11$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description



| **Name** |`MONTHW12`|`YEARW12`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave12`|`ALSA-Wave12`|
| **Categories** |`1 = Correct; 0 = Incorrect`|`1 = Correct; 0 = Incorrect`|
| **Missings** |`NA`|`NA`|
| **Description** |  |  |



```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_orientation','ALSA.ALSA-Wave12', variables=list('MONTHW12','YEARW12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_orientation <- opal.execute(o,'ALSA_w12_orientation')
vari <- ALSA_w12_orientation$MONTHW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "MONTHW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_orientation, aes(x=factor(MONTHW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w12_orientation$YEARW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "YEARW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_orientation, aes(x=factor(YEARW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_orientation$id)
ALSA_ds_w12$orientation <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$orientation[which((ALSA_w12_orientation$MONTHW12==1)&(ALSA_w12_orientation$YEARW12==1))]<-1
ALSA_ds_w12$orientation[which((ALSA_w12_orientation$MONTHW12==0)|(ALSA_w12_orientation$YEARW12==0))]<-0

ALSA_ds_w12$orientation <- labelled(ALSA_ds_w12$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=990, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$orientation)
combi<-c(
length(which((ALSA_w12_orientation$MONTHW12==0)|(ALSA_w12_orientation$YEARW12==0))),
length(which((ALSA_w12_orientation$MONTHW12==1)&(ALSA_w12_orientation$YEARW12==1))),
length(which((is.na(ALSA_w12_orientation$YEARW12))&(ALSA_w12_orientation$MONTHW12!=0)))+
length(which(is.na(ALSA_w12_orientation$YEARW12)&is.na(ALSA_w12_orientation$MONTHW12)))
)
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w12
save(orientation, file = "../RData/w12/orientation.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$orientation <- car::recode(ALSA_m_ds_w12$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description


| **Name** |`MONTHW13`|`YEARW13`|
|-|-|-|
| **Label** |`What is the month?`|`What is the year?`|
| **Table name** |`ALSA-Wave13`|`ALSA-Wave13`|
| **Categories** |`1 = Correct; 0 = Incorrect`|`1 = Correct; 0 = Incorrect`|
| **Missings** |`NA`|`NA`|
| **Description** |  |  |




```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_orientation','ALSA.ALSA-Wave13', variables=list('MONTHW13','YEARW13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_orientation <- opal.execute(o,'ALSA_w13_orientation')
vari <- ALSA_w13_orientation$MONTHW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "MONTHW13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_orientation, aes(x=factor(MONTHW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-month") + ylab("Frequency")
vari <- ALSA_w13_orientation$YEARW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "YEARW13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_orientation, aes(x=factor(YEARW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_orientation$id)
ALSA_ds_w13$orientation <- rep(999,length(ALSA_ds_w13$id))
ALSA_ds_w13$orientation[which((ALSA_w13_orientation$MONTHW13==1)&(ALSA_w13_orientation$YEARW13==1))]<-1
ALSA_ds_w13$orientation[which((ALSA_w13_orientation$MONTHW13==0)|(ALSA_w13_orientation$YEARW13==0))]<-0

ALSA_ds_w13$orientation <- labelled(ALSA_ds_w13$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=990, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$orientation)
combi<-c(
length(which((ALSA_w13_orientation$MONTHW13==0)|(ALSA_w13_orientation$YEARW13==0))),
length(which((ALSA_w13_orientation$MONTHW13==1)&(ALSA_w13_orientation$YEARW13==1))),
length(which((is.na(ALSA_w13_orientation$YEARW13))&(ALSA_w13_orientation$MONTHW13!=0)))+
length(which(is.na(ALSA_w13_orientation$YEARW13)&is.na(ALSA_w13_orientation$MONTHW13)))
)
BeforeH <- combi
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
orientation <- ALSA_ds_w13
save(orientation, file = "../RData/w13/orientation.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$orientation <- car::recode(ALSA_m_ds_w13$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
For this study, the variable is a composed combining month, year
which is different from the calculation performed in other studies where day of the month,
day of the week, month, year and season are available. 


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

