---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## ALSA

### Wave 1

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `ACCDHA`
* Label: `number of Falls in year`
* Categories:
   + `Continouos`
* Missings
   + `999 = Missing`
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_recent_falls','ALSA.ALSA-Wave1', variables=list('ACCDHA'), missings = TRUE)
ALSA_w1_recent_falls <- opal.execute(o,'ALSA_w1_recent_falls')
```

```{r local w1, echo=FALSE}
vari <- ALSA_w1_recent_falls$ACCDHA
kable(Categorical_summary(vari, missing_values = c(999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(999))[2], caption = "Type of missing")
ggplot(ALSA_w1_recent_falls, aes(x=factor(ACCDHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `999 into 999` 
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_recent_falls$id)
ALSA_ds_w1$recent_falls <- rep(888,length(ALSA_ds_w1$id))
ALSA_ds_w1$recent_falls[which(ALSA_w1_recent_falls$ACCDHA==0)]<-0
ALSA_ds_w1$recent_falls[which((is.na(ALSA_w1_recent_falls$ACCDHA))|(ALSA_w1_recent_falls$ACCDHA==999))]<-999
ALSA_ds_w1$recent_falls[which((ALSA_w1_recent_falls$ACCDHA>=1)&(ALSA_w1_recent_falls$ACCDHA!=999))]<-1
ALSA_ds_w1$recent_falls <- labelled(ALSA_ds_w1$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- ALSA_ds_w1$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(ALSA_ds_w1$recent_falls)
BeforeH<-c(
  length(which(ALSA_w1_recent_falls$ACCDHA==0)),
  length(which((ALSA_w1_recent_falls$ACCDHA>=1)&(ALSA_w1_recent_falls$ACCDHA!=999))),
  length(which((is.na(ALSA_w1_recent_falls$ACCDHA))|(ALSA_w1_recent_falls$ACCDHA==999)))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","999,NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(ALSA_ds_w1$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w1
save(recent_falls, file = "../RData/w1/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$recent_falls <- car::recode(ALSA_m_ds_w1$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `Q7A`
* Label: `how many falls?`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_recent_falls','ALSA.ALSA-Wave2', variables=list('Q7A'), missings = TRUE)
ALSA_w2_recent_falls <- opal.execute(o,'ALSA_w2_recent_falls')
```

```{r local w2, echo=FALSE}
vari <- ALSA_w2_recent_falls$Q7A
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w2_recent_falls, aes(x=factor(Q7A))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w2}
ALSA_ds_w2 <- tibble(id=ALSA_w2_recent_falls$id)
ALSA_ds_w2$recent_falls <- rep(888,length(ALSA_ds_w2$id))
#ALSA_ds_w2$recent_falls[which(ALSA_w2_recent_falls$Q7A==0)]<-0
ALSA_ds_w2$recent_falls[which(is.na(ALSA_w2_recent_falls$Q7A))]<-999
ALSA_ds_w2$recent_falls[which((ALSA_w2_recent_falls$Q7A>=1)&(ALSA_w2_recent_falls$Q7A!=999))]<-1
ALSA_ds_w2$recent_falls <- labelled(ALSA_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- ALSA_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(ALSA_ds_w2$recent_falls)
BeforeH<-c(
  #length(which(ALSA_w2_recent_falls$Q7A==0)),
  length(which((ALSA_w2_recent_falls$Q7A>=1)&(ALSA_w2_recent_falls$Q7A!=999))),
  length(which(is.na(ALSA_w2_recent_falls$Q7A)))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(ALSA_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$recent_falls <- car::recode(ALSA_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW3`
* Label: `number of Falls in year`
* Categories:
   + `Continouos`
* Missings
   + `999 = Missing`
   + `NA`

```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_recent_falls','ALSA.ALSA-Wave3', variables=list('ACCDHAW3'), missings = TRUE)
ALSA_w3_recent_falls <- opal.execute(o,'ALSA_w3_recent_falls')
```

```{r local w3, echo=FALSE}
vari <- ALSA_w3_recent_falls$ACCDHAW3
kable(Categorical_summary(vari, missing_values = c(999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(999))[2], caption = "Type of missing")
ggplot(ALSA_w3_recent_falls, aes(x=factor(ACCDHAW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `999 into 999` 
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_recent_falls$id)
ALSA_ds_w3$recent_falls <- rep(888,length(ALSA_ds_w3$id))
ALSA_ds_w3$recent_falls[which(ALSA_w3_recent_falls$ACCDHAW3==0)]<-0
ALSA_ds_w3$recent_falls[which((is.na(ALSA_w3_recent_falls$ACCDHAW3))|(ALSA_w3_recent_falls$ACCDHAW3==999))]<-999
ALSA_ds_w3$recent_falls[which((ALSA_w3_recent_falls$ACCDHAW3>=1)&(ALSA_w3_recent_falls$ACCDHAW3!=999))]<-1
ALSA_ds_w3$recent_falls <- labelled(ALSA_ds_w3$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- ALSA_ds_w3$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(ALSA_ds_w3$recent_falls)
BeforeH<-c(
  length(which(ALSA_w3_recent_falls$ACCDHAW3==0)),
  length(which((ALSA_w3_recent_falls$ACCDHAW3>=1)&(ALSA_w3_recent_falls$ACCDHAW3!=999))),
  length(which((is.na(ALSA_w3_recent_falls$ACCDHAW3))|(ALSA_w3_recent_falls$ACCDHAW3==999)))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","999,NA->999") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(ALSA_ds_w3$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w3
save(recent_falls, file = "../RData/w3/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$recent_falls <- car::recode(ALSA_m_ds_w3$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW4`
* Label: `How many falls?`
* Categories:
   + `Continouos`
   + `-1 = Had falls can't remember number`
* Missings
   + `NA`

```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_recent_falls','ALSA.ALSA-Wave4', variables=list('ACCDHAW4'), missings = TRUE)
ALSA_w4_recent_falls <- opal.execute(o,'ALSA_w4_recent_falls')
```

```{r local w4, echo=FALSE}
vari <- ALSA_w4_recent_falls$ACCDHAW4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4_recent_falls, aes(x=factor(ACCDHAW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 and -1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_recent_falls$id)
ALSA_ds_w4$recent_falls <- rep(888,length(ALSA_ds_w4$id))
ALSA_ds_w4$recent_falls[which(ALSA_w4_recent_falls$ACCDHAW4==0)]<-0
ALSA_ds_w4$recent_falls[which(is.na(ALSA_w4_recent_falls$ACCDHAW4))]<-999
ALSA_ds_w4$recent_falls[which(((ALSA_w4_recent_falls$ACCDHAW4>=1)|(ALSA_w4_recent_falls$ACCDHAW4-1))&(ALSA_w4_recent_falls$ACCDHAW4!=999))]<-1
ALSA_ds_w4$recent_falls <- labelled(ALSA_ds_w4$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- ALSA_ds_w4$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(ALSA_ds_w4$recent_falls)
BeforeH<-c(
 # length(which(ALSA_w4_recent_falls$ACCDHAW4==0)),
  length(which(((ALSA_w4_recent_falls$ACCDHAW4>=1)|(ALSA_w4_recent_falls$ACCDHAW4-1))&(ALSA_w4_recent_falls$ACCDHAW4!=999))),
  length(which((is.na(ALSA_w4_recent_falls$ACCDHAW4))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1&-1->1","999,NA->999") 
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(ALSA_ds_w4$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w4
save(recent_falls, file = "../RData/w4/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$recent_falls <- car::recode(ALSA_m_ds_w4$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW5`
* Label: `How many falls?`
* Categories:
   + `Continouos`
* Missings
   + `-1 = Don't know`
   + `NA`

```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_recent_falls','ALSA.ALSA-Wave5', variables=list('ACCDHAW5'), missings = TRUE)
ALSA_w5_recent_falls <- opal.execute(o,'ALSA_w5_recent_falls')
```

```{r local w5, echo=FALSE}
vari <- ALSA_w5_recent_falls$ACCDHAW5
kable(Categorical_summary(vari, missing_values = c(-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1))[2], caption = "Type of missing")
ggplot(ALSA_w5_recent_falls, aes(x=factor(ACCDHAW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `-1 into 999`
* `NA into 999`

**R script:**

```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_recent_falls$id)
ALSA_ds_w5$recent_falls <- rep(888,length(ALSA_ds_w5$id))
#ALSA_ds_w5$recent_falls[which(ALSA_w5_recent_falls$ACCDHAW5==0)]<-0
ALSA_ds_w5$recent_falls[which((is.na(ALSA_w5_recent_falls$ACCDHAW5))|(ALSA_w5_recent_falls$ACCDHAW5==-1))]<-999
ALSA_ds_w5$recent_falls[which(ALSA_w5_recent_falls$ACCDHAW5>=1)]<-1
ALSA_ds_w5$recent_falls <- labelled(ALSA_ds_w5$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- ALSA_ds_w5$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
AfterH <- table(ALSA_ds_w5$recent_falls)
BeforeH<-c(
 # length(which(ALSA_w5_recent_falls$ACCDHAW5==0)),
  length(which(ALSA_w5_recent_falls$ACCDHAW5>=1)),
  length(which((is.na(ALSA_w5_recent_falls$ACCDHAW5))|(ALSA_w5_recent_falls$ACCDHAW5==-1)))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->1","-1,NA->999") 
kable(C)
```

```{r importOPAL w5, echo=FALSE}
label(ALSA_ds_w5$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w5
save(recent_falls, file = "../RData/w5/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$recent_falls <- car::recode(ALSA_m_ds_w5$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW6`
* Label: `number of falls in last year`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w6, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_recent_falls','ALSA.ALSA-Wave6', variables=list('ACCDHAW6'), missings = TRUE)
ALSA_w6_recent_falls <- opal.execute(o,'ALSA_w6_recent_falls')
```

```{r local w6, echo=FALSE}
vari <- ALSA_w6_recent_falls$ACCDHAW6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6_recent_falls, aes(x=factor(ACCDHAW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_recent_falls$id)
ALSA_ds_w6$recent_falls <- rep(888,length(ALSA_ds_w6$id))
ALSA_ds_w6$recent_falls[which(ALSA_w6_recent_falls$ACCDHAW6==0)]<-0
ALSA_ds_w6$recent_falls[which((is.na(ALSA_w6_recent_falls$ACCDHAW6)))]<-999
ALSA_ds_w6$recent_falls[which(ALSA_w6_recent_falls$ACCDHAW6>=1)]<-1
ALSA_ds_w6$recent_falls <- labelled(ALSA_ds_w6$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=FALSE}
vari <- ALSA_ds_w6$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=FALSE}
AfterH <- table(ALSA_ds_w6$recent_falls)
BeforeH<-c(
  length(which(ALSA_w6_recent_falls$ACCDHAW6==0)),
  length(which(ALSA_w6_recent_falls$ACCDHAW6>=1)),
  length(which((is.na(ALSA_w6_recent_falls$ACCDHAW6))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w6, echo=FALSE}
label(ALSA_ds_w6$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w6
save(recent_falls, file = "../RData/w6/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$recent_falls <- car::recode(ALSA_m_ds_w6$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `accdhaw7`
* Label: `how many falls in past year`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w7, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_recent_falls','ALSA.ALSA-Wave7', variables=list('accdhaw7'), missings = TRUE)
ALSA_w7_recent_falls <- opal.execute(o,'ALSA_w7_recent_falls')
```

```{r local w7, echo=FALSE}
vari <-ALSA_w7_recent_falls$accdhaw7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7_recent_falls, aes(x=factor(accdhaw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_recent_falls$id)
ALSA_ds_w7$recent_falls <- rep(888,length(ALSA_ds_w7$id))
ALSA_ds_w7$recent_falls[which(ALSA_w7_recent_falls$accdhaw7==0)]<-0
ALSA_ds_w7$recent_falls[which((is.na(ALSA_w7_recent_falls$accdhaw7)))]<-999
ALSA_ds_w7$recent_falls[which(ALSA_w7_recent_falls$accdhaw7>=1)]<-1
ALSA_ds_w7$recent_falls <- labelled(ALSA_ds_w7$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}
vari <- ALSA_ds_w7$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=FALSE}
AfterH <- table(ALSA_ds_w7$recent_falls)
BeforeH<-c(
  length(which(ALSA_w7_recent_falls$accdhaw7==0)),
  length(which(ALSA_w7_recent_falls$accdhaw7>=1)),
  length(which((is.na(ALSA_w7_recent_falls$accdhaw7))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w7, echo=FALSE}
label(ALSA_ds_w7$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w7
save(recent_falls, file = "../RData/w7/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$recent_falls <- car::recode(ALSA_m_ds_w7$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `accdhaw8`
* Label: `How many falls?`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w8, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w8_recent_falls','ALSA.ALSA-Wave8', variables=list('accdhaw8'), missings = TRUE)
ALSA_w8_recent_falls <- opal.execute(o,'ALSA_w8_recent_falls')
```

```{r local w8, echo=FALSE}
vari <- ALSA_w8_recent_falls$accdhaw8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8_recent_falls, aes(x=factor(accdhaw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_recent_falls$id)
ALSA_ds_w8$recent_falls <- rep(888,length(ALSA_ds_w8$id))
ALSA_ds_w8$recent_falls[which(ALSA_w8_recent_falls$accdhaw8==0)]<-0
ALSA_ds_w8$recent_falls[which((is.na(ALSA_w8_recent_falls$accdhaw8)))]<-999
ALSA_ds_w8$recent_falls[which(ALSA_w8_recent_falls$accdhaw8>=1)]<-1
ALSA_ds_w8$recent_falls <- labelled(ALSA_ds_w8$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=FALSE}
vari <- ALSA_ds_w8$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=FALSE}
AfterH <- table(ALSA_ds_w8$recent_falls)
BeforeH<-c(
  length(which(ALSA_w8_recent_falls$accdhaw8==0)),
  length(which(ALSA_w8_recent_falls$accdhaw8>=1)),
  length(which((is.na(ALSA_w8_recent_falls$accdhaw8))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w8, echo=FALSE}
label(ALSA_ds_w8$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w8
save(recent_falls, file = "../RData/w8/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$recent_falls <- car::recode(ALSA_m_ds_w8$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW9`
* Label: `how many falls in the past year`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w9, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_recent_falls','ALSA.ALSA-Wave9', variables=list('ACCDHAW9'), missings = TRUE)
ALSA_w9_recent_falls <- opal.execute(o,'ALSA_w9_recent_falls')
```

```{r local w9, echo=FALSE}
vari <- ALSA_w9_recent_falls$ACCDHAW9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_recent_falls, aes(x=factor(ACCDHAW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_recent_falls$id)
ALSA_ds_w9$recent_falls <- rep(888,length(ALSA_ds_w9$id))
ALSA_ds_w9$recent_falls[which(ALSA_w9_recent_falls$ACCDHAW9==0)]<-0
ALSA_ds_w9$recent_falls[which((is.na(ALSA_w9_recent_falls$ACCDHAW9)))]<-999
ALSA_ds_w9$recent_falls[which(ALSA_w9_recent_falls$ACCDHAW9>=1)]<-1
ALSA_ds_w9$recent_falls <- labelled(ALSA_ds_w9$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=FALSE}
vari <- ALSA_ds_w9$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=FALSE}
AfterH <- table(ALSA_ds_w9$recent_falls)
BeforeH<-c(
  length(which(ALSA_w9_recent_falls$ACCDHAW9==0)),
  length(which(ALSA_w9_recent_falls$ACCDHAW9>=1)),
  length(which((is.na(ALSA_w9_recent_falls$ACCDHAW9))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w9, echo=FALSE}
label(ALSA_ds_w9$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w9
save(recent_falls, file = "../RData/w9/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$recent_falls <- car::recode(ALSA_m_ds_w9$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `accdhaw10`
* Label: `how many falls?`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w10, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_recent_falls','ALSA.ALSA-Wave10', variables=list('accdhaw10'), missings = TRUE)
ALSA_w10_recent_falls <- opal.execute(o,'ALSA_w10_recent_falls')
```

```{r local w10, echo=FALSE}
vari <- ALSA_w10_recent_falls$accdhaw10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10_recent_falls, aes(x=factor(accdhaw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_recent_falls$id)
ALSA_ds_w10$recent_falls <- rep(888,length(ALSA_ds_w10$id))
ALSA_ds_w10$recent_falls[which(ALSA_w10_recent_falls$accdhaw10==0)]<-0
ALSA_ds_w10$recent_falls[which((is.na(ALSA_w10_recent_falls$accdhaw10)))]<-999
ALSA_ds_w10$recent_falls[which(ALSA_w10_recent_falls$accdhaw10>=1)]<-1
ALSA_ds_w10$recent_falls <- labelled(ALSA_ds_w10$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=FALSE}
vari <- ALSA_ds_w10$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=FALSE}
AfterH <- table(ALSA_ds_w10$recent_falls)
BeforeH<-c(
  length(which(ALSA_w10_recent_falls$accdhaw10==0)),
  length(which(ALSA_w10_recent_falls$accdhaw10>=1)),
  length(which((is.na(ALSA_w10_recent_falls$accdhaw10))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w10, echo=FALSE}
label(ALSA_ds_w10$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w10
save(recent_falls, file = "../RData/w10/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$recent_falls <- car::recode(ALSA_m_ds_w10$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW11`
* Label: `how many falls in the past year`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w11, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_recent_falls','ALSA.ALSA-Wave11', variables=list('ACCDHAW11'), missings = TRUE)
ALSA_w11_recent_falls <- opal.execute(o,'ALSA_w11_recent_falls')
```

```{r local w11, echo=FALSE}
vari <- ALSA_w11_recent_falls$ACCDHAW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_recent_falls, aes(x=factor(ACCDHAW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_recent_falls$id)
ALSA_ds_w11$recent_falls <- rep(888,length(ALSA_ds_w11$id))
ALSA_ds_w11$recent_falls[which(ALSA_w11_recent_falls$ACCDHAW11==0)]<-0
ALSA_ds_w11$recent_falls[which((is.na(ALSA_w11_recent_falls$ACCDHAW11)))]<-999
ALSA_ds_w11$recent_falls[which(ALSA_w11_recent_falls$ACCDHAW11>=1)]<-1
ALSA_ds_w11$recent_falls <- labelled(ALSA_ds_w11$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=FALSE}
vari <- ALSA_ds_w11$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=FALSE}
AfterH <- table(ALSA_ds_w11$recent_falls)
BeforeH<-c(
  length(which(ALSA_w11_recent_falls$ACCDHAW11==0)),
  length(which(ALSA_w11_recent_falls$ACCDHAW11>=1)),
  length(which((is.na(ALSA_w11_recent_falls$ACCDHAW11))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w11, echo=FALSE}
label(ALSA_ds_w11$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w11
save(recent_falls, file = "../RData/w11/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$recent_falls <- car::recode(ALSA_m_ds_w11$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ACCDHAW12`
* Label: `how many falls in the past year`
* Categories:
   + `Continouos`
* Missings
   + `NA`

```{r assign w12, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_recent_falls','ALSA.ALSA-Wave12', variables=list('ACCDHAW12'), missings = TRUE)
ALSA_w12_recent_falls <- opal.execute(o,'ALSA_w12_recent_falls')
```

```{r local w12, echo=FALSE}
vari <- ALSA_w12_recent_falls$ACCDHAW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_recent_falls, aes(x=factor(ACCDHAW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>=1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_recent_falls$id)
ALSA_ds_w12$recent_falls <- rep(888,length(ALSA_ds_w12$id))
ALSA_ds_w12$recent_falls[which(ALSA_w12_recent_falls$ACCDHAW12==0)]<-0
ALSA_ds_w12$recent_falls[which((is.na(ALSA_w12_recent_falls$ACCDHAW12)))]<-999
ALSA_ds_w12$recent_falls[which(ALSA_w12_recent_falls$ACCDHAW12>=1)]<-1
ALSA_ds_w12$recent_falls <- labelled(ALSA_ds_w12$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=FALSE}
vari <- ALSA_ds_w12$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=FALSE}
AfterH <- table(ALSA_ds_w12$recent_falls)
BeforeH<-c(
  length(which(ALSA_w12_recent_falls$ACCDHAW12==0)),
  length(which(ALSA_w12_recent_falls$ACCDHAW12>=1)),
  length(which((is.na(ALSA_w12_recent_falls$ACCDHAW12))))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0",">=1->1","NA->999") 
kable(C)
```

```{r importOPAL w12, echo=FALSE}
label(ALSA_ds_w12$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w12
save(recent_falls, file = "../RData/w12/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$recent_falls <- car::recode(ALSA_m_ds_w12$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `FALLSW13`
* Label: `have you had any falls?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign w13, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_recent_falls','ALSA.ALSA-Wave13', variables=list('FALLSW13'), missings = TRUE)
ALSA_w13_recent_falls <- opal.execute(o,'ALSA_w13_recent_falls')
```

```{r local w13, echo=FALSE}
vari <- ALSA_w13_recent_falls$FALLSW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_recent_falls, aes(x=factor(FALLSW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_recent_falls$id)
ALSA_ds_w13$recent_falls <- car::recode(ALSA_w13_recent_falls$FALLSW13, "1 = '1';0 = '0' ")
ALSA_ds_w13$recent_falls <- labelled(ALSA_ds_w13$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=FALSE}
vari <- ALSA_ds_w13$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=FALSE}
AfterH <- table(ALSA_ds_w13$recent_falls)
X<-table(ALSA_w13_recent_falls$FALLSW13)
BeforeH<-X
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```


```{r importOPAL w13, echo=FALSE}
label(ALSA_ds_w13$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ALSA_ds_w13
save(recent_falls, file = "../RData/w13/recent_falls.RData")
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$recent_falls <- car::recode(ALSA_m_ds_w13$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
