---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```


# Data process

## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `SATLIFE` |
|-|-|
| **Label** | `Satisfied with life`|
| **Table name** | `ALSA-Wave1` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Missings** |`9 = Missing` |
| **Description** |  |  

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave1', variables=list('SATLIFE'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w1, echo=F}

vbl <- ALSA_wb$SATLIFE
vbl_miss <- 9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(SATLIFE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `9 into 999` 
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_wb$id)
ALSA_ds_w1$evaluative_wb <- car::recode(ALSA_wb$SATLIFE, "1=2; 3=1; 4=0; 5=0; 9=999; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}

```



### Wave 2

Not found


### Wave 3


Not found


### Wave 4


#### Study-specific variable description

| **Name** | `ENJLFW4` |
|-|-|
| **Label** | `HOW MUCH DO YOU ENJOY LIFE NOW?`|
| **Table name** | `ALSA-Wave4` | 
| **Categories** | `1 = Very much` <br/> `2 = Quite a bit` <br/> `3 = Reasonably` <br/> `4 = Not much` <br/> `5 = Not at all` | 
| **Missings** |`-1 = Dont know` |
| **Description** |  |  

   

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave4', variables=list('ENJLFW4'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w4, echo=F}

vbl <- ALSA_wb$ENJLFW4
vbl_miss <- -1
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(ENJLFW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `-1 into 998` 
* `NA into 999`

**R script:**

```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_wb$id)
ALSA_ds_w4$evaluative_wb <- car::recode(ALSA_wb$ENJLFW4, "1=2; 3=1; 4=0; 5=0; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ALSA_ds_w4$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w4, echo=F}

```



### Wave 5

Not found.


### Wave 6

#### Study-specific variable description

| **Name** | `SATLIFW6` |
|-|-|
| **Label** | `satisfied with live in general`|
| **Table name** | `ALSA-Wave6` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Missings** |`0 = no answer` |
| **Description** |  |  

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave6', variables=list('SATLIFW6'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w6, echo=F}

vbl <- ALSA_wb$SATLIFW6
vbl_miss <- 0
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(SATLIFW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_wb$id)
ALSA_ds_w6$evaluative_wb <- car::recode(ALSA_wb$SATLIFW6, "1=2; 3=1; 4=0; 5=0; 9=999; 0=999; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w6, echo=F}

```


### Wave 7

#### Study-specific variable description

| **Name** | `satlifw7` |
|-|-|
| **Label** | `satisfied with life in general`|
| **Table name** | `ALSA-Wave7` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Missings** |`0 = Not Answered`|
| **Description** |  |  

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave7', variables=list('satlifw7'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w7, echo=F}

vbl <- ALSA_wb$satlifw7
vbl_miss <- 0
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(satlifw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_wb$id)
ALSA_ds_w7$evaluative_wb <- car::recode(ALSA_wb$satlifw7, "1=2; 3=1; 4=0; 5=0; 9=999; 0=999; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w7, echo=F}

```

### Wave 8

Not found.

### Wave 9

#### Study-specific variable description

| **Name** | `SATLIFW9` |
|-|-|
| **Label** | `satisfied with life in general`|
| **Table name** | `ALSA-Wave9` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Missings** |`0 = Not Answered`|
| **Description** |  |  

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave9', variables=list('SATLIFW9'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w9, echo=F}

vbl <- ALSA_wb$SATLIFW9
vbl_miss <- 0
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(SATLIFW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_wb$id)
ALSA_ds_w9$evaluative_wb <- car::recode(ALSA_wb$SATLIFW9, "1=2; 3=1; 4=0; 5=0; 9=999; 0=999; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w9, echo=F}

```

### Wave 10

Not found



### Wave 11

#### Study-specific variable description

| **Name** | `SATLIFW11` |
|-|-|
| **Label** | `satisfied with life in general`|
| **Table name** | `ALSA-Wave11` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Description** |  |  

   
```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave11', variables=list('SATLIFW11'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w11, echo=F}

vbl <- ALSA_wb$SATLIFW11
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(SATLIFW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_wb$id)
ALSA_ds_w11$evaluative_wb <- car::recode(ALSA_wb$SATLIFW11, "1=2; 3=1; 4=0; 5=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w11, echo=F}

```

### Wave 12

#### Study-specific variable description

| **Name** | `SATLIFW12` |
|-|-|
| **Label** | `satisfied with life in general`|
| **Table name** | `ALSA-Wave12` | 
| **Categories** | `1 = Extremely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Satisfied` <br/> `4 = Somewhat dissatisfied` <br/> `5 = Very dissatisfied` | 
| **Description** |  |  

   
```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave12', variables=list('SATLIFW12'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb')
```

```{r local w12, echo=F}
vbl <- ALSA_wb$SATLIFW12
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(SATLIFW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_wb$id)
ALSA_ds_w12$evaluative_wb <- car::recode(ALSA_wb$SATLIFW12, "1=2; 3=1; 4=0; 5=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vbl <- ALSA_ds_w12$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w12, echo=F}

```

### Wave 13

Not found







## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, results='asis', echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()
lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)
if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
