---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```



# Data process

## Australia

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3 

#### Study-specific variable description

| **Name** | `GOALWSW3` |
|-|-|
| **Label** | `SET GOALS`|
| **Table name** | `ALSA-Wave3` | 
| **Categories** | `1 = Strongly disagree` <br/> `2 = Moderately disagree` <br/> `3 = Mildy disagree` <br/> `4 = Mildly agree` <br/> `5 = Moderately agree` <br/> `6 = Strongly  agree` | 
| **Missings** |`9`<br/>`NA` |
| **Description** |  |  

   

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave3', variables=list('GOALWSW3'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w3, echo=F}

vbl <- ALSA_wb$GOALWSW3
vbl_miss <- c(9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3,4 into 1`
* `5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo w3, tidy=FALSE}

ALSA_ds_w3 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(GOALWSW3, `1`=2, `2`=2, `3`=1,`4`=1,`5`=0, `6`=0, `9`=999)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ALSA_ds_w3$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}

```



### Wave 4


Not found


### Wave 5


#### Study-specific variable description

| **Name** | `LIFEGOW5` |
|-|-|
| **Label** | `Q8B I USED TO SET GOALS FOR MYSELF, BUT`|
| **Table name** | `ALSA-Wave5` | 
| **Categories** | `1 = Strongly disagree` <br/> `2 = Disagree` <br/> `3 = Agree` <br/> `4 = Strongly agree` | 
| **Missings** |`5 = Refused (Do not read)`<br/>`NA` |
| **Description** |  |  

   

```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave5', variables=list('LIFEGOW5'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w5, echo=F}

vbl <- ALSA_wb$LIFEGOW5
vbl_miss <- c(5)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0`
* `5 into 997` 
* `NA into 999`

**R script:**

```{r harmo w5, tidy=FALSE}

ALSA_ds_w5 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(LIFEGOW5, `1`=2, `3`=1,`2`=1,`4`=0, `5`=997)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ALSA_ds_w5$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w5, echo=F}

```


### Wave 6

#### Study-specific variable description

| **Name** | `CESD8W6` |
|-|-|
| **Label** | `I felt hopeful about the future`|
| **Table name** | `ALSA-Wave6` | 
| **Categories** | `1 = rarely or none of the time` <br/> `2 = some of the time` <br/> `3 = quite a bit of the time` <br/> `4 = most or all of the time` | 
| **Missings** |`0 = no answer`<br/>`NA` |
| **Description** |  |  

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave6', variables=list('CESD8W6'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w6, echo=F}

vbl <- ALSA_wb$CESD8W6
vbl_miss <- c(0)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4 into 2`
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w6, tidy=FALSE}

ALSA_ds_w6 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W6, `1`=0, `3`=1,`2`=1,`4`=2, `0`=995)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w6, echo=F}

```


### Wave 7

#### Study-specific variable description

| **Name** | `CESD8W7` |
|-|-|
| **Label** | `I felt hopeful about the future (reversed)`|
| **Table name** | `ALSA-Wave7` | 
| **Categories** | `0 = Most or all of the time` <br/> `1 = Quite a bit of the time` <br/> `2 = Some of the time` <br/> `3 = Rarely or none of the time` | 
| **Missings** |`NA`|
| **Description** |  |  

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave7', variables=list('CESD8W7'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w7, echo=F}

vbl <- ALSA_wb$CESD8W7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* `1,2 into 1`
* `3 into 0`
* `NA into 999`

**R script:**

```{r harmo w7, tidy=FALSE}

ALSA_ds_w7 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W7, `3`=0,`2`=1,`1`=1,`0`=2)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w7, echo=F}

```

### Wave 8


#### Study-specific variable description

| **Name** | `lifegow8` |
|-|-|
| **Label** | ` I used to set goals for myself, but now that seems like a waste of time.`|
| **Table name** | `ALSA-Wave8` | 
| **Categories** | `1 = Strongly disagree` <br/> `2 = Disagree` <br/> `3 = Agree` <br/> `4 = Strongly agree` | 
| **Missings** |`0 = Not Answered`<br/>`NA` |
| **Description** |  |  

   

```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave8', variables=list('lifegow8'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w8, echo=F}

vbl <- ALSA_wb$lifegow8
vbl_miss <- c(0)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0`
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w8, tidy=FALSE}

ALSA_ds_w8 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(lifegow8, `1`=2, `3`=1,`2`=1,`4`=0, `0`=995)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vbl <- ALSA_ds_w8$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w8, echo=F}

```


### Wave 9

#### Study-specific variable description

| **Name** | `CESD8W9` |
|-|-|
| **Label** | `I felt hopeful about the future`|
| **Table name** | `ALSA-Wave9` | 
| **Categories** | `1 = rarely or none of the time` <br/> `2 = some of the time` <br/> `3 = quite a bit of the time` <br/> `4 = most or all of the time` | 
| **Missings** |`0 = Not Answered`<br/>`NA` |
| **Description** |  |  

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave9', variables=list('CESD8W9'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w9, echo=F}

vbl <- ALSA_wb$CESD8W9
vbl_miss <- c(0)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4 into 2`
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w9, tidy=FALSE}

ALSA_ds_w9 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W9, `1`=0, `3`=1,`2`=1,`4`=2, `0`=995)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w9, echo=F}

```


### Wave 10


#### Study-specific variable description

| **Name** | `lifegow10` |
|-|-|
| **Label** | `I used to set goals for myself, but now that seems like a waste of time.`|
| **Table name** | `ALSA-Wave10` | 
| **Categories** | `1 = strongly agree` <br/> `2 = Agree` <br/> `3 = undecided` <br/> `4 = Disagree`<br/> `5 = Strongly disagree` | 
| **Missings** |`99 = Not Answered`<br/>`NA` |
| **Description** |  |  

   

```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave10', variables=list('lifegow10'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w10, echo=F}

vbl <- ALSA_wb$lifegow10
vbl_miss <- c(99)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(ALSA_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `99 into 995` 
* `NA into 999`

**R script:**

```{r harmo w10, tidy=FALSE}

ALSA_ds_w10 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(lifegow10, `1`=0, `3`=1,`2`=0,`4`=2,`5`=2, `99`=995)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vbl <- ALSA_ds_w10$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w10, echo=F}

```



### Wave 11

#### Study-specific variable description

| **Name** | `CESD8W11` |
|-|-|
| **Label** | `I felt hopeful about the future`|
| **Table name** | `ALSA-Wave11` | 
| **Categories** | `0 = Most or all of the time` <br/> `1 = quite a bit of the time` <br/> `2 = some of the time` <br/> `3 = rarely or none of the time` | 
| **Missings** |`NA` |
| **Description** |  |  

   
```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave11', variables=list('CESD8W11'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w11, echo=F}

vbl <- ALSA_wb$CESD8W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(CESD8W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 2`
* `1,2 into 1`
* `3 into 0`
* `NA into 999`

**R script:**

```{r harmo w11, tidy=FALSE}

ALSA_ds_w11 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W11,`2`=1,`1`=1,`3`=0,`0`=2)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w11, echo=F}

```


### Wave 12

#### Study-specific variable description

| **Name** | `CESD8W12` |
|-|-|
| **Label** | `I felt hopeful about the future`|
| **Table name** | `ALSA-Wave12` | 
| **Categories** | `1 = Rarely or none of the time` <br/> `2 = Some of the time` <br/> `3 = Quite a bit of the time` <br/> `4 = Most or all of the time` | 
| **Missings** |`NA` |
| **Description** |  |  

   
```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave12', variables=list('CESD8W12'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w12, echo=F}
vbl <- ALSA_wb$CESD8W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(CESD8W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 2`
* `2,3 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo w12, tidy=FALSE}

ALSA_ds_w12 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W12,`2`=1,`3`=1,`1`=0,`4`=2)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vbl <- ALSA_ds_w12$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w12, echo=F}

```

### Wave 13


#### Study-specific variable description

| **Name** | `CESD8W13` |
|-|-|
| **Label** | `I felt hopeful about the future`|
| **Table name** | `ALSA-Wave13` | 
| **Categories** | `1 = Rarely or none of the time` <br/> `2 = Some of the time` <br/> `3 = Quite a bit of the time` <br/> `4 = Most or all of the time` | 
| **Missings** |`NA` |
| **Description** |  |  

   
```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_wb','ALSA.ALSA-Wave13', variables=list('CESD8W13'), missings = TRUE)
ALSA_wb <- opal.execute(o,'ALSA_wb') %>% update_labelled()
```

```{r local w13, echo=F}
vbl <- ALSA_wb$CESD8W13
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_wb, aes(x=factor(CESD8W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 2`
* `2,3 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo w13, tidy=FALSE}

ALSA_ds_w13 <- ALSA_wb %>%
  mutate(eudaimonic_wb = dplyr::recode(CESD8W13,`2`=1,`3`=1,`1`=0,`4`=2)) %>%
  mutate(eudaimonic_wb = replace_na(eudaimonic_wb, 999)) %>%
  select(id, eudaimonic_wb)

```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vbl <- ALSA_ds_w13$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w13, echo=F}

```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
