---
title: "Sleep"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `sleep`
* Variable label: `Sleep`
* Variable description: `Sleeping problems.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Australia

### Wave 1

#### Study-specific variable description




| **Name** | `CESD11`|
|-|-|
| **Label** | `CES Depression Scale: Item 11` |
| **Table name** | `ALSA-Wave1` |
| **Categories** | `0 = Rarely or none of the time; 1 = Some of the time; 2 = Quite a bit of the time; 3 = Most or all of the time` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_sleep','ALSA.ALSA-Wave1', variables=list('CESD11'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_sleep <- opal.execute(o,'ALSA_w1_sleep')
vari <- ALSA_w1_sleep$CESD11
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "CESD11")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_sleep, aes(x=factor(CESD11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `3 into 0`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_sleep$id)
ALSA_ds_w1$sleep <- car::recode(ALSA_w1_sleep$CESD11, "0 = '1';1 = '0';2 = '0';3 = '0';9 = '999';NA = '999' ")
ALSA_ds_w1$sleep <- labelled(ALSA_ds_w1$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$sleep)
X<-table(ALSA_w1_sleep$CESD11)
BeforeH <- c(sum(X[2:4]),X[1],X[5]+sum(is.na(ALSA_w1_sleep$CESD11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","0->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w1
save(sleep, file = "../RData/w1/sleep.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$sleep <- car::recode(ALSA_m_ds_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.



### Wave 3

#### Study-specific variable description




| **Name** | `CESD11W3`|
|-|-|
| **Label** | `CES Depression Scale: Item 11` |
| **Table name** | `ALSA-Wave3` |
| **Categories** | `0 = Rarely or none of the time; 1 = Some of the time; 2 = Quite a bit of the time; 3 = Most or all of the time` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_sleep','ALSA.ALSA-Wave3', variables=list('CESD11W3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_sleep <- opal.execute(o,'ALSA_w3_sleep')
vari <- ALSA_w3_sleep$CESD11W3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "CESD11W3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_sleep, aes(x=factor(CESD11W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `3 into 0`
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_sleep$id)
ALSA_ds_w3$sleep <- car::recode(ALSA_w3_sleep$CESD11W3, "0 = '1';1 = '0';2 = '0';3 = '0';9 = '999';NA = '999' ")
ALSA_ds_w3$sleep <- labelled(ALSA_ds_w3$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$sleep)
X<-table(ALSA_w3_sleep$CESD11W3)
BeforeH <- c(sum(X[2:4]),X[1],X[5]+sum(is.na(ALSA_w3_sleep$CESD11W3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","0->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w3
save(sleep, file = "../RData/w3/sleep.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$sleep <- car::recode(ALSA_m_ds_w3$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

Not found.

### Wave 5

Not found.


### Wave 6

#### Study-specific variable description




| **Name** | `CESD11W6`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave6` |
| **Categories** | `1 = Rarely or none of the time; 2 = Some of the time; 3 = Quite a bit of the time; 4 = Most or all of the time` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_sleep','ALSA.ALSA-Wave6', variables=list('CESD11W6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_sleep <- opal.execute(o,'ALSA_w6_sleep')
vari <- ALSA_w6_sleep$CESD11W6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "CESD11W6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_sleep, aes(x=factor(CESD11W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_sleep$id)
ALSA_ds_w6$sleep <- car::recode(ALSA_w6_sleep$CESD11W6, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995';NA = '999' ")
ALSA_ds_w6$sleep <- labelled(ALSA_ds_w6$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$sleep)
X<-table(ALSA_w6_sleep$CESD11W6)
BeforeH <- c(sum(X[3:5]),X[2],X[1],sum(is.na(ALSA_w6_sleep$CESD11W6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w6
save(sleep, file = "../RData/w6/sleep.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$sleep <- car::recode(ALSA_m_ds_w6$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `CESD11W7`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave7` |
| **Categories** | `0 = Rarely or none of the time; 1 = Some of the time; 2 = Quite a bit of the time; 3 = Most or all of the time` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_sleep','ALSA.ALSA-Wave7', variables=list('CESD11W7'), missings = TRUE)
```

```{r local w7, echo=F}
ALSA_w7_sleep <- opal.execute(o,'ALSA_w7_sleep')
vari <- ALSA_w7_sleep$CESD11W7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "CESD11W7")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7_sleep, aes(x=factor(CESD11W7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_sleep$id)
ALSA_ds_w7$sleep <- car::recode(ALSA_w7_sleep$CESD11W7, "0 = '1';1 = '0';2 = '0';3 = '0';NA = '999' ")
ALSA_ds_w7$sleep <- labelled(ALSA_ds_w7$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ALSA_ds_w7$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$sleep)
X<-table(ALSA_w7_sleep$CESD11W7)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w7_sleep$CESD11W7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w7
save(sleep, file = "../RData/w7/sleep.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$sleep <- car::recode(ALSA_m_ds_w7$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

Not found.



### Wave 9

#### Study-specific variable description




| **Name** | `CESD11W9`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave9` |
| **Categories** | `4 = Rarely or none of the time; 3 = Some of the time; 2 = Quite a bit of the time; 1 = Most or all of the time` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_sleep','ALSA.ALSA-Wave9', variables=list('CESD11W9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_sleep <- opal.execute(o,'ALSA_w9_sleep')
vari <- ALSA_w9_sleep$CESD11W9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "CESD11W9")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_sleep, aes(x=factor(CESD11W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0`
* `3 into 0`
* `4 into 1`
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_sleep$id)
ALSA_ds_w9$sleep <- car::recode(ALSA_w9_sleep$CESD11W9, "1 = '0';2 = '0';3 = '0';4 = '1';NA = '999' ")
ALSA_ds_w9$sleep <- labelled(ALSA_ds_w9$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$sleep)
X<-table(ALSA_w9_sleep$CESD11W9)
BeforeH <- c(sum(X[1:3]),X[4],sum(is.na(ALSA_w9_sleep$CESD11W9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4->1","NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w9
save(sleep, file = "../RData/w9/sleep.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$sleep <- car::recode(ALSA_m_ds_w9$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

Not found.



### Wave 11

#### Study-specific variable description




| **Name** | `CESD11W11`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave11` |
| **Categories** | `0 = Rarely or none of the time; 1 = Some of the time; 2 = Quite a bit of the time; 3 = Most or all of the time` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_sleep','ALSA.ALSA-Wave11', variables=list('CESD11W11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_sleep <- opal.execute(o,'ALSA_w11_sleep')
vari <- ALSA_w11_sleep$CESD11W11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "CESD11W11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_sleep, aes(x=factor(CESD11W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `3 into 0`
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_sleep$id)
ALSA_ds_w11$sleep <- car::recode(ALSA_w11_sleep$CESD11W11, "0 = '1';1 = '0';2 = '0';3 = '0';NA = '999' ")
ALSA_ds_w11$sleep <- labelled(ALSA_ds_w11$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$sleep)
X<-table(ALSA_w11_sleep$CESD11W11)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w11_sleep$CESD11W11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w11
save(sleep, file = "../RData/w11/sleep.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$sleep <- car::recode(ALSA_m_ds_w11$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description




| **Name** | `CESD11W12`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave` |
| **Categories** | `1 = Rarely or none of the time; 2 = Some of the time; 3 = Quite a bit of the time; 4 = Most or all of the time` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_sleep','ALSA.ALSA-Wave12', variables=list('CESD11W12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_sleep <- opal.execute(o,'ALSA_w12_sleep')
vari <- ALSA_w12_sleep$CESD11W12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "CESD11W12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_sleep, aes(x=factor(CESD11W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_sleep$id)
ALSA_ds_w12$sleep <- car::recode(ALSA_w12_sleep$CESD11W12, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w12$sleep <- labelled(ALSA_ds_w12$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$sleep)
X<-table(ALSA_w12_sleep$CESD11W12)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w12_sleep$CESD11W12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w12
save(sleep, file = "../RData/w12/sleep.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$sleep <- car::recode(ALSA_m_ds_w12$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description




| **Name** | `CESD11W13`|
|-|-|
| **Label** | `My sleep was restless` |
| **Table name** | `ALSA-Wave` |
| **Categories** | `1 = Rarely or none of the time; 2 = Some of the time; 3 = Quite a bit of the time; 4 = Most or all of the time` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_sleep','ALSA.ALSA-Wave13', variables=list('CESD11W13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_sleep <- opal.execute(o,'ALSA_w13_sleep')
vari <- ALSA_w13_sleep$CESD11W13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "CESD11W13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_sleep, aes(x=factor(CESD11W13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_sleep$id)
ALSA_ds_w13$sleep <- car::recode(ALSA_w13_sleep$CESD11W13, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
ALSA_ds_w13$sleep <- labelled(ALSA_ds_w13$sleep, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$sleep)
X<-table(ALSA_w13_sleep$CESD11W13)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w13_sleep$CESD11W13)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
sleep <- ALSA_ds_w13
save(sleep, file = "../RData/w13/sleep.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$sleep <- car::recode(ALSA_m_ds_w13$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
This question is an item of a depression scale.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
