---
title: "Incontinence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `incontinence`
* Variable label: `Incontinence`
* Variable description: `It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Australia

### Wave 1 

#### Study-specific variable description




| **Name** | `ACCDUR`|
|-|-|
| **Label** | `Do you accidentally pass urine?` |
| **Table name** | `ALSA-Wave1` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_incontinence','ALSA.ALSA-Wave1', variables=list('ACCDUR'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_incontinence <- opal.execute(o,'ALSA_w1_incontinence')
vari <- ALSA_w1_incontinence$ACCDUR
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "ACCDUR")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_incontinence, aes(x=factor(ACCDUR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `9 into 999` 
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_incontinence$id)
ALSA_ds_w1$incontinence <- car::recode(ALSA_w1_incontinence$ACCDUR, "1 = '0';2 = '0';3 = '1';9 = '999'; NA = '999' ")
ALSA_ds_w1$incontinence <- labelled(ALSA_ds_w1$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$incontinence)
X<-table(ALSA_w1_incontinence$ACCDUR)
BeforeH <- c(sum(X[c(1,2)]),X[3],X[4]+sum(is.na(ALSA_w1_incontinence$ACCDUR)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w1
save(incontinence, file = "../RData/w1/incontinence.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$incontinence <- car::recode(ALSA_m_ds_w1$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `Q17`|
|-|-|
| **Label** | `Do you accidentally pass urine?` |
| **Table name** | `ALSA-Wave2` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2_incontinence','ALSA.ALSA-Wave2', variables=list('Q17'), missings = TRUE)
```

```{r local w2, echo=F}
ALSA_w2_incontinence <- opal.execute(o,'ALSA_w2_incontinence')
vari <- ALSA_w2_incontinence$Q17
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Q17")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w2_incontinence, aes(x=factor(Q17))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `NA into 999`

**R script:**
```{r harmo w2}
ALSA_ds_w2 <- tibble(id=ALSA_w2_incontinence$id)
ALSA_ds_w2$incontinence <- car::recode(ALSA_w2_incontinence$Q17, "1 = '0';2 = '0';3 = '1'; NA = '999' ")
ALSA_ds_w2$incontinence <- labelled(ALSA_ds_w2$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ALSA_ds_w2$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ALSA_ds_w2$incontinence)
X<-table(ALSA_w2_incontinence$Q17)
BeforeH <- c(sum(X[c(1,2)]),X[3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(ALSA_ds_w2$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w2', ALSA_ds_w2)
#opal.symbol_import(o,'ALSA_ds_w2', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w2
save(incontinence, file = "../RData/w2/incontinence.RData")

ALSA_m_ds_w2 <- ALSA_ds_w2
ALSA_m_ds_w2$incontinence <- car::recode(ALSA_m_ds_w2$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w2', ALSA_m_ds_w2)
#opal.symbol_import(o,'ALSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `ACCDURW3`|
|-|-|
| **Label** | `Do you accidentally pass urine?` |
| **Table name** | `ALSA-Wave3` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_incontinence','ALSA.ALSA-Wave3', variables=list('ACCDURW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_incontinence <- opal.execute(o,'ALSA_w3_incontinence')
vari <- ALSA_w3_incontinence$ACCDURW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "ACCDURW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_incontinence, aes(x=factor(ACCDURW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `9 into 999` 
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_incontinence$id)
ALSA_ds_w3$incontinence <- car::recode(ALSA_w3_incontinence$ACCDURW3, "1 = '0';2 = '0';3 = '1';9 = '999'; NA = '999' ")
ALSA_ds_w3$incontinence <- labelled(ALSA_ds_w3$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$incontinence)
X<-table(ALSA_w3_incontinence$ACCDURW3)
BeforeH <- c(sum(X[c(1,2)]),X[3],X[4]+sum(is.na(ALSA_w3_incontinence$ACCDURW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w3
save(incontinence, file = "../RData/w3/incontinence.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$incontinence <- car::recode(ALSA_m_ds_w3$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description




| **Name** | `ACCDURW4`|
|-|-|
| **Label** | `Do you accidentally pass urine?` |
| **Table name** | `ALSA-Wave4` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `4 = Don't know; NA` |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4_incontinence','ALSA.ALSA-Wave4', variables=list('ACCDURW4'), missings = TRUE)
```

```{r local w4, echo=F}
ALSA_w4_incontinence <- opal.execute(o,'ALSA_w4_incontinence')
vari <- ALSA_w4_incontinence$ACCDURW4
kable(Categorical_summary(vari, missing_values = c(4))[3], caption = "ACCDURW4")
kable(Categorical_summary(vari, missing_values = c(4))[1], caption = "Category")
ggplot(ALSA_w4_incontinence, aes(x=factor(ACCDURW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `4 into 998` 
* `NA into 999`

**R script:**
```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_incontinence$id)
ALSA_ds_w4$incontinence <- car::recode(ALSA_w4_incontinence$ACCDURW4, "1 = '0';2 = '0';3 = '1';4 = '998'; NA = '999' ")
ALSA_ds_w4$incontinence <- labelled(ALSA_ds_w4$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ALSA_ds_w4$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ALSA_ds_w4$incontinence)
X<-table(ALSA_w4_incontinence$ACCDURW4)
BeforeH <- c(sum(X[c(1,2)]),X[3],X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","4->998") 
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(ALSA_ds_w4$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w4
save(incontinence, file = "../RData/w4/incontinence.RData")

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$incontinence <- car::recode(ALSA_m_ds_w4$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description




| **Name** | `ACCDURW5`|
|-|-|
| **Label** | `Do you accidentally pass urine?` |
| **Table name** | `ALSA-Wave5` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `4 = Refused; NA` |
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5_incontinence','ALSA.ALSA-Wave5', variables=list('ACCDURW5'), missings = TRUE)
```

```{r local w5, echo=F}
ALSA_w5_incontinence <- opal.execute(o,'ALSA_w5_incontinence')
vari <- ALSA_w5_incontinence$ACCDURW5
kable(Categorical_summary(vari, missing_values = c(4))[3], caption = "ACCDURW5")
kable(Categorical_summary(vari, missing_values = c(4))[1], caption = "Category")
ggplot(ALSA_w5_incontinence, aes(x=factor(ACCDURW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `4 into 997` 
* `NA into 999`

**R script:**
```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_incontinence$id)
ALSA_ds_w5$incontinence <- car::recode(ALSA_w5_incontinence$ACCDURW5, "1 = '0';2 = '0';3 = '1';4 = '997'; NA = '999' ")
ALSA_ds_w5$incontinence <- labelled(ALSA_ds_w5$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ALSA_ds_w5$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ALSA_ds_w5$incontinence)
X<-table(ALSA_w5_incontinence$ACCDURW5)
BeforeH <- c(sum(X[c(1,2)]),X[3],X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","4->997") 
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(ALSA_ds_w5$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w5
save(incontinence, file = "../RData/w5/incontinence.RData")

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$incontinence <- car::recode(ALSA_m_ds_w5$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6

#### Study-specific variable description




| **Name** | `ACCDURW6`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave6` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_incontinence','ALSA.ALSA-Wave6', variables=list('ACCDURW6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_incontinence <- opal.execute(o,'ALSA_w6_incontinence')
vari <- ALSA_w6_incontinence$ACCDURW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "ACCDURW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_incontinence, aes(x=factor(ACCDURW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_incontinence$id)
ALSA_ds_w6$incontinence <- car::recode(ALSA_w6_incontinence$ACCDURW6, "1 = '0';2 = '0';3 = '1';0 = '995'; NA = '999' ")
ALSA_ds_w6$incontinence <- labelled(ALSA_ds_w6$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$incontinence)
X<-table(ALSA_w6_incontinence$ACCDURW6)
BeforeH <- c(sum(X[c(2,3)]),X[4],X[1],sum(is.na(ALSA_w6_incontinence$ACCDURW6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w6
save(incontinence, file = "../RData/w6/incontinence.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$incontinence <- car::recode(ALSA_m_ds_w6$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `accdurw7`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave7` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_incontinence','ALSA.ALSA-Wave7', variables=list('accdurw7'), missings = TRUE)
```

```{r local w7, echo=F}
ALSA_w7_incontinence <- opal.execute(o,'ALSA_w7_incontinence')
vari <- ALSA_w7_incontinence$accdurw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "accdurw7")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7_incontinence, aes(x=factor(accdurw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_incontinence$id)
ALSA_ds_w7$incontinence <- car::recode(ALSA_w7_incontinence$accdurw7, "1 = '0';2 = '0';3 = '1';0 = '995'; NA = '999' ")
ALSA_ds_w7$incontinence <- labelled(ALSA_ds_w7$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ALSA_ds_w7$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$incontinence)
X<-table(ALSA_w7_incontinence$accdurw7)
BeforeH <- c(sum(X[c(2,3)]),X[4],X[1],sum(is.na(ALSA_w7_incontinence$accdurw7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w7
save(incontinence, file = "../RData/w7/incontinence.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$incontinence <- car::recode(ALSA_m_ds_w7$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

#### Study-specific variable description




| **Name** | `accdurw8`|
|-|-|
| **Label** | `Do you accidentally pass urine` |
| **Table name** | `ALSA-Wave8` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_incontinence','ALSA.ALSA-Wave8', variables=list('accdurw8'), missings = TRUE)
```

```{r local w8, echo=F}
ALSA_w8_incontinence <- opal.execute(o,'ALSA_w8_incontinence')
vari <- ALSA_w8_incontinence$accdurw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "accdurw8")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w8_incontinence, aes(x=factor(accdurw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_incontinence$id)
ALSA_ds_w8$incontinence <- car::recode(ALSA_w8_incontinence$accdurw8, "1 = '0';2 = '0';3 = '1';0 = '995'; NA = '999' ")
ALSA_ds_w8$incontinence <- labelled(ALSA_ds_w8$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vari <- ALSA_ds_w8$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$incontinence)
X<-table(ALSA_w8_incontinence$accdurw8)
BeforeH <- c(sum(X[c(2,3)]),X[4],X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","0->995") 
kable(C)
```






```{r importOPAL w8, echo=FALSE}

label(ALSA_ds_w8$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w8
save(incontinence, file = "../RData/w8/incontinence.RData")

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$incontinence <- car::recode(ALSA_m_ds_w8$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9

#### Study-specific variable description




| **Name** | `ACCDURW9`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave9` |
| **Categories** | `1 = Often; 2 = Occasionally; 3 = Never` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_incontinence','ALSA.ALSA-Wave9', variables=list('ACCDURW9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_incontinence <- opal.execute(o,'ALSA_w9_incontinence')
vari <- ALSA_w9_incontinence$ACCDURW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "ACCDURW9")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9_incontinence, aes(x=factor(ACCDURW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 1`
* `0 into 995` 
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_incontinence$id)
ALSA_ds_w9$incontinence <- car::recode(ALSA_w9_incontinence$ACCDURW9, "1 = '0';2 = '0';3 = '1';0 = '995'; NA = '999' ")
ALSA_ds_w9$incontinence <- labelled(ALSA_ds_w9$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$incontinence)
X<-table(ALSA_w9_incontinence$ACCDURW9)
BeforeH <- c(sum(X[c(2,3)]),X[4],X[1],sum(is.na(ALSA_w9_incontinence$ACCDURW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w9
save(incontinence, file = "../RData/w9/incontinence.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$incontinence <- car::recode(ALSA_m_ds_w9$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description




| **Name** | `accdurw10`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave10` |
| **Categories** | `2 = Often; 1 = Occasionally; 0 = Never` |
| **Missings** | `99 = Not answered; NA` |
| **Description** |  |


```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_incontinence','ALSA.ALSA-Wave10', variables=list('accdurw10'), missings = TRUE)
```

```{r local w10, echo=F}
ALSA_w10_incontinence <- opal.execute(o,'ALSA_w10_incontinence')
vari <- ALSA_w10_incontinence$accdurw10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "accdurw10")
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
ggplot(ALSA_w10_incontinence, aes(x=factor(accdurw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `0 into 1`
* `99 into 995` 
* `NA into 999`

**R script:**
```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_incontinence$id)
ALSA_ds_w10$incontinence <- car::recode(ALSA_w10_incontinence$accdurw10, "1 = '0';2 = '0';0 = '1';99 = '995'; NA = '999' ")
ALSA_ds_w10$incontinence <- labelled(ALSA_ds_w10$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vari <- ALSA_ds_w10$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=F}
AfterH <- table(ALSA_ds_w10$incontinence)
X<-table(ALSA_w10_incontinence$accdurw10)
BeforeH <- c(sum(X[c(2,3)]),X[1],X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","99->995") 
kable(C)
```






```{r importOPAL w10, echo=FALSE}

label(ALSA_ds_w10$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w10
save(incontinence, file = "../RData/w10/incontinence.RData")

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$incontinence <- car::recode(ALSA_m_ds_w10$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description




| **Name** | `ACCDURW11`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave11` |
| **Categories** | `1 = Often; 2 = Occasionally; 0 = Never` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_incontinence','ALSA.ALSA-Wave11', variables=list('ACCDURW11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_incontinence <- opal.execute(o,'ALSA_w11_incontinence')
vari <- ALSA_w11_incontinence$ACCDURW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ACCDURW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_incontinence, aes(x=factor(ACCDURW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_incontinence$id)
ALSA_ds_w11$incontinence <- car::recode(ALSA_w11_incontinence$ACCDURW11, "1 = '0';2 = '0'; 0 = '1'; NA = '999' ")
ALSA_ds_w11$incontinence <- labelled(ALSA_ds_w11$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$incontinence)
X<-table(ALSA_w11_incontinence$ACCDURW11)
BeforeH <- c(sum(X[c(2,3)]),X[1],sum(is.na(ALSA_w11_incontinence$ACCDURW11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w11
save(incontinence, file = "../RData/w11/incontinence.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$incontinence <- car::recode(ALSA_m_ds_w11$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description




| **Name** | `ACCDURW12`|
|-|-|
| **Label** | `accidentally pass urine` |
| **Table name** | `ALSA-Wave12` |
| **Categories** | `1 = Often; 2 = Occasionally; 0 = Never` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_incontinence','ALSA.ALSA-Wave12', variables=list('ACCDURW12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_incontinence <- opal.execute(o,'ALSA_w12_incontinence')
vari <- ALSA_w12_incontinence$ACCDURW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ACCDURW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_incontinence, aes(x=factor(ACCDURW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `0 into 1`
* `NA into 999`

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_incontinence$id)
ALSA_ds_w12$incontinence <- car::recode(ALSA_w12_incontinence$ACCDURW12, "1 = '0';2 = '0'; 0 = '1'; NA = '999' ")
ALSA_ds_w12$incontinence <- labelled(ALSA_ds_w12$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$incontinence)
X<-table(ALSA_w12_incontinence$ACCDURW12)
BeforeH <- c(sum(X[c(2,3)]),X[1],sum(is.na(ALSA_w12_incontinence$ACCDURW12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","NA->999") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w12
save(incontinence, file = "../RData/w12/incontinence.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$incontinence <- car::recode(ALSA_m_ds_w12$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description




| **Name** | `ACCDURW13`|
|-|-|
| **Label** | `Do you accidentally pass urine` |
| **Table name** | `ALSA-Wave13` |
| **Categories** | `2 = Often; 1 = Occasionally; 0 = Never` |
| **Missings** | `3 = Not applicable; NA` |
| **Description** |  |


```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_incontinence','ALSA.ALSA-Wave13', variables=list('ACCDURW13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_incontinence <- opal.execute(o,'ALSA_w13_incontinence')
vari <- ALSA_w13_incontinence$ACCDURW13
kable(Categorical_summary(vari, missing_values = c(3,99))[3], caption = "ACCDURW13")
kable(Categorical_summary(vari, missing_values = c(3,99))[1], caption = "Category")
ggplot(ALSA_w13_incontinence, aes(x=factor(ACCDURW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Incontinence") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `0 into 1`
* `3 into 996`
* `NA into 999`

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_incontinence$id)
ALSA_ds_w13$incontinence <- car::recode(ALSA_w13_incontinence$ACCDURW13, "1 = '0';2 = '0'; 0 = '1'; 3 = '996'; NA = '999' ")
ALSA_ds_w13$incontinence <- labelled(ALSA_ds_w13$incontinence, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$incontinence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "incontinence")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(incontinence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("incontinence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$incontinence)
X<-table(ALSA_w13_incontinence$ACCDURW13)
BeforeH <- c(sum(X[c(2,3)]),X[c(1,4)],sum(is.na(ALSA_w13_incontinence$ACCDURW13)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","3->1","3->996","NA->999") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$incontinence) <- "It measures if the participant has experienced loss of urine (or has used any special device for urine leakage) or not"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
incontinence <- ALSA_ds_w13
save(incontinence, file = "../RData/w13/incontinence.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$incontinence <- car::recode(ALSA_m_ds_w13$incontinence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
