---
title: "Hearing general"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Australia

### Wave 1

#### Study-specific variable description




| **Name** | `HEARING`|
|-|-|
| **Label** | `Hearing Difficulty` |
| **Table name** | `ALSA-Wave1` |
| **Categories** |`1 = Yes; 2 = No` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_hearing_gen','ALSA.ALSA-Wave1', variables=list('HEARING'), missings = TRUE)
```

```{r local w1, echo=F}
ALSA_w1_hearing_gen <- opal.execute(o,'ALSA_w1_hearing_gen')
vari <- ALSA_w1_hearing_gen$HEARING
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "HEARING")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_hearing_gen, aes(x=factor(HEARING))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_hearing_gen$id)
ALSA_ds_w1$hearing_gen <- car::recode(ALSA_w1_hearing_gen$HEARING, "1 = '0';2 = '1'; 9 = '999'; NA = '999' ")
ALSA_ds_w1$hearing_gen <- labelled(ALSA_ds_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ALSA_ds_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$hearing_gen)
X<-table(ALSA_w1_hearing_gen$HEARING)
BeforeH <- c(X[1:2],X[3]+sum(is.na(ALSA_w1_hearing_gen$HEARING)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","9,NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(ALSA_ds_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w1
save(hearing_gen, file = "../RData/w1/hearing_gen.RData")

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$hearing_gen <- car::recode(ALSA_m_ds_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.



### Wave 3

#### Study-specific variable description




| **Name** | `DIFFQUW3`|
|-|-|
| **Label** | `Difficulty hearing in quite room` |
| **Table name** | `ALSA-Wave3` |
| **Categories** |`1 = Not at all difficult; 2 = Slightly difficult; 3 = Moderately difficult; 4 = Very difficult; 5 = Can't hear at all` |
| **Missings** | `9 = Missing; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_hearing_gen','ALSA.ALSA-Wave3', variables=list('DIFFQUW3'), missings = TRUE)
```

```{r local w3, echo=F}
ALSA_w3_hearing_gen <- opal.execute(o,'ALSA_w3_hearing_gen')
vari <- ALSA_w3_hearing_gen$DIFFQUW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "DIFFQUW3")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3_hearing_gen, aes(x=factor(DIFFQUW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `9 into 999`
* `NA into 999`

**R script:**
```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_hearing_gen$id)
ALSA_ds_w3$hearing_gen <- car::recode(ALSA_w3_hearing_gen$DIFFQUW3, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; 9 = '999'; NA = '999' ")
ALSA_ds_w3$hearing_gen <- labelled(ALSA_ds_w3$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ALSA_ds_w3$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$hearing_gen)
X<-table(ALSA_w3_hearing_gen$DIFFQUW3)
BeforeH <- c(sum(X[2:5]),X[1],X[6]+sum(is.na(ALSA_w3_hearing_gen$DIFFQUW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9,NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ALSA_ds_w3$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w3
save(hearing_gen, file = "../RData/w3/hearing_gen.RData")

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$hearing_gen <- car::recode(ALSA_m_ds_w3$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description




| **Name** | `DIFFHRW4`|
|-|-|
| **Label** | `How much difficulty hearing?` |
| **Table name** | `ALSA-Wave4` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty; 5 = Can't hear at all` |
| **Missings** | `-1 = Don't know; NA` |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4_hearing_gen','ALSA.ALSA-Wave4', variables=list('DIFFHRW4'), missings = TRUE)
```

```{r local w4, echo=F}
ALSA_w4_hearing_gen <- opal.execute(o,'ALSA_w4_hearing_gen')
vari <- ALSA_w4_hearing_gen$DIFFHRW4
kable(Categorical_summary(vari, missing_values = c(-1))[3], caption = "DIFFHRW4")
kable(Categorical_summary(vari, missing_values = c(-1))[1], caption = "Category")
ggplot(ALSA_w4_hearing_gen, aes(x=factor(DIFFHRW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0` 
* `-1 into 998`
* `NA into 999`

**R script:**
```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4_hearing_gen$id)
ALSA_ds_w4$hearing_gen <- car::recode(ALSA_w4_hearing_gen$DIFFHRW4, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; -1 = '998'; NA = '999' ")
ALSA_ds_w4$hearing_gen <- labelled(ALSA_ds_w4$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ALSA_ds_w4$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ALSA_ds_w4$hearing_gen)
X<-table(ALSA_w4_hearing_gen$DIFFHRW4)
BeforeH <- c(sum(X[3:6]),X[2],X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","-1->998") 
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(ALSA_ds_w4$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w4', ALSA_ds_w4)
#opal.symbol_import(o,'ALSA_ds_w4', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w4
save(hearing_gen, file = "../RData/w4/hearing_gen.RData")

ALSA_m_ds_w4 <- ALSA_ds_w4
ALSA_m_ds_w4$hearing_gen <- car::recode(ALSA_m_ds_w4$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w4', ALSA_m_ds_w4)
#opal.symbol_import(o,'ALSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description




| **Name** | `DIFFHRW5`|
|-|-|
| **Label** | `How much difficulty, if any, do you have with your hearing (even if you are wearing your hearing aid)?` |
| **Table name** | `ALSA-Wave5` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty` |
| **Missings** | `5 = Refused (Do no read); NA` |
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5_hearing_gen','ALSA.ALSA-Wave5', variables=list('DIFFHRW5'), missings = TRUE)
```

```{r local w5, echo=F}
ALSA_w5_hearing_gen <- opal.execute(o,'ALSA_w5_hearing_gen')
vari <- ALSA_w5_hearing_gen$DIFFHRW5
kable(Categorical_summary(vari, missing_values = c(5))[3], caption = "DIFFHRW5")
kable(Categorical_summary(vari, missing_values = c(5))[1], caption = "Category")
ggplot(ALSA_w5_hearing_gen, aes(x=factor(DIFFHRW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 997` 
* `NA into 999`

**R script:**
```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5_hearing_gen$id)
ALSA_ds_w5$hearing_gen <- car::recode(ALSA_w5_hearing_gen$DIFFHRW5, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '997'; NA = '999' ")
ALSA_ds_w5$hearing_gen <- labelled(ALSA_ds_w5$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ALSA_ds_w5$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ALSA_ds_w5$hearing_gen)
X<-table(ALSA_w5_hearing_gen$DIFFHRW5)
BeforeH <- c(sum(X[2:4]),X[1],X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","5->997") 
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(ALSA_ds_w5$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w5', ALSA_ds_w5)
#opal.symbol_import(o,'ALSA_ds_w5', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w5
save(hearing_gen, file = "../RData/w5/hearing_gen.RData")

ALSA_m_ds_w5 <- ALSA_ds_w5
ALSA_m_ds_w5$hearing_gen <- car::recode(ALSA_m_ds_w5$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w5', ALSA_m_ds_w5)
#opal.symbol_import(o,'ALSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6

#### Study-specific variable description




| **Name** | `DIFFQUW6`|
|-|-|
| **Label** | `difficulty hearing talk in quiet room` |
| **Table name** | `ALSA-Wave6` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty; 5 = Can't hear at all` |
| **Missings** | `0 = No answer; NA` |
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_hearing_gen','ALSA.ALSA-Wave6', variables=list('DIFFQUW6'), missings = TRUE)
```

```{r local w6, echo=F}
ALSA_w6_hearing_gen <- opal.execute(o,'ALSA_w6_hearing_gen')
vari <- ALSA_w6_hearing_gen$DIFFQUW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "DIFFQUW6")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6_hearing_gen, aes(x=factor(DIFFQUW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`
* `0 into 995`
* `NA into 999`

**R script:**
```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_hearing_gen$id)
ALSA_ds_w6$hearing_gen <- car::recode(ALSA_w6_hearing_gen$DIFFQUW6, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';0 = '995'; NA = '999' ")
ALSA_ds_w6$hearing_gen <- labelled(ALSA_ds_w6$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ALSA_ds_w6$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$hearing_gen)
X<-table(ALSA_w6_hearing_gen$DIFFQUW6)
BeforeH <- c(sum(X[3:5]),X[2],X[1],sum(is.na(ALSA_w6_hearing_gen$DIFFQUW6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w6, echo=FALSE}

label(ALSA_ds_w6$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w6
save(hearing_gen, file = "../RData/w6/hearing_gen.RData")

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$hearing_gen <- car::recode(ALSA_m_ds_w6$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `hearw7`|
|-|-|
| **Label** | `Difficulty with hearing` |
| **Table name** | `ALSA-Wave7` |
| **Categories** |`1 = Yes; 2 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_hearing_gen','ALSA.ALSA-Wave7', variables=list('hearw7'), missings = TRUE)
```

```{r local w7, echo=F}
ALSA_w7_hearing_gen <- opal.execute(o,'ALSA_w7_hearing_gen')
vari <- ALSA_w7_hearing_gen$hearw7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "hearw7")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7_hearing_gen, aes(x=factor(hearw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `NA into 999`

**R script:**
```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7_hearing_gen$id)
ALSA_ds_w7$hearing_gen <- car::recode(ALSA_w7_hearing_gen$hearw7, "1 = '0';2 = '1'; NA = '999' ")
ALSA_ds_w7$hearing_gen <- labelled(ALSA_ds_w7$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ALSA_ds_w7$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$hearing_gen)
X<-table(ALSA_w7_hearing_gen$hearw7)
BeforeH <- c(X[1:2],sum(is.na(ALSA_w7_hearing_gen$hearw7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```






```{r importOPAL w7, echo=FALSE}

label(ALSA_ds_w7$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w7
save(hearing_gen, file = "../RData/w7/hearing_gen.RData")

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$hearing_gen <- car::recode(ALSA_m_ds_w7$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```



### Wave 8

#### Study-specific variable description




| **Name** | `diffhrw8`|
|-|-|
| **Label** | `How much difficulty hearing?` |
| **Table name** | `ALSA-Wave8` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty` |
| **Missings** | `0 = Not Answered; NA` |
| **Description** |  |


```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_hearing_gen','ALSA.ALSA-Wave8', variables=list('diffhrw8'), missings = TRUE)
```

```{r local w8, echo=F}
ALSA_w8_hearing_gen <- opal.execute(o,'ALSA_w8_hearing_gen')
vari <- ALSA_w8_hearing_gen$diffhrw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = "diffhrw8")
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w8_hearing_gen, aes(x=factor(diffhrw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `0 into 995`
* `NA into 999`

**R script:**
```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8_hearing_gen$id)
ALSA_ds_w8$hearing_gen <- car::recode(ALSA_w8_hearing_gen$diffhrw8, "1 = '1';2 = '0';3 = '0';4 = '0';0 = '995'; NA = '999' ")
ALSA_ds_w8$hearing_gen <- labelled(ALSA_ds_w8$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vari <- ALSA_ds_w8$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$hearing_gen)
X<-table(ALSA_w8_hearing_gen$diffhrw8)
BeforeH <- c(sum(X[3:5]),X[2:1],sum(is.na(ALSA_w8_hearing_gen$diffhrw8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","0->995","NA->999") 
kable(C)
```






```{r importOPAL w8, echo=FALSE}

label(ALSA_ds_w8$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w8', ALSA_ds_w8)
#opal.symbol_import(o,'ALSA_ds_w8', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w8
save(hearing_gen, file = "../RData/w8/hearing_gen.RData")

ALSA_m_ds_w8 <- ALSA_ds_w8
ALSA_m_ds_w8$hearing_gen <- car::recode(ALSA_m_ds_w8$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w8', ALSA_m_ds_w8)
#opal.symbol_import(o,'ALSA_m_ds_w8', project='_Athlos_Harm_Dataset')
```



### Wave 9

#### Study-specific variable description




| **Name** | `HEARW9`|
|-|-|
| **Label** | `Hearing Difficulty` |
| **Table name** | `ALSA-Wave9` |
| **Categories** |`1 = Yes; 2 = No` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_hearing_gen','ALSA.ALSA-Wave9', variables=list('HEARW9'), missings = TRUE)
```

```{r local w9, echo=F}
ALSA_w9_hearing_gen <- opal.execute(o,'ALSA_w9_hearing_gen')
vari <- ALSA_w9_hearing_gen$HEARW9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "HEARW9")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_hearing_gen, aes(x=factor(HEARW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `NA into 999`

**R script:**
```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_hearing_gen$id)
ALSA_ds_w9$hearing_gen <- car::recode(ALSA_w9_hearing_gen$HEARW9, "1 = '0';2 = '1'; NA = '999' ")
ALSA_ds_w9$hearing_gen <- labelled(ALSA_ds_w9$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vari <- ALSA_ds_w9$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$hearing_gen)
X<-table(ALSA_w9_hearing_gen$HEARW9)
BeforeH <- c(X[1:2],sum(is.na(ALSA_w9_hearing_gen$HEARW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```






```{r importOPAL w9, echo=FALSE}

label(ALSA_ds_w9$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w9
save(hearing_gen, file = "../RData/w9/hearing_gen.RData")

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$hearing_gen <- car::recode(ALSA_m_ds_w9$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```



### Wave 10

#### Study-specific variable description




| **Name** | `diffhrw10`|
|-|-|
| **Label** | `How much difficulty hearing?` |
| **Table name** | `ALSA-Wave10` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty` |
| **Description** |  |


```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_hearing_gen','ALSA.ALSA-Wave10', variables=list('diffhrw10'), missings = TRUE)
```

```{r local w10, echo=F}
ALSA_w10_hearing_gen <- opal.execute(o,'ALSA_w10_hearing_gen')
vari <- ALSA_w10_hearing_gen$diffhrw10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "diffhrw10")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10_hearing_gen, aes(x=factor(diffhrw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`

**R script:**
```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10_hearing_gen$id)
ALSA_ds_w10$hearing_gen <- car::recode(ALSA_w10_hearing_gen$diffhrw10, "1 = '1';2 = '0';3 = '0';4 = '0' ")
ALSA_ds_w10$hearing_gen <- labelled(ALSA_ds_w10$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vari <- ALSA_ds_w10$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=F}
AfterH <- table(ALSA_ds_w10$hearing_gen)
X<-table(ALSA_w10_hearing_gen$diffhrw10)
BeforeH <- c(sum(X[2:4]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1") 
kable(C)
```






```{r importOPAL w10, echo=FALSE}

label(ALSA_ds_w10$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w10', ALSA_ds_w10)
#opal.symbol_import(o,'ALSA_ds_w10', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w10
save(hearing_gen, file = "../RData/w10/hearing_gen.RData")

ALSA_m_ds_w10 <- ALSA_ds_w10
ALSA_m_ds_w10$hearing_gen <- car::recode(ALSA_m_ds_w10$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w10', ALSA_m_ds_w10)
#opal.symbol_import(o,'ALSA_m_ds_w10', project='_Athlos_Harm_Dataset')
```



### Wave 11

#### Study-specific variable description




| **Name** | `HEARW11`|
|-|-|
| **Label** | `Hearing Difficulty` |
| **Table name** | `ALSA-Wave11` |
| **Categories** |`1 = Yes; 2 = No` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_hearing_gen','ALSA.ALSA-Wave11', variables=list('HEARW11'), missings = TRUE)
```

```{r local w11, echo=F}
ALSA_w11_hearing_gen <- opal.execute(o,'ALSA_w11_hearing_gen')
vari <- ALSA_w11_hearing_gen$HEARW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "HEARW11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_hearing_gen, aes(x=factor(HEARW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `NA into 999`

**R script:**
```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_hearing_gen$id)
ALSA_ds_w11$hearing_gen <- car::recode(ALSA_w11_hearing_gen$HEARW11, "1 = '0';2 = '1'; NA = '999' ")
ALSA_ds_w11$hearing_gen <- labelled(ALSA_ds_w11$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vari <- ALSA_ds_w11$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
AfterH <- table(ALSA_ds_w11$hearing_gen)
X<-table(ALSA_w11_hearing_gen$HEARW11)
BeforeH <- c((X[1:2]),sum(is.na(ALSA_w11_hearing_gen$HEARW11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```






```{r importOPAL w11, echo=FALSE}

label(ALSA_ds_w11$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w11
save(hearing_gen, file = "../RData/w11/hearing_gen.RData")

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$hearing_gen <- car::recode(ALSA_m_ds_w11$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```



### Wave 12

#### Study-specific variable description




| **Name** | `HEARW12`|
|-|-|
| **Label** | `Hearing Difficulty` |
| **Table name** | `ALSA-Wave12` |
| **Categories** |`1 = Yes; 2 = No` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_hearing_gen','ALSA.ALSA-Wave12', variables=list('HEARW12'), missings = TRUE)
```

```{r local w12, echo=F}
ALSA_w12_hearing_gen <- opal.execute(o,'ALSA_w12_hearing_gen')
vari <- ALSA_w12_hearing_gen$HEARW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "HEARW12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_hearing_gen, aes(x=factor(HEARW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `NA into 999`

**R script:**
```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_hearing_gen$id)
ALSA_ds_w12$hearing_gen <- car::recode(ALSA_w12_hearing_gen$HEARW12, "1 = '0';2 = '1'; NA = '999' ")
ALSA_ds_w12$hearing_gen <- labelled(ALSA_ds_w12$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vari <- ALSA_ds_w12$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
AfterH <- table(ALSA_ds_w12$hearing_gen)
X<-table(ALSA_w12_hearing_gen$HEARW12)
BeforeH <- c((X[1:2]),sum(is.na(ALSA_w12_hearing_gen$HEARW12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```






```{r importOPAL w12, echo=FALSE}

label(ALSA_ds_w12$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w12
save(hearing_gen, file = "../RData/w12/hearing_gen.RData")

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$hearing_gen <- car::recode(ALSA_m_ds_w12$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```



### Wave 13

#### Study-specific variable description




| **Name** | `DIFFHRW13`|
|-|-|
| **Label** | `How much, if any, difficulty to you have hearing even when wearing your hearing aid` |
| **Table name** | `ALSA-Wave13` |
| **Categories** |`1 = None; 2 = Slight difficulty; 3 = Moderate difficulty; 4 = Great difficulty` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_hearing_gen','ALSA.ALSA-Wave13', variables=list('DIFFHRW13'), missings = TRUE)
```

```{r local w13, echo=F}
ALSA_w13_hearing_gen <- opal.execute(o,'ALSA_w13_hearing_gen')
vari <- ALSA_w13_hearing_gen$DIFFHRW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "DIFFHRW13")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13_hearing_gen, aes(x=factor(DIFFHRW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999`

**R script:**
```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13_hearing_gen$id)
ALSA_ds_w13$hearing_gen <- car::recode(ALSA_w13_hearing_gen$DIFFHRW13, "1 = '1';2 = '0';3 = '0';4 = '0'; NA = '999' ")
ALSA_ds_w13$hearing_gen <- labelled(ALSA_ds_w13$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vari <- ALSA_ds_w13$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
AfterH <- table(ALSA_ds_w13$hearing_gen)
X<-table(ALSA_w13_hearing_gen$DIFFHRW13)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(ALSA_w13_hearing_gen$DIFFHRW13)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w13, echo=FALSE}

label(ALSA_ds_w13$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'ALSA_ds_w13', ALSA_ds_w13)
#opal.symbol_import(o,'ALSA_ds_w13', project='_Athlos_Harm_Dataset')
hearing_gen <- ALSA_ds_w13
save(hearing_gen, file = "../RData/w13/hearing_gen.RData")

ALSA_m_ds_w13 <- ALSA_ds_w13
ALSA_m_ds_w13$hearing_gen <- car::recode(ALSA_m_ds_w13$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w13', ALSA_m_ds_w13)
#opal.symbol_import(o,'ALSA_m_ds_w13', project='_Athlos_Harm_Dataset')
```



# Quality estimation
Two slightly different concepts are used here depending on the wave: "difficulty for hearing" and "difficulty hearing some talking in a quite room".
However, we can assume that both concepts are similar and they are matching the meaning of the harmonised variable proposed.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
