---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Finland


### Wave 1 

#### Study-specific variable description

| **Name** | `SYNTVUOSI` |
|----------|------------|
| **Label** | `Year of birth` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Description** |  |

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w1_ybirth','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('SYNTVUOSI'), missings = TRUE)
Health20002011_w1_ybirth <- opal.execute(o,'Health20002011_w1_ybirth')
```

```{r local1, echo=F}
vari <- Health20002011_w1_ybirth$SYNTVUOSI
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1_ybirth, aes(SYNTVUOSI)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_ybirth$id)
Health20002011_ds_w1$ybirth <- car::recode(Health20002011_w1_ybirth$SYNTVUOSI, "NA=999")
Health20002011_ds_w1$ybirth <- labelled(Health20002011_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- Health20002011_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
ybirth <- Health20002011_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")
rm(ybirth)

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$ybirth <- car::recode(Health20002011_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description

| **Name** | `SYNTVUOSI` |
|----------|------------|
| **Label** | `Year of birth` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w1_ybirth','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('SYNTVUOSI'), missings = TRUE)
opal.assign.table.tibble(o, 'Health20002011_w2_id','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('OSITE'), missings = TRUE)
```


```{r local2, echo=F}
Health20002011_w1_ybirth <- opal.execute(o,'Health20002011_w1_ybirth')
Health20002011_w2_id <- opal.execute(o,'Health20002011_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SYNTVUOSI=as.numeric(new_2[,2]))
  new_22
}



Health20002011_w2_ybirth <- Add_indiv(old = Health20002011_w1_ybirth, new = Health20002011_w2_id)


vari <- Health20002011_w2_ybirth$SYNTVUOSI
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2_ybirth, aes(SYNTVUOSI)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_ybirth$id)
Health20002011_ds_w2$ybirth <- car::recode(Health20002011_w2_ybirth$SYNTVUOSI, "NA=999")
Health20002011_ds_w2$ybirth <- labelled(Health20002011_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- Health20002011_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1900, 1980)
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
ybirth <- Health20002011_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
rm(ybirth)

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$ybirth <- car::recode(Health20002011_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
