---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process

## Finland

### Wave 1 

#### Study-specific variable description


| **Name** | `IKA2` |
|----------|------------|
| **Label** | `T2000: age, 1.7.2000` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w1_age','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('IKA2'), missings = TRUE)
```

```{r local1, echo=F}
Health20002011_w1_age <- opal.execute(o,'Health20002011_w1_age')
vari <- Health20002011_w1_age$IKA2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "IKA2")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1_age, aes(IKA2)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_age$id)
Health20002011_ds_w1$age <- car::recode(Health20002011_w1_age$IKA2, "NA=999")
Health20002011_ds_w1$age <- labelled(Health20002011_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- Health20002011_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```











### Wave 2 

#### Study-specific variable description


| **Name** | `IKA2` |
|----------|------------|
| **Label** | `H2011::AGE 1.7.2011` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Description** |  |




```{r assign2, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w2_age','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('IKA2'), missings = TRUE)
```

```{r local2, echo=F}
Health20002011_w2_age <- opal.execute(o,'Health20002011_w2_age')
vari <- Health20002011_w2_age$IKA2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "IKA2")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2_age, aes(IKA2)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_age$id)
Health20002011_ds_w2$age <- car::recode(Health20002011_w2_age$IKA2, "NA=999")
Health20002011_ds_w2$age <- labelled(Health20002011_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- Health20002011_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
