---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```

<!-- ########################################################## --> 

# Data process


## Finland
### Wave 1 

#### Study-specific variable description

 

| **Name** | `SP2`|
|-|-|
| **Label** | `T2000: gender, 1.7.2000`|
| **Table name** |`t00_athlos_2017_02_23`|
| **Categories** | `1 = male`<br/>`2 = female`|
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_sex','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w1_sex <- opal.execute(o,'Health20002011_w1_sex')
```

```{r local1, echo=FALSE}
vari <- Health20002011_w1_sex$SP2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1_sex, aes(x=factor(SP2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "male" into 1`
* `2 "female" into 0`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_sex$id)
Health20002011_ds_w1$sex <- car::recode(Health20002011_w1_sex$SP2, "2=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(Health20002011_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(Health20002011_ds_w1$sex)
BeforeH <- table(Health20002011_w1_sex$SP2)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```








### Wave 2 

#### Study-specific variable description

 

| **Name** | `SP2`|
|-|-|
| **Label** | `H2011::GENDER`|
| **Table name** |`t11_athlos_2017_02_27`|
| **Categories** | `1 = male`<br/>`2 = female`|


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w2_sex','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w2_sex <- opal.execute(o,'Health20002011_w2_sex')
```

```{r local2, echo=FALSE}
vari <- Health20002011_w2_sex$SP2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2_sex, aes(x=factor(SP2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_sex$id)
Health20002011_ds_w2$sex <- car::recode(Health20002011_w2_sex$SP2, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(Health20002011_ds_w2$sex)
BeforeH <- table(Health20002011_w2_sex$SP2)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}
source("../../helpfunctions.r")
```




```{r summ, echo=F}
# All study waves and populations with abbreviated and descriptive names
health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))
# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))
if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}
m.hds <- list()
lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)
if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}
```


# Quality estimation

No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
