---
title: "Sex"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

```{r lab, echo=FALSE}
ds_label <- "Sex"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `sex`
* Variable label: `biological sex`
* Variable description: `participant's biological sex`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | female
1        | male

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process


## Finland
### Wave 1 

#### Study-specific variable description

 

* Name: `SP2`
* Label: `T2000: gender, 1.7.2000`
* Categories: 
    + `1 = male`
    + `2 = female`
* Description:
```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_sex','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w1_sex <- opal.execute(o,'Health20002011_w1_sex')
```

```{r local1, echo=FALSE}
vari <- Health20002011_w1_sex$SP2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1_sex, aes(x=factor(SP2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "male" into 1`
* `2 "female" into 0`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_sex$id)
Health20002011_ds_w1$sex <- car::recode(Health20002011_w1_sex$SP2, "2=0; NA=999")
Health20002011_ds_w1$sex <- labelled(Health20002011_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(Health20002011_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(Health20002011_ds_w1$sex)
BeforeH <- table(Health20002011_w1_sex$SP2)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```


```{r importOPAL1, echo=FALSE}
val_labels(Health20002011_ds_w1) <- NULL
opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
sex <- Health20002011_ds_w1
save(sex, file = "../RData/w1/sex.RData")
rm(sex)

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$sex <- car::recode(Health20002011_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description

 

* Name: `SP2`
* Label: `H2011::GENDER`
* Categories: 
    + `1 = male`
    + `2 = female`
* Description:
```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w2_sex','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w2_sex <- opal.execute(o,'Health20002011_w2_sex')
```

```{r local2, echo=FALSE}
vari <- Health20002011_w2_sex$SP2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2_sex, aes(x=factor(SP2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_sex$id)
Health20002011_ds_w2$sex <- car::recode(Health20002011_w2_sex$SP2, "2=0; NA=999")
Health20002011_ds_w2$sex <- labelled(Health20002011_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(Health20002011_ds_w2$sex)
BeforeH <- table(Health20002011_w2_sex$SP2)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```


```{r importOPAL2, echo=FALSE}
val_labels(Health20002011_ds_w2) <- NULL
opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
sex <- Health20002011_ds_w2
save(sex, file = "../RData/w2/sex.RData")
rm(sex)

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$sex <- car::recode(Health20002011_m_ds_w2$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
