---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Level of education"
ds_label_all <- "Highest level of formal education achieved"
```



<!-- ########################################################## --> 

# Data process

## Finland

### Wave 1 

#### Study-specific variable description

* Name: `AC01`
* Label: `Basic level of education`
* Categories: 
    + `1 = less than elementary school`
    + `2 = elementary school`
    + `3 = lower secondary school`
    + `4 = less than 9 years`
    + `5 = middle school`
    + `6 = comprehensive school`
    + `7 = part of upper secondary school`
    + `8 = matriculation examination`
    
* Name: `AC02`
* Label: `Highest level of education`
* Categories: 
    + `1 = nothing`
    + `2 = vocational course`
    + `3 = vocational school`
    + `4 = vocational training`
    + `5 = vocational college`
    + `6 = special vocational degree`
    + `7 = university of applied sciences`
    + `8 = lower university degree Bachelor's degree`
    + `9 = higher university degree Master's degree`
    + `10 = licentiate's degree`
    + `11 = doctoral degree`


* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_educ','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('AC01', 'AC02'), missings = TRUE)
Health20002011_w1_educ <- opal.execute(o,'Health20002011_w1_educ')
```

```{r local1,  echo=FALSE}
vari <- Health20002011_w1_educ$AC01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1_educ, aes(x=factor(AC01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")


vari <- Health20002011_w1_educ$AC02
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1_educ, aes(x=factor(AC02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if AC01=1 into 0`
* `if AC01=2 into 1`
* `if AC01=3 into 1`
* `if AC01=4 into 1`
* `if AC01=5 into 1`
* `if AC01=6 into 1`
* `if AC01=7 into 2`
* `if AC01=8 into 2`
* `if AC02=1 into 2`
* `if AC02=2 into 2`
* `if AC02=3 into 2`
* `if AC02=4 into 2`
* `if AC02=5 into 2`
* `if AC02=6 into 2`
* `if AC02=7 into 2`
* `if AC02=8 into 3`
* `if AC02=9 into 3`
* `if AC02=10 into 3`
* `if AC02=11 into 3`

**R script:**

```{r harmo1,   echo=TRUE}
Health20002011_w1_educ$AC01_2 <- car::recode(Health20002011_w1_educ$AC01, "1=0; 2:6=1; 7:8=2")
Health20002011_w1_educ$AC02_2 <- car::recode(Health20002011_w1_educ$AC02, "1:7=2; 8:11=3")

Health20002011_w1_educ$AC012 <- Health20002011_w1_educ$AC02_2
Health20002011_w1_educ$AC012[is.na(Health20002011_w1_educ$AC02_2)] <- Health20002011_w1_educ$AC01_2[is.na(Health20002011_w1_educ$AC02_2)]


Health20002011_ds_w1 <- tibble(id=Health20002011_w1_educ$id)
Health20002011_ds_w1$education <- car::recode(Health20002011_w1_educ$AC012, "NA=999")
Health20002011_ds_w1$education <- labelled(Health20002011_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- Health20002011_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Level of Education") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(Health20002011_w1_educ$AC012, useNA = "ifany")
AfterH <- table(Health20002011_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(AC01=2-6)->1", "(AC01=7-8, AC02=1-7)->2", "(AC02=8-11)->3", "NA->999")
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(Health20002011_ds_w1$education) <- ds_label_all
education <- Health20002011_ds_w1
save(education, file = "../RData/w1/education.RData")
```



### Wave 2 

#### Study-specific variable description

* Name: `AC01`
* Label: `Basic level of education`
* Categories: 
    + `1 = less than elementary school`
    + `2 = elementary school`
    + `3 = lower secondary school`
    + `4 = less than 9 years`
    + `5 = middle school`
    + `6 = comprehensive school`
    + `7 = part of upper secondary school`
    + `8 = matriculation examination`
    
* Name: `AC02`
* Label: `Highest level of education`
* Categories: 
    + `1 = no vocational education at all`
    + `2 = training or technical certificate for courses completed`
    + `3 = vocational school certificate, apprenticeship contract`
    + `4 = vocational school e.g. technical school`
    + `5 = atechnical college qualification`
    + `6 = aspecial vocational qualification e.g. a mastership examination`
    + `7 = adegree of higher vocational qualification`
    + `8 = alower university qualification`
    + `9 = ahigher university qualification`
    + `10 = licentiate examination`
    + `11 = doctor's degree`

* Description: 
```{r assign2,  echo=FALSE,  echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w2_educ','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('AC01', 'AC02'), missings = TRUE)
Health20002011_w2_educ <- opal.execute(o,'Health20002011_w2_educ')
```

```{r local2,  echo=FALSE}
vari <- Health20002011_w2_educ$AC01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2_educ, aes(x=factor(AC01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")

vari <- Health20002011_w2_educ$AC02
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2_educ, aes(x=factor(AC02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if AC01=1 into 0`
* `if AC01=2 into 1`
* `if AC01=3 into 1`
* `if AC01=4 into 1`
* `if AC01=5 into 1`
* `if AC01=6 into 1`
* `if AC01=7 into 2`
* `if AC01=8 into 2`
* `if AC02=1 into 2`
* `if AC02=2 into 2`
* `if AC02=3 into 2`
* `if AC02=4 into 2`
* `if AC02=5 into 2`
* `if AC02=6 into 2`
* `if AC02=7 into 2`
* `if AC02=8 into 3`
* `if AC02=9 into 3`
* `if AC02=10 into 3`
* `if AC02=11 into 3`

**R script:**

```{r harmo2,   echo=TRUE}
Health20002011_w2_educ$AC01_2 <- car::recode(Health20002011_w2_educ$AC01, "1=0; 2:6=1; 7:8=2")
Health20002011_w2_educ$AC02_2 <- car::recode(Health20002011_w2_educ$AC02, "1:7=2; 8:11=3")

Health20002011_w2_educ$AC012 <- Health20002011_w2_educ$AC02_2
Health20002011_w2_educ$AC012[is.na(Health20002011_w2_educ$AC02_2)] <- Health20002011_w2_educ$AC01_2[is.na(Health20002011_w2_educ$AC02_2)]

Health20002011_ds_w2 <- tibble(id=Health20002011_w2_educ$id)
Health20002011_ds_w2$education <- car::recode(Health20002011_w2_educ$AC012, "NA=999")
Health20002011_ds_w2$education <- labelled(Health20002011_ds_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- Health20002011_ds_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Level of Education") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(Health20002011_w2_educ$AC012, useNA = "ifany")
AfterH <- table(Health20002011_ds_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(AC01=2-6)->1", "(AC01=7-8, AC02=1-7)->2", "(AC02=8-11)->3", "NA->999")
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(Health20002011_ds_w2$education) <- ds_label_all
education <- Health20002011_ds_w2
save(education, file = "../RData/w2/education.RData")
```
 
# Quality estimation

There are two variables regarding to level of education (ac01 and ac02). The first one is about basic education and the second one is about the highest completed education attained after the basic education. We used ac02 to create the harmonized variable. If it was missing, we used ac01. 

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```




