---
title: "Residence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `residence`
* Variable label: `Current residence`
* Variable description: `Current residence`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Community living
1        | Institutions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Current residence"
```

# Data process

## Finland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `GB01_L`
* Label: `Home: institution`
* Categories: 
    + `0 = no`
    + `1 = yes`

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_resi','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('GB01_L'), missings = TRUE)
Health20002011_w1_resi <- opal.execute(o,'Health20002011_w1_resi')
```

```{r local1, echo=FALSE}
vari <- Health20002011_w1_resi$GB01_L
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1_resi, aes(x=factor(GB01_L))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "no" into 1`
* `keep "yes" into 0`

R code of the ALGORITHM:

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_resi$id)
Health20002011_ds_w1$residence <- car::recode(Health20002011_w1_resi$GB01_L, "NA=999")
Health20002011_ds_w1$residence <- labelled(Health20002011_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$residence 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- c(table(Health20002011_w1_resi$GB01_L), sum(is.na(Health20002011_w1_resi$GB01_L)))
AfterH <- table(Health20002011_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```


```{r importOPAL1, echo=FALSE}
label(Health20002011_ds_w1) <- ds_label
residence <- Health20002011_ds_w1
save(residence, file = "../RData/w1/residence.RData")
```






### Health2000-2011 - Wave 2 

There is no variable. 


### Quality estimation
[Comments on the quality of the new harmonised variable.]




