---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `AD01` |
|-|-|
| **Label** | `Main activity` |
| **Table name**  | `t00_athlos_2017_02_23` | 
| **Categories** | `1 = full-time job`<br/>`2 = parti-time job`<br/>`3 = student`<br/>`4 = retired`<br/>`5 = unemployed or laid off`<br/>`6 = housekeeping`<br/>`7 = military or non-military service`<br/>`8 = other` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('AD01'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$AD01
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(AD01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4,5,6,7,8 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$employed <- car::recode(Health20002011_w1$AD01, "c(1,2) = 1; c(3,4,5,6,7,8) = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2


#### Study-specific variable description


| **Name** | `AD01` |
|-|-|
| **Label** | `Main activity` |
| **Table name**  | `t11_athlos_2017_02_27` | 
| **Categories** | `1 = full-time employment`<br/>`2 = part-time employment also part-time pensioners`<br/>`3 = student`<br/>`4 = retired`<br/>`5 = unemployed or temporarily laid-off`<br/>`6 = management of own household or care of family members`<br/>`7 = conscript or non-military service`<br/>`8 = other` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('AD01'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$AD01
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(AD01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4,5,6,7,8 into 0`
* `NA into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$employed <- car::recode(Health20002011_w2$AD01, "c(1,2) = 1; c(3,4,5,6,7,8) = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}
Health20002011_ds_w1$employed <- labelled(Health20002011_ds_w1$employed, labels = cat_label)
label(Health20002011_ds_w1$employed) <- ds_label
Health20002011_ds_w2$employed <- labelled(Health20002011_ds_w2$employed, labels = cat_label)
label(Health20002011_ds_w2$employed) <- ds_label

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$employed <- car::recode(Health20002011_m_ds_w1$employed, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$employed <- car::recode(Health20002011_m_ds_w2$employed, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$employed)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$employed)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$employed), length(Health20002011_ds_w2$employed)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","employed")], Health20002011_m_ds_w2[,c("id","employed")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  employed <- l.Health20002011[[index]]
  save(employed, file = paste0(datafolder,names(l.Health20002011)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





