---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ydeath`
* Variable label: `year of death`
* Domain: `Death`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## England




### Wave 1 

There is no variable.


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_ydeath','ELSA.elsa_eol_w2_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
ELSA_w2_ydeath <- opal.execute(o,'ELSA_w2_ydeath')

ELSA_w2_ydeath <- ELSA_w2_ydeath[-which(ELSA_w2_ydeath$id==115040),]
```

```{r local2, echo=F}
Categorical_summary(var = ELSA_w2_ydeath$EiDateY, missing_values = c(-9, -8, -1))
ggplot(ELSA_w2_ydeath, aes(EiDateY)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Refused/not answered" into 997`
* `recode -8 "Don't know" into 998`
* `recode -1 "Not applicable" into 996`
* `NA into 999`


**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_ydeath$id)
ELSA_ds_w2$ydeath <- car::recode(ELSA_w2_ydeath$EiDateY, "-9=997; -8=998; -1=996; NA=999")
ELSA_ds_w2$ydeath <- labelled(ELSA_ds_w2$ydeath, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ELSA_ds_w2$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ELSA_w2_ydeath$EiDateY, useNA = "ifany")
AfterH <- table(ELSA_ds_w2$ydeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


```{r importOPAL2, echo=F}
val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$ydeath <- car::recode(ELSA_m_ds_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
ydeath <- ELSA_ds_w2
save(ydeath, file = paste0(datafolder, "/w2/ydeath.RData"))
```





### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_ydeath','ELSA.elsa_eol_w3_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
ELSA_w3_ydeath <- opal.execute(o,'ELSA_w3_ydeath')

ELSA_w3_ydeath <- ELSA_w3_ydeath[-which(ELSA_w3_ydeath$id==101432),]
```

```{r local3, echo=F}
Categorical_summary(var = ELSA_w3_ydeath$EiDateY, missing_values = c(-9, -8, -1))
ggplot(ELSA_w3_ydeath, aes(EiDateY)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Refused/not answered" into 997`
* `recode -8 "Don't know" into 998`
* `recode -1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_ydeath$id)
ELSA_ds_w3$ydeath <- car::recode(ELSA_w3_ydeath$EiDateY, "-9=997; -8=998; -1=996; NA=999")
ELSA_ds_w3$ydeath <- labelled(ELSA_ds_w3$ydeath, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ELSA_ds_w3$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ELSA_w3_ydeath$EiDateY, useNA = "ifany")
AfterH <- table(ELSA_ds_w3$ydeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```

```{r importOPAL3, echo=F}
val_labels(ELSA_ds_w3) <- NULL
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$ydeath <- car::recode(ELSA_m_ds_w3$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
ydeath <- ELSA_ds_w3
save(ydeath, file = paste0(datafolder, "/w3/ydeath.RData"))
```



### Wave 4

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_ydeath','ELSA.elsa_eol_w4_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
ELSA_w4_ydeath <- opal.execute(o,'ELSA_w4_ydeath')

ELSA_w4_ydeath <- ELSA_w4_ydeath[-which(ELSA_w4_ydeath$id==114235),]
```

```{r local4, echo=F}
Categorical_summary(var = ELSA_w4_ydeath$EiDateY, missing_values = c(-9, -8, -1))
ggplot(ELSA_w4_ydeath, aes(EiDateY)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Refused/not answered" into 997`
* `recode -8 "Don't know" into 998`
* `recode -1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_ydeath$id)
ELSA_ds_w4$ydeath <- car::recode(ELSA_w4_ydeath$EiDateY, "-9=997; -8=998; -1=996; NA=999")
ELSA_ds_w4$ydeath <- labelled(ELSA_ds_w4$ydeath, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ELSA_w4_ydeath$EiDateY, useNA = "ifany")
AfterH <- table(ELSA_ds_w4$ydeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```

```{r importOPAL4, echo=F}
val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$ydeath <- car::recode(ELSA_m_ds_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```




```{r,  echo=FALSE}
ydeath <- ELSA_ds_w4
save(ydeath, file = paste0(datafolder, "/w4/ydeath.RData"))
```




### Wave 5

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_yinter','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w6_ydeath','ELSA.elsa_endoflife_w6archive',
                         variables=list('EiDateY'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_yinter <- opal.execute(o,'ELSA_w5_yinter')
ELSA_w6_ydeath <- opal.execute(o,'ELSA_w6_ydeath')

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

ELSA_w5_LS <- same_indiv(old = ELSA_w6_ydeath, new = ELSA_w5_yinter)

```

#### Harmonisation algorithm
It is going to compute the variable from the study-specific variable from wave 6, the individuals with the same year of interview than year of death. The others individuals will be recoded as missing. 

**R script:**

```{r harmo5}

ELSA_w5_LS$yinter <- ELSA_w5_yinter$iintdaty
ELSA_w5_LS$ydeathw5 <- NA
ELSA_w5_LS$ydeathw5[which(ELSA_w5_LS$ydeath==2011 & ELSA_w5_LS$yinter==2011 | ELSA_w5_LS$ydeath==2010)] <- ELSA_w5_LS$ydeath[which(ELSA_w5_LS$ydeath==2011 & ELSA_w5_LS$yinter==2011 | ELSA_w5_LS$ydeath==2010)]


ELSA_ds_w5 <- tibble(id=ELSA_w5_LS$id)
ELSA_ds_w5$ydeath <- car::recode(ELSA_w5_LS$ydeathw5, "NA=999")
ELSA_ds_w5$ydeath <- labelled(ELSA_ds_w5$ydeath, labels = c("Alive"=0, "Dead"=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = ELSA_ds_w5$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
```


```{r importOPAL5, echo=F}
val_labels(ELSA_ds_w5) <- NULL
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$ydeath <- car::recode(ELSA_m_ds_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
ydeath <- ELSA_ds_w5
save(ydeath, file = paste0(datafolder, "/w5/ydeath.RData"))
```


### Wave 6

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_ydeath','ELSA.elsa_endoflife_w6archive',
                         variables=list('EiDateY'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_ydeath <- opal.execute(o,'ELSA_w6_ydeath')
Categorical_summary(var = ELSA_w6_ydeath$EiDateY, missing_values = c(-9, -8, -1))
ggplot(ELSA_w6_ydeath, aes(factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Refused/not answered" into 997`
* `recode -8 "Don't know" into 998`
* `recode -1 "Not applicable" into 996`
* `NA into 999`


**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_ydeath$id)
ELSA_ds_w6$ydeath <- car::recode(ELSA_w6_ydeath$EiDateY, "-9=997; -8=998; -1=996; NA=999")
ELSA_ds_w6$ydeath <- labelled(ELSA_ds_w6$ydeath, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ELSA_w6_ydeath$EiDateY, useNA = "ifany")
AfterH <- table(ELSA_ds_w6$ydeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "-8->998")
kable(C)
```


```{r importOPAL6, echo=F}
val_labels(ELSA_ds_w6) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$ydeath <- car::recode(ELSA_m_ds_w6$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
ydeath <- ELSA_ds_w6
save(ydeath, file = paste0(datafolder, "/w6/ydeath.RData"))
```


### Wave 7

Not found.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

# Quality estimation

No comments

