---
title: "Year of Death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ydeathDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ydeathDS.R')
```

# Data process




## England


### Wave non-specific

#### Study-specific variable description


| **Name** |`yrdeath`|
|-|-|
| **Label** |`Year of death - updated Feb 2012`|
| **Table name** |`index_file_wave_0-wave_5_v2`|
| **Units** |`years`|
| **Missings** |`-3 = Details being checked with ONS`<br/>`-2 = Information not available or not applicable`|
| **Description** |  |

```{r assign_all, echo=F}


opal.assign.table.tibble(o,'ELSA_w1_ybirth','ELSA.wave_1_core_data_v3',
                         variables=list('indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w2_ybirth','ELSA.wave_2_core_data_v4',
                         variables=list('indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w3_ybirth','ELSA.wave_3_elsa_data_v4',
                         variables=list('indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w4_ybirth','ELSA.wave_4_elsa_data_v3',
                         variables=list('indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w5_ybirth','ELSA.wave_5_elsa_data_v4',
                         variables=list('indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w6_ybirth','ELSA.wave_6_elsa_data_v2',
                         variables=list('Indobyr'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w7_ybirth','ELSA.wave_7_elsa_data',
                         variables=list('Indobyr'), missings = TRUE)

core1 <- opal.execute(o,'ELSA_w1_ybirth')
core2 <- opal.execute(o,'ELSA_w2_ybirth')
core3 <- opal.execute(o,'ELSA_w3_ybirth')
core4 <- opal.execute(o,'ELSA_w4_ybirth')
core5 <- opal.execute(o,'ELSA_w5_ybirth')
core6 <- opal.execute(o,'ELSA_w6_ybirth')
core7 <- opal.execute(o,'ELSA_w7_ybirth')

opal.assign.table.tibble(o, 'ELSA_w2_ydeath','ELSA.elsa_eol_w2_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w3_ydeath','ELSA.elsa_eol_w3_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w4_ydeath','ELSA.elsa_eol_w4_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w6_ydeath','ELSA.elsa_endoflife_w6archive',
                         variables=list('EiDateY'), missings = TRUE)
eol2 <- opal.execute(o,'ELSA_w2_ydeath')
eol3 <- opal.execute(o,'ELSA_w3_ydeath')
eol4 <- opal.execute(o,'ELSA_w4_ydeath')
eol6 <- opal.execute(o,'ELSA_w6_ydeath')

opal.assign.table.tibble(o,'ELSA','ELSA.index_file_wave_0-wave_5_v2',
                         variables=list('yrdeath','mortstat'), missings = TRUE)
elsa <- opal.execute(o,'ELSA')

```




```{r local, echo=F}


vbl <- elsa$yrdeath
vbl_miss <- c(-2, -3)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "yrdeath")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = label(vbl))
ggplot(elsa, aes(x=factor(vbl))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

* `Priorize year of death taken from official mortality data (the National Health Service Central Register)`
* `Otherwise, keep years of death answered in EOL interviews`
* `Correct an impossible year of death with the given in EOL interview`
* `harmonise those id's dead during wave n (2000 + n*2,2001 + n*2) in wave n if they do not participate in it or otherwise in wave n+1`

**R script:**

```{r global_harmo}


# Individuals with potential information on death and in some wave up to 0. Values -2,-3 of yrdeath have no useful information to harmonise
elsa <- elsa %>%
  filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id,core5$id,core6$id,core7$id))) %>%
  mutate_at("yrdeath",~replace(.,list = which(. %in% c(-2,-3)), values = NA)) %>%
  filter_at(vars(-id),any_vars(!is.na(.)))
# elsa <- elsa %>%
#   filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id,core5$id,core6$id,core7$id))) %>%
#   mutate_at("yrdeath",~replace(.,list = which(. %in% c(-2,-3)), values = NA)) %>%
#   mutate_at("mortstat",~replace(.,list = which(. %in% c(-1,-0)), values = NA)) %>%
#   filter_at(vars(-id),any_vars(!is.na(.)))

# Individuals in EoL interviews not interviewed in any wave from 1 are removed. We keep them only in first EoL interview they appear.
# Printed lengths of cases
# 135 - 1 = 134
ids2 <- (eol2 %>% filter(id %in% Reduce(union,list(core1$id,core2$id))))$id
# 375 - 1 = 374
ids3 <- setdiff((eol3 %>% filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id))))$id, eol2$id)
# 242 -1 - 4 = 237
ids4 <- setdiff((eol4 %>% filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id))))$id, union(eol2$id,eol3$id))
# 240
ids6 <- setdiff((eol6 %>% filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id,core5$id,core6$id))))$id,Reduce(union,list(eol2$id,eol3$id,eol4$id)))
# 134 + 374 + 237 + 240 = 985
ids <- Reduce(union, list(ids2,ids3,ids4,ids6))

eol <- full_join(eol2 %>% filter(id %in% ids2),eol3 %>% filter(id %in% ids3), by = "id", suffix = c(".w2",".w3"))
eol <- full_join(eol, eol4 %>% filter(id %in% ids4), by = "id")
eol <- full_join(eol, eol6 %>% filter(id %in% ids6), by = "id", suffix = c(".w4",".w6"))
eol <- eol %>% mutate(EiDateY = coalesce(EiDateY.w2,EiDateY.w3,EiDateY.w4,EiDateY.w6))

# elsa_eol <- full_join(eol %>% select(id,EiDateY) %>% mutate_at("EiDateY",~replace(.,list = which(. %in% c(-8,2000)), values = NA)), elsa %>% filter(!is.na(yrdeath) | id %in% eol$id), by = "id")

# Priorize year of death taken from official mortality data (the National Health Service Central Register). 
# Otherwise, keep years of death answered in EOL interviews. 
# Correct an impossible year of death with the given in EOL interview.

elsa_eol <- full_join(eol %>% select(id,EiDateY), elsa %>% filter(!is.na(yrdeath) | id %in% eol$id), by = "id") %>% mutate(ydeath = coalesce(yrdeath,as.numeric(EiDateY))) %>% mutate(ydeath=replace(ydeath,id %in% ids3 & yrdeath==2010,EiDateY[which(id %in% ids3 & yrdeath==2010)]))


dids2 <- union((elsa_eol %>% filter(ydeath %in% c(2002,2003)))$id,(elsa_eol %>% filter(ydeath %in% c(2004,2005) & !id %in% core2$id))$id)
dids3 <- setdiff(union((elsa_eol %>% filter(ydeath %in% c(2004,2005)))$id,(elsa_eol %>% filter(ydeath %in% c(2006,2007) & !id %in% core3$id))$id),dids2)
dids4 <- setdiff(union((elsa_eol %>% filter(ydeath %in% c(2006,2007)))$id,(elsa_eol %>% filter(ydeath %in% c(2008,2009) & !id %in% core4$id))$id),dids3)
dids5 <- setdiff(union((elsa_eol %>% filter(ydeath %in% c(2008,2009)))$id,(elsa_eol %>% filter(ydeath %in% c(2010,2011) & !id %in% core5$id))$id),dids4)
dids6 <- setdiff(union((elsa_eol %>% filter(ydeath %in% c(2010,2011)))$id,(elsa_eol %>% filter(ydeath %in% c(2012,2013) & !id %in% core6$id))$id),dids5)

```




```{r descript0, echo=F}


# NEW
kable(elsa_eol %>% filter(mortstat==1), caption = "Id's with EOL interview and mortality status = alive have died mainly in 2012")

kable(frq((elsa_eol %>% filter(id %in% ids2))$yrdeath), caption = "Id's with associated wave 2 EOL interview have died before 2006")
kable(frq((elsa_eol %>% filter(id %in% ids2))$EiDateY), caption = "Years of death given in wave 2 EOL interview are previous to 2006")
kable(frq((elsa_eol %>% filter(id %in% ids3))$yrdeath), caption = "There is 1 id with associated wave 3 EOL interview and with death date after 2007")
kable(elsa_eol %>% filter(id %in% ids3 & yrdeath==2010), caption = "This id has died in 2006")

kable(frq((elsa_eol %>% filter(id %in% ids3))$EiDateY), caption = "Years of death given in wave 3 EOL interview are previous to 2008")
kable(frq((elsa_eol %>% filter(id %in% ids4))$yrdeath), caption = "Id's with associated wave 4 EOL interview have died before 2010")
kable(frq((elsa_eol %>% filter(id %in% ids4))$EiDateY), caption = "Years of death given in wave 4 EOL interview are previous to 2010")
kable(frq((elsa_eol %>% filter(id %in% ids6))$yrdeath), caption = "Id's with associated wave 6 interview have died before 2014")
kable(frq((elsa_eol %>% filter(id %in% ids6))$EiDateY), caption = "Years of death given in wave 6 EOL interview are previous to 2014")


kable(frq((elsa_eol %>% filter(id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id,core5$id,core6$id,core7$id))))$EiDateY),caption = "There are 1618 id's with an impossible year of death (2000) or missing data answered in EOL interviews")
kable(frq((elsa_eol %>% filter((EiDateY %in% c(-8,2000) | is.na(EiDateY)) & id %in% Reduce(union,list(core1$id,core2$id,core3$id,core4$id,core5$id,core6$id,core7$id))))$ydeath), caption = "Their years of death")

kable(frq((elsa_eol %>% filter(id %in% core2$id))$yrdeath),caption = "Id's interviewed in wave 2 died in 2004 or later")
kable(frq((elsa_eol %>% filter(id %in% core2$id))$EiDateY),caption = "Years of death given in EOL interviews of id's interviewed in wave 2 are posterior to 2004 up to the wrong or missing data commented above")
kable(frq((elsa_eol %>% filter(id %in% core3$id))$yrdeath),caption = "Id's interviewed in wave 3 died in 2006 or later")
kable(frq((elsa_eol %>% filter(id %in% core3$id))$EiDateY),caption = "Years of death given in EOL interviews of id's interviewed in wave 3 are posterior to 2006 up to the wrong or missing data commented above")
kable(frq((elsa_eol %>% filter(id %in% core4$id))$yrdeath),caption = "Id's interviewed in wave 4 died in 2008 or later")
kable(frq((elsa_eol %>% filter(id %in% core4$id))$EiDateY),caption = "Years of death given in EOL interviews of id's interviewed in wave 4 are posterior to 2008 up to the wrong or missing data commented above and a 2007 value")
kable(elsa_eol %>% filter(id %in% core4$id & EiDateY==2007), caption = "The id with extraneous EOL data has died in 2009")

kable(frq((elsa_eol %>% filter(id %in% core5$id))$yrdeath),caption = "Id's interviewed in wave 5 died in 2010 or later")
kable(frq((elsa_eol %>% filter(id %in% core5$id))$EiDateY),caption = "Years of death given in EOL interviews of id's interviewed in wave 5 are posterior to 2010")

cat(paste("There are", length((elsa_eol %>% filter(id %in% union(core6$id,core7$id)))$id),"id's died and interviewed in the two last waves"))





```


### Wave 1 

Not applicable.

### Wave 2

#### Study-specific variable description


| **Name** |`EiDateY`|
|-|-|
| **Label** |`Year of death`|
| **Table name** |`elsa_eol_w2_archive_v1`|
| **Units** |`years`|
| **Missings** |`-9 = Refused/not answered`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |



```{r local2, echo=F}


vbl <- (eol %>% filter(id %in% ids2))$EiDateY
vbl_miss <- c(-9, -8, -1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "EiDateY")
#kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = label(vbl))
ggplot(eol, aes(x=factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(id %in% ids2)) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=dids2)
ELSA_ds_w2$ydeath <-(elsa_eol %>% filter(id %in% dids2))$ydeath

```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}

vbl <- ELSA_ds_w2$ydeath
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Values")
ggplot(ELSA_ds_w2, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 

```

#### Validation
```{r crosstabulation2, echo=F}

```






### Wave 3

#### Study-specific variable description


| **Name** |`EiDateY`|
|-|-|
| **Label** |`Year of death`|
| **Table name** |`elsa_eol_w3_archive_v1`|
| **Units** |`years`|
| **Missings** |`-9 = Refused/not answered`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |



```{r local3, echo=F}

vbl <- (eol %>% filter(id %in% ids3))$EiDateY
vbl_miss <- c(-9, -8, -1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "EiDateY")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = label(vbl))
ggplot(eol, aes(x=factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(id %in% ids3)) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:


**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=dids3)
ELSA_ds_w3$ydeath <-(elsa_eol %>% filter(id %in% dids3))$ydeath

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}

vbl <- ELSA_ds_w3$ydeath
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Values")
ggplot(ELSA_ds_w3, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}

```




### Wave 4

#### Study-specific variable description


| **Name** |`EiDateY`|
|-|-|
| **Label** |`Year of death`|
| **Table name** |`elsa_eol_w4_archive_v1`|
| **Units** |`years`|
| **Missings** |`-9 = Refused/not answered`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |



```{r local4, echo=F}

vbl <- (eol %>% filter(id %in% ids4))$EiDateY
vbl_miss <- c(-9, -8, -1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "EiDateY")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = label(vbl))
ggplot(eol, aes(x=factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(id %in% ids4)) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:


**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=dids4)
ELSA_ds_w4$ydeath <-(elsa_eol %>% filter(id %in% dids4))$ydeath

```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}

vbl <- ELSA_ds_w4$ydeath
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Values")
ggplot(ELSA_ds_w4, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 

```

#### Validation
```{r crosstabulation4, echo=F}

```







### Wave 5

#### Study-specific variable description


There is no wave-specific variable.

#### Harmonisation algorithm
The variable is going to computed from the study-specific variable from wave 6, but the missing values have to be recoded as follows:


**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=dids5)
ELSA_ds_w5$ydeath <-(elsa_eol %>% filter(id %in% dids5))$ydeath
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}

vbl <- ELSA_ds_w5$ydeath
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Values")
ggplot(ELSA_ds_w5, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation5, echo=F}
```



### Wave 6

#### Study-specific variable description


| **Name** |`EiDateY`|
|-|-|
| **Label** |`Year of death`|
| **Table name** |`elsa_endoflife_w6archive`|
| **Units** |`years`|
| **Missings** |`-9 = Refused/not answered`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign6, echo=F}
```

```{r local6, echo=F}

vbl <- (eol %>% filter(id %in% ids6))$EiDateY
vbl_miss <- c(-9, -8, -1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "EiDateY")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = label(vbl))
ggplot(eol, aes(x=factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(id %in% ids6)) + xlab(label(vbl)) + ylab("Frequency")


```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:


**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=dids6)
ELSA_ds_w6$ydeath <-(elsa_eol %>% filter(id %in% dids6))$ydeath
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}

vbl <- ELSA_ds_w6$ydeath
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Values")
ggplot(ELSA_ds_w6, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation6, echo=F}

```




### Wave 7

Not available data



## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```


# Quality estimation

No comments



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
