---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```

<!-- ########################################################## --> 

# Data process

## ELSA

### Wave 1 


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_id','ELSA.wave_1_core_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w1_id <- opal.execute(o,'ELSA_w1_id')
```



#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}

ELSA_ds_w1 <- tibble(id=ELSA_w1_id$id)
ELSA_ds_w1$living_status <- 0

```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```




### Wave 2

#### Study-specific variable description


| **Name** |`ydeath`|`iintdaty`|
|-|-|-|
| **Label** |`Year of death`|`Year of Individual Interview`|
| **Table name** |`elsa_w2_hd`|`wave_2_ifs_derived_variables`|
| **Units** |`years`|`years`|
| **Missings** |`NA`|  |
| **Description** |  |  |



```{r assign2, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w2_yinter','ELSA.wave_2_ifs_derived_variables',variables=list('iintdaty'), missings = TRUE)
ELSA_w2_yinter <- opal.execute(o,'ELSA_w2_yinter')
load(paste0(datafolder,"w2/ydeath",".RData"))
ELSA_w2_LS <- full_join(ELSA_w2_yinter,ydeath, by = "id")
rm(ydeath)
```

```{r local2, echo=FALSE}


vari <- ELSA_w2_LS$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w2_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_w2_LS$ydeath
kable(Categorical_summary(var = vari, missing_values = NA)[2], caption = "ydeath")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w2_LS, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_LS$id)
ELSA_ds_w2$living_status <- NA
ELSA_ds_w2$living_status[!is.na(ELSA_w2_LS$ydeath)] <- 1
ELSA_ds_w2$living_status[!is.na(ELSA_w2_LS$iintdaty)] <- 0
ELSA_ds_w2$living_status[is.na(ELSA_w2_LS$ydeath) & is.na(ELSA_w2_LS$iintdaty)] <- 2

```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```






### Wave 3

#### Study-specific variable description


| **Name** |`ydeath`|`iintdaty`|
|-|-|-|
| **Label** |`Year of death`|`Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`elsa_w3_hd`|`wave_3_ifs_derived_variables`|
| **Units** |`years`|`years`|
| **Missings** |`NA`|  |
| **Description** |  |  |


```{r assign3, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w3_yinter','ELSA.wave_3_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w3_yinter <- opal.execute(o,'ELSA_w3_yinter')
load(paste0(datafolder,"w3/ydeath",".RData"))
ELSA_w3_LS <- full_join(ELSA_w3_yinter,ydeath, by = "id")
rm(ydeath)
```

```{r local3, echo=FALSE}


vari <- ELSA_w3_LS$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w3_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_w3_LS$ydeath
kable(Categorical_summary(var = vari, missing_values = NA)[2], caption = "ydeath")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w3_LS, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals dead in previous waves into 1`

There are two individuals with date of interview and date of death that are going to be considered as they were alive for this interview because they were interviewed. 

**R script:**

```{r harmo3}

ELSA_ds_w3 <- tibble(id=ELSA_w3_LS$id)
ELSA_ds_w3$living_status <- NA
ELSA_ds_w3$living_status[!is.na(ELSA_w3_LS$ydeath)] <- 1
ELSA_ds_w3$living_status[!is.na(ELSA_w3_LS$iintdaty)] <- 0
ELSA_ds_w3$living_status[is.na(ELSA_w3_LS$ydeath) & is.na(ELSA_w3_LS$iintdaty)] <- 2
ELSA_ds_w3 <- rbind(ELSA_ds_w3, ELSA_ds_w2 %>% filter(living_status == 1 & !id %in% ELSA_ds_w3$id))

```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
```



### Wave 4

#### Study-specific variable description


| **Name** |`ydeath`|`iintdaty`|
|-|-|-|
| **Label** |`Year of death`|`Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`elsa_w4_hd`|`wave_4_ifs_derived_variables`|
| **Units** |`years`|`years`|
| **Missings** |`NA`|  |
| **Description** |  |  |



```{r assign4, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w4_yinter','ELSA.wave_4_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w4_yinter <- opal.execute(o,'ELSA_w4_yinter')

load(paste0(datafolder,"w4/ydeath",".RData"))
ELSA_w4_LS <- full_join(ELSA_w4_yinter,ydeath, by = "id")
rm(ydeath)

```

```{r local4, echo=FALSE}

vari <- ELSA_w4_LS$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w4_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_w4_LS$ydeath
kable(Categorical_summary(var = vari, missing_values = NA)[2], caption = "ydeath")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w4_LS, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals dead in previous waves into 1`

**R script:**

```{r harmo4}


ELSA_ds_w4 <- tibble(id=ELSA_w4_LS$id)
ELSA_ds_w4$living_status <- NA
ELSA_ds_w4$living_status[!is.na(ELSA_w4_LS$ydeath)] <- 1
ELSA_ds_w4$living_status[!is.na(ELSA_w4_LS$iintdaty)] <- 0
ELSA_ds_w4$living_status[is.na(ELSA_w4_LS$ydeath) & is.na(ELSA_w4_LS$iintdaty)] <- 2
ELSA_ds_w4 <- rbind(ELSA_ds_w4, ELSA_ds_w3 %>% filter(living_status == 1 & !id %in% ELSA_ds_w4$id))

```

#### Statistics of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_ds_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
```






### Wave 5

#### Study-specific variable description


| **Name** |`ydeath`|`iintdaty`|
|-|-|-|
| **Label** |`Year of death`|`year of individual interview`|
| **Table name** |`elsa_w5_hd`|`wave_5_ifs_derived_variables`|
| **Units** |`years`|`years`|
| **Missings** |`NA`|  |
| **Description** |  |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_yinter','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w5_yinter <- opal.execute(o,'ELSA_w5_yinter')

load(paste0(datafolder,"w5/ydeath",".RData"))
ELSA_w5_LS <- full_join(ELSA_w5_yinter,ydeath, by = "id")
rm(ydeath)

```

```{r local5, echo=FALSE}


vari <- ELSA_w5_LS$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w5_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_w5_LS$ydeath
kable(Categorical_summary(var = vari, missing_values = NA)[2], caption = "ydeath")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w5_LS, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `death individuals in previous waves into 1`
* `individuals without date of interview either as was not dead in previous waves into 2`
* `individuals dead in previous waves into 1`

**R script:**

```{r harmo5}

ELSA_ds_w5 <- tibble(id=ELSA_w5_LS$id)
ELSA_ds_w5$living_status <- NA
ELSA_ds_w5$living_status[!is.na(ELSA_w5_LS$ydeath)] <- 1
ELSA_ds_w5$living_status[!is.na(ELSA_w5_LS$iintdaty)] <- 0
ELSA_ds_w5$living_status[is.na(ELSA_w5_LS$iintdaty) & is.na(ELSA_w5_LS$ydeath)] <- 2
ELSA_ds_w5 <- rbind(ELSA_ds_w5, ELSA_ds_w4 %>% filter(living_status == 1 & !id %in% ELSA_ds_w5$id))

```

#### Statistics of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_ds_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
```



### Wave 6

#### Study-specific variables


| **Name** |`ydeath`|`iintdaty`|`mortstat`|
|-|-|-|-|
| **Label** |`Year of death`|`year of individual interview`|`Mortality status from ONS -updated Feb 2012`|
| **Table name** |`elsa_w6_hd`|`wave_6_ifs_derived_variables`|`index_file_wave_0-wave_5_v2`|
| **Units** |`years`|`years`|`-2 = Dead - information from other sources`<br/>`-1 = No permission to check`<br/>`0 = Permission given but no trace`<br/>`1 = Alive`<br/>`2 = Dead`|
| **Missings** |`NA`|  |  |
| **Description** |  |  |  |

```{r assign6, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w6_yinter','ELSA.wave_6_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w6_yinter <- opal.execute(o,'ELSA_w6_yinter')
load(paste0(datafolder,"w6/ydeath",".RData"))
ELSA_w6_LS <- full_join(ELSA_w6_yinter,ydeath, by = "id")
rm(ydeath)
opal.assign.table.tibble(o,'ELSA','ELSA.index_file_wave_0-wave_5_v2',
                         variables=list('mortstat'), missings = TRUE)
elsa <- opal.execute(o,'ELSA')

ELSA_w6_LS <- left_join(ELSA_w6_LS,elsa, by = "id")
```

```{r local6, echo=FALSE}


vari <- ELSA_w6_LS$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w6_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") +  xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_w6_LS$ydeath
kable(Categorical_summary(var = vari, missing_values = NA)[2], caption = "ydeath")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w6_LS, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") +  xlab(label(vari)) + ylab("Frequency")


vari <- ELSA_w6_LS$mortstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "mortstat") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w6_LS, aes(factor(vari))) + geom_histogram(stat="count", fill="steelblue") +  xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals dead in previous waves into 1`

**R script:**

```{r harmo6}

ELSA_ds_w6 <- tibble(id=ELSA_w6_LS$id)
ELSA_ds_w6$living_status <- 2
ELSA_ds_w6$living_status[which(!is.na(ELSA_w6_LS$ydeath) | ELSA_w6_LS$mortstat %in% c(-2,2))] <- 1
ELSA_ds_w6$living_status[!is.na(ELSA_w6_LS$iintdaty)] <- 0
ELSA_ds_w6 <- rbind(ELSA_ds_w6, ELSA_ds_w5 %>% filter(living_status == 1 & !id %in% ELSA_ds_w6$id))

```

#### Statistics of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
```




### Wave 7

#### Study-specific variables


| **Name** |`iintdaty`|
|-|-|
| **Label** |`Year of Individual Interview`|
| **Table name** |`wave_7_elsa_data`|
| **Units** |`years`|
| **Description** |  |


```{r assign7, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w7_yinter','ELSA.wave_7_elsa_data',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w7_yinter <- opal.execute(o,'ELSA_w7_yinter')
```

```{r local7, echo=FALSE}


vari <- ELSA_w7_yinter$iintdaty
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "iintdaty") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Values")
ggplot(ELSA_w7_yinter, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals without date of interview into 2`
* `individuals dead in previous waves into 1`

**R script:**

```{r harmo7}

ELSA_ds_w7 <- tibble(id=ELSA_w7_yinter$id)
ELSA_ds_w7$living_status <- NA
ELSA_ds_w7$living_status[!is.na(ELSA_w7_yinter$iintdaty)] <- 0
ELSA_ds_w7$living_status[is.na(ELSA_w7_yinter$iintdaty)] <- 2
ELSA_ds_w7 <- rbind(ELSA_ds_w7, ELSA_ds_w6 %>% filter(living_status == 1 & !id %in% ELSA_ds_w7$id))

```

#### Statistics of the new harmonised variable
```{r descript7, echo=FALSE}
vari <- ELSA_ds_w7$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=FALSE}
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){

  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
At wave 2 there are 109 new individuals interviewed. 
At wave 3 there are 1729 new individuals interviewed. 
At wave 4 there are 2689 new individuals interviewed. At wave 5 there are 142 new individuals interviewed, 
and we don't have date of death, therefore we don't know the individuals that died between wave 4 and 5. 
At wave 6 there are 1215 new individuals interviewed. 
At wave 7 there are 509 new individuals interviewed.

The ELSA sample has been refreshed four times, at waves 3, 4, 6 and 7. The new individuals interviewed are either new participants or partners. For this reason, there are new individuals interviewed even at waves that there wasn't refreshment.

At wave 7 we do not have information about dead individuals.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```