---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```

<!-- ########################################################## --> 

# Data process

## ELSA

### Wave 1 


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_id','ELSA.wave_1_core_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w1_id <- opal.execute(o,'ELSA_w1_id')
```



#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_id$id)
ELSA_ds_w1$living_status <- 0
ELSA_ds_w1$living_status <- labelled(ELSA_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$living_status <- car::recode(ELSA_m_ds_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
living_status <- ELSA_ds_w1
save(living_status, file = paste0(datafolder, "/w1/living_status.RData"))
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Name: `iintdaty`
* Label: `Year of Individual Interview`
* Type of variable: `countinous`

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w2_ydeath','ELSA.elsa_eol_w2_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w2_ids','ELSA.wave_2_derived_variables',
                         variables=list('chonat'), missings = TRUE)
ELSA_w2_ydeath <- opal.execute(o,'ELSA_w2_ydeath')
ELSA_w2_ids <- opal.execute(o,'ELSA_w2_ids')

ELSA_w2_ydeath <- ELSA_w2_ydeath[-which(ELSA_w2_ydeath$id==115040),]

opal.assign.table.tibble(o, 'ELSA_w2_yinter','ELSA.wave_2_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w2_yinter <- opal.execute(o,'ELSA_w2_yinter')
```

```{r local2, echo=FALSE}
IDS <- tibble(id=c(ELSA_w2_ids$id, ELSA_w2_ydeath$id[!(ELSA_w2_ydeath$id%in%ELSA_w2_ids$id)]))
ELSA_w2_LS <- left_join(x = IDS, y = ELSA_w2_ydeath, by = 'id')
ELSA_w2_LS <- left_join(x = ELSA_w2_LS, y = ELSA_w2_yinter, by = 'id')

vari <- ELSA_w2_LS$iintdaty
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w2_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

vari <- ELSA_w2_LS$EiDateY
kable(Continuous_summary(var = vari, missing_values = c(-9,-8,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2_LS, aes(factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_LS$id)
ELSA_ds_w2$living_status <- NA
ELSA_ds_w2$living_status[!is.na(ELSA_w2_LS$iintdaty)] <- 0
ELSA_ds_w2$living_status[!is.na(ELSA_w2_LS$EiDateY)] <- 1
ELSA_ds_w2$living_status[is.na(ELSA_w2_LS$EiDateY) & is.na(ELSA_w2_LS$iintdaty)] <- 2
ELSA_ds_w2$living_status <- labelled(ELSA_ds_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```

```{r importOPAL2, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$living_status <- car::recode(ELSA_m_ds_w2$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
living_status <- ELSA_ds_w2
save(living_status, file = paste0(datafolder, "/w2/living_status.RData"))
```





### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_ydeath','ELSA.elsa_eol_w3_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w3_yinter','ELSA.wave_3_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w3_ydeath <- opal.execute(o,'ELSA_w3_ydeath')
ELSA_w3_yinter <- opal.execute(o,'ELSA_w3_yinter')

ELSA_w3_ydeath <- ELSA_w3_ydeath[-which(ELSA_w3_ydeath$id==101432),]
```

```{r local3, echo=FALSE}
all_ids_w3 <- c(ELSA_w3_yinter$id, ELSA_w3_ydeath$id[!(ELSA_w3_ydeath$id %in% ELSA_w3_yinter$id)])

#dim(ELSA_ds_w2)
#length(all_ids_w3)
#sum(!all_ids_w3 %in% ELSA_ds_w2$id) #10144 - 8415 = 1729


IDS_w3 <- tibble(id= c(all_ids_w3, ELSA_w2_LS$id[!(ELSA_w2_LS$id %in% all_ids_w3)]))

ELSA_w3_LS <- left_join(x = IDS_w3, y = ELSA_w3_ydeath, by = 'id')
ELSA_w3_LS <- left_join(x = ELSA_w3_LS, y = ELSA_w3_yinter, by = 'id')


vari <- ELSA_w3_LS$iintdaty
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w3_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

vari <- ELSA_w3_LS$EiDateY
kable(Continuous_summary(var = vari, missing_values = c(-9,-8,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w3_LS, aes(factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals death in previous waves into 1`

There are two individuals with date of interview and date of death that are going to be considered as they were alive for this interview because they were interview. 

**R script:**

```{r harmo3}
ids_deaths_w2 <- ELSA_ds_w2$id[which(ELSA_ds_w2$living_status==1)]

ELSA_ds_w3 <- tibble(id=ELSA_w3_LS$id)
ELSA_ds_w3$living_status <- NA
ELSA_ds_w3$living_status[!is.na(ELSA_w3_LS$EiDateY)] <- 1
ELSA_ds_w3$living_status[!is.na(ELSA_w3_LS$iintdaty)] <- 0
ELSA_ds_w3$living_status[is.na(ELSA_w3_LS$EiDateY) & is.na(ELSA_w3_LS$iintdaty)] <- 2
ELSA_ds_w3$living_status[which(ELSA_ds_w3$id %in% ids_deaths_w2)] <- 1
ELSA_ds_w3$living_status <- labelled(ELSA_ds_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
```

```{r importOPAL3, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$living_status <- car::recode(ELSA_m_ds_w3$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
living_status <- ELSA_ds_w3
save(living_status, file = paste0(datafolder, "/w3/living_status.RData"))
```



### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`

```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w4_ydeath','ELSA.elsa_eol_w4_archive_v1',
                         variables=list('EiDateY'), missings = TRUE)
ELSA_w4_ydeath <- opal.execute(o,'ELSA_w4_ydeath')
opal.assign.table.tibble(o, 'ELSA_w4_yinter','ELSA.wave_4_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w4_yinter <- opal.execute(o,'ELSA_w4_yinter')

ELSA_w4_ydeath <- ELSA_w4_ydeath[-which(ELSA_w4_ydeath$id==114235),]
```

```{r local4, echo=FALSE}
all_ids_w4 <- c(ELSA_w4_yinter$id,ELSA_w4_ydeath$id)

IDS_w4 <- tibble(id= c(all_ids_w4, ELSA_ds_w3$id[!(ELSA_ds_w3$id %in% all_ids_w4)]))

ELSA_w4_LS <- left_join(x = IDS_w4, y = ELSA_w4_ydeath, by = 'id')
ELSA_w4_LS <- left_join(x = ELSA_w4_LS, y = ELSA_w4_yinter, by = 'id')

vari <- ELSA_w4_LS$iintdaty
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w4_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

vari <- ELSA_w4_LS$EiDateY
kable(Continuous_summary(var = vari, missing_values = c(-9,-8,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w4_LS, aes(factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals death in previous waves into 1`

**R script:**

```{r harmo4}
ids_deaths_w3 <- c(ids_deaths_w2,ELSA_ds_w3$id[which(ELSA_ds_w3$living_status==1 & !ELSA_ds_w3$id %in% ids_deaths_w2)])


ELSA_ds_w4 <- tibble(id=ELSA_w4_LS$id)
ELSA_ds_w4$living_status <- NA
ELSA_ds_w4$living_status[!is.na(ELSA_w4_LS$iintdaty)] <- 0
ELSA_ds_w4$living_status[!is.na(ELSA_w4_LS$EiDateY)] <- 1
ELSA_ds_w4$living_status[is.na(ELSA_w4_LS$EiDateY) & is.na(ELSA_w4_LS$iintdaty)] <- 2
ELSA_ds_w4$living_status[which(ELSA_ds_w4$id %in% ids_deaths_w3)] <- 1
ELSA_ds_w4$living_status <- labelled(ELSA_ds_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
```

```{r importOPAL4, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$living_status <- car::recode(ELSA_m_ds_w4$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
living_status <- ELSA_ds_w4
save(living_status, file = paste0(datafolder, "/w4/living_status.RData"))
```






### Wave 5

#### Study-specific variable description


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_yinter','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w5_yinter <- opal.execute(o,'ELSA_w5_yinter')
```

```{r local5, echo=FALSE}

#dim(ELSA_w5_yinter)
#dim(ELSA_ds_w4)
#sum(ELSA_w5_yinter$id %in% ELSA_ds_w4$id) #10274  - 10132 = 142


IDS_w5 <- tibble(id = c(ELSA_w5_yinter$id , ELSA_ds_w4$id[!(ELSA_ds_w4$id %in% ELSA_w5_yinter$id)]))
ELSA_w5_LS <- left_join(x = IDS_w5, y = ELSA_w5_yinter, by = 'id')
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `death individuals in previous waves into 1`
* `individuals without date of interview either as was not dead in previous waves into 2`

**R script:**

```{r harmo5}
ids_deaths_w4 <- c(ids_deaths_w3,ELSA_ds_w4$id[which(ELSA_ds_w4$living_status==1 & !ELSA_ds_w4$id %in% ids_deaths_w3)])


ELSA_ds_w5 <- tibble(id=ELSA_w5_LS$id)
ELSA_ds_w5$living_status <- NA
ELSA_ds_w5$living_status[!is.na(ELSA_w5_LS$iintdaty)] <- 0
ELSA_ds_w5$living_status[is.na(ELSA_w5_LS$iintdaty)] <- 2
ELSA_ds_w5$living_status[which(ELSA_ds_w5$id %in% ids_deaths_w4)] <- 1
ELSA_ds_w5$living_status <- labelled(ELSA_ds_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
```

```{r importOPAL5, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$living_status <- car::recode(ELSA_m_ds_w5$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
living_status <- ELSA_ds_w5
save(living_status, file = paste0(datafolder, "/w5/living_status.RData"))
```


### Wave 6

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `EiDateY`
* Label: `Year of death`
* Type of variable: `countinous`
* Missings
    + `-9 = Refused/not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`

```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w6_ydeath','ELSA.elsa_endoflife_w6archive',
                         variables=list('EiDateY'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w6_yinter','ELSA.wave_6_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w6_ydeath <- opal.execute(o,'ELSA_w6_ydeath')
ELSA_w6_yinter <- opal.execute(o,'ELSA_w6_yinter')
```

```{r local6, echo=FALSE}
all_ids_w6 <- c(ELSA_w6_ydeath$id ,ELSA_w6_yinter$id)

#dim(ELSA_ds_w5)
#length(all_ids_w6)
#sum(all_ids_w6 %in% ELSA_ds_w5$id) #11292 - 8603 = 1215



IDS_W6 <- tibble(id=c(all_ids_w6, ELSA_ds_w5$id[!(ELSA_ds_w5$id %in% all_ids_w6)]))

ELSA_w6_LS <- left_join(x = IDS_W6, y = ELSA_w6_ydeath, by = 'id')
ELSA_w6_LS <- left_join(x = ELSA_w6_LS, y = ELSA_w6_yinter, by = 'id')

vari <- ELSA_w6_LS$iintdaty
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w6_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

vari <- ELSA_w6_LS$EiDateY
kable(Continuous_summary(var = vari, missing_values = c(-9,-8,-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w6_LS, aes(factor(EiDateY))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals with date of death into 1`
* `individuals without date of interview and death into 2`
* `individuals death in previous waves into 1`

**R script:**

```{r harmo6}
ids_deaths_w5 <- c(ids_deaths_w4,ELSA_ds_w5$id[which(ELSA_ds_w5$living_status==1 & !ELSA_ds_w5$id %in% ids_deaths_w4)])

ELSA_ds_w6 <- tibble(id=ELSA_w6_LS$id)
ELSA_ds_w6$living_status <- NA
ELSA_ds_w6$living_status[!is.na(ELSA_w6_LS$iintdaty)] <- 0
ELSA_ds_w6$living_status[!is.na(ELSA_w6_LS$EiDateY)] <- 1
ELSA_ds_w6$living_status[is.na(ELSA_w6_LS$EiDateY) & is.na(ELSA_w6_LS$iintdaty)] <- 2
ELSA_ds_w6$living_status[which(ELSA_ds_w6$id %in% ids_deaths_w5)] <- 1
ELSA_ds_w6$living_status <- labelled(ELSA_ds_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
```


```{r importOPAL6, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$living_status <- car::recode(ELSA_m_ds_w6$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
living_status <- ELSA_ds_w6
save(living_status, file = paste0(datafolder, "/w6/living_status.RData"))
```


### Wave 7

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview`
* Type of variable: `countinous`


```{r assign7, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w7_yinter','ELSA.wave_7_elsa_data',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w7_yinter <- opal.execute(o,'ELSA_w7_yinter')
```

```{r local7, echo=FALSE}


#dim(ELSA_w7_yinter)
#dim(ELSA_ds_w6)
#sum(ELSA_w7_yinter$id %in% ELSA_ds_w6$id) #9666 - 9157 = 509




IDS_w7 <- tibble(id = c(ELSA_w7_yinter$id , ELSA_ds_w6$id[!(ELSA_ds_w6$id %in% ELSA_w7_yinter$id)]))
ELSA_w7_LS <- left_join(x = IDS_w7, y = ELSA_w7_yinter, by = 'id')

vari <- ELSA_w7_LS$iintdaty
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w7_LS, aes(factor(iintdaty))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that have date of interview into 0`
* `individuals without date of interview into 2`
* `individuals death in previous waves into 1`

**R script:**

```{r harmo7}
ids_deaths_w6 <- c(ids_deaths_w5,ELSA_ds_w6$id[which(ELSA_ds_w6$living_status==1 & !ELSA_ds_w6$id %in% ids_deaths_w5)])

ELSA_ds_w7 <- tibble(id=ELSA_w7_LS$id)
ELSA_ds_w7$living_status <- NA
ELSA_ds_w7$living_status[!is.na(ELSA_w7_LS$iintdaty)] <- 0
ELSA_ds_w7$living_status[is.na(ELSA_w7_LS$iintdaty)] <- 2
ELSA_ds_w7$living_status[which(ELSA_ds_w7$id %in% ids_deaths_w6)] <- 1
ELSA_ds_w7$living_status <- labelled(ELSA_ds_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=FALSE}
vari <- ELSA_ds_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=FALSE}
```


```{r importOPAL7, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$living_status <- car::recode(ELSA_m_ds_w7$living_status, "c(991, 992, 993, 994, 995, 997, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
living_status <- ELSA_ds_w7
save(living_status, file = paste0(datafolder, "/w7/living_status.RData"))
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

# savingRD <- function(l.hds,vbl_name){
#   
#   for(index in seq_along(l.hds)){
#     assign(vbl_name,l.hds[[index]])
#     save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
#   }
# 
# }

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
At wave 2 there are 109 new individuals interviewed. 
At wave 3 there are 1729 new individuals interviewed. 
At wave 4 there are 2689 new individuals interviewed. At wave 5 there are 142 new individuals interviewed, 
and we don't have date of death, therefore we don't know the individuals that died between wave 4 and 5. 
At wave 6 there are 1215 new individuals interviewed. 
At wave 7 there are 509 new individuals interviewed.

The ELSA sample has been refreshed four times, at waves 3, 4, 6 and 7. The new individuals interviewed are either new participants or partners. For this reason, there are new individuals interviewed even at waves that there wasn't refreshment.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```