---
title: "Asthma"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_asthma`
* Variable label: `History of  Asthma`
* Variable description: `history of asthma diagnosis`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No asthma
1        | Asthma

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_asthma_age`
* Variable label: `Age first diagnosed asthma`
* Variable description: `The age first told had asthma diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Asthma"
ds_label_age <- "Age first diagnosed asthma"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1


#### Study-specific variable description

| **Name** | `q4033_asthma` |
|-|-|
| **Label** | `Asthma`|
| **Table name**  | `Courage_Finland_w1`|
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `NA`|
| **Description** |  |

```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q4033_asthma'), missings = T)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')

```

```{r local fin_w1, echo=F}

vbl <- COURAGE_fin_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_asthma` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo fin_w1}

# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$h_asthma <- car::recode(COURAGE_fin_w1$q4033_asthma, "2=0; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation fin_w1, echo=F}

AfterH <- table(COURAGE_ds_fin_w1$h_asthma, useNA = "ifany")
BeforeH <- table(COURAGE_fin_w1$q4033_asthma, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
rm(COURAGE_fin_w1)

```



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `q4033_asthma` |
|-|-|
| **Label** | `Asthma`|
| **Table name**  | `Courage_Poland_w1`|
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** |`8 = DK`|
| **Description** |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q4033_asthma'), missings = T)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- COURAGE_pol_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(COURAGE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_asthma` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `8 into 998`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$h_asthma <- car::recode(COURAGE_pol_w1$q4033_asthma, "2=0; 8=998; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(COURAGE_ds_pol_w1$h_asthma, useNA = "ifany")
BeforeH <- table(COURAGE_pol_w1$q4033_asthma, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->998")
kable(C)
rm(COURAGE_pol_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q4033_asthma_s1` |`age`|`yintw (pol_w1)`|`yintw (pol_w2)`|
|-|-|-|-|-|
| **Label** | `Asthma`|`age`|`year of interview`|`year of interview`|
| **Table name**  | `Courage_Poland_w2`|`age`|`yintw`|`yintw`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',variables=list('q4033_asthma_s1'), missings = T)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')
load(paste0(datafolder,"pol_w2/age.RData"))
COURAGE_pol_w2 <- left_join(COURAGE_pol_w2,age, by="id")
load(paste0(datafolder,"pol_w1/yintw.RData"))
COURAGE_pol_w2 <- left_join(COURAGE_pol_w2,yintw, by="id")
names(COURAGE_pol_w2)[4] <- "yintw_pol_w1"
rm(yintw)
load(paste0(datafolder,"pol_w2/yintw.RData"))
COURAGE_pol_w2 <- left_join(COURAGE_pol_w2,yintw, by="id")
names(COURAGE_pol_w2)[5] <- "yintw_pol_w2"
rm(yintw)

```

```{r local pol_w2, echo=F}

vbl <- COURAGE_pol_w2$q4033_asthma_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q4033_asthma_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(COURAGE_pol_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_pol_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(15,95)

vbl <- COURAGE_pol_w2$yintw_pol_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(yintw_pol_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$yintw_pol_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(yintw_pol_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_asthma` from the study-specific variable it has to be recoded as follows:

* `q4033_asthma == 2 and q4033_asthma_s1 == 2 into 0`
* `q4033_asthma == 1 or q4033_asthma_s1 == 1 into 1`
* `otherwise into 999`

To compute `h_asthma_age` from the study-specific variable it has to be recoded as follows:

* `if h_asthma == 1 in w2 and 0 in w1, h_asthma_age = age-(year of interview w2-year of interview w1)/2`
* `if h_asthma == 0, h_asthma_age = 996`
* `h_asthma == missing into 999`

**R script:**

```{r harmo pol_w2}

COURAGE_pol_w2 <- left_join(COURAGE_pol_w2, COURAGE_ds_pol_w1, by = "id")

# Categorical variable harmonization
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$h_asthma <- rep(999,length(COURAGE_pol_w2$id))
COURAGE_ds_pol_w2$h_asthma[which(COURAGE_pol_w2$q4033_asthma_s1 == 2 & ((is.na(COURAGE_pol_w2$h_asthma)) | COURAGE_pol_w2$h_asthma != 1))] <- 0
COURAGE_ds_pol_w2$h_asthma[which(COURAGE_pol_w2$q4033_asthma_s1 == 1 | ((!is.na(COURAGE_pol_w2$q4033_asthma_s1)) & COURAGE_pol_w2$h_asthma == 1))] <- 1

# Continuous variable harmonization
COURAGE_ds_pol_w2$h_asthma_age <- rep(999,length(COURAGE_pol_w2$id))
COURAGE_ds_pol_w2$h_asthma_age[which(COURAGE_ds_pol_w2$h_asthma == 0)] <- 996
COURAGE_ds_pol_w2$h_asthma_age[which(COURAGE_ds_pol_w2$h_asthma == 1 & COURAGE_pol_w2$h_asthma==0)] <- COURAGE_pol_w2$age[which(COURAGE_ds_pol_w2$h_asthma == 1 & COURAGE_pol_w2$h_asthma==0)]-(COURAGE_pol_w2$yintw_pol_w2[which(COURAGE_ds_pol_w2$h_asthma == 1 & COURAGE_pol_w2$h_asthma==0)]-COURAGE_pol_w2$yintw_pol_w1[which(COURAGE_ds_pol_w2$h_asthma == 1 & COURAGE_pol_w2$h_asthma==0)])/2

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- COURAGE_ds_pol_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_pol_w2$h_asthma_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w2, aes(h_asthma_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(15,90)

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(COURAGE_ds_pol_w2$h_asthma, useNA = "ifany")
X <- c(
  sum(COURAGE_pol_w2$q4033_asthma_s1 == 2 & ((is.na(COURAGE_pol_w2$h_asthma)) | COURAGE_pol_w2$h_asthma != 1),na.rm=T),
  sum(COURAGE_pol_w2$q4033_asthma_s1 == 1 | ((!is.na(COURAGE_pol_w2$q4033_asthma_s1)) & COURAGE_pol_w2$h_asthma == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(COURAGE_pol_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

cat("There are 45 individuals who answered in the previous wave that they were diagnosed to have asthma and in the second wave that they were not told to have it. We harmonize them as having it.")
kable(frq(COURAGE_pol_w2$h_asthma[which(COURAGE_pol_w2$q4033_asthma_s1==2)]), align = 'c')
#kable(COURAGE_pol_w2[which(COURAGE_pol_w2$id %in% COURAGE_pol_w2$id[which(COURAGE_pol_w2$q4033_asthma_s1==2 & COURAGE_pol_w2$h_asthma==1)]),], align = 'c')

```



## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q4033_asthma` |
|-|-|
| **Label** | `Asthma`|
| **Table name**  | `Courage_Spain_w1`|
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `8 = DK` |
| **Description** |  |

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q4033_asthma'), missings = T)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')

```

```{r local spain_w1, echo=F}

vbl <- COURAGE_spain_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_asthma` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `NA into 999`
* `8 into 998`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$h_asthma <- car::recode(COURAGE_spain_w1$q4033_asthma, "2=0; NA=999; 8 = 998")

```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w1, echo=F}

AfterH <- table(COURAGE_ds_spain_w1$h_asthma, useNA = "ifany")
BeforeH <- table(COURAGE_spain_w1$q4033_asthma, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->998")
kable(C)
rm(COURAGE_spain_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q4033_asthma_s1` |`age`|`yintw (spain_w1)`|`yintw (spain_w2)`|
|-|-|-|-|-|
| **Label** | `Asthma`|`age`|`year of interview`|`year of interview`|
| **Table name**  | `Courage_Spain_w2_1`|`age`|`yintw`|`yintw`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA`| `999 = Missing` |  |  |
| **Description** |  |  |  |  |

```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q4033_asthma_s1'), missings = T)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
load(paste0(datafolder,"spain_w2/age.RData"))
COURAGE_spain_w2 <- left_join(COURAGE_spain_w2,age, by="id")
load(paste0(datafolder,"spain_w1/yintw.RData"))
COURAGE_spain_w2 <- left_join(COURAGE_spain_w2,yintw, by="id")
names(COURAGE_spain_w2)[4] <- "yintw_spain_w1"
rm(yintw)
load(paste0(datafolder,"spain_w2/yintw.RData"))
COURAGE_spain_w2 <- left_join(COURAGE_spain_w2,yintw, by="id")
names(COURAGE_spain_w2)[5] <- "yintw_spain_w2"
rm(yintw)

```

```{r local spain_w2, echo=F}

vbl <- COURAGE_spain_w2$q4033_asthma_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q4033_asthma_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(COURAGE_spain_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_spain_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(20,115)

vbl <- COURAGE_spain_w2$yintw_spain_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(yintw_spain_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$yintw_spain_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(yintw_spain_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_asthma` from the study-specific variable it has to be recoded as follows:

* `q4033_asthma == 2 and q4033_asthma_s1 == 2 into 0`
* `q4033_asthma == 1 or q4033_asthma_s1 == 1 into 1`
* `otherwise into 999`

To compute `h_asthma_age` from the study-specific variable it has to be recoded as follows:

* `if h_asthma == 1 in w2 and 0 in w1, h_asthma_age = age-(year of interview w2-year of interview w1)/2`
* `if h_asthma == 0, h_asthma_age = 996`
* `h_asthma == missing into 999`

**R script:**

```{r harmo spain_w2}

# Categorical variable harmonization
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)

COURAGE_spain_w2 <- left_join(COURAGE_spain_w2, COURAGE_ds_spain_w1, by = "id")
COURAGE_ds_spain_w2$h_asthma <- rep(999,length(COURAGE_spain_w2$id))
COURAGE_ds_spain_w2$h_asthma[which(COURAGE_spain_w2$q4033_asthma_s1 == 2 & ((is.na(COURAGE_spain_w2$h_asthma)) | COURAGE_spain_w2$h_asthma != 1))] <- 0
COURAGE_ds_spain_w2$h_asthma[which(COURAGE_spain_w2$q4033_asthma_s1 == 1 | ((!is.na(COURAGE_spain_w2$q4033_asthma_s1)) & COURAGE_spain_w2$h_asthma == 1))] <- 1

# Continuous variable harmonization
COURAGE_ds_spain_w2$h_asthma_age <- rep(999,length(COURAGE_spain_w2$id))
COURAGE_ds_spain_w2$h_asthma_age[which(COURAGE_ds_spain_w2$h_asthma == 0)] <- 996
COURAGE_ds_spain_w2$h_asthma_age[which(COURAGE_ds_spain_w2$h_asthma == 1 & COURAGE_spain_w2$h_asthma==0)] <- COURAGE_spain_w2$age[which(COURAGE_ds_spain_w2$h_asthma == 1 & COURAGE_spain_w2$h_asthma==0)]-(COURAGE_spain_w2$yintw_spain_w2[which(COURAGE_ds_spain_w2$h_asthma == 1 & COURAGE_spain_w2$h_asthma==0)]-COURAGE_spain_w2$yintw_spain_w1[which(COURAGE_ds_spain_w2$h_asthma == 1 & COURAGE_spain_w2$h_asthma==0)])/2


```


#### Statistics of the new harmonized variable

```{r descript spain_w2, echo=F}

vbl <- COURAGE_ds_spain_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_spain_w2$h_asthma_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(h_asthma_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,90)

```


#### Validation

```{r crosstabulation spain_w2, echo=F,results='asis'}

AfterH <- table(COURAGE_ds_spain_w2$h_asthma, useNA = "ifany")
X <- c(
  sum(COURAGE_spain_w2$q4033_asthma_s1 == 2 & ((is.na(COURAGE_spain_w2$h_asthma)) | COURAGE_spain_w2$h_asthma != 1),na.rm=T),
  sum(COURAGE_spain_w2$q4033_asthma_s1 == 1 | ((!is.na(COURAGE_spain_w2$q4033_asthma_s1)) & COURAGE_spain_w2$h_asthma == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(COURAGE_spain_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

cat("There is one individual who answered in the previous wave that was diagnosed to have asthma and in the second wave that was not told to have it. We harmonize as having it.")
kable(frq(COURAGE_spain_w2$h_asthma[which(COURAGE_spain_w2$q4033_asthma_s1==2)]), align = 'c')

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

lb.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, spain_w1 = COURAGE_ds_spain_w1)
lf.hds <- list(pol_w2 = COURAGE_ds_pol_w2, spain_w2 = COURAGE_ds_spain_w2)

for(name in names(lb.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

l.hds <- c(lb.hds,lf.hds)
ln.hds <- c("fin_w1","pol_w1","pol_w2","spain_w1","spain_w2")

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[["fin_w1"]][[2]]), length(l.hds[["pol_w1"]][[2]]) , length(l.hds[["pol_w2"]][[2]]), length(l.hds[["spain_w1"]][[2]]), length(l.hds[["spain_w2"]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Poland_W2", "Spain_W1", "Spain_W2")
kable(t.hds)

```



# Quality estimation

We assume that if an individual answers it has asthma in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of the corresponding validations.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_asthma <- l.hds[[index]]
  save(h_asthma, file = paste0(datafolder,names(l.hds)[index],"/h_asthma.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





