---
title: "Respiratory diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_respiratory`
* Variable label: `Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`
* Variable description: `The participant has one or more of the following respiratory diseases: respiratory, chronic bronchitis, emphysema, chronic pulmonary disease, chronic obstructive pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no respiratory disease
1        | yes, respiratory disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1


#### Study-specific variable description

| **Name** | `q4033_asthma` |`q4025_lungs`|
|-|-|-|
| **Label** | `Asthma`|`Lung disease`|
| **Table name**  | `Courage_Finland_w1`| `Courage_Finland_w1`|
| **Categories** | `1 = Yes; 2 = No` | `1 = Yes; 2 = No` |
| **Missings** | `NA`|`NA`|
| **Description** |  |  |

```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q4033_asthma','q4025_lungs'), missings = T)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')

```

```{r local fin_w1, echo=F}

vbl <- COURAGE_fin_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q4025_lungs
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_fin_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q4025_lungs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `NA into 999`


**R script:**

```{r harmo fin_w1}

COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$h_respiratory <- rep(999,length(COURAGE_fin_w1$id))
COURAGE_ds_fin_w1$h_respiratory[which(COURAGE_fin_w1$q4033_asthma == 2 & COURAGE_fin_w1$q4025_lungs == 2)] <- 0
COURAGE_ds_fin_w1$h_respiratory[which(COURAGE_fin_w1$q4033_asthma == 1 | COURAGE_fin_w1$q4025_lungs == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation fin_w1, echo=F}

AfterH <- table(COURAGE_ds_fin_w1$h_respiratory, useNA = "ifany")
X <- c(
  sum(COURAGE_fin_w1$q4033_asthma == 2 & COURAGE_fin_w1$q4025_lungs == 2,na.rm=T),
  sum(COURAGE_fin_w1$q4033_asthma == 1 | COURAGE_fin_w1$q4025_lungs == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(COURAGE_fin_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","otherwise->999")
kable(C)
rm(COURAGE_fin_w1)

```



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `q4033_asthma` |`q4025_lungs`|
|-|-|-|
| **Label** | `Asthma`|`Lung disease`|
| **Table name**  | `Courage_Poland_w1`| `Courage_Poland_w1`|
| **Categories** | `1 = Yes; 2 = No` |`1 = Yes; 2 = No` |
| **Missings** | `8 = DK`<br/>`NA`|  |
| **Description** |  |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q4033_asthma','q4025_lungs'), missings = T)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- COURAGE_pol_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(COURAGE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q4025_lungs
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q4025_lungs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `otherwise into 999`
* `8 into 998`

**R script:**

```{r harmo pol_w1}

COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$h_respiratory <- rep(999,length(COURAGE_pol_w1$id))
COURAGE_ds_pol_w1$h_respiratory[which(COURAGE_pol_w1$q4033_asthma == 2 & COURAGE_pol_w1$q4025_lungs == 2)] <- 0
COURAGE_ds_pol_w1$h_respiratory[which(COURAGE_pol_w1$q4033_asthma == 8 & (COURAGE_pol_w1$q4025_lungs != 1 | is.na(COURAGE_pol_w1$q4025_lungs)))] <- 998
COURAGE_ds_pol_w1$h_respiratory[which(COURAGE_pol_w1$q4033_asthma == 1 | COURAGE_pol_w1$q4025_lungs == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(COURAGE_ds_pol_w1$h_respiratory, useNA = "ifany")
X <- c(
  sum(COURAGE_pol_w1$q4033_asthma == 2 & COURAGE_pol_w1$q4025_lungs == 2,na.rm=T),
  sum(COURAGE_pol_w1$q4033_asthma == 1 | COURAGE_pol_w1$q4025_lungs == 1,na.rm=T),
  sum(COURAGE_pol_w1$q4033_asthma == 8 & (COURAGE_pol_w1$q4025_lungs != 1 | is.na(COURAGE_pol_w1$q4025_lungs)),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q4033_asthma_s1` |`q4025_lungs_s1`|
|-|-|-|
| **Label** | `Asthma`|`Lung disease`|
| **Table name**  | `Courage_Poland_w2`| `Courage_Poland_w2`|
| **Categories** | `1 = Yes; 2 = No` |`1 = Yes; 2 = No`|
| **Missings** | `NA`| `NA` |
| **Description** |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',variables=list('q4033_asthma_s1','q4025_lungs_s1'), missings = T)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')

```

```{r local pol_w2, echo=F}

vbl <- COURAGE_pol_w2$q4033_asthma_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q4033_asthma_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$q4025_lungs_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q4025_lungs_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 (across waves) into 0`
* `some 1 (across waves) into 1`
* `otherwise into 999`

**R script:**

```{r harmo pol_w2}

COURAGE_pol_w2 <- left_join(COURAGE_pol_w2, COURAGE_ds_pol_w1, by = "id")

COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$h_respiratory <- rep(999,length(COURAGE_pol_w2$id))
COURAGE_ds_pol_w2$h_respiratory[which((is.na(COURAGE_pol_w2$h_respiratory) | COURAGE_pol_w2$h_respiratory != 1) & COURAGE_pol_w2$q4033_asthma_s1 == 2 & COURAGE_pol_w2$q4025_lungs_s1 == 2)] <- 0
COURAGE_ds_pol_w2$h_respiratory[which((!(is.na(COURAGE_pol_w2$q4033_asthma_s1) & is.na(COURAGE_pol_w2$q4025_lungs_s1)) & COURAGE_pol_w2$h_respiratory == 1) | COURAGE_pol_w2$q4033_asthma_s1 == 1 | COURAGE_pol_w2$q4025_lungs_s1 == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- COURAGE_ds_pol_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(COURAGE_ds_pol_w2$h_respiratory, useNA = "ifany")
X <- c(
  sum((is.na(COURAGE_pol_w2$h_respiratory) | COURAGE_pol_w2$h_respiratory != 1) & COURAGE_pol_w2$q4033_asthma_s1 == 2 & COURAGE_pol_w2$q4025_lungs_s1 == 2,na.rm=T),
  sum((!(is.na(COURAGE_pol_w2$q4033_asthma_s1) & is.na(COURAGE_pol_w2$q4025_lungs_s1)) & COURAGE_pol_w2$h_respiratory == 1) | COURAGE_pol_w2$q4033_asthma_s1 == 1 | COURAGE_pol_w2$q4025_lungs_s1 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(COURAGE_pol_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

COURAGE_pol_w2<-left_join(COURAGE_pol_w2,COURAGE_pol_w1,by="id")

cat("There are 45 individuals who answered in the previous wave that they were diagnosed to have asthma and 102 who answered to have diagnosed lung diseases, and that in the second wave they were not told to have them. We harmonize them as having respiratory disorders")
kable(frq(COURAGE_pol_w2$q4033_asthma[COURAGE_pol_w2$q4033_asthma_s1==2]), align = 'c')
kable(frq(COURAGE_pol_w2$q4025_lungs[COURAGE_pol_w2$q4025_lungs_s1==2]), align = 'c')

```



## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q4033_asthma` |`q4025_lungs`|
|-|-|-|
| **Label** | `Asthma`|`Lung disease`|
| **Table name**  | `Courage_Spain_w1`| `Courage_Spain_w1`|
| **Categories** | `1 = Yes; 2 = No` |`1 = Yes; 2 = No` |
| **Missings** | `8 = DK`<br/>`NA`| `8 = DK` |
| **Description** |  |  |


```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q4033_asthma','q4025_lungs'), missings = T)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')

```

```{r local spain_w1, echo=F}

vbl <- COURAGE_spain_w1$q4033_asthma
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q4033_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q4025_lungs
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q4025_lungs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `NA into 999`
* `8 into 998`

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$h_respiratory <- rep(999,length(COURAGE_spain_w1$id))
COURAGE_ds_spain_w1$h_respiratory[which(COURAGE_spain_w1$q4033_asthma == 2 & COURAGE_spain_w1$q4025_lungs == 2)] <- 0
COURAGE_ds_spain_w1$h_respiratory[which((COURAGE_spain_w1$q4033_asthma == 8 & (COURAGE_spain_w1$q4025_lungs != 1 | is.na(COURAGE_pol_w1$q4025_lungs))) | (COURAGE_spain_w1$q4025_lungs == 8 & (COURAGE_spain_w1$q4033_asthma != 1 | is.na(COURAGE_pol_w1$q4033_asthma))))] <- 998
COURAGE_ds_spain_w1$h_respiratory[which(COURAGE_spain_w1$q4033_asthma == 1 | COURAGE_spain_w1$q4025_lungs == 1)] <- 1


```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w1, echo=F}

AfterH <- table(COURAGE_ds_spain_w1$h_respiratory, useNA = "ifany")
X <- c(
  sum(COURAGE_spain_w1$q4033_asthma == 2 & COURAGE_spain_w1$q4025_lungs == 2,na.rm=T),
  sum(COURAGE_spain_w1$q4033_asthma == 1 | COURAGE_spain_w1$q4025_lungs == 1,na.rm=T),
  sum((COURAGE_spain_w1$q4033_asthma == 8 & (COURAGE_spain_w1$q4025_lungs != 1 | is.na(COURAGE_pol_w1$q4025_lungs))) | (COURAGE_spain_w1$q4025_lungs == 8 & (COURAGE_spain_w1$q4033_asthma != 1 | is.na(COURAGE_pol_w1$q4033_asthma))),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q4033_asthma_s1` |`q4025_lungs_s1`|
|-|-|-|
| **Label** | `Asthma`|`Lung disease`|
| **Table name**  | `Courage_Spain_w2_1`| `Courage_Spain_w2_1`|
| **Categories** | `1 = Yes; 2 = No` |`1 = Yes; 2 = No`|
| **Missings** | `NA`| `8 = DK`<br/>`NA` |
| **Description** |  |  |

```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q4033_asthma_s1','q4025_lungs_s1'), missings = T)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')

```

```{r local spain_w2, echo=F}

vbl <- COURAGE_spain_w2$q4033_asthma_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q4033_asthma_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$q4025_lungs_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q4025_lungs_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 (across waves) into 0`
* `some 1 (across waves) into 1`
* `8 into 998`
* `otherwise into 999`

**R script:**

```{r harmo spain_w2}

COURAGE_spain_w2 <- left_join(COURAGE_spain_w2, COURAGE_ds_spain_w1, by = "id")

COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$h_respiratory <- rep(999,length(COURAGE_spain_w2$id))
COURAGE_ds_spain_w2$h_respiratory[which((is.na(COURAGE_spain_w2$h_respiratory) | COURAGE_spain_w2$h_respiratory != 1) & COURAGE_spain_w2$q4033_asthma_s1 == 2 & COURAGE_spain_w2$q4025_lungs_s1 == 2)] <- 0
COURAGE_ds_spain_w2$h_respiratory[which((!(is.na(COURAGE_spain_w2$q4033_asthma_s1) & is.na(COURAGE_spain_w2$q4025_lungs_s1)) & COURAGE_spain_w2$h_respiratory == 1) | COURAGE_spain_w2$q4033_asthma_s1 == 1 | COURAGE_spain_w2$q4025_lungs_s1 == 1)] <- 1
COURAGE_ds_spain_w2$h_respiratory[which((is.na(COURAGE_spain_w2$h_respiratory) | COURAGE_spain_w2$h_respiratory != 1) & (COURAGE_spain_w2$q4033_asthma_s1 == 2 | is.na(COURAGE_spain_w2$q4033_asthma_s1)) & COURAGE_spain_w2$q4025_lungs_s1 == 8)] <- 998



```


#### Statistics of the new harmonized variable

```{r descript spain_w2, echo=F}

vbl <- COURAGE_ds_spain_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w2, echo=F, results='asis'}

AfterH <- table(COURAGE_ds_spain_w2$h_respiratory, useNA = "ifany")
X <- c(
  sum((is.na(COURAGE_spain_w2$h_respiratory) | COURAGE_spain_w2$h_respiratory != 1) & COURAGE_spain_w2$q4033_asthma_s1 == 2 & COURAGE_spain_w2$q4025_lungs_s1 == 2,na.rm=T),
  sum((!(is.na(COURAGE_spain_w2$q4033_asthma_s1) & is.na(COURAGE_spain_w2$q4025_lungs_s1)) & COURAGE_spain_w2$h_respiratory == 1) | COURAGE_spain_w2$q4033_asthma_s1 == 1 | COURAGE_spain_w2$q4025_lungs_s1 == 1,na.rm=T),
  sum((is.na(COURAGE_spain_w2$h_respiratory) | COURAGE_spain_w2$h_respiratory != 1) & (COURAGE_spain_w2$q4033_asthma_s1 == 2 | is.na(COURAGE_spain_w2$q4033_asthma_s1)) & COURAGE_spain_w2$q4025_lungs_s1 == 8,na.rm=T)
)
BeforeH <- c(X[1:3],length(COURAGE_spain_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","8->998","NA->999")
kable(C)

COURAGE_spain_w2<-left_join(COURAGE_spain_w2,COURAGE_spain_w1,by="id")

cat("There is 1 individual who answered in the previous wave that they were diagnosed to have asthma and 1 who answered to have diagnosed lung diseases, and that in the second wave they were not told to have them. We harmonize them as having respiratory disorders")
kable(frq(COURAGE_spain_w2$q4033_asthma[COURAGE_spain_w2$q4033_asthma_s1==2]), align = 'c')
kable(frq(COURAGE_spain_w2$q4025_lungs[COURAGE_spain_w2$q4025_lungs_s1==2]), align = 'c')
```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}


l.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, pol_w2 = COURAGE_ds_pol_w2, spain_w1 = COURAGE_ds_spain_w1, spain_w2 = COURAGE_ds_spain_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("COURAGE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Poland_W2", "Spain_W1", "Spain_W2")
kable(t.hds)

```



# Quality estimation

We assume that if an individual answers it has respiratory disorders in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of the corresponding validations.
The harmonized variable contains information about: asthma, emphysema, bronchitis and COPD.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_respiratory <- l.hds[[index]]
  save(h_respiratory, file = paste0(datafolder,names(l.hds)[index],"/h_respiratory.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





