---
title: "Close spouse"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/close_spouseDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/close_spouseDS.R')
```

<!-- ########################################################## --> 

# Data process


## Australia

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description

| **Name ** |`CONFW3`|`CONRELW3`|`OTCNFW3`|`OTCNRLW3`|
|-|-|-|-|-|
| **Label** |`CONFIDANT`|`RELATIONSHIP WITH CONFIDANT`|`SECOND CONFIDANT`|`RELATIONSHIP WITH CONFIDANT`|
| **Table name** |`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|
| **Categories** |`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|
| **Missings** |  |  |  |  |
| **Description** |  |  |  |  |


```{r assign3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3_close_spouse','ALSA.ALSA-Wave3',variables=list('CONFW3','CONRELW3','OTCNFW3','OTCNRLW3'), missings = TRUE)
ALSA_w3_close_spouse <- opal.execute(o,'ALSA_w3_close_spouse')

```

```{r local3, echo=F}

Categorical_summary(var = ALSA_w3_close_spouse$CONFW3, missing_values = NA)
ggplot(ALSA_w3_close_spouse, aes(x=factor(CONFW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is there any one special person that you feel very close") + ylab("Frequency")
Categorical_summary(var = ALSA_w3_close_spouse$CONRELW3, missing_values = NA)
ggplot(ALSA_w3_close_spouse, aes(x=factor(CONRELW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship with that person") + ylab("Frequency")
Categorical_summary(var = ALSA_w3_close_spouse$OTCNFW3, missing_values = NA)
ggplot(ALSA_w3_close_spouse, aes(x=factor(OTCNFW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Again, is there any OTHER special person that you feel very close") + ylab("Frequency")
Categorical_summary(var = ALSA_w3_close_spouse$OTCNRLW3, missing_values = NA)
ggplot(ALSA_w3_close_spouse, aes(x=factor(OTCNRLW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship with that person") + ylab("Frequency")

```


#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if (CONFW3 = 1 AND CONRELW3 = 1) OR (OTCNFW3 = 1 AND OTCNRLW3 = 1) into 1`
* `else if [ CONFW3 = 2 OR (CONFW3 = 1 AND CONRELW3 NE 1 AND OTCNFW3 = 1 AND OTCNRLW3 NE 1) OR `
  `(CONFW3 = 1 AND CONRELW3 NE 1 AND OTCNFW3 = 2) ] into 0`
* `NA into 999`

**R script:**

```{r harmo3}

ALSA_ds_w3 <- tibble(id=ALSA_w3_close_spouse$id)

ALSA_w3_close_spouse$CONFW3 <- car::recode(as.vector(ALSA_w3_close_spouse$CONFW3), "NA='-999'")
ALSA_w3_close_spouse$CONRELW3 <- car::recode(as.vector(ALSA_w3_close_spouse$CONRELW3), "NA='-999'")
ALSA_w3_close_spouse$OTCNFW3 <- car::recode(as.vector(ALSA_w3_close_spouse$OTCNFW3), "NA='-999'")
ALSA_w3_close_spouse$OTCNRLW3 <- car::recode(as.vector(ALSA_w3_close_spouse$OTCNRLW3), "NA='-999'")

ALSA_ds_w3$close_spouse <- c(NA)  # I think it is required
for(i in 1:dim(ALSA_w3_close_spouse)[1]){
  if( (ALSA_w3_close_spouse$CONFW3[i] == 1 & ALSA_w3_close_spouse$CONRELW3[i] == 1) |
      (ALSA_w3_close_spouse$OTCNFW3[i] == 1 & ALSA_w3_close_spouse$OTCNRLW3[i] == 1) ) { 
    ALSA_ds_w3$close_spouse[i] = 1 }
  
  else if( ALSA_w3_close_spouse$CONFW3[i] == 2 | 
           ( ALSA_w3_close_spouse$CONFW3[i] == 1 & !(ALSA_w3_close_spouse$CONRELW3[i] == 1) &
             ALSA_w3_close_spouse$OTCNFW3[i] == 1 & !(ALSA_w3_close_spouse$OTCNRLW3[i] == 1) ) |
           ( ALSA_w3_close_spouse$CONFW3[i] == 1 & !(ALSA_w3_close_spouse$CONRELW3[i] == 1) & 
             ALSA_w3_close_spouse$OTCNFW3[i] == 2) ) {
    ALSA_ds_w3$close_spouse[i] = 0 }
}
ALSA_ds_w3$close_spouse <- car::recode(as.vector(ALSA_ds_w3$close_spouse), "NA='999'")
ALSA_ds_w3$close_spouse <- labelled(ALSA_ds_w3$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript3, echo=F}

Categorical_summary(var = ALSA_ds_w3$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")

```

#### Validation

```{r crosstabulation3, echo=F}

```


### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

#### Study-specific variable description

| **Name ** |`CONFW6`|`CONRELW6`|`OTCNFW6`|`OTCNRLW6`|
|-|-|-|-|-|
| **Label** |`have confidant`|`relationship of confidant`|`other special person`|`relationship of other special person`|
| **Table name** |`ALSA-Wave6`|`ALSA-Wave6`|`ALSA-Wave6`|`ALSA-Wave6`|
| **Categories** |`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|
| **Missings** |`0 = no answer`|`0 = no answer`|`0 = no answer`|`0 = no answer`|
| **Description** |  |  |  |  |

```{r assign6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6_close_spouse','ALSA.ALSA-Wave6',variables=list('CONFW6','CONRELW6','OTCNFW6','OTCNRLW6'), missings = TRUE)
ALSA_w6_close_spouse <- opal.execute(o,'ALSA_w6_close_spouse')

```

```{r local6, echo=F}

Categorical_summary(var = ALSA_w6_close_spouse$CONFW6, missing_values = NA)
ggplot(ALSA_w6_close_spouse, aes(x=factor(CONFW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w6_close_spouse$CONRELW6, missing_values = NA)
ggplot(ALSA_w6_close_spouse, aes(x=factor(CONRELW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of confidant") + ylab("Frequency")
Categorical_summary(var = ALSA_w6_close_spouse$OTCNFW6, missing_values = NA)
ggplot(ALSA_w6_close_spouse, aes(x=factor(OTCNFW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have other special person?") + ylab("Frequency")
Categorical_summary(var = ALSA_w6_close_spouse$OTCNRLW6, missing_values = NA)
ggplot(ALSA_w6_close_spouse, aes(x=factor(OTCNRLW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of other special person") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if (CONFW6 = 1 AND CONRELW6 = 1) OR (OTCNFW6 = 1 AND OTCNRLW6 = 1) into 1`
* `else if [CONFW6 = 2 OR (CONFW6 = 1 AND CONRELW6 NE 1 AND OTCNFW6 = 1 AND OTCNRLW6 NE 1) OR `
  `(CONFW6 = 1 AND CONRELW6 NE 1 AND OTCNFW6 = 2) ] into 0`
* `else if any equals 0 into 995`
* `NA into 999`

**R script:**

```{r harmo6}

ALSA_ds_w6 <- tibble(id=ALSA_w6_close_spouse$id)

ALSA_w6_close_spouse$CONFW6 <- car::recode(as.vector(ALSA_w6_close_spouse$CONFW6), "NA='-999'")
ALSA_w6_close_spouse$CONRELW6 <- car::recode(as.vector(ALSA_w6_close_spouse$CONRELW6), "NA='-999'")
ALSA_w6_close_spouse$OTCNFW6 <- car::recode(as.vector(ALSA_w6_close_spouse$OTCNFW6), "NA='-999'")
ALSA_w6_close_spouse$OTCNRLW6 <- car::recode(as.vector(ALSA_w6_close_spouse$OTCNRLW6), "NA='-999'")

ALSA_ds_w6$close_spouse <- c(NA)  # I think it is required
for(i in 1:dim(ALSA_w6_close_spouse)[1]){
  if( (ALSA_w6_close_spouse$CONFW6[i] == 1 & ALSA_w6_close_spouse$CONRELW6[i] == 1) |
      (ALSA_w6_close_spouse$OTCNFW6[i] == 1 & ALSA_w6_close_spouse$OTCNRLW6[i] == 1) ) { 
    ALSA_ds_w6$close_spouse[i] = 1 }
  
  else if( ALSA_w6_close_spouse$CONFW6[i] == 2 | 
           ( ALSA_w6_close_spouse$CONFW6[i] == 1 & ALSA_w6_close_spouse$CONRELW6[i] > 1 &
             ALSA_w6_close_spouse$OTCNFW6[i] == 1 & ALSA_w6_close_spouse$OTCNRLW6[i] > 1 ) |
           ( ALSA_w6_close_spouse$CONFW6[i] == 1 & ALSA_w6_close_spouse$CONRELW6[i] > 1 &
             ALSA_w6_close_spouse$OTCNFW6[i] == 2 ) ) {
    ALSA_ds_w6$close_spouse[i] = 0 }
  
  else if( ALSA_w6_close_spouse$CONFW6[i] == 0 | ALSA_w6_close_spouse$OTCNFW6[i] == 0 | 
           ALSA_w6_close_spouse$CONRELW6[i] == 0 | ALSA_w6_close_spouse$OTCNRLW6[i] == 0 ) {
    ALSA_ds_w6$close_spouse[i] = 995 }
}
ALSA_ds_w6$close_spouse <- car::recode(as.vector(ALSA_ds_w6$close_spouse), "NA='999'")
ALSA_ds_w6$close_spouse <- labelled(ALSA_ds_w6$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript6, echo=F}

Categorical_summary(var = ALSA_ds_w6$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")

```

#### Validation
```{r crosstabulation6, echo=F}

```

### Wave 7

#### Study-specific variable description



| **Name ** |`confw7`|`conrelw7`|`otcnfw7`|`otcnrlw7`|
|-|-|-|-|-|
| **Label** |`have confidant`|`relationship of confidant`|`other special person`|`relationship of other special person`|
| **Table name** |`ALSA-Wave7`|`ALSA-Wave7`|`ALSA-Wave7`|`ALSA-Wave7`|
| **Categories** |`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|`1 = yes`<br/>`2 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|
| **Missings** |`0 = no answer`<br/>`99 = Missing`|`0 = no answer`<br/>`99 = Missing`|`0 = no answer`<br/>`99 = Missing`|`0 = no answer`<br/>`99 = No other person`|
| **Description** |  |  |  |  |

```{r assign7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7_close_spouse','ALSA.ALSA-Wave7',variables=list('confw7','conrelw7','otcnfw7','otcnrlw7'), missings = TRUE)
ALSA_w7_close_spouse <- opal.execute(o,'ALSA_w7_close_spouse')

```

```{r local7, echo=F}

Categorical_summary(var = ALSA_w7_close_spouse$confw7, missing_values = NA)
ggplot(ALSA_w7_close_spouse, aes(x=factor(confw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w7_close_spouse$conrelw7, missing_values = NA)
ggplot(ALSA_w7_close_spouse, aes(x=factor(conrelw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of confidant") + ylab("Frequency")
Categorical_summary(var = ALSA_w7_close_spouse$otcnfw7, missing_values = NA)
ggplot(ALSA_w7_close_spouse, aes(x=factor(otcnfw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have other special person?") + ylab("Frequency")
Categorical_summary(var = ALSA_w7_close_spouse$otcnrlw7, missing_values = NA)
ggplot(ALSA_w7_close_spouse, aes(x=factor(otcnrlw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of other special person") + ylab("Frequency")

```



#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if (confw7 = 1 AND conrelw7 = 1) OR (otcnfw7 = 1 AND otcnrlw7 = 1) into 1`
* `else if [confw7 = 2 OR (confw7 = 1 AND conrelw7 NE 1 AND otcnfw7 = 1 AND otcnrlw7 NE 1) OR `
  `(confw7 = 1 AND conrelw7 NE 1 AND (otcnfw7 = 2 OR otcnrlw7 = 99) ] into 0`
* `else if any equals 0 into 995`
* `else if any (except otcnrlw7) equals 99 into 999`
* `NA into 999`

**R script:**

```{r harmo7}

ALSA_ds_w7 <- tibble(id=ALSA_w7_close_spouse$id)

ALSA_w7_close_spouse$confw7 <- car::recode(as.vector(ALSA_w7_close_spouse$confw7), "NA='-999'")
ALSA_w7_close_spouse$conrelw7 <- car::recode(as.vector(ALSA_w7_close_spouse$conrelw7), "NA='-999'")
ALSA_w7_close_spouse$otcnfw7 <- car::recode(as.vector(ALSA_w7_close_spouse$otcnfw7), "NA='-999'")
ALSA_w7_close_spouse$otcnrlw7 <- car::recode(as.vector(ALSA_w7_close_spouse$otcnrlw7), "NA='-999'")

ALSA_ds_w7$close_spouse <- c(NA)  # I think it is required
for(i in 1:dim(ALSA_w7_close_spouse)[1]){
  if( (ALSA_w7_close_spouse$confw7[i] == 1 & ALSA_w7_close_spouse$conrelw7[i] == 1) |
      (ALSA_w7_close_spouse$otcnfw7[i] == 1 & ALSA_w7_close_spouse$otcnrlw7[i] == 1) ) { 
    ALSA_ds_w7$close_spouse[i] = 1 }
  
  else if( ALSA_w7_close_spouse$confw7[i] == 2 | 
           ( ALSA_w7_close_spouse$confw7[i] == 1 & ALSA_w7_close_spouse$conrelw7[i] > 1 &
             ALSA_w7_close_spouse$otcnfw7[i] == 1 & ALSA_w7_close_spouse$otcnrlw7[i] > 1 ) |
           ( ALSA_w7_close_spouse$confw7[i] == 1 & ALSA_w7_close_spouse$conrelw7[i] > 1 &
             ( ALSA_w7_close_spouse$otcnfw7[i] == 2 | ALSA_w7_close_spouse$otcnfw7[i] == 99 ) ) ) {
    ALSA_ds_w7$close_spouse[i] = 0 }
  
  else if( ALSA_w7_close_spouse$confw7[i] == 0 | ALSA_w7_close_spouse$otcnfw7[i] == 0 | 
           ALSA_w7_close_spouse$conrelw7[i] == 0 | ALSA_w7_close_spouse$otcnrlw7[i] == 0 ) {
    ALSA_ds_w7$close_spouse[i] = 995 }
  
  else if( ALSA_w7_close_spouse$confw7[i] == 99 | ALSA_w7_close_spouse$otcnfw7[i] == 99 | 
           ALSA_w7_close_spouse$conrelw7[i] == 99 ) {
    ALSA_ds_w7$close_spouse[i] = 999 }
}
ALSA_ds_w7$close_spouse <- car::recode(as.vector(ALSA_ds_w7$close_spouse), "NA='999'")
ALSA_ds_w7$close_spouse <- labelled(ALSA_ds_w7$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript7, echo=F}

Categorical_summary(var = ALSA_ds_w7$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")

```

#### Validation
```{r crosstabulation7, echo=F}

```



### Wave 8

Not found.

### Wave 9

Not found.

### Wave 10

Not found.

### Wave 11

#### Study-specific variable description



| **Name ** |`CONFW11`|`CONRELW11`|`OTCNFW11`|`OTCNRLW11`|
|-|-|-|-|-|
| **Label** |`have confidant`|`relationship of confidant`|`other confidant`|`relationship of other confidant`|
| **Table name** |`ALSA-Wave11`|`ALSA-Wave11`|`ALSA-Wave11`|`ALSA-Wave11`|
| **Categories** |`1 = yes`<br/>`0 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|`1 = yes`<br/>`0 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|
| **Missings** |  |  |  |  |
| **Description** |  |  |  |  |

```{r assign11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11_close_spouse','ALSA.ALSA-Wave11', variables=list('CONFW11','CONRELW11','OTCNFW11','OTCNRLW11'), missings = TRUE)
ALSA_w11_close_spouse <- opal.execute(o,'ALSA_w11_close_spouse')

```

```{r local11, echo=F}

Categorical_summary(var = ALSA_w11_close_spouse$CONFW11, missing_values = NA)
ggplot(ALSA_w11_close_spouse, aes(x=factor(CONFW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w11_close_spouse$CONRELW11, missing_values = NA)
ggplot(ALSA_w11_close_spouse, aes(x=factor(CONRELW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of confidant") + ylab("Frequency")
Categorical_summary(var = ALSA_w11_close_spouse$OTCNFW11, missing_values = NA)
ggplot(ALSA_w11_close_spouse, aes(x=factor(OTCNFW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have other confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w11_close_spouse$OTCNRLW11, missing_values = NA)
ggplot(ALSA_w11_close_spouse, aes(x=factor(OTCNRLW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of other confidant") + ylab("Frequency")

```


#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if (CONFW11 = 1 AND CONRELW11 = 1) OR (OTCNFW11 = 1 AND OTCNRLW11 = 1) into 1`
* `else if [ CONFW11 = 0 OR (CONFW11 = 1 AND CONRELW11 NE 1 AND OTCNFW11 = 1 AND OTCNRLW11 NE 1) OR `
  `(CONFW11 = 1 AND CONRELW11 NE 1 AND OTCNFW11 = 0) ] into 0`
* `NA into 999`

**R script:**

```{r harmo11}

ALSA_ds_w11 <- tibble(id=ALSA_w11_close_spouse$id)

ALSA_w11_close_spouse$CONFW11 <- car::recode(as.vector(ALSA_w11_close_spouse$CONFW11), "NA='-999'")
ALSA_w11_close_spouse$CONRELW11 <- car::recode(as.vector(ALSA_w11_close_spouse$CONRELW11), "NA='-999'")
ALSA_w11_close_spouse$OTCNFW11 <- car::recode(as.vector(ALSA_w11_close_spouse$OTCNFW11), "NA='-999'")
ALSA_w11_close_spouse$OTCNRLW11 <- car::recode(as.vector(ALSA_w11_close_spouse$OTCNRLW11), "NA='-999'")

ALSA_ds_w11$close_spouse <- c(NA)  # I think it is required
for(i in 1:dim(ALSA_w11_close_spouse)[1]){
  if( (ALSA_w11_close_spouse$CONFW11[i] == 1 & ALSA_w11_close_spouse$CONRELW11[i] == 1) |
      (ALSA_w11_close_spouse$OTCNFW11[i] == 1 & ALSA_w11_close_spouse$OTCNRLW11[i] == 1) ) { 
    ALSA_ds_w11$close_spouse[i] = 1 }
  
  else if( ALSA_w11_close_spouse$CONFW11[i] == 0 | 
           ( ALSA_w11_close_spouse$CONFW11[i] == 1 & !(ALSA_w11_close_spouse$CONRELW11[i] == 1) &
             ALSA_w11_close_spouse$OTCNFW11[i] == 1 & !(ALSA_w11_close_spouse$OTCNRLW11[i] == 1) ) |
           ( ALSA_w11_close_spouse$CONFW11[i] == 1 & !(ALSA_w11_close_spouse$CONRELW11[i] == 1) & 
             ALSA_w11_close_spouse$OTCNFW11[i] == 0) ) {
    ALSA_ds_w11$close_spouse[i] = 0 }
}
ALSA_ds_w11$close_spouse <- car::recode(as.vector(ALSA_ds_w11$close_spouse), "NA='999'")
ALSA_ds_w11$close_spouse <- labelled(ALSA_ds_w11$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript11, echo=F}

Categorical_summary(var = ALSA_ds_w11$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")

```

#### Validation
```{r crosstabulation11, echo=F}

```


### Wave 12


#### Study-specific variable description



| **Name ** |`CONFW12`|`CONRELW12`|`OTCNFW12`|`OTCNRLW11`|
|-|-|-|-|-|
| **Label** |`have confidant`|`relationship of confidant`|`other confidant`|`relationship of other confidant`|
| **Table name** |`ALSA-Wave12`|`ALSA-Wave12`|`ALSA-Wave12`|`ALSA-Wave12`|
| **Categories** |`1 = yes`<br/>`0 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|`1 = yes`<br/>`0 = no`|`1 = Spouse`<br/>`2 = Daughter`<br/>`3 = Daughter-in-law`<br/>`4 = Son`<br/>`5 = Son-in-law`<br/>`6 = Brother`<br/>`7 = Sister`<br/>`8 = Other male relative`<br/>`9 = Other female relative`<br/>`10 = Male friend`<br/>`11 = Female friend`|
| **Missings** |  |  |  |  |
| **Description** |  |  |  |  |

```{r assign12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12_close_spouse','ALSA.ALSA-Wave12',  variables=list('CONFW12','CONRELW12','OTCNFW12','OTCNRLW12'), missings = TRUE)
ALSA_w12_close_spouse <- opal.execute(o,'ALSA_w12_close_spouse')

```

```{r local12, echo=F}

Categorical_summary(var = ALSA_w12_close_spouse$CONFW12, missing_values = NA)
ggplot(ALSA_w12_close_spouse, aes(x=factor(CONFW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w12_close_spouse$CONRELW12, missing_values = NA)
ggplot(ALSA_w12_close_spouse, aes(x=factor(CONRELW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of confidant") + ylab("Frequency")
Categorical_summary(var = ALSA_w12_close_spouse$OTCNFW12, missing_values = NA)
ggplot(ALSA_w12_close_spouse, aes(x=factor(OTCNFW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("have other confidant?") + ylab("Frequency")
Categorical_summary(var = ALSA_w12_close_spouse$OTCNRLW12, missing_values = NA)
ggplot(ALSA_w12_close_spouse, aes(x=factor(OTCNRLW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("relationship of other confidant") + ylab("Frequency")

```


#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if (CONFW12 = 1 AND CONRELW12 = 1) OR (OTCNFW12 = 1 AND OTCNRLW12 = 1) into 1`
* `else if [ CONFW12 = 0 OR (CONFW12 = 1 AND CONRELW12 NE 1 AND OTCNFW12 = 1 AND OTCNRLW12 NE 1) OR `
  `(CONFW12 = 1 AND CONRELW12 NE 1 AND OTCNFW12 = 0) ] into 0`
* `NA into 999`

**R script:**

```{r harmo12}

ALSA_ds_w12 <- tibble(id=ALSA_w12_close_spouse$id)

ALSA_w12_close_spouse$CONFW12 <- car::recode(as.vector(ALSA_w12_close_spouse$CONFW12), "NA='-999'")
ALSA_w12_close_spouse$CONRELW12 <- car::recode(as.vector(ALSA_w12_close_spouse$CONRELW12), "NA='-999'")
ALSA_w12_close_spouse$OTCNFW12 <- car::recode(as.vector(ALSA_w12_close_spouse$OTCNFW12), "NA='-999'")
ALSA_w12_close_spouse$OTCNRLW12 <- car::recode(as.vector(ALSA_w12_close_spouse$OTCNRLW12), "NA='-999'")

ALSA_ds_w12$close_spouse <- c(NA)  # I think it is required
for(i in 1:dim(ALSA_w12_close_spouse)[1]){
  if( (ALSA_w12_close_spouse$CONFW12[i] == 1 & ALSA_w12_close_spouse$CONRELW12[i] == 1) |
      (ALSA_w12_close_spouse$OTCNFW12[i] == 1 & ALSA_w12_close_spouse$OTCNRLW12[i] == 1) ) { 
    ALSA_ds_w12$close_spouse[i] = 1 }
  
  else if( ALSA_w12_close_spouse$CONFW12[i] == 0 | 
           ( ALSA_w12_close_spouse$CONFW12[i] == 1 & !(ALSA_w12_close_spouse$CONRELW12[i] == 1) &
             ALSA_w12_close_spouse$OTCNFW12[i] == 1 & !(ALSA_w12_close_spouse$OTCNRLW12[i] == 1) ) |
           ( ALSA_w12_close_spouse$CONFW12[i] == 1 & !(ALSA_w12_close_spouse$CONRELW12[i] == 1) & 
             ALSA_w12_close_spouse$OTCNFW12[i] == 0) ) {
    ALSA_ds_w12$close_spouse[i] = 0 }
}
ALSA_ds_w12$close_spouse <- car::recode(as.vector(ALSA_ds_w12$close_spouse), "NA='999'")
ALSA_ds_w12$close_spouse <- labelled(ALSA_ds_w12$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript12, echo=F}

Categorical_summary(var = ALSA_ds_w12$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")

```

#### Validation
```{r crosstabulation12, echo=F}

```


### Wave 13

Not found.





```{r final, echo=F}

l.hds <- list(w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(name in names(l.hds)) {
  names(l.hds[[name]])[2] <- "close_spouse"
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","close_spouse")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","close_spouse")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  close_spouse <- l.hds[[index]]
  save(close_spouse, file = paste0(datafolder,names(l.hds)[index],"/close_spouse.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
