---
title: "Emotional support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/emot_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/emot_supDS.R')
```

<!-- ########################################################## --> 

# Data process


## Australia

### Wave 1

#### Study-specific variable description


| **Name** |`EMOTSUPP`|
|-|-|
| **Label** |`Would you say you can count on your partner for emotional support when you need it?`|
| **Table name** |`ALSA-Wave1`|
| **Categories**|`1 = Yes`<br/>`2 = No`|
| **Missings**|`9 = Missing`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_emo_sup','ALSA.ALSA-Wave1', variables=list('EMOTSUPP'), missings = TRUE)
ALSA_w1_emo_sup <- opal.execute(o,'ALSA_w1_emo_sup')
```

```{r local1, echo=F}
Categorical_summary(var = ALSA_w1_emo_sup$EMOTSUPP, missing_values = NA)
ggplot(ALSA_w1_emo_sup, aes(x=factor(EMOTSUPP))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Would you say you can count on your partner for emotional support when you need it?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `9 into 999`
* `NA into 999`

**R script:**

```{r harmo1}
ALSA_ds_w1 <- tibble(id=ALSA_w1_emo_sup$id)
ALSA_ds_w1$emot_sup <- car::recode(as.vector(ALSA_w1_emo_sup$EMOTSUPP), "1='1'; 2='0'; 9='999'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ALSA_ds_w1$emot_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Receives emotional support from someone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ALSA_ds_w1$emot_sup)
BeforeH <- table(ALSA_w1_emo_sup$EMOTSUPP, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[3]] <- sum(BeforeH[c(3:4)])
BeforeH1[[1]] <- BeforeH[[2]]
BeforeH1[[2]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("2->0","1->1","9&NA->999")
kable(C)
```

### Wave 2

Not found.


### Wave 3

Not found.

### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.

### Wave 8

Not found.

### Wave 9

Not found.

### Wave 10

Not found.

### Wave 11

Not found.


### Wave 12

Not found.


### Wave 13

Not found.



```{r final, echo=F}

l.hds <- list(w1 = ALSA_ds_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

A tables is generated: 

Percentages of categories in each harmonised variable.



```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


```


# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  emot_sup <- l.hds[[index]]
  save(emot_sup, file = paste0(datafolder,names(l.hds)[index],"/emot_sup.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
