---
title: "Participation in senior club/organization"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `sen_club`
* Variable label: `Participation in senior club/organization`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Australia

### Wave 1 

#### Study-specific variable description

| **Name** |`SOCMEMB`|`AAP19`|
|-|-|
| **Label** |`Social membership`|`Social activities (club, church, etc.)`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Less than once a month`<br/>`2 = About once a month`<br/>`3 = About once a week`<br/>`4 = More than once a week`|
| **Missings** |`9 = Missing`<br/>`NA`|`9 = Missing`<br/>`NA`|


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',  variables=list('SOCMEMB','AAP19'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')

```

```{r local1, echo=F}

vari <- ALSA_w1$SOCMEMB
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "SOCMEMB") 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_w1, aes(x=factor(SOCMEMB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Social membership") + ylab("Frequency")


vbl <- ALSA_w1$AAP19
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = "AAP19") 
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_w1, aes(x=factor(AAP19))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if SOCMEMB == 1 and AAP19 == 3 or 4, then 1`
* `if SOCMEMB == 0 or AAP19 == 1 or 2, then 0`
* `otherwise into 999`

**R script:**



```{r harmo1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$sen_club <- rep(999,length(ALSA_w1$id))
ALSA_ds_w1$sen_club[which(ALSA_w1$SOCMEMB==1 & ALSA_w1$AAP19 %in% c(3,4))] <- 1
ALSA_ds_w1$sen_club[which(ALSA_w1$SOCMEMB==0 | ALSA_w1$AAP19 %in% c(1,2))] <- 0

ALSA_ds_w1$sen_club <- labelled(ALSA_ds_w1$sen_club, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```

#### Statistical description of the new harmonised variable


```{r descript1, echo=FALSE}
vbl <- ALSA_ds_w1$sen_club
kable(Categorical_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sen_club") 
kable(Categorical_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(ALSA_ds_w1, aes(x=factor(sen_club))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in senior club/organization") + ylab("Frequency")
```


```{r crosstabulation1, echo=F}
#### Validation

```

 
 

### Wave 2
Not found.


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `MEMBER2`
* Label: `MEMBER: Senior Citzens`
* Categories:
    + `0 = Not MEMBER`
    + `1 = MEMBER`
    
* Name: `MEMBER7`
* Label: `MEMBER: Aged Pensioners`
* Categories:
    + `0 = Not MEMBER`
    + `1 = MEMBER`

* Name: `MEMBER22`
* Label: `MEMBER: Retired Persons Groups `
* Categories:
    + `0 = Not MEMBER`
    + `1 = MEMBER`
    
* Name: `MEMBER24`
* Label: `MEMBER: Over 50 clubs `
* Categories:
    + `0 = Not MEMBER`
    + `1 = MEMBER`
    
* Name: `MEMBER25`
* Label: `MEMBER: Over 60 clubs`
* Categories:
    + `0 = Not MEMBER`
    + `1 = MEMBER`
    
    
* Name: `STIL2W3`
* Label: `STILL MEMBER OF Senior Citzens?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `STIL7W3`
* Label: `STILL MEMBER OF Aged Pensioners?`
* Categories:
    + `1 = Yes`
    + `2 = No`

* Name: `STIL22W3`
* Label: `STILL MEMBER OF Retired Persons Groups?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `STIL24W3`
* Label: `STILL MEMBER OF Over 50 clubs?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `STIL25W3`
* Label: `STILL MEMBER OF Over 60 clubs?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_sen_club','ALSA.ALSA-Wave3', 
                        variables=list('MEMBER2','MEMBER7','MEMBER22','MEMBER24','MEMBER25',
                                       'STIL2W3','STIL7W3','STIL22W3','STIL24W3','STIL25W3'), missings = TRUE)
```

```{r local3, echo=F}
ALSA_w3_sen_club <- opal.execute(o,'ALSA_w3_sen_club')
vari <-  ALSA_w3_sen_club$MEMBER2
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "MEMBER2") 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w3_sen_club$MEMBER2, missing_values = NA)
ggplot(ALSA_w3_sen_club, aes(x=factor(MEMBER2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MEMBER: Senior Citzens") + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL2W3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "STIL2W3") 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w3_sen_club$STIL2W3, missing_values = NA)
ggplot(ALSA_w3_sen_club, aes(x=factor(STIL2W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STILL MEMBER OF Senior Citzens?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of MEMBER or STILl MEMBER equals 1 then 1`
* `if all memebers are equal 0 and STILl memebers are equal 2 then 0`
* `NA or 9 into 999`

**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_sen_club$id)

ALSA_w3_sen_club$MEMBER2 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER2), "NA='-999'")
ALSA_w3_sen_club$MEMBER7 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER7), "NA='-999'")
ALSA_w3_sen_club$MEMBER22 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER22), "NA='-999'")
ALSA_w3_sen_club$MEMBER24 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER24), "NA='-999'")
ALSA_w3_sen_club$MEMBER25 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER25), "NA='-999'")
ALSA_w3_sen_club$STIL2W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL2W3), "NA='-999'")
ALSA_w3_sen_club$STIL7W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL7W3), "NA='-999'")
ALSA_w3_sen_club$STIL22W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL22W3), "NA='-999'")
ALSA_w3_sen_club$STIL24W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL24W3), "NA='-999'")
ALSA_w3_sen_club$STIL25W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL25W3), "NA='-999'")

ALSA_ds_w3$sen_club <- c(NA)
for(i in 1:dim(ALSA_w3_sen_club)[1]){
  if( ALSA_w3_sen_club$MEMBER2[i] == 1 | ALSA_w3_sen_club$MEMBER7[i] == 1 | ALSA_w3_sen_club$MEMBER22[i] == 1 | 
      ALSA_w3_sen_club$MEMBER24[i] == 1 | ALSA_w3_sen_club$MEMBER25[i] == 1 |
      ALSA_w3_sen_club$STIL2W3[i] == 1 | ALSA_w3_sen_club$STIL7W3[i] == 1 | ALSA_w3_sen_club$STIL22W3[i] == 1 | 
      ALSA_w3_sen_club$STIL24W3[i] == 1 | ALSA_w3_sen_club$STIL25W3[i] == 1 ) { 
  ALSA_ds_w3$sen_club[i] = 1 }
  else if( ALSA_w3_sen_club$MEMBER2[i] == 0 & ALSA_w3_sen_club$MEMBER7[i] == 0 & ALSA_w3_sen_club$MEMBER22[i] == 0 & 
           ALSA_w3_sen_club$MEMBER24[i] == 0 & ALSA_w3_sen_club$MEMBER25[i] == 0 &
           ALSA_w3_sen_club$STIL2W3[i] == 2 & ALSA_w3_sen_club$STIL7W3[i] == 2 & ALSA_w3_sen_club$STIL22W3[i] == 2 & 
           ALSA_w3_sen_club$STIL24W3[i] == 2 & ALSA_w3_sen_club$STIL25W3[i] == 2 ) { 
  ALSA_ds_w3$sen_club[i] = 0 }
}

ALSA_ds_w3$sen_club <- car::recode(as.vector(ALSA_ds_w3$sen_club), "NA='999'")
ALSA_ds_w3$sen_club <- labelled(ALSA_ds_w3$sen_club, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ALSA_ds_w3$sen_club, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(sen_club))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in senior club/organization") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```

 
### Wave 4
Not found.

### Wave 5
Not found.

### Wave 6
Not found.

### Wave 7
Not found.

### Wave 8
Not found.

### Wave 9
Not found.

### Wave 10
Not found.

### Wave 11
Not found.

### Wave 12
Not found.

### Wave 13
Not found.

```{r save, echo=FALSE}

sen_club <- ALSA_ds_w1
save(sen_club, file = "../RData/w1/sen_club.RData")
rm(sen_club)


sen_club <- ALSA_ds_w3
save(sen_club, file = "../RData/w3/sen_club.RData")
rm(sen_club)



```



# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


