---
title: "Participation in senior club/organization"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sen_clubDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sen_clubDS.R')
```

<!-- ########################################################## --> 

# Data process

## Australia

### Wave 1 

#### Study-specific variable description

| **Name** |`SOCMEMB`|`AAP19`|
|-|-|-|
| **Label** |`Social membership`|`Social activities (club, church, etc.)`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Less than once a month`<br/>`2 = About once a month`<br/>`3 = About once a week`<br/>`4 = More than once a week`|
| **Missings** |`9 = Missing`<br/>`NA`|`9 = Missing`<br/>`NA`|


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',  variables=list('SOCMEMB','AAP19'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')

```

```{r local1, echo=F}

vari <- ALSA_w1$SOCMEMB
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "SOCMEMB") 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_w1, aes(x=factor(SOCMEMB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Social membership") + ylab("Frequency")


vbl <- ALSA_w1$AAP19
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = "AAP19") 
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_w1, aes(x=factor(AAP19))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if SOCMEMB == 1 and AAP19 == 3 or 4, then 1`
* `if SOCMEMB == 0 or AAP19 == 1 or 2, then 0`
* `otherwise into 999`

**R script:**



```{r harmo1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$sen_club <- rep(999,length(ALSA_w1$id))
ALSA_ds_w1$sen_club[which(ALSA_w1$SOCMEMB==1 & ALSA_w1$AAP19 %in% c(3,4))] <- 1
ALSA_ds_w1$sen_club[which(ALSA_w1$SOCMEMB==0 | ALSA_w1$AAP19 %in% c(1,2))] <- 0

ALSA_ds_w1$sen_club <- labelled(ALSA_ds_w1$sen_club, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```

#### Statistical description of the new harmonised variable


```{r descript1, echo=FALSE}

vbl <- ALSA_ds_w1$sen_club
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(sen_club))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}


```

 
 

### Wave 2
Not found.


### Wave 3

#### Study-specific variable description


| **Name** |`MEMBER2`|`MEMBER7`|`MEMBER22`|`MEMBER24`|`MEMBER25`|`STIL2W3`|`STIL7W3`|`STIL22W3`|`STIL24W3`|`STIL25W3`|
|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`MEMBER: Senior Citzens`|`MEMBER: Aged Pensioners`|`MEMBER: Retired Persons Groups `|`MEMBER: Over 50 clubs `|`MEMBER: Over 60 clubs`|`STILL MEMBER OF Senior Citzens?`|`STILL MEMBER OF Aged Pensioners?`|`STILL MEMBER OF Retired Persons Groups?`|`STILL MEMBER OF Over 50 clubs?`|`STILL MEMBER OF Over 60 clubs?`|
| **Categories** |`1 = MEMBER`<br/>`0 = Not MEMBER`|`1 = MEMBER`<br/>`0 = Not MEMBER`|`1 = MEMBER`<br/>`0 = Not MEMBER`|`1 = MEMBER`<br/>`0 = Not MEMBER`|`1 = MEMBER`<br/>`0 = Not MEMBER`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|
| **Description** |||||||||||


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_sen_club','ALSA.ALSA-Wave3', 
                        variables=list('MEMBER2','MEMBER7','MEMBER22','MEMBER24','MEMBER25',
                                       'STIL2W3','STIL7W3','STIL22W3','STIL24W3','STIL25W3'), missings = TRUE)
ALSA_w3_sen_club <- opal.execute(o,'ALSA_w3_sen_club')
```

```{r local3, echo=F}
vari <-  ALSA_w3_sen_club$MEMBER2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-  ALSA_w3_sen_club$MEMBER7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-  ALSA_w3_sen_club$MEMBER22
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-  ALSA_w3_sen_club$MEMBER24
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-  ALSA_w3_sen_club$MEMBER25
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL2W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL7W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL22W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL24W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ALSA_w3_sen_club$STIL25W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sen_club, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of MEMBER or STILl MEMBER equals 1 then 1`
* `if all memebers are equal 0 and STILl memebers are equal 2 then 0`
* `NA or 9 into 999`

**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_sen_club$id)

ALSA_w3_sen_club$MEMBER2 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER2), "NA='-999'")
ALSA_w3_sen_club$MEMBER7 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER7), "NA='-999'")
ALSA_w3_sen_club$MEMBER22 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER22), "NA='-999'")
ALSA_w3_sen_club$MEMBER24 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER24), "NA='-999'")
ALSA_w3_sen_club$MEMBER25 <- car::recode(as.vector(ALSA_w3_sen_club$MEMBER25), "NA='-999'")
ALSA_w3_sen_club$STIL2W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL2W3), "NA='-999'")
ALSA_w3_sen_club$STIL7W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL7W3), "NA='-999'")
ALSA_w3_sen_club$STIL22W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL22W3), "NA='-999'")
ALSA_w3_sen_club$STIL24W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL24W3), "NA='-999'")
ALSA_w3_sen_club$STIL25W3 <- car::recode(as.vector(ALSA_w3_sen_club$STIL25W3), "NA='-999'")

ALSA_ds_w3$sen_club <- c(NA)
for(i in 1:dim(ALSA_w3_sen_club)[1]){
  if( ALSA_w3_sen_club$MEMBER2[i] == 1 | ALSA_w3_sen_club$MEMBER7[i] == 1 | ALSA_w3_sen_club$MEMBER22[i] == 1 | 
      ALSA_w3_sen_club$MEMBER24[i] == 1 | ALSA_w3_sen_club$MEMBER25[i] == 1 |
      ALSA_w3_sen_club$STIL2W3[i] == 1 | ALSA_w3_sen_club$STIL7W3[i] == 1 | ALSA_w3_sen_club$STIL22W3[i] == 1 | 
      ALSA_w3_sen_club$STIL24W3[i] == 1 | ALSA_w3_sen_club$STIL25W3[i] == 1 ) { 
  ALSA_ds_w3$sen_club[i] = 1 }
  else if( ALSA_w3_sen_club$MEMBER2[i] == 0 & ALSA_w3_sen_club$MEMBER7[i] == 0 & ALSA_w3_sen_club$MEMBER22[i] == 0 & 
           ALSA_w3_sen_club$MEMBER24[i] == 0 & ALSA_w3_sen_club$MEMBER25[i] == 0) { 
  ALSA_ds_w3$sen_club[i] = 0 }
}

ALSA_ds_w3$sen_club <- car::recode(as.vector(ALSA_ds_w3$sen_club), "NA='999'")
ALSA_ds_w3$sen_club <- labelled(ALSA_ds_w3$sen_club, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vbl <- ALSA_ds_w3$sen_club
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(sen_club))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```

 
### Wave 4
Not found.

### Wave 5
Not found.

### Wave 6
Not found.

### Wave 7
Not found.

### Wave 8
Not found.

### Wave 9
Not found.

### Wave 10
Not found.

### Wave 11
Not found.

### Wave 12
Not found.

### Wave 13
Not found.




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


