---
title: "Sport Activities"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sportDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sportDS.R')
```

<!-- ########################################################## --> 


# Data process

## Australia


### Wave 1 

Not found.

### Wave 2

Not found.


### Wave 3

#### Study-specific variable description


| **Name** |`MEMBER16`|`MEMBER17`|`MEMBER20`|`STIL16W3`|`STIL17W3`|`STIL20W3`|
|-|-|-|-|-|-|-|
| **Label** |`MEMBER: Football Clubs`|`MEMBER: Other Sporting Group`|`MEMBER: Golf Clubs`|`STILL MEMBER OF Football Clubs`|`STILL MEMBER OF Other Sporting Group`|`STILL MEMBER OF Golf Clubs`|
| **Table name** |`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|`ALSA-Wave3`|
| **Categories** |`0 = Not member`<br/>`1 = Member`|`0 = Not member`<br/>`1 = Member`|`0 = Not member`<br/>`1 = Member`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|
| **Missings** |  |  |  |`NA`|`NA`|`NA`<br/>`9 = Missing`|
| **Description** |  |  |  |  |  |  |


    

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_sport','ALSA.ALSA-Wave3', variables=list('MEMBER16','MEMBER17','MEMBER20','STIL16W3','STIL17W3','STIL20W3'), missings = TRUE)
ALSA_w3_sport <- opal.execute(o,'ALSA_w3_sport')
```

```{r local3, echo=F}

vari <- ALSA_w3_sport$MEMBER16
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sport, aes(x=factor(MEMBER16))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MEMBER OF Football Clubs?") + ylab("Frequency")

vari <- ALSA_w3_sport$MEMBER17
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sport, aes(x=factor(MEMBER17))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MEMBER OF Other Sporting Clubs?") + ylab("Frequency")

vari <- ALSA_w3_sport$MEMBER20
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sport, aes(x=factor(MEMBER20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("MEMBER OF Golf Clubs?") + ylab("Frequency")

vari <- ALSA_w3_sport$STIL16W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sport, aes(x=factor(STIL16W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STILL MEMBER OF Football Clubs?") + ylab("Frequency")

vari <- ALSA_w3_sport$STIL17W3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_sport, aes(x=factor(STIL17W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STILL MEMBER OF Other Sporting Clubs?") + ylab("Frequency")

vari <- ALSA_w3_sport$STIL20W3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_w3_sport, aes(x=factor(STIL20W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STILL MEMBER OF Golf Clubs?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if (MEMBER16 and MEMBER17 and MEMBER20 = 0 ) OR (MEMBER16=1 and STIL16w3 =2) or (MEMBER17=1 and STIL17w3=2) or (MEMBER20=1 and STIL20w3 = 2) - recode to 0`  
* `if (MEMBER16=1 and STIL16w3 =1) or(MEMBER17=1 and STIL17w3=1) or (MEMBER20=1 and STIL17w3 = 1) - recode to 1`
* `NA or 9 into 999`


**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_sport$id)

ALSA_w3_sport$MEMBER16 <- car::recode(as.vector(ALSA_w3_sport$MEMBER16), "NA='-999'")
ALSA_w3_sport$MEMBER17 <- car::recode(as.vector(ALSA_w3_sport$MEMBER17), "NA='-999'")
ALSA_w3_sport$MEMBER20 <- car::recode(as.vector(ALSA_w3_sport$MEMBER20), "NA='-999'")
ALSA_w3_sport$STIL16W3 <- car::recode(as.vector(ALSA_w3_sport$STIL16W3), "NA='-999'")
ALSA_w3_sport$STIL17W3 <- car::recode(as.vector(ALSA_w3_sport$STIL17W3), "NA='-999'")
ALSA_w3_sport$STIL20W3 <- car::recode(as.vector(ALSA_w3_sport$STIL20W3), "NA='-999'")

ALSA_ds_w3$sport <- c(NA)
for(i in 1:dim(ALSA_w3_sport)[1]){
  if((ALSA_w3_sport$MEMBER16[i] == 0 & ALSA_w3_sport$MEMBER17[i] == 0 & ALSA_w3_sport$MEMBER20[i] == 0 ) |
     (ALSA_w3_sport$MEMBER16[i] == 1 & ALSA_w3_sport$STIL16W3==2) |
     (ALSA_w3_sport$MEMBER17[i] == 1 & ALSA_w3_sport$STIL17W3==2) |
     (ALSA_w3_sport$MEMBER20[i] == 1 & ALSA_w3_sport$STIL20W3==2)) { 
    ALSA_ds_w3$sport[i] = 0 }
else if( (ALSA_w3_sport$MEMBER16[i] == 1 & ALSA_w3_sport$STIL16W3[i] == 1 )| 
         (ALSA_w3_sport$MEMBER17[i] == 1 & ALSA_w3_sport$STIL17W3[i] == 1) | 
         (ALSA_w3_sport$MEMBER20[i] == 1 & ALSA_w3_sport$STIL20W3[i] == 1) ) { 
  ALSA_ds_w3$sport[i] = 1 }

}

ALSA_ds_w3$sport <- car::recode(as.vector(ALSA_ds_w3$sport), "NA='999'")
ALSA_ds_w3$sport <- labelled(ALSA_ds_w3$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ALSA_ds_w3$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```

### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.

### Wave 8

Not found.

### Wave 9

Not found.


### Wave 10

Not found.

### Wave 11

Not found.

### Wave 12

Not found.


### Wave 13

Not found.


```{r save, echo=FALSE}
sport <- ALSA_ds_w3
save(sport, file = "../RData/w3/sport.RData")
rm(sport)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
