---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process

## Australia


### Wave 1 

#### Study-specific variable description

| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`SOCMEMB`|`Social membership`|`ALSA-Wave1`|`1 = Yes; 2 = No`|`9 = Missing`|

**Description**

```{r assign1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1_part_clubs','ALSA.ALSA-Wave1', variables=list('SOCMEMB'), missings = TRUE)
ALSA_w1_part_clubs <- opal.execute(o,'ALSA_w1_part_clubs')

```

```{r local1, echo=F}

vbl <- ALSA_w1_part_clubs$SOCMEMB
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = 'SOCMEMB')
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1_part_clubs, aes(x=factor(SOCMEMB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `SOCMEMB equals 1 into 1`
* `SOCMEMB=2 into 0`
* `NA or 9 into 999`

**R script:**

```{r harmo1}

ALSA_ds_w1 <- tibble(id=ALSA_w1_part_clubs$id)
ALSA_ds_w1$part_clubs <- car::recode(as.vector(ALSA_w1_part_clubs$SOCMEMB), "2=0;9=999;NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}

vbl <- ALSA_ds_w1$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}

```




### Wave 2

Not found.


### Wave 3

#### Study-specific variable description




| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`MEMBER1`|`R.S.L.`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER2`|`Senior Citzens`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER3`|`Probus`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER4`|`Church/Religious`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER5`|`Bowls`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER6`|`Rotary`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER7`|`Aged Pensioners`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER8`|`Community Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER9`|`Social Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER10`|`Specific Interest-Hobby`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER11`|`Craft Groups`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER12`|`Masons, Lodges`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER13`|`Specific Interest-Other`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER14`|`Charity/Volunteer`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER15`|`Other Ex-service Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER16`|`Football Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER17`|`Other part_clubsing Groups`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER18`|`ARPA`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER19`|`Bridge/Card Clubs `|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER20`|`Golf Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER21`|`Agricultral/Horticultural`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER22`|`Retired Persons Groups`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER23`|`Cooinda`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER24`|`Over 50`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER25`|`Over 60`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER26`|`Friendship/Fellowship`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER27`|`Art Appreciation`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER28`|`Music/Dance`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER29`|`Lions`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER30`|`CWA`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER31`|`Travel Clubs`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER32`|`Special Womens Groups`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER33`|`Legacy`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`MEMBER34`|`Other Society`|`ALSA-Wave3`|`0 = Not MEMBER; 1 = MEMBER`|  |  |
|`STIL1W3`|`Social MEMBERship`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL2W3`|`Senior Citzens`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL3W3`|`Probus`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL4W3`|`Church/Religious`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL5W3`|`Bowls`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL6W3`|`Rotary`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL7W3`|`Aged Pensioners`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL8W3`|`Community Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL9W3`|`Social Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL10W3`|`Specific Interest-Hobby`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL11W3`|`Craft Groups`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL12W3`|`Masons, Lodges`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL13W3`|`Specific Interest-Other`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL14W3`|`Charity/Volunteer`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL15W3`|`Other Ex-service Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL16W3`|`Football Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL17W3`|`Other part_clubsing Groups`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL18W3`|`ARPA`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL19W3`|`Bridge/Card Clubs `|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL20W3`|`Golf Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL21W3`|`Agricultral/Horticultural`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL22W3`|`Retired Persons Groups`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL23W3`|`Cooinda`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL24W3`|`Over 50`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL25W3`|`Over 60`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL26W3`|`Friendship/Fellowship`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL27W3`|`Art Appreciation`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL28W3`|`Music/Dance`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL29W3`|`Lions`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL30W3`|`CWA`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL31W3`|`Travel Clubs`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL32W3`|`Special Womens Groups`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL33W3`|`Legacy`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |
|`STIL34W3`|`Other Society`|`ALSA-Wave3`|`1 = Yes; 2 = No`|  |  |

**Description**

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_part_clubs','ALSA.ALSA-Wave3', 
                        variables=list('MEMBER1','MEMBER2','MEMBER3','MEMBER4','MEMBER5','MEMBER6',
                                       'MEMBER7','MEMBER8','MEMBER9','MEMBER10','MEMBER11','MEMBER12',
                                       'MEMBER13','MEMBER14','MEMBER15','MEMBER16','MEMBER17','MEMBER18',
                                       'MEMBER19','MEMBER20','MEMBER21','MEMBER22','MEMBER23','MEMBER24',
                                       'MEMBER25','MEMBER26','MEMBER27','MEMBER28','MEMBER29','MEMBER30',
                                       'MEMBER31','MEMBER32','MEMBER33','MEMBER34',
                                       'STIL1W3','STIL2W3','STIL3W3','STIL4W3','STIL5W3','STIL6W3',
                                       'STIL7W3','STIL8W3','STIL9W3','STIL10W3','STIL11W3','STIL12W3',
                                       'STIL13W3','STIL14W3','STIL15W3','STIL16W3','STIL17W3','STIL18W3',
                                       'STIL19W3','STIL20W3','STIL21W3','STIL22W3','STIL23W3','STIL24W3',
                                       'STIL25W3','STIL26W3','STIL27W3','STIL28W3','STIL29W3','STIL30W3',
                                       'STIL31W3','STIL32W3','STIL33W3','STIL34W3'), missings = TRUE)
ALSA_w3_part_clubs <- opal.execute(o,'ALSA_w3_part_clubs')

```

```{r local3, echo=F}

#Include a shiny app

vbl <- ALSA_w3_part_clubs$MEMBER1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'MEMBER1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_part_clubs, aes(x=factor(MEMBER1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w3_part_clubs$STIL1W3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'STIL1W3')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3_part_clubs, aes(x=factor(STIL1W3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of MEMBER or STIL MEMBER equals 1 then 0`
* `else if all memebers are equal 0 or all STILl MEMBERs are equal 2 then 0` 
# because there are lots of NAs in STIL_w3 variables, I use OR for "all STILl MEMBERs are equal 2" condition
* `NA into 999`

**R script:**

```{r harmo3}
ALSA_ds_w3 <- tibble(id=ALSA_w3_part_clubs$id)

ALSA_w3_part_clubs$MEMBER1 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER1), "NA='-999'")
ALSA_w3_part_clubs$MEMBER2 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER2), "NA='-999'")
ALSA_w3_part_clubs$MEMBER3 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER3), "NA='-999'")
ALSA_w3_part_clubs$MEMBER4 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER4), "NA='-999'")
ALSA_w3_part_clubs$MEMBER5 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER5), "NA='-999'")
ALSA_w3_part_clubs$MEMBER6 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER6), "NA='-999'")
ALSA_w3_part_clubs$MEMBER7 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER7), "NA='-999'")
ALSA_w3_part_clubs$MEMBER8 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER8), "NA='-999'")
ALSA_w3_part_clubs$MEMBER9 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER9), "NA='-999'")
ALSA_w3_part_clubs$MEMBER10 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER10), "NA='-999'")
ALSA_w3_part_clubs$MEMBER11 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER11), "NA='-999'")
ALSA_w3_part_clubs$MEMBER12 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER12), "NA='-999'")
ALSA_w3_part_clubs$MEMBER13 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER13), "NA='-999'")
ALSA_w3_part_clubs$MEMBER14 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER14), "NA='-999'")
ALSA_w3_part_clubs$MEMBER15 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER15), "NA='-999'")
ALSA_w3_part_clubs$MEMBER16 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER16), "NA='-999'")
ALSA_w3_part_clubs$MEMBER17 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER17), "NA='-999'")
ALSA_w3_part_clubs$MEMBER18 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER18), "NA='-999'")
ALSA_w3_part_clubs$MEMBER19 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER19), "NA='-999'")
ALSA_w3_part_clubs$MEMBER20 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER20), "NA='-999'")
ALSA_w3_part_clubs$MEMBER21 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER21), "NA='-999'")
ALSA_w3_part_clubs$MEMBER22 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER22), "NA='-999'")
ALSA_w3_part_clubs$MEMBER23 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER23), "NA='-999'")
ALSA_w3_part_clubs$MEMBER24 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER24), "NA='-999'")
ALSA_w3_part_clubs$MEMBER25 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER25), "NA='-999'")
ALSA_w3_part_clubs$MEMBER26 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER26), "NA='-999'")
ALSA_w3_part_clubs$MEMBER27 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER27), "NA='-999'")
ALSA_w3_part_clubs$MEMBER28 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER28), "NA='-999'")
ALSA_w3_part_clubs$MEMBER29 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER29), "NA='-999'")
ALSA_w3_part_clubs$MEMBER30 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER30), "NA='-999'")
ALSA_w3_part_clubs$MEMBER31 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER31), "NA='-999'")
ALSA_w3_part_clubs$MEMBER32 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER32), "NA='-999'")
ALSA_w3_part_clubs$MEMBER33 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER33), "NA='-999'")
ALSA_w3_part_clubs$MEMBER34 <- car::recode(as.vector(ALSA_w3_part_clubs$MEMBER34), "NA='-999'")
ALSA_w3_part_clubs$STIL1W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL1W3), "NA='-999'")
ALSA_w3_part_clubs$STIL2W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL2W3), "NA='-999'")
ALSA_w3_part_clubs$STIL3W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL3W3), "NA='-999'")
ALSA_w3_part_clubs$STIL4W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL4W3), "NA='-999'")
ALSA_w3_part_clubs$STIL5W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL5W3), "NA='-999'")
ALSA_w3_part_clubs$STIL6W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL6W3), "NA='-999'")
ALSA_w3_part_clubs$STIL7W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL7W3), "NA='-999'")
ALSA_w3_part_clubs$STIL8W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL8W3), "NA='-999'")
ALSA_w3_part_clubs$STIL9W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL9W3), "NA='-999'")
ALSA_w3_part_clubs$STIL10W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL10W3), "NA='-999'")
ALSA_w3_part_clubs$STIL11W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL11W3), "NA='-999'")
ALSA_w3_part_clubs$STIL12W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL12W3), "NA='-999'")
ALSA_w3_part_clubs$STIL13W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL13W3), "NA='-999'")
ALSA_w3_part_clubs$STIL14W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL14W3), "NA='-999'")
ALSA_w3_part_clubs$STIL15W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL15W3), "NA='-999'")
ALSA_w3_part_clubs$STIL16W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL16W3), "NA='-999'")
ALSA_w3_part_clubs$STIL17W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL17W3), "NA='-999'")
ALSA_w3_part_clubs$STIL18W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL18W3), "NA='-999'")
ALSA_w3_part_clubs$STIL19W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL19W3), "NA='-999'")
ALSA_w3_part_clubs$STIL20W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL20W3), "NA='-999'")
ALSA_w3_part_clubs$STIL21W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL21W3), "NA='-999'")
ALSA_w3_part_clubs$STIL22W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL22W3), "NA='-999'")
ALSA_w3_part_clubs$STIL23W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL23W3), "NA='-999'")
ALSA_w3_part_clubs$STIL24W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL24W3), "NA='-999'")
ALSA_w3_part_clubs$STIL25W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL25W3), "NA='-999'")
ALSA_w3_part_clubs$STIL26W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL26W3), "NA='-999'")
ALSA_w3_part_clubs$STIL27W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL27W3), "NA='-999'")
ALSA_w3_part_clubs$STIL28W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL28W3), "NA='-999'")
ALSA_w3_part_clubs$STIL29W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL29W3), "NA='-999'")
ALSA_w3_part_clubs$STIL30W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL30W3), "NA='-999'")
ALSA_w3_part_clubs$STIL31W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL31W3), "NA='-999'")
ALSA_w3_part_clubs$STIL32W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL32W3), "NA='-999'")
ALSA_w3_part_clubs$STIL33W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL33W3), "NA='-999'")
ALSA_w3_part_clubs$STIL34W3 <- car::recode(as.vector(ALSA_w3_part_clubs$STIL34W3), "NA='-999'")


ALSA_ds_w3$part_clubs <- c(NA)
for(i in 1:dim(ALSA_w3_part_clubs)[1]){
  if( ALSA_w3_part_clubs$MEMBER1[i] == 1 | ALSA_w3_part_clubs$MEMBER2[i] == 1 | ALSA_w3_part_clubs$MEMBER3[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER4[i] == 1 | ALSA_w3_part_clubs$MEMBER5[i] == 1 | ALSA_w3_part_clubs$MEMBER6[i] == 1 | ALSA_w3_part_clubs$MEMBER7[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER8[i] == 1 | ALSA_w3_part_clubs$MEMBER9[i] == 1 | ALSA_w3_part_clubs$MEMBER10[i] == 1 | ALSA_w3_part_clubs$MEMBER11[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER12[i] == 1 | ALSA_w3_part_clubs$MEMBER13[i] == 1 | ALSA_w3_part_clubs$MEMBER14[i] == 1 | ALSA_w3_part_clubs$MEMBER15[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER16[i] == 1 | ALSA_w3_part_clubs$MEMBER17[i] == 1 | ALSA_w3_part_clubs$MEMBER18[i] == 1 | ALSA_w3_part_clubs$MEMBER19[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER20[i] == 1 | ALSA_w3_part_clubs$MEMBER21[i] == 1 | ALSA_w3_part_clubs$MEMBER22[i] == 1 | ALSA_w3_part_clubs$MEMBER23[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER24[i] == 1 | ALSA_w3_part_clubs$MEMBER25[i] == 1 | ALSA_w3_part_clubs$MEMBER26[i] == 1 | ALSA_w3_part_clubs$MEMBER27[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER28[i] == 1 | ALSA_w3_part_clubs$MEMBER29[i] == 1 | ALSA_w3_part_clubs$MEMBER30[i] == 1 | ALSA_w3_part_clubs$MEMBER31[i] == 1 | 
      ALSA_w3_part_clubs$MEMBER32[i] == 1 | ALSA_w3_part_clubs$MEMBER33[i] == 1 | ALSA_w3_part_clubs$MEMBER34[i] == 1 |
      ALSA_w3_part_clubs$STIL1W3[i] == 1 | ALSA_w3_part_clubs$STIL2W3[i] == 1 | ALSA_w3_part_clubs$STIL3W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL4W3[i] == 1 | ALSA_w3_part_clubs$STIL5W3[i] == 1 | ALSA_w3_part_clubs$STIL6W3[i] == 1 | ALSA_w3_part_clubs$STIL7W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL8W3[i] == 1 | ALSA_w3_part_clubs$STIL9W3[i] == 1 | ALSA_w3_part_clubs$STIL10W3[i] == 1 | ALSA_w3_part_clubs$STIL11W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL12W3[i] == 1 | ALSA_w3_part_clubs$STIL13W3[i] == 1 | ALSA_w3_part_clubs$STIL14W3[i] == 1 | ALSA_w3_part_clubs$STIL15W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL16W3[i] == 1 | ALSA_w3_part_clubs$STIL17W3[i] == 1 | ALSA_w3_part_clubs$STIL18W3[i] == 1 | ALSA_w3_part_clubs$STIL19W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL20W3[i] == 1 | ALSA_w3_part_clubs$STIL21W3[i] == 1 | ALSA_w3_part_clubs$STIL22W3[i] == 1 | ALSA_w3_part_clubs$STIL23W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL24W3[i] == 1 | ALSA_w3_part_clubs$STIL25W3[i] == 1 | ALSA_w3_part_clubs$STIL26W3[i] == 1 | ALSA_w3_part_clubs$STIL27W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL28W3[i] == 1 | ALSA_w3_part_clubs$STIL29W3[i] == 1 | ALSA_w3_part_clubs$STIL30W3[i] == 1 | ALSA_w3_part_clubs$STIL31W3[i] == 1 | 
      ALSA_w3_part_clubs$STIL32W3[i] == 1 | ALSA_w3_part_clubs$STIL33W3[i] == 1 | ALSA_w3_part_clubs$STIL34W3[i] == 1 ) { 
    ALSA_ds_w3$part_clubs[i] = 1 }
  else if( ( ALSA_w3_part_clubs$MEMBER1[i] == 0 & ALSA_w3_part_clubs$MEMBER2[i] == 0 & ALSA_w3_part_clubs$MEMBER3[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER4[i] == 0 & ALSA_w3_part_clubs$MEMBER5[i] == 0 & ALSA_w3_part_clubs$MEMBER6[i] == 0 & ALSA_w3_part_clubs$MEMBER7[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER8[i] == 0 & ALSA_w3_part_clubs$MEMBER9[i] == 0 & ALSA_w3_part_clubs$MEMBER10[i] == 0 & ALSA_w3_part_clubs$MEMBER11[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER12[i] == 0 & ALSA_w3_part_clubs$MEMBER13[i] == 0 & ALSA_w3_part_clubs$MEMBER14[i] == 0 & ALSA_w3_part_clubs$MEMBER15[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER16[i] == 0 & ALSA_w3_part_clubs$MEMBER17[i] == 0 & ALSA_w3_part_clubs$MEMBER18[i] == 0 & ALSA_w3_part_clubs$MEMBER19[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER20[i] == 0 & ALSA_w3_part_clubs$MEMBER21[i] == 0 & ALSA_w3_part_clubs$MEMBER22[i] == 0 & ALSA_w3_part_clubs$MEMBER23[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER24[i] == 0 & ALSA_w3_part_clubs$MEMBER25[i] == 0 & ALSA_w3_part_clubs$MEMBER26[i] == 0 & ALSA_w3_part_clubs$MEMBER27[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER28[i] == 0 & ALSA_w3_part_clubs$MEMBER29[i] == 0 & ALSA_w3_part_clubs$MEMBER30[i] == 0 & ALSA_w3_part_clubs$MEMBER31[i] == 0 & 
      ALSA_w3_part_clubs$MEMBER32[i] == 0 & ALSA_w3_part_clubs$MEMBER33[i] == 0 & ALSA_w3_part_clubs$MEMBER34[i] == 0 ) |
      ( ALSA_w3_part_clubs$STIL1W3[i] == 2 & ALSA_w3_part_clubs$STIL2W3[i] == 2 & ALSA_w3_part_clubs$STIL3W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL4W3[i] == 2 & ALSA_w3_part_clubs$STIL5W3[i] == 2 & ALSA_w3_part_clubs$STIL6W3[i] == 2 & ALSA_w3_part_clubs$STIL7W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL8W3[i] == 2 & ALSA_w3_part_clubs$STIL9W3[i] == 2 & ALSA_w3_part_clubs$STIL10W3[i] == 2 & ALSA_w3_part_clubs$STIL11W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL12W3[i] == 2 & ALSA_w3_part_clubs$STIL13W3[i] == 2 & ALSA_w3_part_clubs$STIL14W3[i] == 2 & ALSA_w3_part_clubs$STIL15W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL16W3[i] == 2 & ALSA_w3_part_clubs$STIL17W3[i] == 2 & ALSA_w3_part_clubs$STIL18W3[i] == 2 & ALSA_w3_part_clubs$STIL19W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL20W3[i] == 2 & ALSA_w3_part_clubs$STIL21W3[i] == 2 & ALSA_w3_part_clubs$STIL22W3[i] == 2 & ALSA_w3_part_clubs$STIL23W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL24W3[i] == 2 & ALSA_w3_part_clubs$STIL25W3[i] == 2 & ALSA_w3_part_clubs$STIL26W3[i] == 2 & ALSA_w3_part_clubs$STIL27W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL28W3[i] == 2 & ALSA_w3_part_clubs$STIL29W3[i] == 2 & ALSA_w3_part_clubs$STIL30W3[i] == 2 & ALSA_w3_part_clubs$STIL31W3[i] == 2 & 
      ALSA_w3_part_clubs$STIL32W3[i] == 2 & ALSA_w3_part_clubs$STIL33W3[i] == 2 & ALSA_w3_part_clubs$STIL34W3[i] == 2 ) ) { 
    ALSA_ds_w3$part_clubs[i] = 0 }
}

ALSA_ds_w3$part_clubs <- car::recode(as.vector(ALSA_ds_w3$part_clubs), "NA='999'")
ALSA_ds_w3$part_clubs <- labelled(ALSA_ds_w3$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}

vbl <- ALSA_ds_w3$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation3, echo=F}

```


### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`AAP19W6`|`How often have you participated in social activities at a centre such as a club, a church, or a community centre? (Bingo, senior citizens, RSL, a hotel, self-education courses.)`|`ALSA-Wave6`|`1 = less than once a month`<br/>`2 = about once a month`<br/>`3 = about once a week`<br/>`4 = more than once a week`|`0 = no answer`|

**Description**

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_part_clubs','ALSA.ALSA-Wave6', variables=list('AAP19W6'), missings = TRUE)
ALSA_w6_part_clubs <- opal.execute(o,'ALSA_w6_part_clubs')
```

```{r local6, echo=F}

vbl <- ALSA_w6_part_clubs$AAP19W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'AAP19W6')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6_part_clubs, aes(x=factor(AAP19W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `1 into 0; 2,3,4 into 1; 0 into 995`
* `NA into 999`

**R script:**

```{r harmo6}
ALSA_ds_w6 <- tibble(id=ALSA_w6_part_clubs$id)
ALSA_ds_w6$part_clubs <- car::recode(as.vector(ALSA_w6_part_clubs$AAP19W6), "1='0'; 2:4='1'; 0='995'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}

vbl <- ALSA_ds_w6$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ALSA_ds_w6$part_clubs)
BeforeH <- table(ALSA_w6_part_clubs$AAP19W6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[2]]
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[1]]
BeforeH1[[4]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","0->995","NA->999")
kable(C)
```






### Wave 7

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`aap19w7`|`How often have you participated in social activities at a centre such as a club, a church, or a community centre? (Bingo, senior citizens, RSL, a hotel, self-education courses.)`|`ALSA-Wave7`|`1 = less than once a month`<br/>`2 = about once a month`<br/>`3 = about once a week`<br/>`4 = more than once a week`|`0 = no answer`<br/>`9 = Missing`|

**Description**


```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_part_clubs','ALSA.ALSA-Wave7',variables=list('aap19w7'), missings = TRUE)
ALSA_w7_part_clubs <- opal.execute(o,'ALSA_w7_part_clubs')
```

```{r local7, echo=F}

vbl <- ALSA_w7_part_clubs$aap19w7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'aap19w7')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7_part_clubs, aes(x=factor(aap19w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0; 2,3,4 into 1; 0 into 995; 9 into 999`
* `NA into 999`

**R script:**

```{r harmo7}

ALSA_ds_w7 <- tibble(id=ALSA_w7_part_clubs$id)
ALSA_ds_w7$part_clubs <- car::recode(as.vector(ALSA_w7_part_clubs$aap19w7), "1='0'; 2:4='1'; 0='995'; 9='999'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}

vbl <- ALSA_ds_w7$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ALSA_ds_w7$part_clubs)
BeforeH <- table(ALSA_w7_part_clubs$aap19w7, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[2]]
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[1]]
BeforeH1[[4]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","0->995","NA->999")
kable(C)
```





### Wave 8

Not found.



### Wave 9

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`AAP19W9`|`How often have you participated in social activities at a centre such as a club, a church, or a community centre? (Bingo, senior citizens, RSL, a hotel, self-education courses.)`|`ALSA-Wave9`|`1 = less than once a month`<br/>`2 = about once a month`<br/>`3 = about once a week`<br/>`4 = more than once a week`|`0 = no answer`|

**Description**


```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_part_clubs','ALSA.ALSA-Wave9',variables=list('AAP19W9'), missings = TRUE)
ALSA_w9_part_clubs <- opal.execute(o,'ALSA_w9_part_clubs')
```

```{r local9, echo=F}

vbl <- ALSA_w9_part_clubs$AAP19W9
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'AAP19W9')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9_part_clubs, aes(x=factor(AAP19W9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0; 2,3,4 into 1; 0 into 995`
* `NA into 999`

**R script:**

```{r harmo9}
ALSA_ds_w9 <- tibble(id=ALSA_w9_part_clubs$id)
ALSA_ds_w9$part_clubs <- car::recode(as.vector(ALSA_w9_part_clubs$AAP19W9), "1='0'; 2:4='1'; 0='995'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript9, echo=F}

vbl <- ALSA_ds_w9$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation9, echo=F}
AfterH <- table(ALSA_ds_w9$part_clubs)
BeforeH <- table(ALSA_w9_part_clubs$AAP19W9, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[2]]
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[1]]
BeforeH1[[4]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","0->995","NA->999")
kable(C)
```



### Wave 10

Not found.





### Wave 11

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`AAP19W11`|`How often have you participated in social activities at a centre such as a club, a church, or a community centre? (Bingo, senior citizens, RSL, a hotel, self-education courses.)`|`ALSA-Wave11`|`1 = less than once a month`<br/>`2 = about once a month`<br/>`3 = about once a week`<br/>`4 = more than once a week`||

**Description**


```{r assign11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11_part_clubs','ALSA.ALSA-Wave11', variables=list('AAP19W11'), missings = TRUE)
ALSA_w11_part_clubs <- opal.execute(o,'ALSA_w11_part_clubs')

```

```{r local11, echo=F}

vbl <- ALSA_w11_part_clubs$AAP19W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'AAP19W11')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11_part_clubs, aes(x=factor(AAP19W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0; 2,3,4 into 1`
* `NA into 999`

**R script:**

```{r harmo11}
ALSA_ds_w11 <- tibble(id=ALSA_w11_part_clubs$id)
ALSA_ds_w11$part_clubs <- car::recode(as.vector(ALSA_w11_part_clubs$AAP19W11), "1='0'; 2:4='1'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript11, echo=F}

vbl <- ALSA_ds_w11$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation11, echo=F}
AfterH <- table(ALSA_ds_w11$part_clubs)
BeforeH <- table(ALSA_w11_part_clubs$AAP19W11, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2:4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","NA->999")
kable(C)
```







### Wave 12

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|-|
|`AAP19W12`|`How often have you participated in social activities at a centre such as a club, a church, or a community centre? (Bingo, senior citizens, RSL, a hotel, self-education courses.)`|`ALSA-Wave12`|`1 = less than once a month`<br/>`2 = about once a month`<br/>`3 = about once a week`<br/>`4 = more than once a week`||

**Description**


```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_part_clubs','ALSA.ALSA-Wave12', variables=list('AAP19W12'), missings = TRUE)
ALSA_w12_part_clubs <- opal.execute(o,'ALSA_w12_part_clubs')
```

```{r local12, echo=F}

vbl <- ALSA_w12_part_clubs$AAP19W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'AAP19W12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12_part_clubs, aes(x=factor(AAP19W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0; 2,3,4 into 1`
* `NA into 999`

**R script:**

```{r harmo12}
ALSA_ds_w12 <- tibble(id=ALSA_w12_part_clubs$id)
ALSA_ds_w12$part_clubs <- car::recode(as.vector(ALSA_w12_part_clubs$AAP19W12), "1='0'; 2:4='1'; NA='999'")
```

#### Statistics of the new harmonised variable
```{r descript12, echo=F}

vbl <- ALSA_ds_w12$part_clubs
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation12, echo=F}
AfterH <- table(ALSA_ds_w12$part_clubs)
BeforeH <- table(ALSA_w12_part_clubs$AAP19W12, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2:4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","NA->999")
kable(C)
```





### Wave 13

Not found.



```{r final, echo=F}

l.hds <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w9 = ALSA_ds_w9, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","part_clubs")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","part_clubs")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  part_clubs <- l.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(l.hds)[index],"/part_clubs.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
