---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Australia

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVMENT`
* Label: `Bereavement`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings: 
    + `9.0 = Missing`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_bereav','ALSA.ALSA-Wave1',variables=list('BRVMENT'), missings = TRUE)
```

```{r local1, echo=F}
ALSA_w1_bereav <- opal.execute(o,'ALSA_w1_bereav')
vari <- ALSA_w1_bereav$BRVMENT 
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w1_bereav$BRVMENT, missing_values = NA)
ggplot(ALSA_w1_bereav, aes(x=factor(BRVMENT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bereavement") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `9 into 999`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_bereav$id)
ALSA_ds_w1$bereav <- car::recode(as.vector(ALSA_w1_bereav$BRVMENT), "1='1'; 2='0'; 9='999'; NA='999'")
ALSA_ds_w1$bereav <- labelled(ALSA_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ALSA_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ALSA_ds_w1$bereav)
BeforeH <- table(ALSA_w1_bereav$BRVMENT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[c(1,2)] <- BeforeH[c(2,1)]
BeforeH1[[3]] <- sum(BeforeH[c(3,4)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("2->0","1","9&NA->999")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `Q37`
* Label: `Have you lost anybody close to you?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2_bereav','ALSA.ALSA-Wave2', variables=list('Q37'), missings = TRUE)
```

```{r local2, echo=F}
ALSA_w2_bereav <- opal.execute(o,'ALSA_w2_bereav')
vari <- ALSA_w2_bereav$Q37 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w2_bereav$Q37, missing_values = NA)
ggplot(ALSA_w2_bereav, aes(x=factor(Q37))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she lost anybody close to him/her?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_bereav$id)
ALSA_ds_w2$bereav <- car::recode(as.vector(ALSA_w2_bereav$Q37), "1='1'; 2='0'; NA='999'")
ALSA_ds_w2$bereav <- labelled(ALSA_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ALSA_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ALSA_ds_w1$bereav)
BeforeH <- table(ALSA_w1_bereav$BRVMENT, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("2->0","1","NA->999")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVW3`
* Label: `BEREAVEMENT`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `9.0`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_bereav','ALSA.ALSA-Wave3',variables=list('BRVW3'), missings = TRUE)
```

```{r local3, echo=F}
ALSA_w3_bereav <- opal.execute(o,'ALSA_w3_bereav')
vari <- ALSA_w3_bereav$BRVW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w3_bereav$BRVW3, missing_values = NA)
ggplot(ALSA_w3_bereav, aes(x=factor(BRVW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bereavement") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_bereav$id)
ALSA_ds_w3$bereav <- car::recode(as.vector(ALSA_w3_bereav$BRVW3), "1='1'; 2='0'; 9='999'; NA='999'")
ALSA_ds_w3$bereav <- labelled(ALSA_ds_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ALSA_ds_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ALSA_ds_w3$bereav)
BeforeH <- table(ALSA_w3_bereav$BRVW3, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[c(1,2)] <- BeforeH[c(2,1)]
BeforeH1[[3]] <- sum(BeforeH[c(3,4)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("2->0","1","9&NA->999")
kable(C)
```

 
 




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVMTW4`
* Label: `HAVE YOU LOST ANYBODY CLOSE TO YOU?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `3.0 = Dont know`
  
* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4_bereav','ALSA.ALSA-Wave4',variables=list('BRVMTW4'), missings = TRUE)
```

```{r local4, echo=F}
ALSA_w4_bereav <- opal.execute(o,'ALSA_w4_bereav')
vari <- ALSA_w4_bereav$BRVMTW4
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(3))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w4_bereav$BRVMTW4, missing_values = NA)
ggplot(ALSA_w4_bereav, aes(x=factor(BRVMTW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she lost anybody close to him/her?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`
* `3 into 998`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_bereav$id)
ALSA_ds_w4$bereav <- car::recode(as.vector(ALSA_w4_bereav$BRVMTW4), "1='1'; 2='0'; 3='998'; NA='999'")
ALSA_ds_w4$bereav <- labelled(ALSA_ds_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ALSA_ds_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ALSA_ds_w4$bereav)
BeforeH <- table(ALSA_w4_bereav$BRVMTW4, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","3->998")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVMTW5`
* Label: `HAVE YOU LOST ANYBODY CLOSE TO YOU?`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`


* Name: `MARITW5`
* Label: `Q3 COULD YOU PLEASE TELL ME YOUR CURRENT MARITAL STATUS?`
* Categories: 
    + `1.0 = Married`
    + `2.0 = De facto`
    + `3.0 = Separated`
    + `4.0 = Divorced`
    + `5.0 = Widowed`
    + `6.0 = Never married`
    + `8.0 = Other`
* Missings:    
    + `7.0 = Refused (Do not read)`

* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5_bereav','ALSA.ALSA-Wave5',variables=list('BRVMTW5','MARITW5'), missings = TRUE)
```

```{r local5, echo=F}
ALSA_w5_bereav <- opal.execute(o,'ALSA_w5_bereav')
vari <- ALSA_w5_bereav$BRVMTW5 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w5_bereav$BRVMTW5, missing_values = NA)
ggplot(ALSA_w5_bereav, aes(x=factor(BRVMTW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she lost anybody close to him/her?") + ylab("Frequency")

vari <- ALSA_w5_bereav$MARITW5
kable(Categorical_summary(vari, missing_values = c(7))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(7))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(7))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w5_bereav$MARITW5, missing_values = NA)
ggplot(ALSA_w5_bereav, aes(x=factor(MARITW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `BRVMTW5=1 OR MARITW5=5 into 1`
* `BRVMTW5=2 AND MARITW5 in (1,2,3,4,6,8) into 0`
* `BRVMTW5=2 AND MARITW5=7 into 997`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_bereav$id)

ALSA_w5_bereav$MARITW5 <- car::recode(as.vector(ALSA_w5_bereav$MARITW5), "NA='-999'")
ALSA_w5_bereav$BRVMTW5 <- car::recode(as.vector(ALSA_w5_bereav$BRVMTW5), "NA='-999'")

ALSA_ds_w5$bereav <- c(NA)  
for(i in 1:dim(ALSA_w5_bereav)[1]){
  if(ALSA_w5_bereav$MARITW5[i] == 5 | ALSA_w5_bereav$BRVMTW5[i] == 1) { 
    ALSA_ds_w5$bereav[i] = 1 }
  else if(ALSA_w5_bereav$MARITW5[i] %in% c(1,2,3,4,6,8) & ALSA_w5_bereav$BRVMTW5[i] == 2) { 
    ALSA_ds_w5$bereav[i] = 0 }
  else if(ALSA_w5_bereav$MARITW5[i] == 7 & ALSA_w5_bereav$BRVMTW5[i] == 2) { 
    ALSA_ds_w5$bereav[i] = 997 }
}

ALSA_ds_w5$bereav <- car::recode(as.vector(ALSA_ds_w5$bereav), "NA='999'")
ALSA_ds_w5$bereav <- labelled(ALSA_ds_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ALSA_ds_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ALSA_ds_w5$bereav)
BeforeH <- table(ALSA_w5_bereav$BRVMTW5, ALSA_w5_bereav$MARITW5, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[1,]), sum(BeforeH[2,5]))
BeforeH1[[1]] <- sum(BeforeH[2,c(1,2,3,4,6)])
BeforeH1[[3]] <- BeforeH[2,7]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","7->997")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:
    
* Name: `BRVW6`
* Label: `lost anyone close in last 2 yrs`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `0.0 = no answer`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_bereav','ALSA.ALSA-Wave6',variables=list('BRVW6'), missings = TRUE)
```

```{r local6, echo=F}
ALSA_w6_bereav <- opal.execute(o,'ALSA_w6_bereav')
vari <- ALSA_w6_bereav$BRVW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w6_bereav$BRVW6, missing_values = NA)
ggplot(ALSA_w6_bereav, aes(x=factor(BRVW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she lost anybody close to him/her in last 2 years?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`
* `0 no answer into 995`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_bereav$id)
ALSA_ds_w6$bereav <- car::recode(as.vector(ALSA_w6_bereav$BRVW6), "1='1'; 2='0'; 0='995'; NA='999'")
ALSA_ds_w6$bereav <- labelled(ALSA_ds_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ALSA_ds_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ALSA_ds_w6$bereav)
BeforeH <- table(ALSA_w6_bereav$BRVW6, useNA='ifany')[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","0->995","NA->999")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `brvw7`
* Label: `lost anyone close in last 2 yrs`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `0.0 = Not Answered`
    + `9.0 = Missing`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_bereav','ALSA.ALSA-Wave7',variables=list('brvw7'), missings = TRUE)
```

```{r local7, echo=F}
ALSA_w7_bereav <- opal.execute(o,'ALSA_w7_bereav')
vari <- ALSA_w7_bereav$brvw7
kable(Categorical_summary(vari, missing_values = c(0,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0,9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w7_bereav$brvw7, missing_values = NA)
ggplot(ALSA_w7_bereav, aes(x=factor(brvw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she lost anybody close to him/her in last 2 years?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`
* `0 Not Answered into 995`
* `9 into 999`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_bereav$id)
ALSA_ds_w7$bereav <- car::recode(as.vector(ALSA_w7_bereav$brvw7), "1='1'; 2='0'; 0='995'; 9='999'; NA='999'")
ALSA_ds_w7$bereav <- labelled(ALSA_ds_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ALSA_ds_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ALSA_ds_w7$bereav)
BeforeH <- table(ALSA_w7_bereav$brvw7, useNA='ifany')[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","0->995","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `brvmtw8`
* Label: `excluding husband/wife have you lost anybody close to you through death in the last 12`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `0.0 = Not Answered`
    
* Name: `maritw8`
* Label: `Marital status`
* Categories: 
    + `1.0 = Married`
    + `2.0 = De facto`
    + `3.0 = Separated`
    + `4.0 = Divorced`
    + `5.0 = Widowed`
    + `6.0 = Never married`
* Missings:    
    + `0.0 = Not Answered`

* Description: 
```{r assign8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8_bereav','ALSA.ALSA-Wave8',variables=list('brvmtw8','maritw8'), missings = TRUE)
```

```{r local8, echo=F}
ALSA_w8_bereav <- opal.execute(o,'ALSA_w8_bereav')

vari <- ALSA_w8_bereav$brvmtw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w8_bereav$brvmtw8, missing_values = NA)
ggplot(ALSA_w8_bereav, aes(x=factor(brvmtw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Excluding husband/wife has he/she lost anybody close to him/her in the last 12 months?") + ylab("Frequency")

vari <- ALSA_w8_bereav$maritw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w8_bereav$maritw8, missing_values = NA)
ggplot(ALSA_w8_bereav, aes(x=factor(maritw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `maritw8 = 5 OR brvmtw8 = 1 into 1`
* `maritw8 in (1,2,3,4,6) AND brvmtw8 = 2 into 0`
* `maritw8 = 0 AND brvmtw8 = 2 into 995`
* `maritw8 in (1,2,3,4,6) AND brvmtw8 = 0 into 995`
* `maritw8 = 0 AND brvmtw8 = 0 into 995`
* `NA into 999`

**R script:**

```{r harmo8, echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_bereav$id)

ALSA_w8_bereav$maritw8 <- car::recode(as.vector(ALSA_w8_bereav$maritw8), "NA='-999'")
ALSA_w8_bereav$brvmtw8 <- car::recode(as.vector(ALSA_w8_bereav$brvmtw8), "NA='-999'")

ALSA_ds_w8$bereav <- c(NA)  
for(i in 1:dim(ALSA_w8_bereav)[1]){
if(ALSA_w8_bereav$maritw8[i] == 5 | ALSA_w8_bereav$brvmtw8[i] == 1) { 
  ALSA_ds_w8$bereav[i] = 1 }
else if(ALSA_w8_bereav$maritw8[i] %in% c(1,2,3,4,6) & ALSA_w8_bereav$brvmtw8[i] == 2) { 
  ALSA_ds_w8$bereav[i] = 0 }
else if(ALSA_w8_bereav$maritw8[i] == 0 & ALSA_w8_bereav$brvmtw8[i] == 2) { 
  ALSA_ds_w8$bereav[i] = 995 }
else if(ALSA_w8_bereav$maritw8[i] %in% c(1,2,3,4,6) & ALSA_w8_bereav$brvmtw8[i] == 0) { 
  ALSA_ds_w8$bereav[i] = 995 }
else if(ALSA_w8_bereav$maritw8[i] == 0 & ALSA_w8_bereav$brvmtw8[i] == 0) { 
  ALSA_ds_w8$bereav[i] = 995 }
}

ALSA_ds_w8$bereav <- car::recode(as.vector(ALSA_ds_w8$bereav), "NA='999'")
ALSA_ds_w8$bereav <- labelled(ALSA_ds_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8, echo=F}
vari <- ALSA_ds_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8, echo=F}
AfterH <- table(ALSA_ds_w8$bereav)
BeforeH <- table(ALSA_w8_bereav$brvmtw8, ALSA_w8_bereav$maritw8, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[3,c(2,3,4,6)])
BeforeH1[[2]] <- sum(sum(BeforeH[2,]), sum(BeforeH[c(1,3),5]))
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVW9`
* Label: `lost anyone close to you through death in last 3 yrs`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `0.0 = Not Answered`

* Description: 
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_bereav','ALSA.ALSA-Wave9',variables=list('BRVW9'), missings = TRUE)
```

```{r local9, echo=F}
ALSA_w9_bereav <- opal.execute(o,'ALSA_w9_bereav')
vari <- ALSA_w9_bereav$BRVW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w9_bereav$BRVW9, missing_values = NA)
ggplot(ALSA_w9_bereav, aes(x=factor(BRVW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("has he/she lost anybody close to him/her in the last 3 years?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`
* `0 Not Answered into 995`
* `NA into 999`

**R script:**

```{r harmo9, echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_bereav$id)
ALSA_ds_w9$bereav <- car::recode(as.vector(ALSA_w9_bereav$BRVW9), "1='1'; 2='0'; 0='995'; NA='999'")
ALSA_ds_w9$bereav <- labelled(ALSA_ds_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9, echo=F}
vari <- ALSA_ds_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9, echo=F}
AfterH <- table(ALSA_ds_w9$bereav)
BeforeH <- table(ALSA_w9_bereav$BRVW9, useNA='ifany')[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","0->995","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `brvw10`
* Label: `have you lost anybody close to you through death in the last 12`
* Categories: 
    + `0.0 = No`
    + `1.0 = Yes`
* Missings:    
    + `99.0 = Not Answered`

* Description: 
```{r assign10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10_bereav','ALSA.ALSA-Wave10',variables=list('brvw10'), missings = TRUE)
```

```{r local10, echo=F}
ALSA_w10_bereav <- opal.execute(o,'ALSA_w10_bereav')
vari <- ALSA_w10_bereav$brvw10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w10_bereav$brvw10, missing_values = NA)
ggplot(ALSA_w10_bereav, aes(x=factor(brvw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Lost anyone close to him/her through death in last 12 months?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `leave as it is, but 99 recode into 995 and NA into 999`

**R script:**

```{r harmo10, echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_bereav$id)
ALSA_ds_w10$bereav <- car::recode(as.vector(ALSA_w10_bereav$brvw10), "1='1'; 0='0'; 99='995'; NA='999'")
ALSA_ds_w10$bereav <- labelled(ALSA_ds_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10, echo=F}
vari <- ALSA_ds_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10, echo=F}
AfterH <- table(ALSA_ds_w10$bereav)
BeforeH <- table(ALSA_w10_bereav$brvw10, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVW11`
* Label: `lost anyone close to you through death in last 12 months`
* Categories: 
    + `0.0 = No`
    + `1.0 = Yes`

    
* Description: 
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_bereav','ALSA.ALSA-Wave11',variables=list('BRVW11'), missings = TRUE)
```

```{r local11, echo=F}
ALSA_w11_bereav <- opal.execute(o,'ALSA_w11_bereav')
vari <- ALSA_w11_bereav$BRVW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w11_bereav$BRVW11, missing_values = NA)
ggplot(ALSA_w11_bereav, aes(x=factor(BRVW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Lost anyone close to him/her through death in last 12 months?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `leave as it is but NA into 999`

**R script:**

```{r harmo11, echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_bereav$id)
ALSA_ds_w11$bereav <- car::recode(as.vector(ALSA_w11_bereav$BRVW11), "NA='999'")
ALSA_ds_w11$bereav <- labelled(ALSA_ds_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=F}
vari <- ALSA_ds_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11, echo=F}
AfterH <- table(ALSA_ds_w11$bereav)
BeforeH <- table(ALSA_w11_bereav$BRVW11, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


### Wave 12

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVW11`
* Label: `lost anyone close to you through death in last 12 months`
* Categories: 
    + `0.0 = No`
    + `1.0 = Yes`
    
* Description: 
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_bereav','ALSA.ALSA-Wave12',variables=list('BRVW12'), missings = TRUE)
```

```{r local12, echo=F}
ALSA_w12_bereav <- opal.execute(o,'ALSA_w12_bereav')
vari <- ALSA_w12_bereav$BRVW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w12_bereav$BRVW12, missing_values = NA)
ggplot(ALSA_w12_bereav, aes(x=factor(BRVW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Lost anyone close to him/her through death in last 12 months?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `leave as it is but NA into 999`

**R script:**

```{r harmo12, echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_bereav$id)
ALSA_ds_w12$bereav <- car::recode(as.vector(ALSA_w12_bereav$BRVW12), "NA='999'")
ALSA_ds_w12$bereav <- labelled(ALSA_ds_w12$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript12, echo=F}
vari <- ALSA_ds_w12$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12, echo=F}
AfterH <- table(ALSA_ds_w12$bereav)
BeforeH <- table(ALSA_w12_bereav$BRVW12, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 




### Wave 13

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BRVW13`
* Label: `lost anyone close to you through death in last 12 months`
* Categories: 
    + `0.0 = No`
    + `1.0 = Yes`
    
* Description: 
```{r assign13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13_bereav','ALSA.ALSA-Wave13', variables=list('BRVW13'), missings = TRUE)
```

```{r local13, echo=F}
ALSA_w13_bereav <- opal.execute(o,'ALSA_w13_bereav')
vari <- ALSA_w13_bereav$BRVW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w13_bereav$BRVW13, missing_values = NA)
ggplot(ALSA_w13_bereav, aes(x=factor(BRVW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Lost anyone close to him/her through death in last 12 months?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `leave as it is but NA into 999`

**R script:**

```{r harmo13, echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_bereav$id)
ALSA_ds_w13$bereav <- car::recode(as.vector(ALSA_w13_bereav$BRVW13), "NA='999'")
ALSA_ds_w13$bereav <- labelled(ALSA_ds_w13$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript13, echo=F}
vari <- ALSA_ds_w13$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w13$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w13, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation13, echo=F}
AfterH <- table(ALSA_ds_w13$bereav)
BeforeH <- table(ALSA_w13_bereav$BRVW13, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 
```{r save, echo=FALSE}
bereav <- ALSA_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w3
save(bereav, file = "../RData/w3/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w4
save(bereav, file = "../RData/w4/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w5
save(bereav, file = "../RData/w5/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w6
save(bereav, file = "../RData/w6/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w7
save(bereav, file = "../RData/w7/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w8
save(bereav, file = "../RData/w8/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w9
save(bereav, file = "../RData/w9/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w10
save(bereav, file = "../RData/w10/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w11
save(bereav, file = "../RData/w11/bereav.RData")
rm(bereav)

bereav <- ALSA_ds_w12
save(bereav, file = "../RData/w12/bereav.RData")
rm(bereav)


bereav <- ALSA_ds_w13
save(bereav, file = "../RData/w13/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
