---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Australia
### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `CHILDREN`
* Label: `How many children do or did you have (including stepchildren and adopted children)?`
* Missings: 
    + `99 = Missing`
    
    
    
* Name: `SSTLALV`
* Label: `How many sons are still alive?  `
* Missings: 
    + `99 = Missing`
    
* Name: `DSTLALV`
* Label: `How many daughters are still alive?`
* Missings: 
    + `99 = Missing`
    
    
* Name: `GRANDCH`
* Label: `Do you have any grandchildren`
* Categories:
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `9 = Missing`
        

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_child','ALSA.ALSA-Wave1',variables=list('CHILDREN','SSTLALV','DSTLALV','GRANDCH'), missings = TRUE)
```

```{r local1, echo=F}
ALSA_w1_child <- opal.execute(o,'ALSA_w1_child')

vari <- ALSA_w1_child$CHILDREN
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w1_child$CHILDREN, missing_values = NA)
ggplot(ALSA_w1_child, aes(x=factor(CHILDREN))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")

vari <-  ALSA_w1_child$SSTLALV
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w1_child$SSTLALV, missing_values = NA)
ggplot(ALSA_w1_child, aes(x=factor(SSTLALV))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of sons still alive") + ylab("Frequency")

vari <- ALSA_w1_child$DSTLALV
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w1_child$DSTLALV[i] == 0 , missing_values = NA)
ggplot(ALSA_w1_child, aes(x=factor(DSTLALV))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of daughters still alive") + ylab("Frequency")

vari <- ALSA_w1_child$GRANDCH
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Continuous_summary(var = ALSA_w1_child$GRANDCH, missing_values = NA)
ggplot(ALSA_w1_child, aes(x=factor(GRANDCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `CHILDREN: `
* `CHILDREN=0 into 0`
* `(CHILDREN=1:hi and SSTLALV=0 and DSTLALV=0) into 0`
* `(CHILDREN=1:hi and (SSTLALV=1:hi OR DSTLALV=1:hi) into 1`
* `99 and NA into 999`


* `GRANDCHILDREN: `
* `2 into 0; 1 into 1; 9 and NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_child$id)

ALSA_w1_child$CHILDREN <- car::recode(as.vector(ALSA_w1_child$CHILDREN), "NA='-999'")
ALSA_w1_child$SSTLALV <- car::recode(as.vector(ALSA_w1_child$SSTLALV), "NA='-999'")
ALSA_w1_child$DSTLALV <- car::recode(as.vector(ALSA_w1_child$DSTLALV), "NA='-999'")

ALSA_ds_w1$child <- c(NA)  
for(i in 1:dim(ALSA_w1_child)[1]){
  if(ALSA_w1_child$CHILDREN[i] == 0 | (ALSA_w1_child$CHILDREN[i] >0 & ALSA_w1_child$SSTLALV[i] == 0 & ALSA_w1_child$DSTLALV[i] == 0)) {
    ALSA_ds_w1$child[i] = 0 }
  else if( ALSA_w1_child$CHILDREN[i] > 0 & (ALSA_w1_child$SSTLALV[i] >0 | ALSA_w1_child$DSTLALV[i]>0)) {
    ALSA_ds_w1$child[i] = 1 }
}
ALSA_ds_w1$child <- car::recode(as.vector(ALSA_ds_w1$child), "NA='999'")
ALSA_ds_w1$child <- labelled(ALSA_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

ALSA_ds_w1$grchild <- car::recode(as.vector(ALSA_w1_child$GRANDCH), "2='0'; 1='1'; 9='999'; NA='999'")
ALSA_ds_w1$grchild <- labelled(ALSA_ds_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ALSA_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ALSA_ds_w1$grchild)
BeforeH <- table(ALSA_w1_child$GRANDCH, useNA='ifany')
BeforeH[[3]] <- sum(BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","9&NA->999")
kable(C, caption = "grchild")

```

 
 

### Wave 2
Not found.

### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `LIVCHW3`
* Label: `How many living children do you (or your husband-wife-partner) have?`
* Missings:
    + `99  `
    
* Name: `HMGDCHW3`
* Label: 'How many living grandchildren do you (or your husband -wife - partner) have?                                                      `
* Missings:
    + `99  `

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_child','ALSA.ALSA-Wave3',variables=list('LIVCHW3','HMGDCHW3'), missings = TRUE)
```

```{r local3, echo=F}
ALSA_w3_child <- opal.execute(o,'ALSA_w3_child')

vari <- ALSA_w3_child$LIVCHW3
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w3_child$LIVCHW3, missing_values = NA)
ggplot(ALSA_w3_child, aes(x=factor(LIVCHW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number living children") + ylab("Frequency")

vari <- ALSA_w3_child$HMGDCHW3
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w3_child$HMGDCHW3, missing_values = NA)
ggplot(ALSA_w3_child, aes(x=factor(HMGDCHW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number living grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `CHILDREN and GRANDCHILDREN`
* `0 into 0; 1-30 into 1; 99 into 999; 999 into 999; NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_child$id)
ALSA_ds_w3$child <- car::recode(as.vector(ALSA_w3_child$LIVCHW3), "0='0'; 99='999'; 999='999'; NA='999'; 1:hi='1'")
ALSA_ds_w3$child <- labelled(ALSA_ds_w3$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w3$grchild <- car::recode(as.vector(ALSA_w3_child$HMGDCHW3), "0='0'; 99='999'; 999='999'; NA='999'; 1:hi='1'")
ALSA_ds_w3$grchild <- labelled(ALSA_ds_w3$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ALSA_ds_w3$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w3$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w3$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w3$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ALSA_ds_w3$grchild)
BeforeH <- table(ALSA_w3_child$HMGDCHW3, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:31)])
BeforeH[[3]] <- sum(BeforeH[c(32,33)])
BeforeH <- BeforeH[c(1,2,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","999&NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w3$child)
BeforeH2 <- table(ALSA_w3_child$LIVCHW3, useNA='ifany')
BeforeH2[[2]] <- sum(BeforeH2[c(2:12)])
BeforeH2[[3]] <- sum(BeforeH2[c(13,14)])
BeforeH2 <- BeforeH2[c(1,2,3)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","99&NA->999")
kable(C, caption = "child")
```

 
 

### Wave 4
Not found.

### Wave 5
Not found.

### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `LIVCHW6`
* Label: `How many living children do you (or your husband-wife-partner) have?`
* Missings:    
    + `0.0 = no answer`

* Name: `GRANCHW6`
* Label: `Do you have any grandchildren?`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `0 = no answer`


* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6_child','ALSA.ALSA-Wave6',variables=list('LIVCHW6','GRANCHW6'), missings = TRUE)
```

```{r local6, echo=F}
ALSA_w6_child <- opal.execute(o,'ALSA_w6_child')

vari <- ALSA_w6_child$LIVCHW6
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w6_child$LIVCHW6, missing_values = NA)
ggplot(ALSA_w6_child, aes(x=factor(LIVCHW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living children") + ylab("Frequency")

vari <-  ALSA_w6_child$GRANCHW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w6_child$GRANCHW6, missing_values = NA)
ggplot(ALSA_w6_child, aes(x=factor(GRANCHW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `CHILDREN`
* `0 into 0; 1-30 into 1`

* `GRANDCHILDREN`
* `2 into 0; 1 into 1; 0 into 995`

* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_child$id)

ALSA_ds_w6$child <- car::recode(as.vector(ALSA_w6_child$LIVCHW6), "0='0'; NA='999'; 1:hi='1'")
ALSA_ds_w6$child <- labelled(ALSA_ds_w6$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w6$grchild <- car::recode(as.vector(ALSA_w6_child$GRANCHW6), "2='0'; 1='1'; 0='995'; NA='999'")
ALSA_ds_w6$grchild <- labelled(ALSA_ds_w6$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ALSA_ds_w6$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w6$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w6$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w6$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH1 <- table(ALSA_ds_w6$grchild)
BeforeH1 <- table(ALSA_w6_child$GRANCHW6, useNA='ifany')
BeforeH1 <- BeforeH1[c(3,2,1,4)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","0->995","NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w6$child)
BeforeH2 <- table(ALSA_w6_child$LIVCHW6, useNA='ifany')
BeforeH2[[2]] <- sum(BeforeH2[c(2:11)])
BeforeH2 <- BeforeH2[c(1,2,12)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "child")
```

 
 



### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `livchw7`
* Label: `how many living children do you and your spouse have`

* Name: `granchw7`
* Label: `Do you have any grandchildren?`
* Categories:
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `0 = Not answered`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_child','ALSA.ALSA-Wave7',variables=list('livchw7','granchw7'), missings = TRUE)
```

```{r local7, echo=F}
ALSA_w7_child <- opal.execute(o,'ALSA_w7_child')

vari <- ALSA_w7_child$livchw7
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w7_child$livchw7, missing_values = NA)
ggplot(ALSA_w7_child, aes(x=factor(livchw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living children does he/she and his/her spouse have") + ylab("Frequency")

vari <- ALSA_w7_child$granchw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w7_child$granchw7, missing_values = NA)
ggplot(ALSA_w7_child, aes(x=factor(granchw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have any grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `CHILDREN`
* `0 into 0; 1-30 into 1`

* `GRANDCHILDREN`
* `2 into 0; 1 into 1; 0 into 995`

* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_child$id)

ALSA_ds_w7$child <- car::recode(as.vector(ALSA_w7_child$livchw7), "0='0'; NA='999'; 1:hi='1'")
ALSA_ds_w7$child <- labelled(ALSA_ds_w7$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w7$grchild <- car::recode(as.vector(ALSA_w7_child$granchw7), "1='1'; 2='0'; 0='995'; NA='999'")
ALSA_ds_w7$grchild <- labelled(ALSA_ds_w7$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ALSA_ds_w7$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w7$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w7$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w7$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH1 <- table(ALSA_ds_w7$grchild)
BeforeH1 <- table(ALSA_w7_child$granchw7, useNA='ifany')
BeforeH1 <- BeforeH1[c(3,2,1,4)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","0->995","NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w7$child)
BeforeH2 <- table(ALSA_w7_child$livchw7, useNA='ifany')
BeforeH2[[2]] <- sum(BeforeH2[c(2:9)])
BeforeH2 <- BeforeH2[c(1,2,10)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "child")
```

 
 

### Wave 8
Not found.

### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `LIVCHW9`
* Label: `how many living children do you and your spouse have`

* Name: `GRANCHW9`
* Label: `Do you have any grandchildren?`
* Categories:
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `0 = Not answered`

* Description: 
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_child','ALSA.ALSA-Wave9',variables=list('LIVCHW9','GRANCHW9'), missings = TRUE)
```

```{r local9, echo=F}
ALSA_w9_child <- opal.execute(o,'ALSA_w9_child')

vari <- ALSA_w9_child$LIVCHW9
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ALSA_w9_child$LIVCHW9, missing_values = NA)
ggplot(ALSA_w9_child, aes(x=factor(LIVCHW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living children does he/she and his/her spouse have") + ylab("Frequency")

vari <- ALSA_w9_child$GRANCHW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w9_child$GRANCHW9, missing_values = NA)
ggplot(ALSA_w9_child, aes(x=factor(GRANCHW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `CHILDREN`
* `0 into 0; 1-30 into 1`

* `GRANDCHILDREN`
* `2 into 0; 1 into 1; 0 into 995`

* `NA into 999`

**R script:**

```{r harmo9, echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_child$id)

ALSA_ds_w9$child <- car::recode(as.vector(ALSA_w9_child$LIVCHW9), "0='0'; NA='999'; 1:hi='1'")
ALSA_ds_w9$child <- labelled(ALSA_ds_w9$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w9$grchild <- car::recode(as.vector(ALSA_w9_child$GRANCHW9), "1='1'; 2='0'; 0='995'; NA='999'")
ALSA_ds_w9$grchild <- labelled(ALSA_ds_w9$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9, echo=F}
vari <- ALSA_ds_w9$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w9$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9, echo=F}
AfterH1 <- table(ALSA_ds_w9$grchild)
BeforeH1 <- table(ALSA_w9_child$GRANCHW9, useNA='ifany')
BeforeH1 <- BeforeH1[c(3,2,1,4)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","0->995","NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w9$child)
BeforeH2 <- table(ALSA_w9_child$LIVCHW9, useNA='ifany')
BeforeH2[[2]] <- sum(BeforeH2[c(2:8)])
BeforeH2 <- BeforeH2[c(1,2,9)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "child")
```

 
 

### Wave 10
Not found.

### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `LIVCHW11`
* Label: `Do you and your spouse have any living children`
* Categories:
    + `0 = No`
    + `1 = Yes`

* Name: `GRANCHW11`
* Label: `Do you have any grandchildren?`
* Categories:
    + `0 = No`
    + `1 = Yes`

    
* Description: 
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_child','ALSA.ALSA-Wave11',variables=list('LIVCHW11','GRANCHW11'), missings = TRUE)
```

```{r local11, echo=F}
ALSA_w11_child <- opal.execute(o,'ALSA_w11_child')

vari <- ALSA_w11_child$LIVCHW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w11_child$LIVCHW11, missing_values = NA)
ggplot(ALSA_w11_child, aes(x=factor(LIVCHW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Does he/she and his/her spouse have any living children") + ylab("Frequency")

vari <- ALSA_w11_child$GRANCHW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w11_child$GRANCHW11, missing_values = NA)
ggplot(ALSA_w11_child, aes(x=factor(GRANCHW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `as they are, but NA into 999`

**R script:**

```{r harmo11, echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_child$id)

ALSA_ds_w11$child <- car::recode(as.vector(ALSA_w11_child$LIVCHW11), "NA='999'")
ALSA_ds_w11$child <- labelled(ALSA_ds_w11$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w11$grchild <- car::recode(as.vector(ALSA_w11_child$GRANCHW11), "NA='999'")
ALSA_ds_w11$grchild <- labelled(ALSA_ds_w11$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=F}
vari <- ALSA_ds_w11$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w11$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11, echo=F}
AfterH1 <- table(ALSA_ds_w11$grchild)
BeforeH1 <- table(ALSA_w11_child$GRANCHW11, useNA='ifany')
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w11$child)
BeforeH2 <- table(ALSA_w11_child$LIVCHW11, useNA='ifany')
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "child")
```

 
 


### Wave 12

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `LIVCHW12`
* Label: `Do you and your spouse have any living children`
* Categories:
    + `0 = No`
    + `1 = Yes`

* Name: `GRANCHW12`
* Label: `Do you have any grandchildren?`
* Categories:
    + `0 = No`
    + `1 = Yes`

    
* Description: 
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_child','ALSA.ALSA-Wave12',variables=list('LIVCHW12','GRANCHW12'), missings = TRUE)
```

```{r local12, echo=F}
ALSA_w12_child <- opal.execute(o,'ALSA_w12_child')

vari <- ALSA_w12_child$LIVCHW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w12_child$LIVCHW12, missing_values = NA)
ggplot(ALSA_w12_child, aes(x=factor(LIVCHW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Does he/she and his/her spouse have any living children") + ylab("Frequency")

vari <- ALSA_w12_child$GRANCHW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w12_child$GRANCHW12, missing_values = NA)
ggplot(ALSA_w12_child, aes(x=factor(GRANCHW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any grandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `as they are, but NA into 999`

**R script:**

```{r harmo12, echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_child$id)

ALSA_ds_w12$child <- car::recode(as.vector(ALSA_w12_child$LIVCHW12), "NA='999'")
ALSA_ds_w12$child <- labelled(ALSA_ds_w12$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ALSA_ds_w12$grchild <- car::recode(as.vector(ALSA_w12_child$GRANCHW12), "NA='999'")
ALSA_ds_w12$grchild <- labelled(ALSA_ds_w12$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript12, echo=F}
vari <- ALSA_ds_w12$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ALSA_ds_w12$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12, echo=F}
AfterH1 <- table(ALSA_ds_w12$grchild)
BeforeH1 <- table(ALSA_w12_child$GRANCHW12, useNA='ifany')
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "grchild")

AfterH2 <- table(ALSA_ds_w12$child)
BeforeH2 <- table(ALSA_w12_child$LIVCHW12, useNA='ifany')
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("0","1","NA->999")
kable(C, caption = "child")
```


### Wave 13

Not found.
 
```{r save, echo=FALSE}
child <- ALSA_ds_w1[,-3]
save(child, file = "../RData/w1/child.RData")
rm(child)

child <- ALSA_ds_w3[,-3]
save(child, file = "../RData/w3/child.RData")
rm(child)

child <- ALSA_ds_w6[,-3]
save(child, file = "../RData/w6/child.RData")
rm(child)

child <- ALSA_ds_w7[,-3]
save(child, file = "../RData/w7/child.RData")
rm(child)


child <- ALSA_ds_w9[,-3]
save(child, file = "../RData/w9/child.RData")
rm(child)


child <- ALSA_ds_w11[,-3]
save(child, file = "../RData/w11/child.RData")
rm(child)

child <- ALSA_ds_w12[,-3]
save(child, file = "../RData/w12/child.RData")
rm(child)


grchild <- ALSA_ds_w1[,-2]
save(grchild, file = "../RData/w1/grchild.RData")
rm(grchild)

grchild <- ALSA_ds_w3[,-2]
save(grchild, file = "../RData/w3/grchild.RData")
rm(grchild)

grchild <- ALSA_ds_w6[,-2]
save(grchild, file = "../RData/w6/grchild.RData")
rm(grchild)

grchild <- ALSA_ds_w7[,-2]
save(grchild, file = "../RData/w7/grchild.RData")
rm(grchild)


grchild <- ALSA_ds_w9[,-2]
save(grchild, file = "../RData/w9/grchild.RData")
rm(grchild)


grchild <- ALSA_ds_w11[,-2]
save(grchild, file = "../RData/w11/grchild.RData")
rm(grchild)

grchild <- ALSA_ds_w12[,-2]
save(grchild, file = "../RData/w12/grchild.RData")
rm(grchild)
```



# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```