---
title: "Contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```


<!-- ########################################################## --> 

# Data process

## Australia

### Wave 1 

#### Study-specific variable description


| **Name** |`CONTFRND`|
|-|-|
| **Label** |`Contact with friends`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Amost every day`<br/>`2 = A few times a week`<br/>`3 = Once a week`<br/>`4 = Few times a month`<br/>`5 = Once a month`<br/>`6 = Every few months`<br/>`7 = Once a year`<br/>`8 = Less often`<br/>`9 = Never`|
| **Missings** |`99 = Missing`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1_cont_fr','ALSA.ALSA-Wave1',variables=list('CONTFRND'), missings = TRUE)
```

```{r local1, echo=F}
ALSA_w1_cont_fr <- opal.execute(o,'ALSA_w1_cont_fr')
vari <- ALSA_w1_cont_fr$CONTFRND
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w1_cont_fr$CONTFRND, missing_values = NA)
ggplot(ALSA_w1_cont_fr, aes(x=factor(CONTFRND))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `CONTFRND in (1,2,3,4,5) into 1`
* `CONTFRND in (6,7,8,9) into 0`
* `99 and NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_cont_fr$id)
ALSA_ds_w1$cont_fr <- car::recode(as.vector(ALSA_w1_cont_fr$CONTFRND), "1:5='1'; 6:9='0'; 99='999'; NA='999'")
ALSA_ds_w1$cont_fr <- labelled(ALSA_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

 
```{r descript1, echo=F}
vari <- ALSA_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ALSA_ds_w1$cont_fr)
BeforeH1 <- table(ALSA_w1_cont_fr$CONTFRND, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- sum(BeforeH1[c('6':'9')])
BeforeH[[2]] <- sum(BeforeH1[c('1':'5')])
BeforeH[[3]] <- sum(BeforeH1[c(length(BeforeH1),length(BeforeH1)-1)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6:9->0","1:5->1","99&NA->999")

kable(C)
```


### Wave 2
Not found.

### Wave 3
Not found.

### Wave 4
Not found.

### Wave 5
Not found.

### Wave 6
Not found.

### Wave 7
Not found.

### Wave 8
Not found.


### Wave 9

#### Study-specific variable description



| **Name** |`CONTFRNDW9`|
|-|-|
| **Label** |`face to face contact with friends`|
| **Table name** |`ALSA-Wave9`|
| **Categories** |`1 = More than once per week`<br/>`2 = Once a week`<br/>`3 = 2 or 3 times a month`<br/>`4 = Almost once a month`<br/>`5 = Less than once a month`<br/>`6 = Never`|
| **Missings** |`0 = Not Answered`|
| **Description** |  |


```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9_cont_fr','ALSA.ALSA-Wave9',variables=list('CONTFRNDW9'), missings = TRUE)
```

```{r local9, echo=F}
ALSA_w9_cont_fr <- opal.execute(o,'ALSA_w9_cont_fr')
vari <- ALSA_w1_cont_fr$CONTFRND
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w9_cont_fr$CONTFRNDW9, missing_values = NA)
ggplot(ALSA_w9_cont_fr, aes(x=factor(CONTFRNDW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("face to face contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2,3 or 4 into 1`
* `5 or 6 into 0`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo9, echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_cont_fr$id)
ALSA_ds_w9$cont_fr <- car::recode(as.vector(ALSA_w9_cont_fr$CONTFRNDW9), "1:4='1'; 5:6='0'; 0='995'; NA='999'")
ALSA_ds_w9$cont_fr <- labelled(ALSA_ds_w9$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

 
```{r descript9, echo=F}
vari <- ALSA_ds_w9$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9, echo=F}
AfterH <- table(ALSA_ds_w9$cont_fr)
BeforeH1 <- table(ALSA_w9_cont_fr$CONTFRNDW9, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- sum(BeforeH1[c('5','6')])
BeforeH[[2]] <- sum(BeforeH1[c('1':'4')])
BeforeH[[3]] <- BeforeH1[['0']]
BeforeH[[4]] <- BeforeH1[[length(BeforeH1)]]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5:6->0","1:5->1","0->995","NA->999")

kable(C)
```

### Wave 10
Not found.


### Wave 11

#### Study-specific variable description



| **Name** |`CONTFRNDW11`|
|-|-|
| **Label** |`face to face contact with friends`|
| **Table name** |`ALSA-Wave11`|
| **Categories** |`1 = More than once per week`<br/>`2 = Once a week`<br/>`3 = Two or 3 times a month`<br/>`4 = Almost once a month`<br/>`5 = Less than once a month`<br/>`6 = Never`|
| **Description** |  |
    
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11_cont_fr','ALSA.ALSA-Wave11',variables=list('CONTFRNDW11'), missings = TRUE)
```

```{r local11, echo=F}
ALSA_w11_cont_fr <- opal.execute(o,'ALSA_w11_cont_fr')
vari <- ALSA_w11_cont_fr$CONTFRNDW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w11_cont_fr$CONTFRNDW11, missing_values = NA)
ggplot(ALSA_w11_cont_fr, aes(x=factor(CONTFRNDW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("face to face contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2,3 or 4 into 1`
* `5 or 6 into 0`
* `NA into 999`

**R script:**

```{r harmo11, echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_cont_fr$id)
ALSA_ds_w11$cont_fr <- car::recode(as.vector(ALSA_w11_cont_fr$CONTFRNDW11), "1:4='1'; 5:6='0'; NA='999'")
ALSA_ds_w11$cont_fr <- labelled(ALSA_ds_w11$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

 
```{r descript11, echo=F}
vari <- ALSA_ds_w11$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11, echo=F}
AfterH <- table(ALSA_ds_w11$cont_fr)
BeforeH1 <- table(ALSA_w11_cont_fr$CONTFRNDW11, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- sum(BeforeH1[c('5','6')])
BeforeH[[2]] <- sum(BeforeH1[c('1':'4')])
BeforeH[[3]] <- BeforeH1[[length(BeforeH1)]]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5:6->0","1:5->1","NA->999")

kable(C)
```


### Wave 12

#### Study-specific variable description


| **Name** |`CONTFRNDW12`|
|-|-|
| **Label** |`face to face contact with friends`|
| **Table name** |`ALSA-Wave12`|
| **Categories** |`1 = More than once per week`<br/>`2 = Once a week`<br/>`3 = Two or 3 times a month`<br/>`4 = Almost once a month`<br/>`5 = Less than once a month`<br/>`6 = Never`|
| **Description** |  |

 
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12_cont_fr','ALSA.ALSA-Wave12',variables=list('CONTFRNDW12'), missings = TRUE)
```

```{r local12, echo=F}
ALSA_w12_cont_fr <- opal.execute(o,'ALSA_w12_cont_fr')
vari <- ALSA_w12_cont_fr$CONTFRNDW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w12_cont_fr$CONTFRNDW12, missing_values = NA)
ggplot(ALSA_w12_cont_fr, aes(x=factor(CONTFRNDW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("face to face contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2,3 or 4 into 1`
* `5 or 6 into 0`
* `NA into 999`

**R script:**

```{r harmo12, echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_cont_fr$id)
ALSA_ds_w12$cont_fr <- car::recode(as.vector(ALSA_w12_cont_fr$CONTFRNDW12), "1:4='1'; 5:6='0'; NA='999'")
ALSA_ds_w12$cont_fr <- labelled(ALSA_ds_w12$cont_fr, labels = c("lack of friends"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

 
```{r descript12, echo=F}
vari <- ALSA_ds_w12$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12, echo=F}
AfterH <- table(ALSA_ds_w12$cont_fr)
BeforeH1 <- table(ALSA_w12_cont_fr$CONTFRNDW12, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[1]] <- sum(BeforeH1[c('5','6')])
BeforeH[[2]] <- sum(BeforeH1[c('1':'4')])
BeforeH[[3]] <- BeforeH1[[length(BeforeH1)]]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5:6->0","1:5->1","NA->999")

kable(C)
```

 
### Wave 13

Not found.



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
 

