---
title: "Mobility - Sitting"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_sit`
* Variable label: `Difficulty for sitting for long periods`
* Variable description: `Difficulty for sitting for long periods`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



# Data process

## China

### Wave 1 

#### Study-specific variable description


Not found.


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `db004`
* Label: `Difficulty with sitting`
* Categories:
   + `1 = No, I Don't Have Any Difficulty` 
   + `2 = I Have Difficulty but Can Still Do It` 
   + `3 = Yes, I Have Difficulty and Need Help ` 
   + `4 = I Can Not Do It`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_mob_sit2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('db004'), missings = TRUE)
CHARLS_w2_mob_sit2 <- opal.execute(o,'CHARLS_w2_mob_sit2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], db004=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_mob_sit <- Add_indiv(old = CHARLS_w2_mob_sit2, new = CHARLS_w2_id)
```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_mob_sit$db004 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Mobility - Sitting")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_mob_sit, aes(x=factor(db004))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Mobility - Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0`
* `4 into 0`
* `NA into 999` 
 
**R script**

```{r harmo w2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_mob_sit$id)
CHARLS_ds_w2$mob_sit <- car::recode(CHARLS_w2_mob_sit$db004, "1 =1; 2=0; 3=0; 4=0; NA=999")
CHARLS_ds_w2$mob_sit <- labelled(CHARLS_ds_w2$mob_sit, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$mob_sit # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Mobility - Sitting")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(mob_sit))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Mobility - Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(CHARLS_ds_w2$mob_sit)
X <- table(CHARLS_w2_mob_sit$db004)
BeforeH<- c(sum(X[2:4]),(X[1]),sum(is.na(CHARLS_w2_mob_sit$db004)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```



```{r importOPAL w2, echo=FALSE}
label(CHARLS_ds_w2$mob_sit) <- "Difficulty for sitting for long periods"
#opal.assign.data(o, 'CHARLS_ds_w2', CHARLS_ds_w2)
#opal.symbol_import(o,'CHARLS_ds_w2', project='_Athlos_Harm_Dataset')
mob_sit <- CHARLS_ds_w2
save(mob_sit, file = "../RData/w2/mob_sit.RData")

CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$mob_sit <- car::recode(CHARLS_m_ds_w2$mob_sit, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w2', CHARLS_m_ds_w2)
#opal.symbol_import(o,'CHARLS_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
