---
title: "Cognition - Immediate recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_immDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_immDS.R')
```



# Data process

## China

### Wave 1 

#### Study-specific variable description


| **Name** |`dc006s1; dc006s2; dc006s3; dc006s4; dc006s5; dc006s6; dc006s7; dc006s8; dc006s9; dc006s10; dc006s11`|
|-|-|
| **Label** |`Words Recall`|
| **Table name** |`health_status_and_functioning_wave1`|
| **Categories** |`1:10 = DC006_Wordlist[1:10]`<br/>`11 = 0`|
| **Missings** |`NA`|
| **Description** |  |

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_cog_imm2','CHARLS.health_status_and_functioning_wave1', variables=list('dc006s1','dc006s2','dc006s3','dc006s4','dc006s5','dc006s6','dc006s7','dc006s8','dc006s9','dc006s10','dc006s11'), missings = TRUE)
CHARLS_w1_cog_imm2 <- opal.execute(o,'CHARLS_w1_cog_imm2')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_cog_imm2$oldid <- CHARLS_w1_cog_imm2$id
CHARLS_w1_cog_imm2$id <- CHARLS_ids(ids = CHARLS_w1_cog_imm2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i],rep(NA,12))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,13]), dc006s1=as.numeric(new_2[,2]), dc006s2=as.numeric(new_2[,3]), dc006s3=as.numeric(new_2[,4]), dc006s4=as.numeric(new_2[,5]), dc006s5=as.numeric(new_2[,6]), dc006s6=as.numeric(new_2[,7]), dc006s7=as.numeric(new_2[,8]), dc006s8=as.numeric(new_2[,9]), dc006s9=as.numeric(new_2[,10]), dc006s10=as.numeric(new_2[,11]), dc006s11=as.numeric(new_2[,12]))
  new_22
}

CHARLS_w1_cog_imm <- Add_indiv(old = CHARLS_w1_cog_imm2, new = CHARLS_w1_id)
```

```{r local w1, echo=FALSE}
vari <- CHARLS_w1_cog_imm2$dc006s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s8))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s9))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s10))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_cog_imm2$dc006s11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_imm2, aes(x=factor(dc006s11))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_imm_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `11 into 0` 
* `NA into 999` 

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1` 

**R script**

```{r harmo w1}
##cog_imm_c
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_cog_imm$id)
CHARLS_ds_w1$cog_imm_c <- 0
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s1==1)] <- CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s1==1)]+1 
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s2==2)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s2==2)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s3==3)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s3==3)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s4==4)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s4==4)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s5==5)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s5==5)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s6==6)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s6==6)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s7==7)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s7==7)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s8==8)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s8==8)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s9==9)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s9==9)]+1
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s10==10)]<-CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s10==10)]+1
CHARLS_ds_w1$cog_imm_c[which((CHARLS_ds_w1$cog_imm_c)==0)] <- 999
CHARLS_ds_w1$cog_imm_c[which(CHARLS_w1_cog_imm$dc006s11==11)] <- 0
CHARLS_ds_w1$cog_imm_c <- labelled(CHARLS_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(CHARLS_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

CHARLS_ds_w1$cog_imm <- car::recode(CHARLS_ds_w1[[2]], "0:Q=0; (Q+1):10=1; NA=999")
CHARLS_ds_w1$cog_imm <- labelled(CHARLS_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- CHARLS_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_imm_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_imm)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(CHARLS_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(CHARLS_ds_w1[[2]])<=Q), sum(na.omit(CHARLS_ds_w1[[2]])>Q & na.omit(CHARLS_ds_w1[[2]])<900), sum(na.omit(CHARLS_ds_w1[[2]])==999))
Dicotomic <- table(CHARLS_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:20->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```




### Wave 2 

#### Study-specific variable description


| **Name** |`dc006_1_s1; dc006_1_s2; dc006_1_s3; dc006_1_s4; dc006_1_s5; dc006_1_s6; dc006_1_s7; dc006_1_s8; dc006_1_s9; dc006_1_s10; dc006_1_s11`|
|-|-|
| **Label** |`Words Recall`|
| **Table name** |`Health_Status_and_Functioning_wave2`|
| **Categories** |`1:10 = DC006_Wordlist[1:10]`<br/>`11 = 0`|
| **Missings** |`NA`|
| **Description** |  |

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_cog_imm2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('dc006_1_s1','dc006_1_s2','dc006_1_s3','dc006_1_s4','dc006_1_s5','dc006_1_s6','dc006_1_s7','dc006_1_s8','dc006_1_s9','dc006_1_s10','dc006_1_s11'), missings = TRUE)
CHARLS_w2_cog_imm2 <- opal.execute(o,'CHARLS_w2_cog_imm2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA, 11))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], dc006_1_s1=as.numeric(new_2[,2]), dc006_1_s2=as.numeric(new_2[,3]), dc006_1_s3=as.numeric(new_2[,4]), dc006_1_s4=as.numeric(new_2[,5]), dc006_1_s5=as.numeric(new_2[,6]), dc006_1_s6=as.numeric(new_2[,7]), dc006_1_s7=as.numeric(new_2[,8]), dc006_1_s8=as.numeric(new_2[,9]), dc006_1_s9=as.numeric(new_2[,10]), dc006_1_s10=as.numeric(new_2[,11]), dc006_1_s11=as.numeric(new_2[,12]))
  new_22
}

CHARLS_w2_cog_imm <- Add_indiv(old = CHARLS_w2_cog_imm2, new = CHARLS_w2_id)
```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_cog_imm2$dc006_1_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")


vari <- CHARLS_w2_cog_imm2$dc006_1_s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s8))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s9))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s10))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_cog_imm2$dc006_1_s11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_imm2, aes(x=factor(dc006_1_s11))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonized variable `cog_imm_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `11 into 0` 
* `NA into 999` 

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1` 
 
**R script**

```{r harmo w2}
##cog_del_c
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_cog_imm$id)
CHARLS_ds_w2$cog_imm_c <- rep(0,length(CHARLS_w2_cog_imm$id))
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s1==1)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s1==1)]+1 
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s2==2)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s2==2)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s3==3)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s3==3)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s4==4)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s4==4)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s5==5)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s5==5)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s6==6)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s6==6)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s7==7)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s7==7)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s8==8)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s8==8)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s9==9)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s9==9)]+1
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s10==10)]<-CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s10==10)]+1
CHARLS_ds_w2$cog_imm_c[which((CHARLS_ds_w2$cog_imm_c)==0)]<-999
CHARLS_ds_w2$cog_imm_c[which(CHARLS_w2_cog_imm$dc006_1_s11==11)]<-0
CHARLS_ds_w2$cog_imm_c <- labelled(CHARLS_ds_w2$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(CHARLS_ds_w2$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

CHARLS_ds_w2$cog_imm <- car::recode(CHARLS_ds_w2[[2]], "0:Q=0; (Q+1):10=1; NA=999")
CHARLS_ds_w2$cog_imm <- labelled(CHARLS_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_imm_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_ds_w2$cog_imm
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_imm) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(CHARLS_ds_w2[[2]])<=Q), sum(na.omit(CHARLS_ds_w2[[2]])>Q & na.omit(CHARLS_ds_w2[[2]])<900), sum(na.omit(CHARLS_ds_w2[[2]])==999))
Dicotomic <- table(CHARLS_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:20->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```







<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_imm)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_imm_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

charlslist <- lmlist # CHARLS list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `cog_imm` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(hd_vbl %in% names(get0(paste0("CHARLS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- charlslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- charlslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_imm))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `cog_imm_c` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("CHARLS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- charlslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- charlslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_imm_c))
}





```








# Quality estimation

No comments




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
