---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `orientation`
* Variable label: `Difficulties for orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `dc001s1`
* Label: `Today's date: Year`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct` 
* Missings
   + `NA`
   
* Name: `dc001s2`
* Label: `Today's date: Month`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct` 
* Missings
   + `NA`
  
* Name: `dc001s3`
* Label: `Today's date: Day`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct`   
* Missings
   + `NA`
   
* Name: `dc002`
* Label: `Today's date: day of week`
* Categories:
   + `1 = Day of Week OK/Correct ` 
   + `2 = Day of Week Not OK/ Incorrect` 
* Missings
   + `NA`

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_orientation2','CHARLS.health_status_and_functioning_wave1', variables=list('dc001s1','dc001s2','dc001s3','dc002'), missings = TRUE)
CHARLS_w1_orientation2 <- opal.execute(o,'CHARLS_w1_orientation2')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_orientation2$oldid <- CHARLS_w1_orientation2$id
CHARLS_w1_orientation2$id <- CHARLS_ids(ids = CHARLS_w1_orientation2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,5))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,6]), dc001s1=as.numeric(new_2[,2]), dc001s2=as.numeric(new_2[,3]), dc001s3=as.numeric(new_2[,4]), dc002=as.numeric(new_2[,5]))
  new_22
}

CHARLS_w1_orientation <- Add_indiv(old = CHARLS_w1_orientation2, new = CHARLS_w1_id)
```

```{r local w1, echo=F}
vari <- CHARLS_w1_orientation$dc001s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_orientation, aes(x=factor(dc001s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w1_orientation$dc001s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_orientation, aes(x=factor(dc001s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w1_orientation$dc001s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_orientation, aes(x=factor(dc001s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w1_orientation$dc002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_orientation, aes(x=factor(dc002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `All the answers correct into 1`
* `Some of the answers incorrect into 0` 
 
**R script**

```{r harmo w1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_orientation$id)
CHARLS_ds_w1$orientation <- rep(0,length(CHARLS_ds_w1$id))
CHARLS_ds_w1$orientation[which((CHARLS_w1_orientation$dc001s1==1)&(CHARLS_w1_orientation$dc001s2==2)&(CHARLS_w1_orientation$dc001s3==3)&(CHARLS_w1_orientation$dc002==1))]<-1
CHARLS_ds_w1$orientation[which((is.na(CHARLS_w1_orientation$dc001s1))&(is.na(CHARLS_w1_orientation$dc001s2))&(is.na(CHARLS_w1_orientation$dc001s3))&(is.na(CHARLS_w1_orientation$dc002)))]<-999
CHARLS_ds_w1$orientation <- labelled(CHARLS_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- CHARLS_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Orientation") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(CHARLS_ds_w1$orientation)
x1<-sum(na.omit((CHARLS_w1_orientation$dc001s1==1)&(CHARLS_w1_orientation$dc001s2==2)&(CHARLS_w1_orientation$dc001s3==3)&(CHARLS_w1_orientation$dc002==1)))
x2<-sum((is.na(CHARLS_w1_orientation$dc001s1))&(is.na(CHARLS_w1_orientation$dc001s2))&(is.na(CHARLS_w1_orientation$dc001s3))&(is.na(CHARLS_w1_orientation$dc002)))
BeforeH<- c(length(CHARLS_w1_orientation$dc001s1)-x1-x2,x1,x2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Some incorrect->0","All correct->1","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(CHARLS_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'CHARLS_ds_w1', CHARLS_ds_w1)
#opal.symbol_import(o,'CHARLS_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- CHARLS_ds_w1
save(orientation, file = "../RData/w1/orientation.RData")

CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$orientation <- car::recode(CHARLS_m_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w1', CHARLS_m_ds_w1)
#opal.symbol_import(o,'CHARLS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `dc001s1`
* Label: `Checking Date: Year`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct` 
* Missings
   + `NA`
   
* Name: `dc001s2`
* Label: `Checking Date: Month`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct` 
* Missings
   + `NA`
  
* Name: `dc001s3`
* Label: `Checking Date: Day`
* Categories:
   + `1 = Year is correct` 
   + `2 = Month is correct` 
   + `3 = Day is correct`   
* Missings
   + `NA`
   
* Name: `dc002`
* Label: `Checking Day of Week`
* Categories:
   + `1 = Day of Week OK/Correct ` 
   + `2 = Day of Week Not OK/ Incorrect` 
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_orientation2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('dc001s1','dc001s2','dc001s3','dc002'), missings = TRUE)
CHARLS_w2_orientation2 <- opal.execute(o,'CHARLS_w2_orientation2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,4))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], dc001s1=as.numeric(new_2[,2]), dc001s2=as.numeric(new_2[,3]), dc001s3=as.numeric(new_2[,4]), dc002=as.numeric(new_2[,5]))
  new_22
}

CHARLS_w2_orientation <- Add_indiv(old = CHARLS_w2_orientation2, new = CHARLS_w2_id)
```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_orientation$dc001s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_orientation, aes(x=factor(dc001s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w2_orientation$dc001s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_orientation, aes(x=factor(dc001s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w2_orientation$dc001s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_orientation, aes(x=factor(dc001s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")

vari <- CHARLS_w2_orientation$dc002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Orientation in time") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_orientation, aes(x=factor(dc002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation in time") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `All the answers correct into 1`
* `Some of the answers incorrect into 0` 

**R script:**

```{r harmo w2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_orientation$id)
CHARLS_ds_w2$orientation <- rep(0,length(CHARLS_ds_w2$id))
CHARLS_ds_w2$orientation[which((CHARLS_w2_orientation$dc001s1==1)&(CHARLS_w2_orientation$dc001s2==2)&(CHARLS_w2_orientation$dc001s3==3)&(CHARLS_w2_orientation$dc002==1))]<-1
CHARLS_ds_w2$orientation[which((is.na(CHARLS_w2_orientation$dc001s1))&(is.na(CHARLS_w2_orientation$dc001s2))&(is.na(CHARLS_w2_orientation$dc001s3))&(is.na(CHARLS_w2_orientation$dc002)))]<-999
CHARLS_ds_w2$orientation <- labelled(CHARLS_ds_w2$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Orientation") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w2, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(CHARLS_ds_w2$orientation)
x1<-sum(na.omit((CHARLS_w2_orientation$dc001s1==1)&(CHARLS_w2_orientation$dc001s2==2)&(CHARLS_w2_orientation$dc001s3==3)&(CHARLS_w2_orientation$dc002==1)))
x2<-sum((is.na(CHARLS_w2_orientation$dc001s1))&(is.na(CHARLS_w2_orientation$dc001s2))&(is.na(CHARLS_w2_orientation$dc001s3))&(is.na(CHARLS_w2_orientation$dc002)))
BeforeH<- c(length(CHARLS_w2_orientation$dc001s1)-x1-x2,x1,x2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Some incorrect->0","All correct->1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(CHARLS_ds_w2$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'CHARLS_ds_w2', CHARLS_ds_w2)
#opal.symbol_import(o,'CHARLS_ds_w2', project='_Athlos_Harm_Dataset')
orientation <- CHARLS_ds_w2
save(orientation, file = "../RData/w2/orientation.RData")

CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$orientation <- car::recode(CHARLS_m_ds_w2$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w2', CHARLS_m_ds_w2)
#opal.symbol_import(o,'CHARLS_m_ds_w2', project='_Athlos_Harm_Dataset')
```

# Quality estimation
For this study, the variable is a composed combining day of the month,
day of the week, month, and year which is different from the calculation performed in other studies where day of the month,
season is also available (or some of these variables are not).

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
