---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del_c`
* Variable label: `Cognition - delayed recall - Continuous`
* Variable description: `Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Delayed recall"
ds_label_cog_del_c <- "Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_del <- "Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `dc027s1; dc027s2; dc027s3; dc027s4; dc027s5; dc027s6; dc027s7; dc027s8; dc027s9; dc027s10; dc027s11`
* Label: `Recall Words`
* Categories:
   + `1 - 10`
   + `11 = 0`
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_cog_del2','CHARLS.health_status_and_functioning_wave1', variables=list('dc027s1','dc027s2','dc027s3','dc027s4','dc027s5','dc027s6','dc027s7','dc027s8','dc027s9','dc027s10','dc027s11'), missings = TRUE)
CHARLS_w1_cog_del2 <- opal.execute(o,'CHARLS_w1_cog_del2')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_cog_del2$oldid <- CHARLS_w1_cog_del2$id
CHARLS_w1_cog_del2$id <- CHARLS_ids(ids = CHARLS_w1_cog_del2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i],rep(NA,12))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,13]), dc027s1=as.numeric(new_2[,2]), dc027s2=as.numeric(new_2[,3]), dc027s3=as.numeric(new_2[,4]), dc027s4=as.numeric(new_2[,5]), dc027s5=as.numeric(new_2[,6]), dc027s6=as.numeric(new_2[,7]), dc027s7=as.numeric(new_2[,8]), dc027s8=as.numeric(new_2[,9]), dc027s9=as.numeric(new_2[,10]), dc027s10=as.numeric(new_2[,11]), dc027s11=as.numeric(new_2[,12]))
  new_22
}

CHARLS_w1_cog_del <- Add_indiv(old = CHARLS_w1_cog_del2, new = CHARLS_w1_id)
```

```{r local w1, echo=FALSE}
vari <- CHARLS_w1_cog_del$dc027s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s8))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s9))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s10))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w1_cog_del$dc027s11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_cog_del, aes(x=factor(dc027s11))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `11 into 0` 
* `NA into 999` 

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w1}
##cog_del_c
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_cog_del$id)
CHARLS_ds_w1$cog_del_c <- rep(0,length(CHARLS_w1_cog_del$id))
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s1==1)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s1==1)]+1 
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s2==2)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s2==2)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s3==3)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s3==3)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s4==4)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s4==4)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s5==5)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s5==5)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s6==6)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s6==6)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s7==7)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s7==7)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s8==8)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s8==8)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s9==9)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s9==9)]+1
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s10==10)]<-CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s10==10)]+1
CHARLS_ds_w1$cog_del_c[which((CHARLS_ds_w1$cog_del_c)==0)]<-999
CHARLS_ds_w1$cog_del_c[which(CHARLS_w1_cog_del$dc027s11==11)]<-0
CHARLS_ds_w1$cog_del_c <- labelled(CHARLS_ds_w1$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(CHARLS_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

CHARLS_ds_w1$cog_del <- car::recode(CHARLS_ds_w1[[2]], "0:Q=0; (Q+1):10=1; NA=999")
CHARLS_ds_w1$cog_del <- labelled(CHARLS_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- CHARLS_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("cog_del") + ylab("Frequency")

vari <- CHARLS_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall categorical") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(CHARLS_ds_w1[[2]])<=Q), sum(na.omit(CHARLS_ds_w1[[2]])>Q&na.omit(CHARLS_ds_w1[[2]])<900), sum(na.omit(CHARLS_ds_w1[[2]])==999))
Dicotomic <- table(CHARLS_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:2->0","3:20->1", "NA") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
label(CHARLS_ds_w1$cog_del) <- "Cognition- delayed recall"
#opal.assign.data(o, 'CHARLS_ds_w1', CHARLS_ds_w1)
#opal.symbol_import(o,'CHARLS_ds_w1', project='_Athlos_Harm_Dataset')
cog_del <- CHARLS_ds_w1
save(cog_del, file = "../RData/w1/cog_del.RData")
rm(cog_del)

CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$cog_del <- car::recode(CHARLS_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
CHARLS_m_ds_w1$cog_del_c <- car::recode(CHARLS_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w1', CHARLS_m_ds_w1)
#opal.symbol_import(o,'CHARLS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `dc027s1; dc027s2; dc027s3; dc027s4; dc027s5; dc027s6; dc027s7; dc027s8; dc027s9; dc027s10; dc027s11`
* Label: `Recall Words`
* Categories:
   + `1 - 10`
   + `11 = 0`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_cog_del2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('dc027s1','dc027s2','dc027s3','dc027s4','dc027s5','dc027s6','dc027s7','dc027s8','dc027s9','dc027s10','dc027s11'), missings = TRUE)
CHARLS_w2_cog_del2 <- opal.execute(o,'CHARLS_w2_cog_del2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA, 11))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], dc027s1=as.numeric(new_2[,2]), dc027s2=as.numeric(new_2[,3]), dc027s3=as.numeric(new_2[,4]), dc027s4=as.numeric(new_2[,5]), dc027s5=as.numeric(new_2[,6]), dc027s6=as.numeric(new_2[,7]), dc027s7=as.numeric(new_2[,8]), dc027s8=as.numeric(new_2[,9]), dc027s9=as.numeric(new_2[,10]), dc027s10=as.numeric(new_2[,11]), dc027s11=as.numeric(new_2[,12]))
  new_22
}

CHARLS_w2_cog_del <- Add_indiv(old = CHARLS_w2_cog_del2, new = CHARLS_w2_id)
```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_cog_del$dc027s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")


vari <- CHARLS_w2_cog_del$dc027s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")


vari <- CHARLS_w2_cog_del$dc027s4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")


vari <- CHARLS_w2_cog_del$dc027s5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")


vari <- CHARLS_w2_cog_del$dc027s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s8))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s9))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s10))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")

vari <- CHARLS_w2_cog_del$dc027s11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_cog_del, aes(x=factor(dc027s11))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `11 into 0` 
* `NA into 999` 

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w2}
##cog_del_c
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_cog_del$id)
CHARLS_ds_w2$cog_del_c <- rep(0,length(CHARLS_w2_cog_del$id))
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s1==1)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s1==1)]+1 
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s2==2)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s2==2)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s3==3)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s3==3)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s4==4)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s4==4)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s5==5)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s5==5)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s6==6)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s6==6)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s7==7)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s7==7)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s8==8)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s8==8)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s9==9)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s9==9)]+1
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s10==10)]<-CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s10==10)]+1
CHARLS_ds_w2$cog_del_c[which((CHARLS_ds_w2$cog_del_c)==0)]<-999
CHARLS_ds_w2$cog_del_c[which(CHARLS_w2_cog_del$dc027s11==11)]<-0
CHARLS_ds_w2$cog_del_c <- labelled(CHARLS_ds_w2$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(CHARLS_ds_w2$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

CHARLS_ds_w2$cog_del <- car::recode(CHARLS_ds_w2[[2]], "0:Q=0; (Q+1):10=1; NA=999")
CHARLS_ds_w2$cog_del <- labelled(CHARLS_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("cog_del") + ylab("Frequency")

vari <- CHARLS_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(CHARLS_ds_w2[[2]])<=Q), sum(na.omit(CHARLS_ds_w2[[2]])>Q & na.omit(CHARLS_ds_w1[[2]])<900), sum(na.omit(CHARLS_ds_w2[[2]])==999))
Dicotomic <- table(CHARLS_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:2->0","3:20->1", "NA") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w2, echo=FALSE}
label(CHARLS_ds_w2$cog_del) <- "Cognition- delayed recall"
#opal.assign.data(o, 'CHARLS_ds_w2', CHARLS_ds_w2)
#opal.symbol_import(o,'CHARLS_ds_w2', project='_Athlos_Harm_Dataset')
cog_del <- CHARLS_ds_w2
save(cog_del, file = "../RData/w2/cog_del.RData")
rm(cog_del)

CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$cog_del <- car::recode(CHARLS_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
CHARLS_m_ds_w2$cog_del_c <- car::recode(CHARLS_m_ds_w2$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w2', CHARLS_m_ds_w2)
#opal.symbol_import(o,'CHARLS_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
