---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_CHARLS.r")
require(pander)
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `da001`
* Label: `Self Comment of Your Health`
* Categories:

   + `1 = Excellent` 
   + `2 = Very good` 
   + `3 = Good` 
   + `4 = Fair` 
   + `5 = Poor`
   
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_srh2','CHARLS.health_status_and_functioning_wave1', variables=list('da001'), missings = TRUE)
CHARLS_w1_srh2 <- opal.execute(o,'CHARLS_w1_srh2')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_srh2$oldid <- CHARLS_w1_srh2$id
CHARLS_w1_srh2$id <- CHARLS_ids(ids = CHARLS_w1_srh2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), da001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_srh <- Add_indiv(old = CHARLS_w1_srh2, new = CHARLS_w1_id)
```

```{r local w1, echo=FALSE}
vari <- CHARLS_w1_srh$da001 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Self Rated Health") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(CHARLS_w1_srh, aes(x=factor(da001))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1`
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `NA into 999` 
 
**R script**

```{r harmo w1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_srh$id)
CHARLS_ds_w1$srh <- car::recode(CHARLS_w1_srh$da001, "1=1; 2=1; 3=1; 4=2; 5=3; NA=999")
CHARLS_ds_w1$srh <- labelled(CHARLS_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- CHARLS_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "marital_status") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(CHARLS_ds_w1$srh)
X <- table(CHARLS_w1_srh$da001)
BeforeH<- c(sum(X[1:3]),(X[c(4,5)]),sum(is.na(CHARLS_w1_srh$da001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(CHARLS_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- CHARLS_ds_w1
save(srh, file = "../RData/w1/srh.RData")

```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `da001`
* Label: `Self Assessed  Health Status (Excellent)`
* Categories:
   + `1 = Excellent` 
   + `2 = Very good` 
   + `3 = Good` 
   + `4 = Fair` 
   + `5 = Poor`
* Missings
   + `NA`
   
* Name: `da002`
* Label: `Self Assessed  Health Status (Very Good)`
* Categories:
   + `1 = Very good` 
   + `2 = Good` 
   + `3 = Fair` 
   + `4 = Poor` 
   + `5 = Very poor`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_srh2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('da001','da002'), missings = TRUE)
CHARLS_w2_srh2 <- opal.execute(o,'CHARLS_w2_srh2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], da001=as.numeric(new_2[,2]), da002=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_srh <- Add_indiv(old = CHARLS_w2_srh2, new = CHARLS_w2_id)
```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_srh$da001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Self Rated Health") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_srh, aes(x=factor(da001))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Self Rated Health") + ylab("Frequency")

vari <- CHARLS_w2_srh$da002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Self Rated Health") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_srh, aes(x=factor(da002))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `for da001:`
* `1 into 1` 
* `2 into 1`
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `NA into 999` 

* `for da002:`
* `1 into 1` 
* `2 into 1`
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `NA into 999` 
 

```{r harmo w2}
CHARLS_w2_srh$srh1 <- car::recode(CHARLS_w2_srh$da001, "1=1; 2=1; 3=1; 4=2; 5=3; NA=999")
CHARLS_w2_srh$srh2 <- car::recode(CHARLS_w2_srh$da002, "1=1; 2=1; 3=2; 4=3; 5=3; NA=999")

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_srh$id, srh=CHARLS_w2_srh$srh2)
CHARLS_ds_w2$srh[which(CHARLS_ds_w2$srh==999)] <- CHARLS_w2_srh$srh1[which(CHARLS_ds_w2$srh==999)]
CHARLS_ds_w2$srh <- labelled(CHARLS_ds_w2$srh, labels = c(Good=1, Fair=2, Bad=3, Missing=999, Do_not_know=998, Refuse=997, Not_attempt_not_done=996, Does_not_answer=995,  Not_applicable=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Self Rated Health") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") +xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(CHARLS_ds_w2$srh)
X <- table(CHARLS_w2_srh$da001)
Y <- table(CHARLS_w2_srh$da002)
Z<-cbind(CHARLS_w2_srh$da001,CHARLS_w2_srh$da002)
BeforeH<- c(sum(c(X[1:3],Y[1:2])),X[4]+Y[3]-dim(na.omit(Z))[1],sum(c(X[5],Y[4:5])),sum(is.na(CHARLS_w2_srh$da001)==is.na(CHARLS_w2_srh$da002))-dim(na.omit(Z))[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("da001(1,2,3),da002(1,2)->1","da001(4),da002(3)->2","da001(5),da002(4,5)","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}
label(CHARLS_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- CHARLS_ds_w2
save(srh, file = "../RData/w2/srh.RData")

```


# Quality estimation

There is only one question about self-rated health in wave 1. However, two questions on self-rated health with different scales were used at wave 2.  Respondents were asked to rate their health status twice, at the beginning of the general health section and again at the end. Question order was assigned randomly.

The decision of harmonising the DataSchema variable was to take the variable at the beginning based on the conclusions extracted in Bowling and Windsor - JECH 2008;62:81-85.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

