---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
source("../CHARLS_ids.R")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```


# Data process



## China


### Wave 1


#### Study-specific variable description

| **Name** | `dc028` |
|-|-|
| **Label** | `Self Comment of Your Life`|
| **Table name**  | `health_status_and_functioning_wave1`|
| **Categories** | `1 = Completely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Somewhat satisfied` <br/> `4 = Not very satisfied` <br/> `5 = Not at all satisfied` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_wb_2','CHARLS.health_status_and_functioning_wave1',variables=list('dc028'), missings = T)
CHARLS_wb_2 <- opal.execute(o,'CHARLS_wb_2')

opal.assign.table.tibble(o, 'CHARLS_wb_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_wb_id <- opal.execute(o,'CHARLS_wb_id')


# adding a zero to the old id's in CHARLS_wb with CHARLS_ids
CHARLS_wb_2$oldid <- CHARLS_wb_2$id
CHARLS_wb_2$id <- CHARLS_ids(ids = CHARLS_wb_2$oldid)

CHARLS_wb <- left_join(CHARLS_wb_id, CHARLS_wb_2, by="id") %>% 
  select(id, dc028)
```

```{r local w1, echo=F}

vbl <- CHARLS_wb$dc028
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_wb)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_wb, aes(x=factor(dc028))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_wb$id)
CHARLS_ds_w1$evaluative_wb <- car::recode(CHARLS_wb$dc028, "1=2; 3=1; 4=0; 5=0; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}
vbl <- CHARLS_ds_w1$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation

```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=FALSE}
evaluative_wb <- CHARLS_ds_w1
save(evaluative_wb, file = "../RData/w1/evaluative_wb.RData")
rm(evaluative_wb)
```



### Wave 2

#### Study-specific variable description

| **Name** | `dc028` |
|-|-|
| **Label** | `Life Satisfaction`|
| **Table name**  | `Health_Status_and_Functioning_wave2`|
| **Categories** | `1 = Completely satisfied` <br/> `2 = Very satisfied` <br/> `3 = Somewhat satisfied` <br/> `4 = Not very satisfied` <br/> `5 = Not at all satisfied` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_2', 'CHARLS.Health_Status_and_Functioning_wave2', variables=list('dc028'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_wb <- left_join(CHARLS_w2_id,CHARLS_w2_2, by="id") %>% 
  select(id, dc028)
```

```{r local w2, echo=F}
vbl <- CHARLS_wb$dc028
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_wb)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_wb, aes(x=factor(dc028))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3 into 1`
* `4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo w2}
# Categorical variable harmonization
CHARLS_ds_w2 <- tibble(id=CHARLS_wb$id)
CHARLS_ds_w2$evaluative_wb <- car::recode(CHARLS_wb$dc028, "1=2; 3=1; 4=0; 5=0; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}
vbl <- CHARLS_ds_w2$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation

```{r crosstabulation w2, echo=F}
```


```{r importOPAL W2, echo=FALSE}
evaluative_wb <- CHARLS_ds_w2
save(evaluative_wb, file = "../RData/w2/evaluative_wb.RData")
rm(evaluative_wb)
```


# Quality estimation





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





