---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process



## China


### Wave 1


#### Study-specific variable description

| **Name** | `dc013` |
|-|-|
| **Label** | `Felt Hopeful About the Future`|
| **Table name**  | `health_status_and_functioning_wave1`|
| **Categories** | `1 = Rarely or none of the time <1 day` <br/> `2 = Some or a little of the time 1-2 days` <br/> `3 = Occasionally or a moderate amount of the time 3-4 days` <br/> `4 = Most or all of the time 5-7 days` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_wb_2','CHARLS.health_status_and_functioning_wave1',variables=list('dc013'), missings = T)
CHARLS_wb_2 <- opal.execute(o,'CHARLS_wb_2')

opal.assign.table.tibble(o, 'CHARLS_wb_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_wb_id <- opal.execute(o,'CHARLS_wb_id')


# adding a zero to the old id's in CHARLS_wb with CHARLS_ids
CHARLS_wb_2$oldid <- CHARLS_wb_2$id
CHARLS_wb_2$id <- CHARLS_ids(ids = CHARLS_wb_2$oldid)

CHARLS_wb <- left_join(CHARLS_wb_id, CHARLS_wb_2, by="id") %>% 
  select(id, dc013)

```

```{r local w1, echo=F}

vbl <- CHARLS_wb$dc013
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_wb, aes(x=factor(dc013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4 into 2`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_wb$id)
CHARLS_ds_w1$eudaimonic_wb <- car::recode(CHARLS_wb$dc013, "1=0; 2:3=1; 4=2; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}
vbl <- CHARLS_ds_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation

```{r crosstabulation w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** | `dc013` |
|-|-|
| **Label** | `I Felt Hopeful about The Future.`|
| **Table name**  | `Health_Status_and_Functioning_wave2`|
| **Categories** | `1 = Rarely or None of The Time <1 Day` <br/> `2 = Some or A Little of The Time 1-2 Days` <br/> `3 = Occasionally or A Moderate Amount of The Time 3-4 Days` <br/> `4 = Most or all of The Time 5-7 Days` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_2', 'CHARLS.Health_Status_and_Functioning_wave2', variables=list('dc013'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_wb <- left_join(CHARLS_w2_id,CHARLS_w2_2, by="id") %>% 
  select(id, dc013)
```

```{r local w2, echo=F}
vbl <- CHARLS_wb$dc013
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_wb)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_wb, aes(x=factor(dc013))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4 into 2`
* `NA into 999`

**R script:**

```{r harmo w2}
# Categorical variable harmonization
CHARLS_ds_w2 <- tibble(id=CHARLS_wb$id)
CHARLS_ds_w2$eudaimonic_wb <- car::recode(CHARLS_wb$dc013, "1=0; 2:3=1; 4=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}
vbl <- CHARLS_ds_w2$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation

```{r crosstabulation w2, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)

}
```





# Quality estimation





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





