---
title: "Hearing General"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `da005_4_`
* Label: `Hearing Problem`
* Categories:
   + `1 = Yes` 
   + `2 = No` 
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_hearing_gen2','CHARLS.health_status_and_functioning_wave1', variables=list('da005_4_'), missings = TRUE)
CHARLS_w1_hearing_gen2 <- opal.execute(o,'CHARLS_w1_hearing_gen2')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_hearing_gen2$oldid <- CHARLS_w1_hearing_gen2$id
CHARLS_w1_hearing_gen2$id <- CHARLS_ids(ids = CHARLS_w1_hearing_gen2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), da005_4_=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_hearing_gen <- Add_indiv(old = CHARLS_w1_hearing_gen2, new = CHARLS_w1_id)

```

```{r local w1, echo=FALSE}
vari <- CHARLS_w1_hearing_gen$da005_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Hearing - General") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_hearing_gen, aes(x=factor(da005_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1` 
* `NA into 999` 

**R script** 

```{r harmo w1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_hearing_gen$id)
CHARLS_ds_w1$hearing_gen <- car::recode(CHARLS_w1_hearing_gen$da005_4_, "1 = '0';2 = '1';NA = '999'")
CHARLS_ds_w1$hearing_gen <- labelled(CHARLS_ds_w1$hearing_gen, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- CHARLS_ds_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Hearing - General") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(CHARLS_ds_w1$hearing_gen)
X <- table(CHARLS_w1_hearing_gen$da005_4_)
BeforeH<- c(X[1:2],sum(is.na(CHARLS_w1_hearing_gen$da005_4_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(CHARLS_ds_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'CHARLS_ds_w1', CHARLS_ds_w1)
#opal.symbol_import(o,'CHARLS_ds_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- CHARLS_ds_w1
save(hearing_gen, file = "../RData/w1/hearing_gen.RData")

CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$hearing_gen <- car::recode(CHARLS_m_ds_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w1', CHARLS_m_ds_w1)
#opal.symbol_import(o,'CHARLS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variables

The study-specific variables elected to be harmonised is:


* Name: `da005_4_`
* Label: `Hearing Problem`
* Categories:
   + `1 = Yes` 
   + `2 = No` 
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_hearing_gen2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('da005_4_'), missings = TRUE)
CHARLS_w2_hearing_gen2 <- opal.execute(o,'CHARLS_w2_hearing_gen2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], da005_4_=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_hearing_gen <- Add_indiv(old = CHARLS_w2_hearing_gen2, new = CHARLS_w2_id)

```

```{r local w2, echo=FALSE}
vari <- CHARLS_w2_hearing_gen$da005_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Hearing - General") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


ggplot(CHARLS_w2_hearing_gen, aes(x=factor(da005_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1` 
* `NA into 999` 

**R script**

```{r harmo w2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_hearing_gen$id)
CHARLS_ds_w2$hearing_gen <- car::recode(CHARLS_w2_hearing_gen$da005_4_, "1 = '0';2 = '1';NA = '999'")
CHARLS_ds_w2$hearing_gen <- labelled(CHARLS_ds_w2$hearing_gen, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- CHARLS_ds_w2$hearing_gen 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Hearing - General") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(CHARLS_ds_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(CHARLS_ds_w2$hearing_gen)
X <- table(CHARLS_w2_hearing_gen$da005_4_)
BeforeH<- c(X[1:2],sum(is.na(CHARLS_w2_hearing_gen$da005_4_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","NA->999") 
kable(C)
```



```{r importOPAL w2, echo=FALSE}
label(CHARLS_ds_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'CHARLS_ds_w2', CHARLS_ds_w2)
#opal.symbol_import(o,'CHARLS_ds_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- CHARLS_ds_w2
save(hearing_gen, file = "../RData/w2/hearing_gen.RData")

CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$hearing_gen <- car::recode(CHARLS_m_ds_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'CHARLS_m_ds_w2', CHARLS_m_ds_w2)
#opal.symbol_import(o,'CHARLS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
