---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```



<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1

#### Study-specific variable description

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |


```{r assign_cuba1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-Cuba-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_cuba1, echo=FALSE}
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm

The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**


```{r harmo_cuba1, echo=TRUE}
t1066_ds_cuba_w1 <- tibble(id=t1066_dep$id)
t1066_ds_cuba_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_cuba_w1$depression <- labelled(t1066_ds_cuba_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cuba1, echo=FALSE}
vari <- t1066_ds_cuba_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba1, echo=FALSE}
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_cuba_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_cuba_w1, echo=FALSE}
label(t1066_ds_cuba_w1$depression) <- ds_label_all
depression <- t1066_ds_cuba_w1
save(depression, file = "../RData/cuba_w1/depression.RData")
rm(depression, t1066_dep)
```




### Wave 2 

#### Study-specific variable description

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-Cuba-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |


```{r assign_cuba2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-Cuba-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_cuba2, echo=FALSE}
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cuba2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_dep$id)
t1066_ds_cuba_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_cuba_w2$depression <- labelled(t1066_ds_cuba_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cuba2, echo=FALSE}
vari <- t1066_ds_cuba_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba2, echo=FALSE}
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_cuba_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```


```{r importOPAL_cuba_w2, echo=FALSE}
label(t1066_ds_cuba_w2$depression) <- ds_label_all
depression <- t1066_ds_cuba_w2
save(depression, file = "../RData/cuba_w2/depression.RData")
rm(depression, t1066_dep)
```


## India 

### Wave 1 

#### Study-specific variable description


| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-India-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_india1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-India-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_india1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_india1, echo=TRUE} 
t1066_ds_india_w1 <- tibble(id=t1066_dep$id)
t1066_ds_india_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_india_w1$depression <- labelled(t1066_ds_india_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_india1, echo=FALSE} 
vari <- t1066_ds_india_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_india_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_india1, echo=FALSE}
label(t1066_ds_india_w1$depression) <- ds_label_all
depression <- t1066_ds_india_w1
save(depression, file = "../RData/india_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

### Wave 2 

#### Study-specific variable description

There is no variable. 
 

 

## Urban China 

### Wave 1 

#### Study-specific variable description

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_UCh1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanChina-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UCh1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UCh1, echo=TRUE} 
t1066_ds_UCh_w1 <- tibble(id=t1066_dep$id)
t1066_ds_UCh_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UCh_w1$depression <- labelled(t1066_ds_UCh_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UCh1, echo=FALSE} 
vari <- t1066_ds_UCh_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UCh_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_UCh1, echo=FALSE}
label(t1066_ds_UCh_w1$depression) <- ds_label_all
depression <- t1066_ds_UCh_w1
save(depression, file = "../RData/UCh_w1/depression.RData")
rm(depression, t1066_dep)
```





### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanChina-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_UCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanChina-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UCh2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UCh2, echo=TRUE} 
t1066_ds_UCh_w2 <- tibble(id=t1066_dep$id)
t1066_ds_UCh_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UCh_w2$depression <- labelled(t1066_ds_UCh_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UCh2, echo=FALSE} 
vari <- t1066_ds_UCh_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UCh_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_UCh2, echo=FALSE}
label(t1066_ds_UCh_w2$depression) <- ds_label_all
depression <- t1066_ds_UCh_w2
save(depression, file = "../RData/UCh_w2/depression.RData")
rm(depression, t1066_dep)
```


 

## Rural China 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RCh1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralChina-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RCh1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RCh1, echo=TRUE} 
t1066_ds_RCh_w1 <- tibble(id=t1066_dep$id)
t1066_ds_RCh_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RCh_w1$depression <- labelled(t1066_ds_RCh_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RCh1, echo=FALSE} 
vari <- t1066_ds_RCh_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RCh_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_RCh1, echo=FALSE}
label(t1066_ds_RCh_w1$depression) <- ds_label_all
depression <- t1066_ds_RCh_w1
save(depression, file = "../RData/RCh_w1/depression.RData")
rm(depression, t1066_dep)
```

 

### Wave 2 

#### Study-specific variable description


| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralChina-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralChina-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RCh2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RCh2, echo=TRUE} 
t1066_ds_RCh_w2 <- tibble(id=t1066_dep$id)
t1066_ds_RCh_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RCh_w2$depression <- labelled(t1066_ds_RCh_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RCh2, echo=FALSE} 
vari <- t1066_ds_RCh_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RCh_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_RCh2, echo=FALSE}
label(t1066_ds_RCh_w2$depression) <- ds_label_all
depression <- t1066_ds_RCh_w2
save(depression, file = "../RData/RCh_w2/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

## Dominican Republic 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_DR1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_DR1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_DR1, echo=TRUE} 
t1066_ds_DR_w1 <- tibble(id=t1066_dep$id)
t1066_ds_DR_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_DR_w1$depression <- labelled(t1066_ds_DR_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_DR1, echo=FALSE} 
vari <- t1066_ds_DR_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_DR_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_DR1, echo=FALSE}
label(t1066_ds_DR_w1$depression) <- ds_label_all
depression <- t1066_ds_DR_w1
save(depression, file = "../RData/DR_w1/depression.RData")
rm(depression, t1066_dep)
```


 

### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_DR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-DominicanRepublic-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_DR2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_DR2, echo=TRUE} 
t1066_ds_DR_w2 <- tibble(id=t1066_dep$id)
t1066_ds_DR_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_DR_w2$depression <- labelled(t1066_ds_DR_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_DR2, echo=FALSE} 
vari <- t1066_ds_DR_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_DR_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_DR2, echo=FALSE}
label(t1066_ds_DR_w2$depression) <- ds_label_all
depression <- t1066_ds_DR_w2
save(depression, file = "../RData/DR_w2/depression.RData")
rm(depression, t1066_dep)
```
 

 

## Venezuela 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_V1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-Venezuela-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_V1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_V1, echo=TRUE} 
t1066_ds_Ven_w1 <- tibble(id=t1066_dep$id)
t1066_ds_Ven_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_Ven_w1$depression <- labelled(t1066_ds_Ven_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_V1, echo=FALSE} 
vari <- t1066_ds_Ven_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_Ven_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_Ven_w1, echo=FALSE}
label(t1066_ds_Ven_w1$depression) <- ds_label_all
depression <- t1066_ds_Ven_w1
save(depression, file = "../RData/Ven_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-Venezuela-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_V2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-Venezuela-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_V2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_V2, echo=TRUE} 
t1066_ds_Ven_w2 <- tibble(id=t1066_dep$id)
t1066_ds_Ven_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_Ven_w2$depression <- labelled(t1066_ds_Ven_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_V2, echo=FALSE} 
vari <- t1066_ds_Ven_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_Ven_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_V2, echo=FALSE}
label(t1066_ds_Ven_w2$depression) <- ds_label_all
depression <- t1066_ds_Ven_w2
save(depression, file = "../RData/Ven_w2/depression.RData")
rm(depression, t1066_dep)
```
 

 

## Urban Peru 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_UP, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanPeru-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UP1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UP1, echo=TRUE} 
t1066_ds_UP_w1 <- tibble(id=t1066_dep$id)
t1066_ds_UP_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UP_w1$depression <- labelled(t1066_ds_UP_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UP1, echo=FALSE} 
vari <- t1066_ds_UP_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UP_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_UP_w1, echo=FALSE}
label(t1066_ds_UP_w1$depression) <- ds_label_all
depression <- t1066_ds_UP_w1
save(depression, file = "../RData/UP_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

 


### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanPeru-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_UP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanPeru-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UP2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UP2, echo=TRUE} 
t1066_ds_UP_w2 <- tibble(id=t1066_dep$id)
t1066_ds_UP_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UP_w2$depression <- labelled(t1066_ds_UP_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UP2, echo=FALSE} 
vari <- t1066_ds_UP_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UP_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_UP_w2, echo=FALSE}
label(t1066_ds_UP_w2$depression) <- ds_label_all
depression <- t1066_ds_UP_w2
save(depression, file = "../RData/UP_w2/depression.RData")
rm(depression, t1066_dep)
```
 

 


## Rural Peru 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RP, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralPeru-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RP1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RP1, echo=TRUE} 
t1066_ds_RP_w1 <- tibble(id=t1066_dep$id)
t1066_ds_RP_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RP_w1$depression <- labelled(t1066_ds_RP_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RP1, echo=FALSE} 
vari <- t1066_ds_RP_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RP_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_RP_w1, echo=FALSE}
label(t1066_ds_RP_w1$depression) <- ds_label_all
depression <- t1066_ds_RP_w1
save(depression, file = "../RData/RP_w1/depression.RData")
rm(depression, t1066_dep)
```
 

 


### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralPeru-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralPeru-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RP2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RP2, echo=TRUE} 
t1066_ds_RP_w2 <- tibble(id=t1066_dep$id)
t1066_ds_RP_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RP_w2$depression <- labelled(t1066_ds_RP_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RP2, echo=FALSE} 
vari <- t1066_ds_RP_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RP_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPALRP_w2, echo=FALSE}
label(t1066_ds_RP_w2$depression) <- ds_label_all
depression <- t1066_ds_RP_w2
save(depression, file = "../RData/RP_w2/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

## Urban Mexico 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_UM1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanMexico-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UM1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UM1, echo=TRUE} 
t1066_ds_UM_w1 <- tibble(id=t1066_dep$id)
t1066_ds_UM_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UM_w1$depression <- labelled(t1066_ds_UM_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UM1, echo=FALSE} 
vari <- t1066_ds_UM_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UM_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_UM_w1, echo=FALSE}
label(t1066_ds_UM_w1$depression) <- ds_label_all
depression <- t1066_ds_UM_w1
save(depression, file = "../RData/UM_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

### Wave 2

#### Study-specific variable description

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-UrbanMexico-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |


```{r assign_UM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-UrbanMexico-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_UM2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UM2, echo=TRUE} 
t1066_ds_UM_w2 <- tibble(id=t1066_dep$id)
t1066_ds_UM_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_UM_w2$depression <- labelled(t1066_ds_UM_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UM2, echo=FALSE} 
vari <- t1066_ds_UM_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_UM_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_UM_w2, echo=FALSE}
label(t1066_ds_UM_w2$depression) <- ds_label_all
depression <- t1066_ds_UM_w2
save(depression, file = "../RData/UM_w2/depression.RData")
rm(depression, t1066_dep)
```

 

 


## Rural Mexico 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RM1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralMexico-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RM1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RM1, echo=TRUE} 
t1066_ds_RM_w1 <- tibble(id=t1066_dep$id)
t1066_ds_RM_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RM_w1$depression <- labelled(t1066_ds_RM_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RM1, echo=FALSE} 
vari <- t1066_ds_RM_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RM_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_RM_w1, echo=FALSE}
label(t1066_ds_RM_w1$depression) <- ds_label_all
depression <- t1066_ds_RM_w1
save(depression, file = "../RData/RM_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

 

### Wave 2 

#### Study-specific variable description


| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-RuralMexico-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_RM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-RuralMexico-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_RM2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RM2, echo=TRUE} 
t1066_ds_RM_w2 <- tibble(id=t1066_dep$id)
t1066_ds_RM_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_RM_w2$depression <- labelled(t1066_ds_RM_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RM2, echo=FALSE} 
vari <- t1066_ds_RM_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_RM_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
```{r importOPAL_RM_w2, echo=FALSE}
label(t1066_ds_RM_w2$depression) <- ds_label_all
depression <- t1066_ds_RM_w2
save(depression, file = "../RData/RM_w2/depression.RData")
rm(depression, t1066_dep)
```
 

 

## Puerto Rico 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_PR1, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-PuertoRico-Baseline',
                         variables=list('eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_PR1, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_PR1, echo=TRUE} 
t1066_ds_PR_w1 <- tibble(id=t1066_dep$id)
t1066_ds_PR_w1$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_PR_w1$depression <- labelled(t1066_ds_PR_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_PR1, echo=FALSE} 
vari <- t1066_ds_PR_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR1, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_PR_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_PR_w1, echo=FALSE}
label(t1066_ds_PR_w1$depression) <- ds_label_all
depression <- t1066_ds_PR_w1
save(depression, file = "../RData/PR_w1/depression.RData")
rm(depression, t1066_dep)
```
 
 

### Wave 2 

#### Study-specific variable description

 

| **Name** | `f_eurocase45`|
|-|-|
| **Label** | `euro-d case - 4/5 cutpoint`|
| **Table name** | `1066-PuertoRico-Followup` |
| **Categories** |`0 = non-case (score of 4 or less); 1 = probable EURO-D depression (score of 5 or more)`|
| **Description** |  |

```{r assign_PR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_dep','10-66.1066-PuertoRico-Followup',
                         variables=list('f_eurocase45'), missings = TRUE)
t1066_dep <- opal.execute(o,'t1066_dep')
```

```{r local_PR2, echo=FALSE} 
vari <- t1066_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(t1066_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_PR2, echo=TRUE} 
t1066_ds_PR_w2 <- tibble(id=t1066_dep$id)
t1066_ds_PR_w2$depression <- car::recode(t1066_dep[[2]], "NA=999")
t1066_ds_PR_w2$depression <- labelled(t1066_ds_PR_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_PR2, echo=FALSE} 
vari <- t1066_ds_PR_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=FALSE} 
BeforeH <- table(t1066_dep[[2]], useNA = 'ifany')
AfterH <- table(t1066_ds_PR_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

```{r importOPAL_PR_w2, echo=FALSE}
label(t1066_ds_PR_w2$depression) <- ds_label_all
depression <- t1066_ds_PR_w2
save(depression, file = "../RData/PR_w2/depression.RData")
rm(depression, t1066_dep)
```
 
 
# Quality estimation

They used the EURO-D to assess depression. 
Each item is scored 0 (symptom not present) or 1 (symptom present), generating a simple ordinal scale with a maximum score of 12. The cut-point for the identification of DSM-IV major depression and GMS/AGECAT depression was greater or equal than 4.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```