---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/bereavDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/bereavDS.R')
```



# Data process

## HRS

### Wave 1 

#### Study-specific variable description



| **Name** | `R1MSTAT`|
|-|-|
| **Label** |`R1MSTAT:W1 R Marital Status`|
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign1 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_bereav','HRS.HRS-HRS-w1',variables=list('R1MSTAT'), missings = TRUE)
```

```{r local1 hrs, echo=F}
HRS_hrs_w1_bereav <- opal.execute(o,'HRS_hrs_w1_bereav')
vari <- HRS_hrs_w1_bereav$R1MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w1_bereav$R1MSTAT, missing_values = NA)
ggplot(HRS_hrs_w1_bereav, aes(x=factor(R1MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo1 hrs, echo=TRUE}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_bereav$id)
HRS_ds_hrs_w1$bereav <- car::recode(as.vector(HRS_hrs_w1_bereav$R1MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w1$bereav <- labelled(HRS_ds_hrs_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 hrs, echo=F}
vari <- HRS_ds_hrs_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w1$bereav)
BeforeH <- table(HRS_hrs_w1_bereav$R1MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description



| **Name** | `R2MSTAT`|
|-|-|
| **Label** |`R2MSTAT:W2 R Marital Status`|
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign2 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w2_bereav','HRS.HRS-HRS-w2',variables=list('R2MSTAT'), missings = TRUE)
```

```{r local2 hrs, echo=F}
HRS_hrs_w2_bereav <- opal.execute(o,'HRS_hrs_w2_bereav')
vari <- HRS_hrs_w2_bereav$R2MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w2_bereav$R2MSTAT, missing_values = NA)
ggplot(HRS_hrs_w2_bereav, aes(x=factor(R2MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo2 hrs, echo=TRUE}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_bereav$id)
HRS_ds_hrs_w2$bereav <- car::recode(as.vector(HRS_hrs_w2_bereav$R2MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w2$bereav <- labelled(HRS_ds_hrs_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 hrs, echo=F}
vari <- HRS_ds_hrs_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w2$bereav)
BeforeH <- table(HRS_hrs_w2_bereav$R2MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description



| **Name** | `R3MSTAT`|
|-|-|
| **Label** |`R3MSTAT:W3 R Marital Status`|
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign3 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w3_bereav','HRS.HRS-HRS-w3',variables=list('R3MSTAT'), missings = TRUE)
```

```{r local3 hrs, echo=F}
HRS_hrs_w3_bereav <- opal.execute(o,'HRS_hrs_w3_bereav')
vari <- HRS_hrs_w3_bereav$R3MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w3_bereav$R3MSTAT, missing_values = NA)
ggplot(HRS_hrs_w3_bereav, aes(x=factor(R3MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo3 hrs, echo=TRUE}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_bereav$id)
HRS_ds_hrs_w3$bereav <- car::recode(as.vector(HRS_hrs_w3_bereav$R3MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w3$bereav <- labelled(HRS_ds_hrs_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 hrs, echo=F}
vari <- HRS_ds_hrs_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w3$bereav)
BeforeH <- table(HRS_hrs_w3_bereav$R3MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:4,6)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 4

#### Study-specific variable description



| **Name** | `R4MSTAT`|
|-|-|
| **Label** |`R4MSTAT:W4 R Marital Status`|
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign4 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_bereav','HRS.HRS-HRS-w4',variables=list('R4MSTAT'), missings = TRUE)
```

```{r local4 hrs, echo=F}
HRS_hrs_w4_bereav <- opal.execute(o,'HRS_hrs_w4_bereav')
vari <- HRS_hrs_w4_bereav$R4MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w4_bereav$R4MSTAT, missing_values = NA)
ggplot(HRS_hrs_w4_bereav, aes(x=factor(R4MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo4 hrs, echo=TRUE}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_bereav$id)
HRS_ds_hrs_w4$bereav <- car::recode(as.vector(HRS_hrs_w4_bereav$R4MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w4$bereav <- labelled(HRS_ds_hrs_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4 hrs, echo=F}
vari <- HRS_ds_hrs_w4$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w4$bereav)
BeforeH <- table(HRS_hrs_w4_bereav$R4MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description



| **Name** | `R5MSTAT`|
|-|-|
| **Label** |`R5MSTAT:W5 R Marital Status`|
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign5 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_bereav','HRS.HRS-HRS-w5',variables=list('R5MSTAT'), missings = TRUE)
```

```{r local5 hrs, echo=F}
HRS_hrs_w5_bereav <- opal.execute(o,'HRS_hrs_w5_bereav')
vari <- HRS_hrs_w5_bereav$R5MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w5_bereav$R5MSTAT, missing_values = NA)
ggplot(HRS_hrs_w5_bereav, aes(x=factor(R5MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo5 hrs, echo=TRUE}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_bereav$id)
HRS_ds_hrs_w5$bereav <- car::recode(as.vector(HRS_hrs_w5_bereav$R5MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w5$bereav <- labelled(HRS_ds_hrs_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5 hrs, echo=F}
vari <- HRS_ds_hrs_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w5$bereav)
BeforeH <- table(HRS_hrs_w5_bereav$R5MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description



| **Name** | `R6MSTAT`|
|-|-|
| **Label** |`R6MSTAT:W6 R Marital Status`|
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign6 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_bereav','HRS.HRS-HRS-w6',variables=list('R6MSTAT'), missings = TRUE)
```

```{r local6 hrs, echo=F}
HRS_hrs_w6_bereav <- opal.execute(o,'HRS_hrs_w6_bereav')
vari <- HRS_hrs_w6_bereav$R6MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w6_bereav$R6MSTAT, missing_values = NA)
ggplot(HRS_hrs_w6_bereav, aes(x=factor(R6MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo6 hrs, echo=TRUE}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_bereav$id)
HRS_ds_hrs_w6$bereav <- car::recode(as.vector(HRS_hrs_w6_bereav$R6MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w6$bereav <- labelled(HRS_ds_hrs_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6 hrs, echo=F}
vari <- HRS_ds_hrs_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w6$bereav)
BeforeH <- table(HRS_hrs_w6_bereav$R6MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description



| **Name** | `R7MSTAT`|
|-|-|
| **Label** |`R7MSTAT:W7 R Marital Status`|
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign7 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_bereav','HRS.HRS-HRS-w7',variables=list('R7MSTAT'), missings = TRUE)
```

```{r local7 hrs, echo=F}
HRS_hrs_w7_bereav <- opal.execute(o,'HRS_hrs_w7_bereav')
vari <- HRS_hrs_w7_bereav$R7MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w7_bereav$R7MSTAT, missing_values = NA)
ggplot(HRS_hrs_w7_bereav, aes(x=factor(R7MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo7 hrs, echo=TRUE}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_bereav$id)
HRS_ds_hrs_w7$bereav <- car::recode(as.vector(HRS_hrs_w7_bereav$R7MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w7$bereav <- labelled(HRS_ds_hrs_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7 hrs, echo=F}
vari <- HRS_ds_hrs_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w7$bereav)
BeforeH <- table(HRS_hrs_w7_bereav$R7MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description



| **Name** | `R8MSTAT`|
|-|-|
| **Label** |`R8MSTAT:W8 R Marital Status`|
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign8 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_bereav','HRS.HRS-HRS-w8',variables=list('R8MSTAT'), missings = TRUE)
```

```{r local8 hrs, echo=F}
HRS_hrs_w8_bereav <- opal.execute(o,'HRS_hrs_w8_bereav')
vari <- HRS_hrs_w8_bereav$R8MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w8_bereav$R8MSTAT, missing_values = NA)
ggplot(HRS_hrs_w8_bereav, aes(x=factor(R8MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo8 hrs, echo=TRUE}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_bereav$id)
HRS_ds_hrs_w8$bereav <- car::recode(as.vector(HRS_hrs_w8_bereav$R8MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w8$bereav <- labelled(HRS_ds_hrs_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8 hrs, echo=F}
vari <- HRS_ds_hrs_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w8$bereav)
BeforeH <- table(HRS_hrs_w8_bereav$R8MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description



| **Name** | `R9MSTAT`|
|-|-|
| **Label** |`R9MSTAT:W9 R Marital Status`|
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign9 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_bereav','HRS.HRS-HRS-w9',variables=list('R9MSTAT'), missings = TRUE)
```

```{r local9 hrs, echo=F}
HRS_hrs_w9_bereav <- opal.execute(o,'HRS_hrs_w9_bereav')
vari <- HRS_hrs_w9_bereav$R9MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w9_bereav$R9MSTAT, missing_values = NA)
ggplot(HRS_hrs_w9_bereav, aes(x=factor(R9MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo9 hrs, echo=TRUE}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_bereav$id)
HRS_ds_hrs_w9$bereav <- car::recode(as.vector(HRS_hrs_w9_bereav$R9MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w9$bereav <- labelled(HRS_ds_hrs_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9 hrs, echo=F}
vari <- HRS_ds_hrs_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w9$bereav)
BeforeH <- table(HRS_hrs_w9_bereav$R9MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_bereav','HRS.HRS-HRS-w10',variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 hrs, echo=F}
HRS_hrs_w10_bereav <- opal.execute(o,'HRS_hrs_w10_bereav')
vari <- HRS_hrs_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_hrs_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 hrs, echo=TRUE}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_bereav$id)
HRS_ds_hrs_w10$bereav <- car::recode(as.vector(HRS_hrs_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w10$bereav <- labelled(HRS_ds_hrs_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 hrs, echo=F}
vari <- HRS_ds_hrs_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w10$bereav)
BeforeH <- table(HRS_hrs_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 hrs, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_bereav','HRS.HRS-HRS-w11',variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 hrs, echo=F}
HRS_hrs_w11_bereav <- opal.execute(o,'HRS_hrs_w11_bereav')
vari <- HRS_hrs_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_hrs_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_hrs_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 hrs, echo=TRUE}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_bereav$id)
HRS_ds_hrs_w11$bereav <- car::recode(as.vector(HRS_hrs_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_hrs_w11$bereav <- labelled(HRS_ds_hrs_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 hrs, echo=F}
vari <- HRS_ds_hrs_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_hrs_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 hrs, echo=F}
AfterH <- table(HRS_ds_hrs_w11$bereav)
BeforeH <- table(HRS_hrs_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 


## AHEAD
### Wave 2

#### Study-specific variable description



| **Name** | `R2MSTAT`|
|-|-|
| **Label** |`R2MSTAT:W2 R Marital Status`|
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign2 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_bereav','HRS.HRS-AHEAD-w2', variables=list('R2MSTAT'), missings = TRUE)
```

```{r local2 ahead, echo=F}
HRS_ahead_w2_bereav <- opal.execute(o,'HRS_ahead_w2_bereav')
vari <- HRS_ahead_w2_bereav$R2MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w2_bereav$R2MSTAT, missing_values = NA)
ggplot(HRS_ahead_w2_bereav, aes(x=factor(R2MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo2 ahead, echo=TRUE}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_bereav$id)
HRS_ds_ahead_w2$bereav <- car::recode(as.vector(HRS_ahead_w2_bereav$R2MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w2$bereav <- labelled(HRS_ds_ahead_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 ahead, echo=F}
vari <- HRS_ds_ahead_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w2$bereav)
BeforeH <- table(HRS_ahead_w2_bereav$R2MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:4,6)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description



| **Name** | `R3MSTAT`|
|-|-|
| **Label** |`R3MSTAT:W3 R Marital Status`|
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign3 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_bereav','HRS.HRS-AHEAD-w3',variables=list('R3MSTAT'), missings = TRUE)
```

```{r local3 ahead, echo=F}
HRS_ahead_w3_bereav <- opal.execute(o,'HRS_ahead_w3_bereav')
vari <- HRS_ahead_w3_bereav$R3MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w3_bereav$R3MSTAT, missing_values = NA)
ggplot(HRS_ahead_w3_bereav, aes(x=factor(R3MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo3 ahead, echo=TRUE}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_bereav$id)
HRS_ds_ahead_w3$bereav <- car::recode(as.vector(HRS_ahead_w3_bereav$R3MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w3$bereav <- labelled(HRS_ds_ahead_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3 ahead, echo=F}
vari <- HRS_ds_ahead_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w3$bereav)
BeforeH <- table(HRS_ahead_w3_bereav$R3MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:4,6)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 4

#### Study-specific variable description



| **Name** | `R4MSTAT`|
|-|-|
| **Label** |`R4MSTAT:W4 R Marital Status`|
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign4 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_bereav','HRS.HRS-AHEAD-w4',variables=list('R4MSTAT'), missings = TRUE)
```

```{r local4 ahead, echo=F}
HRS_ahead_w4_bereav <- opal.execute(o,'HRS_ahead_w4_bereav')
vari <- HRS_ahead_w4_bereav$R4MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w4_bereav$R4MSTAT, missing_values = NA)
ggplot(HRS_ahead_w4_bereav, aes(x=factor(R4MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo4 ahead, echo=TRUE}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_bereav$id)
HRS_ds_ahead_w4$bereav <- car::recode(as.vector(HRS_ahead_w4_bereav$R4MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w4$bereav <- labelled(HRS_ds_ahead_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4 ahead, echo=F}
vari <- HRS_ds_ahead_w4$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w4$bereav)
BeforeH <- table(HRS_ahead_w4_bereav$R4MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description



| **Name** | `R5MSTAT`|
|-|-|
| **Label** |`R5MSTAT:W5 R Marital Status`|
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign5 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_bereav','HRS.HRS-AHEAD-w5',variables=list('R5MSTAT'), missings = TRUE)
```

```{r local5 ahead, echo=F}
HRS_ahead_w5_bereav <- opal.execute(o,'HRS_ahead_w5_bereav')
vari <- HRS_ahead_w5_bereav$R5MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w5_bereav$R5MSTAT, missing_values = NA)
ggplot(HRS_ahead_w5_bereav, aes(x=factor(R5MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo5 ahead, echo=TRUE}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_bereav$id)
HRS_ds_ahead_w5$bereav <- car::recode(as.vector(HRS_ahead_w5_bereav$R5MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w5$bereav <- labelled(HRS_ds_ahead_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5 ahead, echo=F}
vari <- HRS_ds_ahead_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w5$bereav)
BeforeH <- table(HRS_ahead_w5_bereav$R5MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description



| **Name** | `R6MSTAT`|
|-|-|
| **Label** |`R6MSTAT:W6 R Marital Status`|
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign6 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_bereav','HRS.HRS-AHEAD-w6',variables=list('R6MSTAT'), missings = TRUE)
```

```{r local6 ahead, echo=F}
HRS_ahead_w6_bereav <- opal.execute(o,'HRS_ahead_w6_bereav')
vari <- HRS_ahead_w6_bereav$R6MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w6_bereav$R6MSTAT, missing_values = NA)
ggplot(HRS_ahead_w6_bereav, aes(x=factor(R6MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo6 ahead, echo=TRUE}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_bereav$id)
HRS_ds_ahead_w6$bereav <- car::recode(as.vector(HRS_ahead_w6_bereav$R6MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w6$bereav <- labelled(HRS_ds_ahead_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6 ahead, echo=F}
vari <- HRS_ds_ahead_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w6$bereav)
BeforeH <- table(HRS_ahead_w6_bereav$R6MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description



| **Name** | `R7MSTAT`|
|-|-|
| **Label** |`R7MSTAT:W7 R Marital Status`|
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign7 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_bereav','HRS.HRS-AHEAD-w7',variables=list('R7MSTAT'), missings = TRUE)
```

```{r local7 ahead, echo=F}
HRS_ahead_w7_bereav <- opal.execute(o,'HRS_ahead_w7_bereav')
vari <- HRS_ahead_w7_bereav$R7MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w7_bereav$R7MSTAT, missing_values = NA)
ggplot(HRS_ahead_w7_bereav, aes(x=factor(R7MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo7 ahead, echo=TRUE}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_bereav$id)
HRS_ds_ahead_w7$bereav <- car::recode(as.vector(HRS_ahead_w7_bereav$R7MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w7$bereav <- labelled(HRS_ds_ahead_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7 ahead, echo=F}
vari <- HRS_ds_ahead_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w7$bereav)
BeforeH <- table(HRS_ahead_w7_bereav$R7MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description



| **Name** | `R8MSTAT`|
|-|-|
| **Label** |`R8MSTAT:W8 R Marital Status`|
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign8 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_bereav','HRS.HRS-AHEAD-w8',variables=list('R8MSTAT'), missings = TRUE)
```

```{r local8 ahead, echo=F}
HRS_ahead_w8_bereav <- opal.execute(o,'HRS_ahead_w8_bereav')
vari <- HRS_ahead_w8_bereav$R8MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w8_bereav$R8MSTAT, missing_values = NA)
ggplot(HRS_ahead_w8_bereav, aes(x=factor(R8MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo8 ahead, echo=TRUE}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_bereav$id)
HRS_ds_ahead_w8$bereav <- car::recode(as.vector(HRS_ahead_w8_bereav$R8MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w8$bereav <- labelled(HRS_ds_ahead_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8 ahead, echo=F}
vari <- HRS_ds_ahead_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w8$bereav)
BeforeH <- table(HRS_ahead_w8_bereav$R8MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description



| **Name** | `R9MSTAT`|
|-|-|
| **Label** |`R9MSTAT:W9 R Marital Status`|
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign9 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_bereav','HRS.HRS-AHEAD-w9',variables=list('R9MSTAT'), missings = TRUE)
```

```{r local9 ahead, echo=F}
HRS_ahead_w9_bereav <- opal.execute(o,'HRS_ahead_w9_bereav')
vari <- HRS_ahead_w9_bereav$R9MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w9_bereav$R9MSTAT, missing_values = NA)
ggplot(HRS_ahead_w9_bereav, aes(x=factor(R9MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo9 ahead, echo=TRUE}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_bereav$id)
HRS_ds_ahead_w9$bereav <- car::recode(as.vector(HRS_ahead_w9_bereav$R9MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w9$bereav <- labelled(HRS_ds_ahead_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9 ahead, echo=F}
vari <- HRS_ds_ahead_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w9$bereav)
BeforeH <- table(HRS_ahead_w9_bereav$R9MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_bereav','HRS.HRS-AHEAD-w10',variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 ahead, echo=F}
HRS_ahead_w10_bereav <- opal.execute(o,'HRS_ahead_w10_bereav')
vari <- HRS_ahead_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_ahead_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 ahead, echo=TRUE}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_bereav$id)
HRS_ds_ahead_w10$bereav <- car::recode(as.vector(HRS_ahead_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w10$bereav <- labelled(HRS_ds_ahead_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 ahead, echo=F}
vari <- HRS_ds_ahead_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w10$bereav)
BeforeH <- table(HRS_ahead_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 ahead, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_bereav','HRS.HRS-AHEAD-w11', variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 ahead, echo=F}
HRS_ahead_w11_bereav <- opal.execute(o,'HRS_ahead_w11_bereav')
vari <- HRS_ahead_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ahead_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_ahead_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 ahead, echo=TRUE}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_bereav$id)
HRS_ds_ahead_w11$bereav <- car::recode(as.vector(HRS_ahead_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ahead_w11$bereav <- labelled(HRS_ds_ahead_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 ahead, echo=F}
vari <- HRS_ds_ahead_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ahead_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 ahead, echo=F}
AfterH <- table(HRS_ds_ahead_w11$bereav)
BeforeH <- table(HRS_ahead_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 


## CODA

### Wave 4

#### Study-specific variable description



| **Name** | `R4MSTAT`|
|-|-|
| **Label** |`R4MSTAT:W4 R Marital Status`|
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign4 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_bereav','HRS.HRS-CODA-w4',variables=list('R4MSTAT'), missings = TRUE)
```

```{r local4 coda, echo=F}
HRS_coda_w4_bereav <- opal.execute(o,'HRS_coda_w4_bereav')
vari <- HRS_coda_w4_bereav$R4MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w4_bereav$R4MSTAT, missing_values = NA)
ggplot(HRS_coda_w4_bereav, aes(x=factor(R4MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo4 coda, echo=TRUE}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_bereav$id)
HRS_ds_coda_w4$bereav <- car::recode(as.vector(HRS_coda_w4_bereav$R4MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w4$bereav <- labelled(HRS_ds_coda_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4 coda, echo=F}
vari <- HRS_ds_coda_w4$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4 coda, echo=F}
AfterH <- table(HRS_ds_coda_w4$bereav)
BeforeH <- table(HRS_coda_w4_bereav$R4MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description



| **Name** | `R5MSTAT`|
|-|-|
| **Label** |`R5MSTAT:W5 R Marital Status`|
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign5 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_bereav','HRS.HRS-CODA-w5',variables=list('R5MSTAT'), missings = TRUE)
```

```{r local5 coda, echo=F}
HRS_coda_w5_bereav <- opal.execute(o,'HRS_coda_w5_bereav')
vari <- HRS_coda_w5_bereav$R5MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w5_bereav$R5MSTAT, missing_values = NA)
ggplot(HRS_coda_w5_bereav, aes(x=factor(R5MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`

**R script:**

```{r harmo5 coda, echo=TRUE}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_bereav$id)
HRS_ds_coda_w5$bereav <- car::recode(as.vector(HRS_coda_w5_bereav$R5MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w5$bereav <- labelled(HRS_ds_coda_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5 coda, echo=F}
vari <- HRS_ds_coda_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5 coda, echo=F}
AfterH <- table(HRS_ds_coda_w5$bereav)
BeforeH <- table(HRS_coda_w5_bereav$R5MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description



| **Name** | `R6MSTAT`|
|-|-|
| **Label** |`R6MSTAT:W6 R Marital Status`|
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign6 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_bereav','HRS.HRS-CODA-w6',variables=list('R6MSTAT'), missings = TRUE)
```

```{r local6 coda, echo=F}
HRS_coda_w6_bereav <- opal.execute(o,'HRS_coda_w6_bereav')
vari <- HRS_coda_w6_bereav$R6MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w6_bereav$R6MSTAT, missing_values = NA)
ggplot(HRS_coda_w6_bereav, aes(x=factor(R6MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo6 coda, echo=TRUE}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_bereav$id)
HRS_ds_coda_w6$bereav <- car::recode(as.vector(HRS_coda_w6_bereav$R6MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w6$bereav <- labelled(HRS_ds_coda_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6 coda, echo=F}
vari <- HRS_ds_coda_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6 coda, echo=F}
AfterH <- table(HRS_ds_coda_w6$bereav)
BeforeH <- table(HRS_coda_w6_bereav$R6MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description



| **Name** | `R7MSTAT`|
|-|-|
| **Label** |`R7MSTAT:W7 R Marital Status`|
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign7 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_bereav','HRS.HRS-CODA-w7',variables=list('R7MSTAT'), missings = TRUE)
```

```{r local7 coda, echo=F}
HRS_coda_w7_bereav <- opal.execute(o,'HRS_coda_w7_bereav')
vari <- HRS_coda_w7_bereav$R7MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w7_bereav$R7MSTAT, missing_values = NA)
ggplot(HRS_coda_w7_bereav, aes(x=factor(R7MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo7 coda, echo=TRUE}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_bereav$id)
HRS_ds_coda_w7$bereav <- car::recode(as.vector(HRS_coda_w7_bereav$R7MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w7$bereav <- labelled(HRS_ds_coda_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7 coda, echo=F}
vari <- HRS_ds_coda_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7 coda, echo=F}
AfterH <- table(HRS_ds_coda_w7$bereav)
BeforeH <- table(HRS_coda_w7_bereav$R7MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description



| **Name** | `R8MSTAT`|
|-|-|
| **Label** |`R8MSTAT:W8 R Marital Status`|
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign8 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_bereav','HRS.HRS-CODA-w8',variables=list('R8MSTAT'), missings = TRUE)
```

```{r local8 coda, echo=F}
HRS_coda_w8_bereav <- opal.execute(o,'HRS_coda_w8_bereav')
vari <- HRS_coda_w8_bereav$R8MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w8_bereav$R8MSTAT, missing_values = NA)
ggplot(HRS_coda_w8_bereav, aes(x=factor(R8MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo8 coda, echo=TRUE}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_bereav$id)
HRS_ds_coda_w8$bereav <- car::recode(as.vector(HRS_coda_w8_bereav$R8MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w8$bereav <- labelled(HRS_ds_coda_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8 coda, echo=F}
vari <- HRS_ds_coda_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8 coda, echo=F}
AfterH <- table(HRS_ds_coda_w8$bereav)
BeforeH <- table(HRS_coda_w8_bereav$R8MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description



| **Name** | `R9MSTAT`|
|-|-|
| **Label** |`R9MSTAT:W9 R Marital Status`|
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign9 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_bereav','HRS.HRS-CODA-w9',variables=list('R9MSTAT'), missings = TRUE)
```

```{r local9 coda, echo=F}
HRS_coda_w9_bereav <- opal.execute(o,'HRS_coda_w9_bereav')
vari <- HRS_coda_w9_bereav$R9MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w9_bereav$R9MSTAT, missing_values = NA)
ggplot(HRS_coda_w9_bereav, aes(x=factor(R9MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo9 coda, echo=TRUE}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_bereav$id)
HRS_ds_coda_w9$bereav <- car::recode(as.vector(HRS_coda_w9_bereav$R9MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w9$bereav <- labelled(HRS_ds_coda_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9 coda, echo=F}
vari <- HRS_ds_coda_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9 coda, echo=F}
AfterH <- table(HRS_ds_coda_w9$bereav)
BeforeH <- table(HRS_coda_w9_bereav$R9MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_bereav','HRS.HRS-CODA-w10',variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 coda, echo=F}
HRS_coda_w10_bereav <- opal.execute(o,'HRS_coda_w10_bereav')
vari <- HRS_coda_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_coda_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 coda, echo=TRUE}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_bereav$id)
HRS_ds_coda_w10$bereav <- car::recode(as.vector(HRS_coda_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w10$bereav <- labelled(HRS_ds_coda_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 coda, echo=F}
vari <- HRS_ds_coda_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 coda, echo=F}
AfterH <- table(HRS_ds_coda_w10$bereav)
BeforeH <- table(HRS_coda_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 coda, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_bereav','HRS.HRS-CODA-w11',variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 coda, echo=F}
HRS_coda_w11_bereav <- opal.execute(o,'HRS_coda_w11_bereav')
vari <- HRS_coda_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_coda_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_coda_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 coda, echo=TRUE}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_bereav$id)
HRS_ds_coda_w11$bereav <- car::recode(as.vector(HRS_coda_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_coda_w11$bereav <- labelled(HRS_ds_coda_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 coda, echo=F}
vari <- HRS_ds_coda_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_coda_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 coda, echo=F}
AfterH <- table(HRS_ds_coda_w11$bereav)
BeforeH <- table(HRS_coda_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 


## WB
### Wave 4

#### Study-specific variable description



| **Name** | `R4MSTAT`|
|-|-|
| **Label** |`R4MSTAT:W4 R Marital Status`|
| **Table name** |`HRS-WB-w4`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign4 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_bereav','HRS.HRS-WB-w4',variables=list('R4MSTAT'), missings = TRUE)
```

```{r local4 wb, echo=F}
HRS_wb_w4_bereav <- opal.execute(o,'HRS_wb_w4_bereav')
vari <- HRS_wb_w4_bereav$R4MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w4_bereav$R4MSTAT, missing_values = NA)
ggplot(HRS_wb_w4_bereav, aes(x=factor(R4MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo4 wb, echo=TRUE}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_bereav$id)
HRS_ds_wb_w4$bereav <- car::recode(as.vector(HRS_wb_w4_bereav$R4MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w4$bereav <- labelled(HRS_ds_wb_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4 wb, echo=F}
vari <- HRS_ds_wb_w4$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4 wb, echo=F}
AfterH <- table(HRS_ds_wb_w4$bereav)
BeforeH <- table(HRS_wb_w4_bereav$R4MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description



| **Name** | `R5MSTAT`|
|-|-|
| **Label** |`R5MSTAT:W5 R Marital Status`|
| **Table name** |`HRS-WB-w5`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign5 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_bereav','HRS.HRS-WB-w5',variables=list('R5MSTAT'), missings = TRUE)
```

```{r local5 wb, echo=F}
HRS_wb_w5_bereav <- opal.execute(o,'HRS_wb_w5_bereav')
vari <- HRS_wb_w5_bereav$R5MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w5_bereav$R5MSTAT, missing_values = NA)
ggplot(HRS_wb_w5_bereav, aes(x=factor(R5MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo5 wb, echo=TRUE}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_bereav$id)
HRS_ds_wb_w5$bereav <- car::recode(as.vector(HRS_wb_w5_bereav$R5MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w5$bereav <- labelled(HRS_ds_wb_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5 wb, echo=F}
vari <- HRS_ds_wb_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5 wb, echo=F}
AfterH <- table(HRS_ds_wb_w5$bereav)
BeforeH <- table(HRS_wb_w5_bereav$R5MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description



| **Name** | `R6MSTAT`|
|-|-|
| **Label** |`R6MSTAT:W6 R Marital Status`|
| **Table name** |`HRS-WB-w6`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign6 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_bereav','HRS.HRS-WB-w6',variables=list('R6MSTAT'), missings = TRUE)
```

```{r local6 wb, echo=F}
HRS_wb_w6_bereav <- opal.execute(o,'HRS_wb_w6_bereav')
vari <- HRS_wb_w6_bereav$R6MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w6_bereav$R6MSTAT, missing_values = NA)
ggplot(HRS_wb_w6_bereav, aes(x=factor(R6MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo6 wb, echo=TRUE}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_bereav$id)
HRS_ds_wb_w6$bereav <- car::recode(as.vector(HRS_wb_w6_bereav$R6MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w6$bereav <- labelled(HRS_ds_wb_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6 wb, echo=F}
vari <- HRS_ds_wb_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6 wb, echo=F}
AfterH <- table(HRS_ds_wb_w6$bereav)
BeforeH <- table(HRS_wb_w6_bereav$R6MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description



| **Name** | `R7MSTAT`|
|-|-|
| **Label** |`R7MSTAT:W7 R Marital Status`|
| **Table name** |`HRS-WB-w7`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign7 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_bereav','HRS.HRS-WB-w7',variables=list('R7MSTAT'), missings = TRUE)
```

```{r local7 wb, echo=F}
HRS_wb_w7_bereav <- opal.execute(o,'HRS_wb_w7_bereav')
vari <- HRS_wb_w7_bereav$R7MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w7_bereav$R7MSTAT, missing_values = NA)
ggplot(HRS_wb_w7_bereav, aes(x=factor(R7MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo7 wb, echo=TRUE}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_bereav$id)
HRS_ds_wb_w7$bereav <- car::recode(as.vector(HRS_wb_w7_bereav$R7MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w7$bereav <- labelled(HRS_ds_wb_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7 wb, echo=F}
vari <- HRS_ds_wb_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7 wb, echo=F}
AfterH <- table(HRS_ds_wb_w7$bereav)
BeforeH <- table(HRS_wb_w7_bereav$R7MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description



| **Name** | `R8MSTAT`|
|-|-|
| **Label** |`R8MSTAT:W8 R Marital Status`|
| **Table name** |`HRS-WB-w8`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign8 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_bereav','HRS.HRS-WB-w8',variables=list('R8MSTAT'), missings = TRUE)
```

```{r local8 wb, echo=F}
HRS_wb_w8_bereav <- opal.execute(o,'HRS_wb_w8_bereav')
vari <- HRS_wb_w8_bereav$R8MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w8_bereav$R8MSTAT, missing_values = NA)
ggplot(HRS_wb_w8_bereav, aes(x=factor(R8MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo8 wb, echo=TRUE}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_bereav$id)
HRS_ds_wb_w8$bereav <- car::recode(as.vector(HRS_wb_w8_bereav$R8MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w8$bereav <- labelled(HRS_ds_wb_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8 wb, echo=F}
vari <- HRS_ds_wb_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8 wb, echo=F}
AfterH <- table(HRS_ds_wb_w8$bereav)
BeforeH <- table(HRS_wb_w8_bereav$R8MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description



| **Name** | `R9MSTAT`|
|-|-|
| **Label** |`R9MSTAT:W9 R Marital Status`|
| **Table name** |`HRS-WB-w9`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign9 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_bereav','HRS.HRS-WB-w9',variables=list('R9MSTAT'), missings = TRUE)
```

```{r local9 wb, echo=F}
HRS_wb_w9_bereav <- opal.execute(o,'HRS_wb_w9_bereav')
vari <- HRS_wb_w9_bereav$R9MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w9_bereav$R9MSTAT, missing_values = NA)
ggplot(HRS_wb_w9_bereav, aes(x=factor(R9MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo9 wb, echo=TRUE}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_bereav$id)
HRS_ds_wb_w9$bereav <- car::recode(as.vector(HRS_wb_w9_bereav$R9MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w9$bereav <- labelled(HRS_ds_wb_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9 wb, echo=F}
vari <- HRS_ds_wb_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9 wb, echo=F}
AfterH <- table(HRS_ds_wb_w9$bereav)
BeforeH <- table(HRS_wb_w9_bereav$R9MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-WB-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_bereav','HRS.HRS-WB-w10', variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 wb, echo=F}
HRS_wb_w10_bereav <- opal.execute(o,'HRS_wb_w10_bereav')
vari <- HRS_wb_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_wb_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 wb, echo=TRUE}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_bereav$id)
HRS_ds_wb_w10$bereav <- car::recode(as.vector(HRS_wb_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w10$bereav <- labelled(HRS_ds_wb_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 wb, echo=F}
vari <- HRS_ds_wb_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 wb, echo=F}
AfterH <- table(HRS_ds_wb_w10$bereav)
BeforeH <- table(HRS_wb_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-WB-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 wb, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_bereav','HRS.HRS-WB-w11',variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 wb, echo=F}
HRS_wb_w11_bereav <- opal.execute(o,'HRS_wb_w11_bereav')
vari <- HRS_wb_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_wb_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_wb_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 wb, echo=TRUE}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_bereav$id)
HRS_ds_wb_w11$bereav <- car::recode(as.vector(HRS_wb_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_wb_w11$bereav <- labelled(HRS_ds_wb_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 wb, echo=F}
vari <- HRS_ds_wb_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_wb_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 wb, echo=F}
AfterH <- table(HRS_ds_wb_w11$bereav)
BeforeH <- table(HRS_wb_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 


## EBB

### Wave 7

#### Study-specific variable description



| **Name** | `R7MSTAT`|
|-|-|
| **Label** |`R7MSTAT:W7 R Marital Status`|
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign7 ebb, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_bereav','HRS.HRS-EBB-w7',variables=list('R7MSTAT'), missings = TRUE)
```

```{r local7 ebb, echo=F}
HRS_ebb_w7_bereav <- opal.execute(o,'HRS_ebb_w7_bereav')
vari <- HRS_ebb_w7_bereav$R7MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ebb_w7_bereav$R7MSTAT, missing_values = NA)
ggplot(HRS_ebb_w7_bereav, aes(x=factor(R7MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo7 ebb, echo=TRUE}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_bereav$id)
HRS_ds_ebb_w7$bereav <- car::recode(as.vector(HRS_ebb_w7_bereav$R7MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ebb_w7$bereav <- labelled(HRS_ds_ebb_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7 ebb, echo=F}
vari <- HRS_ds_ebb_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ebb_w7$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7 ebb, echo=F}
AfterH <- table(HRS_ds_ebb_w7$bereav)
BeforeH <- table(HRS_ebb_w7_bereav$R7MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:5,7)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 8

#### Study-specific variable description



| **Name** | `R8MSTAT`|
|-|-|
| **Label** |`R8MSTAT:W8 R Marital Status`|
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign8 ebb, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_bereav','HRS.HRS-EBB-w8',variables=list('R8MSTAT'), missings = TRUE)
```

```{r local8 ebb, echo=F}
HRS_ebb_w8_bereav <- opal.execute(o,'HRS_ebb_w8_bereav')
vari <- HRS_ebb_w8_bereav$R8MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ebb_w8_bereav$R8MSTAT, missing_values = NA)
ggplot(HRS_ebb_w8_bereav, aes(x=factor(R8MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo8 ebb, echo=TRUE}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_bereav$id)
HRS_ds_ebb_w8$bereav <- car::recode(as.vector(HRS_ebb_w8_bereav$R8MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ebb_w8$bereav <- labelled(HRS_ds_ebb_w8$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8 ebb, echo=F}
vari <- HRS_ds_ebb_w8$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ebb_w8$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w8, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8 ebb, echo=F}
AfterH <- table(HRS_ds_ebb_w8$bereav)
BeforeH <- table(HRS_ebb_w8_bereav$R8MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 



### Wave 9

#### Study-specific variable description



| **Name** | `R9MSTAT`|
|-|-|
| **Label** |`R9MSTAT:W9 R Marital Status`|
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign9 ebb, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_bereav','HRS.HRS-EBB-w9',variables=list('R9MSTAT'), missings = TRUE)
```

```{r local9 ebb, echo=F}
HRS_ebb_w9_bereav <- opal.execute(o,'HRS_ebb_w9_bereav')
vari <- HRS_ebb_w9_bereav$R9MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ebb_w9_bereav$R9MSTAT, missing_values = NA)
ggplot(HRS_ebb_w9_bereav, aes(x=factor(R9MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo9 ebb, echo=TRUE}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_bereav$id)
HRS_ds_ebb_w9$bereav <- car::recode(as.vector(HRS_ebb_w9_bereav$R9MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ebb_w9$bereav <- labelled(HRS_ds_ebb_w9$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9 ebb, echo=F}
vari <- HRS_ds_ebb_w9$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ebb_w9$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w9, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9 ebb, echo=F}
AfterH <- table(HRS_ds_ebb_w9$bereav)
BeforeH <- table(HRS_ebb_w9_bereav$R9MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 ebb, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_bereav','HRS.HRS-EBB-w10',variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 ebb, echo=F}
HRS_ebb_w10_bereav <- opal.execute(o,'HRS_ebb_w10_bereav')
vari <- HRS_ebb_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ebb_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_ebb_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 ebb, echo=TRUE}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_bereav$id)
HRS_ds_ebb_w10$bereav <- car::recode(as.vector(HRS_ebb_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ebb_w10$bereav <- labelled(HRS_ds_ebb_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 ebb, echo=F}
vari <- HRS_ds_ebb_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ebb_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 ebb, echo=F}
AfterH <- table(HRS_ds_ebb_w10$bereav)
BeforeH <- table(HRS_ebb_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 ebb, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_bereav','HRS.HRS-EBB-w11', variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 ebb, echo=F}
HRS_ebb_w11_bereav <- opal.execute(o,'HRS_ebb_w11_bereav')
vari <- HRS_ebb_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_ebb_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_ebb_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 ebb, echo=TRUE}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_bereav$id)
HRS_ds_ebb_w11$bereav <- car::recode(as.vector(HRS_ebb_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_ebb_w11$bereav <- labelled(HRS_ds_ebb_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 ebb, echo=F}
vari <- HRS_ds_ebb_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_ebb_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 ebb, echo=F}
AfterH <- table(HRS_ds_ebb_w11$bereav)
BeforeH <- table(HRS_ebb_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 


## MBB
### Wave 10

#### Study-specific variable description



| **Name** | `R10MSTAT`|
|-|-|
| **Label** |`R10MSTAT:W10 R Marital Status`|
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |











 
```{r assign10 mbb, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_bereav','HRS.HRS-MBB-w10',variables=list('R10MSTAT'), missings = TRUE)
```

```{r local10 mbb, echo=F}
HRS_mbb_w10_bereav <- opal.execute(o,'HRS_mbb_w10_bereav')
vari <- HRS_mbb_w10_bereav$R10MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_mbb_w10_bereav$R10MSTAT, missing_values = NA)
ggplot(HRS_mbb_w10_bereav, aes(x=factor(R10MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo10 mbb, echo=TRUE}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_bereav$id)
HRS_ds_mbb_w10$bereav <- car::recode(as.vector(HRS_mbb_w10_bereav$R10MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_mbb_w10$bereav <- labelled(HRS_ds_mbb_w10$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10 mbb, echo=F}
vari <- HRS_ds_mbb_w10$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_mbb_w10$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w10, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10 mbb, echo=F}
AfterH <- table(HRS_ds_mbb_w10$bereav)
BeforeH <- table(HRS_mbb_w10_bereav$R10MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```

 
 




### Wave 11

#### Study-specific variable description



| **Name** | `R11MSTAT`|
|-|-|
| **Label** |`R11MSTAT:W11 R Marital Status`|
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`1 = Married`<br/>`2 = Married, spouse absent`<br/>`3 = Partnered`<br/>`4 = Separated`<br/>`5 = Divorced`<br/>`6 = Separated/Divorced`<br/>`7 = Widowed`<br/>`8 = Never Married`|
| **Missings** |`NA`|
| **Description** |  |










    
 
```{r assign11 mbb, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_bereav','HRS.HRS-MBB-w11',variables=list('R11MSTAT'), missings = TRUE)
```

```{r local11 mbb, echo=F}
HRS_mbb_w11_bereav <- opal.execute(o,'HRS_mbb_w11_bereav')
vari <- HRS_mbb_w11_bereav$R11MSTAT
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HRS_mbb_w11_bereav$R11MSTAT, missing_values = NA)
ggplot(HRS_mbb_w11_bereav, aes(x=factor(R11MSTAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `7 into 1`
* `1:6,8 into 0`
* `NA into 999`

**R script:**

```{r harmo11 mbb, echo=TRUE}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_bereav$id)
HRS_ds_mbb_w11$bereav <- car::recode(as.vector(HRS_mbb_w11_bereav$R11MSTAT), "7='1'; 1:6='0'; 8='0'; NA='999'")
HRS_ds_mbb_w11$bereav <- labelled(HRS_ds_mbb_w11$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11 mbb, echo=F}
vari <- HRS_ds_mbb_w11$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_ds_mbb_w11$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w11, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11 mbb, echo=F}
AfterH <- table(HRS_ds_mbb_w11$bereav)
BeforeH <- table(HRS_mbb_w11_bereav$R11MSTAT, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[['7']]
BeforeH1[[1]] <- sum(BeforeH[c(1:6,8)])
BeforeH1[[3]] <- BeforeH[[length(BeforeH)]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:6&8->0","7->1","NA->999")
kable(C)
```







```{r final, echo=F}

l.hrs <- list(hrs_w1 = HRS_ds_hrs_w1, hrs_w2 = HRS_ds_hrs_w2, hrs_w3 = HRS_ds_hrs_w3, hrs_w4 = HRS_ds_hrs_w4, hrs_w5 = HRS_ds_hrs_w5, hrs_w6 = HRS_ds_hrs_w6, hrs_w7 = HRS_ds_hrs_w7, hrs_w8 = HRS_ds_hrs_w8, hrs_w9 = HRS_ds_hrs_w9, hrs_w10 = HRS_ds_hrs_w10, hrs_w11 = HRS_ds_hrs_w11, ahead_w2 = HRS_ds_ahead_w2, ahead_w3 = HRS_ds_ahead_w3, ahead_w4 = HRS_ds_ahead_w4, ahead_w5 = HRS_ds_ahead_w5, ahead_w6 = HRS_ds_ahead_w6, ahead_w7 = HRS_ds_ahead_w7, ahead_w8 = HRS_ds_ahead_w8, ahead_w9 = HRS_ds_ahead_w9, ahead_w10 = HRS_ds_ahead_w10, ahead_w11 = HRS_ds_ahead_w11, coda_w4 = HRS_ds_coda_w4, coda_w5 = HRS_ds_coda_w5, coda_w6 = HRS_ds_coda_w6, coda_w7 = HRS_ds_coda_w7, coda_w8 = HRS_ds_coda_w8, coda_w9 = HRS_ds_coda_w9, coda_w10 = HRS_ds_coda_w10, coda_w11 = HRS_ds_coda_w11, wb_w4 = HRS_ds_wb_w4, wb_w5 = HRS_ds_wb_w5, wb_w6 = HRS_ds_wb_w6, wb_w7 = HRS_ds_wb_w7, wb_w8 = HRS_ds_wb_w8, wb_w9 = HRS_ds_wb_w9, wb_w10 = HRS_ds_wb_w10, wb_w11 = HRS_ds_wb_w11, ebb_w7 = HRS_ds_ebb_w7, ebb_w8 = HRS_ds_ebb_w8, ebb_w9 = HRS_ds_ebb_w9, ebb_w10 = HRS_ds_ebb_w10, ebb_w11 = HRS_ds_ebb_w11, mbb_w10 = HRS_ds_mbb_w10, mbb_w11 = HRS_ds_mbb_w11)

for(name in names(l.hrs)) {
  m_name <- paste0("HRS_m_ds_",name)
  aux_object <- l.hrs[[name]]
  label(l.hrs[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hrs[[name]][[2]] <- labelled(l.hrs[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

```




## Summary of descriptive statistics of the harmonised variable `bereav` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


**R script:**

```{r summ}

# Table HRS
l.hds <- l.hrs[grep("hrs_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])



# Table AHEAD
l.hds <- l.hrs[grep("ahead_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])



# Table CODA
l.hds <- l.hrs[grep("coda_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


# Table WB
l.hds <- l.hrs[grep("wb_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


# Table EBB
l.hds <- l.hrs[grep("ebb_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


# Table MBB
l.hds <- l.hrs[grep("mbb_w",names(l.hrs))]
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))
kable(t.hds)

dbb <- get(paste0("HRS_m_ds_",names(l.hds)[1]))[,c("id","bereav")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("HRS_m_ds_",names(l.hds)[ind]))[,c("id","bereav")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", substr(names(l.hds),regexpr("_w[0-9]",names(l.hds))+1,nchar(names(l.hds))))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```











```{r save, echo=FALSE}
bereav <- HRS_ds_ahead_w2
save(bereav, file = "../RData/ahead_w2/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w3
save(bereav, file = "../RData/ahead_w3/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w4
save(bereav, file = "../RData/ahead_w4/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w5
save(bereav, file = "../RData/ahead_w5/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w6
save(bereav, file = "../RData/ahead_w6/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w7
save(bereav, file = "../RData/ahead_w7/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w8
save(bereav, file = "../RData/ahead_w8/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w9
save(bereav, file = "../RData/ahead_w9/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w10
save(bereav, file = "../RData/ahead_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ahead_w11
save(bereav, file = "../RData/ahead_w11/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w4
save(bereav, file = "../RData/coda_w4/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w5
save(bereav, file = "../RData/coda_w5/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w6
save(bereav, file = "../RData/coda_w6/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w7
save(bereav, file = "../RData/coda_w7/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w8
save(bereav, file = "../RData/coda_w8/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w9
save(bereav, file = "../RData/coda_w9/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w10
save(bereav, file = "../RData/coda_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_coda_w11
save(bereav, file = "../RData/coda_w11/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ebb_w7
save(bereav, file = "../RData/ebb_w7/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ebb_w8
save(bereav, file = "../RData/ebb_w8/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ebb_w9
save(bereav, file = "../RData/ebb_w9/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ebb_w10
save(bereav, file = "../RData/ebb_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_ebb_w11
save(bereav, file = "../RData/ebb_w11/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w1
save(bereav, file = "../RData/hrs_w1/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w2
save(bereav, file = "../RData/hrs_w2/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w3
save(bereav, file = "../RData/hrs_w3/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w4
save(bereav, file = "../RData/hrs_w4/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w5
save(bereav, file = "../RData/hrs_w5/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w6
save(bereav, file = "../RData/hrs_w6/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w7
save(bereav, file = "../RData/hrs_w7/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w8
save(bereav, file = "../RData/hrs_w8/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w9
save(bereav, file = "../RData/hrs_w9/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w10
save(bereav, file = "../RData/hrs_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_hrs_w11
save(bereav, file = "../RData/hrs_w11/bereav.RData")
rm(bereav)

bereav <- HRS_ds_mbb_w10
save(bereav, file = "../RData/mbb_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_mbb_w11
save(bereav, file = "../RData/mbb_w11/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w4
save(bereav, file = "../RData/wb_w4/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w5
save(bereav, file = "../RData/wb_w5/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w6
save(bereav, file = "../RData/wb_w6/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w7
save(bereav, file = "../RData/wb_w7/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w8
save(bereav, file = "../RData/wb_w8/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w9
save(bereav, file = "../RData/wb_w9/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w10
save(bereav, file = "../RData/wb_w10/bereav.RData")
rm(bereav)

bereav <- HRS_ds_wb_w11
save(bereav, file = "../RData/wb_w11/bereav.RData")
rm(bereav)


```

# Quality estimation

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

