---
title: "Day of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `dintw`
* Variable label: `day of interview`
* Variable description: `day of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Mexico

### MHAS - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ps31_1`
* Label: `Day of interview`


```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_dinter','Mexican Health Aging Study.MHAS-2001',
                         variables=list('ps31_1'), missings = TRUE)
```

```{r local1}
MHAS_w1_dinter <- opal.execute(o,'MHAS_w1_dinter')
Continuous_summary(var = MHAS_w1_dinter$ps31_1, missing_values = NA)
ggplot(MHAS_w1_dinter, aes(x=factor(ps31_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

There is a value that is a value 0 that is a mistake and it will be recoded as missing with 999 code. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_dinter$id)
MHAS_ds_w1$dintw <- car::recode(MHAS_w1_dinter$ps31_1, "NA=999; 0=999")
MHAS_ds_w1$dintw <- labelled(MHAS_ds_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = MHAS_ds_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation1}
BeforeH <- table(MHAS_w1_dinter$ps31_1, useNA = "ifany")
BeforeH <- c(BeforeH[2:length(BeforeH)], BeforeH[1])
AfterH <- table(MHAS_ds_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "0->999")
kable(C)
```



#### Import to OPAL
```{r importOPAL1}
val_labels(MHAS_ds_w1) <- NULL
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
dintw <- MHAS_ds_w1
save(dintw, file = "../RData/w1/dintw.RData")
rm(dintw)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$dintw <- car::recode(MHAS_m_ds_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```








### MHAS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ent4_1`
* Label: `Day of interview`


```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_dinter','Mexican Health Aging Study.MHAS_2003',
                         variables=list('ent4_1'), missings = TRUE)

```

```{r local2}
MHAS_w2_dinter <- opal.execute(o,'MHAS_w2_dinter')
Continuous_summary(var = MHAS_w2_dinter$ent4_1, missing_values = NA)
ggplot(MHAS_w2_dinter, aes(x=factor(ent4_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_dinter$id)
MHAS_ds_w2$dintw <- car::recode(MHAS_w2_dinter$ent4_1, "NA=999")
MHAS_ds_w2$dintw <- labelled(MHAS_ds_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = MHAS_ds_w2$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation2}
BeforeH <- table(MHAS_w2_dinter$ent4_1, useNA = "ifany")
AfterH <- table(MHAS_ds_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```



#### Import to OPAL
```{r importOPAL2}
val_labels(MHAS_ds_w2) <- NULL
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
dintw <- MHAS_ds_w2
save(dintw, file = "../RData/w2/dintw.RData")
rm(dintw)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$dintw <- car::recode(MHAS_m_ds_w2$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```








### MHAS - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `int_date_12`
* Label: `Interview date 2012`
* Type of variable: `countinous`

```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_dinter','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('int_date_12'), missings = TRUE)

```	


```{r local3}
MHAS_w3_dinter <- opal.execute(o,'MHAS_w3_dinter')

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i],function(x) substring(x, first=c(1, 4, 7), last=c(2, 5, 10)))))
    }
  colnames(D) <- c("Day", "Month", "Year")
  D
}

MHAS_w3_dinter <- cbind(MHAS_w3_dinter, Date_of_birth(MHAS_w3_dinter$int_date_12))
Continuous_summary(var = MHAS_w3_dinter$Day, missing_values = NA)
ggplot(MHAS_w3_dinter, aes(x=factor(Day))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_dinter$id)
MHAS_ds_w3$dintw <- car::recode(MHAS_w3_dinter$Day, "NA=999")
MHAS_ds_w3$dintw <- labelled(MHAS_ds_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = MHAS_ds_w3$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation3}
BeforeH <- table(MHAS_w3_dinter$Day, useNA = "ifany")
AfterH <- table(MHAS_ds_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

#### Quality estimation
No comments.

#### Import to OPAL
```{r importOPAL3}
val_labels(MHAS_ds_w3) <- NULL
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
dintw <- MHAS_ds_w3
save(dintw, file = "../RData/w3/dintw.RData")
rm(dintw)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$dintw <- car::recode(MHAS_m_ds_w3$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
