---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/yintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/yintwDS.R')
```

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

No variable.

``` {r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('sexo'), missings = TRUE)
MHAS_w1 <- opal.execute(o,'MHAS_w1')
```

#### Harmonisation algorithm
The harmonized variable is going to be computed as 2001.

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$yintw <- 2001
```

#### Statistics of the new harmonised variable
``` {r descript1, echo=F}
vbl <- MHAS_ds_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
``` {r crosstabulation1, echo=F}
```









### Wave 2 

#### Study-specific variable description

No variable.


``` {r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',variables=list('cunicah'), missings = TRUE)
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')
```	



#### Harmonisation algorithm
The harmonized variable is going to be computed as 2003.

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_id$id)
MHAS_ds_w2$yintw <- 2003
```

#### Statistics of the new harmonised variable
``` {r descript2, echo=F}
vbl <- MHAS_ds_w2$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
``` {r crosstabulation2, echo=F}
```









### Wave 3 

#### Study-specific variable description

| **Name** |`int_date_12`|
|-|-|
| **Label** |`Interview date 2012`|
| **Table name** |`MHAS_2012_new`|
| **Type of variable** |`date`|
| **Description** |  |


``` {r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new', variables=list('int_date_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')

```	



```{r preharm}

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i],function(x) substring(x, first=c(1, 4, 7), last=c(2, 5, 10)))))
    }
  colnames(D) <- c("Day", "Month", "Year")
  D
}

MHAS_w3 <- cbind(MHAS_w3, Date_of_birth(MHAS_w3$int_date_12))

```

``` {r local3, echo=F}

vbl <- MHAS_w3$Year
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_w3, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded 2012 since is the most frequent value.

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$yintw <- car::recode(MHAS_w3$Year, "NA=2012")
MHAS_ds_w3$yintw <- labelled(MHAS_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
``` {r descript3, echo=F}
vbl <- MHAS_ds_w3$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
``` {r crosstabulation3, echo=F}
BeforeH <- table(MHAS_w3$Year, useNA = "ifany")
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2,4)]), BeforeH[3])
AfterH <- table(MHAS_ds_w3$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2009", "(NA,2012)->2012", "2013")
kable(C)

```







## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation
In waves 1 and 2, the authors of the study do not reveal the exact date of the interview for anonymization reasons. For harmonization purposes we assume is that of the wave (based on study time lapse information).

In wave 3, the study-specific variable with the interview date assign 2009 as year of interview to three individuals, even when the data collection for third wave was along 2012.

```{r echo=F}

kable(MHAS_w3[which(MHAS_ds_w3$yintw==2009),], align = 'c')

```





```{r closeRsession, echo=FALSE}
opal.logout(o)
```
