---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```



# Data process



## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `factori_01` |
|-|-|
| **Label** | `Person weight 2001`|
| **Table name**  | `master_follow_up_file_2012_nomissUNID`|
| **Categories** | `continuous` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_id','Mexican Health Aging Study.MHAS-2001',variables=list('unhhid'), missings = T)
MHAS_w1_id <- opal.execute(o,'MHAS_w1_id')

opal.assign.table.tibble(o, 'MHAS_w1_factor','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID',variables=list('factori_01'), missings = T)
MHAS_w1_factor <- opal.execute(o,'MHAS_w1_factor')

MHAS_w1 <- left_join(MHAS_w1_id,MHAS_w1_factor,by="id")

```


```{r local w1, echo=F}


vbl <- MHAS_w1$factori_01
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'factori_01')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w1,!vbl %in% vbl_miss), aes(factori_01)) + geom_bar(stat="bin",  fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

**R script:**

```{r harmo w1}

MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
n <- length(MHAS_w1$id[which(!is.na(MHAS_w1$factori_01))])
N <- sum(MHAS_w1$factori_01,na.rm = T)
MHAS_ds_w1$w <- car::recode(MHAS_w1$factori_01*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin",  fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 2

#### Study-specific variable description

| **Name** | `factori_03`|
|-|-|
| **Label** | `Person weight 2003`|
| **Table name**  | `MHAS_2003`|
| **Categories** | `continuous` |
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',variables=list('cunicah'), missings = T)
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')

opal.assign.table.tibble(o, 'MHAS_w2_factor','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID',variables=list('factori_03'), missings = T)
MHAS_w2_factor <- opal.execute(o,'MHAS_w2_factor')

MHAS_w2 <- left_join(MHAS_w2_id,MHAS_w2_factor,by="id")

```


```{r local w2, echo=F}


vbl <- MHAS_w2$factori_03
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'factori_03')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2,!vbl %in% vbl_miss), aes(factori_03)) + geom_bar(stat="bin",  fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

**R script:**

```{r harmo w2}

MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
n <- length(MHAS_w2$id[which(!is.na(MHAS_w2$factori_03))])
N <- sum(MHAS_w2$factori_03,na.rm = T)
MHAS_ds_w2$w <- car::recode(MHAS_w2$factori_03*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w2,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin",  fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


### Wave 3

#### Study-specific variable description

| **Name** | `factori_12`|
|-|-|
| **Label** | `Individual weight 2012`|
| **Table name**  | `MHAS_2012_new`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3_id','Mexican Health Aging Study.MHAS_2012_new',variables=list('cunicah'), missings = T)
MHAS_w3_id <- opal.execute(o,'MHAS_w3_id')

opal.assign.table.tibble(o, 'MHAS_w3_factor','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID',variables=list('factori_12'), missings = T)
MHAS_w3_factor <- opal.execute(o,'MHAS_w3_factor')

MHAS_w3 <- left_join(MHAS_w3_id,MHAS_w3_factor,by="id")

```


```{r local w3, echo=F}


vbl <- MHAS_w3$factori_12
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'factori_12')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3,!vbl %in% vbl_miss), aes(factori_12)) + geom_bar(stat="bin",  fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

**R script:**

```{r harmo w3}

MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
n <- length(MHAS_w3$id[which(!is.na(MHAS_w3$factori_12))])
N <- sum(MHAS_w3$factori_12,na.rm = T)
MHAS_ds_w3$w <- car::recode(MHAS_w3$factori_12*n/N,"NA=999")

```



#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w3,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="bin",  fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

label(MHAS_ds_w1$w) <- ds_label
label(MHAS_ds_w2$w) <- ds_label
label(MHAS_ds_w3$w) <- ds_label

l.MHAS <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(index in seq_along(l.MHAS)){
  w <- l.MHAS[[index]]
  save(w, file = paste0(datafolder,names(l.MHAS)[index],"/w.RData"))
}

```
<!-- ########################################################## --> 


# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





