---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process



## Finland


### Wave 1


#### Study-specific variable description

| **Name** | `q1503_work_now` | `q1504_reason`|`q1505_stop_age`|`q1501_ever_worked`|
|-|-|-|-|-|
| **Label** | `Currently working?`| `Reason not working`|`age stop`| `Ever worked`|
| **Table name**  | `Courage_Finland_w1`| `Courage_Finland_w1`| `Courage_Finland_w1`|`Courage_Finland_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` |`1 = HOMEMAKER`<br/>`2 = COULDN'T FIND WORK`<br/>`3 = UNPAID/VOLUNTARY`<br/>`4 = STUDIES/TRAINING`<br/>`5 = HEALTH`<br/>`6 = CARE FAMILY`<br/>`7 = NO NEED`<br/>`8 = NOT PERMITTED`<br/>`9 = RETIRED/TOO OLD`<br/>`10 = LAID OFF`<br/>`11 = SEASONAL WORK`<br/>`12 = VACATION/SICK LEAVE`<br/>`87 = OTHER, SPECIFY`|`continuous`|`1 = YES WORKED`<br/>`2 = NEVER WORKED`|
| **Missings** | `NA`| `NA`|`-8 = DK`|`NA`|
| **Description** |  |  |  |  |

```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q1503_work_now','q1504_reason','q1505_stop_age','q1501_ever_worked'), missings = T)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')

```

```{r local fin_w1, echo=F}

vbl <- COURAGE_fin_w1$q1503_work_now
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1503_work_now')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q1503_work_now))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q1504_reason
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1504_reason')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q1504_reason))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q1505_stop_age
vbl_miss <- c(-8)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505_stop_age')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(COURAGE_fin_w1,!vbl %in% vbl_miss), aes(q1505_stop_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q1501_ever_worked
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1501_ever_worked')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q1501_ever_worked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504_reason == 9 into 1`
* `q1504_reason == 1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 12 or 87 or q1503_work_now == 1 into 0`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = q1505_stop_age`
* `-8 into 998`
* `if retired == 0 or q1501_ever_worked == 2, age_retired = 996`

**R script:**

```{r harmo fin_w1}

# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$retired <- car::recode(COURAGE_fin_w1$q1504_reason, "c(9) = 1; c(1,2,3,4,5,6,7,8,10,11,12,87) = 0; c(NA) = 999")
COURAGE_ds_fin_w1$retired[which(COURAGE_fin_w1$q1503_work_now==1 & is.na(COURAGE_fin_w1$q1504_reason))] <- 0

# Continuous variable harmonization
COURAGE_ds_fin_w1$age_retired <- car::recode(COURAGE_fin_w1$q1505_stop_age, "-8 = 998; NA = 999")
COURAGE_ds_fin_w1$age_retired[which(COURAGE_ds_fin_w1$retired == 0 | COURAGE_fin_w1$q1501_ever_worked == 2)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_fin_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(COURAGE_ds_fin_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation fin_w1, echo=F}

AfterH <- table(COURAGE_ds_fin_w1$retired, useNA = "ifany")
X <- table(COURAGE_fin_w1$q1503_work_now,COURAGE_fin_w1$q1504_reason, useNA = "ifany")
BeforeH <- c(sum(X[,c("1","2","3","4","5","6","7","10","11","12","87")],X[1,length(X[1,])]),sum(X[,c("9")]),sum(X[3,length(X[3,])]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4,5,6,7,8,10,11,12->0","9->1","NA->999")
kable(C)
rm(COURAGE_fin_w1)

```



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `q1503_work_now` | `q1504_reason`|`q1505_stop_age`|`q1501_ever_worked`|
|-|-|-|-|-|
| **Label** | `Currently working?`| `Reason not working`|`age stop`|`Ever worked`|
| **Table name**  | `Courage_Poland_w1`| `Courage_Poland_w1`| `Courage_Poland_w1`| `Courage_Poland_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` |`1 = HOMEMAKER`<br/>`2 = COULDN'T FIND WORK`<br/>`3 = UNPAID/VOLUNTARY`<br/>`4 = STUDIES/TRAINING`<br/>`5 = HEALTH`<br/>`6 = CARE FAMILY`<br/>`7 = NO NEED`<br/>`8 = NOT PERMITTED`<br/>`9 = RETIRED/TOO OLD`<br/>`10 = LAID OFF`<br/>`11 = SEASONAL WORK`<br/>`12 = VACATION/SICK LEAVE`<br/>`87 = OTHER, SPECIFY`|`continuous`|`1 = YES WORKED`<br/>`2 = NEVER WORKED`|
| **Missings** | `NA`| `NA`|`-8 = DK`|`NA`|
| **Description** |  |  |  |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q1503_work_now','q1504_reason','q1505_stop_age','q1501_ever_worked'), missings = T)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- COURAGE_pol_w1$q1503_work_now
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1503_work_now')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q1503_work_now))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q1504_reason
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1504_reason')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q1504_reason))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q1505_stop_age
vbl_miss <- c(-8)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505_stop_age')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(COURAGE_pol_w1,!vbl %in% vbl_miss), aes(q1505_stop_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q1501_ever_worked
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1501_ever_worked')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q1501_ever_worked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504_reason == 9 into 1`
* `q1504_reason == 1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 12 or 87 or q1503_work_now == 1 into 0`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = q1505_stop_age`
* `-8 into 998`
* `if retired == 0 or q1501_ever_worked == 2, age_retired = 996`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$retired <- car::recode(COURAGE_pol_w1$q1504_reason, "c(9) = 1; c(1,2,3,4,5,6,7,8,10,11,12,87) = 0; c(NA) = 999")
COURAGE_ds_pol_w1$retired[which(COURAGE_pol_w1$q1503_work_now==1 & is.na(COURAGE_pol_w1$q1504_reason))] <- 0

# Continuous variable harmonization
COURAGE_ds_pol_w1$age_retired <- car::recode(COURAGE_pol_w1$q1505_stop_age, "-8 = 998; NA = 999")
COURAGE_ds_pol_w1$age_retired[which(COURAGE_ds_pol_w1$retired == 0 | COURAGE_pol_w1$q1501_ever_worked == 2)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_pol_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(COURAGE_ds_pol_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(COURAGE_ds_pol_w1$retired, useNA = "ifany")
X <- table(COURAGE_pol_w1$q1503_work_now,COURAGE_pol_w1$q1504_reason, useNA = "ifany")
BeforeH <- c(sum(X[,c("1","2","3","4","5","6","7","8","10","11","12","87")],X[1,length(X[1,])]),sum(X[,c("9")]),sum(X[3,length(X[3,])]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4,5,6,7,8,10,11,12->0","9->1","NA->999")
kable(C)
rm(COURAGE_pol_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q1503_work_now_s1` | `q1504_reason_s1`|`q1505_stop_age_s1`| `q1501_ever_worked_s1`|
|-|-|-|-|-|
| **Label** | `Currently working?`| `Reason not working`|`age stop`| `Ever worked`|
| **Table name**  | `Courage_Poland_w2`| `Courage_Poland_w2`| `Courage_Poland_w2`|`Courage_Poland_w2`||
| **Categories** | `1 = YES`<br/>`2 = NO` |`1 = HOMEMAKER`<br/>`2 = COULDN'T FIND WORK`<br/>`3 = UNPAID/VOLUNTARY`<br/>`4 = STUDIES/TRAINING`<br/>`5 = HEALTH`<br/>`6 = CARE FAMILY`<br/>`7 = NO NEED`<br/>`8 = NOT PERMITTED`<br/>`9 = RETIRED/TOO OLD`<br/>`10 = LAID OFF`<br/>`11 = SEASONAL WORK`<br/>`12 = VACATION/SICK LEAVE`<br/>`87 = OTHER, SPECIFY`|`continuous`|`1 = YES WORKED`<br/>`2 = NEVER WORKED`|
| **Missings** | `NA`| `NA`|`-8 = DK`|`NA`|
| **Description** |  |  |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',variables=list('q1503_work_now_s1','q1504_reason_s1','q1505_stop_age_s1','q1501_ever_worked_s1'), missings = T)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')

```

```{r local pol_w2, echo=F}

vbl <- COURAGE_pol_w2$q1503_work_now_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1503_work_now_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q1503_work_now_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$q1504_reason_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1504_reason_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q1504_reason_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$q1505_stop_age_s1
vbl_miss <- c(-8)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505_stop_age_s1')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(COURAGE_pol_w2,!vbl %in% vbl_miss), aes(q1505_stop_age_s1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$q1501_ever_worked_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1501_ever_worked_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(q1501_ever_worked_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504_reason == 9 into 1`
* `q1504_reason == 1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 12 or 87 or q1503_work_now == 1 into 0`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = q1505_stop_age`
* `-8 into 998`
* `if retired == 0 or q1501_ever_worked == 2, age_retired = 996`

**R script:**

```{r harmo pol_w2}

# Categorical variable harmonization
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$retired <- car::recode(COURAGE_pol_w2$q1504_reason_s1, "c(9) = 1; c(1,2,3,4,5,6,7,8,10,11,12,87) = 0; c(NA) = 999")
COURAGE_ds_pol_w2$retired[which(COURAGE_pol_w2$q1503_work_now_s1==1 & is.na(COURAGE_pol_w2$q1504_reason_s1))] <- 0

# Continuous variable harmonization
COURAGE_ds_pol_w2$age_retired <- car::recode(COURAGE_pol_w2$q1505_stop_age_s1, "-8 = 998; NA = 999")
COURAGE_ds_pol_w2$age_retired[which(COURAGE_ds_pol_w2$retired == 0 | COURAGE_pol_w2$q1501_ever_worked_s1 == 2)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- COURAGE_ds_pol_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_pol_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(COURAGE_ds_pol_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(COURAGE_ds_pol_w2$retired, useNA = "ifany")
X <- table(COURAGE_pol_w2$q1503_work_now_s1,COURAGE_pol_w2$q1504_reason_s1, useNA = "ifany")
BeforeH <- c(sum(X[,c("1","2","3","4","5","6","7","8","10","11","12","87")],X[1,length(X[1,])]),sum(X[,c("9")]),sum(X[3,length(X[3,])]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4,5,6,7,8,10,11,12->0","9->1","NA->999")
kable(C)
rm(COURAGE_pol_w1)

```



## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q1503_work_now` | `q1504_reason`|`q1505_stop_age`|`q1501_ever_worked`|
|-|-|-|-|-|
| **Label** | `Currently working?`| `Reason not working`|`age stop`|`Ever worked`|
| **Table name**  | `Courage_Spain_w1`| `Courage_Spain_w1`| `Courage_Spain_w1`| `Courage_Spain_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` |`1 = HOMEMAKER`<br/>`2 = COULDN'T FIND WORK`<br/>`3 = UNPAID/VOLUNTARY`<br/>`4 = STUDIES/TRAINING`<br/>`5 = HEALTH`<br/>`6 = CARE FAMILY`<br/>`7 = NO NEED`<br/>`8 = NOT PERMITTED`<br/>`9 = RETIRED/TOO OLD`<br/>`10 = LAID OFF`<br/>`11 = SEASONAL WORK`<br/>`12 = VACATION/SICK LEAVE`<br/>`87 = OTHER, SPECIFY`|`continuous`|`1 = YES WORKED`<br/>`2 = NEVER WORKED`|
| **Missings** | `NA`| `NA`|`-8 = DK`|`NA`|
| **Description** |  |  |  |  |

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q1503_work_now','q1504_reason','q1505_stop_age','q1501_ever_worked'), missings = T)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')

```

```{r local spain_w1, echo=F}

vbl <- COURAGE_spain_w1$q1503_work_now
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1503_work_now')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q1503_work_now))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q1504_reason
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1504_reason')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q1504_reason))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q1505_stop_age
vbl_miss <- c(-8)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505_stop_age')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(COURAGE_spain_w1,!vbl %in% vbl_miss), aes(q1505_stop_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q1501_ever_worked
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1501_ever_worked')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q1501_ever_worked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504_reason == 9 into 1`
* `q1504_reason == 1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 12 or 87 or q1503_work_now == 1 into 0`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = q1505_stop_age`
* `-8 into 998`
* `if retired == 0 or q1501_ever_worked == 2, age_retired = 996`

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$retired <- car::recode(COURAGE_spain_w1$q1504_reason, "c(9) = 1; c(1,2,3,4,5,6,7,8,10,11,12,87) = 0; c(NA) = 999")
COURAGE_ds_spain_w1$retired[which(COURAGE_spain_w1$q1503_work_now==1 & is.na(COURAGE_spain_w1$q1504_reason))] <- 0

# Continuous variable harmonization
COURAGE_ds_spain_w1$age_retired <- car::recode(COURAGE_spain_w1$q1505_stop_age, "-8 = 998; NA = 999")
COURAGE_ds_spain_w1$age_retired[which(COURAGE_ds_spain_w1$retired == 0 | COURAGE_spain_w1$q1501_ever_worked == 2)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_spain_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(COURAGE_ds_spain_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w1, echo=F}

AfterH <- table(COURAGE_ds_spain_w1$retired, useNA = "ifany")
X <- table(COURAGE_spain_w1$q1503_work_now,COURAGE_spain_w1$q1504_reason, useNA = "ifany")
BeforeH <- c(sum(X[,c("1","2","3","4","5","6","7","8","10","11","12","87")],X[1,length(X[1,])]),sum(X[,c("9")]),sum(X[3,length(X[3,])]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4,5,6,7,8,10,11,12->0","9->1","NA->999")
kable(C)
rm(COURAGE_spain_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q1503_work_now_s1` | `q1504_reason_s1`|`q1505_stop_age_s1`|`q1501_ever_worked_s1`|
|-|-|-|-|-|
| **Label** | `Currently working?`| `Reason not working`|`age stop`|`Ever worked`|
| **Table name**  | `Courage_Spain_w2_1`| `Courage_Spain_w2_1`| `Courage_Spain_w2_1`| `Courage_Spain_w2_1`|
| **Categories** | `1 = YES`<br/>`2 = NO` |`1 = HOMEMAKER`<br/>`2 = COULDN'T FIND WORK`<br/>`3 = UNPAID/VOLUNTARY`<br/>`4 = STUDIES/TRAINING`<br/>`5 = HEALTH`<br/>`6 = CARE FAMILY`<br/>`7 = NO NEED`<br/>`8 = NOT PERMITTED`<br/>`9 = RETIRED/TOO OLD`<br/>`10 = LAID OFF`<br/>`11 = SEASONAL WORK`<br/>`12 = VACATION/SICK LEAVE`<br/>`87 = OTHER, SPECIFY`|`continuous`|`1 = YES WORKED`<br/>`2 = NEVER WORKED`|
| **Missings** | `NA`| `NA`|`-8 = DK`|`NA`|
| **Description** |  |  |  |  |

```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q1503_work_now_s1','q1504_reason_s1','q1505_stop_age_s1','q1501_ever_worked_s1'), missings = T)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')

```

```{r local spain_w2, echo=F}

vbl <- COURAGE_spain_w2$q1503_work_now_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1503_work_now_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q1503_work_now_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$q1504_reason_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1504_reason_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q1504_reason_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$q1505_stop_age_s1
vbl_miss <- c(-8)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505_stop_age_s1')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(COURAGE_spain_w2,!vbl %in% vbl_miss), aes(q1505_stop_age_s1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$q1501_ever_worked_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q1501_ever_worked_s1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q1501_ever_worked_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504_reason == 9 into 1`
* `q1504_reason == 1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 12 or 87 or q1503_work_now == 1 into 0`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = q1505_stop_age`
* `-8 into 998`
* `if retired == 0 or q1501_ever_worked == 2, age_retired = 996`

**R script:**

```{r harmo spain_w2}

# Categorical variable harmonization
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$retired <- car::recode(COURAGE_spain_w2$q1504_reason_s1, "c(9) = 1; c(1,2,3,4,5,6,7,8,10,11,12,87) = 0; c(NA) = 999")
COURAGE_ds_spain_w2$retired[which(COURAGE_spain_w2$q1503_work_now_s1==1 & is.na(COURAGE_spain_w2$q1504_reason_s1))] <- 0

# Continuous variable harmonization
COURAGE_ds_spain_w2$age_retired <- car::recode(COURAGE_spain_w2$q1505_stop_age_s1, "-8 = 998; NA = 999")
COURAGE_ds_spain_w2$age_retired[which(COURAGE_ds_spain_w2$retired == 0 | COURAGE_spain_w2$q1501_ever_worked_s1 == 2)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript spain_w2, echo=F}

vbl <- COURAGE_ds_spain_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- COURAGE_ds_spain_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(COURAGE_ds_spain_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w2, echo=F,results='asis'}

AfterH <- table(COURAGE_ds_spain_w2$retired, useNA = "ifany")
X <- table(COURAGE_spain_w2$q1503_work_now_s1,COURAGE_spain_w2$q1504_reason_s1, useNA = "ifany")
BeforeH <- c(sum(X[,c("1","2","3","4","5","6","7","10","11","12","87")],X[1,length(X[1,])]),sum(X[,c("9")]),sum(X[3,length(X[3,])]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4,5,6,7,8,10,11,12->0","9->1","NA->999")
kable(C)
rm(COURAGE_pol_w1)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

lb.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, spain_w1 = COURAGE_ds_spain_w1)
lf.hds <- list(pol_w2 = COURAGE_ds_pol_w2, spain_w2 = COURAGE_ds_spain_w2)

for(name in names(lb.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  label(lb.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lb.hds[[name]][[3]] <- labelled(lb.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

l.hds <- c(lb.hds,lf.hds)
ln.hds <- c("fin_w1","pol_w1","pol_w2","spain_w1","spain_w2")

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[ln.hds[1]]][[2]]), length(l.hds[[ln.hds[2]]][[2]]) , length(l.hds[[ln.hds[3]]][[2]]), length(l.hds[[ln.hds[4]]][[2]]), length(l.hds[[ln.hds[5]]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Poland_W2", "Spain_W1", "Spain_W2")
kable(t.hds)

```



# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





