---
title: "Migration"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/migrationDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/migrationDS.R')
```


# Data process

## Finland

### Wave 1

#### Study-specific variable description

| **Name** | `q1020_always` | `q1022_previous` |
|-|-|-|
| **Label** | `Always lived here?`| `Lived before`|
| **Table name**  | `Courage_Finland_w1`| `Courage_Finland_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` | `2 = Other city in this state` <br/> `3 = Other rural in this state` <br/> `4 = Other city outside state but this country` <br/> `5 = Other rural outside state but same country` <br/> `Outside country` |
| **Missings** |`8 = DK` <br/> `9 = REFUSED`|`NA` |
| **Description** |  | |


```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q1020_always', 'q1022_previous'), missings = T)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')

```



```{r local fin_w1, echo=F}

vbl <- COURAGE_fin_w1$q1020_always
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q1020_always))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q1022_previous
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q1022_previous))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded as follows:

* `q1020_always = 2 and q1022_previous = 6, NA into 1`
* `q1020_always = 1,2 and q1022_previous = 2,3,4,5 into 0`
* `q1020_always = 8 into 998`
* `q1020_always = 9 into 997`
* `NA into 999`

**R script:**

```{r harmo fin_w1}

# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$migration <- NA
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always == 2 & COURAGE_fin_w1$q1022_previous == 6] <- 1
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always %in% 1:2 & COURAGE_fin_w1$q1022_previous %in% 2:5] <- 0
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always == 1 & is.na(COURAGE_fin_w1$q1022_previous)] <- 0
COURAGE_ds_fin_w1$migration[is.na(COURAGE_fin_w1$q1020_always) & is.na(COURAGE_fin_w1$q1022_previous)] <- 999
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always == 2 & is.na(COURAGE_fin_w1$q1022_previous)] <- 999
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always == 8] <- 998
COURAGE_ds_fin_w1$migration[COURAGE_fin_w1$q1020_always == 9] <- 997
COURAGE_ds_fin_w1$migration[is.na(COURAGE_fin_w1$q1020_always) & is.na(COURAGE_fin_w1$q1022_previous)] <- 999

```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation fin_w1, echo=F}

```



## Poland

### Wave 1


#### Study-specific variable description

| **Name** | `q1020_always` | `q1022_previous` |
|-|-|-|
| **Label** | `Always lived here?`| `Lived before`|
| **Table name**  | `Courage_Finland_w1`| `Courage_Finland_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` | `2 = Other city in this state` <br/> `3 = Other rural in this state` <br/> `4 = Other city outside state but this country` <br/> `5 = Other rural outside state but same country` <br/> `Outside country` |
| **Missings** |`8 = DK` <br/> `9 = REFUSED`|`NA` |
| **Description** |  | |


```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q1020_always', 'q1022_previous'), missings = T)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')

```



```{r local pol_w1, echo=F}

vbl <- COURAGE_pol_w1$q1020_always
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(COURAGE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q1020_always))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q1022_previous
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q1022_previous))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded as follows:

* `q1020_always = 2 and q1022_previous = 6, NA into 1`
* `q1020_always = 1,2 and q1022_previous = 2,3,4,5 into 0`
* `q1020_always = 8 into 998`
* `q1020_always = 9 into 997`
* `NA into 999`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$migration <- NA
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always == 2 & COURAGE_pol_w1$q1022_previous == 6] <- 1
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always %in% 1:2 & COURAGE_pol_w1$q1022_previous %in% 2:5] <- 0
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always == 1 & is.na(COURAGE_pol_w1$q1022_previous)] <- 0
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always == 2 & is.na(COURAGE_pol_w1$q1022_previous)] <- 999
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always == 8] <- 998
COURAGE_ds_pol_w1$migration[COURAGE_pol_w1$q1020_always == 9] <- 997
COURAGE_ds_pol_w1$migration[is.na(COURAGE_pol_w1$q1020_always) & is.na(COURAGE_pol_w1$q1022_previous)] <- 999

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation pol_w1, echo=F}

```




### Wave 2



Not found. 

## Spain

### Wave 1


#### Study-specific variable description

| **Name** | `q1020_always` | `q1022_previous` |
|-|-|-|
| **Label** | `Always lived here?`| `Lived before`|
| **Table name**  | `Courage_Finland_w1`| `Courage_Finland_w1`|
| **Categories** | `1 = YES`<br/>`2 = NO` | `2 = Other city in this state` <br/> `3 = Other rural in this state` <br/> `4 = Other city outside state but this country` <br/> `5 = Other rural outside state but same country` <br/> `Outside country` |
| **Missings** |`8 = DK` <br/> `9 = REFUSED`|`NA` |
| **Description** |  | |

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q1020_always', 'q1022_previous'), missings = T)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')

```



```{r local spain_w1, echo=F}

vbl <- COURAGE_spain_w1$q1020_always
vbl_miss <- c(-8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q1020_always))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q1022_previous
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q1022_previous))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `oral_problems` from the study-specific variable it has to be recoded as follows:

* `q1020_always = 2 and q1022_previous = 6, NA into 1`
* `q1020_always = 1,2 and q1022_previous = 2,3,4,5 into 0`
* `q1020_always = 8 into 998`
* `q1020_always = 9 into 997`
* `NA into 999`

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$migration <- NA
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always == 2 & COURAGE_spain_w1$q1022_previous == 6] <- 1
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always %in% 1:2 & COURAGE_spain_w1$q1022_previous %in% 2:5] <- 0
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always == 1 & is.na(COURAGE_spain_w1$q1022_previous)] <- 0
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always == 2 & is.na(COURAGE_spain_w1$q1022_previous)] <- 999
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always == 8] <- 998
COURAGE_ds_spain_w1$migration[COURAGE_spain_w1$q1020_always == 9] <- 997
COURAGE_ds_spain_w1$migration[is.na(COURAGE_spain_w1$q1020_always) & is.na(COURAGE_spain_w1$q1022_previous)] <- 999


```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation spain_w1, echo=F}

```




### Wave 2



Not found.



## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:







```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





