---
title: "Day of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/dbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/dbirthDS.R')
```

# Data process

## Finland

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Finland_w1` |
| **Description** |  |


```{r assign_fin, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_birth','Courage.Courage_Finland_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_fin_w1_birth <- opal.execute(o,'COURAGE_fin_w1_birth')
```
**R script:**

```{r pref1}
COURAGE_fin_w1_birth$dbirth <- as.numeric(format(COURAGE_fin_w1_birth$q1010_birth_date, '%d'))

```

```{r local_fin, echo=F}

vari <- COURAGE_fin_w1_birth$dbirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dbirth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_fin_w1_birth, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_birth$id)
COURAGE_ds_fin_w1$dbirth <- car::recode(COURAGE_fin_w1_birth$dbirth, "NA=999")
COURAGE_ds_fin_w1$dbirth <- labelled(COURAGE_ds_fin_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin, echo=F}
vari <- COURAGE_ds_fin_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_fin_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_fin, echo=F}
```





```{r importOPAL_fin, echo=F}

#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$dbirth <- car::recode(COURAGE_m_ds_fin_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```



## Poland

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Poland_w1` |
| **Description** |  |


```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_birth','Courage.Courage_Poland_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_pol_w1_birth <- opal.execute(o,'COURAGE_pol_w1_birth')
```
**R script:**

```{r prep1}
COURAGE_pol_w1_birth$dbirth <- as.numeric(format(COURAGE_pol_w1_birth$q1010_birth_date, '%d'))

```

```{r local_pol1, echo=F}

vari <- COURAGE_pol_w1_birth$dbirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dbirth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w1_birth, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_birth$id)
COURAGE_ds_pol_w1$dbirth <- car::recode(COURAGE_pol_w1_birth$dbirth, "NA=999")
COURAGE_ds_pol_w1$dbirth <- labelled(COURAGE_ds_pol_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}
vari <- COURAGE_ds_pol_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_pol1, echo=F}
```



```{r importOPAL_pol1, echo=F}

#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$dbirth <- car::recode(COURAGE_m_ds_pol_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Poland_w1` |
| **Description** |  |

```{r assign_pol2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_birth','Courage.Courage_Poland_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_pol_w1_birth <- opal.execute(o,'COURAGE_pol_w1_birth')


opal.assign.table.tibble(o, 'COURAGE_pol_w2_id','Courage.Courage_Poland_w2',
                         variables=list('q1001_cognitive_s1'), missings = TRUE)
COURAGE_pol_w2_id <- opal.execute(o,'COURAGE_pol_w2_id')

```
**R script:**

```{r prep2}
COURAGE_pol_w1_birth$dbirth <- as.numeric(format(COURAGE_pol_w1_birth$q1010_birth_date, '%d'))

```

```{r local_pol2, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], q1010_birth_date=suppressWarnings(as.numeric(new_2[,2])), dbirth=suppressWarnings(as.numeric(new_2[,3])))
  new_22
}

COURAGE_pol_w2_birth <- Add_indiv(old = COURAGE_pol_w1_birth, new = COURAGE_pol_w2_id)

vari <- COURAGE_pol_w2_birth$dbirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dbirth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w2_birth, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_pol2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_birth$id)
COURAGE_ds_pol_w2$dbirth <- car::recode(COURAGE_pol_w2_birth$dbirth, "NA=999")
COURAGE_ds_pol_w2$dbirth <- labelled(COURAGE_ds_pol_w2$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol2, echo=F}
vari <- COURAGE_ds_pol_w2$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w2, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_pol2, echo=F}

```



```{r importOPAL_pol2, echo=F}

#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$dbirth <- car::recode(COURAGE_m_ds_pol_w2$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```





## Spain

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Spain_w1` |
| **Description** |  |

```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')
```
**R script:**

```{r pres1}

# From study sources, the saved dates of birth for id's "724000884", "724003756" are wrong and unknown.
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724000884")] <- NA
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724003756")] <- NA
# From study sources, the saved year of birth for id "724004854" is wrong, being the correct 1932.
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724004854")] <- "1932-07-20"

COURAGE_spain_w1_birth$dbirth <- as.numeric(format(COURAGE_spain_w1_birth$q1010_birth_date, '%d'))

```

```{r local_spain1, echo=F}

vari <- COURAGE_spain_w1_birth$dbirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dbirth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w1_birth, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_birth$id)
COURAGE_ds_spain_w1$dbirth <- car::recode(COURAGE_spain_w1_birth$dbirth, "NA=999")
COURAGE_ds_spain_w1$dbirth <- labelled(COURAGE_ds_spain_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vari <- COURAGE_ds_spain_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_spain1, echo=F}
```



```{r importOPAL_spain1, echo=F}

#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$dbirth <- car::recode(COURAGE_m_ds_spain_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Spain_w1` |
| **Description** |  |


```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')

opal.assign.table.tibble(o, 'COURAGE_spain_w2_id','Courage.Courage_Spain_w2_1',
                         variables=list('q0002_hhid'), missings = TRUE)
COURAGE_spain_w2_id <- opal.execute(o,'COURAGE_spain_w2_id')
```
**R script:**

```{r pres2}

# From study sources, the saved dates of birth for id's "724000884", "724003756" are wrong and unknown.
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724000884")] <- NA
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724003756")] <- NA
# From study sources, the saved year of birth for id "724004854" is wrong, being the correct 1932.
COURAGE_spain_w1_birth$q1010_birth_date[which(COURAGE_spain_w1_birth$id=="724004854")] <- "1932-07-20"

COURAGE_spain_w1_birth$dbirth <- as.numeric(format(COURAGE_spain_w1_birth$q1010_birth_date, '%d'))

```

```{r local_spain2, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], q1010_birth_date=suppressWarnings(as.numeric(new_2[,2])), dbirth=suppressWarnings(as.numeric(new_2[,3])))
  new_22
}

COURAGE_spain_w2_birth <- Add_indiv(old = COURAGE_spain_w1_birth, new = COURAGE_spain_w2_id)

vari <- COURAGE_spain_w2_birth$dbirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dbirth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w2_birth, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_birth$id)
COURAGE_ds_spain_w2$dbirth <- car::recode(COURAGE_spain_w2_birth$dbirth, "NA=999")
COURAGE_ds_spain_w2$dbirth <- labelled(COURAGE_ds_spain_w2$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vari <- COURAGE_ds_spain_w2$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_spain2, echo=F}
```



```{r importOPAL_spain2, echo=F}

#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$dbirth <- car::recode(COURAGE_m_ds_spain_w2$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
