---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

```{r lab, echo=FALSE}
ds_label <- "Year of birth"
```



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Finnish

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Finland_w1` |
| **Description** |  |



```{r assign_fin, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_birth','Courage.Courage_Finland_w1', variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_fin_w1_birth <- opal.execute(o,'COURAGE_fin_w1_birth')
```

```{r local_fin, echo=F}
COURAGE_fin_w1_birth$ybirth <- as.numeric(format(COURAGE_fin_w1_birth$q1010_birth_date, '%Y'))

vari <- COURAGE_fin_w1_birth$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_fin_w1_birth, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

The values larger than 1993 are considered missing since the interview was in 2011 and the participants had to be 18 years old as youngest.


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `1994+ into 999`


**R script:**

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_birth$id)
COURAGE_ds_fin_w1$ybirth <- car::recode(COURAGE_fin_w1_birth$ybirth, "1994:hi=999; NA=999")
COURAGE_ds_fin_w1$ybirth <- labelled(COURAGE_ds_fin_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(COURAGE_ds_fin_w1$ybirth) <- ds_label
```

#### Statistics of the new harmonised variable
```{r descript_fin, echo=F}
vari <- COURAGE_ds_fin_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_fin_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(1915,1995)
```

#### Validation
```{r crosstabulation_fin, echo=F, results='asis'}
#number of 999:
sum(na.omit(COURAGE_fin_w1_birth$ybirth>1993))+sum(is.na(COURAGE_fin_w1_birth$ybirth))
```





```{r importOPAL_fin, echo=F}

#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$ybirth <- car::recode(COURAGE_m_ds_fin_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```



## Polish


### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Poland_w1` |
| **Description** |  |

```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_birth','Courage.Courage_Poland_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_pol_w1_birth <- opal.execute(o,'COURAGE_pol_w1_birth')
```

```{r local_pol1, echo=F}
COURAGE_pol_w1_birth$ybirth <- as.numeric(format(COURAGE_pol_w1_birth$q1010_birth_date, '%Y'))

vari <- COURAGE_pol_w1_birth$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w1_birth, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

The values larger than 1993 are considered missing since the interview was in 2011 and the participants had to be 18 years old as youngest.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_birth$id)
COURAGE_ds_pol_w1$ybirth <- car::recode(COURAGE_pol_w1_birth$ybirth, "NA=999")
COURAGE_ds_pol_w1$ybirth <- labelled(COURAGE_ds_pol_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(COURAGE_ds_pol_w1$ybirth) <- ds_label
```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}
vari <- COURAGE_ds_pol_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1913,1993)
```

#### Validation
```{r crosstabulation_pol1, echo=F}
```





```{r importOPAL_pol1, echo=F}

#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$ybirth <- car::recode(COURAGE_m_ds_pol_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Poland_w1` |
| **Description** |  |

```{r assign_pol2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_birth','Courage.Courage_Poland_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)

opal.assign.table.tibble(o, 'COURAGE_pol_w2_id','Courage.Courage_Poland_w2',
                         variables=list('q1001_cognitive_s1'), missings = TRUE)

COURAGE_pol_w1_birth <- opal.execute(o,'COURAGE_pol_w1_birth')
COURAGE_pol_w1_birth$ybirth <- as.numeric(format(COURAGE_pol_w1_birth$q1010_birth_date, '%Y'))

COURAGE_pol_w2_id <- opal.execute(o,'COURAGE_pol_w2_id')
```

```{r local_pol2, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], q1010_birth_date=suppressWarnings(as.numeric(new_2[,2])), ybirth=suppressWarnings(as.numeric(new_2[,3])))
  new_22
}

COURAGE_pol_w2_birth <- Add_indiv(old = COURAGE_pol_w1_birth, new = COURAGE_pol_w2_id)



vari <- COURAGE_pol_w2_birth$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w2_birth, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

The values larger than 1993 are considered missing since the interview was in 2011 and the participants had to be 18 years old as youngest.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_pol2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_birth$id)
COURAGE_ds_pol_w2$ybirth <- car::recode(COURAGE_pol_w2_birth$ybirth, "NA=999")
COURAGE_ds_pol_w2$ybirth <- labelled(COURAGE_ds_pol_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(COURAGE_ds_pol_w2$ybirth) <- ds_label

```

#### Statistics of the new harmonised variable
```{r descript_pol2, echo=F}
vari <- COURAGE_ds_pol_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1913,1993)
```

#### Validation
```{r crosstabulation_pol2, echo=F}

```





```{r importOPAL_pol2, echo=F}

#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$ybirth <- car::recode(COURAGE_m_ds_pol_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```





## Spain

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Spain_w1` |
| **Description** |  |

```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')
```

```{r local_spain1, echo=F}
COURAGE_spain_w1_birth$ybirth <- as.numeric(format(COURAGE_spain_w1_birth$q1010_birth_date, '%Y'))

vari <- COURAGE_spain_w1_birth$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w1_birth, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

The values larger than 1993 are considered missing since the interview was in 2011 and the participants had to be 18 years old as youngest.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `1994+ into 999`


**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_birth$id)
COURAGE_ds_spain_w1$ybirth <- car::recode(COURAGE_spain_w1_birth$ybirth, "1994:hi=999; NA=999")
COURAGE_ds_spain_w1$ybirth <- labelled(COURAGE_ds_spain_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(COURAGE_ds_spain_w1$ybirth) <- ds_label
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vari <- COURAGE_ds_spain_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(1900,1995)
```

#### Validation
```{r crosstabulation_spain1, echo=F, results='asis'}
#number of 999:
sum(na.omit(COURAGE_spain_w1_birth$ybirth>1993))+sum(is.na(COURAGE_spain_w1_birth$ybirth))
```





```{r importOPAL_spain1, echo=F}

#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$ybirth <- car::recode(COURAGE_m_ds_spain_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `q1010_birth_date` |
|----------|------------|
| **Label** | `birth date (day, month, year)` |
| **Table name** | `Courage_Spain_w1` |
| **Description** |  |

```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')

COURAGE_spain_w1_birth$ybirth <- as.numeric(format(COURAGE_spain_w1_birth$q1010_birth_date, '%Y'))

opal.assign.table.tibble(o, 'COURAGE_spain_w2_id','Courage.Courage_Spain_w2_1',
                         variables=list('q0002_hhid'), missings = TRUE)
COURAGE_spain_w2_id <- opal.execute(o,'COURAGE_spain_w2_id')
```

```{r local_spain2, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], q1010_birth_date=suppressWarnings(as.numeric(new_2[,2])), ybirth=suppressWarnings(as.numeric(new_2[,3])))
  new_22
}

COURAGE_spain_w2_birth <- Add_indiv(old = COURAGE_spain_w1_birth, new = COURAGE_spain_w2_id)


vari <- COURAGE_spain_w2_birth$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w2_birth, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

The values larger than 1993 are considered missing since the interview was in 2011 and the participants had to be 18 years old as youngest.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `1994+ into 999`


**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w1_birth$id)
COURAGE_ds_spain_w2$ybirth <- car::recode(COURAGE_spain_w1_birth$ybirth, "1994:hi=999; NA=999")
COURAGE_ds_spain_w2$ybirth <- labelled(COURAGE_ds_spain_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(COURAGE_ds_spain_w2$ybirth) <- ds_label
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vari <- COURAGE_ds_spain_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(1900,1995)
```

#### Validation
```{r crosstabulation_spain2, echo=F, results='asis'}
#number of 999:
sum(na.omit(COURAGE_spain_w1_birth$ybirth>1993))+sum(is.na(COURAGE_spain_w1_birth$ybirth))
```





```{r importOPAL_spain2, echo=F}

#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$ybirth <- car::recode(COURAGE_m_ds_spain_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
[Comments on the quality of the new harmonised variable.]



We assume the same subjects are being interviewed and therefore the variable 
is the same for both waves.


```{r save, echo=FALSE}
ybirth <- COURAGE_ds_spain_w1
save(ybirth, file = "../RData/spain_w1/ybirth.RData")
rm(ybirth)

ybirth <- COURAGE_ds_spain_w2
save(ybirth, file = "../RData/spain_w2/ybirth.RData")
rm(ybirth)

ybirth <- COURAGE_ds_pol_w1
save(ybirth, file = "../RData/pol_w1/ybirth.RData")
rm(ybirth)

ybirth <- COURAGE_ds_pol_w2
save(ybirth, file = "../RData/pol_w2/ybirth.RData")
rm(ybirth)

ybirth <- COURAGE_ds_fin_w1
save(ybirth, file = "../RData/fin_w1/ybirth.RData")
rm(ybirth)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
