---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Finnish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1 = NEVER MARRIED (AND NO COHABITING)`
    + `2 = CURRENTLY MARRIED`
    + `3 = COHABITING`
    + `4 = SEPARATED/DIVORCED`
    + `5 = WIDOWED`

* Description: 
```{r assign_fin,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_ms','Courage.Courage_Finland_w1',
                         variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local_fin,  echo=FALSE}
COURAGE_fin_w1_ms <- opal.execute(o,'COURAGE_fin_w1_ms')
vari <- COURAGE_fin_w1_ms$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_fin_w1_ms$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_fin_w1_ms, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NEVER MARRIED (AND NO COHABITING)" into 1`
* `keep "CURRENTLY MARRIED" into 2`
* `recode 3 "COHABITING" into 2`
* `recode 4 "SEPARATED/DIVORCED" into 3`
* `recode 5 "WIDOWED" into 4`
* `recode NA into 999`


**R script:**

```{r harmo_fin,   echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_ms$id)
COURAGE_ds_fin_w1$marital_status <- car::recode(COURAGE_fin_w1_ms$q1012_mar_stat, " 3=2; 4=3; 5=4; NA=999")
COURAGE_ds_fin_w1$marital_status <- labelled(COURAGE_ds_fin_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_fin,  echo=FALSE}
vari <- COURAGE_ds_fin_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin,  echo=FALSE}
BeforeH <- table(COURAGE_fin_w1_ms$q1012_mar_stat)
BeforeH <- c( BeforeH[1], sum(BeforeH[c(2, 3)]), BeforeH[4], BeforeH[5], sum(is.na(COURAGE_fin_w1_ms$q1012_mar_stat))) 
AfterH <- table(COURAGE_ds_fin_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "4->3", "5->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_fin,  echo=FALSE}
val_labels(COURAGE_ds_fin_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$marital_status <- car::recode(COURAGE_m_ds_fin_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```





## Polish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1 = NEVER MARRIED (AND NO COHABITING)`
    + `2 = CURRENTLY MARRIED`
    + `3 = COHABITING`
    + `4 = SEPARATED/DIVORCED`
    + `5 = WIDOWED`

* Description: 
```{r assign_pol1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_ms','Courage.Courage_Poland_w1',
                         variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local_pol1,  echo=FALSE}
COURAGE_pol_w1_ms <- opal.execute(o,'COURAGE_pol_w1_ms')
vari <- COURAGE_pol_w1_ms$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w1_ms$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_pol_w1_ms, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NEVER MARRIED (AND NO COHABITING)" into 1`
* `keep "CURRENTLY MARRIED" into 2`
* `recode 3 "COHABITING" into 2`
* `recode 4 "SEPARATED/DIVORCED" into 3`
* `recode 5 "WIDOWED" into 4`
* `recode NA into 999`


**R script:**

```{r harmo_pol1,   echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_ms$id)
COURAGE_ds_pol_w1$marital_status <- car::recode(COURAGE_pol_w1_ms$q1012_mar_stat, " 3=2; 4=3; 5=4; NA=999")
COURAGE_ds_pol_w1$marital_status <- labelled(COURAGE_ds_pol_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol1,  echo=FALSE}
vari <- COURAGE_ds_pol_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1,  echo=FALSE}
BeforeH <- table(COURAGE_pol_w1_ms$q1012_mar_stat)
BeforeH <- c( BeforeH[1], sum(BeforeH[c(2, 3)]), BeforeH[4], BeforeH[5])
AfterH <- table(COURAGE_ds_pol_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "4->3", "5->4")
kable(C)
```

 
 

 
```{r importOPAL_pol1,  echo=FALSE}
val_labels(COURAGE_ds_pol_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$marital_status <- car::recode(COURAGE_m_ds_pol_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

 

* Name: `q1012_mar_stat_s1`
* Label: `Marital status`
* Categories: 
    + `1 = NEVER MARRIED (AND NO COHABITING)`
    + `2 = CURRENTLY MARRIED`
    + `3 = COHABITING`
    + `4 = SEPARATED/DIVORCED`
    + `5 = WIDOWED`

* Description: 
```{r assign_pol2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_ms','Courage.Courage_Poland_w2',
                         variables=list('q1012_mar_stat_s1'), missings = TRUE)
```

```{r local_pol2,  echo=FALSE}
COURAGE_pol_w2_ms <- opal.execute(o,'COURAGE_pol_w2_ms')
vari <- COURAGE_pol_w2_ms$q1012_mar_stat_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_pol_w2_ms$q1012_mar_stat_s1, missing_values = NA)
ggplot(COURAGE_pol_w2_ms, aes(x=factor(q1012_mar_stat_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NEVER MARRIED (AND NO COHABITING)" into 1`
* `keep "CURRENTLY MARRIED" into 2`
* `recode 3 "COHABITING" into 2`
* `recode 4 "SEPARATED/DIVORCED" into 3`
* `recode 5 "WIDOWED" into 4`
* `recode NA into 999`

**R script:**

```{r harmo_pol2,   echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_ms$id)
COURAGE_ds_pol_w2$marital_status <- car::recode(COURAGE_pol_w2_ms$q1012_mar_stat_s1, " 3=2; 4=3; 5=4; NA=999")
COURAGE_ds_pol_w2$marital_status <- labelled(COURAGE_ds_pol_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol2,  echo=FALSE}
vari <- COURAGE_ds_pol_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2,  echo=FALSE}
BeforeH <- table(COURAGE_pol_w2_ms$q1012_mar_stat_s1)
BeforeH <- c( BeforeH[1], BeforeH[2], BeforeH[3], BeforeH[4], sum(is.na(COURAGE_pol_w2_ms$q1012_mar_stat_s1))) 
AfterH <- table(COURAGE_ds_pol_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "4->3", "5->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_pol2,  echo=FALSE}
val_labels(COURAGE_ds_pol_w2) <- NULL
opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$marital_status <- car::recode(COURAGE_m_ds_pol_w2$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```






## Spanish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q1012_mar_stat`
* Label: `Marital status`
* Categories: 
    + `1 = NEVER MARRIED (AND NO COHABITING)`
    + `2 = CURRENTLY MARRIED`
    + `3 = COHABITING`
    + `4 = SEPARATED/DIVORCED`
    + `5 = WIDOWED`

* Description: 
```{r assign_spain1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_ms','Courage.Courage_Spain_w1',
                         variables=list('q1012_mar_stat'), missings = TRUE)
```

```{r local_spain1,  echo=FALSE}
COURAGE_spain_w1_ms <- opal.execute(o,'COURAGE_spain_w1_ms')
vari <- COURAGE_spain_w1_ms$q1012_mar_stat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w1_ms$q1012_mar_stat, missing_values = NA)
ggplot(COURAGE_spain_w1_ms, aes(x=factor(q1012_mar_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NEVER MARRIED (AND NO COHABITING)" into 1`
* `keep "CURRENTLY MARRIED" into 2`
* `recode 3 "COHABITING" into 2`
* `recode 4 "SEPARATED/DIVORCED" into 3`
* `recode 5 "WIDOWED" into 4`
* `recode NA into 999`


**R script:**

```{r harmo_spain1,   echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_ms$id)
COURAGE_ds_spain_w1$marital_status <- car::recode(COURAGE_spain_w1_ms$q1012_mar_stat, " 3=2; 4=3; 5=4; NA=999")
COURAGE_ds_spain_w1$marital_status <- labelled(COURAGE_ds_spain_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain1,  echo=FALSE}
vari <- COURAGE_ds_spain_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1,  echo=FALSE}
BeforeH <- table(COURAGE_spain_w1_ms$q1012_mar_stat)
BeforeH <- c( BeforeH[1], sum(BeforeH[c(2, 3)]), BeforeH[4], BeforeH[5])
AfterH <- table(COURAGE_ds_spain_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "4->3", "5->4")
kable(C)
```

 
 

 
```{r importOPAL_spain1,  echo=FALSE}
val_labels(COURAGE_ds_spain_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$marital_status <- car::recode(COURAGE_m_ds_spain_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description

 

* Name: `q1012_mar_stat_s1`
* Label: `Marital status`
* Categories: 
    + `1 = NEVER MARRIED (AND NO COHABITING)`
    + `2 = CURRENTLY MARRIED`
    + `3 = COHABITING`
    + `4 = SEPARATED/DIVORCED`
    + `5 = WIDOWED`

* Description: 
```{r assign_spain2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_ms','Courage.Courage_Spain_w2_1',
                         variables=list('q1012_mar_stat_s1'), missings = TRUE)
```

```{r local_spain2,  echo=FALSE}
COURAGE_spain_w2_ms <- opal.execute(o,'COURAGE_spain_w2_ms')
vari <- COURAGE_spain_w2_ms$q1012_mar_stat_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = COURAGE_spain_w2_ms$q1012_mar_stat_s1, missing_values = NA)
ggplot(COURAGE_spain_w2_ms, aes(x=factor(q1012_mar_stat_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NEVER MARRIED (AND NO COHABITING)" into 1`
* `keep "CURRENTLY MARRIED" into 2`
* `recode 3 "COHABITING" into 2`
* `recode 4 "SEPARATED/DIVORCED" into 3`
* `recode 5 "WIDOWED" into 4`
* `recode NA into 999`


**R script:**

```{r harmo_spain2,   echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_ms$id)
COURAGE_ds_spain_w2$marital_status <- car::recode(COURAGE_spain_w2_ms$q1012_mar_stat_s1, " 3=2; 4=3; 5=4; NA=999")
COURAGE_ds_spain_w2$marital_status <- labelled(COURAGE_ds_spain_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain2,  echo=FALSE}
vari <- COURAGE_ds_spain_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2,  echo=FALSE}
BeforeH <- table(COURAGE_spain_w2_ms$q1012_mar_stat_s1)
BeforeH <- c( BeforeH[1], sum(BeforeH[c(2, 3)]), BeforeH[4], BeforeH[5], sum(is.na(COURAGE_spain_w2_ms$q1012_mar_stat_s1))) 
AfterH <- table(COURAGE_ds_spain_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "4->3", "5->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_spain2,  echo=FALSE}
val_labels(COURAGE_ds_spain_w2) <- NULL
opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$marital_status <- car::recode(COURAGE_m_ds_spain_w2$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation

No comments

```{r save, echo=FALSE}
marital_status <- COURAGE_ds_spain_w1
save(marital_status, file = "../RData/spain_w1/marital_status.RData")
rm(marital_status)

marital_status <- COURAGE_ds_spain_w2
save(marital_status, file = "../RData/spain_w2/marital_status.RData")
rm(marital_status)

marital_status <- COURAGE_ds_pol_w1
save(marital_status, file = "../RData/pol_w1/marital_status.RData")
rm(marital_status)

marital_status <- COURAGE_ds_pol_w2
save(marital_status, file = "../RData/pol_w2/marital_status.RData")
rm(marital_status)

marital_status <- COURAGE_ds_fin_w1
save(marital_status, file = "../RData/fin_w1/marital_status.RData")
rm(marital_status)
```


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```


