---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Finnish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q0409_education_01`
* Label: `Level of education`
* Categories: 
    + `0 = NO FORMAL EDUCATION`
    + `1 = LESS THAN PRIMARY SCHOOL`
    + `2 = PRIMARY SCHOOL COMPLETED`
    + `3 = SECONDARY SCHOOL COMPLETED`
    + `4 = HIGH SCHOOL (OR EQUIVALENT) COMPLETED`
    + `5 = COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED`
    + `6 = POST GRADUATE DEGREE COMPLETED`
* Missings: 
    + `8 = DK`

* Description:
```{r assign_fin, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_educ','Courage.Courage_Finland_w1',
                         variables=list('q0409_education_01'), missings = TRUE)
```

```{r local_fin, echo=FALSE}
COURAGE_fin_w1_educ <- opal.execute(o,'COURAGE_fin_w1_educ')
vari <- COURAGE_fin_w1_educ$q0409_education_01
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_fin_w1_educ$q0409_education_01, missing_values = c(8))
ggplot(COURAGE_fin_w1_educ, aes(x=factor(q0409_education_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NO FORMAL EDUCATION" into 0`
* `recode 1 "LESS THAN PRIMARY SCHOOL" into 0`
* `recode 2 "PRIMARY SCHOOL COMPLETED" into 1`
* `recode 3 "SECONDARY SCHOOL COMPLETED" into 2`
* `recode 4 "HIGH SCHOOL (OR EQUIVALENT) COMPLETED" into 2`
* `recode 5 "COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED" into 3`
* `recode 6 "POST GRADUATE DEGREE COMPLETED" into 3`
* `recode 8 "DK" into 998`

**R script:**

```{r harmo_fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_educ$id)
COURAGE_ds_fin_w1$education <- car::recode(COURAGE_fin_w1_educ$q0409_education_01, "1=0; 2=1; 3=2; 4=2; 5=3; 6=3; 8=998; NA=999")
COURAGE_ds_fin_w1$education <- labelled(COURAGE_ds_fin_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_fin, echo=FALSE}
vari <- COURAGE_ds_fin_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin, echo=FALSE}
BeforeH <- table(COURAGE_fin_w1_educ$q0409_education_01)
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3],sum(BeforeH[4:5]), sum(BeforeH[6:7]), sum(is.na(COURAGE_fin_w1_educ$q0409_education_01)))
AfterH <- table(COURAGE_ds_fin_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(0,1)->0", "2->1", "(3,4)->2", "(5,6)->3", "NA->999")
kable(C)
```


```{r importOPAL_fin, echo=FALSE}
val_labels(COURAGE_ds_fin_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$education <- car::recode(COURAGE_m_ds_fin_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```





## Polish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q0409_education_01`
* Label: `Level of education`
* Categories: 
    + `0 = NO FORMAL EDUCATION`
    + `1 = LESS THAN PRIMARY SCHOOL`
    + `2 = PRIMARY SCHOOL COMPLETED`
    + `3 = SECONDARY SCHOOL COMPLETED`
    + `4 = HIGH SCHOOL (OR EQUIVALENT) COMPLETED`
    + `5 = COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED`
    + `6 = POST GRADUATE DEGREE COMPLETED`
* Missings: 
    + `8 = DK`
* Description:
```{r assign_pol1, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_educ','Courage.Courage_Poland_w1',
                         variables=list('q0409_education_01'), missings = TRUE)
```

```{r local_pol1, echo=FALSE}
COURAGE_pol_w1_educ <- opal.execute(o,'COURAGE_pol_w1_educ')
vari <- COURAGE_pol_w1_educ$q0409_education_01
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w1_educ$q0409_education_01, missing_values = c(8))
ggplot(COURAGE_pol_w1_educ, aes(x=factor(q0409_education_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NO FORMAL EDUCATION" into 0`
* `recode 1 "LESS THAN PRIMARY SCHOOL" into 0`
* `recode 2 "PRIMARY SCHOOL COMPLETED" into 1`
* `recode 3 "SECONDARY SCHOOL COMPLETED" into 2`
* `recode 4 "HIGH SCHOOL (OR EQUIVALENT) COMPLETED" into 2`
* `recode 5 "COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED" into 3`
* `recode 6 "POST GRADUATE DEGREE COMPLETED" into 3`
* `recode 8 "DK" into 998`


**R script:**

```{r harmo_pol1, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_educ$id)
COURAGE_ds_pol_w1$education <- car::recode(COURAGE_pol_w1_educ$q0409_education_01, "1=0; 2=1; 3=2; 4=2; 5=3; 6=3; 8=998; NA=999")
COURAGE_ds_pol_w1$education <- labelled(COURAGE_ds_pol_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol1, echo=FALSE}
vari <- COURAGE_ds_pol_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1, echo=FALSE}
BeforeH <- table(COURAGE_pol_w1_educ$q0409_education_01)
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3],sum(BeforeH[4:5]), sum(BeforeH[6:7]))
AfterH <- table(COURAGE_ds_pol_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(0,1)->0", "2->1", "(3,4)->2", "(5,6)->3")
kable(C)
```


```{r importOPAL_pol1, echo=FALSE}
val_labels(COURAGE_ds_pol_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$education <- car::recode(COURAGE_m_ds_pol_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

 

* Name: `q1016_highest_s1`
* Label: `Highest level education`
* Categories: 
    + `0 = NO FORMAL EDUCATION`
    + `1 = LESS THAN PRIMARY SCHOOL`
    + `2 = PRIMARY SCHOOL COMPLETED`
    + `3 = SECONDARY SCHOOL COMPLETED`
    + `4 = HIGH SCHOOL (OR EQUIVALENT) COMPLETED`
    + `5 = COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED`
    + `6 = POST GRADUATE DEGREE COMPLETED`
* Missings: 
    + `-8 = DK`
* Description:
```{r assign_pol2, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_educ','Courage.Courage_Poland_w2',
                         variables=list('q1016_highest_s1'), missings = TRUE)
```

```{r local_pol2, echo=FALSE}
COURAGE_pol_w2_educ <- opal.execute(o,'COURAGE_pol_w2_educ')
vari <- COURAGE_pol_w2_educ$q1016_highest_s1
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_pol_w2_educ$q1016_highest_s1, missing_values = c(-8))
ggplot(COURAGE_pol_w2_educ, aes(x=factor(q1016_highest_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NO FORMAL EDUCATION" into 0`
* `recode 1 "LESS THAN PRIMARY SCHOOL" into 0`
* `recode 2 "PRIMARY SCHOOL COMPLETED" into 1`
* `recode 3 "SECONDARY SCHOOL COMPLETED" into 2`
* `recode 4 "HIGH SCHOOL (OR EQUIVALENT) COMPLETED" into 2`
* `recode 5 "COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED" into 3`
* `recode 6 "POST GRADUATE DEGREE COMPLETED" into 3`
* `recode -8 "DK" into 998`


**R script:**

```{r harmo_pol2, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_educ$id)
COURAGE_ds_pol_w2$education <- car::recode(COURAGE_pol_w2_educ$q1016_highest_s1, "1=0; 2=1; 3=2; 4=2; 5=3; 6=3; -8=998; NA=999")
COURAGE_ds_pol_w2$education <- labelled(COURAGE_ds_pol_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol2, echo=FALSE}
vari <- COURAGE_ds_pol_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2, echo=FALSE}
BeforeH <- table(COURAGE_pol_w2_educ$q1016_highest_s1)
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3],sum(BeforeH[4:5]), sum(BeforeH[6:7]), sum(is.na(COURAGE_pol_w2_educ$q1016_highest_s1)))
AfterH <- table(COURAGE_ds_pol_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(0,1)->0", "2->1", "(3,4)->2", "(5,6)->3", "NA->999")
kable(C)
```


```{r importOPAL_pol2, echo=FALSE}
val_labels(COURAGE_ds_pol_w2) <- NULL
opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$education <- car::recode(COURAGE_m_ds_pol_w2$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```






## Spanish population
### Wave 1 

#### Study-specific variable description

 

* Name: `q0409_education_01`
* Label: `Level of education`
* Categories: 
    + `0 = NO FORMAL EDUCATION`
    + `1 = LESS THAN PRIMARY SCHOOL`
    + `2 = PRIMARY SCHOOL COMPLETED`
    + `3 = SECONDARY SCHOOL COMPLETED`
    + `4 = HIGH SCHOOL (OR EQUIVALENT) COMPLETED`
    + `5 = COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED`
    + `6 = POST GRADUATE DEGREE COMPLETED`
* Missings: 
    + `8 = DK`
* Description:
```{r assign_spain1, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_educ','Courage.Courage_Spain_w1',
                         variables=list('q0409_education_01'), missings = TRUE)
```

```{r local_spain1, echo=FALSE}
COURAGE_spain_w1_educ <- opal.execute(o,'COURAGE_spain_w1_educ')
vari <- COURAGE_spain_w1_educ$q0409_education_01
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w1_educ$q0409_education_01, missing_values = c(8))
ggplot(COURAGE_spain_w1_educ, aes(x=factor(q0409_education_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NO FORMAL EDUCATION" into 0`
* `recode 1 "LESS THAN PRIMARY SCHOOL" into 0`
* `recode 2 "PRIMARY SCHOOL COMPLETED" into 1`
* `recode 3 "SECONDARY SCHOOL COMPLETED" into 2`
* `recode 4 "HIGH SCHOOL (OR EQUIVALENT) COMPLETED" into 2`
* `recode 5 "COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED" into 3`
* `recode 6 "POST GRADUATE DEGREE COMPLETED" into 3`
* `recode 8 "DK" into 998`


**R script:**

```{r harmo_spain1, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_educ$id)
COURAGE_ds_spain_w1$education <- car::recode(COURAGE_spain_w1_educ$q0409_education_01, "1=0; 2=1; 3=2; 4=2; 5=3; 6=3; 8=998; NA=999")
COURAGE_ds_spain_w1$education <- labelled(COURAGE_ds_spain_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain1, echo=FALSE}
vari <- COURAGE_ds_spain_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1, echo=FALSE}
BeforeH <- table(COURAGE_spain_w1_educ$q0409_education_01)
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3],sum(BeforeH[4:5]), sum(BeforeH[6:7]), BeforeH[8])
AfterH <- table(COURAGE_ds_spain_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(0,1)->0", "2->1", "(3,4)->2", "(5,6)->3", "8->998")
kable(C)
```


```{r importOPAL_spain1, echo=FALSE}
val_labels(COURAGE_ds_spain_w1) <- NULL
opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$education <- car::recode(COURAGE_m_ds_spain_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

 

* Name: `q1016_highest_s1`
* Label: `Highest level education`
* Categories: 
    + `0 = NO FORMAL EDUCATION`
    + `1 = LESS THAN PRIMARY SCHOOL`
    + `2 = PRIMARY SCHOOL COMPLETED`
    + `3 = SECONDARY SCHOOL COMPLETED`
    + `4 = HIGH SCHOOL (OR EQUIVALENT) COMPLETED`
    + `5 = COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED`
    + `6 = POST GRADUATE DEGREE COMPLETED`
    + `7 = Estudios universitarios completos de grado superior`
* Missings: 
    + `-8 = DK`

* Description:
```{r assign_spain2, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_educ','Courage.Courage_Spain_w2_1',
                         variables=list('q1016_highest_s1'), missings = TRUE)
```

```{r local_spain2, echo=FALSE}
COURAGE_spain_w2_educ <- opal.execute(o,'COURAGE_spain_w2_educ')
vari <- COURAGE_spain_w2_educ$q1016_highest_s1
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_spain_w2_educ$q1016_highest_s1, missing_values = c(-8))
ggplot(COURAGE_spain_w2_educ, aes(x=factor(q1016_highest_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "NO FORMAL EDUCATION" into 0`
* `recode 1 "LESS THAN PRIMARY SCHOOL" into 0`
* `recode 2 "PRIMARY SCHOOL COMPLETED" into 1`
* `recode 3 "SECONDARY SCHOOL COMPLETED" into 2`
* `recode 4 "HIGH SCHOOL (OR EQUIVALENT) COMPLETED" into 2`
* `recode 5 "COLLEGE/PREUNIVERSITY/UNIVERSITY COMPLETED" into 3`
* `recode 6 "POST GRADUATE DEGREE COMPLETED" into 3`
* `recode 7 "Estudios universitarios completos de grado superior" into 3`
* `recode -8 "DK" into 998`


**R script:**

```{r harmo_spain2, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_educ$id)
COURAGE_ds_spain_w2$education <- car::recode(COURAGE_spain_w2_educ$q1016_highest_s1, "1=0; 2=1; 3=2; 4=2; 5=3; 6=3;7=3; -8=998; NA=999")
COURAGE_ds_spain_w2$education <- labelled(COURAGE_ds_spain_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain2, echo=FALSE}
vari <- COURAGE_ds_spain_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2, echo=FALSE}
BeforeH <- table(COURAGE_spain_w2_educ$q1016_highest_s1)
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3],sum(BeforeH[4:5]), sum(BeforeH[6:8]), sum(is.na(COURAGE_spain_w2_educ$q1016_highest_s1)))
AfterH <- table(COURAGE_ds_spain_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(0,1)->0", "2->1", "(3,4)->2", "(5,6,7)->3", "NA->999")
kable(C)
```


```{r importOPAL_spain2, echo=FALSE}
val_labels(COURAGE_ds_spain_w2) <- NULL
opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$education <- car::recode(COURAGE_m_ds_spain_w2$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments


```{r save, echo=FALSE}
education <- COURAGE_ds_spain_w1
save(education, file = "../RData/spain_w1/education.RData")
rm(education)

education <- COURAGE_ds_spain_w2
save(education, file = "../RData/spain_w2/education.RData")
rm(education)

education <- COURAGE_ds_pol_w1
save(education, file = "../RData/pol_w1/education.RData")
rm(education)

education <- COURAGE_ds_pol_w2
save(education, file = "../RData/pol_w2/education.RData")
rm(education)

education <- COURAGE_ds_fin_w1
save(education, file = "../RData/fin_w1/education.RData")
rm(education)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```