---
title: "Stroke or myocardial infarction (heart attack) or angina"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd`
* Variable label: `Stroke or myocardial infarction (heart attack) or angina`
* Variable description: `stroke, myocardial infarction, heart attack or angina diagnosed by a doctor`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no, the participant has not been diagnosed by angina or stroke or myocardial infarction or heart attack
1        | yes, the participant has been diagnosed by angina or stroke or myocardial infarction or heart attack

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke or myocardial infarction (heart attack) or angina"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `h_angina` |`mi_ha`|`stroke`|
|-|-|-|-|
| **Label** | `History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  |`h_angina` |`mi_ha`|`stroke`| 
| **Categories** | `0 = no history of angina`<br/>`1 = history of angina` |`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Description** |  |  |  |

```{r assign w1, echo=F}

load(paste0(datafolder,"w1/h_angina.RData"))
TILDA_w1 <- tibble(id=h_angina$id)
TILDA_w1$h_angina <- h_angina$h_angina
rm(h_angina)
load(paste0(datafolder,"w1/mi_ha.RData"))
TILDA_w1$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w1/stroke.RData"))
TILDA_w1$stroke <- stroke$stroke
rm(stroke)

```

```{r local w1, echo=F}

vbl <- TILDA_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(TILDA_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(TILDA_w1)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$cvd <-rep(999,length(TILDA_w1$id))
TILDA_ds_w1$cvd[which(TILDA_w1$h_angina==0 & TILDA_w1$mi_ha==0 & TILDA_w1$stroke==0)] <- 0
TILDA_ds_w1$cvd[which(TILDA_w1$h_angina==1 | TILDA_w1$mi_ha==1 | TILDA_w1$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$cvd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cvd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(TILDA_ds_w1$cvd, useNA = "ifany")
X <- c(
  sum(TILDA_w1$h_angina==0 & TILDA_w1$mi_ha==0 & TILDA_w1$stroke==0,na.rm=T),
  sum(TILDA_w1$h_angina==1 | TILDA_w1$mi_ha==1 | TILDA_w1$stroke==1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



### Wave 2


Not found.




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$cvd <- labelled(TILDA_ds_w1$cvd, labels = cat_label)
label(TILDA_ds_w1$cvd) <- ds_label

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$cvd <- car::recode(TILDA_m_ds_w1$cvd, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$cvd)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(TILDA_ds_w1$cvd)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

# dbb <- merge(TILDA_m_ds_w1[,c("id","cvd")], TILDA_m_ds_w2[,c("id","cvd")], by="id", suffixes = c(".w1",".w2"), all=T)
# names(dbb) <- c("id", "w1", "w2")
# v.dbb <- paste(dbb[,2],dbb[,3],sep="")
# f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
# kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation

It contains information about angina, myocardial infarction and stroke.
It has been built from the harmonized single disease variables.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1)

for(index in seq_along(l.TILDA)){
  cvd <- l.TILDA[[index]]
  save(cvd, file = paste0(datafolder,names(l.TILDA)[index],"/cvd.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





