---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `ph201_05` |`ph213`|
|-|-|-|
| **Label** | `Has a doctor ever told you that you have any of the conditions on this card?: 5. Diabetes or high blood sugar`|`Approximately how old were you when you were first told by a doctor that you had diabetes or high blood sugar?`|
| **Table name**  | `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** | `1 = Diabetes or high blood sugar`<br/>`0 = NOT Diabetes or high blood sugar` |`49 = Less than 50`<br/>`59 = 50-59`<br/>`69 = 60-69`<br/>`70 = 70+`|
| **Missings** |  | `-98 = Don't Know`<br/>`-1 = Not applicable` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('ph201_05','ph213'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$ph201_05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph201_05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph213
kable(Categorical_summary(vbl, missing_values = c(-1,-98))[3], caption = names(TILDA_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-98))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph213))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `ph201_05 == 0  into 0`
* `ph201_05 == 1 into 1`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 and ph213 ==49, h_diabetes_age = 40`
* `if h_diabetes == 1 and ph213 ==59, h_diabetes_age = 50`
* `if h_diabetes == 1 and ph213 ==69, h_diabetes_age = 60`
* `if h_diabetes == 1 and ph213 ==70, h_diabetes_age = 70`
* `if h_diabetes == 1 and ph213 ==-98, h_diabetes_age = 998`
* `if h_diabetes == 0 (<==> ph213 == -1), h_diabetes_age = 996`
* `otherwise into 999`
**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$h_diabetes <-TILDA_w1$ph201_05

# Continuous variable harmonization
diabetes_age <- car::recode(TILDA_w1$ph213[TILDA_ds_w1$h_diabetes==1],"49=40;59=50;69=60;-98=998")
TILDA_ds_w1$h_diabetes_age <- car::recode(TILDA_ds_w1$h_diabetes, "0=996; 1=diabetes_age")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- TILDA_ds_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(x=factor(h_diabetes_age))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}
continuous <- c(sum(TILDA_ds_w1$h_diabetes_age==996),sum(TILDA_ds_w1$h_diabetes_age!=996))
dichotomous <- table(TILDA_ds_w1$h_diabetes, useNA = "ifany")
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->40:70 & 998")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$h_diabetes <- labelled(TILDA_ds_w1$h_diabetes, labels = cat_label)
label(TILDA_ds_w1$h_diabetes) <- ds_label
TILDA_ds_w1$h_diabetes_age <- labelled(TILDA_ds_w1$h_diabetes_age, labels = cont_label)
label(TILDA_ds_w1$h_diabetes_age) <- ds_label_age

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$h_diabetes <- car::recode(TILDA_m_ds_w1$h_diabetes, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$h_diabetes)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(TILDA_ds_w1$h_diabetes)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation

No comments

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1)

for(index in seq_along(l.TILDA)){
  h_diabetes <- l.TILDA[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.TILDA)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





