---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_hypertension`
* Variable label: `History of Hypertension`
* Variable description: `history of hypertension or high blood pressure`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT High blood pressure or hypertension 
1        | High blood pressure or hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_hypertension_age`
* Variable label: `Age first diagnosed hypertension`
* Variable description: `The age first told had hypertension diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Hypertension"
ds_label_age <- "Age first diagnosed hypertension"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `ph201_01` |`ph202`|
|-|-|-|
| **Label** | `Has a doctor ever told you that you have any of the conditions on this card?`|`Approximately how old were you when you were first told by a doctor that you .`|
| **Table name**  | `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** | `1 = High blood pressure or hypertension`<br/>`0 = NOT High blood pressure or hypertension` |`continuous`<br/>`29 = Less than 30`<br/>`80 = 80+`|
| **Missings** |  | `-98 = Don't Know`<br/>`-1 = Not applicable` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('ph201_01','ph202'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$ph201_01
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph201_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph202
kable(Continuous_summary(var = vbl, missing_values = c(-1,-98))[3], caption = names(TILDA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-1,-98))$summary, caption = "Summary")
ggplot(TILDA_w1, aes(ph202)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(25,85)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `ph201_01 == 0  into 0`
* `ph201_01 == 1 into 1`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = ph202`
* `if h_hypertension == 0 (<==> ph202 == -1), h_hypertension_age = 996`
* `otherwise into 999`
**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$h_hypertension <-TILDA_w1$ph201_01

# Continuous variable harmonization
hypertension_age <- car::recode(as.numeric(TILDA_w1$ph202[TILDA_ds_w1$h_hypertension==1]),"-98=998")
TILDA_ds_w1$h_hypertension_age <- car::recode(TILDA_ds_w1$h_hypertension, "0=996; 1=hypertension_age")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- TILDA_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,85)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(TILDA_ds_w1$h_hypertension_age==996),sum(TILDA_ds_w1$h_hypertension_age!=996))
dichotomous <- table(TILDA_ds_w1$h_hypertension, useNA = "ifany")
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missings) age values")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description



| **Name** | `ph201_01` |`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `ph201 - [Since our last interview] has a doctor ever told [you/Rname] that [you/`|`Age`|`Year of interview`|`Year of interview`|
| **Table name**  | `TILDA-AMF-v23`| `age`|`yintw`|`yintw`|
| **Categories** | `1 = High blood pressure or hypertension`<br/>`0 = NOT High blood pressure or hypertension` |`continuous`|`continuous`|`continuous`|
| **Missings** |  |  |  |  |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23',variables=list('ph201_01'), missings = T)
TILDA_w2 <- opal.execute(o,'TILDA_w2')
load(paste0(datafolder,"w2/age.RData"))
TILDA_w2 <- left_join(TILDA_w2,age,by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
TILDA_w2 <- left_join(TILDA_w2,yintw, by="id")
names(TILDA_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
TILDA_w2 <- left_join(TILDA_w2,yintw, by="id")
names(TILDA_w2)[5] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- TILDA_w2$ph201_01
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph201_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$age
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(TILDA_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(50,85)

vbl <- TILDA_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `ph201_01 (w1) == 0 and ph201_01 (w2) == 0 into 0`
* `ph201_01 (w1) == 1 or ph201_01 (w2) == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = age - (year of interview (w2) - year of interview (w1))/2`
* `if h_hypertension == 1 in w2 and 1 in w1, h_hypertension_age = age from w1`
* `if h_hypertension == 0 (<==> ph202 == -1), h_hypertension_age = 996`
* `otherwise into 999`
**R script:**

```{r harmo w2}

TILDA_w2 <- left_join(TILDA_w2,TILDA_ds_w1, by = "id")

# Categorical variable harmonization
TILDA_ds_w2 <- tibble(id=TILDA_w2$id)
TILDA_ds_w2$h_hypertension <- rep(999,length(TILDA_w2$id))
TILDA_ds_w2$h_hypertension[which(TILDA_w2$ph201_01==0 & (TILDA_w2$h_hypertension != 1 | is.na(TILDA_w2$h_hypertension)))] <- 0
TILDA_ds_w2$h_hypertension[which(TILDA_w2$ph201_01==1 | (!is.na(TILDA_w2$ph201_01) & TILDA_w2$h_hypertension == 1))] <- 1

# Continuous variable harmonization
TILDA_ds_w2$h_hypertension_age <- rep(999,length(TILDA_w2$id))
TILDA_ds_w2$h_hypertension_age[which(TILDA_ds_w2$h_hypertension == 1 & !is.na(TILDA_w2$h_hypertension_age) & !TILDA_w2$h_hypertension_age %in% miss_values_vector)] <- TILDA_w2$h_hypertension_age[which(TILDA_ds_w2$h_hypertension == 1 & !is.na(TILDA_w2$h_hypertension_age) & !TILDA_w2$h_hypertension_age %in% miss_values_vector)]
TILDA_ds_w2$h_hypertension_age[which(TILDA_ds_w2$h_hypertension == 1 & TILDA_w2$h_hypertension == 0)] <- TILDA_w2$age[which(TILDA_ds_w2$h_hypertension == 1 & TILDA_w2$h_hypertension == 0)] - (TILDA_w2$yintw_w2[which(TILDA_ds_w2$h_hypertension == 1 & TILDA_w2$h_hypertension == 0)] - TILDA_w2$yintw_w1[which(TILDA_ds_w2$h_hypertension == 1 & TILDA_w2$h_hypertension == 0)])/2

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- TILDA_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- TILDA_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,85)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(TILDA_ds_w2$h_hypertension)
X <- c(
  sum(TILDA_w2$ph201_01==0 & (TILDA_w2$h_hypertension != 1 | is.na(TILDA_w2$h_hypertension))),
  sum(TILDA_w2$ph201_01==1 | (!is.na(TILDA_w2$ph201_01) & TILDA_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0->0","1->1")
kable(C)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$h_hypertension <- labelled(TILDA_ds_w1$h_hypertension, labels = cat_label)
label(TILDA_ds_w1$h_hypertension) <- ds_label
TILDA_ds_w1$h_hypertension_age <- labelled(TILDA_ds_w1$h_hypertension_age, labels = cont_label)
label(TILDA_ds_w1$h_hypertension_age) <- ds_label_age
TILDA_ds_w2$h_hypertension <- labelled(TILDA_ds_w2$h_hypertension, labels = cat_label)
label(TILDA_ds_w2$h_hypertension) <- ds_label
TILDA_ds_w2$h_hypertension_age <- labelled(TILDA_ds_w2$h_hypertension_age, labels = cont_label)
label(TILDA_ds_w2$h_hypertension_age) <- ds_label_age

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$h_hypertension <- car::recode(TILDA_m_ds_w1$h_hypertension, "miss_values_vector=NA")
TILDA_m_ds_w2 <- TILDA_ds_w1
TILDA_m_ds_w2$h_hypertension <- car::recode(TILDA_m_ds_w2$h_hypertension, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$h_hypertension)[[1]][,c(1:2,4)]
tt[4] <- frq(TILDA_ds_w2$h_hypertension)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(TILDA_ds_w1$h_hypertension), length(TILDA_ds_w2$h_hypertension)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(TILDA_m_ds_w1[,c("id","h_hypertension")], TILDA_m_ds_w2[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation

* To compute age of diagnostic in the second wave we use the harmonized variable age, which is identical with the study-specific variable age. We have to note that in this variable, the individuals with ages less than 52 and greater or equal than 82 are collapsed to 51 and 82 years old respectively.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1, w2 = TILDA_ds_w2)

for(index in seq_along(l.TILDA)){
  h_hypertension <- l.TILDA[[index]]
  save(h_hypertension, file = paste0(datafolder,names(l.TILDA)[index],"/h_hypertension.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





