---
title: "Angina"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_angina`
* Variable label: `History of angina`
* Variable description: `history of angina`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no history of angina
1        | history of angina

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_angina_age`
* Variable label: `Age first diagnosed angina`
* Variable description: `The age first told had angina diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of angina"
ds_label_age <- "Age first diagnosed angina"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `ph201_02` |`ph203`|
|-|-|-|
| **Label** | `Has a doctor ever told you that you have any of the conditions on this card?`|`Approximately how old were you when you were first told by a doctor that you ...`|
| **Table name**  | `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** | `1 =  Angina`<br/>`0 = NOT Angina` |`1 = Less than 50`<br/>`2 = 50-54`<br/>`3 = 55-59`<br/>`4 = 60-64`<br/>`5 = 65-69`<br/>`6 = 70+`|
| **Missings** |  | `-98 = Don't Know`<br/>`-99 = Refused`<br/>`-1 = Not applicable` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('ph201_02','ph203'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$ph201_02
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph201_02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph203
kable(Categorical_summary(vbl, missing_values = c(-1,-98,-99))[3], caption = names(TILDA_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-98,-99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph203))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_angina` from the study-specific variable it has to be recoded as follows:

* `ph201_02 == 0  into 0`
* `ph201_02 == 1 into 1`

To compute `h_angina_age` from the study-specific variable it has to be recoded as follows:

* `if h_angina == 1 and ph203 ==1, h_angina_age = 40`
* `if h_angina == 1 and ph203 ==2, h_angina_age = 50`
* `if h_angina == 1 and ph203 ==3, h_angina_age = 55`
* `if h_angina == 1 and ph203 ==4, h_angina_age = 60`
* `if h_angina == 1 and ph203 ==5, h_angina_age = 65`
* `if h_angina == 1 and ph203 ==6, h_angina_age = 70`
* `if h_angina == 1 and ph203 ==-98, h_angina_age = 998`
* `if h_angina == 1 and ph203 ==-99, h_angina_age = 997`
* `if h_angina == 0 (<==> ph203 == -1), h_angina_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$h_angina <-TILDA_w1$ph201_02

# Continuous variable harmonization
angina_age <- car::recode(TILDA_w1$ph203[TILDA_ds_w1$h_angina==1],"1=40;2=50;3=55;4=60;5=65;6=70;-98=998;-99=997")
TILDA_ds_w1$h_angina_age <- car::recode(TILDA_ds_w1$h_angina, "0=996; 1=angina_age")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- TILDA_ds_w1$h_angina_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(x=factor(h_angina_age))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(TILDA_ds_w1$h_angina_age==996),sum(TILDA_ds_w1$h_angina_age!=996))
dichotomous <- table(TILDA_ds_w1$h_angina, useNA = "ifany")
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missings) age values")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$h_angina <- labelled(TILDA_ds_w1$h_angina, labels = cat_label)
label(TILDA_ds_w1$h_angina) <- ds_label
TILDA_ds_w1$h_angina_age <- labelled(TILDA_ds_w1$h_angina_age, labels = cont_label)
label(TILDA_ds_w1$h_angina_age) <- ds_label_age

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$h_angina <- car::recode(TILDA_m_ds_w1$h_angina, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$h_angina)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(TILDA_ds_w1$h_angina)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

# dbb <- merge(TILDA_m_ds_w1[,c("id","h_angina")], TILDA_m_ds_w2[,c("id","h_angina")], by="id", suffixes = c(".w1",".w2"), all=T)
# names(dbb) <- c("id", "w1", "w2")
# v.dbb <- paste(dbb[,2],dbb[,3],sep="")
# f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
# kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation

No comments

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1)

for(index in seq_along(l.TILDA)){
  h_angina <- l.TILDA[[index]]
  save(h_angina, file = paste0(datafolder,names(l.TILDA)[index],"/h_angina.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





