---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```


# Data process

## Finland

### Wave 1 


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_id','Health2000-2011.Date_of_interview_wave1',
                         variables=list('dinterview'), missings = TRUE)
Health20002011_w1_id <- opal.execute(o,'Health20002011_w1_id')
```

#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_id$id)
Health20002011_ds_w1$living_status <- 0

```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```





### Wave 2 


| **Name** |`dinterview`|
|-|-|
| **Label** |  |
| **Table name** |`Date_of_interview_wave2`|
| **Type of variable** |`date`|
| **Description** |  |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1_id','Health2000-2011.Date_of_interview_wave1',
                         variables=list('dinterview'), missings = TRUE)
Health20002011_w1_id <- opal.execute(o,'Health20002011_w1_id')

opal.assign.table.tibble(o, 'Health20002011_w2_dinter','Health2000-2011.Date_of_interview_wave2',
                         variables=list('dinterview'), missings = TRUE)
Health20002011_w2_dinter <- opal.execute(o,'Health20002011_w2_dinter')


Health20002011_w2_ls <- full_join(x = Health20002011_w1_id, y = Health20002011_w2_dinter, by='id', suffix=c(".w1",""))
```


```{r local w2, echo=F}
vari <- Health20002011_w2_ls$dinterview
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "dinterview")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2_ls, aes(dinterview)) + geom_histogram(stat="count", fill="steelblue") + xlab("Date of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonize variable is going to be derived as follows: 

* `individuals that have date of interview in wave 2 as 0`
* `individuals that dont't have date of interview in wave 2 as 2`

**R script:**

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_ls$id)
Health20002011_ds_w2$living_status <- 0
Health20002011_ds_w2$living_status[is.na(Health20002011_w2_ls$dinterview)] <- 2

```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```





#### Validation
```{r crosstabulation2, echo=FALSE}
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation
We don't have death information, therefore the only values that appear are 0 (alive) and 2 (dropout). 


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
