---
title: "Suicidal Ideation last month"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/suicidal_ideation_lmDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/suicidal_ideation_lmDS.R')
```


# Data process

## Finland

### Wave 1 

Not found. 

### Wave 2 

#### Study-specific variable description

| **Name** | `T11_KYS3_K1023`| 
|-|-|
| **Label** | `Thoughts of ending your life`| 
| **Table name** | `t11_athlos_2017_02_27` | 
| **Categories** | `1 = Not at all` <br/> `2 = Alittle` <br/> `3 = Quite a bit` <br/> `4 = Extremely` | 
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_si_lm','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('T11_KYS3_K1023'), missings = TRUE)
Health20002011_si_lm <- opal.execute(o,'Health20002011_si_lm')
```

```{r local2, echo=FALSE}
vbl <- Health20002011_si_lm[[2]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_si_lm)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_si_lm, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `T11_KYS3_K1023 = 1` into `0`
* `T11_KYS3_K1023 = 2,3,4` into `1`
* `T11_KYS3_K1023 = NA` into `999`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_si_lm$id)
Health20002011_ds_w2$suicidal_ideation_lm <- car::recode(Health20002011_si_lm$T11_KYS3_K1023, "1=0; 2=1; 3=1; 4=1; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$suicidal_ideation_lm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(suicidal_ideation_lm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Suicidal Ideation last month") + ylab("Frequency")
```

#### Validation

```{r importOPAL2, echo=FALSE}
suicidal_ideation_lm <- Health20002011_ds_w2
save(suicidal_ideation_lm, file = "../RData/w2/suicidal_ideation_lm.RData")
rm(suicidal_ideation_lm)
```


# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
