---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightDS.R')
```

# Data process





## SHARE

### Wave 1 

#### Study-specific variable description


| **Name** | `ph012_` |
|----------|------------|
| **Label** | `weight of respondent` |
| **Table name** | `sharew1_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_weig','SHARE.sharew1_rel2-6-0_ph',
                         variables=list('ph012_'), missings = TRUE)
```

```{r local1, echo=F}
SHARE_w1_weig <- opal.execute(o,'SHARE_w1_weig')
vari <- SHARE_w1_weig$ph012_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w1_weig, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,220)
```

The values lower than 30 are going to be consider as mistakes and they are going to be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_weig$id)
SHARE_ds_w1$weight <- car::recode(SHARE_w1_weig$ph012_, "NA=999; -2=997; -1=998; 1:10=999")
SHARE_ds_w1$weight <- labelled(SHARE_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$weight
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "weight")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(30,200)
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- c(sum(na.omit(SHARE_w1_weig$ph012_)==-1), 
             sum(na.omit(SHARE_w1_weig$ph012_==-2)),
             sum( 
               sum(is.na(SHARE_w1_weig$ph012_)),
               sum(0<na.omit(SHARE_w1_weig$ph012_) & na.omit(SHARE_w1_weig$ph012_<11))))
AfterH <- c(sum(SHARE_ds_w1$weight==998), sum(SHARE_ds_w1$weight==997), sum(SHARE_ds_w1$weight==999))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("-1->997","-2->997", "(NA,lo:10)->999")
kable(C)
```



### Wave 2 

#### Study-specific variable description


| **Name** | `ph012_` |
|----------|------------|
| **Label** | `weight of respondent` |
| **Table name** | `sharew2_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_weig','SHARE.sharew2_rel2-6-0_ph',
                         variables=list('ph012_'), missings = TRUE)
```

```{r local2, echo=F}
SHARE_w2_weig <- opal.execute(o,'SHARE_w2_weig')
vari <- SHARE_w2_weig$ph012_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w2_weig, aes(ph012_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% c(vbl_miss,-3,11111111))) + xlab("Weight") + ylab("Frequency")

```

There is a value -3 that is going to be consider as a mistake and it will be recoded as 999. There are also values from 1 to 10 that are going to be consider as other mistakes and they will be recoded as 999. Finally, there is a value 11111111 that is going to be considered as a mistake and it will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_weig$id)
SHARE_ds_w2$weight <- car::recode(SHARE_w2_weig$ph012_, "NA=999; -3=999; 1:10=999; 11111111=999; -2=997; -1=998")
SHARE_ds_w2$weight <- labelled(SHARE_ds_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$weight
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "weight")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(weight)) + geom_bar(stat="count", fill="steelblue", width = 0.4) + xlab("weight") + ylab("Frequency") +  xlim(25,200)
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- c(sum(na.omit(SHARE_w2_weig$ph012_)==-1), 
             sum(na.omit(SHARE_w2_weig$ph012_==-2)),
             sum( 
               sum(is.na(SHARE_w2_weig$ph012_)),
               sum(0<na.omit(SHARE_w2_weig$ph012_) & na.omit(SHARE_w2_weig$ph012_<11)), sum(na.omit(SHARE_w2_weig$ph012_==11111111)), sum(na.omit(SHARE_w2_weig$ph012_==-3))))
AfterH <- c(sum(SHARE_ds_w2$weight==998), sum(SHARE_ds_w2$weight==997), sum(SHARE_ds_w2$weight==999))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("-1->997","-2->997", "(NA,lo:10,-3,111111)->999")
kable(C)
```




### Wave 3 

There is no variable.



### Wave 4 

#### Study-specific variable description


| **Name** | `ph012_` |
|----------|------------|
| **Label** | `weight of respondent` |
| **Table name** | `sharew4_rel1-1-1_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_weig','SHARE.sharew4_rel1-1-1_ph',
                         variables=list('ph012_'), missings = TRUE)
```

```{r local4, echo=F}
SHARE_w4_weig <- opal.execute(o,'SHARE_w4_weig')
vari <- SHARE_w4_weig$ph012_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w4_weig, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,220)
```

There are values from 0 to 18 that are going to be consider as a mistake and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_weig$id)
SHARE_ds_w4$weight <- car::recode(SHARE_w4_weig$ph012_, "NA=999; -2=997; -1=998; 0:18=999")
SHARE_ds_w4$weight <- labelled(SHARE_ds_w4$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$weight
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "weight")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(30,220)
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- c(sum(na.omit(SHARE_w4_weig$ph012_)==-1), 
             sum(na.omit(SHARE_w4_weig$ph012_==-2)),
             sum( 
               sum(is.na(SHARE_w4_weig$ph012_)),
               sum(0<na.omit(SHARE_w4_weig$ph012_) & na.omit(SHARE_w4_weig$ph012_<19))))
AfterH <- c(sum(SHARE_ds_w4$weight==998), sum(SHARE_ds_w4$weight==997), sum(SHARE_ds_w4$weight==999))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("-1->997","-2->997", "(NA,lo:18)->999")
kable(C)
```




### Wave 5 

#### Study-specific variable description


| **Name** | `ph012_` |
|----------|------------|
| **Label** | `weight of respondent` |
| **Table name** | `sharew5_rel1-0-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_weig','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('ph012_'), missings = TRUE)
```

```{r local5, echo=F}
SHARE_w5_weig <- opal.execute(o,'SHARE_w5_weig')
vari <- SHARE_w5_weig$ph012_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w5_weig, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,220)
```

There are values from 0 to 18 that are going to be consider as a mistake and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_weig$id)
SHARE_ds_w5$weight <- car::recode(SHARE_w5_weig$ph012_, "NA=999; -2=997; -1=998; 0:18=999")
SHARE_ds_w5$weight <- labelled(SHARE_ds_w5$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$weight
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "weight")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(30,220)
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- c(sum(na.omit(SHARE_w5_weig$ph012_)==-1), 
             sum(na.omit(SHARE_w5_weig$ph012_==-2)),
             sum( 
               sum(is.na(SHARE_w5_weig$ph012_)),
               sum(0<=na.omit(SHARE_w5_weig$ph012_) & na.omit(SHARE_w5_weig$ph012_<19))))
AfterH <- c(sum(SHARE_ds_w5$weight==998), sum(SHARE_ds_w5$weight==997), sum(SHARE_ds_w5$weight==999))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("-1->997","-2->997", "(NA,lo:18)->999")
kable(C)
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[2,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
Self reported weight.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

