---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/heightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/heightDS.R')
```



<!-- ########################################################## --> 

# Data process




## SHARE

### Wave 1 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew1_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_heig','SHARE.sharew1_rel2-6-0_ph', variables=list('ph013_'), missings = TRUE)
SHARE_w1_heig <- opal.execute(o,'SHARE_w1_heig')
```

```{r local1, echo=F}
vari <- SHARE_w1_heig$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w1_heig, aes(ph013_)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_heig$id)
SHARE_ds_w1$height <- car::recode(SHARE_w1_heig$ph013_, "NA=999; -2=997; -1=998")
SHARE_ds_w1$height <- labelled(SHARE_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "height")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}
```








### Wave 2 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew2_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_heig','SHARE.sharew2_rel2-6-0_ph',variables=list('ph013_'), missings = TRUE)
SHARE_w2_heig <- opal.execute(o,'SHARE_w2_heig')
```

```{r local2, echo=F}
vari <- SHARE_w2_heig$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w2_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:


Values between 1 and 2 are assumed to be measured in meters.
Values between 10 and 20 are assumed to be measured in decimeters.

Other values lower than 60 are going to be considered as mistakes and they will be recoded as 999.


* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo2}



SHARE_w2_heig$height <- SHARE_w2_heig$ph013_

SHARE_w2_heig$height[which(SHARE_w2_heig$ph013_>=1 & SHARE_w2_heig$ph013_<2)] <- SHARE_w2_heig$ph013_[which(SHARE_w2_heig$ph013_>=1 & SHARE_w2_heig$ph013_<2)]*100

SHARE_w2_heig$height[which(SHARE_w2_heig$ph013_>=10 & SHARE_w2_heig$ph013_<20)] <- SHARE_w2_heig$ph013_[which(SHARE_w2_heig$ph013_>=10 & SHARE_w2_heig$ph013_<20)]*10



SHARE_ds_w2 <- tibble(id=SHARE_w2_heig$id)


SHARE_ds_w2$height <- car::recode(SHARE_w2_heig$height, "NA=999; -2=997; -1=998; 0:60=999")
SHARE_ds_w2$height <- labelled(SHARE_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "height")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(height)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency") 

```

#### Validation
```{r crosstabulation2, echo=F}
```






### Wave 3 

There is no variable.



### Wave 4 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew4_rel1-1-1_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_heig','SHARE.sharew4_rel1-1-1_ph', variables=list('ph013_'), missings = TRUE)
SHARE_w4_heig <- opal.execute(o,'SHARE_w4_heig')
```

```{r local4, echo=F}
vari <- SHARE_w4_heig$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w4_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

Values between 1 and 2 are assumed to be measured in meters.
Values between 10 and 20 are assumed to be measured in decimeters.

Other values lower than 60 are going to be considered as mistakes and they will be recoded as 999.

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo4}

SHARE_w4_heig$height <- SHARE_w4_heig$ph013_

SHARE_w4_heig$height[which(SHARE_w4_heig$ph013_>=1 & SHARE_w4_heig$ph013_<2)] <- SHARE_w4_heig$ph013_[which(SHARE_w4_heig$ph013_>=1 & SHARE_w4_heig$ph013_<2)]*100

SHARE_w4_heig$height[which(SHARE_w4_heig$ph013_>=10 & SHARE_w4_heig$ph013_<20)] <- SHARE_w4_heig$ph013_[which(SHARE_w4_heig$ph013_>=10 & SHARE_w4_heig$ph013_<20)]*10


SHARE_ds_w4 <- tibble(id=SHARE_w4_heig$id)
SHARE_ds_w4$height <- car::recode(SHARE_w4_heig$height, "NA=999; -2=997; -1=998; 0:59=999")
SHARE_ds_w4$height <- labelled(SHARE_ds_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "height")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(height)) + geom_bar(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency")

```

#### Validation
```{r crosstabulation4, echo=F}
kable(SHARE_w4_heig[which(SHARE_w4_heig$ph013_<101 & SHARE_w4_heig$ph013_>=60),],align = 'c',caption = 'There are unusual values that are lower than 100.')
```






### Wave 5 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew5_rel1-0-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_heig','SHARE.sharew5_rel1-0-0_ph',variables=list('ph013_'), missings = TRUE)
SHARE_w5_heig <- opal.execute(o,'SHARE_w5_heig')
```

```{r local5, echo=F}
vari <- SHARE_w5_heig$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w5_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```



#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

Values between 1 and 2 are assumed to be measured in meters.
Values between 10 and 20 are assumed to be measured in decimeters.

Other values lower than 60 are going to be considered as mistakes and they will be recoded as 999.

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo5}


SHARE_w5_heig$height <- SHARE_w5_heig$ph013_

SHARE_w5_heig$height[which(SHARE_w5_heig$ph013_>=1 & SHARE_w5_heig$ph013_<2)] <- SHARE_w5_heig$ph013_[which(SHARE_w5_heig$ph013_>=1 & SHARE_w5_heig$ph013_<2)]*100

SHARE_w5_heig$height[which(SHARE_w5_heig$ph013_>=10 & SHARE_w5_heig$ph013_<20)] <- SHARE_w5_heig$ph013_[which(SHARE_w5_heig$ph013_>=10 & SHARE_w5_heig$ph013_<20)]*10


SHARE_ds_w5 <- tibble(id=SHARE_w5_heig$id)
SHARE_ds_w5$height <- car::recode(SHARE_w5_heig$ph013_, "NA=999; -2=997; -1=998; 0:59=999")
SHARE_ds_w5$height <- labelled(SHARE_ds_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "height")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(height)) + geom_bar(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
kable(SHARE_w5_heig[which(SHARE_w5_heig$ph013_<100 & SHARE_w5_heig$ph013_>59),],align = 'c',caption = 'There are unusual values that are lower than 100: ')
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
This variable was a self-reported measure.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

