---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `Height`
* Variable label: `Height of the participant`
* Variable description: `Anthropomeric measure for height should be measured in centimeters`
* Domain: `Physical measures `
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process




## SHARE

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

### Wave 1 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew1_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_heig','SHARE.sharew1_rel2-6-0_ph',
                         variables=list('ph013_'), missings = TRUE)
```

```{r local1, echo=F}
SHARE_w1_heig <- opal.execute(o,'SHARE_w1_heig')
vari <- SHARE_w1_heig$ph013_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w1_heig, aes(ph013_)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_heig$id)
SHARE_ds_w1$height <- car::recode(SHARE_w1_heig$ph013_, "NA=999; -2=997; -1=998")
SHARE_ds_w1$height <- labelled(SHARE_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "height")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}
#val_labels(SHARE_ds_w1) <- NULL
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew2_rel2-6-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_heig','SHARE.sharew2_rel2-6-0_ph',
                         variables=list('ph013_'), missings = TRUE)
```

```{r local2, echo=F}
SHARE_w2_heig <- opal.execute(o,'SHARE_w2_heig')
vari <- SHARE_w2_heig$ph013_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w2_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4) + xlab("Height") + ylab("Frequency")
```

There are values smaller than 77 that are going to be considered as mistakes and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_heig$id)
SHARE_ds_w2$height <- car::recode(SHARE_w2_heig$ph013_, "NA=999; -2=997; -1=998; 1:77=999")
SHARE_ds_w2$height <- labelled(SHARE_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "height")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(height)) + geom_bar(stat="count", fill="steelblue",width = 0.4) + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}
#val_labels(SHARE_ds_w2) <- NULL
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

There is no variable.



### Wave 4 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew4_rel1-1-1_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_heig','SHARE.sharew4_rel1-1-1_ph',
                         variables=list('ph013_'), missings = TRUE)
```

```{r local4, echo=F}
SHARE_w4_heig <- opal.execute(o,'SHARE_w4_heig')
vari <- SHARE_w4_heig$ph013_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w4_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4) + xlab("Height") + ylab("Frequency")
```

There are values smaller than 60 that are going to be considered as mistakes and they will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_heig$id)
SHARE_ds_w4$height <- car::recode(SHARE_w4_heig$ph013_, "NA=999; -2=997; -1=998; 0:60=999")
SHARE_ds_w4$height <- labelled(SHARE_ds_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "height")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(height)) + geom_bar(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation4, echo=F}
kable(SHARE_w4_heig[which(SHARE_w4_heig$ph013_<101 & SHARE_w4_heig$ph013_>60),],align = 'c',caption = 'There are unusual values that are lower than 100.')
```





```{r importOPAL4, echo=F}
#val_labels(SHARE_ds_w4) <- NULL
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description


| **Name** | `ph013_` |
|----------|------------|
| **Label** | `how tall are you?` |
| **Table name** | `sharew5_rel1-0-0_ph` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_heig','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('ph013_'), missings = TRUE)
```

```{r local5, echo=F}
SHARE_w5_heig <- opal.execute(o,'SHARE_w5_heig')
vari <- SHARE_w5_heig$ph013_
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w5_heig, aes(ph013_)) + geom_bar(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

There are values smaller than 60 that are going to be considered as mistakes and they will be recoded as 999.


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_heig$id)
SHARE_ds_w5$height <- car::recode(SHARE_w5_heig$ph013_, "NA=999; -2=997; -1=998; 0:60")
SHARE_ds_w5$height <- labelled(SHARE_ds_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "height")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(height)) + geom_bar(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation5, echo=F}
kable(SHARE_w5_heig[which(SHARE_w5_heig$ph013_<100 & SHARE_w5_heig$ph013_>59),],align = 'c',caption = 'There are unusual values that are lower than 100: ')
```





```{r importOPAL5, echo=F}
#val_labels(SHARE_ds_w5) <- NULL
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
height <- SHARE_ds_w1
save(height, file = paste0(datafolder, "/w1/height.RData"))
```

```{r,  echo=FALSE}
height <- SHARE_ds_w2
save(height, file = paste0(datafolder, "/w2/height.RData"))
```

```{r,  echo=FALSE}
height <- SHARE_ds_w4
save(height, file = paste0(datafolder, "/w4/height.RData"))
```

```{r,  echo=FALSE}
height <- SHARE_ds_w5
save(height, file = paste0(datafolder, "/w5/height.RData"))
```


# Quality estimation
This variable was a self report measure.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

