---
title: "BMI"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/bmiDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/bmiDS.R')
```




<!-- ########################################################## --> 

# Data process

**Functions:**

```{r function}

# Computation of bmi from height and weight
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  miss <- c(miss,999)
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
  }else{
    bmi <- Weigth/((Heigth/100)^2)
  }
  for(msv in miss){
    bmi[Heigth==msv] <- msv
    bmi[Weigth==msv] <- msv
  }
  bmi
}

# Assignation of new values to an old column
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}

```

## SHARE

### Wave 1 

#### Study-specific variable description


| **Name** | `ph012_` | `ph013_` |
|----------|------------|-|
| **Label** | `weight of respondent` | `how tall are you?` |
| **Table name** | `sharew1_rel2-6-0_ph` |`sharew1_rel2-6-0_ph` |
| **Units** |`kg`|`cm`|
| **Missings** | `-2 = refusal; -1 = don't know` | `-2 = refusal; -1 = don't know` |
| **Description** |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_ph',variables=list('ph012_', 'ph013_'), missings = TRUE)
SHARE_w1 <- opal.execute(o,'SHARE_w1')
```

```{r local1, echo=F}

vari <- SHARE_w1$ph012_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w1, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")

vari <- SHARE_w1$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w1, aes(ph013_)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight(kg)/height(m)^2

The individuals with weight lower than 30 are going to be consider as mistakes and they are going to be recoded as 999.

The missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo1}

SHARE_w1$ph012_ <- car::recode(SHARE_w1$ph012_, "1:10=NA")

SHARE_w1$bmi <- compute_bmi(Heigth = SHARE_w1$ph013_, 
                        Weigth = SHARE_w1$ph012_, miss = c(-2, -1), 
                        heigth_m = FALSE)

SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$bmi <- car::recode(SHARE_w1$bmi, "NA=999; -1=998; -2=997")

SHARE_ds <- SHARE_w1[,c("id","ph013_")]
SHARE_ds$ph013_ <- car::recode(SHARE_w1$ph013_,"NA=999; -2=997; -1=998")
names(SHARE_ds)[2] <- "height"
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$bmi
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "bmi")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1, data = .%>% filter(!vari %in% miss_values_vector)) + xlab("BMI") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
kable(SHARE_w1[which(SHARE_w1$bmi>70 & SHARE_w1$bmi<900),],align = 'c',caption = 'There are unusual values that are higher than 70:')
```





### Wave 2 

#### Study-specific variable description


| **Name** | `ph012_` | `ph013_` |
|----------|------------|-|
| **Label** | `weight of respondent` | `how tall are you?` |
| **Table name** | `sharew2_rel2-6-0_ph` |`sharew2_rel2-6-0_ph` |
| **Units** |`kg`|`cm`|
| **Missings** | `-2 = refusal; -1 = don't know` | `-2 = refusal; -1 = don't know` |
| **Description** |  |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_ph',variables=list('ph012_', 'ph013_'), missings = TRUE)
SHARE_w2 <- opal.execute(o,'SHARE_w2')
```

```{r local2, echo=F}

vari <- SHARE_w2$ph012_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w2, aes(ph012_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% c(vbl_miss,-3,11111111))) + xlab("Weight") + ylab("Frequency")

vari <- SHARE_w2$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w2, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

In the weight variable the values -3, 1 to 10 and 11111111 are going to be considered as mistakes and they will be recoded as 999. 

Height values between 1 and 2 are assumed to be measured in meters.
Height values between 10 and 20 are assumed to be measured in decimeters.

Other height values lower than 60 are going to be considered as mistakes and they will be recoded as 999.


The missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into imputed values from previous wave or 999`

**R script:**

```{r harmo2}

SHARE_w2$ph012_ <- car::recode(SHARE_w2$ph012_, "-3=NA; 1:10=NA; 11111111=NA")

SHARE_w2$height <- SHARE_w2$ph013_

# We use the harmonized variable of wave 1 instead of the study-specific variable
SHARE_w2 <- left_join(SHARE_w2, SHARE_ds, by = "id",suffix = c("","_w1"))


SHARE_w2$height[which(SHARE_w2$ph013_>=1 & SHARE_w2$ph013_<2)] <- SHARE_w2$ph013_[which(SHARE_w2$ph013_>=1 & SHARE_w2$ph013_<2)]*100

SHARE_w2$height[which(SHARE_w2$ph013_>=10 & SHARE_w2$ph013_<20)] <- SHARE_w2$ph013_[which(SHARE_w2$ph013_>=10 & SHARE_w2$ph013_<20)]*10

SHARE_w2$height[which((is.na(SHARE_w2$height) | SHARE_w2$height<=60) & !SHARE_w2$height_w1 %in% miss_values_vector & !is.na(SHARE_w2$height_w1))] <- SHARE_w2$height_w1[which((is.na(SHARE_w2$height) | SHARE_w2$height<=60) & !SHARE_w2$height_w1 %in% miss_values_vector & !is.na(SHARE_w2$height_w1))]

SHARE_w2$height <- car::recode(SHARE_w2$height, "0:60=NA")



SHARE_w2$bmi <- compute_bmi(Heigth = SHARE_w2$height, 
                        Weigth = SHARE_w2$ph012_, miss = c(-2, -1), 
                        heigth_m = FALSE)


SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$bmi <- car::recode(SHARE_w2$bmi, "NA=999; -1=998; -2=997")



# We update the height of the individuals in the global table

SHARE_w2$height <- car::recode(SHARE_w2$height, "NA=999; -2=997; -1=998")
SHARE_ds_prov <- SHARE_ds
SHARE_ds_prov <- assign_merge(SHARE_ds_prov,SHARE_w2[,c("id","height")],log_vec=SHARE_w2$id,col_end_index = 2, col_st_index = 3)
SHARE_ds <- SHARE_ds_prov
rm(SHARE_ds_prov)


```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$bmi
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "bmi")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1, data = .%>% filter(!vari %in% miss_values_vector)) + xlab("BMI") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}


pander(Continuous_summary(SHARE_w2$bmi[which((SHARE_w2$ph013_>=1 & SHARE_w2$ph013_<2) | (SHARE_w2$ph013_>=10 & SHARE_w2$ph013_<20))],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with transformed values from meters or decimeters to centimeters')

kable(SHARE_w2[which(((SHARE_w2$ph013_>=1 & SHARE_w2$ph013_<2) | (SHARE_w2$ph013_>=10 & SHARE_w2$ph013_<20)) & SHARE_w2$bmi>60 & SHARE_w2$bmi<990),], align='c', caption = 'From the same subset of individuals than above, those with harmonised bmi higher than 60')

kable(SHARE_w2[which(!((SHARE_w2$ph013_>=1 & SHARE_w2$ph013_<2) | (SHARE_w2$ph013_>=10 & SHARE_w2$ph013_<20)) & SHARE_w2$bmi>60 & SHARE_w2$bmi<990),], align='c', caption = 'From the complementary subset of individuals, those with harmonised bmi higher than 60')

kable(SHARE_w2[which((SHARE_w2$bmi<12 & SHARE_w2$bmi>-1) | (SHARE_w2$bmi>70 & SHARE_w2$bmi<900)),],align = 'c',caption = 'In general there are unusual values that are lower than 12 or higher than 70:')

pander(Continuous_summary(SHARE_w2$bmi[which((is.na(SHARE_w2$ph013_) | SHARE_w2$ph013_<1 | (SHARE_w2$ph013_>=2 & SHARE_w2$ph013_<10) | (SHARE_w2$ph013_>=20 & SHARE_w2$ph013_<=60)) & !SHARE_w2$height_w1 %in% miss_values_vector)],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with height imputed from wave 1')
```








### Wave 3 

There is no variable.



### Wave 4 

#### Study-specific variable description


| **Name** | `ph012_` | `ph013_` |
|----------|------------|-|
| **Label** | `weight of respondent` | `how tall are you?` |
| **Table name** | `sharew4_rel1-1-1_ph` |`sharew4_rel1-1-1_ph` |
| **Units** |`kg`|`cm`|
| **Missings** | `-2 = refusal; -1 = don't know` | `-2 = refusal; -1 = don't know` |
| **Description** |  |  |



```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_ph',variables=list('ph012_', 'ph013_'), missings = TRUE)
SHARE_w4 <- opal.execute(o,'SHARE_w4')
```

```{r local4, echo=F}

vari <- SHARE_w4$ph012_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w4, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")

vari <- SHARE_w4$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w4, aes(ph013_)) + geom_bar(stat="count", fill="steelblue",width = 0.4, data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The individuals with weight values from 0 to 18 that are going to be consider as a mistake and they will be recoded as 999.

Height values between 1 and 2 are assumed to be measured in meters.
Height values between 10 and 20 are assumed to be measured in decimeters.

Other height values lower than 60 are going to be considered as mistakes and they will be recoded as 999. 

The missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into imputed values from previous waves or 999`

**R script:**

```{r harmo4}

SHARE_w4$ph012_ <- car::recode(SHARE_w4$ph012_, "0:18=NA")

SHARE_w4$height <- SHARE_w4$ph013_

# We use the harmonized variable of previous waves instead of the study-specific variable
SHARE_w4 <- left_join(SHARE_w4, SHARE_ds, by = "id",suffix = c("","_pw"))

SHARE_w4$height[which(SHARE_w4$ph013_>=1 & SHARE_w4$ph013_<2)] <- SHARE_w4$ph013_[which(SHARE_w4$ph013_>=1 & SHARE_w4$ph013_<2)]*100

SHARE_w4$height[which(SHARE_w4$ph013_>=10 & SHARE_w4$ph013_<20)] <- SHARE_w4$ph013_[which(SHARE_w4$ph013_>=10 & SHARE_w4$ph013_<20)]*10

SHARE_w4$height[which((is.na(SHARE_w4$height) | SHARE_w4$height<=59) & !SHARE_w4$height_pw %in% miss_values_vector & !is.na(SHARE_w4$height_pw))] <- SHARE_w4$height_pw[which((is.na(SHARE_w4$height) | SHARE_w4$height<=59) & !SHARE_w4$height_pw %in% miss_values_vector & !is.na(SHARE_w4$height_pw))]

SHARE_w4$height <- car::recode(SHARE_w4$height, "0:59=NA")


SHARE_w4$bmi <- compute_bmi(Heigth = SHARE_w4$height, 
                        Weigth = SHARE_w4$ph012_, miss = c(-2, -1), 
                        heigth_m = FALSE)

SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$bmi <- car::recode(SHARE_w4$bmi, "NA=999; -1=998; -2=997")

# We update the height of the individuals in the global table

SHARE_w4$height <- car::recode(SHARE_w4$height, "NA=999; -2=997; -1=998")
SHARE_ds_prov <- SHARE_ds
SHARE_ds_prov <- assign_merge(SHARE_ds_prov,SHARE_w4[,c("id","height")],log_vec=SHARE_w4$id,col_end_index = 2, col_st_index = 3)
SHARE_ds <- SHARE_ds_prov
rm(SHARE_ds_prov)

```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$bmi
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "bmi")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1, data = .%>% filter(!vari %in% miss_values_vector)) + xlab("BMI") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

pander(Continuous_summary(SHARE_w4$bmi[which((SHARE_w4$ph013_>=1 & SHARE_w4$ph013_<2) | (SHARE_w4$ph013_>=10 & SHARE_w4$ph013_<20))],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with transformed values from meters or decimeters to centimeters')

kable(SHARE_w4[which(((SHARE_w4$ph013_>=1 & SHARE_w4$ph013_<2) | (SHARE_w4$ph013_>=10 & SHARE_w4$ph013_<20)) & SHARE_w4$bmi>60 & SHARE_w4$bmi<990),], align='c', caption = 'From the same subset of individuals than above, those with harmonised bmi higher than 60')

kable(SHARE_w4[which(!((SHARE_w4$ph013_>=1 & SHARE_w4$ph013_<2) | (SHARE_w4$ph013_>=10 & SHARE_w4$ph013_<20)) & SHARE_w4$bmi>60 & SHARE_w4$bmi<990),], align='c', caption = 'From the complementary subset of individuals, those with harmonised bmi higher than 60')


kable(SHARE_w4[which((SHARE_w4$bmi<12 & SHARE_w4$bmi>-1) | (SHARE_w4$bmi>70 & SHARE_w4$bmi<900)),],align = 'c',caption = 'In general, there are unusual values that are lower than 12 or higher than 70:')

pander(Continuous_summary(SHARE_w4$bmi[which((is.na(SHARE_w4$ph013_) | SHARE_w4$ph013_<1 | (SHARE_w4$ph013_>=2 & SHARE_w4$ph013_<10) | (SHARE_w4$ph013_>=20 & SHARE_w4$ph013_<=59)) & !SHARE_w4$height_pw %in% miss_values_vector)],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with height imputed from previous waves')

```









### Wave 5 

#### Study-specific variable description


| **Name** | `ph012_` | `ph013_` |
|----------|------------|-|
| **Label** | `weight of respondent` | `how tall are you?` |
| **Table name** | `sharew5_rel1-0-0_ph` |`sharew5_rel1-0-0_ph` |
| **Units** |`kg`|`cm`|
| **Missings** | `-2 = refusal; -1 = don't know` | `-2 = refusal; -1 = don't know` |
| **Description** |  |  |

    
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_ph',variables=list('ph012_', 'ph013_'), missings = TRUE)
SHARE_w5 <- opal.execute(o,'SHARE_w5')
```

```{r local5, echo=F}

vari <- SHARE_w5$ph012_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph012_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w5, aes(ph012_)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 

vari <- SHARE_w5$ph013_
vbl_miss <- c(-2,-1)
kable(Continuous_summary(vari, missing_values = c(-2, -1))[3], caption = "ph013_")
pander(Continuous_summary(vari, missing_values = c(-2, -1))$summary, caption = "Summary")
ggplot(SHARE_w5, aes(ph013_)) + geom_bar(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The individues with weigth values from 0 to 18 that are going to be consider as a mistake and they will be recoded as 999.

Height values between 1 and 2 are assumed to be measured in meters.
Height values between 10 and 20 are assumed to be measured in decimeters.

Other height values lower than 60 are going to be considered as mistakes and they will be recoded as 999. 

The missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `NA into imputed values from previous waves or 999`

**R script:**

```{r harmo5}

SHARE_w5$ph012_ <- car::recode(SHARE_w5$ph012_, "0:18=NA")


SHARE_w5$height <- SHARE_w5$ph013_

# We use the harmonized variable of previous waves instead of the study-specific variable
SHARE_w5 <- left_join(SHARE_w5, SHARE_ds, by = "id",suffix = c("","_pw"))

SHARE_w5$height[which(SHARE_w5$ph013_>=1 & SHARE_w5$ph013_<2)] <- SHARE_w5$ph013_[which(SHARE_w5$ph013_>=1 & SHARE_w5$ph013_<2)]*100

SHARE_w5$height[which(SHARE_w5$ph013_>=10 & SHARE_w5$ph013_<20)] <- SHARE_w5$ph013_[which(SHARE_w5$ph013_>=10 & SHARE_w5$ph013_<20)]*10

SHARE_w5$height[which((is.na(SHARE_w5$height) | SHARE_w5$height<=59) & !SHARE_w5$height_pw %in% miss_values_vector & !is.na(SHARE_w5$height_pw))] <- SHARE_w5$height_pw[which((is.na(SHARE_w5$height) | SHARE_w5$height<=59) & !SHARE_w5$height_pw %in% miss_values_vector & !is.na(SHARE_w5$height_pw))]

SHARE_w5$height <- car::recode(SHARE_w5$height, "0:59=NA")


SHARE_w5$bmi <- compute_bmi(Heigth = SHARE_w5$height, 
                        Weigth = SHARE_w5$ph012_, miss = c(-2, -1), 
                        heigth_m = FALSE)


SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$bmi <- car::recode(SHARE_w5$bmi, "NA=999; -1=998; -2=997")
SHARE_ds_w5$bmi <- labelled(SHARE_ds_w5$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$bmi
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "bmi")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1, data = .%>% filter(!vari %in% miss_values_vector)) + xlab("BMI") + ylab("Frequency")

```

#### Validation
```{r crosstabulation5, echo=F}


pander(Continuous_summary(SHARE_w5$bmi[which((SHARE_w5$ph013_>=1 & SHARE_w5$ph013_<2) | (SHARE_w5$ph013_>=10 & SHARE_w5$ph013_<20))],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with transformed values from meters or decimeters to centimeters')

kable(SHARE_w5[which(((SHARE_w5$ph013_>=1 & SHARE_w5$ph013_<2) | (SHARE_w5$ph013_>=10 & SHARE_w5$ph013_<20)) & SHARE_w5$bmi>60 & SHARE_w5$bmi<990),], align='c', caption = 'From the same subset of individuals than above, those with harmonised bmi higher than 60')

kable(SHARE_w5[which(!((SHARE_w5$ph013_>=1 & SHARE_w5$ph013_<2) | (SHARE_w5$ph013_>=10 & SHARE_w5$ph013_<20)) & SHARE_w5$bmi>60 & SHARE_w5$bmi<990),], align='c', caption = 'From the complementary subset of individuals, those with harmonised bmi higher than 60')



kable(SHARE_w5[which((SHARE_w5$bmi<12 & SHARE_w5$bmi>-1) | (SHARE_w5$bmi>70 & SHARE_w5$bmi<900)),],align = 'c',caption = 'There are unusual values that are lower than 12 or higher than 70:')

pander(Continuous_summary(SHARE_w5$bmi[which((is.na(SHARE_w5$ph013_) | SHARE_w5$ph013_<1 | (SHARE_w5$ph013_>=2 & SHARE_w5$ph013_<10) | (SHARE_w5$ph013_>=20 & SHARE_w5$ph013_<=59)) & !SHARE_w5$height_pw %in% miss_values_vector)],missing_values = c(-1,-2,999))$summary, caption = 'BMI summary of individuals with height imputed from previous waves')

```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[2,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
* Individuals with very extreme values were specified with all their data used in this harmonisation at each validation. We keep that data as it is even when it seems wrong.
* Due to the big quantity of missing values for new individuals in waves 2 and 4, we decided to impute the height answered in previous waves.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

