---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/obesityDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/obesityDS.R')
```

<!-- ######################################################## --> 

# Data process




## SHARE
### Wave 1

#### Study-specific variable description


| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign_aksst1, include=FALSE}
#opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w1',
#                         variables=list('bmi'), missings = TRUE)
#SHARE_bmi <- opal.execute(o,'SHARE_bmi')

load(paste0(datafolder, "/w1/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local_aksst1, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1 ) + xlab("BMI") + ylab("Frequency") + xlim(10,80)
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w1$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999")
SHARE_ds_w1$obesity <- labelled(SHARE_ds_w1[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
vari <- SHARE_ds_w1$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(x=factor(SHARE_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab1, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum(na.omit(SHARE_bmi[[2]])==999))
AfterH <- table(SHARE_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997","998","999") 
kable(C)
```


```{r read1, include=FALSE}
rm(SHARE_bmi)
```


### Wave 2

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign2, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w2',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w2/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local2, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**


```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w2$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w2$obesity <- labelled(SHARE_ds_w2[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(x=factor(SHARE_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000) ) ))
AfterH <- table(SHARE_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(>1000,999)->999") 
kable(C)
```


```{r read2, include=FALSE}
rm(SHARE_bmi)
```


### Wave 3

There is no variable.


### Wave 4

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign4, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w4',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w4/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local4, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w4$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w4$obesity <- labelled(SHARE_ds_w4[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(x=factor(SHARE_ds_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab4, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000), sum(is.na(SHARE_bmi[[2]])) ) ))
AfterH <- table(SHARE_ds_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(999,NA,>1000)->999") 
kable(C)
```



```{r read4, include=FALSE}
rm(SHARE_bmi)
```



### Wave 5

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


```{r assign5, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w5',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w5/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local5, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w5$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w5$obesity <- labelled(SHARE_ds_w5[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(x=factor(SHARE_ds_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab5, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000), sum(is.na(SHARE_bmi[[2]])) ) ))
AfterH <- table(SHARE_ds_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(999,NA,>1000)->999") 
kable(C)
```



```{r read5, include=FALSE}
rm(SHARE_bmi)
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO classification. Finally, the resulting BMI variable was coded as follows: BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.



<!--- ## Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

