---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ######################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ######################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `obesity`
* Variable label: `Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2.`
* Variable description: `the BMI variable should be created by dividing weight and hiegh variables by means of the following equation= weight (kg)/height(m)^2. Then, the Obesity variable should be generated according to the WHO cutoff point for BMI classification`
* Domain: `Physical measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not obese
1        | Obese

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ######################################################## --> 

# Data process




```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```



```{r lab, echo=FALSE}
ds_label <- "Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2"
```
## SHARE
### Wave 1

#### Study-specific variable description


| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign_aksst1, include=FALSE}
#opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w1',
#                         variables=list('bmi'), missings = TRUE)
#SHARE_bmi <- opal.execute(o,'SHARE_bmi')

load(paste0(datafolder, "/w1/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local_aksst1, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1 ) + xlab("BMI") + ylab("Frequency") + xlim(10,80)
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w1$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999")
SHARE_ds_w1$obesity <- labelled(SHARE_ds_w1[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
vari <- SHARE_ds_w1$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(x=factor(SHARE_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab1, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum(na.omit(SHARE_bmi[[2]])==999))
AfterH <- table(SHARE_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997","998","999") 
kable(C)
```


```{r read1, include=FALSE}
rm(SHARE_bmi)
```


### Wave 2

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign2, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w2',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w2/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local2, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**


```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w2$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w2$obesity <- labelled(SHARE_ds_w2[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(x=factor(SHARE_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000) ) ))
AfterH <- table(SHARE_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(>1000,999)->999") 
kable(C)
```


```{r read2, include=FALSE}
rm(SHARE_bmi)
```


### Wave 3

There is no variable.


### Wave 4

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


    
```{r assign4, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w4',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w4/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local4, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w4$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w4$obesity <- labelled(SHARE_ds_w4[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(x=factor(SHARE_ds_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab4, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000), sum(is.na(SHARE_bmi[[2]])) ) ))
AfterH <- table(SHARE_ds_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(999,NA,>1000)->999") 
kable(C)
```



```{r read4, include=FALSE}
rm(SHARE_bmi)
```



### Wave 5

#### Study-specific variable description

| **Name** | `bmi`|
|-|-|
| **Label** | `Body Mass Index calculated as weight (kg)/height(m)^2` |
| **Table name** | `bmi` |
| **Missings** | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |


```{r assign5, include=FALSE}
# opal.assign.table.tibble(o, 'SHARE_bmi','_Athlos_Harm_Dataset.SHARE_ds_w5',
#                          variables=list('bmi'), missings = TRUE)
# SHARE_bmi <- opal.execute(o,'SHARE_bmi')
load(paste0(datafolder, "/w5/bmi.RData"))
SHARE_bmi <- bmi
SHARE_bmi$bmi <- as.numeric(SHARE_bmi$bmi)
```

```{r local5, echo=F}
vari <- SHARE_bmi$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "bmi")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_bmi, aes(bmi)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.1) + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_bmi$id)
SHARE_ds_w5$obesity <- car::recode(SHARE_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
SHARE_ds_w5$obesity <- labelled(SHARE_ds_w5[[2]], labels = c("not obese"=0, "obese"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "obesity")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(x=factor(SHARE_ds_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab5, echo=F}
BeforeH <- c(sum(na.omit(SHARE_bmi[[2]])<30),sum(na.omit(SHARE_bmi[[2]])>=30 & na.omit(SHARE_bmi[[2]])<=900), sum(na.omit(SHARE_bmi[[2]])==997), sum(na.omit(SHARE_bmi[[2]])==998), sum( c(sum(na.omit(SHARE_bmi[[2]])==999), sum(na.omit(SHARE_bmi[[2]])>=1000), sum(is.na(SHARE_bmi[[2]])) ) ))
AfterH <- table(SHARE_ds_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","997", "998", "(999,NA,>1000)->999") 
kable(C)
```



```{r read5, include=FALSE}
rm(SHARE_bmi)
```


<!--- ############################################# Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE}
SHARE_m_ds_w1   <- SHARE_ds_w1
SHARE_m_ds_w2   <- SHARE_ds_w2
#SHARE_m_ds_w3   <- SHARE_ds_w3
SHARE_m_ds_w4   <- SHARE_ds_w4
SHARE_m_ds_w5   <- SHARE_ds_w5

#l.hds <- list(SHARE_ds_w1 = SHARE_ds_w1 , SHARE_ds_w2 = SHARE_ds_w2,      SHARE_ds_w3=SHARE_ds_w3, SHARE_ds_w4 = SHARE_ds_w4, SHARE_ds_w5=SHARE_ds_w5)

#m.hds <- list(SHARE_m_ds_w1 = SHARE_m_ds_w1 , SHARE_m_ds_w2 = SHARE_m_ds_w2, SHARE_m_ds_w3 = SHARE_m_ds_w3, SHARE_m_ds_w4 = SHARE_m_ds_w4, SHARE_m_ds_w5 = SHARE_m_ds_w5)

l.hds <- list(SHARE_ds_w1 = SHARE_ds_w1 , SHARE_ds_w2 = SHARE_ds_w2, SHARE_ds_w4 = SHARE_ds_w4, SHARE_ds_w5=SHARE_ds_w5)

m.hds <- list(SHARE_m_ds_w1 = SHARE_m_ds_w1 , SHARE_m_ds_w2 = SHARE_m_ds_w2, SHARE_m_ds_w4 = SHARE_m_ds_w4, SHARE_m_ds_w5 = SHARE_m_ds_w5)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1, "Respond, died after this wave"=2, "Respond(proxy), died"=3, "No respond, alive"=4, "No respond, died this wave"=5, "No respond, died previous waves"=6, "No respond, dropped from sample"=7))

  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}
```



## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}

t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]) )
names(t.hds)<-c("val", "label", "Wave1", "Wave2", "Wave4", "Wave5")
kable(t.hds)
```



```{r,  echo=FALSE}
obesity <- SHARE_ds_w1
save(obesity, file = paste0(datafolder, "/w1/obesity.RData"))
```

```{r,  echo=FALSE}
obesity <- SHARE_ds_w2
save(obesity, file = paste0(datafolder, "/w2/obesity.RData"))
```

```{r,  echo=FALSE}
obesity <- SHARE_ds_w4
save(obesity, file = paste0(datafolder, "/w4/obesity.RData"))
```

```{r,  echo=FALSE}
obesity <- SHARE_ds_w5
save(obesity, file = paste0(datafolder, "/w5/obesity.RData"))
```


# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.



<!--- ## Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

