---
title: "Arterial hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ah`
* Variable label: `Arterial hypertension`
* Variable description: `Arterial hypertension. Means of all diastolic blood pressure measures.`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no hypertension
1        | hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Arterial hypertension"
ds_label_all <- "Arterial hypertension. Means of all diastolic blood pressure measures."
```

# Data process

## Greece

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dbp`
* Label: `diastolic blood pressure`
* Type of variable: `countinous`

* Name: `sbp`
* Label: `systolic blood pressure`
* Type of variable: `countinous`

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_ah','ATTICA.ATTICA_Baseline',
                         variables=list('dbp', 'sbp'), missings = TRUE)
ATTICA_ah <- opal.execute(o,'ATTICA_ah')
```

```{r local1, echo=FALSE}
vari <- ATTICA_ah$dbp
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_ah, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")

vari <- ATTICA_ah$sbp
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_ah, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable, first of all, it has to be created two categorical variables as follows:

* dh:
  + `dbp >= 90 into 1`
  + `dbp < 90 into 0`

* sh:
  + `sbp >= 140 into 1`
  + `sbp < 140 into 0`

After that, to compute the harmonized variable from this two variables has to be recoded as follows

* `if dh = 0 and sh = 0 into 0`
* `if dh = 1 and sh = 0 into 1`
* `if dh = 0 and sh = 1 into 1`
* `if dh = 1 and sh = 1 into 1`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
ATTICA_ah$dh <- recode(ATTICA_ah$dbp, "0:89=0; 90:hi=1")
ATTICA_ah$sh <- recode(ATTICA_ah$sbp, "0:139=0; 140:hi=1")

ATTICA_ds_w1 <- tibble(id=ATTICA_ah$id)
ATTICA_ds_w1$ah <- NA
ATTICA_ds_w1$ah[which(ATTICA_ah$dh==0 & ATTICA_ah$sh==0)] <- 0
ATTICA_ds_w1$ah[which(ATTICA_ah$dh==1 & ATTICA_ah$sh==0)] <- 1
ATTICA_ds_w1$ah[which(ATTICA_ah$dh==0 & ATTICA_ah$sh==1)] <- 1
ATTICA_ds_w1$ah[which(ATTICA_ah$dh==1 & ATTICA_ah$sh==1)] <- 1
ATTICA_ds_w1$ah <- labelled(ATTICA_ds_w1$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ATTICA_ds_w1$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1}


#### Quality estimation
No comments.


```

```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'ATTICA_ds_w1', ATTICA_ds_w1)
#opal.symbol_import(o,'ATTICA_ds_w1', project='_Athlos_Harm_Dataset')

label(ATTICA_ds_w1) <- ds_label_all
ah <- ATTICA_ds_w1
save(ah, file = "../RData/w1/ah.RData")
```





### ATTICA - Wave 2 

There is no variable.

### ATTICA - Wave 3 

There is no variable.
