---
title: "BMI"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `bmi`
* Label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `the BMI variable should be created by dividing weight and heigh variables with the following equation= weight (kg)/height(m)^2.`


### ATTICA - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bmi`
* Label: `Body Mass Index (kg/m2)`
* Type of variable: `countinous`

```{r assign1}
opal.assign.table.tibble(o, 'ATTICA_w1_bmi','ATTICA.ATTICA_Baseline',
                         variables=list('bmi'), missings = TRUE)
```

```{r local1}
ATTICA_w1_bmi <- opal.execute(o,'ATTICA_w1_bmi')
Continuous_summary(var = ATTICA_w1_bmi$bmi, missing_values = NA)
ggplot(ATTICA_w1_bmi, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

R code of the ALGORITHM:

```{r harmo1}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_bmi$id)
ATTICA_ds_w1$bmi <- car::recode(ATTICA_w1_bmi$bmi, "NA=999")
ATTICA_ds_w1$bmi <- labelled(ATTICA_ds_w1$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = ATTICA_ds_w1$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,120)
```

#### Validation
It is going to check if weight and heigth values are correct by computing BMI with the formula: weight/height^2. 
```{r crosstabulation1}
opal.assign.table.tibble(o, 'ATTICA_w1_whb','ATTICA.ATTICA_Baseline',
                         variables=list('weight', 'height', 'bmi'), missings = TRUE)
ATTICA_w1_whb <- opal.execute(o,'ATTICA_w1_whb')

ATTICA_w1_whb$bmi_c <- ATTICA_w1_whb$weight/(ATTICA_w1_whb$height/100)^2


ATTICA_w1_whb$proff <- ATTICA_w1_whb$bmi - ATTICA_w1_whb$bmi_c
summary(ATTICA_w1_whb$proff)
```


### ATTICA - Wave 2 

There is no variable.

### ATTICA - Wave 3 

There is no variable.


# Quality estimation
No comments.

```{r save, echo=FALSE}
bmi <- ATTICA_ds_w1
save(bmi, file = "../RData/w1/bmi.RData")
rm(bmi)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

