---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process




## South Africa


### Wave 1


#### Study-specific variable description

| **Name** | `q1503`|`q1501`|`q1504` |`q1505`|
|-|-|-|-|-|
| **Label** | `q1503: currently working?`|`q1501: ever worked`|`q1504: main reason not working?`|`q1505: age stop working`|
| **Table name**  | `southAfricaINDdata`|`southAfricaINDdata`|`southAfricaINDdata`|`southAfricaINDdata`|
| **Categories** | `1 = yes working`<br/>`2 = not working` | `1 = yes worked`<br/>`2 = not worked`|`1 = homemaker`<br/>`2 = can't find work`<br/>`3 = do voluntary/unpaid`<br/>`4 = studies/training`<br/>`5 = health/disability`<br/>`6 = care of family member`<br/>`7 = no need`<br/>`8 =  spouse/family object`<br/>`9 =  retired/too old`<br/>`10 = laid off/redundant`<br/>`11 = seasonal`<br/>`12 = temporary time off`<br/>`87 = other`|`continuous`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` | `-8 = don't know`<br/>`NA` | `-9 = not applicable`<br/>`-8 = don't know`<br/>`NA` | 
| **Description** |  |  |  |  |

```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('q1503','q1501','q1504','q1505'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1503')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q1501
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1501')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q1501))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q1504
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = 'q1504')
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q1504))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q1505
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_SA_w1,!vbl %in% vbl_miss), aes(q1505)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504 == 9 into 1`
* `q1504 != 9 into 0`
* `q1501 == 2 into 996`
* `q1503 == 1 into 0`
* `-8 into 998`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 0, age_retired = 996`
* `if retired == 2, age_retired = q1505`
* `-8 into 998`
* `-9 into 996`

**R script:**

```{r harmo SA_w1}

# Categorical variable harmonization
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$retired <- car::recode(SAGE_SA_w1$q1504,"9=1; -8=998; c(1,2,3,4,5,6,7,8,10,11,12,87)=0; NA=999")
SAGE_ds_SA_w1$retired[which(SAGE_SA_w1$q1501==2)] <- 996
SAGE_ds_SA_w1$retired[which(SAGE_SA_w1$q1503==1)] <- 0

# Continuous variable harmonization
SAGE_ds_SA_w1$age_retired <- rep(999,length(SAGE_SA_w1$id))
SAGE_ds_SA_w1$age_retired[which(SAGE_ds_SA_w1$retired==1)] <- car::recode(SAGE_SA_w1$q1505[which(SAGE_ds_SA_w1$retired==1)], "-8=998; -9=996; NA=999")
SAGE_ds_SA_w1$age_retired[which(SAGE_ds_SA_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SAGE_ds_SA_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_SA_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}

```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `q1503`|`q1501`|`q1504` |`q1505`|
|-|-|-|-|-|
| **Label** | `q1503: currently working?`|`q1501: ever worked`|`q1504: main reason not working?`|`q1505: age stop working`|
| **Table name**  | `ghanaINDData`|`ghanaINDData`|`ghanaINDData`|`ghanaINDData`|
| **Categories** | `1 = yes working`<br/>`2 = not working` | `1 = yes worked`<br/>`2 = not worked`|`1 = homemaker`<br/>`2 = can't find work`<br/>`3 = do voluntary/unpaid`<br/>`4 = studies/training`<br/>`5 = health/disability`<br/>`6 = care of family member`<br/>`7 = no need`<br/>`8 =  spouse/family object`<br/>`9 =  retired/too old`<br/>`10 = laid off/redundant`<br/>`11 = seasonal`<br/>`12 = temporary time off`<br/>`87 = other`|`continuous`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` | `98 = not applicable`<br/>`97 = refused`<br/>`88 = don't know`<br/>`NA` |`-9 = not applicable`<br/>`-8 = don't know`<br/>`NA` | 
| **Description** |  |  |  |  |

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('q1503','q1501','q1504','q1505'), missings = T)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')

```

```{r local ghana_w1, echo=F}

vbl <- SAGE_ghana_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1503')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q1501
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1501')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q1501))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q1504
kable(Categorical_summary(vbl, missing_values = c(88))[3], caption = 'q1504')
kable(Categorical_summary(vbl, missing_values = c(88))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q1504))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q1505
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_ghana_w1,!vbl %in% vbl_miss), aes(q1505)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504 == 9 into 1`
* `q1504 != 9 into 0`
* `q1501 == 2 into 996`
* `q1503 == 1 into 0`
* `88 into 998`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 0, age_retired = 996`
* `if retired == 2, age_retired = q1505`
* `-8 into 998`
* `-9 into 996`

**R script:**

```{r harmo ghana_w1}

# Categorical variable harmonization
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$retired <- car::recode(SAGE_ghana_w1$q1504,"c(9)=1; 88=998; c(1,6,3,4,2,5,7,8,10,11,12,87)=0; NA=999")
SAGE_ds_ghana_w1$retired[which(SAGE_ghana_w1$q1503==1)] <- 0
SAGE_ds_ghana_w1$retired[which(SAGE_ghana_w1$q1501==2)] <- 996

# Continuous variable harmonization
SAGE_ds_ghana_w1$age_retired <- rep(999,length(SAGE_ghana_w1$id))
SAGE_ds_ghana_w1$age_retired[which(SAGE_ds_ghana_w1$retired==1)] <- car::recode(SAGE_ghana_w1$q1505[which(SAGE_ds_ghana_w1$retired==1)], "-8=998; -9=996; NA=999")
SAGE_ds_ghana_w1$age_retired[which(SAGE_ds_ghana_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SAGE_ds_ghana_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_ghana_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}

```





## China


### Wave 1



#### Study-specific variable description

| **Name** | `q1503`|`q1501`|`q1504` |`q1505`|
|-|-|-|-|-|
| **Label** | `q1503: currently working?`|`q1501: ever worked`|`q1504: main reason not working?`|`q1505: age stop working`|
| **Table name**  | `chinaINDData`|`chinaINDData`|`chinaINDData`|`chinaINDData`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |`1 = yes worked`<br/>`2 = not worked`|`1 = homemaker`<br/>`2 = can't find work`<br/>`3 = do voluntary/unpaid`<br/>`4 = studies/training`<br/>`5 = health/disability`<br/>`6 = care of family member`<br/>`7 = no need`<br/>`8 =  spouse/family object`<br/>`9 =  retired/too old`<br/>`10 = laid off/redundant`<br/>`11 = seasonal`<br/>`12 = temporary time off`<br/>`87 = other`|`continuous`|
| **Missings** |`NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q1503','q1501','q1504','q1505'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1503')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q1501
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1501')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q1501))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q1504
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = 'q1504')
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q1504))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q1505
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_china_w1,!vbl %in% vbl_miss), aes(q1505)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504 == 9 into 1`
* `q1504 != 9 into 0`
* `q1501 == 2 into 996`
* `q1503 == 1 into 0`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 0, age_retired = 996`
* `if retired == 2, age_retired = q1505`
* `-8 into 998`
* `-9 into 996`

**R script:**

```{r harmo china_w1}

# Categorical variable harmonization
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$retired <- car::recode(SAGE_china_w1$q1504,"c(9)=1; c(3,4,1,2,5,7,8,6,10,11,12,87)=0; NA=999")
SAGE_ds_china_w1$retired[which(SAGE_china_w1$q1503==1)] <- 0
SAGE_ds_china_w1$retired[which(SAGE_china_w1$q1501==2)] <- 996

# Continuous variable harmonization
SAGE_ds_china_w1$age_retired <- rep(999,length(SAGE_china_w1$id))
SAGE_ds_china_w1$age_retired[which(SAGE_ds_china_w1$retired==1)] <- car::recode(SAGE_china_w1$q1505[which(SAGE_ds_china_w1$retired==1)], "-8=998; -9=996; NA=999")
SAGE_ds_china_w1$age_retired[which(SAGE_ds_china_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SAGE_ds_china_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_china_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}

```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `q1503`|`q1501`|`q1504` |`q1505a`|`age`|
|-|-|-|-|-|-|
| **Label** | `Q1503: Currently working?`|`q1501: ever worked`|`Q1504: Main reason not working?`|`Q1505a: Years ago stopped work`|`age`|
| **Table name**  | `indiaINDData`|`indiaINDData`|`indiaINDData`|`indiaINDData`|`age`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |`1 = yes worked`<br/>`2 = not worked`|`1 = homemaker`<br/>`2 = can't find work`<br/>`3 = do voluntary/unpaid`<br/>`4 = studies/training`<br/>`5 = health/disability`<br/>`6 = care of family member`<br/>`7 = no need`<br/>`8 =  spouse/family object`<br/>`9 =  retired/too old`<br/>`10 = laid off/redundant`<br/>`11 = seasonal`<br/>`12 = temporary time off`<br/>`87 = other`|`continuous`|`continuous`|
| **Missings** |`NA` |`NA` | `NA` | `-9 = Not applicable`<br/>`-8 = Don't know`<br/>`NA` |  |
| **Description** |  |  |  |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('q1503','q1501','q1504','q1505a'), missings = T)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')
load(paste0(datafolder,"india_w1/age.RData"))
SAGE_india_w1 <- left_join(SAGE_india_w1,age,by="id")
rm(age)

```

```{r local india_w1, echo=F}

vbl <- SAGE_india_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1503')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q1501
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1501')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q1501))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q1504
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = 'q1504')
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q1504))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q1505a
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505a')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_india_w1,!vbl %in% vbl_miss), aes(q1505a)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$age
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'age')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_india_w1,!vbl %in% vbl_miss), aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504 == 9 into 1`
* `q1504 != 9 into 0`
* `q1501 == 2 into 996`
* `q1503 == 1 into 0`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 0, age_retired = 996`
* `if retired == 2, age_retired = age - q1505a`
* `-8 into 998`
* `-9 into 996`

**R script:**

```{r harmo india_w1}

# Categorical variable harmonization
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$retired <- car::recode(SAGE_india_w1$q1504,"c(9)=1; c(3,4,1,2,5,7,8,6,10,11,12,87)=0; NA=999")
SAGE_ds_india_w1$retired[which(SAGE_india_w1$q1503==1)] <- 0
SAGE_ds_india_w1$retired[which(SAGE_india_w1$q1501==2)] <- 996

# Continuous variable harmonization
SAGE_ds_india_w1$age_retired <- SAGE_india_w1$age - SAGE_india_w1$q1505a
SAGE_ds_india_w1$age_retired[which(SAGE_india_w1$q1505a==-8)] <- 998
SAGE_ds_india_w1$age_retired[which(SAGE_ds_india_w1$retired==0 | SAGE_india_w1$q1505a==-9)] <- 996
SAGE_ds_india_w1$age_retired <- car::recode(SAGE_ds_india_w1$age_retired,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SAGE_ds_india_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_india_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

```





## Russian Federation

Not found harmonizable variable.



## Mexico


### Wave 1

#### Study-specific variable description

| **Name** | `q1503`|`q1501`|`q1504` |`q1505`|
|-|-|-|-|-|
| **Label** | `q1503: currently working?`|`q1501: ever worked`|`q1504: main reason not working?`|`q1505: age stop working`|
| **Table name**  | `mexicoINDdata`|`mexicoINDdata`|`mexicoINDdata`|`mexicoINDdata`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |`1 = yes worked`<br/>`2 = not worked`|`1 = homemaker`<br/>`2 = can't find work`<br/>`3 = do voluntary/unpaid`<br/>`4 = studies/training`<br/>`5 = health/disability`<br/>`6 = care of family member`<br/>`7 = no need`<br/>`8 =  spouse/family object`<br/>`9 =  retired/too old`<br/>`10 = laid off/redundant`<br/>`11 = seasonal`<br/>`12 = temporary time off`<br/>`87 = other`|`continuous`|
| **Missings** |`NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q1503','q1501','q1504','q1505'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1503')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q1501
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q1501')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q1501))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q1504
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = 'q1504')
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q1504))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q1505
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'q1505')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SAGE_mexico_w1,!vbl %in% vbl_miss), aes(q1505)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `q1504 == 9 into 1`
* `q1504 != 9 into 0`
* `q1501 == 2 into 996`
* `q1503 == 1 into 0`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 0, age_retired = 996`
* `if retired == 2, age_retired = q1505`
* `-8 into 998`
* `-9 into 996`

**R script:**

```{r harmo mexico_w1}

# Categorical variable harmonization
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$retired <- car::recode(SAGE_mexico_w1$q1504,"9=1; c(3,4,1,2,5,7,8,6,10,11,12,87)=0; NA=999")
SAGE_ds_mexico_w1$retired[which(SAGE_mexico_w1$q1503==1)] <- 0
SAGE_ds_mexico_w1$retired[which(SAGE_mexico_w1$q1501==2)] <- 996

# Continuous variable harmonization
SAGE_ds_mexico_w1$age_retired <- rep(999,length(SAGE_mexico_w1$id))
SAGE_ds_mexico_w1$age_retired[which(SAGE_ds_mexico_w1$retired==1)] <- car::recode(SAGE_mexico_w1$q1505[which(SAGE_ds_mexico_w1$retired==1)], "-8=998; -9=996; NA=999")
SAGE_ds_mexico_w1$age_retired[which(SAGE_ds_mexico_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- SAGE_ds_mexico_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_mexico_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("SAGE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Mexico_W1")
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





