---
title: "Childhood socioeconomic position"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/childsepDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/childsepDS.R')
```


# Data process

## South Africa


### Wave 1


#### Study-specific variable description


| **Name** | `q1027` |`q1031`|
|-|-|-|
| **Label** | `q1027: mother occupation`| `q1031: father occupation`|
| **Table name** | `southAfricaINDdata`| `southAfricaINDdata`|
| **Categories** |  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces`|  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces` |
| **Missings** | `88 = Don't know`<br/>`NA` | `88 = Don't know`<br/>`NA` |
| **Description** |  |  |


```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('q1027','q1031'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1') %>% update_labelled()

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$q1027
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q1031
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `childsep` from the study-specific variables its minimum has to be recoded as follows:

* `1:2 into 0`
* `3:5,10 into 1`
* `6:9 into 2`
* `88 into 998`
* `NA into 999`

**R script:**


```{r harmo SA_w1, tidy=FALSE}


SAGE_ds_SA_w1 <- SAGE_SA_w1 %>%
  mutate(
    q1027 = dplyr::recode(q1027, `6` = 12L, `10` = 6L),
    q1031 = dplyr::recode(q1031, `6` = 12L, `10` = 6L)
  ) %>%
  mutate(childsep = do.call(pmin, c(select(., q1027, q1031), na.rm = TRUE))) %>%
  mutate(
    childsep = case_when(
      childsep %in% c(1:2) ~ 0,
      childsep %in% c(3:6) ~ 1,
      childsep %in% c(7:9,12) ~ 2,
      childsep %in% c(88) ~ 998,
      TRUE ~ 999
    )
  ) %>%
  select(id, childsep)
  

```



#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}
```



## Ghana


### Wave 1

Data not harmonisable.

## China


### Wave 1


#### Study-specific variable description


| **Name** | `q1027` |`q1031`|
|-|-|-|
| **Label** | `q1027: mother occupation`| `q1031: father occupation`|
| **Table name** | `chinaINDData`| `chinaINDData`|
| **Categories** |  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces`<br/> `11 = Other`|  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces`<br/> `11 = Other` |
| **Missings** | `88 = Don't know`<br/>`NA` | `88 = Don't know`<br/>`NA` |
| **Description** |  |  |


```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q1027','q1031'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1') %>% update_labelled()

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$q1027
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q1031
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `childsep` from the study-specific variables its minimum has to be recoded as follows:

* `1:2 into 0`
* `3:5,10 into 1`
* `6:9 into 2`
* `88 into 998`
* `0,NA into 999`

**R script:**


```{r harmo china_w1, tidy=FALSE}


SAGE_ds_china_w1 <- SAGE_china_w1 %>%
  mutate(
    q1027 = dplyr::recode(q1027, `6` = 12L, `10` = 6L),
    q1031 = dplyr::recode(set_na(q1031, na = c(0)), `6` = 12L, `10` = 6L)
  ) %>%
  mutate(childsep = do.call(pmin, c(select(., q1027, q1031), na.rm = TRUE))) %>%
  mutate(
    childsep = case_when(
      childsep %in% c(1:2) ~ 0,
      childsep %in% c(3:6) ~ 1,
      childsep %in% c(7:9, 12) ~ 2,
      childsep %in% c(88) ~ 998,
      TRUE ~ 999
    )
  ) %>%
  select(id, childsep)
  

```



#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}
```


## India


### Wave 1

Data not harmonisable.

## Russian Federation


### Wave 1

Data not harmonisable.


## Mexico


### Wave 1


#### Study-specific variable description


| **Name** | `q1027` |`q1031`|
|-|-|-|
| **Label** | `q1027: mother occupation`| `q1031: father occupation`|
| **Table name** | `mexicoINDdata`| `mexicoINDdata`|
| **Categories** |  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces`<br/> `11 = Other`|  `1 = Legislators, senior officials and managers` <br/> `2 = Professionals` <br/> `3 = Technicians and associate professionals` <br/> `4 = Clerks` <br/> `5 = Service workers and shop and market sales workers` <br/> `6 = Skilled agricultural and fishery workers` <br/>`7 = Craft and related trades workers`<br/> `8 = Plant and machine operators and assemblers`<br/> `9 = Elementary occupations`<br/> `10 = Armed forces`<br/> `11 = Other` |
| **Missings** | `88 = Don't know`<br/>`NA` | `88 = Don't know`<br/>`NA` |
| **Description** |  |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q1027','q1031'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1') %>% update_labelled()

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$q1027
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q1031
vbl_miss <- c(88)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `childsep` from the study-specific variables its minimum has to be recoded as follows:

* `1:2 into 0`
* `3:5,10 into 1`
* `6:9 into 2`
* `88 into 998`
* `11,NA into 999`

**R script:**


```{r harmo mexico_w1, tidy=FALSE, tidy=FALSE}


SAGE_ds_mexico_w1 <- SAGE_mexico_w1 %>%
  mutate(
    q1027 = dplyr::recode(set_na(q1027, na = c(11)), `6` = 12L, `10` = 6L),
    q1031 = dplyr::recode(set_na(q1031, na = c(11)), `6` = 12L, `10` = 6L)
  ) %>%
  mutate(childsep = do.call(pmin, c(select(., q1027, q1031), na.rm = TRUE))) %>%
  mutate(
    childsep = case_when(
      childsep %in% c(1:2) ~ 0,
      childsep %in% c(3:6) ~ 1,
      childsep %in% c(7:9,12) ~ 2,
      childsep %in% c(88) ~ 998,
      TRUE ~ 999
    )
  ) %>%
  select(id, childsep)
  

```



#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```


# Quality estimation





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

