---
title: "Wealth"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `wealth`
* Variable label: `Total score based in all sources of income transformed into a comparable and normalized categoric variable.`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical ordinal`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | 1st quintile
2        | 2nd quintile
3        | 3rd quintile
4        | 4th quintile
5        | 5th quintile

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Comments: `Need to pay attention to specificities like: before/after taxes or contributions. People: HH income is prioritized. When not available individual/caregiver/informant/family income is caolected. Source: Pension/family/work/government/disablity/total. all sources are taken into account. For some studies, the maximum value can be compared (and crossed by sex and age to control biases) . Time-lapse: weekly, monthly, in the last 12 months. 'Many values are missing since not all respondents have all sources of income or, within the household there is not always more members, in these cases do not confuse missing data with missing values and mean a 0 should be added to the total sum in each case.`

```{r lab, echo=FALSE}
ds_label <- "wealth"
ds_label_all <- "Total score based in all sources of income transformed into a comparable and normalized categoric variable"
```

<!-- ########################################################## --> 

# Data process

## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `southAfricaINDdata` | 
| **Categories** | `continuous` |
| **Description** |  |


```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.southAfricaINDdata',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local1,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
SAGE_SA_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_SA_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_SA_ds_w1$wealth <- as.integer(SAGE_SA_ds_w1$wealth)
SAGE_SA_ds_w1$wealth <- labelled(SAGE_SA_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- SAGE_SA_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_SA_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_SA_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_SA_ds_w1
save(wealth, file = "../RData/SA_w1/wealth.RData")
rm(wealth)
```






## Ghana 

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `ghanaINDData` | 
| **Categories** | `continuous` |
| **Description** |  |

```{r assign_ghana,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.ghanaINDData',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local_ghana,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ghana,   echo=TRUE}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_ghana_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_ghana_ds_w1$wealth <- as.integer(SAGE_ghana_ds_w1$wealth)
SAGE_ghana_ds_w1$wealth <- labelled(SAGE_ghana_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ghana,  echo=FALSE}
vari <- SAGE_ghana_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_ghana_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_ghana_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_ghana,  echo=FALSE}
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_ghana_ds_w1
save(wealth, file = "../RData/ghana_w1/wealth.RData")
rm(wealth)

SAGE_ghana_m_ds_w1 <- SAGE_ghana_ds_w1
SAGE_ghana_m_ds_w1$wealth <- car::recode(SAGE_ghana_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```





## China 

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `chinaINDData` | 
| **Categories** | `continuous` |
| **Description** |  |

```{r assign_china,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.chinaINDData',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local_china,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_china,   echo=TRUE}
SAGE_china_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_china_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_china_ds_w1$wealth <- as.integer(SAGE_china_ds_w1$wealth)
SAGE_china_ds_w1$wealth <- labelled(SAGE_china_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_china,  echo=FALSE}
vari <- SAGE_china_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_china_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_china_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_china,  echo=FALSE}
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_china_ds_w1
save(wealth, file = "../RData/china_w1/wealth.RData")
rm(wealth)

SAGE_china_m_ds_w1 <- SAGE_china_ds_w1
SAGE_china_m_ds_w1$wealth <- car::recode(SAGE_china_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## India 

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `indiaINDData` | 
| **Categories** | `continuous` |
| **Description** |  |


```{r assign_india,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.indiaINDData',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local_india,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_india,   echo=TRUE}
SAGE_india_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_india_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_india_ds_w1$wealth <- as.integer(SAGE_india_ds_w1$wealth)
SAGE_india_ds_w1$wealth <- labelled(SAGE_india_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_india,  echo=FALSE}
vari <- SAGE_india_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_india_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_india_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_india,  echo=FALSE}
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_india_ds_w1
save(wealth, file = "../RData/india_w1/wealth.RData")
rm(wealth)

SAGE_india_m_ds_w1 <- SAGE_india_ds_w1
SAGE_india_m_ds_w1$wealth <- car::recode(SAGE_india_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Russia 

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `russiaINDdata` | 
| **Categories** | `continuous` |
| **Description** |  |

```{r assign_russia,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.russiaINDdata',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local_russia,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_russia,   echo=TRUE}
SAGE_russia_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_russia_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_russia_ds_w1$wealth <- as.integer(SAGE_russia_ds_w1$wealth)
SAGE_russia_ds_w1$wealth <- labelled(SAGE_russia_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_russia,  echo=FALSE}
vari <- SAGE_russia_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_russia_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_russia_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_russia,  echo=FALSE}
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_russia_ds_w1
save(wealth, file = "../RData/russia_w1/wealth.RData")
rm(wealth)

SAGE_russia_m_ds_w1 <- SAGE_russia_ds_w1
SAGE_russia_m_ds_w1$wealth <- car::recode(SAGE_russia_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Mexico 

### Wave 1 

#### Study-specific variable description

| **Name** | `quintile_c`| 
|-|-|
| **Label** | `permanent income quintile` | 
| **Table name** | `southAfricaINDdata` | 
| **Categories** | `continuous` |
| **Description** |  |

```{r assign_Mexico,  echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_wealth','SAGE.mexicoINDdata',
                         variables=list('quintile_c'), missings = TRUE)
SAGE_wealth <- opal.execute(o,'SAGE_wealth')
```

```{r local_Mexico,  echo=FALSE}
vari <- SAGE_wealth$quintile_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_wealth, aes(x=factor(quintile_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_Mexico,   echo=TRUE}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_wealth$id)
SAGE_mexico_ds_w1$wealth <- car::recode(SAGE_wealth$quintile_c, "NA=999")
SAGE_mexico_ds_w1$wealth <- as.integer(SAGE_mexico_ds_w1$wealth)
SAGE_mexico_ds_w1$wealth <- labelled(SAGE_mexico_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_Mexico,  echo=FALSE}
vari <- SAGE_mexico_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_mexico_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico,  echo=FALSE}
BeforeH <- table(SAGE_wealth$quintile_c, useNA = 'ifany')
AfterH <- table(SAGE_mexico_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_Mexico,  echo=FALSE}
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
wealth <- SAGE_mexico_ds_w1
save(wealth, file = "../RData/mexico_w1/wealth.RData")
rm(wealth)

SAGE_mexico_m_ds_w1 <- SAGE_mexico_ds_w1
SAGE_mexico_m_ds_w1$wealth <- car::recode(SAGE_mexico_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation


The list of household assets refers to: sources and amount of household income; improved household expenditure on food,
goods and services, health care.
Do not have information yet on how this quintiles were created, we suppose it will be similar to the COURAGE calculation.


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```