---
title: "Day of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/dbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/dbirthDS.R')
```

# Data process

## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `birth date dd` |
| **Table name** | `southAfricaINDdata` |
| **Missings** | `-8 = don't know` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_dbirth','SAGE.southAfricaINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_SA_w1_dbirth <- opal.execute(o,'SAGE_SA_w1_dbirth')
```

```{r local1, echo=F}
vari <- SAGE_SA_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_SA_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1_dbirth$id)
SAGE_ds_SA_w1$dbirth <- car::recode(SAGE_SA_w1_dbirth$q1010_dd, "-8=998; NA=999")
SAGE_ds_SA_w1$dbirth <- labelled(SAGE_ds_SA_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SAGE_ds_SA_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_SA_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'SAGE_ds_SA_w1', SAGE_ds_SA_w1)
#opal.symbol_import(o,'SAGE_ds_SA_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_SA_w1
save(dbirth, file = "../RData/SA_w1/dbirth.RData")
rm(dbirth)

SAGE_SA_m_ds_w1 <- SAGE_ds_SA_w1
SAGE_SA_m_ds_w1$dbirth <- car::recode(SAGE_SA_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_SA_m_ds_w1', SAGE_SA_m_ds_w1)
#opal.symbol_import(o,'SAGE_SA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




## Ghana

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `dd` |
| **Table name** | `ghanaINDData` |
| **Missings** | `-8 = don't know` |
| **Description** |  |


```{r assign_ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_dbirth','SAGE.ghanaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_ghana_w1_dbirth <- opal.execute(o,'SAGE_ghana_w1_dbirth')
```

```{r local_ghana, echo=F}
vari <- SAGE_ghana_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`


**R script:**

```{r harmo_ghana}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1_dbirth$id)
SAGE_ds_ghana_w1$dbirth <- car::recode(SAGE_ghana_w1_dbirth$q1010_dd, "NA=999; -8=998")
SAGE_ds_ghana_w1$dbirth <- labelled(SAGE_ds_ghana_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vari <- SAGE_ds_ghana_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_ghana_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana, echo=F}
```





```{r importOPAL_ghana, echo=F}

#opal.assign.data(o, 'SAGE_ds_ghana_w1', SAGE_ds_ghana_w1)
#opal.symbol_import(o,'SAGE_ds_ghana_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_ghana_w1
save(dbirth, file = "../RData/ghana_w1/dbirth.RData")
rm(dbirth)

SAGE_ghana_m_ds_w1 <- SAGE_ds_ghana_w1
SAGE_ghana_m_ds_w1$dbirth <- car::recode(SAGE_ghana_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```





## China

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `dd` |
| **Table name** | `chinaINDData` |
| **Missings** | `-8 = don't know`<br/>`-6`<br/>`0`<br/>`NA` |
| **Description** |  |


```{r assign_china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_dbirth','SAGE.chinaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_china_w1_dbirth <- opal.execute(o,'SAGE_china_w1_dbirth')
```

```{r local_china, echo=F}
vari <- SAGE_china_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8,-6,0))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8,-6,0))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-6,0))$summary, caption = "Summary")
ggplot(SAGE_china_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8,-6,0))) + xlab("Day of birth") + ylab("Frequency")
```

There are values -6 and 0 that are going to be consider as missing and recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_china}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1_dbirth$id)
SAGE_ds_china_w1$dbirth <- car::recode(SAGE_china_w1_dbirth$q1010_dd, "c(NA, -6, 0)='999'; -8='998'")
SAGE_ds_china_w1$dbirth <- labelled(SAGE_ds_china_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vari <- SAGE_ds_china_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_china_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china, echo=F}
```





```{r importOPAL_china, echo=F}

#opal.assign.data(o, 'SAGE_ds_china_w1', SAGE_ds_china_w1)
#opal.symbol_import(o,'SAGE_ds_china_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_china_w1
save(dbirth, file = "../RData/china_w1/dbirth.RData")
rm(dbirth)

SAGE_china_m_ds_w1 <- SAGE_ds_china_w1
SAGE_china_m_ds_w1$dbirth <- car::recode(SAGE_china_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## India

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `DD` |
| **Table name** | `indiaINDData` |
| **Missings** | `-8 = don't know` |
| **Description** |  |


```{r assign_india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_dbirth','SAGE.indiaINDData',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_india_w1_dbirth <- opal.execute(o,'SAGE_india_w1_dbirth')
```

```{r local_india, echo=F}
vari <- SAGE_india_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_india_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_india}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1_dbirth$id)
SAGE_ds_india_w1$dbirth <- car::recode(SAGE_india_w1_dbirth$q1010_dd, "-8=998; NA=999")
SAGE_ds_india_w1$dbirth <- labelled(SAGE_ds_india_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vari <- SAGE_ds_india_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_india_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india, echo=F}
```





```{r importOPAL_india, echo=F}

#opal.assign.data(o, 'SAGE_ds_india_w1', SAGE_ds_india_w1)
#opal.symbol_import(o,'SAGE_ds_india_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_india_w1
save(dbirth, file = "../RData/india_w1/dbirth.RData")
rm(dbirth)

SAGE_india_m_ds_w1 <- SAGE_ds_india_w1
SAGE_india_m_ds_w1$dbirth <- car::recode(SAGE_india_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Russia

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `dd` |
| **Table name** | `russiaINDdata` |
| **Missings** | `-8 = don't know` |
| **Description** |  |


```{r assign_russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_dbirth','SAGE.russiaINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_russia_w1_dbirth <- opal.execute(o,'SAGE_russia_w1_dbirth')
```

```{r local_russia, echo=F}
vari <- SAGE_russia_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_russia_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_russia}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1_dbirth$id)
SAGE_ds_russia_w1$dbirth <- car::recode(SAGE_russia_w1_dbirth$q1010_dd, "-8='998'; NA='999'")
SAGE_ds_russia_w1$dbirth <- labelled(SAGE_ds_russia_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vari <- SAGE_ds_russia_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_russia_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia, echo=F}
```





```{r importOPAL_russia, echo=F}

#opal.assign.data(o, 'SAGE_ds_russia_w1', SAGE_ds_russia_w1)
#opal.symbol_import(o,'SAGE_ds_russia_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_russia_w1
save(dbirth, file = "../RData/russia_w1/dbirth.RData")
rm(dbirth)

SAGE_russia_m_ds_w1 <- SAGE_ds_russia_w1
SAGE_russia_m_ds_w1$dbirth <- car::recode(SAGE_russia_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_dd` |
|----------|------------|
| **Label** | `dd` |
| **Table name** | `mexicoINDdata` |
| **Missings** | `-8 = don't know` |
| **Description** |  |


```{r assign_Mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_dbirth','SAGE.mexicoINDdata',
                         variables=list('q1010_dd'), missings = TRUE)
SAGE_mexico_w1_dbirth <- opal.execute(o,'SAGE_mexico_w1_dbirth')
```

```{r local_Mexico, echo=F}
vari <- SAGE_mexico_w1_dbirth$q1010_dd
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_mexico_w1_dbirth, aes(q1010_dd)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_Mexico}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1_dbirth$id)
SAGE_ds_mexico_w1$dbirth <- car::recode(SAGE_mexico_w1_dbirth$q1010_dd, "-8=998; NA=999")
SAGE_ds_mexico_w1$dbirth <- labelled(SAGE_ds_mexico_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vari <- SAGE_ds_mexico_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_mexico_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
```





```{r importOPAL_Mexico, echo=F}

#opal.assign.data(o, 'SAGE_ds_mexico_w1', SAGE_ds_mexico_w1)
#opal.symbol_import(o,'SAGE_ds_mexico_w1', project='_Athlos_Harm_Dataset')
dbirth <- SAGE_ds_mexico_w1
save(dbirth, file = "../RData/mexico_w1/dbirth.RData")
rm(dbirth)

SAGE_mexico_m_ds_w1 <- SAGE_ds_mexico_w1
SAGE_mexico_m_ds_w1$dbirth <- car::recode(SAGE_mexico_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

SAGE.cw <- list(SA_w1 = "SA_w1", ghana_w1 = "ghana_w1", china_w1 = "china_w1", india_w1 = "india_w1", russia_w1 = "russia_w1", mexico_w1 = "mexico_w1")

# Consider only harmonised waves
l.hds <- lapply(SAGE.cw, function(wname) if(exists(paste0("SAGE_ds_",wname))){wname = get(paste0("SAGE_ds_",wname))})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

# Labelling of the tibbles and creating new tibbles with all missings recodified as NA

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("SAGE_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("SAGE_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],toupper(names(l.hds)))
kable(t.hds,caption=ds_label)



```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
