---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```



# Data process
## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yy` | `q1011`|`yintw`|
|----------|------------|--|--|
| **Label** | `yyyy` | `q1011: age in yyys`|`Year of interview`|
| **Table name** | `southAfricaINDdata` | `southAfricaINDdata` |`sage_sa_w1_hd`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1_ybirth','SAGE.southAfricaINDdata',  variables=list('q1010_yy','q1011'), missings = TRUE)
SAGE_SA_w1_ybirth <- opal.execute(o,'SAGE_SA_w1_ybirth')

opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_sa_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_SA_w1_ybirth <- left_join(SAGE_SA_w1_ybirth,SAGE_w1, by="id")

```

```{r local1, echo=F}
vari <- SAGE_SA_w1_ybirth$q1010_yy
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = NA)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_SA_w1_ybirth, aes(q1010_yy)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")

vbl <- SAGE_SA_w1_ybirth$q1011
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q1011")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_SA_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vbl <- SAGE_SA_w1_ybirth$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_SA_w1_ybirth, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `q1010_yy`, but the missing values have to be recoded as follows:

* `impute as yintw - age`
* `NA into 999`

**R script:**

```{r harmo1}

SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1_ybirth$id)
SAGE_ds_SA_w1$ybirth <- SAGE_SA_w1_ybirth$q1010_yy

SAGE_SA_w1_ybirth$yintw <- car::recode(SAGE_SA_w1_ybirth$yintw, "miss_values_vector=NA")
SAGE_ds_SA_w1$ybirth[is.na(SAGE_SA_w1_ybirth$q1010_yy)] <- SAGE_SA_w1_ybirth$yintw[is.na(SAGE_SA_w1_ybirth$q1010_yy)] - SAGE_SA_w1_ybirth$q1011[is.na(SAGE_SA_w1_ybirth$q1010_yy)]

SAGE_ds_SA_w1$ybirth <- car::recode(SAGE_ds_SA_w1$ybirth,"NA=999")
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SAGE_ds_SA_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_SA_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'SAGE_ds_SA_w1', SAGE_ds_SA_w1)
#opal.symbol_import(o,'SAGE_ds_SA_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_SA_w1
save(ybirth, file = "../RData/SA_w1/ybirth.RData")
rm(ybirth)

SAGE_SA_m_ds_w1 <- SAGE_ds_SA_w1
SAGE_SA_m_ds_w1$ybirth <- car::recode(SAGE_SA_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_SA_m_ds_w1', SAGE_SA_m_ds_w1)
#opal.symbol_import(o,'SAGE_SA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




## Ghana

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yyyy` |`q0407`|`yintw`|`q1011`|
|-----|-----|------|---|---|
| **Label** | `yyyy` | `age`|`Year of interview`| `q1011: age in yyys`| 
| **Table name** | `ghanaINDData` | `ghanaINDData` |`sage_ghana_w1_hd`| `ghanaINDData` |
| **Missings** | `-8 = dk`<br/>`NA` | `NA` |  | `-8 = dk`<br/>`NA` |
| **Description** |  |  |  |  |


```{r assign_ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_ybirth','SAGE.ghanaINDData',  variables=list('q1010_yyyy','q0407','q1011'), missings = TRUE)
SAGE_ghana_w1_ybirth <- opal.execute(o,'SAGE_ghana_w1_ybirth')

opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_ghana_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_ghana_w1_ybirth <- left_join(SAGE_ghana_w1_ybirth,SAGE_w1, by="id")

```

```{r local_ghana, echo=F}
vari <- SAGE_ghana_w1_ybirth$q1010_yyyy
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_ybirth, aes(q1010_yyyy)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Year of birth") + ylab("Frequency")

vbl <- SAGE_ghana_w1_ybirth$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_ybirth, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1_ybirth$q1011
vbl_miss <- c(-8)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q1011")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue", data =. %>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1_ybirth$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ghana_w1_ybirth, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `q1010_yyyy`, but the missing values have to be recoded as follows:

* `impute as yintw - age`
* `NA into 999`
* `-8 into 998`


**R script:**

```{r harmo_ghana}

SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1_ybirth$id)
SAGE_ds_ghana_w1$ybirth <- car::recode(SAGE_ghana_w1_ybirth$q1010_yyyy, "-8=998; NA=999")


SAGE_ghana_w1_ybirth$yintw <- car::recode(SAGE_ghana_w1_ybirth$yintw, "miss_values_vector=NA")

SAGE_ghana_w1_ybirth$q1011 <- car::recode(SAGE_ghana_w1_ybirth$q1011,"-8=NA")

SAGE_ds_ghana_w1$ybirth[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q1011))] <- SAGE_ghana_w1_ybirth$yintw[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q1011))] - SAGE_ghana_w1_ybirth$q1011[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q1011))]


SAGE_ds_ghana_w1$ybirth[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q0407))] <- SAGE_ghana_w1_ybirth$yintw[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q0407))] - SAGE_ghana_w1_ybirth$q0407[which(SAGE_ds_ghana_w1$ybirth %in% miss_values_vector & !is.na(SAGE_ghana_w1_ybirth$q0407))]


```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vari <- SAGE_ds_ghana_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_ghana_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana, echo=F}
```





```{r importOPAL_ghana, echo=F}

#opal.assign.data(o, 'SAGE_ds_ghana_w1', SAGE_ds_ghana_w1)
#opal.symbol_import(o,'SAGE_ds_ghana_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_ghana_w1
save(ybirth, file = "../RData/ghana_w1/ybirth.RData")
rm(ybirth)

SAGE_ghana_m_ds_w1 <- SAGE_ds_ghana_w1
SAGE_ghana_m_ds_w1$ybirth <- car::recode(SAGE_ghana_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```





## China

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yyyy` | `q1011`|`yintw`|
|----------|---|------|---|
| **Label** | `yyyy` | `q1011: age in yyys`|`Year of interview`|
| **Table name** | `chinaINDData` |`chinaINDData` |`sage_china_w1_hd`|
| **Missings** | `-8 = dk`<br/>`NA` | `NA` |  |
| **Description** |  |  |  |


```{r assign_china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_ybirth','SAGE.chinaINDData',  variables=list('q1010_yyyy','q1011'), missings = TRUE)
SAGE_china_w1_ybirth <- opal.execute(o,'SAGE_china_w1_ybirth')


opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_china_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_china_w1_ybirth <- left_join(SAGE_china_w1_ybirth,SAGE_w1, by="id")


```

```{r local_china, echo=F}

vari <- SAGE_china_w1_ybirth$q1010_yyyy
vbl_miss <- c(-8:1850,2009:19561)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(SAGE_china_w1_ybirth, aes(q1010_yyyy)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% vbl_miss)) + xlab("Year of birth") + ylab("Frequency")

vbl <- SAGE_china_w1_ybirth$q1011
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q1011")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_china_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1_ybirth$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_china_w1_ybirth, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `q1010_yyyy`, but the missing values have to be recoded as follows:

As the ages are from 18 to 102 and the interview took place between 2007 and 2010, the values of `q1010_yyyy` lowers than 1905 and higher than 1992 are going to be considered as missings and they are going to be recoded as 999.


* `impute as yintw - age`
* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_china}

SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1_ybirth$id)
SAGE_ds_china_w1$ybirth <- car::recode(SAGE_china_w1_ybirth$q1010_yyyy, "NA=999; -8=998; 0:1850=999; 2009:hi=999")

SAGE_china_w1_ybirth$yintw <- car::recode(SAGE_china_w1_ybirth$yintw, "miss_values_vector=NA")
SAGE_ds_china_w1$ybirth[which(SAGE_ds_china_w1$ybirth %in% miss_values_vector & !is.na(SAGE_china_w1_ybirth$q1011))] <- SAGE_china_w1_ybirth$yintw[which(SAGE_ds_china_w1$ybirth %in% miss_values_vector & !is.na(SAGE_china_w1_ybirth$q1011))] - SAGE_china_w1_ybirth$q1011[which(SAGE_ds_china_w1$ybirth %in% miss_values_vector & !is.na(SAGE_china_w1_ybirth$q1011))]


```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vari <- SAGE_ds_china_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_china_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china, echo=F}
```





```{r importOPAL_china, echo=F}

#opal.assign.data(o, 'SAGE_ds_china_w1', SAGE_ds_china_w1)
#opal.symbol_import(o,'SAGE_ds_china_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_china_w1
save(ybirth, file = "../RData/china_w1/ybirth.RData")
rm(ybirth)

SAGE_china_m_ds_w1 <- SAGE_ds_china_w1
SAGE_china_m_ds_w1$ybirth <- car::recode(SAGE_china_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## India

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yyyy` | `q1011`|`yintw`|
|-----|-----|------|----|--|
| **Label** | `YYYY` |`q1011: age in yyys`|`Year of interview`|
| **Table name** | `indiaINDData` |`indiaINDData` |`sage_india_w1_hd`|
| **Missings** | `-8 = DK`<br/>`NA` |  |  |
| **Description** |  |  |  |


```{r assign_india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_ybirth','SAGE.indiaINDData',   variables=list('q1010_yyyy','q1011'), missings = TRUE)
SAGE_india_w1_ybirth <- opal.execute(o,'SAGE_india_w1_ybirth')


opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_india_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_india_w1_ybirth <- left_join(SAGE_india_w1_ybirth,SAGE_w1, by="id")

```

```{r local_india, echo=F}
vari <- SAGE_india_w1_ybirth$q1010_yyyy
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_india_w1_ybirth, aes(q1010_yyyy)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Year of birth") + ylab("Frequency")

vbl <- SAGE_india_w1_ybirth$q1011
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q1011")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_india_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vbl <- SAGE_india_w1_ybirth$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_india_w1_ybirth, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `q1010_yyyy`, but the missing values have to be recoded as follows:

* `impute as yintw - age`
* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_india}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1_ybirth$id)
SAGE_ds_india_w1$ybirth <- car::recode(SAGE_india_w1_ybirth$q1010_yyyy, "-8=998; NA=999")


SAGE_india_w1_ybirth$yintw <- car::recode(SAGE_india_w1_ybirth$yintw, "miss_values_vector=NA")
SAGE_ds_india_w1$ybirth[which(SAGE_ds_india_w1$ybirth %in% miss_values_vector & !is.na(SAGE_india_w1_ybirth$q1011))] <- SAGE_india_w1_ybirth$yintw[which(SAGE_ds_india_w1$ybirth %in% miss_values_vector & !is.na(SAGE_india_w1_ybirth$q1011))] - SAGE_india_w1_ybirth$q1011[which(SAGE_ds_india_w1$ybirth %in% miss_values_vector & !is.na(SAGE_india_w1_ybirth$q1011))]

```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vari <- SAGE_ds_india_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_india_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india, echo=F}
```





```{r importOPAL_india, echo=F}

#opal.assign.data(o, 'SAGE_ds_india_w1', SAGE_ds_india_w1)
#opal.symbol_import(o,'SAGE_ds_india_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_india_w1
save(ybirth, file = "../RData/india_w1/ybirth.RData")
rm(ybirth)

SAGE_india_m_ds_w1 <- SAGE_ds_india_w1
SAGE_india_m_ds_w1$ybirth <- car::recode(SAGE_india_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Russia

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yyyy` | `q0407`|`yintw`|`q1011`|
|------|----|---|------|---|
| **Label** | `yyyy` | `age`|`Year of interview`|`q1011: age in yyys`|
| **Table name** | `russiaINDdata` | `russiaINDdata` |`sage_russia_w1_hd`|`russiaINDdata` |
| **Missings** | `-8 = dk`<br/>`NA` | `NA` |  | `NA` |
| **Description** |  |  |  |  |


```{r assign_russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_ybirth','SAGE.russiaINDdata',  variables=list('q1010_yyyy','q0407','q1011'), missings = TRUE)
SAGE_russia_w1_ybirth <- opal.execute(o,'SAGE_russia_w1_ybirth')


opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_russia_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_russia_w1_ybirth <- left_join(SAGE_russia_w1_ybirth,SAGE_w1, by="id")

```

```{r local_russia, echo=F}
vari <- SAGE_russia_w1_ybirth$q1010_yyyy
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_russia_w1_ybirth, aes(q1010_yyyy)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% c(-8))) + xlab("Year of birth") + ylab("Frequency")

vbl <- SAGE_russia_w1_ybirth$q1011
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q1011")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_russia_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vbl <- SAGE_russia_w1_ybirth$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_russia_w1_ybirth, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vbl <- SAGE_russia_w1_ybirth$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_russia_w1_ybirth, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

kable(frq(is.na((SAGE_russia_w1_ybirth %>% filter(is.na(q1010_yyyy)))$q1011)), caption = 'All missing values of q1010_yyyy (year of birth) are also missing values of q1011 (age)')

```

#### Harmonisation algorithm

Individuals cannot have been born after 1990 according to the years of interview, since they must be aged 18 or older. Therefore, such years of birth will be recoded as missing.
The harmonized variable is the same than the study-specific variable `q1010_yyyy`, but the missing values have to be recoded as follows:

* `impute as yintw - age`
* `NA into 999`
* `-8 into 998`

**R script:**

```{r harmo_russia}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1_ybirth$id)
SAGE_ds_russia_w1$ybirth <- car::recode(SAGE_russia_w1_ybirth$q1010_yyyy, "-8=998; NA=999; 1990:hi=999")

SAGE_russia_w1_ybirth$yintw <- car::recode(SAGE_russia_w1_ybirth$yintw, "miss_values_vector=NA")

SAGE_ds_russia_w1$ybirth[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q1011))] <- SAGE_russia_w1_ybirth$yintw[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q1011))] - SAGE_russia_w1_ybirth$q1011[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q1011))]

SAGE_ds_russia_w1$ybirth[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q0407))] <- SAGE_russia_w1_ybirth$yintw[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q0407))] - SAGE_russia_w1_ybirth$q0407[which(SAGE_ds_russia_w1$ybirth %in% miss_values_vector & !is.na(SAGE_russia_w1_ybirth$q0407))]

```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vari <- SAGE_ds_russia_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_russia_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia, echo=F}
```





```{r importOPAL_russia, echo=F}

#opal.assign.data(o, 'SAGE_ds_russia_w1', SAGE_ds_russia_w1)
#opal.symbol_import(o,'SAGE_ds_russia_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_russia_w1
save(ybirth, file = "../RData/russia_w1/ybirth.RData")
rm(ybirth)

SAGE_russia_m_ds_w1 <- SAGE_ds_russia_w1
SAGE_russia_m_ds_w1$ybirth <- car::recode(SAGE_russia_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `q1010_yy` | `q1011`|`yintw`|
|----------|-|-----|------|
| **Label** | `yyyy` | `q1011: age in yyys`|`Year of interview`|
| **Table name** | `mexicoINDdata` | `mexicoINDdata` |`sage_mexico_w1_hd`|
| **Missings** | `NA` | `-8 = dk`<br/>`NA` |  |
| **Description** |  |  |  |


```{r assign_Mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_ybirth','SAGE.mexicoINDdata',
                         variables=list('q1010_yy','q1011'), missings = TRUE)
SAGE_mexico_w1_ybirth <- opal.execute(o,'SAGE_mexico_w1_ybirth')


opal.assign.table.tibble(o, 'SAGE_w1','SAGE_HD.sage_mexico_w1_hd', variables=list('yintw'), missings = TRUE)
SAGE_w1 <- opal.execute(o,'SAGE_w1')

SAGE_mexico_w1_ybirth <- left_join(SAGE_mexico_w1_ybirth,SAGE_w1, by="id")

```

```{r local_Mexico, echo=F}
vari <- SAGE_mexico_w1_ybirth$q1010_yy
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Values")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_mexico_w1_ybirth, aes(q1010_yy)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")

vari <- SAGE_mexico_w1_ybirth$q1011
vbl_miss <- c(-8)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = "q1011")
kable(Continuous_summary(vari, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(SAGE_mexico_w1_ybirth, aes(q1011)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab(label(vari)) + ylab("Frequency")

vari <- SAGE_mexico_w1_ybirth$yintw
kable(Categorical_summary(var = vari, missing_values = NA)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1_ybirth, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
Individuals cannot have been born after 1992 according to the years of interview, since they must be aged 18 or older. Therefore, such years of birth will be recoded as missing.
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_Mexico}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1_ybirth$id)
SAGE_ds_mexico_w1$ybirth <- car::recode(SAGE_mexico_w1_ybirth$q1010_yy, "NA=999;1992:hi=999")

SAGE_ds_mexico_w1$ybirth[which(is.na(SAGE_mexico_w1_ybirth$q1010_yy) & SAGE_mexico_w1_ybirth$q1011!=-8)] <- SAGE_mexico_w1_ybirth$yintw[which(is.na(SAGE_mexico_w1_ybirth$q1010_yy) & SAGE_mexico_w1_ybirth$q1011!=-8)] - SAGE_mexico_w1_ybirth$q1011[which(is.na(SAGE_mexico_w1_ybirth$q1010_yy) & SAGE_mexico_w1_ybirth$q1011!=-8)]

SAGE_ds_mexico_w1$ybirth <- car::recode(SAGE_ds_mexico_w1$ybirth,"NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vari <- SAGE_ds_mexico_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SAGE_ds_mexico_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue",data = . %>% filter(!vari %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
```





```{r importOPAL_Mexico, echo=F}

#opal.assign.data(o, 'SAGE_ds_mexico_w1', SAGE_ds_mexico_w1)
#opal.symbol_import(o,'SAGE_ds_mexico_w1', project='_Athlos_Harm_Dataset')
ybirth <- SAGE_ds_mexico_w1
save(ybirth, file = "../RData/mexico_w1/ybirth.RData")
rm(ybirth)

SAGE_mexico_m_ds_w1 <- SAGE_ds_mexico_w1
SAGE_mexico_m_ds_w1$ybirth <- car::recode(SAGE_mexico_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
