---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process

## South Africa

### Wave 1 

#### Study-specific variable description



| **Name** | `q0407`|`ybirth`| `mbirth` | `mintw` | `yintw` |
|-|-|-|-|-|-|
| **Label** | `age`|  `Year of birth` | `Month of birth` | `Month of interview` | `Year of interview` |
| **Table name** | `southAfricaINDdata` |`sage_SA_w1_hd`\* | `sage_SA_w1_hd`\* | `sage_SA_w1_hd`\* | `sage_SA_w1_hd`\* |
| **Missings** | `NA` | `999 = Missing`   |  `999 = Missing` |  `999 = Missing` |    |
| **Description** |  |  |  |  |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',
                         variables=list('q0407'), missings = TRUE)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

load("../RData/SA_w1/mbirth.RData")
load("../RData/SA_w1/ybirth.RData")
load("../RData/SA_w1/mintw.RData")
load("../RData/SA_w1/yintw.RData")

SAGE_SA_w1 <- left_join(SAGE_SA_w1, mbirth, by="id")
SAGE_SA_w1 <- left_join(SAGE_SA_w1, ybirth, by="id")
SAGE_SA_w1 <- left_join(SAGE_SA_w1,yintw, by="id")
SAGE_SA_w1 <- left_join(SAGE_SA_w1,mintw, by="id")
rm(mbirth)
rm(ybirth)
rm(mintw)
rm(yintw)

```



\* These tables are not extracted from the database SAGE, but from ATHLOS. They contain already harmonised variables.




```{r local1, echo=F}
vbl <- SAGE_SA_w1$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_SA_w1, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$age <- car::recode(SAGE_SA_w1$q0407, "NA=999")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SAGE_SA_w1$age <- comp_age(y_birth=SAGE_SA_w1$ybirth , m_birth=SAGE_SA_w1$mbirth ,
         y_int=SAGE_SA_w1$yintw , m_int=SAGE_SA_w1$mintw , miss=miss_values_vector)

SAGE_ds_SA_w1$age[which(SAGE_ds_SA_w1$age %in% miss_values_vector & !SAGE_SA_w1$age %in% miss_values_vector)] <- SAGE_SA_w1$age[which(SAGE_ds_SA_w1$age %in% miss_values_vector & !SAGE_SA_w1$age %in% miss_values_vector)]

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- SAGE_ds_SA_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_SA_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

SAGE_SA_w1 <- SAGE_SA_w1[,1:2]
load(paste0(datafolder,"SA_w1/ybirth",".RData"))
load(paste0(datafolder,"SA_w1/yintw",".RData"))
SAGE_SA_w1 <- left_join(SAGE_SA_w1,yintw, by="id")
SAGE_SA_w1 <- left_join(SAGE_SA_w1,ybirth, by="id")
SAGE_SA_w1$ybirth <- car::recode(SAGE_SA_w1$ybirth, "miss_values_vector=NA")
SAGE_SA_w1$yintw <- car::recode(SAGE_SA_w1$yintw, "miss_values_vector=NA")
SAGE_SA_w1$cage <- SAGE_SA_w1$yintw-SAGE_SA_w1$ybirth
SAGE_SA_w1$diff <- abs(SAGE_SA_w1$q0407 - SAGE_SA_w1$cage)
SAGE_SA_w1 <- remove_val_labels(SAGE_SA_w1)
kable(frq(SAGE_SA_w1$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
SAstr <- paste("The",length(SAGE_SA_w1$diff[which(SAGE_SA_w1$diff>2)]),"individuals with difference greater than 2")
kable(SAGE_SA_w1[which(SAGE_SA_w1$diff>2),], align = 'c', caption = SAstr)

```








## Ghana

### Wave 1 

#### Study-specific variable description



| **Name** | `q0407`|
|-|-|
| **Label** | `age`|
| **Table name** | `ghanaINDData` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign_ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',
                         variables=list('q0407'), missings = TRUE)
```

```{r local_ghana, echo=F}
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')
vbl <- SAGE_ghana_w1$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_ghana_w1, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_ghana}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$age <- car::recode(SAGE_ghana_w1$q0407, "NA=999")
SAGE_ds_ghana_w1$age <- labelled(SAGE_ds_ghana_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vbl <- SAGE_ds_ghana_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_ghana_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ghana, echo=F}


SAGE_ghana_w1 <- SAGE_ghana_w1[,1:2]
load(paste0(datafolder,"ghana_w1/ybirth",".RData"))
load(paste0(datafolder,"ghana_w1/yintw",".RData"))
SAGE_ghana_w1 <- left_join(SAGE_ghana_w1,yintw, by="id")
SAGE_ghana_w1 <- left_join(SAGE_ghana_w1,ybirth, by="id")
SAGE_ghana_w1$ybirth <- car::recode(SAGE_ghana_w1$ybirth, "miss_values_vector=NA")
SAGE_ghana_w1$yintw <- car::recode(SAGE_ghana_w1$yintw, "miss_values_vector=NA")
SAGE_ghana_w1$cage <- SAGE_ghana_w1$yintw-SAGE_ghana_w1$ybirth
SAGE_ghana_w1$diff <- abs(SAGE_ghana_w1$q0407 - SAGE_ghana_w1$cage)
SAGE_ghana_w1 <- remove_val_labels(SAGE_ghana_w1)
kable(frq(SAGE_ghana_w1$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
SAstr <- paste("The",length(SAGE_ghana_w1$diff[which(SAGE_ghana_w1$diff>2)]),"individuals with difference greater than 2")
kable(SAGE_ghana_w1[which(SAGE_ghana_w1$diff>2),], align = 'c', caption = SAstr)

```








## China

### Wave 1 

#### Study-specific variable description



| **Name** | `q0407`| `ybirth`| `mbirth` | `mintw` | `yintw` |
|-|-|-|-|-|-|
| **Label** | `age`| `Year of birth` | `Month of birth` | `Month of interview` | `Year of interview` |
| **Table name** | `chinaINDData` |`sage_china_w1_hd`\* | `sage_china_w1_hd`\* | `sage_china_w1_hd`\* | `sage_china_w1_hd`\* |
| **Missings** | `NA` | `999 = Missing`   |  `999 = Missing` |  `999 = Missing` |    |
| **Description** |  |  |  |  |  |


\* These tables are not extracted from the database SAGE, but from ATHLOS. They contain already harmonised variables.

```{r assign_china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',
                         variables=list('q0407'), missings = TRUE)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')



load("../RData/china_w1/mbirth.RData")
load("../RData/china_w1/ybirth.RData")
load("../RData/china_w1/mintw.RData")
load("../RData/china_w1/yintw.RData")

SAGE_china_w1 <- left_join(SAGE_china_w1,mbirth, by="id")
SAGE_china_w1 <- left_join(SAGE_china_w1,ybirth, by="id")
SAGE_china_w1 <- left_join(SAGE_china_w1,yintw, by="id")
SAGE_china_w1 <- left_join(SAGE_china_w1,mintw, by="id")
rm(mbirth)
rm(ybirth)
rm(mintw)
rm(yintw)

```

```{r local_china, echo=F}
vbl <- SAGE_china_w1$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_china_w1, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

There are values lower than 18, the limit age, therefore these individuals are going to be considered as missing and they will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_china}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$age <- car::recode(SAGE_china_w1$q0407, "NA=999; lo:17=999")

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

SAGE_china_w1$age <- comp_age(y_birth=SAGE_china_w1$ybirth , m_birth=SAGE_china_w1$mbirth ,
         y_int=SAGE_china_w1$yintw , m_int=SAGE_china_w1$mintw , miss=miss_values_vector)

SAGE_ds_china_w1$age[which(SAGE_ds_china_w1$age %in% miss_values_vector & !SAGE_china_w1$age %in% miss_values_vector)] <- SAGE_china_w1$age[which(SAGE_ds_china_w1$age %in% miss_values_vector & !SAGE_china_w1$age %in% miss_values_vector)]
```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vbl <- SAGE_ds_china_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_china_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_china, echo=F,results='asis'}
cat("The difference between the resulting and the initial missing values are the values lower than 18:", sum(SAGE_ds_china_w1$age %in% miss_values_vector)-sum(is.na(SAGE_china_w1$q0407)),"=",sum(SAGE_china_w1$q0407 %in% 0:17))


SAGE_china_w1 <- SAGE_china_w1[,1:2]
load(paste0(datafolder,"china_w1/ybirth",".RData"))
load(paste0(datafolder,"china_w1/yintw",".RData"))
SAGE_china_w1 <- left_join(SAGE_china_w1,yintw, by="id")
SAGE_china_w1 <- left_join(SAGE_china_w1,ybirth, by="id")
SAGE_china_w1$ybirth <- car::recode(SAGE_china_w1$ybirth, "miss_values_vector=NA")
SAGE_china_w1$yintw <- car::recode(SAGE_china_w1$yintw, "miss_values_vector=NA")
SAGE_china_w1$cage <- SAGE_china_w1$yintw-SAGE_china_w1$ybirth
SAGE_china_w1$diff <- abs(SAGE_china_w1$q0407 - SAGE_china_w1$cage)
SAGE_china_w1 <- remove_val_labels(SAGE_china_w1)
kable(frq(SAGE_china_w1$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
SAstr <- paste("The",length(SAGE_china_w1$diff[which(SAGE_china_w1$diff>2)]),"individuals with difference greater than 2")
kable(SAGE_china_w1[which(SAGE_china_w1$diff>2),], align = 'c', caption = SAstr)

```










## India

### Wave 1 

#### Study-specific variable description



| **Name** | `q0407`|
|-|-|
| **Label** | `age`|
| **Table name** | `indiaINDData` |
| **Description** |  |



```{r assign_india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',
                         variables=list('q0407'), missings = TRUE)
```

```{r local_india, echo=F}
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')
vbl <- SAGE_india_w1$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_india_w1, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_india}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$age <- car::recode(SAGE_india_w1$q0407, "NA=999")
SAGE_ds_india_w1$age <- labelled(SAGE_ds_india_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vbl <- SAGE_ds_india_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_india_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_india, echo=F}


SAGE_india_w1 <- SAGE_india_w1[,1:2]
load(paste0(datafolder,"india_w1/ybirth",".RData"))
load(paste0(datafolder,"india_w1/yintw",".RData"))
SAGE_india_w1 <- left_join(SAGE_india_w1,yintw, by="id")
SAGE_india_w1 <- left_join(SAGE_india_w1,ybirth, by="id")
SAGE_india_w1$ybirth <- car::recode(SAGE_india_w1$ybirth, "miss_values_vector=NA")
SAGE_india_w1$yintw <- car::recode(SAGE_india_w1$yintw, "miss_values_vector=NA")
SAGE_india_w1$cage <- SAGE_india_w1$yintw-SAGE_india_w1$ybirth
SAGE_india_w1$diff <- abs(SAGE_india_w1$q0407 - SAGE_india_w1$cage)
SAGE_india_w1 <- remove_val_labels(SAGE_india_w1)
kable(frq(SAGE_india_w1$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
SAstr <- paste("The",length(SAGE_india_w1$diff[which(SAGE_india_w1$diff>2)]),"individuals with difference greater than 2")
kable(SAGE_india_w1[which(SAGE_india_w1$diff>2),], align = 'c', caption = SAstr)

```








## Russia

### Wave 1 

#### Study-specific variable description



| **Name** | `q0407`|
|-|-|
| **Label** | `age`|
| **Table name** | `russiaINDdata` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign_russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',
                         variables=list('q0407'), missings = TRUE)
```

```{r local_russia, echo=F}
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')
vbl <- SAGE_russia_w1$q0407
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q0407")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_russia_w1, aes(q0407)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_russia}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$age <- car::recode(SAGE_russia_w1$q0407, "NA=999")
SAGE_ds_russia_w1$age <- labelled(SAGE_ds_russia_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vbl <- SAGE_ds_russia_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_russia_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_russia, echo=F}


SAGE_russia_w1 <- SAGE_russia_w1[,1:2]
load(paste0(datafolder,"russia_w1/ybirth",".RData"))
load(paste0(datafolder,"russia_w1/yintw",".RData"))
SAGE_russia_w1 <- left_join(SAGE_russia_w1,yintw, by="id")
SAGE_russia_w1 <- left_join(SAGE_russia_w1,ybirth, by="id")
SAGE_russia_w1$ybirth <- car::recode(SAGE_russia_w1$ybirth, "miss_values_vector=NA")
SAGE_russia_w1$yintw <- car::recode(SAGE_russia_w1$yintw, "miss_values_vector=NA")
SAGE_russia_w1$cage <- SAGE_russia_w1$yintw-SAGE_russia_w1$ybirth
SAGE_russia_w1$diff <- abs(SAGE_russia_w1$q0407 - SAGE_russia_w1$cage)
SAGE_russia_w1 <- remove_val_labels(SAGE_russia_w1)
kable(frq(SAGE_russia_w1$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
SAstr <- paste("The",length(SAGE_russia_w1$diff[which(SAGE_russia_w1$diff>2)]),"individuals with difference greater than 2")
kable(SAGE_russia_w1[which(SAGE_russia_w1$diff>2),], align = 'c', caption = SAstr)

```








## Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `ybirth`| `mbirth` | `mintw` | `yintw` |
|-|-|-|-|-|
| **Label** |  `Year of birth` | `Month of birth` | `Month of interview` | `Year of interview` |
| **Table name** |`sage_mexico_w1_hd`\* | `sage_mexico_w1_hd`\* | `sage_mexico_w1_hd`\* | `sage_mexico_w1_hd`\* |
| **Missings** | `999 = Missing`   |  `999 = Missing` |  `999 = Missing` |    |
| **Description** |  |  |  |  |

\* These tables are not extracted from the database SAGE, but from ATHLOS. They contain already harmonised variables.

```{r assign_Mexico, echo=F}
load("../RData/mexico_w1/mbirth.RData")
load("../RData/mexico_w1/ybirth.RData")
load("../RData/mexico_w1/mintw.RData")
load("../RData/mexico_w1/yintw.RData")

SAGE_mexico_w1 <- left_join(mbirth,ybirth, by="id")
SAGE_mexico_w1 <- left_join(SAGE_mexico_w1,yintw, by="id")
SAGE_mexico_w1 <- left_join(SAGE_mexico_w1,mintw, by="id")
rm(mbirth)
rm(ybirth)
rm(mintw)
rm(yintw)

```



```{r local_Mexico, echo=F}

vbl <- SAGE_mexico_w1$ybirth
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "ybirth")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(SAGE_mexico_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("year of birth") + ylab("Frequency")

vbl <- SAGE_mexico_w1$mbirth
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = "mbirth")
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Summary")
ggplot(SAGE_mexico_w1, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of birth") + ylab("Frequency")

vbl <- SAGE_mexico_w1$mintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Summary")
ggplot(SAGE_mexico_w1, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of interview") + ylab("Frequency")

vbl <- SAGE_mexico_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Summary")
ggplot(SAGE_mexico_w1, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab("year of interview") + ylab("Frequency")


```

#### Harmonisation algorithm
Since all the values of the study-specific variable for age are missing data, to compute the harmonized variable it has to be applied the following formula: 

* `date of interview - date of birth`

and recode the missings as follows:

* `NA into 999`

**R script:**

```{r harmo_Mexico}
#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- y_int[m_int<m_birth]-y_birth[m_int<m_birth]-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  age[mis!=0] <- mis[mis!=0]
  
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)

SAGE_ds_mexico_w1$age <- comp_age(y_birth=SAGE_mexico_w1$ybirth , m_birth=SAGE_mexico_w1$mbirth ,
         y_int=SAGE_mexico_w1$yintw , m_int=SAGE_mexico_w1$mintw , miss=miss_values_vector)



```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vbl <- SAGE_ds_mexico_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
 ggplot(SAGE_ds_mexico_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("age") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation

* The data of study-specific variable `q0407` is all missing for the Mexico cohort.
* Incompatible data is specified at each validation.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
