---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```


## South Africa

### Wave 1 

#### Study-specific variable description

 
| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`southAfricaINDdata`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_SA_w1_sex','SAGE.southAfricaINDdata',
                         variables=list('q1009'), missings = TRUE)
SAGE_SA_w1_sex <- opal.execute(o,'SAGE_SA_w1_sex')
```

```{r local1, echo=FALSE}
vari <- SAGE_SA_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_SA_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo1, echo=TRUE}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1_sex$id)
SAGE_ds_SA_w1$sex <- car::recode(SAGE_SA_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_SA_w1$sex <- labelled(SAGE_ds_SA_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- SAGE_ds_SA_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(SAGE_ds_SA_w1$sex)
BeforeH <- c(table(SAGE_SA_w1_sex$q1009)[c(2,1)], sum(is.na(SAGE_SA_w1_sex$q1009)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```






## Ghana 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`ghanaINDData`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ghana, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_sex','SAGE.ghanaINDData',
                         variables=list('q1009'), missings = TRUE)
SAGE_ghana_w1_sex <- opal.execute(o,'SAGE_ghana_w1_sex')
```

```{r local_ghana, echo=FALSE}
vari <- SAGE_ghana_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_ghana_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo_ghana, echo=TRUE}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1_sex$id)
SAGE_ds_ghana_w1$sex <- car::recode(SAGE_ghana_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_ghana_w1$sex <- labelled(SAGE_ds_ghana_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ghana, echo=FALSE}
vari <- SAGE_ds_ghana_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana, echo=FALSE}
AfterH <- table(SAGE_ds_ghana_w1$sex)
BeforeH <- c(table(SAGE_ghana_w1_sex$q1009)[c(2,1)], sum(is.na(SAGE_ghana_w1_sex$q1009)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```








## China 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`chinaINDData`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_china, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_china_w1_sex','SAGE.chinaINDData',
                         variables=list('q1009'), missings = TRUE)
SAGE_china_w1_sex <- opal.execute(o,'SAGE_china_w1_sex')
```

```{r local_china, echo=FALSE}
vari <- SAGE_china_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo_china, echo=TRUE}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1_sex$id)
SAGE_ds_china_w1$sex <- car::recode(SAGE_china_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_china_w1$sex <- labelled(SAGE_ds_china_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_china, echo=FALSE}
vari <- SAGE_ds_china_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china, echo=FALSE}
AfterH <- table(SAGE_ds_china_w1$sex)
BeforeH <- c(table(SAGE_china_w1_sex$q1009)[c(2,1)], sum(is.na(SAGE_china_w1_sex$q1009)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```








## India 

### Wave 1 

#### Study-specific variable description

| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`indiaINDData`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |




```{r assign_india, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_india_w1_sex','SAGE.indiaINDData',
                         variables=list('q1009'), missings = TRUE)
SAGE_india_w1_sex <- opal.execute(o,'SAGE_india_w1_sex')
```

```{r local_india, echo=FALSE}
vari <- SAGE_india_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_india_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo_india, echo=TRUE}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1_sex$id)
SAGE_ds_india_w1$sex <- car::recode(SAGE_india_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_india_w1$sex <- labelled(SAGE_ds_india_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_india, echo=FALSE}
vari <- SAGE_ds_india_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india, echo=FALSE}
AfterH <- table(SAGE_ds_india_w1$sex)
BeforeH <- table(SAGE_india_w1_sex$q1009)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```









## Russia 

### Wave 1 

#### Study-specific variable description

| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`russiaINDdata`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |




```{r assign_russia, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_russia_w1_sex','SAGE.russiaINDdata',
                         variables=list('q1009'), missings = TRUE)
SAGE_russia_w1_sex <- opal.execute(o,'SAGE_russia_w1_sex')
```

```{r local_russia, echo=FALSE}
vari <- SAGE_russia_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_russia_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo_russia, echo=TRUE}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1_sex$id)
SAGE_ds_russia_w1$sex <- car::recode(SAGE_russia_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_russia_w1$sex <- labelled(SAGE_ds_russia_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_russia, echo=FALSE}
vari <- SAGE_ds_russia_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia, echo=FALSE}
AfterH <- table(SAGE_ds_russia_w1$sex)
BeforeH <- c(table(SAGE_russia_w1_sex$q1009)[c(2,1)], sum(is.na(SAGE_russia_w1_sex$q1009)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```








## Mexico 

### Wave 1 

#### Study-specific variable description

| **Name** | `q1009`|
|-|-|
| **Label** | `sex`|
| **Table name** |`mexicoINDdata`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |




```{r assign_Mexico, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_sex','SAGE.mexicoINDdata',
                         variables=list('q1009'), missings = TRUE)
SAGE_mexico_w1_sex <- opal.execute(o,'SAGE_mexico_w1_sex')
```

```{r local_Mexico, echo=FALSE}
vari <- SAGE_mexico_w1_sex$q1009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1_sex, aes(x=factor(q1009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo_Mexico, echo=TRUE}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1_sex$id)
SAGE_ds_mexico_w1$sex <- car::recode(SAGE_mexico_w1_sex$q1009, "2=0; NA=999")
SAGE_ds_mexico_w1$sex <- labelled(SAGE_ds_mexico_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_Mexico, echo=FALSE}
vari <- SAGE_ds_mexico_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico, echo=FALSE}
AfterH <- table(SAGE_ds_mexico_w1$sex)
BeforeH <- c(table(SAGE_mexico_w1_sex$q1009)[c(2,1)], sum(is.na(SAGE_mexico_w1_sex$q1009)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}
# All study waves and populations with abbreviated and descriptive names
sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))
# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))
if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}
m.hds <- list()
lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)
if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}
```


# Quality estimation
No comments.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```