---
title: "Residence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `residence`
* Variable label: `Current residence`
* Variable description: `Current residence`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Community living
1        | Institutions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Current residence"
```

# Data process


## South Africa

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`
 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_resi','SAGE.southAfricaINDdata',
                         variables=list('q0414'), missings = TRUE)
```

```{r local1, echo=F}
SAGE_SA_w1_resi <- opal.execute(o,'SAGE_SA_w1_resi')
vari <- SAGE_SA_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_SA_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_resi$id)
SAGE_SA_ds_w1$residence <- car::recode(SAGE_SA_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_SA_ds_w1$residence <- labelled(SAGE_SA_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SAGE_SA_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- c(table(SAGE_SA_w1_resi$q0414), sum(is.na(SAGE_SA_w1_resi$q0414)))[c(2,1,3,4)]
AfterH <- table(SAGE_SA_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "8->998", "NA->999")
kable(C)
```





```{r importOPAL1, echo=F}
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_SA_ds_w1
save(residence, file = "../RData/SA_w1/residence.RData")
rm(residence)

SAGE_SA_m_ds_w1 <- SAGE_SA_ds_w1
SAGE_SA_m_ds_w1$residence <- car::recode(SAGE_SA_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_SA_m_ds_w1', SAGE_SA_m_ds_w1)
#opal.symbol_import(o,'SAGE_SA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




## Ghana

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`

```{r assign_ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_resi','SAGE.ghanaINDData',
                         variables=list('q0414'), missings = TRUE)
```

```{r local_ghana, echo=F}
SAGE_ghana_w1_resi <- opal.execute(o,'SAGE_ghana_w1_resi')
vari <- SAGE_ghana_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_ghana_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo_ghana}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_resi$id)
SAGE_ghana_ds_w1$residence <- car::recode(SAGE_ghana_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_ghana_ds_w1$residence <- labelled(SAGE_ghana_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana, echo=F}
vari <- SAGE_ghana_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ghana, echo=F}
BeforeH <- c(table(SAGE_ghana_w1_resi$q0414), sum(is.na(SAGE_ghana_w1_resi$q0414)))[c(2,1,3,4)]
AfterH <- table(SAGE_ghana_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "8->998", "NA->999")
kable(C)
```





```{r importOPAL_ghana, echo=F}
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_ghana_ds_w1
save(residence, file = "../RData/ghana_w1/residence.RData")
rm(residence)

SAGE_ghana_m_ds_w1 <- SAGE_ghana_ds_w1
SAGE_ghana_m_ds_w1$residence <- car::recode(SAGE_ghana_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_ghana_m_ds_w1', SAGE_ghana_m_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_m_ds_w1', project='_Athlos_Harm_Dataset')
```





## China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`

```{r assign_china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_resi','SAGE.chinaINDData',
                         variables=list('q0414'), missings = TRUE)
```

```{r local_china, echo=F}
SAGE_china_w1_resi <- opal.execute(o,'SAGE_china_w1_resi')
vari <- SAGE_china_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_china_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo_china}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_resi$id)
SAGE_china_ds_w1$residence <- car::recode(SAGE_china_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_china_ds_w1$residence <- labelled(SAGE_china_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china, echo=F}
vari <- SAGE_china_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_china, echo=F}
BeforeH <- c(table(SAGE_china_w1_resi$q0414), sum(is.na(SAGE_china_w1_resi$q0414)))[c(2,1,3)]
AfterH <- table(SAGE_china_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```





```{r importOPAL_china, echo=F}
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_china_ds_w1
save(residence, file = "../RData/china_w1/residence.RData")
rm(residence)

SAGE_china_m_ds_w1 <- SAGE_china_ds_w1
SAGE_china_m_ds_w1$residence <- car::recode(SAGE_china_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_china_m_ds_w1', SAGE_china_m_ds_w1)
#opal.symbol_import(o,'SAGE_china_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`

```{r assign_india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_resi','SAGE.indiaINDData',
                         variables=list('q0414'), missings = TRUE)
```

```{r local_india, echo=F}
SAGE_india_w1_resi <- opal.execute(o,'SAGE_india_w1_resi')
vari <- SAGE_india_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_india_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo_india}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_resi$id)
SAGE_india_ds_w1$residence <- car::recode(SAGE_india_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_india_ds_w1$residence <- labelled(SAGE_india_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india, echo=F}
vari <- SAGE_india_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india, echo=F}
BeforeH <- c(table(SAGE_india_w1_resi$q0414), sum(is.na(SAGE_india_w1_resi$q0414)))[c(2,1,3)]
AfterH <- table(SAGE_india_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```





```{r importOPAL_india, echo=F}
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_india_ds_w1
save(residence, file = "../RData/india_w1/residence.RData")
rm(residence)

SAGE_india_m_ds_w1 <- SAGE_india_ds_w1
SAGE_india_m_ds_w1$residence <- car::recode(SAGE_india_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_india_m_ds_w1', SAGE_india_m_ds_w1)
#opal.symbol_import(o,'SAGE_india_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Russia

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`

```{r assign_russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_resi','SAGE.russiaINDdata',
                         variables=list('q0414'), missings = TRUE)
```

```{r local_russia, echo=F}
SAGE_russia_w1_resi <- opal.execute(o,'SAGE_russia_w1_resi')
vari <- SAGE_russia_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_russia_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo_russia}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_resi$id)
SAGE_russia_ds_w1$residence <- car::recode(SAGE_russia_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_russia_ds_w1$residence <- labelled(SAGE_russia_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia, echo=F}
vari <- SAGE_russia_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_russia, echo=F}
BeforeH <- c(table(SAGE_russia_w1_resi$q0414), sum(is.na(SAGE_russia_w1_resi$q0414)))[c(2,1,3,4)]
AfterH <- table(SAGE_russia_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "8->998", "NA->999")
kable(C)
```





```{r importOPAL_russia, echo=F}
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_russia_ds_w1
save(residence, file = "../RData/russia_w1/residence.RData")
rm(residence)

SAGE_russia_m_ds_w1 <- SAGE_russia_ds_w1
SAGE_russia_m_ds_w1$residence <- car::recode(SAGE_russia_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_russia_m_ds_w1', SAGE_russia_m_ds_w1)
#opal.symbol_import(o,'SAGE_russia_m_ds_w1', project='_Athlos_Harm_Dataset')
```






## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q0414`
* Label: `in institution?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `8 = don't know`
    + `9 = not applicable`

```{r assign_Mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_resi','SAGE.mexicoINDdata',
                         variables=list('q0414'), missings = TRUE)
```

```{r local_Mexico, echo=F}
SAGE_mexico_w1_resi <- opal.execute(o,'SAGE_mexico_w1_resi')
vari <- SAGE_mexico_w1_resi$q0414
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = 'q0414') 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_w1_resi$q0414, missing_values = c(8,9))
ggplot(SAGE_mexico_w1_resi, aes(x=factor(q0414))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

Is all missing. 

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "yes" into 1`
* `recode 2 "no" into 0`
* `recode 8 "don't know" into 998`
* `recode 9 "not applicable" into 996`

**R script:**

```{r harmo_Mexico}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_resi$id)
SAGE_mexico_ds_w1$residence <- car::recode(SAGE_mexico_w1_resi$q0414, "2=0; 8=998; 9=996; NA=999")
SAGE_mexico_ds_w1$residence <- labelled(SAGE_mexico_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico, echo=F}
vari <- SAGE_mexico_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_Mexico, echo=F}
BeforeH <- sum(is.na(SAGE_mexico_w1_resi$q0414))
AfterH <- table(SAGE_mexico_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("NA->999")
kable(C)
```





```{r importOPAL_Mexico, echo=F}
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
residence <- SAGE_mexico_ds_w1
save(residence, file = "../RData/mexico_w1/residence.RData")
rm(residence)

SAGE_mexico_m_ds_w1 <- SAGE_mexico_ds_w1
SAGE_mexico_m_ds_w1$residence <- car::recode(SAGE_mexico_m_ds_w1$residence, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_mexico_m_ds_w1', SAGE_mexico_m_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_m_ds_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation
[Comments on the quality of the new harmonised variable.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
