---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```



# Data process




## South Africa


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `q1503: currently working?`|
| **Table name**  | `southAfricaINDdata`| 
| **Categories** | `1 = yes working`<br/>`2 = not working` |
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |

```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('q1503'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(SAGE_SA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo SA_w1}

# Categorical variable harmonization
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$employed <- car::recode(SAGE_SA_w1$q1503,"2=0;8=998;9=996;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}

```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `q1503: currently working?`|
| **Table name**  | `ghanaINDData`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('q1503'), missings = T)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')

```

```{r local ghana_w1, echo=F}

vbl <- SAGE_ghana_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(SAGE_ghana_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo ghana_w1}

# Categorical variable harmonization
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$employed <- car::recode(SAGE_ghana_w1$q1503,"2=0;8=998;9=996;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}

```





## China


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `q1503: currently working?`|
| **Table name**  | `chinaINDData`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |
| **Missings** | `NA`|
| **Description** |  |

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q1503'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$q1503
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_china_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo china_w1}

# Categorical variable harmonization
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$employed <- car::recode(SAGE_china_w1$q1503,"2=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}

```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `Q1503: Currently working?`|
| **Table name**  | `indiaINDData`|
| **Categories** | `1 = Yes working`<br/>`2 = Not working` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('q1503'), missings = T)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')

```

```{r local india_w1, echo=F}

vbl <- SAGE_india_w1$q1503
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo india_w1}

# Categorical variable harmonization
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$employed <- car::recode(SAGE_india_w1$q1503,"2=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

```





## Russian Federation


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `q1503: currently working?`|
| **Table name**  | `russiaINDdata`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |
| **Missings** | `NA`<br/>`9 = Not applicable` |
| **Description** |  |

```{r assign russia_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',variables=list('q1503'), missings = T)
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')

```

```{r local russia_w1, echo=F}

vbl <- SAGE_russia_w1$q1503
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(SAGE_russia_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo russia_w1}

# Categorical variable harmonization
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$employed <- car::recode(SAGE_russia_w1$q1503,"2=0;9=996;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript russia_w1, echo=F}

vbl <- SAGE_ds_russia_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation russia_w1, echo=F}

```




## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `q1503` |
|-|-|
| **Label** | `q1503: currently working?`|
| **Table name**  | `mexicoINDdata`|
| **Categories** | `1 = yes working`<br/>`2 = not working` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q1503'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$q1503
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_mexico_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q1503))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo mexico_w1}

# Categorical variable harmonization
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$employed <- car::recode(SAGE_mexico_w1$q1503,"2=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  m_name <- paste0("SAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds)

```



# Quality estimation

No comments


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  employed <- l.hds[[index]]
  save(employed, file = paste0(datafolder,names(l.hds)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





