---
title: "Emotional support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/emot_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/emot_supDS.R')
```

<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1

Not found.

### Wave 2

#### Study-specific variable description


| **Name** |`w2socialsupport1`|
|-|-|
| **Label** |`Is there anyone in your life you can turn to when you need to talk to someone/share your problems and feelings? Whom? (wife-husband/son-daughter/other family members/friends/other)?`|
| **Table name** |`ENRICA_spss_wave2`|
| **Categories** |`1 = Yes`<br/>`0 = No`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_emot_sup','ENRICA.ENRICA_spss_wave2',variables=list('w2socialsupport1'), missings = TRUE)
ENRICA_w2_emot_sup <- opal.execute(o,'ENRICA_w2_emot_sup')
```

```{r local2, echo=F}
Categorical_summary(var = ENRICA_w2_emot_sup$w2socialsupport1, missing_values = NA)
ggplot(ENRICA_w2_emot_sup, aes(x=factor(w2socialsupport1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is there anyone in your life you can turn to when you need to talk to someone/share your problems and feelings?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `0 into 0`
* `NA into 999`

**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_emot_sup$id)
ENRICA_ds_w2$emot_sup <- car::recode(as.vector(ENRICA_w2_emot_sup$w2socialsupport1), "1='1'; 0='0'; NA='999'")
ENRICA_ds_w2$emot_sup <- labelled(ENRICA_ds_w2$emot_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ENRICA_ds_w2$emot_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Receives emotional support from someone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ENRICA_ds_w2$emot_sup)
BeforeH <- table(ENRICA_w2_emot_sup$w2socialsupport1, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


```{r final, echo=F}

l.hds <- list(w2 = ENRICA_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ENRICA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

One table are generated: 

Percentages of categories in each harmonised variable.



```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

```


# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  emot_sup <- l.hds[[index]]
  save(emot_sup, file = paste0(datafolder,names(l.hds)[index],"/emot_sup.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
