---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Spanish population
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w1maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'ENRICA_w1_bereav','ENRICA.ENRICA_spss_wave1',variables=list('w1maritalstatus'), missings = TRUE)
```

```{r local1}
ENRICA_w1_bereav <- opal.execute(o,'ENRICA_w1_bereav')
vari <- ENRICA_w1_bereav$w1maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w1_bereav$w1maritalstatus, missing_values = NA)
ggplot(ENRICA_w1_bereav, aes(x=factor(w1maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 Widow(er) into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_bereav$id)
ENRICA_ds_w1$bereav <- car::recode(as.vector(ENRICA_w1_bereav$w1maritalstatus), "4='1'; 1:3='0'; NA='999'")
ENRICA_ds_w1$bereav <- labelled(ENRICA_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- ENRICA_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(ENRICA_ds_w1$bereav)
BeforeH <- table(ENRICA_w1_bereav$w1maritalstatus, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'ENRICA_w2_bereav','ENRICA.ENRICA_spss_wave2',variables=list('w2maritalstatus'), missings = TRUE)
```

```{r local2}
ENRICA_w2_bereav <- opal.execute(o,'ENRICA_w2_bereav')
vari <- ENRICA_w2_bereav$w2maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w2_bereav$w2maritalstatus, missing_values = NA)
ggplot(ENRICA_w2_bereav, aes(x=factor(w2maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 Widow(er) into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_bereav$id)
ENRICA_ds_w2$bereav <- car::recode(as.vector(ENRICA_w2_bereav$w2maritalstatus), "4='1'; 1:3='0'; NA='999'")
ENRICA_ds_w2$bereav <- labelled(ENRICA_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- ENRICA_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(ENRICA_ds_w2$bereav)
BeforeH <- table(ENRICA_w2_bereav$w2maritalstatus, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```

 
 


### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w3maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign3}
opal.assign.table.tibble(o, 'ENRICA_w3_bereav','ENRICA.ENRICA_spss_wave3',variables=list('w3maritalstatus'), missings = TRUE)
```

```{r local3}
ENRICA_w3_bereav <- opal.execute(o,'ENRICA_w3_bereav')
vari <- ENRICA_w3_bereav$w3maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w3_bereav$w3maritalstatus, missing_values = NA)
ggplot(ENRICA_w3_bereav, aes(x=factor(w3maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 Widow(er) into 1`
* `1,2,3 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_bereav$id)
ENRICA_ds_w3$bereav <- car::recode(as.vector(ENRICA_w3_bereav$w3maritalstatus), "4='1'; 1:3='0'; NA='999'")
ENRICA_ds_w3$bereav <- labelled(ENRICA_ds_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3}
vari <- ENRICA_ds_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3}
AfterH <- table(ENRICA_ds_w3$bereav)
BeforeH <- table(ENRICA_w3_bereav$w3maritalstatus, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(2,3)] <- BeforeH[c(4,5)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3->0","4->1","NA->999")
kable(C)
```

 
 
```{r save, echo=FALSE}
bereav <- ENRICA_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- ENRICA_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)

bereav <- ENRICA_ds_w3
save(bereav, file = "../RData/w3/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```