---
title: "Ever experienced financial problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `fin_prob`
* Variable label: `Ever experienced financial problems?`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1

Not found.

### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2making_ends_meet`
* Label: `Currently, taking into account your family's monthly net income: is it difficult for you to make ends meet?`
* Categories: 
    + `1 = very difficult`
    + `2 = difficult`
    + `3 = relatively difficult`
    + `4 = relatively easy`
    + `5 = easy`
    + `6 = very easy`


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_fin_prob','ENRICA.ENRICA_spss_wave2',variables=list('w2making_ends_meet'), missings = TRUE)
```

```{r local2, echo=F}
ENRICA_w2_fin_prob <- opal.execute(o,'ENRICA_w2_fin_prob')
vari <- ENRICA_w2_fin_prob$w2making_ends_meet
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w2_fin_prob$w2making_ends_meet, missing_values = NA)
ggplot(ENRICA_w2_fin_prob, aes(x=factor(w2making_ends_meet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Taking into account your family's monthly net income: is it difficult for you to make ends meet?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2,3 into 1`
* `4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_fin_prob$id)
ENRICA_ds_w2$fin_prob <- car::recode(as.vector(ENRICA_w2_fin_prob$w2making_ends_meet), "1:3='1'; 4:6='0'; NA='999'")
ENRICA_ds_w2$fin_prob <- labelled(ENRICA_ds_w2$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991) )
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ENRICA_ds_w2$fin_prob)
BeforeH <- table(ENRICA_w2_fin_prob$w2making_ends_meet, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(4:6)])
BeforeH1[[2]] <- sum(BeforeH[c(1:3)])
BeforeH1[[3]] <- BeforeH[[7]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:6->>0","1:3->1","NA->999")
kable(C)
```

### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w3making_ends_meet`
* Label: `Currently, taking into account your family's monthly net income: is it difficult for you to make ends meet?`
* Categories: 
    + `1 = very difficult`
    + `2 = difficult`
    + `3 = relatively difficult`
    + `4 = relatively easy`
    + `5 = easy`
    + `6 = very easy`
    
* Name: `fin_prob` harmonized in Wave2

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_fin_prob','ENRICA.ENRICA_spss_wave3',variables=list('w3making_ends_meet'), missings = TRUE)
```

```{r local3, echo=F}
ENRICA_w3_fin_prob <- opal.execute(o,'ENRICA_w3_fin_prob')
vari <- ENRICA_w3_fin_prob$w3making_ends_meet
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w3_fin_prob$w3making_ends_meet, missing_values = NA)
ggplot(ENRICA_w3_fin_prob, aes(x=factor(w3making_ends_meet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Taking into account your family's monthly net income: is it difficult for you to make ends meet?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if fin_prob=1 or w3making_ends_meet in 1,2,3 then 1`
* `4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, w3making_ends_meet=new$w3making_ends_meet, fin_prob=new_2$fin_prob) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = ENRICA_ds_w2 (fin_prob)
# new = ENRICA_w3_fin_prob (w3making_ends_meet)

ENRICA_w3_fin_prob_2 <- same_indiv(ENRICA_ds_w2, ENRICA_w3_fin_prob)

ENRICA_ds_w3 <- tibble(id=ENRICA_w3_fin_prob_2$id)

ENRICA_w3_fin_prob_2$fin_prob <- car::recode(as.vector(ENRICA_w3_fin_prob_2$fin_prob), "NA='-999'")
ENRICA_w3_fin_prob_2$w3making_ends_meet <- car::recode(as.vector(ENRICA_w3_fin_prob_2$w3making_ends_meet), "NA='-999'")

ENRICA_ds_w3$fin_prob <- c(NA)   
for(i in 1:dim(ENRICA_w3_fin_prob_2[1])){
  if( ENRICA_w3_fin_prob_2$fin_prob[i] == 1 | ENRICA_w3_fin_prob_2$w3making_ends_meet[i] %in% c(1,2,3) ) { 
    ENRICA_ds_w3$fin_prob[i] = 1 }
  else if( ENRICA_w3_fin_prob_2$w3making_ends_meet[i] %in% c(4,5,6) ) { 
    ENRICA_ds_w3$fin_prob[i] = 0 }
}

ENRICA_ds_w3$fin_prob <- car::recode(as.vector(ENRICA_ds_w3$fin_prob), "NA='999'")
ENRICA_ds_w3$fin_prob <- labelled(ENRICA_ds_w3$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ENRICA_ds_w3$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ENRICA_ds_w3$fin_prob)
BeforeH <- table(ENRICA_w3_fin_prob_2$w3making_ends_meet,ENRICA_w3_fin_prob_2$fin_prob, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[c(2,3,4),c(1,3)]),sum(BeforeH[,2]))
BeforeH1[[1]] <- sum(BeforeH[c(5,6,7),c(1,3)])
BeforeH1[[3]] <- sum(BeforeH[1,c(1,3)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```



```{r save, echo=FALSE}
fin_prob <- ENRICA_ds_w2
save(fin_prob, file = "../RData/w2/fin_prob.RData")
rm(fin_prob)

fin_prob <- ENRICA_ds_w3
save(fin_prob, file = "../RData/w3/fin_prob.RData")
rm(fin_prob)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```






