---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process
## Spanish population


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w1maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'ENRICA_w1_spouse','ENRICA.ENRICA_spss_wave1',variables=list('w1maritalstatus'), missings = TRUE)
```

```{r local1}
ENRICA_w1_spouse <- opal.execute(o,'ENRICA_w1_spouse')
vari <- ENRICA_w1_spouse$w1maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w1_spouse$w1maritalstatus, missing_values = NA)
ggplot(ENRICA_w1_spouse, aes(x=factor(w1maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 Married into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_spouse$id)
ENRICA_ds_w1$spouse <- car::recode(as.vector(ENRICA_w1_spouse$w1maritalstatus), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
ENRICA_ds_w1$spouse <- labelled(ENRICA_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- ENRICA_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(ENRICA_ds_w1$spouse)
BeforeH <- table(ENRICA_w1_spouse$w1maritalstatus, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,3,4->0","2->1","NA->999")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'ENRICA_w2_spouse','ENRICA.ENRICA_spss_wave2',variables=list('w2maritalstatus'), missings = TRUE)
```

```{r local2}
ENRICA_w2_spouse <- opal.execute(o,'ENRICA_w2_spouse')
vari <- ENRICA_w2_spouse$w3maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w2_spouse$w2maritalstatus, missing_values = NA)
ggplot(ENRICA_w2_spouse, aes(x=factor(w2maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 Married into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_spouse$id)
ENRICA_ds_w2$spouse <- car::recode(as.vector(ENRICA_w2_spouse$w2maritalstatus), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
ENRICA_ds_w2$spouse <- labelled(ENRICA_ds_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- ENRICA_ds_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(ENRICA_ds_w2$spouse)
BeforeH <- table(ENRICA_w2_spouse$w2maritalstatus, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,3,4->0","2->1","NA->999")

kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w3maritalstatus`
* Label: ``
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widow(er)`

* Description: 
```{r assign3}
opal.assign.table.tibble(o, 'ENRICA_w3_spouse','ENRICA.ENRICA_spss_wave3',variables=list('w3maritalstatus'), missings = TRUE)
```

```{r local3}
ENRICA_w3_spouse <- opal.execute(o,'ENRICA_w3_spouse')
vari <- ENRICA_w3_spouse$w3maritalstatus
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w3_spouse$w3maritalstatus, missing_values = NA)
ggplot(ENRICA_w3_spouse, aes(x=factor(w3maritalstatus))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2 Married into 1`
* `1, 3, 4 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_spouse$id)
ENRICA_ds_w3$spouse <- car::recode(as.vector(ENRICA_w3_spouse$w3maritalstatus), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
ENRICA_ds_w3$spouse <- labelled(ENRICA_ds_w3$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3}
vari <- ENRICA_ds_w3$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has spouse/partner") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3}
AfterH <- table(ENRICA_ds_w3$spouse)
BeforeH <- table(ENRICA_w3_spouse$w3maritalstatus, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,3,4->0","2->1","NA->999")

kable(C)
```

 
```{r save, echo=FALSE}
spouse <- ENRICA_ds_w1
save(spouse, file = "../RData/w1/spouse.RData")
rm(spouse)

spouse <- ENRICA_ds_w2
save(spouse, file = "../RData/w2/spouse.RData")
rm(spouse)

spouse <- ENRICA_ds_w3
save(spouse, file = "../RData/w3/spouse.RData")
rm(spouse)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
