---
title: "Contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```


<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1

Not found. 

### Wave 2

#### Study-specific variable description


| **Name** |`w2socialnetwork_contact_friends`|
|-|-|
| **Label** |`Frequency of telephone and face-to-face contact with friends`|
| **Table name** |`ENRICA_spss_wave2`|
| **Categories** |`1 = day`<br/>`2 = 1-2 week`<br/>`3 = 1-2month`<br/>`4 = every other month`<br/>`5 = infrequently`<br/>`6 = never`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_cont_fr','ENRICA.ENRICA_spss_wave2',variables=list('w2socialnetwork_contact_friends'), missings = TRUE)
ENRICA_w2_cont_fr <- opal.execute(o,'ENRICA_w2_cont_fr')
```

```{r local2, echo=F}
vari <- ENRICA_w2_cont_fr$w2socialnetwork_contact_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_cont_fr, aes(x=factor(w2socialnetwork_contact_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of telephone and face-to-face contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2 or 3 into 1`
* `4,5 or 6 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_cont_fr$id)
ENRICA_ds_w2$cont_fr <- car::recode(as.vector(ENRICA_w2_cont_fr$w2socialnetwork_contact_friends), "1:3='1'; 4:6='0'; NA='999'")
ENRICA_ds_w2$cont_fr <- labelled(ENRICA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ENRICA_ds_w2$cont_fr)
BeforeHa <- table(ENRICA_w2_cont_fr$w2socialnetwork_contact_friends, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[2]] <- sum(BeforeHa[[1]],BeforeHa[[2]],BeforeHa[[3]])
BeforeH[[1]] <- sum(BeforeHa[[4]],BeforeHa[[5]],BeforeHa[[6]])
BeforeH[[3]] <- BeforeHa[[7]]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")

kable(C)
```

### Wave 3
Not found.

```{r save, echo=FALSE}
cont_fr <- ENRICA_ds_w2
save(cont_fr, file = "../RData/w2/cont_fr.RData")
rm(cont_fr)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
