---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_fr`
* Variable label: `Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## Spanish population

### Wave 1
not found. 

### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2socialnetwork_contact_friends`
* Label: `Frequency of telephone and face-to-face contact with friends`
* Categories:
    + `1 = day`
    + `2 = 1-2 week`
    + `3 = 1-2month`
    + `4 = every other month`
    + `5 = infrequently`
    + `6 = never`


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'ENRICA_w2_cont_fr','ENRICA.ENRICA_spss_wave2',variables=list('w2socialnetwork_contact_friends'), missings = TRUE)
```

```{r local2}
ENRICA_w2_cont_fr <- opal.execute(o,'ENRICA_w2_cont_fr')
vari <- ENRICA_w2_cont_fr$w2socialnetwork_contact_friends
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w2_cont_fr$w2socialnetwork_contact_friends, missing_values = NA)
ggplot(ENRICA_w2_cont_fr, aes(x=factor(w2socialnetwork_contact_friends))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of telephone and face-to-face contact with friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1,2 or 3 into 1`
* `4,5 or 6 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_cont_fr$id)
ENRICA_ds_w2$cont_fr <- car::recode(as.vector(ENRICA_w2_cont_fr$w2socialnetwork_contact_friends), "1:3='1'; 4:6='0'; NA='999'")
ENRICA_ds_w2$cont_fr <- labelled(ENRICA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- ENRICA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(ENRICA_ds_w2$cont_fr)
BeforeHa <- table(ENRICA_w2_cont_fr$w2socialnetwork_contact_friends, useNA='ifany')
BeforeH <- c(NA)
BeforeH[[2]] <- sum(BeforeHa[[1]],BeforeHa[[2]],BeforeHa[[3]])
BeforeH[[1]] <- sum(BeforeHa[[4]],BeforeHa[[5]],BeforeHa[[6]])
BeforeH[[3]] <- BeforeHa[[7]]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")

kable(C)
```

### Wave 3
Not found.

```{r save, echo=FALSE}
cont_fr <- ENRICA_ds_w2
save(cont_fr, file = "../RData/w2/cont_fr.RData")
rm(cont_fr)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
