---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```


<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

| **Name** | `w01dep2`|
|-|-|
| **Label** | `CES-D10 Stnadard Depress stauts`|
| **Table name** | `w01_main_e` |
| **Categories** |`0 = No depression; 1 = Depression`|
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_dep','KLOSA.w01_main_e',
                         variables=list('w01dep2'), missings = TRUE)
KLOSA_dep <- opal.execute(o,'KLOSA_dep')
```

```{r local1, echo=FALSE}
vari <- KLOSA_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_dep, aes(x=factor(KLOSA_dep[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_dep$id)
KLOSA_ds_w1$depression <- car::recode(KLOSA_dep[[2]], "NA=999")
KLOSA_ds_w1$depression <- labelled(KLOSA_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- KLOSA_ds_w1[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(KLOSA_dep[[2]], useNA = 'ifany')
AfterH <- table(KLOSA_ds_w1$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')

label(KLOSA_ds_w1$depression) <- ds_label_all
depression <- KLOSA_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(depression)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$depression <- car::recode(KLOSA_m_ds_w1$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description


| **Name** | `w02dep1`|
|-|-|
| **Label** | `Whether been suffered depression or not`|
| **Table name** | `w02_main_e_spss` |
| **Categories** |`0 = no; 1 = yes`|
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_dep','KLOSA.w02_main_e_spss',
                         variables=list('w02dep1'), missings = TRUE)
KLOSA_dep <- opal.execute(o,'KLOSA_dep')
```

```{r local2, echo=FALSE}
vari <- KLOSA_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_dep, aes(x=factor(KLOSA_dep[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_dep$id)
KLOSA_ds_w2$depression <- car::recode(KLOSA_dep[[2]], "NA=999")
KLOSA_ds_w2$depression <- labelled(KLOSA_ds_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- KLOSA_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(KLOSA_dep[[2]], useNA = 'ifany')
AfterH <- table(KLOSA_ds_w2$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


```{r importOPAL2, echo=FALSE}
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w2$depression) <- ds_label_all
depression <- KLOSA_ds_w2
save(depression, file = "../RData/w2/depression.RData")
rm(depression)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$depression <- car::recode(KLOSA_m_ds_w2$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

| **Name** | `w03dep1`|
|-|-|
| **Label** | `suffered depression or not`|
| **Table name** | `w03_main_e_spss_albert` |
| **Categories** |`0 = no; 1 = yes`|
| **Description** |  |

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_dep','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03dep1'), missings = TRUE)
KLOSA_dep <- opal.execute(o,'KLOSA_dep')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_dep$id <- substr(KLOSA_dep$id,1,nchar(KLOSA_dep$id)-2)
```

```{r local3, echo=FALSE}
vari <- KLOSA_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_dep, aes(x=factor(KLOSA_dep[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_dep$id)
KLOSA_ds_w3$depression <- car::recode(KLOSA_dep[[2]], "NA=999")
KLOSA_ds_w3$depression <- labelled(KLOSA_ds_w3[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- KLOSA_ds_w3[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(KLOSA_dep[[2]], useNA = 'ifany')
AfterH <- table(KLOSA_ds_w3$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


```{r importOPAL3, echo=FALSE}
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w3$depression) <- ds_label_all
depression <- KLOSA_ds_w3
save(depression, file = "../RData/w3/depression.RData")
rm(depression)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$depression <- car::recode(KLOSA_m_ds_w3$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

#### Study-specific variable description

| **Name** | `w04dep1`|
|-|-|
| **Label** | `suffered depression or not`|
| **Table name** | `w04_main_e_spss` |
| **Categories** |`0 = no; 1 = yes`|
| **Description** |  |

```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_dep','KLOSA.w04_main_e_spss',
                         variables=list('w04dep1'), missings = TRUE)
KLOSA_dep <- opal.execute(o,'KLOSA_dep')
```

```{r local4, echo=FALSE}
vari <- KLOSA_dep[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_dep, aes(x=factor(KLOSA_dep[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable except for the missing values that have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_dep$id)
KLOSA_ds_w4$depression <- car::recode(KLOSA_dep[[2]], "NA=999")
KLOSA_ds_w4$depression <- labelled(KLOSA_ds_w4[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- KLOSA_ds_w4[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
BeforeH <- table(KLOSA_dep[[2]], useNA = 'ifany')
AfterH <- table(KLOSA_ds_w4$depression)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


```{r importOPAL4, echo=FALSE}
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w4$depression) <- ds_label_all
depression <- KLOSA_ds_w4
save(depression, file = "../RData/w4/depression.RData")
rm(depression)


KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$depression <- car::recode(KLOSA_m_ds_w4$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```