---
title: "Smoking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/smokingDS.R')
```



# Data process

## Europe

### Wave 1 

#### Study-specific variable description

| **Name** | `cusmoke` |
|-|-|
| **Label** | `ever smoked daily` |
| **Table name** | `sharew1_rel2-6-0_gv_health` |
| **Categories:**| `1 = yes` <br/> `5 = no`|
| **Missings:**|`-2 = refusal` <br/> `-1 = don't know` <br/> `NA`|
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_gv_health', variables=list('cusmoke'), missings = TRUE)
SHARE_w1 <- opal.execute(o,'SHARE_w1')
```

```{r local w1, echo=F}
vbl <- SHARE_w1$cusmoke
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w1, aes(x=factor(cusmoke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute `smoking` from the study-specific variable it has to be recoded as follows:

* `1 into 2` 
* `2 into 0` 
* `5 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}
SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$smoking <- car::recode(SHARE_w1$cusmoke, "1 = 2;2 = 0;5 = 1;-2 = 997;-1 = 998;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- SHARE_ds_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation
```{r crosstabulation w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** | `br001_` | `br002_` | `br022_` |
|-|-|-|-|
| **Label** | `ever smoked daily` | `smoke at the present time` | `stopped smoking`|
| **Table name** | `sharew2_rel2-6-0_br` | `sharew2_rel2-6-0_br` | `sharew2_rel2-6-0_br` |
| **Categories:**| `1 = yes` <br/> `5 = no`| `1 = yes` <br/> `5 = no`| `1 = yes, I stopped after last interview` <br/> `5 = no, I did not smoke by last interview` <br/> `3 = no, I still smoke nowadays`|
| **Missings:**|`-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `NA` |
| **Description** |  | | |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_br', variables=list('br001_','br002_','br022_'), missings = TRUE)
SHARE_w2 <- opal.execute(o,'SHARE_w2')
```

```{r local w2, echo=F}
vbl <- SHARE_w2$br001_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(br001_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w2$br002_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(br002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w2$br022_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w2)[4])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2, aes(x=factor(br022_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute `smoking` from the study-specific variable it has to be recoded as follows:

* `br001_=5 into 0` 
* `(br001_=1&br002_=5)|(br022_=1|br022_=2) into 1` 
* `br002_=1 into 2`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo w2}
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$smoking <- rep(999,length(SHARE_ds_w2$id))
SHARE_ds_w2$smoking[SHARE_w2$br001_==5] <- 0
SHARE_ds_w2$smoking[(SHARE_w2$br001_==1&SHARE_w2$br002_==5)|(SHARE_w2$br022_==1|SHARE_w2$br022_==2)] <- 1
SHARE_ds_w2$smoking[SHARE_w2$br002_==1] <- 2
SHARE_ds_w2$smoking[SHARE_w2$br001_==-2|SHARE_w2$br002_==-2|SHARE_w2$br022_==-2]<-997
SHARE_ds_w2$smoking[SHARE_w2$br001_==-1|SHARE_w2$br002_==-1|SHARE_w2$br022_==-1]<-998

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- SHARE_ds_w2$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(SHARE_ds_w2$smoking)
X<-c(sum(na.omit(SHARE_w2$br001_==5)),sum(na.omit((SHARE_w2$br001_==1&SHARE_w2$br002_==5)|(SHARE_w2$br022_==1|SHARE_w2$br022_==2))),sum(na.omit(SHARE_w2$br002_==1)),sum(na.omit(SHARE_w2$br001_==-2|SHARE_w2$br002_==-2|SHARE_w2$br022_==-2)),sum(na.omit(SHARE_w2$br001_==-1|SHARE_w2$br002_==-1|SHARE_w2$br022_==-1)))
BeforeH <- c(X,length(SHARE_w2$br001_)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("br001_=5->0","(br001_=1&br002_=5)|(br022_=1|br022_=2)->1","br002_=1->2","-2->997","-1->998","NA->999") 
kable(C)
```



### Wave 3

Not found



### Wave 4

#### Study-specific variable description

| **Name** | `br001_` | `br002_` | `br022_` |
|-|-|-|-|
| **Label** | `ever smoked daily` | `smoke at the present time` | `stopped smoking`|
| **Table name** | `sharew4_rel1-1-1_br` | `sharew4_rel1-1-1_br` | `sharew4_rel1-1-1_br` |
| **Categories:**| `1 = yes` <br/> `5 = no`| `1 = yes` <br/> `5 = no`| `1 = yes, I stopped after last interview` <br/> `5 = no, I did not smoke by last interview` <br/> `3 = no, I still smoke nowadays`|
| **Missings:**|`-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `-1 = don't know` <br/> `NA` |
| **Description** |  | | |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_br', variables=list('br001_','br002_','br022_'), missings = TRUE)
SHARE_w4 <- opal.execute(o,'SHARE_w4')
```

```{r local w4, echo=F}
vbl <- SHARE_w4$br001_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(br001_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w4$br002_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(br002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w4$br022_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w4)[4])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4, aes(x=factor(br022_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute `smoking` from the study-specific variable it has to be recoded as follows:

* `br001_=5 into 0` 
* `(br001_=1&br002_=5)|(br022_=1|br022_=2) into 1` 
* `br002_=1 into 2`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo w4}
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$smoking <- rep(999,length(SHARE_ds_w4$id))
SHARE_ds_w4$smoking[SHARE_w4$br001_==5] <- 0
SHARE_ds_w4$smoking[(SHARE_w4$br001_==1&SHARE_w4$br002_==5)|(SHARE_w4$br022_==1|SHARE_w4$br022_==2)] <- 1
SHARE_ds_w4$smoking[SHARE_w4$br002_==1] <- 2
SHARE_ds_w4$smoking[SHARE_w4$br001_==-2|SHARE_w4$br002_==-2|SHARE_w4$br022_==-2]<-997
SHARE_ds_w4$smoking[SHARE_w4$br001_==-1|SHARE_w4$br002_==-1|SHARE_w4$br022_==-1]<-998

```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- SHARE_ds_w4$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(SHARE_ds_w4$smoking)
X<-c(sum(na.omit(SHARE_w4$br001_==5)),sum(na.omit((SHARE_w4$br001_==1&SHARE_w4$br002_==5)|(SHARE_w4$br022_==1|SHARE_w4$br022_==2))),sum(na.omit(SHARE_w4$br002_==1)),sum(na.omit(SHARE_w4$br001_==-2|SHARE_w4$br002_==-2|SHARE_w4$br022_==-2)),sum(na.omit(SHARE_w4$br001_==-1|SHARE_w4$br002_==-1|SHARE_w4$br022_==-1)))
BeforeH <- c(X,length(SHARE_w4$br001_)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("br001_=5->0","(br001_=1&br002_=5)|(br022_=1|br022_=2)->1","br002_=1->2","-2->997","-1->998","NA->999") 
kable(C)
```




### Wave 5

#### Study-specific variable description

| **Name** | `br001_` | `br002_` | `br022_` |
|-|-|-|-|
| **Label** | `ever smoked daily` | `smoke at the present time` | `stopped smoking`|
| **Table name** | `sharew5_rel1-0-0_br` | `sharew5_rel1-0-0_br` | `sharew5_rel1-0-0_br` |
| **Categories:**| `1 = yes` <br/> `5 = no`| `1 = yes` <br/> `5 = no`| `1 = yes, I stopped after last interview` <br/> `5 = no, I did not smoke by last interview` <br/> `3 = no, I still smoke nowadays`|
| **Missings:**|`-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `-2 = refusal` <br/> `-1 = don't know` <br/> `NA`| `-2 = refusal` <br/> `-1 = don't know` <br/> `NA` |
| **Description** |  |  |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_br', variables=list('br001_','br002_','br022_'), missings = TRUE)
SHARE_w5 <- opal.execute(o,'SHARE_w5')
```

```{r local w5, echo=F}
vbl <- SHARE_w5$br001_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(br001_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w5$br002_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[3])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(br002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_w5$br022_
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[3], caption = names(SHARE_w5)[4])
kable(Categorical_summary(vbl, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5, aes(x=factor(br022_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute `smoking` from the study-specific variable it has to be recoded as follows:

* `br001_=5 into 0` 
* `(br001_=1&br002_=5)|(br022_=1|br022_=2) into 1` 
* `br002_=1 into 2`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo w5}
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$smoking <- rep(999,length(SHARE_ds_w5$id))
SHARE_ds_w5$smoking[SHARE_w5$br001_==5] <- 0
SHARE_ds_w5$smoking[(SHARE_w5$br001_==1&SHARE_w5$br002_==5)|(SHARE_w5$br022_==1|SHARE_w5$br022_==2)] <- 1
SHARE_ds_w5$smoking[SHARE_w5$br002_==1] <- 2
SHARE_ds_w5$smoking[SHARE_w5$br001_==-2|SHARE_w5$br002_==-2|SHARE_w5$br022_==-2]<-997
SHARE_ds_w5$smoking[SHARE_w5$br001_==-1|SHARE_w5$br002_==-1|SHARE_w5$br022_==-1]<-998

```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- SHARE_ds_w5$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(SHARE_ds_w5$smoking)
X<-c(sum(na.omit(SHARE_w5$br001_==5)),sum(na.omit((SHARE_w5$br001_==1&SHARE_w5$br002_==5)|(SHARE_w5$br022_==1|SHARE_w5$br022_==2))),sum(na.omit(SHARE_w5$br002_==1)),sum(na.omit(SHARE_w5$br001_==-2|SHARE_w5$br002_==-2|SHARE_w5$br022_==-2)),sum(na.omit(SHARE_w5$br001_==-1|SHARE_w5$br002_==-1|SHARE_w5$br022_==-1)))
BeforeH <- c(X,length(SHARE_w5$br001_)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("br001_=5->0","(br001_=1&br002_=5)|(br022_=1|br022_=2)->1","br002_=1->2","-2->997","-1->998","NA->999") 
kable(C)
```




```{r final, echo=F}

l.hds <- list(w1 = SHARE_ds_w1, w2 = SHARE_ds_w2, w4 = SHARE_ds_w4, w5 = SHARE_ds_w5)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("SHARE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("SHARE_m_ds_",names(l.hds)[1]))[,c("id","smoking")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("SHARE_m_ds_",names(l.hds)[ind]))[,c("id","smoking")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  smoking <- l.hds[[index]]
  save(smoking, file = paste0(datafolder,names(l.hds)[index],"/smoking.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
