---
title: "Cardiovascular diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd_all`
* Variable label: `History of all Cardiovascular diseases`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: angina, stroke, myocardial infarction, heart attack, coronary heart disease, congestive heart failure, heart murmur, valve disease, cerebral vascular disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No, the participant has not been diagnosed of any of these conditions
1        | Yes, the participant has been diagnosed by any of these conditions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of all Cardiovascular diseases"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## China


### Wave 1


#### Study-specific variable description

| **Name** | `da007_7_` |`stroke`|
|-|-|-|
| **Label** | `Heart Problems`|`Stroke`|
| **Table name**  | `health_status_and_functioning_wave1`|`stroke`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`0 = No`<br/>`1 = Yes` |
| **Missings** | `NA` |`999 = Missing`|
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.health_status_and_functioning_wave1',variables=list('da007_7_'), missings = T)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
load(paste0(datafolder,"w1/stroke.RData"))


# adding a zero to the old id's in CHARLS_w1 with CHARLS_ids
CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), da007_7_=as.numeric(new_2[,2]))
  new_22
}
CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)
CHARLS_w1 <- left_join(CHARLS_w1,stroke, by="id")

```

```{r local w1, echo=F}

vbl <- CHARLS_w1$da007_7_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(da007_7_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(CHARLS_w1)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `none 1 into 0`
* `some 1 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$cvd_all <- rep(999,length(CHARLS_w1$id))
CHARLS_ds_w1$cvd_all[which(CHARLS_w1$da007_7_==2 & CHARLS_w1$stroke==0)] <- 0
CHARLS_ds_w1$cvd_all[which(CHARLS_w1$da007_7_==1 | CHARLS_w1$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- CHARLS_ds_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(CHARLS_ds_w1$cvd_all, useNA = "ifany")
X <- c(
  sum(CHARLS_w1$da007_7_==2 & CHARLS_w1$stroke==0,na.rm=T),
  sum(CHARLS_w1$da007_7_==1 | CHARLS_w1$stroke==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(CHARLS_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("none 1->0","some 1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `da007_7_` |`stroke`|
|-|-|-|
| **Label** | `Have Been Diagnosed of Disease`|`Stroke`|
| **Table name**  | `Health_Status_and_Functioning_wave2`|`stroke`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`0 = No`<br/>`1 = Yes` |
| **Missings** | `NA` |`999 = Missing`|
| **Description** |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Health_Status_and_Functioning_wave2',variables=list('da007_7_'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
load(paste0(datafolder,"w2/stroke.RData"))

Add_indiv <- function(old, new){

  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)

  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }

  new_22 <- data.frame(id=new_2[,1], da007_7_=as.numeric(new_2[,2]))
  new_22
}
CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)
CHARLS_w2 <- left_join(CHARLS_w2,stroke, by="id")

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$da007_7_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(da007_7_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(CHARLS_w2)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `none 1 into 0`
* `some 1 into 1`
* `NA into 999`



**R script:**

```{r harmo w2}

# Categorical variable harmonization
CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$cvd_all <- rep(999,length(CHARLS_w2$id))
CHARLS_ds_w2$cvd_all[which(CHARLS_w2$da007_7_==2 & CHARLS_w2$stroke==0)] <- 0
CHARLS_ds_w2$cvd_all[which(CHARLS_w2$da007_7_==1 | CHARLS_w2$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- CHARLS_ds_w2$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(CHARLS_ds_w2$cvd_all, useNA = "ifany")
X <- c(
  sum(CHARLS_w2$da007_7_==2 & CHARLS_w2$stroke==0,na.rm=T),
  sum(CHARLS_w2$da007_7_==1 | CHARLS_w2$stroke==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(CHARLS_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("none 1->0","some 1->1","NA->999")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
CHARLS_ds_w1$cvd_all <- labelled(CHARLS_ds_w1$cvd_all, labels = cat_label)
label(CHARLS_ds_w1$cvd_all) <- ds_label
CHARLS_ds_w2$cvd_all <- labelled(CHARLS_ds_w2$cvd_all, labels = cat_label)
label(CHARLS_ds_w2$cvd_all) <- ds_label


CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$cvd_all <- car::recode(CHARLS_m_ds_w1$cvd_all, "miss_values_vector=NA")
CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$cvd_all <- car::recode(CHARLS_m_ds_w2$cvd_all, "miss_values_vector=NA")


tt <-    frq(CHARLS_ds_w1$cvd_all)[[1]][,c(1:2,4)]
tt[4] <- frq(CHARLS_ds_w2$cvd_all)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(CHARLS_ds_w1$cvd_all), length(CHARLS_ds_w2$cvd_all)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(CHARLS_m_ds_w1[,c("id","cvd_all")], CHARLS_m_ds_w2[,c("id","cvd_all")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

This harmonized variable contains information about: Heart problems is about heart attack disease, angina, congestive heart failure or other heart problems and stroke.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.CHARLS <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(index in seq_along(l.CHARLS)){
  cvd_all <- l.CHARLS[[index]]
  save(cvd_all, file = paste0(datafolder,names(l.CHARLS)[index],"/cvd_all.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





