---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cancer`
* Variable label: `Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)`
* Variable description: `cancer diagnosis since the last interview`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no cancer
1        | cancer

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cancer_age`
* Variable label: `Age of cancer diagnosis`
* Variable description: `Age of each episode of cancer`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)"
ds_label_age <- "Age of cancer diagnosis"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## China


### Wave 1


#### Study-specific variable description

| **Name** | `da007_4_` |`da009_2_4_`|`da009_1_4_`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Cancer or Malignant Tumor`|`The Age of Being Diagnosed of Cancer or Malignant Tumor`|`The Year of Being Diagnosed of Cancer or Malignant Tumor`|`year of birth`|
| **Table name**  | `health_status_and_functioning_wave1`| `health_status_and_functioning_wave1`| `health_status_and_functioning_wave1`|`ybirth`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.health_status_and_functioning_wave1',variables=list('da007_4_','da009_2_4_','da009_1_4_'), missings = T)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
load(paste0(datafolder,"w1/ybirth.RData"))

# adding a zero to the old id's in CHARLS_w1 with CHARLS_ids
CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA,NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,5]), da007_4_=as.numeric(new_2[,2]), da009_1_4_=as.numeric(new_2[,3]), da009_2_4_=as.numeric(new_2[,4]))
  new_22
}
CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)
CHARLS_w1 <- left_join(CHARLS_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- CHARLS_w1$da007_4_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(da007_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$da009_1_4_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w1)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(da009_1_4_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$da009_2_4_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w1)[5])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(da009_2_4_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$ybirth
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = names(CHARLS_w1)[6])
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,2000)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = da009_1_4_ - ybirth`
* `if cancer == 1, and da009_1_4_ == NA, cancer_age = da009_2_4_`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$cancer <- car::recode(CHARLS_w1$da007_4_, "2=0; NA=999")

# Continuous variable harmonization
CHARLS_ds_w1$cancer_age <- rep(999,length(CHARLS_w1$id))
CHARLS_ds_w1$cancer_age[which(CHARLS_ds_w1$cancer == 0)] <- 996
CHARLS_ds_w1$cancer_age[which(CHARLS_ds_w1$cancer == 1 & CHARLS_w1$ybirth != 999)] <- CHARLS_w1$da009_1_4_[which(CHARLS_ds_w1$cancer == 1 & CHARLS_w1$ybirth != 999)] - CHARLS_w1$ybirth[which(CHARLS_ds_w1$cancer == 1 & CHARLS_w1$ybirth != 999)]
CHARLS_ds_w1$cancer_age[which(CHARLS_ds_w1$cancer == 1 & (is.na(CHARLS_w1$da009_1_4_) | CHARLS_w1$ybirth == 999))] <- CHARLS_w1$da009_2_4_[which(CHARLS_ds_w1$cancer == 1 & (is.na(CHARLS_w1$da009_1_4_) | CHARLS_w1$ybirth == 999))]
CHARLS_ds_w1$cancer_age <- car::recode(CHARLS_ds_w1$cancer_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- CHARLS_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- CHARLS_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(20,80)

```


#### Validation

```{r crosstabulation w1, echo=F}

kable(CHARLS_w1[which((!is.na(CHARLS_w1$da009_1_4_) & CHARLS_ds_w1$cancer == 0) | (!is.na(CHARLS_w1$da009_2_4_) & CHARLS_ds_w1$cancer == 0)),], align = 'c', caption = 'There are 8 individuals which answer they did not have cancer but next give a year or age of diagnosis. We assume this diagnosis is negative and believe their negative answer.')

AfterH <- table(CHARLS_ds_w1$cancer, useNA = "ifany")
BeforeH <- table(CHARLS_w1$da007_4_, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `da007_4_` |`da009_2_4_`|`da009_1_4_`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Have Been Diagnosed of Disease`|`Diagnosed Age`|`Diagnosed Year`|`year of birth`|
| **Table name**  | `Health_Status_and_Functioning_wave2`|`Health_Status_and_Functioning_wave2`|`Health_Status_and_Functioning_wave2`|`ybirth`|
| **Categories** | `1 = Yes; 2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA`| `NA` | `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Health_Status_and_Functioning_wave2',variables=list('da007_4_','da009_2_4_','da009_1_4_'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
load(paste0(datafolder,"w2/ybirth.RData"))

Add_indiv <- function(old, new){

  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)

  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA,NA)
    }
  }

  new_22 <- data.frame(id=new_2[,1], da007_4_=as.numeric(new_2[,2]), da009_1_4_=as.numeric(new_2[,3]), da009_2_4_=as.numeric(new_2[,4]))
  new_22
}
CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)
#CHARLS_w2 <- left_join(CHARLS_w2_id,CHARLS_w2_2)[c(1,3,4,5)]
CHARLS_w2 <- left_join(CHARLS_w2,ybirth, by="id")

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$da007_4_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(da007_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$da009_1_4_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(da009_1_4_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$da009_2_4_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w2)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(da009_2_4_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(40,85)

vbl <- CHARLS_w2$ybirth
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = names(CHARLS_w2)[5])
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1995)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1 in w2 and w1, cancer_age = age from w1`
* `if cancer == 1 in w2 and 0 in w1, cancer_age = da009_1_4_ - ybirth`
* `if cancer == 1 in w2 and 0 in w1, and da009_1_4_ == NA, cancer_age = da009_2_4_`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`



**R script:**

```{r harmo w2}

CHARLS_w2 <- left_join(CHARLS_w2,CHARLS_w1,by="id",suffix=c("","_w1"))

# Before following we correct a mistake; a year recorded in the ages variable. We record it in the diagnosed years variable.
CHARLS_w2$da009_1_4_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_4_>2000)])] <- CHARLS_w2$da009_2_4_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_4_>2000)])]
CHARLS_w2$da009_2_4_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_4_>2000)])] <- rep(NA,length(CHARLS_w2$da009_2_4_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_4_>2000)])]))

# The value CHARLS_w2$da007_4_ is missing for 92 individuals with diagnosed age or year. We update the value.
CHARLS_w2$da007_4_[which(is.na(CHARLS_w2$da007_4_) & (!is.na(CHARLS_w2$da009_1_4_) | !is.na(CHARLS_w2$da009_2_4_)))] <- 1

# Categorical variable harmonization
CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$cancer <- rep(999,length(CHARLS_w2$id))
CHARLS_ds_w2$cancer[which(CHARLS_w2$da007_4_==2)] <- 0
# Individuals having cancer since wave 1, so their year of diagnostic is at least 2011 and greater than the answered in wave 1 or missing but until wave 1 they have no cancer.
CHARLS_ds_w2$cancer[which(CHARLS_w2$da007_4_==1 & (((CHARLS_w2$da009_1_4_>=2011 & (CHARLS_w2$da009_1_4_>CHARLS_w2$da009_1_4__w1 | is.na(CHARLS_w2$da009_1_4__w1))) | (CHARLS_w2$da007_4__w1 == 2 | is.na(CHARLS_w2$da007_4__w1)))))] <- 1

# Continuous variable harmonization
CHARLS_ds_w2$cancer_age <- rep(999,length(CHARLS_w2$id))
CHARLS_ds_w2$cancer_age[which(CHARLS_ds_w2$cancer == 0)] <- 996
# Use of diagnosed year
CHARLS_ds_w2$cancer_age[which(CHARLS_ds_w2$cancer == 1 & CHARLS_w2$ybirth>1850 & (CHARLS_w2$da009_1_4_>=2011 | !CHARLS_ds_w2$id %in% CHARLS_ds_w1$id))] <- CHARLS_w2$da009_1_4_[which(CHARLS_ds_w2$cancer == 1 & CHARLS_w2$ybirth>1850 & (CHARLS_w2$da009_1_4_>=2011 | !CHARLS_ds_w2$id %in% CHARLS_ds_w1$id))] - CHARLS_w2$ybirth[which(CHARLS_ds_w2$cancer == 1 & CHARLS_w2$ybirth>1850 & (CHARLS_w2$da009_1_4_>=2011 | !CHARLS_ds_w2$id %in% CHARLS_ds_w1$id))]
# Use of diagnosed age for the individuals the previous do not apply due to missing
CHARLS_ds_w2$cancer_age[which(CHARLS_ds_w2$cancer == 1 & (is.na(CHARLS_w2$da009_1_4_) | CHARLS_w2$ybirth<1850) & (CHARLS_w2$da009_2_4_ >= 2011 - CHARLS_w2$ybirth | !CHARLS_ds_w2$id %in% CHARLS_ds_w1$id) & CHARLS_w2$da009_2_4_ <= 2014 - CHARLS_w2$ybirth)] <- CHARLS_w2$da009_2_4_[which(CHARLS_ds_w2$cancer == 1 & (is.na(CHARLS_w2$da009_1_4_) | CHARLS_w2$ybirth<1850) & (CHARLS_w2$da009_2_4_ >= 2011 - CHARLS_w2$ybirth | !CHARLS_ds_w2$id %in% CHARLS_ds_w1$id) & CHARLS_w2$da009_2_4_ <= 2014 - CHARLS_w2$ybirth)]
CHARLS_ds_w2$cancer_age <- car::recode(CHARLS_ds_w2$cancer_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- CHARLS_ds_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- CHARLS_ds_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,90)

```


#### Validation

```{r crosstabulation w2, echo=F}


AfterH <- table(CHARLS_ds_w2$cancer, useNA = "ifany")
X <- c(
  sum(CHARLS_w2$da007_4_==2,na.rm=T),
  sum(CHARLS_w2$da007_4_==1 & (((CHARLS_w2$da009_1_4_>=2011 & (CHARLS_w2$da009_1_4_>CHARLS_w2$da009_1_4__w1 | is.na(CHARLS_w2$da009_1_4__w1))) | (CHARLS_w2$da007_4__w1 == 2 | is.na(CHARLS_w2$da007_4__w1)))),na.rm=T)
)
BeforeH <- c(X[1:2],length(CHARLS_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
CHARLS_ds_w1$cancer <- labelled(CHARLS_ds_w1$cancer, labels = cat_label)
label(CHARLS_ds_w1$cancer) <- ds_label
CHARLS_ds_w1$cancer_age <- labelled(CHARLS_ds_w1$cancer_age, labels = cont_label)
label(CHARLS_ds_w2$cancer_age) <- ds_label_age
CHARLS_ds_w2$cancer <- labelled(CHARLS_ds_w2$cancer, labels = cat_label)
label(CHARLS_ds_w2$cancer) <- ds_label
CHARLS_ds_w2$cancer_age <- labelled(CHARLS_ds_w2$cancer_age, labels = cont_label)
label(CHARLS_ds_w2$cancer_age) <- ds_label_age


CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$cancer <- car::recode(CHARLS_m_ds_w1$cancer, "miss_values_vector=NA")
CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$cancer <- car::recode(CHARLS_m_ds_w2$cancer, "miss_values_vector=NA")


tt <-    frq(CHARLS_ds_w1$cancer)[[1]][,c(1:2,4)]
tt[4] <- frq(CHARLS_ds_w2$cancer)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(CHARLS_ds_w1$cancer), length(CHARLS_ds_w2$cancer)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(CHARLS_m_ds_w1[,c("id","cancer")], CHARLS_m_ds_w2[,c("id","cancer")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

Minor skin cancers are not included in this variable. 

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.CHARLS <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(index in seq_along(l.CHARLS)){
  cancer <- l.CHARLS[[index]]
  save(cancer, file = paste0(datafolder,names(l.CHARLS)[index],"/cancer.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





