---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hypertensionDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hypertensionDS.R')
```

# Data process



## China


### Wave 1


#### Study-specific variable description

| **Name** | `da007_1_` |`da009_2_1_`|`da009_1_1_`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Hypertension`|`The Age of Being Diagnosed of Hypertension`|`The Year of Being Diagnosed of Hypertension`|`year of birth`|
| **Table name**  | `health_status_and_functioning_wave1`| `health_status_and_functioning_wave1`| `health_status_and_functioning_wave1`|`ybirth`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.health_status_and_functioning_wave1',variables=list('da007_1_','da009_2_1_','da009_1_1_'), missings = T)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
load(paste0(datafolder,"w1/ybirth.RData"))

# adding a zero to the old id's in CHARLS_w1 with CHARLS_ids
CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA,NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,5]), da007_1_=as.numeric(new_2[,2]), da009_1_1_=as.numeric(new_2[,3]), da009_2_1_=as.numeric(new_2[,4]))
  new_22
}
CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)
CHARLS_w1 <- left_join(CHARLS_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- CHARLS_w1$da007_1_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(da007_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$da009_1_1_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w1)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(da009_1_1_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$da009_2_1_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w1)[5])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(da009_2_1_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$ybirth
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = names(CHARLS_w1)[6])
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = da009_1_1_ - ybirth`
* `if h_hypertension == 1, and da009_1_1_ == NA, h_hypertension_age = da009_2_1_`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$h_hypertension <- car::recode(CHARLS_w1$da007_1_, "2=0; NA=999")

# Continuous variable harmonization
CHARLS_ds_w1$h_hypertension_age <- rep(999,length(CHARLS_w1$id))
CHARLS_ds_w1$h_hypertension_age[which(CHARLS_ds_w1$h_hypertension == 0)] <- 996
CHARLS_ds_w1$h_hypertension_age[which(CHARLS_ds_w1$h_hypertension == 1 & CHARLS_w1$ybirth != 999)] <- CHARLS_w1$da009_1_1_[which(CHARLS_ds_w1$h_hypertension == 1 & CHARLS_w1$ybirth != 999)] - CHARLS_w1$ybirth[which(CHARLS_ds_w1$h_hypertension == 1 & CHARLS_w1$ybirth != 999)]
CHARLS_ds_w1$h_hypertension_age[which(CHARLS_ds_w1$h_hypertension == 1 & (is.na(CHARLS_w1$da009_1_1_) | CHARLS_w1$ybirth == 999))] <- CHARLS_w1$da009_2_1_[which(CHARLS_ds_w1$h_hypertension == 1 & (is.na(CHARLS_w1$da009_1_1_) | CHARLS_w1$ybirth == 999))]
CHARLS_ds_w1$h_hypertension_age <- car::recode(CHARLS_ds_w1$h_hypertension_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- CHARLS_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- CHARLS_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

CHARLS_w1$diff_age <- CHARLS_w1$da009_1_1_- CHARLS_w1$ybirth
kable(CHARLS_w1[which(!is.na(CHARLS_w1$da009_2_1_) & !is.na(CHARLS_w1$da009_1_1_) & CHARLS_w1$da009_2_1_!=CHARLS_w1$diff_age),],align = 'c',caption = 'There are five discrepancies between the age answered in da009_2_1_ and the age obtained obtained by means of the years of diagnosis and birth. We assume to be correct the second age.')

kable(CHARLS_w1[which((!is.na(CHARLS_w1$da009_1_1_) & CHARLS_ds_w1$h_hypertension == 0) | (!is.na(CHARLS_w1$da009_2_1_) & CHARLS_ds_w1$h_hypertension == 0)),], align = 'c', caption = 'There are 133 individuals which answer they do not have hypertension but next give a year or age of diagnosis. We assume this diagnosis is negative and believe their negative answer.')

AfterH <- table(CHARLS_ds_w1$h_hypertension, useNA = "ifany")
BeforeH <- table(CHARLS_w1$da007_1_, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `da007_1_` |`da009_2_1_`|`da009_1_1_`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Have Been Diagnosed of Disease`|`Diagnosed Age`|`Diagnosed Year`|`year of birth`|
| **Table name**  | `Health_Status_and_Functioning_wave2`|`Health_Status_and_Functioning_wave2`|`Health_Status_and_Functioning_wave2`|`ybirth`|
| **Categories** | `1 = Yes; 2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA`| `NA` | `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Health_Status_and_Functioning_wave2',variables=list('da007_1_','da009_2_1_','da009_1_1_'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
load(paste0(datafolder,"w2/ybirth.RData"))

Add_indiv <- function(old, new){

  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)

  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA,NA)
    }
  }

  new_22 <- data.frame(id=new_2[,1], da007_1_=as.numeric(new_2[,2]), da009_1_1_=as.numeric(new_2[,3]), da009_2_1_=as.numeric(new_2[,4]))
  new_22
}
CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)
#CHARLS_w2 <- left_join(CHARLS_w2_id,CHARLS_w2_2)[c(1,3,4,5)]
CHARLS_w2 <- left_join(CHARLS_w2,ybirth, by="id")

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$da007_1_
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(da007_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$da009_1_1_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(da009_1_1_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$da009_2_1_
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(CHARLS_w2)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(da009_2_1_)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,85)

vbl <- CHARLS_w2$ybirth
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = names(CHARLS_w2)[5])
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `da007_1_ (w1) == 2 and da007_1_ (w2) == 2 into 0`
* `da007_1_ (w1) == 1 or da007_1_ (w2) == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and w1, h_hypertension_age = age from w1`
* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = da009_1_1_ - ybirth`
* `if h_hypertension == 1 in w2 and 0 in w1, and da009_1_1_ == NA, h_hypertension_age = da009_2_1_`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise into 999`



**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
CHARLS_w2 <- left_join(CHARLS_w2, CHARLS_ds_w1, by = "id")

# Categorical variable harmonization
CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$h_hypertension <- rep(999,length(CHARLS_w2$id))

# Before following we correct a mistake; some years recorded in the ages variable. We record them in the diagnosed years variable.
CHARLS_w2$da009_1_1_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_1_>1900)])] <- CHARLS_w2$da009_2_1_[which(CHARLS_w2$id %in% CHARLS_w2$id[which(CHARLS_w2$da009_2_1_>1900)])]

# Since the value CHARLS_w2$h_hypertension (wave 1) is missing (NA) for all the individuals for which CHARLS_w2$da007_1_ == 2, we consider:
CHARLS_ds_w2$h_hypertension[which(CHARLS_w2$da007_1_ == 2)] <- 0
# The value CHARLS_w2$da007_1_ is missing for 1373 individuals with diagnosed age or year. Therefore, we compute these individuals as having hypertension
CHARLS_ds_w2$h_hypertension[which(CHARLS_w2$da007_1_ == 1 | (CHARLS_w2$h_hypertension == 1) | (is.na(CHARLS_w2$da007_1_) & (!is.na(CHARLS_w2$da009_1_1_) | !is.na(CHARLS_w2$da009_2_1_))))] <- 1

# Continuous variable harmonization
CHARLS_ds_w2$h_hypertension_age <- rep(999,length(CHARLS_w2$id))
CHARLS_ds_w2$h_hypertension_age[which(CHARLS_ds_w2$h_hypertension == 0)] <- 996
# Use of diagnosed year
CHARLS_ds_w2$h_hypertension_age[which(CHARLS_ds_w2$h_hypertension == 1 & CHARLS_w2$ybirth>1850)] <- CHARLS_w2$da009_1_1_[which(CHARLS_ds_w2$h_hypertension == 1 & CHARLS_w2$ybirth>1850)] - CHARLS_w2$ybirth[which(CHARLS_ds_w2$h_hypertension == 1 & CHARLS_w2$ybirth>1850)]
# Use of diagnosed age for the individuals the previous do not apply due to missing
CHARLS_ds_w2$h_hypertension_age[which(CHARLS_ds_w2$h_hypertension == 1 & (is.na(CHARLS_w2$da009_1_1_) | CHARLS_w2$ybirth<1850))] <- CHARLS_w2$da009_2_1_[which(CHARLS_ds_w2$h_hypertension == 1 & (is.na(CHARLS_w2$da009_1_1_) | CHARLS_w2$ybirth<1850))]
# Use of ages obtained in wave 1
CHARLS_ds_w2$h_hypertension_age[which(CHARLS_ds_w2$h_hypertension == 1 & !is.na(CHARLS_w2$h_hypertension_age) & !CHARLS_w2$h_hypertension_age %in% miss_values_vector)] <- CHARLS_w2$h_hypertension_age[which(CHARLS_ds_w2$h_hypertension == 1 & !is.na(CHARLS_w2$h_hypertension_age) & !CHARLS_w2$h_hypertension_age %in% miss_values_vector)]
CHARLS_ds_w2$h_hypertension_age <- car::recode(CHARLS_ds_w2$h_hypertension_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- CHARLS_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- CHARLS_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(CHARLS_ds_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(CHARLS_w2$da007_1_)) & CHARLS_w2$da007_1_ == 2)),
  sum(CHARLS_w2$da007_1_ == 1 | (CHARLS_w2$h_hypertension == 1) | (is.na(CHARLS_w2$da007_1_) & (!is.na(CHARLS_w2$da009_1_1_) | !is.na(CHARLS_w2$da009_2_1_))),na.rm=T)
)
BeforeH <- c(X[1:2],length(CHARLS_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

```



<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

charlslist <- lmlist # CHARLS list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_hypertension` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(hd_vbl %in% names(get0(paste0("CHARLS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- charlslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- charlslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_hypertension_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("CHARLS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- charlslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- charlslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```




# Quality estimation

No comments







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





