---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01D010` | `w01D002` |`w01D601m`|`w01D601y`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** | `The current retirement state of a respondent (if currently we do not make application activity)`|`Main job`|`Day of retirement (unit: month)`|`Day of retirement (unit: year)`|`month of birth`|`year of birth`|
| **Table name**  | `w01_main_e`|`w01_main_e`| `w01_main_e`|`w01_main_e`| `mbirth`|`ybirth`|
| **Categories** |  `1 = Worked before but currently retired`<br/>`3 = Worked before and intend to work in the future`<br/>`5 = Never had a job before` | `1 = Wage workers`<br/>`2 = Self employed`<br/>`3 = Non wage family worker(for 18 hours or more per week)`<br/>`4 = Non wage family worker(for less than 18 hours)` |`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` | `-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` |  |  |
| **Description** |  |  |  |  |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01D010','w01D002','w01D601m','w01D601y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/mbirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,mbirth, by ="id")
rm(mbirth)
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth, by ="id")
rm(ybirth)

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01D010
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D010')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01D601m
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w01D601m')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w1,!vbl %in% vbl_miss), aes(w01D601m)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w1$w01D601y
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w01D601y')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w1,!vbl %in% vbl_miss), aes(w01D601y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w1,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w1$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w1,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable `w01D010` it has to be recoded as follows:

* `change 3,5 into 0`
* `keep up 1 into 1`
* `w01D002 == 1,2 or 3 into 0`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = date of retirement - date of birth`
* `-8 into 997`
* `-9 into 998`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$retired <- car::recode(KLOSA_w1$w01D010,"c(3,5) = 0; NA = 999")
KLOSA_ds_w1$retired[which(KLOSA_w1$w01D002 %in% c(1,2,3))] <- 0

# Continuous variable harmonization
KLOSA_w1$month <- car::recode(KLOSA_w1$w01D601m, "-9 = 998; -8 = 997; NA = 999")
KLOSA_w1$year <- car::recode(KLOSA_w1$w01D601y, "-9 = 998; -8 = 997; NA = 999")

#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

KLOSA_ds_w1$age_retired <- comp_age(y_birth=KLOSA_w1$ybirth, m_birth=KLOSA_w1$mbirth , a_year=KLOSA_w1$year, a_month=KLOSA_w1$month, miss=miss_values_vector)
KLOSA_ds_w1$age_retired[which(KLOSA_ds_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(KLOSA_ds_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02D006` |`w02D002`|`w02D501m`|`w02D501y`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** | `The respondent's status of labor market`|`Main job`|`Since last interview, the time of retirement (mm) (a new retiree)`|`Since last interview, the time of retirement (yyyy) (a new retiree)`|`month of birth`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`|`mbirth`|`ybirth`|
| **Categories** | `1 = Never had a job before`<br/>`3 = Currently retired (no intent to work unless circumstances change)`<br/>`5 = Intend to work if the wage and working conditions meet my expectations and circumstances are good`<br/>`7 = Intend to work if the wage and working conditions meet my expectations`<br/>`9 = Intend to work even if the wage and working conditions are slightly below my expectations` |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |`-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` | `-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` |  |  |
| **Description** |  |  |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02D006','w02D002','w02D501m','w02D501y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/mbirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,mbirth, by ="id")
rm(mbirth)
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth, by ="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02D006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D006')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02D501m
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w02D501m')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w2,!vbl %in% vbl_miss), aes(w02D501m)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w2$w02D501y
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w02D501y')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w2,!vbl %in% vbl_miss), aes(w02D501y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w2,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w2$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w2,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable `w02D006` it has to be recoded as follows:

* `change 1,5,7 or 9 into 0`
* `change 3 into 1`
* `NA into 999`
* `w02D002 == 1,2 or 3 into 0`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = date of retirement - date of birth`
* `-8 into 997`
* `-9 into 998`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$retired <- car::recode(KLOSA_w2$w02D006,"c(1,5,7,9) = 0; 3 = 1; NA = 999")
KLOSA_ds_w2$retired[which(KLOSA_w2$w02D002 %in% c(1,2,3))] <- 0

KLOSA_w2 <- left_join(KLOSA_w2,KLOSA_ds_w1, by="id")

# Continuous variable harmonization
KLOSA_w2$month <- car::recode(KLOSA_w2$w02D501m, "-9 = 998; -8 = 997; NA = 999")
KLOSA_w2$year <- car::recode(KLOSA_w2$w02D501y, "-9 = 998; -8 = 997; NA = 999")

#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

KLOSA_ds_w2$age_retired <- comp_age(y_birth=KLOSA_w2$ybirth, m_birth=KLOSA_w2$mbirth , a_year=KLOSA_w2$year, a_month=KLOSA_w2$month, miss=miss_values_vector)
KLOSA_ds_w2$age_retired[which(!is.na(KLOSA_w2$age_retired) & !KLOSA_w2$age_retired %in% miss_values_vector)] <- KLOSA_w2$age_retired[which(!is.na(KLOSA_w2$age_retired) & !KLOSA_w2$age_retired %in% miss_values_vector)]
KLOSA_ds_w2$age_retired[which(KLOSA_ds_w2$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(KLOSA_ds_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03D006` |`w03D002`|`w03D501m`|`w03D501y`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** | `The respondent's status of labor market`|`Main job`|`Since last interview, the time of retirement (mm) (a new retiree)`|`Since last interview, the time of retirement (yyyy) (a new retiree)`|`month of birth`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`mbirth`|`ybirth`|
| **Categories** | `1 = Never had a job before`<br/>`3 = Currently retired (no intent to work unless circumstances change)`<br/>`5 = Intend to work if the wage and working conditions meet my expectations and circumstances are good`<br/>`7 = Intend to work if the wage and working conditions meet my expectations`<br/>`9 = Intend to work even if the wage and working conditions are slightly below my expectations` |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |`-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` | `-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` |  |  |
| **Description** |  |  |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03D006','w03D002','w03D501m','w03D501y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)
load(paste0(datafolder,"w3/mbirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,mbirth, by ="id")
rm(mbirth)
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth, by ="id")
rm(ybirth)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03D006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D006')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03D501m
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w03D501m')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w3,!vbl %in% vbl_miss), aes(w03D501m)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w3$w03D501y
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w03D501y')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w3,!vbl %in% vbl_miss), aes(w03D501y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w3,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w3$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w3,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable `w03D006` it has to be recoded as follows:

* `change 1,5,7 or 9 into 0`
* `change 3 into 1`
* `NA into 999`
* `w03D002 == 1,2 or 3 into 0`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = date of retirement - date of birth`
* `-8 into 997`
* `-9 into 998`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$retired <- car::recode(KLOSA_w3$w03D006,"c(1,5,7,9) = 0; 3 = 1; NA = 999")
KLOSA_ds_w3$retired[which(KLOSA_w3$w03D002 %in% c(1,2,3))] <- 0

# Continuous variable harmonization
KLOSA_w3$month <- car::recode(KLOSA_w3$w03D501m, "-9 = 998; -8 = 997; NA = 999")
KLOSA_w3$year <- car::recode(KLOSA_w3$w03D501y, "-9 = 998; -8 = 997; NA = 999")

#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

KLOSA_ds_w3$age_retired <- comp_age(y_birth=KLOSA_w3$ybirth, m_birth=KLOSA_w3$mbirth , a_year=KLOSA_w3$year, a_month=KLOSA_w3$month, miss=miss_values_vector)
KLOSA_ds_w3$age_retired[which(!is.na(KLOSA_w3$age_retired) & !KLOSA_w3$age_retired %in% miss_values_vector)] <- KLOSA_w3$age_retired[which(!is.na(KLOSA_w3$age_retired) & !KLOSA_w3$age_retired %in% miss_values_vector)]
KLOSA_ds_w3$age_retired[which(KLOSA_ds_w3$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(KLOSA_ds_w3,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

```



### Wave 4


#### Study-specific variable description

| **Name** | `w04D006` |`w04D002`|`w04D501m`|`w04D501y`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** | `The respondent's status of labor market`|`Main job`|`Since last interview, the time of retirement (mm) (a new retiree)`|`Since last interview, the time of retirement (yyyy) (a new retiree)`|`month of birth`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`w04_main_e_spss`| `w04_main_e_spss`|`mbirth`|`ybirth`|
| **Categories** | `1 = Never had a job before`<br/>`3 = Currently retired (no intent to work unless circumstances change)`<br/>`5 = Intend to work if the wage and working conditions meet my expectations and circumstances are good`<br/>`7 = Intend to work if the wage and working conditions meet my expectations`<br/>`9 = Intend to work even if the wage and working conditions are slightly below my expectations` |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`| `continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |`-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` | `-9 = Do not know`<br/>`-8 = Refuse to answer`<br/>`NA` |  |  |
| **Description** |  |  |  |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04D006','w04D002','w04D501m','w04D501y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/mbirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,mbirth, by ="id")
rm(mbirth)
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth, by ="id")
rm(ybirth)

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04D006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D006')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04D501m
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w04D501m')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w4,!vbl %in% vbl_miss), aes(w04D501m)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w4$w04D501y
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w04D501y')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w4,!vbl %in% vbl_miss), aes(w04D501y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w4,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- KLOSA_w4$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(KLOSA_w4,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable `w04D006` it has to be recoded as follows:

* `change 1,5,7 or 9 into 0`
* `change 3 into 1`
* `NA into 999`
* `w04D002 == 1,2 or 3 into 0`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = date of retirement - date of birth`
* `-8 into 997`
* `-9 into 998`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$retired <- car::recode(KLOSA_w4$w04D006,"c(1,5,7,9) = 0; 3 = 1; NA = 999")
KLOSA_ds_w4$retired[which(KLOSA_w4$w04D002 %in% c(1,2,3))] <- 0

# Continuous variable harmonization
KLOSA_w4$month <- car::recode(KLOSA_w4$w04D501m, "-9 = 998; -8 = 997; NA = 999")
KLOSA_w4$year <- car::recode(KLOSA_w4$w04D501y, "-9 = 998; -8 = 997; NA = 999")

#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

KLOSA_ds_w4$age_retired <- comp_age(y_birth=KLOSA_w4$ybirth, m_birth=KLOSA_w4$mbirth , a_year=KLOSA_w4$year, a_month=KLOSA_w4$month, miss=miss_values_vector)
KLOSA_ds_w4$age_retired[which(!is.na(KLOSA_w4$age_retired) & !KLOSA_w4$age_retired %in% miss_values_vector)] <- KLOSA_w4$age_retired[which(!is.na(KLOSA_w4$age_retired) & !KLOSA_w4$age_retired %in% miss_values_vector)]
KLOSA_ds_w4$age_retired[which(KLOSA_ds_w4$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(KLOSA_ds_w4,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}


```






<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

klosalist <- lmlist # KLOSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `retired` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `age_retired` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```


# Quality estimation







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





