---
title: "Sick or disabled"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sickdisDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sickdisDS.R')
```



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01D002` | `w01D007` | `w01D003` | `w01D006` |
|-|-|-|-|-|
| **Label** | `Main job`|`The reason that do not work in spite of having found a job`|`A reason limiting work in round trip the average of less than 18 hours`|`Are you able to work if you are offered a job right now?`|
| **Table name**  | `w01_main_e`| `w01_main_e`| `w01_main_e`|`w01_main_e`|
| **Categories** | `1 = Wage workers`<br/>`2 = Self employed`<br/>`3 = Non wage family worker(for 18 hours or more per week)`<br/>`4 = Non wage family worker(for less than 18 hours)` | `1 = Health problems`<br/>`2 = Childrearing or housework`<br/>`3 = Studentship`<br/>`4 = Wanted to take a break`<br/>`5 = Not enough work to do`<br/>`6 = Other` | `1 = Health problems`<br/>`2 = Childrearing or housework`<br/>`3 = Studentship`<br/>`4 = Wanted to take a break`<br/>`5 = Not enough work to do`<br/>`6 = Other` |`1 = Yes`<br/>`5 = No`|
| **Missings** | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01D002','w01D007','w01D003','w01D006'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01D007
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D007')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01D003
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D003')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01D006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01D006')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01D006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `w01D003 == 1 or w01D007 == 1 into 1`
* `w01D002 == 1,2 or 3 or w01D003 == 2,3,4,5 or 6 or w01D006 == 1 or w01D007 == 2,3,4,5 or 6 into 0`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$sickdis <- rep(999,length(KLOSA_w1$id))
KLOSA_ds_w1$sickdis[which(KLOSA_w1$w01D002 != 4 | KLOSA_w1$w01D003 != 1)] <- 0
KLOSA_ds_w1$sickdis[which(KLOSA_w1$w01D006 == 1 | KLOSA_w1$w01D007 != 1)] <- 0
KLOSA_ds_w1$sickdis[which(rowSums(KLOSA_w1[,c("w01D003","w01D007")]==1,na.rm = T)>0)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** |`w02D002`| `w02D405` |`w02D003`|`w02D404`|
|-|-|-|-|-|
| **Label** |`Main job`| `The reason why do not have a job, even though a suitable job is existed(a job seeker/an unemployed person)`|`A reason of limiting work in round trip _the average of less than 18 hours`|`Willing of employment, if a suitable job is existed(a job seeker/an unemployed person)`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`|
| **Categories** |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`| `1 = Need to care for a family member`<br/>`2 = Housework`<br/>`3 = No financial need`<br/>`4 = Old age`<br/>`5 = Poor health`<br/>`6 = Wish to take a break`<br/>`7 = (After retirement) Do not want to work`<br/>`8 = Others` | `1 = Health problems`<br/>`2 = Childcare or housework`<br/>`3 = Attending school`<br/>`4 = Wanted to take a break`<br/>`5 = Not enough work to do`<br/>`6 = Others` |`1 = yes`<br/>`5 = no`|
| **Missings** | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02D002','w02D405','w02D003','w02D404'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02D405
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D405')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D405))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02D003
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D003')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02D404
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02D404')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02D404))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `w02D003 == 1 or w02D405 == 1 into 1`
* `w02D002 == 1,2 or 3 or w02D003 == 2,3,4,5 or 6 or w02D404 == 1 or w02D405 == 2,3,4,5,6,7 or 8 into 0`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$sickdis <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$sickdis[which(KLOSA_w2$w02D002 != 4 | KLOSA_w2$w02D003 != 1)] <- 0
KLOSA_ds_w2$sickdis[which(KLOSA_w2$w02D404 == 1 | KLOSA_w2$w02D405 != 1)] <- 0
KLOSA_ds_w2$sickdis[which(rowSums(KLOSA_w2[,c("w02D003","w02D405")]==1,na.rm = T)>0)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

```



### Wave 3



#### Study-specific variable description

| **Name** |`w03D002`| `w03D405` |`w03D003`|`w03D404`|
|-|-|-|-|-|
| **Label** |`Main job`| `The reason why do not have a job, even though a suitable job is existed(a job seeker/an unemployed person)`|`A reason limiting work in round trip the average of less than 18 hours`|`Willing of employment, if a suitable job is existed`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|
| **Categories** |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`| `1 = Need to care for a family member`<br/>`2 = Housework`<br/>`3 = No financial need`<br/>`4 = Old age`<br/>`5 = Poor health`<br/>`6 = Wish to take a break`<br/>`7 = (After retirement) Do not want to work`<br/>`8 = Others` | `1 = Health problems`<br/>`2 = Childcare or housework`<br/>`3 = Attending school`<br/>`4 = Wanted to take a break`<br/>`5 = Not enough work to do`<br/>`6 = Others` |`1 = yes`<br/>`5 = no`|
| **Missings** | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03D002','w03D405','w03D003','w03D404'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03D405
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D405')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D405))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03D003
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D003')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03D404
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03D404')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03D404))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `w03D003 == 1 or w03D405 == 1 into 1`
* `w03D002 == 1,2 or 3 or w03D003 == 2,3,4,5 or 6 or w03D404 == 1 or w03D405 == 2,3,4,5,6,7 or 8 into 0`
* `otherwise into 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$sickdis <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$sickdis[which(KLOSA_w3$w03D002 != 4 | KLOSA_w3$w03D003 != 1)] <- 0
KLOSA_ds_w3$sickdis[which(KLOSA_w3$w03D404 == 1 | KLOSA_w3$w03D405 != 1)] <- 0
KLOSA_ds_w3$sickdis[which(rowSums(KLOSA_w3[,c("w03D003","w03D405")]==1,na.rm = T)>0)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

```



### Wave 4


#### Study-specific variable description

| **Name** |`w04D002`| `w04D405` |`w04D003`|`w04D404`|
|-|-|-|-|-|
| **Label** |`Main job`| `The reason why do not have a job, even though a suitable job is existed(a job seeker/an unemployed person)`|`A reason limiting work in round trip the average of less than 18 hours`|`willing of employment, if a suitable job is existed(a job seeker/an unemployed person)`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`| `w04_main_e_spss`| `w04_main_e_spss`|
| **Categories** |`1 = I am employed by another person or a company and receive wages`<br/>`2 = I am self-employed??`<br/>`3 = I help my family / relative's business without pay for 18 hours or more per week`<br/>`4 = I help my family / relative's business without pay for less than 18 hours a week`| `1 = Need to care for a family member`<br/>`2 = Housework`<br/>`3 = No financial need`<br/>`4 = Old age`<br/>`5 = Poor health`<br/>`6 = Wish to take a break`<br/>`7 = (After retirement) Do not want to work`<br/>`8 = Others` |`1 = Health problems`<br/>`2 = Childcare or housework`<br/>`3 = Attending school`<br/>`4 = Wanted to take a break`<br/>`5 = Not enough work to do`<br/>`6 = Others` |`1 = yes`<br/>`5 = no`|
| **Missings** | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04D002','w04D405','w04D003','w04D404'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04D002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04D405
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D405')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D405))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04D003
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D003')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04D404
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04D404')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04D404))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `w04D003 == 1 or w04D405 == 1 into 1`
* `w04D002 == 1,2 or 3 or w04D003 == 2,3,4,5 or 6 or w04D404 == 1 or w04D405 == 2,3,4,5,6,7 or 8 into 0`
* `otherwise into 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$sickdis <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$sickdis[which(KLOSA_w4$w04D002 != 4 | KLOSA_w4$w04D003 != 1)] <- 0
KLOSA_ds_w4$sickdis[which(KLOSA_w4$w04D404 == 1 | KLOSA_w4$w04D405 != 1)] <- 0
KLOSA_ds_w4$sickdis[which(rowSums(KLOSA_w4[,c("w04D003","w04D405")]==1,na.rm = T)>0)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}


```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
KLOSA_ds_w1$sickdis <- labelled(KLOSA_ds_w1$sickdis, labels = cat_label)
label(KLOSA_ds_w1$sickdis) <- ds_label
KLOSA_ds_w2$sickdis <- labelled(KLOSA_ds_w2$sickdis, labels = cat_label)
label(KLOSA_ds_w2$sickdis) <- ds_label
KLOSA_ds_w3$sickdis <- labelled(KLOSA_ds_w3$sickdis, labels = cat_label)
label(KLOSA_ds_w3$sickdis) <- ds_label
KLOSA_ds_w4$sickdis <- labelled(KLOSA_ds_w4$sickdis, labels = cat_label)
label(KLOSA_ds_w4$sickdis) <- ds_label

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$sickdis <- car::recode(KLOSA_m_ds_w1$sickdis, "miss_values_vector=NA")
KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$sickdis <- car::recode(KLOSA_m_ds_w2$sickdis, "miss_values_vector=NA")
KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$sickdis <- car::recode(KLOSA_m_ds_w3$sickdis, "miss_values_vector=NA")
KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$sickdis <- car::recode(KLOSA_m_ds_w4$sickdis, "miss_values_vector=NA")


tt <-    frq(KLOSA_ds_w1$sickdis)[[1]][,c(1:2,4)]
tt[4] <- frq(KLOSA_ds_w2$sickdis)[[1]][,c(4)]
tt[5] <- frq(KLOSA_ds_w3$sickdis)[[1]][,c(4)]
tt[6] <- frq(KLOSA_ds_w4$sickdis)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(KLOSA_ds_w1$sickdis), length(KLOSA_ds_w2$sickdis), length(KLOSA_ds_w3$sickdis), length(KLOSA_ds_w4$sickdis)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4")
kable(tt)

dbb <- merge(KLOSA_m_ds_w1[,c("id","sickdis")], KLOSA_m_ds_w2[,c("id","sickdis")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, KLOSA_m_ds_w3[,c("id","sickdis")], by="id", all=T)
dbb <- merge(dbb, KLOSA_m_ds_w4[,c("id","sickdis")], by="id", suffixes = c(".w3",".w4"), all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.KLOSA <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)

for(index in seq_along(l.KLOSA)){
  sickdis <- l.KLOSA[[index]]
  save(sickdis, file = paste0(datafolder,names(l.KLOSA)[index],"/sickdis.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





