---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mbirthDS.R')
```



# Data process

## Korea


### Wave 1 

#### Study-specific variable description

| **Name** | `w01A001` |
|----------|------------|
| **Label** | `The date when the respondent is born` |
| **Table name** | `w01_main_e` |
| **Description** |  |

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_birth','KLOSA.w01_main_e',
                         variables=list('w01A001'), missings = TRUE)
KLOSA_w1_birth <- opal.execute(o,'KLOSA_w1_birth')
```


**R script:**

```{r pre1}
#This function return a table with the date of birth separated by columns:
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 6)))))
  }
  colnames(D) <- c("Year", "Month" )
  D
}

KLOSA_w1_birth <- cbind(KLOSA_w1_birth, Date_of_birth(KLOSA_w1_birth$w01A001))
```


```{r local1, echo=F}

vari <- KLOSA_w1_birth$Month
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Month") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_birth, aes(x=factor(Month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_birth$id)
KLOSA_ds_w1$mbirth <- car::recode(KLOSA_w1_birth$Month, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(KLOSA_w1_birth$Month)
AfterH <- table(KLOSA_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
mbirth <- KLOSA_ds_w1
save(mbirth, file = "../RData/w1/mbirth.RData")
rm(mbirth)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$mbirth <- car::recode(KLOSA_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description

| **Name** | `w02A002m` |
|----------|------------|
| **Label** | `The date when the respondent was born(mm)` |
| **Table name** | `w02_main_e_spss` |
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_mbirth','KLOSA.w02_main_e_spss',
                         variables=list('w02A002m'), missings = TRUE)
KLOSA_w2_mbirth <- opal.execute(o,'KLOSA_w2_mbirth')
```

```{r local2, echo=F}
vari <- KLOSA_w2_mbirth$w02A002m
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w02A002m") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_mbirth, aes(x=factor(w02A002m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_mbirth$id)
KLOSA_ds_w2$mbirth <- car::recode(KLOSA_w2_mbirth$w02A002m, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(KLOSA_w2_mbirth$w02A002m)
AfterH <- table(KLOSA_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
mbirth <- KLOSA_ds_w2
save(mbirth, file = "../RData/w2/mbirth.RData")
rm(mbirth)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$mbirth <- car::recode(KLOSA_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

| **Name** | `w03A002m` |
|----------|------------|
| **Label** | `The date when the respondent is born(mm)` |
| **Table name** | `w03_main_e_spss_albert` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_mbirth','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03A002m'), missings = TRUE)
KLOSA_w3_mbirth <- opal.execute(o,'KLOSA_w3_mbirth')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_mbirth$id <- substr(KLOSA_w3_mbirth$id,1,nchar(KLOSA_w3_mbirth$id)-2)

```

```{r local3, echo=F}
vari <- KLOSA_w3_mbirth$w03A002m
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w03A002m") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_mbirth, aes(x=factor(w03A002m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_mbirth$id)
KLOSA_ds_w3$mbirth <- car::recode(KLOSA_w3_mbirth$w03A002m, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(KLOSA_w3_mbirth$w03A002m)
AfterH <- table(KLOSA_ds_w3$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
mbirth <- KLOSA_ds_w3
save(mbirth, file = "../RData/w3/mbirth.RData")
rm(mbirth)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$mbirth <- car::recode(KLOSA_m_ds_w3$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4 

#### Study-specific variable description

| **Name** | `w04A002m` |
|----------|------------|
| **Label** | `The date when the respondent is born(mm)` |
| **Table name** | `w04_main_e_spss` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_mbirth','KLOSA.w04_main_e_spss',
                         variables=list('w04A002m'), missings = TRUE)
KLOSA_w4_mbirth <- opal.execute(o,'KLOSA_w4_mbirth')
```

```{r local4, echo=F}
vari <- KLOSA_w4_mbirth$w04A002m
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w04A002m") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_mbirth, aes(x=factor(w04A002m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_mbirth$id)
KLOSA_ds_w4$mbirth <- car::recode(KLOSA_w4_mbirth$w04A002m, "NA=999")
KLOSA_ds_w4$mbirth <- labelled(KLOSA_ds_w4$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(KLOSA_w4_mbirth$w04A002m)
AfterH <- table(KLOSA_ds_w4$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL4, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
mbirth <- KLOSA_ds_w4
save(mbirth, file = "../RData/w4/mbirth.RData")
rm(mbirth)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$mbirth <- car::recode(KLOSA_m_ds_w4$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

l.hds <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("KLOSA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("KLOSA_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)



```




# Quality estimation
No comments.





```{r closeRsession, echo=FALSE}
opal.logout(o)
```
