---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


## Korea

### Wave 1 

#### Study-specific variable description



| **Name** | `w01A001_age` |
|-|-|
| **Label** | `Respondent age` |
| **Table name** | `w01_main_e` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_age','KLOSA.w01_main_e',
                         variables=list('w01A001_age'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_age <- opal.execute(o,'KLOSA_w1_age')
vari <- KLOSA_w1_age$w01A001_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w01A001_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1_age, aes(w01A001_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_age$id)
KLOSA_ds_w1$age <- car::recode(KLOSA_w1_age$w01A001_age, "NA=999")
KLOSA_ds_w1$age <- labelled(KLOSA_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(KLOSA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
age <- KLOSA_ds_w1
save(age, file = "../RData/w1/age.RData")
rm(age)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$age <- car::recode(KLOSA_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description



| **Name** | `w02A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w02_main_e_spss` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_age','KLOSA.w02_main_e_spss',
                         variables=list('w02A002_age'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_age <- opal.execute(o,'KLOSA_w2_age')
vari <- KLOSA_w2_age$w02A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w02A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w2_age, aes(w02A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_age$id)
KLOSA_ds_w2$age <- car::recode(KLOSA_w2_age$w02A002_age, "NA=999")
KLOSA_ds_w2$age <- labelled(KLOSA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(KLOSA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
age <- KLOSA_ds_w2
save(age, file = "../RData/w2/age.RData")
rm(age)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$age <- car::recode(KLOSA_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3 

#### Study-specific variable description



| **Name** | `w03A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w03_main_e_spss_albert` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_age','KLOSA.w03_main_e_spss_albert', variables=list('w03A002_age'), missings = TRUE)
KLOSA_w3_age <- opal.execute(o,'KLOSA_w3_age')

# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_age$id <- substr(KLOSA_w3_age$id,1,nchar(KLOSA_w3_age$id)-2)

```

```{r local3, echo=F}
vari <- KLOSA_w3_age$w03A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w03A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w3_age, aes(w03A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_age$id)
KLOSA_ds_w3$age <- car::recode(KLOSA_w3_age$w03A002_age, "NA=999")
KLOSA_ds_w3$age <- labelled(KLOSA_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(KLOSA_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
age <- KLOSA_ds_w3
save(age, file = "../RData/w3/age.RData")
rm(age)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$age <- car::recode(KLOSA_m_ds_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```






### Wave 4 

#### Study-specific variable description



| **Name** | `w04A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w04_main_e_spss` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_age','KLOSA.w04_main_e_spss',
                         variables=list('w04A002_age'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_age <- opal.execute(o,'KLOSA_w4_age')
vari <- KLOSA_w4_age$w04A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w04A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w4_age, aes(w04A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 2 years, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_age$id)
KLOSA_ds_w4$age <- car::recode(KLOSA_w4_age$w04A002_age, "NA=999")
KLOSA_ds_w4$age <- labelled(KLOSA_ds_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(KLOSA_ds_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation4, echo=F}
```





```{r importOPAL4, echo=F}

#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
age <- KLOSA_ds_w4
save(age, file = "../RData/w4/age.RData")
rm(age)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$age <- car::recode(KLOSA_m_ds_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
