---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process


## Korea

### Wave 1 

#### Study-specific variable description



| **Name** | `w01A001_age` |
|-|-|
| **Label** | `Respondent age` |
| **Table name** | `w01_main_e` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_age','KLOSA.w01_main_e',
                         variables=list('w01A001_age'), missings = TRUE)
KLOSA_w1_age <- opal.execute(o,'KLOSA_w1_age')
```

```{r local1, echo=F}
vari <- KLOSA_w1_age$w01A001_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w01A001_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1_age, aes(w01A001_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_age$id)
KLOSA_ds_w1$age <- car::recode(KLOSA_w1_age$w01A001_age, "NA=999")
KLOSA_ds_w1$age <- labelled(KLOSA_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```








### Wave 2 

#### Study-specific variable description



| **Name** | `w02A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w02_main_e_spss` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_age','KLOSA.w02_main_e_spss',
                         variables=list('w02A002_age'), missings = TRUE)
KLOSA_w2_age <- opal.execute(o,'KLOSA_w2_age')
```

```{r local2, echo=F}
vari <- KLOSA_w2_age$w02A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w02A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w2_age, aes(w02A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_age$id)
KLOSA_ds_w2$age <- car::recode(KLOSA_w2_age$w02A002_age, "NA=999")
KLOSA_ds_w2$age <- labelled(KLOSA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
```








### Wave 3 

#### Study-specific variable description



| **Name** | `w03A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w03_main_e_spss_albert` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_age','KLOSA.w03_main_e_spss_albert', variables=list('w03A002_age'), missings = TRUE)
KLOSA_w3_age <- opal.execute(o,'KLOSA_w3_age')

# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_age$id <- substr(KLOSA_w3_age$id,1,nchar(KLOSA_w3_age$id)-2)

```

```{r local3, echo=F}
vari <- KLOSA_w3_age$w03A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w03A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w3_age, aes(w03A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_age$id)
KLOSA_ds_w3$age <- car::recode(KLOSA_w3_age$w03A002_age, "NA=999")
KLOSA_ds_w3$age <- labelled(KLOSA_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}
```







### Wave 4 

#### Study-specific variable description



| **Name** | `w04A002_age` |
|-|-|
| **Label** | `The respondont's age` |
| **Table name** | `w04_main_e_spss` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_age','KLOSA.w04_main_e_spss',
                         variables=list('w04A002_age'), missings = TRUE)
KLOSA_w4_age <- opal.execute(o,'KLOSA_w4_age')
```

```{r local4, echo=F}
vari <- KLOSA_w4_age$w04A002_age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w04A002_age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w4_age, aes(w04A002_age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 2 years, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_age$id)
KLOSA_ds_w4$age <- car::recode(KLOSA_w4_age$w04A002_age, "NA=999")
KLOSA_ds_w4$age <- labelled(KLOSA_ds_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation4, echo=F}
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")
rm(labelling)
labelling <- labelling_c
rm(summaries)
summaries <- summaries_c

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))

# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation


```{r, echo=FALSE}

klosa_age <- Reduce(full_join, lapply(l.hds, \(.x) rename_with(.x[[1]], .fn = \(.yn) paste(.yn, .x[[2]], sep = "_"), .cols = `age`)))
klosa_age |> 
  pivot_longer(cols = -id) |> 
  arrange(id,name) |> 
  filter(!is.na(value)) |> 
  group_by(id) |> 
  mutate(odd = any(value<=lag(value, default = -Inf))) |> 
  ungroup() |> 
  filter(odd) |> 
  mutate(name = sub("age_", "", name)) |> 
  pivot_wider(id_cols = "id", names_from = "name") |> 
  kable(caption = "Imposible age trajectories")
```

**R script:**

```{r}
# Corrections after previous trajectories and birth year corrections

KLOSA_ds_w1$age[KLOSA_ds_w1$id=="13141"] <- 70
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="13141"] <- 72
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="13142"] <- 62
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="13142"] <- 64
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="23131"] <- 63
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="23131"] <- 65
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="24743"] <- 97
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="24743"] <- 99
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="29623"] <- 81
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="29623"] <- 83
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="32622"] <- 70
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="32622"] <- 72
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="37072"] <- 57
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="37072"] <- 59
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="40522"] <- 59
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="40522"] <- 61
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="44591"] <- 68
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="44591"] <- 70
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="52301"] <- 60
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="52301"] <- 62
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="52922"] <- 59
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="52922"] <- 61

KLOSA_ds_w1$age[KLOSA_ds_w1$id=="4382"] <- 67
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="4382"] <- 69
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="20211"] <- 66
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="20211"] <- 68
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="24502"] <- 58
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="24502"] <- 60
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="32301"] <- 54
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="32301"] <- 56
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="32302"] <- 55
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="32302"] <- 57
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="37071"] <- 59
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="37071"] <- 61
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="39191"] <- 77
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="39191"] <- 79
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="40542"] <- 53
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="40542"] <- 55
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="49241"] <- 60
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="49241"] <- 62
KLOSA_ds_w1$age[KLOSA_ds_w1$id=="54131"] <- 48
KLOSA_ds_w2$age[KLOSA_ds_w2$id=="54131"] <- 50

```

```{r, echo=FALSE}
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}
klosa_age <- Reduce(full_join, lapply(l.hds, \(.x) rename_with(.x[[1]], .fn = \(.yn) paste(.yn, .x[[2]], sep = "_"), .cols = `age`)))

klosa_age |> 
  pivot_longer(cols = -id) |> 
  arrange(id,name) |> 
  group_by(id) |> 
  mutate(odd = any(!is.na(lag(value)) & value != 2+lag(value))) |> 
  ungroup() |> 
  filter(!is.na(value)) |> 
  filter(odd) |> 
  mutate(name = sub("age_", "", name)) |> 
  pivot_wider(id_cols = "id", names_from = "name") |> 
  select(id, W1, W2, W3, W4) |> 
  kable(caption = "Other non-KLOSA-consistent age trajectories")
```

```{r}
# Corrections after previous trajectories and birth year corrections

KLOSA_ds_w1$age[KLOSA_ds_w1$id=="982"] <- 54
KLOSA_ds_w3$age[KLOSA_ds_w3$id=="29122"] <- 65
KLOSA_ds_w3$age[KLOSA_ds_w3$id=="37221"] <- 54

```

``` {r save, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

lmlist <- labelling(lmlist[[1]],lmlist[[2]])
# Saving tibbles
savingRD(lmlist[[1]],vbl_name=hd_vbl)


```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
