---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```




<!-- ########################################################## --> 

# Data process


## Korea

### Wave 1 

#### Study-specific variable description



| **Name** | `w01gender1`|
|-|-|
| **Label** | `Respondent sex`|
| **Table name** |`w01_main_e`|
| **Categories** |`1 = Male`<br/>`5 = Female`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_sex','KLOSA.w01_main_e',
                         variables=list('w01gender1'), missings = TRUE)
KLOSA_w1_sex <- opal.execute(o,'KLOSA_w1_sex')
```

```{r local1, echo=FALSE}
vari <- KLOSA_w1_sex$w01gender1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1_sex, aes(x=factor(w01gender1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_sex$id)
KLOSA_ds_w1$sex <- car::recode(KLOSA_w1_sex$w01gender1, "5=0; NA=999")
KLOSA_ds_w1$sex <- labelled(KLOSA_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- KLOSA_ds_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(KLOSA_ds_w1$sex)
BeforeH <- table(KLOSA_w1_sex$w01gender1)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```






### Wave 2 

#### Study-specific variable description



| **Name** | `w02gender1`|
|-|-|
| **Label** | `The respondont's sex`|
| **Table name** |`w02_main_e_spss`|
| **Categories** |`1 = Male`<br/>`5 = Female`|
| **Description** |  |




```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_sex','KLOSA.w02_main_e_spss',
                         variables=list('w02gender1'), missings = TRUE)
KLOSA_w2_sex <- opal.execute(o,'KLOSA_w2_sex')
```

```{r local2, echo=FALSE}
vari <- KLOSA_w2_sex$w02gender1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_sex, aes(x=factor(w02gender1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "Female" into 0`
* `keep "Male" into 1`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_sex$id)
KLOSA_ds_w2$sex <- car::recode(KLOSA_w2_sex$w02gender1, "5=0; NA=999")
KLOSA_ds_w2$sex <- labelled(KLOSA_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- KLOSA_ds_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(KLOSA_ds_w2$sex)
BeforeH <- table(KLOSA_w2_sex$w02gender1)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```








### Wave 3 

#### Study-specific variable description


| **Name** | `w03gender1`|
|-|-|
| **Label** | `The respondont's sex`|
| **Table name** |`w03_main_e_spss_albert`|
| **Categories** |`1 = Male`<br/>`5 = Female`|
| **Description** |  |



```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_sex','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03gender1'), missings = TRUE)
KLOSA_w3_sex <- opal.execute(o,'KLOSA_w3_sex')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_sex$id <- substr(KLOSA_w3_sex$id,1,nchar(KLOSA_w3_sex$id)-2)

```

```{r local3, echo=FALSE}
vari <- KLOSA_w3_sex$w03gender1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_sex, aes(x=factor(w03gender1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "Female" into 0`
* `keep "Male" into 1`


**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_sex$id)
KLOSA_ds_w3$sex <- car::recode(KLOSA_w3_sex$w03gender1, "5=0; NA=999")
KLOSA_ds_w3$sex <- labelled(KLOSA_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- KLOSA_ds_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(KLOSA_ds_w3$sex)
BeforeH <- table(KLOSA_w3_sex$w03gender1)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```







### Wave 4 

#### Study-specific variable description


| **Name** | `w04gender1`|
|-|-|
| **Label** | `The respondont's sex`|
| **Table name** |`w03_main_e_spss_albert`|
| **Categories** |`1 = Male`<br/>`5 = Female`|
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_sex','KLOSA.w04_main_e_spss',
                         variables=list('w04gender1'), missings = TRUE)
KLOSA_w4_sex <- opal.execute(o,'KLOSA_w4_sex')
```

```{r local4, echo=FALSE}
vari <- KLOSA_w4_sex$w04gender1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_sex, aes(x=factor(w04gender1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "Female" into 0`
* `keep "Male" into 1`


**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_sex$id)
KLOSA_ds_w4$sex <- car::recode(KLOSA_w4_sex$w04gender1, "5=0; NA=999")
KLOSA_ds_w4$sex <- labelled(KLOSA_ds_w4$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- KLOSA_ds_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
AfterH <- table(KLOSA_ds_w4$sex)
BeforeH <- table(KLOSA_w4_sex$w04gender1)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}
source("../../helpfunctions.r")
```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))

# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)

}
```


# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
