---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Korea
### Wave 1 

#### Study-specific variable description

 

* Name: `W01A006`
* Label: `Currently marital status`
* Categories: 
    + `1 = Currently married or living with a partner`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never married`
* Missings: 
    + `-8 = Refuse to answer`


* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_ms','KLOSA.w01_main_e',
                         variables=list('W01A006'), missings = TRUE)
```

```{r local1,  echo=FALSE}
KLOSA_w1_ms <- opal.execute(o,'KLOSA_w1_ms')
vari <- KLOSA_w1_ms$W01A006
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = "W01A006") 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w1_ms$W01A006, missing_values = c(-8))
ggplot(KLOSA_w1_ms, aes(x=factor(W01A006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Currently married or living with a partner" into 2`
* `recode 2 "Separated" into 3`
* `keep "Divorced" into 3`
* `keep "Widowed or missing (dispersed family)" into 4`
* `recode 5 "Never married" into 1`
* `recode -8 "Refuse to answer"`
* `recode NA into 999`


**R script:**

```{r harmo1,   echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_ms$id)
KLOSA_ds_w1$marital_status <- car::recode(KLOSA_w1_ms$W01A006, "1=2; 2=3; 5=1; -8=997; NA=999")
KLOSA_ds_w1$marital_status <- labelled(KLOSA_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- KLOSA_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(KLOSA_w1_ms$W01A006)
BeforeH <- c(BeforeH[5], BeforeH[1], sum(BeforeH[c(2,3)]), BeforeH[4] )
AfterH <- table(KLOSA_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1->2", "3", "4")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
val_labels(KLOSA_ds_w1) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
marital_status <- KLOSA_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$marital_status <- car::recode(KLOSA_m_ds_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description

 

* Name: `w02marital`
* Label: `In 2008, currently the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never been married`

* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_ms','KLOSA.w02_main_e_spss',
                         variables=list('w02marital'), missings = TRUE)
```

```{r local2,  echo=FALSE}
KLOSA_w2_ms <- opal.execute(o,'KLOSA_w2_ms')
vari <- KLOSA_w2_ms$w02marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_ms$w02marital, missing_values = NA)
ggplot(KLOSA_w2_ms, aes(x=factor(w02marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Currently married or living with a partner" into 2`
* `recode 2 "Separated" into 3`
* `keep "Divorced" into 3`
* `keep "Widowed or missing (dispersed family)" into 4`
* `recode 5 "Never been married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_ms$id)
KLOSA_ds_w2$marital_status <- car::recode(KLOSA_w2_ms$w02marital, "1=2; 2=3;5=1;-9=998; NA=999")
KLOSA_ds_w2$marital_status <- labelled(KLOSA_ds_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- KLOSA_ds_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(KLOSA_w2_ms$w02marital)
BeforeH <- c(BeforeH[5], BeforeH[1], sum(BeforeH[c(2,3)]), BeforeH[4] )
AfterH <- table(KLOSA_ds_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1->2", "3", "4")
kable(C)
```

 
 

 
```{r importOPAL2,  echo=FALSE}
val_labels(KLOSA_ds_w2) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
marital_status <- KLOSA_ds_w2
save(marital_status, file = "../RData/w2/marital_status.RData")
rm(marital_status)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$marital_status <- car::recode(KLOSA_m_ds_w2$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")

#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variable description

 

* Name: `w03marital`
* Label: `In 2010, the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never married`


* Description: 
```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_ms','KLOSA.w03_main_e_spss_albert', variables=list('w03marital'), missings = TRUE)
KLOSA_w3_ms <- opal.execute(o,'KLOSA_w3_ms')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_ms$id <- substr(KLOSA_w3_ms$id,1,nchar(KLOSA_w3_ms$id)-2)

```

```{r local3,  echo=FALSE}
vari <- KLOSA_w3_ms$w03marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_ms$w03marital, missing_values = NA)
ggplot(KLOSA_w3_ms, aes(x=factor(w03marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Currently married or living with a partner" into 2`
* `recode 2 "Separated" into 3`
* `keep "Divorced" into 3`
* `keep "Widowed or missing (dispersed family)" into 4`
* `recode 5 "Never married" into 1`
* `recode NA into 999`



**R script:**

```{r harmo3,   echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_ms$id)
KLOSA_ds_w3$marital_status <- car::recode(KLOSA_w3_ms$w03marital, "1=2; 2=3; 5=1; NA=999")
KLOSA_ds_w3$marital_status <- labelled(KLOSA_ds_w3$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- KLOSA_ds_w3$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- table(KLOSA_w3_ms$w03marital)
BeforeH <- c(BeforeH[5], BeforeH[1], sum(BeforeH[c(2,3)]), BeforeH[4] )
AfterH <- table(KLOSA_ds_w3$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1->2", "3", "4")
kable(C)
```

 
 

 
```{r importOPAL3,  echo=FALSE}
val_labels(KLOSA_ds_w3) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
marital_status <- KLOSA_ds_w3
save(marital_status, file = "../RData/w3/marital_status.RData")
rm(marital_status)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$marital_status <- car::recode(KLOSA_m_ds_w3$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

#### Study-specific variable description

 

* Name: `w04marital`
* Label: `In 2012, the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never married`



* Description: 
```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_ms','KLOSA.w04_main_e_spss',
                         variables=list('w04marital'), missings = TRUE)
```

```{r local4,  echo=FALSE}
KLOSA_w4_ms <- opal.execute(o,'KLOSA_w4_ms')
vari <- KLOSA_w4_ms$w04marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_ms$w04marital, missing_values = NA)
ggplot(KLOSA_w4_ms, aes(x=factor(w04marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Currently married or living with a partner" into 2`
* `recode 2 "Separated" into 3`
* `keep "Divorced" into 3`
* `keep "Widowed or missing (dispersed family)" into 4`
* `recode 5 "Never married" into 1`
* `recode NA into 999`


**R script:**

```{r harmo4,   echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_ms$id)
KLOSA_ds_w4$marital_status <- car::recode(KLOSA_w4_ms$w04marital, "1=2; 2=3; 5=1; NA=999")
KLOSA_ds_w4$marital_status <- labelled(KLOSA_ds_w4$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- KLOSA_ds_w4$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4,  echo=FALSE}
BeforeH <- table(KLOSA_w4_ms$w04marital)
BeforeH <- c(BeforeH[5], BeforeH[1], sum(BeforeH[c(2,3)]), BeforeH[4] )
AfterH <- table(KLOSA_ds_w4$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1->2", "3", "4")
kable(C)
```

 
 

 
```{r importOPAL4,  echo=FALSE}
val_labels(KLOSA_ds_w4) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
marital_status <- KLOSA_ds_w4
save(marital_status, file = "../RData/w4/marital_status.RData")
rm(marital_status)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$marital_status <- car::recode(KLOSA_m_ds_w4$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")

#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```

