---
title: "Parental education"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/parenteduDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/parenteduDS.R')
```



# Data process


## Korea

### Wave 1 

#### Study-specific variable description

| **Name** | `w01B007` |`w01B017`|
|-|-|-|
| **Label** | `Father's scholarship`| `Mother's scholarship`|
| **Table name** | `w01_main_e`| `w01_main_e`|
| **Categories** | `1 = No formal education(illiterate)` <br/> `2 = No formal education(capable of reading)` <br/> `3 = Elementary school` <br/> `4 = Middle school` <br/> `5 = High school` <br/> `6 = Two-year college` <br/> `7 = College grad` <br/> `8 =  Post` <br/> `9 = Post college (PhD)` <br/> `97 =  Other`|`1 = No formal education(illiterate)` <br/> `2 = No formal education(capable of reading)` <br/> `3 = Elementary school` <br/> `4 = Middle school` <br/> `5 = High school` <br/> `6 = Two-year college` <br/> `7 = College grad` <br/> `8 =  Post` <br/> `9 = Post college (PhD)` <br/> `97 =  Other`|
| **Missings** | `-9 = Do not know`<br/>`-8 =  Refuse to answer`<br/>`NA` |  `-9 = Do not know`<br/>`-8 =  Refuse to answer`<br/>`NA` |
| **Description** |  |  |



```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e', variables=list('w01B007','w01B017'), missings = TRUE)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1') %>% update_labelled()


```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01B007
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01B017
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables its maximum (up to `97`) has to be recoded as follows:

* `1:3 into 2`
* `4:5 into 1`
* `6:9 into 0`
* `97, NA into 999`
* `-9 into 998`
* `-8 into 997`

**R script:**

```{r harmo w1, tidy=FALSE}


KLOSA_ds_w1 <- KLOSA_w1 %>%
  mutate(
    w01B007 = dplyr::recode(w01B007, `97` = -97L),
    w01B017 = dplyr::recode(w01B017, `97` = -97L)
  ) %>%
  mutate(parentedu = do.call(pmax, c(select(., w01B007, w01B017), na.rm = TRUE))) %>%
  mutate(
    parentedu = case_when(
      parentedu %in% c(1:3) ~ 2,
      parentedu %in% c(4:5) ~ 1,
      parentedu %in% c(6:9) ~ 0,
      parentedu %in% c(-8) ~ 997,
      parentedu %in% c(-9) ~ 998,
      TRUE ~ 999
    )
  ) %>%
  select(id, parentedu)
  

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(parentedu))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}
```



### Wave 2

#### Study-specific variable description

Wave 1 variables

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss', variables=list('HHID'), missings = TRUE)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2') %>% 
  update_labelled() %>%
  select(id)

```


#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables keep wave 1 harmonisation

**R script:**

```{r harmo w2}


KLOSA_ds_w2 <- KLOSA_w2 %>%
  left_join(KLOSA_ds_w1, by ="id")
  

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(parentedu))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}
```



### Wave 3

#### Study-specific variable description

Wave 1 variables

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert', variables=list('HHID'), missings = TRUE)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3') %>% 
  update_labelled() %>%
  mutate(id = substr(id, 1, nchar(id) - 2)) %>%
  select(id)

```


#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables keep wave 1 harmonisation

**R script:**

```{r harmo w3}


KLOSA_ds_w3 <- KLOSA_w3 %>%
  left_join(KLOSA_ds_w1, by ="id")
  

```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(parentedu))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}
```




### Wave 4

#### Study-specific variable description

Wave 1 variables

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss', variables=list('HHID'), missings = TRUE)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4') %>% 
  update_labelled() %>%
  select(id)

```


#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables keep wave 1 harmonisation

**R script:**

```{r harmo w4}


KLOSA_ds_w4 <- KLOSA_w4 %>%
  left_join(KLOSA_ds_w1, by ="id")
  

```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(parentedu))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w4, echo=F}
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))

# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
