---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Korea
### Wave 1 

#### Study-specific variable description

 

* Name: `w01A003`
* Label: `Educational background(a school).`
* Categories: 
    + `1 = No formal education (illiterate)`
    + `2 = No formal education (capable of reading)`
    + `3 = Elementary school`
    + `4 = Middle school`
    + `5 = High school`
    + `6 = Two-year college`
    + `7 = College grad`
    + `8 = Post college (Master)`
    + `9 = Post college (PhD)`
    + `97 = Other`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`


* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1_educ','KLOSA.w01_main_e',
                         variables=list('w01A003'), missings = TRUE)
```

```{r local1,  echo=FALSE}
KLOSA_w1_educ <- opal.execute(o,'KLOSA_w1_educ')
vari <- KLOSA_w1_educ$w01A003
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w1_educ$w01A003, missing_values = c(-8,-9))
ggplot(KLOSA_w1_educ, aes(x=factor(w01A003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education (illiterate)" into 0`
* `recode 2 "No formal education (capable of reading)" into 0`
* `recode 3 "Elementary school" into 1`
* `recode 4 "Middle school" into 2`
* `recode 5 "High school" into 2`
* `recode 6 "Two-year college" into 3`
* `recode 7 "College grad" into 3`
* `recode 8 "Post college (Master)" into 3`
* `recode 9 "Post college (PhD)" into 3`
* `recode 97 "Other" into 999`
* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_educ$id)
KLOSA_ds_w1$education <- car::recode(KLOSA_w1_educ$w01A003, "1=0; 2=0; 3=1; 4=2; 5=2; 6=3; 7=3; 8=3; 9=3; 97=999; -8=997; -9=998; NA=999")
KLOSA_ds_w1$education <- labelled(KLOSA_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- KLOSA_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(KLOSA_w1_educ$w01A003)
BeforeH <- c(sum(BeforeH[2:3]), BeforeH[4],sum(BeforeH[5:6]), sum(BeforeH[7:10]), BeforeH[1])
AfterH <- table(KLOSA_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2)->0", "3->1", "(4,5)->2", "(6,7,8,9)->3", "-8->997")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
val_labels(KLOSA_ds_w1) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
education <- KLOSA_ds_w1
save(education, file = "../RData/w1/education.RData")
rm(education)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$education <- car::recode(KLOSA_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")

#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description

 

* Name: `w02A005_`
* Label: `In last interview, respondent's educational background re-answer`
* Categories: 
    + `1 = No formal education (illiterate)`
    + `2 = No formal education (capable of reading)`
    + `3 = Elementary school`
    + `4 = Middle school`
    + `5 = High school`
    + `6 = Two-year college`
    + `7 = College grad`
    + `8 = Post college (Master)`
    + `9 = Post college (PhD)`
    + `97 = Other`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`

* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2_educ','KLOSA.w02_main_e_spss',
                         variables=list('w02A005_'), missings = TRUE)
```

```{r local2,  echo=FALSE}
KLOSA_w2_educ <- opal.execute(o,'KLOSA_w2_educ')
vari <- KLOSA_w2_educ$w02A005_
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w2_educ$w02A005_, missing_values = c(-8,-9))
ggplot(KLOSA_w2_educ, aes(x=factor(w02A005_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education (illiterate)" into 0`
* `recode 2 "No formal education (capable of reading)" into 0`
* `recode 3 "Elementary school" into 1`
* `recode 4 "Middle school" into 2`
* `recode 5 "High school" into 2`
* `recode 6 "Two-year college" into 3`
* `recode 7 "College grad" into 3`
* `recode 8 "Post college (Master)" into 3`
* `recode 9 "Post college (PhD)" into 3`
* `recode 97 "Other" into 999`
* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_educ$id)
KLOSA_ds_w2$education <- car::recode(KLOSA_w2_educ$w02A005_, "1=0; 2=0; 3=1; 4=2; 5=2; 6=3; 7=3; 8=3; 9=3; 97=999; -8=997; -9=998; NA=999")
KLOSA_ds_w2$education <- labelled(KLOSA_ds_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- KLOSA_ds_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(KLOSA_w2_educ$w02A005_)
BeforeH <- c(sum(BeforeH[2:3]), BeforeH[4],sum(BeforeH[5:6]), sum(BeforeH[7:10]), BeforeH[1])
AfterH <- table(KLOSA_ds_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2)->0", "3->1", "(4,5)->2", "(6,7,8,9)->3", "-8->997")
kable(C)
```

 
 

 
```{r importOPAL2,  echo=FALSE}
val_labels(KLOSA_ds_w2) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
education <- KLOSA_ds_w2
save(education, file = "../RData/w2/education.RData")
rm(education)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$education <- car::recode(KLOSA_m_ds_w2$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")

#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

 

* Name: `w03A005_`
* Label: `In last survey, respondent's educational background re-answer`
* Categories: 
    + `1 = No formal education (illiterate)`
    + `2 = No formal education (capable of reading)`
    + `3 = Elementary school`
    + `4 = Middle school`
    + `5 = High school`
    + `6 = Two-year college`
    + `7 = College grad`
    + `8 = Post college (Master)`
    + `9 = Post college (PhD)`
    + `97 = Other`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`

* Description: 
```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3_educ','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03A005_'), missings = TRUE)
KLOSA_w3_educ <- opal.execute(o,'KLOSA_w3_educ')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_educ$id <- substr(KLOSA_w3_educ$id,1,nchar(KLOSA_w3_educ$id)-2)

```

```{r local3,  echo=FALSE}
vari <- KLOSA_w3_educ$w03A005_
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w3_educ$w03A005_, missing_values = c(-8,-9))
ggplot(KLOSA_w3_educ, aes(x=factor(w03A005_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education (illiterate)" into 0`
* `recode 2 "No formal education (capable of reading)" into 0`
* `recode 3 "Elementary school" into 1`
* `recode 4 "Middle school" into 2`
* `recode 5 "High school" into 2`
* `recode 6 "Two-year college" into 3`
* `recode 7 "College grad" into 3`
* `recode 8 "Post college (Master)" into 3`
* `recode 9 "Post college (PhD)" into 3`
* `recode 97 "Other" into 999`
* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo3,   echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_educ$id)
KLOSA_ds_w3$education <- car::recode(KLOSA_w3_educ$w03A005_, "1=0; 2=0; 3=1; 4=2; 5=2; 6=3; 7=3; 8=3; 9=3; 97=999; -8=997; -9=998; NA=999")
KLOSA_ds_w3$education <- labelled(KLOSA_ds_w3$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- KLOSA_ds_w3$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- table(KLOSA_w3_educ$w03A005_)
BeforeH <- c(sum(BeforeH[2:3]), BeforeH[4],sum(BeforeH[5:6]), sum(BeforeH[7:10]), BeforeH[1])
AfterH <- table(KLOSA_ds_w3$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2)->0", "3->1", "(4,5)->2", "(6,7,8,9)->3", "-8->997")
kable(C)
```

 
 

 
```{r importOPAL3,  echo=FALSE}
val_labels(KLOSA_ds_w3) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
education <- KLOSA_ds_w3
save(education, file = "../RData/w3/education.RData")
rm(education)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$education <- car::recode(KLOSA_m_ds_w3$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```







### Wave 4 

#### Study-specific variable description

 

* Name: `w04A005`
* Label: `In last survey, respondent's educational background re-answer`
* Categories: 
    + `1 = No formal education (illiterate)`
    + `2 = No formal education (capable of reading)`
    + `3 = Elementary school`
    + `4 = Middle school`
    + `5 = High school`
    + `6 = Two-year college`
    + `7 = College grad`
    + `8 = Post college (Master)`
    + `9 = Post college (PhD)`
    + `97 = Other`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`

* Description: 
```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4_educ','KLOSA.w04_main_e_spss',
                         variables=list('w04A005'), missings = TRUE)
```

```{r local4,  echo=FALSE}
KLOSA_w4_educ <- opal.execute(o,'KLOSA_w4_educ')
vari <- KLOSA_w4_educ$w04A005
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w4_educ$w04A005, missing_values = c(-8,-9))
ggplot(KLOSA_w4_educ, aes(x=factor(w04A005))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education (illiterate)" into 0`
* `recode 2 "No formal education (capable of reading)" into 0`
* `recode 3 "Elementary school" into 1`
* `recode 4 "Middle school" into 2`
* `recode 5 "High school" into 2`
* `recode 6 "Two-year college" into 3`
* `recode 7 "College grad" into 3`
* `recode 8 "Post college (Master)" into 3`
* `recode 9 "Post college (PhD)" into 3`
* `recode 97 "Other" into 999`
* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `recode NA into 999`


**R script:**

```{r harmo4,   echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_educ$id)
KLOSA_ds_w4$education <- car::recode(KLOSA_w4_educ$w04A005, "1=0; 2=0; 3=1; 4=2; 5=2; 6=3; 7=3; 8=3; 9=3; 97=999; -8=997; -9=998; NA=999")
KLOSA_ds_w4$education <- labelled(KLOSA_ds_w4$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- KLOSA_ds_w4$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4,  echo=FALSE}
BeforeH <- table(KLOSA_w4_educ$w04A005)
BeforeH <- c(sum(BeforeH[2:3]), BeforeH[4],sum(BeforeH[5:6]), sum(BeforeH[7:10]), BeforeH[1])
AfterH <- table(KLOSA_ds_w4$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2)->0", "3->1", "(4,5)->2", "(6,7,8,9)->3", "-8->997")
kable(C)
```

 
 

 
```{r importOPAL4,  echo=FALSE}
val_labels(KLOSA_ds_w4) <- NULL

#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
education <- KLOSA_ds_w4
save(education, file = "../RData/w4/education.RData")
rm(education)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$education <- car::recode(KLOSA_m_ds_w4$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")

#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```


