---
title: "Level of Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/level_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/level_paDS.R')
```




# Data process


## Cuba

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign cuba w1, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')
```

```{r local cuba w1, echo=F}
vbl <- t1066_cuba_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo cuba w1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$level_pa<-Recode(t1066_cuba_w1$PACTIVE, "NA='999'")
t1066_ds_cuba_w1$level_pa <- labelled(t1066_ds_cuba_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cuba w1, echo=F}
vbl <- t1066_ds_cuba_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$level_pa)
X<-table(t1066_cuba_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_cuba_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-Cuba-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`0` <br/> `NA`|
| **Description** |  |


```{r assign cuba w2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
```

```{r local cuba w2, echo=F}
vbl <- t1066_cuba_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(t1066_cuba_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 999` 
* `NA into 999`

```{r harmo cuba w2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$level_pa <-  Recode(t1066_cuba_w2$f_PACTIVE, "0 = '999';NA='999'")
t1066_ds_cuba_w2$level_pa <- labelled(t1066_ds_cuba_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cuba w2, echo=F}
vbl <- t1066_ds_cuba_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation cuba w2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$level_pa)
X<-table(t1066_cuba_w2$f_PACTIVE)
BeforeH <- c(X[2:5],sum(is.na(t1066_cuba_w2$f_PACTIVE),X[1]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","0,NA->999") 
kable(C)
```





## India

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-India-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')
```

```{r local India w1, echo=F}
vbl <- t1066_india_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$level_pa <- Recode(t1066_india_w1$PACTIVE, "NA='999'")
t1066_ds_india_w1$level_pa <- labelled(t1066_ds_india_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
vbl <- t1066_ds_india_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$level_pa)
X<-table(t1066_india_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_india_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





## Urban China

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** | |
| **Description** |  |



```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')
```

```{r local UrbanChina w1, echo=F}
vbl <- t1066_UCh_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$level_pa <- Recode(t1066_UCh_w1$PACTIVE, "")
t1066_ds_UCh_w1$level_pa <- labelled(t1066_ds_UCh_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
vbl <- t1066_ds_UCh_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$level_pa)
X<-table(t1066_UCh_w1$PACTIVE)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanChina-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`0` <br/> `NA`|
| **Description** |  |

```{r assign UrbanChina w2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
```

```{r local UrbanChina w2, echo=F}
vbl <- t1066_UCh_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(t1066_UCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 999` 
* `NA into 999`

```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$level_pa <-  Recode(t1066_UCh_w2$f_PACTIVE, "0 = '999';NA ='999'")
t1066_ds_UCh_w2$level_pa <- labelled(t1066_ds_UCh_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=F}
vbl <- t1066_ds_UCh_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$level_pa)
X<-table(t1066_UCh_w2$f_PACTIVE)
BeforeH <- c(X[2:5],sum(is.na(t1066_UCh_w2$f_PACTIVE),X[1]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","0,NA->999") 
kable(C)
```




## Rural China

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |



```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')
```

```{r local RuralChina w1, echo=F}
vbl <- t1066_RCh_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$level_pa <- Recode(t1066_RCh_w1$PACTIVE, "NA='999'")
t1066_ds_RCh_w1$level_pa <- labelled(t1066_ds_RCh_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
vbl <- t1066_ds_RCh_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$level_pa)
X<-table(t1066_RCh_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_RCh_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```




### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralChina-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** | |
| **Description** |  |

   


```{r assign RuralChina w2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')
```

```{r local RuralChina w2, echo=F}
vbl <- t1066_RCh_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$level_pa <-  Recode(t1066_RCh_w2$f_PACTIVE, "")
t1066_ds_RCh_w2$level_pa <- labelled(t1066_ds_RCh_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=F}
vbl <- t1066_ds_RCh_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$level_pa)
X<-table(t1066_RCh_w2$f_PACTIVE)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4") 
kable(C)
```





## Dominican Republic

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')
```

```{r local DominicanRepublic w1, echo=F}
vbl <- t1066_DR_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$level_pa <- Recode(t1066_DR_w1$PACTIVE, "NA='999'")
t1066_ds_DR_w1$level_pa <- labelled(t1066_ds_DR_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
vbl <- t1066_ds_DR_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$level_pa)
X<-table(t1066_DR_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_DR_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign DominicanRepublic w2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
```

```{r local DominicanRepublic w2, echo=F}
vbl <- t1066_DR_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$level_pa <-  Recode(t1066_DR_w2$f_PACTIVE, "NA='999'")
t1066_ds_DR_w2$level_pa <- labelled(t1066_ds_DR_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=F}
vbl <- t1066_ds_DR_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=F}
AfterH <- table(t1066_ds_DR_w2$level_pa)
X<-table(t1066_DR_w2$f_PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_DR_w2$f_PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





## Venezuela

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-Venezuela-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')
```

```{r local Venezuela w1, echo=F}
vbl <- t1066_Ven_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$level_pa <- Recode(t1066_Ven_w1$PACTIVE, "NA='999'")
t1066_ds_Ven_w1$level_pa <- labelled(t1066_ds_Ven_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
vbl <- t1066_ds_Ven_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$level_pa)
X<-table(t1066_Ven_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_Ven_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-Venezuela-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |



```{r assign Venezuela w2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')
```

```{r local Venezuela w2, echo=F}
vbl <- t1066_Ven_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$level_pa <-  Recode(t1066_Ven_w2$f_PACTIVE, "NA='999'")
t1066_ds_Ven_w2$level_pa <- labelled(t1066_ds_Ven_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=F}
vbl <- t1066_ds_Ven_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$level_pa)
X<-table(t1066_Ven_w2$f_PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_Ven_w2$f_PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```




## Urban Peru

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')
```

```{r local UrbanPeru w1, echo=F}
vbl <- t1066_UP_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$level_pa <- Recode(t1066_UP_w1$PACTIVE, "NA='999'")
t1066_ds_UP_w1$level_pa <- labelled(t1066_ds_UP_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
vbl <- t1066_ds_UP_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$level_pa)
X<-table(t1066_UP_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_UP_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```




### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanPeru-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** | |
| **Description** |  |



```{r assign UrbanPeru w2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')
```

```{r local UrbanPeru w2, echo=F}
vbl <- t1066_UP_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$level_pa <-  Recode(t1066_UP_w2$f_PACTIVE, "")
t1066_ds_UP_w2$level_pa <- labelled(t1066_ds_UP_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=F}
vbl <- t1066_ds_UP_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=F}
AfterH <- table(t1066_ds_UP_w2$level_pa)
X<-table(t1066_UP_w2$f_PACTIVE)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4") 
kable(C)
```




## Rural Peru

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')
```

```{r local RuralPeru w1, echo=F}
vbl <- t1066_RP_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$level_pa <- Recode(t1066_RP_w1$PACTIVE, "NA = '999'")
t1066_ds_RP_w1$level_pa <- labelled(t1066_ds_RP_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
vbl <- t1066_ds_RP_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$level_pa)
X<-table(t1066_RP_w1$PACTIVE)
BeforeH <- c(X, sum(is.na(t1066_RP_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralPeru-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** | |
| **Description** |  |

```{r assign RuralPeru w2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
```

```{r local RuralPeru w2, echo=F}
vbl <- t1066_RP_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$level_pa <-  Recode(t1066_RP_w2$f_PACTIVE, "")
t1066_ds_RP_w2$level_pa <- labelled(t1066_ds_RP_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=F}
vbl <- t1066_ds_RP_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=F}
AfterH <- table(t1066_ds_RP_w2$level_pa)
X<-table(t1066_RP_w2$f_PACTIVE)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4") 
kable(C)
```





## Urban Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')
```

```{r local UrbanMexico w1, echo=F}
vbl <- t1066_UM_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$level_pa <- Recode(t1066_UM_w1$PACTIVE, "NA='999'")
t1066_ds_UM_w1$level_pa <- labelled(t1066_ds_UM_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
vbl <- t1066_ds_UM_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$level_pa)
X<-table(t1066_UM_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_UM_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-UrbanMexico-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign UrbanMexico w2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')
```

```{r local UrbanMexico w2, echo=F}
vbl <- t1066_UM_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$level_pa <-  Recode(t1066_UM_w2$f_PACTIVE, "NA='999'")
t1066_ds_UM_w2$level_pa <- labelled(t1066_ds_UM_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=F}
vbl <- t1066_ds_UM_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=F}
AfterH <- table(t1066_ds_UM_w2$level_pa)
X<-table(t1066_UM_w2$f_PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_UM_w2$f_PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





## Rural Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |

```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')
```

```{r local RuralMexico w1, echo=F}
vbl <- t1066_RM_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$level_pa <- Recode(t1066_RM_w1$PACTIVE, "NA='999'")
t1066_ds_RM_w1$level_pa <- labelled(t1066_ds_RM_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
vbl <- t1066_ds_RM_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$level_pa)
X<-table(t1066_RM_w1$PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_RM_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-RuralMexico-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign RuralMexico w2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')
```

```{r local RuralMexico w2, echo=F}
vbl <- t1066_RM_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$level_pa <-  Recode(t1066_RM_w2$f_PACTIVE, "NA='999'")
t1066_ds_RM_w2$level_pa <- labelled(t1066_ds_RM_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=F}
vbl <- t1066_ds_RM_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=F}
AfterH <- table(t1066_ds_RM_w2$level_pa)
X<-table(t1066_RM_w2$f_PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_RM_w2$f_PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





## Puerto Rico

### Wave 1 

#### Study-specific variable description

| **Name** | `PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline', variables=list('PACTIVE'), missings = TRUE)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')
```

```{r local PuertoRico w1, echo=F}
vbl <- t1066_PR_w1$PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$level_pa <- Recode(t1066_PR_w1$PACTIVE, "NA = '999'")
t1066_ds_PR_w1$level_pa <- labelled(t1066_ds_PR_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
vbl <- t1066_ds_PR_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$level_pa)
X<-table(t1066_PR_w1$PACTIVE)
BeforeH <- c(X, sum(is.na(t1066_PR_w1$PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `f_PACTIVE` |
|-|-|
| **Label** | `physical activity` |
| **Table name** | `1066-PuertoRico-Followup` |
| **Categories** | `1 = very physically active` <br/> `2 = fairly` <br/> `3 = not very` <br/> `4 = not at all` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign PuertoRico w2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup', variables=list('f_PACTIVE'), missings = TRUE)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')
```

```{r local PuertoRico w2, echo=F}
vbl <- t1066_PR_w2$f_PACTIVE
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PACTIVE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$level_pa <-  Recode(t1066_PR_w2$f_PACTIVE, "NA='999'")
t1066_ds_PR_w2$level_pa <- labelled(t1066_ds_PR_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=F}
vbl <- t1066_ds_PR_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=F}
AfterH <- table(t1066_ds_PR_w2$level_pa)
X<-table(t1066_PR_w2$f_PACTIVE)
BeforeH <- c(X,sum(is.na(t1066_PR_w2$f_PACTIVE)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2->2","3->3","4->4","NA->999") 
kable(C)
```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[15,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[15,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  level_pa <- lb.hds[[index]]
  save(level_pa, file = paste0(datafolder,names(lb.hds)[index],"/level_pa.RData"))
}

for(index in seq_along(lf.hds)){
  level_pa <- lf.hds[[index]]
  save(level_pa, file = paste0(datafolder,names(lf.hds)[index],"/level_pa.RData"))
}


```
<!-- ########################################################## --> 







# Quality estimation

```{r closeRsession, echo=FALSE}
opal.logout(o)
```