---
title: "Systolic"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `sbp`
* Variable label: `Systolic blood pressure of participant at each wave`
* Variable description: `Means of all sistolic blood pressure measures`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


### SAGE - South Africa - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

```{r assign1}
opal.assign.table.tibble(o, 'SAGE_SA_w1_sbp','SAGE.southAfricaINDdata',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local1}
SAGE_SA_w1_sbp <- opal.execute(o,'SAGE_SA_w1_sbp')

Continuous_summary(var = SAGE_SA_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_SA_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_SA_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_SA_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_SA_w1_sbp$q2503_s, missing_values = c(-9, -8))
ggplot(SAGE_SA_w1_sbp, aes(q2503_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`

R code of the ALGORITHM:

```{r harmo1}
SAGE_SA_w1_sbp$mean_sbp <- apply(X = SAGE_SA_w1_sbp[,c(2,3, 4)], MARGIN = 1, FUN = mean)

###Individue with NA in the second and third one
ids_na <- which(!is.na(SAGE_SA_w1_sbp$q2501_s) & is.na(SAGE_SA_w1_sbp$q2502_s) & is.na(SAGE_SA_w1_sbp$q2503_s))

SAGE_SA_w1_sbp$mean_sbp[ids_na] <- SAGE_SA_w1_sbp$q2501_s[ids_na]


###Individue with -8 in the fist one
ids_01_8 <- which(SAGE_SA_w1_sbp$q2501_s==-8 & (SAGE_SA_w1_sbp$q2502_s!=-8 | SAGE_SA_w1_sbp$q2503_s!=-8))

#Individue with -8 only in the fist one
ids_01_8_only <- ids_01_8[c(1,3,4)]

SAGE_SA_w1_sbp$mean_sbp[ids_01_8_only] <- apply(X = SAGE_SA_w1_sbp[ids_01_8_only,c(3, 4)], MARGIN = 1, FUN = mean)
#Individue with -8 in the fist and second one
ids_01_8_and_02 <- ids_01_8[c(2,5)]

SAGE_SA_w1_sbp$mean_sbp[ids_01_8_and_02] <- SAGE_SA_w1_sbp$q2503_s[ids_01_8_and_02]


###Individue with -8 in the second one
ids_02_8 <- which(SAGE_SA_w1_sbp$q2502_s==-8 & (SAGE_SA_w1_sbp$q2501_s!=-8 | SAGE_SA_w1_sbp$q2503_s!=-8))
ids_02_8_2 <- ids_02_8[-c(6, 12)]

#Individue with -8 only in second one
ids_02_8_2_only <- ids_02_8_2[c(3, 5:7, 9)]

SAGE_SA_w1_sbp$mean_sbp[ids_02_8_2_only] <- apply(X = SAGE_SA_w1_sbp[ids_02_8_2_only,c(2, 4)], MARGIN = 1, FUN = mean)


###Individue with -8 in the third one
ids_03_8 <- which(SAGE_SA_w1_sbp$q2503_s==-8 & (SAGE_SA_w1_sbp$q2501_s!=-8 | SAGE_SA_w1_sbp$q2502_s!=-8))

#Individue with -8 only in the third one
ids_03_8_only <- ids_03_8[c(2, 4:12, 14, 16, 17)]

SAGE_SA_w1_sbp$mean_sbp[ids_03_8_only] <- apply(X = SAGE_SA_w1_sbp[ids_03_8_only,c(2, 3)], MARGIN = 1, FUN = mean)

#Individue with -8 in the second and third one
ids_03_8_and_02 <- ids_03_8[c(1, 3, 13, 15, 18)]

SAGE_SA_w1_sbp$mean_sbp[ids_03_8_and_02] <- SAGE_SA_w1_sbp$q2501_s[ids_03_8_and_02]



SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_sbp$id)
SAGE_SA_ds_w1$sbp <- car::recode(SAGE_SA_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_SA_ds_w1$sbp <- labelled(SAGE_SA_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = SAGE_SA_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL1}
#val_labels(SAGE_SA_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_SA_ds_w1
save(sbp, file = "../RData/SA_w1/sbp.RData")
rm(sbp)
```




### SAGE - Ghana - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

```{r assign_ghana}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_sbp','SAGE.ghanaINDData',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local_ghana}
SAGE_ghana_w1_sbp <- opal.execute(o,'SAGE_ghana_w1_sbp')

Continuous_summary(var = SAGE_ghana_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_ghana_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_ghana_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_ghana_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_ghana_w1_sbp$q2503_s, missing_values = c(-9, -8))
ggplot(SAGE_ghana_w1_sbp, aes(q2503_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`


R code of the ALGORITHM:

```{r harmo_ghana}
SAGE_ghana_w1_sbp$mean_sbp <- apply(X = SAGE_ghana_w1_sbp[,c(2,3,4)], MARGIN = 1, FUN = mean)

### -8 only in the first one
id8_only01 <- which(SAGE_ghana_w1_sbp$q2501_s==-8 & SAGE_ghana_w1_sbp$q2502_s!=-8 & SAGE_ghana_w1_sbp$q2503_s!=-8)

SAGE_ghana_w1_sbp$mean_sbp[id8_only01] <- apply(X = SAGE_ghana_w1_sbp[id8_only01,c(3,4)], MARGIN = 1, FUN = mean)

### -8 only in the second one
id8_only02 <- which(SAGE_ghana_w1_sbp$q2501_s!=-8 & SAGE_ghana_w1_sbp$q2502_s==-8 & SAGE_ghana_w1_sbp$q2503_s!=-8)

SAGE_ghana_w1_sbp$mean_sbp[id8_only02] <- apply(X = SAGE_ghana_w1_sbp[id8_only02,c(2,4)], MARGIN = 1, FUN = mean)

### -8 only in the third one
id8_only03 <- which(SAGE_ghana_w1_sbp$q2501_s!=-8 & SAGE_ghana_w1_sbp$q2502_s!=-8 & SAGE_ghana_w1_sbp$q2503_s==-8)

SAGE_ghana_w1_sbp$mean_sbp[id8_only03] <- apply(X = SAGE_ghana_w1_sbp[id8_only03,c(2,3)], MARGIN = 1, FUN = mean)

### -8 in the first and second one
id8_01_02 <- which(SAGE_ghana_w1_sbp$q2501_s==-8 & SAGE_ghana_w1_sbp$q2502_s==-8 & SAGE_ghana_w1_sbp$q2503_s!=-8)

SAGE_ghana_w1_sbp$mean_sbp[id8_01_02] <- SAGE_ghana_w1_sbp$q2503_s[id8_01_02]

### -8 in the second and third one
id8_02_03 <- which(SAGE_ghana_w1_sbp$q2501_s!=-8 & SAGE_ghana_w1_sbp$q2502_s==-8 & SAGE_ghana_w1_sbp$q2503_s==-8)

SAGE_ghana_w1_sbp$mean_sbp[id8_02_03] <- SAGE_ghana_w1_sbp$q2501_s[id8_02_03]


SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_sbp$id)
SAGE_ghana_ds_w1$sbp <- car::recode(SAGE_ghana_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_ghana_ds_w1$sbp <- labelled(SAGE_ghana_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana}
Continuous_summary(var = SAGE_ghana_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation_ghana}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_ghana}
#val_labels(SAGE_ghana_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_ghana_ds_w1
save(sbp, file = "../RData/ghana_w1/sbp.RData")
rm(sbp)
```





### SAGE - China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

```{r assign_china}
opal.assign.table.tibble(o, 'SAGE_china_w1_sbp','SAGE.chinaINDData',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local_china}
SAGE_china_w1_sbp <- opal.execute(o,'SAGE_china_w1_sbp')

Continuous_summary(var = SAGE_china_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_china_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_china_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_china_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_china_w1_sbp$q2503_s, missing_values = c(-9, -8))
ggplot(SAGE_china_w1_sbp, aes(q2503_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`


R code of the ALGORITHM:

```{r harmo_china}
SAGE_china_w1_sbp$mean_sbp <- apply(X = SAGE_china_w1_sbp[,c(2,3,4)], MARGIN = 1, FUN = mean)

### NA only in the third one
id_na_only03 <- which(!is.na(SAGE_china_w1_sbp$q2501_s) & !is.na(SAGE_china_w1_sbp$q2502_s) & is.na(SAGE_china_w1_sbp$q2503_s))

SAGE_china_w1_sbp$mean_sbp[id_na_only03] <- apply(X = SAGE_china_w1_sbp[id_na_only03,c(2,3)], MARGIN = 1, FUN = mean)


### NA in the second and third one
id_na_02_03 <- which(!is.na(SAGE_china_w1_sbp$q2501_s) & is.na(SAGE_china_w1_sbp$q2502_s) & is.na(SAGE_china_w1_sbp$q2503_s))

SAGE_china_w1_sbp$mean_sbp[id_na_02_03] <- SAGE_china_w1_sbp$q2501_s[id_na_02_03]


SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_sbp$id)
SAGE_china_ds_w1$sbp <- car::recode(SAGE_china_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_china_ds_w1$sbp <- labelled(SAGE_china_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china}
Continuous_summary(var = SAGE_china_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation_china}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_china}
#val_labels(SAGE_china_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_china_ds_w1
save(sbp, file = "../RData/china_w1/sbp.RData")
rm(sbp)
```






### SAGE - India - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

```{r assign_india}
opal.assign.table.tibble(o, 'SAGE_india_w1_sbp','SAGE.indiaINDData',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local_india}
SAGE_india_w1_sbp <- opal.execute(o,'SAGE_india_w1_sbp')

Continuous_summary(var = SAGE_india_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_india_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_india_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_india_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_india_w1_sbp$q2503_s, missing_values = c(-9, -8))
ggplot(SAGE_india_w1_sbp, aes(q2503_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`

R code of the ALGORITHM:

```{r harmo_india}
SAGE_india_w1_sbp$mean_sbp <- apply(X = SAGE_india_w1_sbp[,c(2,3,4)], MARGIN = 1, FUN = mean)

### -8 only in the third one
id8_only03 <- which(SAGE_india_w1_sbp$q2501_s!=-8 & SAGE_india_w1_sbp$q2502_s!=-8 & SAGE_india_w1_sbp$q2503_s==-8)

SAGE_india_w1_sbp$mean_sbp[id8_only03] <- apply(X = SAGE_india_w1_sbp[id8_only03,c(2,3)], MARGIN = 1, FUN = mean)

### -8 in the first and third one
id8_01_03 <- which(SAGE_india_w1_sbp$q2501_s==-8 & SAGE_india_w1_sbp$q2502_s!=-8 & SAGE_india_w1_sbp$q2503_s==-8)

SAGE_india_w1_sbp$mean_sbp[id8_01_03] <- SAGE_india_w1_sbp$q2502_s[id8_01_03]

### -8 in the second and third one
id8_02_03 <- which(SAGE_india_w1_sbp$q2501_s!=-8 & SAGE_india_w1_sbp$q2502_s==-8 & SAGE_india_w1_sbp$q2503_s==-8)

SAGE_india_w1_sbp$mean_sbp[id8_02_03] <- SAGE_india_w1_sbp$q2501_s[id8_02_03]




### -9 only in the first one
id9_only01 <- which(SAGE_india_w1_sbp$q2501_s==-9 & SAGE_india_w1_sbp$q2502_s!=-9 & SAGE_india_w1_sbp$q2503_s!=-9)

SAGE_india_w1_sbp$mean_sbp[id9_only01] <- apply(X = SAGE_india_w1_sbp[id9_only01,c(3,4)], MARGIN = 1, FUN = mean)

### -9 only in the second one
id9_only02 <- which(SAGE_india_w1_sbp$q2501_s!=-9 & SAGE_india_w1_sbp$q2502_s==-9 & SAGE_india_w1_sbp$q2503_s!=-9)

SAGE_india_w1_sbp$mean_sbp[id9_only02] <- apply(X = SAGE_india_w1_sbp[id9_only02,c(2,4)], MARGIN = 1, FUN = mean)


### -9 in the second and third one
id9_02_03 <- which(SAGE_india_w1_sbp$q2501_s!=-9 & SAGE_india_w1_sbp$q2502_s==-9 & SAGE_india_w1_sbp$q2503_s==-9)

SAGE_india_w1_sbp$mean_sbp[id9_02_03] <- SAGE_india_w1_sbp$q2501_s[id9_02_03]




SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_sbp$id)
SAGE_india_ds_w1$sbp <- car::recode(SAGE_india_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_india_ds_w1$sbp <- labelled(SAGE_india_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india}
Continuous_summary(var = SAGE_india_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation_india}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_india}
#val_labels(SAGE_india_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_india_ds_w1
save(sbp, file = "../RData/india_w1/sbp.RData")
rm(sbp)
```






### SAGE - Russia - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`


```{r assign_russia}
opal.assign.table.tibble(o, 'SAGE_russia_w1_sbp','SAGE.russiaINDdata',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local_russia}
SAGE_russia_w1_sbp <- opal.execute(o,'SAGE_russia_w1_sbp')

Continuous_summary(var = SAGE_russia_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_russia_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_russia_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_russia_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_russia_w1_sbp$q2503_s, missing_values = c(-9, -8))
ggplot(SAGE_russia_w1_sbp, aes(q2503_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`

R code of the ALGORITHM:

```{r harmo_russia}
SAGE_russia_w1_sbp$mean_sbp <- apply(X = SAGE_russia_w1_sbp[,c(2,3,4)], MARGIN = 1, FUN = mean)

### -8 only in the third one
id8_only03 <- which(SAGE_russia_w1_sbp$q2501_s!=-8 & SAGE_russia_w1_sbp$q2502_s!=-8 & SAGE_russia_w1_sbp$q2503_s==-8)

SAGE_russia_w1_sbp$mean_sbp[id8_only03] <- apply(X = SAGE_russia_w1_sbp[id8_only03,c(2,3)], MARGIN = 1, FUN = mean)


### -8 in the second and third one
id8_02_03 <- which(SAGE_russia_w1_sbp$q2501_s!=-8 & SAGE_russia_w1_sbp$q2502_s==-8 & SAGE_russia_w1_sbp$q2503_s==-8)

SAGE_russia_w1_sbp$mean_sbp[id8_02_03] <- SAGE_russia_w1_sbp$q2501_s[id8_02_03]





### -9 only in the second one
id9_only02 <- which(SAGE_russia_w1_sbp$q2501_s!=-9 & SAGE_russia_w1_sbp$q2502_s==-9 & SAGE_russia_w1_sbp$q2503_s!=-9)

SAGE_russia_w1_sbp$mean_sbp[id9_only02] <- apply(X = SAGE_russia_w1_sbp[id9_only02,c(2,4)], MARGIN = 1, FUN = mean)

### -9 only in the third one
id9_only03 <- which(SAGE_russia_w1_sbp$q2501_s!=-9 & SAGE_russia_w1_sbp$q2502_s!=-9 & SAGE_russia_w1_sbp$q2503_s==-9)

SAGE_russia_w1_sbp$mean_sbp[id9_only03] <- apply(X = SAGE_russia_w1_sbp[id9_only03,c(2,3)], MARGIN = 1, FUN = mean)

### -9 in the second and third one
id9_02_03 <- which(SAGE_russia_w1_sbp$q2501_s!=-9 & SAGE_russia_w1_sbp$q2502_s==-9 & SAGE_russia_w1_sbp$q2503_s==-9)

SAGE_russia_w1_sbp$mean_sbp[id9_02_03] <- SAGE_russia_w1_sbp$q2501_s[id9_02_03]



SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_sbp$id)
SAGE_russia_ds_w1$sbp <- car::recode(SAGE_russia_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_russia_ds_w1$sbp <- labelled(SAGE_russia_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia}
Continuous_summary(var = SAGE_russia_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation_russia}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_russia}
#val_labels(SAGE_russia_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_russia_ds_w1
save(sbp, file = "../RData/russia_w1/sbp.RData")
rm(sbp)
```






### SAGE - Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2501_s`
* Label: `systolic(1)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2502_s`
* Label: `systolic(2)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

* Name: `q2503_s`
* Label: `systolic(3)`
* Type of variable: `countinous`
* Missings
    + `-9 = refused`
    + `-8 = don't know`

```{r assign_Mexico}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_sbp','SAGE.mexicoINDdata',
                         variables=list('q2501_s', 'q2502_s', 'q2503_s'), missings = TRUE)
```

```{r local_Mexico}
SAGE_mexico_w1_sbp <- opal.execute(o,'SAGE_mexico_w1_sbp')

Continuous_summary(var = SAGE_mexico_w1_sbp$q2501_s, missing_values = c(-9, -8))
ggplot(SAGE_mexico_w1_sbp, aes(q2501_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_mexico_w1_sbp$q2502_s, missing_values = c(-9, -8))
ggplot(SAGE_mexico_w1_sbp, aes(q2502_s)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency")

Continuous_summary(var = SAGE_mexico_w1_sbp$q2503_s, missing_values = c(-9, -8))
```

#### Harmonisation algorithm
The harmonized variable is the mean value between the first, second and third measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 997`
* `-8 into 998`

R code of the ALGORITHM:

```{r harmo_Mexico}
SAGE_mexico_w1_sbp$mean_sbp <- apply(X = SAGE_mexico_w1_sbp[,c(2,3)], MARGIN = 1, FUN = mean)

### -8 in the first one
id8_01_03 <- which(SAGE_mexico_w1_sbp$q2501_s==-8 & SAGE_mexico_w1_sbp$q2502_s!=-8 )

SAGE_mexico_w1_sbp$mean_sbp[id8_01_03] <- SAGE_mexico_w1_sbp$q2502_s[id8_01_03]

### -8 in the second one
id8_02_03 <- which(SAGE_mexico_w1_sbp$q2501_s!=-8 & SAGE_mexico_w1_sbp$q2502_s==-8 )

SAGE_mexico_w1_sbp$mean_sbp[id8_02_03] <- SAGE_mexico_w1_sbp$q2501_s[id8_02_03]

SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_sbp$id)
SAGE_mexico_ds_w1$sbp <- car::recode(SAGE_mexico_w1_sbp$mean_sbp, "NA=999; -8=998; -9=997")
SAGE_mexico_ds_w1$sbp <- labelled(SAGE_mexico_ds_w1$sbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico}
Continuous_summary(var = SAGE_mexico_ds_w1$sbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(sbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Systolic Blood Pressure") + ylab("Frequency") + xlim(50,300) 
```

#### Validation
```{r crosstabulation_Mexico}
```

#### Quality estimation
The harmonized variable is the mean value between the first, 
second and third measurement of the study available variables



#### Import to OPAL
```{r importOPAL_Mexico}
#val_labels(SAGE_mexico_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
sbp <- SAGE_mexico_ds_w1
save(sbp, file = "../RData/mexico_w1/sbp.RData")
rm(sbp)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
