---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `weight`
* Variable label: `Weight of the participant in kg`
* Domain: `Physical measures `
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Comments: `Weight should be collected in kilograms. It should be determined whether the  variable was collected through a self reported measure or an athropometric test.`




<!-- ########################################################## --> 

# Data process



```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


### SAGE - South Africa - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`

```{r assign1}
opal.assign.table.tibble(o, 'SAGE_SA_w1_weig','SAGE.southAfricaINDdata',
                         variables=list('q2507'), missings = TRUE)
```

```{r local1}
SAGE_SA_w1_weig <- opal.execute(o,'SAGE_SA_w1_weig')
Continuous_summary(var = SAGE_SA_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_SA_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(32,194)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`

R code of the ALGORITHM:

```{r harmo1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_weig$id)
SAGE_SA_ds_w1$weight <- car::recode(SAGE_SA_w1_weig$q2507, "NA=999; 998=993")
SAGE_SA_ds_w1$weight <- labelled(SAGE_SA_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = SAGE_SA_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL1}
#val_labels(SAGE_SA_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
```




### SAGE - Ghana - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`

```{r assign_ghana}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_weig','SAGE.ghanaINDData',
                         variables=list('q2507'), missings = TRUE)
```

```{r local_ghana}
SAGE_ghana_w1_weig <- opal.execute(o,'SAGE_ghana_w1_weig')
Continuous_summary(var = SAGE_ghana_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_ghana_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(32,194)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`


R code of the ALGORITHM:

```{r harmo_ghana}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_weig$id)
SAGE_ghana_ds_w1$weight <- car::recode(SAGE_ghana_w1_weig$q2507, "NA=999; 998=993")
SAGE_ghana_ds_w1$weight <- labelled(SAGE_ghana_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ghana}
Continuous_summary(var = SAGE_ghana_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ghana}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_ghana}
#val_labels(SAGE_ghana_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
```





### SAGE - China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`

```{r assign_china}
opal.assign.table.tibble(o, 'SAGE_china_w1_weig','SAGE.chinaINDData',
                         variables=list('q2507'), missings = TRUE)
```

```{r local_china}
SAGE_china_w1_weig <- opal.execute(o,'SAGE_china_w1_weig')
Continuous_summary(var = SAGE_china_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_china_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(32,194)
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`


R code of the ALGORITHM:

```{r harmo_china}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_weig$id)
SAGE_china_ds_w1$weight <- car::recode(SAGE_china_w1_weig$q2507, "NA=999; 998=993")
SAGE_china_ds_w1$weight <- labelled(SAGE_china_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_china}
Continuous_summary(var = SAGE_china_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
There are unusual values that are lower than 30:
```{r crosstabulation_china}
SAGE_china_w1_weig[which(SAGE_china_w1_weig$q2507<30),]
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_china}
#val_labels(SAGE_china_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
```






### SAGE - India - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`

```{r assign_india}
opal.assign.table.tibble(o, 'SAGE_india_w1_weig','SAGE.indiaINDData',
                         variables=list('q2507'), missings = TRUE)
```

```{r local_india}
SAGE_india_w1_weig <- opal.execute(o,'SAGE_india_w1_weig')
Continuous_summary(var = SAGE_india_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_india_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(32,194)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`

R code of the ALGORITHM:

```{r harmo_india}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_weig$id)
SAGE_india_ds_w1$weight <- car::recode(SAGE_india_w1_weig$q2507, "NA=999; 998=993")
SAGE_india_ds_w1$weight <- labelled(SAGE_india_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india}
Continuous_summary(var = SAGE_india_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_india}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_india}
#val_labels(SAGE_india_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
```






### SAGE - Russia - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`


```{r assign_russia}
opal.assign.table.tibble(o, 'SAGE_russia_w1_weig','SAGE.russiaINDdata',
                         variables=list('q2507'), missings = TRUE)
```

```{r local_russia}
SAGE_russia_w1_weig <- opal.execute(o,'SAGE_russia_w1_weig')
Continuous_summary(var = SAGE_russia_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_russia_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(32,194)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`

R code of the ALGORITHM:

```{r harmo_russia}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_weig$id)
SAGE_russia_ds_w1$weight <- car::recode(SAGE_russia_w1_weig$q2507, "NA=999; 998=993")
SAGE_russia_ds_w1$weight <- labelled(SAGE_russia_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_russia}
Continuous_summary(var = SAGE_russia_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_russia}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_russia}
#val_labels(SAGE_russia_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
```






### SAGE - Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507`
* Label: `true weight (kg)`
* Type of variable: `countinous`
* Missings
    + `997 = refused`
    + `998 = not able`

```{r assign_Mexico}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_weig','SAGE.mexicoINDdata',
                         variables=list('q2507'), missings = TRUE)
```

```{r local_Mexico}
SAGE_mexico_w1_weig <- opal.execute(o,'SAGE_mexico_w1_weig')
Continuous_summary(var = SAGE_mexico_w1_weig$q2507, missing_values = c(997,998))
ggplot(SAGE_mexico_w1_weig, aes(q2507)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(32,194)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `keep "refuse" into 997`
* `998 "not able" into 993`

R code of the ALGORITHM:

```{r harmo_Mexico}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_weig$id)
SAGE_mexico_ds_w1$weight <- car::recode(SAGE_mexico_w1_weig$q2507, "NA=999; 998=993")
SAGE_mexico_ds_w1$weight <- labelled(SAGE_mexico_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_Mexico}
Continuous_summary(var = SAGE_mexico_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_Mexico}
```

#### Quality estimation
No comments.



#### Import to OPAL
```{r importOPAL_Mexico}
#val_labels(SAGE_mexico_ds_w1) <- NULL
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
weight <- SAGE_SA_ds_w1
save(weight, file = paste0(datafolder, "/SA_w1/weight.RData"))
```

```{r,  echo=FALSE}
weight <- SAGE_ghana_ds_w1
save(weight, file = paste0(datafolder, "/ghana_w1/weight.RData"))
```

```{r,  echo=FALSE}
weight <- SAGE_china_ds_w1
save(weight, file = paste0(datafolder, "/china_w1/weight.RData"))
```

```{r,  echo=FALSE}
weight <- SAGE_india_ds_w1
save(weight, file = paste0(datafolder, "/india_w1/weight.RData"))
```

```{r,  echo=FALSE}
weight <- SAGE_russia_ds_w1
save(weight, file = paste0(datafolder, "/russia_w1/weight.RData"))
```

```{r,  echo=FALSE}
weight <- SAGE_mexico_ds_w1
save(weight, file = paste0(datafolder, "/mexico_w1/weight.RData"))
```




```{r closeRsession, echo=FALSE}
opal.logout(o)
```




