---
title: "Sick or disabled"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sickdisDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sickdisDS.R')
```



# Data process




## India


### Wave 1


#### Study-specific variable description



| **Name** |  `we004` |`we004_other`|
|-|-|-|
| **Label** |`best description of current work status`|`best description of current work status other`|
| **Table name**  | `LASI-Pilot_all`| `LASI-Pilot_all`|
| **Categories** | `1 = disabled: unable to work`<br/>`2 = unemployed: interested in working but unable to find a job`<br/>`3 = homemaker`<br/>`4 = other, please specify` |`...`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all',variables=list('we004','we004_other'), missings = T)
LASI_w1 <- opal.execute(o,'LASI_w1')

```

```{r local w1, echo=F}

vbl <- LASI_w1$we004
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(we004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

kable(frq(LASI_w1$we004_other[which(!is.na(LASI_w1$we004_other))])[[1]][frq(LASI_w1$we004_other[which(!is.na(LASI_w1$we004_other))])[[1]][,2]>2,], align = 'c',caption = 'we004_other')

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `keep up 1 into 1`
* `change 2,3,4 into 0`
* `other unable conditions into 1`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$sickdis <- car::recode(LASI_w1$we004, "c(2,3,4)=0; NA=999")
unable <- c("HEALTH CONDITION NOT VERY WELL .","Heart Patient","MENTALLY DISABLED","not working due to ageing problem","R is not well she can move only with the help oy others","R is too old cant work","SHE IS VERY OLD","She si very old","unable to work","Unable to Work","UNHEALTHY CONDITION","Very old")
LASI_ds_w1$sickdis[which(LASI_w1$we004_other %in% unable)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- LASI_ds_w1$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}


```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
LASI_ds_w1$sickdis <- labelled(LASI_ds_w1$sickdis, labels = cat_label)
label(LASI_ds_w1$sickdis) <- ds_label

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$sickdis <- car::recode(LASI_m_ds_w1$sickdis, "miss_values_vector=NA")

tt <- frq(LASI_ds_w1$sickdis)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(LASI_ds_w1$sickdis)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.LASI <- list(w1 = LASI_ds_w1)

for(index in seq_along(l.LASI)){
  sickdis <- l.LASI[[index]]
  save(sickdis, file = paste0(datafolder,names(l.LASI)[index],"/sickdis.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





