---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process
## India
### Wave 1 

#### Study-specific variable description

 

* Name: `rmaritalstatus_h`
* Label: ` r marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = separated/deserted`
    + `4 = divorced`
    + `5 = widowed`
    



* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_ms','LASI.LASI-Pilot_all',
                         variables=list('rmaritalstatus_h'), missings = TRUE)
```


```{r local1,  echo=FALSE}
LASI_w1_ms <- opal.execute(o,'LASI_w1_ms')
vari <- LASI_w1_ms$rmaritalstatus_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_ms$rmaritalstatus_h, missing_values = NA)
ggplot(LASI_w1_ms, aes(x=factor(rmaritalstatus_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "never married" into 1`
* `keep "currently married" into 2`
* `keep "separated/deserted" into 3`
* `recode 4 "divorced" into 3`
* `recode 5 "widowed" into 4`

**R script:**

```{r harmo1,   echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_ms$id)
LASI_ds_w1$marital_status <- car::recode(LASI_w1_ms$rmaritalstatus_h, "4=3; 5=4; NA=999")
LASI_ds_w1$marital_status <- labelled(LASI_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- LASI_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- c(table(LASI_w1_ms$rmaritalstatus_h), sum(is.na(LASI_w1_ms$rmaritalstatus_h)))
BeforeH <- c(BeforeH[c(1,2)], sum(BeforeH[c(3, 4)]), BeforeH[5], BeforeH[6] )
AfterH <- table(LASI_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","2", "(3,4)->3", "5->4", "NA->999")
kable(C)
```


```{r importOPAL1,  echo=FALSE}
val_labels(LASI_ds_w1) <- NULL
opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
marital_status <- LASI_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$marital_status <- car::recode(LASI_m_ds_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```




