---
title: "Living alone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `living_alone`
* Variable label: `Participant is currently living alone`
* Variable description: `Participant is currently living alone`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process 

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `cv002_intro` |
|-|-|
| **Label** | `number of people in the household` |
| **Table name** | `LASI-Pilot_all` |
| **Description** |  |

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_la','LASI.LASI-Pilot_all',
                         variables=list('cv002_intro'), missings = TRUE)
```

```{r local1, echo=F}
LASI_w1_la <- opal.execute(o,'LASI_w1_la')
vari <- LASI_w1_la$cv002_intro
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_la$cv002_intro, missing_values = NA)
ggplot(LASI_w1_la, aes(x=factor(cv002_intro))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 into 1`
* `>1 into 0`
* `NA into 999`

**R script:**

```{r harmo1}
LASI_ds_w1 <- tibble(id=LASI_w1_la$id)
LASI_ds_w1$living_alone <- car::recode(LASI_w1_la$cv002_intro, "2:hi=0; NA=999")
LASI_ds_w1$living_alone  <- labelled(LASI_ds_w1$living_alone , labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- LASI_ds_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```


#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(LASI_w1_la$cv002_intro)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(LASI_ds_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=2->0","1")
kable(C)
```


```{r importOPAL1, echo=F}
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
living_alone <- LASI_ds_w1
save(living_alone, file = "../RData/w1/living_alone.RData")
rm(living_alone)

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$living_alone <- car::recode(LASI_m_ds_w1$living_alone, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```







