---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```



# Data process




## India


### Wave 1


#### Study-specific variable description



| **Name** | `we001` | `we002` |
|-|-|-|
| **Label** | `engaged in agricultural work in past year`|`work for at least on hour last week`|
| **Table name**  | `LASI-Pilot_all`| `LASI-Pilot_all`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all',variables=list('we001','we002'), missings = T)
LASI_w1 <- opal.execute(o,'LASI_w1')

```

```{r local w1, echo=F}

vbl <- LASI_w1$we001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(we001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$we002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(we002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$employed <- rep(999,length(LASI_w1$id))
LASI_ds_w1$employed[which(LASI_w1$we001==2 & LASI_w1$we002==2)] <- 0
LASI_ds_w1$employed[which(LASI_w1$we001==1 | LASI_w1$we002==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- LASI_ds_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}


```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
LASI_ds_w1$employed <- labelled(LASI_ds_w1$employed, labels = cat_label)
label(LASI_ds_w1$employed) <- ds_label

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$employed <- car::recode(LASI_m_ds_w1$employed, "miss_values_vector=NA")

tt <- frq(LASI_ds_w1$employed)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(LASI_ds_w1$employed)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation

It is assumed that agricultural work is employment and if it is not paid, it provides food etc.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.LASI <- list(w1 = LASI_ds_w1)

for(index in seq_along(l.LASI)){
  employed <- l.LASI[[index]]
  save(employed, file = paste0(datafolder,names(l.LASI)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





