---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C009` |`w01C010y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not diabetes diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `-9 = Do not know` | `-9 = Do not know` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C009','w01C010y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C009
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C010y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(w01C010y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1960,2006)

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`
* `-9 into 998`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = w01C010y-ybirth`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`
* `-9 into 998`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$h_diabetes <- car::recode(KLOSA_w1$w01C009,"-9=998; 5=0")

KLOSA_ds_w1$h_diabetes <- labelled(KLOSA_ds_w1$h_diabetes, labels = cat_label)

# Continuous variable harmonization
KLOSA_ds_w1$h_diabetes_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$h_diabetes_age[KLOSA_ds_w1$h_diabetes==1 & KLOSA_w1$w01C010y != -9] <- KLOSA_w1$w01C010y[KLOSA_ds_w1$h_diabetes==1 & KLOSA_w1$w01C010y != -9] - KLOSA_w1$ybirth[KLOSA_ds_w1$h_diabetes==1 & KLOSA_w1$w01C010y != -9]
KLOSA_ds_w1$h_diabetes_age[KLOSA_ds_w1$h_diabetes==1 & KLOSA_w1$w01C010y == -9] <- 998
KLOSA_ds_w1$h_diabetes_age[KLOSA_ds_w1$h_diabetes==0] <- 996

KLOSA_ds_w1$h_diabetes_age <- labelled(KLOSA_ds_w1$h_diabetes_age, labels = cont_label)

# We build a global table in order to have updated the diabetes status of all the individuals through the different waves
KLOSA_ds <- KLOSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(15,85)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$h_diabetes)
BeforeH <- table(KLOSA_w1$w01C009, useNA = "ifany")[c(3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C011` |`w02C012y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with diabetes or not`|`The first time of diabetes diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C011','w02C012y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C011
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C011))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C012y
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(x=factor(w02C012y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `w01C009 == 5 and w02C011 == 5 into 0`
* `w01C009 == 1 or w02C011 == 1 into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w2 and 0 in w1, h_diabetes_age = w02C012y-ybirth`
* `if h_diabetes == 1 in w2 and w1, h_diabetes_age = age from wave 1`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_w2 <- left_join(KLOSA_w2, KLOSA_ds_w1, by = "id")
KLOSA_ds_w2$h_diabetes <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_diabetes[((!is.na(KLOSA_w2$w02C011)) & KLOSA_w2$w02C011 == 5) & (KLOSA_w2$h_diabetes != 1)] <- 0
KLOSA_ds_w2$h_diabetes[((!is.na(KLOSA_w2$w02C011)) & KLOSA_w2$w02C011 == 1) | ((!is.na(KLOSA_w2$h_diabetes)) & KLOSA_w2$h_diabetes == 1)] <- 1

KLOSA_ds_w2$h_diabetes <- labelled(KLOSA_ds_w2$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w2,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w2$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_diabetes <- KLOSA_ds_prov$h_diabetes
rm(KLOSA_ds_prov)

# Continuous variable harmonization
diabetes_age <- KLOSA_w2$w02C012y[KLOSA_ds_w2$h_diabetes == 1 & (KLOSA_w2$h_diabetes==0 | is.na(KLOSA_w2$h_diabetes) | KLOSA_w2$h_diabetes_age %in% miss_values_vector)]-KLOSA_w2$ybirth[KLOSA_ds_w2$h_diabetes == 1 & (KLOSA_w2$h_diabetes==0 | is.na(KLOSA_w2$h_diabetes) | KLOSA_w2$h_diabetes_age %in% miss_values_vector)]

KLOSA_ds_w2$h_diabetes_age <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_diabetes_age[KLOSA_ds_w2$h_diabetes == 0] <- 996
KLOSA_ds_w2$h_diabetes_age[KLOSA_ds_w2$h_diabetes == 1 & (KLOSA_w2$h_diabetes==0 | is.na(KLOSA_w2$h_diabetes) | KLOSA_w2$h_diabetes_age %in% miss_values_vector)] <- diabetes_age
KLOSA_ds_w2$h_diabetes_age[KLOSA_ds_w2$h_diabetes == 1 & KLOSA_w2$h_diabetes==1 & !is.na(KLOSA_w2$h_diabetes) & !KLOSA_w2$h_diabetes_age %in% miss_values_vector] <- car::recode(KLOSA_w2$h_diabetes_age[KLOSA_ds_w2$h_diabetes == 1 & KLOSA_w2$h_diabetes==1 & !is.na(KLOSA_w2$h_diabetes) & !KLOSA_w2$h_diabetes_age %in% miss_values_vector],"miss_values_vector=999")
KLOSA_ds_w2$h_diabetes_age <- car::recode(KLOSA_ds_w2$h_diabetes_age, "NA=999")
KLOSA_ds$h_diabetes_age[(KLOSA_ds$id %in% KLOSA_ds_w2$id) & (KLOSA_ds$h_diabetes != 999)] <- KLOSA_ds_w2$h_diabetes_age[KLOSA_ds_w2$h_diabetes != 999]

KLOSA_ds_w2$h_diabetes_age <- labelled(KLOSA_ds_w2$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(15,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$h_diabetes, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w2$w02C011)) & KLOSA_w2$w02C011 == 5) & (KLOSA_w2$h_diabetes != 1)),
  sum(((!is.na(KLOSA_w2$w02C011)) & KLOSA_w2$w02C011 == 1) | ((!is.na(KLOSA_w2$h_diabetes)) & KLOSA_w2$h_diabetes == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C011` |`w03C012y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not diabetes diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -9 = Don't know` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C011','w03C012y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C011
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C011))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C012y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(factor(w03C012y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `w01C009 == 5 and w02C011 == 5 and w03C011 == 5 into 0`
* `w01C009 == 1 or w02C011 == 1 or w03C011 == 1 into 1`
* `-9 into 998`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w3 and 0 in previous waves, h_diabetes_age = w03C012y-ybirth`
* `if h_diabetes == 1 in w3 and other wave, h_diabetes_age as previously`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `-9 into 998`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)

KLOSA_w3 <- left_join(KLOSA_w3, KLOSA_ds, by = "id")
KLOSA_ds_w3$h_diabetes <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_diabetes[((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == 5) & (KLOSA_w3$h_diabetes != 1)] <- 0
KLOSA_ds_w3$h_diabetes[((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == 1) | ((!is.na(KLOSA_w3$h_diabetes)) & KLOSA_w3$h_diabetes == 1)] <- 1
KLOSA_ds_w3$h_diabetes[((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == -9) & (KLOSA_w3$h_diabetes != 1)] <- 998

KLOSA_ds_w3$h_diabetes <- labelled(KLOSA_ds_w3$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w3,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_diabetes <- KLOSA_ds_prov$h_diabetes
rm(KLOSA_ds_prov)



# Continuous variable harmonization
diabetes_age <- KLOSA_w3$w03C012y[KLOSA_ds_w3$h_diabetes == 1 & (KLOSA_w3$h_diabetes==0 | is.na(KLOSA_w3$h_diabetes) | KLOSA_w3$h_diabetes_age %in% miss_values_vector)]-KLOSA_w3$ybirth[KLOSA_ds_w3$h_diabetes == 1 & (KLOSA_w3$h_diabetes==0 | is.na(KLOSA_w3$h_diabetes) | KLOSA_w3$h_diabetes_age %in% miss_values_vector)]
KLOSA_ds_w3$h_diabetes_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes == 0] <- 996
KLOSA_ds_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes == 1 & (KLOSA_w3$h_diabetes==0 | is.na(KLOSA_w3$h_diabetes) | KLOSA_w3$h_diabetes_age %in% miss_values_vector)] <- diabetes_age
KLOSA_ds_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes == 1 & KLOSA_w3$w03C012y==-9] <- 998
KLOSA_ds_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes == 1 & KLOSA_w3$h_diabetes!=0 & !is.na(KLOSA_w3$h_diabetes) & !KLOSA_w3$h_diabetes_age %in% miss_values_vector] <- car::recode(KLOSA_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes == 1 & KLOSA_w3$h_diabetes!=0 & !is.na(KLOSA_w3$h_diabetes) & !KLOSA_w3$h_diabetes_age %in% miss_values_vector],"miss_values_vector=999")
KLOSA_ds_w3$h_diabetes_age <- car::recode(KLOSA_ds_w3$h_diabetes_age, "NA=999")
KLOSA_ds$h_diabetes_age[(KLOSA_ds$id %in% KLOSA_ds_w3$id) & (KLOSA_ds$h_diabetes != 999)] <- KLOSA_ds_w3$h_diabetes_age[KLOSA_ds_w3$h_diabetes != 999]

KLOSA_ds_w3$h_diabetes_age <- labelled(KLOSA_ds_w3$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(15,95)

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$h_diabetes, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == 5) & (KLOSA_w3$h_diabetes != 1)),
  sum(((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == 1) | ((!is.na(KLOSA_w3$h_diabetes)) & KLOSA_w3$h_diabetes == 1)),
  sum(((!is.na(KLOSA_w3$w03C011)) & KLOSA_w3$w03C011 == -9) & (KLOSA_w3$h_diabetes != 1))
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```




### Wave 4


#### Study-specific variable description

| **Name** | `w04C011` |`w04C012y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not diabetes diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -9 = Don't know` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C011','w04C012y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C011
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C011))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C012y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C012y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `w01C009 == 5 and w02C011 == 5 and w03C011 == 5 and w04C011 == 5 into 0`
* `w01C009 == 1 or w02C011 == 1 or w03C011 == 1 or w04C011 == 1 into 1`
* `-9 into 998`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w4 and 0 in previous waves, h_diabetes_age = w04C012y-ybirth`
* `if h_diabetes == 1 in w4 and other wave, h_diabetes_age as previously`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `-9 into 998`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)

KLOSA_w4 <- left_join(KLOSA_w4, KLOSA_ds, by = "id")
KLOSA_ds_w4$h_diabetes <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_diabetes[((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == 5) & (KLOSA_w4$h_diabetes != 1)] <- 0
KLOSA_ds_w4$h_diabetes[((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == 1) | ((!is.na(KLOSA_w4$h_diabetes)) & KLOSA_w4$h_diabetes == 1)] <- 1
KLOSA_ds_w4$h_diabetes[((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == -9) & (KLOSA_w4$h_diabetes != 1)] <- 998

KLOSA_ds_w4$h_diabetes <- labelled(KLOSA_ds_w4$h_diabetes, labels = cat_label)

# # We update the diabetes status of the individuals in the global table
# assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
#   newtib <- left_join(endtib,sttib,by="id")
#   newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
#   id_ind <- match("id",names(newtib))
#   newtib <- newtib[,c(id_ind,col_end_index)]
#   names(newtib)[2] <- "x"
#   newtib$x <- car::recode(newtib$x,"NA=999")
#   names(newtib)[2] <- names(endtib)[col_end_index]
#   newtib
# }
# KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
# KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w4,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w4$id),col_end_index = 2, col_st_index = 3)
# KLOSA_ds$h_diabetes <- KLOSA_ds_prov$h_diabetes
# rm(KLOSA_ds_prov)

# Continuous variable harmonization
diabetes_age <- KLOSA_w4$w04C012y[KLOSA_ds_w4$h_diabetes == 1 & (KLOSA_w4$h_diabetes==0 | is.na(KLOSA_w4$h_diabetes) | KLOSA_w4$h_diabetes_age %in% miss_values_vector)]-KLOSA_w4$ybirth[KLOSA_ds_w4$h_diabetes == 1 & (KLOSA_w4$h_diabetes==0 | is.na(KLOSA_w4$h_diabetes) | KLOSA_w4$h_diabetes_age %in% miss_values_vector)]
KLOSA_ds_w4$h_diabetes_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes == 0] <- 996
KLOSA_ds_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes == 1 & (KLOSA_w4$h_diabetes==0 | is.na(KLOSA_w4$h_diabetes) | KLOSA_w4$h_diabetes_age %in% miss_values_vector)] <- diabetes_age
KLOSA_ds_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes == 1 & KLOSA_w4$w04C012y==-9] <- 998
KLOSA_ds_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes == 1 & KLOSA_w4$h_diabetes!=0 & !is.na(KLOSA_w4$h_diabetes) & !KLOSA_w4$h_diabetes_age %in% miss_values_vector] <- car::recode(KLOSA_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes == 1 & KLOSA_w4$h_diabetes!=0 & !is.na(KLOSA_w4$h_diabetes) & !KLOSA_w4$h_diabetes_age %in% miss_values_vector],"miss_values_vector=999")
KLOSA_ds_w4$h_diabetes_age <- car::recode(KLOSA_ds_w4$h_diabetes_age, "NA=999")
#KLOSA_ds$h_diabetes_age[(KLOSA_ds$id %in% KLOSA_ds_w4$id) & (KLOSA_ds$h_diabetes != 999)] <- KLOSA_ds_w4$h_diabetes_age[KLOSA_ds_w4$h_diabetes != 999]

KLOSA_ds_w4$h_diabetes_age <- labelled(KLOSA_ds_w4$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(15,95)

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$h_diabetes, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == 5) & (KLOSA_w4$h_diabetes != 1)),
  sum(((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == 1) | ((!is.na(KLOSA_w4$h_diabetes)) & KLOSA_w4$h_diabetes == 1)),
  sum(((!is.na(KLOSA_w4$w04C011)) & KLOSA_w4$w04C011 == -9) & (KLOSA_w4$h_diabetes != 1))
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
KLOSA_ds_w1$h_diabetes <- labelled(KLOSA_ds_w1$h_diabetes, labels = cat_label)
label(KLOSA_ds_w1$h_diabetes) <- ds_label
KLOSA_ds_w1$h_diabetes_age <- labelled(KLOSA_ds_w1$h_diabetes_age, labels = cont_label)
label(KLOSA_ds_w1$h_diabetes_age) <- ds_label_age
KLOSA_ds_w2$h_diabetes <- labelled(KLOSA_ds_w2$h_diabetes, labels = cat_label)
label(KLOSA_ds_w2$h_diabetes) <- ds_label
KLOSA_ds_w2$h_diabetes_age <- labelled(KLOSA_ds_w2$h_diabetes_age, labels = cont_label)
label(KLOSA_ds_w2$h_diabetes_age) <- ds_label_age
KLOSA_ds_w3$h_diabetes <- labelled(KLOSA_ds_w3$h_diabetes, labels = cat_label)
label(KLOSA_ds_w3$h_diabetes) <- ds_label
KLOSA_ds_w3$h_diabetes_age <- labelled(KLOSA_ds_w3$h_diabetes_age, labels = cont_label)
label(KLOSA_ds_w3$h_diabetes_age) <- ds_label_age
KLOSA_ds_w4$h_diabetes <- labelled(KLOSA_ds_w4$h_diabetes, labels = cat_label)
label(KLOSA_ds_w4$h_diabetes) <- ds_label
KLOSA_ds_w4$h_diabetes_age <- labelled(KLOSA_ds_w4$h_diabetes_age, labels = cont_label)
label(KLOSA_ds_w4$h_diabetes_age) <- ds_label_age

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$h_diabetes <- car::recode(KLOSA_m_ds_w1$h_diabetes, "miss_values_vector=NA")
KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$h_diabetes <- car::recode(KLOSA_m_ds_w2$h_diabetes, "miss_values_vector=NA")
KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$h_diabetes <- car::recode(KLOSA_m_ds_w3$h_diabetes, "miss_values_vector=NA")
KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$h_diabetes <- car::recode(KLOSA_m_ds_w4$h_diabetes, "miss_values_vector=NA")


tt <-    frq(KLOSA_ds_w1$h_diabetes)[[1]][,c(1:2,4)]
tt[4] <- frq(KLOSA_ds_w2$h_diabetes)[[1]][,c(4)]
tt[5] <- frq(KLOSA_ds_w3$h_diabetes)[[1]][,c(4)]
tt[6] <- frq(KLOSA_ds_w4$h_diabetes)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(KLOSA_ds_w1$h_diabetes), length(KLOSA_ds_w2$h_diabetes), length(KLOSA_ds_w3$h_diabetes), length(KLOSA_ds_w4$h_diabetes)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4")
kable(tt)

dbb <- merge(KLOSA_m_ds_w1[,c("id","h_diabetes")], KLOSA_m_ds_w2[,c("id","h_diabetes")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, KLOSA_m_ds_w3[,c("id","h_diabetes")], by="id", all=T)
dbb <- merge(dbb, KLOSA_m_ds_w4[,c("id","h_diabetes")], by="id", suffixes = c(".w3",".w4"), all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

The diagnostic diabetes data for individuals which tell in a wave that they have diabetes appears as missing in the next waves. Since all the individuals in the tables are alive (checked by means of the harmonized variable `living status`) we assume it is because the data is asked only for the period between interviews. Therefore we codify them as having diabetes.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.KLOSA <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)

for(index in seq_along(l.KLOSA)){
  h_diabetes <- l.KLOSA[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.KLOSA)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





