---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cpdDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cpdDS.R')
```




# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C019` |`w01C020y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not chronic lung disease diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 5 = no` |`continuous`|`continuous`|
| **Missings** |  | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C019','w01C020y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C019
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C019))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C020y
vbl_miss <- c(-9)
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% vbl_miss), aes(w01C020y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1, h_cpd_age = w01C020y-ybirth`
* `if h_cpd == 0, h_cpd_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$h_cpd <- car::recode(KLOSA_w1$w01C019,"5=0")

# Continuous variable harmonization
KLOSA_ds_w1$h_cpd_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$h_cpd_age[which(KLOSA_ds_w1$h_cpd==1 & !KLOSA_w1$w01C020y %in% c(-9))] <- KLOSA_w1$w01C020y[which(KLOSA_ds_w1$h_cpd==1 & !KLOSA_w1$w01C020y %in% c(-9))] - KLOSA_w1$ybirth[which(KLOSA_ds_w1$h_cpd==1 & !KLOSA_w1$w01C020y %in% c(-9))]
KLOSA_ds_w1$h_cpd_age[which(KLOSA_ds_w1$h_cpd==1 & KLOSA_w1$w01C020y == -9)] <- 998
KLOSA_ds_w1$h_cpd_age[which(KLOSA_ds_w1$h_cpd==0)] <- 996

# We build a global table in order to have updated the chronic pulmonary disorders status of all the individuals through the different waves
KLOSA_ds <- KLOSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$h_cpd)
BeforeH <- table(KLOSA_w1$w01C019, useNA = "ifany")[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C023` |`w02C024y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with chronic lung disease or not`|`The first time of chronic lung disease diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C023','w02C024y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C023
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C023))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C024y
vbl_miss <- c(-9)
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w2 %>% filter(!vbl %in% vbl_miss), aes(x=w02C024y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `w01C019 == 5 and w02C023 == 5 into 0`
* `w01C019 == 1 or w02C023 == 1 into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age = w02C024y-ybirth`
* `if h_cpd == 1 in w2 and w1, h_cpd_age = age from wave 1`
* `if h_cpd == 0, h_cpd_age = 996`
* `-9 into 998`
* `h_cpd == missing into 999`

**R script:**

```{r harmo w2}

KLOSA_w2 <- left_join(KLOSA_w2, KLOSA_ds_w1, by = "id")

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$h_cpd <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_cpd[which(((!is.na(KLOSA_w2$w02C023)) & KLOSA_w2$w02C023 == 5) & (KLOSA_w2$h_cpd != 1))] <- 0
KLOSA_ds_w2$h_cpd[which(((!is.na(KLOSA_w2$w02C023)) & KLOSA_w2$w02C023 == 1) | ((!is.na(KLOSA_w2$h_cpd)) & KLOSA_w2$h_cpd == 1))] <- 1

# We update the chronic pulmonary disorders status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w2,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w2$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_cpd <- KLOSA_ds_prov$h_cpd
rm(KLOSA_ds_prov)

# Continuous variable harmonization
cpd_age <- KLOSA_w2$w02C024y[which(KLOSA_ds_w2$h_cpd == 1 & (KLOSA_w2$h_cpd==0 | is.na(KLOSA_w2$h_cpd) | KLOSA_w2$h_cpd_age %in% miss_values_vector))] - KLOSA_w2$ybirth[which(KLOSA_ds_w2$h_cpd == 1 & (KLOSA_w2$h_cpd==0 | is.na(KLOSA_w2$h_cpd) | KLOSA_w2$h_cpd_age %in% miss_values_vector))]

KLOSA_ds_w2$h_cpd_age <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd == 0)] <- 996
KLOSA_ds_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd == 1 & (KLOSA_w2$h_cpd==0 | is.na(KLOSA_w2$h_cpd) | KLOSA_w2$h_cpd_age %in% miss_values_vector))] <- cpd_age
KLOSA_ds_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd == 1 & KLOSA_w2$w02C024y==-9)] <- 998
KLOSA_ds_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd == 1 & KLOSA_w2$h_cpd==1 & !is.na(KLOSA_w2$h_cpd) & !KLOSA_w2$h_cpd_age %in% miss_values_vector)] <- car::recode(KLOSA_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd == 1 & KLOSA_w2$h_cpd==1 & !KLOSA_w2$h_cpd_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w2$h_cpd_age <- car::recode(KLOSA_ds_w2$h_cpd_age, "NA=999")
KLOSA_ds$h_cpd_age[which((KLOSA_ds$id %in% KLOSA_ds_w2$id) & (KLOSA_ds$h_cpd != 999))] <- KLOSA_ds_w2$h_cpd_age[which(KLOSA_ds_w2$h_cpd != 999)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w2$w02C023)) & KLOSA_w2$w02C023 == 5) & (KLOSA_w2$h_cpd != 1)),
  sum(((!is.na(KLOSA_w2$w02C023)) & KLOSA_w2$w02C023 == 1) | ((!is.na(KLOSA_w2$h_cpd)) & KLOSA_w2$h_cpd == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C023` |`w03C024y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not chronic lung disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C023','w03C024y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C023
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C023))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C024y
vbl_miss <- c(-9)
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3 %>% filter(!vbl %in% vbl_miss), aes(factor(w03C024y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `w01C019 == 5 and w02C023 == 5 and w03C023 == 5 into 0`
* `w01C019 == 1 or w02C023 == 1 or w03C023 == 1 into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w3 and 0 in previous waves, h_cpd_age = w03C024y-ybirth`
* `if h_cpd == 1 in w3 and other wave, h_cpd_age as previously`
* `if h_cpd == 0, h_cpd_age = 996`
* `-9 into 998`
* `h_cpd == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
KLOSA_w3 <- left_join(KLOSA_w3, KLOSA_ds, by = "id")

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$h_cpd <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_cpd[which(((!is.na(KLOSA_w3$w03C023)) & KLOSA_w3$w03C023 == 5) & (KLOSA_w3$h_cpd != 1))] <- 0
KLOSA_ds_w3$h_cpd[which(((!is.na(KLOSA_w3$w03C023)) & KLOSA_w3$w03C023 == 1) | ((!is.na(KLOSA_w3$h_cpd)) & KLOSA_w3$h_cpd == 1))] <- 1

# We update the chronic pulmonary disorders status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w3,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_cpd <- KLOSA_ds_prov$h_cpd
rm(KLOSA_ds_prov)

# Continuous variable harmonization
cpd_age <- KLOSA_w3$w03C024y[which(KLOSA_ds_w3$h_cpd == 1 & (KLOSA_w3$h_cpd==0 | is.na(KLOSA_w3$h_cpd) | KLOSA_w3$h_cpd_age %in% miss_values_vector))] - KLOSA_w3$ybirth[which(KLOSA_ds_w3$h_cpd == 1 & (KLOSA_w3$h_cpd==0 | is.na(KLOSA_w3$h_cpd) | KLOSA_w3$h_cpd_age %in% miss_values_vector))]
KLOSA_ds_w3$h_cpd_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd == 0)] <- 996
KLOSA_ds_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd == 1 & (KLOSA_w3$h_cpd==0 | is.na(KLOSA_w3$h_cpd) | KLOSA_w3$h_cpd_age %in% miss_values_vector))] <- cpd_age
KLOSA_ds_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd == 1 & KLOSA_w3$w03C024y==-9)] <- 998
KLOSA_ds_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd == 1 & KLOSA_w3$h_cpd!=0 & !is.na(KLOSA_w3$h_cpd) & !KLOSA_w3$h_cpd_age %in% miss_values_vector)] <- car::recode(KLOSA_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd == 1 & KLOSA_w3$h_cpd!=0 & !is.na(KLOSA_w3$h_cpd) & !KLOSA_w3$h_cpd_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w3$h_cpd_age <- car::recode(KLOSA_ds_w3$h_cpd_age, "NA=999")
KLOSA_ds$h_cpd_age[which((KLOSA_ds$id %in% KLOSA_ds_w3$id) & (KLOSA_ds$h_cpd != 999))] <- KLOSA_ds_w3$h_cpd_age[which(KLOSA_ds_w3$h_cpd != 999)]

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w3$w03C023)) & KLOSA_w3$w03C023 == 5) & (KLOSA_w3$h_cpd != 1)),
  sum(((!is.na(KLOSA_w3$w03C023)) & KLOSA_w3$w03C023 == 1) | ((!is.na(KLOSA_w3$h_cpd)) & KLOSA_w3$h_cpd == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```




### Wave 4


#### Study-specific variable description

| **Name** | `w04C023` |`w04C024y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not chronic lung disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -9 = Don't know` | `NA` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C023','w04C024y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C023
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C023))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C024y
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C024y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `w01C019 == 5 and w02C023 == 5 and w03C023 == 5 and w04C023 == 5 into 0`
* `w01C019 == 1 or w02C023 == 1 or w03C023 == 1 or w04C023 == 1 into 1`
* `-9 into 998`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w4 and 0 in previous waves, h_cpd_age = w04C024y-ybirth`
* `if h_cpd == 1 in w4 and other wave, h_cpd_age as previously`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
KLOSA_w4 <- left_join(KLOSA_w4, KLOSA_ds, by = "id")

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$h_cpd <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_cpd[which(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == 5) & (KLOSA_w4$h_cpd != 1))] <- 0
KLOSA_ds_w4$h_cpd[which(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == 1) | ((!is.na(KLOSA_w4$h_cpd)) & KLOSA_w4$h_cpd == 1))] <- 1
KLOSA_ds_w4$h_cpd[which(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == -9) & (KLOSA_w4$h_cpd != 1))] <- 998

# We update the chronic pulmonary disorders status of the individuals in the global table
rm(KLOSA_ds)

# Continuous variable harmonization
cpd_age <- KLOSA_w4$w04C024y[which(KLOSA_ds_w4$h_cpd == 1 & (KLOSA_w4$h_cpd==0 | is.na(KLOSA_w4$h_cpd) | KLOSA_w4$h_cpd_age %in% miss_values_vector))] - KLOSA_w4$ybirth[which(KLOSA_ds_w4$h_cpd == 1 & (KLOSA_w4$h_cpd==0 | is.na(KLOSA_w4$h_cpd) | KLOSA_w4$h_cpd_age %in% miss_values_vector))]
KLOSA_ds_w4$h_cpd_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_cpd_age[which(KLOSA_ds_w4$h_cpd == 0)] <- 996
KLOSA_ds_w4$h_cpd_age[which(KLOSA_ds_w4$h_cpd == 1 & (KLOSA_w4$h_cpd==0 | is.na(KLOSA_w4$h_cpd) | KLOSA_w4$h_cpd_age %in% miss_values_vector))] <- cpd_age
KLOSA_ds_w4$h_cpd_age[which(KLOSA_ds_w4$h_cpd == 1 & KLOSA_w4$h_cpd!=0 & !is.na(KLOSA_w4$h_cpd) & !KLOSA_w4$h_cpd_age %in% miss_values_vector)] <- car::recode(KLOSA_w4$h_cpd_age[which(KLOSA_ds_w4$h_cpd == 1 & KLOSA_w4$h_cpd!=0 & !is.na(KLOSA_w4$h_cpd) & !KLOSA_w4$h_cpd_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w4$h_cpd_age <- car::recode(KLOSA_ds_w4$h_cpd_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == 5) & (KLOSA_w4$h_cpd != 1)),
  sum(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == 1) | ((!is.na(KLOSA_w4$h_cpd)) & KLOSA_w4$h_cpd == 1)),
  sum(((!is.na(KLOSA_w4$w04C023)) & KLOSA_w4$w04C023 == -9) & (KLOSA_w4$h_cpd != 1))
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```






<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

klosalist <- lmlist # KLOSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_cpd` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_cpd_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```



# Quality estimation

The chronic pulmonary disorders data for individuals which tell in a wave that they have been diagnosed with chronic lung disease appears as missing in the next waves. Since all the individuals in the tables are alive (checked by means of the harmonized variable `living status`) we assume it is because the data is asked only for the period between interviews. Therefore we codify them as having chronic pulmonary disorders







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





