---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hypertensionDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hypertensionDS.R')
```



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C005` |`w01C006y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not high blood pressure diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 5 = no` |`continuous`|`continuous`|
| **Missings** |  | `-9 = Do not know; -8 = Refuse to answer; NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C005','w01C006y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C005
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C005))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C006y
vbl_miss <- c(-9,-8)
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9,-8))$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% vbl_miss), aes(w01C006y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = w01C006y-ybirth`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-9 into 998`
* `-8 into 997`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$h_hypertension <- car::recode(KLOSA_w1$w01C005,"5=0")

KLOSA_ds_w1$h_hypertension <- labelled(KLOSA_ds_w1$h_hypertension, labels = cat_label)

# Continuous variable harmonization
KLOSA_ds_w1$h_hypertension_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$h_hypertension_age[which(KLOSA_ds_w1$h_hypertension==1 & !KLOSA_w1$w01C006y %in% c(-9,-8))] <- KLOSA_w1$w01C006y[which(KLOSA_ds_w1$h_hypertension==1 & !KLOSA_w1$w01C006y %in% c(-9,-8))] - KLOSA_w1$ybirth[which(KLOSA_ds_w1$h_hypertension==1 & !KLOSA_w1$w01C006y %in% c(-9,-8))]
KLOSA_ds_w1$h_hypertension_age[which(KLOSA_ds_w1$h_hypertension==1 & KLOSA_w1$w01C006y == -9)] <- 998
KLOSA_ds_w1$h_hypertension_age[which(KLOSA_ds_w1$h_hypertension==1 & KLOSA_w1$w01C006y == -8)] <- 997
KLOSA_ds_w1$h_hypertension_age[which(KLOSA_ds_w1$h_hypertension==0)] <- 996

KLOSA_ds_w1$h_hypertension_age <- labelled(KLOSA_ds_w1$h_hypertension_age, labels = cont_label)

# We build a global table in order to have updated the hypertension status of all the individuals through the different waves
KLOSA_ds <- KLOSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$h_hypertension)
BeforeH <- table(KLOSA_w1$w01C005, useNA = "ifany")[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C006` |`w02C007y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with high blood pressure or not`|`The first time of high blood pressure diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C006','w02C007y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C007y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(x=factor(w02C007y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `w01C005 == 5 and w02C006 == 5 into 0`
* `w01C005 == 1 or w02C006 == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = w02C007y-ybirth`
* `if h_hypertension == 1 in w2 and w1, h_hypertension_age = age from wave 1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-9 into 998`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_w2 <- left_join(KLOSA_w2, KLOSA_ds_w1, by = "id")
KLOSA_ds_w2$h_hypertension <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_hypertension[which(((!is.na(KLOSA_w2$w02C006)) & KLOSA_w2$w02C006 == 5) & (KLOSA_w2$h_hypertension != 1))] <- 0
KLOSA_ds_w2$h_hypertension[which(((!is.na(KLOSA_w2$w02C006)) & KLOSA_w2$w02C006 == 1) | ((!is.na(KLOSA_w2$h_hypertension)) & KLOSA_w2$h_hypertension == 1))] <- 1

KLOSA_ds_w2$h_hypertension <- labelled(KLOSA_ds_w2$h_hypertension, labels = cat_label)

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w2,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w2$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_hypertension <- KLOSA_ds_prov$h_hypertension
rm(KLOSA_ds_prov)

# Continuous variable harmonization
hypertension_age <- KLOSA_w2$w02C007y[which(KLOSA_ds_w2$h_hypertension == 1 & (KLOSA_w2$h_hypertension==0 | is.na(KLOSA_w2$h_hypertension) | KLOSA_w2$h_hypertension_age %in% miss_values_vector))] - KLOSA_w2$ybirth[which(KLOSA_ds_w2$h_hypertension == 1 & (KLOSA_w2$h_hypertension==0 | is.na(KLOSA_w2$h_hypertension) | KLOSA_w2$h_hypertension_age %in% miss_values_vector))]

KLOSA_ds_w2$h_hypertension_age <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension == 0)] <- 996
KLOSA_ds_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension == 1 & (KLOSA_w2$h_hypertension==0 | is.na(KLOSA_w2$h_hypertension) | KLOSA_w2$h_hypertension_age %in% miss_values_vector))] <- hypertension_age
KLOSA_ds_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension == 1 & KLOSA_w2$w02C007y==-9)] <- 998
KLOSA_ds_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension == 1 & KLOSA_w2$h_hypertension==1 & !is.na(KLOSA_w2$h_hypertension) & !KLOSA_w2$h_hypertension_age %in% miss_values_vector)] <- car::recode(KLOSA_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension == 1 & KLOSA_w2$h_hypertension==1 & !KLOSA_w2$h_hypertension_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w2$h_hypertension_age <- car::recode(KLOSA_ds_w2$h_hypertension_age, "NA=999")
KLOSA_ds$h_hypertension_age[which((KLOSA_ds$id %in% KLOSA_ds_w2$id) & (KLOSA_ds$h_hypertension != 999))] <- KLOSA_ds_w2$h_hypertension_age[which(KLOSA_ds_w2$h_hypertension != 999)]

KLOSA_ds_w2$h_hypertension_age <- labelled(KLOSA_ds_w2$h_hypertension_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w2$w02C006)) & KLOSA_w2$w02C006 == 5) & (KLOSA_w2$h_hypertension != 1)),
  sum(((!is.na(KLOSA_w2$w02C006)) & KLOSA_w2$w02C006 == 1) | ((!is.na(KLOSA_w2$h_hypertension)) & KLOSA_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C006` |`w03C007y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not high blood pressure diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C006','w03C007y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C007y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(factor(w03C007y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `w01C005 == 5 and w02C006 == 5 and w03C006 == 5 into 0`
* `w01C005 == 1 or w02C006 == 1 or w03C006 == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w3 and 0 in previous waves, h_hypertension_age = w03C007y-ybirth`
* `if h_hypertension == 1 in w3 and other wave, h_hypertension_age as previously`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-9 into 998`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)

KLOSA_w3 <- left_join(KLOSA_w3, KLOSA_ds, by = "id")
KLOSA_ds_w3$h_hypertension <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_hypertension[which(((!is.na(KLOSA_w3$w03C006)) & KLOSA_w3$w03C006 == 5) & (KLOSA_w3$h_hypertension != 1))] <- 0
KLOSA_ds_w3$h_hypertension[which(((!is.na(KLOSA_w3$w03C006)) & KLOSA_w3$w03C006 == 1) | ((!is.na(KLOSA_w3$h_hypertension)) & KLOSA_w3$h_hypertension == 1))] <- 1

KLOSA_ds_w3$h_hypertension <- labelled(KLOSA_ds_w3$h_hypertension, labels = cat_label)

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w3,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_hypertension <- KLOSA_ds_prov$h_hypertension
rm(KLOSA_ds_prov)



# Continuous variable harmonization
hypertension_age <- KLOSA_w3$w03C007y[which(KLOSA_ds_w3$h_hypertension == 1 & (KLOSA_w3$h_hypertension==0 | is.na(KLOSA_w3$h_hypertension) | KLOSA_w3$h_hypertension_age %in% miss_values_vector))] - KLOSA_w3$ybirth[which(KLOSA_ds_w3$h_hypertension == 1 & (KLOSA_w3$h_hypertension==0 | is.na(KLOSA_w3$h_hypertension) | KLOSA_w3$h_hypertension_age %in% miss_values_vector))]
KLOSA_ds_w3$h_hypertension_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension == 0)] <- 996
KLOSA_ds_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension == 1 & (KLOSA_w3$h_hypertension==0 | is.na(KLOSA_w3$h_hypertension) | KLOSA_w3$h_hypertension_age %in% miss_values_vector))] <- hypertension_age
KLOSA_ds_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension == 1 & KLOSA_w3$w03C007y==-9)] <- 998
KLOSA_ds_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension == 1 & KLOSA_w3$h_hypertension!=0 & !is.na(KLOSA_w3$h_hypertension) & ! KLOSA_w3$h_hypertension_age %in% miss_values_vector)] <- car::recode(KLOSA_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension == 1 & KLOSA_w3$h_hypertension!=0 & !is.na(KLOSA_w3$h_hypertension) & !KLOSA_w3$h_hypertension_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w3$h_hypertension_age <- car::recode(KLOSA_ds_w3$h_hypertension_age, "NA=999")
KLOSA_ds$h_hypertension_age[which((KLOSA_ds$id %in% KLOSA_ds_w3$id) & (KLOSA_ds$h_hypertension != 999))] <- KLOSA_ds_w3$h_hypertension_age[which(KLOSA_ds_w3$h_hypertension != 999)]

KLOSA_ds_w3$h_hypertension_age <- labelled(KLOSA_ds_w3$h_hypertension_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w3$w03C006)) & KLOSA_w3$w03C006 == 5) & (KLOSA_w3$h_hypertension != 1)),
  sum(((!is.na(KLOSA_w3$w03C006)) & KLOSA_w3$w03C006 == 1) | ((!is.na(KLOSA_w3$h_hypertension)) & KLOSA_w3$h_hypertension == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```




### Wave 4


#### Study-specific variable description

| **Name** | `w04C006` |`w04C007y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not high blood pressure diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C006','w04C007y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C007y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C007y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `w01C005 == 5 and w02C006 == 5 and w03C006 == 5 and w04C006 == 5 into 0`
* `w01C005 == 1 or w02C006 == 1 or w03C006 == 1 or w04C006 == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w4 and 0 in previous waves, h_hypertension_age = w04C007y-ybirth`
* `if h_hypertension == 1 in w4 and other wave, h_hypertension_age as previously`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `-9 into 998`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)

KLOSA_w4 <- left_join(KLOSA_w4, KLOSA_ds, by = "id")
KLOSA_ds_w4$h_hypertension <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_hypertension[which(((!is.na(KLOSA_w4$w04C006)) & KLOSA_w4$w04C006 == 5) & (KLOSA_w4$h_hypertension != 1))] <- 0
KLOSA_ds_w4$h_hypertension[which(((!is.na(KLOSA_w4$w04C006)) & KLOSA_w4$w04C006 == 1) | ((!is.na(KLOSA_w4$h_hypertension)) & KLOSA_w4$h_hypertension == 1))] <- 1

KLOSA_ds_w4$h_hypertension <- labelled(KLOSA_ds_w4$h_hypertension, labels = cat_label)

# # We update the hypertension status of the individuals in the global table
rm(KLOSA_ds)

# Continuous variable harmonization
hypertension_age <- KLOSA_w4$w04C007y[which(KLOSA_ds_w4$h_hypertension == 1 & (KLOSA_w4$h_hypertension==0 | is.na(KLOSA_w4$h_hypertension) | KLOSA_w4$h_hypertension_age %in% miss_values_vector))]-KLOSA_w4$ybirth[which(KLOSA_ds_w4$h_hypertension == 1 & (KLOSA_w4$h_hypertension==0 | is.na(KLOSA_w4$h_hypertension) | KLOSA_w4$h_hypertension_age %in% miss_values_vector))]
KLOSA_ds_w4$h_hypertension_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_hypertension_age[which(KLOSA_ds_w4$h_hypertension == 0)] <- 996
KLOSA_ds_w4$h_hypertension_age[which(KLOSA_ds_w4$h_hypertension == 1 & (KLOSA_w4$h_hypertension==0 | is.na(KLOSA_w4$h_hypertension) | KLOSA_w4$h_hypertension_age %in% miss_values_vector))] <- hypertension_age
KLOSA_ds_w4$h_hypertension_age[which(KLOSA_ds_w4$h_hypertension == 1 & KLOSA_w4$w04C007y==-9)] <- 998
KLOSA_ds_w4$h_hypertension_age[which(KLOSA_ds_w4$h_hypertension == 1 & KLOSA_w4$h_hypertension!=0 & !is.na(KLOSA_w4$h_hypertension) & !KLOSA_w4$h_hypertension_age %in% miss_values_vector)] <- car::recode(KLOSA_w4$h_hypertension_age[which(KLOSA_ds_w4$h_hypertension == 1 & KLOSA_w4$h_hypertension!=0 & !is.na(KLOSA_w4$h_hypertension) & !KLOSA_w4$h_hypertension_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w4$h_hypertension_age <- car::recode(KLOSA_ds_w4$h_hypertension_age, "NA=999")
#KLOSA_ds$h_hypertension_age[(KLOSA_ds$id %in% KLOSA_ds_w4$id) & (KLOSA_ds$h_hypertension != 999)] <- KLOSA_ds_w4$h_hypertension_age[KLOSA_ds_w4$h_hypertension != 999]

KLOSA_ds_w4$h_hypertension_age <- labelled(KLOSA_ds_w4$h_hypertension_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w4$w04C006)) & KLOSA_w4$w04C006 == 5) & (KLOSA_w4$h_hypertension != 1)),
  sum(((!is.na(KLOSA_w4$w04C006)) & KLOSA_w4$w04C006 == 1) | ((!is.na(KLOSA_w4$h_hypertension)) & KLOSA_w4$h_hypertension == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

klosalist <- lmlist # KLOSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_hypertension` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_hypertension_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```




# Quality estimation

The diagnostic hypertension data for individuals which tell in a wave that they have hypertension appears as missing in the next waves. Since all the individuals in the tables are alive (checked by means of the harmonized variable `living status`) we assume it is because the data is asked only for the period between interviews. Therefore we codify them as having hypertension.





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





