---
title: "Joint disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```

<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/joint_disordersDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/joint_disordersDS.R')
```



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C039` |`w01C040y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not arthritis and class Henri Matisse diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 5 = no` |`continuous`|`continuous`|
| **Missings** |`-9 = Do not know`  | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C039','w01C040y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C039
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C039))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C040y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(w01C040y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1940,2010)

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`
* `-9 into 998`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1, h_joint_disorders_age = w01C040y-ybirth`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$h_joint_disorders <- car::recode(KLOSA_w1$w01C039,"5=0; -9=998")

KLOSA_ds_w1$h_joint_disorders <- labelled(KLOSA_ds_w1$h_joint_disorders, labels = cat_label)

# Continuous variable harmonization
KLOSA_ds_w1$h_joint_disorders_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$h_joint_disorders_age[KLOSA_ds_w1$h_joint_disorders==1 & (!KLOSA_w1$w01C040y %in% c(-9)) & !is.na(KLOSA_w1$w01C040y)] <- KLOSA_w1$w01C040y[KLOSA_ds_w1$h_joint_disorders==1 & !is.na(KLOSA_w1$w01C040y) & !KLOSA_w1$w01C040y %in% c(-9)] - KLOSA_w1$ybirth[KLOSA_ds_w1$h_joint_disorders==1 & !is.na(KLOSA_w1$w01C040y) & !KLOSA_w1$w01C040y %in% c(-9)]
KLOSA_ds_w1$h_joint_disorders_age[KLOSA_ds_w1$h_joint_disorders==1 & KLOSA_w1$w01C040y == -9] <- 998
KLOSA_ds_w1$h_joint_disorders_age[KLOSA_ds_w1$h_joint_disorders==0] <- 996

KLOSA_ds_w1$h_joint_disorders_age <- labelled(KLOSA_ds_w1$h_joint_disorders_age, labels = cont_label)

# We build a global table in order to have updated the joint disorders status of all the individuals through the different waves
KLOSA_ds <- KLOSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,90)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$h_joint_disorders)
BeforeH <- table(KLOSA_w1$w01C039, useNA = "ifany")[c(3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C048` |`w02C049y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with arthritis and rheumatism disease or not`|`The first time of arthritis and rheumatism disease diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C048','w02C049y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C048
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C048))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C049y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(x=factor(w02C049y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `w01C039 == 5 and w02C048 == 5 into 0`
* `w01C039 == 1 or w02C048 == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w2 and 0 in w1, h_joint_disorders_age = w02C049y-ybirth`
* `if h_joint_disorders == 1 in w2 and w1, h_joint_disorders_age = age from wave 1`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `-9 into 998`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w2}

KLOSA_w2 <- left_join(KLOSA_w2, KLOSA_ds, by = "id")

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$h_joint_disorders <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_joint_disorders[((!is.na(KLOSA_w2$w02C048)) & KLOSA_w2$w02C048 == 5) & (KLOSA_w2$h_joint_disorders != 1)] <- 0
KLOSA_ds_w2$h_joint_disorders[((!is.na(KLOSA_w2$w02C048)) & KLOSA_w2$w02C048 == 1) | ((!is.na(KLOSA_w2$h_joint_disorders)) & KLOSA_w2$h_joint_disorders == 1)] <- 1

KLOSA_ds_w2$h_joint_disorders <- labelled(KLOSA_ds_w2$h_joint_disorders, labels = cat_label)

# We update the joint disorders status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w2,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w2$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_joint_disorders <- KLOSA_ds_prov$h_joint_disorders
rm(KLOSA_ds_prov)

# Continuous variable harmonization
joint_disorders_age <- KLOSA_w2$w02C049y[KLOSA_ds_w2$h_joint_disorders == 1 & (KLOSA_w2$h_joint_disorders==0 | is.na(KLOSA_w2$h_joint_disorders) | KLOSA_w2$h_joint_disorders_age %in% miss_values_vector)]-KLOSA_w2$ybirth[KLOSA_ds_w2$h_joint_disorders == 1 & (KLOSA_w2$h_joint_disorders==0 | is.na(KLOSA_w2$h_joint_disorders) | KLOSA_w2$h_joint_disorders_age %in% miss_values_vector)]

KLOSA_ds_w2$h_joint_disorders_age <- rep(999,length(KLOSA_w2$id))
KLOSA_ds_w2$h_joint_disorders_age[KLOSA_ds_w2$h_joint_disorders == 0] <- 996
KLOSA_ds_w2$h_joint_disorders_age[KLOSA_ds_w2$h_joint_disorders == 1 & (KLOSA_w2$h_joint_disorders==0 | is.na(KLOSA_w2$h_joint_disorders) | KLOSA_w2$h_joint_disorders_age %in% miss_values_vector)] <- joint_disorders_age
KLOSA_ds_w2$h_joint_disorders_age[KLOSA_ds_w2$h_joint_disorders == 1 & KLOSA_w2$w02C049y==-9] <- 998
KLOSA_ds_w2$h_joint_disorders_age[KLOSA_ds_w2$h_joint_disorders == 1 & KLOSA_w2$h_joint_disorders==1 & !is.na(KLOSA_w2$h_joint_disorders) & !KLOSA_w2$h_joint_disorders_age %in% miss_values_vector] <- car::recode(KLOSA_w2$h_joint_disorders_age[which(KLOSA_ds_w2$h_joint_disorders == 1 & KLOSA_w2$h_joint_disorders==1 & !KLOSA_w2$h_joint_disorders_age %in% miss_values_vector)],"miss_values_vector=999")
KLOSA_ds_w2$h_joint_disorders_age <- car::recode(KLOSA_ds_w2$h_joint_disorders_age, "NA=999")
KLOSA_ds$h_joint_disorders_age[(KLOSA_ds$id %in% KLOSA_ds_w2$id) & (KLOSA_ds$h_joint_disorders != 999)] <- KLOSA_ds_w2$h_joint_disorders_age[KLOSA_ds_w2$h_joint_disorders != 999]

KLOSA_ds_w2$h_joint_disorders_age <- labelled(KLOSA_ds_w2$h_joint_disorders_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$h_joint_disorders, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w2$w02C048)) & KLOSA_w2$w02C048 == 5) & (KLOSA_w2$h_joint_disorders != 1)),
  sum(((!is.na(KLOSA_w2$w02C048)) & KLOSA_w2$w02C048 == 1) | ((!is.na(KLOSA_w2$h_joint_disorders)) & KLOSA_w2$h_joint_disorders == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C048` |`w03C049y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not arthritis and class Henri Matisse diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C048','w03C049y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C048
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C048))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C049y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(factor(w03C049y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `w01C039 == 5 and w02C048 == 5 and w03C048 == 5 into 0`
* `w01C039 == 1 or w02C048 == 1 or w03C048 == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w3 and 0 in previous waves, h_joint_disorders_age = w03C049y-ybirth`
* `if h_joint_disorders == 1 in w3 and other wave, h_joint_disorders_age as previously`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `-9 into 998`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
KLOSA_w3 <- left_join(KLOSA_w3, KLOSA_ds, by = "id")

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$h_joint_disorders <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_joint_disorders[((!is.na(KLOSA_w3$w03C048)) & KLOSA_w3$w03C048 == 5) & (KLOSA_w3$h_joint_disorders != 1)] <- 0
KLOSA_ds_w3$h_joint_disorders[((!is.na(KLOSA_w3$w03C048)) & KLOSA_w3$w03C048 == 1) | ((!is.na(KLOSA_w3$h_joint_disorders)) & KLOSA_w3$h_joint_disorders == 1)] <- 1

KLOSA_ds_w3$h_joint_disorders <- labelled(KLOSA_ds_w3$h_joint_disorders, labels = cat_label)

# We update the joint disorders status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
KLOSA_ds_prov <- KLOSA_ds[,c(1,2)]
KLOSA_ds_prov <- assign_merge(KLOSA_ds_prov,KLOSA_ds_w3,log_vec=(KLOSA_ds_prov$id %in% KLOSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
KLOSA_ds$h_joint_disorders <- KLOSA_ds_prov$h_joint_disorders
rm(KLOSA_ds_prov)



# Continuous variable harmonization
joint_disorders_age <- KLOSA_w3$w03C049y[KLOSA_ds_w3$h_joint_disorders == 1 & (KLOSA_w3$h_joint_disorders==0 | is.na(KLOSA_w3$h_joint_disorders) | KLOSA_w3$h_joint_disorders_age %in% miss_values_vector)]-KLOSA_w3$ybirth[KLOSA_ds_w3$h_joint_disorders == 1 & (KLOSA_w3$h_joint_disorders==0 | is.na(KLOSA_w3$h_joint_disorders) | KLOSA_w3$h_joint_disorders_age %in% miss_values_vector)]
KLOSA_ds_w3$h_joint_disorders_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders == 0] <- 996
KLOSA_ds_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders == 1 & (KLOSA_w3$h_joint_disorders==0 | is.na(KLOSA_w3$h_joint_disorders) | KLOSA_w3$h_joint_disorders_age %in% miss_values_vector)] <- joint_disorders_age
KLOSA_ds_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders == 1 & KLOSA_w3$w03C049y==-9] <- 998
KLOSA_ds_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders == 1 & KLOSA_w3$h_joint_disorders!=0 & !is.na(KLOSA_w3$h_joint_disorders) & !KLOSA_w3$h_joint_disorders_age %in% miss_values_vector] <- car::recode(KLOSA_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders == 1 & KLOSA_w3$h_joint_disorders!=0 & !is.na(KLOSA_w3$h_joint_disorders) & !KLOSA_w3$h_joint_disorders_age %in% miss_values_vector],"miss_values_vector=999")
KLOSA_ds_w3$h_joint_disorders_age <- car::recode(KLOSA_ds_w3$h_joint_disorders_age, "NA=999")
KLOSA_ds$h_joint_disorders_age[(KLOSA_ds$id %in% KLOSA_ds_w3$id) & (KLOSA_ds$h_joint_disorders != 999)] <- KLOSA_ds_w3$h_joint_disorders_age[KLOSA_ds_w3$h_joint_disorders != 999]

KLOSA_ds_w3$h_joint_disorders_age <- labelled(KLOSA_ds_w3$h_joint_disorders_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,95)

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$h_joint_disorders, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w3$w03C048)) & KLOSA_w3$w03C048 == 5) & (KLOSA_w3$h_joint_disorders != 1)),
  sum(((!is.na(KLOSA_w3$w03C048)) & KLOSA_w3$w03C048 == 1) | ((!is.na(KLOSA_w3$h_joint_disorders)) & KLOSA_w3$h_joint_disorders == 1))
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1")
kable(C)

```




### Wave 4


#### Study-specific variable description

| **Name** | `w04C048` |`w04C049y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not arthritis and class Henri Matisse diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -9 = Don't know` | `NA` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C048','w04C049y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C048
kable(Categorical_summary(vbl, missing_values = c(-9))[3], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-9))[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C048))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C049y
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C049y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `w01C039 == 5 and w02C048 == 5 and w03C048 == 5 and w04C048 == 5 into 0`
* `w01C039 == 1 or w02C048 == 1 or w03C048 == 1 or w04C048 == 1 into 1`
* `-9 into 998`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w4 and 0 in previous waves, h_joint_disorders_age = w04C049y-ybirth`
* `if h_joint_disorders == 1 in w4 and other wave, h_joint_disorders_age as previously`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w4}

# We use the harmonized variable of previous waves instead of the study-specific variables
KLOSA_w4 <- left_join(KLOSA_w4, KLOSA_ds, by = "id")

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$h_joint_disorders <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_joint_disorders[((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == 5) & (KLOSA_w4$h_joint_disorders != 1)] <- 0
KLOSA_ds_w4$h_joint_disorders[((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == 1) | ((!is.na(KLOSA_w4$h_joint_disorders)) & KLOSA_w4$h_joint_disorders == 1)] <- 1
KLOSA_ds_w4$h_joint_disorders[((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == -9) & (KLOSA_w4$h_joint_disorders != 1)] <- 998

KLOSA_ds_w4$h_joint_disorders <- labelled(KLOSA_ds_w4$h_joint_disorders, labels = cat_label)

# Continuous variable harmonization
joint_disorders_age <- KLOSA_w4$w04C049y[KLOSA_ds_w4$h_joint_disorders == 1 & (KLOSA_w4$h_joint_disorders==0 | is.na(KLOSA_w4$h_joint_disorders) | KLOSA_w4$h_joint_disorders_age %in% miss_values_vector)]-KLOSA_w4$ybirth[KLOSA_ds_w4$h_joint_disorders == 1 & (KLOSA_w4$h_joint_disorders==0 | is.na(KLOSA_w4$h_joint_disorders) | KLOSA_w4$h_joint_disorders_age %in% miss_values_vector)]
KLOSA_ds_w4$h_joint_disorders_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$h_joint_disorders_age[KLOSA_ds_w4$h_joint_disorders == 0] <- 996
KLOSA_ds_w4$h_joint_disorders_age[KLOSA_ds_w4$h_joint_disorders == 1 & (KLOSA_w4$h_joint_disorders==0 | is.na(KLOSA_w4$h_joint_disorders) | KLOSA_w4$h_joint_disorders_age %in% miss_values_vector)] <- joint_disorders_age
KLOSA_ds_w4$h_joint_disorders_age[KLOSA_ds_w4$h_joint_disorders == 1 & KLOSA_w4$h_joint_disorders!=0 & !is.na(KLOSA_w4$h_joint_disorders) & !KLOSA_w4$h_joint_disorders_age %in% miss_values_vector] <- car::recode(KLOSA_w4$h_joint_disorders_age[KLOSA_ds_w4$h_joint_disorders == 1 & KLOSA_w4$h_joint_disorders!=0 & !is.na(KLOSA_w4$h_joint_disorders) & !KLOSA_w4$h_joint_disorders_age %in% miss_values_vector],"miss_values_vector=999")
KLOSA_ds_w4$h_joint_disorders_age <- car::recode(KLOSA_ds_w4$h_joint_disorders_age, "NA=999")

KLOSA_ds_w4$h_joint_disorders_age <- labelled(KLOSA_ds_w4$h_joint_disorders_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$h_joint_disorders, useNA = "ifany")
X <- c(
  sum(((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == 5) & (KLOSA_w4$h_joint_disorders != 1)),
  sum(((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == 1) | ((!is.na(KLOSA_w4$h_joint_disorders)) & KLOSA_w4$h_joint_disorders == 1)),
  sum(((!is.na(KLOSA_w4$w04C048)) & KLOSA_w4$w04C048 == -9) & (KLOSA_w4$h_joint_disorders != 1))
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-9->998")
kable(C)

```





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

klosalist <- lmlist # KLOSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_joint_disorders` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_joint_disorders_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```



# Quality estimation

The diagnostic joint disorders data for the individuals which tell in a wave that they have joint disorders appears as missing in the next waves (except in one case). Since all the individuals in the tables are alive (checked by means of the harmonized variable `living status`) we assume it is because the data is asked only for the period between interviews. Therefore we codify them as having joint disorders.





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





