---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `stroke`
* Variable label: `Stroke`
* Variable description: `Diagnosis of stroke or cerebral vascular disease since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT A stroke (cerebral vascular disease) 
1        | A stroke (cerebral vascular disease)

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `stroke_age`
* Variable label: `Age of each episode of stroke`
* Variable description: `Age of each episode of stroke`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke"
ds_label_age <- "Age of each episode of stroke"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C031` |`w01C032y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 3 = (vol) Possible stroke or transient ischemic attack(TIA); 5 = no` |`continuous`|`continuous`|
| **Missings** |  | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C031','w01C032y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C031
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C031))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C032y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(w01C032y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1965,2010)

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w01C032y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$stroke <- car::recode(KLOSA_w1$w01C031,"3=1; 5=0")

# Continuous variable harmonization
KLOSA_ds_w1$stroke_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$stroke_age[KLOSA_ds_w1$stroke==1] <- KLOSA_w1$w01C032y[KLOSA_ds_w1$stroke==1] - KLOSA_w1$ybirth[KLOSA_ds_w1$stroke==1]
KLOSA_ds_w1$stroke_age[KLOSA_ds_w1$stroke==1 & KLOSA_w1$w01C032y == -9] <- 998
KLOSA_ds_w1$stroke_age[KLOSA_ds_w1$stroke==0] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(35,90)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$stroke)
X <- table(KLOSA_w1$w01C031, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C038` |`w02C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with cerebral vascular disease or not`|`The first time of cerebral vascular disease diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 3= Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C038','w02C039y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C038
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C039y
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(x=factor(w02C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1965)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w02C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `NA into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$stroke <- car::recode(KLOSA_w2$w02C038,"3=1; 5=0; NA=999")

# Continuous variable harmonization
KLOSA_ds_w2$stroke_age <- rep(999,length(KLOSA_ds_w2$id))
KLOSA_ds_w2$stroke_age[KLOSA_ds_w2$stroke==1] <- KLOSA_w2$w02C039y[KLOSA_ds_w2$stroke==1] - KLOSA_w2$ybirth[KLOSA_ds_w2$stroke==1]
KLOSA_ds_w2$stroke_age[KLOSA_ds_w2$stroke==0] <- 996
KLOSA_ds_w2$stroke_age <- car::recode(KLOSA_ds_w2$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,90)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$stroke)
X <- table(KLOSA_w2$w02C038, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","NA->999")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C038` |`w03C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 3 = Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C038','w03C039y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C038
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C039y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(factor(w03C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w03C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$stroke <- car::recode(KLOSA_w3$w03C038,"3=1; 5=0; NA=999")

# Continuous variable harmonization
KLOSA_ds_w3$stroke_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$stroke_age[KLOSA_ds_w3$stroke == 0] <- 996
KLOSA_ds_w3$stroke_age[KLOSA_ds_w3$stroke == 1] <- KLOSA_w3$w03C039y[KLOSA_ds_w3$stroke == 1]-KLOSA_w3$ybirth[KLOSA_ds_w3$stroke == 1]
KLOSA_ds_w3$stroke_age[KLOSA_ds_w3$stroke == 1 & KLOSA_w3$w03C039y==-9] <- 998
KLOSA_ds_w3$stroke_age <- car::recode(KLOSA_ds_w3$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,95)

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$stroke)
X <- table(KLOSA_w3$w03C038, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","NA->999")
kable(C)

```



### Wave 4


#### Study-specific variable description

| **Name** | `w04C038` |`w04C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 3 = Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -8 = Refuse to answer` | `NA; -8 = Refuse to answer` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C038','w04C039y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C038
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C039y
kable(Continuous_summary(var = vbl, missing_values = c(-8))[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1965)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`
* `-8 into 997`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w04C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `NA into 999`
* `-8 into 997`
* `stroke == missing into 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$stroke <- car::recode(KLOSA_w4$w04C038,"3=1; 5=0; -8=997; NA=999")

# Continuous variable harmonization
KLOSA_ds_w4$stroke_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$stroke_age[KLOSA_ds_w4$stroke == 0] <- 996
KLOSA_ds_w4$stroke_age[KLOSA_ds_w4$stroke == 1] <- KLOSA_w4$w04C039y[KLOSA_ds_w4$stroke == 1]-KLOSA_w4$ybirth[KLOSA_ds_w4$stroke == 1]
KLOSA_ds_w4$stroke_age[KLOSA_ds_w4$stroke == 1 & KLOSA_w4$w04C039y==-8] <- 997
KLOSA_ds_w4$stroke_age <- car::recode(KLOSA_ds_w4$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,95)

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$stroke)
X <- table(KLOSA_w4$w04C038, useNA = "ifany")
BeforeH <- c(X[4],sum(X[2:3]),X[c(1,5)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","-8->997","NA->999")
kable(C)


```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
KLOSA_ds_w1$stroke <- labelled(KLOSA_ds_w1$stroke, labels = cat_label)
label(KLOSA_ds_w1$stroke) <- ds_label
KLOSA_ds_w1$stroke_age <- labelled(KLOSA_ds_w1$stroke_age, labels = cont_label)
label(KLOSA_ds_w1$stroke_age) <- ds_label_age
KLOSA_ds_w2$stroke <- labelled(KLOSA_ds_w2$stroke, labels = cat_label)
label(KLOSA_ds_w2$stroke) <- ds_label
KLOSA_ds_w2$stroke_age <- labelled(KLOSA_ds_w2$stroke_age, labels = cont_label)
label(KLOSA_ds_w2$stroke_age) <- ds_label_age
KLOSA_ds_w3$stroke <- labelled(KLOSA_ds_w3$stroke, labels = cat_label)
label(KLOSA_ds_w3$stroke) <- ds_label
KLOSA_ds_w3$stroke_age <- labelled(KLOSA_ds_w3$stroke_age, labels = cont_label)
label(KLOSA_ds_w3$stroke_age) <- ds_label_age
KLOSA_ds_w4$stroke <- labelled(KLOSA_ds_w4$stroke, labels = cat_label)
label(KLOSA_ds_w4$stroke) <- ds_label
KLOSA_ds_w4$stroke_age <- labelled(KLOSA_ds_w4$stroke_age, labels = cont_label)
label(KLOSA_ds_w4$stroke_age) <- ds_label_age

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$stroke <- car::recode(KLOSA_m_ds_w1$stroke, "miss_values_vector=NA")
KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$stroke <- car::recode(KLOSA_m_ds_w2$stroke, "miss_values_vector=NA")
KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$stroke <- car::recode(KLOSA_m_ds_w3$stroke, "miss_values_vector=NA")
KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$stroke <- car::recode(KLOSA_m_ds_w4$stroke, "miss_values_vector=NA")


tt <-    frq(KLOSA_ds_w1$stroke)[[1]][,c(1:2,4)]
tt[4] <- frq(KLOSA_ds_w2$stroke)[[1]][,c(4)]
tt[5] <- frq(KLOSA_ds_w3$stroke)[[1]][,c(4)]
tt[6] <- frq(KLOSA_ds_w4$stroke)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(KLOSA_ds_w1$stroke), length(KLOSA_ds_w2$stroke), length(KLOSA_ds_w3$stroke), length(KLOSA_ds_w4$stroke)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4")
kable(tt)

dbb <- merge(KLOSA_m_ds_w1[,c("id","stroke")], KLOSA_m_ds_w2[,c("id","stroke")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, KLOSA_m_ds_w3[,c("id","stroke")], by="id", all=T)
dbb <- merge(dbb, KLOSA_m_ds_w4[,c("id","stroke")], by="id", suffixes = c(".w3",".w4"), all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

* The diagnostic stroke data for individuals which tell in a wave that they have stroke is missing in all the next waves, so the age of diagnostic too. This fact is preserved in the harmonized variable.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.KLOSA <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)

for(index in seq_along(l.KLOSA)){
  stroke <- l.KLOSA[[index]]
  save(stroke, file = paste0(datafolder,names(l.KLOSA)[index],"/stroke.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





