---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---



<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/strokeDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/strokeDS.R')
```

# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C031` |`w01C032y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic`|`Time that is diagnosed by first(unit : Year)`|`year of birth`|
| **Table name**  | `w01_main_e`| `w01_main_e`|`ybirth`|
| **Categories** | `1 = Yes; 3 = (vol) Possible stroke or transient ischemic attack(TIA); 5 = no` |`continuous`|`continuous`|
| **Missings** |  | `-9 = Do not know; NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C031','w01C032y'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
KLOSA_w1 <- left_join(KLOSA_w1,ybirth,by="id")

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C031
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C031))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C032y
vbl_miss <- c(-9)
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% vbl_miss), aes(w01C032y)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w01C032y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$stroke <- car::recode(KLOSA_w1$w01C031,"3=1; 5=0")

# Continuous variable harmonization
KLOSA_ds_w1$stroke_age <- rep(999,length(KLOSA_ds_w1$id))
KLOSA_ds_w1$stroke_age[which(KLOSA_ds_w1$stroke==1)] <- KLOSA_w1$w01C032y[which(KLOSA_ds_w1$stroke==1)] - KLOSA_w1$ybirth[which(KLOSA_ds_w1$stroke==1)]
KLOSA_ds_w1$stroke_age[which(KLOSA_ds_w1$stroke==1 & KLOSA_w1$w01C032y == -9)] <- 998
KLOSA_ds_w1$stroke_age[which(KLOSA_ds_w1$stroke==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(KLOSA_ds_w1$stroke)
X <- table(KLOSA_w1$w01C031, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C038` |`w02C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Since previous interview, whether been diagnosed with cerebral vascular disease or not`|`The first time of cerebral vascular disease diagnostic(yyyy)`|`year of birth`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 3= Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C038','w02C039y'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
KLOSA_w2 <- left_join(KLOSA_w2,ybirth,by="id")

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C038
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C039y
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(KLOSA_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(x=factor(w02C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w02C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `NA into 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$stroke <- car::recode(KLOSA_w2$w02C038,"3=1; 5=0; NA=999")

# Continuous variable harmonization
KLOSA_ds_w2$stroke_age <- rep(999,length(KLOSA_ds_w2$id))
KLOSA_ds_w2$stroke_age[which(KLOSA_ds_w2$stroke==1)] <- KLOSA_w2$w02C039y[which(KLOSA_ds_w2$stroke==1)] - KLOSA_w2$ybirth[which(KLOSA_ds_w2$stroke==1)]
KLOSA_ds_w2$stroke_age[which(KLOSA_ds_w2$stroke==0)] <- 996
KLOSA_ds_w2$stroke_age <- car::recode(KLOSA_ds_w2$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(KLOSA_ds_w2$stroke)
X <- table(KLOSA_w2$w02C038, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","NA->999")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C038` |`w03C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|`ybirth`|
| **Categories** | `1 = yes; 3 = Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA; -9 = Don't know` |  |
| **Description** |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C038','w03C039y'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)
load(paste0(datafolder,"w3/ybirth.RData"))
KLOSA_w3 <- left_join(KLOSA_w3,ybirth,by="id")

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C038
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C039y
kable(Continuous_summary(var = vbl, missing_values = c(-9))[3], caption = names(KLOSA_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(-9))$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(factor(w03C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w03C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$stroke <- car::recode(KLOSA_w3$w03C038,"3=1; 5=0; NA=999")

# Continuous variable harmonization
KLOSA_ds_w3$stroke_age <- rep(999,length(KLOSA_w3$id))
KLOSA_ds_w3$stroke_age[which(KLOSA_ds_w3$stroke == 0)] <- 996
KLOSA_ds_w3$stroke_age[which(KLOSA_ds_w3$stroke == 1)] <- KLOSA_w3$w03C039y[which(KLOSA_ds_w3$stroke == 1)]-KLOSA_w3$ybirth[which(KLOSA_ds_w3$stroke == 1)]
KLOSA_ds_w3$stroke_age[which(KLOSA_ds_w3$stroke == 1 & KLOSA_w3$w03C039y==-9)] <- 998
KLOSA_ds_w3$stroke_age <- car::recode(KLOSA_ds_w3$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w3$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w3 %>% filter(!vbl %in% miss_values_vector), aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w3$stroke)
X <- table(KLOSA_w3$w03C038, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","NA->999")
kable(C)

```



### Wave 4


#### Study-specific variable description

| **Name** | `w04C038` |`w04C039y`|`ybirth`|
|-|-|-|-|
| **Label** | `Whether or not cerebral vascular disease diagnostic since previous interview`|`The time when is diagnosed by first(yyyy)`|`year of birth`|
| **Table name**  | `w04_main_e_spss`| `w04_main_e_spss`|`ybirth`|
| **Categories** | `1 = yes; 3 = Possible stroke or transient ischemic attack; 5 = no` |`continuous`|`continuous`|
| **Missings** | `NA; -8 = Refuse to answer` | `NA; -8 = Refuse to answer` |  |
| **Description** |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C038','w04C039y'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
load(paste0(datafolder,"w4/ybirth.RData"))
KLOSA_w4 <- left_join(KLOSA_w4,ybirth,by="id")

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C038
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = c(-8))[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C038))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C039y
kable(Continuous_summary(var = vbl, missing_values = c(-8))[3], caption = names(KLOSA_w4)[3])
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(factor(w04C039y))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(KLOSA_w4)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_w4 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `change 5 into 0`
* `change 3 into 1`
* `keep up 1 into 1`
* `NA into 999`
* `-8 into 997`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = w04C039y-ybirth`
* `if stroke == 0, stroke_age = 996`
* `NA into 999`
* `-8 into 997`
* `stroke == missing into 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$stroke <- car::recode(KLOSA_w4$w04C038,"3=1; 5=0; -8=997; NA=999")

# Continuous variable harmonization
KLOSA_ds_w4$stroke_age <- rep(999,length(KLOSA_w4$id))
KLOSA_ds_w4$stroke_age[which(KLOSA_ds_w4$stroke == 0)] <- 996
KLOSA_ds_w4$stroke_age[which(KLOSA_ds_w4$stroke == 1)] <- KLOSA_w4$w04C039y[which(KLOSA_ds_w4$stroke == 1)]-KLOSA_w4$ybirth[which(KLOSA_ds_w4$stroke == 1)]
KLOSA_ds_w4$stroke_age[which(KLOSA_ds_w4$stroke == 1 & KLOSA_w4$w04C039y==-8)] <- 997
KLOSA_ds_w4$stroke_age <- car::recode(KLOSA_ds_w4$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- KLOSA_ds_w4$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(KLOSA_ds_w4 %>% filter(!vbl %in% miss_values_vector), aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(KLOSA_ds_w4$stroke)
X <- table(KLOSA_w4$w04C038, useNA = "ifany")
BeforeH <- c(X[4],sum(X[2:3]),X[c(1,5)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1,3->1","-8->997","NA->999")
kable(C)


```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

klosalist <- lmlist # KLOSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `stroke` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `stroke_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("KLOSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- klosalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- klosalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```



# Quality estimation

* The diagnostic stroke data for individuals which tell in a wave that they have stroke is missing in all the next waves, so the age of diagnostic too. This fact is preserved in the harmonized variable.






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





