---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_hypertension`
* Variable label: `History of Hypertension`
* Variable description: `history of hypertension or high blood pressure`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT High blood pressure or hypertension 
1        | High blood pressure or hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_hypertension_age`
* Variable label: `Age first diagnosed hypertension`
* Variable description: `The age first told had hypertension diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Hypertension"
ds_label_age <- "Age first diagnosed hypertension"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Spain


### Wave 1


#### Study-specific variable description

| **Name** | `w1hypertension` |
|-|-|
| **Label** | `Hypertension`|
| **Table name**  | `ENRICA_spss_wave1`|
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Missings** |`NA`|
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1',variables=list('w1hypertension'), missings = T)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
ENRICA_w1$w1hypertension <- as.numeric(ENRICA_w1$w1hypertension)

```

```{r local w1, echo=F}

vbl <- ENRICA_w1$w1hypertension
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w1, aes(x=factor(w1hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$h_hypertension <- car::recode(ENRICA_w1$w1hypertension,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ENRICA_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ENRICA_ds_w1$h_hypertension)
BeforeH <- table(ENRICA_w1$w1hypertension, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2hypertension` |`ybirth`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Hypertension`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `ENRICA_spss_wave2`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2',variables=list('w2hypertension'), missings = T)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
ENRICA_w2$w2hypertension <- as.numeric(ENRICA_w2$w2hypertension)
load(paste0(datafolder,"w2/ybirth.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,ybirth, by="id")
load(paste0(datafolder,"w1/yintw.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,yintw, by="id")
names(ENRICA_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,yintw, by="id")
names(ENRICA_w2)[5] <- "yintw_w2"

```

```{r local w2, echo=F}

vbl <- ENRICA_w2$w2hypertension
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(w2hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ENRICA_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1955)

vbl <- ENRICA_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `w1hypertension == 0 and w2hypertension == 0 into 0`
* `w1hypertension == 1 or w2hypertension == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = (year of interview w2-year of interview w1)/2+(year of interview w1 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of its study-specific variable
ENRICA_w2 <- left_join(ENRICA_w2, ENRICA_ds_w1, by = "id")

ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$h_hypertension <- rep(999,length(ENRICA_w2$id))
ENRICA_ds_w2$h_hypertension[which(ENRICA_w2$w2hypertension == 0 & (ENRICA_w2$h_hypertension != 1 | is.na(ENRICA_w2$h_hypertension)))] <- 0
ENRICA_ds_w2$h_hypertension[which(ENRICA_w2$w2hypertension == 1 | ((!is.na(ENRICA_w2$w2hypertension)) & ENRICA_w2$h_hypertension == 1))] <- 1

# Continuous variable harmonization
ENRICA_ds_w2$h_hypertension_age <- rep(999,length(ENRICA_w2$id))
ENRICA_ds_w2$h_hypertension_age[which(ENRICA_ds_w2$h_hypertension == 0)] <- 996
ENRICA_ds_w2$h_hypertension_age[which(ENRICA_ds_w2$h_hypertension == 1 & ENRICA_w2$h_hypertension==0)] <- (ENRICA_w2$yintw_w2[which(ENRICA_ds_w2$h_hypertension == 1 & ENRICA_w2$h_hypertension==0)]+ENRICA_w2$yintw_w1[which(ENRICA_ds_w2$h_hypertension == 1 & ENRICA_w2$h_hypertension==0)])/2-ENRICA_w2$ybirth[which(ENRICA_ds_w2$h_hypertension == 1 & ENRICA_w2$h_hypertension==0)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ENRICA_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ENRICA_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ENRICA_ds_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(ENRICA_w2$w2hypertension)) & ENRICA_w2$w2hypertension == 0) & (ENRICA_w2$h_hypertension != 1)),
  sum(((!is.na(ENRICA_w2$w2hypertension)) & ENRICA_w2$w2hypertension == 1) | ((!is.na(ENRICA_w2$h_hypertension)) & (!is.na(ENRICA_w2$w2hypertension)) & ENRICA_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(ENRICA_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 3

#### Study-specific variable description


| **Name** | `w3hypertension` |`ybirth`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Hypertension`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `ENRICA_spss_wave3`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3',variables=list('w3hypertension'), missings = T)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
ENRICA_w3$w3hypertension <- as.numeric(ENRICA_w3$w3hypertension)
load(paste0(datafolder,"w3/ybirth.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,ybirth, by="id")
load(paste0(datafolder,"w3/yintw.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,yintw, by="id")
names(ENRICA_w3)[4] <- "yintw_w3"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,yintw, by="id")
names(ENRICA_w3)[5] <- "yintw_w2"

```

```{r local w3, echo=F}

vbl <- ENRICA_w3$w3hypertension
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(w3hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ENRICA_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1915,1950)

vbl <- ENRICA_w3$yintw_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(yintw_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w3$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `w1hypertension == 0 and w2hypertension == 0 and w3hypertension == 0 into 0`
* `w1hypertension == 1 or w2hypertension == 1 or w3hypertension == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w3 and 0 in w2, h_hypertension_age = (year of interview w3-year of interview w2)/2+(year of interview w2 - ybirth)`
* `if h_hypertension == 1 in w3 and w2, h_hypertension_age as in w2`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 2 instead of the study-specific variables from all the previous waves
ENRICA_w3 <- left_join(ENRICA_w3, ENRICA_ds_w2, by = "id")

ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w3$h_hypertension <- rep(999,length(ENRICA_w3$id))
ENRICA_ds_w3$h_hypertension[which(ENRICA_w3$w3hypertension == 0 & (ENRICA_w3$h_hypertension != 1 | is.na(ENRICA_w3$h_hypertension)))] <- 0
ENRICA_ds_w3$h_hypertension[which(ENRICA_w3$w3hypertension == 1 | ((!is.na(ENRICA_w3$w3hypertension)) & ENRICA_w3$h_hypertension == 1))] <- 1

# Continuous variable harmonization
ENRICA_ds_w3$h_hypertension_age <- rep(999,length(ENRICA_w3$id))
ENRICA_ds_w3$h_hypertension_age[which(ENRICA_ds_w3$h_hypertension == 0)] <- 996
ENRICA_ds_w3$h_hypertension_age[which(ENRICA_ds_w3$h_hypertension == 1 & ENRICA_w3$h_hypertension==0)] <- (ENRICA_w3$yintw_w3[which(ENRICA_ds_w3$h_hypertension == 1 & ENRICA_w3$h_hypertension==0)]+ENRICA_w3$yintw_w2[which(ENRICA_ds_w3$h_hypertension == 1 & ENRICA_w3$h_hypertension==0)])/2-ENRICA_w3$ybirth[which(ENRICA_ds_w3$h_hypertension == 1 & ENRICA_w3$h_hypertension==0)]

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ENRICA_ds_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ENRICA_ds_w3$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,95)

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ENRICA_ds_w3$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(ENRICA_w3$w3hypertension)) & ENRICA_w3$w3hypertension == 0) & ((!is.na(ENRICA_w3$h_hypertension)) & ENRICA_w3$h_hypertension == 0)),
  sum(((!is.na(ENRICA_w3$w3hypertension)) & ENRICA_w3$w3hypertension == 1) | ((!is.na(ENRICA_w3$h_hypertension)) & (!is.na(ENRICA_w3$w3hypertension)) & ENRICA_w3$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(ENRICA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ENRICA_ds_w1$h_hypertension <- labelled(ENRICA_ds_w1$h_hypertension, labels = cat_label)
label(ENRICA_ds_w1$h_hypertension) <- ds_label
ENRICA_ds_w2$h_hypertension <- labelled(ENRICA_ds_w2$h_hypertension, labels = cat_label)
label(ENRICA_ds_w2$h_hypertension) <- ds_label
ENRICA_ds_w2$h_hypertension_age <- labelled(ENRICA_ds_w2$h_hypertension_age, labels = cont_label)
label(ENRICA_ds_w2$h_hypertension_age) <- ds_label_age
ENRICA_ds_w3$h_hypertension <- labelled(ENRICA_ds_w3$h_hypertension, labels = cat_label)
label(ENRICA_ds_w3$h_hypertension) <- ds_label
ENRICA_ds_w3$h_hypertension_age <- labelled(ENRICA_ds_w3$h_hypertension_age, labels = cont_label)
label(ENRICA_ds_w3$h_hypertension_age) <- ds_label_age

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$h_hypertension <- car::recode(ENRICA_m_ds_w1$h_hypertension, "miss_values_vector=NA")
ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$h_hypertension <- car::recode(ENRICA_m_ds_w2$h_hypertension, "miss_values_vector=NA")
ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$h_hypertension <- car::recode(ENRICA_m_ds_w3$h_hypertension, "miss_values_vector=NA")


tt <-    frq(ENRICA_ds_w1$h_hypertension)[[1]][,c(1:2,4)]
tt[4] <- frq(ENRICA_ds_w2$h_hypertension)[[1]][,c(4)]
tt[5] <- frq(ENRICA_ds_w3$h_hypertension)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ENRICA_ds_w1$h_hypertension), length(ENRICA_ds_w2$h_hypertension), length(ENRICA_ds_w3$h_hypertension)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3")
kable(tt)

dbb <- merge(ENRICA_m_ds_w1[,c("id","h_hypertension")], ENRICA_m_ds_w2[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ENRICA_m_ds_w3[,c("id","h_hypertension")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

The information is not based on hypertension diagnosis, the label description is: Participants were considered to have hypertension if SBP was >=140, DBP was >=90 or if they were receiving antihypertensive medication.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ENRICA <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2, w3 = ENRICA_ds_w3)

for(index in seq_along(l.ENRICA)){
  h_hypertension <- l.ENRICA[[index]]
  save(h_hypertension, file = paste0(datafolder,names(l.ENRICA)[index],"/h_hypertension.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





