---
title: "Joint disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```

<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/joint_disordersDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/joint_disordersDS.R')
```



# Data process



## Spain


### Wave 1


#### Study-specific variable description

| **Name** | `w1arthritis` |
|-|-|
| **Label** | `Medical diagnosis of arthritis?`|
| **Table name**  | `ENRICA_spss_wave1`|
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Missings** |`NA`|
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1',variables=list('w1arthritis'), missings = T)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
ENRICA_w1$w1arthritis <- as.numeric(ENRICA_w1$w1arthritis)

```

```{r local w1, echo=F}

vbl <- ENRICA_w1$w1arthritis
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w1, aes(x=factor(w1arthritis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$h_joint_disorders <- car::recode(ENRICA_w1$w1arthritis,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ENRICA_ds_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ENRICA_ds_w1$h_joint_disorders)
BeforeH <- table(ENRICA_w1$w1arthritis, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2arthritis` |`ybirth`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** |  |`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `ENRICA_spss_wave2`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2',variables=list('w2arthritis'), missings = T)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
ENRICA_w2$w2arthritis <- as.numeric(ENRICA_w2$w2arthritis)
load(paste0(datafolder,"w2/ybirth.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,ybirth, by="id")
load(paste0(datafolder,"w1/yintw.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,yintw, by="id")
names(ENRICA_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
ENRICA_w2 <- left_join(ENRICA_w2,yintw, by="id")
names(ENRICA_w2)[5] <- "yintw_w2"

```

```{r local w2, echo=F}
# Since the variable w2arthritis comes without label, we assign it:

vbl <- ENRICA_w2$w2arthritis
label(vbl) <- "Medical diagnosis of osteoarthritis or arthritis"
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(w2arthritis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ENRICA_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1955)

vbl <- ENRICA_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `w1arthritis == 0 and w2arthritis == 0 into 0`
* `w1arthritis == 1 or w2arthritis == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w2 and 0 in w1, h_joint_disorders_age = (year of interview w2-year of interview w1)/2+(year of interview w1 - ybirth)`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of its study-specific variable
ENRICA_w2 <- left_join(ENRICA_w2, ENRICA_ds_w1, by = "id")

ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$h_joint_disorders <- rep(999,length(ENRICA_w2$id))
ENRICA_ds_w2$h_joint_disorders[which(ENRICA_w2$w2arthritis == 0 & (ENRICA_w2$h_joint_disorders != 1 | is.na(ENRICA_w2$h_joint_disorders)))] <- 0
ENRICA_ds_w2$h_joint_disorders[which(ENRICA_w2$w2arthritis == 1 | ((!is.na(ENRICA_w2$w2arthritis)) & ENRICA_w2$h_joint_disorders == 1))] <- 1

# Continuous variable harmonization
ENRICA_ds_w2$h_joint_disorders_age <- rep(999,length(ENRICA_w2$id))
ENRICA_ds_w2$h_joint_disorders_age[which(ENRICA_ds_w2$h_joint_disorders == 0)] <- 996
ENRICA_ds_w2$h_joint_disorders_age[which(ENRICA_ds_w2$h_joint_disorders == 1 & ENRICA_w2$h_joint_disorders==0)] <- (ENRICA_w2$yintw_w2[which(ENRICA_ds_w2$h_joint_disorders == 1 & ENRICA_w2$h_joint_disorders==0)]+ENRICA_w2$yintw_w1[which(ENRICA_ds_w2$h_joint_disorders == 1 & ENRICA_w2$h_joint_disorders==0)])/2-ENRICA_w2$ybirth[which(ENRICA_ds_w2$h_joint_disorders == 1 & ENRICA_w2$h_joint_disorders==0)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ENRICA_ds_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ENRICA_ds_w2$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ENRICA_ds_w2$h_joint_disorders, useNA = "ifany")
X <- c(
  sum(((!is.na(ENRICA_w2$w2arthritis)) & ENRICA_w2$w2arthritis == 0) & (ENRICA_w2$h_joint_disorders != 1)),
  sum(((!is.na(ENRICA_w2$w2arthritis)) & ENRICA_w2$w2arthritis == 1) | ((!is.na(ENRICA_w2$h_joint_disorders)) & (!is.na(ENRICA_w2$w2arthritis)) & ENRICA_w2$h_joint_disorders == 1))
)
BeforeH <- c(X[1:2],length(ENRICA_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 3

#### Study-specific variable description


| **Name** | `w3arthritis` |`ybirth`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** |  |`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `ENRICA_spss_wave3`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3',variables=list('w3arthritis'), missings = T)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
ENRICA_w3$w3arthritis <- as.numeric(ENRICA_w3$w3arthritis)
load(paste0(datafolder,"w3/ybirth.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,ybirth, by="id")
load(paste0(datafolder,"w3/yintw.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,yintw, by="id")
names(ENRICA_w3)[4] <- "yintw_w3"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
ENRICA_w3 <- left_join(ENRICA_w3,yintw, by="id")
names(ENRICA_w3)[5] <- "yintw_w2"

```

```{r local w3, echo=F}
# Since the variable w2arthritis comes without label, we assign it:

vbl <- ENRICA_w3$w3arthritis
label(vbl) <- "Medical diagnosis of osteoarthritis or arthritis"
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(w3arthritis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ENRICA_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1915,1950)

vbl <- ENRICA_w3$yintw_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(yintw_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ENRICA_w3$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `w1arthritis == 0 and w2arthritis == 0 and w3arthritis == 0 into 0`
* `w1arthritis == 1 or w2arthritis == 1 or w3arthritis == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w3 and 0 in w2, h_joint_disorders_age = (year of interview w3-year of interview w2)/2+(year of interview w2 - ybirth)`
* `if h_joint_disorders == 1 in w3 and w2, h_joint_disorders_age as in w2`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 2 instead of the study-specific variables from all the previous waves
ENRICA_w3 <- left_join(ENRICA_w3, ENRICA_ds_w2, by = "id")

ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w3$h_joint_disorders <- rep(999,length(ENRICA_w3$id))
ENRICA_ds_w3$h_joint_disorders[which(ENRICA_w3$w3arthritis == 0 & (ENRICA_w3$h_joint_disorders != 1 | is.na(ENRICA_w3$h_joint_disorders)))] <- 0
ENRICA_ds_w3$h_joint_disorders[which(ENRICA_w3$w3arthritis == 1 | ((!is.na(ENRICA_w3$w3arthritis)) & ENRICA_w3$h_joint_disorders == 1))] <- 1

# Continuous variable harmonization
ENRICA_ds_w3$h_joint_disorders_age <- rep(999,length(ENRICA_w3$id))
ENRICA_ds_w3$h_joint_disorders_age[which(ENRICA_ds_w3$h_joint_disorders == 0)] <- 996
ENRICA_ds_w3$h_joint_disorders_age[which(ENRICA_ds_w3$h_joint_disorders == 1 & ENRICA_w3$h_joint_disorders==0)] <- (ENRICA_w3$yintw_w3[which(ENRICA_ds_w3$h_joint_disorders == 1 & ENRICA_w3$h_joint_disorders==0)]+ENRICA_w3$yintw_w2[which(ENRICA_ds_w3$h_joint_disorders == 1 & ENRICA_w3$h_joint_disorders==0)])/2-ENRICA_w3$ybirth[which(ENRICA_ds_w3$h_joint_disorders == 1 & ENRICA_w3$h_joint_disorders==0)]

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ENRICA_ds_w3$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ENRICA_ds_w3$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,95)

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ENRICA_ds_w3$h_joint_disorders, useNA = "ifany")
X <- c(
  sum(((!is.na(ENRICA_w3$w3arthritis)) & ENRICA_w3$w3arthritis == 0) & ((!is.na(ENRICA_w3$h_joint_disorders)) & ENRICA_w3$h_joint_disorders == 0)),
  sum(((!is.na(ENRICA_w3$w3arthritis)) & ENRICA_w3$w3arthritis == 1) | ((!is.na(ENRICA_w3$h_joint_disorders)) & (!is.na(ENRICA_w3$w3arthritis)) & ENRICA_w3$h_joint_disorders == 1))
)
BeforeH <- c(X[1:2],length(ENRICA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

enrica.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(enrica.cw, function(wname) if(exists(paste0("ENRICA_ds_",wname[1]))){wname = list(get(paste0("ENRICA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

enricalist <- lmlist # ENRICA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_joint_disorders` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(enrica.cw, function(wname) if(hd_vbl %in% names(get0(paste0("ENRICA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- enricalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- enricalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))

}



```






## Summary of descriptive statistics of the harmonised variable `h_joint_disorders_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(enrica.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("ENRICA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- enricalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- enricalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```




# Quality estimation

No comments







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





