---
title: "Triglycerides"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/triglyceridesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/triglyceridesDS.R')
```


# Data process


## Greece

### Wave 1 

#### Study-specific variable description

| **Name** | `tgl` |
|-|-|
| **Label** | `Triglycerides (mg/dl)` |
| **Table name** | `ATTICA_Baseline` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign w1, echo=F }

opal.assign.table.tibble(o, 'ATTICA_w1','ATTICA.ATTICA_Baseline', variables=list('tgl'), missings = TRUE)
ATTICA_w1 <- opal.execute(o,'ATTICA_w1')

```

```{r local w1, echo=F}

vbl <- ATTICA_w1$tgl
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "tgl") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w1, aes(tgl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `triglycerides` from the study-specific variable it has to be recoded as follows:

* `do not change the scale`
* `NA into 999`

**R script:**

```{r harmo w1}

ATTICA_ds_w1 <- tibble(id=ATTICA_w1$id)
ATTICA_ds_w1$triglycerides <- car::recode(ATTICA_w1$tgl, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- ATTICA_ds_w1$triglycerides
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ATTICA_ds_w1,!vbl %in% miss_values_vector), aes(triglycerides)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=F}

triglycerides <- ATTICA_ds_w1 
save(triglycerides, file = paste0(datafolder,"w1/triglycerides.RData"))
rm(triglycerides)

```




### Wave 2

Not found


### Wave 3

Not found



# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
