---
title: "Day of Death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ddeathDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ddeathDS.R')
```



# Data process

## Cuba

### Wave 1

There is no variable. 


### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |


```{r assign_cuba2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Cuba-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Cuba-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_cuba2, echo=FALSE}
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cuba2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_cuba_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_cuba_w2$ddeath <- labelled(t1066_ds_cuba_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cuba2, echo=FALSE}
vari <- t1066_ds_cuba_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba2, echo=FALSE}
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_cuba_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


```{r importOPAL_cuba_w2, echo=FALSE}
label(t1066_ds_cuba_w2$ddeath) <- ds_label
ddeath <- t1066_ds_cuba_w2
save(ddeath, file = "../RData/cuba_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```



## India

### Wave 1 

There is no variable.

<!--
### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `1066-India-Followup` |
| **Description** |  |


```{r assign_india2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-India-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_india_w2_death','10-66.1066-India-Followup',
                         variables=list('death_date'), missings = TRUE)
t1066_india_w2_death <- opal.execute(o,'t1066_india_w2_death')
t1066_india_w2_death$ddeath <- format(t1066_india_w2_death$death_date, '%d')
t1066_india_w2_death <- t1066_india_w2_death[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_india_w2_death <- same_indiv(old = t1066_india_w2_death, new = t1066_id_w1)
```

```{r local_india2, echo=FALSE}
vari <- t1066_india_w2_death$ddeath
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_india_w2_death, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_india2}
t1066_ds_india_w2 <- tibble(id=t1066_india_w2_death$id)
t1066_ds_india_w2$ddeath <- car::recode(t1066_india_w2_death$ddeath, "NA=999")
t1066_ds_india_w2$ddeath <- labelled(t1066_ds_india_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india2, echo=FALSE}
vari <- t1066_ds_india_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_india_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india2, echo=FALSE}
BeforeH <- table(t1066_india_w2_death$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_india_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_india_w2, echo=FALSE}
label(t1066_ds_india_w2$ddeath) <- ds_label
ddeath <- t1066_ds_india_w2
save(ddeath, file = "../RData/india_w2/ddeath.RData")
```
-->


## Urban China

### Wave 1

There is no variable.





## Wave 2 

#### Study-specific variable description

 
| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_UCh2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UCh2, echo=TRUE} 
t1066_ds_UCh_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_UCh_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_UCh_w2$ddeath <- labelled(t1066_ds_UCh_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UCh2, echo=FALSE} 
vari <- t1066_ds_UCh_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_UCh_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_UCh2, echo=FALSE}
label(t1066_ds_UCh_w2$ddeath) <- ds_label
ddeath <- t1066_ds_UCh_w2
save(ddeath, file = "../RData/UCh_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```



## Rural China

### Wave 1

There is no variable.





### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_RCh2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RCh2, echo=TRUE} 
t1066_ds_RCh_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_RCh_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_RCh_w2$ddeath <- labelled(t1066_ds_RCh_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RCh2, echo=FALSE} 
vari <- t1066_ds_RCh_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_RCh_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_RCh2, echo=FALSE}
label(t1066_ds_RCh_w2$ddeath) <- ds_label
ddeath <- t1066_ds_RCh_w2
save(ddeath, file = "../RData/RCh_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```
 
 


## Dominican Republic

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_DR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-DominicanRepublic-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_DR2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_DR2, echo=TRUE} 
t1066_ds_DR_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_DR_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_DR_w2$ddeath <- labelled(t1066_ds_DR_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_DR2, echo=FALSE} 
vari <- t1066_ds_DR_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_DR_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_DR_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_DR2, echo=FALSE}
label(t1066_ds_DR_w2$ddeath) <- ds_label
ddeath <- t1066_ds_DR_w2
save(ddeath, file = "../RData/DR_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```


## Venezuela

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_V2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Venezuela-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Venezuela-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_V2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_V2, echo=TRUE} 
t1066_ds_Ven_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_Ven_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_Ven_w2$ddeath <- labelled(t1066_ds_Ven_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_V2, echo=FALSE} 
vari <- t1066_ds_Ven_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_Ven_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_V2, echo=FALSE}
label(t1066_ds_Ven_w2$ddeath) <- ds_label
ddeath <- t1066_ds_Ven_w2
save(ddeath, file = "../RData/Ven_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```
 


## Urban Peru

### Wave 1

There is no variable.



### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_UP2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UP2, echo=TRUE} 
t1066_ds_UP_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_UP_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_UP_w2$ddeath <- labelled(t1066_ds_UP_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UP2, echo=FALSE} 
vari <- t1066_ds_UP_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UP_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_UP_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_UP_w2, echo=FALSE}
label(t1066_ds_UP_w2$ddeath) <- ds_label
ddeath <- t1066_ds_UP_w2
save(ddeath, file = "../RData/UP_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```



## Rural Peru

### Wave 1

There is no variable.







### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_RP2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RP2, echo=TRUE} 
t1066_ds_RP_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_RP_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_RP_w2$ddeath <- labelled(t1066_ds_RP_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RP2, echo=FALSE} 
vari <- t1066_ds_RP_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RP_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_RP_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPALRP_w2, echo=FALSE}
label(t1066_ds_RP_w2$ddeath) <- ds_label
ddeath <- t1066_ds_RP_w2
save(ddeath, file = "../RData/RP_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```






## Urban Mexico

### Wave 1

There is no variable.







### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_UM2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UM2, echo=TRUE} 
t1066_ds_UM_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_UM_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_UM_w2$ddeath <- labelled(t1066_ds_UM_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UM2, echo=FALSE} 
vari <- t1066_ds_UM_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UM_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_UM_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_UM_w2, echo=FALSE}
label(t1066_ds_UM_w2$ddeath) <- ds_label
ddeath <- t1066_ds_UM_w2
save(ddeath, file = "../RData/UM_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```





## Rural Mexico

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_RM2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RM2, echo=TRUE} 
t1066_ds_RM_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_RM_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_RM_w2$ddeath <- labelled(t1066_ds_RM_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RM2, echo=FALSE} 
vari <- t1066_ds_RM_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RM_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_RM_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_RM_w2, echo=FALSE}
label(t1066_ds_RM_w2$ddeath) <- ds_label
ddeath <- t1066_ds_RM_w2
save(ddeath, file = "../RData/RM_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```
 





## Puerto Rico

### Wave 1

There is no variable.





### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_PR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-PuertoRico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-PuertoRico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ddeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ddeath2 <- opal.execute(o,'t1066_ddeath2')
t1066_ddeath2$ddeath <- format(t1066_ddeath2$death_date, '%d')
t1066_ddeath2 <- t1066_ddeath2[c("id", "ddeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ddeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ddeath <- same_indiv(old = t1066_ddeath2, new = t1066_id_w1)
```

```{r local_PR2, echo=FALSE} 
vari <- t1066_ddeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ddeath, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_PR2, echo=TRUE} 
t1066_ds_PR_w2 <- tibble(id=t1066_ddeath$id)
t1066_ds_PR_w2$ddeath <- car::recode(t1066_ddeath$ddeath, "NA=999")
t1066_ds_PR_w2$ddeath <- labelled(t1066_ds_PR_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_PR2, echo=FALSE} 
vari <- t1066_ds_PR_w2$ddeath
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_PR_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue",data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=FALSE} 
BeforeH <- table(t1066_ddeath$ddeath, useNA = "ifany")
AfterH <- table(t1066_ds_PR_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_PR_w2, echo=FALSE}
label(t1066_ds_PR_w2$ddeath) <- ds_label
ddeath <- t1066_ds_PR_w2
save(ddeath, file = "../RData/PR_w2/ddeath.RData")
rm(ddeath, t1066_id_w1, t1066_id_w2, t1066_ddeath2, t1066_ddeath)
```












## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
}




```











# Quality estimation

<!--Variable only available for the second wave of India-->

No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
