---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ydeath`
* Variable label: `Year of death`
* Variable description: `year of death`
* Domain: `Death`
* Value type: `continous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Year of death"
```



## Cuba

### Wave 1

There is no variable.





### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |


```{r assign_cuba2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Cuba-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Cuba-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_cuba2, echo=FALSE}
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cuba2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_cuba_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_cuba_w2$ydeath <- labelled(t1066_ds_cuba_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cuba2, echo=FALSE}
vari <- t1066_ds_cuba_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba2, echo=FALSE}
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_cuba_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


```{r importOPAL_cuba_w2, echo=FALSE}
label(t1066_ds_cuba_w2$ydeath) <- ds_label
ydeath <- t1066_ds_cuba_w2
save(ydeath, file = "../RData/cuba_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```






## India

### Wave 1 

There is no variable.


### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `1066-India-Followup` |
| **Description** |  |


```{r assign_india2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-India-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_india_w2_ydeath','10-66.1066-India-Followup',
                         variables=list('death_date'), missings = TRUE)
t1066_india_w2_ydeath <- opal.execute(o,'t1066_india_w2_ydeath')
t1066_india_w2_ydeath$ydeath <- format(t1066_india_w2_ydeath$death_date, '%Y')

t1066_india_w2_ydeath <- t1066_india_w2_ydeath[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_india_w2_death <- same_indiv(old = t1066_india_w2_ydeath, new = t1066_id_w1)
```

```{r local_india2, echo=FALSE}
vari <- t1066_india_w2_death$ydeath
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_india_w2_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_india2}
t1066_ds_india_w2 <- tibble(id=t1066_india_w2_ydeath$id)
t1066_ds_india_w2$ydeath <- car::recode(t1066_india_w2_ydeath$ydeath, "NA=999")
t1066_ds_india_w2$ydeath <- labelled(t1066_ds_india_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india2, echo=FALSE}
vari <- t1066_ds_india_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india2, echo=FALSE}
BeforeH <- table(t1066_india_w2_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_india_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_india2, echo=FALSE}
#opal.assign.data(o, 't1066_ds_india_w2', t1066_ds_india_w2)
#opal.symbol_import(o,'t1066_ds_india_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w2 <- t1066_ds_india_w2
t1066_m_ds_india_w2$ydeath <- car::recode(t1066_m_ds_india_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w2', t1066_m_ds_india_w2)
#opal.symbol_import(o,'t1066_m_ds_india_w2', project='_Athlos_Harm_Dataset')
label(t1066_ds_india_w2$ydeath) <- ds_label
ydeath <- t1066_ds_india_w2
save(ydeath, file = "../RData/india_w2/ydeath.RData")
```







## Urban China

### Wave 1

There is no variable.





## Wave 2 

#### Study-specific variable description

 
| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_UCh2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UCh2, echo=TRUE} 
t1066_ds_UCh_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_UCh_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_UCh_w2$ydeath <- labelled(t1066_ds_UCh_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UCh2, echo=FALSE} 
vari <- t1066_ds_UCh_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_UCh_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_UCh2, echo=FALSE}
label(t1066_ds_UCh_w2$ydeath) <- ds_label
ydeath <- t1066_ds_UCh_w2
save(ydeath, file = "../RData/UCh_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```





## Rural China

### Wave 1

There is no variable.





### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_RCh2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RCh2, echo=TRUE} 
t1066_ds_RCh_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_RCh_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_RCh_w2$ydeath <- labelled(t1066_ds_RCh_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RCh2, echo=FALSE} 
vari <- t1066_ds_RCh_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_RCh_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_RCh2, echo=FALSE}
label(t1066_ds_RCh_w2$ydeath) <- ds_label
ydeath <- t1066_ds_RCh_w2
save(ydeath, file = "../RData/RCh_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```
 



## Dominican Republic

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_DR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-DominicanRepublic-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_DR2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_DR2, echo=TRUE} 
t1066_ds_DR_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_DR_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_DR_w2$ydeath <- labelled(t1066_ds_DR_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_DR2, echo=FALSE} 
vari <- t1066_ds_DR_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_DR_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_DR2, echo=FALSE}
label(t1066_ds_DR_w2$ydeath) <- ds_label
ydeath <- t1066_ds_DR_w2
save(ydeath, file = "../RData/DR_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```



## Venezuela

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_V2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Venezuela-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Venezuela-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_V2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_V2, echo=TRUE} 
t1066_ds_Ven_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_Ven_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_Ven_w2$ydeath <- labelled(t1066_ds_Ven_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_V2, echo=FALSE} 
vari <- t1066_ds_Ven_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_Ven_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_V2, echo=FALSE}
label(t1066_ds_Ven_w2$ydeath) <- ds_label
ydeath <- t1066_ds_Ven_w2
save(ydeath, file = "../RData/Ven_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```
 




## Urban Peru

### Wave 1

There is no variable.



### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_UP2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UP2, echo=TRUE} 
t1066_ds_UP_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_UP_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_UP_w2$ydeath <- labelled(t1066_ds_UP_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UP2, echo=FALSE} 
vari <- t1066_ds_UP_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_UP_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_UP_w2, echo=FALSE}
label(t1066_ds_UP_w2$ydeath) <- ds_label
ydeath <- t1066_ds_UP_w2
save(ydeath, file = "../RData/UP_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```



## Rural Peru

### Wave 1

There is no variable.







### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_RP2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RP2, echo=TRUE} 
t1066_ds_RP_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_RP_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_RP_w2$ydeath <- labelled(t1066_ds_RP_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RP2, echo=FALSE} 
vari <- t1066_ds_RP_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_RP_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPALRP_w2, echo=FALSE}
label(t1066_ds_RP_w2$ydeath) <- ds_label
ydeath <- t1066_ds_RP_w2
save(ydeath, file = "../RData/RP_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```










## Urban Mexico

### Wave 1

There is no variable.







### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_UM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_UM2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_UM2, echo=TRUE} 
t1066_ds_UM_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_UM_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_UM_w2$ydeath <- labelled(t1066_ds_UM_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UM2, echo=FALSE} 
vari <- t1066_ds_UM_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_UM_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_UM_w2, echo=FALSE}
label(t1066_ds_UM_w2$ydeath) <- ds_label
ydeath <- t1066_ds_UM_w2
save(ydeath, file = "../RData/UM_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```






## Rural Mexico

### Wave 1

There is no variable.






### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_RM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_RM2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_RM2, echo=TRUE} 
t1066_ds_RM_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_RM_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_RM_w2$ydeath <- labelled(t1066_ds_RM_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RM2, echo=FALSE} 
vari <- t1066_ds_RM_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_RM_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

 
```{r importOPAL_RM_w2, echo=FALSE}
label(t1066_ds_RM_w2$ydeath) <- ds_label
ydeath <- t1066_ds_RM_w2
save(ydeath, file = "../RData/RM_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```
 





## Puerto Rico

### Wave 1

There is no variable.





### Wave 2

#### Study-specific variable description

| **Name** | `death_date`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Description** |  |

```{r assign_PR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-PuertoRico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-PuertoRico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_ydeath2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date'), missings = TRUE)
t1066_ydeath2 <- opal.execute(o,'t1066_ydeath2')
t1066_ydeath2$ydeath <- format(t1066_ydeath2$death_date, '%Y')
t1066_ydeath2 <- t1066_ydeath2[c("id", "ydeath")]

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]))
  new_22
}

t1066_ydeath <- same_indiv(old = t1066_ydeath2, new = t1066_id_w1)
```

```{r local_PR2, echo=FALSE} 
vari <- t1066_ydeath[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_ydeath, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_PR2, echo=TRUE} 
t1066_ds_PR_w2 <- tibble(id=t1066_ydeath$id)
t1066_ds_PR_w2$ydeath <- car::recode(t1066_ydeath$ydeath, "NA=999")
t1066_ds_PR_w2$ydeath <- labelled(t1066_ds_PR_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_PR2, echo=FALSE} 
vari <- t1066_ds_PR_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=FALSE} 
BeforeH <- table(t1066_ydeath$ydeath, useNA = "ifany")
AfterH <- table(t1066_ds_PR_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL_PR_w2, echo=FALSE}
label(t1066_ds_PR_w2$ydeath) <- ds_label
ydeath <- t1066_ds_PR_w2
save(ydeath, file = "../RData/PR_w2/ydeath.RData")
rm(ydeath, t1066_id_w1, t1066_id_w2, t1066_ydeath2, t1066_ydeath)
```

#### Quality estimation


This variable is available only for the second wave of India.

[Comments on the quality of the new harmonised variable.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

