---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```




# Data process

## Cuba

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_cuba1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Cuba-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_cuba_w1$living_status <- 0
t1066_ds_cuba_w1$living_status <- labelled(t1066_ds_cuba_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba1, echo=FALSE}
vari <- t1066_ds_cuba_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |


```{r assign_cuba2, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Cuba-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Cuba-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_cuba2, echo=FALSE}
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')` 

**R script:**

```{r harmo_cuba2, echo=TRUE}
t1066_ds_cuba_w2 <- tibble(id=t1066_death$id)
t1066_ds_cuba_w2$living_status <- 2
t1066_ds_cuba_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_cuba_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_cuba_w2$living_status <- labelled(t1066_ds_cuba_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cuba2, echo=FALSE}
vari <- t1066_ds_cuba_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
There is a individual that we have date of death and it is posterior to follow up interview:
```{r crosstabulation_cuba2, echo=FALSE}
dd <- t1066_death[which(t1066_death$dead==1),]
ddd <- t1066_death[!is.na(t1066_death$ydeath),]
kable(ddd[!(ddd$id %in% dd$id),])
```









## India

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_india1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_india_w1_id','10-66.1066-India-Baseline',
                         variables=list('DATE'), missings = TRUE)
t1066_india_w1_id <- opal.execute(o,'t1066_india_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_india1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_id$id)
t1066_ds_india_w1$living_status <- 0
t1066_ds_india_w1$living_status <- labelled(t1066_ds_india_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india1, echo=FALSE}
vari <- t1066_ds_india_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india1, echo=FALSE}
```




<!--
### Wave 2

#### Study-specific variable description


| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_india2, echo=FALSE, eval = FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-India-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-India-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_india2, echo=FALSE, eval = FALSE}
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_india2, eval = FALSE}
t1066_ds_india_w2 <- tibble(id=t1066_death$id)
t1066_ds_india_w2$living_status <- 2
t1066_ds_india_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_india_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_india_w2$living_status <- labelled(t1066_ds_india_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india2, echo=FALSE, eval = FALSE}
vari <- t1066_ds_india_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
There is a individual that we have date of death and it is the same than to follow up interview:
```{r crosstabulation_india2, echo=FALSE, eval = FALSE}
dd <- t1066_death[which(t1066_death$dead==1),]
ddd <- t1066_death[!is.na(t1066_death$ydeath),]
kable(ddd[!(ddd$id %in% dd$id),])
```

```{r importOPAL_india2, echo=FALSE, eval = FALSE}
label(t1066_ds_india_w2$living_status) <- ds_label
living_status <- t1066_ds_india_w2
save(living_status, file = "../RData/india_w2/living_status.RData")
rm(living_status, t1066_id_w1, t1066_id_w2, t1066_death2, t1066_death)
```

-->


## Urban China

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign__UCh1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_UCh1, echo=FALSE}
t1066_ds_UCh_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_UCh_w1$living_status <- 0
t1066_ds_UCh_w1$living_status <- labelled(t1066_ds_UCh_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh1, echo=FALSE}
vari <- t1066_ds_UCh_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation





## Wave 2 

#### Study-specific variable description

 
| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_UCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_UCh2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_UCh2, echo=TRUE} 
t1066_ds_UCh_w2 <- tibble(id=t1066_death$id)
t1066_ds_UCh_w2$living_status <- 2
t1066_ds_UCh_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_UCh_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_UCh_w2$living_status <- labelled(t1066_ds_UCh_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UCh2, echo=FALSE} 
vari <- t1066_ds_UCh_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=FALSE} 
```

 




## Rural China

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign__RCh1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_RCh1}
t1066_ds_RCh_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_RCh_w1$living_status <- 0
t1066_ds_RCh_w1$living_status <- labelled(t1066_ds_RCh_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh1, echo=FALSE}
vari <- t1066_ds_RCh_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation




### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_RCh2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralChina-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralChina-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_RCh2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_RCh2, echo=TRUE} 
t1066_ds_RCh_w2 <- tibble(id=t1066_death$id)
t1066_ds_RCh_w2$living_status <- 2
t1066_ds_RCh_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_RCh_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_RCh_w2$living_status <- labelled(t1066_ds_RCh_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RCh2, echo=FALSE} 
vari <- t1066_ds_RCh_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=FALSE} 
```




## Dominican Republic

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_DR1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_DR_w1$living_status <- 0
t1066_ds_DR_w1$living_status <- labelled(t1066_ds_DR_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR1, echo=FALSE}
vari <- t1066_ds_DR_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation





### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_DR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-DominicanRepublic-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_DR2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_DR2, echo=TRUE} 
t1066_ds_DR_w2 <- tibble(id=t1066_death$id)
t1066_ds_DR_w2$living_status <- 2
t1066_ds_DR_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_DR_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_DR_w2$living_status <- labelled(t1066_ds_DR_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_DR2, echo=FALSE} 
vari <- t1066_ds_DR_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=FALSE} 
```

 





## Venezuela

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_V1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Venezuela-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_V1}
t1066_ds_Ven_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_Ven_w1$living_status <- 0
t1066_ds_Ven_w1$living_status <- labelled(t1066_ds_Ven_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V1, echo=FALSE}
vari <- t1066_ds_Ven_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
#### Validation






### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |


```{r assign_V2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-Venezuela-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-Venezuela-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_V2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_V2, echo=TRUE} 
t1066_ds_Ven_w2 <- tibble(id=t1066_death$id)
t1066_ds_Ven_w2$living_status <- 2
t1066_ds_Ven_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_Ven_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_Ven_w2$living_status <- labelled(t1066_ds_Ven_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_V2, echo=FALSE} 
vari <- t1066_ds_Ven_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=FALSE} 
```

 





## Urban Peru

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign__UP1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_UP_w1$living_status <- 0
t1066_ds_UP_w1$living_status <- labelled(t1066_ds_UP_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP1, echo=FALSE}
vari <- t1066_ds_UP_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation



### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_UP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_UP2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_UP2, echo=TRUE} 
t1066_ds_UP_w2 <- tibble(id=t1066_death$id)
t1066_ds_UP_w2$living_status <- 2
t1066_ds_UP_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_UP_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_UP_w2$living_status <- labelled(t1066_ds_UP_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UP2, echo=FALSE} 
vari <- t1066_ds_UP_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=FALSE} 
```

 




## Rural Peru

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_RP, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_iRP}
t1066_ds_RP_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_RP_w1$living_status <- 0
t1066_ds_RP_w1$living_status <- labelled(t1066_ds_RP_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP, echo=FALSE}
vari <- t1066_ds_RP_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation







### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_RP2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralPeru-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_RP2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_RP2, echo=TRUE} 
t1066_ds_RP_w2 <- tibble(id=t1066_death$id)
t1066_ds_RP_w2$living_status <- 2
t1066_ds_RP_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_RP_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_RP_w2$living_status <- labelled(t1066_ds_RP_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RP2, echo=FALSE} 
vari <- t1066_ds_RP_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=FALSE} 
```








## Urban Mexico

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_UM1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_UM_w1$living_status <- 0
t1066_ds_UM_w1$living_status <- labelled(t1066_ds_UM_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM1, echo=FALSE}
vari <- t1066_ds_UM_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation







### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_UM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-UrbanMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-UrbanMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_UM2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_UM2, echo=TRUE} 
t1066_ds_UM_w2 <- tibble(id=t1066_death$id)
t1066_ds_UM_w2$living_status <- 2
t1066_ds_UM_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_UM_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_UM_w2$living_status <- labelled(t1066_ds_UM_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_UM2, echo=FALSE} 
vari <- t1066_ds_UM_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=FALSE} 
```






## Rural Mexico

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_RM1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_RM_w1$living_status <- 0
t1066_ds_RM_w1$living_status <- labelled(t1066_ds_RM_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM1, echo=FALSE}
vari <- t1066_ds_RM_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation






### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_RM2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-RuralMexico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-RuralMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_RM2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`


**R script:**

```{r harmo_RM2, echo=TRUE} 
t1066_ds_RM_w2 <- tibble(id=t1066_death$id)
t1066_ds_RM_w2$living_status <- 2
t1066_ds_RM_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_RM_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_RM_w2$living_status <- labelled(t1066_ds_RM_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_RM2, echo=FALSE} 
vari <- t1066_ds_RM_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=FALSE} 
```

 








## Puerto Rico

### Wave 1
#### Study-specific variable description

Not study-specific variable used.
```{r assign_PR1, echo=FALSE}
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-PuertoRico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_id_w1$id)
t1066_ds_PR_w1$living_status <- 0
t1066_ds_PR_w1$living_status <- labelled(t1066_ds_PR_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR1, echo=FALSE}
vari <- t1066_ds_PR_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation







### Wave 2

#### Study-specific variable description

| **Name** | `dead`|
|-|-|
| **Label** | `dead by follow-up?`|
| **Table name** | `pyears_(mortality_cohort)_2_0` |
| **Categories** |`0 = alive at follow-up - reinterviewed or refused` |
| | `1 = dead` |
| **Description** |  |

```{r assign_PR2, echo=FALSE} 
opal.assign.table.tibble(o, 't1066_id_w1','10-66.1066-PuertoRico-Baseline',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w1 <- opal.execute(o,'t1066_id_w1')

opal.assign.table.tibble(o, 't1066_id_w2','10-66.1066-PuertoRico-Followup',
                         variables=list('centreid'), missings = TRUE)
t1066_id_w2 <- opal.execute(o,'t1066_id_w2')

opal.assign.table.tibble(o, 't1066_death2','10-66.pyears_(mortality_cohort)_2_0',
                         variables=list('death_date','dead'), missings = TRUE)
t1066_death2 <- opal.execute(o,'t1066_death2')
t1066_death2$ydeath <- format(t1066_death2$death_date, '%Y')

t1066_death2 <- t1066_death2[c("id", "ydeath", "dead")]


same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ydeath=as.numeric(new_2[,2]), dead=as.numeric(new_2[,3]))
  new_22
}

t1066_death <- same_indiv(old = t1066_death2, new = t1066_id_w1)
```

```{r local_PR2, echo=FALSE} 
vari <- t1066_death$dead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(t1066_death, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 ('alive') `
* `the individuals with a value 1 in dead variable into 1 ('death') `
* `the individuals don't include in wave 2 and with 1 or missing in dead varibale into 2 ('dropout')`

**R script:**

```{r harmo_PR2, echo=TRUE} 
t1066_ds_PR_w2 <- tibble(id=t1066_death$id)
t1066_ds_PR_w2$living_status <- 2
t1066_ds_PR_w2$living_status[t1066_death$id %in% t1066_id_w2$id] <- 0
t1066_ds_PR_w2$living_status[which(t1066_death$dead==1)] <- 1
t1066_ds_PR_w2$living_status <- labelled(t1066_ds_PR_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_PR2, echo=FALSE} 
vari <- t1066_ds_PR_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=FALSE} 
```












```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


```



## Descriptive statistics of the harmonised variable `living_status` accross populations and waves

Percentages of categories in each harmonised variable:

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# Consider only waves with some variable harmonised

l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```












# Quality estimation

<!--Not available except for India. -->



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
