---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `yintw`
* Variable label: `Year of interview`
* Variable description: `year of interviewe`
* Domain: `Other administrative variables`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Year of interview"
```

# Data process

## Ireland

### Wave 1 


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_id','TILDA.TILDA-AMF-v16',
                         variables=list('age'), missings = TRUE)
TILDA_w1_id <- opal.execute(o,'TILDA_w1_id')
```

#### Harmonisation algorithm

As there is no variable codifying the year of interview, 
the knowledge of the study allow us to assume it is 2010. 


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_id$id)
TILDA_ds_w1$yintw <- 2010
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$yintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```

```{r importOPAL1, echo=F}
label(TILDA_ds_w1$yintw) <- ds_label
yintw <- TILDA_ds_w1
save(yintw, file = "../RData/w1/yintw.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$yintw <- recode(TILDA_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_id','TILDA.TILDA-AMF-v23',
                         variables=list('age'), missings = TRUE)
TILDA_w2_id <- opal.execute(o,'TILDA_w2_id')
```

#### Harmonisation algorithm

As there is no variable codifying the year of interview, the knowledge of the study allow us to assume it is 2012. 

**R script:**

```{r harmo2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_id$id)
TILDA_ds_w2$yintw <- 2012
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$yintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
```

```{r importOPAL2, echo=F}
label(TILDA_ds_w2$yintw) <- ds_label
yintw <- TILDA_ds_w2
save(yintw, file = "../RData/w2/yintw.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$yintw <- recode(TILDA_m_ds_w2$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

# Quality estimation
The authors of the study do not reveal the exact date of the interview for anonymization reasons. 
For harmonization purposes we assume is that of the wave (based on study time lapse information).

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
