---
title: "Cognition"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_stat`
* Variable label: `Cognitive status of the participant, assessed by the Mini Mental State Examination`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:
* Comments: `The test used is the Mini Mental State Examination (MMSE). Two values have been created for the potential variable: 0=no cognitive impairment (when the score is greater or equal to 23) and 1=cognitive impairment (when the score is lower to 23).`

**Code** | **Category Label**
-------- | ------------------------
0        | no cognitive impairment
1        | cognitive impairment

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Cognitive status"
ds_label_all <- "Cognitive status of the participant, assessed by the Mini Mental State Examination"
```

<!-- ########################################################## --> 

# Data process


## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** | `COGmmse_ha`|
|-|-|
| **Label** | `Mini-mental state examination (Health Assessment)`|
| **Table name** | `TILDA-AMF-v16` |
| **Description** |  |

```{r assign1, echo=FALSE} 
opal.assign.table.tibble(o, 'TILDA_cog','TILDA.TILDA-AMF-v16',
                         variables=list('COGmmse_ha'), missings = TRUE)
TILDA_cog <- opal.execute(o,'TILDA_cog')
```

```{r local1, echo=FALSE} 
vari <- TILDA_cog$COGmmse_ha
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_cog, aes(TILDA_cog[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `COGmmse_ha < 24 into 1` 
* `COGmmse_ha >= 24 into 0`
* `NA into 999`



**R script:**

```{r harmo1, echo=TRUE} 
TILDA_ds_w1 <- tibble(id=TILDA_cog$id)
TILDA_ds_w1$cog_stat <- car::recode(TILDA_cog[[2]], "lo:23=1; 24:900=0; NA=999")
TILDA_ds_w1$cog_stat <- labelled(TILDA_ds_w1$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE} 
vari <- TILDA_ds_w1$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE} 
BeforeH <- c(sum(na.omit(TILDA_cog[[2]])>23),sum(na.omit(TILDA_cog[[2]])<=23), sum(is.na(TILDA_cog[[2]])))
AfterH <- table(TILDA_ds_w1$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(24-30)->0","(0-23)->1", "NA->999")
kable(C)
```


```{r importOPAL1, echo=FALSE} 
label(TILDA_ds_w1$cog_stat) <- ds_label_all
cog_stat <- TILDA_ds_w1
save(cog_stat, file = "../RData/w1/cog_stat.RData")

#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$cog_stat <- car::recode(TILDA_m_ds_w1$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
rm(TILDA_cog, cog_stat)
```







### Wave 2 

#### Study-specific variable description


| **Name** | `mmsescr_capi`|
|-|-|
| **Label** | `HADS-A Anxiety Scale (collected during CAPI)`|
| **Table name** | `TILDA-AMF-v23` |
| **Description** |  |


```{r assign2, echo=FALSE} 
opal.assign.table.tibble(o, 'TILDA_cog','TILDA.TILDA-AMF-v23',
                         variables=list('mmsescr_capi'), missings = TRUE)
TILDA_cog <- opal.execute(o,'TILDA_cog')
```

```{r local2, echo=FALSE} 
vari <- TILDA_cog$mmsescr_capi
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "MMSE points") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_cog, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `mmsescr_capi < 24 into 1` 
* `mmsescr_capi >= 24 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE} 
TILDA_ds_w2 <- tibble(id=TILDA_cog$id)
TILDA_ds_w2$cog_stat <- car::recode(TILDA_cog[[2]], "lo:23=1; 24:900=0; NA=999")
TILDA_ds_w2$cog_stat <- labelled(TILDA_ds_w2$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE} 
vari <- TILDA_ds_w2$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE} 
BeforeH <- c(sum(na.omit(TILDA_cog[[2]])>23),sum(na.omit(TILDA_cog[[2]])<=23))
AfterH <- table(TILDA_ds_w2$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(24-30)->0","(0-23)->1")
kable(C)
```


```{r importOPAL2, echo=FALSE} 
label(TILDA_ds_w2$cog_stat) <- ds_label_all
cog_stat <- TILDA_ds_w2
save(cog_stat, file = "../RData/w2/cog_stat.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$cog_stat <- car::recode(TILDA_m_ds_w2$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```