---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```


<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** | `MHcesd_capi`|
|-|-|
| **Label** | `CES-D From CAPI`|
| **Table name** | `TILDA-AMF-v16` |
| **Description** |  |

```{r assign1, echo=FALSE} 
opal.assign.table.tibble(o, 'TILDA_dep','TILDA.TILDA-AMF-v16',
                         variables=list('MHcesd_capi'), missings = TRUE)
TILDA_dep <- opal.execute(o,'TILDA_dep')
```

```{r local1, echo=FALSE} 
vari <- TILDA_dep[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_dep, aes(TILDA_dep[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `MHcesd_capi < 16 into 0` 
* `MHcesd_capi >= 16 into 1`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE} 
TILDA_ds_w1 <- tibble(id=TILDA_dep$id)
TILDA_ds_w1$depression <- car::recode(TILDA_dep[[2]], "lo:15=0; 16:hi=1; NA=999")
TILDA_ds_w1$depression <- labelled(TILDA_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE} 
vari <- TILDA_ds_w1[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE} 
BeforeH <- c(sum(na.omit(TILDA_dep[[2]])<16),sum(na.omit(TILDA_dep[[2]])>=16), sum(is.na(TILDA_dep[[2]])))
AfterH <- table(TILDA_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<16->0",">=16->1","NA->999") 
kable(C)
```


```{r importOPAL1, echo=FALSE} 
label(TILDA_ds_w1$depression) <- ds_label_all
depression <- TILDA_ds_w1
save(depression, file = "../RData/w1/depression.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$depression <- car::recode(TILDA_m_ds_w1$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
rm(TILDA_dep, depression)
```







### Wave 2 

#### Study-specific variable description


| **Name** | `MHcesd_capi`|
|-|-|
| **Label** | `CES-D From CAPI`|
| **Table name** | `TILDA-AMF-v23` |
| **Description** |  |


```{r assign2, echo=FALSE} 
opal.assign.table.tibble(o, 'TILDA_dep','TILDA.TILDA-AMF-v23',
                         variables=list('MHcesd_capi'), missings = TRUE)
TILDA_dep <- opal.execute(o,'TILDA_dep')
```

```{r local2, echo=FALSE} 
vari <- TILDA_dep[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_dep, aes(TILDA_dep[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `MHcesd_capi < 16 into 0` 
* `MHcesd_capi >= 16 into 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE} 
TILDA_ds_w2 <- tibble(id=TILDA_dep$id)
TILDA_ds_w2$depression <- car::recode(TILDA_dep[[2]], "lo:15=0; 16:hi=1; NA=999")
TILDA_ds_w2$depression <- labelled(TILDA_ds_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE} 
vari <- TILDA_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE} 
BeforeH <- c(sum(na.omit(TILDA_dep[[2]])<16),sum(na.omit(TILDA_dep[[2]])>=16), sum(is.na(TILDA_dep[[2]])))
AfterH <- table(TILDA_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<16->0",">=16->1","NA->999") 
kable(C)
```


```{r importOPAL2, echo=FALSE} 
label(TILDA_ds_w2$depression) <- ds_label_all
depression <- TILDA_ds_w2
save(depression, file = "../RData/w2/depression.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$depression <- car::recode(TILDA_m_ds_w2$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

They used the Center for Epidemiologic Studies Depression Scale (CES-D). 20 ITEM VERSION TEST
We used the final score variable, and used 16 as cut-off score (Each of the 20 items is measured on a four point scale leading to a total score of 60. A cutoff score of =16 is used to determine clinically significant (case level) depressive symptoms.  =16)




```{r closeRsession, echo=FALSE} 
opal.logout(o)
```