---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_034`|`c_035_a`|`c_035_b`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENT JOB`|`C-034:CURRENT SITUATION`|`C-035:AGE OF RETIREMENT`|`C-035:AGE OF RETIREMENT`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`| `jstar_2007_5cities`| `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Age: ___`<br/>`2 = Don't know`<br/>`3 = Refused to answer`|`continuous`|
| **Missings** | `NA` | `NA` |`NA` | `NA` |`NA` |
| **Description** |  |  |  |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('c_000','c_001','c_034','c_035_a','c_035_b'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_035_a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035_a')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_035_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_035_b
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_035_b')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w1,!vbl %in% vbl_miss), aes(c_035_b)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable, it has to be recoded as follows:

* `c_034 == 2,3,4 into 0`
* `c_034 == 1 into 1`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1 and c_035_a == 1, age_retired = c_035_b`
* `if retired == 1 and c_035_a == 2, age_retired = 998`
* `if retired == 1 and c_035_a == 3, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`


**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$retired <- car::recode(JSTAR_aksst_w1$c_034,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w1$retired[which(JSTAR_aksst_w1$c_001 %in% c(1,2))] <- 0
JSTAR_ds_aksst_w1$retired[which(JSTAR_aksst_w1$c_000==2)] <- 997

# Continuous variable harmonization
age_ <- car::recode(JSTAR_aksst_w1$c_035_b[which(JSTAR_aksst_w1$c_035_a==1)],"NA = 999")
age_retired <- car::recode(JSTAR_aksst_w1$c_035_a[which(JSTAR_ds_aksst_w1$retired==1)], "1 = age_; 2 = 998; 3 = 997; NA = 999")
JSTAR_ds_aksst_w1$age_retired <- car::recode(JSTAR_ds_aksst_w1$retired, "1 = age_retired; 0 = 996; miss_values_vector = 999")
rm(age_retired)
rm(age_)

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_aksst_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('c_000','c_001','c_035','c_036_a','c_036_b','c_036_c'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
load(paste0(datafolder,"aksst_w2/ybirth.RData"))
JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"aksst_w2/mbirth.RData"))
JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,mbirth, by="id")
rm(mbirth)

```


| **Name** | `c_000` | `c_001` |`c_035`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C1`|`C-001:CURRENTLY WORKING`|`C-035:CURRENT SITUATION`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`| `jstar_2009_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

| **Name** |`c_036_a`|`c_036_b`|`c_036_c`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|
| **Label** | `C-036:AGE OF RETIREMENT`|`C-036:AGE OF RETIREMENT, YEAR`|`C-036:AGE OF RETIREMENT, MONTH`|`month of birth`|`year of birth`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`| `jstar_2009_5cities`|`mbirth`|`ybirth`|
| **Categories** |`1 = Age: ___`<br/>`2 = Don't know`<br/>`3 = Refused to answer`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `4`<br/>`NA` | `NA` | `NA` |`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r locala aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$c_036_a
kable(Categorical_summary(vbl, missing_values = c(4))[3], caption = 'c_036_a')
kable(Categorical_summary(vbl, missing_values = c(4))[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_036_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_036_b
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_b')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w2,!vbl %in% vbl_miss), aes(c_036_b)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_036_c
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_c')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w2,!vbl %in% vbl_miss), aes(c_036_c)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- JSTAR_aksst_w2$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w2,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- JSTAR_aksst_w2$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w2,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```




#### Harmonisation algorithm

To compute `retired` from the study-specific variable `c_001`, it has to be recoded as follows:

* `c_035 == 2,3,4 into 0`
* `c_035 == 1 into 1`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `4,NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`
* `c_036_a == 1 into 1`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, c_036_c, c_036_b into month, year of retirement and age_retired = date of retirement - date of birth`
* `if retired == 1 and c_036_a == 2, age_retired = 998`
* `if retired == 1 and c_036_a == 3, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`


**R script:**

```{r harmo aksst_w2}

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$retired <- car::recode(JSTAR_aksst_w2$c_035,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w2$retired[which(JSTAR_aksst_w2$c_001 %in% c(1,2))] <- 0
JSTAR_ds_aksst_w2$retired[which(JSTAR_aksst_w2$c_000==2)] <- 997
JSTAR_ds_aksst_w2$retired[which(JSTAR_aksst_w2$c_036_a==1)] <- 1

# Continuous variable harmonization
JSTAR_aksst_w2$month <- car::recode(JSTAR_aksst_w2$c_036_c,"NA=999")
JSTAR_aksst_w2$year <- car::recode(JSTAR_aksst_w2$c_036_b,"NA=999")


#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

JSTAR_ds_aksst_w2$age_retired <- comp_age(y_birth=JSTAR_aksst_w2$ybirth, m_birth=JSTAR_aksst_w2$mbirth , a_year=JSTAR_aksst_w2$year, a_month=JSTAR_aksst_w2$month, miss=miss_values_vector)

JSTAR_ds_aksst_w2$age_retired[which(JSTAR_ds_aksst_w2$age_retired==999)] <- car::recode(JSTAR_aksst_w2$c_036_a[which(JSTAR_ds_aksst_w2$age_retired==999)],"c(1,4) = 999; 2 = 998; 3 = 997; NA = 999")
JSTAR_ds_aksst_w2$age_retired[which(JSTAR_ds_aksst_w2$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_aksst_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

```



### Wave 3


#### Study-specific variable description

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('c_000','c_001','c_035','c_036_a','c_036_f','c_036_g'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
load(paste0(datafolder,"aksst_w3/ybirth.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"aksst_w3/mbirth.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,mbirth, by="id")
rm(mbirth)

```


| **Name** | `c_000` | `c_001` |`c_035`|
|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-035:CURRENT SITUATION`|
| **Table name**  | `jstar_2011_5cities`| `jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Homemaker`<br/>`3 = Taking a rest due to illness, injuries, etc.`<br/>`4 = Other (Specify:)`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |


```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

| **Name** |`C_036_a`|`c_036_f`|`c_036_g`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|
| **Label** | `11C-036:AGE OF RETIREMENT`|`11C-036:AGE OF RETIREMENT, YEAR`|`11C-036:AGE OF RETIREMENT, MONTH`|`month of birth`|`year of birth`|
| **Table name**  | `jstar_2011_5cities`| `jstar_2011_5cities`| `jstar_2011_5cities`|`mbirth`|`ybirth`|
| **Categories** |`1 = Age: ___`<br/>`2 = Don't know`<br/>`3 = Refused to answer`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `4`<br/>`NA` | `NA` | `NA` |`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |


```{r locala aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$c_036_a
kable(Categorical_summary(vbl, missing_values = c(4))[3], caption = 'c_036_a')
kable(Categorical_summary(vbl, missing_values = c(4))[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_036_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_036_f
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_f')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w3,!vbl %in% vbl_miss), aes(c_036_f)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_036_g
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_g')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w3,!vbl %in% vbl_miss), aes(c_036_g)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- JSTAR_aksst_w3$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w3,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- JSTAR_aksst_w3$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_aksst_w3,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `c_035 == 2,3,4 into 0`
* `c_035 == 1 into 1`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, c_036_g, c_036_f into month, year of retirement and age_retired = date of retirement - date of birth`
* `if retired == 1 and c_036_a == 2, age_retired = 998`
* `if retired == 1 and c_036_a == 3, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$retired <- car::recode(JSTAR_aksst_w3$c_035,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w3$retired[which(JSTAR_aksst_w3$c_001 %in% c(1,2))] <- 0
JSTAR_ds_aksst_w3$retired[which(JSTAR_aksst_w3$c_000==2)] <- 997

# Continuous variable harmonization
JSTAR_aksst_w3$month <- car::recode(JSTAR_aksst_w3$c_036_g,"NA=999")
JSTAR_aksst_w3$year <- car::recode(JSTAR_aksst_w3$c_036_f,"NA=999")


#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

JSTAR_ds_aksst_w3$age_retired <- comp_age(y_birth=JSTAR_aksst_w3$ybirth, m_birth=JSTAR_aksst_w3$mbirth , a_year=JSTAR_aksst_w3$year, a_month=JSTAR_aksst_w3$month, miss=miss_values_vector)

JSTAR_ds_aksst_w3$age_retired[which(JSTAR_ds_aksst_w3$age_retired==999)] <- car::recode(JSTAR_aksst_w3$c_036_a[which(JSTAR_ds_aksst_w3$age_retired==999)],"c(1,4) = 999; 2 = 998; 3 = 997; NA = 999")
JSTAR_ds_aksst_w3$age_retired[which(JSTAR_ds_aksst_w3$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w3$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_aksst_w3,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

```



## tn

### Wave 1

#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_034`|`c_035_a`|`c_035_b`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-034:CURRENT SITUATION`|`C-035:AGE OF RETIREMENT`|`C-035:AGE OF RETIREMENT`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|`jstar_2009_2cities`| `jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Age: ___`<br/>`2 = Don't know`<br/>`3 = Refused to answer`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |


```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('c_000','c_001','c_034','c_035_a','c_035_b'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_035_a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035_a')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_035_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_035_b
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_035_b')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_tn_w1,!vbl %in% vbl_miss), aes(c_035_b)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `c_034 == 2,3,4 into 0`
* `c_034 == 1 into 1`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1 and c_035_a == 1, age_retired = c_035_b`
* `if retired == 1 and c_035_a == 2, age_retired = 998`
* `if retired == 1 and c_035_a == 3, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$retired <- car::recode(JSTAR_tn_w1$c_034,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_tn_w1$retired[which(JSTAR_tn_w1$c_001 %in% c(1,2))] <- 0
JSTAR_ds_tn_w1$retired[which(JSTAR_tn_w1$c_000==2)] <- 997

# Continuous variable harmonization
age_ <- JSTAR_tn_w1$c_035_b[which(JSTAR_tn_w1$c_035_a==1)]
age_retired <- car::recode(JSTAR_tn_w1$c_035_a[which(JSTAR_ds_tn_w1$retired==1)], "1 = age_; 2 = 998; 3 = 997; NA = 999")
JSTAR_ds_tn_w1$age_retired <- car::recode(JSTAR_ds_tn_w1$retired, "1 = age_retired; 0 = 996; miss_values_vector = 999")
rm(age_retired)
rm(age_)

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_tn_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('c_000','c_001','c_035','c_036_a','c_036_f','c_036_g'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
load(paste0(datafolder,"tn_w2/ybirth.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"tn_w2/mbirth.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,mbirth, by="id")
rm(mbirth)

```

| **Name** | `c_000` | `c_001` |`c_035`|
|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-035:CURRENT SITUATION`|
| **Table name**  | `jstar_2011_2cities`| `jstar_2011_2cities`|`jstar_2011_2cities`| `jstar_2011_2cities`|`jstar_2011_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Homemaker`<br/>`3 = Taking a rest due to illness, injuries, etc.`<br/>`4 = Other (Specify:)`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


| **Name** |`C_036_a`|`c_036_f`|`c_036_g`|`mbirth`|`ybirth`|
|-|-|-|-|-|-|
| **Label** | `11C-036:AGE OF RETIREMENT`|`11C-036:AGE OF RETIREMENT, YEAR`|`11C-036:AGE OF RETIREMENT, MONTH`|`month of birth`|`year of birth`|
| **Table name**  | `jstar_2011_2cities`| `jstar_2011_2cities`| `jstar_2011_2cities`|`mbirth`|`ybirth`|
| **Categories** |`1 = Age: ___`<br/>`2 = Don't know`<br/>`3 = Refused to answer`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |


```{r locala tn_w2, echo=F}

vbl <- JSTAR_tn_w2$c_036_a
kable(Categorical_summary(vbl, missing_values = c(4))[3], caption = 'c_036_a')
kable(Categorical_summary(vbl, missing_values = c(4))[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_036_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_036_f
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_f')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_tn_w2,!vbl %in% vbl_miss), aes(c_036_f)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_036_g
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_036_g')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_tn_w2,!vbl %in% vbl_miss), aes(c_036_g)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))

vbl <- JSTAR_tn_w2$mbirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'mbirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_tn_w2,!vbl %in% vbl_miss), aes(mbirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")+scale_x_continuous(breaks=c(3,6,9,12))+scale_y_continuous(breaks=c(0,1,2))

vbl <- JSTAR_tn_w2$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_tn_w2,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `c_035 == 2,3,4 into 0`
* `c_035 == 1 into 1`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, c_036_g, c_036_f into month, year of retirement and age_retired = date of retirement - date of birth`
* `if retired == 1 and c_036_a == 2, age_retired = 998`
* `if retired == 1 and c_036_a == 3, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$retired <- car::recode(JSTAR_tn_w2$c_035,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_tn_w2$retired[which(JSTAR_tn_w2$c_001 %in% c(1,2))] <- 0
JSTAR_ds_tn_w2$retired[which(JSTAR_tn_w2$c_000==2)] <- 997

# Continuous variable harmonization
JSTAR_tn_w2$month <- car::recode(JSTAR_tn_w2$c_036_g,"NA=999")
JSTAR_tn_w2$year <- car::recode(JSTAR_tn_w2$c_036_f,"NA=999")


#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

JSTAR_ds_tn_w2$age_retired <- comp_age(y_birth=JSTAR_tn_w2$ybirth, m_birth=JSTAR_tn_w2$mbirth , a_year=JSTAR_tn_w2$year, a_month=JSTAR_tn_w2$month, miss=miss_values_vector)

JSTAR_ds_tn_w2$age_retired[which(JSTAR_ds_tn_w2$age_retired==999)] <- car::recode(JSTAR_tn_w2$c_036_a[which(JSTAR_ds_tn_w2$age_retired==999)],"1 = 999; 2 = 998; 3 = 997; NA = 999")
JSTAR_ds_tn_w2$age_retired[which(JSTAR_ds_tn_w2$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_tn_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}


```



## cth

### Wave 1


#### Study-specific variable description

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('c_000','c_001','c_034','c_035_a','c_035_h'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')
load(paste0(datafolder,"cth_w1/ybirth.RData"))
JSTAR_cth_w1 <- left_join(JSTAR_cth_w1,ybirth, by="id")
rm(ybirth)

```

| **Name** | `c_000` | `c_001` |`c_034`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-034:CURRENT SITUATION`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


| **Name** |`c_035_a`|`c_035_h`|`ybirth`|
|-|-|-|-|
| **Label** | `C-035:AGE OF RETIREMENT`|`C-035:YEAR OF RETIREMENT`|`year of birth`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|`ybirth`|
| **Categories** |`1 = In Japnese calendar Showa ( ) year ( ) month`<br/>`2 = In Japanese calendar Heisei ( ) year ( ) month`<br/>`3 = In Western calendar ( ) year ( ) month`<br/>`4 = Don't know`<br/>`5 = Refused to answer`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |


```{r locala cth_w1, echo=F}

vbl <- JSTAR_cth_w1$c_035_a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035_a')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_035_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_035_h
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'c_035_h')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_cth_w1,!vbl %in% vbl_miss), aes(c_035_h)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(JSTAR_cth_w1,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue" ) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `c_034 == 2,3,4 into 0`
* `c_034 == 1 into 1`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 into 0`
* `c_000 == 2 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, c_035_h into year of retirement and age_retired = year of retirement - year of birth`
* `if retired == 1 and c_035_a == 4, age_retired = 998`
* `if retired == 1 and c_035_a == 5, age_retired = 997`
* `if retired == 0, age_retired = 996`
* `otherwise, age_retired = 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$retired <- car::recode(JSTAR_cth_w1$c_034,"c(2,3,4) = 0; 1 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_cth_w1$retired[which(JSTAR_cth_w1$c_001 %in% c(1,2))] <- 0
JSTAR_ds_cth_w1$retired[which(JSTAR_cth_w1$c_000==2)] <- 997
JSTAR_ds_cth_w1$retired[which(JSTAR_cth_w1$c_035_a==2)] <- 1

# Continuous variable harmonization
JSTAR_ds_cth_w1$age_retired <- JSTAR_cth_w1$c_035_h - JSTAR_cth_w1$ybirth
JSTAR_ds_cth_w1$age_retired[which(JSTAR_ds_cth_w1$age_retired<1)] <- 999

JSTAR_ds_cth_w1$age_retired[which(is.na(JSTAR_ds_cth_w1$age_retired))] <- car::recode(JSTAR_cth_w1$c_035_a[which(is.na(JSTAR_ds_cth_w1$age_retired))],"c(1,2) = 999; 4 = 998; 5 = 997; NA = 999")
JSTAR_ds_cth_w1$age_retired[which(JSTAR_ds_cth_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_cth_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(JSTAR_ds_cth_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}


```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size",sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label",toupper(names(l.hds)))
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





