---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mbirthDS.R')
```




# Data process

## aksst

### Wave 1 

#### Study-specific variable description

| **Name** | `k_001_3_c` |
|----------|------------|
| **Label** | `CORRECT MONTH OF BIRTH OF THE RESPONDENT` |
| **Table name** | `jstar_2009_5cities` |
| **Description** |  |


```{r assign_aksst1, echo=F, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_mbirth','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('k_001_3_c'), missings = TRUE)
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_id','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_b'), missings = TRUE)
JSTAR_aksst_w2_mbirth <- opal.execute(o,'JSTAR_aksst_w2_mbirth')
JSTAR_aksst_w1_id <- opal.execute(o,'JSTAR_aksst_w1_id')
```

```{r local_aksst1, echo=F, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], k_001_3_c=as.numeric(new_2[,2]))
  new_22
}

JSTAR_aksst_w1_mbirth <- Add_indiv(old = JSTAR_aksst_w2_mbirth, new = JSTAR_aksst_w1_id)

vari <- JSTAR_aksst_w1_mbirth$k_001_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "k_001_3_c") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_mbirth, aes(x=factor(k_001_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst1}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_mbirth$id)
JSTAR_ds_aksst_w1$mbirth <- car::recode(JSTAR_aksst_w1_mbirth$k_001_3_c, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_aksst1, echo=F, echo=F}
vari <- JSTAR_ds_aksst_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst1, echo=F, echo=F}
BeforeH <- c(table(JSTAR_aksst_w1_mbirth$k_001_3_c), sum(is.na(JSTAR_aksst_w1_mbirth$k_001_3_c)))
AfterH <- table(JSTAR_ds_aksst_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:10], "NA->999")
kable(C)
```





```{r importOPAL_aksst1, echo=F, echo=F}

#opal.assign.data(o, 'JSTAR_ds_aksst_w1', JSTAR_ds_aksst_w1)
#opal.symbol_import(o,'JSTAR_ds_aksst_w1', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_ds_aksst_w1
save(mbirth, file = "../RData/aksst_w1/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w1 <- JSTAR_ds_aksst_w1
JSTAR_aksst_m_ds_w1$mbirth <- car::recode(JSTAR_aksst_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w1', JSTAR_aksst_m_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `k_001_3_c` |
|----------|------------|
| **Label** | `CORRECT MONTH OF BIRTH OF THE RESPONDENT` |
| **Table name** | `jstar_2009_5cities` |
| **Description** |  |



```{r assign_aksst2, echo=F, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_mbirth','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('k_001_3_c'), missings = TRUE)
JSTAR_aksst_w2_mbirth <- opal.execute(o,'JSTAR_aksst_w2_mbirth')
```

```{r local_aksst2, echo=F, echo=F}
vari <- JSTAR_aksst_w2_mbirth$k_001_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "k_001_3_c") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_mbirth, aes(x=factor(k_001_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_mbirth$id)
JSTAR_ds_aksst_w2$mbirth <- car::recode(JSTAR_aksst_w2_mbirth$k_001_3_c, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_aksst2, echo=F}
vari <- JSTAR_ds_aksst_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst2, echo=F}
BeforeH <- c(table(JSTAR_aksst_w2_mbirth$k_001_3_c), sum(is.na(JSTAR_aksst_w2_mbirth$k_001_3_c)))
AfterH <- table(JSTAR_ds_aksst_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:10], "NA->999")
kable(C)
```





```{r importOPAL_aksst2, echo=F}

#opal.assign.data(o, 'JSTAR_ds_aksst_w2', JSTAR_ds_aksst_w2)
#opal.symbol_import(o,'JSTAR_ds_aksst_w2', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_ds_aksst_w2
save(mbirth, file = "../RData/aksst_w2/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w2 <- JSTAR_ds_aksst_w2
JSTAR_aksst_m_ds_w2$mbirth <- car::recode(JSTAR_aksst_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w2', JSTAR_aksst_m_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|-|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_5cities` |
| **Description** |  |



```{r assign_aksst3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_mbirth','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('k_001_3_g'), missings = TRUE)
JSTAR_aksst_w3_mbirth <- opal.execute(o,'JSTAR_aksst_w3_mbirth')
```

```{r local_aksst3, echo=F}
vari <- JSTAR_aksst_w3_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "k_001_3_g") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_mbirth$id)
JSTAR_ds_aksst_w3$mbirth <- car::recode(JSTAR_aksst_w3_mbirth$k_001_3_g, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_aksst3, echo=F}
vari <- JSTAR_ds_aksst_w3$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst3, echo=F}
BeforeH <- c(table(JSTAR_aksst_w3_mbirth$k_001_3_g), sum(is.na(JSTAR_aksst_w3_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_ds_aksst_w3$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:9], "NA->999")
kable(C)
```





```{r importOPAL_aksst3, echo=F}

#opal.assign.data(o, 'JSTAR_ds_aksst_w3', JSTAR_ds_aksst_w3)
#opal.symbol_import(o,'JSTAR_ds_aksst_w3', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_ds_aksst_w3
save(mbirth, file = "../RData/aksst_w3/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w3 <- JSTAR_ds_aksst_w3
JSTAR_aksst_m_ds_w3$mbirth <- car::recode(JSTAR_aksst_m_ds_w3$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w3', JSTAR_aksst_m_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w3', project='_Athlos_Harm_Dataset')
```





## tn

### Wave 1 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_2cities` |
| **Description** |  |



```{r assign_tn1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_mbirth','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('k_001_3_g'), missings = TRUE)
opal.assign.table.tibble(o, 'JSTAR_tn_w1_id','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_000_b'), missings = TRUE)
JSTAR_tn_w2_mbirth <- opal.execute(o,'JSTAR_tn_w2_mbirth')
JSTAR_tn_w1_id <- opal.execute(o,'JSTAR_tn_w1_id')
```

```{r local_tn1, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], k_001_3_g=as.numeric(new_2[,2]))
  new_22
}

JSTAR_tn_w1_mbirth <- Add_indiv(old = JSTAR_tn_w2_mbirth, new = JSTAR_tn_w1_id)

vari <- JSTAR_tn_w1_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "k_001_3_g") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn1}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_mbirth$id)
JSTAR_ds_tn_w1$mbirth <- car::recode(JSTAR_tn_w1_mbirth$k_001_3_g, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_tn1, echo=F}
vari <- JSTAR_ds_tn_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn1, echo=F}
BeforeH <- c(table(JSTAR_tn_w1_mbirth$k_001_3_g), sum(is.na(JSTAR_tn_w1_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_ds_tn_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:6], "NA->999")
kable(C)
```





```{r importOPAL_tn1, echo=F}

#opal.assign.data(o, 'JSTAR_ds_tn_w1', JSTAR_ds_tn_w1)
#opal.symbol_import(o,'JSTAR_ds_tn_w1', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_ds_tn_w1
save(mbirth, file = "../RData/tn_w1/mbirth.RData")
rm(mbirth)

JSTAR_tn_m_ds_w1 <- JSTAR_ds_tn_w1
JSTAR_tn_m_ds_w1$mbirth <- car::recode(JSTAR_tn_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w1', JSTAR_tn_m_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_2cities` |
| **Description** |  |




```{r assign_tn2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_mbirth','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('k_001_3_g'), missings = TRUE)
JSTAR_tn_w2_mbirth <- opal.execute(o,'JSTAR_tn_w2_mbirth')
```

```{r local_tn2, echo=F}
vari <- JSTAR_tn_w2_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "k_001_3_g") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_mbirth$id)
JSTAR_ds_tn_w2$mbirth <- car::recode(JSTAR_tn_w2_mbirth$k_001_3_g, "NA=999")
```

#### Statistics of the new harmonised variable
```{r descript_tn2, echo=F}
vari <- JSTAR_ds_tn_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn2, echo=F}
BeforeH <- c(table(JSTAR_tn_w2_mbirth$k_001_3_g), sum(is.na(JSTAR_tn_w2_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_ds_tn_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:6], "NA->999")
kable(C)
```





```{r importOPAL_tn2, echo=F}

#opal.assign.data(o, 'JSTAR_ds_tn_w2', JSTAR_ds_tn_w2)
#opal.symbol_import(o,'JSTAR_ds_tn_w2', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_ds_tn_w2
save(mbirth, file = "../RData/tn_w2/mbirth.RData")
rm(mbirth)

JSTAR_tn_m_ds_w2 <- JSTAR_ds_tn_w2
JSTAR_tn_m_ds_w2$mbirth <- car::recode(JSTAR_tn_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w2', JSTAR_tn_m_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w2', project='_Athlos_Harm_Dataset')
```





## cth

### Wave 1 

No variable.



## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation

No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
