---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


```{r lab, echo=FALSE}
ds_label <- "Month of birth"
```





# Description of DataSchema variable 

The description of harmonised variable is the following:


* Short name: `mbirth`
* Variable label: `month of birth`
* Variable description: `Month of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## aksst

### Wave 1 

#### Study-specific variable description

| **Name** | `k_001_3_c` |
|----------|------------|
| **Label** | `CORRECT MONTH OF BIRTH OF THE RESPONDENT` |
| **Table name** | `jstar_2009_5cities` |
| **Description** |  |


```{r assign_aksst1, echo=F, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_mbirth','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('k_001_3_c'), missings = TRUE)
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_id','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_b'), missings = TRUE)
JSTAR_aksst_w2_mbirth <- opal.execute(o,'JSTAR_aksst_w2_mbirth')
JSTAR_aksst_w1_id <- opal.execute(o,'JSTAR_aksst_w1_id')
```

```{r local_aksst1, echo=F, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], k_001_3_c=as.numeric(new_2[,2]))
  new_22
}

JSTAR_aksst_w1_mbirth <- Add_indiv(old = JSTAR_aksst_w2_mbirth, new = JSTAR_aksst_w1_id)

vari <- JSTAR_aksst_w1_mbirth$k_001_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_mbirth, aes(x=factor(k_001_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_mbirth$id)
JSTAR_aksst_ds_w1$mbirth <- car::recode(JSTAR_aksst_w1_mbirth$k_001_3_c, "NA=999")
JSTAR_aksst_ds_w1$mbirth <- labelled(JSTAR_aksst_ds_w1$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst1, echo=F, echo=F}
vari <- JSTAR_aksst_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst1, echo=F, echo=F}
BeforeH <- c(table(JSTAR_aksst_w1_mbirth$k_001_3_c), sum(is.na(JSTAR_aksst_w1_mbirth$k_001_3_c)))
AfterH <- table(JSTAR_aksst_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:10], "NA->999")
kable(C)
```





```{r importOPAL_aksst1, echo=F, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_aksst_ds_w1
save(mbirth, file = "../RData/aksst_w1/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_aksst_m_ds_w1$mbirth <- car::recode(JSTAR_aksst_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w1', JSTAR_aksst_m_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `k_001_3_c` |
|----------|------------|
| **Label** | `CORRECT MONTH OF BIRTH OF THE RESPONDENT` |
| **Table name** | `jstar_2009_5cities` |
| **Description** |  |



```{r assign_aksst2, echo=F, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_mbirth','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('k_001_3_c'), missings = TRUE)
JSTAR_aksst_w2_mbirth <- opal.execute(o,'JSTAR_aksst_w2_mbirth')
```

```{r local_aksst2, echo=F, echo=F}
vari <- JSTAR_aksst_w2_mbirth$k_001_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_mbirth, aes(x=factor(k_001_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_mbirth$id)
JSTAR_aksst_ds_w2$mbirth <- car::recode(JSTAR_aksst_w2_mbirth$k_001_3_c, "NA=999")
JSTAR_aksst_ds_w2$mbirth <- labelled(JSTAR_aksst_ds_w2$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst2, echo=F}
vari <- JSTAR_aksst_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst2, echo=F}
BeforeH <- c(table(JSTAR_aksst_w2_mbirth$k_001_3_c), sum(is.na(JSTAR_aksst_w2_mbirth$k_001_3_c)))
AfterH <- table(JSTAR_aksst_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:10], "NA->999")
kable(C)
```





```{r importOPAL_aksst2, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_aksst_ds_w2
save(mbirth, file = "../RData/aksst_w2/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_aksst_m_ds_w2$mbirth <- car::recode(JSTAR_aksst_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w2', JSTAR_aksst_m_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|-|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_5cities` |
| **Description** |  |



```{r assign_aksst3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_mbirth','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('k_001_3_g'), missings = TRUE)
JSTAR_aksst_w3_mbirth <- opal.execute(o,'JSTAR_aksst_w3_mbirth')
```

```{r local_aksst3, echo=F}
vari <- JSTAR_aksst_w3_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_mbirth$id)
JSTAR_aksst_ds_w3$mbirth <- car::recode(JSTAR_aksst_w3_mbirth$k_001_3_g, "NA=999")
JSTAR_aksst_ds_w3$mbirth <- labelled(JSTAR_aksst_ds_w3$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst3, echo=F}
vari <- JSTAR_aksst_ds_w3$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst3, echo=F}
BeforeH <- c(table(JSTAR_aksst_w3_mbirth$k_001_3_g), sum(is.na(JSTAR_aksst_w3_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_aksst_ds_w3$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:9], "NA->999")
kable(C)
```





```{r importOPAL_aksst3, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_aksst_ds_w3
save(mbirth, file = "../RData/aksst_w3/mbirth.RData")
rm(mbirth)

JSTAR_aksst_m_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_aksst_m_ds_w3$mbirth <- car::recode(JSTAR_aksst_m_ds_w3$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w3', JSTAR_aksst_m_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w3', project='_Athlos_Harm_Dataset')
```





## tn

### Wave 1 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_2cities` |
| **Description** |  |



```{r assign_tn1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_mbirth','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('k_001_3_g'), missings = TRUE)
opal.assign.table.tibble(o, 'JSTAR_tn_w1_id','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_000_b'), missings = TRUE)
JSTAR_tn_w2_mbirth <- opal.execute(o,'JSTAR_tn_w2_mbirth')
JSTAR_tn_w1_id <- opal.execute(o,'JSTAR_tn_w1_id')
```

```{r local_tn1, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], k_001_3_g=as.numeric(new_2[,2]))
  new_22
}

JSTAR_tn_w1_mbirth <- Add_indiv(old = JSTAR_tn_w2_mbirth, new = JSTAR_tn_w1_id)

vari <- JSTAR_tn_w1_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_mbirth$id)
JSTAR_tn_ds_w1$mbirth <- car::recode(JSTAR_tn_w1_mbirth$k_001_3_g, "NA=999")
JSTAR_tn_ds_w1$mbirth <- labelled(JSTAR_tn_ds_w1$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_tn1, echo=F}
vari <- JSTAR_tn_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn1, echo=F}
BeforeH <- c(table(JSTAR_tn_w1_mbirth$k_001_3_g), sum(is.na(JSTAR_tn_w1_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_tn_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:6], "NA->999")
kable(C)
```





```{r importOPAL_tn1, echo=F}

#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_tn_ds_w1
save(mbirth, file = "../RData/tn_w1/mbirth.RData")
rm(mbirth)

JSTAR_tn_m_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_tn_m_ds_w1$mbirth <- car::recode(JSTAR_tn_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w1', JSTAR_tn_m_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description

| **Name** | `k_001_3_g` |
|----------|------------|
| **Label** | `CORRECT BIRTH DATE OF THE RESPONDENT, MONTH` |
| **Table name** | `jstar_2011_2cities` |
| **Description** |  |




```{r assign_tn2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_mbirth','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('k_001_3_g'), missings = TRUE)
JSTAR_tn_w2_mbirth <- opal.execute(o,'JSTAR_tn_w2_mbirth')
```

```{r local_tn2, echo=F}
vari <- JSTAR_tn_w2_mbirth$k_001_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_mbirth, aes(x=factor(k_001_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_mbirth$id)
JSTAR_tn_ds_w2$mbirth <- car::recode(JSTAR_tn_w2_mbirth$k_001_3_g, "NA=999")
JSTAR_tn_ds_w2$mbirth <- labelled(JSTAR_tn_ds_w2$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_tn2, echo=F}
vari <- JSTAR_tn_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn2, echo=F}
BeforeH <- c(table(JSTAR_tn_w2_mbirth$k_001_3_g), sum(is.na(JSTAR_tn_w2_mbirth$k_001_3_g)))
AfterH <- table(JSTAR_tn_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:6], "NA->999")
kable(C)
```





```{r importOPAL_tn2, echo=F}

#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
mbirth <- JSTAR_tn_ds_w2
save(mbirth, file = "../RData/tn_w2/mbirth.RData")
rm(mbirth)

JSTAR_tn_m_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_tn_m_ds_w2$mbirth <- car::recode(JSTAR_tn_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w2', JSTAR_tn_m_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w2', project='_Athlos_Harm_Dataset')
```





## cth

### Wave 1 

There is no variable.




# Quality estimation

No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
