---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



# Data process


## aksst

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** | `jstar_2007_5cities` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign_aksst1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_age','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_aksst1, echo=F}
JSTAR_aksst_w1_age <- opal.execute(o,'JSTAR_aksst_w1_age')
vari <- JSTAR_aksst_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_age$id)
JSTAR_aksst_ds_w1$age <- car::recode(JSTAR_aksst_w1_age$respondent_age_year, "NA=999")
JSTAR_aksst_ds_w1$age <- labelled(JSTAR_aksst_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst1, echo=F}
vari <- JSTAR_aksst_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(46, 77)
```

#### Validation
```{r crosstabulation_aksst1, echo=F}
```





```{r importOPAL_aksst1, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
age <- JSTAR_aksst_ds_w1
save(age, file = "../RData/aksst_w1/age.RData")
rm(age)

JSTAR_aksst_m_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_aksst_m_ds_w1$age <- car::recode(JSTAR_aksst_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w1', JSTAR_aksst_m_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2009_5cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_aksst2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_age','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_aksst2, echo=F}
JSTAR_aksst_w2_age <- opal.execute(o,'JSTAR_aksst_w2_age')
vari <- JSTAR_aksst_w2_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2_age$id)
JSTAR_aksst_ds_w2$age <- car::recode(JSTAR_aksst_w2_age$respondent_age_year, "NA=999")
JSTAR_aksst_ds_w2$age <- labelled(JSTAR_aksst_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst2, echo=F}
vari <- JSTAR_aksst_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(52, 78)
```

#### Validation
```{r crosstabulation_aksst2, echo=F}
```





```{r importOPAL_aksst2, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
age <- JSTAR_aksst_ds_w2
save(age, file = "../RData/aksst_w2/age.RData")
rm(age)

JSTAR_aksst_m_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_aksst_m_ds_w2$age <- car::recode(JSTAR_aksst_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w2', JSTAR_aksst_m_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2011_5cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_aksst3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_age','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_aksst3, echo=F}
JSTAR_aksst_w3_age <- opal.execute(o,'JSTAR_aksst_w3_age')
vari <- JSTAR_aksst_w3_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3_age$id)
JSTAR_aksst_ds_w3$age <- car::recode(JSTAR_aksst_w3_age$respondent_age_year, "NA=999")
JSTAR_aksst_ds_w3$age <- labelled(JSTAR_aksst_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst3, echo=F}
vari <- JSTAR_aksst_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(54, 80)
```

#### Validation
```{r crosstabulation_aksst3, echo=F}
```





```{r importOPAL_aksst3, echo=F}

#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
age <- JSTAR_aksst_ds_w3
save(age, file = "../RData/aksst_w3/age.RData")
rm(age)

JSTAR_aksst_m_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_aksst_m_ds_w3$age <- car::recode(JSTAR_aksst_m_ds_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_aksst_m_ds_w3', JSTAR_aksst_m_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w3', project='_Athlos_Harm_Dataset')
```





## tn

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2009_2cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_tn1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_age','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_tn1, echo=F}
JSTAR_tn_w1_age <- opal.execute(o,'JSTAR_tn_w1_age')
vari <- JSTAR_tn_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_age$id)
JSTAR_tn_ds_w1$age <- car::recode(JSTAR_tn_w1_age$respondent_age_year, "NA=999")
JSTAR_tn_ds_w1$age <- labelled(JSTAR_tn_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_tn1, echo=F}
vari <- JSTAR_tn_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_tn_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(50, 76)
```

#### Validation
```{r crosstabulation_tn1, echo=F}
```





```{r importOPAL_tn1, echo=F}

#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
age <- JSTAR_tn_ds_w1
save(age, file = "../RData/tn_w1/age.RData")
rm(age)

JSTAR_tn_m_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_tn_m_ds_w1$age <- car::recode(JSTAR_tn_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w1', JSTAR_tn_m_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2011_2cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_tn2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_age','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_tn2, echo=F}
JSTAR_tn_w2_age <- opal.execute(o,'JSTAR_tn_w2_age')
vari <- JSTAR_tn_w2_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2_age$id)
JSTAR_tn_ds_w2$age <- car::recode(JSTAR_tn_w2_age$respondent_age_year, "NA=999")
JSTAR_tn_ds_w2$age <- labelled(JSTAR_tn_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_tn2, echo=F}
vari <- JSTAR_tn_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_tn_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(52, 78)
```

#### Validation
```{r crosstabulation_tn2, echo=F}
```





```{r importOPAL_tn2, echo=F}

#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
age <- JSTAR_tn_ds_w2
save(age, file = "../RData/tn_w2/age.RData")
rm(age)

JSTAR_tn_m_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_tn_m_ds_w2$age <- car::recode(JSTAR_tn_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_tn_m_ds_w2', JSTAR_tn_m_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w2', project='_Athlos_Harm_Dataset')
```





## cth

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2011_3cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_cth1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_age','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('respondent_age_year'), missings = TRUE)
```

```{r local_cth1, echo=F}
JSTAR_cth_w1_age <- opal.execute(o,'JSTAR_cth_w1_age')
vari <- JSTAR_cth_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "respondent_age_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cth1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_age$id)
JSTAR_cth_ds_w1$age <- car::recode(JSTAR_cth_w1_age$respondent_age_year, "NA='999'")
JSTAR_cth_ds_w1$age <- labelled(JSTAR_cth_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cth1, echo=F}
vari <- JSTAR_cth_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_cth_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(48, 75)
```

#### Validation
```{r crosstabulation_cth1, echo=F}
```





```{r importOPAL_cth1, echo=F}

#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
age <- JSTAR_cth_ds_w1
save(age, file = "../RData/cth_w1/age.RData")
rm(age)

JSTAR_cth_m_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_cth_m_ds_w1$age <- car::recode(JSTAR_cth_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_cth_m_ds_w1', JSTAR_cth_m_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_m_ds_w1', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

