---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process


## aksst

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** | `jstar_2007_5cities` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign_aksst1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_age','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('respondent_age_year'), missings = TRUE)
JSTAR_aksst_w1_age <- opal.execute(o,'JSTAR_aksst_w1_age')

```

```{r local_aksst1, echo=F}
vari <- JSTAR_aksst_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst1}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_age$id)
JSTAR_ds_aksst_w1$age <- car::recode(JSTAR_aksst_w1_age$respondent_age_year, "NA=999")
JSTAR_ds_aksst_w1$age <- labelled(JSTAR_ds_aksst_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_aksst1, echo=F}
vari <- JSTAR_ds_aksst_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(46, 77)
```

#### Validation
```{r crosstabulation_aksst1, echo=F}

load(paste0(datafolder,"aksst_w1/ybirth",".RData"))
load(paste0(datafolder,"aksst_w1/yintw",".RData"))
JSTAR_aksst_w1_age <- left_join(JSTAR_aksst_w1_age,yintw, by="id")
JSTAR_aksst_w1_age <- left_join(JSTAR_aksst_w1_age,ybirth, by="id")
JSTAR_aksst_w1_age$ybirth <- car::recode(JSTAR_aksst_w1_age$ybirth, "miss_values_vector=NA")
JSTAR_aksst_w1_age$yintw <- car::recode(JSTAR_aksst_w1_age$yintw, "miss_values_vector=NA")
JSTAR_aksst_w1_age$cage <- JSTAR_aksst_w1_age$yintw-JSTAR_aksst_w1_age$ybirth
JSTAR_aksst_w1_age$diff <- abs(JSTAR_aksst_w1_age$respondent_age_year - JSTAR_aksst_w1_age$cage)
JSTAR_aksst_w1_age <- remove_val_labels(JSTAR_aksst_w1_age)
kable(frq(JSTAR_aksst_w1_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(JSTAR_aksst_w1_age[which(JSTAR_aksst_w1_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```










### Wave 2 

#### Study-specific variable description



| **Name** | `respondent_age_year` |`living_status`|
|-|-|-|
| **Label** | `RESPONDENT AGE YEAR` |`Living status`|
| **Table name** |`jstar_2009_5cities`|`jstar_aksst_w2_hd`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|  |
| **Description** |  |  |


```{r assign_aksst2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2_age','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('respondent_age_year'), missings = TRUE)
JSTAR_aksst_w2_age <- opal.execute(o,'JSTAR_aksst_w2_age')

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_HD.jstar_aksst_w2_hd', variables=list('living_status'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

JSTAR_aksst_w2_age <- left_join(JSTAR_aksst_w2_age,JSTAR_aksst_w2,by="id")

```

```{r local_aksst2, echo=F}
vari <- JSTAR_aksst_w2_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w2_age$living_status
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "living_status")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2_age, aes(living_status)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_aksst2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2_age$id)
JSTAR_ds_aksst_w2$age <- car::recode(JSTAR_aksst_w2_age$respondent_age_year, "NA=999")
JSTAR_ds_aksst_w2$age[which(JSTAR_aksst_w2_age$living_status %in% c(1,2))] <- 996

```

#### Statistics of the new harmonised variable
```{r descript_aksst2, echo=F}
vari <- JSTAR_ds_aksst_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(52, 78)
```

#### Validation
```{r crosstabulation_aksst2, echo=F}


load(paste0(datafolder,"aksst_w2/ybirth",".RData"))
load(paste0(datafolder,"aksst_w2/yintw",".RData"))
JSTAR_aksst_w2_age <- left_join(JSTAR_aksst_w2_age,yintw, by="id")
JSTAR_aksst_w2_age <- left_join(JSTAR_aksst_w2_age,ybirth, by="id")
JSTAR_aksst_w2_age$ybirth <- car::recode(JSTAR_aksst_w2_age$ybirth, "miss_values_vector=NA")
JSTAR_aksst_w2_age$yintw <- car::recode(JSTAR_aksst_w2_age$yintw, "miss_values_vector=NA")
JSTAR_aksst_w2_age$cage <- JSTAR_aksst_w2_age$yintw-JSTAR_aksst_w2_age$ybirth
JSTAR_aksst_w2_age$diff <- abs(JSTAR_aksst_w2_age$respondent_age_year - JSTAR_aksst_w2_age$cage)
JSTAR_aksst_w2_age <- remove_val_labels(JSTAR_aksst_w2_age)
kable(frq(JSTAR_aksst_w2_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(JSTAR_aksst_w2_age[which(JSTAR_aksst_w2_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```






### Wave 3 

#### Study-specific variable description



| **Name** | `respondent_age_year` |`living_status`|
|-|-|-|
| **Label** | `RESPONDENT AGE YEAR` |`Living status`|
| **Table name** |`jstar_2011_5cities`|`jstar_aksst_w3_hd`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|  |
| **Description** |  |  |


```{r assign_aksst3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3_age','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('respondent_age_year'), missings = TRUE)
JSTAR_aksst_w3_age <- opal.execute(o,'JSTAR_aksst_w3_age')

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_HD.jstar_aksst_w3_hd', variables=list('living_status'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

JSTAR_aksst_w3_age <- left_join(JSTAR_aksst_w3_age,JSTAR_aksst_w3,by="id")
```

```{r local_aksst3, echo=F}
vari <- JSTAR_aksst_w3_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_aksst_w3_age$living_status
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "living_status")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3_age, aes(living_status)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_aksst3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3_age$id)
JSTAR_ds_aksst_w3$age <- car::recode(JSTAR_aksst_w3_age$respondent_age_year, "NA=999")
JSTAR_ds_aksst_w3$age[which(JSTAR_aksst_w3_age$living_status %in% c(1,2))] <- 996
```

#### Statistics of the new harmonised variable
```{r descript_aksst3, echo=F}
vari <- JSTAR_ds_aksst_w3$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(54, 80)
```

#### Validation
```{r crosstabulation_aksst3, echo=F}


load(paste0(datafolder,"aksst_w3/ybirth",".RData"))
load(paste0(datafolder,"aksst_w3/yintw",".RData"))
JSTAR_aksst_w3_age <- left_join(JSTAR_aksst_w3_age,yintw, by="id")
JSTAR_aksst_w3_age <- left_join(JSTAR_aksst_w3_age,ybirth, by="id")
JSTAR_aksst_w3_age$ybirth <- car::recode(JSTAR_aksst_w3_age$ybirth, "miss_values_vector=NA")
JSTAR_aksst_w3_age$yintw <- car::recode(JSTAR_aksst_w3_age$yintw, "miss_values_vector=NA")
JSTAR_aksst_w3_age$cage <- JSTAR_aksst_w3_age$yintw-JSTAR_aksst_w3_age$ybirth
JSTAR_aksst_w3_age$diff <- abs(JSTAR_aksst_w3_age$respondent_age_year - JSTAR_aksst_w3_age$cage)
JSTAR_aksst_w3_age <- remove_val_labels(JSTAR_aksst_w3_age)
kable(frq(JSTAR_aksst_w3_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(JSTAR_aksst_w3_age[which(JSTAR_aksst_w3_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```






## tn

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2009_2cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_tn1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_age','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('respondent_age_year'), missings = TRUE)
JSTAR_tn_w1_age <- opal.execute(o,'JSTAR_tn_w1_age')
```

```{r local_tn1, echo=F}
vari <- JSTAR_tn_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_tn1}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_age$id)
JSTAR_ds_tn_w1$age <- car::recode(JSTAR_tn_w1_age$respondent_age_year, "NA=999")
JSTAR_ds_tn_w1$age <- labelled(JSTAR_ds_tn_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_tn1, echo=F}
vari <- JSTAR_ds_tn_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(50, 76)
```

#### Validation
```{r crosstabulation_tn1, echo=F}

load(paste0(datafolder,"tn_w1/ybirth",".RData"))
load(paste0(datafolder,"tn_w1/yintw",".RData"))
JSTAR_tn_w1_age <- left_join(JSTAR_tn_w1_age,yintw, by="id")
JSTAR_tn_w1_age <- left_join(JSTAR_tn_w1_age,ybirth, by="id")
JSTAR_tn_w1_age$ybirth <- car::recode(JSTAR_tn_w1_age$ybirth, "miss_values_vector=NA")
JSTAR_tn_w1_age$yintw <- car::recode(JSTAR_tn_w1_age$yintw, "miss_values_vector=NA")
JSTAR_tn_w1_age$cage <- JSTAR_tn_w1_age$yintw-JSTAR_tn_w1_age$ybirth
JSTAR_tn_w1_age$diff <- abs(JSTAR_tn_w1_age$respondent_age_year - JSTAR_tn_w1_age$cage)
JSTAR_tn_w1_age <- remove_val_labels(JSTAR_tn_w1_age)
kable(frq(JSTAR_tn_w1_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')

```







### Wave 2 

#### Study-specific variable description



| **Name** | `respondent_age_year` |
|-|-|
| **Label** | `RESPONDENT AGE YEAR` |
| **Table name** |`jstar_2011_2cities`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_tn2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2_age','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('respondent_age_year'), missings = TRUE)
JSTAR_tn_w2_age <- opal.execute(o,'JSTAR_tn_w2_age')

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_HD.jstar_tn_w2_hd', variables=list('living_status'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

JSTAR_tn_w2_age <- left_join(JSTAR_tn_w2_age,JSTAR_tn_w2,by="id")

```

```{r local_tn2, echo=F}
vari <- JSTAR_tn_w2_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_tn_w2_age$living_status
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "living_status")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2_age, aes(living_status)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_tn2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2_age$id)
JSTAR_ds_tn_w2$age <- car::recode(JSTAR_tn_w2_age$respondent_age_year, "NA=999")
JSTAR_ds_tn_w2$age[which(JSTAR_tn_w2_age$living_status %in% c(1,2))] <- 996
```

#### Statistics of the new harmonised variable
```{r descript_tn2, echo=F}
vari <- JSTAR_ds_tn_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(52, 78)
```

#### Validation
```{r crosstabulation_tn2, echo=F}


load(paste0(datafolder,"tn_w2/ybirth",".RData"))
load(paste0(datafolder,"tn_w2/yintw",".RData"))
JSTAR_tn_w2_age <- left_join(JSTAR_tn_w2_age,yintw, by="id")
JSTAR_tn_w2_age <- left_join(JSTAR_tn_w2_age,ybirth, by="id")
JSTAR_tn_w2_age$ybirth <- car::recode(JSTAR_tn_w2_age$ybirth, "miss_values_vector=NA")
JSTAR_tn_w2_age$yintw <- car::recode(JSTAR_tn_w2_age$yintw, "miss_values_vector=NA")
JSTAR_tn_w2_age$cage <- JSTAR_tn_w2_age$yintw-JSTAR_tn_w2_age$ybirth
JSTAR_tn_w2_age$diff <- abs(JSTAR_tn_w2_age$respondent_age_year - JSTAR_tn_w2_age$cage)
JSTAR_tn_w2_age <- remove_val_labels(JSTAR_tn_w2_age)
kable(frq(JSTAR_tn_w2_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')

```






## cth

### Wave 1 

#### Study-specific variable description



| **Name** | `respondent_age_year` |`ybirth`|`yintw`|
|-|-|-|-|
| **Label** | `RESPONDENT AGE YEAR` |`Year of birth`|`Year of interview`|
| **Table name** |`jstar_2011_3cities`|`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|
| **Missings** |`NA`|  |  |
| **Description** |  |  |  |


```{r assign_cth1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_age','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('respondent_age_year'), missings = TRUE)
JSTAR_cth_w1_age <- opal.execute(o,'JSTAR_cth_w1_age')

opal.assign.table.tibble(o, 'JSTAR_cth_w1_yb','JSTAR_HD.jstar_cth_w1_hd', variables=list('ybirth','yintw'), missings = TRUE)
JSTAR_cth_w1_yb <- opal.execute(o,'JSTAR_cth_w1_yb')

JSTAR_cth_w1_age <- left_join(JSTAR_cth_w1_age,JSTAR_cth_w1_yb)

```

```{r local_cth1, echo=F}
vari <- JSTAR_cth_w1_age$respondent_age_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1_age, aes(respondent_age_year)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 

vari <- JSTAR_cth_w1_age$ybirth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1_age, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 

vari <- JSTAR_cth_w1_age$yintw
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "yintw")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Summary")
ggplot(JSTAR_cth_w1_age, aes(factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cth1}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_age$id)
JSTAR_ds_cth_w1$age <- car::recode(JSTAR_cth_w1_age$respondent_age_year, "NA='999'")
JSTAR_ds_cth_w1$age[which(JSTAR_ds_cth_w1$age %in% miss_values_vector)] <- JSTAR_cth_w1_age$yintw[which(JSTAR_ds_cth_w1$age %in% miss_values_vector)] - JSTAR_cth_w1_age$ybirth[which(JSTAR_ds_cth_w1$age %in% miss_values_vector)]
JSTAR_ds_cth_w1$age <- labelled(JSTAR_ds_cth_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cth1, echo=F}
vari <- JSTAR_ds_cth_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(48, 75)
```

#### Validation
```{r crosstabulation_cth1, echo=F}

JSTAR_cth_w1_age$ybirth <- car::recode(JSTAR_cth_w1_age$ybirth, "miss_values_vector=NA")
JSTAR_cth_w1_age$yintw <- car::recode(JSTAR_cth_w1_age$yintw, "miss_values_vector=NA")
JSTAR_cth_w1_age$cage <- JSTAR_cth_w1_age$yintw-JSTAR_cth_w1_age$ybirth
JSTAR_cth_w1_age$diff <- abs(JSTAR_cth_w1_age$respondent_age_year - JSTAR_cth_w1_age$cage)
JSTAR_cth_w1_age <- remove_val_labels(JSTAR_cth_w1_age)
kable(frq(JSTAR_cth_w1_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')

```










## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```













# Quality estimation
Individuals with incompatible data are specified at each validation.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

