---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```




<!-- ########################################################## --> 

# Data process


## aksst 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2007_5cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign_aksst1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_sex','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_aksst_w1_sex <- opal.execute(o,'JSTAR_aksst_w1_sex')
```

```{r local_aksst1, echo=FALSE}
vari <- JSTAR_aksst_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_aksst1, echo=TRUE}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1_sex$id)
JSTAR_ds_aksst_w1$sex <- car::recode(JSTAR_aksst_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=FALSE}
vari <- JSTAR_ds_aksst_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst1, echo=FALSE}
AfterH <- table(JSTAR_ds_aksst_w1$sex)
BeforeH <- c(table(JSTAR_aksst_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_aksst_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```








### Wave 2 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2007_5cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |
 
 
```{r assign_aksst2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_sex','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_aksst_w1_sex <- opal.execute(o,'JSTAR_aksst_w1_sex')
```

```{r local_aksst2, echo=FALSE}
vari <- JSTAR_aksst_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_aksst2, echo=TRUE}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w1_sex$id)
JSTAR_ds_aksst_w2$sex <- car::recode(JSTAR_aksst_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=FALSE}
vari <- JSTAR_ds_aksst_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst2, echo=FALSE}
AfterH <- table(JSTAR_ds_aksst_w2$sex)
BeforeH <- c(table(JSTAR_aksst_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_aksst_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```










### Wave 3 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2007_5cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign_aksst3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_sex','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_aksst_w1_sex <- opal.execute(o,'JSTAR_aksst_w1_sex')
```

```{r local_aksst3, echo=FALSE}
vari <- JSTAR_aksst_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_aksst3, echo=TRUE}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w1_sex$id)
JSTAR_ds_aksst_w3$sex <- car::recode(JSTAR_aksst_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_ds_aksst_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst3, echo=FALSE}
AfterH <- table(JSTAR_ds_aksst_w3$sex)
BeforeH <- c(table(JSTAR_aksst_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_aksst_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```






## tn 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2009_2cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign_tn1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_sex','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_tn_w1_sex <- opal.execute(o,'JSTAR_tn_w1_sex')
```

```{r local_tn1, echo=FALSE}
vari <- JSTAR_tn_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_tn1, echo=TRUE}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1_sex$id)
JSTAR_ds_tn_w1$sex <- car::recode(JSTAR_tn_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_tn1, echo=FALSE}
vari <- JSTAR_ds_tn_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn1, echo=FALSE}
AfterH <- table(JSTAR_ds_tn_w1$sex)
BeforeH <- c(table(JSTAR_tn_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_tn_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```








### Wave 2 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2009_2cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign_tn2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_sex','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_tn_w1_sex <- opal.execute(o,'JSTAR_tn_w1_sex')
```

```{r local_tn2, echo=FALSE}
vari <- JSTAR_tn_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_tn2, echo=TRUE}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w1_sex$id)
JSTAR_ds_tn_w2$sex <- car::recode(JSTAR_tn_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_ds_tn_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn2, echo=FALSE}
AfterH <- table(JSTAR_ds_tn_w2$sex)
BeforeH <- c(table(JSTAR_tn_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_tn_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```







## cth 

### Wave 1 

#### Study-specific variable description

 

| **Name** | `a_000_0`|
|-|-|
| **Label** | `SEX`|
| **Table name** |`jstar_2011_3cities`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign_cth1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_sex','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_cth_w1_sex <- opal.execute(o,'JSTAR_cth_w1_sex')
```

```{r local_cth1, echo=FALSE}
vari <- JSTAR_cth_w1_sex$a_000_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1_sex, aes(x=factor(a_000_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`

**R script:**

```{r harmo_cth1, echo=TRUE}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1_sex$id)
JSTAR_ds_cth_w1$sex <- car::recode(JSTAR_cth_w1_sex$a_000_0, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=FALSE}
vari <- JSTAR_ds_cth_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cth1, echo=FALSE}
AfterH <- table(JSTAR_ds_cth_w1$sex)
BeforeH <- c(table(JSTAR_cth_w1_sex$a_000_0)[c(2,1)], sum(is.na(JSTAR_cth_w1_sex$a_000_0)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```



```{r helpfunctions, echo=F}
source("../../helpfunctions.r")
```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:



```{r summ, echo=F}
# All study waves and populations with abbreviated and descriptive names
jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))
# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))
if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}
m.hds <- list()
lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)
if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```