---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## aksst 
### Wave 1 

#### Study-specific variable description

 

* Name: `a_002_a`
* Label: `HIGHEST SCHOOL`
* Categories: 
    + `1 = elementary/middle school`
    + `2 = high school (including old-system middle school, girls' school, trade school, normal school)`
    + `3 = junior college (including technical high school, etc.)`
    + `4 = vocational school`
    + `5 = university (including old-system high school, old-system technical college)`
    + `6 = graduate school (Master's)`
    + `7 = graduate school (Ph.D)`
    + `8 = other`
* Missings: 
    + `9 = don't know`
    + `10 = refused to answer`

    
* Description: 
```{r assign_aksst1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1_educ','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_002_a'), missings = TRUE)
```

```{r local_aksst1,  echo=FALSE}
JSTAR_aksst_w1_educ <- opal.execute(o,'JSTAR_aksst_w1_educ')
vari <- JSTAR_aksst_w1_educ$a_002_a
kable(Categorical_summary(vari, missing_values = c(9, 10))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9, 10))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9, 10))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_w1_educ$a_002_a, missing_values = c(9,10))
ggplot(JSTAR_aksst_w1_educ, aes(x=factor(a_002_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "elementary/middle school" into 1`
* `keep "high school (including old-system middle school, girls' school, trade school, normal school)" into 2`
* `recode 3 "junior college (including technical high school, etc.)" into 2`
* `recode 4 "vocational school" into 2`
* `recode 5 "university (including old-system high school, old-system technical college)" into 3`
* `recode 6 "graduate school (Master's)" into 3`
* `recode 7 "graduate school (Ph.D)" into 3`
* `recode 8 "other" into 999`
* `recode 9 "don't know" into 998`
* `recode 10 "refused to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo_aksst1,   echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1_educ$id)
JSTAR_aksst_ds_w1$education <- car::recode(JSTAR_aksst_w1_educ$a_002_a, "3=2; 4=2; 5=3; 6=3; 7=3; 8=999; 9=998; 10=997;  NA=999")
JSTAR_aksst_ds_w1$education <- labelled(JSTAR_aksst_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1,  echo=FALSE}
vari <- JSTAR_aksst_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_aksst1,  echo=FALSE}
BeforeH <- table(JSTAR_aksst_w1_educ$a_002_a)
BeforeH <- c(BeforeH[1], sum(BeforeH[2:4]),sum(BeforeH[5:7]), BeforeH[10], BeforeH[9], sum( BeforeH[8],sum(is.na(JSTAR_aksst_w1_educ$a_002_a))))
AfterH <- table(JSTAR_aksst_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "(2,3,4)->2", "(5,6,7)->3", "10->997", "9->998", "(8,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL_aksst1,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w1) <- NULL
opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
education <- JSTAR_aksst_ds_w1
save(education, file = "../RData/aksst_w1/education.RData")
rm(education)

JSTAR_aksst_m_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_aksst_m_ds_w1$education <- car::recode(JSTAR_aksst_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_aksst_m_ds_w1', JSTAR_aksst_m_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

There is no variable.


### Wave 3 

There is no variable.




## tn 
### Wave 1 

#### Study-specific variable description

 

* Name: `a_002_1`
* Label: `HIGHEST SCHOOL`
* Categories: 
    + `1 = Elementary/middle school`
    + `2 = High school (including old-system middle school, girls' school, trade school, normal school)`
    + `3 = Junior college (including technical high school, etc.)`
    + `4 = Vocational school`
    + `5 = University (including old-system high school, old-system technical college)`
    + `6 = Graduate school (Master's)`
    + `7 = Graduate school (Ph.D)`
    + `8 = Other`
* Missings: 
    + `9 = Don't know`
    + `10 = Refused to answer`

* Description: 
```{r assign_tn1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_tn_w1_educ','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_002_1'), missings = TRUE)
```

```{r local_tn1,  echo=FALSE}
JSTAR_tn_w1_educ <- opal.execute(o,'JSTAR_tn_w1_educ')
vari <- JSTAR_tn_w1_educ$a_002_1
kable(Categorical_summary(vari, missing_values = c(9, 10))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(9, 10))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9, 10))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_w1_educ$a_002_1, missing_values = c(9,10))
ggplot(JSTAR_tn_w1_educ, aes(x=factor(a_002_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "elementary/middle school" into 1`
* `keep "high school (including old-system middle school, girls' school, trade school, normal school)" into 2`
* `recode 3 "junior college (including technical high school, etc.)" into 2`
* `recode 4 "vocational school" into 2`
* `recode 5 "university (including old-system high school, old-system technical college)" into 3`
* `recode 6 "graduate school (Master's)" into 3`
* `recode 7 "graduate school (Ph.D)" into 3`
* `recode 8 "other" into 999`
* `recode 9 "don't know" into 998`
* `recode 10 "refused to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo_tn1,   echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1_educ$id)
JSTAR_tn_ds_w1$education <- car::recode(JSTAR_tn_w1_educ$a_002_1, "3=2; 4=2; 5=3; 6=3; 7=3; 8=999; 9=998; 10=997;  NA=999")
JSTAR_tn_ds_w1$education <- labelled(JSTAR_tn_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_tn1,  echo=FALSE}
vari <- JSTAR_tn_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_tn1,  echo=FALSE}
BeforeH <- table(JSTAR_tn_w1_educ$a_002_1)
BeforeH <- c(BeforeH[1], sum(BeforeH[2:4]),sum(BeforeH[5:7]), BeforeH[10], BeforeH[9], sum( BeforeH[8],sum(is.na(JSTAR_tn_w1_educ$a_002_1))))
AfterH <- table(JSTAR_tn_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "(2,3,4)->2", "(5,6,7)->3", "10->997", "9->998", "(8,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL_tn1,  echo=FALSE}
val_labels(JSTAR_tn_ds_w1) <- NULL
opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
education <- JSTAR_tn_ds_w1
save(education, file = "../RData/tn_w1/education.RData")
rm(education)

JSTAR_tn_m_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_tn_m_ds_w1$education <- car::recode(JSTAR_tn_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_tn_m_ds_w1', JSTAR_tn_m_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

There is no variable.



## cth 
### Wave 1 

#### Study-specific variable description

 

* Name: `a_002_1`
* Label: `HIGHEST SCHOOL`
* Categories: 
    + `1 = Elementary/middle school`
    + `2 = High school (including old-system middle school, girls' school, trade school, normal school)`
    + `3 = Junior college (including technical high school, etc.)`
    + `4 = Vocational school`
    + `5 = University (including old-system high school, old-system technical college)`
    + `6 = Graduate school (Master's)`
    + `7 = Graduate school (Ph.D)`
    + `8 = Other`
* Missings: 
    + `9 = Don't know`
    + `10 = Refused to answer`

* Description: 
```{r assign_cth1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_cth_w1_educ','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_002_1'), missings = TRUE)
```

```{r local_cth1,  echo=FALSE}
JSTAR_cth_w1_educ <- opal.execute(o,'JSTAR_cth_w1_educ')
vari <- JSTAR_cth_w1_educ$a_002_1
kable(Categorical_summary(vari, missing_values = c(9, 10))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(9, 10))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9, 10))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_w1_educ$a_002_1, missing_values = c(9,10))
ggplot(JSTAR_cth_w1_educ, aes(x=factor(a_002_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "elementary/middle school" into 1`
* `keep "high school (including old-system middle school, girls' school, trade school, normal school)" into 2`
* `recode 3 "junior college (including technical high school, etc.)" into 2`
* `recode 4 "vocational school" into 2`
* `recode 5 "university (including old-system high school, old-system technical college)" into 3`
* `recode 6 "graduate school (Master's)" into 3`
* `recode 7 "graduate school (Ph.D)" into 3`
* `recode 8 "other" into 999`
* `recode 9 "don't know" into 998`
* `recode 10 "refused to answer" into 997`
* `recode NA into 999`

**R script:**

```{r harmo_cth1,   echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1_educ$id)
JSTAR_cth_ds_w1$education <- car::recode(JSTAR_cth_w1_educ$a_002_1, "3=2; 4=2; 5=3; 6=3; 7=3; 8=999; 9=998; 10=997;  NA=999")
JSTAR_cth_ds_w1$education <- labelled(JSTAR_cth_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cth1,  echo=FALSE}
vari <- JSTAR_cth_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cth1,  echo=FALSE}
BeforeH <- table(JSTAR_cth_w1_educ$a_002_1)
BeforeH <- c(BeforeH[1], sum(BeforeH[2:4]),sum(BeforeH[5:7]), BeforeH[10], BeforeH[9], sum( BeforeH[8],sum(is.na(JSTAR_cth_w1_educ$a_002_1))))
AfterH <- table(JSTAR_cth_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "(2,3,4)->2", "(5,6,7)->3", "10->997", "9->998", "(8,NA)->999")
kable(C)
```

 
 

 
```{r importOPAL_cth1,  echo=FALSE}
val_labels(JSTAR_cth_ds_w1) <- NULL
opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
education <- JSTAR_cth_ds_w1
save(education, file = "../RData/cth_w1/education.RData")
rm(education)

JSTAR_cth_m_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_cth_m_ds_w1$education <- car::recode(JSTAR_cth_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_cth_m_ds_w1', JSTAR_cth_m_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_m_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```

