---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_024`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENT JOB`|`C-024:FREQUENCY OF PAYMENT`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Self-employed, so Don't receive pay`<br/>`5 = Other (Describe: )`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('c_000','c_001','c_024'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable `c_001`, it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_024 == 4 into 0`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$employed <- car::recode(JSTAR_aksst_w1$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_aksst_w1$employed[which(JSTAR_aksst_w1$c_000==2)] <- 997
JSTAR_ds_aksst_w1$employed[which(JSTAR_aksst_w1$c_024==4)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `c_000` | `c_001` |`c_014`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C1`|`C-001:CURRENTLY WORKING`|`C-014:HOW THE WAGE IS CALCULATED`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`| `jstar_2009_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly wage`<br/>`2 = Daily wage`<br/>`3 = Monthly salary`<br/>`4 = Percentage payment/piece rate wage (specify)`<br/>`5 = Other ways of payment (specify)`<br/>`6 = Not paid because self-employed`<br/>`7 = Don't know`<br/>`8 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('c_000','c_001','c_014'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_014')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable `c_001`, it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_014 == 6 into 0`

**R script:**

```{r harmo aksst_w2}

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$employed <- car::recode(JSTAR_aksst_w2$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_aksst_w2$employed[which(JSTAR_aksst_w2$c_000==2)] <- 997
JSTAR_ds_aksst_w2$employed[which(JSTAR_aksst_w2$c_014==6)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

```



### Wave 3


#### Study-specific variable description


| **Name** | `c_000` | `c_001` |`c_014`|
|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-014:HOW THE WAGE IS CALCULATED`|
| **Table name**  | `jstar_2011_5cities`| `jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Yearly`<br/>`5 = On a percentage commission or piece rate basis`<br/>`6 = Other calculation method (Specify:)`<br/>`7 = Self-employed and receiving no wage`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('c_000','c_001','c_014'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_014 == 7 into 0`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$employed <- car::recode(JSTAR_aksst_w3$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_aksst_w3$employed[which(JSTAR_aksst_w3$c_014==7)] <- 0
JSTAR_ds_aksst_w3$employed[which(JSTAR_aksst_w3$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_024`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-024:HOW THE WAGE IS CALCULATED`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Self-employed, so don't receive pay`<br/>`5 = Other (Describe: )`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |


```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('c_000','c_001','c_024'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_024 == 4 into 0`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$employed <- car::recode(JSTAR_tn_w1$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_tn_w1$employed[which(JSTAR_tn_w1$c_024==4)] <- 0
JSTAR_ds_tn_w1$employed[which(JSTAR_tn_w1$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `c_000` | `c_001` |`c_014`|
|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-014:HOW THE WAGE IS CALCULATED`|
| **Table name**  | `jstar_2011_2cities`| `jstar_2011_2cities`| `jstar_2011_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Yearly`<br/>`5 = On a percentage commission or piece rate basis`<br/>`6 = Other calculation method (Specify:)`<br/>`7 = Self-employed and receiving no wage`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('c_000','c_001','c_014'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_014 == 7 into 0`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$employed <- car::recode(JSTAR_tn_w2$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_tn_w2$employed[which(JSTAR_tn_w2$c_000==2)] <- 997
JSTAR_ds_tn_w2$employed[which(JSTAR_tn_w2$c_014==7)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}


```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_024`|
|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-024:HOW THE WAGE IS CALCULATED`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly wage`<br/>`2 = Daily wage`<br/>`3 = Monthly salary`<br/>`4 = Yearly salary`<br/>`5 = Percentage payment/piece rate wage (specify)`<br/>`6 = Other ways of payment (specify)`<br/>`7 = Not paid because self-employed`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('c_000','c_001','c_024'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `3 into 0`
* `1,2 into 1`
* `4 into 998`
* `5 into 997`
* `NA into 999`
* `c_000 == 2 into 997`
* `c_024 == 7 into 0`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$employed <- car::recode(JSTAR_cth_w1$c_001,"c(1,2) = 1; 3 = 0; 4 = 998; 5 = 997; NA=999")
JSTAR_ds_cth_w1$employed[which(JSTAR_cth_w1$c_000==2)] <- 997
JSTAR_ds_cth_w1$employed[which(JSTAR_cth_w1$c_024==7)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}


```








## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W1", "AKSST_W2", "AKSST_W3", "TN_W1", "TN_W2", "CTH_W1")
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  employed <- l.hds[[index]]
  save(employed, file = paste0(datafolder,names(l.hds)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





