---
title: "Non paid work"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/nonpaid_workDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/nonpaid_workDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_034`|`c_024`|`c_002`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENT JOB`|`C-034:CURRENT SITUATION`|`C-024:FREQUENCY OF PAYMENT`|`C-002:CURRENT JOB SITUATION`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`| `jstar_2007_5cities`|`jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Self-employed, so Don't receive pay`<br/>`5 = Other (Describe: )`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|`1 = Employee (including public employees)`<br/>`2 = Executive of company or organization`<br/>`3 = Owner of independent business`<br/>`4 = Helps in independent business`<br/>`5 = Side job at home`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|
| **Missings** | `NA` | `NA` |`NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('c_000','c_001','c_034','c_024','c_002'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_024')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable, it has to be recoded as follows:

* `c_034 == 1,3,4 into 996`
* `c_034 == 2 into 1`
* `c_024 == 4 and c_002 == 3 into 2`
* `c_024 == 4 and c_002 != 3 and c_034 != 2 into 3`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_024 != 4 into 996`
* `c_000 == 2 into 997`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$nonpaid_work <- car::recode(JSTAR_aksst_w1$c_034,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w1$nonpaid_work[which(JSTAR_aksst_w1$c_001 %in% c(1,2))] <- 996
JSTAR_ds_aksst_w1$nonpaid_work[which(JSTAR_aksst_w1$c_024==4 & JSTAR_aksst_w1$c_002==3)] <- 2
JSTAR_ds_aksst_w1$nonpaid_work[which(JSTAR_aksst_w1$c_024==4 & JSTAR_aksst_w1$c_002!=3 & JSTAR_aksst_w1$c_034!=2)] <- 3
JSTAR_ds_aksst_w1$nonpaid_work[which(JSTAR_aksst_w1$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `c_000` | `c_001` |`c_035`|`c_014`|`c_004`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C1`|`C-001:CURRENTLY WORKING`|`C-035:CURRENT SITUATION`|`C-014:HOW THE WAGE IS CALCULATED`|`C-004:CURRENT JOB SITUATION`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`| `jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Hourly wage`<br/>`2 = Daily wage`<br/>`3 = Monthly salary`<br/>`4 = Percentage payment/piece rate wage (specify)`<br/>`5 = Other ways of payment (specify)`<br/>`6 = Not paid because self-employed`<br/>`7 = Don't know`<br/>`8 = Refused to answer`|`1 = Employee (including public employees)`<br/>`2 = Executive of company or organization`<br/>`3 = Owner of independent business`<br/>`4 = Helps in independent business`<br/>`5 = Side job at home`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('c_000','c_001','c_035','c_014','c_004'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_004
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_004')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_014')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable `c_001`, it has to be recoded as follows:

* `c_035 == 1,3,4 into 996`
* `c_035 == 2 into 1`
* `c_014 == 6 and c_004 == 3 into 2`
* `c_014 == 6 and c_004 != 3 into 3`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_014 != 6 into 996`
* `c_000 == 2 into 997`

<!--
* `c_014 == 4 and c_004 == 5 into 1`
#JSTAR_ds_aksst_w2$nonpaid_work[which(JSTAR_aksst_w2$c_014==4 & JSTAR_aksst_w2$c_004==5)] <- 1
-->

**R script:**

```{r harmo aksst_w2}

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$nonpaid_work <- car::recode(JSTAR_aksst_w2$c_035,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w2$nonpaid_work[which(JSTAR_aksst_w2$c_001 %in% c(1,2))] <- 996
JSTAR_ds_aksst_w2$nonpaid_work[which(JSTAR_aksst_w2$c_014==6 & JSTAR_aksst_w2$c_004==3)] <- 2
JSTAR_ds_aksst_w2$nonpaid_work[which(JSTAR_aksst_w2$c_014==6 & !JSTAR_aksst_w2$c_004 %in% c(3))] <- 3
JSTAR_ds_aksst_w2$nonpaid_work[which(JSTAR_aksst_w2$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

```



### Wave 3


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_035`|`c_014`|`c_004`|
|-|-|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-035:CURRENT SITUATION`|`11C-014:HOW THE WAGE IS CALCULATED`|`11C-004:FORM OF EMPLOYMENT`|
| **Table name**  | `jstar_2011_5cities`| `jstar_2011_5cities`|`jstar_2011_5cities`| `jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Homemaker`<br/>`3 = Taking a rest due to illness, injuries, etc.`<br/>`4 = Other (Specify:)`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Yearly`<br/>`5 = On a percentage commission or piece rate basis`<br/>`6 = Other calculation method (Specify:)`<br/>`7 = Self-employed and receiving no wage`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|`1 = Working as an employee at a company, organization, public agency, etc.`<br/>`2 = Serving as an executive of a company, organization, etc.`<br/>`3 = Running own business`<br/>`4 = Helping run family business`<br/>`5 = Working from home`<br/>`6 = Performing tasks upon request from the senior human resource center at which the respondent is registered`<br/>`7 = Performing tasks on an as-needed basis when requested by neighbors, companies, etc.`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |


```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('c_000','c_001','c_035','c_014','c_004'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_004
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_004')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_014')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `c_035 == 1,3,4 into 996`
* `c_035 == 2 into 1`
* `c_014 == 7 and c_004 == 3,4 into 2`
* `c_014 == 7 and c_004 != 3,4 into 3`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_014 != 7 into 996`
* `c_000 == 2 into 997`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$nonpaid_work <- car::recode(JSTAR_aksst_w3$c_035,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_aksst_w3$nonpaid_work[which(JSTAR_aksst_w3$c_001 %in% c(1,2))] <- 996
JSTAR_ds_aksst_w3$nonpaid_work[which(JSTAR_aksst_w3$c_014==7 & JSTAR_aksst_w3$c_004 %in% c(3,4))] <- 2
JSTAR_ds_aksst_w3$nonpaid_work[which(JSTAR_aksst_w3$c_014==7 & !JSTAR_aksst_w3$c_004 %in% c(3,4))] <- 3
JSTAR_ds_aksst_w3$nonpaid_work[which(JSTAR_aksst_w3$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_034`|`c_024`|`c_002`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-034:CURRENT SITUATION`|`C-024:HOW THE WAGE IS CALCULATED`|`C-002:CURRENT JOB SITUATION`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|`jstar_2009_2cities`| `jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Self-employed, so don't receive pay`<br/>`5 = Other (Describe: )`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|`1 = Employee (including public employees)`<br/>`2 = Executive of company or organization`<br/>`3 = Owner of independent business`<br/>`4 = Helps in independent business`<br/>`5 = Side job at home`<br/>`6 = Don't know`<br/>`7 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` |  `NA` | `NA` |
| **Description** |  |  |  |  |  |


```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('c_000','c_001','c_034','c_024','c_002'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_024')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `c_034 == 1,3,4 into 996`
* `c_034 == 2 into 1`
* `c_024 == 4 and c_002 == 3 into 2`
* `c_024 == 4 and c_002 != 3 into 3`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_024 != 4 into 996`
* `c_000 == 2 into 997`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$nonpaid_work <- car::recode(JSTAR_tn_w1$c_034,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_tn_w1$nonpaid_work[which(JSTAR_tn_w1$c_001 %in% c(1,2))] <- 996
JSTAR_ds_tn_w1$nonpaid_work[which(JSTAR_tn_w1$c_024==4 & JSTAR_tn_w1$c_002==3)] <- 2
JSTAR_ds_tn_w1$nonpaid_work[which(JSTAR_tn_w1$c_024==4 & JSTAR_tn_w1$c_002!=3)] <- 3
JSTAR_ds_tn_w1$nonpaid_work[which(JSTAR_tn_w1$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_035`|`c_014`|`c_004`|
|-|-|-|-|-|-|
| **Label** | `11C-000:CONTINUE SECTION C1`|`11C-001:CURRENT WORKING`|`11C-035:CURRENT SITUATION`|`11C-014:HOW THE WAGE IS CALCULATED`|`11C-004:FORM OF EMPLOYMENT`|
| **Table name**  | `jstar_2011_2cities`| `jstar_2011_2cities`|`jstar_2011_2cities`| `jstar_2011_2cities`|`jstar_2011_2cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Retired`<br/>`2 = Homemaker`<br/>`3 = Taking a rest due to illness, injuries, etc.`<br/>`4 = Other (Specify:)`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Hourly`<br/>`2 = Daily`<br/>`3 = Monthly`<br/>`4 = Yearly`<br/>`5 = On a percentage commission or piece rate basis`<br/>`6 = Other calculation method (Specify:)`<br/>`7 = Self-employed and receiving no wage`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|`1 = Working as an employee at a company, organization, public agency, etc.`<br/>`2 = Serving as an executive of a company, organization, etc.`<br/>`3 = Running own business`<br/>`4 = Helping run family business`<br/>`5 = Working from home`<br/>`6 = Performing tasks upon request from the senior human resource center at which the respondent is registered`<br/>`7 = Performing tasks on an as-needed basis when requested by neighbors, companies, etc.`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |


```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('c_000','c_001','c_014','c_035','c_004'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_004
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_004')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_014
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_014')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_014))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$c_035
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_035')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(c_035))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `c_035 == 1,3,4 into 996`
* `c_035 == 2 into 1`
* `c_014 == 7 and c_004 == 3,4 into 2`
* `c_014 == 7 and c_004 != 3,4 into 3`
* `c_035 == 5 into 998`
* `c_035 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_014 != 7 into 996`
* `c_000 == 2 into 997`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$nonpaid_work <- car::recode(JSTAR_tn_w2$c_035,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_tn_w2$nonpaid_work[which(JSTAR_tn_w2$c_001 %in% c(1,2))] <- 996
JSTAR_ds_tn_w2$nonpaid_work[which(JSTAR_tn_w2$c_014==7 & JSTAR_tn_w2$c_004 %in% c(3,4))] <- 2
JSTAR_ds_tn_w2$nonpaid_work[which(JSTAR_tn_w2$c_014==7 & !JSTAR_tn_w2$c_004 %in% c(3,4))] <- 3
JSTAR_ds_tn_w2$nonpaid_work[which(JSTAR_tn_w2$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}


```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `c_000` | `c_001` |`c_024`|`c_034`|`c_002`|
|-|-|-|-|-|-|
| **Label** | `C-000:CONTINUE SECTION C`|`C-001:CURRENTLY WORKING`|`C-024:HOW THE WAGE IS CALCULATED`|`C-034:CURRENT SITUATION`|`C-002:CURRENT JOB SITUATION`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** | `1 = Yes`<br/>`2 = Refused to answer` | `1 = Yes`<br/>`2 = Temporarily not working`<br/>`3 = No`<br/>`4 = Don't know`<br/>`5 = Refused to answer` |`1 = Hourly wage`<br/>`2 = Daily wage`<br/>`3 = Monthly salary`<br/>`4 = Yearly salary`<br/>`5 = Percentage payment/piece rate wage (specify)`<br/>`6 = Other ways of payment (specify)`<br/>`7 = Not paid because self-employed`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|`1 = Retired`<br/>`2 = Keep house`<br/>`3 = Receiving medical care`<br/>`4 = Other`<br/>`5 = Don't know`<br/>`6 = Refused to answer`|`1 = Working as an employee at a company, organization, public agency, etc.`<br/>`2 = Serving as an executive of a company, organization, etc.`<br/>`3 = Running own business`<br/>`4 = Helping run family business`<br/>`5 = Working from home`<br/>`6 = Performing tasks upon request from the senior human resource center at which the respondent is registered`<br/>`7 = Performing tasks on an as-needed basis when requested by neighbors, companies, etc.`<br/>`8 = Don't know`<br/>`9 = Refused to answer`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('c_000','c_001','c_024','c_034','c_002'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$c_000
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_000')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_000))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_001
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_001')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_024
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_024')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_024))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_034
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_034')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_034))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$c_002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'c_002')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(c_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `c_034 == 1,3,4 into 996`
* `c_034 == 2 into 1`
* `c_024 == 7 and c_002 == 3,4 into 2`
* `c_024 == 7 and c_002 != 3,4 into 3`
* `c_034 == 5 into 998`
* `c_034 == 6 into 997`
* `NA into 999`
* `c_001 == 1 or 2 and c_024 != 7 into 996`
* `c_000 == 2 into 997`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$nonpaid_work <- car::recode(JSTAR_cth_w1$c_034,"c(1,3,4) = 996; 2 = 1; 5 = 998; 6 = 997; NA=999")
JSTAR_ds_cth_w1$nonpaid_work[which(JSTAR_cth_w1$c_001 %in% c(1,2))] <- 996
JSTAR_ds_cth_w1$nonpaid_work[which(JSTAR_cth_w1$c_024==7 & JSTAR_cth_w1$c_002 %in% c(3,4))] <- 2
JSTAR_ds_cth_w1$nonpaid_work[which(JSTAR_cth_w1$c_024==7 & !JSTAR_cth_w1$c_002 %in% c(3,4))] <- 3
JSTAR_ds_cth_w1$nonpaid_work[which(JSTAR_cth_w1$c_000==2)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}


```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size",sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label",toupper(names(l.hds)))
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  nonpaid_work <- l.hds[[index]]
  save(nonpaid_work, file = paste0(datafolder,names(l.hds)[index],"/nonpaid_work.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





