---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `divorce`
* Variable label: `Experience of divorce/separation`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Greece

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `family`
* Label: `Marital status`
* Categories: 
    + `1.0 = Never married`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widowed`
* Description:
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_divorce','ATTICA.ATTICA_Baseline',variables=list('family'), missings = TRUE)
```

```{r local1, echo=F}
ATTICA_w1_divorce <- opal.execute(o,'ATTICA_w1_divorce')

vari <- ATTICA_w1_divorce$family
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ATTICA_w1_divorce$family, missing_values = NA)
ggplot(ATTICA_w1_divorce, aes(x=factor(family))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 into 1`
* `1, 2, 4 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_divorce$id)
ATTICA_ds_w1$divorce <- car::recode(as.vector(ATTICA_w1_divorce$family), "3='1'; 1:2='0'; 4='0'; NA='999'")
ATTICA_ds_w1$divorce <- labelled(ATTICA_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ATTICA_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ATTICA_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ATTICA_ds_w1$divorce)
BeforeH <- table(ATTICA_w1_divorce$family, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[3]]
BeforeH1[[1]] <- sum(BeforeH[c(1,2,4)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,4->0","3->1")
kable(C)
```



```{r save, echo=FALSE}
divorce <- ATTICA_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



