---
title: "Ever experienced financial problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `fin_prob`
* Variable label: `Ever experienced financial problems?`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Greece

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `financia`
* Label: `Financial status`
* Categories: 
    + `1 = Bad`
    + `2 = Poor`
    + `3 = Good`
    + `4 = Very good`

* Description:
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_fin_prob','ATTICA.ATTICA_Baseline',variables=list('financia'), missings = TRUE)
```

```{r local1, echo=F}
ATTICA_w1_fin_prob <- opal.execute(o,'ATTICA_w1_fin_prob')
vari <- ATTICA_w1_fin_prob$financia
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ATTICA_w1_fin_prob$financia, missing_values = NA)
ggplot(ATTICA_w1_fin_prob, aes(x=factor(financia))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4 into 0`
* `NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_fin_prob$id)
ATTICA_ds_w1$fin_prob <- car::recode(as.vector(ATTICA_w1_fin_prob$financia), "1:2='1'; 3:4='0'; NA='999'")
ATTICA_ds_w1$fin_prob <- labelled(ATTICA_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ATTICA_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ATTICA_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ATTICA_ds_w1$fin_prob)
BeforeH <- table(ATTICA_w1_fin_prob$financia, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(3:4)])
BeforeH1[[2]] <- sum(BeforeH[c(1:2)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->>0","1:2->1","NA->999")
kable(C)
```

```{r save, echo=FALSE}
fin_prob <- ATTICA_ds_w1
save(fin_prob, file = "../RData/w1/fin_prob.RData")
rm(fin_prob)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

