---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process


## Greece
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `family`
* Label: `Marital status`
* Categories: 
    + `1.0 = Never married`
    + `2.0 = Married`
    + `3.0 = Divorced`
    + `4.0 = Widowed`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_spouse','ATTICA.ATTICA_Baseline',variables=list('family'), missings = TRUE)
```

```{r local1, echo=F}
ATTICA_w1_spouse <- opal.execute(o,'ATTICA_w1_spouse')
vari <- ATTICA_w1_spouse$family
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ATTICA_w1_spouse$family, missing_values = NA)
ggplot(ATTICA_w1_spouse, aes(x=factor(family))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 Married into 1`
* `1, 3, 4 into 0`
* `NA into 999`



**R script:** 
```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_spouse$id)
ATTICA_ds_w1$spouse <- car::recode(as.vector(ATTICA_w1_spouse$family), "2='1'; 1='0'; 3='0'; 4='0'; NA='999'")
ATTICA_ds_w1$spouse <- labelled(ATTICA_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ATTICA_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ATTICA_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ATTICA_ds_w1$spouse)
BeforeH <- table(ATTICA_w1_spouse$family, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH <- BeforeH[c(1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,3,4->0","2->1")
kable(C)
```



### Wave 2
Not found.

### Wave 3
Not found.


```{r save, echo=FALSE}
spouse <- ATTICA_ds_w1
save(spouse, file = "../RData/w1/spouse.RData")
rm(spouse)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
