---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Greece

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `child`
* Label: `Number of children`

* Description:
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_child','ATTICA.ATTICA_Baseline', variables=list('child'), missings = TRUE)
```

```{r local1, echo=F}
ATTICA_w1_child <- opal.execute(o,'ATTICA_w1_child')
vari <- ATTICA_w1_child$child
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ATTICA_w1_child$child, missing_values = NA)
ggplot(ATTICA_w1_child, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0; 1:hi into 1`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_child$id)
ATTICA_ds_w1$child <- car::recode(as.vector(ATTICA_w1_child$child), "0='0'; NA='999'; 1:hi='1'")
ATTICA_ds_w1$child <- labelled(ATTICA_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ATTICA_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ATTICA_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ATTICA_ds_w1$child)
BeforeH <- table(ATTICA_w1_child$child, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:10)])
BeforeH <- BeforeH[c(1,2,11)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2
Not found.

### Wave 3
Not found.


```{r save, echo=FALSE}
child <- ATTICA_w1_child
save(child, file = "../RData/w1/child.RData")
rm(child)



```

# Quality estimation

`grchild` cannot be harmonized.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
