---
title: "Cardiovascular diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w2_dv.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd_all`
* Variable label: `History of all Cardiovascular diseases`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: angina, stroke, myocardial infarction, heart attack, coronary heart disease, congestive heart failure, heart murmur, valve disease, cerebral vascular disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No, the participant has not been diagnosed of any of these conditions
1        | Yes, the participant has been diagnosed by any of these conditions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of all Cardiovascular diseases"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## England


### Wave 1


#### Study-specific variable description

| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` |`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** | `1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |  |  |  |  |  |



```{r assign w1, echo=F}

load(paste0(datafolder,"w1/h_angina.RData"))
load(paste0(datafolder,"w1/mi_ha.RData"))
load(paste0(datafolder,"w1/stroke.RData"))
ELSA_w1$h_angina <- h_angina$h_angina
ELSA_w1$mi_ha <- mi_ha$mi_ha
ELSA_w1$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w1, echo=F}

vbl <- ELSA_w1$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `h_angina ==1 or mi_ha == 1 or stroke == 1 (<==> some hedimX == 2 or 3 or 8) or some hedimX == 4 or 5 into 1`
* `hedim01 == -9 into 997`
* `hedim01 == -8 into 998`
* `otherwise into 0`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$cvd_all <- rep(0,length(ELSA_w1$id))
ELSA_ds_w1$cvd_all[which(ELSA_w1$hedim01 %in% c(4,5) | ELSA_w1$hedim02 %in% c(4,5) | ELSA_w1$hedim03 %in% c(4,5) | ELSA_w1$hedim04 %in% c(4,5) | ELSA_w1$hedim05 %in% c(4,5) | ELSA_w1$hedim06 %in% c(4,5) | ELSA_w1$hedim07 %in% c(4,5) | ELSA_w1$h_angina==1 | ELSA_w1$mi_ha==1 | ELSA_w1$stroke==1)] <- 1
ELSA_ds_w1$cvd_all[which(ELSA_w1$hedim01==-9)] <- 997
ELSA_ds_w1$cvd_all[which(ELSA_w1$hedim01==-8)] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$cvd_all)
X <- c(
  sum(ELSA_w1$hedim01 %in% c(2,3,8,4,5) | ELSA_w1$hedim02 %in% c(2,3,8,4,5) | ELSA_w1$hedim03 %in% c(2,3,8,4,5) | ELSA_w1$hedim04 %in% c(2,3,8,4,5) | ELSA_w1$hedim05 %in% c(2,3,8,4,5) | ELSA_w1$hedim06 %in% c(2,3,8,4,5) | ELSA_w1$hedim07 %in% c(2,3,8,4,5),na.rm=T),
  sum(ELSA_w1$hedim01==-9),
  sum(ELSA_w1$hedim01==-8)
)
BeforeH <- c(length(ELSA_w1$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=4,5,2,3,8->0","hedimX %in% c(2,3,8,4,5)->1","hedimX==-9->997","hedimX==-8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` | `hedim08` | `h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Diagnosed cardiovascular condit. newly reported at W2 (1st mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (2nd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (3rd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (4th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (5th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (6th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (7th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (8th mention) (merged var)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |  |  |  |  |  |  |


```{r assign w2, echo=F}

load(paste0(datafolder,"w2/h_angina.RData"))
load(paste0(datafolder,"w2/mi_ha.RData"))
load(paste0(datafolder,"w2/stroke.RData"))
ELSA_w2$h_angina <- h_angina$h_angina
ELSA_w2$mi_ha <- mi_ha$mi_ha
ELSA_w2$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim08
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim08')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim08))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `h_angina ==1 or mi_ha == 1 or stroke == 1 (<==> some hedimX == 2 or 3 or 8) or some hedimX == 4 or 5 into 1`
* `h_angina == mi_ha == stroke == 997 into 997`
* `h_angina == mi_ha == stroke == 998 into 998`
* `otherwise into 0`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$cvd_all <- rep(0,length(ELSA_w2$id))
ELSA_ds_w2$cvd_all[which(ELSA_w2$hedim01 %in% c(4,5) | ELSA_w2$hedim02 %in% c(4,5) | ELSA_w2$hedim03 %in% c(4,5) | ELSA_w2$hedim04 %in% c(4,5) | ELSA_w2$hedim05 %in% c(4,5) | ELSA_w2$hedim06 %in% c(4,5) | ELSA_w2$hedim07 %in% c(4,5) | ELSA_w2$hedim08 %in% c(4,5) | ELSA_w2$h_angina==1 | ELSA_w2$mi_ha==1 | ELSA_w2$stroke==1)] <- 1
ELSA_ds_w2$cvd_all[which(ELSA_w2$h_angina==997 & ELSA_w2$mi_ha==997 & ELSA_w2$stroke==997)] <- 997
ELSA_ds_w2$cvd_all[which(ELSA_w2$h_angina==998 & ELSA_w2$mi_ha==998 & ELSA_w2$stroke==998)] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$cvd_all)
X <- c(
  sum(ELSA_w2$hedim01 %in% c(3,8,4,5) | ELSA_w2$hedim02 %in% c(3,8,4,5) | ELSA_w2$hedim03 %in% c(3,8,4,5) | ELSA_w2$hedim04 %in% c(3,8,4,5) | ELSA_w2$hedim05 %in% c(3,8,4,5) | ELSA_w2$hedim06 %in% c(3,8,4,5) | ELSA_w2$hedim07 %in% c(3,8,4,5) | ELSA_w2$hedim08 %in% c(3,8,4,5) | ELSA_w2$h_angina == 1,na.rm=T),
  sum(ELSA_w2$h_angina==997 & ELSA_w2$mi_ha==997 & ELSA_w2$stroke==997,na.rm=T),
  sum(ELSA_w2$h_angina==998 & ELSA_w2$mi_ha==998 & ELSA_w2$stroke==998,na.rm=T)
)
# We set aside h_angina since it is a chronic condition, so it also takes into account the first wave.
BeforeH <- c(length(ELSA_w2$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=2,3,8,4,5->0","hedimX==2,3,8,4,5->1","hedimX==-9->997","hedimX==-8->998")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `dhedimhf` |`dhedimhm`|`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|
| **Label** |`CVD: congestive heart failure diagnosis newly reported (merged)`|`CVD: heart murmur diagnosis newly reported (merged)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_3_elsa_data_v4`|`wave_3_elsa_data_v4`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`1 = Mentioned`<br/>`0 = Not mentioned`|`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|`996 = Not applicable`|`996 = Not applicable`|`996 = Not applicable`|
| **Description** |  |  |  |  |  |


```{r assign w3, echo=F}

load(paste0(datafolder,"w3/h_angina.RData"))
load(paste0(datafolder,"w3/mi_ha.RData"))
load(paste0(datafolder,"w3/stroke.RData"))
ELSA_w3$h_angina <- h_angina$h_angina
ELSA_w3$mi_ha <- mi_ha$mi_ha
ELSA_w3$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$dhedimhf
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedimhf')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedimhf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$dhedimhm
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedimhm')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedimhm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 0 into 0`
* `-1/996 into 996`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$cvd_all <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$cvd_all[which(ELSA_w3$h_angina==0 & ELSA_w3$mi_ha==0 & ELSA_w3$stroke==0 & ELSA_w3$dhedimhf==0 & ELSA_w3$dhedimhm==0)] <- 0
ELSA_ds_w3$cvd_all[which(ELSA_w3$h_angina==1 | ELSA_w3$mi_ha==1 | ELSA_w3$stroke==1 | ELSA_w3$dhedimhf==1 | ELSA_w3$dhedimhm==1)] <- 1
ELSA_ds_w3$cvd_all[which(ELSA_w3$h_angina==996 & ELSA_w3$mi_ha==996 & ELSA_w3$stroke==996 & ELSA_w3$dhedimhf==-1 & ELSA_w3$dhedimhm==-1)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$cvd_all)
X <- c(
  sum(ELSA_w3$h_angina==0 & ELSA_w3$mi_ha==0 & ELSA_w3$stroke==0 & ELSA_w3$dhedimhf==0 & ELSA_w3$dhedimhm==0,na.rm=T),
  sum(ELSA_w3$h_angina==1 | ELSA_w3$mi_ha==1 | ELSA_w3$stroke==1 | ELSA_w3$dhedimhf==1 | ELSA_w3$dhedimhm==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(ELSA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-1/996->996")
kable(C)

```






### Wave 4

#### Study-specific variable description

| **Name** | `hedimhf` |`hedimhm`|`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|
| **Label** |`CVD: congestive heart failure diagnosis newly reported (merged)`|`CVD: heart murmur diagnosis newly reported (merged)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_4_elsa_data_v3`|`wave_4_elsa_data_v3`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`1 = Mentioned`<br/>`0 = Not mentioned`|`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|`997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |


```{r assign w4, echo=F}

load(paste0(datafolder,"w4/h_angina.RData"))
load(paste0(datafolder,"w4/mi_ha.RData"))
load(paste0(datafolder,"w4/stroke.RData"))
ELSA_w4$h_angina <- h_angina$h_angina
ELSA_w4$mi_ha <- mi_ha$mi_ha
ELSA_w4$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$hedimhf
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhf')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedimhf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$hedimhm
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhm')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedimhm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 0 into 0`
* `-9/997 into 997`
* `-8/998 into 998`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$cvd_all <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$cvd_all[which(ELSA_w4$h_angina==0 & ELSA_w4$mi_ha==0 & ELSA_w4$stroke==0 & ELSA_w4$hedimhf==0 & ELSA_w4$hedimhm==0)] <- 0
ELSA_ds_w4$cvd_all[which(ELSA_w4$h_angina==1 | ELSA_w4$mi_ha==1 | ELSA_w4$stroke==1 | ELSA_w4$hedimhf==1 | ELSA_w4$hedimhm==1)] <- 1
ELSA_ds_w4$cvd_all[which(ELSA_w4$h_angina==998 & ELSA_w4$mi_ha==998 & ELSA_w4$stroke==998 & ELSA_w4$hedimhf==-8 & ELSA_w4$hedimhm==-8)] <- 998
ELSA_ds_w4$cvd_all[which(ELSA_w4$h_angina==997 & ELSA_w4$mi_ha==997 & ELSA_w4$stroke==997 & ELSA_w4$hedimhf==-9 & ELSA_w4$hedimhm==-9)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$cvd_all)
X <- c(
  sum(ELSA_w4$h_angina==0 & ELSA_w4$mi_ha==0 & ELSA_w4$stroke==0 & ELSA_w4$hedimhf==0 & ELSA_w4$hedimhm==0,na.rm=T),
  sum(ELSA_w4$h_angina==1 | ELSA_w4$mi_ha==1 | ELSA_w4$stroke==1 | ELSA_w4$hedimhf==1 | ELSA_w4$hedimhm==1,na.rm = T),
  sum(ELSA_w4$h_angina==997 | ELSA_w4$mi_ha==997 | ELSA_w4$stroke==997 | ELSA_w4$hedimhf==-9 | ELSA_w4$hedimhm==-9,na.rm=T),
  sum(ELSA_w4$h_angina==998 | ELSA_w4$mi_ha==998 | ELSA_w4$stroke==998 | ELSA_w4$hedimhf==-8 | ELSA_w4$hedimhm==-8,na.rm = T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-9/997->997","-8/998->998")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `hedimhf` |`hedimhm`|`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|
| **Label** |`CVD: congestive heart failure diagnosis newly reported (merged)`|`CVD: heart murmur diagnosis newly reported (merged)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_5_elsa_data_v4`|`wave_5_elsa_data_v4`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`1 = Mentioned`<br/>`0 = Not mentioned`|`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|`997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |


```{r assign w5, echo=F}

load(paste0(datafolder,"w5/h_angina.RData"))
load(paste0(datafolder,"w5/mi_ha.RData"))
load(paste0(datafolder,"w5/stroke.RData"))
ELSA_w5$h_angina <- h_angina$h_angina
ELSA_w5$mi_ha <- mi_ha$mi_ha
ELSA_w5$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$hedimhf
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhf')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedimhf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$hedimhm
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhm')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedimhm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 0 into 0`
* `-9/997 into 997`
* `-8/998 into 998`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$cvd_all <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$cvd_all[which(ELSA_w5$h_angina==0 & ELSA_w5$mi_ha==0 & ELSA_w5$stroke==0 & ELSA_w5$hedimhf==0 & ELSA_w5$hedimhm==0)] <- 0
ELSA_ds_w5$cvd_all[which(ELSA_w5$h_angina==1 | ELSA_w5$mi_ha==1 | ELSA_w5$stroke==1 | ELSA_w5$hedimhf==1 | ELSA_w5$hedimhm==1)] <- 1
ELSA_ds_w5$cvd_all[which(ELSA_w5$h_angina==998 & ELSA_w5$mi_ha==998 & ELSA_w5$stroke==998 & ELSA_w5$hedimhf==-8 & ELSA_w5$hedimhm==-8)] <- 998
ELSA_ds_w5$cvd_all[which(ELSA_w5$h_angina==997 & ELSA_w5$mi_ha==997 & ELSA_w5$stroke==997 & ELSA_w5$hedimhf==-9 & ELSA_w5$hedimhm==-9)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$cvd_all)
X <- c(
  sum(ELSA_w5$h_angina==0 & ELSA_w5$mi_ha==0 & ELSA_w5$stroke==0 & ELSA_w5$hedimhf==0 & ELSA_w5$hedimhm==0,na.rm=T),
  sum(ELSA_w5$h_angina==1 | ELSA_w5$mi_ha==1 | ELSA_w5$stroke==1 | ELSA_w5$hedimhf==1 | ELSA_w5$hedimhm==1,na.rm = T),
  sum(ELSA_w5$h_angina==997 & (ELSA_w5$mi_ha==997 | ELSA_w5$stroke==997 | ELSA_w5$hedimhf==-9 | ELSA_w5$hedimhm==-9),na.rm=T),
  sum(ELSA_w5$h_angina==998 & (ELSA_w5$mi_ha==998 | ELSA_w5$stroke==998 | ELSA_w5$hedimhf==-8 | ELSA_w5$hedimhm==-8),na.rm = T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-9/997->997","-8/998->998")
kable(C)

```





### Wave 6

#### Study-specific variable description

| **Name** | `hedimhf` |`hedimhm`|`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|
| **Label** |`CVD: congestive heart failure diagnosis newly reported (merged)`|`CVD: heart murmur diagnosis newly reported (merged)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_6_elsa_data_v2`|`wave_6_elsa_data_v2`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`1 = Mentioned`<br/>`0 = Not mentioned`|`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|`997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |


```{r assign w6, echo=F}

load(paste0(datafolder,"w6/h_angina.RData"))
load(paste0(datafolder,"w6/mi_ha.RData"))
load(paste0(datafolder,"w6/stroke.RData"))
ELSA_w6$h_angina <- h_angina$h_angina
ELSA_w6$mi_ha <- mi_ha$mi_ha
ELSA_w6$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$hedimhf
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhf')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedimhf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$hedimhm
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhm')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedimhm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 0 into 0`
* `-9/997 into 997`
* `-8/998 into 998`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$cvd_all <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$cvd_all[which(ELSA_w6$h_angina==0 & ELSA_w6$mi_ha==0 & ELSA_w6$stroke==0 & ELSA_w6$hedimhf==0 & ELSA_w6$hedimhm==0)] <- 0
ELSA_ds_w6$cvd_all[which(ELSA_w6$h_angina==1 | ELSA_w6$mi_ha==1 | ELSA_w6$stroke==1 | ELSA_w6$hedimhf==1 | ELSA_w6$hedimhm==1)] <- 1
ELSA_ds_w6$cvd_all[which(ELSA_w6$h_angina==998 & ELSA_w6$mi_ha==998 & ELSA_w6$stroke==998 & ELSA_w6$hedimhf==-8 & ELSA_w6$hedimhm==-8)] <- 998
ELSA_ds_w6$cvd_all[which(ELSA_w6$h_angina==997 & ELSA_w6$mi_ha==997 & ELSA_w6$stroke==997 & ELSA_w6$hedimhf==-9 & ELSA_w6$hedimhm==-9)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$cvd_all)
X <- c(
  sum(ELSA_w6$h_angina==0 & ELSA_w6$mi_ha==0 & ELSA_w6$stroke==0 & ELSA_w6$hedimhf==0 & ELSA_w6$hedimhm==0,na.rm=T),
  sum(ELSA_w6$h_angina==1 | ELSA_w6$mi_ha==1 | ELSA_w6$stroke==1 | ELSA_w6$hedimhf==1 | ELSA_w6$hedimhm==1,na.rm = T),
  sum(ELSA_w6$h_angina==997 & (ELSA_w6$mi_ha==997 | ELSA_w6$stroke==997 | ELSA_w6$hedimhf==-9 | ELSA_w6$hedimhm==-9),na.rm=T),
  sum(ELSA_w6$h_angina==998 & (ELSA_w6$mi_ha==998 | ELSA_w6$stroke==998 | ELSA_w6$hedimhf==-8 | ELSA_w6$hedimhm==-8),na.rm = T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-9/997->997","-8/998->998")
kable(C)

```






### Wave 7

#### Study-specific variable description

| **Name** | `hedimhf` |`hedimhm`|`h_angina`|`mi_ha`|`stroke`|
|-|-|-|-|-|-|
| **Label** |`CVD: congestive heart failure diagnosis newly reported (merged)`|`CVD: heart murmur diagnosis newly reported (merged)`|`History of angina`|`Myocardial infarction or heart attack`|`Stroke`|
| **Table name**  | `wave_7_elsa_data`|`wave_7_elsa_data`|`h_angina`|`mi_ha`|`stroke`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`1 = Mentioned`<br/>`0 = Not mentioned`|`0 = no history of angina`<br/>`1 = history of angina`|`0 = No`<br/>`1 = Yes`|`0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|`997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` | `997 = Refuse`<br/>`998 = Do not know` |
| **Description** |  |  |  |  |  |


```{r assign w7, echo=F}

load(paste0(datafolder,"w7/h_angina.RData"))
load(paste0(datafolder,"w7/mi_ha.RData"))
load(paste0(datafolder,"w7/stroke.RData"))
ELSA_w7$h_angina <- h_angina$h_angina
ELSA_w7$mi_ha <- mi_ha$mi_ha
ELSA_w7$stroke <- stroke$stroke
rm(h_angina)
rm(mi_ha)
rm(stroke)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$hedimhf
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhf')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedimhf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$hedimhm
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimhm')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedimhm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'h_angina')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'mi_ha')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'stroke')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 0 into 0`
* `-9/997 into 997`
* `-8/998 into 998`

**R script:**

```{r harmo w7}

# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$cvd_all <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$cvd_all[which(ELSA_w7$h_angina==0 & ELSA_w7$mi_ha==0 & ELSA_w7$stroke==0 & ELSA_w7$hedimhf==0 & ELSA_w7$hedimhm==0)] <- 0
ELSA_ds_w7$cvd_all[which(ELSA_w7$h_angina==1 | ELSA_w7$mi_ha==1 | ELSA_w7$stroke==1 | ELSA_w7$hedimhf==1 | ELSA_w7$hedimhm==1)] <- 1
ELSA_ds_w7$cvd_all[which(ELSA_w7$h_angina==998 & ELSA_w7$mi_ha==998 & ELSA_w7$stroke==998 & ELSA_w7$hedimhf==-8 & ELSA_w7$hedimhm==-8)] <- 998
ELSA_ds_w7$cvd_all[which(ELSA_w7$h_angina==997 & ELSA_w7$mi_ha==997 & ELSA_w7$stroke==997 & ELSA_w7$hedimhf==-9 & ELSA_w7$hedimhm==-9)] <- 997

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$cvd_all)
X <- c(
  sum(ELSA_w7$h_angina==0 & ELSA_w7$mi_ha==0 & ELSA_w7$stroke==0 & ELSA_w7$hedimhf==0 & ELSA_w7$hedimhm==0,na.rm=T),
  sum(ELSA_w7$h_angina==1 | ELSA_w7$mi_ha==1 | ELSA_w7$stroke==1 | ELSA_w7$hedimhf==1 | ELSA_w7$hedimhm==1,na.rm = T),
  sum(ELSA_w7$h_angina==997 | (ELSA_w7$mi_ha==997 | ELSA_w7$stroke==997 | ELSA_w7$hedimhf==-9 | ELSA_w7$hedimhm==-9),na.rm=T),
  sum(ELSA_w7$h_angina==998 | (ELSA_w7$mi_ha==998 | ELSA_w7$stroke==998 | ELSA_w7$hedimhf==-8 | ELSA_w7$hedimhm==-8),na.rm = T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","-9/997->997","-8/998->998")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]) , length(l.hds[[6]][[2]]), length(l.hds[[7]][[2]])
             )
names(t.hds)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(t.hds)

dbb <- merge(ELSA_m_ds_w1[,c("id","cvd_all")], ELSA_m_ds_w2[,c("id","cvd_all")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w3[,c("id","cvd_all")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4[,c("id","cvd_all")], by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w5[,c("id","cvd_all")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6[,c("id","cvd_all")], by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w7[,c("id","cvd_all")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2","w4","w5")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation

The harmonized variable contains information about: angina, myocardial infarction, stroke, congestive heart failure and heart murmur.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  cvd_all <- l.hds[[index]]
  save(cvd_all, file = paste0(datafolder,names(l.hds)[index],"/cvd_all.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```




