---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w2_dv.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cancer`
* Variable label: `Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)`
* Variable description: `cancer diagnosis since the last interview`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no cancer
1        | cancer

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cancer_age`
* Variable label: `Age of cancer diagnosis`
* Variable description: `Age of each episode of cancer`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)"
ds_label_age <- "Age of cancer diagnosis"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## England


### Wave 1


#### Study-specific variable description

| **Name** | `hedib01` | `hedib02` | `hedib03` | `hedib04` | `hedib05` | `hedib06` | `hedib07` | `hedib08` | `hedib09` | `hedib10` |`heagg`|
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Approximately how old were you when first told by a doctor that you had cancer or a malignant tumour? {years}`|
| **Table name**  | `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`|
| **Categories** | `1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Yes`<br/>`2 = No`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |  |  |  |  |  |  |


```{r assign w1, echo=F}

```

```{r local w1, echo=F}

vbl <- ELSA_w1$hedib01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib08
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib08')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib08))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib09
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib09')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib09))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib10
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib10')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$heagg
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'heagg')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heagg)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `some hedibX == 5 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heagg`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$cancer <- rep(0,length(ELSA_w1$id))
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==5 | ELSA_w1$hedib02==5 | ELSA_w1$hedib03==5 | ELSA_w1$hedib04==5 | ELSA_w1$hedib05==5 | ELSA_w1$hedib06==5 | ELSA_w1$hedib07==5 | ELSA_w1$hedib08==5 | ELSA_w1$hedib09==5 | ELSA_w1$hedib10==5)] <- 1
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==-9)] <- 997
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w1$cancer_age <- rep(999,length(ELSA_w1$id))
ELSA_ds_w1$cancer_age[which(ELSA_ds_w1$cancer==0)] <- 996
ELSA_ds_w1$cancer_age[which(ELSA_ds_w1$cancer==1)] <- car::recode(ELSA_w1$heagg[which(ELSA_ds_w1$cancer==1)],"-1=996;-8=998;-9=997")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$cancer)
X <- c(
  sum(ELSA_w1$hedib01==5 | ELSA_w1$hedib02==5 | ELSA_w1$hedib03==5 | ELSA_w1$hedib04==5 | ELSA_w1$hedib05==5 | ELSA_w1$hedib06==5 | ELSA_w1$hedib07==5 | ELSA_w1$hedib08==5 | ELSA_w1$hedib09==5 | ELSA_w1$hedib10==5,na.rm=T),
  sum(ELSA_w1$hedib01==-9),
  sum(ELSA_w1$hedib01==-8)
)
BeforeH <- c(length(ELSA_w1$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibX!=5->0","hedibX==5->1","hedibX==-9->997","hedibX==-8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `hedib01` | `hedib02` | `hedib03` | `hedib04` |`HeAggRY`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** |`Diagnosed chronic condition newly reported at W2 (1st mention)`|`Diagnosed chronic condition newly reported at W2 (2nd mention)`|`Diagnosed chronic condition newly reported at W2 (3rd mention)`|`Diagnosed chronic condition newly reported at W2 (4th mention)`|`Year told had cancer in last 2 years`|`year of birth`|
| **Table name**  | `wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`| `wave_2_core_data_v4`|`ybirth`|
| **Categories** |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |
| **Description** |  |  |  |  |  |  |


```{r assign w2, echo=F}

load(paste0(datafolder,"w2/ybirth.RData"))
ELSA_w2 <- left_join(ELSA_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$hedib01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1980,2010)

vbl <- ELSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `some hedibX == 5 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$cancer <- rep(0,length(ELSA_w2$id))
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==5 | ELSA_w2$hedib02==5 | ELSA_w2$hedib03==5 | ELSA_w2$hedib04==5)] <- 1
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==-9)] <- 997
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w2$cancer_age <- rep(999,length(ELSA_w2$id))
ELSA_ds_w2$cancer_age[which(ELSA_ds_w2$cancer==0)] <- 996
ELSA_ds_w2$cancer_age[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w2$HeAggRY[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))] - ELSA_w2$ybirth[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w2$cancer_age <- car::recode(ELSA_ds_w2$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$cancer)
X <- c(
  sum(ELSA_w2$hedib01==5 | ELSA_w2$hedib02==5 | ELSA_w2$hedib03==5 | ELSA_w2$hedib04==5,na.rm=T),
  sum(ELSA_w2$hedib01==-9,na.rm=T),
  sum(ELSA_w2$hedib01==-8,na.rm=T)
)
BeforeH <- c(length(ELSA_w2$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibX!=5->0","hedibX==5->1","hedibX==-9->997","hedibX==-8->998")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `dhedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_3_elsa_data_v4`|`ybirth`| `wave_3_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `998 = Do not know` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |


```{r assign w3, echo=F}

load(paste0(datafolder,"w3/ybirth.RData"))
ELSA_w3 <- left_join(ELSA_w3,ybirth, by="id")
rm(ybirth)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$dhedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1980,2010)

vbl <- ELSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `dhedibca == 1 into 1`
* `dhedibca == 0 into 0`
* `dhedibca == -1 into 996`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$cancer <- car::recode(ELSA_w3$dhedibca,"-1=996")

# Continuous variable harmonization
ELSA_ds_w3$cancer_age <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$cancer_age[which(ELSA_ds_w3$cancer==0)] <- 996
ELSA_ds_w3$cancer_age[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] <- ELSA_w3$heaggry[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] - ELSA_w3$ybirth[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)]
ELSA_ds_w3$cancer_age <- car::recode(ELSA_ds_w3$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w3$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(40,95)

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$cancer)
BeforeH <- table(ELSA_w3$dhedibca)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("dhedibca==0->0","dhedibca==1->1","dhedibca==-1->996")
kable(C)

```






### Wave 4

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_4_elsa_data_v3`|`ybirth`|`wave_4_elsa_data_v3`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-2 = Capi/Interview Error`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |


```{r assign w4, echo=F}

load(paste0(datafolder,"w4/ybirth.RData"))
ELSA_w4 <- left_join(ELSA_w4,ybirth, by="id")
rm(ybirth)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1955,2010)

vbl <- ELSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -1 into 996`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-2 into 991`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$cancer <- car::recode(ELSA_w4$hedibca,"-1=996;-8=998;-9=997")


# Continuous variable harmonization
ELSA_ds_w4$cancer_age <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$cancer_age[which(ELSA_ds_w4$cancer==0)] <- 996
ELSA_ds_w4$cancer_age[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))] <- ELSA_w4$heaggry[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))] - ELSA_w4$ybirth[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))]
ELSA_ds_w4$cancer_age <- car::recode(ELSA_ds_w4$cancer_age, "-1=996;-8=998;-9=997;-2=991;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w4$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$cancer)
BeforeH <- table(ELSA_w4$hedibca)[c(4,5,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-1->996","hedibca==-9->997","hedibca==-8->998")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_5_elsa_data_v4`|`ybirth`|`wave_5_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |

```{r assign w5, echo=F}

load(paste0(datafolder,"w5/ybirth.RData"))
ELSA_w5 <- left_join(ELSA_w5,ybirth, by="id")
rm(ybirth)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1970,2015)

vbl <- ELSA_w5$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -1 into 996`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$cancer <- car::recode(ELSA_w5$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w5$cancer_age <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$cancer_age[which(ELSA_ds_w5$cancer==0)] <- 996
ELSA_ds_w5$cancer_age[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))] <- ELSA_w5$heaggry[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))] - ELSA_w5$ybirth[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))]
ELSA_ds_w5$cancer_age <- car::recode(ELSA_ds_w5$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w5$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$cancer)
BeforeH <- table(ELSA_w5$hedibca)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-9->997","hedibca==-8->998")
kable(C)

```





### Wave 6

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`HeAggRY`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_6_elsa_data_v2`|`ybirth`|`wave_6_elsa_data_v2`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |


```{r assign w6, echo=F}

load(paste0(datafolder,"w6/ybirth.RData"))
ELSA_w6 <- left_join(ELSA_w6,ybirth, by="id")
rm(ybirth)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1960,2015)

vbl <- ELSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$cancer <- car::recode(ELSA_w6$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w6$cancer_age <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$cancer_age[which(ELSA_ds_w6$cancer==0)] <- 996
ELSA_ds_w6$cancer_age[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w6$HeAggRY[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))] - ELSA_w6$ybirth[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w6$cancer_age <- car::recode(ELSA_ds_w6$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w6$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$cancer)
BeforeH <- table(ELSA_w6$hedibca)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-9->997","hedibca==-8->998")
kable(C)

```






### Wave 7

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`HeAggRY`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_7_elsa_data`|`ybirth`|`wave_7_elsa_data`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |

```{r assign w7, echo=F}

load(paste0(datafolder,"w7/ybirth.RData"))
ELSA_w7 <- left_join(ELSA_w7,ybirth, by="id")
rm(ybirth)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1960,2020)

vbl <- ELSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w7}


# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$cancer <- car::recode(ELSA_w7$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w7$cancer_age <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$cancer_age[which(ELSA_ds_w7$cancer==0)] <- 996
ELSA_ds_w7$cancer_age[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w7$HeAggRY[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))] - ELSA_w7$ybirth[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w7$cancer_age <- car::recode(ELSA_ds_w7$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w7$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$cancer)
BeforeH <- table(ELSA_w7$hedibca)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-8->998")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]) , length(l.hds[[6]][[2]]), length(l.hds[[7]][[2]])
             )
names(t.hds)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(t.hds)

dbb <- merge(ELSA_m_ds_w1[,c("id","cancer")], ELSA_m_ds_w2[,c("id","cancer")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w3[,c("id","cancer")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4[,c("id","cancer")], by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w5[,c("id","cancer")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6[,c("id","cancer")], by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w7[,c("id","cancer")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2","w4","w5")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation

No comments


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  cancer <- l.hds[[index]]
  save(cancer, file = paste0(datafolder,names(l.hds)[index],"/cancer.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```




