---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cancerDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cancerDS.R')
```

```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w2_dv.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 




# Data process




## England


### Wave 1


#### Study-specific variable description

| **Name** | `hedib01` | `hedib02` | `hedib03` | `hedib04` | `hedib05` | `hedib06` | `hedib07` | `hedib08` | `hedib09` | `hedib10` |`heagg`|
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Has a doctor ever told you that you [have/have had] any of the conditions in this card?{chronic lung disease ..}`|`Approximately how old were you when first told by a doctor that you had cancer or a malignant tumour? {years}`|
| **Table name**  | `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`|
| **Categories** | `1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Yes`<br/>`2 = No`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |  |  |  |  |  |  |


```{r assign w1, echo=F}

```

```{r local w1, echo=F}

vbl <- ELSA_w1$hedib01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib08
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib08')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib08))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib09
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib09')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib09))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedib10
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib10')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedib10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$heagg
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'heagg')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heagg)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `some hedibX == 5 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heagg`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$cancer <- rep(0,length(ELSA_w1$id))
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==5 | ELSA_w1$hedib02==5 | ELSA_w1$hedib03==5 | ELSA_w1$hedib04==5 | ELSA_w1$hedib05==5 | ELSA_w1$hedib06==5 | ELSA_w1$hedib07==5 | ELSA_w1$hedib08==5 | ELSA_w1$hedib09==5 | ELSA_w1$hedib10==5)] <- 1
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==-9)] <- 997
ELSA_ds_w1$cancer[which(ELSA_w1$hedib01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w1$cancer_age <- rep(999,length(ELSA_w1$id))
ELSA_ds_w1$cancer_age[which(ELSA_ds_w1$cancer==0)] <- 996
ELSA_ds_w1$cancer_age[which(ELSA_ds_w1$cancer==1)] <- car::recode(ELSA_w1$heagg[which(ELSA_ds_w1$cancer==1)],"-1=996;-8=998;-9=997")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$cancer)
X <- c(
  sum(ELSA_w1$hedib01==5 | ELSA_w1$hedib02==5 | ELSA_w1$hedib03==5 | ELSA_w1$hedib04==5 | ELSA_w1$hedib05==5 | ELSA_w1$hedib06==5 | ELSA_w1$hedib07==5 | ELSA_w1$hedib08==5 | ELSA_w1$hedib09==5 | ELSA_w1$hedib10==5,na.rm=T),
  sum(ELSA_w1$hedib01==-9),
  sum(ELSA_w1$hedib01==-8)
)
BeforeH <- c(length(ELSA_w1$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibX!=5->0","hedibX==5->1","hedibX==-9->997","hedibX==-8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `hedib01` | `hedib02` | `hedib03` | `hedib04` |`HeAggRY`|`ybirth`|
|-|-|-|-|-|-|-|
| **Label** |`Diagnosed chronic condition newly reported at W2 (1st mention)`|`Diagnosed chronic condition newly reported at W2 (2nd mention)`|`Diagnosed chronic condition newly reported at W2 (3rd mention)`|`Diagnosed chronic condition newly reported at W2 (4th mention)`|`Year told had cancer in last 2 years`|`year of birth`|
| **Table name**  | `wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`| `wave_2_core_data_v4`|`elsa_w2_hd`|
| **Categories** |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`1 = Chronic lung disease such as chronic bronchitis or emphysema`<br/>`2 = Asthma`<br/>`3 = Arthritis (including osteoarthritis , or rheumatism)`<br/>`4 = Osteoporosis, sometimes called thin or brittle bones`<br/>`5 = Cancer or a malignant tumour (excluding minor skin cancers)`<br/>`6 = Parkinson s disease`<br/>`7 = Any emotional, nervous or psychiatric problems`<br/>`8 = Alzheimer s disease`<br/>`9 = Dementia, organic brain syndrome, senility or any other seri`<br/>`96 = None of these` |`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |
| **Description** |  |  |  |  |  |  |


```{r assign w2, echo=F}

load(paste0(datafolder,"w2/ybirth.RData"))
ELSA_w2 <- left_join(ELSA_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$hedib01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedib04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedib04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedib04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1980,2010)

vbl <- ELSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `some hedibX == 5 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$cancer <- rep(0,length(ELSA_w2$id))
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==5 | ELSA_w2$hedib02==5 | ELSA_w2$hedib03==5 | ELSA_w2$hedib04==5)] <- 1
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==-9)] <- 997
ELSA_ds_w2$cancer[which(ELSA_w2$hedib01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w2$cancer_age <- rep(999,length(ELSA_w2$id))
ELSA_ds_w2$cancer_age[which(ELSA_ds_w2$cancer==0)] <- 996
ELSA_ds_w2$cancer_age[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w2$HeAggRY[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))] - ELSA_w2$ybirth[which(ELSA_ds_w2$cancer==1 & !ELSA_w2$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w2$cancer_age <- car::recode(ELSA_ds_w2$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$cancer)
X <- c(
  sum(ELSA_w2$hedib01==5 | ELSA_w2$hedib02==5 | ELSA_w2$hedib03==5 | ELSA_w2$hedib04==5,na.rm=T),
  sum(ELSA_w2$hedib01==-9,na.rm=T),
  sum(ELSA_w2$hedib01==-8,na.rm=T)
)
BeforeH <- c(length(ELSA_w2$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibX!=5->0","hedibX==5->1","hedibX==-9->997","hedibX==-8->998")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `dhedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_3_elsa_data_v4`|`elsa_w3_hd`| `wave_3_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `998 = Do not know` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |


```{r assign w3, echo=F}

load(paste0(datafolder,"w3/ybirth.RData"))
ELSA_w3 <- left_join(ELSA_w3,ybirth, by="id")
rm(ybirth)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$dhedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1980,2010)

vbl <- ELSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `dhedibca == 1 into 1`
* `dhedibca == 0 into 0`
* `dhedibca == -1 into 996`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$cancer <- car::recode(ELSA_w3$dhedibca,"-1=996")

# Continuous variable harmonization
ELSA_ds_w3$cancer_age <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$cancer_age[which(ELSA_ds_w3$cancer==0)] <- 996
ELSA_ds_w3$cancer_age[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] <- ELSA_w3$heaggry[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] - ELSA_w3$ybirth[which(ELSA_ds_w3$cancer==1 & !ELSA_w3$heaggry %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)]
ELSA_ds_w3$cancer_age <- car::recode(ELSA_ds_w3$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w3$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(40,95)

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$cancer)
BeforeH <- table(ELSA_w3$dhedibca)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("dhedibca==0->0","dhedibca==1->1","dhedibca==-1->996")
kable(C)

```






### Wave 4

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_4_elsa_data_v3`|`elsa_w4_hd`|`wave_4_elsa_data_v3`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-2 = Capi/Interview Error`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |


```{r assign w4, echo=F}

load(paste0(datafolder,"w4/ybirth.RData"))
ELSA_w4 <- left_join(ELSA_w4,ybirth, by="id")
rm(ybirth)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1955,2010)

vbl <- ELSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -1 into 996`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-2 into 991`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$cancer <- car::recode(ELSA_w4$hedibca,"-1=996;-8=998;-9=997")


# Continuous variable harmonization
ELSA_ds_w4$cancer_age <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$cancer_age[which(ELSA_ds_w4$cancer==0)] <- 996
ELSA_ds_w4$cancer_age[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))] <- ELSA_w4$heaggry[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))] - ELSA_w4$ybirth[which(ELSA_ds_w4$cancer==1 & !ELSA_w4$heaggry %in% c(-1,-8,-9,-2))]
ELSA_ds_w4$cancer_age <- car::recode(ELSA_ds_w4$cancer_age, "-1=996;-8=998;-9=997;-2=991;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w4$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$cancer)
BeforeH <- table(ELSA_w4$hedibca)[c(4,5,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-1->996","hedibca==-9->997","hedibca==-8->998")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`heaggry`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_5_elsa_data_v4`|`elsa_w5_hd`|`wave_5_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |

```{r assign w5, echo=F}

load(paste0(datafolder,"w5/ybirth.RData"))
ELSA_w5 <- left_join(ELSA_w5,ybirth, by="id")
rm(ybirth)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$heaggry
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heaggry')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heaggry)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1970,2015)

vbl <- ELSA_w5$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -1 into 996`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = heaggry-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$cancer <- car::recode(ELSA_w5$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w5$cancer_age <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$cancer_age[which(ELSA_ds_w5$cancer==0)] <- 996
ELSA_ds_w5$cancer_age[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))] <- ELSA_w5$heaggry[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))] - ELSA_w5$ybirth[which(ELSA_ds_w5$cancer==1 & !ELSA_w5$heaggry %in% c(-1,-8,-9))]
ELSA_ds_w5$cancer_age <- car::recode(ELSA_ds_w5$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w5$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$cancer)
BeforeH <- table(ELSA_w5$hedibca)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-9->997","hedibca==-8->998")
kable(C)

```





### Wave 6

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`HeAggRY`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_6_elsa_data_v2`|`elsa_w6_hd`|`wave_6_elsa_data_v2`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |


```{r assign w6, echo=F}

load(paste0(datafolder,"w6/ybirth.RData"))
ELSA_w6 <- left_join(ELSA_w6,ybirth, by="id")
rm(ybirth)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1960,2015)

vbl <- ELSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1985)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -9 into 997`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$cancer <- car::recode(ELSA_w6$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w6$cancer_age <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$cancer_age[which(ELSA_ds_w6$cancer==0)] <- 996
ELSA_ds_w6$cancer_age[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w6$HeAggRY[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))] - ELSA_w6$ybirth[which(ELSA_ds_w6$cancer==1 & !ELSA_w6$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w6$cancer_age <- car::recode(ELSA_ds_w6$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w6$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$cancer)
BeforeH <- table(ELSA_w6$hedibca)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-9->997","hedibca==-8->998")
kable(C)

```






### Wave 7

#### Study-specific variable description

| **Name** | `hedibca` |`ybirth`|`HeAggRY`|
|-|-|-|-|
| **Label** |`Chronic: cancer diagnosis newly reported`|`year of birth`|`Year told had cancer since last interview`|
| **Table name**  | `wave_7_elsa_data`|`elsa_w7_hd`|`wave_7_elsa_data`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |

```{r assign w7, echo=F}

load(paste0(datafolder,"w7/ybirth.RData"))
ELSA_w7 <- left_join(ELSA_w7,ybirth, by="id")
rm(ybirth)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$hedibca
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedibca')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedibca))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$HeAggRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAggRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeAggRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1960,2020)

vbl <- ELSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1990)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `hedibca == 1 into 1`
* `hedibca == 0 into 0`
* `hedibca == -8 into 998`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = HeAggRY-ybirth`
* `if cancer == 0, cancer_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, cancer_age = 999`

**R script:**

```{r harmo w7}


# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$cancer <- car::recode(ELSA_w7$hedibca,"-1=996;-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w7$cancer_age <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$cancer_age[which(ELSA_ds_w7$cancer==0)] <- 996
ELSA_ds_w7$cancer_age[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))] <- ELSA_w7$HeAggRY[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))] - ELSA_w7$ybirth[which(ELSA_ds_w7$cancer==1 & !ELSA_w7$HeAggRY %in% c(-1,-8,-9))]
ELSA_ds_w7$cancer_age <- car::recode(ELSA_ds_w7$cancer_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w7$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$cancer)
BeforeH <- table(ELSA_w7$hedibca)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedibca==0->0","hedibca==1->1","hedibca==-8->998")
kable(C)

```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

elsalist <- lmlist # ELSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `cancer` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("ELSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- elsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- elsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))

}



```






## Summary of descriptive statistics of the harmonised variable `cancer_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("ELSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- elsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- elsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```


# Quality estimation

No comments






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```




