---
title: "Oral Health Problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/oral_problemsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/oral_problemsDS.R')
```




# Data process


## England

### Wave 1 

Not found.


### Wave 2

Not found.




### Wave 3

#### Study-specific variable description

| **Name** | `hedent` |
|-|-|
| **Label** | `Whether has own teeth` |
| **Table name** | `wave_3_elsa_data_v4` |
| **Categories** | `1 =  Has no natural teeth and wears dentures` <br/> `2 = Has both natural teeth and denture(s)` <br/> `3 = Has only natural teeth` <br/> `4 = Has neither natural teeth nor dentures` |
| **Missings** | `-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |



```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('hedent'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')
```

```{r local w3, echo=F}
vbl <- ELSA_w3$hedent
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(hedent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `oral_problems` from the study-specific variable it has to be recoded as follows:

* `1,4 into 1`
* `2,3 into 0`
* `-9 into 997`
* `-8 into 998`
* `-1,-2 into 996`

**R script:**

```{r harmo w3}

ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$oral_problems <- car::recode(ELSA_w3$hedent, "c(1,4) = 1; c(2,3) = 0; c(-1,-2) = 996; -9 = 997; -8 = 998 ")

```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$oral_problems
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(oral_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}

```



### Wave 4

Not found.


### Wave 5

#### Study-specific variable description

| **Name** | `hedent` |
|-|-|
| **Label** | `Whether has natural teeth, dentures or neither` |
| **Table name** | `wave_5_elsa_data_v4` |
| **Categories** | `1 =  Has no natural teeth and wears dentures` <br/> `2 = Has both natural teeth and denture(s)` <br/> `3 = Has only natural teeth` <br/> `4 = Has neither natural teeth nor dentures` |
| **Missings** | `-1 = Not applicable`<br/>`-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4', variables=list('hedent'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')
```

```{r local w5, echo=F}
vbl <- ELSA_w5$hedent
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `oral_problems` from the study-specific variable it has to be recoded as follows:

* `1,4 into 1`
* `2,3 into 0`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

**R script:**

```{r harmo w5}

ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$oral_problems <- car::recode(ELSA_w5$hedent, "c(1,4) = 1; c(2,3) = 0; c(-1) = 996; -9 = 997; -8 = 998 ")

```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$oral_problems
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(oral_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w5, echo=F}

```




### Wave 6

Not found.


### Wave 7

#### Study-specific variable description

| **Name** | `HeDntF` |`HeDntG`|
|-|-|-|
| **Label** | `Whether dentures in upper jaw` |`Whether dentures in lower jaw`|
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories** | `1 = Yes` <br/> `2 = No` | `1 = Yes` <br/> `2 = No` |
| **Missings** | `-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |  |



```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('HeDntF','HeDntG'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=F}

vbl <- ELSA_w7$HeDntF
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(HeDntF))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$HeDntG
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w7)[3])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(HeDntG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `oral_problems` from the study-specific variables, they have to be recoded as follows:

* `all 1 into 1`
* `some 2 into 0`
* `-9 into 997`
* `-8 into 998`
* `-1,-2 into 996`

**R script:**

```{r harmo w7}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$oral_problems <- 999
ELSA_ds_w7$oral_problems[which(ELSA_w7$HeDntF == -9 | ELSA_w7$HeDntG == -9)] <- 997
ELSA_ds_w7$oral_problems[which(ELSA_w7$HeDntF == -8 | ELSA_w7$HeDntG == -8)] <- 998
ELSA_ds_w7$oral_problems[which(ELSA_w7$HeDntF %in% c(-1,-2) | ELSA_w7$HeDntG %in% c(-1,-2))] <- 996
ELSA_ds_w7$oral_problems[which(ELSA_w7$HeDntF == 2 | ELSA_w7$HeDntG == 2)] <- 0
ELSA_ds_w7$oral_problems[which(ELSA_w7$HeDntF == 1 & ELSA_w7$HeDntG == 1)] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$oral_problems
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(oral_problems))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w7, echo=F}

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
