---
title: "Respiratory diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
# load("ELSA_w1.rdata")
# load("ELSA_w2.rdata")
# load("ELSA_w2_dv.rdata")
# load("ELSA_w3.rdata")
# load("ELSA_w4.rdata")
# load("ELSA_w5.rdata")
# load("ELSA_w6.rdata")
# load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_respiratory`
* Variable label: `Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`
* Variable description: `The participant has one or more of the following respiratory diseases: respiratory, chronic bronchitis, emphysema, chronic pulmonary disease, chronic obstructive pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no respiratory disease
1        | yes, respiratory disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## England


### Wave 1

#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `997 = Refuse`<br/>`998 = Do not know` |  `997 = Refuse`<br/>`998 = Do not know`  |
| **Description** |  |  |

```{r assign w1, echo=F}

load(paste0(datafolder,"w1/h_asthma.RData"))
load(paste0(datafolder,"w1/h_cpd.RData"))
ELSA_w1 <- tibble(id=h_asthma$id)
ELSA_w1$h_asthma <- h_asthma$h_asthma
ELSA_w1$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w1, echo=F}

vbl <- ELSA_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$h_respiratory <- rep(999,length(ELSA_w1$id))

ELSA_ds_w1$h_respiratory[which(ELSA_w1$h_asthma==0 & ELSA_w1$h_cpd==0)] <- 0
ELSA_ds_w1$h_respiratory[which(ELSA_w1$h_asthma == 1 | ELSA_w1$h_cpd == 1)] <- 1
ELSA_ds_w1$h_respiratory[which((ELSA_w1$h_asthma==997 & (ELSA_w1$h_cpd != 1 | is.na(ELSA_w1$h_cpd))) | (ELSA_w1$h_cpd==997 & (ELSA_w1$h_asthma != 1 | is.na(ELSA_w1$h_asthma))))] <- 997
ELSA_ds_w1$h_respiratory[which((ELSA_w1$h_asthma==998 & (ELSA_w1$h_cpd != 1 | is.na(ELSA_w1$h_cpd))) | (ELSA_w1$h_cpd==998 & (ELSA_w1$h_asthma != 1 | is.na(ELSA_w1$h_asthma))))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$h_respiratory)
X <- c(
  sum(ELSA_w1$h_asthma==0 & ELSA_w1$h_cpd==0,na.rm = T),
  sum(ELSA_w1$h_asthma == 1 | ELSA_w1$h_cpd == 1,na.rm=T),
  sum((ELSA_w1$h_asthma==997 & (ELSA_w1$h_cpd != 1 | is.na(ELSA_w1$h_cpd))) | (ELSA_w1$h_cpd==997 & (ELSA_w1$h_asthma != 1 | is.na(ELSA_w1$h_asthma))),na.rm=T),
  sum((ELSA_w1$h_asthma==998 & (ELSA_w1$h_cpd != 1 | is.na(ELSA_w1$h_cpd))) | (ELSA_w1$h_cpd==998 & (ELSA_w1$h_asthma != 1 | is.na(ELSA_w1$h_asthma))),na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `997 = Refuse`<br/>`998 = Do not know` |  `997 = Refuse`<br/>`998 = Do not know`  |
| **Description** |  |  |

```{r assign w2, echo=F}

load(paste0(datafolder,"w2/h_asthma.RData"))
load(paste0(datafolder,"w2/h_cpd.RData"))
ELSA_w2 <- tibble(id=h_asthma$id)
ELSA_w2$h_asthma <- h_asthma$h_asthma
ELSA_w2$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w2)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)

ELSA_ds_w2$h_respiratory <- rep(999,length(ELSA_ds_w2$id))
ELSA_ds_w2$h_respiratory[which(ELSA_w2$h_asthma == 0 & ELSA_w2$h_cpd == 0)] <- 0
ELSA_ds_w2$h_respiratory[which(ELSA_w2$h_asthma == 1 | ELSA_w2$h_cpd == 1)] <- 1
ELSA_ds_w2$h_respiratory[which((ELSA_w2$h_asthma == 997 & ELSA_w2$h_cpd != 1) | (ELSA_w2$h_cpd == 997 & ELSA_w2$h_asthma != 1))] <- 997
ELSA_ds_w2$h_respiratory[which((ELSA_w2$h_asthma == 998 & ELSA_w2$h_cpd != 1) | (ELSA_w2$h_cpd == 998 & ELSA_w2$h_asthma != 1))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w2$h_respiratory)
X <- c(
  sum(ELSA_w2$h_asthma == 0 & ELSA_w2$h_cpd == 0,na.rm = T),
  sum(ELSA_w2$h_asthma == 1 | ELSA_w2$h_cpd == 1,na.rm=T),
  sum((ELSA_w2$h_asthma == 997 & ELSA_w2$h_cpd != 1) | (ELSA_w2$h_cpd == 997 & ELSA_w2$h_asthma != 1),na.rm=T),
  sum((ELSA_w2$h_asthma == 998 & ELSA_w2$h_cpd != 1) | (ELSA_w2$h_cpd == 998 & ELSA_w2$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `996 = Not applicable` |  `996 = Not applicable`  |
| **Description** |  |  |

```{r assign w3, echo=F}

load(paste0(datafolder,"w3/h_asthma.RData"))
load(paste0(datafolder,"w3/h_cpd.RData"))
ELSA_w3 <- tibble(id=h_asthma$id)
ELSA_w3$h_asthma <- h_asthma$h_asthma
ELSA_w3$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w3)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)

ELSA_ds_w3$h_respiratory <- rep(999,length(ELSA_ds_w3$id))
ELSA_ds_w3$h_respiratory[which(ELSA_w3$h_asthma == 0 & ELSA_w3$h_cpd == 0)] <- 0
ELSA_ds_w3$h_respiratory[which(ELSA_w3$h_asthma == 1 | ELSA_w3$h_cpd == 1)] <- 1
ELSA_ds_w3$h_respiratory[which((ELSA_w3$h_asthma == 996 & ELSA_w3$h_cpd != 1) | (ELSA_w3$h_cpd == 996 & ELSA_w3$h_asthma != 1))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w3$h_respiratory)
X <- c(
  sum(ELSA_w3$h_asthma == 0 & ELSA_w3$h_cpd == 0,na.rm = T),
  sum(ELSA_w3$h_asthma == 1 | ELSA_w3$h_cpd == 1,na.rm=T),
  sum((ELSA_w3$h_asthma == 996 & ELSA_w3$h_cpd != 1) | (ELSA_w3$h_cpd == 996 & ELSA_w3$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","996->996")
kable(C)

```



### Wave 4


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `997 = Refuse`<br/>`998 = Do not know` |  `997 = Refuse`<br/>`998 = Do not know`  |
| **Description** |  |  |

```{r assign w4, echo=F}

load(paste0(datafolder,"w4/h_asthma.RData"))
load(paste0(datafolder,"w4/h_cpd.RData"))
ELSA_w4 <- tibble(id=h_asthma$id)
ELSA_w4$h_asthma <- h_asthma$h_asthma
ELSA_w4$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w4)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)

ELSA_ds_w4$h_respiratory <- rep(999,length(ELSA_ds_w4$id))
ELSA_ds_w4$h_respiratory[which(ELSA_w4$h_asthma == 0 & ELSA_w4$h_cpd == 0)] <- 0
ELSA_ds_w4$h_respiratory[which(ELSA_w4$h_asthma == 1 | ELSA_w4$h_cpd == 1)] <- 1
ELSA_ds_w4$h_respiratory[which((ELSA_w4$h_asthma == 997 & ELSA_w4$h_cpd != 1) | (ELSA_w4$h_cpd == 997 & ELSA_w4$h_asthma != 1))] <- 997
ELSA_ds_w4$h_respiratory[which((ELSA_w4$h_asthma == 998 & ELSA_w4$h_cpd != 1) | (ELSA_w4$h_cpd == 998 & ELSA_w4$h_asthma != 1))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w4$h_respiratory)
X <- c(
  sum(ELSA_w4$h_asthma == 0 & ELSA_w4$h_cpd == 0,na.rm = T),
  sum(ELSA_w4$h_asthma == 1 | ELSA_w4$h_cpd == 1,na.rm=T),
  sum((ELSA_w4$h_asthma == 997 & ELSA_w4$h_cpd != 1) | (ELSA_w4$h_cpd == 997 & ELSA_w4$h_asthma != 1),na.rm=T),
  sum((ELSA_w4$h_asthma == 998 & ELSA_w4$h_cpd != 1) | (ELSA_w4$h_cpd == 998 & ELSA_w4$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998")
kable(C)

```




### Wave 5


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `997 = Refuse`<br/>`998 = Do not know` |  `997 = Refuse`<br/>`998 = Do not know`  |
| **Description** |  |  |

```{r assign w5, echo=F}

load(paste0(datafolder,"w5/h_asthma.RData"))
load(paste0(datafolder,"w5/h_cpd.RData"))
ELSA_w5 <- tibble(id=h_asthma$id)
ELSA_w5$h_asthma <- h_asthma$h_asthma
ELSA_w5$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w5)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)

ELSA_ds_w5$h_respiratory <- rep(999,length(ELSA_ds_w5$id))
ELSA_ds_w5$h_respiratory[which(ELSA_w5$h_asthma == 0 & ELSA_w5$h_cpd == 0)] <- 0
ELSA_ds_w5$h_respiratory[which(ELSA_w5$h_asthma == 1 | ELSA_w5$h_cpd == 1)] <- 1
ELSA_ds_w5$h_respiratory[which((ELSA_w5$h_asthma == 997 & ELSA_w5$h_cpd != 1) | (ELSA_w5$h_cpd == 997 & ELSA_w5$h_asthma != 1))] <- 997
ELSA_ds_w5$h_respiratory[which((ELSA_w5$h_asthma == 998 & ELSA_w5$h_cpd != 1) | (ELSA_w5$h_cpd == 998 & ELSA_w5$h_asthma != 1))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w5$h_respiratory)
X <- c(
  sum(ELSA_w5$h_asthma == 0 & ELSA_w5$h_cpd == 0,na.rm = T),
  sum(ELSA_w5$h_asthma == 1 | ELSA_w5$h_cpd == 1,na.rm=T),
  sum((ELSA_w5$h_asthma == 997 & ELSA_w5$h_cpd != 1) | (ELSA_w5$h_cpd == 997 & ELSA_w5$h_asthma != 1),na.rm=T),
  sum((ELSA_w5$h_asthma == 998 & ELSA_w5$h_cpd != 1) | (ELSA_w5$h_cpd == 998 & ELSA_w5$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998")
kable(C)

```




### Wave 6


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `997 = Refuse`<br/>`998 = Do not know` |  `997 = Refuse`<br/>`998 = Do not know`  |
| **Description** |  |  |

```{r assign w6, echo=F}

load(paste0(datafolder,"w6/h_asthma.RData"))
load(paste0(datafolder,"w6/h_cpd.RData"))
ELSA_w6 <- tibble(id=h_asthma$id)
ELSA_w6$h_asthma <- h_asthma$h_asthma
ELSA_w6$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w6)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)

ELSA_ds_w6$h_respiratory <- rep(999,length(ELSA_ds_w6$id))
ELSA_ds_w6$h_respiratory[which(ELSA_w6$h_asthma == 0 & ELSA_w6$h_cpd == 0)] <- 0
ELSA_ds_w6$h_respiratory[which(ELSA_w6$h_asthma == 1 | ELSA_w6$h_cpd == 1)] <- 1
ELSA_ds_w6$h_respiratory[which((ELSA_w6$h_asthma == 997 & ELSA_w6$h_cpd != 1) | (ELSA_w6$h_cpd == 997 & ELSA_w6$h_asthma != 1))] <- 997
ELSA_ds_w6$h_respiratory[which((ELSA_w6$h_asthma == 998 & ELSA_w6$h_cpd != 1) | (ELSA_w6$h_cpd == 998 & ELSA_w6$h_asthma != 1))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w6$h_respiratory)
X <- c(
  sum(ELSA_w6$h_asthma == 0 & ELSA_w6$h_cpd == 0,na.rm = T),
  sum(ELSA_w6$h_asthma == 1 | ELSA_w6$h_cpd == 1,na.rm=T),
  sum((ELSA_w6$h_asthma == 997 & ELSA_w6$h_cpd != 1) | (ELSA_w6$h_cpd == 997 & ELSA_w6$h_asthma != 1),na.rm=T),
  sum((ELSA_w6$h_asthma == 998 & ELSA_w6$h_cpd != 1) | (ELSA_w6$h_cpd == 998 & ELSA_w6$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","997->997","998->998")
kable(C)

```




### Wave 7


#### Study-specific variable description

| **Name** | `h_asthma` |`h_cpd`|
|-|-|-|
| **Label** | `History of  Asthma` |`History of chronic pulmonary disorders`|
| **Table name**  | `h_asthma` | `h_cpd` |
| **Categories** | `1 = Asthma`<br/>`0 = No asthma` |`1 = chronic pulmonary disease`<br/>`0 = NO chronic pulmonary disease` |
| **Missings** | `998 = Do not know` |  `998 = Do not know`  |
| **Description** |  |  |

```{r assign w7, echo=F}

load(paste0(datafolder,"w7/h_asthma.RData"))
load(paste0(datafolder,"w7/h_cpd.RData"))
ELSA_w7 <- tibble(id=h_asthma$id)
ELSA_w7$h_asthma <- h_asthma$h_asthma
ELSA_w7$h_cpd <- h_cpd$h_cpd
rm(h_asthma)
rm(h_cpd)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(h_asthma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ELSA_w7)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_asthma == 0 and h_cpd == 0 into 0`
* `h_asthma == 1 or h_cpd ==  1 into 1`
* `keep missing values into themselves`

**R script:**

```{r harmo w7}

# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)

ELSA_ds_w7$h_respiratory <- rep(999,length(ELSA_ds_w7$id))
ELSA_ds_w7$h_respiratory[which(ELSA_w7$h_asthma == 0 & ELSA_w7$h_cpd == 0)] <- 0
ELSA_ds_w7$h_respiratory[which(ELSA_w7$h_asthma == 1 | ELSA_w7$h_cpd == 1)] <- 1
ELSA_ds_w7$h_respiratory[which((ELSA_w7$h_asthma == 998 & ELSA_w7$h_cpd != 1) | (ELSA_w7$h_cpd == 998 & ELSA_w7$h_asthma != 1))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w7, echo=F, results='asis'}

AfterH <- table(ELSA_ds_w7$h_respiratory)
X <- c(
  sum(ELSA_w7$h_asthma == 0 & ELSA_w7$h_cpd == 0,na.rm = T),
  sum(ELSA_w7$h_asthma == 1 | ELSA_w7$h_cpd == 1,na.rm=T),
  sum((ELSA_w7$h_asthma == 998 & ELSA_w7$h_cpd != 1) | (ELSA_w7$h_cpd == 998 & ELSA_w7$h_asthma != 1),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","998->998")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]) , length(l.hds[[6]][[2]]), length(l.hds[[7]][[2]])
             )
names(t.hds)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(t.hds)

dbb <- merge(ELSA_m_ds_w1[,c("id","h_respiratory")], ELSA_m_ds_w2[,c("id","h_respiratory")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w3[,c("id","h_respiratory")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4[,c("id","h_respiratory")], by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w5[,c("id","h_respiratory")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6[,c("id","h_respiratory")], by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w7[,c("id","h_respiratory")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2","w3","w4","w5","w6","w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

The harmonizated variable contains information about asthma and chronic lung disease, such as chronic bronchitis and emphysema.
It has been built from the harmonized single disease variables. 


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_respiratory <- l.hds[[index]]
  save(h_respiratory, file = paste0(datafolder,names(l.hds)[index],"/h_respiratory.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





