---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hypertensionDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hypertensionDS.R')
```

```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w2_dv.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 





# Data process




## England


### Wave 1


#### Study-specific variable description


| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` |
|-|-|-|-|-|-|-|-|
| **Label** |`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|
| **Table name**  | `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`|
| **Categories** | `1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |  |  |




```{r assign w1, echo=F}

```

```{r local w1, echo=F}

vbl <- ELSA_w1$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `some hedimX == 1 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$h_hypertension <- rep(0,length(ELSA_w1$id))
ELSA_ds_w1$h_hypertension[which((ELSA_w1$hedim01==1 | ELSA_w1$hedim02==1 | ELSA_w1$hedim03==1 | ELSA_w1$hedim04==1 | ELSA_w1$hedim05==1 | ELSA_w1$hedim06==1 | ELSA_w1$hedim07==1))] <- 1
ELSA_ds_w1$h_hypertension[which(ELSA_w1$hedim01==-9)] <- 997
ELSA_ds_w1$h_hypertension[which(ELSA_w1$hedim01==-8)] <- 998

# Global table
ELSA_ds <- ELSA_ds_w1
ELSA_ds$h_hypertension_age <- rep(999,length(ELSA_ds$id))

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$h_hypertension)
X <- c(
  sum((ELSA_w1$hedim01==1 | ELSA_w1$hedim02==1 | ELSA_w1$hedim03==1 | ELSA_w1$hedim04==1 | ELSA_w1$hedim05==1 | ELSA_w1$hedim06==1 | ELSA_w1$hedim07==1),na.rm=T),
  sum(ELSA_w1$hedim01==-9),
  sum(ELSA_w1$hedim01==-8)
)
BeforeH <- c(length(ELSA_w1$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=1->0","hedimX==1->1","hedimX==-9->997","hedimX==-8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` | `hedim08` | `hedia01`|`ybirth`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Diagnosed cardiovascular condit. newly reported at W2 (1st mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (2nd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (3rd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (4th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (5th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (6th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (7th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (8th mention) (merged var)`|`Diagnosed cardiovascular condition newly reported at W2 (1st mention)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`elsa_w2_hd`|`elsa_w1_hd`|`elsa_w2_hd`|
| **Categories** |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` | `continuous` | `continuous` | `continuous` |
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|   |  |  |
| **Description** |  |  |  |  |  |  |  |  |  |  |  |  |



```{r assign w2, echo=F}

load(paste0(datafolder,"w2/ybirth.RData"))
ELSA_w2 <- left_join(ELSA_w2,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w1/yintw.RData"))
ELSA_w2 <- left_join(ELSA_w2,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
ELSA_w2 <- left_join(ELSA_w2,yintw, by="id",suffix=c("_w1","_w2"))
rm(yintw)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim08
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim08')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim08))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedia01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedia01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedia01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w1)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w2)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension w1 == 1 or some hediaX == 1 into 1`
* `h_hypertension w1 != 1 and hedia01 == -9 into 997`
* `h_hypertension w1 != 1 and hedia01 == -8 into 998`
* `otherwise into 0`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = (year of interview w2-year of interview w1)/2+(year of interview w1 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w2}

ELSA_w2 <- left_join(ELSA_w2,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$h_hypertension <- rep(0,length(ELSA_w2$id))
ELSA_ds_w2$h_hypertension[which(ELSA_w2$h_hypertension==1 | ((ELSA_w2$hedia01==1 | ELSA_w2$hedia02==1 | ELSA_w2$hedia03==1 | ELSA_w2$hedia04==1 | ELSA_w2$hedia05==1 | ELSA_w2$hedia06==1 | ELSA_w2$hedia07==1 | ELSA_w2$hedia08==1)))] <- 1
ELSA_ds_w2$h_hypertension[which((ELSA_w2$h_hypertension!=1 | is.na(ELSA_w2$h_hypertension)) & ELSA_w2$hedia01==-9)] <- 997
ELSA_ds_w2$h_hypertension[which((ELSA_w2$h_hypertension!=1 | is.na(ELSA_w2$h_hypertension)) & ELSA_w2$hedia01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w2$h_hypertension_age <- rep(999,length(ELSA_w2$id))
ELSA_ds_w2$h_hypertension_age[which(ELSA_ds_w2$h_hypertension==0)] <- 996
ELSA_ds_w2$h_hypertension_age[which(ELSA_ds_w2$h_hypertension==1 & ELSA_w2$h_hypertension==0)] <- floor((ELSA_w2$yintw_w2[which(ELSA_ds_w2$h_hypertension==1 & ELSA_w2$h_hypertension==0)] + ELSA_w2$yintw_w1[which(ELSA_ds_w2$h_hypertension==1 & ELSA_w2$h_hypertension==0)])/2 - ELSA_w2$ybirth[which(ELSA_ds_w2$h_hypertension==1 & ELSA_w2$h_hypertension==0)])

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w2,log_vec=ELSA_ds_w2$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w2,log_vec=ELSA_ds_w2$id[which(ELSA_ds_w2$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$h_hypertension_age <- ELSA_ds_aux$h_hypertension_age
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$h_hypertension)
X <- c(
  sum(ELSA_w2$h_hypertension==1 | ((ELSA_w2$hedia01==1 | ELSA_w2$hedia02==1 | ELSA_w2$hedia03==1 | ELSA_w2$hedia04==1 | ELSA_w2$hedia05==1 | ELSA_w2$hedia06==1 | ELSA_w2$hedia07==1 | ELSA_w2$hedia08==1)),na.rm=T),
  sum((ELSA_w2$h_hypertension!=1 | is.na(ELSA_w2$h_hypertension)) & ELSA_w2$hedia01==-9,na.rm=T),
  sum((ELSA_w2$h_hypertension!=1 | is.na(ELSA_w2$h_hypertension)) & ELSA_w2$hedia01==-8,na.rm=T)
)
BeforeH <- c(length(ELSA_w2$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=1->0","hedimX==1->1","hedia01==-9->997","hedia01==-8->998")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `dhedimbp` |`ybirth`|`yintw (w2)`|`yintw (w3)`|
|-|-|-|-|-|
| **Label** |`CVD: high blood pressure diagnosis newly reported (merged)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_3_elsa_data_v4`|`elsa_w3_hd`|`elsa_w2_hd`|`elsa_w3_hd`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`998 = Do not know`|   |  |
| **Description** |  |  |  |  |


```{r assign w3, echo=F}

load(paste0(datafolder,"w3/ybirth.RData"))
ELSA_w3 <- left_join(ELSA_w3,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w2/yintw.RData"))
ELSA_w3 <- left_join(ELSA_w3,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w3/yintw.RData"))
ELSA_w3 <- left_join(ELSA_w3,yintw, by="id",suffix=c("_w2","_w3"))
rm(yintw)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$dhedimbp
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedimbp')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedimbp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$yintw_w2
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w2)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$yintw_w3
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w3)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(yintw_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension previous == 1 or dhedimbp == 1 into 1`
* `h_hypertension previous == 0 and dhedimbp == 0 into 0`
* `dhedimbp == -1 into 996`
* `otherwise into 999`


To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w3 and 0 in w2, h_hypertension_age = (year of interview w3-year of interview w2)/2+(year of interview w2 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w3}

ELSA_w3 <- left_join(ELSA_w3,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$h_hypertension <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$h_hypertension[which((ELSA_w3$h_hypertension!=1 | is.na(ELSA_w3$h_hypertension)) & (ELSA_w3$dhedimbp==0))] <- 0
ELSA_ds_w3$h_hypertension[which(ELSA_w3$h_hypertension==1 | (ELSA_w3$dhedimbp==1))] <- 1
ELSA_ds_w3$h_hypertension[which((ELSA_w3$h_hypertension!=1 | is.na(ELSA_w3$h_hypertension)) & (ELSA_w3$dhedimbp==-1))] <- 996

ELSA_w3 <- left_join(ELSA_w3,ELSA_ds_w2,by="id",suffix=c("","_w2"))

# Continuous variable harmonization
ELSA_ds_w3$h_hypertension_age <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$h_hypertension_age[which(ELSA_ds_w3$h_hypertension==0)] <- 996
ELSA_ds_w3$h_hypertension_age[which(ELSA_ds_w3$h_hypertension==1 & ELSA_w3$h_hypertension_w2==0 & ELSA_w3$ybirth!=998)] <- floor((ELSA_w3$yintw_w2[which(ELSA_ds_w3$h_hypertension==1 & ELSA_w3$h_hypertension_w2==0 & ELSA_w3$ybirth!=998)] + ELSA_w3$yintw_w3[which(ELSA_ds_w3$h_hypertension==1 & ELSA_w3$h_hypertension_w2==0 & ELSA_w3$ybirth!=998)])/2 - ELSA_w3$ybirth[which(ELSA_ds_w3$h_hypertension==1 & ELSA_w3$h_hypertension_w2==0 & ELSA_w3$ybirth!=998)])
ELSA_ds_w3$h_hypertension_age[which(ELSA_ds_w3$h_hypertension==1 & !is.na(ELSA_w3$h_hypertension_age) & !ELSA_w3$h_hypertension_age %in% miss_values_vector)] <- ELSA_w3$h_hypertension_age[which(ELSA_ds_w3$h_hypertension==1 & !is.na(ELSA_w3$h_hypertension_age) & !ELSA_w3$h_hypertension_age %in% miss_values_vector)]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w3,log_vec=ELSA_ds_w3$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w3,log_vec=ELSA_ds_w3$id[which(ELSA_ds_w3$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$h_hypertension_age <- ELSA_ds_aux$h_hypertension_age
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w3$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$h_hypertension)
X <- c(
  sum((ELSA_w3$h_hypertension!=1 | is.na(ELSA_w3$h_hypertension)) & (ELSA_w3$dhedimbp==0),na.rm=T),
  sum(ELSA_w3$h_hypertension==1 | (ELSA_w3$dhedimbp==1),na.rm=T),
  sum((ELSA_w3$h_hypertension!=1 | is.na(ELSA_w3$h_hypertension)) & (ELSA_w3$dhedimbp==-1),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("dhedimbp==0->0","dhedimbp==1->1","dhedimbp==-1->996")
kable(C)

```






### Wave 4

#### Study-specific variable description

| **Name** | `hedimbp` |`ybirth`|`yintw (w3)`|`yintw (w4)`|
|-|-|-|-|-|-|
| **Label** |`CVD: high blood pressure diagnosis newly reported (merged)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_4_elsa_data_v3`|`elsa_w4_hd`|`elsa_w3_hd`|`elsa_w4_hd`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |   |  |
| **Description** |  |  |  |  |


```{r assign w4, echo=F}

load(paste0(datafolder,"w4/ybirth.RData"))
ELSA_w4 <- left_join(ELSA_w4,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w3/yintw.RData"))
ELSA_w4 <- left_join(ELSA_w4,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w4/yintw.RData"))
ELSA_w4 <- left_join(ELSA_w4,yintw, by="id",suffix=c("_w3","_w4"))
rm(yintw)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$hedimbp
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimbp')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedimbp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$yintw_w4
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w4)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(yintw_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$yintw_w3
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w3)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(yintw_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension previous == 1 or hedimbp == 1 into 1`
* `h_hypertension previous == 0 and hedimbp == 0 into 0`
* `hedimbp == -9 into 997`
* `hedimbp == -8 into 998`
* `otherwise into 999`


To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w4 and 0 in w3, h_hypertension_age = (year of interview w4-year of interview w3)/2+(year of interview w3 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w4}

ELSA_w4 <- left_join(ELSA_w4,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$h_hypertension <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$h_hypertension[which((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & (ELSA_w4$hedimbp==0))] <- 0
ELSA_ds_w4$h_hypertension[which(ELSA_w4$h_hypertension==1 | (ELSA_w4$hedimbp==1))] <- 1
ELSA_ds_w4$h_hypertension[which((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & ELSA_w4$hedimbp==-9)] <- 997
ELSA_ds_w4$h_hypertension[which((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & ELSA_w4$hedimbp==-8)] <- 998

ELSA_w4 <- left_join(ELSA_w4,ELSA_ds_w3,by="id",suffix=c("","_w3"))

# Continuous variable harmonization
ELSA_ds_w4$h_hypertension_age <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$h_hypertension_age[which(ELSA_ds_w4$h_hypertension==0)] <- 996
ELSA_ds_w4$h_hypertension_age[which(ELSA_ds_w4$h_hypertension==1 & ELSA_w4$h_hypertension_w3==0)] <- floor((ELSA_w4$yintw_w3[which(ELSA_ds_w4$h_hypertension==1 & ELSA_w4$h_hypertension_w3==0)] + ELSA_w4$yintw_w4[which(ELSA_ds_w4$h_hypertension==1 & ELSA_w4$h_hypertension_w3==0)])/2 - ELSA_w4$ybirth[which(ELSA_ds_w4$h_hypertension==1 & ELSA_w4$h_hypertension_w3==0)])
ELSA_ds_w4$h_hypertension_age[which(ELSA_ds_w4$h_hypertension==1 & !is.na(ELSA_w4$h_hypertension_age) & !ELSA_w4$h_hypertension_age %in% miss_values_vector)] <- ELSA_w4$h_hypertension_age[which(ELSA_ds_w4$h_hypertension==1 & !is.na(ELSA_w4$h_hypertension_age) & !ELSA_w4$h_hypertension_age %in% miss_values_vector)]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w4,log_vec=ELSA_ds_w4$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w4,log_vec=ELSA_ds_w4$id[which(ELSA_ds_w4$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$h_hypertension_age <- ELSA_ds_aux$h_hypertension_age
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w4$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$h_hypertension)
X <- c(
  sum((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & (ELSA_w4$hedimbp==0),na.rm=T),
  sum(ELSA_w4$h_hypertension==1 | (ELSA_w4$hedimbp==1),na.rm=T),
  sum((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & ELSA_w4$hedimbp==-9,na.rm=T),
  sum((ELSA_w4$h_hypertension!=1 | is.na(ELSA_w4$h_hypertension)) & ELSA_w4$hedimbp==-8,na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimbp==0->0","hedimbp==1->1","hedimbp==-9->997","hedimbp==-8->998")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `hedimbp` |`ybirth`|`yintw (w4)`|`yintw (w5)`|
|-|-|-|-|-|-|
| **Label** |`CVD: high blood pressure diagnosis newly reported (merged)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_5_elsa_data_v4`|`elsa_w5_hd`|`elsa_w4_hd`|`elsa_w5_hd`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |  |  |
| **Description** |  |  |  |  |


```{r assign w5, echo=F}

load(paste0(datafolder,"w5/ybirth.RData"))
ELSA_w5 <- left_join(ELSA_w5,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w4/yintw.RData"))
ELSA_w5 <- left_join(ELSA_w5,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w5/yintw.RData"))
ELSA_w5 <- left_join(ELSA_w5,yintw, by="id",suffix=c("_w4","_w5"))
rm(yintw)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$hedimbp
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimbp')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedimbp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$yintw_w4
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w4)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(yintw_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$yintw_w5
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w5)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(yintw_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension previous == 1 or hedimbp == 1 into 1`
* `h_hypertension previous == 0 and hedimbp == 0 into 0`
* `hedimbp == -9 into 997`
* `hedimbp == -8 into 998`
* `otherwise into 999`


To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w5 and 0 in w4, h_hypertension_age = (year of interview w5-year of interview w4)/2+(year of interview w4 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w5}

ELSA_w5 <- left_join(ELSA_w5,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$h_hypertension <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$h_hypertension[which((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & (ELSA_w5$hedimbp==0))] <- 0
ELSA_ds_w5$h_hypertension[which(ELSA_w5$h_hypertension==1 | (ELSA_w5$hedimbp==1))] <- 1
ELSA_ds_w5$h_hypertension[which((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & ELSA_w5$hedimbp==-9)] <- 997
ELSA_ds_w5$h_hypertension[which((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & ELSA_w5$hedimbp==-8)] <- 998

ELSA_w5 <- left_join(ELSA_w5,ELSA_ds_w4,by="id",suffix=c("","_w4"))

# Continuous variable harmonization
ELSA_ds_w5$h_hypertension_age <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$h_hypertension_age[which(ELSA_ds_w5$h_hypertension==0)] <- 996
ELSA_ds_w5$h_hypertension_age[which(ELSA_ds_w5$h_hypertension==1 & ELSA_w5$h_hypertension_w4==0)] <- floor((ELSA_w5$yintw_w5[which(ELSA_ds_w5$h_hypertension==1 & ELSA_w5$h_hypertension_w4==0)] + ELSA_w5$yintw_w4[which(ELSA_ds_w5$h_hypertension==1 & ELSA_w5$h_hypertension_w4==0)])/2 - ELSA_w5$ybirth[which(ELSA_ds_w5$h_hypertension==1 & ELSA_w5$h_hypertension_w4==0)])
ELSA_ds_w5$h_hypertension_age[which(ELSA_ds_w5$h_hypertension==1 & !is.na(ELSA_w5$h_hypertension_age) & !ELSA_w5$h_hypertension_age %in% miss_values_vector)] <- ELSA_w5$h_hypertension_age[which(ELSA_ds_w5$h_hypertension==1 & !is.na(ELSA_w5$h_hypertension_age) & !ELSA_w5$h_hypertension_age %in% miss_values_vector)]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w5,log_vec=ELSA_ds_w5$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w5,log_vec=ELSA_ds_w5$id[which(ELSA_ds_w5$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$h_hypertension_age <- ELSA_ds_aux$h_hypertension_age
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w5$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$h_hypertension)
X <- c(
  sum((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & (ELSA_w5$hedimbp==0),na.rm=T),
  sum(ELSA_w5$h_hypertension==1 | (ELSA_w5$hedimbp==1),na.rm=T),
  sum((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & ELSA_w5$hedimbp==-9,na.rm=T),
  sum((ELSA_w5$h_hypertension!=1 | is.na(ELSA_w5$h_hypertension)) & ELSA_w5$hedimbp==-8,na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimbp==0->0","hedimbp==1->1","hedimbp==-9->997","hedimbp==-8->998")
kable(C)

```





### Wave 6

#### Study-specific variable description

| **Name** | `hedimbp` |`ybirth`|`yintw (w5)`|`yintw (w6)`|
|-|-|-|-|-|
| **Label** |`CVD: high blood pressure diagnosis newly reported (merged)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_6_elsa_data_v2`|`elsa_w6_hd`|`elsa_w5_hd`|`elsa_w6_hd`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |   |  |
| **Description** |  |  |  |  |


```{r assign w6, echo=F}

load(paste0(datafolder,"w6/ybirth.RData"))
ELSA_w6 <- left_join(ELSA_w6,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w5/yintw.RData"))
ELSA_w6 <- left_join(ELSA_w6,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w6/yintw.RData"))
ELSA_w6 <- left_join(ELSA_w6,yintw, by="id",suffix=c("_w5","_w6"))
rm(yintw)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$hedimbp
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimbp')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedimbp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$yintw_w6
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w6)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(yintw_w6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$yintw_w5
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w5)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(yintw_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension previous == 1 or hedimbp == 1 into 1`
* `h_hypertension previous == 0 and hedimbp == 0 into 0`
* `hedimbp == -9 into 997`
* `hedimbp == -8 into 998`
* `otherwise into 999`


To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w6 and 0 in w5, h_hypertension_age = (year of interview w6-year of interview w5)/2+(year of interview w5 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w6}

ELSA_w6 <- left_join(ELSA_w6,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$h_hypertension <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$h_hypertension[which((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & (ELSA_w6$hedimbp==0))] <- 0
ELSA_ds_w6$h_hypertension[which(ELSA_w6$h_hypertension==1 | (ELSA_w6$hedimbp==1))] <- 1
ELSA_ds_w6$h_hypertension[which((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & ELSA_w6$hedimbp==-9)] <- 997
ELSA_ds_w6$h_hypertension[which((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & ELSA_w6$hedimbp==-8)] <- 998

ELSA_w6 <- left_join(ELSA_w6,ELSA_ds_w5,by="id",suffix=c("","_w5"))

# Continuous variable harmonization
ELSA_ds_w6$h_hypertension_age <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$h_hypertension_age[which(ELSA_ds_w6$h_hypertension==0)] <- 996
ELSA_ds_w6$h_hypertension_age[which(ELSA_ds_w6$h_hypertension==1 & ELSA_w6$h_hypertension_w5==0)] <- floor((ELSA_w6$yintw_w5[which(ELSA_ds_w6$h_hypertension==1 & ELSA_w6$h_hypertension_w5==0)] + ELSA_w6$yintw_w6[which(ELSA_ds_w6$h_hypertension==1 & ELSA_w6$h_hypertension_w5==0)])/2 - ELSA_w6$ybirth[which(ELSA_ds_w6$h_hypertension==1 & ELSA_w6$h_hypertension_w5==0)])
ELSA_ds_w6$h_hypertension_age[which(ELSA_ds_w6$h_hypertension==1 & !is.na(ELSA_w6$h_hypertension_age) & !ELSA_w6$h_hypertension_age %in% miss_values_vector)] <- ELSA_w6$h_hypertension_age[which(ELSA_ds_w6$h_hypertension==1 & !is.na(ELSA_w6$h_hypertension_age) & !ELSA_w6$h_hypertension_age %in% miss_values_vector)]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w6,log_vec=ELSA_ds_w6$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w6,log_vec=ELSA_ds_w6$id[which(ELSA_ds_w6$h_hypertension != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$h_hypertension_age <- ELSA_ds_aux$h_hypertension_age
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w6$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$h_hypertension)
X <- c(
  sum((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & (ELSA_w6$hedimbp==0),na.rm=T),
  sum(ELSA_w6$h_hypertension==1 | (ELSA_w6$hedimbp==1),na.rm=T),
  sum((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & ELSA_w6$hedimbp==-9,na.rm=T),
  sum((ELSA_w6$h_hypertension!=1 | is.na(ELSA_w6$h_hypertension)) & ELSA_w6$hedimbp==-8,na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimbp==0->0","hedimbp==1->1","hedimbp==-9->997","hedimbp==-8->998")
kable(C)

```






### Wave 7

#### Study-specific variable description

| **Name** | `hedimbp` |`ybirth`|`yintw (w5)`|`yintw (w6)`|
|-|-|-|-|-|
| **Label** |`CVD: high blood pressure diagnosis newly reported (merged)`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `wave_7_elsa_data`|`elsa_w7_hd`|`elsa_w6_hd`|`elsa_w7_hd`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  |   |  |
| **Description** |  |  |  |  |



```{r assign w7, echo=F}

load(paste0(datafolder,"w7/ybirth.RData"))
ELSA_w7 <- left_join(ELSA_w7,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w6/yintw.RData"))
ELSA_w7 <- left_join(ELSA_w7,yintw, by="id")
rm(yintw)
load(paste0(datafolder,"w7/yintw.RData"))
ELSA_w7 <- left_join(ELSA_w7,yintw, by="id",suffix=c("_w6","_w7"))
rm(yintw)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$hedimbp
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimbp')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedimbp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$yintw_w6
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w6)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(yintw_w6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$yintw_w7
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = 'yintw (w7)')
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(yintw_w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_hypertension previous == 1 or hedimbp == 1 into 1`
* `h_hypertension previous == 0 and hedimbp == 0 into 0`
* `h_hypertension previous == 0 and hedimbp == -9 into 997`
* `h_hypertension previous == 0 and hedimbp == -8 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w7 and 0 in w6, h_hypertension_age = (year of interview w7-year of interview w6)/2+(year of interview w6 - ybirth)`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise, h_hypertension_age = 999`

**R script:**

```{r harmo w7}

ELSA_w7 <- left_join(ELSA_w7,ELSA_ds,by="id")

# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$h_hypertension <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$h_hypertension[which((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & (ELSA_w7$hedimbp==0))] <- 0
ELSA_ds_w7$h_hypertension[which(ELSA_w7$h_hypertension==1 | ELSA_w7$hedimbp==1)] <- 1
ELSA_ds_w7$h_hypertension[which((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & ELSA_w7$hedimbp==-9)] <- 997
ELSA_ds_w7$h_hypertension[which((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & ELSA_w7$hedimbp==-8)] <- 998

ELSA_w7 <- left_join(ELSA_w7,ELSA_ds_w6,by="id",suffix=c("","_w6"))

# Continuous variable harmonization
ELSA_ds_w7$h_hypertension_age <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$h_hypertension_age[which(ELSA_ds_w7$h_hypertension==0)] <- 996
ELSA_ds_w7$h_hypertension_age[which(ELSA_ds_w7$h_hypertension==1 & ELSA_w7$h_hypertension_w6==0)] <- floor((ELSA_w7$yintw_w6[which(ELSA_ds_w7$h_hypertension==1 & ELSA_w7$h_hypertension_w6==0)] + ELSA_w7$yintw_w7[which(ELSA_ds_w7$h_hypertension==1 & ELSA_w7$h_hypertension_w6==0)])/2 - ELSA_w7$ybirth[which(ELSA_ds_w7$h_hypertension==1 & ELSA_w7$h_hypertension_w6==0)])
ELSA_ds_w7$h_hypertension_age[which(ELSA_ds_w7$h_hypertension==1 & !is.na(ELSA_w7$h_hypertension_age) & !ELSA_w7$h_hypertension_age %in% miss_values_vector)] <- ELSA_w7$h_hypertension_age[which(ELSA_ds_w7$h_hypertension==1 & !is.na(ELSA_w7$h_hypertension_age) & !ELSA_w7$h_hypertension_age %in% miss_values_vector)]


# Update of global table
rm(ELSA_ds)

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w7$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue", data = . %>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$h_hypertension)
X <- c(
  sum((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & (ELSA_w7$hedimbp==0),na.rm=T),
  sum(ELSA_w7$h_hypertension==1 | ELSA_w7$hedimbp==1,na.rm=T),
  sum((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & ELSA_w7$hedimbp==-9,na.rm=T),
  sum((ELSA_w7$h_hypertension!=1 | is.na(ELSA_w7$h_hypertension)) & ELSA_w7$hedimbp==-8,na.rm=T)
)
BeforeH <- c(X[1:4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimbp==0->0","hedimbp==1->1","hedimbp==-9->997","hedimbp==-8->998")
kable(C)

```


<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

elsalist <- lmlist # ELSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_hypertension` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("ELSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- elsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- elsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))

}



```






## Summary of descriptive statistics of the harmonised variable `h_hypertension_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("ELSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- elsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- elsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```


# Quality estimation

* We assume that if an individual answers it has hypertension in one wave, it has for all the next waves.







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```




