---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
```{r load, echo=F}
# Loading local datasets of ELSA for domain diseases:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w2_dv.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `stroke`
* Variable label: `Stroke`
* Variable description: `Diagnosis of stroke or cerebral vascular disease since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT A stroke (cerebral vascular disease) 
1        | A stroke (cerebral vascular disease)

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `stroke_age`
* Variable label: `Age of each episode of stroke`
* Variable description: `Age of each episode of stroke`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke"
ds_label_age <- "Age of each episode of stroke"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## England


### Wave 1


#### Study-specific variable description

| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` |`heage`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`MERGED - Has a doctor ever told you that you [have/have had] any of the conditions in this card? {heart conditions}`|`Approximately how old were you when first told by a doctor that you had a stroke? {years}`|
| **Table name**  | `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`| `wave_1_core_data_v3`|
| **Categories** | `1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |  |  |  |  |  |



```{r assign w1, echo=F}

```

```{r local w1, echo=F}

vbl <- ELSA_w1$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$heage
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'heage')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,95)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `some hedimX == 8 into 1`
* `-9 into 997`
* `-8 into 998`
* `otherwise into 0`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = heage`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$stroke <- rep(0,length(ELSA_w1$id))
ELSA_ds_w1$stroke[which(ELSA_w1$hedim01==8 | ELSA_w1$hedim02==8 | ELSA_w1$hedim03==8 | ELSA_w1$hedim04==8 | ELSA_w1$hedim05==8 | ELSA_w1$hedim06==8 | ELSA_w1$hedim07==8)] <- 1
ELSA_ds_w1$stroke[which(ELSA_w1$hedim01==-9)] <- 997
ELSA_ds_w1$stroke[which(ELSA_w1$hedim01==-8)] <- 998

# Continuous variable harmonization
ELSA_ds_w1$stroke_age <- rep(999,length(ELSA_w1$id))
ELSA_ds_w1$stroke_age[which(ELSA_ds_w1$stroke==0)] <- 996
ELSA_ds_w1$stroke_age[which(ELSA_ds_w1$stroke==1)] <- car::recode(ELSA_w1$heage[which(ELSA_ds_w1$stroke==1)],"-1=996;-8=998;-9=997")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,110)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$stroke)
X <- c(
  sum(ELSA_w1$hedim01==8 | ELSA_w1$hedim02==8 | ELSA_w1$hedim03==8 | ELSA_w1$hedim04==8 | ELSA_w1$hedim05==8 | ELSA_w1$hedim06==8 | ELSA_w1$hedim07==8,na.rm=T),
  sum(ELSA_w1$hedim01==-9),
  sum(ELSA_w1$hedim01==-8)
)
BeforeH <- c(length(ELSA_w1$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=8->0","hedimX==8->1","hedimX==-9->997","hedimX==-8->998")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `hedim01` | `hedim02` | `hedim03` | `hedim04` | `hedim05` | `hedim06` | `hedim07` | `hedim08` | `hedia01`|`HeAgeRY`|`ybirth`|
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Diagnosed cardiovascular condit. newly reported at W2 (1st mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (2nd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (3rd mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (4th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (5th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (6th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (7th mention) (merged var)`|`Diagnosed cardiovascular condit. newly reported at W2 (8th mention) (merged var)`|`Diagnosed cardiovascular condition newly reported at W2 (1st mention)`|`Year told had stroke in last 2 years`|`year of birth`|
| **Table name**  | `wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`| `wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|`ybirth`|
| **Categories** |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`51 = Valvular heart disease`<br/>`52 = Ischaemic heart disease (incl. Bypass grafts)`<br/>`85 = Other answer - not codeable 01 to 08`<br/>`86 = Irrelevant response - not codeable 01 to 08`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` |`1 = High blood pressure or hypertension`<br/>`2 = Angina`<br/>`3 = A heart attack (including myocardial infarction or coronary)`<br/>`4 = Congestive heart failure`<br/>`5 = A heart murmur`<br/>`6 = An abnormal heart rhythm`<br/>`7 = Diabetes or high blood sugar`<br/>`8 = A stroke (cerebral vascular disease)`<br/>`9 = High cholesterol`<br/>`95 = Any other heart trouble (SPECIFY)`<br/>`96 = None of these` | `continuous` | `continuous` |
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |`-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|  |
| **Description** |  |  |  |  |  |  |  |  |  |  |  |


```{r assign w2, echo=F}

load(paste0(datafolder,"w2/ybirth.RData"))
ELSA_w2 <- left_join(ELSA_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- ELSA_w2$hedim01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim02
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim02')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim03
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim03')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim04
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim04')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim04))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim05
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim05')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim06
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim06')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim07
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim07')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedim08
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedim08')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedim08))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$hedia01
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedia01')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(hedia01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$HeAgeRY
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'HeAgeRY')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeAgeRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1990,2010)

vbl <- ELSA_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `some hedimX == 8 into 1`
* `hedia01 == -9 and hedimX == -1 into 997`
* `hedia01 == -8 and hedimX == -1 into 998`
* `otherwise into 0`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = HeAgeRY - ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$stroke <- rep(0,length(ELSA_w2$id))
ELSA_ds_w2$stroke[which(ELSA_w2$hedim01==8 | ELSA_w2$hedim02==8 | ELSA_w2$hedim03==8 | ELSA_w2$hedim04==8 | ELSA_w2$hedim05==8 | ELSA_w2$hedim06==8 | ELSA_w2$hedim07==8 | ELSA_w2$hedim08==8)] <- 1
ELSA_ds_w2$stroke[which(ELSA_w2$hedia01==-9 & ELSA_w2$hedim01==-1)] <- 997
ELSA_ds_w2$stroke[which(ELSA_w2$hedia01==-8 & ELSA_w2$hedim01==-1)] <- 998

# Continuous variable harmonization
ELSA_ds_w2$stroke_age <- rep(999,length(ELSA_w2$id))
ELSA_ds_w2$stroke_age[which(ELSA_ds_w2$stroke==0)] <- 996
ELSA_ds_w2$stroke_age[which(ELSA_ds_w2$stroke==1 & !ELSA_w2$HeAgeRY %in% c(-1,-8,-9))] <- ELSA_w2$HeAgeRY[which(ELSA_ds_w2$stroke==1 & !ELSA_w2$HeAgeRY %in% c(-1,-8,-9))] - ELSA_w2$ybirth[which(ELSA_ds_w2$stroke==1 & !ELSA_w2$HeAgeRY %in% c(-1,-8,-9))]
ELSA_ds_w2$stroke_age <- car::recode(ELSA_ds_w2$stroke_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,95)

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$stroke)
X <- c(
  sum(ELSA_w2$hedim01==8 | ELSA_w2$hedim02==8 | ELSA_w2$hedim03==8 | ELSA_w2$hedim04==8 | ELSA_w2$hedim05==8 | ELSA_w2$hedim06==8 | ELSA_w2$hedim07==8 | ELSA_w2$hedim08==8,na.rm=T),
  sum(ELSA_w2$hedim01==-1 & ELSA_w2$hedia01==-9,na.rm=T),
  sum(ELSA_w2$hedim01==-1 & ELSA_w2$hedia01==-8,na.rm=T)
)
BeforeH <- c(length(ELSA_w2$id)-sum(X),X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimX!=8->0","hedimX==8->1","hedimX==-9->997","hedimX==-8->998")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `dhedimst` |`ybirth`|`heagery`|
|-|-|-|-|
| **Label** |`CVD: stroke diagnosis newly reported (merged)`|`year of birth`|`Year told had stroke since last interview`|
| **Table name**  | `wave_3_elsa_data_v4`|`ybirth`|`wave_3_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |  `998 = Do not know` | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |  |  |


```{r assign w3, echo=F}

load(paste0(datafolder,"w3/ybirth.RData"))
ELSA_w3 <- left_join(ELSA_w3,ybirth, by="id")
rm(ybirth)

```

```{r local w3, echo=F}

vbl <- ELSA_w3$dhedimst
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'dhedimst')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(dhedimst))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1990)

vbl <- ELSA_w3$heagery
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1))[3], caption = 'heagery')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heagery)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1990,2010)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `dhedimst == 1 into 1`
* `dhedimst == 0 into 0`
* `dhedimst == -1 into 996`


To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = heagery - ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$stroke <- car::recode(ELSA_w3$dhedimst,"-1=996")

# Continuous variable harmonization
ELSA_ds_w3$stroke_age <- rep(999,length(ELSA_w3$id))
ELSA_ds_w3$stroke_age[which(ELSA_ds_w3$stroke==0)] <- 996
ELSA_ds_w3$stroke_age[which(ELSA_ds_w3$stroke==1 & !ELSA_w3$heagery %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] <- ELSA_w3$heagery[which(ELSA_ds_w3$stroke==1 & !ELSA_w3$heagery %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)] - ELSA_w3$ybirth[which(ELSA_ds_w3$stroke==1 & !ELSA_w3$heagery %in% c(-1,-8,-9) & ELSA_w3$ybirth!=998)]
ELSA_ds_w3$stroke_age <- car::recode(ELSA_ds_w3$stroke_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w3$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(40,95)

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$stroke)
BeforeH <- table(ELSA_w3$dhedimst)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("dhedimst==0->0","dhedimst==1->1","dhedimst==-1->996")
kable(C)

```






### Wave 4

#### Study-specific variable description

| **Name** | `hedimst` |`ybirth`|`heagery`|
|-|-|-|-|
| **Label** |`CVD: stroke diagnosis newly reported (merged)`|`year of birth`|`Year told had stroke since last interview`|
| **Table name**  | `wave_4_elsa_data_v3`|`ybirth`|`wave_4_elsa_data_v3`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-2 = Capi/Interview Error`<br/>`-1 = Not applicable`|
| **Description** |  |  |  |


```{r assign w4, echo=F}

load(paste0(datafolder,"w4/ybirth.RData"))
ELSA_w4 <- left_join(ELSA_w4,ybirth, by="id")
rm(ybirth)

```

```{r local w4, echo=F}

vbl <- ELSA_w4$hedimst
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimst')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(hedimst))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$heagery
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heagery')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heagery)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1990,2010)

vbl <- ELSA_w4$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w4, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `hedimst == 1 into 1`
* `hedimst == -9 into 997`
* `hedimst == -8 into 998`
* `hedimst == 0 into 0`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = heagery-ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-2 into 991`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$stroke <- car::recode(ELSA_w4$hedimst,"-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w4$stroke_age <- rep(999,length(ELSA_w4$id))
ELSA_ds_w4$stroke_age[which(ELSA_ds_w4$stroke==0)] <- 996
ELSA_ds_w4$stroke_age[which(ELSA_ds_w4$stroke==1 & !ELSA_w4$heagery %in% c(-1,-8,-9,-2))] <- ELSA_w4$heagery[which(ELSA_ds_w4$stroke==1 & !ELSA_w4$heagery %in% c(-1,-8,-9,-2))] - ELSA_w4$ybirth[which(ELSA_ds_w4$stroke==1 & !ELSA_w4$heagery %in% c(-1,-8,-9,-2))]
ELSA_ds_w4$stroke_age <- car::recode(ELSA_ds_w4$stroke_age, "-1=996;-8=998;-9=997;-2=991;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w4$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,100)

```


#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$stroke)
BeforeH <- table(ELSA_w4$hedimst)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimst==0->0","hedimst==1->1","hedimst==-9->997","hedimst==-8->998")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `hedimst` |`ybirth`|`heagery`|
|-|-|-|-|
| **Label** |`CVD: stroke diagnosis newly reported (merged)`|`year of birth`|`Year told had heart attack since last interview`|
| **Table name**  | `wave_5_elsa_data_v4`|`ybirth`|`wave_5_elsa_data_v4`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |   | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |
| **Description** |  |  |  |


```{r assign w5, echo=F}

load(paste0(datafolder,"w5/ybirth.RData"))
ELSA_w5 <- left_join(ELSA_w5,ybirth, by="id")
rm(ybirth)

```

```{r local w5, echo=F}

vbl <- ELSA_w5$hedimst
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimst')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(hedimst))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$heagery
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'heagery')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heagery)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1975,2015)

vbl <- ELSA_w5$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w5, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1985)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `hedimst == 1 into 1`
* `hedimst == -9 into 997`
* `hedimst == -8 into 998`
* `hedimst == 0 into 0`


To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = heagery - ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$stroke <- car::recode(ELSA_w5$hedimst,"-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w5$stroke_age <- rep(999,length(ELSA_w5$id))
ELSA_ds_w5$stroke_age[which(ELSA_ds_w5$stroke==0)] <- 996
ELSA_ds_w5$stroke_age[which(ELSA_ds_w5$stroke==1 & !ELSA_w5$heagery %in% c(-1,-8,-9))] <- ELSA_w5$heagery[which(ELSA_ds_w5$stroke==1 & !ELSA_w5$heagery %in% c(-1,-8,-9))] - ELSA_w5$ybirth[which(ELSA_ds_w5$stroke==1 & !ELSA_w5$heagery %in% c(-1,-8,-9))]
ELSA_ds_w5$stroke_age <- car::recode(ELSA_ds_w5$stroke_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w5$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(30,95)

```


#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$stroke)
BeforeH <- table(ELSA_w5$hedimst)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimst==0->0","hedimst==1->1","hedimst==-9->997","hedimst==-8->998")
kable(C)

```





### Wave 6

#### Study-specific variable description

| **Name** | `hedimst` |`ybirth`|`HeAgeRY`|
|-|-|-|-|
| **Label** |`CVD: stroke diagnosis newly reported (merged)`|`year of birth`|`Year told had heart attack since last interview`|
| **Table name**  | `wave_6_elsa_data_v2`|`ybirth`|`wave_6_elsa_data_v2`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |    | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |  |  |


```{r assign w6, echo=F}

load(paste0(datafolder,"w6/ybirth.RData"))
ELSA_w6 <- left_join(ELSA_w6,ybirth, by="id")
rm(ybirth)

```

```{r local w6, echo=F}

vbl <- ELSA_w6$hedimst
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimst')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(hedimst))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$HeAgeRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAgeRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeAgeRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1980,2015)

vbl <- ELSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1985)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `hedimst == 1 into 1`
* `hedimst == -9 into 997`
* `hedimst == -8 into 998`
* `hedimst == 0 into 0`


To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = HeAgeRY - ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$stroke <- car::recode(ELSA_w6$hedimst,"-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w6$stroke_age <- rep(999,length(ELSA_w6$id))
ELSA_ds_w6$stroke_age[which(ELSA_ds_w6$stroke==0)] <- 996
ELSA_ds_w6$stroke_age[which(ELSA_ds_w6$stroke==1 & !ELSA_w6$HeAgeRY %in% c(-1,-8,-9))] <- ELSA_w6$HeAgeRY[which(ELSA_ds_w6$stroke==1 & !ELSA_w6$HeAgeRY %in% c(-1,-8,-9))] - ELSA_w6$ybirth[which(ELSA_ds_w6$stroke==1 & !ELSA_w6$HeAgeRY %in% c(-1,-8,-9))]
ELSA_ds_w6$stroke_age <- car::recode(ELSA_ds_w6$stroke_age, "-1=996;-8=998;-9=997;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w6$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,95)

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$stroke)
BeforeH <- table(ELSA_w6$hedimst)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimst==0->0","hedimst==1->1","hedimst==-9->997","hedimst==-8->998")
kable(C)

```






### Wave 7

#### Study-specific variable description

| **Name** | `hedimst` |`ybirth`|`HeAgeRY`|
|-|-|-|-|
| **Label** |`CVD: stroke diagnosis newly reported (merged)`|`year of birth`|`Year told had heart attack since last interview`|
| **Table name**  | `wave_7_elsa_data`|`ybirth`|`wave_7_elsa_data`|
| **Categories** |`1 = Mentioned`<br/>`0 = Not mentioned`|`continuous`|`continuous`|
| **Missings** | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable` |    | `-9 = Refusal`<br/>`-8 = Don't know`<br/>`-1 = Not applicable`|
| **Description** |  |  |  |


```{r assign w7, echo=F}

load(paste0(datafolder,"w7/ybirth.RData"))
ELSA_w7 <- left_join(ELSA_w7,ybirth, by="id")
rm(ybirth)

```

```{r local w7, echo=F}

vbl <- ELSA_w7$hedimst
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[3], caption = 'hedimst')
kable(Categorical_summary(vbl, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(hedimst))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$HeAgeRY
kable(Continuous_summary(var = vbl, missing_values = c(-9,-8,-1,-2))[3], caption = 'HeAgeRY')
pander(Continuous_summary(vbl, missing_values = c(-9,-8,-1,-2))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeAgeRY)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(2000,2020)

vbl <- ELSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1990)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `hedimst == 1 into 1`
* `hedimst == -9 into 997`
* `hedimst == -8 into 998`
* `hedimst == 0 into 0`


To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = HeAgeRY - ybirth`
* `if stroke == 0, stroke_age = 996`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `otherwise, stroke_age = 999`

**R script:**

```{r harmo w7}

# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$stroke <- car::recode(ELSA_w7$hedimst,"-8=998;-9=997")

# Continuous variable harmonization
ELSA_ds_w7$stroke_age <- rep(999,length(ELSA_w7$id))
ELSA_ds_w7$stroke_age[which(ELSA_ds_w7$stroke==0)] <- 996
ELSA_ds_w7$stroke_age[which(ELSA_ds_w7$stroke==1 & !ELSA_w7$HeAgeRY %in% c(-1,-8,-9))] <- ELSA_w7$HeAgeRY[which(ELSA_ds_w7$stroke==1 & !ELSA_w7$HeAgeRY %in% c(-1,-8,-9))] - ELSA_w7$ybirth[which(ELSA_ds_w7$stroke==1 & !ELSA_w7$HeAgeRY %in% c(-1,-8,-9))]
ELSA_ds_w7$stroke_age <- car::recode(ELSA_ds_w7$stroke_age, "-1=996;-8=998;-9=997;NA=999")


```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w7$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(40,95)

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$stroke)
BeforeH <- table(ELSA_w7$hedimst)[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("hedimst==0->0","hedimst==1->1","hedimst==-9->997","hedimst==-8->998")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]) , length(l.hds[[6]][[2]]), length(l.hds[[7]][[2]])
             )
names(t.hds)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(t.hds)

dbb <- merge(ELSA_m_ds_w1[,c("id","stroke")], ELSA_m_ds_w2[,c("id","stroke")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w3[,c("id","stroke")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4[,c("id","stroke")], by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w5[,c("id","stroke")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6[,c("id","stroke")], by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb,ELSA_m_ds_w7[,c("id","stroke")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2","w4","w5")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation


No comments

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  stroke <- l.hds[[index]]
  save(stroke, file = paste0(datafolder,names(l.hds)[index],"/stroke.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```




