---
title: "dementia_age case"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/dementia_ageDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/dementia_ageDS.R')
```


# Data process

## England 

### Wave 1 

#### Study-specific variable description

| **Name** | `HeAgj`| `HeAgjRY` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` | 
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`| `-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`|
| **Description** | | |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem','ELSA.wave_3_elsa_data_v4',
                         variables=list('heagjry', 'heagj'), missings = TRUE)
ELSA_dem <- opal.execute(o,'ELSA_dem')

load("../RData/w1/dementia.RData")
load("../RData/w1/ybirth.RData")

ELSA_dem_a <- left_join(dementia,ELSA_dem)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local1, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`heagjry - ybirth` or `heagj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w1$dementia_age <- ELSA_dem_a$heagjry - ELSA_dem_a$ybirth

ELSA_ds_w1$dementia_age[ELSA_dem_a$heagjry == -1] <- 996
ELSA_ds_w1$dementia_age[ELSA_dem_a$heagjry == -8] <- 998
ELSA_ds_w1$dementia_age[ELSA_dem_a$heagjry == -9] <- 997

ELSA_ds_w1$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)] <- car::recode(ELSA_dem_a$heagj[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)], "-9=997; -8=998; -1=996")

ELSA_ds_w1$dementia_age[ELSA_ds_w1$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
ELSA_ds_w1$dementia_age[ELSA_dem_a$dementia == 0] <- 996

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Validation


### Wave 2

#### Study-specific variable description

| **Name** | `HeAgj`| `HeAgjRY` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` | 
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`| `-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`|
| **Description** | | |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem','ELSA.wave_3_elsa_data_v4',
                         variables=list('heagjry', 'heagj'), missings = TRUE)
ELSA_dem <- opal.execute(o,'ELSA_dem')

load("../RData/w2/dementia.RData")
load("../RData/w3/ybirth.RData")

ELSA_dem_a <- left_join(dementia, ELSA_dem)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local2, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`heagjry - ybirth` or `heagj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w2$dementia_age <- ELSA_dem_a$heagjry - ELSA_dem_a$ybirth

ELSA_ds_w2$dementia_age[ELSA_dem_a$heagjry == -1] <- 996
ELSA_ds_w2$dementia_age[ELSA_dem_a$heagjry == -8] <- 998
ELSA_ds_w2$dementia_age[ELSA_dem_a$heagjry == -9] <- 997

ELSA_ds_w2$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)] <- car::recode(ELSA_dem_a$heagj[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)], "-9=997; -8=998; -1=996")

ELSA_ds_w2$dementia_age[ELSA_ds_w2$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
ELSA_ds_w2$dementia_age[ELSA_dem_a$dementia == 0] <- 996
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```



### Wave 3

#### Study-specific variable description


| **Name** | `HeAgj`| `HeAgjRY` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` | 
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`| `-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`|
| **Description** | | |

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem','ELSA.wave_3_elsa_data_v4',
                         variables=list('heagjry', 'heagj'), missings = TRUE)
ELSA_dem <- opal.execute(o,'ELSA_dem')

load("../RData/w3/dementia.RData")
load("../RData/w3/ybirth.RData")

ELSA_dem_a <- left_join(ELSA_dem, dementia)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local3, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`heagjry - ybirth` or `heagj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`


**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w3$dementia_age <- ELSA_dem_a$heagjry - ELSA_dem_a$ybirth

ELSA_ds_w3$dementia_age[ELSA_dem_a$heagjry == -1] <- 996
ELSA_ds_w3$dementia_age[ELSA_dem_a$heagjry == -8] <- 998
ELSA_ds_w3$dementia_age[ELSA_dem_a$heagjry == -9] <- 997

ELSA_ds_w3$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)] <- car::recode(ELSA_dem_a$heagj[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)], "-9=997; -8=998; -1=996")

ELSA_ds_w3$dementia_age[ELSA_ds_w3$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```

#### Validation


### Wave 4

#### Study-specific variable description

| **Name** | `heagj`| `heagjry` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` |
| **Table name** | `wave_4_elsa_data_v3` | `wave_4_elsa_data_v3` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't know` <br/> `-2 = Capi/Interview Error` <br/> `-1 = Not applicable`|`-9 = Refusal` <br/> `-8 = Don't know` <br/> `-2 = Capi/Interview Error` <br/> `-1 = Not applicable`|
| **Description** | |  | 

```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem_a','ELSA.wave_4_elsa_data_v3',
                         variables=list('heagj', 'heagjry'), missings = TRUE)
ELSA_dem_a <- opal.execute(o,'ELSA_dem_a')

load("../RData/w4/dementia.RData")
load("../RData/w3/ybirth.RData")

ELSA_dem_a <- left_join(ELSA_dem_a, dementia)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local4, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9,-2))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9,-2))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9,-2))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + xlab("heagj") + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9,-2))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9,-2))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9,-2))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + xlab("heagjry") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`heagjry - ybirth` or `heagj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `-2 into 991`
* `NA into 996`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w4$dementia_age <- ELSA_dem_a$heagjry - ELSA_dem_a$ybirth

ELSA_ds_w4$dementia_age[ELSA_dem_a$heagjry == -1] <- 996
ELSA_ds_w4$dementia_age[ELSA_dem_a$heagjry == -8] <- 998
ELSA_ds_w4$dementia_age[ELSA_dem_a$heagjry == -9] <- 997
ELSA_ds_w4$dementia_age[ELSA_dem_a$heagjry == -2] <- 991

ELSA_ds_w4$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)] <- car::recode(ELSA_dem_a$heagj[ELSA_dem_a$dementia==1 & ELSA_dem_a$heagjry %in% c(-8,-2,-1)], "-9=997; -8=998; -1=996")

ELSA_ds_w4$dementia_age[ELSA_ds_w4$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(vari))+ geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```

#### Validation

### Wave 5

#### Study-specific variable description

| **Name** | `heagjry`| 
|-|-|
| **Label** | `Year told had dementia since last interview`| 
| **Table name** | `wave_5_elsa_data_v4` |
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't know` <br/> `-1 = Item Not Applicable` |
| **Description** | | 

```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem_a','ELSA.wave_5_elsa_data_v4',
                         variables=list('heagjry'), missings = TRUE)
ELSA_dem_a <- opal.execute(o,'ELSA_dem_a')

load("../RData/w5/dementia.RData")
load("../RData/w5/ybirth.RData")

ELSA_dem_a <- left_join(ELSA_dem_a, dementia)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local5, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency") + xlim(c(1900,2000))
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`heagjry - ybirth`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w5$dementia_age <- ELSA_dem_a$heagjry - ELSA_dem_a$ybirth

ELSA_ds_w5$dementia_age[ELSA_dem_a$heagjry == -1] <- 996
ELSA_ds_w5$dementia_age[ELSA_dem_a$heagjry == -8] <- 998
ELSA_ds_w5$dementia_age[ELSA_dem_a$heagjry == -9] <- 997

ELSA_ds_w5$dementia_age[ELSA_ds_w5$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```

#### Validation



### Wave 6

#### Study-specific variable description

| **Name** | `HeAgj`| `HeAgjRY` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` | 
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`| `-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`|
| **Description** | | |

```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem_a','ELSA.wave_6_elsa_data_v2',
                         variables=list('HeAgj', 'HeAgjRY'), missings = TRUE)
ELSA_dem_a <- opal.execute(o,'ELSA_dem_a')

load("../RData/w6/dementia.RData")
load("../RData/w6/ybirth.RData")

ELSA_dem_a <- left_join(ELSA_dem_a, dementia)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local6, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = label(vari))
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_dem_a, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`HeAgjRY - ybirth` or `HeAgj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`


**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w6$dementia_age <- ELSA_dem_a$HeAgjRY - ELSA_dem_a$ybirth

ELSA_ds_w6$dementia_age[ELSA_dem_a$HeAgjRY == -1] <- 996
ELSA_ds_w6$dementia_age[ELSA_dem_a$HeAgjRY == -8] <- 998
ELSA_ds_w6$dementia_age[ELSA_dem_a$HeAgjRY == -9] <- 997

ELSA_ds_w6$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$HeAgjRY %in% c(-8,-1)] <- car::recode(ELSA_dem_a$HeAgj[ELSA_dem_a$dementia==1 & ELSA_dem_a$HeAgjRY %in% c(-8,-1)], "-9=997; -8=998; -1=996")


ELSA_ds_w6$dementia_age[ELSA_ds_w6$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```

#### Validation


### Wave 7

#### Study-specific variable description

| **Name** | `HeAgj`| `HeAgjRY` |
|-|-|-|
| **Label** | `Age told had dementia`| `Year told had dementia since last interview` | 
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` | 
| **Missing** |`-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`| `-9 = Refusal` <br/> `-8 = Don't Know` <br/> `-1 = Item not applicable`|
| **Description** | | |

```{r assign7, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_dem_a','ELSA.wave_7_elsa_data',
                         variables=list('HeAgj', 'HeAgjRY'), missings = TRUE)
ELSA_dem_a <- opal.execute(o,'ELSA_dem_a')

load("../RData/w7/dementia.RData")
load("../RData/w7/ybirth.RData")

ELSA_dem_a <- left_join(ELSA_dem_a, dementia)
ELSA_dem_a <- left_join(ELSA_dem_a, ybirth)
```

```{r local7, echo=FALSE}
vari <- ELSA_dem_a[[2]]
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[2], caption = "Type of missing")
ggplot(ELSA_dem_a, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_dem_a[[3]]
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -8,-9))[2], caption = "Type of missing")
ggplot(ELSA_dem_a, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be computed as follows:

`HeAgjRY - ybirth` or `HeAgj`

and the missing values have to be recoded as follows:

* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `NA into 996`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_dem_a$id)
ELSA_ds_w7$dementia_age <- ELSA_dem_a$HeAgjRY - ELSA_dem_a$ybirth

ELSA_ds_w7$dementia_age[ELSA_dem_a$HeAgjRY == -1] <- 996
ELSA_ds_w7$dementia_age[ELSA_dem_a$HeAgjRY == -8] <- 998
ELSA_ds_w7$dementia_age[ELSA_dem_a$HeAgjRY == -9] <- 997

ELSA_ds_w7$dementia_age[ELSA_dem_a$dementia==1 & ELSA_dem_a$HeAgjRY %in% c(-8,-1)] <- car::recode(ELSA_dem_a$HeAgj[ELSA_dem_a$dementia==1 & ELSA_dem_a$HeAgjRY %in% c(-8,-1)], "-9=997; -8=998; -1=996")


ELSA_ds_w7$dementia_age[ELSA_ds_w7$dementia_age == 996 & ELSA_dem_a$dementia == 1] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=FALSE}
vari <- ELSA_ds_w7$dementia_age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = 'dementia age')
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + ylab("Frequency") + xlab("Dementia age") 
```

#### Validation

# Quality estimation



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

elsalist <- lmlist # ELSA list


```



# Quality estimation


No comments







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

