---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `height of the participant`
* Variable description: `Anthropometric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Finland


### Health2000-2011 - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `BMII_PITUUS2`
* Label: `Height in meters`
* Type of variable: `countinous`

```{r assign1}
opal.assign.table.tibble(o, 'Health20002011_w1_heig','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('BMII_PITUUS2'), missings = TRUE)
```

```{r local1}
Health20002011_w1_heig <- opal.execute(o,'Health20002011_w1_heig')
Continuous_summary(var = Health20002011_w1_heig$BMII_PITUUS2, missing_values = NA)
ggplot(Health20002011_w1_heig, aes(BMII_PITUUS2)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable but we have to transform the values from m to cm multiplying by 100 and the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
Health20002011_w1_heig$height_m <- Health20002011_w1_heig$BMII_PITUUS2*100

Health20002011_ds_w1 <- tibble(id=Health20002011_w1_heig$id)
Health20002011_ds_w1$height <- car::recode(Health20002011_w1_heig$height_m, "NA=999")
Health20002011_ds_w1$height <- labelled(Health20002011_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = Health20002011_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL1}
#val_labels(Health20002011_ds_w1) <- NULL
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
height <- Health20002011_ds_w1
save(height, file = "../RData/w1/height.RData")
rm(height)
```






### Health2000-2011 - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `KYS1_K17B`
* Label: `Height`
* Type of variable: `countinous`

```{r assign2}
opal.assign.table.tibble(o, 'Health20002011_w2_heigh','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('KYS1_K17B'), missings = TRUE)
```

```{r local2}
Health20002011_w2_heigh <- opal.execute(o,'Health20002011_w2_heigh')
Continuous_summary(var = Health20002011_w2_heigh$KYS1_K17B, missing_values = NA)
ggplot(Health20002011_w2_heigh, aes(KYS1_K17B)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_heigh$id)
Health20002011_ds_w2$height <- car::recode(Health20002011_w2_heigh$KYS1_K17B, "NA=999")
Health20002011_ds_w2$height <- labelled(Health20002011_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = Health20002011_ds_w2$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation2}
```

#### Quality estimation
No comments.

#### Import to OPAL
```{r importOPAL2}
#val_labels(Health20002011_ds_w2) <- NULL
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
height <- Health20002011_ds_w2
save(height, file = "../RData/w2/height.RData")
rm(height)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```


