---
title: "Mobility - getting up from sitting down"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_up`
* Variable label: `Difficulty for getting up from sitting down`
* Variable description: `Difficulty for getting up from sitting down`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Finland


### Wave 1 

#### Study-specific variable description




| **Name** | `TOKY_7TUOLI1`|
|-|-|
| **Label** | `Getting up from chair` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Categories** |`0 = can without hands; 1 = can with the help of the hands; 2 = unable to`|
| **Missings** |`NA`|
| **Description** |  |

 

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w1_mob_up','Health2000-2011.t00_athlos_2017_02_23', variables=list('TOKY_7TUOLI1'), missings = TRUE)
```

```{r local w1, echo=F}
HEALTH2000_w1_mob_up <- opal.execute(o,'HEALTH2000_w1_mob_up')
vari <- HEALTH2000_w1_mob_up$TOKY_7TUOLI1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "TOKY_7TUOLI1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_mob_up, aes(x=factor(TOKY_7TUOLI1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1,2 into 0`
* `NA into 999`

**R script:**
```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_mob_up$id)
Health20002011_ds_w1$mob_up <- car::recode(HEALTH2000_w1_mob_up$TOKY_7TUOLI1, "0 = '1';1 = '0';2 = '0';NA = '999' ")
Health20002011_ds_w1$mob_up <- labelled(Health20002011_ds_w1$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- Health20002011_ds_w1$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(Health20002011_ds_w1$mob_up)
X<-table(HEALTH2000_w1_mob_up$TOKY_7TUOLI1)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HEALTH2000_w1_mob_up$TOKY_7TUOLI1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999")
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(Health20002011_ds_w1$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
mob_up <- Health20002011_ds_w1
save(mob_up, file = "../RData/w1/mob_up.RData")

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$mob_up <- car::recode(Health20002011_m_ds_w1$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `TOKY_7TUOLI1_T11`|
|-|-|
| **Label** | `Chair stand once, modification` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories** |`0 = Yes, without hands; 1 = Yes, with hands; 2 = No`|
| **Missings** |`NA`|
| **Description** |  |

 

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w2_mob_up','Health2000-2011.t11_athlos_2017_02_27', variables=list('TOKY_7TUOLI1_T11'), missings = TRUE)
```

```{r local w2, echo=F}
HEALTH2000_w2_mob_up <- opal.execute(o,'HEALTH2000_w2_mob_up')
vari <- HEALTH2000_w2_mob_up$TOKY_7TUOLI1_T11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "TOKY_7TUOLI1_T11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_mob_up, aes(x=factor(TOKY_7TUOLI1_T11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1,2 into 0`
* `NA into 999`

**R script:**
```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_mob_up$id)
Health20002011_ds_w2$mob_up <- car::recode(HEALTH2000_w2_mob_up$TOKY_7TUOLI1_T11, "0 = '1';1 = '0';2 = '0';NA = '999' ")
Health20002011_ds_w2$mob_up <- labelled(Health20002011_ds_w2$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- Health20002011_ds_w2$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$mob_up)
X<-table(HEALTH2000_w2_mob_up$TOKY_7TUOLI1_T11)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HEALTH2000_w2_mob_up$TOKY_7TUOLI1_T11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999")
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(Health20002011_ds_w2$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
mob_up <- Health20002011_ds_w2
save(mob_up, file = "../RData/w2/mob_up.RData")

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$mob_up <- car::recode(Health20002011_m_ds_w2$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
