---
title: "Mobility - Extending arms"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_arm`
* Variable label: `Difficulty for reaching / extending arms`
* Variable description: `Difficulty for reaching / extending arms`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


## Finland


### Wave 1

#### Study-specific variable description




| **Name** | `TOKY_6OLKAVARNOSTO`|
|-|-|
| **Label** | `Lifting up upper arms` |
| **Table name** |`t00_athlos_2017_02_23`|
| **Categories** |`0 = normal; 1 = some difficulty; 2 = unable to do`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w1_mob_arm','Health2000-2011.t00_athlos_2017_02_23', variables=list('TOKY_6OLKAVARNOSTO'), missings = TRUE)
```

```{r local w1, echo=F}
HEALTH2000_w1_mob_arm <- opal.execute(o,'HEALTH2000_w1_mob_arm')
vari <- HEALTH2000_w1_mob_arm$TOKY_6OLKAVARNOSTO
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "TOKY_6OLKAVARNOSTO")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_mob_arm, aes(x=factor(TOKY_6OLKAVARNOSTO))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1,2 into 0`
* `NA into 999`

**R script:**
```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_mob_arm$id)
Health20002011_ds_w1$mob_arm <- car::recode(HEALTH2000_w1_mob_arm$TOKY_6OLKAVARNOSTO, "0 = '1';1 = '0';2 = '0';NA = '999' ")
Health20002011_ds_w1$mob_arm <- labelled(Health20002011_ds_w1$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- Health20002011_ds_w1$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(Health20002011_ds_w1$mob_arm)
X<-table(HEALTH2000_w1_mob_arm$TOKY_6OLKAVARNOSTO)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HEALTH2000_w1_mob_arm$TOKY_6OLKAVARNOSTO)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999")
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(Health20002011_ds_w1$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
mob_arm <- Health20002011_ds_w1
save(mob_arm, file = "../RData/w1/mob_arm.RData")

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$mob_arm <- car::recode(Health20002011_m_ds_w1$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `TOKY_6OLKAVARNOSTO_T11`|
|-|-|
| **Label** | `Lifting up upper arms, modification` |
| **Table name** |`t11_athlos_2017_02_27`|
| **Categories** |`0 = Normal; 1 = Complicated; 2 = Does not manage`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w2_mob_arm','Health2000-2011.t11_athlos_2017_02_27', variables=list('TOKY_6OLKAVARNOSTO_T11'), missings = TRUE)
```

```{r local w2, echo=F}
HEALTH2000_w2_mob_arm <- opal.execute(o,'HEALTH2000_w2_mob_arm')
vari <- HEALTH2000_w2_mob_arm$TOKY_6OLKAVARNOSTO_T11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "TOKY_6OLKAVARNOSTO_T11")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_mob_arm, aes(x=factor(TOKY_6OLKAVARNOSTO_T11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1,2 into 0`
* `NA into 999`

**R script:**
```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_mob_arm$id)
Health20002011_ds_w2$mob_arm <- car::recode(HEALTH2000_w2_mob_arm$TOKY_6OLKAVARNOSTO_T11, "0 = '1';1 = '0';2 = '0';NA = '999' ")
Health20002011_ds_w2$mob_arm <- labelled(Health20002011_ds_w2$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- Health20002011_ds_w2$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$mob_arm)
X<-table(HEALTH2000_w2_mob_arm$TOKY_6OLKAVARNOSTO_T11)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HEALTH2000_w2_mob_arm$TOKY_6OLKAVARNOSTO_T11)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999")
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(Health20002011_ds_w2$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
mob_arm <- Health20002011_ds_w2
save(mob_arm, file = "../RData/w2/mob_arm.RData")

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$mob_arm <- car::recode(Health20002011_m_ds_w2$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation
In this study there is not exactly the same variable definiton (Lifting up upper arms) as in others (reaching-extending arms)

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
