---
title: "Memory"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `memory`
* Variable label: `Difficulties with memory`
* Variable description: `Difficulties with memory`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Presence of difficulties with memory
1        | Absence of memory difficulties

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 

## Finland


### Wave 1 

#### Study-specific variable description




| **Name** | `HF10`|
|-|-|
| **Label** | `Memory: present memory` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Categories** | `1 = very good; 2 = good; 3 = satisfactory; 4 = poor; 5 = very poor` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w1_memory','Health2000-2011.t00_athlos_2017_02_23', variables=list('HF10'), missings = TRUE)
```

```{r local w1, echo=F}
HEALTH2000_w1_memory <- opal.execute(o,'HEALTH2000_w1_memory')
vari <- HEALTH2000_w1_memory$HF10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "HF10")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_memory, aes(x=factor(HF10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 very good into 1` 
* `2 good into 1` 
* `3 satisfactory into 1` 
* `4 poor into 0` 
* `5 very poor into 0`                                            
* `NA into 999`


**R script:**
```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_memory$id)
Health20002011_ds_w1$memory <- car::recode(HEALTH2000_w1_memory$HF10, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';NA = '999' ")
Health20002011_ds_w1$memory <- labelled(Health20002011_ds_w1$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- Health20002011_ds_w1$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(Health20002011_ds_w1$memory)
X<- table(HEALTH2000_w1_memory$HF10)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(HEALTH2000_w1_memory$HF10)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(Health20002011_ds_w1$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
memory <- Health20002011_ds_w1
save(memory, file = "../RData/w1/memory.RData")

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$memory <- car::recode(Health20002011_m_ds_w1$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `HF10`|
|-|-|
| **Label** | `Memory: present memory` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories** | `1 = very good; 2 = good; 3 = satisfactory; 4 = poor; 5 = very poor` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w2_memory','Health2000-2011.t11_athlos_2017_02_27', variables=list('HF10'), missings = TRUE)
```

```{r local w2, echo=F}
HEALTH2000_w2_memory <- opal.execute(o,'HEALTH2000_w2_memory')
vari <- HEALTH2000_w2_memory$HF10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "HF10")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_memory, aes(x=factor(HF10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 very good into 1` 
* `2 good into 1` 
* `3 satisfactory into 1` 
* `4 poor into 0` 
* `5 very poor into 0`                                            
* `NA into 999`


**R script:**
```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_memory$id)
Health20002011_ds_w2$memory <- car::recode(HEALTH2000_w2_memory$HF10, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';NA = '999' ")
Health20002011_ds_w2$memory <- labelled(Health20002011_ds_w2$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- Health20002011_ds_w2$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$memory)
X<- table(HEALTH2000_w2_memory$HF10)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(HEALTH2000_w2_memory$HF10)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(Health20002011_ds_w2$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
memory <- Health20002011_ds_w2
save(memory, file = "../RData/w2/memory.RData")

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$memory <- car::recode(Health20002011_m_ds_w2$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
