---
title: "ADL - Eating"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_eating`
* Variable label: `ADL-Difficulties for eating`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 



## Finnish population
### Wave 1 

#### Study-specific variable description

 


* Name: `HA01D`
* Label: `Managing: eating`
* Categories:
   + `1 = without difficulties`
   + `2 = with minor difficulties`
   + `3 = with major difficulties`
   + `4 = not at all`
* Missings
   + `NA`


* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w1_adl_eating','Health2000-2011.t00_athlos_2017_02_23', variables=list('HA01D'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
HEALTH2000_w1_adl_eating <- opal.execute(o,'HEALTH2000_w1_adl_eating')
vari <- HEALTH2000_w1_adl_eating$HA01D # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w1_adl_eating$HA01D)
ggplot(HEALTH2000_w1_adl_eating, aes(x=factor(HA01D))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`  
* `2,3,4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_adl_eating$id)
Health20002011_ds_w1$adl_eating <- car::recode(HEALTH2000_w1_adl_eating$HA01D, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
Health20002011_ds_w1$adl_eating <- labelled(Health20002011_ds_w1$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- Health20002011_ds_w1$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = Health20002011_ds_w1$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(Health20002011_ds_w1$adl_eating)
X<-table(HEALTH2000_w1_adl_eating$HA01D)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(HEALTH2000_w1_adl_eating$HA01D)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(Health20002011_ds_w1) <- NULL
label(Health20002011_ds_w1$adl_eating) <- "Difficulties for eating"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$adl_eating <- car::recode(Health20002011_m_ds_w1$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- Health20002011_ds_w1
save(adl_eating, file = paste0(datafolder, "/w1/adl_eating.RData"))
```



### Wave 2

#### Study-specific variable description

 


* Name: `HA01D`
* Label: `Managing: eating`
* Categories:
   + `1 = without difficulties`
   + `2 = with minor difficulties`
   + `3 = with major difficulties`
   + `4 = not at all`
* Missings
   + `NA`


* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w2_adl_eating','Health2000-2011.t11_athlos_2017_02_27', variables=list('HA01D'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
HEALTH2000_w2_adl_eating <- opal.execute(o,'HEALTH2000_w2_adl_eating')
vari <- HEALTH2000_w2_adl_eating$HA01D # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w2_adl_eating$HA01D)
ggplot(HEALTH2000_w2_adl_eating, aes(x=factor(HA01D))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`  
* `2,3,4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_adl_eating$id)
Health20002011_ds_w2$adl_eating <- car::recode(HEALTH2000_w2_adl_eating$HA01D, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
Health20002011_ds_w2$adl_eating <- labelled(Health20002011_ds_w2$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- Health20002011_ds_w2$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = Health20002011_ds_w2$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(Health20002011_ds_w2$adl_eating)
X<-table(HEALTH2000_w2_adl_eating$HA01D)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(HEALTH2000_w2_adl_eating$HA01D)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(Health20002011_ds_w2) <- NULL
label(Health20002011_ds_w2$adl_eating) <- "Difficulties for eating"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$adl_eating <- car::recode(Health20002011_m_ds_w2$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- Health20002011_ds_w2
save(adl_eating, file = paste0(datafolder, "/w2/adl_eating.RData"))
```

# Quality control

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
