---
title: "IADL - Difficulties for taking medications"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_medication`
* Variable label: `IADL - Difficulties for taking medications`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## Finnish population
### Wave 1 

#### Study-specific variable description

 


* Name: `HD01`
* Label: `Do you because of your reduced functional capacity receive repeatedly assistance or help in your everyday activities, e.g. household work, washing up, shopping?`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings
    + `NA`
* Description:
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w1_iadl_medication','Health2000-2011.t00_athlos_2017_02_23', variables=list('HD01','HD01A5','HD02','HD02A5'), missings = TRUE)
```

```{r local1 w1,  echo=FALSE}
HEALTH2000_w1_iadl_medication <- opal.execute(o,'HEALTH2000_w1_iadl_medication')
vari <- HEALTH2000_w1_iadl_medication$HD01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w1_iadl_medication$HD01)
ggplot(HEALTH2000_w1_iadl_medication, aes(x=factor(HD01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")

```

* Name: `HD01A5`
* Label: `In which activities would you need assistance or help: taking care of my medication`
* Categories:
    + `0 = no`
    + `1 = yes`
* Missings
    + `NA`
* Description:
```{r local2 w1,  echo=FALSE}
vari <- HEALTH2000_w1_iadl_medication$HD01A5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w1_iadl_medication$HD01A5)
ggplot(HEALTH2000_w1_iadl_medication, aes(x=factor(HD01A5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")
```

* Name: `HD02`
* Label: `Would you need this kind of assistance or help?`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings
    + `NA`
* Description:
```{r local3 w1,  echo=FALSE}
vari <- HEALTH2000_w1_iadl_medication$HD02
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w1_iadl_medication$HD02)
ggplot(HEALTH2000_w1_iadl_medication, aes(x=factor(HD02))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")

```

* Name: `HD02A5`
* Label: `In which activities would you need assistance or help`
* Categories:
    + `0 = no`
    + `1 = yes`
* Missings
    + `NA`

* Description: 


```{r local4 w1,  echo=FALSE}
vari <- HEALTH2000_w1_iadl_medication$HD02A5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w1_iadl_medication$HD02A5)
ggplot(HEALTH2000_w1_iadl_medication, aes(x=factor(HD02A5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(HD01 = 1 & HD01A5 = 1) | (HD02 = 1 & HD02A5 = 1) into 0`
* `(HD01 = 1 & HD01A5 = 0) into 1`
* `HD01 = 0 & (HD02 = 0 | (HD02 = 1 & HD02A5 = 0)) into 1`
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_iadl_medication$id)
Health20002011_ds_w1$iadl_medication <- rep(999,length(HEALTH2000_w1_iadl_medication$id))

Health20002011_ds_w1$iadl_medication[which( (HEALTH2000_w1_iadl_medication$HD01==1 & HEALTH2000_w1_iadl_medication$HD01A5==1) | (HEALTH2000_w1_iadl_medication$HD02==1 & HEALTH2000_w1_iadl_medication$HD02A5==1))]<-0

Health20002011_ds_w1$iadl_medication[which( 
( !is.na(HEALTH2000_w1_iadl_medication$HD01) & !is.na(HEALTH2000_w1_iadl_medication$HD01A5) & HEALTH2000_w1_iadl_medication$HD01==1 & HEALTH2000_w1_iadl_medication$HD01A5==0 ) | (!is.na(HEALTH2000_w1_iadl_medication$HD01) & HEALTH2000_w1_iadl_medication$HD01==0 & ( !is.na(HEALTH2000_w1_iadl_medication$HD02) & (HEALTH2000_w1_iadl_medication$HD02==1 & !is.na(HEALTH2000_w1_iadl_medication$HD02A5) &  HEALTH2000_w1_iadl_medication$HD02A5==0) | HEALTH2000_w1_iadl_medication$HD02==0))
)]<-1


Health20002011_ds_w1$iadl_medication <- labelled(Health20002011_ds_w1$iadl_medication, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- Health20002011_ds_w1$iadl_medication # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w1$iadl_medication, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(iadl_medication))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")
```



#### Validation

The individuals answering 'Yes' to `HD01` and No to `HD01A15` have missing values in `HD02` and `HD02A15`, therefore we assume they have no difficulty. Nevertheless, the design of the questionnaire only allow us to know that they do not receive help or assistance taking medication, but not if they need it.

<!--
If this was not the case, the good harmonization set to assign 1 would be
( !is.na(HEALTH2000_w1_iadl_medication$HD01) & (HEALTH2000_w1_iadl_medication$HD01==0 | (!is.na(HEALTH2000_w1_iadl_medication$HD01A5) & (HEALTH2000_w1_iadl_medication$HD01==1 & HEALTH2000_w1_iadl_medication$HD01A5==0) ) ) ) & ( !is.na(HEALTH2000_w1_iadl_medication$HD02) & (HEALTH2000_w1_iadl_medication$HD02==0 | (!is.na(HEALTH2000_w1_iadl_medication$HD02A5) & (HEALTH2000_w1_iadl_medication$HD02==1 & HEALTH2000_w1_iadl_medication$HD02A5==0) ) ) )
-->

```{r crosstabulation w1,  echo=FALSE}

cat("There are",length(HEALTH2000_w1_iadl_medication$id[HEALTH2000_w1_iadl_medication$HD01==1 & HEALTH2000_w1_iadl_medication$HD01A5==0 & !is.na(HEALTH2000_w1_iadl_medication$HD01) & !is.na(HEALTH2000_w1_iadl_medication$HD01A5)]),"individuals with the data mentioned just above.")

kable(HEALTH2000_w1_iadl_medication[!is.na(HEALTH2000_w1_iadl_medication$HD02A5) & is.na(HEALTH2000_w1_iadl_medication$HD02),],align = 'c',caption = 'There is an individual whose data is missing in all the variables but in HD02A5. It is categorized as missing (999).')
kable(HEALTH2000_w1_iadl_medication[!is.na(HEALTH2000_w1_iadl_medication$HD02) & is.na(HEALTH2000_w1_iadl_medication$HD02A5) & is.na(HEALTH2000_w1_iadl_medication$HD01),],align = 'c',caption = 'There are three individuals whose data is missing in all the variables but in HD02. They are categorized as missing (999).')


AfterH <- table(Health20002011_ds_w1$iadl_medication)
X<-c(
  sum((HEALTH2000_w1_iadl_medication$HD01==1&HEALTH2000_w1_iadl_medication$HD01A5==1)|(HEALTH2000_w1_iadl_medication$HD02==1&HEALTH2000_w1_iadl_medication$HD02A5==1),na.rm=TRUE),
  sum(
    ( !is.na(HEALTH2000_w1_iadl_medication$HD01) & !is.na(HEALTH2000_w1_iadl_medication$HD01A5) & HEALTH2000_w1_iadl_medication$HD01==1 & HEALTH2000_w1_iadl_medication$HD01A5==0 ) | (!is.na(HEALTH2000_w1_iadl_medication$HD01) & HEALTH2000_w1_iadl_medication$HD01==0 & ( !is.na(HEALTH2000_w1_iadl_medication$HD02) & (HEALTH2000_w1_iadl_medication$HD02==1 & !is.na(HEALTH2000_w1_iadl_medication$HD02A5) &  HEALTH2000_w1_iadl_medication$HD02A5==0) | HEALTH2000_w1_iadl_medication$HD02==0)),
    na.rm=TRUE)
  )
BeforeH <- c(X[1:2],length(HEALTH2000_w1_iadl_medication$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("HD01=1&HD01A5=1,HD02=1&HD02A5=1->0","(HD01=1&HD01A5 = 0), HD01=0&(HD02=0|(HD02=1&HD02A5=0)->1","NA->999") 
kable(C)





```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(Health20002011_ds_w1) <- NULL
label(Health20002011_ds_w1$iadl_medication) <- "Difficulties for taking medications"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$iadl_medication <- car::recode(Health20002011_m_ds_w1$iadl_medication, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_medication <- Health20002011_ds_w1
save(iadl_medication, file = paste0(datafolder, "/w1/iadl_medication.RData"))
```


### Wave 2

#### Study-specific variable description

 


* Name: `HA01H`
* Label: `dosing and taking medication?`
* Categories:
    + `1 = without difficulties`
    + `2 = with minor difficulties`
    + `3 = with major difficulties`
    + `4 = not at all`
* Missings
    + `NA`


* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w2_iadl_medication','Health2000-2011.t11_athlos_2017_02_27', variables=list('HA01H'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
HEALTH2000_w2_iadl_medication <- opal.execute(o,'HEALTH2000_w2_iadl_medication')
vari <- HEALTH2000_w2_iadl_medication$HA01H
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HEALTH2000_w2_iadl_medication$HA01H)
ggplot(HEALTH2000_w2_iadl_medication, aes(x=factor(HA01H))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3,4 into 0`
* `NA into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_iadl_medication$id)
Health20002011_ds_w2$iadl_medication <- car::recode(HEALTH2000_w2_iadl_medication$HA01H, "1 = '1';2 = '1';3 = '0';4 = '0';NA = '999' ")
Health20002011_ds_w2$iadl_medication <- labelled(Health20002011_ds_w2$iadl_medication, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- Health20002011_ds_w2$iadl_medication # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w2$iadl_medication, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(iadl_medication))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Taking medications") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(Health20002011_ds_w2$iadl_medication)
X<-table(HEALTH2000_w2_iadl_medication$HA01H)
BeforeH <- c(sum(X[3:4]),sum(X[1:2]),sum(is.na(HEALTH2000_w2_iadl_medication$HA01H)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4->0","1,2->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(Health20002011_ds_w2) <- NULL
label(Health20002011_ds_w2$iadl_medication) <- "Difficulties for taking medications"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$iadl_medication <- car::recode(Health20002011_m_ds_w2$iadl_medication, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_medication <- Health20002011_ds_w2
save(iadl_medication, file = paste0(datafolder, "/w2/iadl_medication.RData"))
```

# Quality estimation

At w1, the harmonized variable is a combination of the following var-questions:

HD01. Do you because of your reduced functional capacity receive repeatedly assistance or help in your everyday activities, e.g. household work, washing up, shopping? 

HD01A5. In which activities would you need assistance or help: taking care of my medication

HD02. Would you need this kind of assistance or help?

HD02A5. In which activities would you need assistance or help


```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
