---
title: "Limitations in ADLs - Shopping for groceries"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_shopping`
* Variable label: `IADL - Difficulties for shopping groceries`
* Variable description: `IADL - Difficulties for shopping groceries`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for shopping groceries"
```


# Data process

## HEALTH 2000

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `HA02H`
* Label: `how do you manage nowadays the following: shopping?`
* Categories:
   + `1 = without difficulties`
   + `2 = with minor difficulties`
   + `3 = with major difficulties`
   + `4 = not at all`
* Missings
   + `NA`


```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w1_iadl_shopping','Health2000-2011.t00_athlos_2017_02_23', variables=list('HA02H'), missings = TRUE)
HEALTH2000_w1_iadl_shopping <- opal.execute(o,'HEALTH2000_w1_iadl_shopping')
```

```{r local w1, echo=FALSE}
vari <- HEALTH2000_w1_iadl_shopping$HA02H
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_iadl_shopping, aes(x=factor(HA02H))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_iadl_shopping$id)
Health20002011_ds_w1$iadl_shopping <- recode(HEALTH2000_w1_iadl_shopping$HA02H, "1=1; 2=0; 3=0; 4=0; NA=999")
Health20002011_ds_w1$iadl_shopping <- labelled(Health20002011_ds_w1$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- Health20002011_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(Health20002011_ds_w1$iadl_shopping)
X <- table(HEALTH2000_w1_iadl_shopping$HA02H)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(HEALTH2000_w1_iadl_shopping$HA02H)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(Health20002011_ds_w1$iadl_shopping) <- ds_label
iadl_shopping <- Health20002011_ds_w1
save(iadl_shopping, file = "../RData/w1/iadl_shopping.RData")
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$iadl_shopping <- recode(Health20002011_m_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `HA02H`
* Label: `how do you manage nowadays the following: shopping?`
* Categories:
   + `1 = without difficulties`
   + `2 = with minor difficulties`
   + `3 = with major difficulties`
   + `4 = not at all`
* Missings
   + `NA`


```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w2_iadl_shopping','Health2000-2011.t11_athlos_2017_02_27', variables=list('HA02H'), missings = TRUE)
HEALTH2000_w2_iadl_shopping <- opal.execute(o,'HEALTH2000_w2_iadl_shopping')
```

```{r local w2, echo=FALSE}
vari <- HEALTH2000_w2_iadl_shopping$HA02H
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_iadl_shopping, aes(x=factor(HA02H))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4 into 0`
* `NA into 999`

**R script:**

```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_iadl_shopping$id)
Health20002011_ds_w2$iadl_shopping <- recode(HEALTH2000_w2_iadl_shopping$HA02H, "1=1; 2=0 ; 3=0; 4=0; NA=999")
Health20002011_ds_w2$iadl_shopping <- labelled(Health20002011_ds_w2$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- Health20002011_ds_w2$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(Health20002011_ds_w2$iadl_shopping)
X<-table(HEALTH2000_w2_iadl_shopping$HA02H)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(HEALTH2000_w2_iadl_shopping$HA02H)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(Health20002011_ds_w2$iadl_shopping) <- ds_label
iadl_shopping <- Health20002011_ds_w2
save(iadl_shopping, file = "../RData/w2/iadl_shopping.RData")
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$iadl_shopping <- recode(Health20002011_m_ds_w2$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
