---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## HEALTH 2000

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `BA01`
* Label: `Current health`
* Categories:
   + `1 = Good`
   + `2 = Rather Good`
   + `3 = Moderate`
   + `4 = Rather Poor`
   + `5 = Poor`
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w1_srh','Health2000-2011.t00_athlos_2017_02_23', variables=list('BA01'), missings = TRUE)
HEALTH2000_w1_srh <- opal.execute(o,'HEALTH2000_w1_srh')
```

```{r local w1, echo=FALSE}
vari <- HEALTH2000_w1_srh$BA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_srh, aes(x=factor(BA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_srh$id)
Health20002011_ds_w1$srh <- recode(HEALTH2000_w1_srh$BA01, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';NA = '999' ")
Health20002011_ds_w1$srh <- labelled(Health20002011_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- Health20002011_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(Health20002011_ds_w1$srh)
X<-table(HEALTH2000_w1_srh$BA01)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]),sum(is.na(HEALTH2000_w1_srh$BA01)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","NA->999")
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(Health20002011_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- Health20002011_ds_w1
save(srh, file = "../RData/w1/srh.RData")
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$srh <- recode(Health20002011_m_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



#### HEALTH2000 - Wave 2

##### Study-specific variables

The study-specific variables elected to be harmonised is:


* Name: `BA01`
* Label: `Current health`
* Categories:
   + `1 = Good`
   + `2 = Rather Good`
   + `3 = Moderate`
   + `4 = Rather Poor`
   + `5 = Poor`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w2_srh','Health2000-2011.t11_athlos_2017_02_27', variables=list('BA01'), missings = TRUE)
HEALTH2000_w2_srh <- opal.execute(o,'HEALTH2000_w2_srh')
```

```{r local w2, echo=FALSE}
vari <- HEALTH2000_w2_srh$BA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_srh, aes(x=factor(BA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_srh$id)
Health20002011_ds_w2$srh <- recode(HEALTH2000_w2_srh$BA01, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';NA = '999' ")
Health20002011_ds_w2$srh <- labelled(Health20002011_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- Health20002011_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(Health20002011_ds_w2$srh)
X<-table(HEALTH2000_w2_srh$BA01)
BeforeH <- c(sum(X[1:2]),X[3],sum(X[4:5]),sum(is.na(HEALTH2000_w2_srh$BA01)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","NA->999")
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(Health20002011_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- Health20002011_ds_w2
save(srh, file = "../RData/w2/srh.RData")
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$srh <- recode(Health20002011_m_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

####Quality estimation

The original values are not exactly the same between waves.



#### Close OPAL R Session
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
