---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## HEALTH2000

### Wave 1

#### Study-specific variable description

Not found



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `OIRE_62`
* Label: `How many times have you fallen while walking in the past 12 months? `
* Categories:
   + `Continuous Variable 1-30`
* Missings
   + `NA`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'HEALTH2000_w2_recent_falls','Health2000-2011.t11_athlos_2017_02_27', variables=list('OIRE_62'), missings = TRUE)
HEALTH2000_w2_recent_falls <- opal.execute(o,'HEALTH2000_w2_recent_falls')
```

```{r local w2, echo=FALSE}
vari <- HEALTH2000_w2_recent_falls$OIRE_62
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_recent_falls, aes(x=factor(OIRE_62))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `>0 into 1`
* `NA into 999`

**R script:**

```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_recent_falls$id)
Health20002011_ds_w2$recent_falls <- recode(HEALTH2000_w2_recent_falls$OIRE_62, "0 = '0';1 = '1';2 = '1';3 = '1';4 = '1';5 = '1';6 = '1';7 = '1';8 = '1';9 = '1';10 = '1';11 = '1';15 = '1';20 = '1';22 = '1';25 = '1';30 = '1';NA = '999' ")
Health20002011_ds_w2$recent_falls <- labelled(Health20002011_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- Health20002011_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(Health20002011_ds_w2$recent_falls)
X<-sum(HEALTH2000_w2_recent_falls$OIRE_62>0,na.rm=TRUE)
BeforeH <- c(X[1],sum(is.na(HEALTH2000_w2_recent_falls$OIRE_62)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">0->1","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(Health20002011_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- Health20002011_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$recent_falls <- recode(Health20002011_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
