---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```


# Data process

## Finland

### Wave 1 

#### Study-specific variable description

 
| **Name** | `KYS3_K1613`| 
|-|-|
| **Label** | `OHIP: dissatisfied with life`| 
| **Table name** | `t00_athlos_2017_02_23` | 
| **Categories** | `1 = Very often` <br/> `2 = Fairly often` <br/> `3 = Occassionally` <br/> `4 = Hardly ever` <br/> `5 = Never` |
| **Missings** |`6 = Don't know` | 
| **Description** |  | 

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_wb','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('KYS3_K1613'), missings = TRUE)
Health20002011_wb <- opal.execute(o,'Health20002011_wb')
```

```{r local1, echo=FALSE}
vbl <- Health20002011_wb$KYS3_K1613
vbl_miss <- 6
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Health20002011_wb)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(Health20002011_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `6 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_wb$id)
Health20002011_ds_w1$evaluative_wb <- car::recode(Health20002011_wb$KYS3_K1613, "1=0; 2=0; 3=1; 4=2; 5=2; 6=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```

```{r importOPAL1, echo=FALSE}
evaluative_wb <- Health20002011_ds_w1
save(evaluative_wb, file = "../RData/w1/evaluative_wb.RData")
rm(evaluative_wb)
```


### Wave 2 

#### Study-specific variable description

| **Name** | `KYS3_K1613`| 
|-|-|
| **Label** | `OHIP: dissatisfied with life`| 
| **Table name** | `t11_athlos_2017_02_27` | 
| **Categories** | `1 = Very often` <br/> `2 = Fairly often` <br/> `3 = Occassionally` <br/> `4 = Hardly ever` <br/> `5 = Never` |
| **Missings** |`6 = Don't know` | 
| **Description** |  | 

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_wb','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('KYS3_K1613'), missings = TRUE)
Health20002011_wb <- opal.execute(o,'Health20002011_wb')
```

```{r local2, echo=FALSE}
vbl <- Health20002011_wb$KYS3_K1613
vbl_miss <- 6
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Health20002011_wb)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(Health20002011_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `6 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_wb$id)
Health20002011_ds_w2$evaluative_wb <- car::recode(Health20002011_wb$KYS3_K1613, "1=0; 2=0; 3=1; 4=2; 5=2; 6=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL2, echo=FALSE}
evaluative_wb <- Health20002011_ds_w2
save(evaluative_wb, file = "../RData/w2/evaluative_wb.RData")
rm(evaluative_wb)
```


# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
