---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Finland


### Wave 1

Not found.


### Wave 2

#### Study-specific variable description



| **Name** | `T11_KYS1_K43_1`|
|-|-|
| **Label** | `Do you have: enough energy for everyday life`|
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories** |  `1 = Not at all; 2 = A little; 3 = Moderately; 4 = Mostly; 5 = Completely` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w2_energy','Health2000-2011.t11_athlos_2017_02_27', variables=list('T11_KYS1_K43_1'), missings = TRUE)
```

```{r local w2, echo=F}
HEALTH2000_w2_energy <- opal.execute(o,'HEALTH2000_w2_energy')
vari <- HEALTH2000_w2_energy$T11_KYS1_K43_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "T11_KYS1_K43_1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_energy, aes(x=factor(T11_KYS1_K43_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 0` 
  * `2 into 0`
  * `3 into 0` 
  * `4 into 1`
  * `5 into 1`
  * `NA into 999`

```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_energy$id)
Health20002011_ds_w2$energy <- car::recode(HEALTH2000_w2_energy$T11_KYS1_K43_1, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1'; NA = '999' ")
Health20002011_ds_w2$energy <- labelled(Health20002011_ds_w2$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- Health20002011_ds_w2$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$energy)
X<-table(HEALTH2000_w2_energy$T11_KYS1_K43_1)
BeforeH <- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(HEALTH2000_w2_energy$T11_KYS1_K43_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}
label(Health20002011_ds_w2$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
energy <- Health20002011_ds_w2
save(energy, file = "../RData/w2/energy.RData")

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$energy <- car::recode(Health20002011_m_ds_w2$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
