---
title: "Hearing general"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process



## Finland


### Wave 1 

#### Study-specific variable description




| **Name** | `KYS3_KUUL`|
|-|-|
| **Label** | `15D hearing` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Categories** |`1 = I can hear normally, i.e. normal speech with or without a hearing aid; 2 = I hear normal speech with a little difficulty; 3 = I hear normal speech with considerable difficulty, in conversation I need voices to be louder than normal; 4 = I hear even loud voices poorly, I am almost deaf` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w1_hearing_gen','Health2000-2011.t00_athlos_2017_02_23', variables=list('KYS3_KUUL'), missings = TRUE)
```

```{r local w1, echo=F}
HEALTH2000_w1_hearing_gen <- opal.execute(o,'HEALTH2000_w1_hearing_gen')
vari <- HEALTH2000_w1_hearing_gen$KYS3_KUUL
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "KYS3_KUUL")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w1_hearing_gen, aes(x=factor(KYS3_KUUL))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0` 
* `NA into 999`

**R script:**
```{r harmo w1}
Health20002011_ds_w1 <- tibble(id=HEALTH2000_w1_hearing_gen$id)
Health20002011_ds_w1$hearing_gen <- car::recode(HEALTH2000_w1_hearing_gen$KYS3_KUUL, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
Health20002011_ds_w1$hearing_gen <- labelled(Health20002011_ds_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- Health20002011_ds_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(Health20002011_ds_w1$hearing_gen)
X<-table(HEALTH2000_w1_hearing_gen$KYS3_KUUL)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HEALTH2000_w1_hearing_gen$KYS3_KUUL)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999")  
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(Health20002011_ds_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- Health20002011_ds_w1
save(hearing_gen, file = "../RData/w1/hearing_gen.RData")

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$hearing_gen <- car::recode(Health20002011_m_ds_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `KYS3_KUUL`|
|-|-|
| **Label** | `hearing` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories** |`1 = I can hear normally, i.e. normal speech with or without a hearing aid; 2 = I hear normal speech with a little difficulty; 3 = I hear normal speech with considerable difficulty, in conversation I need voices to be louder than normal; 4 = I hear even loud voices poorly, I am almost deaf` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'HEALTH2000_w2_hearing_gen','Health2000-2011.t11_athlos_2017_02_27', variables=list('KYS3_KUUL'), missings = TRUE)
```

```{r local w2, echo=F}
HEALTH2000_w2_hearing_gen <- opal.execute(o,'HEALTH2000_w2_hearing_gen')
vari <- HEALTH2000_w2_hearing_gen$KYS3_KUUL
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "KYS3_KUUL")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HEALTH2000_w2_hearing_gen, aes(x=factor(KYS3_KUUL))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4 into 0` 
* `NA into 999`

**R script:**
```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=HEALTH2000_w2_hearing_gen$id)
Health20002011_ds_w2$hearing_gen <- car::recode(HEALTH2000_w2_hearing_gen$KYS3_KUUL, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
Health20002011_ds_w2$hearing_gen <- labelled(Health20002011_ds_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- Health20002011_ds_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$hearing_gen)
X<-table(HEALTH2000_w2_hearing_gen$KYS3_KUUL)
BeforeH <- c(sum(X[2:4]),X[1],sum(is.na(HEALTH2000_w2_hearing_gen$KYS3_KUUL)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999")  
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(Health20002011_ds_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- Health20002011_ds_w2
save(hearing_gen, file = "../RData/w2/hearing_gen.RData")

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$hearing_gen <- car::recode(Health20002011_m_ds_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation
In this study the variable collects the hearing/auditory range of the respondent "with or without it using hearing aid 
or auditory device", while the variable original definition was: "using hearing aid or auditory device"

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
