---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```




# Data process

## Finland


### Wave 1 


```{r assign_fin1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_id','Courage.Courage_Finland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_fin_w1_id <- opal.execute(o,'COURAGE_fin_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_fin1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_id$id)
COURAGE_ds_fin_w1$living_status <- 0
COURAGE_ds_fin_w1$living_status <- labelled(COURAGE_ds_fin_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin1, echo=F}
vari <- COURAGE_ds_fin_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin1, echo=F}
```








## Poland

### Wave 1 


```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_id','Courage.Courage_Poland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_pol_w1_id <- opal.execute(o,'COURAGE_pol_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_id$id)
COURAGE_ds_pol_w1$living_status <- 0
COURAGE_ds_pol_w1$living_status <- labelled(COURAGE_ds_pol_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}
vari <- COURAGE_ds_pol_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1, echo=F}
```







### Wave 2 

```{r assign_pol2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_id','Courage.Courage_Poland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_pol_w1_id <- opal.execute(o,'COURAGE_pol_w1_id')

opal.assign.table.tibble(o, 'COURAGE_pol_w2_id','Courage.Courage_Poland_w2',
                         variables=list('q1004_MMSE'), missings = TRUE)
COURAGE_pol_w2_id <- opal.execute(o,'COURAGE_pol_w2_id')
```


#### Harmonisation algorithm

The harmonize variable is going to be derived as follows: 

* `individuals that appear in wave 2 as 0`
* `individuals that don't appear in wave 2 as 2`


**R script:**
```{r harmo_pol2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w1_id$id)
COURAGE_ds_pol_w2$living_status <- 2
COURAGE_ds_pol_w2$living_status[COURAGE_pol_w1_id$id %in%  COURAGE_pol_w2_id$id] <- 0
COURAGE_ds_pol_w2$living_status <- labelled(COURAGE_ds_pol_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol2, echo=F}
vari <- COURAGE_ds_pol_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2, echo=F}
m <- sum(!(COURAGE_pol_w1_id$id %in% COURAGE_pol_w2_id$id))
BeforeH <- c(dim(COURAGE_pol_w1_id)[1]-m, m)
AfterH <- table(COURAGE_ds_pol_w2$living_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","2")
kable(C)
```








## Spain

### Wave 1



```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_birth$id)
COURAGE_ds_spain_w1$living_status <- 0
COURAGE_ds_spain_w1$living_status <- labelled(COURAGE_ds_spain_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vari <- COURAGE_ds_spain_w1$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1, echo=F}
```


```{r importOPAL_spain1, echo=F}
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$living_status <- car::recode(COURAGE_m_ds_spain_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```









### Wave 2

#### Study-specific variable description



    
| **Name** | `Death`| `q0007_updated`|
|-|-|-|
| **Label** | `Has the individual died? (revised until June 2015)`| `Q0007a updated with mortality data found by UAM`|
| **Table name** | `FinalResultCodes(q0007)_wave1Actualizada` | `FinalResultCodes(q0007)_wave1Actualizada` |
| **Categories** | `0 = No` <br/>  `1 = Yes`| `1 = Completed interview` <br/>  `2 = Partial interview` <br/>  `6 = Final refusal by household` <br/>  `7 = Unable to locate household or individual respondent` <br/>  `8 = No interview because individual respondent is not eligible:` <br/>  `9 = Language barrier` <br/>  `10 = House is vacant or household occupants are elsewhere (season` <br/>  `11 = Unsafe or dangerous area or no access to household/indivudua` <br/>  `14 = Deceased informant` <br/>  `15 = Individual respondent in a health institution:hospital, resi` <br/>  `19 = Final refusal by individual respondent` <br/>  `21 = Address doesn't exist` <br/>  `22 = Didn't sign the consent in previuos study` <br/>  `23 = Didn't sign the current consent` <br/>  `24 = Individual respondent in institution: jail, convent and not` |
| **Description** |  |  |


```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_ls','Courage.FinalResultCodes(q0007)_wave1Actualizada',
                         variables=list('Death', 'q0007_updated'), missings = TRUE)
COURAGE_spain_w2_ls <- opal.execute(o,'COURAGE_spain_w2_ls')
```

```{r local_spain2, echo=F}
vari <- COURAGE_spain_w2_ls$Death
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2_ls, aes(Death)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- COURAGE_spain_w2_ls$q0007_updated
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2_ls, aes(q0007_updated)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the variable 'Death' but the living individuals that have different values of 1 and 2 of the variable q0007_updated will be considered as drop outs and recoded as 2.

**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_ls$id)
COURAGE_ds_spain_w2$living_status <- COURAGE_spain_w2_ls$Death
COURAGE_ds_spain_w2$living_status[which(!(COURAGE_spain_w2_ls$q0007_updated %in% c(1:2)) & COURAGE_spain_w2_ls$Death==0)] <- 2
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vari <- COURAGE_ds_spain_w2$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2, echo=F}
```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:







```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
As there are no death information for Polish population, living status has only values 0 (alive) and 2 (dropout). 





```{r closeRsession, echo=FALSE}
opal.logout(o)
```

