---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```

# Data process

## Finnish


### Wave 1 


```{r assign_fin1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_id','Courage.Courage_Finland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_fin_w1_id <- opal.execute(o,'COURAGE_fin_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_fin1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_id$id)
COURAGE_ds_fin_w1$living_status <- 0
COURAGE_ds_fin_w1$living_status <- labelled(COURAGE_ds_fin_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin1, echo=F}
vari <- COURAGE_ds_fin_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin1, echo=F}
```


```{r importOPAL_fin1, echo=F}
living_status <- COURAGE_ds_fin_w1
save(living_status, file = "../RData/fin_w1/living_status.RData")
rm(living_status)
```







## Polish

### Wave 1 


```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_id','Courage.Courage_Poland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_pol_w1_id <- opal.execute(o,'COURAGE_pol_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_id$id)
COURAGE_ds_pol_w1$living_status <- 0
COURAGE_ds_pol_w1$living_status <- labelled(COURAGE_ds_pol_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}
vari <- COURAGE_ds_pol_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1, echo=F}
```


```{r importOPAL_pol1, echo=F}
living_status <- COURAGE_ds_pol_w1
save(living_status, file = "../RData/pol_w1/living_status.RData")
rm(living_status)
```







### Wave 2 

```{r assign_pol2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_id','Courage.Courage_Poland_w1',
                         variables=list('q0001_rc'), missings = TRUE)
COURAGE_pol_w1_id <- opal.execute(o,'COURAGE_pol_w1_id')

opal.assign.table.tibble(o, 'COURAGE_pol_w2_id','Courage.Courage_Poland_w2',
                         variables=list('q1004_MMSE'), missings = TRUE)
COURAGE_pol_w2_id <- opal.execute(o,'COURAGE_pol_w2_id')
```


#### Harmonisation algorithm

The harmonize variable is going to be derived as follows: 

* `individuals that appear in wave 2 as 0`
* `individuals that doesn't appear in wave 2 as 2`


**R script:**
```{r harmo_pol2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w1_id$id)
COURAGE_ds_pol_w2$living_status <- 2
COURAGE_ds_pol_w2$living_status[COURAGE_pol_w1_id$id %in%  COURAGE_pol_w2_id$id] <- 0
COURAGE_ds_pol_w2$living_status <- labelled(COURAGE_ds_pol_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol2, echo=F}
vari <- COURAGE_ds_pol_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2, echo=F}
m <- sum(!(COURAGE_pol_w1_id$id %in% COURAGE_pol_w2_id$id))
BeforeH <- c(dim(COURAGE_pol_w1_id)[1]-m, m)
AfterH <- table(COURAGE_ds_pol_w2$living_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","2")
kable(C)
```


```{r importOPAL_pol2, echo=F}
living_status <- COURAGE_ds_pol_w2
save(living_status, file = "../RData/pol_w2/living_status.RData")
rm(living_status)
```







## Spain

### Wave 1

#### Study-specific variable description


```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_birth','Courage.Courage_Spain_w1',
                         variables=list('q1010_birth_date'), missings = TRUE)
COURAGE_spain_w1_birth <- opal.execute(o,'COURAGE_spain_w1_birth')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_birth$id)
COURAGE_ds_spain_w1$living_status <- 0
COURAGE_ds_spain_w1$living_status <- labelled(COURAGE_ds_spain_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vari <- COURAGE_ds_spain_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1, echo=F}
```


```{r importOPAL_spain1, echo=F}
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$living_status <- car::recode(COURAGE_m_ds_spain_w1$living_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```









### Wave 2

#### Study-specific variable description


The study-specific variable elected to be harmonised is:

* Name: `Death`
* Label: `Has the individual died? (revised until June 2015)`
* Categories: 
    + `0 = No`
    + `1 = Yes`

```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_ls','Courage.FinalResultCodes(q0007)_wave1Actualizada',
                         variables=list('Death'), missings = TRUE)
COURAGE_spain_w1_ls <- opal.execute(o,'COURAGE_spain_w1_ls')

opal.assign.table.tibble(o, 'COURAGE_spain_inter','Courage.Courage_Spain_w2_1',
                         variables=list('q0006_date_s1'), missings = TRUE)
COURAGE_spain_inter <- opal.execute(o,'COURAGE_spain_inter')

COURAGE_spain_w1_ls <- left_join(x = COURAGE_spain_w1_ls, y = COURAGE_spain_inter, by = 'id')
```

```{r local_spain2, echo=F}
vari <- COURAGE_spain_w1_ls$Death
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1_ls, aes(Death)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than 'Death', the individuals that don't have date of interview are considered as drop outs if they are alive. 

**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w1_ls$id)
COURAGE_ds_spain_w2$living_status <- COURAGE_spain_w1_ls$Death
COURAGE_ds_spain_w2$living_status[which(is.na(COURAGE_spain_w1_ls$q0006_date_s1) & COURAGE_spain_w1_ls$Death==0)] <- 2
COURAGE_ds_spain_w2$living_status <- labelled(COURAGE_ds_spain_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vari <- COURAGE_ds_spain_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2, echo=F}
```


# Quality estimation
As there are no death information for Polish population, living status has only values 0 (alive) and 2 (dropout). 

```{r save, echo=FALSE}
living_status <- COURAGE_ds_spain_w1
save(living_status, file = "../RData/spain_w1/living_status.RData")
rm(living_status)

living_status <- COURAGE_ds_spain_w2
save(living_status, file = "../RData/spain_w2/living_status.RData")
rm(living_status)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

