---
title: "Suicidal Ideation last 12 months"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/suicidal_ideation_12mDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/suicidal_ideation_12mDS.R')
```



# Data process

## Finland

### Wave 1

#### Study-specific variable description

| **Name** | `q4058_morbid` |
|-|-|
| **Label** | `Morbid thoughts` | 
| **Table name**  | `Courage_Finland_w1` | 
| **Categories** | `1 = Yes` <br/> `2 = No` | 
| **Missings** | `8 = DK` |
| **Description** |  | 


```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_si_12m', 'Courage.Courage_Finland_w1', variables=list('q4058_morbid'), missings = T)
Courage_si_12m <- opal.execute(o,'Courage_si_12m')

```



```{r local fin_w1, echo=F}

vbl <- Courage_si_12m$q4058_morbid
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4058_morbid))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep 1 into 1`
* `recode 2 into 0`
* `recode 8 into 998`
* `NA into 999`

**R script:**

```{r harmo fin_w1}

# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=Courage_si_12m$id)
COURAGE_ds_fin_w1$suicidal_ideation_12m <- car::recode(Courage_si_12m$q4058_morbid, "2=0; 8=998; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$suicidal_ideation_12m
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(suicidal_ideation_12m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation fin_w1, echo=F}

```



## Poland

### Wave 1


#### Study-specific variable description

| **Name** | `q4058_morbid` |
|-|-|
| **Label** | `Morbid thoughts`| 
| **Table name**  | `Courage_Poland_w1`| 
| **Categories** | `1 = Yes`<br/>`2 = No` | `
| **Missings** |`8 = DK`|
| **Description** |  | 


```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_si_12m', 'Courage.Courage_Poland_w1', variables=list('q4058_morbid'), missings = T)
Courage_si_12m <- opal.execute(o,'Courage_si_12m')

```



```{r local pol_w1, echo=F}

vbl <- Courage_si_12m$q4058_morbid
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4058_morbid))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep 1 into 1`
* `recode 2 into 0`
* `recode 8 into 998`
* `NA into 999`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=Courage_si_12m$id)
COURAGE_ds_pol_w1$suicidal_ideation_12m <- car::recode(Courage_si_12m$q4058_morbid, "2=0; 8=998; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$suicidal_ideation_12m
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(suicidal_ideation_12m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation pol_w1, echo=F}

```




### Wave 2

#### Study-specific variable description

| **Name** | `q4058_morbid_s1` |
|-|-|
| **Label** | `thinking about death`| 
| **Table name**  | `Courage_Poland_w2`| 
| **Categories** | `1 = Yes`<br/>`2 = No` | `
| **Missings** |`8 = DK`|
| **Description** |  | 


```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'Courage_si_12m', 'Courage.Courage_Poland_w2', variables=list('q4058_morbid_s1'), missings = T)
Courage_si_12m <- opal.execute(o,'Courage_si_12m')

```



```{r local pol_w2, echo=F}

vbl <- Courage_si_12m$q4058_morbid_s1
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4058_morbid_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep 1 into 1`
* `recode 2 into 0`
* `recode 8 into 998`
* `recode 9 into 996`
* `NA into 999`


**R script:**

```{r harmo pol_w2}

# Categorical variable harmonization
COURAGE_ds_pol_w2 <- tibble(id=Courage_si_12m$id)
COURAGE_ds_pol_w2$suicidal_ideation_12m <- car::recode(Courage_si_12m$q4058_morbid_s1, "2=0; 8=998; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- COURAGE_ds_pol_w2$suicidal_ideation_12m
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(suicidal_ideation_12m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation pol_w2, echo=F}

```


## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q4585_ideation` | `q4587_ideat12` |
|-|-|-|
| **Label** | `Suicidal ideation`| `Suicidal ideation in past 12 months`|
| **Table name**  | `Courage_Spain_w1`| `Courage_Spain_w1`|
| **Categories** | `1 = Yes` <br/> `2 = No` | `1 = Yes` <br/> `2 = No` | 
| **Missings** |`8 = DK` <br/> `9 = RF` | `8 = DK` <br/> `9 = RF` |
| **Description** |  | |

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_si_12m','Courage.Courage_Spain_w1',variables=list('q4585_ideation', 'q4587_ideat12'), missings = T)
Courage_si_12m <- opal.execute(o,'Courage_si_12m')

```



```{r local spain_w1, echo=F}

vbl <- Courage_si_12m$q4585_ideation
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4585_ideation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Courage_si_12m$q4587_ideat12
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4587_ideat12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* if `q4585_ideation = 2` into `0`
* if `q4585_ideation = 1`
    + if `q4587_ideat12 = 2` into `0`
    + if `q4587_ideat12 = 1` into `1`
* if `q4585_ideation = 8, 9 or NA` 
    + if `q4587_ideat12 = 1` into `1`
    + if `q4587_ideat12 = 2` into `0`
    + if `q4587_ideat12 = 8` into `998`
    + if `q4587_ideat12 = 9` into `997`
    + if `q4587_ideat12 = NA` into `999`

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=Courage_si_12m$id)
COURAGE_ds_spain_w1$suicidal_ideation_12m <- NA
COURAGE_ds_spain_w1$suicidal_ideation_12m[Courage_si_12m$q4585_ideation == 2 | (Courage_si_12m$q4585_ideation == 1 & Courage_si_12m$q4587_ideat12 == 2) | (Courage_si_12m$q4585_ideation %in% 8:9 & Courage_si_12m$q4587_ideat12 == 2) | (is.na(Courage_si_12m$q4585_ideation) & Courage_si_12m$q4587_ideat12 == 2)] <- 0

COURAGE_ds_spain_w1$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation == 1 & Courage_si_12m$q4587_ideat12 == 1) | (Courage_si_12m$q4585_ideation %in% 8:9 & Courage_si_12m$q4587_ideat12 == 1) | (is.na(Courage_si_12m$q4585_ideation) & Courage_si_12m$q4587_ideat12 == 1)] <- 1

COURAGE_ds_spain_w1$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation %in% 8:9 & Courage_si_12m$q4587_ideat12 == 8) | (is.na(Courage_si_12m$q4585_ideation) & Courage_si_12m$q4587_ideat12 == 8) | (Courage_si_12m$q4585_ideation == 8 & is.na(Courage_si_12m$q4587_ideat12))] <- 998
COURAGE_ds_spain_w1$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation %in% 8:9 & Courage_si_12m$q4587_ideat12 == 9) | (is.na(Courage_si_12m$q4585_ideation) & Courage_si_12m$q4587_ideat12 == 9) | (Courage_si_12m$q4585_ideation == 9 & is.na(Courage_si_12m$q4587_ideat12))] <- 997

COURAGE_ds_spain_w1$suicidal_ideation_12m[(is.na(Courage_si_12m$q4585_ideation) & is.na(Courage_si_12m$q4587_ideat12))] <- 999
```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$suicidal_ideation_12m
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(suicidal_ideation_12m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation spain_w1, echo=F}

```




### Wave 2


#### Study-specific variable description

| **Name** | `q4585_ideation_s1` | `q4587_ideat12_s1` |
|-|-|-|
| **Label** | `Suicidal ideation`| `Suicidal ideation in past 12 months`|
| **Table name**  | `Courage_Spain_w2_1`| `Courage_Spain_w2_1`|
| **Categories** | `1 = Yes` <br/> `2 = No` | `1 = Yes` <br/> `2 = No` | 
| **Missings** |`8 = DK` <br/> `9 = RF` | `8 = DK` <br/> `9 = RF` |
| **Description** |  | |

```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'Courage_si_12m','Courage.Courage_Spain_w2_1',variables=list('q4585_ideation_s1', 'q4587_ideat12_s1'), missings = T)
Courage_si_12m <- opal.execute(o,'Courage_si_12m')

```



```{r local spain_w2, echo=F}

vbl <- Courage_si_12m$q4585_ideation_s1
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4585_ideation_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Courage_si_12m$q4587_ideat12_s1
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(Courage_si_12m)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(Courage_si_12m, aes(x=factor(q4587_ideat12_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* if `q4585_ideation_s1 = 2` into `0`
* if `q4585_ideation_s1 = 1`
    + if `q4587_ideat12_s1 = 2` into `0`
    + if `q4587_ideat12_s1 = 1` into `1`
* if `q4585_ideation_s1 = 8, 9 or NA` 
    + if `q4587_ideat12_s1 = 1` into `1`
    + if `q4587_ideat12_s1 = 2` into `0`
    + if `q4587_ideat12_s1 = 8` into `998`
    + if `q4587_ideat12_s1 = 9` into `997`
    + if `q4587_ideat12_s1 = NA` into `999`

**R script:**

```{r harmo spain_w2}

# Categorical variable harmonization
COURAGE_ds_spain_w2 <- tibble(id=Courage_si_12m$id)
COURAGE_ds_spain_w2$suicidal_ideation_12m <- NA
COURAGE_ds_spain_w2$suicidal_ideation_12m[Courage_si_12m$q4585_ideation_s1 == 2 | (Courage_si_12m$q4585_ideation_s1 == 1 & Courage_si_12m$q4587_ideat12_s1 == 2) | (Courage_si_12m$q4585_ideation_s1 %in% 8:9 & Courage_si_12m$q4587_ideat12_s1 == 2) | (is.na(Courage_si_12m$q4585_ideation_s1) & Courage_si_12m$q4587_ideat12_s1 == 2)] <- 0

COURAGE_ds_spain_w2$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation_s1 == 1 & Courage_si_12m$q4587_ideat12_s1 == 1) | (Courage_si_12m$q4585_ideation_s1 %in% 8:9 & Courage_si_12m$q4587_ideat12_s1 == 1) | (is.na(Courage_si_12m$q4585_ideation_s1) & Courage_si_12m$q4587_ideat12_s1 == 1)] <- 1

COURAGE_ds_spain_w2$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation_s1 %in% 8:9 & Courage_si_12m$q4587_ideat12_s1 == 8) | (is.na(Courage_si_12m$q4585_ideation_s1) & Courage_si_12m$q4587_ideat12_s1 == 8) | (Courage_si_12m$q4585_ideation_s1 == 8 & is.na(Courage_si_12m$q4587_ideat12_s1))] <- 998
COURAGE_ds_spain_w2$suicidal_ideation_12m[(Courage_si_12m$q4585_ideation_s1 %in% 8:9 & Courage_si_12m$q4587_ideat12_s1 == 9) | (is.na(Courage_si_12m$q4585_ideation_s1) & Courage_si_12m$q4587_ideat12_s1 == 9) | (Courage_si_12m$q4585_ideation_s1 == 9 & is.na(Courage_si_12m$q4587_ideat12_s1))] <- 997

COURAGE_ds_spain_w2$suicidal_ideation_12m[(is.na(Courage_si_12m$q4585_ideation_s1) & is.na(Courage_si_12m$q4587_ideat12_s1))] <- 999
```


#### Statistics of the new harmonized variable

```{r descript spain_w2, echo=F}

vbl <- COURAGE_ds_spain_w2$suicidal_ideation_12m
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(suicidal_ideation_12m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation spain_w2, echo=F}

```




## Descriptive statistics of the harmonised variable accross populations and waves

In Poland the suicidal ideation was evaluated with the item Q4058. This item was not answered by all the participants, only the people that have depression answered. In Spain the suicidal ideation was evaluated with the item Q4585. This item was answered by all the participants.






```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation

The specific variables from the study that have been used were only answered by the individuals with depression. For this reason, there are a lot missing values. 


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





