---
title: "Day of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ddeath`
* Variable label: `Day of death`
* Variable description: `day of death`
* Domain: `Death`
* Value type: `continous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Day of death"
```



# Data process

## Spain
    
### Wave 1 

There is no variable.




### Wave 2 

#### Study-specific variable description

| **Name** | `F_defuncion`|
|-|-|
| **Label** | `F_defuncion`|
| **Table name** | `selfreported_fdefuncion` |
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w2_dinter','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2d_interview'), missings = TRUE)
ENRICA_w2_dinter <- opal.execute(o,'ENRICA_w2_dinter')

opal.assign.table.tibble(o, 'ENRICA_dead','ENRICA.selfreported_fdefuncion',
                         variables=list('F_defuncion'), missings = TRUE)
ENRICA_dead <- opal.execute(o,'ENRICA_dead')

ENRICA_dead$d_dead <- as.Date(ENRICA_dead$F_defuncion, "%m/%d/%Y")
ENRICA_dead$ddead <- as.numeric(format(ENRICA_dead$d_dead, '%d'))
```

```{r local2, echo=FALSE}
vari <- ENRICA_dead$ddead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_dead, aes(ddead)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable.

**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_dead$id)
ENRICA_ds_w2$ddeath <- car::recode(ENRICA_dead$ddead, "NA=999")
ENRICA_ds_w2$ddeath <- labelled(ENRICA_ds_w2$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ENRICA_ds_w2$ddeath
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(ENRICA_dead$ddead, useNA = "ifany")
AfterH <- table(ENRICA_ds_w2$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

```{r importOPAL2, echo=FALSE}
#val_labels(ENRICA_ds_w2) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

ddeath <- ENRICA_ds_w2
save(ddeath, file = "../RData/w2/ddeath.RData")
rm(ddeath)
```




### Wave 3 

#### Study-specific variable description

| **Name** | `F_defuncion`|
|-|-|
| **Label** | `F_defuncion`|
| **Table name** | `selfreported_fdefuncion` |
| **Description** |  |


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w3_dinter','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3d_interview'), missings = TRUE)
ENRICA_w3_dinter <- opal.execute(o,'ENRICA_w3_dinter')

opal.assign.table.tibble(o, 'ENRICA_dead','ENRICA.selfreported_fdefuncion',
                         variables=list('F_defuncion'), missings = TRUE)
ENRICA_dead <- opal.execute(o,'ENRICA_dead')

ENRICA_dead$d_dead <- as.Date(ENRICA_dead$F_defuncion, "%m/%d/%Y")
ENRICA_dead$ddead <- as.numeric(format(ENRICA_dead$d_dead, '%d'))
```

```{r local3, echo=FALSE}
vari <- ENRICA_dead$ddead
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_dead, aes(ddead)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable.

**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_dead$id)
ENRICA_ds_w3$ddeath <- car::recode(ENRICA_dead$ddead, "NA=999")
ENRICA_ds_w3$ddeath <- labelled(ENRICA_ds_w3$ddeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ENRICA_ds_w3$ddeath
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(ddeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(ENRICA_dead$ddead, useNA = "ifany")
AfterH <- table(ENRICA_ds_w3$ddeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


```{r importOPAL3, echo=FALSE}
#val_labels(ENRICA_ds_w3) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

ddeath <- ENRICA_ds_w3
save(ddeath, file = "../RData/w3/ddeath.RData")
rm(ddeath)

```

### Quality estimation
Either wave 2 or 3 have the same dates of deads, that doesn't mean that all the individuals with date od interview are dead at that wave. 



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
