---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```


# Data process

## Spain

### Wave 1 


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w1_id','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1d_interview'), missings = TRUE)
ENRICA_w1_id <- opal.execute(o,'ENRICA_w1_id')
```


#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_id$id)
ENRICA_ds_w1$living_status <- 0
ENRICA_ds_w1$living_status <- labelled(ENRICA_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ENRICA_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```

```{r importOPAL1, echo=FALSE}
#val_labels(ENRICA_ds_w1) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')

living_status <- ENRICA_ds_w1
save(living_status, file = "../RData/w1/living_status.RData")
rm(living_status)
```






### Wave 2 

#### Study-specific variable description

| **Name** | `F_defuncion`| `w2d_interview`|
|-|-|-|
| **Label** | `F_defuncion`| |
| **Table name** | `selfreported_fdefuncion` | `ENRICA_spss_wave2` |
| **Description** |  | |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w2_id','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2d_interview'), missings = TRUE)
ENRICA_w2_id <- opal.execute(o,'ENRICA_w2_id')

opal.assign.table.tibble(o, 'ENRICA_dead','ENRICA.selfreported_fdefuncion',
                         variables=list('F_defuncion'), missings = TRUE)
ENRICA_dead <- opal.execute(o,'ENRICA_dead')

ENRICA_dead$F_defuncion <- as.Date(ENRICA_dead$F_defuncion, "%m/%d/%Y")

ENRICA_ls <- left_join(x = ENRICA_w2_id, y = ENRICA_dead, by = 'id')
```

```{r local2, echo=FALSE}
vari <- ENRICA_w2_id$w2d_interview
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w2_id, aes(w2d_interview)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of interview") + ylab("Frequency")

vari <- ENRICA_ls$F_defuncion
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_ls, aes(F_defuncion)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of death") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonize variable is going to be derived as follows: 

* `individuals that has date of interview earlier than the date of death as 0`
* `individuals without date of death and with date od interview as 0`
* `individuals that has date of interview later than the date of death as 1`

**R script:**


```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_ls$id)
ENRICA_ds_w2$living_status <- NA
ENRICA_ds_w2$living_status[which(ENRICA_ls$w2d_interview > ENRICA_ls$F_defuncion)] <- 1
ENRICA_ds_w2$living_status[which(ENRICA_ls$w2d_interview < ENRICA_ls$F_defuncion)] <- 0
ENRICA_ds_w2$living_status[which(!is.na(ENRICA_ls$w2d_interview) & is.na(ENRICA_ls$F_defuncion))] <- 0
ENRICA_ds_w2$living_status[is.na(ENRICA_w2_id$w2d_interview)] <- 2
ENRICA_ds_w2$living_status <- labelled(ENRICA_ds_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ENRICA_ds_w2$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```

```{r importOPAL2, echo=FALSE}
#val_labels(ENRICA_ds_w2) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

living_status <- ENRICA_ds_w2
save(living_status, file = "../RData/w2/living_status.RData")
rm(living_status)
```




### Wave 3 

#### Study-specific variable description

| **Name** | `F_defuncion`| `w3d_interview`|
|-|-|-|
| **Label** | `F_defuncion`| |
| **Table name** | `selfreported_fdefuncion` | `ENRICA_spss_wave3` |
| **Description** |  | |

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w3_id','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3d_interview'), missings = TRUE)
ENRICA_w3_id <- opal.execute(o,'ENRICA_w3_id')
opal.assign.table.tibble(o, 'ENRICA_dead','ENRICA.selfreported_fdefuncion',
                         variables=list('F_defuncion'), missings = TRUE)
ENRICA_dead <- opal.execute(o,'ENRICA_dead')

ENRICA_dead$F_defuncion <- as.Date(ENRICA_dead$F_defuncion, "%m/%d/%Y")

ENRICA_ls <- left_join(x = ENRICA_w3_id, y = ENRICA_dead, by = 'id')
```

```{r local3, echo=FALSE}
vari <- ENRICA_ls$w3d_interview
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_ls, aes(w3d_interview)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of interview") + ylab("Frequency")

vari <- ENRICA_ls$F_defuncion
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_ls, aes(F_defuncion)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is going to be derived as follows: 

* `individuals that has date of interview earlier than the date of death as 0`
* `individuals without date of death and with date of interview as 0`
* `individuals that has date of interview later than the date of death as 1`
* `individuals neither date of interview nor date of death as 2`
* `individuals without date of interview and date of death earlier than 19-06-2015 as 1`
* `individuals without date of interview and date of death later than 19-06-2015 as 2`

**R script:**


```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_ls$id)
ENRICA_ds_w3$living_status <- NA
ENRICA_ds_w3$living_status[which(ENRICA_ls$w3d_interview > ENRICA_ls$F_defuncion)] <- 1
ENRICA_ds_w3$living_status[which(ENRICA_ls$w3d_interview < ENRICA_ls$F_defuncion)] <- 0
ENRICA_ds_w3$living_status[which(!is.na(ENRICA_ls$w3d_interview) & is.na(ENRICA_ls$F_defuncion))] <- 0
ENRICA_ds_w3$living_status[which(is.na(ENRICA_ls$w3d_interview) &  ENRICA_ls$F_defuncion<as.Date("19-06-2015", "%d-%m-%Y"))] <- 1
ENRICA_ds_w3$living_status[which(is.na(ENRICA_ls$w3d_interview) &  ENRICA_ls$F_defuncion>as.Date("19-06-2015", "%d-%m-%Y"))] <- 2
ENRICA_ds_w3$living_status[which(is.na(ENRICA_ls$w3d_interview) &  is.na(ENRICA_ls$F_defuncion))] <- 2
ENRICA_ds_w3$living_status <- labelled(ENRICA_ds_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ENRICA_ds_w3$living_status
kable(Categorical_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Missing values")
ggplot(ENRICA_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=FALSE}
```

```{r importOPAL3, echo=FALSE}
#val_labels(ENRICA_ds_w3) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

living_status <- ENRICA_ds_w3
save(living_status, file = "../RData/w3/living_status.RData")
rm(living_status)
```


### Quality estimation
At wave 3 the individuals without date of interview and date of death later than the last interview done 
were considered as drop outs. 


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
