---
title: "Dementia case"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/dementiaDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/dementiaDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst 

### Wave 1 

#### Study-specific variable description

There is no variable.





### Wave 2 

#### Study-specific variable description

There is no variable.

### Wave 3 

#### Study-specific variable description


| **Name** | `h_001_18`| 
|-|-|
| **Label** | `Q10:MENTAL CONDITION LAST WEEK -1- FELT UNUSUAL IN SOME WAY`| `Q10:MENTAL CONDITION LAST WEEK -2- HAD NO APPETITE` | 
| **Table name** | `jstar_2011_5cities` | 
| **Categories** |`1 = Newly diagnosed with or indicated` <br/> `2 = Fully recovered once but recurred in the past 2 years` <br/> `3 = Still be treated` <br/> `4 = Fully recovered/Never diagnosed with/indicated` |  
| **Description** |  |  

```{r assign_aksst3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_dem','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('h_001_18'), missings = TRUE)
JSTAR_dem <- opal.execute(o,'JSTAR_dem')
```

```{r local_aksst3, echo=FALSE}
vari <- JSTAR_dem[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,4 into 0`
* `1,3 into 1`


**R script:**

```{r harmo_aksst3, echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_dem$id)
JSTAR_aksst_ds_w3$dementia <- car::recode(JSTAR_dem[[2]], "2=0; 3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$dementia
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(JSTAR_aksst_ds_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_aksst3, echo=FALSE}
dementia <- JSTAR_aksst_ds_w3
save(dementia, file = "../RData/aksst_w3/dementia.RData")
rm(dementia, JSTAR_dep)
```


#### Validation


## tn 

### Wave 1 

#### Study-specific variable description


There is no variable.




### Wave 2 

#### Study-specific variable description

| **Name** | `h_001_18`| 
|-|-|
| **Label** | `Q10:MENTAL CONDITION LAST WEEK -1- FELT UNUSUAL IN SOME WAY`| `Q10:MENTAL CONDITION LAST WEEK -2- HAD NO APPETITE` | 
| **Table name** | `jstar_2011_2citie` | 
| **Categories** |`1 = Newly diagnosed with or indicated` <br/> `2 = Fully recovered once but recurred in the past 2 years` <br/> `3 = Still be treated` <br/> `4 = Fully recovered/Never diagnosed with/indicated` |  
| **Description** |  |  


```{r assign_tn2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_dem','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('h_001_18'), missings = TRUE)
JSTAR_dem <- opal.execute(o,'JSTAR_dem')
```

```{r local_tn2, echo=FALSE}
vari <- JSTAR_dem[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `2,4 into 0`
* `1,3 into 1`

**R script:**

```{r harmo_tn2, echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_dem$id)
JSTAR_tn_ds_w2$dementia <- car::recode(JSTAR_dem[[2]], "2=0; 3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$dementia
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(JSTAR_tn_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Validation

```{r importOPAL_tn2, echo=FALSE}
dementia <- JSTAR_tn_ds_w2
save(dementia, file = "../RData/tn_w2/dementia.RData")
rm(dementia, JSTAR_dep)
```



## cth 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `h_001_18`| 
|-|-|
| **Label** | `Q10:MENTAL CONDITION LAST WEEK -1- FELT UNUSUAL IN SOME WAY`| `Q10:MENTAL CONDITION LAST WEEK -2- HAD NO APPETITE` | 
| **Table name** | `jstar_2011_3cities` | 
| **Categories** |`1 = Newly diagnosed with or indicated` <br/> `2 = Fully recovered once but recurred in the past 2 years` <br/> `3 = Still be treated` <br/> `4 = Fully recovered/Never diagnosed with/indicated` |  
| **Description** |  |  



```{r assign_cth1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_dem','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('h_001_18'), missings = TRUE)
JSTAR_dem <- opal.execute(o,'JSTAR_dem')
```

```{r local_cth1, echo=FALSE}
vari <- JSTAR_dem[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `2,4 into 0`
* `1,3 into 1`


**R script:**

```{r harmo_cth1, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_dem$id)
JSTAR_cth_ds_w1$dementia <- car::recode(JSTAR_dem[[2]], "2=0; 3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$dementia
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(JSTAR_cth_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Validation

```{r importOPAL_cth1, echo=FALSE}
dementia <- JSTAR_cth_ds_w1
save(dementia, file = "../RData/cth_w1/dementia.RData")
rm(dementia, JSTAR_dep)
```


# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```