---
title: "Age of dementia diagnosis"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/dementia_ageDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/dementia_ageDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst 

### Wave 1 

#### Study-specific variable description

There is no variable.





### Wave 2 

#### Study-specific variable description

There is no variable.

### Wave 3 

#### Study-specific variable description


There is no variable.

#### Validation


## tn 

### Wave 1 

#### Study-specific variable description


There is no variable.




### Wave 2 

#### Study-specific variable description

There is no variable.




## cth 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `h_001_18_1`| 
|-|-|
| **Label** | `DEMENTIA, AGE` | 
| **Table name** | `jstar_2011_3cities` | 
| **Categories** |`1 = Newly diagnosed with or indicated` <br/> `2 = Fully recovered once but recurred in the past 2 years` <br/> `3 = Still be treated` <br/> `4 = Fully recovered/Never diagnosed with/indicated` |  
| **Description** |  |  



```{r assign_cth1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_dem','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('h_001_18_1'), missings = TRUE)
JSTAR_dem <- opal.execute(o,'JSTAR_dem')
```

```{r local_cth1, echo=FALSE}
vari <- JSTAR_dem[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = label(vari))
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_dem, aes(vari)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cth1, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_dem$id)
JSTAR_cth_ds_w1$dementia_age <- car::recode(JSTAR_dem[[2]], "2=0; 3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$dementia_age
kable(Continuous_summary(var = vari, missing_values = )[3], caption = "dementia_age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_cth_ds_w1, aes(dementia_age)) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(!vari %in% miss_values_vector)) + xlab("dementia_age") + ylab("Frequency")
```

#### Validation


```{r importOPAL_cth1, echo=FALSE}
dementia_age <- JSTAR_cth_ds_w1
save(dementia_age, file = "../RData/cth_w1/dementia_age.RData")
rm(dementia_age, JSTAR_dep)
```


# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```