---
title: "Month of interview"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ######################################################### --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")
```

<!-- ######################################################### --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `month_of_interview`
* Label: `month of interview"`
* Categories: 
    + `1 = january`
    + `2 = february`
    + `3 = march`
    + `4 = april`
    + `5 = may`
    + `6 = june`
    + `7 = july`
    + `8 = august`
    + `9 = september`
    + `10 = october`
    + `11 = november`
    + `12 = december`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not applicable`
    + `995 = Does not answer`
    + `996 = Not attempt/not done`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`



# Data process

## Wave 1 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `imonth`
* Label: `Interview Month`


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_minter2','CHARLS.weight_wave1', variables=list('imonth'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',     variables=list('var'), missings = TRUE)
```

```{r local1, echo=F}
CHARLS_w1_minter2 <- opal.execute(o,'CHARLS_w1_minter2')
CHARLS_w1_minter2$id[CHARLS_w1_minter2$id==151156201] <- "15115620101"
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_minter2$oldid <- CHARLS_w1_minter2$id
CHARLS_w1_minter2$id <- CHARLS_ids(ids = CHARLS_w1_minter2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), imonth=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_minter <- Add_indiv(old = CHARLS_w1_minter2, new = CHARLS_w1_id)


Categorical_summary(var = CHARLS_w1_minter$imonth, missing_values = NA)
ggplot(CHARLS_w1_minter, aes(x=factor(imonth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but missing values should be recoded as follows:

* `NA into 999`


R script:

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_minter$id)
CHARLS_ds_w1$mintw <- car::recode(CHARLS_w1_minter$imonth, "NA=999")
CHARLS_ds_w1$mintw <- labelled(CHARLS_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = CHARLS_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(CHARLS_w1_minter$imonth)
AfterH <- table(CHARLS_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "6", "7", "8", "9", "10", "11", "12")
C
```




## Wave 2 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `imonth`
* Label: `Birth Month`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_minter2','CHARLS.Weights_modif_albert_wave2',
                         variables=list('imonth'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=F}
CHARLS_w2_minter2 <- opal.execute(o,'CHARLS_w2_minter2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], imonth=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_minter <- Add_indiv(old = CHARLS_w2_minter2, new = CHARLS_w2_id)

Categorical_summary(var = CHARLS_w2_minter$imonth, missing_values = NA)
ggplot(CHARLS_w2_minter, aes(x=factor(imonth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but missing values should be recoded as follows:

* `NA into 999`


R script:

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_minter$id)
CHARLS_ds_w2$mintw <- car::recode(CHARLS_w2_minter$imonth, "NA=999")
CHARLS_ds_w2$mintw <- labelled(CHARLS_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = CHARLS_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(CHARLS_w2_minter$imonth, useNA = "ifany")
AfterH <- table(CHARLS_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "7", "8", "9", "10", "11", "12", "NA->999")
C
```


# Quality control

No comments.




```{r save, echo=FALSE}
mintw <- CHARLS_ds_w1
save(mintw, file = "../RData/w1/mintw.RData")
rm(mintw)

mintw <- CHARLS_ds_w2
save(mintw, file = "../RData/w2/mintw.RData")
rm(mintw)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
