---
title: "Year of interview"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ######################################################### --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")
```

<!-- ######################################################### --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `yintw`
* Label: `year of interview`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`


# Data process

## Wave 1 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `iyear`
* Label: `Interview Year`
* Type of variable: `countinous`

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_yinter2','CHARLS.weight_wave1',
                         variables=list('iyear'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=F}
CHARLS_w1_yinter2 <- opal.execute(o,'CHARLS_w1_yinter2')
CHARLS_w1_yinter2$id[CHARLS_w1_yinter2$id==151156201] <- "15115620101"
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_yinter2$oldid <- CHARLS_w1_yinter2$id
CHARLS_w1_yinter2$id <- CHARLS_ids(ids = CHARLS_w1_yinter2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), iyear=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_yinter <- Add_indiv(old = CHARLS_w1_yinter2, new = CHARLS_w1_id)

Categorical_summary(var = CHARLS_w1_yinter$iyear, missing_values = NA)
ggplot(CHARLS_w1_yinter, aes(x=factor(iyear))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values should be recoded as follows:

* `NA into 999`

R script:

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_yinter$id)
CHARLS_ds_w1$yintw <- car::recode(CHARLS_w1_yinter$iyear, "NA=999")
CHARLS_ds_w1$yintw <- labelled(CHARLS_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = CHARLS_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(CHARLS_w1_yinter$iyear)
AfterH <- table(CHARLS_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2011", "2012")
C
```

## Wave 2 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `iyear`
* Label: `Interview Year`
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_yinter2','CHARLS.Weights_modif_albert_wave2',
                         variables=list('iyear'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=F}
CHARLS_w2_yinter2 <- opal.execute(o,'CHARLS_w2_yinter2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], iyear=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_yinter <- Add_indiv(old = CHARLS_w2_yinter2, new = CHARLS_w2_id)


Categorical_summary(var = CHARLS_w2_yinter$iyear, missing_values = NA)
ggplot(CHARLS_w2_yinter, aes(x=factor(iyear))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values should be recoded as follows:

* `NA into 999`

R script:

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_yinter$id)
CHARLS_ds_w2$yintw <- car::recode(CHARLS_w2_yinter$iyear, "NA=999")
CHARLS_ds_w2$yintw <- labelled(CHARLS_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = CHARLS_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation2, echo=F}
H <- table(CHARLS_w2_yinter$iyear, CHARLS_ds_w2$yintw, useNA = "ifany")
#BeforeH <- c(sum(BeforeH[1], BeforeH[3]), BeforeH[2])
#AfterH <- table(CHARLS_ds_w2$yintw)
#C <- rbind(BeforeH,AfterH)
#colnames(C) <- c("2013", "2014", "999")
H
```

# Quality control

The date was the same as the study specific variable taking into account the wave time lapse information.
We do not know the status of the participants missing in wave 2.
(Need to check living status variable if they are deaths or dropouts).



```{r save, echo=FALSE}
yintw <- CHARLS_ds_w1
save(yintw, file = "../RData/w1/yintw.RData")
rm(yintw)

yintw <- CHARLS_ds_w2
save(yintw, file = "../RData/w2/yintw.RData")
rm(yintw)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```