---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```



# Data process

## Wave 1 

### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `ind_weight`
* Label: `Individual Weight without Non-response Adjustment`

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'charls_w1_w2','CHARLS.weight_wave1', variables=list('ind_weight'), missings = TRUE)
charls_w1_w2 <- opal.execute(o,'charls_w1_w2')

charls_w1_w2$id[which(charls_w1_w2$id==151156201)] <- "15115620101"

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


charls_w1_w2$oldid <- charls_w1_w2$id
charls_w1_w2$id <- CHARLS_ids(ids = charls_w1_w2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ind_weight=as.numeric(new_2[,2]))
  new_22
}

charls_w1_w <- Add_indiv(old = charls_w1_w2, new = CHARLS_w1_id)
```

```{r local1, echo=F}
Continuous_summary(var = charls_w1_w$ind_weight, missing_values = NA)
```

### Harmonization algorithm

**R script:**

```{r harmo1}
CHARLS_ds_w1   <- tibble(id=charls_w1_w$id)
sn <- length(charls_w1_w$ind_weight[!is.na(charls_w1_w$ind_weight)]) # (s)ample (n)umber: Nº individuals with non-missing weight
pn <- sum(charls_w1_w$ind_weight, na.rm=T) # (p)opulation (n)umber: Nº of individuals in the population
CHARLS_ds_w1$w <- charls_w1_w$ind_weight * sn / pn
CHARLS_ds_w1$w <- car::recode(CHARLS_ds_w1$w, "NA=996")
CHARLS_ds_w1$w <- labelled(CHARLS_ds_w1$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(CHARLS_ds_w1) <- c("id","w")
label(CHARLS_ds_w1$w) <- "Weights for sample representativeness"
```

### Statistics of the new harmonised variable
```{r descript1, echo=F}
Continuous_summary(var = CHARLS_ds_w1$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```



## Wave 2

### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `INDV_weight`
* Label: `Cross-section Individual Weight without Nonresponse Adjustment`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'charls_w2_w2','CHARLS.Weights_modif_albert_wave2', variables=list('INDV_weight'), missings = TRUE)
charls_w2_w2 <- opal.execute(o,'charls_w2_w2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], INDV_weight=as.numeric(new_2[,2]))
  new_22
}

charls_w2_w <- Add_indiv(old = charls_w2_w2, new = CHARLS_w2_id)
```

```{r local2, echo=F}
Continuous_summary(var = charls_w2_w$INDV_weight, missing_values = NA)
```

### Harmonization algorithm

**R script:**

```{r harmo2}
CHARLS_ds_w2   <- tibble(id=charls_w2_w$id)
sn <- length(charls_w2_w$INDV_weight[!is.na(charls_w2_w$INDV_weight)]) # (s)ample (n)umber: Nº individuals with non-missing weight
pn <- sum(charls_w2_w$INDV_weight, na.rm=T) # (p)opulation (n)umber: Nº of individuals in the population
CHARLS_ds_w2$w <- charls_w2_w$INDV_weight * sn / pn
CHARLS_ds_w2$w <- car::recode(CHARLS_ds_w2$w, "NA=996")
CHARLS_ds_w2$w <- labelled(CHARLS_ds_w2$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(CHARLS_ds_w2) <- c("id","w")
label(CHARLS_ds_w2$w) <- "Weights for sample representativeness"
```

### Statistics of the new harmonised variable
```{r descript2, echo=F}
Continuous_summary(var = CHARLS_ds_w2$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```


# Quality estimation

The date was the same as the study specific variable taking into account the wave time lapse information.
We do not know the status of the participants missing in wave 2.
(Need to check living status variable if they are deaths or dropouts).




```{r save, echo=FALSE}
w <- CHARLS_ds_w1
save(w, file = "../RData/w1/w.RData")
rm(w)

w <- CHARLS_ds_w2
save(w, file = "../RData/w2/w.RData")
rm(w)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


