---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```


<!-- ########################################################## --> 

# Data process

## CHARLS: China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variable description

| **Name** | `proxy`| `proxy`| `proxy`| `proxy`| `proxy`| `proxy`| `proxy`| `proxy`|
|-|-|-|-|-|-|-|-|-|
| **Label** | `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`| `Interview Done by Proxy`|
| **Table name** | `household_roster_wave1` | `family_information_wave1` | `demographic_background_wave1` | `work_retirement_and_pension_wave1` | `household_income_wave1` | `health_status_and_functioning_wave1` | `health_care_and_insurance_wave1` | `family_transfer_wave1` |
| **Categories** |`0 = No`| `0 = No`| `0 = No`| `0 = No`| `0 = No`| `0 = No`| `0 = No`| `0 = No`|
| | `1 = Yes` | `1 = Yes` | `1 = Yes` | `1 = Yes` | `1 = Yes` | `1 = Yes` | `1 = Yes` | `1 = Yes` |
| **Description** |  |  |  |  |  |  |  |  |

```{r assign1, echo=FALSE}

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


opal.assign.table.tibble(o, 'CHARLS_p1','CHARLS.household_roster_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p1 <- opal.execute(o,'CHARLS_p1')

names(CHARLS_p1) <- c("id", "proxy1")
CHARLS_p1$id <- CHARLS_ids(ids = CHARLS_p1$id)

CHARLS_proxy <- left_join(CHARLS_w1_id, CHARLS_p1, by='id')
CHARLS_proxy <- CHARLS_proxy[,-2]


opal.assign.table.tibble(o, 'CHARLS_p2','CHARLS.family_information_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p2 <- opal.execute(o,'CHARLS_p2')

names(CHARLS_p2) <- c("id", "proxy2")
CHARLS_p2$id <- CHARLS_ids(ids = CHARLS_p2$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p2, by='id')


opal.assign.table.tibble(o, 'CHARLS_p3','CHARLS.demographic_background_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p3 <- opal.execute(o,'CHARLS_p3')

names(CHARLS_p3) <- c("id", "proxy3")
CHARLS_p3$id <- CHARLS_ids(ids = CHARLS_p3$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p3, by='id')


opal.assign.table.tibble(o, 'CHARLS_p4','CHARLS.work_retirement_and_pension_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p4 <- opal.execute(o,'CHARLS_p4')

names(CHARLS_p4) <- c("id", "proxy4")
CHARLS_p4$id <- CHARLS_ids(ids = CHARLS_p4$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p4, by='id')


opal.assign.table.tibble(o, 'CHARLS_p5','CHARLS.household_income_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p5 <- opal.execute(o,'CHARLS_p5')

names(CHARLS_p5) <- c("id", "proxy5")
CHARLS_p5$id <- CHARLS_ids(ids = CHARLS_p5$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p5, by='id')


opal.assign.table.tibble(o, 'CHARLS_p6','CHARLS.health_status_and_functioning_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p6 <- opal.execute(o,'CHARLS_p6')

names(CHARLS_p6) <- c("id", "proxy6")
CHARLS_p6$id <- CHARLS_ids(ids = CHARLS_p6$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p6, by='id')


opal.assign.table.tibble(o, 'CHARLS_p7','CHARLS.health_care_and_insurance_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p7 <- opal.execute(o,'CHARLS_p7')

names(CHARLS_p7) <- c("id", "proxy7")
CHARLS_p7$id <- CHARLS_ids(ids = CHARLS_p7$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p7, by='id')


opal.assign.table.tibble(o, 'CHARLS_p8','CHARLS.family_transfer_wave1', variables=list('proxy'), missings = TRUE)
CHARLS_p8 <- opal.execute(o,'CHARLS_p8')

names(CHARLS_p8) <- c("id", "proxy8")
CHARLS_p8$id <- CHARLS_ids(ids = CHARLS_p8$id)

CHARLS_proxy <- left_join(CHARLS_proxy, CHARLS_p8, by='id')


```

```{r local1, echo=FALSE}
vari <- CHARLS_proxy$proxy1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_proxy$proxy8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

* `if any of the variables is 1 (yes) recode proxy = 1`
* `otherwise proxy = 0`

**R script:**

```{r harmo1, echo=TRUE}


CHARLS_proxy$all <- apply(CHARLS_proxy[,-1], MARGIN = 1, function(x) paste0(x[1], x[2], x[3], x[4], x[5], x[6], x[7], x[8]))

CHARLS_proxy$have1 <- apply(CHARLS_proxy[,2:9], MARGIN = 1, FUN = function(x) sum(x==1, na.rm = TRUE)>=1)
CHARLS_proxy$nmis <- apply(CHARLS_proxy[,2:9], MARGIN = 1, FUN = function(x) sum(is.na(x)))

CHARLS_ds_w1 <- tibble(id=CHARLS_proxy$id)
CHARLS_ds_w1$proxy <- 0
CHARLS_ds_w1$proxy[which(CHARLS_proxy$have1)] <- 1
CHARLS_ds_w1$proxy[CHARLS_proxy$nmis==8] <- 999
CHARLS_ds_w1$proxy <- labelled(CHARLS_ds_w1$proxy, labels = cat_label)
label(CHARLS_ds_w1$proxy) <- ds_label_all

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 2 

Not found.





# Quality estimation

The next variables were found looking study-specific variables on the existence of a proxy respondent. The corresponding questions ask about receiving assistance in the respective answering sections. We think that the idea of receiving assistance could introduce bias, so we choose keep the `proxy` variables used above.

| **Table name** | **Variable** |
|-|-|
| `household_roster_wave1` | `a020`\* |
| `demographic_background_wave1` | `bf008` |
| `family_transfer_wave1` | `cg003` |
| `health_status_and_functioning_wave1` | `db032` |
| `health_care_and_insurance_wave1` | `ef006` |
| `work_retirement_and_pension_wave1` | `fn081` |
| `household_income_wave1` | `ge011`\*, `ha076` |
| `individual_income_wave1` | `hd012` |
| `Demographic_Background_wave2` | `bf008` |
| `Family_Information_wave2` | `cg003_w2_2_` |
| `Family_Transfer_wave2` | `cf007_w2` |
| `Health_Status_and_Functioning_wave2` | `db032` |
| `Health_Care_and_Insurance_wave2` | `ef006` |
| `Household_Income_wave2` | `ge011`, `ha076` |
| `Individual_Income_wave2` | `hd012` |

\*Found in the questionnaire but not in the databasis.



```{r save, echo=FALSE}
proxy <- CHARLS_ds_w1
save(proxy, file = "../RData/w1/proxy.RData")
rm(proxy)

```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
