---
title: "Number of times in Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_vig_paDS.R')
```





# Data process









## Finland

### Wave 1 


#### Study-specific variable description

| **Name** | `q3026_days` |`vig_pa`|
|-|-|-|
| **Label** | `In a typical week, on how many days do you do vigorous intensity sports, fitness or recreational (leisure) activities?` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `Courage_Finland_w1` | `vig_pa`|
| **Categories:**| `continuous` |`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |


```{r assign fin w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1', variables=list('q3026_days'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
load(paste0(datafolder,"fin_w1/vig_pa.RData"))
COURAGE_fin_w1 <- left_join(COURAGE_fin_w1,vig_pa, by="id")
rm(vig_pa)

```

```{r local fin w1, echo=F}
vbl <- COURAGE_fin_w1$q3026_days
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_fin_w1)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_fin_w1, aes(q3026_days)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

vbl <- COURAGE_fin_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable `q3026_days` it has to be recoded as follows:

* `q3026*2`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo fin w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$n_vig_pa <- car::recode(COURAGE_fin_w1$q3026_days*2, "NA = 999 ")
COURAGE_ds_fin_w1$n_vig_pa[which(COURAGE_fin_w1$vig_pa==0)] <- 0
```

#### Statistical description of the new harmonised variable
```{r descript fin w1, echo=F}
vbl <- COURAGE_ds_fin_w1$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_fin_w1, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation fin w1, echo=F}
```





## Poland

### Wave 1 


#### Study-specific variable description

| **Name** | `q3026_days` |`vig_pa`|
|-|-|-|
| **Label** | `In a typical week, on how many days do you do vigorous intensity sports, fitness or recreational (leisure) activities?` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `Courage_Poland_w1` |`vig_pa`|
| **Categories:**| `continuous` |`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` |`991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |


```{r assign pol w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1', variables=list('q3026_days'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
load(paste0(datafolder,"pol_w1/vig_pa.RData"))
COURAGE_pol_w1 <- left_join(COURAGE_pol_w1,vig_pa, by="id")
rm(vig_pa)

```

```{r local pol w1, echo=F}
vbl <- COURAGE_pol_w1$q3026_days
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_pol_w1)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w1, aes(q3026_days)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable `q3026_days` it has to be recoded as follows:

* `q3026*2`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo pol w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$n_vig_pa <- car::recode(COURAGE_pol_w1$q3026_days*2, "NA = 999 ")
COURAGE_ds_pol_w1$n_vig_pa[which(COURAGE_pol_w1$vig_pa==0)] <- 0
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=F}
vbl <- COURAGE_ds_pol_w1$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w1, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation pol w1, echo=F}
```





### Wave 2


#### Study-specific variable description

| **Name** | `q3026_days_s1` | `vig_pa`|
|-|-|-|
| **Label** | `In a typical week, on how many days do you do vigorous intensity sports, fitness or recreational (leisure) activities?` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `Courage_Poland_w2` |`vig_pa`|
| **Categories:**| `continuous` |`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |


```{r assign pol w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2', variables=list('q3026_days_s1'), missings = TRUE)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')
load(paste0(datafolder,"pol_w2/vig_pa.RData"))
COURAGE_pol_w2 <- left_join(COURAGE_pol_w2,vig_pa, by="id")
rm(vig_pa)

```

```{r local pol w2, echo=F}
vbl <- COURAGE_pol_w2$q3026_days_s1
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_pol_w2)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_pol_w2, aes(q3026_days_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w2$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(COURAGE_pol_w2, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable `q3026_days` it has to be recoded as follows:

* `q3026*2`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo pol w2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$n_vig_pa <- car::recode(COURAGE_pol_w2$q3026_days_s1*2, "NA = 999 ")
COURAGE_ds_pol_w2$n_vig_pa[which(COURAGE_pol_w2$vig_pa==0)] <- 0
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=F}
vbl <- COURAGE_ds_pol_w2$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w2, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation pol w2, echo=F}
```







## Spain

### Wave 1 


#### Study-specific variable description

| **Name** | `q3026_days` |`vig_pa`|
|-|-|-|
| **Label** |`In a typical week, on how many days do you do vigorous intensity sports, fitness or recreational (leisure) activities?` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `Courage_Spain_w1` |
`vig_pa`|
| **Categories:**| `continuous` |`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` |`991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |


```{r assign spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1', variables=list('q3026_days'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
load(paste0(datafolder,"spain_w1/vig_pa.RData"))
COURAGE_spain_w1 <- left_join(COURAGE_spain_w1,vig_pa, by="id")
rm(vig_pa)

```

```{r local spain w1, echo=F}
vbl <- COURAGE_spain_w1$q3026_days
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_spain_w1)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w1, aes(q3026_days)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable `q3026_days` it has to be recoded as follows:

* `q3026*2`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$n_vig_pa <- car::recode(COURAGE_spain_w1$q3026_days*2, "NA = 999 ")
COURAGE_ds_spain_w1$n_vig_pa[which(COURAGE_spain_w1$vig_pa==0)] <- 0
```

#### Statistical description of the new harmonised variable
```{r descript spain w1, echo=F}
vbl <- COURAGE_ds_spain_w1$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w1, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation spain w1, echo=F}
```







### Wave 2


#### Study-specific variable description

| **Name** | `q3026_days_s1` | `vig_pa`|
|-|-|-|
| **Label** |`In a typical week, on how many days do you do vigorous intensity sports, fitness or recreational (leisure) activities?` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `Courage_Spain_w2_1` |`vig_pa`|
| **Categories:**| `continuous` |`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` |  `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |


```{r assign spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1', variables=list('q3026_days_s1'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
load(paste0(datafolder,"spain_w2/vig_pa.RData"))
COURAGE_spain_w2 <- left_join(COURAGE_spain_w2,vig_pa, by="id")
rm(vig_pa)

```

```{r local spain w2, echo=F}
vbl <- COURAGE_spain_w2$q3026_days_s1
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(COURAGE_spain_w2)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_spain_w2, aes(q3026_days_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable `q3026_days` it has to be recoded as follows:

* `q3026*2`						
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$n_vig_pa <- car::recode(COURAGE_spain_w2$q3026_days_s1*2, "NA = 999 ")
COURAGE_ds_spain_w2$n_vig_pa[which(COURAGE_spain_w2$vig_pa==0)] <- 0
```

#### Statistical description of the new harmonised variable
```{r descript spain w2, echo=F}
vbl <- COURAGE_ds_spain_w2$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation spain w2, echo=F}
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
