---
title: "Current smoker"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/current_smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/current_smokingDS.R')
```



# Data process



## Finland


### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3001_used_tobac`
* Label: `Used tobaco?`
* Categories:
   + `1 = YES` 
   + `2 = NO` 
* Missings
   + `NA`

* Name: `q3002_use_tobaco`
* Label: `Use tobaco?`
* Categories:
   + `1 = YES, DAILY`
   + `2 = YES, NOT DAILY`
   + `3 = NOT AT ALL` 
* Missings
   + `NA`

```{r assign finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_finland_w1_current_smoking','Courage.Courage_Finland_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
```

```{r local finland w1, echo=F}
COURAGE_finland_w1_current_smoking <- opal.execute(o,'COURAGE_finland_w1_current_smoking')
Categorical_summary(COURAGE_finland_w1_current_smoking$q3001_used_tobac)
ggplot(COURAGE_finland_w1_current_smoking, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
Categorical_summary(COURAGE_finland_w1_current_smoking$q3002_use_tobaco)
ggplot(COURAGE_finland_w1_current_smoking, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001_used_tobac=1 & q3002_use_tobaco=1,2 into 1` 
* `q3001_used_tobac=1 & q3002_use_tobaco=3 into 0`
* `q3001_used_tobac=2 into 0`
* `NA into 999` 

```{r harmo finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_finland_w1_current_smoking$id)
COURAGE_ds_fin_w1$current_smoking <- rep(999,length(COURAGE_ds_fin_w1$id))
COURAGE_ds_fin_w1$current_smoking[COURAGE_finland_w1_current_smoking$q3001_used_tobac==2|(COURAGE_finland_w1_current_smoking$q3001_used_tobac==1&COURAGE_finland_w1_current_smoking$q3002_use_tobaco==3)]<-0
COURAGE_ds_fin_w1$current_smoking[COURAGE_finland_w1_current_smoking$q3001_used_tobac==1&(COURAGE_finland_w1_current_smoking$q3002_use_tobaco==1|COURAGE_finland_w1_current_smoking$q3002_use_tobaco==2)]<-1
#COURAGE_ds_fin_w1$current_smoking <- Recode(COURAGE_finland_w1_current_smoking$q3001_used_tobac, "1 = '1';2 = '0';NA = '999'")
COURAGE_ds_fin_w1$current_smoking <- labelled(COURAGE_ds_fin_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript finland w1, echo=F}
Categorical_summary(var = COURAGE_ds_fin_w1$current_smoking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$current_smoking)
X <- c(sum(na.omit(COURAGE_finland_w1_current_smoking$q3001_used_tobac==2|(COURAGE_finland_w1_current_smoking$q3001_used_tobac==1&COURAGE_finland_w1_current_smoking$q3002_use_tobaco==3))),sum(na.omit(COURAGE_finland_w1_current_smoking$q3001_used_tobac==1&(COURAGE_finland_w1_current_smoking$q3002_use_tobaco==1|COURAGE_finland_w1_current_smoking$q3002_use_tobaco==2))))
BeforeH<- c(X[1:2],sum(is.na(COURAGE_finland_w1_current_smoking$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001_used_tobac=2|(q3001_used_tobac=1&q3002_use_tobaco=3)->0","q3001_used_tobac=1&q3002_use_tobaco=1,2->1","NA->999") 
kable(C)
```





## Poland


### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3001_used_tobac`
* Label: `Used tobaco?`
* Categories:
   + `1 = YES` 
   + `2 = NO` 
* Missings
   + `NA`

* Name: `q3002_use_tobaco`
* Label: `Use tobaco?`
* Categories:
   + `1 = YES, DAILY`
   + `2 = YES, NOT DAILY`
   + `3 = NOT AT ALL` 
* Missings
   + `NA`

```{r assign poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_poland_w1_current_smoking','Courage.Courage_Poland_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
```

```{r local poland w1, echo=F}
COURAGE_poland_w1_current_smoking <- opal.execute(o,'COURAGE_poland_w1_current_smoking')
Categorical_summary(COURAGE_poland_w1_current_smoking$q3001_used_tobac)
ggplot(COURAGE_poland_w1_current_smoking, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
Categorical_summary(COURAGE_poland_w1_current_smoking$q3002_use_tobaco)
ggplot(COURAGE_poland_w1_current_smoking, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001_used_tobac=1 & q3002_use_tobaco=1,2 into 1` 
* `q3001_used_tobac=1 & q3002_use_tobaco=3 into 0`
* `q3001_used_tobac=2 into 0`
* `NA into 999` 

```{r harmo poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_poland_w1_current_smoking$id)
COURAGE_ds_pol_w1$current_smoking <- rep(999,length(COURAGE_ds_pol_w1$id))
COURAGE_ds_pol_w1$current_smoking[COURAGE_poland_w1_current_smoking$q3001_used_tobac==2|(COURAGE_poland_w1_current_smoking$q3001_used_tobac==1&COURAGE_poland_w1_current_smoking$q3002_use_tobaco==3)]<-0
COURAGE_ds_pol_w1$current_smoking[COURAGE_poland_w1_current_smoking$q3001_used_tobac==1&(COURAGE_poland_w1_current_smoking$q3002_use_tobaco==1|COURAGE_poland_w1_current_smoking$q3002_use_tobaco==2)]<-1
#COURAGE_ds_pol_w1$current_smoking <- Recode(COURAGE_poland_w1_current_smoking$q3001_used_tobac, "1 = '1';2 = '0';NA = '999'")
COURAGE_ds_pol_w1$current_smoking <- labelled(COURAGE_ds_pol_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript poland w1, echo=F}
Categorical_summary(var = COURAGE_ds_pol_w1$current_smoking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$current_smoking)
X <- c(sum(na.omit(COURAGE_poland_w1_current_smoking$q3001_used_tobac==2|(COURAGE_poland_w1_current_smoking$q3001_used_tobac==1&COURAGE_poland_w1_current_smoking$q3002_use_tobaco==3))),sum(na.omit(COURAGE_poland_w1_current_smoking$q3001_used_tobac==1&(COURAGE_poland_w1_current_smoking$q3002_use_tobaco==1|COURAGE_poland_w1_current_smoking$q3002_use_tobaco==2))))
BeforeH<- c(X[1:2],sum(is.na(COURAGE_poland_w1_current_smoking$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001_used_tobac=2|(q3001_used_tobac=1&q3002_use_tobaco=3)->0","q3001_used_tobac=1&q3002_use_tobaco=1,2->1","NA->999") 
kable(C)
```





### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3002_use_tobaco_s1`
* Label: `Use tobaco?`
* Categories:
   + `1 = YES, DAILY`
   + `2 = YES, NOT DAILY`
   + `3 = NOT AT ALL` 
* Missings
   + `NA`

```{r assign poland w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_poland_w2_current_smoking','Courage.Courage_Poland_w2', variables=list('q3002_use_tobaco_s1'), missings = TRUE)
```

```{r local poland w2, echo=F}
COURAGE_poland_w2_current_smoking <- opal.execute(o,'COURAGE_poland_w2_current_smoking')
Categorical_summary(COURAGE_poland_w2_current_smoking$q3002_use_tobaco_s1)
ggplot(COURAGE_poland_w2_current_smoking, aes(x=factor(q3002_use_tobaco_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3 into 0`
* `NA into 999` 

```{r harmo poland w2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_poland_w2_current_smoking$id)
COURAGE_ds_pol_w2$current_smoking <- Recode(COURAGE_poland_w2_current_smoking$q3002_use_tobaco_s1, "1 = '1';2 = '1';3 = '0';NA = '999'")
COURAGE_ds_pol_w2$current_smoking <- labelled(COURAGE_ds_pol_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript poland w2, echo=F}
Categorical_summary(var = COURAGE_ds_pol_w2$current_smoking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w2, echo=F}
AfterH <- table(COURAGE_ds_pol_w2$current_smoking)
X <- table(COURAGE_poland_w2_current_smoking$q3002_use_tobaco_s1)
BeforeH<- c(sum(X[3]),sum(X[1:2]),sum(is.na(COURAGE_poland_w2_current_smoking$q3002_use_tobaco_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->0","1,2->1","NA->999") 
kable(C)
```



## Spain

#### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3001_used_tobac`
* Label: `Used tobaco?`
* Categories:
   + `1 = YES` 
   + `2 = NO` 
* Missings
   + `NA`

* Name: `q3002_use_tobaco`
* Label: `Use tobaco?`
* Categories:
   + `1 = YES, DAILY`
   + `2 = YES, NOT DAILY`
   + `3 = NOT AT ALL` 
* Missings
   + `NA`

```{r assign spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_current_smoking','Courage.Courage_Spain_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
```

```{r local spain w1, echo=F}
COURAGE_spain_w1_current_smoking <- opal.execute(o,'COURAGE_spain_w1_current_smoking')
Categorical_summary(COURAGE_spain_w1_current_smoking$q3001_used_tobac)
ggplot(COURAGE_spain_w1_current_smoking, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
Categorical_summary(COURAGE_spain_w1_current_smoking$q3002_use_tobaco)
ggplot(COURAGE_spain_w1_current_smoking, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001_used_tobac=1 & q3002_use_tobaco=1,2 into 1` 
* `q3001_used_tobac=1 & q3002_use_tobaco=3 into 0`
* `q3001_used_tobac=2 into 0`
* `NA into 999` 

```{r harmo spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_current_smoking$id)
COURAGE_ds_spain_w1$current_smoking <- rep(999,length(COURAGE_ds_spain_w1$id))
COURAGE_ds_spain_w1$current_smoking[COURAGE_spain_w1_current_smoking$q3001_used_tobac==2|(COURAGE_spain_w1_current_smoking$q3001_used_tobac==1&COURAGE_spain_w1_current_smoking$q3002_use_tobaco==3)]<-0
COURAGE_ds_spain_w1$current_smoking[COURAGE_spain_w1_current_smoking$q3001_used_tobac==1&(COURAGE_spain_w1_current_smoking$q3002_use_tobaco==1|COURAGE_spain_w1_current_smoking$q3002_use_tobaco==2)]<-1
#COURAGE_ds_spain_w1$current_smoking <- Recode(COURAGE_spain_w1_current_smoking$q3001_used_tobac, "1 = '1';2 = '0';NA = '999'")
COURAGE_ds_spain_w1$current_smoking <- labelled(COURAGE_ds_spain_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w1, echo=F}
Categorical_summary(var = COURAGE_ds_spain_w1$current_smoking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$current_smoking)
X <- c(sum(na.omit(COURAGE_spain_w1_current_smoking$q3001_used_tobac==2|(COURAGE_spain_w1_current_smoking$q3001_used_tobac==1&COURAGE_spain_w1_current_smoking$q3002_use_tobaco==3))),sum(na.omit(COURAGE_spain_w1_current_smoking$q3001_used_tobac==1&(COURAGE_spain_w1_current_smoking$q3002_use_tobaco==1|COURAGE_spain_w1_current_smoking$q3002_use_tobaco==2))))
BeforeH<- c(X[1:2],sum(is.na(COURAGE_spain_w1_current_smoking$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001_used_tobac=2|(q3001_used_tobac=1&q3002_use_tobaco=3)->0","q3001_used_tobac=1&q3002_use_tobaco=1,2->1","NA->999") 
kable(C)
```






### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3001_used_tobac_s1`
* Label: `Used tobaco?`
* Categories:
   + `1 = YES` 
   + `2 = NO` 
* Missings
   + `NA`

* Name: `q3002_use_tobaco_s1`
* Label: `Use tobaco?`
* Categories:
   + `1 = YES, DAILY`
   + `2 = YES, NOT DAILY`
   + `3 = NOT AT ALL`
   + `4 = The participant said that he/she had never smoked before`
* Missings
   + `NA`

```{r assign spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_current_smoking','Courage.Courage_Spain_w2_1', variables=list('q3001_used_tobac_s1','q3002_use_tobaco_s1'), missings = TRUE)
```

```{r local spain w2, echo=F}
COURAGE_spain_w2_current_smoking <- opal.execute(o,'COURAGE_spain_w2_current_smoking')
Categorical_summary(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1)
ggplot(COURAGE_spain_w2_current_smoking, aes(x=factor(q3001_used_tobac_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
Categorical_summary(COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1)
ggplot(COURAGE_spain_w2_current_smoking, aes(x=factor(q3002_use_tobaco_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001_used_tobac_s1=1 & q3002_use_tobaco_s1=1,2 into 1` 
* `q3001_used_tobac_s1=1 & q3002_use_tobaco_s1=3,4 into 0`
* `q3001_used_tobac_s1=2 into 0`
* `NA into 999` 

```{r harmo spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_current_smoking$id)
COURAGE_ds_spain_w2$current_smoking <- rep(999,length(COURAGE_ds_spain_w2$id))
COURAGE_ds_spain_w2$current_smoking[COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==2|(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==1&(COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==3|COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==4))]<-0
COURAGE_ds_spain_w2$current_smoking[COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==1&(COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==1|COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==2)]<-1
#COURAGE_ds_spain_w2$current_smoking <- Recode(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1, "1 = '1';2 = '0';NA = '999'")
COURAGE_ds_spain_w2$current_smoking <- labelled(COURAGE_ds_spain_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w2, echo=F}
Categorical_summary(var = COURAGE_ds_spain_w2$current_smoking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$current_smoking)
X <- c(sum(na.omit(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==2|(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==1&(COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==3|COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==4)))),sum(na.omit(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1==1&(COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==1|COURAGE_spain_w2_current_smoking$q3002_use_tobaco_s1==2))))
BeforeH<- c(X[1:2],sum(is.na(COURAGE_spain_w2_current_smoking$q3001_used_tobac_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001_used_tobac_s1=2|(q3001_used_tobac_s1=1&q3002_use_tobaco_s1=3,4)->0","q3001_used_tobac_s1=1&q3002_use_tobaco_s1=1,2->1","NA->999") 
kable(C)
```





```{r final, echo = F}

l.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, pol_w2 = COURAGE_ds_pol_w2, spain_w1 = COURAGE_ds_spain_w1, spain_w2 = COURAGE_ds_spain_w2)
ln.hds <- names(l.hds)

for(name in names(l.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**


```{r summ}
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[ln.hds[1]]][[2]]), length(l.hds[[ln.hds[2]]][[2]]) , length(l.hds[[ln.hds[3]]][[2]]), length(l.hds[[ln.hds[4]]][[2]]), length(l.hds[[ln.hds[5]]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Poland_W2", "Spain_W1", "Spain_W2")
kable(t.hds)

```


# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  current_smoking <- l.hds[[index]]
  save(current_smoking, file = paste0(datafolder,names(l.hds)[index],"/current_smoking.RData"))
}

```
<!-- ########################################################## --> 

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
