---
title: "Smoking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/smokingDS.R')
```

# Data process


## Finland

### Wave 1 

#### Study-specific variable description

| **Name** | `q3001_used_tobac` | `q3002_use_tobaco` |
|-|-|-|
| **Label** | `Used tobaco?` | `Use tobaco?` |
| **Table name** | `Courage_Finland_w1` | `Courage_Finland_w1` |
| **Categories:**| `1 = YES` <br/> `2 = NO` | `1 = YES, DAILY` <br/> `2 = YES, NOT DAILY` <br/> `3 = NOT AT ALL` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
```

```{r local finland w1, echo=F}
vbl <- COURAGE_fin_w1$q3001_used_tobac
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_fin_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_fin_w1$q3002_use_tobaco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_fin_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001=2 into 0`
* `q3001=1&q3002=3 into 1` 
* `q3002=1|q3002=2 into 2` 
* `NA into 999` 

```{r harmo finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$smoking <- rep(999,length(COURAGE_ds_fin_w1$id))
COURAGE_ds_fin_w1$smoking[which(COURAGE_fin_w1$q3001_used_tobac==2)]<-0
COURAGE_ds_fin_w1$smoking[which(COURAGE_fin_w1$q3001_used_tobac==1&COURAGE_fin_w1$q3002_use_tobaco==3)]<-1
COURAGE_ds_fin_w1$smoking[which(COURAGE_fin_w1$q3002_use_tobaco==1|COURAGE_fin_w1$q3002_use_tobaco==2)]<-2
```

#### Statistical description of the new harmonised variable
```{r descript finland w1, echo=F}
vbl <- COURAGE_ds_fin_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$smoking)
X <- c(sum(na.omit(COURAGE_fin_w1$q3001_used_tobac==2)),sum(na.omit(COURAGE_fin_w1$q3001_used_tobac==1&COURAGE_fin_w1$q3002_use_tobaco==3)),sum(na.omit(COURAGE_fin_w1$q3002_use_tobaco==1|COURAGE_fin_w1$q3002_use_tobaco==2)))
BeforeH<- c(X,sum(is.na(COURAGE_fin_w1$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001=2->0","q3001=1&q3002=3->1","q3002=1|q3002=2->1","NA->999") 
kable(C)
```


## Poland

### Wave 1 

#### Study-specific variable description

| **Name** | `q3001_used_tobac` | `q3002_use_tobaco` |
|-|-|-|
| **Label** | `Used tobaco?` | `Use tobaco?` |
| **Table name** | `Courage_Poland_w1` | `Courage_Poland_w1` |
| **Categories:**| `1 = YES` <br/> `2 = NO` | `1 = YES, DAILY` <br/> `2 = YES, NOT DAILY` <br/> `3 = NOT AT ALL` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |

```{r assign poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
```

```{r local poland w1, echo=F}
vbl <- COURAGE_pol_w1$q3001_used_tobac
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_pol_w1$q3002_use_tobaco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_pol_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001=2 into 0`
* `q3001=1&q3002=3 into 1` 
* `q3002=1|q3002=2 into 2` 
* `NA into 999`  

```{r harmo poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$smoking <- rep(999,length(COURAGE_ds_pol_w1$id))
COURAGE_ds_pol_w1$smoking[which(COURAGE_pol_w1$q3001_used_tobac==2)]<-0
COURAGE_ds_pol_w1$smoking[which(COURAGE_pol_w1$q3001_used_tobac==1&COURAGE_pol_w1$q3002_use_tobaco==3)]<-1
COURAGE_ds_pol_w1$smoking[which(COURAGE_pol_w1$q3002_use_tobaco==1|COURAGE_pol_w1$q3002_use_tobaco==2)]<-2
```

#### Statistical description of the new harmonised variable
```{r descript poland w1, echo=F}
vbl <- COURAGE_ds_pol_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$smoking)
X <- c(sum(na.omit(COURAGE_pol_w1$q3001_used_tobac==2)),sum(na.omit(COURAGE_pol_w1$q3001_used_tobac==1&COURAGE_pol_w1$q3002_use_tobaco==3)),sum(na.omit(COURAGE_pol_w1$q3002_use_tobaco==1|COURAGE_pol_w1$q3002_use_tobaco==2)))
BeforeH<- c(X,sum(is.na(COURAGE_pol_w1$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001=2->0","q3001=1&q3002=3->1","q3002=1|q3002=2->1","NA->999") 
kable(C)
```



### Wave 2

Not found




## Spain

### Wave 1 

#### Study-specific variable description

| **Name** | `q3001_used_tobac` | `q3002_use_tobaco` |
|-|-|-|
| **Label** | `Used tobaco?` | `Use tobaco?` |
| **Table name** | `Courage_Spain_w1` | `Courage_Spain_w1` |
| **Categories:**| `1 = YES` <br/> `2 = NO` | `1 = YES, DAILY` <br/> `2 = YES, NOT DAILY` <br/> `3 = NOT AT ALL` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |

```{r assign spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1', variables=list('q3001_used_tobac','q3002_use_tobaco'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
```

```{r local spain w1, echo=F}
vbl <- COURAGE_spain_w1$q3001_used_tobac
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q3001_used_tobac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w1$q3002_use_tobaco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(q3002_use_tobaco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001=2 into 0`
* `q3001=1&q3002=3 into 1` 
* `q3002=1|q3002=2 into 2` 
* `NA into 999` 

```{r harmo spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$smoking <- rep(999,length(COURAGE_ds_spain_w1$id))
COURAGE_ds_spain_w1$smoking[which(COURAGE_spain_w1$q3001_used_tobac==2)]<-0
COURAGE_ds_spain_w1$smoking[which(COURAGE_spain_w1$q3001_used_tobac==1&COURAGE_spain_w1$q3002_use_tobaco==3)]<-1
COURAGE_ds_spain_w1$smoking[which(COURAGE_spain_w1$q3002_use_tobaco==1|COURAGE_spain_w1$q3002_use_tobaco==2)]<-2

```

#### Statistical description of the new harmonised variable
```{r descript spain w1, echo=F}
vbl <- COURAGE_ds_spain_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$smoking)
X <- c(sum(na.omit(COURAGE_spain_w1$q3001_used_tobac==2)),sum(na.omit(COURAGE_spain_w1$q3001_used_tobac==1&COURAGE_spain_w1$q3002_use_tobaco==3)),sum(na.omit(COURAGE_spain_w1$q3002_use_tobaco==1|COURAGE_spain_w1$q3002_use_tobaco==2)))
BeforeH<- c(X,sum(is.na(COURAGE_spain_w1$q3001_used_tobac)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001=2->0","q3001=1&q3002=3->1","q3002=1|q3002=2->1","NA->999") 
kable(C)
```




### Wave 2 

#### Study-specific variable description


| **Name** | `q3001_used_tobac_s1` | `q3002_use_tobaco_s1` |
|-|-|-|
| **Label** | `Used tobaco?` | `Use tobaco?` |
| **Table name** | `Courage_Spain_w2_1` | `Courage_Spain_w2_1` |
| **Categories:**| `1 = YES` <br/> `2 = NO` | `1 = YES, DAILY` <br/> `2 = YES, NOT DAILY` <br/> `3 = NOT AT ALL` <br/> `4 = The participant said that he/she had never smoked before` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |

```{r assign spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1', variables=list('q3001_used_tobac_s1','q3002_use_tobaco_s1'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
```

```{r local spain w2, echo=F}
vbl <- COURAGE_spain_w2$q3001_used_tobac_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q3001_used_tobac_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- COURAGE_spain_w2$q3002_use_tobaco_s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(COURAGE_spain_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(q3002_use_tobaco_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3001=2 into 0`
* `q3001=1&q3002=3 into 1` 
* `q3002=1|q3002=2 into 2` 
* `NA into 999` 

```{r harmo spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$smoking <- rep(999,length(COURAGE_ds_spain_w2$id))
COURAGE_ds_spain_w2$smoking[which(COURAGE_spain_w2$q3001_used_tobac_s1==2)]<-0
COURAGE_ds_spain_w2$smoking[which(COURAGE_spain_w2$q3001_used_tobac_s1==1&COURAGE_spain_w2$q3002_use_tobaco_s1==3)]<-1
COURAGE_ds_spain_w2$smoking[which(COURAGE_spain_w2$q3002_use_tobaco_s1==1|COURAGE_spain_w2$q3002_use_tobaco_s1==2)]<-2

```

#### Statistical description of the new harmonised variable
```{r descript spain w2, echo=F}
vbl <- COURAGE_ds_spain_w2$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$smoking)
X <- c(sum(na.omit(COURAGE_spain_w2$q3001_used_tobac_s1==2)),sum(na.omit(COURAGE_spain_w2$q3001_used_tobac_s1==1&COURAGE_spain_w2$q3002_use_tobaco_s1==3)),sum(na.omit(COURAGE_spain_w2$q3002_use_tobaco_s1==1|COURAGE_spain_w2$q3002_use_tobaco_s1==2)))
BeforeH<- c(X,sum(is.na(COURAGE_spain_w2$q3001_used_tobac_s1),na.omit(COURAGE_spain_w2$q3002_use_tobaco_s1==4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3001=2->0","q3001=1&q3002=3->1","q3002=1|q3002=2->1","NA->999") 
kable(C)
```





```{r final, echo = F}

l.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, spain_w1 = COURAGE_ds_spain_w1, spain_w2 = COURAGE_ds_spain_w2)
ln.hds <- names(l.hds)

for(name in names(l.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  assign(m_name, aux_object)
  rm(aux_object)
}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**


```{r summ}
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", 
             length(l.hds[[ln.hds[1]]][[2]]), length(l.hds[[ln.hds[2]]][[2]]) , length(l.hds[[ln.hds[3]]][[2]]), length(l.hds[[ln.hds[4]]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Spain_W1", "Spain_W2")
kable(t.hds)

```


# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  smoking <- l.hds[[index]]
  save(smoking, file = paste0(datafolder,names(l.hds)[index],"/smoking.RData"))
}

```
