---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```

# Data process

## Finland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a_cig_manuf`
* Label: `Manufact cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b_cig_hand`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_finland_w1_n_cigarettes','Courage.Courage_Finland_w1', variables=list('q3004a_cig_manuf','q3004b_cig_hand'), missings = TRUE)
```

```{r local finland w1, echo=F}
COURAGE_finland_w1_n_cigarettes <- opal.execute(o,'COURAGE_finland_w1_n_cigarettes')
Continuous_summary(COURAGE_finland_w1_n_cigarettes$q3004a_cig_manuf)
ggplot(COURAGE_finland_w1_n_cigarettes, aes(x=factor(q3004a_cig_manuf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
Continuous_summary(COURAGE_finland_w1_n_cigarettes$q3004b_cig_hand)
ggplot(COURAGE_finland_w1_n_cigarettes, aes(x=factor(q3004b_cig_hand))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a_cig_manuf+q3004b_cig_hand)*7` 
* `NA into 999`

```{r harmo finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_finland_w1_n_cigarettes$id)
COURAGE_ds_fin_w1$n_cigarettes <- Recode((COURAGE_finland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_finland_w1_n_cigarettes$q3004b_cig_hand)*7, "NA = '999' ")
COURAGE_ds_fin_w1$n_cigarettes <- labelled(COURAGE_ds_fin_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript finland w1, echo=F}
Continuous_summary(var = COURAGE_ds_fin_w1$n_cigarettes, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(n_cigarettes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$n_cigarettes)
X <- table((COURAGE_finland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_finland_w1_n_cigarettes$q3004b_cig_hand)*7)
BeforeH <- c(X,length(COURAGE_finland_w1_n_cigarettes$q3004a_cig_manuf)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(COURAGE_finland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_finland_w1_n_cigarettes$q3004b_cig_hand)))),"->",sort(unique(na.omit(COURAGE_ds_fin_w1$n_cigarettes)))[-29],sep=""),"NA->999")
kable(C)
```


## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a_cig_manuf`
* Label: `Manufact cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b_cig_hand`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_poland_w1_n_cigarettes','Courage.Courage_Poland_w1', variables=list('q3004a_cig_manuf','q3004b_cig_hand'), missings = TRUE)
```

```{r local poland w1, echo=F}
COURAGE_poland_w1_n_cigarettes <- opal.execute(o,'COURAGE_poland_w1_n_cigarettes')
Continuous_summary(COURAGE_poland_w1_n_cigarettes$q3004a_cig_manuf)
ggplot(COURAGE_poland_w1_n_cigarettes, aes(x=factor(q3004a_cig_manuf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
Continuous_summary(COURAGE_poland_w1_n_cigarettes$q3004b_cig_hand)
ggplot(COURAGE_poland_w1_n_cigarettes, aes(x=factor(q3004b_cig_hand))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a_cig_manuf+q3004b_cig_hand)*7` 
* `NA into 999`

```{r harmo poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_poland_w1_n_cigarettes$id)
COURAGE_ds_pol_w1$n_cigarettes <- Recode((COURAGE_poland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_poland_w1_n_cigarettes$q3004b_cig_hand)*7, "NA = '999' ")
COURAGE_ds_pol_w1$n_cigarettes <- labelled(COURAGE_ds_pol_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript poland w1, echo=F}
Continuous_summary(var = COURAGE_ds_pol_w1$n_cigarettes, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(n_cigarettes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$n_cigarettes)
X <- table((COURAGE_poland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_poland_w1_n_cigarettes$q3004b_cig_hand)*7)
BeforeH <- c(X,length(COURAGE_poland_w1_n_cigarettes$q3004a_cig_manuf)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(COURAGE_poland_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_poland_w1_n_cigarettes$q3004b_cig_hand)))),"->",sort(unique(na.omit(COURAGE_ds_pol_w1$n_cigarettes)))[-32],sep=""),"NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004_lpap`
* Label: `How many cigaretes od you smoke each day?`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign poland w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_poland_w2_n_cigarettes','Courage.Courage_Poland_w2', variables=list('q3004_lpap'), missings = TRUE)
```

```{r local poland w2, echo=F}
COURAGE_poland_w2_n_cigarettes <- opal.execute(o,'COURAGE_poland_w2_n_cigarettes')
Continuous_summary(COURAGE_poland_w2_n_cigarettes$q3004_lpap)
ggplot(COURAGE_poland_w2_n_cigarettes, aes(x=factor(q3004_lpap))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q3004_lpap*7` 
* `NA into 999`

```{r harmo poland w2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_poland_w2_n_cigarettes$id)
COURAGE_ds_pol_w2$n_cigarettes <- Recode(COURAGE_poland_w2_n_cigarettes$q3004_lpap*7, "NA = '999' ")
COURAGE_ds_pol_w2$n_cigarettes <- labelled(COURAGE_ds_pol_w2$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript poland w2, echo=F}
Continuous_summary(var = COURAGE_ds_pol_w2$n_cigarettes, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(n_cigarettes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w2, echo=F}
AfterH <- table(COURAGE_ds_pol_w2$n_cigarettes)
X <- table(COURAGE_poland_w2_n_cigarettes$q3004_lpap*7)
BeforeH <- c(X,length(COURAGE_poland_w2_n_cigarettes$q3004_lpap)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(unique(na.omit(COURAGE_poland_w2_n_cigarettes$q3004_lpap))),"->",sort(unique(na.omit(COURAGE_ds_pol_w2$n_cigarettes)))[-23],sep=""),"NA->999")
kable(C)
```

## Spain

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a_cig_manuf`
* Label: `Manufact cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b_cig_hand`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_n_cigarettes','Courage.Courage_Spain_w1', variables=list('q3004a_cig_manuf','q3004b_cig_hand'), missings = TRUE)
```

```{r local spain w1, echo=F}
COURAGE_spain_w1_n_cigarettes <- opal.execute(o,'COURAGE_spain_w1_n_cigarettes')
Continuous_summary(COURAGE_spain_w1_n_cigarettes$q3004a_cig_manuf)
ggplot(COURAGE_spain_w1_n_cigarettes, aes(x=factor(q3004a_cig_manuf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
Continuous_summary(COURAGE_spain_w1_n_cigarettes$q3004b_cig_hand)
ggplot(COURAGE_spain_w1_n_cigarettes, aes(x=factor(q3004b_cig_hand))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a_cig_manuf+q3004b_cig_hand)*7` 
* `NA into 999`

```{r harmo spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_n_cigarettes$id)
COURAGE_ds_spain_w1$n_cigarettes <- Recode((COURAGE_spain_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_spain_w1_n_cigarettes$q3004b_cig_hand)*7, "NA = '999' ")
COURAGE_ds_spain_w1$n_cigarettes <- labelled(COURAGE_ds_spain_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w1, echo=F}
Continuous_summary(var = COURAGE_ds_spain_w1$n_cigarettes, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(n_cigarettes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$n_cigarettes)
X <- table((COURAGE_spain_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_spain_w1_n_cigarettes$q3004b_cig_hand)*7)
BeforeH <- c(X,length(COURAGE_spain_w1_n_cigarettes$q3004a_cig_manuf)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(COURAGE_spain_w1_n_cigarettes$q3004a_cig_manuf+COURAGE_spain_w1_n_cigarettes$q3004b_cig_hand)))),"->",sort(unique(na.omit(COURAGE_ds_spain_w1$n_cigarettes)))[-32],sep=""),"NA->999")
kable(C)
```




### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a_cig_manuf_s1`
* Label: `Manufact cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b_cig_hand_s1`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_n_cigarettes','Courage.Courage_Spain_w2_1', variables=list('q3004a_cig_manuf_s1','q3004b_cig_hand_s1'), missings = TRUE)
```

```{r local spain w2, echo=F}
COURAGE_spain_w2_n_cigarettes <- opal.execute(o,'COURAGE_spain_w2_n_cigarettes')
Continuous_summary(COURAGE_spain_w2_n_cigarettes$q3004a_cig_manuf_s1)
ggplot(COURAGE_spain_w2_n_cigarettes, aes(x=factor(q3004a_cig_manuf_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
Continuous_summary(COURAGE_spain_w2_n_cigarettes$q3004b_cig_hand_s1)
ggplot(COURAGE_spain_w2_n_cigarettes, aes(x=factor(q3004b_cig_hand_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a_cig_manuf_s1+q3004b_cig_hand_s1)*7` 
* `NA into 999`

```{r harmo spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_n_cigarettes$id)
COURAGE_ds_spain_w2$n_cigarettes <- Recode((COURAGE_spain_w2_n_cigarettes$q3004a_cig_manuf_s1+COURAGE_spain_w2_n_cigarettes$q3004b_cig_hand_s1)*7, "NA = '999' ")
COURAGE_ds_spain_w2$n_cigarettes <- labelled(COURAGE_ds_spain_w2$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w2, echo=F}
Continuous_summary(var = COURAGE_ds_spain_w2$n_cigarettes, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(n_cigarettes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$n_cigarettes)
X <- table((COURAGE_spain_w2_n_cigarettes$q3004a_cig_manuf_s1+COURAGE_spain_w2_n_cigarettes$q3004b_cig_hand_s1)*7)
BeforeH <- c(X,length(COURAGE_spain_w2_n_cigarettes$q3004a_cig_manuf_s1)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(COURAGE_spain_w2_n_cigarettes$q3004a_cig_manuf_s1+COURAGE_spain_w2_n_cigarettes$q3004b_cig_hand_s1)))),"->",sort(unique(na.omit(COURAGE_ds_spain_w2$n_cigarettes)))[-29],sep=""),"NA->999")
kable(C)
```





```{r final, echo=F}

l.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, pol_w2 = COURAGE_ds_pol_w2, spain_w1 = COURAGE_ds_spain_w1, spain_w2 = COURAGE_ds_spain_w2)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
