---
title: "Level of Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/level_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/level_paDS.R')
```




# Data process


## Finland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `physical`
* Label: `Physical activity`
* Categories:
   + `0 = high`
   + `1 = moderate`
   + `2 = low`
* Missings
   + `NA`


```{r assign finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_finland_w1_level_pa','Courage.Courage_Finland_w1', variables=list('physical'), missings = TRUE)
```

```{r local finland w1, echo=F}
COURAGE_finland_w1_level_pa <- opal.execute(o,'COURAGE_finland_w1_level_pa')
Categorical_summary(COURAGE_finland_w1_level_pa$physical)
ggplot(COURAGE_finland_w1_level_pa, aes(x=factor(physical))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 2`
* `2 into 3`
* `NA into 999`

```{r harmo finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_finland_w1_level_pa$id)
COURAGE_ds_fin_w1$level_pa <- Recode(COURAGE_finland_w1_level_pa$physical, "0 = '1';1 = '2';2 = '3';NA = '999' ")
COURAGE_ds_fin_w1$level_pa <- labelled(COURAGE_ds_fin_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript finland w1, echo=F}
Categorical_summary(var = COURAGE_ds_fin_w1$level_pa, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$level_pa)
X<-table(COURAGE_finland_w1_level_pa$physical)
BeforeH <- c(X[1:3],sum(is.na(COURAGE_finland_w1_level_pa$physical)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1->2","2->3","NA->999") 
kable(C)
```


## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `physical`
* Label: `Physical activity`
* Categories:
   + `0 = high`
   + `1 = moderate`
   + `2 = low`
* Missings
   + `NA`


```{r assign poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_poland_w1_level_pa','Courage.Courage_Poland_w1', variables=list('physical'), missings = TRUE)
```

```{r local poland w1, echo=F}
COURAGE_poland_w1_level_pa <- opal.execute(o,'COURAGE_poland_w1_level_pa')
Categorical_summary(COURAGE_poland_w1_level_pa$physical)
ggplot(COURAGE_poland_w1_level_pa, aes(x=factor(physical))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 2`
* `2 into 3`
* `NA into 999`

```{r harmo poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_poland_w1_level_pa$id)
COURAGE_ds_pol_w1$level_pa <- Recode(COURAGE_poland_w1_level_pa$physical, "0 = '1';1 = '2';2 = '3';NA = '999' ")
COURAGE_ds_pol_w1$level_pa <- labelled(COURAGE_ds_pol_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript poland w1, echo=F}
Categorical_summary(var = COURAGE_ds_pol_w1$level_pa, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$level_pa)
X<-table(COURAGE_poland_w1_level_pa$physical)
BeforeH <- c(X[1:3],sum(is.na(COURAGE_poland_w1_level_pa$physical)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1->2","2->3","NA->999") 
kable(C)
```



### Wave 2

Not found



## Spain


### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `physical`
* Label: `Physical activity`
* Categories:
   + `0 = high`
   + `1 = moderate`
   + `2 = low`
* Missings
   + `NA`


```{r assign spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_level_pa','Courage.Courage_Spain_w1', variables=list('physical'), missings = TRUE)
```

```{r local spain w1, echo=F}
COURAGE_spain_w1_level_pa <- opal.execute(o,'COURAGE_spain_w1_level_pa')
Categorical_summary(COURAGE_spain_w1_level_pa$physical)
ggplot(COURAGE_spain_w1_level_pa, aes(x=factor(physical))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 2`
* `2 into 3`
* `NA into 999`

```{r harmo spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_level_pa$id)
COURAGE_ds_spain_w1$level_pa <- Recode(COURAGE_spain_w1_level_pa$physical, "0 = '1';1 = '2';2 = '3';NA = '999' ")
COURAGE_ds_spain_w1$level_pa <- labelled(COURAGE_ds_spain_w1$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w1, echo=F}
Categorical_summary(var = COURAGE_ds_spain_w1$level_pa, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$level_pa)
X<-table(COURAGE_spain_w1_level_pa$physical)
BeforeH <- c(X[1:3],sum(is.na(COURAGE_spain_w1_level_pa$physical)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1->2","2->3","NA->999") 
kable(C)
```







### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `physical`
* Label: `Physical activity`
* Categories:
   + `0 = high`
   + `1 = moderate`
   + `2 = low`
* Missings
   + `NA`


```{r assign spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_level_pa','Courage.Courage_Spain_w2_1', variables=list('physical'), missings = TRUE)
```

```{r local spain w2, echo=F}
COURAGE_spain_w2_level_pa <- opal.execute(o,'COURAGE_spain_w2_level_pa')
Categorical_summary(COURAGE_spain_w2_level_pa$physical)
ggplot(COURAGE_spain_w2_level_pa, aes(x=factor(physical))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 2`
* `2 into 3`
* `NA into 999`

```{r harmo spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_level_pa$id)
COURAGE_ds_spain_w2$level_pa <- Recode(COURAGE_spain_w2_level_pa$physical, "0 = '1';1 = '2';2 = '3';NA = '999' ")
COURAGE_ds_spain_w2$level_pa <- labelled(COURAGE_ds_spain_w2$level_pa, labels = c(High=1, Moderate=2, Low=3, Inactive=4, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript spain w2, echo=F}
Categorical_summary(var = COURAGE_ds_spain_w2$level_pa, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Physical activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$level_pa)
X<-table(COURAGE_spain_w2_level_pa$physical)
BeforeH <- c(X[1:3],sum(is.na(COURAGE_spain_w2_level_pa$physical)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->1","1->2","2->3","NA->999") 
kable(C)
```





```{r final, echo = F}

l.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, spain_w1 = COURAGE_ds_spain_w1, spain_w2 = COURAGE_ds_spain_w2)
ln.hds <- names(l.hds)

for(name in names(l.hds)) {
  m_name <- paste0("COURAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  assign(m_name, aux_object)
  rm(aux_object)
}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**


```{r summ}
t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[15,] <- c("n", "sample size", 
             length(l.hds[[ln.hds[1]]][[2]]), length(l.hds[[ln.hds[2]]][[2]]) , length(l.hds[[ln.hds[3]]][[2]]), length(l.hds[[ln.hds[4]]][[2]]))
names(t.hds)<-c("val", "label", "Finland_w1", "Poland_W1", "Spain_W1", "Spain_W2")
kable(t.hds)

```


# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  level_pa <- l.hds[[index]]
  save(level_pa, file = paste0(datafolder,names(l.hds)[index],"/level_pa.RData"))
}

```
