---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```

<!-- ########################################################## --> 

# Data process



## SHARE 

### Wave 1 

#### Study-specific variable description

| **Name** | `eurodcat`|
|-|-|
| **Label** | `EURO-D caseness`|
| **Table name** | `sharew1_rel2-6-0_gv_health` |
| **Categories** |`0 = no`|
| | `1=yes` |
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dep','SHARE.sharew1_rel2-6-0_gv_health',
                         variables=list('eurodcat'), missings = TRUE)
SHARE_dep <- opal.execute(o,'SHARE_dep')
```

```{r local1, echo=FALSE}
vari <- SHARE_dep$eurodcat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**


```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_dep$id)
SHARE_ds_w1$depression <- car::recode(SHARE_dep[[2]], "NA=999")
SHARE_ds_w1$depression <- labelled(SHARE_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- SHARE_ds_w1[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(SHARE_dep[[2]], useNA = 'ifany')
AfterH <- table(SHARE_ds_w1$depression, useNA = 'ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL1, echo=FALSE}
label(SHARE_ds_w1$depression) <- ds_label_all
depression <- SHARE_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(SHARE_dep, depression)
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$depression <- car::recode(SHARE_m_ds_w1$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description


| **Name** | `eurodcat`|
|-|-|
| **Label** | `EURO-D caseness`|
| **Table name** | `sharew2_rel2-6-0_gv_health` |
| **Categories** |`0 = no`|
| | `1=yes` |
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dep','SHARE.sharew2_rel2-6-0_gv_health',
                         variables=list('eurodcat'), missings = TRUE)
SHARE_dep <- opal.execute(o,'SHARE_dep')
```

```{r local2, echo=FALSE}
vari <- SHARE_dep$eurodcat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_dep$id)
SHARE_ds_w2$depression <- car::recode(SHARE_dep[[2]], "NA=999")
SHARE_ds_w2$depression <- labelled(SHARE_ds_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- SHARE_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(SHARE_dep[[2]], useNA = 'ifany')
AfterH <- table(SHARE_ds_w2$depression, useNA = 'ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL2, echo=FALSE}
label(SHARE_ds_w2$depression) <- ds_label_all
depression <- SHARE_ds_w2
save(depression, file = "../RData/w2/depression.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')
rm(SHARE_dep, depression)

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$depression <- car::recode(SHARE_m_ds_w2$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

There is no variable.





### Wave 4 

#### Study-specific variable description



| **Name** | `eurodcat`|
|-|-|
| **Label** | `EURO-D caseness`|
| **Table name** | `sharew4_rel1-1-1_gv_health` |
| **Categories** |`0 = no`|
| | `1=yes` |
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dep','SHARE.sharew4_rel1-1-1_gv_health',
                         variables=list('eurodcat'), missings = TRUE)
SHARE_dep <- opal.execute(o,'SHARE_dep')
```

```{r local4, echo=FALSE}
vari <- SHARE_dep$eurodcat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_dep$id)
SHARE_ds_w4$depression <- car::recode(SHARE_dep[[2]], "NA=999")
SHARE_ds_w4$depression <- labelled(SHARE_ds_w4[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- SHARE_ds_w4[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
BeforeH <- table(SHARE_dep[[2]], useNA = 'ifany')
AfterH <- table(SHARE_ds_w4$depression, useNA = 'ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL4, echo=FALSE}
label(SHARE_ds_w4$depression) <- ds_label_all
depression <- SHARE_ds_w4
save(depression, file = "../RData/w4/depression.RData")
rm(SHARE_dep, depression)
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$depression <- car::recode(SHARE_m_ds_w4$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```





### Wave 5 

#### Study-specific variable description

| **Name** | `eurodcat`|
|-|-|
| **Label** | `EURO-D caseness`|
| **Table name** | `sharew5_rel1-0-0_gv_health` |
| **Categories** |`0 = no`|
| | `1=yes` |
| **Missings** |`-2 = Refusal`|
| | `-1 = Don't know` |
| **Description** |  |

```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dep','SHARE.sharew5_rel1-0-0_gv_health',
                         variables=list('eurodcat'), missings = TRUE)
SHARE_dep <- opal.execute(o,'SHARE_dep')
```

```{r local5, echo=FALSE}
vari <- SHARE_dep$eurodcat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_dep$id)
SHARE_ds_w5$depression <- car::recode(SHARE_dep[[2]], "NA=999")
SHARE_ds_w5$depression <- labelled(SHARE_ds_w5[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- SHARE_ds_w5[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(depression))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
BeforeH <- table(SHARE_dep[[2]], useNA = 'ifany')
AfterH <- table(SHARE_ds_w5$depression, useNA = 'ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL5, echo=FALSE}
label(SHARE_ds_w5$depression) <- ds_label_all
depression <- SHARE_ds_w5
save(depression, file = "../RData/w5/depression.RData")
rm(SHARE_dep, depression)
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$depression <- car::recode(SHARE_m_ds_w5$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```




# Quality estimation

They used the EURO-D scale. We used the final score variable in binary format. 


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
