---
title: "Dementia case"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/dementiaDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/dementiaDS.R')
```

<!-- ########################################################## --> 

# Data process

## SHARE 

### Wave 1 

#### Study-specific variable description

There is no variable.



### Wave 2 

#### Study-specific variable description


| **Name** | `ph006d16`|
|-|-|
| **Label** | `doctor told you had: alzheimer's disease, dementia, senility`|
| **Table name** | `sharew2_rel2-6-0_ph` |
| **Categories** |`0 = not selected` <br/> `1 = selected`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dem','SHARE.sharew2_rel2-6-0_ph',
                         variables=list('ph006d16'), missings = TRUE)
SHARE_dem <- opal.execute(o,'SHARE_dem')
```

```{r local2, echo=FALSE}
vari <- SHARE_dem[[2]]
kable(Categorical_summary(vari, missing_values = c(-1:-2))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* keep `0 into 0`
* keep `1 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_dem$id)
SHARE_ds_w2$dementia <- car::recode(SHARE_dem[[2]], "-2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- SHARE_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(dementia))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL2, echo=FALSE}
dementia <- SHARE_ds_w2
save(dementia, file = "../RData/w2/dementia.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')
rm(SHARE_dep, dementia)
```




### Wave 3 

There is no variable.





### Wave 4 

#### Study-specific variable description



| **Name** | `ph006d16`|
|-|-|
| **Label** | `doctor told you had: alzheimer's disease, dementia, senility`|
| **Table name** | `sharew4_rel1-1-1_ph` |
| **Categories** |`0 = not selected` <br/> `1 = selected`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |



```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dem','SHARE.sharew4_rel1-1-1_ph',
                         variables=list('ph006d16'), missings = TRUE)
SHARE_dem <- opal.execute(o,'SHARE_dem')
```

```{r local4, echo=FALSE}
vari <- SHARE_dem[[2]]
kable(Categorical_summary(vari, missing_values = c(-1:-2))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* keep `0 into 0`
* keep `1 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_dem$id)
SHARE_ds_w4$dementia <- car::recode(SHARE_dem[[2]], "-2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- SHARE_ds_w4[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(dementia))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation


```{r importOPAL4, echo=FALSE}
dementia <- SHARE_ds_w4
save(dementia, file = "../RData/w4/dementia.RData")
rm(SHARE_dep, dementia)
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5 

#### Study-specific variable description

| **Name** | `ph006d16`|
|-|-|
| **Label** | `doctor told you had: alzheimer's disease, dementia, senility`|
| **Table name** | `sharew5_rel1-0-0_ph` |
| **Categories** |`0 = not selected` <br/> `1 = selected`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_dem','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('ph006d16'), missings = TRUE)
SHARE_dem <- opal.execute(o,'SHARE_dem')
```

```{r local5, echo=FALSE}
vari <- SHARE_dem[[2]]
kable(Categorical_summary(vari, missing_values = c(-1:-2))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_dem, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* keep `0 into 0`
* keep `1 into 1`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`


**R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_dem$id)
SHARE_ds_w5$dementia <- car::recode(SHARE_dem[[2]], "-2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- SHARE_ds_w5[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(dementia))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL5, echo=FALSE}
dementia <- SHARE_ds_w5
save(dementia, file = "../RData/w5/dementia.RData")
rm(SHARE_dep, dementia)
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')
```


# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
