---
title: "Current smoker"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/current_smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/current_smokingDS.R')
```




# Data process


## Cuba

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign cuba w1, echo=F}
opal.assign.table.tibble(o, 's1066_cuba_w1_current_smoking','10-66.1066-Cuba-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local cuba w1, echo=F}
s1066_cuba_w1_current_smoking <- opal.execute(o,'s1066_cuba_w1_current_smoking')
Categorical_summary(s1066_cuba_w1_current_smoking$PSMKNOW)
ggplot(s1066_cuba_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_cuba_w1_current_smoking$id)
t1066_ds_cuba_w1$current_smoking<-Recode(s1066_cuba_w1_current_smoking$PSMKNOW, "1 = '1';0='0'; NA='999'")
t1066_ds_cuba_w1$current_smoking <- labelled(t1066_ds_cuba_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cuba w1, echo=F}
Categorical_summary(var = t1066_ds_cuba_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$current_smoking)
X<-table(s1066_cuba_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_cuba_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign cuba w2, echo=F}
opal.assign.table.tibble(o, 's1066_cuba_w2_current_smoking','10-66.1066-Cuba-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local cuba w2, echo=F}
s1066_cuba_w2_current_smoking <- opal.execute(o,'s1066_cuba_w2_current_smoking')
Categorical_summary(s1066_cuba_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_cuba_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo cuba w2}
t1066_ds_cuba_w2 <- tibble(id=s1066_cuba_w2_current_smoking$id)
t1066_ds_cuba_w2$current_smoking <-  Recode(s1066_cuba_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'; NA='999'")
t1066_ds_cuba_w2$current_smoking <- labelled(t1066_ds_cuba_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cuba w2, echo=F}
Categorical_summary(var = t1066_ds_cuba_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation cuba w2, echo=F}
AfterH <- table(t1066_ds_cuba_w2$current_smoking)
X<-table(s1066_cuba_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_cuba_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_cuba_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1", "NA->999") 
kable(C)
```

## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 's1066_India_w1_current_smoking','10-66.1066-India-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local India w1, echo=F}
s1066_India_w1_current_smoking <- opal.execute(o,'s1066_India_w1_current_smoking')
Categorical_summary(s1066_India_w1_current_smoking$PSMKNOW)
ggplot(s1066_India_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_current_smoking$id)
t1066_ds_india_w1$current_smoking <- Recode(s1066_India_w1_current_smoking$PSMKNOW, "1 = '1';0='0';NA=999")
t1066_ds_india_w1$current_smoking <- labelled(t1066_ds_india_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
Categorical_summary(var = t1066_ds_india_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$current_smoking)
X<-table(s1066_India_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_India_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



## UrbanChina

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_current_smoking','10-66.1066-UrbanChina-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local UrbanChina w1, echo=F}
s1066_UrbanChina_w1_current_smoking <- opal.execute(o,'s1066_UrbanChina_w1_current_smoking')
Categorical_summary(s1066_UrbanChina_w1_current_smoking$PSMKNOW)
ggplot(s1066_UrbanChina_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_current_smoking$id)
t1066_ds_UCh_w1$current_smoking <- Recode(s1066_UrbanChina_w1_current_smoking$PSMKNOW, "0 = '0';1 ='1';NA = '999'")
t1066_ds_UCh_w1$current_smoking <- labelled(t1066_ds_UCh_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
Categorical_summary(var = t1066_ds_UCh_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$current_smoking)
X<-table(s1066_UrbanChina_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_UrbanChina_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign UrbanChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w2_current_smoking','10-66.1066-UrbanChina-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local UrbanChina w2, echo=F}
s1066_UrbanChina_w2_current_smoking <- opal.execute(o,'s1066_UrbanChina_w2_current_smoking')
Categorical_summary(s1066_UrbanChina_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_UrbanChina_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`

```{r harmo UrbanChina w2}
t1066_ds_UCh_w2 <- tibble(id=s1066_UrbanChina_w2_current_smoking$id)
t1066_ds_UCh_w2$current_smoking <-  Recode(s1066_UrbanChina_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'")
t1066_ds_UCh_w2$current_smoking <- labelled(t1066_ds_UCh_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w2, echo=F}
Categorical_summary(var = t1066_ds_UCh_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w2, echo=F}
AfterH <- table(t1066_ds_UCh_w2$current_smoking)
X<-table(s1066_UrbanChina_w2_current_smoking$f_PSMOKE1)
#nas<-length(s1066_UrbanChina_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_UrbanChina_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```


## RuralChina

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_current_smoking','10-66.1066-RuralChina-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local RuralChina w1, echo=F}
s1066_RuralChina_w1_current_smoking <- opal.execute(o,'s1066_RuralChina_w1_current_smoking')
Categorical_summary(s1066_RuralChina_w1_current_smoking$PSMKNOW)
ggplot(s1066_RuralChina_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_current_smoking$id)
t1066_ds_RCh_w1$current_smoking <- Recode(s1066_RuralChina_w1_current_smoking$PSMKNOW, "0 = '0';1='1';NA='999'")
t1066_ds_RCh_w1$current_smoking <- labelled(t1066_ds_RCh_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
Categorical_summary(var = t1066_ds_RCh_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$current_smoking)
X<-table(s1066_RuralChina_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_RuralChina_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign RuralChina w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w2_current_smoking','10-66.1066-RuralChina-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local RuralChina w2, echo=F}
s1066_RuralChina_w2_current_smoking <- opal.execute(o,'s1066_RuralChina_w2_current_smoking')
Categorical_summary(s1066_RuralChina_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_RuralChina_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo RuralChina w2}
t1066_ds_RCh_w2 <- tibble(id=s1066_RuralChina_w2_current_smoking$id)
t1066_ds_RCh_w2$current_smoking <-  Recode(s1066_RuralChina_w2_current_smoking$f_PSMOKE1, "0 = '0';1='1'; NA='999'")
t1066_ds_RCh_w2$current_smoking <- labelled(t1066_ds_RCh_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w2, echo=F}
Categorical_summary(var = t1066_ds_RCh_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w2, echo=F}
AfterH <- table(t1066_ds_RCh_w2$current_smoking)
X<-table(s1066_RuralChina_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_RuralChina_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_RuralChina_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```




## DominicanRepublic

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_current_smoking','10-66.1066-DominicanRepublic-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local DominicanRepublic w1, echo=F}
s1066_DominicanRepublic_w1_current_smoking <- opal.execute(o,'s1066_DominicanRepublic_w1_current_smoking')
Categorical_summary(s1066_DominicanRepublic_w1_current_smoking$PSMKNOW)
ggplot(s1066_DominicanRepublic_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_current_smoking$id)
t1066_ds_DR_w1$current_smoking <- Recode(s1066_DominicanRepublic_w1_current_smoking$PSMKNOW, "0 = '0';1 ='1';NA='999'")
t1066_ds_DR_w1$current_smoking <- labelled(t1066_ds_DR_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
Categorical_summary(var = t1066_ds_DR_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$current_smoking)
X<-table(s1066_DominicanRepublic_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_DominicanRepublic_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign DominicanRepublic w2, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w2_current_smoking','10-66.1066-DominicanRepublic-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local DominicanRepublic w2, echo=F}
s1066_DominicanRepublic_w2_current_smoking <- opal.execute(o,'s1066_DominicanRepublic_w2_current_smoking')
Categorical_summary(s1066_DominicanRepublic_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_DominicanRepublic_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo DominicanRepublic w2}
t1066_ds_DR_w2 <- tibble(id=s1066_DominicanRepublic_w2_current_smoking$id)
t1066_ds_DR_w2$current_smoking <-  Recode(s1066_DominicanRepublic_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'; NA='999'")
t1066_ds_DR_w2$current_smoking <- labelled(t1066_ds_DR_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w2, echo=F}
Categorical_summary(var = t1066_ds_DR_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w2, echo=F}
AfterH <- table(t1066_ds_DR_w2$current_smoking)
X<-table(s1066_DominicanRepublic_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_DominicanRepublic_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_DominicanRepublic_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_current_smoking','10-66.1066-Venezuela-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local Venezuela w1, echo=F}
s1066_Venezuela_w1_current_smoking <- opal.execute(o,'s1066_Venezuela_w1_current_smoking')
Categorical_summary(s1066_Venezuela_w1_current_smoking$PSMKNOW)
ggplot(s1066_Venezuela_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_current_smoking$id)
t1066_ds_Ven_w1$current_smoking <- Recode(s1066_Venezuela_w1_current_smoking$PSMKNOW, "0 = '0';1='1';NA='999'")
t1066_ds_Ven_w1$current_smoking <- labelled(t1066_ds_Ven_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
Categorical_summary(var = t1066_ds_Ven_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$current_smoking)
X<-table(s1066_Venezuela_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_Venezuela_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign Venezuela w2, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w2_current_smoking','10-66.1066-Venezuela-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local Venezuela w2, echo=F}
s1066_Venezuela_w2_current_smoking <- opal.execute(o,'s1066_Venezuela_w2_current_smoking')
Categorical_summary(s1066_Venezuela_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_Venezuela_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo Venezuela w2}
t1066_ds_Ven_w2 <- tibble(id=s1066_Venezuela_w2_current_smoking$id)
t1066_ds_Ven_w2$current_smoking <-  Recode(s1066_Venezuela_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'; NA='999'")
t1066_ds_Ven_w2$current_smoking <- labelled(t1066_ds_Ven_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w2, echo=F}
Categorical_summary(var = t1066_ds_Ven_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w2, echo=F}
AfterH <- table(t1066_ds_Ven_w2$current_smoking)
X<-table(s1066_Venezuela_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_Venezuela_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_Venezuela_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



## Urban Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_current_smoking','10-66.1066-UrbanPeru-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local UrbanPeru w1, echo=F}
s1066_UrbanPeru_w1_current_smoking <- opal.execute(o,'s1066_UrbanPeru_w1_current_smoking')
Categorical_summary(s1066_UrbanPeru_w1_current_smoking$PSMKNOW)
ggplot(s1066_UrbanPeru_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_current_smoking$id)
t1066_ds_UP_w1$current_smoking <- Recode(s1066_UrbanPeru_w1_current_smoking$PSMKNOW, "0 = '0';1='1';NA='999'")
t1066_ds_UP_w1$current_smoking <- labelled(t1066_ds_UP_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
Categorical_summary(var = t1066_ds_UP_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$current_smoking)
X<-table(s1066_UrbanPeru_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_UrbanPeru_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign UrbanPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w2_current_smoking','10-66.1066-UrbanPeru-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local UrbanPeru w2, echo=F}
s1066_UrbanPeru_w2_current_smoking <- opal.execute(o,'s1066_UrbanPeru_w2_current_smoking')
Categorical_summary(s1066_UrbanPeru_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_UrbanPeru_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo UrbanPeru w2}
t1066_ds_UP_w2 <- tibble(id=s1066_UrbanPeru_w2_current_smoking$id)
t1066_ds_UP_w2$current_smoking <-  Recode(s1066_UrbanPeru_w2_current_smoking$f_PSMOKE1, "0 = '0';1='1'; NA='999'")
t1066_ds_UP_w2$current_smoking <- labelled(t1066_ds_UP_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w2, echo=F}
Categorical_summary(var = t1066_ds_UP_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w2, echo=F}
AfterH <- table(t1066_ds_UP_w2$current_smoking)
X<-table(s1066_UrbanPeru_w2_current_smoking$f_PSMOKE1)
#nas<-length(s1066_UrbanPeru_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_UrbanPeru_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```


## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_current_smoking','10-66.1066-RuralPeru-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local RuralPeru w1, echo=F}
s1066_RuralPeru_w1_current_smoking <- opal.execute(o,'s1066_RuralPeru_w1_current_smoking')
Categorical_summary(s1066_RuralPeru_w1_current_smoking$PSMKNOW)
ggplot(s1066_RuralPeru_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_current_smoking$id)
t1066_ds_RP_w1$current_smoking <- Recode(s1066_RuralPeru_w1_current_smoking$PSMKNOW, "0 = '0';1 ='1'; NA = '999'")
t1066_ds_RP_w1$current_smoking <- labelled(t1066_ds_RP_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
Categorical_summary(var = t1066_ds_RP_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$current_smoking)
X<-table(s1066_RuralPeru_w1_current_smoking$PSMKNOW)
BeforeH <- c(X, sum(is.na(s1066_RuralPeru_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign RuralPeru w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w2_current_smoking','10-66.1066-RuralPeru-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local RuralPeru w2, echo=F}
s1066_RuralPeru_w2_current_smoking <- opal.execute(o,'s1066_RuralPeru_w2_current_smoking')
Categorical_summary(s1066_RuralPeru_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_RuralPeru_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`

```{r harmo RuralPeru w2}
t1066_ds_RP_w2 <- tibble(id=s1066_RuralPeru_w2_current_smoking$id)
t1066_ds_RP_w2$current_smoking <-  Recode(s1066_RuralPeru_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'")
t1066_ds_RP_w2$current_smoking <- labelled(t1066_ds_RP_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w2, echo=F}
Categorical_summary(var = t1066_ds_RP_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w2, echo=F}
AfterH <- table(t1066_ds_RP_w2$current_smoking)
X<-table(s1066_RuralPeru_w2_current_smoking$f_PSMOKE1)
#nas<-length(s1066_RuralPeru_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_RuralPeru_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1") 
kable(C)
```



## Urban Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_current_smoking','10-66.1066-UrbanMexico-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local UrbanMexico w1, echo=F}
s1066_UrbanMexico_w1_current_smoking <- opal.execute(o,'s1066_UrbanMexico_w1_current_smoking')
Categorical_summary(s1066_UrbanMexico_w1_current_smoking$PSMKNOW)
ggplot(s1066_UrbanMexico_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_current_smoking$id)
t1066_ds_UM_w1$current_smoking <- Recode(s1066_UrbanMexico_w1_current_smoking$PSMKNOW, "0 = '0';1='1';NA='999'")
t1066_ds_UM_w1$current_smoking <- labelled(t1066_ds_UM_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
Categorical_summary(var = t1066_ds_UM_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$current_smoking)
X<-table(s1066_UrbanMexico_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_UrbanMexico_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign UrbanMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w2_current_smoking','10-66.1066-UrbanMexico-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local UrbanMexico w2, echo=F}
s1066_UrbanMexico_w2_current_smoking <- opal.execute(o,'s1066_UrbanMexico_w2_current_smoking')
Categorical_summary(s1066_UrbanMexico_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_UrbanMexico_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo UrbanMexico w2}
t1066_ds_UM_w2 <- tibble(id=s1066_UrbanMexico_w2_current_smoking$id)
t1066_ds_UM_w2$current_smoking <-  Recode(s1066_UrbanMexico_w2_current_smoking$f_PSMOKE1, "0 = '0';1='1'; NA='999'")
t1066_ds_UM_w2$current_smoking <- labelled(t1066_ds_UM_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w2, echo=F}
Categorical_summary(var = t1066_ds_UM_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w2, echo=F}
AfterH <- table(t1066_ds_UM_w2$current_smoking)
X<-table(s1066_UrbanMexico_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_UrbanMexico_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_UrbanMexico_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



## Rural Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_current_smoking','10-66.1066-RuralMexico-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local RuralMexico w1, echo=F}
s1066_RuralMexico_w1_current_smoking <- opal.execute(o,'s1066_RuralMexico_w1_current_smoking')
Categorical_summary(s1066_RuralMexico_w1_current_smoking$PSMKNOW)
ggplot(s1066_RuralMexico_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_current_smoking$id)
t1066_ds_RM_w1$current_smoking <- Recode(s1066_RuralMexico_w1_current_smoking$PSMKNOW, "0 = '0';1 ='1';NA='999'")
t1066_ds_RM_w1$current_smoking <- labelled(t1066_ds_RM_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
Categorical_summary(var = t1066_ds_RM_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$current_smoking)
X<-table(s1066_RuralMexico_w1_current_smoking$PSMKNOW)
BeforeH <- c(X,sum(is.na(s1066_RuralMexico_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign RuralMexico w2, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w2_current_smoking','10-66.1066-RuralMexico-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local RuralMexico w2, echo=F}
s1066_RuralMexico_w2_current_smoking <- opal.execute(o,'s1066_RuralMexico_w2_current_smoking')
Categorical_summary(s1066_RuralMexico_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_RuralMexico_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo RuralMexico w2}
t1066_ds_RM_w2 <- tibble(id=s1066_RuralMexico_w2_current_smoking$id)
t1066_ds_RM_w2$current_smoking <-  Recode(s1066_RuralMexico_w2_current_smoking$f_PSMOKE1, "0 = '0';1='1'; NA='999'")
t1066_ds_RM_w2$current_smoking <- labelled(t1066_ds_RM_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w2, echo=F}
Categorical_summary(var = t1066_ds_RM_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w2, echo=F}
AfterH <- table(t1066_ds_RM_w2$current_smoking)
X<-table(s1066_RuralMexico_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_RuralMexico_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_RuralMexico_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



## PuertoRico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `PSMKNOW`
* Label: `still smoking regularly?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`


```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_current_smoking','10-66.1066-PuertoRico-Baseline', variables=list('PSMKNOW'), missings = TRUE)
```

```{r local PuertoRico w1, echo=F}
s1066_PuertoRico_w1_current_smoking <- opal.execute(o,'s1066_PuertoRico_w1_current_smoking')
Categorical_summary(s1066_PuertoRico_w1_current_smoking$PSMKNOW)
ggplot(s1066_PuertoRico_w1_current_smoking, aes(x=factor(PSMKNOW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_current_smoking$id)
t1066_ds_PR_w1$current_smoking <- Recode(s1066_PuertoRico_w1_current_smoking$PSMKNOW, "0 = '0';1 ='1';NA = '999'")
t1066_ds_PR_w1$current_smoking <- labelled(t1066_ds_PR_w1$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
Categorical_summary(var = t1066_ds_PR_w1$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$current_smoking)
X<-table(s1066_PuertoRico_w1_current_smoking$PSMKNOW)
BeforeH <- c(X, sum(is.na(s1066_PuertoRico_w1_current_smoking$PSMKNOW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `f_PSMOKE1`
* Label: `in the last week, did you smoke or use tobacco?`
* Categories:
   + `0 = No`
   + `1 = Yes`
* Missings
   + `NA`

```{r assign PuertoRico w2, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w2_current_smoking','10-66.1066-PuertoRico-Followup', variables=list('f_PSMOKE1'), missings = TRUE)
```

```{r local PuertoRico w2, echo=F}
s1066_PuertoRico_w2_current_smoking <- opal.execute(o,'s1066_PuertoRico_w2_current_smoking')
Categorical_summary(s1066_PuertoRico_w2_current_smoking$f_PSMOKE1)
ggplot(s1066_PuertoRico_w2_current_smoking, aes(x=factor(f_PSMOKE1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `NA into 999`

```{r harmo PuertoRico w2}
t1066_ds_PR_w2 <- tibble(id=s1066_PuertoRico_w2_current_smoking$id)
t1066_ds_PR_w2$current_smoking <-  Recode(s1066_PuertoRico_w2_current_smoking$f_PSMOKE1, "0 = '0';1 ='1'; NA='999'")
t1066_ds_PR_w2$current_smoking <- labelled(t1066_ds_PR_w2$current_smoking, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w2, echo=F}
Categorical_summary(var = t1066_ds_PR_w2$current_smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w2, echo=F}
AfterH <- table(t1066_ds_PR_w2$current_smoking)
X<-table(s1066_PuertoRico_w2_current_smoking$f_PSMOKE1)
nas<-length(s1066_PuertoRico_w2_current_smoking$f_PSMOKE1)-length(na.omit(s1066_PuertoRico_w2_current_smoking$f_PSMOKE1))
BeforeH <- c(X,nas)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999") 
kable(C)
```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[13,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[13,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  current_smoking <- lb.hds[[index]]
  save(current_smoking, file = paste0(datafolder,names(lb.hds)[index],"/current_smoking.RData"))
}

for(index in seq_along(lf.hds)){
  current_smoking <- lf.hds[[index]]
  save(current_smoking, file = paste0(datafolder,names(lf.hds)[index],"/current_smoking.RData"))
}


```
<!-- ########################################################## --> 







# Quality estimation

```{r closeRsession, echo=FALSE}
opal.logout(o)
```