---
title: "Smoking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/smokingDS.R')
```




# Data process


## Cuba

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign cuba w1, echo=F}
opal.assign.table.tibble(o, 's1066_cuba_w1_smoking','10-66.1066-Cuba-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local cuba w1, echo=F}
s1066_cuba_w1_smoking <- opal.execute(o,'s1066_cuba_w1_smoking')
Categorical_summary(s1066_cuba_w1_smoking$smokstat)
ggplot(s1066_cuba_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo cuba w1}
t1066_ds_cuba_w1 <- tibble(id=s1066_cuba_w1_smoking$id)
t1066_ds_cuba_w1$smoking<-Recode(s1066_cuba_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999'")
t1066_ds_cuba_w1$smoking <- labelled(t1066_ds_cuba_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript cuba w1, echo=F}
Categorical_summary(var = t1066_ds_cuba_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cuba w1, echo=F}
AfterH <- table(t1066_ds_cuba_w1$smoking)
X<-table(s1066_cuba_w1_smoking$smokstat)
BeforeH <- c(X,sum(is.na(s1066_cuba_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```




### Wave 2 

Not found.



## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 's1066_India_w1_smoking','10-66.1066-India-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local India w1, echo=F}
s1066_India_w1_smoking <- opal.execute(o,'s1066_India_w1_smoking')
Categorical_summary(s1066_India_w1_smoking$smokstat)
ggplot(s1066_India_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo India w1}
t1066_ds_india_w1 <- tibble(id=s1066_India_w1_smoking$id)
t1066_ds_india_w1$smoking <- Recode(s1066_India_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_india_w1$smoking <- labelled(t1066_ds_india_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
Categorical_summary(var = t1066_ds_india_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(t1066_ds_india_w1$smoking)
X<-table(s1066_India_w1_smoking$smokstat)
BeforeH <- c(X,sum(is.na(s1066_India_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```




## Urban China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings


```{r assign UrbanChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanChina_w1_smoking','10-66.1066-UrbanChina-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local UrbanChina w1, echo=F}
s1066_UrbanChina_w1_smoking <- opal.execute(o,'s1066_UrbanChina_w1_smoking')
Categorical_summary(s1066_UrbanChina_w1_smoking$smokstat)
ggplot(s1066_UrbanChina_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`

```{r harmo UrbanChina w1}
t1066_ds_UCh_w1 <- tibble(id=s1066_UrbanChina_w1_smoking$id)
t1066_ds_UCh_w1$smoking <- Recode(s1066_UrbanChina_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2' ")
t1066_ds_UCh_w1$smoking <- labelled(t1066_ds_UCh_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript UrbanChina w1, echo=F}
Categorical_summary(var = t1066_ds_UCh_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanChina w1, echo=F}
AfterH <- table(t1066_ds_UCh_w1$smoking)
X<-table(s1066_UrbanChina_w1_smoking$smokstat)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2") 
kable(C)
```



### Wave 2 

Not found.



## Rural China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings


```{r assign RuralChina w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralChina_w1_smoking','10-66.1066-RuralChina-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local RuralChina w1, echo=F}
s1066_RuralChina_w1_smoking <- opal.execute(o,'s1066_RuralChina_w1_smoking')
Categorical_summary(s1066_RuralChina_w1_smoking$smokstat)
ggplot(s1066_RuralChina_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`

```{r harmo RuralChina w1}
t1066_ds_RCh_w1 <- tibble(id=s1066_RuralChina_w1_smoking$id)
t1066_ds_RCh_w1$smoking <- Recode(s1066_RuralChina_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2' ")
t1066_ds_RCh_w1$smoking <- labelled(t1066_ds_RCh_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript RuralChina w1, echo=F}
Categorical_summary(var = t1066_ds_RCh_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralChina w1, echo=F}
AfterH <- table(t1066_ds_RCh_w1$smoking)
X<-table(s1066_RuralChina_w1_smoking$smokstat)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2") 
kable(C)
```



### Wave 2 

Not found.



## Dominican Republic

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign DominicanRepublic w1, echo=F}
opal.assign.table.tibble(o, 's1066_DominicanRepublic_w1_smoking','10-66.1066-DominicanRepublic-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local DominicanRepublic w1, echo=F}
s1066_DominicanRepublic_w1_smoking <- opal.execute(o,'s1066_DominicanRepublic_w1_smoking')
Categorical_summary(s1066_DominicanRepublic_w1_smoking$smokstat)
ggplot(s1066_DominicanRepublic_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo DominicanRepublic w1}
t1066_ds_DR_w1 <- tibble(id=s1066_DominicanRepublic_w1_smoking$id)
t1066_ds_DR_w1$smoking <- Recode(s1066_DominicanRepublic_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_DR_w1$smoking <- labelled(t1066_ds_DR_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript DominicanRepublic w1, echo=F}
Categorical_summary(var = t1066_ds_DR_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation DominicanRepublic w1, echo=F}
AfterH <- table(t1066_ds_DR_w1$smoking)
X<-table(s1066_DominicanRepublic_w1_smoking$smokstat)
BeforeH <- c(X,sum(is.na(s1066_DominicanRepublic_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```


### Wave 2 

Not found.



## Venezuela

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign Venezuela w1, echo=F}
opal.assign.table.tibble(o, 's1066_Venezuela_w1_smoking','10-66.1066-Venezuela-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local Venezuela w1, echo=F}
s1066_Venezuela_w1_smoking <- opal.execute(o,'s1066_Venezuela_w1_smoking')
Categorical_summary(s1066_Venezuela_w1_smoking$smokstat)
ggplot(s1066_Venezuela_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo Venezuela w1}
t1066_ds_Ven_w1 <- tibble(id=s1066_Venezuela_w1_smoking$id)
t1066_ds_Ven_w1$smoking <- Recode(s1066_Venezuela_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_Ven_w1$smoking <- labelled(t1066_ds_Ven_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript Venezuela w1, echo=F}
Categorical_summary(var = t1066_ds_Ven_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Venezuela w1, echo=F}
AfterH <- table(t1066_ds_Ven_w1$smoking)
X<-table(s1066_Venezuela_w1_smoking$smokstat)
BeforeH <- c(X,sum(is.na(s1066_Venezuela_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```



### Wave 2 

Not found.



## Urban Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign UrbanPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanPeru_w1_smoking','10-66.1066-UrbanPeru-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local UrbanPeru w1, echo=F}
s1066_UrbanPeru_w1_smoking <- opal.execute(o,'s1066_UrbanPeru_w1_smoking')
Categorical_summary(s1066_UrbanPeru_w1_smoking$smokstat)
ggplot(s1066_UrbanPeru_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo UrbanPeru w1}
t1066_ds_UP_w1 <- tibble(id=s1066_UrbanPeru_w1_smoking$id)
t1066_ds_UP_w1$smoking <- Recode(s1066_UrbanPeru_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_UP_w1$smoking <- labelled(t1066_ds_UP_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript UrbanPeru w1, echo=F}
Categorical_summary(var = t1066_ds_UP_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanPeru w1, echo=F}
AfterH <- table(t1066_ds_UP_w1$smoking)
X<-table(s1066_UrbanPeru_w1_smoking$smokstat)
BeforeH <- c(X,sum(is.na(s1066_UrbanPeru_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```



### Wave 2 

Not found.



## Rural Peru

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign RuralPeru w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralPeru_w1_smoking','10-66.1066-RuralPeru-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local RuralPeru w1, echo=F}
s1066_RuralPeru_w1_smoking <- opal.execute(o,'s1066_RuralPeru_w1_smoking')
Categorical_summary(s1066_RuralPeru_w1_smoking$smokstat)
ggplot(s1066_RuralPeru_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo RuralPeru w1}
t1066_ds_RP_w1 <- tibble(id=s1066_RuralPeru_w1_smoking$id)
t1066_ds_RP_w1$smoking <- Recode(s1066_RuralPeru_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_RP_w1$smoking <- labelled(t1066_ds_RP_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript RuralPeru w1, echo=F}
Categorical_summary(var = t1066_ds_RP_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralPeru w1, echo=F}
AfterH <- table(t1066_ds_RP_w1$smoking)
X<-table(s1066_RuralPeru_w1_smoking$smokstat)
BeforeH <- c(X, sum(is.na(s1066_RuralPeru_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```


### Wave 2 

Not found.



## Urban Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings

```{r assign UrbanMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_UrbanMexico_w1_smoking','10-66.1066-UrbanMexico-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local UrbanMexico w1, echo=F}
s1066_UrbanMexico_w1_smoking <- opal.execute(o,'s1066_UrbanMexico_w1_smoking')
Categorical_summary(s1066_UrbanMexico_w1_smoking$smokstat)
ggplot(s1066_UrbanMexico_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`

```{r harmo UrbanMexico w1}
t1066_ds_UM_w1 <- tibble(id=s1066_UrbanMexico_w1_smoking$id)
t1066_ds_UM_w1$smoking <- Recode(s1066_UrbanMexico_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2' ")
t1066_ds_UM_w1$smoking <- labelled(t1066_ds_UM_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript UrbanMexico w1, echo=F}
Categorical_summary(var = t1066_ds_UM_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation UrbanMexico w1, echo=F}
AfterH <- table(t1066_ds_UM_w1$smoking)
X<-table(s1066_UrbanMexico_w1_smoking$smokstat)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2") 
kable(C)
```


### Wave 2 

Not found.



## Rural Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings


```{r assign RuralMexico w1, echo=F}
opal.assign.table.tibble(o, 's1066_RuralMexico_w1_smoking','10-66.1066-RuralMexico-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local RuralMexico w1, echo=F}
s1066_RuralMexico_w1_smoking <- opal.execute(o,'s1066_RuralMexico_w1_smoking')
Categorical_summary(s1066_RuralMexico_w1_smoking$smokstat)
ggplot(s1066_RuralMexico_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`

```{r harmo RuralMexico w1}
t1066_ds_RM_w1 <- tibble(id=s1066_RuralMexico_w1_smoking$id)
t1066_ds_RM_w1$smoking <- Recode(s1066_RuralMexico_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2' ")
t1066_ds_RM_w1$smoking <- labelled(t1066_ds_RM_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript RuralMexico w1, echo=F}
Categorical_summary(var = t1066_ds_RM_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation RuralMexico w1, echo=F}
AfterH <- table(t1066_ds_RM_w1$smoking)
X<-table(s1066_RuralMexico_w1_smoking$smokstat)
BeforeH <- c(X)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2") 
kable(C)
```



### Wave 2 

Not found.



## Puerto Rico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `smokstat`
* Label: `current smoking status (never/ ex/ current smoker)`
* Categories:
   + `0 = never smoked`
   + `1 = ex-smoker`
   + `2 = current smoker`
* Missings
   + `NA`


```{r assign PuertoRico w1, echo=F}
opal.assign.table.tibble(o, 's1066_PuertoRico_w1_smoking','10-66.1066-PuertoRico-Baseline', variables=list('smokstat'), missings = TRUE)
```

```{r local PuertoRico w1, echo=F}
s1066_PuertoRico_w1_smoking <- opal.execute(o,'s1066_PuertoRico_w1_smoking')
Categorical_summary(s1066_PuertoRico_w1_smoking$smokstat)
ggplot(s1066_PuertoRico_w1_smoking, aes(x=factor(smokstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `1 into 1`
* `2 into 2`
* `NA into 999`

```{r harmo PuertoRico w1}
t1066_ds_PR_w1 <- tibble(id=s1066_PuertoRico_w1_smoking$id)
t1066_ds_PR_w1$smoking <- Recode(s1066_PuertoRico_w1_smoking$smokstat, "0 = '0';1 = '1';2 = '2'; NA = '999' ")
t1066_ds_PR_w1$smoking <- labelled(t1066_ds_PR_w1$smoking, labels = cat_label)
```

#### Statistical description of the new harmonised variable
```{r descript PuertoRico w1, echo=F}
Categorical_summary(var = t1066_ds_PR_w1$smoking,missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Smoking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation PuertoRico w1, echo=F}
AfterH <- table(t1066_ds_PR_w1$smoking)
X<-table(s1066_PuertoRico_w1_smoking$smokstat)
BeforeH <- c(X, sum(is.na(s1066_PuertoRico_w1_smoking$smokstat)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2->2","NA->999") 
kable(C)
```



### Wave 2 

Not found.


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

#lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}
# 
# for(name in names(lf.hds)) {
#   aux_object <- lf.hds[[name]]
#   label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
#   lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
#   aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
#   aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
#   m_name <- paste0("t1066_m_ds_",name)
#   assign(m_name, aux_object)
#   rm(aux_object)
# }

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[14,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)
# 
# tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
# for (i in seq_along(lf.hds)){
#   tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
# }
# tf.hds[13,] <- c("n", "sample size", 
#              length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
#              )
# names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
# kable(tf.hds)
# 


```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  smoking <- lb.hds[[index]]
  save(smoking, file = paste0(datafolder,names(lb.hds)[index],"/smoking.RData"))
}
# 
# for(index in seq_along(lf.hds)){
#   smoking <- lf.hds[[index]]
#   save(smoking, file = paste0(datafolder,names(lf.hds)[index],"/smoking.RData"))
# }


```
<!-- ########################################################## --> 







# Quality estimation

```{r closeRsession, echo=FALSE}
opal.logout(o)
```