---
title: "Sick or disabled"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sickdisDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sickdisDS.R')
```



# Data process



## Spain


### Wave 1


#### Study-specific variable description

| **Name** | `w1labourforce` |
|-|-|
| **Label** |   |
| **Table name**  | `ENRICA_spss_wave1`|
| **Categories** | `1 = Employed`<br/>`2 = Unemployed`<br/>`3 = Retired`<br/>`4 = Housewife`<br/>`6 = Unable to work` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1',variables=list('w1labourforce'), missings = T)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
ENRICA_w1$w1labourforce <- as.numeric(ENRICA_w1$w1labourforce)

```

```{r local w1, echo=F}

vbl <- ENRICA_w1$w1labourforce
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w1, aes(x=factor(w1labourforce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `change 1,2,3,4 into 0`
* `change 6 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$sickdis <- car::recode(ENRICA_w1$w1labourforce,"c(1,2,3,4) = 0; 6 = 1; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ENRICA_ds_w1$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ENRICA_ds_w1$sickdis)
X <- table(ENRICA_w1$w1labourforce, useNA = "ifany")
BeforeH <- c(sum(X[c("1","2","3","4")],na.rm = T),sum(X[c("6")]),X[length(X)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","6->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2labourforce` |
|-|-|
| **Label** |    |
| **Table name**  | `ENRICA_spss_wave2`|
| **Categories** | `1 = Employed`<br/>`2 = Unemployed`<br/>`3 = Retired`<br/>`4 = Housewife`<br/>`6 = Unable to work` |
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2',variables=list('w2labourforce'), missings = T)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
ENRICA_w2$w2labourforce <- as.numeric(ENRICA_w2$w2labourforce)

```

```{r local w2, echo=F}

vbl <- ENRICA_w2$w2labourforce
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(w2labourforce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `change 1,2,3,4 into 0`
* `change 6 into 1`
* `NA into 999`

**R script:**

```{r harmo w2}

ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$sickdis <- car::recode(ENRICA_w2$w2labourforce,"c(1,2,3,4) = 0; 6 = 1; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ENRICA_ds_w2$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ENRICA_ds_w2$sickdis)
X <- table(ENRICA_w2$w2labourforce, useNA = "ifany")
BeforeH <- c(sum(X[c("1","2","3","4")],na.rm = T),sum(X[c("6")]),X[length(X)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","6->1","NA->999")
kable(C)

```



### Wave 3

#### Study-specific variable description


| **Name** | `w3labourforce` |
|-|-|
| **Label** |    |
| **Table name**  | `ENRICA_spss_wave3`|
| **Categories** | `1 = Employed`<br/>`2 = Unemployed`<br/>`3 = Retired`<br/>`4 = Housewife`<br/>`6 = Unable to work` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3',variables=list('w3labourforce'), missings = T)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
ENRICA_w3$w3labourforce <- as.numeric(ENRICA_w3$w3labourforce)

```

```{r local w3, echo=F}

vbl <- ENRICA_w3$w3labourforce
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(w3labourforce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `sickdis` from the study-specific variable it has to be recoded as follows:

* `change 1,2,3,4 into 0`
* `change 6 into 1`
* `NA into 999`
* `NA into 999`

**R script:**

```{r harmo w3}

ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w3$sickdis <- car::recode(ENRICA_w3$w3labourforce,"c(1,2,3,4) = 0; 6 = 1; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ENRICA_ds_w3$sickdis
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(sickdis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ENRICA_ds_w3$sickdis)
X <- table(ENRICA_w3$w3labourforce, useNA = "ifany")
BeforeH <- c(sum(X[c("1","2","3","4")],na.rm = T),X[length(X)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","NA->999")
kable(C)

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ENRICA_ds_w1$sickdis <- labelled(ENRICA_ds_w1$sickdis, labels = cat_label)
label(ENRICA_ds_w1$sickdis) <- ds_label
ENRICA_ds_w2$sickdis <- labelled(ENRICA_ds_w2$sickdis, labels = cat_label)
label(ENRICA_ds_w2$sickdis) <- ds_label
ENRICA_ds_w3$sickdis <- labelled(ENRICA_ds_w3$sickdis, labels = cat_label)
label(ENRICA_ds_w3$sickdis) <- ds_label

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$sickdis <- car::recode(ENRICA_m_ds_w1$sickdis, "miss_values_vector=NA")
ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$sickdis <- car::recode(ENRICA_m_ds_w2$sickdis, "miss_values_vector=NA")
ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$sickdis <- car::recode(ENRICA_m_ds_w3$sickdis, "miss_values_vector=NA")


tt <-    frq(ENRICA_ds_w1$sickdis)[[1]][,c(1:2,4)]
tt[4] <- frq(ENRICA_ds_w2$sickdis)[[1]][,c(4)]
tt[5] <- frq(ENRICA_ds_w3$sickdis)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ENRICA_ds_w1$sickdis), length(ENRICA_ds_w2$sickdis), length(ENRICA_ds_w3$sickdis)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3")
kable(tt)

dbb <- merge(ENRICA_m_ds_w1[,c("id","sickdis")], ENRICA_m_ds_w2[,c("id","sickdis")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ENRICA_m_ds_w3[,c("id","sickdis")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ENRICA <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2, w3 = ENRICA_ds_w3)

for(index in seq_along(l.ENRICA)){
  sickdis <- l.ENRICA[[index]]
  save(sickdis, file = paste0(datafolder,names(l.ENRICA)[index],"/sickdis.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





