---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mbirthDS.R')
```

# Data process

## Spain
    
### Wave 1 

#### Study-specific variables

| **Name** | `m_birth` |
|----------|------------|
| **Label** | `mes de nacimiento` |
| **Table name** | `ENRICA_spss_wave1` |
| **Missings** |`99 = ns/nc`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1_mbirth','ENRICA.ENRICA_spss_wave1',
                         variables=list('m_birth'), missings = TRUE)
ENRICA_w1_mbirth <- opal.execute(o,'ENRICA_w1_mbirth')
```

```{r local1, echo=F}
vari <- ENRICA_w1_mbirth$m_birth
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "m_birth") 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(ENRICA_w1_mbirth, aes(m_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of birth") + ylab("Frequency") + scale_x_continuous(breaks = c(3,6,9,12))
```

There is values 0 in the study-specific variable that we are going to be considered as mistakes and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `99 'ns/nc' into 998`
* `NA into 999`


**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_mbirth$id)
ENRICA_ds_w1$mbirth <- car::recode(ENRICA_w1_mbirth$m_birth, "c(NA, 0)=999; 99=998")
ENRICA_ds_w1$mbirth <- labelled(ENRICA_ds_w1$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ENRICA_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ENRICA_w1_mbirth$m_birth, useNA = "ifany")
BeforeH <- c(BeforeH[1:12])
AfterH <- table(ENRICA_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12])
kable(C)

```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
mbirth <- ENRICA_ds_w1
save(mbirth, file = "../RData/w1/mbirth.RData")
rm(mbirth)

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$mbirth <- car::recode(ENRICA_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w1', ENRICA_m_ds_w1)
#opal.symbol_import(o,'ENRICA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variables

| **Name** | `m_birth` |
|----------|------------|
| **Label** | `mes de nacimiento` |
| **Table name** | `ENRICA_spss_wave2` |
| **Missings** |`99 = ns/nc`|
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_mbirth','ENRICA.ENRICA_spss_wave2',
                         variables=list('m_birth'), missings = TRUE)
ENRICA_w2_mbirth <- opal.execute(o,'ENRICA_w2_mbirth')
```

```{r local2, echo=F}
vari <- ENRICA_w2_mbirth$m_birth
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "m_birth") 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(ENRICA_w2_mbirth, aes(m_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of birth") + ylab("Frequency") + scale_x_continuous(breaks = c(3,6,9,12))
```

There is values 0 in the study-specific variable that we are going to be considered as mistakes and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `99 'ns/nc' into 998`
* `NA into 999`


**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_mbirth$id)
ENRICA_ds_w2$mbirth <- car::recode(ENRICA_w2_mbirth$m_birth, "c(NA, 0)=999; 99=998")
ENRICA_ds_w2$mbirth <- labelled(ENRICA_ds_w2$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ENRICA_w2_mbirth$m_birth, useNA = "ifany")
BeforeH <- c(BeforeH[1:12])
AfterH <- table(ENRICA_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12])
kable(C)

```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
mbirth <- ENRICA_ds_w2
save(mbirth, file = "../RData/w2/mbirth.RData")
rm(mbirth)

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$mbirth <- car::recode(ENRICA_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variables

| **Name** | `m_birth` |
|----------|------------|
| **Label** | `mes de nacimiento` |
| **Table name** | `ENRICA_spss_wave3` |
| **Missings** |`99 = ns/nc`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_mbirth','ENRICA.ENRICA_spss_wave3',
                         variables=list('m_birth'), missings = TRUE)
ENRICA_w3_mbirth <- opal.execute(o,'ENRICA_w3_mbirth')
```

```{r local3, echo=F}
vari <- ENRICA_w3_mbirth$m_birth
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "m_birth") 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(ENRICA_w3_mbirth, aes(m_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of birth") + ylab("Frequency") + scale_x_continuous(breaks = c(3,6,9,12))
```

There is values 0 in the study-specific variable that we are going to be considered as mistakes and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `99 'ns/nc' into 998`
* `NA into 999`

**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_mbirth$id)
ENRICA_ds_w3$mbirth <- car::recode(ENRICA_w3_mbirth$m_birth, "c(NA, 0)=999; 99=998")
ENRICA_ds_w3$mbirth <- labelled(ENRICA_ds_w3$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ENRICA_ds_w3$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ENRICA_w3_mbirth$m_birth, useNA = "ifany")
BeforeH <- c(BeforeH[1:12])
AfterH <- table(ENRICA_ds_w3$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12])
kable(C)
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
mbirth <- ENRICA_ds_w3
save(mbirth, file = "../RData/w3/mbirth.RData")
rm(mbirth)

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$mbirth <- car::recode(ENRICA_m_ds_w3$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```







## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

l.hds <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2, w3 = ENRICA_ds_w3)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("ENRICA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("ENRICA_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)



```






# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
