---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Spain    
    
### Wave 1 

#### Study-specific variable description

| **Name** | `y_birth` |
|----------|------------|
| **Label** | `año de nacimiento` |
| **Table name** | `ENRICA_spss_wave1` |
| **Missings** |`9999 = ns/nc`|
| **Description** |  |




```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1_ybirth','ENRICA.ENRICA_spss_wave1',
                         variables=list('y_birth'), missings = TRUE)
ENRICA_w1_ybirth <- opal.execute(o,'ENRICA_w1_ybirth')
```

```{r local1, echo=F}
vari <- ENRICA_w1_ybirth$y_birth
kable(Continuous_summary(var = vari, missing_values = c(9999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(9999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(9999))$summary, caption = "Summary")
ggplot(ENRICA_w1_ybirth, aes(y_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 2008)

#The data set ENRICA_ds_w1 has the variables age, year_of_birth and year_of_interview:
#ENRICA_ds_w1$compr_year_of_birth <- ENRICA_ds_w1$year_of_interview - ENRICA_ds_w1$age
#ENRICA_ds_w1$compr <- ENRICA_ds_w1$compr_year_of_birth - ENRICA_ds_w1$ybirth
#table(ENRICA_ds_w1$compr)
#err <- c(which(ENRICA_ds_w1$compr==-63), which(ENRICA_ds_w1$compr==-55), which(ENRICA_ds_w1$compr==-50), 
#         which(ENRICA_ds_w1$compr==-40), which(ENRICA_ds_w1$compr==-30), which(ENRICA_ds_w1$compr==-29), 
#         which(ENRICA_ds_w1$compr==-28), which(ENRICA_ds_w1$compr==-15), #which(ENRICA_ds_w1$compr==-10), 
#         which(ENRICA_ds_w1$compr==-9), which(ENRICA_ds_w1$compr==-8), #which(ENRICA_ds_w1$compr==-6), 
#         which(ENRICA_ds_w1$compr==-5), which(ENRICA_ds_w1$compr==-4), which(ENRICA_ds_w1$compr==-3), 
#         which(ENRICA_ds_w1$compr==-2), which(ENRICA_ds_w1$compr==2), which(ENRICA_ds_w1$compr==3), 
#         which(ENRICA_ds_w1$compr==4), which(ENRICA_ds_w1$compr==5), which(ENRICA_ds_w1$compr==6), 
#         which(ENRICA_ds_w1$compr==7), which(ENRICA_ds_w1$compr==8), which(ENRICA_ds_w1$compr==9), 
#         which(ENRICA_ds_w1$compr==10), which(ENRICA_ds_w1$compr==929), which(ENRICA_ds_w1$compr==931), 
#         which(ENRICA_ds_w1$compr==934), which(ENRICA_ds_w1$compr==941), which(ENRICA_ds_w1$compr==944), 
#         which(ENRICA_ds_w1$compr==1946))
#View(ENRICA_ds_w1[err,])
#ENRICA_ds_w1_error <- ENRICA_ds_w1[err,]
#table(ENRICA_ds_w1_error$ybirth)
```

The values 0 and higher than 1950 are considered as mistakes and recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `9999 'ns/nc' into 998`
* `NA into 999`

**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_ybirth$id)
ENRICA_ds_w1$ybirth <- car::recode(ENRICA_w1_ybirth$y_birth, "NA=999; 1951:2008=999; 0=999; 9999=998")
ENRICA_ds_w1$ybirth <- labelled(ENRICA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript, echo=F}
vari <- ENRICA_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 1950)
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
ybirth <- ENRICA_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")
rm(ybirth)

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$ybirth <- car::recode(ENRICA_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w1', ENRICA_m_ds_w1)
#opal.symbol_import(o,'ENRICA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `y_birth` |
|----------|------------|
| **Label** | `año de nacimiento` |
| **Table name** | `ENRICA_spss_wave2` |
| **Missings** |`9999 = ns/nc`|
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_ybirth','ENRICA.ENRICA_spss_wave2',
                         variables=list('y_birth'), missings = TRUE)
ENRICA_w2_ybirth <- opal.execute(o,'ENRICA_w2_ybirth')
```

```{r local2, echo=F}
vari <-  ENRICA_w2_ybirth$y_birth
kable(Continuous_summary(var = vari, missing_values = c(9999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(9999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(9999))$summary, caption = "Summary")
ggplot(ENRICA_w2_ybirth, aes(y_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 2008)
```

As it has been seen in baseline the values 0 and higher than 1950 are considered as mistakes and recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `9999 'ns/nc' into 998`
* `NA into 999`

**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_ybirth$id)
ENRICA_ds_w2$ybirth <- car::recode(ENRICA_w2_ybirth$y_birth, "NA=999; 1951:2008=999; 0=999; 9999=998")
ENRICA_ds_w2$ybirth <- labelled(ENRICA_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 1950)
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
ybirth <- ENRICA_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
rm(ybirth)

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$ybirth <- car::recode(ENRICA_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variable description

| **Name** | `y_birth` |
|----------|------------|
| **Label** | `año de nacimiento` |
| **Table name** | `ENRICA_spss_wave3` |
| **Missings** |`9999 = ns/nc`|
| **Description** |  |

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_ybirth','ENRICA.ENRICA_spss_wave3',
                         variables=list('y_birth'), missings = TRUE)
ENRICA_w3_ybirth <- opal.execute(o,'ENRICA_w3_ybirth')
```

```{r local3, echo=F}
vari <- ENRICA_w3_ybirth$y_birth
kable(Continuous_summary(var = vari, missing_values = c(9999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(9999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(9999))$summary, caption = "Summary")
ggplot(ENRICA_w3_ybirth, aes(y_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 2008)
```

As it has been seen in baseline the values 0 and higher than 1950 are considered as mistakes and recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `9999 'ns/nc' into 998`
* `NA into 999`


**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_ybirth$id)
ENRICA_ds_w3$ybirth <- car::recode(ENRICA_w3_ybirth$y_birth, "NA=999; 1951:2008=999; 0=999; 9999=998")
ENRICA_ds_w3$ybirth <- labelled(ENRICA_ds_w3$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ENRICA_ds_w3$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1912, 1950)
```

#### Validation
```{r crosstabulation3, echo=F}
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
ybirth <- ENRICA_ds_w3
save(ybirth, file = "../RData/w3/ybirth.RData")
rm(ybirth)

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$ybirth <- car::recode(ENRICA_m_ds_w3$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
