---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```

# Data process

## Spain

### Wave 1 

#### Study-specific variable description


| **Name** | `w1age` |
|----------|------------|
| **Label** | `age baseline` |
| **Table name** | `ENRICA_spss_wave1` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1_age','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1age'), missings = TRUE)
ENRICA_w1_age <- opal.execute(o,'ENRICA_w1_age')
```

```{r local1, echo=F}
vari <- ENRICA_w1_age$w1age
kable(Continuous_summary(vari, missing_values = NA )[3], caption = "w1age")
pander(Continuous_summary(vari, missing_values = NA )$summary, caption = "Summary")
ggplot(ENRICA_w1_age, aes(w1age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_age$id)
ENRICA_ds_w1$age <- car::recode(ENRICA_w1_age$w1age, "NA='999'")
ENRICA_ds_w1$age <- labelled(ENRICA_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ENRICA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency") 

```

#### Validation
```{r crosstabulation1, echo=F}

load(paste0(datafolder,"w1/ybirth",".RData"))
load(paste0(datafolder,"w1/yintw",".RData"))
ENRICA_w1_age <- left_join(ENRICA_w1_age,yintw, by="id")
ENRICA_w1_age <- left_join(ENRICA_w1_age,ybirth, by="id")
ENRICA_w1_age$ybirth <- car::recode(ENRICA_w1_age$ybirth, "miss_values_vector=NA")
ENRICA_w1_age$yintw <- car::recode(ENRICA_w1_age$yintw, "miss_values_vector=NA")
ENRICA_w1_age$cage <- ENRICA_w1_age$yintw-ENRICA_w1_age$ybirth
ENRICA_w1_age$diff <- abs(ENRICA_w1_age$w1age - ENRICA_w1_age$cage)
ENRICA_w1_age <- remove_val_labels(ENRICA_w1_age)
kable(frq(ENRICA_w1_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(ENRICA_w1_age[which(ENRICA_w1_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```







### Wave 2 

#### Study-specific variable description

| **Name** | `w2age` |
|----------|------------|
| **Label** | `age wave 2` |
| **Table name** | `ENRICA_spss_wave2` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_age','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2age'), missings = TRUE)
```

```{r local2, echo=F}
ENRICA_w2_age <- opal.execute(o,'ENRICA_w2_age')
vari <- ENRICA_w2_age$w2age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w2age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w2_age, aes(w2age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-7988.0, NA into 999`

**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_age$id)
ENRICA_ds_w2$age <- car::recode(ENRICA_w2_age$w2age, "-7988.0=999; NA='999'")
ENRICA_ds_w2$age <- labelled(ENRICA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency") 

```

#### Validation
```{r crosstabulation2, echo=F}

load(paste0(datafolder,"w2/ybirth",".RData"))
load(paste0(datafolder,"w2/yintw",".RData"))
ENRICA_w2_age <- left_join(ENRICA_w2_age,yintw, by="id")
ENRICA_w2_age <- left_join(ENRICA_w2_age,ybirth, by="id")
ENRICA_w2_age$ybirth <- car::recode(ENRICA_w2_age$ybirth, "miss_values_vector=NA")
ENRICA_w2_age$yintw <- car::recode(ENRICA_w2_age$yintw, "miss_values_vector=NA")
ENRICA_w2_age$cage <- ENRICA_w2_age$yintw-ENRICA_w2_age$ybirth
ENRICA_w2_age$diff <- abs(ENRICA_w2_age$w2age - ENRICA_w2_age$cage)
ENRICA_w2_age <- remove_val_labels(ENRICA_w2_age)
kable(frq(ENRICA_w2_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(ENRICA_w2_age[which(ENRICA_w2_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```





### Wave 3 

#### Study-specific variable description


| **Name** | `w3age` |
|----------|------------|
| **Label** | `age wave 3` |
| **Table name** | `ENRICA_spss_wave3` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_age','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3age'), missings = TRUE)
ENRICA_w3_age <- opal.execute(o,'ENRICA_w3_age')
```

```{r local3, echo=F}
vari <- ENRICA_w3_age$w3age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "w3age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w3_age, aes(w3age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_age$id)
ENRICA_ds_w3$age <- car::recode(ENRICA_w3_age$w3age, "NA='999'")
ENRICA_ds_w3$age <- labelled(ENRICA_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ENRICA_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency") + xlim(60,100)
```

#### Validation
```{r crosstabulation3, echo=F}

load(paste0(datafolder,"w3/ybirth",".RData"))
load(paste0(datafolder,"w3/yintw",".RData"))
ENRICA_w3_age <- left_join(ENRICA_w3_age,yintw, by="id")
ENRICA_w3_age <- left_join(ENRICA_w3_age,ybirth, by="id")
ENRICA_w3_age$ybirth <- car::recode(ENRICA_w3_age$ybirth, "miss_values_vector=NA")
ENRICA_w3_age$yintw <- car::recode(ENRICA_w3_age$yintw, "miss_values_vector=NA")
ENRICA_w3_age$cage <- ENRICA_w3_age$yintw-ENRICA_w3_age$ybirth
ENRICA_w3_age$diff <- abs(ENRICA_w3_age$w3age - ENRICA_w3_age$cage)
ENRICA_w3_age <- remove_val_labels(ENRICA_w3_age)
kable(frq(ENRICA_w3_age$diff), caption = 'Frequencies of differences between harmonised age and age computed as year of interview - year of birth')
kable(ENRICA_w3_age[which(ENRICA_w3_age$diff>2),], align = 'c', caption = 'Individuals with difference greater than 2')

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


enrica.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(enrica.cw, function(wname) if(exists(paste0("ENRICA_ds_",wname[1]))){wname = list(get(paste0("ENRICA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation

Individuals with incompatible data are specified at each validation.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
