---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Level of education"
ds_label_all <- "Highest level of formal education achieved"
```


<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1 

#### Study-specific variable description


* Name: `p61`
* Label: `¿Cuál es el máximo nivel de estudios que ha completado usted?`
* Categories: 
    + `1 = no sabe leer ni escribir`
    + `2 = enseñanza primaria incompleta pero sabe leer y escribir en a`
    + `3 = enseñanza primaria completa`
    + `4 = enseñanza secundaria 1a etapa`
    + `5 = enseñanza secundaria 2a etapa`
    + `6 = estudios universitarios medios`
    + `7 = estudios universitarios superiores`
* Missings
   + `98 = otros (especificar)`
   + `99 = (no leer) ns/nc`
* Description:

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w1_educ','ENRICA.ENRICA_spss_wave1',
                         variables=list('p61'), missings = TRUE)
ENRICA_w1_educ <- opal.execute(o,'ENRICA_w1_educ')
```

```{r local1, echo=FALSE}
vari <- ENRICA_w1_educ$p61
kable(Categorical_summary(vari, missing_values = c(97,99))[3], caption = "Education") 
kable(Categorical_summary(vari, missing_values = c(97,99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(97,99))[2], caption = "Type of missing")
ggplot(ENRICA_w1_educ, aes(x=factor(p61))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "no sabe leer ni escribir" into 0`
* `2 "enseñanza primaria incompleta pero sabe leer y escribir en a" into 0`
* `3 "enseñanza primaria completa" into 1`
* `4 "enseñanza secundaria 1a etapa" into 2`
* `5 "enseñanza secundaria 2a etapa" into 2`
* `6 "estudios universitarios medios" into 3`
* `7 "estudios universitarios superiores" into 3`
* `98 "otros (especificar)" into 999`
* `99 "(no leer) ns/nc" into 998`

**R script:**

```{r harmo1, echo=TRUE}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_educ$id)
ENRICA_ds_w1$education <- car::recode(ENRICA_w1_educ$p61, "1=0; 2=0; 3=1; 4=2; 5=2; 6=3; 7=3; 98=999; 99=998; NA=999")
ENRICA_ds_w1$education <- labelled(ENRICA_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ENRICA_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Level of Education") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(ENRICA_w1_educ$p61, useNA = "ifany")
BeforeH <- c(sum(BeforeH[1:2]), BeforeH[3], sum(BeforeH[4:5]), sum(BeforeH[6:7]))
AfterH <- table(ENRICA_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2)->0", "3->1", "(4,5)->2", "(6,7)->3")
kable(C)
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
education <- ENRICA_ds_w1
save(education, file = "../RData/w1/education.RData")
rm(education)

label(ENRICA_ds_w1$education) <- ds_label_all
#education <- ENRICA_ds_w1
#save(education, file = "../RData/w1/education.RData")
```






### Wave 2 

Not found.



### Wave 3 

Not found.

# Quality estimation

No comments


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
