---
title: "Living alone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `living_alone`
* Variable label: `Participant is currently living alone`
* Variable description: `Participant is currently living alone`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 

## Spain


### Wave 1 

#### Study-specific variable description



| **Name** | `w1livingalone`|
|-|-|
| **Label** |  |
| **Table name** | `ENRICA_spss_wave1` |
| **Categories** |`0 = No; 1 = Yes`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1_la','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1livingalone'), missings = TRUE)
```

```{r local1, echo=F}
ENRICA_w1_la <- opal.execute(o,'ENRICA_w1_la')
vari <- ENRICA_w1_la$w1livingalone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w1_la$w1livingalone, missing_values = NA)
ggplot(ENRICA_w1_la, aes(x=factor(w1livingalone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_la$id)
ENRICA_ds_w1$living_alone <- car::recode(ENRICA_w1_la$w1livingalone, "NA=999")
ENRICA_ds_w1$living_alone <- labelled(ENRICA_ds_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ENRICA_ds_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ENRICA_w1_la$w1livingalone)
AfterH <- table(ENRICA_ds_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
living_alone <- ENRICA_ds_w1
save(living_alone, file = "../RData/w1/living_alone.RData")
rm(living_alone)

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$living_alone <- car::recode(ENRICA_m_ds_w1$living_alone, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w1', ENRICA_m_ds_w1)
#opal.symbol_import(o,'ENRICA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description



| **Name** | `w2livingalone`|
|-|-|
| **Label** |  |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** |`0 = No; 1 = Yes`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_la','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2livingalone'), missings = TRUE)
```

```{r local2, echo=F}
ENRICA_w2_la <- opal.execute(o,'ENRICA_w2_la')
vari <- ENRICA_w2_la$w2livingalone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w2_la$w2livingalone, missing_values = NA)
ggplot(ENRICA_w2_la, aes(x=factor(w2livingalone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_la$id)
ENRICA_ds_w2$living_alone <- car::recode(ENRICA_w2_la$w2livingalone, "NA=999")
ENRICA_ds_w2$living_alone <- labelled(ENRICA_ds_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ENRICA_ds_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ENRICA_w2_la$w2livingalone, useNA = "ifany")
AfterH <- table(ENRICA_ds_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
living_alone <- ENRICA_ds_w2
save(living_alone, file = "../RData/w2/living_alone.RData")
rm(living_alone)

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$living_alone <- car::recode(ENRICA_m_ds_w2$living_alone, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description



| **Name** | `w3livingalone`|
|-|-|
| **Label** |  |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** |`0 = No; 1 = Yes`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_la','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3livingalone'), missings = TRUE)
```

```{r local3, echo=F}
ENRICA_w3_la <- opal.execute(o,'ENRICA_w3_la')
vari <- ENRICA_w3_la$w3livingalone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ENRICA_w3_la$w3livingalone, missing_values = NA)
ggplot(ENRICA_w3_la, aes(x=factor(w3livingalone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_la$id)
ENRICA_ds_w3$living_alone <- car::recode(ENRICA_w3_la$w3livingalone, "NA=999")
ENRICA_ds_w3$living_alone <- labelled(ENRICA_ds_w3$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ENRICA_ds_w3$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ENRICA_w3_la$w3livingalone, useNA = "ifany")
AfterH <- table(ENRICA_ds_w3$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
living_alone <- ENRICA_ds_w3
save(living_alone, file = "../RData/w3/living_alone.RData")
rm(living_alone)

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$living_alone <- car::recode(ENRICA_m_ds_w3$living_alone, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
