---
title: "Current smoker"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../../CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/current_smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/current_smokingDS.R')
```



# Data process


## China

### Wave 1 

#### Study-specific variable description

| **Name** | `da059` | `da061` |
|-|-|-|
| **Label** | `Smoke or Not` | `Still Smoking or Not` |
| **Table name** | `health_status_and_functioning_wave1` |  `health_status_and_functioning_wave1` |
| **Categories:**| `1 = Yes` <br/> `2 = No`| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.health_status_and_functioning_wave1', variables=list('da059','da061'), missings = TRUE)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')


opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids', variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,4]), da059=as.numeric(new_2[,2]), da061=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)

```

```{r local w1, echo=F}
vbl <- CHARLS_w1$da059
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'da059')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(da059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$da061
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'da061')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(da061))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `da059=1&da061=1 into 1` 
* `da059=2|(da059=1&da061=2) into 0`                                           
* `NA into 999`

**R script:**

```{r harmo w1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$current_smoking <- rep(999,length(CHARLS_ds_w1$id))
CHARLS_ds_w1$current_smoking[which(CHARLS_w1$da059==2 | (CHARLS_w1$da059==1&CHARLS_w1$da061==2))]<-0
CHARLS_ds_w1$current_smoking[which(CHARLS_w1$da059==1 & CHARLS_w1$da061==1)]<-1
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- CHARLS_ds_w1$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(CHARLS_ds_w1$current_smoking)
X <- c(sum(na.omit(CHARLS_w1$da059==2|(CHARLS_w1$da059==1&CHARLS_w1$da061==2))),sum(na.omit(CHARLS_w1$da059==1&CHARLS_w1$da061==1)))
BeforeH<- c(X[1:2],sum(is.na(CHARLS_w1$da059),na.omit(is.na(CHARLS_w1$da061)&(CHARLS_w1$da059==1))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("da059=2|(da059=1&da061=2)->0","da059=1&da061=1->1","NA->999") 
kable(C)
```




### Wave 2

#### Study-specific variable description

| **Name** | `da059` | `da061` |
|-|-|-|
| **Label** | `Smoke or Not` | `Still Smoking or Not` |
| **Table name** | `Health_Status_and_Functioning_wave2` |  `Health_Status_and_Functioning_wave2` |
| **Categories:**| `1 = Yes` <br/> `2 = No`| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |

   
```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('da059','da061'), missings = TRUE)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')



opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids', variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], da059=as.numeric(new_2[,2]), da061=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$da059
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'da059')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(da059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$da061
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'da061')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(da061))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `da059=1&da061=1 into 1` 
* `da059=2|(da059=1&da061=2) into 0`                                           
* `NA into 999`

**R script:**

```{r harmo w2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$current_smoking <- rep(999,length(CHARLS_ds_w2$id))
CHARLS_ds_w2$current_smoking[which(CHARLS_w2$da059==2 | (CHARLS_w2$da059==1&CHARLS_w2$da061==2))]<-0
CHARLS_ds_w2$current_smoking[which(CHARLS_w2$da059==1 & CHARLS_w2$da061==1)]<-1
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- CHARLS_ds_w2$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(CHARLS_ds_w2$current_smoking)
X <- c(sum(na.omit(CHARLS_w2$da059==2|(CHARLS_w2$da059==1&CHARLS_w2$da061==2))),sum(na.omit(CHARLS_w2$da059==1&CHARLS_w2$da061==1)))
BeforeH<- c(X[1:2],sum(is.na(CHARLS_w2$da059),na.omit(is.na(CHARLS_w2$da061)&(CHARLS_w2$da059==1))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("da059=2|(da059=1&da061=2)->0","da059=1&da061=1->1","NA->999") 
kable(C)
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}
CHARLS_ds_w1$current_smoking <- labelled(CHARLS_ds_w1$current_smoking, labels = cat_label)
label(CHARLS_ds_w1$current_smoking) <- ds_label
CHARLS_ds_w2$current_smoking <- labelled(CHARLS_ds_w2$current_smoking, labels = cat_label)
label(CHARLS_ds_w2$current_smoking) <- ds_label


CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$current_smoking <- car::recode(CHARLS_m_ds_w1$current_smoking, "miss_values_vector=NA")
CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$current_smoking <- car::recode(CHARLS_m_ds_w2$current_smoking, "miss_values_vector=NA")


tt <-    frq(CHARLS_ds_w1$current_smoking)[[1]][,c(1:2,4)]
tt[4] <- frq(CHARLS_ds_w2$current_smoking)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(CHARLS_ds_w1$current_smoking), length(CHARLS_ds_w2$current_smoking)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(CHARLS_m_ds_w1[,c("id","current_smoking")], CHARLS_m_ds_w2[,c("id","current_smoking")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.CHARLS <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(index in seq_along(l.CHARLS)){
  current_smoking <- l.CHARLS[[index]]
  save(current_smoking, file = paste0(datafolder,names(l.CHARLS)[index],"/current_smoking.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
