---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
source("../../CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process


## China


### Wave 1 

#### Study-specific variable description

| **Name** | `da063` |
|-|-|
| **Label** | `The Number of Cigarettes You Consume` |
| **Table name** | `health_status_and_functioning_wave1` |  `health_status_and_functioning_wave1` |
| **Categories:**| `continuous`|
| **Missings:**| `NA` |
| **Description** |  | 


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.health_status_and_functioning_wave1', variables=list('da063'), missings = TRUE)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')


opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids', variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), da063=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)

```

```{r local w1, echo=F}
vbl <- CHARLS_w1$da063
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = 'da063') 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1, aes(da063)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(0,125)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `da063*7`
* `NA into 999`

**R script:**

```{r harmo w1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$n_cigarettes <- car::recode(CHARLS_w1$da063*7, "NA = '999' ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- CHARLS_ds_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,850) 
```

#### Validation
```{r crosstabulation w1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name** | `da063` |
|-|-|
| **Label** | `The Number of Cigarettes You Consume` |
| **Table name** | `Health_Status_and_Functioning_wave2` |
| **Categories:**| `continuous`|
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Health_Status_and_Functioning_wave2', variables=list('da063'), missings = TRUE)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')


opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids', variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], da063=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)
```

```{r local w2, echo=F}
vbl <- CHARLS_w2$da063
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2, aes(da063)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(0,105)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `da063*7`
* `NA into 999`

**R script:**

```{r harmo w2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$n_cigarettes <- car::recode(CHARLS_w2$da063*7, "NA = '999' ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- CHARLS_ds_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,710)
```

#### Validation
```{r crosstabulation w2, echo=F}
```





```{r final, echo=F}

l.hds <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
