---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```


# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `mintw`
* Variable label: `month of interview`
* Variable description: `month of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01mniw_m`
* Label: `The this questionnaire interview date (a month).`
* Type of variable: `countinous`

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_minter','KLOSA.w01_main_e',
                         variables=list('w01mniw_m'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_minter <- opal.execute(o,'KLOSA_w1_minter')
Categorical_summary(var = KLOSA_w1_minter$w01mniw_m, missing_values = NA)
ggplot(KLOSA_w1_minter, aes(x=factor(w01mniw_m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_minter$id)
KLOSA_ds_w1$mintw <- car::recode(KLOSA_w1_minter$w01mniw_m, "NA=999")
KLOSA_ds_w1$mintw <- labelled(KLOSA_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = KLOSA_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(KLOSA_w1_minter$w01mniw_m, useNA = "ifany")
AfterH <- table(KLOSA_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


```{r importOPAL1, echo=F}
val_labels(KLOSA_ds_w1) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
mintw <- KLOSA_ds_w1
save(mintw, file = "../RData/w1/mintw.RData")
rm(mintw)

KLOSA_m_ds_w1 <- KLOSA_ds_w1
KLOSA_m_ds_w1$mintw <- car::recode(KLOSA_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w1', KLOSA_m_ds_w1)
#opal.symbol_import(o,'KLOSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02mniw_m`
* Label: `The this questionnaire interview date (a month).`
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_minter','KLOSA.w02_main_e_spss',
                         variables=list('w02mniw_m'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_minter <- opal.execute(o,'KLOSA_w2_minter')
Categorical_summary(var = KLOSA_w2_minter$w02mniw_m, missing_values = NA)
ggplot(KLOSA_w2_minter, aes(x=factor(w02mniw_m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_minter$id)
KLOSA_ds_w2$mintw <- car::recode(KLOSA_w2_minter$w02mniw_m, "NA=999")
KLOSA_ds_w2$mintw <- labelled(KLOSA_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = KLOSA_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(KLOSA_w2_minter$w02mniw_m, useNA = "ifany")
AfterH <- table(KLOSA_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL2, echo=F}
val_labels(KLOSA_ds_w2) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
mintw <- KLOSA_ds_w2
save(mintw, file = "../RData/w2/mintw.RData")
rm(mintw)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$mintw <- car::recode(KLOSA_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03mniw_m`
* Label: `The date when the respondent is born(yyyy)`
* Type of variable: `countinous`

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_minter','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03mniw_m'), missings = TRUE)
KLOSA_w3_minter <- opal.execute(o,'KLOSA_w3_minter')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_minter$id <- substr(KLOSA_w3_minter$id,1,nchar(KLOSA_w3_minter$id)-2)
```

```{r local3, echo=F}
Categorical_summary(var = KLOSA_w3_minter$w03mniw_m, missing_values = NA)
ggplot(KLOSA_w3_minter, aes(x=factor(w03mniw_m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_minter$id)
KLOSA_ds_w3$mintw <- car::recode(KLOSA_w3_minter$w03mniw_m, "NA=999")
KLOSA_ds_w3$mintw <- labelled(KLOSA_ds_w3$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = KLOSA_ds_w3$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(KLOSA_w3_minter$w03mniw_m, useNA = "ifany")
AfterH <- table(KLOSA_ds_w3$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL3, echo=F}
val_labels(KLOSA_ds_w3) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
mintw <- KLOSA_ds_w3
save(mintw, file = "../RData/w3/mintw.RData")
rm(mintw)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$mintw <- car::recode(KLOSA_m_ds_w3$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```






### KLOSA - Wave 4 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04mniw_m`
* Label: `The this questionnaire interview date (mm).`
* Type of variable: `countinous`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_minter','KLOSA.w04_main_e_spss',
                         variables=list('w04mniw_m'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_minter <- opal.execute(o,'KLOSA_w4_minter')
Categorical_summary(var = KLOSA_w4_minter$w04mniw_m, missing_values = NA)
ggplot(KLOSA_w4_minter, aes(x=factor(w04mniw_m))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 2 years, 
but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_minter$id)
KLOSA_ds_w4$mintw <- car::recode(KLOSA_w4_minter$w04mniw_m, "NA=999")
KLOSA_ds_w4$mintw <- labelled(KLOSA_ds_w4$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = KLOSA_ds_w4$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(KLOSA_w4_minter$w04mniw_m, useNA = "ifany")
AfterH <- table(KLOSA_ds_w4$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


```{r importOPAL4, echo=F}
val_labels(KLOSA_ds_w4) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
mintw <- KLOSA_ds_w4
save(mintw, file = "../RData/w4/mintw.RData")
rm(mintw)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$mintw <- car::recode(KLOSA_m_ds_w4$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


#### Quality estimation
The date was based in the study specific variable taking into account the waves time lapse.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
