---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```

<!-- ########################################################## --> 


<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',
                         variables=list('w01gender1'), missings = TRUE)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$respondent <- 0
KLOSA_ds_w1$respondent <- labelled(KLOSA_ds_w1$respondent, labels = cat_label)
label(KLOSA_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- KLOSA_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL1, echo=FALSE}
respondent <- KLOSA_ds_w1
save(respondent, file = "../RData/w1/respondent.RData")
rm(respondent)
```





### Wave 2 

#### Study-specific variable description


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',
                         variables=list('w02gender1'), missings = TRUE)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$respondent <- 0
KLOSA_ds_w2$respondent <- labelled(KLOSA_ds_w2$respondent, labels = cat_label)
label(KLOSA_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- KLOSA_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL2, echo=FALSE}
respondent <- KLOSA_ds_w2
save(respondent, file = "../RData/w2/respondent.RData")
rm(respondent)
```






### Wave 3 

#### Study-specific variable description

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03gender1'), missings = TRUE)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 


**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$respondent <- 0
KLOSA_ds_w3$respondent <- labelled(KLOSA_ds_w3$respondent, labels = cat_label)
label(KLOSA_ds_w3$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- KLOSA_ds_w3$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL3, echo=FALSE}
respondent <- KLOSA_ds_w3
save(respondent, file = "../RData/w3/respondent.RData")
rm(respondent)
```





### Wave 4 

#### Study-specific variable description

```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',
                         variables=list('w04gender1'), missings = TRUE)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$respondent <- 0
KLOSA_ds_w4$respondent <- labelled(KLOSA_ds_w4$respondent, labels = cat_label)
label(KLOSA_ds_w4$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- KLOSA_ds_w4$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL4, echo=FALSE}
respondent <- KLOSA_ds_w4
save(respondent, file = "../RData/w4/respondent.RData")
rm(respondent)
```


# Quality estimation

All eligible household members are participants, and there is no information specifying their relationship.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```