---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightDS.R')
```


# Data process

## China

### Wave 1 

#### Study-specific variable description


| **Name** |`ql002`|
|-|-|
| **Label** |`Weight Measurement`|
| **Table name** |`biomarkers_wave1`|
| **Units** |`kg`|
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_weig2','CHARLS.biomarkers_wave1',
                         variables=list('ql002'), missings = TRUE)
CHARLS_w1_weig2 <- opal.execute(o,'CHARLS_w1_weig2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


CHARLS_w1_weig2$oldid <- CHARLS_w1_weig2$id
CHARLS_w1_weig2$id <- CHARLS_ids(ids = CHARLS_w1_weig2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ql002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_weig <- Add_indiv(old = CHARLS_w1_weig2, new = CHARLS_w1_id)
```

```{r local1, echo=FALSE}
vari <- CHARLS_w1_weig$ql002
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ql002") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_weig, aes(ql002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

The values under 20 kg are going to be recoded as missing values 999.

**R script:**

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_weig$id)
CHARLS_ds_w1$weight <- car::recode(CHARLS_w1_weig$ql002, "NA=999; 0:18 = 999")
CHARLS_ds_w1$weight <- labelled(CHARLS_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$weight
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("weight") + ylab("Frequency")
```

#### Validation
There are some unusual values that are lower than 30kg:
```{r crosstabulation1, echo=FALSE}
kable(CHARLS_ds_w1[which(CHARLS_ds_w1$weight<30),])
```


### Wave 2 

#### Study-specific variable description


| **Name** |`ql002`|
|-|-|
| **Label** |`Weight Measurement`|
| **Table name** |`Biomarker_wave2`|
| **Units** |`kg`|
| **Description** |  |




```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_weig2','CHARLS.Biomarker_wave2',
                         variables=list('ql002'), missings = TRUE)
CHARLS_w2_weig2 <- opal.execute(o,'CHARLS_w2_weig2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ql002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_weig <- Add_indiv(old = CHARLS_w2_weig2, new = CHARLS_w2_id)
```

```{r local2, echo=FALSE}
vari <- CHARLS_w2_weig$ql002
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ql002") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_weig, aes(ql002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_weig$id)
CHARLS_ds_w2$weight <- car::recode(CHARLS_w2_weig$ql002, "NA=999")
CHARLS_ds_w2$weight <- labelled(CHARLS_ds_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$weight
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("weight") + ylab("Frequency")
```

#### Validation
There are some unusual values that are lower than 30kg:
```{r crosstabulation2, echo=FALSE}
kable(CHARLS_ds_w2[which(CHARLS_ds_w2$weight<30),])
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation
Anthropometric measure.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

