---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/heightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/heightDS.R')
```

# Data process

## China

### Wave 1 

#### Study-specific variable description


| **Name** |`qi002`|
|-|-|
| **Label** |`Height`|
| **Table name** |`biomarkers_wave1`|
| **Units** |`cm`|
| **Missings** |`993 = R tried but was unable`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_heig2','CHARLS.biomarkers_wave1',
                         variables=list('qi002'), missings = TRUE)
CHARLS_w1_heig2 <- opal.execute(o,'CHARLS_w1_heig2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_heig2$oldid <- CHARLS_w1_heig2$id
CHARLS_w1_heig2$id <- CHARLS_ids(ids = CHARLS_w1_heig2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), qi002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_heig <- Add_indiv(old = CHARLS_w1_heig2, new = CHARLS_w1_id)
```

```{r local1, echo=FALSE}

vari <- CHARLS_w1_heig$qi002
vbl_miss <- c(993)
kable(Continuous_summary(var = vari, missing_values = c(993))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(993))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(993))$summary, caption = "Summary")
ggplot(CHARLS_w1_heig, aes(qi002)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `keep 993 into 993`
* `NA into 999`
* `qi002 < 2 assumed to be measured in metres into qi002*100`
* `10<qi002 < 20 assumed to be measured in decimetres into qi002*10`
* `else, qi002<60 into 999`

**R script:**

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_heig$id)
CHARLS_w1_heig$qi002[which(CHARLS_w1_heig$qi002<2)] <- CHARLS_w1_heig$qi002[which(CHARLS_w1_heig$qi002<2)]*100
CHARLS_w1_heig$qi002[which(CHARLS_w1_heig$qi002<20)] <- CHARLS_w1_heig$qi002[which(CHARLS_w1_heig$qi002<20)]*10

CHARLS_ds_w1$height <- car::recode(CHARLS_w1_heig$qi002, "0:59=999; NA=999")

```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency")

```

#### Validation

```{r crosstabulation1, echo=FALSE}
kable(CHARLS_ds_w1[which(CHARLS_ds_w1$height<100),], caption = 'There are some unusual values that are lower than 100cm. ')

```





### Wave 2 

#### Study-specific variable description


| **Name** |`qi002`|
|-|-|
| **Label** |`Height`|
| **Table name** |`Biomarker_wave2`|
| **Units** |`cm`|
| **Missings** |`993 = R tried but was unable`|
| **Description** |  |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_heig2','CHARLS.Biomarker_wave2',
                         variables=list('qi002'), missings = TRUE)
CHARLS_w2_heig2 <- opal.execute(o,'CHARLS_w2_heig2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], qi002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_heig <- Add_indiv(old = CHARLS_w2_heig2, new = CHARLS_w2_id)
```

```{r local2, echo=FALSE}
vari <- CHARLS_w2_heig$qi002
vbl_miss <- c(993)
kable(Continuous_summary(var = vari, missing_values = c(993))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(993))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(993))$summary, caption = "Summary")
ggplot(CHARLS_w2_heig, aes(qi002)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% vbl_miss)) + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `qi002 < 2 assumed to be measured in metres into qi002*100`
* `else, qi002<60 into 999`


**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_heig$id)
CHARLS_w2_heig$qi002[which(CHARLS_w2_heig$qi002<2)] <- CHARLS_w2_heig$qi002[which(CHARLS_w2_heig$qi002<2)]*100

CHARLS_ds_w2$height <- car::recode(CHARLS_w2_heig$qi002, "0:59=999;NA=999")
CHARLS_ds_w2$height <- labelled(CHARLS_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$height
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab("height") + ylab("Frequency")

```

#### Validation
There are some unusual values that are lower than 100cm. 
```{r crosstabulation2, echo=FALSE}
kable(CHARLS_ds_w2[which(CHARLS_ds_w2$height<100),])
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}




# Creation of longitudinal variance frequencies for each population

longvar <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  dbb$var <- apply(dbb[,2:(length(m.hds)+1)],1,var,na.rm=T)
  
  
  return(dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing individuals with great longitudinal variance
  f.dbb <- longvar(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[which(f.dbb$var>200),], caption = 'Individuals with difference of height across waves higher than 20 cm'))
  print(knitr::kable(f.dbb[which(f.dbb$w2<80),], caption = 'Individuals with height lower than 80 cm in wave 2'))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



Since there are only two years of difference between waves, we impute with the most standard height the individuals of the previous list of high differences for which this can be decided.

Since the bmi computed for the two individuals with height lower than 80 cm which not appear in the previous set is extremely high (over 100), the height of one (78.6 by "321116318001") seems to be an error as it coincides with the reported weight, and they have data only in wave 2, we recode their height as missing.

**R script:**

```{r}
  # Corrections

CHARLS_ds_w1$height[CHARLS_ds_w1$id=="057457110002"] <- CHARLS_ds_w2$height[CHARLS_ds_w2$id=="057457110002"]
CHARLS_ds_w2$height[CHARLS_ds_w2$id=="262728205002"] <- CHARLS_ds_w1$height[CHARLS_ds_w1$id=="262728205002"]
CHARLS_ds_w1$height[CHARLS_ds_w1$id=="262728217001"] <- CHARLS_ds_w2$height[CHARLS_ds_w2$id=="262728217001"]
CHARLS_ds_w1$height[CHARLS_ds_w1$id=="268606118002"] <- CHARLS_ds_w2$height[CHARLS_ds_w2$id=="268606118002"]
CHARLS_ds_w2$height[CHARLS_ds_w2$id=="324045228001"] <- CHARLS_ds_w1$height[CHARLS_ds_w1$id=="324045228001"]


CHARLS_ds_w2$height[CHARLS_ds_w2$id=="057633306001"] <- 999
CHARLS_ds_w2$height[CHARLS_ds_w2$id=="321116318001"] <- 999

```


``` {r save, echo=F}



# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


lmlist <- labelling(lmlist[[1]],lmlist[[2]])
print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
# Saving tibbles
savingRD(lmlist[[1]],vbl_name=hd_vbl)


```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


