---
title: "BMI"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `bmi`
* Label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `the BMI variable should be created by dividing weight and heigh variables with the following equation= weight (kg)/height(m)^2.`

```{r lab, echo=FALSE}
ds_label <- "bmi"
ds_label_all <- "Body Mass Index calculated as weight (kg)/height(m)^2"
```

# Data process

## CHARLS

### Wave 1 

The study-specific variable elected to be harmonised is:

* Name: `ql002`
* Label: `Weight Measurement`
* Type of variable: `countinous`
* Name: `qi002`
* Label: `Height`
* Type of variable: `countinous`
* Missings: 
    + `993 = Disable to measure`


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_bmi2','CHARLS.biomarkers_wave1',
                         variables=list('ql002', 'qi002'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=FALSE}
CHARLS_w1_bmi2 <- opal.execute(o,'CHARLS_w1_bmi2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
CHARLS_w1_bmi2$oldid <- CHARLS_w1_bmi2$id
CHARLS_w1_bmi2$id <- CHARLS_ids(ids = CHARLS_w1_bmi2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,4]), qi002=as.numeric(new_2[,2]), ql002=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w1_bmi <- Add_indiv(old = CHARLS_w1_bmi2, new = CHARLS_w1_id)

vari <- CHARLS_w1_bmi$ql002
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Weight") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_bmi, aes(ql002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")

vari <- CHARLS_w1_bmi$qi002
kable(Continuous_summary(var = vari, missing_values = c(993))[3], caption = "Height")
kable(Continuous_summary(vari, missing_values = c(993))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(993))$summary, caption = "Summary")
ggplot(CHARLS_w1_bmi, aes(qi002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `keep 993 into 993`
* `NA into 999`

**R script:**

```{r harmo1}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  }
  bmi
}

CHARLS_w1_bmi$bmi <- compute_bmi(Heigth = CHARLS_w1_bmi$qi002, 
                        Weigth = CHARLS_w1_bmi$ql002, miss = c(993), 
                        heigth_m = FALSE)

CHARLS_ds_w1 <- tibble(id=CHARLS_w1_bmi$id)
CHARLS_ds_w1$bmi <- car::recode(CHARLS_w1_bmi$bmi, "NA=999")
CHARLS_ds_w1$bmi <- labelled(CHARLS_ds_w1$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are some unusual values:
```{r crosstabulation1, echo=FALSE}
tt <- CHARLS_w1_bmi[which(CHARLS_w1_bmi$bmi<13 | CHARLS_w1_bmi$bmi>75 & CHARLS_w1_bmi$bmi<900 | CHARLS_w1_bmi$bmi>999),]
names(tt) <- c("id", "old_id", "Height", "Weight", "bmi")
kable(tt)
```






### CHARLS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ql002`
* Label: `Weight Measuremen`
* Type of variable: `countinous`
* Name: `qi002`
* Label: `Height`
* Type of variable: `countinous`


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_bmi2','CHARLS.Biomarker_wave2',
                         variables=list('ql002', 'qi002'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=FALSE}
CHARLS_w2_bmi2 <- opal.execute(o,'CHARLS_w2_bmi2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, ncol = dim(old)[2] , nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], qi002=as.numeric(new_2[,2]), ql002=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_bmi <- Add_indiv(old = CHARLS_w2_bmi2, new = CHARLS_w2_id)


vari <- CHARLS_w2_bmi$ql002
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_bmi, aes(ql002)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency")

vari <- CHARLS_w2_bmi$qi002
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_bmi, aes(qi002)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `keep 993 into 993`
* `NA into 999`

**R script:**

```{r harmo2}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  }
  bmi
}

CHARLS_w2_bmi$bmi <- compute_bmi(Heigth = CHARLS_w2_bmi$qi002, 
                        Weigth = CHARLS_w2_bmi$ql002, miss = c(993), 
                        heigth_m = FALSE)

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_bmi$id)
CHARLS_ds_w2$bmi <- car::recode(CHARLS_w2_bmi$bmi, "NA=999")
CHARLS_ds_w2$bmi <- labelled(CHARLS_ds_w2$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are unusual values:
```{r crosstabulation2, echo=FALSE}
tt <- CHARLS_w2_bmi[which(CHARLS_w2_bmi$bmi<13 | CHARLS_w2_bmi$bmi>75 & CHARLS_w2_bmi$bmi<900 | CHARLS_w2_bmi$bmi>999),]
names(tt) <- c("id", "Height", "Weight", "bmi")
kable(tt)

```

# Quality control
No comments.


```{r save, echo=FALSE}
bmi <- CHARLS_ds_w1
save(bmi, file = "../RData/w1/bmi.RData")
rm(bmi)

bmi <- CHARLS_ds_w2
save(bmi, file = "../RData/w2/bmi.RData")
rm(bmi)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



