---
title: "Obesity"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:

* Name: `obesity`
* Label: `Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2.`
* Type of variable: `categorical`
* Categories: 
    + `0 = not obese`
    + `1 = obese`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `the BMI variable should be created by dividing weight and hiegh variables by means of the following equation= weight (kg)/height(m)^2. Then, the Obesity variable should be generated according to the WHO cutoff point for BMI classification.`



```{r lab, echo=FALSE}
ds_label <- "obesity"
ds_label_all <- "Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2"
```

# Data process

## CHARLS

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `bmi`
* Label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Type of variable: `countinous`
* Missings
   + `NA` 

```{r read1, echo=FALSE}
load("../RData/w1/bmi.RData")
CHARLS_obe <- bmi
#opal.assign.table.tibble(o, 'CHARLS_obe','_Athlos_Harm_Dataset.CHARLS_m_ds_w1', variables=list('bmi'), missings = TRUE)
#CHARLS_obe <- opal.execute(o,'CHARLS_obe')
CHARLS_obe[[2]] <- as.numeric(CHARLS_obe[[2]])
```

```{r local11, echo=FALSE}
vari <- CHARLS_obe[[2]]
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_obe, aes(x=factor(CHARLS_obe[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**

```{r harmo11}
CHARLS_ds_w1 <- tibble(id=CHARLS_obe$id)
CHARLS_ds_w1$obesity <- car::recode(CHARLS_obe[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
CHARLS_ds_w1$obesity <- labelled(CHARLS_ds_w1[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=FALSE}
vari <- CHARLS_ds_w1$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(x=factor(CHARLS_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab11, echo=FALSE}
BeforeH <- c(sum(na.omit(CHARLS_obe[[2]])<30),sum(na.omit(CHARLS_obe[[2]])>=30), sum(is.na(CHARLS_obe[[2]])))
AfterH <- table(CHARLS_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```



```{r read, echo=FALSE}
rm(CHARLS_obe)
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `bmi`
* Label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Type of variable: `countinous`
* Missings
   + `NA` 

```{r read2, echo=FALSE}
load("../RData/w2/bmi.RData")
CHARLS_obe <- bmi
#opal.assign.table.tibble(o, 'CHARLS_obe','_Athlos_Harm_Dataset.CHARLS_m_ds_w2', variables=list('bmi'), missings = TRUE)
#CHARLS_obe <- opal.execute(o,'CHARLS_obe')
CHARLS_obe[[2]] <- as.numeric(CHARLS_obe[[2]])
```

```{r local2, echo=FALSE}
vari <- CHARLS_obe[[2]]
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_obe, aes(x=factor(CHARLS_obe[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_obe$id)
CHARLS_ds_w2$obesity <- car::recode(CHARLS_obe[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
CHARLS_ds_w2$obesity <- labelled(CHARLS_ds_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$obesity
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(x=factor(CHARLS_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=FALSE}
BeforeH <- c(sum(na.omit(CHARLS_obe[[2]])<30),sum(na.omit(CHARLS_obe[[2]])>=30), sum(is.na(CHARLS_obe[[2]])))
AfterH <- table(CHARLS_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE}
CHARLS_m_ds_w1   <- CHARLS_ds_w1
CHARLS_m_ds_w2   <- CHARLS_ds_w2

l.hds <- list(CHARLS_ds_w1 = CHARLS_ds_w1 , CHARLS_ds_w2 = CHARLS_ds_w2)

m.hds <- list(CHARLS_m_ds_w1 = CHARLS_m_ds_w1 , CHARLS_m_ds_w2 = CHARLS_m_ds_w2)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label_all # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1))

 

}

```


### Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ, echo=FALSE}

# Table HRS
t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]))
names(t.hds)<-c("val", "label", "Wave1", "Wave2")
kable(t.hds)
```

# Quality control
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.

```{r save, echo=FALSE}
obesity <- CHARLS_ds_w1
save(obesity, file = "../RData/w1/obesity.RData")
rm(obesity)

obesity <- CHARLS_ds_w2
save(obesity, file = "../RData/w2/obesity.RData")
rm(obesity)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



