---
title: "Waist"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `waist`
* Label: `waist circumference of the participant`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `Antropomeric measure for waist circumference should be measured in centimeters.`

```{r lab, echo=FALSE}
ds_label <- "waist"
ds_label_all <- "waist circumference of the participant in centimeters"
```

# Data process

## CHARLS

### Wave 1 

The study-specific variable elected to be harmonised is:

* Name: `qm002`
* Label: `Waist Measurement`
* Type of variable: `countinous`
* Missings
   + `993 = R tried but was unable to do it`
   + `999 = R chose not to do it`

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_waist2','CHARLS.biomarkers_wave1',
                         variables=list('qm002'), missings = TRUE)
CHARLS_w1_waist2 <- opal.execute(o,'CHARLS_w1_waist2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_waist2$oldid <- CHARLS_w1_waist2$id
CHARLS_w1_waist2$id <- CHARLS_ids(ids = CHARLS_w1_waist2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), qm002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_waist <- Add_indiv(old = CHARLS_w1_waist2, new = CHARLS_w1_id)

```

```{r local1, echo=FALSE}
vari <- CHARLS_w1_waist$qm002
kable(Continuous_summary(var = vari, missing_values = c(993, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(993, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(993, 999))$summary, caption = "Summary")
ggplot(CHARLS_w1_waist, aes(qm002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `keep "R tried but was unable to do it" into 993`
* `999 into 997`
* `NA into 999`


**R script:**

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_waist$id)
CHARLS_ds_w1$waist <- car::recode(CHARLS_w1_waist$qm002, "NA=999; 999=997")
CHARLS_ds_w1$waist <- labelled(CHARLS_ds_w1$waist, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$waist
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(waist)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `qm002`
* Label: `Waist Circumference`
* Type of variable: `countinous`
* Missings
   + `993 = R tried but was unable to do it`
   + `999 = R chose not to do it`


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_waist2','CHARLS.Biomarker_wave2',
                         variables=list('qm002'), missings = TRUE)
CHARLS_w2_waist2 <- opal.execute(o,'CHARLS_w2_waist2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], qm002=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_waist <- Add_indiv(old = CHARLS_w2_waist2, new = CHARLS_w2_id)
```

```{r local2, echo=FALSE}
vari <- CHARLS_w2_waist$qm002
kable(Continuous_summary(var = vari, missing_values = c(993, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(993, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(993, 999))$summary, caption = "Summary")
ggplot(CHARLS_w2_waist, aes(qm002)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency")
```

There are some individuals with waist values 993 that are going to be considered as mistakes and they will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `keep "R tried but was unable to do it" into 993`
* `999 into 997`
* `NA into 999`


**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_waist$id)
CHARLS_ds_w2$waist <- car::recode(CHARLS_w2_waist$qm002, "NA=999; 999=997")
CHARLS_ds_w2$waist <- labelled(CHARLS_ds_w2$waist, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$waist
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(waist)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```


#### Quality estimation
No coments.





```{r save, echo=FALSE}
waist <- CHARLS_ds_w1
save(waist, file = "../RData/w1/waist.RData")
rm(waist)

waist <- CHARLS_ds_w2
save(waist, file = "../RData/w2/waist.RData")
rm(waist)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



