---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```


# Data process


## England

### Wave 1 

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_1_core_data_v3` | `wave_1_core_data_v3` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1','ELSA.wave_1_core_data_v3', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')
```

```{r local w1, echo=F}
vbl <- ELSA_w1$heskb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heskb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$heskc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heskc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

**R script:**

```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
# All individuals have the same missing values for both variables.
ELSA_ds_w1$n_cigarettes <- car::recode((ELSA_w1$heskb*5+ELSA_w1$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ELSA_ds_w1$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```





### Wave 2

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_2_core_data_v4` | `wave_2_core_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_core_data_v4', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')
```

```{r local w2, echo=F}
vbl <- ELSA_w2$HeSkb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$HeSkc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
# All individuals have the same missing values for both variables, but there is an individual whose answer to HeSkb is 13 and that has missing value -8 in HeSkc. 
ELSA_ds_w2$n_cigarettes <- car::recode((ELSA_w2$HeSkb*5+ELSA_w2$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
ELSA_ds_w2$n_cigarettes[which(ELSA_w2$HeSkc==-8)] <- 998

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- ELSA_ds_w2$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
```





### Wave 3

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')
```

```{r local w3, echo=F}
vbl <- ELSA_w3$heskb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heskb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$heskc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heskc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
# All individuals have the same missing values for both variables, but there is an individual whose answer to heskb is 25 and that has missing value -8 in heskc. 
ELSA_ds_w3$n_cigarettes <- car::recode((ELSA_w3$heskb*5+ELSA_w3$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
ELSA_ds_w3$n_cigarettes[which(ELSA_w3$heskc==-8)] <- 998
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ELSA_ds_w3$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
```





### Wave 4 

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_4_elsa_data_v3` | `wave_4_elsa_data_v3` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` | `-1 = Not applicable` <br/> `-8 = Don't Know` |
| **Description** |  | |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')
```

```{r local w4, echo=F}
vbl <- ELSA_w4$heskb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heskb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$heskc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heskc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
# All individuals have the same missing values for both variables.
ELSA_ds_w4$n_cigarettes <- car::recode((ELSA_w4$heskb*5+ELSA_w4$heskc*2), "-1*7 = 996;-8*7 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ELSA_ds_w4$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_5_elsa_data_v4` | `wave_5_elsa_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')
```

```{r local w5, echo=F}
vbl <- ELSA_w5$heskb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heskb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$heskc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heskc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
# All individuals have the same missing values for both variables.
ELSA_ds_w5$n_cigarettes <- car::recode((ELSA_w5$heskb*5+ELSA_w5$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ELSA_ds_w5$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` | `-1 = Not applicable` <br/> `-8 = Don't Know` |
| **Description** |  | |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_elsa_data_v2', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')
```

```{r local w6, echo=F}
vbl <- ELSA_w6$HeSkb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$HeSkc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
# All individuals have the same missing values for both variables, but there is an individual whose answer to HeSkc is 0 and that has missing value -8 in HeSkb. 
ELSA_ds_w6$n_cigarettes <- car::recode((ELSA_w6$HeSkb*5+ELSA_w6$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997; -8*5 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ELSA_ds_w6$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `Number of cigarettes smoke per weekday` | `Number of cigarettes smoke per weekend day` |
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local w7, echo=F}
vbl <- ELSA_w7$HeSkb
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$HeSkc
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
# All individuals have the same missing values for both variables, but there is an individual whose answer to HeSkb is 0 and that has missing value -8 in HeSkc, and another whose answer to HeSkc is 10 and that has missing value -8 in HeSkb
ELSA_ds_w7$n_cigarettes <- car::recode((ELSA_w7$HeSkb*5+ELSA_w7$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ; -8*2 = 998")
ELSA_ds_w7$n_cigarettes[which(ELSA_w7$HeSkb==-8)] <- 998
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ELSA_ds_w7$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name="n_cigarettes")
}



```



# Quality estimation
[Comments on the quality of the new harmonised variable.]

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
