---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```


# Data process


## England

### Wave 1 

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_1_core_data_v3` | `wave_1_core_data_v3` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1','ELSA.wave_1_core_data_v3', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')
```

```{r local w1, echo=F}
vbl <- ELSA_w1$heskb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heskb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,62)

vbl <- ELSA_w1$heskc
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ELSA_w1, aes(heskc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,52)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

**R script:**

```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$n_cigarettes <- car::recode((ELSA_w1$heskb*5+ELSA_w1$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ELSA_ds_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,410) 
```

#### Validation
```{r crosstabulation w1, echo=F}
```





### Wave 2

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_2_core_data_v4` | `wave_2_core_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_core_data_v4', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')
```

```{r local w2, echo=F}
vbl <- ELSA_w2$HeSkb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,62)

vbl <- ELSA_w2$HeSkc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w2, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,62)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$n_cigarettes <- car::recode((ELSA_w2$HeSkb*5+ELSA_w2$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- ELSA_ds_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,380) 
```

#### Validation
```{r crosstabulation w2, echo=F}
```





### Wave 3

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')
```

```{r local w3, echo=F}
vbl <- ELSA_w3$heskb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heskb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,62)

vbl <- ELSA_w3$heskc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w3, aes(heskc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,62)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$n_cigarettes <- car::recode((ELSA_w3$heskb*5+ELSA_w3$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ELSA_ds_w3$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,430) 
```

#### Validation
```{r crosstabulation w3, echo=F}
```





### Wave 4 

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_4_elsa_data_v3` | `wave_4_elsa_data_v3` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` | `-1 = Not applicable` <br/> `-8 = Don't Know` |
| **Description** |  | |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')
```

```{r local w4, echo=F}
vbl <- ELSA_w4$heskb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heskb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,105)

vbl <- ELSA_w4$heskc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w4, aes(heskc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,145)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$n_cigarettes <- car::recode((ELSA_w4$heskb*5+ELSA_w4$heskc*2), "-1*7 = 996;-8*7 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ELSA_ds_w4$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,710) 
```

#### Validation
```{r crosstabulation w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `heskb` | `heskc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_5_elsa_data_v4` | `wave_5_elsa_data_v4` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4', variables=list('heskb','heskc'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')
```

```{r local w5, echo=F}
vbl <- ELSA_w5$heskb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heskb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,155)

vbl <- ELSA_w5$heskc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w5, aes(heskc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,82)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `heskb*5+heskc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$n_cigarettes <- car::recode((ELSA_w5$heskb*5+ELSA_w5$heskc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ELSA_ds_w5$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,880) 
```

#### Validation
```{r crosstabulation w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `About how many cigarettes a day do you usually smoke on weekdays?` | `About how many cigarettes a day do you usually smoke on weekends?` |
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` | `-1 = Not applicable` <br/> `-8 = Don't Know` |
| **Description** |  | |


```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_elsa_data_v2', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')
```

```{r local w6, echo=F}
vbl <- ELSA_w6$HeSkb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,82)

vbl <- ELSA_w6$HeSkc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w6, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,68)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$n_cigarettes <- car::recode((ELSA_w6$HeSkb*5+ELSA_w6$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ELSA_ds_w6$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,470) 
```

#### Validation
```{r crosstabulation w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `HeSkb` | `HeSkc` |
|-|-|-|
| **Label** | `Number of cigarettes smoke per weekday` | `Number of cigarettes smoke per weekend day` |
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories:**| `continuous`| `continuous`|
| **Missings:**| `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable` <br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  | |


```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('HeSkb','HeSkc'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local w7, echo=F}
vbl <- ELSA_w7$HeSkb
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeSkb)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,82)

vbl <- ELSA_w7$HeSkc
kable(Continuous_summary(vbl, missing_values = c(-1,-8,-9))[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w7, aes(HeSkc)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-.45,68)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `HeSkb*5+HeSkc*2` 
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`


**R script:**

```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$n_cigarettes <- car::recode((ELSA_w7$HeSkb*5+ELSA_w7$HeSkc*2), "-1*7 = 996;-8*7 = 998;-9*7 = 997 ")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ELSA_ds_w7$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,470) 
```

#### Validation
```{r crosstabulation w7, echo=F}
```



```{r final, echo=F}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
