---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```





# Data process




## England




### Wave 1

#### Study-specific variable description

| **Name** | `heala` |
|-|-|
| **Label** | `In the past 12 months have you taken an alcoholic drink .? {frequency}` |
| **Table name** | `wave_1_core_data_v3` |
| **Categories** |`1 =  ... twice a day or more,`<br/>`2 = daily or almost daily,`<br/>`3 = once or twice a week,`<br/>`4 = once or twice a month,`<br/>`5 = special occasions only,`<br/>`6 = or, not at all?`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o,'ELSA_w1','ELSA.wave_1_core_data_v3',variables=list('heala'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')

```

```{r local w1, echo=F}

vbl <- ELSA_w1$heala
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'heala')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(heala))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5 into 1`
* `6 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2 into 2`
* `3,4,5 into 1`
* `6 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w1}

ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$current_oh <- car::recode(ELSA_w1$heala, "c(1,2,3,4,5) = 1; c(6) = 0; -1 = 996; -8 = 998; -9 = 997")
ELSA_ds_w1$freq_oh <- car::recode(ELSA_w1$heala, "c(1,2) = 2; c(3,4,5) = 1; c(6) = 0; -1 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w1, echo=F}

```




### Wave 2

#### Study-specific variable description

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_2_core_data_v4` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Item not applicable`<br/>`-9 = Not answered`|
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o,'ELSA_w2','ELSA.wave_2_core_data_v4',variables=list('scako'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

```

```{r local w2, echo=F}

vbl <- ELSA_w2$scako
vbl_miss <- c(-1,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

**R script:**

```{r harmo w2}

ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$current_oh <- car::recode(ELSA_w2$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")
ELSA_ds_w2$freq_oh <- car::recode(ELSA_w2$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w2, echo=F}

```




### Wave 3

#### Study-specific variable description

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_3_elsa_data_v4` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Item not applicable`<br/>`-9 = Not answered`|
| **Description** |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o,'ELSA_w3','ELSA.wave_3_elsa_data_v4',variables=list('scako'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')

```

```{r local w3, echo=F}

vbl <- ELSA_w3$scako
vbl_miss <- c(-1,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

**R script:**

```{r harmo w3}

ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$current_oh <- car::recode(ELSA_w3$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")
ELSA_ds_w3$freq_oh <- car::recode(ELSA_w3$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w3$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w3, echo=F}

```




### Wave 4

#### Study-specific variable description

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_4_elsa_data_v3` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Not applicable`<br/>`-9 = Not answered`|
| **Description** |  |


```{r assign w4, echo=F}

opal.assign.table.tibble(o,'ELSA_w4','ELSA.wave_4_elsa_data_v3',variables=list('scako'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')

```

```{r local w4, echo=F}

vbl <- ELSA_w4$scako
vbl_miss <- c(-1,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1 into 996`
* `-9 into 995`

**R script:**

```{r harmo w4}

ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$current_oh <- car::recode(ELSA_w4$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")
ELSA_ds_w4$freq_oh <- car::recode(ELSA_w4$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; -1 = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w4$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w4, echo=F}

```




### Wave 5

#### Study-specific variable description

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_5_elsa_data_v4` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Item not applicable`<br/>`-2 = Schedule Not Applicable`<br/>`-9 = Not answered`|
| **Description** |  |


```{r assign w5, echo=F}

opal.assign.table.tibble(o,'ELSA_w5','ELSA.wave_5_elsa_data_v4',variables=list('scako'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')

```

```{r local w5, echo=F}

vbl <- ELSA_w5$scako
vbl_miss <- c(-1,-2,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

**R script:**

```{r harmo w5}

ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$current_oh <- car::recode(ELSA_w5$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")
ELSA_ds_w5$freq_oh <- car::recode(ELSA_w5$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w5$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w5, echo=F}

```




### Wave 6

#### Study-specific variable description

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_6_elsa_data_v2` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Item not applicable`<br/>`-2 = Schedule Not Applicable`<br/>`-9 = Not answered`|
| **Description** |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o,'ELSA_w6','ELSA.wave_6_elsa_data_v2',variables=list('scako'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')

```

```{r local w6, echo=F}

vbl <- ELSA_w6$scako
vbl_miss <- c(-1,-2,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

**R script:**

```{r harmo w6}

ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$current_oh <- car::recode(ELSA_w6$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")
ELSA_ds_w6$freq_oh <- car::recode(ELSA_w6$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w6$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w6, echo=F}

```





### Wave 7

| **Name** | `scako` |
|-|-|
| **Label** | `How often respondent has had an alcoholic drink during the last 12 months` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** |`1 = Almost every day`<br/>`2 = Five or six days a week`<br/>`3 = Three or four days a week`<br/>`4 = Once or twice a week`<br/>`5 = Once or twice a month`<br/>`6 = Once every couple of months`<br/>`7 = Once or twice a year`<br/>`8 = Not at all in the last 12 months`|
| **Missings** |`-1 = Item not applicable`<br/>`-2 = Schedule Not Applicable`<br/>`-9 = Not answered`|
| **Description** |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o,'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('scako'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=F}

vbl <- ELSA_w7$scako
vbl_miss <- c(-1,-2,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'scako')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(scako))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3,4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 2`
* `4,5,6,7 into 1`
* `8 into 0`
* `-1,-2 into 996`
* `-9 into 995`

**R script:**

```{r harmo w7}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$current_oh <- car::recode(ELSA_w7$scako, "c(1,2,3,4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")
ELSA_ds_w7$freq_oh <- car::recode(ELSA_w7$scako, "c(1,2,3) = 2; c(4,5,6,7) = 1; c(8) = 0; c(-1,-2) = 996; -9 = 995")

```

#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ELSA_ds_w7$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w7, echo=F}

```




```{r final, echo=F}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```






## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```







<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

* Past drinking cannot be harmonized.


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```



