---
title: "Level of Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/level_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/level_paDS.R')
```


# Data process


## England

### Wave 1 

Not found.



### Wave 2

#### Study-specific variable description

| **Name** | `palevel` |
|-|-|
| **Label** | `Physical activity summary` |
| **Table name** | `wave_2_derived_variables` |
| **Categories:**| `0 = Sedentary` <br/> `1 = Low` <br/> `2 = Moderate` <br/> `3 = High` |
| **Missings:**|  `-1 = Not applicable` <br/> `-6 = See INWAVE` <br/> `-8 = Not known`  |
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ELSA_w2_id','ELSA.wave_2_core_data_v4', variables=list('PersNo'), missings = TRUE)
ELSA_w2_id <- opal.execute(o,'ELSA_w2_id')

opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_derived_variables', variables=list('palevel'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

ELSA_w2 <- left_join(ELSA_w2_id,ELSA_w2, by="id")
```

```{r local w2, echo=F}

vbl <- ELSA_w2$palevel
kable(Categorical_summary(vbl, missing_values = c(-1,-6,-8))[3], caption = names(ELSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(-1,-6,-8))[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(palevel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 4`
* `1 into 3`
* `3 into 1`
* `-8 into 998`
* `-6 into 996`
* `-1 into 996`

**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$level_pa <- car::recode(ELSA_w2$palevel, "0 = 4;1 = 3;3 = 1;-8 = 998;-6 = 996;-1 = 996 ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- ELSA_ds_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
```




### Wave 3

#### Study-specific variable description

| **Name** | `palevel` |
|-|-|
| **Label** | `Physical activity summary` |
| **Table name** | `wave_3_elsa_data_v4` |
| **Categories:**| `0 = Sedentary` <br/> `1 = Low` <br/> `2 = Moderate` <br/> `3 = High` |
| **Missings:**|  `-8 = Not known`  |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('palevel'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')
```

```{r local w3, echo=F}
vbl <- ELSA_w3$palevel
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = names(ELSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(palevel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 4`
* `1 into 3`
* `3 into 1`
* `-8 into 998`

**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$level_pa <- car::recode(ELSA_w3$palevel, "0 = 4;1 = 3;3 = 1;-8 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ELSA_ds_w3$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
```




### Wave 4

#### Study-specific variable description

| **Name** | `palevel` |
|-|-|
| **Label** | `Physical activity summary` |
| **Table name** | `wave_4_elsa_data_v3` |
| **Categories:**| `0 = Sedentary` <br/> `1 = Low` <br/> `2 = Moderate` <br/> `3 = High` |
| **Missings:**|  `-8 = Not known`  |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3', variables=list('palevel'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')
```

```{r local w4, echo=F}
vbl <- ELSA_w4$palevel
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = names(ELSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(palevel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 4`
* `1 into 3`
* `3 into 1`
* `-8 into 998`

**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$level_pa <- car::recode(ELSA_w4$palevel, "0 = 4;3 = 1;1 = 3;-8 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ELSA_ds_w4$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `palevel` |
|-|-|
| **Label** | `Physical activity summary` |
| **Table name** | `wave_5_elsa_data_v4_modif_Laia` |
| **Categories:**| `0 = Sedentary` <br/> `1 = Low` <br/> `2 = Moderate` <br/> `3 = High` |
| **Missings:**| `-8 = Not known` |
| **Description** |  |


```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4_modif_Laia', variables=list('palevel'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')
```

```{r local w5, echo=F}
vbl <- ELSA_w5$palevel
kable(Categorical_summary(vbl, missing_values = c(-8))[3], caption = names(ELSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(palevel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 4`
* `1 into 3`
* `2 into 2`
* `3 into 1`
* `-8 into 998`

**R script:**

```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$level_pa <- car::recode(ELSA_w5$palevel, "0 = 4;3 = 1;1 = 3;-8 = 998 ")
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ELSA_ds_w5$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
```




### Wave 6

Not found

### Wave 7

Not found



```{r final, echo=F}

l.hds <- list(w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[15,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","level_pa")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","level_pa")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  level_pa <- l.hds[[index]]
  save(level_pa, file = paste0(datafolder,names(l.hds)[index],"/level_pa.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
