---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `c60` |`c61`|
|-|-|-|
| **Label** | `Drink now`|`How often drink`|
| **Table name**  | `MHAS-2001`| `MHAS-2001`|
| **Categories** | `1 = Yes`<br/>`2 = No`<br/>`3 = Never has used alcohol`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('c60','c61'), missings = T)
MHAS_w1 <- opal.execute(o,'MHAS_w1')

```

```{r local w1, echo=F}

vbl <- MHAS_w1$c60
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(c60))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$c61
vbl_miss <- c(8,9)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "c61") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w1, aes(x=factor(c61))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `c60` it has to be recoded as follows:

* `1 into 1`
* `2,3 into 0`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `c61` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3 to 7 into 2`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `past_oh` from the study-specific variable `c60` it has to be recoded as follows:

* `3 into 0`
* `2 into 1`
* `1 into 996`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$current_oh <- car::recode(MHAS_w1$c60, "c(2,3)=0; 8=995; 9=998; NA=999")
MHAS_ds_w1$freq_oh <- car::recode(MHAS_w1$c61, "c(1,2)=1; c(3,4,5,6,7)=2; 8=995; 9=998; NA=999")
MHAS_ds_w1$past_oh <- car::recode(MHAS_w1$c60, "c(3)=0; 2=1; 1=996; 8=995; 9=998; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- MHAS_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- MHAS_ds_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `c59a`|`c59b`|
|-|-|-|
| **Label** | `Currently drink alcohol`|`Days per week drank alcohol in last three months`|
| **Table name**  | `MHAS_2003`| `MHAS_2003`|
| **Categories** |`1 = Yes`<br/>`2 = No`<br/>`3 = Has never used alcohol`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know` | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` |
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('c59a','c59b'), missings = T)
MHAS_w2 <- opal.execute(o,'MHAS_w2')

```

```{r local w2, echo=F}

vbl <- MHAS_w2$c59a
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(c59a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$c59b
vbl_miss <- c(8,9)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "c59b") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w2, aes(x=factor(c59b))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `c59a` it has to be recoded as follows:

* `change 2,3 into 0`
* `keep up 1 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `c59b` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3 to 7 into 2`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `past_oh` from the study-specific variable `c59a` it has to be recoded as follows:

* `3 into 0`
* `1 into 996`
* `2 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

**R script:**


```{r harmo w2}

# Categorical variable harmonization
MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$current_oh <- car::recode(MHAS_w2$c59a, "c(2,3)=0; 8=995; 9=998; NA=999")
MHAS_ds_w2$freq_oh <- car::recode(MHAS_w2$c59b, "c(1,2)=1; c(3,4,5,6,7)=2; 8=995; 9=998; NA=999")
MHAS_ds_w2$past_oh <- car::recode(MHAS_w2$c59a, "c(3)=0; 1=996; 2=1; 8=995; 9=998; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- MHAS_ds_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- MHAS_ds_w2$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}


```



### Wave 3

#### Study-specific variable description

| **Name** | `c59a_12`|`c59b_12`|
|-|-|-|
| **Label** | `Respondent currently drinks alcohol`|`Last 3 months: Number of days per week he/she drank alcohol`|
| **Table name**  | `MHAS_2012_new`| `MHAS_2012_new`|
| **Categories** | `1 = Yes `<br/>`2 = No`<br/>`3 = Never drank alcohol`|`continuous`|
| **Missings** | `8 = RF`<br/>`9 = DK`<br/>`NA` |`8 = RF`<br/>`9 = DK`<br/>`NA` |
| **Description** |  |  |



```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('c59a_12','c59b_12'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3')

```

```{r local w3, echo=F}

vbl <- MHAS_w3$c59a_12
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(c59a_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$c59b_12
vbl_miss <- c(8,9)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "c59b_12") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w3, aes(x=factor(c59b_12))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `c59a_12` it has to be recoded as follows:

* `change 2,3 into 0`
* `keep up 1 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `c59b_12` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3 to 7 into 2`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `past_oh` from the study-specific variable `c59a_12` it has to be recoded as follows:

* `3 into 0`
* `1 into 996`
* `2 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$current_oh <- car::recode(MHAS_w3$c59a_12, "c(2,3)=0; 8=995; 9=998; NA=999")
MHAS_ds_w3$freq_oh <- car::recode(MHAS_w3$c59b_12, "c(1,2)=1; c(3,4,5,6,7)=2; 8=995; 9=998; NA=999")
MHAS_ds_w3$past_oh <- car::recode(MHAS_w3$c59a_12, "c(3)=0; 1 = 996; 2=1; 8=995; 9=998; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- MHAS_ds_w3$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- MHAS_ds_w3$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

```


```{r final, echo=F}

l.hds <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  label(l.hds[[name]][[4]]) <- label(aux_object[[4]]) <- ds_label_past # Text value assigned at the DS description, at the top
  l.hds[[name]][[4]] <- labelled(l.hds[[name]][[4]], labels = cat_label)
  aux_object[[4]] <- car::recode(aux_object[[4]], "miss_values_vector=NA")
  aux_object[[4]] <- labelled(aux_object[[4]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```


## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ curr}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```




## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```





## Summary of descriptive statistics of the harmonised variable `past_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ past}

t.hds <- frq(l.hds[[1]][4])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][4])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","past_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","past_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```





# Quality estimation

To harmonize `past_oh` we use the variables `c60`, `c59a` and `c59a_12` taking into account: 

* the questionaire instruction: `Even if the respondent drinks only one or two alcoholic beverages per year (in special occasions, for instance) mark YES.`
* and that if an individual is current drinker is codified as not applicable since we do not know its past-drinking condition.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





