---
title: "Arterial hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ah`
* Variable label: `Arterial hypertension`
* Variable description: `Arterial hypertension. Means of all diastolic blood pressure measures.`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no hypertension
1        | hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Arterial hypertension"
ds_label_all <- "Arterial hypertension. Means of all diastolic blood pressure measures."
```

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `c4`
* Label: `Hypertension`
* Type of variable: `Categorical`
* Categories: 
    + `1 = Yes`
    + `2 = no`
* Missings
    + `8 = Doesn't answer`
    + `9 = Doesn't know`


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_ah','Mexican Health Aging Study.MHAS-2001',
                         variables=list('c4'), missings = TRUE)
MHAS_ah <- opal.execute(o,'MHAS_ah')
```

```{r local1, echo=FALSE}
vari <- MHAS_ah$c4
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_ah, aes(x=factor(c4))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 2 "no" into 0`
* `recode 8 "Doesn't answer" into 995`
* `recode 9 "Doesn't know" into 998`
* `NA as 999`

R code of the ALGORITHM:

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_ah$id)
MHAS_ds_w1$ah <- car::recode(MHAS_ah$c4, "2=0; 8=995; 9=998; NA=999")
MHAS_ds_w1$ah <- labelled(MHAS_ds_w1$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- MHAS_ds_w1$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(MHAS_ah$c4, useNA = 'ifany')[c(2,1,3:5)]
AfterH <- table(MHAS_ds_w1$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "8->995", "9->998", "NA->999")
kable(C)
```

```{r importOPAL1, echo=FALSE}
#val_labels(MHAS_ds_w1) <- NULL
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
label(MHAS_ds_w1$ah) <- ds_label_all
ah <- MHAS_ds_w1
save(ah, file = "../RData/w1/ah.RData")
rm(ah)
```





### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `c4`
* Label: `Hypertension`
* Type of variable: `Categorical`
* Categories: 
    + `1 = Yes`
    + `2 = no`
* Missings
    + `8 = Doesn't answer`
    + `9 = Doesn't know`


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_ah','Mexican Health Aging Study.MHAS_2003',
                         variables=list('c4'), missings = TRUE)
MHAS_ah <- opal.execute(o,'MHAS_ah')
```

```{r local2, echo=FALSE}
vari <- MHAS_ah$c4
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_ah, aes(x=factor(c4))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 2 "no" into 0`
* `recode 8 "Doesn't answer" into 995`
* `recode 9 "Doesn't know" into 998`
* `NA as 999`
 
**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_ah$id)
MHAS_ds_w2$ah <- car::recode(MHAS_ah$c4, "2=0; 8=995; 9=998; NA=999")
MHAS_ds_w2$ah <- labelled(MHAS_ds_w2$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- MHAS_ds_w2$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(MHAS_ah$c4, useNA = 'ifany')[c(2,1,3)]
AfterH <- table(MHAS_ds_w2$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "9->998")
kable(C)
```

```{r importOPAL2, echo=FALSE}
#val_labels(MHAS_ds_w2) <- NULL
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
label(MHAS_ds_w2$ah) <- ds_label_all
ah <- MHAS_ds_w2
save(ah, file = "../RData/w2/ah.RData")
rm(ah)
```






### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `c4`
* Label: `Hypertension`
* Type of variable: `Categorical`
* Categories: 
    + `1 = Yes`
    + `2 = no`
* Missings
    + `8 = Doesn't answer`
    + `9 = Doesn't know`


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_ah','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('c4_12'), missings = TRUE)
MHAS_ah <- opal.execute(o,'MHAS_ah')
```

```{r local3, echo=FALSE}
vari <- MHAS_ah$c4_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_ah, aes(x=factor(c4_12))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```


#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 2 "no" into 0`
* `recode 8 "Doesn't answer" into 995`
* `recode 9 "Doesn't know" into 998`
* `NA as 999`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_ah$id)
MHAS_ds_w3$ah <- car::recode(MHAS_ah$c4_12, "2=0; 8=995; 9=998; NA=999")
MHAS_ds_w3$ah <- labelled(MHAS_ds_w3$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- MHAS_ds_w3$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(MHAS_ah$c4_12, useNA = 'ifany')[c(2,1,3:5)]
AfterH <- table(MHAS_ds_w3$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "8->995", "9->998", "NA->999")
kable(C)
```

```{r importOPAL3, echo=FALSE}
#val_labels(MHAS_ds_w3) <- NULL
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')

label(MHAS_ds_w3$ah) <- ds_label_all
ah <- MHAS_ds_w3
save(ah, file = "../RData/w3/ah.RData")
rm(ah)
```


# Quality estimation

The variable chosen (c4) to harmonized arterial hypertension as a physical 
measure doesn't fit in the definition of the variable, but it was decided to 
take it is better than nothing.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

