---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightDS.R')
```

# Data process

## Mexico


### Wave 1 

#### Study-specific variable description



| **Name** |`c71`|
|-|-|
| **Label** |`Weight`|
| **Table name** |`MHAS-2001`|
| **Units** |`kg`|
| **Missings** |`888 = Doesn't answer`<br/>`999 = Doesn't know`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',
                         variables=list('c71'), missings = TRUE)
MHAS_w1 <- opal.execute(o,'MHAS_w1')
```

```{r local1, echo=F}
vbl <- MHAS_w1$c71
vbl_miss <- c(888,999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "c71")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w1, aes(c71)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$weight <- car::recode(MHAS_w1$c71, "888=995; 999=998; NA=999")
MHAS_ds_w1$weight <- labelled(MHAS_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- MHAS_ds_w1$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```





### Wave 2 

#### Study-specific variable description



| **Name** |`c66`|
|-|-|
| **Label** |`Weight`|
| **Table name** |`MHAS_2003`|
| **Units** |`kg`|
| **Missings** |`888 = Doesn't answer`<br/>`999 = Doesn't know`|
| **Description** |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',
                         variables=list('c66'), missings = TRUE)
MHAS_w2 <- opal.execute(o,'MHAS_w2')
```

```{r local2, echo=F}
vbl <- MHAS_w2$c66
vbl_miss <- c(888,999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "c66")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w2, aes(c66)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`
 

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$weight <- car::recode(MHAS_w2$c66, "888=995; 999=998; NA=999")
MHAS_ds_w2$weight <- labelled(MHAS_ds_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vbl <- MHAS_ds_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation

```{r crosstabulation2, echo=F}
kable(MHAS_w2[which(MHAS_w2$c66<30),], caption = 'There is an unusual value that is lower than 30:')
```







### Wave 3 

#### Study-specific variable description


| **Name** |`peso1_12`|`peso2_12`|
|-|-|-|
| **Label** |`Weight - first measurement`|`Weight - second measurement`|
| **Table name** |`MHAS_2012_new`|`MHAS_2012_new`|
| **Units** |`kg`|`kg`|
| **Missings** |`995.0 = Tried, but could not do 995.0`<br/>`996.0 = Did not try 996.0`<br/>`997.0 = Cannot stand 997.0`<br/>`999.0 = Refused to provide 999.0`|`995.0 = Tried, but could not do 995.0`<br/>`996.0 = Did not try 996.0`<br/>`997.0 = Cannot stand 997.0`<br/>`999.0 = Refused to provide 999.0`|
| **Description** |  |  |





```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('peso1_12', 'peso2_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
```

```{r local3, echo=F}
vbl <- MHAS_w3$peso1_12
vbl_miss <- c(995, 996, 997, 999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "peso1_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w3, aes(peso1_12)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 

vbl <- MHAS_w3$peso2_12
vbl_miss <- c(995, 996, 997, 999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "peso2_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(MHAS_w3, aes(peso2_12)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 

```

```{r, echo=FALSE}
cat(paste("The individuals with no missing data are",sum(complete.cases(MHAS_w3[,1:3]))))

kable(table(MHAS_w3$peso1_12[which(MHAS_w3$peso1_12 %in% c(vbl_miss,NA))],MHAS_w3$peso2_12[which(MHAS_w3$peso2_12 %in% c(vbl_miss,NA))], useNA = "ifany"), caption = 'Cross tabulation of missing values')
```


#### Harmonisation algorithm
The harmonized variable is the mean value between the first and second measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `recode 995 "Tried, but could not do 995.0" into 993`
* `recode 996 "Did not try 996.0" into 994`
* `recode 997 "Cannot stand 997.0" into 993`
* `recode 999 "Refused to provide 999.0" into 997`
* `NA as 999`

**R script:**

```{r harmo3}
MHAS_w3$mean_peso <- apply(X = MHAS_w3[,c(2,3)], MARGIN = 1, FUN = mean, na.rm = T)
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$weight <- car::recode(MHAS_w3$mean_peso, "995=993; 996=994; 997=993; 999=997; NA=999")
MHAS_ds_w3$weight <- labelled(MHAS_ds_w3$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vbl <- MHAS_ds_w3$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(weight)) + geom_histogram(stat="bin", binwidth = 0.1, fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}
```











## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation
Self reported weight.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

