---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `height of the participant`
* Variable description: `Anthropometric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### MHAS - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `c72`
* Label: `Height`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`


```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_heig','Mexican Health Aging Study.MHAS-2001',
                         variables=list('c72'), missings = TRUE)
```

```{r local1}
MHAS_w1_heig <- opal.execute(o,'MHAS_w1_heig')
Continuous_summary(var = MHAS_w1_heig$c72, missing_values = c(888,999))
ggplot(MHAS_w1_heig, aes(c72)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

There are values larger than 915 that are going to be considered as mistakes and They will be recoded as 999.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`

R code of the ALGORITHM:

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_heig$id)
MHAS_ds_w1$height <- car::recode(MHAS_w1_heig$c72, "NA=999; 915:992=999; 888=995; 999=998 ")
MHAS_ds_w1$height <- labelled(MHAS_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = MHAS_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation

```{r crosstabulation1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL1}
#val_labels(MHAS_ds_w1) <- NULL
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
height <- MHAS_ds_w1
save(height, file = "../RData/w1/height.RData")
rm(height)
```







### MHAS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `c67`
* Label: `Height without shoes`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`


```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_heig','Mexican Health Aging Study.MHAS_2003',
                         variables=list('c67'), missings = TRUE)
```

```{r local2}
MHAS_w2_heig <- opal.execute(o,'MHAS_w2_heig')
Continuous_summary(var = MHAS_w2_heig$c67, missing_values = c(888,999))
ggplot(MHAS_w2_heig, aes(c67)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

There is a value 20 that is going to be considered as a mistake, it will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`
 

R code of the ALGORITHM:

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_heig$id)
MHAS_ds_w2$height <- car::recode(MHAS_w2_heig$c67, "888=995; 999=998; NA=999")
MHAS_ds_w2$height <- labelled(MHAS_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = MHAS_ds_w2$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation2}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL2}
#val_labels(MHAS_ds_w2) <- NULL
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
height <- MHAS_ds_w2
save(height, file = "../RData/w2/height.RData")
rm(height)
```







### MHAS - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `estatu1_12`
* Label: `Height - first measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`
* Name: `estatu2_12`
* Label: `Weight - second measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`


```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_heig','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('estatu1_12', 'estatu2_12'), missings = TRUE)
```

```{r local3}
MHAS_w3_heig <- opal.execute(o,'MHAS_w3_heig')
Continuous_summary(var = MHAS_w3_heig$estatu1_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_heig, aes(estatu1_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
Continuous_summary(var = MHAS_w3_heig$estatu2_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_heig, aes(estatu2_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")

sum(complete.cases(MHAS_w3_heig[,1:3]))
```


#### Harmonisation algorithm
The harmonized variable is the mean value between the first and second measurement of the study-specific variables, but the missing values have to be recoded as follows:

* `recode 995 "Tried, but could not do 995.0" into 993`
* `recode 996 "Did not try 996.0" into 994`
* `recode 997 "Cannot stand 997.0" into 993`
* `recode 999 "Refused to provide 999.0" into 997`
* `NA as 999`

R code of the ALGORITHM:

```{r harmo3}
MHAS_w3_heig$mean_estatu <- apply(X = MHAS_w3_heig[,c(2,3)], MARGIN = 1, FUN = mean)

MHAS_ds_w3 <- tibble(id=MHAS_w3_heig$id)
MHAS_ds_w3$height <- car::recode(MHAS_w3_heig$mean_estatu, "995=993; 996=994; 997=993; 999=997; NA=999")
MHAS_ds_w3$height <- labelled(MHAS_ds_w3$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = MHAS_ds_w3$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,200) 
```

#### Validation
```{r crosstabulation3}
```

#### Quality estimation
Anthropometric Measure.

#### Import to OPAL
```{r importOPAL3}
#val_labels(MHAS_ds_w3) <- NULL
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
height <- MHAS_ds_w3
save(height, file = "../RData/w3/height.RData")
rm(height)
```
