---
title: "BMI"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `bmi`
* Variable label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Variable description: `the BMI variable should be created by dividing weight and height variables with the following equation= weight (kg)/height(m)^2`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process



```{r lab, echo=FALSE}
ds_label <- "Body Mass Index calculated as weight (kg)/height(m)^2"
```


## Mexico

### MHAS - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `c71`
* Label: `Weight`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`

* Name: `c72`
* Label: `Height`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`


```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_bmi','Mexican Health Aging Study.MHAS-2001',
                         variables=list('c71', 'c72'), missings = TRUE)
```

```{r local1}
MHAS_w1_bmi <- opal.execute(o,'MHAS_w1_bmi')

Continuous_summary(var = MHAS_w1_bmi$c71, missing_values = c(888,999))
ggplot(MHAS_w1_bmi, aes(c71)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,180)

Continuous_summary(var = MHAS_w1_bmi$c72, missing_values = c(888,999))
ggplot(MHAS_w1_bmi, aes(c72)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)

```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`

R code of the ALGORITHM:

```{r harmo1}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=9999")
  Weigth <- car::recode(Weigth, "NA=9999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  }
  bmi
}

MHAS_w1_bmi$c72_2 <- car::recode(MHAS_w1_bmi$c72, "915:992=999")

MHAS_w1_bmi$bmi <- compute_bmi(Heigth = MHAS_w1_bmi$c72_2, 
                        Weigth = MHAS_w1_bmi$c71, miss = c(888,999), 
                        heigth_m = FALSE)


MHAS_ds_w1 <- tibble(id=MHAS_w1_bmi$id)
MHAS_ds_w1$bmi <- car::recode(MHAS_w1_bmi$bmi, "888=995; 999=998; 9999=999")
MHAS_ds_w1$bmi <- labelled(MHAS_ds_w1$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = MHAS_ds_w1$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are some unusual values that are lower than 13 and higger than 70:
```{r crosstabulation1}
MHAS_w1_bmi[which(MHAS_w1_bmi$bmi<13 | (MHAS_w1_bmi$bmi>70 & MHAS_w1_bmi$bmi<887)),]
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]




### MHAS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `c66`
* Label: `Weight`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`

* Name: `c67`
* Label: `Height without shoes`
* Type of variable: `countinous`
* Missings
    + `888 = Doesn't answer`
    + `999 = Doesn't know`

```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_bmi','Mexican Health Aging Study.MHAS_2003',
                         variables=list('c66', 'c67'), missings = TRUE)
```

```{r local2}
MHAS_w2_bmi <- opal.execute(o,'MHAS_w2_bmi')
Continuous_summary(var = MHAS_w2_bmi$c66, missing_values = c(888,999))
ggplot(MHAS_w2_bmi, aes(c66)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(20,180)

Continuous_summary(var = MHAS_w2_bmi$c67, missing_values = c(888,999))
ggplot(MHAS_w2_bmi, aes(c67)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)
```

There is a individual with weigth value 20 that is going to be considered as a mistake, it will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `recode 888 "Doesn't answer" into 995`
* `recode 999 "Doesn't know" into 998`
* `NA as 999`
 

R code of the ALGORITHM:

```{r harmo2}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=9999")
  Weigth <- car::recode(Weigth, "NA=9999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  }
  bmi
}

MHAS_w2_bmi$c66 <- car::recode(MHAS_w2_bmi$c66 , "20=999")

MHAS_w2_bmi$bmi <- compute_bmi(Heigth = MHAS_w2_bmi$c67, 
                        Weigth = MHAS_w2_bmi$c66, miss = c(888,999), 
                        heigth_m = FALSE)


MHAS_ds_w2 <- tibble(id=MHAS_w2_bmi$id)
MHAS_ds_w2$bmi <- car::recode(MHAS_w2_bmi$bmi, "888=995; 999=998; 9999=999")
MHAS_ds_w2$bmi <- labelled(MHAS_ds_w2$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = MHAS_ds_w2$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
 ggplot(MHAS_ds_w2, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are some unusual values that are lower than 13 and higger than 70:
```{r crosstabulation2}
MHAS_w2_bmi[which(MHAS_w2_bmi$bmi<13 | (MHAS_w2_bmi$bmi>70 & MHAS_w2_bmi$bmi<887)),]
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]





### MHAS - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `peso1_12`
* Label: `Weight - first measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`
* Name: `peso2_12`
* Label: `Weight - second measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`
    
* Name: `estatu1_12`
* Label: `Height - first measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`
* Name: `estatu2_12`
* Label: `Weight - second measurement`
* Type of variable: `countinous`
* Missings
    + `995.0 = Tried, but could not do 995.0`
    + `996.0 = Did not try 996.0`
    + `997.0 = Cannot stand 997.0`
    + `999.0 = Refused to provide 999.0`


```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_bmi','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('peso1_12', 'peso2_12', 'estatu1_12', 'estatu2_12'), missings = TRUE)
```

```{r local3}
MHAS_w3_bmi <- opal.execute(o,'MHAS_w3_bmi')

Continuous_summary(var = MHAS_w3_bmi$peso1_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_bmi, aes(peso1_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,150)
Continuous_summary(var = MHAS_w3_bmi$peso2_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_bmi, aes(peso2_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(30,150)

Continuous_summary(var = MHAS_w3_bmi$estatu1_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_bmi, aes(estatu1_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
Continuous_summary(var = MHAS_w3_bmi$estatu2_12, missing_values = c(995, 996, 997, 999))
ggplot(MHAS_w3_bmi, aes(estatu2_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `recode 995 "Tried, but could not do 995.0" into 993`
* `recode 996 "Did not try 996.0" into 994`
* `recode 997 "Cannot stand 997.0" into 993`
* `recode 999 "Refused to provide 999.0" into 997`
* `NA as 999`

R code of the ALGORITHM:

```{r harmo3}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=9999")
  Weigth <- car::recode(Weigth, "NA=9999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    bmi[Heigth==miss[4]] <- Heigth[Heigth==miss[4]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    bmi[Heigth==miss[4]] <- Heigth[Heigth==miss[4]]
    
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==9999] <- 9999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    bmi[Heigth==miss[4]] <- Heigth[Heigth==miss[4]]
    
    bmi[Weigth==9999] <- 9999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    bmi[Heigth==miss[4]] <- Heigth[Heigth==miss[4]]
  }
  bmi
}

MHAS_w3_bmi$mean_estatu <- apply(X = MHAS_w3_bmi[,c(2,3)], MARGIN = 1, FUN = mean)
MHAS_w3_bmi$mean_peso <- apply(X = MHAS_w3_bmi[,c(4,5)], MARGIN = 1, FUN = mean)

MHAS_w3_bmi$bmi <- compute_bmi(Heigth = MHAS_w3_bmi$mean_estatu, 
                        Weigth = MHAS_w3_bmi$mean_peso, miss = c(995, 996, 997, 999), 
                        heigth_m = FALSE)


MHAS_ds_w3 <- tibble(id=MHAS_w3_bmi$id)
MHAS_ds_w3$bmi <- car::recode(MHAS_w3_bmi$bmi, "995=993; 996=994; 997=993; 999=997; 9999=999")
MHAS_ds_w3$bmi <- labelled(MHAS_ds_w3$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = MHAS_ds_w3$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
 ggplot(MHAS_ds_w3, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
```{r crosstabulation3}
```


#### Quality estimation
No comments.



<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE}
bmi <- MHAS_m_ds_w1   <- MHAS_ds_w1
save(bmi, file = "../RData/w1/bmi.RData")
rm(bmi)

bmi <- MHAS_m_ds_w2   <- MHAS_ds_w2
save(bmi, file = "../RData/w2/bmi.RData")
rm(bmi)

bmi <- MHAS_m_ds_w3   <- MHAS_ds_w3
save(bmi, file = "../RData/w3/bmi.RData")
rm(bmi)


l.hds <- list(MHAS_ds_w1 = MHAS_ds_w1 , MHAS_ds_w2 = MHAS_ds_w2, MHAS_ds_w3=MHAS_ds_w3)

m.hds <- list(MHAS_m_ds_w1 = MHAS_m_ds_w1 , MHAS_m_ds_w2 = MHAS_m_ds_w2, MHAS_m_ds_w3 = MHAS_m_ds_w3)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}
```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}
# Table HRS
#t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
#for (i in 1:length(l.hds)){
#  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4]
#}
#t.hds[13,] <- c("n", "sample size", 
#             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]))
#names(t.hds)<-c("val", "label", "Wave1", "Wave2", "Wave3")
#kable(t.hds)
```



<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
#opal.logout(o)
```
