---
title: "Stroke or myocardial infarction (heart attack)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd_hard`
* Variable label: `History of stroke or myocardial infarction (heart attack)`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: stroke or myocardial infarction or heart attack`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no, the participant has not been diagnosed by stroke or myocardial infarction or heart attack
1        | yes, no, the participant has been diagnosed by stroke or myocardial infarction or heart attack

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of stroke or myocardial infarction (heart attack)"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke`|`Myocardial infarction or heart attack`|
| **Table name**  | `stroke`|`mi_ha`|
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** | `999 = Missing`|`999 = Missing`|
| **Description** |  |  |

```{r assign pol_w1, echo=F}

load(paste0(datafolder,"pol_w1/stroke.RData"))
load(paste0(datafolder,"pol_w1/mi_ha.RData"))
HAPIEE_pol_w1 <- tibble(id=stroke$id)
HAPIEE_pol_w1$stroke <- stroke$stroke
HAPIEE_pol_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_pol_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_pol_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `otherwise, keep up missing values into themselves`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$cvd_hard <- rep(999,length(HAPIEE_pol_w1$id))
HAPIEE_ds_pol_w1$cvd_hard[which(HAPIEE_pol_w1$stroke==0 & HAPIEE_pol_w1$mi_ha==0)] <- 0
HAPIEE_ds_pol_w1$cvd_hard[which(HAPIEE_pol_w1$stroke==1 | HAPIEE_pol_w1$mi_ha==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(HAPIEE_ds_pol_w1$cvd_hard, useNA = "ifany")
X <- c(
  sum(HAPIEE_pol_w1$stroke==0 & HAPIEE_pol_w1$mi_ha==0,na.rm=T),
  sum(HAPIEE_pol_w1$stroke==1 | HAPIEE_pol_w1$mi_ha==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(HAPIEE_pol_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","999->999")
kable(C)

```



### Wave 2

Not found.


## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke`|`Myocardial infarction or heart attack`|
| **Table name**  | `stroke`|`mi_ha`|
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** | `999 = Missing`|`999 = Missing`|
| **Description** |  |  |

```{r assign cz_w1, echo=F}

load(paste0(datafolder,"cz_w1/stroke.RData"))
load(paste0(datafolder,"cz_w1/mi_ha.RData"))
HAPIEE_cz_w1 <- tibble(id=stroke$id)
HAPIEE_cz_w1$stroke <- stroke$stroke
HAPIEE_cz_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(h_angina)
rm(mi_ha)

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_cz_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_cz_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `otherwise, keep up missing values into themselves`

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$cvd_hard <- rep(999,length(HAPIEE_cz_w1$id))
HAPIEE_ds_cz_w1$cvd_hard[which(HAPIEE_cz_w1$stroke==0 & HAPIEE_cz_w1$mi_ha==0)] <- 0
HAPIEE_ds_cz_w1$cvd_hard[which(HAPIEE_cz_w1$stroke==1 | HAPIEE_cz_w1$mi_ha==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w1, echo=F}

AfterH <- table(HAPIEE_ds_cz_w1$cvd_hard, useNA = "ifany")
X <- c(
  sum(HAPIEE_cz_w1$stroke==0 & HAPIEE_cz_w1$mi_ha==0,na.rm=T),
  sum(HAPIEE_cz_w1$stroke==1 | HAPIEE_cz_w1$mi_ha==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(HAPIEE_cz_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","999->999")
kable(C)

```



### Wave 2

Not found.




## Lithuania


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |
|-|-|
| **Label** | `Stroke`|
| **Table name**  | `stroke`|
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |
| **Missings** | `999 = Missing`|
| **Description** |  |

```{r assign li_w1, echo=F}

load(paste0(datafolder,"li_w1/stroke.RData"))
HAPIEE_li_w1 <- stroke
rm(stroke)

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `otherwise, keep up missing values into themselves`

**R script:**

```{r harmo li_w1}

# Categorical variable harmonization
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$cvd_hard <- HAPIEE_li_w1$stroke

```


#### Statistics of the new harmonized variable

```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation li_w1, echo=F,results='asis'}

AfterH <- table(HAPIEE_ds_li_w1$cvd_hard, useNA = "ifany")
BeforeH <- table(HAPIEE_li_w1$stroke, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","999->999")
kable(C)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

l.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, cz_w1 = HAPIEE_ds_cz_w1, li_w1 = HAPIEE_ds_li_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]))
names(t.hds)<-c("val", "label", "Poland_W1", "Czech_Republic_W1", "Lithuania_W1")
kable(t.hds)
  
```



# Quality estimation

The harmonized variable is about myocardial infarction and stroke. 
It has been built form the harmonized single disease variables. 

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  cvd_hard <- l.hds[[index]]
  save(cvd_hard, file = paste0(datafolder,names(l.hds)[index],"/cvd_hard.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





