---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `h15` |
|-|-|
| **Label** | `Ever been told by a doctor you have diabetes`|
| **Table name**  | `Po_baseline_etic`|
| **Categories** | `Yes; No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',variables=list('h15'), missings = T)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$h15
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(h15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `change No into 0`
* `change Yes into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$h_diabetes <- car::recode(HAPIEE_pol_w1$h15, "'No'=0; 'Yes'=1; NA=999")

HAPIEE_ds_pol_w1$h_diabetes <- labelled(HAPIEE_ds_pol_w1$h_diabetes, labels = cat_label)

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(HAPIEE_ds_pol_w1$h_diabetes, useNA = "ifany")
BeforeH <- table(HAPIEE_pol_w1$h15, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","Yes->1","NA->999")
kable(C)
rm(HAPIEE_pol_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `w2h15` |`ybirth`|`yintw (pol_w1)`|`yintw (pol_w2)`|
|-|-|-|-|-|
| **Label** | `Ever told by doctor that you have diabetes?`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Po_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `yes; no` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA; .b = Refused; .c = Don't know`|  |  |  |
| **Description** |  |  |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic',variables=list('w2h15'), missings = T)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')
load(paste0(datafolder,"pol_w2/ybirth.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,ybirth, by="id")
load(paste0(datafolder,"pol_w1/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[4] <- "yintw_pol_w1"
rm(yintw)
load(paste0(datafolder,"pol_w2/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[5] <- "yintw_pol_w2"
rm(yintw)

```

```{r local pol_w2, echo=F}

vbl <- HAPIEE_pol_w2$w2h15
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[3], caption = names(HAPIEE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(w2h15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_pol_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_pol_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

vbl <- HAPIEE_pol_w2$yintw_pol_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_pol_w2$yintw_pol_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `h15 == 'no' and w2h15 == 'no' into 0`
* `h15 == 'yes' or w2h15 == 'yes' into 1`
* `.b into 997`
* `.c into 998`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w2 and 0 in w1, h_diabetes_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo pol_w2}

# Categorical variable harmonization
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w2$id)

HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2, HAPIEE_ds_pol_w1, by = "id")
HAPIEE_ds_pol_w2$h_diabetes <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_diabetes[((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == 'no') & (HAPIEE_pol_w2$h_diabetes != 1)] <- 0
HAPIEE_ds_pol_w2$h_diabetes[((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == 'yes') | ((!is.na(HAPIEE_pol_w2$h_diabetes)) & (!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$h_diabetes == 1)] <- 1
HAPIEE_ds_pol_w2$h_diabetes[((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == '.b') & (HAPIEE_pol_w2$h_diabetes != 1)] <- 997
HAPIEE_ds_pol_w2$h_diabetes[((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == '.c') & (HAPIEE_pol_w2$h_diabetes != 1)] <- 998

HAPIEE_ds_pol_w2$h_diabetes <- labelled(HAPIEE_ds_pol_w2$h_diabetes, labels = cat_label)

# Continuous variable harmonization
diabetes_age <- (HAPIEE_pol_w2$yintw_pol_w2[HAPIEE_ds_pol_w2$h_diabetes == 1 & HAPIEE_pol_w2$h_diabetes==0]+HAPIEE_pol_w2$yintw_pol_w1[HAPIEE_ds_pol_w2$h_diabetes == 1 & HAPIEE_pol_w2$h_diabetes==0])/2-HAPIEE_pol_w2$ybirth[HAPIEE_ds_pol_w2$h_diabetes == 1 & HAPIEE_pol_w2$h_diabetes==0]

HAPIEE_ds_pol_w2$h_diabetes_age <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_diabetes_age[HAPIEE_ds_pol_w2$h_diabetes == 0] <- 996
HAPIEE_ds_pol_w2$h_diabetes_age[HAPIEE_ds_pol_w2$h_diabetes == 1 & HAPIEE_pol_w2$h_diabetes==0] <- diabetes_age

HAPIEE_ds_pol_w2$h_diabetes_age <- labelled(HAPIEE_ds_pol_w2$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- HAPIEE_ds_pol_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w2$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_pol_w2, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,75)

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_pol_w2$h_diabetes, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == 'no') & (HAPIEE_pol_w2$h_diabetes != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == 'yes') | ((!is.na(HAPIEE_pol_w2$h_diabetes)) & (!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$h_diabetes == 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == '.b') & (HAPIEE_pol_w2$h_diabetes != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h15)) & HAPIEE_pol_w2$w2h15 == '.c') & (HAPIEE_pol_w2$h_diabetes != 1))
)
BeforeH <- c(X[1:4],length(HAPIEE_pol_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("no->0","yes->1",".b->997",".c->998","NA->999")
kable(C)

cat("There are 235 individuals who answered in the previous wave that they were diagnosed to have diabetes and in the second wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(HAPIEE_pol_w2$h_diabetes[HAPIEE_pol_w2$w2h15=='no']), align = 'c')
kable(HAPIEE_pol_w2[HAPIEE_pol_w2$id %in% HAPIEE_pol_w2$id[HAPIEE_pol_w2$w2h15=='no' & HAPIEE_pol_w2$h_diabetes==1],], align = 'c')

rm(HAPIEE_pol_w2)

```



## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `h15` |`h15a`|
|-|-|-|
| **Label** | `Ever been told by a doctor you have diabetes`|`Cz,Li: If YES (you been told by a doctor you have diabetes), at what age?`|
| **Table name**  | `Cz_baseline_etic`|`Cz_baseline_etic`|
| **Categories** | `Yes; No` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cz_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',variables=list('h15','h15a'), missings = T)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$h15
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(h15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w1$h15a
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(HAPIEE_cz_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1, aes(h15a)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(0,75)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `change No into 0`
* `change Yes into 1`
* `NA into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = h15a`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$h_diabetes <- car::recode(HAPIEE_cz_w1$h15, "'No'=0; NA=999; 'Yes' = 1")

HAPIEE_ds_cz_w1$h_diabetes <- labelled(HAPIEE_ds_cz_w1$h_diabetes, labels = cat_label)

# Continuous variable harmonization

HAPIEE_ds_cz_w1$h_diabetes_age <- car::recode(HAPIEE_cz_w1$h15a, "NA=999")
HAPIEE_ds_cz_w1$h_diabetes_age[HAPIEE_ds_cz_w1$h_diabetes==0] <- 996

HAPIEE_ds_cz_w1$h_diabetes_age <- labelled(HAPIEE_ds_cz_w1$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,75)

```


#### Validation

```{r crosstabulation cz_w1, echo=F}

AfterH <- table(HAPIEE_ds_cz_w1$h_diabetes, useNA = "ifany")
BeforeH <- table(HAPIEE_cz_w1$h15, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","Yes->1","NA->999")
kable(C)
rm(HAPIEE_cz_w1)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2h15` |`ybirth`|`yintw (cz_w1)`|`yintw (cz_w2)`|
|-|-|-|-|-|
| **Label** | `Ever told by doctor that you have diabetes?`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Cz_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `yes; no` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign cz_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic',variables=list('w2h15'), missings = T)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')
load(paste0(datafolder,"cz_w2/ybirth.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,ybirth, by="id")
load(paste0(datafolder,"cz_w1/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[4] <- "yintw_cz_w1"
rm(yintw)
load(paste0(datafolder,"cz_w2/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[5] <- "yintw_cz_w2"
rm(yintw)

```


```{r local cz_w2, echo=F}

vbl <- HAPIEE_cz_w2$w2h15
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(w2h15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_cz_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

vbl <- HAPIEE_cz_w2$yintw_cz_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w2$yintw_cz_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `h15 == 'no' and w2h15 == 'no' into 0`
* `h15 == 'yes' or w2h15 == 'yes' into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w2 and 0 in w1, h_diabetes_age = age-(year of interview w2-year of interview w1)/2`
* `if h_diabetes == 1 in w2 and in w1, h_diabetes_age = age obtained in w1`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo cz_w2}

# Categorical variable harmonization
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w2$id)

HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2, HAPIEE_ds_cz_w1, by = "id")
HAPIEE_ds_cz_w2$h_diabetes <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_diabetes[((!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$w2h15 == 'no') & (HAPIEE_cz_w2$h_diabetes != 1)] <- 0
HAPIEE_ds_cz_w2$h_diabetes[((!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$w2h15 == 'yes') | ((!is.na(HAPIEE_cz_w2$h_diabetes)) & (!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$h_diabetes == 1)] <- 1

HAPIEE_ds_cz_w2$h_diabetes <- labelled(HAPIEE_ds_cz_w2$h_diabetes, labels = cat_label)

# Continuous variable harmonization
diabetes_age <- (HAPIEE_cz_w2$yintw_cz_w2[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==0]+HAPIEE_cz_w2$yintw_cz_w1[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==0])/2-HAPIEE_cz_w2$ybirth[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==0]

HAPIEE_ds_cz_w2$h_diabetes_age <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_diabetes_age[HAPIEE_ds_cz_w2$h_diabetes == 0] <- 996
HAPIEE_ds_cz_w2$h_diabetes_age[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==0] <- diabetes_age
HAPIEE_ds_cz_w2$h_diabetes_age[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==1] <- car::recode(HAPIEE_cz_w2$h_diabetes_age[HAPIEE_ds_cz_w2$h_diabetes == 1 & HAPIEE_cz_w2$h_diabetes==1],"miss_values_vector=999")
HAPIEE_ds_cz_w2$h_diabetes_age <- car::recode(HAPIEE_ds_cz_w2$h_diabetes_age, "NA=999")

HAPIEE_ds_cz_w2$h_diabetes_age <- labelled(HAPIEE_ds_cz_w2$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript cz_w2, echo=F}

vbl <- HAPIEE_ds_cz_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w2$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w2, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,75)

```


#### Validation

```{r crosstabulation cz_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_cz_w2$h_diabetes, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$w2h15 == 'no') & (HAPIEE_cz_w2$h_diabetes != 1)),
  sum(((!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$w2h15 == 'yes') | ((!is.na(HAPIEE_cz_w2$h_diabetes)) & (!is.na(HAPIEE_cz_w2$w2h15)) & HAPIEE_cz_w2$h_diabetes == 1))
)
BeforeH <- c(X[1:2],length(HAPIEE_cz_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","Yes->1","NA->999")
kable(C)

cat("There are 95 individuals who answered in the previous wave that they were diagnosed to have diabetes and in the second wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(HAPIEE_cz_w2$h_diabetes[HAPIEE_cz_w2$w2h15=='no']), align = 'c')
kable(HAPIEE_cz_w2[HAPIEE_cz_w2$id %in% HAPIEE_cz_w2$id[HAPIEE_cz_w2$w2h15=='no' & HAPIEE_cz_w2$h_diabetes==1],], align = 'c')

rm(HAPIEE_cz_w2)

```



## Lithuania


### Wave 1


#### Study-specific variable description

| **Name** | `h15` |`h15a`|
|-|-|-|
| **Label** | `Ever told by doctor that you have diabetes?`|`Cz,Li: If YES (you been told by a doctor you have diabetes), at what age?`|
| **Table name**  | `Li_baseline_etic`| `Li_baseline_etic`|
| **Categories** | `Yes; No` |`continuous`|
| **Missings** | `NA; .c = Don't know`|`NA; 998; 999`|
| **Description** |  |  |

```{r assign li_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic',variables=list('h15','h15a'), missings = T)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$h15
kable(Categorical_summary(vbl, missing_values = c('.c'))[3], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = c('.c'))[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(h15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_li_w1$h15a
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_li_w1)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_li_w1, aes(h15a)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(5,75)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `change No into 0`
* `change Yes into 1`
* `NA into 999`
* `.c into 998`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = h15a`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo li_w1}

# Categorical variable harmonization
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$h_diabetes <- car::recode(HAPIEE_li_w1$h15, "'No'=0; 'Yes'=1; NA=999; '.c'=998")

HAPIEE_ds_li_w1$h_diabetes <- labelled(HAPIEE_ds_li_w1$h_diabetes, labels = cat_label)

# Continuous variable harmonization

HAPIEE_ds_li_w1$h_diabetes_age <- car::recode(HAPIEE_li_w1$h15a, "NA=999")
HAPIEE_ds_li_w1$h_diabetes_age[HAPIEE_ds_li_w1$h_diabetes==0] <- 996

HAPIEE_ds_li_w1$h_diabetes_age <- labelled(HAPIEE_ds_li_w1$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_li_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_li_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,75)

```


#### Validation

```{r crosstabulation li_w1, echo=F,results='asis'}

AfterH <- table(HAPIEE_ds_li_w1$h_diabetes, useNA = "ifany")
BeforeH <- table(HAPIEE_li_w1$h15, useNA = "ifany")[c(2,3,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","Yes->1",".c->998","NA->999")
kable(C)
rm(HAPIEE_li_w1)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

lb.hds <- list(pol_w1 = HAPIEE_ds_pol_w1)
lf.hds <- list(pol_w2 = HAPIEE_ds_pol_w2, cz_w1 = HAPIEE_ds_cz_w1, cz_w2 = HAPIEE_ds_cz_w2, li_w1 = HAPIEE_ds_li_w1)
l.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, pol_w2 = HAPIEE_ds_pol_w2, cz_w1 = HAPIEE_ds_cz_w1, cz_w2 = HAPIEE_ds_cz_w2, li_w1 = HAPIEE_ds_li_w1)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]))
names(t.hds)<-c("val", "label", "Poland_W1", "Poland_W2", "Czech_Republic_W1", "Czech_Republic_W2", "Lithuania_W1")
kable(t.hds)
  
```



# Quality estimation
We assume that if an individual answers it has diabetes in one wave, it has diabetes for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_diabetes <- l.hds[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.hds)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





