---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cpdDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cpdDS.R')
```



# Data process

```{r HAPIEE categories}

yes_vector <- c('Yes, diagnosed, never hospitalised','Yes, diagnosed & hospitalised','Yes diagnosed and hospitalized','Yes diagnosed, not hospitalized','Li: Yes, angina')

```


## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `h10d` |
|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Po_baseline_etic`|
| **Categories** |  `Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`  |
| **Missings** | `NA` |
| **Description** |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$h10d
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$h_cpd <- car::recode(HAPIEE_pol_w1$h10d, "yes_vector=1; 'No or do not know'=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(HAPIEE_ds_pol_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_pol_w1$h10d, useNA = "ifany")
BeforeH <- c(X[1],sum(X[2:3]), X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1","NA->999")
kable(C)
rm(HAPIEE_pol_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `w2h10d` |`ybirth`|`yintw (pol_w1)`|`yintw (pol_w2)`|
|-|-|-|-|-|
| **Label** | `Ever diagnosed/hospitalised - Chronic respiratory disease`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Po_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `No or do not know`<br/>`Yes diagnosed, not hospitalized`<br/>`Yes diagnosed and hospitalized` |`continuous`|`continuous`|`continuous`|
| **Missings** | `.b = Refused`<br/>`.c = Don't know`<br/>`NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic',variables=list('w2h10d'), missings = T)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')
load(paste0(datafolder,"pol_w2/ybirth.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,ybirth, by="id")
load(paste0(datafolder,"pol_w1/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[4] <- "yintw_pol_w1"
rm(yintw)
load(paste0(datafolder,"pol_w2/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[5] <- "yintw_pol_w2"
rm(yintw)

```

```{r local pol_w2, echo=F}

vbl <- HAPIEE_pol_w2$w2h10d
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[3], caption = names(HAPIEE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(w2h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_pol_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_pol_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_pol_w2$yintw_pol_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_pol_w2$yintw_pol_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all No (across waves) or do not know into 0`
* `some Yes (across waves) into 1`
* `.b into 997`
* `.c into 998`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo pol_w2}

HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2, HAPIEE_ds_pol_w1, by = "id")

# Categorical variable harmonization
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w2$id)
HAPIEE_ds_pol_w2$h_cpd <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == 'No or do not know' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 0
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d %in% yes_vector | ((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$h_cpd == 1))] <- 1
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == '.b' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 997
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == '.c' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 998

# Continuous variable harmonization
HAPIEE_ds_pol_w2$h_cpd_age <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_cpd_age[which(HAPIEE_ds_pol_w2$h_cpd == 0)] <- 996
HAPIEE_ds_pol_w2$h_cpd_age[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)] <- floor((HAPIEE_pol_w2$yintw_pol_w2[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)]+HAPIEE_pol_w2$yintw_pol_w1[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)])/2-HAPIEE_pol_w2$ybirth[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)])

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- HAPIEE_ds_pol_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_pol_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_pol_w2$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == 'No or do not know') & (HAPIEE_pol_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d %in% yes_vector) | ((!is.na(HAPIEE_pol_w2$h_cpd)) & (!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$h_cpd == 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == '.b') & (HAPIEE_pol_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == '.c') & (HAPIEE_pol_w2$h_cpd != 1))
)
BeforeH <- c(X[1:4],length(HAPIEE_pol_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all No->0","some Yes->1",".b->997",".c->998","NA->999")
kable(C)

cat("There are 467 individuals who had some chronic respiratory disease in the previous wave and in the second wave answer that they were not told to have it. We harmonize them as having it")
kable(frq(HAPIEE_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d=='No or do not know')]), align = 'c')

rm(HAPIEE_pol_w2)

```



## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `h10d` |
|-|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Cz_baseline_etic`|
| **Categories** |`Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`|
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign cz_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$h10d
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$h_cpd <- car::recode(HAPIEE_cz_w1$h10d, "yes_vector=1; 'No or do not know'=0;9=999;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w1, echo=F}

AfterH <- table(HAPIEE_ds_cz_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_cz_w1$h10d, useNA = "ifany")
BeforeH <- c(X[2],sum(X[3:4]), sum(X[c(1,5)]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1","9,NA->999")
kable(C)
rm(HAPIEE_cz_w1)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2h10d` |`ybirth`|`yintw (cz_w1)`|`yintw (cz_w2)`|
|-|-|-|-|-|
| **Label** | `Ever diagnosed/hospitalised - Chronic respiratory disease`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Cz_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `No or do not know`<br/>`Yes diagnosed, not hospitalized`<br/>`Yes diagnosed and hospitalized`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign cz_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic',variables=list('w2h10d'), missings = T)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')
load(paste0(datafolder,"cz_w2/ybirth.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,ybirth, by="id")
load(paste0(datafolder,"cz_w1/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[4] <- "yintw_cz_w1"
rm(yintw)
load(paste0(datafolder,"cz_w2/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[5] <- "yintw_cz_w2"
rm(yintw)

```


```{r local cz_w2, echo=F}

vbl <- HAPIEE_cz_w2$w2h10d
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(w2h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_cz_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_cz_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w2$yintw_cz_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w2$yintw_cz_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all No (across waves) or do not know into 0`
* `some Yes (across waves) into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo cz_w2}

HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2, HAPIEE_ds_cz_w1, by = "id")

# Categorical variable harmonization
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w2$id)
HAPIEE_ds_cz_w2$h_cpd <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_cpd[which(HAPIEE_cz_w2$w2h10d == 'No or do not know' & (HAPIEE_cz_w2$h_cpd != 1 | is.na(HAPIEE_cz_w2$h_cpd)))] <- 0
HAPIEE_ds_cz_w2$h_cpd[which(HAPIEE_cz_w2$w2h10d %in% yes_vector | ((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$h_cpd == 1))] <- 1

# Continuous variable harmonization
HAPIEE_ds_cz_w2$h_cpd_age <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_cpd_age[which(HAPIEE_ds_cz_w2$h_cpd == 0)] <- 996
HAPIEE_ds_cz_w2$h_cpd_age[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)] <- floor((HAPIEE_cz_w2$yintw_cz_w2[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)]+HAPIEE_cz_w2$yintw_cz_w1[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)])/2-HAPIEE_cz_w2$ybirth[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)])


```


#### Statistics of the new harmonized variable

```{r descript cz_w2, echo=F}

vbl <- HAPIEE_ds_cz_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_cz_w2$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$w2h10d == 'No or do not know') & (HAPIEE_cz_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$w2h10d %in% yes_vector) | ((!is.na(HAPIEE_cz_w2$h_cpd)) & (!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$h_cpd == 1))
)
BeforeH <- c(X[1:2],length(HAPIEE_cz_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all No->0","some Yes->1","NA->999")
kable(C)

cat("There are 313 individuals who had some chronic respiratory disease in the previous wave and in the second wave answer that they were not told to have it. We harmonize them as having it")
kable(frq(HAPIEE_cz_w2$h_cpd[which(HAPIEE_cz_w2$w2h10d=='No or do not know')]), align = 'c')

rm(HAPIEE_cz_w2)

```



## Lithuania


### Wave 1


#### Study-specific variable description

| **Name** | `h10d` |
|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Li_baseline_etic`|
| **Categories** |`Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`|
| **Missings** | `.c = Don't know`<br/>`NA` |
| **Description** |  |

```{r assign li_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$h10d
kable(Categorical_summary(vbl, missing_values = c('.c'))[3], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = c('.c'))[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `.c into 998`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo li_w1}

# Categorical variable harmonization
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$h_cpd <- car::recode(HAPIEE_li_w1$h10d, "yes_vector=1; 'No or do not know'=0;NA=999; '.c'=998")

```


#### Statistics of the new harmonized variable

```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation li_w1, echo=F,results='asis'}

AfterH <- table(HAPIEE_ds_li_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_li_w1$h10d, useNA = "ifany")
BeforeH <- c(X[2],sum(X[3:4]), X[1],X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1",".c->998","NA->999")
kable(C)
rm(HAPIEE_li_w1)

```





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name = hd_vbl){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name = hd_vbl){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

hapiee.cw <- list(pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), cz_w1 = c("cz_w1","Czech Republic w1"), cz_w2 = c("cz_w2","Czech Republic w2"), li_w1 = c("li_w1","Lithuania w1"))

```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(hapiee.cw, function(wname) if(exists(paste0("HAPIEE_ds_",wname[1]))){wname = list(get(paste0("HAPIEE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

hapieelist <- lmlist # baseline list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_cpd` accross populations and waves

Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(hapiee.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HAPIEE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- hapieelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- hapieelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
}





```






## Summary of descriptive statistics of the harmonised variable `h_cpd_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(hapiee.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("HAPIEE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- hapieelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- hapieelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}



```



# Quality estimation
* We assume that if an individual has chronic pulmonary diseases in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





