---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_cpd`
* Variable label: `History of chronic pulmonary disorders`
* Variable description: `history of chronic pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NO chronic pulmonary disease
1        | chronic pulmonary disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_cpd_age`
* Variable label: `Age first diagnosed chronic pulmonary disease`
* Variable description: `The age first told had chronic lung disease diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of chronic pulmonary disorders"
ds_label_age <- "Age first diagnosed chronic pulmonary disease"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
yes_vector <- c('Yes, diagnosed, never hospitalised','Yes, diagnosed & hospitalised','Yes diagnosed and hospitalized','Yes diagnosed, not hospitalized','Li: Yes, angina')
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `h10d` |
|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Po_baseline_etic`|
| **Categories** |  `Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`  |
| **Missings** | `NA` |
| **Description** |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$h10d
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$h_cpd <- car::recode(HAPIEE_pol_w1$h10d, "yes_vector=1; 'No or do not know'=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

AfterH <- table(HAPIEE_ds_pol_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_pol_w1$h10d, useNA = "ifany")
BeforeH <- c(X[1],sum(X[2:3]), X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1","NA->999")
kable(C)
rm(HAPIEE_pol_w1)

```



### Wave 2

#### Study-specific variable description

| **Name** | `w2h10d` |`ybirth`|`yintw (pol_w1)`|`yintw (pol_w2)`|
|-|-|-|-|-|
| **Label** | `Ever diagnosed/hospitalised - Chronic respiratory disease`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Po_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `No or do not know`<br/>`Yes diagnosed, not hospitalized`<br/>`Yes diagnosed and hospitalized` |`continuous`|`continuous`|`continuous`|
| **Missings** | `.b = Refused`<br/>`.c = Don't know`<br/>`NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic',variables=list('w2h10d'), missings = T)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')
load(paste0(datafolder,"pol_w2/ybirth.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,ybirth, by="id")
load(paste0(datafolder,"pol_w1/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[4] <- "yintw_pol_w1"
rm(yintw)
load(paste0(datafolder,"pol_w2/yintw.RData"))
HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2,yintw, by="id")
names(HAPIEE_pol_w2)[5] <- "yintw_pol_w2"
rm(yintw)

```

```{r local pol_w2, echo=F}

vbl <- HAPIEE_pol_w2$w2h10d
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[3], caption = names(HAPIEE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = c('.b','.c'))[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(w2h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_pol_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_pol_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

vbl <- HAPIEE_pol_w2$yintw_pol_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_pol_w2$yintw_pol_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(yintw_pol_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all No (across waves) or do not know into 0`
* `some Yes (across waves) into 1`
* `.b into 997`
* `.c into 998`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo pol_w2}

HAPIEE_pol_w2 <- left_join(HAPIEE_pol_w2, HAPIEE_ds_pol_w1, by = "id")

# Categorical variable harmonization
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w2$id)
HAPIEE_ds_pol_w2$h_cpd <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == 'No or do not know' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 0
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d %in% yes_vector | ((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$h_cpd == 1))] <- 1
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == '.b' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 997
HAPIEE_ds_pol_w2$h_cpd[which(HAPIEE_pol_w2$w2h10d == '.c' & (HAPIEE_pol_w2$h_cpd != 1 | is.na(HAPIEE_pol_w2$h_cpd)))] <- 998

# Continuous variable harmonization
HAPIEE_ds_pol_w2$h_cpd_age <- rep(999,length(HAPIEE_pol_w2$id))
HAPIEE_ds_pol_w2$h_cpd_age[which(HAPIEE_ds_pol_w2$h_cpd == 0)] <- 996
HAPIEE_ds_pol_w2$h_cpd_age[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)] <- (HAPIEE_pol_w2$yintw_pol_w2[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)]+HAPIEE_pol_w2$yintw_pol_w1[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)])/2-HAPIEE_pol_w2$ybirth[which(HAPIEE_ds_pol_w2$h_cpd == 1 & HAPIEE_pol_w2$h_cpd==0)]

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- HAPIEE_ds_pol_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_pol_w2, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,75)

```


#### Validation

```{r crosstabulation pol_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_pol_w2$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == 'No or do not know') & (HAPIEE_pol_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d %in% yes_vector) | ((!is.na(HAPIEE_pol_w2$h_cpd)) & (!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$h_cpd == 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == '.b') & (HAPIEE_pol_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_pol_w2$w2h10d)) & HAPIEE_pol_w2$w2h10d == '.c') & (HAPIEE_pol_w2$h_cpd != 1))
)
BeforeH <- c(X[1:4],length(HAPIEE_pol_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all No->0","some Yes->1",".b->997",".c->998","NA->999")
kable(C)

cat("There are 467 individuals who had some chronic respiratory disease in the previous wave and in the second wave answer that they were not told to have it. We harmonize them as having it")
kable(frq(HAPIEE_pol_w2$h_cpd[HAPIEE_pol_w2$w2h10d=='No or do not know']), align = 'c')

rm(HAPIEE_pol_w2)

```



## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `h10d` |
|-|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Cz_baseline_etic`|
| **Categories** |`Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`|
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign cz_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$h10d
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$h_cpd <- car::recode(HAPIEE_cz_w1$h10d, "yes_vector=1; 'No or do not know'=0;9=999;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w1, echo=F}

AfterH <- table(HAPIEE_ds_cz_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_cz_w1$h10d, useNA = "ifany")
BeforeH <- c(X[2],sum(X[3:4]), sum(X[c(1,5)]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1","9,NA->999")
kable(C)
rm(HAPIEE_cz_w1)

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2h10d` |`ybirth`|`yintw (cz_w1)`|`yintw (cz_w2)`|
|-|-|-|-|-|
| **Label** | `Ever diagnosed/hospitalised - Chronic respiratory disease`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `Cz_reexamination_etic`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `No or do not know`<br/>`Yes diagnosed, not hospitalized`<br/>`Yes diagnosed and hospitalized`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA`|  |  |  |
| **Description** |  |  |  |  |

```{r assign cz_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic',variables=list('w2h10d'), missings = T)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')
load(paste0(datafolder,"cz_w2/ybirth.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,ybirth, by="id")
load(paste0(datafolder,"cz_w1/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[4] <- "yintw_cz_w1"
rm(yintw)
load(paste0(datafolder,"cz_w2/yintw.RData"))
HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2,yintw, by="id")
names(HAPIEE_cz_w2)[5] <- "yintw_cz_w2"
rm(yintw)

```


```{r local cz_w2, echo=F}

vbl <- HAPIEE_cz_w2$w2h10d
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(w2h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

vbl <- HAPIEE_cz_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(HAPIEE_cz_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

vbl <- HAPIEE_cz_w2$yintw_cz_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HAPIEE_cz_w2$yintw_cz_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(yintw_cz_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all No (across waves) or do not know into 0`
* `some Yes (across waves) into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo cz_w2}

HAPIEE_cz_w2 <- left_join(HAPIEE_cz_w2, HAPIEE_ds_cz_w1, by = "id")

# Categorical variable harmonization
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w2$id)
HAPIEE_ds_cz_w2$h_cpd <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_cpd[which(HAPIEE_cz_w2$w2h10d == 'No or do not know' & (HAPIEE_cz_w2$h_cpd != 1 | is.na(HAPIEE_cz_w2$h_cpd)))] <- 0
HAPIEE_ds_cz_w2$h_cpd[which(HAPIEE_cz_w2$w2h10d %in% yes_vector | ((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$h_cpd == 1))] <- 1

# Continuous variable harmonization
HAPIEE_ds_cz_w2$h_cpd_age <- rep(999,length(HAPIEE_cz_w2$id))
HAPIEE_ds_cz_w2$h_cpd_age[which(HAPIEE_ds_cz_w2$h_cpd == 0)] <- 996
HAPIEE_ds_cz_w2$h_cpd_age[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)] <- (HAPIEE_cz_w2$yintw_cz_w2[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)]+HAPIEE_cz_w2$yintw_cz_w1[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)])/2-HAPIEE_cz_w2$ybirth[which(HAPIEE_ds_cz_w2$h_cpd == 1 & HAPIEE_cz_w2$h_cpd==0)]


```


#### Statistics of the new harmonized variable

```{r descript cz_w2, echo=F}

vbl <- HAPIEE_ds_cz_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w2, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(45,75)

```


#### Validation

```{r crosstabulation cz_w2, echo=F, results='asis'}

AfterH <- table(HAPIEE_ds_cz_w2$h_cpd, useNA = "ifany")
X <- c(
  sum(((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$w2h10d == 'No or do not know') & (HAPIEE_cz_w2$h_cpd != 1)),
  sum(((!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$w2h10d %in% yes_vector) | ((!is.na(HAPIEE_cz_w2$h_cpd)) & (!is.na(HAPIEE_cz_w2$w2h10d)) & HAPIEE_cz_w2$h_cpd == 1))
)
BeforeH <- c(X[1:2],length(HAPIEE_cz_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all No->0","some Yes->1","NA->999")
kable(C)

cat("There are 313 individuals who had some chronic respiratory disease in the previous wave and in the second wave answer that they were not told to have it. We harmonize them as having it")
kable(frq(HAPIEE_cz_w2$h_cpd[HAPIEE_cz_w2$w2h10d=='No or do not know']), align = 'c')

rm(HAPIEE_cz_w2)

```



## Lithuania


### Wave 1


#### Study-specific variable description

| **Name** | `h10d` |
|-|-|
| **Label** | `Diagnosed/hospitalised for chronic respiratory disease`|
| **Table name**  | `Li_baseline_etic`|
| **Categories** |`Yes, diagnosed, never hospitalised`<br/>`Yes, diagnosed & hospitalised`<br/>`No or do not know`|
| **Missings** | `.c = Don't know`<br/>`NA` |
| **Description** |  |

```{r assign li_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic',variables=list('h10d'), missings = T)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$h10d
kable(Categorical_summary(vbl, missing_values = c('.c'))[3], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = c('.c'))[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(h10d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=5))

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `No or do not know into 0`
* `some Yes into 1`
* `.c into 998`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo li_w1}

# Categorical variable harmonization
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$h_cpd <- car::recode(HAPIEE_li_w1$h10d, "yes_vector=1; 'No or do not know'=0;NA=999; '.c'=998")

```


#### Statistics of the new harmonized variable

```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation li_w1, echo=F,results='asis'}

AfterH <- table(HAPIEE_ds_li_w1$h_cpd, useNA = "ifany")
X <- table(HAPIEE_li_w1$h10d, useNA = "ifany")
BeforeH <- c(X[2],sum(X[3:4]), X[1],X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("No->0","some Yes->1",".c->998","NA->999")
kable(C)
rm(HAPIEE_li_w1)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

lb.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, cz_w1 = HAPIEE_ds_cz_w1, li_w1 = HAPIEE_ds_li_w1)
lf.hds <- list(pol_w2 = HAPIEE_ds_pol_w2, cz_w2 = HAPIEE_ds_cz_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

l.hds <- c(lb.hds,lf.hds)
ln.hds <- c("pol_w1","pol_w2","cz_w1","cz_w2","li_w1")

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[ln.hds[1]]][[2]]), length(l.hds[[ln.hds[2]]][[2]]) , length(l.hds[[ln.hds[3]]][[2]]), length(l.hds[[ln.hds[4]]][[2]]), length(l.hds[[ln.hds[5]]][[2]]))
names(t.hds)<-c("val", "label", "Poland_W1", "Poland_W2", "Czech_Republic_W1", "Czech_Republic_W2", "Lithuania_W1")
kable(t.hds)
  
```



# Quality estimation
* We assume that if an individual has chronic pulmonary diseases in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_cpd <- l.hds[[index]]
  save(h_cpd, file = paste0(datafolder,names(l.hds)[index],"/h_cpd.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





