---
title: "Month of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mdeath`
* Variable label: `Month of death`
* Variable description: `month of death`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | january
2        | february
3        | march 
4        | april
5        | may
6        | june
7        | july
8        | august
9        | september
10       | october
11       | november
12       | december

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Month of death"
```



# Data process

## SHARE

### Wave 1 

There is no variable. 



### Wave 2 

#### Study-specific variable description

| **Name** | `xt008_` |
|----------|------------|
| **Label** | `month of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = january` |
| | `2 = february` |
| | `3 = march` |
| | `4 = april` |
| | `5 = may` |
| | `6 = june` |
| | `7 = july` |
| | `8 = august` |
| | `9 = september` |
| | `10 = october` |
| | `11 = november` |
| | `12 = december` |
| | `13 = today` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew2_rel2-6-0_xt',
                         variables=list('xt008_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')
SHARE_death3 <- SHARE_death2

opal.assign.table.tibble(o, 'SHARE_yinterview','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('int_year_w2'), missings = TRUE)
SHARE_yinterview <- opal.execute(o,'SHARE_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')

opal.assign.table.tibble(o, 'SHARE_id_w5','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('hhid5'), missings = TRUE)
SHARE_id_w5 <- opal.execute(o,'SHARE_id_w5')

```

```{r local2, echo=F}
vari <- SHARE_death2$xt008_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt008_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm

The harmonize variable is the same of the study-specific variable except for the missing values that have to be recoded as follows:

* ` 13 today into the month of interview`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There are tree individuals that appear as deaead in wave 2 but they did not participate in wave 1 that are going to be removed (See in Validation). There are four individuals that has date of death and in wave 4 or 5 are alive, therefore their date of death is going to be removed. 

**R script:**

```{r harmo2}
SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% SHARE_id_w1$id),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w4$id)),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w5$id)),]

ids <- as.character(c(SHARE_yinterview$id, SHARE_death2$id))
  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w2 <- tibble(id=SHARE_death$id)
SHARE_ds_w2$mdeath <- car::recode(SHARE_death$death, "-2=997; -1=998;  NA=999")
SHARE_ds_w2$mdeath <- labelled(SHARE_ds_w2$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=996,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(mdeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F,results='asis'}
kable(SHARE_death[which(!(SHARE_death3$id %in% SHARE_id_w1$id)),])
```

```{r crosstabulation21, echo=F,results='asis'}
BeforeH <- table(SHARE_death$death, useNA = "ifany")
BeforeH <- BeforeH[c(3:(length(BeforeH)-1), 1,2,length(BeforeH))]
AfterH <- table(SHARE_ds_w2$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-3)], "-2->997", "-1->998", "NA->999")
kable(C)
```

```{r importOPAL2, echo=F}
label(SHARE_ds_w2$mdeath) <- ds_label
mdeath <- SHARE_ds_w2
save(mdeath, file = "../RData/w2/mdeath.RData")
rm(mdeath, SHARE_death2, SHARE_death2)
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$mdeath <- car::recode(SHARE_m_ds_w2$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variable description

| **Name** | `sl_xt008_` |
|----------|------------|
| **Label** | `month of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = january` |
| | `2 = february` |
| | `3 = march` |
| | `4 = april` |
| | `5 = may` |
| | `6 = june` |
| | `7 = july` |
| | `8 = august` |
| | `9 = september` |
| | `10 = october` |
| | `11 = november` |
| | `12 = december` |
| | `13 = today` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew3_rel1_xt',
                         variables=list('sl_xt008_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')
SHARE_death3 <- SHARE_death2

opal.assign.table.tibble(o, 'SHARE_yinterview','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('int_year_w3'), missings = TRUE)
SHARE_yinterview <- opal.execute(o,'SHARE_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')
```

```{r local3, echo=F}
vari <- SHARE_death2$sl_xt008_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(sl_xt008_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable except for the missing values that have to be recoded as follows:

* ` 13 today into the month of interview`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`


There are nine individuals that appear as dead in wave 3 but they did not participate in wave 1 and 2 that are going to be removed (see in Validation). There is one individual that has date of death and in wave 4 is alive, therefore her/his date of death is going to be removed.

**R script:**

```{r harmo3}
ids_w1_w2 <- as.character(c(SHARE_id_w1$id, SHARE_id_w2$id[which(!(SHARE_id_w2$id %in% SHARE_id_w1$id))])) 

SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% ids_w1_w2),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w4$id)),]

ids <- as.character(c(SHARE_id_w3$id, SHARE_death2$id))
  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w3 <- tibble(id=SHARE_death$id)
SHARE_ds_w3$mdeath <- car::recode(SHARE_death$death, "-2=997; -1=998;  NA=999")
SHARE_ds_w3$mdeath <- labelled(SHARE_ds_w3$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=996,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(mdeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F,results='asis'}
kable(SHARE_death2[which(!(SHARE_death3$id %in% ids_w1_w2)),])
```

```{r crosstabulation31, echo=F,results='asis'}
BeforeH <- table(SHARE_death$death, useNA = "ifany")
BeforeH <- BeforeH[c(2:(length(BeforeH)-1), 1,length(BeforeH))]
AfterH <- table(SHARE_ds_w3$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-2)], "-1->998", "NA->999")
kable(C)
```


```{r importOPAL3, echo=F}
label(SHARE_ds_w3$mdeath) <- ds_label
mdeath <- SHARE_ds_w3
save(mdeath, file = "../RData/w3/mdeath.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$mdeath <- car::recode(SHARE_m_ds_w3$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4 

#### Study-specific variable description

| **Name** | `xt008_` |
|----------|------------|
| **Label** | `month of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = january` |
| | `2 = february` |
| | `3 = march` |
| | `4 = april` |
| | `5 = may` |
| | `6 = june` |
| | `7 = july` |
| | `8 = august` |
| | `9 = september` |
| | `10 = october` |
| | `11 = november` |
| | `12 = december` |
| | `13 = today` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew4_rel1-1-1_xt',
                         variables=list('xt008_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')
SHARE_death3 <- SHARE_death2

opal.assign.table.tibble(o, 'SHARE_w4_yinterview','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('int_year_w4'), missings = TRUE)
SHARE_w4_yinterview <- opal.execute(o,'SHARE_w4_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')
```

```{r local4, echo=F}
vari <- SHARE_death2$xt008_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt008_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable except for the missing values that have to be recoded as follows:

* ` 13 today into the month of interview`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There are 12 individuals that appear as dead in wave 2 but they did not participate in wave 1 that are going to be removed (See in Validation). 

**R script:**

```{r harmo4}
ids_w1_w2 <- as.character(c(SHARE_id_w1$id, SHARE_id_w2$id[which(!(SHARE_id_w2$id %in% SHARE_id_w1$id))])) 
ids_w1_w2_w3 <- as.character(c(ids_w1_w2, SHARE_id_w3$id[which(!(SHARE_id_w3$id %in% ids_w1_w2))])) 
SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% ids_w1_w2_w3),]

ids <- as.character(c(SHARE_id_w4$id, SHARE_death2$id))  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w4 <- tibble(id=SHARE_death$id)
SHARE_ds_w4$mdeath <- car::recode(SHARE_death$death, "-2=997; -1=998;  NA=999")
SHARE_ds_w4$mdeath <- labelled(SHARE_ds_w4$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=996,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(mdeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F,results='asis'}
kable(SHARE_death2[which(!(SHARE_death3$id %in% ids_w1_w2_w3)),])
```

```{r crosstabulation41, echo=F,results='asis'}
BeforeH <- table(SHARE_death$death, useNA = "ifany")
BeforeH <- BeforeH[c(3:(length(BeforeH)-1), 1,2,length(BeforeH))]
AfterH <- table(SHARE_ds_w4$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-3)], "-2->997", "-1->998", "NA->999")
kable(C)
```


```{r importOPAL4, echo=F}
label(SHARE_ds_w4$mdeath) <- ds_label
mdeath <- SHARE_ds_w4
save(mdeath, file = "../RData/w4/mdeath.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$mdeath <- car::recode(SHARE_m_ds_w4$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description

| **Name** | `xt008_` |
|----------|------------|
| **Label** | `month of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = january` |
| | `2 = february` |
| | `3 = march` |
| | `4 = april` |
| | `5 = may` |
| | `6 = june` |
| | `7 = july` |
| | `8 = august` |
| | `9 = september` |
| | `10 = october` |
| | `11 = november` |
| | `12 = december` |
| | `13 = today` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew5_rel1-0-0_xt',
                         variables=list('xt008_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')

opal.assign.table.tibble(o, 'SHARE_w5_yinterview','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('int_year_w5'), missings = TRUE)
SHARE_w5_yinterview <- opal.execute(o,'SHARE_w5_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')

opal.assign.table.tibble(o, 'SHARE_id_w5','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('hhid5'), missings = TRUE)
SHARE_id_w5 <- opal.execute(o,'SHARE_id_w5')
```

```{r local5, echo=F}
vari <- SHARE_death2$xt008_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt008_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable except for the missing values that have to be recoded as follows:

* ` 13 today into the month of interview`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo5}
ids <- as.character(c(SHARE_id_w5$id, SHARE_death2$id))
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w5 <- tibble(id=SHARE_death$id)
SHARE_ds_w5$mdeath <- car::recode(SHARE_death$death, "-2=997; -1=998;  NA=999")
SHARE_ds_w5$mdeath <- labelled(SHARE_ds_w5$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=996,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(mdeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F,results='asis'}
BeforeH <- table(SHARE_death$death, useNA = "ifany")
BeforeH <- BeforeH[c(2:(length(BeforeH)-1), 1,length(BeforeH))]
AfterH <- table(SHARE_ds_w5$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-2)], "-1->998", "NA->999")
kable(C)
```





```{r importOPAL5, echo=F}
label(SHARE_ds_w5$mdeath) <- ds_label
mdeath <- SHARE_ds_w5
save(mdeath, file = "../RData/w5/mdeath.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$mdeath <- car::recode(SHARE_m_ds_w5$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```



# Quality estimation
There may be individuals with date of death in some follow up interview after the follow up interview, it means that those individuals, even have date of death, are alive in that wave. 

In SHARE we are not going to take into accound the drop outs since in each wave participate different contries. It means that some individuals that participate in wave 1 and don't participate in wave 2 may be becouse they don't have to participate instead of because they are drop outs.  

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
