---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ydeath`
* Variable label: `Year of death`
* Variable description: `year of death`
* Domain: `Death`
* Value type: `continous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Year of death"
```


# Data process

## SHARE

### Wave 1 

There is no variable. 



### Wave 2 

#### Study-specific variable description

| **Name** | `xt009_` |
|----------|------------|
| **Label** | `year of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = 2004` |
| | `2 = 2005` |
| | `3 = 2006` |
| | `4 = 2007` |
| | `5 = 2008` |
| | `6 = 2009` |
| | `7 = 2010` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew2_rel2-6-0_xt',
                         variables=list('xt009_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')

opal.assign.table.tibble(o, 'SHARE_yinterview','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('int_year_w2'), missings = TRUE)
SHARE_yinterview <- opal.execute(o,'SHARE_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')

opal.assign.table.tibble(o, 'SHARE_id_w5','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('hhid5'), missings = TRUE)
SHARE_id_w5 <- opal.execute(o,'SHARE_id_w5')

```

```{r local2, echo=F}
vari <- SHARE_death2$xt009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt009_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* ` 1 into 2004`
* ` 2 into 2005`
* ` 3 into 2006`
* ` 4 into 2007`
* ` 5 into 2008`
* ` 6 into 2009`
* ` 7 into 2010`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There are tree individuals that appear as deaead in wave 2 but they did not participate in wave 1 that are going to be removed (See in Validation). There are tree individuals that has date of death and in wave 4 are alive that their date of death is going to be removed. 

**R script:**

```{r harmo2}
SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% SHARE_id_w1$id),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w4$id)),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w5$id)),]

ids <- as.character(c(SHARE_yinterview$id, SHARE_death2$id))
  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w2 <- tibble(id=SHARE_death$id)
SHARE_ds_w2$ydeath <- car::recode(SHARE_death$death, "1=2004; 2=2005; 3=2006; 4=2007; 5=2008; 6=2009; 7=2010; -2=997; -1=998;  NA=999")
SHARE_ds_w2$ydeath <- labelled(SHARE_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F,results='asis'}
kable(SHARE_death[which(!(SHARE_death2$id %in% SHARE_id_w1$id)),])
```



```{r importOPAL2, echo=F}
label(SHARE_ds_w2$ydeath) <- ds_label
ydeath <- SHARE_ds_w2
save(ydeath, file = "../RData/w2/ydeath.RData")
rm(ydeath, SHARE_death2, SHARE_death2)
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$ydeath <- car::recode(SHARE_m_ds_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variable description

| **Name** | `xt009_` |
|----------|------------|
| **Label** | `year of decease` |
| **Table name** | `sharew2_rel2-6-0_xt` |
| **Categories** | `1 = 2004` |
| | `2 = 2005` |
| | `3 = 2006` |
| | `4 = 2007` |
| | `5 = 2008` |
| | `6 = 2009` |
| | `7 = 2010` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew3_rel1_xt',
                         variables=list('sl_xt009_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')

opal.assign.table.tibble(o, 'SHARE_yinterview','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('int_year_w3'), missings = TRUE)
SHARE_yinterview <- opal.execute(o,'SHARE_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')
```

```{r local3, echo=F}
vari <- SHARE_death2$sl_xt009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(sl_xt009_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* ` 1 into 2004`
* ` 2 into 2005`
* ` 3 into 2006`
* ` 4 into 2007`
* ` 5 into 2008`
* ` 6 into 2009`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There are nine individuals that appear as dead in wave 3 but they did not participate in wave 1 and 2 that are going to be removed (see in Validation). There is one individual that has date of death and in wave 4 is alive that her/his date of death is going to be removed.

**R script:**

```{r harmo3}
ids_w1_w2 <- as.character(c(SHARE_id_w1$id, SHARE_id_w2$id[which(!(SHARE_id_w2$id %in% SHARE_id_w1$id))])) 

SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% ids_w1_w2),]
SHARE_death2 <- SHARE_death2[which(!(SHARE_death2$id %in% SHARE_id_w4$id)),]

ids <- as.character(c(SHARE_id_w3$id, SHARE_death2$id))
  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w3 <- tibble(id=SHARE_death$id)
SHARE_ds_w3$ydeath <- car::recode(SHARE_death$death, "1=2004; 2=2005; 3=2006; 4=2007; 5=2008; 6=2009; -2=997; -1=998;  NA=999")
SHARE_ds_w3$ydeath <- labelled(SHARE_ds_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F,results='asis'}
kable(SHARE_death2[which(!(SHARE_death2$id %in% ids_w1_w2)),])
```


```{r importOPAL3, echo=F}
label(SHARE_ds_w3$ydeath) <- ds_label
ydeath <- SHARE_ds_w3
save(ydeath, file = "../RData/w3/ydeath.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$ydeath <- car::recode(SHARE_m_ds_w3$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4 

#### Study-specific variable description

| **Name** | `xt009_` |
|----------|------------|
| **Label** | `year of decease` |
| **Table name** | `sharew4_rel1-1-1_xt` |
| **Categories** | `1 = 2006` |
| | `2 = 2007` |
| | `3 = 2008` |
| | `4 = 2009` |
| | `5 = 2010` |
| | `6 = 2011` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew4_rel1-1-1_xt',
                         variables=list('xt009_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')

opal.assign.table.tibble(o, 'SHARE_w4_yinterview','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('int_year_w4'), missings = TRUE)
SHARE_w4_yinterview <- opal.execute(o,'SHARE_w4_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')
```

```{r local4, echo=F}
vari <- SHARE_death2$xt009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt009_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* ` 1 into 2006`
* ` 2 into 2007`
* ` 3 into 2008`
* ` 4 into 2009`
* ` 5 into 2010`
* ` 6 into 2011`
* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

There are 12 individuals that appear as deaead in wave 2 but they did not participate in wave 1 that are going to be removed. (See in Validation) 

**R script:**

```{r harmo4}
ids_w1_w2 <- as.character(c(SHARE_id_w1$id, SHARE_id_w2$id[which(!(SHARE_id_w2$id %in% SHARE_id_w1$id))])) 
ids_w1_w2_w3 <- as.character(c(ids_w1_w2, SHARE_id_w3$id[which(!(SHARE_id_w3$id %in% ids_w1_w2))])) 
SHARE_death2 <- SHARE_death2[which(SHARE_death2$id %in% ids_w1_w2_w3),]

ids <- as.character(c(SHARE_id_w4$id, SHARE_death2$id))  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w4 <- tibble(id=SHARE_death$id)
SHARE_ds_w4$ydeath <- car::recode(SHARE_death$death, "1=2006; 2=2007; 3=2008; 4=2009; 5=2010; 6=2011; -2=997; -1=998;  NA=999")
SHARE_ds_w4$ydeath <- labelled(SHARE_ds_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F,results='asis'}
kable(SHARE_death2[which(!(SHARE_death2$id %in% ids_w1_w2_w3)),])
```


```{r importOPAL4, echo=F}
label(SHARE_ds_w4$ydeath) <- ds_label
ydeath <- SHARE_ds_w4
save(ydeath, file = "../RData/w4/ydeath.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$ydeath <- car::recode(SHARE_m_ds_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description

| **Name** | `xt009_` |
|----------|------------|
| **Label** | `year of decease` |
| **Table name** | `sharew5_rel1-0-0_xt` |
| **Missings** | `-2 = refusal`|
| | `-1 = don't know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_death2','SHARE.sharew5_rel1-0-0_xt',
                         variables=list('xt009_'), missings = TRUE)
SHARE_death2 <- opal.execute(o,'SHARE_death2')

opal.assign.table.tibble(o, 'SHARE_w5_yinterview','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('int_year_w5'), missings = TRUE)
SHARE_w5_yinterview <- opal.execute(o,'SHARE_w5_yinterview')

opal.assign.table.tibble(o, 'SHARE_id_w1','SHARE.sharew1_rel2-6-0_gv_weights',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w1 <- opal.execute(o,'SHARE_id_w1')

opal.assign.table.tibble(o, 'SHARE_id_w2','SHARE.sharew2_rel2-6-0_ws',
                         variables=list('hhid'), missings = TRUE)
SHARE_id_w2 <- opal.execute(o,'SHARE_id_w2')

opal.assign.table.tibble(o, 'SHARE_id_w3','SHARE.sharew3_rel1_gv_weights',
                         variables=list('hhid3'), missings = TRUE)
SHARE_id_w3 <- opal.execute(o,'SHARE_id_w3')

opal.assign.table.tibble(o, 'SHARE_id_w4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('hhid4'), missings = TRUE)
SHARE_id_w4 <- opal.execute(o,'SHARE_id_w4')

opal.assign.table.tibble(o, 'SHARE_id_w5','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('hhid5'), missings = TRUE)
SHARE_id_w5 <- opal.execute(o,'SHARE_id_w5')
```

```{r local5, echo=F}
vari <- SHARE_death2$xt009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_death2, aes(x=factor(xt009_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* ` -2 "refusal" into 997`
* ` -1 "don't know" into 998`

**R script:**

```{r harmo5}
ids <- as.character(c(SHARE_id_w5$id, SHARE_death2$id))
  
  
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], death=as.numeric(new_2[,2]))
  new_22
}

SHARE_death <- Add_indiv(old = SHARE_death2, new = ids)

SHARE_ds_w5 <- tibble(id=SHARE_death$id)
SHARE_ds_w5$ydeath <- car::recode(SHARE_death$death, "-2=997; -1=998;  NA=999")
SHARE_ds_w5$ydeath <- labelled(SHARE_ds_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F,results='asis'}
```





```{r importOPAL5, echo=F}
label(SHARE_ds_w5$ydeath) <- ds_label
ydeath <- SHARE_ds_w5
save(ydeath, file = "../RData/w5/ydeath.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$ydeath <- car::recode(SHARE_m_ds_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```



# Quality estimation
There may be individuals with date of death in some follow up interview after the follow up interview, it means that those individuals, even have date of death, are alive in that wave. 

In SHARE we are not going to take into accound the drop outs since in each wave participate different contries. It means that some individuals that participate in wave 1 and don't participate in wave 2 may be becouse they don't have to participate instead of because they are drop outs.  

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
