---
title: "Eye sight - General vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_gen`
* Variable label: `Eyesight - general vision`
* Variable description: `Difficulties in  eye sight using glasses or corrective lens as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## aksst

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_1`|
|-|-|
| **Label** | `D-008-1:EYESIGHT WITH GLASSES` |
| **Table name** | `jstar_2007_5cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well; 6 = Don't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 5 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_eye_gen','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('d_008_1'), missings = TRUE)
```

```{r local 5 cities w1, echo=F}
JSTAR_5cities_w1_eye_gen <- opal.execute(o,'JSTAR_5cities_w1_eye_gen')
vari <- JSTAR_5cities_w1_eye_gen$d_008_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_eye_gen, aes(x=factor(d_008_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_eye_gen$id)
JSTAR_aksst_ds_w1$eye_gen <- car::recode(JSTAR_5cities_w1_eye_gen$d_008_1, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$eye_gen <- labelled(JSTAR_aksst_ds_w1$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=F}
vari <- JSTAR_aksst_ds_w1$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=F}
AfterH <- table(JSTAR_aksst_ds_w1$eye_gen)
X<-table(JSTAR_5cities_w1_eye_gen$d_008_1)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_5cities_w1_eye_gen$d_008_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w1, echo=FALSE}

label(JSTAR_aksst_ds_w1$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_aksst_ds_w1
save(eye_gen, file = "../RData/aksst_w1/eye_gen.RData")

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$eye_gen <- car::recode(JSTAR_m_aksst_ds_w1$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2

#### Study-specific variable description




| **Name** | `d_008_1`|
|-|-|
| **Label** | `D-008-1:EYESIGHT WITH GLASSES` |
| **Table name** | `jstar_2009_5cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = Can see only so-so; 5 = Can't see well; 6 = Can't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign 5 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_eye_gen','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('d_008_1'), missings = TRUE)
```

```{r local 5 cities w2, echo=F}
JSTAR_5cities_w2_eye_gen <- opal.execute(o,'JSTAR_5cities_w2_eye_gen')
vari <- JSTAR_5cities_w2_eye_gen$d_008_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_eye_gen, aes(x=factor(d_008_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_eye_gen$id)
JSTAR_aksst_ds_w2$eye_gen <- car::recode(JSTAR_5cities_w2_eye_gen$d_008_1, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$eye_gen <- labelled(JSTAR_aksst_ds_w2$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=F}
vari <- JSTAR_aksst_ds_w2$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=F}
AfterH <- table(JSTAR_aksst_ds_w2$eye_gen)
X<-table(JSTAR_5cities_w2_eye_gen$d_008_1)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_5cities_w2_eye_gen$d_008_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w2, echo=FALSE}

label(JSTAR_aksst_ds_w2$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_aksst_ds_w2
save(eye_gen, file = "../RData/aksst_w2/eye_gen.RData")

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$eye_gen <- car::recode(JSTAR_m_aksst_ds_w2$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `d_008`|
|-|-|
| **Label** | `11D-008:EYESIGHT WITH OPHTHALMIC DEVICES` |
| **Table name** | `jstar_2011_5cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well; 6 = Don't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign 5 cities w3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_eye_gen','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('d_008'), missings = TRUE)
```

```{r local 5 cities w3, echo=F}
JSTAR_5cities_w3_eye_gen <- opal.execute(o,'JSTAR_5cities_w3_eye_gen')
vari <- JSTAR_5cities_w3_eye_gen$d_008
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_eye_gen, aes(x=factor(d_008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_eye_gen$id)
JSTAR_aksst_ds_w3$eye_gen <- car::recode(JSTAR_5cities_w3_eye_gen$d_008, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_aksst_ds_w3$eye_gen <- labelled(JSTAR_aksst_ds_w3$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w3, echo=F}
vari <- JSTAR_aksst_ds_w3$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3, echo=F}
AfterH <- table(JSTAR_aksst_ds_w3$eye_gen)
X<-table(JSTAR_5cities_w3_eye_gen$d_008)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_5cities_w3_eye_gen$d_008)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w3, echo=FALSE}

label(JSTAR_aksst_ds_w3$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_aksst_ds_w3
save(eye_gen, file = "../RData/aksst_w3/eye_gen.RData")

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$eye_gen <- car::recode(JSTAR_m_aksst_ds_w3$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```

## tn

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_1`|
|-|-|
| **Label** | `D-008-1:EYESIGHT WITH GLASSES` |
| **Table name** | `jstar_2009_2cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well; 6 = Don't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 2 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_eye_gen','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('d_008_1'), missings = TRUE)
```

```{r local 2 cities w1, echo=F}
JSTAR_2cities_w1_eye_gen <- opal.execute(o,'JSTAR_2cities_w1_eye_gen')
vari <- JSTAR_2cities_w1_eye_gen$d_008_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_eye_gen, aes(x=factor(d_008_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_eye_gen$id)
JSTAR_tn_ds_w1$eye_gen <- car::recode(JSTAR_2cities_w1_eye_gen$d_008_1, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_tn_ds_w1$eye_gen <- labelled(JSTAR_tn_ds_w1$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=F}
vari <- JSTAR_tn_ds_w1$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=F}
AfterH <- table(JSTAR_tn_ds_w1$eye_gen)
X<-table(JSTAR_2cities_w1_eye_gen$d_008_1)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_2cities_w1_eye_gen$d_008_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w1, echo=FALSE}

label(JSTAR_tn_ds_w1$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_tn_ds_w1
save(eye_gen, file = "../RData/tn_w1/eye_gen.RData")

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$eye_gen <- car::recode(JSTAR_m_tn_ds_w1$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `d_008`|
|-|-|
| **Label** | `11D-008:EYESIGHT WITH OPHTHALMIC DEVICES` |
| **Table name** | `jstar_2011_2cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well; 6 = Don't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 2 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_eye_gen','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('d_008'), missings = TRUE)
```

```{r local 2 cities w2, echo=F}
JSTAR_2cities_w2_eye_gen <- opal.execute(o,'JSTAR_2cities_w2_eye_gen')
vari <- JSTAR_2cities_w2_eye_gen$d_008
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_eye_gen, aes(x=factor(d_008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 2 cities w2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_eye_gen$id)
JSTAR_tn_ds_w2$eye_gen <- car::recode(JSTAR_2cities_w2_eye_gen$d_008, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_tn_ds_w2$eye_gen <- labelled(JSTAR_tn_ds_w2$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w2, echo=F}
vari <- JSTAR_tn_ds_w2$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w2, echo=F}
AfterH <- table(JSTAR_tn_ds_w2$eye_gen)
X<-table(JSTAR_2cities_w2_eye_gen$d_008)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_2cities_w2_eye_gen$d_008)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w2, echo=FALSE}

label(JSTAR_tn_ds_w2$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_tn_ds_w2
save(eye_gen, file = "../RData/tn_w2/eye_gen.RData")

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$eye_gen <- car::recode(JSTAR_m_tn_ds_w2$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```


## cth

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_1`|
|-|-|
| **Label** | `D-008-1:EYESIGHT WITH GLASSES` |
| **Table name** | `jstar_2011_3cities` |
| **Categories** |  `1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well; 6 = Don't see at all, or am visually impaired`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 3 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_eye_gen','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('d_008_1'), missings = TRUE)
```

```{r local 3 cities w1, echo=F}
JSTAR_3cities_w1_eye_gen <- opal.execute(o,'JSTAR_3cities_w1_eye_gen')
vari <- JSTAR_3cities_w1_eye_gen$d_008_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_eye_gen, aes(x=factor(d_008_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0` 
* `NA into 999`

**R script:**
```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_eye_gen$id)
JSTAR_cth_ds_w1$eye_gen <- car::recode(JSTAR_3cities_w1_eye_gen$d_008_1, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999' ")
JSTAR_cth_ds_w1$eye_gen <- labelled(JSTAR_cth_ds_w1$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=F}
vari <- JSTAR_cth_ds_w1$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=F}
AfterH <- table(JSTAR_cth_ds_w1$eye_gen)
X<-table(JSTAR_3cities_w1_eye_gen$d_008_1)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),sum(is.na(JSTAR_3cities_w1_eye_gen$d_008_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 3 cities w1, echo=FALSE}

label(JSTAR_cth_ds_w1$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
eye_gen <- JSTAR_cth_ds_w1
save(eye_gen, file = "../RData/cth_w1/eye_gen.RData")

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$eye_gen <- car::recode(JSTAR_m_cth_ds_w1$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
