---
title: "Eye sight - Near vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_near`
* Variable label: `Eyesight - Near vision`
* Variable description: `Difficulties for near vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## aksst

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_3`|
|-|-|
| **Label** | `D-008-3:EYESIGHT NEAR` |
| **Table name** | `jstar_2007_5cities` |
| **Categories** |`1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 5 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_eye_near','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('d_008_3'), missings = TRUE)
```

```{r local 5 cities w1, echo=F}
JSTAR_5cities_w1_eye_near <- opal.execute(o,'JSTAR_5cities_w1_eye_near')
vari <- JSTAR_5cities_w1_eye_near$d_008_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_eye_near, aes(x=factor(d_008_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_eye_near$id)
JSTAR_aksst_ds_w1$eye_near <- car::recode(JSTAR_5cities_w1_eye_near$d_008_3, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$eye_near <- labelled(JSTAR_aksst_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=F}
vari <- JSTAR_aksst_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=F}
AfterH <- table(JSTAR_aksst_ds_w1$eye_near)
X<-table(JSTAR_5cities_w1_eye_near$d_008_3)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(JSTAR_5cities_w1_eye_near$d_008_3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w1, echo=FALSE}

label(JSTAR_aksst_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- JSTAR_aksst_ds_w1
save(eye_near, file = "../RData/aksst_w1/eye_near.RData")

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$eye_near <- car::recode(JSTAR_m_aksst_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `d_008_3`|
|-|-|
| **Label** | `D-008-3:EYESIGHT IN SEEING CLOSE OBJECTS` |
| **Table name** | `jstar_2009_5cities` |
| **Categories** |`1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = Can see only so-so; 5 = Can't see well`|
| **Missings** |`NA` |
| **Description** |  |



```{r assign 5 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_eye_near','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('d_008_3'), missings = TRUE)
```

```{r local 5 cities w2, echo=F}
JSTAR_5cities_w2_eye_near <- opal.execute(o,'JSTAR_5cities_w2_eye_near')
vari <- JSTAR_5cities_w2_eye_near$d_008_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_eye_near, aes(x=factor(d_008_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_eye_near$id)
JSTAR_aksst_ds_w2$eye_near <- car::recode(JSTAR_5cities_w2_eye_near$d_008_3, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$eye_near <- labelled(JSTAR_aksst_ds_w2$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=F}
vari <- JSTAR_aksst_ds_w2$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=F}
AfterH <- table(JSTAR_aksst_ds_w2$eye_near)
X<-table(JSTAR_5cities_w2_eye_near$d_008_3)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(JSTAR_5cities_w2_eye_near$d_008_3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w2, echo=FALSE}

label(JSTAR_aksst_ds_w2$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
eye_near <- JSTAR_aksst_ds_w2
save(eye_near, file = "../RData/aksst_w2/eye_near.RData")

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$eye_near <- car::recode(JSTAR_m_aksst_ds_w2$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

Not found.



## tn

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_3`|
|-|-|
| **Label** | `D-008-3:EYESIGHT IN SEEING CLOSE OBJECTS` |
| **Table name** | `jstar_2009_2cities` |
| **Categories** |`1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign 2 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_eye_near','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('d_008_3'), missings = TRUE)
```

```{r local 2 cities w1, echo=F}
JSTAR_2cities_w1_eye_near <- opal.execute(o,'JSTAR_2cities_w1_eye_near')
vari <- JSTAR_2cities_w1_eye_near$d_008_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_eye_near, aes(x=factor(d_008_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `NA into 999`

**R script:**
```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_eye_near$id)
JSTAR_tn_ds_w1$eye_near <- car::recode(JSTAR_2cities_w1_eye_near$d_008_3, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999' ")
JSTAR_tn_ds_w1$eye_near <- labelled(JSTAR_tn_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=F}
vari <- JSTAR_tn_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=F}
AfterH <- table(JSTAR_tn_ds_w1$eye_near)
X<-table(JSTAR_2cities_w1_eye_near$d_008_3)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(JSTAR_2cities_w1_eye_near$d_008_3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w1, echo=FALSE}

label(JSTAR_tn_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- JSTAR_tn_ds_w1
save(eye_near, file = "../RData/tn_w1/eye_near.RData")

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$eye_near <- car::recode(JSTAR_m_tn_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.



## cth

### Wave 1 

#### Study-specific variable description




| **Name** | `d_008_3`|
|-|-|
| **Label** | `D-008-3:EYESIGHT IN SEEING CLOSE OBJECTS WITH GLASSES` |
| **Table name** | `jstar_2011_3cities` |
| **Categories** |`1 = Can see very well; 2 = Can see well; 3 = Can see at an average level; 4 = See only so-so; 5 = Don't see well`|
| **Missings** |`NA` |
| **Description** |  |


```{r assign 3 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_eye_near','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('d_008_3'), missings = TRUE)
```

```{r local 3 cities w1, echo=F}
JSTAR_3cities_w1_eye_near <- opal.execute(o,'JSTAR_3cities_w1_eye_near')
vari <- JSTAR_3cities_w1_eye_near$d_008_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_008_3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_eye_near, aes(x=factor(d_008_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `NA into 999`

**R script:**
```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_eye_near$id)
JSTAR_cth_ds_w1$eye_near <- car::recode(JSTAR_3cities_w1_eye_near$d_008_3, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999' ")
JSTAR_cth_ds_w1$eye_near <- labelled(JSTAR_cth_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=F}
vari <- JSTAR_cth_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=F}
AfterH <- table(JSTAR_cth_ds_w1$eye_near)
X<-table(JSTAR_3cities_w1_eye_near$d_008_3)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(JSTAR_3cities_w1_eye_near$d_008_3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL 3 cities w1, echo=FALSE}

label(JSTAR_cth_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- JSTAR_cth_ds_w1
save(eye_near, file = "../RData/cth_w1/eye_near.RData")

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$eye_near <- car::recode(JSTAR_m_cth_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
