---
title: "Mobility - Extending arms"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_arm`
* Variable label: `Difficulty for reaching / extending arms`
* Variable description: `Difficulty for reaching / extending arms`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## aksst


### Wave 1 

#### Study-specific variable description




| **Name** | `d_014_7`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2007_5cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign 5 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_mob_arm','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('d_014_7'), missings = TRUE)
```

```{r local 5 cities w1, echo=F}
JSTAR_5cities_w1_mob_arm <- opal.execute(o,'JSTAR_5cities_w1_mob_arm')
vari <- JSTAR_5cities_w1_mob_arm$d_014_7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_7")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_mob_arm, aes(x=factor(d_014_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_mob_arm$id)
JSTAR_aksst_ds_w1$mob_arm <- car::recode(JSTAR_5cities_w1_mob_arm$d_014_7, "0 = '1';1 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$mob_arm <- labelled(JSTAR_aksst_ds_w1$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=F}
vari <- JSTAR_aksst_ds_w1$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=F}
AfterH <- table(JSTAR_aksst_ds_w1$mob_arm)
X<-table(JSTAR_5cities_w1_mob_arm$d_014_7)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w1_mob_arm$d_014_7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w1, echo=FALSE}

label(JSTAR_aksst_ds_w1$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_aksst_ds_w1
save(mob_arm, file = "../RData/aksst_w1/mob_arm.RData")

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$mob_arm <- car::recode(JSTAR_m_aksst_ds_w1$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `d_014_g`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2009_5cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign 5 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_mob_arm','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('d_014_g'), missings = TRUE)
```

```{r local 5 cities w2, echo=F}
JSTAR_5cities_w2_mob_arm <- opal.execute(o,'JSTAR_5cities_w2_mob_arm')
vari <- JSTAR_5cities_w2_mob_arm$d_014_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_g")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_mob_arm, aes(x=factor(d_014_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_mob_arm$id)
JSTAR_aksst_ds_w2$mob_arm <- car::recode(JSTAR_5cities_w2_mob_arm$d_014_g, "0 = '1';1 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$mob_arm <- labelled(JSTAR_aksst_ds_w2$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=F}
vari <- JSTAR_aksst_ds_w2$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=F}
AfterH <- table(JSTAR_aksst_ds_w2$mob_arm)
X<-table(JSTAR_5cities_w2_mob_arm$d_014_g)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w2_mob_arm$d_014_g)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w2, echo=FALSE}

label(JSTAR_aksst_ds_w2$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_aksst_ds_w2
save(mob_arm, file = "../RData/aksst_w2/mob_arm.RData")

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$mob_arm <- car::recode(JSTAR_m_aksst_ds_w2$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `d_014_g`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2011_5cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign 5 cities w3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_mob_arm','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('d_014_g'), missings = TRUE)
```

```{r local 5 cities w3, echo=F}
JSTAR_5cities_w3_mob_arm <- opal.execute(o,'JSTAR_5cities_w3_mob_arm')
vari <- JSTAR_5cities_w3_mob_arm$d_014_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_g")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_mob_arm, aes(x=factor(d_014_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 5 cities w3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_mob_arm$id)
JSTAR_aksst_ds_w3$mob_arm <- car::recode(JSTAR_5cities_w3_mob_arm$d_014_g, "0 = '1';1 = '0';NA = '999' ")
JSTAR_aksst_ds_w3$mob_arm <- labelled(JSTAR_aksst_ds_w3$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w3, echo=F}
vari <- JSTAR_aksst_ds_w3$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3, echo=F}
AfterH <- table(JSTAR_aksst_ds_w3$mob_arm)
X<-table(JSTAR_5cities_w3_mob_arm$d_014_g)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w3_mob_arm$d_014_g)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w3, echo=FALSE}

label(JSTAR_aksst_ds_w3$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_aksst_ds_w3
save(mob_arm, file = "../RData/aksst_w3/mob_arm.RData")

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$mob_arm <- car::recode(JSTAR_m_aksst_ds_w3$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```


## tn

### Wave 1 

#### Study-specific variable description




| **Name** | `d_014_g`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2009_2cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign 2 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_mob_arm','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('d_014_g'), missings = TRUE)
```

```{r local 2 cities w1, echo=F}
JSTAR_2cities_w1_mob_arm <- opal.execute(o,'JSTAR_2cities_w1_mob_arm')
vari <- JSTAR_2cities_w1_mob_arm$d_014_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_g")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_mob_arm, aes(x=factor(d_014_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_mob_arm$id)
JSTAR_tn_ds_w1$mob_arm <- car::recode(JSTAR_2cities_w1_mob_arm$d_014_g, "0 = '1';1 = '0';NA = '999' ")
JSTAR_tn_ds_w1$mob_arm <- labelled(JSTAR_tn_ds_w1$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=F}
vari <- JSTAR_tn_ds_w1$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=F}
AfterH <- table(JSTAR_tn_ds_w1$mob_arm)
X<-table(JSTAR_2cities_w1_mob_arm$d_014_g)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w1_mob_arm$d_014_g)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w1, echo=FALSE}

label(JSTAR_tn_ds_w1$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_tn_ds_w1
save(mob_arm, file = "../RData/tn_w1/mob_arm.RData")

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$mob_arm <- car::recode(JSTAR_m_tn_ds_w1$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `d_014_g`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2011_2cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign 2 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_mob_arm','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('d_014_g'), missings = TRUE)
```

```{r local 2 cities w2, echo=F}
JSTAR_2cities_w2_mob_arm <- opal.execute(o,'JSTAR_2cities_w2_mob_arm')
vari <- JSTAR_2cities_w2_mob_arm$d_014_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_g")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_mob_arm, aes(x=factor(d_014_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 2 cities w2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_mob_arm$id)
JSTAR_tn_ds_w2$mob_arm <- car::recode(JSTAR_2cities_w2_mob_arm$d_014_g, "0 = '1';1 = '0';NA = '999' ")
JSTAR_tn_ds_w2$mob_arm <- labelled(JSTAR_tn_ds_w2$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w2, echo=F}
vari <- JSTAR_tn_ds_w2$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w2, echo=F}
AfterH <- table(JSTAR_tn_ds_w2$mob_arm)
X<-table(JSTAR_2cities_w2_mob_arm$d_014_g)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w2_mob_arm$d_014_g)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w2, echo=FALSE}

label(JSTAR_tn_ds_w2$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_tn_ds_w2
save(mob_arm, file = "../RData/tn_w2/mob_arm.RData")

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$mob_arm <- car::recode(JSTAR_m_tn_ds_w2$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```


## cth

### Wave 1 

#### Study-specific variable description




| **Name** | `d_014_g`|
|-|-|
| **Label** | `D-014-7:DIFFICULTY RISING ARM` |
| **Table name** |`jstar_2011_3cities`|
| **Categories** |`0 = No; 1 = Yes(Has difficulty)`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign 3 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_mob_arm','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('d_014_g'), missings = TRUE)
```

```{r local 3 cities w1, echo=F}
JSTAR_3cities_w1_mob_arm <- opal.execute(o,'JSTAR_3cities_w1_mob_arm')
vari <- JSTAR_3cities_w1_mob_arm$d_014_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "d_014_g")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_mob_arm, aes(x=factor(d_014_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* `NA into 999`

**R script:**
```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_mob_arm$id)
JSTAR_cth_ds_w1$mob_arm <- car::recode(JSTAR_3cities_w1_mob_arm$d_014_g, "0 = '1';1 = '0';NA = '999' ")
JSTAR_cth_ds_w1$mob_arm <- labelled(JSTAR_cth_ds_w1$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=F}
vari <- JSTAR_cth_ds_w1$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=F}
AfterH <- table(JSTAR_cth_ds_w1$mob_arm)
X<-table(JSTAR_3cities_w1_mob_arm$d_014_g)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_3cities_w1_mob_arm$d_014_g)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






```{r importOPAL 3 cities w1, echo=FALSE}

label(JSTAR_cth_ds_w1$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
mob_arm <- JSTAR_cth_ds_w1
save(mob_arm, file = "../RData/cth_w1/mob_arm.RData")

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$mob_arm <- car::recode(JSTAR_m_cth_ds_w1$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```