---
title: "ADL - Using the toilet"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```
<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_toilet`
* Variable label: `ADL-Difficulties for using the toilet`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process



## aksst
### Wave 1

#### Study-specific variable description

 


* Name: `d_013_6`
* Label: `D-013-6:DIFFICULTY IN USING A TOILET`
* Categories:
    + `1 Yes (Has difficulty)`
    + `0 No`
* Missings
    + `NA`

* Description: 
```{r assign 5 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_adl_toilet','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('d_013_6'), missings = TRUE)
```

```{r local 5 cities w1,  echo=FALSE}
JSTAR_5cities_w1_adl_toilet <- opal.execute(o,'JSTAR_5cities_w1_adl_toilet')
vari <- JSTAR_5cities_w1_adl_toilet$d_013_6 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


#Categorical_summary(JSTAR_5cities_w1_adl_toilet$d_013_6)
ggplot(JSTAR_5cities_w1_adl_toilet, aes(x=factor(d_013_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo 5 cities w1,   echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_adl_toilet$id)
JSTAR_aksst_ds_w1$adl_toilet <- car::recode(JSTAR_5cities_w1_adl_toilet$d_013_6, "0 = '1';1 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$adl_toilet <- labelled(JSTAR_aksst_ds_w1$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1,  echo=FALSE}
vari <- JSTAR_aksst_ds_w1$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")


#Categorical_summary(var = JSTAR_aksst_ds_w1$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 991, 992, 993, 994, 995, 996, 997, 998, 999, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w1$adl_toilet)
X<-table(JSTAR_5cities_w1_adl_toilet$d_013_6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w1_adl_toilet$d_013_6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 5 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w1) <- NULL
label(JSTAR_aksst_ds_w1$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$adl_toilet <- car::recode(JSTAR_m_aksst_ds_w1$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_toilet <- JSTAR_aksst_ds_w1
save(adl_toilet, file = paste0(datafolder, "/aksst_w1/adl_toilet.RData"))
```

### Wave 2

#### Study-specific variable description

 


* Name: `d_013_6`
* Label: `D-013-6:DIFFICULTY IN USING A TOILET`
* Categories:
    + `1 Yes (Has difficulty)`
    + `0 No`
* Missings
    + `NA`

* Description: 
```{r assign 5 cities w2,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_adl_toilet','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('d_013_6'), missings = TRUE)
```

```{r local 5 cities w2,  echo=FALSE}
JSTAR_5cities_w2_adl_toilet <- opal.execute(o,'JSTAR_5cities_w2_adl_toilet')
vari <- JSTAR_5cities_w2_adl_toilet$d_013_6 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


#Categorical_summary(JSTAR_5cities_w2_adl_toilet$d_013_6)
ggplot(JSTAR_5cities_w2_adl_toilet, aes(x=factor(d_013_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo 5 cities w2,   echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_adl_toilet$id)
JSTAR_aksst_ds_w2$adl_toilet <- car::recode(JSTAR_5cities_w2_adl_toilet$d_013_6, "0 = '1';1 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$adl_toilet <- labelled(JSTAR_aksst_ds_w2$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2,  echo=FALSE}
vari <- JSTAR_aksst_ds_w2$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = JSTAR_aksst_ds_w2$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 991, 992, 993, 994, 995, 996, 997, 998, 999, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2,  echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w2$adl_toilet)
X<-table(JSTAR_5cities_w2_adl_toilet$d_013_6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w2_adl_toilet$d_013_6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 5 cities w2, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w2) <- NULL
label(JSTAR_aksst_ds_w2$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$adl_toilet <- car::recode(JSTAR_m_aksst_ds_w2$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_toilet <- JSTAR_aksst_ds_w2
save(adl_toilet, file = paste0(datafolder, "/aksst_w2/adl_toilet.RData"))
```

### Wave 3

Not found.


## cth
#### Wave 1

#### Study-specific variable description

 


* Name: `d_013_6`
* Label: `D-013-6:DIFFICULTY IN USING A TOILET`
* Categories:
    + `1 Yes (Has difficulty)`
    + `0 No`
* Missings
    + `NA`

* Description: 
```{r assign 3 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_adl_toilet','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('d_013_6'), missings = TRUE)
```

```{r local 3 cities w1,  echo=FALSE}
JSTAR_3cities_w1_adl_toilet <- opal.execute(o,'JSTAR_3cities_w1_adl_toilet')

vari <- JSTAR_3cities_w1_adl_toilet$d_013_6 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


#Categorical_summary(JSTAR_3cities_w1_adl_toilet$d_013_6)
ggplot(JSTAR_3cities_w1_adl_toilet, aes(x=factor(d_013_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo 3 cities w1,   echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_adl_toilet$id)
JSTAR_cth_ds_w1$adl_toilet <- car::recode(JSTAR_3cities_w1_adl_toilet$d_013_6, "0 = '1';1 = '0';NA = '999' ")
JSTAR_cth_ds_w1$adl_toilet <- labelled(JSTAR_cth_ds_w1$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1,  echo=FALSE}
vari <- JSTAR_cth_ds_w1$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = JSTAR_cth_ds_w1$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 991, 992, 993, 994, 995, 996, 997, 998, 999, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_cth_ds_w1$adl_toilet)
X<-table(JSTAR_3cities_w1_adl_toilet$d_013_6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_3cities_w1_adl_toilet$d_013_6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 3 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_cth_ds_w1) <- NULL
label(JSTAR_cth_ds_w1$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$adl_toilet <- car::recode(JSTAR_m_cth_ds_w1$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_toilet <- JSTAR_cth_ds_w1
save(adl_toilet, file = paste0(datafolder, "/cth_w1/adl_toilet.RData"))
```
## tn
### Wave 1

#### Study-specific variable description

 


* Name: `d_013_6`
* Label: `D-013-6:DIFFICULTY IN USING A TOILET`
* Categories:
    + `1 Yes (Has difficulty)`
    + `0 No`
* Missings
    + `NA`

* Description: 
```{r assign 2 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_adl_toilet','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('d_013_6'), missings = TRUE)
```

```{r local 2 cities w1,  echo=FALSE}
JSTAR_2cities_w1_adl_toilet <- opal.execute(o,'JSTAR_2cities_w1_adl_toilet')

vari <- JSTAR_2cities_w1_adl_toilet$d_013_6 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")


#Categorical_summary(JSTAR_2cities_w1_adl_toilet$d_013_6)
ggplot(JSTAR_2cities_w1_adl_toilet, aes(x=factor(d_013_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `NA into 999`

**R script:** 
```{r harmo 2 cities w1,   echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_adl_toilet$id)
JSTAR_tn_ds_w1$adl_toilet <- car::recode(JSTAR_2cities_w1_adl_toilet$d_013_6, "0 = '1';1 = '0';NA = '999' ")
JSTAR_tn_ds_w1$adl_toilet <- labelled(JSTAR_tn_ds_w1$adl_toilet, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1,  echo=FALSE}
vari <- JSTAR_tn_ds_w1$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = JSTAR_tn_ds_w1$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 991, 992, 993, 994, 995, 996, 997, 998, 999, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w1$adl_toilet)
X<-table(JSTAR_2cities_w1_adl_toilet$d_013_6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w1_adl_toilet$d_013_6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 2 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_tn_ds_w1) <- NULL
label(JSTAR_tn_ds_w1$adl_toilet) <- "Difficulties for using the toilet"
opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$adl_toilet <- car::recode(JSTAR_m_tn_ds_w1$adl_toilet, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_toilet <- JSTAR_tn_ds_w1
save(adl_toilet, file = paste0(datafolder, "/tn_w1/adl_toilet.RData"))
```

### Wave 2
Not found.



# Quality control


No comments


```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
