---
title: "IADL - Difficulties for managing money"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_money`
* Variable label: `IADL - Difficulties for managing money, bills, expenses`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## a-k-s-s-t
### Wave 1

#### Study-specific variable description

 


* Name: `tome8`
* Label: `Q2:DAILY ACTIVITIES -4- CAN YOU PAY AN INVOICE?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 5 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_iadl_money','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('tome8', 'tome9'), missings = TRUE)
```

```{r local 5 cities w1,  echo=FALSE}
JSTAR_5cities_w1_iadl_money <- opal.execute(o,'JSTAR_5cities_w1_iadl_money')
vari <- JSTAR_5cities_w1_iadl_money$tome8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w1_iadl_money$tome8)
ggplot(JSTAR_5cities_w1_iadl_money, aes(x=factor(tome8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

```{r local 5 cities2 w1,  echo=FALSE}
JSTAR_5cities_w1_iadl_money <- opal.execute(o,'JSTAR_5cities_w1_iadl_money')
vari <- JSTAR_5cities_w1_iadl_money$tome9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w1_iadl_money$tome9)
ggplot(JSTAR_5cities_w1_iadl_money, aes(x=factor(tome9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `both 1 into 1` 
* `tome8 or tome9 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 5 cities w1,   echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_iadl_money$id)
JSTAR_aksst_ds_w1$iadl_money <- rep(0, length(JSTAR_5cities_w1_iadl_money$id))
JSTAR_aksst_ds_w1$iadl_money[which((JSTAR_5cities_w1_iadl_money$tome8==1)&(JSTAR_5cities_w1_iadl_money$tome9==1))]<-1
JSTAR_aksst_ds_w1$iadl_money[which((JSTAR_5cities_w1_iadl_money$tome8==2)|(JSTAR_5cities_w1_iadl_money$tome9==2))]<-2
JSTAR_aksst_ds_w1$iadl_money[which(is.na(JSTAR_5cities_w1_iadl_money$tome8)&is.na(JSTAR_5cities_w1_iadl_money$tome9))] <- NA
JSTAR_aksst_ds_w1$iadl_money[which(is.na(JSTAR_5cities_w1_iadl_money$tome8)&(JSTAR_5cities_w1_iadl_money$tome9==1))] <- NA
JSTAR_aksst_ds_w1$iadl_money[which(is.na(JSTAR_5cities_w1_iadl_money$tome9)&(JSTAR_5cities_w1_iadl_money$tome8==1))] <- NA

JSTAR_aksst_ds_w1$iadl_money <- car::recode(JSTAR_aksst_ds_w1$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$iadl_money <- labelled(JSTAR_aksst_ds_w1$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```




#### Statistical description of the new harmonised variable
```{r descript 5 cities w1,  echo=FALSE}
vari <- JSTAR_aksst_ds_w1$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w1$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w1$iadl_money)
X<-table(JSTAR_5cities_w1_iadl_money$tome8)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w1_iadl_money$tome8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 5 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w1) <- NULL
label(JSTAR_aksst_ds_w1$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$iadl_money <- car::recode(JSTAR_m_aksst_ds_w1$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_aksst_ds_w1
save(iadl_money, file = paste0(datafolder, "/aksst_w1/iadl_money.RData"))
```

### Wave 2

#### Study-specific variable description

 


* Name: `tome87`
* Label: `Q8:DAILY ACTIVITIES -4- CAN YOU PAY YOUR BILLS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 5 cities w2,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_iadl_money','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('tome87', 'tome88'), missings = TRUE)
```

```{r local 5 cities w2,  echo=FALSE}
JSTAR_5cities_w2_iadl_money <- opal.execute(o,'JSTAR_5cities_w2_iadl_money')
vari <- JSTAR_5cities_w2_iadl_money$tome87
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w2_iadl_money$tome87)
ggplot(JSTAR_5cities_w2_iadl_money, aes(x=factor(tome87))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

```{r local 5 cities2 w2,  echo=FALSE}
JSTAR_5cities_w2_iadl_money <- opal.execute(o,'JSTAR_5cities_w2_iadl_money')
vari <- JSTAR_5cities_w2_iadl_money$tome88
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w2_iadl_money$tome88)
ggplot(JSTAR_5cities_w2_iadl_money, aes(x=factor(tome88))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `both 1 into 1` 
* `tome87 or tome88 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 5 cities w2,   echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_iadl_money$id)
JSTAR_aksst_ds_w2$iadl_money <- rep(0, length(JSTAR_5cities_w2_iadl_money$id))
JSTAR_aksst_ds_w2$iadl_money[which((JSTAR_5cities_w2_iadl_money$tome87==1)&(JSTAR_5cities_w2_iadl_money$tome88==1))]<-1
JSTAR_aksst_ds_w2$iadl_money[which((JSTAR_5cities_w2_iadl_money$tome87==2)|(JSTAR_5cities_w2_iadl_money$tome88==2))]<-2
JSTAR_aksst_ds_w2$iadl_money[which(is.na(JSTAR_5cities_w2_iadl_money$tome87)&is.na(JSTAR_5cities_w2_iadl_money$tome88))] <- NA
JSTAR_aksst_ds_w2$iadl_money[which(is.na(JSTAR_5cities_w2_iadl_money$tome87)&(JSTAR_5cities_w2_iadl_money$tome88==1))] <- NA
JSTAR_aksst_ds_w2$iadl_money[which(is.na(JSTAR_5cities_w2_iadl_money$tome88)&(JSTAR_5cities_w2_iadl_money$tome87==1))] <- NA
JSTAR_aksst_ds_w2$iadl_money <- car::recode(JSTAR_aksst_ds_w2$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$iadl_money <- labelled(JSTAR_aksst_ds_w2$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2,  echo=FALSE}
vari <- JSTAR_aksst_ds_w2$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w2$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2,  echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w2$iadl_money)
X<-table(JSTAR_5cities_w2_iadl_money$tome87)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w2_iadl_money$tome87)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 5 cities w2, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w2) <- NULL
label(JSTAR_aksst_ds_w2$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$iadl_money <- car::recode(JSTAR_m_aksst_ds_w2$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_aksst_ds_w2
save(iadl_money, file = paste0(datafolder, "/aksst_w2/iadl_money.RData"))
```

### Wave 3

#### Study-specific variable description

 


* Name: `q6_4`
* Label: `11Q6:DAILY ACTIVITIES -4- PAY YOUR BILLS`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 5 cities w3,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_iadl_money','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('q6_4', 'q6_5'), missings = TRUE)
```

```{r local 5 cities w3,  echo=FALSE}
JSTAR_5cities_w3_iadl_money <- opal.execute(o,'JSTAR_5cities_w3_iadl_money')
vari <- JSTAR_5cities_w3_iadl_money$q6_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w3_iadl_money$q6_4)
ggplot(JSTAR_5cities_w3_iadl_money, aes(x=factor(q6_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

```{r local 5 cities2 w3,  echo=FALSE}
JSTAR_5cities_w3_iadl_money <- opal.execute(o,'JSTAR_5cities_w3_iadl_money')
vari <- JSTAR_5cities_w3_iadl_money$q6_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_5cities_w3_iadl_money$q6_5)
ggplot(JSTAR_5cities_w3_iadl_money, aes(x=factor(q6_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `both 1 into 1` 
* `q6_4 or q6_5 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 5 cities w3,   echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_iadl_money$id)
JSTAR_aksst_ds_w3$iadl_money <- rep(0, length(JSTAR_5cities_w3_iadl_money$id))
JSTAR_aksst_ds_w3$iadl_money[which((JSTAR_5cities_w3_iadl_money$q6_4==1)&(JSTAR_5cities_w3_iadl_money$q6_5==1))]<-1
JSTAR_aksst_ds_w3$iadl_money[which((JSTAR_5cities_w3_iadl_money$q6_4==2)|(JSTAR_5cities_w3_iadl_money$q6_5==2))]<-2
JSTAR_aksst_ds_w3$iadl_money[which(is.na(JSTAR_5cities_w3_iadl_money$q6_4)&is.na(JSTAR_5cities_w3_iadl_money$q6_5))] <- NA
JSTAR_aksst_ds_w3$iadl_money[which(is.na(JSTAR_5cities_w3_iadl_money$q6_4)&(JSTAR_5cities_w3_iadl_money$q6_5==1))] <- NA
JSTAR_aksst_ds_w3$iadl_money[which(is.na(JSTAR_5cities_w3_iadl_money$q6_5)&(JSTAR_5cities_w3_iadl_money$q6_4==1))] <- NA
JSTAR_aksst_ds_w3$iadl_money <- car::recode(JSTAR_aksst_ds_w3$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w3$iadl_money <- labelled(JSTAR_aksst_ds_w3$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable

```{r descript 5 cities w3,  echo=FALSE}
vari <- JSTAR_aksst_ds_w3$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_aksst_ds_w3$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3,  echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w3$iadl_money)
X<-table(JSTAR_5cities_w3_iadl_money$q6_4)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w3_iadl_money$q6_4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 5 cities w3, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_aksst_ds_w3) <- NULL
label(JSTAR_aksst_ds_w3$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$iadl_money <- car::recode(JSTAR_m_aksst_ds_w3$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_aksst_ds_w3
save(iadl_money, file = paste0(datafolder, "/aksst_w3/iadl_money.RData"))
```


## c-t-h
### Wave 1

#### Study-specific variable description

 


* Name: `q2_4`
* Label: `Q2:DAILY ACTIVITIES -4- CAN YOU PAY YOUR BILLS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 3 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_iadl_money','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q2_4', 'q2_5'), missings = TRUE)
```

```{r local 3 cities w1,  echo=FALSE}
JSTAR_3cities_w1_iadl_money <- opal.execute(o,'JSTAR_3cities_w1_iadl_money')
vari <- JSTAR_3cities_w1_iadl_money$q2_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_3cities_w1_iadl_money$q2_4)
ggplot(JSTAR_3cities_w1_iadl_money, aes(x=factor(q2_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

```{r local 3 cities2 w1,  echo=FALSE}
JSTAR_3cities_w1_iadl_money <- opal.execute(o,'JSTAR_3cities_w1_iadl_money')
vari <- JSTAR_3cities_w1_iadl_money$q2_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_3cities_w1_iadl_money$q2_5)
ggplot(JSTAR_3cities_w1_iadl_money, aes(x=factor(q2_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `both 1 into 1` 
* `q2_4 or q2_5 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 3 cities w1,   echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_iadl_money$id)
JSTAR_cth_ds_w1$iadl_money <- rep(0, length(JSTAR_3cities_w1_iadl_money$id))
JSTAR_cth_ds_w1$iadl_money[which((JSTAR_3cities_w1_iadl_money$q2_4==1)&(JSTAR_3cities_w1_iadl_money$q2_5==1))]<-1
JSTAR_cth_ds_w1$iadl_money[which((JSTAR_3cities_w1_iadl_money$q2_4==2)|(JSTAR_3cities_w1_iadl_money$q2_5==2))]<-2
JSTAR_cth_ds_w1$iadl_money[which(is.na(JSTAR_3cities_w1_iadl_money$q2_4)&is.na(JSTAR_3cities_w1_iadl_money$q2_5))] <- NA
JSTAR_cth_ds_w1$iadl_money[which(is.na(JSTAR_3cities_w1_iadl_money$q2_4)&(JSTAR_3cities_w1_iadl_money$q2_5==1))] <- NA
JSTAR_cth_ds_w1$iadl_money[which(is.na(JSTAR_3cities_w1_iadl_money$q2_5)&(JSTAR_3cities_w1_iadl_money$q2_4==1))] <- NA
summary(JSTAR_cth_ds_w1$iadl_money)
JSTAR_cth_ds_w1$iadl_money <- car::recode(JSTAR_cth_ds_w1$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_cth_ds_w1$iadl_money <- labelled(JSTAR_cth_ds_w1$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```


#### Statistical description of the new harmonised variable
```{r descript 3 cities w1,  echo=FALSE}
vari <- JSTAR_cth_ds_w1$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_cth_ds_w1$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_cth_ds_w1, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_cth_ds_w1$iadl_money)
X<-table(JSTAR_3cities_w1_iadl_money$q2_4)
BeforeH <- c(X[c(2:1)],sum(is.na(JSTAR_3cities_w1_iadl_money$q2_4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 3 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_cth_ds_w1) <- NULL
label(JSTAR_cth_ds_w1$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$iadl_money <- car::recode(JSTAR_m_cth_ds_w1$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_cth_ds_w1
save(iadl_money, file = paste0(datafolder, "/cth_w1/iadl_money.RData"))
```

## t-n
### Wave 1

#### Study-specific variable description

 


* Name: `tome8`
* Label: `Q2:DAILY ACTIVITIES -4- CAN YOU PAY YOUR BILLS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 2 cities w1,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_iadl_money','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('tome8', 'tome9'), missings = TRUE)
```

```{r local 2 cities w1,  echo=FALSE}
JSTAR_2cities_w1_iadl_money <- opal.execute(o,'JSTAR_2cities_w1_iadl_money')
vari <- JSTAR_2cities_w1_iadl_money$tome8
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_2cities_w1_iadl_money$tome8)
ggplot(JSTAR_2cities_w1_iadl_money, aes(x=factor(tome8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```


```{r local 2 cities2 w1,  echo=FALSE}
JSTAR_2cities_w1_iadl_money <- opal.execute(o,'JSTAR_2cities_w1_iadl_money')
vari <- JSTAR_2cities_w1_iadl_money$tome9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_2cities_w1_iadl_money$tome9)
ggplot(JSTAR_2cities_w1_iadl_money, aes(x=factor(tome9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `both 1 into 1` 
* `tome8 or tome9 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 2 cities w1,   echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_iadl_money$id)
JSTAR_tn_ds_w1$iadl_money <- rep(0, length(JSTAR_2cities_w1_iadl_money$id))
JSTAR_tn_ds_w1$iadl_money[which((JSTAR_2cities_w1_iadl_money$tome8==1)&(JSTAR_2cities_w1_iadl_money$tome9==1))]<-1
JSTAR_tn_ds_w1$iadl_money[which((JSTAR_2cities_w1_iadl_money$tome8==2)|(JSTAR_2cities_w1_iadl_money$tome9==2))]<-2
JSTAR_tn_ds_w1$iadl_money[which(is.na(JSTAR_2cities_w1_iadl_money$tome8)&is.na(JSTAR_2cities_w1_iadl_money$tome9))] <- NA
JSTAR_tn_ds_w1$iadl_money[which(is.na(JSTAR_2cities_w1_iadl_money$tome8)&(JSTAR_2cities_w1_iadl_money$tome9==1))] <- NA
JSTAR_tn_ds_w1$iadl_money[which(is.na(JSTAR_2cities_w1_iadl_money$tome9)&(JSTAR_2cities_w1_iadl_money$tome8==1))] <- NA
JSTAR_tn_ds_w1$iadl_money <- car::recode(JSTAR_tn_ds_w1$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_tn_ds_w1$iadl_money <- labelled(JSTAR_tn_ds_w1$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```



#### Statistical description of the new harmonised variable
```{r descript 2 cities w1,  echo=FALSE}
vari <- JSTAR_tn_ds_w1$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w1$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w1, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1,  echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w1$iadl_money)
X<-table(JSTAR_2cities_w1_iadl_money$tome8)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w1_iadl_money$tome8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 2 cities w1, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_tn_ds_w1) <- NULL
label(JSTAR_tn_ds_w1$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$iadl_money <- car::recode(JSTAR_m_tn_ds_w1$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_tn_ds_w1
save(iadl_money, file = paste0(datafolder, "/tn_w1/iadl_money.RData"))
```

### Wave 2

#### Study-specific variable description

 


* Name: `q6_4`
* Label: `11Q6:DAILY ACTIVITIES -4- PAY YOUR BILLS`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

* Description: 
```{r assign 2 cities w2,  echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_iadl_money','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('q6_4', 'q6_5'), missings = TRUE)
```

```{r local 2 cities w2,  echo=FALSE}
JSTAR_2cities_w2_iadl_money <- opal.execute(o,'JSTAR_2cities_w2_iadl_money')
vari <- JSTAR_2cities_w2_iadl_money$q6_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_2cities_w2_iadl_money$q6_4)
ggplot(JSTAR_2cities_w2_iadl_money, aes(x=factor(q6_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

```{r local 2 cities2 w2,  echo=FALSE}
JSTAR_2cities_w2_iadl_money <- opal.execute(o,'JSTAR_2cities_w2_iadl_money')
vari <- JSTAR_2cities_w2_iadl_money$q6_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(JSTAR_2cities_w2_iadl_money$q6_5)
ggplot(JSTAR_2cities_w2_iadl_money, aes(x=factor(q6_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
* `both 1 into 1` 
* `q6_4 or q6_5 2 into 0` 
* `both NA or one NA and the other 1 into 999`

**R script:** 
```{r harmo 2 cities w2,   echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_iadl_money$id)
JSTAR_tn_ds_w2$iadl_money <- rep(0, length(JSTAR_2cities_w2_iadl_money$id))
JSTAR_tn_ds_w2$iadl_money[which((JSTAR_2cities_w2_iadl_money$q6_4==1)&(JSTAR_2cities_w2_iadl_money$q6_5==1))]<-1
JSTAR_tn_ds_w2$iadl_money[which((JSTAR_2cities_w2_iadl_money$q6_4==2)|(JSTAR_2cities_w2_iadl_money$q6_5==2))]<-2
JSTAR_tn_ds_w2$iadl_money[which(is.na(JSTAR_2cities_w2_iadl_money$q6_4)&is.na(JSTAR_2cities_w2_iadl_money$q6_5))] <- NA
JSTAR_tn_ds_w2$iadl_money[which(is.na(JSTAR_2cities_w2_iadl_money$q6_4)&(JSTAR_2cities_w2_iadl_money$q6_5==1))] <- NA
JSTAR_tn_ds_w2$iadl_money[which(is.na(JSTAR_2cities_w2_iadl_money$q6_5)&(JSTAR_2cities_w2_iadl_money$q6_4==1))] <- NA

JSTAR_tn_ds_w2$iadl_money <- car::recode(JSTAR_tn_ds_w2$iadl_money, "1 = '1';2 = '0';NA = '999' ")
JSTAR_tn_ds_w2$iadl_money <- labelled(JSTAR_tn_ds_w2$iadl_money, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```



#### Statistical description of the new harmonised variable
```{r descript 2 cities w2,  echo=FALSE}
vari <- JSTAR_tn_ds_w2$iadl_money # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = JSTAR_tn_ds_w2$iadl_money, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(JSTAR_tn_ds_w2, aes(x=factor(iadl_money))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Managing money") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w2,  echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w2$iadl_money)
X<-table(JSTAR_2cities_w2_iadl_money$q6_4)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w2_iadl_money$q6_4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL 2 cities w2, echo=FALSE,  echo=FALSE}
val_labels(JSTAR_tn_ds_w2) <- NULL
label(JSTAR_tn_ds_w2$iadl_money) <- "Difficulties for managing money, bills, expenses"
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$iadl_money <- car::recode(JSTAR_m_tn_ds_w2$iadl_money, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_money <- JSTAR_tn_ds_w2
save(iadl_money, file = paste0(datafolder, "/tn_w2/iadl_money.RData"))
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
