---
title: "Limitations in ADLs - Shopping for groceries"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_shopping`
* Variable label: `IADL - Difficulties for shopping groceries`
* Variable description: `IADL - Difficulties for shopping groceries`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for shopping groceries"
```


# Data process

## 5 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `tome6`
* Label: `Q2:DAILY ACTIVITIES -2- CAN YOU GO SHOPPING FOR GROCERIES?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 5 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_iadl_shopping','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('tome6'), missings = TRUE)
JSTAR_5cities_w1_iadl_shopping <- opal.execute(o,'JSTAR_5cities_w1_iadl_shopping')
```

```{r local 5 cities w1, echo=FALSE}
vari <- JSTAR_5cities_w1_iadl_shopping$tome6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_iadl_shopping, aes(x=factor(tome6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_iadl_shopping$id)
JSTAR_aksst_ds_w1$iadl_shopping <- recode(JSTAR_5cities_w1_iadl_shopping$tome6, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w1$iadl_shopping <- labelled(JSTAR_aksst_ds_w1$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=FALSE}
vari <- JSTAR_aksst_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w1$iadl_shopping)
X<-table(JSTAR_5cities_w1_iadl_shopping$tome6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w1_iadl_shopping$tome6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w1, echo=FALSE}
label(JSTAR_aksst_ds_w1$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_aksst_ds_w1
save(iadl_shopping, file = "../RData/aksst_w1/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$iadl_shopping <- recode(JSTAR_m_aksst_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



#### JSTAR - 5 cities - Wave 2

##### Study-specific variables

The study-specific variables elected to be harmonised is:


* Name: `tome85`
* Label: `Q8:DAILY ACTIVITIES -2- CAN YOU SHOP FOR DAILY NEEDS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 5 cities w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_iadl_shopping','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('tome85'), missings = TRUE)
JSTAR_5cities_w2_iadl_shopping <- opal.execute(o,'JSTAR_5cities_w2_iadl_shopping')
```

```{r local 5 cities w2, echo=FALSE}
vari <- JSTAR_5cities_w2_iadl_shopping$tome85
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_iadl_shopping, aes(x=factor(tome85))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_iadl_shopping$id)
JSTAR_aksst_ds_w2$iadl_shopping <- recode(JSTAR_5cities_w2_iadl_shopping$tome85, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w2$iadl_shopping <- labelled(JSTAR_aksst_ds_w2$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=FALSE}
vari <- JSTAR_aksst_ds_w2$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w2$iadl_shopping)
X<-table(JSTAR_5cities_w2_iadl_shopping$tome85)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w2_iadl_shopping$tome85)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w2, echo=FALSE}
label(JSTAR_aksst_ds_w2$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_aksst_ds_w2
save(iadl_shopping, file = "../RData/aksst_w2/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$iadl_shopping <- recode(JSTAR_m_aksst_ds_w2$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `q6_2`
* Label: `11Q6:DAILY ACTIVITIES -2- SHOP FOR DAILY NEED`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 5 cities w3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_iadl_shopping','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('q6_2'), missings = TRUE)
JSTAR_5cities_w3_iadl_shopping <- opal.execute(o,'JSTAR_5cities_w3_iadl_shopping')
```

```{r local 5 cities w3, echo=FALSE}
vari <- JSTAR_5cities_w3_iadl_shopping$q6_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_iadl_shopping, aes(x=factor(q6_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 5 cities w3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_iadl_shopping$id)
JSTAR_aksst_ds_w3$iadl_shopping <- recode(JSTAR_5cities_w3_iadl_shopping$q6_2, "1 = '1';2 = '0';NA = '999' ")
JSTAR_aksst_ds_w3$iadl_shopping <- labelled(JSTAR_aksst_ds_w3$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w3$iadl_shopping)
X<-table(JSTAR_5cities_w3_iadl_shopping$q6_2)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_5cities_w3_iadl_shopping$q6_2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w3, echo=FALSE}
label(JSTAR_aksst_ds_w3$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_aksst_ds_w3
save(iadl_shopping, file = "../RData/aksst_w3/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$iadl_shopping <- recode(JSTAR_m_aksst_ds_w3$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```




## 3 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q2_2`
* Label: `Q2:DAILY ACTIVITIES -2- CAN YOU SHOP FOR DAILY NEEDS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 3 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_iadl_shopping','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q2_2'), missings = TRUE)
JSTAR_3cities_w1_iadl_shopping <- opal.execute(o,'JSTAR_3cities_w1_iadl_shopping')
```

```{r local 3 cities w1, echo=FALSE}
vari <- JSTAR_3cities_w1_iadl_shopping$q2_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_iadl_shopping, aes(x=factor(q2_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_iadl_shopping$id)
JSTAR_cth_ds_w1$iadl_shopping <- recode(JSTAR_3cities_w1_iadl_shopping$q2_2, "1 = '1';2 = '0';NA = '999' ")
JSTAR_cth_ds_w1$iadl_shopping <- labelled(JSTAR_cth_ds_w1$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=FALSE}
AfterH <- table(JSTAR_cth_ds_w1$iadl_shopping)
X<-table(JSTAR_3cities_w1_iadl_shopping$q2_2)
BeforeH <- c(X[c(2:1)],sum(is.na(JSTAR_3cities_w1_iadl_shopping$q2_2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 3 cities w1, echo=FALSE}
label(JSTAR_cth_ds_w1$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_cth_ds_w1
save(iadl_shopping, file = "../RData/cth_w1/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$iadl_shopping <- recode(JSTAR_m_cth_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```




## 2 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `tome6`
* Label: `Q2:DAILY ACTIVITIES -2- CAN YOU SHOP FOR DAILY NEEDS?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 2 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_iadl_shopping','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('tome6'), missings = TRUE)
JSTAR_2cities_w1_iadl_shopping <- opal.execute(o,'JSTAR_2cities_w1_iadl_shopping')
```

```{r local 2 cities w1, echo=FALSE}
vari <- JSTAR_2cities_w1_iadl_shopping$tome6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_iadl_shopping, aes(x=factor(tome6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_iadl_shopping$id)
JSTAR_tn_ds_w1$iadl_shopping <- recode(JSTAR_2cities_w1_iadl_shopping$tome6, "1 = '1';2 = '0';NA = '999' ")
JSTAR_tn_ds_w1$iadl_shopping <- labelled(JSTAR_tn_ds_w1$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=FALSE}
vari <- JSTAR_tn_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w1$iadl_shopping)
X<-table(JSTAR_2cities_w1_iadl_shopping$tome6)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w1_iadl_shopping$tome6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 2 cities w1, echo=FALSE}
label(JSTAR_tn_ds_w1$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_tn_ds_w1
save(iadl_shopping, file = "../RData/tn_w1/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$iadl_shopping <- recode(JSTAR_m_tn_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```




### 2 cities

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q6_2`
* Label: `11Q6:DAILY ACTIVITIES -2- SHOP FOR DAILY NEED`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `NA` 

```{r assign 2 cities w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_iadl_shopping','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('q6_2'), missings = TRUE)
JSTAR_2cities_w2_iadl_shopping <- opal.execute(o,'JSTAR_2cities_w2_iadl_shopping')
```

```{r local 2 cities w2, echo=FALSE}
vari <- JSTAR_2cities_w2_iadl_shopping$q6_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_iadl_shopping, aes(x=factor(q6_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo 2 cities w2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_iadl_shopping$id)
JSTAR_tn_ds_w2$iadl_shopping <- recode(JSTAR_2cities_w2_iadl_shopping$q6_2, "1 = '1';2 = '0';NA = '999' ")
JSTAR_tn_ds_w2$iadl_shopping <- labelled(JSTAR_tn_ds_w2$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w2, echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w2$iadl_shopping)
X<-table(JSTAR_2cities_w2_iadl_shopping$q6_2)
BeforeH <- c(X[2:1],sum(is.na(JSTAR_2cities_w2_iadl_shopping$q6_2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL 2 cities w2, echo=FALSE}
label(JSTAR_tn_ds_w2$iadl_shopping) <- "Difficulties for shopping groceries"
iadl_shopping <- JSTAR_tn_ds_w2
save(iadl_shopping, file = "../RData/tn_w2/iadl_shopping.RData")
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$iadl_shopping <- recode(JSTAR_m_tn_ds_w2$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
