---
title: "Cognition - Immediate recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_imm_c`
* Variable label: `Cognition - Immediate recall - Continuous`
* Variable description: `Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable.`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_imm`
* Variable label: `Cognition - Immediate recall`
* Variable description: `Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Immediate recall"
ds_label_cog_imm_c <- "Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_imm <- "Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## 5 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `b_005_a`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_b`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_c`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_d`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_e`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_f`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_g`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_h`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_i`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_j`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 5 cities w1}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_cog_imm','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('b_005_a','b_005_b','b_005_c','b_005_d','b_005_e','b_005_f','b_005_g','b_005_h','b_005_i','b_005_j'), missings = TRUE)
JSTAR_5cities_w1_cog_imm <- opal.execute(o,'JSTAR_5cities_w1_cog_imm')
```

```{r local 5 cities w1}
vari <- JSTAR_5cities_w1_cog_imm$b_005_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_imm$b_005_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_imm, aes(x=factor(b_005_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

```{r harmo 5 cities w1}
#can not seperate 0 correct answers and Missing
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_cog_imm$id)
JSTAR_aksst_ds_w1$cog_imm_c <- 0
for(i in 1:length(JSTAR_aksst_ds_w1$cog_imm_c))
{
  if(is.na(JSTAR_5cities_w1_cog_imm$b_005_a[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_b[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_c[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_d[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_e[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_f[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_g[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_h[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_i[i])==TRUE&is.na(JSTAR_5cities_w1_cog_imm$b_005_j[i])==TRUE)
    JSTAR_aksst_ds_w1$cog_imm_c[i] <- 999
  else
    JSTAR_aksst_ds_w1$cog_imm_c[i] <- sum(JSTAR_5cities_w1_cog_imm$b_005_a[i],JSTAR_5cities_w1_cog_imm$b_005_b[i],JSTAR_5cities_w1_cog_imm$b_005_c[i],JSTAR_5cities_w1_cog_imm$b_005_d[i],JSTAR_5cities_w1_cog_imm$b_005_e[i],JSTAR_5cities_w1_cog_imm$b_005_f[i],JSTAR_5cities_w1_cog_imm$b_005_g[i],JSTAR_5cities_w1_cog_imm$b_005_h[i],JSTAR_5cities_w1_cog_imm$b_005_i[i],JSTAR_5cities_w1_cog_imm$b_005_j[i],na.rm=TRUE)
}
JSTAR_aksst_ds_w1$cog_imm_c <- labelled(JSTAR_aksst_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(JSTAR_aksst_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_aksst_ds_w1$cog_imm <- car::recode(JSTAR_aksst_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_aksst_ds_w1$cog_imm <- labelled(JSTAR_aksst_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1}
vari <- JSTAR_aksst_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_aksst_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1}
Continuous <- c(sum(na.omit(JSTAR_aksst_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_aksst_ds_w1[[2]])>Q & na.omit(JSTAR_aksst_ds_w1[[2]])<900), sum(na.omit(JSTAR_aksst_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_aksst_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 5 cities w1, echo=FALSE}
label(JSTAR_aksst_ds_w1$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_aksst_ds_w1$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_aksst_ds_w1
save(cog_imm, file = "../RData/aksst_w1/cog_imm.RData")
rm(cog_imm)

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$cog_imm <- car::recode(JSTAR_m_aksst_ds_w1$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_aksst_ds_w1$cog_imm_c <- car::recode(JSTAR_m_aksst_ds_w1$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `b_005_a`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_b`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_c`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_d`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_e`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_f`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_g`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_h`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_i`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_j`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 5 cities w2}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_cog_imm','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('b_005_a','b_005_b','b_005_c','b_005_d','b_005_e','b_005_f','b_005_g','b_005_h','b_005_i','b_005_j'), missings = TRUE)
JSTAR_5cities_w2_cog_imm <- opal.execute(o,'JSTAR_5cities_w2_cog_imm')
```

```{r local 5 cities w2}
vari <- JSTAR_5cities_w2_cog_imm$b_005_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_imm$b_005_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_imm, aes(x=factor(b_005_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

```{r harmo 5 cities w2}
#can not seperate 0 correct answers and Missing
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_cog_imm$id)
JSTAR_aksst_ds_w2$cog_imm_c <- rep(0,length(JSTAR_aksst_ds_w2$id))
for(i in 1:length(JSTAR_aksst_ds_w2$cog_imm_c))
{
  if(is.na(JSTAR_5cities_w2_cog_imm$b_005_a[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_b[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_c[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_d[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_e[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_f[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_g[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_h[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_i[i])==TRUE&is.na(JSTAR_5cities_w2_cog_imm$b_005_j[i])==TRUE)
    JSTAR_aksst_ds_w2$cog_imm_c[i] <- 999
  else
    JSTAR_aksst_ds_w2$cog_imm_c[i] <- sum(JSTAR_5cities_w2_cog_imm$b_005_a[i],JSTAR_5cities_w2_cog_imm$b_005_b[i],JSTAR_5cities_w2_cog_imm$b_005_c[i],JSTAR_5cities_w2_cog_imm$b_005_d[i],JSTAR_5cities_w2_cog_imm$b_005_e[i],JSTAR_5cities_w2_cog_imm$b_005_f[i],JSTAR_5cities_w2_cog_imm$b_005_g[i],JSTAR_5cities_w2_cog_imm$b_005_h[i],JSTAR_5cities_w2_cog_imm$b_005_i[i],JSTAR_5cities_w2_cog_imm$b_005_j[i],na.rm=TRUE)
}
#JSTAR_aksst_ds_w2$cog_imm_c <- car::recode(JSTAR_5cities_w2_cog_imm$b_005_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_aksst_ds_w2$cog_imm_c <- labelled(JSTAR_aksst_ds_w2$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(JSTAR_aksst_ds_w2$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_aksst_ds_w2$cog_imm <- car::recode(JSTAR_aksst_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_aksst_ds_w2$cog_imm <- labelled(JSTAR_aksst_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2}
vari <- JSTAR_aksst_ds_w2$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_aksst_ds_w2$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2}
Continous <- c(sum(na.omit(JSTAR_aksst_ds_w2[[2]])<=Q), sum(na.omit(JSTAR_aksst_ds_w2[[2]])>Q & na.omit(JSTAR_aksst_ds_w2[[2]])<900), sum(na.omit(JSTAR_aksst_ds_w2[[2]])==999))
Dicotomic <- table(JSTAR_aksst_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 5 cities w2, echo=FALSE}
label(JSTAR_aksst_ds_w2$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_aksst_ds_w2$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_aksst_ds_w2
save(cog_imm, file = "../RData/aksst_w2/cog_imm.RData")
rm(cog_imm)

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$cog_imm <- car::recode(JSTAR_m_aksst_ds_w2$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_aksst_ds_w2$cog_imm_c <- car::recode(JSTAR_m_aksst_ds_w2$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```




### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_008_0`
* Label: `11F-008-0:GO TO "11F-008-1/"11F-008-2/"11F-008-3 DEPENDING ON THE RANDOM VARIABLE`
* Categories:
    + `1`
    + `2`
    + `3`
* Missings
   + `NA`
   
* Name: `f_008_1_a`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: MASK`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_1_b`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: YAWN"`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_c`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SWING`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_d`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SILVER`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_e`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: CARIES`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_f`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: DIAMOND`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_g`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SALAD`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_h`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: TENNIS`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_i`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SCARF`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_1_j`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: BABY CHICK`
* Categories:
    + `1`
* Missings
   + `NA`

   
* Name: `f_008_2_a`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: PET`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_2_b`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: DANGO`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_c`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: SLIPPER`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_d`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: TELEPHONE POLE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_e`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: DISH`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_f`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: COAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_g`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: MILK`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_h`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: POOL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_i`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: SPRAY`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_2_j`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: FISH SAUSAGE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_a`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: RIBBON`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_3_b`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: FOX`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_c`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: STRAW`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_d`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: SAND BEACH`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_e`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: BROWN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_f`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_g`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: CROW`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_h`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: NOTEBOOK`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_i`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: CREAM`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_3_j`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: TUNA`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 5 cities w3}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_cog_imm','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('f_008_0','f_008_1_a','f_008_1_b','f_008_1_c','f_008_1_d','f_008_1_e','f_008_1_f','f_008_1_g','f_008_1_h','f_008_1_i','f_008_1_j','f_008_2_a','f_008_2_b','f_008_2_c','f_008_2_d','f_008_2_e','f_008_2_f','f_008_2_g','f_008_2_h','f_008_2_i','f_008_2_j','f_008_3_a','f_008_3_b','f_008_3_c','f_008_3_d','f_008_3_e','f_008_3_f','f_008_3_g','f_008_3_h','f_008_3_i','f_008_3_j'), missings = TRUE)
JSTAR_5cities_w3_cog_imm <- opal.execute(o,'JSTAR_5cities_w3_cog_imm')
```

```{r local 5 cities w3}
vari <- JSTAR_5cities_w3_cog_imm$f_008_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_1_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_1_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_2_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_2_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_5cities_w3_cog_imm$f_008_3_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_cog_imm, aes(x=factor(f_008_3_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 from the list asked to each individual and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

```{r harmo 5 cities w3}
#can not seperate 0 correct answers and Missing
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_cog_imm$id)
JSTAR_aksst_ds_w3$cog_imm_c <- rep(0,length(JSTAR_aksst_ds_w3$id))
for(i in 1:length(JSTAR_aksst_ds_w3$cog_imm_c))
{
  if(is.na(JSTAR_5cities_w3_cog_imm$f_008_0[i]))  
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- 999
  else{
      if(JSTAR_5cities_w3_cog_imm$f_008_0[i]==1){
         if(is.na(JSTAR_5cities_w3_cog_imm$f_008_1_a[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_b[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_c[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_d[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_e[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_f[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_g[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_h[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_i[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_1_j[i])==TRUE)
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- 999
          else
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- sum(JSTAR_5cities_w3_cog_imm$f_008_1_a[i],JSTAR_5cities_w3_cog_imm$f_008_1_b[i],JSTAR_5cities_w3_cog_imm$f_008_1_c[i],JSTAR_5cities_w3_cog_imm$f_008_1_d[i],JSTAR_5cities_w3_cog_imm$f_008_1_e[i],JSTAR_5cities_w3_cog_imm$f_008_1_f[i],JSTAR_5cities_w3_cog_imm$f_008_1_g[i],JSTAR_5cities_w3_cog_imm$f_008_1_h[i],JSTAR_5cities_w3_cog_imm$f_008_1_i[i],JSTAR_5cities_w3_cog_imm$f_008_1_j[i],na.rm=TRUE)}
      else{
          if(JSTAR_5cities_w3_cog_imm$f_008_0[i]==2){
            if(is.na(JSTAR_5cities_w3_cog_imm$f_008_2_a[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_b[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_c[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_d[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_e[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_f[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_g[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_h[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_i[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_2_j[i])==TRUE)
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- 999
            else
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- sum(JSTAR_5cities_w3_cog_imm$f_008_2_a[i],JSTAR_5cities_w3_cog_imm$f_008_2_b[i],JSTAR_5cities_w3_cog_imm$f_008_2_c[i],JSTAR_5cities_w3_cog_imm$f_008_2_d[i],JSTAR_5cities_w3_cog_imm$f_008_2_e[i],JSTAR_5cities_w3_cog_imm$f_008_2_f[i],JSTAR_5cities_w3_cog_imm$f_008_2_g[i],JSTAR_5cities_w3_cog_imm$f_008_2_h[i],JSTAR_5cities_w3_cog_imm$f_008_2_i[i],JSTAR_5cities_w3_cog_imm$f_008_2_j[i],na.rm=TRUE)}  
          else{
              if(JSTAR_5cities_w3_cog_imm$f_008_0[i]==3){
                if(is.na(JSTAR_5cities_w3_cog_imm$f_008_3_a[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_b[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_c[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_d[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_e[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_f[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_g[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_h[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_i[i])==TRUE&is.na(JSTAR_5cities_w3_cog_imm$f_008_3_j[i])==TRUE)
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- 999
                else
    JSTAR_aksst_ds_w3$cog_imm_c[i] <- sum(JSTAR_5cities_w3_cog_imm$f_008_3_a[i],JSTAR_5cities_w3_cog_imm$f_008_3_b[i],JSTAR_5cities_w3_cog_imm$f_008_3_c[i],JSTAR_5cities_w3_cog_imm$f_008_3_d[i],JSTAR_5cities_w3_cog_imm$f_008_3_e[i],JSTAR_5cities_w3_cog_imm$f_008_3_f[i],JSTAR_5cities_w3_cog_imm$f_008_3_g[i],JSTAR_5cities_w3_cog_imm$f_008_3_h[i],JSTAR_5cities_w3_cog_imm$f_008_3_i[i],JSTAR_5cities_w3_cog_imm$f_008_3_j[i],na.rm=TRUE)}}}
}
}
#JSTAR_aksst_ds_w3$cog_imm_c <- car::recode(JSTAR_5cities_w3_cog_imm$f_008_1_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_aksst_ds_w3$cog_imm_c <- labelled(JSTAR_aksst_ds_w3$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))


##cog_imm
Q <- quantile(car::recode(JSTAR_aksst_ds_w3$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_aksst_ds_w3$cog_imm <- car::recode(JSTAR_aksst_ds_w3[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_aksst_ds_w3$cog_imm <- labelled(JSTAR_aksst_ds_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w3}
vari <- JSTAR_aksst_ds_w3$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_aksst_ds_w3$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3}
Continuous <- c(sum(na.omit(JSTAR_aksst_ds_w3[[2]])<=Q), sum(na.omit(JSTAR_aksst_ds_w3[[2]])>Q & na.omit(JSTAR_aksst_ds_w3[[2]])<900), sum(na.omit(JSTAR_aksst_ds_w3[[2]])==999))
Dicotomic <- table(JSTAR_aksst_ds_w3[[3]], useNA = "ifany")
C <- rbind(Continuous,Dicotomic)
colnames(C) <- c("0:2->0","3:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 5 cities w3, echo=FALSE}
label(JSTAR_aksst_ds_w3$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_aksst_ds_w3$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_aksst_ds_w3
save(cog_imm, file = "../RData/aksst_w3/cog_imm.RData")
rm(cog_imm)

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$cog_imm <- car::recode(JSTAR_m_aksst_ds_w3$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_aksst_ds_w3$cog_imm_c <- car::recode(JSTAR_m_aksst_ds_w3$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```


## 3 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `b_005_a`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_b`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_c`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_d`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_e`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_f`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_g`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_h`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_i`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_j`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 3 cities w1}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_cog_imm','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('b_005_a','b_005_b','b_005_c','b_005_d','b_005_e','b_005_f','b_005_g','b_005_h','b_005_i','b_005_j'), missings = TRUE)
JSTAR_3cities_w1_cog_imm <- opal.execute(o,'JSTAR_3cities_w1_cog_imm')
```

```{r local 3 cities w1}
vari <- JSTAR_3cities_w1_cog_imm$b_005_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_imm$b_005_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_imm, aes(x=factor(b_005_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`


```{r harmo 3 cities w1}
#can not seperate 0 correct answers and Missing
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_cog_imm$id)
JSTAR_cth_ds_w1$cog_imm_c <- rep(0,length(JSTAR_cth_ds_w1$id))
for(i in 1:length(JSTAR_cth_ds_w1$cog_imm_c))
{
  if(is.na(JSTAR_3cities_w1_cog_imm$b_005_a[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_b[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_c[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_d[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_e[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_f[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_g[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_h[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_i[i])==TRUE&is.na(JSTAR_3cities_w1_cog_imm$b_005_j[i])==TRUE)
    JSTAR_cth_ds_w1$cog_imm_c[i] <- 999
  else
    JSTAR_cth_ds_w1$cog_imm_c[i] <- sum(JSTAR_3cities_w1_cog_imm$b_005_a[i],JSTAR_3cities_w1_cog_imm$b_005_b[i],JSTAR_3cities_w1_cog_imm$b_005_c[i],JSTAR_3cities_w1_cog_imm$b_005_d[i],JSTAR_3cities_w1_cog_imm$b_005_e[i],JSTAR_3cities_w1_cog_imm$b_005_f[i],JSTAR_3cities_w1_cog_imm$b_005_g[i],JSTAR_3cities_w1_cog_imm$b_005_h[i],JSTAR_3cities_w1_cog_imm$b_005_i[i],JSTAR_3cities_w1_cog_imm$b_005_j[i],na.rm=TRUE)
}
#JSTAR_cth_ds_w1$cog_imm_c <- car::recode(JSTAR_3cities_w1_cog_imm$b_005_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_cth_ds_w1$cog_imm_c <- labelled(JSTAR_cth_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(JSTAR_cth_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_cth_ds_w1$cog_imm <- car::recode(JSTAR_cth_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_cth_ds_w1$cog_imm <- labelled(JSTAR_cth_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1}
vari <- JSTAR_cth_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_cth_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1}
Continuous <- c(sum(na.omit(JSTAR_cth_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_cth_ds_w1[[2]])>Q & na.omit(JSTAR_cth_ds_w1[[2]])<900), sum(na.omit(JSTAR_cth_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_cth_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 3 cities w1, echo=FALSE}
label(JSTAR_cth_ds_w1$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_cth_ds_w1$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_cth_ds_w1
save(cog_imm, file = "../RData/cth_w1/cog_imm.RData")
rm(cog_imm)

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$cog_imm <- car::recode(JSTAR_m_cth_ds_w1$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_cth_ds_w1$cog_imm_c <- car::recode(JSTAR_m_cth_ds_w1$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```



## 2 cities 

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `b_005_a`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_b`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_c`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_d`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_e`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_f`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_g`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_h`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_005_i`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_005_j`
* Label: `B-005:THE WORDS RESOPNDENT CORRECTLY RECALLS - 1ST TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 2 cities w1}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_cog_imm','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('b_005_a','b_005_b','b_005_c','b_005_d','b_005_e','b_005_f','b_005_g','b_005_h','b_005_i','b_005_j'), missings = TRUE)
JSTAR_2cities_w1_cog_imm <- opal.execute(o,'JSTAR_2cities_w1_cog_imm')
```

```{r local 2 cities w1}
vari <- JSTAR_2cities_w1_cog_imm$b_005_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_imm$b_005_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_imm, aes(x=factor(b_005_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

```{r harmo 2 cities w1}
#can not seperate 0 correct answers and Missing
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_cog_imm$id)
JSTAR_tn_ds_w1$cog_imm_c <- rep(0,length(JSTAR_tn_ds_w1$id))
for(i in 1:length(JSTAR_tn_ds_w1$cog_imm_c))
{
  if(is.na(JSTAR_2cities_w1_cog_imm$b_005_a[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_b[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_c[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_d[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_e[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_f[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_g[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_h[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_i[i])==TRUE&is.na(JSTAR_2cities_w1_cog_imm$b_005_j[i])==TRUE)
    JSTAR_tn_ds_w1$cog_imm_c[i] <- 999
  else
    JSTAR_tn_ds_w1$cog_imm_c[i] <- sum(JSTAR_2cities_w1_cog_imm$b_005_a[i],JSTAR_2cities_w1_cog_imm$b_005_b[i],JSTAR_2cities_w1_cog_imm$b_005_c[i],JSTAR_2cities_w1_cog_imm$b_005_d[i],JSTAR_2cities_w1_cog_imm$b_005_e[i],JSTAR_2cities_w1_cog_imm$b_005_f[i],JSTAR_2cities_w1_cog_imm$b_005_g[i],JSTAR_2cities_w1_cog_imm$b_005_h[i],JSTAR_2cities_w1_cog_imm$b_005_i[i],JSTAR_2cities_w1_cog_imm$b_005_j[i],na.rm=TRUE)
}
#JSTAR_tn_ds_w1$cog_imm_c <- car::recode(JSTAR_2cities_w1_cog_imm$b_005_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_tn_ds_w1$cog_imm_c <- labelled(JSTAR_tn_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(JSTAR_tn_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_tn_ds_w1$cog_imm <- car::recode(JSTAR_tn_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_tn_ds_w1$cog_imm <- labelled(JSTAR_tn_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1}
vari <- JSTAR_tn_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_tn_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1}
Continous <- c(sum(na.omit(JSTAR_tn_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_tn_ds_w1[[2]])>Q & na.omit(JSTAR_tn_ds_w1[[2]])<900), sum(na.omit(JSTAR_tn_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_tn_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 2 cities w1, echo=FALSE}
label(JSTAR_tn_ds_w1$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_tn_ds_w1$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_tn_ds_w1
save(cog_imm, file = "../RData/tn_w1/cog_imm.RData")
rm(cog_imm)

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$cog_imm <- car::recode(JSTAR_m_tn_ds_w1$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_tn_ds_w1$cog_imm_c <- car::recode(JSTAR_m_tn_ds_w1$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `f_008_0`
* Label: `11F-008-0:GO TO "11F-008-1/"11F-008-2/"11F-008-3 DEPENDING ON THE RANDOM VARIABLE`
* Categories:
    + `1`
    + `2`
    + `3`
* Missings
   + `NA`
   
* Name: `f_008_1_a`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: MASK`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_1_b`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: YAWN"`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_c`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SWING`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_d`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SILVER`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_e`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: CARIES`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_f`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: DIAMOND`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_g`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SALAD`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_h`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: TENNIS`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_1_i`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: SCARF`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_1_j`
* Label: `11F-008-1(MA):MEMORIZING VOCABULARY TEST: BABY CHICK`
* Categories:
    + `1`
* Missings
   + `NA`

   
* Name: `f_008_2_a`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: PET`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_2_b`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: DANGO`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_c`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: SLIPPER`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_d`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: TELEPHONE POLE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_e`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: DISH`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_f`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: COAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_g`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: MILK`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_h`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: POOL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_2_i`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: SPRAY`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_2_j`
* Label: `11F-008-2(MA):MEMORIZING VOCABULARY TEST: FISH SAUSAGE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_a`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: RIBBON`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_3_b`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: FOX`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_c`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: STRAW`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_d`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: SAND BEACH`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_e`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: BROWN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_f`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_g`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: CROW`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_h`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: NOTEBOOK`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `f_008_3_i`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: CREAM`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `f_008_3_j`
* Label: `11F-008-3(MA):MEMORIZING VOCABULARY TEST: TUNA`
* Categories:
    + `1`
* Missings
   + `NA`

```{r assign 2 cities w2}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_cog_imm','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('f_008_0','f_008_1_a','f_008_1_b','f_008_1_c','f_008_1_d','f_008_1_e','f_008_1_f','f_008_1_g','f_008_1_h','f_008_1_i','f_008_1_j','f_008_2_a','f_008_2_b','f_008_2_c','f_008_2_d','f_008_2_e','f_008_2_f','f_008_2_g','f_008_2_h','f_008_2_i','f_008_2_j','f_008_3_a','f_008_3_b','f_008_3_c','f_008_3_d','f_008_3_e','f_008_3_f','f_008_3_g','f_008_3_h','f_008_3_i','f_008_3_j'), missings = TRUE)
JSTAR_2cities_w2_cog_imm <- opal.execute(o,'JSTAR_2cities_w2_cog_imm')
```

```{r local 2 cities w2}
vari <- JSTAR_2cities_w2_cog_imm$f_008_0
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_1_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_1_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_2_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_2_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- JSTAR_2cities_w2_cog_imm$f_008_3_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_cog_imm, aes(x=factor(f_008_3_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

```{r harmo 2 cities w2}
#can not seperate 0 correct answers and Missing
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_cog_imm$id)
JSTAR_tn_ds_w2$cog_imm_c <- rep(0,length(JSTAR_tn_ds_w2$id))
for(i in 1:length(JSTAR_tn_ds_w2$cog_imm_c))
{
  if(is.na(JSTAR_2cities_w2_cog_imm$f_008_0[i]))  
    JSTAR_tn_ds_w2$cog_imm_c[i] <- 999
  else{
      if(JSTAR_2cities_w2_cog_imm$f_008_0[i]==1){
         if(is.na(JSTAR_2cities_w2_cog_imm$f_008_1_a[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_b[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_c[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_d[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_e[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_f[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_g[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_h[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_i[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_1_j[i])==TRUE)
    JSTAR_tn_ds_w2$cog_imm_c[i] <- 999
          else
    JSTAR_tn_ds_w2$cog_imm_c[i] <- sum(JSTAR_2cities_w2_cog_imm$f_008_1_a[i],JSTAR_2cities_w2_cog_imm$f_008_1_b[i],JSTAR_2cities_w2_cog_imm$f_008_1_c[i],JSTAR_2cities_w2_cog_imm$f_008_1_d[i],JSTAR_2cities_w2_cog_imm$f_008_1_e[i],JSTAR_2cities_w2_cog_imm$f_008_1_f[i],JSTAR_2cities_w2_cog_imm$f_008_1_g[i],JSTAR_2cities_w2_cog_imm$f_008_1_h[i],JSTAR_2cities_w2_cog_imm$f_008_1_i[i],JSTAR_2cities_w2_cog_imm$f_008_1_j[i],na.rm=TRUE)}
      else{
          if(JSTAR_2cities_w2_cog_imm$f_008_0[i]==2){
            if(is.na(JSTAR_2cities_w2_cog_imm$f_008_2_a[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_b[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_c[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_d[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_e[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_f[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_g[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_h[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_i[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_2_j[i])==TRUE)
    JSTAR_tn_ds_w2$cog_imm_c[i] <- 999
            else
    JSTAR_tn_ds_w2$cog_imm_c[i] <- sum(JSTAR_2cities_w2_cog_imm$f_008_2_a[i],JSTAR_2cities_w2_cog_imm$f_008_2_b[i],JSTAR_2cities_w2_cog_imm$f_008_2_c[i],JSTAR_2cities_w2_cog_imm$f_008_2_d[i],JSTAR_2cities_w2_cog_imm$f_008_2_e[i],JSTAR_2cities_w2_cog_imm$f_008_2_f[i],JSTAR_2cities_w2_cog_imm$f_008_2_g[i],JSTAR_2cities_w2_cog_imm$f_008_2_h[i],JSTAR_2cities_w2_cog_imm$f_008_2_i[i],JSTAR_2cities_w2_cog_imm$f_008_2_j[i],na.rm=TRUE)}  
          else{
              if(JSTAR_2cities_w2_cog_imm$f_008_0[i]==3){
                if(is.na(JSTAR_2cities_w2_cog_imm$f_008_3_a[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_b[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_c[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_d[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_e[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_f[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_g[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_h[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_i[i])==TRUE&is.na(JSTAR_2cities_w2_cog_imm$f_008_3_j[i])==TRUE)
    JSTAR_tn_ds_w2$cog_imm_c[i] <- 999
                else
    JSTAR_tn_ds_w2$cog_imm_c[i] <- sum(JSTAR_2cities_w2_cog_imm$f_008_3_a[i],JSTAR_2cities_w2_cog_imm$f_008_3_b[i],JSTAR_2cities_w2_cog_imm$f_008_3_c[i],JSTAR_2cities_w2_cog_imm$f_008_3_d[i],JSTAR_2cities_w2_cog_imm$f_008_3_e[i],JSTAR_2cities_w2_cog_imm$f_008_3_f[i],JSTAR_2cities_w2_cog_imm$f_008_3_g[i],JSTAR_2cities_w2_cog_imm$f_008_3_h[i],JSTAR_2cities_w2_cog_imm$f_008_3_i[i],JSTAR_2cities_w2_cog_imm$f_008_3_j[i],na.rm=TRUE)}}}
}
}
#JSTAR_tn_ds_w2$cog_imm_c <- car::recode(JSTAR_2cities_w2_cog_imm$f_008_1_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_tn_ds_w2$cog_imm_c <- labelled(JSTAR_tn_ds_w2$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(JSTAR_tn_ds_w2$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_tn_ds_w2$cog_imm <- car::recode(JSTAR_tn_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_tn_ds_w2$cog_imm <- labelled(JSTAR_tn_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_tn_ds_w2$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w2, echo=FALSE}
Continous <- c(sum(na.omit(JSTAR_tn_ds_w2[[2]])<=Q), sum(na.omit(JSTAR_tn_ds_w2[[2]])>Q & na.omit(JSTAR_tn_ds_w2[[2]])<900), sum(na.omit(JSTAR_tn_ds_w2[[2]])==999))
Dicotomic <- table(JSTAR_tn_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 2 cities w2, echo=FALSE}
label(JSTAR_tn_ds_w2$cog_imm_c) <- ds_label_cog_imm_c
label(JSTAR_tn_ds_w2$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
cog_imm <- JSTAR_tn_ds_w2
save(cog_imm, file = "../RData/tn_w2/cog_imm.RData")
rm(cog_imm)

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$cog_imm <- car::recode(JSTAR_m_tn_ds_w2$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_tn_ds_w2$cog_imm_c <- car::recode(JSTAR_m_tn_ds_w2$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation

Recall of 10 words (one trial). The word list as well as the protocol were changed for the 2011 survey in 5 and 2 cities (i.e. 3rd wave 5 cities and 2nd wave 2 cities). In the 2011 survey, three versions of the word list were randomly allocated between the participants. The words  used in 2011 in 5 and 2 cities were different from those used in previous waves.


[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
