---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process



## aksst

### Wave 1

#### Study-specific variable description


| **Name** |`b_003_1`|`b_003_2`|`b_003_3`|`b_003_4`|
|-|-|-|-|-|
| **Label** |`DATE-YEAR`|`DATE-MONTH`|`DATE-DAY OF MONTH`|`DAY OF THE WEEK`|
| **Table name** |`jstar_2007_5cities`|`jstar_2007_5cities`|`jstar_2007_5cities`|`jstar_2007_5cities`|
| **Categories** |`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|
| **Missings** |`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|
| **Description** |  |  |  |  |


```{r assign 5 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_orientation','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('b_003_1','b_003_2','b_003_3','b_003_4'), missings = TRUE)
```

```{r local 5 cities w1, echo=F}
JSTAR_5cities_w1_orientation <- opal.execute(o,'JSTAR_5cities_w1_orientation')
vari <- JSTAR_5cities_w1_orientation$b_003_1
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_1")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w1_orientation, aes(x=factor(b_003_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
vari <- JSTAR_5cities_w1_orientation$b_003_2
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_2")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w1_orientation, aes(x=factor(b_003_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- JSTAR_5cities_w1_orientation$b_003_3
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_3")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w1_orientation, aes(x=factor(b_003_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- JSTAR_5cities_w1_orientation$b_003_4
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_4")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w1_orientation, aes(x=factor(b_003_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `NA into 999`

**R script:**
```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_orientation$id)
JSTAR_aksst_ds_w1$orientation <- rep(999,length(JSTAR_aksst_ds_w1$id))
JSTAR_aksst_ds_w1$orientation[((JSTAR_5cities_w1_orientation$b_003_1==1)&(JSTAR_5cities_w1_orientation$b_003_2==1)&(JSTAR_5cities_w1_orientation$b_003_3==1)&(JSTAR_5cities_w1_orientation$b_003_4==1))]<-1
JSTAR_aksst_ds_w1$orientation[((JSTAR_5cities_w1_orientation$b_003_1==3)|(JSTAR_5cities_w1_orientation$b_003_2==3)|(JSTAR_5cities_w1_orientation$b_003_3==3)|(JSTAR_5cities_w1_orientation$b_003_4==3))]<-997
JSTAR_aksst_ds_w1$orientation[((JSTAR_5cities_w1_orientation$b_003_1==2)|(JSTAR_5cities_w1_orientation$b_003_2==2)|(JSTAR_5cities_w1_orientation$b_003_3==2)|(JSTAR_5cities_w1_orientation$b_003_4==2))]<- 0
JSTAR_aksst_ds_w1$orientation <- labelled(JSTAR_aksst_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=F}
vari <- JSTAR_aksst_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=F}
AfterH <- table(JSTAR_aksst_ds_w1$orientation)
combi<-sum(na.omit((JSTAR_5cities_w1_orientation$b_003_1==1)&(JSTAR_5cities_w1_orientation$b_003_2==1)&(JSTAR_5cities_w1_orientation$b_003_3==1)&(JSTAR_5cities_w1_orientation$b_003_4==1)))
ref<-sum(na.omit((JSTAR_5cities_w1_orientation$b_003_1==3)|(JSTAR_5cities_w1_orientation$b_003_2==3)|(JSTAR_5cities_w1_orientation$b_003_3==3)|(JSTAR_5cities_w1_orientation$b_003_4==3)))
nota<-length(JSTAR_5cities_w1_orientation$b_003_1)-length(na.omit(JSTAR_5cities_w1_orientation$b_003_1))
BeforeH <- c(length(JSTAR_5cities_w1_orientation$b_003_1)-combi-nota-ref,combi,ref,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","3->997","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w1, echo=FALSE}

label(JSTAR_aksst_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- JSTAR_aksst_ds_w1
save(orientation, file = "../RData/aksst_w1/orientation.RData")

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$orientation <- car::recode(JSTAR_m_aksst_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



<!--### JSTAR - 5 cities - Wave 2-->

### Wave 2

#### Study-specific variable description



| **Name** |`b_003_1`|`b_003_2`|`b_003_3`|`b_003_4`|
|-|-|-|-|-|
| **Label** |`DATE-YEAR`|`DATE-MONTH`|`DATE-DAY OF MONTH`|`DAY OF THE WEEK`|
| **Table name** |`jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|
| **Categories** |`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|
| **Missings** |`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|
| **Description** |  |  |  |  |




```{r assign 5 cities w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_orientation','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('b_003_1','b_003_2','b_003_3','b_003_4'), missings = TRUE)
```

```{r local 5 cities w2, echo=F}
JSTAR_5cities_w2_orientation <- opal.execute(o,'JSTAR_5cities_w2_orientation')
vari <- JSTAR_5cities_w2_orientation$b_003_1
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_1")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w2_orientation, aes(x=factor(b_003_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
vari <- JSTAR_5cities_w2_orientation$b_003_2
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_2")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w2_orientation, aes(x=factor(b_003_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- JSTAR_5cities_w2_orientation$b_003_3
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_3")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w2_orientation, aes(x=factor(b_003_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- JSTAR_5cities_w2_orientation$b_003_4
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_4")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_5cities_w2_orientation, aes(x=factor(b_003_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `NA into 999`

**R script:**
```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_orientation$id)
JSTAR_aksst_ds_w2$orientation <- rep( 999,length(JSTAR_aksst_ds_w2$id))
JSTAR_aksst_ds_w2$orientation[((JSTAR_5cities_w2_orientation$b_003_1==1)&(JSTAR_5cities_w2_orientation$b_003_2==1)&(JSTAR_5cities_w2_orientation$b_003_3==1)&(JSTAR_5cities_w2_orientation$b_003_4==1))]<-1
JSTAR_aksst_ds_w2$orientation[((JSTAR_5cities_w2_orientation$b_003_1==3)|(JSTAR_5cities_w2_orientation$b_003_2==3)|(JSTAR_5cities_w2_orientation$b_003_3==3)|(JSTAR_5cities_w2_orientation$b_003_4==3))]<-997
JSTAR_aksst_ds_w2$orientation[((JSTAR_5cities_w2_orientation$b_003_1==2)|(JSTAR_5cities_w2_orientation$b_003_2==2)|(JSTAR_5cities_w2_orientation$b_003_3==2)|(JSTAR_5cities_w2_orientation$b_003_4==2))]<- 0
JSTAR_aksst_ds_w2$orientation <- labelled(JSTAR_aksst_ds_w2$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=F}
vari <- JSTAR_aksst_ds_w2$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=F}
AfterH <- table(JSTAR_aksst_ds_w2$orientation)
combi<-sum(na.omit((JSTAR_5cities_w2_orientation$b_003_1==1)&(JSTAR_5cities_w2_orientation$b_003_2==1)&(JSTAR_5cities_w2_orientation$b_003_3==1)&(JSTAR_5cities_w2_orientation$b_003_4==1)))
ref<-sum(na.omit((JSTAR_5cities_w2_orientation$b_003_1==3)|(JSTAR_5cities_w2_orientation$b_003_2==3)|(JSTAR_5cities_w2_orientation$b_003_3==3)|(JSTAR_5cities_w2_orientation$b_003_4==3)))
nota<-length(JSTAR_5cities_w2_orientation$b_003_1)-min(length(na.omit(JSTAR_5cities_w2_orientation$b_003_1)),length(na.omit(JSTAR_5cities_w2_orientation$b_003_2)),length(na.omit(JSTAR_5cities_w2_orientation$b_003_3)),length(na.omit(JSTAR_5cities_w2_orientation$b_003_4)))
BeforeH <- c(length(JSTAR_5cities_w2_orientation$b_003_1)-combi-nota-ref,combi,ref,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","3->997","NA->999") 
kable(C)
```






```{r importOPAL 5 cities w2, echo=FALSE}

label(JSTAR_aksst_ds_w2$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
orientation <- JSTAR_aksst_ds_w2
save(orientation, file = "../RData/aksst_w2/orientation.RData")

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$orientation <- car::recode(JSTAR_m_aksst_ds_w2$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



<!--### JSTAR - 5 cities - Wave 3-->

### Wave 3

Not found.





<!--### JSTAR - 2 cities - Wave 1-->

## tn

### Wave 1

#### Study-specific variable description



| **Name** |`b_003_1`|`b_003_2`|`b_003_3`|`b_003_4`|
|-|-|-|-|-|
| **Label** |`DATE-YEAR`|`DATE-MONTH`|`DATE-DAY OF MONTH`|`DAY OF THE WEEK`|
| **Table name** |`jstar_2009_2cities`|`jstar_2009_2cities`|`jstar_2009_2cities`|`jstar_2009_2cities`|
| **Categories** |`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|
| **Missings** |`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|
| **Description** |  |  |  |  |


```{r assign 2 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_orientation','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('b_003_1','b_003_2','b_003_3','b_003_4'), missings = TRUE)
```

```{r local 2 cities w1, echo=F}
JSTAR_2cities_w1_orientation <- opal.execute(o,'JSTAR_2cities_w1_orientation')
vari <- JSTAR_2cities_w1_orientation$b_003_1
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_1")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_2cities_w1_orientation, aes(x=factor(b_003_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
vari <- JSTAR_2cities_w1_orientation$b_003_2
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_2")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_2cities_w1_orientation, aes(x=factor(b_003_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- JSTAR_2cities_w1_orientation$b_003_3
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_3")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_2cities_w1_orientation, aes(x=factor(b_003_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- JSTAR_2cities_w1_orientation$b_003_4
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_4")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_2cities_w1_orientation, aes(x=factor(b_003_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `NA into 999`

**R script:**
```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_orientation$id)
JSTAR_tn_ds_w1$orientation <- rep( 999,length(JSTAR_tn_ds_w1$id))
JSTAR_tn_ds_w1$orientation[((JSTAR_2cities_w1_orientation$b_003_1==1)&(JSTAR_2cities_w1_orientation$b_003_2==1)&(JSTAR_2cities_w1_orientation$b_003_3==1)&(JSTAR_2cities_w1_orientation$b_003_4==1))]<-1
JSTAR_tn_ds_w1$orientation[((JSTAR_2cities_w1_orientation$b_003_1==3)|(JSTAR_2cities_w1_orientation$b_003_2==3)|(JSTAR_2cities_w1_orientation$b_003_3==3)|(JSTAR_2cities_w1_orientation$b_003_4==3))]<-997
JSTAR_tn_ds_w1$orientation[((JSTAR_2cities_w1_orientation$b_003_1==2)|(JSTAR_2cities_w1_orientation$b_003_2==2)|(JSTAR_2cities_w1_orientation$b_003_3==2)|(JSTAR_2cities_w1_orientation$b_003_4==2))]<- 0
JSTAR_tn_ds_w1$orientation <- labelled(JSTAR_tn_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=F}
vari <- JSTAR_tn_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=F}
AfterH <- table(JSTAR_tn_ds_w1$orientation)
combi<-sum(na.omit((JSTAR_2cities_w1_orientation$b_003_1==1)&(JSTAR_2cities_w1_orientation$b_003_2==1)&(JSTAR_2cities_w1_orientation$b_003_3==1)&(JSTAR_2cities_w1_orientation$b_003_4==1)))
ref<-sum(na.omit((JSTAR_2cities_w1_orientation$b_003_1==3)|(JSTAR_2cities_w1_orientation$b_003_2==3)|(JSTAR_2cities_w1_orientation$b_003_3==3)|(JSTAR_2cities_w1_orientation$b_003_4==3)))
nota<-length(JSTAR_2cities_w1_orientation$b_003_1)-min(length(na.omit(JSTAR_2cities_w1_orientation$b_003_1)),length(na.omit(JSTAR_2cities_w1_orientation$b_003_2)),length(na.omit(JSTAR_2cities_w1_orientation$b_003_3)),length(na.omit(JSTAR_2cities_w1_orientation$b_003_4)))
BeforeH <- c(length(JSTAR_2cities_w1_orientation$b_003_1)-combi-nota-ref,combi,ref,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","3->997","NA->999") 
kable(C)
```






```{r importOPAL 2 cities w1, echo=FALSE}

label(JSTAR_tn_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- JSTAR_tn_ds_w1
save(orientation, file = "../RData/tn_w1/orientation.RData")

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$orientation <- car::recode(JSTAR_m_tn_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



<!--### JSTAR - 2 cities - Wave 2-->

### Wave 2

Not found.


<!--### JSTAR - 3 cities - Wave 1-->

## cth

### Wave 1


#### Study-specific variable description


| **Name** |`b_003_1`|`b_003_2`|`b_003_3`|`b_003_4`|
|-|-|-|-|-|
| **Label** |`DATE-YEAR`|`DATE-MONTH`|`DATE-DAY OF MONTH`|`DAY OF THE WEEK`|
| **Table name** |`jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|`jstar_2011_3cities`|
| **Categories** |`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|`1 = Answered correctly; 2 = Incorrect/did not know`|
| **Missings** |`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|`3 = Refused to answer; NA`|
| **Description** |  |  |  |  |


   

```{r assign 3 cities w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_orientation','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('b_003_1','b_003_2','b_003_3','b_003_4'), missings = TRUE)
```

```{r local 3 cities w1, echo=F}
JSTAR_3cities_w1_orientation <- opal.execute(o,'JSTAR_3cities_w1_orientation')
vari <- JSTAR_3cities_w1_orientation$b_003_1
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_1")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_3cities_w1_orientation, aes(x=factor(b_003_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
vari <- JSTAR_3cities_w1_orientation$b_003_2
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_2")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_3cities_w1_orientation, aes(x=factor(b_003_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- JSTAR_3cities_w1_orientation$b_003_3
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_3")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_3cities_w1_orientation, aes(x=factor(b_003_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- JSTAR_3cities_w1_orientation$b_003_4
kable(Categorical_summary(vari, missing_values = c(3))[3], caption = "b_003_4")
kable(Categorical_summary(vari, missing_values = c(3))[1], caption = "Category")
ggplot(JSTAR_3cities_w1_orientation, aes(x=factor(b_003_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `3 into 997`
* `NA into 999`

**R script:**
```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_orientation$id)
JSTAR_cth_ds_w1$orientation <- rep( 999,length(JSTAR_cth_ds_w1$id))
JSTAR_cth_ds_w1$orientation[((JSTAR_3cities_w1_orientation$b_003_1==1)&(JSTAR_3cities_w1_orientation$b_003_2==1)&(JSTAR_3cities_w1_orientation$b_003_3==1)&(JSTAR_3cities_w1_orientation$b_003_4==1))]<-1
JSTAR_cth_ds_w1$orientation[((JSTAR_3cities_w1_orientation$b_003_1==3)|(JSTAR_3cities_w1_orientation$b_003_2==3)|(JSTAR_3cities_w1_orientation$b_003_3==3)|(JSTAR_3cities_w1_orientation$b_003_4==3))]<-997
JSTAR_cth_ds_w1$orientation[((JSTAR_3cities_w1_orientation$b_003_1==2)|(JSTAR_3cities_w1_orientation$b_003_2==2)|(JSTAR_3cities_w1_orientation$b_003_3==2)|(JSTAR_3cities_w1_orientation$b_003_4==2))]<- 0
JSTAR_cth_ds_w1$orientation <- labelled(JSTAR_cth_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=F}
vari <- JSTAR_cth_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=F}
AfterH <- table(JSTAR_cth_ds_w1$orientation)
combi<-sum(na.omit((JSTAR_3cities_w1_orientation$b_003_1==1)&(JSTAR_3cities_w1_orientation$b_003_2==1)&(JSTAR_3cities_w1_orientation$b_003_3==1)&(JSTAR_3cities_w1_orientation$b_003_4==1)))
ref<-sum(na.omit((JSTAR_3cities_w1_orientation$b_003_1==3)|(JSTAR_3cities_w1_orientation$b_003_2==3)|(JSTAR_3cities_w1_orientation$b_003_3==3)|(JSTAR_3cities_w1_orientation$b_003_4==3)))
nota<-length(JSTAR_3cities_w1_orientation$b_003_1)-min(length(na.omit(JSTAR_3cities_w1_orientation$b_003_1)),length(na.omit(JSTAR_3cities_w1_orientation$b_003_2)),length(na.omit(JSTAR_3cities_w1_orientation$b_003_3)),length(na.omit(JSTAR_3cities_w1_orientation$b_003_4)))
BeforeH <- c(length(JSTAR_3cities_w1_orientation$b_003_1)-combi-nota-ref,combi,ref,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","3->997","NA->999") 
kable(C)
```






```{r importOPAL 3 cities w1, echo=FALSE}

label(JSTAR_cth_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- JSTAR_cth_ds_w1
save(orientation, file = "../RData/cth_w1/orientation.RData")

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$orientation <- car::recode(JSTAR_m_cth_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
For this study, the variable is a composed combining day of the month, day ofthe week, month, and year which is different 
from the calculation performed in other studies other variables are also available (or some 
of these variables are not).




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
