---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del_c`
* Variable label: `Cognition - delayed recall - Continuous`
* Variable description: `Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Delayed recall"
ds_label_cog_del_c <- "Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_del <- "Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## 5 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `b_011_a`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_b`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_c`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_d`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_e`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_f`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_g`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_h`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_i`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_j`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`
   
```{r assign 5 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j'), missings = TRUE)
JSTAR_5cities_w1_cog_del <- opal.execute(o,'JSTAR_5cities_w1_cog_del')
```

```{r local 5 cities w1, echo=FALSE}
vari <- JSTAR_5cities_w1_cog_del$b_011_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(b_011_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 5 cities w1}
##cog_del_c
#can not seperate 0 correct answers and Missing
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_cog_del$id)
JSTAR_aksst_ds_w1$cog_del_c <- rep(0,length(JSTAR_aksst_ds_w1$id))
for(i in 1:length(JSTAR_aksst_ds_w1$cog_del_c))
{
  if(is.na(JSTAR_5cities_w1_cog_del$b_011_a[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_b[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_c[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_d[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_e[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_f[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_g[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_h[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_i[i])==TRUE&is.na(JSTAR_5cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_aksst_ds_w1$cog_del_c[i] <- 999
  else
    JSTAR_aksst_ds_w1$cog_del_c[i] <- sum(JSTAR_5cities_w1_cog_del$b_011_a[i],JSTAR_5cities_w1_cog_del$b_011_b[i],JSTAR_5cities_w1_cog_del$b_011_c[i],JSTAR_5cities_w1_cog_del$b_011_d[i],JSTAR_5cities_w1_cog_del$b_011_e[i],JSTAR_5cities_w1_cog_del$b_011_f[i],JSTAR_5cities_w1_cog_del$b_011_g[i],JSTAR_5cities_w1_cog_del$b_011_h[i],JSTAR_5cities_w1_cog_del$b_011_i[i],JSTAR_5cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}
#JSTAR_aksst_ds_w1$cog_del_c <- recode(JSTAR_5cities_w1_cog_del$b_011_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_aksst_ds_w1$cog_del_c <- labelled(JSTAR_aksst_ds_w1$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(JSTAR_aksst_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_aksst_ds_w1$cog_del <- car::recode(JSTAR_aksst_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_aksst_ds_w1$cog_del <- labelled(JSTAR_aksst_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=FALSE}
vari <- JSTAR_aksst_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_aksst_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=FALSE}
Continous <- c(sum(na.omit(JSTAR_aksst_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_aksst_ds_w1[[2]])>Q & na.omit(JSTAR_aksst_ds_w1[[2]])<900), sum(na.omit(JSTAR_aksst_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_aksst_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 5 cities w1, echo=FALSE}
label(JSTAR_aksst_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(JSTAR_aksst_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- JSTAR_aksst_ds_w1
save(cog_del, file = "../RData/aksst_w1/cog_del.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$cog_del <- recode(JSTAR_m_aksst_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_aksst_ds_w1$cog_del_c <- recode(JSTAR_m_aksst_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `b_011_a`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_b`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_c`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_d`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_e`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_f`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_g`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_h`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_i`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_j`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`
   
```{r assign 5 cities w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_cog_del','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j'), missings = TRUE)
JSTAR_5cities_w2_cog_del <- opal.execute(o,'JSTAR_5cities_w2_cog_del')
```

```{r local 5 cities w2, echo=FALSE}
vari <- JSTAR_5cities_w2_cog_del$b_011_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(b_011_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 5 cities w2}
#can not seperate 0 correct answers and Missing
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_cog_del$id)
JSTAR_aksst_ds_w2$cog_del_c <- rep(0,length(JSTAR_aksst_ds_w2$id))
for(i in 1:length(JSTAR_aksst_ds_w2$cog_del_c))
{
  if(is.na(JSTAR_5cities_w2_cog_del$b_011_a[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_b[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_c[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_d[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_e[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_f[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_g[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_h[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_i[i])==TRUE&is.na(JSTAR_5cities_w2_cog_del$b_011_j[i])==TRUE)
    JSTAR_aksst_ds_w2$cog_del_c[i] <- 999
  else
    JSTAR_aksst_ds_w2$cog_del_c[i] <- sum(JSTAR_5cities_w2_cog_del$b_011_a[i],JSTAR_5cities_w2_cog_del$b_011_b[i],JSTAR_5cities_w2_cog_del$b_011_c[i],JSTAR_5cities_w2_cog_del$b_011_d[i],JSTAR_5cities_w2_cog_del$b_011_e[i],JSTAR_5cities_w2_cog_del$b_011_f[i],JSTAR_5cities_w2_cog_del$b_011_g[i],JSTAR_5cities_w2_cog_del$b_011_h[i],JSTAR_5cities_w2_cog_del$b_011_i[i],JSTAR_5cities_w2_cog_del$b_011_j[i],na.rm=TRUE)
}
#JSTAR_aksst_ds_w2$cog_del_c <- recode(JSTAR_5cities_w2_cog_del$b_011_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_aksst_ds_w2$cog_del_c <- labelled(JSTAR_aksst_ds_w2$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(JSTAR_aksst_ds_w2$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_aksst_ds_w2$cog_del <- car::recode(JSTAR_aksst_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_aksst_ds_w2$cog_del <- labelled(JSTAR_aksst_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=FALSE}
vari <- JSTAR_aksst_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_aksst_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=FALSE}
Continous <- c(sum(na.omit(JSTAR_aksst_ds_w2[[2]])<=Q), sum(na.omit(JSTAR_aksst_ds_w2[[2]])>Q & na.omit(JSTAR_aksst_ds_w2[[2]])<900), sum(na.omit(JSTAR_aksst_ds_w2[[2]])==999))
Dicotomic <- table(JSTAR_aksst_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 5 cities w2, echo=FALSE}
label(JSTAR_aksst_ds_w2$cog_del_c) <- ds_label_cog_del_c
label(JSTAR_aksst_ds_w2$cog_del) <- ds_label_cog_del
cog_del <- JSTAR_aksst_ds_w2
save(cog_del, file = "../RData/aksst_w2/cog_del.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$cog_del <- recode(JSTAR_m_aksst_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_aksst_ds_w2$cog_del_c <- recode(JSTAR_m_aksst_ds_w2$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

Not found



## 3 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `b_011_a`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_b`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_c`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_d`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_e`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_f`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_g`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_h`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_i`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_j`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`
 
   
```{r assign 3 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j'), missings = TRUE)
JSTAR_3cities_w1_cog_del <- opal.execute(o,'JSTAR_3cities_w1_cog_del')
```

```{r local 3 cities w1, echo=FALSE}
vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(b_011_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 3 cities w1}
#can not seperate 0 correct answers and Missing
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_cog_del$id)
JSTAR_cth_ds_w1$cog_del_c <- rep(0,length(JSTAR_cth_ds_w1$id))
for(i in 1:length(JSTAR_cth_ds_w1$cog_del_c))
{
  if(is.na(JSTAR_3cities_w1_cog_del$b_011_a[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_b[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_c[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_d[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_e[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_f[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_g[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_h[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_i[i])==TRUE&is.na(JSTAR_3cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_cth_ds_w1$cog_del_c[i] <- 999
  else
    JSTAR_cth_ds_w1$cog_del_c[i] <- sum(JSTAR_3cities_w1_cog_del$b_011_a[i],JSTAR_3cities_w1_cog_del$b_011_b[i],JSTAR_3cities_w1_cog_del$b_011_c[i],JSTAR_3cities_w1_cog_del$b_011_d[i],JSTAR_3cities_w1_cog_del$b_011_e[i],JSTAR_3cities_w1_cog_del$b_011_f[i],JSTAR_3cities_w1_cog_del$b_011_g[i],JSTAR_3cities_w1_cog_del$b_011_h[i],JSTAR_3cities_w1_cog_del$b_011_i[i],JSTAR_3cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}
#JSTAR_cth_ds_w1$cog_del_c <- recode(JSTAR_3cities_w1_cog_del$b_011_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_cth_ds_w1$cog_del_c <- labelled(JSTAR_cth_ds_w1$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(JSTAR_cth_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_cth_ds_w1$cog_del <- car::recode(JSTAR_cth_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_cth_ds_w1$cog_del <- labelled(JSTAR_cth_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_cth_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=FALSE}
Continous <- c(sum(na.omit(JSTAR_cth_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_cth_ds_w1[[2]])>Q & na.omit(JSTAR_cth_ds_w1[[2]])<900), sum(na.omit(JSTAR_cth_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_cth_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 3 cities w1, echo=FALSE}
label(JSTAR_cth_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(JSTAR_cth_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- JSTAR_cth_ds_w1
save(cog_del, file = "../RData/cth_w1/cog_del.RData")
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$cog_del <- recode(JSTAR_m_cth_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_cth_ds_w1$cog_del_c <- recode(JSTAR_m_cth_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```




## 2 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `b_011_a`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_b`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_c`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_d`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_e`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_f`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_g`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_h`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`
* Categories:
    + `1`
* Missings
   + `NA`
   
* Name: `b_011_i`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`
* Categories:
    + `1`
* Missings
   + `NA`

* Name: `b_011_j`
* Label: `B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`
* Categories:
    + `1`
* Missings
   + `NA`
   
```{r assign 2 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j'), missings = TRUE)
JSTAR_2cities_w1_cog_del <- opal.execute(o,'JSTAR_2cities_w1_cog_del')
```

```{r local 2 cities w1, echo=FALSE}
vari <- JSTAR_2cities_w1_cog_del$b_011_a
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_d
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_d))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_e
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_g))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_h
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_h))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_i
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_011_j
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(b_011_j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 2 cities w1}
#can not seperate 0 correct answers and Missing
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_cog_del$id)
JSTAR_tn_ds_w1$cog_del_c <- rep(0,length(JSTAR_tn_ds_w1$id))
for(i in 1:length(JSTAR_tn_ds_w1$cog_del_c))
{
  if(is.na(JSTAR_2cities_w1_cog_del$b_011_a[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_b[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_c[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_d[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_e[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_f[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_g[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_h[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_i[i])==TRUE&is.na(JSTAR_2cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_tn_ds_w1$cog_del_c[i] <- 999
  else
    JSTAR_tn_ds_w1$cog_del_c[i] <- sum(JSTAR_2cities_w1_cog_del$b_011_a[i],JSTAR_2cities_w1_cog_del$b_011_b[i],JSTAR_2cities_w1_cog_del$b_011_c[i],JSTAR_2cities_w1_cog_del$b_011_d[i],JSTAR_2cities_w1_cog_del$b_011_e[i],JSTAR_2cities_w1_cog_del$b_011_f[i],JSTAR_2cities_w1_cog_del$b_011_g[i],JSTAR_2cities_w1_cog_del$b_011_h[i],JSTAR_2cities_w1_cog_del$b_011_i[i],JSTAR_2cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}
#JSTAR_tn_ds_w1$cog_del_c <- recode(JSTAR_2cities_w1_cog_del$b_011_a, "-9 = '997';-8 = '998';-1 = '994' ")
JSTAR_tn_ds_w1$cog_del_c <- labelled(JSTAR_tn_ds_w1$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(JSTAR_tn_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_tn_ds_w1$cog_del <- car::recode(JSTAR_tn_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
JSTAR_tn_ds_w1$cog_del <- labelled(JSTAR_tn_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=FALSE}
vari <- JSTAR_tn_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_tn_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=FALSE}
Continous <- c(sum(na.omit(JSTAR_tn_ds_w1[[2]])<=Q), sum(na.omit(JSTAR_tn_ds_w1[[2]])>Q & na.omit(JSTAR_tn_ds_w1[[2]])<900), sum(na.omit(JSTAR_tn_ds_w1[[2]])==999))
Dicotomic <- table(JSTAR_tn_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL 2 cities w1, echo=FALSE}
label(JSTAR_tn_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(JSTAR_tn_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- JSTAR_tn_ds_w1
save(cog_del, file = "../RData/tn_w1/cog_del.RData")
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$cog_del <- recode(JSTAR_m_tn_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
JSTAR_m_tn_ds_w1$cog_del_c <- recode(JSTAR_m_tn_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found

#Quality estimation:

Delayed recall of 10 words (following a single immediate recall trial). The word list as well as the protocol for the immediate recall test were changed for the 2011 survey in 5 and 2 cities (i.e. 3rd wave 5 cities and 2nd wave 2 cities), and it appears that delayed recall test was not done (information could not be found in the questionnaire).


