---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_delDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_delDS.R')
```

# Data process

## AKSST

### Wave 1 

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|
|`b_001`|`B-001:RESPONDENT ACCEPT ANSWERING MEMORY TEST`|`jstar_2007_5cities`|`1 = Yes`<br/>`2 = No`|`NA`|
|`b_004`|`B-004:WHETHER A RESPONDENT CATCH ON HOW TO TEST HIS/HER MEMORY`|`jstar_2007_5cities`|`1 = Yes`<br/>`2 = Refused to answer`<br/>`3 = Did not understand instructions`|`NA`|
|`b_011_a`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_b`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_c`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_d`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_e`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_f`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_g`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_h`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_i`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_j`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_k`|`B-011:STOP ANSWERING WORDS LIST TEST IN MIDSTREAM - 2ND TRIAL`|`jstar_2007_5cities`|`1`|`NA`|
|`b_011_l`|`B-011:CAN'T REMEMBER MORE AFTER ONE MINUTE HIATUS - 2ND TRIAL`|`jstar_2007_5cities`|`1`|`NA`|

**Description**



```{r assign 5 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('b_001','b_004','b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j','b_011_k','b_011_l'), missings = TRUE)
JSTAR_5cities_w1_cog_del <- opal.execute(o,'JSTAR_5cities_w1_cog_del')
```

```{r local 5 cities w1, echo=FALSE}


vari <- JSTAR_5cities_w1_cog_del$b_001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_5cities_w1_cog_del$b_004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


JSTAR_5cities_w1_cog_del_labels <- data.frame(names = names(JSTAR_5cities_w1_cog_del), varlabels = as.character(var_label(JSTAR_5cities_w1_cog_del)))

JSTAR_5cities_w1_cog_del_labels <- JSTAR_5cities_w1_cog_del %>% 
  gather(-id,-b_001,-b_004, key = "var", value = "value") %>% 
  left_join(JSTAR_5cities_w1_cog_del_labels, by = c("var"="names")) %>%
  mutate(word = 
           case_when(
             (value==1 & !var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr("- [^-]+$",varlabels)+2,nchar(as.character(varlabels))),
             
             (value==1 & var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr(":",varlabels)+1,regexpr(" - 2",varlabels)-1)
  ))

ggplot(JSTAR_5cities_w1_cog_del_labels, aes(x=factor(word))) + 
  geom_bar(stat="count", width=0.4, fill="steelblue") + 
  xlab(paste("B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL\nSample size: ",Categorical_summary(vari, missing_values = NA)[2][[1]][,1])) + ylab("Frequency") + 
  facet_wrap(~ var, scales = "free") + 
  geom_text(stat='count', aes(label=..count..), vjust="inward") + theme(axis.text.x = element_text(angle = 8))

JSTAR_5cities_w1_cog_del <- JSTAR_5cities_w1_cog_del %>% mutate(rowNAs = rowSums(is.na(select(., starts_with("b_011")))))
JSTAR_5cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(b_004) %>% kable(caption = "Frequencies of b_004 for refused b_001")
JSTAR_5cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(rowNAs, show.na = "auto") %>% kable(caption = "Missings b_011 for refused b_001")
JSTAR_5cities_w1_cog_del %>% filter(b_004 == 2) %>% kable(caption = "Missings b_011 for refused b_004")


```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 5 cities w1}

JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_5cities_w1_cog_del$id)

JSTAR_ds_aksst_w1$cog_del_c <- rep(0,length(JSTAR_ds_aksst_w1$id))

for(i in 1:length(JSTAR_ds_aksst_w1$cog_del_c))
{
  if(is.na(JSTAR_5cities_w1_cog_del$b_011_a[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_b[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_c[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_d[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_e[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_f[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_g[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_h[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_i[i])==TRUE & is.na(JSTAR_5cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_ds_aksst_w1$cog_del_c[i] <- 999
  else
    JSTAR_ds_aksst_w1$cog_del_c[i] <- sum(JSTAR_5cities_w1_cog_del$b_011_a[i],JSTAR_5cities_w1_cog_del$b_011_b[i],JSTAR_5cities_w1_cog_del$b_011_c[i],JSTAR_5cities_w1_cog_del$b_011_d[i],JSTAR_5cities_w1_cog_del$b_011_e[i],JSTAR_5cities_w1_cog_del$b_011_f[i],JSTAR_5cities_w1_cog_del$b_011_g[i],JSTAR_5cities_w1_cog_del$b_011_h[i],JSTAR_5cities_w1_cog_del$b_011_i[i],JSTAR_5cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}


JSTAR_ds_aksst_w1$cog_del_c[which(JSTAR_5cities_w1_cog_del$b_004 == 2 | JSTAR_5cities_w1_cog_del$b_001 == 2)] <- 997
JSTAR_ds_aksst_w1$cog_del_c[which(JSTAR_5cities_w1_cog_del$b_011_l == 1 & JSTAR_ds_aksst_w1$cog_del_c == 999)] <- 0
JSTAR_ds_aksst_w1$cog_del_c[which(JSTAR_5cities_w1_cog_del$b_011_k == 1 & JSTAR_ds_aksst_w1$cog_del_c == 999)] <- 997


##cog_del
Q <- quantile(car::recode(JSTAR_ds_aksst_w1$cog_del_c, "miss_values_vector=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_ds_aksst_w1$cog_del <- car::recode(JSTAR_ds_aksst_w1[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=FALSE}
vari <- JSTAR_ds_aksst_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_ds_aksst_w1$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=FALSE}

```



### Wave 2 

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|
|`b_001`|`B-001:RESPONDENT ACCEPT ANSWERING MEMORY TEST`|`jstar_2009_5cities`|`1 = Yes`<br/>`2 = No`|`NA`|
|`b_004`|`B-004:WHETHER A RESPONDENT CATCH ON HOW TO TEST HIS/HER MEMORY`|`jstar_2009_5cities`|`1 = Yes`<br/>`2 = Refused to answer`<br/>`3 = Did not understand instructions`|`NA`|
|`b_011_a`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_b`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_c`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_d`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_e`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_f`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_g`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_h`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_i`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_j`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_k`|`B-011:STOP ANSWERING WORDS LIST TEST IN MIDSTREAM - 2ND TRIAL`|`jstar_2009_5cities`|`1`|`NA`|
|`b_011_l`|`B-011:CAN'T REMEMBER MORE AFTER ONE MINUTE HIATUS - 2ND TRIAL`|`jstar_2009_5cities`|`1`|`NA`|


```{r assign 5 cities w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_cog_del','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('b_001','b_004','b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j','b_011_k','b_011_l'), missings = TRUE)
JSTAR_5cities_w2_cog_del <- opal.execute(o,'JSTAR_5cities_w2_cog_del')
```

```{r local 5 cities w2, echo=FALSE}

vari <- JSTAR_5cities_w2_cog_del$b_001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_5cities_w2_cog_del$b_004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w2_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


JSTAR_5cities_w2_cog_del_labels <- data.frame(names = names(JSTAR_5cities_w2_cog_del), varlabels = as.character(var_label(JSTAR_5cities_w2_cog_del)))

JSTAR_5cities_w2_cog_del_labels <- JSTAR_5cities_w2_cog_del %>% 
  gather(-id,-b_001,-b_004, key = "var", value = "value") %>% 
  left_join(JSTAR_5cities_w2_cog_del_labels, by = c("var"="names")) %>%
  mutate(word = 
           case_when(
             (!var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr("- [^-]+$",varlabels)+2,nchar(as.character(varlabels))),
             
             (var %in% c("b_011_k","b_011_l")) ~ varlabels %>% str_extract("[a-zA-Z']+\\s[a-zA-Z']+")
  ))


ggplot(JSTAR_5cities_w2_cog_del_labels, aes(x=factor(value))) + 
  geom_bar(stat="count", width=0.4, fill="steelblue") + 
  xlab(paste("B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL\nSample size: ",Categorical_summary(vari, missing_values = NA)[2][[1]][,1])) + ylab("Frequency") + 
  facet_wrap(~ var + word, scales = "free") + 
  geom_text(stat='count', aes(label=..count..), vjust="inward") + theme(axis.text.x = element_text(angle = 8))

JSTAR_5cities_w2_cog_del <- JSTAR_5cities_w2_cog_del %>% mutate(rowNAs = rowSums(is.na(select(., starts_with("b_011")))))
JSTAR_5cities_w2_cog_del <- JSTAR_5cities_w2_cog_del %>% mutate(rowZs = rowSums(select(., starts_with("b_011"),-b_011_k,-b_011_l) == 0))
JSTAR_5cities_w2_cog_del %>% filter(b_001 == 2) %>% frq(b_004) %>% kable(caption = "Frequencies of b_004 for refused b_001")
JSTAR_5cities_w2_cog_del %>% filter(b_001 == 2) %>% frq(rowNAs, show.na = "auto") %>% kable(caption = "Missings b_011 for refused b_001")
JSTAR_5cities_w2_cog_del %>% filter(b_004 == 2) %>% frq(rowZs, show.na = "auto") %>% kable(caption = "Zeroes b_011 for refused b_004")

```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 5 cities w2}

JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_5cities_w2_cog_del$id)
JSTAR_ds_aksst_w2$cog_del_c <- rep(0,length(JSTAR_ds_aksst_w2$id))
for(i in 1:length(JSTAR_ds_aksst_w2$cog_del_c))
{
  if(is.na(JSTAR_5cities_w2_cog_del$b_011_a[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_b[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_c[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_d[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_e[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_f[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_g[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_h[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_i[i])==TRUE & is.na(JSTAR_5cities_w2_cog_del$b_011_j[i])==TRUE)
    JSTAR_ds_aksst_w2$cog_del_c[i] <- 999
  else
    JSTAR_ds_aksst_w2$cog_del_c[i] <- sum(JSTAR_5cities_w2_cog_del$b_011_a[i],JSTAR_5cities_w2_cog_del$b_011_b[i],JSTAR_5cities_w2_cog_del$b_011_c[i],JSTAR_5cities_w2_cog_del$b_011_d[i],JSTAR_5cities_w2_cog_del$b_011_e[i],JSTAR_5cities_w2_cog_del$b_011_f[i],JSTAR_5cities_w2_cog_del$b_011_g[i],JSTAR_5cities_w2_cog_del$b_011_h[i],JSTAR_5cities_w2_cog_del$b_011_i[i],JSTAR_5cities_w2_cog_del$b_011_j[i],na.rm=TRUE)
}

JSTAR_ds_aksst_w2$cog_del_c[which((JSTAR_5cities_w2_cog_del$b_004 == 2 | JSTAR_5cities_w2_cog_del$b_001 == 2) & JSTAR_ds_aksst_w2$cog_del_c == 999)] <- 997
JSTAR_ds_aksst_w2$cog_del_c[which(JSTAR_5cities_w2_cog_del$b_011_l == 1 & JSTAR_ds_aksst_w2$cog_del_c == 999)] <- 0
JSTAR_ds_aksst_w2$cog_del_c[which(JSTAR_5cities_w2_cog_del$b_011_k == 1 & JSTAR_ds_aksst_w2$cog_del_c == 999)] <- 997


##cog_del
Q <- quantile(car::recode(JSTAR_ds_aksst_w2$cog_del_c, "miss_values_vector=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_ds_aksst_w2$cog_del <- car::recode(JSTAR_ds_aksst_w2[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=FALSE}
vari <- JSTAR_ds_aksst_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_ds_aksst_w2$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=FALSE}

```




### Wave 3 

Not found.




## TN

### Wave 1 

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|
|`b_001`|`B-001:CONTINUE SECTION B`|`jstar_2009_2cities`|`1 = Yes`<br/>`2 = No`|`NA`|
|`b_004`|`B-004:WHETHER A RESPONDENT CATCH ON HOW TO TEST HIS/HER MEMORY`|`jstar_2009_2cities`|`1 = Yes`<br/>`2 = Refused to answer`<br/>`3 = Did not understand instructions`|`NA`|
|`b_011_a`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_b`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_c`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_d`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_e`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_f`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_g`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_h`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_i`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_j`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_k`|`B-011:STOP ANSWERING WORDS LIST TEST IN MIDSTREAM - 2ND TRIAL`|`jstar_2009_2cities`|`1`|`NA`|
|`b_011_l`|`B-011:CAN'T REMEMBER MORE AFTER ONE MINUTE HIATUS - 2ND TRIAL`|`jstar_2009_2cities`|`1`|`NA`|

**Description**


   
```{r assign 2 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('b_001','b_004','b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j','b_011_k','b_011_l'), missings = TRUE)
JSTAR_2cities_w1_cog_del <- opal.execute(o,'JSTAR_2cities_w1_cog_del')
```

```{r local 2 cities w1, echo=FALSE}

vari <- JSTAR_2cities_w1_cog_del$b_001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_2cities_w1_cog_del$b_004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


JSTAR_2cities_w1_cog_del_labels <- data.frame(names = names(JSTAR_2cities_w1_cog_del), varlabels = as.character(var_label(JSTAR_2cities_w1_cog_del)))

JSTAR_2cities_w1_cog_del_labels <- JSTAR_2cities_w1_cog_del %>% 
  gather(-id,-b_001,-b_004, key = "var", value = "value") %>% 
  left_join(JSTAR_2cities_w1_cog_del_labels, by = c("var"="names")) %>%
  mutate(word = 
           case_when(
             (value==1 & !var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr("- [^-]+$",varlabels)+2,nchar(as.character(varlabels))),
             
             (value==1 & var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr(":",varlabels)+1,regexpr(" - 2",varlabels)-1)
  ))


ggplot(JSTAR_2cities_w1_cog_del_labels, aes(x=factor(word))) + 
  geom_bar(stat="count", width=0.4, fill="steelblue") + 
  xlab(paste("B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL\nSample size: ",Categorical_summary(vari, missing_values = NA)[2][[1]][,1])) + ylab("Frequency") + 
  facet_wrap(~ var, scales = "free") + 
  geom_text(stat='count', aes(label=..count..), vjust="inward") + theme(axis.text.x = element_text(angle = 8))



JSTAR_2cities_w1_cog_del <- JSTAR_2cities_w1_cog_del %>% mutate(rowNAs = rowSums(is.na(select(., starts_with("b_011")))))
JSTAR_2cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(b_004) %>% kable(caption = "Frequencies of b_004 for refused b_001")
JSTAR_2cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(rowNAs, show.na = "auto") %>% kable(caption = "Missings b_011 for refused b_001")
JSTAR_2cities_w1_cog_del %>% filter(b_004 == 2) %>% kable(caption = "Missings b_011 for refused b_004")

```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 2 cities w1}

JSTAR_ds_tn_w1 <- tibble(id=JSTAR_2cities_w1_cog_del$id)
JSTAR_ds_tn_w1$cog_del_c <- rep(0,length(JSTAR_ds_tn_w1$id))
for(i in 1:length(JSTAR_ds_tn_w1$cog_del_c))
{
  if(is.na(JSTAR_2cities_w1_cog_del$b_011_a[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_b[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_c[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_d[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_e[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_f[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_g[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_h[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_i[i])==TRUE & is.na(JSTAR_2cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_ds_tn_w1$cog_del_c[i] <- 999
  else
    JSTAR_ds_tn_w1$cog_del_c[i] <- sum(JSTAR_2cities_w1_cog_del$b_011_a[i],JSTAR_2cities_w1_cog_del$b_011_b[i],JSTAR_2cities_w1_cog_del$b_011_c[i],JSTAR_2cities_w1_cog_del$b_011_d[i],JSTAR_2cities_w1_cog_del$b_011_e[i],JSTAR_2cities_w1_cog_del$b_011_f[i],JSTAR_2cities_w1_cog_del$b_011_g[i],JSTAR_2cities_w1_cog_del$b_011_h[i],JSTAR_2cities_w1_cog_del$b_011_i[i],JSTAR_2cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}

JSTAR_ds_tn_w1$cog_del_c[which(JSTAR_2cities_w1_cog_del$b_004 == 2 | JSTAR_2cities_w1_cog_del$b_001 == 2)] <- 997
JSTAR_ds_tn_w1$cog_del_c[which(JSTAR_2cities_w1_cog_del$b_011_l == 1 & JSTAR_ds_tn_w1$cog_del_c == 999)] <- 0
JSTAR_ds_tn_w1$cog_del_c[which(JSTAR_2cities_w1_cog_del$b_011_k == 1 & JSTAR_ds_tn_w1$cog_del_c == 999)] <- 997


##cog_del
Q <- quantile(car::recode(JSTAR_ds_tn_w1$cog_del_c, "miss_values_vector=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_ds_tn_w1$cog_del <- car::recode(JSTAR_ds_tn_w1[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=FALSE}
vari <- JSTAR_ds_tn_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_ds_tn_w1$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=FALSE}

```




### Wave 2

Not found.



## CTH

### Wave 1 

#### Study-specific variable description


| **Name** | **Label** | **Table name** | **Categories** | **Missings** |
|-|-|-|-|-|
|`b_001`|`B-001:CONTINUE SECTION B`|`jstar_2011_3cities`|`1 = Yes`<br/>`2 = No`|`NA`|
|`b_004`|`B-004:WHETHER A RESPONDENT CATCH ON HOW TO TEST HIS/HER MEMORY`|`jstar_2011_3cities`|`1 = Yes`<br/>`2 = Refused to answer`<br/>`3 = Did not understand instructions`|`NA`|
|`b_011_a`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - DOG`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_b`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - KNIFE`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_c`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - RAILCAR`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_d`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BASEBALL`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_e`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - CAT`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_f`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - PAN`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_g`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - AIRCLAFT`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_h`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - HORSE`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_i`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - SWIMMING`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_j`|`B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL - BICYCLE`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_k`|`B-011:STOP ANSWERING WORDS LIST TEST IN MIDSTREAM - 2ND TRIAL`|`jstar_2011_3cities`|`1`|`NA`|
|`b_011_l`|`B-011:CAN'T REMEMBER MORE AFTER ONE MINUTE HIATUS - 2ND TRIAL`|`jstar_2011_3cities`|`1`|`NA`|



 
   
```{r assign 3 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_cog_del','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('b_001','b_004','b_011_a','b_011_b','b_011_c','b_011_d','b_011_e','b_011_f','b_011_g','b_011_h','b_011_i','b_011_j','b_011_k','b_011_l'), missings = TRUE)
JSTAR_3cities_w1_cog_del <- opal.execute(o,'JSTAR_3cities_w1_cog_del')
```

```{r local 3 cities w1, echo=FALSE}

vari <- JSTAR_3cities_w1_cog_del$b_001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- JSTAR_3cities_w1_cog_del$b_004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari,"spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


JSTAR_3cities_w1_cog_del_labels <- data.frame(names = names(JSTAR_3cities_w1_cog_del), varlabels = as.character(var_label(JSTAR_3cities_w1_cog_del)))

JSTAR_3cities_w1_cog_del_labels <- JSTAR_3cities_w1_cog_del %>% 
  gather(-id,-b_001,-b_004, key = "var", value = "value") %>% 
  left_join(JSTAR_3cities_w1_cog_del_labels, by = c("var"="names")) %>%
  mutate(word = 
           case_when(
             (value==1 & !var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr("- [^-]+$",varlabels)+2,nchar(as.character(varlabels))),
             
             (value==1 & var %in% c("b_011_k","b_011_l")) ~ substr(varlabels,regexpr(":",varlabels)+1,regexpr(" - 2",varlabels)-1)
  ))


ggplot(JSTAR_3cities_w1_cog_del_labels, aes(x=factor(word))) + 
  geom_bar(stat="count", width=0.4, fill="steelblue") + 
  xlab(paste("B-011:THE WORDS RESOPNDENT CORRECTLY RECALLS - 2ND TRIAL\nSample size: ",Categorical_summary(vari, missing_values = NA)[2][[1]][,1])) + ylab("Frequency") + 
  facet_wrap(~ var, scales = "free") + 
  geom_text(stat='count', aes(label=..count..), vjust="inward") + theme(axis.text.x = element_text(angle = 8))


JSTAR_3cities_w1_cog_del <- JSTAR_3cities_w1_cog_del %>% mutate(rowNAs = rowSums(is.na(select(., starts_with("b_011")))))

JSTAR_3cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(b_004) %>% kable(caption = "Frequencies of b_004 for refused b_001")
JSTAR_3cities_w1_cog_del %>% filter(b_001 == 2) %>% frq(rowNAs, show.na = "auto") %>% kable(caption = "Missings b_011 for refused b_001")
JSTAR_3cities_w1_cog_del %>% filter(b_004 == 2) %>% kable(caption = "Missings b_011 for refused b_004")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variables it has to be sumed all the 1 and the missing values have to be recoded as follows:

* `all NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo 3 cities w1}

JSTAR_ds_cth_w1 <- tibble(id=JSTAR_3cities_w1_cog_del$id)
JSTAR_ds_cth_w1$cog_del_c <- rep(0,length(JSTAR_ds_cth_w1$id))
for(i in 1:length(JSTAR_ds_cth_w1$cog_del_c))
{
  if(is.na(JSTAR_3cities_w1_cog_del$b_011_a[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_b[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_c[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_d[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_e[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_f[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_g[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_h[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_i[i])==TRUE & is.na(JSTAR_3cities_w1_cog_del$b_011_j[i])==TRUE)
    JSTAR_ds_cth_w1$cog_del_c[i] <- 999
  else
    JSTAR_ds_cth_w1$cog_del_c[i] <- sum(JSTAR_3cities_w1_cog_del$b_011_a[i],JSTAR_3cities_w1_cog_del$b_011_b[i],JSTAR_3cities_w1_cog_del$b_011_c[i],JSTAR_3cities_w1_cog_del$b_011_d[i],JSTAR_3cities_w1_cog_del$b_011_e[i],JSTAR_3cities_w1_cog_del$b_011_f[i],JSTAR_3cities_w1_cog_del$b_011_g[i],JSTAR_3cities_w1_cog_del$b_011_h[i],JSTAR_3cities_w1_cog_del$b_011_i[i],JSTAR_3cities_w1_cog_del$b_011_j[i],na.rm=TRUE)
}

JSTAR_ds_cth_w1$cog_del_c[which((JSTAR_3cities_w1_cog_del$b_004 == 2 | JSTAR_3cities_w1_cog_del$b_001 == 2) & JSTAR_ds_cth_w1$cog_del_c == 999)] <- 997
JSTAR_ds_cth_w1$cog_del_c[which(JSTAR_3cities_w1_cog_del$b_011_l == 1 & JSTAR_ds_cth_w1$cog_del_c == 999)] <- 0
JSTAR_ds_cth_w1$cog_del_c[which(JSTAR_3cities_w1_cog_del$b_011_k == 1 & JSTAR_ds_cth_w1$cog_del_c == 999)] <- 997

##cog_del
Q <- quantile(car::recode(JSTAR_ds_cth_w1$cog_del_c, "miss_values_vector=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

JSTAR_ds_cth_w1$cog_del <- car::recode(JSTAR_ds_cth_w1[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=FALSE}
vari <- JSTAR_ds_cth_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- JSTAR_ds_cth_w1$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=FALSE}

```



## Descriptive statistics of the harmonised variable `cog_del` accross populations and waves





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name = hd_vbl,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name = hd_vbl){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name = hd_vbl){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))


```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

jstarlist <- lmlist # baseline list




```



<!--Descriptives-->


Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_vbl %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
}





```






## Summary of descriptive statistics of the harmonised variable `cog_del_c` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}



```







# Quality estimation

Delayed recall of 10 words (following a single immediate recall trial). The word list as well as the protocol for the immediate recall test were changed for the 2011 survey in 5 and 2 cities (i.e. 3rd wave 5 cities and 2nd wave 2 cities), and it appears that delayed recall test was not done (information could not be found in the questionnaire).


