---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing





```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## 5 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `D-002:HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Fairly good`
   + `3 = Average`
   + `4 = Not very good`
   + `5 = Not good`
* Missings
   + `6 = Don't know` 
   + `NA`    

```{r assign 5 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w1_srh','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('d_002'), missings = TRUE)
JSTAR_5cities_w1_srh <- opal.execute(o,'JSTAR_5cities_w1_srh')
```

```{r local 5 cities w1, echo=FALSE}
vari <- JSTAR_5cities_w1_srh$d_002
kable(Categorical_summary(vari, missing_values = c(6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6))[2], caption = "Type of missing")
ggplot(JSTAR_5cities_w1_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `6 Don't know into 998`
* `NA into 999`

**R script:**

```{r harmo 5 cities w1}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_5cities_w1_srh$id)
JSTAR_aksst_ds_w1$srh <- recode(JSTAR_5cities_w1_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';6 = '998';NA = '999' ")
JSTAR_aksst_ds_w1$srh <- labelled(JSTAR_aksst_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w1, echo=FALSE}
vari <- JSTAR_aksst_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w1, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w1$srh)
X<-table(JSTAR_5cities_w1_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),X[6],sum(is.na(JSTAR_5cities_w1_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","6->998","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w1, echo=FALSE}
label(JSTAR_aksst_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_aksst_ds_w1
save(srh, file = "../RData/aksst_w1/srh.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w1 <- JSTAR_aksst_ds_w1
JSTAR_m_aksst_ds_w1$srh <- recode(JSTAR_m_aksst_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w1', JSTAR_m_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `D-002:CURRENT HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Fairly good`
   + `3 = Average`
   + `4 = Not very good`
   + `5 = Not good`
* Missings
   + `6 = Refused to answer` 
   + `NA`    

```{r assign 5 cities w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w2_srh','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('d_002'), missings = TRUE)
JSTAR_5cities_w2_srh <- opal.execute(o,'JSTAR_5cities_w2_srh')
```

```{r local 5 cities w2, echo=FALSE}
vari <- JSTAR_5cities_w2_srh$d_002
kable(Categorical_summary(vari, missing_values = c(6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6))[2], caption = "Type of missing")
ggplot(JSTAR_5cities_w2_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `6 Don't know into 997`
* `NA into 999`

**R script:**

```{r harmo 5 cities w2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_5cities_w2_srh$id)
JSTAR_aksst_ds_w2$srh <- recode(JSTAR_5cities_w2_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';6 = '997';NA = '999' ")
JSTAR_aksst_ds_w2$srh <- labelled(JSTAR_aksst_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w2, echo=FALSE}
vari <- JSTAR_aksst_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w2, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w2$srh)
X<-table(JSTAR_5cities_w2_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),X[6],sum(is.na(JSTAR_5cities_w2_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","6->997","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w2, echo=FALSE}
label(JSTAR_aksst_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_aksst_ds_w2
save(srh, file = "../RData/aksst_w2/srh.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w2 <- JSTAR_aksst_ds_w2
JSTAR_m_aksst_ds_w2$srh <- recode(JSTAR_m_aksst_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w2', JSTAR_m_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `11D-002:CURRENT HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Relatively good`
   + `3 = Average`
   + `4 = Relatively poor`
   + `5 = Poor`
* Missings
   + `NA`    

```{r assign 5 cities w3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_5cities_w3_srh','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('d_002'), missings = TRUE)
JSTAR_5cities_w3_srh <- opal.execute(o,'JSTAR_5cities_w3_srh')
```

```{r local 5 cities w3, echo=FALSE}
vari <- JSTAR_5cities_w3_srh$d_002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_5cities_w3_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo 5 cities w3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_5cities_w3_srh$id)
JSTAR_aksst_ds_w3$srh <- recode(JSTAR_5cities_w3_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';NA = '999' ")
JSTAR_aksst_ds_w3$srh <- labelled(JSTAR_aksst_ds_w3$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 5 cities w3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 5 cities w3, echo=FALSE}
AfterH <- table(JSTAR_aksst_ds_w3$srh)
X<-table(JSTAR_5cities_w3_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),sum(is.na(JSTAR_5cities_w3_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","NA->999") 
kable(C)
```

```{r importOPAL 5 cities w3, echo=FALSE}
label(JSTAR_aksst_ds_w3$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_aksst_ds_w3
save(srh, file = "../RData/aksst_w3/srh.RData")
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')

JSTAR_m_aksst_ds_w3 <- JSTAR_aksst_ds_w3
JSTAR_m_aksst_ds_w3$srh <- recode(JSTAR_m_aksst_ds_w3$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_aksst_ds_w3', JSTAR_m_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_m_aksst_ds_w3', project='_Athlos_Harm_Dataset')
```



## 3 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `D-002:CURRENT HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Fairly good`
   + `3 = Average`
   + `4 = Not very good`
   + `5 = Not good`
* Missings
   + `6 = Refused to answer` 
   + `NA`    

```{r assign 3 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_3cities_w1_srh','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('d_002'), missings = TRUE)
JSTAR_3cities_w1_srh <- opal.execute(o,'JSTAR_3cities_w1_srh')
```

```{r local 3 cities w1, echo=FALSE}
vari <- JSTAR_3cities_w1_srh$d_002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_3cities_w1_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `6 Don't know into 997`
* `NA into 999`

**R script:**

```{r harmo 3 cities w1}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_3cities_w1_srh$id)
JSTAR_cth_ds_w1$srh <- recode(JSTAR_3cities_w1_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';6 = '997';NA = '999' ")
JSTAR_cth_ds_w1$srh <- labelled(JSTAR_cth_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 3 cities w1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 3 cities w1, echo=FALSE}
AfterH <- table(JSTAR_cth_ds_w1$srh)
X<-table(JSTAR_3cities_w1_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),X[6],sum(is.na(JSTAR_3cities_w1_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","6->997","NA->999") 
kable(C)
```

```{r importOPAL 3 cities w1, echo=FALSE}
label(JSTAR_cth_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_cth_ds_w1
save(srh, file = "../RData/cth_w1/srh.RData")
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_cth_ds_w1 <- JSTAR_cth_ds_w1
JSTAR_m_cth_ds_w1$srh <- recode(JSTAR_m_cth_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_cth_ds_w1', JSTAR_m_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_m_cth_ds_w1', project='_Athlos_Harm_Dataset')
```



## 2 cities

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `D-002:CURRENT HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Fairly good`
   + `3 = Average`
   + `4 = Not very good`
   + `5 = Not good`
* Missings
   + `6 = Refused to answer` 
   + `NA`    

```{r assign 2 cities w1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w1_srh','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('d_002'), missings = TRUE)
JSTAR_2cities_w1_srh <- opal.execute(o,'JSTAR_2cities_w1_srh')
```

```{r local 2 cities w1, echo=FALSE}
vari <- JSTAR_2cities_w1_srh$d_002
kable(Categorical_summary(vari, missing_values = c(6))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(6))[2], caption = "Type of missing")
ggplot(JSTAR_2cities_w1_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `6 Don't know into 997`
* `NA into 999`

**R script:**

```{r harmo 2 cities w1}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_2cities_w1_srh$id)
JSTAR_tn_ds_w1$srh <- recode(JSTAR_2cities_w1_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';6 = '997';NA = '999' ")
JSTAR_tn_ds_w1$srh <- labelled(JSTAR_tn_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript 2 cities w1, echo=FALSE}
vari <- JSTAR_tn_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation 2 cities w1, echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w1$srh)
X<-table(JSTAR_2cities_w1_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),X[6],sum(is.na(JSTAR_2cities_w1_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","6->997","NA->999") 
kable(C)
```

```{r importOPAL 2 cities w1, echo=FALSE}
label(JSTAR_tn_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_tn_ds_w1
save(srh, file = "../RData/tn_w1/srh.RData")
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w1 <- JSTAR_tn_ds_w1
JSTAR_m_tn_ds_w1$srh <- recode(JSTAR_m_tn_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w1', JSTAR_m_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `d_002`
* Label: `11D-002:CURRENT HEALTH STATUS`
* Categories:
   + `1 = Good`
   + `2 = Relatively good`
   + `3 = Average`
   + `4 = Relatively poor`
   + `5 = Poor`
* Missings
   + `NA`    

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_2cities_w2_srh','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('d_002'), missings = TRUE)
JSTAR_2cities_w2_srh <- opal.execute(o,'JSTAR_2cities_w2_srh')
```

```{r local w2, echo=FALSE}
vari <- JSTAR_2cities_w2_srh$d_002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_2cities_w2_srh, aes(x=factor(d_002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 2`
* `4 into 3`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo w2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_2cities_w2_srh$id)
JSTAR_tn_ds_w2$srh <- recode(JSTAR_2cities_w2_srh$d_002, "1 = '1';2 = '1';3 = '2';4 = '3';5 = '3';NA = '999' ")
JSTAR_tn_ds_w2$srh <- labelled(JSTAR_tn_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(JSTAR_tn_ds_w2$srh)
X<-table(JSTAR_2cities_w2_srh$d_002)
BeforeH <- c(sum(X[c(1:2)]),X[3],sum(X[c(4:5)]),sum(is.na(JSTAR_2cities_w2_srh$d_002)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->1","3->2","4,5->3","NA->999") 
kable(C)
```

```{r importOPAL 2 cities w2, echo=FALSE}
label(JSTAR_tn_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- JSTAR_tn_ds_w2
save(srh, file = "../RData/tn_w2/srh.RData")
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')

JSTAR_m_tn_ds_w2 <- JSTAR_tn_ds_w2
JSTAR_m_tn_ds_w2$srh <- recode(JSTAR_m_tn_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'JSTAR_m_tn_ds_w2', JSTAR_m_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_m_tn_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
