---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst 

### Wave 1 

#### Study-specific variable description

| **Name** | `tome65`| 
|-|-|
| **Label** | `Q9:HOW SATISFIED ARE YOU WITH YOUR LIFE IN GENERAL?` | 
| **Table name** | `jstar_2007_5cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_aksst1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('tome65'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
```

```{r local_aksst1, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 


**R script:**

```{r harmo_aksst1, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_wb$id)
JSTAR_aksst_ds_w1$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=FALSE}
vari <- JSTAR_aksst_ds_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(JSTAR_aksst_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_aksst1, echo=FALSE}
evaluative_wb <- JSTAR_aksst_ds_w1
save(evaluative_wb, file = "../RData/aksst_w1/evaluative_wb.RData")
rm(evaluative_wb)
```





### Wave 2 

#### Study-specific variable description

| **Name** | `tome121`| 
|-|-|
| **Label** | `Q10B:ARE YOU SATISFIED WITH YOUR CURRENT LIFE?` | 
| **Table name** | `jstar_2009_5cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_aksst2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('tome121'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
```

```{r local_aksst2, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 


**R script:**

```{r harmo_aksst2, echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_wb$id)
JSTAR_aksst_ds_w2$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=FALSE}
vari <- JSTAR_aksst_ds_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(JSTAR_aksst_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_aksst2, echo=FALSE}
evaluative_wb <- JSTAR_aksst_ds_w2
save(evaluative_wb, file = "../RData/aksst_w2/evaluative_wb.RData")
rm(evaluative_wb)
```

### Wave 3 

#### Study-specific variable description

| **Name** | `q9`| 
|-|-|
| **Label** | `11Q9:ARE YOU SATISFIED WITH YOUR CURRENT LIFE?` | 
| **Table name** | `jstar_2011_5cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_aksst3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('q9'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
#have a wrong value
JSTAR_wb$q9[JSTAR_wb$id == 60] <- NA
```

```{r local_aksst3, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 

**R script:**

```{r harmo_aksst3, echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_wb$id)
JSTAR_aksst_ds_w3$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(JSTAR_aksst_ds_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_aksst3, echo=FALSE}
evaluative_wb <- JSTAR_aksst_ds_w3
save(evaluative_wb, file = "../RData/aksst_w3/evaluative_wb.RData")
rm(evaluative_wb)
```

#### Validation


## tn 

### Wave 1 

#### Study-specific variable description

| **Name** | `tome65`| 
|-|-|
| **Label** | `Q9:ARE YOU SATISFIED WITH YOUR CURRENT LIFE?` | 
| **Table name** | `jstar_2009_2cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_tn1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('tome65'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
```

```{r local_tn1, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 

**R script:**

```{r harmo_tn1, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_wb$id)
JSTAR_tn_ds_w1$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_tn1, echo=FALSE}
vari <- JSTAR_tn_ds_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(JSTAR_tn_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_tn1, echo=FALSE}
evaluative_wb <- JSTAR_tn_ds_w1
save(evaluative_wb, file = "../RData/tn_w1/evaluative_wb.RData")
rm(evaluative_wb)
```

#### Validation



### Wave 2 

#### Study-specific variable description

| **Name** | `q9`| 
|-|-|
| **Label** | `Q9:ARE YOU SATISFIED WITH YOUR CURRENT LIFE?` | 
| **Table name** | `jstar_2011_2cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_tn2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('q9'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
#have a wrong value
JSTAR_wb$q9[JSTAR_wb$id == 5231] <- NA
```

```{r local_tn2, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 

**R script:**

```{r harmo_tn2, echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_wb$id)
JSTAR_tn_ds_w2$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(JSTAR_tn_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_tn2, echo=FALSE}
evaluative_wb <- JSTAR_tn_ds_w2
save(evaluative_wb, file = "../RData/tn_w2/evaluative_wb.RData")
rm(evaluative_wb)
```

#### Validation


## cth 

### Wave 1 

#### Study-specific variable description

 
| **Name** | `q9`| 
|-|-|
| **Label** | `Q9:ARE YOU SATISFIED WITH YOUR CURRENT LIFE?` | 
| **Table name** | `jstar_2011_3cities` | 
| **Categories** |`1 = Satisfied` <br/> `2 = Fairly satisfied` <br/> `3 = Somewhat unsatisfied` <br/> `4 = Unsatisfied` |  
| **Description** |  |  

```{r assign_cth1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('q9'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
```

```{r local_cth1, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3,4 into 0` 

**R script:**

```{r harmo_cth1, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_wb$id)
JSTAR_cth_ds_w1$evaluative_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=0; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$evaluative_wb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(JSTAR_cth_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

```{r importOPAL_cth1, echo=FALSE}
evaluative_wb <- JSTAR_cth_ds_w1
save(evaluative_wb, file = "../RData/cth_w1/evaluative_wb.RData")
rm(evaluative_wb)
```

#### Validation



# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```