---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process

## aksst 

### Wave 1 

Not found.



### Wave 2 

#### Study-specific variable description

| **Name** | `tome156`| 
|-|-|
| **Label** | `Q19:DO YOU THINK THAT - YOU FEEL YOUR LIFE IS MEANINGFUL` | 
| **Table name** | `jstar_2009_5cities` | 
| **Categories** |`1 = Often` <br/> `2 = Sometimes` <br/> `3 = Seldom` <br/> `4 = Never` |  
| **Missings** |`NA`|  
| **Description** |  |  

```{r assign_aksst2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('tome156'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')
```

```{r local_aksst2, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "tome156") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0` 


**R script:**

```{r harmo_aksst2, echo=TRUE}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_wb$id)
JSTAR_ds_aksst_w2$eudaimonic_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2:3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=FALSE}
vari <- JSTAR_ds_aksst_w2$eudaimonic_wb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(JSTAR_ds_aksst_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```




#### Validation

```{r crosstabulation aksst_w2, echo=F}
```





### Wave 3 

#### Study-specific variable description

| **Name** | `q15_11`| 
|-|-|
| **Label** | `11Q15:YOU THINK THAT - YOU FEEL YOUR LIFE IS MEANINGFUL` | 
| **Table name** | `jstar_2011_5cities` | 
| **Categories** |`1 = Often` <br/> `2 = Sometimes` <br/> `3 = Seldom` <br/> `4 = Never` |  
| **Description** |  |  

```{r assign_aksst3, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('q15_11'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')


```

```{r local_aksst3, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q15_11") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0` 

**R script:**

```{r harmo_aksst3, echo=TRUE}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_wb$id)
JSTAR_ds_aksst_w3$eudaimonic_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2:3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_ds_aksst_w3$eudaimonic_wb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(JSTAR_ds_aksst_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



#### Validation


## tn 

### Wave 1 

Not found.

### Wave 2 

#### Study-specific variable description

| **Name** | `q15_11`| 
|-|-|
| **Label** | `11Q15:YOU THINK THAT - YOU FEEL YOUR LIFE IS MEANINGFUL` | 
| **Table name** | `jstar_2011_2cities` | 
| **Categories** |`1 = Often` <br/> `2 = Sometimes` <br/> `3 = Seldom` <br/> `4 = Never` |  
| **Description** |  |  

```{r assign_tn2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_wb','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('q15_11'), missings = TRUE)
JSTAR_wb <- opal.execute(o,'JSTAR_wb')

```

```{r local_tn2, echo=FALSE}
vari <- JSTAR_wb[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q15_11") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_wb, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0` 

**R script:**

```{r harmo_tn2, echo=TRUE}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_wb$id)
JSTAR_ds_tn_w2$eudaimonic_wb <- car::recode(JSTAR_wb[[2]], "1=2; 2=1; 3=1; 4=0; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_ds_tn_w2$eudaimonic_wb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(JSTAR_ds_tn_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



#### Validation


## cth 

### Wave 1 

Not found.

## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```