---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mintwDS.R')
```

<!-- ########################################################## --> 


# Data process

## Finland

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_date`|
|-|-|
| **Label** | `Date final results`|
| **Table name** |`Courage_Finland_w1`|
| **Type of variable** |`date`|
| **Description** |  |


```{r assign_fin, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1', variables=list('q0006_date'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
```

```{r preharm fin_w1}
COURAGE_fin_w1$minter <- as.numeric(format(COURAGE_fin_w1$q0006_date, '%m'))

```

```{r local_fin, echo=F}
vbl <- COURAGE_fin_w1$minter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "minter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_fin_w1, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```



#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$mintw <- car::recode(COURAGE_fin_w1$minter, "NA=999")
COURAGE_ds_fin_w1$mintw <- labelled(COURAGE_ds_fin_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin, echo=F}
vbl <- COURAGE_ds_fin_w1$mintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin, echo=F}
BeforeH <- table(COURAGE_fin_w1$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_fin_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```








## Poland

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_date`|
|-|-|
| **Label** | `Date final results`|
| **Table name** |`Courage_Poland_w1`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1', variables=list('q0006_date'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
```

```{r preharm pol_w1}
COURAGE_pol_w1$minter <- as.numeric(format(COURAGE_pol_w1$q0006_date, '%m'))

```

```{r local_pol1, echo=F}
vbl <- COURAGE_pol_w1$minter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "minter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_pol_w1, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$mintw <- car::recode(COURAGE_pol_w1$minter, "NA=999")
COURAGE_ds_pol_w1$mintw <- labelled(COURAGE_ds_pol_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}
vbl <- COURAGE_ds_pol_w1$mintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1, echo=F}
BeforeH <- table(COURAGE_pol_w1$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_pol_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





### Wave 2 

There is no variable.







## Spain

### Wave 1 

#### Study-specific variable description



| **Name** | `q0006_date`|
|-|-|
| **Label** | `Date final results`|
| **Table name** |`Courage_Spain_w1`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1', variables=list('q0006_date'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
```

```{r preharm spain_w1}
COURAGE_spain_w1$minter <- as.numeric(format(COURAGE_spain_w1$q0006_date, '%m'))

```

```{r local_spain1, echo=F}
vbl <- COURAGE_spain_w1$minter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "minter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w1, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$mintw <- car::recode(COURAGE_spain_w1$minter, "NA=999")
COURAGE_ds_spain_w1$mintw <- labelled(COURAGE_ds_spain_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vbl <- COURAGE_ds_spain_w1$mintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1, echo=F}
BeforeH <- table(COURAGE_spain_w1$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_spain_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```







### Wave 2 

#### Study-specific variable description



| **Name** | `q0006_date_s1`|
|-|-|
| **Label** | `Date final results`|
| **Table name** |`Courage_Spain_w2_1`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q0006_date_s1'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
```

```{r preharm spain_w2}
COURAGE_spain_w2$minter <- as.numeric(format(COURAGE_spain_w2$q0006_date_s1, '%m'))

```

```{r local_spain2, echo=F}
vbl <- COURAGE_spain_w2$minter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "minter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_spain_w2, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$mintw <- car::recode(COURAGE_spain_w2$minter, "NA=999")
COURAGE_ds_spain_w2$mintw <- labelled(COURAGE_ds_spain_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vbl <- COURAGE_ds_spain_w2$mintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2, echo=F}
BeforeH <- table(COURAGE_spain_w2$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_spain_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


