---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:
  
* Name: `mintw`
* Label: `month of interview"`
* Categories: 
    + `1 = january`
    + `2 = february`
    + `3 = march`
    + `4 = april`
    + `5 = may`
    + `6 = june`
    + `7 = july`
    + `8 = august`
    + `9 = september`
    + `10 = october`
    + `11 = november`
    + `12 = december`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`


### COURAGE - Finnish - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_date`
* Label: `Date final results`
* Type of variable: `countinous`


```{r assign_fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_inter','Courage.Courage_Finland_w1',
                         variables=list('q0006_date'), missings = TRUE)
```

```{r local_fin}
COURAGE_fin_w1_inter <- opal.execute(o,'COURAGE_fin_w1_inter')
COURAGE_fin_w1_inter$minter <- as.numeric(format(COURAGE_fin_w1_inter$q0006_date, '%m'))
Categorical_summary(var = COURAGE_fin_w1_inter$minter, missing_values = NA)
ggplot(COURAGE_fin_w1_inter, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```



#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_inter$id)
COURAGE_ds_fin_w1$mintw <- car::recode(COURAGE_fin_w1_inter$minter, "NA=999")
COURAGE_ds_fin_w1$mintw <- labelled(COURAGE_ds_fin_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin}
Categorical_summary(var = COURAGE_ds_fin_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin}
BeforeH <- table(COURAGE_fin_w1_inter$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_fin_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
C
```








### COURAGE - Polish - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_date`
* Label: `Date final results`
* Type of variable: `countinous`

```{r assign_pol1}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_inter','Courage.Courage_Poland_w1',
                         variables=list('q0006_date'), missings = TRUE)
```

```{r local_pol1}
COURAGE_pol_w1_inter <- opal.execute(o,'COURAGE_pol_w1_inter')
COURAGE_pol_w1_inter$minter <- as.numeric(format(COURAGE_pol_w1_inter$q0006_date, '%m'))
Categorical_summary(var = COURAGE_pol_w1_inter$minter, missing_values = NA)
ggplot(COURAGE_pol_w1_inter, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


R code of the ALGORITHM:

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_inter$id)
COURAGE_ds_pol_w1$mintw <- car::recode(COURAGE_pol_w1_inter$minter, "NA=999")
COURAGE_ds_pol_w1$mintw <- labelled(COURAGE_ds_pol_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1}
Categorical_summary(var = COURAGE_ds_pol_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1}
BeforeH <- table(COURAGE_pol_w1_inter$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_pol_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
C
```





### COURAGE - Polish - Wave 2 

There is no variable.







### COURAGE - Spain - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_date`
* Label: `Date final results`
* Type of variable: `countinous`

```{r assign_spain1}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_inter','Courage.Courage_Spain_w1',
                         variables=list('q0006_date'), missings = TRUE)
```

```{r local_spain1}
COURAGE_spain_w1_inter <- opal.execute(o,'COURAGE_spain_w1_inter')
COURAGE_spain_w1_inter$minter <- as.numeric(format(COURAGE_spain_w1_inter$q0006_date, '%m'))
Categorical_summary(var = COURAGE_spain_w1_inter$minter, missing_values = NA)
ggplot(COURAGE_spain_w1_inter, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


R code of the ALGORITHM:

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_inter$id)
COURAGE_ds_spain_w1$mintw <- car::recode(COURAGE_spain_w1_inter$minter, "NA=999")
COURAGE_ds_spain_w1$mintw <- labelled(COURAGE_ds_spain_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1}
Categorical_summary(var = COURAGE_ds_spain_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1}
BeforeH <- table(COURAGE_spain_w1_inter$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_spain_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
C
```







### COURAGE - Spain - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q0006_date_s1`
* Label: `Date final results`
* Type of variable: `countinous`

```{r assign_spain2}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_inter','Courage.Courage_Spain_w2_1',
                         variables=list('q0006_date_s1'), missings = TRUE)
```

```{r local_spain2}
COURAGE_spain_w1_inter <- opal.execute(o,'COURAGE_spain_w1_inter')
COURAGE_spain_w1_inter$minter <- as.numeric(format(COURAGE_spain_w1_inter$q0006_date_s1, '%m'))
Categorical_summary(var = COURAGE_spain_w1_inter$minter, missing_values = NA)
ggplot(COURAGE_spain_w1_inter, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w1_inter$id)
COURAGE_ds_spain_w2$mintw <- car::recode(COURAGE_spain_w1_inter$minter, "NA=999")
COURAGE_ds_spain_w2$mintw <- labelled(COURAGE_ds_spain_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2}
Categorical_summary(var = COURAGE_ds_spain_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2}
BeforeH <- table(COURAGE_spain_w1_inter$minter, useNA = "ifany")
AfterH <- table(COURAGE_ds_spain_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```

# Quality estimation
No comments.


```{r save, echo=FALSE}
mintw <- COURAGE_ds_spain_w1
save(mintw, file = "../RData/spain_w1/mintw.RData")
rm(mintw)

mintw <- COURAGE_ds_spain_w2
save(mintw, file = "../RData/spain_w2/mintw.RData")
rm(mintw)

mintw <- COURAGE_ds_pol_w1
save(mintw, file = "../RData/pol_w1/mintw.RData")
rm(mintw)


mintw <- COURAGE_ds_fin_w1
save(mintw, file = "../RData/fin_w1/mintw.RData")
rm(mintw)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


