---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```

<!-- ########################################################## --> 

# Data process

## Finnish 

### Wave 1 

#### Study-specific variable description


```{r assign_fin, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',
                         variables=list('q1009_sex'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_fin, echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$respondent <- 0
COURAGE_ds_fin_w1$respondent <- labelled(COURAGE_ds_fin_w1$respondent, labels = cat_label)
label(COURAGE_ds_fin_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_fin, echo=FALSE}
vari <- COURAGE_ds_fin_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_fin, echo=FALSE}
respondent <- COURAGE_ds_fin_w1
save(respondent, file = "../RData/fin_w1/respondent.RData")
rm(respondent)
```






## Polish 

### Wave 1 

#### Study-specific variable description

 

```{r assign_pol1, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',
                         variables=list('q1009_sex'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_pol1, echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$respondent <- 0
COURAGE_ds_pol_w1$respondent <- labelled(COURAGE_ds_pol_w1$respondent, labels = cat_label)
label(COURAGE_ds_pol_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_pol1, echo=FALSE}
vari <- COURAGE_ds_pol_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_pol1, echo=FALSE}
respondent <- COURAGE_ds_pol_w1
save(respondent, file = "../RData/pol_w1/respondent.RData")
rm(respondent)
```



### Wave 2 

#### Study-specific variable description

```{r assign_pol2, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',
                         variables=list('q0403b_first_02_s1'), missings = TRUE)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_pol2, echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$respondent <- 0
COURAGE_ds_pol_w2$respondent <- labelled(COURAGE_ds_pol_w2$respondent, labels = cat_label)
label(COURAGE_ds_pol_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_pol2, echo=FALSE}
vari <- COURAGE_ds_pol_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_pol2, echo=FALSE}
respondent <- COURAGE_ds_pol_w2
save(respondent, file = "../RData/pol_w2/respondent.RData")
rm(respondent)
```







## Spain 

### Wave 1 

#### Study-specific variable description

```{r assign_spain1, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',
                         variables=list('q1009_sex'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 


**R script:**

```{r harmo_spain1, echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$respondent <- 0
COURAGE_ds_spain_w1$respondent <- labelled(COURAGE_ds_spain_w1$respondent, labels = cat_label)
label(COURAGE_ds_spain_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_spain1, echo=FALSE}
vari <- COURAGE_ds_spain_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



```{r importOPAL_spain1, echo=FALSE}
respondent <- COURAGE_ds_spain_w1
save(respondent, file = "../RData/spain_w1/respondent.RData")
rm(respondent)
```





### Wave 2 

#### Study-specific variable description

```{r assign_spain2, echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',
                         variables=list('q0002_hhid'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_spain2, echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$respondent <- 0
COURAGE_ds_spain_w2$respondent <- labelled(COURAGE_ds_spain_w2$respondent, labels = cat_label)
label(COURAGE_ds_spain_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_spain2, echo=FALSE}
vari <- COURAGE_ds_spain_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_spain2, echo=FALSE}
respondent <- COURAGE_ds_spain_w2
save(respondent, file = "../RData/spain_w2/respondent.RData")
rm(respondent)
```

# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
