---
title: "Household ID"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/household_idDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/household_idDS.R')
```



# Data process



## Finland


### Wave 1


#### Study-specific variable description

| **Name** | `q0002_hhid`|
|-|-|
| **Label** | `HOUSEHOLD ID`|
| **Table name**  | `Courage_Finland_w1`|
| **Categories** | `text`|


```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q0002_hhid'), missings = T)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')

```



#### Harmonisation algorithm



**R script:**

```{r harmo fin_w1}

# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$household_id <- as.character(COURAGE_fin_w1$q0002_hhid)

```



## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `q0002_hhid`|
|-|-|
| **Label** | `HOUSEHOLD ID`|
| **Table name**  | `Courage_Poland_w1`|
| **Categories** | `text`|

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1',variables=list('q0002_hhid'), missings = T)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')

```


#### Harmonisation algorithm



**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)
COURAGE_ds_pol_w1$household_id <- as.character(COURAGE_pol_w1$q0002_hhid)

```



### Wave 2

#### Study-specific variable description

No variable

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2',variables=list('q1503_work_now_s1'), missings = T)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')

```


#### Harmonisation algorithm

* `Take the householdID's from wave 1. This covers all participants since thare is no refreshment.`

**R script:**

```{r harmo pol_w2}

COURAGE_pol_w2 <- left_join(COURAGE_pol_w2,COURAGE_pol_w1,by="id")

# Categorical variable harmonization
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$household_id <- as.character(COURAGE_pol_w2$q0002_hhid)

```



## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q0002_hhid`|
|-|-|
| **Label** | `HOUSEHOLD ID`|
| **Table name**  | `Courage_Spain_w1`|
| **Categories** | `text`|

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1',variables=list('q0002_hhid'), missings = T)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')

```

#### Harmonisation algorithm


**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$household_id <- as.character(COURAGE_spain_w1$q0002_hhid)

```



### Wave 2

#### Study-specific variable description

| **Name** | `q0002_hhid`|
|-|-|
| **Label** | `HOUSEHOLD ID`|
| **Table name**  | `Courage_Spain_w2_1`|
| **Categories** | `text`|

```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q0002_hhid'), missings = T)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')

```



#### Harmonisation algorithm


**R script:**

```{r harmo spain_w2}

# Categorical variable harmonization
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$household_id <- as.character(COURAGE_spain_w2$q0002_hhid)

```




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


lb.hds <- list(fin_w1 = COURAGE_ds_fin_w1, pol_w1 = COURAGE_ds_pol_w1, spain_w1 = COURAGE_ds_spain_w1)
lf.hds <- list(pol_w2 = COURAGE_ds_pol_w2, spain_w2 = COURAGE_ds_spain_w2)


l.hds <- c(lb.hds,lf.hds)

for(index in seq_along(l.hds)){
  label(l.hds[[index]][[2]]) <- ds_label
  household_id <- l.hds[[index]]
  save(household_id, file = paste0(datafolder,names(l.hds)[index],"/household_id.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





