---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```




# Data process

## Mexico

### Wave 1 

```{r read1, include=FALSE}
opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')
```


#### Harmonisation algorithm

It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo11}
MHAS_ds_w1 <- tibble(id=MHAS_id_w1$id)
MHAS_ds_w1$living_status <- 0
MHAS_ds_w1$living_status <- labelled(MHAS_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=F}
vari <- MHAS_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstab11, echo=F}
```



### Wave 2

#### Study-specific variable description


| **Name** |`tipne_03`|`fallecido_03`|
|-|-|-|
| **Label** |`Type of non-interview 2003`|`Died between 2001 and 2003`|
| **Table name** |`master_follow_up_file_2012_nomissUNID`|`master_follow_up_file_2012_nomissUNID`|
| **Categories** |`0 = Interviewed`<br/>`21 = Changed location and cannot be located`<br/>`22 = Refused Core Interview`<br/>`23 =  Refused Proxy Interview`<br/>`24 = Refused Next of Kin Interview`<br/>`25 = Unable without informant`<br/> `26 = Absent and there is no informant`<br/>`27 = Deceased without an informant`<br/>`28 = Deceased in 2001 and no interview in 2003`<br/>`29 = Other`|`0 = Alive in 2003`<br/>`1 = Died between 2001-2003`|
| **Description** |  |  |



```{r read2, include=FALSE}

opal.assign.table.tibble(o, 'MHAS_is1','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID', variables=list('tipne_03', 'tipent_03', 'fallecido_03'), missings = TRUE)
MHAS_is1 <- opal.execute(o,'MHAS_is1')

opal.assign.table.tibble(o, 'MHAS_is2','Mexican Health Aging Study.MHAS_2003', variables=list('a_tipent'), missings = TRUE)
MHAS_is2 <- opal.execute(o,'MHAS_is2')

opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')

#sum(MHAS_is2$id %in% MHAS_is1$id) #hay 11 ind que no aparecen en master_follow up 
#MHAS_is2[which(!(MHAS_is2$id %in% MHAS_is1$id)),]

#sum(MHAS_id_w1$id %in% MHAS_is2$id)

ids_w1_w2 <- tibble(id=c(MHAS_is2$id, MHAS_id_w1$id[!(MHAS_id_w1$id %in% MHAS_is2$id)]))

MHAS_ls_w2 <- left_join(x=ids_w1_w2, y=MHAS_is1, by='id')

#dim(MHAS_id_w1)
#dim(MHAS_is2)
#sum(MHAS_is2$id %in% MHAS_id_w1$id) #13676-13373=303 individuos nuevos de la w2
#View(MHAS_is2[!(MHAS_is2$id %in% MHAS_id_w1$id),])

#sum(!is.na(MHAS_ls_w2$tipent_03[which(is.na(MHAS_ls_w2$tipne_03) | MHAS_ls_w2$tipne_03>20)])) #todos NA
#View(MHAS_ls_w2[which(is.na(MHAS_ls_w2$tipne_03) | MHAS_ls_w2$tipne_03>20),])

#table(MHAS_ls_w2$tipne_03, useNA = 'ifany')
```

```{r local2, echo=F}
vari <- MHAS_ls_w2$tipne_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w2, aes(x=factor(tipne_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 

vari <- MHAS_ls_w2$fallecido_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w2, aes(x=factor(fallecido_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that appear at wave 2 and tipne_03=0 and fallecido_03=0 into 0`
* `individuals that doesn't appear at wave 2:`
    + `tipne_03 = 27 or 28 or fallecido_03 = 1 into 1`
    + `else into 2`
    


```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_ls_w2$id)
MHAS_ds_w2$living_status <- 2
MHAS_ds_w2$living_status[which(MHAS_ds_w2$id %in% MHAS_is2$id)] <- 0
MHAS_ds_w2$living_status[which(MHAS_ls_w2$tipne_03 %in% c(27,28) | MHAS_ls_w2$fallecido_03==1)] <- 1
MHAS_ds_w2$living_status <- labelled(MHAS_ds_w2[[2]], labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=F}
BeforeH <- c(dim(MHAS_is2)[1], sum(c(sum(MHAS_ls_w2$tipne_03 %in% c(27,28)), sum(MHAS_ls_w2$fallecido_03==1, na.rm = TRUE))), dim(MHAS_ls_w2)[1]-dim(MHAS_is2)[1] - sum(MHAS_ls_w2$tipne_03 %in% c(27,28)))
AfterH <- table(MHAS_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH) 
kable(C)
```


### Wave 3

#### Study-specific variable description

| **Name** |`fallecido_12`|`fallecido_03`|
|-|-|-|
| **Label** |`Died between 2003 and 2012`|`Died between 2001 and 2003`|
| **Table name** |`master_follow_up_file_2012_nomissUNID`|`master_follow_up_file_2012_nomissUNID`|
| **Categories** |`0 = Alive in 2012`<br/>`1 = Died between 2003-2012`|`0 = Alive in 2003`<br/>`1 = Died between 2001-2003`|
| **Description** |  |  |

```{r read3, include=FALSE}
opal.assign.table.tibble(o, 'MHAS_master','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID', variables=list('tipne_12', 'fallecido_12', 'fallecido_03'), missings = TRUE)
MHAS_master <- opal.execute(o,'MHAS_master')

opal.assign.table.tibble(o, 'MHAS_id_w3','Mexican Health Aging Study.MHAS_2012_new', variables=list('tipent_12'), missings = TRUE)
MHAS_id_w3 <- opal.execute(o,'MHAS_id_w3')

opal.assign.table.tibble(o, 'MHAS_id_w2','Mexican Health Aging Study.MHAS_2003', variables=list('a_tipent'), missings = TRUE)
MHAS_id_w2 <- opal.execute(o,'MHAS_id_w2')

opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')

#table(MHAS_master$tipne_12[which(MHAS_master$id %in% MHAS_id_w3$id)], useNA = 'ifany') #todos 1


ids_w1_w2_v <- c(MHAS_id_w2$id, MHAS_id_w1$id[!(MHAS_id_w1$id %in% MHAS_id_w2$id)])
ids_w1_w2_w3_v <- c(MHAS_id_w3$id, ids_w1_w2_v[!(ids_w1_w2_v %in% MHAS_id_w3$id)])

ids_w1_w2_w3 <- tibble(id=ids_w1_w2_w3_v)


MHAS_ls_w3 <- left_join(x=ids_w1_w2_w3, y=MHAS_master, by='id')
```

```{r local3, echo=F}
vari <- MHAS_ls_w3$fallecido_12
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w3, aes(x=factor(fallecido_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living status") + ylab("Frequency")

vari <- MHAS_ls_w3$fallecido_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w3, aes(x=factor(fallecido_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living status") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variables, they have to be recoded as follows:

* `individuals that appear at wave 3, fallecido_03=0 and fallecido_12=0 into 0`
* `individuals that doesn't appear at wave 3:`
    + `fallecido_12 = 1 into 1`
    + `otherwise into 2`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_ls_w3$id)
MHAS_ds_w3$living_status <- 2
MHAS_ds_w3$living_status[which(MHAS_ds_w3$id %in% MHAS_id_w3$id)] <- 0
MHAS_ds_w3$living_status[which(MHAS_ls_w3$fallecido_12==1 | MHAS_ls_w3$fallecido_03==1)] <- 1
MHAS_ds_w3$living_status <- labelled(MHAS_ds_w3[[2]], labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab3, echo=F}
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```









# Quality estimation
In each wave there are refreshment of individuals, for this reason the number of individuals in each wave is the 
number of individuals that are interviewed in that wave and the individuals that weren't interviewed but were in the 
previous waves. 





```{r closeRsession, echo=FALSE}
opal.logout(o)
```

