---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```


# Data process

## Mexico

### Wave 1 

```{r read1, include=FALSE}
opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')
```


#### Harmonisation algorithm

It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo11}
MHAS_ds_w1 <- tibble(id=MHAS_id_w1$id)
MHAS_ds_w1$living_status <- 0
MHAS_ds_w1$living_status <- labelled(MHAS_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=F}
vari <- MHAS_ds_w1$living_status
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstab11, echo=F}
```



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `tipne_03`
* Label: `Type of non-interview 2003`
* Categories: 
    + `0 = Interviewed`
    + `21 = Changed location and cannot be located`
    + `22 = Refused Core Interview`
    + `23 =  Refused Proxy Interview`
    + `24 = Refused Next of Kin Interview`
    + `25 = Unable without informant`
    + `26 = Absent and there is no informant`
    + `27 = Deceased without an informant`
    + `28 = Deceased in 2001 and no interview in 2003`
    + `29 = Other`

* Name: `fallecido_03`
* Label: `Died between 2001 and 2003`
* Categories: 
    + `0 = Interviewed`
    + `21 = Changed location and cannot be located`

```{r read2, include=FALSE}
opal.assign.table.tibble(o, 'MHAS_is1','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID', variables=list('tipne_03', 'tipent_03', 'fallecido_03'), missings = TRUE)
MHAS_is1 <- opal.execute(o,'MHAS_is1')

opal.assign.table.tibble(o, 'MHAS_is2','Mexican Health Aging Study.MHAS_2003', variables=list('a_tipent'), missings = TRUE)
MHAS_is2 <- opal.execute(o,'MHAS_is2')

opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')

#sum(MHAS_is2$id %in% MHAS_is1$id) #hay 11 ind que no aparecen en master_follow up 
#MHAS_is2[which(!(MHAS_is2$id %in% MHAS_is1$id)),]

#sum(MHAS_id_w1$id %in% MHAS_is2$id)

ids_w1_w2 <- tibble(id=c(MHAS_is2$id, MHAS_id_w1$id[!(MHAS_id_w1$id %in% MHAS_is2$id)]))

MHAS_ls_w2 <- left_join(x=ids_w1_w2, y=MHAS_is1, by='id')

#dim(MHAS_id_w1)
#dim(MHAS_is2)
#sum(MHAS_is2$id %in% MHAS_id_w1$id) #13676-13373=303 individuos nuevos de la w2
#View(MHAS_is2[!(MHAS_is2$id %in% MHAS_id_w1$id),])

#sum(!is.na(MHAS_ls_w2$tipent_03[which(is.na(MHAS_ls_w2$tipne_03) | MHAS_ls_w2$tipne_03>20)])) #todos NA
#View(MHAS_ls_w2[which(is.na(MHAS_ls_w2$tipne_03) | MHAS_ls_w2$tipne_03>20),])

#table(MHAS_ls_w2$tipne_03, useNA = 'ifany')
```

```{r local2, echo=F}
vari <- MHAS_ls_w2$tipne_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w2, aes(x=factor(tipne_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of interview") + ylab("Frequency") 

vari <- MHAS_ls_w2$fallecido_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w2, aes(x=factor(fallecido_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of interview") + ylab("Frequency") 
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `individuals that appear at wave 2 and tipne_03=0 and fallecido_03=0 into 0`
* `individuals that doesn't appear at wave 2:`
    + `tipne_03 = 27 or 28 or fallecido_03 = 1 into 1`
    + `else into 2`
    


```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_ls_w2$id)
MHAS_ds_w2$living_status <- 2
MHAS_ds_w2$living_status[which(MHAS_ds_w2$id %in% MHAS_is2$id)] <- 0
MHAS_ds_w2$living_status[which(MHAS_ls_w2$tipne_03 %in% c(27,28) | MHAS_ls_w2$fallecido_03==1)] <- 1
MHAS_ds_w2$living_status <- labelled(MHAS_ds_w2[[2]], labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=F}
BeforeH <- c(dim(MHAS_is2)[1], sum(c(sum(MHAS_ls_w2$tipne_03 %in% c(27,28)), sum(MHAS_ls_w2$fallecido_03==1, na.rm = TRUE))), dim(MHAS_ls_w2)[1]-dim(MHAS_is2)[1] - sum(MHAS_ls_w2$tipne_03 %in% c(27,28)))
AfterH <- table(MHAS_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH) 
kable(C)
```


### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:
   
* Name: `fallecido_12`
* Label: `Died between 2003 and 2012`
* Categories: 
    + `0 = Alive in 2012`
    + `1 = Died between 2003-2012`

```{r read3, include=FALSE}
opal.assign.table.tibble(o, 'MHAS_master','Mexican Health Aging Study.master_follow_up_file_2012_nomissUNID', variables=list('tipne_12', 'fallecido_12', 'fallecido_03'), missings = TRUE)
MHAS_master <- opal.execute(o,'MHAS_master')

opal.assign.table.tibble(o, 'MHAS_id_w3','Mexican Health Aging Study.MHAS_2012_new', variables=list('tipent_12'), missings = TRUE)
MHAS_id_w3 <- opal.execute(o,'MHAS_id_w3')

opal.assign.table.tibble(o, 'MHAS_id_w2','Mexican Health Aging Study.MHAS_2003', variables=list('a_tipent'), missings = TRUE)
MHAS_id_w2 <- opal.execute(o,'MHAS_id_w2')

opal.assign.table.tibble(o, 'MHAS_id_w1','Mexican Health Aging Study.MHAS-2001', variables=list('unhhid'), missings = TRUE)
MHAS_id_w1 <- opal.execute(o,'MHAS_id_w1')

#table(MHAS_master$tipne_12[which(MHAS_master$id %in% MHAS_id_w3$id)], useNA = 'ifany') #todos 1


ids_w1_w2_v <- c(MHAS_id_w2$id, MHAS_id_w1$id[!(MHAS_id_w1$id %in% MHAS_id_w2$id)])
ids_w1_w2_w3_v <- c(MHAS_id_w3$id, ids_w1_w2_v[!(ids_w1_w2_v %in% MHAS_id_w3$id)])

ids_w1_w2_w3 <- tibble(id=ids_w1_w2_w3_v)


MHAS_ls_w3 <- left_join(x=ids_w1_w2_w3, y=MHAS_master, by='id')
```

```{r local3, echo=F}
vari <- MHAS_ls_w3$fallecido_12
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w3, aes(x=factor(fallecido_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living status") + ylab("Frequency")

vari <- MHAS_ls_w3$fallecido_03
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_ls_w3, aes(x=factor(fallecido_03))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living status") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variables, they have to be recoded as follows:

* `individuals that appear at wave 3, fallecido_03=0 and fallecido_12=0 into 0`
* `individuals that doesn't appear at wave 3:`
    + `fallecido_12 = 1 into 1`
    + `otherwise into 2`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_ls_w3$id)
MHAS_ds_w3$living_status <- 2
MHAS_ds_w3$living_status[which(MHAS_ds_w3$id %in% MHAS_id_w3$id)] <- 0
MHAS_ds_w3$living_status[which(MHAS_ls_w3$fallecido_12==1 | MHAS_ls_w3$fallecido_03==1)] <- 1
MHAS_ds_w3$living_status <- labelled(MHAS_ds_w3[[2]], labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab3, echo=F}
```

# Quality estimation
In each wave there are refreshment of individuals, for this reason the number of individuals in each wave is the 
number of individuals that are interviewed in that wave and the individuals that weren't interviewed but were in the 
previous waves. 



<!--- ################################### Import to OPAL #################################-->
```{r importOPAL, echo=FALSE}
living_status <- MHAS_m_ds_w1   <- MHAS_ds_w1
save(living_status, file = "../RData/w1/living_status.RData")
rm(living_status)

living_status <- MHAS_m_ds_w2   <- MHAS_ds_w2
save(living_status, file = "../RData/w2/living_status.RData")
rm(living_status)

living_status <- MHAS_m_ds_w3   <- MHAS_ds_w3
save(living_status, file = "../RData/w3/living_status.RData")
rm(living_status)


l.hds <- list(MHAS_ds_w1 = MHAS_ds_w1 , MHAS_ds_w2 = MHAS_ds_w2, MHAS_ds_w3=MHAS_ds_w3)

m.hds <- list(MHAS_m_ds_w1 = MHAS_m_ds_w1 , MHAS_m_ds_w2 = MHAS_m_ds_w2, MHAS_m_ds_w3 = MHAS_m_ds_w3)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1))

  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}

# Table HRS
t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]))
names(t.hds)<-c("val", "label", "Wave1", "Wave2", "Wave3")
kable(t.hds)
```



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

