---
title: "Time walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/t_walksDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/t_walksDS.R')
```



# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

| **Name** | `bh105` |
|-|-|
| **Label** | `During the last 7 days, on how many days did you walk for at least 10 minutes?` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories:**| `continuous`|
| **Missings:**| `-99 = refused`<br/> `-98 = don't know`|
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('bh105'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1')
```

```{r local w1, echo=F}
vbl <- TILDA_w1$bh105
kable(Continuous_summary(vbl, missing_values = c(-99,-98))[3], caption = 'bh105') 
pander(Continuous_summary(vbl, missing_values = c(-99,-98))$summary, caption = "Summary")
ggplot(TILDA_w1, aes(bh105)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of walks") + ylab("Frequency") + coord_cartesian(xlim = c(-.45,7.45))
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `>0 into 1`
* `-99 into 997`
* `-98 into 998`


**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$t_walks <- rep(1,length(TILDA_w1$id))
TILDA_ds_w1$t_walks[TILDA_w1$bh105==0] <- 0
TILDA_ds_w1$t_walks[TILDA_w1$bh105==-98] <- 998
TILDA_ds_w1$t_walks[TILDA_w1$bh105==-99] <- 997 
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- TILDA_ds_w1$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$t_walks)
X <- table(TILDA_w1$bh105)
BeforeH <- c(X[3], sum(X[4:10]), X[1:2])
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("0->0", "otherwise->1", "-99->997", "-98->998")
kable(C)
```

```{r importOPAL w1, echo=F}
label(TILDA_ds_w1$t_walks) <- ds_label
t_walks <- TILDA_ds_w1 
save(t_walks, file = paste0(datafolder,"w1/t_walks.RData"))
rm(t_walks)
```





### Wave 2

Not found.



# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
