---
title: "Smoking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/smokingDS.R')
```





# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

| **Name** | `BEHsmoker` |
|-|-|
| **Label** | `Smoker` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories:**| `0 = Never` <br/> `1 = Past`<br/> `2 = Current`|
| **Missings:**|`NA`|
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('BEHsmoker'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1')
```

```{r local w1, echo=F}
vbl <- TILDA_w1$BEHsmoker
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(BEHsmoker))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$smoking <- car::recode(TILDA_w1$BEHsmoker, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- TILDA_ds_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=F}
label(TILDA_ds_w1$smoking) <- ds_label
smoking <- TILDA_ds_w1 
save(smoking, file = paste0(datafolder,"w1/smoking.RData"))
rm(smoking)
```





### Wave 2

Not found.





# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
