---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `SCQalcohol`|`SCQalcofreq`|
|-|-|-|
| **Label** | `drink alcohol`|`frequency of drinking alcohol`|
| **Table name**  | `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** | `1 =  yes`<br/>`2 = no`|`1 = almost every day`<br/>`2 = five or six days a week`<br/>`3 = three or four days a week`<br/>`4 = once or twice a week`<br/>`5 = once or twice a month`<br/>`6 = less than once a month`<br/>`7 = not at all in the last 6 months`<br/>`-878 = Adjacent boxes 7&8 ticked`<br/>`-867 = Adjacent boxes 6&7 ticked`<br/>`-856 = Adjacent boxes 5&6 ticked`<br/>`-845 = Adjacent boxes 4&5 ticked`<br/>`-834 = Adjacent boxes 3&4 ticked`<br/>`-823 = Adjacent boxes 2&3 ticked`<br/>`-812 = Adjacent boxes 1&2 ticked`|
| **Missings** |`-99 = not answered`<br/>`NA`|`-9 = Refused`<br/>`-99 = Refused`<br/>`-98 = Don't Know`<br/>`-1 = Not applicable`<br/>`NA` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('SCQalcohol','SCQalcofreq'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$SCQalcohol
kable(Categorical_summary(vbl, missing_values = c(-99))[3], caption = 'SCQalcohol')
kable(Categorical_summary(vbl, missing_values = c(-99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(SCQalcohol))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$SCQalcofreq
kable(Categorical_summary(vbl, missing_values = c(-99,-9,-98,-1))[3], caption = 'SCQalcofreq')
kable(Categorical_summary(vbl, missing_values = c(-99,-9,-98,-1))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(SCQalcofreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `SCQalcohol` it has to be recoded as follows:

* `2  into 0`
* `1 into 1`
* `-99 into 995`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `SCQalcofreq` it has to be recoded as follows:

* `-1,7 into 0`
* `6,5,-856 into 1`
* `1,2,3,4,-845,-834,-823,-812 into 2`
* `-99 into 997`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$current_oh <-car::recode(TILDA_w1$SCQalcohol, "2=0; -99=995; NA=999")
TILDA_ds_w1$freq_oh <-car::recode(TILDA_w1$SCQalcofreq, "c(-1,7)=0; c(5,6,-856)=1; c(1,2,3,4,-845,-834,-823,-812)=2; -99=997; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- TILDA_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2


#### Study-specific variable description



| **Name** | `SCQAlcoHis2`|`SCQAlcoFreq1`|
|-|-|-|
| **Label** | `SCQAlcoHis2: Have you had an alcoholic drink of any kind in the last 12 months?`|`During the last 12 months, how often have you had drunk any alcoholic beverages, like beer, cider, wine, spirits or cocktails?`|
| **Table name**  | `TILDA-AMF-v23`| `TILDA-AMF-v23`|
| **Categories** |  `1 =  Yes`<br/>`2 = No`  |`1 = Daily`<br/>`2 = 4-6 days a week`<br/>`3 = 2-3 days a week`<br/>`4 = Once a week`<br/>`5 = 2-3 days a month`<br/>`6 = Once a month`<br/>`7 = One or a couple of days per year`<br/>`-878 = Adjacent boxes 7&8 ticked`<br/>`-867 = Adjacent boxes 6&7 ticked`<br/>`-856 = Adjacent boxes 5&6 ticked`<br/>`-845 = Adjacent boxes 4&5 ticked`<br/>`-834 = Adjacent boxes 3&4 ticked`<br/>`-823 = Adjacent boxes 2&3 ticked`<br/>`-812 = Adjacent boxes 1&2 ticked`|
| **Missings** | `-99 = No Response`<br/>`-1 = Not applicable`<br/>`NA` |`-99 = No Response`<br/>`-1 = Not applicable`<br/>`NA` |
| **Description** |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23',variables=list('SCQAlcoHis2','SCQAlcoFreq1'), missings = T)
TILDA_w2 <- opal.execute(o,'TILDA_w2')

```

```{r local w2, echo=F}

vbl <- TILDA_w2$SCQAlcoHis2
kable(Categorical_summary(vbl, missing_values = c(-99,-1))[3], caption = 'SCQAlcoHis2')
kable(Categorical_summary(vbl, missing_values = c(-99,-1))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(SCQAlcoHis2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$SCQAlcoFreq1
kable(Categorical_summary(vbl, missing_values = c(-99,-1))[3], caption = 'SCQAlcoFreq1')
kable(Categorical_summary(vbl, missing_values = c(-99,-1))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(SCQAlcoFreq1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `SCQAlcoHis2` it has to be recoded as follows:

* `-1,2  into 0`
* `1 into 1`
* `-99 into 995`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `SCQAlcoFreq1` it has to be recoded as follows:

* `-1 into 0`
* `current_oh == 0 into 0`
* `6,5,7,-856,-867 into 1`
* `1,2,3,4,-845,-834,-823,-812 into 2`
* `-99 into 995`
* `NA into 999`


**R script:**

```{r harmo w2}


# Categorical variable harmonization
TILDA_ds_w2 <- tibble(id=TILDA_w2$id)
TILDA_ds_w2$current_oh <- car::recode(TILDA_w2$SCQAlcoHis2, "c(2,-1)=0; -99=995; NA=999")
TILDA_ds_w2$freq_oh <-car::recode(TILDA_w2$SCQAlcoFreq1, "-1=0; c(5,6,7,-856,-867)=1; c(1,2,3,4,-845,-834,-823,-812)=2; -99=995; NA=999")
TILDA_ds_w2$freq_oh[which(TILDA_ds_w2$current_oh==0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- TILDA_ds_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- TILDA_ds_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

```


```{r final, echo=F}

l.hds <- list(w1 = TILDA_ds_w1, w2 = TILDA_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  m_name <- paste0("TILDA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```



## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


**R script:**

```{r summ current}


t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("TILDA_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("TILDA_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```

## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


**R script:**

```{r summ freq}


t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("TILDA_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("TILDA_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation

* In wave 2, the variable `SCQAlcoFreq2` asks the same question than `SCQAlcoFreq1` with the difference that it is about the drinking freguency along the last month.
* Past drinking cannot be harmonized.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





