---
title: "Level of Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/level_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/level_paDS.R')
```



# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

| **Name** | `bh101` | `bh103` |
|-|-|-|
| **Label** | `During the last 7 days, on how many days did you do vigorous physical activity` | `During the last 7 days, on how many days did you do moderate physical activity` |
| **Table name** | `TILDA-AMF-v16` | `TILDA-AMF-v16` |
| **Categories** | `continuous`| `continuous`|
| **Missings** | `-99 = refused` <br/> `-98 = don't know`| `-99 = refused` <br/>  `-98 = don't know`|
| **Description** |  | |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('bh101','bh103'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1')
```

```{r local w1, echo=F}
vbl <- TILDA_w1$bh101
vbl_miss <- c(-99,-98)
kable(Continuous_summary(vbl, missing_values = c(-99,-98))[3], caption = 'bh101') 
pander(Continuous_summary(vbl, missing_values = c(-99,-98))$summary, caption = "Summary")
ggplot(TILDA_w1, aes(bh101)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")


vbl <- TILDA_w1$bh103
vbl_miss <- c(-99,-98)
kable(Continuous_summary(vbl, missing_values = c(-99,-98))[3], caption = 'bh103') 
pander(Continuous_summary(vbl, missing_values = c(-99,-98))$summary, caption = "Summary")
ggplot(TILDA_w1, aes(bh103)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

The harmonized variable is the highest score of both measurements and to compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `bh101=0|bh103=0 into 4`
* `bh101=1|bh103=1 into 3`
* `bh101=2-3|bh103=2-3 into 2`
* `bh101=4-7|bh103=4-7 into 1`
* `-99 into 997`
* `-98 into 998`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$level_pa <- rep(999,length(TILDA_w1$id))
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101==-98|TILDA_w1$bh103==-98)] <- 998
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101==-99|TILDA_w1$bh103==-99)] <- 997
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101==0|TILDA_w1$bh103==0)] <- 4
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101==1|TILDA_w1$bh103==1)] <- 3
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101 %in% c(2,3) | TILDA_w1$bh103 %in% c(2,3))] <- 2
TILDA_ds_w1$level_pa[which(TILDA_w1$bh101 %in% c(4,5,6,7) | TILDA_w1$bh103 %in% c(4,5,6,7))] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- TILDA_ds_w1$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}

```





### Wave 2

#### Study-specific variable description

| **Name** | `bh101` | `bh103` |
|-|-|-|
| **Label** | `During the last 7 days, on how many days did you do vigorous physical activity` | `During the last 7 days, on how many days did you do moderate physical activity` |
| **Table name** | `TILDA-AMF-v23` | `TILDA-AMF-v23` |
| **Categories** | `continuous`| `continuous`|
| **Missings** | |  `-98 = don't know`|
| **Description** |  | |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23', variables=list('bh101','bh103'), missings = TRUE)
TILDA_w2 <- opal.execute(o,'TILDA_w2')
```

```{r local w2, echo=F}

vbl <- TILDA_w2$bh101
vbl_miss <- c(-98)
kable(Continuous_summary(vbl, missing_values = c(-98))[3], caption = 'bh101') 
pander(Continuous_summary(vbl, missing_values = c(-98))$summary, caption = "Summary")
ggplot(TILDA_w2, aes(bh101)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")

vbl <- TILDA_w2$bh103
vbl_miss <- c(-98)
kable(Continuous_summary(vbl, missing_values = c(-98))[3], caption = 'bh103') 
pander(Continuous_summary(vbl, missing_values = c(-98))$summary, caption = "Summary")
ggplot(TILDA_w2, aes(bh103)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")

```

#### Harmonisation algorithm

The harmonized variable is the highest score of both measurements and to compute `level_pa` from the study-specific variable it has to be recoded as follows:

* `bh101=0|bh103=0 into 4`
* `bh101=1|bh103=1 into 3`
* `bh101=2-3|bh103=2-3 into 2`
* `bh101=4-7|bh103=4-7 into 1`
* `-98 into 998`

**R script:**

```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2$id)
TILDA_ds_w2$level_pa <- rep(999,length(TILDA_w2$id))
TILDA_ds_w2$level_pa[which(TILDA_w2$bh101==-98|TILDA_w2$bh103==-98)] <- 998
TILDA_ds_w2$level_pa[which(TILDA_w2$bh101==0|TILDA_w2$bh103==0)] <- 4
TILDA_ds_w2$level_pa[which(TILDA_w2$bh101==1|TILDA_w2$bh103==1)] <- 3
TILDA_ds_w2$level_pa[which(TILDA_w2$bh101 %in% c(2,3) | TILDA_w2$bh103 %in%  c(2,3))] <- 2
TILDA_ds_w2$level_pa[which(TILDA_w2$bh101 %in% c(4,5,6,7) | TILDA_w2$bh103 %in% c(4,5,6,7))] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- TILDA_ds_w2$level_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(level_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}

```









```{r final, echo=F}

l.hds <- list(w1 = TILDA_ds_w1, w2 = TILDA_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  m_name <- paste0("TILDA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[15,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("TILDA_m_ds_",names(l.hds)[1]))[,c("id","level_pa")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("TILDA_m_ds_",names(l.hds)[ind]))[,c("id","level_pa")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  level_pa <- l.hds[[index]]
  save(level_pa, file = paste0(datafolder,names(l.hds)[index],"/level_pa.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
