---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:
  
* Name: `ydeath`
* Label: `year of death`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`



### CHARLS - Wave 1 


There is no variable.






### CHARLS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `exb001_1`
* Label: `The Date on Which R Died (Year)`
* Type of variable: `countinous`

```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_ydeath2','CHARLS.Exit_Interview_wave2',
                         variables=list('exb001_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2}
CHARLS_w2_ydeath2 <- opal.execute(o,'CHARLS_w2_ydeath2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], exb001_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ydeath <- Add_indiv(old = CHARLS_w2_ydeath2, new = CHARLS_w2_id)

Categorical_summary(var = CHARLS_w2_ydeath$exb001_1, missing_values = NA)
ggplot(CHARLS_w2_ydeath, aes(exb001_1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


R code of the ALGORITHM:

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_ydeath$id)
CHARLS_ds_w2$ydeath <- car::recode(CHARLS_w2_ydeath$exb001_1, "NA=999")
CHARLS_ds_w2$ydeath <- labelled(CHARLS_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Categorical_summary(var = CHARLS_ds_w2$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") + xlim(2010,2014)
```

#### Validation
```{r crosstabulation2}
BeforeH <- table(CHARLS_w2_ydeath$exb001_1, useNA = "ifany")
AfterH <- table(CHARLS_ds_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```



# Quality control


No comments


```{r save, echo=FALSE}
ydeath <- CHARLS_ds_w2
save(ydeath, file = "../RData/w2/ydeath.RData")
rm(ydeath)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
