---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Age of death (Life expectancy)`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```

# Data process

## CHARLS

### Wave 1 

#### Study-specific variable description

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
```

#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

**R script:**

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_id$id)
CHARLS_ds_w1$living_status <- 0
CHARLS_ds_w1$living_status <- labelled(CHARLS_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```



### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `exb001_2`
* Label: `The Date on Which R Died (Month)`
* Type of variable: `countinous`


* Name: `exb001_1`
* Label: `The Date on Which R Died (Year)`
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_inter2','CHARLS.Weights_modif_albert_wave2',
                         variables=list('imonth', 'iyear'), missings = TRUE)
CHARLS_w2_inter2 <- opal.execute(o,'CHARLS_w2_inter2')

opal.assign.table.tibble(o, 'CHARLS_w2_death2','CHARLS.Exit_Interview_wave2',
                         variables=list('exb001_2', 'exb001_1'), missings = TRUE)
CHARLS_w2_death2 <- opal.execute(o,'CHARLS_w2_death2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
```

```{r local2, echo=F}
#there are missing individuals in w2 that participate in w1 that have to be added:
ids_missingw2 <- CHARLS_w1_id$id[!(CHARLS_w1_id$id %in% CHARLS_w2_id$id)]
ids_w2 <- as.character(c(CHARLS_w2_id$id , ids_missingw2))

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], imonth=as.numeric(new_2[,2]), iyear=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_inter <- Add_indiv(old = CHARLS_w2_inter2, new = ids_w2)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = length(new), ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new)){
    if(sum(new[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new[i]==old$id),]
    } else {
      new_2[i,] <- c(new[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], exb001_1=as.numeric(new_2[,2]),  exb001_2=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_death <- Add_indiv(old=CHARLS_w2_death2, new=ids_w2)


CHARLS_w2_ls <- merge(CHARLS_w2_inter, CHARLS_w2_death, by='id')



vari <- CHARLS_w2_ls$iyear
kable(Categorical_summary(vari, missing_values = c(-9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9))[2], caption = "Type of missing")
ggplot(CHARLS_w2_ls, aes(factor(iyear))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")

vari <- CHARLS_w2_ls$exb001_1
kable(Categorical_summary(vari, missing_values = c(-9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9))[2], caption = "Type of missing")
ggplot(CHARLS_w2_ls, aes(factor(exb001_1))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable it have to recode: 

* `the individuals include in wave 2 dataset as 0 'alive' `
* `the individuals with a value in year of death into 1 'death' `
* `the individuals don't include in wave 2 and without year of death into 2 'dropout'` 

**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_ls$id)
CHARLS_ds_w2$living_status <- 2
CHARLS_ds_w2$living_status[CHARLS_w2_ls$id %in% CHARLS_w2_id$id] <- 0
CHARLS_ds_w2$living_status[!is.na(CHARLS_w2_ls$exb001_1)] <- 1

CHARLS_ds_w2$living_status <- labelled(CHARLS_ds_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
```

# Quality estimation
No comments.

```{r save, echo=FALSE}
living_status <- CHARLS_ds_w1
save(living_status, file = "../RData/w1/living_status.RData")
rm(living_status)

living_status <- CHARLS_ds_w2
save(living_status, file = "../RData/w2/living_status.RData")
rm(living_status)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

