---
title: "Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/vig_paDS.R')
```



# Data process


## HRS

### Wave 1 

#### Study-specific variable description

| **Name** | `R1VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w1` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1','HRS.HRS-HRS-w1', variables=list('R1VIGACT'), missings = TRUE)
HRS_hrs_w1 <- opal.execute(o,'HRS_hrs_w1')
```

```{r local hrs w1, echo=F}
vbl <- HRS_hrs_w1$R1VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1, aes(x=factor(R1VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1$id)
HRS_ds_hrs_w1$vig_pa <- car::recode(HRS_hrs_w1$R1VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w1, echo=F}
vbl <- HRS_ds_hrs_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** | `R2VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w2` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w2, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w2','HRS.HRS-HRS-w2', variables=list('R2VIGACT'), missings = TRUE)
HRS_hrs_w2 <- opal.execute(o,'HRS_hrs_w2')
```

```{r local hrs w2, echo=F}
vbl <- HRS_hrs_w2$R2VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2, aes(x=factor(R2VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2$id)
HRS_ds_hrs_w2$vig_pa <- car::recode(HRS_hrs_w2$R2VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w2, echo=F}
vbl <- HRS_ds_hrs_w2$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w2, echo=F}
```



### Wave 3 

#### Study-specific variable description

| **Name** | `R3VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w3` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w3, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w3','HRS.HRS-HRS-w3', variables=list('R3VIGACT'), missings = TRUE)
HRS_hrs_w3 <- opal.execute(o,'HRS_hrs_w3')
```

```{r local hrs w3, echo=F}
vbl <- HRS_hrs_w3$R3VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3, aes(x=factor(R3VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3$id)
HRS_ds_hrs_w3$vig_pa <- car::recode(HRS_hrs_w3$R3VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w3, echo=F}
vbl <- HRS_ds_hrs_w3$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w3, echo=F}
```



### Wave 4

#### Study-specific variable description

| **Name** | `R4VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w4` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4','HRS.HRS-HRS-w4', variables=list('R4VIGACT'), missings = TRUE)
HRS_hrs_w4 <- opal.execute(o,'HRS_hrs_w4')
```

```{r local hrs w4, echo=F}
vbl <- HRS_hrs_w4$R4VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4, aes(x=factor(R4VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4$id)
HRS_ds_hrs_w4$vig_pa <- car::recode(HRS_hrs_w4$R4VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w4, echo=F}
vbl <- HRS_ds_hrs_w4$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `R5VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w5` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5','HRS.HRS-HRS-w5', variables=list('R5VIGACT'), missings = TRUE)
HRS_hrs_w5 <- opal.execute(o,'HRS_hrs_w5')
```

```{r local hrs w5, echo=F}
vbl <- HRS_hrs_w5$R5VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5, aes(x=factor(R5VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5$id)
HRS_ds_hrs_w5$vig_pa <- car::recode(HRS_hrs_w5$R5VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w5, echo=F}
vbl <- HRS_ds_hrs_w5$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `R6VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-HRS-w6` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6','HRS.HRS-HRS-w6', variables=list('R6VIGACT'), missings = TRUE)
HRS_hrs_w6 <- opal.execute(o,'HRS_hrs_w6')
```

```{r local hrs w6, echo=F}
vbl <- HRS_hrs_w6$R6VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6, aes(x=factor(R6VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo hrs w6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6$id)
HRS_ds_hrs_w6$vig_pa <- car::recode(HRS_hrs_w6$R6VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w6, echo=F}
vbl <- HRS_ds_hrs_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-HRS-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7','HRS.HRS-HRS-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_hrs_w7 <- opal.execute(o,'HRS_hrs_w7')
```

```{r local hrs w7, echo=F}
vbl <- HRS_hrs_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7$id)
HRS_ds_hrs_w7$vig_pa <- car::recode(HRS_hrs_w7$R7VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w7, echo=F}
vbl <- HRS_ds_hrs_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w7, echo=F}
AfterH <- table(HRS_ds_hrs_w7$vig_pa)
X<-table(HRS_hrs_w7$R7VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_hrs_w7$R7VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 8

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-HRS-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8','HRS.HRS-HRS-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_hrs_w8 <- opal.execute(o,'HRS_hrs_w8')
```

```{r local hrs w8, echo=F}
vbl <- HRS_hrs_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8$id)
HRS_ds_hrs_w8$vig_pa <- car::recode(HRS_hrs_w8$R8VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w8, echo=F}
vbl <- HRS_ds_hrs_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w8, echo=F}
AfterH <- table(HRS_ds_hrs_w8$vig_pa)
X<-table(HRS_hrs_w8$R8VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_hrs_w8$R8VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-HRS-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9','HRS.HRS-HRS-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_hrs_w9 <- opal.execute(o,'HRS_hrs_w9')
```

```{r local hrs w9, echo=F}
vbl <- HRS_hrs_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9$id)
HRS_ds_hrs_w9$vig_pa <- car::recode(HRS_hrs_w9$R9VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w9, echo=F}
vbl <- HRS_ds_hrs_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w9, echo=F}
AfterH <- table(HRS_ds_hrs_w9$vig_pa)
X<-table(HRS_hrs_w9$R9VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_hrs_w9$R9VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-HRS-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10','HRS.HRS-HRS-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_hrs_w10 <- opal.execute(o,'HRS_hrs_w10')
```

```{r local hrs w10, echo=F}
vbl <- HRS_hrs_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10$id)
HRS_ds_hrs_w10$vig_pa <- car::recode(HRS_hrs_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w10, echo=F}
vbl <- HRS_ds_hrs_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w10, echo=F}
AfterH <- table(HRS_ds_hrs_w10$vig_pa)
X<-table(HRS_hrs_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_hrs_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-HRS-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11','HRS.HRS-HRS-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_hrs_w11 <- opal.execute(o,'HRS_hrs_w11')
```

```{r local hrs w11, echo=F}
vbl <- HRS_hrs_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11$id)
HRS_ds_hrs_w11$vig_pa <- car::recode(HRS_hrs_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w11, echo=F}
vbl <- HRS_ds_hrs_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w11, echo=F}
AfterH <- table(HRS_ds_hrs_w11$vig_pa)
X<-table(HRS_hrs_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_hrs_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





## AHEAD


### Wave 2

#### Study-specific variable description

| **Name** | `R2VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-AHEAD-w2` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2','HRS.HRS-AHEAD-w2', variables=list('R2VIGACT'), missings = TRUE)
HRS_ahead_w2 <- opal.execute(o,'HRS_ahead_w2')
```

```{r local ahead w2, echo=F}
vbl <- HRS_ahead_w2$R2VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w2, aes(x=factor(R2VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo ahead w2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2$id)
HRS_ds_ahead_w2$vig_pa <- car::recode(HRS_ahead_w2$R2VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w2, echo=F}
vbl <- HRS_ds_ahead_w2$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w2, echo=F}
```




### Wave 3 

#### Study-specific variable description

| **Name** | `R3VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-AHEAD-w3` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3','HRS.HRS-AHEAD-w3', variables=list('R3VIGACT'), missings = TRUE)
HRS_ahead_w3 <- opal.execute(o,'HRS_ahead_w3')
```

```{r local ahead w3, echo=F}
vbl <- HRS_ahead_w3$R3VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w3, aes(x=factor(R3VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo ahead w3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3$id)
HRS_ds_ahead_w3$vig_pa <- car::recode(HRS_ahead_w3$R3VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w3, echo=F}
vbl <- HRS_ds_ahead_w3$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w3, echo=F}
```





### Wave 4

#### Study-specific variable description

| **Name** | `R4VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-AHEAD-w4` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4','HRS.HRS-AHEAD-w4', variables=list('R4VIGACT'), missings = TRUE)
HRS_ahead_w4 <- opal.execute(o,'HRS_ahead_w4')
```

```{r local ahead w4, echo=F}
vbl <- HRS_ahead_w4$R4VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4, aes(x=factor(R4VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo ahead w4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4$id)
HRS_ds_ahead_w4$vig_pa <- car::recode(HRS_ahead_w4$R4VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w4, echo=F}
vbl <- HRS_ds_ahead_w4$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `R5VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-AHEAD-w5` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5','HRS.HRS-AHEAD-w5', variables=list('R5VIGACT'), missings = TRUE)
HRS_ahead_w5 <- opal.execute(o,'HRS_ahead_w5')
```

```{r local ahead w5, echo=F}
vbl <- HRS_ahead_w5$R5VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5, aes(x=factor(R5VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo ahead w5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5$id)
HRS_ds_ahead_w5$vig_pa <- car::recode(HRS_ahead_w5$R5VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w5, echo=F}
vbl <- HRS_ds_ahead_w5$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w5, echo=F}
```




### Wave 6

#### Study-specific variable description

| **Name** | `R6VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-AHEAD-w6` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6','HRS.HRS-AHEAD-w6', variables=list('R6VIGACT'), missings = TRUE)
HRS_ahead_w6 <- opal.execute(o,'HRS_ahead_w6')
```

```{r local ahead w6, echo=F}
vbl <- HRS_ahead_w6$R6VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6, aes(x=factor(R6VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo ahead w6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6$id)
HRS_ds_ahead_w6$vig_pa <- car::recode(HRS_ahead_w6$R6VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w6, echo=F}
vbl <- HRS_ds_ahead_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-AHEAD-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7','HRS.HRS-AHEAD-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_ahead_w7 <- opal.execute(o,'HRS_ahead_w7')
```

```{r local ahead w7, echo=F}
vbl <- HRS_ahead_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7$id)
HRS_ds_ahead_w7$vig_pa <- car::recode(HRS_ahead_w7$R7VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w7, echo=F}
vbl <- HRS_ds_ahead_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w7, echo=F}
AfterH <- table(HRS_ds_ahead_w7$vig_pa)
X<-table(HRS_ahead_w7$R7VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ahead_w7$R7VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 8

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-AHEAD-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8','HRS.HRS-AHEAD-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_ahead_w8 <- opal.execute(o,'HRS_ahead_w8')
```

```{r local ahead w8, echo=F}
vbl <- HRS_ahead_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8$id)
HRS_ds_ahead_w8$vig_pa <- car::recode(HRS_ahead_w8$R8VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w8, echo=F}
vbl <- HRS_ds_ahead_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w8, echo=F}
AfterH <- table(HRS_ds_ahead_w8$vig_pa)
X<-table(HRS_ahead_w8$R8VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ahead_w8$R8VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-AHEAD-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9','HRS.HRS-AHEAD-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_ahead_w9 <- opal.execute(o,'HRS_ahead_w9')
```

```{r local ahead w9, echo=F}
vbl <- HRS_ahead_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9$id)
HRS_ds_ahead_w9$vig_pa <- car::recode(HRS_ahead_w9$R9VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w9, echo=F}
vbl <- HRS_ds_ahead_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w9, echo=F}
AfterH <- table(HRS_ds_ahead_w9$vig_pa)
X<-table(HRS_ahead_w9$R9VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ahead_w9$R9VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-AHEAD-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10','HRS.HRS-AHEAD-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_ahead_w10 <- opal.execute(o,'HRS_ahead_w10')
```

```{r local ahead w10, echo=F}
vbl <- HRS_ahead_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10$id)
HRS_ds_ahead_w10$vig_pa <- car::recode(HRS_ahead_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w10, echo=F}
vbl <- HRS_ds_ahead_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w10, echo=F}
AfterH <- table(HRS_ds_ahead_w10$vig_pa)
X<-table(HRS_ahead_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ahead_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-AHEAD-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11','HRS.HRS-AHEAD-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_ahead_w11 <- opal.execute(o,'HRS_ahead_w11')
```

```{r local ahead w11, echo=F}
vbl <- HRS_ahead_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11$id)
HRS_ds_ahead_w11$vig_pa <- car::recode(HRS_ahead_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w11, echo=F}
vbl <- HRS_ds_ahead_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w11, echo=F}
AfterH <- table(HRS_ds_ahead_w11$vig_pa)
X<-table(HRS_ahead_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ahead_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```








## CODA

### Wave 4

#### Study-specific variable description

| **Name** | `R4VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-CODA-w4` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4','HRS.HRS-CODA-w4', variables=list('R4VIGACT'), missings = TRUE)
HRS_coda_w4 <- opal.execute(o,'HRS_coda_w4')
```

```{r local coda w4, echo=F}
vbl <- HRS_coda_w4$R4VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4, aes(x=factor(R4VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo coda w4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4$id)
HRS_ds_coda_w4$vig_pa <- car::recode(HRS_coda_w4$R4VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w4, echo=F}
vbl <- HRS_ds_coda_w4$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `R5VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-CODA-w5` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5','HRS.HRS-CODA-w5', variables=list('R5VIGACT'), missings = TRUE)
HRS_coda_w5 <- opal.execute(o,'HRS_coda_w5')
```

```{r local coda w5, echo=F}
vbl <- HRS_coda_w5$R5VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5, aes(x=factor(R5VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo coda w5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5$id)
HRS_ds_coda_w5$vig_pa <- car::recode(HRS_coda_w5$R5VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w5, echo=F}
vbl <- HRS_ds_coda_w5$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `R6VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-CODA-w6` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6','HRS.HRS-CODA-w6', variables=list('R6VIGACT'), missings = TRUE)
HRS_coda_w6 <- opal.execute(o,'HRS_coda_w6')
```

```{r local coda w6, echo=F}
vbl <- HRS_coda_w6$R6VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6, aes(x=factor(R6VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo coda w6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6$id)
HRS_ds_coda_w6$vig_pa <- car::recode(HRS_coda_w6$R6VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w6, echo=F}
vbl <- HRS_ds_coda_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w6, echo=F}
```






### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-CODA-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7','HRS.HRS-CODA-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_coda_w7 <- opal.execute(o,'HRS_coda_w7')
```

```{r local coda w7, echo=F}
vbl <- HRS_coda_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7$id)
HRS_ds_coda_w7$vig_pa <- car::recode(HRS_coda_w7$R7VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w7, echo=F}
vbl <- HRS_ds_coda_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w7, echo=F}
AfterH <- table(HRS_ds_coda_w7$vig_pa)
X<-table(HRS_coda_w7$R7VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_coda_w7$R7VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 8

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-CODA-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8','HRS.HRS-CODA-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_coda_w8 <- opal.execute(o,'HRS_coda_w8')
```

```{r local coda w8, echo=F}
vbl <- HRS_coda_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8$id)
HRS_ds_coda_w8$vig_pa <- car::recode(HRS_coda_w8$R8VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w8, echo=F}
vbl <- HRS_ds_coda_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w8, echo=F}
AfterH <- table(HRS_ds_coda_w8$vig_pa)
X<-table(HRS_coda_w8$R8VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_coda_w8$R8VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-CODA-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9','HRS.HRS-CODA-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_coda_w9 <- opal.execute(o,'HRS_coda_w9')
```

```{r local coda w9, echo=F}
vbl <- HRS_coda_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9$id)
HRS_ds_coda_w9$vig_pa <- car::recode(HRS_coda_w9$R9VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w9, echo=F}
vbl <- HRS_ds_coda_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w9, echo=F}
AfterH <- table(HRS_ds_coda_w9$vig_pa)
X<-table(HRS_coda_w9$R9VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_coda_w9$R9VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-CODA-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10','HRS.HRS-CODA-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_coda_w10 <- opal.execute(o,'HRS_coda_w10')
```

```{r local coda w10, echo=F}
vbl <- HRS_coda_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10$id)
HRS_ds_coda_w10$vig_pa <- car::recode(HRS_coda_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w10, echo=F}
vbl <- HRS_ds_coda_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w10, echo=F}
AfterH <- table(HRS_ds_coda_w10$vig_pa)
X<-table(HRS_coda_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_coda_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-CODA-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11','HRS.HRS-CODA-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_coda_w11 <- opal.execute(o,'HRS_coda_w11')
```

```{r local coda w11, echo=F}
vbl <- HRS_coda_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11$id)
HRS_ds_coda_w11$vig_pa <- car::recode(HRS_coda_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w11, echo=F}
vbl <- HRS_ds_coda_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w11, echo=F}
AfterH <- table(HRS_ds_coda_w11$vig_pa)
X<-table(HRS_coda_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_coda_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```







## WB

### Wave 4

#### Study-specific variable description

| **Name** | `R4VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-WB-w4` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4','HRS.HRS-WB-w4', variables=list('R4VIGACT'), missings = TRUE)
HRS_wb_w4 <- opal.execute(o,'HRS_wb_w4')
```

```{r local wb w4, echo=F}
vbl <- HRS_wb_w4$R4VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4, aes(x=factor(R4VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo wb w4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4$id)
HRS_ds_wb_w4$vig_pa <- car::recode(HRS_wb_w4$R4VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w4, echo=F}
vbl <- HRS_ds_wb_w4$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `R5VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-WB-w5` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5','HRS.HRS-WB-w5', variables=list('R5VIGACT'), missings = TRUE)
HRS_wb_w5 <- opal.execute(o,'HRS_wb_w5')
```

```{r local wb w5, echo=F}
vbl <- HRS_wb_w5$R5VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5, aes(x=factor(R5VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo wb w5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5$id)
HRS_ds_wb_w5$vig_pa <- car::recode(HRS_wb_w5$R5VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w5, echo=F}
vbl <- HRS_ds_wb_w5$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w5, echo=F}
```




### Wave 6

#### Study-specific variable description

| **Name** | `R6VIGACT` |
|-|-|
| **Label** | `R Wtr vigorus phys act 3+/wk` |
| **Table name** | `HRS-WB-w6` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6','HRS.HRS-WB-w6', variables=list('R6VIGACT'), missings = TRUE)
HRS_wb_w6 <- opal.execute(o,'HRS_wb_w6')
```

```{r local wb w6, echo=F}
vbl <- HRS_wb_w6$R6VIGACT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6, aes(x=factor(R6VIGACT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo wb w6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6$id)
HRS_ds_wb_w6$vig_pa <- car::recode(HRS_wb_w6$R6VIGACT, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w6, echo=F}
vbl <- HRS_ds_wb_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w6, echo=F}
```





### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-WB-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7','HRS.HRS-WB-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_wb_w7 <- opal.execute(o,'HRS_wb_w7')
```

```{r local wb w7, echo=F}
vbl <- HRS_wb_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7$id)
HRS_ds_wb_w7$vig_pa <- car::recode(HRS_wb_w7$R7VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w7, echo=F}
vbl <- HRS_ds_wb_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w7, echo=F}
AfterH <- table(HRS_ds_wb_w7$vig_pa)
X<-table(HRS_wb_w7$R7VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_wb_w7$R7VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 8

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-WB-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8','HRS.HRS-WB-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_wb_w8 <- opal.execute(o,'HRS_wb_w8')
```

```{r local wb w8, echo=F}
vbl <- HRS_wb_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8$id)
HRS_ds_wb_w8$vig_pa <- car::recode(HRS_wb_w8$R8VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w8, echo=F}
vbl <- HRS_ds_wb_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w8, echo=F}
AfterH <- table(HRS_ds_wb_w8$vig_pa)
X<-table(HRS_wb_w8$R8VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_wb_w8$R8VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-WB-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9','HRS.HRS-WB-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_wb_w9 <- opal.execute(o,'HRS_wb_w9')
```

```{r local wb w9, echo=F}
vbl <- HRS_wb_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9$id)
HRS_ds_wb_w9$vig_pa <- car::recode(HRS_wb_w9$R9VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w9, echo=F}
vbl <- HRS_ds_wb_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w9, echo=F}
AfterH <- table(HRS_ds_wb_w9$vig_pa)
X<-table(HRS_wb_w9$R9VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_wb_w9$R9VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-WB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10','HRS.HRS-WB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_wb_w10 <- opal.execute(o,'HRS_wb_w10')
```

```{r local wb w10, echo=F}
vbl <- HRS_wb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10$id)
HRS_ds_wb_w10$vig_pa <- car::recode(HRS_wb_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w10, echo=F}
vbl <- HRS_ds_wb_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w10, echo=F}
AfterH <- table(HRS_ds_wb_w10$vig_pa)
X<-table(HRS_wb_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_wb_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-WB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11','HRS.HRS-WB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_wb_w11 <- opal.execute(o,'HRS_wb_w11')
```

```{r local wb w11, echo=F}
vbl <- HRS_wb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11$id)
HRS_ds_wb_w11$vig_pa <- car::recode(HRS_wb_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w11, echo=F}
vbl <- HRS_ds_wb_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w11, echo=F}
AfterH <- table(HRS_ds_wb_w11$vig_pa)
X<-table(HRS_wb_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_wb_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```







## EBB


### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-EBB-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7','HRS.HRS-EBB-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_ebb_w7 <- opal.execute(o,'HRS_ebb_w7')
```

```{r local ebb w7, echo=F}
vbl <- HRS_ebb_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7$id)
HRS_ds_ebb_w7$vig_pa <- car::recode(HRS_ebb_w7$R7VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w7, echo=F}
vbl <- HRS_ds_ebb_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w7, echo=F}
AfterH <- table(HRS_ds_ebb_w7$vig_pa)
X<-table(HRS_ebb_w7$R7VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ebb_w7$R7VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 8

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-EBB-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8','HRS.HRS-EBB-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_ebb_w8 <- opal.execute(o,'HRS_ebb_w8')
```

```{r local ebb w8, echo=F}
vbl <- HRS_ebb_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8$id)
HRS_ds_ebb_w8$vig_pa <- car::recode(HRS_ebb_w8$R8VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w8, echo=F}
vbl <- HRS_ds_ebb_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w8, echo=F}
AfterH <- table(HRS_ds_ebb_w8$vig_pa)
X<-table(HRS_ebb_w8$R8VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ebb_w8$R8VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-EBB-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9','HRS.HRS-EBB-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_ebb_w9 <- opal.execute(o,'HRS_ebb_w9')
```

```{r local ebb w9, echo=F}
vbl <- HRS_ebb_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9$id)
HRS_ds_ebb_w9$vig_pa <- car::recode(HRS_ebb_w9$R9VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w9, echo=F}
vbl <- HRS_ds_ebb_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w9, echo=F}
AfterH <- table(HRS_ds_ebb_w9$vig_pa)
X<-table(HRS_ebb_w9$R9VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ebb_w9$R9VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-EBB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10','HRS.HRS-EBB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_ebb_w10 <- opal.execute(o,'HRS_ebb_w10')
```

```{r local ebb w10, echo=F}
vbl <- HRS_ebb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10$id)
HRS_ds_ebb_w10$vig_pa <- car::recode(HRS_ebb_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w10, echo=F}
vbl <- HRS_ds_ebb_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w10, echo=F}
AfterH <- table(HRS_ds_ebb_w10$vig_pa)
X<-table(HRS_ebb_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ebb_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-EBB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11','HRS.HRS-EBB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_ebb_w11 <- opal.execute(o,'HRS_ebb_w11')
```

```{r local ebb w11, echo=F}
vbl <- HRS_ebb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11$id)
HRS_ds_ebb_w11$vig_pa <- car::recode(HRS_ebb_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w11, echo=F}
vbl <- HRS_ds_ebb_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w11, echo=F}
AfterH <- table(HRS_ds_ebb_w11$vig_pa)
X<-table(HRS_ebb_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_ebb_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






## MBB


### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-MBB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign mbb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10','HRS.HRS-MBB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_mbb_w10 <- opal.execute(o,'HRS_mbb_w10')
```

```{r local mbb w10, echo=F}
vbl <- HRS_mbb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10$id)
HRS_ds_mbb_w10$vig_pa <- car::recode(HRS_mbb_w10$R10VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w10, echo=F}
vbl <- HRS_ds_mbb_w10$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation mbb w10, echo=F}
AfterH <- table(HRS_ds_mbb_w10$vig_pa)
X<-table(HRS_mbb_w10$R10VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_mbb_w10$R10VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```





### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `R Freq vigorous phys activ` |
| **Table name** | `HRS-MBB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never`|
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign mbb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11','HRS.HRS-MBB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_mbb_w11 <- opal.execute(o,'HRS_mbb_w11')
```

```{r local mbb w11, echo=F}
vbl <- HRS_mbb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2-5 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11$id)
HRS_ds_mbb_w11$vig_pa <- car::recode(HRS_mbb_w11$R11VGACTX, "2 = 0;3 = 0;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w11, echo=F}
vbl <- HRS_ds_mbb_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation mbb w11, echo=F}
AfterH <- table(HRS_ds_mbb_w11$vig_pa)
X<-table(HRS_mbb_w11$R11VGACTX)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(HRS_mbb_w11$R11VGACTX)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```











# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
