---
title: "Number of times in Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_vig_paDS.R')
```




# Data process


## HRS

### Wave 1 

#### Study-specific variable description

| **Name** | `R1VGACTF` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w1` |
| **Categories:**|  `1 = 3 or more per week` <br/> `2 = 1 to 2 per week` <br/> `3 = 1 to 3 per month` <br/> `4 = less than 1 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

  

```{r assign hrs w1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1','HRS.HRS-HRS-w1', variables=list('R1VGACTF'), missings = TRUE)
HRS_hrs_w1 <- opal.execute(o,'HRS_hrs_w1')
```

```{r local hrs w1, echo=F}
vbl <- HRS_hrs_w1$R1VGACTF
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1, aes(x=factor(R1VGACTF))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 10`
* `2 into 3`
* `3 into 1`
* `4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1$id)
HRS_ds_hrs_w1$n_vig_pa <- car::recode(HRS_hrs_w1$R1VGACTF, "1 = 10;2 = 3;4 = 1;4 = 0;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w1, echo=F}
vbl <- HRS_ds_hrs_w1$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w1, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  +scale_x_continuous(breaks=c(0,3,6,9,12))
```

#### Validation
```{r crosstabulation hrs w1, echo=F}
```

```{r importOPAL hrs w1, echo=F}




```




### Wave 2

Not found.


### Wave 3 

Not found.


### Wave 4

Not found.


### Wave 5

Not found.


### Wave 6

Not found.


### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7','HRS.HRS-HRS-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_hrs_w7 <- opal.execute(o,'HRS_hrs_w7')
```

```{r local hrs w7, echo=F}
vbl <- HRS_hrs_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7$id)
HRS_ds_hrs_w7$n_vig_pa <- car::recode(HRS_hrs_w7$R7VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w7, echo=F}
vbl <- HRS_ds_hrs_w7$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w7, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation hrs w7, echo=F}
```

```{r importOPAL hrs w7, echo=F}




```




### Wave 7

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8','HRS.HRS-HRS-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_hrs_w8 <- opal.execute(o,'HRS_hrs_w8')
```

```{r local hrs w8, echo=F}
vbl <- HRS_hrs_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8$id)
HRS_ds_hrs_w8$n_vig_pa <- car::recode(HRS_hrs_w8$R8VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w8, echo=F}
vbl <- HRS_ds_hrs_w8$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w8, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation hrs w8, echo=F}
```

```{r importOPAL hrs w8, echo=F}




```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9','HRS.HRS-HRS-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_hrs_w9 <- opal.execute(o,'HRS_hrs_w9')
```

```{r local hrs w9, echo=F}
vbl <- HRS_hrs_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9$id)
HRS_ds_hrs_w9$n_vig_pa <- car::recode(HRS_hrs_w9$R9VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w9, echo=F}
vbl <- HRS_ds_hrs_w9$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w9, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation hrs w9, echo=F}
```

```{r importOPAL hrs w9, echo=F}




```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10','HRS.HRS-HRS-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_hrs_w10 <- opal.execute(o,'HRS_hrs_w10')
```

```{r local hrs w10, echo=F}
vbl <- HRS_hrs_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10$id)
HRS_ds_hrs_w10$n_vig_pa <- car::recode(HRS_hrs_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w10, echo=F}
vbl <- HRS_ds_hrs_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation hrs w10, echo=F}
```

```{r importOPAL hrs w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-HRS-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign hrs w11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11','HRS.HRS-HRS-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_hrs_w11 <- opal.execute(o,'HRS_hrs_w11')
```

```{r local hrs w11, echo=F}
vbl <- HRS_hrs_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11$id)
HRS_ds_hrs_w11$n_vig_pa <- car::recode(HRS_hrs_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w11, echo=F}
vbl <- HRS_ds_hrs_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation hrs w11, echo=F}
```

```{r importOPAL hrs w11, echo=F}




```


## AHEAD


### Wave 2

Not found.


### Wave 3 

Not found.


### Wave 4

Not found.



### Wave 5

Not found.


### Wave 6

Not found.




### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-AHEAD-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7','HRS.HRS-AHEAD-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_ahead_w7 <- opal.execute(o,'HRS_ahead_w7')
```

```{r local ahead w7, echo=F}
vbl <- HRS_ahead_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7$id)
HRS_ds_ahead_w7$n_vig_pa <- car::recode(HRS_ahead_w7$R7VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w7, echo=F}
vbl <- HRS_ds_ahead_w7$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w7, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ahead w7, echo=F}
```

```{r importOPAL ahead w7, echo=F}




```




### Wave 7

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-AHEAD-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8','HRS.HRS-AHEAD-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_ahead_w8 <- opal.execute(o,'HRS_ahead_w8')
```

```{r local ahead w8, echo=F}
vbl <- HRS_ahead_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8$id)
HRS_ds_ahead_w8$n_vig_pa <- car::recode(HRS_ahead_w8$R8VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w8, echo=F}
vbl <- HRS_ds_ahead_w8$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w8, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ahead w8, echo=F}
```

```{r importOPAL ahead w8, echo=F}




```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-AHEAD-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9','HRS.HRS-AHEAD-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_ahead_w9 <- opal.execute(o,'HRS_ahead_w9')
```

```{r local ahead w9, echo=F}
vbl <- HRS_ahead_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9$id)
HRS_ds_ahead_w9$n_vig_pa <- car::recode(HRS_ahead_w9$R9VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w9, echo=F}
vbl <- HRS_ds_ahead_w9$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w9, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ahead w9, echo=F}
```

```{r importOPAL ahead w9, echo=F}




```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-AHEAD-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10','HRS.HRS-AHEAD-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_ahead_w10 <- opal.execute(o,'HRS_ahead_w10')
```

```{r local ahead w10, echo=F}
vbl <- HRS_ahead_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10$id)
HRS_ds_ahead_w10$n_vig_pa <- car::recode(HRS_ahead_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w10, echo=F}
vbl <- HRS_ds_ahead_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ahead w10, echo=F}
```

```{r importOPAL ahead w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-AHEAD-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ahead w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11','HRS.HRS-AHEAD-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_ahead_w11 <- opal.execute(o,'HRS_ahead_w11')
```

```{r local ahead w11, echo=F}
vbl <- HRS_ahead_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11$id)
HRS_ds_ahead_w11$n_vig_pa <- car::recode(HRS_ahead_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w11, echo=F}
vbl <- HRS_ds_ahead_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ahead w11, echo=F}
```

```{r importOPAL ahead w11, echo=F}




```




## CODA

### Wave 4

Not found.


### Wave 5

Not found.


### Wave 6

Not found.



### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-CODA-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7','HRS.HRS-CODA-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_coda_w7 <- opal.execute(o,'HRS_coda_w7')
```

```{r local coda w7, echo=F}
vbl <- HRS_coda_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7$id)
HRS_ds_coda_w7$n_vig_pa <- car::recode(HRS_coda_w7$R7VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w7, echo=F}
vbl <- HRS_ds_coda_w7$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w7, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation coda w7, echo=F}
```

```{r importOPAL coda w7, echo=F}




```




### Wave 7

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-CODA-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8','HRS.HRS-CODA-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_coda_w8 <- opal.execute(o,'HRS_coda_w8')
```

```{r local coda w8, echo=F}
vbl <- HRS_coda_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8$id)
HRS_ds_coda_w8$n_vig_pa <- car::recode(HRS_coda_w8$R8VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w8, echo=F}
vbl <- HRS_ds_coda_w8$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w8, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation coda w8, echo=F}
```

```{r importOPAL coda w8, echo=F}




```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-CODA-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9','HRS.HRS-CODA-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_coda_w9 <- opal.execute(o,'HRS_coda_w9')
```

```{r local coda w9, echo=F}
vbl <- HRS_coda_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9$id)
HRS_ds_coda_w9$n_vig_pa <- car::recode(HRS_coda_w9$R9VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w9, echo=F}
vbl <- HRS_ds_coda_w9$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w9, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation coda w9, echo=F}
```

```{r importOPAL coda w9, echo=F}




```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-CODA-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10','HRS.HRS-CODA-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_coda_w10 <- opal.execute(o,'HRS_coda_w10')
```

```{r local coda w10, echo=F}
vbl <- HRS_coda_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10$id)
HRS_ds_coda_w10$n_vig_pa <- car::recode(HRS_coda_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w10, echo=F}
vbl <- HRS_ds_coda_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation coda w10, echo=F}
```

```{r importOPAL coda w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-CODA-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign coda w11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11','HRS.HRS-CODA-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_coda_w11 <- opal.execute(o,'HRS_coda_w11')
```

```{r local coda w11, echo=F}
vbl <- HRS_coda_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11$id)
HRS_ds_coda_w11$n_vig_pa <- car::recode(HRS_coda_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript coda w11, echo=F}
vbl <- HRS_ds_coda_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation coda w11, echo=F}
```

```{r importOPAL coda w11, echo=F}




```





## WB

### Wave 4

Not found.


### Wave 5

Not found.


### Wave 6

Not found.



### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-WB-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7','HRS.HRS-WB-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_wb_w7 <- opal.execute(o,'HRS_wb_w7')
```

```{r local wb w7, echo=F}
vbl <- HRS_wb_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7$id)
HRS_ds_wb_w7$n_vig_pa <- car::recode(HRS_wb_w7$R7VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w7, echo=F}
vbl <- HRS_ds_wb_w7$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w7, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation wb w7, echo=F}
```

```{r importOPAL wb w7, echo=F}




```




### Wave 7

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-WB-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8','HRS.HRS-WB-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_wb_w8 <- opal.execute(o,'HRS_wb_w8')
```

```{r local wb w8, echo=F}
vbl <- HRS_wb_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8$id)
HRS_ds_wb_w8$n_vig_pa <- car::recode(HRS_wb_w8$R8VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w8, echo=F}
vbl <- HRS_ds_wb_w8$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w8, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation wb w8, echo=F}
```

```{r importOPAL wb w8, echo=F}




```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-WB-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9','HRS.HRS-WB-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_wb_w9 <- opal.execute(o,'HRS_wb_w9')
```

```{r local wb w9, echo=F}
vbl <- HRS_wb_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9$id)
HRS_ds_wb_w9$n_vig_pa <- car::recode(HRS_wb_w9$R9VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w9, echo=F}
vbl <- HRS_ds_wb_w9$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w9, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation wb w9, echo=F}
```

```{r importOPAL wb w9, echo=F}




```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-WB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10','HRS.HRS-WB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_wb_w10 <- opal.execute(o,'HRS_wb_w10')
```

```{r local wb w10, echo=F}
vbl <- HRS_wb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10$id)
HRS_ds_wb_w10$n_vig_pa <- car::recode(HRS_wb_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w10, echo=F}
vbl <- HRS_ds_wb_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation wb w10, echo=F}
```

```{r importOPAL wb w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-WB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign wb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11','HRS.HRS-WB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_wb_w11 <- opal.execute(o,'HRS_wb_w11')
```

```{r local wb w11, echo=F}
vbl <- HRS_wb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11$id)
HRS_ds_wb_w11$n_vig_pa <- car::recode(HRS_wb_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript wb w11, echo=F}
vbl <- HRS_ds_wb_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation wb w11, echo=F}
```

```{r importOPAL wb w11, echo=F}




```




## EBB



### Wave 7

#### Study-specific variable description

| **Name** | `R7VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-EBB-w7` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7','HRS.HRS-EBB-w7', variables=list('R7VGACTX'), missings = TRUE)
HRS_ebb_w7 <- opal.execute(o,'HRS_ebb_w7')
```

```{r local ebb w7, echo=F}
vbl <- HRS_ebb_w7$R7VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7, aes(x=factor(R7VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7$id)
HRS_ds_ebb_w7$n_vig_pa <- car::recode(HRS_ebb_w7$R7VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w7, echo=F}
vbl <- HRS_ds_ebb_w7$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w7, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ebb w7, echo=F}
```

```{r importOPAL ebb w7, echo=F}




```




### Wave 7

#### Study-specific variable description

| **Name** | `R8VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-EBB-w8` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8','HRS.HRS-EBB-w8', variables=list('R8VGACTX'), missings = TRUE)
HRS_ebb_w8 <- opal.execute(o,'HRS_ebb_w8')
```

```{r local ebb w8, echo=F}
vbl <- HRS_ebb_w8$R8VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8, aes(x=factor(R8VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8$id)
HRS_ds_ebb_w8$n_vig_pa <- car::recode(HRS_ebb_w8$R8VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w8, echo=F}
vbl <- HRS_ds_ebb_w8$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w8, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ebb w8, echo=F}
```

```{r importOPAL ebb w8, echo=F}




```




### Wave 9

#### Study-specific variable description

| **Name** | `R9VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-EBB-w9` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9','HRS.HRS-EBB-w9', variables=list('R9VGACTX'), missings = TRUE)
HRS_ebb_w9 <- opal.execute(o,'HRS_ebb_w9')
```

```{r local ebb w9, echo=F}
vbl <- HRS_ebb_w9$R9VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9, aes(x=factor(R9VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9$id)
HRS_ds_ebb_w9$n_vig_pa <- car::recode(HRS_ebb_w9$R9VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w9, echo=F}
vbl <- HRS_ds_ebb_w9$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w9, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ebb w9, echo=F}
```

```{r importOPAL ebb w9, echo=F}




```




### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-EBB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10','HRS.HRS-EBB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_ebb_w10 <- opal.execute(o,'HRS_ebb_w10')
```

```{r local ebb w10, echo=F}
vbl <- HRS_ebb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10$id)
HRS_ds_ebb_w10$n_vig_pa <- car::recode(HRS_ebb_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w10, echo=F}
vbl <- HRS_ds_ebb_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ebb w10, echo=F}
```

```{r importOPAL ebb w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-EBB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign ebb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11','HRS.HRS-EBB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_ebb_w11 <- opal.execute(o,'HRS_ebb_w11')
```

```{r local ebb w11, echo=F}
vbl <- HRS_ebb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11$id)
HRS_ds_ebb_w11$n_vig_pa <- car::recode(HRS_ebb_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w11, echo=F}
vbl <- HRS_ds_ebb_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation ebb w11, echo=F}
```

```{r importOPAL ebb w11, echo=F}




```




## MBB


### Wave 10

#### Study-specific variable description

| **Name** | `R10VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-MBB-w10` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign mbb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10','HRS.HRS-MBB-w10', variables=list('R10VGACTX'), missings = TRUE)
HRS_mbb_w10 <- opal.execute(o,'HRS_mbb_w10')
```

```{r local mbb w10, echo=F}
vbl <- HRS_mbb_w10$R10VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10, aes(x=factor(R10VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10$id)
HRS_ds_mbb_w10$n_vig_pa <- car::recode(HRS_mbb_w10$R10VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w10, echo=F}
vbl <- HRS_ds_mbb_w10$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w10, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation mbb w10, echo=F}
```

```{r importOPAL mbb w10, echo=F}




```




### Wave 11

#### Study-specific variable description

| **Name** | `R11VGACTX` |
|-|-|
| **Label** | `Freq vigorous phys activities` |
| **Table name** | `HRS-MBB-w11` |
| **Categories:**| `1 = every day` <br/> `2 = More than 1 per week` <br/> `3 = 1 per week` <br/> `4 = 1 to 3 per month` <br/> `5 = Never` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign mbb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11','HRS.HRS-MBB-w11', variables=list('R11VGACTX'), missings = TRUE)
HRS_mbb_w11 <- opal.execute(o,'HRS_mbb_w11')
```

```{r local mbb w11, echo=F}
vbl <- HRS_mbb_w11$R11VGACTX
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11, aes(x=factor(R11VGACTX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 14`
* `2 into 7`
* `3 into 2`
* `4 into 1`
* `5 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11$id)
HRS_ds_mbb_w11$n_vig_pa <- car::recode(HRS_mbb_w11$R11VGACTX, "1 = 14;2 = 7;3 = 2;4 = 1;5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w11, echo=F}
vbl <- HRS_ds_mbb_w11$n_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption= ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w11, aes(n_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")  
```

#### Validation
```{r crosstabulation mbb w11, echo=F}
```

```{r importOPAL mbb w11, echo=F}




```










## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}








# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




```









# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
