---
title: "Arterial hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ah`
* Variable label: `Arterial hypertension`
* Variable description: `Arterial hypertension. Means of all diastolic blood pressure measures.`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no hypertension
1        | hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Arterial hypertension"
ds_label_all <- "Arterial hypertension. Means of all diastolic blood pressure measures."
```

# Data process

## India

### Wave 1 

#### Study-specific variable description

* Name: `ht002`
* Label: `health professional told you that you have hbp or hypertension`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Description:

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_ah','LASI.LASI-Pilot_all',
                         variables=list('ht002'), missings = TRUE)
LASI_ah <- opal.execute(o,'LASI_ah')
```

```{r local1, echo=FALSE}
vari <- LASI_ah$ht002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_ah, aes(x=factor(ht002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `2 "no" into 0`
* `keep "yes" into 1`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_ah$id)
LASI_ds_w1$ah <- car::recode(LASI_ah$ht002, "2=0; NA=999")
LASI_ds_w1$ah <- labelled(LASI_ds_w1$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- LASI_ds_w1$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(LASI_ds_w1$ah, useNA = 'ifany')
BeforeH <- table(LASI_ah$ht002, useNA = 'ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')

#LASI_m_ds_w1 <- LASI_ds_w1
#LASI_m_ds_w1$sex <- car::recode(LASI_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')

label(LASI_ds_w1) <- ds_label_all
ah <- LASI_ds_w1
save(ah, file = "../RData/w1/ah.RData")
```

# Quality estimation

The variable chosen (ht002) to harmonized arterial hypertension as a physical 
measure doesn't fit in the definition of the variable, but it was decided to take 
it is better than nothing.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

