---
title: "Frequency of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_vig_paDS.R')
```



# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `ht221` |
|-|-|
| **Label** | `how many days of vigorous activity for at least 10 minutes` |
| **Table name** | `LASI-Pilot_all` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('ht221'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local w1, echo=F}
vbl <- LASI_w1$ht221
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(LASI_w1)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(LASI_w1, aes(ht221)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `>5 into 4`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$f_vig_pa <- car::recode(LASI_w1$ht221, "3 = 2;4 = 3;5 = 3;6 = 4;7 = 4;8 = 4;14 = 4;16 = 4;20 = 4;21 = 4;42 = 4;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- LASI_ds_w1$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$f_vig_pa)
X<-table(LASI_w1$ht221)
BeforeH <- c(X[1:2],sum(X[3:4]),sum(X[5:6]),sum(X[7:13]),sum(is.na(LASI_w1$ht221)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","2,3->2","4,5->3",">5->4","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=F}
f_vig_pa <- LASI_ds_w1 
save(f_vig_pa, file = "../RData/w1/f_vig_pa.RData")
rm(f_vig_pa)
```



# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
