---
title: "Current smoker"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/current_smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/current_smokingDS.R')
```



# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `ht206s1` | `ht206s2` |`ht206s3` |
|-|-|-|-|
| **Label** | `currently smoke or quit` | `currently smoke or quit` | `currently smoke or quit` |
| **Table name** | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` |
| **Categories:**| `1 = yes, i chew or sniff tobacco products` | `2 = yes, i smoke tobacco products` | `3 = no, i quit` |
| **Missings:**| `NA` | `NA` | `NA` |
| **Description** |  | | |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('ht206s1','ht206s2','ht206s3'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local w1, echo=F}
vbl <- LASI_w1$ht206s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht206s2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht206s3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `1,2 into 1` 
* `3 into 0`
* `3 & ( 1 | 2 ) into 991`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$current_smoking <- rep(999,length(LASI_ds_w1$id))
LASI_ds_w1$current_smoking[(LASI_w1$ht206s1==1)|(LASI_w1$ht206s2==2)] <- 1
LASI_ds_w1$current_smoking[(LASI_w1$ht206s3==3)] <- 0
LASI_ds_w1$current_smoking[(LASI_w1$ht206s3==3)&((LASI_w1$ht206s1==1)|(LASI_w1$ht206s2==2))] <- 991
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- LASI_ds_w1$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$current_smoking)
X<-c(sum(na.omit(LASI_w1$ht206s3==3))-sum(na.omit(LASI_w1$ht206s3==3&(LASI_w1$ht206s1==1|LASI_w1$ht206s2==2))),sum(na.omit(LASI_w1$ht206s1==1),na.omit(LASI_w1$ht206s2==2))-sum(na.omit(LASI_w1$ht206s1==1&LASI_w1$ht206s2==2))-sum(na.omit(LASI_w1$ht206s3==3&(LASI_w1$ht206s1==1|LASI_w1$ht206s2==2))),sum(na.omit(LASI_w1$ht206s3==3&(LASI_w1$ht206s1==1|LASI_w1$ht206s2==2))))
BeforeH <- c(X[1:3],length(LASI_w1$ht206s1)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->0","1,2->1","3&(1|2)->991","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=F}
label(LASI_ds_w1$current_smoking) <- ds_label
current_smoking <- LASI_ds_w1 
save(current_smoking, file = paste0(datafolder,"w1/current_smoking.RData"))
rm(current_smoking)
```





# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
