---
title: "Smoking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/smokingDS.R')
```




# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `ht205` | `ht206s1` | `ht206s2` |`ht206s3` |
|-|-|-|-|-|
| **Label** | `Have you ever smoked tobacco [cigarette, bidi, cigar, hookah] or used smokeless tobacco [such as chewing tobacco, gutka, pan masala, etc.]?` | `currently smoke or quit` | `currently smoke or quit` | `currently smoke or quit` |
| **Table name** | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` | `LASI-Pilot_all` |
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes, i chew or sniff tobacco products` | `2 = yes, i smoke tobacco products` | `3 = no, i quit` |
| **Missings:**| `NA` | `NA` | `NA` | `NA` |
| **Description** |  | | | |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('ht205','ht206s1','ht206s2','ht206s3'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local w1, echo=F}
vbl <- LASI_w1$ht205
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "ht205")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht205))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht206s1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "ht206s1")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht206s2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "ht206s2")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht206s3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "ht206s3")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht206s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `smoking` from the study-specific variable it has to be recoded as follows:

* `ht205=2 into 0` 
* `ht205=1&ht206s3=3 into 1` 
* `ht205=1&(ht206s1=1|ht206s2=2) into 2`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$smoking <- rep(999,length(LASI_ds_w1$id))
LASI_ds_w1$smoking[which(LASI_w1$ht205==2)] <- 0
LASI_ds_w1$smoking[which(LASI_w1$ht205==1&LASI_w1$ht206s3==3)] <- 1
LASI_ds_w1$smoking[which(LASI_w1$ht205==1&(LASI_w1$ht206s1==1|LASI_w1$ht206s2==2))] <- 2
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- LASI_ds_w1$smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$smoking)
X<-c(sum(na.omit(LASI_w1$ht205==2)),sum(na.omit(LASI_w1$ht205==1&LASI_w1$ht206s3==3&(LASI_w1$ht206s1!=1|is.na(LASI_w1$ht206s1)==TRUE)&(LASI_w1$ht206s2!=2|is.na(LASI_w1$ht206s2)==TRUE))),sum(na.omit(LASI_w1$ht205==1&(LASI_w1$ht206s1==1|LASI_w1$ht206s2==2))))
BeforeH <- c(X,length(LASI_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("ht205=2->0","ht205=1&ht206s3=3->1","ht205=1&(ht206s1=1|ht206s2=2)->2","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=F}
label(LASI_ds_w1$smoking) <- ds_label
smoking <- LASI_ds_w1 
save(smoking, file = paste0(datafolder,"w1/smoking.RData"))
rm(smoking)
```





# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
