---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `ht208_number_cigarettes` |
|-|-|
| **Label** | `number cigarettes` |
| **Table name** | `LASI-Pilot_all` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('ht208_number_cigarettes'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local w1, echo=F}
vbl <- LASI_w1$ht208_number_cigarettes
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(LASI_w1, aes(ht208_number_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(-1,27)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `ht208_number_cigarettes*7`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$n_cigarettes <- car::recode(LASI_w1$ht208_number_cigarettes*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- LASI_ds_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(LASI_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,185) 
```

#### Validation
```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=F}
label(LASI_ds_w1$n_cigarettes) <- ds_label
n_cigarettes <- LASI_ds_w1 
save(n_cigarettes, file = paste0(datafolder,"w1/n_cigarettes.RData"))
rm(n_cigarettes)
```




# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
