---
title: "Day of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `dintw`
* Variable label: `day of interview`
* Variable description: `day of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## HRS

###  Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R1IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_dinter','HRS.HRS-HRS-w1_date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs1, echo=F}
HRS_hrs_w1_dinter <- opal.execute(o,'HRS_hrs_w1_dinter')
HRS_hrs_w1_dinter$dinter <- as.numeric(format(HRS_hrs_w1_dinter$ dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w1_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w1_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_dinter$id)
HRS_ds_hrs_w1$dintw <- car::recode(HRS_hrs_w1_dinter$dinter, "NA=999")
HRS_ds_hrs_w1$dintw <- labelled(HRS_ds_hrs_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
Continuous_summary(var = HRS_ds_hrs_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w1, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs1, echo=F}
BeforeH <- table(HRS_hrs_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs1, echo=F}

dintw <- HRS_ds_hrs_w1
save(dintw, file = "../RData/hrs_w1/dintw.RData")
rm(dintw)
```








###  Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R2IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w2_dinter','HRS.HRS-HRS-w2-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_dinter <- opal.execute(o,'HRS_hrs_w2_dinter')
HRS_hrs_w2_dinter$dinter <- as.numeric(format(HRS_hrs_w2_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w2_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w2_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_dinter$id)
HRS_ds_hrs_w2$dintw <- car::recode(HRS_hrs_w2_dinter$dinter, "NA=999")
HRS_ds_hrs_w2$dintw <- labelled(HRS_ds_hrs_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
Continuous_summary(var = HRS_ds_hrs_w2$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w2, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs2, echo=F}
BeforeH <- table(HRS_hrs_w2_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs2, echo=F}

dintw <- HRS_ds_hrs_w2
save(dintw, file = "../RData/hrs_w2/dintw.RData")
rm(dintw)
```






###  Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R3IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w3_dinter','HRS.HRS-HRS-w3-date_of_interview',variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_dinter <- opal.execute(o,'HRS_hrs_w3_dinter')
HRS_hrs_w3_dinter$dinter <- as.numeric(format(HRS_hrs_w3_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w3_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w3_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_dinter$id)
HRS_ds_hrs_w3$dintw <- car::recode(HRS_hrs_w3_dinter$dinter, "NA=999")
HRS_ds_hrs_w3$dintw <- labelled(HRS_ds_hrs_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
Continuous_summary(var = HRS_ds_hrs_w3$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w3, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs3, echo=F}
BeforeH <- table(HRS_hrs_w3_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs3, echo=F}

dintw <- HRS_ds_hrs_w3
save(dintw, file = "../RData/hrs_w3/dintw.RData")
rm(dintw)
```








###  Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R1IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_dinter','HRS.HRS-HRS-w4-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_dinter <- opal.execute(o,'HRS_hrs_w4_dinter')
HRS_hrs_w4_dinter$dinter <- as.numeric(format(HRS_hrs_w4_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w4_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w4_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_dinter$id)
HRS_ds_hrs_w4$dintw <- car::recode(HRS_hrs_w4_dinter$dinter, "NA=999")
HRS_ds_hrs_w4$dintw <- labelled(HRS_ds_hrs_w4$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
Continuous_summary(var = HRS_ds_hrs_w4$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w4, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs4, echo=F}
BeforeH <- table(HRS_hrs_w4_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w4$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs4, echo=F}

dintw <- HRS_ds_hrs_w4
save(dintw, file = "../RData/hrs_w4/dintw.RData")
rm(dintw)
```






###  Wave 5

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_dinter','HRS.HRS-HRS-w5-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_dinter <- opal.execute(o,'HRS_hrs_w5_dinter')
HRS_hrs_w5_dinter$dinter <- as.numeric(format(HRS_hrs_w5_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w5_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w5_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_dinter$id)
HRS_ds_hrs_w5$dintw <- car::recode(HRS_hrs_w5_dinter$dinter, "NA=999")
HRS_ds_hrs_w5$dintw <- labelled(HRS_ds_hrs_w5$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
Continuous_summary(var = HRS_ds_hrs_w5$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w5, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs5, echo=F}
BeforeH <- table(HRS_hrs_w5_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w5$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs5, echo=F}

dintw <- HRS_ds_hrs_w5
save(dintw, file = "../RData/hrs_w5/dintw.RData")
rm(dintw)
```






###  Wave 6

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_dinter','HRS.HRS-HRS-w6-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_dinter <- opal.execute(o,'HRS_hrs_w6_dinter')
HRS_hrs_w6_dinter$dinter <- as.numeric(format(HRS_hrs_w6_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w6_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w6_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_dinter$id)
HRS_ds_hrs_w6$dintw <- car::recode(HRS_hrs_w6_dinter$dinter, "NA=999")
HRS_ds_hrs_w6$dintw <- labelled(HRS_ds_hrs_w6$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
Continuous_summary(var = HRS_ds_hrs_w6$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w6, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs6, echo=F}
BeforeH <- table(HRS_hrs_w6_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w6$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs6, echo=F}

dintw <- HRS_ds_hrs_w6
save(dintw, file = "../RData/hrs_w6/dintw.RData")
rm(dintw)
```



###  Wave 7

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `RABYEAR`
* Label: `R birth year`
* Type of variable: `countinous`


```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_dinter','HRS.HRS-HRS-w7-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_dinter <- opal.execute(o,'HRS_hrs_w7_dinter')
HRS_hrs_w7_dinter$dinter <- as.numeric(format(HRS_hrs_w7_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w7_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w7_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_dinter$id)
HRS_ds_hrs_w7$dintw <- car::recode(HRS_hrs_w7_dinter$dinter, "NA=999")
HRS_ds_hrs_w7$dintw <- labelled(HRS_ds_hrs_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
Continuous_summary(var = HRS_ds_hrs_w7$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w7, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation_hrs7, echo=F}
BeforeH <- table(HRS_hrs_w7_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

### Quality estimation



```{r importOPAL_hrs7, echo=F}

dintw <- HRS_ds_hrs_w7
save(dintw, file = "../RData/hrs_w7/dintw.RData")
rm(dintw)
```








###  Wave 8

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_dinter','HRS.HRS-HRS-w8-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_dinter <- opal.execute(o,'HRS_hrs_w8_dinter')
HRS_hrs_w8_dinter$dinter <- as.numeric(format(HRS_hrs_w8_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w8_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w8_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_dinter$id)
HRS_ds_hrs_w8$dintw <- car::recode(HRS_hrs_w8_dinter$dinter, "NA=999")
HRS_ds_hrs_w8$dintw <- labelled(HRS_ds_hrs_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
Continuous_summary(var = HRS_ds_hrs_w8$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w8, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation_hrs8, echo=F}
BeforeH <- table(HRS_hrs_w8_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

### Quality estimation



```{r importOPAL_hrs8, echo=F}

dintw <- HRS_ds_hrs_w8
save(dintw, file = "../RData/hrs_w8/dintw.RData")
rm(dintw)
```








###  Wave 9

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R1IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_dinter','HRS.HRS-HRS-w9-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_dinter <- opal.execute(o,'HRS_hrs_w9_dinter')
HRS_hrs_w9_dinter$dinter <- as.numeric(format(HRS_hrs_w9_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w9_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w9_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_dinter$id)
HRS_ds_hrs_w9$dintw <- car::recode(HRS_hrs_w9_dinter$dinter, "NA=999")
HRS_ds_hrs_w9$dintw <- labelled(HRS_ds_hrs_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
Continuous_summary(var = HRS_ds_hrs_w9$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w9, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs9, echo=F}
BeforeH <- table(HRS_hrs_w9_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs9, echo=F}

dintw <- HRS_ds_hrs_w9
save(dintw, file = "../RData/hrs_w9/dintw.RData")
rm(dintw)
```







###  Wave 10

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_dinter','HRS.HRS-HRS-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_dinter <- opal.execute(o,'HRS_hrs_w10_dinter')
HRS_hrs_w10_dinter$dinter <- as.numeric(format(HRS_hrs_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_dinter$id)
HRS_ds_hrs_w10$dintw <- car::recode(HRS_hrs_w10_dinter$dinter, "NA=999")
HRS_ds_hrs_w10$dintw <- labelled(HRS_ds_hrs_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
Continuous_summary(var = HRS_ds_hrs_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs10, echo=F}
BeforeH <- table(HRS_hrs_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs10, echo=F}
dintw <- HRS_ds_hrs_w10
save(dintw, file = "../RData/hrs_w10/dintw.RData")
rm(dintw)

```







###  Wave 11

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_dinter','HRS.HRS-HRS-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_hrs11, echo=F}
HRS_hrs_w11_dinter <- opal.execute(o,'HRS_hrs_w11_dinter')
HRS_hrs_w11_dinter$dinter <- as.numeric(format(HRS_hrs_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_hrs_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_hrs_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_dinter$id)
HRS_ds_hrs_w11$dintw <- car::recode(HRS_hrs_w11_dinter$dinter, "NA=999")
HRS_ds_hrs_w11$dintw <- labelled(HRS_ds_hrs_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
Continuous_summary(var = HRS_ds_hrs_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs11, echo=F}
BeforeH <- table(HRS_hrs_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs11, echo=F}

dintw <- HRS_ds_hrs_w11
save(dintw, file = "../RData/hrs_w11/dintw.RData")
rm(dintw)
```




## AHEAD

###  Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R2IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_dinter','HRS.HRS-AHEAD-w2-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_dinter <- opal.execute(o,'HRS_ahead_w2_dinter')
HRS_ahead_w2_dinter$dinter <- as.numeric(format(HRS_ahead_w2_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w2_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w2_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_dinter$id)
HRS_ds_ahead_w2$dintw <- car::recode(HRS_ahead_w2_dinter$dinter, "NA=999")
HRS_ds_ahead_w2$dintw <- labelled(HRS_ds_ahead_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
Continuous_summary(var = HRS_ds_ahead_w2$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w2, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead2, echo=F}
BeforeH <- table(HRS_ahead_w2_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead2, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w2', HRS_ds_ahead_w2)
#opal.symbol_import(o,'HRS_ds_ahead_w2', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w2
save(dintw, file = "../RData/ahead_w2/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
HRS_m_ds_ahead_w2$dintw <- car::recode(HRS_m_ds_ahead_w2$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w2', HRS_m_ds_ahead_w2)
#opal.symbol_import(o,'HRS_m_ds_ahead_w2', project='_Athlos_Harm_Dataset')
```





###  Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R3IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_dinter','HRS.HRS-AHEAD-w3-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_dinter <- opal.execute(o,'HRS_ahead_w3_dinter')
HRS_ahead_w3_dinter$dinter <- as.numeric(format(HRS_ahead_w3_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w3_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w3_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_dinter$id)
HRS_ds_ahead_w3$dintw <- car::recode(HRS_ahead_w3_dinter$dinter, "NA=999")
HRS_ds_ahead_w3$dintw <- labelled(HRS_ds_ahead_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
Continuous_summary(var = HRS_ds_ahead_w3$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w3, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead3, echo=F}
BeforeH <- table(HRS_ahead_w3_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead3, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w3', HRS_ds_ahead_w3)
#opal.symbol_import(o,'HRS_ds_ahead_w3', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w3
save(dintw, file = "../RData/ahead_w3/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
HRS_m_ds_ahead_w3$dintw <- car::recode(HRS_m_ds_ahead_w3$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w3', HRS_m_ds_ahead_w3)
#opal.symbol_import(o,'HRS_m_ds_ahead_w3', project='_Athlos_Harm_Dataset')
```








###  Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_dinter','HRS.HRS-AHEAD-w4-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_dinter <- opal.execute(o,'HRS_ahead_w4_dinter')
HRS_ahead_w4_dinter$dinter <- as.numeric(format(HRS_ahead_w4_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w4_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w4_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_dinter$id)
HRS_ds_ahead_w4$dintw <- car::recode(HRS_ahead_w4_dinter$dinter, "NA=999")
HRS_ds_ahead_w4$dintw <- labelled(HRS_ds_ahead_w4$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
Continuous_summary(var = HRS_ds_ahead_w4$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w4, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead4, echo=F}
BeforeH <- table(HRS_ahead_w4_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w4$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead4, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w4', HRS_ds_ahead_w4)
#opal.symbol_import(o,'HRS_ds_ahead_w4', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w4
save(dintw, file = "../RData/ahead_w4/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
HRS_m_ds_ahead_w4$dintw <- car::recode(HRS_m_ds_ahead_w4$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w4', HRS_m_ds_ahead_w4)
#opal.symbol_import(o,'HRS_m_ds_ahead_w4', project='_Athlos_Harm_Dataset')
```







###  Wave 5 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_dinter','HRS.HRS-AHEAD-w5-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_dinter <- opal.execute(o,'HRS_ahead_w5_dinter')
HRS_ahead_w5_dinter$dinter <- as.numeric(format(HRS_ahead_w5_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w5_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w5_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_dinter$id)
HRS_ds_ahead_w5$dintw <- car::recode(HRS_ahead_w5_dinter$dinter, "NA=999")
HRS_ds_ahead_w5$dintw <- labelled(HRS_ds_ahead_w5$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
Continuous_summary(var = HRS_ds_ahead_w5$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w5, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation_ahead5, echo=F}
BeforeH <- table(HRS_ahead_w5_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w5$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

### Quality estimation



```{r importOPAL_ahead5, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w5', HRS_ds_ahead_w5)
#opal.symbol_import(o,'HRS_ds_ahead_w5', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w5
save(dintw, file = "../RData/ahead_w5/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
HRS_m_ds_ahead_w5$dintw <- car::recode(HRS_m_ds_ahead_w5$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w5', HRS_m_ds_ahead_w5)
#opal.symbol_import(o,'HRS_m_ds_ahead_w5', project='_Athlos_Harm_Dataset')
```








###  Wave 6 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_dinter','HRS.HRS-AHEAD-w6-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_dinter <- opal.execute(o,'HRS_ahead_w6_dinter')
HRS_ahead_w6_dinter$dinter <- as.numeric(format(HRS_ahead_w6_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w6_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w6_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_dinter$id)
HRS_ds_ahead_w6$dintw <- car::recode(HRS_ahead_w6_dinter$dinter, "NA=999")
HRS_ds_ahead_w6$dintw <- labelled(HRS_ds_ahead_w6$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
Continuous_summary(var = HRS_ds_ahead_w6$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w6, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead6, echo=F}
BeforeH <- table(HRS_ahead_w6_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w6$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead6, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w6', HRS_ds_ahead_w6)
#opal.symbol_import(o,'HRS_ds_ahead_w6', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w6
save(dintw, file = "../RData/ahead_w6/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
HRS_m_ds_ahead_w6$dintw <- car::recode(HRS_m_ds_ahead_w6$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w6', HRS_m_ds_ahead_w6)
#opal.symbol_import(o,'HRS_m_ds_ahead_w6', project='_Athlos_Harm_Dataset')
```







###  Wave 7 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_dinter','HRS.HRS-AHEAD-w7-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_dinter <- opal.execute(o,'HRS_ahead_w7_dinter')
HRS_ahead_w7_dinter$dinter <- as.numeric(format(HRS_ahead_w7_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w7_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w7_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_dinter$id)
HRS_ds_ahead_w7$dintw <- car::recode(HRS_ahead_w7_dinter$dinter, "NA=999")
HRS_ds_ahead_w7$dintw <- labelled(HRS_ds_ahead_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
Continuous_summary(var = HRS_ds_ahead_w7$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w7, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead7, echo=F}
BeforeH <- table(HRS_ahead_w7_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead7, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w7', HRS_ds_ahead_w7)
#opal.symbol_import(o,'HRS_ds_ahead_w7', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w7
save(dintw, file = "../RData/ahead_w7/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
HRS_m_ds_ahead_w7$dintw <- car::recode(HRS_m_ds_ahead_w7$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w7', HRS_m_ds_ahead_w7)
#opal.symbol_import(o,'HRS_m_ds_ahead_w7', project='_Athlos_Harm_Dataset')
```








###  Wave 8 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`



```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_dinter','HRS.HRS-AHEAD-w8-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_dinter <- opal.execute(o,'HRS_ahead_w8_dinter')
HRS_ahead_w8_dinter$dinter <- as.numeric(format(HRS_ahead_w8_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w8_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w8_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_dinter$id)
HRS_ds_ahead_w8$dintw <- car::recode(HRS_ahead_w8_dinter$dinter, "NA=999")
HRS_ds_ahead_w8$dintw <- labelled(HRS_ds_ahead_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
Continuous_summary(var = HRS_ds_ahead_w8$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w8, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead8, echo=F}
BeforeH <- table(HRS_ahead_w8_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead8, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w8', HRS_ds_ahead_w8)
#opal.symbol_import(o,'HRS_ds_ahead_w8', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w8
save(dintw, file = "../RData/ahead_w8/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
HRS_m_ds_ahead_w8$dintw <- car::recode(HRS_m_ds_ahead_w8$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w8', HRS_m_ds_ahead_w8)
#opal.symbol_import(o,'HRS_m_ds_ahead_w8', project='_Athlos_Harm_Dataset')
```








###  Wave 9 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_dinter','HRS.HRS-AHEAD-w9-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_dinter <- opal.execute(o,'HRS_ahead_w9_dinter')
HRS_ahead_w9_dinter$dinter <- as.numeric(format(HRS_ahead_w9_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w9_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w9_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_dinter$id)
HRS_ds_ahead_w9$dintw <- car::recode(HRS_ahead_w9_dinter$dinter, "NA=999")
HRS_ds_ahead_w9$dintw <- labelled(HRS_ds_ahead_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
Continuous_summary(var = HRS_ds_ahead_w9$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w9, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead9, echo=F}
BeforeH <- table(HRS_ahead_w9_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead9, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w9', HRS_ds_ahead_w9)
#opal.symbol_import(o,'HRS_ds_ahead_w9', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w9
save(dintw, file = "../RData/ahead_w9/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
HRS_m_ds_ahead_w9$dintw <- car::recode(HRS_m_ds_ahead_w9$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w9', HRS_m_ds_ahead_w9)
#opal.symbol_import(o,'HRS_m_ds_ahead_w9', project='_Athlos_Harm_Dataset')
```







###  Wave 10 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_dinter','HRS.HRS-AHEAD-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_dinter <- opal.execute(o,'HRS_ahead_w10_dinter')
HRS_ahead_w10_dinter$dinter <- as.numeric(format(HRS_ahead_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_dinter$id)
HRS_ds_ahead_w10$dintw <- car::recode(HRS_ahead_w10_dinter$dinter, "NA=999")
HRS_ds_ahead_w10$dintw <- labelled(HRS_ds_ahead_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
Continuous_summary(var = HRS_ds_ahead_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead10, echo=F}
BeforeH <- table(HRS_ahead_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead10, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w10', HRS_ds_ahead_w10)
#opal.symbol_import(o,'HRS_ds_ahead_w10', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w10
save(dintw, file = "../RData/ahead_w10/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
HRS_m_ds_ahead_w10$dintw <- car::recode(HRS_m_ds_ahead_w10$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w10', HRS_m_ds_ahead_w10)
#opal.symbol_import(o,'HRS_m_ds_ahead_w10', project='_Athlos_Harm_Dataset')
```







###  Wave 11 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_dinter','HRS.HRS-AHEAD-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_dinter <- opal.execute(o,'HRS_ahead_w11_dinter')
HRS_ahead_w11_dinter$dinter <- as.numeric(format(HRS_ahead_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ahead_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_ahead_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_dinter$id)
HRS_ds_ahead_w11$dintw <- car::recode(HRS_ahead_w11_dinter$dinter, "NA=999")
HRS_ds_ahead_w11$dintw <- labelled(HRS_ds_ahead_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
Continuous_summary(var = HRS_ds_ahead_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead11, echo=F}
BeforeH <- table(HRS_ahead_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead11, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w11', HRS_ds_ahead_w11)
#opal.symbol_import(o,'HRS_ds_ahead_w11', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ahead_w11
save(dintw, file = "../RData/ahead_w11/dintw.RData")
rm(dintw)

HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
HRS_m_ds_ahead_w11$dintw <- car::recode(HRS_m_ds_ahead_w11$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w11', HRS_m_ds_ahead_w11)
#opal.symbol_import(o,'HRS_m_ds_ahead_w11', project='_Athlos_Harm_Dataset')
```



## CODA

###  Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_dinter','HRS.HRS-CODA-w4-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_dinter <- opal.execute(o,'HRS_coda_w4_dinter')
HRS_coda_w4_dinter$dinter <- as.numeric(format(HRS_coda_w4_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w4_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w4_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_dinter$id)
HRS_ds_coda_w4$dintw <- car::recode(HRS_coda_w4_dinter$dinter, "NA=999")
HRS_ds_coda_w4$dintw <- labelled(HRS_ds_coda_w4$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
Continuous_summary(var = HRS_ds_coda_w4$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w4, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda4, echo=F}
BeforeH <- table(HRS_coda_w4_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w4$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda4, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w4', HRS_ds_coda_w4)
#opal.symbol_import(o,'HRS_ds_coda_w4', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w4
save(dintw, file = "../RData/coda_w4/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
HRS_m_ds_coda_w4$dintw <- car::recode(HRS_m_ds_coda_w4$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w4', HRS_m_ds_coda_w4)
#opal.symbol_import(o,'HRS_m_ds_coda_w4', project='_Athlos_Harm_Dataset')
```








###  Wave 5 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_dinter','HRS.HRS-CODA-w5-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_dinter <- opal.execute(o,'HRS_coda_w5_dinter')
HRS_coda_w5_dinter$dinter <- as.numeric(format(HRS_coda_w5_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w5_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w5_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_dinter$id)
HRS_ds_coda_w5$dintw <- car::recode(HRS_coda_w5_dinter$dinter, "NA=999")
HRS_ds_coda_w5$dintw <- labelled(HRS_ds_coda_w5$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
Continuous_summary(var = HRS_ds_coda_w5$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w5, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda5, echo=F}
BeforeH <- table(HRS_coda_w5_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w5$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda5, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w5', HRS_ds_coda_w5)
#opal.symbol_import(o,'HRS_ds_coda_w5', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w5
save(dintw, file = "../RData/coda_w5/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
HRS_m_ds_coda_w5$dintw <- car::recode(HRS_m_ds_coda_w5$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w5', HRS_m_ds_coda_w5)
#opal.symbol_import(o,'HRS_m_ds_coda_w5', project='_Athlos_Harm_Dataset')
```










###  Wave 6 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_dinter','HRS.HRS-CODA-w6-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_dinter <- opal.execute(o,'HRS_coda_w6_dinter')
HRS_coda_w6_dinter$dinter <- as.numeric(format(HRS_coda_w6_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w6_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w6_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_dinter$id)
HRS_ds_coda_w6$dintw <- car::recode(HRS_coda_w6_dinter$dinter, "NA=999")
HRS_ds_coda_w6$dintw <- labelled(HRS_ds_coda_w6$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
Continuous_summary(var = HRS_ds_coda_w6$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w6, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda6, echo=F}
BeforeH <- table(HRS_coda_w6_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w6$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda6, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w6', HRS_ds_coda_w6)
#opal.symbol_import(o,'HRS_ds_coda_w6', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w6
save(dintw, file = "../RData/coda_w6/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
HRS_m_ds_coda_w6$dintw <- car::recode(HRS_m_ds_coda_w6$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w6', HRS_m_ds_coda_w6)
#opal.symbol_import(o,'HRS_m_ds_coda_w6', project='_Athlos_Harm_Dataset')
```







###  Wave 7 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_dinter','HRS.HRS-CODA-w7-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_dinter <- opal.execute(o,'HRS_coda_w7_dinter')
HRS_coda_w7_dinter$dinter <- as.numeric(format(HRS_coda_w7_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w7_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w7_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_dinter$id)
HRS_ds_coda_w7$dintw <- car::recode(HRS_coda_w7_dinter$dinter, "NA=999")
HRS_ds_coda_w7$dintw <- labelled(HRS_ds_coda_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
Continuous_summary(var = HRS_ds_coda_w7$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w7, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda7, echo=F}
BeforeH <- table(HRS_coda_w7_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda7, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w7', HRS_ds_coda_w7)
#opal.symbol_import(o,'HRS_ds_coda_w7', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w7
save(dintw, file = "../RData/coda_w7/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
HRS_m_ds_coda_w7$dintw <- car::recode(HRS_m_ds_coda_w7$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w7', HRS_m_ds_coda_w7)
#opal.symbol_import(o,'HRS_m_ds_coda_w7', project='_Athlos_Harm_Dataset')
```







###  Wave 8 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R1IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_dinter','HRS.HRS-CODA-w8-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_dinter <- opal.execute(o,'HRS_coda_w8_dinter')
HRS_coda_w8_dinter$dinter <- as.numeric(format(HRS_coda_w8_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w8_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w8_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_dinter$id)
HRS_ds_coda_w8$dintw <- car::recode(HRS_coda_w8_dinter$dinter, "NA=999")
HRS_ds_coda_w8$dintw <- labelled(HRS_ds_coda_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
Continuous_summary(var = HRS_ds_coda_w8$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w8, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda8, echo=F}
BeforeH <- table(HRS_coda_w8_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda8, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w8
save(dintw, file = "../RData/coda_w8/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
HRS_m_ds_coda_w8$dintw <- car::recode(HRS_m_ds_coda_w8$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w8', HRS_m_ds_coda_w8)
#opal.symbol_import(o,'HRS_m_ds_coda_w8', project='_Athlos_Harm_Dataset')
```







###  Wave 9 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_dinter','HRS.HRS-CODA-w9-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_dinter <- opal.execute(o,'HRS_coda_w9_dinter')
HRS_coda_w9_dinter$dinter <- as.numeric(format(HRS_coda_w9_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w9_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w9_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_dinter$id)
HRS_ds_coda_w9$dintw <- car::recode(HRS_coda_w9_dinter$dinter, "NA=999")
HRS_ds_coda_w9$dintw <- labelled(HRS_ds_coda_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
Continuous_summary(var = HRS_ds_coda_w9$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w9, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda9, echo=F}
BeforeH <- table(HRS_coda_w9_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda9, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w9
save(dintw, file = "../RData/coda_w9/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
HRS_m_ds_coda_w9$dintw <- car::recode(HRS_m_ds_coda_w9$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w9', HRS_m_ds_coda_w9)
#opal.symbol_import(o,'HRS_m_ds_coda_w9', project='_Athlos_Harm_Dataset')
```







###  Wave 10 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_dinter','HRS.HRS-CODA-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_dinter <- opal.execute(o,'HRS_coda_w10_dinter')
HRS_coda_w10_dinter$dinter <- as.numeric(format(HRS_coda_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_dinter$id)
HRS_ds_coda_w10$dintw <- car::recode(HRS_coda_w10_dinter$dinter, "NA=999")
HRS_ds_coda_w10$dintw <- labelled(HRS_ds_coda_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
Continuous_summary(var = HRS_ds_coda_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda10, echo=F}
BeforeH <- table(HRS_coda_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda10, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w10
save(dintw, file = "../RData/coda_w10/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
HRS_m_ds_coda_w10$dintw <- car::recode(HRS_m_ds_coda_w10$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w10', HRS_m_ds_coda_w10)
#opal.symbol_import(o,'HRS_m_ds_coda_w10', project='_Athlos_Harm_Dataset')
```







###  Wave 11 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_dinter','HRS.HRS-CODA-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_dinter <- opal.execute(o,'HRS_coda_w11_dinter')
HRS_coda_w11_dinter$dinter <- as.numeric(format(HRS_coda_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_coda_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_coda_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_dinter$id)
HRS_ds_coda_w11$dintw <- car::recode(HRS_coda_w11_dinter$dinter, "NA=999")
HRS_ds_coda_w11$dintw <- labelled(HRS_ds_coda_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
Continuous_summary(var = HRS_ds_coda_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda11, echo=F}
BeforeH <- table(HRS_coda_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda11, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_coda_w11
save(dintw, file = "../RData/coda_w11/dintw.RData")
rm(dintw)

HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
HRS_m_ds_coda_w11$dintw <- car::recode(HRS_m_ds_coda_w11$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w11', HRS_m_ds_coda_w11)
#opal.symbol_import(o,'HRS_m_ds_coda_w11', project='_Athlos_Harm_Dataset')
```






## WB

###  Wave 4  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_dinter','HRS.HRS-WB-w4-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_dinter <- opal.execute(o,'HRS_wb_w4_dinter')
HRS_wb_w4_dinter$dinter <- as.numeric(format(HRS_wb_w4_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w4_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w4_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_dinter$id)
HRS_ds_wb_w4$dintw <- car::recode(HRS_wb_w4_dinter$dinter, "NA=999")
HRS_ds_wb_w4$dintw <- labelled(HRS_ds_wb_w4$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
Continuous_summary(var = HRS_ds_wb_w4$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w4, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb4, echo=F}
BeforeH <- table(HRS_wb_w4_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w4$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


```{r importOPAL_wb4, echo=F}
dintw <- HRS_ds_wb_w4
save(dintw, file = "../RData/wb_w4/dintw.RData")
rm(dintw)
```









###  Wave 5  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_ybirth','HRS.HRS-WB-w5-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_ybirth <- opal.execute(o,'HRS_wb_w5_ybirth')
HRS_wb_w5_ybirth$dinter <- as.numeric(format(HRS_wb_w5_ybirth$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w5_ybirth$dinter, missing_values = NA)
ggplot(HRS_wb_w5_ybirth, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_ybirth$id)
HRS_ds_wb_w5$dintw <- car::recode(HRS_wb_w5_ybirth$dinter, "NA=999")
HRS_ds_wb_w5$dintw <- labelled(HRS_ds_wb_w5$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
Continuous_summary(var = HRS_ds_wb_w5$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w5, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb5, echo=F}
BeforeH <- table(HRS_wb_w5_ybirth$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w5$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb5, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w5
save(dintw, file = "../RData/wb_w5/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
HRS_m_ds_wb_w5$dintw <- car::recode(HRS_m_ds_wb_w5$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w5', HRS_m_ds_wb_w5)
#opal.symbol_import(o,'HRS_m_ds_wb_w5', project='_Athlos_Harm_Dataset')
```








###  Wave 6  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_dinter','HRS.HRS-WB-w6-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_dinter <- opal.execute(o,'HRS_wb_w6_dinter')
HRS_wb_w6_dinter$dinter <- as.numeric(format(HRS_wb_w6_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w6_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w6_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_dinter$id)
HRS_ds_wb_w6$dintw <- car::recode(HRS_wb_w6_dinter$dinter, "NA=999")
HRS_ds_wb_w6$dintw <- labelled(HRS_ds_wb_w6$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
Continuous_summary(var = HRS_ds_wb_w6$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w6, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb6, echo=F}
BeforeH <- table(HRS_wb_w6_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w6$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb6, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w6
save(dintw, file = "../RData/wb_w6/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
HRS_m_ds_wb_w6$dintw <- car::recode(HRS_m_ds_wb_w6$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w6', HRS_m_ds_wb_w6)
#opal.symbol_import(o,'HRS_m_ds_wb_w6', project='_Athlos_Harm_Dataset')
```







###  Wave 7  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_dinter','HRS.HRS-WB-w7-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_dinter <- opal.execute(o,'HRS_wb_w7_dinter')
HRS_wb_w7_dinter$dinter <- as.numeric(format(HRS_wb_w7_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w7_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w7_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_dinter$id)
HRS_ds_wb_w7$dintw <- car::recode(HRS_wb_w7_dinter$dinter, "NA=999")
HRS_ds_wb_w7$dintw <- labelled(HRS_ds_wb_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
Continuous_summary(var = HRS_ds_wb_w7$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w7, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb7, echo=F}
BeforeH <- table(HRS_wb_w7_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb7, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w7
save(dintw, file = "../RData/wb_w7/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
HRS_m_ds_wb_w7$dintw <- car::recode(HRS_m_ds_wb_w7$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w7', HRS_m_ds_wb_w7)
#opal.symbol_import(o,'HRS_m_ds_wb_w7', project='_Athlos_Harm_Dataset')
```








###  Wave 8  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_dinter','HRS.HRS-WB-w8-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_dinter <- opal.execute(o,'HRS_wb_w8_dinter')
HRS_wb_w8_dinter$dinter <- as.numeric(format(HRS_wb_w8_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w8_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w8_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_dinter$id)
HRS_ds_wb_w8$dintw <- car::recode(HRS_wb_w8_dinter$dinter, "NA=999")
HRS_ds_wb_w8$dintw <- labelled(HRS_ds_wb_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
Continuous_summary(var = HRS_ds_wb_w8$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w8, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb8, echo=F}
BeforeH <- table(HRS_wb_w8_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb8, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w8
save(dintw, file = "../RData/wb_w8/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
HRS_m_ds_wb_w8$dintw <- car::recode(HRS_m_ds_wb_w8$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w8', HRS_m_ds_wb_w8)
#opal.symbol_import(o,'HRS_m_ds_wb_w8', project='_Athlos_Harm_Dataset')
```








###  Wave 9  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_dinter','HRS.HRS-WB-w9-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_dinter <- opal.execute(o,'HRS_wb_w9_dinter')
HRS_wb_w9_dinter$dinter <- as.numeric(format(HRS_wb_w9_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w9_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w9_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_dinter$id)
HRS_ds_wb_w9$dintw <- car::recode(HRS_wb_w9_dinter$dinter, "NA=999")
HRS_ds_wb_w9$dintw <- labelled(HRS_ds_wb_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
Continuous_summary(var = HRS_ds_wb_w9$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w9, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb9, echo=F}
BeforeH <- table(HRS_wb_w9_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb9, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w9
save(dintw, file = "../RData/wb_w9/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
HRS_m_ds_wb_w9$dintw <- car::recode(HRS_m_ds_wb_w9$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w9', HRS_m_ds_wb_w9)
#opal.symbol_import(o,'HRS_m_ds_wb_w9', project='_Athlos_Harm_Dataset')
```







###  Wave 10  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_dinter','HRS.HRS-WB-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_dinter <- opal.execute(o,'HRS_wb_w10_dinter')
HRS_wb_w10_dinter$dinter <- as.numeric(format(HRS_wb_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_dinter$id)
HRS_ds_wb_w10$dintw <- car::recode(HRS_wb_w10_dinter$dinter, "NA=999")
HRS_ds_wb_w10$dintw <- labelled(HRS_ds_wb_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
Continuous_summary(var = HRS_ds_wb_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb10, echo=F}
BeforeH <- table(HRS_wb_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb10, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w10
save(dintw, file = "../RData/wb_w10/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
HRS_m_ds_wb_w10$dintw <- car::recode(HRS_m_ds_wb_w10$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w10', HRS_m_ds_wb_w10)
#opal.symbol_import(o,'HRS_m_ds_wb_w10', project='_Athlos_Harm_Dataset')
```







###  Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_dinter','HRS.HRS-WB-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_dinter <- opal.execute(o,'HRS_wb_w11_dinter')
HRS_wb_w11_dinter$dinter <- as.numeric(format(HRS_wb_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_wb_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_wb_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_dinter$id)
HRS_ds_wb_w11$dintw <- car::recode(HRS_wb_w11_dinter$dinter, "NA=999")
HRS_ds_wb_w11$dintw <- labelled(HRS_ds_wb_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
Continuous_summary(var = HRS_ds_wb_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb11, echo=F}
BeforeH <- table(HRS_wb_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb11, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_wb_w11
save(dintw, file = "../RData/wb_w11/dintw.RData")
rm(dintw)

HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
HRS_m_ds_wb_w11$dintw <- car::recode(HRS_m_ds_wb_w11$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w11', HRS_m_ds_wb_w11)
#opal.symbol_import(o,'HRS_m_ds_wb_w11', project='_Athlos_Harm_Dataset')
```







###  Wave 7  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_dinter','HRS.HRS-EBB-w7-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_dinter <- opal.execute(o,'HRS_ebb_w7_dinter')
HRS_ebb_w7_dinter$dinter <- as.numeric(format(HRS_ebb_w7_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ebb_w7_dinter$dinter, missing_values = NA)
ggplot(HRS_ebb_w7_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_dinter$id)
HRS_ds_ebb_w7$dintw <- car::recode(HRS_ebb_w7_dinter$dinter, "NA=999")
HRS_ds_ebb_w7$dintw <- labelled(HRS_ds_ebb_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
Continuous_summary(var = HRS_ds_ebb_w7$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w7, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb7, echo=F}
BeforeH <- table(HRS_ebb_w7_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb7, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ebb_w7
save(dintw, file = "../RData/ebb_w7/dintw.RData")
rm(dintw)

HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
HRS_m_ds_ebb_w7$dintw <- car::recode(HRS_m_ds_ebb_w7$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w7', HRS_m_ds_ebb_w7)
#opal.symbol_import(o,'HRS_m_ds_ebb_w7', project='_Athlos_Harm_Dataset')
```







###  Wave 8  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_dinter','HRS.HRS-EBB-w8-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_dinter <- opal.execute(o,'HRS_ebb_w8_dinter')
HRS_ebb_w8_dinter$dinter <- as.numeric(format(HRS_ebb_w8_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ebb_w8_dinter$dinter, missing_values = NA)
ggplot(HRS_ebb_w8_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_dinter$id)
HRS_ds_ebb_w8$dintw <- car::recode(HRS_ebb_w8_dinter$dinter, "NA=999")
HRS_ds_ebb_w8$dintw <- labelled(HRS_ds_ebb_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
Continuous_summary(var = HRS_ds_ebb_w8$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w8, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb8, echo=F}
BeforeH <- table(HRS_ebb_w8_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb8, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ebb_w8
save(dintw, file = "../RData/ebb_w8/dintw.RData")
rm(dintw)

HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
HRS_m_ds_ebb_w8$dintw <- car::recode(HRS_m_ds_ebb_w8$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w8', HRS_m_ds_ebb_w8)
#opal.symbol_import(o,'HRS_m_ds_ebb_w8', project='_Athlos_Harm_Dataset')
```







###  Wave 9  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_dinter','HRS.HRS-EBB-w9-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_dinter <- opal.execute(o,'HRS_ebb_w9_dinter')
HRS_ebb_w9_dinter$dinter <- as.numeric(format(HRS_ebb_w9_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ebb_w9_dinter$dinter, missing_values = NA)
ggplot(HRS_ebb_w9_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_dinter$id)
HRS_ds_ebb_w9$dintw <- car::recode(HRS_ebb_w9_dinter$dinter, "NA=999")
HRS_ds_ebb_w9$dintw <- labelled(HRS_ds_ebb_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
Continuous_summary(var = HRS_ds_ebb_w9$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w9, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb9, echo=F}
BeforeH <- table(HRS_ebb_w9_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb9, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ebb_w9
save(dintw, file = "../RData/ebb_w9/dintw.RData")
rm(dintw)

HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
HRS_m_ds_ebb_w9$dintw <- car::recode(HRS_m_ds_ebb_w9$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w9', HRS_m_ds_ebb_w9)
#opal.symbol_import(o,'HRS_m_ds_ebb_w9', project='_Athlos_Harm_Dataset')
```







###  Wave 10  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_dinter','HRS.HRS-EBB-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_dinter <- opal.execute(o,'HRS_ebb_w10_dinter')
HRS_ebb_w10_dinter$dinter <- as.numeric(format(HRS_ebb_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ebb_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_ebb_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_dinter$id)
HRS_ds_ebb_w10$dintw <- car::recode(HRS_ebb_w10_dinter$dinter, "NA=999")
HRS_ds_ebb_w10$dintw <- labelled(HRS_ds_ebb_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
Continuous_summary(var = HRS_ds_ebb_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb10, echo=F}
BeforeH <- table(HRS_ebb_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb10, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ebb_w10
save(dintw, file = "../RData/ebb_w10/dintw.RData")
rm(dintw)

HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
HRS_m_ds_ebb_w10$dintw <- car::recode(HRS_m_ds_ebb_w10$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w10', HRS_m_ds_ebb_w10)
#opal.symbol_import(o,'HRS_m_ds_ebb_w10', project='_Athlos_Harm_Dataset')
```







###  Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_dinter','HRS.HRS-EBB-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_dinter <- opal.execute(o,'HRS_ebb_w11_dinter')
HRS_ebb_w11_dinter$dinter <- as.numeric(format(HRS_ebb_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_ebb_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_ebb_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_dinter$id)
HRS_ds_ebb_w11$dintw <- car::recode(HRS_ebb_w11_dinter$dinter, "NA=999")
HRS_ds_ebb_w11$dintw <- labelled(HRS_ds_ebb_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
Continuous_summary(var = HRS_ds_ebb_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb11, echo=F}
BeforeH <- table(HRS_ebb_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb11, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_ebb_w11
save(dintw, file = "../RData/ebb_w11/dintw.RData")
rm(dintw)

HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
HRS_m_ds_ebb_w11$dintw <- car::recode(HRS_m_ds_ebb_w11$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w11', HRS_m_ds_ebb_w11)
#opal.symbol_import(o,'HRS_m_ds_ebb_w11', project='_Athlos_Harm_Dataset')
```




## MBB

### Wave 10

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`

```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_dinter','HRS.HRS-MBB-w10-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_dinter <- opal.execute(o,'HRS_mbb_w10_dinter')
HRS_mbb_w10_dinter$dinter <- as.numeric(format(HRS_mbb_w10_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_mbb_w10_dinter$dinter, missing_values = NA)
ggplot(HRS_mbb_w10_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_dinter$id)
HRS_ds_mbb_w10$dintw <- car::recode(HRS_mbb_w10_dinter$dinter, "NA=999")
HRS_ds_mbb_w10$dintw <- labelled(HRS_ds_mbb_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
Continuous_summary(var = HRS_ds_mbb_w10$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w10, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb10, echo=F}
BeforeH <- table(HRS_mbb_w10_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb10, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_mbb_w10
save(dintw, file = "../RData/mbb_w10/dintw.RData")
rm(dintw)

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
HRS_m_ds_mbb_w10$dintw <- car::recode(HRS_m_ds_mbb_w10$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w10', HRS_m_ds_mbb_w10)
#opal.symbol_import(o,'HRS_m_ds_mbb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11IWBEG`
* Label: `Interview Begin Date`
* Type of variable: `countinous`


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_dinter','HRS.HRS-MBB-w11-date_of_interview',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_dinter <- opal.execute(o,'HRS_mbb_w11_dinter')
HRS_mbb_w11_dinter$dinter <- as.numeric(format(HRS_mbb_w11_dinter$dinterview, '%d'))
Continuous_summary(var = HRS_mbb_w11_dinter$dinter, missing_values = NA)
ggplot(HRS_mbb_w11_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Data process
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_dinter$id)
HRS_ds_mbb_w11$dintw <- car::recode(HRS_mbb_w11_dinter$dinter, "NA=999")
HRS_ds_mbb_w11$dintw <- labelled(HRS_ds_mbb_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
Continuous_summary(var = HRS_ds_mbb_w11$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w11, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb11, echo=F}
BeforeH <- table(HRS_mbb_w11_dinter$dinter, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb11, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
dintw <- HRS_ds_mbb_w11
save(dintw, file = "../RData/mbb_w11/dintw.RData")
rm(dintw)

HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
HRS_m_ds_mbb_w11$dintw <- car::recode(HRS_m_ds_mbb_w11$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w11', HRS_m_ds_mbb_w11)
#opal.symbol_import(o,'HRS_m_ds_mbb_w11', project='_Athlos_Harm_Dataset')
```
#### Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
