---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```



# Data process



## HRS

### Wave 1

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w1`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w1, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w1','HRS.HRS-HRS-w1',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w1 <- opal.execute(o,'HRS_hrs_w1')

```

```{r local hrs_w1, echo=F}

vbl <- HRS_hrs_w1$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w1,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")



```


#### Harmonisation algorithm








**R script:**

```{r harmo hrs_w1}

# Categorical variable harmonization
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1$id)
HRS_ds_hrs_w1$w <- car::recode(as.character(HRS_hrs_w1$RAWTSAMP),"NA=999")

```




#### Statistics of the new harmonized variable

```{r descript hrs_w1, echo=F}

vbl <- HRS_ds_hrs_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w1,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```










### Wave 2

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w2`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w2, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w2','HRS.HRS-HRS-w2',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w2 <- opal.execute(o,'HRS_hrs_w2')












```

```{r local hrs_w2, echo=F}

vbl <- HRS_hrs_w2$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w2,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")













```


#### Harmonisation algorithm













**R script:**

```{r harmo hrs_w2}

# Categorical variable harmonization
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2$id)
HRS_ds_hrs_w2$w <- car::recode(as.character(HRS_hrs_w2$RAWTSAMP),"NA=999")






```




#### Statistics of the new harmonized variable

```{r descript hrs_w2, echo=F}

vbl <- HRS_ds_hrs_w2$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w2,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```







### Wave 3

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w3`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w3, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w3','HRS.HRS-HRS-w3',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w3 <- opal.execute(o,'HRS_hrs_w3')












```

```{r local hrs_w3, echo=F}

vbl <- HRS_hrs_w3$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w3,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")











```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w3}

# Categorical variable harmonization
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3$id)
HRS_ds_hrs_w3$w <- car::recode(as.character(HRS_hrs_w3$RAWTSAMP),"NA=999")







```






#### Statistics of the new harmonized variable

```{r descript hrs_w3, echo=F}

vbl <- HRS_ds_hrs_w3$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w3,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```










### Wave 4

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w4`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w4, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w4','HRS.HRS-HRS-w4',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w4 <- opal.execute(o,'HRS_hrs_w4')












```

```{r local hrs_w4, echo=F}

vbl <- HRS_hrs_w4$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w4,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")











```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w4}


# Categorical variable harmonization
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4$id)
HRS_ds_hrs_w4$w <- car::recode(as.character(HRS_hrs_w4$RAWTSAMP),"NA=999")







```




#### Statistics of the new harmonized variable

```{r descript hrs_w4, echo=F}

vbl <- HRS_ds_hrs_w4$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w4,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```










### Wave 5

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w5`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w5, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w5','HRS.HRS-HRS-w5',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w5 <- opal.execute(o,'HRS_hrs_w5')












```

```{r local hrs_w5, echo=F}

vbl <- HRS_hrs_w5$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w5,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w5}




# Categorical variable harmonization
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5$id)
HRS_ds_hrs_w5$w <- car::recode(as.character(HRS_hrs_w5$RAWTSAMP),"NA=999")







```








#### Statistics of the new harmonized variable

```{r descript hrs_w5, echo=F}

vbl <- HRS_ds_hrs_w5$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w5,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```






### Wave 6

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w6`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w6, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w6','HRS.HRS-HRS-w6',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w6 <- opal.execute(o,'HRS_hrs_w6')












```

```{r local hrs_w6, echo=F}

vbl <- HRS_hrs_w6$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w6,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w6}




# Categorical variable harmonization
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6$id)
HRS_ds_hrs_w6$w <- car::recode(as.character(HRS_hrs_w6$RAWTSAMP),"NA=999")







```










#### Statistics of the new harmonized variable

```{r descript hrs_w6, echo=F}

vbl <- HRS_ds_hrs_w6$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w6,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 7

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w7`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w7, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w7','HRS.HRS-HRS-w7',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w7 <- opal.execute(o,'HRS_hrs_w7')












```

```{r local hrs_w7, echo=F}

vbl <- HRS_hrs_w7$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w7,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w7}




# Categorical variable harmonization
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7$id)
HRS_ds_hrs_w7$w <- car::recode(as.character(HRS_hrs_w7$RAWTSAMP),"NA=999")






```






#### Statistics of the new harmonized variable

```{r descript hrs_w7, echo=F}

vbl <- HRS_ds_hrs_w7$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w7,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```






### Wave 8

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w8`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w8, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w8','HRS.HRS-HRS-w8',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w8 <- opal.execute(o,'HRS_hrs_w8')












```

```{r local hrs_w8, echo=F}

vbl <- HRS_hrs_w8$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w8,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w8}




# Categorical variable harmonization
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8$id)
HRS_ds_hrs_w8$w <- car::recode(as.character(HRS_hrs_w8$RAWTSAMP),"NA=999")







```






#### Statistics of the new harmonized variable

```{r descript hrs_w8, echo=F}

vbl <- HRS_ds_hrs_w8$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w8,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```






### Wave 9

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w9`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w9, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w9','HRS.HRS-HRS-w9',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w9 <- opal.execute(o,'HRS_hrs_w9')












```

```{r local hrs_w9, echo=F}

vbl <- HRS_hrs_w9$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w9,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w9}




# Categorical variable harmonization
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9$id)
HRS_ds_hrs_w9$w <- car::recode(as.character(HRS_hrs_w9$RAWTSAMP),"NA=999")







```











#### Statistics of the new harmonized variable

```{r descript hrs_w9, echo=F}

vbl <- HRS_ds_hrs_w9$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w9,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w10','HRS.HRS-HRS-w10',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w10 <- opal.execute(o,'HRS_hrs_w10')












```

```{r local hrs_w10, echo=F}

vbl <- HRS_hrs_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w10}




# Categorical variable harmonization
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10$id)
HRS_ds_hrs_w10$w <- car::recode(as.character(HRS_hrs_w10$RAWTSAMP),"NA=999")







```








#### Statistics of the new harmonized variable

```{r descript hrs_w10, echo=F}

vbl <- HRS_ds_hrs_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-HRS-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign hrs_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w11','HRS.HRS-HRS-w11',variables=list('RAWTSAMP'), missings = T)
HRS_hrs_w11 <- opal.execute(o,'HRS_hrs_w11')












```

```{r local hrs_w11, echo=F}

vbl <- HRS_hrs_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_hrs_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo hrs_w11}




# Categorical variable harmonization
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11$id)
HRS_ds_hrs_w11$w <- car::recode(as.character(HRS_hrs_w11$RAWTSAMP),"NA=999")







```












#### Statistics of the new harmonized variable

```{r descript hrs_w11, echo=F}

vbl <- HRS_ds_hrs_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_hrs_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





## AHEAD


### Wave 2

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w2`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w2, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w2','HRS.HRS-AHEAD-w2',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w2 <- opal.execute(o,'HRS_ahead_w2')

```

```{r local ahead_w2, echo=F}

vbl <- HRS_ahead_w2$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w2,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm









**R script:**

```{r harmo ahead_w2}

# Categorical variable harmonization
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2$id)
HRS_ds_ahead_w2$w <- car::recode(as.character(HRS_ahead_w2$RAWTSAMP),"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript ahead_w2, echo=F}

vbl <- HRS_ds_ahead_w2$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w2,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 3

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w3`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w3, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w3','HRS.HRS-AHEAD-w3',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w3 <- opal.execute(o,'HRS_ahead_w3')












```

```{r local ahead_w3, echo=F}

vbl <- HRS_ahead_w3$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w3,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm













**R script:**

```{r harmo ahead_w3}




# Categorical variable harmonization
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3$id)
HRS_ds_ahead_w3$w <- car::recode(as.character(HRS_ahead_w3$RAWTSAMP),"NA=999")







```











#### Statistics of the new harmonized variable

```{r descript ahead_w3, echo=F}

vbl <- HRS_ds_ahead_w3$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w3,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 4

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w4`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w4, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w4','HRS.HRS-AHEAD-w4',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w4 <- opal.execute(o,'HRS_ahead_w4')












```

```{r local ahead_w4, echo=F}

vbl <- HRS_ahead_w4$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w4,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w4}




# Categorical variable harmonization
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4$id)
HRS_ds_ahead_w4$w <- car::recode(as.character(HRS_ahead_w4$RAWTSAMP),"NA=999")






```




#### Statistics of the new harmonized variable

```{r descript ahead_w4, echo=F}

vbl <- HRS_ds_ahead_w4$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w4,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 5

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w5`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w5, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w5','HRS.HRS-AHEAD-w5',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w5 <- opal.execute(o,'HRS_ahead_w5')












```

```{r local ahead_w5, echo=F}

vbl <- HRS_ahead_w5$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w5,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w5}




# Categorical variable harmonization
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5$id)
HRS_ds_ahead_w5$w <- car::recode(as.character(HRS_ahead_w5$RAWTSAMP),"NA=999")







```



#### Statistics of the new harmonized variable

```{r descript ahead_w5, echo=F}

vbl <- HRS_ds_ahead_w5$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w5,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 6

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w6`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w6, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w6','HRS.HRS-AHEAD-w6',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w6 <- opal.execute(o,'HRS_ahead_w6')












```

```{r local ahead_w6, echo=F}

vbl <- HRS_ahead_w6$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w6,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w6}




# Categorical variable harmonization
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6$id)
HRS_ds_ahead_w6$w <- car::recode(as.character(HRS_ahead_w6$RAWTSAMP),"NA=999")






```






#### Statistics of the new harmonized variable

```{r descript ahead_w6, echo=F}

vbl <- HRS_ds_ahead_w6$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w6,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 7

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w7`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w7, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w7','HRS.HRS-AHEAD-w7',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w7 <- opal.execute(o,'HRS_ahead_w7')












```

```{r local ahead_w7, echo=F}

vbl <- HRS_ahead_w7$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w7,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")








```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w7}




# Categorical variable harmonization
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7$id)
HRS_ds_ahead_w7$w <- car::recode(as.character(HRS_ahead_w7$RAWTSAMP),"NA=999")







```








#### Statistics of the new harmonized variable

```{r descript ahead_w7, echo=F}

vbl <- HRS_ds_ahead_w7$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w7,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 8

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w8`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w8, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w8','HRS.HRS-AHEAD-w8',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w8 <- opal.execute(o,'HRS_ahead_w8')












```

```{r local ahead_w8, echo=F}

vbl <- HRS_ahead_w8$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w8,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")








```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w8}




# Categorical variable harmonization
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8$id)
HRS_ds_ahead_w8$w <- car::recode(as.character(HRS_ahead_w8$RAWTSAMP),"NA=999")







```








#### Statistics of the new harmonized variable

```{r descript ahead_w8, echo=F}

vbl <- HRS_ds_ahead_w8$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w8,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 9

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w9`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w9, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w9','HRS.HRS-AHEAD-w9',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w9 <- opal.execute(o,'HRS_ahead_w9')












```

```{r local ahead_w9, echo=F}

vbl <- HRS_ahead_w9$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w9,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w9}




# Categorical variable harmonization
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9$id)
HRS_ds_ahead_w9$w <- car::recode(as.character(HRS_ahead_w9$RAWTSAMP),"NA=999")






```








#### Statistics of the new harmonized variable

```{r descript ahead_w9, echo=F}

vbl <- HRS_ds_ahead_w9$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w9,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w10','HRS.HRS-AHEAD-w10',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w10 <- opal.execute(o,'HRS_ahead_w10')












```

```{r local ahead_w10, echo=F}

vbl <- HRS_ahead_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w10}




# Categorical variable harmonization
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10$id)
HRS_ds_ahead_w10$w <- car::recode(as.character(HRS_ahead_w10$RAWTSAMP),"NA=999")






```



#### Statistics of the new harmonized variable

```{r descript ahead_w10, echo=F}

vbl <- HRS_ds_ahead_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-AHEAD-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ahead_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_ahead_w11','HRS.HRS-AHEAD-w11',variables=list('RAWTSAMP'), missings = T)
HRS_ahead_w11 <- opal.execute(o,'HRS_ahead_w11')












```

```{r local ahead_w11, echo=F}

vbl <- HRS_ahead_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ahead_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ahead_w11}




# Categorical variable harmonization
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11$id)
HRS_ds_ahead_w11$w <- car::recode(as.character(HRS_ahead_w11$RAWTSAMP),"NA=999")






```











#### Statistics of the new harmonized variable

```{r descript ahead_w11, echo=F}

vbl <- HRS_ds_ahead_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ahead_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



## CODA

### Wave 4

All data is missing.

### Wave 5

All data is missing.

### Wave 6

All data is missing.

### Wave 7

All data is missing.

### Wave 8

All data is missing.

### Wave 9

All data is missing.

### Wave 10

All data is missing.

### Wave 11

All data is missing.



## WB

### Wave 4

All data is missing.

### Wave 5

All data is missing.

### Wave 6

All data is missing.

### Wave 7

All data is missing.

### Wave 8

All data is missing.

### Wave 9

All data is missing.

### Wave 10

All data is missing.

### Wave 11

All data is missing.

## EBB

### Wave 7

All data is missing.

### Wave 8

All data is missing.

### Wave 9

All data is missing.

### Wave 10

All data is missing.

### Wave 11

All data is missing.

## MBB

### Wave 10

All data is missing.

### Wave 11

All data is missing.

<!--
#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w4`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w4, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w4','HRS.HRS-CODA-w4',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w4 <- opal.execute(o,'HRS_coda_w4')

```

```{r local coda_w4, echo=F}

vbl <- HRS_coda_w4$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w4,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm









**R script:**

```{r harmo coda_w4}

# Categorical variable harmonization
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4$id)
HRS_ds_coda_w4$w <- car::recode(as.character(HRS_coda_w4$RAWTSAMP),"NA=999")

```




#### Statistics of the new harmonized variable

```{r descript coda_w4, echo=F}

vbl <- HRS_ds_coda_w4$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w4,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


### Wave 5

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w5`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w5, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w5','HRS.HRS-CODA-w5',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w5 <- opal.execute(o,'HRS_coda_w5')












```

```{r local coda_w5, echo=F}

vbl <- HRS_coda_w5$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w5,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm













**R script:**

```{r harmo coda_w5}




# Categorical variable harmonization
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5$id)
HRS_ds_coda_w5$w <- car::recode(as.character(HRS_coda_w5$RAWTSAMP),"NA=999")






```

#### Statistics of the new harmonized variable

```{r descript coda_w5, echo=F}

vbl <- HRS_ds_coda_w5$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w5,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 6

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w6`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w6, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w6','HRS.HRS-CODA-w6',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w6 <- opal.execute(o,'HRS_coda_w6')












```

```{r local coda_w6, echo=F}

vbl <- HRS_coda_w6$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w6,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w6}




# Categorical variable harmonization
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6$id)
HRS_ds_coda_w6$w <- car::recode(as.character(HRS_coda_w6$RAWTSAMP),"NA=999")






```












#### Statistics of the new harmonized variable

```{r descript coda_w6, echo=F}

vbl <- HRS_ds_coda_w6$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w6,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 7

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w7`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w7, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w7','HRS.HRS-CODA-w7',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w7 <- opal.execute(o,'HRS_coda_w7')












```

```{r local coda_w7, echo=F}

vbl <- HRS_coda_w7$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w7,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w7}




# Categorical variable harmonization
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7$id)
HRS_ds_coda_w7$w <- car::recode(as.character(HRS_coda_w7$RAWTSAMP),"NA=999")






```













#### Statistics of the new harmonized variable

```{r descript coda_w7, echo=F}

vbl <- HRS_ds_coda_w7$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w7,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 8

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w8`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w8, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w8','HRS.HRS-CODA-w8',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w8 <- opal.execute(o,'HRS_coda_w8')












```

```{r local coda_w8, echo=F}

vbl <- HRS_coda_w8$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w8,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w8}




# Categorical variable harmonization
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8$id)
HRS_ds_coda_w8$w <- car::recode(as.character(HRS_coda_w8$RAWTSAMP),"NA=999")






```


#### Statistics of the new harmonized variable

```{r descript coda_w8, echo=F}

vbl <- HRS_ds_coda_w8$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w8,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 9

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w9`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w9, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w9','HRS.HRS-CODA-w9',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w9 <- opal.execute(o,'HRS_coda_w9')












```

```{r local coda_w9, echo=F}

vbl <- HRS_coda_w9$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w9,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w9}




# Categorical variable harmonization
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9$id)
HRS_ds_coda_w9$w <- car::recode(as.character(HRS_coda_w9$RAWTSAMP),"NA=999")






```


#### Statistics of the new harmonized variable

```{r descript coda_w9, echo=F}

vbl <- HRS_ds_coda_w9$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w9,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w10','HRS.HRS-CODA-w10',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w10 <- opal.execute(o,'HRS_coda_w10')












```

```{r local coda_w10, echo=F}

vbl <- HRS_coda_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w10}




# Categorical variable harmonization
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10$id)
HRS_ds_coda_w10$w <- car::recode(as.character(HRS_coda_w10$RAWTSAMP),"NA=999")






```

#### Statistics of the new harmonized variable

```{r descript coda_w10, echo=F}

vbl <- HRS_ds_coda_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-CODA-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign coda_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_coda_w11','HRS.HRS-CODA-w11',variables=list('RAWTSAMP'), missings = T)
HRS_coda_w11 <- opal.execute(o,'HRS_coda_w11')












```

```{r local coda_w11, echo=F}

vbl <- HRS_coda_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_coda_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo coda_w11}




# Categorical variable harmonization
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11$id)
HRS_ds_coda_w11$w <- car::recode(as.character(HRS_coda_w11$RAWTSAMP),"NA=999")







```










#### Statistics of the new harmonized variable

```{r descript coda_w11, echo=F}

vbl <- HRS_ds_coda_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_coda_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





## WB

### Wave 4

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w4`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w4, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w4','HRS.HRS-WB-w4',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w4 <- opal.execute(o,'HRS_wb_w4')

```

```{r local wb_w4, echo=F}

vbl <- HRS_wb_w4$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w4,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm









**R script:**

```{r harmo wb_w4}

# Categorical variable harmonization
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4$id)
HRS_ds_wb_w4$w <- car::recode(as.character(HRS_wb_w4$RAWTSAMP),"NA=999")

```

#### Statistics of the new harmonized variable

```{r descript wb_w4, echo=F}

vbl <- HRS_ds_wb_w4$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w4,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```






### Wave 5

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w5`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w5, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w5','HRS.HRS-WB-w5',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w5 <- opal.execute(o,'HRS_wb_w5')












```

```{r local wb_w5, echo=F}

vbl <- HRS_wb_w5$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w5,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm













**R script:**

```{r harmo wb_w5}




# Categorical variable harmonization
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5$id)
HRS_ds_wb_w5$w <- car::recode(as.character(HRS_wb_w5$RAWTSAMP),"NA=999")






```


#### Statistics of the new harmonized variable

```{r descript wb_w5, echo=F}

vbl <- HRS_ds_wb_w5$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w5,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 6

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w6`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w6, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w6','HRS.HRS-WB-w6',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w6 <- opal.execute(o,'HRS_wb_w6')












```

```{r local wb_w6, echo=F}

vbl <- HRS_wb_w6$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w6,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w6}




# Categorical variable harmonization
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6$id)
HRS_ds_wb_w6$w <- car::recode(as.character(HRS_wb_w6$RAWTSAMP),"NA=999")






```


#### Statistics of the new harmonized variable

```{r descript wb_w6, echo=F}

vbl <- HRS_ds_wb_w6$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w6,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 7

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w7`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w7, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w7','HRS.HRS-WB-w7',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w7 <- opal.execute(o,'HRS_wb_w7')












```

```{r local wb_w7, echo=F}

vbl <- HRS_wb_w7$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w7,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w7}




# Categorical variable harmonization
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7$id)
HRS_ds_wb_w7$w <- car::recode(as.character(HRS_wb_w7$RAWTSAMP),"NA=999")






```










#### Statistics of the new harmonized variable

```{r descript wb_w7, echo=F}

vbl <- HRS_ds_wb_w7$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w7,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 8

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w8`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w8, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w8','HRS.HRS-WB-w8',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w8 <- opal.execute(o,'HRS_wb_w8')












```

```{r local wb_w8, echo=F}

vbl <- HRS_wb_w8$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w8,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w8}




# Categorical variable harmonization
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8$id)
HRS_ds_wb_w8$w <- car::recode(as.character(HRS_wb_w8$RAWTSAMP),"NA=999")







```




#### Statistics of the new harmonized variable

```{r descript wb_w8, echo=F}

vbl <- HRS_ds_wb_w8$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w8,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 9

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w9`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w9, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w9','HRS.HRS-WB-w9',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w9 <- opal.execute(o,'HRS_wb_w9')












```

```{r local wb_w9, echo=F}

vbl <- HRS_wb_w9$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w9,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w9}




# Categorical variable harmonization
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9$id)
HRS_ds_wb_w9$w <- car::recode(as.character(HRS_wb_w9$RAWTSAMP),"NA=999")






```








#### Statistics of the new harmonized variable

```{r descript wb_w9, echo=F}

vbl <- HRS_ds_wb_w9$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w9,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w10','HRS.HRS-WB-w10',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w10 <- opal.execute(o,'HRS_wb_w10')












```

```{r local wb_w10, echo=F}

vbl <- HRS_wb_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w10}




# Categorical variable harmonization
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10$id)
HRS_ds_wb_w10$w <- car::recode(as.character(HRS_wb_w10$RAWTSAMP),"NA=999")






```




#### Statistics of the new harmonized variable

```{r descript wb_w10, echo=F}

vbl <- HRS_ds_wb_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-WB-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign wb_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_wb_w11','HRS.HRS-WB-w11',variables=list('RAWTSAMP'), missings = T)
HRS_wb_w11 <- opal.execute(o,'HRS_wb_w11')












```

```{r local wb_w11, echo=F}

vbl <- HRS_wb_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_wb_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")








```


#### Harmonisation algorithm














**R script:**

```{r harmo wb_w11}




# Categorical variable harmonization
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11$id)
HRS_ds_wb_w11$w <- car::recode(as.character(HRS_wb_w11$RAWTSAMP),"NA=999")







```





#### Statistics of the new harmonized variable

```{r descript wb_w11, echo=F}

vbl <- HRS_ds_wb_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_wb_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




## EBB


### Wave 7

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-EBB-w7`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ebb_w7, echo=F}

opal.assign.table.tibble(o, 'HRS_ebb_w7','HRS.HRS-EBB-w7',variables=list('RAWTSAMP'), missings = T)
HRS_ebb_w7 <- opal.execute(o,'HRS_ebb_w7')

```

```{r local ebb_w7, echo=F}

vbl <- HRS_ebb_w7$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ebb_w7,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm









**R script:**

```{r harmo ebb_w7}

# Categorical variable harmonization
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7$id)
HRS_ds_ebb_w7$w <- car::recode(as.character(HRS_ebb_w7$RAWTSAMP),"NA=999")

```

#### Statistics of the new harmonized variable

```{r descript ebb_w7, echo=F}

vbl <- HRS_ds_ebb_w7$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ebb_w7,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 8

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-EBB-w8`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ebb_w8, echo=F}

opal.assign.table.tibble(o, 'HRS_ebb_w8','HRS.HRS-EBB-w8',variables=list('RAWTSAMP'), missings = T)
HRS_ebb_w8 <- opal.execute(o,'HRS_ebb_w8')












```

```{r local ebb_w8, echo=F}

vbl <- HRS_ebb_w8$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ebb_w8,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm













**R script:**

```{r harmo ebb_w8}




# Categorical variable harmonization
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8$id)
HRS_ds_ebb_w8$w <- car::recode(as.character(HRS_ebb_w8$RAWTSAMP),"NA=999")






```




#### Statistics of the new harmonized variable

```{r descript ebb_w8, echo=F}

vbl <- HRS_ds_ebb_w8$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ebb_w8,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 9

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-EBB-w9`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ebb_w9, echo=F}

opal.assign.table.tibble(o, 'HRS_ebb_w9','HRS.HRS-EBB-w9',variables=list('RAWTSAMP'), missings = T)
HRS_ebb_w9 <- opal.execute(o,'HRS_ebb_w9')












```

```{r local ebb_w9, echo=F}

vbl <- HRS_ebb_w9$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ebb_w9,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm














**R script:**

```{r harmo ebb_w9}




# Categorical variable harmonization
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9$id)
HRS_ds_ebb_w9$w <- car::recode(as.character(HRS_ebb_w9$RAWTSAMP),"NA=999")






```




#### Statistics of the new harmonized variable

```{r descript ebb_w9, echo=F}

vbl <- HRS_ds_ebb_w9$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ebb_w9,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-EBB-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ebb_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_ebb_w10','HRS.HRS-EBB-w10',variables=list('RAWTSAMP'), missings = T)
HRS_ebb_w10 <- opal.execute(o,'HRS_ebb_w10')












```

```{r local ebb_w10, echo=F}

vbl <- HRS_ebb_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ebb_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ebb_w10}




# Categorical variable harmonization
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10$id)
HRS_ds_ebb_w10$w <- car::recode(as.character(HRS_ebb_w10$RAWTSAMP),"NA=999")






```






#### Statistics of the new harmonized variable

```{r descript ebb_w10, echo=F}

vbl <- HRS_ds_ebb_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ebb_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-EBB-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign ebb_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_ebb_w11','HRS.HRS-EBB-w11',variables=list('RAWTSAMP'), missings = T)
HRS_ebb_w11 <- opal.execute(o,'HRS_ebb_w11')












```

```{r local ebb_w11, echo=F}

vbl <- HRS_ebb_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_ebb_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm














**R script:**

```{r harmo ebb_w11}




# Categorical variable harmonization
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11$id)
HRS_ds_ebb_w11$w <- car::recode(as.character(HRS_ebb_w11$RAWTSAMP),"NA=999")






```



#### Statistics of the new harmonized variable

```{r descript ebb_w11, echo=F}

vbl <- HRS_ds_ebb_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_ebb_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



## MBB


### Wave 10

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-MBB-w10`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign mbb_w10, echo=F}

opal.assign.table.tibble(o, 'HRS_mbb_w10','HRS.HRS-MBB-w10',variables=list('RAWTSAMP'), missings = T)
HRS_mbb_w10 <- opal.execute(o,'HRS_mbb_w10')

```

```{r local mbb_w10, echo=F}

vbl <- HRS_mbb_w10$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_mbb_w10,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")






```


#### Harmonisation algorithm









**R script:**

```{r harmo mbb_w10}

# Categorical variable harmonization
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10$id)
HRS_ds_mbb_w10$w <- car::recode(as.character(HRS_mbb_w10$RAWTSAMP),"NA=999")

```





#### Statistics of the new harmonized variable

```{r descript mbb_w10, echo=F}

vbl <- HRS_ds_mbb_w10$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_mbb_w10,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



### Wave 11

#### Study-specific variable description

| **Name** | `RAWTSAMP` |
|-|-|
| **Label** | `RAWTSAMP: Sampling Weight`|
| **Table name**  | `HRS-MBB-w11`|
| **Categories** | `continuous` |
| **Description** |  |



```{r assign mbb_w11, echo=F}

opal.assign.table.tibble(o, 'HRS_mbb_w11','HRS.HRS-MBB-w11',variables=list('RAWTSAMP'), missings = T)
HRS_mbb_w11 <- opal.execute(o,'HRS_mbb_w11')












```

```{r local mbb_w11, echo=F}

vbl <- HRS_mbb_w11$RAWTSAMP
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'RAWTSAMP')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HRS_mbb_w11,!vbl %in% vbl_miss), aes(x=factor(RAWTSAMP))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")







```


#### Harmonisation algorithm













**R script:**

```{r harmo mbb_w11}




# Categorical variable harmonization
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11$id)
HRS_ds_mbb_w11$w <- car::recode(as.character(HRS_mbb_w11$RAWTSAMP),"NA=999")






```










#### Statistics of the new harmonized variable

```{r descript mbb_w11, echo=F}

vbl <- HRS_ds_mbb_w11$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HRS_ds_mbb_w11,!vbl %in% miss_values_vector), aes(x=factor(w))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

-->




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


lb.hrs <- list(hrs_w1 = HRS_ds_hrs_w1, ahead_w2 = HRS_ds_ahead_w2)#, coda_w4 = HRS_ds_coda_w4, wb_w4 = HRS_ds_wb_w4, ebb_w7 = HRS_ds_ebb_w7, mbb_w10 = HRS_ds_mbb_w10)

lf.hrs <- list(hrs_w2 = HRS_ds_hrs_w2, hrs_w3 = HRS_ds_hrs_w3, hrs_w4 = HRS_ds_hrs_w4, hrs_w5 = HRS_ds_hrs_w5, hrs_w6 = HRS_ds_hrs_w6, hrs_w7 = HRS_ds_hrs_w7, hrs_w8 = HRS_ds_hrs_w8, hrs_w9 = HRS_ds_hrs_w9, hrs_w10 = HRS_ds_hrs_w10, hrs_w11 = HRS_ds_hrs_w11, ahead_w3 = HRS_ds_ahead_w3, ahead_w4 = HRS_ds_ahead_w4, ahead_w5 = HRS_ds_ahead_w5, ahead_w6 = HRS_ds_ahead_w6, ahead_w7 = HRS_ds_ahead_w7, ahead_w8 = HRS_ds_ahead_w8, ahead_w9 = HRS_ds_ahead_w9, ahead_w10 = HRS_ds_ahead_w10, ahead_w11 = HRS_ds_ahead_w11)#, coda_w5 = HRS_ds_coda_w5, coda_w6 = HRS_ds_coda_w6, coda_w7 = HRS_ds_coda_w7, coda_w8 = HRS_ds_coda_w8, coda_w9 = HRS_ds_coda_w9, coda_w10 = HRS_ds_coda_w10, coda_w11 = HRS_ds_coda_w11, wb_w5 = HRS_ds_wb_w5, wb_w6 = HRS_ds_wb_w6, wb_w7 = HRS_ds_wb_w7, wb_w8 = HRS_ds_wb_w8, wb_w9 = HRS_ds_wb_w9, wb_w10 = HRS_ds_wb_w10, wb_w11 = HRS_ds_wb_w11, ebb_w8 = HRS_ds_ebb_w8, ebb_w9 = HRS_ds_ebb_w9, ebb_w10 = HRS_ds_ebb_w10, ebb_w11 = HRS_ds_ebb_w11, mbb_w11 = HRS_ds_mbb_w11)



for(name in names(lb.hrs)){
  label(lb.hrs[[name]][[2]]) <- ds_label
  w <- lb.hrs[[name]]
  save(w, file = paste0(datafolder,name,"/w.RData"))
}

for(name in names(lf.hrs)) {
  label(lf.hrs[[name]][[2]]) <- ds_label
  w <- lf.hrs[[name]]
  save(w, file = paste0(datafolder,name,"/w.RData"))
}


```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





