---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```

<!-- ########################################################## --> 

# Data process

## HRS sub-sample

### Wave 1 

#### Study-specific variable description

| **Name** | `R1PROXY` |
|-|-|
| **Label** | `Whether Proxy Interview` |
| **Table name** | `HRS-HRS-w1` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs1, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w1',
                         variables=list('R1PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs1, echo=FALSE}
vari <- HRS_proxy$R1PROXY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(R1PROXY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs1, echo=TRUE}
HRS_ds_hrs_w1 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w1$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w1$proxy <- labelled(HRS_ds_hrs_w1$proxy, labels = cat_label)
label(HRS_ds_hrs_w1$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=FALSE}
vari <- HRS_ds_hrs_w1$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_hrs1, echo=FALSE}
proxy <- HRS_ds_hrs_w1
save(proxy, file = "../RData/hrs_w1/proxy.RData")
rm(proxy)
```




### Wave 2 

#### Study-specific variable description

| **Name** | `R2PROXY`|
|-|-|
| **Label** | `W2 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w2` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w2',
                         variables=list('R2PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs2, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs2, echo=TRUE}
HRS_ds_hrs_w2 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w2$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w2$proxy <- labelled(HRS_ds_hrs_w2$proxy, labels = cat_label)
label(HRS_ds_hrs_w2$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=FALSE}
vari <- HRS_ds_hrs_w2$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r imporOPAL_hrs2, echo=FALSE}
proxy <- HRS_ds_hrs_w2
save(proxy, file = "../RData/hrs_w2/proxy.RData")
rm(proxy)
```






### Wave 3 

#### Study-specific variable description


| **Name** | `R3PROXY`|
|-|-|
| **Label** | `W3 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w3` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w3',
                         variables=list('R3PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs3, echo=FALSE}
vari <- HRS_proxy$R3PROXY
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(R3PROXY))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs3, echo=TRUE}
HRS_ds_hrs_w3 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w3$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w3$proxy <- labelled(HRS_ds_hrs_w3$proxy, labels = cat_label)
label(HRS_ds_hrs_w3$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=FALSE}
vari <- HRS_ds_hrs_w3$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_hrs3, echo=FALSE}
proxy <- HRS_ds_hrs_w3
save(proxy, file = "../RData/hrs_w3/proxy.RData")
rm(proxy, HRS_proxy)
```








### Wave 4 

#### Study-specific variable description

 

| **Name** | `R4PROXY`|
|-|-|
| **Label** | `W4 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w4` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w4',
                         variables=list('R4PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs4, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs4, echo=TRUE}
HRS_ds_hrs_w4 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w4$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w4$proxy <- labelled(HRS_ds_hrs_w4$proxy, labels = cat_label)
label(HRS_ds_hrs_w4$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=FALSE}
vari <- HRS_ds_hrs_w4$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_hrs4, echo=FALSE}
proxy <- HRS_ds_hrs_w4
save(proxy, file = "../RData/hrs_w4/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 5

#### Study-specific variable description

 

| **Name** | `R5PROXY`|
|-|-|
| **Label** | `W5 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w5` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w5',
                         variables=list('R5PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs5, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs5, echo=TRUE}
HRS_ds_hrs_w5 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w5$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w5$proxy <- labelled(HRS_ds_hrs_w5$proxy, labels = cat_label)
label(HRS_ds_hrs_w5$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=FALSE}
vari <- HRS_ds_hrs_w5$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
 

 
```{r importOPAL_hrs5, echo=FALSE}
proxy <- HRS_ds_hrs_w5
save(proxy, file = "../RData/hrs_w5/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 6

#### Study-specific variable description

| **Name** | `R6PROXY`|
|-|-|
| **Label** | `W6 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w6` |
| **Description** |  |

```{r assign_hrs6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w6',
                         variables=list('R6PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs6, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs6, echo=TRUE}
HRS_ds_hrs_w6 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w6$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w6$proxy <- labelled(HRS_ds_hrs_w6$proxy, labels = cat_label)
label(HRS_ds_hrs_w6$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=FALSE}
vari <- HRS_ds_hrs_w6$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r importOPAL_hrs6, echo=FALSE}
proxy <- HRS_ds_hrs_w6
save(proxy, file = "../RData/hrs_w6/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 7

#### Study-specific variable description

 

| **Name** | `R7PROXY`|
|-|-|
| **Label** | `W7 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w7` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w7',
                         variables=list('R7PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs7, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs7, echo=TRUE}
HRS_ds_hrs_w7 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w7$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w7$proxy <- labelled(HRS_ds_hrs_w7$proxy, labels = cat_label)
label(HRS_ds_hrs_w7$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=FALSE}
vari <- HRS_ds_hrs_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_hrs7, echo=FALSE}
proxy <- HRS_ds_hrs_w7
save(proxy, file = "../RData/hrs_w7/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 8

#### Study-specific variable description

| **Name** | `R8PROXY`|
|-|-|
| **Label** | `W8 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w8',
                         variables=list('R8PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs8, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs8, echo=TRUE}
HRS_ds_hrs_w8 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w8$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w8$proxy <- labelled(HRS_ds_hrs_w8$proxy, labels = cat_label)
label(HRS_ds_hrs_w8$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=FALSE}
vari <- HRS_ds_hrs_w8$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 

 
```{r importOPAL_hrs8, echo=FALSE}
proxy <- HRS_ds_hrs_w8
save(proxy, file = "../RData/hrs_w8/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 9

#### Study-specific variable description

| **Name** | `R9PROXY`|
|-|-|
| **Label** | `W9 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w9',
                         variables=list('R9PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs9, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs9, echo=TRUE}
HRS_ds_hrs_w9 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w9$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w9$proxy <- labelled(HRS_ds_hrs_w9$proxy, labels = cat_label)
label(HRS_ds_hrs_w9$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=FALSE}
vari <- HRS_ds_hrs_w9$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r importOPAL_hrs9, echo=FALSE}
proxy <- HRS_ds_hrs_w9
save(proxy, file = "../RData/hrs_w9/proxy.RData")
rm(proxy, HRS_proxy)
```







### Wave 10

#### Study-specific variable description

| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_hrs10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs10, echo=TRUE}
HRS_ds_hrs_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w10$proxy <- labelled(HRS_ds_hrs_w10$proxy, labels = cat_label)
label(HRS_ds_hrs_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=FALSE}
vari <- HRS_ds_hrs_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_hrs10, echo=FALSE}
proxy <- HRS_ds_hrs_w10
save(proxy, file = "../RData/hrs_w10/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 11

#### Study-specific variable description

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-HRS-w11` |
| **Description** |  |

```{r assign_hrs11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-HRS-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_hrs11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_hrs11, echo=TRUE}
HRS_ds_hrs_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_hrs_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_hrs_w11$proxy <- labelled(HRS_ds_hrs_w11$proxy, labels = cat_label)
label(HRS_ds_hrs_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=FALSE}
vari <- HRS_ds_hrs_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r importOPAL_hrs11, echo=FALSE}
proxy <- HRS_ds_hrs_w11
save(proxy, file = "../RData/hrs_w11/proxy.RData")
rm(proxy, HRS_proxy)
```



## AHEAD sub-sample

### Wave 2 

#### Study-specific variable description

| **Name** | `R2PROXY`|
|-|-|
| **Label** | `W2 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w2` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w2',
                         variables=list('R2PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead2, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead2, echo=TRUE}
HRS_ds_ahead_w2 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w2$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w2$proxy <- labelled(HRS_ds_ahead_w2$proxy, labels = cat_label)
label(HRS_ds_ahead_w2$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=FALSE}
vari <- HRS_ds_ahead_w2$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r importOPAL_ahead2, echo=FALSE}
proxy <- HRS_ds_ahead_w2
save(proxy, file = "../RData/ahead_w2/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 3 

#### Study-specific variable description

 

| **Name** | `R3PROXY`|
|-|-|
| **Label** | `W3 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w3` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w3',
                         variables=list('R3PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead3, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead3, echo=TRUE}
HRS_ds_ahead_w3 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w3$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w3$proxy <- labelled(HRS_ds_ahead_w3$proxy, labels = cat_label)
label(HRS_ds_ahead_w3$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=FALSE}
vari <- HRS_ds_ahead_w3$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



 
```{r importOPAL_ahead3, echo=FALSE}
proxy <- HRS_ds_ahead_w3
save(proxy, file = "../RData/ahead_w3/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 4 

#### Study-specific variable description

 
| **Name** | `R4PROXY`|
|-|-|
| **Label** | `W4 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w4` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w4',
                         variables=list('R4PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead4, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead4, echo=TRUE}
HRS_ds_ahead_w4 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w4$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w4$proxy <- labelled(HRS_ds_ahead_w4$proxy, labels = cat_label)
label(HRS_ds_ahead_w4$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=FALSE}
vari <- HRS_ds_ahead_w4$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ahead4, echo=FALSE}
proxy <- HRS_ds_ahead_w4
save(proxy, file = "../RData/ahead_w4/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 5 

#### Study-specific variable description

 
| **Name** | `R5PROXY`|
|-|-|
| **Label** | `W5 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w5` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w5',
                         variables=list('R5PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead5, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead5, echo=TRUE}
HRS_ds_ahead_w5 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w5$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w5$proxy <- labelled(HRS_ds_ahead_w5$proxy, labels = cat_label)
label(HRS_ds_ahead_w5$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=FALSE}
vari <- HRS_ds_ahead_w5$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL_ahead5, echo=FALSE}
proxy <- HRS_ds_ahead_w5
save(proxy, file = "../RData/ahead_w5/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 6 

#### Study-specific variable description

| **Name** | `R6PROXY`|
|-|-|
| **Label** | `W6 CESD score`|
| **Table name** | `HRS-AHEAD-w6` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w6',
                         variables=list('R6PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead6, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead6, echo=TRUE}
HRS_ds_ahead_w6 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w6$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w6$proxy <- labelled(HRS_ds_ahead_w6$proxy, labels = cat_label)
label(HRS_ds_ahead_w6$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=FALSE}
vari <- HRS_ds_ahead_w6$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL_ahead6, echo=FALSE}
proxy <- HRS_ds_ahead_w6
save(proxy, file = "../RData/ahead_w6/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 7 

#### Study-specific variable description

| **Name** | `R7PROXY`|
|-|-|
| **Label** | `W7 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w7` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w7',
                         variables=list('R7PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead7, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead7, echo=TRUE}
HRS_ds_ahead_w7 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w7$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w7$proxy <- labelled(HRS_ds_ahead_w7$proxy, labels = cat_label)
label(HRS_ds_ahead_w7$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=FALSE}
vari <- HRS_ds_ahead_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ahead7, echo=FALSE}
proxy <- HRS_ds_ahead_w7
save(proxy, file = "../RData/ahead_w7/proxy.RData")
rm(proxy)
```







### Wave 8 

#### Study-specific variable description

| **Name** | `R8PROXY`|
|-|-|
| **Label** | `W8 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w8',
                         variables=list('R8PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead8, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead8, echo=TRUE}
HRS_ds_ahead_w8 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w8$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w8$proxy <- labelled(HRS_ds_ahead_w8$proxy, labels = cat_label)
label(HRS_ds_ahead_w8$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=FALSE}
vari <- HRS_ds_ahead_w8$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ahead8, echo=FALSE}
proxy <- HRS_ds_ahead_w8
save(proxy, file = "../RData/ahead_w8/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 9 

#### Study-specific variable description

| **Name** | `R9PROXY`|
|-|-|
| **Label** | `W9 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w9` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w9',
                         variables=list('R9PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead9, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`


**R script:**

```{r harmo_ahead9, echo=TRUE}
HRS_ds_ahead_w9 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w9$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w9$proxy <- labelled(HRS_ds_ahead_w9$proxy, labels = cat_label)
label(HRS_ds_ahead_w9$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=FALSE}
vari <- HRS_ds_ahead_w9$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_ahead9, echo=FALSE}
proxy <- HRS_ds_ahead_w9
save(proxy, file = "../RData/ahead_w9/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 10 

#### Study-specific variable description


| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead10, echo=TRUE}
HRS_ds_ahead_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w10$proxy <- labelled(HRS_ds_ahead_w10$proxy, labels = cat_label)
label(HRS_ds_ahead_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=FALSE}
vari <- HRS_ds_ahead_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ahead10, echo=FALSE}
proxy <- HRS_ds_ahead_w10
save(proxy, file = "../RData/ahead_w10/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 11 

#### Study-specific variable description

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-AHEAD-w11` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ahead11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-AHEAD-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ahead11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ahead11, echo=TRUE}
HRS_ds_ahead_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_ahead_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ahead_w11$proxy <- labelled(HRS_ds_ahead_w11$proxy, labels = cat_label)
label(HRS_ds_ahead_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=FALSE}
vari <- HRS_ds_ahead_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL_ahead11, echo=FALSE}
proxy <- HRS_ds_ahead_w11
save(proxy, file = "../RData/ahead_w11/proxy.RData")
rm(proxy, HRS_proxy)
```




## The Children of the proxy (CODA) sub-sample

### Wave 4 

#### Study-specific variable description

| **Name** | `R4PROXY`|
|-|-|
| **Label** | `W4 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w4` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w4',
                         variables=list('R4PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda4, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`


**R script:**

```{r harmo_coda4, echo=TRUE}
HRS_ds_coda_w4 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w4$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w4$proxy <- labelled(HRS_ds_coda_w4$proxy, labels = cat_label)
label(HRS_ds_coda_w4$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=FALSE}
vari <- HRS_ds_coda_w4$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda4, echo=FALSE}
proxy <- HRS_ds_coda_w4
save(proxy, file = "../RData/coda_w4/proxy.RData")
rm(proxy, HRS_proxy)
```







### Wave 5 

#### Study-specific variable description

| **Name** | `R5PROXY`|
|-|-|
| **Label** | `W5 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w5` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w5',
                         variables=list('R5PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda5, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda5, echo=TRUE}
HRS_ds_coda_w5 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w5$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w5$proxy <- labelled(HRS_ds_coda_w5$proxy, labels = cat_label)
label(HRS_ds_coda_w5$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=FALSE}
vari <- HRS_ds_coda_w5$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda5, echo=FALSE}
proxy <- HRS_ds_coda_w5
save(proxy, file = "../RData/coda_w5/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 6 

#### Study-specific variable description

| **Name** | `R6PROXY`|
|-|-|
| **Label** | `W6 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w6` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w6',
                         variables=list('R6PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda6, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda6, echo=TRUE}
HRS_ds_coda_w6 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w6$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w6$proxy <- labelled(HRS_ds_coda_w6$proxy, labels = cat_label)
label(HRS_ds_coda_w6$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=FALSE}
vari <- HRS_ds_coda_w6$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda6, echo=FALSE}
proxy <- HRS_ds_coda_w6
save(proxy, file = "../RData/coda_w6/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 7 

#### Study-specific variable description

| **Name** | `R7PROXY`|
|-|-|
| **Label** | `W7 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w7` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w7',
                         variables=list('R7PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda7, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda7, echo=TRUE}
HRS_ds_coda_w7 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w7$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w7$proxy <- labelled(HRS_ds_coda_w7$proxy, labels = cat_label)
label(HRS_ds_coda_w7$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=FALSE}
vari <- HRS_ds_coda_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda7, echo=FALSE}
proxy <- HRS_ds_coda_w7
save(proxy, file = "../RData/coda_w7/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 8 

#### Study-specific variable description

| **Name** | `R8PROXY`|
|-|-|
| **Label** | `W8 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w8',
                         variables=list('R8PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda8, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda8, echo=TRUE}
HRS_ds_coda_w8 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w8$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w8$proxy <- labelled(HRS_ds_coda_w8$proxy, labels = cat_label)
label(HRS_ds_coda_w8$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=FALSE}
vari <- HRS_ds_coda_w8$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda8, echo=FALSE}
proxy <- HRS_ds_coda_w8
save(proxy, file = "../RData/coda_w8/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 9 

#### Study-specific variable description

| **Name** | `R9PROXY`|
|-|-|
| **Label** | `W9 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w9` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w9',
                         variables=list('R9PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda9, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda9, echo=TRUE}
HRS_ds_coda_w9 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w9$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w9$proxy <- labelled(HRS_ds_coda_w9$proxy, labels = cat_label)
label(HRS_ds_coda_w9$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=FALSE}
vari <- HRS_ds_coda_w9$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL_coda9, echo=FALSE}
proxy <- HRS_ds_coda_w9
save(proxy, file = "../RData/coda_w9/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 10 

#### Study-specific variable description

| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda10, echo=TRUE}
HRS_ds_coda_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w10$proxy <- labelled(HRS_ds_coda_w10$proxy, labels = cat_label)
label(HRS_ds_coda_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=FALSE}
vari <- HRS_ds_coda_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda10, echo=FALSE}
proxy <- HRS_ds_coda_w10
save(proxy, file = "../RData/coda_w10/proxy.RData")
rm(proxy)
```






### Wave 11 

#### Study-specific variable description

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-CODA-w11` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_coda11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-CODA-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_coda11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_coda11, echo=TRUE}
HRS_ds_coda_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_coda_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_coda_w11$proxy <- labelled(HRS_ds_coda_w11$proxy, labels = cat_label)
label(HRS_ds_coda_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=FALSE}
vari <- HRS_ds_coda_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_coda11, echo=FALSE}
proxy <- HRS_ds_coda_w11
save(proxy, file = "../RData/coda_w11/proxy.RData")
rm(proxy, HRS_proxy)
```






## The War Baby (WB) sub-sample 

### Wave 4  

#### Study-specific variable description

| **Name** | `R4PROXY`|
|-|-|
| **Label** | `W4 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w4` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w4',
                         variables=list('R4PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb4, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb4, echo=TRUE}
HRS_ds_wb_w4 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w4$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w4$proxy <- labelled(HRS_ds_wb_w4$proxy, labels = cat_label)
label(HRS_ds_wb_w4$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=FALSE}
vari <- HRS_ds_wb_w4$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_wb4, echo=FALSE}
proxy <- HRS_ds_wb_w4
save(proxy, file = "../RData/wb_w4/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 5  

#### Study-specific variable description

 

| **Name** | `R5PROXY`|
|-|-|
| **Label** | `W5 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w5` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w5',
                         variables=list('R5PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb5, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb5, echo=TRUE}
HRS_ds_wb_w5 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w5$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w5$proxy <- labelled(HRS_ds_wb_w5$proxy, labels = cat_label)
label(HRS_ds_wb_w5$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=FALSE}
vari <- HRS_ds_wb_w5$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_wb5, echo=FALSE}
proxy <- HRS_ds_wb_w5
save(proxy, file = "../RData/wb_w5/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 6  

#### Study-specific variable description

| **Name** | `R6PROXY`|
|-|-|
| **Label** | `W6 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w6` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w6',
                         variables=list('R6PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb6, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb6, echo=TRUE}
HRS_ds_wb_w6 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w6$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w6$proxy <- labelled(HRS_ds_wb_w6$proxy, labels = cat_label)
label(HRS_ds_wb_w6$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=FALSE}
vari <- HRS_ds_wb_w6$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_wb6, echo=FALSE}
proxy <- HRS_ds_wb_w6
save(proxy, file = "../RData/wb_w6/proxy.RData")
rm(proxy, HRS_proxy)
```







### Wave 7  

#### Study-specific variable description

| **Name** | `R7PROXY`|
|-|-|
| **Label** | `W7 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w7` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w7',
                         variables=list('R7PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb7, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb7, echo=TRUE}
HRS_ds_wb_w7 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w7$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w7$proxy <- labelled(HRS_ds_wb_w7$proxy, labels = cat_label)
label(HRS_ds_wb_w7$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=FALSE}
vari <- HRS_ds_wb_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 
```{r importOPAL_wb7, echo=FALSE}
proxy <- HRS_ds_wb_w7
save(proxy, file = "../RData/wb_w7/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 8  

#### Study-specific variable description

| **Name** | `HRS_ds_wb_w7`|
|-|-|
| **Label** | `W8 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |


```{r assign_wb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w8',
                         variables=list('HRS_ds_wb_w7'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb8, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb8, echo=TRUE}
HRS_ds_wb_w8 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w8$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w8$proxy <- labelled(HRS_ds_wb_w8$proxy, labels = cat_label)
label(HRS_ds_wb_w8$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=FALSE}
vari <- HRS_ds_wb_w8$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_wb8, echo=FALSE}
proxy <- HRS_ds_wb_w8
save(proxy, file = "../RData/wb_w8/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 9  

#### Study-specific variable description

| **Name** | `R9PROXY`|
|-|-|
| **Label** | `W9 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w9` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w9',
                         variables=list('R9PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb9, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb9, echo=TRUE}
HRS_ds_wb_w9 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w9$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w9$proxy <- labelled(HRS_ds_wb_w9$proxy, labels = cat_label)
label(HRS_ds_wb_w9$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=FALSE}
vari <- HRS_ds_wb_w9$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL_wb9, echo=FALSE}
proxy <- HRS_ds_wb_w9
save(proxy, file = "../RData/wb_w9/proxy.RData")
rm(proxy, HRS_proxy)
```






### Wave 10  

#### Study-specific variable description

| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb10, echo=TRUE}
HRS_ds_wb_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w10$proxy <- labelled(HRS_ds_wb_w10$proxy, labels = cat_label)
label(HRS_ds_wb_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=FALSE}
vari <- HRS_ds_wb_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_wb10, echo=FALSE}
proxy <- HRS_ds_wb_w10
save(proxy, file = "../RData/wb_w10/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 11  

#### Study-specific variable description

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-WB-w11` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_wb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-WB-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_wb11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_wb11, echo=TRUE}
HRS_ds_wb_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_wb_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_wb_w11$proxy <- labelled(HRS_ds_wb_w11$proxy, labels = cat_label)
label(HRS_ds_wb_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=FALSE}
vari <- HRS_ds_wb_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_wb11, echo=FALSE}
proxy <- HRS_ds_wb_w11
save(proxy, file = "../RData/wb_w11/proxy.RData")
rm(proxy, HRS_proxy)
```





## The Early Baby Boomer (EBB) sub-sample

### Wave 7  

#### Study-specific variable description

| **Name** | `R7PROXY`|
|-|-|
| **Label** | `W7 Whether Proxy Interview`|
| **Table name** | `HRS-EBB-w7` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ebb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-EBB-w7',
                         variables=list('R7PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ebb7, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ebb7, echo=TRUE}
HRS_ds_ebb_w7 <- tibble(id=HRS_proxy$id)
HRS_ds_ebb_w7$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ebb_w7$proxy <- labelled(HRS_ds_ebb_w7$proxy, labels = cat_label)
label(HRS_ds_ebb_w7$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=FALSE}
vari <- HRS_ds_ebb_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ebb7, echo=FALSE}
proxy <- HRS_ds_ebb_w7
save(proxy, file = "../RData/ebb_w7/proxy.RData")
rm(proxy, HRS_proxy)
```





### Wave 8  

#### Study-specific variable description

| **Name** | `R8PROXY`|
|-|-|
| **Label** | `W8 Whether Proxy Interview`|
| **Table name** | `HRS-EBB-w8` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ebb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-EBB-w8',
                         variables=list('R8PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ebb8, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ebb8, echo=TRUE}
HRS_ds_ebb_w8 <- tibble(id=HRS_proxy$id)
HRS_ds_ebb_w8$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ebb_w8$proxy <- labelled(HRS_ds_ebb_w8$proxy, labels = cat_label)
label(HRS_ds_ebb_w8$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=FALSE}
vari <- HRS_ds_ebb_w8$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ebb8, echo=FALSE}
proxy <- HRS_ds_ebb_w8
save(proxy, file = "../RData/ebb_w8/proxy.RData")
rm(proxy)
```





### Wave 9  

#### Study-specific variable description

 

| **Name** | `R9PROXY`|
|-|-|
| **Label** | `W9 Whether Proxy Interview`|
| **Table name** | `HRS-EBB-w9` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ebb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-EBB-w9',
                         variables=list('R9PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ebb9, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ebb9, echo=TRUE}
HRS_ds_ebb_w9 <- tibble(id=HRS_proxy$id)
HRS_ds_ebb_w9$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ebb_w9$proxy <- labelled(HRS_ds_ebb_w9$proxy, labels = cat_label)
label(HRS_ds_ebb_w9$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=FALSE}
vari <- HRS_ds_ebb_w9$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ebb9, echo=FALSE}
proxy <- HRS_ds_ebb_w9
save(proxy, file = "../RData/ebb_w9/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 10  

#### Study-specific variable description

| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-EBB-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ebb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-EBB-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ebb10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ebb10, echo=TRUE}
HRS_ds_ebb_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_ebb_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ebb_w10$proxy <- labelled(HRS_ds_ebb_w10$proxy, labels = cat_label)
label(HRS_ds_ebb_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=FALSE}
vari <- HRS_ds_ebb_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_ebb10, echo=FALSE}
proxy <- HRS_ds_ebb_w10
save(proxy, file = "../RData/ebb_w10/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 11  

#### Study-specific variable description

 

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-EBB-w11` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_ebb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-EBB-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_ebb11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_ebb11, echo=TRUE}
HRS_ds_ebb_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_ebb_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_ebb_w11$proxy <- labelled(HRS_ds_ebb_w11$proxy, labels = cat_label)
label(HRS_ds_ebb_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=FALSE}
vari <- HRS_ds_ebb_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


 
```{r importOPAL_ebb11, echo=FALSE}
proxy <- HRS_ds_ebb_w11
save(proxy, file = "../RData/ebb_w11/proxy.RData")
rm(proxy, HRS_proxy)
```




## The Mid Baby Boomer (MBB) sub-sample

### Wave 10  

#### Study-specific variable description

 

| **Name** | `R10PROXY`|
|-|-|
| **Label** | `W10 Whether Proxy Interview`|
| **Table name** | `HRS-MBB-w10` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_mbb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-MBB-w10',
                         variables=list('R10PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_mbb10, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_mbb10, echo=TRUE}
HRS_ds_mbb_w10 <- tibble(id=HRS_proxy$id)
HRS_ds_mbb_w10$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_mbb_w10$proxy <- labelled(HRS_ds_mbb_w10$proxy, labels = cat_label)
label(HRS_ds_mbb_w10$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=FALSE}
vari <- HRS_ds_mbb_w10$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_mbb10, echo=FALSE}
proxy <- HRS_ds_mbb_w10
save(proxy, file = "../RData/mbb_w10/proxy.RData")
rm(proxy, HRS_proxy)
```




### Wave 11  

#### Study-specific variable description

| **Name** | `R11PROXY`|
|-|-|
| **Label** | `W11 Whether Proxy Interview`|
| **Table name** | `HRS-MBB-w11` |
| **Categories** | `0 = not proxy` |
| | `1 = proxy` | 
| | `2 = partial proxy` | 
| | `3 = proxy, R deceased` | 
| **Description** |  |

```{r assign_mbb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_proxy','HRS.HRS-MBB-w11',
                         variables=list('R11PROXY'), missings = TRUE)
HRS_proxy <- opal.execute(o,'HRS_proxy')
```

```{r local_mbb11, echo=FALSE}
vari <- HRS_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "not proxy" as 0`
* `keep "proxy" into 1`
* `recode 2 and 3 into 1`
* `NA into 999`

**R script:**

```{r harmo_mbb11, echo=TRUE}
HRS_ds_mbb_w11 <- tibble(id=HRS_proxy$id)
HRS_ds_mbb_w11$proxy <- car::recode(HRS_proxy[[2]], "2:3=1; NA=999")
HRS_ds_mbb_w11$proxy <- labelled(HRS_ds_mbb_w11$proxy, labels = cat_label)
label(HRS_ds_mbb_w11$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=FALSE}
vari <- HRS_ds_mbb_w11$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_mbb11, echo=FALSE}
proxy <- HRS_ds_mbb_w11
save(proxy, file = "../RData/mbb_w11/proxy.RData")
rm(proxy, HRS_proxy)
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables
# 
# savingRD <- function(l.hds,vbl_name){
#   
#   for(index in seq_along(l.hds)){
#     assign(vbl_name,l.hds[[index]])
#     save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
#   }
# 
# }

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```









# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```