---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 

<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```


# Data process

## HRS

| **Name** |`RAHRSAMP`|`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|-|
| **Label** |`RAHRSAMP: HRS Sample-Age Elig/Hrs92 Resp`|`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-HRS-w1`|`HRS-HRS-w1`|`HRS-HRS-w1`|`HRS-HRS-w1`|
| **Categories** |`0 = Not in Sample`<br/>`1 = In Samp,Hrs92 Resp b.1931-41`|`continuous`|`text`|`text`|
| **Description** |  |  |  |  |



#### Study-specific variable description

```{r assign_hrs, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-HRS-w1',variables=list('PN','RABYEAR','RAHRSAMP','HHID'), missings = T)
HRS <- opal.execute(o,'HRS')

```



```{r local_hrs, echo=FALSE}

vbl <- HRS$RAHRSAMP
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attributes(vbl)$`spss::shortName`)
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = 'Category')
ggplot(HRS, aes(factor(vbl))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

kable(table(HRS$RAHRSAMP,HRS$RABYEAR))
```

#### Harmonisation algorithm

Following the elegibility method specified in the cohort profile:

* `The first respondent in a household among ones verifying RAHRSAMP==1 into 0 participant`
* `If all respondents in a household have RAHRSAMP==0, the first one born from 1931 to 1941 into 0 participant`
* `Otherwise, 1 spouse/partner`

**R script:**

```{r harmo_hrs}

HRS_samp1 <- HRS %>% filter(RAHRSAMP==1) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))
HRS_samp0 <- HRS %>% filter((!HHID %in% HRS_samp1$HHID) & RABYEAR>=1931 & RABYEAR<=1941) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% union(HRS_samp1$fid,HRS_samp0$fid))] <- 0

for(df in 1:11){
  assign(paste0("HRS_ds_hrs_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,HRS_samp1,respondent)


```




#### Statistics of the new harmonised variable
```{r descript_hrs, echo=F}

vbl <- HRS_ds_hrs_w1$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```





## AHEAD


| **Name** |`RAAHDSMP`|`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|-|
| **Label** |`RAAHDSMP: AHEAD Sample-Age Elig/Ahd93 Resp`|`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-AHEAD-w2`|`HRS-AHEAD-w2`|`HRS-AHEAD-w2`|`HRS-AHEAD-w2`|
| **Categories** |`0 = Not in Sample`<br/>`1 = In Sample,Ahd93 Resp b.bef 1924`|`continuous`|`text`|`text`|
| **Description** |  |  |  |  |




```{r assign_ahead, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-AHEAD-w2',variables=list('RAAHDSMP','RABYEAR','HHID','PN'), missings = T)
HRS <- opal.execute(o,'HRS')

```



```{r local_ahead, echo=FALSE}

vbl <- HRS$RAAHDSMP
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attributes(vbl)$`spss::shortName`)
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = 'Category')
ggplot(HRS, aes(factor(vbl))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

kable(table(HRS$RAAHDSMP,HRS$RABYEAR))
```


#### Harmonisation algorithm


Following the elegibility method specified in the cohort profile:

* `The first respondent in a household among ones verifying RAAHDSMP==1 into 0 participant`
* `If all respondents in a household have RAAHDSMP==0, the first one born before 1924 into 0 participant`
* `Otherwise, 1 spouse/partner`


**R script:**

```{r harmo_ahead}

HRS_samp1 <- HRS %>% filter(RAAHDSMP==1) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))
HRS_samp0 <- HRS %>% filter((!HHID %in% HRS_samp1$HHID) & RABYEAR<1924) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% union(HRS_samp1$fid,HRS_samp0$fid))] <- 0

for(df in 2:11){
  assign(paste0("HRS_ds_ahead_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,HRS_samp1,respondent)

```



#### Statistics of the new harmonised variable
```{r descript_ahead, echo=F}

vbl <- HRS_ds_ahead_w2$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## CODA


| **Name** |`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|
| **Label** |`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-CODA-w4`|`HRS-CODA-w4`|`HRS-CODA-w4`|
| **Categories** |`continuous`|`text`|`text`|
| **Description** |  |  |  |


```{r assign_coda, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-CODA-w4',variables=list('RABYEAR','HHID','PN'), missings = T)
HRS <- opal.execute(o,'HRS')

```



```{r local_coda, echo=FALSE}

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


Following the elegibility method specified in the cohort profile:

* `The first respondent in a household born from 1924 to 1930 into 0 participant`
* `Otherwise, 1 spouse/partner`

**R script:**

```{r harmo_coda}

HRS_samp0 <- HRS %>% filter(RABYEAR>=1924 & RABYEAR<=1930) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% HRS_samp0$fid)] <- 0

for(df in 4:11){
  assign(paste0("HRS_ds_coda_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,respondent)

```




#### Statistics of the new harmonised variable
```{r descript_coda, echo=F}

vbl <- HRS_ds_coda_w4$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




## WB


| **Name** |`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|
| **Label** |`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-WB-w4`|`HRS-WB-w4`|`HRS-WB-w4`|
| **Categories** |`continuous`|`text`|`text`|
| **Description** |  |  |  |

```{r assign_wb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-WB-w4',variables=list('RABYEAR','HHID','PN'), missings = T)
HRS <- opal.execute(o,'HRS')

```



```{r local_wb, echo=FALSE}

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


Following the elegibility method specified in the cohort profile:

* `The first respondent in a household born from 1942 to 1947 into 0 participant`
* `Otherwise, 1 spouse/partner`

**R script:**

```{r harmo_wb}

HRS_samp0 <- HRS %>% filter(RABYEAR>=1942 & RABYEAR<=1947) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% HRS_samp0$fid)] <- 0

for(df in 4:11){
  assign(paste0("HRS_ds_wb_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,respondent)


```




#### Statistics of the new harmonised variable
```{r descript_wb, echo=F}

vbl <- HRS_ds_wb_w4$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## EBB


| **Name** |`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|
| **Label** |`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-EBB-w7`|`HRS-EBB-w7`|`HRS-EBB-w7`|
| **Categories** |`continuous`|`text`|`text`|
| **Description** |  |  |  |

```{r assign_ebb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-EBB-w7',variables=list('RABYEAR','HHID','PN'), missings = T)
HRS <- opal.execute(o,'HRS')

```


```{r local_ebb, echo=FALSE}

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


Following the elegibility method specified in the cohort profile:

* `The first respondent in a household born from 1948 to 1953 into 0 participant`
* `Otherwise, 1 spouse/partner`

**R script:**

```{r harmo_ebb}

HRS_samp0 <- HRS %>% filter(RABYEAR>=1948 & RABYEAR<=1953) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% HRS_samp0$fid)] <- 0

for(df in 7:11){
  assign(paste0("HRS_ds_ebb_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,respondent)

```




#### Statistics of the new harmonised variable
```{r descript_ebb, echo=F}

vbl <- HRS_ds_ebb_w7$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```






## MBB


| **Name** |`RABYEAR`|`HHID`|`PN`|
|-|-|-|-|
| **Label** |`RABYEAR: R birth year`|`HHID: HHold ID / 6-Char`|`Person Number (CHAR)`|
| **Table name** |`HRS-MBB-w10`|`HRS-MBB-w10`|`HRS-MBB-w10`|
| **Categories** |`continuous`|`text`|`text`|
| **Description** |  |  |  |

```{r assign_mbb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-MBB-w10',variables=list('RABYEAR','HHID','PN'), missings = T)
HRS <- opal.execute(o,'HRS')

```


```{r local_mbb, echo=FALSE}

vbl <- HRS$RABYEAR
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = 'Summary')
ggplot(HRS, aes(vbl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


Following the elegibility method specified in the cohort profile:

* `The first respondent in a household born from 1954 to 1959 into 0 participant`
* `Otherwise, 1 spouse/partner`

**R script:**

```{r harmo_mbb}

HRS_samp0 <- HRS %>% filter(RABYEAR>=1954 & RABYEAR<=1959) %>% arrange(HHID,PN) %>% group_by(HHID) %>% summarise(fid=first(id))

respondent <- tibble(id=HRS$id)
respondent$respondent <- 1
respondent$respondent[which(HRS$id %in% HRS_samp0$fid)] <- 0

for(df in 10:11){
  assign(paste0("HRS_ds_mbb_w",as.character(df)),respondent)
}

rm(HRS,HRS_samp0,respondent)


```



#### Statistics of the new harmonised variable
```{r descript_mbb, echo=F}

vbl <- HRS_ds_mbb_w10$respondent
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){

  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```










# Quality estimation

From the cohort profile:

> The HRS sample was built up over time. The initial HRS cohort, recruited in 1992, consisted of persons born 1931–41 (then aged 51–61) and their spouses of any age. A second study, Asset and Health Dynamics Among the Oldest Old (AHEAD), was fielded the next year to capture the cohort born 1890–1923 (then aged 70 and above). In 1998, the two studies merged and, in order to make the sample fully representative of the USA population over age 50, two new cohorts were enrolled: the Children of the Depression (CODA), born 1924–30, and the War Babies, born 1942–47. HRS now employs a steady-state design, replenishing the sample every 6 years with younger cohorts not previously represented. In 2004, Early Baby Boomers (EBB, born 1948–53) were added, and in 2010, Mid Baby Boomers (MBB, born 1954–59) were added.

> The HRS sample is based on a multi-stage area probability design involving geographical stratification and clustering and oversampling of certain demographic groups.5 To determine eligibility, a brief household screening interview is conducted with each sampled housing unit. Adults (age 18þ) of the household are listed with their age and coupleness status. A primary respondent is randomly selected from all age-eligible household members and, if the selected person is coupled, their spouse or partner is also included in the sample, regardless of age. To date, household screening efforts have been conducted in 1992, 2004 and 2010.

From the RAND HRS Codebook:

> RAHRSAMP identifies HRS-eligible individuals defined as those who are age-eligible and responded to Wave 1. HRS age-eligible individuals are those born from 1931 to 1941, according to RABDATE. A "1" indicates that the individual is HRS-eligible, and a "0" indicates that s/he is not. The spouses of individuals in this sample may or may not be in the sample as well.

>RAAHDSMP identifies AHEAD-eligible individuals defined as those who are age-eligible and responded to Wave 2A. AHEAD age-eligible individuals are those born prior to 1924, according to RABDATE. A "1" indicates that the individual is AHEAD-eligible, and a "0" indicates that s/he is not. The spouses of individuals in this sample may or may not be in the sample as well.


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





