---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 

<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```


# Data process

## HRS


```{r assign_hrs, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-HRS-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_hrs}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 1:11){
  save(respondent,file = paste0("../RData/hrs_w",as.character(df),"/respondent.RData"))
}

```








## AHEAD



```{r assign_ahead, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-AHEAD-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_ahead}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 2:11){
  save(respondent,file = paste0("../RData/ahead_w",as.character(df),"/respondent.RData"))
}

```





## CODA



```{r assign_coda, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-CODA-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_coda}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 4:11){
  save(respondent,file = paste0("../RData/coda_w",as.character(df),"/respondent.RData"))
}

```






## WB


```{r assign_wb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-WB-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_wb}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 4:11){
  save(respondent,file = paste0("../RData/wb_w",as.character(df),"/respondent.RData"))
}

```





## EBB


```{r assign_ebb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-EBB-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_ebb}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 7:11){
  save(respondent,file = paste0("../RData/ebb_w",as.character(df),"/respondent.RData"))
}

```







## MBB


```{r assign_mbb, echo=F}

opal.assign.table.tibble(o, 'HRS','HRS.HRS-MBB-w11',variables=list('R11VGACTX'), missings = T)
HRS <- opal.execute(o,'HRS')

```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_mbb}

respondent <- tibble(id=HRS$id)
respondent$respondent <- 0
respondent$respondent <- labelled(respondent$respondent, labels = cat_label)
label(respondent$respondent) <- ds_label

for(df in 10:11){
  save(respondent,file = paste0("../RData/mbb_w",as.character(df),"/respondent.RData"))
}

```











# Quality estimation

All spouses are participants, and there is no information specifying a main respondent.





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





