---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ############################################################################# --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################################################# --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `Height of the participant`
* Variable description: `Anthropomeric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Height"
ds_label_all <- "Height of the participant"
```


# Data process
  
## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** | `height`|
|-|-|
| **Label** |  |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `continuous; 145 = <=145; 185 = 185+` |
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_heig','TILDA.TILDA-AMF-v16',
                         variables=list('height'), missings = TRUE)
TILDA_w1_heig <- opal.execute(o,'TILDA_w1_heig')
```

```{r local1, echo=FALSE}
vari <- TILDA_w1_heig$height
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = ds_label)
#kable(Continuous_summary(vari, missing_values = c(145,185))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_heig, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")+xlim(140,190)
```

The variable 'height' is categorized on the extreme values.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `The extreme values are preserved`
* `NA into 999`


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_heig$id)
TILDA_ds_w1$height <- car::recode(TILDA_w1_heig$height, "NA=999")
TILDA_ds_w1$height <- labelled(TILDA_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- TILDA_ds_w1$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(140,190) 
```

#### Validation
```{r crosstabulation1, echo=FALSE}

```

```{r importOPAL1, echo=FALSE}
label(TILDA_ds_w1$height) <- ds_label_all
height <- TILDA_ds_w1
save(height, file = "../RData/w1/height.RData")
#val_labels(TILDA_ds_w1) <- NULL
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description



| **Name** | `ph723`|
|-|-|
| **Label** | `Height of Subjects (cm)` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** | `continuous; 149 = Less than 150; 186 = Greater than 185` |
| **Missings** | `-1 = Not applicable or skipped due to routing patterns` |
| **Description** |  |





```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_heig','TILDA.TILDA-AMF-v23',
                         variables=list('ph723'), missings = TRUE)
TILDA_w2_heig <- opal.execute(o,'TILDA_w2_heig')
```

```{r local2, echo=FALSE}
vari <- TILDA_w2_heig$ph723
kable(Continuous_summary(var = vari, missing_values = c(-1))[3], caption = ds_label)
#kable(Continuous_summary(vari, missing_values = c(-1, 149, 186))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1))$summary, caption = "Summary")
ggplot(TILDA_w2_heig, aes(ph723)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(145, 190)
```

The variable 'ph723' is categorized on the extrem values.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `-1 into 996`


**R script:**

```{r harmo2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_heig$id)
TILDA_ds_w2$height <- car::recode(TILDA_w2_heig$ph723, "NA=999; -1=996")
TILDA_ds_w2$height <- labelled(TILDA_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- TILDA_ds_w2$height
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(145, 190) 
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```

```{r importOPAL2, echo=FALSE}
label(TILDA_ds_w2$height) <- ds_label_all
height <- TILDA_ds_w2
save(height, file = "../RData/w2/height.RData")
#val_labels(TILDA_ds_w2) <- NULL
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation
This variable was categorical (dichotomic) in contrast with all the other studies.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
