---
title: "BMI"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ############################################################################# --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################################################# --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `bmi`
* Variable label: `Body Mass Index calculated as weight (kg)/height(m)^2`
* Variable description: `the BMI variable should be created by dividing weight and heigh variables with the following equation= weight (kg)/height(m)^2`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, include=FALSE}
ds_label <- "bmi"
ds_label_all <- "Body Mass Index calculated as weight (kg)/height(m)^2"
```


# Data process

## Ireland

### Wave 1 

#### Study-specific variable description




| **Name** | `FRbmi`|
|-|-|
| **Label** |  |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `continuous; 18 = <18.5; 36 = [36,40); 40 = [40,45); 45 = >=45` |
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_bmi','TILDA.TILDA-AMF-v16',
                         variables=list('FRbmi'), missings = TRUE)
TILDA_w1_bmi <- opal.execute(o,'TILDA_w1_bmi')
```

```{r local1, echo=FALSE}
vari <- TILDA_w1_bmi$FRbmi
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_bmi, aes(FRbmi)) + geom_histogram(stat="count", width=0.1, fill="steelblue") + xlab("BMI") + ylab("Frequency") 
```

The variable 'weight' is categorized on the extreme values and the intervals [36,40) and [40,45).

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_bmi$id)
TILDA_ds_w1$bmi  <- car::recode(TILDA_w1_bmi$FRbmi, "NA=999")
TILDA_ds_w1$bmi <- labelled(TILDA_ds_w1$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- TILDA_ds_w1$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(bmi)) + geom_histogram(stat="count", width=0.1, fill="steelblue") + xlab("BMI") + ylab("Frequency")+xlim(17,46)
```

#### Validation
It is going to check if weight and heigth values are correct by computing BMI with the formula: weight/height^2. 

```{r crosstabulation1}
opal.assign.table.tibble(o, 'TILDA_w1_whb','TILDA.TILDA-AMF-v16',
                         variables=list('weight', 'height', 'FRbmi'), missings = TRUE)
TILDA_w1_whb <- opal.execute(o,'TILDA_w1_whb')

TILDA_w1_whb$bmi_c <- TILDA_w1_whb$weight/(TILDA_w1_whb$height/100)^2

TILDA_w1_whb$proff <- TILDA_w1_whb$FRbmi - TILDA_w1_whb$bmi_c
pander(summary(TILDA_w1_whb$proff))

kable(head(TILDA_w1_whb[which(TILDA_w1_whb$proff>2 | TILDA_w1_whb$proff<(-2)),]),align = 'c')
```

```{r importOPAL1, echo=FALSE}
label(TILDA_ds_w1$bmi) <- ds_label_all
bmi <- TILDA_ds_w1
save(bmi, file = "../RData/w1/bmi.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$bmi <- car::recode(TILDA_m_ds_w1$bmi, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description



| **Name** | `ph720`|`ph723`|
|-|-|-|
| **Label** | `Weight in kilograms` | `Height of Subjects (cm)` |
| **Table name** | `TILDA-AMF-v23` |`TILDA-AMF-v23` |
| **Categories** | `continuous; 49 = Less than 50; 100 = 100+`|`continuous; 149 = Less than 150; 186 = Greater than 185` |
| **Missings** | `-99 = Refused; -98 = Don't know; -1 = Not applicable or skipped due to routing patterns` | `-1 = Not applicable or skipped due to routing patterns` |
| **Description** |  |




```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_bmi','TILDA.TILDA-AMF-v23',
                         variables=list('ph720', 'ph723'), missings = TRUE)
TILDA_w2_bmi <- opal.execute(o,'TILDA_w2_bmi')
```

```{r local2, echo=FALSE}
vari <- TILDA_w2_bmi$ph720
kable(Continuous_summary(var = vari, missing_values = c(-99, -98, -1 ))[3], caption = 'Weight')
kable(Continuous_summary(vari, missing_values = c(-99, -98, -1 ))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-99, -98, -1 ))$summary, caption = "Summary")
ggplot(TILDA_w2_bmi, aes(ph720)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

vari <- TILDA_w2_bmi$ph723
kable(Continuous_summary(var = vari, missing_values = c( -1 ))[3], caption = 'Height')
#kable(Continuous_summary(vari, missing_values = c(149, 186, -99, -98, -1 ))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1 ))$summary, caption = "Summary")
ggplot(TILDA_w2_bmi, aes(ph723)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(140,200)
```

The variables `ph720` and `ph723` are categorized on the extreme values.

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `recode -99 "Refused" to 997`
* `recode -98 "Don't know" to 998`
* `recode -1 "Not applicable or skipped due to routing patterns" to 996`
* `NA into 999`


**R script:**

```{r harmo2}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
  }
  bmi
}

TILDA_w2_bmi$bmi_c <- compute_bmi(Heigth = TILDA_w2_bmi$ph723, 
                        Weigth = TILDA_w2_bmi$ph720, miss = c(-1), 
                        heigth_m = FALSE)

TILDA_ds_w2 <- tibble(id=TILDA_w2_bmi$id)
TILDA_ds_w2$bmi <- car::recode(TILDA_w2_bmi$bmi_c, "NA=999; -99=997; -98=998; -1=996")
TILDA_ds_w2$bmi <- labelled(TILDA_ds_w2$bmi, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- TILDA_ds_w2$bmi
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(round(bmi,3))) + geom_histogram(stat="count", width=0.1, fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,50)
```

#### Validation
```{r crosstabulation2, echo=FALSE}
```

```{r importOPAL2, echo=FALSE}
label(TILDA_ds_w2$bmi) <- ds_label_all
bmi <- TILDA_ds_w2
save(bmi, file = "../RData/w2/bmi.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$bmi <- car::recode(TILDA_m_ds_w2$bmi, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

# Quality estimation
No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
