---
title: "Hip"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `hip`
* Variable label: `hip circumference of the participant`
* Variable description: `Anthropomeric measure for hip circumference should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



```{r lab, echo=FALSE}
ds_label <- "Hip"
ds_label_all <- "Hip circumference of the participant"
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** | `FRhip`|
|-|-|
| **Label** | `Hip circumference (cm)` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `continuous` |
| **Description** |  |


```{r assign1, echo=FALSE} 
opal.assign.table.tibble(o, 'TILDA_w1_hip','TILDA.TILDA-AMF-v16',
                         variables=list('FRhip'), missings = TRUE)
TILDA_w1_hip <- opal.execute(o,'TILDA_w1_hip')
```

```{r local1, echo=FALSE} 
vari <- TILDA_w1_hip$FRhip
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_hip, aes(FRhip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_hip$id)
TILDA_ds_w1$hip <- car::recode(TILDA_w1_hip$FRhip, "NA=999; lo:30=999")
TILDA_ds_w1$hip <- labelled(TILDA_ds_w1$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE} 
vari <- TILDA_ds_w1$hip
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(50,175)
```

#### Validation
```{r crosstabulation1, echo=FALSE} 
```

```{r importOPAL1, echo=FALSE} 
label(TILDA_ds_w1$hip) <- ds_label_all
hip <- TILDA_ds_w1
save(hip, file = "../RData/w1/hip.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

There is no variable.





#### Quality estimation
No coments.






```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
