---
title: "HDL cholesterol"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hdl_cholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hdl_cholDS.R')
```


# Data process


## Mexico


### Wave 1

Not found


### Wave 2

Not found


### Wave 3 

#### Study-specific variable description

| **Name** | `hdlc_12` |
|-|-|
| **Label** | `High-Density Lipoprotein Cholesterol Lab Results mg/dL` |
| **Table name** | `MHAS_2012_new` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign w3, echo=F }

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new', variables=list('hdlc_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')

```

```{r local w3, echo=F}

vbl <- MHAS_w3$hdlc_12
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "hdlc_12") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_w3, aes(hdlc_12)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `hdl_chol` from the study-specific variable it has to be recoded as follows:

* `do not change the scale`
* `NA into 999`

**R script:**

```{r harmo w3}

MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$hdl_chol <- car::recode(MHAS_w3$hdlc_12, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$hdl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w3,!vbl %in% miss_values_vector), aes(hdl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}
```

```{r importOPAL w3, echo=F}

hdl_chol <- MHAS_ds_w3 
save(hdl_chol, file = paste0(datafolder,"w3/hdl_chol.RData"))
rm(hdl_chol)

```





# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
