---
title: "Hearing a conversation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_conv`
* Variable label: `Difficulty for hearing what is said in a conversation`
* Variable description: `It measures if the participant experiences some difficulty (including total disability) for following a conversation  (i.e., if there is a background noise, or several people talking) or not, using a hearing aid as usual.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description




| **Name** | `DISconverse1`|
|-|-|
| **Label** | `Difficulty following a conversation with 1 person` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |  `1 = None; 2 = Some; 3 = Much/impossible` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_hearing_conv','TILDA.TILDA-AMF-v16', variables=list('DISconverse1'), missings = TRUE)
```

```{r local w1, echo=F}
TILDA_w1_hearing_conv <- opal.execute(o,'TILDA_w1_hearing_conv')
vari <- TILDA_w1_hearing_conv$DISconverse1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "DISconverse1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_hearing_conv, aes(x=factor(DISconverse1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0`


**R script:**
```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_hearing_conv$id)
TILDA_ds_w1$hearing_conv <- car::recode(TILDA_w1_hearing_conv$DISconverse1, "1 = '1';2 = '0';3 = '0' ")
TILDA_ds_w1$hearing_conv <- labelled(TILDA_ds_w1$hearing_conv, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- TILDA_ds_w1$hearing_conv
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_conv")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(hearing_conv))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$hearing_conv)
X<-table(TILDA_w1_hearing_conv$DISconverse1)
BeforeH <- c(sum(X[2:3]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3->0","1->1") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(TILDA_ds_w1$hearing_conv) <- "Difficulty for hearing what is said in a conversation"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
hearing_conv <- TILDA_ds_w1
save(hearing_conv, file = "../RData/w1/hearing_conv.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$hearing_conv <- car::recode(TILDA_m_ds_w1$hearing_conv, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `ph109`|
|-|-|
| **Label** | `Can you follow a conversation with one person (with or without a hearing aid)?` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |  `1 = With no difficulty; 2 = With difficulty or no I cannot` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_hearing_conv','TILDA.TILDA-AMF-v23', variables=list('ph109'), missings = TRUE)
```

```{r local w2, echo=F}
TILDA_w2_hearing_conv <- opal.execute(o,'TILDA_w2_hearing_conv')
vari <- TILDA_w2_hearing_conv$ph109
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ph109")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_hearing_conv, aes(x=factor(ph109))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 


**R script:**
```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_hearing_conv$id)
TILDA_ds_w2$hearing_conv <- car::recode(TILDA_w2_hearing_conv$ph109, "1 = '1';2 = '0'")
TILDA_ds_w2$hearing_conv <- labelled(TILDA_ds_w2$hearing_conv, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- TILDA_ds_w2$hearing_conv
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_conv")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(hearing_conv))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(TILDA_ds_w2$hearing_conv)
X<-table(TILDA_w2_hearing_conv$ph109)
BeforeH <- X[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(TILDA_ds_w2$hearing_conv) <- "Difficulty for hearing what is said in a conversation"
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
hearing_conv <- TILDA_ds_w2
save(hearing_conv, file = "../RData/w2/hearing_conv.RData")

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$hearing_conv <- car::recode(TILDA_m_ds_w2$hearing_conv, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
