---
title: "Eye sight - General vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_gen`
* Variable label: `Eyesight - general vision`
* Variable description: `Difficulties in  eye sight using glasses or corrective lens as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description




| **Name** | `ph102`|
|-|-|
| **Label** | `Is your eyesight (using glasses or contact lens if you use them)` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = poor or register/legally blind`|
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_eye_gen','TILDA.TILDA-AMF-v16', variables=list('ph102'), missings = TRUE)
```

```{r local w1, echo=F}
TILDA_w1_eye_gen <- opal.execute(o,'TILDA_w1_eye_gen')
vari <- TILDA_w1_eye_gen$ph102
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ph102")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_eye_gen, aes(x=factor(ph102))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 


**R script:**
```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_eye_gen$id)
TILDA_ds_w1$eye_gen <- car::recode(TILDA_w1_eye_gen$ph102, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0' ")
TILDA_ds_w1$eye_gen <- labelled(TILDA_ds_w1$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- TILDA_ds_w1$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$eye_gen)
X<-table(TILDA_w1_eye_gen$ph102)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(TILDA_ds_w1$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
eye_gen <- TILDA_ds_w1
save(eye_gen, file = "../RData/w1/eye_gen.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$eye_gen <- car::recode(TILDA_m_ds_w1$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `ph102`|
|-|-|
| **Label** | `Is your eyesight (using glasses or contact lenses if you use them).` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = poor or register/legally blind`|
| **Missings** |`99 = Refusal` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_eye_gen','TILDA.TILDA-AMF-v23', variables=list('ph102'), missings = TRUE)
```

```{r local w2, echo=F}
TILDA_w2_eye_gen <- opal.execute(o,'TILDA_w2_eye_gen')
vari <- TILDA_w2_eye_gen$ph102
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "ph102")
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
ggplot(TILDA_w2_eye_gen, aes(x=factor(ph102))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `99 Refusal into 997` 

**R script:**
```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_eye_gen$id)
TILDA_ds_w2$eye_gen <- car::recode(TILDA_w2_eye_gen$ph102, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';99 = '997' ")
TILDA_ds_w2$eye_gen <- labelled(TILDA_ds_w2$eye_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- TILDA_ds_w2$eye_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(eye_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(TILDA_ds_w2$eye_gen)
X<-table(TILDA_w2_eye_gen$ph102)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","99->997") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(TILDA_ds_w2$eye_gen) <- "Eyesight - general vision"
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
eye_gen <- TILDA_ds_w2
save(eye_gen, file = "../RData/w2/eye_gen.RData")

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$eye_gen <- car::recode(TILDA_m_ds_w2$eye_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
