---
title: "Eye sight - Near vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_near`
* Variable label: `Eyesight - Near vision`
* Variable description: `Difficulties for near vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Ireland



### Wave 1 

#### Study-specific variable description


| **Name** | `ph104`|
|-|-|
| **Label** | `How good is your eyesight for seeing things up close, like reading ordinary newspapers?`|
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor?` |
| **Missings** | `98 = Don't Know` |
| **Description** |  |




```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_eye_near','TILDA.TILDA-AMF-v16', variables=list('ph104'), missings = TRUE)
```

```{r local w1, echo=FALSE}
TILDA_w1_eye_near <- opal.execute(o,'TILDA_w1_eye_near')
vari <- TILDA_w1_eye_near$ph104
kable(Categorical_summary(vari, missing_values = c(98))[3], caption = "ph104")
kable(Categorical_summary(vari, missing_values = c(98))[1], caption = "Category")
ggplot(TILDA_w1_eye_near, aes(x=factor(ph104))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0` 
* `98 Don't know into 998` 

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_eye_near$id)
TILDA_ds_w1$eye_near <- car::recode(TILDA_w1_eye_near$ph104, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';98 = '998' ")
TILDA_ds_w1$eye_near <- labelled(TILDA_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(TILDA_ds_w1$eye_near)
X<-table(TILDA_w1_eye_near$ph104)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","98->998") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- TILDA_ds_w1
save(eye_near, file = "../RData/w1/eye_near.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$eye_near <- car::recode(TILDA_m_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2

Not found.



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
