---
title: "Mobility - Walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_walk`
* Variable label: `Mobility - walking`
* Variable description: `Difficulty for walking by yourself and without using any special equipment`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


```{r lab, echo=FALSE}
ds_label <- "Mobility - walking"
ds_label_all <- "Mobility - walking. Difficulty for walking by yourself and without using any special equipment"
```


## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `fl001_01`|
|-|-|
| **Label** | `Because of a physical or mental health problem, do you have difficulty Walking 100 meters (100 yards).?` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`0 = NOT Walking 100 metres (100 yards); 1 = Walking 100 metres (100 yards)` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_mob_walk','TILDA.TILDA-AMF-v16', variables=list('fl001_01'), missings = TRUE)
TILDA_w1_mob_walk <- opal.execute(o,'TILDA_w1_mob_walk')
```

```{r local w1, echo=F}
vari <- TILDA_w1_mob_walk$fl001_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "fl001_01") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_mob_walk, aes(x=factor(fl001_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_mob_walk$id)
TILDA_ds_w1$mob_walk <- car::recode(TILDA_w1_mob_walk$fl001_01, "0 = 1; 1 = 0; NA=999")
TILDA_ds_w1$mob_walk <- labelled(TILDA_ds_w1$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- TILDA_ds_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$mob_walk)
X<-table(TILDA_w1_mob_walk$fl001_01)
BeforeH <- X[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1")
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$mob_walk) <- ds_label_all
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$mob_walk <- car::recode(TILDA_m_ds_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')

mob_walk <- TILDA_ds_w1
save(mob_walk, file = "../RData/w1/mob_walk.RData")
```



### Wave 2 

#### Study-specific variable description



| **Name** | `fl001_01`|
|-|-|
| **Label** | `Because of a physical or mental health problem, do you have difficulty Walking 100 meters (100 yards).?` |
| **Table name** | `` |
| **Categories** |`0 = NOT Walking 100 metres (100 yards); 1 = Walking 100 metres (100 yards)` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_mob_walk','TILDA.TILDA-AMF-v23', variables=list('fl001_01'), missings = TRUE)
TILDA_w2_mob_walk <- opal.execute(o,'TILDA_w2_mob_walk')
```

```{r local w2, echo=F}
vari <- TILDA_w2_mob_walk$fl001_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "fl001_01") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_mob_walk, aes(x=factor(fl001_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_mob_walk$id)
TILDA_ds_w2$mob_walk <- car::recode(TILDA_w2_mob_walk$fl001_01, "0 = 1; 1 = 0; NA=999")
TILDA_ds_w2$mob_walk <- labelled(TILDA_ds_w2$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- TILDA_ds_w2$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(TILDA_ds_w2$mob_walk)
X<-table(TILDA_w2_mob_walk$fl001_01)
BeforeH <- X[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}
label(TILDA_ds_w2$mob_walk) <- ds_label_all
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$mob_walk <- car::recode(TILDA_m_ds_w2$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')

label(TILDA_ds_w2) <- ds_label_all
mob_walk <- TILDA_ds_w2
save(mob_walk, file = "../RData/w2/mob_walk.RData")
```




# Quality estimation
Units used in this study are  "walking 100 meters" or "100 yards" while in other studies, the units used are 1km, 2km or 0,5 miles.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
