---
title: "Mobility - getting up from sitting down"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_up`
* Variable label: `Difficulty for getting up from sitting down`
* Variable description: `Difficulty for getting up from sitting down`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description




| **Name** | `ph413`|
|-|-|
| **Label** | `When getting up from a chair, do you feel` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`1 = Very steady; 2 = Slightly steady; 3 = Slightly unsteady; 4 = Very unsteady`|
| **Missings** |`98 = Don't know; 99 = Refusal`|
| **Description** |  |

 

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_mob_up','TILDA.TILDA-AMF-v16', variables=list('ph413'), missings = TRUE)
```

```{r local w1, echo=F}
TILDA_w1_mob_up <- opal.execute(o,'TILDA_w1_mob_up')
vari <- TILDA_w1_mob_up$ph413
kable(Categorical_summary(vari, missing_values = c(98,99))[3], caption = "ph413")
kable(Categorical_summary(vari, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1_mob_up, aes(x=factor(ph413))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0` 
* `4 into 0` 
* `99 Refusal into 997` 
* `98 Don't know into 998`  

**R script:**
```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_mob_up$id)
TILDA_ds_w1$mob_up <- car::recode(TILDA_w1_mob_up$ph413, "1 = '1';2 = '0';3 = '0';4 = '0';99 = '997';98 = '998'")
TILDA_ds_w1$mob_up <- labelled(TILDA_ds_w1$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- TILDA_ds_w1$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$mob_up)
X<-table(TILDA_w1_mob_up$ph413)
BeforeH <- c(sum(X[2:4]),X[c(1,6,5)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","99->997","98->998") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(TILDA_ds_w1$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
mob_up <- TILDA_ds_w1
save(mob_up, file = "../RData/w1/mob_up.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$mob_up <- car::recode(TILDA_m_ds_w1$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `ph413`|
|-|-|
| **Label** | `ph413 - When getting up from a chair, do you feel...` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`1 = Very steady; 2 = Slightly steady; 3 = Slightly unsteady; 4 = Very unsteady`|
| **Missings** |`98 = Don't know; 99 = Refusal`|
| **Description** |  |

 

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_mob_up','TILDA.TILDA-AMF-v23', variables=list('ph413'), missings = TRUE)
```

```{r local w2, echo=F}
TILDA_w2_mob_up <- opal.execute(o,'TILDA_w2_mob_up')
vari <- TILDA_w2_mob_up$ph413
kable(Categorical_summary(vari, missing_values = c(98,99))[3], caption = "ph413")
kable(Categorical_summary(vari, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w2_mob_up, aes(x=factor(ph413))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `3 into 0` 
* `4 into 0` 
* `99 Refusal into 997` 
* `98 Don't know into 998` 

**R script:**
```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_mob_up$id)
TILDA_ds_w2$mob_up <- car::recode(TILDA_w2_mob_up$ph413, "1 = '1';2 = '0';3 = '0';4 = '0';99 = '997';98 = '998' ")
TILDA_ds_w2$mob_up <- labelled(TILDA_ds_w2$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- TILDA_ds_w2$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(TILDA_ds_w2$mob_up)
X<-table(TILDA_w2_mob_up$ph413)
BeforeH <- c(sum(X[2:4]),X[c(1,6,5)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","99->997","98->998") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(TILDA_ds_w2$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
mob_up <- TILDA_ds_w2
save(mob_up, file = "../RData/w2/mob_up.RData")

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$mob_up <- car::recode(TILDA_m_ds_w2$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
