---
title: "Mobility - climbing stairs"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mob_climbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mob_climbDS.R')
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `fl001_05`|`fl001_06`|
|-|-|-|
| **Label** | `Because of a physical or mental health problem, do you have difficulty Climbing several flights of stairs without resting?` | `Because of a physical or mental health problem, do you have difficulty Climbing one flight of stairs without resting?` |
| **Table name** | `TILDA-AMF-v16` | `TILDA-AMF-v16` |
| **Categories** |`0 = NOT Climbing several flights of stairs without resting`<br/>`1 = Climbing several flights of stairs without resting` |`0 = NOT Climbing one flight of stairs without resting`<br/>`1 = Climbing one flight of stairs without resting` |
| **Description** |  |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('fl001_05','fl001_06'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1') %>% update_labelled()
```

```{r local w1, echo=F}

vbl <- TILDA_w1$fl001_05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Difficulty climbing several flights of stairs") + ylab("Frequency")

vbl <- TILDA_w1$fl001_06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Difficulty climbing one flight of stairs") + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 0 (or missing) into 1`
* `some 1 into 0`
* `NA into 999`

**R script:**

```{r harmo w1, tidy=FALSE}

TILDA_ds_w1 <- TILDA_w1 %>%
  mutate(mob_climb = case_when(
    fl001_05 == 1 | fl001_06 == 1 ~ 0,
    fl001_05 == 0 | fl001_06 == 0 ~ 1,
    TRUE ~ 999
  )) %>%
  select(id, mob_climb)

```

#### Statistical description of the new harmonised variable

```{r descript w1, echo=F}

vari <- TILDA_ds_w1$mob_climb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(mob_climb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}

```



### Wave 2 

#### Study-specific variable description


| **Name** | `fl001_05`|`fl001_06`|
|-|-|-|
| **Label** | `Because of a physical or mental health problem, do you have difficulty Climbing several flights of stairs without resting?` | `Because of a physical or mental health problem, do you have difficulty Climbing one flight of stairs without resting?` |
| **Table name** | `TILDA-AMF-v23` | `TILDA-AMF-v23` |
| **Categories** |`0 = NOT Climbing several flights of stairs without resting`<br/>`1 = Climbing several flights of stairs without resting` |`0 = NOT Climbing one flight of stairs without resting`<br/>`1 = Climbing one flight of stairs without resting` |
| **Description** |  |  |



```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23', variables=list('fl001_05','fl001_06'), missings = TRUE)
TILDA_w2 <- opal.execute(o,'TILDA_w2') %>% update_labelled()

```

```{r local w2, echo=F}

vbl <- TILDA_w2$fl001_05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Difficulty climbing several flights of stairs") + ylab("Frequency")

vbl <- TILDA_w2$fl001_06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Difficulty climbing one flight of stairs") + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 0 (or missing) into 1`
* `some 1 into 0`
* `NA into 999`

**R script:**

```{r harmo w2, tidy=FALSE}

TILDA_ds_w2 <- TILDA_w2 %>%
  mutate(mob_climb = case_when(
    fl001_05 == 1 | fl001_06 == 1 ~ 0,
    fl001_05 == 0 | fl001_06 == 0 ~ 1,
    TRUE ~ 999
  )) %>%
  select(id, mob_climb)

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vari <- TILDA_ds_w2$mob_climb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(mob_climb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
