---
title: "ADL - Using the toilet"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/adl_toiletDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/adl_toiletDS.R')
```

# Data process
## Ireland
### Wave 1

#### Study-specific variable description

 


| **Name** | `fl002_6`|`DISimpairments`|
|-|-|-|
| **Label** | `Because of a physical or mental health problem, do you have difficulty Using the toilet, including getting up or down` |`Number of physical limitations (from fl001)`\*|
| **Table name** | `TILDA-AMF-v16` | `TILDA-AMF-v16` |
| **Categories** |`0 = NOT`<br/>`1 = YES`|`continuous`|
| **Missings** |`-1 = Not applicable`|`NA`|
| **Description** |  |  |

\* `fl001` has data on mobility related ADLs

```{r assign w1, echo=FALSE}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('fl002_6','DISimpairments'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```


```{r local w1, , echo=FALSE}

vbl <- TILDA_w1$fl002_6
vbl_miss <- c(-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`)
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("difficulty Using the toilet, including getting up or down") + ylab("Frequency")

kable(table(TILDA_w1$fl002_6,TILDA_w1$DISimpairments, useNA = "ifany"), caption = 'Cross data of fl002_6 with DISimpairments')

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable `fl002_6` it has to be recoded as follows:

* `0 into 1` 
* `1 into 0` 
* Since `-1` category coincides with no physical limitations (`DISimpairments = 0`) we recode it as 0.

**R script:**

```{r harmo w1, echo=TRUE, tidy=FALSE}

TILDA_ds_w1 <- TILDA_w1 %>%
  mutate(adl_toilet = case_when(
    fl002_6 == 0 ~ 1,
    fl002_6 == 1 ~ 0,
    DISimpairments == 0 ~ 1,
    TRUE ~ 999
  )) %>%
  select(id, adl_toilet)

```

#### Statistical description of the new harmonised variable

```{r descript w1, echo= FALSE}

vbl <- TILDA_ds_w1$adl_toilet
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
  
```{r crosstabulation w1, echo= FALSE}

```



### Wave 2

Not found



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation

CAPI questionnaire ADL section, first ask about physical/mobility limitations (`fl001`; counted in `DISimpairments`) and if respondents answer to have no difficulties they are not asked on ADL's in `fl002`, assuming they also have no difficulties for these ADL's (`DISadl` is coded as 0 if `DISimpairments` is 0). Thus, we make this assumption too.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
