---
title: "IADL - Difficulties for using telephone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_phone`
* Variable label: `IADL - Difficulties for using telephone`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## Ireland
### Wave 1

#### Study-specific variable description

 


| **Name** | `fl025_4`|
|-|-|
| **Label** | `Because of a health or memory problem, do you have difficulty doing any of these activities? Making phone calls` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`0 = NOT Making telephone calls; 1 = Making telephone calls`|
| **Description** |  |




```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_iadl_phone','TILDA.TILDA-AMF-v16', variables=list('fl025_4'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
TILDA_w1_iadl_phone <- opal.execute(o,'TILDA_w1_iadl_phone')
vari <- TILDA_w1_iadl_phone$fl025_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(TILDA_w1_iadl_phone$fl025_4)
ggplot(TILDA_w1_iadl_phone, aes(x=factor(fl025_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 

**R script:** 
```{r harmo w1,   echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_iadl_phone$id)
TILDA_ds_w1$iadl_phone <- car::recode(TILDA_w1_iadl_phone$fl025_4, "0 = '1';1 = '0' ")
TILDA_ds_w1$iadl_phone <- labelled(TILDA_ds_w1$iadl_phone, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- TILDA_ds_w1$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(TILDA_ds_w1$iadl_phone)
X<-table(TILDA_w1_iadl_phone$fl025_4)
BeforeH <- X[c(2:1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1") 
kable(C)
```


```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(TILDA_ds_w1) <- NULL
label(TILDA_ds_w1$iadl_phone) <- "Difficulties for using telephone"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$iadl_phone <- car::recode(TILDA_m_ds_w1$iadl_phone, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_phone <- TILDA_ds_w1
save(iadl_phone, file = paste0(datafolder, "/w1/iadl_phone.RData"))
```


### Wave 2
Not found.


# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
