---
title: "Cognition - Immediate recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_imm_c`
* Variable label: `Cognition - Immediate recall - Continuous`
* Variable description: `Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable.`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_imm`
* Variable label: `Cognition - Immediate recall`
* Variable description: `Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Immediate recall"
ds_label_cog_imm_c <- "Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_imm <- "Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `COGimmediaterecall1`|
|-|-|
| **Label** | `Immediate recall 1` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`Continuous Variable 0-10`|
| **Missings** | `NA` |
| **Description** |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_cog_imm','TILDA.TILDA-AMF-v16', variables=list('COGimmediaterecall1'), missings = TRUE)
TILDA_w1_cog_imm <- opal.execute(o,'TILDA_w1_cog_imm')
```

```{r local w1, echo=FALSE}
vari <- TILDA_w1_cog_imm$COGimmediaterecall1
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_cog_imm, aes(x=factor(COGimmediaterecall1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

**R script**

```{r harmo w1}
##cog_imm_c
TILDA_ds_w1 <- tibble(id=TILDA_w1_cog_imm$id)
TILDA_ds_w1$cog_imm_c <- car::recode(TILDA_w1_cog_imm$COGimmediaterecall1, "NA = 999")
TILDA_ds_w1$cog_imm_c <- labelled(TILDA_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(TILDA_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w1$cog_imm <- car::recode(TILDA_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
TILDA_ds_w1$cog_imm <- labelled(TILDA_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- TILDA_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(TILDA_ds_w1[[2]])<=Q), sum(na.omit(TILDA_ds_w1[[2]])>Q & na.omit(TILDA_ds_w1[[2]])<900), sum(na.omit(TILDA_ds_w1[[2]])==999))
Dicotomic <- table(TILDA_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:5->0","6:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$cog_imm_c) <- ds_label_cog_imm_c
label(TILDA_ds_w1$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
cog_imm <- TILDA_ds_w1
save(cog_imm, file = "../RData/w1/cog_imm.RData")
rm(cog_imm)

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$cog_imm <- car::recode(TILDA_m_ds_w1$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
TILDA_m_ds_w1$cog_imm_c <- car::recode(TILDA_m_ds_w1$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


| **Name** | `ph116`|`ph117`| `ph119`|
|-|-|-|-|
| **Label** | `Interviewer will read the list instead of the computer` | `Now please tell me all the words you can recall. Number of words the respondent correctly recalls (1st read by computer)`| `Now please tell me all the words you can recall. Number of words the respondent correctly recalls (1st read by interviewer)`|
| **Table name** | `TILDA-AMF-v23` |`TILDA-AMF-v23` |`TILDA-AMF-v23` |
| **Categories** |`1 = List read out by computer; 2 = List read out by interviewer`|`Continuous Variable 0-10`|`Continuous Variable 0-10`|
| **Missings** |  | `-1 = Not applicable; 100 = Task not done`| `-1 = Not applicable; 100 = Task not done`|
| **Description** |  |  |  |

   
   

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_cog_imm','TILDA.TILDA-AMF-v23', variables=list('ph116','ph117','ph119'), missings = TRUE)
TILDA_w2_cog_imm <- opal.execute(o,'TILDA_w2_cog_imm')
```

```{r local w2, echo=FALSE}
vari <- TILDA_w2_cog_imm$ph116
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_cog_imm, aes(x=factor(ph116))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- TILDA_w2_cog_imm$ph117
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_imm, aes(x=factor(ph117))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")

vari <- TILDA_w2_cog_imm$ph119
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_imm, aes(x=factor(ph119))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variable the missing values have to be recoded as follows:

* `100 Task not done into 994` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`

**R script**

```{r harmo w2}
##cog_imm_c
TILDA_ds_w2 <- tibble(id=TILDA_w2_cog_imm$id)
TILDA_ds_w2$cog_imm_c <- rep(0,length(TILDA_w2_cog_imm$id))
for(i in 1:length(TILDA_w2_cog_imm$id))
{
  if(TILDA_w2_cog_imm$ph116[i]==1)
    TILDA_ds_w2$cog_imm_c[i]<-TILDA_w2_cog_imm$ph117[i]
  else
    TILDA_ds_w2$cog_imm_c[i]<-TILDA_w2_cog_imm$ph119[i]
}
TILDA_ds_w2$cog_imm_c <- car::recode(TILDA_ds_w2$cog_imm_c, "100 = 994; -1 = 996")
TILDA_ds_w2$cog_imm_c <- labelled(TILDA_ds_w2$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(TILDA_ds_w2$cog_imm_c, "999=NA; 994=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w2$cog_imm <- car::recode(TILDA_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
TILDA_ds_w2$cog_imm <- labelled(TILDA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- TILDA_ds_w2$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- TILDA_ds_w2$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(TILDA_ds_w2[[2]])<=Q), sum(na.omit(TILDA_ds_w2[[2]])>Q & na.omit(TILDA_ds_w2[[2]])<900), sum(na.omit(TILDA_ds_w2[[2]])==994))
Dicotomic <- table(TILDA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:5->0","6:10->1","100->994") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w2, echo=FALSE}
label(TILDA_ds_w2$cog_imm_c) <- ds_label_cog_imm_c
label(TILDA_ds_w2$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
cog_imm <- TILDA_ds_w2
save(cog_imm, file = "../RData/w2/cog_imm.RData")
rm(cog_imm)

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$cog_imm <- car::recode(TILDA_m_ds_w2$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
TILDA_m_ds_w2$cog_imm <- car::recode(TILDA_m_ds_w2$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```





# Quality estimation
[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

No comments

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
