---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Orientation in time"
cat_label <- c("Yes" = 0, "No" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `ph121` |`ph122`|`ph123`|`ph124`|
|-|-|-|-|-|
| **Label** | `Please tell me what year it is`|`What month it is?`|`Can you tell me what day of the week it is?`|`Can you tell me what today's date is?`|
| **Table name**  | `TILDA-AMF-v16`| `TILDA-AMF-v16`| `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** | `1 = Year given correctly`<br/>`2 = Year given incorrectly` | `1 = Month given correctly`<br/>`2 = Month given incorrectly` | `1 = Day of week given correctly`<br/>`2 = Day of week given incorrectly` | `1 = Date given correctly`<br/>`2 = Date given incorrectly` |
| **Missings** | `98 = Don't know`<br/>`99 = Refused` |`98 = Don't know`<br/>`99 = Refused` |`98 = Don't know`<br/>`99 = Refused` |`98 = Don't know`<br/>`99 = Refused` |
| **Description** |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('ph121','ph122','ph123','ph124'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$ph121
kable(Categorical_summary(vbl, missing_values = c(98,99))[3], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph121))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph122
kable(Categorical_summary(vbl, missing_values = c(98,99))[3], caption = names(TILDA_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph123
kable(Categorical_summary(vbl, missing_values = c(98,99))[3], caption = names(TILDA_w1)[4])
kable(Categorical_summary(vbl, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph123))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$ph124
kable(Categorical_summary(vbl, missing_values = c(98,99))[3], caption = names(TILDA_w1)[5])
kable(Categorical_summary(vbl, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(ph124))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `orientation` from the study-specific variable it has to be recoded as follows:

* `all 1  into 1`
* `some 2 into 0`
* `some 98 and no 2 into 998`
* `some 99 and no 2 into 997`

**R script:**

```{r harmo w1}

TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$orientation <-rep(999,length(TILDA_w1$id))
TILDA_ds_w1$orientation[which(TILDA_w1$ph121==1 & TILDA_w1$ph122==1 & TILDA_w1$ph123==1 & TILDA_w1$ph124==1)] <- 1
TILDA_ds_w1$orientation[which(TILDA_w1$ph121==98 | TILDA_w1$ph122==98 | TILDA_w1$ph123==98 | TILDA_w1$ph124==98)] <- 998
TILDA_ds_w1$orientation[which(TILDA_w1$ph121==99 | TILDA_w1$ph122==99 | TILDA_w1$ph123==99 | TILDA_w1$ph124==99)] <- 997
TILDA_ds_w1$orientation[which(TILDA_w1$ph121==2 | TILDA_w1$ph122==2 | TILDA_w1$ph123==2 | TILDA_w1$ph124==2)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$orientation
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$orientation)
BeforeH <- c(
  sum(TILDA_w1$ph121==2 | TILDA_w1$ph122==2 | TILDA_w1$ph123==2 | TILDA_w1$ph124==2,na.rm=T),
  sum(TILDA_w1$ph121==1 & TILDA_w1$ph122==1 & TILDA_w1$ph123==1 & TILDA_w1$ph124==1,na.rm=T),
  sum(TILDA_w1$ph121==99 | TILDA_w1$ph122==99 | TILDA_w1$ph123==99 | TILDA_w1$ph124==99,na.rm=T),
  sum((TILDA_w1$ph121==98 | TILDA_w1$ph122==98 | TILDA_w1$ph123==98 | TILDA_w1$ph124==98) & !(TILDA_w1$ph121==2 | TILDA_w1$ph122==2 | TILDA_w1$ph123==2 | TILDA_w1$ph124==2),na.rm=T)
)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","some 99 and no 2->997","some 98 and no 2->998")
kable(C)

```



### Wave 2


#### Study-specific variable description



| **Name** | `ph121` |`ph122`|`ph123`|`ph124`|`ph126`|
|-|-|-|-|-|-|
| **Label** | `Please tell me what year it is`|`What month it is?`|`Can you tell me what day of the week it is?`|`Can you tell me what today's date is?`|`What season it is.`|
| **Table name**  | `TILDA-AMF-v23`| `TILDA-AMF-v23`| `TILDA-AMF-v23`| `TILDA-AMF-v23`| `TILDA-AMF-v23`|
| **Categories** | `1 = Year given correctly`<br/>`0 = Year given incorrectly` | `1 = Month given correctly`<br/>`0 = Month given incorrectly` | `1 = Day of week given correctly`<br/>`0 = Day of week given incorrectly` | `1 = Date given correctly`<br/>`0 = Date given incorrectly` | `1 = Season  given correctly`<br/>`0 = Season  given incorrectly` |
| **Missings** | `100 = Task not done` |`100 = Task not done` |`100 = Task not done` |`100 = Task not done` |`100 = Task not done`|
| **Description** |  |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23',variables=list('ph121','ph122','ph123','ph124','ph126'), missings = T)
TILDA_w2 <- opal.execute(o,'TILDA_w2')

```

```{r local w2, echo=F}

vbl <- TILDA_w2$ph121
kable(Categorical_summary(vbl, missing_values = c(100))[3], caption = names(TILDA_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(100))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph121))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$ph122
kable(Categorical_summary(vbl, missing_values = c(100))[3], caption = names(TILDA_w2)[4])
kable(Categorical_summary(vbl, missing_values = c(100))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$ph123
kable(Categorical_summary(vbl, missing_values = c(100))[3], caption = names(TILDA_w2)[5])
kable(Categorical_summary(vbl, missing_values = c(100))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph123))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$ph124
kable(Categorical_summary(vbl, missing_values = c(100))[3], caption = names(TILDA_w2)[6])
kable(Categorical_summary(vbl, missing_values = c(100))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph124))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w2$ph126
kable(Categorical_summary(vbl, missing_values = c(100))[3], caption = names(TILDA_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(100))[1], caption = "Category")
ggplot(TILDA_w2, aes(x=factor(ph126))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `orientation` from the study-specific variable it has to be recoded as follows:

* `all 1  into 1`
* `some 0 into 0`
* `some 100 into 994`

**R script:**

```{r harmo w2}

TILDA_ds_w2 <- tibble(id=TILDA_w2$id)
TILDA_ds_w2$orientation <-rep(999,length(TILDA_w2$id))
TILDA_ds_w2$orientation[which(TILDA_w2$ph121==1 & TILDA_w2$ph122==1 & TILDA_w2$ph123==1 & TILDA_w2$ph124==1 & TILDA_w2$ph126==1)] <- 1
TILDA_ds_w2$orientation[which(TILDA_w2$ph121==100 | TILDA_w2$ph122==100 | TILDA_w2$ph123==100 | TILDA_w2$ph124==100 | TILDA_w2$ph126==100)] <- 994
TILDA_ds_w2$orientation[which(TILDA_w2$ph121==0 | TILDA_w2$ph122==0 | TILDA_w2$ph123==0 | TILDA_w2$ph124==0 | TILDA_w2$ph126==0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- TILDA_ds_w2$orientation
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}
AfterH <- table(TILDA_ds_w2$orientation)
BeforeH <- c(
  sum(TILDA_w2$ph121==0 | TILDA_w2$ph122==0 | TILDA_w2$ph123==0 | TILDA_w2$ph124==0 | TILDA_w2$ph126==0,na.rm=T),
  sum(TILDA_w2$ph121==1 & TILDA_w2$ph122==1 & TILDA_w2$ph123==1 & TILDA_w2$ph124==1 & TILDA_w2$ph126==1,na.rm=T),
  sum((TILDA_w2$ph121==100 | TILDA_w2$ph122==100 | TILDA_w2$ph123==100 | TILDA_w2$ph124==100 | TILDA_w2$ph126==100) & !(TILDA_w2$ph121==0 | TILDA_w2$ph122==0 | TILDA_w2$ph123==0 | TILDA_w2$ph124==0 | TILDA_w2$ph126==0),na.rm=T)
)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","some 100 and no 2->994")
kable(C)

```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$orientation <- labelled(TILDA_ds_w1$orientation, labels = cat_label)
label(TILDA_ds_w1$orientation) <- ds_label
TILDA_ds_w2$orientation <- labelled(TILDA_ds_w2$orientation, labels = cat_label)
label(TILDA_ds_w2$orientation) <- ds_label

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$orientation <- car::recode(TILDA_m_ds_w1$orientation, "miss_values_vector=NA")
TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$orientation <- car::recode(TILDA_m_ds_w2$orientation, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$orientation)[[1]][,c(1:2,4)]
tt[4] <- frq(TILDA_ds_w2$orientation)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(TILDA_ds_w1$orientation), length(TILDA_ds_w2$orientation)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(TILDA_m_ds_w1, TILDA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1, w2 = TILDA_ds_w2)

for(index in seq_along(l.TILDA)){
  orientation <- l.TILDA[[index]]
  save(orientation, file = paste0(datafolder,names(l.TILDA)[index],"/orientation.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





