---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_delDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_delDS.R')
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `ph116`|`ph712`| `ph713`|
|-|-|-|-|
| **Label** | `list yourself` | `A little while ago, the computer read you a list of words twice, and you repe…`| `A little while ago, I read you a list of words twice, and you repeated the ones`|
| **Table name** | `TILDA-AMF-v16` |`TILDA-AMF-v16` |`TILDA-AMF-v16` |
| **Categories** |`1 = List read out by computer`<br/>`2 = List read out by interviewer`|`Continuous Variable 0-10`|`Continuous Variable 0-10`|
| **Missings** |  | `-99 = Refused`<br/>`-98 = Don't know`|`-99 = Refused`<br/>`-98 = Don't know`|
| **Description** |  |  |  |


```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_cog_del','TILDA.TILDA-AMF-v16', variables=list('ph116','ph712','ph713'), missings = TRUE)
TILDA_w1_cog_del <- opal.execute(o,'TILDA_w1_cog_del')
```

```{r local w1, echo=FALSE}
vari <- TILDA_w1_cog_del$ph116
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ph116")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- TILDA_w1_cog_del$ph712
vbl_miss <- c(-99,-98)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = "ph712")
kable(Continuous_summary(vari, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(TILDA_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- TILDA_w1_cog_del$ph713
vbl_miss <- c(-99,-98)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = "ph713")
kable(Continuous_summary(vari, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(TILDA_w1_cog_del, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_del_c` from the study-specific variable the missing values have to be recoded as follows:

* `-98 into 0`
* `-99 into 997`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w1}
##cog_del_c
TILDA_ds_w1 <- tibble(id=TILDA_w1_cog_del$id)
TILDA_w1_cog_del <- TILDA_w1_cog_del %>% 
  mutate(cog_del_c = case_when(ph116 == 1 ~ as.integer(ph712),ph116 == 2 ~ as.integer(ph713)))
TILDA_ds_w1$cog_del_c <- car::recode(TILDA_w1_cog_del$cog_del_c, "-98 = 0; -99 = 997")

##cog_del
Q <- quantile(car::recode(TILDA_ds_w1$cog_del_c, "miss_values_vector=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w1$cog_del <- car::recode(TILDA_ds_w1[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- TILDA_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
continuous <- c(sum(na.omit(TILDA_ds_w1[[2]])<=Q), sum(na.omit(TILDA_ds_w1[[2]])>Q&na.omit(TILDA_ds_w1[[2]])<900), sum(na.omit(TILDA_ds_w1[[2]])==997))
dichotomous <- table(TILDA_ds_w1[[3]], useNA = "ifany")
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0:4->0","5:20->1", "-99->997") 
kable(C, caption = "Continuous vs Dichotomous")
```





### Wave 2

#### Study-specific variable description


| **Name** | `ph116`|`ph712`| `ph713`|
|-|-|-|-|
| **Label** | `list yourself` | `A little while ago, the computer read you a list of words twice...`| `A little while ago, I read you a list of words twice...`|
| **Table name** | `TILDA-AMF-v23` |`TILDA-AMF-v23` |`TILDA-AMF-v23` |
| **Categories** |`1 = List read out by computer`<br/>`2 = List read out by interviewer`|`Continuous Variable 0-10`|`Continuous Variable 0-10`|
| **Missings** |  | `-1 = Not applicable`<br/>`100 = Task not done`| `-1 = Not applicable`<br/>`100 = Task not done`|
| **Description** |  |  |  |




```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_cog_del','TILDA.TILDA-AMF-v23', variables=list('ph712','ph713','ph116'), missings = TRUE)
TILDA_w2_cog_del <- opal.execute(o,'TILDA_w2_cog_del')
```

```{r local w2, echo=FALSE}
vari <- TILDA_w2_cog_del$ph116
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ph116") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph116))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


vari <- TILDA_w2_cog_del$ph712
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "ph712")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph712))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- TILDA_w2_cog_del$ph713
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "ph713")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph713))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `100 Task not done into 994` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w2}
##cog_del_c
TILDA_ds_w2 <- tibble(id=TILDA_w2_cog_del$id)
TILDA_w2_cog_del <- TILDA_w2_cog_del %>% 
  mutate(cog_del_c = case_when(ph116 == 1 ~ as.integer(ph712),ph116 == 2 ~ as.integer(ph713)))

TILDA_ds_w2$cog_del_c <- car::recode(TILDA_w2_cog_del$cog_del_c, "100 = 994; -1 = 996")

##cog_del
Q <- quantile(car::recode(TILDA_ds_w2$cog_del_c, "999=NA; 994=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w2$cog_del <- car::recode(TILDA_ds_w2[[2]], "0:Q=0; (Q+1):10=1")

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- TILDA_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w2 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- TILDA_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
continuous <- c(sum(na.omit(TILDA_ds_w2[[2]])<=Q), sum(na.omit(TILDA_ds_w2[[2]])>Q&na.omit(TILDA_ds_w2[[2]])<900), sum(na.omit(TILDA_ds_w2[[2]])==994))
dichotomous <- table(TILDA_ds_w2[[3]], useNA = "ifany")
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0:4->0","5:20->1", "100->994") 
kable(C, caption = "Continuous vs Dichotomous")
```






## Descriptive statistics of the harmonised variable `cog_del` accross populations and waves







<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name=hd_vbl,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

tildalist <- lmlist # TILDA list




```



<!--Descriptives-->



Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(hd_vbl %in% names(get0(paste0("TILDA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- tildalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- tildalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `cog_del_c` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("TILDA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- tildalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- tildalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}





```



# Quality estimation


No comments


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

