---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del_c`
* Variable label: `Cognition - delayed recall - Continuous`
* Variable description: `Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Delayed recall"
ds_label_cog_del_c <- "Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_del <- "Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** | `COGdelayedrecall`|
|-|-|
| **Label** | `Delayed recall` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`Continuous Variable 0-10`|
| **Missings** | `NA` |
| **Description** |  |


```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_cog_del','TILDA.TILDA-AMF-v16', variables=list('COGdelayedrecall'), missings = TRUE)
TILDA_w1_cog_del <- opal.execute(o,'TILDA_w1_cog_del')
```

```{r local w1, echo=FALSE}
vari <- TILDA_w1_cog_del$COGdelayedrecall
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Delayed recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_cog_del, aes(x=factor(COGdelayedrecall))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w1}
##cog_del_c
TILDA_ds_w1 <- tibble(id=TILDA_w1_cog_del$id)
TILDA_ds_w1$cog_del_c <- car::recode(TILDA_w1_cog_del$COGdelayedrecall, "NA = 999")
TILDA_ds_w1$cog_del_c <- labelled(TILDA_ds_w1$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995, Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(TILDA_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w1$cog_del <- car::recode(TILDA_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
TILDA_ds_w1$cog_del <- labelled(TILDA_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995, "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("cog_del") + ylab("Frequency")

vari <- TILDA_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall categorical") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(TILDA_ds_w1[[2]])<=Q), sum(na.omit(TILDA_ds_w1[[2]])>Q&na.omit(TILDA_ds_w1[[2]])<900), sum(na.omit(TILDA_ds_w1[[2]])==999))
Dicotomic <- table(TILDA_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:20->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(TILDA_ds_w1$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
cog_del <- TILDA_ds_w1
save(cog_del, file = "../RData/w1/cog_del.RData")
rm(cog_del)

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$cog_del <- car::recode(TILDA_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
TILDA_m_ds_w1$cog_del_c <- car::recode(TILDA_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


| **Name** | `ph116`|`ph712`| `ph713`|
|-|-|-|-|
| **Label** | `list yourself` | `A little while ago, the computer read you a list of words twice...`| `A little while ago, I read you a list of words twice...`|
| **Table name** | `TILDA-AMF-v23` |`TILDA-AMF-v23` |`TILDA-AMF-v23` |
| **Categories** |`1 = List read out by computer; 2 = List read out by interviewer`|`Continuous Variable 0-10`|`Continuous Variable 0-10`|
| **Missings** |  | `-1 = Not applicable; 100 = Task not done`| `-1 = Not applicable; 100 = Task not done`|
| **Description** |  |  |  |




```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_cog_del','TILDA.TILDA-AMF-v23', variables=list('ph712','ph713','ph116'), missings = TRUE)
TILDA_w2_cog_del <- opal.execute(o,'TILDA_w2_cog_del')
```

```{r local w2, echo=FALSE}
vari <- TILDA_w2_cog_del$ph116
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Delayed recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph116))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")


vari <- TILDA_w2_cog_del$ph712
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph712))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")

vari <- TILDA_w2_cog_del$ph713
kable(Continuous_summary(var = vari, missing_values = c(-1,100))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(-1,100))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,100))$summary, caption = "Summary")
ggplot(TILDA_w2_cog_del, aes(x=factor(ph713))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `100 Task not done into 994` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w2}
##cog_del_c
TILDA_ds_w2 <- tibble(id=TILDA_w2_cog_del$id)
TILDA_ds_w2$cog_del_c <- rep(NA,length(TILDA_ds_w2$id))

for(i in 1:length(TILDA_w2_cog_del$id))
{
  if(TILDA_w2_cog_del$ph116[i]==1)
    TILDA_ds_w2$cog_del_c[i]<-TILDA_w2_cog_del$ph712[i]
  else
    TILDA_ds_w2$cog_del_c[i]<-TILDA_w2_cog_del$ph713[i]
}



TILDA_ds_w2$cog_del_c <- car::recode(TILDA_ds_w2$cog_del_c, "100=994; -1=996")
TILDA_ds_w2$cog_del_c <- labelled(TILDA_ds_w2$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995, Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(TILDA_ds_w2$cog_del_c, "999=NA; 994=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w2$cog_del <- car::recode(TILDA_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
TILDA_ds_w2$cog_del <- labelled(TILDA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995, "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- TILDA_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("cog_del") + ylab("Frequency")

vari <- TILDA_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall categorical") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(TILDA_ds_w2[[2]])<=Q), sum(na.omit(TILDA_ds_w2[[2]])>Q&na.omit(TILDA_ds_w2[[2]])<900), sum(na.omit(TILDA_ds_w2[[2]])==994))
Dicotomic <- table(TILDA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:20->1", "100->994") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w2, echo=FALSE}
label(TILDA_ds_w2$cog_del_c) <- ds_label_cog_del_c
label(TILDA_ds_w2$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')
cog_del <- TILDA_ds_w2
save(cog_del, file = "../RData/w2/cog_del.RData")
rm(cog_del)

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$cog_del <- car::recode(TILDA_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
TILDA_m_ds_w2$cog_del_c <- car::recode(TILDA_m_ds_w2$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

No comments


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

