---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `ph001`|
|-|-|
| **Label** | `Now I would like to ask you some questions about your health.  Would you say?` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Missings** | `98 = Don't know` |
| **Description** |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_srh','TILDA.TILDA-AMF-v16', variables=list('ph001'), missings = TRUE)
TILDA_w1_srh <- opal.execute(o,'TILDA_w1_srh')
```

```{r local w1, echo=FALSE}
vari <- TILDA_w1_srh$ph001
kable(Categorical_summary(vari, missing_values = c(98))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(98))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(98))[2], caption = "Type of missing")
ggplot(TILDA_w1_srh, aes(x=factor(ph001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `98 Don't know into 998`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_srh$id)
TILDA_ds_w1$srh <- car::recode(TILDA_w1_srh$ph001, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';98 = '998' ")
TILDA_ds_w1$srh <- labelled(TILDA_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(TILDA_ds_w1$srh)
X<-table(TILDA_w1_srh$ph001)
BeforeH <- c(sum(X[c(1:3)]),X[c(4,5,6)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","98->998") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- TILDA_ds_w1
save(srh, file = "../RData/w1/srh.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$srh <- car::recode(TILDA_m_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `ph001`|
|-|-|
| **Label** | `ph001 - Now I would like to ask you some questions about your health.  Would you say?` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Description** |  |

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_srh','TILDA.TILDA-AMF-v23', variables=list('ph001'), missings = TRUE)
TILDA_w2_srh <- opal.execute(o,'TILDA_w2_srh')
```

```{r local w2, echo=FALSE}
vari <- TILDA_w2_srh$ph001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w2_srh, aes(x=factor(ph001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`

**R script:**

```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_srh$id)
TILDA_ds_w2$srh <- car::recode(TILDA_w2_srh$ph001, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3' ")
TILDA_ds_w2$srh <- labelled(TILDA_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- TILDA_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(TILDA_ds_w2$srh)
X<-table(TILDA_w2_srh$ph001)
BeforeH <- c(sum(X[c(1:3)]),X[c(4,5)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(TILDA_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- TILDA_ds_w2
save(srh, file = "../RData/w2/srh.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$srh <- car::recode(TILDA_m_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
