---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## Ireland

### Wave 1

#### Study-specific variable description




| **Name** | `ph401`|
|-|-|
| **Label** | `Have you fallen in the last year?` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`1 = Yes; 5 = No`|
| **Missings** | `98 = Don't know` |
| **Description** |  |




```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_recent_falls','TILDA.TILDA-AMF-v16', variables=list('ph401'), missings = TRUE)
TILDA_w1_recent_falls <- opal.execute(o,'TILDA_w1_recent_falls')
```

```{r local w1, echo=FALSE}
vari <- TILDA_w1_recent_falls$ph401
kable(Categorical_summary(vari, missing_values = c(98))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(98))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(98))[2], caption = "Type of missing")
ggplot(TILDA_w1_recent_falls, aes(x=factor(ph401))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `98 Don't know into 998`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_recent_falls$id)
TILDA_ds_w1$recent_falls <- car::recode(TILDA_w1_recent_falls$ph401, "5 = '0';98 = '998' ")
TILDA_ds_w1$recent_falls <- labelled(TILDA_ds_w1$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- TILDA_ds_w1$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(TILDA_ds_w1$recent_falls)
X<-table(TILDA_w1_recent_falls$ph401)
BeforeH <- X[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1","98->998") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- TILDA_ds_w1
save(recent_falls, file = "../RData/w1/recent_falls.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$recent_falls <- car::recode(TILDA_m_ds_w1$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description



| **Name** | `ph401`|
|-|-|
| **Label** | `Have you fallen in the last year?` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`1 = Yes; 5 = No`|
| **Missings** | `98 = Don't know` |
| **Description** |  |


```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w2_recent_falls','TILDA.TILDA-AMF-v23', variables=list('ph401'), missings = TRUE)
TILDA_w2_recent_falls <- opal.execute(o,'TILDA_w2_recent_falls')
```

```{r local w2, echo=FALSE}
vari <- TILDA_w2_recent_falls$ph401
kable(Categorical_summary(vari, missing_values = c(98))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(98))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(98))[2], caption = "Type of missing")
ggplot(TILDA_w2_recent_falls, aes(x=factor(ph401))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `98 Don't know into 998`

**R script:**

```{r harmo w2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_recent_falls$id)
TILDA_ds_w2$recent_falls <- car::recode(TILDA_w2_recent_falls$ph401, "5 = '0';98 = '998'")
TILDA_ds_w2$recent_falls <- labelled(TILDA_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- TILDA_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(TILDA_ds_w2$recent_falls)
X<-table(TILDA_w2_recent_falls$ph401)
BeforeH <- X[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1","98->998") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(TILDA_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- TILDA_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$recent_falls <- car::recode(TILDA_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

