---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

| **Name** | `mh008` |
|-|-|
| **Label** | `I felt hopeful about the future` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `1 = Rarely or none of the time (less than 1 day)` <br/>`2 = Some or a little of the time (1-2 days)` <br/>`3 = Occasionally or a moderate amount of time (3-4 days)`<br/>`4 = All of the time (5-7 days)` |
| **Missings** | `98 = Don't know` <br/> `99 = Refused`|
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_wb','TILDA.TILDA-AMF-v16', variables=list('mh008'), missings = TRUE)
TILDA_wb <- opal.execute(o,'TILDA_wb')
```

```{r local w1, echo=F}

vbl <- TILDA_wb$mh008
vbl_mis <- 98:99
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(TILDA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_mis)[2], caption = "Missigns Categories")
ggplot(TILDA_wb, aes(x=factor(mh008))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 2`
* `2,3 into 1`
* `1 into 0`
* `98 into 998`
* `99 into 997`
* `NA into 999`

**R script:**

```{r harmo w1}

TILDA_ds_w1 <- tibble(id=TILDA_wb$id)
TILDA_ds_w1$eudaimonic_wb <- car::recode(TILDA_wb$mh008, "1=0; 2:3=1; 4=2; 98=998; 99=997; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- TILDA_ds_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}

```







### Wave 2

#### Study-specific variable description

| **Name** | `mh008` |
|-|-|
| **Label** | `MH008: I felt hopeful about the future.` |
| **Table name** | `TILDA-AMF-v23` |
| **Categories** | `1 = Rarely or none of the time (less than 1 day)` <br/>`2 = Some or a little of the time (1-2 days)` <br/>`3 = Occasionally or a moderate amount of time (3-4 days)`<br/>`4 = All of the time (5-7 days)` |
| **Missings** | `98 = Don't know` <br/> `99 = Refused`|
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_wb','TILDA.TILDA-AMF-v23', variables=list('mh008'), missings = TRUE)
TILDA_wb <- opal.execute(o,'TILDA_wb')
```

```{r local w2, echo=F}

vbl <- TILDA_wb$mh008
vbl_mis <- 98:99
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(TILDA_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_mis)[2], caption = "Missigns Categories")
ggplot(TILDA_wb, aes(x=factor(mh008))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 2`
* `2,3 into 1`
* `1 into 0`
* `98 into 998`
* `99 into 997`
* `NA into 999`

**R script:**

```{r harmo w2}

TILDA_ds_w2 <- tibble(id=TILDA_wb$id)
TILDA_ds_w2$eudaimonic_wb <- car::recode(TILDA_wb$mh008, "1=0; 2:3=1; 4=2; 98=998; 99=997; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- TILDA_ds_w2$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
