---
title: "Walking speed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `walking_speed_c`
* Variable label: `Walking speed - Continuous`
* Variable description: `Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance.`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `walking_speed`
* Variable label: `Walking speed`
* Variable description: `Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Walking speed"
ds_label_walking_speed_c <- "Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance"
ds_label_walking_speed <- "Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%."
```


# Data process

## Ireland

### Wave 1

Not found.



### Wave 2 

#### Study-specific variable description

| **Name** | `tug009m`|`tug009s`|`tug009c`|
|-|-|-|-|
| **Label** | `IWER: Enter time taken to complete walk in minutes, seconds and centis`|`IWER: Enter time taken to complete walk in minutes, seconds and centis`|`IWER: Enter time taken to complete walk in minutes, seconds and centis` |
| **Table name** | `TILDA-AMF-v23` |`TILDA-AMF-v23`|`TILDA-AMF-v23`|
| **Missings** | `-1 = Not_applicable` | `-1 = Not_applicable` | `-1 = Not_applicable` |
| **Description** |  |  |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_walking','TILDA.TILDA-AMF-v23', variables=list('tug009m','tug009s','tug009c'), missings = TRUE)
TILDA_w2_walking <- opal.execute(o,'TILDA_w2_walking')
```

```{r local w2, echo=F}
vari <- TILDA_w2_walking$tug009m
kable(Continuous_summary(vari, missing_values = c(-1))[3], caption = "tug009m")
pander(Continuous_summary(vari, missing_values = c(-1))$summary, caption = "Summary")
ggplot(TILDA_w2_walking, aes(tug009m)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("time") + ylab("Frequency")+xlim(-0.5,11)

vari <- TILDA_w2_walking$tug009s
kable(Continuous_summary(vari, missing_values = c(-1))[3], caption = "tug009s")
pander(Continuous_summary(vari, missing_values = c(-1))$summary, caption = "Summary")
ggplot(TILDA_w2_walking, aes(tug009s)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("time") + ylab("Frequency")+xlim(0,61)

vari <- TILDA_w2_walking$tug009c
kable(Continuous_summary(vari, missing_values = c(-1))[3], caption = "tug009c")
pander(Continuous_summary(vari, missing_values = c(-1))$summary, caption = "Summary")
ggplot(TILDA_w2_walking, aes(tug009c)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("time") + ylab("Frequency")+xlim(0,101)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `-1 Not_applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w2}
#walking_speed_c
TILDA_ds_w2 <- tibble(id=TILDA_w2_walking$id)
mmwlk <- 2.44/(TILDA_w2_walking$tug009m*60 + TILDA_w2_walking$tug009s + TILDA_w2_walking$tug009c/100)
TILDA_ds_w2$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-2.44/61.01 = 996")
TILDA_ds_w2$walking_speed_c <- labelled(TILDA_ds_w2$walking_speed_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

#walking_speed
Q <- quantile(car::recode(TILDA_ds_w2$walking_speed_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

TILDA_ds_w2$walking_speed <- car::recode(TILDA_ds_w2[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
TILDA_ds_w2$walking_speed <- labelled(TILDA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- TILDA_ds_w2$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,0.6)

vari <- TILDA_ds_w2$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
Continous <- c(sum(na.omit(TILDA_ds_w2[[2]])<=Q), sum(na.omit(TILDA_ds_w2[[2]])>Q & na.omit(TILDA_ds_w2[[2]])<900), sum(na.omit(TILDA_ds_w2[[2]])==996))
Dicotomic <- table(TILDA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```






```{r importOPAL w2, echo=FALSE}
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

label(TILDA_ds_w2$walking_speed_c) <- ds_label_walking_speed_c
label(TILDA_ds_w2$walking_speed) <- ds_label_walking_speed
walking_speed <- TILDA_ds_w2
save(walking_speed, file = "../RData/w2/walking_speed.RData")
```


# Quality estimation
Measure is calculated combining one/two/three trials if available.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
