---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description




| **Name** | `SCQcasp15`|
|-|-|
| **Label** | `I feel full of energy these days` |
| **Table name** | `TILDA-AMF-v16` |
| **Categories** | `1 = Often; 2 = Sometimes; 3 = Rarely 4 = Never` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_energy','TILDA.TILDA-AMF-v16', variables=list('SCQcasp15'), missings = TRUE)
```

```{r local w1, echo=F}
TILDA_w1_energy <- opal.execute(o,'TILDA_w1_energy')
vari <- TILDA_w1_energy$SCQcasp15
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "SCQcasp15")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_energy, aes(x=factor(SCQcasp15))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2 into 0` 
  * `3 into 0` 
  * `4 into 0` 
  * `NA into 999`

**R script:**

```{r harmo w1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_energy$id)
TILDA_ds_w1$energy <- car::recode(TILDA_w1_energy$SCQcasp15, "1 = '1';2 = '0';3 = '0';4 = '0';NA = '999' ")
TILDA_ds_w1$energy <- labelled(TILDA_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- TILDA_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(TILDA_ds_w1$energy)
X<-table(TILDA_w1_energy$SCQcasp15)
BeforeH <- c(sum(X[2:4]),X[c(1)],sum(is.na(TILDA_w1_energy$SCQcasp15)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(TILDA_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')
energy <- TILDA_ds_w1
save(energy, file = "../RData/w1/energy.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$energy <- car::recode(TILDA_m_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

Not found.




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
