---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/religDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/religDS.R')
```


<!-- ########################################################## --> 

# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Description: 
```{r assign1 china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_relig','SAGE.chinaINDData', variables=list('q6008'), missings = TRUE)
```

```{r local1 china, echo=F}
SAGE_china_w1_relig <- opal.execute(o,'SAGE_china_w1_relig')
vari <- SAGE_china_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_china_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 china, echo=TRUE}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_relig$id)
SAGE_china_ds_w1$relig <- car::recode(as.vector(SAGE_china_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_china_ds_w1$relig <- labelled(SAGE_china_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 china, echo=F}
vari <- SAGE_china_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 china, echo=F}
AfterH <- table(SAGE_china_ds_w1$relig)
BeforeH <- table(SAGE_china_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```



## Ghana
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_relig','SAGE.ghanaINDData',variables=list('q6008'), missings = TRUE)
```


```{r local1 ghana, echo=F}
SAGE_ghana_w1_relig <- opal.execute(o,'SAGE_ghana_w1_relig')
vari <- SAGE_ghana_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_ghana_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 ghana, echo=TRUE}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_relig$id)
SAGE_ghana_ds_w1$relig <- car::recode(as.vector(SAGE_ghana_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_ghana_ds_w1$relig <- labelled(SAGE_ghana_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ghana, echo=F}
vari <- SAGE_ghana_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ghana, echo=F}
AfterH <- table(SAGE_ghana_ds_w1$relig)
BeforeH <- table(SAGE_ghana_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[7]]
BeforeH1[[4]] <- BeforeH[[6]]
BeforeH1[[5]] <- BeforeH[[8]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","9->996","8->998","NA->999")
kable(C)
```


## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Description: 
```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_relig','SAGE.indiaINDData',variables=list('q6008'), missings = TRUE)
```

```{r local1 india, echo=F}
SAGE_india_w1_relig <- opal.execute(o,'SAGE_india_w1_relig')
vari <- SAGE_india_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_india_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_relig$id)
SAGE_india_ds_w1$relig <- car::recode(as.vector(SAGE_india_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_india_ds_w1$relig <- labelled(SAGE_india_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- SAGE_india_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}
AfterH <- table(SAGE_india_ds_w1$relig)
BeforeH <- table(SAGE_india_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
BeforeH1[[4]] <- BeforeH[[7]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","9->996","NA->999")
kable(C)
```




## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Description: 
```{r assign1 mex, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_relig','SAGE.mexicoINDdata',variables=list('q6008'), missings = TRUE)
```

```{r local1 mex, echo=F}
SAGE_mexico_w1_relig <- opal.execute(o,'SAGE_mexico_w1_relig')
vari <- SAGE_mexico_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_mexico_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 mex, echo=TRUE}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_relig$id)
SAGE_mexico_ds_w1$relig <- car::recode(as.vector(SAGE_mexico_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_mexico_ds_w1$relig <- labelled(SAGE_mexico_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 mex, echo=F}
vari <- SAGE_mexico_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 mex, echo=F}
AfterH <- table(SAGE_mexico_ds_w1$relig)
BeforeH <- table(SAGE_mexico_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```



## Russia
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_relig','SAGE.russiaINDdata', variables=list('q6008'), missings = TRUE)
```

```{r local1 russia, echo=F}
SAGE_russia_w1_relig <- opal.execute(o,'SAGE_russia_w1_relig')
vari <- SAGE_russia_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_russia_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 russia, echo=TRUE}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_relig$id)
SAGE_russia_ds_w1$relig <- car::recode(as.vector(SAGE_russia_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_russia_ds_w1$relig <- labelled(SAGE_russia_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 russia, echo=F}
vari <- SAGE_russia_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 russia, echo=F}
AfterH <- table(SAGE_russia_ds_w1$relig)
BeforeH <- table(SAGE_russia_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[7]]
BeforeH1[[4]] <- BeforeH[[6]]
BeforeH1[[5]] <- BeforeH[[8]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","9->996","8->998","NA->999")
kable(C)
```



## South Africa

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q6008`
* Label: `q6008: religious services`
* Categories: 
    + `1 = never`
    + `2 = 1/2 x per year`
    + `3 = 1/2 x per month`
    + `4 = 1/2 x per week`
    + `5 = daily`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 SA, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_relig','SAGE.southAfricaINDdata',variables=list('q6008'), missings = TRUE)
```

```{r local1 SA, echo=F}
SAGE_SA_w1_relig <- opal.execute(o,'SAGE_SA_w1_relig')
vari <- SAGE_SA_w1_relig$q6008
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_w1_relig$q6008, missing_values = NA)
ggplot(SAGE_SA_w1_relig, aes(x=factor(q6008))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("religious services") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 SA, echo=TRUE}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_relig$id)
SAGE_SA_ds_w1$relig <- car::recode(as.vector(SAGE_SA_w1_relig$q6008), "1:2='0'; 3:5='1'; 8='998'; 9='996'; NA='999'")
SAGE_SA_ds_w1$relig <- labelled(SAGE_SA_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 SA, echo=F}
vari <- SAGE_SA_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 SA, echo=F}
AfterH <- table(SAGE_SA_ds_w1$relig)
BeforeH <- table(SAGE_SA_w1_relig$q6008, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[7]]
BeforeH1[[4]] <- BeforeH[[6]]
BeforeH1[[5]] <- BeforeH[[8]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","9->996","8->998","NA->999")
kable(C)
```


```{r save, echo=FALSE}
relig <- SAGE_SA_ds_w1
save(relig, file = "../RData/SA_w1/relig.RData")
rm(relig)

relig <- SAGE_china_ds_w1
save(relig, file = "../RData/china_w1/relig.RData")
rm(relig)

relig <- SAGE_ghana_ds_w1
save(relig, file = "../RData/ghana_w1/relig.RData")
rm(relig)

relig <- SAGE_india_ds_w1
save(relig, file = "../RData/india_w1/relig.RData")
rm(relig)

relig <- SAGE_mexico_ds_w1
save(relig, file = "../RData/mexico_w1/relig.RData")
rm(relig)

relig <- SAGE_russia_ds_w1
save(relig, file = "../RData/russia_w1/relig.RData")
rm(relig)



```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

