---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```



<!-- ########################################################## --> 

# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 china, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_divorce','SAGE.chinaINDData',variables=list('q1012'), missings = TRUE)
```

```{r local1 china, echo=F}
SAGE_china_w1_divorce <- opal.execute(o,'SAGE_china_w1_divorce')
vari <- SAGE_china_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_china_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 china, echo=TRUE}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_divorce$id)
SAGE_china_ds_w1$divorce <- car::recode(as.vector(SAGE_china_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_china_ds_w1$divorce <- labelled(SAGE_china_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 china, echo=F}
vari <- SAGE_china_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 china, echo=F}
AfterH <- table(SAGE_china_ds_w1$divorce)
BeforeH <- table(SAGE_china_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5)])
BeforeH1[c(3,4)] <- BeforeH[c(6,7)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","8->998","NA->999")
kable(C)
```



## Ghana
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_divorce','SAGE.ghanaINDData',variables=list('q1012'), missings = TRUE)
```

```{r local1 ghana, echo=F}
SAGE_ghana_w1_divorce <- opal.execute(o,'SAGE_ghana_w1_divorce')
Cvari <- SAGE_ghana_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#ategorical_summary(var = SAGE_ghana_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_ghana_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 ghana, echo=TRUE}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_divorce$id)
SAGE_ghana_ds_w1$divorce <- car::recode(as.vector(SAGE_ghana_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_ghana_ds_w1$divorce <- labelled(SAGE_ghana_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ghana, echo=F}
vari <- SAGE_ghana_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ghana, echo=F}
AfterH <- table(SAGE_ghana_ds_w1$divorce)
BeforeH <- table(SAGE_ghana_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5)])
BeforeH1[c(3,4)] <- BeforeH[c(6,7)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","8->998","NA->999")
kable(C)
```


## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_divorce','SAGE.indiaINDData', variables=list('q1012'), missings = TRUE)
```

```{r local1 india, echo=F}
SAGE_india_w1_divorce <- opal.execute(o,'SAGE_india_w1_divorce')
vari <- SAGE_india_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_india_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_divorce$id)
SAGE_india_ds_w1$divorce <- car::recode(as.vector(SAGE_india_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_india_ds_w1$divorce <- labelled(SAGE_india_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- SAGE_india_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}
AfterH <- table(SAGE_india_ds_w1$divorce)
BeforeH <- table(SAGE_india_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[3]]
BeforeH1[[1]] <- sum(BeforeH[c(1:2,4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","8->998")
kable(C)
```

## Mexico
  


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_divorce','SAGE.mexicoINDdata',variables=list('q1012'), missings = TRUE)
```

```{r local1 mexico, echo=F}
SAGE_mexico_w1_divorce <- opal.execute(o,'SAGE_mexico_w1_divorce')
vari <- SAGE_mexico_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_mexico_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 mexico, echo=TRUE}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_divorce$id)
SAGE_mexico_ds_w1$divorce <- car::recode(as.vector(SAGE_mexico_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_mexico_ds_w1$divorce <- labelled(SAGE_mexico_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 mexico, echo=F}
vari <- SAGE_mexico_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 mexico, echo=F}
AfterH <- table(SAGE_mexico_ds_w1$divorce)
BeforeH <- table(SAGE_mexico_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5)])
BeforeH1[c(3)] <- BeforeH[c(6)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","NA->999")
kable(C)
```

## Russia

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_divorce','SAGE.russiaINDdata',variables=list('q1012'), missings = TRUE)
```

```{r local1 russia, echo=F}
SAGE_russia_w1_divorce <- opal.execute(o,'SAGE_russia_w1_divorce')
vari <- SAGE_russia_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_russia_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 russia, echo=TRUE}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_divorce$id)
SAGE_russia_ds_w1$divorce <- car::recode(as.vector(SAGE_russia_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_russia_ds_w1$divorce <- labelled(SAGE_russia_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 russia, echo=F}
vari <- SAGE_russia_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 russia, echo=F}
AfterH <- table(SAGE_russia_ds_w1$divorce)
BeforeH <- table(SAGE_russia_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5)])
BeforeH1[c(3,4,5)] <- BeforeH[c(6,7,8)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","8->998","9->996","NA->999")
kable(C)
```

## South Africa 

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 SA, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_divorce','SAGE.southAfricaINDdata',variables=list('q1012'), missings = TRUE)
```

```{r local1 SA, echo=F}
SAGE_SA_w1_divorce <- opal.execute(o,'SAGE_SA_w1_divorce')
vari <- SAGE_SA_w1_divorce$q1012
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_w1_divorce$q1012, missing_values = NA)
ggplot(SAGE_SA_w1_divorce, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 SA, echo=TRUE}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_divorce$id)
SAGE_SA_ds_w1$divorce <- car::recode(as.vector(SAGE_SA_w1_divorce$q1012), "4='1'; 1:3='0'; 5='0'; 8='998'; 9='996'; NA='999'")
SAGE_SA_ds_w1$divorce <- labelled(SAGE_SA_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 SA, echo=F}
vari <- SAGE_SA_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 SA, echo=F}
AfterH <- table(SAGE_SA_ds_w1$divorce)
BeforeH <- table(SAGE_SA_w1_divorce$q1012, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5)])
BeforeH1[c(3,4)] <- BeforeH[c(6,7)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,3,5->0","4->1","8->998","NA->999")
kable(C)
```


```{r save, echo=FALSE}
divorce <- SAGE_russia_ds_w1
save(divorce, file = "../RData/russia_w1/divorce.RData")
rm(divorce)


divorce <- SAGE_mexico_ds_w1
save(divorce, file = "../RData/mexico_w1/divorce.RData")
rm(divorce)


divorce <- SAGE_china_ds_w1
save(divorce, file = "../RData/china_w1/divorce.RData")
rm(divorce)


divorce <- SAGE_india_ds_w1
save(divorce, file = "../RData/india_w1/divorce.RData")
rm(divorce)

divorce <- SAGE_ghana_ds_w1
save(divorce, file = "../RData/ghana_w1/divorce.RData")
rm(divorce)




divorce <- SAGE_SA_ds_w1
save(divorce, file = "../RData/SA_w1/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```





