---
title: "Ever experienced financial problems"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/fin_probDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/fin_probDS.R')
```

<!-- ########################################################## --> 

# Data process


## China

### Wave 1

Not found.

## Ghana
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q8025`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Name: `q8044`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_fin_prob','SAGE.ghanaINDData',variables=list('q8025','q8044'), missings = TRUE)
```

```{r local1 ghana, echo=F}
SAGE_ghana_w1_fin_prob <- opal.execute(o,'SAGE_ghana_w1_fin_prob')
vari <- SAGE_ghana_w1_fin_prob$q8025
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_w1_fin_prob$q8025, missing_values = NA)
ggplot(SAGE_ghana_w1_fin_prob, aes(x=factor(q8025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?") + ylab("Frequency")

vari <- SAGE_ghana_w1_fin_prob$q8044
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_w1_fin_prob$q8044, missing_values = NA)
ggplot(SAGE_ghana_w1_fin_prob, aes(x=factor(q8044))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3,4,5 then 1`
* `if both are equal 1 or 2 then 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 ghana, echo=TRUE}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_fin_prob$id)

SAGE_ghana_w1_fin_prob$q8025 <- car::recode(as.vector(SAGE_ghana_w1_fin_prob$q8025), "NA='-999'")
SAGE_ghana_w1_fin_prob$q8044 <- car::recode(as.vector(SAGE_ghana_w1_fin_prob$q8044), "NA='-999'")

SAGE_ghana_ds_w1$fin_prob <- c(NA)
for(i in 1:dim(SAGE_ghana_w1_fin_prob)[1]){
  if( SAGE_ghana_w1_fin_prob$q8025[i] %in% c(3,4,5) | SAGE_ghana_w1_fin_prob$q8044[i] %in% c(3,4,5) ) {
    SAGE_ghana_ds_w1$fin_prob[i] = 1 }
  else if( SAGE_ghana_w1_fin_prob$q8025[i] %in% c(1,2) & SAGE_ghana_w1_fin_prob$q8044[i] %in% c(1,2) ) {
    SAGE_ghana_ds_w1$fin_prob[i] = 0 }
  else if( SAGE_ghana_w1_fin_prob$q8025[i] == 8 | SAGE_ghana_w1_fin_prob$q8025[i] == 8 ) {
    SAGE_ghana_ds_w1$fin_prob[i] = 998 }
  else if( SAGE_ghana_w1_fin_prob$q8025[i] == 9 | SAGE_ghana_w1_fin_prob$q8025[i] == 9 ) {
    SAGE_ghana_ds_w1$fin_prob[i] = 996 }
}

SAGE_ghana_ds_w1$fin_prob <- car::recode(as.vector(SAGE_ghana_ds_w1$fin_prob), "NA='999'")
SAGE_ghana_ds_w1$fin_prob <- labelled(SAGE_ghana_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ghana, echo=F}
vari <- SAGE_ghana_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ghana, echo=F}

```


## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q8025`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Name: `q8044`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 india, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_fin_prob','SAGE.indiaINDData',variables=list('q8025','q8044'), missings = TRUE)
```

```{r local1 india, echo=F}
SAGE_india_w1_fin_prob <- opal.execute(o,'SAGE_india_w1_fin_prob')

vari <- SAGE_india_w1_fin_prob$q8025
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_w1_fin_prob$q8025, missing_values = NA)
ggplot(SAGE_india_w1_fin_prob, aes(x=factor(q8025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?") + ylab("Frequency")

vari <- SAGE_india_w1_fin_prob$q8044
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_w1_fin_prob$q8044, missing_values = NA)
ggplot(SAGE_india_w1_fin_prob, aes(x=factor(q8044))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3,4,5 then 1`
* `if both are equal 1 or 2 then 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 india, echo=TRUE}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_fin_prob$id)

SAGE_india_w1_fin_prob$q8025 <- car::recode(as.vector(SAGE_india_w1_fin_prob$q8025), "NA='-999'")
SAGE_india_w1_fin_prob$q8044 <- car::recode(as.vector(SAGE_india_w1_fin_prob$q8044), "NA='-999'")

SAGE_india_ds_w1$fin_prob <- c(NA)
for(i in 1:dim(SAGE_india_w1_fin_prob)[1]){
  if( SAGE_india_w1_fin_prob$q8025[i] %in% c(3,4,5) | SAGE_india_w1_fin_prob$q8044[i] %in% c(3,4,5) ) {
    SAGE_india_ds_w1$fin_prob[i] = 1 }
  else if( SAGE_india_w1_fin_prob$q8025[i] %in% c(1,2) & SAGE_india_w1_fin_prob$q8044[i] %in% c(1,2) ) {
    SAGE_india_ds_w1$fin_prob[i] = 0 }
  else if( SAGE_india_w1_fin_prob$q8025[i] == 8 | SAGE_india_w1_fin_prob$q8025[i] == 8 ) {
    SAGE_india_ds_w1$fin_prob[i] = 998 }
  else if( SAGE_india_w1_fin_prob$q8025[i] == 9 | SAGE_india_w1_fin_prob$q8025[i] == 9 ) {
    SAGE_india_ds_w1$fin_prob[i] = 996 }
}

SAGE_india_ds_w1$fin_prob <- car::recode(as.vector(SAGE_india_ds_w1$fin_prob), "NA='999'")
SAGE_india_ds_w1$fin_prob <- labelled(SAGE_india_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india, echo=F}
vari <- SAGE_india_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india, echo=F}

```



## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q8025`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Name: `q8044`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 mexico, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_fin_prob','SAGE.mexicoINDdata',variables=list('q8025','q8044'), missings = TRUE)
```

```{r local1 mexico, echo=F}
SAGE_mexico_w1_fin_prob <- opal.execute(o,'SAGE_mexico_w1_fin_prob')

vari <- SAGE_mexico_w1_fin_prob$q8025
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_w1_fin_prob$q8025, missing_values = NA)
ggplot(SAGE_mexico_w1_fin_prob, aes(x=factor(q8025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?") + ylab("Frequency")

vari <- SAGE_mexico_w1_fin_prob$q8044
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_w1_fin_prob$q8044, missing_values = NA)
ggplot(SAGE_mexico_w1_fin_prob, aes(x=factor(q8044))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3,4,5 then 1`
* `if both are equal 1 or 2 then 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 mexico, echo=TRUE}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_fin_prob$id)

SAGE_mexico_w1_fin_prob$q8025 <- car::recode(as.vector(SAGE_mexico_w1_fin_prob$q8025), "NA='-999'")
SAGE_mexico_w1_fin_prob$q8044 <- car::recode(as.vector(SAGE_mexico_w1_fin_prob$q8044), "NA='-999'")

SAGE_mexico_ds_w1$fin_prob <- c(NA)
for(i in 1:dim(SAGE_mexico_w1_fin_prob)[1]){
  if( SAGE_mexico_w1_fin_prob$q8025[i] %in% c(3,4,5) | SAGE_mexico_w1_fin_prob$q8044[i] %in% c(3,4,5) ) {
    SAGE_mexico_ds_w1$fin_prob[i] = 1 }
  else if( SAGE_mexico_w1_fin_prob$q8025[i] %in% c(1,2) & SAGE_mexico_w1_fin_prob$q8044[i] %in% c(1,2) ) {
    SAGE_mexico_ds_w1$fin_prob[i] = 0 }
  else if( SAGE_mexico_w1_fin_prob$q8025[i] == 8 | SAGE_mexico_w1_fin_prob$q8025[i] == 8 ) {
    SAGE_mexico_ds_w1$fin_prob[i] = 998 }
  else if( SAGE_mexico_w1_fin_prob$q8025[i] == 9 | SAGE_mexico_w1_fin_prob$q8025[i] == 9 ) {
    SAGE_mexico_ds_w1$fin_prob[i] = 996 }
}

SAGE_mexico_ds_w1$fin_prob <- car::recode(as.vector(SAGE_mexico_ds_w1$fin_prob), "NA='999'")
SAGE_mexico_ds_w1$fin_prob <- labelled(SAGE_mexico_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 mexico, echo=F}
vari <- SAGE_mexico_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 mexico, echo=F}

```


## Russia
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q8025`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Name: `q8044`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_fin_prob','SAGE.russiaINDdata',variables=list('q8025','q8044'), missings = TRUE)
```

```{r local1 russia, echo=F}
SAGE_russia_w1_fin_prob <- opal.execute(o,'SAGE_russia_w1_fin_prob')
vari <- SAGE_russia_w1_fin_prob$q8025
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_w1_fin_prob$q8025, missing_values = NA)
ggplot(SAGE_russia_w1_fin_prob, aes(x=factor(q8025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?") + ylab("Frequency")

vari <- SAGE_russia_w1_fin_prob$q8044
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_w1_fin_prob$q8044, missing_values = NA)
ggplot(SAGE_russia_w1_fin_prob, aes(x=factor(q8044))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3,4,5 then 1`
* `if both are equal 1 or 2 then 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 russia, echo=TRUE}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_fin_prob$id)

SAGE_russia_w1_fin_prob$q8025 <- car::recode(as.vector(SAGE_russia_w1_fin_prob$q8025), "NA='-999'")
SAGE_russia_w1_fin_prob$q8044 <- car::recode(as.vector(SAGE_russia_w1_fin_prob$q8044), "NA='-999'")

SAGE_russia_ds_w1$fin_prob <- c(NA)
for(i in 1:dim(SAGE_russia_w1_fin_prob)[1]){
  if( SAGE_russia_w1_fin_prob$q8025[i] %in% c(3,4,5) | SAGE_russia_w1_fin_prob$q8044[i] %in% c(3,4,5) ) {
    SAGE_russia_ds_w1$fin_prob[i] = 1 }
  else if( SAGE_russia_w1_fin_prob$q8025[i] %in% c(1,2) & SAGE_russia_w1_fin_prob$q8044[i] %in% c(1,2) ) {
    SAGE_russia_ds_w1$fin_prob[i] = 0 }
  else if( SAGE_russia_w1_fin_prob$q8025[i] == 8 | SAGE_russia_w1_fin_prob$q8025[i] == 8 ) {
    SAGE_russia_ds_w1$fin_prob[i] = 998 }
  else if( SAGE_russia_w1_fin_prob$q8025[i] == 9 | SAGE_russia_w1_fin_prob$q8025[i] == 9 ) {
    SAGE_russia_ds_w1$fin_prob[i] = 996 }
}

SAGE_russia_ds_w1$fin_prob <- car::recode(as.vector(SAGE_russia_ds_w1$fin_prob), "NA='999'")
SAGE_russia_ds_w1$fin_prob <- labelled(SAGE_russia_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 russia, echo=F}
vari <- SAGE_russia_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 russia, echo=F}

```


## South Africa
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q8025`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`

* Name: `q8044`
* Label: `Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?`
* Categories: 
    + `1 = none`
    + `2 = mild`
    + `3 = moderate`
    + `4 = severe`
    + `5 = extreme`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 sa, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_fin_prob','SAGE.southAfricaINDdata',variables=list('q8025','q8044'), missings = TRUE)
```

```{r local1 sa, echo=F}
SAGE_SA_w1_fin_prob <- opal.execute(o,'SAGE_SA_w1_fin_prob')

vari <- SAGE_SA_w1_fin_prob$q8025
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_w1_fin_prob$q8025, missing_values = NA)
ggplot(SAGE_SA_w1_fin_prob, aes(x=factor(q8025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, or increased costs or expenses?") + ylab("Frequency")

vari <- SAGE_SA_w1_fin_prob$q8044
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_w1_fin_prob$q8044, missing_values = NA)
ggplot(SAGE_SA_w1_fin_prob, aes(x=factor(q8044))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Financial problems due to loss of income, decreased time available for paid employment, increased costs or expenses, or selling household items?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 3,4,5 then 1`
* `if both are equal 1 or 2 then 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 sa, echo=TRUE}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_fin_prob$id)

SAGE_SA_w1_fin_prob$q8025 <- car::recode(as.vector(SAGE_SA_w1_fin_prob$q8025), "NA='-999'")
SAGE_SA_w1_fin_prob$q8044 <- car::recode(as.vector(SAGE_SA_w1_fin_prob$q8044), "NA='-999'")

SAGE_SA_ds_w1$fin_prob <- c(NA)
for(i in 1:dim(SAGE_SA_w1_fin_prob)[1]){
  if( SAGE_SA_w1_fin_prob$q8025[i] %in% c(3,4,5) | SAGE_SA_w1_fin_prob$q8044[i] %in% c(3,4,5) ) {
    SAGE_SA_ds_w1$fin_prob[i] = 1 }
  else if( SAGE_SA_w1_fin_prob$q8025[i] %in% c(1,2) & SAGE_SA_w1_fin_prob$q8044[i] %in% c(1,2) ) {
    SAGE_SA_ds_w1$fin_prob[i] = 0 }
  else if( SAGE_SA_w1_fin_prob$q8025[i] == 8 | SAGE_SA_w1_fin_prob$q8025[i] == 8 ) {
    SAGE_SA_ds_w1$fin_prob[i] = 998 }
  else if( SAGE_SA_w1_fin_prob$q8025[i] == 9 | SAGE_SA_w1_fin_prob$q8025[i] == 9 ) {
    SAGE_SA_ds_w1$fin_prob[i] = 996 }
}

SAGE_SA_ds_w1$fin_prob <- car::recode(as.vector(SAGE_SA_ds_w1$fin_prob), "NA='999'")
SAGE_SA_ds_w1$fin_prob <- labelled(SAGE_SA_ds_w1$fin_prob, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 sa, echo=F}
vari <- SAGE_SA_ds_w1$fin_prob
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_ds_w1$fin_prob, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(fin_prob))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced financial problems?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 sa, echo=F}

```


```{r save, echo=FALSE}
fin_prob <- SAGE_russia_ds_w1
save(fin_prob, file = "../RData/russia_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- SAGE_mexico_ds_w1
save(fin_prob, file = "../RData/mexico_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- SAGE_india_ds_w1
save(fin_prob, file = "../RData/india_w1/fin_prob.RData")
rm(fin_prob)

fin_prob <- SAGE_ghana_ds_w1
save(fin_prob, file = "../RData/ghana_w1/fin_prob.RData")
rm(fin_prob)



fin_prob <- SAGE_SA_ds_w1
save(fin_prob, file = "../RData/SA_w1/fin_prob.RData")
rm(fin_prob)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

