---
title: "Loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lonelinessDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lonelinessDS.R')
```

# Data process

## South Africa


### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`southAfricaINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1SA, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata', variables=list('q7508'), missings = TRUE)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')
```

```{r local1SA, echo=F}
vbl <- SAGE_SA_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1SA}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$loneliness <- car::recode(as.vector(SAGE_SA_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1SA, echo=F}
vbl <- SAGE_ds_SA_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_SA_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1SA, echo=F}
AfterH <- table(SAGE_ds_SA_w1$loneliness)
BeforeH <- table(SAGE_SA_w1$q7508, useNA='ifany')[c(2,1,3,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->998","NA->999")
kable(C)
```



## China

### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`chinaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1China, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q7508'), missings = TRUE)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')
```

```{r local1China, echo=F}
vbl <- SAGE_china_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1China}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$loneliness <- car::recode(as.vector(SAGE_china_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1China, echo=F}
vbl <- SAGE_ds_china_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_china_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1China, echo=F}
AfterH <- table(SAGE_ds_china_w1$loneliness)
BeforeH <- table(SAGE_china_w1$q7508, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```





## Ghana

### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`ghanaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1Ghana, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('q7508'), missings = TRUE)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')
```

```{r local1Ghana, echo=F}
vbl <- SAGE_ghana_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1Ghana}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$loneliness <- car::recode(as.vector(SAGE_ghana_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1Ghana, echo=F}
vbl <- SAGE_ds_ghana_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1Ghana, echo=F}
AfterH <- table(SAGE_ds_ghana_w1$loneliness)
BeforeH <- table(SAGE_ghana_w1$q7508, useNA='ifany')[c(2,1,3,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->998","NA->999")
kable(C)
```



## India

### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`indiaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1India, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('q7508'), missings = TRUE)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')
```

```{r local1India, echo=F}
vbl <- SAGE_india_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1India}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$loneliness <- car::recode(as.vector(SAGE_india_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- SAGE_ds_india_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_india_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1India, echo=F}
AfterH <- table(SAGE_ds_india_w1$loneliness)
BeforeH <- table(SAGE_india_w1$q7508, useNA='ifany')[c(2,1,3,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->996","NA->999")
kable(C)
```



## Russia

### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`russiaINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1Russia, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',variables=list('q7508'), missings = TRUE)
```

```{r local1Russia, echo=F}
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')
vbl <- SAGE_russia_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1Russia}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$loneliness <- car::recode(as.vector(SAGE_russia_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1Russia, echo=F}
vbl <- SAGE_ds_russia_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_russia_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1Russia, echo=F}
AfterH <- table(SAGE_ds_russia_w1$loneliness)
BeforeH <- table(SAGE_russia_w1$q7508, useNA='ifany')[c(2,1,4,3,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->996","8->998","NA->999")
kable(C)
```









## Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `q7508`|
|-|-|
| **Label** | `q7508: lonely`|
| **Table name** |`mexicoINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`|
| **Description** |  |



```{r assign1mex, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q7508'), missings = TRUE)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')
```

```{r local1mex, echo=F}
vbl <- SAGE_mexico_w1$q7508
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q7508")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q7508))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1mex}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$loneliness <- car::recode(as.vector(SAGE_mexico_w1$q7508), "1='1'; 2='0'; 8='998'; 9='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1mex, echo=F}
vbl <- SAGE_ds_mexico_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1mex, echo=F}
AfterH <- table(SAGE_ds_mexico_w1$loneliness)
BeforeH <- table(SAGE_mexico_w1$q7508, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
