---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 china}
opal.assign.table.tibble(o, 'SAGE_china_w1_spouse','SAGE.chinaINDData', variables=list('q1012'), missings = TRUE)
```

```{r local1 china}
SAGE_china_w1_spouse <- opal.execute(o,'SAGE_china_w1_spouse')

vari <- SAGE_china_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_china_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_china_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:** 

```{r harmo1 china, echo=TRUE}
SAGE_china_ds_w1 <- tibble(id=SAGE_china_w1_spouse$id)
SAGE_china_ds_w1$spouse <- car::recode(as.vector(SAGE_china_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_china_ds_w1$spouse <- labelled(SAGE_china_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 china}
vari <- SAGE_china_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_china_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_china_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 china}
AfterH <- table(SAGE_china_ds_w1$spouse)
BeforeH <- table(SAGE_china_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2,6,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","8->998","NA->999")

kable(C)
```

 
 



## Ghana

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 ghana}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_spouse','SAGE.ghanaINDData', variables=list('q1012'), missings = TRUE)
```

```{r local1 ghana}
SAGE_ghana_w1_spouse <- opal.execute(o,'SAGE_ghana_w1_spouse')
vari <- SAGE_ghana_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_ghana_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_ghana_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1 ghana, echo=TRUE }
SAGE_ghana_ds_w1 <- tibble(id=SAGE_ghana_w1_spouse$id)
SAGE_ghana_ds_w1$spouse <- car::recode(as.vector(SAGE_ghana_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_ghana_ds_w1$spouse <- labelled(SAGE_ghana_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 ghana}
vari <- SAGE_ghana_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_ghana_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_ghana_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 ghana}
AfterH <- table(SAGE_ghana_ds_w1$spouse)
BeforeH <- table(SAGE_ghana_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2,6,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","8->998","NA->999")

kable(C)
```

 
 



## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 india}
opal.assign.table.tibble(o, 'SAGE_india_w1_spouse','SAGE.indiaINDData',  variables=list('q1012'), missings = TRUE)
```

```{r local1 india}
SAGE_india_w1_spouse <- opal.execute(o,'SAGE_india_w1_spouse')
vari <- SAGE_india_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_india_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_india_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1 india, echo=TRUE}
SAGE_india_ds_w1 <- tibble(id=SAGE_india_w1_spouse$id)
SAGE_india_ds_w1$spouse <- car::recode(as.vector(SAGE_india_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_india_ds_w1$spouse <- labelled(SAGE_india_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 india}
vari <- SAGE_india_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_india_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_india_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 india}
AfterH <- table(SAGE_india_ds_w1$spouse)
BeforeH <- table(SAGE_india_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[3]],BeforeH[[4]])
BeforeH[[2]] <- sum(BeforeH[[2]])
BeforeH <- BeforeH[c(1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","8->998")

kable(C)
```

 
 



## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 mexico}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_spouse','SAGE.mexicoINDdata', variables=list('q1012'), missings = TRUE)
```

```{r local1 mexico}
SAGE_mexico_w1_spouse <- opal.execute(o,'SAGE_mexico_w1_spouse')
vari <- SAGE_mexico_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_mexico_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_mexico_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1 mexico, echo=TRUE}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_mexico_w1_spouse$id)
SAGE_mexico_ds_w1$spouse <- car::recode(as.vector(SAGE_mexico_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_mexico_ds_w1$spouse <- labelled(SAGE_mexico_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 mexico}
vari <- SAGE_mexico_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_mexico_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_mexico_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 mexico}
AfterH <- table(SAGE_mexico_ds_w1$spouse)
BeforeH <- table(SAGE_mexico_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2,6)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","NA->999")

kable(C)
```

 
 



## Russia
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 russia}
opal.assign.table.tibble(o, 'SAGE_russia_w1_spouse','SAGE.russiaINDdata', variables=list('q1012'), missings = TRUE)
```

```{r local1 russia}
SAGE_russia_w1_spouse <- opal.execute(o,'SAGE_russia_w1_spouse')
vari <- SAGE_russia_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_russia_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_russia_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo1 russia, echo=TRUE}
SAGE_russia_ds_w1 <- tibble(id=SAGE_russia_w1_spouse$id)
SAGE_russia_ds_w1$spouse <- car::recode(as.vector(SAGE_russia_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_russia_ds_w1$spouse <- labelled(SAGE_russia_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 russia}
vari <- SAGE_russia_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_russia_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_russia_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 russia}
AfterH <- table(SAGE_russia_ds_w1$spouse)
BeforeH <- table(SAGE_russia_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2,7,6,8)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","9->996","8->998","NA->999")

kable(C)
```

 
 



## South Africa

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q1012`
* Label: `q1012: marital status`
* Categories: 
    + `1 = never married`
    + `2 = currently married`
    + `3 = cohabiting`
    + `4 = separated/divorced`
    + `5 = widowed`
* Missings:
    + `8 = don't know`
    + `9 = not applicable`


* Description: 
```{r assign1 sa}
opal.assign.table.tibble(o, 'SAGE_SA_w1_spouse','SAGE.southAfricaINDdata', variables=list('q1012'), missings = TRUE)
```

```{r local1 sa}
SAGE_SA_w1_spouse <- opal.execute(o,'SAGE_SA_w1_spouse')
vari <- SAGE_SA_w1_spouse$q1012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = SAGE_SA_w1_spouse$q1012, missing_values = NA)
ggplot(SAGE_SA_w1_spouse, aes(x=factor(q1012))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 OR 3 into 1`
* `1,4,5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:** 

```{r harmo1 sa, echo=TRUE}
SAGE_SA_ds_w1 <- tibble(id=SAGE_SA_w1_spouse$id)
SAGE_SA_ds_w1$spouse <- car::recode(as.vector(SAGE_SA_w1_spouse$q1012), "2:3='1'; 1='0'; 4:5='0'; 8='998'; 9='996'; NA='999'")
SAGE_SA_ds_w1$spouse <- labelled(SAGE_SA_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 sa}
vari <- SAGE_SA_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SAGE_SA_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SAGE_SA_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 sa}
AfterH <- table(SAGE_SA_ds_w1$spouse)
BeforeH <- table(SAGE_SA_w1_spouse$q1012, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[4]],BeforeH[[5]])
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(1,2,6,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,4,5->0","2,3->1","8->998","NA->999")

kable(C)
```

 
 
```{r save, echo=FALSE}
spouse <- SAGE_SA_ds_w1
save(spouse, file = "../RData/SA_w1/spouse.RData")
rm(spouse)

spouse <- SAGE_china_ds_w1
save(spouse, file = "../RData/china_w1/spouse.RData")
rm(spouse)

spouse <- SAGE_ghana_ds_w1
save(spouse, file = "../RData/ghana_w1/spouse.RData")
rm(spouse)

spouse <- SAGE_india_ds_w1
save(spouse, file = "../RData/india_w1/spouse.RData")
rm(spouse)

spouse <- SAGE_mexico_ds_w1
save(spouse, file = "../RData/mexico_w1/spouse.RData")
rm(spouse)

spouse <- SAGE_russia_ds_w1
save(spouse, file = "../RData/russia_w1/spouse.RData")
rm(spouse)



```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

