---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `height of the participant`
* Variable description: `Anthropometric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Spain
  

### ENRICA - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w1height`
* Label: 
* Type of variable: `countinous`

```{r assign1}
opal.assign.table.tibble(o, 'ENRICA_w1_heig','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1height'), missings = TRUE)
```

```{r local1}
ENRICA_w1_heig <- opal.execute(o,'ENRICA_w1_heig')
Continuous_summary(var = ENRICA_w1_heig$w1height, missing_values = NA)
ggplot(ENRICA_w1_heig, aes(w1height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_heig$id)
ENRICA_ds_w1$height <- car::recode(ENRICA_w1_heig$w1height, "NA=999")
ENRICA_ds_w1$height <- labelled(ENRICA_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = ENRICA_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(100,200) 
```

#### Validation
```{r crosstabulation1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL1}
#val_labels(ENRICA_ds_w1) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
height <- ENRICA_ds_w1
save(height, file = "../RData/w1/height.RData")
rm(height)
```






### ENRICA - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2height`
* Label: `Height of Subjects (cm)`
* Type of variable: `countinous`

```{r assign2}
opal.assign.table.tibble(o, 'ENRICA_w2_heig','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2height'), missings = TRUE)
```

```{r local2}
ENRICA_w2_heig <- opal.execute(o,'ENRICA_w2_heig')
Continuous_summary(var = ENRICA_w2_heig$w2height, missing_values = NA)
ggplot(ENRICA_w2_heig, aes(w2height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_heig$id)
ENRICA_ds_w2$height <- car::recode(ENRICA_w2_heig$w2height, "NA=999")
ENRICA_ds_w2$height <- labelled(ENRICA_ds_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = ENRICA_ds_w2$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(100,200) 
```

#### Validation
```{r crosstabulation2}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL2}
#val_labels(ENRICA_ds_w2) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
height <- ENRICA_ds_w2
save(height, file = "../RData/w2/height.RData")
rm(height)
```




### ENRICA - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w3height`
* Label: `Height of Subjects (cm)`
* Type of variable: `countinous`

```{r assign3}
opal.assign.table.tibble(o, 'ENRICA_w3_heig','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3height'), missings = TRUE)
```

```{r local3}
ENRICA_w3_heig <- opal.execute(o,'ENRICA_w3_heig')
Continuous_summary(var = ENRICA_w3_heig$w3height, missing_values = NA)
ggplot(ENRICA_w3_heig, aes(w3height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_heig$id)
ENRICA_ds_w3$height <- car::recode(ENRICA_w3_heig$w3height, "NA=999")
ENRICA_ds_w3$height <- labelled(ENRICA_ds_w3$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = ENRICA_ds_w3$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(100,200) 
```

#### Validation
```{r crosstabulation3}
```

#### Quality estimation
No comments.

#### Import to OPAL
```{r importOPAL3}
#val_labels(ENRICA_ds_w3) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
height <- ENRICA_ds_w3
save(height, file = "../RData/w3/height.RData")
rm(height)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
