---
title: "Day of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `dintw`
* Variable label: `day of interview`
* Domain: `Other administrative variables`
* Value type: `Continuous`

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


### 10/66 - Cuba - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_cuba1}
opal.assign.table.tibble(o, 't1066_cuba_w1_dinter','10-66.1066-Cuba-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_cuba1}
t1066_cuba_w1_dinter <- opal.execute(o,'t1066_cuba_w1_dinter')
t1066_cuba_w1_dinter$dinter <- as.numeric(format(t1066_cuba_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_cuba_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_cuba_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_dinter$id)
t1066_ds_cuba_w1$dintw <- car::recode(t1066_cuba_w1_dinter$dinter, "NA=999")
t1066_ds_cuba_w1$dintw <- labelled(t1066_ds_cuba_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba1}
Continuous_summary(var = t1066_ds_cuba_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_cuba1}
BeforeH <- table(t1066_cuba_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_cuba_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```



#### Import to OPAL
```{r importOPAL_cuba1}
val_labels(t1066_ds_cuba_w1) <- NULL
#opal.assign.data(o, 't1066_ds_cuba_w1', t1066_ds_cuba_w1)
#opal.symbol_import(o,'t1066_ds_cuba_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_cuba_w1 <- t1066_ds_cuba_w1
t1066_m_ds_cuba_w1$dintw <- car::recode(t1066_ds_cuba_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_cuba_w1', t1066_m_ds_cuba_w1)
#opal.symbol_import(o,'t1066_m_ds_cuba_w1', project='_Athlos_Harm_Dataset')
```




### 10/66 - Cuba - Wave 2 

There is no variable.






### 10/66 - India - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_india1}
opal.assign.table.tibble(o, 't1066_india_w1_dinter','10-66.1066-India-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_india1}
t1066_india_w1_dinter <- opal.execute(o,'t1066_india_w1_dinter')
t1066_india_w1_dinter$dinter <- as.numeric(format(t1066_india_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_india_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_india_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_india1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_dinter$id)
t1066_ds_india_w1$dintw <- car::recode(t1066_india_w1_dinter$dinter, "NA=999")
t1066_ds_india_w1$dintw <- labelled(t1066_ds_india_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india1}
Continuous_summary(var = t1066_ds_india_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_india1}
BeforeH <- table(t1066_india_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_india_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```



#### Import to OPAL
```{r importOPAL_india1}
val_labels(t1066_ds_india_w1) <- NULL
#opal.assign.data(o, 't1066_ds_india_w1', t1066_ds_india_w1)
#opal.symbol_import(o,'t1066_ds_india_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w1 <- t1066_ds_india_w1
t1066_m_ds_india_w1$dintw <- car::recode(t1066_m_ds_india_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w1', t1066_m_ds_india_w1)
#opal.symbol_import(o,'t1066_m_ds_india_w1', project='_Athlos_Harm_Dataset')
```






### 10/66 - India - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `fu_DATE`
* Label: `date of interview (follow-up)`


```{r assign_india2}
opal.assign.table.tibble(o, 't1066_india_w2_dinter','10-66.1066-India-Followup',
                         variables=list('fu_DATE'), missings = TRUE)

```

```{r local_india2}
t1066_india_w2_dinter <- opal.execute(o,'t1066_india_w2_dinter')
t1066_india_w2_dinter$dinter <- as.numeric(format(t1066_india_w2_dinter$fu_DATE, '%d'))
Continuous_summary(var = t1066_india_w2_dinter$dinter, missing_values = NA)
ggplot(t1066_india_w2_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_india2}
t1066_ds_india_w2 <- tibble(id=t1066_india_w2_dinter$id)
t1066_ds_india_w2$dintw <- car::recode(t1066_india_w2_dinter$dinter, "NA=999")
t1066_ds_india_w2$dintw <- labelled(t1066_ds_india_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india2}
Continuous_summary(var = t1066_ds_india_w2$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w2, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_india2}
BeforeH <- table(t1066_india_w2_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_india_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```



#### Import to OPAL
```{r importOPAL_india2}
val_labels(t1066_ds_india_w2) <- NULL
#opal.assign.data(o, 't1066_ds_india_w2', t1066_ds_india_w2)
#opal.symbol_import(o,'t1066_ds_india_w2', project='_Athlos_Harm_Dataset')

t1066_m_ds_india_w2 <- t1066_ds_india_w2
t1066_m_ds_india_w2$dintw <- car::recode(t1066_m_ds_india_w2$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_india_w2', t1066_m_ds_india_w2)
#opal.symbol_import(o,'t1066_m_ds_india_w2', project='_Athlos_Harm_Dataset')
```







### 10/66 - Urban China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_UCh1}
opal.assign.table.tibble(o, 't1066_UCh_w1_ybirth','10-66.1066-UrbanChina-Baseline',
                         variables=list('age','DATE'), missings = TRUE)
```

```{r local_UCh1}
t1066_UCh_w1_ybirth <- opal.execute(o,'t1066_UCh_w1_ybirth')
t1066_UCh_w1_ybirth$dinter <- as.numeric(format(t1066_UCh_w1_ybirth$DATE, '%d'))
Continuous_summary(var = t1066_UCh_w1_ybirth$dinter, missing_values = NA)
ggplot(t1066_UCh_w1_ybirth, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UCh1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_ybirth$id)
t1066_ds_UCh_w1$dintw <- car::recode(t1066_UCh_w1_ybirth$dinter, "NA=999")
t1066_ds_UCh_w1$dintw <- labelled(t1066_ds_UCh_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


```{r descript_UCh1}
Continuous_summary(var = t1066_ds_UCh_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```


#### Validation
```{r crosstabulation_UCh1}
BeforeH <- table(t1066_UCh_w1_ybirth$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_UCh_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```



#### Import to OPAL
```{r importOPAL_UCh1}
val_labels(t1066_ds_UCh_w1) <- NULL
#opal.assign.data(o, 't1066_ds_UCh_w1', t1066_ds_UCh_w1)
#opal.symbol_import(o,'t1066_ds_UCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UCh_w1 <- t1066_ds_UCh_w1
t1066_m_ds_UCh_w1$dintw <- car::recode(t1066_m_ds_UCh_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UCh_w1', t1066_m_ds_UCh_w1)
#opal.symbol_import(o,'t1066_m_ds_UCh_w1', project='_Athlos_Harm_Dataset')
```







### 10/66 - Urban China - Wave 2 

There is no variable.






### 10/66 - Rural China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`

```{r assign_RCh1}
opal.assign.table.tibble(o, 't1066_RCh_w1_dinter','10-66.1066-RuralChina-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_RCh1}
t1066_RCh_w1_dinter <- opal.execute(o,'t1066_RCh_w1_dinter')
t1066_RCh_w1_dinter$dinter <- as.numeric(format(t1066_RCh_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_RCh_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_RCh_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RCh1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_dinter$id)
t1066_ds_RCh_w1$dintw <- car::recode(t1066_RCh_w1_dinter$dinter, "NA=999")
t1066_ds_RCh_w1$dintw <- labelled(t1066_ds_RCh_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh1}
Continuous_summary(var = t1066_ds_RCh_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_RCh1}
BeforeH <- table(t1066_RCh_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_RCh_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```



#### Import to OPAL
```{r importOPAL_RCh1}
val_labels(t1066_ds_RCh_w1) <- NULL
#opal.assign.data(o, 't1066_ds_RCh_w1', t1066_ds_RCh_w1)
#opal.symbol_import(o,'t1066_ds_RCh_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RCh_w1 <- t1066_ds_RCh_w1
t1066_m_ds_RCh_w1$dintw <- car::recode(t1066_m_ds_RCh_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RCh_w1', t1066_m_ds_RCh_w1)
#opal.symbol_import(o,'t1066_m_ds_RCh_w1', project='_Athlos_Harm_Dataset')
```






### 10/66 - Rural China - Wave 2 

There is no variable.



### 10/66 - Dominican Republic - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_DR1}
opal.assign.table.tibble(o, 't1066_DR_w1_dinter','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_DR1}
t1066_DR_w1_dinter <- opal.execute(o,'t1066_DR_w1_dinter')
t1066_DR_w1_dinter$dinter <- as.numeric(format(t1066_DR_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_DR_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_DR_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_dinter$id)
t1066_ds_DR_w1$dintw <- car::recode(t1066_DR_w1_dinter$dinter, "NA=999")
t1066_ds_DR_w1$dintw <- labelled(t1066_ds_DR_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR1}
Continuous_summary(var = t1066_ds_DR_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_DR1}
BeforeH <- table(t1066_DR_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_DR_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```


#### Import to OPAL
```{r importOPAL_DR1}
val_labels(t1066_ds_DR_w1) <- NULL
#opal.assign.data(o, 't1066_ds_DR_w1', t1066_ds_DR_w1)
#opal.symbol_import(o,'t1066_ds_DR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_DR_w1 <- t1066_ds_DR_w1
t1066_m_ds_DR_w1$dintw <- car::recode(t1066_m_ds_DR_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_DR_w1', t1066_m_ds_DR_w1)
#opal.symbol_import(o,'t1066_m_ds_DR_w1', project='_Athlos_Harm_Dataset')
```








### 10/66 - Dominican Republic - Wave 2 

There is no variable.




### 10/66 - Venezuela - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_V1}
opal.assign.table.tibble(o, 't1066_Ven_w1_dinter','10-66.1066-Venezuela-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_V1}
t1066_Ven_w1_dinter <- opal.execute(o,'t1066_Ven_w1_dinter')
t1066_Ven_w1_dinter$dinter <- as.numeric(format(t1066_Ven_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_Ven_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_Ven_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_V1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_dinter$id)
t1066_ds_Ven_w1$dintw <- car::recode(t1066_Ven_w1_dinter$dinter, "NA=999")
t1066_ds_Ven_w1$dintw <- labelled(t1066_ds_Ven_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V1}
Continuous_summary(var = t1066_ds_Ven_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_V1}
BeforeH <- table(t1066_Ven_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_Ven_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```


#### Import to OPAL
```{r importOPAL_V1}
val_labels(t1066_ds_Ven_w1) <- NULL
#opal.assign.data(o, 't1066_ds_Ven_w1', t1066_ds_Ven_w1)
#opal.symbol_import(o,'t1066_ds_Ven_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_Ven_w1 <- t1066_ds_Ven_w1
t1066_m_ds_Ven_w1$dintw <- car::recode(t1066_m_ds_Ven_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_Ven_w1', t1066_m_ds_Ven_w1)
#opal.symbol_import(o,'t1066_m_ds_Ven_w1', project='_Athlos_Harm_Dataset')
```





### 10/66 - Venezuela - Wave 2 

There is no variable.




### 10/66 - Urban Peru - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`

```{r assign_UP}
opal.assign.table.tibble(o, 't1066_UP_w1_dinter','10-66.1066-UrbanPeru-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_UP1}
t1066_UP_w1_dinter <- opal.execute(o,'t1066_UP_w1_dinter')
t1066_UP_w1_dinter$dinter <- as.numeric(format(t1066_UP_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_UP_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_UP_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_dinter$id)
t1066_ds_UP_w1$dintw <- car::recode(t1066_UP_w1_dinter$dinter, "NA=999")
t1066_ds_UP_w1$dintw <- labelled(t1066_ds_UP_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP1}
Continuous_summary(var = t1066_ds_UP_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_UP1}
BeforeH <- table(t1066_UP_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_UP_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```



#### Import to OPAL
```{r importOPAL_UP1}
val_labels(t1066_ds_UP_w1) <- NULL
#opal.assign.data(o, 't1066_ds_UP_w1', t1066_ds_UP_w1)
#opal.symbol_import(o,'t1066_ds_UP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UP_w1 <- t1066_ds_UP_w1
t1066_m_ds_UP_w1$dintw <- car::recode(t1066_m_ds_UP_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UP_w1', t1066_m_ds_UP_w1)
#opal.symbol_import(o,'t1066_m_ds_UP_w1', project='_Athlos_Harm_Dataset')
```






### 10/66 - Urban Peru - Wave 2 

There is no variable.






### 10/66 - Rural Peru - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_RP}
opal.assign.table.tibble(o, 't1066_RP_w1_dinter','10-66.1066-RuralPeru-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_RP1}
t1066_RP_w1_dinter <- opal.execute(o,'t1066_RP_w1_dinter')
t1066_RP_w1_dinter$dinter <- as.numeric(format(t1066_RP_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_RP_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_RP_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RP1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_dinter$id)
t1066_ds_RP_w1$dintw <- car::recode(t1066_RP_w1_dinter$dinter, "NA=999")
t1066_ds_RP_w1$dintw <- labelled(t1066_ds_RP_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP1}
Continuous_summary(var = t1066_ds_RP_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_RP1}
BeforeH <- table(t1066_RP_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_RP_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```


#### Import to OPAL
```{r importOPAL_RP1}
val_labels(t1066_ds_RP_w1) <- NULL
#opal.assign.data(o, 't1066_ds_RP_w1', t1066_ds_RP_w1)
#opal.symbol_import(o,'t1066_ds_RP_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RP_w1 <- t1066_ds_RP_w1
t1066_m_ds_RP_w1$dintw <- car::recode(t1066_m_ds_RP_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RP_w1', t1066_m_ds_RP_w1)
#opal.symbol_import(o,'t1066_m_ds_RP_w1', project='_Athlos_Harm_Dataset')
```








### 10/66 - Rural Peru - Wave 2 

There is no variable.







### 10/66 - Urban Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_UM1}
opal.assign.table.tibble(o, 't1066_UM_w1_dinter','10-66.1066-UrbanMexico-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_UM1}
t1066_UM_w1_dinter <- opal.execute(o,'t1066_UM_w1_dinter')
t1066_UM_w1_dinter$dinter <- as.numeric(format(t1066_UM_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_UM_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_UM_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_dinter$id)
t1066_ds_UM_w1$dintw <- car::recode(t1066_UM_w1_dinter$dinter, "NA=999")
t1066_ds_UM_w1$dintw <- labelled(t1066_ds_UM_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM1}
Continuous_summary(var = t1066_ds_UM_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_UM1}
BeforeH <- table(t1066_UM_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_UM_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```



#### Import to OPAL
```{r importOPAL_UM1}
val_labels(t1066_ds_UM_w1) <- NULL
#opal.assign.data(o, 't1066_ds_UM_w1', t1066_ds_UM_w1)
#opal.symbol_import(o,'t1066_ds_UM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_UM_w1 <- t1066_ds_UM_w1
t1066_m_ds_UM_w1$dintw <- car::recode(t1066_m_ds_UM_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_UM_w1', t1066_m_ds_UM_w1)
#opal.symbol_import(o,'t1066_m_ds_UM_w1', project='_Athlos_Harm_Dataset')
```







### 10/66 - Urban Mexico - Wave 2

There is no variable.






### 10/66 - Rural Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`

```{r assign_RM1}
opal.assign.table.tibble(o, 't1066_RM_w1_dinter','10-66.1066-RuralMexico-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_RM1}
t1066_RM_w1_dinter <- opal.execute(o,'t1066_RM_w1_dinter')
t1066_RM_w1_dinter$dinter <- as.numeric(format(t1066_RM_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_RM_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_RM_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_dinter$id)
t1066_ds_RM_w1$dintw <- car::recode(t1066_RM_w1_dinter$dinter, "NA=999")
t1066_ds_RM_w1$dintw <- labelled(t1066_ds_RM_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM1}
Continuous_summary(var = t1066_ds_RM_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```


#### Validation
```{r crosstabulation_RM1}
BeforeH <- table(t1066_RM_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_RM_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```



#### Import to OPAL
```{r importOPAL_RM1}
val_labels(t1066_ds_RM_w1) <- NULL
#opal.assign.data(o, 't1066_ds_RM_w1', t1066_ds_RM_w1)
#opal.symbol_import(o,'t1066_ds_RM_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_RM_w1 <- t1066_ds_RM_w1
t1066_m_ds_RM_w1$dintw <- car::recode(t1066_m_ds_RM_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_RM_w1', t1066_m_ds_RM_w1)
#opal.symbol_import(o,'t1066_m_ds_RM_w1', project='_Athlos_Harm_Dataset')
```







### 10/66 - Rural Mexico - Wave 2 

There is no variable.






### 10/66 - Puerto Rico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DATE`
* Label: `date of baseline interview`


```{r assign_PR1}
opal.assign.table.tibble(o, 't1066_PR_w1_dinter','10-66.1066-PuertoRico-Baseline',
                         variables=list('DATE'), missings = TRUE)
```

```{r local_PR1}
t1066_PR_w1_dinter <- opal.execute(o,'t1066_PR_w1_dinter')
t1066_PR_w1_dinter$dinter <- as.numeric(format(t1066_PR_w1_dinter$DATE, '%d'))
Continuous_summary(var = t1066_PR_w1_dinter$dinter, missing_values = NA)
ggplot(t1066_PR_w1_dinter, aes(dinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_dinter$id)
t1066_ds_PR_w1$dintw <- car::recode(t1066_PR_w1_dinter$dinter, "NA=999")
t1066_ds_PR_w1$dintw <- labelled(t1066_ds_PR_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR1}
Continuous_summary(var = t1066_ds_PR_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation_PR1}
BeforeH <- table(t1066_PR_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(t1066_ds_PR_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
C
```

#### Quality estimation
No comments.


#### Import to OPAL
```{r importOPAL_PR1}
val_labels(t1066_ds_PR_w1) <- NULL
#opal.assign.data(o, 't1066_ds_PR_w1', t1066_ds_PR_w1)
#opal.symbol_import(o,'t1066_ds_PR_w1', project='_Athlos_Harm_Dataset')

t1066_m_ds_PR_w1 <- t1066_ds_PR_w1
t1066_m_ds_PR_w1$dintw <- car::recode(t1066_m_ds_PR_w1$dintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 't1066_m_ds_PR_w1', t1066_m_ds_PR_w1)
#opal.symbol_import(o,'t1066_m_ds_PR_w1', project='_Athlos_Harm_Dataset')
```




### 10/66 - Puerto Rico - Wave 2 

There is no variable.


```{r save, echo=FALSE}
#1
dintw <- t1066_ds_cuba_w1
save(dintw, file = "../RData/cuba_w1/dintw.RData")
rm(dintw)

#2
dintw <- t1066_ds_india_w1
save(dintw, file = "../RData/india_w1/dintw.RData")
rm(dintw)

dintw <- t1066_ds_india_w2
save(dintw, file = "../RData/india_w2/dintw.RData")
rm(dintw)

#3
dintw <- t1066_ds_UCh_w1
save(dintw, file = "../RData/UCh_w1/dintw.RData")
rm(dintw)

#4
dintw <- t1066_ds_RCh_w1
save(dintw, file = "../RData/RCh_w1/dintw.RData")
rm(dintw)

#5
dintw <- t1066_ds_DR_w1
save(dintw, file = "../RData/DR_w1/dintw.RData")
rm(dintw)

#6

dintw <- t1066_ds_Ven_w1
save(dintw, file = "../RData/Ven_w1/dintw.RData")
rm(dintw)

#7

dintw <- t1066_ds_UP_w1
save(dintw, file = "../RData/UP_w1/dintw.RData")
rm(dintw)

#8
dintw <- t1066_ds_RP_w1
save(dintw, file = "../RData/RP_w1/dintw.RData")
rm(dintw)

#9

dintw <- t1066_ds_UM_w1
save(dintw, file = "../RData/UM_w1/dintw.RData")
rm(dintw)

#10
dintw <- t1066_ds_RM_w1
save(dintw, file = "../RData/RM_w1/dintw.RData")
rm(dintw)

#11

dintw <- t1066_ds_PR_w1
save(dintw, file = "../RData/PR_w1/dintw.RData")
rm(dintw)



```



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
