---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `proxy`
* Variable label: `proxy help`
* Variable description: `Is any proxy helping to respond any question?`
* Domain: `Other administrative variables`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        |  No
1        |  Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Proxy"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
```
<!-- ########################################################## --> 

# Data process

## Cuba

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-Cuba-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cuba_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-Cuba-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local cuba_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo cuba_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_cuba_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-Cuba-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cuba_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-Cuba-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local cuba_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo cuba_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_cuba_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



## India

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-India-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign india_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-India-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local india_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo india_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_india_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


### Wave 2
No variable


## Urban China

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanChina-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UCh_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanChina-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UCh_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UCh_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UCh_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanChina-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UCh_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanChina-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UCh_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UCh_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UCh_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## Rural China

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralChina-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RCh_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralChina-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RCh_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RCh_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RCh_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralChina-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RCh_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralChina-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RCh_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RCh_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RCh_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




## Dominican Republic

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-DominicanRepublic-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign DR_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-DominicanRepublic-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local DR_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo DR_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_DR_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-DominicanRepublic-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign DR_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-DominicanRepublic-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local DR_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo DR_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_DR_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```




## Venezuela

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-Venezuela-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign Ven_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-Venezuela-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local Ven_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo Ven_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_Ven_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-Venezuela-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign Ven_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-Venezuela-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local Ven_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo Ven_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_Ven_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## Urban Peru

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanPeru-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UP_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanPeru-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UP_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UP_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UP_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanPeru-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UP_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanPeru-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UP_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UP_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UP_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



## Rural Peru

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralPeru-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RP_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralPeru-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RP_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RP_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RP_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralPeru-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RP_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralPeru-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RP_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RP_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RP_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## Urban Mexico

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanMexico-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UM_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanMexico-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UM_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UM_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UM_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-UrbanMexico-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UM_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-UrbanMexico-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local UM_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo UM_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_UM_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



## Rural Mexico

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralMexico-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RM_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralMexico-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RM_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RM_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RM_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-RuralMexico-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RM_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-RuralMexico-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local RM_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo RM_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_RM_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


## Puerto Rico

### Wave 1

#### Study-specific variable description

| **Name** | `PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-PuertoRico-Baseline` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign PR_w1, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-PuertoRico-Baseline',variables=list('PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local PR_w1, echo=F}
vbl <- tib$PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `PINTER with any other value greater than 1  is recoded as proxy=991 (CAPI/interviewer error)`
* `PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo PR_w1}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_PR_w1 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

### Wave 2

#### Study-specific variable description

| **Name** | `f_PINTER` |
|-|-|
| **Label** | `information from participant or informant?` |
| **Table name**  | `1066-PuertoRico-Followup` |
| **Categories** | `0 = participant only	; 1 = participant and informant` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign PR_w2, echo=F}
opal.assign.table.tibble(o, 'tib','10-66.1066-PuertoRico-Followup',variables=list('f_PINTER'), missings = T)
tib <- opal.execute(o,'tib')
```

```{r local PR_w2, echo=F}
vbl <- tib$f_PINTER
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(tib)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(tib, aes(x=factor(f_PINTER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

Recoding is as follows: 

* `f_PINTER with value 0 (participant only) is recoded as proxy=0 (no help)`
* `f_PINTER with value 1 (participant and informant) is recoded as proxy=1 (with help)`
* `f_PINTER with value 2 (??) is recoded as proxy=991 (CAPI/interviewer error)`
* `f_PINTER with value missing is recoded as proxy=999 (missing)`

```{r harmo PR_w2}
tib_ds <- tibble(id=tib$id)
tib_ds$proxy <- car::recode(tib$f_PINTER, "0=0; 1=1; 2:4=991; NA=999")
tib_ds$proxy <- labelled(tib_ds$proxy, labels = cat_label)
t1066_ds_PR_w2 <- tib_ds
```

#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}
vbl <- tib_ds$proxy
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(tib_ds, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


# Quality estimation

Some study-specific variables have values 2 or 4. We do not have find information in the original sources about the meaning of these values. As there are a very low number, we consider they are an error.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.t1066 <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(index in seq_along(l.t1066)){
  proxy <- l.t1066[[index]]
  save(proxy, file = paste0(datafolder,names(l.t1066)[index],"/proxy.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





