---
title: "Household ID"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/household_idDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/household_idDS.R')
```



# Data process



## Cuba


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-Cuba-Baseline` |
| **Categories** | `text` |


```{r assign cuba_w1, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline',variables=list('HOUSEID'), missings = T)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')

```


#### Harmonisation algorithm


**R script:**

```{r harmo cuba_w1}

t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$household_id <- as.character(t1066_cuba_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-Cuba-Followup` |
| **Categories** | `text` | 


```{r assign cuba_w2, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('HOUSEID'), missings = T)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')

```

#### Harmonisation algorithm


**R script:**

```{r harmo cuba_w2}

t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$household_id <- as.character(t1066_cuba_w2$HOUSEID)

```



## India


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-India-Baseline` |
| **Categories** | `text` |


```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('HOUSEID'), missings = T)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')

```


#### Harmonisation algorithm

**R script:**

```{r harmo india_w1}

t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$household_id <- as.character(t1066_india_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-India-Followup` |
| **Categories** | `text` |


```{r assign india_w2, echo=F}

opal.assign.table.tibble(o, 't1066_india_w2','10-66.1066-India-Followup',variables=list('HOUSEID'), missings = T)
t1066_india_w2 <- opal.execute(o,'t1066_india_w2')

```


#### Harmonisation algorithm

**R script:**

```{r harmo india_w2}

t1066_ds_india_w2 <- tibble(id=t1066_india_w2$id)
t1066_ds_india_w2$household_id <- as.character(t1066_india_w2$HOUSEID)

```



## Urban China


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanChina-Baseline` |
| **Categories** | `text` |


```{r assign UCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('HOUSEID'), missings = T)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')

```


#### Harmonisation algorithm


**R script:**

```{r harmo UCh_w1}

t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$household_id <- as.character(t1066_UCh_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanChina-Followup` |
| **Categories** | `text` | 



```{r assign UCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('HOUSEID'), missings = T)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')

```

#### Harmonisation algorithm

**R script:**

```{r harmo UCh_w2}

t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$household_id <- as.character(t1066_UCh_w2$HOUSEID)

```



## Rural China


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralChina-Baseline` |
| **Categories** | `text` |


```{r assign RCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('HOUSEID'), missings = T)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')

```


#### Harmonisation algorithm

**R script:**

```{r harmo RCh_w1}

t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$household_id <- as.character(t1066_RCh_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralChina-Followup` |
| **Categories** | `text` | 



```{r assign RCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('HOUSEID'), missings = T)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')

```


#### Harmonisation algorithm


**R script:**

```{r harmo RCh_w2}

t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$household_id <- as.character(t1066_RCh_w2$HOUSEID)

```



## Dominican Republic


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-DominicanRepublic-Baseline` |
| **Categories** | `text` |


```{r assign DR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline',variables=list('HOUSEID'), missings = T)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')

```


#### Harmonisation algorithm


**R script:**

```{r harmo DR_w1}

t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$household_id <- as.character(t1066_DR_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-DominicanRepublic-Followup` |
| **Categories** | `text` | 


```{r assign DR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('HOUSEID'), missings = T)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')

```

#### Harmonisation algorithm


**R script:**

```{r harmo DR_w2}

t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$household_id <- as.character(t1066_DR_w2$HOUSEID)

```



## Venezuela


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-Venezuela-Baseline` |
| **Categories** | `text` |


```{r assign Ven_w1, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('HOUSEID'), missings = T)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')

```



#### Harmonisation algorithm



**R script:**

```{r harmo Ven_w1}

t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$household_id <- as.character(t1066_Ven_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-Venezuela-Followup` |
| **Categories** | `text` | 


```{r assign Ven_w2, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('HOUSEID'), missings = T)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')

```


#### Harmonisation algorithm


**R script:**

```{r harmo Ven_w2}

t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$household_id <- as.character(t1066_Ven_w2$HOUSEID)

```



## Urban Peru


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanPeru-Baseline` |
| **Categories** | `text` |


```{r assign UP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('HOUSEID'), missings = T)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')

```

#### Harmonisation algorithm


**R script:**

```{r harmo UP_w1}

t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$household_id <- as.character(t1066_UP_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanPeru-Followup` |
| **Categories** | `text` | 



```{r assign UP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('HOUSEID'), missings = T)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')

```


#### Harmonisation algorithm


**R script:**

```{r harmo UP_w2}

t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$household_id <- as.character(t1066_UP_w2$HOUSEID)

```



## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` |
| **Categories** | `text` |


```{r assign RP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('HOUSEID'), missings = T)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')

```


#### Harmonisation algorithm

**R script:**

```{r harmo RP_w1}

t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$household_id <- as.character(t1066_RP_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralPeru-Followup` |
| **Categories** | `text` | 



```{r assign RP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('HOUSEID'), missings = T)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')

```


#### Harmonisation algorithm


**R script:**

```{r harmo RP_w2}

t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$household_id <- as.character(t1066_RP_w2$HOUSEID)

```



## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanMexico-Baseline` |
| **Categories** | `text` |


```{r assign UM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('HOUSEID'), missings = T)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')

```


#### Harmonisation algorithm

**R script:**

```{r harmo UM_w1}

t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$household_id <- as.character(t1066_UM_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-UrbanMexico-Followup` |
| **Categories** | `text` | 


```{r assign UM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('HOUSEID'), missings = T)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')

```

#### Harmonisation algorithm

**R script:**

```{r harmo UM_w2}

t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$household_id <- as.character(t1066_UM_w2$HOUSEID)

```



## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralMexico-Baseline` |
| **Categories** | `text` |



```{r assign RM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('HOUSEID'), missings = T)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')

```



#### Harmonisation algorithm

**R script:**

```{r harmo RM_w1}

t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$household_id <- as.character(t1066_RM_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-RuralMexico-Followup` |
| **Categories** | `text` | 



```{r assign RM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('HOUSEID'), missings = T)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')

```

#### Harmonisation algorithm

**R script:**

```{r harmo RM_w2}

t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$household_id <- as.character(t1066_RM_w2$HOUSEID)

```



## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-PuertoRico-Baseline` |
| **Categories** | `text` |


```{r assign PR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('HOUSEID'), missings = T)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')

```


#### Harmonisation algorithm


**R script:**

```{r harmo PR_w1}

t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$household_id <- as.character(t1066_PR_w1$HOUSEID)

```



### Wave 2


#### Study-specific variable description

| **Name** | `HOUSEID`|
|-|-|
| **Label** | `Household ID`|
| **Table name**  | `1066-PuertoRico-Followup` |
| **Categories** | `text` | 



```{r assign PR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('HOUSEID'), missings = T)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')

```


#### Harmonisation algorithm


**R script:**

```{r harmo PR_w2}

t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$household_id <- as.character(t1066_PR_w2$HOUSEID)

```




```{r final, echo=F}


lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  label(lb.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
}

for(name in names(lf.hds)) {
  label(lf.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
}


```




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  household_id <- lb.hds[[index]]
  save(household_id, file = paste0(datafolder,names(lb.hds)[index],"/household_id.RData"))
}

for(index in seq_along(lf.hds)){
  household_id <- lf.hds[[index]]
  save(household_id, file = paste0(datafolder,names(lf.hds)[index],"/household_id.RData"))
}


```
<!-- ########################################################## --> 




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





