---
title: "Arterial hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ah`
* Variable label: `Arterial hypertension`
* Variable description: `Arterial hypertension. Means of all diastolic blood pressure measures.`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no hypertension
1        | hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Arterial hypertension"
ds_label_all <- "Arterial hypertension. Means of all diastolic blood pressure measures."
```

# Data process

## KLOSA

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01C005`
* Label: `Whether or not high blood pressure diagnostic`
* Type of variable: `countinous`
* Categories: 
    + `1 = Yes`
    + `5 = no`


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_ah','KLOSA.w01_main_e',
                         variables=list('w01C005'), missings = TRUE)
KLOSA_ah <- opal.execute(o,'KLOSA_ah')
```

```{r local1, echo=FALSE}
vari <- KLOSA_ah$w01C005
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_ah, aes(x=factor(w01C005))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "no" into 0`
* `keep "Yes" into 1`
* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_ah$id)
KLOSA_ds_w1$ah <- car::recode(KLOSA_ah$w01C005, "5=0; NA=999")
KLOSA_ds_w1$ah <- labelled(KLOSA_ds_w1$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- KLOSA_ds_w1$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(KLOSA_ah$w01C005)[c(2,1)]
AfterH <- table(KLOSA_ds_w1$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1")
kable(C)
```

```{r importOPAL1, echo=FALSE}
#val_labels(KLOSA_ds_w1) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w1$ah) <- ds_label_all
ah <- KLOSA_ds_w1
save(ah, file = "../RData/w1/ah.RData")
rm(ah)
```




### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02C006`
* Label: `Since previous interview, whether been diagnosed with high blood pressure or not`
* Type of variable: `countinous`
* Categories: 
    + `1 = Yes`
    + `5 = no`


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_ah','KLOSA.w02_main_e_spss',
                         variables=list('w02C006'), missings = TRUE)
KLOSA_ah <- opal.execute(o,'KLOSA_ah')
```

```{r local2, echo=FALSE}
vari <- KLOSA_ah$w02C006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_ah, aes(x=factor(w02C006))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "no" into 0`
* `keep "Yes" into 1`
* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_ah$id)
KLOSA_ds_w2$ah <- car::recode(KLOSA_ah$w02C006, "5=0; NA=999")
KLOSA_ds_w2$ah <- labelled(KLOSA_ds_w2$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- KLOSA_ds_w2$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(KLOSA_ah$w02C006, useNA = 'ifany')[c(2,1,3)]
AfterH <- table(KLOSA_ds_w2$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1", "NA->999")
kable(C)
```


```{r importOPAL2, echo=FALSE}
#val_labels(KLOSA_ds_w2) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w2$ah) <- ds_label_all
ah <- KLOSA_ds_w2
save(ah, file = "../RData/w2/ah.RData")
rm(ah)
```




### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03C006`
* Label: `Whether or not high blood pressure diagnostic since previous interview`
* Type of variable: `countinous`
* Categories: 
    + `1 = Yes`
    + `5 = no`


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_ah','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03C006'), missings = TRUE)
KLOSA_ah <- opal.execute(o,'KLOSA_ah')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_ah$id <- substr(KLOSA_ah$id,1,nchar(KLOSA_ah$id)-2)
```

```{r local3, echo=FALSE}
vari <- KLOSA_ah$w03C006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_ah, aes(x=factor(w03C006))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "no" into 0`
* `keep "Yes" into 1`
* `NA into 999`

**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_ah$id)
KLOSA_ds_w3$ah <- car::recode(KLOSA_ah$w03C006, "5=0; NA=999")
KLOSA_ds_w3$ah <- labelled(KLOSA_ds_w3$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- KLOSA_ds_w3$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(KLOSA_ah$w03C006, useNA = 'ifany')[c(2,1,3)]
AfterH <- table(KLOSA_ds_w3$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1", "NA->999")
kable(C)
```

```{r importOPAL3, echo=FALSE}
#val_labels(KLOSA_ds_w3) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w3$ah) <- ds_label_all
ah <- KLOSA_ds_w3
save(ah, file = "../RData/w3/ah.RData")
rm(ah)
```






### Wave 4 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04C006`
* Label: `Whether or not high blood pressure diagnostic since previous interview`
* Type of variable: `countinous`
* Categories: 
    + `1 = Yes`
    + `5 = no`

```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'KLOSA_ah','KLOSA.w04_main_e_spss',
                         variables=list('w04C006'), missings = TRUE)
KLOSA_ah <- opal.execute(o,'KLOSA_ah')
```

```{r local4, echo=FALSE}
vari <- KLOSA_ah$w04C006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_ah, aes(x=factor(w04C006))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 "no" into 0`
* `keep "Yes" into 1`
* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_ah$id)
KLOSA_ds_w4$ah <- car::recode(KLOSA_ah$w04C006, "5=0; NA=999")
KLOSA_ds_w4$ah <- labelled(KLOSA_ds_w4$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- KLOSA_ds_w4$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation4, echo=FALSE}
BeforeH <- table(KLOSA_ah$w04C006, useNA = 'ifany')[c(2,1,3)]
AfterH <- table(KLOSA_ds_w4$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1", "NA->999")
kable(C)
```

```{r importOPAL4, echo=FALSE}
#val_labels(KLOSA_ds_w4) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
label(KLOSA_ds_w4$ah) <- ds_label_all
ah <- KLOSA_ds_w4
save(ah, file = "../RData/w4/ah.RData")
rm(ah)
```


# Quality estimation

The variable chosen (C006) to harmonized arterial hypertension as a physical measure 
doesn't fit in the definition of the variable, but it was decided to take it is better
than nothing.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```