---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `weight`
* Variable label: `weight of the participant in kg`
* Variable description: `Weight should be collected in kilograms. It should be determined wheather the  variable was collected through a self reported measure or an anthropometric test`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01C093`
* Label: `Weight (unit : Kilogram)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_weig','KLOSA.w01_main_e', variables=list('w01C093'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_weig <- opal.execute(o,'KLOSA_w1_weig')
Continuous_summary(var = KLOSA_w1_weig$w01C093, missing_values = c(-9,-8))
ggplot(KLOSA_w1_weig, aes(w01C093)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

There are values smallers than 85 that are going to be considered as mistakes and they will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_weig$id)
KLOSA_ds_w1$weight <- car::recode(KLOSA_w1_weig$w01C093, "NA=999; -9=998; -8=997")
KLOSA_ds_w1$weight <- labelled(KLOSA_ds_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Continuous_summary(var = KLOSA_ds_w1$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation1, echo=F}
```

```{r importOPAL1, echo=F}
#val_labels(KLOSA_ds_w1) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w1', KLOSA_ds_w1)
#opal.symbol_import(o,'KLOSA_ds_w1', project='_Athlos_Harm_Dataset')
weight <- KLOSA_ds_w1
save(weight, file = "../RData/w1/weight.RData")
rm(weight)
```




### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02C105`
* Label: `Height (unit : Centimeter)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Do not know`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_weig','KLOSA.w02_main_e_spss',
                         variables=list('w02C105'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_weig <- opal.execute(o,'KLOSA_w2_weig')
Continuous_summary(var = KLOSA_w2_weig$w02C105, missing_values = c(-9))
ggplot(KLOSA_w2_weig, aes(w02C105)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Do not know" into 998`
* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_weig$id)
KLOSA_ds_w2$weight <- car::recode(KLOSA_w2_weig$w02C105, "NA=999; -9=998")
KLOSA_ds_w2$weight <- labelled(KLOSA_ds_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Continuous_summary(var = KLOSA_ds_w2$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation2, echo=F}
```


```{r importOPAL2, echo=F}
#val_labels(KLOSA_ds_w2) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
weight <- KLOSA_ds_w2
save(weight, file = "../RData/w2/weight.RData")
rm(weight)
```




### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03C105`
* Label: `Height (unit : Centimeter)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_weig','KLOSA.w03_main_e_spss_albert',  variables=list('w03C105'), missings = TRUE)
KLOSA_w3_weig <- opal.execute(o,'KLOSA_w3_weig')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_weig$id <- substr(KLOSA_w3_weig$id,1,nchar(KLOSA_w3_weig$id)-2)
```

```{r local3, echo=F}
Continuous_summary(var = KLOSA_w3_weig$w03C105, missing_values = c(-9, -8))
ggplot(KLOSA_w3_weig, aes(w03C105)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_weig$id)
KLOSA_ds_w3$weight <- car::recode(KLOSA_w3_weig$w03C105, "NA=999; -8=997; -9=998")
KLOSA_ds_w3$weight <- labelled(KLOSA_ds_w3$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Continuous_summary(var = KLOSA_ds_w3$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(30,165) 
```

#### Validation
```{r crosstabulation3, echo=F}
```


```{r importOPAL3, echo=F}
#val_labels(KLOSA_ds_w3) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
weight <- KLOSA_ds_w3
save(weight, file = "../RData/w3/weight.RData")
rm(weight)
```






### Wave 4 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04C105`
* Label: `Height (unit : Centimeter)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Do not know`
    + `-8 = Refuse to answer`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_weig','KLOSA.w04_main_e_spss',
                         variables=list('w04C105'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_weig <- opal.execute(o,'KLOSA_w4_weig')
Continuous_summary(var = KLOSA_w4_weig$w04C105, missing_values = c(-9, -8))
ggplot(KLOSA_w4_weig, aes(w04C105)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -9 "Do not know" into 998`
* `recode -8 "Refuse to answer" into 997`
* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_weig$id)
KLOSA_ds_w4$weight <- car::recode(KLOSA_w4_weig$w04C105, "NA=999; -8=997; -9=998")
KLOSA_ds_w4$weight <- labelled(KLOSA_ds_w4$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Continuous_summary(var = KLOSA_ds_w4$weight, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("weight") + ylab("Frequency") + xlim(30,165) 
```

#### Validation
```{r crosstabulation4, echo=F}
```


```{r importOPAL4, echo=F}
#val_labels(KLOSA_ds_w4) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
weight <- KLOSA_ds_w4
save(weight, file = "../RData/w4/weight.RData")
rm(weight)
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```