---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ############################################ --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################ --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `obesity`
* Variable label: `Presence of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2`
* Variable description: `the BMI variable should be created by dividing weight and hiegh variables by means of the following equation= weight (kg)/height(m)^2. Then, the Obesity variable should be generated according to the WHO cutoff point for BMI classification`
* Domain: `Physical measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | not obese
1        | obese

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


```{r lab, echo=FALSE}
ds_label <- "Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2"
```


## Korea

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w01bmi`
* Label: `BMI`
* Type of variable: `countinous`


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_bmi','KLOSA.w01_main_e',
                         variables=list('w01bmi'), missings = TRUE)
KLOSA_bmi <- opal.execute(o,'KLOSA_bmi')
```

```{r local_aksst1, echo=F}
Continuous_summary(KLOSA_bmi[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_bmi, aes(x=KLOSA_bmi[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10, 70)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_bmi$id)
KLOSA_ds_w1$obesity <- car::recode(KLOSA_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999")
KLOSA_ds_w1$obesity <- labelled(KLOSA_ds_w1[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
Categorical_summary(var = KLOSA_ds_w1[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(KLOSA_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab1, echo=F}
BeforeH <- c(sum(na.omit(KLOSA_bmi[[2]])<30),sum(na.omit(KLOSA_bmi[[2]])>=30 & na.omit(KLOSA_bmi[[2]])<=900), sum(is.na(KLOSA_bmi)) )
AfterH <- table(KLOSA_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```

```{r read1, include=FALSE}
rm(KLOSA_bmi)
```

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w02bmi`
* Label: `BMI`
* Type of variable: `countinous`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_bmi','KLOSA.w02_main_e_spss',
                         variables=list('w02bmi'), missings = TRUE)
KLOSA_bmi <- opal.execute(o,'KLOSA_bmi')
```

```{r local2, echo=F}
Continuous_summary(KLOSA_bmi[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_bmi, aes(KLOSA_bmi[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_bmi$id)
KLOSA_ds_w2$obesity <- car::recode(KLOSA_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
KLOSA_ds_w2$obesity <- labelled(KLOSA_ds_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = KLOSA_ds_w2[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(KLOSA_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab2, echo=F}
BeforeH <- c(sum(na.omit(KLOSA_bmi[[2]])<30),sum(na.omit(KLOSA_bmi[[2]])>=30 & na.omit(KLOSA_bmi[[2]])<=900), sum(is.na(KLOSA_bmi)))
AfterH <- table(KLOSA_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```

```{r read2, include=FALSE}
rm(KLOSA_bmi)
```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w03bmi`
* Label: `BMI`
* Type of variable: `countinous`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_bmi','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03bmi'), missings = TRUE)
KLOSA_bmi <- opal.execute(o,'KLOSA_bmi')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_bmi$id <- substr(KLOSA_bmi$id,1,nchar(KLOSA_bmi$id)-2)
```

```{r local4, echo=F}
Continuous_summary(KLOSA_bmi[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_bmi, aes(x=factor(KLOSA_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

```{r harmo4}
KLOSA_ds_w3 <- tibble(id=KLOSA_bmi$id)
KLOSA_ds_w3$obesity <- car::recode(KLOSA_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
KLOSA_ds_w3$obesity <- labelled(KLOSA_ds_w3[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = KLOSA_ds_w3[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(KLOSA_ds_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab4, echo=F}
BeforeH <- c(sum(na.omit(KLOSA_bmi[[2]])<30),sum(na.omit(KLOSA_bmi[[2]])>=30 & na.omit(KLOSA_bmi[[2]])<=900), sum(is.na(KLOSA_bmi)))
AfterH <- table(KLOSA_ds_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1", "NA->999") 
kable(C)
```

```{r read4, include=FALSE}
rm(KLOSA_bmi)
```


### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w04bmi`
* Label: `BMI`
* Type of variable: `countinous`


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_bmi','KLOSA.w04_main_e_spss',
                         variables=list('w04bmi'), missings = TRUE)
KLOSA_bmi <- opal.execute(o,'KLOSA_bmi')
```

```{r local5, echo=F}
Continuous_summary(KLOSA_bmi[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_bmi, aes(x=factor(KLOSA_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `BMI>=1000 into 999`
* `NA into 999`

```{r harmo5}
KLOSA_ds_w4 <- tibble(id=KLOSA_bmi$id)
KLOSA_ds_w4$obesity <- car::recode(KLOSA_bmi[[2]], "lo:29.9999999=0; 30:900=1; NA=999; 1000:hi=999")
KLOSA_ds_w4$obesity <- labelled(KLOSA_ds_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = KLOSA_ds_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(KLOSA_ds_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab5, echo=F}
BeforeH <- c(sum(na.omit(KLOSA_bmi[[2]])<30),sum(na.omit(KLOSA_bmi[[2]])>=30 & na.omit(KLOSA_bmi[[2]])<=900), sum(is.na(KLOSA_bmi)))
AfterH <- table(KLOSA_ds_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```

```{r read5, include=FALSE}
rm(KLOSA_bmi)
```


```{r importOPAL, echo=FALSE}
obesity <- KLOSA_m_ds_w1   <- KLOSA_ds_w1
save(obesity, file = "../RData/w1/obesity.RData")
rm(obesity)

obesity <- KLOSA_m_ds_w2   <- KLOSA_ds_w2
save(obesity, file = "../RData/w2/obesity.RData")
rm(obesity)

obesity <- KLOSA_m_ds_w3   <- KLOSA_ds_w3
save(obesity, file = "../RData/w3/obesity.RData")
rm(obesity)

obesity <- KLOSA_m_ds_w4   <- KLOSA_ds_w4
save(obesity, file = "../RData/w4/obesity.RData")
rm(obesity)



l.hds <- list(KLOSA_ds_w1 = KLOSA_ds_w1 , KLOSA_ds_w2 = KLOSA_ds_w2, KLOSA_ds_w3 = KLOSA_ds_w3, KLOSA_ds_w4=KLOSA_ds_w4)

m.hds <- list(KLOSA_m_ds_w1 = KLOSA_m_ds_w1 , KLOSA_m_ds_w2 = KLOSA_m_ds_w2, KLOSA_m_ds_w3 = KLOSA_m_ds_w3, KLOSA_m_ds_w4 = KLOSA_m_ds_w4)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1, "Respond, died after this wave"=2, "Respond(proxy), died"=3, "No respond, alive"=4, "No respond, died this wave"=5, "No respond, died previous waves"=6, "No respond, dropped from sample"=7))

  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}
```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}

# Table HRS
t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]))
names(t.hds)<-c("val", "label", "Wave1", "Wave2", "Wave3", "Wave4")
kable(t.hds)
```


# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.





```{r closeRsession, echo=FALSE}
opal.logout(o)
```