---
title: "Emotional support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/emot_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/emot_supDS.R')
```

<!-- ########################################################## --> 

# Data process



## Poland

### Wave 1 

All data in the variable found, `p56`, is missing.


### Wave 2

Not found.

## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p56a`
* Label: `Rely on friends first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56b`
* Label: `Rely on relatives first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56c`
* Label: `Rely on employer first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56i`
* Label: `Rely on no-one first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56j`
* Label: `Rely on other first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`


```{r assignc1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_emot_sup','HAPIEE.Cz_baseline_etic',  variables=list('p56a','p56b','p56c','p56i','p56j'), missings = TRUE)
HAPIEE_cz_w1_emot_sup <- opal.execute(o,'HAPIEE_cz_w1_emot_sup')
```

```{r localc1, echo=F}
Categorical_summary(var = HAPIEE_cz_w1_emot_sup$p56a, missing_values = NA)
ggplot(HAPIEE_cz_w1_emot_sup, aes(x=factor(p56a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on friends first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_cz_w1_emot_sup$p56b, missing_values = NA)
ggplot(HAPIEE_cz_w1_emot_sup, aes(x=factor(p56b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on relatives first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_cz_w1_emot_sup$p56c, missing_values = NA)
ggplot(HAPIEE_cz_w1_emot_sup, aes(x=factor(p56c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on employer first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_cz_w1_emot_sup$p56i, missing_values = NA)
ggplot(HAPIEE_cz_w1_emot_sup, aes(x=factor(p56i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on no-one first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_cz_w1_emot_sup$p56j, missing_values = NA)
ggplot(HAPIEE_cz_w1_emot_sup, aes(x=factor(p56j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on other first of all when having problems") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any variable equals 1 or p56i=2 then 1`
* `if all are equal 2 but p56i=1 then 0`
* `9 or NA into 999`

**R script:**

```{r harmoc1}
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1_emot_sup$id)

HAPIEE_cz_w1_emot_sup$p56a <- car::recode(as.vector(HAPIEE_cz_w1_emot_sup$p56a), "NA='-999'")
HAPIEE_cz_w1_emot_sup$p56b <- car::recode(as.vector(HAPIEE_cz_w1_emot_sup$p56b), "NA='-999'")
HAPIEE_cz_w1_emot_sup$p56c <- car::recode(as.vector(HAPIEE_cz_w1_emot_sup$p56c), "NA='-999'")
HAPIEE_cz_w1_emot_sup$p56i <- car::recode(as.vector(HAPIEE_cz_w1_emot_sup$p56i), "NA='-999'")
HAPIEE_cz_w1_emot_sup$p56j <- car::recode(as.vector(HAPIEE_cz_w1_emot_sup$p56j), "NA='-999'")

HAPIEE_ds_cz_w1$emot_sup <- c(NA) # I think it is required
for(i in 1:dim(HAPIEE_cz_w1_emot_sup)[1]){
  if( HAPIEE_cz_w1_emot_sup$p56a[i] == "Yes" | HAPIEE_cz_w1_emot_sup$p56b[i] == "Yes" | HAPIEE_cz_w1_emot_sup$p56c[i] == "Yes" |
      HAPIEE_cz_w1_emot_sup$p56i[i] == "No" | HAPIEE_cz_w1_emot_sup$p56j[i] == "Yes" ) {
    HAPIEE_ds_cz_w1$emot_sup[i] = 1 }
  else if( HAPIEE_cz_w1_emot_sup$p56a[i] == "No" & HAPIEE_cz_w1_emot_sup$p56b[i] == "No" & HAPIEE_cz_w1_emot_sup$p56c[i] == "No" &
      HAPIEE_cz_w1_emot_sup$p56i[i] == "Yes" & HAPIEE_cz_w1_emot_sup$p56j[i] == "No" ) {
    HAPIEE_ds_cz_w1$emot_sup[i] = 0 }
  else if( HAPIEE_cz_w1_emot_sup$p56a[i] == 9 & HAPIEE_cz_w1_emot_sup$p56b[i] == 9 & HAPIEE_cz_w1_emot_sup$p56c[i] == 9 &
      HAPIEE_cz_w1_emot_sup$p56i[i] == 9 & HAPIEE_cz_w1_emot_sup$p56j[i] == 9 ) {
    HAPIEE_ds_cz_w1$emot_sup[i] = 999 }
}

HAPIEE_ds_cz_w1$emot_sup <- car::recode(as.vector(HAPIEE_ds_cz_w1$emot_sup), "NA='999'")
HAPIEE_ds_cz_w1$emot_sup <- labelled(HAPIEE_ds_cz_w1$emot_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptc1, echo=F}
Categorical_summary(var = HAPIEE_ds_cz_w1$emot_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Receives emotional support from someone") + ylab("Frequency")
```

#### Validation
```{r crosstabulationc1, echo=F}

```

### Wave 2

Not found.

## Lithuania
 

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p56a`
* Label: `Rely on friends first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56b`
* Label: `Rely on relatives first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56c`
* Label: `Rely on employer first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56i`
* Label: `Rely on no-one first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    
* Name: `p56j`
* Label: `Rely on other first of all when having problems`
* Categories: 
    + `1 = Yes`
    + `2 = No`


```{r assignl1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_emot_sup','HAPIEE.Li_baseline_etic',  variables=list('p56a','p56b','p56c','p56i','p56j'), missings = TRUE)
HAPIEE_li_w1_emot_sup <- opal.execute(o,'HAPIEE_li_w1_emot_sup')
```

```{r locall1, echo=F}
Categorical_summary(var = HAPIEE_li_w1_emot_sup$p56a, missing_values = NA)
ggplot(HAPIEE_li_w1_emot_sup, aes(x=factor(p56a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on friends first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_li_w1_emot_sup$p56b, missing_values = NA)
ggplot(HAPIEE_li_w1_emot_sup, aes(x=factor(p56b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on relatives first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_li_w1_emot_sup$p56c, missing_values = NA)
ggplot(HAPIEE_li_w1_emot_sup, aes(x=factor(p56c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on employer first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_li_w1_emot_sup$p56i, missing_values = NA)
ggplot(HAPIEE_li_w1_emot_sup, aes(x=factor(p56i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on no-one first of all when having problems") + ylab("Frequency")
Categorical_summary(var = HAPIEE_li_w1_emot_sup$p56j, missing_values = NA)
ggplot(HAPIEE_li_w1_emot_sup, aes(x=factor(p56j))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Rely on other first of all when having problems") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any variable equals 1 or p56i=2 then 1`
* `if all are equal 2 but p56i=1 then 0`
* `NA into 999`

**R script:**

```{r harmol1}
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1_emot_sup$id)

HAPIEE_li_w1_emot_sup$p56a <- car::recode(as.vector(HAPIEE_li_w1_emot_sup$p56a), "NA='-999'")
HAPIEE_li_w1_emot_sup$p56b <- car::recode(as.vector(HAPIEE_li_w1_emot_sup$p56b), "NA='-999'")
HAPIEE_li_w1_emot_sup$p56c <- car::recode(as.vector(HAPIEE_li_w1_emot_sup$p56c), "NA='-999'")
HAPIEE_li_w1_emot_sup$p56i <- car::recode(as.vector(HAPIEE_li_w1_emot_sup$p56i), "NA='-999'")
HAPIEE_li_w1_emot_sup$p56j <- car::recode(as.vector(HAPIEE_li_w1_emot_sup$p56j), "NA='-999'")

HAPIEE_ds_li_w1$emot_sup <- c(NA) # I think it is required
for(i in 1:dim(HAPIEE_li_w1_emot_sup)[1]){
  if( HAPIEE_li_w1_emot_sup$p56a[i] == 'Yes' | HAPIEE_li_w1_emot_sup$p56b[i] == 'Yes' | HAPIEE_li_w1_emot_sup$p56c[i] == 'Yes' |
      HAPIEE_li_w1_emot_sup$p56i[i] == 'No' | HAPIEE_li_w1_emot_sup$p56j[i] == 'Yes' ) {
    HAPIEE_ds_li_w1$emot_sup[i] = 1 }
  else if( HAPIEE_li_w1_emot_sup$p56a[i] == 'No' & HAPIEE_li_w1_emot_sup$p56b[i] == 'No' & HAPIEE_li_w1_emot_sup$p56c[i] == 'No' &
      HAPIEE_li_w1_emot_sup$p56i[i] == 'Yes' & HAPIEE_li_w1_emot_sup$p56j[i] == 'No' ) {
    HAPIEE_ds_li_w1$emot_sup[i] = 0 }
}

HAPIEE_ds_li_w1$emot_sup <- car::recode(as.vector(HAPIEE_ds_li_w1$emot_sup), "NA='999'")
HAPIEE_ds_li_w1$emot_sup <- labelled(HAPIEE_ds_li_w1$emot_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descriptl1, echo=F}
Categorical_summary(var = HAPIEE_ds_li_w1$emot_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_ds_li_w1, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Receives emotional support from someone") + ylab("Frequency")
```

#### Validation
```{r crosstabulationl1, echo=F}

```





```{r final, echo=F}

lb.hds <- list(cz_w1 = HAPIEE_ds_cz_w1, li_w1 = HAPIEE_ds_li_w1)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


l.hds <- c(lb.hds)
ln.hds <- names(lb.hds)

```

## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size",sapply(ln.hds,function(wave) length(l.hds[[wave]][[1]])))
names(t.hds)<-c("val", "label", "Czech_Republic_W1","Lithuania_W1")
kable(t.hds)
  
```

# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  emot_sup <- l.hds[[index]]
  save(emot_sup, file = paste0(datafolder,names(l.hds)[index],"/emot_sup.RData"))
}

```
<!-- ########################################################## --> 


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
