---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `confidant`
* Variable label: `Has friend(s)/confidant`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process


## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p58`
* Label: `How often do you visit friends`
* Categories: 
    + `1.0 = Several times a week`
    + `2.0 = About once a week`
    + `3.0 = Several times a month`
    + `4.0 = About once a month`
    + `5.0 = Less than once a month`
    + `6.0 = I do not have friends`


* Description: 
```{r assign1cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_confidant','HAPIEE.Cz_baseline_etic', variables=list('p58'), missings = TRUE)
```

```{r local1cz, echo=F}
HAPIEE_cz_w1_confidant <- opal.execute(o,'HAPIEE_cz_w1_confidant')
vari <- HAPIEE_cz_w1_confidant$p58
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w1_confidant$p58, missing_values = NA)
ggplot(HAPIEE_cz_w1_confidant, aes(x=factor(p58))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often do you visit friends?") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 I do not have friends into 0`
* `1:5 into 1`
* `NA into 999`

 

**R script:** 
```{r harmo1cz, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_confidant$id)
HAPIEE_cz_ds_w1$confidant <- car::recode(as.vector(HAPIEE_cz_w1_confidant$p58), "'I do not have friends'='0';'About once a month'='1';'About once a week'='1';'Less than once a month'='1';'Several times a month'='1';'Several times a week'='1'; NA='999'")
HAPIEE_cz_ds_w1$confidant <- labelled(HAPIEE_cz_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1cz, echo=F}
vari <- HAPIEE_cz_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$confidant)
BeforeH <- table(HAPIEE_cz_w1_confidant$p58, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(3,1,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 


## Wave 2
Not found.

## Lithuania

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p58`
* Label: `How often do you visit friends`
* Categories: 
    + `1.0 = Several times a week`
    + `2.0 = About once a week`
    + `3.0 = Several times a month`
    + `4.0 = About once a month`
    + `5.0 = Less than once a month`
    + `6.0 = I do not have friends`


* Description: 
```{r assign1li, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_confidant','HAPIEE.Li_baseline_etic', variables=list('p58'), missings = TRUE)
```

```{r local1li, echo=F}
HAPIEE_li_w1_confidant <- opal.execute(o,'HAPIEE_li_w1_confidant')
vari <- HAPIEE_li_w1_confidant$p58
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_li_w1_confidant$p58, missing_values = NA)
ggplot(HAPIEE_li_w1_confidant, aes(x=factor(p58))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often do you visit friends?") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 I do not have friends into 0`
* `1:5 into 1`
* `.b, .c, NA into 999`

 

**R script:** 
```{r harmo1li, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_confidant$id)
HAPIEE_li_ds_w1$confidant <- car::recode(as.vector(HAPIEE_li_w1_confidant$p58), "'I do not have friends'='0'; 'About once a month'='1';'About once a week'='1';'Less than once a month'='1';'Several times a month'='1';'Several times a week'='1';'.b'='999'; '.c'='999'; NA='999'")
HAPIEE_li_ds_w1$confidant <- labelled(HAPIEE_li_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1li, echo=F}
vari <- HAPIEE_li_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1li, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$confidant)
BeforeH <- table(HAPIEE_li_w1_confidant$p58,useNA='ifany')
C <- rbind(BeforeH,AfterH)
BeforeH[[10]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]])
BeforeH[[11]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[9]])
BeforeH <- BeforeH[c(5,10,11)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1",".b, .c or NA->999") 
kable(C)
```


## Poland


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p58`
* Label: `How often do you visit friends`
* Categories: 
    + `1.0 = Several times a week`
    + `2.0 = About once a week`
    + `3.0 = Several times a month`
    + `4.0 = About once a month`
    + `5.0 = Less than once a month`
    + `6.0 = I do not have friends`


* Description: 
```{r assign1pol, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_confidant','HAPIEE.Po_baseline_etic', variables=list('p58'), missings = TRUE)
```

```{r local1pol, echo=F}
HAPIEE_pol_w1_confidant <- opal.execute(o,'HAPIEE_pol_w1_confidant')
vari <- HAPIEE_pol_w1_confidant$p58
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w1_confidant$p58, missing_values = NA)
ggplot(HAPIEE_pol_w1_confidant, aes(x=factor(p58))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often do you visit friends?") + ylab("Frequency") + 
theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6 I do not have friends into 0`
* `1:5 into 1`
* `NA into 999`

 

**R script:** 
```{r harmo1pol, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_confidant$id)
HAPIEE_pol_ds_w1$confidant <- car::recode(as.vector(HAPIEE_pol_w1_confidant$p58), "'I do not have friends'='0';'About once a month'='1';'About once a week'='1';'Less than once a month'='1';'Several times a month'='1';'Several times a week'='1'; NA='999'")
HAPIEE_pol_ds_w1$confidant <- labelled(HAPIEE_pol_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1pol, echo=F}
vari <- HAPIEE_pol_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1pol, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$confidant)
BeforeH <- table(HAPIEE_pol_w1_confidant$p58, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(3,1,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

 
 

## Wave 2
Not found.


```{r save, echo=FALSE}
confidant <- HAPIEE_cz_ds_w1
save(confidant, file = "../RData/cz_w1/confidant.RData")
rm(confidant)

confidant <- HAPIEE_li_ds_w1
save(confidant, file = "../RData/li_w1/confidant.RData")
rm(confidant)

confidant <- HAPIEE_pol_ds_w1
save(confidant, file = "../RData/pol_w1/confidant.RData")
rm(confidant)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```