---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `divorce`
* Variable label: `Experience of divorce/separation`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`


* Description: 
```{r assign1 cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_divorce','HAPIEE.Cz_baseline_etic',variables=list('q4'), missings = TRUE)
```

```{r local1 cz, echo=F}
HAPIEE_cz_w1_divorce <- opal.execute(o,'HAPIEE_cz_w1_divorce')
vari <- HAPIEE_cz_w1_divorce$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w1_divorce$q4, missing_values = NA)
ggplot(HAPIEE_cz_w1_divorce, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1 cz, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_divorce$id)

HAPIEE_cz_w1_divorce$q4 <- car::recode(as.vector(HAPIEE_cz_w1_divorce$q4), "NA='-999'")

HAPIEE_cz_ds_w1$divorce <- c(NA) 
for(i in 1:length(HAPIEE_cz_ds_w1$divorce)){
  if(HAPIEE_cz_w1_divorce$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_cz_ds_w1$divorce[i] ='1'}
  if(HAPIEE_cz_w1_divorce$q4[i] == 'Cohabiting'){HAPIEE_cz_ds_w1$divorce[i] ='0'}
  if(HAPIEE_cz_w1_divorce$q4[i] == 'Married'){HAPIEE_cz_ds_w1$divorce[i] ='0'}
  if(HAPIEE_cz_w1_divorce$q4[i] == 'Single'){HAPIEE_cz_ds_w1$divorce[i] ='0'}
  if(HAPIEE_cz_w1_divorce$q4[i] == 'Widowed'){HAPIEE_cz_ds_w1$divorce[i] ='0'}
}

HAPIEE_cz_ds_w1$divorce <- car::recode(as.vector(HAPIEE_cz_ds_w1$divorce), "NA='999'")
HAPIEE_cz_ds_w1$divorce <- labelled(HAPIEE_cz_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cz, echo=F}
vari <- HAPIEE_cz_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$divorce)
BeforeH <- table(HAPIEE_cz_w1_divorce$q4, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(2,3,5,6)])
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[3]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```

### Wave 2

Not found.

## Lithuania

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`

* Description: 
```{r assign1 li, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_divorce','HAPIEE.Li_baseline_etic', variables=list('q4'), missings = TRUE)
```

```{r local1 li, echo=F}
HAPIEE_li_w1_divorce <- opal.execute(o,'HAPIEE_li_w1_divorce')
vari <- HAPIEE_li_w1_divorce$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_li_w1_divorce$q4, missing_values = NA)
ggplot(HAPIEE_li_w1_divorce, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1 li, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_divorce$id)

HAPIEE_li_w1_divorce$q4 <- car::recode(as.vector(HAPIEE_li_w1_divorce$q4), "NA='-999'")

HAPIEE_li_ds_w1$divorce <- c(NA) 
for(i in 1:length(HAPIEE_li_ds_w1$divorce)){
  if(HAPIEE_li_w1_divorce$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_li_ds_w1$divorce[i] ='1'}
  if(HAPIEE_li_w1_divorce$q4[i] == 'Cohabiting'){HAPIEE_li_ds_w1$divorce[i] ='0'}
  if(HAPIEE_li_w1_divorce$q4[i] == 'Married'){HAPIEE_li_ds_w1$divorce[i] ='0'}
  if(HAPIEE_li_w1_divorce$q4[i] == 'Single'){HAPIEE_li_ds_w1$divorce[i] ='0'}
  if(HAPIEE_li_w1_divorce$q4[i] == 'Widowed'){HAPIEE_li_ds_w1$divorce[i] ='0'}
}

HAPIEE_li_ds_w1$divorce <- car::recode(as.vector(HAPIEE_li_ds_w1$divorce), "NA='999'")
HAPIEE_li_ds_w1$divorce <- labelled(HAPIEE_li_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 li, echo=F}
vari <- HAPIEE_li_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 li, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$divorce)
BeforeH <- table(HAPIEE_li_w1_divorce$q4, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(2,3,5,6)])
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[3]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`


* Description: 
```{r assign1 pol, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_divorce','HAPIEE.Po_baseline_etic', variables=list('q4'), missings = TRUE)
```

```{r local1 pol, echo=F}
HAPIEE_pol_w1_divorce <- opal.execute(o,'HAPIEE_pol_w1_divorce')
vari <- HAPIEE_pol_w1_divorce$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w1_divorce$q4, missing_values = NA)
ggplot(HAPIEE_pol_w1_divorce, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1 pol, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_divorce$id)

HAPIEE_pol_w1_divorce$q4 <- car::recode(as.vector(HAPIEE_pol_w1_divorce$q4), "NA='-999'")

HAPIEE_pol_ds_w1$divorce <- c(NA) 
for(i in 1:length(HAPIEE_pol_ds_w1$divorce)){
  if(HAPIEE_pol_w1_divorce$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_pol_ds_w1$divorce[i] ='1'}
  if(HAPIEE_pol_w1_divorce$q4[i] == 'Cohabiting'){HAPIEE_pol_ds_w1$divorce[i] ='0'}
  if(HAPIEE_pol_w1_divorce$q4[i] == 'Married'){HAPIEE_pol_ds_w1$divorce[i] ='0'}
  if(HAPIEE_pol_w1_divorce$q4[i] == 'Single'){HAPIEE_pol_ds_w1$divorce[i] ='0'}
  if(HAPIEE_pol_w1_divorce$q4[i] == 'Widowed'){HAPIEE_pol_ds_w1$divorce[i] ='0'}
}

HAPIEE_pol_ds_w1$divorce <- car::recode(as.vector(HAPIEE_pol_ds_w1$divorce), "NA='999'")
HAPIEE_pol_ds_w1$divorce <- labelled(HAPIEE_pol_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 pol, echo=F}
vari <- HAPIEE_pol_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 pol, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$divorce)
BeforeH <- table(HAPIEE_pol_w1_divorce$q4, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(2,3,5,6)])
BeforeH1[[2]] <- BeforeH[[4]]
BeforeH1[[3]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

Not found.

```{r save, echo=FALSE}
divorce <- HAPIEE_cz_ds_w1
save(divorce, file = "../RData/cz_w1/divorce.RData")
rm(divorce)

divorce <- HAPIEE_li_ds_w1
save(divorce, file = "../RData/li_w1/divorce.RData")
rm(divorce)


divorce <- HAPIEE_pol_ds_w1
save(divorce, file = "../RData/pol_w1/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



