---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`


* Description: 
```{r assign1 cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_spouse','HAPIEE.Cz_baseline_etic', variables=list('q4'), missings = TRUE)
```

```{r local1 cz, echo=F}
HAPIEE_cz_w1_spouse <- opal.execute(o,'HAPIEE_cz_w1_spouse')
vari <- HAPIEE_cz_w1_spouse$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w1_spouse$q4, missing_values = NA)
ggplot(HAPIEE_cz_w1_spouse, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Cohabiting or Married into 1`
* `Rest into 0`
* `NA into 999`

 

**R script:**
```{r harmo1 cz, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_spouse$id)

HAPIEE_cz_w1_spouse$q4 <- car::recode(as.vector(HAPIEE_cz_w1_spouse$q4), "NA='-999'")

HAPIEE_cz_ds_w1$spouse <- c(NA) 
for(i in 1:length(HAPIEE_cz_ds_w1$spouse)){
  if(HAPIEE_cz_w1_spouse$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_cz_ds_w1$spouse[i] ='0'}
  if(HAPIEE_cz_w1_spouse$q4[i] == 'Cohabiting'){HAPIEE_cz_ds_w1$spouse[i] ='1'}
  if(HAPIEE_cz_w1_spouse$q4[i] == 'Married'){HAPIEE_cz_ds_w1$spouse[i] ='1'}
  if(HAPIEE_cz_w1_spouse$q4[i] == 'Single'){HAPIEE_cz_ds_w1$spouse[i] ='0'}
  if(HAPIEE_cz_w1_spouse$q4[i] == 'Widowed'){HAPIEE_cz_ds_w1$spouse[i] ='0'}
}

HAPIEE_cz_ds_w1$spouse <- car::recode(as.vector(HAPIEE_cz_ds_w1$spouse), "NA='999'")
HAPIEE_cz_ds_w1$spouse <- labelled(HAPIEE_cz_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cz, echo=F}
vari <- HAPIEE_cz_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$spouse)
BeforeH <- table(HAPIEE_cz_w1_spouse$q4, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH[[3]] <- sum(BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","2,3->1","NA->999")

kable(C)
```

 
 

### Wave 2
Not found.

## Lithuania

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`

* Description: 
```{r assign1 li, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_spouse','HAPIEE.Li_baseline_etic', variables=list('q4'), missings = TRUE)
```

```{r local1 li, echo=F}
HAPIEE_li_w1_spouse <- opal.execute(o,'HAPIEE_li_w1_spouse')
vari <- HAPIEE_li_w1_spouse$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_li_w1_spouse$q4, missing_values = NA)
ggplot(HAPIEE_li_w1_spouse, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

 

**R script:**
```{r harmo1 li, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_spouse$id)

HAPIEE_li_w1_spouse$q4 <- car::recode(as.vector(HAPIEE_li_w1_spouse$q4), "NA='-999'")

HAPIEE_li_ds_w1$spouse <- c(NA) 
for(i in 1:length(HAPIEE_li_ds_w1$spouse)){
  if(HAPIEE_li_w1_spouse$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_li_ds_w1$spouse[i] ='0'}
  if(HAPIEE_li_w1_spouse$q4[i] == 'Cohabiting'){HAPIEE_li_ds_w1$spouse[i] ='1'}
  if(HAPIEE_li_w1_spouse$q4[i] == 'Married'){HAPIEE_li_ds_w1$spouse[i] ='1'}
  if(HAPIEE_li_w1_spouse$q4[i] == 'Single'){HAPIEE_li_ds_w1$spouse[i] ='0'}
  if(HAPIEE_li_w1_spouse$q4[i] == 'Widowed'){HAPIEE_li_ds_w1$spouse[i] ='0'}
}

HAPIEE_li_ds_w1$spouse <- car::recode(as.vector(HAPIEE_li_ds_w1$spouse), "NA='999'")
HAPIEE_li_ds_w1$spouse <- labelled(HAPIEE_li_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 li, echo=F}
vari <- HAPIEE_li_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 li, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$spouse)
BeforeH <- table(HAPIEE_li_w1_spouse$q4, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH[[3]] <- sum(BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","2,3->1","NA->999")

kable(C)
```

 

## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `q4`
* Label: `Marital status`
* Categories: 
    + `1.0 = Single`
    + `2.0 = Married`
    + `3.0 = Cohabiting`
    + `4.0 = Divorced or Separated`
    + `5.0 = Widowed`


* Description: 
```{r assign1 po, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_spouse','HAPIEE.Po_baseline_etic', variables=list('q4'), missings = TRUE)
```

```{r local1 po, echo=F}
HAPIEE_pol_w1_spouse <- opal.execute(o,'HAPIEE_pol_w1_spouse')
vari <- HAPIEE_pol_w1_spouse$q4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w1_spouse$q4, missing_values = NA)
ggplot(HAPIEE_pol_w1_spouse, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `NA into 999`

 

**R script:**
```{r harmo1 po, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_spouse$id)

HAPIEE_pol_w1_spouse$q4 <- car::recode(as.vector(HAPIEE_pol_w1_spouse$q4), "NA='-999'")

HAPIEE_pol_ds_w1$spouse <- c(NA) 
for(i in 1:length(HAPIEE_pol_ds_w1$spouse)){
  if(HAPIEE_pol_w1_spouse$q4[i] == 'Russia: Divorced / Separated'){HAPIEE_pol_ds_w1$spouse[i] ='0'}
  if(HAPIEE_pol_w1_spouse$q4[i] == 'Cohabiting'){HAPIEE_pol_ds_w1$spouse[i] ='1'}
  if(HAPIEE_pol_w1_spouse$q4[i] == 'Married'){HAPIEE_pol_ds_w1$spouse[i] ='1'}
  if(HAPIEE_pol_w1_spouse$q4[i] == 'Single'){HAPIEE_pol_ds_w1$spouse[i] ='0'}
  if(HAPIEE_pol_w1_spouse$q4[i] == 'Widowed'){HAPIEE_pol_ds_w1$spouse[i] ='0'}
}

HAPIEE_pol_ds_w1$spouse <- car::recode(as.vector(HAPIEE_pol_ds_w1$spouse), "NA='999'")
HAPIEE_pol_ds_w1$spouse <- labelled(HAPIEE_pol_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 po, echo=F}
vari <- HAPIEE_pol_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 po, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$spouse)
BeforeH <- table(HAPIEE_pol_w1_spouse$q4, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH[[3]] <- sum(BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","2,3->1","NA->999")

kable(C)
```

 
 

### Wave 2
Not found.



```{r save, echo=FALSE}
spouse <- HAPIEE_cz_ds_w1
save(spouse, file = "../RData/cz_w1/spouse.RData")
rm(spouse)

spouse <- HAPIEE_li_ds_w1
save(spouse, file = "../RData/li_w1/spouse.RData")
rm(spouse)

spouse <- HAPIEE_pol_ds_w1
save(spouse, file = "../RData/pol_w1/spouse.RData")
rm(spouse)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
