---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process
## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `s68`
* Label: `How many children (<18 yrs old) live in your house/flat`


* Description: 
```{r assign1 cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_child','HAPIEE.Cz_baseline_etic',variables=list('s68'), missings = TRUE)
```

```{r local1 cz, echo=F}
HAPIEE_cz_w1_child <- opal.execute(o,'HAPIEE_cz_w1_child')
vari <- HAPIEE_cz_w1_child$s68
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = HAPIEE_cz_w1_child$s68, missing_values = NA)
ggplot(HAPIEE_cz_w1_child, aes(x=factor(s68))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many children (<18 yrs old) live in respondent's house/flat") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `>0 into 1`
* `NA into 999`

**R script:**

```{r harmo1 cz, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_child$id)
HAPIEE_cz_ds_w1$child <- car::recode(as.vector(HAPIEE_cz_w1_child$s68), "0='0'; NA='999'; 1:hi='1'")
HAPIEE_cz_ds_w1$child <- labelled(HAPIEE_cz_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cz, echo=F}
vari <- HAPIEE_cz_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$child)
BeforeH <- table(HAPIEE_cz_w1_child$s68, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:11)])
BeforeH <- BeforeH[c(1,2,12)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2child`
* Label: `Have you had any children (natural born or adopted)?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `child`
* Label: `Number of children`
    
* Description: 
```{r assign2 cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_child','HAPIEE.Cz_reexamination_etic',variables=list('w2child','child'), missings = TRUE)
```

```{r local2 cz, echo=F}
HAPIEE_cz_w2_child <- opal.execute(o,'HAPIEE_cz_w2_child')
vari <- HAPIEE_cz_w2_child$w2child
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w2_child$w2child, missing_values = NA)
ggplot(HAPIEE_cz_w2_child, aes(x=factor(w2child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she had any children (natural born or adopted)?") + ylab("Frequency")
## NO ANSWERS in w2child

vari <- HAPIEE_cz_w2_child$child
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = HAPIEE_cz_w2_child$child, missing_values = NA)
ggplot(HAPIEE_cz_w2_child, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w2child=2 or child=0  into 0`
* `w2child=1 or child>0 into 1`
* `NA into 999`

**R script:**

```{r harmo2 cz, echo=TRUE}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_child$id)

HAPIEE_cz_w2_child$w2child <- car::recode(as.vector(HAPIEE_cz_w2_child$w2child), "NA='-999'")
HAPIEE_cz_w2_child$child <- car::recode(as.vector(HAPIEE_cz_w2_child$child), "NA='-999'")

HAPIEE_cz_ds_w2$child <- c(NA)  
for(i in 1:dim(HAPIEE_cz_w2_child)[1]){
  if(HAPIEE_cz_w2_child$w2child[i] == 2 | HAPIEE_cz_w2_child$child[i] == 0) {
    HAPIEE_cz_ds_w2$child[i] = 0 }
  else if(HAPIEE_cz_w2_child$w2child[i] == 1 | HAPIEE_cz_w2_child$child[i] > 0) {
    HAPIEE_cz_ds_w2$child[i] = 1 }
}
HAPIEE_cz_ds_w2$child <- car::recode(as.vector(HAPIEE_cz_ds_w2$child), "NA='999'")
HAPIEE_cz_ds_w2$child <- labelled(HAPIEE_cz_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2 cz, echo=F}
vari <- HAPIEE_cz_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2 cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w2$child)
BeforeH <- table(HAPIEE_cz_w2_child$child, useNA='ifany')
BeforeH[[3]] <- sum(BeforeH[c(3:6)])
BeforeH <- BeforeH[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```

 
 


## Lithuania

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2child`
* Label: `Have you had any children (natural born or adopted)?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `child`
* Label: `Number of children`


* Description: 
```{r assign1 li, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_child','HAPIEE.Li_baseline_etic',variables=list('child','w2child'), missings = TRUE)
```

```{r local1 li, echo=F}
HAPIEE_li_w1_child <- opal.execute(o,'HAPIEE_li_w1_child')
vari <- HAPIEE_li_w1_child$child
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = HAPIEE_li_w1_child$child, missing_values = NA)
ggplot(HAPIEE_li_w1_child, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")

vari <- HAPIEE_li_w1_child$w2child
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_li_w1_child$w2child, missing_values = NA)
ggplot(HAPIEE_li_w1_child, aes(x=factor(w2child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she had any children (natural born or adopted)?") + ylab("Frequency")
### NO ANSWER in w2child!!!
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w2child=2 or child=0  into 0`
* `w2child=1 or child>0 into 1`
* `NA into 999`

**R script:**

```{r harmo1 li, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_child$id)

HAPIEE_li_w1_child$w2child <- car::recode(as.vector(HAPIEE_li_w1_child$w2child), "NA='-999'")
HAPIEE_li_w1_child$child <- car::recode(as.vector(HAPIEE_li_w1_child$child), "NA='-999'") 

HAPIEE_li_ds_w1$child <- c(NA)  
for(i in 1:dim(HAPIEE_li_w1_child)[1]){
  if(HAPIEE_li_w1_child$w2child[i] == 2 | HAPIEE_li_w1_child$child[i] == 0) {
    HAPIEE_li_ds_w1$child[i] = 0 }
  else if(HAPIEE_li_w1_child$w2child[i] == 1 | HAPIEE_li_w1_child$child[i] > 0) {
    HAPIEE_li_ds_w1$child[i] = 1 }
}

HAPIEE_li_ds_w1$child <- car::recode(as.vector(HAPIEE_li_ds_w1$child), "NA='999'")
HAPIEE_li_ds_w1$child <- labelled(HAPIEE_li_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 li, echo=F}
vari <- HAPIEE_li_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 li, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$child)
BeforeH <- table(HAPIEE_li_w1_child$child, useNA='ifany')
BeforeH[[3]] <- sum(BeforeH[c(3:6)])
BeforeH <- BeforeH[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```

 



## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `s68`
* Label: `How many children (<18 yrs old) live in your house/flat`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_child','HAPIEE.Po_baseline_etic', variables=list('s68'), missings = TRUE)
```

```{r local1, echo=F}
HAPIEE_pol_w1_child <- opal.execute(o,'HAPIEE_pol_w1_child')
vari <- HAPIEE_pol_w1_child$s68
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = HAPIEE_pol_w1_child$s68, missing_values = NA)
ggplot(HAPIEE_pol_w1_child, aes(x=factor(s68))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many children (<18 yrs old) live in respondent's house/flat") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `>0 into 1`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_child$id)
HAPIEE_pol_ds_w1$child <- car::recode(as.vector(HAPIEE_pol_w1_child$s68), "0='0'; NA='999'; 1:hi='1'")
HAPIEE_pol_ds_w1$child <- labelled(HAPIEE_pol_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- HAPIEE_pol_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has child/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$child)
BeforeH <- table(HAPIEE_pol_w1_child$s68, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:12)])
BeforeH <- BeforeH[c(1,2,13)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2child`
* Label: `Have you had any children (natural born or adopted)?`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `child`
* Label: `Number of children`
    


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_child','HAPIEE.Po_reexamination_etic',variables=list('w2child','child'), missings = TRUE)
```

```{r local2, echo=F}
HAPIEE_pol_w2_child <- opal.execute(o,'HAPIEE_pol_w2_child')

vari <- HAPIEE_pol_w2_child$w2child
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w2_child$w2child, missing_values = NA)
ggplot(HAPIEE_pol_w2_child, aes(x=factor(w2child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has he/she had any children (natural born or adopted)?") + ylab("Frequency")
### NO ANSWERS to w2child!!!

vari <- HAPIEE_pol_w2_child$child
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = HAPIEE_pol_w2_child$child, missing_values = NA)
ggplot(HAPIEE_pol_w2_child, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w2child=2 or child=0  into 0`
* `w2child=1 or child>0 into 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_child$id)

HAPIEE_pol_w2_child$w2child <- car::recode(as.vector(HAPIEE_pol_w2_child$w2child), "NA='-999'")
HAPIEE_pol_w2_child$child <- car::recode(as.vector(HAPIEE_pol_w2_child$child), "NA='-999'")

HAPIEE_pol_ds_w2$child <- c(NA)  
for(i in 1:dim(HAPIEE_pol_w2_child)[1]){
  if(HAPIEE_pol_w2_child$w2child[i] == 2 | HAPIEE_pol_w2_child$child[i] == 0) {
    HAPIEE_pol_ds_w2$child[i] = 0 }
  else if(HAPIEE_pol_w2_child$w2child[i] == 1 | HAPIEE_pol_w2_child$child[i] > 0) {
    HAPIEE_pol_ds_w2$child[i] = 1 }
}

HAPIEE_pol_ds_w2$child <- car::recode(as.vector(HAPIEE_pol_ds_w2$child), "NA='999'")
HAPIEE_pol_ds_w2$child <- labelled(HAPIEE_pol_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- HAPIEE_pol_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(HAPIEE_pol_ds_w2$child)
BeforeH <- table(HAPIEE_pol_w2_child$child, useNA='ifany')
BeforeH[[3]] <- sum(BeforeH[c(3:6)])
BeforeH <- BeforeH[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```

 
 


```{r save, echo=FALSE}
child <- HAPIEE_cz_ds_w1
save(child, file = "../RData/cz_w1/child.RData")
rm(child)

child <- HAPIEE_cz_ds_w2
save(child, file = "../RData/cz_w2/child.RData")
rm(child)

child <- HAPIEE_li_ds_w1
save(child, file = "../RData/li_w1/child.RData")
rm(child)

child <- HAPIEE_pol_ds_w1
save(child, file = "../RData/pol_w1/child.RData")
rm(child)

child <- HAPIEE_pol_ds_w2
save(child, file = "../RData/pol_w2/child.RData")
rm(child)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
