---
title: "Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_rel`
* Variable label: `Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p57`
* Label: `Regularly in contact with relatives not living in your household?`
* Categories: 
    + `1 = Several times a week`
    + `2 = About once a week`
    + `3 = Several times a month`
    + `4 = About once a month`
    + `5 = Less than once a month`
    + `6 = I do not have any relatives/no relatives outside my household`


* Description: 
```{r assign1 cz, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_cont_rel','HAPIEE.Cz_baseline_etic', variables=list('p57'), missings = TRUE)
```

```{r local1 cz, echo=F}
HAPIEE_cz_w1_cont_rel <- opal.execute(o,'HAPIEE_cz_w1_cont_rel')
vari <- HAPIEE_cz_w1_cont_rel$p57
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w1_cont_rel$p57, missing_values = NA)
ggplot(HAPIEE_cz_w1_cont_rel, aes(x=factor(p57))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Regularly in contact with relatives not living in your household??") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1 cz, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_cont_rel$id)
HAPIEE_cz_ds_w1$cont_rel <- car::recode(as.vector(HAPIEE_cz_w1_cont_rel$p57), "'Several times a week'='1'; 'About once a week'='1';'Several times a month'='0';  'About once a month'='0';'I do not have any relatives/no relatives outside my household'='0'; 'Less than once a month'='0'; NA='999' ")
HAPIEE_cz_ds_w1$cont_rel <- labelled(HAPIEE_cz_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 cz, echo=F}
vari <- HAPIEE_cz_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 cz, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$cont_rel)
BeforeH <- table(HAPIEE_cz_w1_cont_rel$p57, useNA='ifany')
BeforeH[[8]] <- sum(BeforeH[c(2,6)])
BeforeH[[9]] <- sum(BeforeH[c(1,3,4,5)])
BeforeH <- BeforeH[c(9,8,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```





### Wave 2
Not found.

## Lithuania

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p57`
* Label: `Regularly in contact with relatives not living in your household?`
* Categories: 
    + `1 = Several times a week`
    + `2 = About once a week`
    + `3 = Several times a month`
    + `4 = About once a month`
    + `5 = Less than once a month`
    + `6 = I do not have any relatives/no relatives outside my household`
    + ` .b = ???`


* Description: 
```{r assign1 li, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_cont_rel','HAPIEE.Li_baseline_etic',  variables=list('p57'), missings = TRUE)
```

```{r local1 li, echo=F}
HAPIEE_li_w1_cont_rel <- opal.execute(o,'HAPIEE_li_w1_cont_rel')
vari <- HAPIEE_li_w1_cont_rel$p57
kable(Categorical_summary(vari, missing_values = c(".b"))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(".b"))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(".b"))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_w1_cont_rel$p57, missing_values = NA)
ggplot(HAPIEE_li_w1_cont_rel, aes(x=factor(p57))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Regularly in contact with relatives not living in your household??") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4,5,6 into 0`
* `.b or NA into 999`

**R script:**

```{r harmo1 li, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_cont_rel$id)
HAPIEE_li_ds_w1$cont_rel <- car::recode(as.vector(HAPIEE_li_w1_cont_rel$p57), "'Several times a week'='1';'About once a week'='1';'Several times a month'='0';'About once a month'='0';'I do not have any relatives/no relatives outside my household'='0'; 'Less than once a month'='0';  '.b'='999'; NA='999' ")
HAPIEE_li_ds_w1$cont_rel <- labelled(HAPIEE_li_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1 li, echo=F}
vari <- HAPIEE_li_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1 li, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$cont_rel)
BeforeH <- table(HAPIEE_li_w1_cont_rel$p57, useNA='ifany')
BeforeH[[9]] <- sum(BeforeH[c(3,7)])
BeforeH[[10]] <- sum(BeforeH[c(2,4,5,6)])
BeforeH[[11]] <- sum(BeforeH[c(1,8)])
BeforeH <- BeforeH[c(10,9,11)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


## Poland
### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `p57`
* Label: `Regularly in contact with relatives not living in your household?`
* Categories: 
    + `1 = Several times a week`
    + `2 = About once a week`
    + `3 = Several times a month`
    + `4 = About once a month`
    + `5 = Less than once a month`
    + `6 = I do not have any relatives/no relatives outside my household`


* Description: 
```{r assign1po, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_cont_rel','HAPIEE.Po_baseline_etic', 
                        variables=list('p57'), missings = TRUE)
```

```{r local1po, echo=F}
HAPIEE_pol_w1_cont_rel <- opal.execute(o,'HAPIEE_pol_w1_cont_rel')
vari <- HAPIEE_pol_w1_cont_rel$p57
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w1_cont_rel$p57, missing_values = NA)
ggplot(HAPIEE_pol_w1_cont_rel, aes(x=factor(p57))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Regularly in contact with relatives not living in your household??") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1po, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_cont_rel$id)
HAPIEE_pol_ds_w1$cont_rel <- car::recode(as.vector(HAPIEE_pol_w1_cont_rel$p57), "'Several times a week'='1';'About once a week'='1';'Several times a month'='0'; 'About once a month'='0'; 'I do not have any relatives/no relatives outside my household'='0'; 'Less than once a month'='0'; NA='999' ")
HAPIEE_pol_ds_w1$cont_rel <- labelled(HAPIEE_pol_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1po, echo=F}
vari <- HAPIEE_pol_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1po, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$cont_rel)
BeforeH <- table(HAPIEE_pol_w1_cont_rel$p57, useNA='ifany')
BeforeH[[8]] <- sum(BeforeH[c(2,6)])
BeforeH[[9]] <- sum(BeforeH[c(1,3,4,5)])
BeforeH <- BeforeH[c(9,8,7)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2
Not found.


```{r save, echo=FALSE}
cont_rel <- HAPIEE_pol_ds_w1
save(cont_rel, file = "../RData/pol_w1/cont_rel.RData")
rm(cont_rel)

cont_rel <- HAPIEE_li_ds_w1
save(cont_rel, file = "../RData/li_w1/cont_rel.RData")
rm(cont_rel)

cont_rel <- HAPIEE_cz_ds_w1
save(cont_rel, file = "../RData/cz_w1/cont_rel.RData")
rm(cont_rel)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

