---
title: "Stroke or myocardial infarction (heart attack)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cvd_hardDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cvd_hardDS.R')
```



# Data process



## Cuba


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign cuba_w1, echo=F}

load(paste0(datafolder,"cuba_w1/stroke.RData"))
load(paste0(datafolder,"cuba_w1/mi_ha.RData"))
t1066_cuba_w1 <- tibble(id=stroke$id)
t1066_cuba_w1$stroke <- stroke$stroke
t1066_cuba_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local cuba_w1, echo=F}

vbl <- t1066_cuba_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_cuba_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_cuba_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo cuba_w1}

t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$cvd_hard <- rep(999,length(t1066_cuba_w1$id))
t1066_ds_cuba_w1$cvd_hard[which(t1066_cuba_w1$stroke == 1 | t1066_cuba_w1$mi_ha == 1)] <- 1
t1066_ds_cuba_w1$cvd_hard[which(t1066_cuba_w1$stroke == 0 & t1066_cuba_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}

vbl <- t1066_ds_cuba_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w1, echo=F}

AfterH <- table(t1066_ds_cuba_w1$cvd_hard)
X <- c(
  sum(t1066_cuba_w1$stroke == 0 & t1066_cuba_w1$mi_ha == 0,na.rm=T),
  sum(t1066_cuba_w1$stroke == 1 | t1066_cuba_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_cuba_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign cuba_w2, echo=F}

load(paste0(datafolder,"cuba_w2/stroke.RData"))
load(paste0(datafolder,"cuba_w2/mi_ha.RData"))
t1066_cuba_w2 <- tibble(id=stroke$id)
t1066_cuba_w2$stroke <- stroke$stroke
t1066_cuba_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local cuba_w2, echo=F}

vbl <- t1066_cuba_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_cuba_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_cuba_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

To compute `cvd_hard_age` from the study-specific variable it has to be recoded as follows:

* `if cvd_hard == 1 in w2 and 0 in w1, cvd_hard_age = age-(year of interview w2-year of interview w1)/2`
* `if cvd_hard == 0, cvd_hard_age = 996`
* `cvd_hard == missing into 999`

**R script:**

```{r harmo cuba_w2}

t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)

t1066_ds_cuba_w2$cvd_hard <- rep(999,length(t1066_cuba_w2$id))
t1066_ds_cuba_w2$cvd_hard[which(t1066_cuba_w2$stroke == 1 | t1066_cuba_w2$mi_ha == 1)] <- 1
t1066_ds_cuba_w2$cvd_hard[which(t1066_cuba_w2$stroke == 0 & t1066_cuba_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}

vbl <- t1066_ds_cuba_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w2, echo=F}

AfterH <- table(t1066_ds_cuba_w2$cvd_hard)
X <- c(
  sum(t1066_cuba_w2$stroke == 1 | t1066_cuba_w2$mi_ha == 1,na.rm=T),
  sum(t1066_cuba_w2$stroke == 0 & t1066_cuba_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_cuba_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## India


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign india_w1, echo=F}

load(paste0(datafolder,"india_w1/stroke.RData"))
load(paste0(datafolder,"india_w1/mi_ha.RData"))
t1066_india_w1 <- tibble(id=stroke$id)
t1066_india_w1$stroke <- stroke$stroke
t1066_india_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local india_w1, echo=F}

vbl <- t1066_india_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_india_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo india_w1}

t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$cvd_hard <- rep(999,length(t1066_india_w1$id))
t1066_ds_india_w1$cvd_hard[which(t1066_india_w1$stroke == 1 | t1066_india_w1$mi_ha == 1)] <- 1
t1066_ds_india_w1$cvd_hard[which(t1066_india_w1$stroke == 0 & t1066_india_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- t1066_ds_india_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

AfterH <- table(t1066_ds_india_w1$cvd_hard)
X <- c(
  sum(t1066_india_w1$stroke == 0 & t1066_india_w1$mi_ha == 0,na.rm=T),
  sum(t1066_india_w1$stroke == 1 | t1066_india_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_india_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```





## Urban China


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  |   |
| **Description** |  |  |

```{r assign UCh_w1, echo=F}

load(paste0(datafolder,"UCh_w1/stroke.RData"))
load(paste0(datafolder,"UCh_w1/mi_ha.RData"))
t1066_UCh_w1 <- tibble(id=stroke$id)
t1066_UCh_w1$stroke <- stroke$stroke
t1066_UCh_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local UCh_w1, echo=F}

vbl <- t1066_UCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo UCh_w1}

t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$cvd_hard <- rep(999,length(t1066_UCh_w1$id))
t1066_ds_UCh_w1$cvd_hard[which(t1066_UCh_w1$stroke == 1 | t1066_UCh_w1$mi_ha == 1)] <- 1
t1066_ds_UCh_w1$cvd_hard[which(t1066_UCh_w1$stroke == 0 & t1066_UCh_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}

vbl <- t1066_ds_UCh_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w1, echo=F}

AfterH <- table(t1066_ds_UCh_w1$cvd_hard)
X <- c(
  sum(t1066_UCh_w1$stroke == 0 & t1066_UCh_w1$mi_ha == 0,na.rm=T),
  sum(t1066_UCh_w1$stroke == 1 | t1066_UCh_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  |   |
| **Description** |  |  |

```{r assign UCh_w2, echo=F}

load(paste0(datafolder,"UCh_w2/stroke.RData"))
load(paste0(datafolder,"UCh_w2/mi_ha.RData"))
t1066_UCh_w2 <- tibble(id=stroke$id)
t1066_UCh_w2$stroke <- stroke$stroke
t1066_UCh_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)



```

```{r local UCh_w2, echo=F}

vbl <- t1066_UCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo UCh_w2}

t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$cvd_hard <- rep(999,length(t1066_UCh_w2$id))
t1066_ds_UCh_w2$cvd_hard[which(t1066_UCh_w2$stroke == 1 | t1066_UCh_w2$mi_ha == 1)] <- 1
t1066_ds_UCh_w2$cvd_hard[which(t1066_UCh_w2$stroke == 0 & t1066_UCh_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}

vbl <- t1066_ds_UCh_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w2, echo=F}

AfterH <- table(t1066_ds_UCh_w2$cvd_hard)
X <- c(
  sum(t1066_UCh_w2$stroke == 1 | t1066_UCh_w2$mi_ha == 1,na.rm=T),
  sum(t1066_UCh_w2$stroke == 0 & t1066_UCh_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



## Rural China


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  |   |
| **Description** |  |  |

```{r assign RCh_w1, echo=F}

load(paste0(datafolder,"RCh_w1/stroke.RData"))
load(paste0(datafolder,"RCh_w1/mi_ha.RData"))
t1066_RCh_w1 <- tibble(id=stroke$id)
t1066_RCh_w1$stroke <- stroke$stroke
t1066_RCh_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local RCh_w1, echo=F}

vbl <- t1066_RCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo RCh_w1}

t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$cvd_hard <- rep(999,length(t1066_RCh_w1$id))
t1066_ds_RCh_w1$cvd_hard[which(t1066_RCh_w1$stroke == 1 | t1066_RCh_w1$mi_ha == 1)] <- 1
t1066_ds_RCh_w1$cvd_hard[which(t1066_RCh_w1$stroke == 0 & t1066_RCh_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}

vbl <- t1066_ds_RCh_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w1, echo=F}

AfterH <- table(t1066_ds_RCh_w1$cvd_hard)
X <- c(
  sum(t1066_RCh_w1$stroke == 0 & t1066_RCh_w1$mi_ha == 0,na.rm=T),
  sum(t1066_RCh_w1$stroke == 1 | t1066_RCh_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |   |
| **Description** |  |  |

```{r assign RCh_w2, echo=F}

load(paste0(datafolder,"RCh_w2/stroke.RData"))
load(paste0(datafolder,"RCh_w2/mi_ha.RData"))
t1066_RCh_w2 <- tibble(id=stroke$id)
t1066_RCh_w2$stroke <- stroke$stroke
t1066_RCh_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local RCh_w2, echo=F}

vbl <- t1066_RCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo RCh_w2}

t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$cvd_hard <- rep(999,length(t1066_RCh_w2$id))
t1066_ds_RCh_w2$cvd_hard[which(t1066_RCh_w2$stroke == 1 | t1066_RCh_w2$mi_ha == 1)] <- 1
t1066_ds_RCh_w2$cvd_hard[which(t1066_RCh_w2$stroke == 0 & t1066_RCh_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}

vbl <- t1066_ds_RCh_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w2, echo=F}

AfterH <- table(t1066_ds_RCh_w2$cvd_hard)
X <- c(
  sum(t1066_RCh_w2$stroke == 1 | t1066_RCh_w2$mi_ha == 1,na.rm=T),
  sum(t1066_RCh_w2$stroke == 0 & t1066_RCh_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_RCh_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## Dominican Republic


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign DR_w1, echo=F}

load(paste0(datafolder,"DR_w1/stroke.RData"))
load(paste0(datafolder,"DR_w1/mi_ha.RData"))
t1066_DR_w1 <- tibble(id=stroke$id)
t1066_DR_w1$stroke <- stroke$stroke
t1066_DR_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local DR_w1, echo=F}

vbl <- t1066_DR_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_DR_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_DR_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo DR_w1}

t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$cvd_hard <- rep(999,length(t1066_DR_w1$id))
t1066_ds_DR_w1$cvd_hard[which(t1066_DR_w1$stroke == 1 | t1066_DR_w1$mi_ha == 1)] <- 1
t1066_ds_DR_w1$cvd_hard[which(t1066_DR_w1$stroke == 0 & t1066_DR_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}

vbl <- t1066_ds_DR_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w1, echo=F}

AfterH <- table(t1066_ds_DR_w1$cvd_hard)
X <- c(
  sum(t1066_DR_w1$stroke == 0 & t1066_DR_w1$mi_ha == 0,na.rm=T),
  sum(t1066_DR_w1$stroke == 1 | t1066_DR_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_DR_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign DR_w2, echo=F}

load(paste0(datafolder,"DR_w2/stroke.RData"))
load(paste0(datafolder,"DR_w2/mi_ha.RData"))
t1066_DR_w2 <- tibble(id=stroke$id)
t1066_DR_w2$stroke <- stroke$stroke
t1066_DR_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local DR_w2, echo=F}

vbl <- t1066_DR_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_DR_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_DR_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo DR_w2}

t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$cvd_hard <- rep(999,length(t1066_DR_w2$id))
t1066_ds_DR_w2$cvd_hard[which(t1066_DR_w2$stroke == 1 | t1066_DR_w2$mi_ha == 1)] <- 1
t1066_ds_DR_w2$cvd_hard[which(t1066_DR_w2$stroke == 0 & t1066_DR_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}

vbl <- t1066_ds_DR_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w2, echo=F}

AfterH <- table(t1066_ds_DR_w2$cvd_hard)
X <- c(
  sum(t1066_DR_w2$stroke == 1 | t1066_DR_w2$mi_ha == 1,na.rm=T),
  sum(t1066_DR_w2$stroke == 0 & t1066_DR_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_DR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## Venezuela


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign Ven_w1, echo=F}

load(paste0(datafolder,"Ven_w1/stroke.RData"))
load(paste0(datafolder,"Ven_w1/mi_ha.RData"))
t1066_Ven_w1 <- tibble(id=stroke$id)
t1066_Ven_w1$stroke <- stroke$stroke
t1066_Ven_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local Ven_w1, echo=F}

vbl <- t1066_Ven_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_Ven_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_Ven_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo Ven_w1}

t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$cvd_hard <- rep(999,length(t1066_Ven_w1$id))
t1066_ds_Ven_w1$cvd_hard[which(t1066_Ven_w1$stroke == 1 | t1066_Ven_w1$mi_ha == 1)] <- 1
t1066_ds_Ven_w1$cvd_hard[which(t1066_Ven_w1$stroke == 0 & t1066_Ven_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}

vbl <- t1066_ds_Ven_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w1, echo=F}

AfterH <- table(t1066_ds_Ven_w1$cvd_hard)
X <- c(
  sum(t1066_Ven_w1$stroke == 0 & t1066_Ven_w1$mi_ha == 0,na.rm=T),
  sum(t1066_Ven_w1$stroke == 1 | t1066_Ven_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_Ven_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign Ven_w2, echo=F}

load(paste0(datafolder,"Ven_w2/stroke.RData"))
load(paste0(datafolder,"Ven_w2/mi_ha.RData"))
t1066_Ven_w2 <- tibble(id=stroke$id)
t1066_Ven_w2$stroke <- stroke$stroke
t1066_Ven_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)


```

```{r local Ven_w2, echo=F}

vbl <- t1066_Ven_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_Ven_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_Ven_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo Ven_w2}

t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$cvd_hard <- rep(999,length(t1066_Ven_w2$id))
t1066_ds_Ven_w2$cvd_hard[which(t1066_Ven_w2$stroke == 1 | t1066_Ven_w2$mi_ha == 1)] <- 1
t1066_ds_Ven_w2$cvd_hard[which(t1066_Ven_w2$stroke == 0 & t1066_Ven_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}

vbl <- t1066_ds_Ven_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w2, echo=F}

AfterH <- table(t1066_ds_Ven_w2$cvd_hard)
X <- c(
  sum(t1066_Ven_w2$stroke == 1 | t1066_Ven_w2$mi_ha == 1,na.rm=T),
  sum(t1066_Ven_w2$stroke == 0 & t1066_Ven_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_Ven_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## Urban Peru


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign UP_w1, echo=F}

load(paste0(datafolder,"UP_w1/stroke.RData"))
load(paste0(datafolder,"UP_w1/mi_ha.RData"))
t1066_UP_w1 <- tibble(id=stroke$id)
t1066_UP_w1$stroke <- stroke$stroke
t1066_UP_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local UP_w1, echo=F}

vbl <- t1066_UP_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UP_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UP_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo UP_w1}

t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$cvd_hard <- rep(999,length(t1066_UP_w1$id))
t1066_ds_UP_w1$cvd_hard[which(t1066_UP_w1$stroke == 1 | t1066_UP_w1$mi_ha == 1)] <- 1
t1066_ds_UP_w1$cvd_hard[which(t1066_UP_w1$stroke == 0 & t1066_UP_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}

vbl <- t1066_ds_UP_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w1, echo=F}

AfterH <- table(t1066_ds_UP_w1$cvd_hard)
X <- c(
  sum(t1066_UP_w1$stroke == 0 & t1066_UP_w1$mi_ha == 0,na.rm=T),
  sum(t1066_UP_w1$stroke == 1 | t1066_UP_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_UP_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  |   |
| **Description** |  |  |

```{r assign UP_w2, echo=F}

load(paste0(datafolder,"UP_w2/stroke.RData"))
load(paste0(datafolder,"UP_w2/mi_ha.RData"))
t1066_UP_w2 <- tibble(id=stroke$id)
t1066_UP_w2$stroke <- stroke$stroke
t1066_UP_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)


```

```{r local UP_w2, echo=F}

vbl <- t1066_UP_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UP_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UP_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo UP_w2}

t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$cvd_hard <- rep(999,length(t1066_UP_w2$id))
t1066_ds_UP_w2$cvd_hard[which(t1066_UP_w2$stroke == 1 | t1066_UP_w2$mi_ha == 1)] <- 1
t1066_ds_UP_w2$cvd_hard[which(t1066_UP_w2$stroke == 0 & t1066_UP_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}

vbl <- t1066_ds_UP_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w2, echo=F}

AfterH <- table(t1066_ds_UP_w2$cvd_hard)
X <- c(
  sum(t1066_UP_w2$stroke == 1 | t1066_UP_w2$mi_ha == 1,na.rm=T),
  sum(t1066_UP_w2$stroke == 0 & t1066_UP_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign RP_w1, echo=F}

load(paste0(datafolder,"RP_w1/stroke.RData"))
load(paste0(datafolder,"RP_w1/mi_ha.RData"))
t1066_RP_w1 <- tibble(id=stroke$id)
t1066_RP_w1$stroke <- stroke$stroke
t1066_RP_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local RP_w1, echo=F}

vbl <- t1066_RP_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RP_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RP_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo RP_w1}

t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$cvd_hard <- rep(999,length(t1066_RP_w1$id))
t1066_ds_RP_w1$cvd_hard[which(t1066_RP_w1$stroke == 1 | t1066_RP_w1$mi_ha == 1)] <- 1
t1066_ds_RP_w1$cvd_hard[which(t1066_RP_w1$stroke == 0 & t1066_RP_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}

vbl <- t1066_ds_RP_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w1, echo=F}

AfterH <- table(t1066_ds_RP_w1$cvd_hard)
X <- c(
  sum(t1066_RP_w1$stroke == 0 & t1066_RP_w1$mi_ha == 0,na.rm=T),
  sum(t1066_RP_w1$stroke == 1 | t1066_RP_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_RP_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  |   |
| **Description** |  |  |

```{r assign RP_w2, echo=F}

load(paste0(datafolder,"RP_w2/stroke.RData"))
load(paste0(datafolder,"RP_w2/mi_ha.RData"))
t1066_RP_w2 <- tibble(id=stroke$id)
t1066_RP_w2$stroke <- stroke$stroke
t1066_RP_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)


```

```{r local RP_w2, echo=F}

vbl <- t1066_RP_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RP_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RP_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo RP_w2}

t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$cvd_hard <- rep(999,length(t1066_RP_w2$id))
t1066_ds_RP_w2$cvd_hard[which(t1066_RP_w2$stroke == 1 | t1066_RP_w2$mi_ha == 1)] <- 1
t1066_ds_RP_w2$cvd_hard[which(t1066_RP_w2$stroke == 0 & t1066_RP_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}

vbl <- t1066_ds_RP_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w2, echo=F}

AfterH <- table(t1066_ds_RP_w2$cvd_hard)
X <- c(
  sum(t1066_RP_w2$stroke == 1 | t1066_RP_w2$mi_ha == 1,na.rm=T),
  sum(t1066_RP_w2$stroke == 0 & t1066_RP_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |  | `999 = Missing` |
| **Description** |  |  |

```{r assign UM_w1, echo=F}

load(paste0(datafolder,"UM_w1/stroke.RData"))
load(paste0(datafolder,"UM_w1/mi_ha.RData"))
t1066_UM_w1 <- tibble(id=stroke$id)
t1066_UM_w1$stroke <- stroke$stroke
t1066_UM_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local UM_w1, echo=F}

vbl <- t1066_UM_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UM_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UM_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo UM_w1}

t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$cvd_hard <- rep(999,length(t1066_UM_w1$id))
t1066_ds_UM_w1$cvd_hard[which(t1066_UM_w1$stroke == 1 | t1066_UM_w1$mi_ha == 1)] <- 1
t1066_ds_UM_w1$cvd_hard[which(t1066_UM_w1$stroke == 0 & t1066_UM_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}

vbl <- t1066_ds_UM_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w1, echo=F}

AfterH <- table(t1066_ds_UM_w1$cvd_hard)
X <- c(
  sum(t1066_UM_w1$stroke == 0 & t1066_UM_w1$mi_ha == 0,na.rm=T),
  sum(t1066_UM_w1$stroke == 1 | t1066_UM_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_UM_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign UM_w2, echo=F}

load(paste0(datafolder,"UM_w2/stroke.RData"))
load(paste0(datafolder,"UM_w2/mi_ha.RData"))
t1066_UM_w2 <- tibble(id=stroke$id)
t1066_UM_w2$stroke <- stroke$stroke
t1066_UM_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local UM_w2, echo=F}

vbl <- t1066_UM_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UM_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_UM_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo UM_w2}

t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$cvd_hard <- rep(999,length(t1066_UM_w2$id))
t1066_ds_UM_w2$cvd_hard[which(t1066_UM_w2$stroke == 1 | t1066_UM_w2$mi_ha == 1)] <- 1
t1066_ds_UM_w2$cvd_hard[which(t1066_UM_w2$stroke == 0 & t1066_UM_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}

vbl <- t1066_ds_UM_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w2, echo=F}

AfterH <- table(t1066_ds_UM_w2$cvd_hard)
X <- c(
  sum(t1066_UM_w2$stroke == 1 | t1066_UM_w2$mi_ha == 1,na.rm=T),
  sum(t1066_UM_w2$stroke == 0 & t1066_UM_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_UM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign RM_w1, echo=F}

load(paste0(datafolder,"RM_w1/stroke.RData"))
load(paste0(datafolder,"RM_w1/mi_ha.RData"))
t1066_RM_w1 <- tibble(id=stroke$id)
t1066_RM_w1$stroke <- stroke$stroke
t1066_RM_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local RM_w1, echo=F}

vbl <- t1066_RM_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RM_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RM_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo RM_w1}

t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$cvd_hard <- rep(999,length(t1066_RM_w1$id))
t1066_ds_RM_w1$cvd_hard[which(t1066_RM_w1$stroke == 1 | t1066_RM_w1$mi_ha == 1)] <- 1
t1066_ds_RM_w1$cvd_hard[which(t1066_RM_w1$stroke == 0 & t1066_RM_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}

vbl <- t1066_ds_RM_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w1, echo=F}

AfterH <- table(t1066_ds_RM_w1$cvd_hard)
X <- c(
  sum(t1066_RM_w1$stroke == 0 & t1066_RM_w1$mi_ha == 0,na.rm=T),
  sum(t1066_RM_w1$stroke == 1 | t1066_RM_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_RM_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign RM_w2, echo=F}

load(paste0(datafolder,"RM_w2/stroke.RData"))
load(paste0(datafolder,"RM_w2/mi_ha.RData"))
t1066_RM_w2 <- tibble(id=stroke$id)
t1066_RM_w2$stroke <- stroke$stroke
t1066_RM_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local RM_w2, echo=F}

vbl <- t1066_RM_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RM_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_RM_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo RM_w2}

t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$cvd_hard <- rep(999,length(t1066_RM_w2$id))
t1066_ds_RM_w2$cvd_hard[which(t1066_RM_w2$stroke == 1 | t1066_RM_w2$mi_ha == 1)] <- 1
t1066_ds_RM_w2$cvd_hard[which(t1066_RM_w2$stroke == 0 & t1066_RM_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}

vbl <- t1066_ds_RM_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w2, echo=F}

AfterH <- table(t1066_ds_RM_w2$cvd_hard)
X <- c(
  sum(t1066_RM_w2$stroke == 1 | t1066_RM_w2$mi_ha == 1,na.rm=T),
  sum(t1066_RM_w2$stroke == 0 & t1066_RM_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_RM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign PR_w1, echo=F}

load(paste0(datafolder,"PR_w1/stroke.RData"))
load(paste0(datafolder,"PR_w1/mi_ha.RData"))
t1066_PR_w1 <- tibble(id=stroke$id)
t1066_PR_w1$stroke <- stroke$stroke
t1066_PR_w1$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)




```

```{r local PR_w1, echo=F}

vbl <- t1066_PR_w1$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_PR_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_PR_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`



**R script:**

```{r harmo PR_w1}

t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$cvd_hard <- rep(999,length(t1066_PR_w1$id))
t1066_ds_PR_w1$cvd_hard[which(t1066_PR_w1$stroke == 1 | t1066_PR_w1$mi_ha == 1)] <- 1
t1066_ds_PR_w1$cvd_hard[which(t1066_PR_w1$stroke == 0 & t1066_PR_w1$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}

vbl <- t1066_ds_PR_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w1, echo=F}

AfterH <- table(t1066_ds_PR_w1$cvd_hard)
X <- c(
  sum(t1066_PR_w1$stroke == 0 & t1066_PR_w1$mi_ha == 0,na.rm=T),
  sum(t1066_PR_w1$stroke == 1 | t1066_PR_w1$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_PR_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `stroke` |`mi_ha`|
|-|-|-|
| **Label** | `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  | `stroke` | `mi_ha` |
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)` |`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign PR_w2, echo=F}

load(paste0(datafolder,"PR_w2/stroke.RData"))
load(paste0(datafolder,"PR_w2/mi_ha.RData"))
t1066_PR_w2 <- tibble(id=stroke$id)
t1066_PR_w2$stroke <- stroke$stroke
t1066_PR_w2$mi_ha <- mi_ha$mi_ha
rm(stroke)
rm(mi_ha)

```

```{r local PR_w2, echo=F}

vbl <- t1066_PR_w2$stroke
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_PR_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = c(999))[3], caption = names(t1066_PR_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(999))[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `stroke == 1 or mi_ha == 1 into 1`
* `stroke == 0 and mi_ha == 0 into 0`
* `otherwise into 999`

**R script:**

```{r harmo PR_w2}

t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$cvd_hard <- rep(999,length(t1066_PR_w2$id))
t1066_ds_PR_w2$cvd_hard[which(t1066_PR_w2$stroke == 1 | t1066_PR_w2$mi_ha == 1)] <- 1
t1066_ds_PR_w2$cvd_hard[which(t1066_PR_w2$stroke == 0 & t1066_PR_w2$mi_ha == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}

vbl <- t1066_ds_PR_w2$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w2, echo=F}

AfterH <- table(t1066_ds_PR_w2$cvd_hard)
X <- c(
  sum(t1066_PR_w2$stroke == 1 | t1066_PR_w2$mi_ha == 1,na.rm=T),
  sum(t1066_PR_w2$stroke == 0 & t1066_PR_w2$mi_ha == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_PR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


```



## Descriptive statistics of the harmonised variable `cvd_hard` accross populations and waves

Percentages of categories in each harmonised variable:

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# Consider only waves with some variable harmonised

l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation

Contains information about MI_HA and stroke. The harmonized variable has been built from the single disease variables. 




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





