---
title: "Multimorbidity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/multimorbidDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/multimorbidDS.R')
```



# Data process



## Cuba


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_cuba_w1_hd`|`t1066_cuba_w1_hd`|`t1066_cuba_w1_hd`|`t1066_cuba_w1_hd`|`t1066_cuba_w1_hd`| `t1066_cuba_w1_hd` | `t1066_cuba_w1_hd` |`t1066_cuba_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign cuba_w1, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w1','10-66_HD.t1066_cuba_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')

```

```{r local cuba_w1, echo=F}

vbl <- t1066_cuba_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo cuba_w1}

t1066_ds_cuba_w1 <- t1066_cuba_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_cuba_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_cuba_w1 <- t1066_ds_cuba_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}

vbl <- t1066_ds_cuba_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_cuba_w2_hd`|`t1066_cuba_w2_hd`|`t1066_cuba_w2_hd`|`t1066_cuba_w2_hd`|`t1066_cuba_w2_hd`| `t1066_cuba_w2_hd` | `t1066_cuba_w2_hd` |`t1066_cuba_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign cuba_w2, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w2','10-66_HD.t1066_cuba_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')

```

```{r local cuba_w2, echo=F}

vbl <- t1066_cuba_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo cuba_w2}

t1066_ds_cuba_w2 <- t1066_cuba_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_cuba_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))

t1066_ds_cuba_w2 <- t1066_ds_cuba_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}

vbl <- t1066_ds_cuba_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w2, echo=F}
```

## India

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_india_w1_hd`|`t1066_india_w1_hd`|`t1066_india_w1_hd`|`t1066_india_w1_hd`|`t1066_india_w1_hd`| `t1066_india_w1_hd` | `t1066_india_w1_hd` |`t1066_india_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 't1066_india_w1','10-66_HD.t1066_india_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')

```

```{r local india_w1, echo=F}

vbl <- t1066_india_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo india_w1}

t1066_ds_india_w1 <- t1066_india_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_india_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_india_w1 <- t1066_ds_india_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- t1066_ds_india_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}
```

## Urban China

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UCh_w1_hd`|`t1066_UCh_w1_hd`|`t1066_UCh_w1_hd`|`t1066_UCh_w1_hd`|`t1066_UCh_w1_hd`| `t1066_UCh_w1_hd` | `t1066_UCh_w1_hd` |`t1066_UCh_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w1','10-66_HD.t1066_UCh_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')

```

```{r local UCh_w1, echo=F}

vbl <- t1066_UCh_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UCh_w1}

t1066_ds_UCh_w1 <- t1066_UCh_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UCh_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UCh_w1 <- t1066_ds_UCh_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}

vbl <- t1066_ds_UCh_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w1, echo=F}
```



### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UCh_w2_hd`|`t1066_UCh_w2_hd`|`t1066_UCh_w2_hd`|`t1066_UCh_w2_hd`|`t1066_UCh_w2_hd`| `t1066_UCh_w2_hd` | `t1066_UCh_w2_hd` |`t1066_UCh_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w2','10-66_HD.t1066_UCh_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')

```

```{r local UCh_w2, echo=F}

vbl <- t1066_UCh_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UCh_w2}

t1066_ds_UCh_w2 <- t1066_UCh_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UCh_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UCh_w2 <- t1066_ds_UCh_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}

vbl <- t1066_ds_UCh_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w2, echo=F}
```


## Rural China

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RCh_w1_hd`|`t1066_RCh_w1_hd`|`t1066_RCh_w1_hd`|`t1066_RCh_w1_hd`|`t1066_RCh_w1_hd`| `t1066_RCh_w1_hd` | `t1066_RCh_w1_hd` |`t1066_RCh_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w1','10-66_HD.t1066_RCh_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')

```

```{r local RCh_w1, echo=F}

vbl <- t1066_RCh_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RCh_w1}

t1066_ds_RCh_w1 <- t1066_RCh_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RCh_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RCh_w1 <- t1066_ds_RCh_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}

vbl <- t1066_ds_RCh_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w1, echo=F}
```



### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RCh_w2_hd`|`t1066_RCh_w2_hd`|`t1066_RCh_w2_hd`|`t1066_RCh_w2_hd`|`t1066_RCh_w2_hd`| `t1066_RCh_w2_hd` | `t1066_RCh_w2_hd` |`t1066_RCh_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w2','10-66_HD.t1066_RCh_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')

```

```{r local RCh_w2, echo=F}

vbl <- t1066_RCh_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RCh_w2}

t1066_ds_RCh_w2 <- t1066_RCh_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RCh_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RCh_w2 <- t1066_ds_RCh_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}

vbl <- t1066_ds_RCh_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w2, echo=F}
```


## Dominican Republic

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_DR_w1_hd`|`t1066_DR_w1_hd`|`t1066_DR_w1_hd`|`t1066_DR_w1_hd`|`t1066_DR_w1_hd`| `t1066_DR_w1_hd` | `t1066_DR_w1_hd` |`t1066_DR_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign DR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w1','10-66_HD.t1066_DR_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')

```

```{r local DR_w1, echo=F}

vbl <- t1066_DR_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo DR_w1}

t1066_ds_DR_w1 <- t1066_DR_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_DR_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_DR_w1 <- t1066_ds_DR_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}

vbl <- t1066_ds_DR_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w1, echo=F}
```



### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_DR_w2_hd`|`t1066_DR_w2_hd`|`t1066_DR_w2_hd`|`t1066_DR_w2_hd`|`t1066_DR_w2_hd`| `t1066_DR_w2_hd` | `t1066_DR_w2_hd` |`t1066_DR_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign DR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w2','10-66_HD.t1066_DR_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')

```

```{r local DR_w2, echo=F}

vbl <- t1066_DR_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo DR_w2}

t1066_ds_DR_w2 <- t1066_DR_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_DR_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_DR_w2 <- t1066_ds_DR_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}

vbl <- t1066_ds_DR_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w2, echo=F}
```


## Venezuela

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_Ven_w1_hd`|`t1066_Ven_w1_hd`|`t1066_Ven_w1_hd`|`t1066_Ven_w1_hd`|`t1066_Ven_w1_hd`| `t1066_Ven_w1_hd` | `t1066_Ven_w1_hd` |`t1066_Ven_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign Ven_w1, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w1','10-66_HD.t1066_Ven_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')

```

```{r local Ven_w1, echo=F}

vbl <- t1066_Ven_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo Ven_w1}

t1066_ds_Ven_w1 <- t1066_Ven_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_Ven_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_Ven_w1 <- t1066_ds_Ven_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}

vbl <- t1066_ds_Ven_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w1, echo=F}
```



### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_Ven_w2_hd`|`t1066_Ven_w2_hd`|`t1066_Ven_w2_hd`|`t1066_Ven_w2_hd`|`t1066_Ven_w2_hd`| `t1066_Ven_w2_hd` | `t1066_Ven_w2_hd` |`t1066_Ven_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign Ven_w2, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w2','10-66_HD.t1066_Ven_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')

```

```{r local Ven_w2, echo=F}

vbl <- t1066_Ven_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo Ven_w2}

t1066_ds_Ven_w2 <- t1066_Ven_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_Ven_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_Ven_w2 <- t1066_ds_Ven_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}

vbl <- t1066_ds_Ven_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w2, echo=F}
```


## Urban Peru

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UP_w1_hd`|`t1066_UP_w1_hd`|`t1066_UP_w1_hd`|`t1066_UP_w1_hd`|`t1066_UP_w1_hd`| `t1066_UP_w1_hd` | `t1066_UP_w1_hd` |`t1066_UP_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w1','10-66_HD.t1066_UP_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')

```

```{r local UP_w1, echo=F}

vbl <- t1066_UP_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UP_w1}

t1066_ds_UP_w1 <- t1066_UP_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UP_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UP_w1 <- t1066_ds_UP_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}

vbl <- t1066_ds_UP_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UP_w2_hd`|`t1066_UP_w2_hd`|`t1066_UP_w2_hd`|`t1066_UP_w2_hd`|`t1066_UP_w2_hd`| `t1066_UP_w2_hd` | `t1066_UP_w2_hd` |`t1066_UP_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w2','10-66_HD.t1066_UP_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')

```

```{r local UP_w2, echo=F}

vbl <- t1066_UP_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UP_w2}

t1066_ds_UP_w2 <- t1066_UP_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UP_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UP_w2 <- t1066_ds_UP_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}

vbl <- t1066_ds_UP_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w2, echo=F}
```


## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RP_w1_hd`|`t1066_RP_w1_hd`|`t1066_RP_w1_hd`|`t1066_RP_w1_hd`|`t1066_RP_w1_hd`| `t1066_RP_w1_hd` | `t1066_RP_w1_hd` |`t1066_RP_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w1','10-66_HD.t1066_RP_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')

```

```{r local RP_w1, echo=F}

vbl <- t1066_RP_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RP_w1}

t1066_ds_RP_w1 <- t1066_RP_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RP_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RP_w1 <- t1066_ds_RP_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}

vbl <- t1066_ds_RP_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RP_w2_hd`|`t1066_RP_w2_hd`|`t1066_RP_w2_hd`|`t1066_RP_w2_hd`|`t1066_RP_w2_hd`| `t1066_RP_w2_hd` | `t1066_RP_w2_hd` |`t1066_RP_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w2','10-66_HD.t1066_RP_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')

```

```{r local RP_w2, echo=F}

vbl <- t1066_RP_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RP_w2}

t1066_ds_RP_w2 <- t1066_RP_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RP_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RP_w2 <- t1066_ds_RP_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}

vbl <- t1066_ds_RP_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w2, echo=F}
```


## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UM_w1_hd`|`t1066_UM_w1_hd`|`t1066_UM_w1_hd`|`t1066_UM_w1_hd`|`t1066_UM_w1_hd`| `t1066_UM_w1_hd` | `t1066_UM_w1_hd` |`t1066_UM_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w1','10-66_HD.t1066_UM_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')

```

```{r local UM_w1, echo=F}

vbl <- t1066_UM_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UM_w1}

t1066_ds_UM_w1 <- t1066_UM_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UM_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UM_w1 <- t1066_ds_UM_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}

vbl <- t1066_ds_UM_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_UM_w2_hd`|`t1066_UM_w2_hd`|`t1066_UM_w2_hd`|`t1066_UM_w2_hd`|`t1066_UM_w2_hd`| `t1066_UM_w2_hd` | `t1066_UM_w2_hd` |`t1066_UM_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign UM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w2','10-66_HD.t1066_UM_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')

```

```{r local UM_w2, echo=F}

vbl <- t1066_UM_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo UM_w2}

t1066_ds_UM_w2 <- t1066_UM_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_UM_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_UM_w2 <- t1066_ds_UM_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}

vbl <- t1066_ds_UM_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w2, echo=F}
```


## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RM_w1_hd`|`t1066_RM_w1_hd`|`t1066_RM_w1_hd`|`t1066_RM_w1_hd`|`t1066_RM_w1_hd`| `t1066_RM_w1_hd` | `t1066_RM_w1_hd` |`t1066_RM_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w1','10-66_HD.t1066_RM_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')

```

```{r local RM_w1, echo=F}

vbl <- t1066_RM_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RM_w1}

t1066_ds_RM_w1 <- t1066_RM_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RM_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RM_w1 <- t1066_ds_RM_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}

vbl <- t1066_ds_RM_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_RM_w2_hd`|`t1066_RM_w2_hd`|`t1066_RM_w2_hd`|`t1066_RM_w2_hd`|`t1066_RM_w2_hd`| `t1066_RM_w2_hd` | `t1066_RM_w2_hd` |`t1066_RM_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign RM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w2','10-66_HD.t1066_RM_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')

```

```{r local RM_w2, echo=F}

vbl <- t1066_RM_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo RM_w2}

t1066_ds_RM_w2 <- t1066_RM_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_RM_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_RM_w2 <- t1066_ds_RM_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}

vbl <- t1066_ds_RM_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w2, echo=F}
```


## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_PR_w1_hd`|`t1066_PR_w1_hd`|`t1066_PR_w1_hd`|`t1066_PR_w1_hd`|`t1066_PR_w1_hd`| `t1066_PR_w1_hd` | `t1066_PR_w1_hd` |`t1066_PR_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign PR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w1','10-66_HD.t1066_PR_w1_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')

```

```{r local PR_w1, echo=F}

vbl <- t1066_PR_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo PR_w1}

t1066_ds_PR_w1 <- t1066_PR_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_PR_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_PR_w1 <- t1066_ds_PR_w1 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}

vbl <- t1066_ds_PR_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w1, echo=F}
```




### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_hypertension`|`h_joint_disorders`|`h_cpd`| `stroke` |`mi_ha`|`h_angina`|
|-|-|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of asthma`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of chronic pulmonary disorders`| `Stroke` |`Myocardial infarction or heart attack`|`History of angina`|
| **Table name**  |`t1066_PR_w2_hd`|`t1066_PR_w2_hd`|`t1066_PR_w2_hd`|`t1066_PR_w2_hd`|`t1066_PR_w2_hd`| `t1066_PR_w2_hd` | `t1066_PR_w2_hd` |`t1066_PR_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` |`999 = Missing` | `999 = Missing` | `999 = Missing`|
| **Description** |  |  |  |  |  |  |  |  |

```{r assign PR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w2','10-66_HD.t1066_PR_w2_hd',variables=list('h_diabetes','h_asthma','h_hypertension','h_joint_disorders','h_cpd','stroke','mi_ha','h_angina'), missings = T)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')

```

```{r local PR_w2, echo=F}

vbl <- t1066_PR_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_angina")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_hypertension, h_angina, mi_ha, h_joint_disorders, stroke, h_cpd)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo PR_w2}

t1066_ds_PR_w2 <- t1066_PR_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(t1066_PR_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA))
t1066_ds_PR_w2 <- t1066_ds_PR_w2 %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```



#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}

vbl <- t1066_ds_PR_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w2, echo=F}
```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


```



## Descriptive statistics of the harmonised variable `multimorbid` accross populations and waves

Percentages of categories in each harmonised variable:

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# Consider only waves with some variable harmonised

l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```


# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

