---
title: "Myocardial infarction or heart attack"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mi_haDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mi_haDS.R')
```


# Data process




## Cuba


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-Cuba-Baseline` | `1066-Cuba-Baseline` | `1066-Cuba-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |`999 = Missing`|
| **Description** |  |  |  |  |

```{r assign cuba_w1, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')
load(paste0(datafolder,"cuba_w1/age.RData"))
t1066_cuba_w1 <- left_join(t1066_cuba_w1,age, by="id")
rm(age)

```

```{r local cuba_w1, echo=F}

vbl <- t1066_cuba_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_cuba_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_cuba_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,100)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo cuba_w1}

# Categorical variable harmonization
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$mi_ha <- rep(999,length(t1066_cuba_w1$id))
t1066_ds_cuba_w1$mi_ha[which(t1066_cuba_w1$PTOLDHRT==1 & t1066_cuba_w1$PHRTWHAT == 1)] <- 1
t1066_ds_cuba_w1$mi_ha[which(t1066_cuba_w1$PTOLDHRT==0 | (t1066_cuba_w1$PTOLDHRT==1 & t1066_cuba_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There are 2 individuals which specify heart attack in PHRTWHAT and answer PHRTYEAR, while they answer no to PTOLDHRT. We harmonize them as having a heart attack
t1066_ds_cuba_w1$mi_ha[which(t1066_cuba_w1$PHRTWHAT==1 & (t1066_cuba_w1$PTOLDHRT!=1 | is.na(t1066_cuba_w1$PTOLDHRT)))] <- 1

# Continuous variable harmonization
t1066_ds_cuba_w1$mi_ha_age <- rep(999,length(t1066_ds_cuba_w1$id)) 
t1066_ds_cuba_w1$mi_ha_age[which(t1066_ds_cuba_w1$mi_ha == 0)] <- 996
t1066_ds_cuba_w1$mi_ha_age[which(t1066_ds_cuba_w1$mi_ha == 1 & !is.na(t1066_cuba_w1$PHRTYEAR) & t1066_cuba_w1$age != 999)] <- t1066_cuba_w1$age[which(t1066_ds_cuba_w1$mi_ha == 1 & !is.na(t1066_cuba_w1$PHRTYEAR) & t1066_cuba_w1$age != 999)] - (t1066_cuba_w1$PHRTYEAR[which(t1066_ds_cuba_w1$mi_ha == 1 & !is.na(t1066_cuba_w1$PHRTYEAR)  & t1066_cuba_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}

vbl <- t1066_ds_cuba_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_cuba_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,100)+scale_y_continuous(breaks=c(0,2,4,6,8,10))

```


#### Validation

```{r crosstabulation cuba_w1, echo=F}

continuous <- c(sum(t1066_ds_cuba_w1$mi_ha_age==996),sum(t1066_ds_cuba_w1$mi_ha_age!=996))
X <- table(t1066_ds_cuba_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-Cuba-Followup` | `1066-Cuba-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  | `999 = Missing` |
| **Description** |  |  |  |  |  |

```{r assign cuba_w2, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
load(paste0(datafolder,"cuba_w2/age.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,age, by="id")
rm(age)
load(paste0(datafolder,"cuba_w1/yintw.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,yintw, by="id")
names(t1066_cuba_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"cuba_w2/yintw.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,yintw, by="id")
names(t1066_cuba_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local cuba_w2, echo=F}

vbl <- t1066_cuba_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_cuba_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_cuba_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,105)

vbl <- t1066_cuba_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo cuba_w2}


# Categorical variable harmonization
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$mi_ha <- rep(999,length(t1066_ds_cuba_w2$id))
t1066_ds_cuba_w2$mi_ha[which(t1066_cuba_w2$f_PTOLDHRT==0 | (t1066_cuba_w2$f_PTOLDHRT==1 & t1066_cuba_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_cuba_w2$mi_ha[which(t1066_cuba_w2$f_PTOLDHRT==1 & t1066_cuba_w2$f_PHRTWHAT == 1)] <- 1


# Continuous variable harmonization
t1066_ds_cuba_w2$mi_ha_age <- rep(999,length(t1066_ds_cuba_w2$id))
t1066_ds_cuba_w2$mi_ha_age[which(t1066_ds_cuba_w2$mi_ha==0)] <- 996
t1066_ds_cuba_w2$mi_ha_age[which(t1066_ds_cuba_w2$mi_ha==1 & t1066_cuba_w2$age != 999)] <- t1066_cuba_w2$age[which(t1066_ds_cuba_w2$mi_ha==1 & t1066_cuba_w2$age != 999)] - (t1066_cuba_w2$yintw_w2[which(t1066_ds_cuba_w2$mi_ha==1 & t1066_cuba_w2$age != 999)] - t1066_cuba_w2$yintw_w1[which(t1066_ds_cuba_w2$mi_ha==1 & t1066_cuba_w2$age != 999)])/2





```


#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}

vbl <- t1066_ds_cuba_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_cuba_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,95)#+scale_y_continuous(breaks=c(0,2,4,6,8))

```


#### Validation

```{r crosstabulation cuba_w2, echo=F}

AfterH <- table(t1066_ds_cuba_w2$mi_ha)
X <- c(
  sum(t1066_cuba_w2$f_PTOLDHRT==0 | (t1066_cuba_w2$f_PTOLDHRT==1 & t1066_cuba_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_cuba_w2$f_PTOLDHRT==1 & t1066_cuba_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_cuba_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```



## India


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-India-Baseline` | `1066-India-Baseline` | `1066-India-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |`999 = Missing`|
| **Description** |  |  |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')
load(paste0(datafolder,"india_w1/age.RData"))
t1066_india_w1 <- left_join(t1066_india_w1,age, by="id")
rm(age)

```

```{r local india_w1, echo=F}

vbl <- t1066_india_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_india_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_india_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo india_w1}

# Categorical variable harmonization
t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$mi_ha <- rep(999,length(t1066_india_w1$id))
t1066_ds_india_w1$mi_ha[which(t1066_india_w1$PTOLDHRT==1 & t1066_india_w1$PHRTWHAT == 1)] <- 1
t1066_ds_india_w1$mi_ha[which(t1066_india_w1$PTOLDHRT==0 | (t1066_india_w1$PTOLDHRT==1 & t1066_india_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0


# Continuous variable harmonization
t1066_ds_india_w1$mi_ha_age <- rep(999,length(t1066_ds_india_w1$id)) 
t1066_ds_india_w1$mi_ha_age[which(t1066_ds_india_w1$mi_ha == 0)] <- 996
t1066_ds_india_w1$mi_ha_age[which(t1066_ds_india_w1$mi_ha == 1 & !is.na(t1066_india_w1$PHRTYEAR) & t1066_india_w1$age != 999)] <- t1066_india_w1$age[which(t1066_ds_india_w1$mi_ha == 1 & !is.na(t1066_india_w1$PHRTYEAR) & t1066_india_w1$age != 999)] - (t1066_india_w1$PHRTYEAR[which(t1066_ds_india_w1$mi_ha == 1 & !is.na(t1066_india_w1$PHRTYEAR)  & t1066_india_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- t1066_ds_india_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_india_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_india_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,90)+scale_y_continuous(breaks=c(0,2,4,6,8))

```


#### Validation

```{r crosstabulation india_w1, echo=F}

continuous <- c(sum(t1066_ds_india_w1$mi_ha_age==996),sum(t1066_ds_india_w1$mi_ha_age!=996))
X <- table(t1066_ds_india_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```




## Urban China


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-UrbanChina-Baseline` | `1066-UrbanChina-Baseline` | `1066-UrbanChina-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** |  | `NA` | `NA` |  |
| **Description** |  |  |  |  |

```{r assign UCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')
load(paste0(datafolder,"UCh_w1/age.RData"))
t1066_UCh_w1 <- left_join(t1066_UCh_w1,age, by="id")
rm(age)

```

```{r local UCh_w1, echo=F}

vbl <- t1066_UCh_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UCh_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UCh_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,100)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo UCh_w1}

# Categorical variable harmonization
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$mi_ha <- rep(999,length(t1066_UCh_w1$id))
t1066_ds_UCh_w1$mi_ha[which(t1066_UCh_w1$PTOLDHRT==1 & t1066_UCh_w1$PHRTWHAT == 1)] <- 1
t1066_ds_UCh_w1$mi_ha[which(t1066_UCh_w1$PTOLDHRT==0 | (t1066_UCh_w1$PTOLDHRT==1 & t1066_UCh_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0


# Continuous variable harmonization
t1066_ds_UCh_w1$mi_ha_age <- rep(999,length(t1066_ds_UCh_w1$id)) 
t1066_ds_UCh_w1$mi_ha_age[which(t1066_ds_UCh_w1$mi_ha == 0)] <- 996
t1066_ds_UCh_w1$mi_ha_age[which(t1066_ds_UCh_w1$mi_ha == 1 & !is.na(t1066_UCh_w1$PHRTYEAR) & t1066_UCh_w1$age != 999)] <- t1066_UCh_w1$age[which(t1066_ds_UCh_w1$mi_ha == 1 & !is.na(t1066_UCh_w1$PHRTYEAR) & t1066_UCh_w1$age != 999)] - (t1066_UCh_w1$PHRTYEAR[which(t1066_ds_UCh_w1$mi_ha == 1 & !is.na(t1066_UCh_w1$PHRTYEAR)  & t1066_UCh_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}

vbl <- t1066_ds_UCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UCh_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,90)#+scale_y_continuous(breaks=c(0,2,4,6,8))

```


#### Validation

```{r crosstabulation UCh_w1, echo=F}

continuous <- c(sum(t1066_ds_UCh_w1$mi_ha_age==996),sum(t1066_ds_UCh_w1$mi_ha_age!=996))
X <- table(t1066_ds_UCh_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-UrbanChina-Followup` | `1066-UrbanChina-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** |   | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign UCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
load(paste0(datafolder,"UCh_w2/age.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UCh_w1/yintw.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,yintw, by="id")
names(t1066_UCh_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UCh_w2/yintw.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,yintw, by="id")
names(t1066_UCh_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UCh_w2, echo=F}

vbl <- t1066_UCh_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UCh_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UCh_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,95)

vbl <- t1066_UCh_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo UCh_w2}



# Categorical variable harmonization
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$mi_ha <- rep(999,length(t1066_ds_UCh_w2$id))
t1066_ds_UCh_w2$mi_ha[which(t1066_UCh_w2$f_PTOLDHRT==0 | (t1066_UCh_w2$f_PTOLDHRT==1 & t1066_UCh_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_UCh_w2$mi_ha[which(t1066_UCh_w2$f_PTOLDHRT==1 & t1066_UCh_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_UCh_w2$mi_ha_age <- rep(999,length(t1066_ds_UCh_w2$id))
t1066_ds_UCh_w2$mi_ha_age[which(t1066_ds_UCh_w2$mi_ha==0)] <- 996
t1066_ds_UCh_w2$mi_ha_age[which(t1066_ds_UCh_w2$mi_ha==1)] <- t1066_UCh_w2$age[which(t1066_ds_UCh_w2$mi_ha==1)] - (t1066_UCh_w2$yintw_w2[which(t1066_ds_UCh_w2$mi_ha==1)] - t1066_UCh_w2$yintw_w1[which(t1066_ds_UCh_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}

vbl <- t1066_ds_UCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UCh_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,95)

```


#### Validation

```{r crosstabulation UCh_w2, echo=F}

AfterH <- table(t1066_ds_UCh_w2$mi_ha)
X <- c(
  sum(t1066_UCh_w2$f_PTOLDHRT==0 | (t1066_UCh_w2$f_PTOLDHRT==1 & t1066_UCh_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_UCh_w2$f_PTOLDHRT==1 & t1066_UCh_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1")
kable(C)

```



## Rural China


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-RuralChina-Baseline` | `1066-RuralChina-Baseline` | `1066-RuralChina-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** |  | `NA` | `NA` |  |
| **Description** |  |  |  |  |

```{r assign RCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')
load(paste0(datafolder,"RCh_w1/age.RData"))
t1066_RCh_w1 <- left_join(t1066_RCh_w1,age, by="id")
rm(age)

```

```{r local RCh_w1, echo=F}

vbl <- t1066_RCh_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RCh_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RCh_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,110)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo RCh_w1}

# Categorical variable harmonization
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$mi_ha <- rep(999,length(t1066_RCh_w1$id))
t1066_ds_RCh_w1$mi_ha[which(t1066_RCh_w1$PTOLDHRT==1 & t1066_RCh_w1$PHRTWHAT == 1)] <- 1
t1066_ds_RCh_w1$mi_ha[which(t1066_RCh_w1$PTOLDHRT==0 | (t1066_RCh_w1$PTOLDHRT==1 & t1066_RCh_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There is an individual which specifies heart attack in PHRTWHAT and answer PHRTYEAR, while it answers no to PTOLDHRT. We harmonize it as having a heart attack
t1066_ds_RCh_w1$mi_ha[which(t1066_RCh_w1$PHRTWHAT==1 & (t1066_RCh_w1$PTOLDHRT!=1 | is.na(t1066_RCh_w1$PTOLDHRT)))] <- 1


# Continuous variable harmonization
t1066_ds_RCh_w1$mi_ha_age <- rep(999,length(t1066_ds_RCh_w1$id)) 
t1066_ds_RCh_w1$mi_ha_age[which(t1066_ds_RCh_w1$mi_ha == 0)] <- 996
t1066_ds_RCh_w1$mi_ha_age[which(t1066_ds_RCh_w1$mi_ha == 1 & !is.na(t1066_RCh_w1$PHRTYEAR) & t1066_RCh_w1$age != 999)] <- t1066_RCh_w1$age[which(t1066_ds_RCh_w1$mi_ha == 1 & !is.na(t1066_RCh_w1$PHRTYEAR) & t1066_RCh_w1$age != 999)] - (t1066_RCh_w1$PHRTYEAR[which(t1066_ds_RCh_w1$mi_ha == 1 & !is.na(t1066_RCh_w1$PHRTYEAR)  & t1066_RCh_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}

vbl <- t1066_ds_RCh_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RCh_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,90)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation RCh_w1, echo=F}

continuous <- c(sum(t1066_ds_RCh_w1$mi_ha_age==996),sum(t1066_ds_RCh_w1$mi_ha_age!=996))
X <- table(t1066_ds_RCh_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-RuralChina-Followup` | `1066-RuralChina-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** |   | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign RCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')
load(paste0(datafolder,"RCh_w2/age.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RCh_w1/yintw.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,yintw, by="id")
names(t1066_RCh_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RCh_w2/yintw.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,yintw, by="id")
names(t1066_RCh_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RCh_w2, echo=F}

vbl <- t1066_RCh_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RCh_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RCh_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,115)

vbl <- t1066_RCh_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo RCh_w2}



# Categorical variable harmonization
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$mi_ha <- rep(999,length(t1066_ds_RCh_w2$id))
t1066_ds_RCh_w2$mi_ha[which(t1066_RCh_w2$f_PTOLDHRT==0 | (t1066_RCh_w2$f_PTOLDHRT==1 & t1066_RCh_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_RCh_w2$mi_ha[which(t1066_RCh_w2$f_PTOLDHRT==1 & t1066_RCh_w2$f_PHRTWHAT == 1)] <- 1

# There is an individual which specifies heart attack in f_PHRTWHAT, while it answers no to f_PTOLDHRT We harmonize it as having a heart attack
t1066_ds_RCh_w2$mi_ha[which(t1066_RCh_w2$f_PHRTWHAT==1 & (t1066_RCh_w2$f_PTOLDHRT!=1 | is.na(t1066_RCh_w2$f_PTOLDHRT)))] <- 1

# Continuous variable harmonization
t1066_ds_RCh_w2$mi_ha_age <- rep(999,length(t1066_ds_RCh_w2$id))
t1066_ds_RCh_w2$mi_ha_age[which(t1066_ds_RCh_w2$mi_ha==0)] <- 996
t1066_ds_RCh_w2$mi_ha_age[which(t1066_ds_RCh_w2$mi_ha==1)] <- t1066_RCh_w2$age[which(t1066_ds_RCh_w2$mi_ha==1)] - (t1066_RCh_w2$yintw_w2[which(t1066_ds_RCh_w2$mi_ha==1)] - t1066_RCh_w2$yintw_w1[which(t1066_ds_RCh_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}

vbl <- t1066_ds_RCh_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RCh_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,85)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation RCh_w2, echo=F}

AfterH <- table(t1066_ds_RCh_w2$mi_ha)
X <- c(
  sum((t1066_RCh_w2$f_PTOLDHRT==0 & (t1066_RCh_w2$f_PHRTWHAT!=1 | is.na(t1066_RCh_w2$f_PHRTWHAT))) | (t1066_RCh_w2$f_PTOLDHRT==1 & t1066_RCh_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_RCh_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1")
kable(C)

```



## Dominican Republic


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-DominicanRepublic-Baseline` | `1066-DominicanRepublic-Baseline` | `1066-DominicanRepublic-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |  |
| **Description** |  |  |  |  |

```{r assign DR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')
load(paste0(datafolder,"DR_w1/age.RData"))
t1066_DR_w1 <- left_join(t1066_DR_w1,age, by="id")
rm(age)

```

```{r local DR_w1, echo=F}

vbl <- t1066_DR_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_DR_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_DR_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo DR_w1}

# Categorical variable harmonization
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$mi_ha <- rep(999,length(t1066_DR_w1$id))
t1066_ds_DR_w1$mi_ha[which(t1066_DR_w1$PTOLDHRT==1 & t1066_DR_w1$PHRTWHAT == 1)] <- 1
t1066_ds_DR_w1$mi_ha[which(t1066_DR_w1$PTOLDHRT==0 | (t1066_DR_w1$PTOLDHRT==1 & t1066_DR_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0


# Continuous variable harmonization
t1066_ds_DR_w1$mi_ha_age <- rep(999,length(t1066_ds_DR_w1$id)) 
t1066_ds_DR_w1$mi_ha_age[which(t1066_ds_DR_w1$mi_ha == 0)] <- 996
t1066_ds_DR_w1$mi_ha_age[which(t1066_ds_DR_w1$mi_ha == 1 & !is.na(t1066_DR_w1$PHRTYEAR) & t1066_DR_w1$age != 999)] <- t1066_DR_w1$age[which(t1066_ds_DR_w1$mi_ha == 1 & !is.na(t1066_DR_w1$PHRTYEAR) & t1066_DR_w1$age != 999)] - (t1066_DR_w1$PHRTYEAR[which(t1066_ds_DR_w1$mi_ha == 1 & !is.na(t1066_DR_w1$PHRTYEAR)  & t1066_DR_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}

vbl <- t1066_ds_DR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_DR_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_DR_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,95)#+scale_y_continuous(breaks=c(0,2,4,6,8))

```


#### Validation

```{r crosstabulation DR_w1, echo=F}

continuous <- c(sum(t1066_ds_DR_w1$mi_ha_age==996),sum(t1066_ds_DR_w1$mi_ha_age!=996))
X <- table(t1066_ds_DR_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-DominicanRepublic-Followup` | `1066-DominicanRepublic-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign DR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
load(paste0(datafolder,"DR_w2/age.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,age, by="id")
rm(age)
load(paste0(datafolder,"DR_w1/yintw.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,yintw, by="id")
names(t1066_DR_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"DR_w2/yintw.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,yintw, by="id")
names(t1066_DR_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local DR_w2, echo=F}

vbl <- t1066_DR_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_DR_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_DR_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,105)

vbl <- t1066_DR_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo DR_w2}



t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$mi_ha <- rep(999,length(t1066_ds_DR_w2$id))
t1066_ds_DR_w2$mi_ha[which(t1066_DR_w2$f_PTOLDHRT==0 | (t1066_DR_w2$f_PTOLDHRT==1 & t1066_DR_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_DR_w2$mi_ha[which(t1066_DR_w2$f_PTOLDHRT==1 & t1066_DR_w2$f_PHRTWHAT == 1)] <- 1

t1066_ds_DR_w2$mi_ha_age <- rep(999,length(t1066_ds_DR_w2$id))
t1066_ds_DR_w2$mi_ha_age[which(t1066_ds_DR_w2$mi_ha==0)] <- 996
t1066_ds_DR_w2$mi_ha_age[which(t1066_ds_DR_w2$mi_ha==1)] <- t1066_DR_w2$age[which(t1066_ds_DR_w2$mi_ha==1)] - (t1066_DR_w2$yintw_w2[which(t1066_ds_DR_w2$mi_ha==1)] - t1066_DR_w2$yintw_w1[which(t1066_ds_DR_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}

vbl <- t1066_ds_DR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_DR_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_DR_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)+scale_y_continuous(breaks=c(0,2,4))

```


#### Validation

```{r crosstabulation DR_w2, echo=F}

AfterH <- table(t1066_ds_DR_w2$mi_ha)
X <- c(
  sum(t1066_DR_w2$f_PTOLDHRT==0 | (t1066_DR_w2$f_PTOLDHRT==1 & t1066_DR_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_DR_w2$f_PTOLDHRT==1 & t1066_DR_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_DR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```



## Venezuela


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-Venezuela-Baseline` | `1066-Venezuela-Baseline` | `1066-Venezuela-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign Ven_w1, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')
load(paste0(datafolder,"Ven_w1/age.RData"))
t1066_Ven_w1 <- left_join(t1066_Ven_w1,age, by="id")
rm(age)

```

```{r local Ven_w1, echo=F}

vbl <- t1066_Ven_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_Ven_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_Ven_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,110)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo Ven_w1}

# Categorical variable harmonization
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$mi_ha <- rep(999,length(t1066_Ven_w1$id))
t1066_ds_Ven_w1$mi_ha[which(t1066_Ven_w1$PTOLDHRT==1 & t1066_Ven_w1$PHRTWHAT == 1)] <- 1
t1066_ds_Ven_w1$mi_ha[which(t1066_Ven_w1$PTOLDHRT==0 | (t1066_Ven_w1$PTOLDHRT==1 & t1066_Ven_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There is an individual which specifies heart attack in PHRTWHAT and answers PHRTYEAR, while it answers no to PTOLDHRT. We harmonize it as having a heart attack
t1066_ds_Ven_w1$mi_ha[which(t1066_Ven_w1$PHRTWHAT==1 & (t1066_Ven_w1$PTOLDHRT!=1 | is.na(t1066_Ven_w1$PTOLDHRT)))] <- 1


# Continuous variable harmonization
t1066_ds_Ven_w1$mi_ha_age <- rep(999,length(t1066_ds_Ven_w1$id)) 
t1066_ds_Ven_w1$mi_ha_age[which(t1066_ds_Ven_w1$mi_ha == 0)] <- 996
t1066_ds_Ven_w1$mi_ha_age[which(t1066_ds_Ven_w1$mi_ha == 1 & !is.na(t1066_Ven_w1$PHRTYEAR) & t1066_Ven_w1$age != 999)] <- t1066_Ven_w1$age[which(t1066_ds_Ven_w1$mi_ha == 1 & !is.na(t1066_Ven_w1$PHRTYEAR) & t1066_Ven_w1$age != 999)] - (t1066_Ven_w1$PHRTYEAR[which(t1066_ds_Ven_w1$mi_ha == 1 & !is.na(t1066_Ven_w1$PHRTYEAR)  & t1066_Ven_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}

vbl <- t1066_ds_Ven_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_Ven_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,90)+scale_y_continuous(breaks=c(0,2,4,6,8,10))

```


#### Validation

```{r crosstabulation Ven_w1, echo=F}

continuous <- c(sum(t1066_ds_Ven_w1$mi_ha_age==996),sum(t1066_ds_Ven_w1$mi_ha_age!=996))
X <- table(t1066_ds_Ven_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-Venezuela-Followup` | `1066-Venezuela-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign Ven_w2, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')
load(paste0(datafolder,"Ven_w2/age.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,age, by="id")
rm(age)
load(paste0(datafolder,"Ven_w1/yintw.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,yintw, by="id")
names(t1066_Ven_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"Ven_w2/yintw.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,yintw, by="id")
names(t1066_Ven_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local Ven_w2, echo=F}

vbl <- t1066_Ven_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_Ven_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_Ven_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_Ven_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo Ven_w2}



# Categorical variable harmonization
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$mi_ha <- rep(999,length(t1066_ds_Ven_w2$id))
t1066_ds_Ven_w2$mi_ha[which(t1066_Ven_w2$f_PTOLDHRT==0 | (t1066_Ven_w2$f_PTOLDHRT==1 & t1066_Ven_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_Ven_w2$mi_ha[which(t1066_Ven_w2$f_PTOLDHRT==1 & t1066_Ven_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_Ven_w2$mi_ha_age <- rep(999,length(t1066_ds_Ven_w2$id))
t1066_ds_Ven_w2$mi_ha_age[which(t1066_ds_Ven_w2$mi_ha==0)] <- 996
t1066_ds_Ven_w2$mi_ha_age[which(t1066_ds_Ven_w2$mi_ha==1)] <- t1066_Ven_w2$age[which(t1066_ds_Ven_w2$mi_ha==1)] - (t1066_Ven_w2$yintw_w2[which(t1066_ds_Ven_w2$mi_ha==1)] - t1066_Ven_w2$yintw_w1[which(t1066_ds_Ven_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}

vbl <- t1066_ds_Ven_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_Ven_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,95)

```


#### Validation

```{r crosstabulation Ven_w2, echo=F}

AfterH <- table(t1066_ds_Ven_w2$mi_ha)
X <- c(
  sum(t1066_Ven_w2$f_PTOLDHRT==0 | (t1066_Ven_w2$f_PTOLDHRT==1 & t1066_Ven_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_Ven_w2$f_PTOLDHRT==1 & t1066_Ven_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_Ven_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```



## Urban Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-UrbanPeru-Baseline` | `1066-UrbanPeru-Baseline` | `1066-UrbanPeru-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |   |
| **Description** |  |  |  |  |


```{r assign UP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')
load(paste0(datafolder,"UP_w1/age.RData"))
t1066_UP_w1 <- left_join(t1066_UP_w1,age, by="id")
rm(age)

```

```{r local UP_w1, echo=F}

vbl <- t1066_UP_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UP_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UP_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo UP_w1}

# Categorical variable harmonization
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$mi_ha <- rep(999,length(t1066_UP_w1$id))
t1066_ds_UP_w1$mi_ha[which(t1066_UP_w1$PTOLDHRT==1 & t1066_UP_w1$PHRTWHAT == 1)] <- 1
t1066_ds_UP_w1$mi_ha[which(t1066_UP_w1$PTOLDHRT==0 | (t1066_UP_w1$PTOLDHRT==1 & t1066_UP_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There are 2 individuals which specify heart attack in PHRTWHAT and answer PHRTYEAR, while they answer no to PTOLDHRT. We harmonize them as having a heart attack
t1066_ds_UP_w1$mi_ha[which(t1066_UP_w1$PHRTWHAT==1 & (t1066_UP_w1$PTOLDHRT!=1 | is.na(t1066_UP_w1$PTOLDHRT)))] <- 1


# Continuous variable harmonization
t1066_ds_UP_w1$mi_ha_age <- rep(999,length(t1066_ds_UP_w1$id)) 
t1066_ds_UP_w1$mi_ha_age[which(t1066_ds_UP_w1$mi_ha == 0)] <- 996
t1066_ds_UP_w1$mi_ha_age[which(t1066_ds_UP_w1$mi_ha == 1 & !is.na(t1066_UP_w1$PHRTYEAR) & t1066_UP_w1$age != 999)] <- t1066_UP_w1$age[which(t1066_ds_UP_w1$mi_ha == 1 & !is.na(t1066_UP_w1$PHRTYEAR) & t1066_UP_w1$age != 999)] - (t1066_UP_w1$PHRTYEAR[which(t1066_ds_UP_w1$mi_ha == 1 & !is.na(t1066_UP_w1$PHRTYEAR)  & t1066_UP_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}

vbl <- t1066_ds_UP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UP_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UP_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,105)#+scale_y_continuous(breaks=c(0,2,4,6,8))

```


#### Validation

```{r crosstabulation UP_w1, echo=F}

continuous <- c(sum(t1066_ds_UP_w1$mi_ha_age==996),sum(t1066_ds_UP_w1$mi_ha_age!=996))
X <- table(t1066_ds_UP_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-UrbanPeru-Followup` | `1066-UrbanPeru-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** |  | `NA` |  |  |   |
| **Description** |  |  |  |  |  |


```{r assign UP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')
load(paste0(datafolder,"UP_w2/age.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UP_w1/yintw.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,yintw, by="id")
names(t1066_UP_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UP_w2/yintw.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,yintw, by="id")
names(t1066_UP_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UP_w2, echo=F}

vbl <- t1066_UP_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UP_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UP_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_UP_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo UP_w2}



# Categorical variable harmonization
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$mi_ha <- rep(999,length(t1066_ds_UP_w2$id))
t1066_ds_UP_w2$mi_ha[which(t1066_UP_w2$f_PTOLDHRT==0 | (t1066_UP_w2$f_PTOLDHRT==1 & t1066_UP_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_UP_w2$mi_ha[which(t1066_UP_w2$f_PTOLDHRT==1 & t1066_UP_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_UP_w2$mi_ha_age <- rep(999,length(t1066_ds_UP_w2$id))
t1066_ds_UP_w2$mi_ha_age[which(t1066_ds_UP_w2$mi_ha==0)] <- 996
t1066_ds_UP_w2$mi_ha_age[which(t1066_ds_UP_w2$mi_ha==1)] <- t1066_UP_w2$age[which(t1066_ds_UP_w2$mi_ha==1)] - (t1066_UP_w2$yintw_w2[which(t1066_ds_UP_w2$mi_ha==1)] - t1066_UP_w2$yintw_w1[which(t1066_ds_UP_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}

vbl <- t1066_ds_UP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UP_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UP_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,90)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation UP_w2, echo=F}

AfterH <- table(t1066_ds_UP_w2$mi_ha)
X <- c(
  sum(t1066_UP_w2$f_PTOLDHRT==0 | (t1066_UP_w2$f_PTOLDHRT==1 & t1066_UP_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_UP_w2$f_PTOLDHRT==1 & t1066_UP_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1")
kable(C)

```



## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |   |
| **Description** |  |  |  |  |


```{r assign RP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')
load(paste0(datafolder,"RP_w1/age.RData"))
t1066_RP_w1 <- left_join(t1066_RP_w1,age, by="id")
rm(age)

```

```{r local RP_w1, echo=F}

vbl <- t1066_RP_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RP_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RP_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,100)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo RP_w1}

# Categorical variable harmonization
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$mi_ha <- rep(999,length(t1066_RP_w1$id))
t1066_ds_RP_w1$mi_ha[which(t1066_RP_w1$PTOLDHRT==1 & t1066_RP_w1$PHRTWHAT == 1)] <- 1
t1066_ds_RP_w1$mi_ha[which(t1066_RP_w1$PTOLDHRT==0 | (t1066_RP_w1$PTOLDHRT==1 & t1066_RP_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0


# Continuous variable harmonization
t1066_ds_RP_w1$mi_ha_age <- rep(999,length(t1066_ds_RP_w1$id)) 
t1066_ds_RP_w1$mi_ha_age[which(t1066_ds_RP_w1$mi_ha == 0)] <- 996
t1066_ds_RP_w1$mi_ha_age[which(t1066_ds_RP_w1$mi_ha == 1 & !is.na(t1066_RP_w1$PHRTYEAR) & t1066_RP_w1$age != 999)] <- t1066_RP_w1$age[which(t1066_ds_RP_w1$mi_ha == 1 & !is.na(t1066_RP_w1$PHRTYEAR) & t1066_RP_w1$age != 999)] - (t1066_RP_w1$PHRTYEAR[which(t1066_ds_RP_w1$mi_ha == 1 & !is.na(t1066_RP_w1$PHRTYEAR)  & t1066_RP_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}

vbl <- t1066_ds_RP_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RP_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RP_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,95)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation RP_w1, echo=F}

continuous <- c(sum(t1066_ds_RP_w1$mi_ha_age==996),sum(t1066_ds_RP_w1$mi_ha_age!=996))
X <- table(t1066_ds_RP_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-RuralPeru-Followup` | `1066-RuralPeru-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** |   | `NA` |  |  |   |
| **Description** |  |  |  |  |  |


```{r assign RP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
load(paste0(datafolder,"RP_w2/age.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RP_w1/yintw.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,yintw, by="id")
names(t1066_RP_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RP_w2/yintw.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,yintw, by="id")
names(t1066_RP_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RP_w2, echo=F}

vbl <- t1066_RP_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RP_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RP_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_RP_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo RP_w2}



# Categorical variable harmonization
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$mi_ha <- rep(999,length(t1066_ds_RP_w2$id))
t1066_ds_RP_w2$mi_ha[which(t1066_RP_w2$f_PTOLDHRT==0 | (t1066_RP_w2$f_PTOLDHRT==1 & t1066_RP_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_RP_w2$mi_ha[which(t1066_RP_w2$f_PTOLDHRT==1 & t1066_RP_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_RP_w2$mi_ha_age <- rep(999,length(t1066_ds_RP_w2$id))
t1066_ds_RP_w2$mi_ha_age[which(t1066_ds_RP_w2$mi_ha==0)] <- 996
t1066_ds_RP_w2$mi_ha_age[which(t1066_ds_RP_w2$mi_ha==1)] <- t1066_RP_w2$age[which(t1066_ds_RP_w2$mi_ha==1)] - (t1066_RP_w2$yintw_w2[which(t1066_ds_RP_w2$mi_ha==1)] - t1066_RP_w2$yintw_w1[which(t1066_ds_RP_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}

vbl <- t1066_ds_RP_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RP_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RP_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,95)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation RP_w2, echo=F}

AfterH <- table(t1066_ds_RP_w2$mi_ha)
X <- c(
  sum(t1066_RP_w2$f_PTOLDHRT==0 | (t1066_RP_w2$f_PTOLDHRT==1 & t1066_RP_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_RP_w2$f_PTOLDHRT==1 & t1066_RP_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1")
kable(C)

```



## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-UrbanMexico-Baseline` | `1066-UrbanMexico-Baseline` | `1066-UrbanMexico-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** |   | `NA` | `NA` | `999 = Missing`  |
| **Description** |  |  |  |  |


```{r assign UM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')
load(paste0(datafolder,"UM_w1/age.RData"))
t1066_UM_w1 <- left_join(t1066_UM_w1,age, by="id")
rm(age)

```

```{r local UM_w1, echo=F}

vbl <- t1066_UM_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UM_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UM_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo UM_w1}

# Categorical variable harmonization
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$mi_ha <- rep(999,length(t1066_UM_w1$id))
t1066_ds_UM_w1$mi_ha[which(t1066_UM_w1$PTOLDHRT==1 & t1066_UM_w1$PHRTWHAT == 1)] <- 1
t1066_ds_UM_w1$mi_ha[which(t1066_UM_w1$PTOLDHRT==0 | (t1066_UM_w1$PTOLDHRT==1 & t1066_UM_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0


# Continuous variable harmonization
t1066_ds_UM_w1$mi_ha_age <- rep(999,length(t1066_ds_UM_w1$id)) 
t1066_ds_UM_w1$mi_ha_age[which(t1066_ds_UM_w1$mi_ha == 0)] <- 996
t1066_ds_UM_w1$mi_ha_age[which(t1066_ds_UM_w1$mi_ha == 1 & !is.na(t1066_UM_w1$PHRTYEAR) & t1066_UM_w1$age != 999)] <- t1066_UM_w1$age[which(t1066_ds_UM_w1$mi_ha == 1 & !is.na(t1066_UM_w1$PHRTYEAR) & t1066_UM_w1$age != 999)] - (t1066_UM_w1$PHRTYEAR[which(t1066_ds_UM_w1$mi_ha == 1 & !is.na(t1066_UM_w1$PHRTYEAR)  & t1066_UM_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}

vbl <- t1066_ds_UM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UM_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UM_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,90)+scale_y_continuous(breaks=c(0,1,2,3))

```


#### Validation

```{r crosstabulation UM_w1, echo=F}

continuous <- c(sum(t1066_ds_UM_w1$mi_ha_age==996),sum(t1066_ds_UM_w1$mi_ha_age!=996))
X <- table(t1066_ds_UM_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-UrbanMexico-Followup` | `1066-UrbanMexico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign UM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')
load(paste0(datafolder,"UM_w2/age.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UM_w1/yintw.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,yintw, by="id")
names(t1066_UM_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UM_w2/yintw.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,yintw, by="id")
names(t1066_UM_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UM_w2, echo=F}

vbl <- t1066_UM_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UM_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UM_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,100)

vbl <- t1066_UM_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo UM_w2}



# Categorical variable harmonization
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$mi_ha <- rep(999,length(t1066_ds_UM_w2$id))
t1066_ds_UM_w2$mi_ha[which(t1066_UM_w2$f_PTOLDHRT==0 | (t1066_UM_w2$f_PTOLDHRT==1 & t1066_UM_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_UM_w2$mi_ha[which(t1066_UM_w2$f_PTOLDHRT==1 & t1066_UM_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_UM_w2$mi_ha_age <- rep(999,length(t1066_ds_UM_w2$id))
t1066_ds_UM_w2$mi_ha_age[which(t1066_ds_UM_w2$mi_ha==0)] <- 996
t1066_ds_UM_w2$mi_ha_age[which(t1066_ds_UM_w2$mi_ha==1)] <- t1066_UM_w2$age[which(t1066_ds_UM_w2$mi_ha==1)] - (t1066_UM_w2$yintw_w2[which(t1066_ds_UM_w2$mi_ha==1)] - t1066_UM_w2$yintw_w1[which(t1066_ds_UM_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}

vbl <- t1066_ds_UM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UM_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UM_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,90)+scale_y_continuous(breaks=c(0,1,2))

```


#### Validation

```{r crosstabulation UM_w2, echo=F}

AfterH <- table(t1066_ds_UM_w2$mi_ha)
X <- c(
  sum(t1066_UM_w2$f_PTOLDHRT==0 | (t1066_UM_w2$f_PTOLDHRT==1 & t1066_UM_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_UM_w2$f_PTOLDHRT==1 & t1066_UM_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_UM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```



## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-RuralMexico-Baseline` | `1066-RuralMexico-Baseline` | `1066-RuralMexico-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** |   | `NA` | `NA` |  |
| **Description** |  |  |  |  |

```{r assign RM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')
load(paste0(datafolder,"RM_w1/age.RData"))
t1066_RM_w1 <- left_join(t1066_RM_w1,age, by="id")
rm(age)

```

```{r local RM_w1, echo=F}

vbl <- t1066_RM_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RM_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RM_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo RM_w1}

# Categorical variable harmonization
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$mi_ha <- rep(999,length(t1066_RM_w1$id))
t1066_ds_RM_w1$mi_ha[which(t1066_RM_w1$PTOLDHRT==1 & t1066_RM_w1$PHRTWHAT == 1)] <- 1
t1066_ds_RM_w1$mi_ha[which(t1066_RM_w1$PTOLDHRT==0 | (t1066_RM_w1$PTOLDHRT==1 & t1066_RM_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There is an individual which specifies heart attack in PHRTWHAT, while it answers no to PTOLDHRT. We harmonize it as having a heart attack
t1066_ds_RM_w1$mi_ha[which(t1066_RM_w1$PHRTWHAT==1 & (t1066_RM_w1$PTOLDHRT!=1 | is.na(t1066_RM_w1$PTOLDHRT)))] <- 1

# Continuous variable harmonization
t1066_ds_RM_w1$mi_ha_age <- rep(999,length(t1066_ds_RM_w1$id)) 
t1066_ds_RM_w1$mi_ha_age[which(t1066_ds_RM_w1$mi_ha == 0)] <- 996
t1066_ds_RM_w1$mi_ha_age[which(t1066_ds_RM_w1$mi_ha == 1 & !is.na(t1066_RM_w1$PHRTYEAR) & t1066_RM_w1$age != 999)] <- t1066_RM_w1$age[which(t1066_ds_RM_w1$mi_ha == 1 & !is.na(t1066_RM_w1$PHRTYEAR) & t1066_RM_w1$age != 999)] - (t1066_RM_w1$PHRTYEAR[which(t1066_ds_RM_w1$mi_ha == 1 & !is.na(t1066_RM_w1$PHRTYEAR)  & t1066_RM_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}

vbl <- t1066_ds_RM_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RM_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RM_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,85)+scale_y_continuous(breaks=c(0,1))

```


#### Validation

```{r crosstabulation RM_w1, echo=F}

continuous <- c(sum(t1066_ds_RM_w1$mi_ha_age==996),sum(t1066_ds_RM_w1$mi_ha_age!=996))
X <- table(t1066_ds_RM_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-RuralMexico-Followup` | `1066-RuralMexico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign RM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')
load(paste0(datafolder,"RM_w2/age.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RM_w1/yintw.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,yintw, by="id")
names(t1066_RM_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RM_w2/yintw.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,yintw, by="id")
names(t1066_RM_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RM_w2, echo=F}

vbl <- t1066_RM_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RM_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RM_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,110)

vbl <- t1066_RM_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo RM_w2}



# Categorical variable harmonization
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$mi_ha <- rep(999,length(t1066_ds_RM_w2$id))
t1066_ds_RM_w2$mi_ha[which(t1066_RM_w2$f_PTOLDHRT==0 | (t1066_RM_w2$f_PTOLDHRT==1 & t1066_RM_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_RM_w2$mi_ha[which(t1066_RM_w2$f_PTOLDHRT==1 & t1066_RM_w2$f_PHRTWHAT == 1)] <- 1

# Continuous variable harmonization
t1066_ds_RM_w2$mi_ha_age <- rep(999,length(t1066_ds_RM_w2$id))
t1066_ds_RM_w2$mi_ha_age[which(t1066_ds_RM_w2$mi_ha==0)] <- 996
t1066_ds_RM_w2$mi_ha_age[which(t1066_ds_RM_w2$mi_ha==1)] <- t1066_RM_w2$age[which(t1066_ds_RM_w2$mi_ha==1)] - (t1066_RM_w2$yintw_w2[which(t1066_ds_RM_w2$mi_ha==1)] - t1066_RM_w2$yintw_w1[which(t1066_ds_RM_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}

vbl <- t1066_ds_RM_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RM_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RM_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)+scale_y_continuous(breaks=c(0,1))

```


#### Validation

```{r crosstabulation RM_w2, echo=F}

AfterH <- table(t1066_ds_RM_w2$mi_ha)
X <- c(
  sum(t1066_RM_w2$f_PTOLDHRT==0 | (t1066_RM_w2$f_PTOLDHRT==1 & t1066_RM_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_RM_w2$f_PTOLDHRT==1 & t1066_RM_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_RM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```



## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** | `PTOLDHRT` |`PHRTWHAT`|`PHRTYEAR`|`age`|
|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`when told heart problem?`|`age`|
| **Table name**  | `1066-PuertoRico-Baseline` | `1066-PuertoRico-Baseline` | `1066-PuertoRico-Baseline` |`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`1 = 0-5 years ago`<br/>`2 = 5-10 years ago`<br/>`3 = more than 10 years ago`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |  |
| **Description** |  |  |  |  |


```{r assign PR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('PTOLDHRT','PHRTWHAT','PHRTYEAR'), missings = T)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')
load(paste0(datafolder,"PR_w1/age.RData"))
t1066_PR_w1 <- left_join(t1066_PR_w1,age, by="id")
rm(age)

```

```{r local PR_w1, echo=F}

vbl <- t1066_PR_w1$PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$PHRTYEAR
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PHRTYEAR))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_PR_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_PR_w1, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `PTOLDHRT == 1 and PHRTWHAT == 1 into 1`
* `PTOLDHRT == 0 or (PTOLDHRT == 1 and PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `mi_ha == 0 into 996`
* `if mi_ha == 1 mi_ha_age = age - (PHRTYEAR - 1)*5 (if PHRTYEAR == 3, age-10; if PHRTYEAR == 2, age-5; if PHRTYEAR == 1, age)`
* `otherwise into 999`

**R script:**

```{r harmo PR_w1}

# Categorical variable harmonization
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$mi_ha <- rep(999,length(t1066_PR_w1$id))
t1066_ds_PR_w1$mi_ha[which(t1066_PR_w1$PTOLDHRT==1 & t1066_PR_w1$PHRTWHAT == 1)] <- 1
t1066_ds_PR_w1$mi_ha[which(t1066_PR_w1$PTOLDHRT==0 | (t1066_PR_w1$PTOLDHRT==1 & t1066_PR_w1$PHRTWHAT %in% c(2,3,4,5)))] <- 0

# There is an individual which specifies heart attack in PHRTWHAT and answers PHRTYEAR, while it answers no to PTOLDHRT. We harmonize it as having a heart attack
t1066_ds_PR_w1$mi_ha[which(t1066_PR_w1$PHRTWHAT==1 & (t1066_PR_w1$PTOLDHRT!=1 | is.na(t1066_PR_w1$PTOLDHRT)))] <- 1


# Continuous variable harmonization
t1066_ds_PR_w1$mi_ha_age <- rep(999,length(t1066_ds_PR_w1$id)) 
t1066_ds_PR_w1$mi_ha_age[which(t1066_ds_PR_w1$mi_ha == 0)] <- 996
t1066_ds_PR_w1$mi_ha_age[which(t1066_ds_PR_w1$mi_ha == 1 & !is.na(t1066_PR_w1$PHRTYEAR) & t1066_PR_w1$age != 999)] <- t1066_PR_w1$age[which(t1066_ds_PR_w1$mi_ha == 1 & !is.na(t1066_PR_w1$PHRTYEAR) & t1066_PR_w1$age != 999)] - (t1066_PR_w1$PHRTYEAR[which(t1066_ds_PR_w1$mi_ha == 1 & !is.na(t1066_PR_w1$PHRTYEAR)  & t1066_PR_w1$age != 999)] - 1)*5

```


#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}

vbl <- t1066_ds_PR_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_PR_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_PR_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,100)+scale_y_continuous(breaks=c(0,2,4,6,8,10))

```


#### Validation

```{r crosstabulation PR_w1, echo=F}

continuous <- c(sum(t1066_ds_PR_w1$mi_ha_age==996),sum(t1066_ds_PR_w1$mi_ha_age!=996))
X <- table(t1066_ds_PR_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PTOLDHRT` |`f_PHRTWHAT`|`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|-|
| **Label** | `told had heart problem?` |`what was the heart problem?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-PuertoRico-Followup` | `1066-PuertoRico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`1 = heart attack`<br/>`2 = angina`<br/>`3 = heart failure`<br/>`4 = valve problem`<br/>`5 = other` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` | `NA` |  |  |   |
| **Description** |  |  |  |  |  |

```{r assign PR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('f_PTOLDHRT','f_PHRTWHAT'), missings = T)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')
load(paste0(datafolder,"PR_w2/age.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,age, by="id")
rm(age)
load(paste0(datafolder,"PR_w1/yintw.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,yintw, by="id")
names(t1066_PR_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"PR_w2/yintw.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,yintw, by="id")
names(t1066_PR_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local PR_w2, echo=F}

vbl <- t1066_PR_w2$f_PTOLDHRT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PTOLDHRT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$f_PHRTWHAT
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PHRTWHAT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_PR_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_PR_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_PR_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `f_PTOLDHRT == 1 and f_PHRTWHAT == 1 into 1`
* `f_PTOLDHRT == 0 or (f_PTOLDHRT == 1 and f_PHRTWHAT == 2 or 3 or 4 or 5) into 0`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1 in w2 and 0 in w1, mi_ha_age = age-(year of interview w2-year of interview w1)/2`
* `if mi_ha == 1 in w2 and in w1, mi_ha_age from w1`
* `if mi_ha == 0, mi_ha_age = 996`
* `mi_ha == missing into 999`

**R script:**

```{r harmo PR_w2}



# Categorical variable harmonization
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$mi_ha <- rep(999,length(t1066_ds_PR_w2$id))
t1066_ds_PR_w2$mi_ha[which(t1066_PR_w2$f_PTOLDHRT==0 | (t1066_PR_w2$f_PTOLDHRT==1 & t1066_PR_w2$f_PHRTWHAT %in% c(2,3,4,5)))] <- 0
t1066_ds_PR_w2$mi_ha[which(t1066_PR_w2$f_PTOLDHRT==1 & t1066_PR_w2$f_PHRTWHAT == 1)] <- 1


# There are two individuals which specify heart attack in PHRTWHAT, while they answer no to PTOLDHRT. We harmonize them as having a heart attack
t1066_ds_PR_w2$mi_ha[which(t1066_PR_w2$f_PHRTWHAT==1 & (t1066_PR_w2$f_PTOLDHRT!=1 | is.na(t1066_PR_w2$f_PTOLDHRT)))] <- 1



# Continuous variable harmonization
t1066_ds_PR_w2$mi_ha_age <- rep(999,length(t1066_ds_PR_w2$id))
t1066_ds_PR_w2$mi_ha_age[which(t1066_ds_PR_w2$mi_ha==0)] <- 996
t1066_ds_PR_w2$mi_ha_age[which(t1066_ds_PR_w2$mi_ha==1)] <- t1066_PR_w2$age[which(t1066_ds_PR_w2$mi_ha==1)] - (t1066_PR_w2$yintw_w2[which(t1066_ds_PR_w2$mi_ha==1)] - t1066_PR_w2$yintw_w1[which(t1066_ds_PR_w2$mi_ha==1)])/2


```


#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}

vbl <- t1066_ds_PR_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_PR_w2$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_PR_w2, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,100)

```


#### Validation

```{r crosstabulation PR_w2, echo=F}

AfterH <- table(t1066_ds_PR_w2$mi_ha)
X <- c(
  sum((t1066_PR_w2$f_PTOLDHRT==0 & (t1066_PR_w2$f_PHRTWHAT!=1 | is.na(t1066_PR_w2$f_PHRTWHAT))) | (t1066_PR_w2$f_PTOLDHRT==1 & t1066_PR_w2$f_PHRTWHAT %in% c(2,3,4,5)),na.rm=T),
  sum(t1066_PR_w2$f_PHRTWHAT == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_PR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 | (1 & (2,3,4,5))->0","1 & 1->1","otherwise->999")
kable(C)

```






<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[1]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[1]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

blist <- lmlist # baseline list


# Consider only waves with some variable harmonised

l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

flist <- lmlist # followup list


```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `mi_ha` accross populations and waves

Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(hd_vbl %in% names(get0(paste0("t1066_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- blist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- blist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(hd_vbl %in% names(get0(paste0("t1066_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- flist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- flist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
}


```






## Summary of descriptive statistics of the harmonised variable `mi_ha_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("t1066_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- blist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- blist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("t1066_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

if(length(l.hds)>0){
  lmlist[[1]] <- flist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- flist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}


```











# Quality estimation

No comments




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





