---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `stroke`
* Variable label: `Stroke`
* Variable description: `Diagnosis of stroke or cerebral vascular disease since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT A stroke (cerebral vascular disease) 
1        | A stroke (cerebral vascular disease)

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `stroke_age`
* Variable label: `Age of each episode of stroke`
* Variable description: `Age of each episode of stroke`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke"
ds_label_age <- "Age of each episode of stroke"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Cuba


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-Cuba-Baseline` | `1066-Cuba-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cuba_w1, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')

```

```{r local cuba_w1, echo=F}

vbl <- t1066_cuba_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo cuba_w1}

t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$stroke <- rep(999,length(t1066_cuba_w1$id))
t1066_ds_cuba_w1$stroke[which(t1066_cuba_w1$PCVA == 1 & t1066_cuba_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_cuba_w1$stroke[which(t1066_cuba_w1$PCVA == 0 | t1066_cuba_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}

vbl <- t1066_ds_cuba_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w1, echo=F}

AfterH <- table(t1066_ds_cuba_w1$stroke)
X <- c(
  sum(t1066_cuba_w1$PCVA == 0 | t1066_cuba_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_cuba_w1$PCVA == 1 & t1066_cuba_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_cuba_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

#kable(t1066_cuba_w1[which(t1066_cuba_w1$PCVADIAG%in%c(1,2) & t1066_cuba_w1$PCVA==0),],align = 'c',caption = "There is an individual who told didn't have stroke but was diagnosed stroke by a gp. It is harmonized as non-having stroke.")
# Later we should look for these individuals for all the populations and waves.

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  | `1066-Cuba-Followup` | `1066-Cuba-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  | `999 = Missing` |
| **Description** |  |  |  |  |  |

```{r assign cuba_w2, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
load(paste0(datafolder,"cuba_w2/age.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,age, by="id")
rm(age)
load(paste0(datafolder,"cuba_w1/yintw.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,yintw, by="id")
names(t1066_cuba_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"cuba_w2/yintw.RData"))
t1066_cuba_w2 <- left_join(t1066_cuba_w2,yintw, by="id")
names(t1066_cuba_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local cuba_w2, echo=F}

vbl <- t1066_cuba_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_cuba_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_cuba_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,105)

vbl <- t1066_cuba_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_cuba_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo cuba_w2}

t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)

t1066_ds_cuba_w2$stroke <- rep(999,length(t1066_cuba_w2$id))
t1066_ds_cuba_w2$stroke[which(t1066_cuba_w2$f_PCVA == 1 & t1066_cuba_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_cuba_w2$stroke[which(t1066_cuba_w2$f_PCVA == 0 | t1066_cuba_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_cuba_w2$stroke_age <- rep(999,length(t1066_ds_cuba_w2$id))
t1066_ds_cuba_w2$stroke_age[which(t1066_ds_cuba_w2$stroke==0)] <- 996
t1066_ds_cuba_w2$stroke_age[which(t1066_ds_cuba_w2$stroke==1 & t1066_cuba_w2$age != 999)] <- t1066_cuba_w2$age[which(t1066_ds_cuba_w2$stroke==1 & t1066_cuba_w2$age != 999)] - (t1066_cuba_w2$yintw_w2[which(t1066_ds_cuba_w2$stroke==1 & t1066_cuba_w2$age != 999)] - t1066_cuba_w2$yintw_w1[which(t1066_ds_cuba_w2$stroke==1 & t1066_cuba_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}

vbl <- t1066_ds_cuba_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_cuba_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)

```


#### Validation

```{r crosstabulation cuba_w2, echo=F}

AfterH <- table(t1066_ds_cuba_w2$stroke)
X <- c(
  sum(t1066_cuba_w2$f_PCVA == 1 & t1066_cuba_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_cuba_w2$f_PCVA == 0 | t1066_cuba_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_cuba_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## India


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-India-Baseline` | `1066-India-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')

```

```{r local india_w1, echo=F}

vbl <- t1066_india_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_india_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo india_w1}

t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$stroke <- rep(999,length(t1066_india_w1$id))
t1066_ds_india_w1$stroke[which(t1066_india_w1$PCVA == 1 & t1066_india_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_india_w1$stroke[which(t1066_india_w1$PCVA == 0 | t1066_india_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- t1066_ds_india_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

AfterH <- table(t1066_ds_india_w1$stroke)
X <- c(
  sum(t1066_india_w1$PCVA == 0 | t1066_india_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_india_w1$PCVA == 1 & t1066_india_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_india_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


Not found.



## Urban China


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-UrbanChina-Baseline` | `1066-UrbanChina-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** |  | `NA` |
| **Description** |  |  |

```{r assign UCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')

```

```{r local UCh_w1, echo=F}

vbl <- t1066_UCh_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo UCh_w1}

t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$stroke <- rep(999,length(t1066_UCh_w1$id))
t1066_ds_UCh_w1$stroke[which(t1066_UCh_w1$PCVA == 1 & t1066_UCh_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UCh_w1$stroke[which(t1066_UCh_w1$PCVA == 0 | t1066_UCh_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}

vbl <- t1066_ds_UCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w1, echo=F}

AfterH <- table(t1066_ds_UCh_w1$stroke)
X <- c(
  sum(t1066_UCh_w1$PCVA == 0 | t1066_UCh_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_UCh_w1$PCVA == 1 & t1066_UCh_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-UrbanChina-Followup` |`1066-UrbanChina-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** |  | `NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign UCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
load(paste0(datafolder,"UCh_w2/age.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UCh_w1/yintw.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,yintw, by="id")
names(t1066_UCh_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UCh_w2/yintw.RData"))
t1066_UCh_w2 <- left_join(t1066_UCh_w2,yintw, by="id")
names(t1066_UCh_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UCh_w2, echo=F}

vbl <- t1066_UCh_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UCh_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UCh_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,95)

vbl <- t1066_UCh_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UCh_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo UCh_w2}

t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$stroke <- rep(999,length(t1066_UCh_w2$id))
t1066_ds_UCh_w2$stroke[which(t1066_UCh_w2$f_PCVA == 1 & t1066_UCh_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UCh_w2$stroke[which(t1066_UCh_w2$f_PCVA == 0 | t1066_UCh_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_UCh_w2$stroke_age <- rep(999,length(t1066_ds_UCh_w2$id))
t1066_ds_UCh_w2$stroke_age[which(t1066_ds_UCh_w2$stroke==0)] <- 996
t1066_ds_UCh_w2$stroke_age[which(t1066_ds_UCh_w2$stroke==1 & t1066_UCh_w2$age != 999)] <- t1066_UCh_w2$age[which(t1066_ds_UCh_w2$stroke==1 & t1066_UCh_w2$age != 999)] - (t1066_UCh_w2$yintw_w2[which(t1066_ds_UCh_w2$stroke==1 & t1066_UCh_w2$age != 999)] - t1066_UCh_w2$yintw_w1[which(t1066_ds_UCh_w2$stroke==1 & t1066_UCh_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}

vbl <- t1066_ds_UCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UCh_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,90)

```


#### Validation

```{r crosstabulation UCh_w2, echo=F}

AfterH <- table(t1066_ds_UCh_w2$stroke)
X <- c(
  sum(t1066_UCh_w2$f_PCVA == 1 & t1066_UCh_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_UCh_w2$f_PCVA == 0 | t1066_UCh_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



## Rural China


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-RuralChina-Baseline` | `1066-RuralChina-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** |  | `NA` |
| **Description** |  |  |

```{r assign RCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')

```

```{r local RCh_w1, echo=F}

vbl <- t1066_RCh_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo RCh_w1}

t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$stroke <- rep(999,length(t1066_RCh_w1$id))
t1066_ds_RCh_w1$stroke[which(t1066_RCh_w1$PCVA == 1 & t1066_RCh_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RCh_w1$stroke[which(t1066_RCh_w1$PCVA == 0 | t1066_RCh_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}

vbl <- t1066_ds_RCh_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w1, echo=F}

AfterH <- table(t1066_ds_RCh_w1$stroke)
X <- c(
  sum(t1066_RCh_w1$PCVA == 0 | t1066_RCh_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_RCh_w1$PCVA == 1 & t1066_RCh_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-RuralChina-Followup` |`1066-RuralChina-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign RCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')
load(paste0(datafolder,"RCh_w2/age.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RCh_w1/yintw.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,yintw, by="id")
names(t1066_RCh_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RCh_w2/yintw.RData"))
t1066_RCh_w2 <- left_join(t1066_RCh_w2,yintw, by="id")
names(t1066_RCh_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RCh_w2, echo=F}

vbl <- t1066_RCh_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RCh_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RCh_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,115)

vbl <- t1066_RCh_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RCh_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo RCh_w2}

t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$stroke <- rep(999,length(t1066_RCh_w2$id))
t1066_ds_RCh_w2$stroke[which(t1066_RCh_w2$f_PCVA == 1 & t1066_RCh_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RCh_w2$stroke[which(t1066_RCh_w2$f_PCVA == 0 | t1066_RCh_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_RCh_w2$stroke_age <- rep(999,length(t1066_ds_RCh_w2$id))
t1066_ds_RCh_w2$stroke_age[which(t1066_ds_RCh_w2$stroke==0)] <- 996
t1066_ds_RCh_w2$stroke_age[which(t1066_ds_RCh_w2$stroke==1 & t1066_RCh_w2$age != 999)] <- t1066_RCh_w2$age[which(t1066_ds_RCh_w2$stroke==1 & t1066_RCh_w2$age != 999)] - (t1066_RCh_w2$yintw_w2[which(t1066_ds_RCh_w2$stroke==1 & t1066_RCh_w2$age != 999)] - t1066_RCh_w2$yintw_w1[which(t1066_ds_RCh_w2$stroke==1 & t1066_RCh_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}

vbl <- t1066_ds_RCh_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RCh_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,80)

```


#### Validation

```{r crosstabulation RCh_w2, echo=F}

AfterH <- table(t1066_ds_RCh_w2$stroke)
X <- c(
  sum(t1066_RCh_w2$f_PCVA == 1 & t1066_RCh_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_RCh_w2$f_PCVA == 0 | t1066_RCh_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_RCh_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## Dominican Republic


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-DominicanRepublic-Baseline` | `1066-DominicanRepublic-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign DR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')

```

```{r local DR_w1, echo=F}

vbl <- t1066_DR_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo DR_w1}

t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$stroke <- rep(999,length(t1066_DR_w1$id))
t1066_ds_DR_w1$stroke[which(t1066_DR_w1$PCVA == 1 & t1066_DR_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_DR_w1$stroke[which(t1066_DR_w1$PCVA == 0 | t1066_DR_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}

vbl <- t1066_ds_DR_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w1, echo=F}

AfterH <- table(t1066_ds_DR_w1$stroke)
X <- c(
  sum(t1066_DR_w1$PCVA == 0 | t1066_DR_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_DR_w1$PCVA == 1 & t1066_DR_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_DR_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-DominicanRepublic-Followup` |`1066-DominicanRepublic-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign DR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
load(paste0(datafolder,"DR_w2/age.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,age, by="id")
rm(age)
load(paste0(datafolder,"DR_w1/yintw.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,yintw, by="id")
names(t1066_DR_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"DR_w2/yintw.RData"))
t1066_DR_w2 <- left_join(t1066_DR_w2,yintw, by="id")
names(t1066_DR_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local DR_w2, echo=F}

vbl <- t1066_DR_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_DR_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_DR_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,105)

vbl <- t1066_DR_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_DR_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo DR_w2}

t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$stroke <- rep(999,length(t1066_DR_w2$id))
t1066_ds_DR_w2$stroke[which(t1066_DR_w2$f_PCVA == 1 & t1066_DR_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_DR_w2$stroke[which(t1066_DR_w2$f_PCVA == 0 | t1066_DR_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_DR_w2$stroke_age <- rep(999,length(t1066_ds_DR_w2$id))
t1066_ds_DR_w2$stroke_age[which(t1066_ds_DR_w2$stroke==0)] <- 996
t1066_ds_DR_w2$stroke_age[which(t1066_ds_DR_w2$stroke==1 & t1066_DR_w2$age != 999)] <- t1066_DR_w2$age[which(t1066_ds_DR_w2$stroke==1 & t1066_DR_w2$age != 999)] - (t1066_DR_w2$yintw_w2[which(t1066_ds_DR_w2$stroke==1 & t1066_DR_w2$age != 999)] - t1066_DR_w2$yintw_w1[which(t1066_ds_DR_w2$stroke==1 & t1066_DR_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}

vbl <- t1066_ds_DR_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_DR_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_DR_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)

```


#### Validation

```{r crosstabulation DR_w2, echo=F}

AfterH <- table(t1066_ds_DR_w2$stroke)
X <- c(
  sum(t1066_DR_w2$f_PCVA == 1 & t1066_DR_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_DR_w2$f_PCVA == 0 | t1066_DR_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_DR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## Venezuela


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-Venezuela-Baseline` | `1066-Venezuela-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign Ven_w1, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')

```

```{r local Ven_w1, echo=F}

vbl <- t1066_Ven_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo Ven_w1}

t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$stroke <- rep(999,length(t1066_Ven_w1$id))
t1066_ds_Ven_w1$stroke[which(t1066_Ven_w1$PCVA == 1 & t1066_Ven_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_Ven_w1$stroke[which(t1066_Ven_w1$PCVA == 0 | t1066_Ven_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}

vbl <- t1066_ds_Ven_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w1, echo=F}

AfterH <- table(t1066_ds_Ven_w1$stroke)
X <- c(
  sum(t1066_Ven_w1$PCVA == 0 | t1066_Ven_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_Ven_w1$PCVA == 1 & t1066_Ven_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_Ven_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-Venezuela-Followup` |`1066-Venezuela-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign Ven_w2, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')
load(paste0(datafolder,"Ven_w2/age.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,age, by="id")
rm(age)
load(paste0(datafolder,"Ven_w1/yintw.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,yintw, by="id")
names(t1066_Ven_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"Ven_w2/yintw.RData"))
t1066_Ven_w2 <- left_join(t1066_Ven_w2,yintw, by="id")
names(t1066_Ven_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local Ven_w2, echo=F}

vbl <- t1066_Ven_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_Ven_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_Ven_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_Ven_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_Ven_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo Ven_w2}

t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$stroke <- rep(999,length(t1066_Ven_w2$id))
t1066_ds_Ven_w2$stroke[which(t1066_Ven_w2$f_PCVA == 1 & t1066_Ven_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_Ven_w2$stroke[which(t1066_Ven_w2$f_PCVA == 0 | t1066_Ven_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_Ven_w2$stroke_age <- rep(999,length(t1066_ds_Ven_w2$id))
t1066_ds_Ven_w2$stroke_age[which(t1066_ds_Ven_w2$stroke==0)] <- 996
t1066_ds_Ven_w2$stroke_age[which(t1066_ds_Ven_w2$stroke==1 & t1066_Ven_w2$age != 999)] <- t1066_Ven_w2$age[which(t1066_ds_Ven_w2$stroke==1 & t1066_Ven_w2$age != 999)] - (t1066_Ven_w2$yintw_w2[which(t1066_ds_Ven_w2$stroke==1 & t1066_Ven_w2$age != 999)] - t1066_Ven_w2$yintw_w1[which(t1066_ds_Ven_w2$stroke==1 & t1066_Ven_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}

vbl <- t1066_ds_Ven_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_Ven_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,90)

```


#### Validation

```{r crosstabulation Ven_w2, echo=F}

AfterH <- table(t1066_ds_Ven_w2$stroke)
X <- c(
  sum(t1066_Ven_w2$f_PCVA == 1 & t1066_Ven_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_Ven_w2$f_PCVA == 0 | t1066_Ven_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_Ven_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## Urban Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-UrbanPeru-Baseline` | `1066-UrbanPeru-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign UP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')

```

```{r local UP_w1, echo=F}

vbl <- t1066_UP_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo UP_w1}

t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$stroke <- rep(999,length(t1066_UP_w1$id))
t1066_ds_UP_w1$stroke[which(t1066_UP_w1$PCVA == 1 & t1066_UP_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UP_w1$stroke[which(t1066_UP_w1$PCVA == 0 | t1066_UP_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}

vbl <- t1066_ds_UP_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w1, echo=F}

AfterH <- table(t1066_ds_UP_w1$stroke)
X <- c(
  sum(t1066_UP_w1$PCVA == 0 | t1066_UP_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_UP_w1$PCVA == 1 & t1066_UP_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_UP_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-UrbanPeru-Followup` |`1066-UrbanPeru-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** |  |`NA`|  |  |  |
| **Description** |  |  |  |  |  |

```{r assign UP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')
load(paste0(datafolder,"UP_w2/age.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UP_w1/yintw.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,yintw, by="id")
names(t1066_UP_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UP_w2/yintw.RData"))
t1066_UP_w2 <- left_join(t1066_UP_w2,yintw, by="id")
names(t1066_UP_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UP_w2, echo=F}

vbl <- t1066_UP_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UP_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UP_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_UP_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UP_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo UP_w2}

t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$stroke <- rep(999,length(t1066_UP_w2$id))
t1066_ds_UP_w2$stroke[which(t1066_UP_w2$f_PCVA == 1 & t1066_UP_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UP_w2$stroke[which(t1066_UP_w2$f_PCVA == 0 | t1066_UP_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_UP_w2$stroke_age <- rep(999,length(t1066_ds_UP_w2$id))
t1066_ds_UP_w2$stroke_age[which(t1066_ds_UP_w2$stroke==0)] <- 996
t1066_ds_UP_w2$stroke_age[which(t1066_ds_UP_w2$stroke==1 & t1066_UP_w2$age != 999)] <- t1066_UP_w2$age[which(t1066_ds_UP_w2$stroke==1 & t1066_UP_w2$age != 999)] - (t1066_UP_w2$yintw_w2[which(t1066_ds_UP_w2$stroke==1 & t1066_UP_w2$age != 999)] - t1066_UP_w2$yintw_w1[which(t1066_ds_UP_w2$stroke==1 & t1066_UP_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}

vbl <- t1066_ds_UP_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UP_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UP_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)

```


#### Validation

```{r crosstabulation UP_w2, echo=F}

AfterH <- table(t1066_ds_UP_w2$stroke)
X <- c(
  sum(t1066_UP_w2$f_PCVA == 1 & t1066_UP_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_UP_w2$f_PCVA == 0 | t1066_UP_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign RP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')

```

```{r local RP_w1, echo=F}

vbl <- t1066_RP_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo RP_w1}

t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$stroke <- rep(999,length(t1066_RP_w1$id))
t1066_ds_RP_w1$stroke[which(t1066_RP_w1$PCVA == 1 & t1066_RP_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RP_w1$stroke[which(t1066_RP_w1$PCVA == 0 | t1066_RP_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}

vbl <- t1066_ds_RP_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w1, echo=F}

AfterH <- table(t1066_ds_RP_w1$stroke)
X <- c(
  sum(t1066_RP_w1$PCVA == 0 | t1066_RP_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_RP_w1$PCVA == 1 & t1066_RP_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_RP_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-RuralPeru-Followup` |`1066-RuralPeru-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** |  |`NA`|  |  |  |
| **Description** |  |  |  |  |  |

```{r assign RP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
load(paste0(datafolder,"RP_w2/age.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RP_w1/yintw.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,yintw, by="id")
names(t1066_RP_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RP_w2/yintw.RData"))
t1066_RP_w2 <- left_join(t1066_RP_w2,yintw, by="id")
names(t1066_RP_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RP_w2, echo=F}

vbl <- t1066_RP_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RP_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RP_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_RP_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RP_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo RP_w2}

t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$stroke <- rep(999,length(t1066_RP_w2$id))
t1066_ds_RP_w2$stroke[which(t1066_RP_w2$f_PCVA == 1 & t1066_RP_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RP_w2$stroke[which(t1066_RP_w2$f_PCVA == 0 | t1066_RP_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_RP_w2$stroke_age <- rep(999,length(t1066_ds_RP_w2$id))
t1066_ds_RP_w2$stroke_age[which(t1066_ds_RP_w2$stroke==0)] <- 996
t1066_ds_RP_w2$stroke_age[which(t1066_ds_RP_w2$stroke==1 & t1066_RP_w2$age != 999)] <- t1066_RP_w2$age[which(t1066_ds_RP_w2$stroke==1 & t1066_RP_w2$age != 999)] - (t1066_RP_w2$yintw_w2[which(t1066_ds_RP_w2$stroke==1 & t1066_RP_w2$age != 999)] - t1066_RP_w2$yintw_w1[which(t1066_ds_RP_w2$stroke==1 & t1066_RP_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}

vbl <- t1066_ds_RP_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RP_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RP_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(75,85)

```


#### Validation

```{r crosstabulation RP_w2, echo=F}

AfterH <- table(t1066_ds_RP_w2$stroke)
X <- c(
  sum(t1066_RP_w2$f_PCVA == 1 & t1066_RP_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_RP_w2$f_PCVA == 0 | t1066_RP_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-UrbanMexico-Baseline` | `1066-UrbanMexico-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** |  | `NA` |
| **Description** |  |  |

```{r assign UM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')

```

```{r local UM_w1, echo=F}

vbl <- t1066_UM_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo UM_w1}

t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$stroke <- rep(999,length(t1066_UM_w1$id))
t1066_ds_UM_w1$stroke[which(t1066_UM_w1$PCVA == 1 & t1066_UM_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UM_w1$stroke[which(t1066_UM_w1$PCVA == 0 | t1066_UM_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}

vbl <- t1066_ds_UM_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w1, echo=F}

AfterH <- table(t1066_ds_UM_w1$stroke)
X <- c(
  sum(t1066_UM_w1$PCVA == 0 | t1066_UM_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_UM_w1$PCVA == 1 & t1066_UM_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-UrbanMexico-Followup` |`1066-UrbanMexico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign UM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')
load(paste0(datafolder,"UM_w2/age.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,age, by="id")
rm(age)
load(paste0(datafolder,"UM_w1/yintw.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,yintw, by="id")
names(t1066_UM_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"UM_w2/yintw.RData"))
t1066_UM_w2 <- left_join(t1066_UM_w2,yintw, by="id")
names(t1066_UM_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local UM_w2, echo=F}

vbl <- t1066_UM_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_UM_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_UM_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,100)

vbl <- t1066_UM_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_UM_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo UM_w2}

t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$stroke <- rep(999,length(t1066_UM_w2$id))
t1066_ds_UM_w2$stroke[which(t1066_UM_w2$f_PCVA == 1 & t1066_UM_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_UM_w2$stroke[which(t1066_UM_w2$f_PCVA == 0 | t1066_UM_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_UM_w2$stroke_age <- rep(999,length(t1066_ds_UM_w2$id))
t1066_ds_UM_w2$stroke_age[which(t1066_ds_UM_w2$stroke==0)] <- 996
t1066_ds_UM_w2$stroke_age[which(t1066_ds_UM_w2$stroke==1 & t1066_UM_w2$age != 999)] <- t1066_UM_w2$age[which(t1066_ds_UM_w2$stroke==1 & t1066_UM_w2$age != 999)] - (t1066_UM_w2$yintw_w2[which(t1066_ds_UM_w2$stroke==1 & t1066_UM_w2$age != 999)] - t1066_UM_w2$yintw_w1[which(t1066_ds_UM_w2$stroke==1 & t1066_UM_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}

vbl <- t1066_ds_UM_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_UM_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UM_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(70,95)

```


#### Validation

```{r crosstabulation UM_w2, echo=F}

AfterH <- table(t1066_ds_UM_w2$stroke)
X <- c(
  sum(t1066_UM_w2$f_PCVA == 1 & t1066_UM_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_UM_w2$f_PCVA == 0 | t1066_UM_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_UM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-RuralMexico-Baseline` | `1066-RuralMexico-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** |  | `NA` |
| **Description** |  |  |

```{r assign RM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')

```

```{r local RM_w1, echo=F}

vbl <- t1066_RM_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo RM_w1}

t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$stroke <- rep(999,length(t1066_RM_w1$id))
t1066_ds_RM_w1$stroke[which(t1066_RM_w1$PCVA == 1 & t1066_RM_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RM_w1$stroke[which(t1066_RM_w1$PCVA == 0 | t1066_RM_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}

vbl <- t1066_ds_RM_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w1, echo=F}

AfterH <- table(t1066_ds_RM_w1$stroke)
X <- c(
  sum(t1066_RM_w1$PCVA == 0 | t1066_RM_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_RM_w1$PCVA == 1 & t1066_RM_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_RM_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-RuralMexico-Followup` |`1066-RuralMexico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign RM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')
load(paste0(datafolder,"RM_w2/age.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,age, by="id")
rm(age)
load(paste0(datafolder,"RM_w1/yintw.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,yintw, by="id")
names(t1066_RM_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"RM_w2/yintw.RData"))
t1066_RM_w2 <- left_join(t1066_RM_w2,yintw, by="id")
names(t1066_RM_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local RM_w2, echo=F}

vbl <- t1066_RM_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_RM_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_RM_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,110)

vbl <- t1066_RM_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_RM_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo RM_w2}

t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$stroke <- rep(999,length(t1066_RM_w2$id))
t1066_ds_RM_w2$stroke[which(t1066_RM_w2$f_PCVA == 1 & t1066_RM_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_RM_w2$stroke[which(t1066_RM_w2$f_PCVA == 0 | t1066_RM_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_RM_w2$stroke_age <- rep(999,length(t1066_ds_RM_w2$id))
t1066_ds_RM_w2$stroke_age[which(t1066_ds_RM_w2$stroke==0)] <- 996
t1066_ds_RM_w2$stroke_age[which(t1066_ds_RM_w2$stroke==1 & t1066_RM_w2$age != 999)] <- t1066_RM_w2$age[which(t1066_ds_RM_w2$stroke==1 & t1066_RM_w2$age != 999)] - (t1066_RM_w2$yintw_w2[which(t1066_ds_RM_w2$stroke==1 & t1066_RM_w2$age != 999)] - t1066_RM_w2$yintw_w1[which(t1066_ds_RM_w2$stroke==1 & t1066_RM_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}

vbl <- t1066_ds_RM_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_RM_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RM_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,100)

```


#### Validation

```{r crosstabulation RM_w2, echo=F}

AfterH <- table(t1066_ds_RM_w2$stroke)
X <- c(
  sum(t1066_RM_w2$f_PCVA == 1 & t1066_RM_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_RM_w2$f_PCVA == 0 | t1066_RM_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_RM_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** | `PCVA` |`PCVADIAG`|
|-|-|-|
| **Label** | `told had stroke?` |`who diagnosed stroke?`|
| **Table name**  | `1066-PuertoRico-Baseline` | `1066-PuertoRico-Baseline` |
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|
| **Missings** | `NA` |`NA` |
| **Description** |  |  |

```{r assign PR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('PCVA','PCVADIAG'), missings = T)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')

```

```{r local PR_w1, echo=F}

vbl <- t1066_PR_w1$PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w1$PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `PCVA == 1 and PCVADIAG == 1 or 2 into 1`
* `PCVA == 0 or PCVADIAG == 0 into 0`
* `otherwise into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo PR_w1}

t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$stroke <- rep(999,length(t1066_PR_w1$id))
t1066_ds_PR_w1$stroke[which(t1066_PR_w1$PCVA == 1 & t1066_PR_w1$PCVADIAG %in% c(1,2))] <- 1
t1066_ds_PR_w1$stroke[which(t1066_PR_w1$PCVA == 0 | t1066_PR_w1$PCVADIAG == 0)] <- 0

```


#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}

vbl <- t1066_ds_PR_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w1, echo=F}

AfterH <- table(t1066_ds_PR_w1$stroke)
X <- c(
  sum(t1066_PR_w1$PCVA == 0 | t1066_PR_w1$PCVADIAG == 0,na.rm=T),
  sum(t1066_PR_w1$PCVA == 1 & t1066_PR_w1$PCVADIAG %in% c(1,2),na.rm=T)
)
BeforeH <- c(X[1:2],length(t1066_PR_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PCVA`|`f_PCVADIAG` |`yintw (w1)`|`yintw (w2)`|`age`|
|-|-|-|-|-|
| **Label** | `told had stroke (since baseline)?` |`who diagnosed stroke?`|`year of interview`|`year of interview`|`age`|
| **Table name**  |`1066-PuertoRico-Followup` |`1066-PuertoRico-Followup` |`yintw`|`yintw`|`age`|
| **Categories** | `0 = no`<br/>`1 = yes` |`0 = no one`<br/>`1 = gp`<br/>`2 = specialist`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |`NA` |  |  |  |
| **Description** |  |  |  |  |  |

```{r assign PR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('f_PCVA','f_PCVADIAG'), missings = T)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')
load(paste0(datafolder,"PR_w2/age.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,age, by="id")
rm(age)
load(paste0(datafolder,"PR_w1/yintw.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,yintw, by="id")
names(t1066_PR_w2)[5] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"PR_w2/yintw.RData"))
t1066_PR_w2 <- left_join(t1066_PR_w2,yintw, by="id")
names(t1066_PR_w2)[6] <- "yintw_w2"
rm(yintw)

```

```{r local PR_w2, echo=F}

vbl <- t1066_PR_w2$f_PCVA
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PCVA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$f_PCVADIAG
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PCVADIAG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(t1066_PR_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_PR_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(65,105)

vbl <- t1066_PR_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- t1066_PR_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `f_PCVA == 1 and f_PCVADIAG == 1 or 2 into 1`
* `f_PCVA == 0 or f_PCVADIAG == 0 into 0`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2 and 0 in w1, stroke_age = age-(year of interview w2-year of interview w1)/2`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo PR_w2}

t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$stroke <- rep(999,length(t1066_PR_w2$id))
t1066_ds_PR_w2$stroke[which(t1066_PR_w2$f_PCVA == 1 & t1066_PR_w2$f_PCVADIAG %in% c(1,2))] <- 1
t1066_ds_PR_w2$stroke[which(t1066_PR_w2$f_PCVA == 0 | t1066_PR_w2$f_PCVADIAG == 0)] <- 0

t1066_ds_PR_w2$stroke_age <- rep(999,length(t1066_ds_PR_w2$id))
t1066_ds_PR_w2$stroke_age[which(t1066_ds_PR_w2$stroke==0)] <- 996
t1066_ds_PR_w2$stroke_age[which(t1066_ds_PR_w2$stroke==1 & t1066_PR_w2$age != 999)] <- t1066_PR_w2$age[which(t1066_ds_PR_w2$stroke==1 & t1066_PR_w2$age != 999)] - (t1066_PR_w2$yintw_w2[which(t1066_ds_PR_w2$stroke==1 & t1066_PR_w2$age != 999)] - t1066_PR_w2$yintw_w1[which(t1066_ds_PR_w2$stroke==1 & t1066_PR_w2$age != 999)])/2

```


#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}

vbl <- t1066_ds_PR_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- t1066_ds_PR_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_PR_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(65,90)

```


#### Validation

```{r crosstabulation PR_w2, echo=F}

AfterH <- table(t1066_ds_PR_w2$stroke)
X <- c(
  sum(t1066_PR_w2$f_PCVA == 1 & t1066_PR_w2$f_PCVADIAG %in% c(1,2),na.rm=T),
  sum(t1066_PR_w2$f_PCVA == 0 | t1066_PR_w2$f_PCVADIAG == 0,na.rm=T)
)
BeforeH <- c(X[2:1],length(t1066_PR_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0|0->0","1&(1,2)->1","NA->999")
kable(C)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

l.hds <- c(lb.hds,lf.hds)


tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[13,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[13,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  stroke <- l.hds[[index]]
  save(stroke, file = paste0(datafolder,names(l.hds)[index],"/stroke.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

No comments

[Comments on the quality of the new harmonized variable. This section can be done in a later stage, once all variables are harmonized.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





