---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```

# Data process

## Greece

### Wave 1 

#### Study-specific variable description

| **Name**        | `date10` | `age` |
|-----------------|-|-|
| **Label**       | `Date of 10 year follow up` | `Age of Subjects` |
| **Table name**  | `ATTICA_Baseline` | `ATTICA_Baseline` |
| **Description** |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_age','ATTICA.ATTICA_Baseline',
                         variables=list('age'), missings = TRUE)
opal.assign.table.tibble(o, 'ATTICA_w3_dinter','ATTICA.ATTICA_Followup2',
                         variables=list('date10'), missings = TRUE)

ATTICA_w3_dinter <- opal.execute(o,'ATTICA_w3_dinter')
ATTICA_w1_age <- opal.execute(o,'ATTICA_w1_age')
```

```{r local1, echo=F}
ATTICA_w1_age$age_w3 <- ATTICA_w1_age$age+10
ATTICA_w3_dinter$date10 <- as.numeric(format(ATTICA_w3_dinter$date10, '%Y'))

vari <- ATTICA_w3_dinter$date10
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "date10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w3_dinter, aes(factor(date10))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ATTICA_w1_age$age_w3
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age+10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w1_age, aes((age_w3))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

There are 7 values 2103 in year of interview. They are to be recoded as 2013. 

#### Harmonisation algorithm
To harmonize year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age

**R script:**

```{r harmo1}
ATTICA_w3_dinter$year_of_interview <- car::recode(ATTICA_w3_dinter$date10, "NA=2013; 2103=2013")

ATTICA_w1_ybirth <- tibble(id=ATTICA_w1_age$id)
ATTICA_w1_ybirth$year_of_birth <- ATTICA_w3_dinter$year_of_interview - ATTICA_w1_age$age_w3

ATTICA_ds_w1 <- tibble(id=ATTICA_w1_ybirth$id)
ATTICA_ds_w1$ybirth <- car::recode(ATTICA_w1_ybirth$year_of_birth, "NA=999")
ATTICA_ds_w1$ybirth <- labelled(ATTICA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ATTICA_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ATTICA_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```







### Wave 2 

#### Study-specific variable description

| **Name**        | `date10` | `age` |
|-----------------|-|-|
| **Label**       | `Date of 10 year follow up` | `Age of Subjects` |
| **Table name**  | `ATTICA_Baseline` | `ATTICA_Baseline` |
| **Description** |  |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_age','ATTICA.ATTICA_Baseline',
                         variables=list('age'), missings = TRUE)
opal.assign.table.tibble(o, 'ATTICA_w3_dinter','ATTICA.ATTICA_Followup2',
                         variables=list('date10'), missings = TRUE)
```

```{r local2, echo=F}
ATTICA_w3_dinter <- opal.execute(o,'ATTICA_w3_dinter')
ATTICA_w1_age <- opal.execute(o,'ATTICA_w1_age')

ATTICA_w1_age$age_w3 <- ATTICA_w1_age$age+10
ATTICA_w3_dinter$date10 <- as.numeric(format(ATTICA_w3_dinter$date10, '%Y'))

vari <- ATTICA_w3_dinter$date10
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "date10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w3_dinter, aes(factor(date10))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ATTICA_w1_age$age_w3
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age+10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w1_age, aes((age_w3))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

There are 7 values 2103 in year of interview. They are to be recoded as 2013. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age

**R script:**

```{r harmo2}
ATTICA_w3_dinter$year_of_interview <- car::recode(ATTICA_w3_dinter$date10, "NA=2013; 2103=2013")

ATTICA_w2_ybirth <- tibble(id=ATTICA_w1_age$id)
ATTICA_w2_ybirth$year_of_birth <- ATTICA_w3_dinter$year_of_interview - ATTICA_w1_age$age_w3

ATTICA_ds_w2 <- tibble(id=ATTICA_w2_ybirth$id)
ATTICA_ds_w2$ybirth <- car::recode(ATTICA_w2_ybirth$year_of_birth, "NA=999")
ATTICA_ds_w2$ybirth <- labelled(ATTICA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ATTICA_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ATTICA_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
```





### Wave 3 

#### Study-specific variable description

| **Name**        | `date10` | `age` |
|-----------------|-|-|
| **Label**       | `Date of 10 year follow up` | `Age of Subjects` |
| **Table name**  | `ATTICA_Baseline` | `ATTICA_Baseline` |
| **Description** |  |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ATTICA_w1_age','ATTICA.ATTICA_Baseline',
                         variables=list('age'), missings = TRUE)
opal.assign.table.tibble(o, 'ATTICA_w3_dinter','ATTICA.ATTICA_Followup2',
                         variables=list('date10'), missings = TRUE)
```

```{r local3, echo=F}
ATTICA_w3_dinter <- opal.execute(o,'ATTICA_w3_dinter')
ATTICA_w1_age <- opal.execute(o,'ATTICA_w1_age')

ATTICA_w1_age$age_w3 <- ATTICA_w1_age$age+10
ATTICA_w3_dinter$date10 <- as.numeric(format(ATTICA_w3_dinter$date10, '%Y'))

vari <- ATTICA_w3_dinter$date10
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "date10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w3_dinter, aes(factor(date10))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- ATTICA_w1_age$age_w3
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age+10") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w1_age, aes((age_w3))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

There are 7 values 2103 in year of interview. They are to be recoded as 2013. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age

**R script:**

```{r harmo3}
ATTICA_w3_dinter$year_of_interview <- car::recode(ATTICA_w3_dinter$date10, "NA=2013; 2103=2013")

ATTICA_w3_ybirth <- tibble(id=ATTICA_w1_age$id)
ATTICA_w3_ybirth$year_of_birth <- ATTICA_w3_dinter$year_of_interview - ATTICA_w1_age$age_w3

ATTICA_ds_w3 <- tibble(id=ATTICA_w3_ybirth$id)
ATTICA_ds_w3$ybirth <- car::recode(ATTICA_w3_ybirth$year_of_birth, "NA=999")
ATTICA_ds_w3$ybirth <- labelled(ATTICA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ATTICA_ds_w3$ybirth
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ATTICA_ds_w3, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

l.hds <- list(w1 = ATTICA_ds_w1, w2 = ATTICA_ds_w2, w3 = ATTICA_ds_w3)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("ATTICA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("ATTICA_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)



```

# Quality estimation


An interval of error is expected since we do not know the exact age 
(days/months).
"date_birth" is computed as the difference between the actual age and 
the baseline interview date: 
baseline interview date-age in years. 







```{r save, echo=FALSE}
ybirth <- ATTICA_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")
rm(ybirth)

ybirth <- ATTICA_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
rm(ybirth)

ybirth <- ATTICA_ds_w3
save(ybirth, file = "../RData/w3/ybirth.RData")
rm(ybirth)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
