---
title: "Sex"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```


```{r lab, echo=FALSE}
ds_label <- "Sex"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `sex`
* Variable label: `biological sex`
* Variable description: `participant's biological sex`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | female
1        | male

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing





<!-- ########################################################## --> 

# Data process

## ATTICA (Greek Population)

### Wave 1 

#### Study-specific variable description


* Name: `sex`
* Label: `Sex of Subjects`
* Categories: 
    + `0 = Female`
    + `1 = Male`
* Description:
```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_sex','ATTICA.ATTICA_Baseline',
                         variables=list('sex'), missings = TRUE)
ATTICA_w1_sex <- opal.execute(o,'ATTICA_w1_sex')
```

```{r local1, echo=FALSE}
vari <-  ATTICA_w1_sex$sex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ATTICA_w1_sex, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable.

**R script:**

```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_sex$id)
ATTICA_ds_w1$sex <- ATTICA_w1_sex$sex
ATTICA_ds_w1$sex <- labelled(ATTICA_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ATTICA_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(ATTICA_ds_w1$sex)
BeforeH <- table(ATTICA_w1_sex$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 




### Wave 2 

#### Study-specific variable description

* Name: `sex`
* Label: `Sex of Subjects`
* Categories: 
    + `0 = Female`
    + `1 = Male`
* Description:
```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_sex','ATTICA.ATTICA_Baseline',
                         variables=list('sex'), missings = TRUE)
ATTICA_w1_sex <- opal.execute(o,'ATTICA_w1_sex')
```

```{r local2, echo=FALSE}
vari <- ATTICA_w1_sex$sex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ATTICA_w1_sex, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable.

**R script:**

```{r harmo2, echo=TRUE}
ATTICA_ds_w2 <- tibble(id=ATTICA_w1_sex$id)
ATTICA_ds_w2$sex <- ATTICA_w1_sex$sex
ATTICA_ds_w2$sex <- labelled(ATTICA_ds_w2$sex, labels = c("Female"=0, "Male"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ATTICA_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(ATTICA_ds_w2$sex)
BeforeH <- table(ATTICA_w1_sex$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 


### Wave 3 

#### Study-specific variable description


* Name: `sex`
* Label: `Sex of Subjects`
* Categories: 
    + `0 = Female`
    + `1 = Male`
* Description:
```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_sex','ATTICA.ATTICA_Baseline',
                         variables=list('sex'), missings = TRUE)
ATTICA_w1_sex <- opal.execute(o,'ATTICA_w1_sex')
```

```{r local3, echo=FALSE}
vari <- ATTICA_w1_sex$sex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ATTICA_w1_sex, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable.

**R script:**

```{r harmo3, echo=TRUE}
ATTICA_ds_w3 <- tibble(id=ATTICA_w1_sex$id)
ATTICA_ds_w3$sex <- ATTICA_w1_sex$sex
ATTICA_ds_w3$sex <- labelled(ATTICA_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ATTICA_ds_w3$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(ATTICA_ds_w3$sex)
BeforeH <- table(ATTICA_w1_sex$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 

# Quality estimation
No comments.


```{r save, echo=FALSE}
sex <- ATTICA_ds_w1
save(sex, file = "../RData/w1/sex.RData")
rm(sex)

sex <- ATTICA_ds_w2
save(sex, file = "../RData/w2/sex.RData")
rm(sex)

sex <- ATTICA_ds_w3
save(sex, file = "../RData/w3/sex.RData")
rm(sex)
```




```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
