---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing





<!-- ########################################################## --> 

# Data process
## Greek Population

#### Study-specific variable description

 

* Name: `family`
* Label: `Marital status`
* Categories: 
    + `1 = Never married`
    + `2 = Married`
    + `3 = Divorced`
    + `4 = Widowed`
    
* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_ms','ATTICA.ATTICA_Baseline',
                         variables=list('family'), missings = TRUE)
```

```{r local1,  echo=FALSE}
ATTICA_w1_ms <- opal.execute(o,'ATTICA_w1_ms')
vari <- ATTICA_w1_ms$family
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ATTICA_w1_ms, aes(x=factor(family))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("family") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same variable than the study-specific variable.

**R script:**

```{r harmo1,  echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_ms$id)
ATTICA_ds_w1$marital_status <- ATTICA_w1_ms$family
ATTICA_ds_w1$marital_status <- labelled(ATTICA_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- ATTICA_ds_w1$marital_status # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "marital_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital_status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(ATTICA_w1_ms$family)
AfterH <- table(ATTICA_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","2", "3", "4")
kable(C)
```





### Wave 2 

#### Study-specific variable description

There are no variable.




### Wave 3 

#### Study-specific variable description

There are no variable.


# Quality estimation

No comments


```{r save, echo=FALSE}
marital_status <- ATTICA_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)
```


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```