---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Greek population
### Wave 1 

#### Study-specific variable description


* Name: `educat`
* Label: `Years of school`
* Type of variable: `countinous`
* Description:
```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_educ','ATTICA.ATTICA_Baseline',
                         variables=list('educat'), missings = TRUE)
```

```{r local1, echo=FALSE}
ATTICA_w1_educ <- opal.execute(o,'ATTICA_w1_educ')
vari <- ATTICA_w1_educ$educat
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ATTICA_w1_educ$educat, missing_values = NA)
ggplot(ATTICA_w1_educ, aes(educat)) + geom_histogram(stat="count", fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode values between 0 and 5 into 0`
* `recode values between 6 and 11 into 1`
* `recode values between 12 and 17 into 2`
* `recode values 18 or higher into 3`
* `recode NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_educ$id)
ATTICA_ds_w1$education <- car::recode(ATTICA_w1_educ$educat, "0:5='0'; 6:11='1'; 12:17='2'; 18:36='3'; NA='999'")
ATTICA_ds_w1$education <- labelled(ATTICA_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ATTICA_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ATTICA_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(ATTICA_w1_educ$educat)
BeforeH <- c(sum(BeforeH[1:6]), sum(BeforeH[7:12]),sum(BeforeH[13:18]), sum(BeforeH[19:length(BeforeH)]), sum(is.na(ATTICA_w1_educ$educat)))
AfterH <- table(ATTICA_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("[0,5]->0", "[6,11]->1", "[12,17]->2", "18+->3", "NA->999")
kable(C)
```



### Wave 2 

There is no variable.


### Wave 3 

There is no variable.


# Quality estimation

They didn't collected level of education. They collected years of schooling. 
We transformed it into a categorical variable taking into account the ISCED levels and some directions from the greek partners. 


```{r save, echo=FALSE}
education <- ATTICA_ds_w1
save(education, file = "../RData/w1/education.RData")
rm(education)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
