---
title: "Childhood socioeconomic position"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../../CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/childsepDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/childsepDS.R')
```



# Data process


## China

### Wave 1 

#### Study-specific variable description

| **Name** | `ca014_1_` |`ca014_2_`|
|-|-|-|
| **Label** | `Highest Occupation of Your Father`| `Highest Occupation of Your Mother`|
| **Table name** | `family_information_wave1`| `family_information_wave1`|
| **Categories** | `1 = Managers` <br/> `2 = Professionals and technicians` <br/> `3 = Clerks` <br/> `4 = Commercial and service workers` <br/> `5 = Agricultural, forestry, husbandry and fishery producers` <br/> `6 = Production and transportation workers`| `1 = Managers` <br/> `2 = Professionals and technicians` <br/> `3 = Clerks` <br/> `4 = Commercial and service workers` <br/> `5 = Agricultural, forestry, husbandry and fishery producers` <br/> `6 = Production and transportation workers`|
| **Missings** | `7 = Can't be specified (Unclassifiable work)`<br/>`NA` | `7 = Can't be specified (Unclassifiable work)`<br/>`NA` |
| **Description** |  |  |



```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.family_information_wave1', variables=list('ca014_1_','ca014_2_'), missings = TRUE)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')


opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids', variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)



CHARLS_w1 <- left_join(CHARLS_w1_id[, "id"], CHARLS_w1_2, by="id")

```

```{r local w1, echo=F}

vbl <- CHARLS_w1$ca014_1_
vbl_miss <- c(7)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "ca014_1_")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w1$ca014_2_
vbl_miss <- c(7)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "ca014_2_")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variables its minimum (highest occupation) has to be recoded as follows:

* `1:2 into 0`
* `3:4 into 1`
* `5:6 into 2`
* `7 into 993`
* `NA into 999`

**R script:**

```{r harmo w1}

CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$childsep <- car::recode(pmin(CHARLS_w1$ca014_1_,CHARLS_w1$ca014_2_, na.rm = T), "1:2 = 0; 3:4 = 1; 5:6 = 2; 7 = 993; NA = 999")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- CHARLS_ds_w1$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(childsep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** | `ca014_1_` |`ca014_2_`|
|-|-|-|
| **Label** | `Highest Occupation of Your Father`| `Highest Occupation of Your Mother`|
| **Table name** | `Family_Information_wave2`| `Family_Information_wave2`|
| **Categories** | `1 = Managers` <br/> `2 = Professionals and technicians` <br/> `3 = Clerks` <br/> `4 = Commercial and service workers` <br/> `5 = Agricultural, forestry, husbandry and fishery producers` <br/> `6 = Production and transportation workers`| `1 = Managers` <br/> `2 = Professionals and technicians` <br/> `3 = Clerks` <br/> `4 = Commercial and service workers` <br/> `5 = Agricultural, forestry, husbandry and fishery producers` <br/> `6 = Production and transportation workers`|
| **Missings** | `7 = Can't be specified (Unclassifiable work)`<br/>`NA` | `7 = Can't be specified (Unclassifiable work)`<br/>`NA` |
| **Description** |  |  |



```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Family_Information_wave2', variables=list('ca014_1_','ca014_2_'), missings = TRUE)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')


opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')


CHARLS_w2 <- left_join(CHARLS_w2_id[, "id"], CHARLS_w2_2, by="id")

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$ca014_1_
vbl_miss <- c(7)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "ca014_1_")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- CHARLS_w2$ca014_2_
vbl_miss <- c(7)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "ca014_2_")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variables its minimum (highest occupation) has to be recoded as follows:

* `1:2 into 0`
* `3:4 into 1`
* `5:6 into 2`
* `NA into 999`

**R script:**

```{r harmo w2, tidy=FALSE}

CHARLS_ds_w2 <- CHARLS_w2 %>%
  left_join(CHARLS_w1, by = "id", suffix = c("",".w1")) %>%
  mutate(childsep = do.call(pmin, c(select(., contains("ca014")), na.rm = TRUE))) %>%
  mutate(childsep = case_when(
    childsep %in% c(1:2) ~ 0,
    childsep %in% c(3:4) ~ 1,
    childsep %in% c(5:6) ~ 2,
    childsep %in% c(7) ~ 993,
    TRUE ~ 999
  )) %>%
  select(id, childsep)

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- CHARLS_ds_w2$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(childsep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)

}
```




# Quality estimation





```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
