---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mbirthDS.R')
```

# Data process

## China


### Wave 1 

#### Study-specific variable description




| **Name** | `ba002_2` | `ba002_2` |
|----------|------------|-|
| **Label** | `When were You Born:Month` |  `Birth Month` | 
| **Table name** | `Demographic_Background_wave2` |`demographic_background_wave1`|
| **Missings** | `0 = do not remember month and day`<br/>`NA` | `0 = do not remember month and day`<br/>`NA` |
| **Description** |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_mbirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_mbirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_mbirth2 <- opal.execute(o,'CHARLS_w2_mbirth2')
CHARLS_w1_mbirth2 <- opal.execute(o,'CHARLS_w1_mbirth2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
```

```{r local1, echo=F}

CHARLS_w1_mbirth2$oldid <- CHARLS_w1_mbirth2$id
CHARLS_w1_mbirth2$id <- CHARLS_ids(ids = CHARLS_w1_mbirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_mbirth <- Add_indiv(old = CHARLS_w1_mbirth2, new = CHARLS_w1_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_mbirth22 <- Add_indiv(old = CHARLS_w2_mbirth2, new = CHARLS_w1_id)

CHARLS_w1_mbirth$ba002_2_w2 <- CHARLS_w2_mbirth22$ba002_2

vari <- CHARLS_w1_mbirth$ba002_2
vbl_miss <- c(0)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "ba002_2") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(filter(CHARLS_w1_mbirth,!vari %in% vbl_miss), aes(ba002_2)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_mbirth$ba002_2_w2
vbl_miss <- c(0)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "ba002_2_w2") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(filter(CHARLS_w1_mbirth,!vari %in% vbl_miss), aes(ba002_2_w2)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`
* `0 into 998`

Year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.


**R script:**

```{r harmo1}
CHARLS_w1_mbirth$mbirth <- CHARLS_w1_mbirth$ba002_2_w2

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w1_mbirth$mbirth[is.na(CHARLS_w1_mbirth$mbirth)] <- CHARLS_w1_mbirth$ba002_2[is.na(CHARLS_w1_mbirth$mbirth)]

#It is completed the 0 with the study-specific variable from wave 2
CHARLS_w1_mbirth$mbirth[which(CHARLS_w1_mbirth$mbirth==0)] <- CHARLS_w1_mbirth$ba002_2[which(CHARLS_w1_mbirth$mbirth==0)]



CHARLS_ds_w1 <- tibble(id=CHARLS_w1_mbirth$id)
CHARLS_ds_w1$mbirth <- car::recode(CHARLS_w1_mbirth$mbirth, "NA=999; 0=998")
CHARLS_ds_w1$mbirth <- labelled(CHARLS_ds_w1$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(CHARLS_w1_mbirth$mbirth)
BeforeH <- c(BeforeH[2:13], BeforeH[1], sum(is.na(CHARLS_w1_mbirth$mbirth)))
AfterH <- table(CHARLS_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12],"0->998", "NA->999")
kable(C)
```






### Wave 2 

#### Study-specific variable description

| **Name** | `ba002_2` |  `ba002_2` |
|----------|------------|-|-|
| **Label** | `Birth Month` | `When were You Born:Month` |
| **Table name** | `demographic_background_wave1` |`Demographic_Background_wave2`|
| **Missings** | `0 = do not remember month and day`<br/>`NA` | `0 = do not remember month and day`<br/>`NA` |
| **Description** |  |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_mbirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_mbirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_mbirth2 <- opal.execute(o,'CHARLS_w1_mbirth2')
CHARLS_w2_mbirth2 <- opal.execute(o,'CHARLS_w2_mbirth2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
```

```{r local2, echo=F}

CHARLS_w1_mbirth2$oldid <- CHARLS_w1_mbirth2$id
CHARLS_w1_mbirth2$id <- CHARLS_ids(ids = CHARLS_w1_mbirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_mbirth <- Add_indiv(old = CHARLS_w1_mbirth2, new = CHARLS_w2_id)




Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_mbirth <- Add_indiv(old = CHARLS_w2_mbirth2, new = CHARLS_w2_id)
CHARLS_w2_mbirth$ba002_2_w1 <- CHARLS_w1_mbirth$ba002_2

vari <- CHARLS_w2_mbirth$ba002_2_w1
vbl_miss <- c(0)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "ba002_2_w1") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(filter(CHARLS_w2_mbirth,!vari %in% vbl_miss), aes(ba002_2_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_mbirth$ba002_2
vbl_miss <- c(0)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "ba002_2") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(filter(CHARLS_w2_mbirth,!vari %in% vbl_miss), aes(ba002_2)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`
* `0 into 998`

Year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.

**R script:**

```{r harmo2}
CHARLS_w2_mbirth$mbirth <- CHARLS_w2_mbirth$ba002_2

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w2_mbirth$mbirth[is.na(CHARLS_w2_mbirth$mbirth)] <- CHARLS_w2_mbirth$ba002_2_w1[is.na(CHARLS_w2_mbirth$mbirth)]

#It is completed the 0 with the study-specific variable from wave 2
CHARLS_w2_mbirth$mbirth[which(CHARLS_w2_mbirth$mbirth==0)] <- CHARLS_w2_mbirth$ba002_2_w1[which(CHARLS_w2_mbirth$mbirth==0)]


CHARLS_ds_w2 <- tibble(id=CHARLS_w2_mbirth$id)
CHARLS_ds_w2$mbirth <- car::recode(as.numeric(CHARLS_w2_mbirth$mbirth), "NA=999; 0=998")
CHARLS_ds_w2$mbirth <- labelled(CHARLS_ds_w2$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(CHARLS_w2_mbirth$mbirth)
BeforeH <- c(BeforeH[2:13], BeforeH[1], sum(is.na(CHARLS_w2_mbirth$mbirth)))
AfterH <- table(CHARLS_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12], "0->998","NA->999")
kable(C)
```

## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

l.hds <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("CHARLS_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("CHARLS_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)



```


# Quality estimation
No comments.



?1st July? is imputed because month of birth is not available.

For the follow-up wave, we assume the computed variable is the same as for baseline. 



```{r save, echo=FALSE}
mbirth <- CHARLS_ds_w1
save(mbirth, file = "../RData/w1/mbirth.RData")
rm(mbirth)

mbirth <- CHARLS_ds_w2
save(mbirth, file = "../RData/w2/mbirth.RData")
rm(mbirth)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
