---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 

```{r lab, echo=FALSE}
ds_label <- "Month of birth"
```


# Description of DataSchema variable 

The description of harmonised variable is the following:


* Short name: `mbirth`
* Variable label: `month of birth`
* Variable description: `Month of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## CHARLS


### Wave 1 

#### Study-specific variables




| **Name** | `ba002_2` | `ba002_2` |
|----------|------------|-|
| **Label** | `When were You Born:Month` |  `Birth Month` | 
| **Table name** | `Demographic_Background_wave2` |`demographic_background_wave1`|
| **Description** |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_mbirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_mbirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=F}
CHARLS_w2_mbirth2 <- opal.execute(o,'CHARLS_w2_mbirth2')
CHARLS_w1_mbirth2 <- opal.execute(o,'CHARLS_w1_mbirth2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_mbirth2$oldid <- CHARLS_w1_mbirth2$id
CHARLS_w1_mbirth2$id <- CHARLS_ids(ids = CHARLS_w1_mbirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_mbirth <- Add_indiv(old = CHARLS_w1_mbirth2, new = CHARLS_w1_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_mbirth22 <- Add_indiv(old = CHARLS_w2_mbirth2, new = CHARLS_w1_id)

CHARLS_w1_mbirth$ba002_2_w2 <- CHARLS_w2_mbirth22$ba002_2

vari <- CHARLS_w1_mbirth$ba002_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_mbirth, aes(ba002_2)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")

vari <- CHARLS_w1_mbirth$ba002_2_w2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_mbirth, aes(ba002_2_w2)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`
* `0 into 999`

Year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.


**R script:**

```{r harmo1}
CHARLS_w1_mbirth$mbirth <- CHARLS_w1_mbirth$ba002_2_w2

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w1_mbirth$mbirth[is.na(CHARLS_w1_mbirth$mbirth)] <- CHARLS_w1_mbirth$ba002_2[is.na(CHARLS_w1_mbirth$mbirth)]

#It is completed the 0 with the study-specific variable from wave 2
CHARLS_w1_mbirth$mbirth[which(CHARLS_w1_mbirth$mbirth==0)] <- CHARLS_w1_mbirth$ba002_2[which(CHARLS_w1_mbirth$mbirth==0)]



CHARLS_ds_w1 <- tibble(id=CHARLS_w1_mbirth$id)
CHARLS_ds_w1$mbirth <- car::recode(CHARLS_w1_mbirth$mbirth, "NA=999; 0=999")
CHARLS_ds_w1$mbirth <- labelled(CHARLS_ds_w1$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(CHARLS_w1_mbirth$mbirth)
BeforeH <- c(BeforeH[2:13], sum(BeforeH[1], sum(is.na(CHARLS_w1_mbirth$mbirth))))
AfterH <- table(CHARLS_ds_w1$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12], "(0,NA)->999")
C
```






### Wave 2 

#### Study-specific variables

| **Name** | `ba002_2` |  `ba002_2` |
|----------|------------|-|-|
| **Label** | `Birth Month` | `When were You Born:Month` |
| **Table name** | `demographic_background_wave1` |`Demographic_Background_wave2`|
| **Description** |  |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_mbirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_mbirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_2'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=F}
CHARLS_w1_mbirth2 <- opal.execute(o,'CHARLS_w1_mbirth2')
CHARLS_w2_mbirth2 <- opal.execute(o,'CHARLS_w2_mbirth2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w1_mbirth2$oldid <- CHARLS_w1_mbirth2$id
CHARLS_w1_mbirth2$id <- CHARLS_ids(ids = CHARLS_w1_mbirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_mbirth <- Add_indiv(old = CHARLS_w1_mbirth2, new = CHARLS_w2_id)




Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_2=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_mbirth <- Add_indiv(old = CHARLS_w2_mbirth2, new = CHARLS_w2_id)
CHARLS_w2_mbirth$ba002_2_w1 <- CHARLS_w1_mbirth$ba002_2

vari <- CHARLS_w2_mbirth$ba002_2_w1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_mbirth, aes(ba002_2_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")

vari <- CHARLS_w2_mbirth$ba002_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_mbirth, aes(ba002_2)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`

Year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.

**R script:**

```{r harmo2}
CHARLS_w2_mbirth$mbirth <- CHARLS_w2_mbirth$ba002_2

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w2_mbirth$mbirth[is.na(CHARLS_w2_mbirth$mbirth)] <- CHARLS_w2_mbirth$ba002_2_w1[is.na(CHARLS_w2_mbirth$mbirth)]

#It is completed the 0 with the study-specific variable from wave 2
CHARLS_w2_mbirth$mbirth[which(CHARLS_w2_mbirth$mbirth==0)] <- CHARLS_w2_mbirth$ba002_2_w1[which(CHARLS_w2_mbirth$mbirth==0)]


CHARLS_ds_w2 <- tibble(id=CHARLS_w2_mbirth$id)
CHARLS_ds_w2$mbirth <- car::recode(as.numeric(CHARLS_w2_mbirth$mbirth), "NA=999; 0=999")
CHARLS_ds_w2$mbirth <- labelled(CHARLS_ds_w2$mbirth, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(CHARLS_w2_mbirth$mbirth)
BeforeH <- c(BeforeH[2:13], sum(BeforeH[1], sum(is.na(CHARLS_w2_mbirth$mbirth))))
AfterH <- table(CHARLS_ds_w2$mbirth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:12], "(0,NA)->999")
C
```




# Quality estimation
No comments.



“1st July” is imputed because month of birth is not available.

For the follow-up wave, we assume the computed variable is the same as for baseline. 



```{r save, echo=FALSE}
mbirth <- CHARLS_ds_w1
save(mbirth, file = "../RData/w1/mbirth.RData")
rm(mbirth)

mbirth <- CHARLS_ds_w2
save(mbirth, file = "../RData/w2/mbirth.RData")
rm(mbirth)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
