---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```



# Data process

## China

### Wave 1 

#### Study-specific variable description

| **Name** | `ba002_1` | `ba002_1` |
|----------|------------|-|
| **Label** | `When were You Born:Year` |  `Birth Year` |
| **Table name** | `Demographic_Background_wave2` |`demographic_background_wave1`|
| **Description** |  |  |




```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_ybirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_ybirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_ybirth2 <- opal.execute(o,'CHARLS_w2_ybirth2')
CHARLS_w1_ybirth2 <- opal.execute(o,'CHARLS_w1_ybirth2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


CHARLS_w1_ybirth2$oldid <- CHARLS_w1_ybirth2$id
CHARLS_w1_ybirth2$id <- CHARLS_ids(ids = CHARLS_w1_ybirth2$oldid)

```

```{r local1, echo=F}

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_ybirth <- Add_indiv(old = CHARLS_w1_ybirth2, new = CHARLS_w1_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ybirth22 <- Add_indiv(old = CHARLS_w2_ybirth2, new = CHARLS_w1_id)

CHARLS_w1_ybirth$ba002_1_w2 <- CHARLS_w2_ybirth22$ba002_1


vari <-CHARLS_w1_ybirth$ba002_1_w2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1_w2") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_ybirth, aes(ba002_1_w2)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-CHARLS_w1_ybirth$ba002_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_ybirth, aes(ba002_1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`

Since the year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.

**R script:**

```{r harmo1}

CHARLS_w1_ybirth$ba002_1_w1w2 <- CHARLS_w1_ybirth$ba002_1_w2
CHARLS_w1_ybirth$ba002_1_w1w2[is.na(CHARLS_w1_ybirth$ba002_1_w1w2)] <- CHARLS_w1_ybirth$ba002_1[is.na(CHARLS_w1_ybirth$ba002_1_w1w2)]

CHARLS_ds_w1 <- tibble(id=CHARLS_w1_ybirth$id)
CHARLS_ds_w1$ybirth <- car::recode(CHARLS_w1_ybirth$ba002_1_w1w2, "NA=999")
CHARLS_ds_w1$ybirth <- labelled(CHARLS_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1910, 1989)
```

#### Validation
```{r crosstabulation1, echo=F}
```







### Wave 2 

#### Study-specific variable description

| **Name** | `ba002_1` |  `ba002_1` |
|----------|------------|-|
| **Label** | `Birth Year` | `When were You Born:Year` |
| **Table name** | `demographic_background_wave1` |`Demographic_Background_wave2`|
| **Description** |  |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_ybirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_ybirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_ybirth2 <- opal.execute(o,'CHARLS_w1_ybirth2')
CHARLS_w2_ybirth2 <- opal.execute(o,'CHARLS_w2_ybirth2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
```

```{r local2, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ybirth <- Add_indiv(old = CHARLS_w2_ybirth2, new = CHARLS_w2_id)


CHARLS_w1_ybirth2$oldid <- CHARLS_w1_ybirth2$id
CHARLS_w1_ybirth2$id <- CHARLS_ids(ids = CHARLS_w1_ybirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_ybirth22 <- Add_indiv(old = CHARLS_w1_ybirth2, new = CHARLS_w2_id)

CHARLS_w2_ybirth$ba002_1_w1 <- CHARLS_w1_ybirth22$ba002_1


vari <- CHARLS_w2_ybirth$ba002_1_w1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1_w1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_ybirth, aes(ba002_1_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_ybirth$ba002_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_ybirth, aes(ba002_1_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

The year of birth study-specific variable in wave 2 have 77.21% of missing data, because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo2}
CHARLS_w2_ybirth$ybirth <- CHARLS_w2_ybirth$ba002_1

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w2_ybirth$ybirth[is.na(CHARLS_w2_ybirth$ybirth)] <- CHARLS_w2_ybirth$ba002_1_w1[is.na(CHARLS_w2_ybirth$ybirth)]

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_ybirth$id)
CHARLS_ds_w2$ybirth <- car::recode(CHARLS_w2_ybirth$ybirth, "NA=999")
CHARLS_ds_w2$ybirth <- labelled(CHARLS_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1910, 1989)
```

#### Validation
```{r crosstabulation2, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves


```{r summ, echo=F}

l.hds <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("CHARLS_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("CHARLS_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)



```


# Quality estimation
No comments.


```{r save, echo=FALSE}
ybirth <- CHARLS_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")
rm(ybirth)

ybirth <- CHARLS_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
rm(ybirth)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
