---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```



# Data process

## China

### Wave 1 

#### Study-specific variable description

| **Name** | `ba002_1` | `ba002_1` |
|----------|------------|-|
| **Label** | `When were You Born:Year` |  `Birth Year` |
| **Table name** | `Demographic_Background_wave2` |`demographic_background_wave1`|
| **Description** |  |  |




```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_ybirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_ybirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_ybirth2 <- opal.execute(o,'CHARLS_w2_ybirth2')
CHARLS_w1_ybirth2 <- opal.execute(o,'CHARLS_w1_ybirth2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


CHARLS_w1_ybirth2$oldid <- CHARLS_w1_ybirth2$id
CHARLS_w1_ybirth2$id <- CHARLS_ids(ids = CHARLS_w1_ybirth2$oldid)

```

```{r local1, echo=F}

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_ybirth <- Add_indiv(old = CHARLS_w1_ybirth2, new = CHARLS_w1_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ybirth22 <- Add_indiv(old = CHARLS_w2_ybirth2, new = CHARLS_w1_id)

CHARLS_w1_ybirth$ba002_1_w2 <- CHARLS_w2_ybirth22$ba002_1


vari <-CHARLS_w1_ybirth$ba002_1_w2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1_w2") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_ybirth, aes(ba002_1_w2)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <-CHARLS_w1_ybirth$ba002_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_ybirth, aes(ba002_1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`

Since the year of birth study-specific variable in wave 2 have 77.21% of missing data because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.

**R script:**

```{r harmo1}

CHARLS_w1_ybirth$ba002_1_w1w2 <- CHARLS_w1_ybirth$ba002_1_w2
CHARLS_w1_ybirth$ba002_1_w1w2[is.na(CHARLS_w1_ybirth$ba002_1_w1w2)] <- CHARLS_w1_ybirth$ba002_1[is.na(CHARLS_w1_ybirth$ba002_1_w1w2)]

CHARLS_ds_w1 <- tibble(id=CHARLS_w1_ybirth$id)
CHARLS_ds_w1$ybirth <- car::recode(CHARLS_w1_ybirth$ba002_1_w1w2, "NA=999")
CHARLS_ds_w1$ybirth <- labelled(CHARLS_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1910, 1989)
```

#### Validation
```{r crosstabulation1, echo=F}
```







### Wave 2 

#### Study-specific variable description

| **Name** | `ba002_1` |  `ba002_1` |
|----------|------------|-|
| **Label** | `Birth Year` | `When were You Born:Year` |
| **Table name** | `demographic_background_wave1` |`Demographic_Background_wave2`|
| **Description** |  |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_ybirth2','CHARLS.demographic_background_wave1',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_ybirth2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba002_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w1_ybirth2 <- opal.execute(o,'CHARLS_w1_ybirth2')
CHARLS_w2_ybirth2 <- opal.execute(o,'CHARLS_w2_ybirth2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
```

```{r local2, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ybirth <- Add_indiv(old = CHARLS_w2_ybirth2, new = CHARLS_w2_id)


CHARLS_w1_ybirth2$oldid <- CHARLS_w1_ybirth2$id
CHARLS_w1_ybirth2$id <- CHARLS_ids(ids = CHARLS_w1_ybirth2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba002_1=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_ybirth22 <- Add_indiv(old = CHARLS_w1_ybirth2, new = CHARLS_w2_id)

CHARLS_w2_ybirth$ba002_1_w1 <- CHARLS_w1_ybirth22$ba002_1


vari <- CHARLS_w2_ybirth$ba002_1_w1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1_w1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_ybirth, aes(ba002_1_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_ybirth$ba002_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba002_1") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_ybirth, aes(ba002_1_w1)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

The year of birth study-specific variable in wave 2 have 77.21% of missing data, because is a confirmatory variable of year of birth from wave 1. It means that in wave 2 they ask "BA001_W2_1 We record your birth time is [Birth Time], is it right?" if the answer is yes they don't ask for date of birth and age again, but if their answer is No they ask for the date of birth and age again, in other to correct the mistakes of the study-specific variable from wave 1.


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable from wave 2, but the missing values have to be recoded from the study-specific variable from wave 1 and all other missing data have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo2}
CHARLS_w2_ybirth$ybirth <- CHARLS_w2_ybirth$ba002_1

#It is completed the missing data with the study-specific variable from wave 1
CHARLS_w2_ybirth$ybirth[is.na(CHARLS_w2_ybirth$ybirth)] <- CHARLS_w2_ybirth$ba002_1_w1[is.na(CHARLS_w2_ybirth$ybirth)]

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_ybirth$id)
CHARLS_ds_w2$ybirth <- car::recode(CHARLS_w2_ybirth$ybirth, "NA=999")
CHARLS_ds_w2$ybirth <- labelled(CHARLS_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(1910, 1989)
```

#### Validation
```{r crosstabulation2, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
