---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process

## China

### Wave 1 

#### Study-specific variable description

| **Name** | `ba004` |`ybirth`|`mbirth`|`iyear`|`imonth`|
|----------|------------|-|-|-|-|
| **Label** | `Age` | `Year of birth`|`Month of birth`|`Interview Year`|`Interview Month`|
| **Table name** | `demographic_background_wave1` | `charls_w1_hd`\*|`charls_w1_hd`\*|`weight_wave1`|`weight_wave1`|
| **Description** |  |  |  |  |  |

\* These tables are not extracted from the database CHARLS, but from ATHLOS. They contain already harmonised variables.

<!--Cuando se actualicen bbdd de ATHLOS, puesto que las variables de fecha de nacimiento son mbirth, ybirth (y dbirth), abajo tienen que ser actualizadas
-->

```{r assign1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_age2','CHARLS.demographic_background_wave1',variables=list('ba004'), missings = TRUE)
CHARLS_w1_age2 <- opal.execute(o,'CHARLS_w1_age2')


opal.assign.table.tibble(o, 'CHARLS_w1_birth','CHARLS_HD.charls_w1_hd', variables=list('mbirth','ybirth'), missings = TRUE)
CHARLS_w1_birth <- opal.execute(o,'CHARLS_w1_birth')

opal.assign.table.tibble(o, 'CHARLS_w1_inter2','CHARLS.weight_wave1', variables=list('iyear', 'imonth'), missings = TRUE)
CHARLS_w1_inter2 <- opal.execute(o,'CHARLS_w1_inter2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


# adding a zero to the old id's in CHARLS_w1_age2 with CHARLS_ids
CHARLS_w1_age2$oldid <- CHARLS_w1_age2$id
CHARLS_w1_age2$id <- CHARLS_ids(ids = CHARLS_w1_age2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba004=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_age <- Add_indiv(old = CHARLS_w1_age2, new = CHARLS_w1_id)


# adding a zero to the old id's in CHARLS_w1_inter2 with CHARLS_ids (and correction of an id)
CHARLS_w1_inter2$oldid <- CHARLS_w1_inter2$id
CHARLS_w1_inter2$id[CHARLS_w1_inter2$id==151156201] <- "15115620101"
CHARLS_w1_inter2$id <- CHARLS_ids(ids = CHARLS_w1_inter2$id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], iyear=as.numeric(new_2[,2]), imonth=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w1_inter <- Add_indiv(old = CHARLS_w1_inter2, new = CHARLS_w1_id)

```

```{r preharm w1, echo=T}
CHARLS_w1_age$year_of_birth <- car::recode(CHARLS_w1_birth$ybirth, "miss_values_vector=NA")  
CHARLS_w1_age$month_of_birth <- car::recode(CHARLS_w1_birth$mbirth, "miss_values_vector=NA")  
CHARLS_w1_age$iyear <- CHARLS_w1_inter$iyear
CHARLS_w1_age$imonth <- CHARLS_w1_inter$imonth
```

```{r local1, echo=F}

vari <- CHARLS_w1_age$year_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "year_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(year_of_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_age$month_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "month_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(month_of_birth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- as.numeric(CHARLS_w1_age$iyear)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "iyear")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(iyear))) + geom_histogram(stat="count", fill="steelblue") + xlab("year of interview") + ylab("Frequency")

vari <- as.numeric(CHARLS_w1_age$imonth)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "imonth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(imonth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of interview") + ylab("Frequency")

vari <- CHARLS_w1_age$ba004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba004")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(ba004)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missings values have to be recoded as follows:

* `NA into 999`

It is going to compute the age using the formula date_of_interview - date_of_birth because the study-specific variable has 99.81% of missing data. 

**R script:**

```{r harmo1}
CHARLS_w1_age$ba004 <- car::recode(CHARLS_w1_age$ba004, "NA=999")
CHARLS_w1_age$year_of_birth <- car::recode(CHARLS_w1_age$year_of_birth, "NA=999")
CHARLS_w1_age$month_of_birth <- car::recode(CHARLS_w1_age$month_of_birth, "NA=999; 0=999")
CHARLS_w1_age$imonth <- as.numeric(CHARLS_w1_age$imonth)
CHARLS_w1_age$iyear <- as.numeric(CHARLS_w1_age$iyear)

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- (y_int[m_int<m_birth]-y_birth[m_int<m_birth])-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

CHARLS_w1_age$age_c <- comp_age(y_birth=CHARLS_w1_age$year_of_birth, m_birth=CHARLS_w1_age$month_of_birth , y_int=CHARLS_w1_age$iyear, m_int=CHARLS_w1_age$imonth, miss=c(999))

CHARLS_w1_age$age_c[which(CHARLS_w1_age$age_c==999)] <- CHARLS_w1_age$ba004[which(CHARLS_w1_age$age_c==999)]



CHARLS_ds_w1 <- tibble(id=CHARLS_w1_age$id)
CHARLS_ds_w1$age <- car::recode(CHARLS_w1_age$age_c, "NA=999")
CHARLS_ds_w1$age <- labelled(CHARLS_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(17,101)
```


#### Validation
```{r crosstabulation1, echo=F}

CHARLS_w1_age$proff <- CHARLS_w1_age$age_c - CHARLS_w1_age$ba004
CHARLS_w1_age$proff[which(CHARLS_w1_age$age_c==999)] <- NA
CHARLS_w1_age$proff[which(CHARLS_w1_age$ba004==999)] <- NA
kable(CHARLS_w1_age[which(!is.na(CHARLS_w1_age$proff) & CHARLS_w1_age$proff!=0),],align = 'c',caption = 'There are 21 individuals that have discrepancies between the computed age and the reported age. We consider to believe in the computed age. ')

```




### Wave 2 

#### Study-specific variable description

| **Name** | `ba004` |`mbirth`|`ybirth`|`iyear`|`imonth`|`living_status`|
|----------|------|------|-|-|-|-|
| **Label** | `Your Age` | `Month of birth`|`Year of birth`|`Interview Year`|`Interview Month`|`Living status`|
| **Table name** | `Demographic_Background_wave2` | `charls_w2_hd`\*|`charls_w2_hd`\*|`Weights_modif_albert_wave2`|`Weights_modif_albert_wave2`|`charls_w2_hd`\*|
| **Categories** |`continuous`|`continuous`|`continuous`|`continuous`|`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Description** |  |  |  |  |  |  |

\* These tables are not extracted from the database CHARLS, but from ATHLOS. They contain already harmonised variables.


```{r assign2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_age2','CHARLS.Demographic_Background_wave2', variables=list('ba004'), missings = TRUE)
CHARLS_w2_age2 <- opal.execute(o,'CHARLS_w2_age2')

opal.assign.table.tibble(o, 'CHARLS_w2_birth2','CHARLS_HD.charls_w2_hd', variables=list('mbirth','ybirth','living_status'), missings = TRUE)
CHARLS_w2_birth2 <- opal.execute(o,'CHARLS_w2_birth2')


opal.assign.table.tibble(o, 'CHARLS_w2_yinter2','CHARLS.Weights_modif_albert_wave2',variables=list('iyear', 'imonth'), missings = TRUE)
CHARLS_w2_yinter2 <- opal.execute(o,'CHARLS_w2_yinter2')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids', variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w2_birth <- left_join(CHARLS_w2_id,CHARLS_w2_birth2, by="id")

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba004=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_age <- Add_indiv(old = CHARLS_w2_age2, new = CHARLS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], imonth=as.numeric(new_2[,2]), iyear=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_yinter <- Add_indiv(old = CHARLS_w2_yinter2, new = CHARLS_w2_id)



```


```{r preharm w2, echo=T}


CHARLS_w2_age$month_of_birth <- CHARLS_w2_birth$mbirth
CHARLS_w2_age$year_of_birth <- CHARLS_w2_birth$ybirth
CHARLS_w2_age$living_status <- CHARLS_w2_birth$living_status
CHARLS_w2_age$iyear <- CHARLS_w2_yinter$iyear
CHARLS_w2_age$iyear[is.na(CHARLS_w2_age$iyear)] <- 2013
CHARLS_w2_age$imonth <- CHARLS_w2_yinter$imonth

```

```{r local2, echo=F}

vari <- as.numeric(CHARLS_w2_age$ba004)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba004")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(ba004)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vari <- CHARLS_w2_age$year_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "year_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(year_of_birth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_age$month_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "month_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(month_of_birth))) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- as.numeric(CHARLS_w2_age$iyear)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "iyear")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(iyear))) + geom_histogram(stat="count", fill="steelblue") + xlab("year of interview") + ylab("Frequency")

vari <- as.numeric(CHARLS_w2_age$imonth)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "imonth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(imonth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of interview") + ylab("Frequency")

vari <- CHARLS_w2_age$living_status
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "living_status")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")


```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missings values have to be recoded as follows:

* `NA into 999`

It is going to compute the age using the formula date_of_interview - date_of_birth because the study-specific variable has 99.65% of missing data. 

* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo2}
CHARLS_w2_age$ba004 <- car::recode(CHARLS_w2_age$ba004, "NA=999")

CHARLS_w2_age$month_of_birth <- car::recode(CHARLS_w2_age$month_of_birth, "NA=999")
CHARLS_w2_age$year_of_birth <- car::recode(CHARLS_w2_age$year_of_birth, "NA=999")
CHARLS_w2_age$imonth <- car::recode(as.numeric(CHARLS_w2_age$imonth), "NA=999")
CHARLS_w2_age$iyear <- as.numeric(CHARLS_w2_age$iyear)

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- (y_int[m_int<m_birth]-y_birth[m_int<m_birth])-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

CHARLS_w2_age$age_c <- comp_age(y_birth=CHARLS_w2_age$year_of_birth , m_birth=CHARLS_w2_age$month_of_birth ,
         y_int=CHARLS_w2_age$iyear , m_int=CHARLS_w2_age$imonth , miss=c(999))





CHARLS_ds_w2 <- tibble(id=CHARLS_w2_age$id)
CHARLS_ds_w2$age <- car::recode(CHARLS_w2_age$age_c, "NA=999")

CHARLS_ds_w2$age[which(CHARLS_w2_age$living_status %in% c(1,2))] <- 996

```




#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "age")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(16,102)
```

#### Validation
```{r crosstabulation2, echo=F}
CHARLS_w2_age$proff <- CHARLS_w2_age$age_c - CHARLS_w2_age$ba004
CHARLS_w2_age$proff[CHARLS_w2_age$age_c==999] <- NA
CHARLS_w2_age$proff[CHARLS_w2_age$ba004==999] <- NA

kable(CHARLS_w2_age[which(!is.na(CHARLS_w2_age$proff) & CHARLS_w2_age$proff!=0),],align = 'c',caption = 'There are 27 individuals that have discrepancies between the computed age and the reported age. We consider to believe in the computed age.')



```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
