---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## China

### Wave 1 

#### Study-specific variable description

| **Name** | `ba004` |`ybirth`|`mbirth`|`iyear`|`imonth`|
|----------|------------|-|-|-|-|
| **Label** | `Age` | `year of birth`|`month of birth`|`Interview Year`|`Interview Month`|
| **Table name** | `demographic_background_wave1` | `ybirth`\*|`mbirth`\*|`weight_wave1`|`weight_wave1`|
| **Description** |  |  |  |  |  |

\* These tables are not extracted from the database CHARLS, but from ATHLOS. They contain already harmonised variables.

<!--Cuando se actualicen bbdd de ATHLOS, puesto que las variables de fecha de nacimiento son mbirth, ybirth (y dbirth), abajo tienen que ser actualizadas
-->

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_age2','CHARLS.demographic_background_wave1',
                         variables=list('ba004'), missings = TRUE)
# opal.assign.table.tibble(o, 'CHARLS_w1_birth2','_Athlos_Harm_Dataset.CHARLS_m_ds_w1',
#                          variables=list('year_of_birth', 'month_of_birth'), missings = TRUE)
load("../RData/w1/ybirth.RData")
load("../RData/w1/mbirth.RData")
opal.assign.table.tibble(o, 'CHARLS_w1_inter2','CHARLS.weight_wave1',
                         variables=list('iyear', 'imonth'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=F}
CHARLS_w1_age2 <- opal.execute(o,'CHARLS_w1_age2')
#CHARLS_w1_birth2 <- opal.execute(o,'CHARLS_w1_birth2')
CHARLS_w1_inter2 <- opal.execute(o,'CHARLS_w1_inter2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

# adding a zero to the old id's in CHARLS_w1_age2 with CHARLS_ids
CHARLS_w1_age2$oldid <- CHARLS_w1_age2$id
CHARLS_w1_age2$id <- CHARLS_ids(ids = CHARLS_w1_age2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), ba004=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_age <- Add_indiv(old = CHARLS_w1_age2, new = CHARLS_w1_id)


# adding a zero to the old id's in CHARLS_w1_inter2 with CHARLS_ids (and correction of an id)
CHARLS_w1_inter2$oldid <- CHARLS_w1_inter2$id
CHARLS_w1_inter2$id[CHARLS_w1_inter2$id==151156201] <- "15115620101"
CHARLS_w1_inter2$id <- CHARLS_ids(ids = CHARLS_w1_inter2$id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], iyear=as.numeric(new_2[,2]), imonth=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w1_inter <- Add_indiv(old = CHARLS_w1_inter2, new = CHARLS_w1_id)

################################quitar cuando se arregle problema individuos: 

# Add_indiv <- function(old, new){
#   
#   new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
#   oldm <- as.matrix(old)
#   
#   for(i in 1:length(new$id)){
#     if(sum(new$id[i]==old$id)>=1){
#       new_2[i,] <- oldm[which(new$id[i]==old$id),]
#     } else {
#       new_2[i,] <- c(new$id[i], NA, NA, NA)
#     }
#   }
#   
#   new_22 <- data.frame(id=new_2[,1], month_of_birth=as.numeric(new_2[,2]), year_of_birth=as.numeric(new_2[,3]))
#   new_22
# }
# 
# CHARLS_w1_birth2 <- Add_indiv(old = CHARLS_w1_birth2, new = CHARLS_w1_id)
#############################################################################

CHARLS_w1_age$year_of_birth <- car::recode(ybirth$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")  #CHARLS_w1_birth2$year_of_birth
CHARLS_w1_age$month_of_birth <- car::recode(mbirth$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")  #CHARLS_w1_birth2$month_of_birth
CHARLS_w1_age$iyear <- CHARLS_w1_inter$iyear
CHARLS_w1_age$imonth <- CHARLS_w1_inter$imonth


vari <- CHARLS_w1_age$year_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "year_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(year_of_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("year of birth") + ylab("Frequency")

vari <- CHARLS_w1_age$month_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "month_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(month_of_birth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of birth") + ylab("Frequency")

vari <- as.numeric(CHARLS_w1_age$iyear)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "iyear")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(iyear))) + geom_histogram(stat="count", fill="steelblue") + xlab("year of interview") + ylab("Frequency")

vari <- as.numeric(CHARLS_w1_age$imonth)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "imonth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(x=factor(imonth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of interview") + ylab("Frequency")

vari <- CHARLS_w1_age$ba004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba004")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w1_age, aes(ba004)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missings values have to be recoded as follows:

* `NA into 999`

It is going to compute the age using the formula date_of_interview - date_of_birth because the study-specific variable has 99.81% of missing data. 

**R script:**

```{r harmo1}
CHARLS_w1_age$ba004 <- car::recode(CHARLS_w1_age$ba004, "NA=999")
CHARLS_w1_age$year_of_birth <- car::recode(CHARLS_w1_age$year_of_birth, "NA=999")
CHARLS_w1_age$month_of_birth <- car::recode(CHARLS_w1_age$month_of_birth, "NA=999; 0=999")
CHARLS_w1_age$imonth <- as.numeric(CHARLS_w1_age$imonth)
CHARLS_w1_age$iyear <- as.numeric(CHARLS_w1_age$iyear)

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- (y_int[m_int<m_birth]-y_birth[m_int<m_birth])-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

CHARLS_w1_age$age_c <- comp_age(y_birth=CHARLS_w1_age$year_of_birth, m_birth=CHARLS_w1_age$month_of_birth , y_int=CHARLS_w1_age$iyear, m_int=CHARLS_w1_age$imonth, miss=c(999))

CHARLS_w1_age$age_c[which(CHARLS_w1_age$age_c==999)] <- CHARLS_w1_age$ba004[which(CHARLS_w1_age$age_c==999)]



CHARLS_ds_w1 <- tibble(id=CHARLS_w1_age$id)
CHARLS_ds_w1$age <- car::recode(CHARLS_w1_age$age_c, "NA=999")
CHARLS_ds_w1$age <- labelled(CHARLS_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(17,101)
```


#### Validation
```{r crosstabulation1, echo=F}

CHARLS_w1_age$proff <- CHARLS_w1_age$age_c - CHARLS_w1_age$ba004
CHARLS_w1_age$proff[which(CHARLS_w1_age$age_c==999)] <- NA
CHARLS_w1_age$proff[which(CHARLS_w1_age$ba004==999)] <- NA
kable(CHARLS_w1_age[which(!is.na(CHARLS_w1_age$proff) & CHARLS_w1_age$proff!=0),],align = 'c',caption = 'There are 21 individuals that have discrepancies between the computed age and the reported age. We consider to believe in the computed age. ')

```




### Wave 2 

#### Study-specific variable description

| **Name** | `ba004` |`mbirth`|`ybirth`|`iyear`|`imonth`|
|----------|------------|-|-|-|-|
| **Label** | `Your Age` | `month of birth`|`year of birth`|`Interview Year`|`Interview Month`|
| **Table name** | `Demographic_Background_wave2` | `mbirth`\*|`ybirth`\*|`Weights_modif_albert_wave2`|`Weights_modif_albert_wave2`|
| **Description** |  |  |  |  |  |

\* These tables are not extracted from the database CHARLS, but from ATHLOS. They contain already harmonised variables.


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_age2','CHARLS.Demographic_Background_wave2',
                         variables=list('ba004'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_birth','_Athlos_Harm_Dataset.CHARLS_m_ds_w2',
                         variables=list('month_of_birth', 'year_of_birth'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_yinter2','CHARLS.Weights_modif_albert_wave2',
                         variables=list('iyear', 'imonth'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=F}
CHARLS_w2_age2 <- opal.execute(o,'CHARLS_w2_age2')
CHARLS_w2_birth <- opal.execute(o,'CHARLS_w2_birth')
CHARLS_w2_yinter2 <- opal.execute(o,'CHARLS_w2_yinter2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba004=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_age <- Add_indiv(old = CHARLS_w2_age2, new = CHARLS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], imonth=as.numeric(new_2[,2]), iyear=as.numeric(new_2[,3]))
  new_22
}

CHARLS_w2_yinter <- Add_indiv(old = CHARLS_w2_yinter2, new = CHARLS_w2_id)

CHARLS_w2_age$month_of_birth <- CHARLS_w2_birth$month_of_birth
CHARLS_w2_age$year_of_birth <- CHARLS_w2_birth$year_of_birth
CHARLS_w2_age$iyear <- CHARLS_w2_yinter$iyear
CHARLS_w2_age$iyear[is.na(CHARLS_w2_age$iyear)] <- 2013
CHARLS_w2_age$imonth <- CHARLS_w2_yinter$imonth

vari <- as.numeric(CHARLS_w2_age$ba004)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ba004")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(ba004)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")

vari <- CHARLS_w2_age$year_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "year_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(year_of_birth)) + geom_histogram(stat="count", fill="steelblue") + xlab("year of birth") + ylab("Frequency")

vari <- CHARLS_w2_age$month_of_birth
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "month_of_birth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(month_of_birth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of birth") + ylab("Frequency")

vari <- as.numeric(CHARLS_w2_age$iyear)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "iyear")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(iyear))) + geom_histogram(stat="count", fill="steelblue") + xlab("year of interview") + ylab("Frequency")

vari <- as.numeric(CHARLS_w2_age$imonth)
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "imonth")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(CHARLS_w2_age, aes(x=factor(imonth))) + geom_histogram(stat="count", fill="steelblue") + xlab("month of interview") + ylab("Frequency")


```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missings values have to be recoded as follows:

* `NA into 999`

It is going to compute the age using the formula date_of_interview - date_of_birth because the study-specific variable has 99.65% of missing data. 

**R script:**

```{r harmo2}
CHARLS_w2_age$ba004 <- car::recode(CHARLS_w2_age$ba004, "NA=999")

CHARLS_w2_age$month_of_birth <- car::recode(CHARLS_w2_age$month_of_birth, "NA=999")
CHARLS_w2_age$year_of_birth <- car::recode(CHARLS_w2_age$year_of_birth, "NA=999")
CHARLS_w2_age$imonth <- car::recode(as.numeric(CHARLS_w2_age$imonth), "NA=999")
CHARLS_w2_age$iyear <- as.numeric(CHARLS_w2_age$iyear)

#function to compute the age
comp_age <- function(y_birth, m_birth, y_int, m_int, miss){
  #first, it's computed the age of all
  age <- NULL
  age[m_int<m_birth] <- (y_int[m_int<m_birth]-y_birth[m_int<m_birth])-1
  age[m_int>=m_birth] <- y_int[m_int>=m_birth]-y_birth[m_int>=m_birth]
  age[m_birth>900] <- y_int[m_birth>900]-y_birth[m_birth>900]
  
  #It's emphasized the individues that has missing
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_int==miss[i])] <- miss[i]
  }
  mis <- rep(0,length(y_birth))
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  
  age[mis!=0] <- mis[mis!=0]
  
  age

}

CHARLS_w2_age$age_c <- comp_age(y_birth=CHARLS_w2_age$year_of_birth , m_birth=CHARLS_w2_age$month_of_birth ,
         y_int=CHARLS_w2_age$iyear , m_int=CHARLS_w2_age$imonth , miss=c(999))





CHARLS_ds_w2 <- tibble(id=CHARLS_w2_age$id)
CHARLS_ds_w2$age <- car::recode(CHARLS_w2_age$age_c, "NA=999")
CHARLS_ds_w2$age <- labelled(CHARLS_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```




#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(CHARLS_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(16,102)
```

#### Validation
```{r crosstabulation2, echo=F}
CHARLS_w2_age$proff <- CHARLS_w2_age$age_c - CHARLS_w2_age$ba004
CHARLS_w2_age$proff[CHARLS_w2_age$age_c==999] <- NA
CHARLS_w2_age$proff[CHARLS_w2_age$ba004==999] <- NA

kable(CHARLS_w2_age[which(!is.na(CHARLS_w2_age$proff) & CHARLS_w2_age$proff!=0),],align = 'c',caption = 'There are 27 individuals that have discrepancies between the computed age and the reported age. We consider to believe in the computed age.')



```





# Quality estimation
NO comments.


```{r save, echo=FALSE}
age <- CHARLS_ds_w1
save(age, file = "../RData/w1/age.RData")
rm(age)

age <- CHARLS_ds_w2
save(age, file = "../RData/w2/age.RData")
rm(age)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
