---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```

<!-- ########################################################## --> 

# Data process





```{r assign, echo=FALSE}

# WAVE 1 assignation

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

opal.assign.table.tibble(o, 'CHARLS_w1_sex2','CHARLS.demographic_background_wave1',variables=list('rgender'), missings = TRUE)
CHARLS_w1_sex2 <- opal.execute(o,'CHARLS_w1_sex2')

CHARLS_w1_sex2$oldid <- CHARLS_w1_sex2$id
CHARLS_w1_sex2$id <- CHARLS_ids(ids = CHARLS_w1_sex2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), rgender=as.numeric(new_2[,2]))
  new_22
}

# Variable rgender (wave 1) across wave 1 id's

CHARLS_w1_sex <- Add_indiv(old = CHARLS_w1_sex2, new = CHARLS_w1_id)




# WAVE 2 assignation



opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], rgender=as.numeric(new_2[,2]))
  new_22
}

# Variable rgender (wave 1) across wave 2 id's

CHARLS_w1_sex22 <- Add_indiv(old = CHARLS_w1_sex2, new = CHARLS_w2_id)


opal.assign.table.tibble(o, 'CHARLS_w2_sex2','CHARLS.Demographic_Background_wave2', variables=list('ba000_w2_3'), missings = TRUE)
CHARLS_w2_sex2 <- opal.execute(o,'CHARLS_w2_sex2')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], ba000_w2_3=as.numeric(new_2[,2]))
  new_22
}

# Variable ba000_w2_3 (wave 2) across wave 2 id's

CHARLS_w2_sex <- Add_indiv(old = CHARLS_w2_sex2, new = CHARLS_w2_id)

# Variable rgender (wave 1) across wave 2 id's

CHARLS_w2_sex$rgender_w1 <- CHARLS_w1_sex22$rgender


CHARLS_w1_sex <- left_join(CHARLS_w1_sex,CHARLS_w2_sex[,c("id","ba000_w2_3")], by="id")

```


## CHARLS: China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variable description



| **Name** |`rgender`|`ba000_w2_3`|
|-|-|-|
| **Label** |`Gender`|`Gender`|
| **Table name** |`demographic_background_wave1`|`Demographic_Background_wave2`|
| **Categories** |`1 = Male`<br/>`2 = Female`|`1 = Male`<br/>`2 = Female`|
| **Description** |  |  |



```{r local1, echo=FALSE}

vari <- CHARLS_w1_sex$rgender
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "rgender") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_sex, aes(x=factor(rgender))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w1_sex$ba000_w2_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ba000_w2_3") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1_sex, aes(x=factor(ba000_w2_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

CHARLS_w1_sex$proff <- CHARLS_w1_sex$ba000_w2_3 - CHARLS_w1_sex$rgender

# There are 118 individuals having discrepancies of sex between in wave 1 and 2.
mistakes_ind <- CHARLS_w1_sex[which(CHARLS_w1_sex$proff!=0 & !is.na(CHARLS_w1_sex$proff) & CHARLS_w1_sex$rgender!=0),] 

kable(mistakes_ind,align = 'c',caption = 'There are 117 individuals that has discrepancies between sex in wave 1 and 2')

```

#### Harmonisation algorithm
To compute the harmonised variable from the study-specific variable it has to be recoded as follows:

* `2 Female into 0`
* `keep Male into 1`

There is a value 0 in the study-specific variable that we are taking as missing (999).
The 118 individuals with discrepancies between wave 1 and 2 are going to be computed as in wave 2 and when we will have wave 3 we will decide. 


**R script:**

```{r harmo1, echo=TRUE}

CHARLS_ds_w1 <- tibble(id=CHARLS_w1_sex$id)
CHARLS_ds_w1$sex <- car::recode(CHARLS_w1_sex$rgender, "2=0; 0=999; NA=999")
CHARLS_ds_w1$sex[which(!is.na(CHARLS_w1_sex$ba000_w2_3))] <- car::recode(CHARLS_w1_sex$ba000_w2_3[which(!is.na(CHARLS_w1_sex$ba000_w2_3))], "2=0")

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}

vari <- CHARLS_ds_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=FALSE}


```



### Wave 2 

#### Study-specific variable description


| **Name** |`rgender`|`ba000_w2_3`|
|-|-|-|
| **Label** |`Gender`|`Gender`|
| **Table name** |`demographic_background_wave1`|`Demographic_Background_wave2`|
| **Categories** |`1 = Male`<br/>`2 = Female`|`1 = Male`<br/>`2 = Female`|
| **Description** |  |  |




```{r local2, echo=FALSE}


vari <- CHARLS_w2_sex$rgender_w1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "rgender") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_sex, aes(x=factor(rgender_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- CHARLS_w2_sex$ba000_w2_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ba000_w2_3") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2_sex, aes(x=factor(ba000_w2_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonised variable from the study-specific variable from wave 2 it has to be recoded as follows:

* `2 Female into 0`
* `keep Male into 1`

The missing values in the study-specific variable from wave 2 are going to be completed with the study-specific variable from wave 1 if it is possible.

**R script:**

```{r harmo2, echo=TRUE}

CHARLS_w2_sex$sex <- CHARLS_w2_sex$ba000_w2_3
CHARLS_w2_sex$sex[is.na(CHARLS_w2_sex$sex)] <- CHARLS_w2_sex$rgender_w1[is.na(CHARLS_w2_sex$sex)]

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_sex$id)
CHARLS_ds_w2$sex <- car::recode(CHARLS_w2_sex$sex, "2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation

```{r crosstabulation2, echo=FALSE}
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


charls.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(charls.cw, function(wname) if(exists(paste0("CHARLS_ds_",wname[1]))){wname = list(get(paste0("CHARLS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation
No comments.




```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
