---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
source("M:\\WPs\\WP1\\Maelstrom\\data_process\\Rmds\\CHARLS\\1_Sociodemo_econom\\CHARLS_ids.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process
## China (All counties with the exception of Tibet)
### Wave 1 

#### Study-specific variable description

 

* Name: `be001`
* Label: `Marital status`
* Categories: 
    + `1 = Married with spouse present`
    + `2 = Married but not living with spouse temporarily for reasons such as work`
    + `3 = Separated`
    + `4 = Divorced`
    + `5 = Widowed`
    + `6 = Never married`

* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_ms2','CHARLS.demographic_background_wave1',
                         variables=list('be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1,  echo=FALSE}
CHARLS_w1_ms2 <- opal.execute(o,'CHARLS_w1_ms2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
CHARLS_w1_ms2$oldid <- CHARLS_w1_ms2$id
CHARLS_w1_ms2$id <- CHARLS_ids(ids = CHARLS_w1_ms2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), be001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_ms <- Add_indiv(old = CHARLS_w1_ms2, new = CHARLS_w1_id)
vari <- CHARLS_w1_ms$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_ms$be001, missing_values = NA)
ggplot(CHARLS_w1_ms, aes(x=factor(be001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married with spouse present" into 2`
* `keep "Married but not living with spouse temporarily for reasons such as work" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`


**R script:**

```{r harmo1,   echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_ms$id)
CHARLS_ds_w1$marital_status <- car::recode(CHARLS_w1_ms$be001, " 1=2; 4=3; 5=4; 6=1; NA=999")
CHARLS_ds_w1$marital_status <- labelled(CHARLS_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- CHARLS_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(CHARLS_w1_ms$be001)
BeforeH <- c( BeforeH[6], sum(BeforeH[c(1,2)]), sum(BeforeH[c(3,4)]), BeforeH[5], sum(is.na(CHARLS_w1_ms$be001))) 
AfterH <- table(CHARLS_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "NA->999")
kable(C)

```

 
 

 

### Wave 2 

#### Study-specific variable description

 

* Name: `be001`
* Label: `Marital status`
* Categories: 
    + `1 = Married with spouse present`
    + `2 = Married but not living with spouse temporarily for reasons such as work`
    + `3 = Separated`
    + `4 = Divorced`
    + `5 = Widowed`
    + `6 = Never married`
    + `7 = Cohabitated`

* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_ms2','CHARLS.Demographic_Background_wave2',
                         variables=list('be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2,  echo=FALSE}
CHARLS_w2_ms2 <- opal.execute(o,'CHARLS_w2_ms2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], be001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_ms <- Add_indiv(old = CHARLS_w2_ms2, new = CHARLS_w2_id)
vari <- CHARLS_w2_ms$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_ms$be001, missing_values = NA)
ggplot(CHARLS_w2_ms, aes(x=factor(be001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married with spouse present" into 2`
* `keep "Married but not living with spouse temporarily for reasons such as work" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode 7 "Cohabitated" into 2`
* `recode NA into 999`


**R script:**

```{r harmo2,   echo=TRUE}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_ms$id)
CHARLS_ds_w2$marital_status <- car::recode(CHARLS_w2_ms$be001, " 1=2; 4=3; 5=4; 6=1;7=2; NA=999")
CHARLS_ds_w2$marital_status <- labelled(CHARLS_ds_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- CHARLS_ds_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(CHARLS_w2_ms$be001)
BeforeH <- c( BeforeH[6], sum(BeforeH[c(1,2,7)]), sum(BeforeH[c(3,4)]), BeforeH[5], sum(is.na(CHARLS_w2_ms$be001))) 
AfterH <- table(CHARLS_ds_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2,7)->2", "(3,4)->3", "5->4", "NA->999")
kable(C)
```

```{r save, echo=FALSE}
marital_status <- CHARLS_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)

marital_status <- CHARLS_ds_w2
save(marital_status, file = "../RData/w2/marital_status.RData")
rm(marital_status)
```
 


# Quality estimation

The label '2=married but not living with spouse temporarily for reasons such as work' was considered as 'married-cohabitating' in the harmonized variable.It happens in both waves. 


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```