---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
source("M:\\WPs\\WP1\\Maelstrom\\data_process\\Rmds\\CHARLS\\1_Sociodemo_econom\\CHARLS_ids.R")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## China (All counties with the exception of Tibet)


### Wave 1 

#### Study-specific variable description

 

* Name: `bd001`
* Label: `Highest Level of Education Attained`
* Categories: 
    + `1 = No formal education illiterate`
    + `2 = Did not finish primary school but capable of reading or writing`
    + `3 = Sishu`
    + `4 = Elementary school`
    + `5 = Middle school`
    + `6 = High school`
    + `7 = Vocational school`
    + `8 = Two/Three Year College / Associate degree`
    + `9 = Four Year College / Bachelors degree`
    + `10 = Post-graduate, Masters degree`
    + `11 = Post-graduate, Ph.D.`
* Description:
```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w1_educ2','CHARLS.demographic_background_wave1',
                         variables=list('bd001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=FALSE}
CHARLS_w1_educ2 <- opal.execute(o,'CHARLS_w1_educ2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_educ2$oldid <- CHARLS_w1_educ2$id
CHARLS_w1_educ2$id <- CHARLS_ids(ids = CHARLS_w1_educ2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), bd001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w1_educ <- Add_indiv(old = CHARLS_w1_educ2, new = CHARLS_w1_id)
vari <- CHARLS_w1_educ$bd001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_educ$bd001, missing_values = NA)
ggplot(CHARLS_w1_educ, aes(x=factor(bd001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education illiterate" into 0`
* `recode 2 "Did not finish primary school but capable of reading or writing" into 0`
* `recode 3 "Sishu" into 0`
* `recode 4 "Elementary school" into 1`
* `recode 5 "Middle school" into 2`
* `recode 6 "High school" into 2`
* `recode 7 "Vocational school" into 2`
* `recode 8 "Two/Three Year College / Associate degree" into 3`
* `recode 9 "Four Year College / Bachelors degree" into 3`
* `recode 10 "Post-graduate, Masters degree" into 3`
* `recode 11 "Post-graduate, Ph.D." into 3`
* `recode NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_educ$id)
CHARLS_ds_w1$education <- car::recode(CHARLS_w1_educ$bd001, "1=0; 2=0; 3=0; 4=1; 5=2; 6=2; 7=2; 8=3; 9=3; 10=3; 11=3; NA=999")
CHARLS_ds_w1$education <- labelled(CHARLS_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(CHARLS_w1_educ$bd001)
BeforeH <- c(sum(BeforeH[1:3]), BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:10]), sum(is.na(CHARLS_w1_educ$bd001)))
AfterH <- table(CHARLS_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2,3)->0", "4->1", "(5,6,7)->2", "(8,9,10,11)->3", "NA->999")
kable(C)
```






### Wave 2 

#### Study-specific variable description

 

* Name: `bd001`
* Label: `The Highest level of Education Attained Now`
* Categories: 
    + `1 = No formal education illiterate`
    + `2 = Did not finish primary school but capable of reading or writing`
    + `3 = Sishu`
    + `4 = Elementary school`
    + `5 = Middle school`
    + `6 = High school`
    + `7 = Vocational school`
    + `8 = Two/Three Year College / Associate degree`
    + `9 = Four Year College / Bachelors degree`
    + `10 = Post-graduate, Masters degree`
    + `11 = Post-graduate, Ph.D.`
* Description:
```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_w2_educ2','CHARLS.Demographic_Background_wave2',
                         variables=list('bd001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=FALSE}
CHARLS_w2_educ2 <- opal.execute(o,'CHARLS_w2_educ2')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], bd001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_educ <- Add_indiv(old = CHARLS_w2_educ2, new = CHARLS_w2_id)

vari <- CHARLS_w2_educ$bd001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_educ$bd001, missing_values = NA)
ggplot(CHARLS_w2_educ, aes(x=factor(bd001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No formal education illiterate" into 0`
* `recode 2 "Did not finish primary school but capable of reading or writing" into 0`
* `recode 3 "Sishu" into 0`
* `recode 4 "Elementary school" into 1`
* `recode 5 "Middle school" into 2`
* `recode 6 "High school" into 2`
* `recode 7 "Vocational school" into 2`
* `recode 8 "Two/Three Year College / Associate degree" into 3`
* `recode 9 "Four Year College / Bachelors degree" into 3`
* `recode 10 "Post-graduate, Masters degree" into 3`
* `recode 11 "Post-graduate, Ph.D." into 3`
* `recode NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_educ$id)
CHARLS_ds_w2$education <- car::recode(CHARLS_w2_educ$bd001, "1=0; 2=0; 3=0; 4=1; 5=2; 6=2; 7=2; 8=3; 9=3; 10=3; 11=3; NA=999")
CHARLS_ds_w2$education <- labelled(CHARLS_ds_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(CHARLS_w2_educ$bd001)
BeforeH <- c(sum(BeforeH[1:3]), BeforeH[4],sum(BeforeH[5:7]), sum(BeforeH[8:11]), sum(is.na(CHARLS_w2_educ$bd001)))
AfterH <- table(CHARLS_ds_w2$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1,2,3)->0", "4->1", "(5,6,7)->2", "(8,9,10,11)->3", "NA->999")
kable(C)
```



# Quality estimation

'3=sishu' label was considered as 0=less than primary education after talking with Prof. Yaohui Zhao (CHARLS study contact) about its correspondence. 


```{r save, echo=FALSE}
education <- CHARLS_ds_w1
save(education, file = "../RData/w1/education.RData")
rm(education)

education <- CHARLS_ds_w2
save(education, file = "../RData/w2/education.RData")
rm(education)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```