---
title: "Living alone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `living_alone`
* Variable label: `Participant is currently living alone`
* Variable description: `Participant is currently living alone`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## CHARLS

### Wave 1 

#### Study-specific variable description

| **Name** |`be001`|`be002`|`db025_4_`|`db025_9_`|`db025_32_`|`db025_37_`|`db025_2_`|`db025_7_`|`db025_11_`|`db025_35_`|`db025_8_`|`db025_12_`|`db025_31_`|`db025_36_`|`db025_5_`|`db025_33_`|`db025_1_`|`db025_6_`|`db025_10_`|`db025_34_`|`db025_39_`|
|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Marital Status`| `Are You Unmarried but Living with a Partner`|`Is Mother-in-law Living In Your Home`|`Is Children Living In Your Home`|`Is Sibling of Spouse Living In Your Home`|`Is Paid Helper Living In Your Home`|`Is Mother Living In Your Home`|`Is Children Living In Your Home`|`Is Children Living In Your Home`|`Is Grandchild Living In Your Home`|`Is Children Living In Your Home`|`Is Children Living In Your Home`|`Is Sibling Living In Your Home`|`Is Other Relative Living In Your Home`|`Is Father-in-law Living In Your Home`|`Is Brother-in-law,Sister in law Living In Your Home`|`Is Spouse Living In Your Home`|`Is Children Living In Your Home`|`Is Children Living In Your Home`|`Is Children's Spouse Living In Your Home`|`Is Other Living In Your Home`|
| **Table name** |`demographic_background_wave1`|`demographic_background_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|
| **Categories** |`1 = Married with spouse present; 2 = Married but not living with spouse temporarily for reasons such as work; 3 = Separated; 4 = Divorced; 5 = Widowed; 6 = Never married`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|
| **Description** |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_la1','CHARLS.demographic_background_wave1',
                         variables=list('be002', 'be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_la2','CHARLS.health_status_and_functioning_wave1',
                         variables=list('db025_4_', 'db025_9_', 'db025_32_', 'db025_37_', 'db025_2_', 'db025_7_', 'db025_11_', 'db025_35_', 'db025_8_', 'db025_12_', 'db025_31_', 'db025_36_', 'db025_5_', 'db025_33_', 'db025_1_', 'db025_6_', 'db025_10_', 'db025_34_', 'db025_39_'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1, echo=F}
CHARLS_w1_la1 <- opal.execute(o,'CHARLS_w1_la1')
CHARLS_w1_la2 <- opal.execute(o,'CHARLS_w1_la2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_la2$oldid <- CHARLS_w1_la2$id
CHARLS_w1_la2$id <- CHARLS_ids(ids = CHARLS_w1_la2$oldid)


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,20))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,21]), db025_4_=as.numeric(new_2[,2]), db025_9_=as.numeric(new_2[,3]), db025_32_=as.numeric(new_2[,4]), 
db025_37_=as.numeric(new_2[,5]), db025_2_=as.numeric(new_2[,6]), db025_7_=as.numeric(new_2[,7]), db025_11_=as.numeric(new_2[,8]), db025_35_=as.numeric(new_2[,9]), db025_8_=as.numeric(new_2[,10]), db025_12_=as.numeric(new_2[,11]), db025_31_=as.numeric(new_2[,12]), db025_36_=as.numeric(new_2[,13]), db025_5_=as.numeric(new_2[,14]), db025_33_=as.numeric(new_2[,15]), db025_1_=as.numeric(new_2[,16]), db025_6_=as.numeric(new_2[,17]), db025_10_=as.numeric(new_2[,18]), db025_34_=as.numeric(new_2[,19]), db025_39_=as.numeric(new_2[,20]))
  new_22
}


CHARLS_w1_la <- Add_indiv(old = CHARLS_w1_la2, new = CHARLS_w1_id)

CHARLS_w1_la1$be001 <- car::recode(CHARLS_w1_la1$be001, "NA=999")
CHARLS_w1_la1$be002 <- car::recode(CHARLS_w1_la1$be002, "NA=999")
CHARLS_w1_la1$be001_002 <- CHARLS_w1_la1$be001
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001==2] <- 1
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001==3] <- CHARLS_w1_la1$be002[CHARLS_w1_la1$be001==3]
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001==4] <- CHARLS_w1_la1$be002[CHARLS_w1_la1$be001==4]
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001==5] <- CHARLS_w1_la1$be002[CHARLS_w1_la1$be001==5]
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001==6] <- CHARLS_w1_la1$be002[CHARLS_w1_la1$be001==6]
CHARLS_w1_la1$be001_002[CHARLS_w1_la1$be001_002==999] <- NA


CHARLS_w1_la1$oldid <- CHARLS_w1_la1$id
CHARLS_w1_la1$id <- CHARLS_ids(ids = CHARLS_w1_la1$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA, NA, NA, NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,5]), be001_002=as.numeric(new_2[,4]))
  new_22
}

CHARLS_w1_la11 <- Add_indiv(old = CHARLS_w1_la1, new = CHARLS_w1_id)

CHARLS_w1_la$be001_002 <- CHARLS_w1_la11$be001_002

vari <- CHARLS_w1_la$be001_002
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'be001_002') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$be001_002, missing_values = NA)
vari <- CHARLS_w1_la$db025_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_4_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_4_, missing_values = NA)
vari <- CHARLS_w1_la$db025_9_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_9_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_9_, missing_values = NA)
vari <- CHARLS_w1_la$db025_32_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_32_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_32_, missing_values = NA)
vari <- CHARLS_w1_la$db025_37_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_37_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_37_, missing_values = NA)
vari <- CHARLS_w1_la$db025_7_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_7_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_7_, missing_values = NA)
vari <- CHARLS_w1_la$db025_35_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_35_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_35_, missing_values = NA)
vari <- CHARLS_w1_la$db025_12_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_12_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_12_, missing_values = NA)
vari <- CHARLS_w1_la$db025_36_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_36_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_36_, missing_values = NA)
vari <- CHARLS_w1_la$db025_33_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_33_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_33_, missing_values = NA)
vari <- CHARLS_w1_la$db025_6_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_6_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_6_, missing_values = NA)
vari <- CHARLS_w1_la$db025_34_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_34_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_34_, missing_values = NA)
vari <- CHARLS_w1_la$db025_2_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_2_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_2_, missing_values = NA)
vari <- CHARLS_w1_la$db025_11_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_11_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_11_, missing_values = NA)
vari <- CHARLS_w1_la$db025_8_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_8_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_8_, missing_values = NA)
vari <- CHARLS_w1_la$db025_31_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_31_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_31_, missing_values = NA)
vari <- CHARLS_w1_la$db025_5_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_5_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_5_, missing_values = NA)
vari <- CHARLS_w1_la$db025_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_1_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_1_, missing_values = NA)
vari <- CHARLS_w1_la$db025_10_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_10_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_10_, missing_values = NA)
vari <- CHARLS_w1_la$db025_39_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_39_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_la$db025_39_, missing_values = NA)
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variables are to be sum and recoded as follows: 

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

It has to be emphasized that there are a high proportion of NA in the study-specific variables. In order to solve it, it was decided that the missing in the variables means that the question is not applicable for the individual.

It has to take into account that to compute 'be001_002' the category "Married but not living with spouse temporarily for reasons such as work" is considered as the participant is living with his/her spouse.


**R script:**

```{r harmo1}
CHARLS_w1_la$be001_002 <- car::recode(CHARLS_w1_la$be001_002, "2=0")
CHARLS_w1_la$db025_4_ <- car::recode(CHARLS_w1_la$db025_4_, "2=0")
CHARLS_w1_la$db025_9_ <- car::recode(CHARLS_w1_la$db025_9_, "2=0")
CHARLS_w1_la$db025_32_ <- car::recode(CHARLS_w1_la$db025_32_, "2=0")
CHARLS_w1_la$db025_37_ <- car::recode(CHARLS_w1_la$db025_37_, "2=0")
CHARLS_w1_la$db025_7_ <- car::recode(CHARLS_w1_la$db025_7_, "2=0")
CHARLS_w1_la$db025_35_ <- car::recode(CHARLS_w1_la$db025_35_, "2=0")
CHARLS_w1_la$db025_12_ <- car::recode(CHARLS_w1_la$db025_12_, "2=0")
CHARLS_w1_la$db025_36_ <- car::recode(CHARLS_w1_la$db025_36_, "2=0")
CHARLS_w1_la$db025_33_ <- car::recode(CHARLS_w1_la$db025_33_, "2=0")
CHARLS_w1_la$db025_6_ <- car::recode(CHARLS_w1_la$db025_6_, "2=0")
CHARLS_w1_la$db025_34_ <- car::recode(CHARLS_w1_la$db025_34_, "2=0")
CHARLS_w1_la$db025_2_ <- car::recode(CHARLS_w1_la$db025_2_, "2=0")
CHARLS_w1_la$db025_11_ <- car::recode(CHARLS_w1_la$db025_11_, "2=0")
CHARLS_w1_la$db025_8_ <- car::recode(CHARLS_w1_la$db025_8_, "2=0")
CHARLS_w1_la$db025_31_ <- car::recode(CHARLS_w1_la$db025_31_, "2=0")
CHARLS_w1_la$db025_5_ <- car::recode(CHARLS_w1_la$db025_5_, "2=0")
CHARLS_w1_la$db025_1_ <- car::recode(CHARLS_w1_la$db025_1_, "2=0")
CHARLS_w1_la$db025_10_ <- car::recode(CHARLS_w1_la$db025_10_, "2=0")
CHARLS_w1_la$db025_39_ <- car::recode(CHARLS_w1_la$db025_39_, "2=0")

CHARLS_w1_la$sums <- apply(CHARLS_w1_la[,-c(1,2)], MARGIN = 1, FUN = function(x) sum(na.omit(x)) )
CHARLS_w1_la$Nas <- apply(CHARLS_w1_la[,-c(1,2)], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

CHARLS_w1_la$sums[which(CHARLS_w1_la$Nas==20)] <- 999


CHARLS_ds_w1 <- tibble(id=CHARLS_w1_la$id)
CHARLS_ds_w1$living_alone <- car::recode(CHARLS_w1_la$sums, "1:900=0;0=1; NA=999")
CHARLS_ds_w1$living_alone <- labelled(CHARLS_ds_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(CHARLS_w1_la$sums)
BeforeH <- c(sum(BeforeH[2:4]), BeforeH[1], BeforeH[5])
AfterH <- table(CHARLS_ds_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">1->0","0->1", "999")
kable(C)
```




### Wave 2 

#### Study-specific variable description

| **Name** |`be001`|`db025_X_, X=1, 2, 3, 4, 5, 6, 7, 8, 9, 11, 26, 27, 28, 29, 30, 31, 32, 33, 36, 51`|`cm002_w2_1_X_, X=1, 2, 3, 4, 5, 6, 7 ,8 ,9, 10`|
|-|-|-|-|
| **Label** |`Marital Status`|`Helper living at Home`|`Is Other Living In Your Home`|
| **Table name** |`Demographic_Background_wave2`|`Health_Status_and_Functioning_wave2`|`Family_Information_wave2`|
| **Categories** |`1 = Married with spouse present; 2 = Married but not living with spouse temporarily for reasons such as work; 3 = Separated; 4 = Divorced; 5 = Widowed; 6 = Never married; 7 = Cohabitated`|`1 = Yes; 2 = No`|`1 = Yes; 2 = No`|
| **Description** |  |  |  |


    


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_la1','CHARLS.Demographic_Background_wave2',
                         variables=list('be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_la2','CHARLS.Family_Information_wave2',
                         variables=list('cm002_w2_1_4_', 'cm002_w2_1_9_', 'cm002_w2_1_1_', 'cm002_w2_1_6_', 'cm002_w2_1_10_', 'cm002_w2_1_3_', 'cm002_w2_1_8_', 'cm002_w2_1_2_', 'cm002_w2_1_7_', 'cm002_w2_1_5_'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_la3','CHARLS.Health_Status_and_Functioning_wave2',
                         variables=list('db025_1_', 'db025_6_', 'db025_32_', 'db025_51_', 'db025_3_', 'db025_8_', 'db025_11_', 'db025_28_', 'db025_30_', 'db025_2_', 'db025_7_', 'db025_29_', 'db025_31_', 'db025_36_', 'db025_5_', 'db025_26_', 'db025_33_', 'db025_4_', 'db025_9_', 'db025_27_'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2, echo=F}
CHARLS_w2_la1 <- opal.execute(o,'CHARLS_w2_la1')
CHARLS_w2_la2 <- opal.execute(o,'CHARLS_w2_la2')
CHARLS_w2_la3 <- opal.execute(o,'CHARLS_w2_la3')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')


Add_indiv <- function(old, new){
   new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], be001=as.numeric(new_2[,2]))
  new_22
}

CHARLS_w2_la11 <- Add_indiv(old = CHARLS_w2_la1, new = CHARLS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,10))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], cm002_w2_1_4_=as.numeric(new_2[,2]), cm002_w2_1_9_=as.numeric(new_2[,3]), cm002_w2_1_1_=as.numeric(new_2[,4]), 
cm002_w2_1_6_=as.numeric(new_2[,5]), cm002_w2_1_10_=as.numeric(new_2[,6]), cm002_w2_1_3_=as.numeric(new_2[,7]), cm002_w2_1_8_=as.numeric(new_2[,8]), cm002_w2_1_2_=as.numeric(new_2[,9]), cm002_w2_1_7_=as.numeric(new_2[,10]), cm002_w2_1_5_=as.numeric(new_2[,11]))
  new_22
}


CHARLS_w2_la22 <- Add_indiv(old = CHARLS_w2_la2, new = CHARLS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,20))
    }
  }
 
new_22 <- data.frame(id=new_2[,1], db025_1_=as.numeric(new_2[,2]), db025_6_=as.numeric(new_2[,3]), db025_32_=as.numeric(new_2[,4]), 
db025_51_=as.numeric(new_2[,5]), db025_3_=as.numeric(new_2[,6]), db025_8_=as.numeric(new_2[,7]), db025_11_=as.numeric(new_2[,8]), db025_28_=as.numeric(new_2[,9]), db025_30_=as.numeric(new_2[,10]), db025_2_=as.numeric(new_2[,11]), db025_7_=as.numeric(new_2[,12]), db025_29_=as.numeric(new_2[,13]), db025_31_=as.numeric(new_2[,14]), db025_36_=as.numeric(new_2[,15]), db025_5_=as.numeric(new_2[,16]), db025_26_=as.numeric(new_2[,17]), db025_33_=as.numeric(new_2[,18]), db025_4_=as.numeric(new_2[,19]), db025_9_=as.numeric(new_2[,20]), db025_27_=as.numeric(new_2[,20]))
  new_22
}
CHARLS_w2_la33 <- Add_indiv(old = CHARLS_w2_la3, new = CHARLS_w2_id)


CHARLS_w2_la <- cbind(CHARLS_w2_la11, cm002_w2_1_4_=CHARLS_w2_la22$cm002_w2_1_4_, cm002_w2_1_9_=CHARLS_w2_la22$cm002_w2_1_9_, cm002_w2_1_1_=CHARLS_w2_la22$cm002_w2_1_1_, cm002_w2_1_6_=CHARLS_w2_la22$cm002_w2_1_6_, cm002_w2_1_10_=CHARLS_w2_la22$cm002_w2_1_10_, cm002_w2_1_3_=CHARLS_w2_la22$cm002_w2_1_3_, cm002_w2_1_8_=CHARLS_w2_la22$cm002_w2_1_8_, cm002_w2_1_2_=CHARLS_w2_la22$cm002_w2_1_2_, cm002_w2_1_7_=CHARLS_w2_la22$cm002_w2_1_7_, cm002_w2_1_5_=CHARLS_w2_la22$cm002_w2_1_5_,   db025_1_=CHARLS_w2_la33$db025_1_, db025_6_=CHARLS_w2_la33$db025_6_, db025_32_=CHARLS_w2_la33$db025_32_, db025_51_=CHARLS_w2_la33$db025_51_, db025_3_=CHARLS_w2_la33$db025_3_, db025_8_=CHARLS_w2_la33$db025_8_, db025_11_=CHARLS_w2_la33$db025_11_, db025_28_=CHARLS_w2_la33$db025_28_, db025_30_=CHARLS_w2_la33$db025_30_, db025_2_=CHARLS_w2_la33$db025_2_, db025_7_=CHARLS_w2_la33$db025_7_, db025_29_=CHARLS_w2_la33$db025_29_, db025_31_=CHARLS_w2_la33$db025_31_, db025_36_=CHARLS_w2_la33$db025_36_, db025_5_=CHARLS_w2_la33$db025_5_, db025_26_=CHARLS_w2_la33$db025_26_, db025_33_=CHARLS_w2_la33$db025_33_, db025_4_=CHARLS_w2_la33$db025_4_, db025_9_=CHARLS_w2_la33$db025_9_, db025_27_=CHARLS_w2_la33$db025_27_)

vari <- CHARLS_w2_la$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'be001') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$be001, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_4_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_4_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_9_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_9_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_9_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_1_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_1_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_3_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_3_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_3_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_7_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_7_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_7_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_6_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_6_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_6_, missing_values = NA)
vari <- CHARLS_w2_la$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'be001') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_8_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_5_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_5_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_5_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_10_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_10_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_10_, missing_values = NA)
vari <- CHARLS_w2_la$cm002_w2_1_2_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'cm002_w2_1_2_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$cm002_w2_1_2_, missing_values = NA)
vari <- CHARLS_w2_la$db025_51_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_51_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_51_, missing_values = NA)
vari <- CHARLS_w2_la$db025_28_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_28_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_28_, missing_values = NA)
vari <- CHARLS_w2_la$db025_29_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_29_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_29_, missing_values = NA)
vari <- CHARLS_w2_la$db025_26_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_26_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_26_, missing_values = NA)
vari <- CHARLS_w2_la$db025_27_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_27_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_27_, missing_values = NA)
vari <- CHARLS_w2_la$db025_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_1_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_1_, missing_values = NA)
vari <- CHARLS_w2_la$db025_3_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_3_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_3_, missing_values = NA)
vari <- CHARLS_w2_la$db025_30_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_30_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_30_, missing_values = NA)
vari <- CHARLS_w2_la$db025_31_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_31_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_31_, missing_values = NA)
vari <- CHARLS_w2_la$db025_33_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_33_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_33_, missing_values = NA)
vari <- CHARLS_w2_la$db025_6_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_6_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_6_, missing_values = NA)
vari <- CHARLS_w2_la$db025_8_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_8_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_8_, missing_values = NA)
vari <- CHARLS_w2_la$db025_2_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_2_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_2_, missing_values = NA)
vari <- CHARLS_w2_la$db025_36_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_36_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_36_, missing_values = NA)
vari <- CHARLS_w2_la$db025_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_4_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_4_, missing_values = NA)
vari <- CHARLS_w2_la$db025_32_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_32_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_32_, missing_values = NA)
vari <- CHARLS_w2_la$db025_11_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_11_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_11_, missing_values = NA)
vari <- CHARLS_w2_la$db025_7_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_7_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_7_, missing_values = NA)
vari <- CHARLS_w2_la$db025_5_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_5_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_5_, missing_values = NA)
vari <- CHARLS_w2_la$db025_9_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'db025_9_') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_la$db025_9_, missing_values = NA)
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables are to be sum and recoded as follows: 

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

It has to be emphasized that there are a high proportion of NA in the study-specific variables. In order to solve it, it was decided that the missing in the variables means that the question is not applicable for the individual.

It has to take into account that to compute 'be001' the category "Married but not living with spouse temporarily for reasons such as work" is considered as the participant is living with his/her spouse.

**R script:**

```{r harmo2}
CHARLS_w2_la$be001 <- car::recode(CHARLS_w2_la$be001, "c(2, 7)=1; c(3, 4, 5, 6)=0")
CHARLS_w2_la <- car::recode(CHARLS_w2_la, "2=0")

CHARLS_w2_la$sums <- apply(CHARLS_w2_la[,-1], MARGIN = 1, FUN = function(x) sum(na.omit(x)) )

CHARLS_w2_la$Nas <- apply(CHARLS_w2_la[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)) )


CHARLS_ds_w2 <- tibble(id=CHARLS_w2_la$id)
CHARLS_ds_w2$living_alone <- car::recode(CHARLS_w2_la$sums, "1:900=0;0=1; NA=999")
CHARLS_ds_w2$living_alone <- labelled(CHARLS_ds_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(CHARLS_w2_la$sums, useNA = "ifany")
BeforeH <- c(sum(BeforeH[2:14]), BeforeH[1])
AfterH <- table(CHARLS_ds_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">1->0","0->1")
kable(C)
```



# Quality estimation
This variable, as it appears in CHARLS, does not math the original variable definition
(not leaving with family/helper does not mean that the respondent leaves alone).


```{r save, echo=FALSE}
living_alone <- CHARLS_ds_w1
save(living_alone, file = "../RData/w1/living_alone.RData")
rm(living_alone)

living_alone <- CHARLS_ds_w2
save(living_alone, file = "../RData/w2/living_alone.RData")
rm(living_alone)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
