---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
source("../../CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```


# Data process


## China


### Wave 1


#### Study-specific variable description

| **Name** | `fa002` |
|-|-|
| **Label** | `Work for at Least One Hour Last Week`|
| **Table name**  | `work_retirement_and_pension_wave1`| 
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_2','CHARLS.work_retirement_and_pension_wave1',variables=list('fa002'), missings = T)
CHARLS_w1_2 <- opal.execute(o,'CHARLS_w1_2')
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

# adding a zero to the old id's in CHARLS_w1 with CHARLS_ids
CHARLS_w1_2$oldid <- CHARLS_w1_2$id
CHARLS_w1_2$id <- CHARLS_ids(ids = CHARLS_w1_2$oldid)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA,NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,3]), fa002=as.numeric(new_2[,2]))
  new_22
}
CHARLS_w1 <- Add_indiv(old = CHARLS_w1_2, new = CHARLS_w1_id)

```

```{r local w1, echo=F}

vbl <- CHARLS_w1$fa002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w1, aes(x=factor(fa002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
CHARLS_ds_w1 <- tibble(id=CHARLS_w1$id)
CHARLS_ds_w1$employed <- car::recode(CHARLS_w1$fa002,"2=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- CHARLS_ds_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(CHARLS_ds_w1$employed, useNA = "ifany")
BeforeH <- table(CHARLS_w1$fa002, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `fa002` |
|-|-|
| **Label** | `Work for at Least One Hour Last Month`|
| **Table name**  | `Work_Retirement_and_Pension_wave2`|
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_2','CHARLS.Work_Retirement_and_Pension_wave2',variables=list('fa002'), missings = T)
CHARLS_w2_2 <- opal.execute(o,'CHARLS_w2_2')
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

Add_indiv <- function(old, new){

  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)

  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }

  new_22 <- data.frame(id=new_2[,1], fa002=as.numeric(new_2[,2]))
  new_22
}
CHARLS_w2 <- Add_indiv(old = CHARLS_w2_2, new = CHARLS_w2_id)

```

```{r local w2, echo=F}

vbl <- CHARLS_w2$fa002
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(CHARLS_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_w2, aes(x=factor(fa002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`


**R script:**

```{r harmo w2}

CHARLS_ds_w2 <- tibble(id=CHARLS_w2$id)
CHARLS_ds_w2$employed <- car::recode(CHARLS_w2$fa002,"2=0;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- CHARLS_ds_w2$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(CHARLS_ds_w2$employed, useNA = "ifany")
BeforeH <- table(CHARLS_w2$fa002, useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
CHARLS_ds_w1$employed <- labelled(CHARLS_ds_w1$employed, labels = cat_label)
label(CHARLS_ds_w1$employed) <- ds_label
CHARLS_ds_w2$employed <- labelled(CHARLS_ds_w2$employed, labels = cat_label)
label(CHARLS_ds_w2$employed) <- ds_label


CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$employed <- car::recode(CHARLS_m_ds_w1$employed, "miss_values_vector=NA")
CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$employed <- car::recode(CHARLS_m_ds_w2$employed, "miss_values_vector=NA")


tt <-    frq(CHARLS_ds_w1$employed)[[1]][,c(1:2,4)]
tt[4] <- frq(CHARLS_ds_w2$employed)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(CHARLS_ds_w1$employed), length(CHARLS_ds_w2$employed)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(CHARLS_m_ds_w1[,c("id","employed")], CHARLS_m_ds_w2[,c("id","employed")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.CHARLS <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(index in seq_along(l.CHARLS)){
  employed <- l.CHARLS[[index]]
  save(employed, file = paste0(datafolder,names(l.CHARLS)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





