---
title: "Stroke or myocardial infarction (heart attack)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd_hard`
* Variable label: `History of stroke or myocardial infarction (heart attack)`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: stroke or myocardial infarction or heart attack`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no, the participant has not been diagnosed by stroke or myocardial infarction or heart attack
1        | yes, no, the participant has been diagnosed by stroke or myocardial infarction or heart attack

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of stroke or myocardial infarction (heart attack)"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## India


### Wave 1


#### Study-specific variable description



| **Name** |`stroke`|`mi_ha`|
|-|-|-|
| **Label** |`Stroke`|`Myocardial infarction or heart attack`|
| **Table name**  |`stroke`|`mi_ha`|
| **Categories** | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|`0 = No`<br/>`1 = Yes`|
| **Missings** | `999 = Missing` | `999 = Missing` |
| **Description** |  |  |

```{r assign w1, echo=F}

load(paste0(datafolder,"w1/mi_ha.RData"))
LASI_w1 <- tibble(id=mi_ha$id)
LASI_w1$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w1/stroke.RData"))
LASI_w1$stroke <- stroke$stroke
rm(stroke)

```

```{r local w1, echo=F}

vbl <- LASI_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(LASI_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_hard` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$cvd_hard <- rep(999,length(LASI_ds_w1$id))
LASI_ds_w1$cvd_hard[which(LASI_w1$mi_ha == 0 & LASI_w1$stroke == 0)] <- 0
LASI_ds_w1$cvd_hard[which(LASI_w1$mi_ha == 1 | LASI_w1$stroke == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- LASI_ds_w1$cvd_hard
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(cvd_hard))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(LASI_ds_w1$cvd_hard)
X <- c(
  sum(LASI_w1$mi_ha == 0 & LASI_w1$stroke == 0,na.rm=T),
  sum(LASI_w1$mi_ha == 1 | LASI_w1$stroke == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(LASI_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","otherwise->999")
kable(C)

```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
LASI_ds_w1$cvd_hard <- labelled(LASI_ds_w1$cvd_hard, labels = cat_label)
label(LASI_ds_w1$cvd_hard) <- ds_label

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$cvd_hard <- car::recode(LASI_m_ds_w1$cvd_hard, "miss_values_vector=NA")

tt <- frq(LASI_ds_w1$cvd_hard)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(LASI_ds_w1$cvd_hard)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation

It contains information about myocardial infarction and stroke. It has been built from the harmonized single disease variables.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.LASI <- list(w1 = LASI_ds_w1)

for(index in seq_along(l.LASI)){
  cvd_hard <- l.LASI[[index]]
  save(cvd_hard, file = paste0(datafolder,names(l.LASI)[index],"/cvd_hard.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





