---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## India


### Wave 1


#### Study-specific variable description



| **Name** | `ht006` |`ht007`|`ht008_age`|
|-|-|-|-|
| **Label** | `any health professional told you that you have diabetes`|`who diagnosed you with diabetes`|`when first diagnosed with diabetes age`|
| **Table name**  | `LASI-Pilot_all`| `LASI-Pilot_all`|`LASI-Pilot_all`|
| **Categories** | `1 = yes`<br/>`2 = no` |`1 = a doctor mbbs degree`<br/>`2 = ayurvedic, unani, or homeopathic doctor; rmp; siddha`<br/>`3 = other, please specify:`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all',variables=list('ht006','ht007','ht008_age'), missings = T)
LASI_w1 <- opal.execute(o,'LASI_w1')

```

```{r local w1, echo=F}

vbl <- LASI_w1$ht006
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht007
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- LASI_w1$ht008_age
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(LASI_w1)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(LASI_w1, aes(ht008_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(5,80)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `ht006 == 2 or (ht006 == 1 and ht007 == 2 or 3) into 0`
* `ht006 == 1 and ht007 == 1 into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = ht008_age`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$h_diabetes <- rep(999,length(LASI_ds_w1$id))
LASI_ds_w1$h_diabetes[which(LASI_w1$ht006 == 2 | (LASI_w1$ht006 == 1 & LASI_w1$ht007 %in% c(2,3)))] <- 0
LASI_ds_w1$h_diabetes[which(LASI_w1$ht006 == 1 & LASI_w1$ht007 == 1)] <- 1

# Continuous variable harmonization
diabetes_age <- car::recode(LASI_w1$ht008_age[LASI_ds_w1$h_diabetes==1],"NA=999")
LASI_ds_w1$h_diabetes_age <- car::recode(LASI_ds_w1$h_diabetes, "0=996; 1=diabetes_age")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- LASI_ds_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- LASI_ds_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(LASI_ds_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,80)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(LASI_ds_w1$h_diabetes)
X <- c(
  sum(LASI_w1$ht006 == 2 | (LASI_w1$ht006 == 1 & LASI_w1$ht007 %in% c(2,3)),na.rm=T),
  sum(LASI_w1$ht006 == 1 & LASI_w1$ht007 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(LASI_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("ht006=0 or ht007=2,3->0","1->1","otherwise->999")
kable(C)

```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
LASI_ds_w1$h_diabetes <- labelled(LASI_ds_w1$h_diabetes, labels = cat_label)
label(LASI_ds_w1$h_diabetes) <- ds_label
LASI_ds_w1$h_diabetes_age <- labelled(LASI_ds_w1$h_diabetes_age, labels = cont_label)
label(LASI_ds_w1$h_diabetes_age) <- ds_label_age

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$h_diabetes <- car::recode(LASI_m_ds_w1$h_diabetes, "miss_values_vector=NA")

tt <- frq(LASI_ds_w1$h_diabetes)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(LASI_ds_w1$h_diabetes)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation

We codified as 1(yes) if the option "a doctor mbbs degree" was chosen. 

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.LASI <- list(w1 = LASI_ds_w1)

for(index in seq_along(l.LASI)){
  h_diabetes <- l.LASI[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.LASI)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





