---
title: "Myocardial infarction or heart attack"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mi_ha`
* Variable label: `Myocardial infarction or heart attack`
* Variable description: `Myocardial infarction or heart attack since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Myocardial infarction or heart attack"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## India


### Wave 1


#### Study-specific variable description



| **Name** | `ht028` |
|-|-|
| **Label** | `heart attack or myocardial infarction`|
| **Table name**  | `LASI-Pilot_all`|
| **Categories** | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all',variables=list('ht028'), missings = T)
LASI_w1 <- opal.execute(o,'LASI_w1')

```

```{r local w1, echo=F}

vbl <- LASI_w1$ht028
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(ht028))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `ht028 == 2 into 0`
* `ht028 == 1 into 1`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$mi_ha <- car::recode(LASI_w1$ht028,"NA=999;2=0")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- LASI_ds_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(LASI_ds_w1$mi_ha)
BeforeH <- table(LASI_w1$ht028,useNA = "ifany")[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","otherwise->999")
kable(C)

```






## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
LASI_ds_w1$mi_ha <- labelled(LASI_ds_w1$mi_ha, labels = cat_label)
label(LASI_ds_w1$mi_ha) <- ds_label

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$mi_ha <- car::recode(LASI_m_ds_w1$mi_ha, "miss_values_vector=NA")

tt <- frq(LASI_ds_w1$mi_ha)[[1]][,c(1:2,4)]
tt[13,] <- c("n", "sample size", 
             length(LASI_ds_w1$mi_ha)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)

```



# Quality estimation

The question is about 'the last two years'.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.LASI <- list(w1 = LASI_ds_w1)

for(index in seq_along(l.LASI)){
  mi_ha <- l.LASI[[index]]
  save(mi_ha, file = paste0(datafolder,names(l.LASI)[index],"/mi_ha.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





