---
title: "Triglycerides"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/triglyceridesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/triglyceridesDS.R')
```


# Data process


## Ireland


### Wave 1

#### Study-specific variable description

| **Name** | `Bloods_TRIG` |
|-|-|
| **Label** |  |
| **Table name** | `TILDA-AMF-v16` |
| **Categories:**| `continuous` |
| **Missings:**| `Missing`<br/>`No Consent`<br/>`Insufficient Sample`<br/>`NA` |
| **Description** |  | 

   

```{r assign w1, echo=F }

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('Bloods_TRIG'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```


```{r prep}

TILDA_w1$Bloods_TRIG[which(TILDA_w1$Bloods_TRIG == "Missing")] <- "999"
TILDA_w1$Bloods_TRIG[which(TILDA_w1$Bloods_TRIG == "No Consent")] <- "997"
TILDA_w1$Bloods_TRIG[which(TILDA_w1$Bloods_TRIG == "Insufficient Sample")] <- "993"
TILDA_w1$Bloods_TRIG <- as.numeric(TILDA_w1$Bloods_TRIG)

```

```{r local w1, echo=F}

vbl <- TILDA_w1$Bloods_TRIG
vbl_miss <- miss_values_vector
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "Bloods_TRIG") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(TILDA_w1,!vbl %in% vbl_miss), aes(Bloods_TRIG)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `triglycerides` from the study-specific variable it has to be recoded as follows:

* ` multiply mmol/L by 88.57`
* `Missing into 999`
* `No Consent into 997`
* `Insufficient Sample into 993`

**R script:**

```{r harmo w1}

TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$triglycerides <- car::recode(TILDA_w1$Bloods_TRIG, "NA = 999")
TILDA_ds_w1$triglycerides[which(!TILDA_ds_w1$triglycerides %in% miss_values_vector)] <- 88.57*TILDA_ds_w1$triglycerides[which(!TILDA_ds_w1$triglycerides %in% miss_values_vector)]

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$triglycerides
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(TILDA_ds_w1,!vbl %in% miss_values_vector), aes(triglycerides)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}
```




### Wave 2

Not found


<!--## Summary of descriptive statistics of the harmonised variable accross populations and waves-->



```{r summ, echo=F}

l.hds <- list(w1 = TILDA_ds_w1)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("TILDA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("TILDA_m_ds_",name))
  rm(aux_object)
}

# t.summ <- summary(m.hds[[1]][2])[1:6]
# t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
# for (i in seq_along(l.hds)){
#   t.summ <- summary(m.hds[[i]][2])[1:6]
#   t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
# }
# t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
# 
# dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
# kable(t.hds)

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  triglycerides <- l.hds[[index]]
  save(triglycerides, file = paste0(datafolder,names(l.hds)[index],"/triglycerides.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```


