---
title: "Mobility - Pulling or pushing large objects"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

```{r lab, echo=FALSE}
ds_label <- "Difficulty for pulling or pushing large objects"
```


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_pull`
* Variable label: `Difficulty for pulling or pushing large objects`
* Variable description: `Difficulty for pulling or pushing large objects`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process


## HRS

### Wave 1

#### Study-specific variable description




| **Name** | `R1PUSHW`|
|-|-|
| **Label** | ` Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w1, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w1_mob_pull','HRS.HRS-HRS-w1', variables=list('R1PUSHW'), missings = TRUE)
```


```{r local HRS w1, echo=F}
HRS_HRS_w1_mob_pull <- opal.execute(o,'HRS_HRS_w1_mob_pull')
vari <- HRS_HRS_w1_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w1_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w1_mob_pull, aes(x=factor(R1PUSHW))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w1}
HRS_HRS_ds_w1 <- tibble(id=HRS_HRS_w1_mob_pull$id)
HRS_HRS_ds_w1$mob_pull <- car::recode(HRS_HRS_w1_mob_pull$R1PUSHW, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w1$mob_pull <- labelled(HRS_HRS_ds_w1$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w1, echo=F}
vari <- HRS_HRS_ds_w1$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w1, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w1, echo=F}
AfterH <- table(HRS_HRS_ds_w1$mob_pull)
X<-table(HRS_HRS_w1_mob_pull$R1PUSHW)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w1_mob_pull$R1PUSHW)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```





### Wave 2

#### Study-specific variable description




| **Name** | `R2PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w2, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w2_mob_pull','HRS.HRS-HRS-w2', variables=list('R2PUSHA'), missings = TRUE)
```


```{r local HRS w2, echo=F}
HRS_HRS_w2_mob_pull <- opal.execute(o,'HRS_HRS_w2_mob_pull')
vari <- HRS_HRS_w2_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w2_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w2_mob_pull, aes(x=factor(R2PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w2}
HRS_HRS_ds_w2 <- tibble(id=HRS_HRS_w2_mob_pull$id)
HRS_HRS_ds_w2$mob_pull <- car::recode(HRS_HRS_w2_mob_pull$R2PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w2$mob_pull <- labelled(HRS_HRS_ds_w2$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w2, echo=F}
vari <- HRS_HRS_ds_w2$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w2, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w2, echo=F}
AfterH <- table(HRS_HRS_ds_w2$mob_pull)
X<-table(HRS_HRS_w2_mob_pull$R2PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w2_mob_pull$R2PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 3

#### Study-specific variable description




| **Name** | `R3PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w3, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w3_mob_pull','HRS.HRS-HRS-w3', variables=list('R3PUSHA'), missings = TRUE)
```


```{r local HRS w3, echo=F}
HRS_HRS_w3_mob_pull <- opal.execute(o,'HRS_HRS_w3_mob_pull')
vari <- HRS_HRS_w3_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w3_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w3_mob_pull, aes(x=factor(R3PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w3}
HRS_HRS_ds_w3 <- tibble(id=HRS_HRS_w3_mob_pull$id)
HRS_HRS_ds_w3$mob_pull <- car::recode(HRS_HRS_w3_mob_pull$R3PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w3$mob_pull <- labelled(HRS_HRS_ds_w3$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w3, echo=F}
vari <- HRS_HRS_ds_w3$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w3, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w3, echo=F}
AfterH <- table(HRS_HRS_ds_w3$mob_pull)
X<-table(HRS_HRS_w3_mob_pull$R3PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w3_mob_pull$R3PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 4

#### Study-specific variable description




| **Name** | `R4PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w4, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w4_mob_pull','HRS.HRS-HRS-w4', variables=list('R4PUSHA'), missings = TRUE)
```


```{r local HRS w4, echo=F}
HRS_HRS_w4_mob_pull <- opal.execute(o,'HRS_HRS_w4_mob_pull')
vari <- HRS_HRS_w4_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w4_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w4_mob_pull, aes(x=factor(R4PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w4}
HRS_HRS_ds_w4 <- tibble(id=HRS_HRS_w4_mob_pull$id)
HRS_HRS_ds_w4$mob_pull <- car::recode(HRS_HRS_w4_mob_pull$R4PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w4$mob_pull <- labelled(HRS_HRS_ds_w4$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w4, echo=F}
vari <- HRS_HRS_ds_w4$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w4, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w4, echo=F}
AfterH <- table(HRS_HRS_ds_w4$mob_pull)
X<-table(HRS_HRS_w4_mob_pull$R4PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w4_mob_pull$R4PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 5

#### Study-specific variable description




| **Name** | `R5PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w5, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w5_mob_pull','HRS.HRS-HRS-w5', variables=list('R5PUSHA'), missings = TRUE)
```


```{r local HRS w5, echo=F}
HRS_HRS_w5_mob_pull <- opal.execute(o,'HRS_HRS_w5_mob_pull')
vari <- HRS_HRS_w5_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w5_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w5_mob_pull, aes(x=factor(R5PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w5}
HRS_HRS_ds_w5 <- tibble(id=HRS_HRS_w5_mob_pull$id)
HRS_HRS_ds_w5$mob_pull <- car::recode(HRS_HRS_w5_mob_pull$R5PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w5$mob_pull <- labelled(HRS_HRS_ds_w5$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w5, echo=F}
vari <- HRS_HRS_ds_w5$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w5, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w5, echo=F}
AfterH <- table(HRS_HRS_ds_w5$mob_pull)
X<-table(HRS_HRS_w5_mob_pull$R5PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w5_mob_pull$R5PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 6

#### Study-specific variable description




| **Name** | `R6PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w6, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w6_mob_pull','HRS.HRS-HRS-w6', variables=list('R6PUSHA'), missings = TRUE)
```


```{r local HRS w6, echo=F}
HRS_HRS_w6_mob_pull <- opal.execute(o,'HRS_HRS_w6_mob_pull')
vari <- HRS_HRS_w6_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w6_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w6_mob_pull, aes(x=factor(R6PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w6}
HRS_HRS_ds_w6 <- tibble(id=HRS_HRS_w6_mob_pull$id)
HRS_HRS_ds_w6$mob_pull <- car::recode(HRS_HRS_w6_mob_pull$R6PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w6$mob_pull <- labelled(HRS_HRS_ds_w6$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w6, echo=F}
vari <- HRS_HRS_ds_w6$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w6, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w6, echo=F}
AfterH <- table(HRS_HRS_ds_w6$mob_pull)
X<-table(HRS_HRS_w6_mob_pull$R6PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w6_mob_pull$R6PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 7

#### Study-specific variable description




| **Name** | `R7PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w7, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w7_mob_pull','HRS.HRS-HRS-w7', variables=list('R7PUSHA'), missings = TRUE)
```


```{r local HRS w7, echo=F}
HRS_HRS_w7_mob_pull <- opal.execute(o,'HRS_HRS_w7_mob_pull')
vari <- HRS_HRS_w7_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w7_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w7_mob_pull, aes(x=factor(R7PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w7}
HRS_HRS_ds_w7 <- tibble(id=HRS_HRS_w7_mob_pull$id)
HRS_HRS_ds_w7$mob_pull <- car::recode(HRS_HRS_w7_mob_pull$R7PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w7$mob_pull <- labelled(HRS_HRS_ds_w7$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w7, echo=F}
vari <- HRS_HRS_ds_w7$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w7, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w7, echo=F}
AfterH <- table(HRS_HRS_ds_w7$mob_pull)
X<-table(HRS_HRS_w7_mob_pull$R7PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w7_mob_pull$R7PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 8

#### Study-specific variable description




| **Name** | `R8PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w8, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w8_mob_pull','HRS.HRS-HRS-w8', variables=list('R8PUSHA'), missings = TRUE)
```


```{r local HRS w8, echo=F}
HRS_HRS_w8_mob_pull <- opal.execute(o,'HRS_HRS_w8_mob_pull')
vari <- HRS_HRS_w8_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w8_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w8_mob_pull, aes(x=factor(R8PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w8}
HRS_HRS_ds_w8 <- tibble(id=HRS_HRS_w8_mob_pull$id)
HRS_HRS_ds_w8$mob_pull <- car::recode(HRS_HRS_w8_mob_pull$R8PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w8$mob_pull <- labelled(HRS_HRS_ds_w8$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w8, echo=F}
vari <- HRS_HRS_ds_w8$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w8, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w8, echo=F}
AfterH <- table(HRS_HRS_ds_w8$mob_pull)
X<-table(HRS_HRS_w8_mob_pull$R8PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w8_mob_pull$R8PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 9

#### Study-specific variable description




| **Name** | `R9PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w9, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w9_mob_pull','HRS.HRS-HRS-w9', variables=list('R9PUSHA'), missings = TRUE)
```


```{r local HRS w9, echo=F}
HRS_HRS_w9_mob_pull <- opal.execute(o,'HRS_HRS_w9_mob_pull')
vari <- HRS_HRS_w9_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w9_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w9_mob_pull, aes(x=factor(R9PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w9}
HRS_HRS_ds_w9 <- tibble(id=HRS_HRS_w9_mob_pull$id)
HRS_HRS_ds_w9$mob_pull <- car::recode(HRS_HRS_w9_mob_pull$R9PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w9$mob_pull <- labelled(HRS_HRS_ds_w9$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w9, echo=F}
vari <- HRS_HRS_ds_w9$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w9, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w9, echo=F}
AfterH <- table(HRS_HRS_ds_w9$mob_pull)
X<-table(HRS_HRS_w9_mob_pull$R9PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w9_mob_pull$R9PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w10, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w10_mob_pull','HRS.HRS-HRS-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local HRS w10, echo=F}
HRS_HRS_w10_mob_pull <- opal.execute(o,'HRS_HRS_w10_mob_pull')
vari <- HRS_HRS_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w10}
HRS_HRS_ds_w10 <- tibble(id=HRS_HRS_w10_mob_pull$id)
HRS_HRS_ds_w10$mob_pull <- car::recode(HRS_HRS_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w10$mob_pull <- labelled(HRS_HRS_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w10, echo=F}
vari <- HRS_HRS_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w10, echo=F}
AfterH <- table(HRS_HRS_ds_w10$mob_pull)
X<-table(HRS_HRS_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign HRS w11, echo=F}
opal.assign.table.tibble(o, 'HRS_HRS_w11_mob_pull','HRS.HRS-HRS-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local HRS w11, echo=F}
HRS_HRS_w11_mob_pull <- opal.execute(o,'HRS_HRS_w11_mob_pull')
vari <- HRS_HRS_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_HRS_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo HRS w11}
HRS_HRS_ds_w11 <- tibble(id=HRS_HRS_w11_mob_pull$id)
HRS_HRS_ds_w11$mob_pull <- car::recode(HRS_HRS_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_HRS_ds_w11$mob_pull <- labelled(HRS_HRS_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w11, echo=F}
vari <- HRS_HRS_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w11, echo=F}
AfterH <- table(HRS_HRS_ds_w11$mob_pull)
X<-table(HRS_HRS_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






## AHEAD

### Wave 2

#### Study-specific variable description




| **Name** | `R2PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w2, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w2_mob_pull','HRS.HRS-AHEAD-w2', variables=list('R2PUSHA'), missings = TRUE)
```


```{r local AHEAD w2, echo=F}
HRS_AHEAD_w2_mob_pull <- opal.execute(o,'HRS_AHEAD_w2_mob_pull')
vari <- HRS_AHEAD_w2_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w2_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w2_mob_pull, aes(x=factor(R2PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w2}
HRS_AHEAD_ds_w2 <- tibble(id=HRS_AHEAD_w2_mob_pull$id)
HRS_AHEAD_ds_w2$mob_pull <- car::recode(HRS_AHEAD_w2_mob_pull$R2PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w2$mob_pull <- labelled(HRS_AHEAD_ds_w2$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w2, echo=F}
vari <- HRS_AHEAD_ds_w2$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w2, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w2, echo=F}
AfterH <- table(HRS_AHEAD_ds_w2$mob_pull)
X<-table(HRS_AHEAD_w2_mob_pull$R2PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w2_mob_pull$R2PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 3

#### Study-specific variable description




| **Name** | `R3PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w3, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w3_mob_pull','HRS.HRS-AHEAD-w3', variables=list('R3PUSHA'), missings = TRUE)
```


```{r local AHEAD w3, echo=F}
HRS_AHEAD_w3_mob_pull <- opal.execute(o,'HRS_AHEAD_w3_mob_pull')
vari <- HRS_AHEAD_w3_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w3_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w3_mob_pull, aes(x=factor(R3PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w3}
HRS_AHEAD_ds_w3 <- tibble(id=HRS_AHEAD_w3_mob_pull$id)
HRS_AHEAD_ds_w3$mob_pull <- car::recode(HRS_AHEAD_w3_mob_pull$R3PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w3$mob_pull <- labelled(HRS_AHEAD_ds_w3$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w3, echo=F}
vari <- HRS_AHEAD_ds_w3$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w3, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w3, echo=F}
AfterH <- table(HRS_AHEAD_ds_w3$mob_pull)
X<-table(HRS_AHEAD_w3_mob_pull$R3PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w3_mob_pull$R3PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 4

#### Study-specific variable description




| **Name** | `R4PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w4, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w4_mob_pull','HRS.HRS-AHEAD-w4', variables=list('R4PUSHA'), missings = TRUE)
```


```{r local AHEAD w4, echo=F}
HRS_AHEAD_w4_mob_pull <- opal.execute(o,'HRS_AHEAD_w4_mob_pull')
vari <- HRS_AHEAD_w4_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w4_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w4_mob_pull, aes(x=factor(R4PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w4}
HRS_AHEAD_ds_w4 <- tibble(id=HRS_AHEAD_w4_mob_pull$id)
HRS_AHEAD_ds_w4$mob_pull <- car::recode(HRS_AHEAD_w4_mob_pull$R4PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w4$mob_pull <- labelled(HRS_AHEAD_ds_w4$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w4, echo=F}
vari <- HRS_AHEAD_ds_w4$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w4, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w4, echo=F}
AfterH <- table(HRS_AHEAD_ds_w4$mob_pull)
X<-table(HRS_AHEAD_w4_mob_pull$R4PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w4_mob_pull$R4PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 5

#### Study-specific variable description




| **Name** | `R5PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w5, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w5_mob_pull','HRS.HRS-AHEAD-w5', variables=list('R5PUSHA'), missings = TRUE)
```


```{r local AHEAD w5, echo=F}
HRS_AHEAD_w5_mob_pull <- opal.execute(o,'HRS_AHEAD_w5_mob_pull')
vari <- HRS_AHEAD_w5_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w5_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w5_mob_pull, aes(x=factor(R5PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w5}
HRS_AHEAD_ds_w5 <- tibble(id=HRS_AHEAD_w5_mob_pull$id)
HRS_AHEAD_ds_w5$mob_pull <- car::recode(HRS_AHEAD_w5_mob_pull$R5PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w5$mob_pull <- labelled(HRS_AHEAD_ds_w5$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w5, echo=F}
vari <- HRS_AHEAD_ds_w5$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w5, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w5, echo=F}
AfterH <- table(HRS_AHEAD_ds_w5$mob_pull)
X<-table(HRS_AHEAD_w5_mob_pull$R5PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w5_mob_pull$R5PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 6

#### Study-specific variable description




| **Name** | `R6PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w6, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w6_mob_pull','HRS.HRS-AHEAD-w6', variables=list('R6PUSHA'), missings = TRUE)
```


```{r local AHEAD w6, echo=F}
HRS_AHEAD_w6_mob_pull <- opal.execute(o,'HRS_AHEAD_w6_mob_pull')
vari <- HRS_AHEAD_w6_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w6_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w6_mob_pull, aes(x=factor(R6PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w6}
HRS_AHEAD_ds_w6 <- tibble(id=HRS_AHEAD_w6_mob_pull$id)
HRS_AHEAD_ds_w6$mob_pull <- car::recode(HRS_AHEAD_w6_mob_pull$R6PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w6$mob_pull <- labelled(HRS_AHEAD_ds_w6$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w6, echo=F}
vari <- HRS_AHEAD_ds_w6$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w6, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w6, echo=F}
AfterH <- table(HRS_AHEAD_ds_w6$mob_pull)
X<-table(HRS_AHEAD_w6_mob_pull$R6PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w6_mob_pull$R6PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 7

#### Study-specific variable description




| **Name** | `R7PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w7, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w7_mob_pull','HRS.HRS-AHEAD-w7', variables=list('R7PUSHA'), missings = TRUE)
```


```{r local AHEAD w7, echo=F}
HRS_AHEAD_w7_mob_pull <- opal.execute(o,'HRS_AHEAD_w7_mob_pull')
vari <- HRS_AHEAD_w7_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w7_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w7_mob_pull, aes(x=factor(R7PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w7}
HRS_AHEAD_ds_w7 <- tibble(id=HRS_AHEAD_w7_mob_pull$id)
HRS_AHEAD_ds_w7$mob_pull <- car::recode(HRS_AHEAD_w7_mob_pull$R7PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w7$mob_pull <- labelled(HRS_AHEAD_ds_w7$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w7, echo=F}
vari <- HRS_AHEAD_ds_w7$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w7, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w7, echo=F}
AfterH <- table(HRS_AHEAD_ds_w7$mob_pull)
X<-table(HRS_AHEAD_w7_mob_pull$R7PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w7_mob_pull$R7PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 8

#### Study-specific variable description




| **Name** | `R8PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w8, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w8_mob_pull','HRS.HRS-AHEAD-w8', variables=list('R8PUSHA'), missings = TRUE)
```


```{r local AHEAD w8, echo=F}
HRS_AHEAD_w8_mob_pull <- opal.execute(o,'HRS_AHEAD_w8_mob_pull')
vari <- HRS_AHEAD_w8_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w8_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w8_mob_pull, aes(x=factor(R8PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w8}
HRS_AHEAD_ds_w8 <- tibble(id=HRS_AHEAD_w8_mob_pull$id)
HRS_AHEAD_ds_w8$mob_pull <- car::recode(HRS_AHEAD_w8_mob_pull$R8PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w8$mob_pull <- labelled(HRS_AHEAD_ds_w8$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w8, echo=F}
vari <- HRS_AHEAD_ds_w8$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w8, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w8, echo=F}
AfterH <- table(HRS_AHEAD_ds_w8$mob_pull)
X<-table(HRS_AHEAD_w8_mob_pull$R8PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w8_mob_pull$R8PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 9

#### Study-specific variable description




| **Name** | `R9PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w9, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w9_mob_pull','HRS.HRS-AHEAD-w9', variables=list('R9PUSHA'), missings = TRUE)
```


```{r local AHEAD w9, echo=F}
HRS_AHEAD_w9_mob_pull <- opal.execute(o,'HRS_AHEAD_w9_mob_pull')
vari <- HRS_AHEAD_w9_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w9_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w9_mob_pull, aes(x=factor(R9PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w9}
HRS_AHEAD_ds_w9 <- tibble(id=HRS_AHEAD_w9_mob_pull$id)
HRS_AHEAD_ds_w9$mob_pull <- car::recode(HRS_AHEAD_w9_mob_pull$R9PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w9$mob_pull <- labelled(HRS_AHEAD_ds_w9$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w9, echo=F}
vari <- HRS_AHEAD_ds_w9$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w9, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w9, echo=F}
AfterH <- table(HRS_AHEAD_ds_w9$mob_pull)
X<-table(HRS_AHEAD_w9_mob_pull$R9PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w9_mob_pull$R9PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w10, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w10_mob_pull','HRS.HRS-AHEAD-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local AHEAD w10, echo=F}
HRS_AHEAD_w10_mob_pull <- opal.execute(o,'HRS_AHEAD_w10_mob_pull')
vari <- HRS_AHEAD_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w10}
HRS_AHEAD_ds_w10 <- tibble(id=HRS_AHEAD_w10_mob_pull$id)
HRS_AHEAD_ds_w10$mob_pull <- car::recode(HRS_AHEAD_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w10$mob_pull <- labelled(HRS_AHEAD_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w10, echo=F}
vari <- HRS_AHEAD_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w10, echo=F}
AfterH <- table(HRS_AHEAD_ds_w10$mob_pull)
X<-table(HRS_AHEAD_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign AHEAD w11, echo=F}
opal.assign.table.tibble(o, 'HRS_AHEAD_w11_mob_pull','HRS.HRS-AHEAD-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local AHEAD w11, echo=F}
HRS_AHEAD_w11_mob_pull <- opal.execute(o,'HRS_AHEAD_w11_mob_pull')
vari <- HRS_AHEAD_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_AHEAD_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo AHEAD w11}
HRS_AHEAD_ds_w11 <- tibble(id=HRS_AHEAD_w11_mob_pull$id)
HRS_AHEAD_ds_w11$mob_pull <- car::recode(HRS_AHEAD_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_AHEAD_ds_w11$mob_pull <- labelled(HRS_AHEAD_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w11, echo=F}
vari <- HRS_AHEAD_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w11, echo=F}
AfterH <- table(HRS_AHEAD_ds_w11$mob_pull)
X<-table(HRS_AHEAD_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







## CODA

### Wave 4

#### Study-specific variable description




| **Name** | `R4PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w4, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w4_mob_pull','HRS.HRS-CODA-w4', variables=list('R4PUSHA'), missings = TRUE)
```


```{r local CODA w4, echo=F}
HRS_CODA_w4_mob_pull <- opal.execute(o,'HRS_CODA_w4_mob_pull')
vari <- HRS_CODA_w4_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w4_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w4_mob_pull, aes(x=factor(R4PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w4}
HRS_CODA_ds_w4 <- tibble(id=HRS_CODA_w4_mob_pull$id)
HRS_CODA_ds_w4$mob_pull <- car::recode(HRS_CODA_w4_mob_pull$R4PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w4$mob_pull <- labelled(HRS_CODA_ds_w4$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w4, echo=F}
vari <- HRS_CODA_ds_w4$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w4, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w4, echo=F}
AfterH <- table(HRS_CODA_ds_w4$mob_pull)
X<-table(HRS_CODA_w4_mob_pull$R4PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w4_mob_pull$R4PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 5

#### Study-specific variable description




| **Name** | `R5PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w5, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w5_mob_pull','HRS.HRS-CODA-w5', variables=list('R5PUSHA'), missings = TRUE)
```


```{r local CODA w5, echo=F}
HRS_CODA_w5_mob_pull <- opal.execute(o,'HRS_CODA_w5_mob_pull')
vari <- HRS_CODA_w5_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w5_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w5_mob_pull, aes(x=factor(R5PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w5}
HRS_CODA_ds_w5 <- tibble(id=HRS_CODA_w5_mob_pull$id)
HRS_CODA_ds_w5$mob_pull <- car::recode(HRS_CODA_w5_mob_pull$R5PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w5$mob_pull <- labelled(HRS_CODA_ds_w5$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w5, echo=F}
vari <- HRS_CODA_ds_w5$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w5, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w5, echo=F}
AfterH <- table(HRS_CODA_ds_w5$mob_pull)
X<-table(HRS_CODA_w5_mob_pull$R5PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w5_mob_pull$R5PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 6

#### Study-specific variable description




| **Name** | `R6PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w6, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w6_mob_pull','HRS.HRS-CODA-w6', variables=list('R6PUSHA'), missings = TRUE)
```


```{r local CODA w6, echo=F}
HRS_CODA_w6_mob_pull <- opal.execute(o,'HRS_CODA_w6_mob_pull')
vari <- HRS_CODA_w6_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w6_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w6_mob_pull, aes(x=factor(R6PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w6}
HRS_CODA_ds_w6 <- tibble(id=HRS_CODA_w6_mob_pull$id)
HRS_CODA_ds_w6$mob_pull <- car::recode(HRS_CODA_w6_mob_pull$R6PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w6$mob_pull <- labelled(HRS_CODA_ds_w6$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w6, echo=F}
vari <- HRS_CODA_ds_w6$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w6, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w6, echo=F}
AfterH <- table(HRS_CODA_ds_w6$mob_pull)
X<-table(HRS_CODA_w6_mob_pull$R6PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w6_mob_pull$R6PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 7

#### Study-specific variable description




| **Name** | `R7PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w7, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w7_mob_pull','HRS.HRS-CODA-w7', variables=list('R7PUSHA'), missings = TRUE)
```


```{r local CODA w7, echo=F}
HRS_CODA_w7_mob_pull <- opal.execute(o,'HRS_CODA_w7_mob_pull')
vari <- HRS_CODA_w7_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w7_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w7_mob_pull, aes(x=factor(R7PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w7}
HRS_CODA_ds_w7 <- tibble(id=HRS_CODA_w7_mob_pull$id)
HRS_CODA_ds_w7$mob_pull <- car::recode(HRS_CODA_w7_mob_pull$R7PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w7$mob_pull <- labelled(HRS_CODA_ds_w7$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w7, echo=F}
vari <- HRS_CODA_ds_w7$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w7, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w7, echo=F}
AfterH <- table(HRS_CODA_ds_w7$mob_pull)
X<-table(HRS_CODA_w7_mob_pull$R7PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w7_mob_pull$R7PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 8

#### Study-specific variable description




| **Name** | `R8PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w8, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w8_mob_pull','HRS.HRS-CODA-w8', variables=list('R8PUSHA'), missings = TRUE)
```


```{r local CODA w8, echo=F}
HRS_CODA_w8_mob_pull <- opal.execute(o,'HRS_CODA_w8_mob_pull')
vari <- HRS_CODA_w8_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w8_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w8_mob_pull, aes(x=factor(R8PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w8}
HRS_CODA_ds_w8 <- tibble(id=HRS_CODA_w8_mob_pull$id)
HRS_CODA_ds_w8$mob_pull <- car::recode(HRS_CODA_w8_mob_pull$R8PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w8$mob_pull <- labelled(HRS_CODA_ds_w8$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w8, echo=F}
vari <- HRS_CODA_ds_w8$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w8, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w8, echo=F}
AfterH <- table(HRS_CODA_ds_w8$mob_pull)
X<-table(HRS_CODA_w8_mob_pull$R8PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w8_mob_pull$R8PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 9

#### Study-specific variable description




| **Name** | `R9PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w9, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w9_mob_pull','HRS.HRS-CODA-w9', variables=list('R9PUSHA'), missings = TRUE)
```


```{r local CODA w9, echo=F}
HRS_CODA_w9_mob_pull <- opal.execute(o,'HRS_CODA_w9_mob_pull')
vari <- HRS_CODA_w9_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w9_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w9_mob_pull, aes(x=factor(R9PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w9}
HRS_CODA_ds_w9 <- tibble(id=HRS_CODA_w9_mob_pull$id)
HRS_CODA_ds_w9$mob_pull <- car::recode(HRS_CODA_w9_mob_pull$R9PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w9$mob_pull <- labelled(HRS_CODA_ds_w9$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w9, echo=F}
vari <- HRS_CODA_ds_w9$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w9, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w9, echo=F}
AfterH <- table(HRS_CODA_ds_w9$mob_pull)
X<-table(HRS_CODA_w9_mob_pull$R9PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w9_mob_pull$R9PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w10, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w10_mob_pull','HRS.HRS-CODA-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local CODA w10, echo=F}
HRS_CODA_w10_mob_pull <- opal.execute(o,'HRS_CODA_w10_mob_pull')
vari <- HRS_CODA_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w10}
HRS_CODA_ds_w10 <- tibble(id=HRS_CODA_w10_mob_pull$id)
HRS_CODA_ds_w10$mob_pull <- car::recode(HRS_CODA_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w10$mob_pull <- labelled(HRS_CODA_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w10, echo=F}
vari <- HRS_CODA_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w10, echo=F}
AfterH <- table(HRS_CODA_ds_w10$mob_pull)
X<-table(HRS_CODA_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign CODA w11, echo=F}
opal.assign.table.tibble(o, 'HRS_CODA_w11_mob_pull','HRS.HRS-CODA-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local CODA w11, echo=F}
HRS_CODA_w11_mob_pull <- opal.execute(o,'HRS_CODA_w11_mob_pull')
vari <- HRS_CODA_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_CODA_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo CODA w11}
HRS_CODA_ds_w11 <- tibble(id=HRS_CODA_w11_mob_pull$id)
HRS_CODA_ds_w11$mob_pull <- car::recode(HRS_CODA_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_CODA_ds_w11$mob_pull <- labelled(HRS_CODA_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w11, echo=F}
vari <- HRS_CODA_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w11, echo=F}
AfterH <- table(HRS_CODA_ds_w11$mob_pull)
X<-table(HRS_CODA_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







## WB

### Wave 4

#### Study-specific variable description




| **Name** | `R4PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w4`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w4, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w4_mob_pull','HRS.HRS-WB-w4', variables=list('R4PUSHA'), missings = TRUE)
```


```{r local WB w4, echo=F}
HRS_WB_w4_mob_pull <- opal.execute(o,'HRS_WB_w4_mob_pull')
vari <- HRS_WB_w4_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w4_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w4_mob_pull, aes(x=factor(R4PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w4}
HRS_WB_ds_w4 <- tibble(id=HRS_WB_w4_mob_pull$id)
HRS_WB_ds_w4$mob_pull <- car::recode(HRS_WB_w4_mob_pull$R4PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w4$mob_pull <- labelled(HRS_WB_ds_w4$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w4, echo=F}
vari <- HRS_WB_ds_w4$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w4, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w4, echo=F}
AfterH <- table(HRS_WB_ds_w4$mob_pull)
X<-table(HRS_WB_w4_mob_pull$R4PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w4_mob_pull$R4PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 5

#### Study-specific variable description




| **Name** | `R5PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w5`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w5, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w5_mob_pull','HRS.HRS-WB-w5', variables=list('R5PUSHA'), missings = TRUE)
```


```{r local WB w5, echo=F}
HRS_WB_w5_mob_pull <- opal.execute(o,'HRS_WB_w5_mob_pull')
vari <- HRS_WB_w5_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w5_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w5_mob_pull, aes(x=factor(R5PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w5}
HRS_WB_ds_w5 <- tibble(id=HRS_WB_w5_mob_pull$id)
HRS_WB_ds_w5$mob_pull <- car::recode(HRS_WB_w5_mob_pull$R5PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w5$mob_pull <- labelled(HRS_WB_ds_w5$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w5, echo=F}
vari <- HRS_WB_ds_w5$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w5, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w5, echo=F}
AfterH <- table(HRS_WB_ds_w5$mob_pull)
X<-table(HRS_WB_w5_mob_pull$R5PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w5_mob_pull$R5PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 6

#### Study-specific variable description




| **Name** | `R6PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w6`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w6, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w6_mob_pull','HRS.HRS-WB-w6', variables=list('R6PUSHA'), missings = TRUE)
```


```{r local WB w6, echo=F}
HRS_WB_w6_mob_pull <- opal.execute(o,'HRS_WB_w6_mob_pull')
vari <- HRS_WB_w6_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w6_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w6_mob_pull, aes(x=factor(R6PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w6}
HRS_WB_ds_w6 <- tibble(id=HRS_WB_w6_mob_pull$id)
HRS_WB_ds_w6$mob_pull <- car::recode(HRS_WB_w6_mob_pull$R6PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w6$mob_pull <- labelled(HRS_WB_ds_w6$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w6, echo=F}
vari <- HRS_WB_ds_w6$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w6, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w6, echo=F}
AfterH <- table(HRS_WB_ds_w6$mob_pull)
X<-table(HRS_WB_w6_mob_pull$R6PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w6_mob_pull$R6PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 7

#### Study-specific variable description




| **Name** | `R7PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w7`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w7, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w7_mob_pull','HRS.HRS-WB-w7', variables=list('R7PUSHA'), missings = TRUE)
```


```{r local WB w7, echo=F}
HRS_WB_w7_mob_pull <- opal.execute(o,'HRS_WB_w7_mob_pull')
vari <- HRS_WB_w7_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w7_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w7_mob_pull, aes(x=factor(R7PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w7}
HRS_WB_ds_w7 <- tibble(id=HRS_WB_w7_mob_pull$id)
HRS_WB_ds_w7$mob_pull <- car::recode(HRS_WB_w7_mob_pull$R7PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w7$mob_pull <- labelled(HRS_WB_ds_w7$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w7, echo=F}
vari <- HRS_WB_ds_w7$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w7, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w7, echo=F}
AfterH <- table(HRS_WB_ds_w7$mob_pull)
X<-table(HRS_WB_w7_mob_pull$R7PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w7_mob_pull$R7PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 8

#### Study-specific variable description




| **Name** | `R8PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w8`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w8, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w8_mob_pull','HRS.HRS-WB-w8', variables=list('R8PUSHA'), missings = TRUE)
```


```{r local WB w8, echo=F}
HRS_WB_w8_mob_pull <- opal.execute(o,'HRS_WB_w8_mob_pull')
vari <- HRS_WB_w8_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w8_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w8_mob_pull, aes(x=factor(R8PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w8}
HRS_WB_ds_w8 <- tibble(id=HRS_WB_w8_mob_pull$id)
HRS_WB_ds_w8$mob_pull <- car::recode(HRS_WB_w8_mob_pull$R8PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w8$mob_pull <- labelled(HRS_WB_ds_w8$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w8, echo=F}
vari <- HRS_WB_ds_w8$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w8, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w8, echo=F}
AfterH <- table(HRS_WB_ds_w8$mob_pull)
X<-table(HRS_WB_w8_mob_pull$R8PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w8_mob_pull$R8PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 9

#### Study-specific variable description




| **Name** | `R9PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w9`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w9, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w9_mob_pull','HRS.HRS-WB-w9', variables=list('R9PUSHA'), missings = TRUE)
```


```{r local WB w9, echo=F}
HRS_WB_w9_mob_pull <- opal.execute(o,'HRS_WB_w9_mob_pull')
vari <- HRS_WB_w9_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w9_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w9_mob_pull, aes(x=factor(R9PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w9}
HRS_WB_ds_w9 <- tibble(id=HRS_WB_w9_mob_pull$id)
HRS_WB_ds_w9$mob_pull <- car::recode(HRS_WB_w9_mob_pull$R9PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w9$mob_pull <- labelled(HRS_WB_ds_w9$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w9, echo=F}
vari <- HRS_WB_ds_w9$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w9, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w9, echo=F}
AfterH <- table(HRS_WB_ds_w9$mob_pull)
X<-table(HRS_WB_w9_mob_pull$R9PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w9_mob_pull$R9PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w10, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w10_mob_pull','HRS.HRS-WB-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local WB w10, echo=F}
HRS_WB_w10_mob_pull <- opal.execute(o,'HRS_WB_w10_mob_pull')
vari <- HRS_WB_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w10}
HRS_WB_ds_w10 <- tibble(id=HRS_WB_w10_mob_pull$id)
HRS_WB_ds_w10$mob_pull <- car::recode(HRS_WB_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w10$mob_pull <- labelled(HRS_WB_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w10, echo=F}
vari <- HRS_WB_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w10, echo=F}
AfterH <- table(HRS_WB_ds_w10$mob_pull)
X<-table(HRS_WB_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-WB-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign WB w11, echo=F}
opal.assign.table.tibble(o, 'HRS_WB_w11_mob_pull','HRS.HRS-WB-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local WB w11, echo=F}
HRS_WB_w11_mob_pull <- opal.execute(o,'HRS_WB_w11_mob_pull')
vari <- HRS_WB_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_WB_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo WB w11}
HRS_WB_ds_w11 <- tibble(id=HRS_WB_w11_mob_pull$id)
HRS_WB_ds_w11$mob_pull <- car::recode(HRS_WB_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_WB_ds_w11$mob_pull <- labelled(HRS_WB_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w11, echo=F}
vari <- HRS_WB_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w11, echo=F}
AfterH <- table(HRS_WB_ds_w11$mob_pull)
X<-table(HRS_WB_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






## EBB

### Wave 7

#### Study-specific variable description




| **Name** | `R7PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign EBB w7, echo=F}
opal.assign.table.tibble(o, 'HRS_EBB_w7_mob_pull','HRS.HRS-EBB-w7', variables=list('R7PUSHA'), missings = TRUE)
```


```{r local EBB w7, echo=F}
HRS_EBB_w7_mob_pull <- opal.execute(o,'HRS_EBB_w7_mob_pull')
vari <- HRS_EBB_w7_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_EBB_w7_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w7_mob_pull, aes(x=factor(R7PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo EBB w7}
HRS_EBB_ds_w7 <- tibble(id=HRS_EBB_w7_mob_pull$id)
HRS_EBB_ds_w7$mob_pull <- car::recode(HRS_EBB_w7_mob_pull$R7PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_EBB_ds_w7$mob_pull <- labelled(HRS_EBB_ds_w7$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w7, echo=F}
vari <- HRS_EBB_ds_w7$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w7, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w7, echo=F}
AfterH <- table(HRS_EBB_ds_w7$mob_pull)
X<-table(HRS_EBB_w7_mob_pull$R7PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w7_mob_pull$R7PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 8

#### Study-specific variable description




| **Name** | `R8PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign EBB w8, echo=F}
opal.assign.table.tibble(o, 'HRS_EBB_w8_mob_pull','HRS.HRS-EBB-w8', variables=list('R8PUSHA'), missings = TRUE)
```


```{r local EBB w8, echo=F}
HRS_EBB_w8_mob_pull <- opal.execute(o,'HRS_EBB_w8_mob_pull')
vari <- HRS_EBB_w8_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_EBB_w8_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w8_mob_pull, aes(x=factor(R8PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo EBB w8}
HRS_EBB_ds_w8 <- tibble(id=HRS_EBB_w8_mob_pull$id)
HRS_EBB_ds_w8$mob_pull <- car::recode(HRS_EBB_w8_mob_pull$R8PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_EBB_ds_w8$mob_pull <- labelled(HRS_EBB_ds_w8$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w8, echo=F}
vari <- HRS_EBB_ds_w8$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w8, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w8, echo=F}
AfterH <- table(HRS_EBB_ds_w8$mob_pull)
X<-table(HRS_EBB_w8_mob_pull$R8PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w8_mob_pull$R8PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 9

#### Study-specific variable description




| **Name** | `R9PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign EBB w9, echo=F}
opal.assign.table.tibble(o, 'HRS_EBB_w9_mob_pull','HRS.HRS-EBB-w9', variables=list('R9PUSHA'), missings = TRUE)
```


```{r local EBB w9, echo=F}
HRS_EBB_w9_mob_pull <- opal.execute(o,'HRS_EBB_w9_mob_pull')
vari <- HRS_EBB_w9_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_EBB_w9_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w9_mob_pull, aes(x=factor(R9PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo EBB w9}
HRS_EBB_ds_w9 <- tibble(id=HRS_EBB_w9_mob_pull$id)
HRS_EBB_ds_w9$mob_pull <- car::recode(HRS_EBB_w9_mob_pull$R9PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_EBB_ds_w9$mob_pull <- labelled(HRS_EBB_ds_w9$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w9, echo=F}
vari <- HRS_EBB_ds_w9$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w9, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w9, echo=F}
AfterH <- table(HRS_EBB_ds_w9$mob_pull)
X<-table(HRS_EBB_w9_mob_pull$R9PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w9_mob_pull$R9PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```







### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign EBB w10, echo=F}
opal.assign.table.tibble(o, 'HRS_EBB_w10_mob_pull','HRS.HRS-EBB-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local EBB w10, echo=F}
HRS_EBB_w10_mob_pull <- opal.execute(o,'HRS_EBB_w10_mob_pull')
vari <- HRS_EBB_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_EBB_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo EBB w10}
HRS_EBB_ds_w10 <- tibble(id=HRS_EBB_w10_mob_pull$id)
HRS_EBB_ds_w10$mob_pull <- car::recode(HRS_EBB_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_EBB_ds_w10$mob_pull <- labelled(HRS_EBB_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w10, echo=F}
vari <- HRS_EBB_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w10, echo=F}
AfterH <- table(HRS_EBB_ds_w10$mob_pull)
X<-table(HRS_EBB_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign EBB w11, echo=F}
opal.assign.table.tibble(o, 'HRS_EBB_w11_mob_pull','HRS.HRS-EBB-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local EBB w11, echo=F}
HRS_EBB_w11_mob_pull <- opal.execute(o,'HRS_EBB_w11_mob_pull')
vari <- HRS_EBB_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_EBB_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo EBB w11}
HRS_EBB_ds_w11 <- tibble(id=HRS_EBB_w11_mob_pull$id)
HRS_EBB_ds_w11$mob_pull <- car::recode(HRS_EBB_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_EBB_ds_w11$mob_pull <- labelled(HRS_EBB_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w11, echo=F}
vari <- HRS_EBB_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w11, echo=F}
AfterH <- table(HRS_EBB_ds_w11$mob_pull)
X<-table(HRS_EBB_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






## MBB

### Wave 10

#### Study-specific variable description




| **Name** | `R10PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign MBB w10, echo=F}
opal.assign.table.tibble(o, 'HRS_MBB_w10_mob_pull','HRS.HRS-MBB-w10', variables=list('R10PUSHA'), missings = TRUE)
```


```{r local MBB w10, echo=F}
HRS_MBB_w10_mob_pull <- opal.execute(o,'HRS_MBB_w10_mob_pull')
vari <- HRS_MBB_w10_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_MBB_w10_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_MBB_w10_mob_pull, aes(x=factor(R10PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo MBB w10}
HRS_MBB_ds_w10 <- tibble(id=HRS_MBB_w10_mob_pull$id)
HRS_MBB_ds_w10$mob_pull <- car::recode(HRS_MBB_w10_mob_pull$R10PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_MBB_ds_w10$mob_pull <- labelled(HRS_MBB_ds_w10$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w10, echo=F}
vari <- HRS_MBB_ds_w10$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_MBB_ds_w10, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w10, echo=F}
AfterH <- table(HRS_MBB_ds_w10$mob_pull)
X<-table(HRS_MBB_w10_mob_pull$R10PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w10_mob_pull$R10PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```






### Wave 11

#### Study-specific variable description




| **Name** | `R11PUSHA`|
|-|-|
| **Label** | `Any Diff-Push/pull lg obj` |
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`0 = No; 1 = Yes`|
| **Missings** |`NA`|
| **Description** |  |








```{r assign MBB w11, echo=F}
opal.assign.table.tibble(o, 'HRS_MBB_w11_mob_pull','HRS.HRS-MBB-w11', variables=list('R11PUSHA'), missings = TRUE)
```


```{r local MBB w11, echo=F}
HRS_MBB_w11_mob_pull <- opal.execute(o,'HRS_MBB_w11_mob_pull')
vari <- HRS_MBB_w11_mob_pull[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = names(HRS_MBB_w11_mob_pull)[2])
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_MBB_w11_mob_pull, aes(x=factor(R11PUSHA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`



**R script:**
```{r harmo MBB w11}
HRS_MBB_ds_w11 <- tibble(id=HRS_MBB_w11_mob_pull$id)
HRS_MBB_ds_w11$mob_pull <- car::recode(HRS_MBB_w11_mob_pull$R11PUSHA, "1 = '0';0 = '1'; NA='999'")
HRS_MBB_ds_w11$mob_pull <- labelled(HRS_MBB_ds_w11$mob_pull, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w11, echo=F}
vari <- HRS_MBB_ds_w11$mob_pull
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_pull")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_MBB_ds_w11, aes(x=factor(mob_pull))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Pulling or pushing large objects") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w11, echo=F}
AfterH <- table(HRS_MBB_ds_w11$mob_pull)
X<-table(HRS_MBB_w11_mob_pull$R11PUSHA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w11_mob_pull$R11PUSHA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```





<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE}
mob_pull <- HRS_m_ds_hrs_w1  <- HRS_ds_hrs_w1  <- HRS_HRS_ds_w1
save(mob_pull, file = "../RData/hrs_w1/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w2  <- HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
save(mob_pull, file = "../RData/hrs_w2/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w3  <- HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
save(mob_pull, file = "../RData/hrs_w3/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w4  <- HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
save(mob_pull, file = "../RData/hrs_w4/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w5  <- HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
save(mob_pull, file = "../RData/hrs_w5/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w6  <- HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
save(mob_pull, file = "../RData/hrs_w6/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w7  <- HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
save(mob_pull, file = "../RData/hrs_w7/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w8  <- HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
save(mob_pull, file = "../RData/hrs_w8/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w9  <- HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
save(mob_pull, file = "../RData/hrs_w9/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
save(mob_pull, file = "../RData/hrs_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11 <- HRS_HRS_ds_w11
save(mob_pull, file = "../RData/hrs_w11/mob_pull.RData")


mob_pull <- HRS_m_ds_ahead_w2  <- HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
save(mob_pull, file = "../RData/ahead_w2/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w3  <- HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
save(mob_pull, file = "../RData/ahead_w3/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w4  <- HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
save(mob_pull, file = "../RData/ahead_w4/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w5  <- HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
save(mob_pull, file = "../RData/ahead_w5/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w6  <- HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
save(mob_pull, file = "../RData/ahead_w6/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w7  <- HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
save(mob_pull, file = "../RData/ahead_w7/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w8  <- HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
save(mob_pull, file = "../RData/ahead_w8/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w9  <- HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
save(mob_pull, file = "../RData/ahead_w9/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
save(mob_pull, file = "../RData/ahead_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11
save(mob_pull, file = "../RData/ahead_w11/mob_pull.RData")


mob_pull <- HRS_m_ds_coda_w4  <- HRS_ds_coda_w4  <- HRS_CODA_ds_w4
save(mob_pull, file = "../RData/coda_w4/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w5  <- HRS_ds_coda_w5  <- HRS_CODA_ds_w5
save(mob_pull, file = "../RData/coda_w5/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w6  <- HRS_ds_coda_w6  <- HRS_CODA_ds_w6
save(mob_pull, file = "../RData/coda_w6/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w7  <- HRS_ds_coda_w7  <- HRS_CODA_ds_w7
save(mob_pull, file = "../RData/coda_w7/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w8  <- HRS_ds_coda_w8  <- HRS_CODA_ds_w8
save(mob_pull, file = "../RData/coda_w8/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w9  <- HRS_ds_coda_w9  <- HRS_CODA_ds_w9
save(mob_pull, file = "../RData/coda_w9/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w10 <- HRS_ds_coda_w10 <- HRS_CODA_ds_w10
save(mob_pull, file = "../RData/coda_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_coda_w11 <- HRS_ds_coda_w11 <- HRS_CODA_ds_w11
save(mob_pull, file = "../RData/coda_w11/mob_pull.RData")


mob_pull <- HRS_m_ds_wb_w4  <- HRS_ds_wb_w4  <- HRS_WB_ds_w4
save(mob_pull, file = "../RData/wb_w4/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w5  <- HRS_ds_wb_w5  <- HRS_WB_ds_w5
save(mob_pull, file = "../RData/wb_w5/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w6  <- HRS_ds_wb_w6  <- HRS_WB_ds_w6
save(mob_pull, file = "../RData/wb_w6/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w7  <- HRS_ds_wb_w7  <- HRS_WB_ds_w7
save(mob_pull, file = "../RData/wb_w7/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w8  <- HRS_ds_wb_w8  <- HRS_WB_ds_w8
save(mob_pull, file = "../RData/wb_w8/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w9  <- HRS_ds_wb_w9  <- HRS_WB_ds_w9
save(mob_pull, file = "../RData/wb_w9/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w10 <- HRS_ds_wb_w10 <- HRS_WB_ds_w10
save(mob_pull, file = "../RData/wb_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_wb_w11 <- HRS_ds_wb_w11 <- HRS_WB_ds_w11
save(mob_pull, file = "../RData/wb_w11/mob_pull.RData")


mob_pull <- HRS_m_ds_ebb_w7  <- HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
save(mob_pull, file = "../RData/ebb_w7/mob_pull.RData")

mob_pull <- HRS_m_ds_ebb_w8  <- HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
save(mob_pull, file = "../RData/ebb_w8/mob_pull.RData")

mob_pull <- HRS_m_ds_ebb_w9  <- HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
save(mob_pull, file = "../RData/ebb_w9/mob_pull.RData")

mob_pull <- HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
save(mob_pull, file = "../RData/ebb_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11 <- HRS_EBB_ds_w11
save(mob_pull, file = "../RData/ebb_w11/mob_pull.RData")


mob_pull <- HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
save(mob_pull, file = "../RData/mbb_w10/mob_pull.RData")

mob_pull <- HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11 <- HRS_MBB_ds_w11
save(mob_pull, file = "../RData/mbb_w11/mob_pull.RData")


l.hrs <- list(HRS_ds_hrs_w1 = HRS_ds_hrs_w1 , HRS_ds_hrs_w2 = HRS_ds_hrs_w2 ,HRS_ds_hrs_w3 = HRS_ds_hrs_w3 ,HRS_ds_hrs_w4 = HRS_ds_hrs_w4 ,
HRS_ds_hrs_w5 = HRS_ds_hrs_w5 ,HRS_ds_hrs_w6 = HRS_ds_hrs_w6 ,HRS_ds_hrs_w7 = HRS_ds_hrs_w7 ,HRS_ds_hrs_w8 = HRS_ds_hrs_w8 ,
HRS_ds_hrs_w9 = HRS_ds_hrs_w9 ,HRS_ds_hrs_w10 = HRS_ds_hrs_w10 ,HRS_ds_hrs_w11 = HRS_ds_hrs_w11 ,HRS_ds_ahead_w2 = HRS_ds_ahead_w2 ,
HRS_ds_ahead_w3 = HRS_ds_ahead_w3 ,HRS_ds_ahead_w4 = HRS_ds_ahead_w4 ,HRS_ds_ahead_w5 = HRS_ds_ahead_w5 ,HRS_ds_ahead_w6 = HRS_ds_ahead_w6 ,
HRS_ds_ahead_w7 = HRS_ds_ahead_w7 ,HRS_ds_ahead_w8 = HRS_ds_ahead_w8 ,HRS_ds_ahead_w9 = HRS_ds_ahead_w9 ,HRS_ds_ahead_w10 = HRS_ds_ahead_w10 ,
HRS_ds_ahead_w11 = HRS_ds_ahead_w11 ,HRS_ds_coda_w4 = HRS_ds_coda_w4 ,HRS_ds_coda_w5 = HRS_ds_coda_w5 ,HRS_ds_coda_w6 = HRS_ds_coda_w6 ,
HRS_ds_coda_w7 = HRS_ds_coda_w7 ,HRS_ds_coda_w8 = HRS_ds_coda_w8 ,HRS_ds_coda_w9 = HRS_ds_coda_w9 ,HRS_ds_coda_w10 = HRS_ds_coda_w10 ,
HRS_ds_coda_w11 = HRS_ds_coda_w11 ,HRS_ds_wb_w4 = HRS_ds_wb_w4 ,HRS_ds_wb_w5 = HRS_ds_wb_w5 ,HRS_ds_wb_w6 = HRS_ds_wb_w6 ,
HRS_ds_wb_w7 = HRS_ds_wb_w7 ,HRS_ds_wb_w8 = HRS_ds_wb_w8 ,HRS_ds_wb_w9 = HRS_ds_wb_w9 ,HRS_ds_wb_w10 = HRS_ds_wb_w10 ,
HRS_ds_wb_w11 = HRS_ds_wb_w11 ,HRS_ds_ebb_w7 = HRS_ds_ebb_w7 ,HRS_ds_ebb_w8 = HRS_ds_ebb_w8 ,HRS_ds_ebb_w9 = HRS_ds_ebb_w9 ,
HRS_ds_ebb_w10 = HRS_ds_ebb_w10 ,HRS_ds_ebb_w11 = HRS_ds_ebb_w11 ,HRS_ds_mbb_w10 = HRS_ds_mbb_w10 ,HRS_ds_mbb_w11 = HRS_ds_mbb_w11)

m.hrs <- list(HRS_m_ds_hrs_w1 = HRS_m_ds_hrs_w1 , HRS_m_ds_hrs_w2 = HRS_m_ds_hrs_w2 ,HRS_m_ds_hrs_w3 = HRS_m_ds_hrs_w3 ,HRS_m_ds_hrs_w4 = HRS_m_ds_hrs_w4 ,
HRS_m_ds_hrs_w5 = HRS_m_ds_hrs_w5 ,HRS_m_ds_hrs_w6 = HRS_m_ds_hrs_w6 ,HRS_m_ds_hrs_w7 = HRS_m_ds_hrs_w7 ,HRS_m_ds_hrs_w8 = HRS_m_ds_hrs_w8 ,
HRS_m_ds_hrs_w9 = HRS_m_ds_hrs_w9 ,HRS_m_ds_hrs_w10 = HRS_m_ds_hrs_w10 ,HRS_m_ds_hrs_w11 = HRS_m_ds_hrs_w11 ,HRS_m_ds_ahead_w2 = HRS_m_ds_ahead_w2 ,
HRS_m_ds_ahead_w3 = HRS_m_ds_ahead_w3 ,HRS_m_ds_ahead_w4 = HRS_m_ds_ahead_w4 ,HRS_m_ds_ahead_w5 = HRS_m_ds_ahead_w5 ,HRS_m_ds_ahead_w6 = HRS_m_ds_ahead_w6 ,
HRS_m_ds_ahead_w7 = HRS_m_ds_ahead_w7 ,HRS_m_ds_ahead_w8 = HRS_m_ds_ahead_w8 ,HRS_m_ds_ahead_w9 = HRS_m_ds_ahead_w9 ,HRS_m_ds_ahead_w10 = HRS_m_ds_ahead_w10 ,
HRS_m_ds_ahead_w11 = HRS_m_ds_ahead_w11 ,HRS_m_ds_coda_w4 = HRS_m_ds_coda_w4 ,HRS_m_ds_coda_w5 = HRS_m_ds_coda_w5 ,HRS_m_ds_coda_w6 = HRS_m_ds_coda_w6 ,
HRS_m_ds_coda_w7 = HRS_m_ds_coda_w7 ,HRS_m_ds_coda_w8 = HRS_m_ds_coda_w8 ,HRS_m_ds_coda_w9 = HRS_m_ds_coda_w9 ,HRS_m_ds_coda_w10 = HRS_m_ds_coda_w10 ,
HRS_m_ds_coda_w11 = HRS_m_ds_coda_w11 ,HRS_m_ds_wb_w4 = HRS_m_ds_wb_w4 ,HRS_m_ds_wb_w5 = HRS_m_ds_wb_w5 ,HRS_m_ds_wb_w6 = HRS_m_ds_wb_w6 ,
HRS_m_ds_wb_w7 = HRS_m_ds_wb_w7 ,HRS_m_ds_wb_w8 = HRS_m_ds_wb_w8 ,HRS_m_ds_wb_w9 = HRS_m_ds_wb_w9 ,HRS_m_ds_wb_w10 = HRS_m_ds_wb_w10 ,
HRS_m_ds_wb_w11 = HRS_m_ds_wb_w11 ,HRS_m_ds_ebb_w7 = HRS_m_ds_ebb_w7 ,HRS_m_ds_ebb_w8 = HRS_m_ds_ebb_w8 ,HRS_m_ds_ebb_w9 = HRS_m_ds_ebb_w9 ,
HRS_m_ds_ebb_w10 = HRS_m_ds_ebb_w10 ,HRS_m_ds_ebb_w11 = HRS_m_ds_ebb_w11 ,HRS_m_ds_mbb_w10 = HRS_m_ds_mbb_w10 ,HRS_m_ds_mbb_w11 = HRS_m_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- label(m.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hrs[[i]][[2]] <- car::recode(m.hrs[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hrs[[i]][[2]] <- labelled(m.hrs[[i]][[2]], labels = c(Yes=0, No=1))

    nl <- names(l.hrs[i])
    #opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

    ml <- names(m.hrs[i])
    #opal.assign.data(o, ml , m.hrs[[i]])
    #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}

```

## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

# Table HRS
t.hrs <- frq(l.hrs[[3]][2])[[1]][,c(1,2)] 
for (i in 1:11){
  t.hrs[2+i] <- frq(l.hrs[[i]][2])[[1]][,4] 
}
t.hrs[13,] <- c("n", "sample size", 
             length(l.hrs[[1]][[2]]), length(l.hrs[[2]][[2]]), length(l.hrs[[3]][[2]]),
             length(l.hrs[[4]][[2]]), length(l.hrs[[5]][[2]]), length(l.hrs[[6]][[2]]),     
             length(l.hrs[[7]][[2]]), length(l.hrs[[8]][[2]]), length(l.hrs[[9]][[2]]),
             length(l.hrs[[10]][[2]]), length(l.hrs[[11]][[2]]))
names(t.hrs)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.hrs)
  

# Table AHEAD
t.ahead <- frq(l.hrs[[12]][2])[[1]][,c(1,2)] 
for (i in 1:10){
  t.ahead[2+i] <- frq(l.hrs[[i+11]][2])[[1]][,4] 
}
t.ahead[13,] <- c("n", "sample size", 
             length(l.hrs[[12]][[2]]), length(l.hrs[[13]][[2]]), length(l.hrs[[14]][[2]]),
             length(l.hrs[[15]][[2]]), length(l.hrs[[16]][[2]]), length(l.hrs[[17]][[2]]),     
             length(l.hrs[[18]][[2]]), length(l.hrs[[19]][[2]]), length(l.hrs[[20]][[2]]),
             length(l.hrs[[21]][[2]]))
names(t.ahead)<-c("val", "label", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.ahead)



# Table CODA
t.coda <- frq(l.hrs[[22]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.coda[2+i] <- frq(l.hrs[[21+i]][2])[[1]][,4] 
}
t.coda[13,] <- c("n", "sample size", 
             length(l.hrs[[22]][[2]]), length(l.hrs[[23]][[2]]), length(l.hrs[[24]][[2]]),
             length(l.hrs[[25]][[2]]), length(l.hrs[[26]][[2]]), length(l.hrs[[27]][[2]]),     
             length(l.hrs[[28]][[2]]), length(l.hrs[[29]][[2]]))
names(t.coda)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.coda)



# Table WB
t.wb <- frq(l.hrs[[30]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.wb[2+i] <- frq(l.hrs[[31+i]][2])[[1]][,4] 
}
t.wb[13,] <- c("n", "sample size", 
             length(l.hrs[[30]][[2]]), length(l.hrs[[31]][[2]]), length(l.hrs[[32]][[2]]),
             length(l.hrs[[33]][[2]]), length(l.hrs[[34]][[2]]), length(l.hrs[[35]][[2]]),     
             length(l.hrs[[36]][[2]]), length(l.hrs[[37]][[2]]))
names(t.wb)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.wb)



# Table EBB
t.ebb <- frq(l.hrs[[38]][2])[[1]][,c(1,2)] 
for (i in 1:5){
  t.ebb[2+i] <- frq(l.hrs[[37+i]][2])[[1]][,4] 
}
t.ebb[13,] <- c("n", "sample size", 
             length(l.hrs[[38]][[2]]), length(l.hrs[[39]][[2]]), length(l.hrs[[40]][[2]]),
             length(l.hrs[[41]][[2]]), length(l.hrs[[42]][[2]]))
names(t.ebb)<-c("val", "label", "w7", "w8", "w9", "w10", "w11")
kable(t.ebb)



# Table MBB
t.mbb <- frq(l.hrs[[43]][2])[[1]][,c(1,2)] 
for (i in 1:2){
  t.mbb[2+i] <- frq(l.hrs[[42+i]][2])[[1]][,4] 
}
t.mbb[13,] <- c("n", "sample size", length(l.hrs[[43]][[2]]), length(l.hrs[[44]][[2]]))
names(t.mbb)<-c("val", "label", "w10", "w11")
kable(t.mbb)

```


# Quality estimation
No comments

<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```



