---
title: "ADL - Using the toilet"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_toilet`
* Variable label: `ADL-Difficulties for using the toilet`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 

```{r lab, echo=FALSE}
ds_label <- "ADL-Difficulties for using the toilet"
```

<!-- ########################################################## --> 

# Data process
## HRS sub-sample

### Wave 1

No study-specific variable has been found.

### Wave 2

#### Study-specific variable description


* Name: `R2TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't know`


* Description: 
```{r assign HRS w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w2_adl_toilet','HRS.HRS-HRS-w2', variables=list('R2TOILTA'), missings = TRUE)
```


```{r local HRS w2,  echo=FALSE}
HRS_HRS_w2_adl_toilet <- opal.execute(o,'HRS_HRS_w2_adl_toilet')

vari <- HRS_HRS_w2_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w2_adl_toilet[[2]])
ggplot(HRS_HRS_w2_adl_toilet, aes(x=factor(R2TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w2,   echo=TRUE}
HRS_HRS_ds_w2 <- tibble(id=HRS_HRS_w2_adl_toilet$id)
HRS_HRS_ds_w2$adl_toilet <- car::recode(HRS_HRS_w2_adl_toilet$R2TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w2$adl_toilet <- labelled(HRS_HRS_ds_w2$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w2,  echo=FALSE}
vari <- HRS_HRS_ds_w2$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")


#Categorical_summary(var = HRS_HRS_ds_w2$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w2, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w2,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w2$adl_toilet)
X<-table(HRS_HRS_w2_adl_toilet$R2TOILTA)
BeforeH <- sum(is.na(HRS_HRS_w2_adl_toilet$R2TOILTA))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("NA->999") 
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

 


* Name: `R3TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign HRS w3,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w3_adl_toilet','HRS.HRS-HRS-w3', variables=list('R3TOILTA'), missings = TRUE)
```


```{r local HRS w3,  echo=FALSE}
HRS_HRS_w3_adl_toilet <- opal.execute(o,'HRS_HRS_w3_adl_toilet')
vari <- HRS_HRS_w3_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w3_adl_toilet[[2]])
ggplot(HRS_HRS_w3_adl_toilet, aes(x=factor(R3TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w3,   echo=TRUE}
HRS_HRS_ds_w3 <- tibble(id=HRS_HRS_w3_adl_toilet$id)
HRS_HRS_ds_w3$adl_toilet <- car::recode(HRS_HRS_w3_adl_toilet$R3TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w3$adl_toilet <- labelled(HRS_HRS_ds_w3$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w3,  echo=FALSE}
vari <- HRS_HRS_ds_w3$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w3$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w3, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w3,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w3$adl_toilet)
X<-table(HRS_HRS_w3_adl_toilet$R3TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w3_adl_toilet$R3TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

 


* Name: `R4TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign HRS w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w4_adl_toilet','HRS.HRS-HRS-w4', variables=list('R4TOILTA'), missings = TRUE)
```


```{r local HRS w4,  echo=FALSE}
HRS_HRS_w4_adl_toilet <- opal.execute(o,'HRS_HRS_w4_adl_toilet')
vari <- HRS_HRS_w4_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w4_adl_toilet[[2]])
ggplot(HRS_HRS_w4_adl_toilet, aes(x=factor(R4TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w4,   echo=TRUE}
HRS_HRS_ds_w4 <- tibble(id=HRS_HRS_w4_adl_toilet$id)
HRS_HRS_ds_w4$adl_toilet <- car::recode(HRS_HRS_w4_adl_toilet$R4TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w4$adl_toilet <- labelled(HRS_HRS_ds_w4$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w4,  echo=FALSE}
vari <- HRS_HRS_ds_w4$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w4$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w4, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w4,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w4$adl_toilet)
X<-table(HRS_HRS_w4_adl_toilet$R4TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w4_adl_toilet$R4TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

 


* Name: `R5TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`

* Description: 
```{r assign HRS w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w5_adl_toilet','HRS.HRS-HRS-w5', variables=list('R5TOILTA'), missings = TRUE)
```


```{r local HRS w5,  echo=FALSE}
HRS_HRS_w5_adl_toilet <- opal.execute(o,'HRS_HRS_w5_adl_toilet')
vari <- HRS_HRS_w5_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w5_adl_toilet[[2]])
ggplot(HRS_HRS_w5_adl_toilet, aes(x=factor(R5TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w5,   echo=TRUE}
HRS_HRS_ds_w5 <- tibble(id=HRS_HRS_w5_adl_toilet$id)
HRS_HRS_ds_w5$adl_toilet <- car::recode(HRS_HRS_w5_adl_toilet$R5TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w5$adl_toilet <- labelled(HRS_HRS_ds_w5$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w5,  echo=FALSE}
vari <- HRS_HRS_ds_w5$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w5$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w5, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w5,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w5$adl_toilet)
X<-table(HRS_HRS_w5_adl_toilet$R5TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w5_adl_toilet$R5TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

 


* Name: `R6TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`

* Description: 
```{r assign HRS w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w6_adl_toilet','HRS.HRS-HRS-w6', variables=list('R6TOILTA'), missings = TRUE)
```


```{r local HRS w6,  echo=FALSE}
HRS_HRS_w6_adl_toilet <- opal.execute(o,'HRS_HRS_w6_adl_toilet')
vari <- HRS_HRS_w6_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w6_adl_toilet[[2]])
ggplot(HRS_HRS_w6_adl_toilet, aes(x=factor(R6TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w6,   echo=TRUE}
HRS_HRS_ds_w6 <- tibble(id=HRS_HRS_w6_adl_toilet$id)
HRS_HRS_ds_w6$adl_toilet <- car::recode(HRS_HRS_w6_adl_toilet$R6TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w6$adl_toilet <- labelled(HRS_HRS_ds_w6$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w6,  echo=FALSE}
vari <- HRS_HRS_ds_w6$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w6$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w6, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w6,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w6$adl_toilet)
X<-table(HRS_HRS_w6_adl_toilet$R6TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w6_adl_toilet$R6TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

 


* Name: `R7TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign HRS w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w7_adl_toilet','HRS.HRS-HRS-w7', variables=list('R7TOILTA'), missings = TRUE)
```


```{r local HRS w7,  echo=FALSE}
HRS_HRS_w7_adl_toilet <- opal.execute(o,'HRS_HRS_w7_adl_toilet')
vari <- HRS_HRS_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w7_adl_toilet[[2]])
ggplot(HRS_HRS_w7_adl_toilet, aes(x=factor(R7TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w7,   echo=TRUE}
HRS_HRS_ds_w7 <- tibble(id=HRS_HRS_w7_adl_toilet$id)
HRS_HRS_ds_w7$adl_toilet <- car::recode(HRS_HRS_w7_adl_toilet$R7TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w7$adl_toilet <- labelled(HRS_HRS_ds_w7$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w7,  echo=FALSE}
vari <- HRS_HRS_ds_w7$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w7,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w7$adl_toilet)
X<-table(HRS_HRS_w7_adl_toilet$R7TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w7_adl_toilet$R7TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


* Name: `R8TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign HRS w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w8_adl_toilet','HRS.HRS-HRS-w8', variables=list('R8TOILTA'), missings = TRUE)
```


```{r local HRS w8,  echo=FALSE}
HRS_HRS_w8_adl_toilet <- opal.execute(o,'HRS_HRS_w8_adl_toilet')
vari <- HRS_HRS_w8_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w8_adl_toilet[[2]])
ggplot(HRS_HRS_w8_adl_toilet, aes(x=factor(R8TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w8,   echo=TRUE}
HRS_HRS_ds_w8 <- tibble(id=HRS_HRS_w8_adl_toilet$id)
HRS_HRS_ds_w8$adl_toilet <- car::recode(HRS_HRS_w8_adl_toilet$R8TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w8$adl_toilet <- labelled(HRS_HRS_ds_w8$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w8,  echo=FALSE}
vari <- HRS_HRS_ds_w8$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w8,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w8$adl_toilet)
X<-table(HRS_HRS_w8_adl_toilet$R8TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w8_adl_toilet$R8TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

 


* Name: `R9TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign HRS w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w9_adl_toilet','HRS.HRS-HRS-w9', variables=list('R9TOILTA'), missings = TRUE)
```


```{r local HRS w9,  echo=FALSE}
HRS_HRS_w9_adl_toilet <- opal.execute(o,'HRS_HRS_w9_adl_toilet')
vari <- HRS_HRS_w9_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w9_adl_toilet[[2]])
ggplot(HRS_HRS_w9_adl_toilet, aes(x=factor(R9TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w9,   echo=TRUE}
HRS_HRS_ds_w9 <- tibble(id=HRS_HRS_w9_adl_toilet$id)
HRS_HRS_ds_w9$adl_toilet <- car::recode(HRS_HRS_w9_adl_toilet$R9TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w9$adl_toilet <- labelled(HRS_HRS_ds_w9$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w9,  echo=FALSE}
vari <- HRS_HRS_ds_w9$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w9,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w9$adl_toilet)
X<-table(HRS_HRS_w9_adl_toilet$R9TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w9_adl_toilet$R9TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign HRS w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w10_adl_toilet','HRS.HRS-HRS-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local HRS w10,  echo=FALSE}
HRS_HRS_w10_adl_toilet <- opal.execute(o,'HRS_HRS_w10_adl_toilet')
vari <- HRS_HRS_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w10_adl_toilet[[2]])
ggplot(HRS_HRS_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w10,   echo=TRUE}
HRS_HRS_ds_w10 <- tibble(id=HRS_HRS_w10_adl_toilet$id)
HRS_HRS_ds_w10$adl_toilet <- car::recode(HRS_HRS_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w10$adl_toilet <- labelled(HRS_HRS_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w10,  echo=FALSE}
vari <- HRS_HRS_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w10,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w10$adl_toilet)
X<-table(HRS_HRS_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign HRS w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w11_adl_toilet','HRS.HRS-HRS-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local HRS w11,  echo=FALSE}
HRS_HRS_w11_adl_toilet <- opal.execute(o,'HRS_HRS_w11_adl_toilet')
vari <- HRS_HRS_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_HRS_w11_adl_toilet[[2]])
ggplot(HRS_HRS_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo HRS w11,   echo=TRUE}
HRS_HRS_ds_w11 <- tibble(id=HRS_HRS_w11_adl_toilet$id)
HRS_HRS_ds_w11$adl_toilet <- car::recode(HRS_HRS_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_HRS_ds_w11$adl_toilet <- labelled(HRS_HRS_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript HRS w11,  echo=FALSE}
vari <- HRS_HRS_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_HRS_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation HRS w11,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w11$adl_toilet)
X<-table(HRS_HRS_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




## AHEAD sub-sample

### Wave 2

#### Study-specific variable description

 


* Name: `R2TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w2_adl_toilet','HRS.HRS-AHEAD-w2', variables=list('R2TOILTA'), missings = TRUE)
```


```{r local AHEAD w2,  echo=FALSE}
HRS_AHEAD_w2_adl_toilet <- opal.execute(o,'HRS_AHEAD_w2_adl_toilet')
vari <- HRS_AHEAD_w2_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w2_adl_toilet[[2]])
ggplot(HRS_AHEAD_w2_adl_toilet, aes(x=factor(R2TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w2,   echo=TRUE}
HRS_AHEAD_ds_w2 <- tibble(id=HRS_AHEAD_w2_adl_toilet$id)
HRS_AHEAD_ds_w2$adl_toilet <- car::recode(HRS_AHEAD_w2_adl_toilet$R2TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w2$adl_toilet <- labelled(HRS_AHEAD_ds_w2$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w2,  echo=FALSE}
vari <- HRS_AHEAD_ds_w2$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_AHEAD_ds_w2$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w2, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w2,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w2$adl_toilet)
X<-table(HRS_AHEAD_w2_adl_toilet$R2TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w2_adl_toilet$R2TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

 


* Name: `R3TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w3,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w3_adl_toilet','HRS.HRS-AHEAD-w3', variables=list('R3TOILTA'), missings = TRUE)
```


```{r local AHEAD w3,  echo=FALSE}
HRS_AHEAD_w3_adl_toilet <- opal.execute(o,'HRS_AHEAD_w3_adl_toilet')
vari <- HRS_AHEAD_w3_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w3_adl_toilet[[2]])
ggplot(HRS_AHEAD_w3_adl_toilet, aes(x=factor(R3TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w3,   echo=TRUE}
HRS_AHEAD_ds_w3 <- tibble(id=HRS_AHEAD_w3_adl_toilet$id)
HRS_AHEAD_ds_w3$adl_toilet <- car::recode(HRS_AHEAD_w3_adl_toilet$R3TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w3$adl_toilet <- labelled(HRS_AHEAD_ds_w3$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w3,  echo=FALSE}
vari <- HRS_AHEAD_ds_w3$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_AHEAD_ds_w3$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w3, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w3,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w3$adl_toilet)
X<-table(HRS_AHEAD_w3_adl_toilet$R3TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w3_adl_toilet$R3TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

 


* Name: `R4TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w4_adl_toilet','HRS.HRS-AHEAD-w4', variables=list('R4TOILTA'), missings = TRUE)
```


```{r local AHEAD w4,  echo=FALSE}
HRS_AHEAD_w4_adl_toilet <- opal.execute(o,'HRS_AHEAD_w4_adl_toilet')
vari <- HRS_AHEAD_w4_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w4_adl_toilet[[2]])
ggplot(HRS_AHEAD_w4_adl_toilet, aes(x=factor(R4TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w4,   echo=TRUE}
HRS_AHEAD_ds_w4 <- tibble(id=HRS_AHEAD_w4_adl_toilet$id)
HRS_AHEAD_ds_w4$adl_toilet <- car::recode(HRS_AHEAD_w4_adl_toilet$R4TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w4$adl_toilet <- labelled(HRS_AHEAD_ds_w4$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w4,  echo=FALSE}
vari <- HRS_AHEAD_ds_w4$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_AHEAD_ds_w4$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w4, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w4,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w4$adl_toilet)
X<-table(HRS_AHEAD_w4_adl_toilet$R4TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w4_adl_toilet$R4TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

 


* Name: `R5TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w5_adl_toilet','HRS.HRS-AHEAD-w5', variables=list('R5TOILTA'), missings = TRUE)
```


```{r local AHEAD w5,  echo=FALSE}
HRS_AHEAD_w5_adl_toilet <- opal.execute(o,'HRS_AHEAD_w5_adl_toilet')
vari <- HRS_AHEAD_w5_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w5_adl_toilet[[2]])
ggplot(HRS_AHEAD_w5_adl_toilet, aes(x=factor(R5TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w5,   echo=TRUE}
HRS_AHEAD_ds_w5 <- tibble(id=HRS_AHEAD_w5_adl_toilet$id)
HRS_AHEAD_ds_w5$adl_toilet <- car::recode(HRS_AHEAD_w5_adl_toilet$R5TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w5$adl_toilet <- labelled(HRS_AHEAD_ds_w5$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w5,  echo=FALSE}
vari <- HRS_AHEAD_ds_w5$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_AHEAD_ds_w5$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w5, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w5,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w5$adl_toilet)
X<-table(HRS_AHEAD_w5_adl_toilet$R5TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w5_adl_toilet$R5TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

 


* Name: `R6TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w6_adl_toilet','HRS.HRS-AHEAD-w6', variables=list('R6TOILTA'), missings = TRUE)
```


```{r local AHEAD w6,  echo=FALSE}
HRS_AHEAD_w6_adl_toilet <- opal.execute(o,'HRS_AHEAD_w6_adl_toilet')
vari <- HRS_AHEAD_w6_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w6_adl_toilet[[2]])
ggplot(HRS_AHEAD_w6_adl_toilet, aes(x=factor(R6TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w6,   echo=TRUE}
HRS_AHEAD_ds_w6 <- tibble(id=HRS_AHEAD_w6_adl_toilet$id)
HRS_AHEAD_ds_w6$adl_toilet <- car::recode(HRS_AHEAD_w6_adl_toilet$R6TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w6$adl_toilet <- labelled(HRS_AHEAD_ds_w6$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w6,  echo=FALSE}
vari <- HRS_AHEAD_ds_w6$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_AHEAD_ds_w6$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w6, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w6,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w6$adl_toilet)
X<-table(HRS_AHEAD_w6_adl_toilet$R6TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w6_adl_toilet$R6TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

 


* Name: `R7TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w7_adl_toilet','HRS.HRS-AHEAD-w7', variables=list('R7TOILTA'), missings = TRUE)
```


```{r local AHEAD w7,  echo=FALSE}
HRS_AHEAD_w7_adl_toilet <- opal.execute(o,'HRS_AHEAD_w7_adl_toilet')
vari <- HRS_AHEAD_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w7_adl_toilet[[2]])
ggplot(HRS_AHEAD_w7_adl_toilet, aes(x=factor(R7TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w7,   echo=TRUE}
HRS_AHEAD_ds_w7 <- tibble(id=HRS_AHEAD_w7_adl_toilet$id)
HRS_AHEAD_ds_w7$adl_toilet <- car::recode(HRS_AHEAD_w7_adl_toilet$R7TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w7$adl_toilet <- labelled(HRS_AHEAD_ds_w7$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w7,  echo=FALSE}
vari <- HRS_AHEAD_ds_w7$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w7,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w7$adl_toilet)
X<-table(HRS_AHEAD_w7_adl_toilet$R7TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w7_adl_toilet$R7TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


* Name: `R8TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w8_adl_toilet','HRS.HRS-AHEAD-w8', variables=list('R8TOILTA'), missings = TRUE)
```


```{r local AHEAD w8,  echo=FALSE}
HRS_AHEAD_w8_adl_toilet <- opal.execute(o,'HRS_AHEAD_w8_adl_toilet')
vari <- HRS_AHEAD_w8_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w8_adl_toilet[[2]])
ggplot(HRS_AHEAD_w8_adl_toilet, aes(x=factor(R8TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w8,   echo=TRUE}
HRS_AHEAD_ds_w8 <- tibble(id=HRS_AHEAD_w8_adl_toilet$id)
HRS_AHEAD_ds_w8$adl_toilet <- car::recode(HRS_AHEAD_w8_adl_toilet$R8TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w8$adl_toilet <- labelled(HRS_AHEAD_ds_w8$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w8,  echo=FALSE}
vari <- HRS_AHEAD_ds_w8$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w8,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w8$adl_toilet)
X<-table(HRS_AHEAD_w8_adl_toilet$R8TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w8_adl_toilet$R8TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

 


* Name: `R9TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w9_adl_toilet','HRS.HRS-AHEAD-w9', variables=list('R9TOILTA'), missings = TRUE)
```


```{r local AHEAD w9,  echo=FALSE}
HRS_AHEAD_w9_adl_toilet <- opal.execute(o,'HRS_AHEAD_w9_adl_toilet')
vari <- HRS_AHEAD_w9_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w9_adl_toilet[[2]])
ggplot(HRS_AHEAD_w9_adl_toilet, aes(x=factor(R9TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w9,   echo=TRUE}
HRS_AHEAD_ds_w9 <- tibble(id=HRS_AHEAD_w9_adl_toilet$id)
HRS_AHEAD_ds_w9$adl_toilet <- car::recode(HRS_AHEAD_w9_adl_toilet$R9TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w9$adl_toilet <- labelled(HRS_AHEAD_ds_w9$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w9,  echo=FALSE}
vari <- HRS_AHEAD_ds_w9$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w9,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w9$adl_toilet)
X<-table(HRS_AHEAD_w9_adl_toilet$R9TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w9_adl_toilet$R9TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w10_adl_toilet','HRS.HRS-AHEAD-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local AHEAD w10,  echo=FALSE}
HRS_AHEAD_w10_adl_toilet <- opal.execute(o,'HRS_AHEAD_w10_adl_toilet')

vari <- HRS_AHEAD_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w10_adl_toilet[[2]])
ggplot(HRS_AHEAD_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w10,   echo=TRUE}
HRS_AHEAD_ds_w10 <- tibble(id=HRS_AHEAD_w10_adl_toilet$id)
HRS_AHEAD_ds_w10$adl_toilet <- car::recode(HRS_AHEAD_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w10$adl_toilet <- labelled(HRS_AHEAD_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w10,  echo=FALSE}
vari <- HRS_AHEAD_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w10,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w10$adl_toilet)
X<-table(HRS_AHEAD_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`

* Description: 
```{r assign AHEAD w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w11_adl_toilet','HRS.HRS-AHEAD-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local AHEAD w11,  echo=FALSE}
HRS_AHEAD_w11_adl_toilet <- opal.execute(o,'HRS_AHEAD_w11_adl_toilet')
vari <- HRS_AHEAD_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_AHEAD_w11_adl_toilet[[2]])
ggplot(HRS_AHEAD_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w11,   echo=TRUE}
HRS_AHEAD_ds_w11 <- tibble(id=HRS_AHEAD_w11_adl_toilet$id)
HRS_AHEAD_ds_w11$adl_toilet <- car::recode(HRS_AHEAD_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_AHEAD_ds_w11$adl_toilet <- labelled(HRS_AHEAD_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript AHEAD w11,  echo=FALSE}
vari <- HRS_AHEAD_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation AHEAD w11,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w11$adl_toilet)
X<-table(HRS_AHEAD_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



## The Children of the Depression (CODA) sub-sample

### Wave 4

#### Study-specific variable description

 


* Name: `R4TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign CODA w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w4_adl_toilet','HRS.HRS-CODA-w4', variables=list('R4TOILTA'), missings = TRUE)
```


```{r local CODA w4,  echo=FALSE}
HRS_CODA_w4_adl_toilet <- opal.execute(o,'HRS_CODA_w4_adl_toilet')
vari <- HRS_CODA_w4_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w4_adl_toilet[[2]])
ggplot(HRS_CODA_w4_adl_toilet, aes(x=factor(R4TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w4,   echo=TRUE}
HRS_CODA_ds_w4 <- tibble(id=HRS_CODA_w4_adl_toilet$id)
HRS_CODA_ds_w4$adl_toilet <- car::recode(HRS_CODA_w4_adl_toilet$R4TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w4$adl_toilet <- labelled(HRS_CODA_ds_w4$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w4,  echo=FALSE}
vari <- HRS_CODA_ds_w4$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w4$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w4, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w4,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w4$adl_toilet)
X<-table(HRS_CODA_w4_adl_toilet$R4TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w4_adl_toilet$R4TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

 


* Name: `R5TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign CODA w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w5_adl_toilet','HRS.HRS-CODA-w5', variables=list('R5TOILTA'), missings = TRUE)
```


```{r local CODA w5,  echo=FALSE}
HRS_CODA_w5_adl_toilet <- opal.execute(o,'HRS_CODA_w5_adl_toilet')
vari <- HRS_CODA_w5_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w5_adl_toilet[[2]])
ggplot(HRS_CODA_w5_adl_toilet, aes(x=factor(R5TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w5,   echo=TRUE}
HRS_CODA_ds_w5 <- tibble(id=HRS_CODA_w5_adl_toilet$id)
HRS_CODA_ds_w5$adl_toilet <- car::recode(HRS_CODA_w5_adl_toilet$R5TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w5$adl_toilet <- labelled(HRS_CODA_ds_w5$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w5,  echo=FALSE}
vari <- HRS_CODA_ds_w5$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w5$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w5, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w5,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w5$adl_toilet)
X<-table(HRS_CODA_w5_adl_toilet$R5TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w5_adl_toilet$R5TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

 


* Name: `R6TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign CODA w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w6_adl_toilet','HRS.HRS-CODA-w6', variables=list('R6TOILTA'), missings = TRUE)
```


```{r local CODA w6,  echo=FALSE}
HRS_CODA_w6_adl_toilet <- opal.execute(o,'HRS_CODA_w6_adl_toilet')
vari <- HRS_CODA_w6_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w6_adl_toilet[[2]])
ggplot(HRS_CODA_w6_adl_toilet, aes(x=factor(R6TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w6,   echo=TRUE}
HRS_CODA_ds_w6 <- tibble(id=HRS_CODA_w6_adl_toilet$id)
HRS_CODA_ds_w6$adl_toilet <- car::recode(HRS_CODA_w6_adl_toilet$R6TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w6$adl_toilet <- labelled(HRS_CODA_ds_w6$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w6,  echo=FALSE}
vari <- HRS_CODA_ds_w6$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w6$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w6, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w6,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w6$adl_toilet)
X<-table(HRS_CODA_w6_adl_toilet$R6TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w6_adl_toilet$R6TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

 


* Name: `R7TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign CODA w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w7_adl_toilet','HRS.HRS-CODA-w7', variables=list('R7TOILTA'), missings = TRUE)
```


```{r local CODA w7,  echo=FALSE}
HRS_CODA_w7_adl_toilet <- opal.execute(o,'HRS_CODA_w7_adl_toilet')
vari <- HRS_CODA_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w7_adl_toilet[[2]])
ggplot(HRS_CODA_w7_adl_toilet, aes(x=factor(R7TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w7,   echo=TRUE}
HRS_CODA_ds_w7 <- tibble(id=HRS_CODA_w7_adl_toilet$id)
HRS_CODA_ds_w7$adl_toilet <- car::recode(HRS_CODA_w7_adl_toilet$R7TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w7$adl_toilet <- labelled(HRS_CODA_ds_w7$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w7,  echo=FALSE}
vari <- HRS_CODA_ds_w7$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w7,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w7$adl_toilet)
X<-table(HRS_CODA_w7_adl_toilet$R7TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w7_adl_toilet$R7TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


* Name: `R8TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign CODA w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w8_adl_toilet','HRS.HRS-CODA-w8', variables=list('R8TOILTA'), missings = TRUE)
```


```{r local CODA w8,  echo=FALSE}
HRS_CODA_w8_adl_toilet <- opal.execute(o,'HRS_CODA_w8_adl_toilet')
vari <- HRS_CODA_w8_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w8_adl_toilet[[2]])
ggplot(HRS_CODA_w8_adl_toilet, aes(x=factor(R8TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w8,   echo=TRUE}
HRS_CODA_ds_w8 <- tibble(id=HRS_CODA_w8_adl_toilet$id)
HRS_CODA_ds_w8$adl_toilet <- car::recode(HRS_CODA_w8_adl_toilet$R8TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w8$adl_toilet <- labelled(HRS_CODA_ds_w8$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w8,  echo=FALSE}
vari <- HRS_CODA_ds_w8$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w8,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w8$adl_toilet)
X<-table(HRS_CODA_w8_adl_toilet$R8TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w8_adl_toilet$R8TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

 


* Name: `R9TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`

* Description: 
```{r assign CODA w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w9_adl_toilet','HRS.HRS-CODA-w9', variables=list('R9TOILTA'), missings = TRUE)
```


```{r local CODA w9,  echo=FALSE}
HRS_CODA_w9_adl_toilet <- opal.execute(o,'HRS_CODA_w9_adl_toilet')
vari <- HRS_CODA_w9_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w9_adl_toilet[[2]])
ggplot(HRS_CODA_w9_adl_toilet, aes(x=factor(R9TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w9,   echo=TRUE}
HRS_CODA_ds_w9 <- tibble(id=HRS_CODA_w9_adl_toilet$id)
HRS_CODA_ds_w9$adl_toilet <- car::recode(HRS_CODA_w9_adl_toilet$R9TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w9$adl_toilet <- labelled(HRS_CODA_ds_w9$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w9,  echo=FALSE}
vari <- HRS_CODA_ds_w9$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w9,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w9$adl_toilet)
X<-table(HRS_CODA_w9_adl_toilet$R9TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w9_adl_toilet$R9TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign CODA w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w10_adl_toilet','HRS.HRS-CODA-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local CODA w10,  echo=FALSE}
HRS_CODA_w10_adl_toilet <- opal.execute(o,'HRS_CODA_w10_adl_toilet')
vari <- HRS_CODA_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w10_adl_toilet[[2]])
ggplot(HRS_CODA_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w10,   echo=TRUE}
HRS_CODA_ds_w10 <- tibble(id=HRS_CODA_w10_adl_toilet$id)
HRS_CODA_ds_w10$adl_toilet <- car::recode(HRS_CODA_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w10$adl_toilet <- labelled(HRS_CODA_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w10,  echo=FALSE}
vari <- HRS_CODA_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w10,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w10$adl_toilet)
X<-table(HRS_CODA_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign CODA w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w11_adl_toilet','HRS.HRS-CODA-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local CODA w11,  echo=FALSE}
HRS_CODA_w11_adl_toilet <- opal.execute(o,'HRS_CODA_w11_adl_toilet')
vari <- HRS_CODA_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_CODA_w11_adl_toilet[[2]])
ggplot(HRS_CODA_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo CODA w11,   echo=TRUE}
HRS_CODA_ds_w11 <- tibble(id=HRS_CODA_w11_adl_toilet$id)
HRS_CODA_ds_w11$adl_toilet <- car::recode(HRS_CODA_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_CODA_ds_w11$adl_toilet <- labelled(HRS_CODA_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript CODA w11,  echo=FALSE}
vari <- HRS_CODA_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation CODA w11,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w11$adl_toilet)
X<-table(HRS_CODA_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



## The War Baby (WB) sub-sample

### Wave 4

#### Study-specific variable description

 


* Name: `R4TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign WB w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w4_adl_toilet','HRS.HRS-WB-w4', variables=list('R4TOILTA'), missings = TRUE)
```


```{r local WB w4,  echo=FALSE}
HRS_WB_w4_adl_toilet <- opal.execute(o,'HRS_WB_w4_adl_toilet')

vari <- HRS_WB_w4_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w4_adl_toilet[[2]])
ggplot(HRS_WB_w4_adl_toilet, aes(x=factor(R4TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w4,   echo=TRUE}
HRS_WB_ds_w4 <- tibble(id=HRS_WB_w4_adl_toilet$id)
HRS_WB_ds_w4$adl_toilet <- car::recode(HRS_WB_w4_adl_toilet$R4TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w4$adl_toilet <- labelled(HRS_WB_ds_w4$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w4,  echo=FALSE}
vari <- HRS_WB_ds_w4$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w4$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w4, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w4,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w4$adl_toilet)
X<-table(HRS_WB_w4_adl_toilet$R4TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w4_adl_toilet$R4TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

 


* Name: `R5TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign WB w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w5_adl_toilet','HRS.HRS-WB-w5', variables=list('R5TOILTA'), missings = TRUE)
```


```{r local WB w5,  echo=FALSE}
HRS_WB_w5_adl_toilet <- opal.execute(o,'HRS_WB_w5_adl_toilet')
vari <- HRS_WB_w5_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w5_adl_toilet[[2]])
ggplot(HRS_WB_w5_adl_toilet, aes(x=factor(R5TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w5,   echo=TRUE}
HRS_WB_ds_w5 <- tibble(id=HRS_WB_w5_adl_toilet$id)
HRS_WB_ds_w5$adl_toilet <- car::recode(HRS_WB_w5_adl_toilet$R5TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w5$adl_toilet <- labelled(HRS_WB_ds_w5$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w5,  echo=FALSE}
vari <- HRS_WB_ds_w5$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w5$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w5, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w5,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w5$adl_toilet)
X<-table(HRS_WB_w5_adl_toilet$R5TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w5_adl_toilet$R5TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

 


* Name: `R6TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign WB w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w6_adl_toilet','HRS.HRS-WB-w6', variables=list('R6TOILTA'), missings = TRUE)
```


```{r local WB w6,  echo=FALSE}
HRS_WB_w6_adl_toilet <- opal.execute(o,'HRS_WB_w6_adl_toilet')
vari <- HRS_WB_w6_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w6_adl_toilet[[2]])
ggplot(HRS_WB_w6_adl_toilet, aes(x=factor(R6TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w6,   echo=TRUE}
HRS_WB_ds_w6 <- tibble(id=HRS_WB_w6_adl_toilet$id)
HRS_WB_ds_w6$adl_toilet <- car::recode(HRS_WB_w6_adl_toilet$R6TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w6$adl_toilet <- labelled(HRS_WB_ds_w6$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w6,  echo=FALSE}
vari <- HRS_WB_ds_w6$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w6$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w6, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w6,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w6$adl_toilet)
X<-table(HRS_WB_w6_adl_toilet$R6TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w6_adl_toilet$R6TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

 


* Name: `R7TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign WB w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w7_adl_toilet','HRS.HRS-WB-w7', variables=list('R7TOILTA'), missings = TRUE)
```


```{r local WB w7,  echo=FALSE}
HRS_WB_w7_adl_toilet <- opal.execute(o,'HRS_WB_w7_adl_toilet')
vari <- HRS_WB_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w7_adl_toilet[[2]])
ggplot(HRS_WB_w7_adl_toilet, aes(x=factor(R7TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w7,   echo=TRUE}
HRS_WB_ds_w7 <- tibble(id=HRS_WB_w7_adl_toilet$id)
HRS_WB_ds_w7$adl_toilet <- car::recode(HRS_WB_w7_adl_toilet$R7TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w7$adl_toilet <- labelled(HRS_WB_ds_w7$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w7,  echo=FALSE}
vari <- HRS_WB_ds_w7$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_WB_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w7,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w7$adl_toilet)
X<-table(HRS_WB_w7_adl_toilet$R7TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w7_adl_toilet$R7TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


* Name: `R8TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign WB w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w8_adl_toilet','HRS.HRS-WB-w8', variables=list('R8TOILTA'), missings = TRUE)
```


```{r local WB w8,  echo=FALSE}
HRS_WB_w8_adl_toilet <- opal.execute(o,'HRS_WB_w8_adl_toilet')
vari <- HRS_WB_w8_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w8_adl_toilet[[2]])
ggplot(HRS_WB_w8_adl_toilet, aes(x=factor(R8TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w8,   echo=TRUE}
HRS_WB_ds_w8 <- tibble(id=HRS_WB_w8_adl_toilet$id)
HRS_WB_ds_w8$adl_toilet <- car::recode(HRS_WB_w8_adl_toilet$R8TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w8$adl_toilet <- labelled(HRS_WB_ds_w8$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w8,  echo=FALSE}
vari <- HRS_WB_ds_w8$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w8,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w8$adl_toilet)
X<-table(HRS_WB_w8_adl_toilet$R8TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w8_adl_toilet$R8TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

 


* Name: `R9TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign WB w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w9_adl_toilet','HRS.HRS-WB-w9', variables=list('R9TOILTA'), missings = TRUE)
```


```{r local WB w9,  echo=FALSE}
HRS_WB_w9_adl_toilet <- opal.execute(o,'HRS_WB_w9_adl_toilet')
vari <- HRS_WB_w9_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w9_adl_toilet[[2]])
ggplot(HRS_WB_w9_adl_toilet, aes(x=factor(R9TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w9,   echo=TRUE}
HRS_WB_ds_w9 <- tibble(id=HRS_WB_w9_adl_toilet$id)
HRS_WB_ds_w9$adl_toilet <- car::recode(HRS_WB_w9_adl_toilet$R9TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w9$adl_toilet <- labelled(HRS_WB_ds_w9$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w9,  echo=FALSE}
vari <- HRS_WB_ds_w9$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w9,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w9$adl_toilet)
X<-table(HRS_WB_w9_adl_toilet$R9TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w9_adl_toilet$R9TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign WB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w10_adl_toilet','HRS.HRS-WB-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local WB w10,  echo=FALSE}
HRS_WB_w10_adl_toilet <- opal.execute(o,'HRS_WB_w10_adl_toilet')
vari <- HRS_WB_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w10_adl_toilet[[2]])
ggplot(HRS_WB_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w10,   echo=TRUE}
HRS_WB_ds_w10 <- tibble(id=HRS_WB_w10_adl_toilet$id)
HRS_WB_ds_w10$adl_toilet <- car::recode(HRS_WB_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w10$adl_toilet <- labelled(HRS_WB_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w10,  echo=FALSE}
vari <- HRS_WB_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w10,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w10$adl_toilet)
X<-table(HRS_WB_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign WB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w11_adl_toilet','HRS.HRS-WB-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local WB w11,  echo=FALSE}
HRS_WB_w11_adl_toilet <- opal.execute(o,'HRS_WB_w11_adl_toilet')
vari <- HRS_WB_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_WB_w11_adl_toilet[[2]])
ggplot(HRS_WB_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo WB w11,   echo=TRUE}
HRS_WB_ds_w11 <- tibble(id=HRS_WB_w11_adl_toilet$id)
HRS_WB_ds_w11$adl_toilet <- car::recode(HRS_WB_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_WB_ds_w11$adl_toilet <- labelled(HRS_WB_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript WB w11,  echo=FALSE}
vari <- HRS_WB_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation WB w11,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w11$adl_toilet)
X<-table(HRS_WB_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



## The Early Baby Boomer (EBB) sub-sample

### Wave 7

#### Study-specific variable description

 


* Name: `R7TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign EBB w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w7_adl_toilet','HRS.HRS-EBB-w7', variables=list('R7TOILTA'), missings = TRUE)
```


```{r local EBB w7,  echo=FALSE}
HRS_EBB_w7_adl_toilet <- opal.execute(o,'HRS_EBB_w7_adl_toilet')

vari <- HRS_EBB_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_EBB_w7_adl_toilet[[2]])
ggplot(HRS_EBB_w7_adl_toilet, aes(x=factor(R7TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo EBB w7,   echo=TRUE}
HRS_EBB_ds_w7 <- tibble(id=HRS_EBB_w7_adl_toilet$id)
HRS_EBB_ds_w7$adl_toilet <- car::recode(HRS_EBB_w7_adl_toilet$R7TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_EBB_ds_w7$adl_toilet <- labelled(HRS_EBB_ds_w7$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript EBB w7,  echo=FALSE}
vari <- HRS_EBB_ds_w7$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w7$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w7, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation EBB w7,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w7$adl_toilet)
X<-table(HRS_EBB_w7_adl_toilet$R7TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w7_adl_toilet$R7TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

 


* Name: `R8TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign EBB w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w8_adl_toilet','HRS.HRS-EBB-w8', variables=list('R8TOILTA'), missings = TRUE)
```


```{r local EBB w8,  echo=FALSE}
HRS_EBB_w8_adl_toilet <- opal.execute(o,'HRS_EBB_w8_adl_toilet')
vari <- HRS_EBB_w7_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_EBB_w8_adl_toilet[[2]])
ggplot(HRS_EBB_w8_adl_toilet, aes(x=factor(R8TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo EBB w8,   echo=TRUE}
HRS_EBB_ds_w8 <- tibble(id=HRS_EBB_w8_adl_toilet$id)
HRS_EBB_ds_w8$adl_toilet <- car::recode(HRS_EBB_w8_adl_toilet$R8TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_EBB_ds_w8$adl_toilet <- labelled(HRS_EBB_ds_w8$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript EBB w8,  echo=FALSE}
vari <- HRS_EBB_ds_w8$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w8$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w8, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation EBB w8,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w8$adl_toilet)
X<-table(HRS_EBB_w8_adl_toilet$R8TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w8_adl_toilet$R8TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

 


* Name: `R9TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign EBB w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w9_adl_toilet','HRS.HRS-EBB-w9', variables=list('R9TOILTA'), missings = TRUE)
```


```{r local EBB w9,  echo=FALSE}
HRS_EBB_w9_adl_toilet <- opal.execute(o,'HRS_EBB_w9_adl_toilet')
vari <- HRS_EBB_w9_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_EBB_w9_adl_toilet[[2]])
ggplot(HRS_EBB_w9_adl_toilet, aes(x=factor(R9TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo EBB w9,   echo=TRUE}
HRS_EBB_ds_w9 <- tibble(id=HRS_EBB_w9_adl_toilet$id)
HRS_EBB_ds_w9$adl_toilet <- car::recode(HRS_EBB_w9_adl_toilet$R9TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_EBB_ds_w9$adl_toilet <- labelled(HRS_EBB_ds_w9$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript EBB w9,  echo=FALSE}
vari <- HRS_EBB_ds_w9$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w9$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w9, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation EBB w9,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w9$adl_toilet)
X<-table(HRS_EBB_w9_adl_toilet$R9TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w9_adl_toilet$R9TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign EBB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w10_adl_toilet','HRS.HRS-EBB-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local EBB w10,  echo=FALSE}
HRS_EBB_w10_adl_toilet <- opal.execute(o,'HRS_EBB_w10_adl_toilet')
vari <- HRS_EBB_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_EBB_w10_adl_toilet[[2]])
ggplot(HRS_EBB_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo EBB w10,   echo=TRUE}
HRS_EBB_ds_w10 <- tibble(id=HRS_EBB_w10_adl_toilet$id)
HRS_EBB_ds_w10$adl_toilet <- car::recode(HRS_EBB_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_EBB_ds_w10$adl_toilet <- labelled(HRS_EBB_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript EBB w10,  echo=FALSE}
vari <- HRS_EBB_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation EBB w10,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w10$adl_toilet)
X<-table(HRS_EBB_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`


* Description: 
```{r assign EBB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w11_adl_toilet','HRS.HRS-EBB-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local EBB w11,  echo=FALSE}
HRS_EBB_w11_adl_toilet <- opal.execute(o,'HRS_EBB_w11_adl_toilet')
vari <- HRS_EBB_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_EBB_w11_adl_toilet[[2]])
ggplot(HRS_EBB_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo EBB w11,   echo=TRUE}
HRS_EBB_ds_w11 <- tibble(id=HRS_EBB_w11_adl_toilet$id)
HRS_EBB_ds_w11$adl_toilet <- car::recode(HRS_EBB_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_EBB_ds_w11$adl_toilet <- labelled(HRS_EBB_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript EBB w11,  echo=FALSE}
vari <- HRS_EBB_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation EBB w11,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w11$adl_toilet)
X<-table(HRS_EBB_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



##The Mid Baby Boomer (MBB) sub-sample

### Wave 10

#### Study-specific variable description

 


* Name: `R10TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings 
    + `9 = Don't do`


* Description: 
```{r assign MBB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w10_adl_toilet','HRS.HRS-MBB-w10', variables=list('R10TOILTA'), missings = TRUE)
```


```{r local MBB w10,  echo=FALSE}
HRS_MBB_w10_adl_toilet <- opal.execute(o,'HRS_MBB_w10_adl_toilet')
vari <- HRS_MBB_w10_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_MBB_w10_adl_toilet[[2]])
ggplot(HRS_MBB_w10_adl_toilet, aes(x=factor(R10TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo MBB w10,   echo=TRUE}
HRS_MBB_ds_w10 <- tibble(id=HRS_MBB_w10_adl_toilet$id)
HRS_MBB_ds_w10$adl_toilet <- car::recode(HRS_MBB_w10_adl_toilet$R10TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_MBB_ds_w10$adl_toilet <- labelled(HRS_MBB_ds_w10$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript MBB w10,  echo=FALSE}
vari <- HRS_EBB_ds_w10$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

#Categorical_summary(var = HRS_MBB_ds_w10$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_MBB_ds_w10, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation MBB w10,  echo=FALSE}
AfterH <- table(HRS_MBB_ds_w10$adl_toilet)
X<-table(HRS_MBB_w10_adl_toilet$R10TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w10_adl_toilet$R10TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

 


* Name: `R11TOILTA`
* Label: `Some Diff-Using the toilet	`
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do` 
* Missings
    + `9 = Don't do`

* Description: 
```{r assign MBB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w11_adl_toilet','HRS.HRS-MBB-w11', variables=list('R11TOILTA'), missings = TRUE)
```


```{r local MBB w11,  echo=FALSE}
HRS_MBB_w11_adl_toilet <- opal.execute(o,'HRS_MBB_w11_adl_toilet')
vari <- HRS_MBB_w11_adl_toilet[[2]] # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
# SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

#Categorical_summary(HRS_MBB_w11_adl_toilet[[2]])
ggplot(HRS_MBB_w11_adl_toilet, aes(x=factor(R11TOILTA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 998`
* `NA into 999`

**R script:** 
```{r harmo MBB w11,   echo=TRUE}
HRS_MBB_ds_w11 <- tibble(id=HRS_MBB_w11_adl_toilet$id)
HRS_MBB_ds_w11$adl_toilet <- car::recode(HRS_MBB_w11_adl_toilet$R11TOILTA, "1 = '0';0 = '1';2 = '0';9 = '998'; NA='999'")
HRS_MBB_ds_w11$adl_toilet <- labelled(HRS_MBB_ds_w11$adl_toilet, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

###### Statistical description of the new harmonised variable
```{r descript MBB w11,  echo=FALSE}
vari <- HRS_EBB_ds_w11$adl_toilet # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_MBB_ds_w11$adl_toilet, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_MBB_ds_w11, aes(x=factor(adl_toilet))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty using the toilet") + ylab("Frequency")
```

###### Validation
```{r crosstabulation MBB w11,  echo=FALSE}
AfterH <- table(HRS_MBB_ds_w11$adl_toilet)
X<-table(HRS_MBB_w11_adl_toilet$R11TOILTA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w11_adl_toilet$R11TOILTA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2->0","0->1","NA->999") 
kable(C)
```

 
 




<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE,  eval=FALSE}
HRS_m_ds_hrs_w1  <- HRS_ds_hrs_w1  <- HRS_HRS_ds_w1
HRS_m_ds_hrs_w2  <- HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
HRS_m_ds_hrs_w3  <- HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
HRS_m_ds_hrs_w4  <- HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
HRS_m_ds_hrs_w5  <- HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
HRS_m_ds_hrs_w6  <- HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
HRS_m_ds_hrs_w7  <- HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
HRS_m_ds_hrs_w8  <- HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
HRS_m_ds_hrs_w9  <- HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11 <- HRS_HRS_ds_w11

HRS_m_ds_ahead_w2  <- HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
HRS_m_ds_ahead_w3  <- HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
HRS_m_ds_ahead_w4  <- HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
HRS_m_ds_ahead_w5  <- HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
HRS_m_ds_ahead_w6  <- HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
HRS_m_ds_ahead_w7  <- HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
HRS_m_ds_ahead_w8  <- HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
HRS_m_ds_ahead_w9  <- HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11

HRS_m_ds_coda_w4  <- HRS_ds_coda_w4  <- HRS_CODA_ds_w4
HRS_m_ds_coda_w5  <- HRS_ds_coda_w5  <- HRS_CODA_ds_w5
HRS_m_ds_coda_w6  <- HRS_ds_coda_w6  <- HRS_CODA_ds_w6
HRS_m_ds_coda_w7  <- HRS_ds_coda_w7  <- HRS_CODA_ds_w7
HRS_m_ds_coda_w8  <- HRS_ds_coda_w8  <- HRS_CODA_ds_w8
HRS_m_ds_coda_w9  <- HRS_ds_coda_w9  <- HRS_CODA_ds_w9
HRS_m_ds_coda_w10 <- HRS_ds_coda_w10 <- HRS_CODA_ds_w10
HRS_m_ds_coda_w11 <- HRS_ds_coda_w11 <- HRS_CODA_ds_w11

HRS_m_ds_wb_w4  <- HRS_ds_wb_w4  <- HRS_WB_ds_w4
HRS_m_ds_wb_w5  <- HRS_ds_wb_w5  <- HRS_WB_ds_w5
HRS_m_ds_wb_w6  <- HRS_ds_wb_w6  <- HRS_WB_ds_w6
HRS_m_ds_wb_w7  <- HRS_ds_wb_w7  <- HRS_WB_ds_w7
HRS_m_ds_wb_w8  <- HRS_ds_wb_w8  <- HRS_WB_ds_w8
HRS_m_ds_wb_w9  <- HRS_ds_wb_w9  <- HRS_WB_ds_w9
HRS_m_ds_wb_w10 <- HRS_ds_wb_w10 <- HRS_WB_ds_w10
HRS_m_ds_wb_w11 <- HRS_ds_wb_w11 <- HRS_WB_ds_w11

HRS_m_ds_ebb_w7  <- HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
HRS_m_ds_ebb_w8  <- HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
HRS_m_ds_ebb_w9  <- HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11 <- HRS_EBB_ds_w11

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11 <- HRS_MBB_ds_w11

l.hrs <- list(HRS_ds_hrs_w1 = HRS_ds_hrs_w1 , HRS_ds_hrs_w2 = HRS_ds_hrs_w2 ,HRS_ds_hrs_w3 = HRS_ds_hrs_w3 ,HRS_ds_hrs_w4 = HRS_ds_hrs_w4 ,
HRS_ds_hrs_w5 = HRS_ds_hrs_w5 ,HRS_ds_hrs_w6 = HRS_ds_hrs_w6 ,HRS_ds_hrs_w7 = HRS_ds_hrs_w7 ,HRS_ds_hrs_w8 = HRS_ds_hrs_w8 ,
HRS_ds_hrs_w9 = HRS_ds_hrs_w9 ,HRS_ds_hrs_w10 = HRS_ds_hrs_w10 ,HRS_ds_hrs_w11 = HRS_ds_hrs_w11 ,HRS_ds_ahead_w2 = HRS_ds_ahead_w2 ,
HRS_ds_ahead_w3 = HRS_ds_ahead_w3 ,HRS_ds_ahead_w4 = HRS_ds_ahead_w4 ,HRS_ds_ahead_w5 = HRS_ds_ahead_w5 ,HRS_ds_ahead_w6 = HRS_ds_ahead_w6 ,
HRS_ds_ahead_w7 = HRS_ds_ahead_w7 ,HRS_ds_ahead_w8 = HRS_ds_ahead_w8 ,HRS_ds_ahead_w9 = HRS_ds_ahead_w9 ,HRS_ds_ahead_w10 = HRS_ds_ahead_w10 ,
HRS_ds_ahead_w11 = HRS_ds_ahead_w11 ,HRS_ds_coda_w4 = HRS_ds_coda_w4 ,HRS_ds_coda_w5 = HRS_ds_coda_w5 ,HRS_ds_coda_w6 = HRS_ds_coda_w6 ,
HRS_ds_coda_w7 = HRS_ds_coda_w7 ,HRS_ds_coda_w8 = HRS_ds_coda_w8 ,HRS_ds_coda_w9 = HRS_ds_coda_w9 ,HRS_ds_coda_w10 = HRS_ds_coda_w10 ,
HRS_ds_coda_w11 = HRS_ds_coda_w11 ,HRS_ds_wb_w4 = HRS_ds_wb_w4 ,HRS_ds_wb_w5 = HRS_ds_wb_w5 ,HRS_ds_wb_w6 = HRS_ds_wb_w6 ,
HRS_ds_wb_w7 = HRS_ds_wb_w7 ,HRS_ds_wb_w8 = HRS_ds_wb_w8 ,HRS_ds_wb_w9 = HRS_ds_wb_w9 ,HRS_ds_wb_w10 = HRS_ds_wb_w10 ,
HRS_ds_wb_w11 = HRS_ds_wb_w11 ,HRS_ds_ebb_w7 = HRS_ds_ebb_w7 ,HRS_ds_ebb_w8 = HRS_ds_ebb_w8 ,HRS_ds_ebb_w9 = HRS_ds_ebb_w9 ,
HRS_ds_ebb_w10 = HRS_ds_ebb_w10 ,HRS_ds_ebb_w11 = HRS_ds_ebb_w11 ,HRS_ds_mbb_w10 = HRS_ds_mbb_w10 ,HRS_ds_mbb_w11 = HRS_ds_mbb_w11)

m.hrs <- list(HRS_m_ds_hrs_w1 = HRS_m_ds_hrs_w1 , HRS_m_ds_hrs_w2 = HRS_m_ds_hrs_w2 ,HRS_m_ds_hrs_w3 = HRS_m_ds_hrs_w3 ,HRS_m_ds_hrs_w4 = HRS_m_ds_hrs_w4 ,
HRS_m_ds_hrs_w5 = HRS_m_ds_hrs_w5 ,HRS_m_ds_hrs_w6 = HRS_m_ds_hrs_w6 ,HRS_m_ds_hrs_w7 = HRS_m_ds_hrs_w7 ,HRS_m_ds_hrs_w8 = HRS_m_ds_hrs_w8 ,
HRS_m_ds_hrs_w9 = HRS_m_ds_hrs_w9 ,HRS_m_ds_hrs_w10 = HRS_m_ds_hrs_w10 ,HRS_m_ds_hrs_w11 = HRS_m_ds_hrs_w11 ,HRS_m_ds_ahead_w2 = HRS_m_ds_ahead_w2 ,
HRS_m_ds_ahead_w3 = HRS_m_ds_ahead_w3 ,HRS_m_ds_ahead_w4 = HRS_m_ds_ahead_w4 ,HRS_m_ds_ahead_w5 = HRS_m_ds_ahead_w5 ,HRS_m_ds_ahead_w6 = HRS_m_ds_ahead_w6 ,
HRS_m_ds_ahead_w7 = HRS_m_ds_ahead_w7 ,HRS_m_ds_ahead_w8 = HRS_m_ds_ahead_w8 ,HRS_m_ds_ahead_w9 = HRS_m_ds_ahead_w9 ,HRS_m_ds_ahead_w10 = HRS_m_ds_ahead_w10 ,
HRS_m_ds_ahead_w11 = HRS_m_ds_ahead_w11 ,HRS_m_ds_coda_w4 = HRS_m_ds_coda_w4 ,HRS_m_ds_coda_w5 = HRS_m_ds_coda_w5 ,HRS_m_ds_coda_w6 = HRS_m_ds_coda_w6 ,
HRS_m_ds_coda_w7 = HRS_m_ds_coda_w7 ,HRS_m_ds_coda_w8 = HRS_m_ds_coda_w8 ,HRS_m_ds_coda_w9 = HRS_m_ds_coda_w9 ,HRS_m_ds_coda_w10 = HRS_m_ds_coda_w10 ,
HRS_m_ds_coda_w11 = HRS_m_ds_coda_w11 ,HRS_m_ds_wb_w4 = HRS_m_ds_wb_w4 ,HRS_m_ds_wb_w5 = HRS_m_ds_wb_w5 ,HRS_m_ds_wb_w6 = HRS_m_ds_wb_w6 ,
HRS_m_ds_wb_w7 = HRS_m_ds_wb_w7 ,HRS_m_ds_wb_w8 = HRS_m_ds_wb_w8 ,HRS_m_ds_wb_w9 = HRS_m_ds_wb_w9 ,HRS_m_ds_wb_w10 = HRS_m_ds_wb_w10 ,
HRS_m_ds_wb_w11 = HRS_m_ds_wb_w11 ,HRS_m_ds_ebb_w7 = HRS_m_ds_ebb_w7 ,HRS_m_ds_ebb_w8 = HRS_m_ds_ebb_w8 ,HRS_m_ds_ebb_w9 = HRS_m_ds_ebb_w9 ,
HRS_m_ds_ebb_w10 = HRS_m_ds_ebb_w10 ,HRS_m_ds_ebb_w11 = HRS_m_ds_ebb_w11 ,HRS_m_ds_mbb_w10 = HRS_m_ds_mbb_w10 ,HRS_m_ds_mbb_w11 = HRS_m_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- label(m.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hrs[[i]][[2]] <- car::recode(m.hrs[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hrs[[i]][[2]] <- labelled(m.hrs[[i]][[2]], labels = c(Yes=0, No=1))

  if (i!=1){
    nl <- names(l.hrs[i])
    opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

    ml <- names(m.hrs[i])
    opal.assign.data(o, ml , m.hrs[[i]])
    #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  
  }
}

```



```{r save, echo=FALSE}
HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
HRS_ds_hrs_w11 <- HRS_HRS_ds_w11

HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11

HRS_ds_coda_w4  <- HRS_CODA_ds_w4
HRS_ds_coda_w5  <- HRS_CODA_ds_w5
HRS_ds_coda_w6  <- HRS_CODA_ds_w6
HRS_ds_coda_w7  <- HRS_CODA_ds_w7
HRS_ds_coda_w8  <- HRS_CODA_ds_w8
HRS_ds_coda_w9  <- HRS_CODA_ds_w9
HRS_ds_coda_w10 <- HRS_CODA_ds_w10
HRS_ds_coda_w11 <- HRS_CODA_ds_w11

HRS_ds_wb_w4  <- HRS_WB_ds_w4
HRS_ds_wb_w5  <- HRS_WB_ds_w5
HRS_ds_wb_w6  <- HRS_WB_ds_w6
HRS_ds_wb_w7  <- HRS_WB_ds_w7
HRS_ds_wb_w8  <- HRS_WB_ds_w8
HRS_ds_wb_w9 <-  HRS_WB_ds_w9
HRS_ds_wb_w10 <- HRS_WB_ds_w10
HRS_ds_wb_w11 <- HRS_WB_ds_w11

HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
HRS_ds_ebb_w11 <- HRS_EBB_ds_w11

HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
HRS_ds_mbb_w11 <- HRS_MBB_ds_w11

l.hrs <- list( hrs_w2 = HRS_ds_hrs_w2 , hrs_w3 = HRS_ds_hrs_w3 , hrs_w4 = HRS_ds_hrs_w4 ,
 hrs_w5 = HRS_ds_hrs_w5 , hrs_w6 = HRS_ds_hrs_w6 , hrs_w7 = HRS_ds_hrs_w7 , hrs_w8 = HRS_ds_hrs_w8 ,
 hrs_w9 = HRS_ds_hrs_w9 , hrs_w10 = HRS_ds_hrs_w10 , hrs_w11 = HRS_ds_hrs_w11 , ahead_w2 = HRS_ds_ahead_w2 ,
 ahead_w3 = HRS_ds_ahead_w3 , ahead_w4 = HRS_ds_ahead_w4 , ahead_w5 = HRS_ds_ahead_w5 , ahead_w6 = HRS_ds_ahead_w6 ,
 ahead_w7 = HRS_ds_ahead_w7 , ahead_w8 = HRS_ds_ahead_w8 , ahead_w9 = HRS_ds_ahead_w9 , ahead_w10 = HRS_ds_ahead_w10 ,
 ahead_w11 = HRS_ds_ahead_w11 , coda_w4 = HRS_ds_coda_w4 , coda_w5 = HRS_ds_coda_w5 , coda_w6 = HRS_ds_coda_w6 ,
 coda_w7 = HRS_ds_coda_w7 , coda_w8 = HRS_ds_coda_w8 ,  coda_w9 = HRS_ds_coda_w9 ,  coda_w10 = HRS_ds_coda_w10 ,
coda_w11 = HRS_ds_coda_w11 ,  wb_w4 = HRS_ds_wb_w4 ,  wb_w5 = HRS_ds_wb_w5 ,  wb_w6 = HRS_ds_wb_w6 ,
 wb_w7 = HRS_ds_wb_w7 ,  wb_w8 = HRS_ds_wb_w8 ,  wb_w9 = HRS_ds_wb_w9 ,  wb_w10 = HRS_ds_wb_w10 ,
 wb_w11 = HRS_ds_wb_w11 ,  ebb_w7 = HRS_ds_ebb_w7 ,  ebb_w8 = HRS_ds_ebb_w8 ,  ebb_w9 = HRS_ds_ebb_w9 ,
 ebb_w10 = HRS_ds_ebb_w10 ,  ebb_w11 = HRS_ds_ebb_w11 ,  mbb_w10 = HRS_ds_mbb_w10 ,  mbb_w11 = HRS_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.

    nl <- names(l.hrs[i])
    #opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  
    adl_toilet <- l.hrs[[i]]
    save(adl_toilet, file = paste0(datafolder, "/", nl, "/adl_toilet.RData" ))
}


```

# Quality control


'2.Cant do ' was considered as maximum difficulty

### Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

```{r summ,  echo=FALSE, eval=FALSE}

# Table HRS
t.hrs <- frq(l.hrs[[3]][2])[[1]][,c(1,2)] 
for (i in 1:11){
  t.hrs[2+i] <- frq(l.hrs[[i]][2])[[1]][,4] 
}
t.hrs[13,] <- c("n", "sample size", 
             length(l.hrs[[1]][[2]]), length(l.hrs[[2]][[2]]), length(l.hrs[[3]][[2]]),
             length(l.hrs[[4]][[2]]), length(l.hrs[[5]][[2]]), length(l.hrs[[6]][[2]]),     
             length(l.hrs[[7]][[2]]), length(l.hrs[[8]][[2]]), length(l.hrs[[9]][[2]]),
             length(l.hrs[[10]][[2]]), length(l.hrs[[11]][[2]]))
names(t.hrs)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.hrs)
  

# Table AHEAD
t.ahead <- frq(l.hrs[[12]][2])[[1]][,c(1,2)] 
for (i in 1:10){
  t.ahead[2+i] <- frq(l.hrs[[i+11]][2])[[1]][,4] 
}
t.ahead[13,] <- c("n", "sample size", 
             length(l.hrs[[12]][[2]]), length(l.hrs[[13]][[2]]), length(l.hrs[[14]][[2]]),
             length(l.hrs[[15]][[2]]), length(l.hrs[[16]][[2]]), length(l.hrs[[17]][[2]]),     
             length(l.hrs[[18]][[2]]), length(l.hrs[[19]][[2]]), length(l.hrs[[20]][[2]]),
             length(l.hrs[[21]][[2]]))
names(t.ahead)<-c("val", "label", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.ahead)



# Table CODA
t.coda <- frq(l.hrs[[22]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.coda[2+i] <- frq(l.hrs[[21+i]][2])[[1]][,4] 
}
t.coda[13,] <- c("n", "sample size", 
             length(l.hrs[[22]][[2]]), length(l.hrs[[23]][[2]]), length(l.hrs[[24]][[2]]),
             length(l.hrs[[25]][[2]]), length(l.hrs[[26]][[2]]), length(l.hrs[[27]][[2]]),     
             length(l.hrs[[28]][[2]]), length(l.hrs[[29]][[2]]))
names(t.coda)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.coda)



# Table WB
t.wb <- frq(l.hrs[[30]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.wb[2+i] <- frq(l.hrs[[31+i]][2])[[1]][,4] 
}
t.wb[13,] <- c("n", "sample size", 
             length(l.hrs[[30]][[2]]), length(l.hrs[[31]][[2]]), length(l.hrs[[32]][[2]]),
             length(l.hrs[[33]][[2]]), length(l.hrs[[34]][[2]]), length(l.hrs[[35]][[2]]),     
             length(l.hrs[[36]][[2]]), length(l.hrs[[37]][[2]]))
names(t.wb)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.wb)



# Table EBB
t.ebb <- frq(l.hrs[[38]][2])[[1]][,c(1,2)] 
for (i in 1:5){
  t.ebb[2+i] <- frq(l.hrs[[37+i]][2])[[1]][,4] 
}
t.ebb[13,] <- c("n", "sample size", 
             length(l.hrs[[38]][[2]]), length(l.hrs[[39]][[2]]), length(l.hrs[[40]][[2]]),
             length(l.hrs[[41]][[2]]), length(l.hrs[[42]][[2]]))
names(t.ebb)<-c("val", "label", "w7", "w8", "w9", "w10", "w11")
kable(t.ebb)



# Table MBB
t.mbb <- frq(l.hrs[[43]][2])[[1]][,c(1,2)] 
for (i in 1:2){
  t.mbb[2+i] <- frq(l.hrs[[42+i]][2])[[1]][,4] 
}
t.mbb[13,] <- c("n", "sample size", length(l.hrs[[43]][[2]]), length(l.hrs[[44]][[2]]))
names(t.mbb)<-c("val", "label", "w10", "w11")
kable(t.mbb)

```


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```




