---
title: "IADLs - Doing housework"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/iadl_housewkDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/iadl_housewkDS.R')
```


<!-- ########################################################## --> 


# Data process


## HRS

### Wave 1 

These limitation questions are not asked in wave 1.


### Wave 2

#### Study-specific variable description

| **Name** | `r2limhwrk` |
|-|-|
| **Label** | `r2limhwrk:w2 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w2, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w2','HRS.HRS_b_HRS', variables=list('r2limhwrk'), missings = TRUE)
HRS_hrs_w2 <- opal.execute(o,'HRS_hrs_w2')
```

```{r local hrs w2, echo=F}
vbl <- HRS_hrs_w2$r2limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2, aes(x=factor(r2limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`
* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2$id)
HRS_ds_hrs_w2$iadl_housewk <- car::recode(HRS_hrs_w2$r2limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w2, echo=F}
vbl <- HRS_ds_hrs_w2$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w2, echo=F}
```



### Wave 3 

#### Study-specific variable description

| **Name** | `r3limhwrk` |
|-|-|
| **Label** | `r3limhwrk:w3 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w3, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w3','HRS.HRS_b_HRS', variables=list('r3limhwrk'), missings = TRUE)
HRS_hrs_w3 <- opal.execute(o,'HRS_hrs_w3')
```

```{r local hrs w3, echo=F}
vbl <- HRS_hrs_w3$r3limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3, aes(x=factor(r3limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3$id)
HRS_ds_hrs_w3$iadl_housewk <- car::recode(HRS_hrs_w3$r3limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w3, echo=F}
vbl <- HRS_ds_hrs_w3$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w3, echo=F}
```



### Wave 4

#### Study-specific variable description

| **Name** | `r4limhwrk` |
|-|-|
| **Label** | `r4limhwrk:w4 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4','HRS.HRS_b_HRS', variables=list('r4limhwrk'), missings = TRUE)
HRS_hrs_w4 <- opal.execute(o,'HRS_hrs_w4')
```

```{r local hrs w4, echo=F}
vbl <- HRS_hrs_w4$r4limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4, aes(x=factor(r4limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4$id)
HRS_ds_hrs_w4$iadl_housewk <- car::recode(HRS_hrs_w4$r4limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w4, echo=F}
vbl <- HRS_ds_hrs_w4$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `r5limhwrk` |
|-|-|
| **Label** | `r5limhwrk:w5 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5','HRS.HRS_b_HRS', variables=list('r5limhwrk'), missings = TRUE)
HRS_hrs_w5 <- opal.execute(o,'HRS_hrs_w5')
```

```{r local hrs w5, echo=F}
vbl <- HRS_hrs_w5$r5limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5, aes(x=factor(r5limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5$id)
HRS_ds_hrs_w5$iadl_housewk <- car::recode(HRS_hrs_w5$r5limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w5, echo=F}
vbl <- HRS_ds_hrs_w5$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `r6limhwrk` |
|-|-|
| **Label** | `r6limhwrk:w6 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6','HRS.HRS_b_HRS', variables=list('r6limhwrk'), missings = TRUE)
HRS_hrs_w6 <- opal.execute(o,'HRS_hrs_w6')
```

```{r local hrs w6, echo=F}
vbl <- HRS_hrs_w6$r6limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6, aes(x=factor(r6limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6$id)
HRS_ds_hrs_w6$iadl_housewk <- car::recode(HRS_hrs_w6$r6limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w6, echo=F}
vbl <- HRS_ds_hrs_w6$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `r7limhwrk` |
|-|-|
| **Label** | `r7limhwrk:w7 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7','HRS.HRS_b_HRS', variables=list('r7limhwrk'), missings = TRUE)
HRS_hrs_w7 <- opal.execute(o,'HRS_hrs_w7')
```

```{r local hrs w7, echo=F}
vbl <- HRS_hrs_w7$r7limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7, aes(x=factor(r7limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7$id)
HRS_ds_hrs_w7$iadl_housewk <- car::recode(HRS_hrs_w7$r7limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w7, echo=F}
vbl <- HRS_ds_hrs_w7$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w7, echo=F}






```





### Wave 8

#### Study-specific variable description

| **Name** | `r8limhwrk` |
|-|-|
| **Label** | `r8limhwrk:w8 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8','HRS.HRS_b_HRS', variables=list('r8limhwrk'), missings = TRUE)
HRS_hrs_w8 <- opal.execute(o,'HRS_hrs_w8')
```

```{r local hrs w8, echo=F}
vbl <- HRS_hrs_w8$r8limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8, aes(x=factor(r8limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8$id)
HRS_ds_hrs_w8$iadl_housewk <- car::recode(HRS_hrs_w8$r8limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w8, echo=F}
vbl <- HRS_ds_hrs_w8$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w8, echo=F}






```




### Wave 9

#### Study-specific variable description

| **Name** | `r9limhwrk` |
|-|-|
| **Label** | `r9limhwrk:w9 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9','HRS.HRS_b_HRS', variables=list('r9limhwrk'), missings = TRUE)
HRS_hrs_w9 <- opal.execute(o,'HRS_hrs_w9')
```

```{r local hrs w9, echo=F}
vbl <- HRS_hrs_w9$r9limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9, aes(x=factor(r9limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9$id)
HRS_ds_hrs_w9$iadl_housewk <- car::recode(HRS_hrs_w9$r9limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w9, echo=F}
vbl <- HRS_ds_hrs_w9$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w9, echo=F}






```




### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10','HRS.HRS_b_HRS', variables=list('r10limhwrk'), missings = TRUE)
HRS_hrs_w10 <- opal.execute(o,'HRS_hrs_w10')
```

```{r local hrs w10, echo=F}
vbl <- HRS_hrs_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10$id)
HRS_ds_hrs_w10$iadl_housewk <- car::recode(HRS_hrs_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w10, echo=F}
vbl <- HRS_ds_hrs_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w10, echo=F}






```




### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_HRS` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign hrs w11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11','HRS.HRS_b_HRS', variables=list('r11limhwrk'), missings = TRUE)
HRS_hrs_w11 <- opal.execute(o,'HRS_hrs_w11')
```

```{r local hrs w11, echo=F}
vbl <- HRS_hrs_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_hrs_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo hrs w11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11$id)
HRS_ds_hrs_w11$iadl_housewk <- car::recode(HRS_hrs_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript hrs w11, echo=F}
vbl <- HRS_ds_hrs_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation hrs w11, echo=F}






```





## AHEAD

### Wave 2

Limitation questions are not asked to the AHEAD cohorts in waves 2 and 3.


### Wave 3 

Limitation questions are not asked to the AHEAD cohorts in waves 2 and 3.





### Wave 4

#### Study-specific variable description

| **Name** | `r4limhwrk` |
|-|-|
| **Label** | `r4limhwrk:w4 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4','HRS.HRS_b_AHEAD', variables=list('r4limhwrk'), missings = TRUE)
HRS_ahead_w4 <- opal.execute(o,'HRS_ahead_w4')
```

```{r local ahead w4, echo=F}
vbl <- HRS_ahead_w4$r4limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4, aes(x=factor(r4limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4$id)
HRS_ds_ahead_w4$iadl_housewk <- car::recode(HRS_ahead_w4$r4limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w4, echo=F}
vbl <- HRS_ds_ahead_w4$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `r5limhwrk` |
|-|-|
| **Label** | `r5limhwrk:w5 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5','HRS.HRS_b_AHEAD', variables=list('r5limhwrk'), missings = TRUE)
HRS_ahead_w5 <- opal.execute(o,'HRS_ahead_w5')
```

```{r local ahead w5, echo=F}
vbl <- HRS_ahead_w5$r5limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5, aes(x=factor(r5limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5$id)
HRS_ds_ahead_w5$iadl_housewk <- car::recode(HRS_ahead_w5$r5limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w5, echo=F}
vbl <- HRS_ds_ahead_w5$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w5, echo=F}
```




### Wave 6

#### Study-specific variable description

| **Name** | `r6limhwrk` |
|-|-|
| **Label** | `r6limhwrk:w6 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6','HRS.HRS_b_AHEAD', variables=list('r6limhwrk'), missings = TRUE)
HRS_ahead_w6 <- opal.execute(o,'HRS_ahead_w6')
```

```{r local ahead w6, echo=F}
vbl <- HRS_ahead_w6$r6limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6, aes(x=factor(r6limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6$id)
HRS_ds_ahead_w6$iadl_housewk <- car::recode(HRS_ahead_w6$r6limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w6, echo=F}
vbl <- HRS_ds_ahead_w6$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `r7limhwrk` |
|-|-|
| **Label** | `r7limhwrk:w7 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7','HRS.HRS_b_AHEAD', variables=list('r7limhwrk'), missings = TRUE)
HRS_ahead_w7 <- opal.execute(o,'HRS_ahead_w7')
```

```{r local ahead w7, echo=F}
vbl <- HRS_ahead_w7$r7limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7, aes(x=factor(r7limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7$id)
HRS_ds_ahead_w7$iadl_housewk <- car::recode(HRS_ahead_w7$r7limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w7, echo=F}
vbl <- HRS_ds_ahead_w7$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w7, echo=F}






```





### Wave 8

#### Study-specific variable description

| **Name** | `r8limhwrk` |
|-|-|
| **Label** | `r8limhwrk:w8 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8','HRS.HRS_b_AHEAD', variables=list('r8limhwrk'), missings = TRUE)
HRS_ahead_w8 <- opal.execute(o,'HRS_ahead_w8')
```

```{r local ahead w8, echo=F}
vbl <- HRS_ahead_w8$r8limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8, aes(x=factor(r8limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8$id)
HRS_ds_ahead_w8$iadl_housewk <- car::recode(HRS_ahead_w8$r8limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w8, echo=F}
vbl <- HRS_ds_ahead_w8$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w8, echo=F}






```





### Wave 9

#### Study-specific variable description

| **Name** | `r9limhwrk` |
|-|-|
| **Label** | `r9limhwrk:w9 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9','HRS.HRS_b_AHEAD', variables=list('r9limhwrk'), missings = TRUE)
HRS_ahead_w9 <- opal.execute(o,'HRS_ahead_w9')
```

```{r local ahead w9, echo=F}
vbl <- HRS_ahead_w9$r9limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9, aes(x=factor(r9limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9$id)
HRS_ds_ahead_w9$iadl_housewk <- car::recode(HRS_ahead_w9$r9limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w9, echo=F}
vbl <- HRS_ds_ahead_w9$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w9, echo=F}






```




### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10','HRS.HRS_b_AHEAD', variables=list('r10limhwrk'), missings = TRUE)
HRS_ahead_w10 <- opal.execute(o,'HRS_ahead_w10')
```

```{r local ahead w10, echo=F}
vbl <- HRS_ahead_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10$id)
HRS_ds_ahead_w10$iadl_housewk <- car::recode(HRS_ahead_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w10, echo=F}
vbl <- HRS_ds_ahead_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w10, echo=F}






```




### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_AHEAD` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ahead w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11','HRS.HRS_b_AHEAD', variables=list('r11limhwrk'), missings = TRUE)
HRS_ahead_w11 <- opal.execute(o,'HRS_ahead_w11')
```

```{r local ahead w11, echo=F}
vbl <- HRS_ahead_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ahead_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ahead w11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11$id)
HRS_ds_ahead_w11$iadl_housewk <- car::recode(HRS_ahead_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ahead w11, echo=F}
vbl <- HRS_ds_ahead_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ahead w11, echo=F}






```








## CODA

### Wave 4

#### Study-specific variable description

| **Name** | `r4limhwrk` |
|-|-|
| **Label** | `r4limhwrk:w4 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4','HRS.HRS_b_CODA', variables=list('r4limhwrk'), missings = TRUE)
HRS_coda_w4 <- opal.execute(o,'HRS_coda_w4')
```

```{r local coda w4, echo=F}
vbl <- HRS_coda_w4$r4limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4, aes(x=factor(r4limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4$id)
HRS_ds_coda_w4$iadl_housewk <- car::recode(HRS_coda_w4$r4limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w4, echo=F}
vbl <- HRS_ds_coda_w4$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `r5limhwrk` |
|-|-|
| **Label** | `r5limhwrk:w5 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5','HRS.HRS_b_CODA', variables=list('r5limhwrk'), missings = TRUE)
HRS_coda_w5 <- opal.execute(o,'HRS_coda_w5')
```

```{r local coda w5, echo=F}
vbl <- HRS_coda_w5$r5limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5, aes(x=factor(r5limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5$id)
HRS_ds_coda_w5$iadl_housewk <- car::recode(HRS_coda_w5$r5limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w5, echo=F}
vbl <- HRS_ds_coda_w5$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w5, echo=F}
```





### Wave 6

#### Study-specific variable description

| **Name** | `r6limhwrk` |
|-|-|
| **Label** | `r6limhwrk:w6 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6','HRS.HRS_b_CODA', variables=list('r6limhwrk'), missings = TRUE)
HRS_coda_w6 <- opal.execute(o,'HRS_coda_w6')
```

```{r local coda w6, echo=F}
vbl <- HRS_coda_w6$r6limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6, aes(x=factor(r6limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6$id)
HRS_ds_coda_w6$iadl_housewk <- car::recode(HRS_coda_w6$r6limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w6, echo=F}
vbl <- HRS_ds_coda_w6$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w6, echo=F}
```






### Wave 7

#### Study-specific variable description

| **Name** | `r7limhwrk` |
|-|-|
| **Label** | `r7limhwrk:w7 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7','HRS.HRS_b_CODA', variables=list('r7limhwrk'), missings = TRUE)
HRS_coda_w7 <- opal.execute(o,'HRS_coda_w7')
```

```{r local coda w7, echo=F}
vbl <- HRS_coda_w7$r7limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7, aes(x=factor(r7limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7$id)
HRS_ds_coda_w7$iadl_housewk <- car::recode(HRS_coda_w7$r7limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w7, echo=F}
vbl <- HRS_ds_coda_w7$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w7, echo=F}






```





### Wave 8

#### Study-specific variable description

| **Name** | `r8limhwrk` |
|-|-|
| **Label** | `r8limhwrk:w8 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8','HRS.HRS_b_CODA', variables=list('r8limhwrk'), missings = TRUE)
HRS_coda_w8 <- opal.execute(o,'HRS_coda_w8')
```

```{r local coda w8, echo=F}
vbl <- HRS_coda_w8$r8limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8, aes(x=factor(r8limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8$id)
HRS_ds_coda_w8$iadl_housewk <- car::recode(HRS_coda_w8$r8limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w8, echo=F}
vbl <- HRS_ds_coda_w8$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w8, echo=F}






```





### Wave 9

#### Study-specific variable description

| **Name** | `r9limhwrk` |
|-|-|
| **Label** | `r9limhwrk:w9 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9','HRS.HRS_b_CODA', variables=list('r9limhwrk'), missings = TRUE)
HRS_coda_w9 <- opal.execute(o,'HRS_coda_w9')
```

```{r local coda w9, echo=F}
vbl <- HRS_coda_w9$r9limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9, aes(x=factor(r9limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9$id)
HRS_ds_coda_w9$iadl_housewk <- car::recode(HRS_coda_w9$r9limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w9, echo=F}
vbl <- HRS_ds_coda_w9$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w9, echo=F}






```





### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10','HRS.HRS_b_CODA', variables=list('r10limhwrk'), missings = TRUE)
HRS_coda_w10 <- opal.execute(o,'HRS_coda_w10')
```

```{r local coda w10, echo=F}
vbl <- HRS_coda_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10$id)
HRS_ds_coda_w10$iadl_housewk <- car::recode(HRS_coda_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w10, echo=F}
vbl <- HRS_ds_coda_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w10, echo=F}






```





### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_CODA` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign coda w11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11','HRS.HRS_b_CODA', variables=list('r11limhwrk'), missings = TRUE)
HRS_coda_w11 <- opal.execute(o,'HRS_coda_w11')
```

```{r local coda w11, echo=F}
vbl <- HRS_coda_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_coda_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo coda w11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11$id)
HRS_ds_coda_w11$iadl_housewk <- car::recode(HRS_coda_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript coda w11, echo=F}
vbl <- HRS_ds_coda_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation coda w11, echo=F}






```







## WB

### Wave 4

#### Study-specific variable description

| **Name** | `r4limhwrk` |
|-|-|
| **Label** | `r4limhwrk:w4 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4','HRS.HRS_b_WB', variables=list('r4limhwrk'), missings = TRUE)
HRS_wb_w4 <- opal.execute(o,'HRS_wb_w4')
```

```{r local wb w4, echo=F}
vbl <- HRS_wb_w4$r4limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4, aes(x=factor(r4limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4$id)
HRS_ds_wb_w4$iadl_housewk <- car::recode(HRS_wb_w4$r4limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w4, echo=F}
vbl <- HRS_ds_wb_w4$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `r5limhwrk` |
|-|-|
| **Label** | `r5limhwrk:w5 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5','HRS.HRS_b_WB', variables=list('r5limhwrk'), missings = TRUE)
HRS_wb_w5 <- opal.execute(o,'HRS_wb_w5')
```

```{r local wb w5, echo=F}
vbl <- HRS_wb_w5$r5limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5, aes(x=factor(r5limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5$id)
HRS_ds_wb_w5$iadl_housewk <- car::recode(HRS_wb_w5$r5limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w5, echo=F}
vbl <- HRS_ds_wb_w5$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w5, echo=F}
```




### Wave 6

#### Study-specific variable description

| **Name** | `r6limhwrk` |
|-|-|
| **Label** | `r6limhwrk:w6 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6','HRS.HRS_b_WB', variables=list('r6limhwrk'), missings = TRUE)
HRS_wb_w6 <- opal.execute(o,'HRS_wb_w6')
```

```{r local wb w6, echo=F}
vbl <- HRS_wb_w6$r6limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6, aes(x=factor(r6limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6$id)
HRS_ds_wb_w6$iadl_housewk <- car::recode(HRS_wb_w6$r6limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w6, echo=F}
vbl <- HRS_ds_wb_w6$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w6, echo=F}
```





### Wave 7

#### Study-specific variable description

| **Name** | `r7limhwrk` |
|-|-|
| **Label** | `r7limhwrk:w7 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7','HRS.HRS_b_WB', variables=list('r7limhwrk'), missings = TRUE)
HRS_wb_w7 <- opal.execute(o,'HRS_wb_w7')
```

```{r local wb w7, echo=F}
vbl <- HRS_wb_w7$r7limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7, aes(x=factor(r7limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7$id)
HRS_ds_wb_w7$iadl_housewk <- car::recode(HRS_wb_w7$r7limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w7, echo=F}
vbl <- HRS_ds_wb_w7$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w7, echo=F}






```





### Wave 8

#### Study-specific variable description

| **Name** | `r8limhwrk` |
|-|-|
| **Label** | `r8limhwrk:w8 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8','HRS.HRS_b_WB', variables=list('r8limhwrk'), missings = TRUE)
HRS_wb_w8 <- opal.execute(o,'HRS_wb_w8')
```

```{r local wb w8, echo=F}
vbl <- HRS_wb_w8$r8limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8, aes(x=factor(r8limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8$id)
HRS_ds_wb_w8$iadl_housewk <- car::recode(HRS_wb_w8$r8limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w8, echo=F}
vbl <- HRS_ds_wb_w8$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w8, echo=F}






```





### Wave 9

#### Study-specific variable description

| **Name** | `r9limhwrk` |
|-|-|
| **Label** | `r9limhwrk:w9 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9','HRS.HRS_b_WB', variables=list('r9limhwrk'), missings = TRUE)
HRS_wb_w9 <- opal.execute(o,'HRS_wb_w9')
```

```{r local wb w9, echo=F}
vbl <- HRS_wb_w9$r9limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9, aes(x=factor(r9limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9$id)
HRS_ds_wb_w9$iadl_housewk <- car::recode(HRS_wb_w9$r9limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w9, echo=F}
vbl <- HRS_ds_wb_w9$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w9, echo=F}






```




### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10','HRS.HRS_b_WB', variables=list('r10limhwrk'), missings = TRUE)
HRS_wb_w10 <- opal.execute(o,'HRS_wb_w10')
```

```{r local wb w10, echo=F}
vbl <- HRS_wb_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10$id)
HRS_ds_wb_w10$iadl_housewk <- car::recode(HRS_wb_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w10, echo=F}
vbl <- HRS_ds_wb_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w10, echo=F}






```





### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_WB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign wb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11','HRS.HRS_b_WB', variables=list('r11limhwrk'), missings = TRUE)
HRS_wb_w11 <- opal.execute(o,'HRS_wb_w11')
```

```{r local wb w11, echo=F}
vbl <- HRS_wb_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_wb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo wb w11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11$id)
HRS_ds_wb_w11$iadl_housewk <- car::recode(HRS_wb_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript wb w11, echo=F}
vbl <- HRS_ds_wb_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation wb w11, echo=F}






```







## EBB


### Wave 7

#### Study-specific variable description

| **Name** | `r7limhwrk` |
|-|-|
| **Label** | `r7limhwrk:w7 whether health limits r housework` |
| **Table name** | `HRS_b_EBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ebb w7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7','HRS.HRS_b_EBB', variables=list('r7limhwrk'), missings = TRUE)
HRS_ebb_w7 <- opal.execute(o,'HRS_ebb_w7')
```

```{r local ebb w7, echo=F}
vbl <- HRS_ebb_w7$r7limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7, aes(x=factor(r7limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7$id)
HRS_ds_ebb_w7$iadl_housewk <- car::recode(HRS_ebb_w7$r7limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w7, echo=F}
vbl <- HRS_ds_ebb_w7$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w7, echo=F}






```





### Wave 8

#### Study-specific variable description

| **Name** | `r8limhwrk` |
|-|-|
| **Label** | `r8limhwrk:w8 whether health limits r housework` |
| **Table name** | `HRS_b_EBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ebb w8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8','HRS.HRS_b_EBB', variables=list('r8limhwrk'), missings = TRUE)
HRS_ebb_w8 <- opal.execute(o,'HRS_ebb_w8')
```

```{r local ebb w8, echo=F}
vbl <- HRS_ebb_w8$r8limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8, aes(x=factor(r8limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8$id)
HRS_ds_ebb_w8$iadl_housewk <- car::recode(HRS_ebb_w8$r8limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w8, echo=F}
vbl <- HRS_ds_ebb_w8$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w8, echo=F}






```





### Wave 9

#### Study-specific variable description

| **Name** | `r9limhwrk` |
|-|-|
| **Label** | `r9limhwrk:w9 whether health limits r housework` |
| **Table name** | `HRS_b_EBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ebb w9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9','HRS.HRS_b_EBB', variables=list('r9limhwrk'), missings = TRUE)
HRS_ebb_w9 <- opal.execute(o,'HRS_ebb_w9')
```

```{r local ebb w9, echo=F}
vbl <- HRS_ebb_w9$r9limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9, aes(x=factor(r9limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9$id)
HRS_ds_ebb_w9$iadl_housewk <- car::recode(HRS_ebb_w9$r9limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w9, echo=F}
vbl <- HRS_ds_ebb_w9$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w9, echo=F}






```





### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_EBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ebb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10','HRS.HRS_b_EBB', variables=list('r10limhwrk'), missings = TRUE)
HRS_ebb_w10 <- opal.execute(o,'HRS_ebb_w10')
```

```{r local ebb w10, echo=F}
vbl <- HRS_ebb_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10$id)
HRS_ds_ebb_w10$iadl_housewk <- car::recode(HRS_ebb_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w10, echo=F}
vbl <- HRS_ds_ebb_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w10, echo=F}






```





### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_EBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign ebb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11','HRS.HRS_b_EBB', variables=list('r11limhwrk'), missings = TRUE)
HRS_ebb_w11 <- opal.execute(o,'HRS_ebb_w11')
```

```{r local ebb w11, echo=F}
vbl <- HRS_ebb_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_ebb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo ebb w11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11$id)
HRS_ds_ebb_w11$iadl_housewk <- car::recode(HRS_ebb_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript ebb w11, echo=F}
vbl <- HRS_ds_ebb_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ebb w11, echo=F}






```






## MBB


### Wave 10

#### Study-specific variable description

| **Name** | `r10limhwrk` |
|-|-|
| **Label** | `r10limhwrk:w10 whether health limits r housework` |
| **Table name** | `HRS_b_MBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign mbb w10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10','HRS.HRS_b_MBB', variables=list('r10limhwrk'), missings = TRUE)
HRS_mbb_w10 <- opal.execute(o,'HRS_mbb_w10')
```

```{r local mbb w10, echo=F}
vbl <- HRS_mbb_w10$r10limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10, aes(x=factor(r10limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10$id)
HRS_ds_mbb_w10$iadl_housewk <- car::recode(HRS_mbb_w10$r10limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w10, echo=F}
vbl <- HRS_ds_mbb_w10$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation mbb w10, echo=F}






```





### Wave 11

#### Study-specific variable description

| **Name** | `r11limhwrk` |
|-|-|
| **Label** | `r11limhwrk:w11 whether health limits r housework` |
| **Table name** | `HRS_b_MBB` |
| **Categories** |`0 = no`<br/>`1 = yes`|
| **Missings** |`-4 = DK`<br/>`-13 = Missing`<br/>`-15 = Too Old to Work`<br/>`-18 = Refuse`<br/>`-23 = health limits work`<br/>`NA`|
| **Description** |  |

   

```{r assign mbb w11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11','HRS.HRS_b_MBB', variables=list('r11limhwrk'), missings = TRUE)
HRS_mbb_w11 <- opal.execute(o,'HRS_mbb_w11')
```

```{r local mbb w11, echo=F}
vbl <- HRS_mbb_w11$r11limhwrk
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HRS_mbb_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11, aes(x=factor(r11limhwrk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is recoded as follows:

* `0 into 1`
* `1 into 0`
* `-4 into 998`
* `-13 into 999`
* `-15 into 0`

* `-18 into 997`
* `-23 into 0`
* `NA into 999`

**R script:**

```{r harmo mbb w11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11$id)
HRS_ds_mbb_w11$iadl_housewk <- car::recode(HRS_mbb_w11$r11limhwrk, "0 = 1; c(1,-15,-23) = 0; -4 = 998; -13 = 999; -18 = 997; NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript mbb w11, echo=F}
vbl <- HRS_ds_mbb_w11$iadl_housewk
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation mbb w11, echo=F}






```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```











# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
