---
title: "IADL - Difficulties for using telephone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_phone`
* Variable label: `IADL - Difficulties for using telephone`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process
```{r lab, echo=FALSE,  echo=FALSE}
ds_label <- "IADL - Difficulties for using telephone"
```


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## HRS

### Wave 1

No study-specific variable has been found.

```{r assign HRS w1,  echo=FALSE}
HRS_ds_hrs_w1 <- NA
```



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R2PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w2_iadl_phone','HRS.HRS-HRS-w2', variables=list('R2PHONEA'), missings = TRUE)
```


```{r local HRS w2,  echo=FALSE}
HRS_HRS_w2_iadl_phone <- opal.execute(o,'HRS_HRS_w2_iadl_phone')
vari <- HRS_HRS_w2_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w2_iadl_phone[[2]])
ggplot(HRS_HRS_w2_iadl_phone, aes(x=factor(R2PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w2,   echo=TRUE}
HRS_HRS_ds_w2 <- tibble(id=HRS_HRS_w2_iadl_phone$id)
HRS_HRS_ds_w2$iadl_phone <- car::recode(HRS_HRS_w2_iadl_phone$R2PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w2$iadl_phone <- labelled(HRS_HRS_ds_w2$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w2,  echo=FALSE}
vari <- HRS_HRS_ds_w2$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w2$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w2, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w2,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w2$iadl_phone)
X<-table(HRS_HRS_w2_iadl_phone$R2PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w2_iadl_phone$R2PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R3PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w3,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w3_iadl_phone','HRS.HRS-HRS-w3', variables=list('R3PHONEA'), missings = TRUE)
```


```{r local HRS w3,  echo=FALSE}
HRS_HRS_w3_iadl_phone <- opal.execute(o,'HRS_HRS_w3_iadl_phone')
vari <- HRS_HRS_w3_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w3_iadl_phone[[2]])
ggplot(HRS_HRS_w3_iadl_phone, aes(x=factor(R3PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w3,   echo=TRUE}
HRS_HRS_ds_w3 <- tibble(id=HRS_HRS_w3_iadl_phone$id)
HRS_HRS_ds_w3$iadl_phone <- car::recode(HRS_HRS_w3_iadl_phone$R3PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w3$iadl_phone <- labelled(HRS_HRS_ds_w3$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w3,  echo=FALSE}
vari <- HRS_HRS_ds_w3$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w3$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w3, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w3,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w3$iadl_phone)
X<-table(HRS_HRS_w3_iadl_phone$R3PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w3_iadl_phone$R3PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w4_iadl_phone','HRS.HRS-HRS-w4', variables=list('R4PHONEA'), missings = TRUE)
```


```{r local HRS w4,  echo=FALSE}
HRS_HRS_w4_iadl_phone <- opal.execute(o,'HRS_HRS_w4_iadl_phone')
vari <- HRS_HRS_w4_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w4_iadl_phone[[2]])
ggplot(HRS_HRS_w4_iadl_phone, aes(x=factor(R4PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w4,   echo=TRUE}
HRS_HRS_ds_w4 <- tibble(id=HRS_HRS_w4_iadl_phone$id)
HRS_HRS_ds_w4$iadl_phone <- car::recode(HRS_HRS_w4_iadl_phone$R4PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w4$iadl_phone <- labelled(HRS_HRS_ds_w4$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w4,  echo=FALSE}
vari <- HRS_HRS_ds_w4$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w4$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w4, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w4,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w4$iadl_phone)
X<-table(HRS_HRS_w4_iadl_phone$R4PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w4_iadl_phone$R4PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w5_iadl_phone','HRS.HRS-HRS-w5', variables=list('R5PHONEA'), missings = TRUE)
```


```{r local HRS w5,  echo=FALSE}
HRS_HRS_w5_iadl_phone <- opal.execute(o,'HRS_HRS_w5_iadl_phone')
vari <- HRS_HRS_w5_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w5_iadl_phone[[2]])
ggplot(HRS_HRS_w5_iadl_phone, aes(x=factor(R5PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w5,   echo=TRUE}
HRS_HRS_ds_w5 <- tibble(id=HRS_HRS_w5_iadl_phone$id)
HRS_HRS_ds_w5$iadl_phone <- car::recode(HRS_HRS_w5_iadl_phone$R5PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w5$iadl_phone <- labelled(HRS_HRS_ds_w5$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w5,  echo=FALSE}
vari <- HRS_HRS_ds_w5$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w5$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w5, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w5,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w5$iadl_phone)
X<-table(HRS_HRS_w5_iadl_phone$R5PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w5_iadl_phone$R5PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w6_iadl_phone','HRS.HRS-HRS-w6', variables=list('R6PHONEA'), missings = TRUE)
```


```{r local HRS w6,  echo=FALSE}
HRS_HRS_w6_iadl_phone <- opal.execute(o,'HRS_HRS_w6_iadl_phone')
vari <- HRS_HRS_w6_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w6_iadl_phone[[2]])
ggplot(HRS_HRS_w6_iadl_phone, aes(x=factor(R6PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w6,   echo=TRUE}
HRS_HRS_ds_w6 <- tibble(id=HRS_HRS_w6_iadl_phone$id)
HRS_HRS_ds_w6$iadl_phone <- car::recode(HRS_HRS_w6_iadl_phone$R6PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w6$iadl_phone <- labelled(HRS_HRS_ds_w6$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w6,  echo=FALSE}
vari <- HRS_HRS_ds_w6$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w6$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w6, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w6,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w6$iadl_phone)
X<-table(HRS_HRS_w6_iadl_phone$R6PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w6_iadl_phone$R6PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w7_iadl_phone','HRS.HRS-HRS-w7', variables=list('R7PHONEA'), missings = TRUE)
```


```{r local HRS w7,  echo=FALSE}
HRS_HRS_w7_iadl_phone <- opal.execute(o,'HRS_HRS_w7_iadl_phone')
vari <- HRS_HRS_w7_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w7_iadl_phone[[2]])
ggplot(HRS_HRS_w7_iadl_phone, aes(x=factor(R7PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w7,   echo=TRUE}
HRS_HRS_ds_w7 <- tibble(id=HRS_HRS_w7_iadl_phone$id)
HRS_HRS_ds_w7$iadl_phone <- car::recode(HRS_HRS_w7_iadl_phone$R7PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w7$iadl_phone <- labelled(HRS_HRS_ds_w7$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w7,  echo=FALSE}
vari <- HRS_HRS_ds_w7$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w7$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w7, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w7,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w7$iadl_phone)
X<-table(HRS_HRS_w7_iadl_phone$R7PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w7_iadl_phone$R7PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w8_iadl_phone','HRS.HRS-HRS-w8', variables=list('R8PHONEA'), missings = TRUE)
```


```{r local HRS w8,  echo=FALSE}
HRS_HRS_w8_iadl_phone <- opal.execute(o,'HRS_HRS_w8_iadl_phone')
vari <- HRS_HRS_w8_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w8_iadl_phone[[2]])
ggplot(HRS_HRS_w8_iadl_phone, aes(x=factor(R8PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w8,   echo=TRUE}
HRS_HRS_ds_w8 <- tibble(id=HRS_HRS_w8_iadl_phone$id)
HRS_HRS_ds_w8$iadl_phone <- car::recode(HRS_HRS_w8_iadl_phone$R8PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w8$iadl_phone <- labelled(HRS_HRS_ds_w8$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w8,  echo=FALSE}
vari <- HRS_HRS_ds_w8$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w8$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w8, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w8,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w8$iadl_phone)
X<-table(HRS_HRS_w8_iadl_phone$R8PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w8_iadl_phone$R8PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w9_iadl_phone','HRS.HRS-HRS-w9', variables=list('R9PHONEA'), missings = TRUE)
```


```{r local HRS w9,  echo=FALSE}
HRS_HRS_w9_iadl_phone <- opal.execute(o,'HRS_HRS_w9_iadl_phone')
vari <- HRS_HRS_w9_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w9_iadl_phone[[2]])
ggplot(HRS_HRS_w9_iadl_phone, aes(x=factor(R9PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w9,   echo=TRUE}
HRS_HRS_ds_w9 <- tibble(id=HRS_HRS_w9_iadl_phone$id)
HRS_HRS_ds_w9$iadl_phone <- car::recode(HRS_HRS_w9_iadl_phone$R9PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w9$iadl_phone <- labelled(HRS_HRS_ds_w9$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w9,  echo=FALSE}
vari <- HRS_HRS_ds_w9$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w9$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w9, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w9,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w9$iadl_phone)
X<-table(HRS_HRS_w9_iadl_phone$R9PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w9_iadl_phone$R9PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w10_iadl_phone','HRS.HRS-HRS-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local HRS w10,  echo=FALSE}
HRS_HRS_w10_iadl_phone <- opal.execute(o,'HRS_HRS_w10_iadl_phone')
vari <- HRS_HRS_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w10_iadl_phone[[2]])
ggplot(HRS_HRS_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w10,   echo=TRUE}
HRS_HRS_ds_w10 <- tibble(id=HRS_HRS_w10_iadl_phone$id)
HRS_HRS_ds_w10$iadl_phone <- car::recode(HRS_HRS_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w10$iadl_phone <- labelled(HRS_HRS_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w10,  echo=FALSE}
vari <- HRS_HRS_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w10,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w10$iadl_phone)
X<-table(HRS_HRS_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign HRS w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w11_iadl_phone','HRS.HRS-HRS-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local HRS w11,  echo=FALSE}
HRS_HRS_w11_iadl_phone <- opal.execute(o,'HRS_HRS_w11_iadl_phone')
vari <- HRS_HRS_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_HRS_w11_iadl_phone[[2]])
ggplot(HRS_HRS_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo HRS w11,   echo=TRUE}
HRS_HRS_ds_w11 <- tibble(id=HRS_HRS_w11_iadl_phone$id)
HRS_HRS_ds_w11$iadl_phone <- car::recode(HRS_HRS_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_HRS_ds_w11$iadl_phone <- labelled(HRS_HRS_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w11,  echo=FALSE}
vari <- HRS_HRS_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_HRS_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_HRS_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w11,  echo=FALSE}
AfterH <- table(HRS_HRS_ds_w11$iadl_phone)
X<-table(HRS_HRS_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_HRS_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




## AHEAD

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R2PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w2,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w2_iadl_phone','HRS.HRS-AHEAD-w2', variables=list('R2PHONEA'), missings = TRUE)
```


```{r local AHEAD w2,  echo=FALSE}
HRS_AHEAD_w2_iadl_phone <- opal.execute(o,'HRS_AHEAD_w2_iadl_phone')
vari <- HRS_AHEAD_w2_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w2_iadl_phone[[2]])
ggplot(HRS_AHEAD_w2_iadl_phone, aes(x=factor(R2PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w2,   echo=TRUE}
HRS_AHEAD_ds_w2 <- tibble(id=HRS_AHEAD_w2_iadl_phone$id)
HRS_AHEAD_ds_w2$iadl_phone <- car::recode(HRS_AHEAD_w2_iadl_phone$R2PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w2$iadl_phone <- labelled(HRS_AHEAD_ds_w2$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w2,  echo=FALSE}
vari <- HRS_AHEAD_ds_w2$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w2$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w2, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w2,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w2$iadl_phone)
X<-table(HRS_AHEAD_w2_iadl_phone$R2PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w2_iadl_phone$R2PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R3PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w3,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w3_iadl_phone','HRS.HRS-AHEAD-w3', variables=list('R3PHONEA'), missings = TRUE)
```


```{r local AHEAD w3,  echo=FALSE}
HRS_AHEAD_w3_iadl_phone <- opal.execute(o,'HRS_AHEAD_w3_iadl_phone')
vari <- HRS_AHEAD_w3_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w3_iadl_phone[[2]])
ggplot(HRS_AHEAD_w3_iadl_phone, aes(x=factor(R3PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w3,   echo=TRUE}
HRS_AHEAD_ds_w3 <- tibble(id=HRS_AHEAD_w3_iadl_phone$id)
HRS_AHEAD_ds_w3$iadl_phone <- car::recode(HRS_AHEAD_w3_iadl_phone$R3PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w3$iadl_phone <- labelled(HRS_AHEAD_ds_w3$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w3,  echo=FALSE}
vari <- HRS_AHEAD_ds_w3$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w3$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w3, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w3,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w3$iadl_phone)
X<-table(HRS_AHEAD_w3_iadl_phone$R3PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w3_iadl_phone$R3PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w4_iadl_phone','HRS.HRS-AHEAD-w4', variables=list('R4PHONEA'), missings = TRUE)
```


```{r local AHEAD w4,  echo=FALSE}
HRS_AHEAD_w4_iadl_phone <- opal.execute(o,'HRS_AHEAD_w4_iadl_phone')
vari <- HRS_AHEAD_w4_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w4_iadl_phone[[2]])
ggplot(HRS_AHEAD_w4_iadl_phone, aes(x=factor(R4PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w4,   echo=TRUE}
HRS_AHEAD_ds_w4 <- tibble(id=HRS_AHEAD_w4_iadl_phone$id)
HRS_AHEAD_ds_w4$iadl_phone <- car::recode(HRS_AHEAD_w4_iadl_phone$R4PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w4$iadl_phone <- labelled(HRS_AHEAD_ds_w4$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w4,  echo=FALSE}
vari <- HRS_AHEAD_ds_w4$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w4$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w4, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w4,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w4$iadl_phone)
X<-table(HRS_AHEAD_w4_iadl_phone$R4PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w4_iadl_phone$R4PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w5_iadl_phone','HRS.HRS-AHEAD-w5', variables=list('R5PHONEA'), missings = TRUE)
```


```{r local AHEAD w5,  echo=FALSE}
HRS_AHEAD_w5_iadl_phone <- opal.execute(o,'HRS_AHEAD_w5_iadl_phone')
vari <- HRS_AHEAD_w5_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w5_iadl_phone[[2]])
ggplot(HRS_AHEAD_w5_iadl_phone, aes(x=factor(R5PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w5,   echo=TRUE}
HRS_AHEAD_ds_w5 <- tibble(id=HRS_AHEAD_w5_iadl_phone$id)
HRS_AHEAD_ds_w5$iadl_phone <- car::recode(HRS_AHEAD_w5_iadl_phone$R5PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w5$iadl_phone <- labelled(HRS_AHEAD_ds_w5$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w5,  echo=FALSE}
vari <- HRS_AHEAD_ds_w5$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w5$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w5, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w5,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w5$iadl_phone)
X<-table(HRS_AHEAD_w5_iadl_phone$R5PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w5_iadl_phone$R5PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w6_iadl_phone','HRS.HRS-AHEAD-w6', variables=list('R6PHONEA'), missings = TRUE)
```


```{r local AHEAD w6,  echo=FALSE}
HRS_AHEAD_w6_iadl_phone <- opal.execute(o,'HRS_AHEAD_w6_iadl_phone')
vari <- HRS_AHEAD_w6_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w6_iadl_phone[[2]])
ggplot(HRS_AHEAD_w6_iadl_phone, aes(x=factor(R6PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w6,   echo=TRUE}
HRS_AHEAD_ds_w6 <- tibble(id=HRS_AHEAD_w6_iadl_phone$id)
HRS_AHEAD_ds_w6$iadl_phone <- car::recode(HRS_AHEAD_w6_iadl_phone$R6PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w6$iadl_phone <- labelled(HRS_AHEAD_ds_w6$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w6,  echo=FALSE}
vari <- HRS_AHEAD_ds_w6$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w6$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w6, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w6,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w6$iadl_phone)
X<-table(HRS_AHEAD_w6_iadl_phone$R6PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w6_iadl_phone$R6PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w7_iadl_phone','HRS.HRS-AHEAD-w7', variables=list('R7PHONEA'), missings = TRUE)
```


```{r local AHEAD w7,  echo=FALSE}
HRS_AHEAD_w7_iadl_phone <- opal.execute(o,'HRS_AHEAD_w7_iadl_phone')
vari <- HRS_AHEAD_w7_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w7_iadl_phone[[2]])
ggplot(HRS_AHEAD_w7_iadl_phone, aes(x=factor(R7PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w7,   echo=TRUE}
HRS_AHEAD_ds_w7 <- tibble(id=HRS_AHEAD_w7_iadl_phone$id)
HRS_AHEAD_ds_w7$iadl_phone <- car::recode(HRS_AHEAD_w7_iadl_phone$R7PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w7$iadl_phone <- labelled(HRS_AHEAD_ds_w7$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w7,  echo=FALSE}
vari <- HRS_AHEAD_ds_w7$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w7$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w7, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w7,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w7$iadl_phone)
X<-table(HRS_AHEAD_w7_iadl_phone$R7PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w7_iadl_phone$R7PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w8_iadl_phone','HRS.HRS-AHEAD-w8', variables=list('R8PHONEA'), missings = TRUE)
```


```{r local AHEAD w8,  echo=FALSE}
HRS_AHEAD_w8_iadl_phone <- opal.execute(o,'HRS_AHEAD_w8_iadl_phone')
vari <- HRS_AHEAD_w8_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w8_iadl_phone[[2]])
ggplot(HRS_AHEAD_w8_iadl_phone, aes(x=factor(R8PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w8,   echo=TRUE}
HRS_AHEAD_ds_w8 <- tibble(id=HRS_AHEAD_w8_iadl_phone$id)
HRS_AHEAD_ds_w8$iadl_phone <- car::recode(HRS_AHEAD_w8_iadl_phone$R8PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w8$iadl_phone <- labelled(HRS_AHEAD_ds_w8$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w8,  echo=FALSE}
vari <- HRS_AHEAD_ds_w8$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w8$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w8, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w8,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w8$iadl_phone)
X<-table(HRS_AHEAD_w8_iadl_phone$R8PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w8_iadl_phone$R8PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w9_iadl_phone','HRS.HRS-AHEAD-w9', variables=list('R9PHONEA'), missings = TRUE)
```


```{r local AHEAD w9,  echo=FALSE}
HRS_AHEAD_w9_iadl_phone <- opal.execute(o,'HRS_AHEAD_w9_iadl_phone')
vari <- HRS_AHEAD_w9_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w9_iadl_phone[[2]])
ggplot(HRS_AHEAD_w9_iadl_phone, aes(x=factor(R9PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w9,   echo=TRUE}
HRS_AHEAD_ds_w9 <- tibble(id=HRS_AHEAD_w9_iadl_phone$id)
HRS_AHEAD_ds_w9$iadl_phone <- car::recode(HRS_AHEAD_w9_iadl_phone$R9PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w9$iadl_phone <- labelled(HRS_AHEAD_ds_w9$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w9,  echo=FALSE}
vari <- HRS_AHEAD_ds_w9$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w9$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w9, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w9,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w9$iadl_phone)
X<-table(HRS_AHEAD_w9_iadl_phone$R9PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w9_iadl_phone$R9PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w10_iadl_phone','HRS.HRS-AHEAD-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local AHEAD w10,  echo=FALSE}
HRS_AHEAD_w10_iadl_phone <- opal.execute(o,'HRS_AHEAD_w10_iadl_phone')
vari <- HRS_AHEAD_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w10_iadl_phone[[2]])
ggplot(HRS_AHEAD_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w10,   echo=TRUE}
HRS_AHEAD_ds_w10 <- tibble(id=HRS_AHEAD_w10_iadl_phone$id)
HRS_AHEAD_ds_w10$iadl_phone <- car::recode(HRS_AHEAD_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w10$iadl_phone <- labelled(HRS_AHEAD_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w10,  echo=FALSE}
vari <- HRS_AHEAD_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w10,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w10$iadl_phone)
X<-table(HRS_AHEAD_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign AHEAD w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w11_iadl_phone','HRS.HRS-AHEAD-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local AHEAD w11,  echo=FALSE}
HRS_AHEAD_w11_iadl_phone <- opal.execute(o,'HRS_AHEAD_w11_iadl_phone')
vari <- HRS_AHEAD_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_AHEAD_w11_iadl_phone[[2]])
ggplot(HRS_AHEAD_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo AHEAD w11,   echo=TRUE}
HRS_AHEAD_ds_w11 <- tibble(id=HRS_AHEAD_w11_iadl_phone$id)
HRS_AHEAD_ds_w11$iadl_phone <- car::recode(HRS_AHEAD_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_AHEAD_ds_w11$iadl_phone <- labelled(HRS_AHEAD_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w11,  echo=FALSE}
vari <- HRS_AHEAD_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_AHEAD_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_AHEAD_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w11,  echo=FALSE}
AfterH <- table(HRS_AHEAD_ds_w11$iadl_phone)
X<-table(HRS_AHEAD_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_AHEAD_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 






## CODA

### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w4_iadl_phone','HRS.HRS-CODA-w4', variables=list('R4PHONEA'), missings = TRUE)
```


```{r local CODA w4,  echo=FALSE}
HRS_CODA_w4_iadl_phone <- opal.execute(o,'HRS_CODA_w4_iadl_phone')
vari <- HRS_CODA_w4_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w4_iadl_phone[[2]])
ggplot(HRS_CODA_w4_iadl_phone, aes(x=factor(R4PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w4,   echo=TRUE}
HRS_CODA_ds_w4 <- tibble(id=HRS_CODA_w4_iadl_phone$id)
HRS_CODA_ds_w4$iadl_phone <- car::recode(HRS_CODA_w4_iadl_phone$R4PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w4$iadl_phone <- labelled(HRS_CODA_ds_w4$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w4,  echo=FALSE}
vari <- HRS_CODA_ds_w4$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w4$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w4, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w4,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w4$iadl_phone)
X<-table(HRS_CODA_w4_iadl_phone$R4PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w4_iadl_phone$R4PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w5_iadl_phone','HRS.HRS-CODA-w5', variables=list('R5PHONEA'), missings = TRUE)
```


```{r local CODA w5,  echo=FALSE}
HRS_CODA_w5_iadl_phone <- opal.execute(o,'HRS_CODA_w5_iadl_phone')
vari <- HRS_CODA_w5_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w5_iadl_phone[[2]])
ggplot(HRS_CODA_w5_iadl_phone, aes(x=factor(R5PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w5,   echo=TRUE}
HRS_CODA_ds_w5 <- tibble(id=HRS_CODA_w5_iadl_phone$id)
HRS_CODA_ds_w5$iadl_phone <- car::recode(HRS_CODA_w5_iadl_phone$R5PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w5$iadl_phone <- labelled(HRS_CODA_ds_w5$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w5,  echo=FALSE}
vari <- HRS_CODA_ds_w5$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w5$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w5, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w5,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w5$iadl_phone)
X<-table(HRS_CODA_w5_iadl_phone$R5PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w5_iadl_phone$R5PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w6_iadl_phone','HRS.HRS-CODA-w6', variables=list('R6PHONEA'), missings = TRUE)
```


```{r local CODA w6,  echo=FALSE}
HRS_CODA_w6_iadl_phone <- opal.execute(o,'HRS_CODA_w6_iadl_phone')
vari <- HRS_CODA_w6_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w6_iadl_phone[[2]])
ggplot(HRS_CODA_w6_iadl_phone, aes(x=factor(R6PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w6,   echo=TRUE}
HRS_CODA_ds_w6 <- tibble(id=HRS_CODA_w6_iadl_phone$id)
HRS_CODA_ds_w6$iadl_phone <- car::recode(HRS_CODA_w6_iadl_phone$R6PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w6$iadl_phone <- labelled(HRS_CODA_ds_w6$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w6,  echo=FALSE}
vari <- HRS_CODA_ds_w6$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w6$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w6, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w6,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w6$iadl_phone)
X<-table(HRS_CODA_w6_iadl_phone$R6PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w6_iadl_phone$R6PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w7_iadl_phone','HRS.HRS-CODA-w7', variables=list('R7PHONEA'), missings = TRUE)
```


```{r local CODA w7,  echo=FALSE}
HRS_CODA_w7_iadl_phone <- opal.execute(o,'HRS_CODA_w7_iadl_phone')
vari <- HRS_CODA_w7_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w7_iadl_phone[[2]])
ggplot(HRS_CODA_w7_iadl_phone, aes(x=factor(R7PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w7,   echo=TRUE}
HRS_CODA_ds_w7 <- tibble(id=HRS_CODA_w7_iadl_phone$id)
HRS_CODA_ds_w7$iadl_phone <- car::recode(HRS_CODA_w7_iadl_phone$R7PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w7$iadl_phone <- labelled(HRS_CODA_ds_w7$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w7,  echo=FALSE}
vari <- HRS_CODA_ds_w7$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w7$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w7, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w7,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w7$iadl_phone)
X<-table(HRS_CODA_w7_iadl_phone$R7PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w7_iadl_phone$R7PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w8_iadl_phone','HRS.HRS-CODA-w8', variables=list('R8PHONEA'), missings = TRUE)
```


```{r local CODA w8,  echo=FALSE}
HRS_CODA_w8_iadl_phone <- opal.execute(o,'HRS_CODA_w8_iadl_phone')
vari <- HRS_CODA_w8_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w8_iadl_phone[[2]])
ggplot(HRS_CODA_w8_iadl_phone, aes(x=factor(R8PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w8,   echo=TRUE}
HRS_CODA_ds_w8 <- tibble(id=HRS_CODA_w8_iadl_phone$id)
HRS_CODA_ds_w8$iadl_phone <- car::recode(HRS_CODA_w8_iadl_phone$R8PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w8$iadl_phone <- labelled(HRS_CODA_ds_w8$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w8,  echo=FALSE}
vari <- HRS_CODA_ds_w8$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w8$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w8, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w8,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w8$iadl_phone)
X<-table(HRS_CODA_w8_iadl_phone$R8PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w8_iadl_phone$R8PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w9_iadl_phone','HRS.HRS-CODA-w9', variables=list('R9PHONEA'), missings = TRUE)
```


```{r local CODA w9,  echo=FALSE}
HRS_CODA_w9_iadl_phone <- opal.execute(o,'HRS_CODA_w9_iadl_phone')
vari <- HRS_CODA_w9_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w9_iadl_phone[[2]])
ggplot(HRS_CODA_w9_iadl_phone, aes(x=factor(R9PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w9,   echo=TRUE}
HRS_CODA_ds_w9 <- tibble(id=HRS_CODA_w9_iadl_phone$id)
HRS_CODA_ds_w9$iadl_phone <- car::recode(HRS_CODA_w9_iadl_phone$R9PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w9$iadl_phone <- labelled(HRS_CODA_ds_w9$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w9,  echo=FALSE}
vari <- HRS_CODA_ds_w9$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w9$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w9, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w9,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w9$iadl_phone)
X<-table(HRS_CODA_w9_iadl_phone$R9PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w9_iadl_phone$R9PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w10_iadl_phone','HRS.HRS-CODA-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local CODA w10,  echo=FALSE}
HRS_CODA_w10_iadl_phone <- opal.execute(o,'HRS_CODA_w10_iadl_phone')
vari <- HRS_CODA_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w10_iadl_phone[[2]])
ggplot(HRS_CODA_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w10,   echo=TRUE}
HRS_CODA_ds_w10 <- tibble(id=HRS_CODA_w10_iadl_phone$id)
HRS_CODA_ds_w10$iadl_phone <- car::recode(HRS_CODA_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w10$iadl_phone <- labelled(HRS_CODA_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w10,  echo=FALSE}
vari <- HRS_CODA_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w10,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w10$iadl_phone)
X<-table(HRS_CODA_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign CODA w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w11_iadl_phone','HRS.HRS-CODA-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local CODA w11,  echo=FALSE}
HRS_CODA_w11_iadl_phone <- opal.execute(o,'HRS_CODA_w11_iadl_phone')
vari <- HRS_CODA_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_CODA_w11_iadl_phone[[2]])
ggplot(HRS_CODA_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo CODA w11,   echo=TRUE}
HRS_CODA_ds_w11 <- tibble(id=HRS_CODA_w11_iadl_phone$id)
HRS_CODA_ds_w11$iadl_phone <- car::recode(HRS_CODA_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_CODA_ds_w11$iadl_phone <- labelled(HRS_CODA_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w11,  echo=FALSE}
vari <- HRS_CODA_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_CODA_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_CODA_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w11,  echo=FALSE}
AfterH <- table(HRS_CODA_ds_w11$iadl_phone)
X<-table(HRS_CODA_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_CODA_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 





## WB

### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w4,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w4_iadl_phone','HRS.HRS-WB-w4', variables=list('R4PHONEA'), missings = TRUE)
```


```{r local WB w4,  echo=FALSE}
HRS_WB_w4_iadl_phone <- opal.execute(o,'HRS_WB_w4_iadl_phone')
vari <- HRS_WB_w4_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w4_iadl_phone[[2]])
ggplot(HRS_WB_w4_iadl_phone, aes(x=factor(R4PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w4,   echo=TRUE}
HRS_WB_ds_w4 <- tibble(id=HRS_WB_w4_iadl_phone$id)
HRS_WB_ds_w4$iadl_phone <- car::recode(HRS_WB_w4_iadl_phone$R4PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w4$iadl_phone <- labelled(HRS_WB_ds_w4$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w4,  echo=FALSE}
vari <- HRS_WB_ds_w4$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w4$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w4, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w4,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w4$iadl_phone)
X<-table(HRS_WB_w4_iadl_phone$R4PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w4_iadl_phone$R4PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w5,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w5_iadl_phone','HRS.HRS-WB-w5', variables=list('R5PHONEA'), missings = TRUE)
```


```{r local WB w5,  echo=FALSE}
HRS_WB_w5_iadl_phone <- opal.execute(o,'HRS_WB_w5_iadl_phone')
vari <- HRS_WB_w5_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w5_iadl_phone[[2]])
ggplot(HRS_WB_w5_iadl_phone, aes(x=factor(R5PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w5,   echo=TRUE}
HRS_WB_ds_w5 <- tibble(id=HRS_WB_w5_iadl_phone$id)
HRS_WB_ds_w5$iadl_phone <- car::recode(HRS_WB_w5_iadl_phone$R5PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w5$iadl_phone <- labelled(HRS_WB_ds_w5$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w5,  echo=FALSE}
vari <- HRS_WB_ds_w5$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w5$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w5, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w5,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w5$iadl_phone)
X<-table(HRS_WB_w5_iadl_phone$R5PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w5_iadl_phone$R5PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w6,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w6_iadl_phone','HRS.HRS-WB-w6', variables=list('R6PHONEA'), missings = TRUE)
```


```{r local WB w6,  echo=FALSE}
HRS_WB_w6_iadl_phone <- opal.execute(o,'HRS_WB_w6_iadl_phone')
vari <- HRS_WB_w6_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w6_iadl_phone[[2]])
ggplot(HRS_WB_w6_iadl_phone, aes(x=factor(R6PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w6,   echo=TRUE}
HRS_WB_ds_w6 <- tibble(id=HRS_WB_w6_iadl_phone$id)
HRS_WB_ds_w6$iadl_phone <- car::recode(HRS_WB_w6_iadl_phone$R6PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w6$iadl_phone <- labelled(HRS_WB_ds_w6$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w6,  echo=FALSE}
vari <- HRS_WB_ds_w6$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w6$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w6, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w6,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w6$iadl_phone)
X<-table(HRS_WB_w6_iadl_phone$R6PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w6_iadl_phone$R6PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w7_iadl_phone','HRS.HRS-WB-w7', variables=list('R7PHONEA'), missings = TRUE)
```


```{r local WB w7,  echo=FALSE}
HRS_WB_w7_iadl_phone <- opal.execute(o,'HRS_WB_w7_iadl_phone')
vari <- HRS_WB_w7_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w7_iadl_phone[[2]])
ggplot(HRS_WB_w7_iadl_phone, aes(x=factor(R7PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w7,   echo=TRUE}
HRS_WB_ds_w7 <- tibble(id=HRS_WB_w7_iadl_phone$id)
HRS_WB_ds_w7$iadl_phone <- car::recode(HRS_WB_w7_iadl_phone$R7PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w7$iadl_phone <- labelled(HRS_WB_ds_w7$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w7,  echo=FALSE}
vari <- HRS_WB_ds_w7$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w7$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w7, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w7,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w7$iadl_phone)
X<-table(HRS_WB_w7_iadl_phone$R7PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w7_iadl_phone$R7PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w8_iadl_phone','HRS.HRS-WB-w8', variables=list('R8PHONEA'), missings = TRUE)
```


```{r local WB w8,  echo=FALSE}
HRS_WB_w8_iadl_phone <- opal.execute(o,'HRS_WB_w8_iadl_phone')
vari <- HRS_WB_w8_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w8_iadl_phone[[2]])
ggplot(HRS_WB_w8_iadl_phone, aes(x=factor(R8PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w8,   echo=TRUE}
HRS_WB_ds_w8 <- tibble(id=HRS_WB_w8_iadl_phone$id)
HRS_WB_ds_w8$iadl_phone <- car::recode(HRS_WB_w8_iadl_phone$R8PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w8$iadl_phone <- labelled(HRS_WB_ds_w8$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w8,  echo=FALSE}
vari <- HRS_WB_ds_w8$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w8$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w8, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w8,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w8$iadl_phone)
X<-table(HRS_WB_w8_iadl_phone$R8PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w8_iadl_phone$R8PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w9_iadl_phone','HRS.HRS-WB-w9', variables=list('R9PHONEA'), missings = TRUE)
```


```{r local WB w9,  echo=FALSE}
HRS_WB_w9_iadl_phone <- opal.execute(o,'HRS_WB_w9_iadl_phone')
vari <- HRS_WB_w9_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w9_iadl_phone[[2]])
ggplot(HRS_WB_w9_iadl_phone, aes(x=factor(R9PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w9,   echo=TRUE}
HRS_WB_ds_w9 <- tibble(id=HRS_WB_w9_iadl_phone$id)
HRS_WB_ds_w9$iadl_phone <- car::recode(HRS_WB_w9_iadl_phone$R9PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w9$iadl_phone <- labelled(HRS_WB_ds_w9$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w9,  echo=FALSE}
vari <- HRS_WB_ds_w9$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w9$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w9, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w9,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w9$iadl_phone)
X<-table(HRS_WB_w9_iadl_phone$R9PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w9_iadl_phone$R9PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w10_iadl_phone','HRS.HRS-WB-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local WB w10,  echo=FALSE}
HRS_WB_w10_iadl_phone <- opal.execute(o,'HRS_WB_w10_iadl_phone')
vari <- HRS_WB_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w10_iadl_phone[[2]])
ggplot(HRS_WB_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w10,   echo=TRUE}
HRS_WB_ds_w10 <- tibble(id=HRS_WB_w10_iadl_phone$id)
HRS_WB_ds_w10$iadl_phone <- car::recode(HRS_WB_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w10$iadl_phone <- labelled(HRS_WB_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w10,  echo=FALSE}
vari <- HRS_WB_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w10,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w10$iadl_phone)
X<-table(HRS_WB_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign WB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w11_iadl_phone','HRS.HRS-WB-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local WB w11,  echo=FALSE}
HRS_WB_w11_iadl_phone <- opal.execute(o,'HRS_WB_w11_iadl_phone')
vari <- HRS_WB_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_WB_w11_iadl_phone[[2]])
ggplot(HRS_WB_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo WB w11,   echo=TRUE}
HRS_WB_ds_w11 <- tibble(id=HRS_WB_w11_iadl_phone$id)
HRS_WB_ds_w11$iadl_phone <- car::recode(HRS_WB_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_WB_ds_w11$iadl_phone <- labelled(HRS_WB_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w11,  echo=FALSE}
vari <- HRS_WB_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_WB_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_WB_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w11,  echo=FALSE}
AfterH <- table(HRS_WB_ds_w11$iadl_phone)
X<-table(HRS_WB_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_WB_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 





## EBB

### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign EBB w7,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w7_iadl_phone','HRS.HRS-EBB-w7', variables=list('R7PHONEA'), missings = TRUE)
```


```{r local EBB w7,  echo=FALSE}
HRS_EBB_w7_iadl_phone <- opal.execute(o,'HRS_EBB_w7_iadl_phone')
vari <- HRS_EBB_w7_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_EBB_w7_iadl_phone[[2]])
ggplot(HRS_EBB_w7_iadl_phone, aes(x=factor(R7PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo EBB w7,   echo=TRUE}
HRS_EBB_ds_w7 <- tibble(id=HRS_EBB_w7_iadl_phone$id)
HRS_EBB_ds_w7$iadl_phone <- car::recode(HRS_EBB_w7_iadl_phone$R7PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_EBB_ds_w7$iadl_phone <- labelled(HRS_EBB_ds_w7$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w7,  echo=FALSE}
vari <- HRS_EBB_ds_w7$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w7$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w7, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w7,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w7$iadl_phone)
X<-table(HRS_EBB_w7_iadl_phone$R7PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w7_iadl_phone$R7PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do``


* Description: 
```{r assign EBB w8,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w8_iadl_phone','HRS.HRS-EBB-w8', variables=list('R8PHONEA'), missings = TRUE)
```


```{r local EBB w8,  echo=FALSE}
HRS_EBB_w8_iadl_phone <- opal.execute(o,'HRS_EBB_w8_iadl_phone')
vari <- HRS_EBB_w8_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_EBB_w8_iadl_phone[[2]])
ggplot(HRS_EBB_w8_iadl_phone, aes(x=factor(R8PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo EBB w8,   echo=TRUE}
HRS_EBB_ds_w8 <- tibble(id=HRS_EBB_w8_iadl_phone$id)
HRS_EBB_ds_w8$iadl_phone <- car::recode(HRS_EBB_w8_iadl_phone$R8PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_EBB_ds_w8$iadl_phone <- labelled(HRS_EBB_ds_w8$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w8,  echo=FALSE}
vari <- HRS_EBB_ds_w8$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w8$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w8, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w8,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w8$iadl_phone)
X<-table(HRS_EBB_w8_iadl_phone$R8PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w8_iadl_phone$R8PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign EBB w9,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w9_iadl_phone','HRS.HRS-EBB-w9', variables=list('R9PHONEA'), missings = TRUE)
```


```{r local EBB w9,  echo=FALSE}
HRS_EBB_w9_iadl_phone <- opal.execute(o,'HRS_EBB_w9_iadl_phone')
vari <- HRS_EBB_w9_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_EBB_w9_iadl_phone[[2]])
ggplot(HRS_EBB_w9_iadl_phone, aes(x=factor(R9PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo EBB w9,   echo=TRUE}
HRS_EBB_ds_w9 <- tibble(id=HRS_EBB_w9_iadl_phone$id)
HRS_EBB_ds_w9$iadl_phone <- car::recode(HRS_EBB_w9_iadl_phone$R9PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_EBB_ds_w9$iadl_phone <- labelled(HRS_EBB_ds_w9$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w9,  echo=FALSE}
vari <- HRS_EBB_ds_w9$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w9$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w9, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w9,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w9$iadl_phone)
X<-table(HRS_EBB_w9_iadl_phone$R9PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w9_iadl_phone$R9PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign EBB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w10_iadl_phone','HRS.HRS-EBB-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local EBB w10,  echo=FALSE}
HRS_EBB_w10_iadl_phone <- opal.execute(o,'HRS_EBB_w10_iadl_phone')
vari <- HRS_EBB_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_EBB_w10_iadl_phone[[2]])
ggplot(HRS_EBB_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo EBB w10,   echo=TRUE}
HRS_EBB_ds_w10 <- tibble(id=HRS_EBB_w10_iadl_phone$id)
HRS_EBB_ds_w10$iadl_phone <- car::recode(HRS_EBB_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_EBB_ds_w10$iadl_phone <- labelled(HRS_EBB_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w10,  echo=FALSE}
vari <- HRS_EBB_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w10,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w10$iadl_phone)
X<-table(HRS_EBB_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign EBB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w11_iadl_phone','HRS.HRS-EBB-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local EBB w11,  echo=FALSE}
HRS_EBB_w11_iadl_phone <- opal.execute(o,'HRS_EBB_w11_iadl_phone')
vari <- HRS_EBB_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_EBB_w11_iadl_phone[[2]])
ggplot(HRS_EBB_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo EBB w11,   echo=TRUE}
HRS_EBB_ds_w11 <- tibble(id=HRS_EBB_w11_iadl_phone$id)
HRS_EBB_ds_w11$iadl_phone <- car::recode(HRS_EBB_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_EBB_ds_w11$iadl_phone <- labelled(HRS_EBB_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w11,  echo=FALSE}
vari <- HRS_EBB_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_EBB_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_EBB_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w11,  echo=FALSE}
AfterH <- table(HRS_EBB_ds_w11$iadl_phone)
X<-table(HRS_EBB_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_EBB_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


## MBB

### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign MBB w10,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w10_iadl_phone','HRS.HRS-MBB-w10', variables=list('R10PHONEA'), missings = TRUE)
```


```{r local MBB w10,  echo=FALSE}
HRS_MBB_w10_iadl_phone <- opal.execute(o,'HRS_MBB_w10_iadl_phone')
vari <- HRS_MBB_w10_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_MBB_w10_iadl_phone[[2]])
ggplot(HRS_MBB_w10_iadl_phone, aes(x=factor(R10PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo MBB w10,   echo=TRUE}
HRS_MBB_ds_w10 <- tibble(id=HRS_MBB_w10_iadl_phone$id)
HRS_MBB_ds_w10$iadl_phone <- car::recode(HRS_MBB_w10_iadl_phone$R10PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_MBB_ds_w10$iadl_phone <- labelled(HRS_MBB_ds_w10$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w10,  echo=FALSE}
vari <- HRS_MBB_ds_w10$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_MBB_ds_w10$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_MBB_ds_w10, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w10,  echo=FALSE}
AfterH <- table(HRS_MBB_ds_w10$iadl_phone)
X<-table(HRS_MBB_w10_iadl_phone$R10PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w10_iadl_phone$R10PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11PHONEA`
* Label: `R Diff-Use telephone`															 
* Categories:
    + `0 = No`
    + `1 = Yes` 
    + `2 = Can't do`  
* Missings
     
    + `9 = Don't do`


* Description: 
```{r assign MBB w11,  echo=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w11_iadl_phone','HRS.HRS-MBB-w11', variables=list('R11PHONEA'), missings = TRUE)
```


```{r local MBB w11,  echo=FALSE}
HRS_MBB_w11_iadl_phone <- opal.execute(o,'HRS_MBB_w11_iadl_phone')
vari <- HRS_MBB_w11_iadl_phone[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(HRS_MBB_w11_iadl_phone[[2]])
ggplot(HRS_MBB_w11_iadl_phone, aes(x=factor(R11PHONEA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `2 into 0`
* `9 into 995`
* `NA into 999`

**R script:** 
```{r harmo MBB w11,   echo=TRUE}
HRS_MBB_ds_w11 <- tibble(id=HRS_MBB_w11_iadl_phone$id)
HRS_MBB_ds_w11$iadl_phone <- car::recode(HRS_MBB_w11_iadl_phone$R11PHONEA, "1 = '0';0 = '1';2 = '0';9 = '995'; NA='999'")
HRS_MBB_ds_w11$iadl_phone <- labelled(HRS_MBB_ds_w11$iadl_phone, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w11,  echo=FALSE}
vari <- HRS_MBB_ds_w11$iadl_phone # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HRS_MBB_ds_w11$iadl_phone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_MBB_ds_w11, aes(x=factor(iadl_phone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Using telephone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w11,  echo=FALSE}
AfterH <- table(HRS_MBB_ds_w11$iadl_phone)
X<-table(HRS_MBB_w11_iadl_phone$R11PHONEA)
BeforeH <- c(X[2:1],sum(is.na(HRS_MBB_w11_iadl_phone$R11PHONEA)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999") 
kable(C)
```

 
 


<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE,  echo=FALSE}
HRS_m_ds_hrs_w1  <- HRS_ds_hrs_w1  <- HRS_HRS_ds_w1
HRS_m_ds_hrs_w2  <- HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
HRS_m_ds_hrs_w3  <- HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
HRS_m_ds_hrs_w4  <- HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
HRS_m_ds_hrs_w5  <- HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
HRS_m_ds_hrs_w6  <- HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
HRS_m_ds_hrs_w7  <- HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
HRS_m_ds_hrs_w8  <- HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
HRS_m_ds_hrs_w9  <- HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11 <- HRS_HRS_ds_w11

HRS_m_ds_ahead_w2  <- HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
HRS_m_ds_ahead_w3  <- HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
HRS_m_ds_ahead_w4  <- HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
HRS_m_ds_ahead_w5  <- HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
HRS_m_ds_ahead_w6  <- HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
HRS_m_ds_ahead_w7  <- HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
HRS_m_ds_ahead_w8  <- HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
HRS_m_ds_ahead_w9  <- HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11

HRS_m_ds_coda_w4  <- HRS_ds_coda_w4  <- HRS_CODA_ds_w4
HRS_m_ds_coda_w5  <- HRS_ds_coda_w5  <- HRS_CODA_ds_w5
HRS_m_ds_coda_w6  <- HRS_ds_coda_w6  <- HRS_CODA_ds_w6
HRS_m_ds_coda_w7  <- HRS_ds_coda_w7  <- HRS_CODA_ds_w7
HRS_m_ds_coda_w8  <- HRS_ds_coda_w8  <- HRS_CODA_ds_w8
HRS_m_ds_coda_w9  <- HRS_ds_coda_w9  <- HRS_CODA_ds_w9
HRS_m_ds_coda_w10 <- HRS_ds_coda_w10 <- HRS_CODA_ds_w10
HRS_m_ds_coda_w11 <- HRS_ds_coda_w11 <- HRS_CODA_ds_w11

HRS_m_ds_wb_w4  <- HRS_ds_wb_w4  <- HRS_WB_ds_w4
HRS_m_ds_wb_w5  <- HRS_ds_wb_w5  <- HRS_WB_ds_w5
HRS_m_ds_wb_w6  <- HRS_ds_wb_w6  <- HRS_WB_ds_w6
HRS_m_ds_wb_w7  <- HRS_ds_wb_w7  <- HRS_WB_ds_w7
HRS_m_ds_wb_w8  <- HRS_ds_wb_w8  <- HRS_WB_ds_w8
HRS_m_ds_wb_w9  <- HRS_ds_wb_w9  <- HRS_WB_ds_w9
HRS_m_ds_wb_w10 <- HRS_ds_wb_w10 <- HRS_WB_ds_w10
HRS_m_ds_wb_w11 <- HRS_ds_wb_w11 <- HRS_WB_ds_w11

HRS_m_ds_ebb_w7  <- HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
HRS_m_ds_ebb_w8  <- HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
HRS_m_ds_ebb_w9  <- HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11 <- HRS_EBB_ds_w11

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11 <- HRS_MBB_ds_w11

l.hrs <- list(HRS_ds_hrs_w1 = HRS_ds_hrs_w1 , HRS_ds_hrs_w2 = HRS_ds_hrs_w2 ,HRS_ds_hrs_w3 = HRS_ds_hrs_w3 ,HRS_ds_hrs_w4 = HRS_ds_hrs_w4 ,
HRS_ds_hrs_w5 = HRS_ds_hrs_w5 ,HRS_ds_hrs_w6 = HRS_ds_hrs_w6 ,HRS_ds_hrs_w7 = HRS_ds_hrs_w7 ,HRS_ds_hrs_w8 = HRS_ds_hrs_w8 ,
HRS_ds_hrs_w9 = HRS_ds_hrs_w9 ,HRS_ds_hrs_w10 = HRS_ds_hrs_w10 ,HRS_ds_hrs_w11 = HRS_ds_hrs_w11 ,HRS_ds_ahead_w2 = HRS_ds_ahead_w2 ,
HRS_ds_ahead_w3 = HRS_ds_ahead_w3 ,HRS_ds_ahead_w4 = HRS_ds_ahead_w4 ,HRS_ds_ahead_w5 = HRS_ds_ahead_w5 ,HRS_ds_ahead_w6 = HRS_ds_ahead_w6 ,
HRS_ds_ahead_w7 = HRS_ds_ahead_w7 ,HRS_ds_ahead_w8 = HRS_ds_ahead_w8 ,HRS_ds_ahead_w9 = HRS_ds_ahead_w9 ,HRS_ds_ahead_w10 = HRS_ds_ahead_w10 ,
HRS_ds_ahead_w11 = HRS_ds_ahead_w11 ,HRS_ds_coda_w4 = HRS_ds_coda_w4 ,HRS_ds_coda_w5 = HRS_ds_coda_w5 ,HRS_ds_coda_w6 = HRS_ds_coda_w6 ,
HRS_ds_coda_w7 = HRS_ds_coda_w7 ,HRS_ds_coda_w8 = HRS_ds_coda_w8 ,HRS_ds_coda_w9 = HRS_ds_coda_w9 ,HRS_ds_coda_w10 = HRS_ds_coda_w10 ,
HRS_ds_coda_w11 = HRS_ds_coda_w11 ,HRS_ds_wb_w4 = HRS_ds_wb_w4 ,HRS_ds_wb_w5 = HRS_ds_wb_w5 ,HRS_ds_wb_w6 = HRS_ds_wb_w6 ,
HRS_ds_wb_w7 = HRS_ds_wb_w7 ,HRS_ds_wb_w8 = HRS_ds_wb_w8 ,HRS_ds_wb_w9 = HRS_ds_wb_w9 ,HRS_ds_wb_w10 = HRS_ds_wb_w10 ,
HRS_ds_wb_w11 = HRS_ds_wb_w11 ,HRS_ds_ebb_w7 = HRS_ds_ebb_w7 ,HRS_ds_ebb_w8 = HRS_ds_ebb_w8 ,HRS_ds_ebb_w9 = HRS_ds_ebb_w9 ,
HRS_ds_ebb_w10 = HRS_ds_ebb_w10 ,HRS_ds_ebb_w11 = HRS_ds_ebb_w11 ,HRS_ds_mbb_w10 = HRS_ds_mbb_w10 ,HRS_ds_mbb_w11 = HRS_ds_mbb_w11)

m.hrs <- list(HRS_m_ds_hrs_w1 = HRS_m_ds_hrs_w1 , HRS_m_ds_hrs_w2 = HRS_m_ds_hrs_w2 ,HRS_m_ds_hrs_w3 = HRS_m_ds_hrs_w3 ,HRS_m_ds_hrs_w4 = HRS_m_ds_hrs_w4 ,
HRS_m_ds_hrs_w5 = HRS_m_ds_hrs_w5 ,HRS_m_ds_hrs_w6 = HRS_m_ds_hrs_w6 ,HRS_m_ds_hrs_w7 = HRS_m_ds_hrs_w7 ,HRS_m_ds_hrs_w8 = HRS_m_ds_hrs_w8 ,
HRS_m_ds_hrs_w9 = HRS_m_ds_hrs_w9 ,HRS_m_ds_hrs_w10 = HRS_m_ds_hrs_w10 ,HRS_m_ds_hrs_w11 = HRS_m_ds_hrs_w11 ,HRS_m_ds_ahead_w2 = HRS_m_ds_ahead_w2 ,
HRS_m_ds_ahead_w3 = HRS_m_ds_ahead_w3 ,HRS_m_ds_ahead_w4 = HRS_m_ds_ahead_w4 ,HRS_m_ds_ahead_w5 = HRS_m_ds_ahead_w5 ,HRS_m_ds_ahead_w6 = HRS_m_ds_ahead_w6 ,
HRS_m_ds_ahead_w7 = HRS_m_ds_ahead_w7 ,HRS_m_ds_ahead_w8 = HRS_m_ds_ahead_w8 ,HRS_m_ds_ahead_w9 = HRS_m_ds_ahead_w9 ,HRS_m_ds_ahead_w10 = HRS_m_ds_ahead_w10 ,
HRS_m_ds_ahead_w11 = HRS_m_ds_ahead_w11 ,HRS_m_ds_coda_w4 = HRS_m_ds_coda_w4 ,HRS_m_ds_coda_w5 = HRS_m_ds_coda_w5 ,HRS_m_ds_coda_w6 = HRS_m_ds_coda_w6 ,
HRS_m_ds_coda_w7 = HRS_m_ds_coda_w7 ,HRS_m_ds_coda_w8 = HRS_m_ds_coda_w8 ,HRS_m_ds_coda_w9 = HRS_m_ds_coda_w9 ,HRS_m_ds_coda_w10 = HRS_m_ds_coda_w10 ,
HRS_m_ds_coda_w11 = HRS_m_ds_coda_w11 ,HRS_m_ds_wb_w4 = HRS_m_ds_wb_w4 ,HRS_m_ds_wb_w5 = HRS_m_ds_wb_w5 ,HRS_m_ds_wb_w6 = HRS_m_ds_wb_w6 ,
HRS_m_ds_wb_w7 = HRS_m_ds_wb_w7 ,HRS_m_ds_wb_w8 = HRS_m_ds_wb_w8 ,HRS_m_ds_wb_w9 = HRS_m_ds_wb_w9 ,HRS_m_ds_wb_w10 = HRS_m_ds_wb_w10 ,
HRS_m_ds_wb_w11 = HRS_m_ds_wb_w11 ,HRS_m_ds_ebb_w7 = HRS_m_ds_ebb_w7 ,HRS_m_ds_ebb_w8 = HRS_m_ds_ebb_w8 ,HRS_m_ds_ebb_w9 = HRS_m_ds_ebb_w9 ,
HRS_m_ds_ebb_w10 = HRS_m_ds_ebb_w10 ,HRS_m_ds_ebb_w11 = HRS_m_ds_ebb_w11 ,HRS_m_ds_mbb_w10 = HRS_m_ds_mbb_w10 ,HRS_m_ds_mbb_w11 = HRS_m_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- label(m.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hrs[[i]][[2]] <- car::recode(m.hrs[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hrs[[i]][[2]] <- labelled(m.hrs[[i]][[2]], labels = c(Yes=0, No=1))

  if (i!=1){
    nl <- names(l.hrs[i])
    #opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

    ml <- names(m.hrs[i])
    #opal.assign.data(o, ml , m.hrs[[i]])
    #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  
  }
}

```

```{r save, echo=FALSE}
HRS_ds_hrs_w1  <- HRS_HRS_ds_w1
HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
HRS_ds_hrs_w11 <- HRS_HRS_ds_w11

HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11

HRS_ds_coda_w4  <- HRS_CODA_ds_w4
HRS_ds_coda_w5  <- HRS_CODA_ds_w5
HRS_ds_coda_w6  <- HRS_CODA_ds_w6
HRS_ds_coda_w7  <- HRS_CODA_ds_w7
HRS_ds_coda_w8  <- HRS_CODA_ds_w8
HRS_ds_coda_w9  <- HRS_CODA_ds_w9
HRS_ds_coda_w10 <- HRS_CODA_ds_w10
HRS_ds_coda_w11 <- HRS_CODA_ds_w11

HRS_ds_wb_w4  <- HRS_WB_ds_w4
HRS_ds_wb_w5  <- HRS_WB_ds_w5
HRS_ds_wb_w6  <- HRS_WB_ds_w6
HRS_ds_wb_w7  <- HRS_WB_ds_w7
HRS_ds_wb_w8  <- HRS_WB_ds_w8
HRS_ds_wb_w9 <-  HRS_WB_ds_w9
HRS_ds_wb_w10 <- HRS_WB_ds_w10
HRS_ds_wb_w11 <- HRS_WB_ds_w11

HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
HRS_ds_ebb_w11 <- HRS_EBB_ds_w11

HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
HRS_ds_mbb_w11 <- HRS_MBB_ds_w11

l.hrs <- list(   hrs_w1 = HRS_ds_hrs_w1 ,   hrs_w2 = HRS_ds_hrs_w2 , hrs_w3 = HRS_ds_hrs_w3 , hrs_w4 = HRS_ds_hrs_w4 ,
 hrs_w5 = HRS_ds_hrs_w5 , hrs_w6 = HRS_ds_hrs_w6 , hrs_w7 = HRS_ds_hrs_w7 , hrs_w8 = HRS_ds_hrs_w8 ,
 hrs_w9 = HRS_ds_hrs_w9 , hrs_w10 = HRS_ds_hrs_w10 , hrs_w11 = HRS_ds_hrs_w11 , ahead_w2 = HRS_ds_ahead_w2 ,
 ahead_w3 = HRS_ds_ahead_w3 , ahead_w4 = HRS_ds_ahead_w4 , ahead_w5 = HRS_ds_ahead_w5 , ahead_w6 = HRS_ds_ahead_w6 ,
 ahead_w7 = HRS_ds_ahead_w7 , ahead_w8 = HRS_ds_ahead_w8 , ahead_w9 = HRS_ds_ahead_w9 , ahead_w10 = HRS_ds_ahead_w10 ,
 ahead_w11 = HRS_ds_ahead_w11 , coda_w4 = HRS_ds_coda_w4 , coda_w5 = HRS_ds_coda_w5 , coda_w6 = HRS_ds_coda_w6 ,
 coda_w7 = HRS_ds_coda_w7 , coda_w8 = HRS_ds_coda_w8 ,  coda_w9 = HRS_ds_coda_w9 ,  coda_w10 = HRS_ds_coda_w10 ,
coda_w11 = HRS_ds_coda_w11 ,  wb_w4 = HRS_ds_wb_w4 ,  wb_w5 = HRS_ds_wb_w5 ,  wb_w6 = HRS_ds_wb_w6 ,
 wb_w7 = HRS_ds_wb_w7 ,  wb_w8 = HRS_ds_wb_w8 ,  wb_w9 = HRS_ds_wb_w9 ,  wb_w10 = HRS_ds_wb_w10 ,
 wb_w11 = HRS_ds_wb_w11 ,  ebb_w7 = HRS_ds_ebb_w7 ,  ebb_w8 = HRS_ds_ebb_w8 ,  ebb_w9 = HRS_ds_ebb_w9 ,
 ebb_w10 = HRS_ds_ebb_w10 ,  ebb_w11 = HRS_ds_ebb_w11 ,  mbb_w10 = HRS_ds_mbb_w10 ,  mbb_w11 = HRS_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.

    nl <- names(l.hrs[i])
    #opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  
    iadl_phone <- l.hrs[[i]]
    save(iadl_phone, file = paste0(datafolder, "/", nl, "/iadl_phone.RData" ))
}


```


### Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

```{r summ,  echo=FALSE}

# Table HRS
t.hrs <- frq(l.hrs[[3]][2])[[1]][,c(1,2)] 
for (i in 1:11){
  t.hrs[2+i] <- frq(l.hrs[[i]][2])[[1]][,4] 
}
t.hrs[13,] <- c("n", "sample size", 
             length(l.hrs[[1]][[2]]), length(l.hrs[[2]][[2]]), length(l.hrs[[3]][[2]]),
             length(l.hrs[[4]][[2]]), length(l.hrs[[5]][[2]]), length(l.hrs[[6]][[2]]),     
             length(l.hrs[[7]][[2]]), length(l.hrs[[8]][[2]]), length(l.hrs[[9]][[2]]),
             length(l.hrs[[10]][[2]], length(l.hrs[[11]][[2]]))
names(t.hrs)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.hrs)
  

# Table AHEAD
t.ahead <- frq(l.hrs[[12]][2])[[1]][,c(1,2)] 
for (i in 1:10){
  t.ahead[2+i] <- frq(l.hrs[[i+11]][2])[[1]][,4] 
}
t.ahead[13,] <- c("n", "sample size", 
             length(l.hrs[[12]][[2]]), length(l.hrs[[13]][[2]]), length(l.hrs[[14]][[2]]),
             length(l.hrs[[15]][[2]]), length(l.hrs[[16]][[2]]), length(l.hrs[[17]][[2]]),     
             length(l.hrs[[18]][[2]]), length(l.hrs[[19]][[2]]), length(l.hrs[[20]][[2]]),
             length(l.hrs[[21]][[2]]))
names(t.ahead)<-c("val", "label", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.ahead)



# Table CODA
t.coda <- frq(l.hrs[[22]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.coda[2+i] <- frq(l.hrs[[21+i]][2])[[1]][,4] 
}
t.coda[13,] <- c("n", "sample size", 
             length(l.hrs[[22]][[2]]), length(l.hrs[[23]][[2]]), length(l.hrs[[24]][[2]]),
             length(l.hrs[[25]][[2]]), length(l.hrs[[26]][[2]]), length(l.hrs[[27]][[2]]),     
             length(l.hrs[[28]][[2]]), length(l.hrs[[29]][[2]]))
names(t.coda)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.coda)



# Table WB
t.wb <- frq(l.hrs[[30]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.wb[2+i] <- frq(l.hrs[[31+i]][2])[[1]][,4] 
}
t.wb[13,] <- c("n", "sample size", 
             length(l.hrs[[30]][[2]]), length(l.hrs[[31]][[2]]), length(l.hrs[[32]][[2]]),
             length(l.hrs[[33]][[2]]), length(l.hrs[[34]][[2]]), length(l.hrs[[35]][[2]]),     
             length(l.hrs[[36]][[2]]), length(l.hrs[[37]][[2]]))
names(t.wb)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.wb)



# Table EBB
t.ebb <- frq(l.hrs[[38]][2])[[1]][,c(1,2)] 
for (i in 1:5){
  t.ebb[2+i] <- frq(l.hrs[[37+i]][2])[[1]][,4] 
}
t.ebb[13,] <- c("n", "sample size", 
             length(l.hrs[[38]][[2]]), length(l.hrs[[39]][[2]]), length(l.hrs[[40]][[2]]),
             length(l.hrs[[41]][[2]]), length(l.hrs[[42]][[2]]))
names(t.ebb)<-c("val", "label", "w7", "w8", "w9", "w10", "w11")
kable(t.ebb)



# Table MBB
t.mbb <- frq(l.hrs[[43]][2])[[1]][,c(1,2)] 
for (i in 1:2){
  t.mbb[2+i] <- frq(l.hrs[[42+i]][2])[[1]][,4] 
}
t.mbb[13,] <- c("n", "sample size", length(l.hrs[[43]][[2]]), length(l.hrs[[44]][[2]]))
names(t.mbb)<-c("val", "label", "w10", "w11")
kable(t.mbb)


```

#Quality estimation:

'2.Cant do' was considered as maximum difficulty



<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
