---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_delDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_delDS.R')
```



# Data process

## HRS

### Wave 1 

#### Study-specific variable description



| **Name** | `R1DLRC20`|
|-|-|
| **Label** | `W1 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w1`|
| **Type of variable** |`continuous`|
| **Description** |  |








```{r assign_hrs1, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w1',
                         variables=list('R1DLRC20'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs1, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs1}
## cog_del_c
HRS_ds_hrs_w1 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w1$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w1$cog_del_c <- labelled(HRS_ds_hrs_w1[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w1[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w1$cog_del <- car::recode(HRS_ds_hrs_w1[[2]], "0:Q=0; (Q+1):20=1")
HRS_ds_hrs_w1$cog_del <- labelled(HRS_ds_hrs_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=FALSE}
vari <- HRS_ds_hrs_w1[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


vari <- HRS_ds_hrs_w1[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs1, echo=FALSE}





```

```{r read_hrs1, include=FALSE}
rm(HRS_imm)
```


### Wave 2 

#### Study-specific variable description



| **Name** | `R2HDLR20`|
|-|-|
| **Label** | `W2 DELAYED WORD RECALL-HRS94`|
| **Table name** |`HRS-HRS-w2`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs2, include=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w2',
                         variables=list('R2HDLR20'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs2, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs2}
## cog_del_c
HRS_ds_hrs_w2 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w2$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w2$cog_del_c <- labelled(HRS_ds_hrs_w2[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w2[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w2$cog_del <- car::recode(HRS_ds_hrs_w2[[2]], "0:Q=0; (Q+1):20=1")
HRS_ds_hrs_w2$cog_del <- labelled(HRS_ds_hrs_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=FALSE}
vari <- HRS_ds_hrs_w2[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w2 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w2[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs2, echo=FALSE}





```

```{r read_hrs2, include=FALSE}
rm(HRS_imm)
```



### Wave 3 

#### Study-specific variable description



| **Name** | `R3DLRC`|
|-|-|
| **Label** | `W3 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w3`|
| **Type of variable** |`continuous`|
| **Description** |  |








```{r assign_hrs3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w3',
                         variables=list('R3DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs3, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs3}
## cog_del_c
HRS_ds_hrs_w3 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w3$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w3$cog_del_c <- labelled(HRS_ds_hrs_w3[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w3[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w3$cog_del <- car::recode(HRS_ds_hrs_w3[[2]], "0:Q=0; (Q+1):20=1")
HRS_ds_hrs_w3$cog_del <- labelled(HRS_ds_hrs_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=FALSE}
vari <- HRS_ds_hrs_w3[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w3 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w3[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs3, echo=FALSE}





```

```{r read_hrs3, include=FALSE}
rm(HRS_imm)
```



### Wave 4

#### Study-specific variable description



| **Name** | `R4DLRC`|
|-|-|
| **Label** | `W4 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w4`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w4',
                         variables=list('R4DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs4, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs4}
## cog_del_c
HRS_ds_hrs_w4 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w4$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w4$cog_del_c <- labelled(HRS_ds_hrs_w4[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w4[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w4$cog_del <- car::recode(HRS_ds_hrs_w4[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w4$cog_del <- labelled(HRS_ds_hrs_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=FALSE}
vari <- HRS_ds_hrs_w4[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w4 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w4[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs4, echo=FALSE}





```

```{r read_hrs4, include=FALSE}
rm(HRS_imm)
```




### Wave 5

#### Study-specific variable description



| **Name** | `R5DLRC`|
|-|-|
| **Label** | `W5 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w5`|
| **Type of variable** |`continuous`|
| **Description** |  |








```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w5',
                         variables=list('R5DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs5, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs5}
## cog_del_c
HRS_ds_hrs_w5 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w5$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w5$cog_del_c <- labelled(HRS_ds_hrs_w5[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w5[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w5$cog_del <- car::recode(HRS_ds_hrs_w5[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w5$cog_del <- labelled(HRS_ds_hrs_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=FALSE}
vari <- HRS_ds_hrs_w5[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w5 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w5[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs5, echo=FALSE}





```

```{r read_hrs5, include=FALSE}
rm(HRS_imm)
```







### Wave 6

#### Study-specific variable description



| **Name** | `R6DLRC`|
|-|-|
| **Label** | `w6 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w6`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w6',
                         variables=list('R6DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs6, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs6}
## cog_del_c
HRS_ds_hrs_w6 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w6$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w6$cog_del_c <- labelled(HRS_ds_hrs_w6[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w6[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w6$cog_del <- car::recode(HRS_ds_hrs_w6[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w6$cog_del <- labelled(HRS_ds_hrs_w6[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=FALSE}
vari <- HRS_ds_hrs_w6[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w6 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w6[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs6, echo=FALSE}





```

```{r read_hrs6, include=FALSE}
rm(HRS_imm)
```



### Wave 7

#### Study-specific variable description



| **Name** | `R7DLRC`|
|-|-|
| **Label** | `w7 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w7`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w7',
                         variables=list('R7DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs7, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs7}
## cog_del_c
HRS_ds_hrs_w7 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w7$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w7$cog_del_c <- labelled(HRS_ds_hrs_w7[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w7[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w7$cog_del <- car::recode(HRS_ds_hrs_w7[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w7$cog_del <- labelled(HRS_ds_hrs_w7[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=FALSE}
vari <- HRS_ds_hrs_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w7 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w7[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs7, echo=FALSE}





```

```{r read_hrs7, include=FALSE}
rm(HRS_imm)
```






### Wave 8

#### Study-specific variable description



| **Name** | `R8DLRC`|
|-|-|
| **Label** | `w8 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w8`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w8',
                         variables=list('R8DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs8, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs8}
## cog_del_c
HRS_ds_hrs_w8 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w8$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w8$cog_del_c <- labelled(HRS_ds_hrs_w8[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w8[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w8$cog_del <- car::recode(HRS_ds_hrs_w8[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w8$cog_del <- labelled(HRS_ds_hrs_w8[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=FALSE}
vari <- HRS_ds_hrs_w8[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w8 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w8[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs8, echo=FALSE}





```

```{r read_hrs8, include=FALSE}
rm(HRS_imm)
```




### Wave 9

#### Study-specific variable description



| **Name** | `R9DLRC`|
|-|-|
| **Label** | `w9 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w9`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w9',
                         variables=list('R9DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs9, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs9}
## cog_del_c
HRS_ds_hrs_w9 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w9$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w9$cog_del_c <- labelled(HRS_ds_hrs_w9[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w9[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w9$cog_del <- car::recode(HRS_ds_hrs_w9[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w9$cog_del <- labelled(HRS_ds_hrs_w9[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=FALSE}
vari <- HRS_ds_hrs_w9[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w9 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w9[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs9, echo=FALSE}





```

```{r read_hrs9, include=FALSE}
rm(HRS_imm)
```





### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs10}
## cog_del_c
HRS_ds_hrs_w10 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w10$cog_del_c <- labelled(HRS_ds_hrs_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w10$cog_del <- car::recode(HRS_ds_hrs_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w10$cog_del <- labelled(HRS_ds_hrs_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=FALSE}
vari <- HRS_ds_hrs_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs10, echo=FALSE}





```

```{r read_hrs10, include=FALSE}
rm(HRS_imm)
```




### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL`|
| **Table name** |`HRS-HRS-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-HRS-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_hrs11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_hrs11}
## cog_del_c
HRS_ds_hrs_w11 <- tibble(id=HRS_imm$id)
HRS_ds_hrs_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_hrs_w11$cog_del_c <- labelled(HRS_ds_hrs_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_hrs_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_hrs_w11$cog_del <- car::recode(HRS_ds_hrs_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_hrs_w11$cog_del <- labelled(HRS_ds_hrs_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=FALSE}
vari <- HRS_ds_hrs_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_hrs_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs11, echo=FALSE}





```

```{r read_hrs11, include=FALSE}
rm(HRS_imm)
```




## AHEAD

### Wave 2

#### Study-specific variable description



| **Name** | `R2ADLR10`|
|-|-|
| **Label** | `W2 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w2`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w2',
                         variables=list('R2ADLR10'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead2, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead2}
## cog_del_c
HRS_ds_ahead_w2 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w2$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w2$cog_del_c <- labelled(HRS_ds_ahead_w2[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w2[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w2$cog_del <- car::recode(HRS_ds_ahead_w2[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w2$cog_del <- labelled(HRS_ds_ahead_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=FALSE}
vari <- HRS_ds_ahead_w2[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "Immediate recall continuous (with missing codes and non-imputed values)")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w2 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w2[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "Immediate recall categorical (with missing codes and non-imputed values)") 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead2, echo=FALSE}





```

```{r read_ahead2, include=FALSE}
rm(HRS_imm)
```




### Wave 3

#### Study-specific variable description



| **Name** | `R3DLRC`|
|-|-|
| **Label** | `w3 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w3`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w3',
                         variables=list('R3DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead3, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead3}
## cog_del_c
HRS_ds_ahead_w3 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w3$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w3$cog_del_c <- labelled(HRS_ds_ahead_w3[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w3[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w3$cog_del <- car::recode(HRS_ds_ahead_w3[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w3$cog_del <- labelled(HRS_ds_ahead_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=FALSE}
vari <- HRS_ds_ahead_w3[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w3 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w3[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead3, echo=FALSE}





```

```{r read_ahead3, include=FALSE}
rm(HRS_imm)
```





### Wave 4

#### Study-specific variable description



| **Name** | `R4DLRC`|
|-|-|
| **Label** | `w4 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w4`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w4',
                         variables=list('R4DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead4, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead4}
## cog_del_c
HRS_ds_ahead_w4 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w4$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w4$cog_del_c <- labelled(HRS_ds_ahead_w4[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w4[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w4$cog_del <- car::recode(HRS_ds_ahead_w4[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w4$cog_del <- labelled(HRS_ds_ahead_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=FALSE}
vari <- HRS_ds_ahead_w4[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w4 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w4[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead4, echo=FALSE}





```

```{r read_ahead4, include=FALSE}
rm(HRS_imm)
```



### Wave 5

#### Study-specific variable description



| **Name** | `R5DLRC`|
|-|-|
| **Label** | `w5 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w5`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w5',
                         variables=list('R5DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead5, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead5}
## cog_del_c
HRS_ds_ahead_w5 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w5$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w5$cog_del_c <- labelled(HRS_ds_ahead_w5[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w5[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w5$cog_del <- car::recode(HRS_ds_ahead_w5[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w5$cog_del <- labelled(HRS_ds_ahead_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=FALSE}
vari <- HRS_ds_ahead_w5[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w5 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w5[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead5, echo=FALSE}





```

```{r read_ahead5, include=FALSE}
rm(HRS_imm)
```




### Wave 6

#### Study-specific variable description



| **Name** | `R6DLRC`|
|-|-|
| **Label** | `w6 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w6`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w6',
                         variables=list('R6DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead6, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead6}
## cog_del_c
HRS_ds_ahead_w6 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w6$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w6$cog_del_c <- labelled(HRS_ds_ahead_w6[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w6[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w6$cog_del <- car::recode(HRS_ds_ahead_w6[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w6$cog_del <- labelled(HRS_ds_ahead_w6[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=FALSE}
vari <- HRS_ds_ahead_w6[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w6 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w6[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead6, echo=FALSE}





```

```{r read_ahead6, include=FALSE}
rm(HRS_imm)
```



### Wave 7

#### Study-specific variable description



| **Name** | `R7DLRC`|
|-|-|
| **Label** | `w7 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w7`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w7',
                         variables=list('R7DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead7, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_ahead7}
## cog_del_c
HRS_ds_ahead_w7 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w7$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w7$cog_del_c <- labelled(HRS_ds_ahead_w7[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w7[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w7$cog_del <- car::recode(HRS_ds_ahead_w7[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w7$cog_del <- labelled(HRS_ds_ahead_w7[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=FALSE}
vari <- HRS_ds_ahead_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w7 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w7[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead7, echo=FALSE}





```

```{r read_ahead7, include=FALSE}
rm(HRS_imm)
```





### Wave 8

#### Study-specific variable description



| **Name** | `R8DLRC`|
|-|-|
| **Label** | `w8 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w8`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w8',
                         variables=list('R8DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead8, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead8}
## cog_del_c
HRS_ds_ahead_w8 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w8$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w8$cog_del_c <- labelled(HRS_ds_ahead_w8[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w8[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w8$cog_del <- car::recode(HRS_ds_ahead_w8[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w8$cog_del <- labelled(HRS_ds_ahead_w8[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=FALSE}
vari <- HRS_ds_ahead_w8[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w8 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w8[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead8, echo=FALSE}





```

```{r read_ahead8, include=FALSE}
rm(HRS_imm)
```




### Wave 9

#### Study-specific variable description



| **Name** | `R9DLRC`|
|-|-|
| **Label** | `w9 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w9`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w9',
                         variables=list('R9DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead9, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead9}
## cog_del_c
HRS_ds_ahead_w9 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w9$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w9$cog_del_c <- labelled(HRS_ds_ahead_w9[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w9[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w9$cog_del <- car::recode(HRS_ds_ahead_w9[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w9$cog_del <- labelled(HRS_ds_ahead_w9[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=FALSE}
vari <- HRS_ds_ahead_w9[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w9 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w9[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead9, echo=FALSE}





```

```{r read_ahead9, include=FALSE}
rm(HRS_imm)
```




### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ahead10}
## cog_del_c
HRS_ds_ahead_w10 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w10$cog_del_c <- labelled(HRS_ds_ahead_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w10$cog_del <- car::recode(HRS_ds_ahead_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w10$cog_del <- labelled(HRS_ds_ahead_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=FALSE}
vari <- HRS_ds_ahead_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead10, echo=FALSE}





```

```{r read_ahead10, include=FALSE}
rm(HRS_imm)
```



### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-AHEAD-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-AHEAD-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ahead11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_ahead11}
## cog_del_c
HRS_ds_ahead_w11 <- tibble(id=HRS_imm$id)
HRS_ds_ahead_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ahead_w11$cog_del_c <- labelled(HRS_ds_ahead_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ahead_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ahead_w11$cog_del <- car::recode(HRS_ds_ahead_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ahead_w11$cog_del <- labelled(HRS_ds_ahead_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=FALSE}
vari <- HRS_ds_ahead_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ahead_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead11, echo=FALSE}





```

```{r read_ahead11, include=FALSE}
rm(HRS_imm)
```




## CODA

### Wave 4

#### Study-specific variable description



| **Name** | `R4DLRC`|
|-|-|
| **Label** | `w4 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w4`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w4',
                         variables=list('R4DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda4, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda4}
## cog_del_c
HRS_ds_coda_w4 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w4$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w4$cog_del_c <- labelled(HRS_ds_coda_w4[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w4[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w4$cog_del <- car::recode(HRS_ds_coda_w4[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w4$cog_del <- labelled(HRS_ds_coda_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=FALSE}
vari <- HRS_ds_coda_w4[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w4 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w4[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda4, echo=FALSE}





```

```{r read_coda4, include=FALSE}
rm(HRS_imm)
```





### Wave 5

#### Study-specific variable description



| **Name** | `R5DLRC`|
|-|-|
| **Label** | `w5 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w5`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w5',
                         variables=list('R5DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda5, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda5}
## cog_del_c
HRS_ds_coda_w5 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w5$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w5$cog_del_c <- labelled(HRS_ds_coda_w5[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w5[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w5$cog_del <- car::recode(HRS_ds_coda_w5[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w5$cog_del <- labelled(HRS_ds_coda_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=FALSE}
vari <- HRS_ds_coda_w5[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w5 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w5[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda5, echo=FALSE}





```

```{r read_coda5, include=FALSE}
rm(HRS_imm)
```




### Wave 6

#### Study-specific variable description



| **Name** | `R6DLRC`|
|-|-|
| **Label** | `w6 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w6`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w6',
                         variables=list('R6DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda6, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda6}
## cog_del_c
HRS_ds_coda_w6 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w6$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w6$cog_del_c <- labelled(HRS_ds_coda_w6[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w6[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w6$cog_del <- car::recode(HRS_ds_coda_w6[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w6$cog_del <- labelled(HRS_ds_coda_w6[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=FALSE}
vari <- HRS_ds_coda_w6[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w6 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w6[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda6, echo=FALSE}





```

```{r read_coda6, include=FALSE}
rm(HRS_imm)
```





### Wave 7

#### Study-specific variable description



| **Name** | `R7DLRC`|
|-|-|
| **Label** | `w7 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w7`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w7',
                         variables=list('R7DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda7, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_coda7}
## cog_del_c
HRS_ds_coda_w7 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w7$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w7$cog_del_c <- labelled(HRS_ds_coda_w7[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w7[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w7$cog_del <- car::recode(HRS_ds_coda_w7[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w7$cog_del <- labelled(HRS_ds_coda_w7[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=FALSE}
vari <- HRS_ds_coda_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w7 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w7[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda7, echo=FALSE}





```

```{r read_coda7, include=FALSE}
rm(HRS_imm)
```





### Wave 8

#### Study-specific variable description



| **Name** | `R8DLRC`|
|-|-|
| **Label** | `w8 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w8`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w8',
                         variables=list('R8DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda8, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda8}
## cog_del_c
HRS_ds_coda_w8 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w8$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w8$cog_del_c <- labelled(HRS_ds_coda_w8[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w8[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w8$cog_del <- car::recode(HRS_ds_coda_w8[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w8$cog_del <- labelled(HRS_ds_coda_w8[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=FALSE}
vari <- HRS_ds_coda_w8[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w8 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w8[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda8, echo=FALSE}





```

```{r read_coda8, include=FALSE}
rm(HRS_imm)
```




### Wave 9

#### Study-specific variable description



| **Name** | `R9DLRC`|
|-|-|
| **Label** | `w9 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w9`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w9',
                         variables=list('R9DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda9, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda9}
## cog_del_c
HRS_ds_coda_w9 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w9$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w9$cog_del_c <- labelled(HRS_ds_coda_w9[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w9[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w9$cog_del <- car::recode(HRS_ds_coda_w9[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w9$cog_del <- labelled(HRS_ds_coda_w9[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=FALSE}
vari <- HRS_ds_coda_w9[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w9 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w9[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda9, echo=FALSE}





```

```{r read_coda9, include=FALSE}
rm(HRS_imm)
```





### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_coda10}
## cog_del_c
HRS_ds_coda_w10 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w10$cog_del_c <- labelled(HRS_ds_coda_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w10$cog_del <- car::recode(HRS_ds_coda_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w10$cog_del <- labelled(HRS_ds_coda_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=FALSE}
vari <- HRS_ds_coda_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda10, echo=FALSE}





```

```{r read_coda10, include=FALSE}
rm(HRS_imm)
```




### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-CODA-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-CODA-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_coda11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_coda11}
## cog_del_c
HRS_ds_coda_w11 <- tibble(id=HRS_imm$id)
HRS_ds_coda_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_coda_w11$cog_del_c <- labelled(HRS_ds_coda_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_coda_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_coda_w11$cog_del <- car::recode(HRS_ds_coda_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_coda_w11$cog_del <- labelled(HRS_ds_coda_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=FALSE}
vari <- HRS_ds_coda_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_coda_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_coda11, echo=FALSE}





```

```{r read_coda11, include=FALSE}
rm(HRS_imm)
```





## The War Baby (WB)

### Wave 4

#### Study-specific variable description



| **Name** | `R4DLRC`|
|-|-|
| **Label** | `w4 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w4`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w4',
                         variables=list('R4DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb4, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb4}
## cog_del_c
HRS_ds_wb_w4 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w4$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w4$cog_del_c <- labelled(HRS_ds_wb_w4[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w4[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w4$cog_del <- car::recode(HRS_ds_wb_w4[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w4$cog_del <- labelled(HRS_ds_wb_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=FALSE}
vari <- HRS_ds_wb_w4[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w4 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w4[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb4, echo=FALSE}





```

```{r read_wb4, include=FALSE}
rm(HRS_imm)
```



### Wave 5

#### Study-specific variable description



| **Name** | `R5DLRC`|
|-|-|
| **Label** | `w5 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w5`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w5',
                         variables=list('R5DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb5, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb5}
## cog_del_c
HRS_ds_wb_w5 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w5$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w5$cog_del_c <- labelled(HRS_ds_wb_w5[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w5[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w5$cog_del <- car::recode(HRS_ds_wb_w5[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w5$cog_del <- labelled(HRS_ds_wb_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=FALSE}
vari <- HRS_ds_wb_w5[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w5 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w5[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb5, echo=FALSE}





```

```{r read_wb5, include=FALSE}
rm(HRS_imm)
```




### Wave 6

#### Study-specific variable description



| **Name** | `R6DLRC`|
|-|-|
| **Label** | `w6 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w6`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w6',
                         variables=list('R6DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb6, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb6}
## cog_del_c
HRS_ds_wb_w6 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w6$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w6$cog_del_c <- labelled(HRS_ds_wb_w6[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w6[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w6$cog_del <- car::recode(HRS_ds_wb_w6[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w6$cog_del <- labelled(HRS_ds_wb_w6[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=FALSE}
vari <- HRS_ds_wb_w6[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w6 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w6[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb6, echo=FALSE}





```

```{r read_wb6, include=FALSE}
rm(HRS_imm)
```




##### Wave 7

#### Study-specific variable description



| **Name** | `R7DLRC`|
|-|-|
| **Label** | `w7 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w7`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w7',
                         variables=list('R7DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb7, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb7}
## cog_del_c
HRS_ds_wb_w7 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w7$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w7$cog_del_c <- labelled(HRS_ds_wb_w7[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w7[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w7$cog_del <- car::recode(HRS_ds_wb_w7[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w7$cog_del <- labelled(HRS_ds_wb_w7[[3]], labels = c("<=25%"=0, ">25%"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=FALSE}
vari <- HRS_ds_wb_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w7 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


vari <- HRS_ds_wb_w7[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb7, echo=FALSE}





```

```{r read_wb7, include=FALSE}
rm(HRS_imm)
```



### Wave 8

#### Study-specific variable description



| **Name** | `R8DLRC`|
|-|-|
| **Label** | `w8 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w8`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w8',
                         variables=list('R8DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb8, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_wb8}
## cog_del_c
HRS_ds_wb_w8 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w8$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w8$cog_del_c <- labelled(HRS_ds_wb_w8[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w8[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w8$cog_del <- car::recode(HRS_ds_wb_w8[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w8$cog_del <- labelled(HRS_ds_wb_w8[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=FALSE}
vari <- HRS_ds_wb_w8[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w8 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w8[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb8, echo=FALSE}





```

```{r read_wb8, include=FALSE}
rm(HRS_imm)
```






### Wave 9

#### Study-specific variable description



| **Name** | `R9DLRC`|
|-|-|
| **Label** | `w9 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w9`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w9',
                         variables=list('R9DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb9, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb9}
## cog_del_c
HRS_ds_wb_w9 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w9$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w9$cog_del_c <- labelled(HRS_ds_wb_w9[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w9[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w9$cog_del <- car::recode(HRS_ds_wb_w9[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w9$cog_del <- labelled(HRS_ds_wb_w9[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=FALSE}
vari <- HRS_ds_wb_w9[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w9 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w9[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb9, echo=FALSE}





```

```{r read_wb9, include=FALSE}
rm(HRS_imm)
```



### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb10}
## cog_del_c
HRS_ds_wb_w10 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w10$cog_del_c <- labelled(HRS_ds_wb_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w10$cog_del <- car::recode(HRS_ds_wb_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w10$cog_del <- labelled(HRS_ds_wb_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=FALSE}
vari <- HRS_ds_wb_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_wb_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb10, echo=FALSE}





```

```{r read_wb10, include=FALSE}
rm(HRS_imm)
```




### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-WB-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-WB-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_wb11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_wb11}
## cog_del_c
HRS_ds_wb_w11 <- tibble(id=HRS_imm$id)
HRS_ds_wb_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_wb_w11$cog_del_c <- labelled(HRS_ds_wb_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_wb_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_wb_w11$cog_del <- car::recode(HRS_ds_wb_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_wb_w11$cog_del <- labelled(HRS_ds_wb_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=FALSE}
vari <- HRS_ds_wb_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


vari <- HRS_ds_wb_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_wb11, echo=FALSE}





```

```{r read_wb11, include=FALSE}
rm(HRS_imm)
```




## The Early Baby Boomer (EBB)

### Wave 7

#### Study-specific variable description



| **Name** | `R7DLRC`|
|-|-|
| **Label** | `w7 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-EBB-w7`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-EBB-w7',
                         variables=list('R7DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ebb7, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ebb7}
## cog_del_c
HRS_ds_ebb_w7 <- tibble(id=HRS_imm$id)
HRS_ds_ebb_w7$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ebb_w7$cog_del_c <- labelled(HRS_ds_ebb_w7[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ebb_w7[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ebb_w7$cog_del <- car::recode(HRS_ds_ebb_w7[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ebb_w7$cog_del <- labelled(HRS_ds_ebb_w7[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=FALSE}
vari <- HRS_ds_ebb_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w7 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ebb_w7[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb7, echo=FALSE}





```

```{r read_ebb7, include=FALSE}
rm(HRS_imm)
```



### Wave 8

#### Study-specific variable description



| **Name** | `R8DLRC`|
|-|-|
| **Label** | `w8 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-EBB-w8`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-EBB-w8',
                         variables=list('R8DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ebb8, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_ebb8}
## cog_del_c
HRS_ds_ebb_w8 <- tibble(id=HRS_imm$id)
HRS_ds_ebb_w8$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ebb_w8$cog_del_c <- labelled(HRS_ds_ebb_w8[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ebb_w8[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ebb_w8$cog_del <- car::recode(HRS_ds_ebb_w8[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ebb_w8$cog_del <- labelled(HRS_ds_ebb_w8[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=FALSE}
vari <- HRS_ds_ebb_w8[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w8 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ebb_w8[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb8, echo=FALSE}





```

```{r read_ebb8, include=FALSE}
rm(HRS_imm)
```




### Wave 9

#### Study-specific variable description



| **Name** | `R9DLRC`|
|-|-|
| **Label** | `w9 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-EBB-w9`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-EBB-w9',
                         variables=list('R9DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ebb9, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ebb9}
## cog_del_c
HRS_ds_ebb_w9 <- tibble(id=HRS_imm$id)
HRS_ds_ebb_w9$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ebb_w9$cog_del_c <- labelled(HRS_ds_ebb_w9[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ebb_w9[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ebb_w9$cog_del <- car::recode(HRS_ds_ebb_w9[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ebb_w9$cog_del <- labelled(HRS_ds_ebb_w9[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=FALSE}
vari <- HRS_ds_ebb_w9[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w9 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ebb_w9[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb9, echo=FALSE}





```

```{r read_ebb9, include=FALSE}
rm(HRS_imm)
```




### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-EBB-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-EBB-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ebb10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_ebb10}
## cog_del_c
HRS_ds_ebb_w10 <- tibble(id=HRS_imm$id)
HRS_ds_ebb_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ebb_w10$cog_del_c <- labelled(HRS_ds_ebb_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ebb_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ebb_w10$cog_del <- car::recode(HRS_ds_ebb_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ebb_w10$cog_del <- labelled(HRS_ds_ebb_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=FALSE}
vari <- HRS_ds_ebb_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_ebb_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb10, echo=FALSE}





```

```{r read_ebb10, include=FALSE}
rm(HRS_imm)
```




### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-EBB-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-EBB-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_ebb11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_ebb11}
## cog_del_c
HRS_ds_ebb_w11 <- tibble(id=HRS_imm$id)
HRS_ds_ebb_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_ebb_w11$cog_del_c <- labelled(HRS_ds_ebb_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_ebb_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_ebb_w11$cog_del <- car::recode(HRS_ds_ebb_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_ebb_w11$cog_del <- labelled(HRS_ds_ebb_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=FALSE}
vari <- HRS_ds_ebb_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


vari <- HRS_ds_ebb_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb11, echo=FALSE}





```

```{r read_ebb11, include=FALSE}
rm(HRS_imm)
```




## The Mid Baby Boomer (MBB)


### Wave 10

#### Study-specific variable description



| **Name** | `R10DLRC`|
|-|-|
| **Label** | `w10 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-MBB-w10`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-MBB-w10',
                         variables=list('R10DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_mbb10, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`


**R script**


```{r harmo_mbb10}
## cog_del_c
HRS_ds_mbb_w10 <- tibble(id=HRS_imm$id)
HRS_ds_mbb_w10$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_mbb_w10$cog_del_c <- labelled(HRS_ds_mbb_w10[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_mbb_w10[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_mbb_w10$cog_del <- car::recode(HRS_ds_mbb_w10[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_mbb_w10$cog_del <- labelled(HRS_ds_mbb_w10[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=FALSE}
vari <- HRS_ds_mbb_w10[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w10 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


vari <- HRS_ds_mbb_w10[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb10, echo=FALSE}





```

```{r read_mbb10, include=FALSE}
rm(HRS_imm)
```




### Wave 11

#### Study-specific variable description



| **Name** | `R11DLRC`|
|-|-|
| **Label** | `w11 DELAYED WORD RECALL-AHD93`|
| **Table name** |`HRS-MBB-w11`|
| **Type of variable** |`continuous`|
| **Description** |  |









```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_imm','HRS.HRS-MBB-w11',
                         variables=list('R11DLRC'), missings = TRUE)
HRS_imm <- opal.execute(o,'HRS_imm')
```

```{r local_mbb11, echo=FALSE}
vari <- HRS_imm[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attr(vari,"spss::shortName")) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_imm, aes(x=vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")





```

#### Harmonisation algorithm

The harmonized variable `cog_del_c` is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


To compute the harmonized variable `cog_del` from the study-specific variable it has to be recoded as follows

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**


```{r harmo_mbb11}
## cog_del_c
HRS_ds_mbb_w11 <- tibble(id=HRS_imm$id)
HRS_ds_mbb_w11$cog_del_c <- car::recode(HRS_imm[[2]], "NA=999")
HRS_ds_mbb_w11$cog_del_c <- labelled(HRS_ds_mbb_w11[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cog_del
Q <- quantile(car::recode(HRS_ds_mbb_w11[[2]], "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HRS_ds_mbb_w11$cog_del <- car::recode(HRS_ds_mbb_w11[[2]], "0:Q=0; (Q+1):10=1")
HRS_ds_mbb_w11$cog_del <- labelled(HRS_ds_mbb_w11[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=FALSE}
vari <- HRS_ds_mbb_w11[[2]]
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w11 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HRS_ds_mbb_w11[[3]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb11, echo=FALSE}





```

```{r read_mbb11, include=FALSE}
rm(HRS_imm)
```






## Summary of descriptive statistics of the harmonised variable `cog_del` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

<!--AUXILIAR FUNCTIONS-->

```{r helpfunctions, echo=FALSE}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}



# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){

  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names


hrs.hrs.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrs.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrs.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrs.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrs.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrs.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))




```




<!--Labelling and saving-->

```{r, echo=FALSE}

# HRS
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.hrs.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

hrslist <- lmlist # HRS list


# AHEAD
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

aheadlist <- lmlist # AHEAD list



# CODA
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

codalist <- lmlist # CODA list


# WB
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

wblist <- lmlist # WB list



# EBB
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

ebblist <- lmlist # EBB list



# MBB
# Consider only waves with some variable harmonised

l.hds <- lapply(hrs.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_del)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_del_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

mbblist <- lmlist # MBB list

```


<!--Descriptives-->


```{r summ, echo=FALSE}

# HRS
# Consider only harmonised waves
l.hds <- lapply(hrs.hrs.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- hrslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- hrslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))

}



# AHEAD
# Consider only harmonised waves
l.hds <- lapply(hrs.ahead.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- aheadlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- aheadlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
}


# CODA
# Consider only harmonised waves
l.hds <- lapply(hrs.coda.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- codalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- codalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
}




# WB
# Consider only harmonised waves
l.hds <- lapply(hrs.wb.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- wblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- wblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
}



# EBB
# Consider only harmonised waves
l.hds <- lapply(hrs.ebb.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- ebblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- ebblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
}



# MBB
# Consider only harmonised waves
l.hds <- lapply(hrs.mbb.cw, function(wname) if(hd_vbl %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


if(length(l.hds)>0){
  lmlist[[1]] <- mbblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- mbblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_del))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
}

```








## Summary of descriptive statistics of the harmonised variable `cog_del_c` accross populations and waves





```{r summ_c, echo=FALSE}

# HRS
# Consider only harmonised waves
l.hds <- lapply(hrs.hrs.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- hrslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- hrslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}




# AHEAD
# Consider only harmonised waves
l.hds <- lapply(hrs.ahead.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- aheadlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- aheadlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}



# CODA
# Consider only harmonised waves
l.hds <- lapply(hrs.coda.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- codalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- codalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}




# WB
# Consider only harmonised waves
l.hds <- lapply(hrs.wb.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- wblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- wblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}





# EBB
# Consider only harmonised waves
l.hds <- lapply(hrs.ebb.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- ebblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- ebblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}


# MBB
# Consider only harmonised waves
l.hds <- lapply(hrs.mbb.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("HRS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- mbblist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- mbblist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_del_c))
}


```



### Quality estimation
The variable RwDLRC has imputed values. Each wave has a number of imputed values equal to the number of ones in the variable RwFDLRC.




<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
