---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## HRS

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R1SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`
   + `2 = Very good`
   + `3 = Good`
   + `4 = Fair`
   + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w1, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w1_srh','HRS.HRS-HRS-w1', variables=list('R1SHLT'), missings = TRUE)
HRS_HRS_w1_srh <- opal.execute(o,'HRS_HRS_w1_srh')
```


```{r local HRS w1, include=FALSE}
vari <- HRS_HRS_w1_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w1_srh, aes(x=factor(R1SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w1}
HRS_HRS_ds_w1 <- tibble(id=HRS_HRS_w1_srh$id)
HRS_HRS_ds_w1$srh <- car::recode(HRS_HRS_w1_srh$R1SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w1$srh <- labelled(HRS_HRS_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w1, include=FALSE}
vari <- HRS_HRS_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w1, include=FALSE}
AfterH <- table(HRS_HRS_ds_w1$srh)
X<-table(HRS_HRS_w1_srh$R1SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w1_srh$R1SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w1, echo=FALSE}
label(HRS_HRS_ds_w1$srh) <- ds_label_all
srh <- HRS_HRS_ds_w1
save(srh, file = "../RData/hrs_w1/srh.RData")
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R2SHLT`
* Label: `Self-report of health`															 
* Categories:
  + `1 = Excellent`
  + `2 = Very good`
  + `3 = Good`
  + `4 = Fair`
  + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w2, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w2_srh','HRS.HRS-HRS-w2', variables=list('R2SHLT'), missings = TRUE)
HRS_HRS_w2_srh <- opal.execute(o,'HRS_HRS_w2_srh')
```


```{r local HRS w2, include=FALSE}
vari <- HRS_HRS_w2_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w2_srh, aes(x=factor(R2SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w2}
HRS_HRS_ds_w2 <- tibble(id=HRS_HRS_w2_srh$id)
HRS_HRS_ds_w2$srh <- car::recode(HRS_HRS_w2_srh$R2SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w2$srh <- labelled(HRS_HRS_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w2, include=FALSE}
vari <- HRS_HRS_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w2, include=FALSE}
AfterH <- table(HRS_HRS_ds_w2$srh)
X<-table(HRS_HRS_w2_srh$R2SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w1_srh$R1SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w2, echo=FALSE}
label(HRS_HRS_ds_w2$srh) <- ds_label_all
srh <- HRS_HRS_ds_w2
save(srh, file = "../RData/hrs_w2/srh.RData")
```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R3SHLT`
* Label: `Self-report of health`															 
* Categories:
  + `1 = Excellent`    
  + `2 = Very good`    
  + `3 = Good`    
  + `4 = Fair`     
* Missings
   + `NA`


```{r assign HRS w3, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w3_srh','HRS.HRS-HRS-w3', variables=list('R3SHLT'), missings = TRUE)
HRS_HRS_w3_srh <- opal.execute(o,'HRS_HRS_w3_srh')
```


```{r local HRS w3, include=FALSE}
vari <- HRS_HRS_w3_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w3_srh, aes(x=factor(R3SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w3}
HRS_HRS_ds_w3 <- tibble(id=HRS_HRS_w3_srh$id)
HRS_HRS_ds_w3$srh <- car::recode(HRS_HRS_w3_srh$R3SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w3$srh <- labelled(HRS_HRS_ds_w3$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w3, include=FALSE}
vari <- HRS_HRS_ds_w3$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w3, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w3, include=FALSE}
AfterH <- table(HRS_HRS_ds_w3$srh)
X<-table(HRS_HRS_w3_srh$R3SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w3_srh$R3SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w3, echo=FALSE}
label(HRS_HRS_ds_w3$srh) <- ds_label_all
srh <- HRS_HRS_ds_w3
save(srh, file = "../RData/hrs_w3/srh.RData")
```



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4SHLT`
* Label: `Self-report of health`															 
* Categories:
    + `1 = Excellent`    
    + `2 = Very good`    
    + `3 = Good`    
    + `4 = Fair`    
    + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w4, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w4_srh','HRS.HRS-HRS-w4', variables=list('R4SHLT'), missings = TRUE)
HRS_HRS_w4_srh <- opal.execute(o,'HRS_HRS_w4_srh')
```


```{r local HRS w4, include=FALSE}
vari <- HRS_HRS_w4_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w4_srh, aes(x=factor(R4SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w4}
HRS_HRS_ds_w4 <- tibble(id=HRS_HRS_w4_srh$id)
HRS_HRS_ds_w4$srh <- car::recode(HRS_HRS_w4_srh$R4SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w4$srh <- labelled(HRS_HRS_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w4, include=FALSE}
vari <- HRS_HRS_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w4, include=FALSE}
AfterH <- table(HRS_HRS_ds_w4$srh)
X<-table(HRS_HRS_w4_srh$R4SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w4_srh$R4SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w4, echo=FALSE}
label(HRS_HRS_ds_w4$srh) <- ds_label_all
srh <- HRS_HRS_ds_w4
save(srh, file = "../RData/hrs_w4/srh.RData")
```



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5SHLT`
* Label: `Self-report of health`															 
* Categories:
  + `1 = Excellent`    
  + `2 = Very good`    
  + `3 = Good`    
  + `4 = Fair`    
  + `5 = Poor` 
* Missings
   + `NA`


```{r assign HRS w5, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w5_srh','HRS.HRS-HRS-w5', variables=list('R5SHLT'), missings = TRUE)
HRS_HRS_w5_srh <- opal.execute(o,'HRS_HRS_w5_srh')
```


```{r local HRS w5, include=FALSE}
vari <- HRS_HRS_w5_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w5_srh, aes(x=factor(R5SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w5}
HRS_HRS_ds_w5 <- tibble(id=HRS_HRS_w5_srh$id)
HRS_HRS_ds_w5$srh <- car::recode(HRS_HRS_w5_srh$R5SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w5$srh <- labelled(HRS_HRS_ds_w5$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w5, include=FALSE}
vari <- HRS_HRS_ds_w5$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w5, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w5, include=FALSE}
AfterH <- table(HRS_HRS_ds_w5$srh)
X<-table(HRS_HRS_w5_srh$R5SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w5_srh$R5SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w5, echo=FALSE}
label(HRS_HRS_ds_w5$srh) <- ds_label_all
srh <- HRS_HRS_ds_w5
save(srh, file = "../RData/hrs_w5/srh.RData")
```



### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w6, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w6_srh','HRS.HRS-HRS-w6', variables=list('R6SHLT'), missings = TRUE)
HRS_HRS_w6_srh <- opal.execute(o,'HRS_HRS_w6_srh')
```


```{r local HRS w6, include=FALSE}
vari <- HRS_HRS_w6_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w6_srh, aes(x=factor(R6SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w6}
HRS_HRS_ds_w6 <- tibble(id=HRS_HRS_w6_srh$id)
HRS_HRS_ds_w6$srh <- car::recode(HRS_HRS_w6_srh$R6SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w6$srh <- labelled(HRS_HRS_ds_w6$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w6, include=FALSE}
vari <- HRS_HRS_ds_w6$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w6, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w6, include=FALSE}
AfterH <- table(HRS_HRS_ds_w6$srh)
X<-table(HRS_HRS_w6_srh$R6SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w6_srh$R6SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w6, echo=FALSE}
label(HRS_HRS_ds_w6$srh) <- ds_label_all
srh <- HRS_HRS_ds_w6
save(srh, file = "../RData/hrs_w6/srh.RData")
```




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor` 
* Missings
   + `NA`


```{r assign HRS w7, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w7_srh','HRS.HRS-HRS-w7', variables=list('R7SHLT'), missings = TRUE)
HRS_HRS_w7_srh <- opal.execute(o,'HRS_HRS_w7_srh')
```


```{r local HRS w7, include=FALSE}
vari <- HRS_HRS_w7_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w7_srh, aes(x=factor(R7SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w7}
HRS_HRS_ds_w7 <- tibble(id=HRS_HRS_w7_srh$id)
HRS_HRS_ds_w7$srh <- car::recode(HRS_HRS_w7_srh$R7SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w7$srh <- labelled(HRS_HRS_ds_w7$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w7, include=FALSE}
vari <- HRS_HRS_ds_w7$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w7, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w7, include=FALSE}
AfterH <- table(HRS_HRS_ds_w7$srh)
X<-table(HRS_HRS_w7_srh$R7SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w7_srh$R7SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w7, echo=FALSE}
label(HRS_HRS_ds_w7$srh) <- ds_label_all
srh <- HRS_HRS_ds_w7
save(srh, file = "../RData/hrs_w7/srh.RData")
```




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w8, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w8_srh','HRS.HRS-HRS-w8', variables=list('R8SHLT'), missings = TRUE)
HRS_HRS_w8_srh <- opal.execute(o,'HRS_HRS_w8_srh')
```


```{r local HRS w8, include=FALSE}
vari <- HRS_HRS_w8_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w8_srh, aes(x=factor(R8SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w8}
HRS_HRS_ds_w8 <- tibble(id=HRS_HRS_w8_srh$id)
HRS_HRS_ds_w8$srh <- car::recode(HRS_HRS_w8_srh$R8SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w8$srh <- labelled(HRS_HRS_ds_w8$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w8, include=FALSE}
vari <- HRS_HRS_ds_w8$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w8, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w8, include=FALSE}
AfterH <- table(HRS_HRS_ds_w8$srh)
X<-table(HRS_HRS_w8_srh$R8SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w8_srh$R8SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w8, echo=FALSE}
label(HRS_HRS_ds_w8$srh) <- ds_label_all
srh <- HRS_HRS_ds_w8
save(srh, file = "../RData/hrs_w8/srh.RData")
```




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w9, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w9_srh','HRS.HRS-HRS-w9', variables=list('R9SHLT'), missings = TRUE)
HRS_HRS_w9_srh <- opal.execute(o,'HRS_HRS_w9_srh')
```


```{r local HRS w9, include=FALSE}
vari <- HRS_HRS_w9_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w9_srh, aes(x=factor(R9SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w9}
HRS_HRS_ds_w9 <- tibble(id=HRS_HRS_w9_srh$id)
HRS_HRS_ds_w9$srh <- car::recode(HRS_HRS_w9_srh$R9SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w9$srh <- labelled(HRS_HRS_ds_w9$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w9, include=FALSE}
vari <- HRS_HRS_ds_w9$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w9, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w9, include=FALSE}
AfterH <- table(HRS_HRS_ds_w9$srh)
X<-table(HRS_HRS_w9_srh$R9SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w9_srh$R9SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w9, echo=FALSE}
label(HRS_HRS_ds_w9$srh) <- ds_label_all
srh <- HRS_HRS_ds_w9
save(srh, file = "../RData/hrs_w9/srh.RData")
```




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign HRS w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w10_srh','HRS.HRS-HRS-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_HRS_w10_srh <- opal.execute(o,'HRS_HRS_w10_srh')
```


```{r local HRS w10, include=FALSE}
vari <- HRS_HRS_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w10}
HRS_HRS_ds_w10 <- tibble(id=HRS_HRS_w10_srh$id)
HRS_HRS_ds_w10$srh <- car::recode(HRS_HRS_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w10$srh <- labelled(HRS_HRS_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w10, include=FALSE}
vari <- HRS_HRS_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w10, include=FALSE}
AfterH <- table(HRS_HRS_ds_w10$srh)
X<-table(HRS_HRS_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w10, echo=FALSE}
label(HRS_HRS_ds_w10$srh) <- ds_label_all
srh <- HRS_HRS_ds_w10
save(srh, file = "../RData/hrs_w10/srh.RData")
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor` 
* Missings
   + `NA`


```{r assign HRS w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_HRS_w11_srh','HRS.HRS-HRS-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_HRS_w11_srh <- opal.execute(o,'HRS_HRS_w11_srh')
```


```{r local HRS w11, include=FALSE}
vari <- HRS_HRS_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_HRS_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo HRS w11}
HRS_HRS_ds_w11 <- tibble(id=HRS_HRS_w11_srh$id)
HRS_HRS_ds_w11$srh <- car::recode(HRS_HRS_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_HRS_ds_w11$srh <- labelled(HRS_HRS_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript HRS w11, include=FALSE}
vari <- HRS_HRS_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_HRS_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation HRS w11, include=FALSE}
AfterH <- table(HRS_HRS_ds_w11$srh)
X<-table(HRS_HRS_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_HRS_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL HRS w11, echo=FALSE}
label(HRS_HRS_ds_w11$srh) <- ds_label_all
srh <- HRS_HRS_ds_w11
save(srh, file = "../RData/hrs_w11/srh.RData")
```





## AHEAD

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R2SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w2, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w2_srh','HRS.HRS-AHEAD-w2', variables=list('R2SHLT'), missings = TRUE)
HRS_AHEAD_w2_srh <- opal.execute(o,'HRS_AHEAD_w2_srh')
```


```{r local AHEAD w2, include=FALSE}
vari <- HRS_AHEAD_w2_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w2_srh, aes(x=factor(R2SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w2}
HRS_AHEAD_ds_w2 <- tibble(id=HRS_AHEAD_w2_srh$id)
HRS_AHEAD_ds_w2$srh <- car::recode(HRS_AHEAD_w2_srh$R2SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w2$srh <- labelled(HRS_AHEAD_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w2, include=FALSE}
vari <- HRS_AHEAD_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w2, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w2$srh)
X<-table(HRS_AHEAD_w2_srh$R2SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w2_srh$R2SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w2, echo=FALSE}
label(HRS_AHEAD_ds_w2$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w2
save(srh, file = "../RData/ahead_w2/srh.RData")
```


### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R3SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor` 
* Missings
   + `NA`


```{r assign AHEAD w3, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w3_srh','HRS.HRS-AHEAD-w3', variables=list('R3SHLT'), missings = TRUE)
HRS_AHEAD_w3_srh <- opal.execute(o,'HRS_AHEAD_w3_srh')
```


```{r local AHEAD w3, include=FALSE}
vari <- HRS_AHEAD_w3_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w3_srh, aes(x=factor(R3SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w3}
HRS_AHEAD_ds_w3 <- tibble(id=HRS_AHEAD_w3_srh$id)
HRS_AHEAD_ds_w3$srh <- car::recode(HRS_AHEAD_w3_srh$R3SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w3$srh <- labelled(HRS_AHEAD_ds_w3$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w3, include=FALSE}
vari <- HRS_AHEAD_ds_w3$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w3, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w3, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w3$srh)
X<-table(HRS_AHEAD_w3_srh$R3SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w3_srh$R3SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w3, echo=FALSE}
label(HRS_AHEAD_ds_w3$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w3
save(srh, file = "../RData/ahead_w3/srh.RData")
```



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w4, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w4_srh','HRS.HRS-AHEAD-w4', variables=list('R4SHLT'), missings = TRUE)
HRS_AHEAD_w4_srh <- opal.execute(o,'HRS_AHEAD_w4_srh')
```


```{r local AHEAD w4, include=FALSE}
vari <- HRS_AHEAD_w4_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w4_srh, aes(x=factor(R4SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w4}
HRS_AHEAD_ds_w4 <- tibble(id=HRS_AHEAD_w4_srh$id)
HRS_AHEAD_ds_w4$srh <- car::recode(HRS_AHEAD_w4_srh$R4SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w4$srh <- labelled(HRS_AHEAD_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w4, include=FALSE}
vari <- HRS_AHEAD_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w4, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w4$srh)
X<-table(HRS_AHEAD_w4_srh$R4SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w4_srh$R4SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w4, echo=FALSE}
label(HRS_AHEAD_ds_w4$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w4
save(srh, file = "../RData/ahead_w4/srh.RData")
```


### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w5, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w5_srh','HRS.HRS-AHEAD-w5', variables=list('R5SHLT'), missings = TRUE)
HRS_AHEAD_w5_srh <- opal.execute(o,'HRS_AHEAD_w5_srh')
```


```{r local AHEAD w5, include=FALSE}
vari <- HRS_AHEAD_w5_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w5_srh, aes(x=factor(R5SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w5}
HRS_AHEAD_ds_w5 <- tibble(id=HRS_AHEAD_w5_srh$id)
HRS_AHEAD_ds_w5$srh <- car::recode(HRS_AHEAD_w5_srh$R5SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w5$srh <- labelled(HRS_AHEAD_ds_w5$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w5, include=FALSE}
vari <- HRS_AHEAD_ds_w5$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w5, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w5, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w5$srh)
X<-table(HRS_AHEAD_w5_srh$R5SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w5_srh$R5SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w5, echo=FALSE}
label(HRS_AHEAD_ds_w5$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w5
save(srh, file = "../RData/ahead_w5/srh.RData")
```




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w6, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w6_srh','HRS.HRS-AHEAD-w6', variables=list('R6SHLT'), missings = TRUE)
HRS_AHEAD_w6_srh <- opal.execute(o,'HRS_AHEAD_w6_srh')
```


```{r local AHEAD w6, include=FALSE}
vari <- HRS_AHEAD_w6_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w6_srh, aes(x=factor(R6SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w6}
HRS_AHEAD_ds_w6 <- tibble(id=HRS_AHEAD_w6_srh$id)
HRS_AHEAD_ds_w6$srh <- car::recode(HRS_AHEAD_w6_srh$R6SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w6$srh <- labelled(HRS_AHEAD_ds_w6$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w6, include=FALSE}
vari <- HRS_AHEAD_ds_w6$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w6, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w6, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w6$srh)
X<-table(HRS_AHEAD_w6_srh$R6SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w6_srh$R6SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w6, echo=FALSE}
label(HRS_AHEAD_ds_w6$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w6
save(srh, file = "../RData/ahead_w6/srh.RData")
```




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w7, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w7_srh','HRS.HRS-AHEAD-w7', variables=list('R7SHLT'), missings = TRUE)
HRS_AHEAD_w7_srh <- opal.execute(o,'HRS_AHEAD_w7_srh')
```


```{r local AHEAD w7, include=FALSE}
vari <- HRS_AHEAD_w7_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w7_srh, aes(x=factor(R7SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w7}
HRS_AHEAD_ds_w7 <- tibble(id=HRS_AHEAD_w7_srh$id)
HRS_AHEAD_ds_w7$srh <- car::recode(HRS_AHEAD_w7_srh$R7SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w7$srh <- labelled(HRS_AHEAD_ds_w7$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w7, include=FALSE}
vari <- HRS_AHEAD_ds_w7$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w7, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w7, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w7$srh)
X<-table(HRS_AHEAD_w7_srh$R7SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w7_srh$R7SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w7, echo=FALSE}
label(HRS_AHEAD_ds_w7$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w7
save(srh, file = "../RData/ahead_w7/srh.RData")
```



### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w8, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w8_srh','HRS.HRS-AHEAD-w8', variables=list('R8SHLT'), missings = TRUE)
HRS_AHEAD_w8_srh <- opal.execute(o,'HRS_AHEAD_w8_srh')
```


```{r local AHEAD w8, include=FALSE}
vari <- HRS_AHEAD_w8_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w8_srh, aes(x=factor(R8SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w8}
HRS_AHEAD_ds_w8 <- tibble(id=HRS_AHEAD_w8_srh$id)
HRS_AHEAD_ds_w8$srh <- car::recode(HRS_AHEAD_w8_srh$R8SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w8$srh <- labelled(HRS_AHEAD_ds_w8$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w8, include=FALSE}
vari <- HRS_AHEAD_ds_w8$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w8, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w8, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w8$srh)
X<-table(HRS_AHEAD_w8_srh$R8SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w8_srh$R8SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w8, echo=FALSE}
label(HRS_AHEAD_ds_w8$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w8
save(srh, file = "../RData/ahead_w8/srh.RData")
```



### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w9, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w9_srh','HRS.HRS-AHEAD-w9', variables=list('R9SHLT'), missings = TRUE)
HRS_AHEAD_w9_srh <- opal.execute(o,'HRS_AHEAD_w9_srh')
```


```{r local AHEAD w9, include=FALSE}
vari <- HRS_AHEAD_w9_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w9_srh, aes(x=factor(R9SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w9}
HRS_AHEAD_ds_w9 <- tibble(id=HRS_AHEAD_w9_srh$id)
HRS_AHEAD_ds_w9$srh <- car::recode(HRS_AHEAD_w9_srh$R9SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w9$srh <- labelled(HRS_AHEAD_ds_w9$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w9, include=FALSE}
vari <- HRS_AHEAD_ds_w9$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w9, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w9, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w9$srh)
X<-table(HRS_AHEAD_w9_srh$R9SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w9_srh$R9SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w9, echo=FALSE}
label(HRS_AHEAD_ds_w9$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w9
save(srh, file = "../RData/ahead_w9/srh.RData")
```




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w10_srh','HRS.HRS-AHEAD-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_AHEAD_w10_srh <- opal.execute(o,'HRS_AHEAD_w10_srh')
```


```{r local AHEAD w10, include=FALSE}
vari <- HRS_AHEAD_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w10}
HRS_AHEAD_ds_w10 <- tibble(id=HRS_AHEAD_w10_srh$id)
HRS_AHEAD_ds_w10$srh <- car::recode(HRS_AHEAD_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w10$srh <- labelled(HRS_AHEAD_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w10, include=FALSE}
vari <- HRS_AHEAD_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w10, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w10$srh)
X<-table(HRS_AHEAD_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w10, echo=FALSE}
label(HRS_AHEAD_ds_w10$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w10
save(srh, file = "../RData/ahead_w10/srh.RData")
```


### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign AHEAD w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_AHEAD_w11_srh','HRS.HRS-AHEAD-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_AHEAD_w11_srh <- opal.execute(o,'HRS_AHEAD_w11_srh')
```


```{r local AHEAD w11, include=FALSE}
vari <- HRS_AHEAD_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_AHEAD_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo AHEAD w11}
HRS_AHEAD_ds_w11 <- tibble(id=HRS_AHEAD_w11_srh$id)
HRS_AHEAD_ds_w11$srh <- car::recode(HRS_AHEAD_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_AHEAD_ds_w11$srh <- labelled(HRS_AHEAD_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript AHEAD w11, include=FALSE}
vari <- HRS_AHEAD_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_AHEAD_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation AHEAD w11, include=FALSE}
AfterH <- table(HRS_AHEAD_ds_w11$srh)
X<-table(HRS_AHEAD_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_AHEAD_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL AHEAD w11, echo=FALSE}
label(HRS_AHEAD_ds_w11$srh) <- ds_label_all
srh <- HRS_AHEAD_ds_w11
save(srh, file = "../RData/ahead_w11/srh.RData")
```





## CODA

### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w4, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w4_srh','HRS.HRS-CODA-w4', variables=list('R4SHLT'), missings = TRUE)
HRS_CODA_w4_srh <- opal.execute(o,'HRS_CODA_w4_srh')
```


```{r local CODA w4, include=FALSE}
vari <- HRS_CODA_w4_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w4_srh, aes(x=factor(R4SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo CODA w4}
HRS_CODA_ds_w4 <- tibble(id=HRS_CODA_w4_srh$id)
HRS_CODA_ds_w4$srh <- car::recode(HRS_CODA_w4_srh$R4SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w4$srh <- labelled(HRS_CODA_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w4, include=FALSE}
vari <- HRS_CODA_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w4, include=FALSE}
AfterH <- table(HRS_CODA_ds_w4$srh)
X<-table(HRS_CODA_w4_srh$R4SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w4_srh$R4SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w4, echo=FALSE}
label(HRS_CODA_ds_w4$srh) <- ds_label_all
srh <- HRS_CODA_ds_w4
save(srh, file = "../RData/coda_w4/srh.RData")
```



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w5, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w5_srh','HRS.HRS-CODA-w5', variables=list('R5SHLT'), missings = TRUE)
HRS_CODA_w5_srh <- opal.execute(o,'HRS_CODA_w5_srh')
```


```{r local CODA w5, include=FALSE}
vari <- HRS_CODA_w5_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w5_srh, aes(x=factor(R5SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo CODA w5}
HRS_CODA_ds_w5 <- tibble(id=HRS_CODA_w5_srh$id)
HRS_CODA_ds_w5$srh <- car::recode(HRS_CODA_w5_srh$R5SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w5$srh <- labelled(HRS_CODA_ds_w5$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w5, include=FALSE}
vari <- HRS_CODA_ds_w5$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w5, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w5, include=FALSE}
AfterH <- table(HRS_CODA_ds_w5$srh)
X<-table(HRS_CODA_w5_srh$R5SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w5_srh$R5SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w5, echo=FALSE}
label(HRS_CODA_ds_w5$srh) <- ds_label_all
srh <- HRS_CODA_ds_w5
save(srh, file = "../RData/coda_w5/srh.RData")
```



### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w6, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w6_srh','HRS.HRS-CODA-w6', variables=list('R6SHLT'), missings = TRUE)
HRS_CODA_w6_srh <- opal.execute(o,'HRS_CODA_w6_srh')
```


```{r local CODA w6, include=FALSE}
vari <- HRS_CODA_w6_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w6_srh, aes(x=factor(R6SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo CODA w6}
HRS_CODA_ds_w6 <- tibble(id=HRS_CODA_w6_srh$id)
HRS_CODA_ds_w6$srh <- car::recode(HRS_CODA_w6_srh$R6SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w6$srh <- labelled(HRS_CODA_ds_w6$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w6, include=FALSE}
vari <- HRS_CODA_ds_w6$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w6, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w6, include=FALSE}
AfterH <- table(HRS_CODA_ds_w6$srh)
X<-table(HRS_CODA_w6_srh$R6SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w6_srh$R6SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w6, echo=FALSE}
label(HRS_CODA_ds_w6$srh) <- ds_label_all
srh <- HRS_CODA_ds_w6
save(srh, file = "../RData/coda_w6/srh.RData")
```




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`   
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w7, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w7_srh','HRS.HRS-CODA-w7', variables=list('R7SHLT'), missings = TRUE)
HRS_CODA_w7_srh <- opal.execute(o,'HRS_CODA_w7_srh')
```


```{r local CODA w7, include=FALSE}
vari <- HRS_CODA_w7_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w7_srh, aes(x=factor(R7SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo CODA w7}
HRS_CODA_ds_w7 <- tibble(id=HRS_CODA_w7_srh$id)
HRS_CODA_ds_w7$srh <- car::recode(HRS_CODA_w7_srh$R7SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w7$srh <- labelled(HRS_CODA_ds_w7$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w7, include=FALSE}
vari <- HRS_CODA_ds_w7$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w7, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w7, include=FALSE}
AfterH <- table(HRS_CODA_ds_w7$srh)
X<-table(HRS_CODA_w7_srh$R7SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w7_srh$R7SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w7, echo=FALSE}
label(HRS_CODA_ds_w7$srh) <- ds_label_all
srh <- HRS_CODA_ds_w7
save(srh, file = "../RData/coda_w7/srh.RData")
```




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w8, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w8_srh','HRS.HRS-CODA-w8', variables=list('R8SHLT'), missings = TRUE)
HRS_CODA_w8_srh <- opal.execute(o,'HRS_CODA_w8_srh')
```


```{r local CODA w8, include=FALSE}
vari <- HRS_CODA_w8_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w8_srh, aes(x=factor(R8SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo CODA w8}
HRS_CODA_ds_w8 <- tibble(id=HRS_CODA_w8_srh$id)
HRS_CODA_ds_w8$srh <- car::recode(HRS_CODA_w8_srh$R8SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w8$srh <- labelled(HRS_CODA_ds_w8$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w8, include=FALSE}
vari <- HRS_CODA_ds_w8$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w8, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w8, include=FALSE}
AfterH <- table(HRS_CODA_ds_w8$srh)
X<-table(HRS_CODA_w8_srh$R8SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w8_srh$R8SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w8, echo=FALSE}
label(HRS_CODA_ds_w8$srh) <- ds_label_all
srh <- HRS_CODA_ds_w8
save(srh, file = "../RData/coda_w8/srh.RData")
```




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w9, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w9_srh','HRS.HRS-CODA-w9', variables=list('R9SHLT'), missings = TRUE)
HRS_CODA_w9_srh <- opal.execute(o,'HRS_CODA_w9_srh')
```


```{r local CODA w9, include=FALSE}
vari <- HRS_CODA_w9_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w9_srh, aes(x=factor(R9SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `NA into 999`

**R script:**

```{r harmo CODA w9}
HRS_CODA_ds_w9 <- tibble(id=HRS_CODA_w9_srh$id)
HRS_CODA_ds_w9$srh <- car::recode(HRS_CODA_w9_srh$R9SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w9$srh <- labelled(HRS_CODA_ds_w9$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w9, include=FALSE}
vari <- HRS_CODA_ds_w9$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w9, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w9, include=FALSE}
AfterH <- table(HRS_CODA_ds_w9$srh)
X<-table(HRS_CODA_w9_srh$R9SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w9_srh$R9SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w9, echo=FALSE}
label(HRS_CODA_ds_w9$srh) <- ds_label_all
srh <- HRS_CODA_ds_w9
save(srh, file = "../RData/coda_w9/srh.RData")
```




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w10_srh','HRS.HRS-CODA-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_CODA_w10_srh <- opal.execute(o,'HRS_CODA_w10_srh')
```


```{r local CODA w10, include=FALSE}
vari <- HRS_CODA_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `NA into 999`

**R script:**

```{r harmo CODA w10}
HRS_CODA_ds_w10 <- tibble(id=HRS_CODA_w10_srh$id)
HRS_CODA_ds_w10$srh <- car::recode(HRS_CODA_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w10$srh <- labelled(HRS_CODA_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w10, include=FALSE}
vari <- HRS_CODA_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w10, include=FALSE}
AfterH <- table(HRS_CODA_ds_w10$srh)
X<-table(HRS_CODA_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w10, echo=FALSE}
label(HRS_CODA_ds_w10$srh) <- ds_label_all
srh <- HRS_CODA_ds_w10
save(srh, file = "../RData/coda_w10/srh.RData")
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign CODA w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_CODA_w11_srh','HRS.HRS-CODA-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_CODA_w11_srh <- opal.execute(o,'HRS_CODA_w11_srh')
```


```{r local CODA w11, include=FALSE}
vari <- HRS_CODA_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_CODA_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `NA into 999`

**R script:**

```{r harmo CODA w11}
HRS_CODA_ds_w11 <- tibble(id=HRS_CODA_w11_srh$id)
HRS_CODA_ds_w11$srh <- car::recode(HRS_CODA_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_CODA_ds_w11$srh <- labelled(HRS_CODA_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript CODA w11, include=FALSE}
vari <- HRS_CODA_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_CODA_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation CODA w11, include=FALSE}
AfterH <- table(HRS_CODA_ds_w11$srh)
X<-table(HRS_CODA_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_CODA_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL CODA w11, echo=FALSE}
label(HRS_CODA_ds_w11$srh) <- ds_label_all
srh <- HRS_CODA_ds_w11
save(srh, file = "../RData/coda_w11/srh.RData")
```





## WB

### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R4SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w4, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w4_srh','HRS.HRS-WB-w4', variables=list('R4SHLT'), missings = TRUE)
HRS_WB_w4_srh <- opal.execute(o,'HRS_WB_w4_srh')
```


```{r local WB w4, include=FALSE}
vari <- HRS_WB_w4_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w4_srh, aes(x=factor(R4SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w4}
HRS_WB_ds_w4 <- tibble(id=HRS_WB_w4_srh$id)
HRS_WB_ds_w4$srh <- car::recode(HRS_WB_w4_srh$R4SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w4$srh <- labelled(HRS_WB_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w4, include=FALSE}
vari <- HRS_WB_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w4, include=FALSE}
AfterH <- table(HRS_WB_ds_w4$srh)
X<-table(HRS_WB_w4_srh$R4SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w4_srh$R4SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w4, echo=FALSE}
label(HRS_WB_ds_w4$srh) <- ds_label_all
srh <- HRS_WB_ds_w4
save(srh, file = "../RData/wb_w4/srh.RData")
```



### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R5SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w5, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w5_srh','HRS.HRS-WB-w5', variables=list('R5SHLT'), missings = TRUE)
HRS_WB_w5_srh <- opal.execute(o,'HRS_WB_w5_srh')
```


```{r local WB w5, include=FALSE}
vari <- HRS_WB_w5_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w5_srh, aes(x=factor(R5SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w5}
HRS_WB_ds_w5 <- tibble(id=HRS_WB_w5_srh$id)
HRS_WB_ds_w5$srh <- car::recode(HRS_WB_w5_srh$R5SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w5$srh <- labelled(HRS_WB_ds_w5$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w5, include=FALSE}
vari <- HRS_WB_ds_w5$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w5, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w5, include=FALSE}
AfterH <- table(HRS_WB_ds_w5$srh)
X<-table(HRS_WB_w5_srh$R5SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w5_srh$R5SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w5, echo=FALSE}
label(HRS_WB_ds_w5$srh) <- ds_label_all
srh <- HRS_WB_ds_w5
save(srh, file = "../RData/wb_w5/srh.RData")
```




### Wave 6

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R6SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w6, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w6_srh','HRS.HRS-WB-w6', variables=list('R6SHLT'), missings = TRUE)
HRS_WB_w6_srh <- opal.execute(o,'HRS_WB_w6_srh')
```


```{r local WB w6, include=FALSE}
vari <- HRS_WB_w6_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w6_srh, aes(x=factor(R6SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w6}
HRS_WB_ds_w6 <- tibble(id=HRS_WB_w6_srh$id)
HRS_WB_ds_w6$srh <- car::recode(HRS_WB_w6_srh$R6SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w6$srh <- labelled(HRS_WB_ds_w6$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w6, include=FALSE}
vari <- HRS_WB_ds_w6$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w6, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w6, include=FALSE}
AfterH <- table(HRS_WB_ds_w6$srh)
X<-table(HRS_WB_w6_srh$R6SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w6_srh$R6SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w6, echo=FALSE}
label(HRS_WB_ds_w6$srh) <- ds_label_all
srh <- HRS_WB_ds_w6
save(srh, file = "../RData/wb_w6/srh.RData")
```




### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w7, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w7_srh','HRS.HRS-WB-w7', variables=list('R7SHLT'), missings = TRUE)
HRS_WB_w7_srh <- opal.execute(o,'HRS_WB_w7_srh')
```


```{r local WB w7, include=FALSE}
vari <- HRS_WB_w7_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w7_srh, aes(x=factor(R7SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w7}
HRS_WB_ds_w7 <- tibble(id=HRS_WB_w7_srh$id)
HRS_WB_ds_w7$srh <- car::recode(HRS_WB_w7_srh$R7SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w7$srh <- labelled(HRS_WB_ds_w7$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w7, include=FALSE}
vari <- HRS_WB_ds_w7$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w7, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w7, include=FALSE}
AfterH <- table(HRS_WB_ds_w7$srh)
X<-table(HRS_WB_w7_srh$R7SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w7_srh$R7SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w7, echo=FALSE}
label(HRS_WB_ds_w7$srh) <- ds_label_all
srh <- HRS_WB_ds_w7
save(srh, file = "../RData/wb_w7/srh.RData")
```




### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor` 
* Missings
   + `NA`


```{r assign WB w8, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w8_srh','HRS.HRS-WB-w8', variables=list('R8SHLT'), missings = TRUE)
HRS_WB_w8_srh <- opal.execute(o,'HRS_WB_w8_srh')
```


```{r local WB w8, include=FALSE}
vari <- HRS_WB_w8_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w8_srh, aes(x=factor(R8SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w8}
HRS_WB_ds_w8 <- tibble(id=HRS_WB_w8_srh$id)
HRS_WB_ds_w8$srh <- car::recode(HRS_WB_w8_srh$R8SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w8$srh <- labelled(HRS_WB_ds_w8$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w8, include=FALSE}
vari <- HRS_WB_ds_w8$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w8, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w8, include=FALSE}
AfterH <- table(HRS_WB_ds_w8$srh)
X<-table(HRS_WB_w8_srh$R8SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w8_srh$R8SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w8, echo=FALSE}
label(HRS_WB_ds_w8$srh) <- ds_label_all
srh <- HRS_WB_ds_w8
save(srh, file = "../RData/wb_w8/srh.RData")
```




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w9, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w9_srh','HRS.HRS-WB-w9', variables=list('R9SHLT'), missings = TRUE)
HRS_WB_w9_srh <- opal.execute(o,'HRS_WB_w9_srh')
```


```{r local WB w9, include=FALSE}
vari <- HRS_WB_w9_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w9_srh, aes(x=factor(R9SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w9}
HRS_WB_ds_w9 <- tibble(id=HRS_WB_w9_srh$id)
HRS_WB_ds_w9$srh <- car::recode(HRS_WB_w9_srh$R9SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w9$srh <- labelled(HRS_WB_ds_w9$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w9, include=FALSE}
vari <- HRS_WB_ds_w9$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w9, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w9, include=FALSE}
AfterH <- table(HRS_WB_ds_w9$srh)
X<-table(HRS_WB_w9_srh$R9SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w9_srh$R9SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w9, echo=FALSE}
label(HRS_WB_ds_w9$srh) <- ds_label_all
srh <- HRS_WB_ds_w9
save(srh, file = "../RData/wb_w9/srh.RData")
```




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w10_srh','HRS.HRS-WB-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_WB_w10_srh <- opal.execute(o,'HRS_WB_w10_srh')
```


```{r local WB w10, include=FALSE}
vari <- HRS_WB_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w10}
HRS_WB_ds_w10 <- tibble(id=HRS_WB_w10_srh$id)
HRS_WB_ds_w10$srh <- car::recode(HRS_WB_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w10$srh <- labelled(HRS_WB_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w10, include=FALSE}
vari <- HRS_WB_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w10, include=FALSE}
AfterH <- table(HRS_WB_ds_w10$srh)
X<-table(HRS_WB_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w10, echo=FALSE}
label(HRS_WB_ds_w10$srh) <- ds_label_all
srh <- HRS_WB_ds_w10
save(srh, file = "../RData/wb_w10/srh.RData")
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign WB w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_WB_w11_srh','HRS.HRS-WB-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_WB_w11_srh <- opal.execute(o,'HRS_WB_w11_srh')
```


```{r local WB w11, include=FALSE}
vari <- HRS_WB_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_WB_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo WB w11}
HRS_WB_ds_w11 <- tibble(id=HRS_WB_w11_srh$id)
HRS_WB_ds_w11$srh <- car::recode(HRS_WB_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_WB_ds_w11$srh <- labelled(HRS_WB_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript WB w11, include=FALSE}
vari <- HRS_WB_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_WB_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation WB w11, include=FALSE}
AfterH <- table(HRS_WB_ds_w11$srh)
X<-table(HRS_WB_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_WB_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL WB w11, echo=FALSE}
label(HRS_WB_ds_w11$srh) <- ds_label_all
srh <- HRS_WB_ds_w11
save(srh, file = "../RData/wb_w11/srh.RData")
```





## EBB

### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R7SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign EBB w7, include=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w7_srh','HRS.HRS-EBB-w7', variables=list('R7SHLT'), missings = TRUE)
HRS_EBB_w7_srh <- opal.execute(o,'HRS_EBB_w7_srh')
```


```{r local EBB w7, include=FALSE}
vari <- HRS_EBB_w7_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w7_srh, aes(x=factor(R7SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo EBB w7}
HRS_EBB_ds_w7 <- tibble(id=HRS_EBB_w7_srh$id)
HRS_EBB_ds_w7$srh <- car::recode(HRS_EBB_w7_srh$R7SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_EBB_ds_w7$srh <- labelled(HRS_EBB_ds_w7$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w7, include=FALSE}
vari <- HRS_EBB_ds_w7$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w7, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w7, include=FALSE}
AfterH <- table(HRS_EBB_ds_w7$srh)
X<-table(HRS_EBB_w7_srh$R7SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_EBB_w7_srh$R7SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL EBB w7, echo=FALSE}
label(HRS_EBB_ds_w7$srh) <- ds_label_all
srh <- HRS_EBB_ds_w7
save(srh, file = "../RData/ebb_w7/srh.RData")
```



### Wave 8

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R8SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign EBB w8, include=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w8_srh','HRS.HRS-EBB-w8', variables=list('R8SHLT'), missings = TRUE)
HRS_EBB_w8_srh <- opal.execute(o,'HRS_EBB_w8_srh')
```


```{r local EBB w8, include=FALSE}
vari <- HRS_EBB_w8_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w8_srh, aes(x=factor(R8SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo EBB w8}
HRS_EBB_ds_w8 <- tibble(id=HRS_EBB_w8_srh$id)
HRS_EBB_ds_w8$srh <- car::recode(HRS_EBB_w8_srh$R8SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_EBB_ds_w8$srh <- labelled(HRS_EBB_ds_w8$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w8, include=FALSE}
vari <- HRS_EBB_ds_w8$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w8, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w8, include=FALSE}
AfterH <- table(HRS_EBB_ds_w8$srh)
X<-table(HRS_EBB_w8_srh$R8SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_EBB_w8_srh$R8SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL EBB w8, echo=FALSE}
label(HRS_EBB_ds_w8$srh) <- ds_label_all
srh <- HRS_EBB_ds_w8
save(srh, file = "../RData/ebb_w8/srh.RData")
```




### Wave 9

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R9SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign EBB w9, include=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w9_srh','HRS.HRS-EBB-w9', variables=list('R9SHLT'), missings = TRUE)
HRS_EBB_w9_srh <- opal.execute(o,'HRS_EBB_w9_srh')
```


```{r local EBB w9, include=FALSE}
vari <- HRS_EBB_w9_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w9_srh, aes(x=factor(R9SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo EBB w9}
HRS_EBB_ds_w9 <- tibble(id=HRS_EBB_w9_srh$id)
HRS_EBB_ds_w9$srh <- car::recode(HRS_EBB_w9_srh$R9SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_EBB_ds_w9$srh <- labelled(HRS_EBB_ds_w9$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w9, include=FALSE}
vari <- HRS_EBB_ds_w9$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w9, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w9, include=FALSE}
AfterH <- table(HRS_EBB_ds_w9$srh)
X<-table(HRS_EBB_w9_srh$R9SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_EBB_w9_srh$R9SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL EBB w9, echo=FALSE}
label(HRS_EBB_ds_w9$srh) <- ds_label_all
srh <- HRS_EBB_ds_w9
save(srh, file = "../RData/ebb_w9/srh.RData")
```




### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign EBB w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w10_srh','HRS.HRS-EBB-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_EBB_w10_srh <- opal.execute(o,'HRS_EBB_w10_srh')
```


```{r local EBB w10, include=FALSE}
vari <- HRS_EBB_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo EBB w10}
HRS_EBB_ds_w10 <- tibble(id=HRS_EBB_w10_srh$id)
HRS_EBB_ds_w10$srh <- car::recode(HRS_EBB_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_EBB_ds_w10$srh <- labelled(HRS_EBB_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w10, include=FALSE}
vari <- HRS_EBB_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w10, include=FALSE}
AfterH <- table(HRS_EBB_ds_w10$srh)
X<-table(HRS_EBB_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_EBB_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL EBB w10, echo=FALSE}
label(HRS_EBB_ds_w10$srh) <- ds_label_all
srh <- HRS_EBB_ds_w10
save(srh, file = "../RData/ebb_w10/srh.RData")
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign EBB w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_EBB_w11_srh','HRS.HRS-EBB-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_EBB_w11_srh <- opal.execute(o,'HRS_EBB_w11_srh')
```


```{r local EBB w11, include=FALSE}
vari <- HRS_EBB_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_EBB_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo EBB w11}
HRS_EBB_ds_w11 <- tibble(id=HRS_EBB_w11_srh$id)
HRS_EBB_ds_w11$srh <- car::recode(HRS_EBB_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_EBB_ds_w11$srh <- labelled(HRS_EBB_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript EBB w11, include=FALSE}
vari <- HRS_EBB_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_EBB_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation EBB w11, include=FALSE}
AfterH <- table(HRS_EBB_ds_w11$srh)
X<-table(HRS_EBB_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_EBB_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL EBB w11, echo=FALSE}
label(HRS_EBB_ds_w11$srh) <- ds_label_all
srh <- HRS_EBB_ds_w11
save(srh, file = "../RData/ebb_w11/srh.RData")
```



#### MBB

### Wave 10

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R10SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign MBB w10, include=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w10_srh','HRS.HRS-MBB-w10', variables=list('R10SHLT'), missings = TRUE)
HRS_MBB_w10_srh <- opal.execute(o,'HRS_MBB_w10_srh')
```


```{r local MBB w10, include=FALSE}
vari <- HRS_MBB_w10_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_MBB_w10_srh, aes(x=factor(R10SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo MBB w10}
HRS_MBB_ds_w10 <- tibble(id=HRS_MBB_w10_srh$id)
HRS_MBB_ds_w10$srh <- car::recode(HRS_MBB_w10_srh$R10SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_MBB_ds_w10$srh <- labelled(HRS_MBB_ds_w10$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w10, include=FALSE}
vari <- HRS_MBB_ds_w10$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_MBB_ds_w10, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w10, include=FALSE}
AfterH <- table(HRS_MBB_ds_w10$srh)
X<-table(HRS_MBB_w10_srh$R10SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_MBB_w10_srh$R10SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL MBB w10, echo=FALSE}
label(HRS_MBB_ds_w10$srh) <- ds_label_all
srh <- HRS_MBB_ds_w10
save(srh, file = "../RData/mbb_w10/srh.RData")
```



### Wave 11

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `R11SHLT`
* Label: `Self-report of health`															 
* Categories:
   + `1 = Excellent`    
   + `2 = Very good`    
   + `3 = Good`    
   + `4 = Fair`    
   + `5 = Poor`
* Missings
   + `NA`


```{r assign MBB w11, include=FALSE}
opal.assign.table.tibble(o, 'HRS_MBB_w11_srh','HRS.HRS-MBB-w11', variables=list('R11SHLT'), missings = TRUE)
HRS_MBB_w11_srh <- opal.execute(o,'HRS_MBB_w11_srh')
```


```{r local MBB w11, include=FALSE}
vari <- HRS_MBB_w11_srh[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_MBB_w11_srh, aes(x=factor(R11SHLT))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4 into 2`
* `5 into 3`
* `NA into 999`

**R script:**

```{r harmo MBB w11}
HRS_MBB_ds_w11 <- tibble(id=HRS_MBB_w11_srh$id)
HRS_MBB_ds_w11$srh <- car::recode(HRS_MBB_w11_srh$R11SHLT, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA='999'")
HRS_MBB_ds_w11$srh <- labelled(HRS_MBB_ds_w11$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript MBB w11, include=FALSE}
vari <- HRS_MBB_ds_w11$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_MBB_ds_w11, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self-report of health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation MBB w11, include=FALSE}
AfterH <- table(HRS_MBB_ds_w11$srh)
X<-table(HRS_MBB_w11_srh$R11SHLT)
BeforeH <- c(sum(X[1:3]),X[4:5],sum(is.na(HRS_MBB_w11_srh$R11SHLT)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->2","5->3","NA->999") 
C
```

```{r importOPAL MBB w11, echo=FALSE}
label(HRS_MBB_ds_w11$srh) <- ds_label_all
srh <- HRS_MBB_ds_w11
save(srh, file = "../RData/mbb_w11/srh.RData")
```

### Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

<!--- ############################# Import to OPAL ###########################-->
```{r importOPAL, echo=FALSE}
HRS_m_ds_hrs_w1  <- HRS_ds_hrs_w1  <- HRS_HRS_ds_w1
HRS_m_ds_hrs_w2  <- HRS_ds_hrs_w2  <- HRS_HRS_ds_w2
HRS_m_ds_hrs_w3  <- HRS_ds_hrs_w3  <- HRS_HRS_ds_w3
HRS_m_ds_hrs_w4  <- HRS_ds_hrs_w4  <- HRS_HRS_ds_w4
HRS_m_ds_hrs_w5  <- HRS_ds_hrs_w5  <- HRS_HRS_ds_w5
HRS_m_ds_hrs_w6  <- HRS_ds_hrs_w6  <- HRS_HRS_ds_w6
HRS_m_ds_hrs_w7  <- HRS_ds_hrs_w7  <- HRS_HRS_ds_w7
HRS_m_ds_hrs_w8  <- HRS_ds_hrs_w8  <- HRS_HRS_ds_w8
HRS_m_ds_hrs_w9  <- HRS_ds_hrs_w9  <- HRS_HRS_ds_w9
HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10 <- HRS_HRS_ds_w10
HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11 <- HRS_HRS_ds_w11

HRS_m_ds_ahead_w2  <- HRS_ds_ahead_w2  <- HRS_AHEAD_ds_w2
HRS_m_ds_ahead_w3  <- HRS_ds_ahead_w3  <- HRS_AHEAD_ds_w3
HRS_m_ds_ahead_w4  <- HRS_ds_ahead_w4  <- HRS_AHEAD_ds_w4
HRS_m_ds_ahead_w5  <- HRS_ds_ahead_w5  <- HRS_AHEAD_ds_w5
HRS_m_ds_ahead_w6  <- HRS_ds_ahead_w6  <- HRS_AHEAD_ds_w6
HRS_m_ds_ahead_w7  <- HRS_ds_ahead_w7  <- HRS_AHEAD_ds_w7
HRS_m_ds_ahead_w8  <- HRS_ds_ahead_w8  <- HRS_AHEAD_ds_w8
HRS_m_ds_ahead_w9  <- HRS_ds_ahead_w9  <- HRS_AHEAD_ds_w9
HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10 <- HRS_AHEAD_ds_w10
HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11 <- HRS_AHEAD_ds_w11

HRS_m_ds_coda_w4  <- HRS_ds_coda_w4  <- HRS_CODA_ds_w4
HRS_m_ds_coda_w5  <- HRS_ds_coda_w5  <- HRS_CODA_ds_w5
HRS_m_ds_coda_w6  <- HRS_ds_coda_w6  <- HRS_CODA_ds_w6
HRS_m_ds_coda_w7  <- HRS_ds_coda_w7  <- HRS_CODA_ds_w7
HRS_m_ds_coda_w8  <- HRS_ds_coda_w8  <- HRS_CODA_ds_w8
HRS_m_ds_coda_w9  <- HRS_ds_coda_w9  <- HRS_CODA_ds_w9
HRS_m_ds_coda_w10 <- HRS_ds_coda_w10 <- HRS_CODA_ds_w10
HRS_m_ds_coda_w11 <- HRS_ds_coda_w11 <- HRS_CODA_ds_w11

HRS_m_ds_wb_w4  <- HRS_ds_wb_w4  <- HRS_WB_ds_w4
HRS_m_ds_wb_w5  <- HRS_ds_wb_w5  <- HRS_WB_ds_w5
HRS_m_ds_wb_w6  <- HRS_ds_wb_w6  <- HRS_WB_ds_w6
HRS_m_ds_wb_w7  <- HRS_ds_wb_w7  <- HRS_WB_ds_w7
HRS_m_ds_wb_w8  <- HRS_ds_wb_w8  <- HRS_WB_ds_w8
HRS_m_ds_wb_w9  <- HRS_ds_wb_w9  <- HRS_WB_ds_w9
HRS_m_ds_wb_w10 <- HRS_ds_wb_w10 <- HRS_WB_ds_w10
HRS_m_ds_wb_w11 <- HRS_ds_wb_w11 <- HRS_WB_ds_w11

HRS_m_ds_ebb_w7  <- HRS_ds_ebb_w7  <- HRS_EBB_ds_w7
HRS_m_ds_ebb_w8  <- HRS_ds_ebb_w8  <- HRS_EBB_ds_w8
HRS_m_ds_ebb_w9  <- HRS_ds_ebb_w9  <- HRS_EBB_ds_w9
HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10 <- HRS_EBB_ds_w10
HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11 <- HRS_EBB_ds_w11

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10 <- HRS_MBB_ds_w10
HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11 <- HRS_MBB_ds_w11

l.hrs <- list(HRS_ds_hrs_w1 = HRS_ds_hrs_w1 , HRS_ds_hrs_w2 = HRS_ds_hrs_w2 ,HRS_ds_hrs_w3 = HRS_ds_hrs_w3 ,HRS_ds_hrs_w4 = HRS_ds_hrs_w4 ,
HRS_ds_hrs_w5 = HRS_ds_hrs_w5 ,HRS_ds_hrs_w6 = HRS_ds_hrs_w6 ,HRS_ds_hrs_w7 = HRS_ds_hrs_w7 ,HRS_ds_hrs_w8 = HRS_ds_hrs_w8 ,
HRS_ds_hrs_w9 = HRS_ds_hrs_w9 ,HRS_ds_hrs_w10 = HRS_ds_hrs_w10 ,HRS_ds_hrs_w11 = HRS_ds_hrs_w11 ,HRS_ds_ahead_w2 = HRS_ds_ahead_w2 ,
HRS_ds_ahead_w3 = HRS_ds_ahead_w3 ,HRS_ds_ahead_w4 = HRS_ds_ahead_w4 ,HRS_ds_ahead_w5 = HRS_ds_ahead_w5 ,HRS_ds_ahead_w6 = HRS_ds_ahead_w6 ,
HRS_ds_ahead_w7 = HRS_ds_ahead_w7 ,HRS_ds_ahead_w8 = HRS_ds_ahead_w8 ,HRS_ds_ahead_w9 = HRS_ds_ahead_w9 ,HRS_ds_ahead_w10 = HRS_ds_ahead_w10 ,
HRS_ds_ahead_w11 = HRS_ds_ahead_w11 ,HRS_ds_coda_w4 = HRS_ds_coda_w4 ,HRS_ds_coda_w5 = HRS_ds_coda_w5 ,HRS_ds_coda_w6 = HRS_ds_coda_w6 ,
HRS_ds_coda_w7 = HRS_ds_coda_w7 ,HRS_ds_coda_w8 = HRS_ds_coda_w8 ,HRS_ds_coda_w9 = HRS_ds_coda_w9 ,HRS_ds_coda_w10 = HRS_ds_coda_w10 ,
HRS_ds_coda_w11 = HRS_ds_coda_w11 ,HRS_ds_wb_w4 = HRS_ds_wb_w4 ,HRS_ds_wb_w5 = HRS_ds_wb_w5 ,HRS_ds_wb_w6 = HRS_ds_wb_w6 ,
HRS_ds_wb_w7 = HRS_ds_wb_w7 ,HRS_ds_wb_w8 = HRS_ds_wb_w8 ,HRS_ds_wb_w9 = HRS_ds_wb_w9 ,HRS_ds_wb_w10 = HRS_ds_wb_w10 ,
HRS_ds_wb_w11 = HRS_ds_wb_w11 ,HRS_ds_ebb_w7 = HRS_ds_ebb_w7 ,HRS_ds_ebb_w8 = HRS_ds_ebb_w8 ,HRS_ds_ebb_w9 = HRS_ds_ebb_w9 ,
HRS_ds_ebb_w10 = HRS_ds_ebb_w10 ,HRS_ds_ebb_w11 = HRS_ds_ebb_w11 ,HRS_ds_mbb_w10 = HRS_ds_mbb_w10 ,HRS_ds_mbb_w11 = HRS_ds_mbb_w11)

m.hrs <- list(HRS_m_ds_hrs_w1 = HRS_m_ds_hrs_w1 , HRS_m_ds_hrs_w2 = HRS_m_ds_hrs_w2 ,HRS_m_ds_hrs_w3 = HRS_m_ds_hrs_w3 ,HRS_m_ds_hrs_w4 = HRS_m_ds_hrs_w4 ,
HRS_m_ds_hrs_w5 = HRS_m_ds_hrs_w5 ,HRS_m_ds_hrs_w6 = HRS_m_ds_hrs_w6 ,HRS_m_ds_hrs_w7 = HRS_m_ds_hrs_w7 ,HRS_m_ds_hrs_w8 = HRS_m_ds_hrs_w8 ,
HRS_m_ds_hrs_w9 = HRS_m_ds_hrs_w9 ,HRS_m_ds_hrs_w10 = HRS_m_ds_hrs_w10 ,HRS_m_ds_hrs_w11 = HRS_m_ds_hrs_w11 ,HRS_m_ds_ahead_w2 = HRS_m_ds_ahead_w2 ,
HRS_m_ds_ahead_w3 = HRS_m_ds_ahead_w3 ,HRS_m_ds_ahead_w4 = HRS_m_ds_ahead_w4 ,HRS_m_ds_ahead_w5 = HRS_m_ds_ahead_w5 ,HRS_m_ds_ahead_w6 = HRS_m_ds_ahead_w6 ,
HRS_m_ds_ahead_w7 = HRS_m_ds_ahead_w7 ,HRS_m_ds_ahead_w8 = HRS_m_ds_ahead_w8 ,HRS_m_ds_ahead_w9 = HRS_m_ds_ahead_w9 ,HRS_m_ds_ahead_w10 = HRS_m_ds_ahead_w10 ,
HRS_m_ds_ahead_w11 = HRS_m_ds_ahead_w11 ,HRS_m_ds_coda_w4 = HRS_m_ds_coda_w4 ,HRS_m_ds_coda_w5 = HRS_m_ds_coda_w5 ,HRS_m_ds_coda_w6 = HRS_m_ds_coda_w6 ,
HRS_m_ds_coda_w7 = HRS_m_ds_coda_w7 ,HRS_m_ds_coda_w8 = HRS_m_ds_coda_w8 ,HRS_m_ds_coda_w9 = HRS_m_ds_coda_w9 ,HRS_m_ds_coda_w10 = HRS_m_ds_coda_w10 ,
HRS_m_ds_coda_w11 = HRS_m_ds_coda_w11 ,HRS_m_ds_wb_w4 = HRS_m_ds_wb_w4 ,HRS_m_ds_wb_w5 = HRS_m_ds_wb_w5 ,HRS_m_ds_wb_w6 = HRS_m_ds_wb_w6 ,
HRS_m_ds_wb_w7 = HRS_m_ds_wb_w7 ,HRS_m_ds_wb_w8 = HRS_m_ds_wb_w8 ,HRS_m_ds_wb_w9 = HRS_m_ds_wb_w9 ,HRS_m_ds_wb_w10 = HRS_m_ds_wb_w10 ,
HRS_m_ds_wb_w11 = HRS_m_ds_wb_w11 ,HRS_m_ds_ebb_w7 = HRS_m_ds_ebb_w7 ,HRS_m_ds_ebb_w8 = HRS_m_ds_ebb_w8 ,HRS_m_ds_ebb_w9 = HRS_m_ds_ebb_w9 ,
HRS_m_ds_ebb_w10 = HRS_m_ds_ebb_w10 ,HRS_m_ds_ebb_w11 = HRS_m_ds_ebb_w11 ,HRS_m_ds_mbb_w10 = HRS_m_ds_mbb_w10 ,HRS_m_ds_mbb_w11 = HRS_m_ds_mbb_w11)

for(i in 1:length(l.hrs)) {
  label(l.hrs[[i]][[2]]) <- label(m.hrs[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hrs[[i]][[2]] <- car::recode(m.hrs[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hrs[[i]][[2]] <- labelled(m.hrs[[i]][[2]], labels = c(Good=1, Average_Fair_Moderate=2, Poor=3))

    nl <- names(l.hrs[i])
    #opal.assign.data(o, nl , l.hrs[[i]])
    #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

    ml <- names(m.hrs[i])
    #opal.assign.data(o, ml , m.hrs[[i]])
    #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}

```

### Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

```{r summ}

# Table HRS
t.hrs <- frq(l.hrs[[3]][2])[[1]][,c(1,2)] 
for (i in 1:11){
  t.hrs[2+i] <- frq(l.hrs[[i]][2])[[1]][,4] 
}
t.hrs[13,] <- c("n", "sample size", 
             length(l.hrs[[1]][[2]]), length(l.hrs[[2]][[2]]), length(l.hrs[[3]][[2]]),
             length(l.hrs[[4]][[2]]), length(l.hrs[[5]][[2]]), length(l.hrs[[6]][[2]]),     
             length(l.hrs[[7]][[2]]), length(l.hrs[[8]][[2]]), length(l.hrs[[9]][[2]]),
             length(l.hrs[[10]][[2]]), length(l.hrs[[11]][[2]]))
names(t.hrs)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.hrs)
  

# Table AHEAD
t.ahead <- frq(l.hrs[[12]][2])[[1]][,c(1,2)] 
for (i in 1:10){
  t.ahead[2+i] <- frq(l.hrs[[i+11]][2])[[1]][,4] 
}
t.ahead[13,] <- c("n", "sample size", 
             length(l.hrs[[12]][[2]]), length(l.hrs[[13]][[2]]), length(l.hrs[[14]][[2]]),
             length(l.hrs[[15]][[2]]), length(l.hrs[[16]][[2]]), length(l.hrs[[17]][[2]]),     
             length(l.hrs[[18]][[2]]), length(l.hrs[[19]][[2]]), length(l.hrs[[20]][[2]]),
             length(l.hrs[[21]][[2]]))
names(t.ahead)<-c("val", "label", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.ahead)



# Table CODA
t.coda <- frq(l.hrs[[22]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.coda[2+i] <- frq(l.hrs[[21+i]][2])[[1]][,4] 
}
t.coda[13,] <- c("n", "sample size", 
             length(l.hrs[[22]][[2]]), length(l.hrs[[23]][[2]]), length(l.hrs[[24]][[2]]),
             length(l.hrs[[25]][[2]]), length(l.hrs[[26]][[2]]), length(l.hrs[[27]][[2]]),     
             length(l.hrs[[28]][[2]]), length(l.hrs[[29]][[2]]))
names(t.coda)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.coda)



# Table WB
t.wb <- frq(l.hrs[[30]][2])[[1]][,c(1,2)] 
for (i in 1:8){
  t.wb[2+i] <- frq(l.hrs[[31+i]][2])[[1]][,4] 
}
t.wb[13,] <- c("n", "sample size", 
             length(l.hrs[[30]][[2]]), length(l.hrs[[31]][[2]]), length(l.hrs[[32]][[2]]),
             length(l.hrs[[33]][[2]]), length(l.hrs[[34]][[2]]), length(l.hrs[[35]][[2]]),     
             length(l.hrs[[36]][[2]]), length(l.hrs[[37]][[2]]))
names(t.wb)<-c("val", "label", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
kable(t.wb)



# Table EBB
t.ebb <- frq(l.hrs[[38]][2])[[1]][,c(1,2)] 
for (i in 1:5){
  t.ebb[2+i] <- frq(l.hrs[[37+i]][2])[[1]][,4] 
}
t.ebb[13,] <- c("n", "sample size", 
             length(l.hrs[[38]][[2]]), length(l.hrs[[39]][[2]]), length(l.hrs[[40]][[2]]),
             length(l.hrs[[41]][[2]]), length(l.hrs[[42]][[2]]))
names(t.ebb)<-c("val", "label", "w7", "w8", "w9", "w10", "w11")
kable(t.ebb)



# Table MBB
t.mbb <- frq(l.hrs[[43]][2])[[1]][,c(1,2)] 
for (i in 1:2){
  t.mbb[2+i] <- frq(l.hrs[[42+i]][2])[[1]][,4] 
}
t.mbb[13,] <- c("n", "sample size", length(l.hrs[[43]][[2]]), length(l.hrs[[44]][[2]]))
names(t.mbb)<-c("val", "label", "w10", "w11")
kable(t.mbb)

```


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
