---
title: "Cognition"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_stat`
* Variable label: `Cognitive status of the participant, assessed by the Mini Mental State Examination`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:
* Comments: `The test used is the Mini Mental State Examination (MMSE). Two values have been created for the potential variable: 0=no cognitive impairment (when the score is greater or equal to 23) and 1=cognitive impairment (when the score is lower to 23).`

**Code** | **Category Label**
-------- | ------------------------
0        | no cognitive impairment
1        | cognitive impairment

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Cognitive status"
ds_label_all <- "Cognitive status of the participant, assessed by the Mini Mental State Examination"
```


<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

There is no variable. 




## Polish population

### Wave 1 

There is no variable. 





### Wave 2 

#### Study-specific variable description

| **Name** | `q1004_MMSE`|
|-|-|
| **Label** | `MMSE points`|
| **Table name** | `Courage_Poland_w2` |
| **Description** |  |

```{r assign_pol2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_cog','Courage.Courage_Poland_w2',
                         variables=list('q1004_MMSE'), missings = TRUE)
COURAGE_cog <- opal.execute(o,'COURAGE_cog')
```

```{r local_pol2,  echo=FALSE}
vari <- COURAGE_cog$q1004_MMSE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "MMSE points") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_cog, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `q1004_MMSE < 24 into 1` 
* `q1004_MMSE >= 24 into 0`
* `NA into 999`

**R script:**
```{r harmo_pol2,   echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_cog$id)
COURAGE_ds_pol_w2$cog_stat <- car::recode(COURAGE_cog[[2]], "lo:23=1; 24:900=0; NA=999")
COURAGE_ds_pol_w2$cog_stat <- labelled(COURAGE_ds_pol_w2$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol2,  echo=FALSE}
vari <- COURAGE_ds_pol_w2$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2,  echo=FALSE}
BeforeH <- c(sum(na.omit(COURAGE_cog[[2]])>23),sum(na.omit(COURAGE_cog[[2]])<=23), sum(is.na(COURAGE_cog[[2]])))
AfterH <- table(COURAGE_ds_pol_w2$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(24-30)->0","(0-23)->1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_pol2,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_pol_w2$cog_stat) <- ds_label_all
cog_stat <- COURAGE_ds_pol_w2
save(cog_stat, file = "../RData/pol_w2/cog_stat.RData")
rm(cog_stat, COURAGE_cog)

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$cog_stat <- car::recode(COURAGE_m_ds_pol_w2$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```






## Spanish population

### Wave 1 

There is no variable. 




### Wave 2 

#### Study-specific variable description

| **Name** | `sum_MMSEc`|
|-|-|
| **Label** | `Rounded and corrected MMSE total score`|
| **Table name** | `Courage_Spain_w2_1` |
| **Description** |  |

```{r assign_spain2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_cog','Courage.Courage_Spain_w2_1',
                         variables=list('sum_MMSEc'), missings = TRUE)
COURAGE_cog <- opal.execute(o,'COURAGE_cog')
```

```{r local_spain2,  echo=FALSE}
vari <- COURAGE_cog$sum_MMSEc
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "MMSE points") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_cog, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `sum_MMSEc < 24 into 1` 
* `sum_MMSEc >= 24 into 0`
* `NA into 999`

**R script:**

```{r harmo_spain2,   echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_cog$id)
COURAGE_ds_spain_w2$cog_stat <- car::recode(COURAGE_cog[[2]], "lo:23=1; 24:900=0; NA=999")
COURAGE_ds_spain_w2$cog_stat <- labelled(COURAGE_ds_spain_w2$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain2,  echo=FALSE}
vari <- COURAGE_ds_spain_w2$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2,  echo=FALSE}
BeforeH <- c(sum(na.omit(COURAGE_cog[[2]])>23),sum(na.omit(COURAGE_cog[[2]])<=23), sum(is.na(COURAGE_cog[[2]])))
AfterH <- table(COURAGE_ds_spain_w2$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(23-30)->0","(0-22)->1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_spain2,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_spain_w2$cog_stat) <- ds_label_all
cog_stat <- COURAGE_ds_spain_w2
save(cog_stat, file = "../RData/spain_w2/cog_stat.RData")
rm(cog_stat, COURAGE_cog)

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$cog_stat <- car::recode(COURAGE_m_ds_spain_w2$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation


Variable available only for the second waves (Polish and Spanish population).


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```


