---
title: "Anxiety symptoms"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `anxiety_symp`
* Variable label: `Psychological measure of anxiety symptoms`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:
* Comments: `In this template we will collect any anxiety symptom taking individual questions about worry, trembling, anxiety distress or severity, anxiety in general, other body features or scale items that correspond to these anxiety symptoms. In this sense, here we include a broad definition of anxiety symptoms. On a different variable we will have a more strict definition that will collect "anxiety diagnosis" following consensus criteria of strudies or scale manuals. However, only 5 studies include validated scales as such and most of them are different and some of them do not mention cut-off points, are ambiguous about them, or have different criteria depending on their population.`

**Code** | **Category Label**
-------- | --------------------
0        | no anxiety symptoms
1        | presence of anxiety

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Anxiety symptoms"
ds_label_all <- "Psychological measure of anxiety symptoms"
```


<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

#### Study-specific variable description

| **Name** | `q2019_worry`|
|-|-|
| **Label** | `Worry`|
| **Table name** | `Courage_Finland_w1` |
| **Categories** |`1 = None`|
| | `2 = Mild` |
| | `3 = Moderate` |
| | `4 = Severe` |
| | `5 = Extreme` |
| **Missings** | `8 = DK` | 
| | `9 = NA` | 
| **Description** |  |

```{r assign_fin,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_as','Courage.Courage_Finland_w1',
                         variables=list('q2019_worry'), missings = TRUE)
COURAGE_as <- opal.execute(o,'COURAGE_as')
```

```{r local_fin,  echo=FALSE}
vari <- COURAGE_as$q2019_worry
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(COURAGE_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "None" into 0`
* `recode 2 "Mild" into 1`
* `recode 3 "Moderate" into 1`
* `recode 4 "Severe" into 1`
* `recode 5 "Extreme" into 1`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_fin,   echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_as$id)
COURAGE_ds_fin_w1$anxiety_symp <- car::recode(COURAGE_as[[2]], "1=0; 2=1; 3=1; 4=1; 5=1; 8=998; 9=996; NA=999")
COURAGE_ds_fin_w1$anxiety_symp <- labelled(COURAGE_ds_fin_w1$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_fin,  echo=FALSE}
vari <- COURAGE_ds_fin_w1$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_fin,  echo=FALSE}
BeforeH <- table(COURAGE_as[[2]], useNA = 'ifany')
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2:5)]), BeforeH[6], BeforeH[7])
AfterH <- table(COURAGE_ds_fin_w1$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","(2,3,4,5)->1", "8->998", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_fin,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

label(COURAGE_ds_fin_w1$anxiety_symp) <- ds_label_all
anxiety_symp <- COURAGE_ds_fin_w1
save(anxiety_symp, file = "../RData/fin_w1/anxiety_symp.RData")
rm(anxiety_symp, COURAGE_as)

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$anxiety_symp <- car::recode(COURAGE_m_ds_fin_w1$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```





## Polish population

### Wave 1 

#### Study-specific variable description

| **Name** | `q2019_worry`|
|-|-|
| **Label** | `Worry`|
| **Table name** | `Courage_Poland_w1` |
| **Categories** |`1 = None`|
| | `2 = Mild` |
| | `3 = Moderate` |
| | `4 = Severe` |
| | `5 = Extreme` |
| **Missings** | `8 = DK` | 
| | `9 = NA` | 
| **Description** |  |

```{r assign_pol1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_as','Courage.Courage_Poland_w1',
                         variables=list('q2019_worry'), missings = TRUE)
COURAGE_as <- opal.execute(o,'COURAGE_as')
```

```{r local_pol1,  echo=FALSE}
vari <- COURAGE_as$q2019_worry
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(COURAGE_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "None" into 0`
* `recode 2 "Mild" into 1`
* `recode 3 "Moderate" into 1`
* `recode 4 "Severe" into 1`
* `recode 5 "Extreme" into 1`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_pol1,   echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_as$id)
COURAGE_ds_pol_w1$anxiety_symp <- car::recode(COURAGE_as[[2]], "1=0; 2=1; 3=1; 4=1; 5=1; 8=998; 9=996; NA=999")
COURAGE_ds_pol_w1$anxiety_symp <- labelled(COURAGE_ds_pol_w1$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol1,  echo=FALSE}
vari <- COURAGE_ds_pol_w1$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol1,  echo=FALSE}
BeforeH <- table(COURAGE_as[[2]], useNA = 'ifany')
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2:5)]), BeforeH[6])
AfterH <- table(COURAGE_ds_pol_w1$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","(2,3,4,5)->1", "8->998")
kable(C)
```

 

```{r importOPAL_pol1,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

label(COURAGE_ds_pol_w1$anxiety_symp) <- ds_label_all
anxiety_symp <- COURAGE_ds_pol_w1
save(anxiety_symp, file = "../RData/pol_w1/anxiety_symp.RData")
rm(anxiety_symp, COURAGE_as)


COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$anxiety_symp <- car::recode(COURAGE_m_ds_pol_w1$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `q2019_worry_s1`|
|-|-|
| **Label** | `Worry`|
| **Table name** | `Courage_Poland_w2` |
| **Categories** |`1 = None`|
| | `2 = Mild` |
| | `3 = Moderate` |
| | `4 = Severe` |
| | `5 = Extreme` |
| **Missings** | `8 = DK` | 
| | `9 = NA` | 
| **Description** |  |

```{r assign_pol2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_as','Courage.Courage_Poland_w2',
                         variables=list('q2019_worry_s1'), missings = TRUE)
COURAGE_as <- opal.execute(o,'COURAGE_as')
```

```{r local_pol2,  echo=FALSE}
vari <- COURAGE_as$q2019_worry_s1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(COURAGE_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "None" into 0`
* `recode 2 "Mild" into 1`
* `recode 3 "Moderate" into 1`
* `recode 4 "Severe" into 1`
* `recode 5 "Extreme" into 1`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_pol2,   echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_as$id)
COURAGE_ds_pol_w2$anxiety_symp <- car::recode(COURAGE_as[[2]], "1=0; 2=1; 3=1; 4=1; 5=1; 8=998; 9=996; NA=999")
COURAGE_ds_pol_w2$anxiety_symp <- labelled(COURAGE_ds_pol_w2$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_pol2,  echo=FALSE}
vari <- COURAGE_ds_pol_w2$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_pol2,  echo=FALSE}
BeforeH <- table(COURAGE_as[[2]], useNA = 'ifany')
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2:5)]), BeforeH[6])
AfterH <- table(COURAGE_ds_pol_w2$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","(2,3,4,5)->1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_pol2,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_pol_w2$anxiety_symp) <- ds_label_all
anxiety_symp <- COURAGE_ds_pol_w2
save(anxiety_symp, file = "../RData/pol_w2/anxiety_symp.RData")
rm(anxiety_symp, COURAGE_as)

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$anxiety_symp <- car::recode(COURAGE_m_ds_pol_w2$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```






## Spanish population

### Wave 1 

#### Study-specific variable description

| **Name** | `q2019_worry`|
|-|-|
| **Label** | `Worry`|
| **Table name** | `Courage_Spain_w1` |
| **Categories** |`1 = None`|
| | `2 = Mild` |
| | `3 = Moderate` |
| | `4 = Severe` |
| | `5 = Extreme` |
| **Missings** | `8 = DK` | 
| | `9 = NA` | 
| **Description** |  |

```{r assign_spain1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_as','Courage.Courage_Spain_w1',
                         variables=list('q2019_worry'), missings = TRUE)
COURAGE_as <- opal.execute(o,'COURAGE_as')
```

```{r local_spain1,  echo=FALSE}
vari <- COURAGE_as$q2019_worry
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(COURAGE_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "None" into 0`
* `recode 2 "Mild" into 1`
* `recode 3 "Moderate" into 1`
* `recode 4 "Severe" into 1`
* `recode 5 "Extreme" into 1`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_spain1,   echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_as$id)
COURAGE_ds_spain_w1$anxiety_symp <- car::recode(COURAGE_as[[2]], "1=0; 2=1; 3=1; 4=1; 5=1; 8=998; 9=996; NA=999")
COURAGE_ds_spain_w1$anxiety_symp <- labelled(COURAGE_ds_spain_w1$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain1,  echo=FALSE}
vari <- COURAGE_ds_spain_w1$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain1,  echo=FALSE}
BeforeH <- table(COURAGE_as[[2]], useNA = 'ifany')
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2:5)]), BeforeH[6])
AfterH <- table(COURAGE_ds_spain_w1$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","(2,3,4,5)->1", "8->998")
kable(C)
```

 
 

 
```{r importOPAL_spain1,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_spain_w1$anxiety_symp) <- ds_label_all
anxiety_symp <- COURAGE_ds_spain_w1
save(anxiety_symp, file = "../RData/spain_w1/anxiety_symp.RData")
rm(anxiety_symp, COURAGE_as)

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$anxiety_symp <- car::recode(COURAGE_m_ds_spain_w1$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description

| **Name** | `q2019_worry_s1`|
|-|-|
| **Label** | `Worry`|
| **Table name** | `Courage_Finland_w1` |
| **Categories** |`1 = None`|
| | `2 = Mild` |
| | `3 = Moderate` |
| | `4 = Severe` |
| | `5 = Extreme` |
| **Missings** | `8 = DK` | 
| | `9 = NA` | 
| **Description** |  |

```{r assign_spain2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_as','Courage.Courage_Spain_w2_1',
                         variables=list('q2019_worry_s1'), missings = TRUE)
COURAGE_as <- opal.execute(o,'COURAGE_as')
```

```{r local_spain2,  echo=FALSE}
vari <- COURAGE_as$q2019_worry_s1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(COURAGE_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "None" into 0`
* `recode 2 "Mild" into 1`
* `recode 3 "Moderate" into 1`
* `recode 4 "Severe" into 1`
* `recode 5 "Extreme" into 1`
* `recode 8 "DK" into 998`
* `recode 9 "NA" into 996`
* `NA into 999`

**R script:**

```{r harmo_spain2,   echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_as$id)
COURAGE_ds_spain_w2$anxiety_symp <- car::recode(COURAGE_as[[2]], "1=0; 2=1; 3=1; 4=1; 5=1; 8=998; 9=996; NA=999")
COURAGE_ds_spain_w2$anxiety_symp <- labelled(COURAGE_ds_spain_w2$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_spain2,  echo=FALSE}
vari <- COURAGE_ds_spain_w2$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_spain2,  echo=FALSE}
BeforeH <- table(COURAGE_as[[2]], useNA = 'ifany')
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2:5)]), BeforeH[6], BeforeH[7])
AfterH <- table(COURAGE_ds_spain_w2$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","(2,3,4,5)->1", "8->998", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_spain2,  echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_spain_w2$anxiety_symp) <- ds_label_all
anxiety_symp <- COURAGE_ds_spain_w2
save(anxiety_symp, file = "../RData/spain_w2/anxiety_symp.RData")
rm(anxiety_symp, COURAGE_as)

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$anxiety_symp <- car::recode(COURAGE_m_ds_spain_w2$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
The variable informs about overall in an item: in the last 30 days, 
how much of a problem did the person have with worry or anxiety.




```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```


