---
title: "Political activity - Voting"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/pol_votDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/pol_votDS.R')
```

<!-- ########################################################## --> 

# Data process

## India

### Wave 1 

#### Study-specific variable description


| **Name** |`fs510`|
|-|-|
| **Label** |`did you vote?`|
| **Table name**  |`LASI-Pilot_all`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_pol_vot','LASI.LASI-Pilot_all',variables=list('fs510'), missings = TRUE)
LASI_w1_pol_vot <- opal.execute(o,'LASI_w1_pol_vot')
```

```{r local1, echo=F}
vbl <- LASI_w1_pol_vot$fs510
kable(Categorical_summary(vbl, missing_values =NA)[2], caption = "fs510")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_pol_vot, aes(x=factor(fs510))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("did you vote?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo1}
LASI_ds_w1 <- tibble(id=LASI_w1_pol_vot$id)
LASI_ds_w1$pol_vot <- car::recode(as.vector(LASI_w1_pol_vot$fs510), "1='1'; 2='0'; NA='999'")
LASI_ds_w1$pol_vot <- labelled(LASI_ds_w1$pol_vot, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- LASI_ds_w1$pol_vot
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(LASI_ds_w1, aes(x=factor(pol_vot))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Voting?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(LASI_ds_w1$pol_vot)
BeforeH <- table(LASI_w1_pol_vot$fs510, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```

```{r importOPAL w1, echo=F}
pol_vot <- LASI_ds_w1 
save(pol_vot, file = "../RData/w1/pol_vot.RData")
rm(pol_vot)
```




# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
