---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/religDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/religDS.R')
```



<!-- ########################################################## --> 

# Data process
## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `fs509`
* Label: `how often attend religious functions or events outside home`
* Categories:
    + `1 = twice a month or more`
    + `2 = about once a month`
    + `3 = every few months`
    + `4 = about once or twice a year`
    + `5 = less than once a year`
    + `6 = never`
* Missings:
    + `7 = dk`
    + `8 = rf`
* Description:

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_relig','LASI.LASI-Pilot_all', variables=list('fs509'), missings = TRUE)
```

```{r local1, echo=F}
LASI_w1_relig <- opal.execute(o,'LASI_w1_relig')
vari <- LASI_w1_relig$fs509
kable(Categorical_summary(vari, missing_values = c(7,8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(7,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(7,8))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_w1_relig$fs509, missing_values = NA)
ggplot(LASI_w1_relig, aes(x=factor(fs509))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how often attend religious functions or events outside home") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6 into 0`
* `7 into 998`
* `8 into 997`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_relig$id)
LASI_ds_w1$relig <- car::recode(as.vector(LASI_w1_relig$fs509), "1:3='1'; 4:6='0'; 7='998'; 8='997'; NA='999'")
LASI_ds_w1$relig <- labelled(LASI_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- LASI_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(LASI_ds_w1$relig)
BeforeH <- table(LASI_w1_relig$fs509, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(4:6)])
BeforeH1[[2]] <- sum(BeforeH[c(1:3)])
BeforeH1[c(3,4,5)] <- BeforeH[c(8,7,9)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:6->0","1:3->1","8->997","7->998","NA->999")
kable(C)
```


```{r save, echo=FALSE}
relig <- LASI_ds_w1
save(relig, file = "../RData/w1/relig.RData")
rm(relig)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```