---
title: "Can people be trusted? (generalized trust, i.e. trust in other members of the society, not counting relatives and close friends)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/trustDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/trustDS.R')
```



<!-- ########################################################## --> 

# Data process

## India

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `he029`
* Label: `can people in neighborhood be trusted`
* Categories:
    + `1 = strongly agree`
    + `2 = agree`
    + `3 = disagree`
    + `4 = strongly disagree`
* Missings:
    + `5 = dk`
    + `6 = rf`
* Description:

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_trust','LASI.LASI-Pilot_all',variables=list('he029'), missings = TRUE)
```

```{r local1, echo=F}
LASI_w1_trust <- opal.execute(o,'LASI_w1_trust')
vari <- LASI_w1_trust$he029
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(5,6))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_w1_trust$he029, missing_values = NA)
ggplot(LASI_w1_trust, aes(x=factor(he029))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("can people in neighborhood be trusted") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 1`
* `3,4 into 0`
* `7 into 998`
* `8 into 997`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_trust$id)
LASI_ds_w1$trust <- car::recode(as.vector(LASI_w1_trust$he029), "1:2='1'; 3:4='0'; 5='998'; 6='997'; NA='999'")
LASI_ds_w1$trust <- labelled(LASI_ds_w1$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- LASI_ds_w1$trust
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$trust, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(LASI_ds_w1$trust)
BeforeH <- table(LASI_w1_trust$he029, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(1,2)])
BeforeH1[[1]] <- sum(BeforeH[c(3,4)])
BeforeH1[[3]] <- BeforeH[[6]]
BeforeH1[[4]] <- BeforeH[[5]]
BeforeH1[[5]] <- BeforeH[[7]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","6->997","5->998","NA->999")
kable(C)
```

```{r save, echo=FALSE}
trust <- LASI_ds_w1
save(trust, file = "../RData/w1/trust.RData")
rm(trust)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
