---
title: "Ever experienced any natural disaster"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `nat_dis`
* Variable label: `Ever experienced any natural disaster`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Indian population


### Wave 1

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ht065`
* Label: `In the last two years, has your health been severely affected by natural calamities, disasters such as floods, landslides, adverse cold and hot weather, typhoons, droughts, earth-quakes, tsunamis, or any other natural calamities?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Description:
```{r assign1} 
opal.assign.table.tibble(o, 'LASI_w1_nat_dis','LASI.LASI-Pilot_all',variables=list('ht065'), missings = TRUE)
```

```{r local1}
LASI_w1_nat_dis <- opal.execute(o,'LASI_w1_nat_dis')
vari <- LASI_w1_nat_dis$ht065
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_nat_dis$ht065, missing_values = NA)
ggplot(LASI_w1_nat_dis, aes(x=factor(ht065))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In the last two years, has your health been severely affected by natural calamities?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1; 2 into 0`
* `NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_nat_dis$id)
LASI_ds_w1$nat_dis <- car::recode(as.vector(LASI_w1_nat_dis$ht065), "1='1'; 2='0'; NA=999")
LASI_ds_w1$nat_dis <- labelled(LASI_ds_w1$nat_dis, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- LASI_ds_w1$nat_dis
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$nat_dis, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(nat_dis))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever experienced any natural disaster") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(LASI_ds_w1$nat_dis)
BeforeH <- table(LASI_w1_nat_dis$ht065, useNA='ifany')[c(2,1,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")
kable(C)
```

```{r save, echo=FALSE}
nat_dis <- LASI_ds_w1
save(nat_dis, file = "../RData/w1/nat_dis.RData")
rm(nat_dis)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



