---
title: "Loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lonelinessDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lonelinessDS.R')
```

# Data process


## India


### Wave 1

#### Study-specific variable description

| **Name** |`ht314`|`fs605`|
|-|-|-|
| **Label** |`felt lonely`|`how often do you feel lonely`|
| **Table name** |`LASI-Pilot_all`|`LASI-Pilot_all`|
| **Categories** |`1 = rarely or none of the time; less than 1 day`<br/>`2 = some or little of the time; 1 to 2 days`<br/>`3 = occasionally or a moderate amount of the time; 3 to 4 days`<br/>`4 = most or all of the time; 5 to 7 days`|`1 = hardly ever or never`<br/>`2 = some of the time`<br/>`3 = often`|
| **Missings** |`5 = dk`<br/>`6 = rf`|`4 = dk`<br/>`5 = rf`|



```{r assign1, echo=F} 
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all',variables=list('ht314','fs605'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local1, echo=F}

vbl <- LASI_w1$ht314
kable(Categorical_summary(var = vbl, missing_values = c(5,6))[3],caption="ht314")
kable(Categorical_summary(var = vbl, missing_values = c(5,6))[1],caption="Category")
ggplot(LASI_w1, aes(x=factor(ht314))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt lonely") + ylab("Frequency")


vbl <- LASI_w1$fs605
kable(Categorical_summary(var = vbl, missing_values = c(5,4))[3],caption="fs605")
kable(Categorical_summary(var = vbl, missing_values = c(5,4))[1],caption="Category")
ggplot(LASI_w1, aes(x=factor(fs605))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often do you feel lonely") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if ht in 2,3,4 or fs in 2,3 then 1`
* `if ht=1 and fs=1 then 0`
* `if ht=6 or fs=5 then 997`
* `if ht=5 or fs=4 then 998`
* `NA into 999`

**R script:**

```{r harmo1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)

LASI_w1$ht314 <- car::recode(as.vector(LASI_w1$ht314), "NA='-999'")
LASI_w1$fs605 <- car::recode(as.vector(LASI_w1$fs605), "NA='-999'")

LASI_ds_w1$loneliness <- c(NA)
for(i in 1:dim(LASI_w1[1])){
  if( LASI_w1$ht314[i] %in% c(2,3,4) | LASI_w1$fs605[i] %in% c(2,3) ) { 
    LASI_ds_w1$loneliness[i] = 1 }
  else if( LASI_w1$ht314[i] == 1 & LASI_w1$fs605[i] == 1 ) { 
    LASI_ds_w1$loneliness[i] = 0 }
  else if( LASI_w1$ht314[i] == 6 | LASI_w1$fs605[i] == 5 ) { 
    LASI_ds_w1$loneliness[i] = 997 }
  else if( LASI_w1$ht314[i] == 5 | LASI_w1$fs605[i] == 4 ) { 
    LASI_ds_w1$loneliness[i] = 998 }
}

LASI_ds_w1$loneliness <- car::recode(as.vector(LASI_ds_w1$loneliness), "NA='999'")
LASI_ds_w1$loneliness <- labelled(LASI_ds_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}

vbl <- LASI_ds_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(LASI_ds_w1$loneliness)
BeforeH <- table(LASI_w1$ht314, LASI_w1$fs605, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[2,2]
BeforeH1[[2]] <- sum(sum(BeforeH[c(3,4,5),]), sum(BeforeH[c(1,2,6,7),c(3,4)]))
BeforeH1[[3]] <- sum(sum(BeforeH[7,c(1,2,5,6)]), sum(BeforeH[c(1,2,6),6]))
BeforeH1[[4]] <- sum(sum(BeforeH[6,c(1,2,5)]), sum(BeforeH[c(1,2),5]))
BeforeH1[[5]] <- sum(sum(BeforeH[1,c(1,2)]), BeforeH[2,1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","997","998","NA->999")
kable(C)
```

# Quality estimation



```{r importOPAL w1, echo=F}
loneliness <- LASI_ds_w1 
save(loneliness, file = "../RData/w1/loneliness.RData")
rm(loneliness)
```
