---
title: "The number of close people: friends, neighbours or co-workers"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `clspeop`
* Variable label: `The number of close people: friends, neighbours or co-workers`
* Domain: `Social environment`
* Value type: `continuous`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of close people


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Indian population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `fs325`
* Label: `do you have friends?`
* Categories:
    + `1 = yes`
    + `2 = no`

* Name: `fs325a`
* Label: `how many friends would you say you have close relationship with`

    
* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'LASI_w1_clspeop','LASI.LASI-Pilot_all', variables=list('fs325', 'fs325a'), missings = TRUE)
```

```{r local1}
LASI_w1_clspeop <- opal.execute(o,'LASI_w1_clspeop')

vari <- LASI_w1_clspeop$fs325
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_clspeop$fs325, missing_values = NA)
ggplot(LASI_w1_clspeop, aes(x=factor(fs325))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Do you have friends?") + ylab("Frequency")

vari <- LASI_w1_clspeop$fs325a
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = LASI_w1_clspeop$fs325a, missing_values = NA)
ggplot(LASI_w1_clspeop, aes(x=factor(fs325a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if fs325=0 or fs325a=0 -> recode into 0`
* `else -> take values>0 from fs325a`

**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_clspeop$id)

LASI_w1_clspeop$fs325 <-car::recode(as.vector(LASI_w1_clspeop$fs325), "NA='-999'")
LASI_w1_clspeop$fs325a <-car::recode(as.vector(LASI_w1_clspeop$fs325a), "NA='-999'")

LASI_ds_w1$clspeop <- c(NA)   
for(i in 1:dim(LASI_w1_clspeop[1])){
  if( LASI_w1_clspeop$fs325[i] == 2 | LASI_w1_clspeop$fs325a[i] == 0 ) { LASI_ds_w1$clspeop[i] = 0 }
  else if( LASI_w1_clspeop$fs325a[i] > 0 ) { LASI_ds_w1$clspeop[i] = LASI_w1_clspeop$fs325a[i] }
}

LASI_ds_w1$clspeop <-car::recode(as.vector(LASI_ds_w1$clspeop), "NA='999'")
LASI_ds_w1$clspeop <- labelled(LASI_ds_w1$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- LASI_ds_w1$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = LASI_ds_w1$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close persons: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(LASI_ds_w1$clspeop)
BeforeH1 <- table(LASI_w1_clspeop$fs325, LASI_w1_clspeop$fs325a, useNA='ifany')
BeforeH <- table(LASI_w1_clspeop$fs325, LASI_w1_clspeop$fs325a, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH1[2,2],BeforeH1[3,1])
BeforeH[c(2:15)] <- BeforeH1[2, c(3:16)]
BeforeH[[16]] <- sum(BeforeH1[1,1],BeforeH1[2,1])
BeforeH <- BeforeH[c(1:16)]

C <- rbind(BeforeH,AfterH)
colnames(C)[16] <- c("NA->999")

kable(C)
```


```{r save, echo=FALSE}
clspeop <- LASI_ds_w1
save(clspeop, file = "../RData/w1/clspeop.RData")
rm(clspeop)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
