---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `oth_fam`
* Variable label: `Has other (living) family members (e.g. parents, siblings, in-laws, etc.)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## Indian population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `fs302`
* Label: `is father alive`
* Categories: 
    + `1 = yes`
    + `2 = no`
    
* Name: `fs312`
* Label: `is mother alive`
* Categories: 
    + `1 = yes`
    + `2 = no`
    
* Name: `fs321`
* Label: `any living siblings`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Description:   
```{r assign1}
opal.assign.table.tibble(o, 'LASI_w1_oth_fam','LASI.LASI-Pilot_all', variables=list('fs302','fs312','fs321'), missings = TRUE)
```

```{r local1}
LASI_w1_oth_fam <- opal.execute(o,'LASI_w1_oth_fam')
vari <- LASI_w1_oth_fam$fs302
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_oth_fam$fs302, missing_values = NA)
ggplot(LASI_w1_oth_fam, aes(x=factor(fs302))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is father alive?") + ylab("Frequency")
vari <- LASI_w1_oth_fam$fs312
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_oth_fam$fs312, missing_values = NA)
ggplot(LASI_w1_oth_fam, aes(x=factor(fs312))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is mother alive?") + ylab("Frequency")
vari <- LASI_w1_oth_fam$fs321
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = LASI_w1_oth_fam$fs321, missing_values = NA)
ggplot(LASI_w1_oth_fam, aes(x=factor(fs321))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("any living siblings?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all equals 0 then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
LASI_ds_w1 <- tibble(id=LASI_w1_oth_fam$id)

LASI_w1_oth_fam$fs302 <- car::recode(as.vector(LASI_w1_oth_fam$fs302), "NA='-999'")
LASI_w1_oth_fam$fs312 <- car::recode(as.vector(LASI_w1_oth_fam$fs312), "NA='-999'")
LASI_w1_oth_fam$fs321 <- car::recode(as.vector(LASI_w1_oth_fam$fs321), "NA='-999'")

LASI_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(LASI_w1_oth_fam)[1]){
  if(LASI_w1_oth_fam$fs302[i] == 1 | LASI_w1_oth_fam$fs312[i] == 1 | LASI_w1_oth_fam$fs321[i] == 1 ){
    LASI_ds_w1$oth_fam[i] = 1 } 
  else if(LASI_w1_oth_fam$fs302[i] == 2 & LASI_w1_oth_fam$fs312[i] == 2 & LASI_w1_oth_fam$fs321[i] == 2 ){
    LASI_ds_w1$oth_fam[i] = 0 }
}

LASI_ds_w1$oth_fam <- car::recode(as.vector(LASI_ds_w1$oth_fam), "NA='999'")
LASI_ds_w1$oth_fam <- labelled(LASI_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- LASI_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = LASI_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(LASI_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

```{r save}
oth_fam <- LASI_ds_w1
save(oth_fam, file="../RData/w1/oth_fam.RData")
rm(oth_fam)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
