---
title: "Frequency of phone or mail contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_other_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_other_frDS.R')
```

# Data process

## India


### Wave 1 

#### Study-specific variable description


| **Name** |`fs325`|`fs327`|`fs328`|
|-|-|-|-|
| **Label** |`do you have friends`|`speak on the phone with friends`|`write or email friends`|
| **Table name** |`LASI-Pilot_all`|`LASI-Pilot_all`|`LASI-Pilot_all`|
| **Categories** |`1	= Yes`<br/>`2	= No`|`1 = daily`<br/>`2 = three or more times a week`<br/>`3 = once or twice a week`<br/>`4 = once or twice a month`<br/>`5 = every few months`<br/>`6 = once or twice a year`<br/>`7 = less than once a year or never`<br/>`8 = never`|`1 = daily`<br/>`2 = three or more times a week`<br/>`3 = once or twice a week`<br/>`4 = once or twice a month`<br/>`5 = every few months`<br/>`6 = once or twice a year`<br/>`7 = less than once a year or never`<br/>`8 = never`|
| **Missings** |  |`9 = dk`<br/>`10 = rf`|`9 = dk`<br/>`10 = rf`|
| **Description** |  |  |  |




```{r assign1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('fs325','fs327','fs328'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local1, echo=F}


vari <- LASI_w1$fs325
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "fs325")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(fs325))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- LASI_w1$fs327
vbl_miss <- c(9,10)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "fs327")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(fs327))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- LASI_w1$fs328
vbl_miss <- c(9,10)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "fs328")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
ggplot(LASI_w1, aes(x=factor(fs328))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `fs327=1 or 2 OR fs327=1 or 2 into 1`
* `fs327=3 OR fs327=3 into 2`
* `fs327=4 OR fs327=4 into 3`
* `fs327=5 or 6 OR fs327=5 or 6 into 4`
* `fs325=2 or fs327=7 or 8 OR fs327=7 or 8 into 5`
* `9 into 998`
* `10 into 997`
* `NA into 999`


**R script:**

```{r harmo1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)

LASI_w1$fs325 <- car::recode(as.vector(LASI_w1$fs325), "NA='-999'")
LASI_w1$fs327 <- car::recode(as.vector(LASI_w1$fs327), "NA='-999'")
LASI_w1$fs328 <- car::recode(as.vector(LASI_w1$fs328), "NA='-999'")

LASI_ds_w1$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(LASI_w1)[1]){
  if( LASI_w1$fs327[i] %in% c(1,2) | LASI_w1$fs328[i] %in% c(1,2) ){ 
    LASI_ds_w1$f_other_fr[i] = 1 }
  else if( LASI_w1$fs327[i] == 3 | LASI_w1$fs328[i] == 3 ) { 
    LASI_ds_w1$f_other_fr[i] = 2 }
  else if( LASI_w1$fs327[i] == 4 | LASI_w1$fs328[i] == 4 ){ 
    LASI_ds_w1$f_other_fr[i] = 3 }
  else if( LASI_w1$fs327[i] %in% c(5,6) | LASI_w1$fs328[i] %in% c(5,6) ){ 
    LASI_ds_w1$f_other_fr[i] = 4 }
  else if( LASI_w1$fs327[i] %in% c(7,8) | LASI_w1$fs328[i] %in% c(7,8) | LASI_w1$fs325[i] == 2 ){ 
    LASI_ds_w1$f_other_fr[i] = 5 }
  else if( LASI_w1$fs327[i] == 9 | LASI_w1$fs328[i] == 9 ){ LASI_ds_w1$f_other_fr[i] = 998 }
  else if( LASI_w1$fs327[i] == 10 | LASI_w1$fs328[i] == 10 ){ LASI_ds_w1$f_other_fr[i] = 997 }
}

LASI_ds_w1$f_other_fr <- car::recode(as.vector(LASI_ds_w1$f_other_fr), "NA='999'")
LASI_ds_w1$f_other_fr <- labelled(LASI_ds_w1$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- LASI_ds_w1$f_other_fr
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(LASI_ds_w1, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

```{r save, echo=FALSE}
f_other_fr <- LASI_ds_w1
save(f_other_fr, file = "../RData/w1/f_other_fr.RData")
rm(f_other_fr)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

