---
title: "Day of Interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/dintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/dintwDS.R')
```


# Data process

## Australia


### Wave 1 

#### Study-specific variable description




| **Name** | `datew1`|
|-|-|
| **Label** | `Date of Wave1 interview`|
| **Table name** |`dates_of_interview_w1`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.dates_of_interview_w1',
                         variables=list('datew1'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

**R script:**

```{r preharm w1}

ALSA_w1$dinter <- as.numeric(format(ALSA_w1$datew1, '%d'))

```

```{r local1, echo=F}

vbl <- ALSA_w1$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$dintw <- car::recode(ALSA_w1$dinter, "NA=999")
ALSA_ds_w1$dintw <- labelled(ALSA_ds_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- ALSA_ds_w1$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ALSA_w1$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
kable(C)
```







### Wave 2 

#### Study-specific variable description



| **Name** | `datew2`|
|-|-|
| **Label** | |
| **Table name** |`dates_of_interview_w2`|
| **Type of variable** |`date`|
| **Description** |  |

    

    
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2','ALSA.dates_of_interview_w2',
                         variables=list('datew2'), missings = TRUE)
ALSA_w2 <- opal.execute(o,'ALSA_w2')

opal.assign.table.tibble(o, 'ALSA_w2_id','ALSA.ALSA-Wave2', variables=list('DATE'), missings = TRUE)
ALSA_w2_id <- opal.execute(o,'ALSA_w2_id')

ALSA_w2 <- left_join(ALSA_w2_id[,-2],ALSA_w2, by="id")
```

**R script:**

```{r preharm w2}

ALSA_w2$dinter <- as.numeric(format(ALSA_w2$datew2, '%d'))

```


```{r local2, echo=F}

vbl <- ALSA_w2$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w2, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ALSA_ds_w2 <- tibble(id=ALSA_w2$id)
ALSA_ds_w2$dintw <- car::recode(ALSA_w2$dinter, "NA=999")
ALSA_ds_w2$dintw <- labelled(ALSA_ds_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vbl <- ALSA_ds_w2$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w2, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Day of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ALSA_w2$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```











### Wave 3 

#### Study-specific variable description




| **Name** | `datew3`|
|-|-|
| **Label** | `Date of Wave3 interview`|
| **Table name** |`dates_of_interview_w3`|
| **Type of variable** |`date`|
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3','ALSA.dates_of_interview_w3',
                         variables=list('datew3'), missings = TRUE)
ALSA_w3 <- opal.execute(o,'ALSA_w3')
opal.assign.table.tibble(o, 'ALSA_w3_id','ALSA.ALSA-Wave3',
                         variables=list('SEXW3'), missings = TRUE)
ALSA_w3_id <- opal.execute(o,'ALSA_w3_id')
ALSA_w3 <- left_join(ALSA_w3_id[,-2],ALSA_w3, by="id")
```

**R script:**

```{r preharm w3}

ALSA_w3$dinter <- as.numeric(format(ALSA_w3$datew3, '%d'))

```

```{r local3, echo=F}


vbl <- ALSA_w3$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w3, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$dintw <- car::recode(ALSA_w3$dinter, "NA=999")
ALSA_ds_w3$dintw <- labelled(ALSA_ds_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vbl <- ALSA_ds_w3$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w3, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ALSA_w3$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31])
kable(C)
```








### Wave 4 

#### Study-specific variable description




| **Name** | `DATEW4`|
|-|-|
| **Label** | `DATE OF INTERVIEW`|
| **Table name** |`ALSA-Wave4`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4','ALSA.ALSA-Wave4',
                         variables=list('DATEW4'), missings = TRUE)
ALSA_w4 <- opal.execute(o,'ALSA_w4')
```


**R script:**

```{r preharm w4}

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 4, 7), 
                                                                     last=c(2, 5, 8)))))
    }
  colnames(D) <- c("Day", "Month", "Year")
  D
}

ALSA_w4 <- cbind(ALSA_w4, Date_of_birth(ALSA_w4$DATEW4))

```

```{r local4, echo=F}


vbl <- ALSA_w4$Day
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "Day")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w4, aes(Day)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo4}
ALSA_ds_w4 <- tibble(id=ALSA_w4$id)
ALSA_ds_w4$dintw <- car::recode(ALSA_w4$Day, "NA=999")
ALSA_ds_w4$dintw <- labelled(ALSA_ds_w4$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vbl <- ALSA_ds_w4$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w4, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ALSA_w4$Day, useNA = "ifany")
AfterH <- table(ALSA_ds_w4$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```







### Wave 5 

#### Study-specific variable description




| **Name** | `DATE`|
|-|-|
| **Label** | `DATE INTERVIEW COMPLETED`|
| **Table name** |`ALSA-Wave5`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5','ALSA.ALSA-Wave5',
                         variables=list('DATE'), missings = TRUE)
ALSA_w5 <- opal.execute(o,'ALSA_w5')

```

**R script:**

```{r preharm w5}

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 4, 7), 
                                                                     last=c(2, 5, 10)))))
    }
  colnames(D) <- c("Month", "Day", "Year")
  D
}

ALSA_w5 <- cbind(ALSA_w5, Date_of_birth(ALSA_w5$DATE))

```


```{r local5, echo=F}


vbl <- ALSA_w5$Day
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "Day")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w5, aes(x=factor(Day))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ALSA_ds_w5 <- tibble(id=ALSA_w5$id)
ALSA_ds_w5$dintw <- car::recode(ALSA_w5$Day, "NA=999")
ALSA_ds_w5$dintw <- labelled(ALSA_ds_w5$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vbl <- ALSA_ds_w5$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w5, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ALSA_w5$Day, useNA = "ifany")
AfterH <- table(ALSA_ds_w5$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```








### Wave 6 

#### Study-specific variable description



| **Name** | `DATEW6`|
|-|-|
| **Label** | `Wave6 interview date`|
| **Table name** |`ALSA-Wave6`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',
                         variables=list('DATEW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

**R script:**

```{r preharm w6}

ALSA_w6$dinter <- as.numeric(format(ALSA_w6$DATEW6, '%d'))

```

```{r local6, echo=F}
vbl <- ALSA_w6$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$dintw <- car::recode(ALSA_w6$dinter, "NA=999")
ALSA_ds_w6$dintw <- labelled(ALSA_ds_w6$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vbl <- ALSA_ds_w6$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ALSA_w6$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w6$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```




### Wave 7 

#### Study-specific variable description



| **Name** | `datew7`|
|-|-|
| **Label** | `date of interview-W7`|
| **Table name** |`dates_of_interview_w7`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7','ALSA.dates_of_interview_w7',
                         variables=list('datew7'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w7_id','ALSA.ALSA-Wave7',
                         variables=list('sex'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
ALSA_w7_id <- opal.execute(o,'ALSA_w7_id')
ALSA_w7 <- left_join(ALSA_w7_id[,-2],ALSA_w7, by="id")
```


**R script:**

```{r preharm w7}

ALSA_w7$dinter <- as.numeric(format(ALSA_w7$datew7, '%d'))

```

```{r local7, echo=F}
vbl <- ALSA_w7$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$dintw <- car::recode(ALSA_w7$dinter, "NA=996")
ALSA_ds_w7$dintw <- labelled(ALSA_ds_w7$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vbl <- ALSA_ds_w7$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation7, echo=F}
BeforeH <- table(ALSA_w7$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w7$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->996")
kable(C)
```








### Wave 8 

#### Study-specific variable description



| **Name** | `Date`|
|-|-|
| **Label** | `Date`|
| **Table name** |`ALSA-Wave8`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8','ALSA.ALSA-Wave8',
                         variables=list('Date'), missings = TRUE)
ALSA_w8 <- opal.execute(o,'ALSA_w8')
```

**R script:**

```{r preharm w8}

#This function return a table with the date of birth separated by columns:
Date_of_birth <- function(date){
  date <- as.numeric(date)
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
    if(log10(date[i])+1>=8){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    }
    else{
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    }
  }
  colnames(D) <- c("Year", "Month", "Day")
  D
}

ALSA_w8 <- cbind(ALSA_w8, Date_of_birth(ALSA_w8$Date))

```

```{r local8, echo=F}

vbl <- ALSA_w8$Day
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "Day")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w8, aes(x=factor(Day))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo8}
ALSA_ds_w8 <- tibble(id=ALSA_w8$id)
ALSA_ds_w8$dintw <- car::recode(ALSA_w8$Day, "NA=999")
ALSA_ds_w8$dintw <- labelled(ALSA_ds_w8$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript8, echo=F}
vbl <- ALSA_ds_w8$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w8, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation8, echo=F}
BeforeH <- table(ALSA_w8$Day, useNA = "ifany")
AfterH <- table(ALSA_ds_w8$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```





### Wave 9 

#### Study-specific variable description



| **Name** | `DATEW9`|
|-|-|
| **Label** | `Date of interview Wave 9`|
| **Table name** |`ALSA-Wave9`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',
                         variables=list('DATEW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

**R script:**

```{r preharm w9}

#This function return a table with the date of birth separated by columns:
Date_of_birth <- function(date){
  date <- as.numeric(date)
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
    if(is.na(date[i])){
      D[i,] <- rep(NA,3)
    }
    else{
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    } 
  }
 colnames(D) <- c("Year", "Month", "Day")    
 D
}

ALSA_w9 <- cbind(ALSA_w9, Date_of_birth(ALSA_w9$DATEW9))

```


```{r local9, echo=F}


vbl <- ALSA_w9$Day
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "Day")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(x=factor(Day))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$dintw <- car::recode(ALSA_w9$Day, "NA=996")
ALSA_ds_w9$dintw <- labelled(ALSA_ds_w9$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript9, echo=F}
vbl <- ALSA_ds_w9$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w9, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation9, echo=F}
BeforeH <- table(ALSA_w9$Day, useNA = "ifany")
AfterH <- table(ALSA_ds_w9$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->996")
kable(C)
```









### Wave 10 

#### Study-specific variable description



| **Name** | `Date`|
|-|-|
| **Label** | `Date`|
| **Table name** |`ALSA-Wave10`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10','ALSA.ALSA-Wave10',
                         variables=list('Date'), missings = TRUE)
ALSA_w10 <- opal.execute(o,'ALSA_w10')
```

**R script:**

```{r preharm w10}
ALSA_w10$dinter <- as.numeric(format(ALSA_w10$Date, '%d'))

```

```{r local10, echo=F}
vbl <- ALSA_w10$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w10, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo10}
ALSA_ds_w10 <- tibble(id=ALSA_w10$id)
ALSA_ds_w10$dintw <- car::recode(ALSA_w10$dinter, "NA=999")
ALSA_ds_w10$dintw <- labelled(ALSA_ds_w10$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript10, echo=F}
vbl <- ALSA_ds_w10$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w10, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation10, echo=F}
BeforeH <- table(ALSA_w10$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w10$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```






### Wave 11 

#### Study-specific variable description




| **Name** | `DATEW11`|
|-|-|
| **Label** | `Date of interview Wave 11`|
| **Table name** |`ALSA-Wave11`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',
                         variables=list('DATEW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
```

**R script:**

```{r preharm w11}
ALSA_w11$dinter <- as.numeric(format(ALSA_w11$DATEW11, '%d'))

```

```{r local11, echo=F}
vbl <- ALSA_w11$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w11, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo11}
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$dintw <- car::recode(ALSA_w11$dinter, "NA=999")
ALSA_ds_w11$dintw <- labelled(ALSA_ds_w11$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript11, echo=F}
vbl <- ALSA_ds_w11$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w11, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation11, echo=F}
BeforeH <- table(ALSA_w11$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w11$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```







### Wave 12 

#### Study-specific variable description



| **Name** | `DATEW12`|
|-|-|
| **Label** | `Date of interview Wave 12`|
| **Table name** |`ALSA-Wave12`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',
                         variables=list('DATEW12'), missings = TRUE)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
```

**R script:**

```{r preharm w12}
ALSA_w12$dinter <- as.numeric(format(ALSA_w12$DATEW12, '%d'))

```

```{r local12, echo=F}
vbl <- ALSA_w12$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo12}
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$dintw <- car::recode(ALSA_w12$dinter, "NA=999")
ALSA_ds_w12$dintw <- labelled(ALSA_ds_w12$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript12, echo=F}
vbl <- ALSA_ds_w12$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation12, echo=F}
BeforeH <- table(ALSA_w12$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w12$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```








### Wave 13 

#### Study-specific variable description



| **Name** | `DATEW13`|
|-|-|
| **Label** | `Date of interview Wave 13`|
| **Table name** |`ALSA-Wave13`|
| **Type of variable** |`date`|
| **Description** |  |


    
```{r assign13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13','ALSA.ALSA-Wave13',
                         variables=list('DATEW13'), missings = TRUE)
ALSA_w13 <- opal.execute(o,'ALSA_w13')
```

**R script:**

```{r preharm w13}
ALSA_w13$dinter <- as.numeric(format(ALSA_w13$DATEW13, '%d'))

```


```{r local13, echo=F}
vbl <- ALSA_w13$dinter
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "dinter")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w13, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo13}
ALSA_ds_w13 <- tibble(id=ALSA_w13$id)
ALSA_ds_w13$dintw <- car::recode(ALSA_w13$dinter, "NA=999")
ALSA_ds_w13$dintw <- labelled(ALSA_ds_w13$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript13, echo=F}
vbl <- ALSA_ds_w13$dintw
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w13, aes(dintw)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation13, echo=F}
BeforeH <- table(ALSA_w13$dinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w13$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
kable(C)
```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```

# Quality estimation
No comments.





```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
