---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/yintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/yintwDS.R')
```

# Data process

## ALSA

### Wave 1 

#### Study-specific variable description



| **Name** | `datew1`|
|-|-|
| **Label** | `Date of Wave1 interview`|
| **Table name** |`dates_of_interview_w1`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.dates_of_interview_w1', variables=list('datew1'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

**R script:**

```{r preharm w1}

ALSA_w1$yinter <- as.numeric(format(ALSA_w1$datew1, '%y'))

```

```{r local1, echo=F}
vbl <- ALSA_w1$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$yintw <- ALSA_w1$yinter+1900

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- ALSA_ds_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ALSA_w1$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```






### Wave 2 

#### Study-specific variable description



| **Name** | `datew2`|
|-|-|
| **Label** | |
| **Table name** |`dates_of_interview_w2`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ALSA_w2','ALSA.dates_of_interview_w2', variables=list('datew2'), missings = TRUE)
ALSA_w2 <- opal.execute(o,'ALSA_w2')

opal.assign.table.tibble(o, 'ALSA_w2_id','ALSA.ALSA-Wave2', variables=list('DATE'), missings = TRUE)
ALSA_w2_id <- opal.execute(o,'ALSA_w2_id')

ALSA_w2 <- left_join(ALSA_w2_id,ALSA_w2, by="id")
```



**R script:**

```{r preharm w2}

ALSA_w2$yinter <- format(ALSA_w2$datew2, '%y')

```


```{r local2, echo=F}
vbl <- ALSA_w2$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w2, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonised variable is the same of the study-specific variable but the missing values will be recoded as 94 since is the most frecuent value. 

**R script:**

```{r harmo2}
ALSA_ds_w2 <- tibble(id=ALSA_w2$id)
ALSA_ds_w2$yintw <- car::recode(ALSA_w2$yinter, "NA=94")+1900

```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vbl <- ALSA_ds_w2$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ALSA_w2$yinter, useNA = "ifany")
BeforeH <- c(BeforeH[1], BeforeH[2])
AfterH <- table(ALSA_ds_w2$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("93", "94" )
kable(C)
```








### Wave 3 

#### Study-specific variable description



| **Name** | `datew3`|
|-|-|
| **Label** | `Date of Wave3 interview`|
| **Table name** |`dates_of_interview_w3`|
| **Type of variable** |`date`|
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3_yinter','ALSA.dates_of_interview_w3',variables=list('datew3'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w3_id','ALSA.ALSA-Wave3', variables=list('SEXW3'), missings = TRUE)
ALSA_w3_yinter <- opal.execute(o,'ALSA_w3_yinter')
ALSA_w3_id <- opal.execute(o,'ALSA_w3_id')
```


**R script:**

```{r preharm w3}

ALSA_w3_yinter$yinter <- format(ALSA_w3_yinter$datew3, '%Y')
ALSA_w3_yinter$minter <- format(ALSA_w3_yinter$datew3, '%m')

```

```{r local3, echo=F}



ALSA_w3 <- merge(ALSA_w3_id[,"id"], ALSA_w3_yinter, by = "id", all.x = TRUE, all.y = FALSE)


vbl <- ALSA_w3$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonised variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$yintw <- as.numeric(ALSA_w3$yinter)
ALSA_ds_w3$yintw[which(ALSA_ds_w3$id == ALSA_w3[which(ALSA_w3$yinter == 1994 & ALSA_w3$minter=="01"),"id"])] <- 1995

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vbl <- ALSA_ds_w3$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ALSA_w3$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w3$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```








### Wave 4 

#### Study-specific variable description



| **Name** | `DATEW4`|
|-|-|
| **Label** | `DATE OF INTERVIEW`|
| **Table name** |`ALSA-Wave4`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4','ALSA.ALSA-Wave4',variables=list('DATEW4'), missings = TRUE)
ALSA_w4 <- opal.execute(o,'ALSA_w4')
```

**R script:**

```{r preharm w4}

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 4, 7), 
                                                                     last=c(2, 5, 8)))))
    }
  colnames(D) <- c("Day", "Month", "Year")
  D
}

ALSA_w4 <- cbind(ALSA_w4, Date_of_birth(ALSA_w4$DATEW4))

```

```{r local4, echo=F}

vbl <- ALSA_w4$Year
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "Year")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`
The values 5 and 56  are going to be considered as typing mistakes and they are going to be recoded as 95 and 96 	respectively.

**R script:**

```{r harmo4}
ALSA_ds_w4 <- tibble(id=ALSA_w4$id)
ALSA_ds_w4$yintw <- car::recode(ALSA_w4$Year, "5=95; 56=96")+1900

```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vbl <- ALSA_ds_w4$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ALSA_w4$Year, useNA = "ifany")
BeforeH <- c(sum(BeforeH[c(1,3)]), sum(BeforeH[c(2,4)]))
AfterH <- table(ALSA_ds_w4$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 5 

#### Study-specific variable description



| **Name** | `DATE`|
|-|-|
| **Label** | `DATE INTERVIEW COMPLETED`|
| **Table name** |`ALSA-Wave5`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5','ALSA.ALSA-Wave5',variables=list('DATE'), missings = TRUE)
ALSA_w5 <- opal.execute(o,'ALSA_w5')
```

**R script:**

```{r preharm w5}

Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 4, 7), 
                                                                     last=c(2, 5, 10)))))
    }
  colnames(D) <- c("Month", "Day", "Year")
  D
}

ALSA_w5 <- cbind(ALSA_w5, Date_of_birth(ALSA_w5$DATE))

```



```{r local5, echo=F}


vbl <- ALSA_w5$Year
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "Year")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w5, aes(x=factor(Year))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ALSA_ds_w5 <- tibble(id=ALSA_w5$id)
ALSA_ds_w5$yintw <- ALSA_w5$Year

```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vbl <- ALSA_ds_w5$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ALSA_w5$Year, useNA = "ifany")
AfterH <- table(ALSA_ds_w5$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 6 

#### Study-specific variable description



| **Name** | `DATEW6`|
|-|-|
| **Label** | `Wave6 interview date`|
| **Table name** |`ALSA-Wave6`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('DATEW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

**R script:**

```{r preharm w6}

ALSA_w6$yinter <- format(ALSA_w6$DATEW6, '%Y')

```



```{r local6, echo=F}
vbl <- ALSA_w6$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$yintw <- as.numeric(ALSA_w6$yinter)

```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vbl <- ALSA_ds_w6$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ALSA_w6$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w6$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```







### Wave 7 

#### Study-specific variable description



| **Name** | `datew7`|
|-|-|
| **Label** | `date of interview-W7`|
| **Table name** |`dates_of_interview_w7`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7_yinter','ALSA.dates_of_interview_w7',variables=list('datew7'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w7_id','ALSA.ALSA-Wave7', variables=list('sex'), missings = TRUE)
ALSA_w7_yinter <- opal.execute(o,'ALSA_w7_yinter')
ALSA_w7_id <- opal.execute(o,'ALSA_w7_id')
```


**R script:**

```{r preharm w7}

ALSA_w7_yinter$yinter <- format(ALSA_w7_yinter$datew7, '%Y')

```

```{r local7, echo=F}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,2))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], BIRTHDAT=new_2[,2], yinter=as.numeric(new_2[,3]))
  new_22
}

 
ALSA_w7 <- Add_indiv(old = ALSA_w7_yinter, new = ALSA_w7_id)

vbl <- ALSA_w7$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as 996 since they correspond to dead or drop out respondents.


**R script:**

```{r harmo7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$yintw <- car::recode(ALSA_w7$yinter, "NA=996")

```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vbl <- ALSA_ds_w7$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}

```








### Wave 8 

#### Study-specific variable description



| **Name** | `Date`|
|-|-|
| **Label** | `Date`|
| **Table name** |`ALSA-Wave8`|
| **Type of variable** |`date`|
| **Description** |  |
    
```{r assign8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8','ALSA.ALSA-Wave8',variables=list('Date'), missings = TRUE)
ALSA_w8 <- opal.execute(o,'ALSA_w8')
```

**R script:**

```{r preharm w8}

#This function return a table with the date of birth separated by columns:
Date_of_birth <- function(date){
  date <- as.numeric(date)
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
    if(log10(date[i])+1>=8){
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    }
    else{
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    }
  }
  colnames(D) <- c("Year", "Month", "Day")
  D
}

ALSA_w8 <- cbind(ALSA_w8, Date_of_birth(ALSA_w8$Date))

```


```{r local8, echo=F}

vbl <- ALSA_w8$Year
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "Year")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo8}
ALSA_ds_w8 <- tibble(id=ALSA_w8$id)
ALSA_ds_w8$yintw <- ALSA_w8$Year

```

#### Statistics of the new harmonised variable
```{r descript8, echo=F}
vbl <- ALSA_ds_w8$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8, echo=F}
BeforeH <- table(ALSA_w8$Year, useNA = "ifany")
AfterH <- table(ALSA_ds_w8$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```








### Wave 9 

#### Study-specific variable description



| **Name** | `DATEW9`|
|-|-|
| **Label** | `Date of interview Wave 9`|
| **Table name** |`ALSA-Wave9`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('DATEW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

**R script:**

```{r preharm w9}

#This function return a table with the date of birth separated by columns:
Date_of_birth <- function(date){
  date <- as.numeric(date)
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 3)
  for(i in 1:n){
    if(is.na(date[i])){
      D[i,] <- rep(NA,3)
    }
    else{
      D[i,] <- as.numeric(t(sapply(date[i], 
                                               function(x) substring(x, first=c(1, 5, 7), 
                                                                     last=c(4, 6, 8)))))
    } 
  }
 colnames(D) <- c("Year", "Month", "Day")    
 D
}

ALSA_w9 <- cbind(ALSA_w9, Date_of_birth(ALSA_w9$DATEW9))

```

```{r local9, echo=F}

vbl <- ALSA_w9$Year
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "Year")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(Year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values are going to be computed as 996 since they correspond to dead or drop out respondents.


**R script:**

```{r harmo9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$yintw <- car::recode(ALSA_w9$Year, "NA=996")
ALSA_ds_w9$yintw <- labelled(ALSA_ds_w9$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript9, echo=F}
vbl <- ALSA_ds_w9$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9, echo=F}

```







### Wave 10 

#### Study-specific variable description



| **Name** | `Date`|
|-|-|
| **Label** | `Date`|
| **Table name** |`ALSA-Wave10`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10','ALSA.ALSA-Wave10',variables=list('Date'), missings = TRUE)
ALSA_w10 <- opal.execute(o,'ALSA_w10')
```

**R script:**

```{r preharm w10}
ALSA_w10$yinter <- format(ALSA_w10$Date, '%Y')

```

```{r local10, echo=F}
vbl <- ALSA_w10$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo10}
ALSA_ds_w10 <- tibble(id=ALSA_w10$id)
ALSA_ds_w10$yintw <- as.numeric(ALSA_w10$yinter)

```

#### Statistics of the new harmonised variable
```{r descript10, echo=F}
vbl <- ALSA_ds_w10$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10, echo=F}
BeforeH <- table(ALSA_w10$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w10$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 11 

#### Study-specific variable description



| **Name** | `DATEW11`|
|-|-|
| **Label** | `Date of interview Wave 11`|
| **Table name** |`ALSA-Wave11`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('DATEW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
```

**R script:**

```{r preharm w11}
ALSA_w11$yinter <- format(ALSA_w11$DATEW11, '%Y')

```

```{r local11, echo=F}
vbl <- ALSA_w11$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo11}
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$yintw <- as.numeric(ALSA_w11$yinter)

```

#### Statistics of the new harmonised variable
```{r descript11, echo=F}
vbl <- ALSA_ds_w11$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11, echo=F}
BeforeH <- table(ALSA_w11$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w11$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 12 

#### Study-specific variable description



| **Name** | `DATEW12`|
|-|-|
| **Label** | `Date of interview Wave 12`|
| **Table name** |`ALSA-Wave12`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('DATEW12'), missings = TRUE)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
```

**R script:**

```{r preharm w12}
ALSA_w12$yinter <- format(ALSA_w12$DATEW12, '%Y')

```

```{r local12, echo=F}
vbl <- ALSA_w12$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo12}
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$yintw <- as.numeric(ALSA_w12$yinter)
ALSA_ds_w12$yintw <- labelled(ALSA_ds_w12$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript12, echo=F}
vbl <- ALSA_ds_w12$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12, echo=F}
BeforeH <- table(ALSA_w12$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w12$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





### Wave 13 

#### Study-specific variable description



| **Name** | `DATEW13`|
|-|-|
| **Label** | `Date of interview Wave 13`|
| **Table name** |`ALSA-Wave13`|
| **Type of variable** |`date`|
| **Description** |  |

    
```{r assign13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13','ALSA.ALSA-Wave13',variables=list('DATEW13'), missings = TRUE)
ALSA_w13 <- opal.execute(o,'ALSA_w13')
```

**R script:**

```{r preharm w13}
ALSA_w13$yinter <- format(ALSA_w13$DATEW13, '%Y')

```

```{r local13, echo=F}
vbl <- ALSA_w13$yinter
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "yinter")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo13}
ALSA_ds_w13 <- tibble(id=ALSA_w13$id)
ALSA_ds_w13$yintw <- as.numeric(ALSA_w13$yinter)
ALSA_ds_w13$yintw <- labelled(ALSA_ds_w13$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript13, echo=F}
vbl <- ALSA_ds_w13$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation13, echo=F}
BeforeH <- table(ALSA_w13$yinter, useNA = "ifany")
AfterH <- table(ALSA_ds_w13$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")
rm(labelling)
labelling <- labelling_c
rm(summaries)
summaries <- summaries_c


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
The date was the same as the study specific variable taking into account the wave time lapse information. The missing values have been recoded as the most common year between the no missing values. 



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
