---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```


# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `c52a`| `C52b` | `C52c` | `C52d` | `C52e` | `C52f` | `C52g` | `C52h` |
|-|-|-|-|-|-|-|-|-|
| **Label** | `Depression`| `Effort` | `restless sleep` | `Happiness` | `loneliness` | `Enjoy life` | `Sadness` | `Felt tired` | 
| **Table name** | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | 
| **Categories** |`1 = yes`| `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` |
| | `2 = no` | `2 = no`| `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` |
| **Missing** |`8 = RF`| `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | 
| | `9 = DK` | `9 = DK`| `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` |
| **Description** |  ||  |  |  |  |  |  |


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o,  'MHAS_dep','Mexican Health Aging Study.MHAS-2001',
                         variables=list('c52a', 'c52b', 'c52c', 'c52d', 'c52e', 'c52f', 'c52g', 'c52h'), missings = TRUE)
MHAS_dep <- opal.execute(o,'MHAS_dep')
```

```{r local1, echo=FALSE}
vari <- MHAS_dep$c52a
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52c
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52d
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52e
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52f
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52g
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c52h
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 

* The reversed items C52d, c52f: 
    + `recode 1 into 0`
    + `recode 2 into 1`
    
* The direct items c52a, C52b, C52c, C52e, C52g, C52h: 
    + `keep 1 into 1`
    + `recode 2 into 0`


Secondly in order to get the final score the items have to be summed. If one items is missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 8. If more than 1 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 

* `0-3 into 0`
* `>4 into 1`
* `NA into`
    + `997 if the individual has more items = 8 than 9 and NA`
    + `998 if the individual has more items = 9 than 8 and NA`
    + `999 if the individual has more items = NA than 8 and 9`

**R script:**

```{r harmo1, echo=TRUE}
#reversed items
MHAS_dep$pd <- car::recode(MHAS_dep$c52d, "1=0; 2=1; 8=NA; 9=NA")
MHAS_dep$pf <- car::recode(MHAS_dep$c52f, "1=0; 2=1; 8=NA; 9=NA")

#direct items  
MHAS_dep$pa <- car::recode(MHAS_dep$c52a, "2=0; 8=NA; 9=NA")
MHAS_dep$pb <- car::recode(MHAS_dep$c52b, "2=0; 8=NA; 9=NA")
MHAS_dep$pc <- car::recode(MHAS_dep$c52c, "2=0; 8=NA; 9=NA")
MHAS_dep$pe <- car::recode(MHAS_dep$c52e, "2=0; 8=NA; 9=NA")
MHAS_dep$pg <- car::recode(MHAS_dep$c52g, "2=0; 8=NA; 9=NA")
MHAS_dep$ph <- car::recode(MHAS_dep$c52h, "2=0; 8=NA; 9=NA")


MHAS_dep$nmiss <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(is.na(x)))


MHAS_dep$final_score <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))


MHAS_dep$final_score[which(MHAS_dep$nmiss==1)] <- (MHAS_dep$final_score[which(MHAS_dep$nmiss==1)]/7)*8

MHAS_dep$n8 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==8, na.rm = TRUE))
MHAS_dep$n9 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==9, na.rm = TRUE))
MHAS_dep$nNA <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(is.na(x)))

MHAS_dep$max_8_9_NA <- apply(MHAS_dep[,20:22], MARGIN = 1, FUN = function(x) which.max(x))
MHAS_dep$max_8_9_NA <- car::recode(MHAS_dep$max_8_9_NA, "1=997;2=998;3=999")

MHAS_dep$final_score[which(MHAS_dep$nmiss>1)] <- MHAS_dep$max_8_9_NA[which(MHAS_dep$nmiss>1)]

MHAS_ds_w1 <- tibble(id=MHAS_dep$id)
MHAS_ds_w1$depression <- car::recode(MHAS_dep$final_score, "0:3.99999999=0; 4:900=1")
MHAS_ds_w1$depression <- labelled(MHAS_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- MHAS_ds_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(MHAS_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- c(sum(na.omit(MHAS_dep$final_score)<4), sum(na.omit(MHAS_dep$final_score)>=4 & na.omit(MHAS_dep$final_score)<900), sum(na.omit(MHAS_dep$final_score)==997), sum(na.omit(MHAS_dep$final_score)==998), sum(na.omit(MHAS_dep$final_score)==999))
AfterH <- table(MHAS_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<4->0",">=4->1","8->997", "9->998", "NA->999") 
kable(C)
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
label(MHAS_ds_w1$depression) <- ds_label_all
depression <- MHAS_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(depression)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$depression <- car::recode(MHAS_m_ds_w1$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `c49_1`| `c49_2` | `c49_3` | `c49_4` | `c49_5` | `c49_6` | `c49_7` | `c49_8` |
|-|-|-|-|-|-|-|-|-|
| **Label** | `Last week's majority emotions - depressed`| `Last week's majority emotions - everything was an effort` | `Last week's majority emotions - disturbed sleep` | `Last week's majority emotions - happy` | `Last week's majority emotions - alone` | `Last week's majority emotions - enjoying life` | `Last week's majority emotions - sad` | `Last week's majority emotions - tired` | 
| **Table name** | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | `MHAS-2001` | 
| **Categories** |`1 = yes`| `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` |
| | `2 = no` | `2 = no`| `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` |
| **Missing** |`8 = RF`| `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | 
| | `9 = DK` | `9 = DK`| `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` |
| **Description** |  ||  |  |  |  |  |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_dep','Mexican Health Aging Study.MHAS_2003',
                         variables=list('c49_1', 'c49_2', 'c49_3', 'c49_4', 'c49_5', 'c49_6', 'c49_7', 'c49_8'), missings = TRUE)
MHAS_dep <- opal.execute(o,'MHAS_dep')
```

```{r local2, echo=FALSE}
vari <- MHAS_dep$c49_1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_2
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_3
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_4
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_5
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_6
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_7
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_8
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 

* The reversed items c49_4, c49_6: 
    + `recode 1 into 0`
    + `recode 2 into 1`
    
* The direct items c49_1, c49_2, c49_3, c49_5, c49_7, c49_8: 
    + `keep 1 into 1`
    + `recode 2 into 0`


Secondly in order to get the final score the items have to be summed. If one items is missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 8. If more than 1 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 

* `0-3 into 0`
* `>4 into 1`
* `NA into`
    + `997 if the individual has more items = 8 than 9 and NA`
    + `998 if the individual has more items = 9 than 8 and NA`
    + `999 if the individual has more items = NA than 8 and 9`

**R script:**

```{r harmo2, echo=TRUE}
#reversed items
MHAS_dep$p4 <- car::recode(MHAS_dep$c49_4, "1=0; 2=1; 8=NA; 9=NA")
MHAS_dep$p6 <- car::recode(MHAS_dep$c49_6, "1=0; 2=1; 8=NA; 9=NA")

#direct items  
MHAS_dep$p1 <- car::recode(MHAS_dep$c49_1, "2=0; 8=NA; 9=NA")
MHAS_dep$p2 <- car::recode(MHAS_dep$c49_2, "2=0; 8=NA; 9=NA")
MHAS_dep$p3 <- car::recode(MHAS_dep$c49_3, "2=0; 8=NA; 9=NA")
MHAS_dep$p5 <- car::recode(MHAS_dep$c49_5, "2=0; 8=NA; 9=NA")
MHAS_dep$p7 <- car::recode(MHAS_dep$c49_7, "2=0; 8=NA; 9=NA")
MHAS_dep$p8 <- car::recode(MHAS_dep$c49_8, "2=0; 8=NA; 9=NA")


MHAS_dep$nmiss <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(is.na(x)))


MHAS_dep$final_score <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))


MHAS_dep$final_score[which(MHAS_dep$nmiss==1)] <- (MHAS_dep$final_score[which(MHAS_dep$nmiss==1)]/7)*8

MHAS_dep$n8 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==8, na.rm = TRUE))
MHAS_dep$n9 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==9, na.rm = TRUE))
MHAS_dep$nNA <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(is.na(x)))

MHAS_dep$max_8_9_NA <- apply(MHAS_dep[,20:22], MARGIN = 1, FUN = function(x) which.max(x))
MHAS_dep$max_8_9_NA <- car::recode(MHAS_dep$max_8_9_NA, "1=997;2=998;3=999")

MHAS_dep$final_score[which(MHAS_dep$nmiss>1)] <- MHAS_dep$max_8_9_NA[which(MHAS_dep$nmiss>1)]

MHAS_ds_w2 <- tibble(id=MHAS_dep$id)
MHAS_ds_w2$depression <- car::recode(MHAS_dep$final_score, "0:3.99999999=0; 4:900=1")
MHAS_ds_w2$depression <- labelled(MHAS_ds_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- MHAS_ds_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(MHAS_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- c(sum(na.omit(MHAS_dep$final_score)<4), sum(na.omit(MHAS_dep$final_score)>=4 & na.omit(MHAS_dep$final_score)<900), sum(na.omit(MHAS_dep$final_score)==997), sum(na.omit(MHAS_dep$final_score)==998), sum(na.omit(MHAS_dep$final_score)==999))
AfterH <- table(MHAS_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<4->0",">=4->1","8->997", "9->998", "NA->999") 
kable(C)
```


```{r importOPAL2, echo=FALSE}
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
label(MHAS_ds_w2$depression) <- ds_label_all
depression <- MHAS_ds_w2
save(depression, file = "../RData/w2/depression.RData")
rm(depression)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$depression <- car::recode(MHAS_m_ds_w2$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

| **Name** | `c49_1_12`| `c49_2_12` | `c49_3_12` | `c49_4_12` | `c49_5_12` | `c49_6_12` | `c49_7_12` | `c49_8_12` |
|-|-|-|-|-|-|-|-|-|
| **Label** | `Within the past week:Respondent was depressed`| `Within the past week:Respondent experienced difficulty performing` | `Within the past week:Respondent experienced restless sleep` | `Within the past week:Respondent was happy` | `Within the past week:Respondent was lonely` | `Within the past week:Respondent enjoyed life` | `Within the past week:Respondent was sad` | `Within the past week:Respondent felt tired` | 
| **Table name** | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | `MHAS_2012_new` | 
| **Categories** |`1 = yes`| `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` | `1 = yes` |
| | `2 = no` | `2 = no`| `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` | `2 = no` |
| **Missing** |`8 = RF`| `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | `8 = RF` | 
| | `9 = DK` | `9 = DK`| `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` | `9 = DK` |
| **Description** |  ||  |  |  |  |  |  |

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_dep','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('c49_1_12', 'c49_2_12', 'c49_3_12', 'c49_4_12', 'c49_5_12', 'c49_6_12', 'c49_7_12', 'c49_8_12'), missings = TRUE)
MHAS_dep <- opal.execute(o,'MHAS_dep')
```

```{r local3, echo=FALSE}
vari <- MHAS_dep$c49_1_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_3_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_4_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_5_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_6_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_7_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- MHAS_dep$c49_8_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 

* The reversed items c49_4_12, c49_6_12: 
    + `recode 1 into 0`
    + `recode 2 into 1`
    
* The direct items c49_1_12, c49_2_12, c49_3_12,c49_5_12, c49_7_12, c49_8_12: 
    + `keep 1 into 1`
    + `recode 2 into 0`


Secondly in order to get the final score the items have to be summed. If one items is missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 8. If more than 1 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 

* `0-3 into 0`
* `>4 into 1`
* `NA into`
    + `997 if the individual has more items = 8 than 9 and NA`
    + `998 if the individual has more items = 9 than 8 and NA`
    + `999 if the individual has more items = NA than 8 and 9`

**R script:**

```{r harmo3, echo=TRUE}
#reversed items
MHAS_dep$p4 <- car::recode(MHAS_dep$c49_4_12, "1=0; 2=1; 8=NA; 9=NA")
MHAS_dep$p6 <- car::recode(MHAS_dep$c49_6_12, "1=0; 2=1; 8=NA; 9=NA")

#direct items  
MHAS_dep$p1 <- car::recode(MHAS_dep$c49_1_12, "2=0; 8=NA; 9=NA")
MHAS_dep$p2 <- car::recode(MHAS_dep$c49_2_12, "2=0; 8=NA; 9=NA")
MHAS_dep$p3 <- car::recode(MHAS_dep$c49_3_12, "2=0; 8=NA; 9=NA")
MHAS_dep$p5 <- car::recode(MHAS_dep$c49_5_12, "2=0; 8=NA; 9=NA")
MHAS_dep$p7 <- car::recode(MHAS_dep$c49_7_12, "2=0; 8=NA; 9=NA")
MHAS_dep$p8 <- car::recode(MHAS_dep$c49_8_12, "2=0; 8=NA; 9=NA")


MHAS_dep$nmiss <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(is.na(x)))


MHAS_dep$final_score <- apply(MHAS_dep[,10:17], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))


MHAS_dep$final_score[which(MHAS_dep$nmiss==1)] <- (MHAS_dep$final_score[which(MHAS_dep$nmiss==1)]/7)*8

MHAS_dep$n8 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==8, na.rm = TRUE))
MHAS_dep$n9 <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(x==9, na.rm = TRUE))
MHAS_dep$nNA <- apply(MHAS_dep[,2:9], MARGIN = 1, FUN = function(x) sum(is.na(x)))

MHAS_dep$max_8_9_NA <- apply(MHAS_dep[,20:22], MARGIN = 1, FUN = function(x) which.max(x))
MHAS_dep$max_8_9_NA <- car::recode(MHAS_dep$max_8_9_NA, "1=997;2=998;3=999")

MHAS_dep$final_score[which(MHAS_dep$nmiss>1)] <- MHAS_dep$max_8_9_NA[which(MHAS_dep$nmiss>1)]

MHAS_ds_w3 <- tibble(id=MHAS_dep$id)
MHAS_ds_w3$depression <- car::recode(MHAS_dep$final_score, "0:3.99999999=0; 4:900=1")
MHAS_ds_w3$depression <- labelled(MHAS_ds_w3[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- MHAS_ds_w3$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(MHAS_ds_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- c(sum(na.omit(MHAS_dep$final_score)<4), sum(na.omit(MHAS_dep$final_score)>=4 & na.omit(MHAS_dep$final_score)<900), sum(na.omit(MHAS_dep$final_score)==997), sum(na.omit(MHAS_dep$final_score)==998), sum(na.omit(MHAS_dep$final_score)==999))
AfterH <- table(MHAS_ds_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<4->0",">=4->1","8->997", "9->998", "NA->999") 
kable(C)
```


```{r importOPAL3, echo=FALSE}
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
label(MHAS_ds_w3$depression) <- ds_label_all
depression <- MHAS_ds_w3
save(depression, file = "../RData/w3/depression.RData")
rm(depression)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$depression <- car::recode(MHAS_m_ds_w3$depression, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```

# Quality estimation

In the questionnaire there are 9 items, but the last is not a CES-D item 'You felt you had a lot of energy'. For this reason, we deleted C52i (w1), C49_9 (w2), C49_9_12 (w3). We use the ELSA and HRS cut-off for 8-item version test with dichotomic response. =4
We got the final score, due we have only single items
The missing values were treated as follows: maximum 1 missing item was allowed > score the completed items divided by the number of items answered and multiplied by 8


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```



