---
title: "Mobility - Walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_walk`
* Variable label: `Mobility - walking`
* Variable description: `Difficulty for walking by yourself and without using any special equipment`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
   + `1 = None` 
   + `2 = Mild` 
   + `3 = Moderate` 
   + `4 = Severe`
   + `5 = Extreme`
* Missings
   + `9 = Not applicable`
   + `NA`

```{r assign Spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w1_mob_walk','Courage.Courage_Spain_w1', variables=list('q2036_walk'), missings = TRUE)
```

```{r local Spain w1, echo=F}
COURAGE_Spain_w1_mob_walk <-opal.execute(o,'COURAGE_Spain_w1_mob_walk')
vari <- COURAGE_Spain_w1_mob_walk$q2036_walk
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "q2036_walk")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(COURAGE_Spain_w1_mob_walk, aes(x=factor(q2036_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`  
* `9 into 996`
* `NA into 999`

```{r harmo Spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_Spain_w1_mob_walk$id)
COURAGE_ds_spain_w1$mob_walk <- car::recode(COURAGE_Spain_w1_mob_walk$q2036_walk, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';8 = '998'; 9 = '996';NA = '999' ")
COURAGE_ds_spain_w1$mob_walk <- labelled(COURAGE_ds_spain_w1$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w1, echo=F}
vari <- COURAGE_ds_spain_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$mob_walk)
X <- table(COURAGE_Spain_w1_mob_walk$q2036_walk)
BeforeH<- c(sum(X[2:5]),X[c(1,6)],sum(is.na(COURAGE_Spain_w1_mob_walk$q2036_walk)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9->996","NA->999") 
kable(C)
```

```{r importOPAL Spain w1, echo=FALSE}
label(COURAGE_ds_spain_w1$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')
mob_walk <- COURAGE_ds_spain_w1
save(mob_walk, file = "../RData/spain_w1/mob_walk.RData")

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$mob_walk <- car::recode(COURAGE_m_ds_spain_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q2036_walk_s1`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
   + `1 = None` 
   + `2 = Mild` 
   + `3 = Moderate` 
   + `4 = Severe`
   + `5 = Extreme`
* Missings
   + `8 = Don't know`
   + `NA`

```{r assign Spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w2_mob_walk','Courage.Courage_Spain_w2_1', variables=list('q2036_walk_s1'), missings = TRUE)
```

```{r local Spain w2, echo=F}
COURAGE_Spain_w2_mob_walk <- opal.execute(o,'COURAGE_Spain_w2_mob_walk')
vari <- COURAGE_Spain_w2_mob_walk$q2036_walk_s1
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = "q2036_walk_s1")
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
ggplot(COURAGE_Spain_w2_mob_walk, aes(x=factor(q2036_walk_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`   
* `8 into 998`
* `NA into 999`

```{r harmo Spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_Spain_w2_mob_walk$id)
COURAGE_ds_spain_w2$mob_walk <- car::recode(COURAGE_Spain_w2_mob_walk$q2036_walk_s1, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; 8 = '998'; NA = '999' ")
COURAGE_ds_spain_w2$mob_walk <- labelled(COURAGE_ds_spain_w2$mob_walk, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w2, echo=F}
vari <- COURAGE_ds_spain_w2$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$mob_walk)
X <- table(COURAGE_Spain_w2_mob_walk$q2036_walk_s1)
BeforeH<- c(sum(X[2:5]),X[c(1,6)],sum(is.na(COURAGE_Spain_w2_mob_walk$q2036_walk_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","8->998","NA->999") 
kable(C)
```


```{r importOPAL Spain w2, echo=FALSE}
label(COURAGE_ds_spain_w2$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
mob_walk <- COURAGE_ds_spain_w2
save(mob_walk, file = "../RData/spain_w2/mob_walk.RData")

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$mob_walk <- car::recode(COURAGE_m_ds_spain_w2$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```


## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
   + `1 = None` 
   + `2 = Mild` 
   + `3 = Moderate` 
   + `4 = Severe`
   + `5 = Extreme`
* Missings
   + `NA`

```{r assign Poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Poland_w1_mob_walk','Courage.Courage_Poland_w1', variables=list('q2036_walk'), missings = TRUE)
```

```{r local Poland w1, echo=F}
COURAGE_Poland_w1_mob_walk <- opal.execute(o,'COURAGE_Poland_w1_mob_walk')
vari <- COURAGE_Poland_w1_mob_walk$q2036_walk
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2036_walk")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Poland_w1_mob_walk, aes(x=factor(q2036_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`    
* `NA into 999`

```{r harmo Poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_Poland_w1_mob_walk$id)
COURAGE_ds_pol_w1$mob_walk <- car::recode(COURAGE_Poland_w1_mob_walk$q2036_walk, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
COURAGE_ds_pol_w1$mob_walk <- labelled(COURAGE_ds_pol_w1$mob_walk, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w1, echo=F}
vari <- COURAGE_ds_pol_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$mob_walk)
X <- table(COURAGE_Poland_w1_mob_walk$q2036_walk)
BeforeH<- c(sum(X[2:5]),X[c(1)],sum(is.na(COURAGE_Poland_w1_mob_walk$q2036_walk)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```


```{r importOPAL Poland w1, echo=FALSE}
label(COURAGE_ds_pol_w1$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')
mob_walk <- COURAGE_ds_pol_w1
save(mob_walk, file = "../RData/pol_w1/mob_walk.RData")

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$mob_walk <- car::recode(COURAGE_m_ds_pol_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2036_walk_s1`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
   + `1 = None` 
   + `2 = Mild` 
   + `3 = Moderate` 
   + `4 = Severe`
   + `5 = Extreme`
* Missings
   + `NA`

```{r assign Poland w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Poland_w2_mob_walk','Courage.Courage_Poland_w2', variables=list('q2036_walk_s1'), missings = TRUE)
```

```{r local Poland w2, echo=F}
COURAGE_Poland_w2_mob_walk <- opal.execute(o,'COURAGE_Poland_w2_mob_walk')
vari <- COURAGE_Poland_w2_mob_walk$q2036_walk_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2036_walk_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Poland_w2_mob_walk, aes(x=factor(q2036_walk_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`      
* `NA into 999`

```{r harmo Poland w2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_Poland_w2_mob_walk$id)
COURAGE_ds_pol_w2$mob_walk <- car::recode(COURAGE_Poland_w2_mob_walk$q2036_walk_s1, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
COURAGE_ds_pol_w2$mob_walk <- labelled(COURAGE_ds_pol_w2$mob_walk, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w2, echo=F}
vari <- COURAGE_ds_pol_w2$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w2, echo=F}
AfterH <- table(COURAGE_ds_pol_w2$mob_walk)
X <- table(COURAGE_Poland_w2_mob_walk$q2036_walk_s1)
BeforeH<- c(sum(X[2:5]),X[1],sum(is.na(COURAGE_Poland_w2_mob_walk$q2036_walk_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```


```{r importOPAL Poland w2, echo=FALSE}
label(COURAGE_ds_pol_w2$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')
mob_walk <- COURAGE_ds_pol_w2
save(mob_walk, file = "../RData/pol_w2/mob_walk.RData")

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$mob_walk <- car::recode(COURAGE_m_ds_pol_w2$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```


## Finland 

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
   + `1 = None` 
   + `2 = Mild` 
   + `3 = Moderate` 
   + `4 = Severe`
   + `5 = Extreme`
* Missings
   + `8 = Don't know`
   + `9 = Not applicable`
   + `NA`

```{r assign Finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Finland_w1_mob_walk','Courage.Courage_Finland_w1', variables=list('q2036_walk'), missings = TRUE)
```

```{r local Finland w1, echo=F}
COURAGE_Finland_w1_mob_walk <- opal.execute(o,'COURAGE_Finland_w1_mob_walk')
vari <- COURAGE_Finland_w1_mob_walk$q2036_walk
kable(Categorical_summary(vari, missing_values = c(9,8))[3], caption = "q2036_walk")
kable(Categorical_summary(vari, missing_values = c(9,8))[1], caption = "Category")
ggplot(COURAGE_Finland_w1_mob_walk, aes(x=factor(q2036_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`  
* `8 into 998`  
* `9 into 996`  
* `NA into 999`

```{r harmo Finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_Finland_w1_mob_walk$id)
COURAGE_ds_fin_w1$mob_walk <- car::recode(COURAGE_Finland_w1_mob_walk$q2036_walk, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';8 = '998';9 = '996';NA = '999' ")
COURAGE_ds_fin_w1$mob_walk <- labelled(COURAGE_ds_fin_w1$mob_walk, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Finland w1, echo=F}
vari <- COURAGE_ds_fin_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$mob_walk)
X <- table(COURAGE_Finland_w1_mob_walk$q2036_walk)
BeforeH<- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(COURAGE_Finland_w1_mob_walk$q2036_walk)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","9->996","8->998","NA->999") 
kable(C)
```


```{r importOPAL Finland w1, echo=FALSE}
label(COURAGE_ds_fin_w1$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')
mob_walk <- COURAGE_ds_fin_w1
save(mob_walk, file = "../RData/fin_w1/mob_walk.RData")

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$mob_walk <- car::recode(COURAGE_m_ds_fin_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation
The unite in this study was "long distance" or "1km" while in other studies "2km, 100m, 100 yards or 0.5" where the reference.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
