---
title: "ADL- Moving around the home"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `adl_moving`
* Variable label: `ADL-Difficulties for moving around the home`
* Variable description: `ADL-Difficulties for moving around the home`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## Spain

### Wave 1 

#### Study-specific variables description

 


* Name: `q2041_movement`
* Label: `Moving around`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `9 = Not done`
    + `NA`

* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `9 = Not applicable`
    + `NA`
   
* Description: 
```{r assign Spain w1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_Spain_w1_adl_moving','Courage.Courage_Spain_w1', variables=list('q2041_movement', 'q2036_walk'), missings = TRUE)
COURAGE_Spain_w1_adl_moving <-opal.execute(o,'COURAGE_Spain_w1_adl_moving')
```

```{r local Spain w1,  echo=FALSE}
vari <- COURAGE_Spain_w1_adl_moving$q2041_movement # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Spain_w1_adl_moving$q2041_movement, missing_values = c(9))
ggplot(COURAGE_Spain_w1_adl_moving, aes(x=factor(q2041_movement))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")

vari <- COURAGE_Spain_w1_adl_moving$q2036_walk # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Spain_w1_adl_moving$q2036_walk, missing_values = c(9))
ggplot(COURAGE_Spain_w1_adl_moving, aes(x=factor(q2036_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `q2036_walk = 1 into 1`

* `q2041_movement = 1 into 1` 
* `q2041_movement = 2 into 0` 
* `q2041_movement = 3 into 0` 
* `q2041_movement = 4 into 0` 
* `q2041_movement = 5 into 0`  
* `q2041_movement = 9 into 996`
* `q2041_movement = NA into 999`

**R script:** 
```{r harmo Spain w1,   echo=TRUE}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_Spain_w1_adl_moving$id)
COURAGE_ds_spain_w1$adl_moving <- car::recode(COURAGE_Spain_w1_adl_moving$q2041_movement, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';8 = '998'; 9 = '996';NA = '999' ")
COURAGE_ds_spain_w1$adl_moving[which(COURAGE_Spain_w1_adl_moving$q2036_walk==1)] <- 1
COURAGE_ds_spain_w1$adl_moving <- labelled(COURAGE_ds_spain_w1$adl_moving, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w1,  echo=FALSE}
vari <- COURAGE_ds_spain_w1$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w1$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w1,  echo=FALSE}
AfterH <- table(COURAGE_ds_spain_w1$adl_moving)
X <- table(COURAGE_Spain_w1_adl_moving$q2041_movement)
Y <- table(COURAGE_Spain_w1_adl_moving$q2036_walk)
BeforeH <- c(sum(X[2:5]), X[1]+Y[1], length(which(COURAGE_Spain_w1_adl_moving$q2036_walk%nin%1&is.na(COURAGE_Spain_w1_adl_moving$q2041_movement))))
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("walk not 1 + movement = 2,3,4,5 -> 0"," walk = 1 + movement = 1 -> 1","walk = 1 + movement NA -> 999")
kable(C)
```



```{r importOPAL Spain w1, echo=FALSE,  echo=FALSE}
label(COURAGE_ds_spain_w1$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$adl_moving <- car::recode(COURAGE_m_ds_spain_w1$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- COURAGE_ds_spain_w1
save(adl_moving, file = paste0(datafolder, "/spain_w1/adl_moving.RData"))
```

### Wave 2

#### Study-specific variables description

 

* Name: `q2041_movement_s1`
* Label: `Moving around`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `8 = Don't know`
    + `NA`
   
* Name: `q2036_walk_s1`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `8 = Don't know`
    + `NA`

* Description: 
```{r assign Spain w2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_Spain_w2_adl_moving','Courage.Courage_Spain_w2_1', variables=list('q2041_movement_s1', 'q2036_walk_s1'), missings = TRUE)
COURAGE_Spain_w2_adl_moving <- opal.execute(o,'COURAGE_Spain_w2_adl_moving')
```

```{r local Spain w2,  echo=FALSE}
vari <- COURAGE_Spain_w2_adl_moving$q2041_movement_s1 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Spain_w2_adl_moving$q2041_movement_s1, missing_values = c(8))
ggplot(COURAGE_Spain_w2_adl_moving, aes(x=factor(q2041_movement_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")

vari <- COURAGE_Spain_w2_adl_moving$q2036_walk_s1 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Spain_w2_adl_moving$q2036_walk_s1, missing_values = c(8))
ggplot(COURAGE_Spain_w2_adl_moving, aes(x=factor(q2036_walk_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`   
* `8 into 998`
* `NA into 999`

**R script:** 
```{r harmo Spain w2,   echo=TRUE}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_Spain_w2_adl_moving$id)
COURAGE_ds_spain_w2$adl_moving <- car::recode(COURAGE_Spain_w2_adl_moving$q2041_movement_s1, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; 8 = '998'; NA = '999' ")
COURAGE_ds_spain_w2$adl_moving[which(COURAGE_Spain_w2_adl_moving$q2036_walk_s1==1)] <- 1
COURAGE_ds_spain_w2$adl_moving <- labelled(COURAGE_ds_spain_w2$adl_moving, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w2,  echo=FALSE}
vari <- COURAGE_ds_spain_w2$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_spain_w2$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w2,  echo=FALSE}

AfterH <- table(COURAGE_ds_spain_w2$adl_moving)
X <- table(COURAGE_Spain_w2_adl_moving$q2041_movement_s1)
Y <- table(COURAGE_Spain_w2_adl_moving$q2036_walk_s1)
BeforeH <- c(sum(X[2:5]), X[1]+Y[1], length(which(COURAGE_Spain_w2_adl_moving$q2036_walk_s1%nin%1&is.na(COURAGE_Spain_w2_adl_moving$q2041_movement_s1))))
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("walk not 1 + movement = 2,3,4,5 -> 0"," walk = 1 + movement = 1 -> 1","walk = 1 + movement NA -> 999")
kable(C)
```

```{r importOPAL Spain w2, echo=FALSE,  echo=FALSE}
label(COURAGE_ds_spain_w2$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$adl_moving <- car::recode(COURAGE_m_ds_spain_w2$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- COURAGE_ds_spain_w2
save(adl_moving, file = paste0(datafolder, "/spain_w2/adl_moving.RData"))
```

## Poland 

### Wave 1 

#### Study-specific variable description

 

* Name: `q2041_movement`
* Label: `Moving around`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `NA`
   
* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `NA`

* Description: 
```{r assign Poland w1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_Poland_w1_adl_moving','Courage.Courage_Poland_w1', variables=list('q2041_movement', 'q2036_walk'), missings = TRUE)
COURAGE_Poland_w1_adl_moving <- opal.execute(o,'COURAGE_Poland_w1_adl_moving')
```

```{r local Poland w1,  echo=FALSE}
vari <- COURAGE_Poland_w1_adl_moving$q2041_movement # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Poland_w1_adl_moving$q2041_movement)
ggplot(COURAGE_Poland_w1_adl_moving, aes(x=factor(q2041_movement))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")

vari <- COURAGE_Poland_w1_adl_moving$q2036_walk # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Poland_w1_adl_moving$q2036_walk)
ggplot(COURAGE_Poland_w1_adl_moving, aes(x=factor(q2036_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`    
* `NA into 999`

**R script:** 
```{r harmo Poland w1,   echo=TRUE}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_Poland_w1_adl_moving$id)
COURAGE_ds_pol_w1$adl_moving <- car::recode(COURAGE_Poland_w1_adl_moving$q2041_movement, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
COURAGE_ds_pol_w1$adl_moving[which(COURAGE_Poland_w1_adl_moving$q2036_walk==1)] <- 1
COURAGE_ds_pol_w1$adl_moving <- labelled(COURAGE_ds_pol_w1$adl_moving, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w1,  echo=FALSE}
vari <- COURAGE_ds_pol_w1$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w1$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w1,  echo=FALSE}
AfterH <- table(COURAGE_ds_pol_w1$adl_moving)
X <- table(COURAGE_Poland_w1_adl_moving$q2041_movement)
Y <- table(COURAGE_Poland_w1_adl_moving$q2036_walk)
BeforeH <- c(sum(X[2:5]), X[1]+Y[1], length(which(COURAGE_Poland_w1_adl_moving$q2036_walk%nin%1&is.na(COURAGE_Poland_w1_adl_moving$q2041_movement))))
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("walk not 1 + movement = 2,3,4,5 -> 0"," walk = 1 + movement = 1 -> 1","walk = 1 + movement NA -> 999")
kable(C)
```


```{r importOPAL Poland w1, echo=FALSE,  echo=FALSE}
label(COURAGE_ds_pol_w1$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$adl_moving <- car::recode(COURAGE_m_ds_pol_w1$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- COURAGE_ds_pol_w1
save(adl_moving, file = paste0(datafolder, "/pol_w1/adl_moving.RData"))
```
### Wave 2

#### Study-specific variable description

 


* Name: `q2041_movement_s1`
* Label: `Moving around`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `NA`

* Name: `q2036_walk_s1`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `NA`
   
* Description: 
```{r assign Poland w2,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_Poland_w2_adl_moving','Courage.Courage_Poland_w2', variables=list('q2041_movement_s1', 'q2036_walk_s1'), missings = TRUE)
COURAGE_Poland_w2_adl_moving <- opal.execute(o,'COURAGE_Poland_w2_adl_moving')
```

```{r local Poland w2,  echo=FALSE}
vari <- COURAGE_Poland_w2_adl_moving$q2041_movement_s1 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Poland_w2_adl_moving$q2041_movement_s1)
ggplot(COURAGE_Poland_w2_adl_moving, aes(x=factor(q2041_movement_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")

vari <- COURAGE_Poland_w2_adl_moving$q2036_walk_s1 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Poland_w2_adl_moving$q2036_walk_s1)
ggplot(COURAGE_Poland_w2_adl_moving, aes(x=factor(q2036_walk_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`      
* `NA into 999`

**R script:** 
```{r harmo Poland w2,   echo=TRUE}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_Poland_w2_adl_moving$id)
COURAGE_ds_pol_w2$adl_moving <- car::recode(COURAGE_Poland_w2_adl_moving$q2041_movement_s1, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
COURAGE_ds_pol_w2$adl_moving[which(COURAGE_Poland_w2_adl_moving$q2036_walk_s1==1)] <- 1
COURAGE_ds_pol_w2$adl_moving <- labelled(COURAGE_ds_pol_w2$adl_moving, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w2,  echo=FALSE}
vari <- COURAGE_ds_pol_w2$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_pol_w2$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w2,  echo=FALSE}
AfterH <- table(COURAGE_ds_pol_w2$adl_moving)
X <- table(COURAGE_Poland_w2_adl_moving$q2041_movement_s1)
Y <- table(COURAGE_Poland_w2_adl_moving$q2036_walk_s1)
BeforeH <- c(sum(X[2:5]), X[1]+Y[1], length(which(COURAGE_Poland_w2_adl_moving$q2036_walk_s1%nin%1&is.na(COURAGE_Poland_w2_adl_moving$q2041_movement_s1))))
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("walk not 1 + movement = 2,3,4,5 -> 0"," walk = 1 + movement = 1 -> 1","walk = 1 + movement NA -> 999")
kable(C)
```


```{r importOPAL Poland w2, echo=FALSE,  echo=FALSE}
label(COURAGE_ds_pol_w2$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$adl_moving <- car::recode(COURAGE_m_ds_pol_w2$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- COURAGE_ds_pol_w2
save(adl_moving, file = paste0(datafolder, "/pol_w2/adl_moving.RData"))
```

## Finland

### Wave 1 

#### Study-specific variable description

 

* Name: `q2041_movement`
* Label: `Moving around`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `8 = Don't know`
    + `9 = Not applicable`
    + `NA`

* Name: `q2036_walk`
* Label: `Overall in the last 30 days, how much difficulty did you have . in walking a long distance such as a kilometre (or equivalent)?`
* Categories:
    + `1 = None` 
    + `2 = Mild` 
    + `3 = Moderate` 
    + `4 = Severe`
    + `5 = Extreme`
* Missings
    + `8 = Don't know`
    + `9 = Not applicable`
    + `NA`

* Description: 
```{r assign Finland w1,  echo=FALSE}
opal.assign.table.tibble(o, 'COURAGE_Finland_w1_adl_moving','Courage.Courage_Finland_w1', variables=list('q2041_movement', 'q2036_walk'), missings = TRUE)
COURAGE_Finland_w1_adl_moving <- opal.execute(o,'COURAGE_Finland_w1_adl_moving')
```

```{r local Finland w1,  echo=FALSE}
vari <- COURAGE_Finland_w1_adl_moving$q2041_movement # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Finland_w1_adl_moving$q2041_movement, missing_values = c(8,9))
ggplot(COURAGE_Finland_w1_adl_moving, aes(x=factor(q2041_movement))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")

vari <- COURAGE_Finland_w1_adl_moving$q2036_walk # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(COURAGE_Finland_w1_adl_moving$q2036_walk, missing_values = c(8,9))
ggplot(COURAGE_Finland_w1_adl_moving, aes(x=factor(q2041_movement))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `3 into 0` 
* `4 into 0` 
* `5 into 0`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:** 
```{r harmo Finland w1,   echo=TRUE}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_Finland_w1_adl_moving$id)
COURAGE_ds_fin_w1$adl_moving <- car::recode(COURAGE_Finland_w1_adl_moving$q2041_movement, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';8 = '998';9 = '996';NA = '999' ")
COURAGE_ds_fin_w1$adl_moving[which(COURAGE_Finland_w1_adl_moving$q2036_walk==1)] <- 1
COURAGE_ds_fin_w1$adl_moving <- labelled(COURAGE_ds_fin_w1$adl_moving, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Finland w1,  echo=FALSE}
vari <- COURAGE_ds_fin_w1$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = COURAGE_ds_fin_w1$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Finland w1,  echo=FALSE}
AfterH <- table(COURAGE_ds_fin_w1$adl_moving)
X <- table(COURAGE_Finland_w1_adl_moving$q2041_movement)
Y <- table(COURAGE_Finland_w1_adl_moving$q2036_walk)
BeforeH <- c(sum(X[2:5]), X[1]+Y[1], X[7], X[6], length(which(COURAGE_Finland_w1_adl_moving$q2036_walk%nin%1&is.na(COURAGE_Finland_w1_adl_moving$q2041_movement))))
C <- rbind(BeforeH, AfterH)
colnames(C) <- c("walk not 1 + movement = 2,3,4,5 -> 0"," walk = 1 + movement = 1 -> 1",
                 "walk not 1 + movement = 9 -> 996", "walk not 1 + movement = 8 -> 998","walk = 1 + movement NA -> 999")
kable(C)
```

```{r importOPAL Finland w1, echo=FALSE,  echo=FALSE}
label(COURAGE_ds_fin_w1$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$adl_moving <- car::recode(COURAGE_m_ds_fin_w1$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- COURAGE_ds_fin_w1
save(adl_moving, file = paste0(datafolder, "/fin_w1/adl_moving.RData"))
```

# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.

