---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain

### Wave 1

Not found.

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q1038a_s1`
* Label: `Mm year`
* Categories:
   + `0 = Incorrect` 
   + `1 = Correct` 
* Missings
   + `NA`
   
* Name: `q1038c_s1`
* Label: `Mm month`
* Categories:
   + `0 = Incorrect` 
   + `1 = Correct` 
* Missings
   + `NA`
   
* Name: `q1038d_s1`
* Label: `Mm day of the week`
* Categories:
   + `0 = Incorrect` 
   + `1 = Correct` 
* Missings
   + `NA`

* Name: `q1038e_s1`
* Label: `Mm day of the month`
* Categories:
   + `0 = Incorrect` 
   + `1 = Correct` 
* Missings
   + `NA`

```{r assign Spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w2_orientation','Courage.Courage_Spain_w2_1', variables=list('q1038a_s1','q1038c_s1','q1038d_s1','q1038e_s1'), missings = TRUE)
```

```{r local Spain w2, echo=F}
COURAGE_Spain_w2_orientation <- opal.execute(o,'COURAGE_Spain_w2_orientation')
vari <- COURAGE_Spain_w2_orientation$q1038a_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q1038a_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w2_orientation, aes(x=factor(q1038a_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
vari <- COURAGE_Spain_w2_orientation$q1038c_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q1038c_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w2_orientation, aes(x=factor(q1038c_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
vari <- COURAGE_Spain_w2_orientation$q1038d_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q1038d_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w2_orientation, aes(x=factor(q1038d_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
vari <- COURAGE_Spain_w2_orientation$q1038e_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q1038e_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w2_orientation, aes(x=factor(q1038e_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

```{r harmo Spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_Spain_w2_orientation$id)
COURAGE_ds_spain_w2$orientation <- rep(999,length(COURAGE_Spain_w2_orientation$id))
COURAGE_ds_spain_w2$orientation[((COURAGE_Spain_w2_orientation$q1038a_s1==1)&(COURAGE_Spain_w2_orientation$q1038c_s1==1)&(COURAGE_Spain_w2_orientation$q1038d_s1==1)&(COURAGE_Spain_w2_orientation$q1038e_s1==1))]<-1
COURAGE_ds_spain_w2$orientation[((COURAGE_Spain_w2_orientation$q1038a_s1==0)|(COURAGE_Spain_w2_orientation$q1038c_s1==0)|(COURAGE_Spain_w2_orientation$q1038d_s1==0)|(COURAGE_Spain_w2_orientation$q1038e_s1==0))]<-0

COURAGE_ds_spain_w2$orientation <- labelled(COURAGE_ds_spain_w2$orientation, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w2, echo=F}
vari <- COURAGE_ds_spain_w2$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$orientation)
combi<-sum(na.omit((COURAGE_Spain_w2_orientation$q1038a_s1==1)&(COURAGE_Spain_w2_orientation$q1038c_s1==1)&(COURAGE_Spain_w2_orientation$q1038d_s1==1)&(COURAGE_Spain_w2_orientation$q1038e_s1==1)))
nota<-sum((COURAGE_Spain_w2_orientation$q1038a_s1==0)|(COURAGE_Spain_w2_orientation$q1038c_s1==0)|(COURAGE_Spain_w2_orientation$q1038d_s1==0)|(COURAGE_Spain_w2_orientation$q1038e_s1==0),na.rm=T)
BeforeH<- c(nota,combi,length(COURAGE_Spain_w2_orientation$q1038a_s1)-combi-nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```



```{r importOPAL Spain w2, echo=FALSE}
label(COURAGE_ds_spain_w2$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
orientation <- COURAGE_ds_spain_w2
save(orientation, file = "../RData/spain_w2/orientation.RData")

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$orientation <- car::recode(COURAGE_m_ds_spain_w2$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```

## Poland

### Wave 1

Not found.

### Wave 2

Not found.

## Finland 

### Wave 1

Not found.



# Quality estimation
For this study, the variable is a composed combining day of the month,
day of the week, month, and year which is different from the calculation performed in other studies where day of the month,
season is also available (or some of these variables are not).

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
