---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process

## Finland

### Wave 1


#### Study-specific variable description

| **Name** | `q7009c_achieve` |
|-|-|
| **Label** | `Opportunities to achieve`| 
| **Table name**  | `Courage_Finland_w1`| 
| **Categories** | `1 = Not at all`<br/> `2 = A little` <br/> `3 = Moderately` <br/> `4 = Mostly` <br/> `5 = Completely`| 
| **Missings** |`NA`| 
| **Description** |  | 


```{r assign fin_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_wb', 'Courage.Courage_Finland_w1', variables=list('q7009c_achieve'), missings = T)
Courage_wb <- opal.execute(o,'Courage_wb')

```



```{r local fin_w1, echo=F}

vbl <- Courage_wb$q7009c_achieve
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = names(Courage_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Courage_wb, aes(x=factor(q7009c_achieve))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo fin_w1}
# Categorical variable harmonization
COURAGE_ds_fin_w1 <- tibble(id=Courage_wb$id)
COURAGE_ds_fin_w1$eudaimonic_wb <- car::recode(Courage_wb$q7009c_achieve, "1=0; 2=0; 3=1; 4=2; 5=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript fin_w1, echo=F}

vbl <- COURAGE_ds_fin_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation fin_w1, echo=F}

```



## Poland

### Wave 1


#### Study-specific variable description

| **Name** | `q7009c_achieve` |
|-|-|
| **Label** | `Opportunities to achieve`| 
| **Table name**  | `Courage_Poland_w1`| 
| **Categories** | `1 = Not at all`<br/> `2 = A little` <br/> `3 = Moderately` <br/> `4 = Mostly` <br/> `5 = Completely`| 
| **Missings** |`NA`| 
| **Description** |  | 



```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_wb', 'Courage.Courage_Poland_w1', variables=list('q7009c_achieve'), missings = T)
Courage_wb <- opal.execute(o,'Courage_wb')

```



```{r local pol_w1, echo=F}

vbl <- Courage_wb$q7009c_achieve
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = names(Courage_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Courage_wb, aes(x=factor(q7009c_achieve))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
COURAGE_ds_pol_w1 <- tibble(id=Courage_wb$id)
COURAGE_ds_pol_w1$eudaimonic_wb <- car::recode(Courage_wb$q7009c_achieve, "1=0; 2=0; 3=1; 4=2; 5=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- COURAGE_ds_pol_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```



#### Validation

```{r crosstabulation pol_w1, echo=F}

```




### Wave 2

#### Study-specific variable description

| **Name** | `q7009c_achieve_s1` |
|-|-|
| **Label** | `Opportunities to achieve`| 
| **Table name**  | `Courage_Poland_w2`| 
| **Categories** | `1 = Not at all`<br/> `2 = A little` <br/> `3 = Moderately` <br/> `4 = Mostly` <br/> `5 = Completely`| 
| **Missings** |`NA`| 
| **Description** |  | 


```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'Courage_wb', 'Courage.Courage_Poland_w2', variables=list('q7009c_achieve_s1'), missings = T)
Courage_wb <- opal.execute(o,'Courage_wb')

```



```{r local pol_w2, echo=F}

vbl <- Courage_wb$q7009c_achieve_s1
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = names(Courage_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Courage_wb, aes(x=factor(q7009c_achieve_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo pol_w2}

# Categorical variable harmonization
COURAGE_ds_pol_w2 <- tibble(id=Courage_wb$id)
COURAGE_ds_pol_w2$eudaimonic_wb <- car::recode(Courage_wb$q7009c_achieve_s1, "1=0; 2=0; 3=1; 4=2; 5=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- COURAGE_ds_pol_w2$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w2, echo=F}

```


## Spain

### Wave 1

#### Study-specific variable description

| **Name** | `q7009c_achieve` |
|-|-|
| **Label** | `Opportunities to achieve`| 
| **Table name**  | `Courage_Spain_w1`| 
| **Categories** | `1 = Not at all`<br/> `2 = A little` <br/> `3 = Moderately` <br/> `4 = Mostly` <br/> `5 = Completely`| 
| **Missings** |`NA`| 
| **Description** |  |

```{r assign spain_w1, echo=F}

opal.assign.table.tibble(o, 'Courage_wb','Courage.Courage_Spain_w1',variables=list('q7009c_achieve'), missings = T)
Courage_wb <- opal.execute(o,'Courage_wb')

```



```{r local spain_w1, echo=F}

vbl <- Courage_wb$q7009c_achieve
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = names(Courage_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Courage_wb, aes(x=factor(q7009c_achieve))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo spain_w1}

# Categorical variable harmonization
COURAGE_ds_spain_w1 <- tibble(id=Courage_wb$id)
COURAGE_ds_spain_w1$eudaimonic_wb <- car::recode(Courage_wb$q7009c_achieve, "1=0; 2=0; 3=1; 4=2; 5=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript spain_w1, echo=F}

vbl <- COURAGE_ds_spain_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w1, echo=F}

```




### Wave 2


#### Study-specific variable description

| **Name** | `q7009c_achieve_s1` |
|-|-|
| **Label** | `Opportunities to achieve`| 
| **Table name**  | `Courage_Spain_w2_1`| 
| **Categories** | `1 = Not at all`<br/> `2 = A little` <br/> `3 = Moderately` <br/> `4 = Mostly` <br/> `5 = Completely`| 
| **Missings** |`NA`| 
| **Description** |  | 


```{r assign spain_w2, echo=F}

opal.assign.table.tibble(o, 'Courage_wb','Courage.Courage_Spain_w2_1',variables=list('q7009c_achieve_s1'), missings = T)
Courage_wb <- opal.execute(o,'Courage_wb')

```



```{r local spain_w2, echo=F}

vbl <- Courage_wb$q7009c_achieve_s1
vbl_miss <- NA
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = names(Courage_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Courage_wb, aes(x=factor(q7009c_achieve_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2`
* `NA into 999`


**R script:**

```{r harmo spain_w2}

# Categorical variable harmonization
COURAGE_ds_spain_w2 <- tibble(id=Courage_wb$id)
COURAGE_ds_spain_w2$eudaimonic_wb <- car::recode(Courage_wb$q7009c_achieve_s1, "1=0; 2=0; 3=1; 4=2; 5=2; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript spain_w2, echo=F}

vbl <- COURAGE_ds_spain_w2$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation spain_w2, echo=F}

```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:







```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





