---
title: "Walking speed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `walking_speed_c`
* Variable label: `Walking speed - Continuous`
* Variable description: `Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance.`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `walking_speed`
* Variable label: `Walking speed`
* Variable description: `Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Walking speed"
ds_label_walking_speed_c <- "Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance"
ds_label_walking_speed <- "Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%."
```

# Data process

## Spain 

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2513_4m`
* Label: `4 m. time`
* Categories:
   + `Continuous`
* Missings
   + `NA`

```{r assign Spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w1_walking_speed','Courage.Courage_Spain_w1', variables=list('q2513_4m'), missings = TRUE)
COURAGE_Spain_w1_walking_speed <- opal.execute(o,'COURAGE_Spain_w1_walking_speed')
```

```{r local Spain w1, echo=F}
vari <- COURAGE_Spain_w1_walking_speed$q2513_4m
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "q2513_4m")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_Spain_w1_walking_speed, aes(q2513_4m)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("walking_time") + ylab("Frequency")+xlim(0,36)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `4m / time` 
* `NA into 999`
To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo Spain w1}
#walking_speed_c
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_Spain_w1_walking_speed$id)
COURAGE_ds_spain_w1$walking_speed_c <- car::recode(4.0/COURAGE_Spain_w1_walking_speed$q2513_4m, "NA = '999' ")
COURAGE_ds_spain_w1$walking_speed_c <- labelled(COURAGE_ds_spain_w1$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#walking_speed
Q <- quantile(car::recode(COURAGE_ds_spain_w1$walking_speed_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

COURAGE_ds_spain_w1$walking_speed <- car::recode(COURAGE_ds_spain_w1[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
COURAGE_ds_spain_w1$walking_speed <- labelled(COURAGE_ds_spain_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w1, echo=F}
vari <- COURAGE_ds_spain_w1$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w1, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,5)

vari <- COURAGE_ds_spain_w1$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w1, echo=F}
Continous <- c(sum(na.omit(COURAGE_ds_spain_w1[[2]])<=Q), sum(na.omit(COURAGE_ds_spain_w1[[2]])>Q & na.omit(COURAGE_ds_spain_w1[[2]])<900), sum(na.omit(COURAGE_ds_spain_w1[[2]])==999))
Dicotomic <- table(COURAGE_ds_spain_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Spain w1, echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_spain_w1$walking_speed_c) <- ds_label_walking_speed_c
label(COURAGE_ds_spain_w1$walking_speed) <- ds_label_walking_speed
walking_speed <- COURAGE_ds_spain_w1
save(walking_speed, file = "../RData/spain_w1/walking_speed.RData")

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$walking_speed <- car::recode(COURAGE_m_ds_spain_w1$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q2513_4m_s1`
* Label: `4 m. time`
* Categories:
   + `Continuous`
* Missings
   + `NA`

```{r assign Spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w2_walking_speed','Courage.Courage_Spain_w2_1', variables=list('q2513_4m_s1'), missings = TRUE)
COURAGE_Spain_w2_walking_speed <- opal.execute(o,'COURAGE_Spain_w2_walking_speed')
```

```{r local Spain w2, echo=F}
vari <- COURAGE_Spain_w2_walking_speed$q2513_4m_s1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "q2513_4m_s1")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_Spain_w2_walking_speed, aes(q2513_4m_s1)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("walking_time") + ylab("Frequency")+xlim(1,80)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `4m / time` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo Spain w2}
#walking_speed_c
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_Spain_w2_walking_speed$id)
COURAGE_ds_spain_w2$walking_speed_c <- car::recode(4/COURAGE_Spain_w2_walking_speed$q2513_4m_s1, "NA=999")
COURAGE_ds_spain_w2$walking_speed_c <- labelled(COURAGE_ds_spain_w2$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#walking_speed
Q <- quantile(car::recode(COURAGE_ds_spain_w2$walking_speed_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

COURAGE_ds_spain_w2$walking_speed <- car::recode(COURAGE_ds_spain_w2[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
COURAGE_ds_spain_w2$walking_speed <- labelled(COURAGE_ds_spain_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w2, echo=F}
vari <- COURAGE_ds_spain_w2$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,5)

vari <- COURAGE_ds_spain_w2$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w2, echo=F}
Continous <- c(sum(na.omit(COURAGE_ds_spain_w2[[2]])<=Q), sum(na.omit(COURAGE_ds_spain_w2[[2]])>Q & na.omit(COURAGE_ds_spain_w2[[2]])<900), sum(na.omit(COURAGE_ds_spain_w2[[2]])==999))
Dicotomic <- table(COURAGE_ds_spain_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


```{r importOPAL Spain w2, echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_spain_w2$walking_speed_c) <- ds_label_walking_speed_c
label(COURAGE_ds_spain_w2$walking_speed) <- ds_label_walking_speed
walking_speed <- COURAGE_ds_spain_w2
save(walking_speed, file = "../RData/spain_w2/walking_speed.RData")

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$walking_speed <- car::recode(COURAGE_m_ds_spain_w2$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```


## Poland 

### Wave 1 

##### Study-specific variables

The study-specific variables elected to be harmonised is:

* Name: `q2513_4m`
* Label: `4 m. time`
* Categories:
   + `Continuous`
* Missings
   + `NA`

```{r assign Poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Poland_w1_walking_speed','Courage.Courage_Poland_w1', variables=list('q2513_4m'), missings = TRUE)
COURAGE_Poland_w1_walking_speed <- opal.execute(o,'COURAGE_Poland_w1_walking_speed')
```

```{r local Poland w1, echo=F}
vari <- COURAGE_Poland_w1_walking_speed$q2513_4m
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "q2513_4m")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_Poland_w1_walking_speed, aes(q2513_4m)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("walking_time") + ylab("Frequency")+xlim(0,80)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `4m / time` 
* `NA into 999`
To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo Poland w1}
#walking_speed_c
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_Poland_w1_walking_speed$id)
COURAGE_ds_pol_w1$walking_speed_c <- car::recode(4/COURAGE_Poland_w1_walking_speed$q2513_4m, "NA=999")
COURAGE_ds_pol_w1$walking_speed_c <- labelled(COURAGE_ds_pol_w1$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#walking_speed
Q <- quantile(car::recode(COURAGE_ds_pol_w1$walking_speed_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

COURAGE_ds_pol_w1$walking_speed <- car::recode(COURAGE_ds_pol_w1[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
COURAGE_ds_pol_w1$walking_speed <- labelled(COURAGE_ds_pol_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w1, echo=F}
vari <- COURAGE_ds_pol_w1$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w1, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,5)

vari <- COURAGE_ds_pol_w1$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w1, echo=F}
Continous <- c(sum(na.omit(COURAGE_ds_pol_w1[[2]])<=Q), sum(na.omit(COURAGE_ds_pol_w1[[2]])>Q & na.omit(COURAGE_ds_pol_w1[[2]])<900), sum(na.omit(COURAGE_ds_pol_w1[[2]])==999))
Dicotomic <- table(COURAGE_ds_pol_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


```{r importOPAL Poland w1, echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_pol_w1$walking_speed_c) <- ds_label_walking_speed_c
label(COURAGE_ds_pol_w1$walking_speed) <- ds_label_walking_speed
walking_speed <- COURAGE_ds_pol_w1
save(walking_speed, file = "../RData/pol_w1/walking_speed.RData")

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$walking_speed <- car::recode(COURAGE_m_ds_pol_w1$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```

### Wave 2

Not found.


## Finland 

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q2513_4m`
* Label: `4 m. time`
* Categories:
   + `Continuous`
* Missings
   + `NA`

```{r assign Finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Finland_w1_walking_speed','Courage.Courage_Finland_w1', variables=list('q2513_4m'), missings = TRUE)
COURAGE_Finland_w1_walking_speed <- opal.execute(o,'COURAGE_Finland_w1_walking_speed')
```

```{r local Finland w1, echo=F}
vari <- COURAGE_Finland_w1_walking_speed$q2513_4m
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "q2513_4m")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(COURAGE_Finland_w1_walking_speed, aes(q2513_4m)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("walking_time") + ylab("Frequency")+xlim(0,25)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `4m / time` 
* `NA into 999`
* `We assume the answer is transcripted as 0 is due to an interviewer error, so 4/0=Inf -> 991`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo Finland w1}
#walking_speed_c
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_Finland_w1_walking_speed$id)
COURAGE_ds_fin_w1$walking_speed_c <- car::recode(4/COURAGE_Finland_w1_walking_speed$q2513_4m, "NA=999; Inf=991")
COURAGE_ds_fin_w1$walking_speed_c <- labelled(COURAGE_ds_fin_w1$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#walking_speed
Q <- quantile(car::recode(COURAGE_ds_fin_w1$walking_speed_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

COURAGE_ds_fin_w1$walking_speed <- car::recode(COURAGE_ds_fin_w1[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
COURAGE_ds_fin_w1$walking_speed <- labelled(COURAGE_ds_fin_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Finland w1, echo=F}
vari <- COURAGE_ds_fin_w1$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(COURAGE_ds_fin_w1, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,5)

vari <- COURAGE_ds_fin_w1$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Finland w1, echo=F}
Continous <- c(sum(na.omit(COURAGE_ds_fin_w1[[2]])<=Q), sum(na.omit(COURAGE_ds_fin_w1[[2]])>Q & na.omit(COURAGE_ds_fin_w1[[2]])<900), sum(na.omit(COURAGE_ds_fin_w1[[2]])==991),  sum(na.omit(COURAGE_ds_fin_w1[[2]])==999))
Dicotomic <- table(COURAGE_ds_fin_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "0->991", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Finland w1, echo=FALSE}
#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')
label(COURAGE_ds_fin_w1$walking_speed_c) <- ds_label_walking_speed_c
label(COURAGE_ds_fin_w1$walking_speed) <- ds_label_walking_speed
walking_speed <- COURAGE_ds_fin_w1
save(walking_speed, file = "../RData/fin_w1/walking_speed.RData")

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$walking_speed <- car::recode(COURAGE_m_ds_fin_w1$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation
The measure is based in one trial.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
