---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q7009a_energy`
* Label: `Energy`
* Categories:
   + `1 = Not at all` 
   + `2 = A little` 
   + `3 = Moderately` 
   + `4 = Mostly`
   + `5 = Completely`
* Missings
   + `NA`

```{r assign Spain w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w1_energy','Courage.Courage_Spain_w1', variables=list('q7009a_energy'), missings = TRUE)
```

```{r local Spain w1, echo=F}
COURAGE_Spain_w1_energy <-opal.execute(o,'COURAGE_Spain_w1_energy')
vari <- COURAGE_Spain_w1_energy$q7009a_energy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7009a_energy")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w1_energy, aes(x=factor(q7009a_energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 0` 
* `4 into 1` 
* `5 into 1`      
* `NA into 999`

```{r harmo Spain w1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_Spain_w1_energy$id)
COURAGE_ds_spain_w1$energy <- car::recode(COURAGE_Spain_w1_energy$q7009a_energy, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
COURAGE_ds_spain_w1$energy <- labelled(COURAGE_ds_spain_w1$energy, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w1, echo=F}
vari <- COURAGE_ds_spain_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w1, echo=F}
AfterH <- table(COURAGE_ds_spain_w1$energy)
X <- table(COURAGE_Spain_w1_energy$q7009a_energy)
BeforeH<- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(COURAGE_Spain_w1_energy$q7009a_energy)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```


```{r importOPAL Spain w1, echo=FALSE}
label(COURAGE_ds_spain_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'COURAGE_ds_spain_w1', COURAGE_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_ds_spain_w1', project='_Athlos_Harm_Dataset')
energy <- COURAGE_ds_spain_w1
save(energy, file = "../RData/spain_w1/energy.RData")

COURAGE_m_ds_spain_w1 <- COURAGE_ds_spain_w1
COURAGE_m_ds_spain_w1$energy <- car::recode(COURAGE_m_ds_spain_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w1', COURAGE_m_ds_spain_w1)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w1', project='_Athlos_Harm_Dataset')
```

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q7009a_energy_s1`
* Label: `Energy`
* Categories:
   + `1 = Not at all` 
   + `2 = A little` 
   + `3 = Moderately` 
   + `4 = Mostly`
   + `5 = Completely`
* Missings
   + `NA`

```{r assign Spain w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Spain_w2_energy','Courage.Courage_Spain_w2_1', variables=list('q7009a_energy_s1'), missings = TRUE)
```

```{r local Spain w2, echo=F}
COURAGE_Spain_w2_energy <- opal.execute(o,'COURAGE_Spain_w2_energy')
vari <- COURAGE_Spain_w2_energy$q7009a_energy_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7009a_energy_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Spain_w2_energy, aes(x=factor(q7009a_energy_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 0` 
* `4 into 1` 
* `5 into 1`      
* `NA into 999`

```{r harmo Spain w2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_Spain_w2_energy$id)
COURAGE_ds_spain_w2$energy <- car::recode(COURAGE_Spain_w2_energy$q7009a_energy_s1, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
COURAGE_ds_spain_w2$energy <- labelled(COURAGE_ds_spain_w2$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Spain w2, echo=F}
vari <- COURAGE_ds_spain_w2$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_spain_w2, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Spain w2, echo=F}
AfterH <- table(COURAGE_ds_spain_w2$energy)
X <- table(COURAGE_Spain_w2_energy$q7009a_energy_s1)
BeforeH<- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(COURAGE_Spain_w2_energy$q7009a_energy_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```

```{r importOPAL Spain w2, echo=FALSE}
label(COURAGE_ds_spain_w2$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'COURAGE_ds_spain_w2', COURAGE_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_ds_spain_w2', project='_Athlos_Harm_Dataset')
energy <- COURAGE_ds_spain_w2
save(energy, file = "../RData/spain_w2/energy.RData")

COURAGE_m_ds_spain_w2 <- COURAGE_ds_spain_w2
COURAGE_m_ds_spain_w2$energy <- car::recode(COURAGE_m_ds_spain_w2$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_spain_w2', COURAGE_m_ds_spain_w2)
#opal.symbol_import(o,'COURAGE_m_ds_spain_w2', project='_Athlos_Harm_Dataset')
```


## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q7009a_energy`
* Label: `Energy`
* Categories:
   + `1 = Not at all` 
   + `2 = A little` 
   + `3 = Moderately` 
   + `4 = Mostly`
   + `5 = Completely`
* Missings
   + `NA`

```{r assign Poland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Poland_w1_energy','Courage.Courage_Poland_w1', variables=list('q7009a_energy'), missings = TRUE)
```

```{r local Poland w1, echo=F}
COURAGE_Poland_w1_energy <- opal.execute(o,'COURAGE_Poland_w1_energy')
vari <- COURAGE_Poland_w1_energy$q7009a_energy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7009a_energy")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Poland_w1_energy, aes(x=factor(q7009a_energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 0` 
* `4 into 1` 
* `5 into 1`      
* `NA into 999`

```{r harmo Poland w1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_Poland_w1_energy$id)
COURAGE_ds_pol_w1$energy <- car::recode(COURAGE_Poland_w1_energy$q7009a_energy, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
COURAGE_ds_pol_w1$energy <- labelled(COURAGE_ds_pol_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w1, echo=F}
vari <- COURAGE_ds_pol_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w1, echo=F}
AfterH <- table(COURAGE_ds_pol_w1$energy)
X <- table(COURAGE_Poland_w1_energy$q7009a_energy)
BeforeH<- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(COURAGE_Poland_w1_energy$q7009a_energy)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```

```{r importOPAL Poland w1, echo=FALSE}
label(COURAGE_ds_pol_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'COURAGE_ds_pol_w1', COURAGE_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_ds_pol_w1', project='_Athlos_Harm_Dataset')
energy <- COURAGE_ds_pol_w1
save(energy, file = "../RData/pol_w1/energy.RData")

COURAGE_m_ds_pol_w1 <- COURAGE_ds_pol_w1
COURAGE_m_ds_pol_w1$energy <- car::recode(COURAGE_m_ds_pol_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w1', COURAGE_m_ds_pol_w1)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w1', project='_Athlos_Harm_Dataset')
```

### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q7009a_energy_s1`
* Label: `Energy`
* Categories:
   + `1 = Not at all` 
   + `2 = A little` 
   + `3 = Moderately` 
   + `4 = Mostly`
   + `5 = Completely`
* Missings
   + `NA`

```{r assign Poland w2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Poland_w2_energy','Courage.Courage_Poland_w2', variables=list('q7009a_energy_s1'), missings = TRUE)
```

```{r local Poland w2, echo=F}
COURAGE_Poland_w2_energy <- opal.execute(o,'COURAGE_Poland_w2_energy')
vari <- COURAGE_Poland_w2_energy$q7009a_energy_s1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7009a_energy_s1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Poland_w2_energy, aes(x=factor(q7009a_energy_s1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 0` 
* `4 into 1` 
* `5 into 1`      
* `NA into 999`

```{r harmo Poland w2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_Poland_w2_energy$id)
COURAGE_ds_pol_w2$energy <- car::recode(COURAGE_Poland_w2_energy$q7009a_energy_s1, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
COURAGE_ds_pol_w2$energy <- labelled(COURAGE_ds_pol_w2$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Poland w2, echo=F}
vari <- COURAGE_ds_pol_w2$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_pol_w2, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Poland w2, echo=F}
AfterH <- table(COURAGE_ds_pol_w2$energy)
X <- table(COURAGE_Poland_w2_energy$q7009a_energy_s1)
BeforeH<- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(COURAGE_Poland_w2_energy$q7009a_energy_s1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```

```{r importOPAL Poland w2, echo=FALSE}
label(COURAGE_ds_pol_w2$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'COURAGE_ds_pol_w2', COURAGE_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_ds_pol_w2', project='_Athlos_Harm_Dataset')
energy <- COURAGE_ds_pol_w2
save(energy, file = "../RData/pol_w2/energy.RData")

COURAGE_m_ds_pol_w2 <- COURAGE_ds_pol_w2
COURAGE_m_ds_pol_w2$energy <- car::recode(COURAGE_m_ds_pol_w2$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_pol_w2', COURAGE_m_ds_pol_w2)
#opal.symbol_import(o,'COURAGE_m_ds_pol_w2', project='_Athlos_Harm_Dataset')
```


## Finland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `q7009a_energy`
* Label: `Energy`
* Categories:
   + `1 = Not at all` 
   + `2 = A little` 
   + `3 = Moderately` 
   + `4 = Mostly`
   + `5 = Completely`
* Missings
   + `NA`

```{r assign Finland w1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_Finland_w1_energy','Courage.Courage_Finland_w1', variables=list('q7009a_energy'), missings = TRUE)
```

```{r local Finland w1, echo=F}
COURAGE_Finland_w1_energy <- opal.execute(o,'COURAGE_Finland_w1_energy')
vari <- COURAGE_Finland_w1_energy$q7009a_energy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7009a_energy")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(COURAGE_Finland_w1_energy, aes(x=factor(q7009a_energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 0` 
* `3 into 0` 
* `4 into 1` 
* `5 into 1`      
* `NA into 999`

```{r harmo Finland w1}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_Finland_w1_energy$id)
COURAGE_ds_fin_w1$energy <- car::recode(COURAGE_Finland_w1_energy$q7009a_energy, "1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
COURAGE_ds_fin_w1$energy <- labelled(COURAGE_ds_fin_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Finland w1, echo=F}
vari <- COURAGE_ds_fin_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(COURAGE_ds_fin_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Finland w1, echo=F}
AfterH <- table(COURAGE_ds_fin_w1$energy)
X <- table(COURAGE_Finland_w1_energy$q7009a_energy)
BeforeH<- c(sum(X[1:3]),sum(X[4:5]),sum(is.na(COURAGE_Finland_w1_energy$q7009a_energy)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->0","4,5->1","NA->999") 
kable(C)
```

```{r importOPAL Finland w1, echo=FALSE}
label(COURAGE_ds_fin_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'COURAGE_ds_fin_w1', COURAGE_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_ds_fin_w1', project='_Athlos_Harm_Dataset')
energy <- COURAGE_ds_fin_w1
save(energy, file = "../RData/fin_w1/energy.RData")

COURAGE_m_ds_fin_w1 <- COURAGE_ds_fin_w1
COURAGE_m_ds_fin_w1$energy <- car::recode(COURAGE_m_ds_fin_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'COURAGE_m_ds_fin_w1', COURAGE_m_ds_fin_w1)
#opal.symbol_import(o,'COURAGE_m_ds_fin_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation
In some of the studies, what is being measured is the lack of energy or presence of fatigue 
(e.g., as presence of depression), but this measure can be used for assessing if the participant 
experiences a high/low level of energy.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
