---
title: "Wealth"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `wealth`
* Variable label: `Total score based in all sources of income transformed into a comparable and normalized categoric variable.`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical ordinal`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | 1st quintile
2        | 2nd quintile
3        | 3rd quintile
4        | 4th quintile
5        | 5th quintile

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Comments: `Need to pay attention to specificities like: before/after taxes or contributions. People: HH income is prioritized. When not available individual/caregiver/informant/family income is caolected. Source: Pension/family/work/government/disablity/total. all sources are taken into account. For some studies, the maximum value can be compared (and crossed by sex and age to control biases) . Time-lapse: weekly, monthly, in the last 12 months. 'Many values are missing since not all respondents have all sources of income or, within the household there is not always more members, in these cases do not confuse missing data with missing values and mean a 0 should be added to the total sum in each case.`

```{r lab, echo=FALSE}
ds_label <- "Wealth"
ds_label_all <- "Total score based in all sources of income transformed into a comparable and normalized categoric variable"
```

# Data process

## Australia

### Wave 1 

#### Study-specific variable description



| **Name** | `TTLINCYR` |
|----------|------------|
| **Label** | `Total gross income` |
| **Table name** | `ALSA-Wave1` |
| **Categories** | `1 = Up to $5,000` |
| | `2 = $5,001-12,000` |
| | `3 = $12,001-20,000` |
| | `4 = $20,001-30,000` |
| | `5 = $30,001-40,000` |
| | `6 = $40,001-50,000` |
| | `7 = Over $50,000` |
| **Missings** | `9 = Missing` |
| **Description** |  |

    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave1',
                         variables=list('TTLINCYR'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local1, echo=F}
vari <- ALSA_wealth$TTLINCYR
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTLINCYR))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `9 into 999`
* `NA into 999`


**R script:**

```{r harmo1}
ALSA_wealth$TTLINCYR <- car::recode(ALSA_wealth$TTLINCYR, "1=5000; 2=8500; 3=16000; 4=25000; 5=35000; 6=45000; 7=50000; 9=NA")
qq <- quantile(ALSA_wealth$TTLINCYR, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w1 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w1$wealth <- car::recode(ALSA_wealth$TTLINCYR, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w1$wealth[is.na(ALSA_ds_w1$wealth)] <- 999
ALSA_ds_w1$wealth <- as.integer(ALSA_ds_w1$wealth)
ALSA_ds_w1$wealth <- labelled(ALSA_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ALSA_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation



```{r importOPAL1, echo=F}
#opal.assign.data(o, 'ALSA_ds_w1', ALSA_ds_w1)
#opal.symbol_import(o,'ALSA_ds_w1', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$wealth <- car::recode(ALSA_m_ds_w1$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w1', ALSA_m_ds_w1)
#opal.symbol_import(o,'ALSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

There is no variable.






### Wave 3 

#### Study-specific variable description



| **Name** | `TTINCYW3` |
|----------|------------|
| **Label** | `TOTAL INCOME PER ANNUM` |
| **Table name** | `ALSA-Wave3` |
| **Categories** | `1 = Up to 5,000 dollars pa` |
| | `2 = Between 5,000 & 8,500 dollars pa` |
| | `3 = Between 8,500 & 12,000 dollars pa` |
| | `4 = Between 12,000 & 15,000 dollars pa` |
| | `5 = Between 15,000 & 20,000 dollars pa` |
| | `6 = Between 20,001 & 30,000 dollars pa` |
| | `7 = Between 30,000 & 40,000 dollars pa` |
| | `8 = Between 40,000 & 50,000 dollars pa` |
| | `9 = More than 50,000 pa` |
| **Missings** | `99 = Missing` |
| **Description** |  |
    
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave3',
                         variables=list('TTINCYW3'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local3, echo=F}
vari <- ALSA_wealth$TTINCYW3
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTINCYW3))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `99 into 999`
* `NA into 999`

**R script:**

```{r harmo3}
ALSA_wealth$TTINCYW3 <- car::recode(ALSA_wealth$TTINCYW3, "1=5000; 2=6750; 3=10250; 4=13500; 5=17500; 6=25000; 7=35000; 8=4500; 9=50000; 9=NA")
qq <- quantile(ALSA_wealth$TTINCYW3, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w3 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w3$wealth <- car::recode(ALSA_wealth$TTINCYW3, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w3$wealth[is.na(ALSA_ds_w3$wealth)] <- 999
ALSA_ds_w3$wealth <- as.integer(ALSA_ds_w3$wealth)
ALSA_ds_w3$wealth <- labelled(ALSA_ds_w3$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ALSA_ds_w3$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation




```{r importOPAL3, echo=F}

#opal.assign.data(o, 'ALSA_ds_w3', ALSA_ds_w3)
#opal.symbol_import(o,'ALSA_ds_w3', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$wealth <- car::recode(ALSA_m_ds_w3$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w3', ALSA_m_ds_w3)
#opal.symbol_import(o,'ALSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

There is no variable.






### Wave 5 

There is no variable.




### Wave 6 

#### Study-specific variable description



| **Name** | `TTINCYW6` |
|----------|------------|
| **Label** | `gross income` |
| **Table name** | `ALSA-Wave6 ` |
| **Missings** | `99999999 = Missing` |
| **Description** |  |
    
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave6',
                         variables=list('TTINCYW6'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local6, echo=F}
vari <- ALSA_wealth$TTINCYW6
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTINCYW6))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `NA into 999`

**R script:**

```{r harmo6}
ALSA_wealth$TTINCYW6 <- car::recode(ALSA_wealth$TTINCYW6, "'Up to $96            Up to $5,000'=5000 ; '$97-$230             $5001-$12,000'=8500 ; '$231-$385           $12,001- $20,000'=16000; '$386-$577           $20,001-$30,000'=25000; '$578-$769           $30,001-$40,000'=35000; '$770-$961           $40,001-$50,000'=45000; 'Above $961         More than $50,000'=50000; 'Per Week            Per Year'=NA")
qq <- quantile(ALSA_wealth$TTINCYW6, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w6 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w6$wealth <- car::recode(ALSA_wealth$TTINCYW6, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w6$wealth[is.na(ALSA_ds_w6$wealth)] <- 999
ALSA_ds_w6$wealth <- as.integer(ALSA_ds_w6$wealth)
ALSA_ds_w6$wealth <- labelled(ALSA_ds_w6$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vari <- ALSA_ds_w6$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation






```{r importOPAL6, echo=F}

#opal.assign.data(o, 'ALSA_ds_w6', ALSA_ds_w6)
#opal.symbol_import(o,'ALSA_ds_w6', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$wealth <- car::recode(ALSA_m_ds_w6$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w6', ALSA_m_ds_w6)
#opal.symbol_import(o,'ALSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** | `ttincyw7` |
|----------|------------|
| **Label** | `gross income` |
| **Table name** | `ALSA-Wave7` |
| **Categories** | `1 = Up to $5,000 Per Year` |
| | `2 = $5,001 -$12,000` |
| | `3 = $12,001 -$20,000` |
| | `4 = $21,001- $30,000` |
| | `5 = $31,001- $40,000` |
| | `6 = $40,001-$50,000` |
| | `7 = More than $50,000` |
| **Missings** | `0 = Not Answered` |
| **Description** |  |
    
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave7',
                         variables=list('ttincyw7'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local7, echo=F}
vari <- ALSA_wealth$ttincyw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(ttincyw7))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo7}
ALSA_wealth$ttincyw7_2 <- car::recode(ALSA_wealth$ttincyw7, "0=NA; 1=5000; 2=8500; 3=16000; 4=25000; 5=35000; 6=45000; 7=50000")
qq <- quantile(ALSA_wealth$ttincyw7_2, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w7 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w7$wealth <- car::recode(ALSA_wealth$ttincyw7_2, "1:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w7$wealth[is.na(ALSA_ds_w7$wealth)] <- car::recode(ALSA_wealth$ttincyw7[is.na(ALSA_ds_w7$wealth)], "0=995; NA=999")
ALSA_ds_w7$wealth <- as.integer(ALSA_ds_w7$wealth)
ALSA_ds_w7$wealth <- labelled(ALSA_ds_w7$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vari <- ALSA_ds_w7$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation


```{r importOPAL7, echo=F}

#opal.assign.data(o, 'ALSA_ds_w7', ALSA_ds_w7)
#opal.symbol_import(o,'ALSA_ds_w7', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$wealth <- car::recode(ALSA_m_ds_w7$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w7', ALSA_m_ds_w7)
#opal.symbol_import(o,'ALSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```






### Wave 8 

There is no variable.




### Wave 9 

#### Study-specific variable description



| **Name** | `TTINCYW9` |
|----------|------------|
| **Label** | `total income` |
| **Table name** |`ALSA-Wave9`|
| **Categories** | `3 = $2000 or more per week ($104,000 or more per year)` |
| | `4 = $1600 - $1999 per week ($83,200 - $103,999 per year)` |
| | `5 = $1000 - $1599 per week ($52,000 - $83,199 per year)` |
| | `6 = $600 - $999 per week ($32,000 - $51,999 per year)` |
| | `7 = $250 - $599 per week ($13,000 - $31,199 per year)` |
| | `8 = Up to $249 per week (Up to $12,999 per year)` |
| **Missings** | `0 = Not Answered` |
| | `1 = Not stated` |
| | `2 = Unknown` |
| **Description** |  |  
    
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave9',
                         variables=list('TTINCYW9'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local9, echo=F}
vari <- ALSA_wealth$TTINCYW9
kable(Categorical_summary(vari, missing_values = c(0,1,2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(0,1,2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0,1,2))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTINCYW9))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `0 into 995`
* `1 into 997`
* `2 into 998`
* `NA into 999`

**R script:**

```{r harmo9}
ALSA_wealth$TTINCYW9_2 <- car::recode(ALSA_wealth$TTINCYW9, "0=NA; 1=NA; 2=NA; 3=104000; 4=93599.5; 5=67599.5; 6=41999.5; 7=22099.5; 8=12999")
qq <- quantile(ALSA_wealth$TTINCYW9_2, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w9 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w9$wealth <- car::recode(ALSA_wealth$TTINCYW9_2, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w9$wealth[is.na(ALSA_ds_w9$wealth)] <- car::recode(ALSA_wealth$TTINCYW9[is.na(ALSA_ds_w9$wealth)], "0=995; 1=997; 2=998; NA=999")
ALSA_ds_w9$wealth <- as.integer(ALSA_ds_w9$wealth)
ALSA_ds_w9$wealth <- labelled(ALSA_ds_w9$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript9, echo=F}
vari <- ALSA_ds_w9$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation





```{r importOPAL9, echo=F}

#opal.assign.data(o, 'ALSA_ds_w9', ALSA_ds_w9)
#opal.symbol_import(o,'ALSA_ds_w9', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$wealth <- car::recode(ALSA_m_ds_w9$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w9', ALSA_m_ds_w9)
#opal.symbol_import(o,'ALSA_m_ds_w9', project='_Athlos_Harm_Dataset')
```






### Wave 10 

There is no variable. 





### Wave 11 

#### Study-specific variable description



| **Name** | `TTINCYW11` |
|----------|------------|
| **Label** | `total income` |
| **Table name** | `ALSA-Wave11` |
| **Categories** | `1 = Up to $249 per week (Up to $12,999 per year)` |
| | `2 = $250 - $599 per week ($13,000 - $31,199 per year)` |
| | `3 = $600 - $999 per week ($32,000 - $51,999 per year)` |
| | `4 = $1000 - $1599 per week ($52,000 - $83,199 per year)` |
| | `5 = $1600 - $1999 per week ($83,200 - $103,999 per year)` |
| | `6 = $2000 or more per week ($104,000 or more per year)` |
| **Missings** | `7 = Unknown` |
| | `8 = Not stated` |
| **Description** |  |
    
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave11',
                         variables=list('TTINCYW11'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local11, echo=F}
vari <- ALSA_wealth$TTINCYW11
kable(Categorical_summary(vari, missing_values = c(7,8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(7,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(7,8))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTINCYW11))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `7 into 998`
* `8 into 997`
* `NA into 999`

**R script:**

```{r harmo11}
ALSA_wealth$TTINCYW11_2 <- car::recode(ALSA_wealth$TTINCYW11, "1=12999; 2=22099.5; 3=41999.5; 4=67999.5; 5=93599.5; 6=104000; 7=NA; 8=NA")
qq <- quantile(ALSA_wealth$TTINCYW11_2, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w11 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w11$wealth <- car::recode(ALSA_wealth$TTINCYW11_2, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w11$wealth[is.na(ALSA_ds_w11$wealth)] <- car::recode(ALSA_wealth$TTINCYW11[is.na(ALSA_ds_w11$wealth)], "7=998; 8=997; NA=999")
ALSA_ds_w11$wealth <- as.integer(ALSA_ds_w11$wealth)
ALSA_ds_w11$wealth <- labelled(ALSA_ds_w11$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript11, echo=F}
vari <- ALSA_ds_w11$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL11, echo=F}
#opal.assign.data(o, 'ALSA_ds_w11', ALSA_ds_w11)
#opal.symbol_import(o,'ALSA_ds_w11', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$wealth <- car::recode(ALSA_m_ds_w11$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w11', ALSA_m_ds_w11)
#opal.symbol_import(o,'ALSA_m_ds_w11', project='_Athlos_Harm_Dataset')
```






### Wave 12 

#### Study-specific variable description



| **Name** | `TTINCYW12` |
|----------|------------|
| **Label** | `total income` |
| **Table name** | `ALSA-Wave12` |
| **Categories** | `1 = Up to $249 per week (Up to $12,999 per year)` |
| | `2 = $250 - $599 per week ($13,000 - $31,199 per year)` |
| | `3 = $600 - $999 per week ($32,000 - $51,999 per year)` |
| | `4 = $1000 - $1599 per week ($52,000 - $83,199 per year)` |
| | `5 = $1600 - $1999 per week ($83,200 - $103,999 per year)` |
| | `6 = $2000 or more per week ($104,000 or more per year)` |
| **Missings** | `7 = Unknown` |
| | `8 = Not stated` |
| **Description** |  |
    
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_wealth','ALSA.ALSA-Wave12',
                         variables=list('TTINCYW12'), missings = TRUE)
ALSA_wealth <- opal.execute(o,'ALSA_wealth')
```

```{r local12, echo=F}
vari <- ALSA_wealth$TTINCYW12
kable(Categorical_summary(vari, missing_values = c(7,8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(7,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(7,8))[2], caption = "Type of missing")
ggplot(ALSA_wealth, aes(x=factor(TTINCYW12))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study specific varibale calculate the mean value of each category and then, divide the population into 5 groups each containing 20$\%$ of the corresponding N and the missing values have to be recoded as follows: 

* `7 into 998`
* `8 into 997`
* `NA into 999`

**R script:**

```{r harmo12}
ALSA_wealth$TTINCYW12_2 <- car::recode(ALSA_wealth$TTINCYW12, "1=12999; 2=22099.5; 3=41999.5; 4=67999.5; 5=93599.5; 6=104000; 7=NA; 8=NA")
qq <- quantile(ALSA_wealth$TTINCYW12_2, probs = seq(0, 1, .2), na.rm = TRUE)

ALSA_ds_w12 <- tibble(id=ALSA_wealth$id)
ALSA_ds_w12$wealth <- car::recode(ALSA_wealth$TTINCYW12_2, "0:qq[2]=1; (qq[2]+1):qq[3]=2; (qq[3]+1):qq[4]=3; (qq[4]+1):qq[5]=4; (qq[5]+1):hi=5")
ALSA_ds_w12$wealth[is.na(ALSA_ds_w12$wealth)] <- car::recode(ALSA_wealth$TTINCYW12[is.na(ALSA_ds_w12$wealth)], "7=998; 8=997; NA=999")
ALSA_ds_w12$wealth <- as.integer(ALSA_ds_w12$wealth)
ALSA_ds_w12$wealth <- labelled(ALSA_ds_w12$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript12, echo=F}
vari <- ALSA_ds_w12$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation


```{r importOPAL12, echo=F}

#opal.assign.data(o, 'ALSA_ds_w12', ALSA_ds_w12)
#opal.symbol_import(o,'ALSA_ds_w12', project='_Athlos_Harm_Dataset')

ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$wealth <- car::recode(ALSA_m_ds_w12$wealth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ALSA_m_ds_w12', ALSA_m_ds_w12)
#opal.symbol_import(o,'ALSA_m_ds_w12', project='_Athlos_Harm_Dataset')
```





### Wave 13 

There is no variable. 


# Quality estimation
As a continuous variable is not available, calculation was done by using the mean value of each category and creating quintiles based on the 
household income of each participant that divides the 
population into 5 groups each containing 20% of the corresponding N.

This variable was created taking into account 
all sources of respondent's + spouse's income wags and salary before tax,; 
2) sperannuation; 3) income from your own business or partnership; 
4) income from interest dividends or rent; 5) workers compensation; 
6) whole household; 7) care'r pension; 8) disability spport pension; 
9) widowed person's allowence; 10) overseas pension; 11) repariation pension; repatriation TPI; 
13) other pension; 14) other).

```{r save, echo=FALSE}
wealth <- ALSA_ds_w1
save(wealth, file = "../RData/w1/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w3
save(wealth, file = "../RData/w3/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w6
save(wealth, file = "../RData/w6/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w7
save(wealth, file = "../RData/w7/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w9
save(wealth, file = "../RData/w9/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w11
save(wealth, file = "../RData/w11/wealth.RData")
rm(wealth)

wealth <- ALSA_ds_w12
save(wealth, file = "../RData/w12/wealth.RData")
rm(wealth)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

