---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```

<!-- ########################################################## --> 

# Data process

## Australia

### Wave 1

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',variables=list('SEX'), missings = TRUE)
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
```

```{r local1, echo=FALSE}
vari <- ALSA_w1_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w1_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_sex$id)
ALSA_ds_w1$sex <- car::recode(ALSA_w1_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w1$sex <- labelled(ALSA_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ALSA_ds_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(ALSA_w1_sex$SEX)[c(2,1)]
AfterH <- table(ALSA_ds_w1$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```

 
 

 




### Wave 2 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |

   
```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w2_id','ALSA.ALSA-Wave2',
                         variables=list('DATE'), missings = TRUE)

ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w2_id <- opal.execute(o,'ALSA_w2_id')

```

```{r local2, echo=FALSE}

Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w2_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w2_id)

vari <- ALSA_w2_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w2_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_sex$id)
ALSA_ds_w2$sex <- car::recode(ALSA_w2_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w2$sex <- labelled(ALSA_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ALSA_ds_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
id_w2 <- ALSA_ds_w2$id
seg <- ALSA_w2_sex[ALSA_w2_sex$id %in% id_w2, ]# individuos con seguimiento
BeforeH <- table(seg$SEX)[c(2,1)]

AfterH <- table(ALSA_ds_w2$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)

```

 
 

 





### Wave 3 

#### Study-specific variable description

 

| **Name** | `SEXW3`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave3`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_sex','ALSA.ALSA-Wave3', variables=list('SEXW3'), missings = TRUE)
```

```{r local3, echo=FALSE}
ALSA_w3_sex <- opal.execute(o,'ALSA_w3_sex')
vari <- ALSA_w3_sex$SEXW3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w3_sex, aes(x=factor(SEXW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_sex$id)
ALSA_ds_w3$sex <- car::recode(ALSA_w3_sex$SEXW3, "9=999; 2=0; NA=999")
ALSA_ds_w3$sex <- labelled(ALSA_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ALSA_ds_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(ALSA_w3_sex$SEXW3)[c(2,1)]
AfterH <- table(ALSA_ds_w3$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```

 
 

 




### Wave 4 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |

  
```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w4_id','ALSA.ALSA-Wave4',
                         variables=list('W4QUNO'), missings = TRUE)

```

```{r local4, echo=FALSE}
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w4_id <- opal.execute(o,'ALSA_w4_id')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w4_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w4_id)

vari <- ALSA_w4_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w1_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_sex$id)
ALSA_ds_w4$sex <- car::recode(ALSA_w4_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w4$sex <- labelled(ALSA_ds_w4$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ALSA_ds_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
BeforeH <- table(ALSA_w4_sex$SEX)[c(2,1)]
AfterH <- table(ALSA_ds_w4$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```

 
 

 





### Wave 5 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w5_id','ALSA.ALSA-Wave5',
                         variables=list('INTTYPW5'), missings = TRUE)
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w5_id <- opal.execute(o,'ALSA_w5_id')

```

```{r local5, echo=FALSE}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w5_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w5_id)

vari <- ALSA_w5_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w5_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_sex$id)
ALSA_ds_w5$sex <- car::recode(ALSA_w5_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w5$sex <- labelled(ALSA_ds_w5$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ALSA_ds_w5$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
id_w5 <- ALSA_ds_w5$id
seg <- ALSA_w5_sex[ALSA_w5_sex$id %in% id_w5, ]# individuos con seguimiento
BeforeH <- table(seg$SEX)[c(2,1)]


AfterH <- table(ALSA_ds_w5$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)

```

 
 

 





### Wave 6 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |



```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w6_id','ALSA.ALSA-Wave6',
                         variables=list('AGEW6'), missings = TRUE)
```

```{r local6, echo=FALSE}
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w6_id <- opal.execute(o,'ALSA_w6_id')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w6_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w6_id)

vari <- ALSA_w6_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w6_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_sex$id)
ALSA_ds_w6$sex <- car::recode(ALSA_w6_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w6$sex <- labelled(ALSA_ds_w6$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ALSA_ds_w6$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
BeforeH <- table(ALSA_w6_sex$SEX)[c(2,1)]
AfterH <- table(ALSA_ds_w6$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```

 
 

 




### Wave 7 

#### Study-specific variable description

 

| **Name** | `sex`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |

 
```{r assign7, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_sex','ALSA.ALSA-Wave7',
                         variables=list('sex'), missings = TRUE)
ALSA_w7_sex <- opal.execute(o,'ALSA_w7_sex')
```

```{r local7, echo=FALSE}
vari <- ALSA_w7_sex$sex
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w7_sex, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_sex$id)
ALSA_ds_w7$sex <- car::recode(ALSA_w7_sex$sex, "9=999; 2=0; NA=999")
ALSA_ds_w7$sex <- labelled(ALSA_ds_w7$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=FALSE}
vari <- ALSA_ds_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=FALSE}
BeforeH <- table(ALSA_w7_sex$sex)
BeforeH <- c( BeforeH[2], BeforeH[1], sum(is.na(ALSA_w7_sex$sex)))
AfterH <- table(ALSA_ds_w7$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```

 
 

 


### Wave 8 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign8, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w8_id','ALSA.ALSA-Wave8',
                         variables=list('Date'), missings = TRUE)
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w8_id <- opal.execute(o,'ALSA_w8_id')

```

```{r local8, echo=FALSE}

Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w8_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w8_id)

vari <- ALSA_w8_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w8_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo8, echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_sex$id)
ALSA_ds_w8$sex <- car::recode(ALSA_w8_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w8$sex <- labelled(ALSA_ds_w8$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8, echo=FALSE}
vari <- ALSA_ds_w8$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8, echo=FALSE}
id_w8 <- ALSA_ds_w8$id
seg <- ALSA_w8_sex[ALSA_w8_sex$id %in% id_w8, ]# individuos con seguimiento

BeforeH <- table(seg$SEX)[c(2,1)]
AfterH <- table(ALSA_ds_w8$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)

```

 
 

 




### Wave 9 

#### Study-specific variable description

 


| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |

   
```{r assign9, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w9_id','ALSA.ALSA-Wave9',
                         variables=list('sex'), missings = TRUE)
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w9_id <- opal.execute(o,'ALSA_w9_id')



Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w9_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w9_id)

```

```{r local9, echo=FALSE}
vari <- ALSA_w9_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w9_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("SEX") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo9, echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_sex$id)
ALSA_ds_w9$sex <- car::recode(ALSA_w9_sex$SEX, "9=999; 2=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript9, echo=FALSE}
vari <- ALSA_ds_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9, echo=FALSE}
id_w9 <- ALSA_ds_w9$id
seg <- ALSA_w9_sex[ALSA_w9_sex$id %in% id_w9, ]# individuos con seguimiento

BeforeH <- table(seg$SEX)[c(2,1)]
AfterH <- table(ALSA_ds_w9$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```

 
 

 





### Wave 10 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |

   
```{r assign10, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w10_id','ALSA.ALSA-Wave10',
                         variables=list('Date'), missings = TRUE)
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w10_id <- opal.execute(o,'ALSA_w10_id')
```

```{r local10, echo=FALSE}


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w10_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w10_id)

vari <-  ALSA_w10_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w10_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo10, echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_sex$id)
ALSA_ds_w10$sex <- car::recode(ALSA_w10_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w10$sex <- labelled(ALSA_ds_w10$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10, echo=FALSE}
vari <- ALSA_ds_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10, echo=FALSE}
id_w10 <- ALSA_ds_w10$id
seg <- ALSA_w10_sex[ALSA_w10_sex$id %in% id_w10, ]# individuos con seguimiento
BeforeH <- table(seg$SEX)
BeforeH <- c(BeforeH[2], BeforeH[1], sum(is.na(seg$SEX)))
AfterH <- table(ALSA_ds_w10$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)

```

 
 

 



### Wave 11 

#### Study-specific variable description

 

| **Name** | `SEXW11`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |

  
```{r assign11, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_sex','ALSA.ALSA-Wave11',
                         variables=list('SEXW11'), missings = TRUE)
```

```{r local11, echo=FALSE}
ALSA_w11_sex <- opal.execute(o,'ALSA_w11_sex')
vari <- ALSA_w11_sex$SEXW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w11_sex, aes(x=factor(SEXW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo11, echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_sex$id)
ALSA_ds_w11$sex <- car::recode(ALSA_w11_sex$SEXW11, "2=0; NA=999")
ALSA_ds_w11$sex <- labelled(ALSA_ds_w11$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11, echo=FALSE}
vari <- ALSA_ds_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11, echo=FALSE}
BeforeH <- table(ALSA_w11_sex$SEXW11)
BeforeH <- c(BeforeH[2], BeforeH[1], sum(is.na(ALSA_w11_sex$SEXW11)))
AfterH <- table(ALSA_ds_w11$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```

 
 

 




### Wave 12 

#### Study-specific variable description

 

| **Name** | `SEXW12`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave12`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign12, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_sex','ALSA.ALSA-Wave12',
                         variables=list('SEXW12'), missings = TRUE)
```

```{r local12, echo=FALSE}
ALSA_w12_sex <- opal.execute(o,'ALSA_w12_sex')
vari <- ALSA_w12_sex$SEXW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w12_sex, aes(x=factor(SEXW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo12, echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_sex$id)
ALSA_ds_w12$sex <- car::recode(ALSA_w12_sex$SEXW12, "2=0; NA=999")
ALSA_ds_w12$sex <- labelled(ALSA_ds_w12$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript12, echo=FALSE}
vari <- ALSA_ds_w12$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w12, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12, echo=FALSE}
BeforeH <- table(ALSA_w12_sex$SEXW12)
BeforeH <- c(BeforeH[2], BeforeH[1], sum(is.na(ALSA_w12_sex$SEXW12)))
AfterH <- table(ALSA_ds_w12$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```

 
 

 





### Wave 13 

#### Study-specific variable description

 

| **Name** | `SEX`|
|-|-|
| **Label** | `Sex`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign13, echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_sex','ALSA.ALSA-Wave1',
                         variables=list('SEX'), missings = TRUE)
opal.assign.table.tibble(o, 'ALSA_w13_id','ALSA.ALSA-Wave13',
                         variables=list('proxy'), missings = TRUE)

```

```{r local13, echo=FALSE}
ALSA_w1_sex <- opal.execute(o,'ALSA_w1_sex')
ALSA_w13_id <- opal.execute(o,'ALSA_w13_id')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], SEX=as.numeric(new_2[,2]))
  new_22
}

ALSA_w13_sex <- Add_indiv(old = ALSA_w1_sex, new = ALSA_w13_id)

vari <- ALSA_w13_sex$SEX
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w13_sex, aes(x=factor(SEX))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 Male into 1`
* `2 Female into 0`
* `NA into 999`

**R script:**

```{r harmo13, echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_sex$id)
ALSA_ds_w13$sex <- car::recode(ALSA_w13_sex$SEX, "9=999; 2=0; NA=999")
ALSA_ds_w13$sex <- labelled(ALSA_ds_w13$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript13, echo=FALSE}
vari <- ALSA_ds_w13$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w13, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation13, echo=FALSE}
BeforeH <- c(table(ALSA_w13_sex$SEX)[c(2,1)], sum(is.na(ALSA_w13_sex$SEX)))
AfterH <- table(ALSA_ds_w13$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```







## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

detect_ch <- function(m.hds,vbl_name,opt ="frq"){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  dbb$val0 <- sapply(dbb$id,function(ind) TRUE %in% (dbb[dbb$id==ind,2:14]==0))
  dbb$val1 <- sapply(dbb$id,function(ind) TRUE %in% (dbb[dbb$id==ind,2:14]==1))
  dbb$check <- ((dbb$val0==dbb$val1) & (dbb$val0==TRUE))
  if(opt=="frq"){
    return(frq(dbb$check))
  }
  if(opt=="ind"){
    return(dbb[dbb$check==T,])
  }
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  
  
  dch <- detect_ch(lmlist[[2]],vbl_name=hd_vbl,"frq")
  print(kable(dch,align = 'c', caption = 'There are 4 individuals with sex changed across waves'))
  dch <- detect_ch(lmlist[[2]],vbl_name=hd_vbl,"ind")
  print(kable(dch, align = 'c', caption = 'The trajectories of these individuals'))
  
}
```


**R script:**

```{r}
  # Corrections

ALSA_ds_w7$sex[ALSA_ds_w7$id=="12022"] <- 0
ALSA_ds_w7$sex[ALSA_ds_w7$id=="16461"] <- 0
ALSA_ds_w3$sex[ALSA_ds_w3$id=="4942"] <- 0
ALSA_ds_w11$sex[ALSA_ds_w11$id=="8131"] <- 1

```

``` {r save, echo=F}


# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

lmlist <- labelling(lmlist[[1]],lmlist[[2]])
# Saving tibbles
savingRD(lmlist[[1]],vbl_name=hd_vbl)


```








# Quality estimation

As shown above, four individuals are manually corrected after checking their trajectories are paradoxical.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```