---
title: "Marital Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/marital_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/marital_statusDS.R')
```


<!-- ########################################################## --> 

# Data process

## Australia
### Wave 1 

#### Study-specific variable description

 

| **Name** | `MARITST`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave1`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_ms','ALSA.ALSA-Wave1',
                         variables=list('MARITST'), missings = TRUE)
```

```{r local1,  echo=FALSE}
ALSA_w1_ms <- opal.execute(o,'ALSA_w1_ms')
vari <- ALSA_w1_ms$MARITST
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w1_ms, aes(x=factor(MARITST))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode 9 "Missing" into 999`
* `recode NA into 999`


**R script:**

```{r harmo1,   echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_ms$id)
ALSA_ds_w1$marital_status <- car::recode(ALSA_w1_ms$MARITST, " 1=2; 4=3; 5=4; 6=1; 9=999; NA=999")
ALSA_ds_w1$marital_status <- labelled(ALSA_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- ALSA_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(ALSA_w1_ms$MARITST)
BeforeH <- c(BeforeH[6], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(3, 4)]), BeforeH[5], BeforeH[7]) 
AfterH <- table(ALSA_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "(9,NA)->999")
kable(C)
```

 
 

 


### Wave 2 

#### Study-specific variable description

 

| **Name** | `Q3`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave2`|
| **Categories** |`1 = No (still married, defacto)`<br/>`2 = No (still single, separated)`<br/>`3 = Yes, married`<br/>`4 = Yes, defacto`<br/>`5 = Yes, separated`<br/>`6 = Yes, divorced`<br/>`7 = Yes, widowed`|
| **Description** |  |


```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_ms','ALSA.ALSA-Wave2',
                         variables=list('Q3'), missings = TRUE)
```

```{r local2,  echo=FALSE}
ALSA_w2_ms <- opal.execute(o,'ALSA_w2_ms')
vari <- ALSA_w2_ms$Q3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w2_ms, aes(x=factor(Q3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "No (still married, defacto)" into 2`
* `recode 2 "No (still single, separated)" into 1`
* `recode 3 "Yes, married" into 2`
* `recode 4 "Yes, defacto" into 2`
* `recode 5 "Yes, separated" into 3`
* `recode 6 "Yes, divorced" into 3`
* `recode 7 "Yes, widowed" into 4`
* `recode NA into 999`


**R script:**

```{r harmo2,   echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_ms$id)
ALSA_ds_w2$marital_status <- car::recode(ALSA_w2_ms$Q3, " 1=2; 2=1; 3=2; 4=2; 5=3; 6=3; 7=4; NA=999")
ALSA_ds_w2$marital_status <- labelled(ALSA_ds_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- ALSA_ds_w2$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(ALSA_w2_ms$Q3)
BeforeH <- c(BeforeH[2], sum(BeforeH[c(1, 3)]),BeforeH[4], BeforeH[5]) 
AfterH <- table(ALSA_ds_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->1","(1,3,4)->2", "(5,6)->3", "7->4")
kable(C)
```

 
 

 


### Wave 3 

#### Study-specific variable description

 

| **Name** | `MARITW3`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave3`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`9 = Missing`|
| **Description** |  |


```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_ms','ALSA.ALSA-Wave3',
                         variables=list('MARITW3'), missings = TRUE)
```

```{r local3,  echo=FALSE}
ALSA_w3_ms <- opal.execute(o,'ALSA_w3_ms')
vari <- ALSA_w3_ms$MARITW3
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")

ggplot(ALSA_w3_ms, aes(x=factor(MARITW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode 9,NA into 999`

**R script:**

```{r harmo3,   echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_ms$id)
ALSA_ds_w3$marital_status <- car::recode(ALSA_w3_ms$MARITW3, " 1=2; 4=3; 5=4; 6=1; 9=999; NA=999")
ALSA_ds_w3$marital_status <- labelled(ALSA_ds_w3$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- ALSA_ds_w3$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w3, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- table(ALSA_w3_ms$MARITW3)
BeforeH <- c(BeforeH[6], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(3, 4)]), BeforeH[5], sum(BeforeH[7],sum(is.na(ALSA_w3_ms$MARITW3)))) 
AfterH <- table(ALSA_ds_w3$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "(9,NA)->999")
kable(C)
```

 
 

 



### Wave 4 

#### Study-specific variable description

 

| **Name** | `MARITW4`|
|-|-|
| **Label** | `MARITAL STATUS`|
| **Table name** |`ALSA-Wave4`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Description** |  |


```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_ms','ALSA.ALSA-Wave4',
                         variables=list('MARITW4'), missings = TRUE)
```

```{r local4,  echo=FALSE}
ALSA_w4_ms <- opal.execute(o,'ALSA_w4_ms')
vari <- ALSA_w4_ms$MARITW4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w4_ms, aes(x=factor(MARITW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo4,   echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_ms$id)
ALSA_ds_w4$marital_status <- car::recode(ALSA_w4_ms$MARITW4, " 1=2; 4=3; 5=4; 6=1; 9=999; NA=999")
ALSA_ds_w4$marital_status <- labelled(ALSA_ds_w4$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- ALSA_ds_w4$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w4, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4,  echo=FALSE}
BeforeH <- table(ALSA_w4_ms$MARITW4)
BeforeH <- c(BeforeH[6], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(3, 4)]), BeforeH[5]) 
AfterH <- table(ALSA_ds_w4$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4")
kable(C)
```

 
 

 






### Wave 5 

#### Study-specific variable description

 

| **Name** | `MARITW5`|
|-|-|
| **Label** | `Q3 COULD YOU PLEASE TELL ME YOUR CURREN`|
| **Table name** |`ALSA-Wave5`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`<br/>`7 = Refused (Do not read)`<br/>`8 = Other`|
| **Description** |  |


```{r assign5,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_ms','ALSA.ALSA-Wave5',
                         variables=list('MARITW5'), missings = TRUE)
```

```{r local5,  echo=FALSE}
ALSA_w5_ms <- opal.execute(o,'ALSA_w5_ms')
vari <- ALSA_w5_ms$MARITW5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w5_ms, aes(x=factor(MARITW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode 7 "Refused (Do not read)" into 997`
* `recode 8 "Other" into 999`
* `recode NA into 999`


**R script:**

```{r harmo5,   echo=TRUE}
ALSA_ds_w5 <- tibble(id=ALSA_w5_ms$id)
ALSA_ds_w5$marital_status <- car::recode(ALSA_w5_ms$MARITW5, " 1=2; 4=3; 5=4; 6=1; 7=997; 8=999; 9=999; NA=999")
ALSA_ds_w5$marital_status <- labelled(ALSA_ds_w5$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5,  echo=FALSE}
vari <- ALSA_ds_w5$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w5, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5,  echo=FALSE}
BeforeH <- table(ALSA_w5_ms$MARITW5)
BeforeH <- c(BeforeH[6], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(3, 4)]), BeforeH[5], BeforeH[7]) 
AfterH <- table(ALSA_ds_w5$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "7->997")
kable(C)
```

 
 

 




### Wave 6 

#### Study-specific variable description

 

| **Name** | `MARITW6`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave6`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Description** |`0 = no answer`|


```{r assign6,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_ms','ALSA.ALSA-Wave6',
                         variables=list('MARITW6'), missings = TRUE)
```

```{r local6,  echo=FALSE}
ALSA_w6_ms <- opal.execute(o,'ALSA_w6_ms')
vari <- ALSA_w6_ms$MARITW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")

ggplot(ALSA_w6_ms, aes(x=factor(MARITW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 0 "no answer" into 995`
* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo6,   echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_ms$id)
ALSA_ds_w6$marital_status <- car::recode(ALSA_w6_ms$MARITW6, " 1=2; 4=3; 5=4; 6=1; 0=995; NA=999")
ALSA_ds_w6$marital_status <- labelled(ALSA_ds_w6$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6,  echo=FALSE}
vari <- ALSA_ds_w6$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w6, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6,  echo=FALSE}
BeforeH <- table(ALSA_w6_ms$MARITW6)
BeforeH <- c( BeforeH[7], sum(BeforeH[c(2, 3)]), sum(BeforeH[c(4, 5)]), BeforeH[6], BeforeH[1] ) 
AfterH <- table(ALSA_ds_w6$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "0->995")
kable(C)
```

 
 

 





### Wave 7 

#### Study-specific variable description

 

| **Name** | `maritw7`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave7`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`0 = no answer`|
| **Description** |  |


```{r assign7,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_ms','ALSA.ALSA-Wave7',
                         variables=list('maritw7'), missings = TRUE)
```

```{r local7,  echo=FALSE}
ALSA_w7_ms <- opal.execute(o,'ALSA_w7_ms')
vari <- ALSA_w7_ms$maritw7
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")

ggplot(ALSA_w7_ms, aes(x=factor(maritw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 0 "no answer" into 995`
* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo7,   echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_ms$id)
ALSA_ds_w7$marital_status <- car::recode(ALSA_w7_ms$maritw7, " 1=2; 4=3; 5=4; 6=1; 0=995; NA=999")
ALSA_ds_w7$marital_status <- labelled(ALSA_ds_w7$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7,  echo=FALSE}
vari <- ALSA_ds_w7$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w7, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7,  echo=FALSE}
BeforeH <- table(ALSA_w7_ms$maritw7)
BeforeH <- c( BeforeH[6], BeforeH[2], sum(BeforeH[c(3, 4)]), BeforeH[5], BeforeH[1],sum(is.na(ALSA_w7_ms$maritw7))) 

AfterH <- table(ALSA_ds_w7$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "0->995","NA->999")
kable(C)

```

 
 

 



### Wave 8 

#### Study-specific variable description

 

| **Name** | `maritw8`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave8`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`0 = Not Answered`|
| **Description** |  |


```{r assign8,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w8_ms','ALSA.ALSA-Wave8',
                         variables=list('maritw8'), missings = TRUE)
```

```{r local8,  echo=FALSE}
ALSA_w8_ms <- opal.execute(o,'ALSA_w8_ms')
vari <- ALSA_w8_ms$maritw8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")

ggplot(ALSA_w8_ms, aes(x=factor(maritw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 0 "no answer" into 995`
* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo8,   echo=TRUE}
ALSA_ds_w8 <- tibble(id=ALSA_w8_ms$id)
ALSA_ds_w8$marital_status <- car::recode(ALSA_w8_ms$maritw8, " 1=2; 4=3; 5=4; 6=1; 0=995; NA=999")
ALSA_ds_w8$marital_status <- labelled(ALSA_ds_w8$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript8,  echo=FALSE}
vari <- ALSA_ds_w8$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w8, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation8,  echo=FALSE}
BeforeH <- table(ALSA_w8_ms$maritw8)
BeforeH <- c( BeforeH[6], BeforeH[2], sum(BeforeH[c(3, 4)]), BeforeH[5], BeforeH[1] ) 
AfterH <- table(ALSA_ds_w8$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "0->995")
kable(C)
```

 
 

 



### Wave 9 

#### Study-specific variable description

 

| **Name** | `MARITW9`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave9`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`0 = Not Answered`|
| **Description** |  |


```{r assign9,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_ms','ALSA.ALSA-Wave9',
                         variables=list('MARITW9'), missings = TRUE)
```

```{r local9,  echo=FALSE}
ALSA_w9_ms <- opal.execute(o,'ALSA_w9_ms')
vari <- ALSA_w9_ms$MARITW9
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")

ggplot(ALSA_w9_ms, aes(x=factor(MARITW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 0 "no answer" into 995`
* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo9,   echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_ms$id)
ALSA_ds_w9$marital_status <- car::recode(ALSA_w9_ms$MARITW9, " 1=2; 4=3; 5=4; 6=1; 0=995; NA=999")
ALSA_ds_w9$marital_status <- labelled(ALSA_ds_w9$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript9,  echo=FALSE}
vari <- ALSA_ds_w9$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w9, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9,  echo=FALSE}
BeforeH <- table(ALSA_w9_ms$MARITW9)
BeforeH <- c( BeforeH[6], sum(BeforeH[c(2, 3)]), BeforeH[4], BeforeH[5], BeforeH[1], sum(is.na(ALSA_w9_ms$MARITW9)) )
AfterH <- table(ALSA_ds_w9$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "0->995","NA->999")
kable(C)
```

 
 

 


### Wave 10 

#### Study-specific variable description

 

| **Name** | `maritw10`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave10`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Missings** |`99 = Not Answered`|
| **Description** |  |


```{r assign10,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_ms','ALSA.ALSA-Wave10',
                         variables=list('maritw10'), missings = TRUE)
```

```{r local10,  echo=FALSE}
ALSA_w10_ms <- opal.execute(o,'ALSA_w10_ms')
vari <- ALSA_w10_ms$maritw10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")

ggplot(ALSA_w10_ms, aes(x=factor(maritw10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode 99 "no answer" into 995`
* `recode NA into 999`

**R script:**

```{r harmo10,   echo=TRUE}
ALSA_ds_w10 <- tibble(id=ALSA_w10_ms$id)
ALSA_ds_w10$marital_status <- car::recode(ALSA_w10_ms$maritw10, " 1=2; 4=3; 5=4; 6=1; 99=995; NA=999")
ALSA_ds_w10$marital_status <- labelled(ALSA_ds_w10$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript10,  echo=FALSE}
vari <- ALSA_ds_w10$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w10, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10,  echo=FALSE}
BeforeH <- table(ALSA_w10_ms$maritw10)
BeforeH <- c( BeforeH[5], sum(BeforeH[c(1,2)]), BeforeH[3], BeforeH[4], BeforeH[6] ) 
AfterH <- table(ALSA_ds_w10$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4", "99->995")
kable(C)
```

 
 

 


### Wave 11 

#### Study-specific variable description

 

| **Name** | `MARITW11`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave11`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Description** |  |


```{r assign11,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_ms','ALSA.ALSA-Wave11',
                         variables=list('MARITW11'), missings = TRUE)
```

```{r local11,  echo=FALSE}
ALSA_w11_ms <- opal.execute(o,'ALSA_w11_ms')
vari <- ALSA_w11_ms$MARITW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w11_ms, aes(x=factor(MARITW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo11,   echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_ms$id)
ALSA_ds_w11$marital_status <- car::recode(ALSA_w11_ms$MARITW11, " 1=2; 4=3; 5=4; 6=1; NA=999")
ALSA_ds_w11$marital_status <- labelled(ALSA_ds_w11$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript11,  echo=FALSE}
vari <- ALSA_ds_w11$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w11, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11,  echo=FALSE}
BeforeH <- table(ALSA_w11_ms$MARITW11)
BeforeH <- c( BeforeH[5], sum(BeforeH[c(1,2)]), BeforeH[3], BeforeH[4]) 
AfterH <- table(ALSA_ds_w11$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4")
kable(C)
```

 
 

 


### Wave 12 

#### Study-specific variable description

 

| **Name** | `MARITW12`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave12`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Description** |  |


```{r assign12,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_ms','ALSA.ALSA-Wave12',
                         variables=list('MARITW12'), missings = TRUE)
```

```{r local12,  echo=FALSE}
ALSA_w12_ms <- opal.execute(o,'ALSA_w12_ms')
vari <- ALSA_w12_ms$MARITW12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w12_ms, aes(x=factor(MARITW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo12,   echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_ms$id)
ALSA_ds_w12$marital_status <- car::recode(ALSA_w12_ms$MARITW12, " 1=2; 4=3; 5=4; 6=1; NA=999")
ALSA_ds_w12$marital_status <- labelled(ALSA_ds_w12$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript12,  echo=FALSE}
vari <- ALSA_ds_w12$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w12, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12,  echo=FALSE}
BeforeH <- table(ALSA_w12_ms$MARITW12)
BeforeH <- c( BeforeH[4], BeforeH[1], BeforeH[2], BeforeH[3]) 
AfterH <- table(ALSA_ds_w12$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4")
kable(C)
```

 
 

 


### Wave 13 

#### Study-specific variable description

 

| **Name** | `MARITW13`|
|-|-|
| **Label** | `Marital status`|
| **Table name** |`ALSA-Wave13`|
| **Categories** |`1 = Married`<br/>`2 = De facto`<br/>`3 = Separated`<br/>`4 = Divorced`<br/>`5 = Widowed`<br/>`6 = Never married`|
| **Description** |  |


```{r assign13,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_ms','ALSA.ALSA-Wave13',
                         variables=list('MARITW13'), missings = TRUE)
```

```{r local13,  echo=FALSE}
ALSA_w13_ms <- opal.execute(o,'ALSA_w13_ms')
vari <- ALSA_w13_ms$MARITW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")

ggplot(ALSA_w13_ms, aes(x=factor(MARITW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `keep "De facto" into 2`
* `keep "Separated" into 3`
* `recode 4 "Divorced" into 3`
* `recode 5 "Widowed" into 4`
* `recode 6 "Never married" into 1`
* `recode NA into 999`

**R script:**

```{r harmo13,   echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_ms$id)
ALSA_ds_w13$marital_status <- car::recode(ALSA_w13_ms$MARITW13, " 1=2; 4=3; 5=4; 6=1; NA=999")
ALSA_ds_w13$marital_status <- labelled(ALSA_ds_w13$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript13,  echo=FALSE}
vari <- ALSA_ds_w13$marital_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ALSA_ds_w13, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation13,  echo=FALSE}
BeforeH <- table(ALSA_w13_ms$MARITW13)
BeforeH <- c( BeforeH[4], BeforeH[1], BeforeH[2], BeforeH[3]) 
AfterH <- table(ALSA_ds_w13$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","(1,2)->2", "(3,4)->3", "5->4")
kable(C)
```

 
 


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:4])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[15,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




 

# Quality estimation

No comments




```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```