---
title: "Place of residence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/resid_placeDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/resid_placeDS.R')
```

# Data process

## Australia



```{r assign, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('BIRTHDAT'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')

opal.assign.table.tibble(o, 'ALSA_w2','ALSA.ALSA-Wave2',variables=list('DATE'), missings = T)
ALSA_w2 <- opal.execute(o,'ALSA_w2')

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('SEXW3'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

opal.assign.table.tibble(o, 'ALSA_w4','ALSA.ALSA-Wave4',variables=list('W4QUNO'), missings = T)
ALSA_w4 <- opal.execute(o,'ALSA_w4')

opal.assign.table.tibble(o, 'ALSA_w5','ALSA.ALSA-Wave5',variables=list('INTTYPW5'), missings = T)
ALSA_w5 <- opal.execute(o,'ALSA_w5')

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('AGEW6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('sex'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')

opal.assign.table.tibble(o, 'ALSA_w8','ALSA.ALSA-Wave8',variables=list('Date'), missings = T)
ALSA_w8 <- opal.execute(o,'ALSA_w8')

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',variables=list('sex'), missings = T)
ALSA_w9 <- opal.execute(o,'ALSA_w9')

opal.assign.table.tibble(o, 'ALSA_w10','ALSA.ALSA-Wave10',variables=list('Date'), missings = T)
ALSA_w10 <- opal.execute(o,'ALSA_w10')

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('SEXW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('SEXW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')

opal.assign.table.tibble(o, 'ALSA_w13','ALSA.ALSA-Wave13',variables=list('proxy'), missings = T)
ALSA_w13 <- opal.execute(o,'ALSA_w13')



```


#### Harmonisation algorithm

All the interviewed individuals are considered urban. 

**R script:**

```{r harmo}

rm(list=setdiff(ls(), c("o","datafolder","ALSA_w1","ALSA_w2","ALSA_w3","ALSA_w4","ALSA_w5","ALSA_w6","ALSA_w7","ALSA_w8","ALSA_w9","ALSA_w10","ALSA_w11","ALSA_w12","ALSA_w13","ds_label","cat_label") )) 

dflist <- lapply(Filter(function(x) is.data.frame(get(x)), ls()), get)



ind <- 0
for(df in dflist){
  ind <- ind + 1
  resid_place <- tibble(id=df$id)
  resid_place$resid_place <- 0
  resid_place$resid_place <- labelled(resid_place$resid_place, labels = cat_label)
  label(resid_place$resid_place) <- ds_label
  save(resid_place,file = paste0("../RData/w",as.character(ind),"/resid_place",".RData"))
}

```



# Quality estimation

The participants in the ALSA study were from Adelaide (South Australia). It is the capital city of the state of South Australia, and the fifth-most populous city of Australia. Thus, it's a urban place.  [Cohort profile](https://www.ncbi.nlm.nih.gov/pubmed/25468824). In a team meeting of the PSSJD it was decided to consider the ALSA participants as from urban seeting.


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





