---
title: "Residence"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable


The description of harmonised variable is the following:

* Short name: `residence`
* Variable label: `Current residence`
* Variable description: `Current residence`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Community living
1        | Institutions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process 

## ALSA

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICILE`
* Label: `Domicile`
* Categories: 
    + `1 = Community living`
    + `2 = Institution`
* Missings: 
    + `9 = Missing`
    
* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w1_resi','ALSA.ALSA-Wave1',
                         variables=list('DOMICILE'), missings = TRUE)
```

```{r local1,  echo=FALSE}
ALSA_w1_resi <- opal.execute(o,'ALSA_w1_resi')
vari <- ALSA_w1_resi$DOMICILE
kable(Categorical_summary(vari, missing_values = c(9))[3]) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w1_resi$DOMICILE, missing_values = c(9))
ggplot(ALSA_w1_resi, aes(x=factor(DOMICILE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Community living" into 0`
* `recode 2 "Institution" into 1`
* `recode 9 "Missing" into 999`

 

**R script:** 
```{r harmo1,   echo=TRUE}
ALSA_ds_w1 <- tibble(id=ALSA_w1_resi$id)
ALSA_ds_w1$residence <- car::recode(ALSA_w1_resi$DOMICILE, "1=0; 2=1; 9=999; NA=999")
ALSA_ds_w1$residence <- labelled(ALSA_ds_w1$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- ALSA_ds_w1$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w1$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w1, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(ALSA_w1_resi$DOMICILE)
AfterH <- table(ALSA_ds_w1$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1")
kable(C)
```







### Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `Q1B`
* Label: `Type of accommodation`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = Bed sitter room`
    + `7 = Other community living`
    + `8 = Retirement village`
    + `9 = Private rest home`
    + `10 = Hostel`
    + `11 = Nursing home`
    + `12 = Hospital`
    + `13 = Mental institution`
    + `14 = Boarding house`
    + `15 = Other institution`


* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w2_resi','ALSA.ALSA-Wave2',
                         variables=list('Q1B'), missings = TRUE)

```

```{r local2,  echo=FALSE}
ALSA_w2_resi <- opal.execute(o,'ALSA_w2_resi')
vari <- ALSA_w2_resi$Q1B
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w2_resi$Q1B, missing_values = NA)
ggplot(ALSA_w2_resi, aes(x=factor(Q1B))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Retirement village" into 0`
* `recode 9 "Private rest home" into 1`
* `recode 10 "Hostel" into 1`
* `recode 11 "Nursing home" into 1`
* `recode 12 "Hospital" into 1`
* `recode 13 "Mental institution" into 1`
* `recode 14 "Boarding house" into 1`
* `recode 15 "Other institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo2,   echo=TRUE}
ALSA_ds_w2 <- tibble(id=ALSA_w2_resi$id)
ALSA_ds_w2$residence <- car::recode(ALSA_w2_resi$Q1B, "1:8=0; 9:15=1; NA=999")
ALSA_ds_w2$residence <- labelled(ALSA_ds_w2$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- ALSA_ds_w2$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w2$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w2, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(ALSA_w2_resi$Q1B)
BeforeH <- c(sum(BeforeH[1:3]), sum(BeforeH[4:length(BeforeH)]), sum(is.na(ALSA_w2_resi$Q1B)))
AfterH <- table(ALSA_ds_w2$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7)->0","(8:15)->1", "NA->999")
kable(C)
```





### Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW3`
* Label: `DOMICILE`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = Bed sitter room`
    + `7 = Other community living`
    + `8 = Retirement village`
    + `9 = Private rest home`
    + `10 = Hostel`
    + `11 = Nursing home`
    + `12 = Hospital`
    + `13 = Mental institution`
    + `14 = Boarding house`
    + `15 = Other institution`
    
    
* Description: 
```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w3_resi','ALSA.ALSA-Wave3',
                         variables=list('DOMICW3'), missings = TRUE)
```

```{r local3,  echo=FALSE}
ALSA_w3_resi <- opal.execute(o,'ALSA_w3_resi')
vari <- ALSA_w3_resi$DOMICW3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w3_resi$DOMICW3, missing_values = NA)
ggplot(ALSA_w3_resi, aes(x=factor(DOMICW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Retirement village" into 0`
* `recode 9 "Private rest home" into 1`
* `recode 10 "Hostel" into 1`
* `recode 11 "Nursing home" into 1`
* `recode 12 "Hospital" into 1`
* `recode 13 "Mental institution" into 1`
* `recode 14 "Boarding house" into 1`
* `recode 15 "Other institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo3,   echo=TRUE}
ALSA_ds_w3 <- tibble(id=ALSA_w3_resi$id)
ALSA_ds_w3$residence <- car::recode(ALSA_w3_resi$DOMICW3, "1:8=0; 9:15=1; NA=999")
ALSA_ds_w3$residence <- labelled(ALSA_ds_w3$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- ALSA_ds_w3$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w3$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w3, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- table(ALSA_w3_resi$DOMICW3)
BeforeH <- c(sum(BeforeH[1:7]), sum(BeforeH[8:length(BeforeH)]))
AfterH <- table(ALSA_ds_w3$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7)->0","(8:15)->1")
kable(C)
```




### Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ACCOM2W4`
* Label: `TYPE OF ACCOMMODATION`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = Bed sitter room`
    + `7 = Other community living`
    + `8 = Retirement village`
    + `9 = Private rest home`
    + `10 = Hostel`
    + `11 = Nursing home`
    + `12 = Hospital`
    + `13 = Mental institution`
    + `14 = Boarding house`
    + `15 = Other institution`
    + `16 = House,home unit, flat`
    + `17 = Nursing Home , Inst`
    + `18 = Retirement Village`
    + `19 = Hostel`
    
* Description: 
```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w4_resi','ALSA.ALSA-Wave4',
                         variables=list('ACCOM2W4'), missings = TRUE)

```

```{r local4,  echo=FALSE}
ALSA_w4_resi <- opal.execute(o,'ALSA_w4_resi')
vari <- ALSA_w4_resi$ACCOM2W4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w4_resi$ACCOM2W4, missing_values = NA)
ggplot(ALSA_w4_resi, aes(x=factor(ACCOM2W4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Retirement village" into 0`
* `recode 9 "Private rest home" into 1`
* `recode 10 "Hostel" into 1`
* `recode 11 "Nursing home" into 1`
* `recode 12 "Hospital" into 1`
* `recode 13 "Mental institution" into 1`
* `recode 14 "Boarding house" into 1`
* `recode 15 "Other institution" into 1`
* `recode 16 "House,home unit, flat" into 0`
* `recode 17 "Nursing Home , Inst" into 1`
* `recode 18 "Retirement Village" into 1`
* `recode 19 "Hostel" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo4,   echo=TRUE}
ALSA_ds_w4 <- tibble(id=ALSA_w4_resi$id)
ALSA_ds_w4$residence <- car::recode(ALSA_w4_resi$ACCOM2W4, "1:8=0; 9:15=1; 16=0; 17:19=1; NA=999")
ALSA_ds_w4$residence <- labelled(ALSA_ds_w4$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- ALSA_ds_w4$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w4$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w4, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4,  echo=FALSE}
BeforeH <- table(ALSA_w4_resi$ACCOM2W4)
BeforeH <- c(sum(BeforeH[c(1:3,11)]), sum(BeforeH[c(4:10,12:14)]))
AfterH <- table(ALSA_ds_w4$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7, 16)->0","(8:15, 17:19)->1")
kable(C)
```






### Wave 5 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `ACCOM1W5`
* Label: `DO YOU (DOES HE/SHE) LIVE IN A: IN`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = Bed sitter room`
    + `7 = Other community living (Please specify)`
* Name: `ACCOM2W5`
* Label: `WHAT TYPE OF INSTITUTION (DOES HE`
* Categories: 
    + `1 = Retirement village`
    + `2 = Private rest home`
    + `3 = Hostel`
    + `4 = Nursing home`
    + `5 = Hospital`
    + `6 = Mental institution`
    + `7 = Boarding house`
    + `8 = Other institution (Please specify)`
    
* Description: 
```{r assign5,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w5_resi','ALSA.ALSA-Wave5',
                         variables=list('ACCOM1W5', 'ACCOM2W5'), missings = TRUE)
```

```{r local5,  echo=FALSE}
ALSA_w5_resi <- opal.execute(o,'ALSA_w5_resi')

vari <- ALSA_w5_resi$ACCOM1W5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w5_resi$ACCOM1W5, missing_values = NA)
ggplot(ALSA_w5_resi, aes(x=factor(ACCOM1W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")

vari <- ALSA_w5_resi$ACCOM2W5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w5_resi$ACCOM2W5, missing_values = NA)
ggplot(ALSA_w5_resi, aes(x=factor(ACCOM2W5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")

```

The varibale ACCOM1W5 has one value -1, It is going to consider a error, therefore is going to recode as 1. 

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they have to be recoded as follows:

* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Other community living (Please specify)" into 0`
* `recode 1 "Retirement village" into 0`
* `recode 2 "Private rest home" into 1`
* `recode 3 "Hostel" into 1`
* `recode 4 "Nursing home" into 1`
* `recode 5 "Hospital" into 1`
* `recode 6 "Mental institution" into 1`
* `recode 7 "Boarding house" into 1`
* `recode 8 "Other institution (Please specify)" into 1`
* `recode NA into 999`


 

**R script:** 
```{r harmo5,   echo=TRUE}
ALSA_w5_resi$ACCOM1W5_2 <- car::recode(ALSA_w5_resi$ACCOM1W5, "-1=1")
ALSA_w5_resi$ACCOM2W5_2 <- car::recode(ALSA_w5_resi$ACCOM2W5, "1=8; 2=9; 3=10; 
                                  4=11; 5=12; 6=13; 7=14; 8=15")

ALSA_w5_resi$ACCOM12W5 <- ALSA_w5_resi$ACCOM1W5_2
ALSA_w5_resi$ACCOM12W5[is.na(ALSA_w5_resi$ACCOM1W5_2)] <- 
  ALSA_w5_resi$ACCOM2W5_2[is.na(ALSA_w5_resi$ACCOM1W5_2)]


ALSA_ds_w5 <- tibble(id=ALSA_w5_resi$id)
ALSA_ds_w5$residence <- car::recode(ALSA_w5_resi$ACCOM12W5, "1:8=0; 9:15=1; NA=999")
ALSA_ds_w5$residence <- labelled(ALSA_ds_w5$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5,  echo=FALSE}
vari <- ALSA_ds_w5$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w5$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w5, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
First, we would like to know if the no missing values in ACCOM2W5 are missing in ACCOM1W5 and viceversa. 

```{r crosstabulation5.1,  echo=FALSE}
Nas_1 <- ALSA_w5_resi[is.na(ALSA_w5_resi$ACCOM1W5),]
dim(Nas_1)
CC_Nas_1 <- Nas_1[!is.na(Nas_1$ACCOM2W5),]
dim(CC_Nas_1)
sum(is.na(CC_Nas_1$ACCOM2W5))


Nas_2 <- ALSA_w5_resi[is.na(ALSA_w5_resi$ACCOM2W5),]
dim(Nas_2)
CC_Nas_2 <- Nas_2[!is.na(Nas_2$ACCOM1W5),]
dim(CC_Nas_2)
sum(is.na(CC_Nas_2$ACCOM1W5))
```


```{r crosstabulation5,  echo=FALSE}
BeforeH <- table(ALSA_w5_resi$ACCOM12W5)
BeforeH <- c(sum(BeforeH[1:2]), sum(BeforeH[3:length(BeforeH)]), sum(is.na(ALSA_w5_resi$ACCOM12W5)))
AfterH <- table(ALSA_ds_w5$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7)->0","(8:15)->1", "NA->999")
kable(C)
```






### Wave 6 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW6`
* Label: `type of domicile - W6`
* Categories: 
    + `1 = community living`
    + `2 = institution`
* Missings: 
    + `0 = no answer`
    
* Description: 
```{r assign6,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w6_resi','ALSA.ALSA-Wave6',
                         variables=list('DOMICW6'), missings = TRUE)
```

```{r local6,  echo=FALSE}
ALSA_w6_resi <- opal.execute(o,'ALSA_w6_resi')
vari <- ALSA_w6_resi$DOMICW6
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w6_resi$DOMICW6, missing_values = c(0))
ggplot(ALSA_w6_resi, aes(x=factor(DOMICW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode 0 "no answer" into 995`
* `recode NA into 999`

 

**R script:** 
```{r harmo6,   echo=TRUE}
ALSA_ds_w6 <- tibble(id=ALSA_w6_resi$id)
ALSA_ds_w6$residence <- car::recode(ALSA_w6_resi$DOMICW6, "1=0; 2=1; 0=995; NA=999")
ALSA_ds_w6$residence <- labelled(ALSA_ds_w6$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6,  echo=FALSE}
vari <- ALSA_ds_w6$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w6$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w6, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6,  echo=FALSE}
BeforeH <- table(ALSA_w6_resi$DOMICW6)
AfterH <- table(ALSA_ds_w6$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1")
kable(C)
```






### Wave 7 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `domicw7`
* Label: `type of domicile-W7`
* Categories: 
    + `1 = Community living`
    + `2 = Institution`

    
* Description: 
```{r assign7,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w7_resi','ALSA.ALSA-Wave7',
                         variables=list('domicw7'), missings = TRUE)
```

```{r local7,  echo=FALSE}
ALSA_w7_resi <- opal.execute(o,'ALSA_w7_resi')
vari <- ALSA_w7_resi$domicw7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w7_resi$domicw7, missing_values = NA)
ggplot(ALSA_w7_resi, aes(x=factor(domicw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo7,   echo=TRUE}
ALSA_ds_w7 <- tibble(id=ALSA_w7_resi$id)
ALSA_ds_w7$residence <- car::recode(ALSA_w7_resi$domicw7,  "1=0; 2=1; NA=999")
ALSA_ds_w7$residence <- labelled(ALSA_ds_w7$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7,  echo=FALSE}
vari <- ALSA_ds_w7$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w7$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w7, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7,  echo=FALSE}
BeforeH <- c(table(ALSA_w7_resi$domicw7),sum(is.na(ALSA_w7_resi$domicw7)))
AfterH <- table(ALSA_ds_w7$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1", "NA->999")
kable(C)
```





### Wave 8 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `accom1w8`
* Label: `Type of accommodation`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = bed sitter`
    + `7 = other community`
* Missings: 
    + `0 = Not Answered`
* Name: `accom2w8`
* Label: `ACCOM2W8`
* Categories: 
    + `1 = Retirement village`
    + `2 = Private rest home`
    + `3 = Hostel`
    + `4 = Nursing home`
    + `5 = Hospital`
    + `6 = Mental institution`
    + `7 = Boarding house`
    + `8 = Other institution (Please specify)`
* Missings: 
    + `0 = Not Answered`
    
    
* Description: 
```{r assign8,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w8_resi','ALSA.ALSA-Wave8',
                         variables=list('accom1w8', 'accom2w8'), missings = TRUE)
```

```{r local8,  echo=FALSE}
ALSA_w8_resi <- opal.execute(o,'ALSA_w8_resi')

vari <- ALSA_w8_resi$accom1w8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w8_resi$accom1w8, missing_values = c(0))
ggplot(ALSA_w8_resi, aes(x=factor(accom1w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")

vari <- ALSA_w8_resi$accom2w8
kable(Categorical_summary(vari, missing_values = c(0))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(0))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(0))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w8_resi$accom2w8, missing_values = c(0))
ggplot(ALSA_w8_resi, aes(x=factor(accom2w8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they have to be recoded as follows:

* `recode 0 "Not Answered" into 995`
* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Other community living (Please specify)" into 0`
* `recode 0 "Not Answered" into 995`
* `recode 1 "Retirement village" into 0`
* `recode 2 "Private rest home" into 1`
* `recode 3 "Hostel" into 1`
* `recode 4 "Nursing home" into 1`
* `recode 5 "Hospital" into 1`
* `recode 6 "Mental institution" into 1`
* `recode 7 "Boarding house" into 1`
* `recode 8 "Other institution (Please specify)" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo8,   echo=TRUE}
ALSA_w8_resi$ACCOM1W8_2 <- ALSA_w8_resi$accom1w8
ALSA_w8_resi$ACCOM2W8_2 <- car::recode(ALSA_w8_resi$accom2w8, "0=16; 1=8; 2=9; 3=10; 4=11; 5=12; 6=13; 7=14; 8=15")

ALSA_w8_resi$ACCOM12W8 <- ALSA_w8_resi$ACCOM1W8_2
ALSA_w8_resi$ACCOM12W8[is.na(ALSA_w8_resi$ACCOM1W8_2)] <- 
  ALSA_w8_resi$ACCOM2W8_2[is.na(ALSA_w8_resi$ACCOM1W8_2)]


ALSA_ds_w8 <- tibble(id=ALSA_w8_resi$id)
ALSA_ds_w8$residence <- car::recode(ALSA_w8_resi$ACCOM12W8, "1:8=0; 9:15=1; c(0,16)=995; NA=999")
ALSA_ds_w8$residence <- labelled(ALSA_ds_w8$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript8,  echo=FALSE}
vari <- ALSA_ds_w8$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w8$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w8, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
First, we would like to know if the no missing values in accom2w8 are missing in accom1w8 and viceversa. 

```{r crosstabulation8.1,  echo=FALSE}
Nas_1 <- ALSA_w8_resi[is.na(ALSA_w8_resi$accom1w8),]
dim(Nas_1)
CC_Nas_1 <- Nas_1[!is.na(Nas_1$accom2w8),]
dim(CC_Nas_1)
sum(is.na(CC_Nas_1$accom2w8))


Nas_2 <- ALSA_w8_resi[is.na(ALSA_w8_resi$accom2w8),]
dim(Nas_2)
CC_Nas_2 <- Nas_2[!is.na(Nas_2$accom1w8),]
dim(CC_Nas_2)
sum(is.na(CC_Nas_2$accom1w8))
```


```{r crosstabulation8,  echo=FALSE}
BeforeH <- table(ALSA_w8_resi$ACCOM12W8)
BeforeH <- c(sum(BeforeH[2:4]), sum(BeforeH[5:7]), sum(BeforeH[c(1,8)]), sum(is.na(ALSA_w8_resi$ACCOM12W8)))
AfterH <- table(ALSA_ds_w8$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7)->0","(8:15)->1", "(0,16)->995", "NA->999")
kable(C)
```





### Wave 9 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW9`
* Label: `type of domicile W9`
* Categories: 
    + `1 = Community living`
    + `2 = Residential care facility`
    
* Description: 
```{r assign9,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w9_resi','ALSA.ALSA-Wave9',
                         variables=list('DOMICW9'), missings = TRUE)
```

```{r local9,  echo=FALSE}
ALSA_w9_resi <- opal.execute(o,'ALSA_w9_resi')
vari <- ALSA_w9_resi$DOMICW9
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w9_resi$DOMICW9, missing_values = NA)
ggplot(ALSA_w9_resi, aes(x=factor(DOMICW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo9,   echo=TRUE}
ALSA_ds_w9 <- tibble(id=ALSA_w9_resi$id)
ALSA_ds_w9$residence <- car::recode(ALSA_w9_resi$DOMICW9,  "1=0; 2=1; NA=999")
ALSA_ds_w9$residence <- labelled(ALSA_ds_w9$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript9,  echo=FALSE}
vari <- ALSA_ds_w9$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w9$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w9, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation9,  echo=FALSE}
BeforeH <- c(table(ALSA_w9_resi$DOMICW9),sum(is.na(ALSA_w9_resi$DOMICW9)))
AfterH <- table(ALSA_ds_w9$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1", "NA->999")
kable(C)
```




### Wave 10 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `accom1w10`
* Label: `What type of accommodation do you now live in?`
* Categories: 
    + `1 = House`
    + `2 = Home unit or flat`
    + `3 = Granny flat with kitchen`
    + `4 = Granny flat without kitchen`
    + `5 = Non self contained unit`
    + `6 = Bed sitter room`
    + `7 = Other community living (Please specify)`
* Missings: 
    + `99 = Not Answered`
* Name: `accom2w10`
* Label: `What type of accommodation do you now live in?`
* Categories: 
    + `8 = Retirement village`
    + `9 = Private rest home`
    + `10 = Hostel`
    + `11 = Nursing home`
    + `12 = Hospital`
    + `13 = Mental institution`
    + `14 = Boarding house`
    + `15 = Other institution (Please specify)`
* Missings: 
    + `99 = Not Answered`

    
* Description: 
```{r assign10,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w10_resi','ALSA.ALSA-Wave10',
                         variables=list('accom1w10', 'accom2w10'), missings = TRUE)
```

```{r local10,  echo=FALSE}
ALSA_w10_resi <- opal.execute(o,'ALSA_w10_resi')

vari <- ALSA_w10_resi$accom1w10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w10_resi$accom1w10, missing_values = c(99))
ggplot(ALSA_w10_resi, aes(x=factor(accom1w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")

vari <- ALSA_w10_resi$accom2w10
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_w10_resi$accom2w10, missing_values = c(99))
ggplot(ALSA_w10_resi, aes(x=factor(accom2w10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence in institution") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they have to be recoded as follows:

* `recode 1 "House" into 0`
* `recode 2 "Home unit or flat" into 0`
* `recode 3 "Granny flat with kitchen" into 0`
* `recode 4 "Granny flat without kitchen" into 0`
* `recode 5 "Non self contained unit" into 0`
* `recode 6 "Bed sitter room" into 0`
* `recode 7 "Other community living" into 0`
* `recode 8 "Other community living (Please specify)" into 0`
* `recode 99 "Not Answered" into 995`
* `recode 1 "Retirement village" into 0`
* `recode 2 "Private rest home" into 1`
* `recode 3 "Hostel" into 1`
* `recode 4 "Nursing home" into 1`
* `recode 5 "Hospital" into 1`
* `recode 6 "Mental institution" into 1`
* `recode 7 "Boarding house" into 1`
* `recode 8 "Other institution (Please specify)" into 1`
* `recode NA into 999`
* `recode 99 "Not Answered" into 995`

 

**R script:** 
```{r harmo10,   echo=TRUE}
ALSA_w10_resi$ACCOM1W5_2 <- ALSA_w10_resi$accom1w10
ALSA_w10_resi$ACCOM2W5_2 <- car::recode(ALSA_w10_resi$accom2w10, "2=NA")

ALSA_w10_resi$ACCOM12W5 <- ALSA_w10_resi$ACCOM1W5_2
ALSA_w10_resi$ACCOM12W5[is.na(ALSA_w10_resi$ACCOM1W5_2)] <- 
  ALSA_w10_resi$ACCOM2W5_2[is.na(ALSA_w10_resi$ACCOM1W5_2)]

ALSA_ds_w10 <- tibble(id=ALSA_w10_resi$id)
ALSA_ds_w10$residence <- car::recode(ALSA_w10_resi$ACCOM12W5, "1:8=0; 9:15=1; NA=999")
ALSA_ds_w10$residence <- labelled(ALSA_ds_w10$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript10,  echo=FALSE}
vari <- ALSA_ds_w10$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w10$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w10, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation10.1,  echo=FALSE}
Nas_1 <- ALSA_w10_resi[is.na(ALSA_w10_resi$accom1w10),]
dim(Nas_1)
CC_Nas_1 <- Nas_1[!is.na(Nas_1$accom2w10),]
dim(CC_Nas_1)
sum(is.na(CC_Nas_1$accom2w10))


Nas_2 <- ALSA_w10_resi[is.na(ALSA_w10_resi$accom2w10),]
dim(Nas_2)
CC_Nas_2 <- Nas_2[!is.na(Nas_2$accom1w10),]
dim(CC_Nas_2)
sum(is.na(CC_Nas_2$accom1w10))
```


```{r crosstabulation10,  echo=FALSE}
BeforeH <- table(ALSA_w10_resi$ACCOM12W5)
BeforeH <- c(sum(BeforeH[1:3]), sum(BeforeH[4:length(BeforeH)]), sum(c(is.na(ALSA_w10_resi$ACCOM12W5))))
AfterH <- table(ALSA_ds_w10$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(1:7)->0","(8:15)->1", "NA->999")
kable(C)
```




### Wave 11 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW11`
* Label: `type of domicile W11`
* Categories: 
    + `1 = Community living`
    + `2 = Institution`
    
* Description: 
```{r assign11,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w11_resi','ALSA.ALSA-Wave11',
                         variables=list('DOMICW11'), missings = TRUE)
```

```{r local11,  echo=FALSE}
ALSA_w11_resi <- opal.execute(o,'ALSA_w11_resi')
vari <- ALSA_w11_resi$DOMICW11
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w11_resi$DOMICW11, missing_values = NA)
ggplot(ALSA_w11_resi, aes(x=factor(DOMICW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo11,   echo=TRUE}
ALSA_ds_w11 <- tibble(id=ALSA_w11_resi$id)
ALSA_ds_w11$residence <- car::recode(ALSA_w11_resi$DOMICW11,  "1=0; 2=1; NA=999")
ALSA_ds_w11$residence <- labelled(ALSA_ds_w11$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript11,  echo=FALSE}
vari <- ALSA_ds_w11$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w11$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w11, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation11,  echo=FALSE}
BeforeH <- table(ALSA_w11_resi$DOMICW11)
AfterH <- table(ALSA_ds_w11$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1")
kable(C)
```




### Wave 12 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW12`
* Label: `type of domicile-W7`
* Categories: 
    + `1 = Community living`
    + `2 = Residential care facility`
    
* Description: 
```{r assign12,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w12_resi','ALSA.ALSA-Wave12',
                         variables=list('DOMICW12'), missings = TRUE)
```

```{r local12,  echo=FALSE}
ALSA_w12_resi <- opal.execute(o,'ALSA_w12_resi')
vari <-ALSA_w12_resi$DOMICW12 
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w12_resi$DOMICW12, missing_values = NA)
ggplot(ALSA_w12_resi, aes(x=factor(DOMICW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo12,   echo=TRUE}
ALSA_ds_w12 <- tibble(id=ALSA_w12_resi$id)
ALSA_ds_w12$residence <- car::recode(ALSA_w12_resi$DOMICW12,  "1=0; 2=1; NA=999")
ALSA_ds_w12$residence <- labelled(ALSA_ds_w12$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript12,  echo=FALSE}
vari <- ALSA_ds_w12$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w12$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w12, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation12,  echo=FALSE}
BeforeH <- table(ALSA_w12_resi$DOMICW12)
AfterH <- table(ALSA_ds_w12$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1")
kable(C)
```





### Wave 13 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DOMICW13`
* Label: `type of domicile-W7`
* Categories: 
    + `1 = Community living`
    + `2 = Institution`
    
* Description: 
```{r assign13,  echo=FALSE}
opal.assign.table.tibble(o, 'ALSA_w13_resi','ALSA.ALSA-Wave13',
                         variables=list('DOMICW13'), missings = TRUE)
```

```{r local13,  echo=FALSE}
ALSA_w13_resi <- opal.execute(o,'ALSA_w13_resi')
vari <- ALSA_w13_resi$DOMICW13
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ALSA_w13_resi$DOMICW13, missing_values = NA)
ggplot(ALSA_w13_resi, aes(x=factor(DOMICW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "community living" into 0`
* `recode 2 "institution" into 1`
* `recode NA into 999`

 

**R script:** 
```{r harmo13,   echo=TRUE}
ALSA_ds_w13 <- tibble(id=ALSA_w13_resi$id)
ALSA_ds_w13$residence <- car::recode(ALSA_w13_resi$DOMICW13,  "1=0; 2=1; NA=999")
ALSA_ds_w13$residence <- labelled(ALSA_ds_w13$residence, labels = c("Community living"=0, "Institutions"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript13,  echo=FALSE}
vari <- ALSA_ds_w13$residence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ALSA_ds_w13$residence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ALSA_ds_w13, aes(x=factor(residence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Residence") + ylab("Frequency")
```

#### Validation
```{r crosstabulation13,  echo=FALSE}
BeforeH <- table(ALSA_w13_resi$DOMICW13)
AfterH <- table(ALSA_ds_w13$residence)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1")
kable(C)
```

# Quality estimation
[Comments on the quality of the new harmonised variable.]

```{r save, echo=FALSE,  echo=FALSE}
residence <- ALSA_ds_w1
save(residence, file = "../RData/w1/residence.RData")
rm(residence)

residence <- ALSA_ds_w2
save(residence, file = "../RData/w2/residence.RData")
rm(residence)

residence <- ALSA_ds_w3
save(residence, file = "../RData/w3/residence.RData")
rm(residence)

residence <- ALSA_ds_w4
save(residence, file = "../RData/w4/residence.RData")
rm(residence)

residence <- ALSA_ds_w5
save(residence, file = "../RData/w5/residence.RData")
rm(residence)

residence <- ALSA_ds_w6
save(residence, file = "../RData/w6/residence.RData")
rm(residence)

residence <- ALSA_ds_w7
save(residence, file = "../RData/w7/residence.RData")
rm(residence)

residence <- ALSA_ds_w8
save(residence, file = "../RData/w8/residence.RData")
rm(residence)

residence <- ALSA_ds_w9
save(residence, file = "../RData/w9/residence.RData")
rm(residence)

residence <- ALSA_ds_w10
save(residence, file = "../RData/w10/residence.RData")
rm(residence)

residence <- ALSA_ds_w11
save(residence, file = "../RData/w11/residence.RData")
rm(residence)

residence <- ALSA_ds_w12
save(residence, file = "../RData/w12/residence.RData")
rm(residence)

residence <- ALSA_ds_w13
save(residence, file = "../RData/w13/residence.RData")
rm(residence)
```

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
