---
title: "Employed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/employedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/employedDS.R')
```



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `CURRWORK`|
|-|-|
| **Label** | `Currently working`|
| **Table name**  | `ALSA-Wave1` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('CURRWORK'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')

```

```{r local w1, echo=F}

vbl <- ALSA_w1$CURRWORK
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = 'CURRWORK')
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(CURRWORK))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `9, NA into 999`

**R script:**

```{r harmo w1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$employed <- car::recode(ALSA_w1$CURRWORK, "2 = 0; c(9,NA) = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ALSA_ds_w1$employed)
X <- table(ALSA_w1$CURRWORK,useNA = "ifany")
BeforeH <- c(X[2:1],sum(X[3:4]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999")
kable(C)

```



### Wave 2

Not found.


### Wave 3


#### Study-specific variable description

| **Name** | `CURRWKW3`|
|-|-|
| **Label** | `CURRENTLY WORKING`|
| **Table name**  | `ALSA-Wave3` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('CURRWKW3'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$CURRWKW3
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(CURRWKW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo w3}

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$employed <- car::recode(ALSA_w3$CURRWKW3, "2 = 0; c(9,NA) = 999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ALSA_ds_w3$employed)
X <- table(ALSA_w3$CURRWKW3,useNA = "ifany")
BeforeH <- c(X[2:1],sum(X[3:4]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999")
kable(C)

```



### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CURRWKW6`|
|-|-|
| **Label** | `paid employment`|
| **Table name**  | `ALSA-Wave6` |
| **Categories** | `1 = yes`<br/>`2 = no` |
| **Missings** | `0 = no answer`<br/>`NA` |
| **Description** |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CURRWKW6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')

```

```{r local w6, echo=F}

vbl <- ALSA_w6$CURRWKW6
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CURRWKW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w6}

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$employed <- car::recode(ALSA_w6$CURRWKW6, "2 = 0; 0 = 995; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ALSA_ds_w6$employed)
BeforeH <- table(ALSA_w6$CURRWKW6,useNA = "ifany")[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999")
kable(C)

```



### Wave 7


#### Study-specific variable description

| **Name** | `currwkw7`|
|-|-|
| **Label** | `paid employment`|
| **Table name**  | `ALSA-Wave7` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `0 = Not Answered`<br/>`NA` |
| **Description** |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('currwkw7'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')

```

```{r local w7, echo=F}

vbl <- ALSA_w7$currwkw7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(currwkw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `2 into 0`
* `1 into 1`
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w7}

ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$employed <- car::recode(ALSA_w7$currwkw7, "2 = 0; 0 = 995; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ALSA_ds_w7$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ALSA_ds_w7$employed)
BeforeH <- table(ALSA_w7$currwkw7,useNA = "ifany")[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999")
kable(C)

```




### Wave 8

Not found.

### Wave 9

Not found.


### Wave 10

Not found.




### Wave 11


#### Study-specific variable description

| **Name** | `CURRWKW11`|
|-|-|
| **Label** | `currently work in a paid job`|
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `1 = Yes`<br/>`0 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('CURRWKW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$CURRWKW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(CURRWKW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo w11}

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$employed <- car::recode(ALSA_w11$CURRWKW11, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F}

AfterH <- table(ALSA_ds_w11$employed)
BeforeH <- table(ALSA_w11$CURRWKW11,useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```




### Wave 12


#### Study-specific variable description

| **Name** | `CURRWKW12`|
|-|-|
| **Label** | `currently work in a paid job`|
| **Table name**  | `ALSA-Wave12` |
| **Categories** | `1 = Yes`<br/>`0 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('CURRWKW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')

```

```{r local w12, echo=F}

vbl <- ALSA_w12$CURRWKW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(CURRWKW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `employed` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `1 into 1`
* `NA into 999`

**R script:**

```{r harmo w12}

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$employed <- car::recode(ALSA_w12$CURRWKW12, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$employed
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(employed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w12, echo=F}

AfterH <- table(ALSA_ds_w12$employed)
BeforeH <- table(ALSA_w12$CURRWKW12,useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```




### Wave 13

Not found.





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.



```{r summ}

l.hds <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]])
             )
names(t.hds)<-c("val", "label", names(l.hds)[1], names(l.hds)[2], names(l.hds)[3], names(l.hds)[4], names(l.hds)[5], names(l.hds)[6])
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","employed")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","employed")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  employed <- l.hds[[index]]
  save(employed, file = paste0(datafolder,names(l.hds)[index],"/employed.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

In the questionnaires all the used study-specific variables except the one of the wave 1 ask for having at the moment a paid job, so we assume the first one too.


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





