---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Death`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | Dead
2        | Dropout  

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Living status"
ds_label_all <- "The individual is dead or alive?"
```


# Data process

## ATTICA

### Wave 1 

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w1_id','ATTICA.ATTICA_Baseline',
                         variables=list('sex'), missings = TRUE)
ATTICA_w1_id <- opal.execute(o,'ATTICA_w1_id')
```

#### Harmonisation algorithm
It's considered that at baseline all the individuals are alive. Therefore it is going to compute the variable with all the values as 0. 

R code of the ALGORITHM:

```{r harmo1}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_id$id)
ATTICA_ds_w1$living_status <- 0
ATTICA_ds_w1$living_status <- labelled(ATTICA_ds_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ATTICA_ds_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
```





### ATTICA - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `DDetah10`
* Label: `Date of death`
* Type of variable: `date`

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w2_death','ATTICA.ATTICA_Followup2',
                         variables=list('DDetah10'), missings = TRUE)
ATTICA_w2_death <- opal.execute(o,'ATTICA_w2_death')
ATTICA_w2_death$ydeath <- as.numeric(format(ATTICA_w2_death$DDetah10, '%Y'))
ATTICA_w2_death$year_of_interview <- 2006
```

```{r local2, echo=FALSE}
Categorical_summary(var = ATTICA_w2_death$ydeath, missing_values = NA)
Categorical_summary(var = ATTICA_w2_death$year_of_interview, missing_values = NA)
ggplot(ATTICA_w2_death, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is going to be recoded from date of death and interview variables as follow: 

* `the individuals with missing in date of dead but not missing in date of interview into 0`
* `the individuals with any thing missing and:`
    + `year of death after year of interview into 0`
    + `year of death earlier than year of interview into 1`
    + `year of death equal to year of interview`
      - `month of death after month of interview into 0`
      - `month of death after month of interview into 1`

R code of the ALGORITHM:

```{r harmo2}
LS <- function(Ydeath, Yinterview){
  D <- data.frame(Ydeath, Yinterview)
  D$liv_stat <- NA
  
  id2 <- which(is.na(Ydeath) & !is.na(Yinterview))
  D$liv_stat[id2] <- 0
  
  id4 <- which(!is.na(Ydeath) & !is.na(Yinterview))
    id4_1 <- id4[which(D$Ydeath[id4]>D$Yinterview[id4])]
      D$liv_stat[id4_1] <- 0
    id4_2 <- id4[which(D$Ydeath[id4]==D$Yinterview[id4])]
        D$liv_stat[id4_2] <- 0
    id4_3 <- id4[which(D$Ydeath[id4]<D$Yinterview[id4])]
      D$liv_stat[id4_3] <- 1
  
    D$liv_stat
}

ATTICA_w2_death2 <- cbind(ATTICA_w2_death,liv_stat=LS(Ydeath=ATTICA_w2_death$ydeath,Yinterview=ATTICA_w2_death$year_of_interview))


ATTICA_ds_w2 <- tibble(id=ATTICA_w2_death2$id)
ATTICA_ds_w2$living_status <- car::recode(ATTICA_w2_death2$liv_stat, "NA=999")
ATTICA_ds_w2$living_status <- labelled(ATTICA_ds_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ATTICA_ds_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(ATTICA_w2_death2$liv_stat, useNA = "ifany")
AfterH <- table(ATTICA_ds_w2$living_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
C
```









### ATTICA - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `date10`
* Label: `Date of 10 year follow up`

* Name: `DDetah10`
* Label: `Death Date`


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_w3_interdeath','ATTICA.ATTICA_Followup2',
                         variables=list('date10', 'DDetah10'), missings = TRUE)
ATTICA_w3_interdeath <- opal.execute(o,'ATTICA_w3_interdeath')

ATTICA_w3_interdeath$date10[which(ATTICA_w3_interdeath$date10==as.Date("2103-07-29", "%Y-%m-%d"))] <- 
as.Date("2013-07-29", "%Y-%m-%d")
```

```{r local3, echo=FALSE}
vari <- ATTICA_w3_interdeath$date10
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Date of interview") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w3_interdeath, aes(x=date10)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of interview") + ylab("Frequency") 

vari <- ATTICA_w3_interdeath$DDetah10
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Date of death") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_w3_interdeath, aes(x=DDetah10)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Date of death") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is going to be recoded from date of death and interview variables as follow:

* `consider all the individuals as 2`
* `the individuals with data in the wave 3 interview as 0`
* `the individuals with date of death before the last day that the interview take place as 1`

R code of the ALGORITHM:

```{r harmo3}
ATTICA_ds_w3 <- tibble(id=ATTICA_w3_interdeath$id)
ATTICA_ds_w3$living_status <- 2
ATTICA_ds_w3$living_status[!is.na(ATTICA_w3_interdeath$date10)] <- 0
ATTICA_ds_w3$living_status[ATTICA_w3_interdeath$DDetah10 < ATTICA_w3_interdeath$date10] <- 1
ATTICA_ds_w3$living_status[which(is.na(ATTICA_w3_interdeath$date10) & ATTICA_w3_interdeath$DDetah10 < as.Date("28/07/2013", "%d/%m/%Y"))] <- 1
ATTICA_ds_w3$living_status <- labelled(ATTICA_ds_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ATTICA_ds_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3}
```


### Validation throughout waves

```{r valid_ws_hrs, echo=F}
dbb <- left_join(x = ATTICA_ds_w1, y = ATTICA_ds_w2, by = "id", suffix = c(".w1", ".w2"))
dbb <- left_join(x = dbb, y = ATTICA_ds_w3, by = "id")
names(dbb) <- c("id", "w1", "w2", "w3")

dbb$join <- apply(dbb[, 2:4], MARGIN = 1, FUN = function(x) paste(x[1], x[2], x[3], sep=""))
f.dbb <- frq(dbb$join)[[1]][, c(1, 2, 4)]
kable(f.dbb)
#kable(f.dbb[f.dbb[, 3] >= 0.3, ])
```


### Quality estimation

We don't have date of interview in wave 2 and as all the waves have the same number of individuals 
it is not possible to know which ones are dropouts, therefore the variable in wave 2 has only values 
0 (alive) and 1 (dead). 



```{r save, echo=FALSE}
living_status <- ATTICA_ds_w1
save(living_status, file = "../RData/w1/living_status.RData")
rm(living_status)

living_status <- ATTICA_ds_w2
save(living_status, file = "../RData/w2/living_status.RData")
rm(living_status)

living_status <- ATTICA_ds_w3
save(living_status, file = "../RData/w3/living_status.RData")
rm(living_status)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```


