---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```





# Data process




## England




### Wave 1

#### Study-specific variable description

| **Name** | `wpdes` |`wprage`|
|-|-|-|
| **Label** | `Which one of these would you say best describes your current situation?` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_1_core_data_v3` | `wave_1_core_data_v3` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable 01 to 06 or 96`<br/>`86 = Irrelevant response - not codeable 01 to 06 or 96`<br/>`95 = Other (SPECIFY)`<br/>`96 = SPONTANEOUS : Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o,'ELSA_w1','ELSA.wave_1_core_data_v3',variables=list('wpdes','wprage'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')

```

```{r local w1, echo=F}

vbl <- ELSA_w1$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w1$wprage
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'wprage')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w1,!vbl %in% vbl_miss), aes(wprage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$retired <- car::recode(ELSA_w1$wpdes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -8 = 998; -9 = 997")

# Continuous variable harmonization
ELSA_ds_w1$age_retired <- car::recode(ELSA_w1$wprage, "c(-1,0) = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w1$age_retired[which(ELSA_ds_w1$retired == 0)] <- 996

# Correction of the age of retirement of individuals 112305 and 119579, which in wave 1 answer 0 and 107 and have 83 and 74 years old, while in waves 4 and 6 answer 55 and 50 respectively.
ELSA_ds_w1$age_retired[which(ELSA_ds_w1$id=="112305")] <- 55
ELSA_ds_w1$age_retired[which(ELSA_ds_w1$id=="119579")] <- 50

# Global table
ELSA_ds <- ELSA_ds_w1

```




#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w1, echo=F}

```




### Wave 2

#### Study-specific variable description

| **Name** | `wpdes` |`wprage`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_2_core_data_v4` | `wave_2_core_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable 01 to 06 or 96`<br/>`86 = Irrelevant response - not codeable 01 to 06 or 96`<br/>`95 = Other`<br/>`96 = SPONTANEOUS : Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o,'ELSA_w2','ELSA.wave_2_core_data_v4',variables=list('wpdes','wprage'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

```

```{r local w2, echo=F}

vbl <- ELSA_w2$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w2$wprage
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'wprage')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w2,!vbl %in% vbl_miss), aes(wprage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$retired <- car::recode(ELSA_w2$wpdes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -8 = 998; -9 = 997")

ELSA_w2 <- left_join(ELSA_w2,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w2$age_retired <- car::recode(ELSA_w2$wprage, "c(-1,0) = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w2$age_retired[which(!is.na(ELSA_w2$age_retired) & !ELSA_w2$age_retired %in% miss_values_vector)] <- ELSA_w2$age_retired[which(!is.na(ELSA_w2$age_retired) & !ELSA_w2$age_retired %in% miss_values_vector)]
ELSA_ds_w2$age_retired[which(!ELSA_w2$wprage %in% c(-1,0,-8,-9))] <- ELSA_w2$wprage[which(!ELSA_w2$wprage %in% c(-1,0,-8,-9))]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w2,log_vec=ELSA_ds_w2$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w2,log_vec=ELSA_ds_w2$id[which(ELSA_ds_w2$retired != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$age_retired <- ELSA_ds_aux$age_retired
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w2, echo=F}

```




### Wave 3

#### Study-specific variable description

| **Name** | `wpdes` |`wprage`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_3_elsa_data_v4` |`wave_3_elsa_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`95 = Other (SPECIFY)`<br/>`96 = SPONTANEOUS : Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o,'ELSA_w3','ELSA.wave_3_elsa_data_v4',variables=list('wpdes','wprage'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')

```

```{r local w3, echo=F}

vbl <- ELSA_w3$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w3$wprage
vbl_miss <- c(-1,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'wprage')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w3,!vbl %in% vbl_miss), aes(wprage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,95 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$retired <- car::recode(ELSA_w3$wpdes, "c(1,96) = 1; c(2,3,4,5,6,95) = 0; -1 = 996; -8 = 998; -9 = 997")

ELSA_w3 <- left_join(ELSA_w3,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w3$age_retired <- car::recode(ELSA_w3$wprage, "c(-1,0) = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w3$age_retired[which(!is.na(ELSA_w3$age_retired) & !ELSA_w3$age_retired %in% miss_values_vector)] <- ELSA_w3$age_retired[which(!is.na(ELSA_w3$age_retired) & !ELSA_w3$age_retired %in% miss_values_vector)]
ELSA_ds_w3$age_retired[which(!ELSA_w3$wprage %in% c(-1,0,-8,-9))] <- ELSA_w3$wprage[which(!ELSA_w3$wprage %in% c(-1,0,-8,-9))]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w3,log_vec=ELSA_ds_w3$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w3,log_vec=ELSA_ds_w3$id[which(ELSA_ds_w3$retired != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$age_retired <- ELSA_ds_aux$age_retired
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w3$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w3,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w3, echo=F}

```




### Wave 4

#### Study-specific variable description

| **Name** | `wpdes` |`wprage`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_4_elsa_data_v3` |`wave_4_elsa_data_v3` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable`<br/>`86 = Code86`<br/>`95 = Other`<br/>`96 = Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = CAPI/Interview error`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-2 = CAPI/Interview error`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w4, echo=F}

opal.assign.table.tibble(o,'ELSA_w4','ELSA.wave_4_elsa_data_v3',variables=list('wpdes','wprage'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')

```

```{r local w4, echo=F}

vbl <- ELSA_w4$wpdes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w4$wprage
vbl_miss <- c(-1,-2,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'wprage')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w4,!vbl %in% vbl_miss), aes(wprage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-2 into 991`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-2 into 991`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$retired <- car::recode(ELSA_w4$wpdes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -2 = 991; -8 = 998; -9 = 997")

ELSA_w4 <- left_join(ELSA_w4,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w4$age_retired <- car::recode(ELSA_w4$wprage, "c(-1,0) = 996; -2 = 991; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w4$age_retired[which(!is.na(ELSA_w4$age_retired) & !ELSA_w4$age_retired %in% miss_values_vector)] <- ELSA_w4$age_retired[which(!is.na(ELSA_w4$age_retired) & !ELSA_w4$age_retired %in% miss_values_vector)]
ELSA_ds_w4$age_retired[which(!ELSA_w4$wprage %in% c(-2,-1,0,-8,-9))] <- ELSA_w4$wprage[which(!ELSA_w4$wprage %in% c(-2,-1,0,-8,-9))]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w4,log_vec=ELSA_ds_w4$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w4,log_vec=ELSA_ds_w4$id[which(ELSA_ds_w4$retired != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$age_retired <- ELSA_ds_aux$age_retired
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w4$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w4,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w4, echo=F}

```




### Wave 5

#### Study-specific variable description

| **Name** | `wpdes` |`wprage`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_5_elsa_data_v4` | `wave_5_elsa_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w5, echo=F}

opal.assign.table.tibble(o,'ELSA_w5','ELSA.wave_5_elsa_data_v4',variables=list('wpdes','wprage'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')

```

```{r local w5, echo=F}

vbl <- ELSA_w5$wpdes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w5$wprage
vbl_miss <- c(-1,-2,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'wprage')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w5,!vbl %in% vbl_miss), aes(wprage)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w5}

# Categorical variable harmonization
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$retired <- car::recode(ELSA_w5$wpdes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

ELSA_w5 <- left_join(ELSA_w5,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w5$age_retired <- car::recode(ELSA_w5$wprage, "c(-1,0) = 996; -2 = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w5$age_retired[which(!is.na(ELSA_w5$age_retired) & !ELSA_w5$age_retired %in% miss_values_vector)] <- ELSA_w5$age_retired[which(!is.na(ELSA_w5$age_retired) & !ELSA_w5$age_retired %in% miss_values_vector)]
ELSA_ds_w5$age_retired[which(!ELSA_w5$wprage %in% c(-2,-1,0,-8,-9))] <- ELSA_w5$wprage[which(!ELSA_w5$wprage %in% c(-2,-1,0,-8,-9))]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w5,log_vec=ELSA_ds_w5$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w5,log_vec=ELSA_ds_w5$id[which(ELSA_ds_w5$retired != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$age_retired <- ELSA_ds_aux$age_retired
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```

#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w5$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w5,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w5, echo=F}

```




### Wave 6

#### Study-specific variable description

| **Name** | `WpDes` |`WpRAge`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w6, echo=F}

opal.assign.table.tibble(o,'ELSA_w6','ELSA.wave_6_elsa_data_v2',variables=list('WpDes','WpRAge'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')

```

```{r local w6, echo=F}

vbl <- ELSA_w6$WpDes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'WpDes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(WpDes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w6$WpRAge
vbl_miss <- c(-1,-2,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'WpRAge')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w6,!vbl %in% vbl_miss), aes(WpRAge)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = WpRAge`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$retired <- car::recode(ELSA_w6$WpDes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

ELSA_w6 <- left_join(ELSA_w6,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w6$age_retired <- car::recode(ELSA_w6$WpRAge, "c(-1,0) = 996; -2 = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w6$age_retired[which(!is.na(ELSA_w6$age_retired) & !ELSA_w6$age_retired %in% miss_values_vector)] <- ELSA_w6$age_retired[which(!is.na(ELSA_w6$age_retired) & !ELSA_w6$age_retired %in% miss_values_vector)]
ELSA_ds_w6$age_retired[which(!ELSA_w6$WpRAge %in% c(-2,-1,0,-8,-9))] <- ELSA_w6$WpRAge[which(!ELSA_w6$WpRAge %in% c(-2,-1,0,-8,-9))]

# Update of global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ELSA_ds_prov <- ELSA_ds[,c(1,2)]
ELSA_ds_prov <- assign_merge(ELSA_ds_prov,ELSA_ds_w6,log_vec=ELSA_ds_w6$id,col_end_index = 2, col_st_index = 3)
ELSA_ds_aux <- ELSA_ds[,c(1,3)]
ELSA_ds_aux <- assign_merge(ELSA_ds_aux,ELSA_ds_w6,log_vec=ELSA_ds_w6$id[which(ELSA_ds_w6$retired != 999)], col_end_index = 2, col_st_index = 4)
ELSA_ds <- ELSA_ds_prov
ELSA_ds$age_retired <- ELSA_ds_aux$age_retired
rm(ELSA_ds_prov)
rm(ELSA_ds_aux)

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w6$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w6,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w6, echo=F}

```





### Wave 7

| **Name** | `WpDes` |`WpRAge`|
|-|-|-|
| **Label** | `Best description of current situation` |`You said earlier that you were (semi)retired, at what age did you retire?`|
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|`continuous`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |  |


```{r assign w7, echo=F}

opal.assign.table.tibble(o,'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('WpDes','WpRAge'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=F}

vbl <- ELSA_w7$WpDes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'WpDes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(WpDes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ELSA_w7$WpRAge
vbl_miss <- c(-1,-2,-8,-9)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'WpRAge')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(ELSA_w7,!vbl %in% vbl_miss), aes(WpRAge)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `1,96 into 1`
* `2,3,4,5,6,85,86,95 into 0`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = wprage`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`
* `if retired == 0, age_retired = 996`

**R script:**

```{r harmo w7}

# Categorical variable harmonization
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$retired <- car::recode(ELSA_w7$WpDes, "c(1,96) = 1; c(2,3,4,5,6,85,86,95) = 0; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

ELSA_w7 <- left_join(ELSA_w7,ELSA_ds,by="id")

# Continuous variable harmonization
ELSA_ds_w7$age_retired <- car::recode(ELSA_w7$WpRAge, "c(-1,0) = 996; -2 = 996; -8 = 998; -9 = 997; NA = 999")
ELSA_ds_w7$age_retired[which(!is.na(ELSA_w7$age_retired) & !ELSA_w7$age_retired %in% miss_values_vector)] <- ELSA_w7$age_retired[which(!is.na(ELSA_w7$age_retired) & !ELSA_w7$age_retired %in% miss_values_vector)]
ELSA_ds_w7$age_retired[which(!ELSA_w7$WpRAge %in% c(-2,-1,0,-8,-9))] <- ELSA_w7$WpRAge[which(!ELSA_w7$WpRAge %in% c(-2,-1,0,-8,-9))]

# Update of global table
rm(ELSA_ds)

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ELSA_ds_w7$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ELSA_ds_w7,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w7, echo=F}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.



```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label", names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","retired")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","retired")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste0(v.dbb,dbb[,ind+1])
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

The harmonization algorithm is essentially that of g2aging. This means that: 

* Semi-retired is coded as retired; 
* The orden of priority for the age of retired is: first, the age answered at each wave; second, the last age answered at previous waves; third, the missing values. As a consequence, one individual can have different harmonized ages of retirement across waves.


```{r qsumm}

ELSA_ds_join <- full_join(ELSA_ds_w1,ELSA_ds_w2, by="id", suffix=c("_w1",""))
ELSA_ds_join <- full_join(ELSA_ds_join,ELSA_ds_w3, by="id", suffix=c("_w2",""))
ELSA_ds_join <- full_join(ELSA_ds_join,ELSA_ds_w4, by="id", suffix=c("_w3",""))
ELSA_ds_join <- full_join(ELSA_ds_join,ELSA_ds_w5, by="id", suffix=c("_w4",""))
ELSA_ds_join <- full_join(ELSA_ds_join,ELSA_ds_w6, by="id", suffix=c("_w5",""))
ELSA_ds_join <- full_join(ELSA_ds_join,ELSA_ds_w7, by="id", suffix=c("_w6","_w7"))

len_ELSA <- length(ELSA_ds_join$id)

# We save in a list with all the individuals, the variances corresponding to the answered years.

age_columns <- c("age_retired_w1","age_retired_w2","age_retired_w3","age_retired_w4","age_retired_w5","age_retired_w6","age_retired_w7")

nnvar <- function(x){
  partv <- as.numeric(ELSA_ds_join[x,age_columns])
  partv <- partv[!is.na(partv)]
  partvv <- partv[!partv %in% miss_values_vector]
  if(length(partvv)!=0){
    partv <- partvv
  }
  return(var(partv))
} 
ntvar <- lapply( 1:len_ELSA, nnvar)

# The next vector keeps the quantity of non-missing data for each individual
nonmiss <- Reduce("+",lapply(ELSA_ds_join[age_columns], function(x) !x %in% miss_values_vector & !is.na(x)))

ntvar <- unlist(ntvar)
nttib <- tibble(id=ELSA_ds_join$id,varz=ntvar)
ELSA_ds_join <- full_join(ELSA_ds_join,nttib, by="id")

kable(ELSA_ds_join[which(ntvar!=0 & nonmiss>=2),c("id",age_columns,"varz")], align = 'c',caption = 'Individuals which answered more than one non-missing (excluding also 0) age')

```



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```



