---
title: "Childhood socioeconomic position"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/childsepDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/childsepDS.R')
```



# Data process


## England

### Wave 1 

#### Study-specific variable description

| **Name** |`difjob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_1_core_data_v3`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ELSA_w1','ELSA.wave_1_core_data_v3', variables=list('difjob'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')

```

```{r local w1, echo=F}
vbl <- ELSA_w1$difjob
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w1, tidy=FALSE}

ELSA_ds_w1 <- ELSA_w1 %>%
  mutate(childsep = case_when(
    difjob %in% c(2:4) ~ 0,
    difjob %in% c(1,5:8) ~ 1,
    difjob %in% c(9:12,14:15) ~ 2,
    difjob %in% c(-9) ~ 997,
    difjob %in% c(-8) ~ 998,
    difjob %in% c(-1) ~ 996,
    difjob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep)

ELSA_ds <- ELSA_ds_w1 %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  ))

```


#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** |`DiFJob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_2_core_data_v4`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_core_data_v4', variables=list('DiFJob'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

```

```{r local w2, echo=F}
vbl <- ELSA_w2$DiFJob
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

ELSA_aux <- inner_join(ELSA_w1,ELSA_w2, by = "id")
kable(table(ELSA_aux$difjob,ELSA_aux$DiFJob), caption = "Data of individuals in waves 1 and 2")
```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from wave 1`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w2, tidy=FALSE}

ELSA_ds_w2 <- ELSA_w2 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w2 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(2:4) ~ 0,
    DiFJob %in% c(1,5:8) ~ 1,
    DiFJob %in% c(9:12,14:15) ~ 2,
    DiFJob %in% c(-9) ~ 997,
    DiFJob %in% c(-8) ~ 998,
    DiFJob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(-1,-2) & is.na(childsep) ~ 996,
    DiFJob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w2)

ELSA_ds <- ELSA_ds %>%
  full_join(ELSA_ds_w2 %>%
              mutate(misscode = case_when(
                childsep %in% c(991:999) ~ 1,
                TRUE ~ 0
              )), by = "id", suffix = c(".pw",".w2")) %>%
  mutate(childsep = case_when(
    !is.na(misscode.w2) ~ childsep.w2,
    is.na(misscode.w2) ~ childsep.pw
  )) %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  )) %>%
  select(id, childsep, misscode)
```


#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}
```


### Wave 3

#### Study-specific variable description

| **Name** |`difjob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_3_elsa_data_v4`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('difjob'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')

```

```{r local w3, echo=F}
vbl <- ELSA_w3$difjob
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

ELSA_aux <- inner_join(ELSA_w1,ELSA_w3, by = "id", suffix = c(".w1",".w3"))
kable(table(ELSA_aux$difjob.w1,ELSA_aux$difjob.w3), caption = "Data of individuals in waves 1 and 3")

ELSA_aux <- inner_join(ELSA_w2,ELSA_w3, by = "id", suffix = c(".w2",".w3"))
kable(table(ELSA_aux$DiFJob,ELSA_aux$difjob), caption = "Data of individuals in waves 2 and 3")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from previous waves`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1,-2 into 996`
* `13 into 999`

**R script:**
```{r harmo w3, tidy=FALSE}

ELSA_ds_w3 <- ELSA_w3 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w3 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    difjob %in% c(2:4) ~ 0,
    difjob %in% c(1,5:8) ~ 1,
    difjob %in% c(9:12,14:15) ~ 2,
    difjob %in% c(-9) ~ 997,
    difjob %in% c(-8) ~ 998,
    difjob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    difjob %in% c(-1,-2) & is.na(childsep) ~ 996,
    difjob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w3)

ELSA_ds <- ELSA_ds %>%
  full_join(ELSA_ds_w3 %>%
              mutate(misscode = case_when(
                childsep %in% c(991:999) ~ 1,
                TRUE ~ 0
              )), by = "id", suffix = c(".pw",".w3")) %>%
  mutate(childsep = case_when(
    !is.na(misscode.w3) ~ childsep.w3,
    is.na(misscode.w3) ~ childsep.pw
  )) %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  )) %>%
  select(id, childsep, misscode)
```


#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}
```


### Wave 4

#### Study-specific variable description

| **Name** |`difjob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_4_elsa_data_v3`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3', variables=list('difjob'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')

```

```{r local w4, echo=F}
vbl <- ELSA_w4$difjob
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

ELSA_aux <- inner_join(ELSA_w1,ELSA_w4, by = "id", suffix = c(".w1",".w4"))
kable(table(ELSA_aux$difjob.w1,ELSA_aux$difjob.w4), caption = "Data of individuals in waves 1 and 4")


```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from previous waves`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w4, tidy=FALSE}

ELSA_ds_w4 <- ELSA_w4 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w4 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    difjob %in% c(2:4) ~ 0,
    difjob %in% c(1,5:8) ~ 1,
    difjob %in% c(9:12,14:15) ~ 2,
    difjob %in% c(-9) ~ 997,
    difjob %in% c(-8) ~ 998,
    difjob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    difjob %in% c(-1,-2) & is.na(childsep) ~ 996,
    difjob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w4)

ELSA_ds <- ELSA_ds %>%
  full_join(ELSA_ds_w4 %>%
              mutate(misscode = case_when(
                childsep %in% c(991:999) ~ 1,
                TRUE ~ 0
              )), by = "id", suffix = c(".pw",".w4")) %>%
  mutate(childsep = case_when(
    !is.na(misscode.w4) ~ childsep.w4,
    is.na(misscode.w4) ~ childsep.pw
  )) %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  )) %>%
  select(id, childsep, misscode)
```


#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w4, echo=F}
```



### Wave 5

#### Study-specific variable description

| **Name** |`difjob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_5_elsa_data_v4`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w5, echo=F}

opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4', variables=list('difjob'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')

```

```{r local w5, echo=F}
vbl <- ELSA_w5$difjob
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from previous waves`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w5, tidy=FALSE}

ELSA_ds_w5 <- ELSA_w5 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w5 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    difjob %in% c(2:4) ~ 0,
    difjob %in% c(1,5:8) ~ 1,
    difjob %in% c(9:12,14:15) ~ 2,
    difjob %in% c(-9) ~ 997,
    difjob %in% c(-8) ~ 998,
    difjob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    difjob %in% c(-1,-2) & is.na(childsep) ~ 996,
    difjob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w5)

ELSA_ds <- ELSA_ds %>%
  full_join(ELSA_ds_w5 %>%
              mutate(misscode = case_when(
                childsep %in% c(991:999) ~ 1,
                TRUE ~ 0
              )), by = "id", suffix = c(".pw",".w5")) %>%
  mutate(childsep = case_when(
    !is.na(misscode.w5) ~ childsep.w5,
    is.na(misscode.w5) ~ childsep.pw
  )) %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  )) %>%
  select(id, childsep, misscode)
```


#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w5, echo=F}
```



### Wave 6

#### Study-specific variable description

| **Name** |`DiFJob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_6_elsa_data_v2`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_elsa_data_v2', variables=list('DiFJob'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')

```

```{r local w6, echo=F}
vbl <- ELSA_w6$DiFJob
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from previous waves`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w6, tidy=FALSE}

ELSA_ds_w6 <- ELSA_w6 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w6 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(2:4) ~ 0,
    DiFJob %in% c(1,5:8) ~ 1,
    DiFJob %in% c(9:12,14:15) ~ 2,
    DiFJob %in% c(-9) ~ 997,
    DiFJob %in% c(-8) ~ 998,
    DiFJob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(-1,-2) & is.na(childsep) ~ 996,
    DiFJob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w6)

ELSA_ds <- ELSA_ds %>%
  full_join(ELSA_ds_w6 %>%
              mutate(misscode = case_when(
                childsep %in% c(991:999) ~ 1,
                TRUE ~ 0
              )), by = "id", suffix = c(".pw",".w6")) %>%
  mutate(childsep = case_when(
    !is.na(misscode.w6) ~ childsep.w6,
    is.na(misscode.w6) ~ childsep.pw
  )) %>%
  mutate(misscode = case_when(
    childsep %in% c(991:999) ~ 1,
    TRUE ~ 0
  )) %>%
  select(id, childsep, misscode)
```


#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** |`DiFJob`|
|-|-|
| **Label** |`What was your father~s (or main carer~s) job when you were 14?`|
| **Table name** |`wave_7_elsa_data`|
| **Categories** |`1 = Armed Forces`<br/>`2 = Manager or senior official in someone else s business`<br/>`3 = Running his own business`<br/>`4 = Professional or technical`<br/>`5 = Administrative, clerical or secretarial`<br/>`6 = Skilled trade`<br/>`7 = Caring, leisure, travel or personal services`<br/>`8 = Sales or customer service`<br/>`9 = Plant, process or machine drivers or operators`<br/>`10 = Other jobs`<br/>`11 = Something else`<br/>`12 = Casual jobs`<br/>`13 = Retired`<br/>`14 = Unemployed`<br/>`15 = Sick / disabled`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('DiFJob'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=F}
vbl <- ELSA_w7$DiFJob
vbl_mis <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = attr(vbl, "spss::shortName"))
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `childsep` from the study-specific variable it has to be recoded as follows:

* `keep childsep from previous waves`
* `1,5:8 into 1`
* `2:4 into 0`
* `9:12,14:15 into 2`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`
* `13 into 999`

**R script:**
```{r harmo w7, tidy=FALSE}

ELSA_ds_w7 <- ELSA_w7 %>%
  left_join(ELSA_ds, by = "id") %>%
  mutate(childsep.w7 = case_when(
    !childsep %in% c(991:999) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(2:4) ~ 0,
    DiFJob %in% c(1,5:8) ~ 1,
    DiFJob %in% c(9:12,14:15) ~ 2,
    DiFJob %in% c(-9) ~ 997,
    DiFJob %in% c(-8) ~ 998,
    DiFJob %in% c(-1,-2) & !is.na(childsep) ~ childsep,
    DiFJob %in% c(-1,-2) & is.na(childsep) ~ 996,
    DiFJob %in% c(13) ~ 999,
    TRUE ~ 999
  )) %>%
  select(id, childsep = childsep.w7)

rm(ELSA_ds)
```


#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$childsep
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w7, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```