---
title: "Wealth"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/wealthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/wealthDS.R')
```


# Data process



## ELSA

### Wave 1 

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_1_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_1_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local1, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w1$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w1$wealth <- as.integer(ELSA_ds_w1$wealth)
ELSA_ds_w1$wealth <- labelled(ELSA_ds_w1$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w1$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

```{r importOPAL1, echo=FALSE}
#val_labels(ELSA_ds_w1) <- NULL
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w1$wealth) <- ds_label_all
wealth <- ELSA_ds_w1
save(wealth, file = "../RData/w1/wealth.RData")
rm(wealth)
```








### Wave 2 

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_2_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_2_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local2, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**


```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w2$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w2$wealth <- as.integer(ELSA_ds_w2$wealth)
ELSA_ds_w2$wealth <- labelled(ELSA_ds_w2$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w2$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

```{r importOPAL2, echo=FALSE}
#val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w2$wealth) <- ds_label_all
wealth <- ELSA_ds_w2
save(wealth, file = "../RData/w2/wealth.RData")
rm(wealth)
```





### Wave 3

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_3_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_3_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local3, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w3$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w3$wealth <- as.integer(ELSA_ds_w3$wealth)
ELSA_ds_w3$wealth <- labelled(ELSA_ds_w3$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w3$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

```{r importOPAL3, echo=FALSE}
#val_labels(ELSA_ds_w3) <- NULL
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w3$wealth) <- ds_label_all
wealth <- ELSA_ds_w3
save(wealth, file = "../RData/w3/wealth.RData")
rm(wealth)
```



### Wave 4 

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_4_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_4_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local4, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**


```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w4$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w3$wealth <- as.integer(ELSA_ds_w3$wealth)
ELSA_ds_w4$wealth <- labelled(ELSA_ds_w4$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w4$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

```{r importOPAL4, echo=FALSE}
label(ELSA_ds_w4$wealth) <- ds_label_all
wealth <- ELSA_ds_w4
save(wealth, file = "../RData/w4/wealth.RData")
rm(wealth)
```






### Wave 5

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_5_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_5_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local5, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w5$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w3$wealth <- as.integer(ELSA_ds_w3$wealth)
ELSA_ds_w5$wealth <- labelled(ELSA_ds_w5$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w5$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```

```{r importOPAL5, echo=FALSE}
#val_labels(ELSA_ds_w5) <- NULL
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w5$wealth) <- ds_label_all
wealth <- ELSA_ds_w5
save(wealth, file = "../RData/w5/wealth.RData")
rm(wealth)
```





### Wave 6 

#### Study-specific variable description

| **Name** | `yq5_bu_s`| 
|-|-|
| **Label** | `quintiles of BU equivalised income (eqtotinc_bu_s)` | 
| **Table name** | `wave_6_financial_derived_variables` | 
| **Categories** | `categorical ordinal` |
| **Missing categories** | `-999 = not imputed (see user guide)` |
| | `-998 = non-sample member` |
| | `-995 = institutional respondent` |
| **Description** |  |

```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_wealth','ELSA.wave_6_financial_derived_variables',
                         variables=list('yq5_bu_s'), missings = TRUE)
ELSA_wealth <- opal.execute(o,'ELSA_wealth')
```

```{r local6, echo=FALSE}
vari <- ELSA_wealth$yq5_bu_s
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-999, -998, -995))[2], caption = "Type of missing")
ggplot(ELSA_wealth, aes(x=factor(yq5_bu_s))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is tha same than the study-specific variable, the missing values hve to be recoded as follows:

* `-999 into 999`
* `-998 into 996`
* `-995 into 993`
* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_wealth$id)
ELSA_ds_w6$wealth <- car::recode(ELSA_wealth$yq5_bu_s, "NA=999; -999=999; -998=996; -995=993")
ELSA_ds_w6$wealth <- as.integer(ELSA_ds_w6$wealth)
ELSA_ds_w6$wealth <- labelled(ELSA_ds_w6$wealth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$wealth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(wealth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
BeforeH <- table(ELSA_wealth$yq5_bu_s, useNA = 'ifany')
AfterH <- table(ELSA_ds_w6$wealth)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "NA->999")
kable(C)
```


```{r importOPAL6, echo=FALSE}
label(ELSA_ds_w6$wealth) <- ds_label_all
wealth <- ELSA_ds_w6
save(wealth, file = "../RData/w6/wealth.RData")
rm(wealth)
```










## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}



```





```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
}



```









# Quality estimation

Quintiles of BU equivalised income were taken from the original stud which included the value of the house, 
mortgages or loans on the house, and other real estate + asset + income variables.	

In ELSA all age-eligible household members and their spouses or partners were eligible for interviewing. 
ELSA does not impute values for non-responding spouses, so couple-level financial variable where one spouse 
is missing are left missing. For married or cohabiting couples, ELSA asks income and asset questions at the 
individual level or at the couple level, depending on whether the spouses kept their finances separate or 
together. If finances were kept together, one spouse was designated as the financial respondent, who answered 
the income and asset questions for the couple. If spouses kept finances separate each individual in the 
couple answered the income and asset questions for themselves. Pension questions are always asked at the 
individual level.
Some asset variables, namely, value of the house, mortgages or loans on the house, and other real estate, 
are asked of the housing respondent on behalf of the whole household. Note that it is a requirement that 
this individual is a respondent and thus must be otherwise eligible for interview, that is, be 50 years or 
older or the spouse or partner of someone 50 or older. Even though ELSA asks these questions at the 
full-household level, some of these measures are transformed to couple-level in the ELSA financial derived 
variable files by attributing the wealth only to the individuals who are named on the property 
(and their spouses) and where owners are in different couple units, dividing housing wealth accordingly. 
ELSA?s financial derived variables files provide asset and income variables at both the individual and the 
household level. Given our emphasis on harmonization, we combine the individual-level asset and income 
variables into couple-level variables for those variables for which the RAND HRS provides couple-level 
variables. 

ELSA does not impute values for non-responding spouses, so couple-level financial variable based on the 
combination of individual-level variables are left missing when one spouse is missing. 
More information on ELSA Finanical Variables and their imptuations can be found in Financial Derived 
Variables User Guide Waves 1 to 5 (2012).


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

