---
title: "Migration"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/migrationDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/migrationDS.R')
```


# Data process


## England

### Wave 1 

#### Study-specific variable description

| **Name** | `fqcbthr` | `countrr` | `pobr` |
|-|-|-|-|
| **Label** | `ELSA Country of birth collapsed into UK and elsewhere to avoid disclosure` | `HSE Country of birth collapsed into UK and elsewhere to avoid disclosure` | `HSE Country of birth collapsed into UK and elsewhere to avoid disclosure` |
| **Table name** | `wave_1_core_data_v3` | `wave_0_1999_data_prulaia2` | `ELSA.wave_0_1998_data` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable`<br/> `-8 = Don't Know` <br/> `-9 = Refusal` | `-1 = Not applicable`<br/> `-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |  |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1','ELSA.wave_1_core_data_v3', variables=list('fqcbthr'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')

opal.assign.table.tibble(o, 'ELSA_w1_1','ELSA.wave_0_1998_data', variables=list('pobr'), missings = TRUE)
ELSA_w1_1 <- opal.execute(o,'ELSA_w1_1')

opal.assign.table.tibble(o, 'ELSA_w1_2','ELSA.wave_0_1999_data_prulaia2', variables=list('countrr'), missings = TRUE)
ELSA_w1_2 <- opal.execute(o,'ELSA_w1_2')

ELSA_w1 <- ELSA_w1 %>% 
  left_join(ELSA_w1_1, by = "id") %>% 
  left_join(ELSA_w1_2, by = "id")

ELSA_w1$mig_w0 <- ELSA_w1$pobr
ELSA_w1$mig_w0[is.na(ELSA_w1$pobr)] <- ELSA_w1$countrr[is.na(ELSA_w1$pobr)]

ELSA_w1 <- select(ELSA_w1, id, fqcbthr, mig_w0)
```

We creared a variable `mig_w0` with the information of `pobr` and `countrr` because they ware complementary. 

```{r local w1, echo=F}
vbl <- ELSA_w1$fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- ELSA_w1$mig_w0
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(mig_w0))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.

**R script:**

```{r harmo w1}
ELSA_w1$mig_w0 <- car::recode(ELSA_w1$mig_w0, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998; NA=999 ")

ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$migration <- car::recode(ELSA_w1$fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w1$migration[(ELSA_ds_w1$migration %in% c(996,997,998,999))] <- ELSA_w1$mig_w0[(ELSA_ds_w1$migration %in% c(996,997,998,999))]

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_2_core_data_v4` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_core_data_v4', variables=list('fqcbthr'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

ELSA_w2 <- ELSA_w2 %>%
  left_join(ELSA_ds_w1, by = "id")
```

```{r local w2, echo=F}
vbl <- ELSA_w2$fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.


**R script:**

```{r harmo w2}

ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$migration <- car::recode(ELSA_w2$fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w2$migration[(ELSA_ds_w2$migration %in% c(996,997,998,999))] <- ELSA_w2$migration[(ELSA_ds_w2$migration %in% c(996,997,998,999))]

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}

```





### Wave 3

#### Study-specific variable description

| **Name** | `fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_3_elsa_data_v4` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |



```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4', variables=list('fqcbthr'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')

ELSA_w3 <- ELSA_w3 %>%
  left_join(ELSA_ds_w2, by = "id")
```

```{r local w3, echo=F}
vbl <- ELSA_w3$fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.


**R script:**

```{r harmo w3}

ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$migration <- car::recode(ELSA_w3$fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w3$migration[(ELSA_ds_w3$migration %in% c(996,997,998,999))] <- ELSA_w3$migration[(ELSA_ds_w3$migration %in% c(996,997,998,999))]
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}

```



### Wave 4

| **Name** | `fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_4_elsa_data_v3` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |



```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3', variables=list('fqcbthr'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')

ELSA_w4 <- ELSA_w4 %>%
  left_join(ELSA_ds_w3, by = "id")
```

```{r local w4, echo=F}
vbl <- ELSA_w4$fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.


**R script:**

```{r harmo w4}

ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$migration <- car::recode(ELSA_w4$fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w4$migration[(ELSA_ds_w4$migration %in% c(996,997,998,999))] <- ELSA_w4$migration[(ELSA_ds_w4$migration %in% c(996,997,998,999))]

```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w4, echo=F}

```


### Wave 5

#### Study-specific variable description

| **Name** | `fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_5_elsa_data_v4` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |

```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4', variables=list('fqcbthr'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')

ELSA_w5 <- ELSA_w5 %>%
  left_join(ELSA_ds_w4, by = "id")

```

```{r local w5, echo=F}
vbl <- ELSA_w5$fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.

**R script:**

```{r harmo w5}

ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$migration <- car::recode(ELSA_w5$fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w5$migration[(ELSA_ds_w5$migration %in% c(996,997,998,999))] <- ELSA_w5$migration[(ELSA_ds_w5$migration %in% c(996,997,998,999))]
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w5, echo=F}

```




### Wave 6

#### Study-specific variable description

| **Name** | `Fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_6_elsa_data_v2` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_elsa_data_v2', variables=list('Fqcbthr'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')

ELSA_w6 <- ELSA_w6 %>%
  left_join(ELSA_ds_w5, by = "id")

```

```{r local w6, echo=F}
vbl <- ELSA_w6$Fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(Fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.


**R script:**

```{r harmo w6}

ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$migration <- car::recode(ELSA_w6$Fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w6$migration[(ELSA_ds_w6$migration %in% c(996,997,998,999))] <- ELSA_w6$migration[(ELSA_ds_w6$migration %in% c(996,997,998,999))]
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w6, echo=F}

```

### Wave 7

#### Study-specific variable description

| **Name** | `fqcbthr` |
|-|-|
| **Label** | `Country of birth recoded into UK and non-UK` |
| **Table name** | `wave_1_core_data_v3` |
| **Categories** | `1 =  UK` <br/> `2 = Elsewhere outside of UK`  |
| **Missings** | `-1 = Not applicable`<br/>``-8 = Don't Know` <br/> `-9 = Refusal` |
| **Description** |  |


```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('Fqcbthr'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

ELSA_w7 <- ELSA_w7 %>%
  left_join(ELSA_ds_w6, by = "id")

```

```{r local w7, echo=F}

vbl <- ELSA_w7$Fqcbthr
vbl_mis <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_mis)[3], caption = names(ELSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = vbl_mis)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(Fqcbthr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `migration` from the study-specific variable it has to be recoded `fqcbthr` as follows:

* `1 into 0`
* `2 into 1`
* `-9 into 997`
* `-8 into 998`
* `-1 into 996`

The missing values are going to be completed with the information of the last wave.

**R script:**

```{r harmo w7}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$migration <- car::recode(ELSA_w7$Fqcbthr, "1 = 0; 2 = 1; -1 = 996; -9 = 997; -8 = 998 ")
ELSA_ds_w7$migration[(ELSA_ds_w7$migration %in% c(996,997,998,999))] <- ELSA_w7$migration[(ELSA_ds_w7$migration %in% c(996,997,998,999))]
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$migration
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(migration))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w7, echo=F}

```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
