---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## England

### Wave 1 

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_1_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o,'ELSA_w1_age','ELSA.wave_1_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_age <- opal.execute(o,'ELSA_w1_age')
vari <- ELSA_w1_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_age$id)
ELSA_ds_w1$age <- car::recode(ELSA_w1_age$age, "-8=998; NA=999")
ELSA_ds_w1$age <- labelled(ELSA_ds_w1$age, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Validation
```{r crosstabulation1, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w1$age!=ELSA_w1_age$age))
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$age <- car::recode(ELSA_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_2_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_age','ELSA.wave_2_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_age <- opal.execute(o,'ELSA_w2_age')
vari <- ELSA_w2_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w2_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`
* `NA into 999`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.


**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_age$id)
ELSA_ds_w2$age <- car::recode(ELSA_w2_age$age,"-8=998; NA=999")
ELSA_ds_w2$age <- labelled(ELSA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation2, echo=F, results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w2$age!=ELSA_w2_age$age))
```






```{r importOPAL2, echo=F}

#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$age <- car::recode(ELSA_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_3_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_age','ELSA.wave_3_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_age <- opal.execute(o,'ELSA_w3_age')
vari <- ELSA_w3_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w3_age, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("age") + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`
* `NA into 999`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_age$id)
ELSA_ds_w3$age <- car::recode(ELSA_w3_age$age, "-8=998; NA=999")
ELSA_ds_w3$age <- labelled(ELSA_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_w3_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Validation
```{r crosstabulation3, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w3$age!=ELSA_w3_age$age) )

cat("\r\nWe recoded one value -8 as 998.")
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$age <- car::recode(ELSA_m_ds_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_4_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_age','ELSA.wave_4_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_age <- opal.execute(o,'ELSA_w4_age')
vari <- ELSA_w4_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w4_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`
* `NA into 999`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_age$id)
ELSA_ds_w4$age <- car::recode(ELSA_w4_age$age, "-8=998; NA=999")
ELSA_ds_w4$age <- labelled(ELSA_ds_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)

```

#### Validation
```{r crosstabulation4, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w4$age!=ELSA_w4_age$age))
```





```{r importOPAL4, echo=F}

#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$age <- car::recode(ELSA_m_ds_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_5_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_age','ELSA.wave_5_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_age <- opal.execute(o,'ELSA_w5_age')
vari <- ELSA_w5_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w5_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`
* `NA into 999`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.


**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_age$id)
ELSA_ds_w5$age <- car::recode(ELSA_w5_age$age, "-8=998; NA=999")
ELSA_ds_w5$age <- labelled(ELSA_w5_age$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)

```

#### Validation
```{r crosstabulation5, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w5$age!=ELSA_w5_age$age))
```





```{r importOPAL5, echo=F}

#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$age <- car::recode(ELSA_m_ds_w5$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave_6_ifs_derived_variables` |
| **Missings** | `99 = age in years on or before 29/02/1912; -8 = Don't Know` |
| **Description** |  |


```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_age','ELSA.wave_6_ifs_derived_variables',
                         variables=list('age'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_age <- opal.execute(o,'ELSA_w6_age')
vari <- ELSA_w6_age$age
kable(Continuous_summary(vari, missing_values = c(99, -8))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99, -8))$summary, caption = "Summary")
ggplot(ELSA_w6_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `-8 "Do not know" into 998`
* `99 "age in years on or before 29/02/1912" into 99`
* `NA into 999`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_age$id)
ELSA_ds_w6$age <- car::recode(ELSA_w6_age$age, "-8=998; NA=999")
ELSA_ds_w6$age <- labelled(ELSA_ds_w6$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Validation
```{r crosstabulation6, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:",sum(ELSA_ds_w6$age!=ELSA_w6_age$age))
```





```{r importOPAL6, echo=F}

#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$age <- car::recode(ELSA_m_ds_w6$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `age: copy of indage/dhager` |
| **Table name** | `wave7_dv` |
| **Missings** | `99 = age in years on or before 29/02/1912` |
| **Description** |  |


```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_age','ELSA.wave7_dv', variables=list('age'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_age <- opal.execute(o,'ELSA_w7_age')
vari <- ELSA_w7_age$age
kable(Continuous_summary(vari, missing_values = c(99))[3], caption = "age")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
ggplot(ELSA_w7_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `99 "age in years on or before 29/02/1912" into 99`

As the study-specific variable is truncated in 90 years by 99 the value 99 is going to consider as a non missing value, 99 corresponds to the age to the people that was born before 29/02/1912, it means the people greater than 90 years old.

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_age$id)
ELSA_ds_w7$age <- car::recode(ELSA_w7_age$age, "NA=999")
ELSA_ds_w7$age <- labelled(ELSA_ds_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")+ xlim(20, 100)
```

#### Validation
```{r crosstabulation7, echo=F,results='asis'}
cat("The quantity of values of the harmonised variable which disagree with the initial variable is:", sum(ELSA_ds_w7$age!=ELSA_w7_age$age))
```


# Quality estimation
No comments.





```{r save, echo=FALSE}
age <- ELSA_ds_w1
save(age, file = "../RData/w1/age.RData")
rm(age)

age <- ELSA_ds_w2
save(age, file = "../RData/w2/age.RData")
rm(age)

age <- ELSA_ds_w3
save(age, file = "../RData/w3/age.RData")
rm(age)

age <- ELSA_ds_w4
save(age, file = "../RData/w4/age.RData")
rm(age)

age <- ELSA_ds_w5
save(age, file = "../RData/w5/age.RData")
rm(age)

age <- ELSA_ds_w6
save(age, file = "../RData/w6/age.RData")
rm(age)

age <- ELSA_ds_w7
save(age, file = "../RData/w7/age.RData")
rm(age)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
