---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```

<!-- ########################################################## --> 

# Data process

## England 

### Wave 1 

#### Study-specific variable description

| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable`|
| **Table name** |`wave_1_core_data_v3`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_sex','ELSA.wave_1_core_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w1_sex <- opal.execute(o,'ELSA_w1_sex')
```

```{r local1, echo=FALSE}
vari <- ELSA_w1_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w1_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_sex$id)
ELSA_ds_w1$sex <- car::recode(ELSA_w1_sex$indsex, "1=1; 2=0")
ELSA_ds_w1$sex <- labelled(ELSA_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w1$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(ELSA_ds_w1$sex)
BeforeH <- table(ELSA_w1_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 2

#### Study-specific variable description

| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable. Priority: Disex, Dhsex`|
| **Table name** |`wave_2_core_data_v4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-1 = Not applicable`|
| **Description** |  |



```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w2_sex','ELSA.wave_2_core_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w2_sex <- opal.execute(o,'ELSA_w2_sex')
```

```{r local2, echo=FALSE}
vari <- ELSA_w2_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w2_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `-9 "Refusal" into 997` 
* `-8 "Don't Know" into 998` 
* `-1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_sex$id)
ELSA_ds_w2$sex <- car::recode(ELSA_w2_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w2$sex <- labelled(ELSA_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w2$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(ELSA_ds_w2$sex)
BeforeH <- table(ELSA_w2_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```





### Wave 3

#### Study-specific variable description

| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable. Priority: Disex, Dhsex`|
| **Table name** |`wave_3_elsa_data_v4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-1 = Not applicable`|
| **Description** |  |


```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_sex','ELSA.wave_3_elsa_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w3_sex <- opal.execute(o,'ELSA_w3_sex')
```

```{r local3, echo=FALSE}
vari <- ELSA_w3_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w3_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `-9 "Refusal" into 997` 
* `-8 "Don't Know" into 998` 
* `-1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_sex$id)
ELSA_ds_w3$sex <- car::recode(ELSA_w3_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w3$sex <- labelled(ELSA_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w3$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(ELSA_ds_w3$sex)
BeforeH <- table(ELSA_w3_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```



### Wave 4

#### Study-specific variable description


| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable. Priority: Disex, Dhsex`|
| **Table name** |`wave_4_elsa_data_v3`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w4_sex','ELSA.wave_4_elsa_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w4_sex <- opal.execute(o,'ELSA_w4_sex')
```

```{r local4, echo=FALSE}
vari <- ELSA_w4_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w4_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_sex$id)
ELSA_ds_w4$sex <- car::recode(ELSA_w4_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w4$sex <- labelled(ELSA_ds_w4$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w4$sex) <- ds_label


```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
AfterH <- table(ELSA_ds_w4$sex)
BeforeH <- table(ELSA_w4_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 5

#### Study-specific variable description

| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable. Priority: Disex, Dhsex`|
| **Table name** |`wave_5_elsa_data_v4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_sex','ELSA.wave_5_elsa_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w5_sex <- opal.execute(o,'ELSA_w5_sex')
```

```{r local5, echo=FALSE}
vari <- ELSA_w5_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w5_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_sex$id)
ELSA_ds_w5$sex <- car::recode(ELSA_w5_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w5$sex <- labelled(ELSA_ds_w5$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w5$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
AfterH <- table(ELSA_ds_w5$sex)
BeforeH <- table(ELSA_w5_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 6

#### Study-specific variable description

| **Name** | `indsex`|
|-|-|
| **Label** | `Definitive sex variable. Priority: Disex, Dhsex`|
| **Table name** |`wave_6_elsa_data_v2`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w6_sex','ELSA.wave_6_elsa_data_v2',
                         variables=list('indsex'), missings = TRUE)
ELSA_w6_sex <- opal.execute(o,'ELSA_w6_sex')
```

```{r local6, echo=FALSE}
vari <- ELSA_w6_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w6_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_sex$id)
ELSA_ds_w6$sex <- car::recode(ELSA_w6_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w6$sex <- labelled(ELSA_ds_w6$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w6$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
AfterH <- table(ELSA_ds_w6$sex)
BeforeH <- table(ELSA_w6_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```






### Wave 7

#### Study-specific variable description


| **Name** | `indsex` |
|-|-|
| **Label** | `Definitive sex variable: priority disex, dhsex` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign w7, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('indsex'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=FALSE}

vari <- ELSA_w7$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'indsex') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`

**R script:**

```{r harmo w7, echo=TRUE}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$sex <- car::recode(ELSA_w7$indsex, "1=1; 2=0")
ELSA_ds_w7$sex <- labelled(ELSA_ds_w7$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w7$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}

vari <- ELSA_ds_w7$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")

```

#### Validation

```{r crosstabulation w7, echo=FALSE}

AfterH <- table(ELSA_ds_w7$sex)
BeforeH <- table(ELSA_w7$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)

```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation




```{r, echo=F}

ELSA <- full_join(ELSA_ds_w1[which(!ELSA_ds_w1$sex %in% miss_values_vector),],ELSA_ds_w2[which(!ELSA_ds_w2$sex %in% miss_values_vector),], by="id", suffix=c(".w1",".w2"))
ELSA <- full_join(ELSA,ELSA_ds_w3[which(!ELSA_ds_w3$sex %in% miss_values_vector),], by="id")
ELSA <- full_join(ELSA,ELSA_ds_w4[which(!ELSA_ds_w4$sex %in% miss_values_vector),], by="id", suffix=c(".w3",".w4"))
ELSA <- full_join(ELSA,ELSA_ds_w5[which(!ELSA_ds_w5$sex %in% miss_values_vector),], by="id")
ELSA <- full_join(ELSA,ELSA_ds_w6[which(!ELSA_ds_w6$sex %in% miss_values_vector),], by="id", suffix=c(".w5",".w6"))
ELSA <- full_join(ELSA,ELSA_ds_w7[which(!ELSA_ds_w7$sex %in% miss_values_vector),], by="id")
ELSA$var <- apply(ELSA[,-1],1,function(x) var(x, na.rm = T))

ELSstr <- paste("There are ",length(ELSA$id[which(ELSA$var!=0)])," individuals with sex data changing across waves.")

kable(frq(ELSA$var==0), align = 'c', caption = ELSstr)
kable(ELSA[which(ELSA$var!=0),], align = 'c')

```

We do not anything thereon.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```