---
title: "Sex"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->


```{r setup, include=FALSE, echo=FALSE}
source("../../setup_iago.r")
```


```{r lab, echo=FALSE}
ds_label <- "Sex"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `sex`
* Variable label: `biological sex`
* Variable description: `participant's biological sex`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | female
1        | male

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## England 

### Wave 1 

#### Study-specific variable description

* Name: `indsex`
* Label: `Definitive sex variable`
* Categories: 
    + `1.0 = Male`
    + `2.0 = Female`
* Description:

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_sex','ELSA.wave_1_core_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w1_sex <- opal.execute(o,'ELSA_w1_sex')
```

```{r local1, echo=FALSE}
vari <- ELSA_w1_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w1_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_sex$id)
ELSA_ds_w1$sex <- car::recode(ELSA_w1_sex$indsex, "1=1; 2=0")
ELSA_ds_w1$sex <- labelled(ELSA_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w1$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(ELSA_ds_w1$sex)
BeforeH <- table(ELSA_w1_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 2

#### Study-specific variable description

* Name: `indsex`
* Label: `Definitive sex variable. Priority: Disex, Dhsex`
* Categories: 
    + `1 = Male`
    + `2 = Female`
* Missings
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-1 = Not applicable`
* Description:

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w2_sex','ELSA.wave_2_core_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w2_sex <- opal.execute(o,'ELSA_w2_sex')
```

```{r local2, echo=FALSE}
vari <- ELSA_w2_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w2_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `-9 "Refusal" into 997` 
* `-8 "Don't Know" into 998` 
* `-1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_sex$id)
ELSA_ds_w2$sex <- car::recode(ELSA_w2_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w2$sex <- labelled(ELSA_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w2$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(ELSA_ds_w2$sex)
BeforeH <- table(ELSA_w2_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```


```{r importOPAL2, echo=FALSE}
val_labels(ELSA_ds_w2) <- NULL
opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$sex <- car::recode(ELSA_m_ds_w2$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description

* Name: `indsex`
* Label: `Definitive sex variable. Priority: Disex, Dhsex`
* Categories: 
  + `1 = Male`
  + `2 = Female`
* Missings
  + `-9 = Refusal`
  + `-8 = Don't Know`
  + `-1 = Not applicable`
* Description:
```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_sex','ELSA.wave_3_elsa_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w3_sex <- opal.execute(o,'ELSA_w3_sex')
```

```{r local3, echo=FALSE}
vari <- ELSA_w3_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w3_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `-9 "Refusal" into 997` 
* `-8 "Don't Know" into 998` 
* `-1 "Not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_sex$id)
ELSA_ds_w3$sex <- car::recode(ELSA_w3_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w3$sex <- labelled(ELSA_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w3$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Sex") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(ELSA_ds_w3$sex)
BeforeH <- table(ELSA_w3_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```



### Wave 4

#### Study-specific variable description


* Name: `indsex`
* Label: `Definitive sex variable. Priority: Disex, Dhsex`
* Categories: 
   + `1 = Male`
   + `2 = Female`
* Description:
```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w4_sex','ELSA.wave_4_elsa_data_v3',
                         variables=list('indsex'), missings = TRUE)
ELSA_w4_sex <- opal.execute(o,'ELSA_w4_sex')
```

```{r local4, echo=FALSE}
vari <- ELSA_w4_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w4_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_sex$id)
ELSA_ds_w4$sex <- car::recode(ELSA_w4_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w4$sex <- labelled(ELSA_ds_w4$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w4$sex) <- ds_label


```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
AfterH <- table(ELSA_ds_w4$sex)
BeforeH <- table(ELSA_w4_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 5

#### Study-specific variable description

* Name: `indsex`
* Label: `Definitive sex variable. Priority: Disex, Dhsex`
* Categories: 
  + `1.0 = Male`
  + `2.0 = Female`
* Description:
```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_sex','ELSA.wave_5_elsa_data_v4',
                         variables=list('indsex'), missings = TRUE)
ELSA_w5_sex <- opal.execute(o,'ELSA_w5_sex')
```

```{r local5, echo=FALSE}
vari <- ELSA_w5_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w5_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_sex$id)
ELSA_ds_w5$sex <- car::recode(ELSA_w5_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w5$sex <- labelled(ELSA_ds_w5$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w5$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
AfterH <- table(ELSA_ds_w5$sex)
BeforeH <- table(ELSA_w5_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```




### Wave 6

#### Study-specific variable description

* Name: `indsex`
* Label: `Definitive sex variable. Priority: Disex, Dhsex`
* Categories: 
  + `1 = Male`
  + `2 = Female`
* Description:
```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w6_sex','ELSA.wave_6_elsa_data_v2',
                         variables=list('indsex'), missings = TRUE)
ELSA_w6_sex <- opal.execute(o,'ELSA_w6_sex')
```

```{r local6, echo=FALSE}
vari <- ELSA_w6_sex$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w6_sex, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_sex$id)
ELSA_ds_w6$sex <- car::recode(ELSA_w6_sex$indsex, "1=1; 2=0;-9=997; -8=998")
ELSA_ds_w6$sex <- labelled(ELSA_ds_w6$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w6$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
AfterH <- table(ELSA_ds_w6$sex)
BeforeH <- table(ELSA_w6_sex$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```






### Wave 7

#### Study-specific variable description


| **Name** | `indsex` |
|-|-|
| **Label** | `Definitive sex variable: priority disex, dhsex` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |


```{r assign w7, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data', variables=list('indsex'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=FALSE}

vari <- ELSA_w7$indsex
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'indsex') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(indsex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Male" into 1`
* `2 "Female" into 0`

**R script:**

```{r harmo w7, echo=TRUE}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$sex <- car::recode(ELSA_w7$indsex, "1=1; 2=0")
ELSA_ds_w7$sex <- labelled(ELSA_ds_w7$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w7$sex) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}

vari <- ELSA_ds_w7$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sex") + ylab("Frequency")

```

#### Validation

```{r crosstabulation w7, echo=FALSE}

AfterH <- table(ELSA_ds_w7$sex)
BeforeH <- table(ELSA_w7$indsex)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)

```





# Quality estimation
No comments.

```{r save, echo=FALSE}
sex <- ELSA_ds_w1
save(sex, file = "../RData/w1/sex.RData")
rm(sex)

sex <- ELSA_ds_w2
save(sex, file = "../RData/w2/sex.RData")
rm(sex)

sex <- ELSA_ds_w3
save(sex, file = "../RData/w3/sex.RData")
rm(sex)

sex <- ELSA_ds_w4
save(sex, file = "../RData/w4/sex.RData")
rm(sex)

sex <- ELSA_ds_w5
save(sex, file = "../RData/w5/sex.RData")
rm(sex)

sex <- ELSA_ds_w6
save(sex, file = "../RData/w6/sex.RData")
rm(sex)

sex <- ELSA_ds_w7
save(sex, file = "../RData/w7/sex.RData")
rm(sex)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```