---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("../../setup_iago.r")
```
```{r lab, echo=FALSE}
ds_label <- "The current marital status of the participant"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

 

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_ms','ELSA.wave_1_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local1,  echo=FALSE}
ELSA_w1_ms <- opal.execute(o,'ELSA_w1_ms')
vari <- ELSA_w1_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w1_ms$marstat, missing_values = NA)
ggplot(ELSA_w1_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_ms$id)
ELSA_ds_w1$marital_status <- car::recode(ELSA_w1_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w1$marital_status <- labelled(ELSA_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w1$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- ELSA_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
AfterH <- table(ELSA_ds_w1$marital_status)
BeforeH <- table(ELSA_w1_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```

 
 
### Wave 2

#### Study-specific variable description

 

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w2_ms','ELSA.wave_2_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local2,  echo=FALSE}
ELSA_w2_ms <- opal.execute(o,'ELSA_w2_ms')
vari <- ELSA_w2_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w2_ms$marstat, missing_values = NA)
ggplot(ELSA_w2_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_ms$id)
ELSA_ds_w2$marital_status <- car::recode(ELSA_w2_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w2$marital_status <- labelled(ELSA_ds_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w2$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- ELSA_ds_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
AfterH <- table(ELSA_ds_w2$marital_status)
BeforeH <- table(ELSA_w2_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```

 




### Wave 3

#### Study-specific variable description

 

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_ms','ELSA.wave_3_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local3,  echo=FALSE}
ELSA_w3_ms <- opal.execute(o,'ELSA_w3_ms')
vari <- ELSA_w3_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w3_ms$marstat, missing_values = NA)
ggplot(ELSA_w3_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo3,   echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_ms$id)
ELSA_ds_w3$marital_status <- car::recode(ELSA_w3_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w3$marital_status <- labelled(ELSA_ds_w3$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w3$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- ELSA_ds_w3$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
AfterH <- table(ELSA_ds_w3$marital_status)
BeforeH <- table(ELSA_w3_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```

 

### Wave 4

#### Study-specific variable description

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign4,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w4_ms','ELSA.wave_4_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local4,  echo=FALSE}
ELSA_w4_ms <- opal.execute(o,'ELSA_w4_ms')
vari <- ELSA_w4_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w4_ms$marstat, missing_values = NA)
ggplot(ELSA_w4_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo4,   echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_ms$id)
ELSA_ds_w4$marital_status <- car::recode(ELSA_w4_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w4$marital_status <- labelled(ELSA_ds_w4$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- ELSA_ds_w4$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
label(ELSA_ds_w4$marital_status) <- ds_label

```

#### Validation
```{r crosstabulation4,  echo=FALSE}
AfterH <- table(ELSA_ds_w4$marital_status)
BeforeH <- table(ELSA_w4_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```

 
 


### Wave 5

#### Study-specific variable description

 

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign5,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_ms','ELSA.wave_5_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local5,  echo=FALSE}
ELSA_w5_ms <- opal.execute(o,'ELSA_w5_ms')
vari <- ELSA_w5_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w5_ms$marstat, missing_values = NA)
ggplot(ELSA_w5_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo5,   echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_ms$id)
ELSA_ds_w5$marital_status <- car::recode(ELSA_w5_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w5$marital_status <- labelled(ELSA_ds_w5$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w5$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript5,  echo=FALSE}
vari <- ELSA_ds_w5$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5,  echo=FALSE}
AfterH <- table(ELSA_ds_w5$marital_status)
BeforeH <- table(ELSA_w5_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```

 
 

 
### Wave 6

#### Study-specific variable description

 

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1 = married (inc civ pship 06 onwards)`
    + `2 = cohabiting`
    + `3 = single, never married`
    + `4 = widowed`
    + `5 = divorced`
    + `6 = separated`

* Description: 
```{r assign6,  echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w6_ms','ELSA.wave_6_ifs_derived_variables',
                         variables=list('marstat'), missings = TRUE)
```

```{r local6,  echo=FALSE}
ELSA_w6_ms <- opal.execute(o,'ELSA_w6_ms')
vari <- ELSA_w6_ms$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w6_ms$marstat, missing_values = NA)
ggplot(ELSA_w6_ms, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`
* `NA into 999`

**R script:**

```{r harmo6,   echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_ms$id)
ELSA_ds_w6$marital_status <- car::recode(ELSA_w6_ms$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w6$marital_status <- labelled(ELSA_ds_w6$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w6$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript6,  echo=FALSE}
vari <- ELSA_ds_w6$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6,  echo=FALSE}
AfterH <- table(ELSA_ds_w6$marital_status)
BeforeH <- table(ELSA_w6_ms$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)
```






### Wave 7

#### Study-specific variable description

 

| **Name** | `marstat` |
|-|-|
| **Label** | `marital status - couple1 combined with dimar` |
| **Table name** | `wave7_dv` |
| **Categories** |`1 = married (inc civ pship 06 onwards)`<br/>`2 = cohabiting`<br/>`3 = single, never married`<br/>`4 = widowed`<br/>`5 = divorced`<br/>`6 = separated`|
| **Description** |  |

```{r assign w7,  echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w7_0','ELSA.wave7_dv', variables=list('marstat'), missings = TRUE)
ELSA_w7_0 <- opal.execute(o,'ELSA_w7_0')
opal.assign.table.tibble(o, 'ELSA_w7_id','ELSA.wave_7_elsa_data', variables=list('idahhw7'), missings = TRUE)
ELSA_w7_id <- opal.execute(o,'ELSA_w7_id')
ELSA_w7 <- left_join(ELSA_w7_id[,1],ELSA_w7_0, by="id")

```

```{r local w7,  echo=FALSE}

vari <- ELSA_w7$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = 'marstat') 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 married (inc civ pship 06 onwards) into 2`
* `keep 2 cohabiting into 2`
* `3 single, never married into 1`
* `keep 4 widowed into 4`
* `5 divorced into 2`
* `6 separated into 3`


**R script:**

```{r harmo w7,   echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$marital_status <- car::recode(ELSA_w7$marstat, "1=2; 3=1; 5=3; 6=3")
ELSA_ds_w7$marital_status <- labelled(ELSA_ds_w7$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w7$marital_status) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript w7,  echo=FALSE}
vari <- ELSA_ds_w7$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7,  echo=FALSE}

AfterH <- table(ELSA_ds_w7$marital_status)
BeforeH <- table(ELSA_w7$marstat)
BeforeH <- c(BeforeH[3], sum(BeforeH[c(1, 2)]), sum(BeforeH[c(5,6)]), BeforeH[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3->1","(1,2)->2", "(5,6)->3", "4")
kable(C)

```






# Quality estimation

No comments

```{r save, echo=FALSE}
marital_status <- ELSA_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w2
save(marital_status, file = "../RData/w2/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w3
save(marital_status, file = "../RData/w3/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w4
save(marital_status, file = "../RData/w4/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w5
save(marital_status, file = "../RData/w5/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w6
save(marital_status, file = "../RData/w6/marital_status.RData")
rm(marital_status)

marital_status <- ELSA_ds_w7
save(marital_status, file = "../RData/w7/marital_status.RData")
rm(marital_status)
```


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```