---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE, echo=FALSE}
source("../../setup_iago.r")
```
```{r lab, echo=FALSE}
ds_label <- "Highest level of formal education achieved"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Enland

### Wave 1 

#### Study-specific variable description

 

* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`

* Description:
```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w1_educ','ELSA.wave_1_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local1, echo=FALSE}
ELSA_w1_educ <- opal.execute(o,'ELSA_w1_educ')
vari <- ELSA_w1_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_educ$edqual, missing_values = c(-9, -8,-2, -1))
ggplot(ELSA_w1_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_educ$id)
ELSA_ds_w1$education <- car::recode(ELSA_w1_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w1$education <- labelled(ELSA_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w1$education) <- ds_label
```


#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ELSA_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(ELSA_ds_w1$education)
BeforeH <- table(ELSA_w1_educ$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]),BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3", "-1->996", "-9->997", "-8->998", "6->999")
kable(C)
```

 
 
### Wave 2

#### Study-specific variable description

 

* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`
* Description:
```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w2_educ','ELSA.wave_2_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local2, echo=FALSE}
ELSA_w2_educ <- opal.execute(o,'ELSA_w2_educ')
vari <- ELSA_w2_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_educ$edqual, missing_values = c(-9, -8, -2, -1))
ggplot(ELSA_w2_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_educ$id)
ELSA_ds_w2$education <- car::recode(ELSA_w2_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w2$education <- labelled(ELSA_ds_w2$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w2$education) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ELSA_ds_w2$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
AfterH <- table(ELSA_ds_w2$education)
BeforeH <- table(ELSA_w2_educ$edqual)
BeforeH <- c(BeforeH[11], sum(BeforeH[c(6,7,8,9)]), BeforeH[5], BeforeH[3], BeforeH[4], BeforeH[1], BeforeH[2], BeforeH[10])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-1->996", "-9->997", "-8->998", "6->999")
kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

 

* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`
* Description:
```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_educ','ELSA.wave_3_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local3, echo=FALSE}
ELSA_w3_educ <- opal.execute(o,'ELSA_w3_educ')
vari <- ELSA_w3_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_educ$edqual, missing_values = c(-9, -8,-2, -1))
ggplot(ELSA_w3_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_educ$id)
ELSA_ds_w3$education <- car::recode(ELSA_w3_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w3$education <- labelled(ELSA_ds_w3$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w3$education) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(ELSA_ds_w3$education)
BeforeH <- table(ELSA_w3_educ$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]), BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-9->997", "-8->998", "6->999")
kable(C)
```

 
 
### Wave 4

#### Study-specific variable description

 
* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`
* Description:
```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w4_educ','ELSA.wave_4_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local4, echo=FALSE}
ELSA_w4_educ <- opal.execute(o,'ELSA_w4_educ')
vari <- ELSA_w4_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_educ$edqual, missing_values = c(-9, -8,-2, -1))
ggplot(ELSA_w4_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_educ$id)
ELSA_ds_w4$education <- car::recode(ELSA_w4_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w4$education <- labelled(ELSA_ds_w4$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w4$education) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- ELSA_ds_w4$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=FALSE}
AfterH <- table(ELSA_ds_w4$education)
BeforeH <- table(ELSA_w4_educ$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]), BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-9->997", "-8->998", "6->999")
kable(C)
```

 
 

### Wave 5

#### Study-specific variable description

 

* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`
* Description:
```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w5_educ','ELSA.wave_5_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local5, echo=FALSE}
ELSA_w5_educ <- opal.execute(o,'ELSA_w5_educ')
vari <- ELSA_w5_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_educ$edqual, missing_values = c(-9, -8,-2, -1))
ggplot(ELSA_w5_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_educ$id)
ELSA_ds_w5$education <- car::recode(ELSA_w5_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w5$education <- labelled(ELSA_ds_w5$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w5$education) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- ELSA_ds_w5$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=FALSE}
AfterH <- table(ELSA_ds_w5$education)
BeforeH <- table(ELSA_w5_educ$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]), BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-9->997", "-8->998", "6->999")
kable(C)
```

 
 

### Wave 6

#### Study-specific variable description

 

* Name: `edqual`
* Label: `educational qualification - info merged from current and previous waves`
* Categories: 
    + `1 = NVQ4/NVQ5/Degree or equiv`
    + `2 = Higher ed below degree`
    + `3 = NVQ3/GCE A Level equiv`
    + `4 = NVQ2/GCE O Level equiv`
    + `5 = NVQ1/CSE other grade equiv`
    + `6 = Foreign/other`
    + `7 = No qualification`
* Missings: 
    + `-9 = refusal`
    + `-8 = don't know`
    + `-2 = not asked`
    + `-1 = not applicable`
* Description:
```{r assign6, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w6_educ','ELSA.wave_6_ifs_derived_variables',
                         variables=list('edqual'), missings = TRUE)
```

```{r local6, echo=FALSE}
ELSA_w6_educ <- opal.execute(o,'ELSA_w6_educ')
vari <- ELSA_w6_educ$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_educ$edqual, missing_values = c(-9, -8,-2, -1))
ggplot(ELSA_w6_educ, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_educ$id)
ELSA_ds_w6$education <- car::recode(ELSA_w6_educ$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w6$education <- labelled(ELSA_ds_w6$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w6$education) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=FALSE}
vari <- ELSA_ds_w6$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=FALSE}
AfterH <- table(ELSA_ds_w6$education)
BeforeH <- table(ELSA_w6_educ$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]), BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-9->997", "-8->998", "6->999")
kable(C)
```






### Wave 7

#### Study-specific variable description

 


| **Name** | `edqual` |
|-|-|
| **Label** | `educational qualification - info merged from current and previous waves` |
| **Table name** | `wave7_dv` |
| **Categories** |`1 = NVQ4/NVQ5/Degree or equiv`<br/>`2 = Higher ed below degree`<br/>`3 = NVQ3/GCE A Level equiv`<br/>`4 = NVQ2/GCE O Level equiv`<br/>`5 = NVQ1/CSE other grade equiv`<br/>`6 = Foreign/other`<br/>`7 = No qualification`|
| **Missings** |`-9 = refusal`<br/>`-8 = don't know`<br/>`-2 = not asked`<br/>`-1 = not applicable`|
| **Description** |  |

```{r assign7, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv',  variables=list('edqual'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local7, echo=FALSE}
vari <- ELSA_w7$edqual
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[3], caption = 'edqual') 
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9, -8,-2, -1))[2], caption = "Type of missing")
ggplot(ELSA_w7, aes(x=factor(edqual))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable has to be recoded as follows:

* `1 "NVQ4/NVQ5/Degree or equiv" into 3`
* `keep "Higher ed below degree" into 2`
* `3 "NVQ3/GCE A Level equiv" into 2`
* `4 "NVQ2/GCE O Level equiv" into 2`
* `5 "NVQ1/CSE other grade equiv" into 2`
* `6 "Foreign/other" into 999`
* `7 "No qualification" into 0`
* `-9 "refusal" into 997`
* `-8 "don't know" into 998`
* `-2 "not asked" into 995`
* `-1 "not applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$education <- car::recode(ELSA_w7$edqual, "1=3; 3=2; 4=2; 5=2; 6=999; 7=0; -9=997; -8=998;-2=995; -1=996;  NA=999")
ELSA_ds_w7$education <- labelled(ELSA_ds_w7$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
label(ELSA_ds_w7$education) <- ds_label

```

#### Statistical description of the new harmonised variable
```{r descript7, echo=FALSE}
vari <- ELSA_ds_w7$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=FALSE}
AfterH <- table(ELSA_ds_w7$education)
BeforeH <- table(ELSA_w7$edqual)
BeforeH <- c(BeforeH[10], sum(BeforeH[c(5,6,7,8)]), BeforeH[4], BeforeH[3], BeforeH[1], BeforeH[2], BeforeH[9])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("7->0","(2,3,4,5)->2", "1->3","-2->995", "-9->997", "-8->998", "6->999")
kable(C)
```



 
# Quality estimation

No comments

```{r save, echo=FALSE}
education <- ELSA_ds_w1
save(education, file = "../RData/w1/education.RData")
rm(education)

education <- ELSA_ds_w2
save(education, file = "../RData/w2/education.RData")
rm(education)

education <- ELSA_ds_w3
save(education, file = "../RData/w3/education.RData")
rm(education)

education <- ELSA_ds_w4
save(education, file = "../RData/w4/education.RData")
rm(education)

education <- ELSA_ds_w5
save(education, file = "../RData/w5/education.RData")
rm(education)

education <- ELSA_ds_w6
save(education, file = "../RData/w6/education.RData")
rm(education)

education <- ELSA_ds_w7
save(education, file = "../RData/w7/education.RData")
rm(education)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```