---
title: "Non paid work"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/nonpaid_workDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/nonpaid_workDS.R')
```





# Data process




## England




### Wave 1

#### Study-specific variable description

| **Name** | `wpdes` |
|-|-|
| **Label** | `Which one of these would you say best describes your current situation?` |
| **Table name** | `wave_1_core_data_v3` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable 01 to 06 or 96`<br/>`86 = Irrelevant response - not codeable 01 to 06 or 96`<br/>`95 = Other (SPECIFY)`<br/>`96 = SPONTANEOUS : Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o,'ELSA_w1','ELSA.wave_1_core_data_v3',variables=list('wpdes'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')

```

```{r local w1, echo=F}

vbl <- ELSA_w1$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w1}

ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$nonpaid_work <- car::recode(ELSA_w1$wpdes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ELSA_ds_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ELSA_ds_w1$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w1$wpdes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("-8")]),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","-8->998","85,86,95->999")
kable(C)

```




### Wave 2

#### Study-specific variable description

| **Name** | `wpdes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_2_core_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable 01 to 06 or 96`<br/>`86 = Irrelevant response - not codeable 01 to 06 or 96`<br/>`95 = Other`<br/>`96 = SPONTANEOUS : Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o,'ELSA_w2','ELSA.wave_2_core_data_v4',variables=list('wpdes'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')

```

```{r local w2, echo=F}

vbl <- ELSA_w2$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w2}

ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$nonpaid_work <- car::recode(ELSA_w2$wpdes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ELSA_ds_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w2, echo=F}

AfterH <- table(ELSA_ds_w2$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w2$wpdes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("-8")]),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","-8->998","85,86,95->999")
kable(C)

```




### Wave 3

#### Study-specific variable description

| **Name** | `wpdes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_3_elsa_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`95 = Other (SPECIFY)`<br/>`96 = SPONTANEOUS : Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o,'ELSA_w3','ELSA.wave_3_elsa_data_v4',variables=list('wpdes'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')

```

```{r local w3, echo=F}

vbl <- ELSA_w3$wpdes
vbl_miss <- c(-1,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `95 into 999`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w3}

ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$nonpaid_work <- car::recode(ELSA_w3$wpdes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(95) = 999; -1 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ELSA_ds_w3$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ELSA_ds_w3$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w3$wpdes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("-8")]),sum(X[c("95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","-8->998","95->999")
kable(C)

```




### Wave 4

#### Study-specific variable description

| **Name** | `wpdes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_4_elsa_data_v3` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer - not codeable`<br/>`86 = Code86`<br/>`95 = Other`<br/>`96 = Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = CAPI/Interview error`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w4, echo=F}

opal.assign.table.tibble(o,'ELSA_w4','ELSA.wave_4_elsa_data_v3',variables=list('wpdes'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')

```

```{r local w4, echo=F}

vbl <- ELSA_w4$wpdes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-2 into 991`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w4}

ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$nonpaid_work <- car::recode(ELSA_w4$wpdes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -2 = 991; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- ELSA_ds_w4$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w4, echo=F}

AfterH <- table(ELSA_ds_w4$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w4$wpdes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("-8")]),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","-8->998","85,86,95->999")
kable(C)

```




### Wave 5

#### Study-specific variable description

| **Name** | `wpdes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_5_elsa_data_v4` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w5, echo=F}

opal.assign.table.tibble(o,'ELSA_w5','ELSA.wave_5_elsa_data_v4',variables=list('wpdes'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')

```

```{r local w5, echo=F}

vbl <- ELSA_w5$wpdes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'wpdes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(wpdes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w5}

ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$nonpaid_work <- car::recode(ELSA_w5$wpdes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- ELSA_ds_w5$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w5, echo=F}

AfterH <- table(ELSA_ds_w5$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w5$wpdes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("-8")]),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","-8->998","85,86,95->999")
kable(C)

```




### Wave 6

#### Study-specific variable description

| **Name** | `WpDes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_6_elsa_data_v2` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w6, echo=F}

opal.assign.table.tibble(o,'ELSA_w6','ELSA.wave_6_elsa_data_v2',variables=list('WpDes'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')

```

```{r local w6, echo=F}

vbl <- ELSA_w6$WpDes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'WpDes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(WpDes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w6}

ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$nonpaid_work <- car::recode(ELSA_w6$WpDes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ELSA_ds_w6$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ELSA_ds_w6$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w6$WpDes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("-9")]),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","-9->997","85,86,95->999")
kable(C)

```





### Wave 7

| **Name** | `WpDes` |
|-|-|
| **Label** | `Best description of current situation` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** |`1 = Retired`<br/>`2 = Employed`<br/>`3 = Self-employed`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`85 = Other answer`<br/>`86 = Irrelevant response`<br/>`95 = Other (SPECIFY)`<br/>`96 = Semi-retired`|
| **Missings** |`-1 = Not applicable`<br/>`-2 = Schedule not applicable`<br/>`-8 = Don't Know`<br/>`-9 = Refusal`|
| **Description** |  |


```{r assign w7, echo=F}

opal.assign.table.tibble(o,'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('WpDes'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local w7, echo=F}

vbl <- ELSA_w7$WpDes
vbl_miss <- c(-1,-2,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'WpDes')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(WpDes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `6 into 1`
* `1,2,3,4,5,96 into 996`
* `85,86,95 into 999`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997`

**R script:**

```{r harmo w7}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$nonpaid_work <- car::recode(ELSA_w7$WpDes, "c(6) = 1; c(1,2,3,4,5,96) = 996; c(85,86,95) = 999; -1 = 996; -2 = 996; -8 = 998; -9 = 997")

```

#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w7, echo=F}

AfterH <- table(ELSA_ds_w7$nonpaid_work, useNA = "ifany")
X <- table(ELSA_w7$WpDes, useNA = "ifany")
BeforeH <- c(sum(X[c("6")],na.rm=T),sum(X[c("1","2","3","4","5","96")],na.rm=T),sum(X[c("85","86","95")],na.rm=T))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("6->1","1,2,3,4,5,96->996","85,86,95->999")
kable(C)

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.



```{r summ}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label", names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","nonpaid_work")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","nonpaid_work")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste0(v.dbb,dbb[,ind+1])
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  nonpaid_work <- l.hds[[index]]
  save(nonpaid_work, file = paste0(datafolder,names(l.hds)[index],"/nonpaid_work.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```



