---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process

```{r HAPIEE categories}
HAPIEE0_categ <- c('Employed','Pensioner, still employed','Entrepreneur (owner of a company)','Self employed/freelance','Unemployed','Housewife','Farmer')
HAPIEE1_categ <- c('Pensioner,not employed')
```


## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `s70`|`r1`|
|-|-|-|
| **Label** | `What is your current economic activity`|`At what age did you retire`|
| **Table name**  | `Po_baseline_etic`|`Po_baseline_etic`|
| **Categories** | `Pensioner,not employed`<br/>`Employed`<br/>`Pensioner, still employed`<br/>`Entrepreneur (owner of a company)`<br/>`Unemployed`<br/>`Housewife`<br/>`Self employed/freelance`<br/>`Farmer` |`continuous`|
| **Missings** | `NA` |`NA`|
| **Description** |  |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',variables=list('s70','r1'), missings = T)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$s70
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 's70')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(s70))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

vbl <- HAPIEE_pol_w1$r1
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'r1')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HAPIEE_pol_w1,!vbl %in% vbl_miss), aes(r1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `Employed, Entrepreneur (owner of a company), Self employed/freelance, Unemployed, Housewife, Farmer or Pensioner, still employed into 0`
* `Pensioner,not employed into 1`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = r1`
* `NA into 999`

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$retired <- car::recode(HAPIEE_pol_w1$s70, "HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")

# Continuous variable harmonization
HAPIEE_ds_pol_w1$age_retired <- car::recode(HAPIEE_pol_w1$r1, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HAPIEE_ds_pol_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

```



### Wave 2

Not found harmonizable variable.


## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `s70`|`r1`|
|-|-|-|
| **Label** | `What is your current economic activity`|`At what age did you retire`|
| **Table name**  | `Cz_baseline_etic`|`Cz_baseline_etic`|
| **Categories** | `Pensioner,not employed`<br/>`Employed`<br/>`Pensioner, still employed`<br/>`Entrepreneur (owner of a company)`<br/>`Unemployed`<br/>`Housewife`<br/>`Self employed/freelance`<br/>`Farmer` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cz_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',variables=list('s70','r1'), missings = T)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$s70
kable(Categorical_summary(vbl, missing_values = c('9'))[3], caption = 's70')
kable(Categorical_summary(vbl, missing_values = c('9'))[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(s70))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

vbl <- HAPIEE_cz_w1$r1
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'r1')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HAPIEE_cz_w1,!vbl %in% vbl_miss), aes(r1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `Employed, Entrepreneur (owner of a company), Self employed/freelance, Unemployed, Housewife, Farmer or Pensioner, still employed into 0`
* `Pensioner,not employed into 1`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `age_retired = r1`
* `NA into 999`

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$retired <- car::recode(HAPIEE_cz_w1$s70, "HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")

# Continuous variable harmonization
HAPIEE_ds_cz_w1$age_retired <- car::recode(HAPIEE_cz_w1$r1, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HAPIEE_ds_cz_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w1, echo=F}


```



### Wave 2

Not found harmonizable variable.



## Lithuania


Not found harmonizable variable.



## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ}

l.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, cz_w1 = HAPIEE_ds_cz_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size",sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", "Poland_W1","Czech_Republic_W1")
kable(t.hds)
  
```



# Quality estimation

* In Poland baseline there are two variables asking for the same question (but with different data), `At what age did you retire?`: `r1` and `s70a`.
* The variables specified in the template for followup waves are empty or even do not appear in datasets.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





