---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Poland

### Wave 1 

#### Study-specific variable description

| **Name** | `dob` |
|----------|------------|
| **Label** | `Date of birth (definitive)` |
| **Table name** | `Po_baseline_etic` |
| **Description** |  |

```{r assign_po1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_birth','HAPIEE.Po_baseline_etic',
                         variables=list('dob'), missings = TRUE)
HAPIEE_pol_w1_birth <- opal.execute(o,'HAPIEE_pol_w1_birth')
```

```{r local_po1, echo=F}
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_pol_w1_birth <- cbind(HAPIEE_pol_w1_birth,Date_of_birth(HAPIEE_pol_w1_birth$dob))

vari <- HAPIEE_pol_w1_birth$Year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1_birth, aes(Year)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_po1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_birth$id)
HAPIEE_pol_ds_w1$ybirth <- car::recode(HAPIEE_pol_w1_birth$Year, "NA=999")
HAPIEE_pol_ds_w1$ybirth <- labelled(HAPIEE_pol_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1, echo=F}
vari <- HAPIEE_pol_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1, echo=F}
```





```{r importOPAL_po1, echo=F}

#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
ybirth <- HAPIEE_pol_ds_w1
save(ybirth, file = "../RData/pol_w1/ybirth.RData")
rm(ybirth)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$ybirth <- car::recode(HAPIEE_pol_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2

#### Study-specific variable description

| **Name** | `dob` |
|----------|------------|
| **Label** | `Date of birth (definitive)` |
| **Table name** | `Po_baseline_etic` |
| **Description** |  |

```{r assign_po2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_birth','HAPIEE.Po_baseline_etic',
                         variables=list('dob'), missings = TRUE)
HAPIEE_pol_w1_birth <- opal.execute(o,'HAPIEE_pol_w1_birth')
```

```{r local_po2, echo=F}
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_pol_w2_birth <- cbind(HAPIEE_pol_w1_birth,Date_of_birth(HAPIEE_pol_w1_birth$dob))

vari <- HAPIEE_pol_w2_birth$Year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2_birth, aes(Year)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_po2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_birth$id)
HAPIEE_pol_ds_w2$ybirth <- car::recode(HAPIEE_pol_w2_birth$Year, "NA=999")
HAPIEE_pol_ds_w2$ybirth <- labelled(HAPIEE_pol_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po2, echo=F}
vari <- HAPIEE_pol_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po2, echo=F}
```





```{r importOPAL_po2, echo=F}

#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
ybirth <- HAPIEE_pol_ds_w2
save(ybirth, file = "../RData/pol_w2/ybirth.RData")
rm(ybirth)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$ybirth <- car::recode(HAPIEE_pol_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






## Czech Republic 

### Wave 1

#### Study-specific variable description

| **Name** | `dob` |
|----------|------------|
| **Label** | `Date of birth (definitive)` |
| **Table name** | `Cz_baseline_etic` |
| **Description** |  |

```{r assign_cz1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_birth','HAPIEE.Cz_baseline_etic',
                         variables=list('dob'), missings = TRUE)
HAPIEE_cz_w1_birth <- opal.execute(o,'HAPIEE_cz_w1_birth')
```

```{r local_cz1, echo=F}
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_birth <- cbind(HAPIEE_cz_w1_birth,Date_of_birth(HAPIEE_cz_w1_birth$dob))

vari <- HAPIEE_cz_w1_birth$Year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1_birth, aes(Year)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cz1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_birth$id)
HAPIEE_cz_ds_w1$ybirth <- car::recode(HAPIEE_cz_w1_birth$Year, "NA=999")
HAPIEE_cz_ds_w1$ybirth <- labelled(HAPIEE_cz_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1, echo=F}
vari <- HAPIEE_cz_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1, echo=F}
```





```{r importOPAL_cz1, echo=F}

#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
ybirth <- HAPIEE_cz_ds_w1
save(ybirth, file = "../RData/cz_w1/ybirth.RData")
rm(ybirth)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$ybirth <- car::recode(HAPIEE_cz_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2

#### Study-specific variable description

| **Name** | `dob` |
|----------|------------|
| **Label** | `Date of birth (definitive)` |
| **Table name** | `Cz_baseline_etic` |
| **Description** |  |


```{r assign_cz2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_birth','HAPIEE.Cz_baseline_etic',
                         variables=list('dob'), missings = TRUE)
HAPIEE_cz_w1_birth <- opal.execute(o,'HAPIEE_cz_w1_birth')
```

```{r local_cz2, echo=F}
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_cz_w1_birth <- cbind(HAPIEE_cz_w1_birth,Date_of_birth(HAPIEE_cz_w1_birth$dob))

vari <- HAPIEE_cz_w1_birth$Year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1_birth, aes(Year)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cz2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w1_birth$id)
HAPIEE_cz_ds_w2$ybirth <- car::recode(HAPIEE_cz_w1_birth$Year, "NA=999")
HAPIEE_cz_ds_w2$ybirth <- labelled(HAPIEE_cz_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz2, echo=F}
vari <- HAPIEE_cz_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz2, echo=F}
```





```{r importOPAL_cz2, echo=F}

#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
ybirth <- HAPIEE_cz_ds_w2
save(ybirth, file = "../RData/cz_w2/ybirth.RData")
rm(ybirth)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$ybirth <- car::recode(HAPIEE_cz_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```







## Lithuania

### Wave 1

#### Study-specific variable description

| **Name** | `dob` |
|----------|------------|
| **Label** | `Date of birth (definitive)` |
| **Table name** | `Li_baseline_etic` |
| **Description** |  |

```{r assign_li1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_birth','HAPIEE.Li_baseline_etic',
                         variables=list('dob'), missings = TRUE)
HAPIEE_li_w1_birth <- opal.execute(o,'HAPIEE_li_w1_birth')
```

```{r local_li1, echo=F}
Date_of_birth <- function(date){
  n <- length(date)
  D <- matrix(NA, nrow = n, ncol = 2)
  for(i in 1:n){
    D[i,] <- t(sapply(date[i], function(x) substring(x, first=c(1, 5), last=c(4, 7))))
  }
  DD <- data.frame(Year=as.numeric(D[,1]), Month=as.character(D[,2]))
  DD
}

HAPIEE_li_w1_birth <- cbind(HAPIEE_li_w1_birth,Date_of_birth(HAPIEE_li_w1_birth$dob))

vari <- HAPIEE_li_w1_birth$Year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Year of birth") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_li_w1_birth, aes(Year)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_birth$id)
HAPIEE_li_ds_w1$ybirth <- car::recode(HAPIEE_li_w1_birth$Year, "NA=999")
HAPIEE_li_ds_w1$ybirth <- labelled(HAPIEE_li_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1, echo=F}
vari <- HAPIEE_li_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Year of birth")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_li_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1, echo=F}
```





```{r importOPAL_li1, echo=F}

#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
ybirth <- HAPIEE_li_ds_w1
save(ybirth, file = "../RData/li_w1/ybirth.RData")
rm(ybirth)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$ybirth <- car::recode(HAPIEE_li_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```







# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
