---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## Poland

### Wave 1 

#### Study-specific variable description


| **Name** | `age` |
|----------|------------|
| **Label** | `Age on day of interview` |
| **Table name** | `Po_baseline_etic` |
| **Description** |  |


```{r assign_po1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_age','HAPIEE.Po_baseline_etic',
                         variables=list('age'), missings = TRUE)
```

```{r local_po1, echo=F}
HAPIEE_pol_w1_age <- opal.execute(o,'HAPIEE_pol_w1_age')
vari <- HAPIEE_pol_w1_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_po1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_age$id)
HAPIEE_pol_ds_w1$age <- car::recode(HAPIEE_pol_w1_age$age, "NA=999")
HAPIEE_pol_ds_w1$age <- labelled(HAPIEE_pol_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1, echo=F}
vari <- HAPIEE_pol_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_po1, echo=F}
```





```{r importOPAL_po1, echo=F}

#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
age <- HAPIEE_pol_ds_w1
save(age, file = "../RData/pol_w1/age.RData")
rm(age)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$age <- car::recode(HAPIEE_pol_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2

#### Study-specific variable description

| **Name** | `nage` |
|----------|------------|
| **Label** | `Age of participant on day of interview` |
| **Table name** | `Po_reexamination_etic` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign_po2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_age','HAPIEE.Po_reexamination_etic',
                         variables=list('nage'), missings = TRUE)
```

```{r local_po2, echo=F}
HAPIEE_pol_w2_age <- opal.execute(o,'HAPIEE_pol_w2_age')
vari <- HAPIEE_pol_w2_age$nage
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "nage")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2_age, aes(nage)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_po2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_age$id)
HAPIEE_pol_ds_w2$age <- car::recode(HAPIEE_pol_w2_age$nage, "NA=999")
HAPIEE_pol_ds_w2$age <- labelled(HAPIEE_pol_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po2, echo=F}
vari <- HAPIEE_pol_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(49, 75)
```

#### Validation
```{r crosstabulation_po2, echo=F}
```





```{r importOPAL_po2, echo=F}

#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
age <- HAPIEE_pol_ds_w2
save(age, file = "../RData/pol_w2/age.RData")
rm(age)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$age <- car::recode(HAPIEE_pol_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age on day of interview` |
| **Table name** | `Cz_baseline_etic` |
| **Description** |  |




```{r assign_cz1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_age','HAPIEE.Cz_baseline_etic',
                         variables=list('age'), missings = TRUE)
```

```{r local_cz1, echo=F}
HAPIEE_cz_w1_age <- opal.execute(o,'HAPIEE_cz_w1_age')
vari <- HAPIEE_cz_w1_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cz1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_age$id)
HAPIEE_cz_ds_w1$age <- car::recode(HAPIEE_cz_w1_age$age, "NA=999")
HAPIEE_cz_ds_w1$age <- labelled(HAPIEE_cz_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1, echo=F}
vari <- HAPIEE_cz_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1, echo=F}
```





```{r importOPAL_cz1, echo=F}

#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
age <- HAPIEE_cz_ds_w1
save(age, file = "../RData/cz_w1/age.RData")
rm(age)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$age <- car::recode(HAPIEE_cz_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```









### Wave 2

#### Study-specific variable description

| **Name** | `nage` |
|----------|------------|
| **Label** | `Age on day of interview` |
| **Table name** | `Cz_reexamination_etic` |
| **Missings** |`NA`|
| **Description** |  |



```{r assign_cz2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_age','HAPIEE.Cz_reexamination_etic',
                         variables=list('nage'), missings = TRUE)
```

```{r local_cz2, echo=F}
HAPIEE_cz_w2_age <- opal.execute(o,'HAPIEE_cz_w2_age')
vari <- HAPIEE_cz_w2_age$nage
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "nage")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2_age, aes(nage)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_cz2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_age$id)
HAPIEE_cz_ds_w2$age <- car::recode(HAPIEE_cz_w2_age$nage, "NA=999")
HAPIEE_cz_ds_w2$age <- labelled(HAPIEE_cz_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz2, echo=F}
vari <- HAPIEE_cz_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(47, 75)
```

#### Validation
```{r crosstabulation_cz2, echo=F}
```





```{r importOPAL_cz2, echo=F}

#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
age <- HAPIEE_cz_ds_w2
save(age, file = "../RData/cz_w2/age.RData")
rm(age)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$age <- car::recode(HAPIEE_cz_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```







## Lithuania

### Wave 1

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age on day of interview` |
| **Table name** | `Li_baseline_etic` |
| **Missings** |`NA`|
| **Description** |  |


```{r assign_li1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_age','HAPIEE.Li_baseline_etic',
                         variables=list('age'), missings = TRUE)
```

```{r local_li1, echo=F}
HAPIEE_li_w1_age <- opal.execute(o,'HAPIEE_li_w1_age')
vari <- HAPIEE_li_w1_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "age")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_li_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_age$id)
HAPIEE_li_ds_w1$age <- car::recode(HAPIEE_li_w1_age$age, "NA=999")
HAPIEE_li_ds_w1$age <- labelled(HAPIEE_li_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1, echo=F}
vari <- HAPIEE_li_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_li_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(45,75)
```

#### Validation
```{r crosstabulation_li1, echo=F}
```





```{r importOPAL_li1, echo=F}

#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
age <- HAPIEE_li_ds_w1
save(age, file = "../RData/li_w1/age.RData")
rm(age)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$age <- car::recode(HAPIEE_li_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```





# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
