---
title: "Sex"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

```{r lab, echo=FALSE}
ds_label <- "Sex"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `sex`
* Variable label: `biological sex`
* Variable description: `participant's biological sex`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | female
1        | male

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process




## Poland 
### Wave 1

#### Study-specific variable description

 

* Name: `q2`
* Label: `Sex`
* Categories: 
    + `Female`
    + `Male`
* Description:
```{r assign_po1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_sex','HAPIEE.Po_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_pol_w1_sex <- opal.execute(o,'HAPIEE_pol_w1_sex')
```

```{r local_po1, echo=FALSE}
vari <- HAPIEE_pol_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_po1, echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_sex$id)
HAPIEE_pol_ds_w1$sex <- car::recode(HAPIEE_pol_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_pol_ds_w1$sex <- labelled( HAPIEE_pol_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_po1, echo=FALSE}
vari <- HAPIEE_pol_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1, echo=FALSE}
AfterH <- table(HAPIEE_pol_ds_w1$sex)
BeforeH <- table(HAPIEE_pol_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```


```{r importOPAL_po1, echo=FALSE}
val_labels(HAPIEE_pol_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
sex <- HAPIEE_pol_ds_w1
save(sex, file = "../RData/pol_w1/sex.RData")
rm(sex)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$sex <- car::recode(HAPIEE_pol_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description

 

* Name: `q2`
* Label: `Sex`
* Categories: 
    + `Female`
    + `Male`
* Description:
```{r assign_po2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_sex','HAPIEE.Po_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_pol_w1_sex <- opal.execute(o,'HAPIEE_pol_w1_sex')
```

```{r local_po2, echo=FALSE}
vari <- HAPIEE_pol_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_po2, echo=TRUE}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w1_sex$id)
HAPIEE_pol_ds_w2$sex <- car::recode(HAPIEE_pol_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_pol_ds_w2$sex <- labelled( HAPIEE_pol_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_po2, echo=FALSE}
vari <- HAPIEE_pol_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po2, echo=FALSE}
AfterH <- table(HAPIEE_pol_ds_w2$sex)
BeforeH <- table(HAPIEE_pol_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```


```{r importOPAL_po2, echo=FALSE}
val_labels(HAPIEE_pol_ds_w2) <- NULL
opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
sex <- HAPIEE_pol_ds_w2
save(sex, file = "../RData/pol_w2/sex.RData")
rm(sex)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$sex <- car::recode(HAPIEE_pol_m_ds_w2$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






## Czech Republic 
### Wave 1

#### Study-specific variable description

 

* Name: `q2`
* Label: `Sex`
* Categories: 
    + `Female`
    + `Male`
* Description:
```{r assign_cz1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_sex','HAPIEE.Cz_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_cz_w1_sex <- opal.execute(o,'HAPIEE_cz_w1_sex')
```

```{r local_cz1, echo=FALSE}
vari <- HAPIEE_cz_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_cz1, echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_sex$id)
HAPIEE_cz_ds_w1$sex <- car::recode(HAPIEE_cz_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_cz_ds_w1$sex <- labelled( HAPIEE_cz_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cz1, echo=FALSE}
vari <- HAPIEE_cz_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1, echo=FALSE}
AfterH <- table(HAPIEE_cz_ds_w1$sex)
BeforeH <- table(HAPIEE_cz_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```


```{r importOPAL_cz1, echo=FALSE}
val_labels(HAPIEE_cz_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
sex <- HAPIEE_cz_ds_w1
save(sex, file = "../RData/cz_w1/sex.RData")
rm(sex)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$sex <- car::recode(HAPIEE_cz_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2

#### Study-specific variable description

 

* Name: `q2`
* Label: `Sex`
* Categories: 
    + `Female`
    + `Male`
* Description:
```{r assign_cz2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_sex','HAPIEE.Cz_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_cz_w1_sex <- opal.execute(o,'HAPIEE_cz_w1_sex')
```

```{r local_cz2, echo=FALSE}
vari <- HAPIEE_cz_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_cz2, echo=TRUE}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w1_sex$id)
HAPIEE_cz_ds_w2$sex <- car::recode(HAPIEE_cz_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_cz_ds_w2$sex <- labelled( HAPIEE_cz_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cz2, echo=FALSE}
vari <- HAPIEE_cz_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz2, echo=FALSE}
AfterH <- table(HAPIEE_cz_ds_w2$sex)
BeforeH <- table(HAPIEE_cz_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```


```{r importOPAL_cz2, echo=FALSE}
val_labels(HAPIEE_cz_ds_w2) <- NULL
opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
sex <- HAPIEE_cz_ds_w2
save(sex, file = "../RData/cz_w2/sex.RData")
rm(sex)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$sex <- car::recode(HAPIEE_cz_m_ds_w2$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```







## Lithuania 

### Wave 1

#### Study-specific variable description

 

* Name: `q2`
* Label: `Sex`
* Categories: 
    + `Female`
    + `Male`
* Description:
```{r assign_li1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_sex','HAPIEE.Li_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_li_w1_sex <- opal.execute(o,'HAPIEE_li_w1_sex')
```

```{r local_li1, echo=FALSE}
vari <- HAPIEE_li_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_li_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_li1, echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_sex$id)
HAPIEE_li_ds_w1$sex <- car::recode(HAPIEE_li_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_li_ds_w1$sex <- labelled( HAPIEE_li_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_li1, echo=FALSE}
vari <- HAPIEE_li_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1, echo=FALSE}
AfterH <- table(HAPIEE_li_ds_w1$sex)
BeforeH <- table(HAPIEE_li_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```


```{r importOPAL_li1, echo=FALSE}
val_labels(HAPIEE_li_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
sex <- HAPIEE_li_ds_w1
save(sex, file = "../RData/li_w1/sex.RData")
rm(sex)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$sex <- car::recode(HAPIEE_li_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
