---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```

# Data process




## Poland 
### Wave 1

#### Study-specific variable description

 

| **Name** |`q2`|
|-|-|
| **Label** |`Sex`|
| **Table name** |`Po_baseline_etic`|
| **Categories** |`Female`<br/>`Male`|
| **Description** |  |


```{r assign_po1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_sex','HAPIEE.Po_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_pol_w1_sex <- opal.execute(o,'HAPIEE_pol_w1_sex')
```

```{r local_po1, echo=FALSE}
vari <- HAPIEE_pol_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_po1, echo=TRUE}
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1_sex$id)
HAPIEE_ds_pol_w1$sex <- car::recode(HAPIEE_pol_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_ds_pol_w1$sex <- labelled( HAPIEE_ds_pol_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_po1, echo=FALSE}
vari <- HAPIEE_ds_pol_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1, echo=FALSE}
AfterH <- table(HAPIEE_ds_pol_w1$sex)
BeforeH <- table(HAPIEE_pol_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```






### Wave 2

#### Study-specific variable description


| **Name** |`q2`|
|-|-|
| **Label** |`Sex`|
| **Table name** |`Po_baseline_etic`|
| **Categories** |`Female`<br/>`Male`|
| **Description** |  |



```{r assign_po2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_sex','HAPIEE.Po_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_pol_w1_sex <- opal.execute(o,'HAPIEE_pol_w1_sex')
```

```{r local_po2, echo=FALSE}
vari <- HAPIEE_pol_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_po2, echo=TRUE}
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w1_sex$id)
HAPIEE_ds_pol_w2$sex <- car::recode(HAPIEE_pol_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_ds_pol_w2$sex <- labelled( HAPIEE_ds_pol_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_po2, echo=FALSE}
vari <- HAPIEE_ds_pol_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po2, echo=FALSE}
AfterH <- table(HAPIEE_ds_pol_w2$sex)
BeforeH <- table(HAPIEE_pol_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```






## Czech Republic 
### Wave 1

#### Study-specific variable description

 

| **Name** |`q2`|
|-|-|
| **Label** |`Sex`|
| **Table name** |`Cz_baseline_etic`|
| **Categories** |`Female`<br/>`Male`|
| **Description** |  |

```{r assign_cz1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_sex','HAPIEE.Cz_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_cz_w1_sex <- opal.execute(o,'HAPIEE_cz_w1_sex')
```

```{r local_cz1, echo=FALSE}
vari <- HAPIEE_cz_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_cz1, echo=TRUE}
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1_sex$id)
HAPIEE_ds_cz_w1$sex <- car::recode(HAPIEE_cz_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_ds_cz_w1$sex <- labelled( HAPIEE_ds_cz_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cz1, echo=FALSE}
vari <- HAPIEE_ds_cz_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1, echo=FALSE}
AfterH <- table(HAPIEE_ds_cz_w1$sex)
BeforeH <- table(HAPIEE_cz_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```









### Wave 2

#### Study-specific variable description

 

| **Name** |`q2`|
|-|-|
| **Label** |`Sex`|
| **Table name** |`Cz_baseline_etic`|
| **Categories** |`Female`<br/>`Male`|
| **Description** |  |


```{r assign_cz2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_sex','HAPIEE.Cz_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_cz_w1_sex <- opal.execute(o,'HAPIEE_cz_w1_sex')
```

```{r local_cz2, echo=FALSE}
vari <- HAPIEE_cz_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_cz2, echo=TRUE}
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w1_sex$id)
HAPIEE_ds_cz_w2$sex <- car::recode(HAPIEE_cz_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_ds_cz_w2$sex <- labelled( HAPIEE_ds_cz_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cz2, echo=FALSE}
vari <- HAPIEE_ds_cz_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz2, echo=FALSE}
AfterH <- table(HAPIEE_ds_cz_w2$sex)
BeforeH <- table(HAPIEE_cz_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```




## Lithuania 

### Wave 1

#### Study-specific variable description

 
| **Name** |`q2`|
|-|-|
| **Label** |`Sex`|
| **Table name** |`Li_baseline_etic`|
| **Categories** |`Female`<br/>`Male`|
| **Description** |  |




```{r assign_li1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_sex','HAPIEE.Li_baseline_etic',
                         variables=list('q2'), missings = TRUE)
HAPIEE_li_w1_sex <- opal.execute(o,'HAPIEE_li_w1_sex')
```

```{r local_li1, echo=FALSE}
vari <- HAPIEE_li_w1_sex$q2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_li_w1_sex, aes(x=factor(q2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `Female into 0`
* `Male into 1`

**R script:**

```{r harmo_li1, echo=TRUE}
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1_sex$id)
HAPIEE_ds_li_w1$sex <- car::recode(HAPIEE_li_w1_sex$q2, " 'Female'=0; 'Male'=1; NA=999")
HAPIEE_ds_li_w1$sex <- labelled( HAPIEE_ds_li_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_li1, echo=FALSE}
vari <- HAPIEE_ds_li_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1, echo=FALSE}
AfterH <- table(HAPIEE_ds_li_w1$sex)
BeforeH <- table(HAPIEE_li_w1_sex$q2)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Female->0","Male->1")
kable(C)
```








## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hapiee.cw <- list(pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), cz_w1 = c("cz_w1","Czech Republic w1"), cz_w2 = c("cz_w2","Czech Republic w2"), li_w1 = c("li_w1","Lithuania w1"))

# Consider only harmonised waves
l.hds <- lapply(hapiee.cw, function(wname) if(exists(paste0("HAPIEE_ds_",wname[1]))){wname = list(get(paste0("HAPIEE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```









# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
