---
title: "Education"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `education`
* Variable label: `Highest level of formal education achieved`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | less than primary education
1        | primary education
2        | secondary education
3        | tertiary education

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Poland 
### Wave 1 

#### Study-specific variable description

 

* Name: `q3`
* Label: `Highest completed level of education`
* Categories: 
    + `Incomplete primary or no formal education`
    + `Primary`
    + `Vocational (apprenticeship)`
    + `Secondary`
    + `University (degree)`

* Description: 
```{r assign_po1,  echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_educ','HAPIEE.Po_baseline_etic',
                         variables=list('q3'), missings = TRUE)
```

```{r local_po1,  echo=FALSE}
HAPIEE_pol_w1_educ <- opal.execute(o,'HAPIEE_pol_w1_educ')
vari <- HAPIEE_pol_w1_educ$q3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_pol_w1_educ$q3, missing_values = NA)
ggplot(HAPIEE_pol_w1_educ, aes(x=factor(q3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode "Incomplete primary or no formal education" into 0`
* `recode "Primary" into 1`
* `recode "Vocational (apprenticeship)" into 2`
* `recode "Secondary" into 2`
* `recode "University (degree)" into 3`

**R script:**

```{r harmo_po1,   echo=TRUE}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_educ$id)
HAPIEE_pol_ds_w1$education <- car::recode(HAPIEE_pol_w1_educ$q3, "'Incomplete primary or no formal education'=0; 'Primary'=1; 'Vocational (apprenticeship'=2; 'Secondary'=2; 'University (degree)'=3; NA=999")
HAPIEE_pol_ds_w1$education <- labelled(HAPIEE_pol_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_po1,  echo=FALSE}
vari <- HAPIEE_pol_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_pol_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_po1,  echo=FALSE}
BeforeH <- table(HAPIEE_pol_w1_educ$q3)
BeforeH <- c(BeforeH[1], BeforeH[2], sum(BeforeH[c(3,5)]), BeforeH[4], sum(is.na(HAPIEE_pol_w1_educ$q3)))
AfterH <- table(HAPIEE_pol_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "2", "3", "999")
kable(C)

```

 
 

 
```{r importOPAL_po1,  echo=FALSE}
val_labels(HAPIEE_pol_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
education <- HAPIEE_pol_ds_w1
save(education, file = "../RData/pol_w1/education.RData")
rm(education)

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$education <- car::recode(HAPIEE_pol_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2

Not found.




## Czech Republic 
### Wave 1

#### Study-specific variable description

 

* Name: `q3`
* Label: `Highest completed level of education`
* Categories: 
    + `Incomplete primary or no formal education`
    + `Primary`
    + `Vocational (apprenticeship)`
    + `Secondary`
    + `University (degree)`

* Description: 
```{r assign_cz1,  echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_educ','HAPIEE.Cz_baseline_etic',
                         variables=list('q3'), missings = TRUE)
```

```{r local_cz1,  echo=FALSE}
HAPIEE_cz_w1_educ <- opal.execute(o,'HAPIEE_cz_w1_educ')
vari <- HAPIEE_cz_w1_educ$q3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_cz_w1_educ$q3, missing_values = NA)
ggplot(HAPIEE_cz_w1_educ, aes(x=factor(q3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode "Incomplete primary or no formal education" into 0`
* `recode "Primary" into 1`
* `recode "Vocational (apprenticeship)" into 2`
* `recode "Secondary" into 2`
* `recode "University (degree)" into 3`

**R script:**

```{r harmo_cz1,   echo=TRUE}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_educ$id)
HAPIEE_cz_ds_w1$education <- car::recode(HAPIEE_cz_w1_educ$q3, "'Incomplete primary or no formal education'=0; 'Primary'=1; 'Vocational (apprenticeship'=2; 'Secondary'=2; 'University (degree)'=3; NA=999")
HAPIEE_cz_ds_w1$education <- labelled(HAPIEE_cz_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_cz1,  echo=FALSE}
vari <- HAPIEE_cz_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_cz_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cz1,  echo=FALSE}
BeforeH <- table(HAPIEE_cz_w1_educ$q3)
BeforeH <- c(BeforeH[1], BeforeH[2], sum(BeforeH[c(3,5)]), BeforeH[4], sum(is.na(HAPIEE_cz_w1_educ$q3)))
AfterH <- table(HAPIEE_cz_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "2", "3", "999")
kable(C)

```

 
 

 
```{r importOPAL_cz1,  echo=FALSE}
val_labels(HAPIEE_cz_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
education <- HAPIEE_cz_ds_w1
save(education, file = "../RData/cz_w1/education.RData")
rm(education)

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$education <- car::recode(HAPIEE_cz_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2

There is no variable.







## Lithuania 
### Wave 1

#### Study-specific variable description

 

* Name: `q3`
* Label: `Highest completed level of education`
* Categories: 
    + `Incomplete primary or no formal education`
    + `Primary`
    + `Vocational (apprenticeship)`
    + `Secondary`
    + `University (degree)`
    + `College`

* Description: 
```{r assign_li1,  echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_educ','HAPIEE.Li_baseline_etic',
                         variables=list('q3'), missings = TRUE)
```

```{r local_li1,  echo=FALSE}
HAPIEE_li_w1_educ <- opal.execute(o,'HAPIEE_li_w1_educ')
vari <- HAPIEE_li_w1_educ$q3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = HAPIEE_li_w1_educ$q3, missing_values = NA)
ggplot(HAPIEE_li_w1_educ, aes(x=factor(q3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode "Incomplete primary or no formal education" into 0`
* `recode "Primary" into 1`
* `recode "Vocational (apprenticeship)" into 2`
* `recode "Secondary" into 2`
* `recode "University (degree)" into 3`
* `recode "College" into 3`

**R script:**

```{r harmo_li1,   echo=TRUE}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_educ$id)
HAPIEE_li_ds_w1$education <- car::recode(HAPIEE_li_w1_educ$q3, "'Incomplete primary or no formal education'=0; 'Primary'=1; 'Vocational (apprenticeship'=2; 'Secondary'=2; 'University (degree)'=3; 'College'=3; NA=999")
HAPIEE_li_ds_w1$education <- labelled(HAPIEE_li_ds_w1$education, labels = c("less than primary education"=0, "primary education"=1, "secondary education"=2, "tertiary education"=3, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_li1,  echo=FALSE}
vari <- HAPIEE_li_ds_w1$education
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = HAPIEE_li_ds_w1$education, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(x=factor(education))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Level of education") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_li1,  echo=FALSE}
BeforeH <- table(HAPIEE_li_w1_educ$q3)
BeforeH <- c(BeforeH[2], BeforeH[3], sum(BeforeH[c(4,6)]), sum(BeforeH[c(1,5)]), sum(is.na(HAPIEE_li_w1_educ$q3)))
AfterH <- table(HAPIEE_li_ds_w1$education)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0", "1", "2", "3", "999")
kable(C)

```

 
 

 
```{r importOPAL_li1,  echo=FALSE}
val_labels(HAPIEE_li_ds_w1) <- NULL
opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
education <- HAPIEE_li_ds_w1
save(education, file = "../RData/li_w1/education.RData")
rm(education)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$education <- car::recode(HAPIEE_li_m_ds_w1$education, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```

