---
title: "Retired"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/retiredDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/retiredDS.R')
```



# Data process



## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `K55A` |`J1`|`K57_1`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Retirement pension`|`Interview code`|`Start of retirement pension`|`year of birth`|
| **Table name**  | `sect_k`| `sect_j`|`sect_k`|`ybirth`|
| **Categories** | `1 = Yes`<br/>`2 = No`|`1 = Respondent`<br/>`2 = Spouse`<br/>`3 = Other`|`continuous`|`continuous`|
| **Missings** |  | `NA` | `8888 = Doesn't answer`<br/>`9999 = Doesn't know`<br/>`NA` |  |
| **Description** |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_pre','Mexican Health Aging Study.sect_k',variables=list('K55A','K57_1'), missings = T)
MHAS_w1_pre <- opal.execute(o,'MHAS_w1_pre')
opal.assign.table.tibble(o, 'MHAS_w1_2','Mexican Health Aging Study.sect_j',variables=list('J1'), missings = T)
MHAS_w1_2 <- opal.execute(o,'MHAS_w1_2')
MHAS_w1_0 <- inner_join(MHAS_w1_pre,MHAS_w1_2,by="id")
opal.assign.table.tibble(o, 'MHAS_w1_id','Mexican Health Aging Study.MHAS-2001',variables=list('unhhid'), missings = T)
MHAS_w1_id <- opal.execute(o,'MHAS_w1_id')
MHAS_w1_id$unhhid <- paste0(as.character(MHAS_w1_id$unhhid),".0")
MHAS_w1 <- left_join(MHAS_w1_id,MHAS_w1_0,by=c("unhhid"="id"))
load(paste0(datafolder,"w1/ybirth.RData"))
MHAS_w1 <- left_join(MHAS_w1,ybirth,by="id")
rm(ybirth)

```

```{r local w1, echo=F}

vbl <- MHAS_w1_pre$K55A
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'K55A')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_pre, aes(x=factor(K55A))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1_2$J1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'J1')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_2, aes(x=factor(J1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1_pre$K57_1
vbl_miss <- c(8888,9999)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'K57_1')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w1_pre,!vbl %in% vbl_miss), aes(K57_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w1,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

The interviewer manual specifies:

`In the case of single household interviews, conduct both section J and K. Both sections are conducted with only one member of the couple. The election of respondent between the two members of the couple will be done according to the preferences of the couple, expressed at the beginning of section J, in the INTERVIEW CONTROL sheet.`

* `For each household id we get the id corresponding to the respondent from the household id (substring of the id's) and the interview code (J1). For them:`
* `keep up K55a == 2 into 0`
* `keep up K55a == 1 into 1`
* `otherwise into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `For the same individuals as above:`
* `age_retired = K57_1 - ybirth`
* `if retired == 0, age_retired = 996`
* `8888 into 995`
* `9999 into 998`
* `otherwise, age_retired = 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$retired <- rep(999,length(MHAS_w1$id))
MHAS_ds_w1$retired[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$J1),"0.0")==MHAS_w1$id)] <- 2 - MHAS_w1$K55A[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$J1),"0.0")==MHAS_w1$id)]

# Continuous variable harmonization
MHAS_ds_w1$age_retired <- rep(999,length(MHAS_ds_w1$id))
MHAS_ds_w1$age_retired[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$J1),"0.0")==MHAS_w1$id)] <- MHAS_w1$K57_1[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$J1),"0.0")==MHAS_w1$id)] - MHAS_w1$ybirth[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$J1),"0.0")==MHAS_w1$id)]
MHAS_ds_w1$age_retired[which(MHAS_w1$K57_1==9999)] <- 998
MHAS_ds_w1$age_retired[which(MHAS_w1$K57_1==8888)] <- 995
MHAS_ds_w1$age_retired[which(MHAS_ds_w1$retired==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w1$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w1,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `i16`|`i26`|`i28`|`i29`|`ybirth`|
|-|-|-|-|-|-|
| **Label** | `Work status`|`Main reason for not working`|`Reason for leaving last job`|`When leave last job`|`year of birth`|
| **Table name**  | `MHAS_2003`| `MHAS_2003`|`MHAS_2003`|`MHAS_2003`|`ybirth`|
| **Categories** |`1 = Works`<br/>`2 = Looking for a job`<br/>`3 = Does not work`|`1 = Dedicated to household chores`<br/>`2 = Retired`<br/>`3 = Old Age`<br/>`4 = Sick or temporarily disabled`<br/>`5 = Unable to work for rest of life`<br/>`6 = Doesn't have customers or can't find work`<br/>`7 = Other`|`1 = Source of work is bankrupt/closed down/cut down on staff`<br/>`2 = It was temporary and the time period of the work ended`<br/>`3 = The business moved`<br/>`4 = Made very little money`<br/>`5 = The work schedule was inconvenient`<br/>`6 = It wasn't related to respondent's studies or training`<br/>`7 = To care for children or other family members`<br/>`8 = Due to illness`<br/>`9 = Respondent retired`<br/>`10 = Other`|`continuous`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` |`8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` |`88 = Doesn't answer`<br/>`99 = Doesn't know`<br/>`NA` |`8888 = Doesn't answer`<br/>`9999 = Doesn't know`<br/>`NA`|`999 = Missing`|
| **Description** |  |  |  |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('i16','i26','i28','i29'), missings = T)
MHAS_w2 <- opal.execute(o,'MHAS_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
MHAS_w2 <- left_join(MHAS_w2,ybirth,by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- MHAS_w2$i16
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(i16))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$i26
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w2)[3])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(i26))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$i28
kable(Categorical_summary(vbl, missing_values = c(88,99))[3], caption = names(MHAS_w2)[4])
kable(Categorical_summary(vbl, missing_values = c(88,99))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(i28))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$i29
vbl_miss <- c(8888,9999)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'i29')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2,!vbl %in% vbl_miss), aes(i29)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `i26 == 2 or i28 == 9 into 1`
* `i26 == 1,3,4,5,6,7 into 0`
* `i16 == 1,2 into 0`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = i29 - ybirth`
* `if retired == 0 or i28 != 9, age_retired = 996`
* `8,88,8888 into 995`
* `9,99,9999 into 998`

**R script:**


```{r harmo w2}

# Categorical variable harmonization
MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$retired <- car::recode(MHAS_w2$i26, "c(1,3,4,5,6,7)=0; 2=1; 8=995; 9=998; NA=999")
MHAS_ds_w2$retired[which(MHAS_w2$i28 %in% c(9))] <- 1
MHAS_ds_w2$retired[which(MHAS_w2$i16 %in% c(1,2))] <- 0

MHAS_w2 <- left_join(MHAS_w2,MHAS_ds_w1,by="id")
# Continuous variable harmonization
MHAS_ds_w2$age_retired <- rep(999,length(MHAS_ds_w2$id))
MHAS_ds_w2$age_retired[which(MHAS_w2$i16==8 | MHAS_w2$i26==8 | MHAS_w2$i28==88 | MHAS_w2$i29==8888)] <- 995
MHAS_ds_w2$age_retired[which(MHAS_w2$i16==9 | MHAS_w2$i26==9 | MHAS_w2$i28==99 | MHAS_w2$i29==9999)] <- 998
MHAS_ds_w2$age_retired[which(MHAS_w2$ybirth!=999 & !MHAS_w2$i29 %in% c(8888,9999) & MHAS_ds_w2$retired==1 & MHAS_w2$i28==9 & MHAS_w2$i29>=1950)] <- MHAS_w2$i29[which(MHAS_w2$ybirth!=999 & !MHAS_w2$i29 %in% c(8888,9999) & MHAS_ds_w2$retired==1 & MHAS_w2$i28==9 & MHAS_w2$i29>=1950)] - MHAS_w2$ybirth[which(MHAS_w2$ybirth!=999 & !MHAS_w2$i29 %in% c(8888,9999) & MHAS_ds_w2$retired==1 & MHAS_w2$i28==9 & MHAS_w2$i29>=1950)]
MHAS_ds_w2$age_retired[which(MHAS_ds_w2$retired==1 & !is.na(MHAS_w2$age_retired) & !MHAS_w2$age_retired %in% miss_values_vector)] <- MHAS_w2$age_retired[which(MHAS_ds_w2$retired==1 & !is.na(MHAS_w2$age_retired) & !MHAS_w2$age_retired %in% miss_values_vector)]
MHAS_ds_w2$age_retired[which(MHAS_ds_w2$age_retired<=0)] <- 999
MHAS_ds_w2$age_retired[which(MHAS_w2$i28!=9)] <- 996
MHAS_ds_w2$age_retired[which(MHAS_ds_w2$retired==0)] <- 996
```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w2$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w2,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}


```



### Wave 3

#### Study-specific variable description


```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('i16_12','i26_2_12','i26_8_12','i26_9_12','i28_09_12','i29_1_12','i28_88_12','i28_99_12','i29_2_12'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
load(paste0(datafolder,"w3/ybirth.RData"))
MHAS_w3 <- left_join(MHAS_w3,ybirth,by="id")
rm(ybirth)

```


| **Name** |`i16_12`| `i26_2_12`| `i26_8_12`| `i26_9_12`|`i28_09_12`|`i28_88_12`|`i28_99_12`|
|-|-|-|-|-|-|-|-|
| **Label** |`Current work status`| `Reason for not working - retired`|`Reason for not working - RF`|`Reason for not working - DK`|`Reason left last job - retirement`|`Reason left last job - RF`|`Reason left last job - DK`|
| **Table name**  | `MHAS_2012_new`| `MHAS_2012_new`| `MHAS_2012_new`| `MHAS_2012_new`| `MHAS_2012_new`| `MHAS_2012_new`| `MHAS_2012_new`|
| **Categories** |`1 = Are working`<br/>`2 = Are looking for work`<br/>`3 = Don't work`| `0 = Not a selected answer`<br/>`1 = Yes`| `0 = Not a selected answer`<br/>`1 = Yes`| `0 = Not a selected answer`<br/>`1 = Yes`| `0 = Not a selected answer`<br/>`1 = Yes`| `0 = Not a selected answer`<br/>`1 = Yes`| `0 = Not a selected answer`<br/>`1 = Yes`|
| **Missings** |`8 = RF`<br/>`9 = DK`| `NA` | `NA` | `NA` | `NA` | `NA` | `NA` |
| **Description** |  |  |  |  |  |  |  |



```{r local w3, echo=F}

vbl <- MHAS_w3$i16_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i16_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i16_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i26_2_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i26_2_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i26_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i26_8_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i26_8_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i26_8_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i26_9_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i26_9_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i26_9_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i28_09_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i28_09_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i28_09_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i28_88_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i28_88_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i28_88_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i28_99_12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'i28_99_12')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(i28_99_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


| **Name** |`i29_1_12`|`i29_2_12`|`ybirth`|
|-|-|-|-|
| **Label** |`In what year did you leave your last job`|`How many years ago did you leave your last job`|`year of birth`|
| **Table name**  | `MHAS_2012_new`| `MHAS_2012_new`|`ybirth`|
| **Categories** |`continuous`|`continuous`| `continuous`|
| **Missings** |`8888 = Doesn't answer`<br/>`9999 = Doesn't know`<br/>`NA`|`88 = Doesn't answer`<br/>`99 = Doesn't know`<br/>`NA`|`999 = Missing`|
| **Description** |  |  |  |


```{r localc w3, echo=F}

vbl <- MHAS_w3$i29_1_12
vbl_miss <- c(8888,9999)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'i29_1_12')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3,!vbl %in% vbl_miss), aes(i29_1_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$i29_2_12
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'i29_2_12')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3,!vbl %in% vbl_miss), aes(i29_2_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$ybirth
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ybirth')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3,!vbl %in% vbl_miss), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `retired` from the study-specific variable it has to be recoded as follows:

* `keep up i26_2_12`
* `i28_09_12 == 1 into 1`
* `i16_12 == 1,2 into 0`
* `i26_8_12 == 1 into 995`
* `i26_9_12 == 1 into 998`
* `NA into 999`

To compute `age_retired` from the study-specific variable it has to be recoded as follows:

* `if retired == 1, age_retired = i29_1_12 - ybirth`
* `if retired == 0 or i28_09_12 == 0, age_retired = 996`
* `8,88,8888 into 995`
* `9,99,9999 into 998`


**R script:**

```{r harmo w3}

# Categorical variable harmonization
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$retired <- car::recode(MHAS_w3$i26_2_12, "NA=999")
MHAS_ds_w3$retired[which(MHAS_w3$i26_8_12==1)] <- 995
MHAS_ds_w3$retired[which(MHAS_w3$i26_9_12==1)] <- 998
MHAS_ds_w3$retired[which(MHAS_w3$i28_09_12==1)] <- 1
MHAS_ds_w3$retired[which(MHAS_w3$i16_12 %in% c(1,2))] <- 0


MHAS_w3 <- left_join(MHAS_w3,MHAS_ds_w2,by="id")
MHAS_w3 <- left_join(MHAS_w3,MHAS_ds_w1,by="id",suffix=c("_w2","_w1"))
# Continuous variable harmonization
MHAS_ds_w3$age_retired <- rep(999,length(MHAS_ds_w3$id))
MHAS_ds_w3$age_retired[which(MHAS_w3$i16_12==8 | MHAS_w3$i26_8_12==1 | MHAS_w3$i28_88_12==1 | MHAS_w3$i29_1_12==8888)] <- 995
MHAS_ds_w3$age_retired[which(MHAS_w3$i16_12==9 | MHAS_w3$i26_9_12==1 | MHAS_w3$i28_99_12==1 | MHAS_w3$i29_1_12==9999)] <- 998
# Age of retirement computed from variable i29_1_12 (In what year did you leave your last job)
MHAS_ds_w3$age_retired[which(MHAS_w3$ybirth!=999 & !MHAS_w3$i29_1_12 %in% c(8888,9999) & MHAS_ds_w3$retired==1 & MHAS_w3$i28_09_12==1 & MHAS_w3$i29_1_12>=1950)] <- MHAS_w3$i29_1_12[which(MHAS_w3$ybirth!=999 & !MHAS_w3$i29_1_12 %in% c(8888,9999) & MHAS_ds_w3$retired==1 & MHAS_w3$i28_09_12==1 & MHAS_w3$i29_1_12>=1950)] - MHAS_w3$ybirth[which(MHAS_w3$ybirth!=999 & !MHAS_w3$i29_1_12 %in% c(8888,9999) & MHAS_ds_w3$retired==1 & MHAS_w3$i28_09_12==1 & MHAS_w3$i29_1_12>=1950)]
# Age of retirement computed from variable i29_2_12 (How many years ago did you leave your last job)
MHAS_ds_w3$age_retired[which(MHAS_ds_w3$retired==1 & MHAS_ds_w3$age_retired %in% miss_values_vector & MHAS_w3$ybirth!=999 & !MHAS_w3$i29_2_12 %in% c(88,99))] <- (2012 - MHAS_w3$i29_2_12[which(MHAS_ds_w3$retired==1 & MHAS_ds_w3$age_retired %in% miss_values_vector & MHAS_w3$ybirth!=999 & !MHAS_w3$i29_2_12 %in% c(88,99))]) - MHAS_w3$ybirth[which(MHAS_ds_w3$retired==1 & MHAS_ds_w3$age_retired %in% miss_values_vector & MHAS_w3$ybirth!=999 & !MHAS_w3$i29_2_12 %in% c(88,99))]
# Age of retirement obtained in wave 2
MHAS_ds_w3$age_retired[which(MHAS_ds_w3$retired==1 & !is.na(MHAS_w3$age_retired_w2) & !MHAS_w3$age_retired_w2 %in% miss_values_vector)] <- MHAS_w3$age_retired_w2[which(MHAS_ds_w3$retired==1 & !is.na(MHAS_w3$age_retired_w2) & !MHAS_w3$age_retired_w2 %in% miss_values_vector)]
# Age of retirement obtained in wave 1
MHAS_ds_w3$age_retired[which(MHAS_ds_w3$retired==1 & !is.na(MHAS_w3$age_retired_w1) & !MHAS_w3$age_retired_w1 %in% miss_values_vector)] <- MHAS_w3$age_retired_w1[which(MHAS_ds_w3$retired==1 & !is.na(MHAS_w3$age_retired_w1) & !MHAS_w3$age_retired_w1 %in% miss_values_vector)]
# Missing/Non applicable ages
MHAS_ds_w3$age_retired[which(MHAS_ds_w3$age_retired<=0)] <- 999
MHAS_ds_w3$age_retired[which(MHAS_w3$i28_09_12==0)] <- 996
MHAS_ds_w3$age_retired[which(MHAS_ds_w3$retired==0)] <- 996


```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$retired
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(retired))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w3$age_retired
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(MHAS_ds_w3,!vbl %in% miss_values_vector), aes(age_retired)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}

l.hds <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)


for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label", names(l.hds))
kable(t.hds)


dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","retired")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","retired")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste0(v.dbb,dbb[,ind+1])
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```



# Quality estimation

* In wave 1 only answers one member for each household.
* There are some trajectories with no sense (individuals answering first that they are retired and later that they do not). We do not impute them beacuse of lack of knwoledge of the cause.

```{r strange, eval=F, include=F}

cols_vec <- c("id","i16_12","i26_2_12","i28_09_12","i29_1_12","i29_2_12")
kable(MHAS_w2[which(MHAS_w2$id %in% dbb$id[which(dbb$w2==1 & dbb$w3==0 & dbb$w1==0)]),],align = 'c',caption = 'Individuals with trajectory 010 in wave 2')
kable(MHAS_w3[which(MHAS_w3$id %in% dbb$id[which(dbb$w2==1 & dbb$w3==0 & dbb$w1==0)]),cols_vec],align = 'c',caption = 'Individuals with trajectory 010 in wave 3')
kable(MHAS_w3[which(MHAS_w3$id %in% dbb$id[which(dbb$w2==1 & dbb$w3==0 & dbb$w1==1)]),cols_vec],align = 'c',caption = 'Individuals with trajectory 110 in wave 3')
kable(MHAS_w2[which(MHAS_w2$id %in% dbb$id[which(dbb$w2==1 & dbb$w3==0 & is.na(dbb$w1))]),],align = 'c',caption = 'Individuals with trajectory NA10 in wave 2')
kable(MHAS_w3[which(MHAS_w3$id %in% dbb$id[which(dbb$w2==1 & dbb$w3==0 & is.na(dbb$w1))]),cols_vec],align = 'c',caption = 'Individuals with trajectory NA10 in wave 3')
kable(MHAS_w1[which(MHAS_w1$id %in% dbb$id[which(dbb$w2==0 & dbb$w3==0 & dbb$w1==1)]),],align = 'c',caption = 'Individuals with trajectory 100 in wave 1')
kable(MHAS_w2[which(MHAS_w2$id %in% dbb$id[which(dbb$w2==0 & dbb$w3==0 & dbb$w1==1)]),],align = 'c',caption = 'Individuals with trajectory 100 in wave 2')
kable(MHAS_w1[which(MHAS_w1$id %in% dbb$id[which(dbb$w2==0 & dbb$w3==1 & dbb$w1==1)]),],align = 'c',caption = 'Individuals with trajectory 101 in wave 1')
kable(MHAS_w2[which(MHAS_w2$id %in% dbb$id[which(dbb$w2==0 & dbb$w3==1 & dbb$w1==1)]),],align = 'c',caption = 'Individuals with trajectory 101 in wave 2')
kable(MHAS_w1[which(MHAS_w1$id %in% dbb$id[which(is.na(dbb$w2) & dbb$w3==0 & dbb$w1==1)]),],align = 'c',caption = 'Individuals with trajectory 1NA0 in wave 1')
kable(MHAS_w3[which(MHAS_w3$id %in% dbb$id[which(is.na(dbb$w2) & dbb$w3==0 & dbb$w1==1)]),cols_vec],align = 'c',caption = 'Individuals with trajectory 1NA0 in wave 3')


```




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  retired <- l.hds[[index]]
  save(retired, file = paste0(datafolder,names(l.hds)[index],"/retired.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





