---
title: "Day of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 

```{r lab, echo=FALSE}
ds_label <- "Day of birth"
```



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `dbirth`
* Variable label: `day of birth`
* Variable description: `Day of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `a1_1` |
|----------|------------|
| **Label** | `Day of birth` |
| **Table name** | `MHAS-2001` |
| **Missings** | `99 = Don't know` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_dbith','Mexican Health Aging Study.MHAS-2001',
                         variables=list('a1_1'), missings = TRUE)
MHAS_w1_dbith <- opal.execute(o,'MHAS_w1_dbith')
```

```{r local1, echo=F}
vari <- MHAS_w1_dbith$a1_1
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
ggplot(MHAS_w1_dbith, aes(a1_1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(0,33)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 99 "Don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_dbith$id)
MHAS_ds_w1$dbirth <- car::recode(MHAS_w1_dbith$a1_1, "NA=999; 99=998")
MHAS_ds_w1$dbirth <- labelled(MHAS_ds_w1$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
dbirth <- MHAS_ds_w1
save(dbirth, file = "../RData/w1/dbirth.RData")
rm(dbirth)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$dbirth <- car::recode(MHAS_m_ds_w1$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `a1_1` |
|----------|------------|
| **Label** | `Day of birth` |
| **Table name** | `MHAS-2001` |
| **Missings** | `99 = Don't know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_dbith','Mexican Health Aging Study.MHAS-2001',
                         variables=list('a1_1'), missings = TRUE)
opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',
                         variables=list('cunicah'), missings = TRUE)
MHAS_w1_dbith <- opal.execute(o,'MHAS_w1_dbith')
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')
```

```{r local2, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], a1_1=as.numeric(new_2[,2]))
  new_22
}

MHAS_w2_dbith <- Add_indiv(old = MHAS_w1_dbith, new = MHAS_w2_id)

vari <- MHAS_w2_dbith$a1_1
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
ggplot(MHAS_w2_dbith, aes(a1_1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(0,33)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 99 "Don't know" into 998`
* `NA into 999`
 

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_dbith$id)
MHAS_ds_w2$dbirth <- car::recode(MHAS_w2_dbith$a1_1, "NA=999; 99=998")
MHAS_ds_w2$dbirth <- labelled(MHAS_ds_w2$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
dbirth <- MHAS_ds_w2
save(dbirth, file = "../RData/w2/dbirth.RData")
rm(dbirth)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$dbirth <- car::recode(MHAS_m_ds_w2$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```








### Wave 3 

#### Study-specific variable description

| **Name** | `a1_1` |
|----------|------------|
| **Label** | `Day of birth` |
| **Table name** | `MHAS-2001` |
| **Missings** | `99 = Don't know` |
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_dbith','Mexican Health Aging Study.MHAS-2001',
                         variables=list('a1_1'), missings = TRUE)
opal.assign.table.tibble(o, 'MHAS_w3_id','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('cunicah'), missings = TRUE)
MHAS_w1_dbith <- opal.execute(o,'MHAS_w1_dbith')
MHAS_w3_id <- opal.execute(o,'MHAS_w3_id')
```

```{r local3, echo=F}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], a1_1=as.numeric(new_2[,2]))
  new_22
}

MHAS_w3_dbith <- Add_indiv(old = MHAS_w1_dbith, new = MHAS_w3_id)

vari <- MHAS_w3_dbith$a1_1
kable(Continuous_summary(var = vari, missing_values = c(99))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(99))$summary, caption = "Summary")
ggplot(MHAS_w3_dbith, aes(a1_1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(0,33)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 99 "Don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_dbith$id)
MHAS_ds_w3$dbirth <- car::recode(MHAS_w3_dbith$a1_1, "NA=999; 99=998")
MHAS_ds_w3$dbirth <- labelled(MHAS_ds_w3$dbirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$dbirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(dbirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

#### Validation
```{r crosstabulation3, echo=F}
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
dbirth <- MHAS_ds_w3
save(dbirth, file = "../RData/w3/dbirth.RData")
rm(dbirth)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$dbirth <- car::recode(MHAS_m_ds_w3$dbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
