---
title: "Month of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mbirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mbirthDS.R')
```


# Data process

```{r global_assign, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('a1_2'), missings = TRUE)
MHAS_w1 <- opal.execute(o,'MHAS_w1')

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('aa2_2'), missings = TRUE)
MHAS_w2 <- opal.execute(o,'MHAS_w2')
MHAS <- full_join(MHAS_w1,MHAS_w2, by="id")
MHAS_w2 <- left_join(MHAS_w2,MHAS_w1,by="id")

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('aa2_2_12','a2a2_2_12','a2a1_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
MHAS_w3 <- left_join(MHAS_w3,MHAS,by="id")

```


We harmonise all waves together to make possible correct the data given in the first waves with the given later. The harmonisation algorithms of each wave are described in the corresponding paragraphs.

```{r global_harmo}

MHAS_w1$mbirth <- car::recode(MHAS_w1$a1_2, "NA=999; 99=998")

MHAS_w2$mbirth <- car::recode(MHAS_w2$a1_2, "NA=999; 99=998")
MHAS_w2$mbirth[which(MHAS_w2$mbirth %in% miss_values_vector)] <- car::recode(MHAS_w2$aa2_2[which(MHAS_w2$mbirth %in% miss_values_vector)],"NA=999; 99=998")

MHAS_w3$mbirth <- car::recode(MHAS_w3$aa2_2_12, "NA=999; 99=998")
MHAS_w3$mbirth[which(MHAS_w3$mbirth %in% miss_values_vector)] <- car::recode(MHAS_w3$a1_2[which(MHAS_w3$mbirth %in% miss_values_vector)],"NA=999; 99=998")
MHAS_w3$mbirth[which(MHAS_w3$mbirth %in% miss_values_vector)] <- car::recode(MHAS_w3$aa2_2[which(MHAS_w3$mbirth %in% miss_values_vector)],"NA=999; 99=998")
MHAS_w3$mbirth[which((MHAS_w3$a2a1_12==2 & MHAS_w3$a2a2_2_12 %in% 1:12) | (is.na(MHAS_w3$a1_2) & is.na(MHAS_w3$aa2_2) & is.na(MHAS_w3$aa2_2_12)))] <- car::recode(MHAS_w3$a2a2_2_12[which((MHAS_w3$a2a1_12==2 & MHAS_w3$a2a2_2_12 %in% 1:12) | (is.na(MHAS_w3$a1_2) & is.na(MHAS_w3$aa2_2) & is.na(MHAS_w3$aa2_2_12)))],"NA=999; 99=998; 88=997")


```


## Mexico


### Wave 1 

#### Study-specific variable description

| **Name** | `a1_2` |`a2a1_12`|`a2a2_2_12`|
|----------|------|-|-----|
| **Label** | `Month of birth` |`Respondent's original stated birthday correct`|`Correct month of birth`|
| **Table name** | `MHAS-2001` |`MHAS_2012_new`|`MHAS_2012_new`|
| **Categories** |`continuous`|`1 = Yes`<br/>`2 = No`|`continuous`|
| **Missings** | `99 = Don't know` |`NA`|`88 = RF`<br/>`99 = DK`<br/>`NA`|
| **Description** |  |  |  |


```{r assign1, echo=F}
```

```{r local1, echo=F}

vari <- MHAS_w1$a1_2
kable(Categorical_summary(vari, missing_values = c(99))[3], caption = "a1_2") 
kable(Categorical_summary(vari, missing_values = c(99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99))[2], caption = "Type of missing")
ggplot(MHAS_w1, aes(x=factor(a1_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

```

```{r cat1, echo=F}

cat("The other variables descriptions are shown in wave 3 section.")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable `a1_2`. Further:

* `recode 99 "Don't know" into 998`
* `NA into 999`
* `if a2a1_12 == 2, into a2a2_2_12`

**R script:**

```{r harmo1}

MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
auxw1 <- left_join(MHAS_w1[,c("id","mbirth")],MHAS_w3[,c("id","mbirth")],by="id", suffix = c("","_w3"))
auxw1$mbirth[which(!auxw1$mbirth_w3 %in% miss_values_vector & !is.na(auxw1$mbirth_w3))] <- auxw1$mbirth_w3[which(!auxw1$mbirth_w3 %in% miss_values_vector & !is.na(auxw1$mbirth_w3))]
MHAS_ds_w1$mbirth <- car::recode(auxw1$mbirth,"NA=999")
rm(auxw1)

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
mbirth <- MHAS_ds_w1
save(mbirth, file = "../RData/w1/mbirth.RData")
rm(mbirth)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$mbirth <- car::recode(MHAS_m_ds_w1$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```








### Wave 2 

#### Study-specific variable description

| **Name** | `a1_2` |`a2a1_12`|`a2a2_2_12`|`aa2_2`|
|----------|---|---|-|-----|
| **Label** | `Month of birth` |`Respondent's original stated birthday correct`|`Correct month of birth`|`DOB - month`|
| **Table name** | `MHAS-2001` |`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2003`|
| **Categories** |`continuous`|`1 = Yes`<br/>`2 = No`|`continuous`|`continuous`|
| **Missings** | `99 = Don't know` |`NA`|`88 = RF`<br/>`99 = DK`<br/>`NA`| `99 = Don't know`<br/>`NA` |
| **Description** |  |  |  |  |




```{r assign2, echo=F}

```

```{r local2, echo=F}

vari <- MHAS_w2$a1_2
vbl_miss <- c(99)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "a1_2") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(filter(MHAS_w2,!vari %in% vbl_miss), aes(x=factor(a1_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")

vari <- MHAS_w2$aa2_2
vbl_miss <- c(99)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "aa2_2") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(filter(MHAS_w2,!vari %in% vbl_miss), aes(x=factor(aa2_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

```{r cat2, echo=F}

cat("The other variables descriptions are shown in wave 3 section.")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `aa2_2` merged with `a1_2`. Further:

* `recode 99 "Don't know" into 998`
* `NA into 999`
* `if a2a1_12 == 2, into a2a2_2_12`

**R script:**

```{r harmo2}

MHAS_ds_w2 <- tibble(id=MHAS_w2$id)

auxw2 <- left_join(MHAS_w2[,c("id","mbirth")],MHAS_w3[,c("id","mbirth")],by="id", suffix = c("","_w3"))
auxw2$mbirth[which(!auxw2$mbirth_w3 %in% miss_values_vector & !is.na(auxw2$mbirth_w3))] <- auxw2$mbirth_w3[which(!auxw2$mbirth_w3 %in% miss_values_vector & !is.na(auxw2$mbirth_w3))]
MHAS_ds_w2$mbirth <- car::recode(auxw2$mbirth,"NA=999")
rm(auxw2)

```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
mbirth <- MHAS_ds_w2
save(mbirth, file = "../RData/w2/mbirth.RData")
rm(mbirth)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$mbirth <- car::recode(MHAS_m_ds_w2$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

| **Name** | `a1_2` |`a2a1_12`|`a2a2_2_12`|`aa2_2`|`aa2_2_12`|
|------|----|---|---|-|-----|
| **Label** | `Month of birth` |`Respondent's original stated birthday correct`|`Correct month of birth`|`DOB - month`|`Month of birth`|
| **Table name** | `MHAS-2001` |`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2003`|`MHAS_2012_new`|
| **Categories** |`continuous`|`1 = Yes`<br/>`2 = No`|`continuous`|`continuous`|`continuous`|
| **Missings** | `99 = Don't know` |`NA`|`88 = RF`<br/>`99 = DK`<br/>`NA`| `99 = Don't know`<br/>`NA` |`99 = Don't know`<br/>`NA` |
| **Description** |  |  |  |  |  |





```{r assign3, echo=F}
```

```{r local3, echo=F}

vari <- MHAS_w3$a2a1_12
vbl_miss <- NA
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "a2a1_12") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(filter(MHAS_w3,!vari %in% vbl_miss), aes(x=factor(a2a1_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3$aa2_2_12
vbl_miss <- c(99)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "aa2_2_12") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(filter(MHAS_w3,!vari %in% vbl_miss), aes(x=factor(aa2_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3$a2a2_2_12
vbl_miss <- c(88,99)
kable(Categorical_summary(vari, missing_values = vbl_miss)[3], caption = "a2a2_2_12") 
kable(Categorical_summary(vari, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(filter(MHAS_w3,!vari %in% vbl_miss), aes(x=factor(a2a2_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

```{r cat3, echo=F}

cat("The other variables descriptions are shown in for waves 1 and 2")

```

#### Harmonisation algorithm
The harmonised variable is the same than the study-specific variable `aa2_2_12` merged with `a1_2` and `aa2_2`. Further:

* `recode 99 "Don't know" into 998`
* `NA into 999`
* `if a2a1_12 == 2, mbirth into a2a2_2_12`

**R script:**

```{r harmo3}

MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$mbirth <- MHAS_w3$mbirth

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$mbirth
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(mbirth))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
mbirth <- MHAS_ds_w3
save(mbirth, file = "../RData/w3/mbirth.RData")
rm(mbirth)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$mbirth <- car::recode(MHAS_m_ds_w3$mbirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r summ, echo=F}

MHAS.cw <- list(w1 = "w1", w2 = "w2", w3 = "w3")

# Consider only harmonised waves
l.hds <- lapply(MHAS.cw, function(wname) if(exists(paste0("MHAS_ds_",wname))){wname = get(paste0("MHAS_ds_",wname))})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}


m.hds <- list()

# Labelling of the tibbles and creating new tibbles with all missings recodified as NA

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("MHAS_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds,caption=ds_label)


```





# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
