---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `edad` |
|-|-|
| **Label** | `Respondent's Age` |
| **Table name** | `MHAS-2001` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_age','Mexican Health Aging Study.MHAS-2001',
                         variables=list('edad'), missings = TRUE)
```

```{r local1, echo=F}
MHAS_w1_age <- opal.execute(o,'MHAS_w1_age')
vari <- MHAS_w1_age$edad
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "edad")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_w1_age, aes(edad)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_age$id)
MHAS_ds_w1$age <- car::recode(MHAS_w1_age$edad, "NA=999")
MHAS_ds_w1$age <- labelled(MHAS_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```







### Wave 2 

#### Study-specific variable description

| **Name** | `a2` |`living_status`|`mbirth`|`ybirth`|`mintw`|`yintw`|
|-|-|-|-|-|-|-|
| **Label** | `Respondent's Age` |`Living status`|`Month of birth`|`Year of birth`|`Month of interview`|`Year of interview`|
| **Table name** | `MHAS-2003` |`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `888 = Doesn't Answer; 999 = Doesn't Know` |  |`998 = Do not know`<br/>`999 = Missing`|`998 = Do not know`<br/>`999 = Missing`|  |`999 = Missing`|
| **Description** |  |  |  |  |  |  |


```{r assign2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2_age','Mexican Health Aging Study.MHAS_2003', variables=list('a2'), missings = TRUE)
MHAS_w2_age <- opal.execute(o,'MHAS_w2_age')

load(paste0(datafolder,"w2/living_status",".RData"))
MHAS_w2_age <- left_join(MHAS_w2_age,living_status, by = "id")
rm(living_status)


load(paste0(datafolder,"w2/mbirth",".RData"))
MHAS_w2_age <- left_join(MHAS_w2_age,mbirth, by = "id")
rm(mbirth)

load(paste0(datafolder,"w2/ybirth",".RData"))
MHAS_w2_age <- left_join(MHAS_w2_age,ybirth, by = "id")
rm(ybirth)

load(paste0(datafolder,"w2/mintw",".RData"))
MHAS_w2_age <- left_join(MHAS_w2_age,mintw, by = "id")
rm(mintw)

load(paste0(datafolder,"w2/yintw",".RData"))
MHAS_w2_age <- left_join(MHAS_w2_age,yintw, by = "id")
rm(yintw)

```

```{r local2, echo=F}

vari <- MHAS_w2_age$a2
kable(Continuous_summary(vari, missing_values = c(888,999))[3], caption = "a2")
pander(Continuous_summary(vari, missing_values = c(888,999))$summary, caption = "Summary")
ggplot(MHAS_w2_age, aes(a2)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(20,115)

vari <- MHAS_w2_age$living_status
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w2_age$mbirth
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mbirth")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2_age, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w2_age$ybirth
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w2_age, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w2_age$mintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2_age, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w2_age$yintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2_age, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `a2`, but the missing values have to be recoded as follows:

* `recode 888 'Doesn't Answer' as 995`
* `recode 999 'Doesn't Know' as 998`
* `NA into 999`
* `age (wave 2) = date of interview of wave 2 - date of birth`
* `living_status == Dead or Dropout into 996`

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_age$id)
MHAS_ds_w2$age <- car::recode(MHAS_w2_age$a2, "888=995; 999=998; NA=999")




#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

cage <- comp_age(y_birth=MHAS_w2_age$ybirth, m_birth=MHAS_w2_age$mbirth , a_year=MHAS_w2_age$yintw, a_month=MHAS_w2_age$mintw, miss=miss_values_vector)
MHAS_ds_w2$age[which(MHAS_ds_w2$age %in% miss_values_vector & !cage %in% miss_values_vector)] <- cage[which(MHAS_ds_w2$age %in% miss_values_vector & !cage %in% miss_values_vector)]

MHAS_ds_w2$age[which(MHAS_w2_age$living_status %in% c(1,2))] <- 996
MHAS_ds_w2$age <- labelled(MHAS_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(20,115)
```

#### Validation
```{r crosstabulation2, echo=F}
```






### Wave 3 

#### Study-specific variable description

| **Name** | `age_12` |`living_status`|`mbirth`|`ybirth`|`mintw`|`yintw`|
|-|-|-|-|-|-|-|
| **Label** | `Age` |`Living status`|`Month of birth`|`Year of birth`|`Month of interview`|`Year of interview`|
| **Table name** | `MHAS_2012_new` |`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|`continuous`|`continuous`|`continuous`|`continuous`|
| **Missings** | `999 = Doesn't Know` |  |`998 = Do not know`<br/>`999 = Missing`|`998 = Do not know`<br/>`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_age','Mexican Health Aging Study.MHAS_2012_new',variables=list('age_12'), missings = TRUE)
MHAS_w3_age <- opal.execute(o,'MHAS_w3_age')

load(paste0(datafolder,"w3/living_status",".RData"))
MHAS_w3_age <- left_join(MHAS_w3_age,living_status, by = "id")
rm(living_status)


load(paste0(datafolder,"w3/mbirth",".RData"))
MHAS_w3_age <- left_join(MHAS_w3_age,mbirth, by = "id")
rm(mbirth)

load(paste0(datafolder,"w3/ybirth",".RData"))
MHAS_w3_age <- left_join(MHAS_w3_age,ybirth, by = "id")
rm(ybirth)

load(paste0(datafolder,"w3/mintw",".RData"))
MHAS_w3_age <- left_join(MHAS_w3_age,mintw, by = "id")
rm(mintw)

load(paste0(datafolder,"w3/yintw",".RData"))
MHAS_w3_age <- left_join(MHAS_w3_age,yintw, by = "id")
rm(yintw)

```

```{r local3, echo=F}
vari <- MHAS_w3_age$age_12
kable(Continuous_summary(vari, missing_values = c(999))[3], caption = "age_12")
pander(Continuous_summary(vari, missing_values = c(999))$summary, caption = "Summary")
ggplot(MHAS_w3_age, aes(age_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(25,115)

vari <- MHAS_w3_age$living_status
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "living_status")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3_age$mbirth
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mbirth")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3_age, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3_age$ybirth
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w3_age, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3_age$mintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3_age, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS_w3_age$yintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3_age, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable `age_12`, but the missing values have to be recoded as follows:

* `recode 999 'Doesn't Know' as 998`
* `NA into 999`
* `age (wave 3) = date of interview of wave 3 - date of birth`
* `living_status == Dead or Dropout into 996`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_age$id)
MHAS_ds_w3$age <- car::recode(MHAS_w3_age$age_12, "999=998; NA=999")



#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>900)] <- a_year[which(m_birth>900)]-y_birth[which(m_birth>900)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

cage <- comp_age(y_birth=MHAS_w3_age$ybirth, m_birth=MHAS_w3_age$mbirth , a_year=MHAS_w3_age$yintw, a_month=MHAS_w3_age$mintw, miss=miss_values_vector)
MHAS_ds_w3$age[which(MHAS_ds_w3$age %in% miss_values_vector & !cage %in% miss_values_vector)] <- cage[which(MHAS_ds_w3$age %in% miss_values_vector & !cage %in% miss_values_vector)]


MHAS_ds_w3$age[which(MHAS_w3_age$living_status %in% c(1,2))] <- 996
MHAS_ds_w3$age <- labelled(MHAS_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(25,115)
```

#### Validation
```{r crosstabulation3, echo=F}
```










## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation
No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
