---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```

# Data process



**Functions**

```{r}


#function to compute the age
comp_age <- function(y_birth, m_birth, a_year, a_month, miss = miss_values_vector){
  N <- length(y_birth)
  #first, it's computed the age of all
  age <- rep(NA,N)
  age[which(a_month<m_birth)] <- (a_year[which(a_month<m_birth)]-y_birth[which(a_month<m_birth)])-1
  age[which(a_month>=m_birth)] <- a_year[which(a_month>=m_birth)]-y_birth[which(a_month>=m_birth)]
  age[which(m_birth>12)] <- a_year[which(m_birth>12)]-y_birth[which(m_birth>12)]
  
  #It's emphasized the individues having missing
  
  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(y_birth==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]

  mis <- rep(0,N)
  for(i in 1:length(miss)){
    mis[which(a_year==miss[i])] <- miss[i]
  }
  age[which(mis!=0)] <- mis[which(mis!=0)]
  
  
  age

}

```


## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `ybirth` |`mbirth`|`yintw`|`mintw`|
|-|-|-|-|-|
| **Label** | `Year of birth` | `Month of birth` |`Year of interview`|`Month of interview`|
| **Table name** | `mhas_w1_hd` |`mhas_w1_hd` | `mhas_w1_hd` |`mhas_w1_hd` |
| **Missings** |  |`998 = Do not know`|  |  |
| **Description** |  |  |  |  |


```{r assign1, echo=F}

load(paste0(datafolder,"w1/yintw",".RData"))
load(paste0(datafolder,"w1/ybirth",".RData"))
load(paste0(datafolder,"w1/mintw",".RData"))
load(paste0(datafolder,"w1/mbirth",".RData"))
MHAS <- left_join(yintw,ybirth, by="id")
MHAS <- left_join(MHAS,mintw, by="id")
MHAS <- left_join(MHAS,mbirth, by="id")
rm(yintw)
rm(ybirth)
rm(mintw)
rm(mbirth)

```

```{r local1, echo=F}

vari <- MHAS$ybirth
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mbirth
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mbirth")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$yintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is :

* `date of interview - date of birth`

**R script:**

```{r harmo1}

MHAS_ds_w1 <- tibble(id=MHAS$id)
MHAS_ds_w1$age <- comp_age(MHAS$ybirth,MHAS$mbirth,MHAS$yintw,MHAS$mintw)
rm(MHAS)

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}

```







### Wave 2 

#### Study-specific variable description

| **Name** | `ybirth` |`mbirth`|`yintw`|`mintw`|
|-|-|-|-|-|
| **Label** | `Year of birth` | `Month of birth` |`Year of interview`|`Month of interview`|
| **Table name** | `mhas_w2_hd` |`mhas_w2_hd` | `mhas_w2_hd` |`mhas_w2_hd` |
| **Missings** |`998 = Do not know`<br/>`999 = Missing`|`998 = Do not know`<br/>`999 = Missing`|  |  |
| **Description** |  |  |  |  |


```{r assign2, echo=F}

load(paste0(datafolder,"w2/yintw",".RData"))
load(paste0(datafolder,"w2/ybirth",".RData"))
load(paste0(datafolder,"w2/mintw",".RData"))
load(paste0(datafolder,"w2/mbirth",".RData"))
MHAS <- left_join(yintw,ybirth, by="id")
MHAS <- left_join(MHAS,mintw, by="id")
MHAS <- left_join(MHAS,mbirth, by="id")
rm(yintw)
rm(ybirth)
rm(mintw)
rm(mbirth)

```

```{r local2, echo=F}

vari <- MHAS$ybirth
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mbirth
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mbirth")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$yintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is :

* `date of interview - date of birth`

**R script:**

```{r harmo2}

MHAS_ds_w2 <- tibble(id=MHAS$id)
MHAS_ds_w2$age <- comp_age(MHAS$ybirth,MHAS$mbirth,MHAS$yintw,MHAS$mintw)
rm(MHAS)

```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation2, echo=F}



```





### Wave 3 

#### Study-specific variable description

| **Name** | `ybirth` |`mbirth`|`yintw`|`mintw`|
|-|-|-|-|-|
| **Label** | `Year of birth` | `Month of birth` |`Year of interview`|`Month of interview`|
| **Table name** | `mhas_w3_hd` |`mhas_w3_hd` | `mhas_w3_hd` |`mhas_w3_hd` |
| **Missings** |`998 = Do not know`<br/>`999 = Missing`|`998 = Do not know`<br/>`999 = Missing`|  |`999 = Missing`|
| **Description** |  |  |  |  |



```{r assign3, echo=F}

load(paste0(datafolder,"w3/yintw",".RData"))
load(paste0(datafolder,"w3/ybirth",".RData"))
load(paste0(datafolder,"w3/mintw",".RData"))
load(paste0(datafolder,"w3/mbirth",".RData"))
MHAS <- left_join(yintw,ybirth, by="id")
MHAS <- left_join(MHAS,mintw, by="id")
MHAS <- left_join(MHAS,mbirth, by="id")
rm(yintw)
rm(ybirth)
rm(mintw)
rm(mbirth)

```

```{r local3, echo=F}

vari <- MHAS$ybirth
kable(Continuous_summary(vari, missing_values = miss_values_vector)[3], caption = "ybirth")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mbirth
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mbirth")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mbirth))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$yintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "yintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(yintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- MHAS$mintw
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = "mintw")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS, aes(x=factor(mintw))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is :

* `date of interview - date of birth`

**R script:**

```{r harmo3}


MHAS_ds_w3 <- tibble(id=MHAS$id)
MHAS_ds_w3$age <- comp_age(MHAS$ybirth,MHAS$mbirth,MHAS$yintw,MHAS$mintw)
rm(MHAS)

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vari %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation3, echo=F}


```










## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation

Due to multiple paradoxical data along waves and the fact that year of birth (`ybirth`) was corrected in wave 3 we have decided to harmonise age from harmonised variables on dates of birth and interview, instead of using study-specific variables about age.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
