---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `edad` |
|-|-|
| **Label** | `Respondent's Age` |
| **Table name** | `MHAS-2001` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_age','Mexican Health Aging Study.MHAS-2001',
                         variables=list('edad'), missings = TRUE)
```

```{r local1, echo=F}
MHAS_w1_age <- opal.execute(o,'MHAS_w1_age')
vari <- MHAS_w1_age$edad
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "edad")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_w1_age, aes(edad)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_age$id)
MHAS_ds_w1$age <- car::recode(MHAS_w1_age$edad, "NA=999")
MHAS_ds_w1$age <- labelled(MHAS_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}

#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
age <- MHAS_ds_w1
save(age, file = "../RData/w1/age.RData")
rm(age)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$age <- car::recode(MHAS_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2 

#### Study-specific variable description

| **Name** | `a2` |
|-|-|
| **Label** | `Respondent's Age` |
| **Table name** | `MHAS-2003` |
| **Missings** | `888 = Doesn't Answer; 999 = Doesn't Know` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_age','Mexican Health Aging Study.MHAS_2003',
                         variables=list('a2'), missings = TRUE)
```

```{r local2, echo=F}
MHAS_w2_age <- opal.execute(o,'MHAS_w2_age')
vari <- MHAS_w2_age$a2
kable(Continuous_summary(vari, missing_values = c(888,999))[3], caption = "a2")
pander(Continuous_summary(vari, missing_values = c(888,999))$summary, caption = "Summary")
ggplot(MHAS_w2_age, aes(a2)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(20,115)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 888 'Doesn't Answer' as 995`
* `recode 999 'Doesn't Know' as 998`
* `NA into 999`
 

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_age$id)
MHAS_ds_w2$age <- car::recode(MHAS_w2_age$a2, "888=995; 999=998; NA=999")
MHAS_ds_w2$age <- labelled(MHAS_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(20,115)
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}

#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
age <- MHAS_ds_w2
save(age, file = "../RData/w2/age.RData")
rm(age)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$age <- car::recode(MHAS_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

| **Name** | `age_12` |
|-|-|
| **Label** | `Age` |
| **Table name** | `MHAS_2012_new` |
| **Missings** | `999 = Doesn't Know` |
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_age','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('age_12'), missings = TRUE)
```

```{r local3, echo=F}
MHAS_w3_age <- opal.execute(o,'MHAS_w3_age')
vari <- MHAS_w3_age$age_12
kable(Continuous_summary(vari, missing_values = c(999))[3], caption = "age_12")
pander(Continuous_summary(vari, missing_values = c(999))$summary, caption = "Summary")
ggplot(MHAS_w3_age, aes(age_12)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+xlim(25,115)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode 999 'Doesn't Know' as 998`
* `NA into 999`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_age$id)
MHAS_ds_w3$age <- car::recode(MHAS_w3_age$age_12, "999=998; NA=999")
MHAS_ds_w3$age <- labelled(MHAS_ds_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") +xlim(25,115)
```

#### Validation
```{r crosstabulation3, echo=F}
```





```{r importOPAL3, echo=F}

#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
age <- MHAS_ds_w3
save(age, file = "../RData/w3/age.RData")
rm(age)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$age <- car::recode(MHAS_m_ds_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
