---
title: "Sex"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

```{r lab, echo=FALSE}
ds_label <- "Sex"
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `sex`
* Variable label: `biological sex`
* Variable description: `participant's biological sex`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | female
1        | male

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

 * Name: `sexo`
* Label: `Respondent's sex`
* Categories: 
    + `1 = Man`
    + `2 = Woman`
* Description:

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')
```

```{r local1, echo=FALSE}
vari <- MHAS_w1_sex$sexo
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_sex, aes(x=factor(sexo))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_sex$id)
MHAS_ds_w1$sex <- car::recode(MHAS_w1_sex$sexo, "2=0; NA=999")
MHAS_ds_w1$sex <- labelled(MHAS_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- MHAS_ds_w1$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(MHAS_ds_w1$sex)
BeforeH <- table(MHAS_w1_sex$sexo)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```


```{r importOPAL1, echo=FALSE}
val_labels(MHAS_ds_w1) <- NULL
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
sex <- MHAS_ds_w1
save(sex, file = "../RData/w1/sex.RData")
rm(sex)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$sex <- car::recode(MHAS_m_ds_w1$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

* Name: `sexo`
* Label: `Respondent's sex`
* Categories: 
    + `1 = Man`
    + `2 = Woman`
* Description:   

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',
                         variables=list('cunicah'), missings = TRUE)
```

```{r local2, echo=FALSE}
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')

Same_indiv <- function(W1, W2){
  
  W1_2 <- matrix(rep(NA, dim(W1)[1]*dim(W1)[2] ), nrow = dim(W1)[1])
  W1m <- as.matrix(W1)
  
  for(i in 1:length(W1$id)){
    if(sum(W1$id[i]==W2$id)>=1){
      W1_2[i,] <- W1m[i,]
    } else {
      W1_2[i,] <- W1_2[i,]
    }
  }
  
  W1_22 <- data.frame(id=W1_2[,1], sexo=as.numeric(W1_2[,2]))
  W1_22[-which(is.na(W1_22$id)),]
}


MHAS_w2_sex <- Same_indiv(W1 = MHAS_w1_sex, W2 = MHAS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], sexo=as.numeric(new_2[,2]))
  new_22
}

MHAS_w2_sex <- Add_indiv(old = MHAS_w2_sex, new = MHAS_w2_id)

vari <- MHAS_w2_sex$sexo
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w2_sex, aes(x=factor(sexo))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_sex$id)
MHAS_ds_w2$sex <- car::recode(MHAS_w2_sex$sexo, "2=0; NA=999")
MHAS_ds_w2$sex <- labelled(MHAS_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- MHAS_ds_w2$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(MHAS_w2_sex$sexo, useNA = "ifany")[c(2,1,3)]
AfterH <- table(MHAS_ds_w2$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```


```{r importOPAL2, echo=FALSE}
val_labels(MHAS_ds_w2) <- NULL
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
sex <- MHAS_ds_w2
save(sex, file = "../RData/w2/sex.RData")
rm(sex)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$sex <- car::recode(MHAS_m_ds_w2$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

* Name: `sex_12`
* Label: `Sex (Male=1)`
* Categories: 
    + `1 = Male`
    + `2 = Female`
* Description:

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_sex','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('sex_12'), missings = TRUE)
MHAS_w3_sex <- opal.execute(o,'MHAS_w3_sex')
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], sexo=as.numeric(new_2[,2]))
  new_22
}

MHAS_w3_sex$sex_w1 <- Add_indiv(old = MHAS_w1_sex, new = MHAS_w3_sex)$sexo
MHAS_w3_sex$sex_def <- MHAS_w3_sex$sex_12
MHAS_w3_sex$sex_def[is.na(MHAS_w3_sex$sex_def)] <- MHAS_w3_sex$sex_w1[is.na(MHAS_w3_sex$sex_def)]
```

```{r local3, echo=FALSE}
vari <- MHAS_w3_sex$sex_def
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "Cognition - Immediate recall") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3_sex, aes(x=factor(sex_def))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_sex$id)
MHAS_ds_w3$sex <- car::recode(MHAS_w3_sex$sex_def, "2=0; NA=999")
MHAS_ds_w3$sex <- labelled(MHAS_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- MHAS_ds_w3$sex
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(MHAS_ds_w3$sex)
BeforeH <- c(table(MHAS_w3_sex$sex_def)[c(2,1)], sum(is.na(MHAS_w3_sex$sex_def)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```


```{r importOPAL3, echo=FALSE}
val_labels(MHAS_ds_w3) <- NULL
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
sex <- MHAS_ds_w3
save(sex, file = "../RData/w3/sex.RData")
rm(sex)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$sex <- car::recode(MHAS_m_ds_w3$sex, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```



